### 2022-04-03 forwards-and-backwards.tex
initial draft

\documentclass[12pt]{article}
\usepackage{fullpage}
\usepackage{amssymb}
\usepackage{graphics} 
\usepackage{amsmath}
\usepackage[color=yellow]{todonotes}
\usepackage{url}

\usepackage{xcolor}
\usepackage{longtable}
\usepackage[hidelinks]{hyperref}
\usepackage{bbm}

\usepackage{natbib}

\newenvironment {proof}{{\noindent\bf Proof.}}{\hfill $\Box$ \medskip}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{hypothesis}[theorem]{Hypothesis}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{example}[theorem]{Example}
\newtheorem{definition}[theorem]{Definition}

\renewcommand{\theequation}{\arabic{section}.\arabic{equation}}
\def \non{{\nonumber}}
\def \hat{\widehat}
\def \tilde{\widetilde}
\def \bar{\overline}
\newcommand{\IP}{\mathbb P}
\newcommand{\IQ}{\mathbb Q}
\newcommand{\IE}{\mathbb E}
\newcommand{\IR}{\mathbb R}
\newcommand{\IZ}{\mathbb Z}
\newcommand{\IN}{\mathbb N}
\newcommand{\IT}{\mathbb T}
\newcommand{\IC}{\mathbb C}
\newcommand{\ind}{\mathbf{1}}

\newcommand{\plr}[1]{\todo[inline]{Peter: #1}}
\newcommand{\comment}[1]{{\color{blue} \it #1}}

\begin{document}
\pagenumbering{arabic}

\title{\large{\bf
Looking forwards and backwards through locally regulated populations
}}

% OTHER IDEAS:
% A class of nonlinear superprocesses
% Uncovering genealogical structures of locally regulated populations with lookdown constructions on nonlinear superprocesses

\author{ \begin{small}
\begin{tabular}{ll}                              
Alison M. Etheridge 
 & Thomas G. Kurtz \\   
Department of Statistics & Departments of Mathematics and Statistics\\       
Oxford University & University of Wisconsin - Madison \\                   
24-29 St Giles & 480 Lincoln Drive\\                                                         
Oxford OX1 3LB & Madison, WI  53706-1388\\
UK & USA \\                        
etheridg@stats.ox.ac.uk & kurtz@math.wisc.edu     \\
\url{http://www.stats.ox.ac.uk/~etheridg/} & 
\url{http://www.math.wisc.edu/~kurtz/}  \\       \\
\\
Ian Letter&  Peter L. Ralph 
\\   
Department of Statistics & Department of Mathematics \\
Oxford University &University of Oregon\\                   
24-29 St Giles & Fenton Hall\\
Oxford OX1 3LB & Eugene, OR 97403-1222\\
UK & USA \\
restucci@stats.ox.ac.uk  & plr@oregon.edu \\
\url{https://www.stats.ox.ac.uk/~restucci/}&
\url{https://math.uoregon.edu/profile/plr} \\
\\
Terence Tsui 
 &  \\   
Department of Statistics & \\
Oxford University & \\                   
24-29 St Giles& \\
Oxford OX1 3LB & \\
UK & \\
terence.tsui@sjc.ox.ac.uk &      \\
\url{https://www.maths.ox.ac.uk/people/terence.tsui}&  \\
\end{tabular}
\end{small}}

\date{\today}
\maketitle

\begin{abstract}

We do something...

\vspace{.1in}

\noindent {\bf Key words:}  population model, nonlinear superprocess, 
lookdown construction, porous medium equation, 
reaction-diffusion equation, travelling waves, genealogies,

\vspace{.1in}

\noindent {\bf MSC 20}10 {\bf Subject Classification:}  Primary:  
%60J25, 92D10, 92D15, 92D25 92D40  
\\Secondary:   %60F05, 60G09, 60G55, 60G57, 60H15, 60J68

\end{abstract}
\tableofcontents
\newpage

%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

\todo[inline]{
From Terence: Personally, I think the long discussion on porous medium equations distract readers from the main message of our paper - we demonstrated a way to trace genealogy and derive dynamics of ancestral lineage through lookdown construction. I would suggest trimming most of the discussion there and only leaving discussions relevant to ancestries and lineages.}

There is now a huge literature devoted to spatial branching processes,
including branching random walk, 
branching Brownian motion, and the Dawson-Watanabe superprocesses.  
In addition to possessing a rich and beautiful mathematical structure, 
the superprocesses are remarkable for demonstrating a certain `universality', 
arising, as they do, as scaling limits of a vast array of different 
spatial population models \cite[e.g.,][]{chetwynd-diggle/etheridge:2018,
cox/perkins:2005,
cox/durrett/perkins:1999,
cox/durrett/perkins:2000,
holmes:2008,
vanderhofstad/sakai:2010,
vanderhofstad/slade:2003,
vanderhofstad/holmes/perkins:2017}.

These models make mathematical sense in very general spaces, but
in biological applications, typically, 
individuals are assumed to be scattered across one or two-dimensional
Euclidean space. In that setting, it is well known that, 
in the long term, the population will either 
die out, or it will develop clumps of arbitrary density and extent. 
To counter this, it is common to
impose some local regulation by either increasing death rates, or 
reducing birth rates, in proportion to the local population density,
so that the population has a tendency to grow in sparsely populated regions
and shrink where it is overcrowded. This leads to spatial analogues of  
logistic branching processes.

Although it can be more mathematically convenient to work with branching
Brownian motions, in many settings it is biologically more natural to 
develop models based on branching random walk.  
Individuals produce a random number of offspring,
that are thrown off according to some (usually symmetric) 
distribution centred on the location of the parent.   
This is particularly appropriate for modelling plant populations, in which
this dispersal of offspring around the parent is the only source of
spatial motion.

Most models do not distinguish between juveniles and adults, so,
for example, the number of adults produced by a single parent is determined
by the degree of crowding at the the location of the parent. The novelty
of the models that we introduce here is that, although we shall only
follow the adult population, in formulating the dynamics of the
models we shall distinguish
between production of juveniles, which will depend upon the location of 
the adult, and their successful establishment, which will depend on the
location in which a juvenile lands. The result is that not only the absolute 
number, but also the spatial distribution
around their parent, 
of those offspring that survive to adulthood
will depend upon the local population 
density.

We shall consider different classes of scaling limits for our model; the first class consisting of
(generalised) super-processes limits, and the second class where the limits are deterministic. In the
superprocess setting, for our approach to work we measure the local population
density at a point by integrating against a smooth test function, for example 
a Gaussian density centred on that point.  
When the limit is deterministic,
we can simultaneously reduce the parameter in that Gaussian density so that,
in the limit, the local population density is simply the population density 
at that point. Nonetheless, we retain a signal of our two stage approach
to modelling reproduction, and  
in this way we recover a nonlinear partial differential equation. 
This approach requires some technical conditions that we will verify in two important examples,
the porous medium equation with a logistic growth term of the form 
$$\partial_t \varphi = \Delta (\varphi^2)+\varphi(1-\varphi),$$
and a wide class of semi-linear partial differential equations of the form 
$$\partial_t \varphi = \Delta\varphi+ \varphi \left(G(\varphi)-H(\varphi)\right),$$
which include the Fisher-KPP equation and the Allen-Cahn equation.

The porous medium equation (PME)
is a degenerate nonlinear diffusion equation that
has been the subject of intensive study. We refer to~\cite{vazquez:2007} for 
a comprehensive reference. The equation has also been studied with various
forms of noise, see~\cite{barbu/daprato/roeckner:2016}, although not the 
form of noise that will arise from the population dynamics below. 
Deriving nonlinear diffusion equations as limits of weakly interacting 
diffusions goes back at least to~\cite{mckean:1967}, and this 
programme has been
carried out for the PME and its generalisations. 
The degeneracy of the PME
results in some extra analytic
challenges,~\cite{jourdain:2000}.
Recent work in this 
direction has been spurred on by applications
in mathematical finance, %where the porous medium arises 
in particular, in the study of weak limits of systems
of diffusions interacting through their 
rank,~\cite{dembo/shkolnikov/varadhan/zeitouni:2016, jourdain/reygner:2013}
and references therein.
Our approach is different.
We start from individual
based population models, thus providing a microscopic mechanism that leads to 
nonlinear diffusion.
Other microscopic mechanisms have been proposed in the special case of the
PME, see 
e.g.~\cite{feng/iscoe/seppalainen:1997, oelschlaeger:1990}; ours
is specifically motivated by biological considerations.

The porous medium equation with logistic growth is an example of a
reaction-diffusion equation with a nonlinear diffusion term.
Such equations are widely used in a number of contexts in biology in which
it is clear that motility within a population varies with population density.
For example, density dependent dispersal is a common feature in spatial
models in ecology, eukaryotic cell biology, and avascular tumour growth;
see e.g.~\cite{sherratt:2010} and references therein for further discussion. 
We shall pay particular attention to the case in which the equation can be 
thought of as modelling the density of an expanding population. 
The specific equation that we use to illustrate the implications of
our results is one of a class used to study pattern formation in 
bacterial colonies. In particular, it has been suggested as a model for
the expansion of bacteria of the type {\em Paenbacillus dendritiformis} on
a thin layer of agar in a petri dish, 
\cite{cohen/golding/kozlovsky/benjacob/ron:1999}.

Another novelty of our models stems from the use of lookdown construction to retain the dynamics of lines of descent in our population while passing to a scaling limit. The lookdown construction is first introduced in \cite{donnelly/kurtz:1996} to provide a mechanism to trace lineages while passing through a scaling limit for the Moran model. In more recent works, see~\cite{kurtz/rodrigues:2011, etheridge/kurtz:2018}, lookdown constructions are further applied into models of branching populations with spatial structures. In \S \ref{Sec: Lookdown Constructions}, we follow closely the techniques presented in these papers to impose lookdown constructions for our models which allow us to retain information about ancestry of individuals in the population as we pass to a large population limit. This in turn allows us to write down an explicit expression for the generator of the position of ancestral lineages with respect to the travelling wave fronts for populations modelled by a huge class of semi-linear partial differential equations, see Theorem \ref{teo:ancestral lineages}.
This attempt is novel and we have provided the first ever rigorous proof to similar results on ancestral lineages. This result allows us to compare ancestral lineages of individuals sampled from the front of a population evolving according to the PME with logistic growth to those under the Fisher-KPP and Allen-Cahn equations. For example, as a result of the nonlinear diffusion, 
for suitable initial conditions, the solution to the one-dimensional 
porous medium equation with logistic growth converges to a travelling
wave with a sharp cut-off; i.e., in contrast to the classical 
Fisher KPP equation, the solution at time $t$
vanishes beyond $x=x_0+ct$ for some constant wavespeed
$c>0$, \cite{kamin/rosenau:2004}.

\subsection{More motivation, on lineages, to merge with the above}

The history of a natural population is often only accessible indirectly 
through patterns of genetic diversity that have been laid down. From 
genetic data, one can try to infer the genealogical trees that relate 
individuals in a sample from the population. It is therefore of interest
to establish the distribution of genealogical trees relating individuals
sampled from a population evolving according to any proposed mathematical
model.

In general this is an extremely difficult question. However, in specical
circumstances, some progress can be made. One of the settings that
has received a great deal of attention in recent years is that in which 
a population is expanding into new territory as a travelling wave. 
Typically one considers a stationary wavefront moving across $\IR^1$, and
most work has focussed on the classical Fisher-KPP equation with a 
stochastic term, i.e.
$$dw=\big(\Delta w +sw(1-w)\Big)dt +\sqrt{\frac{\alpha(w)}{N}}W(dt,dx),$$
where $W$ is space-time white noise, and $N$ is a measure of the 
local population density. The coefficient
$\alpha(w)$ is generally taken to be either
$w$, corresponding to a superprocess limit, or $w(1-w)$ giving a 
spatial analogue of a Wright-Fisher diffusion. The first is 
appropriate for modelling the range of an expanding population,
the second for the spread of a selectively advantageous 
mutation through an established (selectively neutral) population. 
Because of the logistic control of the growth rate,
individuals in the wavefront can have much greater reproductive success
than those in the `bulk' of the expanding population. 
Tracing backwards in time, individuals sampled
from behind the wave are `caught' by the wave, upon which they become
trapped in the wavefront. If the population density is very high, then over
suitable timescales, the genealogical trees will be dominated by 
periods of extremely rapid coalescence corresponding to a significant 
proportion of the individuals in the front being descended from a particularly
reproductively successful ancestor. For a surprisingly wide range of models, 
it is believed that, for very large $N$ and on suitable timescales, 
genealogies converge to a 
Bolthausen-Sznitman coalescent, e.g.~\cite{brunet/derrida/mueller/munier:2007}. 
On the other hand, if one replaces the logistic growth term of the classical
Fisher-KPP equation with a nonlinearity that reflects cooperative
behaviour in the population, such as
$$wF(w)=w(1-w)(Cw-1),$$
then, for sufficiently large $C$ (strong cooperation),
the nature of the deterministic
wave changes from `pulled' to `pushed', \cite{birzu/hallatschek/korolev:2017}.
In that setting, the genealogies will also be quite different
from the Fisher-KPP case. For example, \cite{etheridge/penington:2020}
shows that for a discrete space model corresponding to this 
nonlinearity with $C>4$, after suitable scaling, the genealogy of a
sample converges not to a Bolthausen-Sznitman coalescent, but to
a Kingman coalescent. 
\todo[inline]{Is that condition $C>4$ correct? the paper with Sarah is done for the equation $\partial_t u = \Delta u + u(1-u)(2u-1+\alpha)$ and valid for $\alpha \in (0,1)$. Factorising we would get that equation would be $\partial_t u = \Delta u + (1-\alpha) u(1-u)(\frac{2}{1-\alpha}u-1)$. Supposing the $(1-\alpha)$ in front does not affect the result (which I suppose wouldn't) we get that $C= \frac{2}{1-\alpha}$ and so $\alpha \in (0,1)$ if and only if $C>2$ ...}
The reason, roughly, is that ancestral lineages
settle to a stationary distribution relative to the position of the 
wavefront which puts very little weight close to the `tip' of the wave, so
that when ancestral lineages meet,
it is typically in a location where population density is
high, where no single ancestor produces a disproportionately large number of 
descendants in a short space of time.

As a first step towards understanding what we should expect in models with
nonlinear diffusion, we consider the position of an ancestral lineage
relative to the wavefront in the deterministic models, and compare that 
to what we see for a classical Fisher-KPP equation. 
In~\S\ref{sec: wright-malecot}, we then indicate how to extend these ideas to 
extract information about relatedness between two individuals in the 
superprocess limit, at least when population intensity is very high, and
we present some evidence to support the conjecture that genealogies 
for populations expanding according to 
our superprocess models with nonlinear diffusion
can be very different from those under 
the classical Fisher-KPP equation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Model and main results}

\plr{Description of the model:}

\plr{Main results (theorems without lookdowns):}

\comment{
There are two dichotomies:
is the limiting process deterministic or a generalized superprocess?
See Figure \ref{fig:super_vs_det_2d} for simulations.
And, are interactions local in the limit or not?
Below we have results for three of these cases;
as for the remaining one (local, superprocess)
TODO: write a note about what happens there (should be possible in 1D, not in higher dimensions).
}

We shall suppose that we start with a population of
$\mathcal{O}(N)$ individuals per unit area distributed in $\mathbb{R}^d$.
In applications we would typically take $\mathbb{R}^2$ or a subset thereof,
although our mathematical results apply in any spatial dimension.
We shall denote the state of the population at time $t$ by $\mathcal{S}_t$
and we shall abuse notation by treating $(\mathcal{S}_t)_{t \geq 0}$
as both the set of locations of the individuals
and a counting measure in which each individual has mass $1$, 
with the understanding that multiple 
points are treated as distinct individuals.  
The parameter $N$ will tend to infinity in our scaling limits, and the 
measure $(\overline{\eta}_t)_{t \geq 0} := (N^{-1} \mathcal{S}_t)_{t \geq 0} $ will converge (weakly) in the space of 
$\sigma$-finite measures on $\mathbb{R}^d$.

It will be simplest to think of the population as evolving in continuous time
and giving birth to one offspring at a time.
The rate at which a juvenile offspring is produced by an individual
will depend on the local population density.
We will write $\gamma(x,\overline{\eta})$ for the rate at which an
individual at location $x$ produces a juvenile offspring
when the state of the population is $\overline{\eta}$,
and $q(x,dy)$ for the distribution of the location of the juvenile 
when the parent is at $x$.
These offspring do not necessarily survive to be counted in the population:
we write $r(y, \overline{\eta})$ for the 
probability of successful establishment (survival to maturity)
of a juvenile at $y$.
It is assumed that maturity is achieved instantaneously,
and we shall only track mature individuals.
Finally, each mature individual located at the point $x$ dies at 
instantaneous rate $\mu(x,\overline{\eta})$.

\plr{I moved up the description of the interaction kernel here,
    so that the whole description of the model is in one place.
    I think this is good, but: some of our results don't depend on this assumption,
    which we should make more clear here. And: do we always use the heat kernel
    for $\varrho$? If so, we should just say so here.  }
Since we are interested in models where interactions are \emph{local},
i.e., reproduction, establishment, and death depend only
on the geographically local environment.
To this end,
we suppose that the birth rate of an individual at $x$
depends on the state of the population only through
a locally averaged density.
Concretely,
given an \emph{interaction distance} $\varepsilon$,
and a probability density $\varrho$ (the \emph{interaction kernel})
we will suppose that
$\gamma(x, \overline{\eta})$, $r(x, \overline{\eta})$, and $\mu(x, \overline{\eta})$
are functions only of $x$ and
\begin{align*}
    \varrho_\varepsilon * \overline{\eta}(x)
    := \int \varepsilon^{-d} \varrho(x/\varepsilon)(x-y) \overline \eta(dy)
    .
\end{align*}
To make the notation less complex, however,
we'll not formalize this until later (\S~\ref{sec: Main Theorems on Convergence}).

\begin{remark}
This model can be easily generalised into one
in which the number of offspring is drawn from a distribution,
\parencite[as in][]{etheridge/kurtz:2018}
and the main statements in our paper will still hold.
We have adopted this simple birth model
so we may demonstrate our proof in a more palatable manner.
\end{remark}

\begin{figure}
    \begin{center}
        FIGURE
    \end{center}
    \caption{
        TODO: Figure depicting deterministic vs superprocess dichotomy:
        showing 2D images of populations,
        one with $\theta/N$ not small, the other with $\theta/N$ small.
        \label{fig:super_vs_det_2d}
    }
\end{figure}

\plr{Main theorem 1:}

\begin{theorem}\label{teo: Main Convergence Theorem - non-linear superprocess}
 Let $(\overline{\eta}^{\varepsilon, \theta,N}(t))_{t \geq 0}$ be the re-scaled model defined in Definition \ref{Def: Rescaled Models} and assume that as $\theta \to \infty$, $N \to \infty$, $\varepsilon(\theta)$ remains constant and $\theta/N \to \ell$.\\~\\
    The sequence of stochastic processes $(\overline{\eta}^{\varepsilon,\theta,N}_t)_{t \geq 0}$ converges weakly (analytically) in distribution as $\theta \to \infty$ to a measure-valued process $(\Xi^\varepsilon_t)_{t \geq 0}$ which satisfies that, for every $f:\mathbb{R}^d \rightarrow \mathbb{R}$,
\begin{align*} M_t &:= \langle f(x), \Xi^\varepsilon_t(dx) \rangle - \langle f(x), \Xi^\varepsilon_0(dx) \rangle \\ &- \int_0^t \big\langle \gamma(x,\varrho_{\varepsilon}*\Xi^{\epsilon}_{s}(x)) \mathcal{B}(f(\cdot)r(\cdot,\varrho_{\varepsilon}*\Xi^{\epsilon}_{s}(\cdot))(x) + f(x)  F(x,\varrho_{\varepsilon}*\Xi^{\epsilon}_{s}(x)), \Xi^\varepsilon_s(dx) \big\rangle ds, \end{align*}
is a martingale. The quadratic variation of $M_t$ is given by 
\begin{align*}
[ M ]_t = \int_0^t \ell\big\langle\gamma\big(x,\varrho_{\varepsilon}*\Xi^{\epsilon}_{s}(x)\big) r\big(x,\varrho_{\varepsilon}*\Xi^{\epsilon}_{s}(x)\big) f^2(x), \Xi^\varepsilon_s (dx) \big\rangle ds. 
\end{align*}
In other words, the limit $(\Xi^\varepsilon_t)_{t \geq 0}$ is a measure-valued process with non-local interactions.
Furthermore, if $\ell=0$ the limit is deterministic. In that case, if $\overline{\eta}^{\varepsilon,\theta}_0$ possesses a density in $L^2(\mathbb{R}^d)$, and the functions $\gamma$, $F$ are Lipschitz, then $(\overline{\eta}^{\varepsilon,\theta}_t)_{t \geq 0}$ possesses a density in $L^2(\mathbb{R}^d)$ and  $(\overline{\eta}^{\varepsilon,\theta}_t)_{t \geq 0}$ converges to a unique limit $(\Xi^\varepsilon(t))_{t \geq 0}$ with density $\varphi^\varepsilon(t,x)$ that solves (weakly) the mollified PDE of the form
\begin{equation}\label{Eq: non-local density PDE equation}
\partial_t \varphi(t,x) = r\big(x,\varrho_{\varepsilon}*\varphi(t,x)\big) \mathcal{B} \Big(\varphi(t,\cdot)\gamma\big(x,\varrho_{\varepsilon}*\varphi(t,\cdot)\big)\Big)(x) + \varphi(t,x) F\big(x,\varrho_{\varepsilon}*\varphi(t,x)\big)    
\end{equation}
\end{theorem}

\plr{Main theorem 2:}

\begin{theorem}\label{teo: Main Convergence Theorem - local pde limit}
 Assume that $\theta/ N \to 0 $ and assume that $\varepsilon(\theta) \to 0$. The sequence of mollifiers $\varrho_{\varepsilon}$ thus converges weakly to the Dirac delta mass, i.e. 
$\int_{\mathbb{R}^d} f(x)\varrho_{\varepsilon}(y-x)dx \to f(y)$. Assume furthermore that the following two conditions holds:
\begin{enumerate}
    \item The rate at which the local interaction strength $\varepsilon:=\varepsilon(\theta)$, speed $\theta$ and mass $\frac{1}{N(\theta)}$ scale satisfy the Equation 
\begin{equation} \label{condepsilon}
\frac{\theta}{N(\theta) \varepsilon(\theta)^{\frac{3 d p}{2}}} + \frac{1}{\theta \varepsilon(\theta)^{\frac{d p}{2}}} \xrightarrow[\theta \rightarrow \infty]{} 0,
\end{equation}

and $\overline{\eta}^{\varepsilon,\theta,N}_0$ is given by a Poisson point process with mean measure $\varphi_0(x)$.
    \item As $\varepsilon \to 0$, the sequence of functions $\{\varphi^\varepsilon(t,x): \varepsilon > 0 \}$ defined in Definition \ref{def: Weak solution formulation, mollified version} converges uniformly in space for any fixed time $t > 0$ to the function $\{\varphi(t,x): x \in \mathbb{R}^d, t >0\}$  which solves the partial differential equation 
    \begin{equation}\label{eq: local PDE limit generalised}
    \partial_t \varphi(t,x)=r(x,\varphi(t,x))\mathcal{B}\left(\varphi(t,\cdot) \gamma\big(\cdot,\varphi(t,\cdot)\big)\right)(x)+ \varphi(t,x)F\big(x,\varphi(t,x)\big)    
    \end{equation}
    with intial condition $\varphi(0,x)=\varphi_0(x)$.
\end{enumerate}
Then the sequence of stochastic processes $\{(\overline{\eta}^{\varepsilon, \theta,N}(t))_{t \geq 0}: \varepsilon > 0\}$ converges weakly (analytically) on finite dimensional distributions (in probability) to the deterministic process $\{\varphi(t,x): x \in \mathbb{R}^d, t >0\}$ defined in Equation \eqref{eq: local PDE limit generalised}.
\end{theorem}

\comment{Set-up and motivation for theorem on lineages.}
In \S \ref{Sec: Lookdown Constructions}, we will introduce a lookdown construction for the model described in \S \ref{sec: individual based model}. A lookdown construction assigns each particle a unique level which enables us to do a richer analysis. The main interest in using a lookdown construction for our
population processes is that it allows us to retain information 
about relatedness between individuals as we pass to the infinite
density limit. In particular, we are able to rigorously establish an equation for the motion of ancestral lineages in our limiting partial differential equation.

Consider a population evolving according to one of our deterministic
limiting models. We shall restrict ourselves
to the setting in which the population is expanding as a travelling wave
through $\IR$, with fixed profile $w(x)$ at rate $\mathfrak{c}$. That is 
$$\Xi_t(x)=w(x-\mathfrak{c}t),$$
for some fixed function $w$, and some $\mathfrak{c}\geq0$.  The profile $w$, if it exists, will satisfy
\begin{equation}
\label{profile}
r\Delta(\gamma w)+F(w)+\mathfrak{c}\nabla w=0.
\end{equation} 
It is convenient to work in a moving frame so that the wavefront is fixed. In this setting we want to investigate the ancestry line of an individual.\\
Note that in our model each individual has one parent only. As a result, as we go backwards in time, each individual has one unique ancestor at any time $t$.
\begin{definition}\label{def: Ancestry Line}
Let $w$ denote the wavefront of an evolving population that solves (\ref{profile}) and let $y \in supp(\Xi_t)$. We define $(L_s(y))_{s \geq 0}$, the ancestry line of an individual sampled at $y$, to be the position of the unique ancestor of $y$ at unit $s$ backwards in time.\\
We define $(\hat{T}_s)_{s \geq 0}$ to be the semi-group satisfying
$$\hat{T}_sf(y):=\mathbb{E}_{y}[f(L_s)]$$ and 
$\hat{\mathcal{L}}$ to be its corresponding generator. 
\end{definition}
The mathematical formulation for $L_s(y)$ will be made explicit once we introduce lookdown construction in \S \ref{Sec: Lookdown Constructions} as it allows us to trace lineages through stochastic differential equations, see \S \ref{sec: stochastic equations for lineages}.

\plr{Main Theorem 3}

\comment{TODO: clarify that this applies to either local or nonlocal population limits}

\begin{theorem} \label{teo:ancestral lineages}
    Let $w$ denote the wavefront of an evolving population that solves (\ref{profile}).
    Then the generator $\hat{\mathcal{L}}$ of the motion of an ancestral line of individuals in this population is given by
    \begin{equation}
    \label{eq: generator of lineage motions}
        \hat{\mathcal{L}} \phi
        =
        r\gamma\left(\Delta\phi+2\frac{\nabla(\gamma w)}{\gamma w}\nabla\phi\right)
        +\mathfrak{c} \nabla\phi.
    \end{equation}
\end{theorem}

\comment{TODO: short note on why it doesn't make sense to do this for a superprocess
         (it'd be Markov backwards in time given the population history probably,
         but it would be like a diffusion on a singular, evolving space or something)
}

%%%%%%%%%%%%%%%%%%%%%%
\section{Examples and applications}

% % % % % % % % % % % %
\subsection{A nonlinear diffusive population: the Porous medium equation}

\begin{figure}
    \begin{center}
        FIGURE
    \end{center}
    \caption{
        Two panels, showing simulated 1D populations under the PME, comparing the simulated
        profile to the analytical solution;
        $\theta/N$ not small on left; small on right.
        (Note: noisier wave should move slower, we'll see this.)
        \label{fig:pme_waves}
    }
\end{figure}

\comment{
    Model set-up including the limit;
    comparison of the simulation profile to deterministic solution.
    See Figure \ref{fig:pme_waves}.
}

% % % % % % % % % % % %
\subsection{Traveling waves: FKPP versus PME}

\begin{figure}
    \begin{center}
        FIGURE
    \end{center}
    \caption{
        Four panels: left pair for FKPP, right for PME.
        Each pair shows (top) lineage traced back in wavefront,
        and (bottom) stationary distribution of lineage location,
        compared to analytical solution for PME.
        \label{fig:pme_vs_fkpp}
    }
\end{figure}

\comment{
    Explain generator in stationary frame;
    derive stationary distribution;
    introduce FKPP;
    compute for PME and FKPP.
    (Also: Allen-Cahn example?)
    The two cases are very different, as shown in Figure \ref{fig:pme_vs_fkpp}.
}
\plr{Merge the following examples, moving introduction of PME to previous section}

Let us investigate the motion of an ancestral lineage in special
cases in which we have an explicit expression for the travelling
wave profile $w$.

\plr{PME:}
Consider the porous medium equation with logistic
growth,
\begin{equation}
\label{travelling wave}
v_t=(v^2)_{xx}+v(1-v).
\end{equation}
This equation has an explicit travelling wave solution
$$w^P(t,x)=\left(1-e^{\frac{1}{2}(x-x_0-t)}\right)_+.$$
Notice that this profile has a sharp boundary at $x=x_0+t$.
There are also travelling wave solutions with $c>1$,
\cite{gilding/kersner:2005}, which lack this property. However, for 
initial conditions that decay sufficiently rapidly at infinity,
such as one might use in modelling a population invading new territory,
the solution converges to~(\ref{travelling wave}), 
\cite{kamin/rosenau:2004}.

Setting $x_0=0$ (for definiteness) and substituting 
$w(x)=(1-e^{x/2})_+$ in our equation for the generator of the
motion of an ancestral
lineage relative to the wavefront, we find that since
in this setting $c=1$,
$\gamma(x,w)=w(x)$, $r(x,w)=1$, and $F(w)=w(1-w)$,
the lineage follows the diffusion with generator
$$\hat{\mathcal L}\phi=w(x)\left(\phi_{xx}+2\frac{(w^2)_x}{w^2}\phi_x\right)
+\phi_x
=\left(1-e^{\frac{1}{2}x}\right)\phi_{xx}-2e^{\frac{1}{2}x}\phi_x+
\phi_x\qquad\mbox{on }x<0.$$
The speed measure corresponding to this diffusion is 
$$m(d\xi)\propto\frac{1}{2(1-\exp{\xi/2})}
\exp\left(\int_\eta^\xi\left\{1-\frac{e^{x/2}}{1-e^{x/2}}\right\}dx\right)
\propto e^\xi\left(1-e^{\xi/2}\right),
\quad\mbox{$\xi<0$},$$
which is integrable and so when suitably normalised gives the unique
stationary distribution. Notice that at stationarity
the lineage will typically be 
significantly behind the front.

\plr{FKPP:}
This behaviour of all this ancestral lineages can be compared to the classical
Fisher-KPP equation.
Under the classical Fisher-KPP equation, the generator of the motion
of ancestral lineages can be deduced from 
exactly the same arguments. 
The equation
$$v_t=v_{xx}+v(1-v),$$
has non-negative travelling wave solutions for all $c\geq 2$, 
but started from any compact perturbation of a Heaviside function, the 
solution will converge to the one with the minimal wavespeed, $c=2$,
\cite{kolmogorov/petrovsky/piscounov:1937, bramson:1983}.
No matter what the initial condition, for any $t>0$ the support of the 
solution will be the whole real line.  In the front the wave profile 
$w^F(x)\sim e^{-x}$.
The generator of the motion of an ancestral lineage is
$$\hat{\mathcal L}\phi=\phi_{xx}+2\frac{w_x}{w}\phi_x+2\phi_x,\qquad
\mbox{on }(-\infty,\infty).$$
Near the tip of the wave ($x$ very big) we have $w^F(x) \sim e^{-x}$ and $w_x^F(x) \sim -e^{-x}$, so
the motion of the lineage
is close to Brownian motion. Whereas in 
the bulk (where $w^F_x\approx 0$) it is approximately Brownian motion 
with drift at rate two to the right. Ancestral lineages are pushed into
the tip of the wave. 
We remark that, even though we do not have an explicit formula for the wave of the travelling front in this case, we can still analyse and get information of the ancestral lineages.

\plr{Include the following as a third comparison?}
We can extend this type of analysis to other equations that are biologically relevant. For example, we now take the following Allen-Cahn equation
\[ v_t = v_{xx} + v(1-v)(2v-1+s), \]
for some $s \in (0,2)$, which is used to model population evolving under selection \cite{Sarah}. This equation have an explicit travelling wave solutions $\Xi_t(x) = w^A(x-st)$, where $w$ is given by
\[ w^A(x) = (1+e^{x})^{-1}. \]
By Theorem \ref{teo:ancestral lineages} the ancestral lineage under this moving frame has generator
\[ \hat{\mathcal{L}}\phi = \phi_{xx}+2 \frac{w_x}{w} \phi_x + s \nabla \phi =  \phi_{xx}-2 \frac{e^x}{1+e^x} \phi_x + s \nabla \phi, \]
lineages in the tip are pushed into the bulk of the wave by the drift $-2(e^{-x}+1)^{-1}$, but that drift gets weaker the deeper we go into the wave. This diffusion has speed measure
\[ m(d\xi) \propto e^{sx}(1+e^x)^{-2}  \] 
which is concentrated around $\log(s/(2-s))$ and decay like $e^{x(s-2)}$ away from that. We note the result above the for the Allen-Cahn are not new, we have just recovered what can be found in \cite{etheridge/penington:2020}.

% % % % % % % % % % % % % % % %
\subsection{Clumping from nonlocal interactions}

\comment{
    Description of the process;
    discussion of when it happens;
    (TODO: how's it affected by $\theta$?)
}

\begin{figure}
    \begin{center}
        FIGURE
    \end{center}
    \caption{
        Two panels: left is 2D picture of clumped population;
        right is a bumpy expanding wavefront.
        \label{fig:clumping}
    }
\end{figure}

% % % % % % % % % % % % % % % %
\subsection{Populations with Varying Lineage Distributions but Same Stationary Profile}

Consider two populations with coefficients $r_1, \gamma_1, \mu_1$ and  $r_2, \gamma_2, \mu_2$, and denote their lineage motion generator and profile as $\hat{\mathcal{L}}_1,w_1$, and $\hat{\mathcal{L}}_2,w_2$. We further assume that our populations have a stationary distribution with $\Xi_t(x)=w(x)$, i.e. $\mathfrak{c}=0$.\\
Let $\beta(x)>0$ and take $r_2(x)=r_1(x)\beta(x),~ \mu_2(x)=\mu_1(x)\beta(x),~ \gamma_2(x)=\gamma_1(x)$. Since $F=r\gamma-\mu$, we have that 
\begin{multline}
\label{eq: same profile scaled}
r_2\Delta(\gamma_2 w_2)+(r_2\gamma_2-\mu_2)(w_2)=0\implies r_1\beta \Delta(\gamma_1 w_2)+(r_1\beta \gamma_1-\mu_1 \beta)(w_2)=0\\
\implies r_1 \Delta(\gamma_1 w_2)+(r_1 \gamma_1-\mu_1)(w_2)=0 \implies w_2=w_1.
\end{multline}
The two populations share the same stationary profile but their ancestral lineage motions are different as 
\begin{equation}
\label{eq: different generator scaled}
\hat{\mathcal{L}}_2 \phi = r_1 \beta \gamma_1\left(\Delta\phi+2\frac{\nabla(\gamma_1 w_1)}{\gamma_1 w_1}\nabla\phi\right)\neq r_1 \gamma_1\left(\Delta\phi+2\frac{\nabla(\gamma_1 w_1)}{\gamma_1 w_1}\nabla\phi\right) = \hat{\mathcal{L}}_1 \phi.
\end{equation}
The stationary distribution of our population is unchanged when we scale $r,\mu$ by a rate of $\beta(x)$,
but the motion of lineages is sped up locally by $\beta$.
This corresponds to making areas with $\beta > 1$ more ``sink-like'',
because there death rate is higher, but also is the establishment of new individuals. Those regions as a result have lower long-term fitness and lineages spend less time there.

%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Heuristics}

% % % % % % % % % % % % % % % % % %
\subsection{Population processes}

Here we present a formal generator calculation which identifies the scaling
limits that appear in our main results and may be more accessible than our 
calculations with the lookdown construction.
For this purpose, we consider two scaling parameters, $N$ and $\theta$;
we shall start with ${\mathcal O}(N)$ individuals per unit area,
each of mass $1/N$,
and we measure time in units of $\theta$ generations,
so that each individual reproduces at rate $\theta$
and disperses juveniles a distance of order $1/\sqrt{\theta}$.
Both $N$ and $\theta$ will tend to infinity in our scaling limits
and we retain different notations in our
heuristic arguments to disentangle their effects.
The functions of $q, r, \gamma, \mu$
can all depend upon the time scaling $\theta$.
Indeed, by analogy with the classical superprocess,
in order to obtain a nontrivial limit, 
we expect to need to assume that the branching is close to critical, with the
difference between birth and death rates proportional to $1/\theta$.

We write ${\cal L}_{(\theta, N)}$ for the generator of the scaled 
population process acting
on test functions of the form 
$$
    \mathcal{F}(\langle f,\overline{\eta}\rangle)
    :=
    \mathcal{F}\left(\int f(x)\overline{\eta}(dx)\right),
$$
where $f\geq 0$ is smooth and compactly supported on $\mathbb{R}^d$ and 
$ \mathcal{F} \in C^\infty ([0,\infty))$.

A Taylor expansion allows us to write
\begin{align}
    {\cal L}_{(\theta, N)} \mathcal{F}(\langle f,\overline{\eta}\rangle)
    &=
     \mathcal{F}'(\langle f,\overline{\eta}\rangle)
    \lim_{\delta t\downarrow 0}\frac{1}{\delta t}
    \mathbb{E}\left[ \left.
            \langle f, \overline{\eta}_{\delta t} \rangle -
            \langle f, \overline{\eta} \rangle
            \right|
            \overline{\eta}_0 = \overline{\eta}
        \right] \nonumber \\
    & {}
    + \frac{1}{2}
        \mathcal{F}''(\langle f,\overline{\eta}\rangle)
        \lim_{\delta t\downarrow 0}\frac{1}{\delta t}
        \mathbb{E}\left[\left.
            \big(\langle f,\overline{\eta}_{\delta t}\rangle -
            \langle f, \overline{\eta}\rangle\big)^2 \right|\overline{\eta}_0=\overline{\eta}
        \right]
    + \varepsilon_{\theta, N}(f, F, \overline{\eta}) ,
    \label{eq:expanmeanvar}
\end{align}
where the terms that make up 
$\varepsilon_{\theta, N}(f, F, \overline{\eta})$
will be negligible in our scaling limit.

% % % % % % % % % % % % % % % %
\subsubsection*{Mean Measure}

Consider first the mean measure. For a suitable 
(smooth, compactly supported) test function $f$, we find
\begin{multline} \label{mean measure}
    {\cal L}_{(\theta, N)}\langle f, \overline{\eta} \rangle
    =
    \lim_{\delta t\downarrow 0}\frac{1}{\delta t}
        \mathbb{E}\left[\left.
            \langle f,\overline{\eta}_{\delta t}\rangle -
            \langle f, \overline{\eta}\rangle
            \right| \overline{\eta}_0=\overline{\eta}
        \right]\\
    =
    \theta\int\int
            f(z) r_\theta(z,\overline{\eta}) q_\theta(x,dz)
        \gamma_\theta(x,\overline{\eta})
    \overline{\eta}(dx)
    -
    \theta\int
        f(x)\mu_\theta(x,\overline{\eta})
    \overline{\eta}(dx).
\end{multline}
The first term is the increment in $\langle f,\overline{\eta}\rangle$
resulting from a birth event
integrated against the rate of such events,
and the second reflects death events.
Note that there is a slight mismatch between the locations at which we are 
measuring birth and death rates, because
the establishment probability is measured at $x$
rather than at the point where juveniles fall (see \eqref{near critical}).
In both terms,
the rate of events has a factor of $N$
(because events happen at a rate proportional to the number of individuals,
whereas $\overline{\eta}$ is the total number divided by $N$)
which is offset by the fact that  
the birth or loss of a single 
individual at the point $y$, say, changes $\langle f,\overline{\eta}\rangle$
by $f(y)/N$.

We use the fact that $\int q_\theta(x,dz)=1$ to rewrite~(\ref{mean measure})
as 
\begin{multline}
\label{rewritten mean measure}
    \int\left(
          \int \theta \left(
            f(z)r_\theta(z,\overline{\eta})
            -
            f(x)r_\theta(x,\overline{\eta})\right)
          q_\theta(x,dz)
        \right)
        \gamma_\theta(x,\overline{\eta})
    \overline{\eta}(dx) \\
    + 
    \theta\int f(x)
        \Big(
            r_\theta(x,\overline{\eta})
            \gamma_\theta(x,\overline{\eta})
            -
            \mu_\theta(x,\overline{\eta})
        \Big)
    \overline{\eta}(dx) .
\end{multline}
Suppose as we take $\theta \to \infty$ that
$\overline{\eta}$ converges to a measure $\Xi$ on $\mathbb{R}^d$.
Then we can take this limit in~(\ref{rewritten mean measure})
under the assumptions that
\begin{eqnarray} \label{near critical}
\left.
\begin{split}
    r_\theta(x,\overline{\eta})
        &\;  \stackrel{\theta\to\infty}{\longrightarrow} \;
        r(x,\Xi)
    \\
    \gamma_\theta(x,\overline{\eta})
        &\;  \stackrel{\theta\to\infty}{\longrightarrow} \;
        \gamma(x,\Xi)
    \\
    \int\theta \Big(
            r(z,\overline{\eta})f(z)
            -
            r(x,\overline{\eta})f(x)
        \Big)q_\theta(x,dz) 
        &\; \stackrel{\theta\to\infty}{\longrightarrow}  \;
        \Delta \big(r(\cdot,\Xi)f(\cdot)\big)(x)
    \\
    \theta \Big(
            r_\theta(x,\overline{\eta})
            \gamma_\theta (x,\overline{\eta})
            -
            \mu_\theta (x,\overline{\eta})
        \Big)
         &\; \stackrel{\theta\to\infty}{\longrightarrow}  \;
        F(x,\Xi),
\end{split}
\right\}
\end{eqnarray}
where $\Delta$ denotes the Laplacian.
The last condition reflects the `near-critical' branching,
and implies that $\mu_\theta(x, \overline{\eta}) \to \gamma(x, \Xi) / r(x, \Xi)$.

Referring back to the original (unscaled) process,
this amounts to assuming that
there are of order $N$ individuals per unit area,
and per-capita birth and death rates
are sufficiently close that population density takes of order $\theta$ time to change.
However, note that although the difference
between the number of births and deaths per unit area
across $\theta$ units of time is of order $N$,
the total number of such events is larger (of order $\theta N$).
As we will see next, the variance of population density per unit of (unscaled) time
is therefore of order $1/N$,
so we will obtain a deterministic limit if $\theta$ is of smaller order than $N$.

Then the mean rate of change of $\langle f, \overline{\eta}\rangle$,
\eqref{rewritten mean measure} converges to
\begin{equation} \label{limit of mean measure equation}
    \int \gamma(x,\Xi)
        \Delta \big(f(\cdot)r(\cdot,\Xi)\big)(x)
    \Xi(dx)
    + \int f(x)
        F(x,\Xi)
    \Xi(dx) .
\end{equation}
As we will see below,
if the limit is deterministic and $\Xi_t$ possesses a density
with respect to the Lesbegue measure,
this means that the density satisfies
\begin{equation}
\label{eq: limit of mean measure equation 2}
    \int f(x) \partial_t \Xi(dx)
    =
    \int \gamma(x,\Xi)
        \Delta \big(f(\cdot)r(\cdot,\Xi)\big)(x)
    \Xi(dx)
    + \int f(x)
        F(x,\Xi)
    \Xi(dx),
\end{equation}
i.e., $\Xi$ is a \textit{weak solution} to the integro-differential equation:
\begin{equation}\label{eq:PDE}
    \partial_t \Xi
    = r \Delta \gamma \Xi + F \Xi .
\end{equation}
(Although this looks like a partial differential equation,
recall that $r$, $\gamma$, and $F$ at $x$ depend on $\Xi$
through a convolution.)

% % % % % % % % % % % % % % % %
\subsubsection*{Quadratic Variation}

We now look at the second order term.
Thinning the birth process to only consider offspring
who successfully mature,
an individual at the point $x$ gives birth to an offspring
who moves to $y$ and successfully matures there
at rate
$$
    \gamma_\theta(x,\overline{\eta}) r_{\theta}(y,\overline{\eta}) q_{\theta}(x, dy) .
$$
The increment to $\langle f, \overline{\eta}\rangle^2$ due to this event is $f(y)^2/N^2$,
so the contribution to the quadratic variation from birth events, which
occur at rate $\theta$ per individual is
$$
    \langle N\theta
        \gamma_\theta(x,\overline{\eta})
        \int
            \frac{1}{N^2} f^2(y) r_{\theta}(y,\overline{\eta})
        q_\theta(x,dy)
        ,
        \overline{\eta}(dx)
    \rangle .
$$
The increment in $\langle f, \overline{\eta}\rangle^2$ resulting from 
the death of an individual at $x$ is $f^2(x)/N^2$, and so combining with the 
above, the second order term in the generator takes the form
$$
    \mathcal{F}''(\langle f, \overline{\eta}\rangle)
    \frac{1}{2}N\theta \left\{
        \langle
            \gamma_\theta(x,\overline{\eta})
            \int \frac{1}{N^2} f^2(y) r_\theta(y,\overline{\eta}) q_\theta(x,dy) 
            ,
            \overline{\eta}(dx)
        \rangle
        +
        \langle
            \mu_\theta(x,\overline{\eta})\frac{1}{N^2}f^2(x) 
            ,
            \overline{\eta}(dx)
        \rangle
    \right\} .
$$
The term $\varepsilon_{\theta,N}(f, F, \overline{\eta})$ in \eqref{eq:expanmeanvar}
is ${\mathcal O}(\theta/N^2)$,
as it depends on higher order moments of $\langle f ,\overline{\eta} \rangle$.
It follows that the quadratic variation of the semi-martingale $\langle f, \overline{\eta} \rangle$
is given by
\begin{equation} \label{quadratic variation}
    \frac{\theta}{N}
    \left\{
        \langle
            \gamma_\theta(x,\overline{\eta})
            \int f^2(y)r_\theta(y,\overline{\eta})q_\theta(x,dy) 
            ,
            \overline{\eta}(dx)
        \rangle
        +
        \langle
            \mu_\theta(x,\overline{\eta})f^2(x) 
            ,
            \overline{\eta}(dx)
        \rangle
    \right\} .
\end{equation}

Let $\ell$ be defined by
\begin{equation}
 \frac{\theta}{N} \rightarrow \ell \in [0,\infty).
 \label{defn:rho}
 \end{equation}
If $\ell=0$ then the quadratic variation of $\overline{\eta}$ goes to $0$, and so we expect a deterministic limit. This limit should be described as the solution to (\ref{eq: limit of mean measure equation 2}). If $\ell$ is positive then the limit is stochastic, and should be understood as the solution of a martingale problem.

One can build many different examples in which our assumptions hold. Our main result establishes that a broad range of models, under which these heuristics can be justified, can be further enriched by a structure called the \textit{lookdown construction} that preserve ancestral relationships under passage to the limit.

\plr{TODO: heuristics of conditions to get a local (PDE) limit?}

% % % % % % % % % % % % % % % % % %
\subsection{Lineages}

\plr{
    TODO: Heuristics for how lineages should move given the population process.
}

%%%%%%%%%%%%%%%%%%%
\section{The lookdown process}

\plr{Motivation for and definition of the lookdown process}

Now we
will present a lookdown construction for $(\overline{\eta}^{\epsilon,\theta,N}(t))_{t \geq 0}$ stated in Definition \ref{Def: Rescaled Models}
in the spirit of~\cite{kurtz/rodrigues:2011}. 
The key benefit of working in such a framework is that
we shall be able to preserve the notion of individuals, and in particular their genealogies, when we pass to the limit. Our notation will follow a standard pattern.

% % % % % % % % % % % % % % % %
\subsection*{Prelimit Models and Notation}\label{Prelimit Models and Notation Section}

In the prelimiting models each individual in the population will be assigned a 
`level' from $[0,\lambda]$. We also let $\lambda$ takes on the role of $N$ in \S \ref{sec: model and results}, i.e. each individual has mass $1/\lambda$ in the scaling limit. Speed is once again scaled by $\theta$ and local radius by $\varepsilon(\theta)$.\\
A state of the discrete population model will be of the form $\eta=\sum\delta_{(x,u)}$, where $x$ denotes the  
spatial location of an individual, and $u$ is its level. Just as we did in \S\ref{prelimiting spatial model}, we shall
abuse notation and treat $\eta$ both as a set and as a counting
measure. The population of \S\ref{prelimiting spatial model}
is recovered as $\overline{\eta}=\frac{1}{\lambda}\sum_{(x,u)\in\eta}\delta_x$, i.e. $\overline{\eta}$ is the spatial projection of our spatial-level model $\eta$. 
Conditional on $\overline{\eta}$, the levels of individuals in 
the population will be independent, uniformly distributed random variables
on $[0,\lambda]$. All of this can be found in \cite{etheridge/kurtz:2018},\cite{kurtz/rodrigues:2011}.
Test functions for this enriched process take the form
\begin{equation}
\label{test functions}
f(\eta)=\prod_{(x,u)\in\eta}g(x,u)=\exp\left(\int\log g(x,u)\eta(dx, du)\right),
\end{equation}
where $g(x,u)$ is differentiable in $u$ and 
smooth in $x$. Moreover, $0\leq g(x,u) \leq 1$ for all $u\in [0,\lambda]$, and 
$g(x,u)\equiv 1$ for $u\geq \lambda$.

In the expressions that follow, we shall often see one or more factor of
$1/g(x,u)$; 
it should be understood that if $g(x,u)=0$, then it simply cancels 
the corresponding factor in $f(\eta)$.

% % % % % % % % % % % % % % % %
\subsection*{Generator of the Scaled Lookdown Model}

In the notation of \S\ref{heuristics}, we now write down the 
generator of the scaled population model with levels where 
$\lambda$ is the scaling factor of the mass of an individual, $\theta(\lambda)$ is the scaling factor for time and the level of an individual particle must be in $[0,\lambda]$.  
Recall that we only track the adult population; maturity, if achieved, is 
instantaneous. Furthermore, at rate $\theta\gamma_{\theta}(x, \overline{\eta})$ a parent gives birth to a single juvenile offspring.

We should consider an initial population of $O(\lambda)$ many particles with levels uniformly distributed between $[0, \lambda]$. We write $(\eta^{\theta, \lambda}(t))_{t \geq 0}$ for our population at the $\theta$th stage of rescaling. To recover the scaling of \S\ref{sec: model and results} we scale the empirical distribution of particles alive with a factor of $1/\lambda$, so we write $$\overline{\eta}^{\theta, \lambda}(t)=\frac{1}{\lambda}\sum\limits_{\substack{(X(t),U(t))\in \eta \\ U(t) < \lambda}} \delta_{X(t)}.$$ 
From here onwards we write $\eta$ to be the particle systems with levels while $\overline{\eta}$ is the normalised empirical distribution. An individual of the population with state $\eta$ living at spatial location $x$ produces
one adult offspring at rate $\theta\gamma^{\mathfrak{m}}_{\theta}(x, \overline{\eta})$, where
$$\gamma^{\mathfrak{m}}_{\theta}(x,\overline{\eta})=\gamma_\theta(x,\overline{\eta})
\int r_\theta (y, \overline{\eta})q_\theta(x,dy).
$$
The location of this offspring is given by
the distribution 
\[ q^{\mathfrak{m}}_\theta(x,\overline{\eta},dy) = \frac{r(y,\overline{\eta}) q_{\theta}(x,dy)}{\int_{\mathbb{R}^d} r(y,\overline{\eta}) q_{\theta}(x,dy)}. \] In the lookdown version of our model, the individual $(x,u)\in\eta^{\theta, \lambda}$ gives
birth to an offspring at rate 
$2(\lambda-u)\lambda^{-1}\theta \gamma^{\mathfrak{m}}_{\theta}(x, \overline{\eta})$. 
(Averaging
over the distribution of the
level $u$ we recover $\theta \gamma^{\mathfrak{m}}_{\theta}(x, \overline{\eta})$.)

A new level $u_1$ is sampled independently and
uniformly from $[u,\lambda]$, and the parent and the offspring 
are assigned in random order to the  levels $\{u, u_1\}$. This random assignment of levels to child and offspring ensures that conditional on $\overline{\eta}$, the levels assigned to individuals are i.i.d. uniform random variables. Otherwise, the levels of the initial population would be lower than those of the descendants.\\
Evidently this mechanism increases the proportion of individuals with
higher levels. To restore the property that,
conditional
on $\overline{\eta}$, the intensity of
levels is conditionally uniform, we impose that 
the level associated with
$(x,u)\in\eta$ evolves
according to the differential equation
$$\dot{v}= \theta \gamma^{\mathfrak{m}}_{\theta}(x, \overline{\eta}) 
\left\{\lambda^{-1}(\lambda -v)^{2}
-(\lambda -v)\right\}.$$

See~\cite{etheridge/kurtz:2018}, Section~3.4 for a detailed explanation.
In order to incorporate death, the level of the individual $(x,u)\in \eta$ 
moves upwards at an additional 
rate $\theta \mu_\theta(x,\overline{\eta})$ (on reaching level $\lambda$ an
individual is deemed to
have died). Overall, we assume that the level associated with $(x,u)\in\eta$
evolves according to
$$\dot{u}= \theta \gamma^{\mathfrak{m}}_{\theta}(x, \overline{\eta}) 
\left\{\lambda^{-1}(\lambda -u)^{2}
-(\lambda -u)\right\}+\theta \mu_\theta(x,\overline{\eta})u.$$
We shall write 
$$b_{\theta, \lambda}(x,\overline{\eta}):=\theta\big\{\gamma^{\mathfrak{m}}_{\theta}(x,\overline{\eta})
-\mu_\theta(x,\overline{\eta})\big\}.$$
Note that this quantity captures the deviation from criticality in the branching
mechanism. In this notation, the differential equation governing the level of the
individual $(x,u)\in\eta$ is
\begin{align}
\dot{u}&=\lambda \theta \gamma^{\mathfrak{m}}_{\theta}(x,\overline{\eta}) 
\left\{\left(1-\frac{u}{\lambda}\right)^{2}
-1 +2\frac{u}{\lambda}\right\} -b_{\theta, \lambda}(x,\overline{\eta})u \nonumber \\
&=\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\overline{\eta}) u^2 -b_{\theta, \lambda}(x,\overline{\eta})u. \label{differential equation for level}
\end{align}
In this setting, the generator of our model acting on the test functions $f(\eta)=\prod_{(x,u) \in \eta}g(x,u)$ satisfies
%We assume that  locations in ${\mathbb{ R}}^d$.
\begin{eqnarray}\label{Generator of prelimit simplest model}
&&A_{\theta, \lambda}f(\eta ) \nonumber \\
&&\quad =f(\eta )\,\sum_{(x,u)\in\eta}\,2\lambda^{-1}\theta \gamma^{\mathfrak{m}}_{\theta}(x, \overline{\eta})
\int_u^{
\lambda}\Bigg(\frac 12\frac {\int_{\mathbb{R}^d}g(y,u)q^{\mathfrak{m}}_\theta(x,\overline{\eta },d
y)g(x,v_1)}{g(x,u)} \label{multgen3}\\
&&\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad
+\frac 12\int_{\mathbb{R}^d}g(y,v_1)q^{\mathfrak{m}}_\theta(x,\overline{\eta} ,dy)-
1\Bigg)dv_1\nonumber\\
&&\quad \quad +f(\eta )\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\overline{\eta}) u^2 -b_{\theta, \lambda}(x,\overline{\eta})u\right)\frac {\partial_u g(x,u)}{g(x,u)}\nonumber\\
&&\quad =f(\eta )\,\sum_{(x,u)\in\eta}\,2 \gamma^{\mathfrak{m}}_{\theta}(x, \overline{\eta})\lambda^{-1}\int_u^{
\lambda}\Bigg(\frac 12\frac {\theta\int_{\mathbb{R}^d}(g(y,u)-g(x,u))q^{\mathfrak{m}}_\theta(x,\bar{
\eta },dy)g(x,v_1)}{g(x,u)}\non\\
&&\qquad\qquad\qquad\qquad\qquad\qquad\qquad +\theta\int_{\mathbb{R}^d}\left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_\theta(x,\overline{\eta },dy)\Bigg)dv_1\nonumber\\
&&\qquad\qquad
+f(\eta )\sum_{(x,u)\in\eta}\,\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\overline{\eta}) u^2 -b_{\theta, \lambda}(x,\overline{\eta})u\right)\frac {\partial_u g(x,u)}{g(x,u)}.\nonumber
\end{eqnarray}
The two terms under the integral
correspond, respectively, to the parent being assigned 
a level other than $u$, and being reallocated to the level $u$ during a
birth event. In the first case, the parent at location $x$, which had level $u$ before the 
event, moves to level $v_1$, and the child is inserted at level $u$ and location $y$; in 
the second the parent retains its level, and offspring is inserted at
level $v_1$.\\~\\

As in Definition \ref{Def: Rescaled Models}, the rates $\gamma_{\theta},r_\theta, \mu_{\theta}$ in our re-scaled lookdown models  depend on the local density of $\eta$ through a mollification with $\varrho_{\varepsilon}$. We will now make our re-scaled lookdown model explicit.

\begin{definition}\label{Def: Rescaled Lookdown Models}
Let the coefficients $\tilde{\gamma}, \tilde{\mu}, \tilde{r}$ satisfy the conditions highlighted in Definition \ref{Def: Rescaled Models} and let $\varrho_{\varepsilon}$ be the kernel defined in Definition \ref{Defn: Kernel and Convolution}. We define the following terms:
\begin{align*}
\gamma^{\mathfrak{m}}_{\varepsilon,\theta}(x, \overline{\eta}):=&~\tilde{\gamma}_{\theta}(x, \varrho_{\varepsilon}*\overline{\eta}(x)) \int \tilde{r}_{\theta}(y, \varrho_{\varepsilon}*\overline{\eta}(y))q_{\theta}(x,dy),\\
 q^{\mathfrak{m}}_{\varepsilon, \theta}(x,\overline{\eta},dy) :=&~ \frac{\tilde{r}_{\theta}(y,\varrho_{\epsilon}*\overline{\eta}(y)) q_{\theta}(x,dy)}{\int_{\mathbb{R}^d} \tilde{r}_{\theta}(y,\varrho_{\epsilon}*\overline{\eta}(y)) q_{\theta}(x,dy)},\\
b_{\varepsilon, \theta, \lambda}(x, \overline{\eta}):=&~ \theta \bigg\{ \tilde{\gamma}_{\theta}(x, \varrho_{\varepsilon}*\overline{\eta}(x)) \int \tilde{r}_{\theta}(y, \varrho_{\varepsilon}*\overline{\eta}(y))q_{\theta}(x,dy)-\tilde{\mu}_{\theta}(x, \varrho_{\varepsilon}*\overline{\eta}(x)) \bigg\}
\end{align*}
At the $\lambda$-stage of re-scaling, our test measures $\eta$ takes value in $\mathcal{M}_F(\mathbb{R}^d \times [0,\lambda])$, the set of finite measures on $\mathbb{R}^d \times [0,\lambda]$, and we define $$\overline{\eta}= \frac{1}{\lambda}\sum_{(x,u) \in \eta}\delta_x.$$
We define $(\eta^{\varepsilon, \theta, \lambda}_t)_{t \geq 0}$ to be the (unique?) solution to the Martingale Problem with initial condition $\eta_0$ and generator $A_{\varepsilon, \theta, \lambda}$ that satisfies
\begin{eqnarray}\label{Eq: Prelimit Lookdown Generator}
&&A_{\epsilon, \theta, \lambda}f(\eta ) \\
&&\quad =f(\eta )\,\sum_{(x,u)\in\eta}\,2 \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(x, \overline{\eta})\Bigg\{ \frac 12 \lambda^{-1}\int_u^{
\lambda}g(x,v_1)dv_1\times \frac { \theta\int_{\mathbb{R}^d}(g(y,u)-g(x,u))q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\bar{
\eta },dy)}{g(x,u)}\non\\
&&\qquad\qquad\qquad\qquad\qquad\qquad\qquad +\lambda^{-1}\theta\int_u^{
\lambda}\int_{\mathbb{R}^d}\left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\overline{\eta },dy)dv_1\nonumber\Bigg\}\\
&&\qquad\qquad
+f(\eta )\sum_{(x,u)\in\eta}\,\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(x,\overline{\eta}) u^2 -b_{\varepsilon,\theta, \lambda}(x,\overline{\eta})u\right)\frac {\partial_u g(x,u)}{g(x,u)}.\nonumber
\end{eqnarray}
for all smooth functions $f \in C(\mathbb{R}^d)$. 
\end{definition}
In \S \ref{sec: Markov Mapping Theorem application}, through an application of the Markov Mapping Theorem, we will show that the spatial projection of $(\eta^{\varepsilon, \theta, \lambda}_t)_{t \geq 0}$ has the same distribution as $(\overline{\eta}^{\varepsilon, \theta, N}_t)_{t \geq 0}$ if we take $\lambda = N$. Specifically, we mean that when $\lambda=N$, 
$$(\overline{\eta}^{\varepsilon,\theta, \lambda}(t))_{t \geq 0}:=\left(\frac{1}{\lambda}\sum\limits_{\substack{(X(t),U(t))\in \eta^{\varepsilon,\theta, \lambda}(t) \\ U(t) < \lambda}} \delta_{X(t)}\right)_{t \geq 0}$$
has the same distribution (as stochastic processes) as $(\overline{\eta}^{\varepsilon,\theta, N}_t)_{t \geq 0}$ in Definition \ref{Def: Rescaled Models}. As a result, we use the same notation $\overline{\eta}$ to denote these two essentially identical processes which take values in the space of empirical measures. On the other hand, we reserve the notation $\eta$ strictly for the spatial-level process.\\~\\ Furthermore, the application of Markov Mapping Theorem implies that particle levels are, conditional on $\overline{\eta}$, i.i.d and uniformly distributed between $[0, \lambda]$.  Theorem A.10 in \cite{kurtz/rodrigues:2011} states that convergence of $(\eta^{\varepsilon, \theta, \lambda}_t)_{t \geq 0}$ to a conditionally Poisson system $(\xi_t)_{t \geq 0}$ with Cox measure $\Xi_t \times \Lambda$ is equivalent to convergence of $(\overline{\eta}^{\varepsilon, \theta, N}_t)_{t \geq 0}$ to $(\Xi_t)_{t \geq 0}$. As a result, it suffices for us to focus on tightness of $(\eta^{\varepsilon, \theta, \lambda}_t)_{t \geq 0}$ and spatial convergence of $(\overline{\eta}^{\varepsilon, \theta, N}_t)_{t \geq 0}$ as $\theta \to \infty$.

%% %% %% %% %% %% %% %% %% %% %% %%
\subsection{Evolution of an Individual Particle}
\label{sec: Evolution of an Individual Particle}

Here we give a general framework of tracking evolution of individual particles in the population described above. We will provide the right scaling of the coefficients introduced in \S \ref{sec: Convergence of Spatial-Level Models}.\\
Particles alive at time zero will be indexed by
$(0, i)$, or more precisely, we index the levels of the particles alive at time $0$ by $(0, i)$ keeping
in mind that at each birth event, the parent particle will, with probability $1/2$ change levels.
Since no two particles born after time $0$ will be born at the same time, we index the rest of
the levels by their birth times. With each level, we can associate a Poisson random measure
$\xi$ on $[0, \infty)^2\times [0,1]\times \{0,1\}$ (eventually, $\lambda \to \infty$) with mean measure $l^3 \times \{\frac{1}{2}\delta_0,\frac{1}{2}\delta_1\}$ which
determines the birth times of the offspring of the particle at that level, the location of the
offspring, and whether the offspring or the parent is placed at the new level. Let $U_{\tau}(t)$ be
the level at time $t \geq \tau$ if the level first appeared at time $\tau$ , and let $X_{\tau}(t), t \geq \tau$ be the
location of the particle with level $U_{\tau}(t)$. 
Now $U_{\tau}$ satisfies
\begin{equation}
U_{\tau}(t)=U_{\tau}(\tau)+\int_{\tau}^{t}(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(s),\overline{\eta}(s))U^2_{\tau}(s)-b_{\varepsilon,\theta,\lambda}(X_{\tau}(s),\overline{\eta}(s))U_{\tau}(s))ds, ~~~ t \geq \tau.    
\end{equation}
If a level has index $\tau$ and $(s,v,w,\kappa)\in \xi_\tau$, then $\tau+s$ gives a potential birth time for an offspring of the particle at level $U_{\tau}$. We say `potential' since if $U_{\tau}(\tau+s)>\lambda$, the corresponding particle is dead. The (potential) new level is 
\begin{equation}\label{New birth potential level}
    U_{\tau+s}(\tau+s)=U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(\tau+s-), \overline{\eta}(\tau+s-))}.
\end{equation}
If $U_{\tau+s}(\tau+s)< \lambda$, a new particle is produced with location $X_{\tau}(\tau+s-)+H(X_{\tau}(\tau+s-), \overline{\eta}(\tau+s-),w)$ where $H(X_{\tau}(\tau+s-), \overline{\eta}(\tau+s-),w)$ is a function such that if $w$ is a uniformly distribution on $[0,1]$, then 
\begin{equation}\label{eq: Individual Evolution Jump Kernel}
P(H(x, \overline{\eta},w)\in C | \overline{\eta},x)=q^{\mathfrak{m}}(x, \overline{\eta},C).    
\end{equation}
Consequently, 
$$X_{\tau}(\tau+s)=X_{\tau}(\tau+s-)+\kappa H(X_{\tau}(\tau+s-), \overline{\eta}(\tau+s),w)$$
and 
$$X_{\tau+s}(\tau+s)=X_{\tau}(\tau+s-)+(1-\kappa) H(X_{\tau}(\tau+s-), \overline{\eta}(\tau+s),w),$$
that is if $\kappa=0$, the parent stays at its current level and the new particle is given the new
level. If $\kappa = 1 $, the parent is given the new level and the new particle is given the original
level. Consequently, for $t \geq \tau$
\begin{align}\label{eq: Spatial evolution of individual lineage}
X_{\tau}(\tau+t)=&X_{\tau}(t)\\
&+\int_{(0,t]\times[0,\infty]\times[0,1]\times\{0,1\}}\mathbbm{1}_{U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(\tau+s-), \overline{\eta}(\tau+s-))}<\lambda\}}\kappa    H(X_{\tau}(\tau+s-), \overline{\eta}(\tau+s),\omega) \\
&\qquad \times \xi_{\tau}(ds,dv,dw,d\kappa).
\end{align}
Starting with an initial particle at level $U_{(0,i)}$ , we can identify a potential line of descent by
taking $(s_1 , v_1 , w_1 , \kappa_1 ) \in \xi_{(0,i)}$ , setting $\tau_1=s_1$ , and then recursively taking $(s_k , v_k , w_k , \kappa_k ) \in \xi_{\tau_k }$ and defining $\tau_{k+1} = \tau_{k} + s_{k+1}$. Each time $\tau$ at which a new level appears has an “ancestory” of this type.\\
We now explain the cases where $\kappa_k=0$ and $\kappa_k=1$. When $\kappa_k=0$, the parent retains the level, so $X_{\tau_{k}}$ remains the same at time $\tau_{k+1}$. When $\kappa_k=1$, the offspring gets its parent's level while the parent inherits a new level sampled between $[U_{\tau_k}(\tau_{k+1}-),\lambda]$. As a result, the spatial location $X_{\tau_{k}}$ jumps from the parent's location to the offspring's location at time $\tau_{k+1}$.  Meanwhile, between $[\tau_k, \tau_{k+1}]$ there maybe further birth events generated by $\xi_{\tau_k}$. If $(s,v,w,\kappa) \in \xi_{\tau_k}$, Equation \eqref{eq: Spatial evolution of individual lineage} holds and gives the spatial evolution of $X_{\tau_k}$ for $t \in [\tau_k, \tau_{k+1}]$.\\

For $\tau=\tau_m$ in a recursion like this, let
\begin{equation}\label{eq: Individual Evolution Recursion Terms}
\zeta^{0}_{\tau}(B)=\sum_{k=1}^{m}\delta_{(s_k,v_k,w_k,(1-\kappa_k))}, ~~~ V_{\tau}(t)=\sum_{k=1}^{m}v_k\mathbbm{1}_{[0, \tau_k]}  (t)  
\end{equation}
and define $U_{\tau}(0)=U_{(0,i)}, X_{\tau}(0)=X_{(0,i)}(0)$, and $\zeta_{\tau}$ by
\begin{equation}\label{eq: integrand in spatial tracing}
\zeta_{\tau}(B)=\zeta_{\tau}^{0}(B)+\sum_{k=0}^{m}\int \mathbbm{1}_{B}(\tau_k+s,v,w,\kappa)\mathbbm{1}_{\{\tau_k+s<\tau_{k+1}\}}\xi_{\tau_k}(ds,dv,dw,d\kappa)    
\end{equation}

where $\tau_{m+1}=\infty$. Then

\begin{align*}
U_{\tau}(t)=&U_{\tau}(0)+\int_{0}^{t}\frac{1}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(s-), \overline{\eta}(s-))}dV_{\tau}(s)\\
&+\int_{0}^{t}\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(s-), \overline{\eta}(s-))U^2_{\tau}(s)-b_{\varepsilon,\theta, \lambda}(X_{\tau}(s),\overline{\eta}(s))U_{\tau}(s))ds,\\  
X_{\tau}(t)=&X_{\tau}(0)+\int_{(0,t]\times[0,\infty]\times[0,1]\times\{0,1\}}\mathbbm{1}_{U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(\tau+s-), \overline{\eta}(\tau+s-))}<\lambda\}}\\
&\qquad \times \kappa   H(X_{\tau}(s-), \overline{\eta}(s-),\omega)\zeta_{\tau}(ds,dv,dw,d\kappa)
\end{align*}
gives the spatial and level dynamics of a lineage. Note that $\zeta^{0}_{\tau}(B)$ produces spatial jumps when $\kappa_k=1$, while the integral against $\xi_{\tau_k}$ in Equation \eqref{eq: integrand in spatial tracing} gives spatial jumps when $(s,v,w,\kappa) \in \xi_{\kappa_k}$, $\tau_k \leq s \leq \tau_{k+1}$, and $\kappa = 1$. This corresponds to the discussion given above.
\begin{remark}
The factor $\frac{1}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(x, \overline{\eta})}$ that scales the jump in levels give an average birth rate of $\theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(s-), \overline{\eta}(s-))$. This is because for the potential birth to be a true birth, we impose that $$U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(\tau+s-), \overline{\eta}(\tau+s-))}< \lambda,$$ where $U_{\tau}(\tau+s)$ is uniformly distributed between $[0, \lambda]$. As a result, a true birth occurs between $[0,\delta t]$ if there exists $(s,v) \in [0,\delta t]\times [0, 2 (\lambda-U_{\tau}(\tau+s)) \lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(\tau+s-), \overline{\eta}(\tau+s-))]$. Averaging this over levels give a Poisson process with rate $ \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(\tau+s-), \overline{\eta}(\tau+s-))$. 
\end{remark}
\begin{remark}
Although the labelling presented here depends on random birth times, we can label each individual in the population deterministically with the Ulam-Harris label. We therefore have a countable particle system. In particular, we can now express our particle systems as
$$\eta(t)=\frac{1}{\lambda}\sum_{U_{\tau}(t) < \lambda} \delta_{X_{\tau}(t),U_{\tau}(t)}, ~~\overline{\eta}(t)=\frac{1}{\lambda}\sum_{ U_{\tau}(t) < \lambda} \delta_{X_{\tau}(t)}.$$
For further discussion refer to \S \ref{sec: Ulam-Harris Labels characterisation}.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Proofs}

\comment{
    To prove convergence, we'll be proving
    (a) tightness
    (b) convergence of generators, and
    (c) uniqueness of the limit.
}

% % % % % % % % % % % % %
\subsection{Tightness of empirical measures}

\comment{In which we Gronwall $\langle 1, \eta_t\rangle$ and the like.}

% % % % % % % % % % % % %
\subsection{Convergence of generators}

% % % % % % % % % % % % %
\subsection{Uniqueness of the limit}

\comment{... for the cases in which we can prove that}

% % % % % % % % % % % % %
\subsection{Convergence of the nonlocal equation to the local equation}

\comment{... for the cases in which we know this.
This then shows that we can take the local, deterministic limit
by taking $\theta, N \to \infty$ first, and then $\epsilon \to 0$ after.
}

% % % % % % % % % % % % %
\subsection{Simultaneous scaling with interaction distance}

\comment{
    Convergence of generators along (something like) the diagonal,
    taking $\epsilon \to 0$ at the same time as the other coefficient.
    (We won't prove tightness here.)
}

% % % % % % % % % % % % %
\subsection{Tightness of the lookdown process}

\comment{
    This comes later because it uses convergence of the population process itself.
}

% % % % % % % % % % % % %
\subsection{Motion of ancestral lineages}

\comment{
    The proof of the theorem on lineages using the lookdown representation.
}

\bibliographystyle{plainnat}
\bibliography{refs.bib}

\end{document}

### 2022-04-05 forwards-and-backwards.tex
edits on the plane

@@
 
-\newenvironment {proof}{{\noindent\bf Proof.}}{\hfill $\Box$ \medskip}
+\newenvironment {proof}{{\noindent\bf Proof }}{\hfill $\Box$ \medskip}
 
@@
 \newcommand{\ind}{\mathbf{1}}
+\newcommand{\bigO}{\mathcal{O}}
+\newcommand{\grad}{\nabla}
+
+%%%%%%% notation
+\newcommand{\DG}{\mathcal{B}}  % generator of the dispersal process
+\newcommand{\meanq}{\vec b}    % mean of dispersal, times theta
+\newcommand{\covq}{\Sigma}     % covariance matrix of dispersal, times theta
+\newcommand{\kernel}{\varrho}  % interaction kernels
+\newcommand{\smooth}[1]{\kernel_{#1} \! * \!}  % convolution by the interaction kernel
+\newcommand{\wavespeed}{\mathfrak{c}}    % speed (vector) of a wave
+\newcommand{\Lgen}{\mathcal{L}}    % generator of a lineage
+\newcommand{\Pgen}{\mathcal{P}}    % generator of the population process
 
@@
 \begin{document}
-\pagenumbering{arabic}
 
@@
 
+\plr{I have not edited the introduction yet! It's just a pile of words. Skip to the next section.}
+
 \todo[inline]{
@@
 is specifically motivated by biological considerations.
-
-The porous medium equation with logistic growth is an example of a
-reaction-diffusion equation with a nonlinear diffusion term.
-Such equations are widely used in a number of contexts in biology in which
-it is clear that motility within a population varies with population density.
-For example, density dependent dispersal is a common feature in spatial
-models in ecology, eukaryotic cell biology, and avascular tumour growth;
-see e.g.~\cite{sherratt:2010} and references therein for further discussion. 
-We shall pay particular attention to the case in which the equation can be 
-thought of as modelling the density of an expanding population. 
-The specific equation that we use to illustrate the implications of
-our results is one of a class used to study pattern formation in 
-bacterial colonies. In particular, it has been suggested as a model for
-the expansion of bacteria of the type {\em Paenbacillus dendritiformis} on
-a thin layer of agar in a petri dish, 
-\cite{cohen/golding/kozlovsky/benjacob/ron:1999}.
 
@@
 
+% % % % % % % % % % % % % %
+\subsection{Structure of the paper}
+
+In the paper we study scaling limits of spatial popultaions,
+obtaining convergence of both the population process
+(i.e., the population density as a function of time,
+although strictly speaking it is a measure that may not have a density)
+as well as of lineages traced back through such a population.
+We retain linages through the rescaling process
+by means of a lookdown construction, which adds technical difficulty
+to an already difficult topic.
+Furthermore, convergence results for the lookdown process
+require convergence of the population process.
+So, we do not introduce the lookdown process until Section X.
+
+First, in section X, we describe the model and the main theorems (Theorems X and Y).
+Next, in section X, we discuss a few striking consequences of these results,
+namely, X Y and Z.
+In section X, we provide heuristic explanations
+of why the theorems ought to be true,
+and some key ideas behind them.
+In Section X we define and discuss the lookdown process that retains the levels.
+This is followed by the technical proofs in section X.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Notes to ourselves}
+
+\plr{For recording/discussing notation decisions.}
+
+$X$ is the original, unscaled process,
+and $\eta(t) = X(t\theta)/N$.
+
+When the process has a density, it is $\varphi(t, x) = d \eta_t(dx)/dx$.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\plr{Description of the model:}
-
-\plr{Main results (theorems without lookdowns):}
+The model we work with is a fairly general model
+of individuals living in continuous space.
+We shall suppose that we start with a population of
+$\bigO(N)$ individuals per unit area distributed in $\mathbb{R}^d$.
+For applications, $d=1$ or $d=2$, but our results apply more generally.
+The population will be distributed over a bounded region,
+so the total number of individuals will also be $\bigO(N)$.
+We describe the state of the population at time $t$
+with a counting measure $X(t)$,
+which assigns one unit of mass to the location of each individual.
+Locations need not be unique, so some locations may have a mass of greater than 1.
+
+It will be simplest to think of the population as evolving in continuous time
+and giving birth to one offspring at a time.
+Population dynamics are controlled by three quantities,
+birth, establishment, and death,
+each of which can depend on spatial location and local population density.
+Each individual gives birth at rate $\gamma$ to a single offspring,
+and the offspring
+then disperses according to a kernel $q(\cdot)$ away from the location of the parent.
+We assume that $q$ is the density of a multivariate Gaussian,
+allowing a nonzero mean and inhomogeneous variance.
+The offspring does not necessarily survive to be counted in the population:
+it ``establishes'' with probability $r$,
+or else it dies immediately.
+Independently, each individual dies with rate $\mu$.
+
+We aim to obtain universal behavior by taking the density, $N$, to infinity,
+and also scaling time by a factor of $\theta$,
+so that defining $\eta(t) = X(\theta t) / N$,
+the process $\{\eta(t)\}_{t \ge 0}$
+will converge to a suitable measure-valued process
+as $N$ and $\theta$ tend to infinity,
+with the nature of the limit depending on how they tend to infinity together.
+Demographic rates in our model
+will be determined by local population density relative to $N$,
+so that population dynamics depend more naturally on $\eta$ (rather than $X$).
+However, to avoid confusion arising from the time scaling,
+we describe the model in terms of $X$ next.
+See Figure~\ref{fig:model_setup} for a conceptual depiction.
+
+\begin{figure}
+    \begin{center}
+        FIGURE
+    \end{center}
+    \caption{
+        Conceptual figure of the model.
+        Left: (cartoon) plot of $\gamma$, $r$, $\mu$, and $F$ against density,
+        showing the equilibrium point.
+        Right: cartoon of interaction and dispersal distances.
+        \label{fig:model_setup}
+    }
+\end{figure}
+
+Birth, establishment, and death can depend on the location of the individual
+and the local population density.
+Since we would like the population density to scale with $N$,
+these are functions of $X/N$, i.e.,
+the counting measure with mass $1/N$ placed at the location of each individual.
+To measure local population density, we convolve the population measure with
+an ``interaction kernel'' -- for simplicity, we take these to be Gaussian
+with various scales, and write
+$$
+    p_{\sigma^2}(x) = \frac{1}{(2 \pi \sigma^2)^{d/2}} e^{-\|x\|^2 / 2 \sigma^2} .
+$$
+Given a nonnegative function $\gamma(x, m) : \IR^d \times \IR_{\ge 0} \to \IR_{\ge 0}$,
+the birth rate of an individual at location $x$ when the state of the population is $X$
+is $\gamma(x, \smooth{\gamma} X(x) / N)$,
+where $\smooth{\gamma} X$ is the convolution of $X$
+with $p_{\epsilon_\gamma^2}$.
+Similarly, the establishment probability of an offspring at location $x$ is
+is $r(x, \smooth{r} X(x) / N)$,
+where $r(x, m) : \IR^d \times \IR_{\ge 0} \to [0, 1]$
+and again $\smooth{r} p_{\epsilon_r^2}$.
+Rather than defining a function $\mu(x, m)$ for the death rate,
+it turns out to be more convenient to parameterize in terms of the net reproductive rate,
+which we denote by $F(x, m)$,
+scaled by $1/\theta$
+so that the population density changes over a time scale of $\theta$,
+i.e., we have ``near-critical branching''.
+Informally, we would like that
+$$
+    F = \theta (r \gamma - \mu) ,
+$$
+and to arrange this we define
+the death rate of an individual at $x$ to be
+\begin{align} \label{eqn:mu_defn}
+    \mu
+    =
+    \max\left\{0, 
+        r(x, \smooth{r} X(x) / N) \gamma(x, \smooth{\gamma} X(x) / N)
+        - \frac{1}{\theta} F(x, \smooth{F} X(x) / N)
+    \right\} ,
+\end{align}
+where again $F(x, m) : \IR^d \times \IR_{\ge 0} \to \IR_{\ge 0}$
+and $\kernel_F = p_{\epsilon_F^2}$.
+
+In summary, demographic parameters depend on local density measured
+for birth over a scale of $\epsilon_\gamma$,
+for establishment over a scale of $\epsilon_r$,
+and for net reproductive rate over a scale of $\epsilon_F$.
+Note that death rates depend in principle on population densities at three different scales,
+so that we could write $\mu = \mu(x, \smooth{\gamma} X(x) / N, \smooth{r} X(x) / N, \smooth{F} X(x) / N)$.
+It might seem like
+we have introduced unnecessary complexity
+with these three different spatial scales on which interactions occur.
+However,
+it will turn out to be useful in the proofs to have $\epsilon_r < \epsilon_\gamma$,
+although in the limit they can be taken equal to each other,
+so informally we think of local density as being determined on a scale of $\epsilon$.
+The value of $\epsilon_F$ is unconstrained.
+
+\begin{remark}
+Although this model allows fairly general birth and death mechanisms,
+there are a number of limitations.
+Perhaps most obviously, to simplify the notation
+individuals give birth to only one offspring at a time,
+although this restriction could be easily lifted
+\citep[as in][]{etheridge/kurtz:2018}.
+Furthermore, individuals do not move during their lifetime,
+and the age of an individual does not affect their fecundity or death rates.
+Finally, there is no notion of mating,
+so availability of mates will not restrict the spread of a population,
+and the lineages we follow will be uniparental.
+For these reasons, the model is most obviously applicable to bacterial populations,
+although we do not anticipate that incorporation of these complications
+will change the general picture.
+\end{remark}
+
+We next summarize the dynamics of the rescaled model $\eta(t) = X(\theta t)/N$,
+and state some assumptions on the parameters.
+
+\begin{definition}[Model parameterization and assumptions]
+    \label{def:model_setup}
+    For each $\theta \ge 0$,
+    let $\left(\eta^\theta(t)\right)_{t \ge 0}$
+    be the continuous-time measure-valued Markov process described above
+    with birth rates, establishment probabilities, and death rates
+    determined as follows.
+    Suppose $\gamma(x, m)$, $r(x, m)$, and $F(x, m)$
+    are bounded, uniformly continuous functions
+    from $\IR^d \times \IR_{\ge 0}$ to $\IR_{\ge 0}$.
+    Furthermore, suppose $r_\theta$ takes values in $[0, 1]$
+    and has uniformly bounded second derivatives,
+    and that $(x, m) \mapsto m^2 \gamma(x, m)$ is unformly bounded.
+    Fix nonnegative values $\epsilon_r$, $\epsilon_\gamma$, and $\epsilon_F$,
+    with $\epsilon_r < \epsilon_\gamma - 1/\theta$.
+    Suppose $F: \IR^d \times \IR_{\ge 0} \to \IR$ is bounded and uniformly continous
+    and define
+    \begin{align}
+        \mu(x, \eta)
+        =
+        r(x, \smooth{r} \eta(x))
+        \gamma(\smooth{\gamma} \eta(x))
+        - \frac{1}{\theta}
+        F(x, \smooth{F} \eta(x)) .
+    \end{align}
+    Let $N$ be a positive number determined by $\theta$.
+    When the state of the process is $\eta$,
+    offspring of mass $1/N$ are produced at location $x$
+    with rate $\theta \gamma(x, \smooth{\gamma} \eta(x)) N \eta(dx)$
+    and adults die at location $x$ with rate $\theta \mu(x, \eta) N \eta(dx)$,
+    (i.e., at rates $\theta \gamma$ and $\theta \mu$ per capita respectively).
+    Offspring disperse to a location offset from the parent's location
+    by an independent Gaussian with mean $\meanq/\theta$
+    and covariance matrix $\covq / \theta$;
+    an offspring at $x$ establishes instantaneously
+    with probability $r(x, \smooth{r} \eta(x))$, or else dies.
+\end{definition}
+
+Since we are taking a diffusion limit,
+we will have use for the following notation:
+
+\begin{definition}[Dispersal generator]
+    \label{def:dispersal_generator}
+    Recall that we have defined the dispersal kernel,
+    $q_\theta(x, dy)$,
+    to be the density of a multivariate Normal
+    with mean $\meanq/\theta$ and covariance matrix $\covq/\theta$.
+    This implies that if we define, for $f : \IR^d \to \IR$,
+    \begin{align}
+    \DG f(x) = \sum_i \meanq_i \partial_{x_i} f(x)
+        + \sum_{ij} \covq_{ij} \partial_{x_i} \partial_{x_j} f(x)
+    \end{align}
+    then
+    \begin{align}
+        \theta \int \left(
+            f(y) - f(x)
+        \right) q_\theta(x, dy)
+    \to \DG f(x) 
+        \qquad \text{as } \theta \to \infty .
+    \end{align}
+\end{definition}
+
+\paragraph{Remark:}
+An equivalent way to describe the model
+would be to say that an individual at $x$ gives birth at rate
+$$
+    \gamma(x, \smooth{\gamma} \eta(x))
+    \int r(x, \smooth{r} \eta(y)) q(x, dy) ,
+$$
+and that offspring disperse according to the kernel
+$$
+    q_\theta^\mathfrak{m}(x, dy)
+    :=
+    \frac{
+        r(y, \smooth{r} \eta(y)) q_\theta(x, dy)
+    }{
+        \int r(x, \smooth{r} \eta(z)) q_\theta(x, dz)
+    } .
+$$
+Clearly, the random walk driven by this dispersal kernel
+should be biased towards regions of higher establishment probability.
+For comparison to future results,
+it is interesting to write down the limiting generator:
+\begin{align*}
+    \lim_{\theta \to \infty}
+    \theta \int (f(y) - f(x)) q_\theta^\mathfrak{m}(x, dy)
+    &=
+    \frac{
+        \DG\left[ f(\cdot) r(\cdot, \smooth{r} \eta(\cdot)) \right](x)
+        - 
+        f(\cdot) \DG\left[ r(\cdot, \smooth{r} \eta(\cdot)) \right](x)
+    }{
+        r(x, \smooth{r} \eta(x))
+    } .
+\end{align*}
+In the simplest case of unbiased, isotropic dispersal,
+$\meanq = 0$ and $\covq = I$, so $\DG = \Delta$,
+and this is equal to
+\begin{align*}
+    \Delta f(x) + 2 \grad f(x) \cdot \grad \log r(\cdot, \smooth{r} \eta(\cdot))(x) .
+\end{align*}
+However, we will see that following a lineage back through the population
+has a different behavior yet again.
+
+% % % % % % % % % % % % % % %
+\subsection{Main results on population processes}
 
 \comment{
-There are two dichotomies:
+Set-up: there are two dichotomies:
 is the limiting process deterministic or a generalized superprocess?
@@
 Below we have results for three of these cases;
-as for the remaining one (local, superprocess)
-TODO: write a note about what happens there (should be possible in 1D, not in higher dimensions).
-}
-
-We shall suppose that we start with a population of
-$\mathcal{O}(N)$ individuals per unit area distributed in $\mathbb{R}^d$.
-In applications we would typically take $\mathbb{R}^2$ or a subset thereof,
-although our mathematical results apply in any spatial dimension.
-We shall denote the state of the population at time $t$ by $\mathcal{S}_t$
-and we shall abuse notation by treating $(\mathcal{S}_t)_{t \geq 0}$
-as both the set of locations of the individuals
-and a counting measure in which each individual has mass $1$, 
-with the understanding that multiple 
-points are treated as distinct individuals.  
-The parameter $N$ will tend to infinity in our scaling limits, and the 
-measure $(\overline{\eta}_t)_{t \geq 0} := (N^{-1} \mathcal{S}_t)_{t \geq 0} $ will converge (weakly) in the space of 
-$\sigma$-finite measures on $\mathbb{R}^d$.
-
-It will be simplest to think of the population as evolving in continuous time
-and giving birth to one offspring at a time.
-The rate at which a juvenile offspring is produced by an individual
-will depend on the local population density.
-We will write $\gamma(x,\overline{\eta})$ for the rate at which an
-individual at location $x$ produces a juvenile offspring
-when the state of the population is $\overline{\eta}$,
-and $q(x,dy)$ for the distribution of the location of the juvenile 
-when the parent is at $x$.
-These offspring do not necessarily survive to be counted in the population:
-we write $r(y, \overline{\eta})$ for the 
-probability of successful establishment (survival to maturity)
-of a juvenile at $y$.
-It is assumed that maturity is achieved instantaneously,
-and we shall only track mature individuals.
-Finally, each mature individual located at the point $x$ dies at 
-instantaneous rate $\mu(x,\overline{\eta})$.
-
-\plr{I moved up the description of the interaction kernel here,
-    so that the whole description of the model is in one place.
-    I think this is good, but: some of our results don't depend on this assumption,
-    which we should make more clear here. And: do we always use the heat kernel
-    for $\varrho$? If so, we should just say so here.  }
-Since we are interested in models where interactions are \emph{local},
-i.e., reproduction, establishment, and death depend only
-on the geographically local environment.
-To this end,
-we suppose that the birth rate of an individual at $x$
-depends on the state of the population only through
-a locally averaged density.
-Concretely,
-given an \emph{interaction distance} $\varepsilon$,
-and a probability density $\varrho$ (the \emph{interaction kernel})
-we will suppose that
-$\gamma(x, \overline{\eta})$, $r(x, \overline{\eta})$, and $\mu(x, \overline{\eta})$
-are functions only of $x$ and
-\begin{align*}
-    \varrho_\varepsilon * \overline{\eta}(x)
-    := \int \varepsilon^{-d} \varrho(x/\varepsilon)(x-y) \overline \eta(dy)
-    .
-\end{align*}
-To make the notation less complex, however,
-we'll not formalize this until later (\S~\ref{sec: Main Theorems on Convergence}).
-
-\begin{remark}
-This model can be easily generalised into one
-in which the number of offspring is drawn from a distribution,
-\parencite[as in][]{etheridge/kurtz:2018}
-and the main statements in our paper will still hold.
-We have adopted this simple birth model
-so we may demonstrate our proof in a more palatable manner.
-\end{remark}
+as for the remaining one (local, superprocess),
+it should be possible in 1D, not in higher dimensions (brief note).
+}
 
@@
 
-\plr{Main theorem 1:}
-
-\begin{theorem}\label{teo: Main Convergence Theorem - non-linear superprocess}
- Let $(\overline{\eta}^{\varepsilon, \theta,N}(t))_{t \geq 0}$ be the re-scaled model defined in Definition \ref{Def: Rescaled Models} and assume that as $\theta \to \infty$, $N \to \infty$, $\varepsilon(\theta)$ remains constant and $\theta/N \to \ell$.\\~\\
-    The sequence of stochastic processes $(\overline{\eta}^{\varepsilon,\theta,N}_t)_{t \geq 0}$ converges weakly (analytically) in distribution as $\theta \to \infty$ to a measure-valued process $(\Xi^\varepsilon_t)_{t \geq 0}$ which satisfies that, for every $f:\mathbb{R}^d \rightarrow \mathbb{R}$,
-\begin{align*} M_t &:= \langle f(x), \Xi^\varepsilon_t(dx) \rangle - \langle f(x), \Xi^\varepsilon_0(dx) \rangle \\ &- \int_0^t \big\langle \gamma(x,\varrho_{\varepsilon}*\Xi^{\epsilon}_{s}(x)) \mathcal{B}(f(\cdot)r(\cdot,\varrho_{\varepsilon}*\Xi^{\epsilon}_{s}(\cdot))(x) + f(x)  F(x,\varrho_{\varepsilon}*\Xi^{\epsilon}_{s}(x)), \Xi^\varepsilon_s(dx) \big\rangle ds, \end{align*}
-is a martingale. The quadratic variation of $M_t$ is given by 
+\begin{theorem} \label{thm:nonlocal_convergence}
+    Let $(\eta^\theta_t)_{t \geq 0}$
+    be as defined in Definition \ref{def:model_setup}
+    and assume that as $\theta \to \infty$, $N \to \infty$
+    in such a way that $\theta/N \to \delta$.
+    (However, interaction distances $\epsilon_r$, $\epsilon_\gamma$, and $\epsilon_F$
+    remain constant.)
+
+    The sequence of stochastic processes
+    $(\eta^\theta_t)_{t \geq 0}$
+    converges along subsequences in distribution as $\theta \to \infty$
+    to a measure-valued process $(\eta_t)_{t \geq 0}$
+    which satisfies that, for every $f:\mathbb{R}^d \rightarrow \mathbb{R}$,
+    \begin{align} \label{eqn:mgale_problem}
+        M_t
+        &:=
+        \langle f(x), \eta_t(dx) \rangle
+        -
+        \langle f(x), \eta_0(dx) \rangle
+        \\ & \qquad
+        -
+        \int_0^t \big\langle
+            \gamma(x, \smooth{\gamma} \eta_s(x))
+            \mathcal{B}\left(
+                f(\cdot) r(\cdot, \smooth{r} \eta_s(\cdot))
+            \right)(x)
+            +
+            f(x)
+            F(x, \smooth{F} \eta_s(x)),
+            \eta_s(dx)
+        \big\rangle ds,
+    \end{align}
+    is a martingale.
+    The quadratic variation of $M_t$ is given by 
+    \begin{align} \label{eqn:mgale_variation}
+        [ M ]_t
+        =
+        \delta
+        \int_0^t
+        \big\langle
+            \gamma\left( x, \smooth{\gamma} \eta_s(x) \right)
+            r\left(x, \smooth{r} \eta_s(x) \right)
+            f^2(x),
+            \eta_s (dx)
+        \big\rangle ds. 
+    \end{align}
+    In other words, the limit is a measure-valued process with non-local interactions.
+    Furthermore, if $\delta = 0$ the limit is deterministic.
+\end{theorem}
+
+Theorem \ref{thm:nonlocal_convergence} provided convergence along subsequences;
+i.e., for any sequence of values of $\theta$
+there is a subsequence that converges.
+However, if the limiting process is unique then the convergence is unqualified.
+In the deterministic case, we have convergence to a nonlocal PDE.
+\comment{Maybe the following two corollaries should be combined?}
+
+\comment{
+    \textbf{Question:}
+    In our outline
+    we said this corollary would be about uniqueness,
+    but is it also about continuity of the limit (i.e., existence of a density)?
+    A lot of my uncertainty in how to phrase these results
+    comes from being unsure what exactly we can say about densities.
+}
+
+\begin{corollary}[Deterministic limits]
+    \label{cor:nonlocal_pde_limits}
+    In the context of Theorem~\ref{thm:nonlocal_convergence},
+    if the limit is deterministic (i.e., $\theta / N \to \delta = 0$), $\eta_0$ has a density,
+    and \comment{additional conditions? can we say something like this??}
+    then any limit $\eta_t(dx)$ has a density $\varphi(t, x)$,
+    which is a weak solution to the nonlocal partial differential equation
+    \begin{equation} \label{eqn:nonlocal_pde}
+        \partial_t \varphi(t, x)
+        =
+        r\left(x, \smooth{r} \varphi(t,x) \right)
+        \mathcal{B} \left[
+            \varphi(t, \cdot)
+            \gamma\big( x, \smooth{\gamma} \varphi(t, \cdot) \big)
+        \right](x)
+        +
+        \varphi(t, x)
+        F\left(x, \smooth{F} \varphi(t,x) \right)
+        .
+    \end{equation}
+    If equation \eqref{eqn:nonlocal_pde} has a unique solution,
+    then $(\eta^\theta_t)_{t \ge 0}$ converges to that solution.
+
+    In particular, if
+    \comment{TODO: find some conditions under which this is true?}
+    then we have convergence to a unique solution.
+\end{corollary}
+
+Informally, equation \eqref{eqn:nonlocal_pde} is the PDE
+\begin{align} \label{eqn:pde}
+    \dot \varphi = r \DG\left( \gamma \varphi \right) + \varphi F ,
+\end{align}
+where $\DG$ is an elliptic second order differential operator,
+and the coefficients $r$, $\gamma$, and $F$
+at $x$ depend nonlocally on $\varphi$
+(i.e., through a smoothed version of $\varphi$).
+
+\begin{corollary}[Superprocess limits] \label{cor:superprocess_uniqueness}
+    In the context of Theorem~\ref{thm:nonlocal_convergence},
+    if the martingale problem
+    defined by equations \eqref{eqn:mgale_problem} and \eqref{eqn:mgale_variation}
+    has a unique solution,
+    then $(\eta^\theta(t))_{t \ge 0}$ converges to that solution
+    as $\theta \to \infty$.
+    \comment{
+        Is this what we want to say here? Could be said better.
+        TODO: see what Dawson \& Li say about uniqueness
+        so we have at least some conditions under which this happens.
+    }
+\end{corollary}
+
+Theorem~\ref{thm:nonlocal_convergence} shows convergence to the solution to a nonlocal PDE
+of the form \eqref{eqn:nonlocal_pde}.
+Since the coefficients at $x$ in \eqref{eqn:nonlocal_pde}
+depend only on the region nearby to $x$,
+we would often expect solutions of the nonlocal PDE to be close to the corresponding local PDE
+as the interaction distances $\epsilon_r$, $\epsilon_\gamma$ and $\epsilon_F$
+go to zero.
+The following propositions give two concrete situations in which that is true.
+
+\comment{I've not got straight exactly how we're framing this
+    (namely, does $\eta$ have a density?).
+    Also, is this one or two propositions --
+    we said initially this would be two,
+    one for FKPP and one for PME,
+    but then maybe the argument was more general?
+}
+
+\begin{proposition}
+    \label{prop:nonlocal_to_local}
+    Suppose that $\eta_\epsilon(t,dx)$ is a solution to equation \eqref{eqn:nonlocal_pde}
+    with $r(x, m) = 1$ for all $x$ and $m$
+    and some $\epsilon_r < \epsilon_\gamma = \epsilon_F = \epsilon$
+    \comment{and assumptions on $\gamma$? and $F$?}.
+    Then $\eta_\epsilon(t, dx)$ converges \comment{in what sense?} as $\epsilon \to 0$
+    to $u(t, x) dx$, which solves
+    \begin{align} \label{eqn:PDE}
+        \partial_t u(t, x)
+        =
+        \DG \left( \gamma(\cdot, u(t, \cdot) u(t, \cdot)  \right)(x)
+        + F(x, u(t, x)) u(t, x) .
+    \end{align}
+\end{proposition}
+
+Theorem \ref{thm:nonlocal_convergence} combined with Proposition \ref{prop:nonlocal_to_local}
+imply that we can take the $\theta \to \infty$ limit
+followed by $\epsilon \to 0$
+to obtain solutions to the PDE \eqref{eqn:PDE}.
+However, it is of substantial interest to know whether
+we can take those two limit simultaneously.
+The general case seems difficult,
+but we can prove such ``diagonal'' convergence in the following situation.
+
+\begin{theorem}[Convergence to a PDE]
+    \label{thm:local_convergence}
+    Let $(\eta^\theta_t)_{t \geq 0}$
+    be as defined in Definition \ref{def:model_setup}
+    and assume that as $\theta \to \infty$, $N \to \infty$
+    and $\epsilon_r < \epsilon_\gamma = \epsilon_F = \epsilon \to 0$
+    in such a way that $\theta/N \to 0$
+    and
+    \comment{TODO: some conditions on $\epsilon$ and $r$ and $\gamma$ and $F$}.
+    Then the sequence of stochastic processes $(\eta^\theta_t)_{t \ge 0}$
+    converges \comment{in some sense}
+    to a measure-valued process with a density $\varphi(t, x)$
+    that solves
+    \begin{align}
+        \partial_t \varphi(t, x)
+        &=
+        \text{whatever the final form is here} .
+    \end{align}
+\end{theorem}
+
+% % % % % % % % % % % %
+\subsection{Main results on lineages}
+
+Now that we have established what we can say about how population density changes with time,
+we turn to results on ancestral lineages,
+i.e., how genealogical ancestry moves across the landscape.
+Informally,
+a \emph{lineage} $(L_t)_{t \ge 0}$
+begun at spatial location $L_0 = x$
+can be obtained by picking a focal individual uniformly at $x$,
+and then for each amount of time $t$ in the past,
+setting $L_t$ to the spatial location of the individual from whom
+the focal individual inherits.
+Since in our model individuals have only one parent, this is unambiguous.
+Although we did not explicitly retain such information,
+it is clear that
+for finite $\theta$ (and hence, finite $N$),
+one could construct the distribution of a lineage $(L_t)_{t=0}^T$
+given the history of the population $(\eta^\theta_t)_{t = 0}^T$,
+for each starting location to which $\eta^\theta_T$ assigns positive mass.
+It is less clear, however, how to formally retain such information in the limit.
+The \emph{lookdown construction} in Section~\ref{sec:lookdown}
+provides just such a construction,
+where lineages are retained in the $N \to \infty$ limit.
+Roughly speaking,
+this works by assigning to each particle a unique ``level''
+that functions as a label and thus allows reconstruction of lineages,
+but also (in some sense) orders individuals by eventual reproductive output,
+allowing a formal limit.
+See~\ref{etheridge/kurtz:2018} for an introduction to these ideas.
+
+A lineage is, in general, a well-defined stochastic process,
+but there are two important questions
+that affect its tractability.
+First, when is it a Markov process given the population process?
+(I.e., given $(\eta_t)_{t=0^T}$ that records numbers of individuals
+but not their ancestry.)
+We expect the answer here to be that a lineage is Markov
+only in the $N \to \infty$ limit.
+\comment{(or, do we know this? we can cite Barton, Depaulis and Etheridge at least for discussion.)}
+Second, does the process have a tractable description?
+If the population process has a density,
+then it turns out that a lineage is a diffusion driven by the density.
+The remaining case is the superprocess limit ($\theta/N \to \delta > 0$);
+in this case, we expect that a lineage could still be described as a generalized diffusion,
+but moving within a stochastic landscape that is singular in $d \ge 2$.
+We focus on the more tractable situation where the population process is deterministic.
+However, the results here apply to either the local or nonlocal case
+(i.e., where the density solves a local or nonlocal PDE).
+
+\comment{
+    \textbf{Note:} the previous write-up motivated things only in the time-stationary case
+    (so, a stationary traveling wave, possibly with wave speed zero;
+    see the corollary below).
+    It'd be very nice to give this more general result,
+    but the proof has to be checked to make sure it still applies,
+    and the notation is time-inhomogeneous and so more annoying
+}
+
+\begin{definition}[Generator of a lineage] \label{def:lineage_generator}
+    Let $(\varphi(x, t))_{0 \le t \le T}$
+    denote the density of a population that solves \eqref{eqn:nonlocal_pde},
+    and let $y$ be a point with $\varphi(y, T) > 0$.
+    We define $(L_s(y))_{s=0}^T$,
+    the ancestral lineage of an individual sampled at $y$ at time $T$,
+    to be the position of the unique ancestor of $y$ alive at time $T - s$.
+    We define
+    $(Q_s)_{s \geq 0}$
+    to be the time inhomogeneous semi-group satisfying
     \begin{align*}
-[ M ]_t = \int_0^t \ell\big\langle\gamma\big(x,\varrho_{\varepsilon}*\Xi^{\epsilon}_{s}(x)\big) r\big(x,\varrho_{\varepsilon}*\Xi^{\epsilon}_{s}(x)\big) f^2(x), \Xi^\varepsilon_s (dx) \big\rangle ds. 
+        Q_s f(y) := \IE_y[ f(L_s) ] ,
     \end{align*}
-In other words, the limit $(\Xi^\varepsilon_t)_{t \geq 0}$ is a measure-valued process with non-local interactions.
-Furthermore, if $\ell=0$ the limit is deterministic.
-In that case, if $\overline{\eta}^{\varepsilon,\theta}_0$ possesses a density in $L^2(\mathbb{R}^d)$, and the functions $\gamma$, $F$ are Lipschitz, then $(\overline{\eta}^{\varepsilon,\theta}_t)_{t \geq 0}$ possesses a density in $L^2(\mathbb{R}^d)$ and  $(\overline{\eta}^{\varepsilon,\theta}_t)_{t \geq 0}$ converges to a unique limit $(\Xi^\varepsilon(t))_{t \geq 0}$ with density $\varphi^\varepsilon(t,x)$ that solves (weakly) the mollified PDE of the form
-\begin{equation}\label{Eq: non-local density PDE equation}
-\partial_t \varphi(t,x) = r\big(x,\varrho_{\varepsilon}*\varphi(t,x)\big) \mathcal{B} \Big(\varphi(t,\cdot)\gamma\big(x,\varrho_{\varepsilon}*\varphi(t,\cdot)\big)\Big)(x) + \varphi(t,x) F\big(x,\varrho_{\varepsilon}*\varphi(t,x)\big)
+    and $\Lgen_s$ to be the generator of this semi-group.
+\end{definition}
+
+Our main result identifies a lineage as a diffusion
+by characterizing its generator.
+To avoid complexity,
+we do this in the case where dispersal is $N(\meanq/\theta, \sigma^2 I/\theta)$,
+in which case $\DG = \sigma^2 \Delta + \meanq \cdot \grad$.
+
+\comment{
+    Allowing a more general dispersal mechanism won't just entail replacing $\Delta$ with $\DG$,
+    it will also change at least one of the $\grad$s to something else (I think).
+}
+
+\begin{theorem} \label{thm:lineages}
+    In the context of Definition~\ref{def:lineage_generator},
+    if the dispersal process is isotropic (i.e., $\covq = \sigma^2 I$),
+    then
+    \begin{equation}
+        \label{eqn:lineage_generator}
+        \Lgen_s f
+        =
+        \sigma^2 r \gamma
+        \left(
+            \Delta f
+            +
+            \left(
+                2 \grad \log(\gamma \varphi)
+                - \meanq
+            \right)
+            \cdot \grad f
+        \right) .
     \end{equation}
+    In other words, 
+    a lineage behaves as a diffusion
+    that is driven by a Brownian motion 
+    run at speed $\sigma^2$ multiplied by the local per-capita production of offspring ($r \gamma$)
+    in a potential equal to the local birth output tilted by migraiton bias
+    ($\varphi \gamma \exp(-\meanq \cdot x / 2 \sigma^2)$).
 \end{theorem}
 
-\plr{Main theorem 2:}
-
-\begin{theorem}\label{teo: Main Convergence Theorem - local pde limit}
- Assume that $\theta/ N \to 0 $ and assume that $\varepsilon(\theta) \to 0$. The sequence of mollifiers $\varrho_{\varepsilon}$ thus converges weakly to the Dirac delta mass, i.e. 
-$\int_{\mathbb{R}^d} f(x)\varrho_{\varepsilon}(y-x)dx \to f(y)$. Assume furthermore that the following two conditions holds:
-\begin{enumerate}
-    \item The rate at which the local interaction strength $\varepsilon:=\varepsilon(\theta)$, speed $\theta$ and mass $\frac{1}{N(\theta)}$ scale satisfy the Equation 
-\begin{equation} \label{condepsilon}
-\frac{\theta}{N(\theta) \varepsilon(\theta)^{\frac{3 d p}{2}}} + \frac{1}{\theta \varepsilon(\theta)^{\frac{d p}{2}}} \xrightarrow[\theta \rightarrow \infty]{} 0,
-\end{equation}
-
-and $\overline{\eta}^{\varepsilon,\theta,N}_0$ is given by a Poisson point process with mean measure $\varphi_0(x)$.
-    \item As $\varepsilon \to 0$, the sequence of functions $\{\varphi^\varepsilon(t,x): \varepsilon > 0 \}$ defined in Definition \ref{def: Weak solution formulation, mollified version} converges uniformly in space for any fixed time $t > 0$ to the function $\{\varphi(t,x): x \in \mathbb{R}^d, t >0\}$  which solves the partial differential equation
-    \begin{equation}\label{eq: local PDE limit generalised}
-    \partial_t \varphi(t,x)=r(x,\varphi(t,x))\mathcal{B}\left(\varphi(t,\cdot) \gamma\big(\cdot,\varphi(t,\cdot)\big)\right)(x)+ \varphi(t,x)F\big(x,\varphi(t,x)\big)    
-    \end{equation}
-    with intial condition $\varphi(0,x)=\varphi_0(x)$.
-\end{enumerate}
-Then the sequence of stochastic processes $\{(\overline{\eta}^{\varepsilon, \theta,N}(t))_{t \geq 0}: \varepsilon > 0\}$ converges weakly (analytically) on finite dimensional distributions (in probability) to the deterministic process $\{\varphi(t,x): x \in \mathbb{R}^d, t >0\}$ defined in Equation \eqref{eq: local PDE limit generalised}.
-\end{theorem}
-
-\comment{Set-up and motivation for theorem on lineages.}
-In \S \ref{Sec: Lookdown Constructions}, we will introduce a lookdown construction for the model described in \S \ref{sec: individual based model}.
-A lookdown construction assigns each particle a unique level which enables us to do a richer analysis.
-The main interest in using a lookdown construction for our
-population processes is that it allows us to retain information 
-about relatedness between individuals as we pass to the infinite
-density limit. In particular, we are able to rigorously establish an equation for the motion of ancestral lineages in our limiting partial differential equation.
-
-Consider a population evolving according to one of our deterministic
-limiting models. We shall restrict ourselves
-to the setting in which the population is expanding as a travelling wave
-through $\IR$, with fixed profile $w(x)$ at rate $\mathfrak{c}$. That is 
-$$\Xi_t(x)=w(x-\mathfrak{c}t),$$
-for some fixed function $w$, and some $\mathfrak{c}\geq0$.  The profile $w$, if it exists, will satisfy
-\begin{equation}
-\label{profile}
-r\Delta(\gamma w)+F(w)+\mathfrak{c}\nabla w=0.
-\end{equation} 
-It is convenient to work in a moving frame so that the wavefront is fixed. In this setting we want to investigate the ancestry line of an individual.\\
-Note that in our model each individual has one parent only. As a result, as we go backwards in time, each individual has one unique ancestor at any time $t$.
-\begin{definition}\label{def: Ancestry Line}
-Let $w$ denote the wavefront of an evolving population that solves (\ref{profile}) and let $y \in supp(\Xi_t)$.
-We define $(L_s(y))_{s \geq 0}$, the ancestry line of an individual sampled at $y$, to be the position of the unique ancestor of $y$ at unit $s$ backwards in time.\\
-We define $(\hat{T}_s)_{s \geq 0}$ to be the semi-group satisfying
-$$\hat{T}_sf(y):=\mathbb{E}_{y}[f(L_s)]$$ and 
-$\hat{\mathcal{L}}$ to be its corresponding generator. 
-\end{definition}
-The mathematical formulation for $L_s(y)$ will be made explicit once we introduce lookdown construction in \S \ref{Sec: Lookdown Constructions} as it allows us to trace lineages through stochastic differential equations, see \S \ref{sec: stochastic equations for lineages}.
-
-\plr{Main Theorem 3}
-
-\comment{TODO: clarify that this applies to either local or nonlocal population limits}
-
-\begin{theorem} \label{teo:ancestral lineages}
-    Let $w$ denote the wavefront of an evolving population that solves (\ref{profile}).
-    Then the generator $\hat{\mathcal{L}}$ of the motion of an ancestral line of individuals in this population is given by
-    \begin{equation}
-    \label{eq: generator of lineage motions}
-        \hat{\mathcal{L}} \phi
-        =
-        r\gamma\left(\Delta\phi+2\frac{\nabla(\gamma w)}{\gamma w}\nabla\phi\right)
-        +\mathfrak{c} \nabla\phi.
-    \end{equation}
-\end{theorem}
-
-\comment{TODO: short note on why it doesn't make sense to do this for a superprocess
-         (it'd be Markov backwards in time given the population history probably,
-         but it would be like a diffusion on a singular, evolving space or something)
-}
+To make the generator readable, we've written it in concise notation,
+omitting the dependencies on location and population density,
+which itself changes with time.
+When interpreting this,
+remember that everything depends on location and density at that location and time --
+for instance, ``$r$'' is actually $r(x, \varphi(T-s, x))$.
+
+\comment{This corollary was the previous theorem in the previous draft.
+    Besides this proposed set-up, we have the additional options of
+    (a) renaming the corollary a theorem and only proving it,
+    or (b) presenting only the corollary here (as a theorem)
+    and presenting the more general theorem later on.
+}
+
+\begin{corollary} \label{cor:wavefront}
+    In addition to the assumptions of Theorem~\ref{thm:lineages},
+    suppose that the population process is described by a traveling wave with speed $\wavespeed$,
+    i.e., the population has density
+    $\varphi(t, x) = w(x - t \wavespeed)$
+    where $w$ solves
+    \begin{align*}
+        r \Delta (\gamma w) + w F(w) + \wavespeed \cdot \grad w = 0 .
+    \end{align*}
+    Then the generator $\Lgen$
+    of the motion of a linages in this population is
+    \begin{align}
+        \Lgen f
+        &=
+        r \gamma
+        \left(
+            \Delta f
+            +
+            2 \grad \log (\gamma w)
+            \cdot \grad f
+        \right)
+        + \wavespeed \cdot \grad f .
+    \end{align}
+\end{corollary}
 
@@
 
+Next,
+we cover some illustrative examples
+and interesting applications.
+
 % % % % % % % % % % % %
-\subsection{A nonlinear diffusive population: the Porous medium equation}
+\subsection{A nonlinear diffusive population: the Porous Medium Equation}
+
+\comment{
+    This section:
+    model set-up including the limit;
+    comparison of the simulation profile to deterministic solution.
+    See Figure \ref{fig:pme_waves}.
+}
+
+Consider the porous medium equation (PME) with logistic growth,
+\begin{equation}
+    \label{eqn:pme}
+    \partial_t v = \partial_x^2 (v^2) + v (1 - v) ,
+\end{equation}
+an example of a reaction-diffusion equation with a nonlinear diffusion term.
+Such equations are widely used in a number of contexts in biology in which
+it is clear that motility within a population varies with population density.
+For example, density dependent dispersal is a common feature in spatial
+models in ecology, eukaryotic cell biology, and avascular tumour growth;
+see e.g.~\cite{sherratt:2010} and references therein for further discussion. 
+We shall pay particular attention to the case in which the equation can be 
+thought of as modelling the density of an expanding population. 
+The specific equation that we use to illustrate the implications of
+our results is one of a class used to study pattern formation in 
+bacterial colonies. In particular, it has been suggested as a model for
+the expansion of bacteria of the type {\em Paenbacillus dendritiformis} on
+a thin layer of agar in a petri dish, 
+\cite{cohen/golding/kozlovsky/benjacob/ron:1999}.
+
+Comparing \eqref{eqn:pme} to \eqref{eqn:pde},
+we see that to set up a limit in which the population density $\varphi$ follows the PME,
+we need $r=1$,
+$\gamma = \varphi$, and $F = 1 - \varphi$.
+Consulting equation~\eqref{eqn:mu_defn},
+we then need death rate to be $\mu = (1 + 1/\theta) \varphi - 1/\varphi$.
+In other words,
+establishment is certain
+and birth rates to increase linearly with population density,
+but to compensate, death rates increase slightly faster (also linearly),
+as shown in Figure~\ref{fig:pme_waves}.
+Alert readers will notice that this violates our boundedness assumptions;
+\comment{(perhaps this is too much detail here)}
+in practice we choose a suitably small value for $\beta$ and define
+\begin{align*}
+    \gamma(x, m) &= (1 - \exp(- \beta m)) / \beta \\
+    F(x, m) &= \exp(- \beta m) / \beta ,
+\end{align*}
+which in turn implies that death rate when local density is $m$
+is roughly $(1 + 1/\theta) (1 - \exp(-\beta m)) / \beta - 1/(\theta \beta)$.
+Birth and death rates are equal at density $m = 1$,
+corresponding to an unscaled density of $N$ individuals per unit area.
 
@@
 
-\comment{
-    Model set-up including the limit;
-    comparison of the simulation profile to deterministic solution.
-    See Figure \ref{fig:pme_waves}.
-}
+This equation has an explicit travelling wave solution
+\begin{align} \label{eqn:pme_wave}
+    w^P(t, x)
+    :=
+    \left( 1 - e^{ \frac{1}{2} (x - x_0 - t) } \right)_+ .
+\end{align}
+Notice that the wave profile has a sharp boundary at $x = x_0 + t$.
+There are also travelling wave solutions with $c>1$ \citep{gilding/kersner:2005},
+which lack this property.
+However, for initial conditions that decay sufficiently rapidly at infinity,
+such as one might use in modelling a population invading new territory,
+the solution converges to \eqref{eqn:pme_wave} \citep{kamin/rosenau:2004}.
+
+Indeed, simulations of this process
+shown in Figure~\ref{fig:pme_waves}
+display traveling wave solutions
+similar to numerical solutions of the PME,
+with increasingly good agreement for larger $\theta$ and $N$.
+As expected, noise slows down the wave.
 
 % % % % % % % % % % % %
-\subsection{Traveling waves: FKPP versus PME}
+\subsection{Traveling waves}
 
@@
     \caption{
-        Four panels: left pair for FKPP, right for PME.
+        Six panels: one pair for FKPP, one for PME, and one for Allen-Cahn.
         Each pair shows (top) lineage traced back in wavefront,
@@
 \comment{
-    Explain generator in stationary frame;
+    This section:
+    explain generator in stationary frame;
     derive stationary distribution;
@@
 }
-\plr{Merge the following examples, moving introduction of PME to previous section}
-
-Let us investigate the motion of an ancestral lineage in special
-cases in which we have an explicit expression for the travelling
+
+It is interesting to investigate the motion of an ancestral lineage
+in special cases in which we have an explicit expression for the travelling
 wave profile $w$.
 
-\plr{PME:}
-Consider the porous medium equation with logistic
-growth,
-\begin{equation}
-\label{travelling wave}
-v_t=(v^2)_{xx}+v(1-v).
-\end{equation}
-This equation has an explicit travelling wave solution
-$$w^P(t,x)=\left(1-e^{\frac{1}{2}(x-x_0-t)}\right)_+.$$
-Notice that this profile has a sharp boundary at $x=x_0+t$.
-There are also travelling wave solutions with $c>1$,
-\cite{gilding/kersner:2005}, which lack this property. However, for 
-initial conditions that decay sufficiently rapidly at infinity,
-such as one might use in modelling a population invading new territory,
-the solution converges to~(\ref{travelling wave}), 
-\cite{kamin/rosenau:2004}.
-
+%%%%%%%%%%
+\paragraph{Porous Media:}
 Setting $x_0=0$ (for definiteness) and substituting
-$w(x)=(1-e^{x/2})_+$ in our equation for the generator of the
-motion of an ancestral
-lineage relative to the wavefront, we find that since
-in this setting $c=1$,
-$\gamma(x,w)=w(x)$, $r(x,w)=1$, and $F(w)=w(1-w)$,
-the lineage follows the diffusion with generator
-$$\hat{\mathcal L}\phi=w(x)\left(\phi_{xx}+2\frac{(w^2)_x}{w^2}\phi_x\right)
-+\phi_x
-=\left(1-e^{\frac{1}{2}x}\right)\phi_{xx}-2e^{\frac{1}{2}x}\phi_x+
-\phi_x\qquad\mbox{on }x<0.$$
-The speed measure corresponding to this diffusion is 
-$$m(d\xi)\propto\frac{1}{2(1-\exp{\xi/2})}
-\exp\left(\int_\eta^\xi\left\{1-\frac{e^{x/2}}{1-e^{x/2}}\right\}dx\right)
-\propto e^\xi\left(1-e^{\xi/2}\right),
-\quad\mbox{$\xi<0$},$$
-which is integrable and so when suitably normalised gives the unique
-stationary distribution. Notice that at stationarity
-the lineage will typically be 
-significantly behind the front.
-
-\plr{FKPP:}
-This behaviour of all this ancestral lineages can be compared to the classical
-Fisher-KPP equation.
-Under the classical Fisher-KPP equation, the generator of the motion
-of ancestral lineages can be deduced from 
-exactly the same arguments. 
-The equation
-$$v_t=v_{xx}+v(1-v),$$
-has non-negative travelling wave solutions for all $c\geq 2$, 
+the form of $w^P$ from equation \eqref{eqn:pme_wave}
+into Corollary~\ref{cor:wavefront},
+with $c=1$,
+$\gamma(x, m) = m$,
+$r(x,w) = 1$,
+and $F(x, m) = (1 - m)$,
+the lineage's generator is, for $x < 0$,
+\comment{(need to decide whether to use $f_x$ or $\delta_x f$)}
+\begin{align*}
+    \Lgen f
+    &=
+        w(x)
+        \left(
+         f_{xx}
+         +
+         2 \frac{(w^2)_x}{w^2} f_x
+        \right)
+        + f_x \\
+    &=
+        \left(1 - e^{\frac{1}{2} x} \right)
+        f_{xx}
+        -
+        2 e^{\frac{1}{2} x} f_x
+        +
+        f_x .
+\end{align*}
+The speed measure corresponding to this diffusion is,
+again for $x < 0$,
+\begin{align*}
+    m(d\xi)
+    &\propto
+        \frac{ 1 }{ 2 (1 - \exp{\xi/2}) }
+        \exp\left(
+            \int_\eta^\xi \left\{
+                1 - \frac{e^{x/2}}{1 - e^{x/2}}
+            \right\} dx
+        \right) \\
+    &\propto
+        e^\xi\left(1-e^{\xi/2}\right),
+        \quad
+        \text{for } \xi < 0 ,
+\end{align*}
+which is integrable and so when suitably normalised gives the unique stationary distribution.
+Notice that at stationarity
+the lineage will typically be significantly behind the front.
+
+%%%%%%%%%%
+\paragraph{Fisher--KPP:}
+A great deal more attention has been paid to the classical Fisher-KPP equation,
+\begin{align} \label{eqn:fkpp}
+    v_t = v_{xx} + v (1-v) .
+\end{align}
+In this case,
+even though we do not have an explicit formula for the wave shape,
+these methods give us information about ancestral lineages.
+The equation has non-negative travelling wave solutions of speed $c$ for all $c \geq 2$, 
 but started from any compact perturbation of a Heaviside function, the 
-solution will converge to the one with the minimal wavespeed, $c=2$,
-\cite{kolmogorov/petrovsky/piscounov:1937, bramson:1983}.
-No matter what the initial condition, for any $t>0$ the support of the 
-solution will be the whole real line.  In the front the wave profile 
-$w^F(x)\sim e^{-x}$.
-The generator of the motion of an ancestral lineage is
-$$\hat{\mathcal L}\phi=\phi_{xx}+2\frac{w_x}{w}\phi_x+2\phi_x,\qquad
-\mbox{on }(-\infty,\infty).$$
-Near the tip of the wave ($x$ very big) we have $w^F(x) \sim e^{-x}$ and $w_x^F(x) \sim -e^{-x}$, so
-the motion of the lineage
-is close to Brownian motion. Whereas in 
-the bulk (where $w^F_x\approx 0$) it is approximately Brownian motion 
-with drift at rate two to the right. Ancestral lineages are pushed into
-the tip of the wave. 
-We remark that, even though we do not have an explicit formula for the wave of the travelling front in this case, we can still analyse and get information of the ancestral lineages.
-
-\plr{Include the following as a third comparison?}
-We can extend this type of analysis to other equations that are biologically relevant. For example, we now take the following Allen-Cahn equation
-\[ v_t = v_{xx} + v(1-v)(2v-1+s), \]
-for some $s \in (0,2)$, which is used to model population evolving under selection \cite{Sarah}. This equation have an explicit travelling wave solutions $\Xi_t(x) = w^A(x-st)$, where $w$ is given by
+solution will converge to the profile $w^F$ with the minimal wavespeed, $c=2$,
+\cite{kolmogorov/petrovsky/piscounov:1937,bramson:1983}.
+No matter what the initial condition,
+for any $t>0$ the support of the 
+solution will be the whole real line. 
+Since in ths case, $r = \gamma = 1$,
+the generator of the motion of an ancestral lineage is
+$$
+    \Lgen \phi
+    =
+    \phi_{xx} + 2 \frac{w_x}{w} \phi_x + 2 \phi_x .
+$$
+Near the tip of the wave (for $x$ large), $w^F(x) \sim e^{-x}$,
+so the motion of the lineage is close to Brownian motion.
+On the other hand, for $x < 0$ the lineage behaves approximately as
+Brownian motion with drift at rate two to the right.
+This implies that
+ancestral lineages are pushed into the tip of the wave,
+and there is no stationary distribution.
+These results agree with those of \comment{XXX}.
+
+%%%%%%%%%%
+\paragraph{Allen-Cahn:}
+Finally, we take the Allen-Cahn equation
+\begin{align} \label{eqn:allen_cahn}
+    v_t = v_{xx} + v(1-v)(2v-1+s),
+\end{align}
+for a given $s \in (0,2)$,
+which is used to model populations evolving under selection \cite{Sarah}.
+This equation also has an explicit travelling wave solution
+of shape
 \[ w^A(x) = (1+e^{x})^{-1}. \]
-By Theorem \ref{teo:ancestral lineages} the ancestral lineage under this moving frame has generator
-\[ \hat{\mathcal{L}}\phi = \phi_{xx}+2 \frac{w_x}{w} \phi_x + s \nabla \phi =  \phi_{xx}-2 \frac{e^x}{1+e^x} \phi_x + s \nabla \phi, \]
-lineages in the tip are pushed into the bulk of the wave by the drift $-2(e^{-x}+1)^{-1}$, but that drift gets weaker the deeper we go into the wave. This diffusion has speed measure
-\[ m(d\xi) \propto e^{sx}(1+e^x)^{-2}  \] 
-which is concentrated around $\log(s/(2-s))$ and decay like $e^{x(s-2)}$ away from that.
-We note the result above the for the Allen-Cahn are not new, we have just recovered what can be found in \cite{etheridge/penington:2020}.
+The generator for ancestral lineages is, in this case,
+\begin{align*}
+    \hat{\mathcal{L}}\phi
+    &=
+    \phi_{xx}
+    + 
+    2 \frac{w_x}{w} \phi_x
+    +
+    s \nabla \phi \\
+    \qquad &=
+    \phi_{xx}
+    -
+    2 \frac{e^x}{1+e^x} \phi_x 
+    + 
+    s \nabla \phi,
+\end{align*}
+so lineages in the tip are pushed into the bulk of the wave by the drift $-2(e^{-x}+1)^{-1}$,
+but that drift gets weaker further to the left.
+This diffusion has speed measure
+$$
+    m(d\xi) \propto e^{sx}(1+e^x)^{-2},
+$$
+which is concentrated around $\log(s/(2-s))$ and decays like $e^{x(s-2)}$ away from this point.
+These results agree with those of \cite{etheridge/penington:2020}.
 
@@
 \section{Heuristics}
+    \label{sec:heuristics}
 
@@
 \subsection{Population processes}
-
-Here we present a formal generator calculation which identifies the scaling
-limits that appear in our main results and may be more accessible than our 
-calculations with the lookdown construction.
-For this purpose, we consider two scaling parameters, $N$ and $\theta$;
-we shall start with ${\mathcal O}(N)$ individuals per unit area,
-each of mass $1/N$,
-and we measure time in units of $\theta$ generations,
-so that each individual reproduces at rate $\theta$
-and disperses juveniles a distance of order $1/\sqrt{\theta}$.
-Both $N$ and $\theta$ will tend to infinity in our scaling limits
-and we retain different notations in our
-heuristic arguments to disentangle their effects.
-The functions of $q, r, \gamma, \mu$
-can all depend upon the time scaling $\theta$.
-Indeed, by analogy with the classical superprocess,
-in order to obtain a nontrivial limit, 
-we expect to need to assume that the branching is close to critical, with the
-difference between birth and death rates proportional to $1/\theta$.
-
-We write ${\cal L}_{(\theta, N)}$ for the generator of the scaled 
-population process acting
+    \label{sec:population_heuristics}
+
+\comment{TODO: short lead-in}
+
+We write $\Pgen^\theta$
+for the generator of the scaled population process $\eta$ acting
 on test functions of the form 
 $$
-    \mathcal{F}(\langle f,\overline{\eta}\rangle)
-    :=
-    \mathcal{F}\left(\int f(x)\overline{\eta}(dx)\right),
+    F( \langle f, \eta\rangle )
+    =
+    F \left( \int f(x)\eta(dx) \right),
 $$
-where $f\geq 0$ is smooth and compactly supported on $\mathbb{R}^d$ and 
-$ \mathcal{F} \in C^\infty ([0,\infty))$.
+where $f \geq 0$ is smooth and compactly supported on $\IR^d$ and 
+$F \in C^\infty ([0,\infty))$.
+Recall that $N \to \infty$ along with $\theta$,
+although we don't remind the reader with extra superscripts.
 
 A Taylor expansion allows us to write
-\begin{align}
-    {\cal L}_{(\theta, N)} \mathcal{F}(\langle f,\overline{\eta}\rangle)
-    &=
-     \mathcal{F}'(\langle f,\overline{\eta}\rangle)
+\begin{multline*}
+    \Pgen^\theta
+    F(\langle f,\eta \rangle)
+    =
+    F'(\langle f, \eta \rangle)
+    \lim_{\delta t\downarrow 0} \frac{1}{\delta t}
+    \IE\left[
+        \left. \langle f, \eta_{\delta t} \rangle
+        -
+        \langle f, \eta \rangle
+        \right| \eta_0=\eta
+    \right]
+    \\
+    \qquad {}
+    + \frac{1}{2}
+        F''(\langle f,\eta\rangle)
     \lim_{\delta t\downarrow 0}\frac{1}{\delta t}
-    \mathbb{E}\left[ \left.
-            \langle f, \overline{\eta}_{\delta t} \rangle -
-            \langle f, \overline{\eta} \rangle
-            \right|
-            \overline{\eta}_0 = \overline{\eta}
-        \right] \nonumber \\
-    & {}
-    + \frac{1}{2}
-        \mathcal{F}''(\langle f,\overline{\eta}\rangle)
-        \lim_{\delta t\downarrow 0}\frac{1}{\delta t}
-        \mathbb{E}\left[\left.
-            \big(\langle f,\overline{\eta}_{\delta t}\rangle -
-            \langle f, \overline{\eta}\rangle\big)^2 \right|\overline{\eta}_0=\overline{\eta}
+    \IE\left[
+        \left.\big(\langle f,\eta_{\delta t}\rangle
+        -
+        \langle f, \eta\rangle\big)^2 \right|\eta_0=\eta
     \right]
-    + \varepsilon_{\theta, N}(f, F, \overline{\eta}) ,
-    \label{eq:expanmeanvar}
-\end{align}
+    +
+    \varepsilon_{\theta}(f, F, \eta),
+\end{multline*}
 where the terms that make up 
-$\varepsilon_{\theta, N}(f, F, \overline{\eta})$
+$\varepsilon_{\theta, N}(f, F, \eta)$
 will be negligible in our scaling limit.
 
-% % % % % % % % % % % % % % % %
-\subsubsection*{Mean Measure}
+\subsubsection*{Mean measure}
 
@@
 (smooth, compactly supported) test function $f$, we find
-\begin{multline} \label{mean measure}
-    {\cal L}_{(\theta, N)}\langle f, \overline{\eta} \rangle
-    =
+\begin{multline}
+\label{mean measure}
+{\cal L}^{(\theta, N)}\langle f,\eta\rangle=
 \lim_{\delta t\downarrow 0}\frac{1}{\delta t}
-        \mathbb{E}\left[\left.
-            \langle f,\overline{\eta}_{\delta t}\rangle -
-            \langle f, \overline{\eta}\rangle
-            \right| \overline{\eta}_0=\overline{\eta}
+\IE\left[\left.\langle f,\eta_{\delta t}\rangle -
+\langle f, \eta\rangle \right|\eta_0=\eta
 \right]\\
-    =
-    \theta\int\int
-            f(z) r_\theta(z,\overline{\eta}) q_\theta(x,dz)
-        \gamma_\theta(x,\overline{\eta})
-    \overline{\eta}(dx)
-    -
-    \theta\int
-        f(x)\mu_\theta(x,\overline{\eta})
-    \overline{\eta}(dx).
+=\theta\int\int f(z)r_\theta(z,\eta)q_\theta(x,dz)
+\gamma_\theta(x,\eta)
+\eta(dx)-\theta\int f(x)\mu_\theta(x,\eta)
+\eta(dx).
 \end{multline}
-The first term is the increment in $\langle f,\overline{\eta}\rangle$
-resulting from a birth event
-integrated against the rate of such events,
+The first term is the increment in $\langle f,\eta\rangle$
+resulting from a birth event (recalling that
+we don't kill the parent) integrated against the rate of such events,
 and the second reflects death events.
-Note that there is a slight mismatch between the locations at which we are 
-measuring birth and death rates, because
-the establishment probability is measured at $x$
-rather than at the point where juveniles fall (see \eqref{near critical}).
-In both terms,
-the rate of events has a factor of $N$
-(because events happen at a rate proportional to the number of individuals,
-whereas $\overline{\eta}$ is the total number divided by $N$)
-which is offset by the fact that  
+In both terms, the 
+rate of events has a factor of $N$ (because events happen at a rate 
+proportional to the number of individuals, whereas $\eta$ is
+the scaled population mass) which is offset by the fact that  
 the birth or loss of a single 
-individual at the point $y$, say, changes $\langle f,\overline{\eta}\rangle$
+individual at the point $y$, say, changes $\langle f,\eta\rangle$
 by $f(y)/N$.
@@
 \label{rewritten mean measure}
-    \int\left(
-          \int \theta \left(
-            f(z)r_\theta(z,\overline{\eta})
-            -
-            f(x)r_\theta(x,\overline{\eta})\right)
-          q_\theta(x,dz)
-        \right)
-        \gamma_\theta(x,\overline{\eta})
-    \overline{\eta}(dx) \\
-    + 
-    \theta\int f(x)
-        \Big(
-            r_\theta(x,\overline{\eta})
-            \gamma_\theta(x,\overline{\eta})
-            -
-            \mu_\theta(x,\overline{\eta})
-        \Big)
-    \overline{\eta}(dx) .
+\int\left(\int \theta \left(
+f(z)r_\theta(z,\eta)- f(x)r_\theta(x,\eta)\right)
+q_\theta(x,dz)\right)
+\gamma_\theta(x,\eta)
+\eta(dx)
+\\
++\int\theta\int f(x)\Big(r_\theta(x,\eta)
+\gamma_\theta(x,\eta)
+-\mu_\theta(x,\eta)\Big)
+\eta(dx).
 \end{multline}
-Suppose as we take $\theta \to \infty$ that
-$\overline{\eta}$ converges to a measure $\Xi$ on $\mathbb{R}^d$.
-Then we can take this limit in~(\ref{rewritten mean measure})
+Suppose that $\eta\to\Xi$, a measure on $\IR^d$,
+in the scaling limit, then we see that we can 
+let $\theta\rightarrow\infty$ in~(\ref{rewritten mean measure})
 under the assumptions that
-\begin{eqnarray} \label{near critical}
-\left.
-\begin{split}
-    r_\theta(x,\overline{\eta})
-        &\;  \stackrel{\theta\to\infty}{\longrightarrow} \;
-        r(x,\Xi)
-    \\
-    \gamma_\theta(x,\overline{\eta})
-        &\;  \stackrel{\theta\to\infty}{\longrightarrow} \;
-        \gamma(x,\Xi)
-    \\
-    \int\theta \Big(
-            r(z,\overline{\eta})f(z)
-            -
-            r(x,\overline{\eta})f(x)
-        \Big)q_\theta(x,dz) 
-        &\; \stackrel{\theta\to\infty}{\longrightarrow}  \;
-        \Delta \big(r(\cdot,\Xi)f(\cdot)\big)(x)
-    \\
-    \theta \Big(
-            r_\theta(x,\overline{\eta})
-            \gamma_\theta (x,\overline{\eta})
-            -
-            \mu_\theta (x,\overline{\eta})
-        \Big)
-         &\; \stackrel{\theta\to\infty}{\longrightarrow}  \;
+\begin{eqnarray}
+r_\theta(x,\eta)&\stackrel{\theta\to\infty}{\longrightarrow}&
+r(x,\Xi)\\
+\gamma_\theta(x,\eta)&\stackrel{\theta\to\infty}{\longrightarrow}&
+\gamma(x,\Xi)\\
+\int\theta \Big(r(z,\eta)f(z)-
+r(x,\eta)f(x)\Big)q_\theta(x,dz) 
+&\stackrel{\theta\to\infty}{\longrightarrow}& 
+\Delta \big(r(\cdot,\Xi)f(\cdot)\big)(x);\\
+\theta \Big(r_\theta(x,\eta)\gamma_\theta (x,\eta)
+-\mu_\theta (x,\eta)\Big)
+ &\stackrel{\theta\to\infty}{\longrightarrow}& 
 F(x,\Xi),
-\end{split}
-\right\}
+\label{near critical}
 \end{eqnarray}
 where $\Delta$ denotes the Laplacian.
-The last condition reflects the `near-critical' branching,
-and implies that $\mu_\theta(x, \overline{\eta}) \to \gamma(x, \Xi) / r(x, \Xi)$.
-
-Referring back to the original (unscaled) process,
-this amounts to assuming that
-there are of order $N$ individuals per unit area,
-and per-capita birth and death rates
-are sufficiently close that population density takes of order $\theta$ time to change.
-However, note that although the difference
-between the number of births and deaths per unit area
-across $\theta$ units of time is of order $N$,
-the total number of such events is larger (of order $\theta N$).
-As we will see next, the variance of population density per unit of (unscaled) time
-is therefore of order $1/N$,
-so we will obtain a deterministic limit if $\theta$ is of smaller order than $N$.
-
-Then the mean rate of change of $\langle f, \overline{\eta}\rangle$,
-\eqref{rewritten mean measure} converges to
-\begin{equation} \label{limit of mean measure equation}
+The last condition reflects the `near-critical' branching. Note that
+there is a slight mismatch between the locations at which we are 
+measuring birth and death rates, because in~(\ref{near critical})
+the establishment probability is 
+measured at $x$ rather than at the point where juveniles fall. 
+This condition also differs from the assumption that
+we use in~\S\ref{scalings with levels} to guarantee convergence of the 
+processes with levels in our lookdown 
+constructions, see~(\ref{lookdown blambda}). 
+Under mild
+regularity conditions on $r$ (which we certainly need to have sensible 
+limiting models) the conditions are equivalent.
+
+Equation~(\ref{rewritten mean measure}) converges to
+\begin{equation}%\begin{multline}
+\label{limit of mean measure equation}
 \int \gamma(x,\Xi)
-        \Delta \big(f(\cdot)r(\cdot,\Xi)\big)(x)
+\Delta
+\big(f(\cdot)r(\cdot,\Xi)\big)(x)
 \Xi(dx)
-    + \int f(x)
++\int f(x)
 F(x,\Xi)
-    \Xi(dx) .
+\Xi(dx)
+.
 \end{equation}
-As we will see below,
-if the limit is deterministic and $\Xi_t$ possesses a density
-with respect to the Lesbegue measure,
-this means that the density satisfies
+
+\subsubsection*{Quadratic variation}
+
+We now look at the second order term.
+We spell out
+this calculation in detail so that it is evident at which points we are 
+exploiting the choice of the Poisson distribution for the number
+of juvenile offspring.
+In the general case one can expect somewhat messier calculations, but
+the same conclusion (up to constants).
+
+When an individual at the point $x$ gives birth, the total number of
+mature offspring is Poisson with parameter
+$$\gamma_\theta(x,\eta)\int 
+r_{\theta}(y,\eta) q_{\theta}(x, dy)
+=\gamma_\theta(x,\eta)p_\theta(x,\eta).$$
+Offspring that survive to maturity are distributed about the parent
+according to 
+$$\overline{q}_\theta(x,\eta,dy):=
+\frac{r_{\theta}(y,\eta)q_\theta(x,dy)} 
+{\int r_{\theta}(z,\eta)q_\theta(x,dz)}. 
+$$
+Writing $X(x)$ for the increment to $\langle f, \eta\rangle$
+due to a single mature offspring of an individual at $x$, 
+and $P(x)$ for the (Poisson) number of mature
+offspring in such an event, the variance of the increment to 
+$\langle f, \eta\rangle$
+resulting from a birth event at $x$ is $\IE[P(x)]\mathtt{var}(X(x))
++\mathtt{var}(P(x))\IE[X(x)]^2=\IE[P]\IE[X(x)^2]$. 
+Since, in this notation, conditional on the value of $\eta$
+immediately before the event,
+$$\IE[X(x)^2]=\int
+\frac{1}{N^2}f^2(y) \overline{q}_\theta(x,\eta,dy),$$
+and
+$$\IE[P(x)]=
+\gamma_\theta (x,\eta) \int 
+r_{\theta}(z,\eta)q_\theta(x,dz),$$ 
+the contribution to the quadratic variation from birth events, which
+occur at rate $\theta$ per individual 
+(so $N\theta |\eta|$ overall), is
+$$\langle N\theta \gamma_\theta(x,\eta)
+\int \frac{1}{N^2}f^2(y)r_{\theta}(y,\eta)
+q_\theta(x,dy) 
+,\eta(dx)\rangle.$$
+The increment in $\langle f, \eta\rangle$ resulting from 
+the death of an individual at $x$ is $f(x)/N^2$, and so combining with the 
+above, the second order term in the generator takes the form
+$$F''(\langle f,\eta\rangle)
+\frac{1}{2}N\theta \left\{
+\langle \gamma_\theta(x,\eta)
+\int \frac{1}{N^2}f^2(y)r_\theta(y,\eta)q_\theta(x,dy) 
+,\eta(dx)\rangle
++\langle \mu_\theta(x,\eta)\frac{1}{N^2}f^2(x) 
+,\eta(dx)\rangle\right\}.
+$$
+The term $\varepsilon_{\theta,N}(f, F, \eta)$ will be 
+${\mathcal O}(\theta/N^2)$.
+
+\subsubsection*{Limit I: deterministic case}
+
+By choosing $\theta/N\rightarrow 0$, the second order term in the generator 
+will vanish and we expect a deterministic limit. 
+Let us suppose that the limit has a smooth density with respect to
+Lebesgue measure, and abuse notation by using $\Xi_t(x)$
+to denote the corresponding density, then integrating the first term in~(\ref{limit of mean measure equation})
+by parts, we find that in the limit as $N\to\infty$,
 \begin{equation}
-\label{eq: limit of mean measure equation 2}
-    \int f(x) \partial_t \Xi(dx)
-    =
-    \int \gamma(x,\Xi)
-        \Delta \big(f(\cdot)r(\cdot,\Xi)\big)(x)
-    \Xi(dx)
-    + \int f(x)
-        F(x,\Xi)
-    \Xi(dx),
+\nonumber
+\frac{d}{dt}\int f(x)\Xi_t(x)dx
+=\int f(x)\left\{r(x,\Xi_t)\Delta\big(\gamma(\cdot,\Xi_t)
+\Xi_t(\cdot)\big)(x)+F(x,\Xi_t)
+\Xi_t(x)
+\right\}dx.
 \end{equation}
-i.e., $\Xi$ is a \textit{weak solution} to the integro-differential equation:
-\begin{equation}\label{eq:PDE}
-    \partial_t \Xi
-    = r \Delta \gamma \Xi + F \Xi .
+In other words, we can expect the limit to be a weak solution to the 
+deterministic equation
+\begin{equation}
+\label{deterministic limit}
+\frac{d\Xi}{dt}
+=r(x,\Xi)\Delta\big(\gamma(\cdot,\Xi)
+\Xi(\cdot)\big)(x)+F(x,\Xi)
+\Xi(x).
 \end{equation}
-(Although this looks like a partial differential equation,
-recall that $r$, $\gamma$, and $F$ at $x$ depend on $\Xi$
-through a convolution.)
-
-% % % % % % % % % % % % % % % %
-\subsubsection*{Quadratic Variation}
-
-We now look at the second order term.
-Thinning the birth process to only consider offspring
-who successfully mature,
-an individual at the point $x$ gives birth to an offspring
-who moves to $y$ and successfully matures there
-at rate
+
+\subsubsection*{Limit II: stochastic case}
+
+If $N=\rho\theta$, for some constant $\rho$,
+the second order term in the generator remains order
+one as $\theta\to\infty$, and  
+we expect a `generalised
+superprocess'
+limit. Assuming some regularity of the coefficients (in particular 
+of $r$), 
+the second order term in the generator will  
+take the form
+$$\frac{1}{\rho}F''(\langle f,\Xi\rangle)
+\langle f^2(x), \gamma(x,\Xi)
+r(x,\Xi)\Xi(dx)\rangle.
 $$
-    \gamma_\theta(x,\overline{\eta}) r_{\theta}(y,\overline{\eta}) q_{\theta}(x, dy) .
-$$
-The increment to $\langle f, \overline{\eta}\rangle^2$ due to this event is $f(y)^2/N^2$,
-so the contribution to the quadratic variation from birth events, which
-occur at rate $\theta$ per individual is
-$$
-    \langle N\theta
-        \gamma_\theta(x,\overline{\eta})
-        \int
-            \frac{1}{N^2} f^2(y) r_{\theta}(y,\overline{\eta})
-        q_\theta(x,dy)
-        ,
-        \overline{\eta}(dx)
-    \rangle .
-$$
-The increment in $\langle f, \overline{\eta}\rangle^2$ resulting from 
-the death of an individual at $x$ is $f^2(x)/N^2$, and so combining with the 
-above, the second order term in the generator takes the form
-$$
-    \mathcal{F}''(\langle f, \overline{\eta}\rangle)
-    \frac{1}{2}N\theta \left\{
-        \langle
-            \gamma_\theta(x,\overline{\eta})
-            \int \frac{1}{N^2} f^2(y) r_\theta(y,\overline{\eta}) q_\theta(x,dy) 
-            ,
-            \overline{\eta}(dx)
-        \rangle
-        +
-        \langle
-            \mu_\theta(x,\overline{\eta})\frac{1}{N^2}f^2(x) 
-            ,
-            \overline{\eta}(dx)
-        \rangle
-    \right\} .
-$$
-The term $\varepsilon_{\theta,N}(f, F, \overline{\eta})$ in \eqref{eq:expanmeanvar}
-is ${\mathcal O}(\theta/N^2)$,
-as it depends on higher order moments of $\langle f ,\overline{\eta} \rangle$.
-It follows that the quadratic variation of the semi-martingale $\langle f, \overline{\eta} \rangle$
-is given by
-\begin{equation} \label{quadratic variation}
-    \frac{\theta}{N}
-    \left\{
-        \langle
-            \gamma_\theta(x,\overline{\eta})
-            \int f^2(y)r_\theta(y,\overline{\eta})q_\theta(x,dy) 
-            ,
-            \overline{\eta}(dx)
-        \rangle
-        +
-        \langle
-            \mu_\theta(x,\overline{\eta})f^2(x) 
-            ,
-            \overline{\eta}(dx)
-        \rangle
-    \right\} .
-\end{equation}
-
-Let $\ell$ be defined by
-\begin{equation}
- \frac{\theta}{N} \rightarrow \ell \in [0,\infty).
- \label{defn:rho}
- \end{equation}
-If $\ell=0$ then the quadratic variation of $\overline{\eta}$ goes to $0$, and so we expect a deterministic limit.
-This limit should be described as the solution to (\ref{eq: limit of mean measure equation 2}).
-If $\ell$ is positive then the limit is stochastic, and should be understood as the solution of a martingale problem.
-
-One can build many different examples in which our assumptions hold.
-Our main result establishes that a broad range of models, under which these heuristics can be justified, can be further enriched by a structure called the \textit{lookdown construction} that preserve ancestral relationships under passage to the limit.
+That is
+$$\langle f(x), \Xi_t(dx)\rangle-\langle f(x), \Xi_0(dx)\rangle
+-\int_0^t\langle\gamma(x,\Xi_s)\Delta\big(r(\cdot,\Xi_s)f(\cdot)\big)(x),
+\Xi_s(dx)\rangle ds$$
+is a martingale with quadratic variation
+$$\frac{2}{\rho}\int_0^t\langle f^2(x) 
+\gamma(x,\Xi_s)r(x,\Xi_s),\Xi_s(dx)\rangle ds.$$
 
@@
 \section{The lookdown process}
-
-\plr{Motivation for and definition of the lookdown process}
+    \label{sec:lookdown}
+
+\plr{Motivation for and definition of the lookdown process; statement of main convergence theorem.}
 
@@
 
+%% %% %% %% %% %% %% %% %% %% %% %%
+\subsection{Stochastic equations for movement of lines of descent}
+    \label{sec:lines_of_descent}
+
+    \plr{This section needs to follow from the previous section better (and maybe be merged with it).}
+
+The main interest in using a lookdown construction for our 
+population processes is that it allows us to retain information 
+about relatedness between individuals as we pass to the infinite
+density limit. In order to exploit this, we generalise the construction of 
+stochastic equations presented in \S \ref{sec: Evolution of an Individual Particle} to the infinite density limit.\\
+In the scaling limit $A^{\text{nl}}_{\varepsilon}$, the spatial movement of particles can be characterised with the map $$h \mapsto \gamma\big(x,(\varrho_{\varepsilon}*\Xi)(x)\big)r\big(x,(\varrho_{\varepsilon}*\Xi)(x)\big)\mathcal{B}^{m}_{\varepsilon}(\Xi)h(x) ,$$
+and as individual particles travel as a random walk in the pre-limit model, we should expect a diffusion limit for individual trajectories.
+\todo[inline]{From Terence: we should try explain in detail why this is the generator of an individual line of descent forward-in-time.
+The main question here is whether we should have a factor of $r$ in the above notation.
+For the proof to work in \S \ref{sec: motion of ancestral lineages} we will need a factor of $r$ but I have been finding it slightly unintuitive particularly since the effect of $r$ has been accounted into $\mathcal{B}^{\mathfrak{m}}$ through the limit.}
+To simply notation, we let the above map be the generator of a process 
+satisfying 
+\[X(t)=X(0)+\int_0^t\sigma (X(s),\Xi (s))dW(s)+\int\beta (X(s),\Xi 
+(s))ds.\]
+\begin{remark}
+In particular recall that as in Remark \ref{Remark: Product Rule on Laplacian}, if $\mathcal{B}$ is the Laplacian operator, then the generator above is merely 
+$$\gamma\big(x,(\varrho_{\varepsilon}*\Xi)(x)\big)\left(\Delta h(x) +2 \nabla h(x) \cdot \nabla \log r( \cdot, (\varrho_{\varepsilon}*\Xi)(\cdot))(x)\right),$$
+and applying Ito's formula we have 
+\begin{equation}\label{eq: Individual lineage generator description}
+\begin{aligned}
+\beta(X(s),\Xi(s))=& 2\gamma\big(X(s),(\varrho_{\varepsilon}*\Xi)(X(s))\big) \nabla \log r (\cdot, (\varrho_{\varepsilon}*\Xi)(\cdot))(X(s))\\
+\sigma(X(s),\Xi(s))=& \sqrt{2\gamma\big(X(s),(\varrho_{\varepsilon}*\Xi)(X(s))\big)}.
+\end{aligned}
+\end{equation}
+\end{remark}
+Furthermore, recall that in our scaling limit, 
+\begin{equation}
+\begin{aligned}
+\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(s), \overline{\eta}(s)) &\to \ell \gamma(X_{\tau}(s),\varrho_\varepsilon*\Xi(X_{\tau}(s)),\\
+b_{\varepsilon,\theta, \lambda}(X_{\tau}(s),\overline{\eta}(s)) &\to  F(X_{\tau}(s), (\varrho_{\varepsilon}*\overline{\eta})(X_{\tau}(s)))\\
+&+\gamma(X_{\tau}(s), (\varrho_{\varepsilon}*\Xi)(X_{\tau}(s)))\mathcal{B}r(\cdot,(\varrho_{\varepsilon}*\overline{\eta})(\cdot))(X_{\tau}(s)).
+\end{aligned}    
+\end{equation}
+
+We now have the required results to establish the individual lineage dynamics in the scaling limit. Our approach should be compared to Perkins stochastic calculus,
+\cite{perkins:1995}. First we label the individuals alive at time $0$
+by $\{(0,i), i\in\IN\}$.
+
+When an individual is born, it is endowed with an
+independent Poisson random measure $\xi$ on $[0,\infty)^2$ with Lebesgue
+mean measure. The first coordinate encodes {\em potential} birth times of 
+offspring of the individual. We say potential, since the parent may have
+died before the potential birth time. 
+Since, after time $0$, no two particles will have the same birth
+time, we index the particles born after time $0$ by 
+their birth times.  
+For example, if a parent has index $\tau$ and $(s,v)\in \xi_\tau$, then 
+$\tau +s$ gives a potential birth time for an offspring which, if
+it is in fact born, will carry
+the label $\tau+s$. 
+The second 
+coordinate of $\xi$ will be used to determine, after scaling, 
+the level of offspring relative to the 
+level of the parent (offspring are always born to levels above that of
+the parent).
+
+Starting with an initial particle 
+$(0,i)$, we can identify a potential line of descent by 
+taking $(s_1,u_1)\in\xi_{(0,i)}$, setting $\tau_1=s_1$, and then recursively 
+taking $(s_{k+1},u_{k+1})\in\xi_{\tau_k}$ and defining $\tau_{k+1}
+=\tau_k+s_{k+1}$.
+
+With each particle, we will 
+associate an independent Brownian motion, $W_\tau$. For times 
+$t>\tau$, the spatial location and level of the particle with
+label $\tau$ are then determined by
+\begin{equation}\label{Eq: Expression for dynamics in scaling limit}
+\begin{aligned}
+X_{\tau}(t)=&X_{\mbox{\rm $\tau$}}(\tau )+\int_{\tau}^t\sigma (X_{
+\tau}(s),\Xi (s))dW_{\tau}(s)+\int_{\tau}^t\beta (X_{\tau}(s),\Xi (
+s))ds\\
+U_{\tau}(t)=&U_{\tau}(\tau )+\int_{\tau}^t\bigg\{\ell \gamma(X_{\tau}(s),\varrho_\varepsilon*\Xi(X_{\tau}(s)U_{\tau}^2(s) \\
+& -\big(F(X_{\tau}(s), (\varrho_{\varepsilon}*\overline{\eta})(X_{\tau}(s)))+\gamma(X_{\tau}(s), (\varrho_{\varepsilon}*\Xi)(X_{\tau}(s)))\mathcal{B}r(\cdot,(\varrho_{\varepsilon}*\overline{\eta})(\cdot))(X_{\tau}(s))\big)U_{\tau}(s))\bigg\}ds.
+\end{aligned}
+\end{equation}
+If $(X_{\tau'},U_{\tau'})$ is the parent of $(X_{\tau},U_{\tau})$, 
+then there is $(s,v)\in\xi_{\tau'}$ 
+such that $\tau =\tau'+s$,
+$X_{\tau}(\tau'+s)=X_{\tau'}(\tau'+s)$ and 
+\begin{equation}
+\label{Eq: expression for offspring level in limit}
+U_{\tau}(\tau )=U_{\tau}(\tau'+s)=U_{\tau'}(\tau'+s)+\frac v{2\ell \gamma(X_{\tau}(s),\varrho_\varepsilon*\Xi(X_{\tau}(s))U_{\tau}^2(s)},
+\end{equation} 
+recognizing 
+that $U_{\tau'}(\tau'+s)$ may be infinite, which means 
+that $(X_{\tau}, U_{\tau})$ doesn't exist.
+To see why we scale $v$ in this way, 
+we observe that
+in order for $U_{\tau}(\tau'+s)$ to be below some fixed level $u_g$,
+we require 
+$v<2\ell \gamma(X_{\tau'}(\tau'+s),\varrho_\varepsilon*\Xi(X_{\tau'}(\tau'+s))U_{\tau}^2(\tau'+s)\big(u_g-U_{\tau'}(\tau'+s)\big)$.
+Recalling
+that $\xi_{\tau'}$ is Poisson on $[0,\infty)^2$ with Lebesgue mean 
+measure, the instantaneous rate at which we see such a $v$ will be
+$2\gamma(X_{\tau'}(\tau'+s), \Xi(\tau'+s))\big(u_g-U_{\tau'}(\tau'+s)\big)$.
+Comparing  this
+with Equation
+\eqref{Eq: Non-local Scaling limit Lookdown Generator}, this is exactly
+the rate of births that we require.
+\begin{remark}
+Note in particular that $\ell=0$ in the deterministic limit , so the increment in Equation \eqref{Eq: expression for offspring level in limit} is always infinite, meaning that no new offspring is born in the deterministic model.
+\end{remark}
+In order to write $X_\tau(t)$ and $U_\tau(t)$ as an integral along
+the whole ancestral path linking individual $\tau$ to its ancestor at 
+time $0$, we associate a counting process $N_{\tau}$ with the indivdual
+$\tau$    
+such that $N_{\tau}(t)$ gives the generation of the ancestor of $\tau$ 
+that is alive at time $t$,
+and a process $A_{\tau}$ such that 
+$A_{\tau}(t)$ is 
+the index of the ancestor of $\tau$ that is alive at time $t$. 
+Finally, let $V_{\tau}(t)=\sum_{k=1}^{N_{\tau}(t)}v_k^{\tau}$ be the sum of the second 
+coordinate of the Poisson points along the ancestral line 
+leading to $\tau$.  Then we can write 
+\begin{eqnarray*}
+X_{\tau}(t)&=&X_{\mbox{\rm $A_{\tau}(0)$}}(0)+\int_0^t\sigma 
+(X_{\tau}(s),\Xi (s))dW_{A_{\tau}(s)}(s)+\int_0^t\beta (X_{\tau}
+(s),\Xi (s))ds,\\
+U_{\tau}(t)&=&U_{A_{\tau}(0)}(0)+\int_0^t\frac 1{2\ell \gamma(X_{\tau}(s-),\varrho_\varepsilon*\Xi(X_{\tau}(s-))}dV_{\tau}(s)\\
+&&\qquad\qquad +\int_{\tau}^t\bigg\{\ell \gamma(X_{\tau}(s),\varrho_\varepsilon*\Xi(X_{\tau}(s)U_{\tau}^2(s) \\
+&&-\big(F(X_{\tau}(s), (\varrho_{\varepsilon}*\overline{\eta})(X_{\tau}(s)))+\gamma(X_{\tau}(s), (\varrho_{\varepsilon}*\Xi)(X_{\tau}(s)))\mathcal{B}r(\cdot,(\varrho_{\varepsilon}*\overline{\eta})(\cdot))(X_{\tau}(s))\big)U_{\tau}(s))\bigg\}ds,\end{eqnarray*}
+where
+\[\langle\Xi (t),\varphi\rangle =\lim_{\epsilon\rightarrow 0}
+\epsilon\sum_{
+\tau\leq t}e^{-\epsilon U_{\tau}(t)}\varphi (X_{\tau}(t)).\]
+
+This representation of individuals allows us to identify all 
+of the individuals in the current population that are descendants of a
+given ancestor at time zero. In theory at least, this allows us to
+recover all the information about genealogies relating individuals 
+sampled from the present day population. This idea draws on the notion
+of `tracers', popular in statistical physics and used in population
+genetics by a number of authors including 
+\cite{biswas/etheridge/klimek:2018, durrett/fan:2016, hallatschek/nelson:2008}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \comment{
+    TODO: write overview.
     To prove convergence, we'll be proving
@@
     (c) uniqueness of the limit.
-}
+
+    Then, to get convergence of the lookdown
+    we use the population process (somehow).
+}
+
+\begin{proof}[Proof of Theorem~\ref{thm:nonlocal_convergence}.]
+
+\comment{INSERT HERE
+    narrative of tightness,
+    proved in Section \ref{sec:population_tightness_proofs},
+    and convergence of generators,
+    proved in Section \ref{sec:population_generators_proofs}.
+}
+
+\end{proof}
 
@@
 \subsection{Tightness of empirical measures}
+    \label{sec:population_tightness_proofs}
+
+\begin{lemma}[Tightness for the population process]
+    Something like:
+    for all suitable $f$
+    and initial states $\eta^\theta_0 \to \eta_0$,
+    \begin{align}
+        \IE\left[
+            \sup_{0 \le t \le T}
+            \langle f, \eta^\theta_t \rangle
+        \right]
+        \le C ,
+    \end{align}
+    uniformly in $\theta$.
+\end{lemma}
 
@@
 \subsection{Convergence of generators}
+    \label{sec:population_generators_proofs}
+
+    \begin{lemma}[Convergence of generators for the population process]
+        As $\theta \to \infty$,
+        \comment{(the generator for the prelimit)}
+        converges to
+        \comment{(the generator for the limit)}.
+    \end{lemma}
 
@@
 \subsection{Uniqueness of the limit}
-
-\comment{... for the cases in which we can prove that}
+    \label{sec:uniqueness_proofs}
+
+Here are the proofs of Corollaries~\ref{cor:nonlocal_pde_limits}
+and \ref{cor:superprocess_uniqueness},
+giving conditions in which the limiting process is unique
+(in which case we have convergence, not just on subsequences).
 
@@
 }
+
+In this section we prove Proposition~\ref{prop:nonlocal_pde_limits}.
 
@@
 
+In this section we prove Theorem~\ref{them:nonlocal_pde_limits}.
+
+% % % % % % % % % % % % %
+\subsection{Proof of convergence for the lookdown process}
+
+The proof of the main result in Section~\ref{sec:lookdown}.
+
+This will depend on Sections~\ref{sec:lookdown_tightness_proofs}
+and \ref{sec:lookdown_generator_proofs}.
+
 % % % % % % % % % % % % %
 \subsection{Tightness of the lookdown process}
+    \label{sec:lookdown_tightness_proofs}
 
@@
 % % % % % % % % % % % % %
+\subsection{Convergence of generators for the lookdown process}
+    \label{sec:lookdown_generator_proofs}
+
+% % % % % % % % % % % % %
 \subsection{Motion of ancestral lineages}
 
+In this section we prove Theorem~\ref{thm:lineages}.
+The argument follows directly from the discussion in Section \ref{sec:lines_of_descent}
+(and so maybe actually that content should be down here).
+
+\begin{proof}[of Theorem~\ref{thm:lineages}]
     \comment{
-    The proof of the theorem on lineages using the lookdown representation.
-}
+        This is actually copied over the proof of Corollary~\ref{cor:wavefront};
+        TODO is to generalize it to time-varying density.
+    }
+
+Let $Y$ denote the diffusion followed by following a single descendent line in this frame; 
+i.e.~the diffusion with generator ${\cal L}^Y\phi=\gamma\Delta(r\phi)-\gamma\phi\Delta r -\mathfrak{c}\nabla\phi $.
+Note in particular here we take $\mathcal{B}=\Delta$.
+We start by expressing the evolution of a singles ancestry line in terms of the descendent line $Y$.
+
+Formally, the intensity of levels at $y$ at time $t$ that are descended from 
+individuals that were at $x$ at time $0$ is
+\begin{equation}
+\label{formal intensity}
+w(x)\IE_x\left[\exp\left(\int_0^t (F+\gamma \Delta r)(Y_s)ds\right)\ind_{Y_t=y}\right]dy,
+\end{equation}
+where the subscript $x$ in the expectation indicates that $Y_0=x$.
+To see why this should be true, 
+suppose that an ancestor has level $u$. Conditional on its 
+spatial motion $\{Y_s\}_{0\leq s\leq t}$, its level at time $t$ will
+be $u\exp(-\int_0^t(F+\gamma\Delta r)(Y_s)ds)$. This will be less than a given level 
+$\lambda$ if $u<\lambda \exp(\int_0^t(F+\gamma\Delta r)(Y_s)ds)$. 
+The intensity of levels at $y$ that are descended from individuals at
+$x$ can therefore be obtained as the limit as $\lambda\to\infty$ of 
+$1/\lambda$ times the number of levels at $x$ at time zero with
+$u<\lambda \exp(\int_0^t(F+\gamma\Delta r)(Y_s)ds)$ and for which
+the corresponding individual is at $y$ at time $t$, which is 
+precisely the quantity in~(\ref{formal intensity}).
+
+It is easy to check that when we integrate~(\ref{formal intensity})
+with respect to $x$ we recover $w(y)dy$. 
+As a consequence of~(\ref{formal intensity}), writing $p(t,y,x)$ for
+the probability density that the ancestor $t$ units in 
+the past of an individual sampled 
+at $y$ was at $x$, then, still formally,
+\begin{equation}
+\label{ptyx}
+p(t,y,x)=\frac{w(x)}{w(y)}\IE_x\left[\exp\left(\int_0^t (F+\gamma\Delta r)(Y_s)ds\right)
+\ind_{Y_t=y}\right].
+\end{equation}
+
+To make~(\ref{ptyx}) meaningful, we multiply by suitable test functions and 
+integrate.
+$$\int\int \psi(y)w(y)p(t,y,x)\phi(x)dydx=\int\phi(x)w(x)
+\IE_x\left[\exp\left(\int_0^t(F+\gamma\Delta r)(Y_s)ds\right)\psi(Y_t)\right]dydx.$$
+
+Writing $\hat{T}_t$ for the semigroup corresponding to the motion of 
+ancestral lineages backwards in time (that is the semigroup corresponding
+to $p(t,x,y)$), we can write this as 
+$$\int \psi(y)w(y)\hat{T}_t\phi(y)dy=\int\phi(x)w(x)
+\IE_x\left[\exp\left(\int_0^t(F+\gamma\Delta r)(Y_s)ds\right)\psi(Y_t)\right]dx.$$
+Differentiating with respect to $t$ at $t=0$, and writing 
+$\hat{\mathcal L}$ for the generator of $\hat{T}_t$, we find
+\begin{eqnarray*}
+\int \psi(y)w(y)\widehat{\mathcal L}\phi(y)dy&=&
+\int\phi(x)w(x)\left({\mathcal L}^Y\psi(x)+\psi(x)(F+\gamma\Delta r)\psi(x)\right)dx\\
+&=&\int\phi(x)w(x)\left(\gamma\Delta(r\psi)-\gamma\psi\Delta r -\mathfrak{c}\nabla\psi 
++(F+\gamma\Delta r)(\psi)\right)dx\\
+&=&\int\phi(x)w(x)\left(\gamma\Delta(r\psi)-\mathfrak{c}\nabla\psi+F(\psi)\right)dx\\
+&=&
+\int\psi(x)\left[r\Delta(\gamma \phi w)+F\phi w+\mathfrak{c}\nabla(\phi w)\right]dx.
+\end{eqnarray*}
+Since $\psi$ was arbitrary,
+\begin{eqnarray*}
+\hat{\mathcal L}\phi&=&\frac{1}{w}\left[ r\Delta (\gamma\phi w)+F\phi w
++\mathfrak{c}\nabla(\phi w)\right]\\
+&=&\frac{\phi}{w}\left[r\Delta(\gamma w)+Fw+\mathfrak{c}\nabla w\right]
++\frac{1}{w}\left[r\gamma w\Delta \phi +2\nabla (\gamma w)
+\nabla\phi+\mathfrak{c}w\nabla\phi\right]\\
+&=&r\gamma\left(\Delta\phi+2\frac{\nabla(\gamma w)}{\gamma w}\nabla\phi\right)
++\mathfrak{c}\nabla\phi,
+\end{eqnarray*}
+where we have used that $w$ solves~(\ref{profile}).
+
+\end{proof}
 

### 2022-04-07 forwards-and-backwards.tex
Update on Overleaf.

@@
 \section{Model and main results}
+    \label{sec: Model and main results}
 
@@
     from $\IR^d \times \IR_{\ge 0}$ to $\IR_{\ge 0}$.
-    Furthermore, suppose $r_\theta$ takes values in $[0, 1]$
+    Furthermore, suppose $r$ takes values in $[0, 1]$
     and has uniformly bounded second derivatives,
@@
         =
-        r(x, \smooth{r} \eta(x))
-        \gamma(\smooth{\gamma} \eta(x))
+        r(x, \smooth{r} \eta^{\theta}(x))
+        \gamma(\smooth{\gamma} \eta^{\theta}(x))
         - \frac{1}{\theta}
-        F(x, \smooth{F} \eta(x)) .
+        F(x, \smooth{F} \eta^{\theta}(x)) .
     \end{align}
@@
     offspring of mass $1/N$ are produced at location $x$
-    with rate $\theta \gamma(x, \smooth{\gamma} \eta(x)) N \eta(dx)$
-    and adults die at location $x$ with rate $\theta \mu(x, \eta) N \eta(dx)$,
+    with rate $\theta \gamma(x, \smooth{\gamma} \eta^{\theta}(x)) N \eta^{\theta}_s(dx)$
+    and adults die at location $x$ with rate $\theta \mu(x, \eta) N \eta^{\theta}_s(dx)$,
     (i.e., at rates $\theta \gamma$ and $\theta \mu$ per capita respectively).
@@
     an offspring at $x$ establishes instantaneously
-    with probability $r(x, \smooth{r} \eta(x))$, or else dies.
+    with probability $r(x, \smooth{r} \eta^{\theta}(x))$, or else dies.
+\end{definition}
+
+We will now define $(\eta^{\theta}(t))_{t \geq 0}$
+explicitly as a solution to a Martingale problem.
+
+\begin{definition}[Martingale Problem Characterisation]
+    \label{Def: Rescaled Models}
+We define $(\eta^{\theta}_t)_{t \geq 0}$ to be the solution to the Martingale Problem,
+with initial condition $\eta^{\theta}_0$,
+such that for all smooth functions $f \in C^{2}_{0}(\mathbb{R}^d)$,
+\begin{equation}
+    \label{eq: Pre-limit Martingale Characterisation}
+\begin{aligned}
+&     M^{\theta}_t(f)\\
+:=&  \langle f,\eta^{\theta}_t \rangle
+        -\langle f,\eta^{\theta}_0 \rangle\\
+ &-  \int_{0}^{t}\bigg\{   \int\left(   \int \theta
+ \left(
+        f(z)r\big(z,\varrho_{r}*\eta^{\theta}_{s}(z)\big)
+            -f(x)r\big(x,\varrho_{r}*\eta^{\theta}_{s}(x)\big)
+            \right)
+                    q_\theta(x,dz)\right)
+                            \gamma\big(x,\varrho_{\gamma}*\eta^{\theta}_{s}(x)\big)
+                            \eta^{\theta}_{s}(dx)\\
+& \qquad +\int 
+f(x)F\big(x,\varrho_{F}*\eta^{\theta}_{s}(x)\big)
+\eta^{\theta}_{s}(dx)\bigg\} ds
+\end{aligned}    
+\end{equation}
+is a martingale with quadratic variation
+\begin{equation}
+\begin{aligned}
+[ M^{\theta}_t(f)] =& 
+\frac{\theta}{N} \int_{0}^{t}\bigg\{
+\langle \gamma\big(x,\varrho_{\gamma}*\eta^{\theta}_{s}(x)\big)
+\int f^2(y)r\big(y,\varrho_{r}*\eta^{\theta}_{s}(y)\big)q_\theta(x,dy) 
+,\eta^{\theta}_{s}(dx)\rangle\\
+& \qquad \qquad +\langle \mu\big(x,\eta^{\theta}_{s}\big)f^2(x) 
+,\eta^{\theta}_{s}(dx)\rangle \bigg\}ds. 
+\end{aligned}    
+\end{equation}
+
 \end{definition}
@@
 $$
-    \gamma(x, \smooth{\gamma} \eta(x))
-    \int r(x, \smooth{r} \eta(y)) q(x, dy) ,
+    \gamma(x, \smooth{\gamma} \eta^{\theta}(x))
+    \int r(x, \smooth{r} \eta^{\theta}(y)) q(x, dy) ,
 $$
@@
     \frac{
-        r(y, \smooth{r} \eta(y)) q_\theta(x, dy)
+        r(y, \smooth{r} \eta^{\theta}(y)) q_\theta(x, dy)
     }{
@@
     }{
-        r(x, \smooth{r} \eta(x))
+        r(x, \smooth{r} \eta^{\theta}(x))
     } .
@@
         \int_0^t \big\langle
-            \gamma(x, \smooth{\gamma} \eta_s(x))
+            \gamma(x, \smooth{\gamma} \eta^{\theta}_{s}(x))
             \mathcal{B}\left(
-                f(\cdot) r(\cdot, \smooth{r} \eta_s(\cdot))
+                f(\cdot) r(\cdot, \smooth{r} \eta^{\theta}_{s}(\cdot))
             \right)(x)
@@
             f(x)
-            F(x, \smooth{F} \eta_s(x)),
-            \eta_s(dx)
+            F(x, \smooth{F} \eta^{\theta}_{s}(x)),
+            \eta^{\theta}_{s}(dx)
         \big\rangle ds,
@@
         \big\langle
-            \gamma\left( x, \smooth{\gamma} \eta_s(x) \right)
-            r\left(x, \smooth{r} \eta_s(x) \right)
+            \gamma\left( x, \smooth{\gamma} \eta^{\theta}_{s}(x) \right)
+            r\left(x, \smooth{r} \eta^{\theta}_{s}(x) \right)
             f^2(x),
-            \eta_s (dx)
+            \eta^{\theta}_{s} (dx)
         \big\rangle ds. 
@@
     =
-    F \left( \int f(x)\eta(dx) \right),
+    F \left( \int f(x)\eta^{\theta}_s(dx) \right),
 $$
@@
 \right]\\
-=\theta\int\int f(z)r_\theta(z,\eta)q_\theta(x,dz)
-\gamma_\theta(x,\eta)
-\eta(dx)-\theta\int f(x)\mu_\theta(x,\eta)
-\eta(dx).
+=\theta\int\int f(z)r(z,\eta)q_\theta(x,dz)
+\gamma(x,\eta)
+\eta^{\theta}_s(dx)-\theta\int f(x)\mu(x,\eta)
+\eta^{\theta}_s(dx).
 \end{multline}
@@
 \int\left(\int \theta \left(
-f(z)r_\theta(z,\eta)- f(x)r_\theta(x,\eta)\right)
+f(z)r(z,\eta)- f(x)r(x,\eta)\right)
 q_\theta(x,dz)\right)
-\gamma_\theta(x,\eta)
-\eta(dx)
+\gamma(x,\eta)
+\eta^{\theta}_s(dx)
 \\
-+\int\theta\int f(x)\Big(r_\theta(x,\eta)
-\gamma_\theta(x,\eta)
--\mu_\theta(x,\eta)\Big)
-\eta(dx).
++\int\theta\int f(x)\Big(r(x,\eta)
+\gamma(x,\eta)
+-\mu(x,\eta)\Big)
+\eta^{\theta}_s(dx).
 \end{multline}
@@
 \begin{eqnarray}
-r_\theta(x,\eta)&\stackrel{\theta\to\infty}{\longrightarrow}&
+r(x,\eta)&\stackrel{\theta\to\infty}{\longrightarrow}&
 r(x,\Xi)\\
-\gamma_\theta(x,\eta)&\stackrel{\theta\to\infty}{\longrightarrow}&
+\gamma(x,\eta)&\stackrel{\theta\to\infty}{\longrightarrow}&
 \gamma(x,\Xi)\\
@@
 \Delta \big(r(\cdot,\Xi)f(\cdot)\big)(x);\\
-\theta \Big(r_\theta(x,\eta)\gamma_\theta (x,\eta)
--\mu_\theta (x,\eta)\Big)
+\theta \Big(r(x,\eta)\gamma (x,\eta)
+-\mu (x,\eta)\Big)
  &\stackrel{\theta\to\infty}{\longrightarrow}& 
@@
 mature offspring is Poisson with parameter
-$$\gamma_\theta(x,\eta)\int 
-r_{\theta}(y,\eta) q_{\theta}(x, dy)
-=\gamma_\theta(x,\eta)p_\theta(x,\eta).$$
+$$\gamma(x,\eta)\int 
+r(y,\eta) q_{\theta}(x, dy)
+=\gamma(x,\eta)p_\theta(x,\eta).$$
 Offspring that survive to maturity are distributed about the parent
@@
 $$\overline{q}_\theta(x,\eta,dy):=
-\frac{r_{\theta}(y,\eta)q_\theta(x,dy)} 
-{\int r_{\theta}(z,\eta)q_\theta(x,dz)}. 
+\frac{r(y,\eta)q_\theta(x,dy)} 
+{\int r(z,\eta)q_\theta(x,dz)}. 
 $$
@@
 $$\IE[P(x)]=
-\gamma_\theta (x,\eta) \int 
-r_{\theta}(z,\eta)q_\theta(x,dz),$$ 
+\gamma (x,\eta) \int 
+r(z,\eta)q_\theta(x,dz),$$ 
 the contribution to the quadratic variation from birth events, which
@@
 (so $N\theta |\eta|$ overall), is
-$$\langle N\theta \gamma_\theta(x,\eta)
-\int \frac{1}{N^2}f^2(y)r_{\theta}(y,\eta)
+$$\langle N\theta \gamma(x,\eta)
+\int \frac{1}{N^2}f^2(y)r(y,\eta)
 q_\theta(x,dy) 
-,\eta(dx)\rangle.$$
+,\eta^{\theta}_s(dx)\rangle.$$
 The increment in $\langle f, \eta\rangle$ resulting from 
@@
 \frac{1}{2}N\theta \left\{
-\langle \gamma_\theta(x,\eta)
-\int \frac{1}{N^2}f^2(y)r_\theta(y,\eta)q_\theta(x,dy) 
-,\eta(dx)\rangle
-+\langle \mu_\theta(x,\eta)\frac{1}{N^2}f^2(x) 
-,\eta(dx)\rangle\right\}.
+\langle \gamma(x,\eta)
+\int \frac{1}{N^2}f^2(y)r(y,\eta)q_\theta(x,dy) 
+,\eta^{\theta}_s(dx)\rangle
++\langle \mu(x,\eta)\frac{1}{N^2}f^2(x) 
+,\eta^{\theta}_s(dx)\rangle\right\}.
 $$
@@
 
-Now we
-will present a lookdown construction for $(\overline{\eta}^{\epsilon,\theta,N}(t))_{t \geq 0}$ stated in Definition \ref{Def: Rescaled Models}
-in the spirit of~\cite{kurtz/rodrigues:2011}. 
+Now we will present a lookdown construction for $(\eta^{\theta}(t))_{t \geq 0}$
+stated in Definition \ref{Def: Rescaled Models} in the spirit of~\cite{kurtz/rodrigues:2011}. 
 The key benefit of working in such a framework is that
-we shall be able to preserve the notion of individuals, and in particular their genealogies, when we pass to the limit. Our notation will follow a standard pattern.
+we shall be able to preserve the notion of individuals,
+and in particular their genealogies,
+when we pass to the limit.
+Our notation will follow a standard pattern.
 
 % % % % % % % % % % % % % % % %
-\subsection*{Prelimit Models and Notation}\label{Prelimit Models and Notation Section}
-
-In the prelimiting models each individual in the population will be assigned a 
-`level' from $[0,\lambda]$.
-We also let $\lambda$ takes on the role of $N$ in \S \ref{sec: model and results}, i.e.
-each individual has mass $1/\lambda$ in the scaling limit.
-Speed is once again scaled by $\theta$ and local radius by $\varepsilon(\theta)$.\\
-A state of the discrete population model will be of the form $\eta=\sum\delta_{(x,u)}$, where $x$ denotes the  
-spatial location of an individual, and $u$ is its level. Just as we did in \S\ref{prelimiting spatial model}, we shall
-abuse notation and treat $\eta$ both as a set and as a counting
-measure. The population of \S\ref{prelimiting spatial model}
-is recovered as $\overline{\eta}=\frac{1}{\lambda}\sum_{(x,u)\in\eta}\delta_x$, i.e. $\overline{\eta}$ is the spatial projection of our spatial-level model $\eta$. 
-Conditional on $\overline{\eta}$, the levels of individuals in 
-the population will be independent, uniformly distributed random variables
-on $[0,\lambda]$. All of this can be found in \cite{etheridge/kurtz:2018},\cite{kurtz/rodrigues:2011}.
+\subsection*{Lookdown Representation and Notation}
+\label{sec: Lookdown Representation and Notation}
+
+In the prelimiting models,
+each individual in the population
+will be assigned a `level' from $[0,\lambda]$.
+
+A state of the discrete population model will be of the form $\xi=\sum\delta_{(x,u)}$,
+where $x$ denotes the spatial location
+of an individual, and $u$ is its level.
+We shall abuse notation and treat $\xi$ both as a set and as a counting measure.
+The spatial population described in \S \ref{sec: Model and main results} is recovered as
+$$\eta=\frac{1}{\lambda}\sum_{(x,u)\in\xi}\delta_x,$$
+i.e. $\eta$ is the re-scaled spatial projection of our spatial-level model $\xi$. 
+Conditional on the spatial population $\eta$,
+the levels of individuals in the population
+will be independently and uniformly distributed
+on $[0,\lambda]$.
+Similar lookdown constructions can be found in \cite{etheridge/kurtz:2018},\cite{kurtz/rodrigues:2011}.
 Test functions for this enriched process take the form
@@
 \label{test functions}
-f(\eta)=\prod_{(x,u)\in\eta}g(x,u)=\exp\left(\int\log g(x,u)\eta(dx, du)\right),
+f(\xi)=\prod_{(x,u)\in \xi}g(x,u)=\exp\left(\int \log g(x,u)\xi(dx, du)\right),
 \end{equation}
 where $g(x,u)$ is differentiable in $u$ and 
-smooth in $x$. Moreover, $0\leq g(x,u) \leq 1$ for all $u\in [0,\lambda]$, and 
-$g(x,u)\equiv 1$ for $u\geq \lambda$.
-
-In the expressions that follow, we shall often see one or more factor of
-$1/g(x,u)$; 
-it should be understood that if $g(x,u)=0$, then it simply cancels 
+smooth in $x$.
+Moreover, $0\leq g(x,u) \leq 1$ for all $u\in [0,\lambda]$,
+and $g(x,u)\equiv 1$ for $u\geq \lambda$.
+
+In the expressions that follow,
+we shall often see one or more factor of $1/g(x,u)$;
+it should be understood that if $g(x,u)=0$,
+then it simply cancels 
 the corresponding factor in $f(\eta)$.
@@
 % % % % % % % % % % % % % % % %
-\subsection*{Generator of the Scaled Lookdown Model}
-
-In the notation of \S\ref{heuristics}, we now write down the 
-generator of the scaled population model with levels where 
-$\lambda$ is the scaling factor of the mass of an individual, $\theta(\lambda)$ is the scaling factor for time and the level of an individual particle must be in $[0,\lambda]$.  
-Recall that we only track the adult population; maturity, if achieved, is 
-instantaneous. Furthermore, at rate $\theta\gamma_{\theta}(x, \overline{\eta})$ a parent gives birth to a single juvenile offspring.
-
-We should consider an initial population of $O(\lambda)$ many particles with levels uniformly distributed between $[0, \lambda]$.
-We write $(\eta^{\theta, \lambda}(t))_{t \geq 0}$ for our population at the $\theta$th stage of rescaling.
-To recover the scaling of \S\ref{sec: model and results} we scale the empirical distribution of particles alive with a factor of $1/\lambda$, so we write $$\overline{\eta}^{\theta, \lambda}(t)=\frac{1}{\lambda}\sum\limits_{\substack{(X(t),U(t))\in \eta \\ U(t) < \lambda}} \delta_{X(t)}.$$
-From here onwards we write $\eta$ to be the particle systems with levels while $\overline{\eta}$ is the normalised empirical distribution.
-An individual of the population with state $\eta$ living at spatial location $x$ produces
-one adult offspring at rate $\theta\gamma^{\mathfrak{m}}_{\theta}(x, \overline{\eta})$, where
-$$\gamma^{\mathfrak{m}}_{\theta}(x,\overline{\eta})=\gamma_\theta(x,\overline{\eta})
-\int r_\theta (y, \overline{\eta})q_\theta(x,dy).
-$$
+\subsubsection*{Generator of the Lookdown Model}
+
+We now write down the generator of
+the scaled population model with levels where 
+$\lambda$ is the scaling factor of the mass of an individual,
+$\theta(\lambda)$ is the scaling factor for time,
+and the level of an individual particle must be in $[0,\lambda]$.
+Recall that we only track the adult population; maturity, if achieved, is instantaneous.
+Furthermore, at rate $\theta\gamma(x, \eta)$,
+a parent gives birth to a single juvenile offspring.
+
+We should consider an initial population of $O(\lambda)$ many particles with levels
+uniformly distributed between $[0, \lambda]$.
+We write $(\xi^{\theta, \lambda}(t))_{t \geq 0}$
+for our population at the $\theta$-th stage of rescaling.
+To recover the scaling in \S\ref{sec: Model and main results},
+we scale the empirical distribution of particles with a factor of $1/\lambda$,
+so we write
+$$\eta^{\theta, \lambda}_t:=\frac{1}{\lambda}\xi^{\theta, \lambda}_t(dx \times [0,\lambda])=
+\frac{1}{\lambda}\sum\limits_{\substack{(X(t),U(t))\in \xi \\ U(t) < \lambda}} \delta_{X(t)}.$$ 
+From here onwards,
+we write $\xi$ to be the particle systems with levels,
+while $\eta$ is the normalised empirical distribution.
+An individual in the spatial population $\eta$ living at spatial location $x$
+produces one adult offspring at rate $\theta\gamma^{\mathfrak{m}}_{\theta}(x, \eta)$, where
+$$\gamma^{\mathfrak{m}}_{\theta}(x,\eta)=\gamma(x,\eta) \int r (y, \eta)q_\theta(x,dy).$$
+
 The location of this offspring is given by
 the distribution 
-\[ q^{\mathfrak{m}}_\theta(x,\overline{\eta},dy) = \frac{r(y,\overline{\eta}) q_{\theta}(x,dy)}{\int_{\mathbb{R}^d} r(y,\overline{\eta}) q_{\theta}(x,dy)}.
-\] In the lookdown version of our model, the individual $(x,u)\in\eta^{\theta, \lambda}$ gives
-birth to an offspring at rate 
-$2(\lambda-u)\lambda^{-1}\theta \gamma^{\mathfrak{m}}_{\theta}(x, \overline{\eta})$. 
-(Averaging
-over the distribution of the
-level $u$ we recover $\theta \gamma^{\mathfrak{m}}_{\theta}(x, \overline{\eta})$.)
+\[ q^{\mathfrak{m}}_\theta(x,\eta,dy) = \frac{r(y,\eta) q_{\theta}(x,dy)}{\int_{\mathbb{R}^d} r(y,\eta) q_{\theta}(x,dy)}. \]
+
+In the lookdown version of our model,
+the individual $(x,u)\in \xi^{\theta, \lambda}$
+gives birth to an offspring at rate 
+$2(\lambda-u)\lambda^{-1}\theta \gamma^{\mathfrak{m}}_{\theta}(x, \eta)$. 
+(Averaging over the distribution of the
+level $u$,
+we recover $\theta \gamma^{\mathfrak{m}}_{\theta}(x, \eta)$.)
 
 A new level $u_1$ is sampled independently and
-uniformly from $[u,\lambda]$, and the parent and the offspring 
-are assigned in random order to the  levels $\{u, u_1\}$.
-This random assignment of levels to child and offspring ensures that conditional on $\overline{\eta}$, the levels assigned to individuals are i.i.d.
+uniformly from $[u,\lambda]$,
+and the parent and the offspring are assigned in random order to the  levels $\{u, u_1\}$.
+This random assignment of levels to parent
+and offspring ensures that conditional on $\eta$,
+the levels assigned to individuals are i.i.d.
 uniform random variables.
-Otherwise, the levels of the initial population would be lower than those of the descendants.\\
-Evidently this mechanism increases the proportion of individuals with
-higher levels. To restore the property that,
-conditional
-on $\overline{\eta}$, the intensity of
-levels is conditionally uniform, we impose that 
-the level associated with
-$(x,u)\in\eta$ evolves
-according to the differential equation
-$$\dot{v}= \theta \gamma^{\mathfrak{m}}_{\theta}(x, \overline{\eta}) 
+Otherwise, the levels of the initial population would be lower than those of the descendants.
+
+Evidently this mechanism increases the proportion
+of individuals with higher levels.
+To restore the property that,
+conditional on $\eta$,
+the intensity of levels is conditionally uniform,
+we impose that 
+the level associated with $(x,u)\in\eta$
+evolves according to the differential equation
+$$\dot{v}= \theta \gamma^{\mathfrak{m}}_{\theta}(x, \eta) 
 \left\{\lambda^{-1}(\lambda -v)^{2}
@@
 See~\cite{etheridge/kurtz:2018}, Section~3.4 for a detailed explanation.
-In order to incorporate death, the level of the individual $(x,u)\in \eta$ 
-moves upwards at an additional 
-rate $\theta \mu_\theta(x,\overline{\eta})$ (on reaching level $\lambda$ an
-individual is deemed to
-have died). Overall, we assume that the level associated with $(x,u)\in\eta$
+In order to incorporate death,
+the level of the individual $(x,u)\in \eta$ 
+moves upwards at an additional rate
+$\theta \mu(x,\eta)$
+(on reaching level $\lambda$
+an individual is deemed to have died).
+Overall, we assume that
+the level associated with $(x,u)\in\eta$
 evolves according to
-$$\dot{u}= \theta \gamma^{\mathfrak{m}}_{\theta}(x, \overline{\eta}) 
+$$\dot{u}= \theta \gamma^{\mathfrak{m}}_{\theta}(x, \eta) 
 \left\{\lambda^{-1}(\lambda -u)^{2}
--(\lambda -u)\right\}+\theta \mu_\theta(x,\overline{\eta})u.$$
+-(\lambda -u)\right\}+\theta \mu(x,\eta)u.$$
 We shall write 
-$$b_{\theta, \lambda}(x,\overline{\eta}):=\theta\big\{\gamma^{\mathfrak{m}}_{\theta}(x,\overline{\eta})
--\mu_\theta(x,\overline{\eta})\big\}.$$
-Note that this quantity captures the deviation from criticality in the branching
-mechanism. In this notation, the differential equation governing the level of the
-individual $(x,u)\in\eta$ is
+$$b_{\theta, \lambda}(x,\eta):=\theta\big\{\gamma^{\mathfrak{m}}_{\theta}(x,\eta)
+-\mu(x,\eta)\big\}.$$
+Note that this quantity captures
+the deviation from criticality
+in the branching mechanism.
+In this notation,
+the differential equation 
+governing the level of the individual $(x,u)\in\eta$ is
 \begin{align}
-\dot{u}&=\lambda \theta \gamma^{\mathfrak{m}}_{\theta}(x,\overline{\eta}) 
+\dot{u}&=\lambda \theta \gamma^{\mathfrak{m}}_{\theta}(x,\eta) 
 \left\{\left(1-\frac{u}{\lambda}\right)^{2}
--1 +2\frac{u}{\lambda}\right\} -b_{\theta, \lambda}(x,\overline{\eta})u \nonumber \\
-&=\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\overline{\eta}) u^2 -b_{\theta, \lambda}(x,\overline{\eta})u. \label{differential equation for level}
+-1 +2\frac{u}{\lambda}\right\} -b_{\theta, \lambda}(x,\eta)u \nonumber \\
+&=\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\eta) u^2 -b_{\theta, \lambda}(x,\eta)u. \label{differential equation for level}
 \end{align}
-In this setting, the generator of our model acting on the test functions $f(\eta)=\prod_{(x,u) \in \eta}g(x,u)$ satisfies
+In this setting, the generator of our model
+acting on the test functions $f(\eta)=\prod_{(x,u) \in \eta}g(x,u)$
+satisfies
 %We assume that  locations in ${\mathbb{ R}}^d$.
+
 \begin{eqnarray}\label{Generator of prelimit simplest model}
 &&A_{\theta, \lambda}f(\eta ) \nonumber \\
-&&\quad =f(\eta )\,\sum_{(x,u)\in\eta}\,2\lambda^{-1}\theta \gamma^{\mathfrak{m}}_{\theta}(x, \overline{\eta})
+&&\quad =f(\eta )\,\sum_{(x,u)\in\eta}\,2\lambda^{-1}\theta \gamma^{\mathfrak{m}}_{\theta}(x, \eta)
 \int_u^{
-\lambda}\Bigg(\frac 12\frac {\int_{\mathbb{R}^d}g(y,u)q^{\mathfrak{m}}_\theta(x,\overline{\eta },d
+\lambda}\Bigg(\frac 12\frac {\int_{\mathbb{R}^d}g(y,u)q^{\mathfrak{m}}_\theta(x,\eta,d
 y)g(x,v_1)}{g(x,u)} \label{multgen3}\\
 &&\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad
-+\frac 12\int_{\mathbb{R}^d}g(y,v_1)q^{\mathfrak{m}}_\theta(x,\overline{\eta} ,dy)-
++\frac 12\int_{\mathbb{R}^d}g(y,v_1)q^{\mathfrak{m}}_\theta(x,\eta ,dy)-
 1\Bigg)dv_1\nonumber\\
-&&\quad \quad +f(\eta )\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\overline{\eta}) u^2 -b_{\theta, \lambda}(x,\overline{\eta})u\right)\frac {\partial_u g(x,u)}{g(x,u)}\nonumber\\
-&&\quad =f(\eta )\,\sum_{(x,u)\in\eta}\,2 \gamma^{\mathfrak{m}}_{\theta}(x, \overline{\eta})\lambda^{-1}\int_u^{
-\lambda}\Bigg(\frac 12\frac {\theta\int_{\mathbb{R}^d}(g(y,u)-g(x,u))q^{\mathfrak{m}}_\theta(x,\bar{
-\eta },dy)g(x,v_1)}{g(x,u)}\non\\
-&&\qquad\qquad\qquad\qquad\qquad\qquad\qquad +\theta\int_{\mathbb{R}^d}\left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_\theta(x,\overline{\eta },dy)\Bigg)dv_1\nonumber\\
+&&\quad \quad +f(\eta )\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\eta) u^2 -b_{\theta, \lambda}(x,\eta)u\right)\frac {\partial_u g(x,u)}{g(x,u)}\nonumber\\
+&&\quad =f(\eta )\,\sum_{(x,u)\in\eta}\,2 \gamma^{\mathfrak{m}}_{\theta}(x, \eta)\lambda^{-1}\int_u^{
+\lambda}\Bigg(\frac 12\frac {\theta\int_{\mathbb{R}^d}(g(y,u)-g(x,u))q^{\mathfrak{m}}_\theta(x,\eta,dy)g(x,v_1)}{g(x,u)}\non\\
+&&\qquad\qquad\qquad\qquad\qquad\qquad\qquad +\theta\int_{\mathbb{R}^d}\left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_\theta(x,\eta,dy)\Bigg)dv_1\nonumber\\
 &&\qquad\qquad
-+f(\eta )\sum_{(x,u)\in\eta}\,\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\overline{\eta}) u^2 -b_{\theta, \lambda}(x,\overline{\eta})u\right)\frac {\partial_u g(x,u)}{g(x,u)}.\nonumber
++f(\eta )\sum_{(x,u)\in\eta}\,\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\eta) u^2 -b_{\theta, \lambda}(x,\eta)u\right)\frac {\partial_u g(x,u)}{g(x,u)}.\nonumber
 \end{eqnarray}
-The two terms under the integral
-correspond, respectively, to the parent being assigned 
-a level other than $u$, and being reallocated to the level $u$ during a
-birth event. In the first case, the parent at location $x$, which had level $u$ before the 
-event, moves to level $v_1$, and the child is inserted at level $u$ and location $y$; in 
-the second the parent retains its level, and offspring is inserted at
-level $v_1$.\\~\\
-
-As in Definition \ref{Def: Rescaled Models}, the rates $\gamma_{\theta},r_\theta, \mu_{\theta}$ in our re-scaled lookdown models  depend on the local density of $\eta$ through a mollification with $\varrho_{\varepsilon}$.
+The two terms under the integral correspond, respectively,
+to the parent being assigned a level other than $u$,
+and being reallocated to the level $u$
+during a birth event.
+In the first case, the parent at location $x$,
+which had level $u$ before the event,
+moves to level $v_1$,
+and the child is inserted at level $u$
+and location $y$;
+in the second the parent retains its level,
+and offspring is inserted at level $v_1$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection*{Scaling of the Pre-limit}
+
+We also let $\lambda$ takes on the role of $N$
+in \S \ref{sec: Model and main results},
+i.e. each individual has mass $1/\lambda$
+in the scaling limit.
+Time is once again scaled by $\theta$
+and local interaction radius by $\varepsilon_{\gamma}$ and $\varepsilon_{r}$.
+
+As in Definition \ref{Def: Rescaled Models},
+the rates $\gamma,r, \mu_{\theta}$
+in our re-scaled lookdown models 
+depend on the local density of $\eta$
+through mollifications with 
+$\varrho_{\gamma}, \varrho_{r}$ and $\varrho_{F}$.
 We will now make our re-scaled lookdown model explicit.
 
-\begin{definition}\label{Def: Rescaled Lookdown Models}
-Let the coefficients $\tilde{\gamma}, \tilde{\mu}, \tilde{r}$ satisfy the conditions highlighted in Definition \ref{Def: Rescaled Models} and let $\varrho_{\varepsilon}$ be the kernel defined in Definition \ref{Defn: Kernel and Convolution}.
+\begin{definition}[Martingale Problem Characterisation]
+\label{Def: Rescaled Lookdown Models}
+Let the coefficients $\gamma, \mu, r$ satisfy the conditions highlighted in Definition \ref{Def: Rescaled Models} and let $\varrho_{\varepsilon}$ be the kernel defined in Definition \ref{Defn: Kernel and Convolution}.
 We define the following terms:
 \begin{align*}
-\gamma^{\mathfrak{m}}_{\varepsilon,\theta}(x, \overline{\eta}):=&~\tilde{\gamma}_{\theta}(x, \varrho_{\varepsilon}*\overline{\eta}(x)) \int \tilde{r}_{\theta}(y, \varrho_{\varepsilon}*\overline{\eta}(y))q_{\theta}(x,dy),\\
- q^{\mathfrak{m}}_{\varepsilon, \theta}(x,\overline{\eta},dy) :=&~ \frac{\tilde{r}_{\theta}(y,\varrho_{\epsilon}*\overline{\eta}(y)) q_{\theta}(x,dy)}{\int_{\mathbb{R}^d} \tilde{r}_{\theta}(y,\varrho_{\epsilon}*\overline{\eta}(y)) q_{\theta}(x,dy)},\\
-b_{\varepsilon, \theta, \lambda}(x, \overline{\eta}):=&~ \theta \bigg\{ \tilde{\gamma}_{\theta}(x, \varrho_{\varepsilon}*\overline{\eta}(x)) \int \tilde{r}_{\theta}(y, \varrho_{\varepsilon}*\overline{\eta}(y))q_{\theta}(x,dy)-\tilde{\mu}_{\theta}(x, \varrho_{\varepsilon}*\overline{\eta}(x)) \bigg\}
+\gamma^{\mathfrak{m}}_{\varepsilon,\theta}(x, \eta):=&~\gamma(x, \varrho_{\varepsilon}*\eta^{\theta}(x)) \int r(y, \varrho_{\varepsilon}*\eta^{\theta}(y))q_{\theta}(x,dy),\\
+ q^{\mathfrak{m}}_{\varepsilon, \theta}(x,\eta,dy) :=&~ \frac{r(y,\varrho_{\epsilon}*\eta^{\theta}(y)) q_{\theta}(x,dy)}{\int_{\mathbb{R}^d} r(y,\varrho_{\epsilon}*\eta^{\theta}(y)) q_{\theta}(x,dy)},\\
+b_{\varepsilon, \theta, \lambda}(x, \eta):=&~ \theta \bigg\{ \gamma(x, \varrho_{\varepsilon}*\eta^{\theta}(x)) \int r(y, \varrho_{\varepsilon}*\eta^{\theta}(y))q_{\theta}(x,dy)-\mu_{\theta}(x, \varrho_{\varepsilon}*\eta^{\theta}(x)) \bigg\}
 \end{align*}
-At the $\lambda$-stage of re-scaling, our test measures $\eta$ takes value in $\mathcal{M}_F(\mathbb{R}^d \times [0,\lambda])$, the set of finite measures on $\mathbb{R}^d \times [0,\lambda]$, and we define $$\overline{\eta}= \frac{1}{\lambda}\sum_{(x,u) \in \eta}\delta_x.$$
+At the $\lambda$-stage of re-scaling, our test measures $\eta$ takes value in $\mathcal{M}_F(\mathbb{R}^d \times [0,\lambda])$, the set of finite measures on $\mathbb{R}^d \times [0,\lambda]$, and we define $$\eta= \frac{1}{\lambda}\sum_{(x,u) \in \eta}\delta_x.$$
 We define $(\eta^{\varepsilon, \theta, \lambda}_t)_{t \geq 0}$ to be the (unique?) solution to the Martingale Problem with initial condition $\eta_0$ and generator $A_{\varepsilon, \theta, \lambda}$ that satisfies
@@
 &&A_{\epsilon, \theta, \lambda}f(\eta ) \\
-&&\quad =f(\eta )\,\sum_{(x,u)\in\eta}\,2 \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(x, \overline{\eta})\Bigg\{ \frac 12 \lambda^{-1}\int_u^{
+&&\quad =f(\eta )\,\sum_{(x,u)\in\eta}\,2 \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(x, \eta)\Bigg\{ \frac 12 \lambda^{-1}\int_u^{
 \lambda}g(x,v_1)dv_1\times \frac { \theta\int_{\mathbb{R}^d}(g(y,u)-g(x,u))q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\bar{
@@
 &&\qquad\qquad\qquad\qquad\qquad\qquad\qquad +\lambda^{-1}\theta\int_u^{
-\lambda}\int_{\mathbb{R}^d}\left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\overline{\eta },dy)dv_1\nonumber\Bigg\}\\
+\lambda}\int_{\mathbb{R}^d}\left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\eta,dy)dv_1\nonumber\Bigg\}\\
 &&\qquad\qquad
-+f(\eta )\sum_{(x,u)\in\eta}\,\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(x,\overline{\eta}) u^2 -b_{\varepsilon,\theta, \lambda}(x,\overline{\eta})u\right)\frac {\partial_u g(x,u)}{g(x,u)}.\nonumber
++f(\eta )\sum_{(x,u)\in\eta}\,\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(x,\eta) u^2 -b_{\varepsilon,\theta, \lambda}(x,\eta)u\right)\frac {\partial_u g(x,u)}{g(x,u)}.\nonumber
 \end{eqnarray}
@@
 \end{definition}
-In \S \ref{sec: Markov Mapping Theorem application}, through an application of the Markov Mapping Theorem, we will show that the spatial projection of $(\eta^{\varepsilon, \theta, \lambda}_t)_{t \geq 0}$ has the same distribution as $(\overline{\eta}^{\varepsilon, \theta, N}_t)_{t \geq 0}$ if we take $\lambda = N$.
+In \S \ref{sec: Markov Mapping Theorem application}, through an application of the Markov Mapping Theorem, we will show that the spatial projection of $(\eta^{\varepsilon, \theta, \lambda}_t)_{t \geq 0}$ has the same distribution as $(\eta^{\varepsilon, \theta, N}_t)_{t \geq 0}$ if we take $\lambda = N$.
 Specifically, we mean that when $\lambda=N$,
-$$(\overline{\eta}^{\varepsilon,\theta, \lambda}(t))_{t \geq 0}:=\left(\frac{1}{\lambda}\sum\limits_{\substack{(X(t),U(t))\in \eta^{\varepsilon,\theta, \lambda}(t) \\ U(t) < \lambda}} \delta_{X(t)}\right)_{t \geq 0}$$
-has the same distribution (as stochastic processes) as $(\overline{\eta}^{\varepsilon,\theta, N}_t)_{t \geq 0}$ in Definition \ref{Def: Rescaled Models}.
-As a result, we use the same notation $\overline{\eta}$ to denote these two essentially identical processes which take values in the space of empirical measures.
-On the other hand, we reserve the notation $\eta$ strictly for the spatial-level process.\\~\\ Furthermore, the application of Markov Mapping Theorem implies that particle levels are, conditional on $\overline{\eta}$, i.i.d and uniformly distributed between $[0, \lambda]$.
-Theorem A.10 in \cite{kurtz/rodrigues:2011} states that convergence of $(\eta^{\varepsilon, \theta, \lambda}_t)_{t \geq 0}$ to a conditionally Poisson system $(\xi_t)_{t \geq 0}$ with Cox measure $\Xi_t \times \Lambda$ is equivalent to convergence of $(\overline{\eta}^{\varepsilon, \theta, N}_t)_{t \geq 0}$ to $(\Xi_t)_{t \geq 0}$.
-As a result, it suffices for us to focus on tightness of $(\eta^{\varepsilon, \theta, \lambda}_t)_{t \geq 0}$ and spatial convergence of $(\overline{\eta}^{\varepsilon, \theta, N}_t)_{t \geq 0}$ as $\theta \to \infty$.
+$$(\eta^{\varepsilon,\theta, \lambda}(t))_{t \geq 0}:=\left(\frac{1}{\lambda}\sum\limits_{\substack{(X(t),U(t))\in \eta^{\varepsilon,\theta, \lambda}(t) \\ U(t) < \lambda}} \delta_{X(t)}\right)_{t \geq 0}$$
+has the same distribution (as stochastic processes) as $(\eta^{\theta}_t)_{t \geq 0}$ in Definition \ref{Def: Rescaled Models}.
+As a result, we use the same notation $\eta$ to denote these two essentially identical processes which take values in the space of empirical measures.
+On the other hand, we reserve the notation $\eta$ strictly for the spatial-level process.\\~\\ Furthermore, the application of Markov Mapping Theorem implies that particle levels are, conditional on $\eta$, i.i.d and uniformly distributed between $[0, \lambda]$.
+Theorem A.10 in \cite{kurtz/rodrigues:2011} states that convergence of $(\eta^{\varepsilon, \theta, \lambda}_t)_{t \geq 0}$ to a conditionally Poisson system $(\xi_t)_{t \geq 0}$ with Cox measure $\Xi_t \times \Lambda$ is equivalent to convergence of $(\eta^{\varepsilon, \theta, N}_t)_{t \geq 0}$ to $(\Xi_t)_{t \geq 0}$.
+As a result, it suffices for us to focus on tightness of $(\eta^{\varepsilon, \theta, \lambda}_t)_{t \geq 0}$ and spatial convergence of $(\eta^{\varepsilon, \theta, N}_t)_{t \geq 0}$ as $\theta \to \infty$.
 
@@
 \begin{equation}
-U_{\tau}(t)=U_{\tau}(\tau)+\int_{\tau}^{t}(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(s),\overline{\eta}(s))U^2_{\tau}(s)-b_{\varepsilon,\theta,\lambda}(X_{\tau}(s),\overline{\eta}(s))U_{\tau}(s))ds, ~~~ t \geq \tau.
+U_{\tau}(t)=U_{\tau}(\tau)+\int_{\tau}^{t}(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(s),\eta(s))U^2_{\tau}(s)-b_{\varepsilon,\theta,\lambda}(X_{\tau}(s),\eta(s))U_{\tau}(s))ds, ~~~ t \geq \tau.
 \end{equation}
@@
 \begin{equation}\label{New birth potential level}
-    U_{\tau+s}(\tau+s)=U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(\tau+s-), \overline{\eta}(\tau+s-))}.
-\end{equation}
-If $U_{\tau+s}(\tau+s)< \lambda$, a new particle is produced with location $X_{\tau}(\tau+s-)+H(X_{\tau}(\tau+s-), \overline{\eta}(\tau+s-),w)$ where $H(X_{\tau}(\tau+s-), \overline{\eta}(\tau+s-),w)$ is a function such that if $w$ is a uniformly distribution on $[0,1]$, then
+    U_{\tau+s}(\tau+s)=U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))}.
+\end{equation}
+If $U_{\tau+s}(\tau+s)< \lambda$, a new particle is produced with location $X_{\tau}(\tau+s-)+H(X_{\tau}(\tau+s-), \eta(\tau+s-),w)$ where $H(X_{\tau}(\tau+s-), \eta(\tau+s-),w)$ is a function such that if $w$ is a uniformly distribution on $[0,1]$, then
 \begin{equation}\label{eq: Individual Evolution Jump Kernel}
-P(H(x, \overline{\eta},w)\in C | \overline{\eta},x)=q^{\mathfrak{m}}(x, \overline{\eta},C).    
+P(H(x, \eta,w)\in C | \eta,x)=q^{\mathfrak{m}}(x, \eta,C).    
 \end{equation}
 Consequently, 
-$$X_{\tau}(\tau+s)=X_{\tau}(\tau+s-)+\kappa H(X_{\tau}(\tau+s-), \overline{\eta}(\tau+s),w)$$
+$$X_{\tau}(\tau+s)=X_{\tau}(\tau+s-)+\kappa H(X_{\tau}(\tau+s-), \eta(\tau+s),w)$$
 and 
-$$X_{\tau+s}(\tau+s)=X_{\tau}(\tau+s-)+(1-\kappa) H(X_{\tau}(\tau+s-), \overline{\eta}(\tau+s),w),$$
+$$X_{\tau+s}(\tau+s)=X_{\tau}(\tau+s-)+(1-\kappa) H(X_{\tau}(\tau+s-), \eta(\tau+s),w),$$
 that is if $\kappa=0$, the parent stays at its current level and the new particle is given the new
@@
 X_{\tau}(\tau+t)=&X_{\tau}(t)\\
-&+\int_{(0,t]\times[0,\infty]\times[0,1]\times\{0,1\}}\mathbbm{1}_{U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(\tau+s-), \overline{\eta}(\tau+s-))}<\lambda\}}\kappa    H(X_{\tau}(\tau+s-), \overline{\eta}(\tau+s),\omega) \\
+&+\int_{(0,t]\times[0,\infty]\times[0,1]\times\{0,1\}}\mathbbm{1}_{U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))}<\lambda\}}\kappa    H(X_{\tau}(\tau+s-), \eta(\tau+s),\omega) \\
 &\qquad \times \xi_{\tau}(ds,dv,dw,d\kappa).
@@
 \begin{align*}
-U_{\tau}(t)=&U_{\tau}(0)+\int_{0}^{t}\frac{1}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(s-), \overline{\eta}(s-))}dV_{\tau}(s)\\
-&+\int_{0}^{t}\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(s-), \overline{\eta}(s-))U^2_{\tau}(s)-b_{\varepsilon,\theta, \lambda}(X_{\tau}(s),\overline{\eta}(s))U_{\tau}(s))ds,\\
-X_{\tau}(t)=&X_{\tau}(0)+\int_{(0,t]\times[0,\infty]\times[0,1]\times\{0,1\}}\mathbbm{1}_{U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(\tau+s-), \overline{\eta}(\tau+s-))}<\lambda\}}\\
-&\qquad \times \kappa   H(X_{\tau}(s-), \overline{\eta}(s-),\omega)\zeta_{\tau}(ds,dv,dw,d\kappa)
+U_{\tau}(t)=&U_{\tau}(0)+\int_{0}^{t}\frac{1}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(s-), \eta(s-))}dV_{\tau}(s)\\
+&+\int_{0}^{t}\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(s-), \eta(s-))U^2_{\tau}(s)-b_{\varepsilon,\theta, \lambda}(X_{\tau}(s),\eta(s))U_{\tau}(s))ds,\\  
+X_{\tau}(t)=&X_{\tau}(0)+\int_{(0,t]\times[0,\infty]\times[0,1]\times\{0,1\}}\mathbbm{1}_{U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))}<\lambda\}}\\
+&\qquad \times \kappa   H(X_{\tau}(s-), \eta(s-),\omega)\zeta_{\tau}(ds,dv,dw,d\kappa)
 \end{align*}
@@
 \begin{remark}
-The factor $\frac{1}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(x, \overline{\eta})}$ that scales the jump in levels give an average birth rate of $\theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(s-), \overline{\eta}(s-))$.
-This is because for the potential birth to be a true birth, we impose that $$U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(\tau+s-), \overline{\eta}(\tau+s-))}< \lambda,$$ where $U_{\tau}(\tau+s)$ is uniformly distributed between $[0, \lambda]$.
-As a result, a true birth occurs between $[0,\delta t]$ if there exists $(s,v) \in [0,\delta t]\times [0, 2 (\lambda-U_{\tau}(\tau+s)) \lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(\tau+s-), \overline{\eta}(\tau+s-))]$.
-Averaging this over levels give a Poisson process with rate $ \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(\tau+s-), \overline{\eta}(\tau+s-))$.
+The factor $\frac{1}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(x, \eta)}$ that scales the jump in levels give an average birth rate of $\theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(s-), \eta(s-))$.
+This is because for the potential birth to be a true birth, we impose that $$U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))}< \lambda,$$ where $U_{\tau}(\tau+s)$ is uniformly distributed between $[0, \lambda]$.
+As a result, a true birth occurs between $[0,\delta t]$ if there exists $(s,v) \in [0,\delta t]\times [0, 2 (\lambda-U_{\tau}(\tau+s)) \lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))]$.
+Averaging this over levels give a Poisson process with rate $ \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))$.
 \end{remark}
@@
 In particular, we can now express our particle systems as
-$$\eta(t)=\frac{1}{\lambda}\sum_{U_{\tau}(t) < \lambda} \delta_{X_{\tau}(t),U_{\tau}(t)}, ~~\overline{\eta}(t)=\frac{1}{\lambda}\sum_{ U_{\tau}(t) < \lambda} \delta_{X_{\tau}(t)}.$$
+$$\eta(t)=\frac{1}{\lambda}\sum_{U_{\tau}(t) < \lambda} \delta_{X_{\tau}(t),U_{\tau}(t)}, ~~\eta(t)=\frac{1}{\lambda}\sum_{ U_{\tau}(t) < \lambda} \delta_{X_{\tau}(t)}.$$
 For further discussion refer to \S \ref{sec: Ulam-Harris Labels characterisation}.
@@
 \begin{aligned}
-\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(s), \overline{\eta}(s)) &\to \ell \gamma(X_{\tau}(s),\varrho_\varepsilon*\Xi(X_{\tau}(s)),\\
-b_{\varepsilon,\theta, \lambda}(X_{\tau}(s),\overline{\eta}(s)) &\to  F(X_{\tau}(s), (\varrho_{\varepsilon}*\overline{\eta})(X_{\tau}(s)))\\
-&+\gamma(X_{\tau}(s), (\varrho_{\varepsilon}*\Xi)(X_{\tau}(s)))\mathcal{B}r(\cdot,(\varrho_{\varepsilon}*\overline{\eta})(\cdot))(X_{\tau}(s)).
+\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(s), \eta(s)) &\to \ell \gamma(X_{\tau}(s),\varrho_\varepsilon*\Xi(X_{\tau}(s)),\\
+b_{\varepsilon,\theta, \lambda}(X_{\tau}(s),\eta(s)) &\to  F(X_{\tau}(s), (\varrho_{\varepsilon}*\eta)(X_{\tau}(s)))\\
+&+\gamma(X_{\tau}(s), (\varrho_{\varepsilon}*\Xi)(X_{\tau}(s)))\mathcal{B}r(\cdot,(\varrho_{\varepsilon}*\eta)(\cdot))(X_{\tau}(s)).
 \end{aligned}    
@@
 U_{\tau}(t)=&U_{\tau}(\tau )+\int_{\tau}^t\bigg\{\ell \gamma(X_{\tau}(s),\varrho_\varepsilon*\Xi(X_{\tau}(s)U_{\tau}^2(s) \\
-& -\big(F(X_{\tau}(s), (\varrho_{\varepsilon}*\overline{\eta})(X_{\tau}(s)))+\gamma(X_{\tau}(s), (\varrho_{\varepsilon}*\Xi)(X_{\tau}(s)))\mathcal{B}r(\cdot,(\varrho_{\varepsilon}*\overline{\eta})(\cdot))(X_{\tau}(s))\big)U_{\tau}(s))\bigg\}ds.
+& -\big(F(X_{\tau}(s), (\varrho_{\varepsilon}*\eta)(X_{\tau}(s)))+\gamma(X_{\tau}(s), (\varrho_{\varepsilon}*\Xi)(X_{\tau}(s)))\mathcal{B}r(\cdot,(\varrho_{\varepsilon}*\eta)(\cdot))(X_{\tau}(s))\big)U_{\tau}(s))\bigg\}ds.
 \end{aligned}
@@
 &&\qquad\qquad +\int_{\tau}^t\bigg\{\ell \gamma(X_{\tau}(s),\varrho_\varepsilon*\Xi(X_{\tau}(s)U_{\tau}^2(s) \\
-&&-\big(F(X_{\tau}(s), (\varrho_{\varepsilon}*\overline{\eta})(X_{\tau}(s)))+\gamma(X_{\tau}(s), (\varrho_{\varepsilon}*\Xi)(X_{\tau}(s)))\mathcal{B}r(\cdot,(\varrho_{\varepsilon}*\overline{\eta})(\cdot))(X_{\tau}(s))\big)U_{\tau}(s))\bigg\}ds,\end{eqnarray*}
+&&-\big(F(X_{\tau}(s), (\varrho_{\varepsilon}*\eta)(X_{\tau}(s)))+\gamma(X_{\tau}(s), (\varrho_{\varepsilon}*\Xi)(X_{\tau}(s)))\mathcal{B}r(\cdot,(\varrho_{\varepsilon}*\eta)(\cdot))(X_{\tau}(s))\big)U_{\tau}(s))\bigg\}ds,\end{eqnarray*}
 where
@@
     \label{sec:population_tightness_proofs}
-
-\begin{lemma}[Tightness for the population process]
-    Something like:
-    for all suitable $f$
-    and initial states $\eta^\theta_0 \to \eta_0$,
+To prove tightness of our population process, 
+we first show that the expected total mass of our population process at some fixed time $T>0$,
+is controlled uniformly across $\theta$.
+This is equivalent to the compact containment condition.
+
+To establish this control,
+we first prove a technical lemma which controls spatial density of our population,
+and then we use the BDG inequality on a martingale
+to give us control over the running supremum of our total population mass.
+
+Once we have control over the total mass of the population, 
+we will also have control over local densities.
+This then allows us to prove that the particle system is tight
+by an application of the Aldous-Rebelleon Criterion.
+
+\subsubsection{Compact Containment Condition}
+Before proving compact containment condition,
+we first prove a technical lemma that involves a bound on the Gaussian kernels.
+\begin{lemma}
+    \label{lem: gamma - r radius comparison}
+    Assume that $\varepsilon_{r}^2 + \frac{1}{\theta} < \varepsilon_{\gamma}^2,$ then
+    for all $f \in \mathcal{C}^{2}_{0}(\mathbb{R}^d)$
+    and for all $\eta \in \mathcal{M}_{f}(\mathbb{R}^d)$, we have
+
+    \begin{equation}\label{eq: gamma - r radius comparison bound}
+    \gamma\big(x,\varrho_{\gamma}*\eta(x)\big) \left| \theta \int_{\mathbb{R}^n} \big\{f\big(\varrho_{r}*\eta(y)\big)-f\big(\varrho_{r}*\eta(x)\big)\big\}\varrho_{1/\theta}(x-y)dy\right| \leq C_{\gamma, f}
+    \end{equation}
+    for some constant $C_{\gamma,f}$ independent of $\eta$ and $\theta$. 
+\end{lemma}
+\begin{proof}
+See Appendix.    
+\end{proof}
+\begin{lemma}[Compact Containment for the population process]
+Assume that $\eta^{\theta}_0 \to \eta_0$ weakly,
+then for all $T>0$, there exists some constant $C(T)$,
+such that
     \begin{align}
@@
             \sup_{0 \le t \le T}
-            \langle f, \eta^\theta_t \rangle
+            \langle 1, \eta^\theta_t \rangle
         \right]
-        \le C ,
+        \le C(T) ,
     \end{align}
@@
 \end{lemma}
-
-\comment{In which we Gronwall $\langle 1, \eta_t\rangle$ and the like.}
+\begin{proof}
+We first take $f \equiv 1$ in Equation \eqref{eq: Pre-limit Martingale Characterisation}. We have that
+
+\begin{equation}
+    \label{eq: Total Mass Martingale Characterisation}
+\begin{aligned}
+     M^{\theta}_t(1):=&  \langle 1,\eta^{\theta}_t \rangle
+        -\langle 1,\eta^{\theta}_0 \rangle\\
+ &-  \int_{0}^{t}\bigg\{   \int\left(   \int \theta
+ \left(
+        r\big(z,\varrho_{r}*\eta^{\theta}_{s}(z)\big)
+            -r\big(x,\varrho_{r}*\eta^{\theta}_{s}(x)\big)
+            \right)
+                    q_\theta(x,dz)\right)
+                            \gamma\big(x,\varrho_{\gamma}*\eta^{\theta}_{s}(x)\big)
+                            \eta^{\theta}_{s}(dx)\\
+& \qquad +\int F\big(x,\varrho_{F}*\eta^{\theta}_{s}(x)\big)
+\eta^{\theta}_{s}(dx)\bigg\} ds
+\end{aligned}    
+\end{equation}
+is a martingale.
+Therefore, taking expectations, we have
+\begin{equation}\label{eq: Total mass control generalised}
+\begin{aligned}
+&\mathbb{E}[\langle 1 ,\eta^{\theta}_{t}\rangle] \\
+\leq &  \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle] \\
+&+ \int_{0}^{t}\mathbb{E}\bigg\langle
+        \gamma\big(x,\varrho_{\gamma}*\eta^{\theta}_{s}(x)\big)
+            \left| \theta \int_{\mathbb{R}^n}
+                    \big\{r\big(\varrho_{r}*\eta^{\theta}_s(y)\big)-r\big(\varrho_{r}*\eta^{\theta}_s(x)\big)\big\}
+                    \varrho_{1/\theta}(x-y)dy\right| + C_F 
+                            ,\eta^{\theta}_s(dx)  \bigg\rangle ds\\
+\leq &  \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle] + (C_{\gamma,r} + C_F)\int_{0}^{t}\mathbb{E} \langle 1  ,\eta^{\theta}_s(dx) \rangle ds,
+\end{aligned}
+\end{equation}
+where the last inequality holds by Lemma \ref{lem: gamma - r radius comparison}.
+
+Applying Gronwall's inequality, we have that 
+\begin{equation}
+ \mathbb{E}[\langle 1 ,\eta^{\theta}_{t}\rangle] \leq \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle]e^{(C_{\gamma,r}+C_F)t}.   
+\end{equation}
+
+To prove compact containment condition, we apply BDG inequality.
+We denote $M^{*}_t(\phi)=\sup_{s \in [0,t]}M_t(\phi)$
+and define $h(t):=\sup_{s \in [0,t]}\langle 1, \eta^{\theta}_{s} \rangle$.
+We have that
+\begin{equation}\label{eq: Control quadratic variation}
+\begin{aligned}
+\mathbb{E}\{M^{*}_t(1)\} \leq & C \mathbb{E}\{[M_t(1)]^{1/2}\}\\
+\leq& C (1+\mathbb{E}\{[M_t(1)]\})\\
+\leq & C+\frac{\theta}{N}\int_{0}^{t} \left\langle \gamma(\varrho_{\gamma}*\eta^{\theta}_{s}(x))\int_{\mathbb{R}^n}r(\varrho_{r}*\eta^{\theta}_{s}(y)) q_\theta(x,dy)+\mu(x,\eta^{\theta}_{s}), \eta^{\theta}_{s}(dx) \right\rangle ds \\
+\leq & C+\frac{2\theta}{N}\int_{0}^{t} \left\langle \gamma(\varrho_{\gamma}*\eta^{\theta}_{s}(x))r(\varrho_{r}*\eta^{\theta}_{s}(x)), \eta^{\theta}_{s}(dx) \right\rangle ds \\
+& + \frac{1}{N}\int_{0}^{t} \left\langle \gamma (\varrho_{\gamma}*\eta^{\theta}_{s}(x))\theta\int_{\mathbb{R}^n}\left(r(\varrho_{r}*\eta^{\theta}_{s}(y))-r(\varrho_{r}*\eta^{\theta}_{s}(x))\right) q_\theta(x,dy), \eta^{\theta}_{s}(dx) \right\rangle ds\\
+\leq & C+ \frac{(2 \theta C_{\gamma,r}+C_{\gamma,r})\mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle]e^{(C_{\gamma,r}+C_F)t}}{N}.
+\end{aligned}
+\end{equation}
+
+As a result, we have that 
+\begin{equation}\label{eq: Total mass control supremum control}
+\begin{aligned}
+&\mathbb{E}[h(t)]:=\mathbb{E}\left[\sup_{s \in [0,t]}\langle 1 ,\eta^{\theta}_{s}\rangle\right] \\
+\leq &  \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle] \\
+&+ \sup_{\tau \in [0,t]} \int_{0}^{\tau}\mathbb{E} \bigg\langle \gamma(\varrho_{r}*\eta^{\theta}_{s}(x)) \left| \theta \int_{\mathbb{R}^n} \big\{r\big(\varrho_{r}*\eta^{\theta}_{s}(y)\big)-r\big(\varrho_{r}*\eta^{\theta}_{s}(x)\big)\big\}\varrho_{1/\theta}(x-y)dy\right| + C_F ,\eta^{\theta}_{s}(dx)  \bigg\rangle dw\\
+&+ \mathbb{E}\{M^{*}_t(1)\}\\
+\leq &  \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle] + (C_{\gamma,r} + C_F)\int_{0}^{t}\mathbb{E} \left[ \sup_{\tau \in [0,s]} \langle 1  ,\eta^{\theta}_{s} \rangle \right]ds+\mathbb{E}\{M^{*}_t(1)\}\\
+\leq &  \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle] + (C_{\gamma,r} + C_F)\int_{0}^{t}\mathbb{E} \left[ h(s) \right]ds+\frac{(2 \theta C_{\gamma,r}+C_{\gamma,r})\mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle]e^{(C_{\gamma,r}+C_F)t}}{N}.
+\end{aligned}
+\end{equation}
+Once again, with Gronwall's inequality we have 
+\begin{equation}
+\mathbb{E}[h(t)] 
+\leq   \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle]
+            \left(1+\frac{(2 \theta C_{\gamma,r}+C_{\gamma,r})e^{(C_{\gamma,r}+C_F)t}}{N}\right)e^{(C_{\gamma,r}+C_F)t}.  
+\end{equation}
+\end{proof}
+
+Note that as $\theta/N \to \ell$ and $N \to \infty$,
+the inequality on the right is bounded above by a constant $C(T)$
+independent of $\theta, N$.
+As a result
+
+\begin{equation}
+\limsup_{\theta \to \infty}\mathbb{P}\left[\sup_{s \in [0,T]}\langle 1 ,\eta^{\theta}_{s}\rangle \geq K\right] \leq \frac{C(T)}{K}    
+\end{equation}
+for any $K > 0$, giving us compact containment condition.
+
+\subsubsection{Controlling Jumps}
+To apply Aldous-Rebolledo criterion,
+(or see Theorem 3.9.1 or Theorem 3.8.6 in \cite{EK})
+it suffices to show that for all $f \in \mathcal{C}^2_{c}(\mathbb{R}^d)$
+and $\tau \in [0,T]$, we have 
+\begin{equation}
+\begin{aligned}
+\limsup_{s \to 0}\limsup_{\theta \to \infty}\mathbb{E}\left[\left| \langle f, \eta^{\theta}_{\tau+s}\rangle - \langle f, \eta^{\theta}_{\tau}\rangle \right|\right]& \to 0;\\
+\limsup_{s \to 0}\limsup_{\theta \to \infty}\mathbb{E}\left[\big| [M^{\theta}_{\tau+s}(f)] - [M^{\theta}_{\tau}(f)] \big|\right]& \to 0.
+\end{aligned}    
+\end{equation}
+Note that
+\begin{equation}
+\begin{aligned}
+ & \mathbb{E}\left[\left| \langle f, \eta^{\theta}_{\tau+s}\rangle - \langle f, \eta^{\theta}_{\tau}\rangle \right|\right] \\
+\leq & \mathbb{E}\Bigg[\bigg| \int_{\tau}^{\tau+s}\bigg\langle \theta\gamma(\varrho_{r}*\eta^{\theta}_{s}(x)) \int_{\mathbb{R}^n} \big\{f(y)r(\varrho_{r}*\eta^{\theta}_{s}(y))-f(x)r(\varrho_{r}*\eta^{\theta}_{s}(x))\big\}\varrho_{1/\theta}(x-y)dy \\
+& \qquad + F(\varrho_{F}*\eta^{\theta}_{s}(x)) f(x),\eta^{\theta}_{s}(dx)  \bigg\rangle ds \bigg|\Bigg].
+\end{aligned}
+\end{equation}
+In particular,
+\begin{multline}
+ \theta\gamma(\varrho_{r}*\eta^{\theta}_{s}(x))\int_{\mathbb{R}^n} \big\{f(y)r(\varrho_{r}*\eta^{\theta}_{s}(y))-f(x)r(\varrho_{r}*\eta^{\theta}_{s}(x))\big\}\varrho_{1/\theta}(x-y)dy \\
+ =  f(x)\theta\gamma(\varrho_{r}*\eta^{\theta}_{s}(x))\int_{\mathbb{R}^n} \big\{r(\varrho_{r}*\eta^{\theta}_{s}(y))-r(\varrho_{r}*\eta^{\theta}_{s}(x))\big\}\varrho_{1/\theta}(x-y)dy\\
+ + \theta\gamma(\varrho_{r}*\eta^{\theta}_{s}(x))\int_{\mathbb{R}^n} \big\{(f(y)-f(x))r(\varrho_{r}*\eta^{\theta}_{s}(y))\big\}\varrho_{1/\theta}(x-y)dy\\
+ \leq C_{\gamma,r}||f||_{\infty} + C_{\gamma}||\Delta f||_{\infty},
+\end{multline}
+since the first term is bounded above by $C_{\gamma,r}f(x)$ by Lemma \ref{lem: gamma - r radius comparison}
+and the second term by $C_{\gamma} \Delta f(x)$ as $r \leq 1$.
+
+Finally,  $F(\varrho_{F}*\eta^{\theta}_{s}(x)) f(x)$ is bounded above by $C_F||f||_{\infty}$, so 
+\begin{multline}
+\mathbb{E}\left[\left| \langle f, \eta^{\theta}_{\tau+s}\rangle - \langle f, \eta^{\theta}_{\tau}\rangle \right|\right] \\
+\leq (C_{\gamma,r}||f||_{\infty} + C_{\gamma,r}||\Delta f||_{\infty}+C_F||f||_{\infty}) \mathbb{E}\bigg\{\int_{\tau}^{\tau+s}\bigg\langle 1,\eta^{\theta}_{s}(dx)  \bigg\rangle  ds\bigg\} \\
+\leq (C_{\gamma,r}||f||_{\infty} + C_{\gamma,r}||\Delta f||_{\infty}+C_F||f||_{\infty}) \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle]e^{(C_{\gamma,r}+C_F)T}(e^s-1)\to 0
+\end{multline}
+as $s \to \infty$. 
+This gives us bound on the first moment.
+
+Similarly, the control on the second moment is given by Equation \eqref{eq: Control quadratic variation}.
+\begin{equation}
+    \label{eq: Controlling Quadratic Jumps}
+\begin{aligned}
+& \mathbb{E}\left[\big| [M^{\theta}_{\tau+s}(f)] - [M^{\theta}_{\tau}(f)] \big|\right]\\
+\leq &\frac{\theta}{N} \mathbb{E} \Bigg\{ \int_{\tau}^{\tau+s}\bigg|
+\langle \gamma\big(x,\varrho_{\gamma}*\eta^{\theta}_{s}(x)\big)
+\int f^2(y)r\big(y,\varrho_{r}*\eta^{\theta}_{s}(y)\big)q_\theta(x,dy) 
+,\eta^{\theta}_{s}(dx)\rangle\\
+& \qquad \qquad \qquad +\langle \mu\big(x,\eta^{\theta}_{s}\big)f^2(x) 
+,\eta^{\theta}_{s}(dx)\rangle \bigg|ds \Bigg\}\\
+\leq & \frac{2\theta}{N}\mathbb{E} \Bigg\{\int_{\tau}^{\tau+s} \left\langle \gamma(\varrho_{\gamma}*\eta^{\theta}_{s}(x))r(\varrho_{r}*\eta^{\theta}_{s}(x)), \eta^{\theta}_{s}(dx) \right\rangle ds\Bigg\} \\
+& + \frac{1}{N}\mathbb{E} \Bigg\{\int_{\tau}^{\tau+s} \left\langle \gamma (\varrho_{\gamma}*\eta^{\theta}_{s}(x))\theta\int_{\mathbb{R}^n}\left(r(\varrho_{r}*\eta^{\theta}_{s}(y))-r(\varrho_{r}*\eta^{\theta}_{s}(x))\right) q_\theta(x,dy), \eta^{\theta}_{s}(dx) \right\rangle ds\Bigg\}\\
+\leq & \frac{(2 \theta C_{\gamma,r}+C_{\gamma,r})\mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle]e^{(C_{\gamma,r}+C_F)T}(e^s-1)}{N} \to 0
+\end{aligned}
+\end{equation}
+as $s \to 0$.
 

### 2022-04-07 forwards-and-backwards.tex
Update on Overleaf.

@@
         =
-        r(x, \smooth{r} \eta^{\theta}(x))
-        \gamma(\smooth{\gamma} \eta^{\theta}(x))
+        r(x, \smooth{r} \eta(x))
+        \gamma(\smooth{\gamma} \eta(x))
         - \frac{1}{\theta}
-        F(x, \smooth{F} \eta^{\theta}(x)) .
+        F(x, \smooth{F} \eta(x)) .
     \end{align}
@@
 $$
-    \gamma(x, \smooth{\gamma} \eta^{\theta}(x))
-    \int r(x, \smooth{r} \eta^{\theta}(y)) q(x, dy) ,
+    \gamma(x, \smooth{\gamma} \eta(x))
+    \int r(x, \smooth{r} \eta(y)) q(x, dy) ,
 $$
@@
     \frac{
-        r(y, \smooth{r} \eta^{\theta}(y)) q_\theta(x, dy)
+        r(y, \smooth{r} \eta(y)) q_\theta(x, dy)
     }{
@@
         \int_0^t \big\langle
-            \gamma(x, \smooth{\gamma} \eta^{\theta}_{s}(x))
+            \gamma(x, \smooth{\gamma} \eta_{s}(x))
             \mathcal{B}\left(
-                f(\cdot) r(\cdot, \smooth{r} \eta^{\theta}_{s}(\cdot))
+                f(\cdot) r(\cdot, \smooth{r} \eta_{s}(\cdot))
             \right)(x)
@@
             f(x)
-            F(x, \smooth{F} \eta^{\theta}_{s}(x)),
-            \eta^{\theta}_{s}(dx)
+            F(x, \smooth{F} \eta_{s}(x)),
+            \eta_{s}(dx)
         \big\rangle ds,
@@
         \big\langle
-            \gamma\left( x, \smooth{\gamma} \eta^{\theta}_{s}(x) \right)
-            r\left(x, \smooth{r} \eta^{\theta}_{s}(x) \right)
+            \gamma\left( x, \smooth{\gamma} \eta_{s}(x) \right)
+            r\left(x, \smooth{r} \eta_{s}(x) \right)
             f^2(x),
-            \eta^{\theta}_{s} (dx)
+            \eta_{s} (dx)
         \big\rangle ds. 
@@
 We now write down the generator of
-the scaled population model with levels where 
-$\lambda$ is the scaling factor of the mass of an individual,
-$\theta(\lambda)$ is the scaling factor for time,
-and the level of an individual particle must be in $[0,\lambda]$.
-Recall that we only track the adult population; maturity, if achieved, is instantaneous.
-Furthermore, at rate $\theta\gamma(x, \eta)$,
-a parent gives birth to a single juvenile offspring.
+the population model with levels between $[0, \lambda]$.
 
@@
 uniformly distributed between $[0, \lambda]$.
-We write $(\xi^{\theta, \lambda}(t))_{t \geq 0}$
-for our population at the $\theta$-th stage of rescaling.
-To recover the scaling in \S\ref{sec: Model and main results},
+We write $(\xi(t))_{t \geq 0}$
+for our population.
+To ensure we have bounded intensity, 
 we scale the empirical distribution of particles with a factor of $1/\lambda$,
 so we write
-$$\eta^{\theta, \lambda}_t:=\frac{1}{\lambda}\xi^{\theta, \lambda}_t(dx \times [0,\lambda])=
+$$\eta_t:=\frac{1}{\lambda}\xi_t(\cdot \times [0,\lambda])=
 \frac{1}{\lambda}\sum\limits_{\substack{(X(t),U(t))\in \xi \\ U(t) < \lambda}} \delta_{X(t)}.$$
+
 From here onwards,
@@
 An individual in the spatial population $\eta$ living at spatial location $x$
-produces one adult offspring at rate $\theta\gamma^{\mathfrak{m}}_{\theta}(x, \eta)$, where
-$$\gamma^{\mathfrak{m}}_{\theta}(x,\eta)=\gamma(x,\eta) \int r (y, \eta)q_\theta(x,dy).$$
-
-The location of this offspring is given by
+produces one adult offspring at rate $\gamma^{\mathfrak{m}}(x, \eta)$, where
+$$\gamma^{\mathfrak{m}}(x,\eta)=\gamma(x,\eta) \int r (y, \eta)q(x,dy),$$
+where $q(x,dy)$ is the dispersion kernel.
+
+Recall that we only track the adult population; maturity, if achieved, is instantaneous.
+The location of this adult offspring is given by
 the distribution 
-\[ q^{\mathfrak{m}}_\theta(x,\eta,dy) = \frac{r(y,\eta) q_{\theta}(x,dy)}{\int_{\mathbb{R}^d} r(y,\eta) q_{\theta}(x,dy)}. \]
+\[ q^{\mathfrak{m}}(x,\eta,dy) = \frac{r(y,\eta) q(x,dy)}{\int_{\mathbb{R}^d} r(y,\eta) q(x,dy)}. \]
 
 In the lookdown version of our model,
-the individual $(x,u)\in \xi^{\theta, \lambda}$
+the individual $(x,u)\in \xi$
 gives birth to an offspring at rate 
-$2(\lambda-u)\lambda^{-1}\theta \gamma^{\mathfrak{m}}_{\theta}(x, \eta)$. 
+$2(\lambda-u)\lambda^{-1} \gamma^{\mathfrak{m}}(x, \eta)$. 
 (Averaging over the distribution of the
 level $u$,
-we recover $\theta \gamma^{\mathfrak{m}}_{\theta}(x, \eta)$.)
+we recover $\gamma^{\mathfrak{m}}(x, \eta)$.)
 
@@
 evolves according to the differential equation
-$$\dot{v}= \theta \gamma^{\mathfrak{m}}_{\theta}(x, \eta) 
+$$\dot{v}=  \gamma^{\mathfrak{m}}(x, \eta) 
 \left\{\lambda^{-1}(\lambda -v)^{2}
@@
 moves upwards at an additional rate
-$\theta \mu(x,\eta)$
+$ \mu(x,\eta)$
 (on reaching level $\lambda$
@@
 evolves according to
-$$\dot{u}= \theta \gamma^{\mathfrak{m}}_{\theta}(x, \eta) 
+$$\dot{u}= \gamma^{\mathfrak{m}}(x, \eta) 
 \left\{\lambda^{-1}(\lambda -u)^{2}
--(\lambda -u)\right\}+\theta \mu(x,\eta)u.$$
+-(\lambda -u)\right\}+\mu(x,\eta)u.$$
 We shall write 
-$$b_{\theta, \lambda}(x,\eta):=\theta\big\{\gamma^{\mathfrak{m}}_{\theta}(x,\eta)
--\mu(x,\eta)\big\}.$$
+$$b(x,\eta):= \big\{\gamma^{\mathfrak{m}}(x,\eta)
+-\mu(x,\eta)\big\}$$
+to be the local branching rate.
 Note that this quantity captures
@@
 \begin{align}
-\dot{u}&=\lambda \theta \gamma^{\mathfrak{m}}_{\theta}(x,\eta) 
+\dot{u}&=\lambda  \gamma^{\mathfrak{m}}(x,\eta) 
 \left\{\left(1-\frac{u}{\lambda}\right)^{2}
--1 +2\frac{u}{\lambda}\right\} -b_{\theta, \lambda}(x,\eta)u \nonumber \\
-&=\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\eta) u^2 -b_{\theta, \lambda}(x,\eta)u. \label{differential equation for level}
+-1 +2\frac{u}{\lambda}\right\} -b(x,\eta)u \nonumber \\
+&=\lambda^{-1}  \gamma^{\mathfrak{m}}(x,\eta) u^2 -b(x,\eta)u. \label{differential equation for level}
 \end{align}
 In this setting, the generator of our model
-acting on the test functions $f(\eta)=\prod_{(x,u) \in \eta}g(x,u)$
+acting on the test functions $f(\xi)=\prod_{(x,u) \in \xi}g(x,u)$
 satisfies
@@
 \begin{eqnarray}\label{Generator of prelimit simplest model}
-&&A_{\theta, \lambda}f(\eta ) \nonumber \\
-&&\quad =f(\eta )\,\sum_{(x,u)\in\eta}\,2\lambda^{-1}\theta \gamma^{\mathfrak{m}}_{\theta}(x, \eta)
+&&Af(\xi ) \nonumber \\
+&&\quad =f(\xi )\,\sum_{(x,u)\in\xi}\,2\lambda^{-1} \gamma^{\mathfrak{m}}(x, \eta)
 \int_u^{
-\lambda}\Bigg(\frac 12\frac {\int_{\mathbb{R}^d}g(y,u)q^{\mathfrak{m}}_\theta(x,\eta,d
+\lambda}\Bigg(\frac 12\frac {\int_{\mathbb{R}^d}g(y,u)q^{\mathfrak{m}}(x,\eta,d
 y)g(x,v_1)}{g(x,u)} \label{multgen3}\\
 &&\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad
-+\frac 12\int_{\mathbb{R}^d}g(y,v_1)q^{\mathfrak{m}}_\theta(x,\eta ,dy)-
++\frac 12\int_{\mathbb{R}^d}g(y,v_1)q^{\mathfrak{m}}(x,\eta ,dy)-
 1\Bigg)dv_1\nonumber\\
-&&\quad \quad +f(\eta )\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\eta) u^2 -b_{\theta, \lambda}(x,\eta)u\right)\frac {\partial_u g(x,u)}{g(x,u)}\nonumber\\
-&&\quad =f(\eta )\,\sum_{(x,u)\in\eta}\,2 \gamma^{\mathfrak{m}}_{\theta}(x, \eta)\lambda^{-1}\int_u^{
-\lambda}\Bigg(\frac 12\frac {\theta\int_{\mathbb{R}^d}(g(y,u)-g(x,u))q^{\mathfrak{m}}_\theta(x,\eta,dy)g(x,v_1)}{g(x,u)}\non\\
-&&\qquad\qquad\qquad\qquad\qquad\qquad\qquad +\theta\int_{\mathbb{R}^d}\left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_\theta(x,\eta,dy)\Bigg)dv_1\nonumber\\
+&&\quad \quad +f(\eta )\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}(x,\eta) u^2 -b(x,\eta)u\right)\frac {\partial_u g(x,u)}{g(x,u)}\nonumber\\
+&&\quad =f(\eta )\,\sum_{(x,u)\in\eta}\,2 \gamma^{\mathfrak{m}}(x, \eta)\lambda^{-1}\int_u^{
+\lambda}\Bigg(\frac 12\frac {\theta\int_{\mathbb{R}^d}(g(y,u)-g(x,u))q^{\mathfrak{m}}(x,\eta,dy)g(x,v_1)}{g(x,u)}\non\\
+&&\qquad\qquad\qquad\qquad\qquad\qquad\qquad +\theta\int_{\mathbb{R}^d}\left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}(x,\eta,dy)\Bigg)dv_1\nonumber\\
 &&\qquad\qquad
-+f(\eta )\sum_{(x,u)\in\eta}\,\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\eta) u^2 -b_{\theta, \lambda}(x,\eta)u\right)\frac {\partial_u g(x,u)}{g(x,u)}.\nonumber
++f(\eta )\sum_{(x,u)\in\eta}\,\left(\lambda^{-1} \gamma^{\mathfrak{m}}(x,\eta) u^2 -b(x,\eta)u\right)\frac {\partial_u g(x,u)}{g(x,u)}.\nonumber
 \end{eqnarray}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection*{Scaling of the Pre-limit}
-
-We also let $\lambda$ takes on the role of $N$
+\subsubsection*{Scaling of the Pre-limit Lookdown Model}
+
+To scale our lookdown model to be consistent with
+the spatial model described in \S \ref{sec: Model and main results},
+we will let $\lambda$ takes on the role of $N$
 in \S \ref{sec: Model and main results},
@@
 in the scaling limit.
-Time is once again scaled by $\theta$
-and local interaction radius by $\varepsilon_{\gamma}$ and $\varepsilon_{r}$.
-
-As in Definition \ref{Def: Rescaled Models},
-the rates $\gamma,r, \mu_{\theta}$
-in our re-scaled lookdown models 
-depend on the local density of $\eta$
-through mollifications with 
-$\varrho_{\gamma}, \varrho_{r}$ and $\varrho_{F}$.
-We will now make our re-scaled lookdown model explicit.
-
+Time is once again scaled by $\theta$,
+and the birth, death and establishment rates 
+depend on local densities given by
+mollification over Gaussian kernels with radius
+$\varepsilon_{\gamma}$, $\varepsilon_{F}$ and $\varepsilon_{r}$.
+
+Explicitly, in the $\theta$-th stage of re-scaling,
+an individual has mass $\frac{1}{\lambda} := \frac{1}{N}$
+and a level between $[0,N]$;
+the established birth rate $\gamma(x,\eta)$ is
+$$\theta\gamma^{\mathfrak{m}}_{\theta}(x, \eta):=~\theta\gamma(x, \varrho_{\gamma}*\eta(x)) \int r(y, \varrho_{r}*\eta(y))q_{\theta}(x,dy);$$
+the local branching mechanism $b(x,\eta)$ is 
+$$b_{\theta}(x, \eta):=~ \theta \bigg\{ \gamma(x, \varrho_{\gamma}*\eta(x)) \int r(y, \varrho_{r}*\eta(y))q_{\theta}(x,dy)-\mu(x, \eta)\bigg\};$$
+and the dispersal kernel $q^{\mathfrak{m}}(x,dy)$ is 
+$$q^{\mathfrak{m}}_{\theta}(x,\eta,dy) :=~ \frac{r(y,\varrho_{r}*\eta(y)) q_{\theta}(x,dy)}{\int_{\mathbb{R}^d} r(y,\varrho_{r}*\eta(y)) q_{\theta}(x,dy)}.$$
+
+We can now define our pre-limit explicitly as a solution to a Martingale Problem.
 \begin{definition}[Martingale Problem Characterisation]
 \label{Def: Rescaled Lookdown Models}
-Let the coefficients $\gamma, \mu, r$ satisfy the conditions highlighted in Definition \ref{Def: Rescaled Models} and let $\varrho_{\varepsilon}$ be the kernel defined in Definition \ref{Defn: Kernel and Convolution}.
-We define the following terms:
-\begin{align*}
-\gamma^{\mathfrak{m}}_{\varepsilon,\theta}(x, \eta):=&~\gamma(x, \varrho_{\varepsilon}*\eta^{\theta}(x)) \int r(y, \varrho_{\varepsilon}*\eta^{\theta}(y))q_{\theta}(x,dy),\\
- q^{\mathfrak{m}}_{\varepsilon, \theta}(x,\eta,dy) :=&~ \frac{r(y,\varrho_{\epsilon}*\eta^{\theta}(y)) q_{\theta}(x,dy)}{\int_{\mathbb{R}^d} r(y,\varrho_{\epsilon}*\eta^{\theta}(y)) q_{\theta}(x,dy)},\\
-b_{\varepsilon, \theta, \lambda}(x, \eta):=&~ \theta \bigg\{ \gamma(x, \varrho_{\varepsilon}*\eta^{\theta}(x)) \int r(y, \varrho_{\varepsilon}*\eta^{\theta}(y))q_{\theta}(x,dy)-\mu_{\theta}(x, \varrho_{\varepsilon}*\eta^{\theta}(x)) \bigg\}
-\end{align*}
-At the $\lambda$-stage of re-scaling, our test measures $\eta$ takes value in $\mathcal{M}_F(\mathbb{R}^d \times [0,\lambda])$, the set of finite measures on $\mathbb{R}^d \times [0,\lambda]$, and we define $$\eta= \frac{1}{\lambda}\sum_{(x,u) \in \eta}\delta_x.$$
-We define $(\eta^{\varepsilon, \theta, \lambda}_t)_{t \geq 0}$ to be the (unique?) solution to the Martingale Problem with initial condition $\eta_0$ and generator $A_{\varepsilon, \theta, \lambda}$ that satisfies
+
+For test measures $\xi$ taking value in $\mathcal{M}_F(\mathbb{R}^d \times [0,N])$,
+the set of finite measures on $\mathbb{R}^d \times [0,N]$,
+we define
+$$\eta:= \frac{1}{N}\xi(\cdot  \times [0, N])=
+\frac{1}{N}\sum_{(x,u) \in \xi}\delta_x$$
+to be its re-scaled spatial projection.
+
+We define $(\xi^{\theta}_t)_{t \geq 0}$
+to be the (unique) solution
+to the Martingale Problem
+with initial condition $\xi_0$
+and generator $A^{\theta}$ that satisfies
+
 \begin{eqnarray}\label{Eq: Prelimit Lookdown Generator}
-&&A_{\epsilon, \theta, \lambda}f(\eta ) \\
-&&\quad =f(\eta )\,\sum_{(x,u)\in\eta}\,2 \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(x, \eta)\Bigg\{ \frac 12 \lambda^{-1}\int_u^{
-\lambda}g(x,v_1)dv_1\times \frac { \theta\int_{\mathbb{R}^d}(g(y,u)-g(x,u))q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\bar{
-\eta },dy)}{g(x,u)}\non\\
+&&A^{\theta}f(\xi ) \\
+&&\quad =f(\xi )\,\sum_{(x,u)\in\eta}\,2 \gamma^{\mathfrak{m}}_{\theta}(x, \eta)\Bigg\{ \frac 12 \lambda^{-1}\int_u^{
+\lambda}g(x,v_1)dv_1\times \frac { \theta\int_{\mathbb{R}^d}(g(y,u)-g(x,u))q^{\mathfrak{m}}_{\theta}(x,\eta,dy) }{g(x,u)}\non\\
 &&\qquad\qquad\qquad\qquad\qquad\qquad\qquad +\lambda^{-1}\theta\int_u^{
-\lambda}\int_{\mathbb{R}^d}\left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\eta,dy)dv_1\nonumber\Bigg\}\\
+\lambda}\int_{\mathbb{R}^d}\left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\theta}(x,\eta,dy)dv_1\nonumber\Bigg\}\\
 &&\qquad\qquad
-+f(\eta )\sum_{(x,u)\in\eta}\,\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(x,\eta) u^2 -b_{\varepsilon,\theta, \lambda}(x,\eta)u\right)\frac {\partial_u g(x,u)}{g(x,u)}.\nonumber
++f(\eta )\sum_{(x,u)\in\xi}\,\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\eta) u^2 -b_{\theta}(x,\eta)u\right)\frac {\partial_u g(x,u)}{g(x,u)}.\nonumber
 \end{eqnarray}
-for all smooth functions $f \in C(\mathbb{R}^d)$. 
+for all smooth functions $f \in C^{2}_{0}(\mathbb{R}^d)$. 
 \end{definition}
-In \S \ref{sec: Markov Mapping Theorem application}, through an application of the Markov Mapping Theorem, we will show that the spatial projection of $(\eta^{\varepsilon, \theta, \lambda}_t)_{t \geq 0}$ has the same distribution as $(\eta^{\varepsilon, \theta, N}_t)_{t \geq 0}$ if we take $\lambda = N$.
+
+In \S \ref{sec: Markov Mapping Theorem Application},
+applying Markov Mapping Theorem,
+we will show that the spatial projection of $(\eta^{\theta}_t)_{t \geq 0}$ has the same distribution as $(\eta^{\varepsilon, \theta, N}_t)_{t \geq 0}$ if we take $\lambda = N$.
 Specifically, we mean that when $\lambda=N$,
-$$(\eta^{\varepsilon,\theta, \lambda}(t))_{t \geq 0}:=\left(\frac{1}{\lambda}\sum\limits_{\substack{(X(t),U(t))\in \eta^{\varepsilon,\theta, \lambda}(t) \\ U(t) < \lambda}} \delta_{X(t)}\right)_{t \geq 0}$$
+$$(\eta^{\theta}(t))_{t \geq 0}:=\left(\frac{1}{\lambda}\sum\limits_{\substack{(X(t),U(t))\in \eta^{\theta}(t) \\ U(t) < \lambda}} \delta_{X(t)}\right)_{t \geq 0}$$
 has the same distribution (as stochastic processes) as $(\eta^{\theta}_t)_{t \geq 0}$ in Definition \ref{Def: Rescaled Models}.
@@
 On the other hand, we reserve the notation $\eta$ strictly for the spatial-level process.\\~\\ Furthermore, the application of Markov Mapping Theorem implies that particle levels are, conditional on $\eta$, i.i.d and uniformly distributed between $[0, \lambda]$.
-Theorem A.10 in \cite{kurtz/rodrigues:2011} states that convergence of $(\eta^{\varepsilon, \theta, \lambda}_t)_{t \geq 0}$ to a conditionally Poisson system $(\xi_t)_{t \geq 0}$ with Cox measure $\Xi_t \times \Lambda$ is equivalent to convergence of $(\eta^{\varepsilon, \theta, N}_t)_{t \geq 0}$ to $(\Xi_t)_{t \geq 0}$.
-As a result, it suffices for us to focus on tightness of $(\eta^{\varepsilon, \theta, \lambda}_t)_{t \geq 0}$ and spatial convergence of $(\eta^{\varepsilon, \theta, N}_t)_{t \geq 0}$ as $\theta \to \infty$.
+Theorem A.10 in \cite{kurtz/rodrigues:2011} states that convergence of $(\eta^{\theta}_t)_{t \geq 0}$ to a conditionally Poisson system $(\xi_t)_{t \geq 0}$ with Cox measure $\Xi_t \times \Lambda$ is equivalent to convergence of $(\eta^{\varepsilon, \theta, N}_t)_{t \geq 0}$ to $(\Xi_t)_{t \geq 0}$.
+As a result, it suffices for us to focus on tightness of $(\eta^{\theta}_t)_{t \geq 0}$ and spatial convergence of $(\eta^{\varepsilon, \theta, N}_t)_{t \geq 0}$ as $\theta \to \infty$.
 
@@
 \begin{equation}
-U_{\tau}(t)=U_{\tau}(\tau)+\int_{\tau}^{t}(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(s),\eta(s))U^2_{\tau}(s)-b_{\varepsilon,\theta,\lambda}(X_{\tau}(s),\eta(s))U_{\tau}(s))ds, ~~~ t \geq \tau.
+U_{\tau}(t)=U_{\tau}(\tau)+\int_{\tau}^{t}(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(s),\eta(s))U^2_{\tau}(s)-b_{\theta}(X_{\tau}(s),\eta(s))U_{\tau}(s))ds, ~~~ t \geq \tau.    
 \end{equation}
@@
 \begin{equation}\label{New birth potential level}
-    U_{\tau+s}(\tau+s)=U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))}.
+    U_{\tau+s}(\tau+s)=U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))}.
 \end{equation}
@@
 X_{\tau}(\tau+t)=&X_{\tau}(t)\\
-&+\int_{(0,t]\times[0,\infty]\times[0,1]\times\{0,1\}}\mathbbm{1}_{U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))}<\lambda\}}\kappa    H(X_{\tau}(\tau+s-), \eta(\tau+s),\omega) \\
+&+\int_{(0,t]\times[0,\infty]\times[0,1]\times\{0,1\}}\mathbbm{1}_{U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))}<\lambda\}}\kappa    H(X_{\tau}(\tau+s-), \eta(\tau+s),\omega) \\
 &\qquad \times \xi_{\tau}(ds,dv,dw,d\kappa).
@@
 \begin{align*}
-U_{\tau}(t)=&U_{\tau}(0)+\int_{0}^{t}\frac{1}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(s-), \eta(s-))}dV_{\tau}(s)\\
-&+\int_{0}^{t}\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(s-), \eta(s-))U^2_{\tau}(s)-b_{\varepsilon,\theta, \lambda}(X_{\tau}(s),\eta(s))U_{\tau}(s))ds,\\  
-X_{\tau}(t)=&X_{\tau}(0)+\int_{(0,t]\times[0,\infty]\times[0,1]\times\{0,1\}}\mathbbm{1}_{U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))}<\lambda\}}\\
+U_{\tau}(t)=&U_{\tau}(0)+\int_{0}^{t}\frac{1}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(s-), \eta(s-))}dV_{\tau}(s)\\
+&+\int_{0}^{t}\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(s-), \eta(s-))U^2_{\tau}(s)-b_{\theta}(X_{\tau}(s),\eta(s))U_{\tau}(s))ds,\\  
+X_{\tau}(t)=&X_{\tau}(0)+\int_{(0,t]\times[0,\infty]\times[0,1]\times\{0,1\}}\mathbbm{1}_{U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))}<\lambda\}}\\
 &\qquad \times \kappa   H(X_{\tau}(s-), \eta(s-),\omega)\zeta_{\tau}(ds,dv,dw,d\kappa)
@@
 \begin{remark}
-The factor $\frac{1}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(x, \eta)}$ that scales the jump in levels give an average birth rate of $\theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(s-), \eta(s-))$.
-This is because for the potential birth to be a true birth, we impose that $$U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))}< \lambda,$$ where $U_{\tau}(\tau+s)$ is uniformly distributed between $[0, \lambda]$.
-As a result, a true birth occurs between $[0,\delta t]$ if there exists $(s,v) \in [0,\delta t]\times [0, 2 (\lambda-U_{\tau}(\tau+s)) \lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))]$.
-Averaging this over levels give a Poisson process with rate $ \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))$.
+The factor $\frac{1}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x, \eta)}$ that scales the jump in levels give an average birth rate of $\theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(s-), \eta(s-))$.
+This is because for the potential birth to be a true birth, we impose that $$U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))}< \lambda,$$ where $U_{\tau}(\tau+s)$ is uniformly distributed between $[0, \lambda]$.
+As a result, a true birth occurs between $[0,\delta t]$ if there exists $(s,v) \in [0,\delta t]\times [0, 2 (\lambda-U_{\tau}(\tau+s)) \lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))]$.
+Averaging this over levels give a Poisson process with rate $ \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))$.
 \end{remark}
@@
 \begin{aligned}
-\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon,\theta}(X_{\tau}(s), \eta(s)) &\to \ell \gamma(X_{\tau}(s),\varrho_\varepsilon*\Xi(X_{\tau}(s)),\\
-b_{\varepsilon,\theta, \lambda}(X_{\tau}(s),\eta(s)) &\to  F(X_{\tau}(s), (\varrho_{\varepsilon}*\eta)(X_{\tau}(s)))\\
+\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(s), \eta(s)) &\to \ell \gamma(X_{\tau}(s),\varrho_\varepsilon*\Xi(X_{\tau}(s)),\\
+b_{\theta}(X_{\tau}(s),\eta(s)) &\to  F(X_{\tau}(s), (\varrho_{\varepsilon}*\eta)(X_{\tau}(s)))\\
 &+\gamma(X_{\tau}(s), (\varrho_{\varepsilon}*\Xi)(X_{\tau}(s)))\mathcal{B}r(\cdot,(\varrho_{\varepsilon}*\eta)(\cdot))(X_{\tau}(s)).
@@
 \end{proof}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\appendix
+\section{Markov Mapping Theorem Applications}
+    \label{sec: Markov Mapping Theorem Application}
+\subsection{Markov Mapping Theorem Application on Generator $A_{\theta}$}\label{sec: Markov Mapping Theorem Application - Prelimit}
+
+We now introduce some notations to simply our calculations.
+For $\xi=\sum \delta_{(x_i,u_i)}$, we write $\textbf{x}=(x_1,x_2,...), \textbf{u}=(u_1,u_2,...)$ to be the collections of particles locations and levels respectively.
+With this notation we will write $f(\xi), f(\textbf{x},\textbf{u})$ interchangeably.
+We write $\Gamma (d\textbf{u})$ as the probability kernel that corresponds to assigning each particle an i.i.d.
+uniform $[0,\lambda]$-level, i.e.
+$$\int f(\textbf{x},\textbf{u})\Gamma (d\textbf{u})=\frac{1}{\lambda^{|\xi|}}\int_{[0,\lambda]^{|\xi|}}f(\textbf{x},\textbf{u})d\textbf{u},$$
+and we denote
+$$\hat{g}(x):=\frac{1}{\lambda}\int_{0}^{\lambda}g(x,u)du, ~~\hat{f}(\xi)=\int f(\xi) \Gamma (d\textbf{u})$$ 
+to be the spatial test functions with averaged level. By independence of the levels of the particles we have that
+$$\hat{f}(\xi)=\int \prod_{(x,u) \in \xi}g(x,u) \Gamma(d\textbf{u})=\prod_{(x,u)\in \xi}\frac{1}{\lambda}\int_{0}^{\lambda} g(x,u) du=\prod_{x_i \in \Xi}\hat{g}(x_i).$$ 
+We will now apply Markov Mapping Theorem while keeping notations consistent to that introduced in Section A.5 in \cite{kurtz/rodrigues:2011} with the aid of Table \ref{Markov Mapping Theorem Notation Table}.
+\begin{table}[h]
+    \centering
+    \begin{tabular}{c|c}
+    Notation in \cite{kurtz/rodrigues:2011} & Notation in this paper \\
+    \hline\\
+      $S$   &  $\mathcal{M}(\mathbb{R}^d \times [0, \lambda))$\\\\
+       $S_0$  &  $\mathcal{M}(\mathbb{R}^d)$\\\\
+       $A$ & $A^{\theta}$\\\\
+       $(X_t)_{t \geq 0}$ & $(\xi^{\theta}_t)_{t \geq 0}$\\\\
+       $\mu_0$ & $\Xi^{\theta}_0 \in \mathcal{M}(\mathbb{R}^d)$\\\\
+       $\nu_0$ & $\xi^{\theta}_0 \in \mathcal{M}(\mathbb{R}^d \times [0,\lambda])$\\\\
+       $f(\xi)$ & $\prod_{(x,u) \in \xi} g(x,u)$\\\\
+        $\gamma_M$ & $ \mathcal{M}(\mathbb{R}^d \times [0, \lambda)) \ni \xi \to \frac{1}{\lambda}\sum_{(x,u) \in \xi, u < \lambda} \delta_{x} \in \mathcal{M}(\mathbb{R}^d)$\\\\
+       $\alpha_M$ & $ \alpha_M(\Xi,d \nu) =     \begin{cases}
+      0 & \text{if } \sum_{(x,u) \in \nu, u < \lambda} \delta_x \neq \Xi\\
+       \prod_{(u_i,x_i) \in \nu} \frac{1}{\lambda} \mathbbm{1}_{[0,\lambda]}du_i & \text{if } \sum_{(x,u) \in \nu, u < \lambda} \delta_x = \Xi,\\
+    \end{cases} $\\
+&      where $du_i$ is the standard Lebesgue measure.
+    \end{tabular}
+    \caption{Markov Mapping Theorem Correspondence}
+    \label{Markov Mapping Theorem Notation Table}
+\end{table}
+\begin{remark}
+Note that $\gamma,\alpha$ in \cite{kurtz/rodrigues:2011} is replaced with $\gamma_M,\alpha_M$ to avoid confusion with the $\gamma, \alpha$ used in previous sections.
+\end{remark}
+First of all, note that $\gamma_M$ is Borel-measurable and $\alpha_M$ is a transition function from $\mathcal{M}(\mathbb{R}^d \times [0, \lambda))$ to $\mathcal{M}(\mathbb{R}^d)$.
+More importantly, we have the following simplified expression for an integral against $\alpha_M$:
+\begin{equation}
+\int_{\mathcal{M}(\mathbb{R}^d\times [0,\lambda])}A^{\theta}f(\nu)\alpha_M(\Xi,d\nu)= \int   A^{\theta}f(\textbf{x},\textbf{u})\Gamma(d\textbf{u}). 
+\end{equation}
+As a result, we can establish that
+\begin{equation}
+\begin{aligned}
+\alpha_M(\Xi,\gamma^{-1}(\Xi)) &= \int_{\nu \in \gamma^{-1}(y)}\alpha_M (\Xi,d\nu) \\
+&= \int_{\nu \in \prod_{x_i \in \Xi} \{x_i\}\times [0,\lambda]}\alpha_M (\Xi,d\nu)\\
+&= \prod_{x_i \in \Xi}\frac{1}{\lambda}\int_{0}^{\lambda} du_i =1
+\end{aligned}
+\end{equation}
+With the simplified integral, it now suffices to show that the Martingale Problem 
+\begin{equation}\label{Markov Mapping Theorem Martingale Condition Simplified}
+C = \left\{\left(\int   f(\textbf{x},\textbf{u})\Gamma(d\textbf{u}),\int   A^{\theta}f(\textbf{x},\textbf{u})\Gamma(d\textbf{u})\right)\right\}    
+\end{equation}
+has a solution, i.e. the process
+\begin{equation}
+\begin{aligned}
+M_t:=& \int   f(\textbf{x}_t,\textbf{u}_t)\Gamma(d\textbf{u})-\int   f(\textbf{x}_0,\textbf{u}_0)\Gamma(d\textbf{u})-\int_{0}^{t}\int   A^{\theta}f(\textbf{x}_s,\textbf{u}_s)\Gamma(d\textbf{u})ds\\
+=&\hat{f}(\xi_t)-\hat{f}(\xi_0)-\int_{0}^{t}\int   A^{\theta}f(\xi_s)\Gamma(d\textbf{u})ds
+\end{aligned}    
+\end{equation}
+is a martingale.\\
+Once we manage to solve the Martingale Problem \eqref{Markov Mapping Theorem Martingale Condition Simplified}, the Markov Mapping Theorem guarantees the following fact:
+\begin{enumerate}
+    \item $N_t:=    f(\xi_t)-   f(\xi_0)-\int_{0}^{t}  A^{\theta}f(\xi_s)ds$ is a martingale for all $f\in D(A^{\theta})$,
+    \item The process $(\gamma_M \circ \xi^{\theta}_t)_{t \geq 0}:= \left(\frac{1}{\lambda}\sum_{(x,u)\in \xi^{\theta}_t, u < \lambda} \delta_x\right)_{t \geq 0}=(\Xi^{\theta}_t)_{t \geq 0}$ solves the Martingale Problem \eqref{Markov Mapping Theorem Martingale Condition Simplified}.
+    \item $\mathbb{P}\{\xi^{\theta}_t \in B | \mathcal{F}^{\Xi^{\theta}}_t\}=\alpha_M(\Xi^{\theta}(t),B), ~~~B \in \mathcal{B}(\mathcal{M}(\mathbb{R}^d \times [0,\lambda])).$
+\end{enumerate}
+Note that in particular, the third statement is equivalent to the fact that conditioned on the spatial configuration $\Xi^{\theta}_t$, the levels of the particles must be i.i.d uniformly between $[0,\lambda]$.
+We may also express this condition through the following equation:
+\begin{equation}\label{Markov Mapping Theorem Cox Condition}
+\mathbb{E}\left[e^{-\int_{S \times [0,\lambda]} f(x,u) \xi^{\varepsilon,\theta,\lambda}(dx \times du)}\bigg| \mathcal{F}^{\Xi^{\varepsilon,\theta, \lambda}}_t\right]=e^{-\int F^{\varepsilon,\theta,\lambda}_f(x) \Xi^{\varepsilon,\theta,\lambda}_t(dx)},
+\end{equation}
+where 
+$$F^{\varepsilon,\theta,\lambda}_f(x):=-\lambda\log \left(\frac{1}{\lambda}\int_{0}^{\lambda}e^{-f(x,u)}du\right)=-\lambda\log \left(1-\frac{1}{\lambda}\int_{0}^{\lambda}(1-e^{-f(x,u)})du\right).$$
+
+Therefore we only need to solve Martingale Problem \eqref{Markov Mapping Theorem Martingale Condition Simplified}.\\
+
+The procedure to solve the Martingale Problem \eqref{Markov Mapping Theorem Martingale Condition Simplified} is rather standard and set out in \cite{kurtz/rodrigues:2011}, albeit we will face more technicalities for this setting.
+Recall that the lookdown generator of our spatial-level process satisfies
+\begin{align}\label{Lookdown generator N lambda theta prelimit}
+A^{\theta}f(\xi)=&f(\xi)\sum_{(x,u)\in\xi}2\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi)\times
+\int_u^{
+\lambda}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\mathbb{R}^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\bar{
+\xi },dy) \nonumber \\
+& \qquad \qquad \qquad \qquad +\int_{\mathbb{R}^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\Xi,dy)\Bigg)dv_1 \nonumber\\
+&+f(\xi )\sum_{(x,u)\in\xi}\,\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)},
+\end{align}
+where $f(\xi) =\prod_{(x,u) \in \xi}g(x,u)$. 
+For easier computation we break the generator into three parts, 
+\begin{equation}
+\begin{aligned}
+A^{\varepsilon, \theta, \lambda,1}f(\xi)=&f(\xi)\sum_{(x,u)\in\xi}2\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi)\times
+\int_u^{
+\lambda}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\mathbb{R}^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\bar{
+\xi },dy)\Bigg)dv_1,\\
+A^{\varepsilon, \theta, \lambda,2}f(\xi)=&f(\xi)\sum_{(x,u)\in\xi}2\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi)\times
+\int_u^{
+\lambda}\Bigg(\frac{1}{2}\int_{\mathbb{R}^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\Xi,dy)\Bigg)dv_1,\\
+A^{\varepsilon, \theta, \lambda,3}f(\xi)=&f(\xi )\sum_{(x,u)\in\xi}\,\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)},
+\end{aligned}
+\end{equation}
+such that 
+$$A^{\theta}f(\xi)=A^{\varepsilon, \theta, \lambda,1}f(\xi)+A^{\varepsilon, \theta, \lambda,2}f(\xi)+A^{\varepsilon, \theta, \lambda,3}f(\xi).$$
+We now calculate each generator evaluated under our probability kernel $\Gamma$.
+\footnotesize 
+\begin{align*}
+&\int A^{\varepsilon, \theta, \lambda,1}f(\xi) \Gamma(d\mathbf{u})\\ &=\int \Bigg\{f(\xi)\sum_{(x,u)\in\xi}2\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi)
+\int_u^{
+\lambda}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\mathbb{R}^d}(g(y,u)-g(x,u))q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\bar{
+\xi },dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
+&=\sum_{(x,u)\in\xi} \int \Bigg\{\frac{f(\xi)}{g(x,u)}2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi)
+\int_u^{
+\lambda}\Bigg(\frac 12 g(x,v_1)\int_{\mathbb{R}^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\bar{
+\xi },dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
+&=\sum_{(x,u)\in\xi}\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\int_{0}^{\lambda}\left\{
+\int_u^{
+\lambda} g(x,v_1)dv_1\times \int_{\mathbb{R}^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\bar{
+\xi },dy)\right\}du\\
+&=\sum_{(x,u)\in\xi}\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\int_{\mathbb{R}^d} \left\{\int_{0}^{\lambda}
+\int_u^{
+\lambda} g(x,v_1) (g(y,u)-g(x,u))dv_1du\right\}q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\bar{
+\xi },dy)
+\end{align*}
+\normalsize
+For the second generator, we have
+\footnotesize
+\begin{align*}
+&\int A^{\varepsilon, \theta, \lambda,2}f(\xi) \Gamma(d\mathbf{u})\\&=\int \Bigg\{f(\xi)\sum_{(x,u)\in\xi}2\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi)\times
+\int_u^{
+\lambda}\Bigg(\int_{\mathbb{R}^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\Xi,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
+&=\sum_{(x,u)\in\xi}\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi)\int \Bigg\{f(\xi)\times
+\int_u^{
+\lambda}\Bigg(\int_{\mathbb{R}^d}\left(g(y,v_1)+g(x,v_1)-2\right)q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\Xi,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
+&=\sum_{(x,u)\in\xi}\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i) \frac{1}{\lambda}\int_{\mathbb{R}^d}\Bigg\{\int_{0}^{\lambda}
+\int_u^{
+\lambda}g(x,u) \left(g(y,v_1)+g(x,v_1)-2\right)dv_1 du\Bigg\} q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\Xi,dy).
+\end{align*}  
+\normalsize
+For the third generator we have that 
+\begin{align*}
+ &\int A^{\varepsilon, \theta, \lambda,3}f(\xi)\Gamma(d\mathbf{u})\\&=\int f(\xi )\,\left(\lambda^{-1} \sum_{(x,u)\in\xi}\theta \gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)}\Gamma(d\mathbf{u}) \\
+ &=\sum_{(x,u)\in\xi}\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\int_{0}^{\lambda}  \left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\partial_u g(x,u)du \\
+ &=-\sum_{(x,u)\in\xi}\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\int_{0}^{\lambda}  \left(2u\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi) -b_{\theta}(x,\Xi)\right)\left(g(x,u)-1\right)du \\
+ &=-\sum_{(x,u)\in\xi}\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\int_{0}^{\lambda}   2ug(x,u)du \\
+ &+\sum_{(x,u)\in\xi}\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\times \lambda^2+\sum_{(x,u)\in\xi}\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)b_{\theta}(x,\Xi)(\hat{g}(x)-1) \\
+\end{align*}
+Using the symmetry we have
+\begin{align*}
+&\int_{0}^{\lambda}
+\int_u^{
+\lambda} g(x,v_1) (g(y,u)-g(x,u))dv_1du+\int_{0}^{\lambda}
+\int_u^{
+\lambda}g(x,u) \left(g(y,v_1)+g(x,v_1)-2\right)dv_1 du
+\\&= \int_{0}^{\lambda}
+\int_u^{
+\lambda}g(x,u)g(y,v_1)+g(y,u)g(x,v_1)-2g(x,u) dv_1 du\\
+&=\frac{1}{2}\int_{0}^{\lambda}\int_{0}^{\lambda}g(x,u)g(y,v_1)+g(y,u)g(x,v_1)dv_1 du - 2 \int_{0}^{\lambda}(\lambda-u)g(x,u)du\\
+&=\lambda^2 \hat{g}(x)\hat{g}(y) -2\lambda^2 \hat{g}(x)+2\int_{0}^{\lambda}ug(x,u)du.
+\end{align*}
+Combining the last equations we have 
+\begin{align*}
+&\int \Bigg(A^{1}_{\theta}f(\xi)+A^{2}_{\theta}f(\xi)+A^{3}_{\theta}f(\xi)\Bigg)\Gamma(d\mathbf{u})\\
+&=  \sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi)\prod_{(x_i,u_i)}\hat{g}(x_i) \left( \int_{\mathbb{R}^n} \hat{g}(y) q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\Xi,dy) - 2+\frac{1}{\hat{g}(x)}\right)+\sum_{(x,u) \in \xi } \prod_{(x_i,u_i)}\hat{g}(x_i)b_{\theta}(x,\Xi)\left(1-\frac{1}{\hat{g}(x)}\right)\\
+&=  \hat{f}(\xi)\sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi) \left(\int_{\mathbb{R}^n} \hat{g}(y) q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\Xi,dy) -1\right)+\hat{f}(\xi)\sum_{(x,u) \in \xi } (b_{\theta}(x,\Xi)-\theta\gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\xi))\left(1-\frac{1}{\hat{g}(x)}\right)\\
+&=  \hat{f}(\xi)\sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi) \left(\int_{\mathbb{R}^n} \hat{g}(y) q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\Xi,dy) -1\right) -\hat{f}(\xi)\sum_{(x,u) \in \xi } \theta \mu_{\varepsilon,\theta}(x,\Xi)\left(1-\frac{1}{\hat{g}(x)}\right),
+\end{align*}
+which corresponds to a spatial-branching process that branches at rate $\theta\gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi)$ leaving offspring around with kernel $ q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\Xi,dy)$ and each particle having death rate given by $\theta \mu_{\varepsilon,\theta}(x,\Xi)$.
+This is precisely the martingale problem in Definition \ref{def: Martingale Problem Characterisation - Product Form}.
+\newpage
+\subsubsection{Markov Mapping Theorem Application on Generator $A^{\text{nl}}_{\varepsilon}$}\label{sec: Markov Mapping Theorem application - limit}
+In this section we consider a general generator limit for the lookdown representation of our spatial model. 
+We define
+\begin{equation}
+\begin{aligned}
+A^{\text{nl}}_{\varepsilon}f(\eta )  =&f(\eta )\sum_{(x,u)\in\eta}\Bigg\{
+ \gamma(x, (\varrho_{\varepsilon}*\Xi)(x))
+ \frac{\mathcal{B}(g(\cdot,u)r( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)-g(x,u)\mathcal{B}r( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)}{g(x,u)}\\
+ &
+  +2\gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x))\times \ell \int_u^{
+\infty}(g(x,v_1)-1)dv_1\\
+&
++\bigg(\ell \gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x)) u^2 \\
+&~~~~~~~-\big(F(x, (\varrho_{\varepsilon}*\Xi)(x))+\gamma(x, (\varrho_{\varepsilon}*\Xi)(x))\mathcal{B}r( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)\big)u\bigg) \frac {\partial_u g(x,u)}{g(x,u)}\Bigg\},
+\end{aligned}    
+\end{equation}
+where our test measure $\eta$ takes value on $\mathcal{M}_F(\mathbb{R}\times [0,\infty))$ and $\Xi:=\lim_{u_0\rightarrow\infty}\frac 1{u_0}\sum_{(u,x)\in \eta:u\leq u_0}\delta_x$.
+
+If we take $\gamma =1, r=1, \mathcal{B}=\Delta,$ and $F(x, (\varrho_{\varepsilon}*\Xi)(x))=G( (\varrho_{\varepsilon}*\Xi)(x))-H( (\varrho_{\varepsilon}*\Xi)(x))$, then we recover $A^{\varepsilon, \infty}$ defined in Equation \eqref{Eq: Non-local Scaling limit Lookdown Generator}.
+
+Similar to the calculations above, we write $\alpha(\Xi,\cdot)$ for the distribution of a conditionally
+Poisson random measure $\eta^{\infty}$ on $\mathbb{R}^d\times [0,\infty)$ with mean measure
+$\Xi(dx)\times \Lambda$ and we calculate $\alpha A^{\text{nl}}_{\varepsilon}f(\eta)$.
+
+Once again, we write
+$$\alpha A^{\text{nl}}_{\varepsilon}f(\eta)=\alpha A^{1}_{nl}f(\eta)+\alpha A^{2}_{nl}f(\eta)+\alpha A^{3}_{nl}f(\eta),$$
+where 
+\small
+\begin{equation}\label{Eq: Decomposition of the Non-local Scaling limit Lookdown Generator}
+\begin{aligned}
+A^{1}_{nl}f(\eta )  =&f(\eta )\sum_{(x,u)\in\eta}
+ \gamma(x, (\varrho_{\varepsilon}*\Xi)(x))
+ \frac{B(g(\cdot,u)r( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)-g(x,u)Br( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)}{g(x,u)},\\
+A^{2}_{nl}f(\eta )  = &
+  f(\eta )\sum_{(x,u)\in\eta}2\gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x))\times \ell \int_u^{
+\infty}(g(x,v_1)-1)dv_1,\\
+ A^{3}_{nl}f(\eta )  =&f(\eta )
+\sum_{(x,u)\in\eta}\bigg(\ell \gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x)) u^2\\
+&\qquad \qquad \qquad \qquad -\big(F(x, (\varrho_{\varepsilon}*\Xi)(x))+\gamma(x, (\varrho_{\varepsilon}*\Xi)(x))Br( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)\big)u\bigg)\frac {\partial_u g(x,u)}{g(x,u)}\\
+\end{aligned}    
+\end{equation}
+\normalsize
+
+We define $h(x)=\int_{0}^{\infty} (1-g(x,u))du$.
+In this case, we have that $$\alpha f(\eta) = \exp \left(\int\int \big(g(x,u)-1\big) du \Xi(dx)\right)= \exp(\langle -h(x),\Xi(dx) \rangle ).$$  As a result we have that
+\begin{equation}\label{Eq: Averaging the Non-local Scaling limit Lookdown Generator Part 1}
+\footnotesize
+\begin{aligned}
+\alpha A^{1}_{nl}f(\eta )  =&
+ \alpha \left\{\sum_{(x,u)\in\eta}\gamma(x, (\varrho_{\varepsilon}*\Xi)(x))\frac{B(g(\cdot,u)r( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)-g(x,u)Br( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)}{g(x,u)}\prod_{(x_i,u_i)}g(x_i,u_i)\right\}\\
+ =&\int\int \bigg( \gamma(x, (\varrho_{\varepsilon}*\Xi)(x))B((g(\cdot,u)-1)r( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)-(g(x,u)-1)Br( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)\bigg)du \Xi(dx)\\
+ &\times \exp \left(\int\int \big(g(x,u)-1\big) du \Xi(dx)\right),\\
+ =& \left\langle \gamma(x, (\varrho_{\varepsilon}*\Xi)(x))B(h(\cdot) r( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)-h(\cdot)Br( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x),\Xi(dx) \right\rangle e^{-\langle h(x),\Xi(dx)\rangle} \\
+ \alpha A^{2}_{nl}f(\eta )  = &
+   \alpha \left\{2\sum_{(x,u)\in\eta}\gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x))\times \ell \int_u^{
+\infty}(g(x,v_1)-1)dv_1\prod_{(x_i,u_i)}g(x_i,u_i)\right\}\\
+=& \int\int \bigg(g(x,u)\gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x))\times \ell \int_u^{
+\infty}(g(x,v_1)-1)dv_1\bigg)du \Xi(dx)e^{-\langle h(x),\Xi(dx)\rangle}\\
+=& 
+\left\langle \ell \gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x))\int g(x,u)\int_u^{
+\infty}(g(x,v_1)-1)dv_1 du,\Xi(dx)\right\rangle e^{-\langle h(x),\Xi(dx)\rangle}\\
+ \alpha A^{3}_{nl}f(\eta )  =&
+\alpha \Bigg\{\sum_{(x,u)\in\eta}\bigg(\ell \gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x)) u^2 -\big(F(x, (\varrho_{\varepsilon}*\Xi)(x))+\gamma(x, (\varrho_{\varepsilon}*\Xi)(x))Br( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)\big)u\bigg)\\
+&\times \frac {\partial_u g(x,u)}{g(x,u)}\prod_{(x_i,u_i)}g(x_i,u_i)\Bigg\}\\
+=& \bigg \langle \ell \gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x))\int \partial_u g(x,u) u^2 du \\
+& ~~~ - \big(F(x, (\varrho_{\varepsilon}*\Xi)(x))+\gamma(x, (\varrho_{\varepsilon}*\Xi)(x))Br( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)\big) \int u \partial_u g(x,u) du ,\Xi(dx)\bigg\rangle \times e^{-\langle h(x),\Xi(dx)\rangle} .
+ \end{aligned}    
+\end{equation}
+\normalsize
+Now note that with integration by parts
+\begin{multline}
+ \ell \gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x))  \int_{0}^{\infty}\partial_u g(x,u) u^2 du  \\=  2\ell\gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x))\int_{0}^{\infty} u (g(x,u)-1) du,
+\end{multline}
+\begin{multline}
+ \big(F(x, (\varrho_{\varepsilon}*\Xi)(x))+\gamma(x, (\varrho_{\varepsilon}*\Xi)(x))Br( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)\big)\int_{0}^{\infty} u \partial_u g(x,u)du \\=\big(F(x, (\varrho_{\varepsilon}*\Xi)(x))+\gamma(x, (\varrho_{\varepsilon}*\Xi)(x))Br( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)\big)\int_{0}^{\infty} (g(x,u)-1) du\\
+ =-\big(F(x, (\varrho_{\varepsilon}*\Xi)(x))+\gamma(x, (\varrho_{\varepsilon}*\Xi)(x))Br( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)\big) h(x)
+\end{multline}
+and furthermore, we apply Fubini theorem to get that 
+\begin{multline}
+  2 \ell \gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x)) \int_{0}^{\infty} u    (g(x,u)-1) du \\
+  =   2 \ell \gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x)) \int_{0}^{\infty} \int_{0}^{u}    dv_1 (g(x,u)-1) du \\
+  =  2 \ell \gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x)) \int_{0}^{\infty}  \int_{v_1}^{\infty}    (g(x,u)-1) du dv_1.
+\end{multline}
+Finally, note also that
+\begin{multline}
+\int 2\bigg(g(x,u)\gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x))\times \ell \int_u^{
+\infty}(g(x,v_1)-1)dv_1\bigg)du\\
+= 2\ell \gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x))\int \bigg( g(x,u) \int_u^{
+\infty}(g(x,v_1)-1)dv_1\bigg)du.
+\end{multline}
+\normalsize
+Combining all results we have that
+\small
+\begin{equation}\label{eq: Non-local lookdown generator MMP calculation}
+\begin{aligned}
+\alpha A^{\text{nl}}_{\varepsilon}f(\eta)
+=&~ e^{-\langle h(x),\Xi(dx)\rangle}  \Bigg\{\left\langle \gamma(x, (\varrho_{\varepsilon}*\Xi)(x))B(h(\cdot) r( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)-h(\cdot)Br( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x),\Xi(dx) \right\rangle\\
+&+\bigg \langle2\ell\gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x))\int_{0}^{\infty} u (g(x,u)-1) du \\
+ &+ \big(F(x, (\varrho_{\varepsilon}*\Xi)(x))+\gamma(x, (\varrho_{\varepsilon}*\Xi)(x))Br( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)\big) h(x) ,\Xi(dx)\bigg\rangle\\
+ & +\left\langle 2 \ell \gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x))\int g(x,u)\int_u^{
+\infty}(g(x,v_1)-1)dv_1 du,\Xi(dx)\right\rangle \Bigg\}\\
+=&~ e^{-\langle h(x),\Xi(dx)\rangle}  \Bigg\{\left\langle \gamma(x, (\varrho_{\varepsilon}*\Xi)(x))B(h(\cdot) r( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)+ F(x, (\varrho_{\varepsilon}*\Xi)(x),\Xi(dx) \right\rangle\\
+&+\bigg \langle 2 \ell \gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x)) \int_{0}^{\infty}  \int_{v_1}^{\infty}    (g(x,u)-1) du dv_1 \\
+ & + 2\ell \gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x))\int_0^{\infty} g(x,u)\int_u^{
+\infty}(g(x,v_1)-1)dv_1 du,\Xi(dx)\bigg\rangle \Bigg\}\\
+=&~ e^{-\langle h(x),\Xi(dx)\rangle}  \Bigg\{\bigg\langle \gamma(x, (\varrho_{\varepsilon}*\Xi)(x))B(h(\cdot) r( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)+ F(x, (\varrho_{\varepsilon}*\Xi)(x)\\
+& + \ell \gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x))2 \int_0^{\infty} (g(x,u)-1)\int_u^{
+\infty}(g(x,v_1)-1)dv_1 du,\Xi(dx)\bigg\rangle \Bigg\}\\
+=&~ e^{-\langle h(x),\Xi(dx)\rangle} \times \Bigg\{\bigg\langle \gamma(x, (\varrho_{\varepsilon}*\Xi)(x))B(h(\cdot) r( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)+ F(x, (\varrho_{\varepsilon}*\Xi)(x)\\
+& + \ell \gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x))h(x)^2,\Xi(dx)\bigg\rangle \Bigg\}\\
+:=&~\mathcal{L}^{nl}_{\varepsilon}\alpha f(\eta),
+\end{aligned}
+\end{equation}
+\normalsize
+where $\mathcal{L}^{nl}_{\varepsilon}$ is the generator of a non-linear superprocess of the form characterised in Equation \eqref{eq: Empirical Measure Martingale characterisation - product form}.
 

### 2022-04-07 forwards-and-backwards.tex
edits to heuristics

@@
 
+\comment{TODO: short lead-in}
+
 % % % % % % % % % % % % % % % % % %
@@
     \label{sec:population_heuristics}
-
-\comment{TODO: short lead-in}
 
@@
     =
-    F \left( \int f(x)\eta^{\theta}_s(dx) \right),
+    F \left( \int f(x)\eta(dx) \right),
 $$
@@
 
+% % % % % % % 
 \subsubsection*{Mean measure}
 
-Consider first the mean measure. For a suitable 
-(smooth, compactly supported) test function $f$, we find
-\begin{multline}
-\label{mean measure}
-{\cal L}^{(\theta, N)}\langle f,\eta\rangle=
-\lim_{\delta t\downarrow 0}\frac{1}{\delta t}
-\IE\left[\left.\langle f,\eta_{\delta t}\rangle -
-\langle f, \eta\rangle \right|\eta_0=\eta
-\right]\\
-=\theta\int\int f(z)r(z,\eta)q_\theta(x,dz)
-\gamma(x,\eta)
-\eta^{\theta}_s(dx)-\theta\int f(x)\mu(x,\eta)
-\eta^{\theta}_s(dx).
-\end{multline}
+Consider first the mean measure.
+The birth rate at location $x$ when the state of the population is $\eta$
+is a function of the location and the measure $\eta$ through a specific form:
+$\gamma(x, \smooth{\gamma} \eta(x))$;
+however, for the moment we will write $\gamma(x, \eta)$ instead
+to make the exposition clearer
+(and similarly for establishment probability $r(x, \eta)$ and death rate $\mu(x, \eta)$).
+Recall that in our parameterization only $\mu$ and the dispersal kernel $q$ depend on $\theta$.
+For a suitable (smooth, compactly supported) test function $f$, we find
+\begin{equation} \label{mean measure}
+    \begin{split}
+    \Pgen^\theta \langle f, \eta \rangle
+    &=
+    \lim_{\delta t\downarrow 0} \frac{1}{\delta t}
+    \IE\left[ \left.
+        \langle f, \eta_{\delta t} \rangle
+        -
+        \langle f, \eta\rangle
+        \right| \eta_0 = \eta
+    \right]
+    \\
+    &=
+    \theta \int
+        \int f(z) r(z,\eta) q_\theta(x,dz)
+    \gamma(x, \eta) \eta(dx)
+    -
+    \theta \int f(x)\mu_\theta(x, \eta)
+    \eta(dx).
+    \end{split}
+\end{equation}
 The first term is the increment in $\langle f,\eta\rangle$
@@
 and the second reflects death events.
-In both terms, the 
-rate of events has a factor of $N$ (because events happen at a rate 
-proportional to the number of individuals, whereas $\eta$ is
-the scaled population mass) which is offset by the fact that  
+In both terms,
+the rate of events has a factor of $N$ (because events happen at a rate 
+proportional to the number of individuals,
+whereas $\eta$ has mass $1/N$ for each individual)
+which is offset by the fact that  
 the birth or loss of a single 
@@
 as 
-\begin{multline}
-\label{rewritten mean measure}
-\int\left(\int \theta \left(
-f(z)r(z,\eta)- f(x)r(x,\eta)\right)
-q_\theta(x,dz)\right)
+\begin{equation}
+\label{eqn:rewritten mean measure}
+\begin{split}
+    \int\left(
+        \int \theta \left( f(z) r(z,\eta)- f(x) r(x,\eta) \right) q_\theta(x,dz)
+    \right)
     \gamma(x,\eta)
-\eta^{\theta}_s(dx)
+    \eta(dx)
     \\
-+\int\theta\int f(x)\Big(r(x,\eta)
-\gamma(x,\eta)
--\mu(x,\eta)\Big)
-\eta^{\theta}_s(dx).
-\end{multline}
-Suppose that $\eta\to\Xi$, a measure on $\IR^d$,
-in the scaling limit, then we see that we can 
-let $\theta\rightarrow\infty$ in~(\ref{rewritten mean measure})
-under the assumptions that
-\begin{eqnarray}
-r(x,\eta)&\stackrel{\theta\to\infty}{\longrightarrow}&
-r(x,\Xi)\\
-\gamma(x,\eta)&\stackrel{\theta\to\infty}{\longrightarrow}&
-\gamma(x,\Xi)\\
-\int\theta \Big(r(z,\eta)f(z)-
-r(x,\eta)f(x)\Big)q_\theta(x,dz) 
-&\stackrel{\theta\to\infty}{\longrightarrow}& 
-\Delta \big(r(\cdot,\Xi)f(\cdot)\big)(x);\\
-\theta \Big(r(x,\eta)\gamma (x,\eta)
--\mu (x,\eta)\Big)
- &\stackrel{\theta\to\infty}{\longrightarrow}& 
-F(x,\Xi),
-\label{near critical}
-\end{eqnarray}
-where $\Delta$ denotes the Laplacian.
-The last condition reflects the `near-critical' branching. Note that
-there is a slight mismatch between the locations at which we are 
-measuring birth and death rates, because in~(\ref{near critical})
+    + \int \int f(x) \theta \Big(
+        r(x,\eta) \gamma(x,\eta)
+        - \mu_\theta(x,\eta)
+    \Big) \eta(dx).
+\end{split}
+\end{equation}
+We have defined $\mu_\theta$ so that the second term is simple:
+\begin{align*}
+    \theta \Big( r(x,\eta) \gamma(x,\eta) - \mu_\theta(x,\eta) \Big)
+    = F(x, \eta) .
+\end{align*}
+This definition --
+is really a `near-critical' assumption that birth and death rates
+differ by something of order $1/\theta$.
+Furthermore, since we've taken $q_\theta$ to be the density of a Normal
+with mean and variance proportional to $1/\theta$,
+\begin{align} \label{eqn:near_critical}
+    \int \theta \Big(
+        r(z,\eta) f(z)
+        -
+        r(x,\eta) f(x)
+    \Big) q_\theta(x,dz) 
+    \qquad \stackrel{\theta\to\infty}{\longrightarrow} \qquad  
+    \DG \big(r(\cdot,\Xi)f(\cdot)\big)(x),
+\end{align}
+where recall if dispersal is simply standard multivariate Gaussian
+with mean zero and covariance $\sigma^2 I / \theta$,
+then $\DG = \sigma^2 \Delta$, where $\Delta$ denotes the Laplacian.
+Note that there is a slight mismatch between the locations at which we are 
+measuring birth and death rates, because in~\eqref{eqn:near_critical}
 the establishment probability is 
 measured at $x$ rather than at the point where juveniles fall. 
+\comment{(IS THIS BIT STILL TRUE:)}
 This condition also differs from the assumption that
@@
 
-Equation~(\ref{rewritten mean measure}) converges to
-\begin{equation}%\begin{multline}
-\label{limit of mean measure equation}
-\int \gamma(x,\Xi)
-\Delta
-\big(f(\cdot)r(\cdot,\Xi)\big)(x)
-\Xi(dx)
-+\int f(x)
-F(x,\Xi)
-\Xi(dx)
-.
-\end{equation}
-
+Equation~\eqref{eqn:rewritten mean measure}) then converges to
+\begin{equation} \label{limit of mean measure equation}
+\int \gamma(x,\eta)
+\DG \big(f(\cdot)r(\cdot,\eta)\big)(x)
+\eta(dx)
++
+\int f(x)
+F(x,\eta)
+\eta(dx) .
+\end{equation}
+More generally, we expect everything to work
+if the remaining parameters ($r$, $\gamma$, and $F$)
+depended on $\theta$, but converged as $\theta \to \infty$.
+
+% % % % % % % 
 \subsubsection*{Quadratic variation}
 
+% Note: this bit in firstversionplus.tex has things written out in detail for
+% the Poisson offspring number case.
+
 We now look at the second order term.
-We spell out
-this calculation in detail so that it is evident at which points we are 
-exploiting the choice of the Poisson distribution for the number
-of juvenile offspring.
-In the general case one can expect somewhat messier calculations, but
-the same conclusion (up to constants).
-
-When an individual at the point $x$ gives birth, the total number of
-mature offspring is Poisson with parameter
-$$\gamma(x,\eta)\int 
-r(y,\eta) q_{\theta}(x, dy)
-=\gamma(x,\eta)p_\theta(x,\eta).$$
-Offspring that survive to maturity are distributed about the parent
-according to 
-$$\overline{q}_\theta(x,\eta,dy):=
-\frac{r(y,\eta)q_\theta(x,dy)} 
-{\int r(z,\eta)q_\theta(x,dz)}. 
+An individual at location $x$ gives birth 
+to a surviving offspring at $y$ at rate
 $$
-Writing $X(x)$ for the increment to $\langle f, \eta\rangle$
-due to a single mature offspring of an individual at $x$, 
-and $P(x)$ for the (Poisson) number of mature
-offspring in such an event, the variance of the increment to 
-$\langle f, \eta\rangle$
-resulting from a birth event at $x$ is $\IE[P(x)]\mathtt{var}(X(x))
-+\mathtt{var}(P(x))\IE[X(x)]^2=\IE[P]\IE[X(x)^2]$. 
-Since, in this notation, conditional on the value of $\eta$
-immediately before the event,
-$$\IE[X(x)^2]=\int
-\frac{1}{N^2}f^2(y) \overline{q}_\theta(x,\eta,dy),$$
-and
-$$\IE[P(x)]=
-\gamma (x,\eta) \int 
-r(z,\eta)q_\theta(x,dz),$$ 
-the contribution to the quadratic variation from birth events, which
-occur at rate $\theta$ per individual 
-(so $N\theta |\eta|$ overall), is
-$$\langle N\theta \gamma(x,\eta)
-\int \frac{1}{N^2}f^2(y)r(y,\eta)
+\gamma(x,\eta) r(y,\eta) q_{\theta}(x, dy) ,
+$$
+and since this increments $\langle f, \eta \rangle$ by $f(y) / N$,
+the contribution to the quadratic variation from birth events,
+which occur at rate $\theta$ per individual 
+(so, rate $N\theta |\eta|$ overall), is
+$$
+\langle
+    N \theta \gamma(x,\eta)
+    \int \frac{1}{N^2} f^2(y) r(y,\eta)
     q_\theta(x,dy) 
-,\eta^{\theta}_s(dx)\rangle.$$
-The increment in $\langle f, \eta\rangle$ resulting from 
-the death of an individual at $x$ is $f(x)/N^2$, and so combining with the 
+    , \eta(dx)
+\rangle .
+$$
+Similarly, the increment in $\langle f, \eta\rangle$ resulting from 
+the death of an individual at $x$ is $f(x)/N$, and so combining with the 
 above, the second order term in the generator takes the form
-$$F''(\langle f,\eta\rangle)
-\frac{1}{2}N\theta \left\{
-\langle \gamma(x,\eta)
+$$
+F''(\langle f,\eta\rangle)
+\frac{1}{2} N \theta
+\left\{
+    \langle
+        \gamma(x,\eta)
         \int \frac{1}{N^2}f^2(y)r(y,\eta)q_\theta(x,dy) 
-,\eta^{\theta}_s(dx)\rangle
-+\langle \mu(x,\eta)\frac{1}{N^2}f^2(x) 
-,\eta^{\theta}_s(dx)\rangle\right\}.
+    , \eta(dx)\rangle
+    +
+    \langle
+        \mu_\theta(x,\eta)\frac{1}{N^2}f^2(x) 
+    ,\eta(dx)\rangle
+\right\} .
 $$
 The term $\varepsilon_{\theta,N}(f, F, \eta)$ will be 
-${\mathcal O}(\theta/N^2)$.
-
+$\bigO(\theta/N^2)$.
+
+% % % % % % % %
 \subsubsection*{Limit I: deterministic case}
+
+\comment{Need to decide what to call the limit here (and above, I guess).}
 
@@
 by parts, we find that in the limit as $N\to\infty$,
-\begin{equation}
-\nonumber
+\begin{equation*}
 \frac{d}{dt}\int f(x)\Xi_t(x)dx
-=\int f(x)\left\{r(x,\Xi_t)\Delta\big(\gamma(\cdot,\Xi_t)
-\Xi_t(\cdot)\big)(x)+F(x,\Xi_t)
-\Xi_t(x)
-\right\}dx.
-\end{equation}
+=
+\int f(x)\left\{r(x,\Xi_t)\DG\big(\gamma(\cdot,\Xi_t)
+\Xi_t(\cdot)\big)(x)
++
+F(x,\Xi_t) \Xi_t(x)
+\right\} dx.
+\end{equation*}
 In other words, we can expect the limit to be a weak solution to the 
@@
 \frac{d\Xi}{dt}
-=r(x,\Xi)\Delta\big(\gamma(\cdot,\Xi)
+=r(x,\Xi)\DG\big(\gamma(\cdot,\Xi)
 \Xi(\cdot)\big)(x)+F(x,\Xi)
@@
 
-If $N=\rho\theta$, for some constant $\rho$,
+If $N=\delta\theta$, for some positive constant $\delta$,
 the second order term in the generator remains order
 one as $\theta\to\infty$, and  
-we expect a `generalised
-superprocess'
-limit. Assuming some regularity of the coefficients (in particular 
-of $r$), 
-the second order term in the generator will  
-take the form
-$$\frac{1}{\rho}F''(\langle f,\Xi\rangle)
+we expect a `generalised superprocess' limit.
+Assuming some regularity of the coefficients (in particular of $r$), 
+the second order term in the generator will take the form
+$$
+\frac{1}{\delta}F''(\langle f,\Xi\rangle)
 \langle f^2(x), \gamma(x,\Xi)
@@
 $$\langle f(x), \Xi_t(dx)\rangle-\langle f(x), \Xi_0(dx)\rangle
--\int_0^t\langle\gamma(x,\Xi_s)\Delta\big(r(\cdot,\Xi_s)f(\cdot)\big)(x),
+-\int_0^t\langle\gamma(x,\Xi_s)\DG\big(r(\cdot,\Xi_s)f(\cdot)\big)(x),
 \Xi_s(dx)\rangle ds$$
 is a martingale with quadratic variation
-$$\frac{2}{\rho}\int_0^t\langle f^2(x) 
+$$\frac{2}{\delta}\int_0^t\langle f^2(x) 
 \gamma(x,\Xi_s)r(x,\Xi_s),\Xi_s(dx)\rangle ds.$$
@@
 on $[0,\lambda]$.
-Similar lookdown constructions can be found in \cite{etheridge/kurtz:2018},\cite{kurtz/rodrigues:2011}.
+Similar lookdown constructions can be found 
+in \cite{etheridge/kurtz:2018},\cite{kurtz/rodrigues:2011}.
 Test functions for this enriched process take the form
@@
 the established birth rate $\gamma(x,\eta)$ is
-$$\theta\gamma^{\mathfrak{m}}_{\theta}(x, \eta):=~\theta\gamma(x, \varrho_{\gamma}*\eta(x)) \int r(y, \varrho_{r}*\eta(y))q_{\theta}(x,dy);$$
+$$\theta\gamma^{\mathfrak{m}}_{\theta}(x, \eta)
+:=~\theta\gamma(x, \varrho_{\gamma}*\eta(x)) \int r(y, \varrho_{r}*\eta(y))q_{\theta}(x,dy);$$
 the local branching mechanism $b(x,\eta)$ is 
@@
 and the dispersal kernel $q^{\mathfrak{m}}(x,dy)$ is 
-$$q^{\mathfrak{m}}_{\theta}(x,\eta,dy) :=~ \frac{r(y,\varrho_{r}*\eta(y)) q_{\theta}(x,dy)}{\int_{\mathbb{R}^d} r(y,\varrho_{r}*\eta(y)) q_{\theta}(x,dy)}.$$
+$$q^{\mathfrak{m}}_{\theta}(x,\eta,dy) 
+:=~ \frac{r(y,\varrho_{r}*\eta(y)) q_{\theta}(x,dy)}{\int_{\mathbb{R}^d} r(y,\varrho_{r}*\eta(y)) q_{\theta}(x,dy)}.$$
 
@@
 &&A^{\theta}f(\xi ) \\
-&&\quad =f(\xi )\,\sum_{(x,u)\in\eta}\,2 \gamma^{\mathfrak{m}}_{\theta}(x, \eta)\Bigg\{ \frac 12 \lambda^{-1}\int_u^{
-\lambda}g(x,v_1)dv_1\times \frac { \theta\int_{\mathbb{R}^d}(g(y,u)-g(x,u))q^{\mathfrak{m}}_{\theta}(x,\eta,dy) }{g(x,u)}\non\\
-&&\qquad\qquad\qquad\qquad\qquad\qquad\qquad +\lambda^{-1}\theta\int_u^{
-\lambda}\int_{\mathbb{R}^d}\left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\theta}(x,\eta,dy)dv_1\nonumber\Bigg\}\\
+&&\quad =f(\xi )\,\sum_{(x,u)\in\eta}\,2 \gamma^{\mathfrak{m}}_{\theta}(x, \eta)\Bigg\{ \frac 12 N^{-1}\int_u^{
+N}g(x,v_1)dv_1\times \frac { \theta\int_{\mathbb{R}^d}(g(y,u)-g(x,u))q^{\mathfrak{m}}_{\theta}(x,\eta,dy) }{g(x,u)}\non\\
+&&\qquad\qquad\qquad\qquad\qquad\qquad\qquad +N^{-1}\theta\int_u^{
+N}\int_{\mathbb{R}^d}\left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\theta}(x,\eta,dy)dv_1\nonumber\Bigg\}\\
 &&\qquad\qquad
-+f(\eta )\sum_{(x,u)\in\xi}\,\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\eta) u^2 -b_{\theta}(x,\eta)u\right)\frac {\partial_u g(x,u)}{g(x,u)}.\nonumber
++f(\eta )\sum_{(x,u)\in\xi}\,\left(N^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\eta) u^2 -b_{\theta}(x,\eta)u\right)\frac {\partial_u g(x,u)}{g(x,u)}.\nonumber
 \end{eqnarray}
@@
 
-In \S \ref{sec: Markov Mapping Theorem Application},
+\begin{remark}
+In Appendix \ref{sec: Markov Mapping Theorem Application},
 applying Markov Mapping Theorem,
-we will show that the spatial projection of $(\eta^{\theta}_t)_{t \geq 0}$ has the same distribution as $(\eta^{\varepsilon, \theta, N}_t)_{t \geq 0}$ if we take $\lambda = N$.
-Specifically, we mean that when $\lambda=N$,
-$$(\eta^{\theta}(t))_{t \geq 0}:=\left(\frac{1}{\lambda}\sum\limits_{\substack{(X(t),U(t))\in \eta^{\theta}(t) \\ U(t) < \lambda}} \delta_{X(t)}\right)_{t \geq 0}$$
-has the same distribution (as stochastic processes) as $(\eta^{\theta}_t)_{t \geq 0}$ in Definition \ref{Def: Rescaled Models}.
-As a result, we use the same notation $\eta$ to denote these two essentially identical processes which take values in the space of empirical measures.
-On the other hand, we reserve the notation $\eta$ strictly for the spatial-level process.\\~\\ Furthermore, the application of Markov Mapping Theorem implies that particle levels are, conditional on $\eta$, i.i.d and uniformly distributed between $[0, \lambda]$.
-Theorem A.10 in \cite{kurtz/rodrigues:2011} states that convergence of $(\eta^{\theta}_t)_{t \geq 0}$ to a conditionally Poisson system $(\xi_t)_{t \geq 0}$ with Cox measure $\Xi_t \times \Lambda$ is equivalent to convergence of $(\eta^{\varepsilon, \theta, N}_t)_{t \geq 0}$ to $(\Xi_t)_{t \geq 0}$.
-As a result, it suffices for us to focus on tightness of $(\eta^{\theta}_t)_{t \geq 0}$ and spatial convergence of $(\eta^{\varepsilon, \theta, N}_t)_{t \geq 0}$ as $\theta \to \infty$.
+we will show that the spatial projection of $(\xi^{\theta}_t)_{t \geq 0}$ defined as 
+$$(\eta^{\theta}(t))_{t \geq 0}
+:=\left(\frac{1}{N}\sum\limits_{(X(t),U(t))\in \xi^{\theta}(t)} \delta_{X(t)}\right)_{t \geq 0}$$
+has the same distribution (as stochastic processes)
+as $(\eta^{\theta}_t)_{t \geq 0}$
+in Definition \ref{Def: Rescaled Models}.
+As a result, we use the same notation $\eta$
+to denote these two identically distributed processes
+which take values in the space of empirical measures.
+On the other hand,
+we reserve the notation $\xi$
+strictly for the spatial-level process.
+
+Furthermore, the application of Markov Mapping Theorem implies that 
+particle levels are, conditional on $\eta$,
+i.i.d and uniformly distributed between $[0, N]$.
+
+Theorem A.10 in \cite{kurtz/rodrigues:2011}
+states that convergence of $(\eta^{\theta}_t)_{t \geq 0}$
+to a conditionally Poisson system $(\xi_t)_{t \geq 0}$
+with Cox measure $\Xi_t \times N$
+is equivalent to convergence of
+$(\eta^{\varepsilon, \theta, N}_t)_{t \geq 0}$ to $(\Xi_t)_{t \geq 0}$.
+As a result, it suffices for us to focus on
+tightness of $(\eta^{\theta}_t)_{t \geq 0}$
+and spatial convergence of $(\eta^{\varepsilon, \theta, N}_t)_{t \geq 0}$
+as $\theta \to \infty$.
+
+\end{remark}
 
@@
     \label{sec: Markov Mapping Theorem Application}
-\subsection{Markov Mapping Theorem Application on Generator $A_{\theta}$}\label{sec: Markov Mapping Theorem Application - Prelimit}
+\subsection{Markov Mapping Theorem Application on Generator $A^{\theta}$}\label{sec: Markov Mapping Theorem Application - Prelimit}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newpage
+\section{Technical Lemmas}
+\subsection{Proof to Lemma \ref{lem: gamma - r radius comparison}}
+
+Suppose that the birth rate at $x$ is
+$\gamma(\rho_\gamma * \eta(x))$
+and the establishment probability is
+$r(\rho_r * \eta(x))$,
+for some functions $\gamma$ and $r$,
+and where $\rho_\gamma$ and $\rho_r$ are some kernels,
+and that the death rate at $x$ is
+$$
+    \mu(x, \eta) = 
+        \gamma(\rho_\gamma * \eta(x))
+        r(\rho_r * \eta(x))
+        +
+        \frac{1}{\theta} F(\rho_R * \eta(x))
+$$
+for some bounded function $F$ and kernel $\rho_R$ (that is probably either $\rho_r$ or $\rho_\gamma$).
+
+To bound $\E\left[\langle 1, \eta_t \rangle\right]$
+by Gronwall,
+we would like to find a bound of the form
+\begin{align} \label{eqn:goal}
+    \theta \int \left[
+        r(\rho_r * \eta(y))
+        -
+        r(\rho_r * \eta(x))
+    \right] q_\theta(x, dy)
+    \le
+    G( \rho_\gamma * \eta(x) ),
+\end{align}
+for some polynomial function $G$.
+
+To do this, first we expand $r(\rho_r * \eta(x))$ to second order.
+Given $y$, with $x < \tilde y < y$,
+\begin{align}
+    r(\rho_r * \eta(y)) - r(\rho_r * \eta(x))
+    &=
+    r'(\rho_r * \eta(x))
+    \left\{
+        \rho_r * \eta(y)
+        -
+        \rho_r * \eta(x)
+    \right\}
+    +
+    \frac{1}{2}
+    r''(\rho_r * \eta(\tilde y))
+    \left\{
+        \rho_r * \eta(y)
+        -
+        \rho_r * \eta(x)
+    \right\}^2 .
+\end{align}
+
+Putting this in Equation \eqref{eqn:goal}, the second term is then
+\begin{align}
+&\theta \int
+    \frac{1}{2}
+    r''(\rho_r * \eta(\tilde y))
+    \left\{
+        \rho_r * \eta(y)
+        -
+        \rho_r * \eta(x)
+    \right\}^2 
+    q_\theta(x, dy)  \\
+&\qquad
+\le \theta \frac{\|r''\|_\infty}{2}
+    \int
+    \left\{
+        \rho_r * \eta(y)
+        -
+        \rho_r * \eta(x)
+    \right\}^2 
+    q_\theta(x, dy)  .
+\end{align}
+
+We will first show that this is bounded by a function of $\rho_\gamma * \eta(x)$,
+i.e., that for any $x < \tilde y < y$ and $\theta$ sufficiently large,
+there is a $C$ with
+\begin{align} \label{eqn:goal2}
+    \theta \int
+    \left\{
+        \rho_r * \eta(y)
+        -
+        \rho_r * \eta(x)
+    \right\}^2 
+    q_\theta(x, dy)  
+\le
+C \rho_\gamma * \eta(x) .
+\end{align}
+
+Leaving aside the $\frac{\|r''\|_\infty}{2}$ constant,
+let's rewrite this so we can use Fubini.
+First note that,
+since $\rho_r *\eta(x) = \int \rho_r(x - w) \eta(dw)$
+is the normalizing constant for the measure proportional to $\rho_r(x - w) \eta(dw)$,
+then applying Jensen's inequality,
+\begin{align}
+&\left\{
+            \rho_r * \eta(y)
+            -
+            \rho_r * \eta(x)
+\right\}^2  \\
+&\qquad
+=
+\left\{
+\int
+    \left(
+        \rho_r(y-w)
+        -
+        \rho_r(x-w)
+    \right)
+\eta(dw)
+\right\}^2  \\
+&\qquad
+=
+\left\{
+\int
+    \left(
+        \frac{\rho_r(y-w)}{\rho_r(x-w)}
+        -
+        1
+    \right)
+    \rho_r(x-w)
+\eta(dw)
+\right\}^2  \\
+&\qquad
+=
+\left(\rho_r * \eta(x)\right)^2 \left\{
+\int
+    \left(
+        \frac{\rho_r(y-w)}{\rho_r(x-w)}
+        -
+        1
+    \right)
+    \frac{\rho_r(x-w)}{\rho_r * \eta(x)}
+\eta(dw)
+\right\}^2  \\
+&\qquad
+\le
+\left(\rho_r * \eta(x)\right)^2 
+\int
+    \left(
+        \frac{\rho_r(y-w)}{\rho_r(x-w)}
+        -
+        1
+    \right)^2
+    \frac{\rho_r(x-w)}{\rho_r * \eta(x)}
+\eta(dw) \\
+&\qquad
+=
+\rho_r * \eta(x)
+\int
+    \left(
+        \frac{\rho_r(y-w)}{\rho_r(x-w)}
+        -
+        1
+    \right)^2
+    \rho_r(x-w)
+\eta(dw) .
+\end{align}
+
+Now, we don't mind having the $\rho_r * \eta(x)$ term,
+so we'd like to bound the remaining bit by $\rho_\gamma * \eta(x)$.
+We'll now bring in the integral over $y$ and use Fubini, so that
+\begin{align}
+&\int \theta
+\int
+    \left(
+        \frac{\rho_r(y-w)}{\rho_r(x-w)}
+        -
+        1
+    \right)^2
+    \rho_r(x-w)
+\eta(dw)
+q_\theta(x, dy) \\
+&\qquad
+=
+\int \theta H_\theta(x, w) \rho_r(x-w) \eta(dw) ,
+\end{align}
+if we define
+\begin{align}
+H_\theta(x, w)
+:=
+\int
+    \left(
+        \frac{\rho_r(y-w)}{\rho_r(x-w)}
+        -
+        1
+    \right)^2
+q_\theta(x, dy) .
+\end{align}
+So, it only remains to bound $\theta H_\theta (w, x) \rho_r(x-w) $ by $\rho_\gamma(x - w)$.
+
+Now, let's assume that $\rho$ and $q$ are all Gaussian;
+to avoid difficulties with notation,
+define  $p_t(x) = \exp(-x^2 / 2t) / (2 \pi t)^{d/2}$
+to be the heat kernel,
+so that $\rho_r(x) = p_{\epsilon_r^2}(x)$
+and $q_\theta(x) = p_{1/\theta}(x)$.
+Writing out $H$,
+\begin{align}
+H_\theta(x, w)
+=
+\int
+    \left(
+        \exp\left(
+            - \frac{1}{2\epsilon_r^2}
+            \left\{
+                (y - w)^2 - (x - w)^2
+            \right\}
+        \right)
+        -
+        1
+    \right)^2
+    \frac{
+        e^{-\theta(y - x)^2 / 2}
+    }{
+        (2 \pi / \theta)^{d/2}
+    }
+dy .
+\end{align}
+
+We'll just multiply this out and evaluate it directly,
+using the fact that
+\begin{align}
+&
+\int e^{-a z - b z^2 / 2} \frac{e^{-\theta z^2 / 2}}{(2 \pi / \theta)^{d/2}} dz
+\\ &\qquad
+=
+\left(
+    \frac{ \theta }{ \theta + b }
+\right)^{d/2}
+\int e^{-a z} \frac{e^{-(\theta + b) z^2 / 2}}{(2 \pi / (\theta + b))^{d/2}} dz
+\\ &\qquad
+= \label{eqn:mgf}
+\left(
+    \frac{ \theta }{ \theta + b }
+\right)^{d/2}
+\exp\left( \frac{ a^2 }{ 2 (\theta + b) } \right) ,
+\end{align}
+(since $Z \sim \text{Normal}(0, \sigma^2)$ then $\E[e^{tZ}] = \exp(\sigma^2 t^2 / 2)$).
+
+Let $z = y - x$ and note that the polynomial in the exponent inside the definition of $H$ is
+\begin{align}
+    (y-w)^2 - (x-w)^2
+    &=
+    (y - x)(y + x - 2w) \\
+    &=
+    z (z + 2x - 2w) ,
+\end{align}
+and so
+\begin{align}
+&
+\left(
+    \exp\left(
+        \frac{1}{2\epsilon_r^2}
+        \left\{
+            (y - w)^2 - (x - w)^2
+        \right\}
+    \right)
+    -
+    1
+\right)^2 \\
+&\qquad
+= \label{eqn:H_form}
+    \exp\left(
+        - \frac{1}{\epsilon_r^2}
+        \left\{
+            z^2 + z (2x - 2w)
+        \right\}
+    \right)
+    - 2 \exp\left(
+        - \frac{1}{2\epsilon_r^2}
+        \left\{
+            z^2 + z (2x - 2w)
+        \right\}
+    \right)
+    + 1 .
+\end{align}
+So, for the first term in $H$ we use \eqref{eqn:mgf} with
+$a = 2 (x-w) / \epsilon_r^2$ and $b = 2 / \epsilon_r^2$,
+while for the second these are each divided by 2.
+So,
+\begin{align}
+H_\theta(x, w)
+&=
+\left(
+    \frac{ \theta }{ \theta + 2/\epsilon_r^2 }
+\right)^{d/2}
+\exp\left( \frac{ 4 (x-w)^2 }{ 2 \epsilon_r^2 (\theta \epsilon_r^2 + 2) } \right)
+- 2
+\left(
+    \frac{ \theta }{ \theta + 1/\epsilon_r^2 }
+\right)^{d/2}
+\exp\left( \frac{ (x-w)^2 }{ 2 \epsilon_r^2 (\theta \epsilon_r^2 + 1) } \right)
++ 1 \\
+&=
+\left(
+    \frac{ 1 }{ 1 + 2/(\theta \epsilon_r^2) }
+\right)^{d/2}
+\exp\left( \frac{ 4 (x-w)^2 }{ 2 \epsilon_r^2 \theta (\epsilon_r^2 + 2/\theta) } \right)
+- 2
+\left(
+    \frac{ 1 }{ 1 + 1/(\theta \epsilon_r^2) }
+\right)^{d/2}
+\exp\left( \frac{ (x-w)^2 }{ 2 \epsilon_r^2 \theta (\epsilon_r^2 + 1/\theta) } \right)
++ 1 .
+\end{align}
+
+If we define $f(u)$ so that $f(1/\theta) = H_\theta(x, w)$,
+then notice since $f(0) = 0$,
+that $\theta f(1/\theta) = f'(u)$ for some $0 \le u \le 1/\theta$,
+by the intermediate value theorem.
+Let's work out what $f'(u)$ is.
+First note that if
+\begin{align}
+    g(u)
+    &=
+    \left( \frac{ 1 }{ 1 + a u } \right)^{d/2}
+    \exp\left(
+    \frac{
+    b u
+    }{
+    1 + c u
+    }
+    \right)
+\end{align}
+then
+\begin{align}
+    g'(u)
+    &=
+\left\{
+    \frac{ - ad/2 }{ 1 + a u }
+    +
+    \frac{b}{1 + cu}
+    -
+    \frac{bcu}{(1+cu)^2}
+\right\}
+    \left( \frac{ 1 }{ 1 + a u } \right)^{d/2}
+    \exp\left(
+    \frac{
+    b u
+    }{
+    1 + c u
+    }
+    \right) \\
+    &=
+\left\{
+    \frac{ - ad/2 }{ 1 + a u }
+    +
+    \frac{b}{(1 + cu)^2}
+\right\}
+    \left( \frac{ 1 }{ 1 + a u } \right)^{d/2}
+    \exp\left(
+    \frac{
+    b u
+    }{
+    1 + c u
+    }
+    \right) .
+\end{align}
+If, as will be the case, all of $a$, $b$, $c$, and $u$ are nonnegative, then
+\begin{align}
+|g'(u)|
+&\le
+ (b + ad/2) \exp(bu) .   
+\end{align}
+Now, note that $f'(u) = g_1'(u) - 2 g_2'(u)$, where $g_1$ and $g_2$ are of this form
+with constants $a_1, b_1, c_1$ and $a_2, b_2, c_2$ respectively.
+
+Again, we'd like to show that for some $C$,
+\begin{align}
+    \theta H_\theta(x, w) \rho_r(x-w) \le C \rho_\gamma(x-w)  .
+\end{align}
+We will have $\rho_\gamma = p_{\epsilon_\gamma^2}$ with $\epsilon_\gamma > \epsilon_r$,
+so that $\rho_r(x-w) / \rho_\gamma(x-w) = C' \exp(-A (x-w)^2 / 2)$
+with $A = \frac{1}{\epsilon_r^2} - \frac{1}{\epsilon_\gamma^2}$.
+Putting this together,
+we will have shown \eqref{eqn:goal2}
+if we can show for some $\theta$ that
+for all $x$ and $w$ and all $u \le 1/\theta$,
+\begin{align} \label{eqn:goal3}
+    f'(u) \exp\left(-A (x-w)^2 \right) \le C .
+\end{align}
+Since $f'(u) = g_1'(u) - 2 g_2'(u)$ we need only prove this bound
+for both $g_1'(u)$ and $g_2'(u)$.
+Referring to \eqref{eqn:H_form}
+we see that $b_1 = 2(x-w)^2 / \epsilon_r^4$
+and that $a$ and $c$ only depend on $\epsilon_r$,
+\begin{align}
+|g_1'(u)|
+&\le
+\left\{
+    C_1 + C_2 (x-w)^2
+\right\}
+\exp\left(
+    \frac{ 2 (x - w)^2 }{ \epsilon_r^4 } u
+\right)  \\
+&\le
+\left\{
+    C_1 + C_2 (x-w)^2
+\right\}
+\exp\left(
+    \frac{ 2 (x - w)^2 }{ \epsilon_r^4 \theta }
+\right) 
+\end{align}
+where $C_1$ and $C_2$ are constants that just depend on $\epsilon_r$.
+Therefore, equation \eqref{eqn:goal3} is satisfied
+if the multiplier of $(x-w)^2$ in the last equation is less than $A$,
+i.e., if
+\begin{align}
+\theta 
+> 
+\frac{ 4 }{ A \epsilon_r^4 }
+=
+\frac{ 4 / \epsilon_r^2 }{1 - \epsilon_r^2 / \epsilon_\gamma^2 } .
+\end{align}
+This is possible if $\epsilon_r < \epsilon_\gamma$.
+
 \bibliographystyle{plainnat}

### 2022-04-07 forwards-and-backwards.tex
Update on Overleaf.

@@
 
-\comment{TODO: short lead-in}
-
 % % % % % % % % % % % % % % % % % %
@@
     \label{sec:population_heuristics}
+
+\comment{TODO: short lead-in}
 
@@
 
-% % % % % % % 
 \subsubsection*{Mean measure}
 
-Consider first the mean measure.
-The birth rate at location $x$ when the state of the population is $\eta$
-is a function of the location and the measure $\eta$ through a specific form:
-$\gamma(x, \smooth{\gamma} \eta(x))$;
-however, for the moment we will write $\gamma(x, \eta)$ instead
-to make the exposition clearer
-(and similarly for establishment probability $r(x, \eta)$ and death rate $\mu(x, \eta)$).
-Recall that in our parameterization only $\mu$ and the dispersal kernel $q$ depend on $\theta$.
-For a suitable (smooth, compactly supported) test function $f$, we find
-\begin{equation} \label{mean measure}
-    \begin{split}
-    \Pgen^\theta \langle f, \eta \rangle
-    &=
-    \lim_{\delta t\downarrow 0} \frac{1}{\delta t}
-    \IE\left[ \left.
-        \langle f, \eta_{\delta t} \rangle
-        -
-        \langle f, \eta\rangle
-        \right| \eta_0 = \eta
-    \right]
-    \\
-    &=
-    \theta \int
-        \int f(z) r(z,\eta) q_\theta(x,dz)
-    \gamma(x, \eta) \eta(dx)
-    -
-    \theta \int f(x)\mu_\theta(x, \eta)
-    \eta(dx).
-    \end{split}
-\end{equation}
+Consider first the mean measure. For a suitable 
+(smooth, compactly supported) test function $f$, we find
+\begin{multline}
+\label{mean measure}
+{\cal L}^{(\theta, N)}\langle f,\eta\rangle=
+\lim_{\delta t\downarrow 0}\frac{1}{\delta t}
+\IE\left[\left.\langle f,\eta_{\delta t}\rangle -
+\langle f, \eta\rangle \right|\eta_0=\eta
+\right]\\
+=\theta\int\int f(z)r(z,\eta)q_\theta(x,dz)
+\gamma(x,\eta)
+\eta^{\theta}_s(dx)-\theta\int f(x)\mu(x,\eta)
+\eta^{\theta}_s(dx).
+\end{multline}
 The first term is the increment in $\langle f,\eta\rangle$
@@
 and the second reflects death events.
-In both terms,
-the rate of events has a factor of $N$ (because events happen at a rate 
-proportional to the number of individuals,
-whereas $\eta$ has mass $1/N$ for each individual)
-which is offset by the fact that  
+In both terms, the 
+rate of events has a factor of $N$ (because events happen at a rate 
+proportional to the number of individuals, whereas $\eta$ is
+the scaled population mass) which is offset by the fact that  
 the birth or loss of a single 
@@
 as 
-\begin{equation}
-\label{eqn:rewritten mean measure}
-\begin{split}
-    \int\left(
-        \int \theta \left( f(z) r(z,\eta)- f(x) r(x,\eta) \right) q_\theta(x,dz)
-    \right)
+\begin{multline}
+\label{rewritten mean measure}
+\int\left(\int \theta \left(
+f(z)r(z,\eta)- f(x)r(x,\eta)\right)
+q_\theta(x,dz)\right)
 \gamma(x,\eta)
-    \eta(dx)
+\eta^{\theta}_s(dx)
 \\
-    + \int \int f(x) \theta \Big(
-        r(x,\eta) \gamma(x,\eta)
-        - \mu_\theta(x,\eta)
-    \Big) \eta(dx).
-\end{split}
-\end{equation}
-We have defined $\mu_\theta$ so that the second term is simple:
-\begin{align*}
-    \theta \Big( r(x,\eta) \gamma(x,\eta) - \mu_\theta(x,\eta) \Big)
-    = F(x, \eta) .
-\end{align*}
-This definition --
-is really a `near-critical' assumption that birth and death rates
-differ by something of order $1/\theta$.
-Furthermore, since we've taken $q_\theta$ to be the density of a Normal
-with mean and variance proportional to $1/\theta$,
-\begin{align} \label{eqn:near_critical}
-    \int \theta \Big(
-        r(z,\eta) f(z)
-        -
-        r(x,\eta) f(x)
-    \Big) q_\theta(x,dz) 
-    \qquad \stackrel{\theta\to\infty}{\longrightarrow} \qquad  
-    \DG \big(r(\cdot,\Xi)f(\cdot)\big)(x),
-\end{align}
-where recall if dispersal is simply standard multivariate Gaussian
-with mean zero and covariance $\sigma^2 I / \theta$,
-then $\DG = \sigma^2 \Delta$, where $\Delta$ denotes the Laplacian.
-Note that there is a slight mismatch between the locations at which we are 
-measuring birth and death rates, because in~\eqref{eqn:near_critical}
++\int\theta\int f(x)\Big(r(x,\eta)
+\gamma(x,\eta)
+-\mu(x,\eta)\Big)
+\eta^{\theta}_s(dx).
+\end{multline}
+Suppose that $\eta\to\Xi$, a measure on $\IR^d$,
+in the scaling limit, then we see that we can 
+let $\theta\rightarrow\infty$ in~(\ref{rewritten mean measure})
+under the assumptions that
+\begin{eqnarray}
+r(x,\eta)&\stackrel{\theta\to\infty}{\longrightarrow}&
+r(x,\Xi)\\
+\gamma(x,\eta)&\stackrel{\theta\to\infty}{\longrightarrow}&
+\gamma(x,\Xi)\\
+\int\theta \Big(r(z,\eta)f(z)-
+r(x,\eta)f(x)\Big)q_\theta(x,dz) 
+&\stackrel{\theta\to\infty}{\longrightarrow}& 
+\Delta \big(r(\cdot,\Xi)f(\cdot)\big)(x);\\
+\theta \Big(r(x,\eta)\gamma (x,\eta)
+-\mu (x,\eta)\Big)
+ &\stackrel{\theta\to\infty}{\longrightarrow}& 
+F(x,\Xi),
+\label{near critical}
+\end{eqnarray}
+where $\Delta$ denotes the Laplacian.
+The last condition reflects the `near-critical' branching. Note that
+there is a slight mismatch between the locations at which we are 
+measuring birth and death rates, because in~(\ref{near critical})
 the establishment probability is 
 measured at $x$ rather than at the point where juveniles fall. 
-\comment{(IS THIS BIT STILL TRUE:)}
 This condition also differs from the assumption that
@@
 
-Equation~\eqref{eqn:rewritten mean measure}) then converges to
-\begin{equation} \label{limit of mean measure equation}
-\int \gamma(x,\eta)
-\DG \big(f(\cdot)r(\cdot,\eta)\big)(x)
-\eta(dx)
-+
-\int f(x)
-F(x,\eta)
-\eta(dx) .
-\end{equation}
-More generally, we expect everything to work
-if the remaining parameters ($r$, $\gamma$, and $F$)
-depended on $\theta$, but converged as $\theta \to \infty$.
-
-% % % % % % % 
+Equation~(\ref{rewritten mean measure}) converges to
+\begin{equation}%\begin{multline}
+\label{limit of mean measure equation}
+\int \gamma(x,\Xi)
+\Delta
+\big(f(\cdot)r(\cdot,\Xi)\big)(x)
+\Xi(dx)
++\int f(x)
+F(x,\Xi)
+\Xi(dx)
+.
+\end{equation}
+
 \subsubsection*{Quadratic variation}
 
-% Note: this bit in firstversionplus.tex has things written out in detail for
-% the Poisson offspring number case.
-
 We now look at the second order term.
-An individual at location $x$ gives birth 
-to a surviving offspring at $y$ at rate
+We spell out
+this calculation in detail so that it is evident at which points we are 
+exploiting the choice of the Poisson distribution for the number
+of juvenile offspring.
+In the general case one can expect somewhat messier calculations, but
+the same conclusion (up to constants).
+
+When an individual at the point $x$ gives birth, the total number of
+mature offspring is Poisson with parameter
+$$\gamma(x,\eta)\int 
+r(y,\eta) q_{\theta}(x, dy)
+=\gamma(x,\eta)p_\theta(x,\eta).$$
+Offspring that survive to maturity are distributed about the parent
+according to 
+$$\overline{q}_\theta(x,\eta,dy):=
+\frac{r(y,\eta)q_\theta(x,dy)} 
+{\int r(z,\eta)q_\theta(x,dz)}. 
 $$
-\gamma(x,\eta) r(y,\eta) q_{\theta}(x, dy) ,
-$$
-and since this increments $\langle f, \eta \rangle$ by $f(y) / N$,
-the contribution to the quadratic variation from birth events,
-which occur at rate $\theta$ per individual 
-(so, rate $N\theta |\eta|$ overall), is
-$$
-\langle
-    N \theta \gamma(x,\eta)
-    \int \frac{1}{N^2} f^2(y) r(y,\eta)
+Writing $X(x)$ for the increment to $\langle f, \eta\rangle$
+due to a single mature offspring of an individual at $x$, 
+and $P(x)$ for the (Poisson) number of mature
+offspring in such an event, the variance of the increment to 
+$\langle f, \eta\rangle$
+resulting from a birth event at $x$ is $\IE[P(x)]\mathtt{var}(X(x))
++\mathtt{var}(P(x))\IE[X(x)]^2=\IE[P]\IE[X(x)^2]$. 
+Since, in this notation, conditional on the value of $\eta$
+immediately before the event,
+$$\IE[X(x)^2]=\int
+\frac{1}{N^2}f^2(y) \overline{q}_\theta(x,\eta,dy),$$
+and
+$$\IE[P(x)]=
+\gamma (x,\eta) \int 
+r(z,\eta)q_\theta(x,dz),$$ 
+the contribution to the quadratic variation from birth events, which
+occur at rate $\theta$ per individual 
+(so $N\theta |\eta|$ overall), is
+$$\langle N\theta \gamma(x,\eta)
+\int \frac{1}{N^2}f^2(y)r(y,\eta)
 q_\theta(x,dy) 
-    , \eta(dx)
-\rangle .
-$$
-Similarly, the increment in $\langle f, \eta\rangle$ resulting from 
-the death of an individual at $x$ is $f(x)/N$, and so combining with the 
+,\eta^{\theta}_s(dx)\rangle.$$
+The increment in $\langle f, \eta\rangle$ resulting from 
+the death of an individual at $x$ is $f(x)/N^2$, and so combining with the 
 above, the second order term in the generator takes the form
-$$
-F''(\langle f,\eta\rangle)
-\frac{1}{2} N \theta
-\left\{
-    \langle
-        \gamma(x,\eta)
+$$F''(\langle f,\eta\rangle)
+\frac{1}{2}N\theta \left\{
+\langle \gamma(x,\eta)
 \int \frac{1}{N^2}f^2(y)r(y,\eta)q_\theta(x,dy) 
-    , \eta(dx)\rangle
-    +
-    \langle
-        \mu_\theta(x,\eta)\frac{1}{N^2}f^2(x) 
-    ,\eta(dx)\rangle
-\right\} .
+,\eta^{\theta}_s(dx)\rangle
++\langle \mu(x,\eta)\frac{1}{N^2}f^2(x) 
+,\eta^{\theta}_s(dx)\rangle\right\}.
 $$
 The term $\varepsilon_{\theta,N}(f, F, \eta)$ will be 
-$\bigO(\theta/N^2)$.
-
-% % % % % % % %
+${\mathcal O}(\theta/N^2)$.
+
 \subsubsection*{Limit I: deterministic case}
-
-\comment{Need to decide what to call the limit here (and above, I guess).}
 
@@
 by parts, we find that in the limit as $N\to\infty$,
-\begin{equation*}
+\begin{equation}
+\nonumber
 \frac{d}{dt}\int f(x)\Xi_t(x)dx
-=
-\int f(x)\left\{r(x,\Xi_t)\DG\big(\gamma(\cdot,\Xi_t)
-\Xi_t(\cdot)\big)(x)
-+
-F(x,\Xi_t) \Xi_t(x)
-\right\} dx.
-\end{equation*}
+=\int f(x)\left\{r(x,\Xi_t)\Delta\big(\gamma(\cdot,\Xi_t)
+\Xi_t(\cdot)\big)(x)+F(x,\Xi_t)
+\Xi_t(x)
+\right\}dx.
+\end{equation}
 In other words, we can expect the limit to be a weak solution to the 
@@
 \frac{d\Xi}{dt}
-=r(x,\Xi)\DG\big(\gamma(\cdot,\Xi)
+=r(x,\Xi)\Delta\big(\gamma(\cdot,\Xi)
 \Xi(\cdot)\big)(x)+F(x,\Xi)
@@
 
-If $N=\delta\theta$, for some positive constant $\delta$,
+If $N=\rho\theta$, for some constant $\rho$,
 the second order term in the generator remains order
 one as $\theta\to\infty$, and  
-we expect a `generalised superprocess' limit.
-Assuming some regularity of the coefficients (in particular of $r$), 
-the second order term in the generator will take the form
-$$
-\frac{1}{\delta}F''(\langle f,\Xi\rangle)
+we expect a `generalised
+superprocess'
+limit. Assuming some regularity of the coefficients (in particular 
+of $r$), 
+the second order term in the generator will  
+take the form
+$$\frac{1}{\rho}F''(\langle f,\Xi\rangle)
 \langle f^2(x), \gamma(x,\Xi)
@@
 $$\langle f(x), \Xi_t(dx)\rangle-\langle f(x), \Xi_0(dx)\rangle
--\int_0^t\langle\gamma(x,\Xi_s)\DG\big(r(\cdot,\Xi_s)f(\cdot)\big)(x),
+-\int_0^t\langle\gamma(x,\Xi_s)\Delta\big(r(\cdot,\Xi_s)f(\cdot)\big)(x),
 \Xi_s(dx)\rangle ds$$
 is a martingale with quadratic variation
-$$\frac{2}{\delta}\int_0^t\langle f^2(x) 
+$$\frac{2}{\rho}\int_0^t\langle f^2(x) 
 \gamma(x,\Xi_s)r(x,\Xi_s),\Xi_s(dx)\rangle ds.$$
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newpage
 \section{Technical Lemmas}

### 2022-04-07 forwards-and-backwards.tex
Update on Overleaf.

--- 2022-04-07 forwards-and-backwards.tex
@@
 \newtheorem{definition}[theorem]{Definition}
+\newtheorem{notation}[theorem]{Notation}
 
@@
 \newcommand{\grad}{\nabla}
+\newcommand{\dif}{\mathrm{d}\,}
 
@@
 \begin{aligned}
-&     M^{\theta}_t(f)\\
-:=&  \langle f,\eta^{\theta}_t \rangle
-        -\langle f,\eta^{\theta}_0 \rangle\\
- &-  \int_{0}^{t}\bigg\{   \int\left(   \int \theta
+M^{\theta}_t(f)
+&:=  \langle f,\eta^{\theta}_t \rangle
+        -\langle f,\eta^{\theta}_0 \rangle
+ \\ &\qquad {}
+ -  \int_{0}^{t}\bigg\{
+        \int\left(   \int \theta
      \left(
@@
                     q_\theta(x,dz)\right)
+        \\ & \qquad \qquad \qquad \qquad {} \times
                             \gamma\big(x,\varrho_{\gamma}*\eta^{\theta}_{s}(x)\big)
-                            \eta^{\theta}_{s}(dx)\\
-& \qquad +\int 
+                            \eta^{\theta}_{s}(dx)
+     \\ & \qquad {} +\int 
      f(x)F\big(x,\varrho_{F}*\eta^{\theta}_{s}(x)\big)
-\eta^{\theta}_{s}(dx)\bigg\} ds
+     \eta^{\theta}_{s}(dx)
+    \bigg\} ds
 \end{aligned}    
@@
 \begin{equation}
-\begin{aligned}
+\begin{aligned} \relax
 [ M^{\theta}_t(f)] =& 
@@
 % % % % % % % % % % % % % % % %
-\subsection*{Lookdown Representation and Notation}
+\subsection{Lookdown Representation and Notation}
 \label{sec: Lookdown Representation and Notation}
@@
 $$b_{\theta}(x, \eta):=~ \theta \bigg\{ \gamma(x, \varrho_{\gamma}*\eta(x)) \int r(y, \varrho_{r}*\eta(y))q_{\theta}(x,dy)-\mu(x, \eta)\bigg\};$$
-and the dispersal kernel $q^{\mathfrak{m}}(x,dy)$ is 
+and the dispersal kernel $q^{\mathfrak{m}}(x,\eta, dy)$ is 
 $$q^{\mathfrak{m}}_{\theta}(x,\eta,dy) 
@@
 As a result, we use the same notation $\eta$
-to denote these two identically distributed processes
-which take values in the space of empirical measures.
+to denote these two identically distributed processes.
 On the other hand,
@@
 is equivalent to convergence of
-$(\eta^{\varepsilon, \theta, N}_t)_{t \geq 0}$ to $(\Xi_t)_{t \geq 0}$.
+$(\eta^{\theta}_t)_{t \geq 0}$ to $(\Xi_t)_{t \geq 0}$.
 As a result, it suffices for us to focus on
 tightness of $(\eta^{\theta}_t)_{t \geq 0}$
-and spatial convergence of $(\eta^{\varepsilon, \theta, N}_t)_{t \geq 0}$
+and spatial convergence of $(\eta^{\theta}_t)_{t \geq 0}$
 as $\theta \to \infty$.
@@
 
-Here we give a general framework of tracking evolution of individual particles in the population described above.
-We will provide the right scaling of the coefficients introduced in \S \ref{sec: Convergence of Spatial-Level Models}.\\
-Particles alive at time zero will be indexed by
-$(0, i)$, or more precisely, we index the levels of the particles alive at time $0$ by $(0, i)$ keeping
-in mind that at each birth event, the parent particle will, with probability $1/2$ change levels.
-Since no two particles born after time $0$ will be born at the same time, we index the rest of
-the levels by their birth times. With each level, we can associate a Poisson random measure
-$\xi$ on $[0, \infty)^2\times [0,1]\times \{0,1\}$ (eventually, $\lambda \to \infty$) with mean measure $l^3 \times \{\frac{1}{2}\delta_0,\frac{1}{2}\delta_1\}$ which
+Here we give a general framework of tracking evolution
+of individual particles in the spatial-level population $\xi(t)_{t \geq 0}$ defined in \S \ref{sec: Lookdown Representation and Notation}.
+
+Particles alive at time zero will be indexed by $(0, i)$,
+or more precisely,
+we index the levels of the particles
+alive at time $0$ by $(0, i)$,
+keeping in mind that at each birth event,
+the parent particle will,
+with probability $1/2$, change levels.
+Since no two particles born after time $0$
+will be born at the same time,
+we index the rest of the levels by their birth times.
+
+With each level,
+we can associate a Poisson random measure
+$\Tilde{\Pi}$ on $[0, \infty)^2\times [0,1]\times \{0,1\}$ (eventually, $\lambda \to \infty$) with mean measure $l^3 \times \{\frac{1}{2}\delta_0,\frac{1}{2}\delta_1\}$ which
 determines the birth times of the offspring of the particle at that level, the location of the
@@
 \begin{proof}
-See Appendix.    
+See Appendix \ref{sec: Proof to gamma-r radius comparison}.    
 \end{proof}
@@
 In this section we prove Proposition~\ref{prop:nonlocal_pde_limits}.
+
+\subsubsection{Porous Media Equation}
+
+\plr{This is from pme.tex.}
+
+We are concerned with non-negative solutions to the equation
+\begin{equation}
+\label{mollified equation}
+\frac{\partial u^\epsilon}{\partial t}=
+%\frac{\partial^2}{\partial x^2}
+\Delta\left(u^\epsilon \cdot u^\epsilon *\zeta_\epsilon\right)
++u^\epsilon\left(1-u^\epsilon*\zeta_\epsilon\right);
+\end{equation}
+where $*$ denotes convolution and we define
+a (non-negative) mollifier by
+$\zeta_\epsilon=\frac{1}{\epsilon}\zeta(\cdot/\epsilon)$, where $\zeta$
+satisfies
+$\zeta\in\cal{S}(\IR)$, $\int\zeta(x)dx=1$. Indeed, for convenience, in
+what follows we shall suppose that $\zeta =\rho*\check{\rho}$ where
+$\check{\rho}(z)=\rho(-z)$ and $\rho$ has
+compact support, although that
+is certainly stronger than we need.
+In particular, we should like to prove that as $\epsilon\to 0$ we have
+convergence to the solution to the porous medium equation with
+logistic growth:
+\begin{equation}
+\label{PME}
+\frac{\partial u}{\partial t}=
+%\frac{\partial^2}{\partial x^2}
+\Delta\left(u^2\right)
++u\left(1-u\right).
+\end{equation}
+
+We work on $[0,T]\times \IT_K$ where $\IT_K$ is the one-dimensional
+torus of size $K$, and $T,K>0$ are fixed but arbitrary.
+
+\begin{remark}
+By taking a sequence $K_n\to\infty$, and doing a bit of work,
+we can presumably then recover the result
+we need for, e.g., a population expanding its range from a compact
+set containing the origin (for which we know the solution to the PME
+converges to two travelling waves, travelling in opposite directions
+\cite{kamin/rosenau:2004}). Such waves have bounded support, even when
+we consider the equation on
+the whole real line, and travel at a fixed speed, so don't feel the boundedness
+of the torus,
+so this should be straightforward. The challenge will be to control the
+mass of the approximating functions that falls beyond that wavefront,
+since they themselves will have full support and so arguably `feel' that they
+are on the torus.
+It is not clear that it is worth doing the details for this paper - this is
+meant as an example.
+\end{remark}
+
+\begin{notation}
+
+Whenever we integrate with respect to $x$, this is implicitly over the
+whole torus $\IT_K$.
+
+We use $\rightharpoonup$ to denote weak convergence in the sense of analysts;
+that is, $u^\epsilon\rightharpoonup u$ in $L^1$ means $\int u^\epsilon v \dif x
+\rightarrow\int uv\dif x$ for all $v\in L^\infty$.
+
+We write $L_t^2(H^1)$ for functions for which the $H^1$ norm in
+space is in $L^2$ with respect to time, i.e.
+$$\int_0^T\int \left\{u(t,x)^2+\left(\frac{d}{dx} u(t,x)\right)^2\right\} \dif x \dif t <\infty,$$
+and $C_t(L^1)$
+will denote functions for which the $L^1$ norm in space is continuous in time.
+\end{notation}
+
+\begin{proposition}
+Suppose that $u_0^\epsilon\in L^1(\IT_K)$, $u_0^\epsilon\geq 0$, and
+$\sup_\epsilon\int u_0^\epsilon|\log u_0^\epsilon|dx<\infty$ with
+$u_0^\epsilon\rightharpoonup u_0^\epsilon$ as $\epsilon\to 0$. Then
+writing $u^\epsilon$ for the solution to~(\ref{mollified equation})
+on $[0,T]\times \IT_K$ with
+initial condition $u_0^\epsilon$,
+$u^\epsilon\rightharpoonup u$ as $\epsilon\to 0$ where
+$u\in L_t^2(H^1)\cap C_t(L^1)$, $\int u|\log u| dx<\infty$, and
+$u$ solves~(\ref{PME}) on $[0,T]\times \IT_K$. Moreover, strong convergence
+of the initial conditions implies strong convergence of the solutions.
+\end{proposition}
+%\noindent
+%{\bf Proof}
+\begin{proof}
+
+Our proof owes a lot to~\cite{lions/mas-gallic:2001}.
+First observe that
+\begin{multline*}
+\int u^\epsilon\cdot u^\epsilon*\zeta_\epsilon\dif x
+= \int\int\int u^\epsilon(x)u^\epsilon(x-y)\rho_\epsilon(y-z)
+\check{\rho}_\epsilon(z)\dif z\dif y\dif x
+\\
+=
+\int\int\int u^\epsilon(\tilde{x}-\tilde{z})
+u^\epsilon(\tilde{x}-\tilde{y})
+\rho_\epsilon(\tilde{y})
+\rho_\epsilon(\tilde{z})\dif \tilde{z}\dif \tilde{y}\dif \tilde{x}
+=\int\left(u^\epsilon*\rho_\epsilon\right(x))^2\dif x,
+\end{multline*}
+where we have set $\tilde{x}=x-z$, $\tilde{y}=y-z$, $\tilde{z}=-z$.
+
+Now note that
+$$\frac{d}{dt}\int u^\epsilon (t,x) \dif x=\int \Delta (u^\epsilon*\zeta_\epsilon)\dif x
++\int u^\epsilon(1-u^\epsilon*\zeta_\epsilon)\dif x= \int u^\epsilon \dif x
+-\int (u^\epsilon*\rho)^2 \dif x.$$
+Thus $\int u^\epsilon(t,x)\dif x$ is uniformly bounded above in $t$
+and $\epsilon$ on $[0,T]$. Note that this also then gives a uniform
+bound on the rate of change of $\int u^\epsilon (t,x) \dif x$, and since
+we are working on $[0,T]$ this will be enough to give continuity in time of the
+$L^1$ norm of the limit
+when we pass to a convergent subsequence.
+
+Now consider
+\begin{eqnarray*}
+\frac{d}{dt}\int u^\epsilon\log u^\epsilon \dif x &=&
+\int (1+\log u^\epsilon)\left[\Delta (u^\epsilon\cdot
+u^\epsilon*\zeta_\epsilon)+u^\epsilon(1-u^\epsilon*\zeta_\epsilon)\right]
+\dif x
+\\
+&=&
+\int (1+\log u^\epsilon)\left[\nabla\left(u^\epsilon\cdot
+\nabla(u^\epsilon*\zeta_\epsilon)+
+\nabla u^\epsilon\cdot u^\epsilon*\zeta_\epsilon\right)
++u^\epsilon(1-u^\epsilon*\zeta_\epsilon)\right] \dif x
+\\
+&=&
+\int \left[-\frac{\nabla u^\epsilon}{u^\epsilon}
+\left(u^\epsilon\cdot \nabla(u^\epsilon*\zeta_\epsilon)
++\nabla u^\epsilon\cdot u^\epsilon*\zeta_\epsilon\right)+
+(1+\log u^\epsilon)u^\epsilon(1-u^\epsilon*\zeta_\epsilon)\right]\dif x
+\\
+&=&
+-\int \left(\nabla (u^\epsilon*\rho_\epsilon)\right)^2 \dif x
+-\int (\nabla u^\epsilon)^2\frac{u^\epsilon*\zeta_\epsilon}{u^\epsilon} \dif x
+\\
+&&+\int
+\left[u^\epsilon+u^\epsilon\log u^\epsilon(1-u^\epsilon*\zeta_\epsilon)
+-u^\epsilon\cdot u^\epsilon*\zeta_\epsilon\right]\dif x\\
+&=&
+-\int \left(\nabla (u^\epsilon*\rho_\epsilon)\right)^2 \dif x
+-\int (\nabla u^\epsilon)^2\frac{u^\epsilon*\zeta_\epsilon}{u^\epsilon} \dif x
+-\int (u^\epsilon*\rho_\epsilon)^2\dif x
+\\
+&&+\int
+\left[u^\epsilon+u^\epsilon\log u^\epsilon(1-u^\epsilon*\zeta_\epsilon)
+%-u^\epsilon\cdot u^\epsilon*\zeta_\epsilon
+\right]\dif x .
+\end{eqnarray*}
+The first three terms are negative; and we already
+saw that the $L^1$ norm
+of $u^\epsilon$ is uniformly bounded.
+Moreover, since $u^\epsilon\log u^\epsilon$ is uniformly bounded below,
+$$-\int u^\epsilon \log u^\epsilon \cdot u^\epsilon*\zeta_\epsilon \dif x
+\leq C\int u^\epsilon*\zeta_\epsilon \dif x=\int u^\epsilon \dif x.$$
+From this we see immediately that $\int u^\epsilon \log u^\epsilon \dif x$
+is uniformly bounded
+above in $\epsilon$ and $t\in [0,T]$. Moreover,
+since we are working on the bounded space $\IT_K$, the lower bound
+on $u^\epsilon\log u^\epsilon$ also allows us to
+bound $\int u^\epsilon\log u^\epsilon \dif x$ uniformly
+below, from which we deduce that
+we have a uniform bound on $\int u^\epsilon|\log u^\epsilon| \dif x$.
+This in turn means that both
+$\int_0^t (u^\epsilon*\rho_\epsilon)^2 \dif x$ and
+$\int_0^t \big(\nabla (u^\epsilon*\rho_\epsilon)\big)^2 \dif x$
+are uniformly bounded in
+$\epsilon$ and $t\in [0,T]$.
+Now observe that
+\begin{equation}
+\label{total equation}
+\int\Delta\left((u^\epsilon*\zeta_\epsilon)u^\epsilon\right)\phi \dif x =
+\int \nabla(u^\epsilon*\zeta_\epsilon)\cdot
+u^\epsilon\cdot\nabla\phi \dif x +\int u^\epsilon*\zeta_\epsilon
+\cdot\nabla u^\epsilon
+\cdot \nabla\phi \dif x.
+\end{equation}
+For the first term
+\begin{eqnarray}
+\nonumber
+\int \nabla(u^\epsilon*\zeta_\epsilon)\cdot u^\epsilon\cdot\nabla\phi \dif x
+&=&
+\int\int\int\nabla u^\epsilon(x-y)\rho_\epsilon(y-z)\check{\rho}_\epsilon(z)
+u^\epsilon(x)\nabla\phi(x)\dif z \dif y \dif x
+\\
+\nonumber
+&=&
+\int\int\int\nabla u^\epsilon(\tilde{x}-\tilde{y})\rho_\epsilon(\tilde{y})
+\rho_\epsilon(\tilde{z})u^\epsilon(\tilde{x}-\tilde{z})
+\nabla\phi(\tilde{x}-\tilde{z})\dif \tilde{z}\dif \tilde{y} \dif \tilde{x}
+\\
+\nonumber
+&=&\int(\nabla u^\epsilon*\rho_\epsilon)\cdot
+\left((u^\epsilon\nabla\phi)*\rho_\epsilon\right)
+\dif x\\
+\nonumber
+&=&
+\frac{1}{2}\int\nabla ((u^\epsilon*\rho_\epsilon)^2)\cdot\nabla\phi \dif x
+\\
+\label{error 1}
+&&+
+\int\nabla(u^\epsilon*\rho_\epsilon)
+\left[(u^\epsilon\cdot\nabla\phi)*\rho_\epsilon-
+\nabla\phi\cdot((u^\epsilon*\rho_\epsilon)\right]\dif x,
+\end{eqnarray}
+where, as before, we have substituted $\tilde{x}=x-z$, $\tilde{y}=y-z$,
+$\tilde{z}=-z$.
+
+To control the term~(\ref{error 1})
+we use the Intermediate Value Theorem to see that
+\begin{multline*}
+\left|\int\left[u^\epsilon(x-y)\nabla\phi(x-y)\rho_\epsilon(y)-
+\nabla\phi(x)u^\epsilon(x-y)\rho_\epsilon(y)
+\right]\dif y\right|
+\\
+\leq C\|\Delta\phi\|_\infty\int u^\epsilon (x-y)\rho_\epsilon(y)y\dif y.
+\end{multline*}
+Since we chose $\rho$ to have compact support,
+$y\rho_\epsilon(y)\leq C\epsilon\rho_\epsilon(y)$
+in the last integral and so the expression~(\ref{error 1}) is
+$\mathcal{O}(\epsilon)$.
+
+Similarly, for the second term in~(\ref{total equation}),
+\begin{eqnarray}
+\nonumber
+\int (u^\epsilon*\zeta_\epsilon)\cdot \nabla u^\epsilon\cdot\nabla\phi \dif x
+&=&
+\int\int\int u^\epsilon(x-y)\rho_\epsilon(y-z)
+\check{\rho}_\epsilon(z)\nabla u^\epsilon(x)\nabla\phi(x)\dif z \dif y \dif x
+\\
+\nonumber
+&=&
+\int\int\int u^\epsilon(\tilde{x}-\tilde{y})\rho_\epsilon(\tilde{y})
+\rho_\epsilon(\tilde{z})\nabla u^\epsilon(\tilde{x}-\tilde{z})
+\nabla\phi(\tilde{x}-\tilde{z})\dif \tilde{z}\dif \tilde{y} \dif\tilde{x}
+\\
+\nonumber
+&=&\int(u^\epsilon*\rho_\epsilon)\cdot
+\left((\nabla u^\epsilon\nabla\phi)*\rho_\epsilon\right) \dif x\\
+\nonumber
+&=&
+\frac{1}{2}\int\nabla ((u^\epsilon*\rho_\epsilon)^2)\cdot\nabla\phi \dif x
+\\
+\label{error 2}
+&&+
+\int (u^\epsilon*\rho_\epsilon)
+\left[(\nabla u^\epsilon\cdot\nabla\phi)*\rho_\epsilon-
+\nabla\phi\cdot((\nabla u^\epsilon*\rho_\epsilon)\right]\dif x,
+\end{eqnarray}
+and~(\ref{error 2}) is controlled in the same way as~(\ref{error 1})
+using the Intermediate Value Theorem:
+\begin{multline*}
+\left|\int\left[\nabla u^\epsilon(x-y)\nabla\phi(x-y)\rho_\epsilon(y)
+-\nabla\phi(x)\nabla u^\epsilon(x-y)\rho_\epsilon(y)
+\right]\dif y\right|
+\\
+\leq C\|\Delta\phi\|_\infty\left|\int \nabla u^\epsilon(x-y)\rho_\epsilon(y)y
+\dif y\right|\\
+\leq C'\|\Delta\phi\|_\infty\epsilon \int\left|
+\nabla u^\epsilon(x-y)\rho_\epsilon(y)
+\right|\dif y.
+\end{multline*}
+
+We now have the ingredients that we need.
+The calculations above yield both a uniform (in $\epsilon$) bound on
+$u^\epsilon*\rho_\epsilon$ in
+$L^1\cap L^2\big([0,T]\times \IT_K\big)$, and
+\begin{multline}
+\int u^\epsilon(t,x)\phi(x)\dif x-\int u^\epsilon (0,x)\phi(x)\dif x
+=\int_0^t\int (u^\epsilon*\rho_\epsilon)^2\Delta\phi(x)\dif x
+\\
++\int_0^t \int u^\epsilon*\rho_\epsilon\left(1- u^\epsilon*\rho_\epsilon\right)
+\phi(x)\dif x
++\mathcal{O}(\epsilon)
+\end{multline}
+(for sufficiently regular $\phi$). Since
+$\int u^\epsilon(t,x)\phi(x)\dif x-
+\int (u^\epsilon*\rho_\epsilon)(t,x)\phi(x)\dif x$ is order $\epsilon$, we see
+that $u^\epsilon*\rho_\epsilon$ converges weakly in $L^1$ to the (unique)
+solution
+to equation~(\ref{PME})
+and, so, therefore, does $u^\epsilon$. Strong convergence, that is
+$\int |u^\epsilon -u|\phi\dif x \to 0$, follows from the
+uniform integrability of $u^\epsilon$ that we
+deduce from the uniform control of
+$\int u^\epsilon|\log u^\epsilon|\dif x$ that we proved above.
+\end{proof}
 
@@
 \begin{align}\label{Lookdown generator N lambda theta prelimit}
-A^{\theta}f(\xi)=&f(\xi)\sum_{(x,u)\in\xi}2\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi)\times
+A^{\theta}f(\xi)=&f(\xi)\sum_{(x,u)\in\xi}2\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\times
 \int_u^{
@@
 & \qquad \qquad \qquad \qquad +\int_{\mathbb{R}^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\Xi,dy)\Bigg)dv_1 \nonumber\\
-&+f(\xi )\sum_{(x,u)\in\xi}\,\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)},
+&+f(\xi )\sum_{(x,u)\in\xi}\,\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)},
 \end{align}
@@
 \begin{aligned}
-A^{\varepsilon, \theta, \lambda,1}f(\xi)=&f(\xi)\sum_{(x,u)\in\xi}2\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi)\times
+A^{\theta,1}f(\xi)=&f(\xi)\sum_{(x,u)\in\xi}2\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\times
 \int_u^{
@@
 \xi },dy)\Bigg)dv_1,\\
-A^{\varepsilon, \theta, \lambda,2}f(\xi)=&f(\xi)\sum_{(x,u)\in\xi}2\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi)\times
+A^{\theta,2}f(\xi)=&f(\xi)\sum_{(x,u)\in\xi}2\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\times
 \int_u^{
 \lambda}\Bigg(\frac{1}{2}\int_{\mathbb{R}^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\Xi,dy)\Bigg)dv_1,\\
-A^{\varepsilon, \theta, \lambda,3}f(\xi)=&f(\xi )\sum_{(x,u)\in\xi}\,\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)},
+A^{\theta,3}f(\xi)=&f(\xi )\sum_{(x,u)\in\xi}\,\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)},
 \end{aligned}
@@
 such that 
-$$A^{\theta}f(\xi)=A^{\varepsilon, \theta, \lambda,1}f(\xi)+A^{\varepsilon, \theta, \lambda,2}f(\xi)+A^{\varepsilon, \theta, \lambda,3}f(\xi).$$
+$$A^{\theta}f(\xi)=A^{\theta,1}f(\xi)+A^{\theta,2}f(\xi)+A^{\theta,3}f(\xi).$$
 We now calculate each generator evaluated under our probability kernel $\Gamma$.
@@
 \begin{align*}
-&\int A^{\varepsilon, \theta, \lambda,1}f(\xi) \Gamma(d\mathbf{u})\\ &=\int \Bigg\{f(\xi)\sum_{(x,u)\in\xi}2\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi)
+&\int A^{\theta,1}f(\xi) \Gamma(d\mathbf{u})\\ &=\int \Bigg\{f(\xi)\sum_{(x,u)\in\xi}2\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)
 \int_u^{
@@
 \xi },dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
-&=\sum_{(x,u)\in\xi} \int \Bigg\{\frac{f(\xi)}{g(x,u)}2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi)
+&=\sum_{(x,u)\in\xi} \int \Bigg\{\frac{f(\xi)}{g(x,u)}2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi)
 \int_u^{
@@
 \xi },dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
-&=\sum_{(x,u)\in\xi}\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\int_{0}^{\lambda}\left\{
+&=\sum_{(x,u)\in\xi}\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\int_{0}^{\lambda}\left\{
 \int_u^{
@@
 \xi },dy)\right\}du\\
-&=\sum_{(x,u)\in\xi}\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\int_{\mathbb{R}^d} \left\{\int_{0}^{\lambda}
+&=\sum_{(x,u)\in\xi}\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\int_{\mathbb{R}^d} \left\{\int_{0}^{\lambda}
 \int_u^{
@@
 \begin{align*}
-&\int A^{\varepsilon, \theta, \lambda,2}f(\xi) \Gamma(d\mathbf{u})\\&=\int \Bigg\{f(\xi)\sum_{(x,u)\in\xi}2\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi)\times
+&\int A^{\theta,2}f(\xi) \Gamma(d\mathbf{u})\\&=\int \Bigg\{f(\xi)\sum_{(x,u)\in\xi}2\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\times
 \int_u^{
 \lambda}\Bigg(\int_{\mathbb{R}^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\Xi,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
-&=\sum_{(x,u)\in\xi}\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi)\int \Bigg\{f(\xi)\times
+&=\sum_{(x,u)\in\xi}\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\int \Bigg\{f(\xi)\times
 \int_u^{
 \lambda}\Bigg(\int_{\mathbb{R}^d}\left(g(y,v_1)+g(x,v_1)-2\right)q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\Xi,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
-&=\sum_{(x,u)\in\xi}\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i) \frac{1}{\lambda}\int_{\mathbb{R}^d}\Bigg\{\int_{0}^{\lambda}
+&=\sum_{(x,u)\in\xi}\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i) \frac{1}{\lambda}\int_{\mathbb{R}^d}\Bigg\{\int_{0}^{\lambda}
 \int_u^{
@@
 \begin{align*}
- &\int A^{\varepsilon, \theta, \lambda,3}f(\xi)\Gamma(d\mathbf{u})\\&=\int f(\xi )\,\left(\lambda^{-1} \sum_{(x,u)\in\xi}\theta \gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)}\Gamma(d\mathbf{u}) \\
- &=\sum_{(x,u)\in\xi}\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\int_{0}^{\lambda}  \left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\partial_u g(x,u)du \\
- &=-\sum_{(x,u)\in\xi}\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\int_{0}^{\lambda}  \left(2u\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi) -b_{\theta}(x,\Xi)\right)\left(g(x,u)-1\right)du \\
- &=-\sum_{(x,u)\in\xi}\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\int_{0}^{\lambda}   2ug(x,u)du \\
- &+\sum_{(x,u)\in\xi}\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\times \lambda^2+\sum_{(x,u)\in\xi}\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)b_{\theta}(x,\Xi)(\hat{g}(x)-1) \\
+ &\int A^{\theta,3}f(\xi)\Gamma(d\mathbf{u})\\&=\int f(\xi )\,\left(\lambda^{-1} \sum_{(x,u)\in\xi}\theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)}\Gamma(d\mathbf{u}) \\
+ &=\sum_{(x,u)\in\xi}\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\int_{0}^{\lambda}  \left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\partial_u g(x,u)du \\
+ &=-\sum_{(x,u)\in\xi}\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\int_{0}^{\lambda}  \left(2u\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) -b_{\theta}(x,\Xi)\right)\left(g(x,u)-1\right)du \\
+ &=-\sum_{(x,u)\in\xi}\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\int_{0}^{\lambda}   2ug(x,u)du \\
+ &+\sum_{(x,u)\in\xi}\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\times \lambda^2+\sum_{(x,u)\in\xi}\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)b_{\theta}(x,\Xi)(\hat{g}(x)-1) \\
 \end{align*}
@@
 &\int \Bigg(A^{1}_{\theta}f(\xi)+A^{2}_{\theta}f(\xi)+A^{3}_{\theta}f(\xi)\Bigg)\Gamma(d\mathbf{u})\\
-&=  \sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi)\prod_{(x_i,u_i)}\hat{g}(x_i) \left( \int_{\mathbb{R}^n} \hat{g}(y) q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\Xi,dy) - 2+\frac{1}{\hat{g}(x)}\right)+\sum_{(x,u) \in \xi } \prod_{(x_i,u_i)}\hat{g}(x_i)b_{\theta}(x,\Xi)\left(1-\frac{1}{\hat{g}(x)}\right)\\
-&=  \hat{f}(\xi)\sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi) \left(\int_{\mathbb{R}^n} \hat{g}(y) q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\Xi,dy) -1\right)+\hat{f}(\xi)\sum_{(x,u) \in \xi } (b_{\theta}(x,\Xi)-\theta\gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\xi))\left(1-\frac{1}{\hat{g}(x)}\right)\\
-&=  \hat{f}(\xi)\sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi) \left(\int_{\mathbb{R}^n} \hat{g}(y) q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\Xi,dy) -1\right) -\hat{f}(\xi)\sum_{(x,u) \in \xi } \theta \mu_{\varepsilon,\theta}(x,\Xi)\left(1-\frac{1}{\hat{g}(x)}\right),
+&=  \sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)}\hat{g}(x_i) \left( \int_{\mathbb{R}^n} \hat{g}(y) q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\Xi,dy) - 2+\frac{1}{\hat{g}(x)}\right)+\sum_{(x,u) \in \xi } \prod_{(x_i,u_i)}\hat{g}(x_i)b_{\theta}(x,\Xi)\left(1-\frac{1}{\hat{g}(x)}\right)\\
+&=  \hat{f}(\xi)\sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi) \left(\int_{\mathbb{R}^n} \hat{g}(y) q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\Xi,dy) -1\right)+\hat{f}(\xi)\sum_{(x,u) \in \xi } (b_{\theta}(x,\Xi)-\theta\gamma^{\mathfrak{m}}_{\theta}(x,\xi))\left(1-\frac{1}{\hat{g}(x)}\right)\\
+&=  \hat{f}(\xi)\sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi) \left(\int_{\mathbb{R}^n} \hat{g}(y) q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\Xi,dy) -1\right) -\hat{f}(\xi)\sum_{(x,u) \in \xi } \theta \mu_{\varepsilon,\theta}(x,\Xi)\left(1-\frac{1}{\hat{g}(x)}\right),
 \end{align*}
-which corresponds to a spatial-branching process that branches at rate $\theta\gamma^{\mathfrak{m}}_{\varepsilon, \theta}(x,\Xi)$ leaving offspring around with kernel $ q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\Xi,dy)$ and each particle having death rate given by $\theta \mu_{\varepsilon,\theta}(x,\Xi)$.
+which corresponds to a spatial-branching process that branches at rate $\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)$ leaving offspring around with kernel $ q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\Xi,dy)$ and each particle having death rate given by $\theta \mu_{\varepsilon,\theta}(x,\Xi)$.
 This is precisely the martingale problem in Definition \ref{def: Martingale Problem Characterisation - Product Form}.
 \newpage
-\subsubsection{Markov Mapping Theorem Application on Generator $A^{\text{nl}}_{\varepsilon}$}\label{sec: Markov Mapping Theorem application - limit}
+\subsection{Markov Mapping Theorem Application on Generator $A^{\text{nl}}_{\varepsilon}$}\label{sec: Markov Mapping Theorem application - limit}
 In this section we consider a general generator limit for the lookdown representation of our spatial model. 
@@
 \subsection{Proof to Lemma \ref{lem: gamma - r radius comparison}}
-
+    \label{sec: Proof to gamma-r radius comparison}
 Suppose that the birth rate at $x$ is
@@
 
-To bound $\E\left[\langle 1, \eta_t \rangle\right]$
+To bound $\IE\left[\langle 1, \eta_t \rangle\right]$
 by Gronwall,
@@
 \end{align}
-(since $Z \sim \text{Normal}(0, \sigma^2)$ then $\E[e^{tZ}] = \exp(\sigma^2 t^2 / 2)$).
+(since $Z \sim \text{Normal}(0, \sigma^2)$ then $\IE[e^{tZ}] = \exp(\sigma^2 t^2 / 2)$).
 

### 2022-04-08 forwards-and-backwards.tex
Update on Overleaf.

@@
 \newcommand{\covq}{\Sigma}     % covariance matrix of dispersal, times theta
-\newcommand{\kernel}{\varrho}  % interaction kernels
+\newcommand{\kernel}{\rho}  % interaction kernels
 \newcommand{\smooth}[1]{\kernel_{#1} \! * \!}  % convolution by the interaction kernel
@@
      \left(
-        f(z)r\big(z,\varrho_{r}*\eta^{\theta}_{s}(z)\big)
-            -f(x)r\big(x,\varrho_{r}*\eta^{\theta}_{s}(x)\big)
+        f(z)r\big(z,\rho_{r}*\eta^{\theta}_{s}(z)\big)
+            -f(x)r\big(x,\rho_{r}*\eta^{\theta}_{s}(x)\big)
             \right)
@@
         \\ & \qquad \qquad \qquad \qquad {} \times
-                            \gamma\big(x,\varrho_{\gamma}*\eta^{\theta}_{s}(x)\big)
+                            \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
                             \eta^{\theta}_{s}(dx)
      \\ & \qquad {} +\int 
-     f(x)F\big(x,\varrho_{F}*\eta^{\theta}_{s}(x)\big)
+     f(x)F\big(x,\rho_{F}*\eta^{\theta}_{s}(x)\big)
      \eta^{\theta}_{s}(dx)
@@
 \frac{\theta}{N} \int_{0}^{t}\bigg\{
-\langle \gamma\big(x,\varrho_{\gamma}*\eta^{\theta}_{s}(x)\big)
-\int f^2(y)r\big(y,\varrho_{r}*\eta^{\theta}_{s}(y)\big)q_\theta(x,dy) 
+\langle \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
+\int f^2(y)r\big(y,\rho_{r}*\eta^{\theta}_{s}(y)\big)q_\theta(x,dy) 
 ,\eta^{\theta}_{s}(dx)\rangle\\
@@
     and assume that as $\theta \to \infty$, $N \to \infty$
-    in such a way that $\theta/N \to \delta$.
+    in such a way that $\theta/N \to \alpha$.
     (However, interaction distances $\epsilon_r$, $\epsilon_\gamma$, and $\epsilon_F$
@@
     is a martingale.
-    The quadratic variation of $M_t$ is given by 
+    The quadratic variation of $M_t$, denoted $\langle M \rangle_t$, is given by 
     \begin{align} \label{eqn:mgale_variation}
-        [ M ]_t
+        \langle M \rangle_t
         =
-        \delta
+        \alpha
         \int_0^t
@@
     In other words, the limit is a measure-valued process with non-local interactions.
-    Furthermore, if $\delta = 0$ the limit is deterministic.
+    Furthermore, if $\alpha = 0$ the limit is deterministic.
 \end{theorem}
@@
 \comment{
-    \textbf{Question:}
-    In our outline
-    we said this corollary would be about uniqueness,
-    but is it also about continuity of the limit (i.e., existence of a density)?
-    A lot of my uncertainty in how to phrase these results
-    comes from being unsure what exactly we can say about densities.
+TODO: insert definition of "weak solution of the PDE \ref{eqn:nonlocal_pde}" heere.
 }
@@
     \label{cor:nonlocal_pde_limits}
+    \comment{(TODO: remove "has a density" and rephrase appropriately)}
     In the context of Theorem~\ref{thm:nonlocal_convergence},
-    if the limit is deterministic (i.e., $\theta / N \to \delta = 0$), $\eta_0$ has a density,
+    if the limit is deterministic (i.e., $\theta / N \to \alpha = 0$), $\eta_0$ has a density,
     and \comment{additional conditions? can we say something like this??}
@@
 (i.e., through a smoothed version of $\varphi$).
+
+\comment{TODO: Tom has conditions (coefficient are Lipschitz?) under which
+    the solution to \eqref{eqn:nonlocal_pdf} has a density (Thm 2.1 in DDMOT);
+    should we insert those here (as a Corollary or Proposition, maybe?)}
 
@@
 then it turns out that a lineage is a diffusion driven by the density.
-The remaining case is the superprocess limit ($\theta/N \to \delta > 0$);
+The remaining case is the superprocess limit ($\theta/N \to \alpha > 0$);
 in this case, we expect that a lineage could still be described as a generalized diffusion,
@@
     +
-    \varepsilon_{\theta}(f, F, \eta),
+    \epsilon_{\theta}(f, F, \eta),
 \end{multline*}
 where the terms that make up 
-$\varepsilon_{\theta, N}(f, F, \eta)$
+$\epsilon_{\theta, N}(f, F, \eta)$
 will be negligible in our scaling limit.
@@
 measured at $x$ rather than at the point where juveniles fall.
-\comment{(IS THIS BIT STILL TRUE:)}
-This condition also differs from the assumption that
-we use in~\S\ref{scalings with levels} to guarantee convergence of the 
-processes with levels in our lookdown 
-constructions, see~(\ref{lookdown blambda}). 
-Under mild
-regularity conditions on $r$ (which we certainly need to have sensible 
-limiting models) the conditions are equivalent.
 
@@
 $$
-The term $\varepsilon_{\theta,N}(f, F, \eta)$ will be 
+The term $\epsilon_{\theta,N}(f, F, \eta)$ will be 
 $\bigO(\theta/N^2)$.
@@
 
-If $N=\delta\theta$, for some positive constant $\delta$,
+If $N=\alpha\theta$, for some positive constant $\alpha$,
 the second order term in the generator remains order
@@
 $$
-\frac{1}{\delta}F''(\langle f,\Xi\rangle)
+\frac{1}{\alpha}F''(\langle f,\Xi\rangle)
 \langle f^2(x), \gamma(x,\Xi)
@@
 is a martingale with quadratic variation
-$$\frac{2}{\delta}\int_0^t\langle f^2(x) 
+$$\frac{2}{\alpha}\int_0^t\langle f^2(x) 
 \gamma(x,\Xi_s)r(x,\Xi_s),\Xi_s(dx)\rangle ds.$$
@@
 mollification over Gaussian kernels with radius
-$\varepsilon_{\gamma}$, $\varepsilon_{F}$ and $\varepsilon_{r}$.
+$\epsilon_{\gamma}$, $\epsilon_{F}$ and $\epsilon_{r}$.
 
@@
 $$\theta\gamma^{\mathfrak{m}}_{\theta}(x, \eta)
-:=~\theta\gamma(x, \varrho_{\gamma}*\eta(x)) \int r(y, \varrho_{r}*\eta(y))q_{\theta}(x,dy);$$
+:=~\theta\gamma(x, \rho_{\gamma}*\eta(x)) \int r(y, \rho_{r}*\eta(y))q_{\theta}(x,dy);$$
 the local branching mechanism $b(x,\eta)$ is 
-$$b_{\theta}(x, \eta):=~ \theta \bigg\{ \gamma(x, \varrho_{\gamma}*\eta(x)) \int r(y, \varrho_{r}*\eta(y))q_{\theta}(x,dy)-\mu(x, \eta)\bigg\};$$
+$$b_{\theta}(x, \eta):=~ \theta \bigg\{ \gamma(x, \rho_{\gamma}*\eta(x)) \int r(y, \rho_{r}*\eta(y))q_{\theta}(x,dy)-\mu(x, \eta)\bigg\};$$
 and the dispersal kernel $q^{\mathfrak{m}}(x,\eta, dy)$ is 
 $$q^{\mathfrak{m}}_{\theta}(x,\eta,dy) 
-:=~ \frac{r(y,\varrho_{r}*\eta(y)) q_{\theta}(x,dy)}{\int_{\mathbb{R}^d} r(y,\varrho_{r}*\eta(y)) q_{\theta}(x,dy)}.$$
+:=~ \frac{r(y,\rho_{r}*\eta(y)) q_{\theta}(x,dy)}{\int_{\mathbb{R}^d} r(y,\rho_{r}*\eta(y)) q_{\theta}(x,dy)}.$$
 
@@
 stochastic equations presented in \S \ref{sec: Evolution of an Individual Particle} to the infinite density limit.\\
-In the scaling limit $A^{\text{nl}}_{\varepsilon}$, the spatial movement of particles can be characterised with the map $$h \mapsto \gamma\big(x,(\varrho_{\varepsilon}*\Xi)(x)\big)r\big(x,(\varrho_{\varepsilon}*\Xi)(x)\big)\mathcal{B}^{m}_{\varepsilon}(\Xi)h(x) ,$$
+In the scaling limit $A^{\text{nl}}_{\epsilon}$, the spatial movement of particles can be characterised with the map $$h \mapsto \gamma\big(x,(\rho_{\epsilon}*\Xi)(x)\big)r\big(x,(\rho_{\epsilon}*\Xi)(x)\big)\mathcal{B}^{m}_{\epsilon}(\Xi)h(x) ,$$
 and as individual particles travel as a random walk in the pre-limit model, we should expect a diffusion limit for individual trajectories.
@@
 In particular recall that as in Remark \ref{Remark: Product Rule on Laplacian}, if $\mathcal{B}$ is the Laplacian operator, then the generator above is merely 
-$$\gamma\big(x,(\varrho_{\varepsilon}*\Xi)(x)\big)\left(\Delta h(x) +2 \nabla h(x) \cdot \nabla \log r( \cdot, (\varrho_{\varepsilon}*\Xi)(\cdot))(x)\right),$$
+$$\gamma\big(x,(\rho_{\epsilon}*\Xi)(x)\big)\left(\Delta h(x) +2 \nabla h(x) \cdot \nabla \log r( \cdot, (\rho_{\epsilon}*\Xi)(\cdot))(x)\right),$$
 and applying Ito's formula we have 
@@
 \begin{aligned}
-\beta(X(s),\Xi(s))=& 2\gamma\big(X(s),(\varrho_{\varepsilon}*\Xi)(X(s))\big) \nabla \log r (\cdot, (\varrho_{\varepsilon}*\Xi)(\cdot))(X(s))\\
-\sigma(X(s),\Xi(s))=& \sqrt{2\gamma\big(X(s),(\varrho_{\varepsilon}*\Xi)(X(s))\big)}.
+\beta(X(s),\Xi(s))=& 2\gamma\big(X(s),(\rho_{\epsilon}*\Xi)(X(s))\big) \nabla \log r (\cdot, (\rho_{\epsilon}*\Xi)(\cdot))(X(s))\\
+\sigma(X(s),\Xi(s))=& \sqrt{2\gamma\big(X(s),(\rho_{\epsilon}*\Xi)(X(s))\big)}.
 \end{aligned}
@@
 \begin{aligned}
-\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(s), \eta(s)) &\to \ell \gamma(X_{\tau}(s),\varrho_\varepsilon*\Xi(X_{\tau}(s)),\\
-b_{\theta}(X_{\tau}(s),\eta(s)) &\to  F(X_{\tau}(s), (\varrho_{\varepsilon}*\eta)(X_{\tau}(s)))\\
-&+\gamma(X_{\tau}(s), (\varrho_{\varepsilon}*\Xi)(X_{\tau}(s)))\mathcal{B}r(\cdot,(\varrho_{\varepsilon}*\eta)(\cdot))(X_{\tau}(s)).
+\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(s), \eta(s)) &\to \ell \gamma(X_{\tau}(s),\rho_\epsilon*\Xi(X_{\tau}(s)),\\
+b_{\theta}(X_{\tau}(s),\eta(s)) &\to  F(X_{\tau}(s), (\rho_{\epsilon}*\eta)(X_{\tau}(s)))\\
+&+\gamma(X_{\tau}(s), (\rho_{\epsilon}*\Xi)(X_{\tau}(s)))\mathcal{B}r(\cdot,(\rho_{\epsilon}*\eta)(\cdot))(X_{\tau}(s)).
 \end{aligned}    
@@
 s))ds\\
-U_{\tau}(t)=&U_{\tau}(\tau )+\int_{\tau}^t\bigg\{\ell \gamma(X_{\tau}(s),\varrho_\varepsilon*\Xi(X_{\tau}(s)U_{\tau}^2(s) \\
-& -\big(F(X_{\tau}(s), (\varrho_{\varepsilon}*\eta)(X_{\tau}(s)))+\gamma(X_{\tau}(s), (\varrho_{\varepsilon}*\Xi)(X_{\tau}(s)))\mathcal{B}r(\cdot,(\varrho_{\varepsilon}*\eta)(\cdot))(X_{\tau}(s))\big)U_{\tau}(s))\bigg\}ds.
+U_{\tau}(t)=&U_{\tau}(\tau )+\int_{\tau}^t\bigg\{\ell \gamma(X_{\tau}(s),\rho_\epsilon*\Xi(X_{\tau}(s)U_{\tau}^2(s) \\
+& -\big(F(X_{\tau}(s), (\rho_{\epsilon}*\eta)(X_{\tau}(s)))+\gamma(X_{\tau}(s), (\rho_{\epsilon}*\Xi)(X_{\tau}(s)))\mathcal{B}r(\cdot,(\rho_{\epsilon}*\eta)(\cdot))(X_{\tau}(s))\big)U_{\tau}(s))\bigg\}ds.
 \end{aligned}
@@
 \label{Eq: expression for offspring level in limit}
-U_{\tau}(\tau )=U_{\tau}(\tau'+s)=U_{\tau'}(\tau'+s)+\frac v{2\ell \gamma(X_{\tau}(s),\varrho_\varepsilon*\Xi(X_{\tau}(s))U_{\tau}^2(s)},
+U_{\tau}(\tau )=U_{\tau}(\tau'+s)=U_{\tau'}(\tau'+s)+\frac v{2\ell \gamma(X_{\tau}(s),\rho_\epsilon*\Xi(X_{\tau}(s))U_{\tau}^2(s)},
 \end{equation} 
@@
 we require 
-$v<2\ell \gamma(X_{\tau'}(\tau'+s),\varrho_\varepsilon*\Xi(X_{\tau'}(\tau'+s))U_{\tau}^2(\tau'+s)\big(u_g-U_{\tau'}(\tau'+s)\big)$.
+$v<2\ell \gamma(X_{\tau'}(\tau'+s),\rho_\epsilon*\Xi(X_{\tau'}(\tau'+s))U_{\tau}^2(\tau'+s)\big(u_g-U_{\tau'}(\tau'+s)\big)$.
 Recalling
@@
 (s),\Xi (s))ds,\\
-U_{\tau}(t)&=&U_{A_{\tau}(0)}(0)+\int_0^t\frac 1{2\ell \gamma(X_{\tau}(s-),\varrho_\varepsilon*\Xi(X_{\tau}(s-))}dV_{\tau}(s)\\
-&&\qquad\qquad +\int_{\tau}^t\bigg\{\ell \gamma(X_{\tau}(s),\varrho_\varepsilon*\Xi(X_{\tau}(s)U_{\tau}^2(s) \\
-&&-\big(F(X_{\tau}(s), (\varrho_{\varepsilon}*\eta)(X_{\tau}(s)))+\gamma(X_{\tau}(s), (\varrho_{\varepsilon}*\Xi)(X_{\tau}(s)))\mathcal{B}r(\cdot,(\varrho_{\varepsilon}*\eta)(\cdot))(X_{\tau}(s))\big)U_{\tau}(s))\bigg\}ds,\end{eqnarray*}
+U_{\tau}(t)&=&U_{A_{\tau}(0)}(0)+\int_0^t\frac 1{2\ell \gamma(X_{\tau}(s-),\rho_\epsilon*\Xi(X_{\tau}(s-))}dV_{\tau}(s)\\
+&&\qquad\qquad +\int_{\tau}^t\bigg\{\ell \gamma(X_{\tau}(s),\rho_\epsilon*\Xi(X_{\tau}(s)U_{\tau}^2(s) \\
+&&-\big(F(X_{\tau}(s), (\rho_{\epsilon}*\eta)(X_{\tau}(s)))+\gamma(X_{\tau}(s), (\rho_{\epsilon}*\Xi)(X_{\tau}(s)))\mathcal{B}r(\cdot,(\rho_{\epsilon}*\eta)(\cdot))(X_{\tau}(s))\big)U_{\tau}(s))\bigg\}ds,\end{eqnarray*}
 where
@@
     \label{lem: gamma - r radius comparison}
-    Assume that $\varepsilon_{r}^2 + \frac{1}{\theta} < \varepsilon_{\gamma}^2,$ then
-    for all $f \in \mathcal{C}^{2}_{0}(\mathbb{R}^d)$
+    Assume that $\epsilon_{r}^2 + \frac{1}{\theta} < \epsilon_{\gamma}^2,$ then
+    for all $f \in \mathcal{C}^{2}_{0}(\mathbb{R}^d \times \mathbb{R})$
+    with bounded first and second derivatives
     and for all $\eta \in \mathcal{M}_{f}(\mathbb{R}^d)$, we have
@@
     \begin{equation}\label{eq: gamma - r radius comparison bound}
-    \gamma\big(x,\varrho_{\gamma}*\eta(x)\big) \left| \theta \int_{\mathbb{R}^n} \big\{f\big(\varrho_{r}*\eta(y)\big)-f\big(\varrho_{r}*\eta(x)\big)\big\}\varrho_{1/\theta}(x-y)dy\right| \leq C_{\gamma, f}
+    \gamma\big(x,\rho_{\gamma}*\eta(x)\big)
+    \left| \theta 
+        \int_{\mathbb{R}^n} 
+            \big\{
+                f\big(y,\rho_{r}*\eta(y)\big)-f\big(x,\rho_{r}*\eta(x)\big)
+            \big\}
+        q_{\theta}(x,dy)
+    \right|
+    \leq C_{\gamma, f}    
     \end{equation}
@@
 \begin{proof}
-See Appendix \ref{sec: Proof to gamma-r radius comparison}.    
+Since $f(x_1,...,x_d,w)$ is twice differentiable, we can Taylor expand $f$ around  $(x_1,...,x_d,\rho_{r}*\eta(x))$ up to second order and obtain that for $x=(x_1,..,x_d)$,
+\begin{equation}
+\begin{aligned}
+&~f\big(y,\rho_{r}*\eta(y)\big)-f\big(x,\rho_{r}*\eta(x)\big)\\
+=&~ \nabla_x f \big(x,\rho_{r}*\eta(x)\big)
+            \cdot (y-x)\\ 
+        &~ + \frac{\partial f}{\partial w}
+            \big(x,\rho_{r}*\eta(x)\big) \left(\rho_{r}*\eta(y)-\rho_{r}*\eta(x)\right)\\
+        &~ + \frac{1}{2}\sum_{1 \leq i,j \leq d }\frac{\partial^2 f}{\partial x_i x_j}
+            \big(z,\rho_{r}*\eta(z)\big) (y_i-x_i)(y_j-x_j)\\
+        &~ + \frac{1}{2}\sum_{1 \leq i \leq d}
+                \frac{\partial^2 f}{\partial w \partial x_i}
+                 \big(z,\rho_{r}*\eta(z)\big) (y_i-x_i)
+                    \left(\rho_{r}*\eta(y)-\rho_{r}*\eta(x)\right)\\
+        &~ + \frac{1}{2}\frac{\partial^2 f}{\partial^2 w}
+            \big(z,\rho_{r}*\eta(z)\big)
+            \left(
+            \rho_{r}*\eta(y)-\rho_{r}*\eta(x)
+            \right)^2,
+\end{aligned}    
+\end{equation}
+where $z=ty+(1-t)x$ for some $t \in [0,1]$.
+
+With the assumptions on $f$, we can bound the magnitude
+of first and second derivatives with 
+some constants $||Df||_{\infty}$ and $||D^2f||_{\infty}$.
+
+Therefore, we have that 
+\begin{equation}
+\begin{aligned}
+&~\left| 
+        \theta \int_{\mathbb{R}^d}
+                f\big(y,\rho_{r}*\eta(y)\big)-f\big(x,\rho_{r}*\eta(x)\big)
+                q_{\theta}(x,dy)
+\right|\\
+\leq &~ ||Df||_{\infty} \left|
+                        \theta \int_{\mathbb{R}^d} \sum_{i=1,..,d}(y_i-x_i) q_{\theta}(x,dy)
+                        \right|\\ 
+        &~ + |Df||_{\infty} 
+            \left| \theta \int_{\mathbb{R}^d}
+               \left(\rho_{r}*\eta(y)-\rho_{r}*\eta(x)\right)
+            q_{\theta}(x,dy) \right| \\
+        &~ + \frac{1}{2}|D^2f||_{\infty}\left|
+                        \theta \int_{\mathbb{R}^d} (y-x)(y-x)^{T} q_{\theta}(x,dy)
+                        \right|\\
+        &~ + \frac{1}{2}|D^2f||_{\infty}    
+                \sum_{1 \leq i \leq d}\left|
+                        \theta \int_{\mathbb{R}^d}
+                        \left(\rho_{r}*\eta(y)-\rho_{r}*\eta(x)\right)
+                  (y_i-x_i)
+                        q_{\theta}(x,dy)
+                        \right|
+                    \\
+        &~ + \frac{1}{2}|D^2f||_{\infty} \left|
+            \theta \int_{\mathbb{R}^d}
+            \left(\rho_{r}*\eta(y)-\rho_{r}*\eta(x)
+            \right)^2
+            q_\theta(x,dy) \right|
+\end{aligned}    
+\end{equation}
+Recall that $q_{\theta}(x,dy)$ is a Gaussian kernel
+with mean $\meanq/\theta$
+and Covariance matrix $\covq / \theta$.
+As a result, the first and third term
+is easily bounded above by 
+$$||Df||_{\infty} \left|
+                        \theta \int_{\mathbb{R}^d} \sum_{i=1,..,d}(y_i-x_i) q_{\theta}(x,dy)
+                        \right|
+                        \leq  ||Df||_{\infty}||\meanq||_{1},$$
+and 
+$$ \frac{1}{2}|D^2f||_{\infty}\left|
+                        \theta \int_{\mathbb{R}^d} (y-x)(y-x)^{T} q_{\theta}(x,dy)
+                        \right| \leq \frac{1}{2}|D^2f||_{\infty} ||\covq||_{1}.$$
+For the cross term, we apply Cauchy's inequality to obtain
+\begin{equation}
+\begin{aligned}
+&\frac{1}{2}|D^2f||_{\infty}\sum_{1 \leq i \leq d}    
+                \left|
+                        \theta \int_{\mathbb{R}^d}
+                        \left(\rho_{r}*\eta(y)-\rho_{r}*\eta(x)\right)
+                  (y_i-x_i)
+                        q_{\theta}(x,dy)
+                        \right|\\
+\leq& \frac{1}{2}|D^2f||_{\infty} \sum_{1 \leq i \leq d} 
+        \sqrt{\theta \int_{\mathbb{R}^d}
+           (y_i-x_i)^2
+            q_\theta(x,dy)
+            }
+        \sqrt{
+            \theta \int_{\mathbb{R}^d}
+            \left(\rho_{r}*\eta(y)-\rho_{r}*\eta(x)
+            \right)^2
+            q_\theta(x,dy) 
+            }    \\
+\leq& \frac{1}{2}|D^2f||_{\infty} ||\covq||_{1/2}
+        \sqrt{
+            \theta \int_{\mathbb{R}^d}
+            \left(\rho_{r}*\eta(y)-\rho_{r}*\eta(x)
+            \right)^2
+            q_\theta(x,dy) 
+            }.    
+\end{aligned}
+\end{equation}
+We are given that $z\gamma(x,z)$ and $z^2 \gamma(x,z)$ is bounded above
+for all $z  \geq 0$.
+Therefore, it suffices to show that
+for all $\eta \in \mathcal{M}_{f}(\mathbb{R}^d)$,
+\begin{equation}
+    \label{eq: r-gamma first moment control}
+\left|\theta \int_{\mathbb{R}^d}
+            \left(\rho_{r}*\eta(y)-\rho_{r}*\eta(x)
+            \right)
+            q_\theta(x,dy)\right|
+            \leq \rho_{\gamma}*\eta(x),    
+\end{equation}
+and
+\begin{equation}
+    \label{eq: r-gamma comparison square term}
+\theta \int_{\mathbb{R}^d}
+            \left(\rho_{r}*\eta(y)-\rho_{r}*\eta(x)
+            \right)^2
+            q_\theta(x,dy)
+            \leq \rho_{\gamma}*\eta(x)^2.    
+\end{equation}
+We first prove Equation \eqref{eq: r-gamma first moment control}.
+Note that 
+$$ \left(\rho_{r}*\eta(y)-\rho_{r}*\eta(x)\right)
+        = \left\langle p_{\epsilon^2_r}(y-w)-p_{\epsilon^2_r}(x-w),             \eta(dw)\right \rangle,$$
+so applying Fubini's theorem, 
+\begin{equation}
+\left|\theta \int_{\mathbb{R}^d}
+            \left(\rho_{r}*\eta(y)-\rho_{r}*\eta(x)
+            \right)
+            q_\theta(x,dy)\right|
+            = \left\langle \left| \theta \int_{\mathbb{R}^d} \left(p_{\epsilon^2_r}(y-w)-p_{\epsilon^2_r}(x-w)\right)
+            q_\theta(x,dy) \right| , \eta(dw)\right \rangle.    
+\end{equation}
+It suffices therefore to show that for all $w \in \mathbb{R}^d$,
+\begin{equation}
+\left| \theta \int_{\mathbb{R}^d} \left(p_{\epsilon^2_r}(y-w)-p_{\epsilon^2_r}(x-w)\right)
+            q_\theta(x,dy) \right| \leq p_{\epsilon^2_{\gamma}}(x-w).
+\end{equation}
+By the Chapman-Kolmogorov equality, we have
+\begin{align}
+&\left| \theta \int_{\mathbb{R}^d}
+                \left(p_{\epsilon^2_r}(y-w)
+                        -p_{\epsilon^2_r}(x-w)
+                \right)
+                q_\theta(x,dy)
+        \right|\\
+        =& \theta \left\{
+                    \frac{\epsilon^2_r }{\left|\covq / \theta +  \epsilon^2_r I \right|^{1/2}}
+                    \exp \left(
+                    \frac{(x-w-\meanq / \theta)^{T}
+                        (\covq /\theta +  \epsilon^2_r I)^{-1}
+                        (x-w-\meanq / \theta)}{2}
+                        -\frac{|x-w|^2}{2\epsilon^2}
+                    \right)
+                    -1\right\}\\
+         & \times p_{\epsilon^2_r}(x-w).
+\end{align}
+If we write 
+\begin{equation}
+F(s)=  \frac{\epsilon^2_r }
+        {\left|\covq s +  \epsilon^2_r I \right|^{1/2}}
+        \exp \left(
+                    \frac{(x-w-\meanq s)^{T}
+                        (\covq s +  \epsilon^2_r I)^{-1}
+                        (x-w-\meanq s)}{2}
+                        -\frac{|x-w|^2}{2\epsilon^2}
+            \right)
+        -1,   
+\end{equation}
+then 
+\begin{align}
+\left| \theta \int_{\mathbb{R}^d}
+                \left(p_{\epsilon^2_r}(y-w)
+                        -p_{\epsilon^2_r}(x-w)
+                \right)
+                q_\theta(x,dy)
+        \right|
+        \leq  \theta \left(F\left(1 / \theta \right)-1\right) 
+                \times \epsilon_\gamma^d \epsilon_r^{-d}
+                p_{\epsilon^2_\gamma}(x-w),
+\end{align}
+so we have our bound 
+as $F(x)$ has bounded derivative in a neighbourhood around $0$.
+
+We now prove Equation \eqref{eq: r-gamma comparison square term}. Applying Jensen's inequality, we have
+\begin{align}
+&\left\{
+            \rho_r * \eta(y)
+            -
+            \rho_r * \eta(x)
+\right\}^2  \\
+&\qquad
+=
+\left\{
+\int
+    \left(
+        \rho_r(y-w)
+        -
+        \rho_r(x-w)
+    \right)
+\eta(dw)
+\right\}^2  \\
+&\qquad
+=
+\left\{
+\int
+    \left(
+        \frac{\rho_r(y-w)}{\rho_r(x-w)}
+        -
+        1
+    \right)
+    \rho_r(x-w)
+\eta(dw)
+\right\}^2  \\
+&\qquad
+=
+\left(\rho_r * \eta(x)\right)^2 \left\{
+\int
+    \left(
+        \frac{\rho_r(y-w)}{\rho_r(x-w)}
+        -
+        1
+    \right)
+    \frac{\rho_r(x-w)}{\rho_r * \eta(x)}
+\eta(dw)
+\right\}^2  \\
+&\qquad
+\le
+\left(\rho_r * \eta(x)\right)^2 
+\int
+    \left(
+        \frac{\rho_r(y-w)}{\rho_r(x-w)}
+        -
+        1
+    \right)^2
+    \frac{\rho_r(x-w)}{\rho_r * \eta(x)}
+\eta(dw) \\
+&\qquad
+=
+\rho_r * \eta(x)
+\int
+    \left(
+        \frac{\rho_r(y-w)}{\rho_r(x-w)}
+        -
+        1
+    \right)^2
+    \rho_r(x-w)
+\eta(dw).
+\end{align}
+Note that since $\epsilon_{\gamma}>\epsilon_{r}$,
+\begin{equation}
+\begin{aligned}
+ \rho_r * \eta(x)=& \int p_{\epsilon^2_r}(x-w) \eta(dw)\\
+                 =&  \int \frac{p_{\epsilon^2_r}(x-w)}{p_{\epsilon^2_\gamma}(x-w)}
+                  p_{\epsilon^2_\gamma}(x-w) \eta(dw)\\
+            \leq & \int \epsilon_\gamma^d \epsilon_r^{-d}
+                   e^{-(x-w)^2(\frac{1}{\varepsilon^2_r}-\frac{1}{\varepsilon^2_\gamma})}
+                   p_{\epsilon^2_\gamma}(x-w) \eta(dw)\\
+            \leq & \epsilon_\gamma^d \epsilon_r^{-d}\rho_\gamma * \eta(x),
+\end{aligned}
+\end{equation}
+it suffices to show that 
+\begin{equation}
+ \theta H_{\theta}(x,w)\rho_r(x-w)\leq \rho_{\gamma}(x-w),
+\end{equation}
+where
+$$H_{\theta}(x,w)=\int_{\mathbb{R}^d}
+    \left(
+        \frac{\rho_r(y-w)}{\rho_r(x-w)}
+        -
+        1
+    \right)^2
+q_{\theta}(x,dy).$$
+
 \end{proof}
@@
  \left(
-        r\big(z,\varrho_{r}*\eta^{\theta}_{s}(z)\big)
-            -r\big(x,\varrho_{r}*\eta^{\theta}_{s}(x)\big)
+        r\big(z,\rho_{r}*\eta^{\theta}_{s}(z)\big)
+            -r\big(x,\rho_{r}*\eta^{\theta}_{s}(x)\big)
             \right)
                     q_\theta(x,dz)\right)
-                            \gamma\big(x,\varrho_{\gamma}*\eta^{\theta}_{s}(x)\big)
+                            \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
                             \eta^{\theta}_{s}(dx)\\
-& \qquad +\int F\big(x,\varrho_{F}*\eta^{\theta}_{s}(x)\big)
+& \qquad +\int F\big(x,\rho_{F}*\eta^{\theta}_{s}(x)\big)
 \eta^{\theta}_{s}(dx)\bigg\} ds
@@
 &+ \int_{0}^{t}\mathbb{E}\bigg\langle
-        \gamma\big(x,\varrho_{\gamma}*\eta^{\theta}_{s}(x)\big)
+        \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
             \left| \theta \int_{\mathbb{R}^n}
-                    \big\{r\big(\varrho_{r}*\eta^{\theta}_s(y)\big)-r\big(\varrho_{r}*\eta^{\theta}_s(x)\big)\big\}
-                    \varrho_{1/\theta}(x-y)dy\right| + C_F 
+                    \big\{r\big(\rho_{r}*\eta^{\theta}_s(y)\big)-r\big(\rho_{r}*\eta^{\theta}_s(x)\big)\big\}
+                    \rho_{1/\theta}(x-y)dy\right| + C_F 
                             ,\eta^{\theta}_s(dx)  \bigg\rangle ds\\
@@
 \leq& C (1+\mathbb{E}\{[M_t(1)]\})\\
-\leq & C+\frac{\theta}{N}\int_{0}^{t} \left\langle \gamma(\varrho_{\gamma}*\eta^{\theta}_{s}(x))\int_{\mathbb{R}^n}r(\varrho_{r}*\eta^{\theta}_{s}(y)) q_\theta(x,dy)+\mu(x,\eta^{\theta}_{s}), \eta^{\theta}_{s}(dx) \right\rangle ds \\
-\leq & C+\frac{2\theta}{N}\int_{0}^{t} \left\langle \gamma(\varrho_{\gamma}*\eta^{\theta}_{s}(x))r(\varrho_{r}*\eta^{\theta}_{s}(x)), \eta^{\theta}_{s}(dx) \right\rangle ds \\
-& + \frac{1}{N}\int_{0}^{t} \left\langle \gamma (\varrho_{\gamma}*\eta^{\theta}_{s}(x))\theta\int_{\mathbb{R}^n}\left(r(\varrho_{r}*\eta^{\theta}_{s}(y))-r(\varrho_{r}*\eta^{\theta}_{s}(x))\right) q_\theta(x,dy), \eta^{\theta}_{s}(dx) \right\rangle ds\\
+\leq & C+\frac{\theta}{N}\int_{0}^{t} \left\langle \gamma(\rho_{\gamma}*\eta^{\theta}_{s}(x))\int_{\mathbb{R}^n}r(\rho_{r}*\eta^{\theta}_{s}(y)) q_\theta(x,dy)+\mu(x,\eta^{\theta}_{s}), \eta^{\theta}_{s}(dx) \right\rangle ds \\
+\leq & C+\frac{2\theta}{N}\int_{0}^{t} \left\langle \gamma(\rho_{\gamma}*\eta^{\theta}_{s}(x))r(\rho_{r}*\eta^{\theta}_{s}(x)), \eta^{\theta}_{s}(dx) \right\rangle ds \\
+& + \frac{1}{N}\int_{0}^{t} \left\langle \gamma (\rho_{\gamma}*\eta^{\theta}_{s}(x))\theta\int_{\mathbb{R}^n}\left(r(\rho_{r}*\eta^{\theta}_{s}(y))-r(\rho_{r}*\eta^{\theta}_{s}(x))\right) q_\theta(x,dy), \eta^{\theta}_{s}(dx) \right\rangle ds\\
 \leq & C+ \frac{(2 \theta C_{\gamma,r}+C_{\gamma,r})\mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle]e^{(C_{\gamma,r}+C_F)t}}{N}.
@@
 \leq &  \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle] \\
-&+ \sup_{\tau \in [0,t]} \int_{0}^{\tau}\mathbb{E} \bigg\langle \gamma(\varrho_{r}*\eta^{\theta}_{s}(x)) \left| \theta \int_{\mathbb{R}^n} \big\{r\big(\varrho_{r}*\eta^{\theta}_{s}(y)\big)-r\big(\varrho_{r}*\eta^{\theta}_{s}(x)\big)\big\}\varrho_{1/\theta}(x-y)dy\right| + C_F ,\eta^{\theta}_{s}(dx)  \bigg\rangle dw\\
+&+ \sup_{\tau \in [0,t]} \int_{0}^{\tau}\mathbb{E} \bigg\langle \gamma(\rho_{r}*\eta^{\theta}_{s}(x)) \left| \theta \int_{\mathbb{R}^n} \big\{r\big(\rho_{r}*\eta^{\theta}_{s}(y)\big)-r\big(\rho_{r}*\eta^{\theta}_{s}(x)\big)\big\}\rho_{1/\theta}(x-y)dy\right| + C_F ,\eta^{\theta}_{s}(dx)  \bigg\rangle dw\\
 &+ \mathbb{E}\{M^{*}_t(1)\}\\
@@
  & \mathbb{E}\left[\left| \langle f, \eta^{\theta}_{\tau+s}\rangle - \langle f, \eta^{\theta}_{\tau}\rangle \right|\right] \\
-\leq & \mathbb{E}\Bigg[\bigg| \int_{\tau}^{\tau+s}\bigg\langle \theta\gamma(\varrho_{r}*\eta^{\theta}_{s}(x)) \int_{\mathbb{R}^n} \big\{f(y)r(\varrho_{r}*\eta^{\theta}_{s}(y))-f(x)r(\varrho_{r}*\eta^{\theta}_{s}(x))\big\}\varrho_{1/\theta}(x-y)dy \\
-& \qquad + F(\varrho_{F}*\eta^{\theta}_{s}(x)) f(x),\eta^{\theta}_{s}(dx)  \bigg\rangle ds \bigg|\Bigg].
+\leq & \mathbb{E}\Bigg[\bigg| \int_{\tau}^{\tau+s}\bigg\langle \theta\gamma(\rho_{r}*\eta^{\theta}_{s}(x)) \int_{\mathbb{R}^n} \big\{f(y)r(\rho_{r}*\eta^{\theta}_{s}(y))-f(x)r(\rho_{r}*\eta^{\theta}_{s}(x))\big\}\rho_{1/\theta}(x-y)dy \\
+& \qquad + F(\rho_{F}*\eta^{\theta}_{s}(x)) f(x),\eta^{\theta}_{s}(dx)  \bigg\rangle ds \bigg|\Bigg].
 \end{aligned}
@@
 \begin{multline}
- \theta\gamma(\varrho_{r}*\eta^{\theta}_{s}(x))\int_{\mathbb{R}^n} \big\{f(y)r(\varrho_{r}*\eta^{\theta}_{s}(y))-f(x)r(\varrho_{r}*\eta^{\theta}_{s}(x))\big\}\varrho_{1/\theta}(x-y)dy \\
- =  f(x)\theta\gamma(\varrho_{r}*\eta^{\theta}_{s}(x))\int_{\mathbb{R}^n} \big\{r(\varrho_{r}*\eta^{\theta}_{s}(y))-r(\varrho_{r}*\eta^{\theta}_{s}(x))\big\}\varrho_{1/\theta}(x-y)dy\\
- + \theta\gamma(\varrho_{r}*\eta^{\theta}_{s}(x))\int_{\mathbb{R}^n} \big\{(f(y)-f(x))r(\varrho_{r}*\eta^{\theta}_{s}(y))\big\}\varrho_{1/\theta}(x-y)dy\\
+ \theta\gamma(\rho_{r}*\eta^{\theta}_{s}(x))\int_{\mathbb{R}^n} \big\{f(y)r(\rho_{r}*\eta^{\theta}_{s}(y))-f(x)r(\rho_{r}*\eta^{\theta}_{s}(x))\big\}\rho_{1/\theta}(x-y)dy \\
+ =  f(x)\theta\gamma(\rho_{r}*\eta^{\theta}_{s}(x))\int_{\mathbb{R}^n} \big\{r(\rho_{r}*\eta^{\theta}_{s}(y))-r(\rho_{r}*\eta^{\theta}_{s}(x))\big\}\rho_{1/\theta}(x-y)dy\\
+ + \theta\gamma(\rho_{r}*\eta^{\theta}_{s}(x))\int_{\mathbb{R}^n} \big\{(f(y)-f(x))r(\rho_{r}*\eta^{\theta}_{s}(y))\big\}\rho_{1/\theta}(x-y)dy\\
  \leq C_{\gamma,r}||f||_{\infty} + C_{\gamma}||\Delta f||_{\infty},
@@
 
-Finally,  $F(\varrho_{F}*\eta^{\theta}_{s}(x)) f(x)$ is bounded above by $C_F||f||_{\infty}$, so 
+Finally,  $F(\rho_{F}*\eta^{\theta}_{s}(x)) f(x)$ is bounded above by $C_F||f||_{\infty}$, so 
 \begin{multline}
@@
 \leq &\frac{\theta}{N} \mathbb{E} \Bigg\{ \int_{\tau}^{\tau+s}\bigg|
-\langle \gamma\big(x,\varrho_{\gamma}*\eta^{\theta}_{s}(x)\big)
-\int f^2(y)r\big(y,\varrho_{r}*\eta^{\theta}_{s}(y)\big)q_\theta(x,dy) 
+\langle \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
+\int f^2(y)r\big(y,\rho_{r}*\eta^{\theta}_{s}(y)\big)q_\theta(x,dy) 
 ,\eta^{\theta}_{s}(dx)\rangle\\
@@
 ,\eta^{\theta}_{s}(dx)\rangle \bigg|ds \Bigg\}\\
-\leq & \frac{2\theta}{N}\mathbb{E} \Bigg\{\int_{\tau}^{\tau+s} \left\langle \gamma(\varrho_{\gamma}*\eta^{\theta}_{s}(x))r(\varrho_{r}*\eta^{\theta}_{s}(x)), \eta^{\theta}_{s}(dx) \right\rangle ds\Bigg\} \\
-& + \frac{1}{N}\mathbb{E} \Bigg\{\int_{\tau}^{\tau+s} \left\langle \gamma (\varrho_{\gamma}*\eta^{\theta}_{s}(x))\theta\int_{\mathbb{R}^n}\left(r(\varrho_{r}*\eta^{\theta}_{s}(y))-r(\varrho_{r}*\eta^{\theta}_{s}(x))\right) q_\theta(x,dy), \eta^{\theta}_{s}(dx) \right\rangle ds\Bigg\}\\
+\leq & \frac{2\theta}{N}\mathbb{E} \Bigg\{\int_{\tau}^{\tau+s} \left\langle \gamma(\rho_{\gamma}*\eta^{\theta}_{s}(x))r(\rho_{r}*\eta^{\theta}_{s}(x)), \eta^{\theta}_{s}(dx) \right\rangle ds\Bigg\} \\
+& + \frac{1}{N}\mathbb{E} \Bigg\{\int_{\tau}^{\tau+s} \left\langle \gamma (\rho_{\gamma}*\eta^{\theta}_{s}(x))\theta\int_{\mathbb{R}^n}\left(r(\rho_{r}*\eta^{\theta}_{s}(y))-r(\rho_{r}*\eta^{\theta}_{s}(x))\right) q_\theta(x,dy), \eta^{\theta}_{s}(dx) \right\rangle ds\Bigg\}\\
 \leq & \frac{(2 \theta C_{\gamma,r}+C_{\gamma,r})\mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle]e^{(C_{\gamma,r}+C_F)T}(e^s-1)}{N} \to 0
@@
 \begin{equation}\label{Markov Mapping Theorem Cox Condition}
-\mathbb{E}\left[e^{-\int_{S \times [0,\lambda]} f(x,u) \xi^{\varepsilon,\theta,\lambda}(dx \times du)}\bigg| \mathcal{F}^{\Xi^{\varepsilon,\theta, \lambda}}_t\right]=e^{-\int F^{\varepsilon,\theta,\lambda}_f(x) \Xi^{\varepsilon,\theta,\lambda}_t(dx)},
+\mathbb{E}\left[e^{-\int_{S \times [0,\lambda]} f(x,u) \xi^{\epsilon,\theta,\lambda}(dx \times du)}\bigg| \mathcal{F}^{\Xi^{\epsilon,\theta, \lambda}}_t\right]=e^{-\int F^{\epsilon,\theta,\lambda}_f(x) \Xi^{\epsilon,\theta,\lambda}_t(dx)},
 \end{equation}
 where 
-$$F^{\varepsilon,\theta,\lambda}_f(x):=-\lambda\log \left(\frac{1}{\lambda}\int_{0}^{\lambda}e^{-f(x,u)}du\right)=-\lambda\log \left(1-\frac{1}{\lambda}\int_{0}^{\lambda}(1-e^{-f(x,u)})du\right).$$
+$$F^{\epsilon,\theta,\lambda}_f(x):=-\lambda\log \left(\frac{1}{\lambda}\int_{0}^{\lambda}e^{-f(x,u)}du\right)=-\lambda\log \left(1-\frac{1}{\lambda}\int_{0}^{\lambda}(1-e^{-f(x,u)})du\right).$$
 
@@
 \int_u^{
-\lambda}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\mathbb{R}^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\bar{
+\lambda}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\mathbb{R}^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
 \xi },dy) \nonumber \\
-& \qquad \qquad \qquad \qquad +\int_{\mathbb{R}^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\Xi,dy)\Bigg)dv_1 \nonumber\\
+& \qquad \qquad \qquad \qquad +\int_{\mathbb{R}^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy)\Bigg)dv_1 \nonumber\\
 &+f(\xi )\sum_{(x,u)\in\xi}\,\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)},
@@
 \int_u^{
-\lambda}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\mathbb{R}^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\bar{
+\lambda}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\mathbb{R}^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
 \xi },dy)\Bigg)dv_1,\\
@@
 \int_u^{
-\lambda}\Bigg(\frac{1}{2}\int_{\mathbb{R}^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\Xi,dy)\Bigg)dv_1,\\
+\lambda}\Bigg(\frac{1}{2}\int_{\mathbb{R}^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy)\Bigg)dv_1,\\
 A^{\theta,3}f(\xi)=&f(\xi )\sum_{(x,u)\in\xi}\,\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)},
@@
 \int_u^{
-\lambda}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\mathbb{R}^d}(g(y,u)-g(x,u))q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\bar{
+\lambda}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\mathbb{R}^d}(g(y,u)-g(x,u))q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
 \xi },dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
@@
 \int_u^{
-\lambda}\Bigg(\frac 12 g(x,v_1)\int_{\mathbb{R}^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\bar{
+\lambda}\Bigg(\frac 12 g(x,v_1)\int_{\mathbb{R}^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
 \xi },dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
@@
 \int_u^{
-\lambda} g(x,v_1)dv_1\times \int_{\mathbb{R}^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\bar{
+\lambda} g(x,v_1)dv_1\times \int_{\mathbb{R}^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
 \xi },dy)\right\}du\\
@@
 \int_u^{
-\lambda} g(x,v_1) (g(y,u)-g(x,u))dv_1du\right\}q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\bar{
+\lambda} g(x,v_1) (g(y,u)-g(x,u))dv_1du\right\}q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
 \xi },dy)
@@
 \int_u^{
-\lambda}\Bigg(\int_{\mathbb{R}^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\Xi,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
+\lambda}\Bigg(\int_{\mathbb{R}^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
 &=\sum_{(x,u)\in\xi}\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\int \Bigg\{f(\xi)\times
 \int_u^{
-\lambda}\Bigg(\int_{\mathbb{R}^d}\left(g(y,v_1)+g(x,v_1)-2\right)q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\Xi,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
+\lambda}\Bigg(\int_{\mathbb{R}^d}\left(g(y,v_1)+g(x,v_1)-2\right)q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
 &=\sum_{(x,u)\in\xi}\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i) \frac{1}{\lambda}\int_{\mathbb{R}^d}\Bigg\{\int_{0}^{\lambda}
 \int_u^{
-\lambda}g(x,u) \left(g(y,v_1)+g(x,v_1)-2\right)dv_1 du\Bigg\} q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\Xi,dy).
+\lambda}g(x,u) \left(g(y,v_1)+g(x,v_1)-2\right)dv_1 du\Bigg\} q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy).
 \end{align*}  
@@
 &\int \Bigg(A^{1}_{\theta}f(\xi)+A^{2}_{\theta}f(\xi)+A^{3}_{\theta}f(\xi)\Bigg)\Gamma(d\mathbf{u})\\
-&=  \sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)}\hat{g}(x_i) \left( \int_{\mathbb{R}^n} \hat{g}(y) q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\Xi,dy) - 2+\frac{1}{\hat{g}(x)}\right)+\sum_{(x,u) \in \xi } \prod_{(x_i,u_i)}\hat{g}(x_i)b_{\theta}(x,\Xi)\left(1-\frac{1}{\hat{g}(x)}\right)\\
-&=  \hat{f}(\xi)\sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi) \left(\int_{\mathbb{R}^n} \hat{g}(y) q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\Xi,dy) -1\right)+\hat{f}(\xi)\sum_{(x,u) \in \xi } (b_{\theta}(x,\Xi)-\theta\gamma^{\mathfrak{m}}_{\theta}(x,\xi))\left(1-\frac{1}{\hat{g}(x)}\right)\\
-&=  \hat{f}(\xi)\sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi) \left(\int_{\mathbb{R}^n} \hat{g}(y) q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\Xi,dy) -1\right) -\hat{f}(\xi)\sum_{(x,u) \in \xi } \theta \mu_{\varepsilon,\theta}(x,\Xi)\left(1-\frac{1}{\hat{g}(x)}\right),
+&=  \sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)}\hat{g}(x_i) \left( \int_{\mathbb{R}^n} \hat{g}(y) q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy) - 2+\frac{1}{\hat{g}(x)}\right)+\sum_{(x,u) \in \xi } \prod_{(x_i,u_i)}\hat{g}(x_i)b_{\theta}(x,\Xi)\left(1-\frac{1}{\hat{g}(x)}\right)\\
+&=  \hat{f}(\xi)\sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi) \left(\int_{\mathbb{R}^n} \hat{g}(y) q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy) -1\right)+\hat{f}(\xi)\sum_{(x,u) \in \xi } (b_{\theta}(x,\Xi)-\theta\gamma^{\mathfrak{m}}_{\theta}(x,\xi))\left(1-\frac{1}{\hat{g}(x)}\right)\\
+&=  \hat{f}(\xi)\sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi) \left(\int_{\mathbb{R}^n} \hat{g}(y) q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy) -1\right) -\hat{f}(\xi)\sum_{(x,u) \in \xi } \theta \mu_{\epsilon,\theta}(x,\Xi)\left(1-\frac{1}{\hat{g}(x)}\right),
 \end{align*}
-which corresponds to a spatial-branching process that branches at rate $\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)$ leaving offspring around with kernel $ q^{\mathfrak{m}}_{\varepsilon,\theta}(x,\Xi,dy)$ and each particle having death rate given by $\theta \mu_{\varepsilon,\theta}(x,\Xi)$.
+which corresponds to a spatial-branching process that branches at rate $\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)$ leaving offspring around with kernel $ q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy)$ and each particle having death rate given by $\theta \mu_{\epsilon,\theta}(x,\Xi)$.
 This is precisely the martingale problem in Definition \ref{def: Martingale Problem Characterisation - Product Form}.
 \newpage
-\subsection{Markov Mapping Theorem Application on Generator $A^{\text{nl}}_{\varepsilon}$}\label{sec: Markov Mapping Theorem application - limit}
+\subsection{Markov Mapping Theorem Application on Generator $A^{\text{nl}}_{\epsilon}$}\label{sec: Markov Mapping Theorem application - limit}
 In this section we consider a general generator limit for the lookdown representation of our spatial model. 
@@
 \begin{aligned}
-A^{\text{nl}}_{\varepsilon}f(\eta )  =&f(\eta )\sum_{(x,u)\in\eta}\Bigg\{
- \gamma(x, (\varrho_{\varepsilon}*\Xi)(x))
- \frac{\mathcal{B}(g(\cdot,u)r( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)-g(x,u)\mathcal{B}r( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)}{g(x,u)}\\
+A^{\text{nl}}_{\epsilon}f(\eta )  =&f(\eta )\sum_{(x,u)\in\eta}\Bigg\{
+ \gamma(x, (\rho_{\epsilon}*\Xi)(x))
+ \frac{\mathcal{B}(g(\cdot,u)r( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)-g(x,u)\mathcal{B}r( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)}{g(x,u)}\\
  &
-  +2\gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x))\times \ell \int_u^{
+  +2\gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\times \ell \int_u^{
 \infty}(g(x,v_1)-1)dv_1\\
 &
-+\bigg(\ell \gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x)) u^2 \\
-&~~~~~~~-\big(F(x, (\varrho_{\varepsilon}*\Xi)(x))+\gamma(x, (\varrho_{\varepsilon}*\Xi)(x))\mathcal{B}r( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)\big)u\bigg) \frac {\partial_u g(x,u)}{g(x,u)}\Bigg\},
++\bigg(\ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x)) u^2 \\
+&~~~~~~~-\big(F(x, (\rho_{\epsilon}*\Xi)(x))+\gamma(x, (\rho_{\epsilon}*\Xi)(x))\mathcal{B}r( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)\big)u\bigg) \frac {\partial_u g(x,u)}{g(x,u)}\Bigg\},
 \end{aligned}    
@@
 
-If we take $\gamma =1, r=1, \mathcal{B}=\Delta,$ and $F(x, (\varrho_{\varepsilon}*\Xi)(x))=G( (\varrho_{\varepsilon}*\Xi)(x))-H( (\varrho_{\varepsilon}*\Xi)(x))$, then we recover $A^{\varepsilon, \infty}$ defined in Equation \eqref{Eq: Non-local Scaling limit Lookdown Generator}.
+If we take $\gamma =1, r=1, \mathcal{B}=\Delta,$ and $F(x, (\rho_{\epsilon}*\Xi)(x))=G( (\rho_{\epsilon}*\Xi)(x))-H( (\rho_{\epsilon}*\Xi)(x))$, then we recover $A^{\epsilon, \infty}$ defined in Equation \eqref{Eq: Non-local Scaling limit Lookdown Generator}.
 
@@
 Poisson random measure $\eta^{\infty}$ on $\mathbb{R}^d\times [0,\infty)$ with mean measure
-$\Xi(dx)\times \Lambda$ and we calculate $\alpha A^{\text{nl}}_{\varepsilon}f(\eta)$.
+$\Xi(dx)\times \Lambda$ and we calculate $\alpha A^{\text{nl}}_{\epsilon}f(\eta)$.
 
 Once again, we write
-$$\alpha A^{\text{nl}}_{\varepsilon}f(\eta)=\alpha A^{1}_{nl}f(\eta)+\alpha A^{2}_{nl}f(\eta)+\alpha A^{3}_{nl}f(\eta),$$
+$$\alpha A^{\text{nl}}_{\epsilon}f(\eta)=\alpha A^{1}_{nl}f(\eta)+\alpha A^{2}_{nl}f(\eta)+\alpha A^{3}_{nl}f(\eta),$$
 where 
@@
 A^{1}_{nl}f(\eta )  =&f(\eta )\sum_{(x,u)\in\eta}
- \gamma(x, (\varrho_{\varepsilon}*\Xi)(x))
- \frac{B(g(\cdot,u)r( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)-g(x,u)Br( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)}{g(x,u)},\\
+ \gamma(x, (\rho_{\epsilon}*\Xi)(x))
+ \frac{B(g(\cdot,u)r( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)-g(x,u)Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)}{g(x,u)},\\
 A^{2}_{nl}f(\eta )  = &
-  f(\eta )\sum_{(x,u)\in\eta}2\gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x))\times \ell \int_u^{
+  f(\eta )\sum_{(x,u)\in\eta}2\gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\times \ell \int_u^{
 \infty}(g(x,v_1)-1)dv_1,\\
  A^{3}_{nl}f(\eta )  =&f(\eta )
-\sum_{(x,u)\in\eta}\bigg(\ell \gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x)) u^2\\
-&\qquad \qquad \qquad \qquad -\big(F(x, (\varrho_{\varepsilon}*\Xi)(x))+\gamma(x, (\varrho_{\varepsilon}*\Xi)(x))Br( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)\big)u\bigg)\frac {\partial_u g(x,u)}{g(x,u)}\\
+\sum_{(x,u)\in\eta}\bigg(\ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x)) u^2\\
+&\qquad \qquad \qquad \qquad -\big(F(x, (\rho_{\epsilon}*\Xi)(x))+\gamma(x, (\rho_{\epsilon}*\Xi)(x))Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)\big)u\bigg)\frac {\partial_u g(x,u)}{g(x,u)}\\
 \end{aligned}    
@@
 \alpha A^{1}_{nl}f(\eta )  =&
- \alpha \left\{\sum_{(x,u)\in\eta}\gamma(x, (\varrho_{\varepsilon}*\Xi)(x))\frac{B(g(\cdot,u)r( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)-g(x,u)Br( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)}{g(x,u)}\prod_{(x_i,u_i)}g(x_i,u_i)\right\}\\
- =&\int\int \bigg( \gamma(x, (\varrho_{\varepsilon}*\Xi)(x))B((g(\cdot,u)-1)r( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)-(g(x,u)-1)Br( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)\bigg)du \Xi(dx)\\
+ \alpha \left\{\sum_{(x,u)\in\eta}\gamma(x, (\rho_{\epsilon}*\Xi)(x))\frac{B(g(\cdot,u)r( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)-g(x,u)Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)}{g(x,u)}\prod_{(x_i,u_i)}g(x_i,u_i)\right\}\\
+ =&\int\int \bigg( \gamma(x, (\rho_{\epsilon}*\Xi)(x))B((g(\cdot,u)-1)r( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)-(g(x,u)-1)Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)\bigg)du \Xi(dx)\\
  &\times \exp \left(\int\int \big(g(x,u)-1\big) du \Xi(dx)\right),\\
- =& \left\langle \gamma(x, (\varrho_{\varepsilon}*\Xi)(x))B(h(\cdot) r( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)-h(\cdot)Br( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x),\Xi(dx) \right\rangle e^{-\langle h(x),\Xi(dx)\rangle} \\
+ =& \left\langle \gamma(x, (\rho_{\epsilon}*\Xi)(x))B(h(\cdot) r( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)-h(\cdot)Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x),\Xi(dx) \right\rangle e^{-\langle h(x),\Xi(dx)\rangle} \\
  \alpha A^{2}_{nl}f(\eta )  = &
-   \alpha \left\{2\sum_{(x,u)\in\eta}\gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x))\times \ell \int_u^{
+   \alpha \left\{2\sum_{(x,u)\in\eta}\gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\times \ell \int_u^{
 \infty}(g(x,v_1)-1)dv_1\prod_{(x_i,u_i)}g(x_i,u_i)\right\}\\
-=& \int\int \bigg(g(x,u)\gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x))\times \ell \int_u^{
+=& \int\int \bigg(g(x,u)\gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\times \ell \int_u^{
 \infty}(g(x,v_1)-1)dv_1\bigg)du \Xi(dx)e^{-\langle h(x),\Xi(dx)\rangle}\\
 =& 
-\left\langle \ell \gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x))\int g(x,u)\int_u^{
+\left\langle \ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\int g(x,u)\int_u^{
 \infty}(g(x,v_1)-1)dv_1 du,\Xi(dx)\right\rangle e^{-\langle h(x),\Xi(dx)\rangle}\\
  \alpha A^{3}_{nl}f(\eta )  =&
-\alpha \Bigg\{\sum_{(x,u)\in\eta}\bigg(\ell \gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x)) u^2 -\big(F(x, (\varrho_{\varepsilon}*\Xi)(x))+\gamma(x, (\varrho_{\varepsilon}*\Xi)(x))Br( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)\big)u\bigg)\\
+\alpha \Bigg\{\sum_{(x,u)\in\eta}\bigg(\ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x)) u^2 -\big(F(x, (\rho_{\epsilon}*\Xi)(x))+\gamma(x, (\rho_{\epsilon}*\Xi)(x))Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)\big)u\bigg)\\
 &\times \frac {\partial_u g(x,u)}{g(x,u)}\prod_{(x_i,u_i)}g(x_i,u_i)\Bigg\}\\
-=& \bigg \langle \ell \gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x))\int \partial_u g(x,u) u^2 du \\
-& ~~~ - \big(F(x, (\varrho_{\varepsilon}*\Xi)(x))+\gamma(x, (\varrho_{\varepsilon}*\Xi)(x))Br( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)\big) \int u \partial_u g(x,u) du ,\Xi(dx)\bigg\rangle \times e^{-\langle h(x),\Xi(dx)\rangle} .
+=& \bigg \langle \ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\int \partial_u g(x,u) u^2 du \\
+& ~~~ - \big(F(x, (\rho_{\epsilon}*\Xi)(x))+\gamma(x, (\rho_{\epsilon}*\Xi)(x))Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)\big) \int u \partial_u g(x,u) du ,\Xi(dx)\bigg\rangle \times e^{-\langle h(x),\Xi(dx)\rangle} .
  \end{aligned}    
@@
 \begin{multline}
- \ell \gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x))  \int_{0}^{\infty}\partial_u g(x,u) u^2 du  \\=  2\ell\gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x))\int_{0}^{\infty} u (g(x,u)-1) du,
+ \ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))  \int_{0}^{\infty}\partial_u g(x,u) u^2 du  \\=  2\ell\gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\int_{0}^{\infty} u (g(x,u)-1) du,
 \end{multline}
 \begin{multline}
- \big(F(x, (\varrho_{\varepsilon}*\Xi)(x))+\gamma(x, (\varrho_{\varepsilon}*\Xi)(x))Br( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)\big)\int_{0}^{\infty} u \partial_u g(x,u)du \\=\big(F(x, (\varrho_{\varepsilon}*\Xi)(x))+\gamma(x, (\varrho_{\varepsilon}*\Xi)(x))Br( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)\big)\int_{0}^{\infty} (g(x,u)-1) du\\
- =-\big(F(x, (\varrho_{\varepsilon}*\Xi)(x))+\gamma(x, (\varrho_{\varepsilon}*\Xi)(x))Br( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)\big) h(x)
+ \big(F(x, (\rho_{\epsilon}*\Xi)(x))+\gamma(x, (\rho_{\epsilon}*\Xi)(x))Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)\big)\int_{0}^{\infty} u \partial_u g(x,u)du \\=\big(F(x, (\rho_{\epsilon}*\Xi)(x))+\gamma(x, (\rho_{\epsilon}*\Xi)(x))Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)\big)\int_{0}^{\infty} (g(x,u)-1) du\\
+ =-\big(F(x, (\rho_{\epsilon}*\Xi)(x))+\gamma(x, (\rho_{\epsilon}*\Xi)(x))Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)\big) h(x)
 \end{multline}
@@
 \begin{multline}
-  2 \ell \gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x)) \int_{0}^{\infty} u    (g(x,u)-1) du \\
-  =   2 \ell \gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x)) \int_{0}^{\infty} \int_{0}^{u}    dv_1 (g(x,u)-1) du \\
-  =  2 \ell \gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x)) \int_{0}^{\infty}  \int_{v_1}^{\infty}    (g(x,u)-1) du dv_1.
+  2 \ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x)) \int_{0}^{\infty} u    (g(x,u)-1) du \\
+  =   2 \ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x)) \int_{0}^{\infty} \int_{0}^{u}    dv_1 (g(x,u)-1) du \\
+  =  2 \ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x)) \int_{0}^{\infty}  \int_{v_1}^{\infty}    (g(x,u)-1) du dv_1.
 \end{multline}
@@
 \begin{multline}
-\int 2\bigg(g(x,u)\gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x))\times \ell \int_u^{
+\int 2\bigg(g(x,u)\gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\times \ell \int_u^{
 \infty}(g(x,v_1)-1)dv_1\bigg)du\\
-= 2\ell \gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x))\int \bigg( g(x,u) \int_u^{
+= 2\ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\int \bigg( g(x,u) \int_u^{
 \infty}(g(x,v_1)-1)dv_1\bigg)du.
@@
 \begin{aligned}
-\alpha A^{\text{nl}}_{\varepsilon}f(\eta)
-=&~ e^{-\langle h(x),\Xi(dx)\rangle}  \Bigg\{\left\langle \gamma(x, (\varrho_{\varepsilon}*\Xi)(x))B(h(\cdot) r( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)-h(\cdot)Br( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x),\Xi(dx) \right\rangle\\
-&+\bigg \langle2\ell\gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x))\int_{0}^{\infty} u (g(x,u)-1) du \\
- &+ \big(F(x, (\varrho_{\varepsilon}*\Xi)(x))+\gamma(x, (\varrho_{\varepsilon}*\Xi)(x))Br( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)\big) h(x) ,\Xi(dx)\bigg\rangle\\
- & +\left\langle 2 \ell \gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x))\int g(x,u)\int_u^{
+\alpha A^{\text{nl}}_{\epsilon}f(\eta)
+=&~ e^{-\langle h(x),\Xi(dx)\rangle}  \Bigg\{\left\langle \gamma(x, (\rho_{\epsilon}*\Xi)(x))B(h(\cdot) r( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)-h(\cdot)Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x),\Xi(dx) \right\rangle\\
+&+\bigg \langle2\ell\gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\int_{0}^{\infty} u (g(x,u)-1) du \\
+ &+ \big(F(x, (\rho_{\epsilon}*\Xi)(x))+\gamma(x, (\rho_{\epsilon}*\Xi)(x))Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)\big) h(x) ,\Xi(dx)\bigg\rangle\\
+ & +\left\langle 2 \ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\int g(x,u)\int_u^{
 \infty}(g(x,v_1)-1)dv_1 du,\Xi(dx)\right\rangle \Bigg\}\\
-=&~ e^{-\langle h(x),\Xi(dx)\rangle}  \Bigg\{\left\langle \gamma(x, (\varrho_{\varepsilon}*\Xi)(x))B(h(\cdot) r( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)+ F(x, (\varrho_{\varepsilon}*\Xi)(x),\Xi(dx) \right\rangle\\
-&+\bigg \langle 2 \ell \gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x)) \int_{0}^{\infty}  \int_{v_1}^{\infty}    (g(x,u)-1) du dv_1 \\
- & + 2\ell \gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x))\int_0^{\infty} g(x,u)\int_u^{
+=&~ e^{-\langle h(x),\Xi(dx)\rangle}  \Bigg\{\left\langle \gamma(x, (\rho_{\epsilon}*\Xi)(x))B(h(\cdot) r( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)+ F(x, (\rho_{\epsilon}*\Xi)(x),\Xi(dx) \right\rangle\\
+&+\bigg \langle 2 \ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x)) \int_{0}^{\infty}  \int_{v_1}^{\infty}    (g(x,u)-1) du dv_1 \\
+ & + 2\ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\int_0^{\infty} g(x,u)\int_u^{
 \infty}(g(x,v_1)-1)dv_1 du,\Xi(dx)\bigg\rangle \Bigg\}\\
-=&~ e^{-\langle h(x),\Xi(dx)\rangle}  \Bigg\{\bigg\langle \gamma(x, (\varrho_{\varepsilon}*\Xi)(x))B(h(\cdot) r( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)+ F(x, (\varrho_{\varepsilon}*\Xi)(x)\\
-& + \ell \gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x))2 \int_0^{\infty} (g(x,u)-1)\int_u^{
+=&~ e^{-\langle h(x),\Xi(dx)\rangle}  \Bigg\{\bigg\langle \gamma(x, (\rho_{\epsilon}*\Xi)(x))B(h(\cdot) r( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)+ F(x, (\rho_{\epsilon}*\Xi)(x)\\
+& + \ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))2 \int_0^{\infty} (g(x,u)-1)\int_u^{
 \infty}(g(x,v_1)-1)dv_1 du,\Xi(dx)\bigg\rangle \Bigg\}\\
-=&~ e^{-\langle h(x),\Xi(dx)\rangle} \times \Bigg\{\bigg\langle \gamma(x, (\varrho_{\varepsilon}*\Xi)(x))B(h(\cdot) r( \cdot, (\varrho_{\varepsilon}* \Xi)(\cdot))(x)+ F(x, (\varrho_{\varepsilon}*\Xi)(x)\\
-& + \ell \gamma(x, (\varrho_{\varepsilon}*\Xi)(x)) r(x, (\varrho_{\varepsilon}*\Xi)(x))h(x)^2,\Xi(dx)\bigg\rangle \Bigg\}\\
-:=&~\mathcal{L}^{nl}_{\varepsilon}\alpha f(\eta),
+=&~ e^{-\langle h(x),\Xi(dx)\rangle} \times \Bigg\{\bigg\langle \gamma(x, (\rho_{\epsilon}*\Xi)(x))B(h(\cdot) r( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)+ F(x, (\rho_{\epsilon}*\Xi)(x)\\
+& + \ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))h(x)^2,\Xi(dx)\bigg\rangle \Bigg\}\\
+:=&~\mathcal{L}^{nl}_{\epsilon}\alpha f(\eta),
 \end{aligned}
@@
 \normalsize
-where $\mathcal{L}^{nl}_{\varepsilon}$ is the generator of a non-linear superprocess of the form characterised in Equation \eqref{eq: Empirical Measure Martingale characterisation - product form}.
+where $\mathcal{L}^{nl}_{\epsilon}$ is the generator of a non-linear superprocess of the form characterised in Equation \eqref{eq: Empirical Measure Martingale characterisation - product form}.
 

### 2022-04-08 forwards-and-backwards.tex
lineage heuristics

@@
 
-\plr{
-    TODO: Heuristics for how lineages should move given the population process.
+Although our proof of Theorem\ref{thm:lineages}
+uses the explicit representation in terms of the lookdown process,
+informal calculations agree with the main result.
+Suppose that we are tracking a lineage that is at location $y$ at time $t$.
+Looking back through time, the lineage will move at the time that individual was born,
+and will jump to the location of the parent of that individual.
+Now, the rate at which new individuals are born to parents at $x$ and establish at $y$
+is
+$$
+    \gamma(x, \eta_t) q(x, dy) r(y, \eta_t) .
+$$
+This implies that the probability a randomly chosen individual near $y$
+is a new offspring from a parent at $x$ in $[t, t+dt)$ is, informally,
+\begin{equation} \label{eqn:informal_rates}
+\frac{
+    \gamma(x, \eta_t) q_\theta(x, dy) r(y, \eta_t) \eta_t(dx)
+}{
+    \eta_t(dy)
+} dt .
+\end{equation}
+Leaving aside questions of whether a lineage can be treated as a randomly chosen individual,
+we might then proceed by defining a continuous-time jump process
+whose transition rates are given by \eqref{eqn:informal_rates} given $(\eta_t)_{t=0}^T$.
+Happily, we are interested in the case when $\eta$ has a density,
+say $\eta_t(dx) = \varphi(x) dx$,
+so interpreting these rates is not too difficult.
+Now recall that $q_\theta(x, dy)$ is a Gaussian kernel
+with mean $x + \meanq/\theta$ and covariance $\covq/\theta$.
+Write $\widetilde q_\theta(y, dx)$ for the ``reverse-time'' distribution,
+i.e., Gaussian with mean $x - \meanq/\theta$ and the same covariance.
+Then, rearranging infinitesimals,
+\eqref{eqn:informal_rates} implies a rate of
+\begin{equation} \label{eqn:informal_rates2}
+\frac{
+    \varphi(x) \gamma(x, \eta_t) r(y, \eta_t)
+}{
+    \varphi(y)
+} \widetilde q_\theta(y, dx) .
+\end{equation}
+Let $(L^\theta_s)_{s=0}^T$ be the location of a lineage that moves according to
+jump rates~\eqref{eqn:informal_rates2},
+back through time (i.e., with the substitution that $s = T-t$).
+Then
+\begin{align} \label{eqn:lineage_generator_Edt}
+    \begin{split}
+    &\IE[f(L^\theta_{s+ds}) \;|\; L_s = y] - f(y)
+    \\&\qquad 
+    =
+    ds \int \left(f(x) - f(y)\right)
+    \frac{
+        \varphi_{T-s}(x) \gamma(x, \eta_{T-s}) r(y, \eta_{T-s})
+    }{
+        \varphi_{T-s}(y)
     }
+    \widetilde q_\theta(y, dx) .
+    \end{split}
+\end{align}
+Referring back to Definition~\ref{def:dispersal_generator},
+recall that as $\theta \to \infty$,
+$$
+    \theta \int (f(x) - f(y)) \widetilde q_\theta(y, dx)
+    \to
+    - \sum_i \meanq_i \partial_{x_i} f(y)
+    + \sum_{ij} \covq_{ij} \partial_{x_i x_j} f(y) ,
+$$
+which is just $\DG$ but with the first derivative terms multiplied by -1.
+\comment{The $\widetilde \DG$ and $\covq \grad$ notation here is terrible; suggestions?}
+Consequently,
+\begin{align*}
+    \theta \int (f(x) - f(y)) g(x) \widetilde q_\theta(y, dx)
+    &\approx
+    - g(y) \sum_i \meanq_i \partial_{x_i} f(y)
+    + g(y) \sum_{ij} \covq_{ij} \partial_{x_i x_j} f(y)
+    + \sum_{ij} \partial_{x_i} g(y) \covq_{ij} \partial_{x_j} f(y)  \\
+    &=
+    g(y) \widetilde \DG f(y)
+    + (\covq \grad g) \cdot \grad f ,
+\end{align*}
+if we define $\widetilde \DG$ to be the same as $\DG$ but with $-\meanq$ substituted for $\meanq$,
+and $(\covq \grad g(y))_i = \sum_j \covq_{ij} \partial_{x_j} g(y)$.
+Applying this to~\eqref{eqn:lineage_generator_Edt} with $g = \varphi_{T-s} \gamma$,
+this suggests that the generator of the limiting process is
+\begin{align*}
+    \Lgen_s f
+    &=
+    \frac{r}{\varphi_{T-s}}
+    \left\{
+        \varphi_{T-s} \gamma \widetilde \DG f
+        + \left(\covq \grad (\varphi_{T-s} \gamma) \right) \cdot \grad f 
+    \right\} \\
+    &=
+    r \gamma
+    \left\{
+        \widetilde \DG f
+        + \left(\covq \grad \log(\varphi_{T-s} \gamma) \right) \cdot \grad f 
+    \right\} .
+\end{align*}
+In other words, the lineage moves at speed equal to the local production of successful offspring,
+$r \gamma$,
+by a time-reversed version of the dispersal distribution,
+but with a drift in the direction of the gradient of the logarithm
+of the production of juveniles, $\grad \log(\phi_{T-s} \gamma)$
+(modified by the covariance of dispersal).
+This \comment{presumably?} agrees with \comment{the theorem}.
 

### 2022-04-10 forwards-and-backwards.tex
.
conceptual figure

@@
     \begin{center}
-        FIGURE
+        \includegraphics{figures/conceptual_figure}
     \end{center}
@@
         Conceptual figure of the model.
-        Left: (cartoon) plot of $\gamma$, $r$, $\mu$, and $F$ against density,
-        showing the equilibrium point.
-        Right: cartoon of interaction and dispersal distances.
+        \textbf{(A)} Example plot of $\gamma$, $\mu$, and $F$
+        (calculated with $r=1$) against scaled local population density.
+        In this example, both birth and death rates increase with population density,
+        but death increases faster,
+        and equilibrium occurs where they cross
+        (and hence where $F=0$).
+        \textb{(B)} Cartoon of interaction ($\epsilon$) and dispersal ($\sigma$) distances.
         \label{fig:model_setup}
@@
 
-Although our proof of Theorem\ref{thm:lineages}
+Although our proof of Theorem~\ref{thm:lineages}
 uses the explicit representation in terms of the lookdown process,
@@
 \begin{align*}
-    \theta \int (f(x) - f(y)) g(x) \widetilde q_\theta(y, dx)
-    &\approx
+    &
+    \theta \int (f(x) - f(y)) g(x) \widetilde q_\theta(y, dx) \\
+    &\qquad \to
     - g(y) \sum_i \meanq_i \partial_{x_i} f(y)
@@
     + \sum_{ij} \partial_{x_i} g(y) \covq_{ij} \partial_{x_j} f(y)  \\
-    &=
+    &\qquad =
     g(y) \widetilde \DG f(y)

### 2022-04-10 figures/make_conceptual_figure.R

@@ -1,0 +1,82 @@
+
+
+##########
+# diagram of continuous-space model
+
+draw_circle <- function (xy, r, radius_label, ...) {
+    xy <- unlist(xy)
+    theta <- seq(0, 2*pi, length.out=101)
+    polygon(xy[1] + r * cos(theta),
+            xy[2] + r * sin(theta), ...)
+    if (!missing(radius_label)) {
+        segments(x0=xy[1], y0=xy[2], x1=xy[1] + r)
+        text(xy[1] + r/2, xy[2], labels=radius_label, pos=3, cex=2)
+    }
+}
+
+set.seed(30)
+N <- 100
+epsilon <- 0.2
+sigma <- 0.2
+H <- 1
+W <- 1
+xy <- data.frame(
+            x=W * (runif(N) - 0.5),
+            y=H * (runif(N) - 0.5)
+        )
+
+xy <- xy[order(xy$x^2 + xy$y^2),]
+
+cairo_pdf(file="conceptual_figure.pdf", width=6, height=3, pointsize=10)
+layout(t(1:2))
+# gamma, mu
+par(mar=c(4,4,1,1), mgp=c(2.5, 0.75, 0))
+    f <- function (x, dt=0.1) { (1 - exp(-dt * x))/dt }
+    curve(f(x), lwd=2,
+          xlim=c(0, 2.5),
+          ylim=c(-0.5, 2),
+          xlab='density / N',
+          ylab='rates (per capita)'
+    )
+    theta <- 0.5
+    curve(f(x^(1+theta)), col='red', lwd=2, add=TRUE)
+    abline(v=1, lty=2)
+    abline(h=0, lty=2)
+    legend("right", lwd=2, lty=1, col=c('black', 'red', 'blue'),
+           legend=c("birth (γ)", "death (μ)", "net (F)"))
+    curve(f(x) - f(x^(1+theta)), lwd=2, col='blue', add=TRUE)
+mtext("A", adj=-0.3, line=-1, cex=1.5)
+
+# circles
+par(mar=c(1,1,1,1))
+    k <- 29
+        plot(xy$x, xy$y, type='n',
+             xlim=c(-1, 1) * W/2, ylim=c(-1, 1) * H/2,
+             asp=1, xaxt='n', xlab='', yaxt='n', ylab='')
+        draw_circle(xy[k,], epsilon, col=adjustcolor("red", 0.5), lwd=2, radius_label=expression(epsilon),
[…]

### 2022-04-11 forwards-and-backwards.tex
Update on Overleaf.

@@
 solution will converge to the profile $w^F$ with the minimal wavespeed, $c=2$,
-\cite{kolmogorov/petrovsky/piscounov:1937,bramson:1983}.
+\cite{kolmogorov/petrovsky/piscounov:1937,\meanqramson:1983}.
 No matter what the initial condition,
@@
 level. If $\kappa = 1 $, the parent is given the new level and the new particle is given the original
+
 level. Consequently, for $t \geq \tau$
@@
         =& \theta \left\{
-                    \frac{\epsilon^2_r }{\left|\covq / \theta +  \epsilon^2_r I \right|^{1/2}}
+                    \frac{\epsilon^d_r }{\left|\covq / \theta +  \epsilon^2_r I \right|^{1/2}}
                     \exp \left(
@@
 \begin{equation}
-F(s)=  \frac{\epsilon^2_r }
+F(s)=  \frac{\epsilon^d_r }
         {\left|\covq s +  \epsilon^2_r I \right|^{1/2}}
@@
 \end{equation}
-then 
+then $F(0)=0$ and
+
+\begin{align}
+F'(s)=&  -\frac{\epsilon^d_r |\covq|}
+        {2\left|\covq s +  \epsilon^2_r I \right|^{3/2}}
+        \exp \left(
+                    \frac{(x-w-\meanq s)^{T}
+                        (\covq s +  \epsilon^2_r I)^{-1}
+                        (x-w-\meanq s)}{2}
+                        -\frac{|x-w|^2}{2\epsilon^2}
+            \right)\\
+    &+\frac{\epsilon^d_r }
+        {\left|\covq s +  \epsilon^2_r I \right|^{1/2}}
+        \exp \left(
+                    \frac{(x-w-\meanq s)^{T}
+                        (\covq s +  \epsilon^2_r I)^{-1}
+                        (x-w-\meanq s)}{2}
+                        -\frac{|x-w|^2}{2\epsilon^2}
+            \right) \\
+    & \qquad \times \frac{1}{2}
+                    \bigg\{
+                         -\meanq^{T}(\covq s + \epsilon^2_r I)^{-1}(x-w-\meanq s)\\
+    & \qquad \qquad     -(x-w-\meanq s)^{T}
+                        (\covq s +  \epsilon^2_r I)^{-1}\meanq\\
+    & \qquad \qquad     -(x-w-\meanq s)^{T}
+                        \covq(\covq s +  \epsilon^2_r I)^{-2}(x-w-\meanq s)                    
+                    \bigg\},
+\end{align}
+which is continuous and bounded near $s=0$.
+As a result,
 \begin{align}
@@
         \right|
-        \leq  \theta \left(F\left(1 / \theta \right)-1\right) 
+        \leq&  \theta \left(F\left(1 / \theta \right)-1\right) 
                 \times \epsilon_\gamma^d \epsilon_r^{-d}
-                p_{\epsilon^2_\gamma}(x-w),
-\end{align}
-so we have our bound 
-as $F(x)$ has bounded derivative in a neighbourhood around $0$.
+                p_{\epsilon^2_\gamma}(x-w)\\
+         =&  F'(u) 
+                \times \epsilon_\gamma^d \epsilon_r^{-d}
+                p_{\epsilon^2_\gamma}(x-w)        
+\end{align}
+for some $u \in [0, 1/\theta]$ by Intermediate Value Theorem. We have therefore established our bound as $F(s)$ has bounded derivative in a neighbourhood around $0$.
 
@@
 \begin{equation}
+    \label{eq: gamma-r convolution comparison}
 \begin{aligned}
@@
             \leq & \int \epsilon_\gamma^d \epsilon_r^{-d}
-                   e^{-(x-w)^2(\frac{1}{\varepsilon^2_r}-\frac{1}{\varepsilon^2_\gamma})}
+                   e^{-(x-w)^2(\frac{1}{\epsilon^2_r}-\frac{1}{\epsilon^2_\gamma})}
                    p_{\epsilon^2_\gamma}(x-w) \eta(dw)\\
@@
 q_{\theta}(x,dy).$$
-
+Writing out $H$,
+\begin{align}
+H_\theta(x, w)
+=
+\int
+    \left(
+        \exp\left(
+            - \frac{1}{2\epsilon_r^2}
+            \left\{
+                ||y - w||^2 - ||x - w||^2
+            \right\}
+        \right)
+        -
+        1
+    \right)^2
+    \frac{
+        e^{-\theta (y - x-\meanq)^{T}\covq^{-1}(y - x-\meanq)  / 2}
+    }{
+        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
+    }
+dy.
+\end{align}
+Writing $z=y-x-\meanq$, we have that 
+\begin{equation}
+\begin{aligned}
+||y - w||^2 - ||x - w||^2 
+=& ||y||^2-||x||^2 -2\langle y-x, w\rangle \\
+=&||x+z+ \meanq||^2-||x||^2-2 \langle z+ \meanq, w\rangle\\
+=&2\langle x, z+ \meanq \rangle + ||z+ \meanq||^2-2 \langle z+ \meanq, w\rangle \\
+=& 2 \langle x-w, z+ \meanq \rangle + ||z+ \meanq||^2\\
+=& 2\langle x-w+ \meanq,\meanq \rangle + 2\langle x-w+ \meanq, z \rangle +||z||^2
+\end{aligned}
+\end{equation}
+As a result, we have 
+\begin{align}
+H_\theta(x, w)
+=&
+\int
+    \left(
+        \exp\left(
+            - \frac{1}{2\epsilon_r^2}
+            \left\{
+                2 \langle x-w, z+ \meanq \rangle + ||z+ \meanq||^2
+            \right\}
+        \right)
+        -
+        1
+    \right)^2
+    \frac{
+        e^{-\theta z^{T}\covq^{-1}z  / 2}
+    }{
+        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
+    }
+dz\\
+=&\exp\left(-\frac{2}{\epsilon_r^2}\langle x-w+ \meanq,\meanq \rangle \right)\\
+& \times \int
+        \frac{
+        \exp\left(
+            - \frac{2}{\epsilon_r^2} \langle x-w+ \meanq, z \rangle
+            - \frac{1}{\epsilon_r^2} ||z||^2
+            \right)
+            e^{-\theta z^{T}\covq^{-1}z  / 2}
+    }{
+        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
+    }
+dz\\ \label{eq: Second moment term matrix calculation}
+&-2\exp\left(-\frac{1}{\epsilon_r^2}\langle x-w+ \meanq,\meanq \rangle \right)\\
+& \qquad \qquad \times     \int
+    \frac{ \exp\left(
+             -\frac{1}{\epsilon_r^2}\langle x-w+ \meanq, z \rangle
+              -\frac{1}{2\epsilon_r^2} ||z||^2
+            \right)e^{-\theta z^{T}\covq^{-1}z  / 2}
+        }{
+        (2 \pi/ \theta)^{d/2} |\covq|^{1/2} \label{eq: first moment term matrix calculation}
+    }
+dz\\
+&+1.
+\end{align}
+We now consider the integral of the form 
+\begin{equation}
+\int \exp(v^{T}z-C||z||^2) \frac{
+        e^{-\theta z^{T}\covq^{-1}z  / 2}
+    }{
+        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
+    }
+dz   
+\end{equation}
+for $v \in \mathbb{R}^d$ and $C>0$. 
+We have 
+\begin{equation}
+\begin{aligned}
+&\int \exp(v^{T}z-C||z||^2) \frac{
+        e^{-\theta z^{T}\covq^{-1}z  / 2}
+    }{
+        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
+    }
+dz\\
+=&\frac{1}{|\covq|^{1/2}|  |\covq^{-1}(I+2C\covq/\theta )|^{1/2}  }\int \exp(v^{T}z) \frac{
+        e^{-\theta z^{T}\covq^{-1}(I+2C\covq/\theta )z  / 2}
+    }{
+        (2 \pi/ \theta)^{d/2}|\covq^{-1}(I+2C\covq/\theta )|^{-1/2} 
+    }
+dz\\
+=& \frac{1}{|I+2C\covq/\theta |^{1/2}} \mathbb{E}_{Z}[\exp (v^{T}Z)]\\
+=&\frac{1}{|I+2C\covq/\theta |^{1/2}}
+\exp 
+\left(
+\frac{1}{2}v^{T}\covq/\theta(I+2C\covq/\theta )^{-1}v
+\right),
+\end{aligned}
+\end{equation}
+where $Z \sim N(0, \covq/\theta \times (I+2C\covq/\theta )^{-1})$.
+
+Now writing $v=\frac{2}{\epsilon_r^2}( w-x-\meanq)$
+and $C=\frac{1}{\epsilon_r^2}$,
+we have the expression in Equation
+\eqref{eq: Second moment term matrix calculation} is 
+$$\frac{1}{|I+2\covq/(\epsilon_r^2\theta) |^{1/2}}
+\exp 
+\left(
+\frac{2}{\epsilon_r^4}( w-x-\meanq)^{T}\covq/\theta\left(I+2\covq/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
+\right).$$
+Similarly, writing $v=\frac{1}{\epsilon_r^2}( w-x-\meanq)$
+and $C=\frac{1}{2\epsilon_r^2}$,
+we have the expression in Equation
+\eqref{eq: first moment term matrix calculation} is 
+$$\frac{1}{|I+\covq/(\epsilon_r^2\theta) |^{1/2}}
+\exp 
+\left(
+\frac{1}{2\epsilon_r^4}( w-x-\meanq)^{T}\covq\left(I+\covq/\theta/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
+\right).$$
+As a result, we have 
+\begin{align*}
+&H_{\theta}(x,w)\\
+=& \frac{1}{|I+2\covq/(\epsilon_r^2\theta) |^{1/2}}
+\exp 
+\left(
+\frac{2}{\epsilon_r^4}( w-x-\meanq)^{T}\covq/\theta\left(I+2\covq/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
+\right)\\
+&-2\frac{1}{|I+\covq/(\epsilon_r^2\theta) |^{1/2}}
+\exp 
+\left(
+\frac{1}{2\epsilon_r^4}( w-x-\meanq)^{T}\covq/\theta\left(I+\covq/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
+\right)\\
+&+1.
+\end{align*}
+If we write $F(1/\theta)=H_{\theta}(x,w)$, i.e.
+\begin{align*}
+&F(s)\\
+=& \frac{1}{|I+2/\epsilon_r^2 \covq s |^{1/2}}
+\exp 
+\left(
+\frac{2}{\epsilon_r^4}( w-x-\meanq)^{T}\covq s \left(I+2/\epsilon_r^2 \covq s\right)^{-1}( w-x-\meanq)
+\right)\\
+&-2\frac{1}{|I+2/\epsilon_r^2 \covq s |^{1/2}}
+\exp 
+\left(
+\frac{1}{2\epsilon_r^4}( w-x-\meanq)^{T}\covq s \left(I+2/\epsilon_r^2 \covq s\right)^{-1}( w-x-\meanq)
+\right)\\
+&+1\\
+&=G_1(s)+2G_2(s)+1
+\end{align*}
+we can check that $F(0)=0$.
+As a result, 
+$$\theta H_{\theta}(x,w)\rho_r(x-w)= \theta F(1/\theta)\rho_r(x-w)=F'(s)\rho_r(x-w),$$
+for some $s \in [0, 1/\theta]$.
+
+In Equation \eqref{eq: gamma-r convolution comparison}, we have established that 
+$\rho_r(x-w) / \rho_\gamma(x-w) = C' \exp(-K (x-w)^2 / 2)$
+with $K = \frac{1}{\epsilon_r^2} - \frac{1}{\epsilon_\gamma^2}$.
+Therefore it suffices to show that for all $x,w \in \mathbb{R}^d$ and $s \in [0, 1/\theta]$, 
+\begin{align} \label{eqn:goal3}
+    F'(s) \exp\left(-A (x-w)^2 \right) \le C .
+\end{align}
+
+We consider how to differentiate function $G$ of the form 
+$$G(s):=\frac{1}{|I+As|^{1/2}}\exp(v^{T}Bs(I+Cs)^{-1}v),$$
+where $A,B,C$ are matrices with non-negative entries and $I$ is the identity matrix.
+
+Since 
+\begin{equation}
+\begin{aligned}
+G'(s)=& - \frac{|A|}{2|I+As|^{3/2}}\exp(v^{T}Bs(I+Cs)^{-1}v)\\
+      & + \frac{1}{|I+As|^{1/2}}\exp(v^{T}Bs(I+Cs)^{-1}v)\\
+      & \qquad \times \left\{ v^{T}B(I+Cs)^{-1}v
+                            - sv^{T}BC(I+Cs)^{-2}v
+                    \right\}\\
+      &=\left(- \frac{|A|}{2|I+As|}+v^{T}B(I+Cs)^{-2}v
+        \right)\\
+      & \qquad \times
+        \frac{1}{|I+As|^{1/2}}\exp(v^{T}Bs(I+Cs)^{-1}v),
+\end{aligned}
+\end{equation}
+using non-negativity of $A,B,C$ we have
+\begin{equation}
+\label{eq: bounds on G'}
+|G'(s)| \leq (|A|+||B||_{2}||v||_2^2)G(s).    
+\end{equation}
+As a result, we have that 
+\begin{equation}
+\label{eq: bounds on G}
+G(s) \leq K e^{|A|+||B||_{2}||v||_2^2)s}.    
+\end{equation}
+
+Finally note that, 
+$$F'(s) \leq G_1'(s)+2G_2'(s),$$
+where 
+$$A_1= 2\epsilon_r^{-2} \covq, ~ v_1=\epsilon_r^{-2}(w-x-\meanq), ~B_1 = 2\covq, ~C_1=2\epsilon_r^{-2} \covq,$$
+and 
+$$A_2= 2\epsilon_r^{-2} \covq, ~ v_2=\epsilon_r^{-2}(w-x-\meanq), ~B_2 = \covq/2, ~C_2=2\epsilon_r^{-2} \covq,$$
+Substituting these quantities on Equation \eqref{eq: bounds on G'} and Equation \eqref{eq: bounds on G} shows that Equation \eqref{eqn:goal3} is satisfied as long as $\epsilon_r < \epsilon_\gamma$.
 \end{proof}
+
 \begin{lemma}[Compact Containment for the population process]
@@
 We first take $f \equiv 1$ in Equation \eqref{eq: Pre-limit Martingale Characterisation}. We have that 
-
 \begin{equation}
@@
     \item The process $(\gamma_M \circ \xi^{\theta}_t)_{t \geq 0}:= \left(\frac{1}{\lambda}\sum_{(x,u)\in \xi^{\theta}_t, u < \lambda} \delta_x\right)_{t \geq 0}=(\Xi^{\theta}_t)_{t \geq 0}$ solves the Martingale Problem \eqref{Markov Mapping Theorem Martingale Condition Simplified}.
-    \item $\mathbb{P}\{\xi^{\theta}_t \in B | \mathcal{F}^{\Xi^{\theta}}_t\}=\alpha_M(\Xi^{\theta}(t),B), ~~~B \in \mathcal{B}(\mathcal{M}(\mathbb{R}^d \times [0,\lambda])).$
+    \item $\mathbb{P}\{\xi^{\theta}_t \in B | \mathcal{F}^{\Xi^{\theta}}_t\}=\alpha_M(\Xi^{\theta}(t),\meanq), ~~~B \in \mathcal{B}(\mathcal{M}(\mathbb{R}^d \times [0,\lambda])).$
 \end{enumerate}

### 2022-04-14 forwards-and-backwards.tex
Update on Overleaf.

@@
         (and hence where $F=0$).
-        \textb{(B)} Cartoon of interaction ($\epsilon$) and dispersal ($\sigma$) distances.
+        \textbf{(B)} Cartoon of interaction ($\epsilon$) and dispersal ($\sigma$) distances.
         \label{fig:model_setup}
@@
                             \eta^{\theta}_{s}(dx)
-     \\ & \qquad {} +\int 
+     \\ & \qquad \qquad {} +\int 
      f(x)F\big(x,\rho_{F}*\eta^{\theta}_{s}(x)\big)
@@
 solution will converge to the profile $w^F$ with the minimal wavespeed, $c=2$,
-\cite{kolmogorov/petrovsky/piscounov:1937,\meanqramson:1983}.
+\cite{kolmogorov/petrovsky/piscounov:1937,ramson:1983}.
 No matter what the initial condition,
@@
 \label{eq: bounds on G}
-G(s) \leq K e^{|A|+||B||_{2}||v||_2^2)s}.    
+G(s) \leq K e^{|A|+||B||_{2}||v||_2^2)s}, ~~   G'(s)(|A|+||B||_{2}||v||_2^2)K e^{|A|+||B||_{2}||v||_2^2)s}.  
 \end{equation}
@@
 $$A_2= 2\epsilon_r^{-2} \covq, ~ v_2=\epsilon_r^{-2}(w-x-\meanq), ~B_2 = \covq/2, ~C_2=2\epsilon_r^{-2} \covq,$$
-Substituting these quantities on Equation \eqref{eq: bounds on G'} and Equation \eqref{eq: bounds on G} shows that Equation \eqref{eqn:goal3} is satisfied as long as $\epsilon_r < \epsilon_\gamma$.
+Substituting these quantities on Equation \eqref{eq: bounds on G} shows that Equation \eqref{eqn:goal3} is satisfied as long as $\epsilon_r < \epsilon_\gamma$.
 \end{proof}
@@
 \begin{lemma}[Compact Containment for the population process]
+    \label{lem: Compact Containment}
 Assume that $\eta^{\theta}_0 \to \eta_0$ weakly,
@@
 uniformly in $\theta$.
+In particular, for any $\epsilon > 0$, there exists some $K_{\epsilon}>0$ such that
+\begin{equation}
+\limsup_{\theta \to \infty}
+    \mathbb{P}\left[\sup_{s \in [0,T]}
+        \langle 1 ,\eta^{\theta}_{s}\rangle
+        > K_\epsilon \right]
+        \leq \frac{C(T)}{K_{\epsilon}} < \epsilon.    
+\end{equation}
 \end{lemma}
@@
 
-\subsubsection{Controlling Jumps}
-To apply Aldous-Rebolledo criterion,
-(or see Theorem 3.9.1 or Theorem 3.8.6 in \cite{EK})
-it suffices to show that for all $f \in \mathcal{C}^2_{c}(\mathbb{R}^d)$
-and $\tau \in [0,T]$, we have 
+\subsubsection{Tightness of $(\langle f, \eta^{\theta}_t \rangle )_{t>0}$}
+\begin{theorem}[Tightness of $(\langle f, \eta^{\theta}_t \rangle )_{t>0}$]
+    \label{teo: Tightness of real-valued projections}
+For all $f \in C^{2}_{0}(\mathbb{R}^d)$, 
+the process
+$(\langle f, \eta^{\theta}_t \rangle)_{t \geq 0}$ is tight.
+\end{theorem}
+\begin{proof}
+We apply the Aldous-Rebolledo criterion \cite{rebolledo:1980}.
+It suffices to show that for all stopping time
+$\tau \in [0,T]$ and for each $\epsilon>0$, there exists $\delta>0$ and $\theta_0>0$ such that 
 \begin{equation}
 \begin{aligned}
-\limsup_{s \to 0}\limsup_{\theta \to \infty}\mathbb{E}\left[\left| \langle f, \eta^{\theta}_{\tau+s}\rangle - \langle f, \eta^{\theta}_{\tau}\rangle \right|\right]& \to 0;\\
-\limsup_{s \to 0}\limsup_{\theta \to \infty}\mathbb{E}\left[\big| [M^{\theta}_{\tau+s}(f)] - [M^{\theta}_{\tau}(f)] \big|\right]& \to 0.
+\sup_{\theta > \theta_0}
+\sup_{s \in [0, \delta]}
+\mathbb{P}\left[\left| \langle f, \eta^{\theta}_{\tau+s}\rangle
+                        - \langle f, \eta^{\theta}_{\tau}\rangle
+                \right|> \epsilon \right]
+                & < \epsilon;\\
+\sup_{\theta > \theta_0}
+\sup_{s \in [0, \delta]}
+\mathbb{P}\left[\big| [M^{\theta}_{\tau+s}(f)] 
+                        - [M^{\theta}_{\tau}(f)] \big|
+                        > \epsilon\right]
+                & < \epsilon.
 \end{aligned}    
@@
 \begin{multline}
-\mathbb{E}\left[\left| \langle f, \eta^{\theta}_{\tau+s}\rangle - \langle f, \eta^{\theta}_{\tau}\rangle \right|\right] \\
-\leq (C_{\gamma,r}||f||_{\infty} + C_{\gamma,r}||\Delta f||_{\infty}+C_F||f||_{\infty}) \mathbb{E}\bigg\{\int_{\tau}^{\tau+s}\bigg\langle 1,\eta^{\theta}_{s}(dx)  \bigg\rangle  ds\bigg\} \\
-\leq (C_{\gamma,r}||f||_{\infty} + C_{\gamma,r}||\Delta f||_{\infty}+C_F||f||_{\infty}) \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle]e^{(C_{\gamma,r}+C_F)T}(e^s-1)\to 0
+\mathbb{E}\left[\left|
+                        \langle f, \eta^{\theta}_{\tau+s}\rangle - \langle f, \eta^{\theta}_{\tau}\rangle
+                \right|\right] \\
+\leq (C_{\gamma,r}||f||_{\infty}
+        + C_{\gamma,r}||\Delta f||_{\infty}
+            +C_F||f||_{\infty})
+    \mathbb{E}\bigg\{
+                        \int_{\tau}^{\tau+s}
+                        \bigg\langle 1,\eta^{\theta}_{s}(dx)  \bigg\rangle 
+                        ds
+                \bigg\} \\
+\leq (C_{\gamma,r}||f||_{\infty}
+            + C_{\gamma,r}||\Delta f||_{\infty}
+                    +C_F||f||_{\infty})
+                \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle]
+                        e^{(C_{\gamma,r}+C_F)T}(e^\delta-1).
 \end{multline}
-as $s \to \infty$. 
-This gives us bound on the first moment.
-
+As $\eta^{\theta}_0$ converges weakly,
+we have that 
+$\sup_{\theta > \theta_0}\mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle] < K$
+for some $K>0$.
+Applying Markov's Inequality,
+we can pick small enough $\delta > 0$ such that 
+\begin{equation}
+\begin{aligned}
+\sup_{\theta > \theta_0}
+\sup_{s \in [0, \delta]}
+\mathbb{P}\left[\left| \langle f, \eta^{\theta}_{\tau+s}\rangle
+                        - \langle f, \eta^{\theta}_{\tau}\rangle
+                \right|> \epsilon \right]
+& \leq \sup_{\theta > \theta_0}
+\sup_{s \in [0, \delta]}
+\frac{
+\mathbb{E}\left[\left| \langle f, \eta^{\theta}_{\tau+s}\rangle
+                        - \langle f, \eta^{\theta}_{\tau}\rangle
+                \right| \right]
+        }{\epsilon}\\
+& < \frac{(C_{\gamma,r}||f||_{\infty}
+            + C_{\gamma,r}||\Delta f||_{\infty}
+                    +C_F||f||_{\infty})
+                Ke^{(C_{\gamma,r}+C_F)T}(e^\delta-1)
+         }{\epsilon}\\
+& < \epsilon.
+\end{aligned}    
+\end{equation}
 Similarly, the control on the second moment is given by Equation \eqref{eq: Control quadratic variation}.
@@
 \begin{aligned}
-& \mathbb{E}\left[\big| [M^{\theta}_{\tau+s}(f)] - [M^{\theta}_{\tau}(f)] \big|\right]\\
+& \sup_{\theta > \theta_0}
+\sup_{s \in [0, \delta]}\mathbb{E}\left[\big| [M^{\theta}_{\tau+s}(f)] - [M^{\theta}_{\tau}(f)] \big|\right]\\
 \leq &\frac{\theta}{N} \mathbb{E} \Bigg\{ \int_{\tau}^{\tau+s}\bigg|
@@
 & + \frac{1}{N}\mathbb{E} \Bigg\{\int_{\tau}^{\tau+s} \left\langle \gamma (\rho_{\gamma}*\eta^{\theta}_{s}(x))\theta\int_{\mathbb{R}^n}\left(r(\rho_{r}*\eta^{\theta}_{s}(y))-r(\rho_{r}*\eta^{\theta}_{s}(x))\right) q_\theta(x,dy), \eta^{\theta}_{s}(dx) \right\rangle ds\Bigg\}\\
-\leq & \frac{(2 \theta C_{\gamma,r}+C_{\gamma,r})\mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle]e^{(C_{\gamma,r}+C_F)T}(e^s-1)}{N} \to 0
+\leq & \frac{(2 \theta C_{\gamma,r}+C_{\gamma,r})\mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle]e^{(C_{\gamma,r}+C_F)T}(e^\delta-1)}{N}.
 \end{aligned}
 \end{equation}
-as $s \to 0$.
+As $\theta / N \to \alpha$ as $\theta \to \infty$,
+there exists some $K'>0$ such that 
+$\sup_{\theta > \theta_0} \theta / N < K'$.
+An application of Markov's inequality proves that
+for small enough $\delta > 0,$
+\begin{equation}
+\begin{aligned}
+\sup_{\theta > \theta_0}
+\sup_{s \in [0, \delta]}
+\mathbb{P}\left[\big| [M^{\theta}_{\tau+s}(f)] 
+                        - [M^{\theta}_{\tau}(f)] \big|
+                        > \epsilon\right]
+&\leq  \sup_{\theta > \theta_0}
+\sup_{s \in [0, \delta]}
+\mathbb{E}\left[\big| [M^{\theta}_{\tau+s}(f)] 
+                        - [M^{\theta}_{\tau}(f)] \big|
+                        \right]/\epsilon \\
+&< K'e^{(C_{\gamma,r}+C_F)T}(e^\delta-1)/\epsilon < \epsilon.
+\end{aligned}    
+\end{equation}
+\end{proof}
+
+\subsubsection{Tightness of $(\eta^{\theta}_t)_{t \geq 0}$}
+\begin{theorem}
+The collection of measure-valued processes 
+$\{(\eta^{\theta}_t)_{t \geq 0}: \theta > 0\}$
+is tight in $\mathcal{D}_{[0,\infty)}(\mathcal{M}_F(\overline{\mathbb{R}^d}))$.
+\end{theorem}
+\begin{proof}
+To prove relative compactness 
+of the processes $(\eta^{\theta}_t)_{t \geq 0}$,
+we apply Theorem 3.9.1. in \cite{EK}.
+
+First of all, the set of measures 
+$\{ \mu: \langle 1, \mu \rangle \leq K \} $
+is compact in $\mathcal{M}_F(\overline{\mathbb{R}^d})$.
+Therefore, by Lemma \ref{lem: Compact Containment},
+our processes satisfy the compact containment condition.
+
+Secondly, the set of functions $\mathcal{C}^{2}_{0}(\overline{\mathbb{R}^d})$ is a dense subset of all continuous functions on $\mathcal{M}_f(\overline{\mathbb{R}^d})$
+under the topology of uniform convergence in compact sets.
+
+Furthermore,
+since each measure $\eta^{\theta}_t$ is concentrated in $\mathbb{R}^d$,
+it suffices to show that the real-valued processes
+$\langle f, \eta^{\theta}_t \rangle$
+is tight for all $f \in \mathcal{C}^{2}_{0}(\mathbb{R}^d)$,
+which is proven in
+Theorem \ref{teo: Tightness of real-valued projections}.
+\end{proof}
 
@@
 
+Before we prove convergence, we define our limit $(\eta^{\infty}(t))_{t>0}$ as a solution to a Martingale Problem with generator $\Pgen$.
+
+\begin{definition}
+    \label{def: MP definition of limit}
+Let $F \in \mathcal{C}^{2}(\mathbb{R})$ and $f \in \mathcal{C}_{0}(\mathbb{R}^d)$.
+We define $\Pgen$ to be a generator
+acting on test functions of the form
+$F_f(\eta):=F (\langle f, \eta \rangle)$
+such that 
+\begin{equation}
+\begin{aligned}
+\Pgen^{\infty} F_f(\eta):=& F'(\langle f, \eta \rangle)
+                   \times \left\{
+                   \big\langle
+                        \gamma(x, \smooth{\gamma} \eta(x))
+                            \mathcal{B}\left(
+                            f(\cdot) r(\cdot, \smooth{r} \eta(\cdot))
+                            \right)(x)
+                    +
+                    f(x)
+                        F(x, \smooth{F} \eta(x)),
+                        \eta(dx)
+                    \big\rangle
+                   \right\}\\
+                &+ \frac{1}{2}F''(\langle f, \eta \rangle)
+                  \times \left\{
+                  \alpha \big\langle
+                    \gamma\left( x, \smooth{\gamma} \eta(x) \right)
+                    r\left(x, \smooth{r} \eta(x) \right)
+                    f^2(x),
+                    \eta (dx)
+                    \big\rangle 
+                  \right\}.
+\end{aligned}    
+\end{equation}
+We define $(\eta^{\infty}(t))_{t \geq 0}$ to be the solution to the Martingale Problem $(\Pgen^{\infty}, \eta_0)$, i.e. 
+for all $F \in \mathcal{C}^{2}(\mathbb{R})$
+and $f \in \mathcal{C}_{0}(\mathbb{R}^d)$,
+$$M_t:=F_f(\eta^{\infty}_t)-F_f(\eta_0)#
+-\int_{0}^{t}\Pgen^{\infty}F_f(\eta^{\infty}_s)ds$$
+is a martingale.
+\end{definition}
+\begin{remark}
+Taking $F(x)=x$ and $F(x)=x^2$, we can recover Equation \eqref{eqn:mgale_problem} and \eqref{eqn:mgale_variation}.
+\end{remark}
 \begin{lemma}[Convergence of generators for the population process]
 As $\theta \to \infty$,
-        \comment{(the generator for the prelimit)}
-        converges to
-        \comment{(the generator for the limit)}.
+$(\eta^{\theta}_t)_{t \geq 0}$ converges in $\mathcal{D}_{[0,\infty)}(\mathcal{M}_f(\mathbb{R}^d))$
+to $(\eta^{\infty}(t))_{t \geq 0}$.
 \end{lemma}
+\begin{proof}
+We use Theorem 4.8.10 in \cite{EK}.
+First of all, the set of functions
+$\{F_f(\eta):= F(\langle f, \eta \rangle ),~
+F \in \mathcal{C}^{2}(\mathbb{R}), ~
+f \in \mathcal{C}_{0}(\mathbb{R}^d)\}$
+is a dense and convergence-determining 
+subset of functions in $\mathcal{M}_f(\mathbb{R}^d)$.
+Therefore, it suffices to show that for any $t>0$,
+\begin{equation}
+    \label{eq: Convergence Condition}
+\lim_{\theta \to \infty}
+\mathbb{E}\left[
+\left(
+F_f(\eta^{\theta}_{t+s})-F_f(\eta^{\theta}_t)
+-\int_{t}^{t+s}\Pgen^{\infty}F_f(\eta^{\theta}_s)ds
+\right)
+\prod_{i=1}^{k}\langle h_i,\eta^{\theta}_{t_i} \rangle
+\right]=0
+\end{equation}
+for all $k\geq 0$, $0\leq t_1<t_2<...,t_k \leq t < t+s$,
+and $h_1,...,h_k \in \mathcal{C}_{0}(\mathbb{R}^d)$.
+
+To prove this,
+we apply Taylor's series expansion
+and make use of the Martingale Problem characterisation
+of $\eta^{\theta}_T$.
+We have
+\begin{equation}
+\begin{aligned}
+&\mathbb{E}\left[F_f(\eta^{\theta}_{t+s})-F_f(\eta^{\theta}_t)\bigg| \mathcal{F}_t \right]\\
+=& F'(\langle f, \eta^{\theta}_t \rangle )
+\mathbb{E}\left[
+                \langle f, \eta^{\theta}_{t+s}\rangle
+                    -\langle f, \eta^{\theta}_t\rangle 
+                    \bigg| \mathcal{F}_t
+         \right]
++\frac{1}{2}F''(\langle f, \eta^{\theta}_t \rangle )
+\mathbb{E}\left[
+                \left(
+                    \langle f, \eta^{\theta}_{t+s}\rangle -\langle f, \eta^{\theta}_t\rangle
+                \right)^2
+                \bigg| \mathcal{F}_t
+        \right]\\
+&+\frac{1}{6}F'''(\langle f, \eta^{\theta}_{t+s'}\rangle)\mathbb{E}\left[
+                \left(
+                    \langle f, \eta^{\theta}_{t+s}\rangle -\langle f, \eta^{\theta}_t\rangle
+                \right)^3
+                \bigg| \mathcal{F}_t
+        \right]\\
+=& F'(\langle f, \eta^{\theta}_t \rangle )\\
+& \times  \int_{0}^{t}\bigg\{
+        \int\left(   \int \theta
+     \left(
+        f(z)r\big(z,\rho_{r}*\eta^{\theta}_{s}(z)\big)
+            -f(x)r\big(x,\rho_{r}*\eta^{\theta}_{s}(x)\big)
+            \right)
+                    q_\theta(x,dz)\right)
+        \\ & \qquad \qquad \qquad \qquad {} \times
+                            \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
+                            \eta^{\theta}_{s}(dx)
+     \\ & \qquad \qquad {} +\int 
+     f(x)F\big(x,\rho_{F}*\eta^{\theta}_{s}(x)\big)
+     \eta^{\theta}_{s}(dx)
+    \bigg\} ds\\
+=+\frac{1}{2}F''(\langle f, \eta^{\theta}_t \rangle )\\
+&\times 
+\end{aligned}
+\end{equation}
+\end{proof}
 

### 2022-04-14 forwards-and-backwards.tex
comments on lookdown section

@@
 
-\plr{Motivation for and definition of the lookdown process; statement of main convergence theorem.}
-
 Now we will present a lookdown construction for $(\eta^{\theta}(t))_{t \geq 0}$
@@
 
+\comment{Below, we write $\lambda$ instead of $N$: change to $N$?}
+
 % % % % % % % % % % % % % % % %
@@
 $$\eta=\frac{1}{\lambda}\sum_{(x,u)\in\xi}\delta_x,$$
-i.e. $\eta$ is the re-scaled spatial projection of our spatial-level model $\xi$. 
+i.e., $\eta$ is the re-scaled spatial projection of our spatial-level model $\xi$. 
 Conditional on the spatial population $\eta$,
@@
 Similar lookdown constructions can be found 
-in \cite{etheridge/kurtz:2018},\cite{kurtz/rodrigues:2011}.
+in \citet{etheridge/kurtz:2018} and \citet{kurtz/rodrigues:2011}.
 Test functions for this enriched process take the form
@@
 smooth in $x$.
-Moreover, $0\leq g(x,u) \leq 1$ for all $u\in [0,\lambda]$,
+We will also assume that $0\leq g(x,u) \leq 1$ for all $u\in [0,\lambda]$,
 and $g(x,u)\equiv 1$ for $u\geq \lambda$.
@@
 
+\comment{This repeats some stuff from above.}
 We should consider an initial population of $O(\lambda)$ many particles with levels
@@
 $$\gamma^{\mathfrak{m}}(x,\eta)=\gamma(x,\eta) \int r (y, \eta)q(x,dy),$$
-where $q(x,dy)$ is the dispersion kernel.
+where $q(x,dy)$ is the dispersal kernel.
+
+\comment{Note: in what happens below, $\gamma^\mathfrak{m}$ is useful in that it makes the
+equation for $\dot u$ nicer, but we could remove $q^\mathfrak{m}$ if we wanted
+(although then \eqref{Generator of prelimit simplest model}
+would then have both a $\gamma$ and a $\gamma^\mathfrak{m}$ in it).}
 
@@
 in the branching mechanism.
+\comment{TODO: explain the connection to $F$.}
 In this notation,
@@
 governing the level of the individual $(x,u)\in\eta$ is
+\comment{TODO: check that $\theta$ is right here, and consistent with the discussion above.}
 \begin{align}
@@
 We can now define our pre-limit explicitly as a solution to a Martingale Problem.
+\comment{TODO: this is a bit redundant with the above.
+Instead, maybe (a) describe the process in words; (b) give this definition;
+then (c) explain why it's the generator, so we only write down the generator once?}
+
+% % % % % % % %
 \begin{definition}[Martingale Problem Characterisation]
@@
 \end{definition}
+
+\comment{Remark on the Remark: this is more than one remark.
+I'm not sure it needs to be in a Remark block: how about just a few paragraphs?}
 

### 2022-04-14 forwards-and-backwards.tex
Update on Overleaf.

@@
 Therefore it suffices to show that for all $x,w \in \mathbb{R}^d$ and $s \in [0, 1/\theta]$, 
-\begin{align} \label{eqn:goal3}
+\begin{align} 
     F'(s) \exp\left(-A (x-w)^2 \right) \le C .
@@
 and $f \in \mathcal{C}_{0}(\mathbb{R}^d)$,
-$$M_t:=F_f(\eta^{\infty}_t)-F_f(\eta_0)#
+$$M_t:=F_f(\eta^{\infty}_t)-F_f(\eta_0)
 -\int_{0}^{t}\Pgen^{\infty}F_f(\eta^{\infty}_s)ds$$
@@
 =+\frac{1}{2}F''(\langle f, \eta^{\theta}_t \rangle )\\
-&\times 
+&\times \frac{\theta}{N} \int_{0}^{t}\bigg\{
+\langle \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
+\int f^2(y)r\big(y,\rho_{r}*\eta^{\theta}_{s}(y)\big)q_\theta(x,dy) 
+,\eta^{\theta}_{s}(dx)\rangle\\
+& \qquad \qquad +\langle \mu\big(x,\eta^{\theta}_{s}\big)f^2(x) 
+,\eta^{\theta}_{s}(dx)\rangle \bigg\}ds.
 \end{aligned}

### 2022-04-14 forwards-and-backwards.tex
Update on Overleaf.

@@
 
-\begin{remark}
 In Appendix \ref{sec: Markov Mapping Theorem Application},
-applying Markov Mapping Theorem,
-we will show that the spatial projection of $(\xi^{\theta}_t)_{t \geq 0}$ defined as 
+we will show that
+if we define $\Gamma (d\textbf{u})$
+as the probability kernel that corresponds to
+assigning each particle an i.i.d. uniform $[0,N]$-level,
+and for any $\xi \in \mathcal{N}_f(\mathbb{R}^d \times [0,\infty))$, we denote
+$$\hat{f}(\xi)=\int f(\xi) \Gamma (d\textbf{u})$$ 
+to be the spatial test functions with averaged level,
+then the process
+\begin{equation}
+\begin{aligned}
+M^{\theta}_t:=&\hat{f}(\xi_t)-\hat{f}(\xi_0)-\int_{0}^{t}\int   A^{\theta}f(\xi_s)\Gamma(d\textbf{u})ds\\
+:=&\hat{f}(\xi_t)-\hat{f}(\xi_0)-\int_{0}^{t}   \Pgen^{\theta}\hat{f}(\xi_s)ds
+\end{aligned}    
+\end{equation}
+is a martingale.
+
+By the Markov Mapping Theorem,
+there exists a solution $(\xi^{\theta}_t)_{t \geq 0}$
+to the Martingale Problem with generator $A^{\theta}$.
+Furthermore,
+the spatial projection of $(\xi^{\theta}_t)_{t \geq 0}$
+shares the same law of $(\eta^{\theta}(t))_{t \geq 0}$,
+i.e.
 $$(\eta^{\theta}(t))_{t \geq 0}
-:=\left(\frac{1}{N}\sum\limits_{(X(t),U(t))\in \xi^{\theta}(t)} \delta_{X(t)}\right)_{t \geq 0}$$
-has the same distribution (as stochastic processes)
-as $(\eta^{\theta}_t)_{t \geq 0}$
-in Definition \ref{Def: Rescaled Models}.
-As a result, we use the same notation $\eta$
-to denote these two identically distributed processes.
-On the other hand,
-we reserve the notation $\xi$
+\sim \left(\frac{1}{N}\sum\limits_{(X(t),U(t))\in \xi^{\theta}(t)} \delta_{X(t)}\right)_{t \geq 0},$$
+and conditional on 
+$(\eta^{\theta}(t))_{t \geq 0}$,
+the levels of particles in $(\xi^{\theta}_t)_{t \geq 0}$
+are i.i.d. uniformly distributed between $[0,N]$.
+
+Therefore, we use the same notation $\eta$
+in our spatial model
+to denote the spatial projection of $\xi$,
+and we reserve the notation $\xi$
 strictly for the spatial-level process.
-
-Furthermore, the application of Markov Mapping Theorem implies that 
-particle levels are, conditional on $\eta$,
-i.i.d and uniformly distributed between $[0, N]$.
 
@@
 to a conditionally Poisson system $(\xi_t)_{t \geq 0}$
-with Cox measure $\Xi_t \times N$
+with Cox measure $\Xi_t \times \Lambda$
 is equivalent to convergence of
@@
 as $\theta \to \infty$.
-
-\end{remark}
 
@@
     \bigg\} ds\\
-=+\frac{1}{2}F''(\langle f, \eta^{\theta}_t \rangle )\\
-&\times \frac{\theta}{N} \int_{0}^{t}\bigg\{
+&+\frac{1}{2}F''(\langle f, \eta^{\theta}_t \rangle )\\
+&\quad \times \frac{\theta}{N} \int_{0}^{t}\bigg\{
 \langle \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
@@
 & \qquad \qquad +\langle \mu\big(x,\eta^{\theta}_{s}\big)f^2(x) 
-,\eta^{\theta}_{s}(dx)\rangle \bigg\}ds.
+,\eta^{\theta}_{s}(dx)\rangle \bigg\}ds\\
+&+\frac{1}{6}F^{(3)}(\langle f, \eta^{\theta}_{t+s'}\rangle)\mathbb{E}\left[
+                \left(
+                    \langle f, \eta^{\theta}_{t+s}\rangle -\langle f, \eta^{\theta}_t\rangle
+                \right)^3
+                \bigg| \mathcal{F}_t
+        \right]
 \end{aligned}
 \end{equation}
+for some $s' \in [0,s]$.
 \end{proof}

### 2022-04-19 forwards-and-backwards.tex
plr edits

@@
 \newcommand{\Pgen}{\mathcal{P}}    % generator of the population process
+\newcommand{\lp}{\xi}              % process with levels
 
@@
 
-Now we will present a lookdown construction for $(\eta^{\theta}(t))_{t \geq 0}$
-stated in Definition \ref{Def: Rescaled Models} in the spirit of~\cite{kurtz/rodrigues:2011}. 
-The key benefit of working in such a framework is that
+Now we will present a lookdown construction for the general process
+(i.e., of Definition \ref{Def: Rescaled Models}),
+in the spirit of~\cite{kurtz/rodrigues:2011}. 
+The key benefit of this construction is that
 we shall be able to preserve the notion of individuals,
@@
 when we pass to the limit.
-Our notation will follow a standard pattern.
-
-\comment{Below, we write $\lambda$ instead of $N$: change to $N$?}
+
+The gneral set-up is as follows.
+Each individual will be labeled with a ``level'',
+which will be a number in $[0, \lambda]$.
+When taking the limit, we will set $\lambda = N$.
+\comment{Should we just use $N$ instead of $\lambda$? Or vice-versa?}
+We will still encode the process embellished by these levels
+as a point measure:
+if the $i^\mathrm{th}$ individual's spatial location is $x_i$
+and level is $u_i$, then we will write:
+$$
+    \lp = \sum_i \delta_{x_i, u_i} ,
+$$
+which is a measure on $\IR^d \times [0, \lambda]$.
+Note that the each individual contributes mass 1 to the measure,
+not $1/N$ as above.
+In some sense, these levels do not affect the process:
+the pushforward of this measure-valued ``spatial-level process'',
+divided by $N$,
+will agree with the purely spatial process defined above.
+Furthermore, the levels of the individuals present at any spatial location
+conditionally uniform on $[0, \lambda]$.
+However, an individual's level in some sense encodes their future reproductive output:
+individuals with lower levels tend to live longer, and have more offspring.
+For more explanation of the set-up and how this is possible,
+see \citet{etheridge/kurtz:2018} and \citet{kurtz/rodrigues:2011}.
+Furthermore, the limiting spatial-level process will still be a point measure,
+and so we explicitly retain the notion of individuals and lineages through to the 
+large-population-density limit.
 
 % % % % % % % % % % % % % % % %
-\subsection{Lookdown Representation and Notation}
-\label{sec: Lookdown Representation and Notation}
-
-In the prelimiting models,
-each individual in the population
-will be assigned a `level' from $[0,\lambda]$.
-
-A state of the discrete population model will be of the form $\xi=\sum\delta_{(x,u)}$,
-where $x$ denotes the spatial location
-of an individual, and $u$ is its level.
-We shall abuse notation and treat $\xi$ both as a set and as a counting measure.
-The spatial population described in \S \ref{sec: Model and main results} is recovered as
-$$\eta=\frac{1}{\lambda}\sum_{(x,u)\in\xi}\delta_x,$$
-i.e., $\eta$ is the re-scaled spatial projection of our spatial-level model $\xi$. 
-Conditional on the spatial population $\eta$,
-the levels of individuals in the population
-will be independently and uniformly distributed
-on $[0,\lambda]$.
-Similar lookdown constructions can be found 
-in \citet{etheridge/kurtz:2018} and \citet{kurtz/rodrigues:2011}.
-Test functions for this enriched process take the form
+\subsection{Definition and generator of the lookdown process}
+\label{sec:lookdown_defn}
+
+In this section,
+we'll define the process $(\lp_t)_{t \ge 0}$ in terms of the dynamics of labeled particles,
+and write down it's generator.
+Since the dynamics depend on the spatial locations of particles,
+we \emph{define} $\eta_t$ to be the corresponding spatial measure,
+i.e.,
+$$
+    \eta_t(\cdot) = \frac{1}{\lambda} \lp_t(\cdot \times [0, \lambda])  .
+$$
+A nontrivial consequence of the way we define $\lp_t$ will be that
+this process has the same distribution as the process $(\eta_t)_{t \ge 0}$ defined above
+in Definition~\ref{Def: Rescaled Models},
+again, after setting $\lambda = N$.
+(This provides our justification for using the same notation for both.)
+Finally, note that we first describe the dynamics of individuals
+in the original time units -- i.e., before scaling by $\theta$,
+which will appear below.
+
+\comment{
+    I've defined $\eta = \lp / N$ to agree with how we define the generator below,
+    for which birth/death add/remove something of mass 1, not $1/\lambda$.
+}
+
+\comment{TODO: this uses the $\gamma(x, \eta)$ notation, which we haven't settled on.}
+
+Suppose that the initial population is composed of $O(\lambda)$ many particles
+with levels uniformly distributed between $[0, \lambda]$.
+Suppose the current state of the population is $\lp$,
+with spatial projection $\eta$.
+Each individual at spatial location $x$ with level $u$
+produces one juvenile offspring at rate 
+$$
+2 \left(1 - \frac{u}{\lambda}\right) \gamma(x, \eta) ,
+$$
+which disperses to a location relative to $x$ drawn from the kernel $q(\cdot)$.
+(Averaging over the uniform distribution of the level $u$,
+we recover the birth rate $\gamma(x, \eta)$.)
+This juvenile -- suppose it's location is $y$ --
+either survives, with probability $r(y, \eta)$, or immediately dies.
+(As before, ``maturity'' is instantaneous.)
+
+A new level $u_1$ is sampled independently and uniformly from $[u,\lambda]$,
+and the parent and the offspring are assigned in random order to the levels $\{u, u_1\}$.
+This random assignment of levels to parent
+and offspring ensures that conditional on $\eta$,
+the levels of each individual at any point in time are independent, uniform random variables.
+
+Evidently this mechanism increases the proportion
+of individuals with higher levels.
+To restore the property that,
+conditional on $\eta$,
+the distribution of levels is conditionally uniform,
+we impose that 
+the level of an individual at location $x$
+evolves according to the differential equation
+$$
+    \dot{v}
+    =
+    % \gamma^{\mathfrak{m}}(x, \eta) \left\{\lambda^{-1}(\lambda -v)^{2} -(\lambda -v)\right\}.
+    - \frac{v}{\lambda} \left(\lambda - v\right)
+    \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q(x, dy) .
+$$
+Since $v \in [0, \lambda]$, this moves levels down;
+see~\cite{etheridge/kurtz:2018}, Section~3.4 for a detailed explanation.
+
+In the lookdown model, levels never cross below 0,
+while particles whose levels move above $\lambda$ are regarded as dead
+(and do not affect to the population any more).
+Therefore, in order to incorporate death,
+the level of the individual at location $x$ with level $u$
+moves upwards at an additional rate $\mu(x,\eta) u$.
+Since levels are uniform,
+it is easy to check that if $\mu$ was constant,
+this would imply an exponential lifetime for each individual;
+see~\cite{etheridge/kurtz:2018}, Section \comment{XXX}
+for more general justification.
+
+Putting these together,
+the level $u$ of an individual at $x$
+evolves according to
+$$
+\dot{u}
+=
+    - \frac{v}{\lambda} \left(\lambda - v\right)
+    \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q(x, dy) 
+    +
+    \mu(x,\eta) u .
+$$
+We shall write 
+$$
+    b(x, \eta)
+    :=
+    \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy)
+    -
+    \mu(x,\eta),
+$$
+which captures the local net difference between reproduction and death,
+i.e., the deviation from criticality of the branching mechanism.
+(This differs from $F = r\gamma - \mu$ defined above
+because $b$ contains the adjustment to fecundity obtained by
+averaging over establishment probabilities in the locations that offspring disperse to.)
+We can then rewrite the differential equation 
+governing the how each individual's level evolves as
+\begin{align}
+\dot{u}
+    &=
+    \lambda \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy)
+    \left\{
+        \left(1-\frac{u}{\lambda}\right)^{2}
+        - 1
+        + 2 \frac{u}{\lambda}
+    \right\}
+    -
+    b(x,\eta)u
+    \nonumber \\
+    &=
+    \lambda^{-1} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
+    -
+    b(x, \eta)u
+    . \label{differential equation for level}
+\end{align}
+
+Now, we can write down the generator for $(\lp_t)_{t \ge 0}$,
+the lookdown process.
+In what follows, we will write sums (and, products) over ``$(x, u) \in \xi$''
+to mean as a sum over the (location, level) pairs of each individual in the population.
+Test functions for $\lp$ then take the form
 \begin{equation}
 \label{test functions}
-f(\xi)=\prod_{(x,u)\in \xi}g(x,u)=\exp\left(\int \log g(x,u)\xi(dx, du)\right),
-\end{equation}
-where $g(x,u)$ is differentiable in $u$ and 
+f(\lp)=\prod_{(x,u)\in \lp}g(x,u)=\exp\left(\int \log g(x,u)\lp(dx, du)\right),
+\end{equation}
+where
+$g(x,u)$ is differentiable in $u$ and 
 smooth in $x$.
@@
 and $g(x,u)\equiv 1$ for $u\geq \lambda$.
-
 In the expressions that follow,
@@
 then it simply cancels 
-the corresponding factor in $f(\eta)$.
-
-% % % % % % % % % % % % % % % %
-\subsubsection*{Generator of the Lookdown Model}
-
-We now write down the generator of
-the population model with levels between $[0, \lambda]$.
-
-\comment{This repeats some stuff from above.}
-We should consider an initial population of $O(\lambda)$ many particles with levels
-uniformly distributed between $[0, \lambda]$.
-We write $(\xi(t))_{t \geq 0}$
-for our population.
-To ensure we have bounded intensity, 
-we scale the empirical distribution of particles with a factor of $1/\lambda$,
-so we write
-$$\eta_t:=\frac{1}{\lambda}\xi_t(\cdot \times [0,\lambda])=
-\frac{1}{\lambda}\sum\limits_{\substack{(X(t),U(t))\in \xi \\ U(t) < \lambda}} \delta_{X(t)}.$$
-
-From here onwards,
-we write $\xi$ to be the particle systems with levels,
-while $\eta$ is the normalised empirical distribution.
-An individual in the spatial population $\eta$ living at spatial location $x$
-produces one adult offspring at rate $\gamma^{\mathfrak{m}}(x, \eta)$, where
-$$\gamma^{\mathfrak{m}}(x,\eta)=\gamma(x,\eta) \int r (y, \eta)q(x,dy),$$
-where $q(x,dy)$ is the dispersal kernel.
-
-\comment{Note: in what happens below, $\gamma^\mathfrak{m}$ is useful in that it makes the
-equation for $\dot u$ nicer, but we could remove $q^\mathfrak{m}$ if we wanted
-(although then \eqref{Generator of prelimit simplest model}
-would then have both a $\gamma$ and a $\gamma^\mathfrak{m}$ in it).}
-
-Recall that we only track the adult population; maturity, if achieved, is instantaneous.
-The location of this adult offspring is given by
-the distribution 
-\[ q^{\mathfrak{m}}(x,\eta,dy) = \frac{r(y,\eta) q(x,dy)}{\int_{\mathbb{R}^d} r(y,\eta) q(x,dy)}. \]
-
-In the lookdown version of our model,
-the individual $(x,u)\in \xi$
-gives birth to an offspring at rate 
-$2(\lambda-u)\lambda^{-1} \gamma^{\mathfrak{m}}(x, \eta)$. 
-(Averaging over the distribution of the
-level $u$,
-we recover $\gamma^{\mathfrak{m}}(x, \eta)$.)
-
-A new level $u_1$ is sampled independently and
-uniformly from $[u,\lambda]$,
-and the parent and the offspring are assigned in random order to the  levels $\{u, u_1\}$.
-This random assignment of levels to parent
-and offspring ensures that conditional on $\eta$,
-the levels assigned to individuals are i.i.d.
-uniform random variables.
-Otherwise, the levels of the initial population would be lower than those of the descendants.
-
-Evidently this mechanism increases the proportion
-of individuals with higher levels.
-To restore the property that,
-conditional on $\eta$,
-the intensity of levels is conditionally uniform,
-we impose that 
-the level associated with $(x,u)\in\eta$
-evolves according to the differential equation
-$$\dot{v}=  \gamma^{\mathfrak{m}}(x, \eta) 
-\left\{\lambda^{-1}(\lambda -v)^{2}
--(\lambda -v)\right\}.$$
-
-See~\cite{etheridge/kurtz:2018}, Section~3.4 for a detailed explanation.
-In order to incorporate death,
-the level of the individual $(x,u)\in \eta$ 
-moves upwards at an additional rate
-$ \mu(x,\eta)$
-(on reaching level $\lambda$
-an individual is deemed to have died).
-Overall, we assume that
-the level associated with $(x,u)\in\eta$
-evolves according to
-$$\dot{u}= \gamma^{\mathfrak{m}}(x, \eta) 
-\left\{\lambda^{-1}(\lambda -u)^{2}
--(\lambda -u)\right\}+\mu(x,\eta)u.$$
-We shall write 
-$$b(x,\eta):= \big\{\gamma^{\mathfrak{m}}(x,\eta)
--\mu(x,\eta)\big\}$$
-to be the local branching rate.
-Note that this quantity captures
-the deviation from criticality
-in the branching mechanism.
-\comment{TODO: explain the connection to $F$.}
-In this notation,
-the differential equation 
-governing the level of the individual $(x,u)\in\eta$ is
-\comment{TODO: check that $\theta$ is right here, and consistent with the discussion above.}
-\begin{align}
-\dot{u}&=\lambda  \gamma^{\mathfrak{m}}(x,\eta) 
-\left\{\left(1-\frac{u}{\lambda}\right)^{2}
--1 +2\frac{u}{\lambda}\right\} -b(x,\eta)u \nonumber \\
-&=\lambda^{-1}  \gamma^{\mathfrak{m}}(x,\eta) u^2 -b(x,\eta)u. \label{differential equation for level}
-\end{align}
-In this setting, the generator of our model
-acting on the test functions $f(\xi)=\prod_{(x,u) \in \xi}g(x,u)$
-satisfies
-%We assume that  locations in ${\mathbb{ R}}^d$.
-
-\begin{eqnarray}\label{Generator of prelimit simplest model}
-&&Af(\xi ) \nonumber \\
-&&\quad =f(\xi )\,\sum_{(x,u)\in\xi}\,2\lambda^{-1} \gamma^{\mathfrak{m}}(x, \eta)
-\int_u^{
-\lambda}\Bigg(\frac 12\frac {\int_{\mathbb{R}^d}g(y,u)q^{\mathfrak{m}}(x,\eta,d
-y)g(x,v_1)}{g(x,u)} \label{multgen3}\\
-&&\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad
-+\frac 12\int_{\mathbb{R}^d}g(y,v_1)q^{\mathfrak{m}}(x,\eta ,dy)-
-1\Bigg)dv_1\nonumber\\
-&&\quad \quad +f(\eta )\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}(x,\eta) u^2 -b(x,\eta)u\right)\frac {\partial_u g(x,u)}{g(x,u)}\nonumber\\
-&&\quad =f(\eta )\,\sum_{(x,u)\in\eta}\,2 \gamma^{\mathfrak{m}}(x, \eta)\lambda^{-1}\int_u^{
-\lambda}\Bigg(\frac 12\frac {\theta\int_{\mathbb{R}^d}(g(y,u)-g(x,u))q^{\mathfrak{m}}(x,\eta,dy)g(x,v_1)}{g(x,u)}\non\\
-&&\qquad\qquad\qquad\qquad\qquad\qquad\qquad +\theta\int_{\mathbb{R}^d}\left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}(x,\eta,dy)\Bigg)dv_1\nonumber\\
-&&\qquad\qquad
-+f(\eta )\sum_{(x,u)\in\eta}\,\left(\lambda^{-1} \gamma^{\mathfrak{m}}(x,\eta) u^2 -b(x,\eta)u\right)\frac {\partial_u g(x,u)}{g(x,u)}.\nonumber
+the corresponding factor in $f(\lp)$.
+
+Recall also that in defining $\eta_t$
+we had not only rescaled mass, dividing each individual's mass by $N$,
+but also time, speeding up time by a factor of $\theta$.
+As a result, per-capita rates described above will have a factor of $\theta$ here.
+
+First consider the terms in the generator that come from birth events.
+Recall that when a birth successfully establishes,
+a new level is generated above the parent's level,
+and this new level is assigned to either the offspring or the parent.
+Since the probability of each is 1/2,
+the contribution of birth to the generator is
+\begin{align*}
+\begin{split}
+    f(\lp)
+    \mapsto
+    f(\lp)
+    \sum_{(x, u) \in \lp}
+    2 \frac{\theta}{\lambda} \gamma(x, \eta)
+    \int_u^\lambda
+    \int_{\IR^d}
+    &
+    \frac{1}{2}
+    \bigg\{
+        \left(
+            g(y, u_1)
+            -
+            1
+        \right)  \\
+    &\qquad {}
+        + \frac{ g(y, u) g(x, u_1) }{ g(x, u) }
+    \bigg\}
+    r(y, \eta) q(x, dy)
+\end{split} .
+\end{align*}
+Here, $u_1$ is the new level and $y$ is the offspring's location,
+and so the two terms in the integral correspond to the two situations:
+in the first, we have added an individual at $(y, u)$,
+while in the second, we replace an individual at $(x, u)$
+by one at $(x, u_1)$ and another at $(y, u)$.
+
+\comment{PLR edited through to here.}
+
+The generator of $\lp$ applied to functions of this form
+is therefore
+\begin{eqnarray}
+&&
+A f(\lp ) \nonumber \\
+&&\quad
+    = f(\lp) \,
+    \sum_{(x,u) \in \lp}\,
+        2 \lambda^{-1} \gamma(x, \eta)
+    \int_u^\lambda \Bigg(
+        \frac{1}{2} \frac{
+            \int_{\mathbb{R}^d} g(y,u) r(y,\eta) q(x, dy) g(x,v_1)
+        }{
+            g(x,u)
+        }
+\label{multgen3}\\
+&&\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad {}
+        + \frac{1}{2} \int_{\mathbb{R}^d} g(y,v_1) r(y,\eta) q(x,dy)
+        - 1
+    \Bigg) dv_1
+\nonumber\\
+&&\quad \quad
+    + f(\lp) \left(
+        \lambda^{-1} \theta
+        \gamma(x,\eta)
+        \int_{\IR^d} r(y, \eta q(x, dy)
+        u^2
+        -
+        b(x,\eta)u
+    \right)
+    \frac {\partial_u g(x,u)}{g(x,u)}
+\nonumber\\
+&&\quad
+    = f(\lp) \,
+    \sum_{(x,u)\in\lp}\,
+    2 \gamma(x, \eta) \frac{\theta}{\lambda}
+    \int_u^\lambda \Bigg(
+        \frac{1}{2} \frac{
+            \int_{\mathbb{R}^d}( g(y,u) - g(x,u) ) r(y, \eta) q(x,dy) g(x,v_1)
+        }{
+            g(x,u)
+        }
+\non\\
+&&\qquad\qquad\qquad\qquad\qquad\qquad\qquad {}
+        + \int_{\mathbb{R}^d} \left(
+            \frac{ g(y,v_1) + g(x,v_1) }{ 2 }
+            -
+            1
+        \right)
+        r(y, \eta) q(x,dy)
+    \Bigg) dv_1
+\nonumber\\
+&&\qquad\qquad {}
+    +
+    f(\lp) \sum_{(x,u)\in\lp}\,
+    \left(
+        \lambda^{-1}
+        \gamma(x,\eta)
+        \int_{\IR^d} r(y, \eta) q(x, dy)
+        u^2
+        -
+        b(x,\eta) u
+    \right)
+    \frac{ \partial_u g(x,u) }{ g(x,u) }
+.\nonumber
 \end{eqnarray}
 The two terms under the integral correspond, respectively,
-to the parent being assigned a level other than $u$,
-and being reallocated to the level $u$
+to either the parent or child being reassigned the new level $v_1$
 during a birth event.
 In the first case, the parent at location $x$,
-which had level $u$ before the event,
-moves to level $v_1$,
-and the child is inserted at level $u$
-and location $y$;
+which had level $u$ before the event, is reassigned to level $v_1$,
+and the child is inserted at level $u$ and location $y$;
 in the second the parent retains its level,
@@
 Here we give a general framework of tracking evolution
-of individual particles in the spatial-level population $\xi(t)_{t \geq 0}$ defined in \S \ref{sec: Lookdown Representation and Notation}.
+of individual particles in the spatial-level population $\xi(t)_{t \geq 0}$ defined in \S \ref{sec:lookdown_defn}.
 

### 2022-04-19 forwards-and-backwards.tex
.

@@
 =
-    - \frac{v}{\lambda} \left(\lambda - v\right)
+    - \frac{u}{\lambda} \left(\lambda - u\right)
     \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q(x, dy) 
@@
 i.e., the deviation from criticality of the branching mechanism.
-(This differs from $F = r\gamma - \mu$ defined above
+(This differs from $F = \theta(r\gamma - \mu)$ defined above
+both by the factor of $\theta$ and
 because $b$ contains the adjustment to fecundity obtained by
@@
     &=
-    \lambda \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy)
+    \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy)
     \left\{
-        \left(1-\frac{u}{\lambda}\right)^{2}
-        - 1
-        + 2 \frac{u}{\lambda}
+        -\frac{u}{\lambda}\left(\lambda - u\right)
+        + u
     \right\}
@@
 \begin{align*}
-\begin{split}
 f(\lp)
-    \mapsto
+&\mapsto
     f(\lp)
@@
     \int_{\IR^d}
-    &
+    \left(
     \frac{1}{2}
     \bigg\{
-        \left(
             g(y, u_1)
-            -
-            1
-        \right)  \\
-    &\qquad {}
         + \frac{ g(y, u) g(x, u_1) }{ g(x, u) }
     \bigg\}
+        - 1
+    \right)
     r(y, \eta) q(x, dy)
-\end{split} .
+    \\ \begin{split}
+&=
+    f(\lp)
+    \sum_{(x, u) \in \lp}
+    2 \gamma(x, \eta)
+    \bigg\{
+        \frac{1}{2 \lambda}
+        \int_u^\lambda
+        g(x, u_1) du_1
+        \frac{
+            \theta \int_{\IR^d} (g(y, u) - g(x, u)) r(y, \eta) q(x, dy)
+        }{
+            g(x, u)
+        }
+    \\ & \qquad \qquad \qquad {}
+        + \frac{\theta}{\lambda}
+        \int_u^\lambda \int_{\IR^d}
+        \left( \frac{g(y, u_1) + g(x, v_1)}{2} - 1 \right)
+        r(y, \eta) q(x, dy)
+    \bigg\}
+    .
+    \end{split}
 \end{align*}
@@
 
-\comment{PLR edited through to here.}
+The remaining term in the generator is due to the motion of particles' levels:
+\begin{align*}
+    f(\lp)
+    \mapsto
+    f(\lp)
+    \theta
+    \sum_{(x, u) \in \lp}
+    \left(
+        \lambda^{-1} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
+        -
+        b(x, \eta)u
+    \right)
+    \frac{\partial_u g(x,u)}{g(x,u)} .
+\end{align*}
 

### 2022-04-19 forwards-and-backwards.tex
edits until defn 6.1

@@
     :=
+    \theta\left(
     \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy)
     -
-    \mu(x,\eta),
+    \mu(x,\eta)
+    \right) ,
 $$
@@
 i.e., the deviation from criticality of the branching mechanism.
-(This differs from $F = \theta(r\gamma - \mu)$ defined above
-both by the factor of $\theta$ and
+(This differs from $F(x,\eta) = \theta(r(x,\eta)\gamma(x,\eta) - \mu(x,\eta))$ defined above
 because $b$ contains the adjustment to fecundity obtained by
 averaging over establishment probabilities in the locations that offspring disperse to.)
+\comment{TODO: make this explanation better.}
 We can then rewrite the differential equation 
@@
     -
-    b(x, \eta)u
+    b(x, \eta) u / \theta
     . \label{differential equation for level}
@@
 Test functions for $\lp$ then take the form
-\begin{equation}
-\label{test functions}
+\begin{equation} \label{eqn:test_functions}
 f(\lp)=\prod_{(x,u)\in \lp}g(x,u)=\exp\left(\int \log g(x,u)\lp(dx, du)\right),
@@
 the contribution of birth to the generator is
-\begin{align*}
-f(\lp)
+\begin{align}
+f(\lp) \nonumber
 &\mapsto
@@
     r(y, \eta) q(x, dy)
-    \\ \begin{split}
+    \\
+    \begin{split} \label{eqn:birth_generator}
 &=
@@
     \end{split}
-\end{align*}
+\end{align}
 Here, $u_1$ is the new level and $y$ is the offspring's location,
@@
 The remaining term in the generator is due to the motion of particles' levels:
-\begin{align*}
+\begin{align} \label{eqn:level_generator}
     f(\lp)
@@
     f(\lp)
-    \theta
     \sum_{(x, u) \in \lp}
     \left(
+    \theta
         \lambda^{-1} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
@@
     \frac{\partial_u g(x,u)}{g(x,u)} .
-\end{align*}
-
-The generator of $\lp$ applied to functions of this form
-is therefore
-\begin{eqnarray}
-&&
-A f(\lp ) \nonumber \\
-&&\quad
-    = f(\lp) \,
-    \sum_{(x,u) \in \lp}\,
-        2 \lambda^{-1} \gamma(x, \eta)
-    \int_u^\lambda \Bigg(
-        \frac{1}{2} \frac{
-            \int_{\mathbb{R}^d} g(y,u) r(y,\eta) q(x, dy) g(x,v_1)
-        }{
-            g(x,u)
-        }
-\label{multgen3}\\
-&&\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad {}
-        + \frac{1}{2} \int_{\mathbb{R}^d} g(y,v_1) r(y,\eta) q(x,dy)
-        - 1
-    \Bigg) dv_1
-\nonumber\\
-&&\quad \quad
-    + f(\lp) \left(
-        \lambda^{-1} \theta
-        \gamma(x,\eta)
-        \int_{\IR^d} r(y, \eta q(x, dy)
-        u^2
-        -
-        b(x,\eta)u
-    \right)
-    \frac {\partial_u g(x,u)}{g(x,u)}
-\nonumber\\
-&&\quad
-    = f(\lp) \,
-    \sum_{(x,u)\in\lp}\,
-    2 \gamma(x, \eta) \frac{\theta}{\lambda}
-    \int_u^\lambda \Bigg(
-        \frac{1}{2} \frac{
-            \int_{\mathbb{R}^d}( g(y,u) - g(x,u) ) r(y, \eta) q(x,dy) g(x,v_1)
-        }{
-            g(x,u)
-        }
-\non\\
-&&\qquad\qquad\qquad\qquad\qquad\qquad\qquad {}
-        + \int_{\mathbb{R}^d} \left(
-            \frac{ g(y,v_1) + g(x,v_1) }{ 2 }
-            -
-            1
-        \right)
-        r(y, \eta) q(x,dy)
-    \Bigg) dv_1
-\nonumber\\
-&&\qquad\qquad {}
-    +
-    f(\lp) \sum_{(x,u)\in\lp}\,
-    \left(
-        \lambda^{-1}
-        \gamma(x,\eta)
-        \int_{\IR^d} r(y, \eta) q(x, dy)
-        u^2
-        -
-        b(x,\eta) u
-    \right)
-    \frac{ \partial_u g(x,u) }{ g(x,u) }
-.\nonumber
-\end{eqnarray}
-The two terms under the integral correspond, respectively,
-to either the parent or child being reassigned the new level $v_1$
-during a birth event.
-In the first case, the parent at location $x$,
-which had level $u$ before the event, is reassigned to level $v_1$,
-and the child is inserted at level $u$ and location $y$;
-in the second the parent retains its level,
-and offspring is inserted at level $v_1$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection*{Scaling of the Pre-limit Lookdown Model}
-
+\end{align}
+
+\comment{TODO: consider whether this is where we stick in
+    these explicit definitions of $\gamma$ and set $\lambda=N$.}
 To scale our lookdown model to be consistent with
@@
 and a level between $[0,N]$;
-the established birth rate $\gamma(x,\eta)$ is
-$$\theta\gamma^{\mathfrak{m}}_{\theta}(x, \eta)
-:=~\theta\gamma(x, \rho_{\gamma}*\eta(x)) \int r(y, \rho_{r}*\eta(y))q_{\theta}(x,dy);$$
+the birth rate is
+$$
+    \gamma(x, \eta)
+    :=
+    \gamma(x, \smooth{\gamma}\eta(x)),
+$$
+the establishment probability is
+$$
+    r(x, \eta)
+    :=
+    r(x, \smooth{r}\eta(x)),
+$$
 the local branching mechanism $b(x,\eta)$ is 
-$$b_{\theta}(x, \eta):=~ \theta \bigg\{ \gamma(x, \rho_{\gamma}*\eta(x)) \int r(y, \rho_{r}*\eta(y))q_{\theta}(x,dy)-\mu(x, \eta)\bigg\};$$
-and the dispersal kernel $q^{\mathfrak{m}}(x,\eta, dy)$ is 
-$$q^{\mathfrak{m}}_{\theta}(x,\eta,dy) 
-:=~ \frac{r(y,\rho_{r}*\eta(y)) q_{\theta}(x,dy)}{\int_{\mathbb{R}^d} r(y,\rho_{r}*\eta(y)) q_{\theta}(x,dy)}.$$
-
-We can now define our pre-limit explicitly as a solution to a Martingale Problem.
-\comment{TODO: this is a bit redundant with the above.
-Instead, maybe (a) describe the process in words; (b) give this definition;
-then (c) explain why it's the generator, so we only write down the generator once?}
+$$
+    b_{\theta}(x, \eta)
+    :=
+    \theta \left(
+        \gamma(x, \smooth{\gamma}\eta(x))
+        \int r(y, \smooth{r}\eta(y)) q_{\theta}(x,dy)
+        -
+        \mu(x, \eta)
+    \right) .
+$$
+and the dispersal kernel is $q_\theta$.
+
+We can now define the spatial-level process
+explicitly as a solution to a Martingale Problem,
+whose generator is just the sum of
+\eqref{eqn:birth_generator} and \eqref{eqn:level_generator}.
 
@@
     \label{Def: Rescaled Lookdown Models}
-
-For test measures $\xi$ taking value in $\mathcal{M}_F(\mathbb{R}^d \times [0,N])$,
-the set of finite measures on $\mathbb{R}^d \times [0,N]$,
-we define
-$$\eta:= \frac{1}{N}\xi(\cdot  \times [0, N])=
-\frac{1}{N}\sum_{(x,u) \in \xi}\delta_x$$
-to be its re-scaled spatial projection.
-
-We define $(\xi^{\theta}_t)_{t \geq 0}$
+We define $(\lp^{\theta}_t)_{t \geq 0}$
 to be the (unique) solution
+    \comment{(I'm not sure why unique is in parentheses here?)}
 to the Martingale Problem
-with initial condition $\xi_0$
+with initial condition $\lp_0 \in \mathcal{M}_F(\mathbb{R}^d \times [0,N])$
 and generator $A^{\theta}$ that satisfies
-
-\begin{eqnarray}\label{Eq: Prelimit Lookdown Generator}
-&&A^{\theta}f(\xi ) \\
-&&\quad =f(\xi )\,\sum_{(x,u)\in\eta}\,2 \gamma^{\mathfrak{m}}_{\theta}(x, \eta)\Bigg\{ \frac 12 N^{-1}\int_u^{
-N}g(x,v_1)dv_1\times \frac { \theta\int_{\mathbb{R}^d}(g(y,u)-g(x,u))q^{\mathfrak{m}}_{\theta}(x,\eta,dy) }{g(x,u)}\non\\
-&&\qquad\qquad\qquad\qquad\qquad\qquad\qquad +N^{-1}\theta\int_u^{
-N}\int_{\mathbb{R}^d}\left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\theta}(x,\eta,dy)dv_1\nonumber\Bigg\}\\
-&&\qquad\qquad
-+f(\eta )\sum_{(x,u)\in\xi}\,\left(N^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\eta) u^2 -b_{\theta}(x,\eta)u\right)\frac {\partial_u g(x,u)}{g(x,u)}.\nonumber
-\end{eqnarray}
-for all smooth functions $f \in C^{2}_{0}(\mathbb{R}^d)$. 
+\begin{equation*}
+\begin{split}
+& A^{\theta}f(\lp ) \\
+&\quad =
+    f(\lp)
+    \,\sum_{(x,u)\in \lp}\,
+    2 \gamma(x, \eta)
+    \Bigg\{ \frac 12 N^{-1}\int_u^N g(x,u_1) du_1
+            \times
+            \frac{
+                \theta \int_{\mathbb{R}^d}
+                (g(y,u) - g(x,u))
+                r(y, \eta) q_{\theta}(x,dy)
+            }{ g(x,u) }
+        \\
+    &\qquad\qquad\qquad\qquad\qquad\qquad\qquad {} +
+        N^{-1}\theta\int_u^N
+        \int_{\mathbb{R}^d}\left(
+            \frac{ g(y,u_1) + g(x,u_1) }{ 2 } - 1
+        \right)
+        r(y, \eta) q_{\theta}(x,dy)
+        du_1
+    \Bigg\}\\
+    &\qquad\qquad {} +
+    f(\lp) \sum_{(x,u)\in\lp}\,
+    \left(
+        \theta N^{-1} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q_\theta(x, dy) u^2 -b_{\theta}(x,\eta)u
+    \right)
+    \frac{\partial_u g(x,u)}{g(x,u)}
+    ,
+\end{split}
+\end{equation*}
+for all smooth functions $g \in C^{2}_{0}(\mathbb{R}^d)$,
+where $f(\lp) = \prod_{(x, u) \in \lp} g(x, u)$ as defined in \eqref{eqn:test_functions},
+and $\eta(\cdot) = \lp(\cdot \times [0, N]) / N$ is the spatial pushforward of $\lp$,
+as before.
 \end{definition}
-
-\comment{Remark on the Remark: this is more than one remark.
-I'm not sure it needs to be in a Remark block: how about just a few paragraphs?}
 
@@
 assigning each particle an i.i.d. uniform $[0,N]$-level,
-and for any $\xi \in \mathcal{N}_f(\mathbb{R}^d \times [0,\infty))$, we denote
-$$\hat{f}(\xi)=\int f(\xi) \Gamma (d\textbf{u})$$ 
+and for any $\lp \in \mathcal{M}_f(\mathbb{R}^d \times [0,\infty))$, we denote
+$$\hat{f}(\lp)=\int f(\lp) \Gamma (d\textbf{u})$$ 
 to be the spatial test functions with averaged level,
@@
 \begin{aligned}
-M^{\theta}_t:=&\hat{f}(\xi_t)-\hat{f}(\xi_0)-\int_{0}^{t}\int   A^{\theta}f(\xi_s)\Gamma(d\textbf{u})ds\\
-:=&\hat{f}(\xi_t)-\hat{f}(\xi_0)-\int_{0}^{t}   \Pgen^{\theta}\hat{f}(\xi_s)ds
+M^{\theta}_t:=&\hat{f}(\lp_t)-\hat{f}(\lp_0)-\int_{0}^{t}\int   A^{\theta}f(\lp_s)\Gamma(d\textbf{u})ds\\
+:=&\hat{f}(\lp_t)-\hat{f}(\lp_0)-\int_{0}^{t}   \Pgen^{\theta}\hat{f}(\lp_s)ds
 \end{aligned}    
@@
 are i.i.d. uniformly distributed between $[0,N]$.
-
-Therefore, we use the same notation $\eta$
-in our spatial model
-to denote the spatial projection of $\xi$,
-and we reserve the notation $\xi$
-strictly for the spatial-level process.
 

### 2022-04-20 forwards-and-backwards.tex
.

@@
     and define
-    \begin{align}
+    \begin{align} \label{eqn:mu_defn}
         \mu(x, \eta)
@@
 Putting these together,
-the level $u$ of an individual at $x$
-evolves according to
+the level $u$ of an individual at $x$ in $\lp$ evolves according to:
 $$
-\dot{u}
+    \dot u
     =
-    - \frac{u}{\lambda} \left(\lambda - u\right)
+    - \frac{\theta}{\lambda} u \left(\lambda - u\right)
     \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q(x, dy) 
     +
-    \mu(x,\eta) u .
+    \theta \mu(x,\eta) u .
 $$
+The factor of $\theta$ appears here because we have rescaled time.
 We shall write 
@@
 i.e., the deviation from criticality of the branching mechanism.
-(This differs from $F(x,\eta) = \theta(r(x,\eta)\gamma(x,\eta) - \mu(x,\eta))$ defined above
-because $b$ contains the adjustment to fecundity obtained by
-averaging over establishment probabilities in the locations that offspring disperse to.)
-\comment{TODO: make this explanation better.}
+Recall from equation \eqref{eqn:mu_defn} that
+$F(x,\eta) = \theta(r(x,\eta)\gamma(x,\eta) - \mu(x,\eta))$,
+and so we will have that
+\begin{align*}
+b(x, \eta)
+&=
+    \theta \gamma(x, \eta) \int_{\IR^d} \left( r(y, \eta) - r(x, \eta) \right) q(x, dy)
+    + F(x, \eta) \\
+&\to
+    \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta) \qquad \text{as } \theta \to \infty .
+\end{align*}
+
 We can then rewrite the differential equation 
-governing the how each individual's level evolves as
+governing how the level of each individual
+in $\lp$ evolves as
 \begin{align}
@@
     &=
-    \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy)
+    \theta \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy)
     \left\{
@@
     -
-    b(x,\eta)u
+    b(x,\eta) u
     \nonumber \\
     &=
-    \lambda^{-1} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
+    \frac{\theta}{\lambda} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
     -
-    b(x, \eta) u / \theta
+    b(x, \eta) u
     . \label{differential equation for level}
 \end{align}
+(The factor of $\theta$ appears because of the rescaling of time for $\lp$.)
 
@@
         \int_u^\lambda \int_{\IR^d}
-        \left( \frac{g(y, u_1) + g(x, v_1)}{2} - 1 \right)
+        \left( \frac{g(y, u_1) + g(x, u_1)}{2} - 1 \right)
         r(y, \eta) q(x, dy)
@@
 by one at $(x, u_1)$ and another at $(y, u)$.
+We've written it in this form because the two pieces
+each naturally converge to separate terns in the limit.
 
@@
 \begin{definition}[Martingale Problem Characterisation]
-    \label{Def: Rescaled Lookdown Models}
+    \label{defn:lookdown_mgale}
 We define $(\lp^{\theta}_t)_{t \geq 0}$
@@
 \end{remark}
+
 \begin{lemma}[Convergence of generators for the population process]
@@
     \label{sec:lookdown_generator_proofs}
+
+\comment{Here's an informal writeup of this convergence;
+mostly I'm doing it to make sure I've got the right stuff above.}
+
+In Definition~\ref{defn:lookdown_mgale} we saw that the generator
+of $(\lp_t)_{t \ge 0}$ is the sum of two parts,
+equations \eqref{eqn:birth_generator} and \eqref{eqn:level_generator}.
+Assume that there is a $u_*$ such that $g(x, u) = 1$ for all $u \ge u_*$.
+We consider these two in turn.
+
+First, the contribution from births is
+\begin{align*}
+\begin{split}
+f(\lp)
+&\mapsto
+    f(\lp)
+    \sum_{(x, u) \in \lp}
+    2 \gamma(x, \eta)
+    \bigg\{
+        \frac{1}{2 \lambda}
+        \int_u^\lambda
+        g(x, u_1) du_1
+        \frac{
+            \theta \int_{\IR^d} (g(y, u) - g(x, u)) r(y, \eta) q(x, dy)
+        }{
+            g(x, u)
+        }
+    \\ & \qquad \qquad \qquad {}
+        + \frac{\theta}{\lambda}
+        \int_u^\lambda \int_{\IR^d}
+        \left( \frac{g(y, u_1) + g(x, u_1)}{2} - 1 \right)
+        r(y, \eta) q(x, dy)
+    \bigg\}
+    .
+    \end{split}
+\end{align*}
+We have that
+\begin{align*}
+    \theta \int_{\IR^d} (g(y, u) - g(x, u)) r(y, \eta) q(x, dy)
+    \to
+    \DG(gr)(x) \qquad \text{as }\theta \to \infty,
+\end{align*}
+i.e., to $\DG\left(g(\cdot, u) r(\cdot, \smooth{r}\eta(\cdot))\right)(x)$.
+Furthermore, by our assumption on $g$,
+$\int_u^\lambda g(x, u_1) du_1 / \lambda \to 1$ for all $x$ and $u$,
+so the first term here converges to
+\begin{align*}
+    2 \gamma(x, \eta)
+        \frac{1}{2}
+        \frac{
+            \DG\left( g(\cdot, u) r(\cdot, \smooth{r}\eta(\cdot))\right)(x)
+        }{
+            g(x, u)
+        } .
+\end{align*}
+This corresponds to each particle moving according to the motion induced by
+$g \mapsto \gamma \DG(gr)$.
+\comment{TODO: explain the $r$-tilted $\DG$ motion somewhere.}
+As for the second term,
+since $\int g(y, u_1) q(x, dy) \to g(x, u_1)$
+and $\theta/\lambda \to \delta$,
+it converges to
+\begin{align*}
+    \delta
+    \int_u^\infty
+    \left( g(x, u_1) - 1 \right)
+    r(x, \eta) .
+\end{align*}
+This corresponds to births at higher levels at rate $\gamma r$.
 

### 2022-04-20 forwards-and-backwards.tex
generator convergence appendix

@@
 and so we will have that
-\begin{align*}
+\begin{align} \label{eqn:b_limit}
 b(x, \eta)
@@
     \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta) \qquad \text{as } \theta \to \infty .
-\end{align*}
+\end{align}
 
@@
 
-\comment{Here's an informal writeup of this convergence;
-mostly I'm doing it to make sure I've got the right stuff above.}
+\comment{
+    I did this informal writeup of convergence of the lookdown generator
+    without looking at the previous version
+    mostly to double-check what we have there
+    (which is probably better).
+}
 
@@
 \begin{align*}
-    2 \gamma(x, \eta)
-        \frac{1}{2}
+    \gamma(x, \eta)
         \frac{
@@
 \begin{align*}
-    \delta
+    2 \delta
+    \gamma(x, \eta)
+    r(x, \eta) 
     \int_u^\infty
     \left( g(x, u_1) - 1 \right)
-    r(x, \eta) .
+    du_1
 \end{align*}
-This corresponds to births at higher levels at rate $\gamma r$.
+This corresponds to births at higher levels at rate $2 \delta \gamma r$.
+
+The remaining term is \eqref{eqn:level_generator}:
+\begin{align*}
+    f(\lp)
+    \mapsto
+    f(\lp)
+    \sum_{(x, u) \in \lp}
+    \left(
+    \theta
+        \lambda^{-1} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
+        -
+        b(x, \eta)u
+    \right)
+    \frac{\partial_u g(x,u)}{g(x,u)} .
+\end{align*}
+The first part only uses the fact that $\theta/\lambda \to \delta$,
+while as noted in \eqref{eqn:b_limit}, $b$ converges to $\gamma \DG r + F$,
+so in total this term converges to
+\begin{align*}
+    f(\lp)
+    \mapsto
+    f(\lp)
+    \sum_{(x, u) \in \lp}
+    \left(
+    \delta
+        \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
+        -
+        \left\{
+            \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta)
+        \right\} u
+    \right)
+    \frac{\partial_u g(x,u)}{g(x,u)} .
+\end{align*}
+In other words, the level of a particle at $x$ evolves according to
+\begin{align*}
+    \dot u
+    =
+    \delta
+        \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
+        -
+        \left\{
+            \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta)
+        \right\} u .
+\end{align*}
 

### 2022-04-20 forwards-and-backwards.tex
.

@@
 \newcommand{\lp}{\xi}              % process with levels
+\newcommand{\labelspace}{\mathcal{I}} % space of labels
 
@@
 %% %% %% %% %% %% %% %% %% %% %% %%
-\subsection{Evolution of an Individual Particle}
+\subsection{Construction of individual lineages}
+
+Although we will \comment{later} show convergece of the lookdown process
+defined by Definition~\ref{defn:lookdown_mgale}
+to a stochastic process in which individuals retain their identities,
+it is convenient to construct the lookdown process
+in a way that explicitly represents the motion of each individual and their offspring.
+This will then make obvious how linages move in the limit.
+
+To construct the process, each individual will have a label in $\labelspace = \bigcup_{k > 1} \IN^k$,
+in such a way that offspring's labels are formed by appending a unique integer
+onto their parent's label (i.e., a Ulam-Harris scheme).
+The behavior of each individual is driven by an associated Poisson process:
+for each label $\ell \in \labelspace$
+we associate a Poisson random measure $\Pi_\ell$
+on $[0, \infty)^2 \times \IR^d \times \{0, 1\}$.
+The mean measure is a product measure:
+on $[0, \infty)^2$ it is Lesbegue,
+on $\IR^d$ it is the dispersal distribution (i.e., $q(0, \cdot)$),
+and on $\{0, 1\}$ it is $\frac{1}{2} \delta_0 + \frac{1}{2} \delta_1$
+(i.e., a coin flip).
+If a point in $\Pi_\ell$ is $(s, v, y, \kappa)$, that will mean that
+$s$ is a potential birth time for individual $\ell$,
+$v$ is used to determine the new level,
+$y$ is the new location relative to that of $\ell$'s location,
+and $\kappa$ is used to determine whether the parent or child takes the new level.
+
+To begin,
+each individuals alive at time zero is indexed by a positive integer.
+Then
+
+%% %% %% %% %% %% %% %% %% %% %% %%
+\subsection{PREVIOUS VERSION OF Evolution of an Individual Particle}
 \label{sec: Evolution of an Individual Particle}

### 2022-04-21 forwards-and-backwards.tex
moar lookdown bits

--- 2022-04-20 forwards-and-backwards.tex
@@
 %% %% %% %% %% %% %% %% %% %% %% %%
-\subsection{Evolution of an Individual Particle}
+\subsection{Construction of individual lineages}
+
+Although we will \comment{later} show convergece of the lookdown process
+defined by Definition~\ref{defn:lookdown_mgale}
+to a stochastic process in which individuals retain their identities,
+it is convenient to construct the lookdown process
+in a way that explicitly represents the motion of each individual and their offspring.
+This will then make obvious how linages move in the limit.
+
+We will construct the process using a Ulam-Harris indexing scheme,
+which associates the outcomes of each branching event with a label obtained
+by appending to the previous label.
+To begin, we assign each extant individual a label from $\IN_{\ge 0}$.
+Suppose an individual with label $a$ and level $u$ reproduces,
+and as a result there are two individuals, one with level $u$ and one with a new level $u_1 > u$.
+The parent individual, previously labeled $a$, might be assigned either level.
+After reproduction, we give a new label to \emph{only} the individual
+that is given the new level $u_1$,
+retaining the label $a$ for the individual with the old level $u$.
+So, there is a unique label assigned at each birth event,
+and it is assigned to the resulting individual with the higher level.
+It would be possible to reconstruct individual identities along a line of descent
+from this construction,
+but we don't write this out.
+
+Concretely, then: for each label $a$ in
+$\labelspace = \bigcup_{k \ge 1} \IN_{\ge 1}^k$
+let $\Pi_a$ be an independent Poisson process on $[0, \infty)^2 \times \IR_d \times \{0,1\}$.
+The mean measure is a product of Lesbegue measure on the first three coordinates
+and $q(0, \cdot)$ on the remainder.
+For a point $(t, v, y, kappa)$ in $\Pi_a$,
+first $t$ will determine possible birth times,
+$v$ will determine levels of the offspring,
+$y$ will give the spatial displacement of the offspring relative to the parent,
+and $\kappa$ will be used to determine whether parent or offspring are assigned the new level.
+Each label $a$ has a birth time $\tau_a$,
+when it is first assigned,
+and a death time $\sigma_a$, when its level first hits $\lambda$.
+For any $\tau_a \le t \le \sigma_a$ we denote by $X_a(t)$ and $U_a(t)$ the spatial location and level
+of the individual carrying label $a$ at time $t$.
+Now, since we have defined labels so that the level does not jump,
+$U_a$ satistifies, for $\tau_a \le t \le \sigma_a$,
+\begin{equation*}
+    \begin{split}
+& U_a(t)
+    =
+    U_a(\tau_a) \\
+&\qquad {}   
+    + \int_{\tau_a}^{t}
+    \left(
+        \frac{\theta}{\lambda} \gamma(X_a(s),\eta(s)) \int_{\IR^d} r(y,\eta(s)) q(X_a(s),dy) U_a(s)^2
+        -
+        b(X_a(s),\eta(s)) U_a(s)
+    \right)
+    ds ,
+\end{split}
+\end{equation*}
+and, of course, $\sigma_a = \inf\{t \ge \tau_a : U_a(t) > \lambda\}$.
+
+Potential reproduction events occur at times $\tau_a + s$ for each point $(s, v, y, \kappa) \in \Pi_a$.
+We say `potential' since if the resulting level is greater than $\lambda$,
+the event does not happen.
+If this is the $j^\text{th}$ such successful event,
+\comment{(need to sort out the "successful" qualifier)}
+the new level is $aj$ (i.e., $a$ with the integer $j$ appended),
+and the (potential) new level is
+\begin{equation*}
+    U_{aj}(\tau_a + s)
+    =
+    U_a(\tau_a + s)
+    +
+    \frac{
+        v
+    }{
+        2 \lambda^{-1} \theta \gamma(X_a(\tau_a + s-), \eta(\tau_a + s-))
+        \int_{\IR^d} r(y, \eta(\tau_a + s-)) q(X_a(\tau_a + s-), dy)
+    }.
+\end{equation*}
+If $U_{aj}(\tau_a+s) < \lambda$,
+a new individual is produced with this level, label $aj$ and
+location 
+$$
+    X_{aj}(\tau_a + s)
+    =
+    X_a(\tau_a+s-) + (1 - \kappa) y .
+$$
+If $\kappa=1$, then it is the original label that moves spatial locations, so
+$$
+    X_a(\tau_a+s)
+    =
+    X_a(\tau_a+s-) + \kappa y .
+$$
+
+%% %% %% %% %% %% %% %% %% %% %% %%
+\subsection{PREVIOUS VERSION OF Evolution of an Individual Particle}
 \label{sec: Evolution of an Individual Particle}

### 2022-04-21 forwards-and-backwards.tex
.

@@
 the level $u$ of an individual at $x$ in $\lp$ evolves according to:
-$$
+\begin{equation} \label{eqn:dot_u}
     \dot u
@@
     \theta \mu(x,\eta) u .
-$$
+\end{equation}
 The factor of $\theta$ appears here because we have rescaled time.
@@
 
-Although we will \comment{later} show convergece of the lookdown process
+Although we will \comment{(later)} show convergece of the lookdown process
 defined by Definition~\ref{defn:lookdown_mgale}
@@
 The parent individual, previously labeled $a$, might be assigned either level.
-After reproduction, we give a new label to \emph{only} the individual
+We will track chains of descendant individuals forwards through time
+following levels, rather than individuals, and will call this a \emph{line of descent}.
+So, after reproduction, we give a new label to \emph{only} the individual
 that is given the new level $u_1$,
@@
 let $\Pi_a$ be an independent Poisson process on $[0, \infty)^2 \times \IR_d \times \{0,1\}$.
-The mean measure is a product of Lesbegue measure on the first three coordinates
-and $q(0, \cdot)$ on the remainder.
-For a point $(t, v, y, kappa)$ in $\Pi_a$,
-first $t$ will determine possible birth times,
+The mean measure is a product of Lesbegue measure on the first two coordinates,
+$q(0, \cdot)$ on $\IR^d$, and $(\delta_0 + \delta_1)/2$ on $\{0, 1\}$.
+It will also be convenient
+to suppose that for each label $a$ we have an enumeration of the points in $\Pi_a$,
+so we may refer to ``the $j^\text{th}$ point in $\Pi_a$'',
+although the precise order of this enumeration is irrelevant.
+If $(t, v, y, \kappa)$ is the $j^\text{th}$ point in $\Pi_a$,
+then $t$ will determine possible birth times,
 $v$ will determine levels of the offspring,
 $y$ will give the spatial displacement of the offspring relative to the parent,
-and $\kappa$ will be used to determine whether parent or offspring are assigned the new level.
+$\kappa$ will be used to determine whether parent or offspring are assigned the new level,
+and the new label produced, if any will be $aj$,
+i.e., the label $a$ with $j$ appended (so, if $a \in \IN_{\ge 0}^k$ then $aj \in \IN_{\ge 0}^{k+1}$).
 Each label $a$ has a birth time $\tau_a$,
@@
 Now, since we have defined labels so that the level does not jump,
-$U_a$ satistifies, for $\tau_a \le t \le \sigma_a$,
+$U_a$ satistifies~\eqref{eqn:dot_u} for $\tau_a \le t \le \sigma_a$, i.e.,
 \begin{equation*}
@@
     \left(
-        \frac{\theta}{\lambda} \gamma(X_a(s),\eta(s)) \int_{\IR^d} r(y,\eta(s)) q(X_a(s),dy) U_a(s)^2
+        \frac{\theta}{\lambda} \gamma(X_a(s),\eta(s))
+        \int_{\IR^d} r(z,\eta(s)) q(X_a(s),dz) U_a(s)^2
         -
@@
 
-Potential reproduction events occur at times $\tau_a + s$ for each point $(s, v, y, \kappa) \in \Pi_a$.
+Potential reproduction events occur at times $\tau_a + s$
+for each point $(s, v, y, \kappa) \in \Pi_a$.
 We say `potential' since if the resulting level is greater than $\lambda$,
 the event does not happen.
-If this is the $j^\text{th}$ such successful event,
-\comment{(need to sort out the "successful" qualifier)}
-the new level is $aj$ (i.e., $a$ with the integer $j$ appended),
-and the (potential) new level is
+If this is the $j^\text{th}$ point in $\Pi_a$,
+the new label is $aj$ and the (potential) new level is
 \begin{equation*}
@@
         2 \lambda^{-1} \theta \gamma(X_a(\tau_a + s-), \eta(\tau_a + s-))
-        \int_{\IR^d} r(y, \eta(\tau_a + s-)) q(X_a(\tau_a + s-), dy)
+        r(X_a(\tau_a + s-) + y, \eta(\tau_a + s-))
     }.
@@
 If $U_{aj}(\tau_a+s) < \lambda$,
-a new individual is produced with this level, label $aj$ and
-location 
+the new individual labeled $aj$ is produced,
+and $\kappa$ determines which label is associated with the new location,
+so
+\begin{align*}
+    X_{aj}(\tau_a + s)
+    &=
+    X_a(\tau_a+s-) + (1 - \kappa) y \\
+    X_a(\tau_a+s)
+    &=
+    X_a(\tau_a+s-) + \kappa y .
+\end{align*}
+If $U_{aj}(\tau_a+s) \ge \lambda$, then $X_a$ is unchanged.
+Recall that the parental \emph{individual} always retains their spatial location,
+so that $\kappa = 0$ corresponds to the parent being assigned a new level,
+and our line of descent switching to the offspring.
+
+Consequently, 
+the \emph{line of descent}
+leading from the initial generation
+to any label $a \in \labelspace$
+can be explicitly constructed as follows.
+Supposed that $a = (a_1, a_2, \ldots, a_n) \in \IN^n$,
+and for $1 \le k \le n$ let $(a)_k = (a_1, a_2, \ldots, a_k)$.
+Then, let $\zeta_a(t)$ denote the counting process that records
+which label is present in the line of descent at time $t$,
+i.e., $\zeta_a(t) = \max\{k \ge 1 : \tau_{(a)_k} \le t\}$.
+This then lets us define $X_a(t)$ all the way back to $t=0$
+by setting $X_a(t) = X_{(a)_{\zeta_a(t)}}(t)$ (and, $U_a(t)$ similarly).
+Now, we can explicitly write down the evolution of $U_a(t)$ and $X_a(t)$.
+
+First, for each $1 \le k < n$
+let $(s_k, v_k, y_k, \kappa_k)$ be the $a_{k+1}^\text{th}$ point in $\Pi_{(a)_k}$
+(this is the sequence of jumps taken by the line of descent).
+Note that $s_k = \tau_{(a)_k}$, and also set $s_0 = 0$.
+Let $\Gamma_a$ by the point process ``experienced by the line of descent leading to $a$'',
+which is for $A \subset [0,\infty)^2 \times \IR^d \times \{0,1\}$
 $$
-    X_{aj}(\tau_a + s)
+\Gamma_a(A)
 =
-    X_a(\tau_a+s-) + (1 - \kappa) y .
+    \sum_{k=1}^n
+    \Pi_{(a)_k}\left(A \cap [s_{k-1}, s_k) \times [0, \infty) \times \IR^d \times \{0,1\}\right) .
 $$
-If $\kappa=1$, then it is the original label that moves spatial locations, so
-$$
-    X_a(\tau_a+s)
-    =
-    X_a(\tau_a+s-) + \kappa y .
-$$
+Then for $0 \le t \le \sigma_a$,
+\begin{align*}
+    X_a(t)
+    &=
+    X_{a_1}(0)
+    +
+    \sum_{k=1}^{\zeta_a(t) - 1}
+    y_k
+    +
+    \int_{
+        [0, t) \times [0, \infty) \times \IR^d \times \{0, 1\}
+    }
+    \kappa y
+    \Gamma_{a}(ds, dv, dy, d\kappa) .
+\end{align*}
+
+% Then for $0 \le t \le \sigma_a$,
+% \begin{align*}
+%     X_a(t)
+%     &=
+%     X_{a_1}(0)
+%     +
+%     \sum_{k=1}^{\zeta_a(t) - 1}
+%     \left(
+%     y_k
+%     +
+%     \int_{
+%         [s_{k-1}, s_{k}) \times [0, \infty) \times \IR^d \times \{0, 1\}
+%     }
+%     \kappa y
+%     \Pi_{(a)_k}(ds, dv, dy, d\kappa)
+%     \right)
+%     \\
+%     &\qquad {}
+%     +
+%     \int_{
+%         [s_{\zeta_a(t)}, t) \times [0, \infty) \times \IR^d \times \{0, 1\}
+%     }
+%     \kappa y
+%     \Pi_{(a)_{\zeta_a(t)}}(ds, dv, dy, d\kappa) .
+% \end{align*}
 

### 2022-04-22 forwards-and-backwards.tex
.

@@
 %% %% %% %% %% %% %% %% %% %% %% %%
-\subsection{Construction of individual lineages}
+\subsection{Construction tracking individual lines of descent}
+
+\comment{This is a rewrite using Ulam-Harris labeling
+of \ref{sec: Evolution of an Individual Particle}.}
 
@@
 If this is the $j^\text{th}$ point in $\Pi_a$,
-the new label is $aj$ and the (potential) new level is
-\begin{equation*}
-    U_{aj}(\tau_a + s)
+the new label is $aj$, the (potential) birth time is $\tau_{aj} = \tau_a + s$.
+For convenience define
+$$
+    \ell(x, y, \eta, v)
     =
-    U_a(\tau_a + s)
-    +
     \frac{
@@
     }{
-        2 \lambda^{-1} \theta \gamma(X_a(\tau_a + s-), \eta(\tau_a + s-))
-        r(X_a(\tau_a + s-) + y, \eta(\tau_a + s-))
-    }.
+        2 \lambda^{-1} \theta \gamma(x, \eta) r(x + y, \eta)
+    } ,
+$$
+and using this, the (potential) new level is
+\begin{equation*}
+    U_{aj}(\tau_{aj})
+    =
+    U_a(\tau_{aj})
+    +
+    \ell(X_a(\tau_{aj}-), y, \eta(\tau_{aj}-), v) .
 \end{equation*}
-If $U_{aj}(\tau_a+s) < \lambda$,
+If $U_{aj}(\tau_{aj}) < \lambda$,
 the new individual labeled $aj$ is produced,
@@
     &=
-    X_a(\tau_a+s-) + (1 - \kappa) y \\
+    X_a(\tau_a+s-) + (1 - \kappa) y .
+\end{align*}
+On the other hand
+if $U_{aj}(\tau_a+s) \ge \lambda$, then $X_a$ is unchanged and $X_{aj}$ is undefined,
+so
+\begin{align*}
     X_a(\tau_a+s)
     &=
-    X_a(\tau_a+s-) + \kappa y .
+    X_a(\tau_a+s-) + \kappa y \mathbbm{1}_{U_{aj}(\tau_{aj}) < \lambda} .
 \end{align*}
-If $U_{aj}(\tau_a+s) \ge \lambda$, then $X_a$ is unchanged.
 Recall that the parental \emph{individual} always retains their spatial location,
@@
 to any label $a \in \labelspace$
+with $U_a(\tau_a) < \lambda$
 can be explicitly constructed as follows.
@@
 
+\comment{Do we want subscript $a$s here, on e.g., $\zeta$?
+I think not, because this is all given a particular $a$?}
+
 First, for each $1 \le k < n$
@@
 Let $\Gamma_a$ by the point process ``experienced by the line of descent leading to $a$'',
+which is easier to define if we treat point processes as sets for a moment,
+defining
+\begin{align*}
+    \Gamma_a
+    &=
+    \bigcup_{k=1}^n 
+    \bigg\{
+        (s, v, y, \kappa) \in \Pi_{(a)_k} \; : \;
+        \tau_{(a)_{k-1}} \le s < \tau_{(a)_{k-1}} 
+    \\& \qquad \qquad 
+        \text{ and }
+        U_{(a)_k}(\tau_{(a)_{k-1}} + s) + \ell( X_{(a)_k}(\tau_{(a)_{k-1}} + s-), y, \eta(\tau_{(a)_{k-1}} + s-), v) < \lambda
+    \bigg\}
+\end{align*}
+\comment{TODO include the switch points}
+
 which is for $A \subset [0,\infty)^2 \times \IR^d \times \{0,1\}$
-$$
+\comment{This is wrong, as it includes non-viable individuals.}
+\begin{align*}
 \Gamma_a(A)
-=
+    &=
     \sum_{k=1}^n
-    \Pi_{(a)_k}\left(A \cap [s_{k-1}, s_k) \times [0, \infty) \times \IR^d \times \{0,1\}\right) .
-$$
+    \Pi_{(a)_k}\left(A \cap [s_{k-1}, s_k) \times [0, \infty) \times \IR^d \times \{0,1\}\right) 
+    \\ &\qquad {}
+    + \sum_{k=1}^{n-1}
+      \delta_{(s_k, v_k, y_k, 1 - \kappa_k)}(A) .
+\end{align*}
+Note that we have included the points at which the line of descent's level jumps,
+flipping $\kappa$ at these points,
+and as a result $\Gamma_a$ has the same distribution as $\Pi_a$
+restricted to $[0, \sigma_a)$.
 Then for $0 \le t \le \sigma_a$,
-\begin{align*}
+\begin{align} \label{eqn:X_line_of_descent}
     X_a(t)
@@
     X_{a_1}(0)
-    +
-    \sum_{k=1}^{\zeta_a(t) - 1}
-    y_k
     +
@@
     \kappa y
-    \Gamma_{a}(ds, dv, dy, d\kappa) .
-\end{align*}
-
-% Then for $0 \le t \le \sigma_a$,
-% \begin{align*}
-%     X_a(t)
-%     &=
-%     X_{a_1}(0)
-%     +
-%     \sum_{k=1}^{\zeta_a(t) - 1}
-%     \left(
-%     y_k
-%     +
-%     \int_{
-%         [s_{k-1}, s_{k}) \times [0, \infty) \times \IR^d \times \{0, 1\}
-%     }
-%     \kappa y
-%     \Pi_{(a)_k}(ds, dv, dy, d\kappa)
-%     \right)
-%     \\
-%     &\qquad {}
-%     +
-%     \int_{
-%         [s_{\zeta_a(t)}, t) \times [0, \infty) \times \IR^d \times \{0, 1\}
-%     }
-%     \kappa y
-%     \Pi_{(a)_{\zeta_a(t)}}(ds, dv, dy, d\kappa) .
-% \end{align*}
+    \mathbbm{1}_{
+        U_{(a)_{\zeta(s)}}(s) + \ell( X_{(a)_{\zeta(s)}}(s-), y, \eta(s-), v) < \lambda
+    }
+    \Gamma_{a}(ds, dv, dy, d\kappa) 
+\end{align}
+and
+\begin{align} \label{eqn:U_line_of_descent}
+    U_a(t)
+    &=
+    U_{a_1}(0)
+    +
+    \sum_{k=1}^{\zeta_a(t) - 1}
+    \frac{
+        v_k
+    }{
+        2 \lambda^{-1} \theta \gamma(X_{(a)_k}(s_k-), \eta(s_k-))
+        r(X_{(a)_k}(s_k-) + y_k, \eta(s_k-))
+    }
+    \\ & \qquad {}
+    +
+    \int_0^t
+    \bigg(
+        \frac{\theta}{\lambda} \gamma(X_a(s),\eta(s))
+        \int_{\IR^d} r(z,\eta(s)) q(X_a(s),dz) U_a(s)^2
+    \\ & \qquad\qquad  \qquad {}
+        -
+        b(X_a(s),\eta(s)) U_a(s)
+    \bigg)
+    dt .
+\end{align}
+
+%% %% %% %% %% %% %% %% %% %% %% %%
+\subsection{Limiting processes for lines of descent}
+
+\comment{This is a rewrite of \ref{sec:lines_of_descent} following on the previous section}
+
+The previous section constructs the lookdown process
+in a way that makes individual lines of descent converge pointwise as $\lambda \to \infty$,
+using the same underlying Poisson processes $\{\Pi_a\}_{a \in \labelspace}$.
+To see this, first note that if the Poisson processes are fixed
+then the set of events to which a given label $a \in \labelspace$ is associated
+is also fixed -- this is the sequence $(s_k, v_k, y_k, \kappa_k)$ associated with a given label $a$.
+Therefore, the processes $\Gamma_a$ are also unchanged.
+First, we clearly need that the spatial measures $\eta$ converge.
+\comment{(hm, no notation for $\eta$ depending on $\lambda$ here; need to introduce this here?)}
+Now, consider equations~\eqref{eqn:X_line_of_descent} and~\eqref{eqn:U_line_of_descent}.
+
+Equation~\eqref{eqn:X_line_of_descent} simply says that $X_a$ follows a random walk
 
@@
 %% %% %% %% %% %% %% %% %% %% %% %%
-\subsection{Stochastic equations for movement of lines of descent}
+\subsection{PREVIOUS VERSION OF Stochastic equations for movement of lines of descent}
     \label{sec:lines_of_descent}

### 2022-04-22 forwards-and-backwards.tex
.

@@
 $U_a$ satistifies~\eqref{eqn:dot_u} for $\tau_a \le t \le \sigma_a$, i.e.,
-\begin{equation*}
+\begin{equation} \label{eqn:U_line_of_descent}
     \begin{split}
@@
 \end{split}
-\end{equation*}
+\end{equation}
 and, of course, $\sigma_a = \inf\{t \ge \tau_a : U_a(t) > \lambda\}$.
@@
 so
-\begin{align*}
+\begin{align} \label{eqn:X_line_of_descent}
     X_a(\tau_a+s)
@@
     X_a(\tau_a+s-) + \kappa y \mathbbm{1}_{U_{aj}(\tau_{aj}) < \lambda} .
-\end{align*}
+\end{align}
 Recall that the parental \emph{individual} always retains their spatial location,
@@
 and our line of descent switching to the offspring.
+
+We can now express our population processes using these levels:
+\begin{align*}
+    \eta_t = \sum_{a : \tau_a > t \;\&\; U_a(t) < \lambda} \delta_{X_a(t)}
+    \qquad \text{and} \qquad
+    \lp = \sum_{a : \tau_a > t \;\&\; U_a(t) < \lambda} \delta_{(X_a(t), U_a(t))} .
+\end{align*}
+
+\comment{
+    The following is quite annoying to get right, but can fixed up.
+    However, I don't think we need it.}
 
@@
 
-\comment{Do we want subscript $a$s here, on e.g., $\zeta$?
-I think not, because this is all given a particular $a$?}
-
 First, for each $1 \le k < n$
@@
 Let $\Gamma_a$ by the point process ``experienced by the line of descent leading to $a$'',
-which is easier to define if we treat point processes as sets for a moment,
-defining
-\begin{align*}
-    \Gamma_a
-    &=
-    \bigcup_{k=1}^n 
-    \bigg\{
-        (s, v, y, \kappa) \in \Pi_{(a)_k} \; : \;
-        \tau_{(a)_{k-1}} \le s < \tau_{(a)_{k-1}} 
-    \\& \qquad \qquad 
-        \text{ and }
-        U_{(a)_k}(\tau_{(a)_{k-1}} + s) + \ell( X_{(a)_k}(\tau_{(a)_{k-1}} + s-), y, \eta(\tau_{(a)_{k-1}} + s-), v) < \lambda
-    \bigg\}
-\end{align*}
-\comment{TODO include the switch points}
-
 which is for $A \subset [0,\infty)^2 \times \IR^d \times \{0,1\}$
-\comment{This is wrong, as it includes non-viable individuals.}
+\comment{This is wrong, because $s$ is relative to birth time.}
 \begin{align*}
@@
 Then for $0 \le t \le \sigma_a$,
-\begin{align} \label{eqn:X_line_of_descent}
+\begin{align*}
     X_a(t)
@@
     \Gamma_{a}(ds, dv, dy, d\kappa) 
-\end{align}
+\end{align*}
 and
-\begin{align} \label{eqn:U_line_of_descent}
+\begin{align*}
     U_a(t)
@@
     dt .
-\end{align}
+\end{align*}
 
@@
 \comment{(hm, no notation for $\eta$ depending on $\lambda$ here; need to introduce this here?)}
-Now, consider equations~\eqref{eqn:X_line_of_descent} and~\eqref{eqn:U_line_of_descent}.
-
-Equation~\eqref{eqn:X_line_of_descent} simply says that $X_a$ follows a random walk
+
+Supposing that they do,
+consider how a line of descent $(X_a(t), U_a(t))$ evolves.
+The line of descent throws off a new line of descent at a higher level
+when there is a point $(s, v, y, \kappa)$ in $\Pi_a$ with 
+\begin{equation} \label{eqn:line_points}
+v < 2 (\lambda - U_a(t)) \lambda^{-1} \theta \gamma(X_a(t), \eta) r(X_a(t)+y, \eta) .
+\end{equation}
+Since the mean measure of the $v$ coordinate is Lebesgue,
+$\theta/\lambda \to \delta$,
+and $q(x, dy) \to \delta_x(dy)$,
+this corresponds in the limit to new lines of descent being thrown off at all times,
+i.e., according to a Poisson process with rate
+$$
+\delta \gamma(X_a(t), \eta) r(X_a(t), \eta) 
+$$
+and uniform intensity on higher levels.
+Again, since in the limit the dispersal distance is zero,
+new levels are produced at the same spatial location.
+However, this affects the location of the line of descent:
+for each new line of descent, there is a $1/2$ chance
+that the line of descent switches location (i.e., moves to $X_a(t) + y$).
+Taking $g$ to be a suitable test function on $\IR^d$, 
+and rewriting~\eqref{eqn:line_points},
+the generator of this motion is, when the level is $u$,
+\begin{align*}
+    g(x)
+    &\mapsto
+    \left(1 - \frac{u}{\lambda}\right) \gamma(x, \eta)
+    \theta \int_{\IR^d} r(x+y, \eta) (g(x+y) - g(x)) q(x, dy) \\
+    &=
+    \left(1 - \frac{u}{\lambda}\right) \gamma(x, \eta)
+    \bigg\{
+        \theta \int_{\IR^d} (r(x+y, \eta) g(x+y) - r(x, \eta) g(x)) q(x, dy) \\
+        &\qquad \qquad {}
+        -
+        \theta \int_{\IR^d} (r(x+y, \eta) - r(x, \eta) ) g(x) q(x, dy) 
+    \bigg\} \\
+    &\to
+    \gamma(x, \eta)
+    \left(
+        \DG(rg)(x) - g(x) \DG(r)(x)
+    \right) .
+\end{align*}
+Notice that the factors of 2 have canceled,
+and that the result is independent of $u$.
 

### 2022-04-22 forwards-and-backwards.tex
.

@@
 \begin{align} \label{eqn:b_limit}
+\begin{split}
 b(x, \eta)
@@
     \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta) \qquad \text{as } \theta \to \infty .
+\end{split}
 \end{align}
@@
 
+The only thing that remains is to describe how the levels change.
+The limit of~\eqref{eqn:line_points} follows from
+equation \eqref{eqn:b_limit} and the fact that
+$\int_{\IR^d} r(z, \eta) q(x, dz) \to r(x, \eta)$.
+
+To write out the joint motion of spatial coordinate and levels,
+it is useful to work out the differential operator above in more detail.
+Recall that $\DG g(x) = \sum_i \meanq_i \partial_i g(x) + \sum_{ij} \covq_{ij} \partial_{ij} g(x)$,
+and for the moment write $r(x)$ for $r(\cdot, \eta(\cdot))(x)$,
+so that
+\begin{align*}
+\DG(rg)(x) - g(x) \DG(r)(x)
+    &=
+    r(x) \sum_i \meanq_i \partial_i g(x)
+    + 2 \sum_{ij} \meanq_i \partial_i r(x) \covq_{ij} \partial_j g(x)
+    + r(x) \sum_{ij} \covq_{ij} \partial_{ij} g(x) \\
+    &=
+    r(x) \left\{
+        \left(
+        \meanq
+        + 2 \covq \grad \log r(x)
+        \right)
+        \cdot
+        \grad g(x)
+        +
+        \sum_{ij} \covq_{ij} \partial_{ij} g(x)
+    \right\} .
+\end{align*}
+
+Now, let $\beta(x, \eta) = \meanq + 2 \Sigma \grad \log r(x, \eta)$,
+and associate with each label an independent $d$-dimensional Brownian motion $W_a$,
+and let $\covq = K K^T$.
+Then, we can summarize the results above by saying that
+in the infinite density limit,
+the spatial locations and level of each line of descent $a$
+behave for $\tau_a \le t < \sigma_a$ as
+\begin{equation*}
+\begin{split}
+X_a(t)
+    &=
+    X_a(\tau_a)
+    +
+    + \int_{\tau_a}^{t}
+    \bigg(
+        \beta(x, \eta(s)) ds
+        +
+        K dW_a(s)
+    \bigg)
+    ds .
+\end{split}
+\begin{split}
+U_a(t)
+    &=
+    U_a(\tau_a)
+    + \int_{\tau_a}^{t}
+    \bigg(
+        \delta \gamma(X_a(s),\eta(s))
+        r(x,\eta(s)) U_a(s)^2
+\\ &\qquad \qquad \qquad {}   
+        -
+        \left\{
+            \gamma(X_a(s),\eta(s)) \DG r(X_a(s),\eta(s))
+            + F(X_a(s), \eta(s))
+        \right\}
+        U_a(s)
+    \bigg)
+    ds .
+\end{split}
+\end{equation*}
+\comment{TODO: add description of Poisson random measure of birth times/levels as below.}
+
 %% %% %% %% %% %% %% %% %% %% %% %%
@@
 \end{remark}
+
 Furthermore, recall that in our scaling limit, 
@@
 \begin{align*}
-    \theta \int_{\IR^d} (g(y, u) - g(x, u)) r(y, \eta) q(x, dy)
-    \to
-    \DG(gr)(x) \qquad \text{as }\theta \to \infty,
+    &\theta \int_{\IR^d} (g(y, u) - g(x, u)) r(y, \eta) q(x, dy) \\
+    &\qquad =
+    \theta \int_{\IR^d} (r(y, \eta) g(y, u) - r(x, \eta) g(x, u)) q(x, dy)
+    - \theta \int_{\IR^d} g(x, u) (r(y, \eta) - r(x, \eta)) q(x, dy) \\
+    &\qquad \to
+    \DG(gr)(x) - g(x) \DG r(x) \qquad \text{as }\theta \to \infty.
 \end{align*}
-i.e., to $\DG\left(g(\cdot, u) r(\cdot, \smooth{r}\eta(\cdot))\right)(x)$.
+i.e., to
+$\DG\left(g(\cdot, u) r(\cdot, \smooth{r}\eta(\cdot))\right)(x)
+- g(\cdot, u) \DG\left(r(\cdot, \smooth{r}\eta(\cdot))\right)(x)$.
 Furthermore, by our assumption on $g$,
@@
             \DG\left( g(\cdot, u) r(\cdot, \smooth{r}\eta(\cdot))\right)(x)
+            -
+            g(\cdot, x) \DG\left( r(\cdot, \smooth{r}\eta(\cdot))\right)(x)
         }{
@@
 This corresponds to each particle moving according to the motion induced by
-$g \mapsto \gamma \DG(gr)$.
-\comment{TODO: explain the $r$-tilted $\DG$ motion somewhere.}
+$g \mapsto \gamma \DG(gr) - g \DG r$.
+\comment{TODO: explain the $r$-tilted $\DG$ motion somewhere earlier, introducing notation for it.}
 As for the second term,

### 2022-04-23 forwards-and-backwards.tex
done with pass through definitions

@@
 
+\comment{The following could be a Proposition?}
+
 Now, let $\beta(x, \eta) = \meanq + 2 \Sigma \grad \log r(x, \eta)$,
@@
 behave for $\tau_a \le t < \sigma_a$ as
-\begin{equation*}
-\begin{split}
+\begin{align*}
 X_a(t)
@@
     X_a(\tau_a)
-    +
     + \int_{\tau_a}^{t}
@@
     \bigg)
-    ds .
-\end{split}
-\begin{split}
+    ds  \\
 U_a(t)
@@
     ds .
-\end{split}
-\end{equation*}
-\comment{TODO: add description of Poisson random measure of birth times/levels as below.}
+\end{align*}
+To complete the description,
+for each label $a \in \labelspace$ let $R_a$ denote an independent Poisson process on $[0, \infty)^2$
+with Lebesgue mean measure,
+and as before order the points of each in some way.
+If the population state at time 0 is $\eta(0)$,
+then let $(x_i, u_i)$ be the points of a Poisson process
+with mean measure on $\IR^d \times [0, \infty)$ a product of $\eta(0)$ and Lebesgue measure.
+\comment{Here I've switched $t$ to be the absolute birth time
+rather than relative to the birth time of the parent; I think it's clearer?
+It, should be made to agree with the previous section.}
+For each point begin a line of descent
+with label $i$, location $X_i(0) = x_i$, level $U_a(0) = u_i$, and birth time $\tau_i = 0$.
+Each point in the $R_a$ denotes a potential birth time for $a$:
+if the $j^\text{th}$ point in $R_a$ is $(t, v)$,
+$\tau_a \ge t$, and and $U_a(t) < \infty$,
+then a new line of descent with label $aj$ is produced,
+with birth time $\tau_{aj} = t$, location $X_{aj}(t) = X_a(t)$, and level
+$$
+    U_{aj}(t) = U_a(t)
+    + \frac{v}{ 2 \delta \gamma(X_a(t), \eta(t)) r(X_a(t), \eta(t)) } .
+$$
+\comment{Perhaps the conclusion of the Propostion would be something like:}
+We can now express our population processes in the limit using these levels:
+\begin{align*}
+    \eta_t = \sum_{a : \tau_a > t \;\&\; U_a(t) < \lambda} \delta_{X_a(t)}
+    \qquad \text{and} \qquad
+    \lp = \sum_{a : \tau_a > t \;\&\; U_a(t) < \lambda} \delta_{(X_a(t), U_a(t))} .
+\end{align*}
 

### 2022-04-24 forwards-and-backwards.tex
errors squashed!

@@
 \newcommand{\DG}{\mathcal{B}}  % generator of the dispersal process
+\newcommand{\DD}{\mathcal{D}}  % the second-order part of the generator of dispersal
 \newcommand{\meanq}{\vec b}    % mean of dispersal, times theta
-\newcommand{\covq}{\Sigma}     % covariance matrix of dispersal, times theta
+\newcommand{\covq}{C}     % covariance matrix of dispersal, times theta
 \newcommand{\kernel}{\rho}  % interaction kernels
@@
 
+$$\lim \frac{\theta}{N} =: \alpha$$
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\comment{TODO: $\meanq$ can vary in space, make that clear?}
+
 \begin{definition}[Dispersal generator]
@@
     \begin{align}
-    \DG f(x) = \sum_i \meanq_i \partial_{x_i} f(x)
-        + \sum_{ij} \covq_{ij} \partial_{x_i} \partial_{x_j} f(x)
+    \DG f(x)
+        =
+        \sum_{ij} \covq_{ij} \partial_{x_i} \partial_{x_j} f(x)
+        + \sum_i \meanq_i \partial_{x_i} f(x)
     \end{align}
@@
     \end{align}
+    We will also denote the adjoint of $\DG$ by
+    $$
+    \DG^* f(x)
+        =
+        \sum_{ij} \covq_{ij} \partial_{x_i} \partial_{x_j} f(x)
+        + \sum_i \partial_{x_i} (f(x) \meanq_i) .
+    $$
 \end{definition}
@@
         r\left(x, \smooth{r} \varphi(t,x) \right)
-        \mathcal{B} \left[
+        \DG^* \left[
             \varphi(t, \cdot)
@@
 \begin{align} \label{eqn:pde}
-    \dot \varphi = r \DG\left( \gamma \varphi \right) + \varphi F ,
+    \dot \varphi = r \DG^* \left( \gamma \varphi \right) + \varphi F ,
 \end{align}
@@
 (i.e., through a smoothed version of $\varphi$).
+To see why it is $\DG^*$ and not $\DG$ that appears in this equation,
+consider the case where dispersal has a mean drift to the right,
+so that the drift term in $\DG$ is $d/dx$.
+Then, the population density at a location with positive slope
+will tend to \emph{decrease}, i.e., proportional to $-d/dx$,
+because the density at a location is determined by the offspring that disperse \emph{to}
+that location, not away from it.
+Furthermore, if dispersal tends to move offspring away from a region
+(i.e., if divergence $\grad \cdot \meanq > 0$)
+this will tend to decrease the local density.
 
@@
 Happily, we are interested in the case when $\eta$ has a density,
-say $\eta_t(dx) = \varphi(x) dx$,
+say $\eta_t(dx) = \varphi_t(x) dx$,
 so interpreting these rates is not too difficult.
@@
 \frac{
-    \varphi(x) \gamma(x, \eta_t) r(y, \eta_t)
+    \gamma(x, \eta_t) r(y, \eta_t) \varphi_t(x) 
 }{
-    \varphi(y)
+    \varphi_t(y)
 } \widetilde q_\theta(y, dx) .
@@
 recall that as $\theta \to \infty$,
-$$
+\begin{align*}
     \theta \int (f(x) - f(y)) \widetilde q_\theta(y, dx)
-    \to
+    &\to
     - \sum_i \meanq_i \partial_{x_i} f(y)
-    + \sum_{ij} \covq_{ij} \partial_{x_i x_j} f(y) ,
-$$
-which is just $\DG$ but with the first derivative terms multiplied by -1.
-\comment{The $\widetilde \DG$ and $\covq \grad$ notation here is terrible; suggestions?}
+    + \sum_{ij} \covq_{ij} \partial_{x_i x_j} f(y) \\
+    = \DD - \meanq \cdot \grad f ,
+\end{align*}
+where $\DD = \sum_{ij} \covq_{ij} \partial_{ij}$.
+(Note that this differs from $\DG^*$ if $\meanq$ can vary across space.)
 Consequently,
@@
     \theta \int (f(x) - f(y)) g(x) \widetilde q_\theta(y, dx) \\
+    &\qquad =
+    \theta \int \left\{
+        (f(x) g(x) - f(y) g(y)) - f(y) (g(x) - g(y))
+    \right\} \widetilde q_\theta(y, dx) \\
     &\qquad \to
-    - g(y) \sum_i \meanq_i \partial_{x_i} f(y)
-    + g(y) \sum_{ij} \covq_{ij} \partial_{x_i x_j} f(y)
-    + \sum_{ij} \partial_{x_i} g(y) \covq_{ij} \partial_{x_j} f(y)  \\
+        \DD(fg)(x) - f(x) \DD g(x) - \meanq \cdot \left( \grad(fg)(x) - f(x) \grad g(x) \right) \\
     &\qquad =
-    g(y) \widetilde \DG f(y)
-    + (\covq \grad g) \cdot \grad f ,
+        g(x) \DD f(x) + 2 (\covq \grad g(x)) \cdot \grad f(x) - g(x) \meanq \cdot \grad f(x) .
 \end{align*}
-if we define $\widetilde \DG$ to be the same as $\DG$ but with $-\meanq$ substituted for $\meanq$,
-and $(\covq \grad g(y))_i = \sum_j \covq_{ij} \partial_{x_j} g(y)$.
 Applying this to~\eqref{eqn:lineage_generator_Edt} with $g = \varphi_{T-s} \gamma$,
 this suggests that the generator of the limiting process is
-\begin{align*}
+\begin{align} \label{eqn:heuristic_lineage_generator}
     \Lgen_s f
@@
     \left\{
-        \varphi_{T-s} \gamma \widetilde \DG f
-        + \left(\covq \grad (\varphi_{T-s} \gamma) \right) \cdot \grad f 
+        \varphi_{T-s} \gamma (\DD f - \meanq \cdot \grad f)
+        + 2 \left(\covq \grad (\varphi_{T-s} \gamma) \right) \cdot \grad f 
     \right\} \\
@@
     \left\{
-        \widetilde \DG f
-        + \left(\covq \grad \log(\varphi_{T-s} \gamma) \right) \cdot \grad f 
+        \DD f - \meanq \cdot \grad f
+        + 2 \left(\covq \grad \log(\varphi_{T-s} \gamma) \right) \cdot \grad f 
     \right\} .
-\end{align*}
+\end{align}
 In other words, the lineage moves at speed equal to the local production of successful offspring,
@@
 but with a drift in the direction of the gradient of the logarithm
-of the production of juveniles, $\grad \log(\phi_{T-s} \gamma)$
+of the production of juveniles, $2 \grad \log(\phi_{T-s} \gamma)$
 (modified by the covariance of dispersal).
@@
     &=
-    X_a(\tau_a+s-) + \kappa y \mathbbm{1}_{U_{aj}(\tau_{aj}) < \lambda} .
+    X_a(\tau_a+s-) + \kappa y \ind_{U_{aj}(\tau_{aj}) < \lambda} .
 \end{align}
@@
     \kappa y
-    \mathbbm{1}_{
+    \ind_{
         U_{(a)_{\zeta(s)}}(s) + \ell( X_{(a)_{\zeta(s)}}(s-), y, \eta(s-), v) < \lambda
@@
 \subsection{Limiting processes for lines of descent}
+\label{sec:limiting_lines_of_descent}
 
@@
 Since the mean measure of the $v$ coordinate is Lebesgue,
-$\theta/\lambda \to \delta$,
+$\theta/\lambda \to \alpha$,
 and $q(x, dy) \to \delta_x(dy)$,
@@
 $$
-\delta \gamma(X_a(t), \eta) r(X_a(t), \eta) 
+\alpha \gamma(X_a(t), \eta) r(X_a(t), \eta) 
 $$
@@
 so that
-\begin{align*}
+\begin{align}
 \DG(rg)(x) - g(x) \DG(r)(x)
-    &=
+    &= \nonumber
     r(x) \sum_i \meanq_i \partial_i g(x)
@@
     + r(x) \sum_{ij} \covq_{ij} \partial_{ij} g(x) \\
-    &=
+    &= \label{eqn:limiting_generator}
     r(x) \left\{
@@
     \right\} .
-\end{align*}
+\end{align}
 
@@
     \bigg(
-        \delta \gamma(X_a(s),\eta(s))
+        \alpha \gamma(X_a(s),\eta(s))
         r(x,\eta(s)) U_a(s)^2
@@
     U_{aj}(t) = U_a(t)
-    + \frac{v}{ 2 \delta \gamma(X_a(t), \eta(t)) r(X_a(t), \eta(t)) } .
+    + \frac{v}{ 2 \alpha \gamma(X_a(t), \eta(t)) r(X_a(t), \eta(t)) } .
 $$
@@
 X_{\tau}(\tau+t)=&X_{\tau}(t)\\
-&+\int_{(0,t]\times[0,\infty]\times[0,1]\times\{0,1\}}\mathbbm{1}_{U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))}<\lambda\}}\kappa    H(X_{\tau}(\tau+s-), \eta(\tau+s),\omega) \\
+&+\int_{(0,t]\times[0,\infty]\times[0,1]\times\{0,1\}}\ind_{U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))}<\lambda\}}\kappa    H(X_{\tau}(\tau+s-), \eta(\tau+s),\omega) \\
 &\qquad \times \xi_{\tau}(ds,dv,dw,d\kappa).
@@
 \begin{equation}\label{eq: Individual Evolution Recursion Terms}
-\zeta^{0}_{\tau}(B)=\sum_{k=1}^{m}\delta_{(s_k,v_k,w_k,(1-\kappa_k))}, ~~~ V_{\tau}(t)=\sum_{k=1}^{m}v_k\mathbbm{1}_{[0, \tau_k]}  (t)  
+\zeta^{0}_{\tau}(B)=\sum_{k=1}^{m}\delta_{(s_k,v_k,w_k,(1-\kappa_k))}, ~~~ V_{\tau}(t)=\sum_{k=1}^{m}v_k\ind_{[0, \tau_k]}  (t)  
 \end{equation}
@@
 \begin{equation}\label{eq: integrand in spatial tracing}
-\zeta_{\tau}(B)=\zeta_{\tau}^{0}(B)+\sum_{k=0}^{m}\int \mathbbm{1}_{B}(\tau_k+s,v,w,\kappa)\mathbbm{1}_{\{\tau_k+s<\tau_{k+1}\}}\xi_{\tau_k}(ds,dv,dw,d\kappa)    
+\zeta_{\tau}(B)=\zeta_{\tau}^{0}(B)+\sum_{k=0}^{m}\int \ind_{B}(\tau_k+s,v,w,\kappa)\ind_{\{\tau_k+s<\tau_{k+1}\}}\xi_{\tau_k}(ds,dv,dw,d\kappa)    
 \end{equation}
@@
 &+\int_{0}^{t}\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(s-), \eta(s-))U^2_{\tau}(s)-b_{\theta}(X_{\tau}(s),\eta(s))U_{\tau}(s))ds,\\  
-X_{\tau}(t)=&X_{\tau}(0)+\int_{(0,t]\times[0,\infty]\times[0,1]\times\{0,1\}}\mathbbm{1}_{U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))}<\lambda\}}\\
+X_{\tau}(t)=&X_{\tau}(0)+\int_{(0,t]\times[0,\infty]\times[0,1]\times\{0,1\}}\ind_{U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))}<\lambda\}}\\
 &\qquad \times \kappa   H(X_{\tau}(s-), \eta(s-),\omega)\zeta_{\tau}(ds,dv,dw,d\kappa)
@@
 since $\int g(y, u_1) q(x, dy) \to g(x, u_1)$
-and $\theta/\lambda \to \delta$,
+and $\theta/\lambda \to \alpha$,
 it converges to
 \begin{align*}
-    2 \delta
+    2 \alpha
     \gamma(x, \eta)
@@
 \end{align*}
-This corresponds to births at higher levels at rate $2 \delta \gamma r$.
+This corresponds to births at higher levels at rate $2 \alpha \gamma r$.
 
@@
 \end{align*}
-The first part only uses the fact that $\theta/\lambda \to \delta$,
+The first part only uses the fact that $\theta/\lambda \to \alpha$,
 while as noted in \eqref{eqn:b_limit}, $b$ converges to $\gamma \DG r + F$,
@@
     \left(
-    \delta
+    \alpha
         \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
@@
     =
-    \delta
+    \alpha
         \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
@@
 In this section we prove Theorem~\ref{thm:lineages}.
-The argument follows directly from the discussion in Section \ref{sec:lines_of_descent}
+The argument follows directly from the discussion in Section \ref{sec:limiting_lines_of_descent}
 (and so maybe actually that content should be down here).
@@
 \begin{proof}[of Theorem~\ref{thm:lineages}]
+
+Here
+\comment{(and in the statement of the theorem)}
+we take the high-density, deterministic limit
+(so, $\theta, N \to \infty$ and $\theta/N \to 0$)
+and so suppose that the limiting process has density $\varphi_t(x)$
+at location $x$ and time $t$.
+Let $Y$ denote the spatial motion followed by a single line of descent.
+Above equation~\eqref{eqn:limiting_generator},
+we showed that $Y$ is a diffusion with generator at time $s$
+$$
+    \mathcal{L}^Y_s g(x) = \gamma ( \DG(rg)(x) - g \DG r(x) ) .
+$$
+The diffusion is time-inhomogeneous if the density is not constant with time
+(since recall that the coefficients $\gamma$ and $r$ depend on the density).
+Formally, the intensity of levels at $y$ at time $t$
+that are descended from individuals that were at $x$ at time $s$
+(with $s < t$) is
+\begin{equation} \label{eqn:formal_intensity}
+    \varphi_s(x) \IE_{s,x} \left[
+        \exp\left(
+            \int_s^t (F + \gamma \DG r)(Y_u) du
+        \right)
+        \ind_{Y_t = y}
+    \right]
+    dy ,
+\end{equation}
+where the subscript $s, x$ in the expectation indicates that $Y_s = x$.
+To see why this should be true, 
+suppose that an ancestor has level $v$. Conditional on its 
+spatial motion $\{Y_u\}_{s\leq u\leq t}$, its level at time $t$ will
+be $v \exp(-\int_s^t(F+\gamma\Delta r)(Y_u)du)$. This will be less than a given level 
+$\lambda$ if $v < \lambda \exp(\int_s^t(F+\gamma\Delta r)(Y_u)du)$. 
+The intensity of levels at $y$ that are descended from individuals at
+$x$ can therefore be obtained as the limit as $\lambda\to\infty$ of 
+$1/\lambda$ times the number of levels at $x$ at time zero with
+$u<\lambda \exp(\int_s^t(F+\gamma\Delta r)(Y_u)du)$ and for which
+the corresponding individual is at $y$ at time $t$, which is 
+precisely the quantity in~\eqref{eqn:formal_intensity}.
+
+By our construction in Section~\ref{sec:limiting_lines_of_descent},
+when we integrate~\eqref{eqn:formal_intensity}
+with respect to $x$ we recover $\varphi_t(y)dy$. 
+Consider an individual sampled at location $y$ at time $t$,
+and write $p(t,s,y,x)$ for the probability density
+that their ancestor at time $s$ was at $x$.
+As a consequence of~\eqref{eqn:formal_intensity},
+still formally,
+\begin{equation}
+\label{eqn:ptsyx}
+    p(t,s,y,x)
+    =
+    \frac{\varphi_s(x)}{\varphi_t(y)}
+    \IE_{s,x}\left[
+        \exp\left( \int_s^t (F + \gamma\DG r)(Y_u) du \right)
+        \ind_{Y_t=y}
+    \right]
+\qquad \text{ for } s < t.
+\end{equation}
+
+To make~(\ref{eqn:ptsyx}) meaningful, we multiply by suitable test functions
+$f$ and $g$ and integrate.
+\begin{align*}
+&\int \int f(y) \varphi_t(y) p(t,s,y,x) g(x) dy dx \\
+&\qquad =
+\int g(x) \varphi_s(x)
+\IE_{x,s}\left[
+    \exp\left(
+        \int_s^t(F+\gamma\DG r)(Y_u)du
+    \right)f(Y_t)
+\right] dx .
+\end{align*}
+
+Writing $\hat{T}_{t,s}$ for the time-inhomogeneous semigroup
+corresponding to the motion of ancestral lineages backwards in time
+\comment{(Use notation for the motion of a lineage introduced above.)}
+(that is, $\hat{T}_{t,s} f(y) = \int p(t,s,x,y) f(x) dy$),
+we can write this as 
+$$
+    \int f(y)\varphi_t(y)\hat{T}_{t,s}g(y)dy
+    =
+    \int g(x) \varphi_s(x)
+        \IE_{s,x} \left[
+            \exp\left(
+                \int_s^t(F+\gamma\DG r)(Y_u)du
+            \right)f(Y_t)
+        \right]dx.
+$$
+Differentiating with respect to $t$ at $t=s$, and writing 
+$\hat{\mathcal L}_s$ for the generator of $\hat{T}_{t,s}$ at time $s$, we find
+\begin{align*}
+&
+    \int f(y) \left\{
+        \varphi_s(y) \widehat{\mathcal L}_s g(y)
+        + \left(
+            r(y) \DG^*(\gamma \varphi_s)(y) + \varphi_s(y) F(y)
+        \right) g(y)
+    \right\} dy \\
+&\qquad =
+    \int g(x) \varphi_s(x) \left(
+        {\mathcal L}^Y_s f(x) + (F(x)+\gamma(x) \DG r(x)) f(x)
+    \right) dx \\
+&\qquad =
+    \int f(x) \left(
+        ({\mathcal L}^Y_s)^* (\varphi_s g)(x) + (F(x) + \gamma(x) \DG r(x)) \varphi_s(x) g(x)
+    \right) dx ,
+\end{align*}
+where $({\mathcal L}^Y_s)^*$ is the adjoint of ${\mathcal L}^Y_s$
+and we have used that $\varphi_s$ solves $\dot \varphi = r \DG^*(\gamma \varphi) + F \varphi$.
+Since $f$ was arbitrary,
+\begin{eqnarray*}
+\hat{\mathcal L}_s g
+    &=&
+    \frac{1}{\varphi_s} \left[
+        ({\mathcal L}^Y_s)^* (\varphi_s g)
+        + \gamma \varphi_s g \DG(r)
+        - r g \DG^*(\gamma \varphi_s)
+    \right] .
+\end{eqnarray*}
+(Note that the $\phi_s F g$ terms have cancelled.)
+After liberal use of the product rule, we'll be able to simplify this last expression.
+To prepare for this, first define
+$$
+    \DD f(x) = \sum_{ij} \covq_{ij} \partial_{ij} f(x),
+$$
+and note that $\DD$ satisfies the following identity:
+\begin{align}
+    \DD(fg)
+    &=
+    f \DD g
+    + 2 (\covq \grad f) \cdot \grad g
+    + g \DD f .
+\end{align}
+
+\comment{Note here we are allowing $\meanq$ to vary with space!}
+
+Now consider the adjoint of $\mathcal{L}^Y_s$.
+Recall that $\DG g = \DD g + \meanq \cdot \grad g$
+and $\DG^* f = \DD f - \grad \cdot (f \meanq)$,
+so
+\begin{align*}
+    ({\mathcal L}^Y_s)^* f
+    &=
+    r \DG^* (\gamma f) - \gamma f \DG r \\
+    &=
+    r \DD(\gamma f) - r \grad \cdot (\gamma f \meanq)
+    - \gamma f \DG r .
+\end{align*}
+We can now expand the expression for $\hat{\mathcal L}_s$ to get
+\begin{eqnarray*}
+\hat{\mathcal L}_s g
+    &=&
+    \frac{1}{\varphi_s} \left[
+        r \DD(\gamma \varphi_s g) - r \grad \cdot (\gamma \varphi_s g \meanq)
+        - \gamma \varphi_s g \DG(r)
+        + \gamma \varphi_s g \DG(r)
+        - r g \DG^*(\gamma \varphi_s)
+    \right] \\
+    &=&
+    \frac{r}{\varphi_s} \left[
+        \DD(\gamma \varphi_s g) - \grad \cdot (\gamma \varphi_s g \meanq)
+        - g \DD(\gamma \varphi_s) + g \grad \cdot (\gamma \varphi_s \meanq)
+    \right] \\
+    &=&
+    \frac{r}{\varphi_s} \left[
+        \gamma \varphi_s \DD g
+        + 2 (\covq \grad (\gamma \varphi_s)) \cdot \grad g
+        - \gamma \varphi_s \meanq \cdot \grad g
+    \right] \\
+    &=&
+    r \gamma \left[
+        \DD g
+        + 2 (\covq \grad \log(\gamma \varphi_s)) \cdot \grad g
+        - \meanq \cdot \grad g
+    \right] ,
+\end{eqnarray*}
+in agreement with \eqref{eqn:heuristic_lineage_generator}.
+
+\end{proof}
+
+\begin{proof}[of Corollary~\ref{cor:wavefront}
     \comment{
-        This is actually copied over the proof of Corollary~\ref{cor:wavefront};
-        TODO is to generalize it to time-varying density.
+        TODO make non-redundant with proof of Theorem \ref{thm:lineages.}.
     }
@@
 \end{proof}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
       0 & \text{if } \sum_{(x,u) \in \nu, u < \lambda} \delta_x \neq \Xi\\
-       \prod_{(u_i,x_i) \in \nu} \frac{1}{\lambda} \mathbbm{1}_{[0,\lambda]}du_i & \text{if } \sum_{(x,u) \in \nu, u < \lambda} \delta_x = \Xi,\\
+       \prod_{(u_i,x_i) \in \nu} \frac{1}{\lambda} \ind_{[0,\lambda]}du_i & \text{if } \sum_{(x,u) \in \nu, u < \lambda} \delta_x = \Xi,\\
     \end{cases} $\\

### 2022-04-25 forwards-and-backwards.tex
theorem rewrite

@@
         =
-        \sum_{ij} \covq_{ij} \partial_{x_i} \partial_{x_j} f(x)
-        + \sum_i \partial_{x_i} (f(x) \meanq_i) .
+        \sum_{ij} \partial_{x_i} \partial_{x_j} (\covq_{ij} f(x))
+        - \sum_i \partial_{x_i} (f(x) \meanq_i) .
     $$
@@
 \comment{
-    \textbf{Note:} the previous write-up motivated things only in the time-stationary case
-    (so, a stationary traveling wave, possibly with wave speed zero;
-    see the corollary below).
-    It'd be very nice to give this more general result,
-    but the proof has to be checked to make sure it still applies,
-    and the notation is time-inhomogeneous and so more annoying
+    TODO: make notation agree with that in the proof.
 }
@@
 
-\comment{
-    Allowing a more general dispersal mechanism won't just entail replacing $\Delta$ with $\DG$,
-    it will also change at least one of the $\grad$s to something else (I think).
-}
-
 \begin{theorem} \label{thm:lineages}
+    In the context of Definition~\ref{def:lineage_generator},
+    \begin{align}
+        \label{eqn:lineage_generator}
+        \Lgen_s f
+        &=
+        \frac{r}{\varphi_s}
+        \left[
+            \DG^*(\gamma \varphi_s f) 
+            - f \DG^* (\gamma \varphi_s)
+        \right] \\
+        &= \label{eqn:lineage_generator2}
+        r\gamma
+        \left[
+            \sum_{ij} \covq_{ij} \partial_{ij} f
+            + 2 \sum_j \left(
+               \sum_i \partial_i (C_{ij} \log(\gamma \varphi_s))
+            \right) \partial_j f
+            - \sum_j \meanq_j \partial_j f
+        \right] .
+    \end{align}
+\end{theorem}
+
+To make the generator readable, we've written it in concise notation,
+omitting the dependencies on location and population density,
+which itself changes with time.
+When interpreting this,
+remember that everything depends on location and density at that location and time --
+for instance, ``$r$'' is actually $r(x, \varphi(T-s, x))$.
+
+\begin{corollary} \label{cor:lineages_simple}
     In the context of Definition~\ref{def:lineage_generator},
@@
     \begin{equation}
-        \label{eqn:lineage_generator}
         \Lgen_s f
@@
             \left(
-                2 \grad \log(\gamma \varphi)
+                2 \grad \log(\gamma \varphi_s)
                 - \meanq
@@
     ($\varphi \gamma \exp(-\meanq \cdot x / 2 \sigma^2)$).
-\end{theorem}
-
-To make the generator readable, we've written it in concise notation,
-omitting the dependencies on location and population density,
-which itself changes with time.
-When interpreting this,
-remember that everything depends on location and density at that location and time --
-for instance, ``$r$'' is actually $r(x, \varphi(T-s, x))$.
+\end{corollary}
 
@@
 (Note that the $\phi_s F g$ terms have cancelled.)
-After liberal use of the product rule, we'll be able to simplify this last expression.
-To prepare for this, first define
-$$
-    \DD f(x) = \sum_{ij} \covq_{ij} \partial_{ij} f(x),
-$$
-and note that $\DD$ satisfies the following identity:
-\begin{align}
-    \DD(fg)
-    &=
-    f \DD g
-    + 2 (\covq \grad f) \cdot \grad g
-    + g \DD f .
-\end{align}
-
-\comment{Note here we are allowing $\meanq$ to vary with space!}
-
-Now consider the adjoint of $\mathcal{L}^Y_s$.
-Recall that $\DG g = \DD g + \meanq \cdot \grad g$
-and $\DG^* f = \DD f - \grad \cdot (f \meanq)$,
-so
+Since the adjoint of ${\mathcal L}^Y_s$ is
 \begin{align*}
@@
     &=
-    r \DG^* (\gamma f) - \gamma f \DG r \\
-    &=
-    r \DD(\gamma f) - r \grad \cdot (\gamma f \meanq)
-    - \gamma f \DG r .
+    r \DG^* (\gamma f) - \gamma f \DG r ,
 \end{align*}
-We can now expand the expression for $\hat{\mathcal L}_s$ to get
+we can rewrite the generator of a lineage as 
 \begin{eqnarray*}
@@
     &=&
-    \frac{1}{\varphi_s} \left[
-        r \DD(\gamma \varphi_s g) - r \grad \cdot (\gamma \varphi_s g \meanq)
-        - \gamma \varphi_s g \DG(r)
-        + \gamma \varphi_s g \DG(r)
-        - r g \DG^*(\gamma \varphi_s)
-    \right] \\
+    \frac{r}{\varphi_s} \left[
+        \DG^* (\gamma \varphi_s g)
+        - g \DG^*(\gamma \varphi_s)
+    \right] .
+\end{eqnarray*}
+This is equation \eqref{eqn:lineage_generator}.
+
+To simplify to equation \eqref{eqn:lineage_generator2},
+this, first define
+$
+    \DD f(x) = \sum_{ij} \covq_{ij} \partial_{ij} f(x),
+$
+% and note that $\DD$ satisfies the following identity:
+% \begin{align}
+%     \DD(fg)
+%     &=
+%     f \DD g
+%     + 2 (\covq \grad f) \cdot \grad g
+%     + g \DD f .
+% \end{align}
+and so the adjoint of $\DD$ is
+$$
+    \DD^* f(x)
+    =
+    \sum_{ij} \partial_{ij} (\covq_{ij} f(x)) .
+$$
+Note that $\DD^*$ satisfies the following identity:
+\begin{align}
+    \DD^*(fg)
+    &=
+    \sum_{ij} \left\{
+        g \partial_{ij} (\covq_{ij} f)
+        + 2 \partial_{i} (\covq_{ij} f) \partial_j(g)
+        + \covq_{ij} f \partial_{ij} g
+    \right\} \\
+    &=
+    g \DD^* f
+    + 2 \mathcal{H} f \cdot \grad g
+    + f \DD g ,
+\end{align}
+where $(\mathcal{H} f)_j = \sum_i \partial_i (C_{ij} f)$.
+    \comment{(Need better notation for that.)}
+So, with $f = \gamma \varphi_s$,
+\begin{eqnarray*}
+\hat{\mathcal L}_s g
     &=&
     \frac{r}{\varphi_s} \left[
-        \DD(\gamma \varphi_s g) - \grad \cdot (\gamma \varphi_s g \meanq)
-        - g \DD(\gamma \varphi_s) + g \grad \cdot (\gamma \varphi_s \meanq)
+        \DD^*(\gamma \varphi_s g) - \grad \cdot (\gamma \varphi_s g \meanq)
+        - g \DD^*(\gamma \varphi_s) + g \grad \cdot (\gamma \varphi_s \meanq)
     \right] \\
@@
         \gamma \varphi_s \DD g
-        + 2 (\covq \grad (\gamma \varphi_s)) \cdot \grad g
+        + 2 \mathcal{H} (\gamma \varphi_s) \cdot \grad g
         - \gamma \varphi_s \meanq \cdot \grad g
@@
         \DD g
-        + 2 (\covq \grad \log(\gamma \varphi_s)) \cdot \grad g
+        + 2 (\mathcal{H} \log(\gamma \varphi_s)) \cdot \grad g
         - \meanq \cdot \grad g
@@
 in agreement with \eqref{eqn:heuristic_lineage_generator}.
+
+\end{proof}
+
+\begin{proof}[of Corollary \ref{cor:lineages_simple}]
+
+In this section, we need only make
+simplify equation \eqref{eqn:lineage_generator}
+in the case where $\covq = \sigma^2 I$.
+
+    \comment{TODO}
 

### 2022-04-25 forwards-and-backwards.tex
fixups

@@
             \sum_{ij} \covq_{ij} \partial_{ij} f
-            + 2 \sum_j \left(
-               \sum_i \partial_i (C_{ij} \log(\gamma \varphi_s))
-            \right) \partial_j f
-            - \sum_j \meanq_j \partial_j f
-        \right] .
+            + 2 \sum_j \vec{m}_j \partial_j f
+        \right] ,
     \end{align}
+    where $\vec{m}$ is the vector
+    $$
+    \vec{m}_j
+    =
+    2 \sum_i C_{ij} \partial_i \log(\gamma \varphi_s)
+    + 2 \sum_i \partial_i C_{ij}
+    - \meanq_j .
+    $$
 \end{theorem}
@@
 Note that $\DD^*$ satisfies the following identity:
-\begin{align}
+\begin{align*}
     \DD^*(fg)
@@
     &=
+    \sum_{ij} \left\{
+        g \partial_{ij} (\covq_{ij} f)
+        + 2 f \partial_{i} (\covq_{ij}) \partial_j(g)
+        + 2 \covq_{ij} \partial_{i} (f) \partial_j(g)
+        + \covq_{ij} f \partial_{ij} g
+    \right\} \\
+    &=
     g \DD^* f
-    + 2 \mathcal{H} f \cdot \grad g
+    + 2 f \vec{c} \cdot \grad g
+    + 2 (C \grad f) \cdot \grad g
     + f \DD g ,
-\end{align}
-where $(\mathcal{H} f)_j = \sum_i \partial_i (C_{ij} f)$.
-    \comment{(Need better notation for that.)}
+\end{align*}
+where $\vec{c}_j = \sum_i \partial_j C_{ij}$.
 So, with $f = \gamma \varphi_s$,
@@
         \gamma \varphi_s \DD g
-        + 2 \mathcal{H} (\gamma \varphi_s) \cdot \grad g
+        + 2 \gamma \varphi_s \vec{c} \cdot \grad g
+        + 2 (C \grad (\gamma \varphi_s)) \cdot \grad g
         - \gamma \varphi_s \meanq \cdot \grad g
@@
         \DD g
-        + 2 (\mathcal{H} \log(\gamma \varphi_s)) \cdot \grad g
+        + 2 \vec{c} \cdot \grad g
+        + 2 (C \grad \log(\gamma \varphi_s)) \cdot \grad g
         - \meanq \cdot \grad g
@@
 \end{eqnarray*}
-in agreement with \eqref{eqn:heuristic_lineage_generator}.
+which is equation \eqref{eqn:lineage_generator}.
 
@@
 
-In this section, we need only make
+In this section, we need only
 simplify equation \eqref{eqn:lineage_generator}
@@
     \comment{
-        TODO make non-redundant with proof of Theorem \ref{thm:lineages.}.
+        TODO make non-redundant with proof of Theorem \ref{thm:lineages}.
     }

### 2022-04-25 forwards-and-backwards.tex
tweaks

@@
 
-\comment{This corollary was the previous theorem in the previous draft.
-    Besides this proposed set-up, we have the additional options of
-    (a) renaming the corollary a theorem and only proving it,
-    or (b) presenting only the corollary here (as a theorem)
-    and presenting the more general theorem later on.
-}
-
 \begin{corollary} \label{cor:wavefront}
-    In addition to the assumptions of Theorem~\ref{thm:lineages},
+    In addition to the assumptions of Corollary~\ref{cor:lineages_simple},
     suppose that the population process is described by a traveling wave with speed $\wavespeed$,
@@
 In this section we prove Theorem~\ref{thm:lineages}.
-The argument follows directly from the discussion in Section \ref{sec:limiting_lines_of_descent}
-(and so maybe actually that content should be down here).
+The argument follows directly from the discussion in Section \ref{sec:limiting_lines_of_descent}.
 
 \begin{proof}[of Theorem~\ref{thm:lineages}]
+
+\comment{(TODO: Use notation for the motion of a lineage introduced in statement of theorem.)}
 
@@
 corresponding to the motion of ancestral lineages backwards in time
-\comment{(Use notation for the motion of a lineage introduced above.)}
 (that is, $\hat{T}_{t,s} f(y) = \int p(t,s,x,y) f(x) dy$),
@@
 Differentiating with respect to $t$ at $t=s$, and writing 
-$\hat{\mathcal L}_s$ for the generator of $\hat{T}_{t,s}$ at time $s$, we find
+$\Lgen_s$ for the generator of $\hat{T}_{t,s}$ at time $s$, we find
 \begin{align*}
@@
     \int f(y) \left\{
-        \varphi_s(y) \widehat{\mathcal L}_s g(y)
+        \varphi_s(y) \Lgen_s g(y)
         + \left(
@@
 \begin{eqnarray*}
-\hat{\mathcal L}_s g
+\Lgen_s g
     &=&
@@
     \DD^*(fg)
-    &=
-    \sum_{ij} \left\{
-        g \partial_{ij} (\covq_{ij} f)
-        + 2 \partial_{i} (\covq_{ij} f) \partial_j(g)
-        + \covq_{ij} f \partial_{ij} g
-    \right\} \\
+%     &=
+%     \sum_{ij} \left\{
+%         g \partial_{ij} (\covq_{ij} f)
+%         + 2 \partial_{i} (\covq_{ij} f) \partial_j(g)
+%         + \covq_{ij} f \partial_{ij} g
+%     \right\} \\
     &=

### 2022-04-26 forwards-and-backwards.tex
notes after meeting

@@
 \newcommand{\labelspace}{\mathcal{I}} % space of labels
+\newcommand{\concat}{\oplus}   % concatenation of labels
 
@@
 
+\comment{TODO: insert remark about writing $\gamma(x, \smooth{\gamma}\eta(x)) = \gamma(x, \eta)$.}
+
 We will now define $(\eta^{\theta}(t))_{t \geq 0}$
@@
         =
-        \DG \left( \gamma(\cdot, u(t, \cdot) u(t, \cdot)  \right)(x)
+        \DG^* \left( \gamma(\cdot, u(t, \cdot) u(t, \cdot)  \right)(x)
         + F(x, u(t, x)) u(t, x) .
@@
 
+\comment{Make forwards-backwards time notation reasonable in this.}
+
+\comment{Perhaps write generator as depending on $\phi$ rather than $s$?
+    Then we can say that the generator is $\Lgen_{\varphi(T-s)}$.}
+
 \begin{theorem} \label{thm:lineages}
@@
         &=
-        \frac{r}{\varphi_s}
+        \frac{r}{\varphi_{T-s}}
         \left[
-            \DG^*(\gamma \varphi_s f) 
-            - f \DG^* (\gamma \varphi_s)
+            \DG^*(\gamma \varphi_{T-s} f) 
+            - f \DG^* (\gamma \varphi_{T-s})
         \right] \\
@@
             \sum_{ij} \covq_{ij} \partial_{ij} f
-            + 2 \sum_j \vec{m}_j \partial_j f
+            + \sum_j \vec{m}(s)_j \partial_j f
         \right] ,
@@
     $$
-    \vec{m}_j
+    \vec{m}(s)_j
     =
-    2 \sum_i C_{ij} \partial_i \log(\gamma \varphi_s)
+    2 \sum_i C_{ij} \partial_i \log(\gamma \varphi_{T-s})
     + 2 \sum_i \partial_i C_{ij}
@@
 $$
+Happily, we are interested in the case when $\eta$ has a density,
+say $\eta_t(dx) = \varphi_t(x) dx$,
+so interpreting these rates is not too difficult.
 This implies that the probability a randomly chosen individual near $y$
@@
 \frac{
-    \gamma(x, \eta_t) q_\theta(x, dy) r(y, \eta_t) \eta_t(dx)
+    \gamma(x, \eta_t) q_\theta(x, dy) r(y, \eta_t) \varphi_t(x)
 }{
-    \eta_t(dy)
-} dt .
+    \varphi_t(y)
+} \frac{ q_\theta(x, dy) }{ dy } dx dt .
 \end{equation}
@@
 we might then proceed by defining a continuous-time jump process
-whose transition rates are given by \eqref{eqn:informal_rates} given $(\eta_t)_{t=0}^T$.
-Happily, we are interested in the case when $\eta$ has a density,
-say $\eta_t(dx) = \varphi_t(x) dx$,
-so interpreting these rates is not too difficult.
-Now recall that $q_\theta(x, dy)$ is a Gaussian kernel
-with mean $x + \meanq/\theta$ and covariance $\covq/\theta$.
-Write $\widetilde q_\theta(y, dx)$ for the ``reverse-time'' distribution,
-i.e., Gaussian with mean $x - \meanq/\theta$ and the same covariance.
-Then, rearranging infinitesimals,
-\eqref{eqn:informal_rates} implies a rate of
-\begin{equation} \label{eqn:informal_rates2}
-\frac{
-    \gamma(x, \eta_t) r(y, \eta_t) \varphi_t(x) 
-}{
-    \varphi_t(y)
-} \widetilde q_\theta(y, dx) .
-\end{equation}
+whose transition rates are given by \eqref{eqn:informal_rates} given $(\varphi_t)_{t=0}^T$.
 Let $(L^\theta_s)_{s=0}^T$ be the location of a lineage that moves according to
-jump rates~\eqref{eqn:informal_rates2},
+jump rates~\eqref{eqn:informal_rates},
 back through time (i.e., with the substitution that $s = T-t$).
-Then
+Then, writing $q_\theta(x, y)$ for the density of $q_\theta$,
 \begin{align} \label{eqn:lineage_generator_Edt}
     \begin{split}
-    &\IE[f(L^\theta_{s+ds}) \;|\; L_s = y] - f(y)
+    &\IE[f(L^\theta_{s+ds}) - f(y) \;|\; L_s = y]
     \\&\qquad 
@@
     }
-    \widetilde q_\theta(y, dx) .
+    q_\theta(x, y) dx .
     \end{split}
 \end{align}
+\comment{I'm not sure if at this point in the paper we want to either
+(a) write out the next statement; (b) restrict to the $\DG = \Delta$ case,
+or (c) leave it as is (as an exercise for the reader, I guess?}
 Referring back to Definition~\ref{def:dispersal_generator},
-recall that as $\theta \to \infty$,
+it is not too hard to show that as $\theta \to \infty$,
 \begin{align*}
-    \theta \int (f(x) - f(y)) \widetilde q_\theta(y, dx)
+    \theta \int (f(x) - f(y)) q_\theta(x, y) dx
     &\to
-    - \sum_i \meanq_i \partial_{x_i} f(y)
-    + \sum_{ij} \covq_{ij} \partial_{x_i x_j} f(y) \\
-    = \DD - \meanq \cdot \grad f ,
+    \DG^* f(x)  - f(x) \DG^* 1 .
 \end{align*}
-where $\DD = \sum_{ij} \covq_{ij} \partial_{ij}$.
-(Note that this differs from $\DG^*$ if $\meanq$ can vary across space.)
 Consequently,
@@
     &
-    \theta \int (f(x) - f(y)) g(x) \widetilde q_\theta(y, dx) \\
+    \theta \int (f(x) - f(y)) g(x) q_\theta(x, y) dx \\
     &\qquad =
@@
         (f(x) g(x) - f(y) g(y)) - f(y) (g(x) - g(y))
-    \right\} \widetilde q_\theta(y, dx) \\
+    \right\} q_\theta(x, y) dx \\
     &\qquad \to
-        \DD(fg)(x) - f(x) \DD g(x) - \meanq \cdot \left( \grad(fg)(x) - f(x) \grad g(x) \right) \\
-    &\qquad =
-        g(x) \DD f(x) + 2 (\covq \grad g(x)) \cdot \grad f(x) - g(x) \meanq \cdot \grad f(x) .
+        \DG^*(fg)(x) - f(x) \DG^* g(x) . 
 \end{align*}
@@
     \left\{
-        \varphi_{T-s} \gamma (\DD f - \meanq \cdot \grad f)
-        + 2 \left(\covq \grad (\varphi_{T-s} \gamma) \right) \cdot \grad f 
-    \right\} \\
-    &=
-    r \gamma
-    \left\{
-        \DD f - \meanq \cdot \grad f
-        + 2 \left(\covq \grad \log(\varphi_{T-s} \gamma) \right) \cdot \grad f 
+        \DG^*(\gamma \varphi_{T-s} f) - f \DG^*(\gamma \varphi_{T-s})
     \right\} .
 \end{align}
-In other words, the lineage moves at speed equal to the local production of successful offspring,
-$r \gamma$,
-by a time-reversed version of the dispersal distribution,
-but with a drift in the direction of the gradient of the logarithm
-of the production of juveniles, $2 \grad \log(\phi_{T-s} \gamma)$
-(modified by the covariance of dispersal).
-This \comment{presumably?} agrees with \comment{the theorem}.
+This agrees with Theorem~\ref{thm:lineages}.
 
@@
 the corresponding factor in $f(\lp)$.
+
+\comment{Maybe we can not introduce $\theta$ before this point in this section, and say we'll put it in now?}
 
@@
 
-\comment{TODO: consider whether this is where we stick in
-    these explicit definitions of $\gamma$ and set $\lambda=N$.}
+\comment{TODO: this note goes much earlier.}
 To scale our lookdown model to be consistent with
@@
 
-\comment{This is a rewrite using Ulam-Harris labeling
-of \ref{sec: Evolution of an Individual Particle}.}
-
 Although we will \comment{(later)} show convergece of the lookdown process
@@
 $\kappa$ will be used to determine whether parent or offspring are assigned the new level,
-and the new label produced, if any will be $aj$,
+and the new label produced will be $a \concat j$,
 i.e., the label $a$ with $j$ appended (so, if $a \in \IN_{\ge 0}^k$ then $aj \in \IN_{\ge 0}^{k+1}$).
@@
 If this is the $j^\text{th}$ point in $\Pi_a$,
-the new label is $aj$, the (potential) birth time is $\tau_{aj} = \tau_a + s$.
+the new label is $a \concat j$, the (potential) birth time is $\tau_{a \concat j} = \tau_a + s$.
 For convenience define
@@
 \begin{equation*}
-    U_{aj}(\tau_{aj})
+    U_{a \concat j}(\tau_{a \concat j})
     =
-    U_a(\tau_{aj})
+    U_a(\tau_{a \concat j})
     +
-    \ell(X_a(\tau_{aj}-), y, \eta(\tau_{aj}-), v) .
+    \ell(X_a(\tau_{a \concat j}-), y, \eta(\tau_{a \concat j}-), v) .
 \end{equation*}
-If $U_{aj}(\tau_{aj}) < \lambda$,
-the new individual labeled $aj$ is produced,
+If $U_{a \concat j}(\tau_{a \concat j}) < \lambda$,
+the new individual labeled $a \concat j$ is produced,
 and $\kappa$ determines which label is associated with the new location,
@@
 \begin{align*}
-    X_{aj}(\tau_a + s)
+    X_{a \concat j}(\tau_a + s)
     &=
@@
 On the other hand
-if $U_{aj}(\tau_a+s) \ge \lambda$, then $X_a$ is unchanged and $X_{aj}$ is undefined,
+if $U_{a \concat j}(\tau_a+s) \ge \lambda$, then $X_a$ is unchanged and $X_{a \concat j}$ is undefined,
 so
@@
     &=
-    X_a(\tau_a+s-) + \kappa y \ind_{U_{aj}(\tau_{aj}) < \lambda} .
+    X_a(\tau_a+s-) + \kappa y \ind_{U_{a \concat j}(\tau_{a \concat j}) < \lambda} .
 \end{align}
@@
 
-\comment{
-    The following is quite annoying to get right, but can fixed up.
-    However, I don't think we need it.}
-
-Consequently, 
-the \emph{line of descent}
-leading from the initial generation
-to any label $a \in \labelspace$
-with $U_a(\tau_a) < \lambda$
-can be explicitly constructed as follows.
-Supposed that $a = (a_1, a_2, \ldots, a_n) \in \IN^n$,
-and for $1 \le k \le n$ let $(a)_k = (a_1, a_2, \ldots, a_k)$.
-Then, let $\zeta_a(t)$ denote the counting process that records
-which label is present in the line of descent at time $t$,
-i.e., $\zeta_a(t) = \max\{k \ge 1 : \tau_{(a)_k} \le t\}$.
-This then lets us define $X_a(t)$ all the way back to $t=0$
-by setting $X_a(t) = X_{(a)_{\zeta_a(t)}}(t)$ (and, $U_a(t)$ similarly).
-Now, we can explicitly write down the evolution of $U_a(t)$ and $X_a(t)$.
-
-First, for each $1 \le k < n$
-let $(s_k, v_k, y_k, \kappa_k)$ be the $a_{k+1}^\text{th}$ point in $\Pi_{(a)_k}$
-(this is the sequence of jumps taken by the line of descent).
-Note that $s_k = \tau_{(a)_k}$, and also set $s_0 = 0$.
-Let $\Gamma_a$ by the point process ``experienced by the line of descent leading to $a$'',
-which is for $A \subset [0,\infty)^2 \times \IR^d \times \{0,1\}$
-\comment{This is wrong, because $s$ is relative to birth time.}
-\begin{align*}
-\Gamma_a(A)
-    &=
-    \sum_{k=1}^n
-    \Pi_{(a)_k}\left(A \cap [s_{k-1}, s_k) \times [0, \infty) \times \IR^d \times \{0,1\}\right) 
-    \\ &\qquad {}
-    + \sum_{k=1}^{n-1}
-      \delta_{(s_k, v_k, y_k, 1 - \kappa_k)}(A) .
-\end{align*}
-Note that we have included the points at which the line of descent's level jumps,
-flipping $\kappa$ at these points,
-and as a result $\Gamma_a$ has the same distribution as $\Pi_a$
-restricted to $[0, \sigma_a)$.
-Then for $0 \le t \le \sigma_a$,
-\begin{align*}
-    X_a(t)
-    &=
-    X_{a_1}(0)
-    +
-    \int_{
-        [0, t) \times [0, \infty) \times \IR^d \times \{0, 1\}
-    }
-    \kappa y
-    \ind_{
-        U_{(a)_{\zeta(s)}}(s) + \ell( X_{(a)_{\zeta(s)}}(s-), y, \eta(s-), v) < \lambda
-    }
-    \Gamma_{a}(ds, dv, dy, d\kappa) 
-\end{align*}
-and
-\begin{align*}
-    U_a(t)
-    &=
-    U_{a_1}(0)
-    +
-    \sum_{k=1}^{\zeta_a(t) - 1}
-    \frac{
-        v_k
-    }{
-        2 \lambda^{-1} \theta \gamma(X_{(a)_k}(s_k-), \eta(s_k-))
-        r(X_{(a)_k}(s_k-) + y_k, \eta(s_k-))
-    }
-    \\ & \qquad {}
-    +
-    \int_0^t
-    \bigg(
-        \frac{\theta}{\lambda} \gamma(X_a(s),\eta(s))
-        \int_{\IR^d} r(z,\eta(s)) q(X_a(s),dz) U_a(s)^2
-    \\ & \qquad\qquad  \qquad {}
-        -
-        b(X_a(s),\eta(s)) U_a(s)
-    \bigg)
-    dt .
-\end{align*}
+\begin{remark}
+    \comment{TODO: say that it's clear how this works following a line of descent
+    all the way from time 0 (in particular, in the infinite density limit,
+    just the spatial part looks just the same despite the jumps in level).}
+\end{remark}
 
@@
 \label{sec:limiting_lines_of_descent}
-
-\comment{This is a rewrite of \ref{sec:lines_of_descent} following on the previous section}
 
@@
 $\tau_a \ge t$, and and $U_a(t) < \infty$,
-then a new line of descent with label $aj$ is produced,
-with birth time $\tau_{aj} = t$, location $X_{aj}(t) = X_a(t)$, and level
-$$
-    U_{aj}(t) = U_a(t)
+then a new line of descent with label $a \concat j$ is produced,
+with birth time $\tau_{a \concat j} = t$, location $X_{a \concat j}(t) = X_a(t)$, and level
+$$
+    U_{a \concat j}(t) = U_a(t)
     + \frac{v}{ 2 \alpha \gamma(X_a(t), \eta(t)) r(X_a(t), \eta(t)) } .
@@
 
-%% %% %% %% %% %% %% %% %% %% %% %%
-\subsection{PREVIOUS VERSION OF Evolution of an Individual Particle}
-\label{sec: Evolution of an Individual Particle}
-
-Here we give a general framework of tracking evolution
-of individual particles in the spatial-level population $\xi(t)_{t \geq 0}$ defined in \S \ref{sec:lookdown_defn}.
-
-Particles alive at time zero will be indexed by $(0, i)$,
-or more precisely,
-we index the levels of the particles
-alive at time $0$ by $(0, i)$,
-keeping in mind that at each birth event,
-the parent particle will,
-with probability $1/2$, change levels.
-Since no two particles born after time $0$
-will be born at the same time,
-we index the rest of the levels by their birth times.
-
-With each level,
-we can associate a Poisson random measure
-$\Tilde{\Pi}$ on $[0, \infty)^2\times [0,1]\times \{0,1\}$ (eventually, $\lambda \to \infty$) with mean measure $l^3 \times \{\frac{1}{2}\delta_0,\frac{1}{2}\delta_1\}$ which
-determines the birth times of the offspring of the particle at that level, the location of the
-offspring, and whether the offspring or the parent is placed at the new level. Let $U_{\tau}(t)$ be
-the level at time $t \geq \tau$ if the level first appeared at time $\tau$ , and let $X_{\tau}(t), t \geq \tau$ be the
-location of the particle with level $U_{\tau}(t)$. 
-Now $U_{\tau}$ satisfies
-\begin{equation}
-U_{\tau}(t)=U_{\tau}(\tau)+\int_{\tau}^{t}(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(s),\eta(s))U^2_{\tau}(s)-b_{\theta}(X_{\tau}(s),\eta(s))U_{\tau}(s))ds, ~~~ t \geq \tau.    
-\end{equation}
-If a level has index $\tau$ and $(s,v,w,\kappa)\in \xi_\tau$, then $\tau+s$ gives a potential birth time for an offspring of the particle at level $U_{\tau}$.
-We say `potential' since if $U_{\tau}(\tau+s)>\lambda$, the corresponding particle is dead.
-The (potential) new level is
-\begin{equation}\label{New birth potential level}
-    U_{\tau+s}(\tau+s)=U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))}.
-\end{equation}
-If $U_{\tau+s}(\tau+s)< \lambda$, a new particle is produced with location $X_{\tau}(\tau+s-)+H(X_{\tau}(\tau+s-), \eta(\tau+s-),w)$ where $H(X_{\tau}(\tau+s-), \eta(\tau+s-),w)$ is a function such that if $w$ is a uniformly distribution on $[0,1]$, then
-\begin{equation}\label{eq: Individual Evolution Jump Kernel}
-P(H(x, \eta,w)\in C | \eta,x)=q^{\mathfrak{m}}(x, \eta,C).    
-\end{equation}
-Consequently, 
-$$X_{\tau}(\tau+s)=X_{\tau}(\tau+s-)+\kappa H(X_{\tau}(\tau+s-), \eta(\tau+s),w)$$
-and 
-$$X_{\tau+s}(\tau+s)=X_{\tau}(\tau+s-)+(1-\kappa) H(X_{\tau}(\tau+s-), \eta(\tau+s),w),$$
-that is if $\kappa=0$, the parent stays at its current level and the new particle is given the new
-level. If $\kappa = 1 $, the parent is given the new level and the new particle is given the original
-
-level. Consequently, for $t \geq \tau$
-\begin{align}\label{eq: Spatial evolution of individual lineage}
-X_{\tau}(\tau+t)=&X_{\tau}(t)\\
-&+\int_{(0,t]\times[0,\infty]\times[0,1]\times\{0,1\}}\ind_{U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))}<\lambda\}}\kappa    H(X_{\tau}(\tau+s-), \eta(\tau+s),\omega) \\
-&\qquad \times \xi_{\tau}(ds,dv,dw,d\kappa).
-\end{align}
-Starting with an initial particle at level $U_{(0,i)}$ , we can identify a potential line of descent by
-taking $(s_1 , v_1 , w_1 , \kappa_1 ) \in \xi_{(0,i)}$ , setting $\tau_1=s_1$ , and then recursively taking $(s_k , v_k , w_k , \kappa_k ) \in \xi_{\tau_k }$ and defining $\tau_{k+1} = \tau_{k} + s_{k+1}$.
-Each time $\tau$ at which a new level appears has an “ancestory” of this type.\\
-We now explain the cases where $\kappa_k=0$ and $\kappa_k=1$.
-When $\kappa_k=0$, the parent retains the level, so $X_{\tau_{k}}$ remains the same at time $\tau_{k+1}$.
-When $\kappa_k=1$, the offspring gets its parent's level while the parent inherits a new level sampled between $[U_{\tau_k}(\tau_{k+1}-),\lambda]$.
-As a result, the spatial location $X_{\tau_{k}}$ jumps from the parent's location to the offspring's location at time $\tau_{k+1}$.
-Meanwhile, between $[\tau_k, \tau_{k+1}]$ there maybe further birth events generated by $\xi_{\tau_k}$.
-If $(s,v,w,\kappa) \in \xi_{\tau_k}$, Equation \eqref{eq: Spatial evolution of individual lineage} holds and gives the spatial evolution of $X_{\tau_k}$ for $t \in [\tau_k, \tau_{k+1}]$.\\
-
-For $\tau=\tau_m$ in a recursion like this, let
-\begin{equation}\label{eq: Individual Evolution Recursion Terms}
-\zeta^{0}_{\tau}(B)=\sum_{k=1}^{m}\delta_{(s_k,v_k,w_k,(1-\kappa_k))}, ~~~ V_{\tau}(t)=\sum_{k=1}^{m}v_k\ind_{[0, \tau_k]}  (t)  
-\end{equation}
-and define $U_{\tau}(0)=U_{(0,i)}, X_{\tau}(0)=X_{(0,i)}(0)$, and $\zeta_{\tau}$ by
-\begin{equation}\label{eq: integrand in spatial tracing}
-\zeta_{\tau}(B)=\zeta_{\tau}^{0}(B)+\sum_{k=0}^{m}\int \ind_{B}(\tau_k+s,v,w,\kappa)\ind_{\{\tau_k+s<\tau_{k+1}\}}\xi_{\tau_k}(ds,dv,dw,d\kappa)    
-\end{equation}
-
-where $\tau_{m+1}=\infty$. Then
-
-\begin{align*}
-U_{\tau}(t)=&U_{\tau}(0)+\int_{0}^{t}\frac{1}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(s-), \eta(s-))}dV_{\tau}(s)\\
-&+\int_{0}^{t}\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(s-), \eta(s-))U^2_{\tau}(s)-b_{\theta}(X_{\tau}(s),\eta(s))U_{\tau}(s))ds,\\  
-X_{\tau}(t)=&X_{\tau}(0)+\int_{(0,t]\times[0,\infty]\times[0,1]\times\{0,1\}}\ind_{U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))}<\lambda\}}\\
-&\qquad \times \kappa   H(X_{\tau}(s-), \eta(s-),\omega)\zeta_{\tau}(ds,dv,dw,d\kappa)
-\end{align*}
-gives the spatial and level dynamics of a lineage.
-Note that $\zeta^{0}_{\tau}(B)$ produces spatial jumps when $\kappa_k=1$, while the integral against $\xi_{\tau_k}$ in Equation \eqref{eq: integrand in spatial tracing} gives spatial jumps when $(s,v,w,\kappa) \in \xi_{\kappa_k}$, $\tau_k \leq s \leq \tau_{k+1}$, and $\kappa = 1$.
-This corresponds to the discussion given above.
-\begin{remark}
-The factor $\frac{1}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x, \eta)}$ that scales the jump in levels give an average birth rate of $\theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(s-), \eta(s-))$.
-This is because for the potential birth to be a true birth, we impose that $$U_{\tau}(\tau+s)+ \frac{v}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))}< \lambda,$$ where $U_{\tau}(\tau+s)$ is uniformly distributed between $[0, \lambda]$.
-As a result, a true birth occurs between $[0,\delta t]$ if there exists $(s,v) \in [0,\delta t]\times [0, 2 (\lambda-U_{\tau}(\tau+s)) \lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))]$.
-Averaging this over levels give a Poisson process with rate $ \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(\tau+s-), \eta(\tau+s-))$.
-\end{remark}
-\begin{remark}
-Although the labelling presented here depends on random birth times, we can label each individual in the population deterministically with the Ulam-Harris label.
-We therefore have a countable particle system.
-In particular, we can now express our particle systems as
-$$\eta(t)=\frac{1}{\lambda}\sum_{U_{\tau}(t) < \lambda} \delta_{X_{\tau}(t),U_{\tau}(t)}, ~~\eta(t)=\frac{1}{\lambda}\sum_{ U_{\tau}(t) < \lambda} \delta_{X_{\tau}(t)}.$$
-For further discussion refer to \S \ref{sec: Ulam-Harris Labels characterisation}.
-\end{remark}
-
-%% %% %% %% %% %% %% %% %% %% %% %%
-\subsection{PREVIOUS VERSION OF Stochastic equations for movement of lines of descent}
-    \label{sec:lines_of_descent}
-
-    \plr{This section needs to follow from the previous section better (and maybe be merged with it).}
-
-The main interest in using a lookdown construction for our 
-population processes is that it allows us to retain information 
-about relatedness between individuals as we pass to the infinite
-density limit. In order to exploit this, we generalise the construction of 
-stochastic equations presented in \S \ref{sec: Evolution of an Individual Particle} to the infinite density limit.\\
-In the scaling limit $A^{\text{nl}}_{\epsilon}$, the spatial movement of particles can be characterised with the map $$h \mapsto \gamma\big(x,(\rho_{\epsilon}*\Xi)(x)\big)r\big(x,(\rho_{\epsilon}*\Xi)(x)\big)\mathcal{B}^{m}_{\epsilon}(\Xi)h(x) ,$$
-and as individual particles travel as a random walk in the pre-limit model, we should expect a diffusion limit for individual trajectories.
-\todo[inline]{From Terence: we should try explain in detail why this is the generator of an individual line of descent forward-in-time.
-The main question here is whether we should have a factor of $r$ in the above notation.
-For the proof to work in \S \ref{sec: motion of ancestral lineages} we will need a factor of $r$ but I have been finding it slightly unintuitive particularly since the effect of $r$ has been accounted into $\mathcal{B}^{\mathfrak{m}}$ through the limit.}
-To simply notation, we let the above map be the generator of a process 
-satisfying 
-\[X(t)=X(0)+\int_0^t\sigma (X(s),\Xi (s))dW(s)+\int\beta (X(s),\Xi 
-(s))ds.\]
-\begin{remark}
-In particular recall that as in Remark \ref{Remark: Product Rule on Laplacian}, if $\mathcal{B}$ is the Laplacian operator, then the generator above is merely 
-$$\gamma\big(x,(\rho_{\epsilon}*\Xi)(x)\big)\left(\Delta h(x) +2 \nabla h(x) \cdot \nabla \log r( \cdot, (\rho_{\epsilon}*\Xi)(\cdot))(x)\right),$$
-and applying Ito's formula we have 
-\begin{equation}\label{eq: Individual lineage generator description}
-\begin{aligned}
-\beta(X(s),\Xi(s))=& 2\gamma\big(X(s),(\rho_{\epsilon}*\Xi)(X(s))\big) \nabla \log r (\cdot, (\rho_{\epsilon}*\Xi)(\cdot))(X(s))\\
-\sigma(X(s),\Xi(s))=& \sqrt{2\gamma\big(X(s),(\rho_{\epsilon}*\Xi)(X(s))\big)}.
-\end{aligned}
-\end{equation}
-\end{remark}
-
-Furthermore, recall that in our scaling limit, 
-\begin{equation}
-\begin{aligned}
-\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(X_{\tau}(s), \eta(s)) &\to \ell \gamma(X_{\tau}(s),\rho_\epsilon*\Xi(X_{\tau}(s)),\\
-b_{\theta}(X_{\tau}(s),\eta(s)) &\to  F(X_{\tau}(s), (\rho_{\epsilon}*\eta)(X_{\tau}(s)))\\
-&+\gamma(X_{\tau}(s), (\rho_{\epsilon}*\Xi)(X_{\tau}(s)))\mathcal{B}r(\cdot,(\rho_{\epsilon}*\eta)(\cdot))(X_{\tau}(s)).
-\end{aligned}    
-\end{equation}
-
-We now have the required results to establish the individual lineage dynamics in the scaling limit. Our approach should be compared to Perkins stochastic calculus,
-\cite{perkins:1995}. First we label the individuals alive at time $0$
-by $\{(0,i), i\in\IN\}$.
-
-When an individual is born, it is endowed with an
-independent Poisson random measure $\xi$ on $[0,\infty)^2$ with Lebesgue
-mean measure. The first coordinate encodes {\em potential} birth times of 
-offspring of the individual. We say potential, since the parent may have
-died before the potential birth time. 
-Since, after time $0$, no two particles will have the same birth
-time, we index the particles born after time $0$ by 
-their birth times.  
-For example, if a parent has index $\tau$ and $(s,v)\in \xi_\tau$, then 
-$\tau +s$ gives a potential birth time for an offspring which, if
-it is in fact born, will carry
-the label $\tau+s$. 
-The second 
-coordinate of $\xi$ will be used to determine, after scaling, 
-the level of offspring relative to the 
-level of the parent (offspring are always born to levels above that of
-the parent).
-
-Starting with an initial particle 
-$(0,i)$, we can identify a potential line of descent by 
-taking $(s_1,u_1)\in\xi_{(0,i)}$, setting $\tau_1=s_1$, and then recursively 
-taking $(s_{k+1},u_{k+1})\in\xi_{\tau_k}$ and defining $\tau_{k+1}
-=\tau_k+s_{k+1}$.
-
-With each particle, we will 
-associate an independent Brownian motion, $W_\tau$. For times 
-$t>\tau$, the spatial location and level of the particle with
-label $\tau$ are then determined by
-\begin{equation}\label{Eq: Expression for dynamics in scaling limit}
-\begin{aligned}
-X_{\tau}(t)=&X_{\mbox{\rm $\tau$}}(\tau )+\int_{\tau}^t\sigma (X_{
-\tau}(s),\Xi (s))dW_{\tau}(s)+\int_{\tau}^t\beta (X_{\tau}(s),\Xi (
-s))ds\\
-U_{\tau}(t)=&U_{\tau}(\tau )+\int_{\tau}^t\bigg\{\ell \gamma(X_{\tau}(s),\rho_\epsilon*\Xi(X_{\tau}(s)U_{\tau}^2(s) \\
-& -\big(F(X_{\tau}(s), (\rho_{\epsilon}*\eta)(X_{\tau}(s)))+\gamma(X_{\tau}(s), (\rho_{\epsilon}*\Xi)(X_{\tau}(s)))\mathcal{B}r(\cdot,(\rho_{\epsilon}*\eta)(\cdot))(X_{\tau}(s))\big)U_{\tau}(s))\bigg\}ds.
-\end{aligned}
-\end{equation}
-If $(X_{\tau'},U_{\tau'})$ is the parent of $(X_{\tau},U_{\tau})$, 
-then there is $(s,v)\in\xi_{\tau'}$ 
-such that $\tau =\tau'+s$,
-$X_{\tau}(\tau'+s)=X_{\tau'}(\tau'+s)$ and 
-\begin{equation}
-\label{Eq: expression for offspring level in limit}
-U_{\tau}(\tau )=U_{\tau}(\tau'+s)=U_{\tau'}(\tau'+s)+\frac v{2\ell \gamma(X_{\tau}(s),\rho_\epsilon*\Xi(X_{\tau}(s))U_{\tau}^2(s)},
-\end{equation} 
-recognizing 
-that $U_{\tau'}(\tau'+s)$ may be infinite, which means 
-that $(X_{\tau}, U_{\tau})$ doesn't exist.
-To see why we scale $v$ in this way, 
-we observe that
-in order for $U_{\tau}(\tau'+s)$ to be below some fixed level $u_g$,
-we require 
-$v<2\ell \gamma(X_{\tau'}(\tau'+s),\rho_\epsilon*\Xi(X_{\tau'}(\tau'+s))U_{\tau}^2(\tau'+s)\big(u_g-U_{\tau'}(\tau'+s)\big)$.
-Recalling
-that $\xi_{\tau'}$ is Poisson on $[0,\infty)^2$ with Lebesgue mean 
-measure, the instantaneous rate at which we see such a $v$ will be
-$2\gamma(X_{\tau'}(\tau'+s), \Xi(\tau'+s))\big(u_g-U_{\tau'}(\tau'+s)\big)$.
-Comparing  this
-with Equation
-\eqref{Eq: Non-local Scaling limit Lookdown Generator}, this is exactly
-the rate of births that we require.
-\begin{remark}
-Note in particular that $\ell=0$ in the deterministic limit , so the increment in Equation \eqref{Eq: expression for offspring level in limit} is always infinite, meaning that no new offspring is born in the deterministic model.
-\end{remark}
-In order to write $X_\tau(t)$ and $U_\tau(t)$ as an integral along
-the whole ancestral path linking individual $\tau$ to its ancestor at 
-time $0$, we associate a counting process $N_{\tau}$ with the indivdual
-$\tau$    
-such that $N_{\tau}(t)$ gives the generation of the ancestor of $\tau$ 
-that is alive at time $t$,
-and a process $A_{\tau}$ such that 
-$A_{\tau}(t)$ is 
-the index of the ancestor of $\tau$ that is alive at time $t$. 
-Finally, let $V_{\tau}(t)=\sum_{k=1}^{N_{\tau}(t)}v_k^{\tau}$ be the sum of the second 
-coordinate of the Poisson points along the ancestral line 
-leading to $\tau$.  Then we can write 
-\begin{eqnarray*}
-X_{\tau}(t)&=&X_{\mbox{\rm $A_{\tau}(0)$}}(0)+\int_0^t\sigma 
-(X_{\tau}(s),\Xi (s))dW_{A_{\tau}(s)}(s)+\int_0^t\beta (X_{\tau}
-(s),\Xi (s))ds,\\
-U_{\tau}(t)&=&U_{A_{\tau}(0)}(0)+\int_0^t\frac 1{2\ell \gamma(X_{\tau}(s-),\rho_\epsilon*\Xi(X_{\tau}(s-))}dV_{\tau}(s)\\
-&&\qquad\qquad +\int_{\tau}^t\bigg\{\ell \gamma(X_{\tau}(s),\rho_\epsilon*\Xi(X_{\tau}(s)U_{\tau}^2(s) \\
-&&-\big(F(X_{\tau}(s), (\rho_{\epsilon}*\eta)(X_{\tau}(s)))+\gamma(X_{\tau}(s), (\rho_{\epsilon}*\Xi)(X_{\tau}(s)))\mathcal{B}r(\cdot,(\rho_{\epsilon}*\eta)(\cdot))(X_{\tau}(s))\big)U_{\tau}(s))\bigg\}ds,\end{eqnarray*}
-where
-\[\langle\Xi (t),\varphi\rangle =\lim_{\epsilon\rightarrow 0}
-\epsilon\sum_{
-\tau\leq t}e^{-\epsilon U_{\tau}(t)}\varphi (X_{\tau}(t)).\]
-
+\comment{TODO: incorporate this in the discussion somewhere (and maybe other refs? see previous version).}
 This representation of individuals allows us to identify all 

### 2022-04-27 forwards-and-backwards.tex
figure

@@
     \begin{center}
-        FIGURE
+        \includegraphics{figures/ex1a/fkpp_123.locations}
+        \includegraphics{figures/ex1b/fkpp_123.locations}
     \end{center}
     \caption{
-        TODO: Figure depicting deterministic vs superprocess dichotomy:
-        showing 2D images of populations,
-        one with $\theta/N$ not small, the other with $\theta/N$ small.
+        Snapshots of two simulations, with small $\theta$ (left) and large $\theta$ (right).
+        Simulations are run with a FKPP-like parameterization:
+        birth and establishment are constant, while death increases linearly with density,
+        at slope $1/\theta$.
+        Left: $\theta=1$. Right: $\theta=100$.
+        Other parameters were the same:
+        dispersal and interactions distance were set to 1,
+        and the equilibrium density is 10 individuals per unit area.
         \label{fig:super_vs_det_2d}

### 2022-04-27 figures/make_plots.sh

@@ -1,0 +1,13 @@
+#!/bin/bash
+
+# smooth and patchy figures
+for DIR in ex1a ex1b
+do
+    pushd $DIR
+    if [ ! -e fkpp_123.trees ]
+    then
+        slim -s 123 ../fkpp.slim
+    fi
+    ../lineage_plotting/plot_density.py fkpp_123.trees 3
+    popd
+done

### 2022-04-27 figures/make_plots.sh
.

@@ -1,5 +1,10 @@
 #!/bin/bash
 
+if [ ! -e lineage_plotting ]
+    echo "Need lineage_plotting repository as a subdirectory."
+    exit 1
+fi
+
 # smooth and patchy figures
 for DIR in ex1a ex1b
 do

### 2022-05-02 forwards-and-backwards.tex
Update on Overleaf.

@@
 \usepackage{url}
-
 \usepackage{xcolor}
@@
 it suffices to show that 
-\begin{equation}
+\begin{equation}\label{eq: gaussian density estimate}
  \theta H_{\theta}(x,w)\rho_r(x-w)\leq \rho_{\gamma}(x-w),
@@
 q_{\theta}(x,dy).$$
-Writing out $H$,
-\begin{align}
-H_\theta(x, w)
-=
-\int
-    \left(
-        \exp\left(
-            - \frac{1}{2\epsilon_r^2}
-            \left\{
-                ||y - w||^2 - ||x - w||^2
-            \right\}
-        \right)
-        -
-        1
-    \right)^2
-    \frac{
-        e^{-\theta (y - x-\meanq)^{T}\covq^{-1}(y - x-\meanq)  / 2}
-    }{
-        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
-    }
-dy.
-\end{align}
-Writing $z=y-x-\meanq$, we have that 
-\begin{equation}
-\begin{aligned}
-||y - w||^2 - ||x - w||^2 
-=& ||y||^2-||x||^2 -2\langle y-x, w\rangle \\
-=&||x+z+ \meanq||^2-||x||^2-2 \langle z+ \meanq, w\rangle\\
-=&2\langle x, z+ \meanq \rangle + ||z+ \meanq||^2-2 \langle z+ \meanq, w\rangle \\
-=& 2 \langle x-w, z+ \meanq \rangle + ||z+ \meanq||^2\\
-=& 2\langle x-w+ \meanq,\meanq \rangle + 2\langle x-w+ \meanq, z \rangle +||z||^2
-\end{aligned}
-\end{equation}
-As a result, we have 
-\begin{align}
-H_\theta(x, w)
-=&
-\int
-    \left(
-        \exp\left(
-            - \frac{1}{2\epsilon_r^2}
-            \left\{
-                2 \langle x-w, z+ \meanq \rangle + ||z+ \meanq||^2
-            \right\}
-        \right)
-        -
-        1
-    \right)^2
-    \frac{
-        e^{-\theta z^{T}\covq^{-1}z  / 2}
-    }{
-        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
-    }
-dz\\
-=&\exp\left(-\frac{2}{\epsilon_r^2}\langle x-w+ \meanq,\meanq \rangle \right)\\
-& \times \int
-        \frac{
-        \exp\left(
-            - \frac{2}{\epsilon_r^2} \langle x-w+ \meanq, z \rangle
-            - \frac{1}{\epsilon_r^2} ||z||^2
-            \right)
-            e^{-\theta z^{T}\covq^{-1}z  / 2}
-    }{
-        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
-    }
-dz\\ \label{eq: Second moment term matrix calculation}
-&-2\exp\left(-\frac{1}{\epsilon_r^2}\langle x-w+ \meanq,\meanq \rangle \right)\\
-& \qquad \qquad \times     \int
-    \frac{ \exp\left(
-             -\frac{1}{\epsilon_r^2}\langle x-w+ \meanq, z \rangle
-              -\frac{1}{2\epsilon_r^2} ||z||^2
-            \right)e^{-\theta z^{T}\covq^{-1}z  / 2}
-        }{
-        (2 \pi/ \theta)^{d/2} |\covq|^{1/2} \label{eq: first moment term matrix calculation}
-    }
-dz\\
-&+1.
-\end{align}
-We now consider the integral of the form 
-\begin{equation}
-\int \exp(v^{T}z-C||z||^2) \frac{
-        e^{-\theta z^{T}\covq^{-1}z  / 2}
-    }{
-        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
-    }
-dz   
-\end{equation}
-for $v \in \mathbb{R}^d$ and $C>0$. 
-We have 
-\begin{equation}
-\begin{aligned}
-&\int \exp(v^{T}z-C||z||^2) \frac{
-        e^{-\theta z^{T}\covq^{-1}z  / 2}
-    }{
-        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
-    }
-dz\\
-=&\frac{1}{|\covq|^{1/2}|  |\covq^{-1}(I+2C\covq/\theta )|^{1/2}  }\int \exp(v^{T}z) \frac{
-        e^{-\theta z^{T}\covq^{-1}(I+2C\covq/\theta )z  / 2}
-    }{
-        (2 \pi/ \theta)^{d/2}|\covq^{-1}(I+2C\covq/\theta )|^{-1/2} 
-    }
-dz\\
-=& \frac{1}{|I+2C\covq/\theta |^{1/2}} \mathbb{E}_{Z}[\exp (v^{T}Z)]\\
-=&\frac{1}{|I+2C\covq/\theta |^{1/2}}
-\exp 
-\left(
-\frac{1}{2}v^{T}\covq/\theta(I+2C\covq/\theta )^{-1}v
-\right),
-\end{aligned}
-\end{equation}
-where $Z \sim N(0, \covq/\theta \times (I+2C\covq/\theta )^{-1})$.
-
-Now writing $v=\frac{2}{\epsilon_r^2}( w-x-\meanq)$
-and $C=\frac{1}{\epsilon_r^2}$,
-we have the expression in Equation
-\eqref{eq: Second moment term matrix calculation} is 
-$$\frac{1}{|I+2\covq/(\epsilon_r^2\theta) |^{1/2}}
-\exp 
-\left(
-\frac{2}{\epsilon_r^4}( w-x-\meanq)^{T}\covq/\theta\left(I+2\covq/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
-\right).$$
-Similarly, writing $v=\frac{1}{\epsilon_r^2}( w-x-\meanq)$
-and $C=\frac{1}{2\epsilon_r^2}$,
-we have the expression in Equation
-\eqref{eq: first moment term matrix calculation} is 
-$$\frac{1}{|I+\covq/(\epsilon_r^2\theta) |^{1/2}}
-\exp 
-\left(
-\frac{1}{2\epsilon_r^4}( w-x-\meanq)^{T}\covq\left(I+\covq/\theta/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
-\right).$$
-As a result, we have 
-\begin{align*}
-&H_{\theta}(x,w)\\
-=& \frac{1}{|I+2\covq/(\epsilon_r^2\theta) |^{1/2}}
-\exp 
-\left(
-\frac{2}{\epsilon_r^4}( w-x-\meanq)^{T}\covq/\theta\left(I+2\covq/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
-\right)\\
-&-2\frac{1}{|I+\covq/(\epsilon_r^2\theta) |^{1/2}}
-\exp 
-\left(
-\frac{1}{2\epsilon_r^4}( w-x-\meanq)^{T}\covq/\theta\left(I+\covq/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
-\right)\\
-&+1.
-\end{align*}
-If we write $F(1/\theta)=H_{\theta}(x,w)$, i.e.
-\begin{align*}
-&F(s)\\
-=& \frac{1}{|I+2/\epsilon_r^2 \covq s |^{1/2}}
-\exp 
-\left(
-\frac{2}{\epsilon_r^4}( w-x-\meanq)^{T}\covq s \left(I+2/\epsilon_r^2 \covq s\right)^{-1}( w-x-\meanq)
-\right)\\
-&-2\frac{1}{|I+2/\epsilon_r^2 \covq s |^{1/2}}
-\exp 
-\left(
-\frac{1}{2\epsilon_r^4}( w-x-\meanq)^{T}\covq s \left(I+2/\epsilon_r^2 \covq s\right)^{-1}( w-x-\meanq)
-\right)\\
-&+1\\
-&=G_1(s)+2G_2(s)+1
-\end{align*}
-we can check that $F(0)=0$.
-As a result, 
-$$\theta H_{\theta}(x,w)\rho_r(x-w)= \theta F(1/\theta)\rho_r(x-w)=F'(s)\rho_r(x-w),$$
-for some $s \in [0, 1/\theta]$.
-
-In Equation \eqref{eq: gamma-r convolution comparison}, we have established that 
-$\rho_r(x-w) / \rho_\gamma(x-w) = C' \exp(-K (x-w)^2 / 2)$
-with $K = \frac{1}{\epsilon_r^2} - \frac{1}{\epsilon_\gamma^2}$.
-Therefore it suffices to show that for all $x,w \in \mathbb{R}^d$ and $s \in [0, 1/\theta]$, 
-\begin{align} 
-    F'(s) \exp\left(-A (x-w)^2 \right) \le C .
-\end{align}
-
-We consider how to differentiate function $G$ of the form 
-$$G(s):=\frac{1}{|I+As|^{1/2}}\exp(v^{T}Bs(I+Cs)^{-1}v),$$
-where $A,B,C$ are matrices with non-negative entries and $I$ is the identity matrix.
-
-Since 
-\begin{equation}
-\begin{aligned}
-G'(s)=& - \frac{|A|}{2|I+As|^{3/2}}\exp(v^{T}Bs(I+Cs)^{-1}v)\\
-      & + \frac{1}{|I+As|^{1/2}}\exp(v^{T}Bs(I+Cs)^{-1}v)\\
-      & \qquad \times \left\{ v^{T}B(I+Cs)^{-1}v
-                            - sv^{T}BC(I+Cs)^{-2}v
-                    \right\}\\
-      &=\left(- \frac{|A|}{2|I+As|}+v^{T}B(I+Cs)^{-2}v
-        \right)\\
-      & \qquad \times
-        \frac{1}{|I+As|^{1/2}}\exp(v^{T}Bs(I+Cs)^{-1}v),
-\end{aligned}
-\end{equation}
-using non-negativity of $A,B,C$ we have
-\begin{equation}
-\label{eq: bounds on G'}
-|G'(s)| \leq (|A|+||B||_{2}||v||_2^2)G(s).    
-\end{equation}
-As a result, we have that 
-\begin{equation}
-\label{eq: bounds on G}
-G(s) \leq K e^{|A|+||B||_{2}||v||_2^2)s}, ~~   G'(s)(|A|+||B||_{2}||v||_2^2)K e^{|A|+||B||_{2}||v||_2^2)s}.  
-\end{equation}
-
-Finally note that, 
-$$F'(s) \leq G_1'(s)+2G_2'(s),$$
-where 
-$$A_1= 2\epsilon_r^{-2} \covq, ~ v_1=\epsilon_r^{-2}(w-x-\meanq), ~B_1 = 2\covq, ~C_1=2\epsilon_r^{-2} \covq,$$
-and 
-$$A_2= 2\epsilon_r^{-2} \covq, ~ v_2=\epsilon_r^{-2}(w-x-\meanq), ~B_2 = \covq/2, ~C_2=2\epsilon_r^{-2} \covq,$$
-Substituting these quantities on Equation \eqref{eq: bounds on G} shows that Equation \eqref{eqn:goal3} is satisfied as long as $\epsilon_r < \epsilon_\gamma$.
+For the proof of Equation \eqref{eq: gaussian density estimate} refer to the Lemma \ref{eq: Gaussin density estimates} in the Appendix.
+
 \end{proof}
@@
 \left(
-F_f(\eta^{\theta}_{t+s})-F_f(\eta^{\theta}_t)
--\int_{t}^{t+s}\Pgen^{\infty}F_f(\eta^{\theta}_s)ds
+F_f(\eta^{\theta}_{t+\tau})-F_f(\eta^{\theta}_t)
+-\int_{t}^{t+\tau}\Pgen^{\infty}F_f(\eta^{\theta}_s)ds
 \right)
@@
 \end{equation}
-for all $k\geq 0$, $0\leq t_1<t_2<...,t_k \leq t < t+s$,
+for all $k\geq 0$, $0\leq t_1<t_2<...,t_k \leq t < t+\tau$,
 and $h_1,...,h_k \in \mathcal{C}_{0}(\mathbb{R}^d)$.
@@
 \begin{aligned}
-&\mathbb{E}\left[F_f(\eta^{\theta}_{t+s})-F_f(\eta^{\theta}_t)\bigg| \mathcal{F}_t \right]\\
+&\mathbb{E}\left[F_f(\eta^{\theta}_{t+\tau})-F_f(\eta^{\theta}_t)\bigg| \mathcal{F}_t \right]\\
 =& F'(\langle f, \eta^{\theta}_t \rangle )
 \mathbb{E}\left[
-                \langle f, \eta^{\theta}_{t+s}\rangle
+                \langle f, \eta^{\theta}_{t+\tau}\rangle
                     -\langle f, \eta^{\theta}_t\rangle 
@@
                 \left(
-                    \langle f, \eta^{\theta}_{t+s}\rangle -\langle f, \eta^{\theta}_t\rangle
+                    \langle f, \eta^{\theta}_{t+\tau}\rangle -\langle f, \eta^{\theta}_t\rangle
                 \right)^2
@@
         \right]\\
-&+\frac{1}{6}F'''(\langle f, \eta^{\theta}_{t+s'}\rangle)\mathbb{E}\left[
+&+\frac{1}{6}F'''(\langle f, \eta^{\theta}_{t+\tau'}\rangle)\mathbb{E}\left[
                 \left(
-                    \langle f, \eta^{\theta}_{t+s}\rangle -\langle f, \eta^{\theta}_t\rangle
+                    \langle f, \eta^{\theta}_{t+\tau}\rangle -\langle f, \eta^{\theta}_t\rangle
                 \right)^3
@@
 =& F'(\langle f, \eta^{\theta}_t \rangle )\\
-& \times  \int_{0}^{t}\bigg\{
+& \times  \int_{t}^{t+\tau}\bigg\{
         \int\left(   \int \theta
@@
 &+\frac{1}{2}F''(\langle f, \eta^{\theta}_t \rangle )\\
-&\quad \times \frac{\theta}{N} \int_{0}^{t}\bigg\{
+&\quad \times \frac{\theta}{N}\int_{t}^{t+\tau}\bigg\{
 \langle \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
@@
 ,\eta^{\theta}_{s}(dx)\rangle \bigg\}ds\\
-&+\frac{1}{6}F^{(3)}(\langle f, \eta^{\theta}_{t+s'}\rangle)\mathbb{E}\left[
+&+\frac{1}{6}F^{(3)}(\langle f, \eta^{\theta}_{t+\tau'}\rangle)\mathbb{E}\left[
                 \left(
-                    \langle f, \eta^{\theta}_{t+s}\rangle -\langle f, \eta^{\theta}_t\rangle
+                    \langle f, \eta^{\theta}_{t+\tau}\rangle -\langle f, \eta^{\theta}_t\rangle
                 \right)^3
@@
 for some $s' \in [0,s]$.
+
+We first show that 
+$$\lim_{\theta \to \infty}\mathbb{E}\left[
+                \left|
+                    \langle f, \eta^{\theta}_{t+\tau}\rangle -\langle f, \eta^{\theta}_t\rangle
+                \right|^3
+                \bigg| \mathcal{F}_t
+        \right] \to 0.$$
+Since the total number of births and deaths
+between $[t,t+\tau]$ is given by Poisson point processes
+with rates $\theta \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)$
+and $\theta \mu\big(x,\eta^{\theta}_{s}\big)$
+respectively,
+and each birth and death events contribute
+an increment of order $\mathcal{O}(1/N^3)$,
+we have that
+\begin{multline}
+\lim_{\theta \to \infty}\mathbb{E}\left[
+                \left|
+                    \langle f, \eta^{\theta}_{t+\tau}\rangle -\langle f, \eta^{\theta}_t\rangle
+                \right|^3
+                \bigg| \mathcal{F}_t
+        \right] \\
+\leq ||f||_{\theta} \frac{\theta}{N^2}\int_{0}^{t}\left\langle\gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)+\mu\big(x,\eta^{\theta}_{s}\big), \eta^{\theta}_s(dx)\right\rangle ds \to 0
+\end{multline}
+as $\theta \to \infty$.
 \end{proof}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \newpage
+
 \section{Technical Lemmas}
-\subsection{Proof to Lemma \ref{lem: gamma - r radius comparison}}
-    \label{sec: Proof to gamma-r radius comparison}
-Suppose that the birth rate at $x$ is
-$\gamma(\rho_\gamma * \eta(x))$
-and the establishment probability is
-$r(\rho_r * \eta(x))$,
-for some functions $\gamma$ and $r$,
-and where $\rho_\gamma$ and $\rho_r$ are some kernels,
-and that the death rate at $x$ is
-$$
-    \mu(x, \eta) = 
-        \gamma(\rho_\gamma * \eta(x))
-        r(\rho_r * \eta(x))
-        +
-        \frac{1}{\theta} F(\rho_R * \eta(x))
-$$
-for some bounded function $F$ and kernel $\rho_R$ (that is probably either $\rho_r$ or $\rho_\gamma$).
-
-To bound $\IE\left[\langle 1, \eta_t \rangle\right]$
-by Gronwall,
-we would like to find a bound of the form
-\begin{align} \label{eqn:goal}
-    \theta \int \left[
-        r(\rho_r * \eta(y))
-        -
-        r(\rho_r * \eta(x))
-    \right] q_\theta(x, dy)
-    \le
-    G( \rho_\gamma * \eta(x) ),
-\end{align}
-for some polynomial function $G$.
-
-To do this, first we expand $r(\rho_r * \eta(x))$ to second order.
-Given $y$, with $x < \tilde y < y$,
-\begin{align}
-    r(\rho_r * \eta(y)) - r(\rho_r * \eta(x))
-    &=
-    r'(\rho_r * \eta(x))
-    \left\{
-        \rho_r * \eta(y)
-        -
-        \rho_r * \eta(x)
-    \right\}
-    +
-    \frac{1}{2}
-    r''(\rho_r * \eta(\tilde y))
-    \left\{
-        \rho_r * \eta(y)
-        -
-        \rho_r * \eta(x)
-    \right\}^2 .
-\end{align}
-
-Putting this in Equation \eqref{eqn:goal}, the second term is then
-\begin{align}
-&\theta \int
-    \frac{1}{2}
-    r''(\rho_r * \eta(\tilde y))
-    \left\{
-        \rho_r * \eta(y)
-        -
-        \rho_r * \eta(x)
-    \right\}^2 
-    q_\theta(x, dy)  \\
-&\qquad
-\le \theta \frac{\|r''\|_\infty}{2}
-    \int
-    \left\{
-        \rho_r * \eta(y)
-        -
-        \rho_r * \eta(x)
-    \right\}^2 
-    q_\theta(x, dy)  .
-\end{align}
-
-We will first show that this is bounded by a function of $\rho_\gamma * \eta(x)$,
-i.e., that for any $x < \tilde y < y$ and $\theta$ sufficiently large,
-there is a $C$ with
-\begin{align} \label{eqn:goal2}
-    \theta \int
-    \left\{
-        \rho_r * \eta(y)
-        -
-        \rho_r * \eta(x)
-    \right\}^2 
-    q_\theta(x, dy)  
-\le
-C \rho_\gamma * \eta(x) .
-\end{align}
-
-Leaving aside the $\frac{\|r''\|_\infty}{2}$ constant,
-let's rewrite this so we can use Fubini.
-First note that,
-since $\rho_r *\eta(x) = \int \rho_r(x - w) \eta(dw)$
-is the normalizing constant for the measure proportional to $\rho_r(x - w) \eta(dw)$,
-then applying Jensen's inequality,
-\begin{align}
-&\left\{
-            \rho_r * \eta(y)
-            -
-            \rho_r * \eta(x)
-\right\}^2  \\
-&\qquad
-=
-\left\{
-\int
-    \left(
-        \rho_r(y-w)
-        -
-        \rho_r(x-w)
-    \right)
-\eta(dw)
-\right\}^2  \\
-&\qquad
-=
-\left\{
-\int
-    \left(
-        \frac{\rho_r(y-w)}{\rho_r(x-w)}
-        -
-        1
-    \right)
-    \rho_r(x-w)
-\eta(dw)
-\right\}^2  \\
-&\qquad
-=
-\left(\rho_r * \eta(x)\right)^2 \left\{
-\int
-    \left(
-        \frac{\rho_r(y-w)}{\rho_r(x-w)}
-        -
-        1
-    \right)
-    \frac{\rho_r(x-w)}{\rho_r * \eta(x)}
-\eta(dw)
-\right\}^2  \\
-&\qquad
-\le
-\left(\rho_r * \eta(x)\right)^2 
-\int
+\subsection{Gaussian Kernel Estimates}
+
+\begin{lemma}\label{eq: Gaussin density estimates}
+\begin{equation}\label{eq: gaussian density estimate}
+ \theta H_{\theta}(x,w)\rho_r(x-w)\leq \rho_{\gamma}(x-w),
+\end{equation}
+where
+$$H_{\theta}(x,w)=\int_{\mathbb{R}^d}
     \left(
@@
     \right)^2
-    \frac{\rho_r(x-w)}{\rho_r * \eta(x)}
-\eta(dw) \\
-&\qquad
-=
-\rho_r * \eta(x)
-\int
-    \left(
-        \frac{\rho_r(y-w)}{\rho_r(x-w)}
-        -
-        1
-    \right)^2
-    \rho_r(x-w)
-\eta(dw) .
-\end{align}
-
-Now, we don't mind having the $\rho_r * \eta(x)$ term,
-so we'd like to bound the remaining bit by $\rho_\gamma * \eta(x)$.
-We'll now bring in the integral over $y$ and use Fubini, so that
-\begin{align}
-&\int \theta
-\int
-    \left(
-        \frac{\rho_r(y-w)}{\rho_r(x-w)}
-        -
-        1
-    \right)^2
-    \rho_r(x-w)
-\eta(dw)
-q_\theta(x, dy) \\
-&\qquad
-=
-\int \theta H_\theta(x, w) \rho_r(x-w) \eta(dw) ,
-\end{align}
-if we define
-\begin{align}
-H_\theta(x, w)
-:=
-\int
-    \left(
-        \frac{\rho_r(y-w)}{\rho_r(x-w)}
-        -
-        1
-    \right)^2
-q_\theta(x, dy) .
-\end{align}
-So, it only remains to bound $\theta H_\theta (w, x) \rho_r(x-w) $ by $\rho_\gamma(x - w)$.
-
-Now, let's assume that $\rho$ and $q$ are all Gaussian;
-to avoid difficulties with notation,
-define  $p_t(x) = \exp(-x^2 / 2t) / (2 \pi t)^{d/2}$
-to be the heat kernel,
-so that $\rho_r(x) = p_{\epsilon_r^2}(x)$
-and $q_\theta(x) = p_{1/\theta}(x)$.
+q_{\theta}(x,dy).$$
+\end{lemma}
+\begin{proof}
+
 Writing out $H$,
@@
             \left\{
-                (y - w)^2 - (x - w)^2
+                ||y - w||^2 - ||x - w||^2
             \right\}
@@
     \frac{
-        e^{-\theta(y - x)^2 / 2}
+        e^{-\theta (y - x-\meanq)^{T}\covq^{-1}(y - x-\meanq)  / 2}
     }{
-        (2 \pi / \theta)^{d/2}
+        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
     }
-dy .
+dy.
 \end{align}
-
-We'll just multiply this out and evaluate it directly,
-using the fact that
+Writing $z=y-x-\meanq$, we have that 
+\begin{equation}
+\begin{aligned}
+||y - w||^2 - ||x - w||^2 
+=& ||y||^2-||x||^2 -2\langle y-x, w\rangle \\
+=&||x+z+ \meanq||^2-||x||^2-2 \langle z+ \meanq, w\rangle\\
+=&2\langle x, z+ \meanq \rangle + ||z+ \meanq||^2-2 \langle z+ \meanq, w\rangle \\
+=& 2 \langle x-w, z+ \meanq \rangle + ||z+ \meanq||^2\\
+=& 2\langle x-w+ \meanq,\meanq \rangle + 2\langle x-w+ \meanq, z \rangle +||z||^2
+\end{aligned}
+\end{equation}
+As a result, we have 
 \begin{align}
-&
-\int e^{-a z - b z^2 / 2} \frac{e^{-\theta z^2 / 2}}{(2 \pi / \theta)^{d/2}} dz
-\\ &\qquad
-=
-\left(
-    \frac{ \theta }{ \theta + b }
-\right)^{d/2}
-\int e^{-a z} \frac{e^{-(\theta + b) z^2 / 2}}{(2 \pi / (\theta + b))^{d/2}} dz
-\\ &\qquad
-= \label{eqn:mgf}
-\left(
-    \frac{ \theta }{ \theta + b }
-\right)^{d/2}
-\exp\left( \frac{ a^2 }{ 2 (\theta + b) } \right) ,
-\end{align}
-(since $Z \sim \text{Normal}(0, \sigma^2)$ then $\IE[e^{tZ}] = \exp(\sigma^2 t^2 / 2)$).
-
-Let $z = y - x$ and note that the polynomial in the exponent inside the definition of $H$ is
-\begin{align}
-    (y-w)^2 - (x-w)^2
-    &=
-    (y - x)(y + x - 2w) \\
-    &=
-    z (z + 2x - 2w) ,
-\end{align}
-and so
-\begin{align}
-&
+H_\theta(x, w)
+=&
+\int
     \left(
         \exp\left(
-        \frac{1}{2\epsilon_r^2}
+            - \frac{1}{2\epsilon_r^2}
             \left\{
-            (y - w)^2 - (x - w)^2
+                2 \langle x-w, z+ \meanq \rangle + ||z+ \meanq||^2
             \right\}
@@
         1
-\right)^2 \\
-&\qquad
-= \label{eqn:H_form}
+    \right)^2
+    \frac{
+        e^{-\theta z^{T}\covq^{-1}z  / 2}
+    }{
+        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
+    }
+dz\\
+=&\exp\left(-\frac{2}{\epsilon_r^2}\langle x-w+ \meanq,\meanq \rangle \right)\\
+& \times \int
+        \frac{
         \exp\left(
-        - \frac{1}{\epsilon_r^2}
-        \left\{
-            z^2 + z (2x - 2w)
-        \right\}
+            - \frac{2}{\epsilon_r^2} \langle x-w+ \meanq, z \rangle
+            - \frac{1}{\epsilon_r^2} ||z||^2
             \right)
-    - 2 \exp\left(
-        - \frac{1}{2\epsilon_r^2}
-        \left\{
-            z^2 + z (2x - 2w)
-        \right\}
-    \right)
-    + 1 .
+            e^{-\theta z^{T}\covq^{-1}z  / 2}
+    }{
+        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
+    }
+dz\\ \label{eq: Second moment term matrix calculation}
+&-2\exp\left(-\frac{1}{\epsilon_r^2}\langle x-w+ \meanq,\meanq \rangle \right)\\
+& \qquad \qquad \times     \int
+    \frac{ \exp\left(
+             -\frac{1}{\epsilon_r^2}\langle x-w+ \meanq, z \rangle
+              -\frac{1}{2\epsilon_r^2} ||z||^2
+            \right)e^{-\theta z^{T}\covq^{-1}z  / 2}
+        }{
+        (2 \pi/ \theta)^{d/2} |\covq|^{1/2} \label{eq: first moment term matrix calculation}
+    }
+dz\\
+&+1.
 \end{align}
-So, for the first term in $H$ we use \eqref{eqn:mgf} with
-$a = 2 (x-w) / \epsilon_r^2$ and $b = 2 / \epsilon_r^2$,
-while for the second these are each divided by 2.
-So,
-\begin{align}
-H_\theta(x, w)
-&=
+We now consider the integral of the form 
+\begin{equation}
+\int \exp(v^{T}z-C||z||^2) \frac{
+        e^{-\theta z^{T}\covq^{-1}z  / 2}
+    }{
+        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
+    }
+dz   
+\end{equation}
+for $v \in \mathbb{R}^d$ and $C>0$. 
+We have 
+\begin{equation}
+\begin{aligned}
+&\int \exp(v^{T}z-C||z||^2) \frac{
+        e^{-\theta z^{T}\covq^{-1}z  / 2}
+    }{
+        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
+    }
+dz\\
+=&\frac{1}{|\covq|^{1/2}|  |\covq^{-1}(I+2C\covq/\theta )|^{1/2}  }\int \exp(v^{T}z) \frac{
+        e^{-\theta z^{T}\covq^{-1}(I+2C\covq/\theta )z  / 2}
+    }{
+        (2 \pi/ \theta)^{d/2}|\covq^{-1}(I+2C\covq/\theta )|^{-1/2} 
+    }
+dz\\
+=& \frac{1}{|I+2C\covq/\theta |^{1/2}} \mathbb{E}_{Z}[\exp (v^{T}Z)]\\
+=&\frac{1}{|I+2C\covq/\theta |^{1/2}}
+\exp 
 \left(
-    \frac{ \theta }{ \theta + 2/\epsilon_r^2 }
-\right)^{d/2}
-\exp\left( \frac{ 4 (x-w)^2 }{ 2 \epsilon_r^2 (\theta \epsilon_r^2 + 2) } \right)
-- 2
+\frac{1}{2}v^{T}\covq/\theta(I+2C\covq/\theta )^{-1}v
+\right),
+\end{aligned}
+\end{equation}
+where $Z \sim N(0, \covq/\theta \times (I+2C\covq/\theta )^{-1})$.
+
+Now writing $v=\frac{2}{\epsilon_r^2}( w-x-\meanq)$
+and $C=\frac{1}{\epsilon_r^2}$,
+we have the expression in Equation
+\eqref{eq: Second moment term matrix calculation} is 
+$$\frac{1}{|I+2\covq/(\epsilon_r^2\theta) |^{1/2}}
+\exp 
 \left(
-    \frac{ \theta }{ \theta + 1/\epsilon_r^2 }
-\right)^{d/2}
-\exp\left( \frac{ (x-w)^2 }{ 2 \epsilon_r^2 (\theta \epsilon_r^2 + 1) } \right)
-+ 1 \\
-&=
+\frac{2}{\epsilon_r^4}( w-x-\meanq)^{T}\covq/\theta\left(I+2\covq/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
+\right).$$
+Similarly, writing $v=\frac{1}{\epsilon_r^2}( w-x-\meanq)$
+and $C=\frac{1}{2\epsilon_r^2}$,
+we have the expression in Equation
+\eqref{eq: first moment term matrix calculation} is 
+$$\frac{1}{|I+\covq/(\epsilon_r^2\theta) |^{1/2}}
+\exp 
 \left(
-    \frac{ 1 }{ 1 + 2/(\theta \epsilon_r^2) }
-\right)^{d/2}
-\exp\left( \frac{ 4 (x-w)^2 }{ 2 \epsilon_r^2 \theta (\epsilon_r^2 + 2/\theta) } \right)
-- 2
+\frac{1}{2\epsilon_r^4}( w-x-\meanq)^{T}\covq\left(I+\covq/\theta/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
+\right).$$
+As a result, we have 
+\begin{align*}
+&H_{\theta}(x,w)\\
+=& \frac{1}{|I+2\covq/(\epsilon_r^2\theta) |^{1/2}}
+\exp 
 \left(
-    \frac{ 1 }{ 1 + 1/(\theta \epsilon_r^2) }
-\right)^{d/2}
-\exp\left( \frac{ (x-w)^2 }{ 2 \epsilon_r^2 \theta (\epsilon_r^2 + 1/\theta) } \right)
-+ 1 .
+\frac{2}{\epsilon_r^4}( w-x-\meanq)^{T}\covq/\theta\left(I+2\covq/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
+\right)\\
+&-2\frac{1}{|I+\covq/(\epsilon_r^2\theta) |^{1/2}}
+\exp 
+\left(
+\frac{1}{2\epsilon_r^4}( w-x-\meanq)^{T}\covq/\theta\left(I+\covq/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
+\right)\\
+&+1.
+\end{align*}
+If we write $F(1/\theta)=H_{\theta}(x,w)$, i.e.
+\begin{align*}
+&F(s)\\
+=& \frac{1}{|I+2/\epsilon_r^2 \covq s |^{1/2}}
+\exp 
+\left(
+\frac{2}{\epsilon_r^4}( w-x-\meanq)^{T}\covq s \left(I+2/\epsilon_r^2 \covq s\right)^{-1}( w-x-\meanq)
+\right)\\
+&-2\frac{1}{|I+2/\epsilon_r^2 \covq s |^{1/2}}
+\exp 
+\left(
+\frac{1}{2\epsilon_r^4}( w-x-\meanq)^{T}\covq s \left(I+2/\epsilon_r^2 \covq s\right)^{-1}( w-x-\meanq)
+\right)\\
+&+1\\
+&=G_1(s)+2G_2(s)+1
+\end{align*}
+we can check that $F(0)=0$.
+As a result, 
+$$\theta H_{\theta}(x,w)\rho_r(x-w)= \theta F(1/\theta)\rho_r(x-w)=F'(s)\rho_r(x-w),$$
+for some $s \in [0, 1/\theta]$.
+
+In Equation \eqref{eq: gamma-r convolution comparison}, we have established that 
+$\rho_r(x-w) / \rho_\gamma(x-w) = C' \exp(-K (x-w)^2 / 2)$
+with $K = \frac{1}{\epsilon_r^2} - \frac{1}{\epsilon_\gamma^2}$.
+Therefore it suffices to show that for all $x,w \in \mathbb{R}^d$ and $s \in [0, 1/\theta]$, 
+\begin{align}\label{eqn:goal3}
+    F'(s) \exp\left(-A (x-w)^2 \right) \le C .
 \end{align}
 
-If we define $f(u)$ so that $f(1/\theta) = H_\theta(x, w)$,
-then notice since $f(0) = 0$,
-that $\theta f(1/\theta) = f'(u)$ for some $0 \le u \le 1/\theta$,
-by the intermediate value theorem.
-Let's work out what $f'(u)$ is.
-First note that if
-\begin{align}
-    g(u)
-    &=
-    \left( \frac{ 1 }{ 1 + a u } \right)^{d/2}
-    \exp\left(
-    \frac{
-    b u
-    }{
-    1 + c u
-    }
-    \right)
-\end{align}
-then
-\begin{align}
-    g'(u)
-    &=
-\left\{
-    \frac{ - ad/2 }{ 1 + a u }
-    +
-    \frac{b}{1 + cu}
-    -
-    \frac{bcu}{(1+cu)^2}
-\right\}
-    \left( \frac{ 1 }{ 1 + a u } \right)^{d/2}
-    \exp\left(
-    \frac{
-    b u
-    }{
-    1 + c u
-    }
-    \right) \\
-    &=
-\left\{
-    \frac{ - ad/2 }{ 1 + a u }
-    +
-    \frac{b}{(1 + cu)^2}
-\right\}
-    \left( \frac{ 1 }{ 1 + a u } \right)^{d/2}
-    \exp\left(
-    \frac{
-    b u
-    }{
-    1 + c u
-    }
-    \right) .
-\end{align}
-If, as will be the case, all of $a$, $b$, $c$, and $u$ are nonnegative, then
-\begin{align}
-|g'(u)|
-&\le
- (b + ad/2) \exp(bu) .   
-\end{align}
-Now, note that $f'(u) = g_1'(u) - 2 g_2'(u)$, where $g_1$ and $g_2$ are of this form
-with constants $a_1, b_1, c_1$ and $a_2, b_2, c_2$ respectively.
-
-Again, we'd like to show that for some $C$,
-\begin{align}
-    \theta H_\theta(x, w) \rho_r(x-w) \le C \rho_\gamma(x-w)  .
-\end{align}
-We will have $\rho_\gamma = p_{\epsilon_\gamma^2}$ with $\epsilon_\gamma > \epsilon_r$,
-so that $\rho_r(x-w) / \rho_\gamma(x-w) = C' \exp(-A (x-w)^2 / 2)$
-with $A = \frac{1}{\epsilon_r^2} - \frac{1}{\epsilon_\gamma^2}$.
-Putting this together,
-we will have shown \eqref{eqn:goal2}
-if we can show for some $\theta$ that
-for all $x$ and $w$ and all $u \le 1/\theta$,
-\begin{align} \label{eqn:goal3}
-    f'(u) \exp\left(-A (x-w)^2 \right) \le C .
-\end{align}
-Since $f'(u) = g_1'(u) - 2 g_2'(u)$ we need only prove this bound
-for both $g_1'(u)$ and $g_2'(u)$.
-Referring to \eqref{eqn:H_form}
-we see that $b_1 = 2(x-w)^2 / \epsilon_r^4$
-and that $a$ and $c$ only depend on $\epsilon_r$,
-\begin{align}
-|g_1'(u)|
-&\le
-\left\{
-    C_1 + C_2 (x-w)^2
-\right\}
-\exp\left(
-    \frac{ 2 (x - w)^2 }{ \epsilon_r^4 } u
-\right)  \\
-&\le
-\left\{
-    C_1 + C_2 (x-w)^2
-\right\}
-\exp\left(
-    \frac{ 2 (x - w)^2 }{ \epsilon_r^4 \theta }
-\right) 
-\end{align}
-where $C_1$ and $C_2$ are constants that just depend on $\epsilon_r$.
-Therefore, equation \eqref{eqn:goal3} is satisfied
-if the multiplier of $(x-w)^2$ in the last equation is less than $A$,
-i.e., if
-\begin{align}
-\theta 
-> 
-\frac{ 4 }{ A \epsilon_r^4 }
-=
-\frac{ 4 / \epsilon_r^2 }{1 - \epsilon_r^2 / \epsilon_\gamma^2 } .
-\end{align}
-This is possible if $\epsilon_r < \epsilon_\gamma$.
+We consider how to differentiate function $G$ of the form 
+$$G(s):=\frac{1}{|I+As|^{1/2}}\exp(v^{T}Bs(I+Cs)^{-1}v),$$
+where $A,B,C$ are matrices with non-negative entries and $I$ is the identity matrix.
+
+Since 
+\begin{equation}
+\begin{aligned}
+G'(s)=& - \frac{|A|}{2|I+As|^{3/2}}\exp(v^{T}Bs(I+Cs)^{-1}v)\\
+      & + \frac{1}{|I+As|^{1/2}}\exp(v^{T}Bs(I+Cs)^{-1}v)\\
+      & \qquad \times \left\{ v^{T}B(I+Cs)^{-1}v
+                            - sv^{T}BC(I+Cs)^{-2}v
+                    \right\}\\
+      &=\left(- \frac{|A|}{2|I+As|}+v^{T}B(I+Cs)^{-2}v
+        \right)\\
+      & \qquad \times
+        \frac{1}{|I+As|^{1/2}}\exp(v^{T}Bs(I+Cs)^{-1}v),
+\end{aligned}
+\end{equation}
+using non-negativity of $A,B,C$ we have
+\begin{equation}
+\label{eq: bounds on G'}
+|G'(s)| \leq (|A|+||B||_{2}||v||_2^2)G(s).    
+\end{equation}
+As a result, we have that 
+\begin{equation}
+\label{eq: bounds on G}
+G(s) \leq K e^{|A|+||B||_{2}||v||_2^2)s}, ~~   G'(s)(|A|+||B||_{2}||v||_2^2)K e^{|A|+||B||_{2}||v||_2^2)s}.  
+\end{equation}
+
+Finally note that, 
+$$F'(s) \leq G_1'(s)+2G_2'(s),$$
+where 
+$$A_1= 2\epsilon_r^{-2} \covq, ~ v_1=\epsilon_r^{-2}(w-x-\meanq), ~B_1 = 2\covq, ~C_1=2\epsilon_r^{-2} \covq,$$
+and 
+$$A_2= 2\epsilon_r^{-2} \covq, ~ v_2=\epsilon_r^{-2}(w-x-\meanq), ~B_2 = \covq/2, ~C_2=2\epsilon_r^{-2} \covq,$$
+Substituting these quantities on Equation \eqref{eq: bounds on G} shows that Equation \eqref{eqn:goal3} is satisfied as long as $\epsilon_r < \epsilon_\gamma$.
+
+\end{proof}
 

### 2022-05-02 forwards-and-backwards.tex
Update on Overleaf.

@@
 \newpage
+
+\comment{TODO: talk about $N \to \infty$ rather than $\theta \to \infty$.}
 
@@
 $$
+\comment{TODO: explain this more.}
 Happily, we are interested in the case when $\eta$ has a density,
@@
 \frac{
-    \gamma(x, \eta_t) q_\theta(x, dy) r(y, \eta_t) \varphi_t(x)
+    \gamma(x, \eta_t) r(y, \eta_t) \varphi_t(x)
 }{
@@
     &\qquad \to
-        \DG^*(fg)(x) - f(x) \DG^* g(x) . 
+        \DG^*(fg)(y) - f(y) \DG^* g(y) . 
 \end{align*}
@@
 When taking the limit, we will set $\lambda = N$.
-\comment{Should we just use $N$ instead of $\lambda$? Or vice-versa?}
+\comment{Should we just use $N$ instead of $\lambda$? Or vice-versa? Change to $N$ but comment that when comparing ot other papers set $\lambda=N$.}
 We will still encode the process embellished by these levels
@@
 \begin{align*}
-    \eta_t = \sum_{a : \tau_a > t \;\&\; U_a(t) < \lambda} \delta_{X_a(t)}
+    \eta_t = \frac{1}{\lambda} \sum_{a : \tau_a > t \;\&\; U_a(t) < \lambda} \delta_{X_a(t)}
     \qquad \text{and} \qquad
@@
 \begin{align*}
-    \eta_t = \sum_{a : \tau_a > t \;\&\; U_a(t) < \lambda} \delta_{X_a(t)}
+    \eta_t = \lim_{\lambda \to \infty} \frac{1}{\lambda} \sum_{a : \tau_a > t \;\&\; U_a(t) < \lambda} \delta_{X_a(t)}
     \qquad \text{and} \qquad
-    \lp = \sum_{a : \tau_a > t \;\&\; U_a(t) < \lambda} \delta_{(X_a(t), U_a(t))} .
+    \lp = \sum_{a : \tau_a > t} \delta_{(X_a(t), U_a(t))} .
 \end{align*}

### 2022-05-03 figures/make_plots.sh
.

@@ -16,3 +16,15 @@ do
     ../lineage_plotting/plot_density.py fkpp_123.trees 3
     popd
 done
+
+# smooth and patchy expanding wave lineages
+for DIR in ex2a ex2b
+do
+    pushd $DIR
+    if [ ! -e pme_123.trees ]
+    then
+        slim -s 123 ../pme.slim
+    fi
+    ../lineage_plotting/plot_1d_lineages.py pme_123.trees 3 1 3 3
+    popd
+done

### 2022-05-06 forwards-and-backwards.tex
Update on Overleaf.

@@
 
-\comment{TODO: talk about $N \to \infty$ rather than $\theta \to \infty$.}
+\comment{TODO: talk about $N \to \infty$ rather than $N \to \infty$.}
 
@@
     \to \DG f(x) 
-        \qquad \text{as } \theta \to \infty .
+        \qquad \text{as } N \to \infty .
     \end{align}
@@
 \begin{align*}
-    \lim_{\theta \to \infty}
+    \lim_{N \to \infty}
     \theta \int (f(y) - f(x)) q_\theta^\mathfrak{m}(x, dy)
@@
     be as defined in Definition \ref{def:model_setup}
-    and assume that as $\theta \to \infty$, $N \to \infty$
+    and assume that as $N \to \infty$, $N \to \infty$
     in such a way that $\theta/N \to \alpha$.
@@
     $(\eta^\theta_t)_{t \geq 0}$
-    converges along subsequences in distribution as $\theta \to \infty$
+    converges along subsequences in distribution as $N \to \infty$
     to a measure-valued process $(\eta_t)_{t \geq 0}$
@@
         \big\langle
-            \gamma\left( x, \smooth{\gamma} \eta_{s}(x) \right)
-            r\left(x, \smooth{r} \eta_{s}(x) \right)
+            \left(\gamma\left( x,  \eta_{s} \right)
+            r\left(x, \eta_{s} \right)+\mu\left(x, \eta_{s} \right)\right)
             f^2(x),
@@
     then $(\eta^\theta(t))_{t \ge 0}$ converges to that solution
-    as $\theta \to \infty$.
+    as $N \to \infty$.
     \comment{
@@
 Theorem \ref{thm:nonlocal_convergence} combined with Proposition \ref{prop:nonlocal_to_local}
-imply that we can take the $\theta \to \infty$ limit
+imply that we can take the $N \to \infty$ limit
 followed by $\epsilon \to 0$
@@
     be as defined in Definition \ref{def:model_setup}
-    and assume that as $\theta \to \infty$, $N \to \infty$
+    and assume that as $N \to \infty$, $N \to \infty$
     and $\epsilon_r < \epsilon_\gamma = \epsilon_F = \epsilon \to 0$
@@
 if the remaining parameters ($r$, $\gamma$, and $F$)
-depended on $\theta$, but converged as $\theta \to \infty$.
+depended on $\theta$, but converged as $N \to \infty$.
 
@@
     \langle
-        \mu_\theta(x,\eta)\frac{1}{N^2}f^2(x) 
+        \mu(x,\eta)\frac{1}{N^2}f^2(x) 
     ,\eta(dx)\rangle
@@
 $$\frac{2}{\alpha}\int_0^t\langle f^2(x) 
-\gamma(x,\Xi_s)r(x,\Xi_s),\Xi_s(dx)\rangle ds.$$
+(\gamma(x,\Xi_s)r(x,\Xi_s)+\mu(x,\Xi_s)),\Xi_s(dx)\rangle ds.$$
 
@@
 Referring back to Definition~\ref{def:dispersal_generator},
-it is not too hard to show that as $\theta \to \infty$,
+it is not too hard to show that as $N \to \infty$,
 \begin{align*}
@@
 &\to
-    \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta) \qquad \text{as } \theta \to \infty .
+    \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta) \qquad \text{as } N \to \infty .
 \end{split}
@@
 and spatial convergence of $(\eta^{\theta}_t)_{t \geq 0}$
-as $\theta \to \infty$.
+as $N \to \infty$.
 
@@
 \end{align}
-for some $u \in [0, 1/\theta]$ by Intermediate Value Theorem. We have therefore established our bound as $F(s)$ has bounded derivative in a neighbourhood around $0$.
+for some $u \in [0, 1/\theta]$ by Mean Value Theorem. We have therefore established our bound as $F(s)$ has bounded derivative in a neighbourhood around $0$.
 
@@
 \begin{equation}
-\limsup_{\theta \to \infty}
+\limsup_{N \to \infty}
     \mathbb{P}\left[\sup_{s \in [0,T]}
@@
 \begin{equation}
-\limsup_{\theta \to \infty}\mathbb{P}\left[\sup_{s \in [0,T]}\langle 1 ,\eta^{\theta}_{s}\rangle \geq K\right] \leq \frac{C(T)}{K}    
+\limsup_{N \to \infty}\mathbb{P}\left[\sup_{s \in [0,T]}\langle 1 ,\eta^{\theta}_{s}\rangle \geq K\right] \leq \frac{C(T)}{K}    
 \end{equation}
@@
 \end{equation}
-As $\theta / N \to \alpha$ as $\theta \to \infty$,
+As $\theta / N \to \alpha$ as $N \to \infty$,
 there exists some $K'>0$ such that 
@@
 
-Before we prove convergence, we define our limit $(\eta^{\infty}(t))_{t>0}$ as a solution to a Martingale Problem with generator $\Pgen$.
+Before we prove convergence, we define our limit $(\eta^{\infty}(t))_{t>0}$ as a solution to a Martingale Problem with generator $\Pgen^{\infty}$.
 
@@
 \begin{equation}
+    \label{eq: Limit Generator Definition}
 \begin{aligned}
@@
                    \right\}\\
-                &+ \frac{1}{2}F''(\langle f, \eta \rangle)
+                &+ \frac{\alpha}{2} F''(\langle f, \eta \rangle)
                   \times \left\{
-                  \alpha \big\langle
-                    \gamma\left( x, \smooth{\gamma} \eta(x) \right)
-                    r\left(x, \smooth{r} \eta(x) \right)
+                  \big\langle
+                    \left(\gamma\left( x, \eta \right)
+                    r\left(x,\eta \right)
+                    +\mu\left(x,\eta \right)
+                    \right)
                     f^2(x),
@@
 -\int_{0}^{t}\Pgen^{\infty}F_f(\eta^{\infty}_s)ds$$
-is a martingale.
+is a martingale, with initial condition distributed as a Poisson measure with mean measure $\eta_0$.
 \end{definition}
+
+In a similar manner,
+we may also define our pre-limit
+$(\eta^{N}(t))_{t>0}$ as a solution
+to a Martingale Problem
+with generator $\Pgen^{N}$.
+
+\begin{definition}
+    \label{def: MP definition of pre-limit}
+Let $F \in \mathcal{C}^{2}(\mathbb{R})$ and $f \in \mathcal{C}_{0}(\mathbb{R}^d)$.
+We define $\Pgen^N$ to be a generator
+acting on test functions of the form
+$F_f(\eta):=F (\langle f, \eta \rangle)$
+such that 
+\begin{equation}
+\begin{aligned}
+\Pgen^{N} F_f(\eta):=& \int_{\mathbb{R}^d} \theta\gamma(x, \eta) \left\{\int_{\mathbb{R}^d} \left\{F(\langle f, \eta \rangle + f(y)/N )-F(\langle f, \eta \rangle )\right\}r(y, \eta)q_{\theta}(x,dy)\right\}N\eta(dx)\\
+&+\int_{\mathbb{R}^d} \theta \mu(x, \eta) \left\{F(\langle f, \eta \rangle - f(x)/N )-F(\langle f, \eta \rangle )\right\}N\eta(dx).
+\end{aligned}    
+\end{equation}
+In this case, our pre-limit model $(\eta^{N}(t))_{t \geq 0}$ is the solution to the Martingale Problem $(\Pgen^{N}, \eta_0)$, i.e. 
+for all $F \in \mathcal{C}^{2}(\mathbb{R})$
+and $f \in \mathcal{C}_{0}(\mathbb{R}^d)$,
+$$M_t:=F_f(\eta^{N}_t)-F_f(\eta_0)
+-\int_{0}^{t}\Pgen^{N}F_f(\eta^{N}_s)ds$$
+is a martingale, and the initial condition is distributed as a Poisson measure with mean measure $\eta_0$.
+\end{definition}
+
 \begin{remark}
-Taking $F(x)=x$ and $F(x)=x^2$, we can recover Equation \eqref{eqn:mgale_problem} and \eqref{eqn:mgale_variation}.
+Taking $F(x)=x$ and $F(x)=x^2$, we can recover Equation \eqref{eqn:mgale_problem} and \eqref{eqn:mgale_variation} for the limit.
+Similarly, we can recover
+Definition \ref{Def: Rescaled Models},
+an equivalent characterisation
+of our pre-limit model.
 \end{remark}
@@
 \begin{lemma}[Convergence of generators for the population process]
-As $\theta \to \infty$,
-$(\eta^{\theta}_t)_{t \geq 0}$ converges in $\mathcal{D}_{[0,\infty)}(\mathcal{M}_f(\mathbb{R}^d))$
-to $(\eta^{\infty}(t))_{t \geq 0}$.
+As $N \to \infty$,
+$(\eta^{N}_t)_{t \geq 0}$ converges in $\mathcal{D}_{[0,\infty)}(\mathcal{M}_f(\mathbb{R}^d))$
+to $(\eta^{N}(t))_{t \geq 0}$.
 \end{lemma}
@@
     \label{eq: Convergence Condition}
-\lim_{\theta \to \infty}
+\lim_{N \to \infty}
 \mathbb{E}\left[
 \left(
-F_f(\eta^{\theta}_{t+\tau})-F_f(\eta^{\theta}_t)
--\int_{t}^{t+\tau}\Pgen^{\infty}F_f(\eta^{\theta}_s)ds
+F_f(\eta^{N}_{t+\tau})-F_f(\eta^{N}_t)
+-\int_{t}^{t+\tau}\Pgen^{\infty}F_f(\eta^{N}_s)ds
 \right)
@@
 To prove this,
-we apply Taylor's series expansion
-and make use of the Martingale Problem characterisation
-of $\eta^{\theta}_T$.
-We have
-\begin{equation}
-\begin{aligned}
-&\mathbb{E}\left[F_f(\eta^{\theta}_{t+\tau})-F_f(\eta^{\theta}_t)\bigg| \mathcal{F}_t \right]\\
-=& F'(\langle f, \eta^{\theta}_t \rangle )
-\mathbb{E}\left[
-                \langle f, \eta^{\theta}_{t+\tau}\rangle
-                    -\langle f, \eta^{\theta}_t\rangle 
-                    \bigg| \mathcal{F}_t
-         \right]
-+\frac{1}{2}F''(\langle f, \eta^{\theta}_t \rangle )
+we make use of the Martingale Problem characterisation
+of $(\eta^{N}_t)_{t \geq 0}$.
+From Definition \ref{def: MP definition of pre-limit},
+we can apply Tower Law
+and obtain that
+\begin{equation}
+    \label{eq: Prelimit MP Application}
+\lim_{N \to \infty}
 \mathbb{E}\left[
 \left(
-                    \langle f, \eta^{\theta}_{t+\tau}\rangle -\langle f, \eta^{\theta}_t\rangle
-                \right)^2
-                \bigg| \mathcal{F}_t
-        \right]\\
-&+\frac{1}{6}F'''(\langle f, \eta^{\theta}_{t+\tau'}\rangle)\mathbb{E}\left[
-                \left(
-                    \langle f, \eta^{\theta}_{t+\tau}\rangle -\langle f, \eta^{\theta}_t\rangle
-                \right)^3
-                \bigg| \mathcal{F}_t
-        \right]\\
-=& F'(\langle f, \eta^{\theta}_t \rangle )\\
-& \times  \int_{t}^{t+\tau}\bigg\{
-        \int\left(   \int \theta
-     \left(
-        f(z)r\big(z,\rho_{r}*\eta^{\theta}_{s}(z)\big)
-            -f(x)r\big(x,\rho_{r}*\eta^{\theta}_{s}(x)\big)
+F_f(\eta^{N}_{t+\tau})-F_f(\eta^{N}_t)
+-\int_{t}^{t+\tau}\Pgen^{N}F_f(\eta^{N}_s)ds
 \right)
-                    q_\theta(x,dz)\right)
-        \\ & \qquad \qquad \qquad \qquad {} \times
-                            \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
-                            \eta^{\theta}_{s}(dx)
-     \\ & \qquad \qquad {} +\int 
-     f(x)F\big(x,\rho_{F}*\eta^{\theta}_{s}(x)\big)
-     \eta^{\theta}_{s}(dx)
-    \bigg\} ds\\
-&+\frac{1}{2}F''(\langle f, \eta^{\theta}_t \rangle )\\
-&\quad \times \frac{\theta}{N}\int_{t}^{t+\tau}\bigg\{
-\langle \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
-\int f^2(y)r\big(y,\rho_{r}*\eta^{\theta}_{s}(y)\big)q_\theta(x,dy) 
-,\eta^{\theta}_{s}(dx)\rangle\\
-& \qquad \qquad +\langle \mu\big(x,\eta^{\theta}_{s}\big)f^2(x) 
-,\eta^{\theta}_{s}(dx)\rangle \bigg\}ds\\
-&+\frac{1}{6}F^{(3)}(\langle f, \eta^{\theta}_{t+\tau'}\rangle)\mathbb{E}\left[
-                \left(
-                    \langle f, \eta^{\theta}_{t+\tau}\rangle -\langle f, \eta^{\theta}_t\rangle
-                \right)^3
-                \bigg| \mathcal{F}_t
-        \right]
+\prod_{i=1}^{k}\langle h_i,\eta^{\theta}_{t_i} \rangle
+\right]=0
+\end{equation}
+for all $k\geq 0$, $0\leq t_1<t_2<...,t_k \leq t < t+\tau$,
+and $h_1,...,h_k \in \mathcal{C}_{0}(\mathbb{R}^d)$.
+
+Therefore, it suffices to show that 
+\begin{equation}
+    \label{eq: Convergence of Spatial Generator}
+\lim_{N \to \infty}
+\mathbb{E}\left[
+\int_{t}^{t+\tau}
+\left|
+\Pgen^{N}F_f(\eta^{N}_s)
+-\Pgen^{\infty}F_f(\eta^{N}_s)
+\right|
+ds
+\times 
+\prod_{i=1}^{k}\langle h_i,\eta^{\theta}_{t_i} \rangle
+\right]=0
+\end{equation}
+We apply Taylor Expansion
+around the term $F(\langle f, \eta \rangle )$
+up to third order.
+This gives
+\begin{equation}
+    \label{eq: Taylor Expansion calculations i}
+\begin{aligned}
+&F(\langle f, \eta \rangle + f(y)/N )-F(\langle f, \eta \rangle )\\
+=& F'(\langle f, \eta \rangle ) \frac{f(y)}{N}
++\frac{1}{2}F''(\langle f, \eta \rangle ) \frac{f^2(y)}{N^2}
++\frac{1}{6}F'''(w ) \frac{f^3(y)}{N^3}
 \end{aligned}
 \end{equation}
-for some $s' \in [0,s]$.
-
-We first show that 
-$$\lim_{\theta \to \infty}\mathbb{E}\left[
-                \left|
-                    \langle f, \eta^{\theta}_{t+\tau}\rangle -\langle f, \eta^{\theta}_t\rangle
-                \right|^3
-                \bigg| \mathcal{F}_t
-        \right] \to 0.$$
-Since the total number of births and deaths
-between $[t,t+\tau]$ is given by Poisson point processes
-with rates $\theta \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)$
-and $\theta \mu\big(x,\eta^{\theta}_{s}\big)$
-respectively,
-and each birth and death events contribute
-an increment of order $\mathcal{O}(1/N^3)$,
-we have that
+for some $w \in [\langle f, \eta \rangle, \langle f, \eta \rangle+ ||f||/N]$.
+Similarly,
+\begin{equation}
+    \label{eq: Taylor Expansion calculations ii}
+\begin{aligned}
+&F(\langle f, \eta \rangle - f(x)/N )-F(\langle f, \eta \rangle )\\
+=& - F'(\langle f, \eta \rangle ) \frac{f(x)}{N}
++\frac{1}{2}F''(\langle f, \eta \rangle ) \frac{f^2(x)}{N^2}
+-\frac{1}{6}F'''(v ) \frac{f^3(x)}{N^3}
+\end{aligned}
+\end{equation}
+for some $v \in [\langle f, \eta \rangle - ||f||/N, \langle f, \eta \rangle ]$.
+
+We may now rewrite $\mathcal{P}^NF(\langle f, \eta \rangle)$ as 
+\small
+\begin{equation} 
+    \label{eq: Pre-Limit Generator Expanded}
+\begin{aligned}
+\Pgen^{N} F_f(\eta):=& F'(\langle f, \eta \rangle)\int_{\mathbb{R}^d}  \theta\left\{\int_{\mathbb{R}^d} \left\{f(y)\gamma(x, \eta) r(y,\eta) -f(x)\mu(x, \eta)\right\}q_{\theta}(x,dy)\right\}\eta(dx)\\
+&+\frac{1}{2}\frac{\theta}{N}F''(\langle f, \eta \rangle)\int_{\mathbb{R}^d} 
+ \left\{\gamma(x, \eta)\int_{\mathbb{R}^d} \left\{f^2(y) r(y,\eta) \right\}q_{\theta}(x,dy)+f^2(x)\mu(x, \eta)\right\}\eta(dx)\\
+&+\frac{1}{6}\frac{\theta}{N^2}\int_{\mathbb{R}^d}\left\{ 
+F'''(w) \left\{\gamma(x, \eta)\int_{\mathbb{R}^d} f^3(y) r(y,\eta) q_{\theta}(x,dy)\right\}-F'''(v)f^3(x)\mu(x, \eta)\right\}\eta(dx)
+\end{aligned}    
+\end{equation}
+\normalsize
+for some $w,v \in [\langle f,\eta \rangle - ||f||/N, \langle f,\eta \rangle + ||f||/N]$.
+
+As $N\to \infty$, 
+$\theta/N \to \alpha$, 
+$\theta/N^2 \to 0$,
+and 
+$$\int_{\mathbb{R}^d} f^m(y) r(y,\eta) q_{\theta}(x,dy) \to f^m(x)r(x, \eta)$$
+for $m=2,3$,
+the third term in Equation \eqref{eq: Pre-Limit Generator Expanded} vanishes
+while the second term converges to
+that of Equation \eqref{eq: Limit Generator Definition}.
+
+Finally, by Equation \eqref{mean measure},
+\eqref{eqn:rewritten mean measure}, \eqref{eqn:near_critical} and
+\eqref{limit of mean measure equation},
+we have 
 \begin{multline}
-\lim_{\theta \to \infty}\mathbb{E}\left[
-                \left|
-                    \langle f, \eta^{\theta}_{t+\tau}\rangle -\langle f, \eta^{\theta}_t\rangle
-                \right|^3
-                \bigg| \mathcal{F}_t
-        \right] \\
-\leq ||f||_{\theta} \frac{\theta}{N^2}\int_{0}^{t}\left\langle\gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)+\mu\big(x,\eta^{\theta}_{s}\big), \eta^{\theta}_s(dx)\right\rangle ds \to 0
+ \theta\left\{\int_{\mathbb{R}^d} \left\{f(y)\gamma(x, \eta) r(y,\eta) -f(x)\mu(x, \eta)\right\}q_{\theta}(x,dy)\right\}
+ \\
+\to \gamma(x, \eta)                           \mathcal{B}\left(
+                            f(\cdot) r(\cdot, \eta)
+                            \right)(x)
+                    +
+                    f(x)
+                        F(x, \eta),
 \end{multline}
-as $\theta \to \infty$.
+so comparing terms we have
+\begin{equation}
+\lim_{N\to \infty} |\mathcal{P}^{N}F\langle f, \eta \rangle - \mathcal{P}^{\infty}F\langle f, \eta \rangle| \to 0,   
+\end{equation}
+and so by Dominated Convergence Theorem,
+we establish Equation 
+\eqref{eq: Convergence of Spatial Generator}
+which concludes our proof.
 \end{proof}
@@
     &\qquad \to
-    \DG(gr)(x) - g(x) \DG r(x) \qquad \text{as }\theta \to \infty.
+    \DG(gr)(x) - g(x) \DG r(x) \qquad \text{as }N \to \infty.
 \end{align*}

### 2022-05-09 forwards-and-backwards.tex
edits 1

@@
 \newcommand{\concat}{\oplus}   % concatenation of labels
+\newcommand{\measures}{\mathcal{M}_F(\IR^d)} % finite measures on Rd
 
@@
 
-\plr{I have not edited the introduction yet! It's just a pile of words. Skip to the next section.}
-
-\todo[inline]{
-From Terence: Personally, I think the long discussion on porous medium equations distract readers from the main message of our paper - we demonstrated a way to trace genealogy and derive dynamics of ancestral lineage through lookdown construction.
-I would suggest trimming most of the discussion there and only leaving discussions relevant to ancestries and lineages.}
+\comment{I think the introduction covers a good set of things in a good order, it's just a bit long.}
+
+As one takes a journey, long or short, the landscape changes:
+forests thicken or thin or change their composition,
+springtime grasslands host intergrading mosaics of different types of flowers.
+The aim of this paper is to understand the implications of a broad class of mechanistic spatial models
+that might describe how such populations live, die, and reproduce:
+How does population density change across space and time?
+And, how might we learn about the underlying dynamics from genealogical or genetic data?
+We work with individual-based models of a single species in continuous space,
+where birth, death and establishment may all depend on spatial location
+as well as on local population density, allowing for stable populations through density-dependent feedback.
 
@@
 
-\subsection{More motivation, on lineages, to merge with the above}
-
+\comment{Need a transition or otherwise to merge this with the above.}
 The history of a natural population is often only accessible indirectly 
@@
 We retain linages through the rescaling process
-by means of a lookdown construction, which adds technical difficulty
-to an already difficult topic.
-Furthermore, convergence results for the lookdown process
-require convergence of the population process.
-So, we do not introduce the lookdown process until Section X.
-
-First, in section X, we describe the model and the main theorems (Theorems X and Y).
-Next, in section X, we discuss a few striking consequences of these results,
-namely, X Y and Z.
-In section X, we provide heuristic explanations
+by means of a lookdown construction.
+First, in section~\ref{sec: Model and main results},
+we describe the model and the main theorems
+(Theorems~\ref{thm:nonlocal_convergence}, \ref{thm:local_convergence}, and~\ref{thm:lineages}).
+Next, in Section~\ref{sec:applications}, we discuss a few striking consequences of these results,
+namely, X Y and Z \comment{TODO}.
+In section \ref{sec:heuristics}, we provide heuristic explanations
 of why the theorems ought to be true,
 and some key ideas behind them.
-In Section X we define and discuss the lookdown process that retains the levels.
-This is followed by the technical proofs in section X.
+In Section \ref{sec:lookdown} we define and discuss the lookdown process that retains the levels.
+This is followed by the technical proofs in section \ref{sec:proofs}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Notes to ourselves}
+\section*{Notes to ourselves}
 
@@
 of individuals living in continuous space.
-We shall suppose that we start with a population of
+We start with a population of
 $\bigO(N)$ individuals per unit area distributed in $\mathbb{R}^d$.
@@
 so the total number of individuals will also be $\bigO(N)$.
-We describe the state of the population at time $t$
-with a counting measure $X(t)$,
+The population changes in continuous time, and
+we describe the state of the population at time $t$ with a counting measure $X(t)$,
 which assigns one unit of mass to the location of each individual.
-Locations need not be unique, so some locations may have a mass of greater than 1.
-
-It will be simplest to think of the population as evolving in continuous time
-and giving birth to one offspring at a time.
+
 Population dynamics are controlled by three quantities,
-birth, establishment, and death,
-each of which can depend on spatial location and local population density.
+birth ($\gamma$), establishment ($r$), and death ($\mu$),
+each of which can depend on spatial location and local population density
+in a way we specify later.
 Each individual gives birth at rate $\gamma$ to a single offspring,
@@
 We assume that $q$ is the density of a multivariate Gaussian,
-allowing a nonzero mean and inhomogeneous variance.
+allowing a nonzero mean and anisotropic variance.
+Both the mean and covariance can change across space,
+but do not depend on population density.
 The offspring does not necessarily survive to be counted in the population:
@@
     \caption{
+        \comment{Perhaps we should have two panels, one with the PME example (currently panel A) and the other with FKPP;
+        right now panel B is not very helpful I think, so maybe should be omitted or added to so it better describes the whole process
+        (including dispersal and establishment).}
         Conceptual figure of the model.
         \textbf{(A)} Example plot of $\gamma$, $\mu$, and $F$
-        (calculated with $r=1$) against scaled local population density.
+        (calculated here with $r=1$) against scaled local population density.
         In this example, both birth and death rates increase with population density,
@@
 To measure local population density, we convolve the population measure with
-an ``interaction kernel'' -- for simplicity, we take these to be Gaussian
-with various scales, and write
-$$
-    p_{\sigma^2}(x) = \frac{1}{(2 \pi \sigma^2)^{d/2}} e^{-\|x\|^2 / 2 \sigma^2} .
-$$
-Given a nonnegative function $\gamma(x, m) : \IR^d \times \IR_{\ge 0} \to \IR_{\ge 0}$,
-the birth rate of an individual at location $x$ when the state of the population is $X$
-is $\gamma(x, \smooth{\gamma} X(x) / N)$,
-where $\smooth{\gamma} X$ is the convolution of $X$
-with $p_{\epsilon_\gamma^2}$.
+an ``interaction kernel'' -- which, for simplicity, we take to be Gaussian,
+which we write as
+$$
+    p_{\epsilon^2}(x) := \frac{1}{(2 \pi \epsilon^2)^{d/2}} e^{-\|x\|^2 / 2 \epsilon^2} ,
+$$
+for an ``interaction distance'' $\epsilon$.
+First consider birth rates, defined by
+a nonnegative function $\gamma(x, m) : \IR^d \times \IR_{\ge 0} \to \IR_{\ge 0}$
+of location $x$ and local population density $m$,
+and an interaction distance $\epsilon_\gamma > 0$.
+Local population density enters through the convolution of $X$ with $p_{\epsilon_\gamma^2}$,
+which we write as $\smooth{\gamma} X$.
+Then, the birth rate of an individual at location $x$ when the state of the population is $X$
+is $\gamma(x, \smooth{\gamma} X(x) / N)$.
 Similarly, the establishment probability of an offspring at location $x$ is
@@
 where $r(x, m) : \IR^d \times \IR_{\ge 0} \to [0, 1]$
-and again $\smooth{r} p_{\epsilon_r^2}$.
+and again $\smooth{r} X$ is the convolution of $p_{\epsilon_r^2}$ with $X$.
 Rather than defining a function $\mu(x, m)$ for the death rate,
@@
 scaled by $1/\theta$
-so that the population density changes over a time scale of $\theta$,
-i.e., we have ``near-critical branching''.
+so that the population density changes over a time scale of $\theta$.
+(This corresponds to a ``near-critical branching'' assumption.)
 Informally, we would like that
@@
 
-In summary, demographic parameters depend on local density measured
+In summary, each of the three demographic parameters depend on local density measured
+with a Gaussian kernel with possibly different scales:
 for birth over a scale of $\epsilon_\gamma$,
@@
 it will turn out to be useful in the proofs to have $\epsilon_r < \epsilon_\gamma$,
-although in the limit they can be taken equal to each other,
+although in the limit they can be taken equal to each other
+(and $\epsilon_F$ is unconstrained),
 so informally we think of local density as being determined on a scale of $\epsilon$.
-The value of $\epsilon_F$ is unconstrained.
 
@@
 and the lineages we follow will be uniparental.
-For these reasons, the model is most obviously applicable to bacterial populations,
+For these reasons, the model is most obviously applicable to bacterial populations or selfing plants,
 although we do not anticipate that incorporation of these complications
@@
 and state some assumptions on the parameters.
+The process takes values in the space of finite measures on $\IR^d$,
+which we write as $\measures$.
 
@@
     \label{def:model_setup}
-    For each $\theta \ge 0$,
-    let $\left(\eta^\theta(t)\right)_{t \ge 0}$
-    be the continuous-time measure-valued Markov process described above
-    with birth rates, establishment probabilities, and death rates
-    determined as follows.
     Suppose $\gamma(x, m)$, $r(x, m)$, and $F(x, m)$
@@
     Fix nonnegative values $\epsilon_r$, $\epsilon_\gamma$, and $\epsilon_F$,
-    with $\epsilon_r < \epsilon_\gamma - 1/\theta$.
+    with $\epsilon_r < \epsilon_\gamma$.
     Suppose $F: \IR^d \times \IR_{\ge 0} \to \IR$ is bounded and uniformly continous
@@
     \end{align}
-    Let $N$ be a positive number determined by $\theta$.
-    When the state of the process is $\eta$,
+    For each $N > 0$ and $\theta \ge 1/(\epsilon_\gamma - \epsilon_r)$,
+    let $\left(\eta^\theta(t)\right)_{t \ge 0}$
+    be the continuous-time measure-valued Markov process described above
+    with birth rates, establishment probabilities, and death rates
+    determined as follows.
+    When the state of the process is $\eta \in \measures$,
     offspring of mass $1/N$ are produced at location $x$
-    with rate $\theta \gamma(x, \smooth{\gamma} \eta^{\theta}(x)) N \eta^{\theta}_s(dx)$
-    and adults die at location $x$ with rate $\theta \mu(x, \eta) N \eta^{\theta}_s(dx)$,
+    with rate $\theta \gamma(x, \smooth{\gamma} \eta(x)) N \eta_s(dx)$
+    and adults die at location $x$ with rate $\theta \mu(x, \smooth{\mu} \eta(x)) N \eta_s(dx)$,
     (i.e., at rates $\theta \gamma$ and $\theta \mu$ per capita respectively).
-    Offspring disperse to a location offset from the parent's location
-    by an independent Gaussian with mean $\meanq/\theta$
-    and covariance matrix $\covq / \theta$;
+    Each offspring disperses to a location offset from the parent's location
+    by an independent Gaussian with mean $\meanq(x) / \theta$
+    and covariance matrix $\covq(x) / \theta$;
     an offspring at $x$ establishes instantaneously
-    with probability $r(x, \smooth{r} \eta^{\theta}(x))$, or else dies.
+    with probability $r(x, \smooth{r} \eta(x))$, or else dies.
 \end{definition}
 
-\comment{TODO: insert remark about writing $\gamma(x, \smooth{\gamma}\eta(x)) = \gamma(x, \eta)$.}
-
-We will now define $(\eta^{\theta}(t))_{t \geq 0}$
-explicitly as a solution to a Martingale problem.
+Expressions like $\gamma(x, \smooth{\gamma} \eta(x))$ will appear often in the paper.
+To make formula more readable, we overload notation to define
+$$
+    \gamma(x, \eta) := \gamma(x, \smooth{\gamma} \eta(x)) ,
+$$
+and similiarly write $\mu(x, \eta)$  for $\mu(x, \smooth{\mu} \eta(x))$ and $r(x, \eta)$ for $r(x, \smooth{r} \eta(x))$.
+When convenient, we may also suppress the arguments completely,
+writing simply $\gamma$, $\mu$, and $r$ for these quantities.
+
+\comment{I'm not quite sure how we want to frame these two things: probably not as two definitions...}
+We will now give another, equivalent definition of $(\eta^{\theta}(t))_{t \geq 0}$,
+this time as a solution to a martingale problem.
 
@@
     \label{Def: Rescaled Models}
-We define $(\eta^{\theta}_t)_{t \geq 0}$ to be the solution to the Martingale Problem,
-with initial condition $\eta^{\theta}_0$,
+We define $(\eta^N_t)_{t \geq 0}$ to be the solution to the Martingale Problem,
+with initial condition $\eta^N_0 \in \measures$,
 such that for all smooth functions $f \in C^{2}_{0}(\mathbb{R}^d)$,
+writing $\langle f, \eta \rangle = \int_{\IR^d} f(x) \eta(dx)$
+and $q_\theta(x, dy)$ as the Gaussian kernel
+with mean $x + \meanq(x)/\theta$ and covariance $\covq(x) / \theta$,
 \begin{equation}
@@
 \begin{aligned}
-M^{\theta}_t(f)
-&:=  \langle f,\eta^{\theta}_t \rangle
-        -\langle f,\eta^{\theta}_0 \rangle
+M^N_t(f)
+&:=  \langle f, \eta^N_t \rangle
+        -\langle f, \eta^N_0 \rangle
  \\ &\qquad {}
@@
              \left(
-        f(z)r\big(z,\rho_{r}*\eta^{\theta}_{s}(z)\big)
-            -f(x)r\big(x,\rho_{r}*\eta^{\theta}_{s}(x)\big)
+                f(z)r(z, \eta^N_{s})
+                - f(x)r(x, \eta^N_{s})
             \right)
-                    q_\theta(x,dz)\right)
-        \\ & \qquad \qquad \qquad \qquad {} \times
-                            \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
-                            \eta^{\theta}_{s}(dx)
-     \\ & \qquad \qquad {} +\int 
-     f(x)F\big(x,\rho_{F}*\eta^{\theta}_{s}(x)\big)
-     \eta^{\theta}_{s}(dx)
+        q_\theta(x,dz) \right)
+\\ & \qquad \qquad \qquad \qquad {}
+        \times \gamma(x, \eta^N_{s}) \eta^N_{s}(dx)
+\\ & \qquad \qquad {}
+    + \int f(x) F(x, \eta^N_{s}) \eta^N_{s}(dx)
     \bigg\} ds
@@
 \begin{aligned} \relax
-[ M^{\theta}_t(f)] =& 
+[ M^N_t(f)] =& 
 \frac{\theta}{N} \int_{0}^{t}\bigg\{
-\langle \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
-\int f^2(y)r\big(y,\rho_{r}*\eta^{\theta}_{s}(y)\big)q_\theta(x,dy) 
-,\eta^{\theta}_{s}(dx)\rangle\\
-& \qquad \qquad +\langle \mu\big(x,\eta^{\theta}_{s}\big)f^2(x) 
-,\eta^{\theta}_{s}(dx)\rangle \bigg\}ds. 
+    \langle \gamma(x, \eta^N_{s})
+        \int f^2(y)r(y, \eta^N_{s}) q_\theta(x,dy) 
+    , \eta^N_{s}(dx) \rangle \\
+& \qquad \qquad {}
+    + \langle \mu(x, \eta^N_{s}) f^2(x) 
+    , \eta^N_{s}(dx)\rangle
+    \bigg\}ds. 
 \end{aligned}    
 \end{equation}
-
 \end{definition}
 
+Note that
+since individuals are produced at rate $N \gamma \eta$ but have mass $1/N$ each,
+these factors of $N$ cancel in~\eqref{eq: Pre-limit Martingale Characterisation}.
 Since we are taking a diffusion limit,
 we will have use for the following notation:
-
-\comment{TODO: $\meanq$ can vary in space, make that clear?}
 
@@
     to be the density of a multivariate Normal
-    with mean $\meanq/\theta$ and covariance matrix $\covq/\theta$.
+    with mean $\meanq(x)/\theta$ and covariance matrix $\covq(x)/\theta$
+    (although sometimes we omit the dependence of $\meanq$ and $\covq$ on $x$).
     This implies that if we define, for $f : \IR^d \to \IR$,
@@
 \paragraph{Remark:}
-An equivalent way to describe the model
-would be to say that an individual at $x$ gives birth at rate
-$$
-    \gamma(x, \smooth{\gamma} \eta(x))
+An equivalent way to describe the model would be to say that
+when the state of the population is $\eta$,
+an individual at $x$ gives birth at rate
+$$
+    \theta \gamma(x, \smooth{\gamma} \eta(x))
     \int r(x, \smooth{r} \eta(y)) q(x, dy) ,
@@
 \section{Examples and applications}
+\label{sec:applications}
 
@@
 \section{Proofs}
+\label{sec:proofs}
 

### 2022-05-09 forwards-and-backwards.tex
edits 2

@@
 \end{align}
+\end{definition}
+
+Expressions like $\gamma(x, \smooth{\gamma} \eta(x))$ will appear often in the paper.
+To make formula more readable, we overload notation to define
+$$
+    \gamma(x, \eta) := \gamma(x, \smooth{\gamma} \eta(x)) ,
+$$
+and similiarly write $\mu(x, \eta)$  for $\mu(x, \smooth{\mu} \eta(x))$ and $r(x, \eta)$ for $r(x, \smooth{r} \eta(x))$.
+When convenient, we may also suppress the arguments completely,
+writing simply $\gamma$, $\mu$, and $r$ for these quantities.
+
 For each $N > 0$ and $\theta \ge 1/(\epsilon_\gamma - \epsilon_r)$,
-    let $\left(\eta^\theta(t)\right)_{t \ge 0}$
-    be the continuous-time measure-valued Markov process described above
+the process $\left(\eta^\theta(t)\right)_{t \ge 0}$
+is the continuous-time measure-valued Markov process described above
 with birth rates, establishment probabilities, and death rates
@@
 offspring of mass $1/N$ are produced at location $x$
-    with rate $\theta \gamma(x, \smooth{\gamma} \eta(x)) N \eta_s(dx)$
-    and adults die at location $x$ with rate $\theta \mu(x, \smooth{\mu} \eta(x)) N \eta_s(dx)$,
+with rate $\theta \gamma(x, \eta) N \eta_s(dx)$
+and adults die at location $x$ with rate $\theta \mu(x, \eta) N \eta_s(dx)$,
 (i.e., at rates $\theta \gamma$ and $\theta \mu$ per capita respectively).
@@
 an offspring at $x$ establishes instantaneously
-    with probability $r(x, \smooth{r} \eta(x))$, or else dies.
-\end{definition}
-
-Expressions like $\gamma(x, \smooth{\gamma} \eta(x))$ will appear often in the paper.
-To make formula more readable, we overload notation to define
-$$
-    \gamma(x, \eta) := \gamma(x, \smooth{\gamma} \eta(x)) ,
-$$
-and similiarly write $\mu(x, \eta)$  for $\mu(x, \smooth{\mu} \eta(x))$ and $r(x, \eta)$ for $r(x, \smooth{r} \eta(x))$.
-When convenient, we may also suppress the arguments completely,
-writing simply $\gamma$, $\mu$, and $r$ for these quantities.
-
-\comment{I'm not quite sure how we want to frame these two things: probably not as two definitions...}
-We will now give another, equivalent definition of $(\eta^{\theta}(t))_{t \geq 0}$,
-this time as a solution to a martingale problem.
+with probability $r(x, \eta)$, or else dies.
+
+We have just effectively defined the process, but to be completely clear,
+we will now give a formal definition as a solution to a martingale problem.
 
@@
 
-\comment{
-Set-up: there are two dichotomies:
-is the limiting process deterministic or a generalized superprocess?
-See Figure \ref{fig:super_vs_det_2d} for simulations.
+Our main results depend on two dichotomies:
+Is the limiting process deterministic or a (generalized) superprocess?
 And, are interactions local in the limit or not?
-Below we have results for three of these cases;
-as for the remaining one (local, superprocess),
-it should be possible in 1D, not in higher dimensions (brief note).
-}
+Below we have results for deterministic limits with local and nonlocal interactions,
+and for superprocess limits with nonlocal interactions.
+See Figure \ref{fig:super_vs_det_2d} for illustrative simulations.
+We suspect that limits are possible the remaining (local, superprocess) case
+in only $d=1$, but do not discuss the case further.
 
@@
 
+Recall when interpreting~\eqref{eqn:mgale_problem}
+that for instance $r(x, \eta_s) = r(x, \smooth{r} \eta_s(x))$,
+and so $\DG(fr)(x) = \DG(f(\cdot) r(\cdot, \smooth{r} \eta_s(\cdot)))(x)$.
+
 Theorem \ref{thm:nonlocal_convergence} provided convergence along subsequences;
@@
 In the deterministic case, we have convergence to a nonlocal PDE.
-\comment{Maybe the following two corollaries should be combined?}
-
+
+\begin{corollary}[Superprocess limits] \label{cor:superprocess_uniqueness}
+    In the context of Theorem~\ref{thm:nonlocal_convergence},
+    if the martingale problem
+    defined by equations \eqref{eqn:mgale_problem} and \eqref{eqn:mgale_variation}
+    has a unique solution,
+    then $(\eta^\theta(t))_{t \ge 0}$ converges to that solution
+    as $N \to \infty$.
     \comment{
-TODO: insert definition of "weak solution of the PDE \ref{eqn:nonlocal_pde}" heere.
+        Is this what we want to say here? Could be said better.
+        TODO: see what Dawson \& Li say about uniqueness
+        so we have at least some conditions under which this happens.
     }
+\end{corollary}
+
+Our results will show that in determinstic limits ``$\eta_t$ solves a PDE'',
+but since $\eta_t$ is a measure for which we don't always know there exists a density,
+we need to formalize the weak sense in which it solves the PDE.
+The notation in the following definition
+is written to suggest the case in which $\eta_t(dx)$ has a density $\varphi_t(x)$.
+
+\begin{definition}[Weak solutions]
+    \label{defn:weak_solutions}
+    We say that $(\eta_t)_{t \ge 0}$, with $\eta_t \in \measures$
+    is a \emph{weak solution} to the PDE
+    $$
+        \dot \varphi = r \DG^*(\gamma \varphi) + \varphi F
+    $$
+    if for all $f \in C_0^\infty(\IR^d)$,
+    $$
+        \frac{d}{dt} \langle f, \eta_t \rangle
+        =
+        \langle
+            \gamma \DG(rf) + f F,
+            \eta_t
+        \rangle .
+    $$
+    \comment{Write this out with $(x)$'s?}
+\end{definition}
 
@@
     \label{cor:nonlocal_pde_limits}
-    \comment{(TODO: remove "has a density" and rephrase appropriately)}
-    In the context of Theorem~\ref{thm:nonlocal_convergence},
-    if the limit is deterministic (i.e., $\theta / N \to \alpha = 0$), $\eta_0$ has a density,
-    and \comment{additional conditions? can we say something like this??}
-    then any limit $\eta_t(dx)$ has a density $\varphi(t, x)$,
-    which is a weak solution to the nonlocal partial differential equation
+    Under the assumptions of Theorem~\ref{thm:nonlocal_convergence},
+    if the limit is deterministic (i.e., $\theta / N \to \alpha = 0$),
+    then any limit $\eta_t$ is a weak solution to the nonlocal partial differential equation
     \begin{equation} \label{eqn:nonlocal_pde}
-        \partial_t \varphi(t, x)
+        \partial_t \varphi_t(x)
         =
-        r\left(x, \smooth{r} \varphi(t,x) \right)
+        r\left(x, \smooth{r} \varphi_t(x) \right)
         \DG^* \left[
-            \varphi(t, \cdot)
-            \gamma\big( x, \smooth{\gamma} \varphi(t, \cdot) \big)
+            \varphi_t(\cdot)
+            \gamma\big( x, \smooth{\gamma} \varphi_t(\cdot) \big)
         \right](x)
         +
-        \varphi(t, x)
-        F\left(x, \smooth{F} \varphi(t,x) \right)
-        .
-    \end{equation}
+        \varphi_t(x)
+        F\left(x, \smooth{F} \varphi_t() \right)
+        ,
+    \end{equation}
+    in the sense of Definition~\ref{defn:weak_solutions}.
     If equation \eqref{eqn:nonlocal_pde} has a unique solution,
     then $(\eta^\theta_t)_{t \ge 0}$ converges to that solution.
-
-    In particular, if
-    \comment{TODO: find some conditions under which this is true?}
-    then we have convergence to a unique solution.
 \end{corollary}
+
+\comment{TODO: find some conditions under which we have convergence to a unique solution?}
+\comment{TODO: Tom has conditions (coefficient are Lipschitz?) under which
+    the solution to \eqref{eqn:nonlocal_pdf} has a density (Thm 2.1 in DDMOT);
+    should we insert those here (as a Corollary or Proposition, maybe?)}
 
@@
 this will tend to decrease the local density.
-
-\comment{TODO: Tom has conditions (coefficient are Lipschitz?) under which
-    the solution to \eqref{eqn:nonlocal_pdf} has a density (Thm 2.1 in DDMOT);
-    should we insert those here (as a Corollary or Proposition, maybe?)}
-
-\begin{corollary}[Superprocess limits] \label{cor:superprocess_uniqueness}
-    In the context of Theorem~\ref{thm:nonlocal_convergence},
-    if the martingale problem
-    defined by equations \eqref{eqn:mgale_problem} and \eqref{eqn:mgale_variation}
-    has a unique solution,
-    then $(\eta^\theta(t))_{t \ge 0}$ converges to that solution
-    as $N \to \infty$.
-    \comment{
-        Is this what we want to say here? Could be said better.
-        TODO: see what Dawson \& Li say about uniqueness
-        so we have at least some conditions under which this happens.
-    }
-\end{corollary}
 

### 2022-05-09 forwards-and-backwards.tex
edits 3

@@
 
-Theorem~\ref{thm:nonlocal_convergence} shows convergence to the solution to a nonlocal PDE
-of the form \eqref{eqn:nonlocal_pde}.
-Since the coefficients at $x$ in \eqref{eqn:nonlocal_pde}
-depend only on the region nearby to $x$,
-we would often expect solutions of the nonlocal PDE to be close to the corresponding local PDE
+Although the coefficients at $x$ in \eqref{eqn:nonlocal_pde} are nonlocal,
+they depend only on the region nearby to $x$,
+and so we would expect solutions of the nonlocal PDE to be close to the corresponding local PDE
 as the interaction distances $\epsilon_r$, $\epsilon_\gamma$ and $\epsilon_F$
-go to zero.
+go to zero:
+for instance, if $\eta_t$ has density $\varphi_t$
+then $\gamma(x, \smooth{\gamma} \eta_t(x)) \to \gamma(x, \varphi_t(x))$ as $\epsilon_\gamma \to 0$.
 The following propositions give two concrete situations in which that is true.
-
-\comment{I've not got straight exactly how we're framing this
-    (namely, does $\eta$ have a density?).
-    Also, is this one or two propositions --
-    we said initially this would be two,
-    one for FKPP and one for PME,
-    but then maybe the argument was more general?
-}
 
@@
     \label{prop:nonlocal_to_local}
-    Suppose that $\eta_\epsilon(t,dx)$ is a solution to equation \eqref{eqn:nonlocal_pde}
+    Suppose that $\eta^\epsilon_t$ is a weak solution to equation \eqref{eqn:nonlocal_pde}
     with $r(x, m) = 1$ for all $x$ and $m$
-    and some $\epsilon_r < \epsilon_\gamma = \epsilon_F = \epsilon$
+    and some $\epsilon_r + 1/\theta < \epsilon_\gamma = \epsilon_F = \epsilon$
     \comment{and assumptions on $\gamma$? and $F$?}.
-    Then $\eta_\epsilon(t, dx)$ converges \comment{in what sense?} as $\epsilon \to 0$
-    to $u(t, x) dx$, which solves
+    Then $\eta^\epsilon_t(dx)$ converges \comment{in what sense?} as $\epsilon \to 0$
+    to $\varphi_t(x) dx$, which is a (strong) solution to
     \begin{align} \label{eqn:PDE}
-        \partial_t u(t, x)
+        \partial_t \varphi(t, x)
         =
-        \DG^* \left( \gamma(\cdot, u(t, \cdot) u(t, \cdot)  \right)(x)
-        + F(x, u(t, x)) u(t, x) .
+        \DG^* \left( \gamma(\cdot, \varphi(t, \cdot)) \varphi(t, \cdot)  \right)(x)
+        + F(x, \varphi(t, x)) \varphi(t, x) .
     \end{align}
@@
 However, it is of substantial interest to know whether
-we can take those two limit simultaneously.
+we can take those two limits simultaneously.
 The general case seems difficult,
@@
     be as defined in Definition \ref{def:model_setup}
-    and assume that as $N \to \infty$, $N \to \infty$
-    and $\epsilon_r < \epsilon_\gamma = \epsilon_F = \epsilon \to 0$
+    and assume that as $N \to \infty$, $\theta \to \infty$
+    and $\epsilon_r + 1/\theta < \epsilon_\gamma = \epsilon_F = \epsilon \to 0$
     in such a way that $\theta/N \to 0$
@@
 we turn to results on ancestral lineages,
-i.e., how genealogical ancestry moves across the landscape.
+i.e., how genealogical ancestry can be traced back across the landscape.
 Informally,
@@
 setting $L_t$ to the spatial location of the individual from whom
-the focal individual inherits.
+the focal individual inherits at that time in the past.
 Since in our model individuals have only one parent, this is unambiguous.
 Although we did not explicitly retain such information,
-it is clear that
-for finite $\theta$ (and hence, finite $N$),
+it is clear that for finite $N$
 one could construct the distribution of a lineage $(L_t)_{t=0}^T$
-given the history of the population $(\eta^\theta_t)_{t = 0}^T$,
-for each starting location to which $\eta^\theta_T$ assigns positive mass.
+given the history of the population $(\eta^N_t)_{t = 0}^T$,
+for each starting location to which $\eta^N_T$ assigns positive mass.
 It is less clear, however, how to formally retain such information in the limit.
@@
 First, when is it a Markov process given the population process?
-(I.e., given $(\eta_t)_{t=0^T}$ that records numbers of individuals
+(In other words, given $(\eta_t)_{t=0}^T$ that records numbers of individuals
 but not their ancestry.)
 We expect the answer here to be that a lineage is Markov
-only in the $N \to \infty$ limit.
-\comment{(or, do we know this? we can cite Barton, Depaulis and Etheridge at least for discussion.)}
+only in the $N \to \infty$ limit
+(see \citet{barton/depaulis/etheridge:2002} for discussion).
 Second, does the process have a tractable description?
@@
 
-\comment{
-    TODO: make notation agree with that in the proof.
-}
-
 \begin{definition}[Generator of a lineage] \label{def:lineage_generator}
-    Let $(\varphi(x, t))_{0 \le t \le T}$
+    Let $(\varphi_t(x))_{0 \le t \le T}$
     denote the density of a population that solves \eqref{eqn:nonlocal_pde},
-    and let $y$ be a point with $\varphi(y, T) > 0$.
+    and let $y$ be a point with $\varphi_T(y) > 0$.
     We define $(L_s(y))_{s=0}^T$,
-    the ancestral lineage of an individual sampled at $y$ at time $T$,
+    the ancestral lineage in this population of an individual sampled at $y$ at time $T$,
     to be the position of the unique ancestor of $y$ alive at time $T - s$.
@@
     \begin{align*}
-        Q_s f(y) := \IE_y[ f(L_s) ] ,
+        Q_s f(y) := \IE_y[ f(L_s) ] .
     \end{align*}
-    and $\Lgen_s$ to be the generator of this semi-group.
 \end{definition}
@@
 by characterizing its generator.
-To avoid complexity,
-we do this in the case where dispersal is $N(\meanq/\theta, \sigma^2 I/\theta)$,
-in which case $\DG = \sigma^2 \Delta + \meanq \cdot \grad$.
-
-\comment{Make forwards-backwards time notation reasonable in this.}
-
-\comment{Perhaps write generator as depending on $\phi$ rather than $s$?
-    Then we can say that the generator is $\Lgen_{\varphi(T-s)}$.}
 
 \begin{theorem} \label{thm:lineages}
-    In the context of Definition~\ref{def:lineage_generator},
+    For $\varphi: \IR^d \to \IR$, define
     \begin{align}
         \label{eqn:lineage_generator}
-        \Lgen_s f
+        \Lgen_\varphi f
         &=
-        \frac{r}{\varphi_{T-s}}
+        \frac{r}{\varphi}
         \left[
-            \DG^*(\gamma \varphi_{T-s} f) 
-            - f \DG^* (\gamma \varphi_{T-s})
+            \DG^*(\gamma \varphi f) 
+            - f \DG^* (\gamma \varphi)
         \right] \\
@@
     =
-    2 \sum_i C_{ij} \partial_i \log(\gamma \varphi_{T-s})
+    2 \sum_i C_{ij} \partial_i \log(\gamma \varphi)
     + 2 \sum_i \partial_i C_{ij}
@@
     $$
+    Then $\Lgen_{\varphi_{T-s}}$ is the generator of the semigroup $Q_s$
+    of Definition~\ref{def:lineage_generator}.
 \end{theorem}
 
-To make the generator readable, we've written it in concise notation,
+As usual,
+to make the generator readable, we've written it in concise notation,
 omitting the dependencies on location and population density,
@@
 remember that everything depends on location and density at that location and time --
-for instance, ``$r$'' is actually $r(x, \varphi(T-s, x))$.
+for instance, ``$r$'' is actually $r(x, \varphi(x))$.
 
 \begin{corollary} \label{cor:lineages_simple}
-    In the context of Definition~\ref{def:lineage_generator},
+    In addition to the assumptions of Theorem~\ref{thm:lineages},
     if the dispersal process is isotropic (i.e., $\covq = \sigma^2 I$),
@@
     \begin{equation}
-        \Lgen_s f
+        \Lgen_\varphi f
         =
@@
             \left(
-                2 \grad \log(\gamma \varphi_s)
+                2 \grad \log(\gamma \varphi)
                 - \meanq
@@
     run at speed $\sigma^2$ multiplied by the local per-capita production of offspring ($r \gamma$)
-    in a potential equal to the local birth output tilted by migraiton bias
-    ($\varphi \gamma \exp(-\meanq \cdot x / 2 \sigma^2)$).
+    in a potential equal to the local birth output tilted by migration bias
+    ($\varphi_s \gamma \exp(-\meanq \cdot x / 2 \sigma^2)$).
 \end{corollary}
@@
     \begin{align*}
-        r \Delta (\gamma w) + w F(w) + \wavespeed \cdot \grad w = 0 .
+        r \Delta (\gamma w) + w F + \wavespeed \cdot \grad w = 0 .
     \end{align*}
-    Then the generator $\Lgen$
-    of the motion of a linages in this population is
+    Then the semigroup 
+    of the motion of a linages in this population 
+    $Q_s$ is time-homogeneous with generator
     \begin{align}
@@
         &=
-        r \gamma
+        \sigma^2 r \gamma
         \left(
@@
         \right)
-        + \wavespeed \cdot \grad f .
+        + (\wavespeed - \meanq) \cdot \grad f .
     \end{align}

### 2022-05-10 forwards-and-backwards.tex
peter edits done

@@
 for example, the number of adults produced by a single parent is determined
-by the degree of crowding at the the location of the parent. The novelty
+by the degree of crowding at the location of the parent. The novelty
 of the models that we introduce here is that, although we shall only
@@
 
-In general this is an extremely difficult question. However, in specical
+In general this is an extremely difficult question. However, in special
 circumstances, some progress can be made. One of the settings that
@@
 
-In the paper we study scaling limits of spatial popultaions,
+In the paper we study scaling limits of spatial populations,
 obtaining convergence of both the population process
@@
 $$\lim \frac{\theta}{N} =: \alpha$$
+
+Were not using $\lambda$, but only $N$.
 
@@
 and has uniformly bounded second derivatives,
-and that $(x, m) \mapsto m^2 \gamma(x, m)$ is unformly bounded.
+and that $(x, m) \mapsto m^2 \gamma(x, m)$ is uniformly bounded.
 Fix nonnegative values $\epsilon_r$, $\epsilon_\gamma$, and $\epsilon_F$,
 with $\epsilon_r < \epsilon_\gamma$.
-Suppose $F: \IR^d \times \IR_{\ge 0} \to \IR$ is bounded and uniformly continous
+Suppose $F: \IR^d \times \IR_{\ge 0} \to \IR$ is bounded and uniformly continuous
 and define
@@
 $$
-and similiarly write $\mu(x, \eta)$  for $\mu(x, \smooth{\mu} \eta(x))$ and $r(x, \eta)$ for $r(x, \smooth{r} \eta(x))$.
+and similarly write $\mu(x, \eta)$  for $\mu(x, \smooth{\mu} \eta(x))$ and $r(x, \eta)$ for $r(x, \smooth{r} \eta(x))$.
 When convenient, we may also suppress the arguments completely,
@@
 For each $N > 0$ and $\theta \ge 1/(\epsilon_\gamma - \epsilon_r)$,
-the process $\left(\eta^\theta(t)\right)_{t \ge 0}$
+the process $\left(\eta^N(t)\right)_{t \ge 0}$
 is the continuous-time measure-valued Markov process described above
@@
 \begin{definition}[Martingale Problem Characterisation]
-    \label{Def: Rescaled Models}
+    \label{defn:mgale_construction},
 We define $(\eta^N_t)_{t \geq 0}$ to be the solution to the Martingale Problem,
@@
 \begin{theorem} \label{thm:nonlocal_convergence}
-    Let $(\eta^\theta_t)_{t \geq 0}$
+    Let $(\eta^N_t)_{t \geq 0}$
     be as defined in Definition \ref{def:model_setup}
@@
     The sequence of stochastic processes
-    $(\eta^\theta_t)_{t \geq 0}$
+    $(\eta^N_t)_{t \geq 0}$
     converges along subsequences in distribution as $N \to \infty$
@@
     has a unique solution,
-    then $(\eta^\theta(t))_{t \ge 0}$ converges to that solution
+    then $(\eta^N(t))_{t \ge 0}$ converges to that solution
     as $N \to \infty$.
@@
 
-Our results will show that in determinstic limits ``$\eta_t$ solves a PDE'',
+Our results will show that in deterministic limits ``$\eta_t$ solves a PDE'',
 but since $\eta_t$ is a measure for which we don't always know there exists a density,
@@
     If equation \eqref{eqn:nonlocal_pde} has a unique solution,
-    then $(\eta^\theta_t)_{t \ge 0}$ converges to that solution.
+    then $(\eta^N_t)_{t \ge 0}$ converges to that solution.
 \end{corollary}
@@
     \label{thm:local_convergence}
-    Let $(\eta^\theta_t)_{t \geq 0}$
+    Let $(\eta^N_t)_{t \geq 0}$
     be as defined in Definition \ref{def:model_setup}
@@
     \comment{TODO: some conditions on $\epsilon$ and $r$ and $\gamma$ and $F$}.
-    Then the sequence of stochastic processes $(\eta^\theta_t)_{t \ge 0}$
+    Then the sequence of stochastic processes $(\eta^N_t)_{t \ge 0}$
     converges \comment{in some sense}
@@
 
-\comment{
-    This section:
-    model set-up including the limit;
-    comparison of the simulation profile to deterministic solution.
-    See Figure \ref{fig:pme_waves}.
-}
-
 Consider the porous medium equation (PME) with logistic growth,
@@
 models in ecology, eukaryotic cell biology, and avascular tumour growth;
-see e.g.~\cite{sherratt:2010} and references therein for further discussion. 
+see~\cite{sherratt:2010} and references therein for further discussion. 
+In particular, it has been suggested as a model for
+the expansion of a certain type of bacteria % of the type {\em Paenbacillus dendritiformis}
+on a thin layer of agar in a petri dish 
+\citep{cohen/golding/kozlovsky/benjacob/ron:1999}. 
 We shall pay particular attention to the case in which the equation can be 
 thought of as modelling the density of an expanding population.
-The specific equation that we use to illustrate the implications of
-our results is one of a class used to study pattern formation in 
-bacterial colonies. In particular, it has been suggested as a model for
-the expansion of bacteria of the type {\em Paenbacillus dendritiformis} on
-a thin layer of agar in a petri dish, 
-\cite{cohen/golding/kozlovsky/benjacob/ron:1999}.
 
@@
 Consulting equation~\eqref{eqn:mu_defn},
-we then need death rate to be $\mu = (1 + 1/\theta) \varphi - 1/\varphi$.
+this implies that $\mu = (1 + 1/\theta) \varphi - 1/\varphi$.
 In other words,
 establishment is certain
-and birth rates to increase linearly with population density,
+and birth rates increase linearly with population density,
 but to compensate, death rates increase slightly faster (also linearly),
 as shown in Figure~\ref{fig:pme_waves}.
-Alert readers will notice that this violates our boundedness assumptions;
-\comment{(perhaps this is too much detail here)}
+Alert readers will notice that
+for finite $\theta$ death rates may be negative,
+and furthermore rates are not bounded;
 in practice we choose a suitably small value for $\beta$ and define
@@
 \end{align*}
-which in turn implies that death rate when local density is $m$
-is roughly $(1 + 1/\theta) (1 - \exp(-\beta m)) / \beta - 1/(\theta \beta)$.
+and set $\mu(x, m) = \max(0, \gamma - \theta F)$.
 Birth and death rates are equal at density $m = 1$,
@@
 
-\comment{
-    This section:
-    explain generator in stationary frame;
-    derive stationary distribution;
-    introduce FKPP;
-    compute for PME and FKPP.
-    (Also: Allen-Cahn example?)
-    The two cases are very different, as shown in Figure \ref{fig:pme_vs_fkpp}.
-}
-
 It is interesting to investigate the motion of an ancestral lineage
@@
 wave profile $w$. 
+We consider three relatively well-studied examples:
+the Porous Media equation (above),
+the Fisher-KPP equation,
+and the Allen-Cahn equation.
+We will work here in one dimension,
+and take $\sigma^2 = 1$ and $\meanq = 0$.
 
@@
 the lineage's generator is, for $x < 0$,
-\comment{(need to decide whether to use $f_x$ or $\delta_x f$)}
+with $f_x$ denoting the spatial derivative of $f$,
 \begin{align*}
@@
         \left(
-         f_{xx}
+         f_{xx}(x)
          +
-         2 \frac{(w^2)_x}{w^2} f_x
+         2 \frac{(w(x)^2)_x}{w(x)^2} f_x(x)
         \right)
-        + f_x \\
+        + f_x(x) \\
     &=
         \left(1 - e^{\frac{1}{2} x} \right)
-        f_{xx}
+        f_{xx}(x)
         -
-        2 e^{\frac{1}{2} x} f_x
+        2 e^{\frac{1}{2} x} f_x(x)
         +
-        f_x .
+        f_x(x) .
 \end{align*}
@@
     &\propto
-        \frac{ 1 }{ 2 (1 - \exp{\xi/2}) }
+        \frac{ 1 }{ 2 (1 - e^{\xi/2}) }
         \exp\left(
@@
 \end{align}
-In this case,
-even though we do not have an explicit formula for the wave shape,
-these methods give us information about ancestral lineages.
+Even though we do not have an explicit formula for the wave shape in this case,
+our methods provide information about ancestral lineages.
 The equation has non-negative travelling wave solutions of speed $c$ for all $c \geq 2$, 
@@
 solution will converge to the profile $w^F$ with the minimal wavespeed, $c=2$,
-\cite{kolmogorov/petrovsky/piscounov:1937,ramson:1983}.
-No matter what the initial condition,
+\cite{kolmogorov/petrovsky/piscounov:1937,bramson:1983}.
+No matter the initial condition,
 for any $t>0$ the support of the 
 solution will be the whole real line. 
-Since in ths case, $r = \gamma = 1$,
+In this case, we must have $r = \gamma = 1$,
+and $F(x, m) = 1 - m$ so $\mu(x, m) = 1 - (1-m)/\theta$.
+This implies that
 the generator of the motion of an ancestral lineage is
-$$
+\begin{equation} \label{eqn:fkpp_generator}
     \Lgen \phi
@@
     \phi_{xx} + 2 \frac{w_x}{w} \phi_x + 2 \phi_x .
-$$
+\end{equation}
 Near the tip of the wave (for $x$ large), $w^F(x) \sim e^{-x}$,
-so the motion of the lineage is close to Brownian motion.
-On the other hand, for $x < 0$ the lineage behaves approximately as
+so \eqref{eqn:fkpp_generator} implies that
+the motion of a lineage is close to unbiased Brownian motion.
+On the other hand, for $x < 0$ a lineage behaves approximately as
 Brownian motion with drift at rate two to the right.
@@
 ancestral lineages are pushed into the tip of the wave,
-and there is no stationary distribution.
-These results agree with those of \comment{XXX}.
+and there is no stationary distribution,
+so that long-term dynamics of genetic inheritance
+depend on the part of the wave not well-approximated by a smooth profile.
+These results agree with those of \comment{TODO: citations}.
 
@@
 which is used to model populations evolving under selection \cite{Sarah}.
-This equation also has an explicit travelling wave solution
-of shape
+This equation also has an explicit travelling wave solution with speed $s$
+and shape
 \[ w^A(x) = (1+e^{x})^{-1}. \]
-The generator for ancestral lineages is, in this case,
+The generator for ancestral lineages is, just as in the Fisher-KPP case,
 \begin{align*}
@@
 \end{align*}
-so lineages in the tip are pushed into the bulk of the wave by the drift $-2(e^{-x}+1)^{-1}$,
-but that drift gets weaker further to the left.
+so lineages in the tip are pushed leftwards into the bulk of the wave by a $-2(e^{-x}+1)^{-1}$,
+that gets weaker further to the left.
 This diffusion has speed measure
@@
 % % % % % % % % % % % % % % % %
-\subsection{Populations with Varying Lineage Distributions but Same Stationary Profile}
-
-Consider two populations with coefficients $r_1, \gamma_1, \mu_1$ and  $r_2, \gamma_2, \mu_2$, and denote their lineage motion generator and profile as $\hat{\mathcal{L}}_1,w_1$, and $\hat{\mathcal{L}}_2,w_2$.
-We further assume that our populations have a stationary distribution with $\Xi_t(x)=w(x)$, i.e.
-$\mathfrak{c}=0$.\\
-Let $\beta(x)>0$ and take $r_2(x)=r_1(x)\beta(x),~ \mu_2(x)=\mu_1(x)\beta(x),~ \gamma_2(x)=\gamma_1(x)$. Since $F=r\gamma-\mu$, we have that 
-\begin{multline}
-\label{eq: same profile scaled}
-r_2\Delta(\gamma_2 w_2)+(r_2\gamma_2-\mu_2)(w_2)=0\implies r_1\beta \Delta(\gamma_1 w_2)+(r_1\beta \gamma_1-\mu_1 \beta)(w_2)=0\\
-\implies r_1 \Delta(\gamma_1 w_2)+(r_1 \gamma_1-\mu_1)(w_2)=0 \implies w_2=w_1.
-\end{multline}
-The two populations share the same stationary profile but their ancestral lineage motions are different as 
-\begin{equation}
-\label{eq: different generator scaled}
-\hat{\mathcal{L}}_2 \phi = r_1 \beta \gamma_1\left(\Delta\phi+2\frac{\nabla(\gamma_1 w_1)}{\gamma_1 w_1}\nabla\phi\right)\neq r_1 \gamma_1\left(\Delta\phi+2\frac{\nabla(\gamma_1 w_1)}{\gamma_1 w_1}\nabla\phi\right) = \hat{\mathcal{L}}_1 \phi.
-\end{equation}
-The stationary distribution of our population is unchanged when we scale $r,\mu$ by a rate of $\beta(x)$,
-but the motion of lineages is sped up locally by $\beta$.
-This corresponds to making areas with $\beta > 1$ more ``sink-like'',
-because there death rate is higher, but also is the establishment of new individuals. Those regions as a result have lower long-term fitness and lineages spend less time there.
+\subsection{Nonuniqueness of population density}
+
+It is natural for applications to wonder about identifiability:
+when can the observed quantities like population density
+or certain summaries of lineage movement uniquely determine
+the underlying demographic parameters?
+Consider a deterministic,
+continuous population generated by parameters $\gamma$, $\mu$, and $r$
+with $meanq = 0$ and $\covq = I$.
+Suppose it has a stationary profile $w(x)$, that must satisfy
+$$
+   r \Delta(\gamma w) + (r \gamma - \mu) w = 0 .
+$$
+It is easy to see that $w$ does not uniquely specify $\gamma$, $\mu$, and $r$:
+let $\beta(x)$ be a smooth, nonnegative function on $\IR^d$,
+and let $r'(x, m) = \beta(x) r(x, m)$ and $\mu'(x, m) = \beta(x) \mu(x, m)$
+(and, let $\gamma' = \gamma$).
+Then the population with parameters $\gamma'$, $\mu'$, and $r'$
+has the same stationary profile(s) as the original population.
+
+Can these two situations be distinguished from summaries of lineage movement?
+The first has lineage generator
+\[
+    f \mapsto \Lgen f = r \gamma \left( \Delta f + 2 \grad \log(\gamma w) \cdot \grad f \right),
+\]
+while the second has lineage generator $f \mapsto \beta(x) \Lgen f(x)$.
+In other words,
+although the stationary profile of the population is unchanged when we scale
+local establishment and death by $\beta$,
+the motion of lineages is sped up locally by $\beta$.
+This corresponds to making areas with $\beta > 1$ more ``sink-like'' and $\beta < 1$ ``source-like'':
+if $\beta(x) > 1$, then at $x$ both the death rate and establishment of new individuals are higher.
+As a result, lineages in the second model spend more time in areas with $\beta < 1$,
+i.e., those areas have higher long-term fitness,
+something that is in principle discernible from genetic data.
 
@@
 
-\comment{TODO: short lead-in}
+In this section we give heuristic arguments for our main results,
+to build intuition before the formal proofs.
 
@@
 
-We write $\Pgen^\theta$
-for the generator of the scaled population process $\eta$ acting
-on test functions of the form 
-$$
-    F( \langle f, \eta\rangle )
-    =
-    F \left( \int f(x)\eta(dx) \right),
-$$
+We write $\Pgen^N$
+for the generator of the scaled population process $\eta^N$
+of Definition~\ref{defn:mgale_construction}
+acting on test functions of the form $F( \langle f, \eta \rangle )$,
 where $f \geq 0$ is smooth and compactly supported on $\IR^d$ and 
 $F \in C^\infty ([0,\infty))$.
-Recall that $N \to \infty$ along with $\theta$,
+Recall that $\theta \to \infty$ along with $N$,
 although we don't remind the reader with extra superscripts.
@@
 \begin{multline*}
-    \Pgen^\theta
+    \Pgen^N
     F(\langle f,\eta \rangle)
@@
     +
-    \epsilon_{\theta}(f, F, \eta),
+    \epsilon_N(f, F, \eta),
 \end{multline*}
 where the terms that make up 
-$\epsilon_{\theta, N}(f, F, \eta)$
+$\epsilon_N(f, F, \eta)$
 will be negligible in our scaling limit.
@@
 
-Consider first the mean measure.
-The birth rate at location $x$ when the state of the population is $\eta$
-is a function of the location and the measure $\eta$ through a specific form:
-$\gamma(x, \smooth{\gamma} \eta(x))$;
-however, for the moment we will write $\gamma(x, \eta)$ instead
-to make the exposition clearer
-(and similarly for establishment probability $r(x, \eta)$ and death rate $\mu(x, \eta)$).
-Recall that in our parameterization only $\mu$ and the dispersal kernel $q$ depend on $\theta$.
+Recall that in our parameterization only death rates $\mu$
+and the dispersal kernel $q$ depend on $\theta$.
 For a suitable (smooth, compactly supported) test function $f$, we find
@@
     \begin{split}
-    \Pgen^\theta \langle f, \eta \rangle
+    \Pgen^N \langle f, \eta \rangle
     &=
@@
 \end{align*}
-This definition --
-is really a `near-critical' assumption that birth and death rates
-differ by something of order $1/\theta$.
-Furthermore, since we've taken $q_\theta$ to be the density of a Normal
-with mean and variance proportional to $1/\theta$,
+Furthermore, recall from Definition~\ref{def:dispersal_generator} that
 \begin{align} \label{eqn:near_critical}
@@
     \qquad \stackrel{\theta\to\infty}{\longrightarrow} \qquad  
-    \DG \big(r(\cdot,\Xi)f(\cdot)\big)(x),
+    \DG \big(r(\cdot,\Xi)f(\cdot)\big)(x) .
 \end{align}
-where recall if dispersal is simply standard multivariate Gaussian
+To make this more familiar,
+remember that if dispersal is simply standard multivariate Gaussian
 with mean zero and covariance $\sigma^2 I / \theta$,
 then $\DG = \sigma^2 \Delta$, where $\Delta$ denotes the Laplacian.
-Note that there is a slight mismatch between the locations at which we are 
-measuring birth and death rates, because in~\eqref{eqn:near_critical}
-the establishment probability is 
-measured at $x$ rather than at the point where juveniles fall.
-
 Equation~\eqref{eqn:rewritten mean measure}) then converges to
@@
 \end{equation}
+This gives the martingale of Theorem~\ref{thm:nonlocal_convergence}.
 More generally, we expect everything to work
 if the remaining parameters ($r$, $\gamma$, and $F$)
-depended on $\theta$, but converged as $N \to \infty$.
+also depended on $N$, but converged as $N \to \infty$.
 
@@
 above, the second order term in the generator takes the form
-$$
-F''(\langle f,\eta\rangle)
+\begin{align*}
+& F''(\langle f,\eta\rangle)
 \frac{1}{2} N \theta
@@
     ,\eta(dx)\rangle
-\right\} .
-$$
-The term $\epsilon_{\theta,N}(f, F, \eta)$ will be 
+\right\} \\
+&\qquad
+= \frac{1}{2} F''(\langle f, \eta \rangle)
+    \frac{\theta}{N}
+    \langle
+        \gamma(x, \eta) \int f^2(y) r(y, \eta) q_\theta(x, dy) + f^2(x) \mu(x, \eta),
+        \eta(dx)
+    \rangle .
+\end{align*}
+Since $\int f^2(y) r(y, \eta) q_\theta(x, dy) \to f^2(x) r(x, \eta)$
+and $\gamma r + \mu = 2 \gamma r - F / \theta \to 2 \gamma r$
+as $\theta \to \infty$,
+this converges to
+\begin{align*}
+\frac{\alpha}{2} F''(\langle f, \eta \rangle)
+    \langle
+        2 \gamma(x, \eta) r(x, \eta),
+        \eta(dx)
+    \rangle .
+\end{align*}
+
+Finally, the term $\epsilon_{\theta,N}(f, F, \eta)$ will be 
 $\bigO(\theta/N^2)$.
 
-% % % % % % % %
-\subsubsection*{Limit I: deterministic case}
-
-\comment{Need to decide what to call the limit here (and above, I guess).}
-
-By choosing $\theta/N\rightarrow 0$, the second order term in the generator 
-will vanish and we expect a deterministic limit. 
-Let us suppose that the limit has a smooth density with respect to
-Lebesgue measure, and abuse notation by using $\Xi_t(x)$
-to denote the corresponding density, then integrating the first term in~(\ref{limit of mean measure equation})
-by parts, we find that in the limit as $N\to\infty$,
-\begin{equation*}
-\frac{d}{dt}\int f(x)\Xi_t(x)dx
+By choosing $\theta/N \rightarrow 0$, the second order term in the generator 
+will vanish and we expect a deterministic limit,
+for which $d/dt \langle f, \eta_t \rangle$ is equal to~\eqref{limit of mean measure equation}.
+In other words, the limit is a weak solution to the deterministic equation
+\begin{equation}
+\label{deterministic limit}
+\frac{d\varrho(x)}{dt}
 =
-\int f(x)\left\{r(x,\Xi_t)\DG\big(\gamma(\cdot,\Xi_t)
-\Xi_t(\cdot)\big)(x)
-+
-F(x,\Xi_t) \Xi_t(x)
-\right\} dx.
-\end{equation*}
-In other words, we can expect the limit to be a weak solution to the 
-deterministic equation
-\begin{equation}
-\label{deterministic limit}
-\frac{d\Xi}{dt}
-=r(x,\Xi)\DG\big(\gamma(\cdot,\Xi)
-\Xi(\cdot)\big)(x)+F(x,\Xi)
-\Xi(x).
-\end{equation}
-
-\subsubsection*{Limit II: stochastic case}
-
-If $N=\alpha\theta$, for some positive constant $\alpha$,
-the second order term in the generator remains order
-one as $\theta\to\infty$, and  
-we expect a `generalised superprocess' limit.
-Assuming some regularity of the coefficients (in particular of $r$), 
-the second order term in the generator will take the form
-$$
-\frac{1}{\alpha}F''(\langle f,\Xi\rangle)
-\langle f^2(x), \gamma(x,\Xi)
-r(x,\Xi)\Xi(dx)\rangle.
-$$
-That is
-$$\langle f(x), \Xi_t(dx)\rangle-\langle f(x), \Xi_0(dx)\rangle
--\int_0^t\langle\gamma(x,\Xi_s)\DG\big(r(\cdot,\Xi_s)f(\cdot)\big)(x),
-\Xi_s(dx)\rangle ds$$
-is a martingale with quadratic variation
-$$\frac{2}{\alpha}\int_0^t\langle f^2(x) 
-(\gamma(x,\Xi_s)r(x,\Xi_s)+\mu(x,\Xi_s)),\Xi_s(dx)\rangle ds.$$
-
-\plr{TODO: heuristics of conditions to get a local (PDE) limit?}
+    r(x,\varrho(x))
+    \DG\big(
+        \gamma(\cdot,\varrho) \varrho(\cdot)
+    \big)(x)
+    + F(x, \varrho(x)) \varrho(x) 
+\end{equation}
+in the sense of Definition~\ref{defn:weak_solutions},
+where $\varrho_t$ is the density of $\eta_t$, if it has a density.
+
+On the other hand, if $N = \alpha \theta$ for some $\alpha > 0$,
+the second order term remains, and we expect a ``generalised superprocess'' limit.
+The limiting quadratic variation
+is exactly as seen in Theorem~\ref{thm:nonlocal_convergence}.
 
@@
 informal calculations agree with the main result.
-Suppose that we are tracking a lineage that is at location $y$ at time $t$.
-Looking back through time, the lineage will move at the time that individual was born,
-and will jump to the location of the parent of that individual.
+Suppose that we have tracked a lineage to an individual at location $y$ at time $t$.
+Looking further back through time, the lineage will move at the time that individual was born,
+and will jump to that individual's parents' locations.
 Now, the rate at which new individuals are born to parents at $x$ and establish at $y$
@@
 whose transition rates are given by \eqref{eqn:informal_rates} given $(\varphi_t)_{t=0}^T$.
-Let $(L^\theta_s)_{s=0}^T$ be the location of a lineage that moves according to
-jump rates~\eqref{eqn:informal_rates},
+Let $(L^N_s)_{s=0}^T$ be the location of a lineage that moves according to these jump rates,
 back through time (i.e., with the substitution that $s = T-t$).
-Then, writing $q_\theta(x, y)$ for the density of $q_\theta$,
+Then, for the moment writing $q_\theta(x, y)$ for the density of $q_\theta$,
 \begin{align} \label{eqn:lineage_generator_Edt}
     \begin{split}
-    &\IE[f(L^\theta_{s+ds}) - f(y) \;|\; L_s = y]
+    &\IE[f(L^N_{s+ds}) - f(y) \;|\; L_s = y]
     \\&\qquad 
@@
 \end{align}
-\comment{I'm not sure if at this point in the paper we want to either
-(a) write out the next statement; (b) restrict to the $\DG = \Delta$ case,
-or (c) leave it as is (as an exercise for the reader, I guess?}
 Referring back to Definition~\ref{def:dispersal_generator},
-it is not too hard to show that as $N \to \infty$,
+a quick calculation shows that as $N \to \infty$,
 \begin{align*}
@@
 
+\comment{Should we just use $N$ instead of $\lambda$? Change to $N$ but comment that when comparing ot other papers set $\lambda=N$.}
+
 Now we will present a lookdown construction for the general process
-(i.e., of Definition \ref{Def: Rescaled Models}),
+(i.e., of Definition \ref{defn:mgale_construction}),
 in the spirit of~\cite{kurtz/rodrigues:2011}. 
-The key benefit of this construction is that
-we shall be able to preserve the notion of individuals,
-and in particular their genealogies,
-when we pass to the limit.
-
-The gneral set-up is as follows.
+The general set-up is as follows.
 Each individual will be labeled with a ``level'',
-which will be a number in $[0, \lambda]$.
-When taking the limit, we will set $\lambda = N$.
-\comment{Should we just use $N$ instead of $\lambda$? Or vice-versa? Change to $N$ but comment that when comparing ot other papers set $\lambda=N$.}
+which will be a number in $[0, N]$.
 We will still encode the process embellished by these levels
@@
 $$
-which is a measure on $\IR^d \times [0, \lambda]$.
-Note that the each individual contributes mass 1 to the measure,
+which is a measure on $\IR^d \times [0, N]$.
+Note that each individual contributes mass 1 to the measure,
 not $1/N$ as above.
@@
 Furthermore, the levels of the individuals present at any spatial location
-conditionally uniform on $[0, \lambda]$.
+are conditionally uniform on $[0, N]$.
 However, an individual's level in some sense encodes their future reproductive output:
@@
 For more explanation of the set-up and how this is possible,
-see \citet{etheridge/kurtz:2018} and \citet{kurtz/rodrigues:2011}.
+see \citet{etheridge/kurtz:2018} and \citet{kurtz/rodrigues:2011}
+(and note that our $N$ corresponds to the $\lambda$ of those papers).
 Furthermore, the limiting spatial-level process will still be a point measure,
@@
 we'll define the process $(\lp_t)_{t \ge 0}$ in terms of the dynamics of labeled particles,
-and write down it's generator.
+and write down its generator.
 Since the dynamics depend on the spatial locations of particles,
-we \emph{define} $\eta_t$ to be the corresponding spatial measure,
+in this section we define $\eta_t$ to be the corresponding spatial measure,
 i.e.,
 $$
-    \eta_t(\cdot) = \frac{1}{\lambda} \lp_t(\cdot \times [0, \lambda])  .
+    \eta_t(\cdot) = \frac{1}{N} \lp_t(\cdot \times [0, N])  .
 $$
@@
 this process has the same distribution as the process $(\eta_t)_{t \ge 0}$ defined above
-in Definition~\ref{Def: Rescaled Models},
-again, after setting $\lambda = N$.
+in Definition~\ref{defn:mgale_construction}.
 (This provides our justification for using the same notation for both.)
@@
     I've defined $\eta = \lp / N$ to agree with how we define the generator below,
-    for which birth/death add/remove something of mass 1, not $1/\lambda$.
+    for which birth/death add/remove something of mass 1, not $1/N$.
 }
@@
 
-Suppose that the initial population is composed of $O(\lambda)$ many particles
-with levels uniformly distributed between $[0, \lambda]$.
+Suppose that the initial population is composed of $O(N)$ many particles
+with levels uniformly distributed between $[0, N]$.
 Suppose the current state of the population is $\lp$,
 with spatial projection $\eta$.
-Each individual at spatial location $x$ with level $u$
+An individual at spatial location $x$ with level $u$
 produces one juvenile offspring at rate 
 $$
-2 \left(1 - \frac{u}{\lambda}\right) \gamma(x, \eta) ,
+2 \left(1 - \frac{u}{N}\right) \gamma(x, \eta) ,
 $$
@@
 
-A new level $u_1$ is sampled independently and uniformly from $[u,\lambda]$,
+A new level $u_1$ is sampled independently and uniformly from $[u,N]$,
 and the parent and the offspring are assigned in random order to the levels $\{u, u_1\}$.
@@
     =
-    % \gamma^{\mathfrak{m}}(x, \eta) \left\{\lambda^{-1}(\lambda -v)^{2} -(\lambda -v)\right\}.
-    - \frac{v}{\lambda} \left(\lambda - v\right)
+    % \gamma^{\mathfrak{m}}(x, \eta) \left\{N^{-1}(N -v)^{2} -(N -v)\right\}.
+    - \frac{v}{N} \left(N - v\right)
     \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q(x, dy) .
 $$
-Since $v \in [0, \lambda]$, this moves levels down;
+Since $v \in [0, N]$, this moves levels down;
 see~\cite{etheridge/kurtz:2018}, Section~3.4 for a detailed explanation.
@@
 In the lookdown model, levels never cross below 0,
-while particles whose levels move above $\lambda$ are regarded as dead
+while particles whose levels move above $N$ are regarded as dead
 (and do not affect to the population any more).
@@
 this would imply an exponential lifetime for each individual;
-see~\cite{etheridge/kurtz:2018}, Section \comment{XXX}
+see~\cite{etheridge/kurtz:2018}, Section \comment{TODO}
 for more general justification.
@@
 Putting these together,
-the level $u$ of an individual at $x$ in $\lp$ evolves according to:
+the level $u$ of an individual at $x$ evolves according to:
 \begin{equation} \label{eqn:dot_u}
@@
     =
-    - \frac{\theta}{\lambda} u \left(\lambda - u\right)
+    - \frac{1}{N} u \left(N - u\right)
     \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q(x, dy) 
@@
 \end{equation}
-The factor of $\theta$ appears here because we have rescaled time.
 We shall write 
@@
 We can then rewrite the differential equation 
-governing how the level of each individual
-in $\lp$ evolves as
+governing how the level of each individual evolves as
 \begin{align}
@@
     &=
-    \theta \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy)
+    \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy)
     \left\{
-        -\frac{u}{\lambda}\left(\lambda - u\right)
+        -\frac{u}{N}\left(N - u\right)
         + u
@@
     -
-    b(x,\eta) u
+    b(x,\eta) u / \theta
     \nonumber \\
     &=
-    \frac{\theta}{\lambda} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
+    \frac{1}{N} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
     -
-    b(x, \eta) u
+    b(x, \eta) u / \theta
     . \label{differential equation for level}
 \end{align}
-(The factor of $\theta$ appears because of the rescaling of time for $\lp$.)
 
@@
 smooth in $x$.
-We will also assume that $0\leq g(x,u) \leq 1$ for all $u\in [0,\lambda]$,
-and $g(x,u)\equiv 1$ for $u\geq \lambda$.
+We will also assume that $0\leq g(x,u) \leq 1$ for all $u\in [0,N]$,
+and $g(x,u)\equiv 1$ for $u\geq N$.
 In the expressions that follow,
@@
 
-\comment{Maybe we can not introduce $\theta$ before this point in this section, and say we'll put it in now?}
-
-Recall also that in defining $\eta_t$
-we had not only rescaled mass, dividing each individual's mass by $N$,
-but also time, speeding up time by a factor of $\theta$.
-As a result, per-capita rates described above will have a factor of $\theta$ here.
+Recall that just as with $\eta_t$, in defining $(\lp_t)_{t \ge 0}$
+we sped up time by a factor of $\theta$.
+As a result, per-capita rates below will have a factor of $\theta$
+not present in the expressions above.
 
 First consider the terms in the generator that come from birth events.
-Recall that when a birth successfully establishes,
+When a birth successfully establishes,
 a new level is generated above the parent's level,
@@
     \sum_{(x, u) \in \lp}
-    2 \frac{\theta}{\lambda} \gamma(x, \eta)
-    \int_u^\lambda
+    2 \frac{\theta}{N} \gamma(x, \eta)
+    \int_u^N
     \int_{\IR^d}
@@
     \bigg\{
-        \frac{1}{2 \lambda}
-        \int_u^\lambda
+        \frac{1}{2 N}
+        \int_u^N
         g(x, u_1) du_1
@@
     \\ & \qquad \qquad \qquad {}
-        + \frac{\theta}{\lambda}
-        \int_u^\lambda \int_{\IR^d}
+        + \frac{\theta}{N}
+        \int_u^N \int_{\IR^d}
         \left( \frac{g(y, u_1) + g(x, u_1)}{2} - 1 \right)
@@
 and so the two terms in the integral correspond to the two situations:
-in the first, we have added an individual at $(y, u)$,
+in the first, we have added an individual at $(y, u_1)$,
 while in the second, we replace an individual at $(x, u)$
@@
 We've written it in this form because the two pieces
-each naturally converge to separate terns in the limit.
+each naturally converge to separate terms in the limit.
 
@@
     \left(
-    \theta
-        \lambda^{-1} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
+    \frac{\theta}{N}
+        \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
         -
@@
 
-\comment{TODO: this note goes much earlier.}
-To scale our lookdown model to be consistent with
-the spatial model described in \S \ref{sec: Model and main results},
-we will let $\lambda$ takes on the role of $N$
-in \S \ref{sec: Model and main results},
-i.e. each individual has mass $1/\lambda$
-in the scaling limit.
-Time is once again scaled by $\theta$,
-and the birth, death and establishment rates 
-depend on local densities given by
-mollification over Gaussian kernels with radius
-$\epsilon_{\gamma}$, $\epsilon_{F}$ and $\epsilon_{r}$.
-
-Explicitly, in the $\theta$-th stage of re-scaling,
-an individual has mass $\frac{1}{\lambda} := \frac{1}{N}$
-and a level between $[0,N]$;
-the birth rate is
-$$
-    \gamma(x, \eta)
-    :=
-    \gamma(x, \smooth{\gamma}\eta(x)),
-$$
-the establishment probability is
-$$
-    r(x, \eta)
-    :=
-    r(x, \smooth{r}\eta(x)),
-$$
-the local branching mechanism $b(x,\eta)$ is 
-$$
-    b_{\theta}(x, \eta)
-    :=
-    \theta \left(
-        \gamma(x, \smooth{\gamma}\eta(x))
-        \int r(y, \smooth{r}\eta(y)) q_{\theta}(x,dy)
-        -
-        \mu(x, \eta)
-    \right) .
-$$
-and the dispersal kernel is $q_\theta$.
-
 We can now define the spatial-level process
@@
     \label{defn:lookdown_mgale}
-We define $(\lp^{\theta}_t)_{t \geq 0}$
+For given positive values of $N$ and $\theta$,
+we define $(\lp^{N}_t)_{t \geq 0}$
 to be the (unique) solution
-    \comment{(I'm not sure why unique is in parentheses here?)}
 to the Martingale Problem
 with initial condition $\lp_0 \in \mathcal{M}_F(\mathbb{R}^d \times [0,N])$
-and generator $A^{\theta}$ that satisfies
+and generator $A^{N}$ that satisfies
 \begin{equation*}
 \begin{split}
-& A^{\theta}f(\lp ) \\
+& A^{N}f(\lp ) \\
 &\quad =
@@
     &\qquad\qquad\qquad\qquad\qquad\qquad\qquad {} +
-        N^{-1}\theta\int_u^N
+        \frac{\theta}{N} \int_u^N
         \int_{\mathbb{R}^d}\left(
@@
     \left(
-        \theta N^{-1} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q_\theta(x, dy) u^2 -b_{\theta}(x,\eta)u
+        \frac{\theta}{N} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q_\theta(x, dy) u^2 -b_{\theta}(x,\eta)u
     \right)
@@
 where $f(\lp) = \prod_{(x, u) \in \lp} g(x, u)$ as defined in \eqref{eqn:test_functions},
-and $\eta(\cdot) = \lp(\cdot \times [0, N]) / N$ is the spatial pushforward of $\lp$,
+and $\eta(\cdot) = \lp(\cdot \times [0, N]) / N$ is the scaled spatial pushforward of $\lp$,
 as before.
 \end{definition}
+
+\comment{I don't think this bit quite makes sense yet without understanding the MMT
+section (but, it should be understandable without understanding that section).}
 
@@
 \begin{aligned}
-M^{\theta}_t:=&\hat{f}(\lp_t)-\hat{f}(\lp_0)-\int_{0}^{t}\int   A^{\theta}f(\lp_s)\Gamma(d\textbf{u})ds\\
-:=&\hat{f}(\lp_t)-\hat{f}(\lp_0)-\int_{0}^{t}   \Pgen^{\theta}\hat{f}(\lp_s)ds
+M^{N}_t:=&\hat{f}(\lp_t)-\hat{f}(\lp_0)-\int_{0}^{t}\int   A^{N}f(\lp_s)\Gamma(d\textbf{u})ds\\
+:=&\hat{f}(\lp_t)-\hat{f}(\lp_0)-\int_{0}^{t}   \Pgen^{N}\hat{f}(\lp_s)ds
 \end{aligned}    
@@
 By the Markov Mapping Theorem,
-there exists a solution $(\xi^{\theta}_t)_{t \geq 0}$
-to the Martingale Problem with generator $A^{\theta}$.
+there exists a solution $(\lp^{N}_t)_{t \geq 0}$
+to the Martingale Problem with generator $A^{N}$.
 Furthermore,
-the spatial projection of $(\xi^{\theta}_t)_{t \geq 0}$
-shares the same law of $(\eta^{\theta}(t))_{t \geq 0}$,
+the spatial projection of $(\lp^{N}_t)_{t \geq 0}$
+shares the same law of $(\eta^{N}(t))_{t \geq 0}$,
 i.e.
-$$(\eta^{\theta}(t))_{t \geq 0}
-\sim \left(\frac{1}{N}\sum\limits_{(X(t),U(t))\in \xi^{\theta}(t)} \delta_{X(t)}\right)_{t \geq 0},$$
+$$(\eta^{N}(t))_{t \geq 0}
+\sim \left(\frac{1}{N}\sum\limits_{(X(t),U(t))\in \lp^{N}(t)} \delta_{X(t)}\right)_{t \geq 0},$$
 and conditional on 
-$(\eta^{\theta}(t))_{t \geq 0}$,
-the levels of particles in $(\xi^{\theta}_t)_{t \geq 0}$
+$(\eta^{N}(t))_{t \geq 0}$,
+the levels of particles in $(\lp^{N}_t)_{t \geq 0}$
 are i.i.d. uniformly distributed between $[0,N]$.
@@
 Theorem A.10 in \cite{kurtz/rodrigues:2011}
-states that convergence of $(\eta^{\theta}_t)_{t \geq 0}$
-to a conditionally Poisson system $(\xi_t)_{t \geq 0}$
-with Cox measure $\Xi_t \times \Lambda$
+states that convergence of $(\eta^{N}_t)_{t \geq 0}$
+to a conditionally Poisson system $(\lp_t)_{t \geq 0}$
+with Cox measure $\eta_t \times \Lambda$
 is equivalent to convergence of
-$(\eta^{\theta}_t)_{t \geq 0}$ to $(\Xi_t)_{t \geq 0}$.
+$(\eta^{N}_t)_{t \geq 0}$ to $(\eta_t)_{t \geq 0}$.
 As a result, it suffices for us to focus on
-tightness of $(\eta^{\theta}_t)_{t \geq 0}$
-and spatial convergence of $(\eta^{\theta}_t)_{t \geq 0}$
+tightness of $(\eta^{N}_t)_{t \geq 0}$
+and spatial convergence of $(\eta^{N}_t)_{t \geq 0}$
 as $N \to \infty$.
@@
 
-Although we will \comment{(later)} show convergece of the lookdown process
+Although in Section \ref{sec:proofs} we will show convergence of the lookdown process
 defined by Definition~\ref{defn:lookdown_mgale}
@@
 in a way that explicitly represents the motion of each individual and their offspring.
-This will then make obvious how linages move in the limit.
+This will then make obvious how lineages move in the limit,
+and will allow us to identify all 
+individuals in the current population that are descendants of a
+given ancestor at time zero. In theory at least, this allows us to
+recover all the information about genealogies relating individuals 
+sampled from the present day population. This idea draws on the notion
+of `tracers', popular in statistical physics and used in population
+genetics by a number of authors including 
+\cite{biswas/etheridge/klimek:2018, durrett/fan:2016, hallatschek/nelson:2008}.
 
@@
 let $\Pi_a$ be an independent Poisson process on $[0, \infty)^2 \times \IR_d \times \{0,1\}$.
-The mean measure is a product of Lesbegue measure on the first two coordinates,
+The mean measure is a product of Lebesgue measure on the first two coordinates,
 $q(0, \cdot)$ on $\IR^d$, and $(\delta_0 + \delta_1)/2$ on $\{0, 1\}$.
@@
 and the new label produced will be $a \concat j$,
-i.e., the label $a$ with $j$ appended (so, if $a \in \IN_{\ge 0}^k$ then $aj \in \IN_{\ge 0}^{k+1}$).
+i.e., the label $a$ with $j$ appended (so, if $a \in \IN_{\ge 0}^k$ then $a \concat j \in \IN_{\ge 0}^{k+1}$).
 Each label $a$ has a birth time $\tau_a$,
 when it is first assigned,
-and a death time $\sigma_a$, when its level first hits $\lambda$.
+and a death time $\sigma_a$, when its level first hits $N$.
 For any $\tau_a \le t \le \sigma_a$ we denote by $X_a(t)$ and $U_a(t)$ the spatial location and level
@@
 Now, since we have defined labels so that the level does not jump,
-$U_a$ satistifies~\eqref{eqn:dot_u} for $\tau_a \le t \le \sigma_a$, i.e.,
+$U_a$ satisfies~\eqref{eqn:dot_u} for $\tau_a \le t \le \sigma_a$, i.e.,
 \begin{equation} \label{eqn:U_line_of_descent}
@@
     \left(
-        \frac{\theta}{\lambda} \gamma(X_a(s),\eta(s))
-        \int_{\IR^d} r(z,\eta(s)) q(X_a(s),dz) U_a(s)^2
+        \frac{\theta}{N} \gamma(X_a(s),\eta_s)
+        \int_{\IR^d} r(z,\eta_s) q(X_a(s),dz) U_a(s)^2
         -
-        b(X_a(s),\eta(s)) U_a(s)
+        b(X_a(s),\eta_s) U_a(s)
     \right)
@@
 \end{equation}
-and, of course, $\sigma_a = \inf\{t \ge \tau_a : U_a(t) > \lambda\}$.
+and, of course, $\sigma_a = \inf\{t \ge \tau_a : U_a(t) > N\}$.
 
@@
 for each point $(s, v, y, \kappa) \in \Pi_a$.
-We say `potential' since if the resulting level is greater than $\lambda$,
+We say `potential' since if the resulting level is greater than $N$,
 the event does not happen.
@@
     }{
-        2 \lambda^{-1} \theta \gamma(x, \eta) r(x + y, \eta)
+        2 N^{-1} \theta \gamma(x, \eta) r(x + y, \eta)
     } ,
@@
 \end{equation*}
-If $U_{a \concat j}(\tau_{a \concat j}) < \lambda$,
+If $U_{a \concat j}(\tau_{a \concat j}) < N$,
 the new individual labeled $a \concat j$ is produced,
@@
 \begin{align*}
-    X_{a \concat j}(\tau_a + s)
+    X_{a \concat j}(\tau_{a \concat j})
     &=
-    X_a(\tau_a+s-) + (1 - \kappa) y .
+    X_a(\tau_{a \concat j}-) + (1 - \kappa) y .
 \end{align*}
 On the other hand
-if $U_{a \concat j}(\tau_a+s) \ge \lambda$, then $X_a$ is unchanged and $X_{a \concat j}$ is undefined,
+if $U_{a \concat j}(\tau_{a \concat j}) \ge N$, then $X_a$ is unchanged and $X_{a \concat j}$ is undefined,
 so
 \begin{align} \label{eqn:X_line_of_descent}
-    X_a(\tau_a+s)
+    X_a(\tau_{a \concat j})
     &=
-    X_a(\tau_a+s-) + \kappa y \ind_{U_{a \concat j}(\tau_{a \concat j}) < \lambda} .
+    X_a(\tau_{a \concat j}-) + \kappa y \ind_{U_{a \concat j}(\tau_{a \concat j}) < N} .
 \end{align}
@@
 
-We can now express our population processes using these levels:
+Although we have described the evolution of a line of descent only for a given label
+(i.e., for $\tau_a \le t < \sigma_a$),
+we can extend the definition to earlier times
+by setting for $0 \le t < \sigma_a$
+$X_a(t)$ equal to $X_{[a]_t}(t)$,
+where $[a]_t$ is the label of the ancestor of label $a$ alive at time $t$,
+and similarly for $U_a(t)$.
+It is then straightforward, albeit tedious,
+to write down the time evolution of $(X_a(t), U_a(t))$ for all time back to $t=0$
+in terms of the driving Poisson processes.
+Although at finite $N$ the spatial process $X_a(t)$ is affected by jumps in the level $U_a(t)$,
+we will see that in the $N \to \infty$ limit
+the behavior of $X_a(t)$ is not affected by these jumps.
+
+We can now express the population processes using these levels:
 \begin{align*}
-    \eta_t = \frac{1}{\lambda} \sum_{a : \tau_a > t \;\&\; U_a(t) < \lambda} \delta_{X_a(t)}
+    \eta^N_t = \frac{1}{N} \sum_{a : \tau_a \le t < \sigma_a} \delta_{X_a(t)}
     \qquad \text{and} \qquad
-    \lp = \sum_{a : \tau_a > t \;\&\; U_a(t) < \lambda} \delta_{(X_a(t), U_a(t))} .
+    \lp^N_t = \sum_{a : \tau_a \le t < \sigma_a} \delta_{(X_a(t), U_a(t))} .
 \end{align*}
-
-\begin{remark}
-    \comment{TODO: say that it's clear how this works following a line of descent
-    all the way from time 0 (in particular, in the infinite density limit,
-    just the spatial part looks just the same despite the jumps in level).}
-\end{remark}
 
@@
 The previous section constructs the lookdown process
-in a way that makes individual lines of descent converge pointwise as $\lambda \to \infty$,
+in a way that makes individual lines of descent converge pointwise as $N \to \infty$,
 using the same underlying Poisson processes $\{\Pi_a\}_{a \in \labelspace}$.
@@
 Therefore, the processes $\Gamma_a$ are also unchanged.
-First, we clearly need that the spatial measures $\eta$ converge.
-\comment{(hm, no notation for $\eta$ depending on $\lambda$ here; need to introduce this here?)}
+First, we clearly need that the spatial projections $\eta$ converge.
 
@@
 \begin{equation} \label{eqn:line_points}
-v < 2 (\lambda - U_a(t)) \lambda^{-1} \theta \gamma(X_a(t), \eta) r(X_a(t)+y, \eta) .
+    v < 2 (N - U_a(\tau_a + s)) N^{-1} \theta \gamma(X_a(\tau_a + s), \eta_{\tau_a + s}) r(X_a(\tau_a + s)+y, \eta_{\tau_a + s}) .
 \end{equation}
 Since the mean measure of the $v$ coordinate is Lebesgue,
-$\theta/\lambda \to \alpha$,
+$\theta/N \to \alpha$,
 and $q(x, dy) \to \delta_x(dy)$,
@@
 $$
-\alpha \gamma(X_a(t), \eta) r(X_a(t), \eta) 
+2 \alpha \gamma(X_a(t), \eta_{\tau_a + s}) r(X_a(t), \eta_{\tau_a + s}) 
 $$
@@
 and rewriting~\eqref{eqn:line_points},
-the generator of this motion is, when the level is $u$,
+the generator of this motion is, when the level is $u$
+and the state of the population is $\eta$,
 \begin{align*}
@@
     &\mapsto
-    \left(1 - \frac{u}{\lambda}\right) \gamma(x, \eta)
+    \left(1 - \frac{u}{N}\right) \gamma(x, \eta)
     \theta \int_{\IR^d} r(x+y, \eta) (g(x+y) - g(x)) q(x, dy) \\
     &=
-    \left(1 - \frac{u}{\lambda}\right) \gamma(x, \eta)
+    \left(1 - \frac{u}{N}\right) \gamma(x, \eta)
     \bigg\{
@@
 
-The only thing that remains is to describe how the levels change.
-The limit of~\eqref{eqn:line_points} follows from
-equation \eqref{eqn:b_limit} and the fact that
-$\int_{\IR^d} r(z, \eta) q(x, dz) \to r(x, \eta)$.
+The only thing that remains is to describe how the levels change,
+but this is immediate from applying equation~\eqref{eqn:b_limit}
+to equation~\eqref{differential equation for level}.
 
@@
 
-\comment{The following could be a Proposition?}
-
-Now, let $\beta(x, \eta) = \meanq + 2 \Sigma \grad \log r(x, \eta)$,
-and associate with each label an independent $d$-dimensional Brownian motion $W_a$,
-and let $\covq = K K^T$.
-Then, we can summarize the results above by saying that
-in the infinite density limit,
-the spatial locations and level of each line of descent $a$
-behave for $\tau_a \le t < \sigma_a$ as
+We summarize the results in a proposition.
+
+\begin{proposition}[Line of descent construction]
+Let $\beta(x, \eta) = \meanq + 2 \covq \grad \log r(x, \eta)$
+and $K$ such that $\covq = K K^T$.
+Associate with each label $a \in \labelspace$
+an independent $d$-dimensional Brownian motion $W_a$
+and an independent Poisson process $R_a$ on $[0, \infty)^2$
+with Lebesgue mean measure,
+as before with points ordered in some way.
+Given $\eta_0 \in \measures$,
+let $(x_i, u_i)$ be the points of a Poisson process
+with mean measure on $\IR^d \times [0, \infty)$ a product of $\eta_0$ and Lebesgue measure.
+For each point begin a line of descent
+with label $i$, location $X_i(0) = x_i$, level $U_a(0) = u_i$, and birth time $\tau_i = 0$.
+Suppose that the spatial locations and level of each line of descent $a$
+behave, for $\tau_a \le t < \sigma_a$ as, as
 \begin{align*}
@@
 \end{align*}
-To complete the description,
-for each label $a \in \labelspace$ let $R_a$ denote an independent Poisson process on $[0, \infty)^2$
-with Lebesgue mean measure,
-and as before order the points of each in some way.
-If the population state at time 0 is $\eta(0)$,
-then let $(x_i, u_i)$ be the points of a Poisson process
-with mean measure on $\IR^d \times [0, \infty)$ a product of $\eta(0)$ and Lebesgue measure.
-\comment{Here I've switched $t$ to be the absolute birth time
-rather than relative to the birth time of the parent; I think it's clearer?
-It, should be made to agree with the previous section.}
-For each point begin a line of descent
-with label $i$, location $X_i(0) = x_i$, level $U_a(0) = u_i$, and birth time $\tau_i = 0$.
 Each point in the $R_a$ denotes a potential birth time for $a$:
-if the $j^\text{th}$ point in $R_a$ is $(t, v)$,
-$\tau_a \ge t$, and and $U_a(t) < \infty$,
+if the $j^\text{th}$ point in $R_a$ is $(t, v)$, with $t < \sigma_a - \tau_a$,
 then a new line of descent with label $a \concat j$ is produced,
-with birth time $\tau_{a \concat j} = t$, location $X_{a \concat j}(t) = X_a(t)$, and level
-$$
-    U_{a \concat j}(t) = U_a(t)
-    + \frac{v}{ 2 \alpha \gamma(X_a(t), \eta(t)) r(X_a(t), \eta(t)) } .
-$$
-\comment{Perhaps the conclusion of the Propostion would be something like:}
-We can now express our population processes in the limit using these levels:
+with birth time $\tau_{a \concat j} = \tau_a + t$,
+location $X_{a \concat j}(\tau_a + t) = X_a(tau_a + t)$, and level
+$$
+    U_{a \concat j}(tau_a + t) = U_a(tau_a + t)
+    + \frac{v}{ 2 \alpha \gamma(X_a(\tau_a + t), \eta_{tau_a + t}) r(X_a(\tau_a + t), \eta_{\tau_a + t}) } .
+$$
+For each $a$, let $\sigma_a = \inf\{t \ge 0: U_a(t) < \infty\}$.
+Then, the processes defined by
 \begin{align*}
-    \eta_t = \lim_{\lambda \to \infty} \frac{1}{\lambda} \sum_{a : \tau_a > t \;\&\; U_a(t) < \lambda} \delta_{X_a(t)}
+    \eta_t = \lim_{N \to \infty} \frac{1}{N} \sum_{a : \tau_a \le t < \sigma_a} \delta_{X_a(t)}
     \qquad \text{and} \qquad
-    \lp = \sum_{a : \tau_a > t} \delta_{(X_a(t), U_a(t))} .
+    \lp_t = \sum_{a : \tau_a \le t < \sigma_a} \delta_{(X_a(t), U_a(t))} 
 \end{align*}
-
-\comment{TODO: incorporate this in the discussion somewhere (and maybe other refs? see previous version).}
-This representation of individuals allows us to identify all 
-of the individuals in the current population that are descendants of a
-given ancestor at time zero. In theory at least, this allows us to
-recover all the information about genealogies relating individuals 
-sampled from the present day population. This idea draws on the notion
-of `tracers', popular in statistical physics and used in population
-genetics by a number of authors including 
-\cite{biswas/etheridge/klimek:2018, durrett/fan:2016, hallatschek/nelson:2008}.
+agree in distribution with those of Definitions~\ref{defn:mgale_construction} and~\ref{defn:lookdown_mgale},
+respectively.
+\end{proposition}
 
@@
 Similarly, we can recover
-Definition \ref{Def: Rescaled Models},
+Definition \ref{defn:mgale_construction},
 an equivalent characterisation
@@
 Furthermore, by our assumption on $g$,
-$\int_u^\lambda g(x, u_1) du_1 / \lambda \to 1$ for all $x$ and $u$,
+$\int_u^N g(x, u_1) du_1 / N \to 1$ for all $x$ and $u$,
 so the first term here converges to
@@
 since $\int g(y, u_1) q(x, dy) \to g(x, u_1)$
-and $\theta/\lambda \to \alpha$,
+and $\theta/N \to \alpha$,
 it converges to
@@
     \theta
-        \lambda^{-1} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
+        N^{-1} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
         -
@@
 \end{align*}
-The first part only uses the fact that $\theta/\lambda \to \alpha$,
+The first part only uses the fact that $\theta/N \to \alpha$,
 while as noted in \eqref{eqn:b_limit}, $b$ converges to $\gamma \DG r + F$,
@@
 be $v \exp(-\int_s^t(F+\gamma\Delta r)(Y_u)du)$. This will be less than a given level 
-$\lambda$ if $v < \lambda \exp(\int_s^t(F+\gamma\Delta r)(Y_u)du)$. 
+$N$ if $v < N \exp(\int_s^t(F+\gamma\Delta r)(Y_u)du)$. 
 The intensity of levels at $y$ that are descended from individuals at
-$x$ can therefore be obtained as the limit as $\lambda\to\infty$ of 
-$1/\lambda$ times the number of levels at $x$ at time zero with
-$u<\lambda \exp(\int_s^t(F+\gamma\Delta r)(Y_u)du)$ and for which
+$x$ can therefore be obtained as the limit as $N\to\infty$ of 
+$1/N$ times the number of levels at $x$ at time zero with
+$u<N \exp(\int_s^t(F+\gamma\Delta r)(Y_u)du)$ and for which
 the corresponding individual is at $y$ at time $t$, which is 
@@
 be $u\exp(-\int_0^t(F+\gamma\Delta r)(Y_s)ds)$. This will be less than a given level 
-$\lambda$ if $u<\lambda \exp(\int_0^t(F+\gamma\Delta r)(Y_s)ds)$. 
+$N$ if $u<N \exp(\int_0^t(F+\gamma\Delta r)(Y_s)ds)$. 
 The intensity of levels at $y$ that are descended from individuals at
-$x$ can therefore be obtained as the limit as $\lambda\to\infty$ of 
-$1/\lambda$ times the number of levels at $x$ at time zero with
-$u<\lambda \exp(\int_0^t(F+\gamma\Delta r)(Y_s)ds)$ and for which
+$x$ can therefore be obtained as the limit as $N\to\infty$ of 
+$1/N$ times the number of levels at $x$ at time zero with
+$u<N \exp(\int_0^t(F+\gamma\Delta r)(Y_s)ds)$ and for which
 the corresponding individual is at $y$ at time $t$, which is 

### 2022-05-12 figures/make_plots.sh
figures

@@ -26,5 +26,19 @@ do
         slim -s 123 ../pme.slim
     fi
     ../lineage_plotting/plot_1d_lineages.py pme_123.trees 3 1 3 3
+    ../lineage_plotting/pme/plot_pme_density.py pme_123.trees 45 55 6
+    popd
+done
+
+# comparison of three wave models
+for MODEL in fkpp pme allen-cahn
+do
+    DIR="ex3_${MODEL}"
+    pushd $DIR
+    if [ ! -e ${MODEL}_123.trees ]
+    then
+        slim -s 123 ../${MODEL}.slim
+    fi
+    ../lineage_plotting/plot_1d_lineages.py ${MODEL}_123.trees 3 1 3 3
     popd
 done

### 2022-05-19 OneStepConvergence.tex
Update on Overleaf.

\documentclass[a4paper,12pt]{article}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bbm}
\usepackage[margin=1in]{geometry}
\usepackage{mathrsfs}
\usepackage[color=yellow]{todonotes}
\usepackage{tikz}
\usepackage{enumitem}
\usetikzlibrary{arrows}
\usetikzlibrary{shapes}
%\usepackage{subcaption} 
\usepackage[utf8]{inputenc}
\usepackage[backend=biber,style=alphabetic, maxbibnames=99]{biblatex}
\addbibresource{Mendeley.bib}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{assumptions}[theorem]{Assumptions}
\newtheorem{assumption}[theorem]{Assumption}

\newcommand{\norma}{\mathrm{Norm}}
\newcommand{\EE}{\mathbb{E}}
\newcommand{\IE}{\mathbb{E}}
\newcommand{\FF}{\mathbb{F}}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\IN}{\mathbb{N}}
\newcommand{\OP}{\mathbb{O}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\IP}{\mathbb{P}}
\newcommand{\QQ}{\mathbb{Q}}
\newcommand{\IQ}{\mathbb{Q}}
\newcommand{\GG}{\mathbb{G}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\IR}{\mathbb{R}}
\newcommand{\AS}{\mathbb{S}}
\newcommand{\AT}{\mathbb{T}}
\newcommand{\IT}{\mathbb{T}}
\newcommand{\VV}{\mathbb{V}}
%\newcommand{\DD}{\mathbb{D}}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\IZ}{\mathbb{Z}}
\newcommand{\qm}{{\mathfrak q}}
\newcommand{\A}{{\cal A}}
\newcommand{\B}{{\cal B}}
\newcommand{\C}{{\cal C}}
\newcommand{\D}{{\cal D}}
\newcommand{\E}{{\cal E}}
\newcommand{\F}{{\cal F}}
\newcommand{\G}{{\cal G}}
\newcommand{\hH}{{\cal H}}
\newcommand{\K}{{\cal K}}
\newcommand{\I}{{\cal I}}
\newcommand{\T}{{\cal T}}
\newcommand{\J}{{\cal J}}
\newcommand{\aL}{{\cal L}}
\newcommand{\aB}{{\bf B}}
\newcommand{\aP}{{\bf P}} 
\newcommand{\aE}{{\bf E}}
\newcommand{\wP}{{\widetilde{P}}}
\newcommand{\M}{{\cal M}}
\newcommand{\N}{{\cal N}}
\newcommand{\cO}{{\cal O}}
\newcommand{\R}{{\cal R}}
\newcommand{\hS}{{\cal S}}
\newcommand{\tT}{{\cal T}}
\newcommand{\U}{{\cal U}}
\newcommand{\V}{{\cal V}}
\newcommand{\dd}{{\mathbbm{d}}}

\newcommand{\bigO}[1]{{\mathcal {O}\left(#1\right)}}
\newcommand{\littleo}[1]{{\emph{o}\left(#1\right)}}

\newcommand{\W}{{\mathbf W}} %%% I AM CHANGING THIS HERE TO SAVE CHANGING ALL THE \W's TO SOMETHING ELSE, BUT WANT CONSISTENT NOTATION FOR ONE-DIMENSIONAL AND MULTI-DIMENSIONAL HISTORICAL PROCESSES

\newcommand{\X}{{\cal X}}
\newcommand{\Y}{{\cal Y}}
\newcommand{\cZ}{{\cal Z}}
\newcommand{\FV}{{SLFVS$\Omega$}}
\newcommand{\oI}{{\overline{I}}}
\newcommand{\oJ}{{\overline{J}}}
\newcommand{\oK}{{\overline{K}}}
\newcommand{\oL}{{\overline{L}}}
\newcommand{\omu}{{\overline{\mu}}}
\newcommand{\orh}{{\overline{\rho}}}
\newcommand{\oAS}{{\overline{\AS}}}
\newcommand{\trho}{{\widehat{\rho}}}
\newcommand{\Int}{{\rm int}}
\newcommand{\oX}{{\G^+_0}}
\newcommand{\Cl}{{\rm cl}}
\newcommand{\1}{{\bf {1}}}
\def\v{\boldsymbol} %for vectors in bold text, use as \v{x
\font\gsymb=cmsy10 scaled \magstep3
\newcommand{\gtimes}{\hbox{\gsymb \char2}}
\def\hbn{\hfill\break\noindent}
\def\hch{\hfill\cr\hfill}
\let\scr=\scriptstyle
\def\sgn{\mathop{\rm sgn}\nolimits}
\def\One{{\mathbf 1}}
\def\one{ {\rm 1 \hskip -2.7pt  I}}
\def\d{^{\delta}}
\newcommand{\ds}{\displaystyle}
\newcommand{\lt}{\leadsto}

\def\v{\boldsymbol} %for vectors in bold text, use as \v{x}

\def\dim{\mathbbm{d}}

\def\Ca{($\mathscr{C}1$)}
\def\Cb{($\mathscr{C}2$)}
\def\Cc{($\mathscr{C}3$)}
\def\Cd{($\mathscr{C}4$)}
\def\Ce{($\mathscr{C}5$)}

\def\epsilon{\varepsilon}

\begin{document}

These notes are an attempt of writing the one-step convergence of the particle system to a PDE limit.

\textbf{In this whole document $\rho_\epsilon$ will be the density of a normal with mean $0$ and variance $\epsilon^2$, and $q_\theta$ the density of a normal with mean $0$ and variance $1/\theta$. That is, $\rho_\epsilon(x) = p_{\epsilon^2}(x)$ and $q_\theta = p_{1/\theta}(x)$.}

In this document we assume we have the particle system with (unscaled) birth rate constant and equal $1$ and death rate at position $x$ given by $1+F(\rho_\epsilon*\overline{\eta}(x))/\theta$. That is, the martingale problem for the scaled system $\overline{\eta}_t$, is that for any smooth function $\phi$ we can write
\begin{align}
&\langle\phi(x),\overline{\eta}_{t}(dx)\rangle-\langle\phi(x),\overline{\eta}_{0}(dx)\rangle = M_t(\phi)   + \int_{0}^{t}\langle \theta  \int_{\mathbb{R}^d} \left( \phi(y)-\phi(x)\right) q_\theta(x,dy), \overline{\eta}_s^\epsilon(dx) \rangle ds \nonumber \\
 & + \int_0^t \langle  F(\langle \rho_\epsilon(y-x), \overline{\eta}_s(dy) \rangle)\phi(x),\overline{\eta}_s^{\varepsilon, \theta, N}(dx)  \rangle ds. \label{mgp1}
\end{align}
where $M_t(\phi)$ is a martingale with quadratic variation:
\begin{align}
[M(\phi)]_t&:=\frac{\theta}{N}\int_{0}^{t}\bigg\{ \left\langle \int_{\mathbb{R}^d} \phi^2(y) q_\theta(x,dy), \overline{\eta}_s^{\varepsilon, \theta, N}(dx) \right\rangle \nonumber\\
&+ \left\langle  \left(2 + \frac{F(\langle \rho_\epsilon(y-x), \overline{\eta}_s(dy)\rangle )}{\theta } \right)\phi^2(x), \overline{\eta}_s^{\varepsilon, \theta, N}(dx))\right\rangle   \bigg\}ds.  \label{mgp2}
\end{align}

We have the following result.

\begin{theorem} \label{TeoremOneStepConvergence}
Let $(\overline{\eta}_t)_{t \geq 0}$ be the scaled particle system with $r_\theta \equiv \gamma_\theta = 1$. Suppose $F(x)$ is a polynomial such that:
\begin{enumerate}
\item $F(x)1_{x>0}$  is bounded above.
\item $|F'(x)1_{x>0}|$ is bounded.
\end{enumerate}
We will also suppose $\theta$ is big enough so that $1- \frac{F(x)1_{x>0}}{\theta}$ is non-negative.

We will assume $\overline{\eta}_0:=\overline{\eta}_0(\epsilon,N,\theta)$ is a sequence of initial conditions for $(\overline{\eta}_t)_{t \geq 0}$ such that there exists a finite constant $C>0$ independent of $\epsilon, N, \theta$, 
\begin{enumerate}
\item $\langle 1 , \overline{\eta}_0 \rangle < C $
\item  $\Vert \rho_\epsilon * \overline{\eta}_0(x) \Vert_\infty < C$ for all $x \in \mathbb{R}^d$
\item $|\rho_\epsilon * \overline{\eta}_0(x) - \rho_\epsilon * \overline{\eta}_0(y)| \leq C \Vert x - y \Vert  $ for all $x,y \in \mathbb{R}^d$
\item $(\rho_\epsilon * \overline{\eta}_0(x) dx) \Rightarrow u_0(x)dx$ for some $u_0(x) \in \mathcal{C}^2(\mathbb{R}^d)$, where $\Rightarrow$ denotes weak convergence. 
\end{enumerate}
Furthermore, suppose that,
\begin{equation}
\frac{\theta}{\epsilon^d N} + \frac{1}{\theta \epsilon^{2}}\rightarrow 0 \label{ConditionsForConvergence}
\end{equation}
Fix $T>0$. Then, the measure $((\rho_\epsilon *\overline{\eta}_t)(x) dx)_{t \geq 0}$ converges weakly in $D([0,T], \mathcal{M}_F(\mathbb{R}^d))$ to a measure $(\Xi_t(dx))_{t \geq 0}$. Moreover, up to a modification on a set of measure zero, $\Xi_t(x) = u_t(x)dx$, where $u_t(x)$ is a weak solution to:
\[ \partial_t u = \frac{1}{2}\Delta u + u F(u) \]
with initial condition $u_0$. That is, for every smooth function with compact support $f$ and $t>0$, we have:
\begin{equation*}
 \int \partial_t  u_t(x) f(x) dx = \int u_t(x)\frac{1}{2} \Delta f(x) dx + \int f(x) u_t(x) F(u_t(x)) dx.
\end{equation*}
\end{theorem}
 \todo[inline]{Question: Why do we need that regularity on $u_0$? I believe all we need is that (\ref{aprox3}) holds, and for that I am almost sure that $u_0$ only need to satisfy the first three hypothesis for $\overline{\eta}_0(x)$. Furthermore,  if I am not mistaken, those are all implied by $u_0(x) \in L^1(\mathbb{R}^d) \cap L^2(\mathbb{R}^d) \cap \mathcal{C}^1(\mathbb{R}^d)$ in case we want a nice space to put on the result.}

To prove this we will proceed in a standard pattern, proving $C$-tightness of the measure and then identifying the limit.

As a preliminary, we will prove some basic tools we are going to need all the way through. First, we prove that, under the conditions of Theorem~\ref{TeoremOneStepConvergence}, $\overline{\eta}_t$ has a uniformly bounded total mass in expectation. We then prove some regularity estimates of a random walk with Gaussian jumps. While this may seem disconnected from our goal the generator of this random walk is in the first integral element that appears in the martingale problem for $\overline{\eta}_t$, equation (\ref{mgp1}). It is then, no surprise, that we need some control over the regularity this term brings to our particle system.

We then focus on $C$-tighness of $\rho_\epsilon * \overline{\eta}_t(x)dx$. For this we will prove that for fixed $x$, the random variable $\rho_\epsilon*\overline{\eta}_t(x)$ has uniformly bounded expectation. Using this and the regularity of the random walk mention above, we will be able to prove the $C$-tightness of $\rho_\epsilon * \overline{\eta}_t(x)dx$.

Then we will proceed to identify the limit. For this, a continuity estimate for $(\rho_\epsilon*\overline{\eta}_t(x))$ is needed, which is again a consequence of the random walk estimates mentioned above. Using this we focus on controlling the convergence of \textit{non-linear terms} in the martingale problem of $(\rho_\epsilon*\overline{\eta}_t(x))$ (as the others converge as a consequence of weak convergence). Those do not converge as a consequence of weak convergence, since they are not written as an integral on $M^{\otimes k}(\mathbb{R}^d)$ of $(\rho_\epsilon*\overline{\eta}_t(x) dx)$ (for some $k \in \mathbb{N}$). Instead, we will first compare the quadratic terms to terms only involving $\rho_\epsilon*\overline{\eta}_s$ (and not $\overline{\eta}_s(dy)$) and then we will exchange those terms with a suitable integral in $M^{\otimes2}(\mathbb{R}^d)$, for which convergence do follow easily.

\section{Preliminaries}
\subsection{Boundedness of the total mass}
\begin{lemma} \label{Lemma:UniformlyBoundedMass}
Under the assumptions of Theorem~\ref{TeoremOneStepConvergence}, there is a finite constant $C$ (independent of $\epsilon, N, \theta$), such that $\EE\left[ \sup_{0 \leq s \leq T} \langle 1, \overline{\eta}_s \rangle \right] \leq C$.
\end{lemma}
\begin{proof}
By putting $\phi(x)=1$ in the martingale problem of $\overline{\eta}_t$, equation (\ref{mgp1}), we have,
\begin{align} \label{eq:MPTotalMass}
\langle 1, \overline{\eta}_t \rangle &= \langle 1, \overline{\eta}_0 \rangle + \int_0^t \langle F(\rho_\epsilon * \overline{\eta}_s), \overline{\eta}_s \rangle ds + M_t
\end{align}
where $M_t$ is a martingale with quadratic variation,
\begin{align} \label{eq:QVTotalMass}
[M]_t = \frac{\theta}{N}\int_0^t \langle 2 + \frac{F(\rho_\epsilon* \overline{\eta}_s)}{\theta}, \overline{\eta}_s \rangle d s 
\end{align}
By taking expectations in (\ref{eq:MPTotalMass}) we get,
\[ \EE[\langle 1, \overline{\eta}_t \rangle] =  \EE[\langle 1, \overline{\eta}_0 \rangle]  + \int_0^t \langle F(\rho * \overline{\eta}_s), \overline{\eta}_s \rangle ds ]   \leq C +   C \mathbb{E}\left[ \int_0^t \langle 1, \overline{\eta}_s \rangle ds \right].\] 
In last inequality we used that $F(x)1_{x >0}$ and $\langle 1, \overline{\eta}_0 \rangle$ are uniformly bounded above. By Gronwall's inequality we deduce $\EE[\langle 1, \overline{\eta}_s \rangle]$ is bounded on $[0,T]$. Hence, by taking expectations in (\ref{eq:QVTotalMass}) and using again the bound on $F(x)1_{x>0}$ we get,
\[ \EE\left[ [M]_t \right] \leq \frac{\theta}{N} C \int_0^t \mathbb{E}\left[ \langle 1, \overline{\eta}_s \rangle ds \right] \leq \frac{\theta}{N}C t \]
Note that, with this, $\EE[ [M]_t]$ is bounded (and in fact $\mathcal{O}(\theta/N)$). By the Burkholder-Davis-Gundy inequality and then's Jensen inequality we get
\begin{align*} \EE\left[ \sup_{0 \leq t \leq T} M_t \right] \leq C \EE\left[ [M]_T^{1/2} \right] \leq C \EE[M]_T^{1/2} \leq C   \end{align*}
Taking supremum and then expectation in (\ref{eq:MPTotalMass}) and using the last inequality gives the result.
\end{proof}

\subsection{Regularity estimates of the density of a Gaussian random walk}
Let us write $\mathcal{L}^\theta f(x) := \theta \int (f(y)-f(x))q_\theta(x,y) dy$ with $q_\theta$ is a Gaussian kernel of mean $0$ and variance $1/\theta$. We note that $\mathcal{L}^\theta$ is the generator of a continuous random walk, where at rate $\theta$ we have the arrival of Gaussian jumps of mean $0$ and variance $1/\theta$.

In what follows we let $\psi_t^{\epsilon, x}(y)$ be the solution of:
\begin{equation} \frac{\partial}{ \partial_t} \psi_t^{\epsilon,x} = \mathcal{L}^\theta \psi_t^{\epsilon, x} \label{AlmostHeatEquation} \end{equation}
with initial condition $\psi_0^{\epsilon,x}(y) = \rho_\epsilon(y-x)$. We have the following result for $\psi_t^{\epsilon,x}$.

\begin{lemma} \label{PsiBoundHS}
Fix $t>0$ and let $T(t)$ be a random variable such that $\theta T(t) \sim Poisson(\theta t)$. Then:
\[ \psi^{\epsilon,x}_t(y) = \mathbb{E}\left[ p_{\epsilon^2+T(t)}(x,y)\right] \]
Moreover,
\[ \Vert \psi^{\epsilon,x}_t \Vert_\infty \leq \mathcal{O}\left( \frac{1}{(t+\epsilon^2)^{d/2}} + \frac{1}{\epsilon^2 \theta} \right) \]
\end{lemma}
\begin{proof}
The first claim of this result follows immediately from $\mathcal{L}^\theta$ being the generator of a continuous random walk, where jumps with mean $0$ and variance $1/\theta$ arrive at rate $\theta$.

For the second claim we note that $T(t)-t$ has mean $0$ and variance $t/\theta$.  So by Chebyshev's inequality we get,
\begin{equation}
\PP\left[  \frac{|T(t)-t|}{\epsilon^2+t} > \frac{1}{2} \right] \leq \frac{4t}{\theta(\epsilon^2+t)^2} \leq \frac{2}{\epsilon^2 \theta}. \label{eq:IneqConcentrationT}
\end{equation}
Thus, by using standard bounds for the heat semigroup we get that,
\begin{align*}
\Vert \psi^{\epsilon,x} \Vert_\infty & \leq \EE\left[  \frac{1}{2 \pi (\epsilon^2+T(t))^{d/2}}\right] \\ & = \frac{1}{(2 \pi(\epsilon^2+t)^{d/2}} \EE\left[\left(\frac{1}{1+\frac{T(t)-t}{\epsilon^2+t}} \right)^{d/2} \right] \\ &\leq \frac{\pi^{-d/2}}{(\epsilon^2+t)^{d/2}} + \frac{2}{\epsilon^2 \theta}
\end{align*}
where in the last inequality we partition over $\{ |T(t)-t| > (\epsilon^2+t)/2\}$ and its complement, and use (\ref{eq:IneqConcentrationT}).
\end{proof}
We will need a further comparison of $\psi_t^{\epsilon,x}$ to the heat semigroup.
\begin{lemma}
For every $x \in \mathbb{R}^d$ and $t>0$ we have,
\begin{align*}
|\psi_t^{\epsilon,x} - p_{\epsilon^2+t}(x,y)| &\leq \frac{C}{\epsilon^2 \theta}\left(\psi_t^{\epsilon,x}(y) + p_{\epsilon^2+t}(x,y) + p_{3/2(\epsilon^2+t)}(x,y)+p_{3(\epsilon^2+t)}(x,y) \right)
\end{align*} \label{Lemma:BoundPsiHS2}
\end{lemma}
\begin{proof}
From Lemma~\ref{PsiBoundHS} we have that $\psi_t^{\epsilon,x} = \EE\left[ p_{N(t)/\theta+\epsilon^2}(x,y) \right]$ with $N(t)$ a Poisson process of rate $\theta$. We write $\tau(t) = N(t)-t$, which has mean $0$ and variance $t/\theta$. In particular,
\begin{equation}
\PP[|\tau(t)| > (\epsilon^2+t)/2] \leq \frac{4t}{\theta(\epsilon+t)^2} \leq \frac{2}{\theta \epsilon^2} \label{eq:ConcentrationTau}
\end{equation}
Consider first the even in which $|\tau(t)| \leq (\epsilon^2+t)/2$. Under such event we have that,
\begin{equation} |p_{\epsilon^2+t+\tau(t)}(x,y) - p_{\epsilon^2+t}(x,y) | = |\tau(t)| \left| \frac{\partial p_s(x,y)}{\partial s} \right| \end{equation}
for some $s \in (\epsilon^2+t-|\tau(t)|, \epsilon^2+t+|\tau(t)|)$. Without loss of generality we suppose $x=0$ and write $p_s(y):=p_s(0,y)$ to simplify notation. Then,
\[ \frac{\partial}{\partial s} \frac{1}{(2 \pi s)^{d/2}} \exp(-\frac{\Vert y \Vert^2}{2s}) = - \frac{d}{s} p_s(y) + \frac{y^2}{2 s^2} p_s(y)\]
Now for $s \in ((\epsilon^2+t)/2,3(\epsilon^2+t)/2)$ we have,
\[ p_s(y) \leq 3^{d/2} p_{3/2(\epsilon^2+t)}(y) \, \, ,\text{ and } \, \, \frac{1}{s} \leq \frac{2}{\epsilon^2+t}\]
Morever, since $\frac{y^2}{4s} e^{-y^2/4s} \leq 1$ for all $y$,
\begin{align*}
\frac{y^2}{s^2}  p_s(y) &= \frac{1}{s} \frac{4}{(2 \pi s)^{d/2}}\exp(-\frac{y^2}{4s}) \frac{y^2}{4s} \exp( - \frac{y^2}{4 s}) \\ &\leq  4\frac{ 2^{d/2}}{s} p_{2s}(y) \\ &\leq \frac{4}{s}  2^{d/2} 3^{d/2} p_{3(\epsilon^2+t)}(y)  \\ & \leq 8 \frac{ 2^{d/2} 3^{d/2}}{\epsilon^2+t} p_{3(\epsilon^2+t)}(y)
\end{align*}
Combining the last estimates
\begin{align*}
|\psi_t^{\epsilon,x}(y)-p_{\epsilon^2+t}(x,y)| & = | \mathbb{E}\left[ (1_{|\tau(t)| > (\epsilon^2+t)/2}+1_{|\tau(t)| \leq (\epsilon^2+t)/2})(p_{t+\epsilon^2+\tau(t)}(x,y)-p_{\epsilon^2+t}(x,y)) \right]| \\ &\leq \PP[|\tau(t)| \geq (\epsilon^2+t)/2] \EE[p_{t+\epsilon^2+\tau(t)}(x,y) + p_{\epsilon^2+t})(x,y)] \\ &+ \mathbb{E}\left[ \frac{|\tau(t)|}{\epsilon^2+t}\right]\left( 2d3d^{d/2} p_{3(\epsilon^2+t)/2} (x,y) + 8 2^{d/2}3^{d/2} p_{3(\epsilon^2+t)}(x,y)\right) \\ & \leq \frac{2}{\theta \epsilon^2} (\psi_t^{\epsilon,x}(y)+p_{\epsilon^2+t}(x,y)) + \mathbb{E}\left[ \frac{|\tau(t)|}{\epsilon^2+t}\right] C (p_{3/2(\epsilon^2+t)}(x,y) + p_{3(\epsilon^2+t)}(x,y))
\end{align*}
Finally, since
\[ \mathbb{E}\left[ \frac{|\tau(t)|}{\epsilon^2+t}\right] \leq \mathbb{E}\left[ \frac{\tau(t)^2}{\epsilon^2+t}\right] \leq \frac{1}{2 \theta \epsilon^2} \]
the result follows.
\end{proof}
The last result will be incredibly useful when combined with the next bound for the heat kernel.
\begin{lemma}
Let $s>0, x, y, z\in \mathbb{R}^d$. The following estimate holds
\[ |p_s(x,z) - p_s(y,z)| \leq \frac{C|x-y|}{\sqrt{s}} \left(p_{2s}(x,z) + p_{2s}(y,z)\right) \]
where the constant $C$ does not depend on $x,y,z$ or $s$.\label{Lemma:ContinuityHS}
\end{lemma}
\begin{proof}
Expanding the difference of two square we can rewrite,
\begin{align*}
&\exp\left(-\frac{(y-z)^2}{2 s} \right)-\exp\left(-\frac{(x-z)^2}{2 s} \right) \\ &= \left(\exp\left(-\frac{(y-z)^2}{4 s} \right)-\exp\left(-\frac{(x-z)^2}{4 s} \right) \right)\left(\exp\left(-\frac{(y-z)^2}{4 s} \right)+\exp\left(-\frac{(x-z)^2}{4 s} \right) \right)
\end{align*}
by using the intermediate value theorem we can write the right hand side as,
\[ (y-x) \left( - \frac{2(w-z)}{4s} \exp\left(-\frac{(w-z)^2}{4s}\right)\right) 2^{d/2}\left( p_{2s}(y,z)+p_{2s}(x,z) \right)\]
for some $w \in [y,z]$. Using the fact that $x e^{-x^2}$ is uniformly bounded we can bounded the first bracket in the last equation by $C/\sqrt{s}$ and the result follows.
\end{proof}

\subsection{The martingale problem for a time dependent function.}
Before proceeding we do the following observation. For any time, dependent function $\phi_t(x)$ the martingale problem for $\overline{\eta}_t$, (\ref{mgp1}), gives that
\begin{align}
\langle \overline{\eta}_t(dx), \phi_0(x)\rangle &= \langle \overline{\eta}_0(dx), \phi_t(x)\rangle +  M_t(\phi_\cdot(\cdot)) - \int_0^t \langle \partial_t \phi_{t-s}(x), \overline{\eta}_s(dx) \rangle  ds \nonumber \\ & + \int_0^t \langle \mathcal{L}^\theta \phi_{t-s}(x), \overline{\eta}_s(dx) \rangle ds+ \int_{0}^t \langle \phi_{t-s}(x)F (\rho_\epsilon*\overline{\eta}_s)(x) ) , \overline{\eta}_s(dx) \rangle ds \label{timeMGP}
\end{align}
with $M_t(\phi_\cdot(\cdot))$ a martingale with having quadratic variation:
\[ [M(\phi_\cdot(\cdot))]_t = \frac{\theta}{N}\int_0^t \langle \int_{\mathbb{R}^d} \phi_s(z)^2 q_\theta(y,dz) + \left( 2 + \frac{F(\rho_\epsilon*\overline{\eta}_s(y))}{\theta}\right) \phi_s(y)^2, \overline{\eta}_s(dy) \rangle ds \]
\section{Tightness}

\subsection{Uniform bound for $\{ \rho_\epsilon * \overline{\eta}_s (x)\}_{0 \leq s \leq T}$ for fixed $T$}
\begin{lemma} \label{FirstBoundLocalDensity}
Under the conditions of Theorem~\ref{TeoremOneStepConvergence} there is a constant $C>0$ (independent of $\epsilon, N, \theta, x$ and $T$) such that,
\[ \EE[ \rho_\epsilon*\overline{\eta}_t(x) ] < C \]
for all $t \in [0,T]$ and $x \in \mathbb{R}^d$.
\end{lemma}
\begin{proof}
Recall $\psi_t^{\epsilon,x}$, the solution of (\ref{AlmostHeatEquation}) with initial condition $\psi_0^{\epsilon,x}(y)=\rho_\epsilon(y-x)$. By replacing $\phi_t$ with $\psi_t^{\epsilon,x}$ in (\ref{timeMGP}) we can write,
\begin{align}
(\rho_\epsilon*\overline{\eta}_t(x)) = \langle \psi_t^{\epsilon,x}(y), \overline{\eta}_0(dy) \rangle  + \int_0^t \langle \psi_{t-s}^{\epsilon,x}(y) F(\rho_\epsilon*\overline{\eta}_s(y)), \overline{\eta}_s(dy) \rangle ds + M_t \label{MartingaleProblemMolifier}
\end{align}
where $F$ is uniformly bounded above. Hence, if we take expectation,
\begin{align}
\EE[\rho_\epsilon * \overline{\eta}_t(x)]&= \EE[\langle \psi_t^{\epsilon,x}(y), \overline{\eta}_0(dy) \rangle] + C \EE[\int_0^t \langle \psi_{t-s}^{\epsilon,x}(y), \overline{\eta}_s(dy) \rangle ds] \nonumber \\ & \leq  \EE[\langle p_{\epsilon^2+T(t)}(x,y),\overline{\eta}_0(dy)\rangle] + C \int_0^t \Vert \psi_{t-s}^{\epsilon,0} \Vert_\infty \EE[\sup_{0 \leq s \leq t} \langle 1, \overline{\eta}_s(dy) \rangle] ds \\ & \leq C + C \int_0^t \Vert \psi_{t-s}^{\epsilon,0} \Vert_\infty ds \label{BoundForMolifier}
\end{align}
Where in the last inequality we used Lemma~\ref{Lemma:UniformlyBoundedMass} and our first assumption on the initial condition. Furthermore, using Lemma \ref{PsiBoundHS} we can bound $\Vert \psi_{t-s}^{\epsilon,0} \Vert_\infty$ by $C (t-s+\epsilon^2)^{-d/2}$. In dimension one the reminding term is immediately uniformly bounded. For $d=2$ we can iterate. By using again the martingale problem and the same arguments we used to get (\ref{BoundForMolifier}) we get,
\begin{equation} \label{IterationBoundPsi}
\EE[\langle \psi_{t-s}^{\epsilon,x}, \overline{\eta}_s(dy)\rangle] \leq \EE[\langle \psi_{t}^{\epsilon,x}(y), \overline{\eta}_0(dy) \rangle]  + C \int_0^s \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du
\end{equation}
Hence, using (\ref{IterationBoundPsi}) in (\ref{BoundForMolifier}) gives
\begin{align*}
\EE[ \rho_\epsilon * \overline{\eta}_t(x)  ] &\leq \EE[\langle \psi_t^{\epsilon,x}(y), \overline{\eta}_0(dy) \rangle] + \int_0^t C\langle \psi_{t}^{\epsilon,x}, \overline{\eta}_0(dy)\rangle ds + C^2 \int_0^t \int_0^s  \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du ds \\ &= (1+Ct) \EE[ \langle \psi_t^{\epsilon,x}, \overline{\eta}_0(dy) \rangle] + C^2 \int_0^t (t-u) \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du \\ &\leq C(1+t) + C^2 \int_0^t (t-u) \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du
\end{align*}
which again is uniformly bounded using Lemma \ref{PsiBoundHS}. It is easy to see this iteration can be used to prove an uniform bound in any dimension.

\end{proof}

\begin{remark} \label{Remark:BoundLocalDensity}
It is convenient to remark that from $\EE\left[ \langle \rho_\epsilon(x,y), \overline{\eta}_t(dy) \rangle \right]$ being bounded it follows that $\EE[ \langle p_{s+\epsilon^2}(x,y), \overline{\eta}_t(dy) \rangle ]$ is bounded for all $s>0$. Indeed, this follows from writing $p_{s+\epsilon^2} = p_s * p_{\epsilon^2}$ and integrating.
\end{remark}

\begin{corollary}
Let $(M_t)_{t \geq 0}$ be the martingale in (\ref{MartingaleProblemMolifier}). Then
\[ \EE\left[ [M]_t \right] \leq \frac{C \theta}{ N \epsilon^{d}} \]
where $C$ is independent of $\epsilon,\theta,N$. \label{Cor:ControlQVMQ}
\end{corollary}
\begin{proof}
Indeed, note we can explicitly write the quadratic variation of $M_t$ by,
\[ [M]_t = \frac{\theta}{N} \int_0^t \langle \int_{\mathbb{R}^d} \psi_{t-s}^{\epsilon,x}(z)^2 q_\theta(y,dz) + \left(2+\frac{F(\rho_\epsilon * \overline{\eta}_s(y))}{\theta}\right)\psi_{t-s}^{\epsilon,x}(y)^2, \overline{\eta}_s(dy) \rangle  ds\]
using Lemma~\ref{PsiBoundHS} we can get the following bound,
\[ \psi_{t-s}^{\epsilon,x}(y)^2 \leq \psi_{t-s}^{\epsilon,x}(y) \frac{C}{(\epsilon^2+t-s)^{d/2}} \leq \frac{C}{\epsilon^d} \psi_{t-s}^{\epsilon,x}(y). \]
Hence, by using the last inequality the upper bound on $F(x)1_{x}$ we deduce that:
\begin{align*}
[M]_t &\leq \frac{C \theta}{\epsilon^d N} \int_0^t \left\{  \langle \int \psi_{t-s}^{\epsilon,x}(z) q_\theta(y,dz), \overline{\eta}_s(dy) \rangle + \langle \psi_{t-s}^{\epsilon,x}(y), \overline{\eta}_s(dy)\rangle \right\} ds 
\end{align*}
Taking expectations and using the bound of Lemma~\ref{FirstBoundLocalDensity} we get the result.
\end{proof}

%\begin{corollary}
%Under the conditions of Theorem~\ref{TeoremOneStepConvergence} there is a constant $C>0$ (independent of $\epsilon, N, \theta,x$ and $T$) such that,
%\[ \EE[ \sup_{0 \leq s \leq T} \rho_\epsilon*\overline{\eta}_s(x) ] < C \]
%for all $t \in [0,T]$ and $x \in \mathbb{R}^d$.
%\end{corollary}
%\begin{proof}
%The proof follows the same pattern as Lemma~\ref{Lemma:UniformlyBoundedMass}.
%\end{proof}

%\todo[inline]{Do we need that? May erase it latter if we dont.}

\subsection{$C$-tightness of $\rho_\epsilon * \overline{\eta}_t(x) dx$ }
\begin{lemma}
Under the assumptions of Theorem~\ref{TeoremOneStepConvergence} the sequence of measure valued process $\{ \rho*\overline{\eta}_t(x) dx \}_{t \geq 0}$ (taking values in $D([0,T], \mathcal{M}_F(\mathbb{R}^d))$ is $C$-tight.
\end{lemma}
\begin{proof}

Let $f \in C_c^2$ (that is, compactly supported and with smooth second derivative). We will show convergence of $\int f(x) \rho_\epsilon * \overline{\eta}_t(x) dx$ (which is enough to establish weak convergence of the measures $\rho_\epsilon * \overline{\eta}_t(x) dx$). For this note that,
\begin{align*}
\int f(x) \rho_\epsilon * \overline{\eta}_t(x) dx &= \int \int f(x) \rho_\epsilon (x-y) \overline{\eta}(dy) dx \\ & = \langle \int fd(x) \rho_\epsilon(x-y) dx, \overline{\eta}(dy) \rangle \\ &= \langle T_{\epsilon^2} f(y), \overline{\eta}_t(dy) \rangle
\end{align*}
where $T_t$ denotes the heat semigroup. Substituting this on the martingale problem for $\overline{\eta}_t$, (\ref{mgp1}), we get,
\begin{align}
\langle T_{\epsilon^2} f(y), \overline{\eta}_t(dy) \rangle & = \langle T_{\epsilon^2}
 f(y), \overline{\eta}_0(dy) \rangle + \theta \int_0^t \langle \int (T_{\epsilon^2} f(z) - T_{\epsilon^2} f(y))q_\theta(y,z)dz, \overline{\eta}_s(dy)\rangle ds \nonumber \\ &+\int_0^t \langle T_{\epsilon^2} f(y) F(\rho_\epsilon*\overline{\eta}_s(y)), \overline{\eta}_s(dy) \rangle ds + \widehat{M}_t \label{MGPT_epsilon} \end{align}
 with $\widehat{M}_t$ a martingale. Now note that,
 \begin{align}
    | \theta \int (T_{\epsilon^2} f(z) - T_{\epsilon^2}f(y))q_\theta(y,z) dz | &= |\theta( T_{\epsilon^2 + 1/\theta} f(y) - T_{\epsilon^2}f(y)| \nonumber \\ &= | \Delta T_{\epsilon+1/\tilde{\theta}} f(y) | \nonumber \\ &=|T_{\epsilon^2 + 1/\tilde{\theta}} \Delta f(y) | \leq \Vert \Delta f \Vert_{\infty} \label{ShortBoundLaplacianHS}
 \end{align}
for some $\tilde{\theta} \in [0,1/\theta]$ by intermediate value theorem. Hence, proceding as we did in Lemma~\ref{Lemma:UniformlyBoundedMass}, we can use that $F(x)1_{x > 0}$ is bounded above and Gronwall's inequality to conclude that,
\[ \EE\left[\langle T_{\epsilon^2} f(y), \overline{\eta}_t(dy) \rangle \right] \text{ is uniformly bounded for } t \in [0,T].\]
To proceed we note that the quadratic variation of $\widehat{M}_t$ is;
\[ [ \widehat{M}]_t = \frac{\theta}{N}\int_0^t \langle T_{1/\theta}(T_{\epsilon^2}f(\cdot)^2)(y) + \left(2+\frac{F(\rho_\epsilon*\overline{\eta}_s(y))}{\theta}\right)T_{\epsilon^2}f(y)^2, \overline{\eta}_s(dy) \rangle ds \]
And so, computing as in the last inequality of (\ref{ShortBoundLaplacianHS}) gives that,
\begin{align*}
\EE\left[ [\widehat{M}]_t \right] \leq \frac{\theta}{N} \Vert f \Vert_\infty C \int_0^t \mathbb{E}\left[ \langle 1, \overline{\eta}_s(dy) \right] ds < \frac{\theta}{N} t C
\end{align*}
where in the last inequality we have used Lemma~\ref{Lemma:UniformlyBoundedMass}.Hence, using Burkholder-Davis-Gundy we can conclude,
\[ \EE[\sup_{0 \leq t \leq T} [\widehat{M}]_t ] \text{ is uniformly bounded (for fixed } f \text{)} \]
Therefore, by taking supremum and expectation and in (\ref{MGPT_epsilon}) we conclude that
\[ \EE[\sup_{0 \leq t \leq T} \langle T_{\epsilon^2} f, \overline{\eta}_t \rangle ] \text{ is uniformly bounded (for fixed } f \text{)} \]
To conclude $C$-tightness we would require that, for $T>0$, $\alpha > 0$ there is some $\delta >0$ so that for $\theta$ and $N$ large enough,
\begin{align}
&\PP\left[ \sup_{u,v \in [0,T], |u-v| < \delta} | \int f, \rho_\epsilon*\overline{\eta}_u(x) dx   - \int f, \rho_\epsilon*\overline{\eta}_v(x) dx   > \alpha \right] \\ &=
\PP\left[ \sup_{u,v \in [0,T], |u-v| < \delta} | \langle T_{\epsilon^2} f, \overline{\eta}_u \rangle - \langle T_{\epsilon^2} f,\overline{\eta}_v \rangle > \alpha \right] < \alpha \label{conditionCtightness}
\end{align}
But, from our estimates above, we have
\begin{align*}
|\langle T_{\epsilon^2} f, \overline{\eta}_u \rangle - \langle T_{\epsilon^2} f,\overline{\eta}_v \rangle|  \leq ( \Vert \Delta f \Vert_\infty+C) |u-v| \sup_{0 \leq s \leq T } \langle 1, \overline{\eta}_s \rangle + \sup_{s \leq T}\widehat{M}_s
\end{align*}
Taking expectations we get,
\begin{equation}
\EE\left[ |\langle T_{\epsilon^2} f, \overline{\eta}_u \rangle - \langle T_{\epsilon^2} f,\overline{\eta}_v \rangle|\right] \leq \widehat{C} |u-v| + \frac{\widehat{C}\theta}{N}\end{equation}
Using this and Markov inequality give that (\ref{conditionCtightness}) holds with $\delta = \alpha/(3 \widehat{C}|u-v|)$, for $N,\theta$ big enough so $\widehat{C}\theta/N$ is bounded by $\alpha/3$ (Note the last condition is possible by (\ref{ConditionsForConvergence})). Thus we have concluded $C$-tightness. 
\end{proof}
\section{Identifying the limit}
\subsection{Continuity estimate}
In this section we prove the following continuity estimate for $\rho_\epsilon * \overline{\eta}_t(x)$.

\begin{proposition} \label{ContinuityEstimate}
Under the same conditions of Theorem~\ref{TeoremOneStepConvergence} we have that for all $y,x \in \mathbb{R}^d$,
\[ \EE[|\rho_\epsilon*\overline{\eta}_s(x) -\rho_\epsilon*\overline{\eta}_s(y)| ] \leq \mathcal{O}\left( |y-x| + \left(\frac{\theta}{N \epsilon^2}\right)^{1/2} + \frac{1}{\epsilon^2 \theta} \right)\]
\end{proposition}
\begin{proof}
By using (\ref{MartingaleProblemMolifier}) (and an obvious abuse of notation) we can write,
\begin{align}
& |\rho_\epsilon*\overline{\eta}_t(x)-\rho_\epsilon*\overline{\eta}_t(y)| \nonumber \\ &= |\langle \rho_\epsilon(y-z)-\rho_\epsilon(x-z),\overline{\eta}_t(dz) \rangle | \nonumber\\ &\leq  |M_t(x)-M_t(y)|  +\langle \psi_t^{\epsilon,y}(z)-\psi_t^{\epsilon,x}(z), \overline{\eta}_0(dz)\rangle \nonumber \\ &+ |\int_0^t \langle (\psi_{t-s}^{\epsilon,z}(x) - \psi_{t-s}^{\epsilon, y}(x) )F(\rho_\epsilon*\overline{\eta}_s(x)), \overline{\eta}_s(dx) \rangle  ds |  \label{eq:bound1CE} \end{align} 
For the martingale term; note that Corollary~\ref{Cor:ControlQVMQ} and the Burkholder-Davis-Gundy inequality give,
\[
\EE[\sup_{s \leq t} M_t(x) + M_t(y)] \leq C\left(\frac{\theta}{N \epsilon^d}\right)^{1/2}. \]
On the other hand, since $F(x)1_{x >0}$ is bounded above, by combining Lemma~\ref{FirstBoundLocalDensity}, Remark~\ref{Remark:BoundLocalDensity} and Lemma~\ref{Lemma:BoundPsiHS2} we can replace $\psi_t^{\epsilon, y}$ and $\psi_t^{\epsilon,x}$ by the heat kernels by paying an error of order $\mathcal{O}(1/(\epsilon^2\theta))$. That is, 
\begin{align*}
&\EE\left[|\rho_\epsilon*\overline{\eta}_t(x)-\rho_\epsilon*\overline{\eta}_t(y)| \right] \leq \EE[|\langle p_{\epsilon^2+t}(y,z)-p_{\epsilon^2+t}(x,z),\overline{\eta}_0(dz)\rangle|]  \\ &+\mathbb{E}\left[ \int_0^t C \langle |p_{\epsilon^2+t}(y,z)-p_{\epsilon^2+t}(x,z)|,\overline{\eta}_s(dz)\rangle ds \right]+ \mathcal{O}\left( \left( \frac{\theta}{N \epsilon^d}\right)^{1/2} + \frac{1}{\epsilon^2 \theta} \right)\end{align*}
By using Lemma~\ref{Lemma:ContinuityHS}, Lemma~\ref{FirstBoundLocalDensity}, Remark~\ref{Remark:BoundLocalDensity} and our hypothesis on the initial condition we get that,
\begin{align*}
\EE\left[|\rho_\epsilon*\overline{\eta}_t(x)-\rho_\epsilon*\overline{\eta}_t(y)| \right] &\leq \EE[|\langle p_{\epsilon^2+t}(y,z)-p_{\epsilon^2+t}(x,z),\overline{\eta}_0(dz)\rangle|] \\ & + C \int_0^t \frac{1}{\sqrt{s+\epsilon^2}} ds |x-y| \\ &\leq C|x-y| +\mathcal{O}\left( \left( \frac{\theta}{N \epsilon^d}\right)^{1/2} + \frac{1}{\epsilon^2 \theta} \right)
\end{align*}
as required.
\end{proof}

\subsection{Identifying the limit of $\langle T_{\epsilon^2} f(y), \overline{\eta}_t (dy) \rangle$.}
We now prove the identification of the limit. We recall that, the main difficulty, is the non-linear term of the martingale problem. To deal with them, our first step would prove that an approximation of the form:
\begin{align*}
\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\overline{\eta}_s(dy)), \overline{\eta}_s(dy) \rangle \sim \langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \overline{\eta}_s(dy)), \rho_\epsilon * \overline{\eta}_s(y) dy \rangle
\end{align*}
This is the content of the next result.
\begin{proposition} \label{CuadraticApprox}
Under the condition of Theorem~\ref{TeoremOneStepConvergence} there is a constant $C>0$ such that
\begin{equation*}
\EE[|\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\overline{\eta}_s(dy)), \overline{\eta}_s(dy) \rangle - \langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \overline{\eta}_s(dy)), \rho_\epsilon * \overline{\eta}_s(y) dy \rangle|]
\end{equation*}
is bounded by,
\begin{equation*}
C \left( \left(\frac{\theta}{\epsilon^d N}\right)^{1/2} + \frac{1}{\epsilon^2 \theta}+ \left(\frac{\theta}{\epsilon^d N}\right)^{1/3} + \epsilon +  \epsilon^2\right) 
\end{equation*}
\end{proposition}
\begin{proof}
We first note that,
\begin{align*}
    &\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\overline{\eta}_s(dy)), \overline{\eta}_s(dy) \rangle - \langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \overline{\eta}_s(dy)), \rho_\epsilon * \overline{\eta}_s(y) dy \rangle \\ & = \langle \int T_{\epsilon^2} f(y) F(\rho_\epsilon * \overline{\eta}_s(y))\rho_\epsilon(y-w) dy, \overline{\eta}(dw)\rangle - \langle T_{\epsilon^2} f(w) F(\rho_\epsilon*\overline{\eta}_s(w)), \overline{\eta_s}(dw) \rangle \\ &= \langle \int \{ T_{\epsilon^2} f(y) F(\rho_\epsilon*\overline{\eta}_s(y))-T_{\epsilon^2}f(w) F(\rho_\epsilon*\overline{\eta}_s(w))\} \rho_\epsilon(w-y)dy, \overline{\eta}_s(dw) \rangle.
\end{align*}
Let us denote $I$ the integral against $dy$ in the last expresion, that is 
\[ I :=  \int \{ T_{\epsilon^2} f(y) F(\rho_\epsilon*\overline{\eta}_s(y))-T_{\epsilon^2}f(w) F(\rho_\epsilon*\overline{\eta}_s(w))\} \rho_\epsilon(w-y)dy \]
And note that $|I|$ is bounded by
\begin{align}
& \int \left\{ |F(\rho_\epsilon*\overline{\eta}_s(y))-F(\rho_\epsilon*\overline{\eta}_s(w))|T_{\epsilon^2}f(y)+F(\rho_\epsilon*\overline{\eta}_s(w))|T_{\epsilon^2}f(y)-T_{\epsilon^2}f(w))|\right\} \rho_{\epsilon}(w-y)dy \nonumber \\ &\leq \int C |\rho_\epsilon*\overline{\eta}_s(y)-\rho_\epsilon*\overline{\eta}_s(w)| \rho_\epsilon(w-y)dy + C \epsilon^2 \Vert \Delta f \Vert_2 \label{FirstBoundCT}
\end{align}
where in the last inequality we have used $F(x)1_{x>0}$ and $|F'(x)1_{x>0}|$ are both bounded above. We now aim to replace $\rho_\epsilon*\overline{\eta}_s(y)-\rho_\epsilon*\overline{\eta}_s(w)$ with its expectation. For this note that, 
\begin{align}
Var( \overline{\eta}_s*\rho_\epsilon(z)) &=  Var( \overline{\eta}_s*\rho_\epsilon(z) - \mathbb{E}(\overline{\eta}_s*\rho_\epsilon(z))) \nonumber \\ &= \EE[ [ \overline{\eta}*\rho_\epsilon(z) ]_s] \nonumber \\ &= \EE[ [ M]_s ] = \mathcal{O}\left( \frac{\theta}{\epsilon^{d} N} \right) \label{eq:AlmostDeterministic}
\end{align}
in the second equality we have used that $\overline{\eta}_s*\rho_\epsilon(z) - \mathbb{E}(\overline{\eta}_s*\rho_\epsilon(z))$ is a mean zero martingale and in the third one that $M(\rho_\epsilon)$ and $\overline{\eta} * \rho_\epsilon(z)$ differ only on finite variation terms and hence have the same quadratic variation. The last inequality is then an application of Corollary~\ref{Cor:ControlQVMQ}. By a polarization argument is then follows that: 
\[ Var(\rho_\epsilon * \overline{\eta}_s(y) - \rho_\epsilon * \overline{\eta}_s(w)) = \mathcal{O}\left(\frac{\theta}{N \epsilon^d}\right).\]
Hence, by  Tshecyshev inequality we got that, there is a constant $C$ such that, 
\[ \PP\left[|\rho_\epsilon * \overline{\eta}_s(y) - \rho_\epsilon * \overline{\eta}_s(w) - \EE[\rho_\epsilon * \overline{\eta}_s(y) - \rho_\epsilon * \overline{\eta}_s(w)]| > C \left(\frac{\theta}{\epsilon^d N}\right)^{1/3}\right] \leq \mathcal{O}\left(\frac{\theta}{\epsilon^d N}\right)^{1/3} \]
Using this last bound, Proposition~\ref{ContinuityEstimate}, Lemma~\ref{Lemma:UniformlyBoundedMass} and (\ref{FirstBoundCT}) gives that,
\begin{align*}
&\EE[|\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\overline{\eta}_s(dy)), \overline{\eta}_s(dy) \rangle - \langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \overline{\eta}_s(dy)), \rho_\epsilon * \overline{\eta}_s(y) dy \rangle|] \\ &\leq   C \EE[ \langle \int | y - w |  \rho_\epsilon(w-y)dy, \overline{\eta}_s(dw) \rangle  ]  \\  &+ \mathcal{O}\left( \left(\frac{\theta}{\epsilon^d N}\right)^{1/2} + \frac{1}{\epsilon^2 \theta}+ \left(\frac{\theta}{\epsilon^d N}\right)^{1/3} + \epsilon^2\right) \\ &= \mathcal{O}\left( \left(\frac{\theta}{\epsilon^d N}\right)^{1/2} + \frac{1}{\epsilon^2 \theta}+ \left(\frac{\theta}{\epsilon^d N}\right)^{1/3} + \epsilon +  \epsilon^2\right) 
\end{align*}
which completes the proof.
\end{proof}
Now, to finish the characterisation of the limit, it remain to show that:
\[ \int f(x) \rho_\epsilon * \overline{\eta}_t(x) F(\rho_\epsilon * \overline{\eta}_t(x)) dx \rightarrow \int f(x) u_t(x) F(u_t(x)) dx \]
where $u_t(x)dx$ is the limit of $\rho_\epsilon*\overline{\eta}_t(x)dx$. As we mention as the start of this note this does now follow from weak convergence of $\rho_\epsilon*\overline{\eta}(x)dx$. For proving this, we recall that $F(x)$ is a polynomial, so we just need to prove said convergence of powers of $(\rho_\epsilon*\overline{\eta}_t(x))$. To illustrate how to proceed, we will prove the convergence,
\begin{equation} \label{eq:QuadConvergence} \int f(x) \rho_\epsilon * \overline{\eta}_t(x) \rho_\epsilon * \overline{\eta}_t(x)^2 dx \rightarrow \int f(x) u_t(x) u_t(x)^2 dx \end{equation}
with the understanding that converge of higher powers will follows in a similar fashion with rougher notation. To achieve (\ref{eq:QuadConvergence}) we proceed by proving an approximation of the form,
\begin{equation}
\label{aprox2}
\langle f, (\overline{\eta}_s * \rho_\epsilon)^2 \rangle \sim \int \int f(z) (\rho_\epsilon * \overline{\eta}_s)(z) K_\delta (z,y) (\rho_\epsilon * \overline{\eta}_s)(y) dz dy.
\end{equation}
where $K_\delta$ is a smooth Kernel that converges (weakly) to a Dirac mass when $\delta$ goes to $0$ (we will take the heat kernel at time $\delta$). We first argue why this is enough. Note the right hand side of (\ref{aprox2}) can written with some abuse of notation as
\[ \int_{\mathbb{R}^{d} \otimes \mathbb{R}^d} f(z) K_\delta(z,y) (\rho_\epsilon * \overline{\eta}_s(dz) \otimes (\rho_\epsilon * \overline{\eta}_s(dy)). \]
Weak convergence of $\rho_\epsilon * \overline{\eta}$ (plus continuity of the mapping $(z,y) \rightarrow f(z) K_\delta(z,y)$) gives that the last term converges in $L^1$ to
\[ \int_{\mathbb{R}^{d} \otimes \mathbb{R}^d} f(z) K_\delta(z,y) (u_s(dz) \otimes (u_s(dy)). \]
Finally, by a direct analogue of (\ref{aprox2}) we can say that
\begin{equation} \int_{\mathbb{R}^{d} \otimes \mathbb{R}^d} f(z) K_\delta(z,y) (u_s(dz) \otimes (u_s(dy)) \sim \langle f(x), u_s^2(x) dx \rangle. \label{aprox3} \end{equation}
which is what we seek. We proceed then to prove (\ref{aprox2}), with the understanding that (\ref{aprox3}) follows in a similar way and give even better error terms.
\begin{theorem}
Under the conditions of Theorem~\ref{TeoremOneStepConvergence}, we have that for any $s>0$,
\begin{align*}
\mathbb{E}&\left[\left| \langle f(y), (\overline{\eta}_s * \rho_\epsilon(y))^2) dy\rangle - \int \int f(x) (\rho_\epsilon * \overline{\eta}_s)(z) K_\delta (z,y) (\rho_\epsilon * \overline{\eta}_s)(y) dz dy. \right|\right]
\end{align*}
is bounded by,
\[  \mathcal{O}\left(\delta+\frac{\theta}{\epsilon^d N} + \left( \frac{\theta}{\epsilon^d N} \right)^{1/2} + \frac{1}{\epsilon^2 \theta} \right)  \]
in particular, under (\ref{ConditionsForConvergence}), the last term goes to $0$ uniformly in $\theta,\epsilon,N$ and $\delta$.
\end{theorem}
\begin{proof}
First note,
\begin{align}
\mathbb{E}&\left[| \langle f, (\overline{\eta}_s * \rho_\epsilon(y))^2) dy \rangle - \int \int f(x) (\rho_\epsilon * \overline{\eta}_s)(z) K_\delta (z,y) (\rho_\epsilon * \overline{\eta}_s)(y) dz dy. |\right] \nonumber \\ &\leq  \Vert f \Vert_\infty \int_{S_f} \int \left| \mathbb{E}\left[ \left\{ (\rho_\epsilon * \overline{\eta}_s)(z)-(\rho_\epsilon * \overline{\eta}_s)(y) \right\} (\rho_\epsilon * \overline{\eta}_s)(z)\right] \right| K_\delta(z,y) dz dy    \label{b1}
\end{align}

For separating the last product in the expected value we note that (\ref{eq:AlmostDeterministic}) implies that:
\begin{equation}
\label{yeet1}
\EE[\overline{\eta}_s*\rho_\epsilon(z)^2] = \EE[\overline{\eta}_s*\rho_\epsilon(z)]^2 + \mathcal{O}\left( \frac{\theta}{\epsilon^{d}N} \right)
\end{equation}
And furthermore, by a polarization argument, we can get:
\begin{equation}
\label{yeet2}
\EE[\overline{\eta}_s*\rho_\epsilon(z) \overline{\eta}_s*\rho_\epsilon(y)] = \EE[\overline{\eta}_s*\rho_\epsilon(z)]\EE[\overline{\eta}_s*\rho_\epsilon(y)] + \mathcal{O}\left( \frac{\theta}{\epsilon^{d}N} \right)
\end{equation}
Using (\ref{yeet1}) and (\ref{yeet2}) we get that the right hand side of (\ref{b1}) can be bounded by;
\begin{align}
&\Vert f \Vert_\infty \int_{S_f} \int \mathbb{E}\left[| (\rho_\epsilon * \overline{\eta}_s)(z)-(\rho_\epsilon * \overline{\eta}_s)(y) | (\rho_\epsilon * \overline{\eta}_s)(z)\right] K_\delta(z,y) dy dz   \nonumber \\ &\leq C \Vert f \Vert_\infty \int_{S_f} \int \mathbb{E}\left[| (\rho_\epsilon * \overline{\eta}_s)(z)-(\rho_\epsilon * \overline{\eta}_s)(y) |\right] \mathbb{E}\left[\rho_\epsilon * \overline{\eta}_s(z) \right] K_\delta(z,y) dy dz + \mathcal{O}\left( \frac{\theta}{\epsilon^{d}N} \right)   \label{b1andahalf}
\end{align}
An application of Proposition~\ref{ContinuityEstimate} then gives that (\ref{b1andahalf}) is bounded by,
\begin{align*}
&C\Vert f \Vert_\infty \int_{S_f} \int C   | y - z|  K_\delta(z,y) dy dz + \mathcal{O}\left( \frac{\theta}{\epsilon^d N} + \left( \frac{\theta}{\epsilon^d N} \right)^{1/2} + \frac{1}{\epsilon^2 \theta} \right)  \\ & \leq  \mathcal{O}\left(\delta +  \frac{\theta}{\epsilon^d N} + \left( \frac{\theta}{\epsilon^d N} \right)^{1/2} + \frac{1}{\epsilon^2 \theta} \right) 
\end{align*}
Concluding the result.
\end{proof}
\subsection{Conclusion}
Under the condition (\ref{ConditionsForConvergence}) we have that all the errors in our approximations go to $0$. It is then we can deduce that quadratic (and analogously, higher order) terms in the martingale problem for $\rho_\epsilon*\overline{\eta}_t(x)dx$, (\ref{MGPT_epsilon}), converges to the corresponding term of the weak limit. Any linear term converge trivially by weak convergence. By a Taylor's expansion we can also conclude that,
\begin{align*}
\int_0^t \langle \mathcal{L}^\theta T_{\epsilon^2} f, \overline{\eta}_s(dx)\rangle ds &= \int_0^t \langle \frac{1}{2} \Delta T_{\epsilon^2} f(x), \overline{\eta}_s(dx) \rangle + \mathcal{O}(\theta^{-1}) 
\\ &= \int_0^t \langle \frac{1}{2} \Delta f(x), \rho_\epsilon* \overline{\eta}_s(x) dx \rangle ds + \mathcal{O}(\theta^{-1} + \epsilon).
\end{align*}
Thus, by weak convergence we can deduce
\[ \int_0^t \langle \mathcal{L}^\theta T_{\epsilon^2} f, \overline{\eta}_s(dx)\rangle ds \rightarrow \int_0^t \langle \frac{1}{2} \Delta f(x), u_s(x) dx \rangle ds \]
Putting all the convergences together, this identifies the limit of $\rho_\epsilon*\overline{\eta}_s(x)dx$ as we have claimed in Theorem~\ref{TeoremOneStepConvergence}.

\end{document}

### 2022-05-19 forwards-and-backwards.tex
.
figures
Update on Overleaf.

@@
 
-\comment{TODO: talk about $N \to \infty$ rather than $N \to \infty$.}
+\comment{TODO: talk about $N \to \infty$ rather than $\theta \to \infty$.}
 
@@
         =
-        \sum_{ij} \covq_{ij} \partial_{x_i} \partial_{x_j} f(x)
-        + \sum_i \meanq_i \partial_{x_i} f(x)
+        \sum_{ij} \covq(x)_{ij} \partial_{x_i} \partial_{x_j} f(x)
+        + \sum_i \meanq(x)_i \partial_{x_i} f(x)
     \end{align}
@@
         =
-        \sum_{ij} \partial_{x_i} \partial_{x_j} (\covq_{ij} f(x))
-        - \sum_i \partial_{x_i} (f(x) \meanq_i) .
+        \sum_{ij} \partial_{x_i} \partial_{x_j} (\covq(x)_{ij} f(x))
+        - \sum_i \partial_{x_i} (f(x) \meanq(x)_i) .
     $$
@@
         \varphi_t(x)
-        F\left(x, \smooth{F} \varphi_t() \right)
+        F\left(x, \smooth{F} \varphi_t(x) \right)
         ,
@@
 allowing a formal limit.
-See~\ref{etheridge/kurtz:2018} for an introduction to these ideas.
+See~\citet{etheridge/kurtz:2018} for an introduction to these ideas.
 
@@
     \begin{center}
-        FIGURE
+        \includegraphics[width=0.45\textwidth]{figures/ex2a/pme_123.steps}
+        \includegraphics[width=0.45\textwidth]{figures/ex2b/pme_123.steps}
     \end{center}
@@
     \begin{center}
-        FIGURE
+        \includegraphics{figures/ex3_fkpp/fkpp_123.lineages}
+        \includegraphics{figures/ex3_fkpp/fkpp_123.lineagehist}
+        \includegraphics{figures/ex3_pme/pme_123.lineages}
+        \includegraphics{figures/ex3_pme/pme_123.lineagehist}
+        \includegraphics{figures/ex3_allen-cahn/allen-cahn_123.lineages}
+        \includegraphics{figures/ex3_allen-cahn/allen-cahn_123.lineagehist}
     \end{center}
@@
 %% %% %% %% %% %% %% %% %% %% %% %%
-\subsection{Construction tracking individual lines of descent}
+\subsection{Construction tracking individual lines of descent} \label{sec: individual lines of descent}
 
@@
 \end{align*}
+
+\subsubsection{Evolution of levels along a whole line of descent}
+We now write down expressions
+that give the spatial and level dynamic
+of a whole line of descent.
+In particular, our description is consistent
+for any $N \in \mathbb{N}$.
+
+Recall that
+the particle with label $(a_0,a_1,..,a_k)$
+is the offspring
+with a new level
+from the $a_k$-th potential birth
+of $(a_0,...,a_{k-1})$,
+who is again the offspring
+with a new level from
+the $a_{k-1}$-th potential birth
+of $(a_0,...,a_{k-2})$, 
+etc..
+In particular, 
+the particle with label $(a_0)$
+is the direct descendant of
+the $a_0$-th original ancestor
+of the whole population, i.e.
+it has never experienced
+a jump in level throughout
+its ancestry.
+
+For simplicity, for $a=(a_0,..,a_k)$,
+we denote $[a]_{i}:=(a_0,..,a_i)$
+to be the $i$-th generation 
+ancestor of the lineage $a$.
+In particular, if at time $t$,
+if the ancestral lineage $[a]_t$
+is at its $i(t)$-th generation,
+then $[a]_t = [a]_{i(t)}$.
+
+We also write 
+$(s_{[a]_{i}}, v_{[a]_{i}}, y_{[a]_{i}}, \kappa_{[a]_{i}})
+\in \Pi_{[a]_{i-1}}$
+to be the reproduction event
+that creates $[a]_{i}$ from $[a]_{i-1}$,
+and similarly,
+$(s_{[a]_{i} \concat j}, v_{[a]_{i} \concat j}, y_{[a]_{i} \concat j}, \kappa_{[a]_{i} \concat j})
+\in \Pi_{[a]_{i-1}}$
+to be the reproduction event 
+that creates $[a]_{i} \concat j$
+from $[a]_{i-1}$.
+
+We first write down an expression
+for the level of particle $a=(a_0,a_1,..,a_k)$ at time $t$.
+Since we ensure that
+the level of a particle
+only jumps when a reproduction event
+creates a new label,
+the level of particle $a=(a_0,a_1,..,a_k)$ is determined
+by $k$ many jumps,
+and subsequent continuous evolutions
+given by Equation \eqref{eqn:U_line_of_descent}.
+
+Under this notation, for $t> 0$,
+\begin{equation}
+\label{eq: level_across_lineage}
+\begin{aligned}
+&U^{N}_{[a]_{k}}(t)- U^{N}_{[a]_{0}}(0)\\
+=& \sum_{i=1}^{k} \int_{\tau_{[a]_{i-1}}}^{\tau_{[a]_{i}}}
+\left(
+        \frac{\theta}{N} \gamma(X_{[a]_{i-1}}(s),\eta_s)
+        \int_{\IR^d} r(z,\eta_s) q(X_{[a]_{i-1}}(s),dz) U_{[a]_{i-1}}(s)^2
+        -
+        b(X_{[a]_{i-1}}(s),\eta_s) U_{[a]_{i-1}}(s)
+    \right)
+    ds\\
+&+\int_{\tau_{[a]_{i}}}^{t}
+\left(
+        \frac{\theta}{N} \gamma(X_{[a]_{i}}(s),\eta_s)
+        \int_{\IR^d} r(z,\eta_s) q(X_{[a]_{i}}(s),dz) U_{[a]_{i}}(s)^2
+        -
+        b(X_{[a]_{i}}(s),\eta_s) U_{[a]_{i}}(s)
+    \right)
+    ds\\
+&+\sum_{i=1}^{k}
+    \left( \ell(X_{[a]_{i-1}}(\tau_{[a]_{i}}-), y_{[a]_{i}}, \eta(\tau_{[a]_{i}}-), v_{[a]_{i}})
+    \right)
+\end{aligned}    
+\end{equation}
+where the first two terms correspond to
+sum of the evolution along the same generation,
+and the second term corresponds
+to the sum of jumps in levels
+when a new label is introduced.
+
+To preserve consistency 
+as we send $N \to \infty$
+in our scaling limit,
+we allow $U_{[a]_t}(t)$ to hit $\infty$.
+To identify dead lines of descent,
+for a label $a$,
+we define
+$\sigma_{a}^{N}:= \inf\{t \geq 0 : U_{[a]_t}(t) > N\}$.
+In the $N$-th scaling regime,
+we proclaim the individual
+$a$ to be dead
+at time $t$
+when $t > \sigma_{a}^{N}$
+
+Note that in particular,
+if $U_{[a]_i}(t)>N$
+at some time $t$
+in the $i$-th generation,
+then $U_{[a]_j}(t)>N$
+for all $j \geq i$
+and
+$\sigma_{[a]_j}^{N}=\sigma_{[a]_i}^{N}$.
+In words, all descendants of dead
+particles are dead by default.
+
+Similarly, we generalise the notion of death above
+to the infinity case by considering 
+$\sigma_{[a]_t}^{\infty}:=\inf\{t \geq 0 : U_{[a]_t}(t) =\infty\}$.
+
+\subsubsection{Spatial jumps along a whole line of descent}
+
+We now write down an expression for the
+spatial location of $[a]_t$ at time $t$.
+Note that in the spatial case,
+jumps occur along the same generation
+whenever $\kappa = 0$ in successful birth events,
+and occur across two generations
+whenever $\kappa = 1$ in successful birth
+events.
+
+To illustrate this, consider the spatial location of $(a_0,a_1)=(2,3)$ with birth time $\tau_{(2,3)}$ at some time $t>\tau_{(2,3)}$.
+If $U_{(2,1)}(\tau_{(2,1)}) < N$,
+the first birth event of the ancestor
+with label $(2)$
+is successful.
+If $\kappa = 0$ in this birth event,
+the parent and offspring swap labels,
+resulting in
+a spatial jump for the label $(2)$.
+On the contrary, 
+if $U_{(2,2)}(\tau_{(2,2)}) \geq N$
+or $\kappa = 1$
+in the second birth event of $(2)$,
+the parent does not give birth
+or retains its label,
+so there is no spatial jump.
+
+On the other hand, 
+if $\kappa=1$ when $(2,3)$ is born,
+the new label is given to
+the offspring
+with new spatial location,
+resulting in a jump,
+and vice versa.
+
+After $(2,3)$ is born,
+whenever the particle with label
+$(2,3)$ gives birth, 
+if $\kappa = 0$, the label $(2,3)$
+is adopted by the offspring
+which results in a spatial jump
+in the position of $(2,3)$
+again.
+
+Under this notation, for $t>\tau_{[a]_k}$,
+
+\begin{equation}
+\label{eq: space_across_lineage}
+\begin{aligned}
+&X^{N}_{[a]_{k}}(t)- X^{N}_{[a]_{0}}(0)\\
+=& \sum_{i=1}^{k}
+\sum_{j=1}^{a_i-1}
+(1-\kappa_{[a]_{i-1}\concat j}) y_{[a]_{i-1}\concat j} \ind_{U_{[a]_{i-1}\concat j}(\tau_{[a]_{i-1}\concat j}) < N}\\
+&+ \sum_{i=1}^{k}
+\kappa_{[a]_i} y_{[a]_i} \ind_{U_{[a]_i}(\tau_{[a]_i}) < N}\\
+&+\int_{\tau_{[a]_k}}^{t}
+(1-\kappa)y
+\ind_{ \{
+        U_{[a]_k}(\tau_{[a]_k}+s)
+        +\ell(X_{[a]_k}(\tau_{[a]_k}+s),y,\eta_{[a]_k}(\tau_{[a]_k}+s),v) < N
+        \}
+      } 
+\Pi_{[a]_k}(dsdvdyd\kappa),
+\end{aligned}    
+\end{equation}
+where the first term
+corresponds to 
+the sum of $a_{i}-1$ many potential jumps
+in the $(i-1)-th$ generation;
+the second term corresponds to 
+the sum of $k$ many potential jumps
+when the $k$-th generation is introduced;
+and the last term
+corresponds to sum of 
+potential jumps that occured in
+the current generation from 
+time $\tau_{[a]_k}$
+to current time $t >\tau_{[a]_k}$.
 
@@
 $$
-    U_{a \concat j}(tau_a + t) = U_a(tau_a + t)
-    + \frac{v}{ 2 \alpha \gamma(X_a(\tau_a + t), \eta_{tau_a + t}) r(X_a(\tau_a + t), \eta_{\tau_a + t}) } .
+    U_{a \concat j}(\tau_a + t) = U_a(\tau_a + t)
+    + \frac{v}{ 2 \alpha \gamma(X_a(\tau_a + t), \eta_{\tau_a + t}) r(X_a(\tau_a + t), \eta_{\tau_a + t}) } .
 $$
@@
 % % % % % % % % % % % % %
-\subsection{Proof of convergence for the lookdown process}
-
-The proof of the main result in Section~\ref{sec:lookdown}.
-
-This will depend on Sections~\ref{sec:lookdown_tightness_proofs}
-and \ref{sec:lookdown_generator_proofs}.
-
-% % % % % % % % % % % % %
 \subsection{Tightness of the lookdown process}
     \label{sec:lookdown_tightness_proofs}
+
+In this section,
+we will prove tightness
+of the spatial and level trajectory
+of a line of descent
+(constructed in \S \ref{sec: individual lines of descent})
+as a forward-in-time process.
+
+In Appendix \ref{sec: Topologies on Lookdown},
+we will prove that
+tightness of the whole lookdown process
+holds given
+tightness of 
+all ancestral lineages
+in a countable product topology.
+
+To prove tightness of the 
+spatial and level locations
+of a typical line of descent,
+we will show that the
+jumps in
+spatial and level locations
+of the line of descent
+in finite time
+can be controlled.
+
+Recall that the lines of descents
+track chains of descendant
+individuals forwards through time following the \textit{levels}.
+
+\subsubsection{Tightness of Spatial Trajectories}
+Before proving tightness of our spatial trajectories, 
+note that for a fixed label
+$a=(a_0,a_1,..,a_k)$,
+the spatial evolution of 
+$X^N_{a}(t)$ for $t \geq \tau^N_{a}$
+is determined
+purely by the last term 
+in Equation \eqref{eq: space_across_lineage}.
+
+As a result, the spatial jumps are 
+driven by 
+an underlying Poisson point process. 
+It is therefore sufficient
+to prove that square of 
+these increments are bounded
+in small time scales.
+
+\begin{lemma} \label{lem: tightness of individual spatial trajectory}
+For fixed $a=(a_0,a_1,..,a_k)$,
+$\{(X^{N}_{a}(t))_{t \geq \tau^{N}_a}: N \in \mathbb{N},  \}$ is relatively compact in 
+$D_{\mathbb{R}^d}[0,\infty )$ where $\mathbb{R}^d$ is equipped with the standard Euclidean metric. 
+\end{lemma}
+\begin{proof}
+First,
+note that the birth time
+of $a$ at the $N$-th scaling
+regime, denoted as
+$\tau^{N}_a$,
+is identical in distribution
+for all $N > 0$.
+This is because the birth time
+of $a=(a_0,a_1,...,a_k)$
+comes after $a_1$ births
+in the 1st generation,
+followed by $a_2$ births
+in the 2nd generation, etc..
+Therefore $\tau^N_{a} \sim Gamma(\sum_{i=1}^{k}a_i,1)$.
+
+Now we prove
+convergence in distribution
+of the birth locations $X^N_{a}(\tau^N_{a})$.
+From Equation \eqref{eq: space_across_lineage},
+we have
+\begin{equation}
+\begin{aligned}
+&X^{N}_{[a]_{k}}(\tau^N_{a})- X^{N}_{[a]_{0}}(0)\\
+=& \sum_{i=1}^{k}
+\sum_{j=1}^{a_i-1}
+(1-\kappa_{[a]_{i-1}\concat j}) y_{[a]_{i-1}\concat j} \ind_{U^N_{[a]_{i-1}\concat j}(\tau_{[a]_{i-1}\concat j}) < N}\\
+&+ \sum_{i=1}^{k}
+\kappa_{[a]_i} y_{[a]_i} \ind_{U^N_{[a]_i}(\tau_{[a]_i}) < N}.
+\end{aligned}    
+\end{equation}
+
+Since $(s_{[a]_{i} \concat j}, v_{[a]_{i} \concat j}, y_{[a]_{i} \concat j}, \kappa_{[a]_{i} \concat j})
+\in \Pi_{[a]_{i-1}}$
+are all iid random variables 
+for each $i$ and $j$,
+and that the sum above is finite,
+it suffices to show that
+the quantities 
+\begin{equation}
+\mathbb{P}(U^N_{[a]_{i-1} \concat j}(\tau_{[a]_{i-1} \concat j}) < N)    
+\end{equation}
+converges
+for all $i=1,..,k$ and $j=1,..,a_i$.
+
+Writing out
+$U^N_{[a]_{i-1} \concat j}(\tau_{[a]_{i-1} \concat j})$,
+we have
+\begin{equation}
+\begin{aligned}
+&\mathbb{P}(U^N_{[a]_{i-1} \concat j}(\tau_{[a]_{i-1} \concat j}) < N) \\
+=&\mathbb{P}(U^N_{[a]_{i-1} }(\tau_{[a]_{i-1} \concat j})
+    +
+    \ell(
+    X^N_{[a]_{i-1} }(\tau_{[a]_{i-1} \concat j}-),
+    y_{[a]_{i-1} \concat j},
+    \eta^{N}(\tau_{[a]_{i-1} \concat j}-),
+    v_{[a]_{i-1} \concat j})
+    < N)\\
+=&\mathbb{P}\left(
+    \frac{
+        v_{[a]_{i-1} \concat j}
+    }{
+        2 N^{-1} \theta \gamma(x, \eta) r(x + y, \eta)
+    }
+    < N-U^N_{[a]_{i-1} }(\tau_{[a]_{i-1} \concat j})
+    \right)\\
+=&\mathbb{P}\left(
+            v^N_{[a]_{i-1} \concat j}
+    < (2 \theta \gamma(x, \eta) r(x + y, \eta)-  2 N^{-1} \theta \gamma(x, \eta) r(x + y, \eta)U^N_{[a]_{i-1} }(\tau_{[a]_{i-1} \concat j}))
+    \right)\\
+=& \frac{(2 \theta \gamma(x, \eta) r(x + y, \eta)-  2 N^{-1} \theta \gamma(x, \eta) r(x + y, \eta)U^N_{[a]_{i-1} }(\tau_{[a]_{i-1} \concat j}))}{N}\\
+\to & 2\alpha \gamma(x, \eta) r(x + y, \eta).
+\end{aligned}    
+\end{equation}
+
+We write $S_{t,r}:=(t,t+r  ]\times [0,\infty )\times [0,1]\times 
+\{0,1\}$ to be the region for the Poisson measure driving $(X^{\varepsilon,\theta, \lambda}_{\mathfrak{u}}(t))$ between time $t$ and $(t+r)$ and write $\tilde\Pi_{\tau_u}(ds,dv,dw,d\kappa):=\Pi_{\tau_u}(ds,dv,dw, d\kappa) - ds\times dv\times dw \times (\frac{1}{2}\delta_{0}+\frac{1}{2}\delta_{1})d\kappa$ be the compensated Poisson point process of $\Pi_{\tau_u}$.
+For $t\geq\tau_\mathfrak{u}$, we can compute
+\small
+\begin{eqnarray*}
+&&\mathbb{E}[|X^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t+r )-X^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t)|^2|{\cal F}_t^{
+\eta}]\\
+&&= \mathbb{E}\left[\left|\int_{S_{t,r}}{\bf 1}_{\{U_{\tau_{\mathfrak{u}}}(s)+\frac v{2\lambda^{-1}\theta \gamma^{\mathfrak{m}}_\theta(X^{\varepsilon,\theta, \lambda}_{
+\tau_{\mathfrak{u}}}(s-),\overline{\eta}^{\varepsilon,\theta, \lambda}(s-))}<\lambda \}}\kappa 
+H(X^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(s-),\overline{\eta}^{\varepsilon,\theta, \lambda}(s-),w)\Pi_{\tau_{\mathfrak{u}}}(ds,dv,dw,d\kappa )\right|^2\Bigg|{\cal F}_t^{\eta}\right]\\
+&&\leq 2\mathbb{E}\left[\left|\int_{S_{t,r}}{\bf 1}_{\{v < 2 \theta \gamma^{\mathfrak{m}}_\theta(X^{\varepsilon,\theta, \lambda}_{
+\tau}(s-),\overline{\eta}^{\varepsilon,\theta, \lambda}(s-))\}}{\bf 1}_{\kappa =1}
+H(X^{\varepsilon,\theta, \lambda}_{\tau}(s-),\overline{\eta}^{\varepsilon,\theta, \lambda}(s-),w)\tilde\Pi_{\tau_{\mathfrak{u}}}(ds,dv,dw,d\kappa )\right|^2\Bigg|{\cal F}_t^{\eta}\right]\\
+&&\quad +2\mathbb{E}\left[\left|\int_{t}^{t+r}\int_{\{v < 2 \theta \gamma^{\mathfrak{m}}_\theta(X^{\varepsilon,\theta, \lambda}_{
+\tau_{\mathfrak{u}}}(s-),\overline{\eta}^{\varepsilon,\theta, \lambda}(s-))\}}\frac{1}{2}\left| \int_{\mathbb{R}^d} (y-X^{\varepsilon,\theta, \lambda}_{\tau}(s-)) q^{\mathfrak{m}}_{\theta, \varepsilon}(X^{\varepsilon,\theta, \lambda}_{\tau}(s-),\overline{\eta}^{\varepsilon,\theta, \lambda}(s-),dy) \right|
+dvds \right|^2\Bigg|{\cal F}_t^{\eta}\right]\\
+&&\leq 2\mathbb{E}\left[\int_{t}^{(t+r)   }\theta (1+C_G)\int_{{\mathbb{R}}^d}|y-X^{\varepsilon,\theta, \lambda}_{
+\tau_{\mathfrak{u}}}(s)|^2q^{\mathfrak{m}}_{\varepsilon,\theta}(X^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(s),\bar{\eta}^{\varepsilon,\theta,\lambda}(s-),dy)ds\Bigg|{\cal F}_t^{\eta}\right]\\
+&&\quad +2\mathbb{E}\left[\left|\int_{t}^{(t+r)    } \theta (1+C_G)\left|\int_{{\mathbb{R}}^d}
+(y-X^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(s))q^{\mathfrak{m}}_{\varepsilon,\theta}(X^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(s),
+\overline{\eta}^{\varepsilon,\theta, \lambda}(s),dy)\right|ds\right|^2\Bigg|{\cal F}_t^{\eta}\right]\\
+&&\leq 2r \overline{\beta}(1+C_G)+2(r \overline{\alpha}(1+C_G))^2.\end{eqnarray*}
+\normalsize
+
+The first inequality uses the fact that $(A+B)^2 \leq 2A^2+2B^2$ as well as the definition of the transition kernel $H$.
+The second inequality holds because birth events occur at rate $2 \theta \gamma^{\mathfrak{m}}_{\theta}$ bounded above by $2\theta (1+C_G)$.
+The third inequality holds given the assumptions on the dispersal kernel.
+
+Finally, since $\overline{\eta}_0$ has compact support, we can take $t=\tau_u$ and apply Markov inequality to get that for every $\delta>0$, there exists $N_{\delta}>0$ such that
+\begin{equation}\label{eq: Compact Containment Condition for individual spatial motion}
+\sup_{\varepsilon, \theta, \lambda}\sup_{T>0}\mathbb{P}\left[|X^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(\tau_{\mathfrak{u}}+T)-X^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(\tau_{\mathfrak{u}})|>N_{\delta}\right]\leq   \frac{2r \overline{\beta}(1+C_G)+2(r \overline{\alpha}(1+C_G))^2}{N_{\delta}^2}  < \delta,
+\end{equation}
+giving us compact containment condition. Relative compactness thus follows by Theorem 3.8.6.
+of \cite{ethier/kurtz:1986}.
+\end{proof}
+\begin{remark}
+Note that under the assumptions laid out in Theorem \ref{teo: Non-local interaction Convergence} and Theorem \ref{teo: Local Interaction Convergence}, $r \equiv 1$, so 
+$$\gamma^{\mathfrak{m}}_{\varepsilon,\theta}(x, \overline{\eta})=\tilde\gamma_{\theta}(x, \varrho_{\varepsilon}*\overline{\eta})= 1+\frac{G(\varrho_{\varepsilon}*\overline{\eta})}{\theta} \leq (1+C_G)$$
+for all $\theta > 1$, and 
+$$q^{\mathfrak{m}}_{\varepsilon,\theta,\lambda}(x,\overline{\eta},dy)=q_{\theta}(x,dy).$$
+In particular, we have the inequalities
+\begin{align}
+   \sup_{\varepsilon, \theta}\limsup_{x, \overline{\eta}} \theta \left| \int_{\mathbb{R}^d} (y-x) q^{\mathfrak{m}}_{ \varepsilon, \theta}(x,\overline{\eta},dy) \right| =& \sup_{\theta}\limsup_{x} \theta \left| \int_{\mathbb{R}^d} (y-x) q_{\theta}(x,dy) \right| =  0,\\
+   \sup_{\varepsilon, \theta}\limsup_{x, \overline{\eta}} \theta \int_{\mathbb{R}^d} |y-x|^2 q^{\mathfrak{m}}_{ \varepsilon, \theta}(x,\overline{\eta},dy)  =& \sup_{\theta}\limsup_{x} \theta \int_{\mathbb{R}^d} |y-x|^2 q_{\theta}(x,dy) =  1,
+\end{align}
+as the last term can be expressed as $\theta \mathbb{E}_{x}[(B_{1/\theta}-x)^2]=1$.
+As a result, Lemma \ref{lem: tightness of individual spatial trajectory} holds for the setting in Theorem \ref{teo: Non-local interaction Convergence} and Theorem \ref{teo: Local Interaction Convergence}.
+\end{remark}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Tightness of Level Processes}
+Proving tightness of the level process is slightly trickier as the levels of many particles will drift towards infinity in finite time.
+These particles however will not contribute to the metric associated with the vague topology and thus we will retain relative compactness.
+The main argument relies on the observation that particles with levels lower than some threshold $\overline{U}_{N, \delta}$  have regulated level increments of order $\delta$ over any small time interval of length $r$ given large enough $\lambda$.
+As a result, we can evaluate our level process against test functions $(g_n)_{n=1,..,N}$ with cut off smaller than $\overline{U}_{N, \delta}$.
+
+\begin{lemma} \label{tightness of levels} For fixed $\mathfrak{u}\in \mathcal{U}$,
+$\{(U^{\varepsilon,\theta, \lambda}_{\tau_\mathfrak{u}}(t))_{t \geq 0}, \lambda >0\}$ is relatively compact in 
+$\mathcal{D}_{[0,\infty]}[0,\infty )$ where $[0,\infty]$ is equipped with the metric $\mathfrak{d}$ for the vague topology in $[0,\infty]$ (see Theorem  \ref{Vague times Euclidean is Polish}).
+\end{lemma}
+
+\begin{proof}
+
+\textbf{Introducing a cutoff range:} It suffices to show that for any $\delta > 0$ and for any particle $\mathfrak{u} \in \mathcal{U}$, there exists small enough  $r>0$ such that $\mathbb{E}[\mathfrak{d}(U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t+r),U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t))|{\cal F}_t^{
+\eta}]< \delta$. \\
+For this, pick $K_{\delta} \in \mathbb{N}$ such that $\frac{1}{2^{K_{\delta}}} < \delta/2$. then we have that 
+\begin{multline}
+\mathfrak{d}(U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t+r),U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t))\leq  \sum_{n=1}^{K_{\delta}}\frac{1 \wedge |g_n(U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t+r))-g_n(U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t))|}{2^n} +  \delta/2.
+\end{multline}
+Now it suffices to prove that for small enough $r$, $|g_n(U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t+r))-g_n(U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t))| < \delta / (2K_{\delta})$.
+
+Pick $\overline{U}_{K_{\delta}, \delta}>0$ large enough such that $\text{supp}(g_n)\subset [0,\overline{U}_{K_{\delta}, \delta}]$ for all $n=1,..,K_{\delta}$.
+Since we picked $g_n$ to be continuous and differentiable with compact support, by Mean Value Theorem we have that
+$$|g_n(U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t+r))-g_n(U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t))|<C'_{g_1,..,g_{K_\delta}}(|U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t+r)-U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t)|\wedge \overline{U}_{K_{\delta}, \delta}), $$
+uniformly over $n=1,..,K_{\delta}$ for some constant $C'_{g_1,...,g_{K_{\delta}}}$.
+Note that it suffices to consider $|U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t+r)-U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t)|\wedge \overline{U}_{K_{\delta}, \delta}$ because $g_n(u)=g_n(\overline{U}_{K_{\delta}, \delta})=0$ for all $u > \overline{U}_{K_{\delta}, \delta}$.
+We proceed to bound $|U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t+r)-U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t)|$ given that $U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t) < \overline{U}_{K_{\delta}, \delta}$.
+
+\textbf{Controlling downward drift:} We first consider the case where $\tau_{\mathfrak{u}}< t$, i.e. the particle $\mathfrak{u}$ is born before time $t$. 
+We have that 
+\small
+\begin{equation}
+\begin{aligned}
+U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t+r)-U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t) =  &   \int_{t}^{(t+r)  }\frac{1}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon, \theta}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s),\Xi^{\varepsilon, \theta, \lambda}(s))}dV^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s)\\
+&+\int_{t}^{(t+r)  }\bigg(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon, \theta}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s),\Xi^{\varepsilon, \theta, \lambda}(s))U^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s)^2 - b_{\varepsilon, \theta, \lambda}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s),\Xi^{\varepsilon, \theta, \lambda}(s))U^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s)\bigg)ds,
+\end{aligned}
+\end{equation}
+\normalsize
+where the first term corresponds to positive jumps and the second term corresponds to the evolution according to a quadratic differential equation.
+To control the downward drift of our levels from the quadratic evolution,
+we neglect all positive drift and obtain
+\begin{equation}
+\begin{aligned}
+\mathbb{E}[U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t+r)-U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t)] \geq   &   - \int_{t}^{(t+r)  } G(\varrho_{\varepsilon}*\Xi^{\varepsilon, \theta, \lambda}_s(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s))) U^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s)ds\\
+\geq& - rC_G\overline{U}_{K_{\delta}, \delta}.
+\end{aligned}    
+\end{equation}
+
+\textbf{Controlling Upward Drift with Comparison Principle:}
+On the other hand, the positive increments are due to jumps and the quadratic evolution. To control the quadratic upward drift, we apply comparison principle.
+
+The process $(W_s)_{s \geq 0}:=(U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t+s)\wedge \overline{U}_{K_{\delta}, \delta})_{s \geq 0}$ satisfy the differential inequality with jumps of the form
+\begin{equation}
+\begin{aligned}
+ dW_s \leq& \frac{1}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon, \theta}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s),\Xi^{\varepsilon, \theta, \lambda}(s))}dV^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s)\wedge \overline{U}_{K_{\delta}, \delta}\\
+ &+\bigg(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon, \theta}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s),\Xi^{\varepsilon, \theta, \lambda}(s))W_s^2 - b_{\varepsilon, \theta, \lambda}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s),\Xi^{\varepsilon, \theta, \lambda}(s))W_s\bigg)\mathbbm{1}_{W_s \leq \overline{U}_{K_{\delta}, \delta}}ds,
+\end{aligned}
+\end{equation}
+with initial condition $W_0=U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t)\leq \overline{U}_{K_{\delta},\delta}$.
+The first term is due to the fact that all jumps of $(U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t+s))_{s \geq 0}$ that lands above $\overline{U}_{K_{\delta}, \delta}$ will result in  the process $(W_s)_{s \geq 0}$ landing on $\overline{U}_{K_{\delta}, \delta}$.
+The indicator function in the second term is due to the process staying at $\overline{U}_{K_{\delta}, \delta}$ once the process hit the value.
+
+Note that we have $\gamma^{\mathfrak{m}}_{\varepsilon, \theta}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s),\Xi^{\varepsilon, \theta, \lambda}(s)) \leq (1+C_G),$ and $- b_{\varepsilon, \theta, \lambda}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s),\Xi^{\varepsilon, \theta, \lambda}(s)) \leq \varrho_{\varepsilon}*\Xi^{\varepsilon, \theta, \lambda}_{s}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s)).$ Furthermore, recall that $V_{\tau}(t)=\sum_{k=1}^{m}v_k\mathbbm{1}_{[0, \tau_k]}  (t)  $ and all jumps are at most of size $\overline{U}_{K_{\delta}, \delta}$ for the process $(W_s)_{s \geq 0}$, By the comparison principle, for any $s \geq 0$, $W_s-W_0$ is bounded above by the increment $\widetilde{W}_s-\widetilde{W}_0$ of a process $(\widetilde{W}_s)_{s \geq 0}$ which satisfies
+\begin{equation}
+\begin{aligned}
+ d\widetilde{W}_s =& \overline{U}_{K_{\delta}, \delta} dN_{\tau_\mathfrak{u}}(s) +\bigg(\lambda^{-1} \theta (1+C_G)\overline{U}_{K_{\delta}, \delta}^2 + \varrho_{\varepsilon}*\Xi^{\varepsilon, \theta, \lambda}_{s}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s)) \overline{U}_{K_{\delta}, \delta}\bigg)ds.
+\end{aligned}
+\end{equation}
+Here $(N_{\tau_\mathfrak{u}}(s))_{s \geq 0}$ is the Poisson point process $N_{\tau_\mathfrak{u}}(t)=\sum_{k=1}^{m}\mathbbm{1}_{[0, \tau_k]}  (t) $ with rate $1$ and $\widetilde{W}_0 = \overline{U}_{K_{\delta}, \delta}$.
+
+Taking expectations, we have that 
+\begin{equation}
+\begin{aligned}
+\mathbb{E}[\widetilde{W}_{t+r}-\widetilde{W}_t] \leq &   \overline{U}_{K_{\delta}, \delta}r + \lambda^{-1} \theta (1+C_G)\overline{U}_{K_{\delta}, \delta}^2r + \overline{U}_{K_{\delta}, \delta} \int_{t}^{t+r}\mathbb{E}\left[\varrho_{\varepsilon}*\Xi^{\varepsilon, \theta, \lambda}_{s}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s))\right]ds\\
+\leq & \overline{U}_{K_{\delta}, \delta}r + \lambda^{-1} \theta (1+C_G)\overline{U}_{K_{\delta}, \delta}^2r +\overline{U}_{K_{\delta}, \delta} \int_{t}^{t+r}\left(C_0
++   K' e^{C_G s}\right)e^s ds \\
+= & \overline{U}_{K_{\delta}, \delta}r + \lambda^{-1} \theta (1+C_G)\overline{U}_{K_{\delta}, \delta}^2r +\overline{U}_{K_{\delta}, \delta} +(C_0e^t+\frac{C_0K'}{C_G+1}e^{C_G+1})(e^{r}-1).
+\end{aligned}
+\end{equation}
+
+\textbf{Controlling Increments by Birth Events:}
+Now consider the scenario where $t > \tau_u$, i.e.
+the particle $\mathfrak{u}$ has not been born at time $t$.
+Denote $\mathcal{B}^{\varepsilon,\theta, \lambda}_{\mathfrak{u}}([t,t+r  ])$ to be the event that particle $\mathfrak{u}$ is born between $[t,t+r  ]$ with level smaller than $U_{K_{\delta}, \delta}$.
+In this case,
+\begin{multline}
+ |g_n(U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t+r))-g_n(U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t))|\\
+ =g_n(U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t+r))\times\mathbbm{1}_{\mathcal{B}^{\varepsilon,\theta, \lambda}_{\mathfrak{u}}([t,t+r  ])}\\
+ < C_{g_1,...,g_n}\times \mathbbm{1}_{\mathcal{B}^{\varepsilon,\theta, \lambda}_{\mathfrak{u}}([t,t+r  ])},   
+\end{multline}
+for some uniform bound $C_{g_1,...,g_n}$ over $\{||g_n||_{\infty}: n =1,...,N \}$.
+It suffices therefore to show that the probability for a particle $\mathfrak{u}$ to be born or gives birth in some time interval of length less than or equal to $r$ can be arbitrarily small given small enough $r$.
+Let $\mathcal{N}^{\varepsilon,\theta, \lambda}_{\mathfrak{u}}([t,t+r  ])$ to be the number of particles born between $[t,t+r]$ with level smaller than $U_{K_{\delta}, \delta}$.
+Then
+\begin{equation}
+\begin{aligned}
+\mathbb{P}[\mathcal{B}^{\varepsilon,\theta, \lambda}_{\mathfrak{u}}([t,t+r  ])]  \leq&  \mathbb{P}[\mathcal{N}^{\varepsilon,\theta, \lambda}_{\mathfrak{u}}([t,t+r  ]) \geq 1]\\
+\leq & \mathbb{E}[\mathcal{N}^{\varepsilon,\theta, \lambda}_{\mathfrak{u}}([t,t+r  ]) ].
+\end{aligned}
+\end{equation}
+Recall that we have bounds over the total mass of the particle systems, so at time $t$, the expected number of particles alive in the $N$-th stage of scaling is bounded above $\lambda_NC_0e^{C_Gt}$ (with $\lambda_N=N$).
+The particles have levels that are independently and uniformly distributed between $[0, \lambda_N]$.
+Therefore, the expected number of particles with levels between $[0,U_{K_{\delta}, \delta}]$ is $U_{K_{\delta}, \delta}C_0e^{C_Gt}$.
+The number of births within an interval of length $r$ is a sum of Poisson random variables, and so we have
+$$\mathbb{E}[\mathcal{N}^{\varepsilon,\theta, \lambda}_{\mathfrak{u}}([t,t+r  ]) ]=U_{K_{\delta}, \delta}C_0e^{C_Gt}r.$$
+
+\textbf{Conclusion:} Combining all of the above results, we have that for any $\delta > 0$,
+\begin{equation}
+\begin{aligned}
+\mathbb{E}[\mathfrak{d}(U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t+r),U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t))] \leq & \mathbb{E}\left[\sum_{n=1}^{K_{\delta}}\frac{1 \wedge |g_n(U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t+r))-g_n(U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t))|}{2^n}\right] +  \delta/2\\
+\leq &\mathbb{E}\left[\sum_{n=1}^{K_{\delta}}\frac{1 \wedge |g_n(U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t+r))-g_n(U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t))|}{2^n}: \tau_{\mathfrak{u}} \leq t \right]\\
+& + \mathbb{E}\left[\sum_{n=1}^{K_{\delta}}\frac{1 \wedge |g_n(U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t+r))-g_n(U^{\varepsilon,\theta, \lambda}_{\tau_{\mathfrak{u}}}(t))|}{2^n}: \tau_{\mathfrak{u}} \geq t \right] + \delta/2\\
+\leq & C'_{g_1,...,g_n}\bigg(\overline{U}_{K_{\delta}, \delta}r + \lambda^{-1} \theta (1+C_G)\overline{U}_{K_{\delta}, \delta}^2r\\
+& \qquad \qquad  +\overline{U}_{K_{\delta}, \delta} +(C_0e^t+\frac{C_0K'}{C_G+1}e^{C_G+1})(e^{r}-1)\bigg)\\
+& + C'_{g_1,...,g_n}U_{K_{\delta}, \delta}C_0e^{C_Gt}r+\delta/2\\
+< & \delta 
+\end{aligned}    
+\end{equation}
+for small enough $r>0$. In particular, this choice of $r$ is independent of $\varepsilon, \theta, \lambda$. Therefore we have proved tightness of our level processes by \cite{EK} Theorem 3.8.6.
+\end{proof}
+\subsubsection{Convergence in $\mathcal{D}_{[0,\infty)}\left(\mathcal{N}_f(\mathbb{R}^d \times [0, \infty)\right)$ to $(\xi^{ \infty}_t)_{t \geq 0}$, where $\mathcal{N}_f(\mathbb{R}^d \times [0, \infty)$}
+Now that we have proven tightness for individual level and spatial trajectories, by Corollary \ref{cor: convergence in p implies convergence in p-infty}, Lemma \ref{lem: Countable Implies Vague} and Theorem \ref{teo: Theorem A12 Kurtz Rodrigues generalised}, we have proved that the particle system $(\xi^{\varepsilon_N, \theta_N,\lambda_N}_t)_{t \geq 0}$ converges in $\mathcal{D}_{[0,\infty)}\left(\mathcal{N}_f(\mathbb{R}^d \times [0, \infty)\right)$ to $(\xi^{ \infty}_t)_{t \geq 0}$, where $\mathcal{N}_f(\mathbb{R}^d \times [0, \infty)$ is equipped with the $\mathfrak{p}^{wv}$-topology.
+Furthermore, its spatial projection $(\overline{\eta}^{\varepsilon_N, \theta_N,\lambda_N}_t)_{t \geq 0}$ converges to $(\overline{\eta}^{\infty}_t)_{t \geq 0}$ in $\mathcal{D}_{[0,\infty)}\left(\mathcal{M}_f(\mathbb{R}^d \right)$, where $\mathcal{M}_f(\mathbb{R}^d)$ is equipped with the weak topology.
+
+In the next section, we will show how we identify the limit process.
 
@@
 }
+
+% % % % % % % % % % % % %
+\subsection{Proof of convergence for the lookdown process}
+
+The proof of the main result in Section~\ref{sec:lookdown}.
+
+This will depend on Sections~\ref{sec:lookdown_tightness_proofs}
+and \ref{sec:lookdown_generator_proofs}.
 
@@
 \end{proof}
+\section{Topological Results on Lookdown Representations}
+\label{sec: Topologies on Lookdown}
+\subsection{Particle Systems under Product Topology}\label{sec: Convergence in Product Topology}
+
+We define the topology $\mathfrak{p}$ on $\mathbb{R}^d \times [0,\infty]:$
+we say $(x_n,u_n) \to (x,u)$ in topology $\mathfrak{p}$ if 
+\begin{enumerate}
+    \item $|x_n-x| \to 0$ in $\mathbb{R}^d$.
+    \item  For all $g \in C_{c}([0,\infty])$, the space of continuous functions with compact support on $[0,\infty]$, $g(u_n) \to g(u).$ Since this is the vague convergence for $(\delta_{u_n})_{n \in \mathbb{N}}$ we will abuse a bit the notation and denote this by the symbol $u_n \xrightarrow{vague} u$.
+\end{enumerate}
+In other words, our topology is Euclidean in space ($\mathbb{R}$) and vague in level ($[0,\infty]$).
+\begin{lemma}\label{Vague times Euclidean is Polish}
+The space $\mathbb{R}^d \times [0,\infty]$ under topology $\mathfrak{p}$ is Polish.
+\end{lemma}
+\begin{proof}
+It suffices to show that the convergence of $u_n \xrightarrow{vague} u$ is metrisable and gives a separable space.
+The space $C_c([0,\infty])$ is dense, so we pick a countable dense subset $S:=\{h_n: n \in \mathbb{N}\} \subset C^{1}_c([0,\infty])$ and define the metric $\mathfrak{d}$ such that $\mathfrak{d}(u,v)=\sum_{n=1}^{\infty}\frac{1 \wedge |h_n(u)-h_n(v)|}{2^n}$.\\ Assume that $u_n \xrightarrow{vague} u$.
+Pick arbitrary $\delta>0$ and take $N$ large enough such that $\frac{1}{2^N}<\delta/2$.
+Furthermore, pick $n$ large enough such that $\inf_{i=1,2,...,N}|h_i(u_n)-h_i(u)|<\delta/2$.
+From this we immediately have that $\mathfrak{d}(u_n,u)<\delta$.
+Thus $\mathfrak{d}(u_n,u) \to 0$.\\\\
+Conversely assume that $\mathfrak{d}(u_n,u) \to 0$.
+For any $h \in \mathcal{C}^{1}_c([0,\infty])$ and for any $\delta>0$, pick $g_N$ such that $||h-h_N||_{\infty}<\delta /3$ and $n$ large enough such that $\mathfrak{d}(u_n,u)< \frac{\delta}{3 \times 2^N}$.
+Then $|h(u)-h(u_n)|< |h(u)-h_N(u)|+|h_N(u)-h_N(u_n)|+|h_N(u_n)-h(u_n)|<\delta$, and so $h(u_n) \to h(u)$.\\\\
+Finally, one can easily check that $\mathbb{Q}$ is a countable dense set in $[0,\infty]$ equipped with the metric $\mathfrak{d}$.
+\end{proof}
+The metric $d_{\mathfrak{p}}$ satisfies
+$$d_{\mathfrak{p}}((x_1,u_1),(x_2,u_2))=||x_1-x_2||+\mathfrak{d}(u_1,u_2).$$
+\begin{definition}[Test functions for $\mathfrak{p}$]\label{def: Test functions for p-topology}
+We define $$\mathfrak{G}:= \{g(x,u):~~\text{for all } x \in \mathbb{R}^d, ~ u \in [0, \infty],~~ g(\cdot,u) \in C_0(\mathbb{R}^d), ~~ g(x, \cdot) \in C_{c}([0,\infty])  \}$$
+to be the test functions on $\mathbb{R}^d \times [0, \infty]$ under the $\mathfrak{p}$-topology. Similarly, we define 
+$$\mathfrak{G}_{\leq 1}:=\{g \in \mathcal{C}_{b}(\mathbb{R}^d \times [0, \infty]): ~ 0< g \leq 1 ~\& ~\exists ~ U_g ~s.t. ~~g(\cdot,u)\equiv 1 \text{ for all } u\geq U_g\}$$
+to be the set of test functions bounded above by $1$.
+\end{definition}
+
+\begin{lemma}\label{lem: convergence determining test functions}
+The collection of test functions $\mathfrak{G}$ is dense in $\mathcal{C}_{0}(\mathbb{R}^d \times [0, \infty], \mathbb{R})$ under the topology of uniform convergence given by metric $d_{\mathfrak{p}}$.
+It is also convergence determining.
+\end{lemma}
+\begin{proof}
+It is immediately clear that $\mathfrak{G}$ forms an algebra and vanishes nowhere.
+Furthermore, for any $(x_1,u_1), (x_2,u_2) \in \mathbb{R}^d \times [0, \infty]$ such that $d_{\mathfrak{p}}((x_1,u_1), (x_2,u_2)) > \delta$, by definition, $$||x_1-x_2||+\sum_{n=1}^{\infty}\frac{1 \wedge |h_n(u_1)-h_n(u_2)|}{2^n}>\delta.$$
+As a result, there must exists some $K>0$ such that 
+$$||x_1-x_2||+\sum_{n=1}^{K}|h_n(u_1)-h_n(u_2)|>\delta/2,$$
+and $$\max \{||x_1-x_2||,|h_1(u_1)-h_1(u_2)|,..., |h_n(u_1)-h_n(u_2)|\}>0.$$
+We write $g_0(x,u)=\varrho*||x|| \mathbbm{1}_{B((x_1,u_1),2\delta)}$ and $g_n(x,u)=\varrho*h_n(u)\mathbbm{1}_{B((x_1,u_1),2\delta)}$ for all $n =1,...,K$.
+Here we pick $\varrho$ to be some mollifier such that $g_0,..,g_K$ are all continuous and in $\mathfrak{G}$.
+Therefore,
+$$\inf_{(x',u'): d_{\mathfrak{p}}((x,u),(x',u'))> \delta} \max_{0 \leq n \leq K} |g_n(x,u)-g_n(x',u')| >0.$$
+According to Theorem 3.4.5.
+in \cite{EK}, $\mathfrak{G}$ is strongly separable and thus separable.
+Density in $\mathcal{C}_{0}(\mathbb{R}^d \times [0, \infty], \mathbb{R})$ follows from the Stone-Weierstrass Theorem and by Theorem 3.4.6.
+in \cite{EK}, $\mathfrak{G}$ is convergence determining.
+\end{proof}
+\begin{definition}[State Space for Individual Trajectories]\label{metric for countable topology}
+We denote $\mathcal{X}_{\mathfrak{u}}$ to be the state space of the spatial-level location of particle $\mathfrak{u}$, i.e.
+we impose $\mathcal{X}_{\mathfrak{u}}$ to be the space $\mathbb{R}^d \times [0,\infty]$ equipped with the topology $\mathfrak{p}$ defined above.
+We define $d_{\mathfrak{p}}$ to be the metric for the Polish space $\mathbb{R}^d \times [0,\infty]$ under the topology $\mathfrak{p}$.
+
+We denote the countable product space of $\mathcal{X}_{\mathfrak{u}}$ as
+$\prod_{\mathfrak{u} \in \mathcal{U}}\mathcal{X}_{\mathfrak{u}}$, with a typical element $(\textbf{x},\textbf{u})$ having the form
+$$(\textbf{x},\textbf{u}):=\big((x_\mathfrak{u_1},u_\mathfrak{u_1}),(x_\mathfrak{u_2},u_\mathfrak{u_2}),...,(x_\mathfrak{u_n},u_\mathfrak{u_n}),...\big).$$
+
+We define the product metric $d_{\mathfrak{p}^{\infty}}$ as follows: for two countable particle systems $(\textbf{x}^1,\textbf{u}^1):=\big((x^1_\mathfrak{u_1},u^1_\mathfrak{u_1}),(x^1_\mathfrak{u_2},u^1_\mathfrak{u_2}),...,(x^1_\mathfrak{u_n},u^1_\mathfrak{u_n}),...\big)$ and $(\textbf{x}^2,\textbf{u}^2):=\big((x^2_\mathfrak{u_1},u^2_\mathfrak{u_1}),(x^2_\mathfrak{u_2},u^2_\mathfrak{u_2}),...,(x^2_\mathfrak{u_n},u^2_\mathfrak{u_n}),...\big)$,
+$$d_{\mathfrak{p}^{\infty}}\big((\textbf{x}^1,\textbf{u}^1),(\textbf{x}^2,\textbf{u}^2)\big):=\sum_{n=1}^{\infty}\frac{d_{\mathfrak{p}}\big((x^1_{\mathfrak{u}_n},u^1_{\mathfrak{u}_n}), (x^2_{\mathfrak{u}_n},u^2_{\mathfrak{u}_n})\big)\wedge 1}{2^n}.$$
+
+Since $(\mathcal{X}_{\mathfrak{u}},\mathfrak{p})$ is a Polish space with metric $d_{\mathfrak{p}}$, the countable product space 
+$\prod_{\mathfrak{u} \in \mathcal{U}}\mathcal{X}_{\mathfrak{u}}$ under the canonical product metric $d_{\mathfrak{p}^{\infty}}$
+is also a Polish space.
+\end{definition}
+
+\begin{lemma}[Convergence-determining test functions under $\mathfrak{p}^{\infty}$-topology]\label{lem: test functions under countable topology}
+The collection of functions given by 
+\begin{equation}
+M_{\infty}=\left\{F_{g,n}(\textbf{x},\textbf{u}):=\prod_{k=1}^{n}g_k(x_k,u_k): n\geq 1, ~~ k=1,...,n,~~ g_k \in \mathfrak{G}\cup\{1\}\right\}    
+\end{equation}
+is convergence-determining in the space $\prod_{\mathfrak{u} \in \mathcal{U}}\mathcal{X}_{\mathfrak{u}}$ under the $\mathfrak{p}^{\infty}$-topology.
+\end{lemma}
+\begin{proof}
+This follows immediately from Theorem 3.4.6 in \cite{EK} and Lemma \ref{lem: convergence determining test functions}.
+\end{proof}
+
+\begin{corollary}\label{cor: convergence in p implies convergence in p-infty} For each $\mathfrak{u} \in \mathcal{U}$, we let $\mathcal{X}_{\mathfrak{u}}= \mathbb{R}^{d}\times[0, \infty]$ equipped with the $\mathfrak{p}$-topology.
+Suppose the process $(U^{n}_{\mathfrak{u}}(t),X^{n}_{\mathfrak{u}}(t))_{t \geq 0}$ converges to some $(U^{\infty}_{\mathfrak{u}}(t),X^{\infty}_{\mathfrak{u}}(t))_{t \geq 0}$ under the Skorokhod topology in $\mathcal{D}_{[0,\infty)}(\mathcal{X}_{\mathfrak{u}})$ for each $\mathfrak{u} \in \mathcal{U}$.
+Then the countable product process satisfies
+\begin{equation}
+\Big(\textbf{X}^{n}_{\mathfrak{u}}(t ),\textbf{U}^{n}_{\mathfrak{u}}(t )\Big)_{t \geq 0} \to \Big(\textbf{X}^{\infty}_{\mathfrak{u}}(t ),\textbf{U}^{\infty}_{\mathfrak{u}}(t )\Big)_{t \geq 0}~~ \text{ in } ~~ \mathcal{D}_{[0,\infty)}\prod_{\mathfrak{u} \in \mathcal{U}}\mathcal{X}_{\mathfrak{u}},
+\end{equation}
+under the Skorokhod topology, where $\prod_{\mathfrak{u} \in \mathcal{U}}\mathcal{X}_{\mathfrak{u}}$ is equipped with the $\mathfrak{p}^{\infty}$ topology given by the metric $d_{\mathfrak{p}^{\infty}}$.
+\end{corollary}
+\begin{proof}
+By Lemma \ref{lem: test functions under countable topology} and Corollary 3.9.2 in \cite{EK}, using the fact that $M_{\infty}$ strongly separate points, it suffices to show that for any finite set $\{F_{g_1,n_1},...,F_{g_k,n_k} \} \in M_{\infty}$, as $m \to \infty$,
+\begin{multline}
+\left(F_{g_1,n_1}(\textbf{X}^{m}_{\mathfrak{u}}(t ),\textbf{U}^{m}_{\mathfrak{u}}(t )),F_{g_2,n_2}(\textbf{X}^{m}_{\mathfrak{u}}(t ),\textbf{U}^{m}_{\mathfrak{u}}(t )),...,F_{g_k,n_k}(\textbf{X}^{m}_{\mathfrak{u}}(t ),\textbf{U}^{m}_{\mathfrak{u}}(t ))\right)\\
+\to \left(F_{g_1,n_1}(\textbf{X}^{\infty}_{\mathfrak{u}}(t ),\textbf{U}^{\infty}_{\mathfrak{u}}(t )),F_{g_2,n_2}(\textbf{X}^{\infty}_{\mathfrak{u}}(t ),\textbf{U}^{\infty}_{\mathfrak{u}}(t )),...,F_{g_k,n_k}(\textbf{X}^{\infty}_{\mathfrak{u}}(t ),\textbf{U}^{\infty}_{\mathfrak{u}}(t ))\right) \text{  in  } \mathcal{D}_{[0,\infty)}\mathbb{R}^{k}.
+\end{multline}
+As the expression above concerns finite-dimensional convergence of finite products, it suffices to show that for any arbitrary $g \in \mathfrak{G}$ and $\mathfrak{u}  \in \mathcal{U}$, the process 
+$\left(g(U^{n}_{\mathfrak{u}}(t),X^{n}_{\mathfrak{u}}(t))\right)_{t \geq 0}$ converges to $\left(g(U^{\infty}_{\mathfrak{u}}(t),X^{\infty}_{\mathfrak{u}}(t))\right)_{t \geq 0}$ in $\mathcal{D}_{[0,\infty)}(\mathbb{R})$, which is equivalent to the process $(U^{n}_{\mathfrak{u}}(t),X^{n}_{\mathfrak{u}}(t))_{t \geq 0}$ converging to some $(U^{\infty}_{\mathfrak{u}}(t),X^{\infty}_{\mathfrak{u}}(t))_{t \geq 0}$ under the Skorokhod topology in $\mathcal{D}_{\mathcal{X}_{\mathfrak{u}}}([0,\infty))$.
+\end{proof}
+
+Given the above topological set-up, 
+our population system at the $\lambda$-th stage of scaling is
+$$\Big(\textbf{X}^{\varepsilon,\theta, \lambda}_{\mathfrak{u}}(t ),\textbf{U}^{\varepsilon,\theta, \lambda}_{\mathfrak{u}}(t )\Big)_{t \geq 0}:=\Big((X^{\varepsilon,\theta, \lambda}_{\mathfrak{u}_1}(t),U^{\varepsilon,\theta, \lambda}_{\mathfrak{u}_1}(t)),(X^{\varepsilon,\theta, \lambda}_{\mathfrak{u}_2}(t),U^{\varepsilon,\theta, \lambda}_{\mathfrak{u}_2}(t)),....\Big)_{t \geq 0} \in \mathcal{D}_{[0,\infty)}\left(\prod_{\mathfrak{u} \in \mathcal{U}}\mathcal{X}_{\mathfrak{u}}\right),$$
+which is again a Polish space.
+Before proving tightness of our process in the above space, we shall highlight why proving convergence in this topology is useful.
+First of all, it is simpler to prove convergence of our particle system in the product topology - it suffices to prove that the trajectories of the spatial location and level of an individual particle converge.
+Furthermore, as shown in \S \ref{sec: Empirical Measure Topology}, convergence in the product topology gives convergence of the empirical measures in $\mathcal{M}_{F}(\mathbb{R}^d, [0, \infty])$ under a Polish metric.
+
+\subsection{Particle Systems as Empirical Measures}\label{sec: Empirical Measure Topology}
+\begin{definition}\label{def: Weak-Vague topology convergence}
+We say that a sequence of point measures $\xi^{n} \in \mathcal{N}_f(\mathbb{R}^d \times [0, \infty])$ converges in the $\mathfrak{p}^{wv}$-topology if for all $f \in C_0(\mathbb{R}^d)$ and all $h \in \mathcal{C}_c([0, \infty])$,
+\begin{equation}\label{eq: Weak-Vague topology characterisation}
+\int_{\mathbb{R}^d \times [0, \infty]}f(x)h(u)\xi^{n}(dx,du) \to    \int_{\mathbb{R}^d \times [0, \infty]}f(x)h(u)\xi^{\infty}(dx,du) 
+\end{equation}
+for some measure $\xi^{\infty} \in \mathcal{N}_{f}(\mathbb{R}^d \times [0, \infty])$.
+\end{definition}
+\begin{lemma}\label{lem: Metrizability of the weak-vague topology}
+The topology $\mathfrak{p}^{wv}$ is metrizable and gives a Polish space.
+\end{lemma}
+\begin{proof}
+Take $\{h_n: n \in \mathbb{N}\}$ to be a dense set of functions in $\mathcal{C}_c([0, \infty])$ and let $\{f_m : m \in \mathbb{N}\}$ be a dense set of functions in $\mathcal{C}_0(\mathbb{R}^d)$.
+For a point measure $\xi \in \mathcal{N}_f(\mathbb{R}^d \times [0, \infty])$, we define $\xi_{X} := \sum_{(x,u) \in \xi} \delta_x \in \mathcal{N}_f(\mathbb{R}^d)$ to be its spatial projection and $\xi_{U} := \sum_{(x,u) \in \xi} \delta_u \in \mathcal{N}_f([0,\infty])$ to be its level projection.
+For $\xi, \zeta \in \mathcal{N}_f(\mathbb{R}^d \times [0, \infty])$, we define
+$$\mathfrak{d}'(\xi, \zeta):=\sum_{m=1}^{\infty}\frac{|h_m(\xi_U)-h_m(\zeta_U)|\wedge 1}{2^m}+\sum_{n=1}^{\infty}\frac{|f_n(\xi_X)-f_n(\zeta_X)|\wedge 1}{2^n}.$$
+
+The proof will be nearly identical as that of Lemma \ref{Vague times Euclidean is Polish}.
+In particular, the set of point measures on rational points is countable and dense in $\mathcal{N}_{f}(\mathbb{R}^d \times [0, \infty])$ under $\mathfrak{p}^{wv}$.
+\end{proof}
+\begin{lemma}\label{lem: Dense set for test functions on empirical measures}[Dense set of $C_{c}(\mathcal{N}_f(\mathbb{R}^d \times [0, \infty)),\mathbb{R})$] For $g \in \mathfrak{G}_{\leq 1}$, define $F_g(\xi):= \exp(-\langle \log g, \cdot \rangle )$.
+The set of functions
+$$\left\{\sum_{m=1}^{N}a_m F_{g_m}(\cdot) ~~|~~ g_1,...,g_N \in \mathfrak{G}_{\leq 1}\right\}$$
+is dense in $C_{c}(\mathcal{N}_f(\mathbb{R}^d \times [0, \infty)),\mathbb{R})$.
+\end{lemma}
+\begin{proof}
+Direct application of Stone-Weierstrass Theorem.
+These finite combinations are closed under addition by construction, and they are closed under multiplication as $F_{g_1}(\cdot) \times F_{g_2}(\cdot):=F_{g_1 \times g_2}(\cdot)$.
+Thus we have a subalgebra that also clearly separates points and vanishes nowhere.
+\end{proof}
+
+\subsection{Convergences in Equivalent Topologies}
+
+We now introduce an important lemma which shows convergence in $\mathfrak{p}^{\infty}$ implies that in $\mathfrak{p}^{wv}$.
+\begin{lemma}\label{lem: Countable Implies Vague}
+Assume that 
+\begin{equation}
+\Big(\textbf{X}^{n}_{\mathfrak{u}}(t ),\textbf{U}^{n}_{\mathfrak{u}}(t )\Big)_{t \geq 0} \to \Big(\textbf{X}^{\infty}_{\mathfrak{u}}(t ),\textbf{U}^{\infty}_{\mathfrak{u}}(t )\Big)_{t \geq 0}~~ \text{ in } ~~ \mathcal{D}_{[0,\infty)}\left(\prod_{\mathfrak{u} \in \mathcal{U}}\mathcal{X}_{\mathfrak{u}}\right),
+\end{equation}
+where $\prod_{\mathfrak{u} \in \mathcal{U}}\mathcal{X}_{\mathfrak{u}}$ is equipped with the $\mathfrak{p}^{\infty}$ topology given by the metric $d_{\mathfrak{p}^{\infty}}$.
+Assume furthermore that for all $t \geq 0$, $g \in \mathfrak{G}_{\leq 1}$ and for all $\varepsilon \geq 0$, we may find some finite set $A_g \subset \mathcal{U}$ such that the stopping times $$\rho_{A_g,n}:= \inf\{t \geq 0: U^{n}_{\mathfrak{u}}(t) \leq U_{g} \text{ for all } \mathfrak{u} \in A_g\}$$
+satisfies 
+$$\limsup_{n \to \infty}\mathbb{P}\{ \rho_{A_g,n} \leq t\} \leq \varepsilon /2.$$
+
+Then the sequence of associated empirical measures $(\xi^n(t))_{t \geq 0}:=(\sum_{\mathfrak{u} \in \mathcal{U}}\delta_{X^{n}_{\mathfrak{u}}(t),U^{n}_{\mathfrak{u}}(t)})_{t \geq 0}$ converges to $(\xi^{\infty}(t))_{t \geq 0}:=(\sum_{\mathfrak{u} \in \mathcal{U}}\delta_{X^{\infty}_{\mathfrak{u}}(t),U^{\infty}_{\mathfrak{u}}(t)})_{t \geq 0}$ in $\mathcal{D}_{[0,\infty)}\left(\mathcal{N}_f(\mathbb{R}^d \times [0, \infty)\right)$ where $\mathcal{N}_f(\mathbb{R}^d \times [0, \infty)$ is equipped with the metric $\mathfrak{d}'$.
+\end{lemma}
+\begin{proof}
+By Lemma \ref{lem: Dense set for test functions on empirical measures} and Theorem 3.9.1 in \cite{EK}, it suffices to show that for any $g \in \mathfrak{G}_{\leq 1}$, the real-valued sequence $\left(\prod_{\mathfrak{u} \in \mathcal{U}} g(X^{n}_{\mathfrak{u}}(t), U^{n}_{\mathfrak{u}}(t))\right)_{t \geq 0}$ converges to
+$\left(\prod_{\mathfrak{u} \in \mathcal{U}} g(X^{\infty}_{\mathfrak{u}}(t), U^{\infty}_{\mathfrak{u}}(t))\right)_{t \geq 0}$
+in the $\mathcal{D}_{[0,\infty)}(\mathbb{R})$ topology. To prove so, we must prove convergence in finite-dimensional distribution and tightness.
+
+\textbf{Convergence in finite-dimensional distribution:} 
+It suffices to prove convergence in distribution for one fixed $t$. Let $\mathcal{U}^N:\bigcup_{m=0}^{N}\{0,1\}^m$, and note that the function
+$$\prod_{\mathfrak{u} \in \mathcal{U}^{N}} g(X^{n}_{\mathfrak{u}}(t), U^{n}_{\mathfrak{u}}(t))$$
+is bounded above by $1$ and decrease monotonically with respect to $N$. Furthermore, one can show easily that the set 
+$$\{g(x,u): ~g(x,u)=f(x)h(u), ~~f \in C_0(\mathbb{R}^d), ~ 0\leq f \leq 1 ~ \& ~~ h \in \mathcal{C}_c([0,\infty]), ~ 0\leq h \leq 1\}$$
+is dense in $\mathfrak{G}_{\leq 1}$ under the supremum norm.
+
+As we have that 
+\begin{equation}
+\Big(\textbf{X}^{n}_{\mathfrak{u}}(t ),\textbf{U}^{n}_{\mathfrak{u}}(t )\Big)_{t \geq 0} \to \Big(\textbf{X}^{\infty}_{\mathfrak{u}}(t ),\textbf{U}^{\infty}_{\mathfrak{u}}(t )\Big)_{t \geq 0}~~ \text{ in } ~~ \mathcal{D}_{[0,\infty)}\prod_{\mathfrak{u} \in \mathcal{U}}\mathcal{X}_{\mathfrak{u}},
+\end{equation}
+using the test functions in Lemma \ref{lem: convergence determining test functions} we have that for any finite set $A=\{\mathfrak{u}_1,...,\mathfrak{u}_m\} \subset \mathcal{U}$, 
+\begin{multline}\label{eq: Convergence of finite product in skorokhod space}
+\left(\prod_{i=1}^{m}g\Big(x^{n}_{\mathfrak{u_i}}(t ),u^{n}_{\mathfrak{u_i}}(t )\Big)\right)_{t \geq 0}=\left( F_{g,m}(\textbf{X}^{m}_{\mathfrak{u}}(t ),\textbf{U}^{m}_{\mathfrak{u}}(t ))\right)_{t \geq 0} \\
+\to \left( F_{g,m}(\textbf{X}^{\infty}_{\mathfrak{u}}(t ),\textbf{U}^{\infty}_{\mathfrak{u}}(t )) \right)_{t \geq 0}=  \left(\prod_{i=1}^{m}g\Big(x^{\infty}_{\mathfrak{u_i}}(t ),u^{\infty}_{\mathfrak{u_i}}(t )\Big)\right)_{t \geq 0} \text{  in  } \mathcal{D}_{[0,\infty)}(\mathbb{R}).
+\end{multline}
+
+Therefore, we can apply Monotone Convergence Theorem to obtain for any arbitrary $t >0$,
+\begin{equation}
+\begin{aligned}
+\lim_{n \to \infty}\mathbb{E}^{n}\bigg[\prod_{\mathfrak{u} \in \mathcal{U}} g(X^{n}_{\mathfrak{u}}(t), U^{n}_{\mathfrak{u}}(t))\bigg]=&\lim_{n \to \infty}\lim_{N \to \infty}\mathbb{E}^{n}\bigg[\prod_{\mathfrak{u} \in \mathcal{U}^N} g(X^{n}_{\mathfrak{u}}(t), U^{n}_{\mathfrak{u}}(t))\bigg]\\
+=&\lim_{N \to \infty}\lim_{n \to \infty}\mathbb{E}^{n}\bigg[\prod_{\mathfrak{u} \in \mathcal{U}^N} g(X^{n}_{\mathfrak{u}}(t), U^{n}_{\mathfrak{u}}(t))\bigg]\\
+=&\lim_{N \to \infty}\mathbb{E}^{\infty}\bigg[\prod_{\mathfrak{u} \in \mathcal{U}^N} g(X^{\infty}_{\mathfrak{u}}(t), U^{\infty}_{\mathfrak{u}}(t))\bigg]\\
+=&\mathbb{E}^{\infty}\bigg[\prod_{\mathfrak{u} \in \mathcal{U}} g(X^{\infty}_{\mathfrak{u}}(t), U^{\infty}_{\mathfrak{u}}(t))\bigg],
+\end{aligned}
+\end{equation}
+where the third equality uses Equation \eqref{eq: Convergence of finite product in skorokhod space} alongside a density argument, and the first and last equalities are due to the monotonicity of the product with respect to $N$.
+
+\textbf{Tightness:} By Aldous Criterion, or Lemma 16.12 in \cite{kallenberg2002foundations}, we want to show that for all $t \geq 0$ and arbitrary $g \in \mathfrak{G}_{\leq 1}$,
+\begin{equation}\label{eq: infinite product tightness criteria}
+   \lim_{h \to 0} \limsup_{n \to \infty} \sup_{\sigma, \tau}\mathbb{E} \left\{\left| \prod_{\mathfrak{u} \in \mathcal{U}} g(X^{n}_{\mathfrak{u}}(\sigma), U^{n}_{\mathfrak{u}}(\sigma)) -\prod_{\mathfrak{u} \in \mathcal{U}} g(X^{n}_{\mathfrak{u}}(\tau), U^{n}_{\mathfrak{u}}(\tau)) \right| \wedge 1 \right\} =0,
+\end{equation}
+where the sup extends over all $\mathcal{F}^n$-optional times $\sigma, \tau \leq t$ with $\sigma \leq \tau \leq \sigma +h$.
+
+By Assumption, for any $\varepsilon > 0$, $g \in \mathfrak{G}_{\leq 1}$, we may find some finite set $A_g$ such that the stopping time $$\rho_{A_g,n}:= \inf\{t \geq 0: U^{n}_{\mathfrak{u}}(t) \leq U_{g} \text{ for all } \mathfrak{u} \in A_g\}$$
+satisfies 
+$$\limsup_{n \to \infty}\mathbb{P}\{ \rho_{A_g,n} \leq t\} \leq \varepsilon /2.$$
+As a result, conditioning on $\{ \rho_{A_g} \leq t\}$, we have 
+\begin{multline}
+   \lim_{h \to 0} \limsup_{n \to \infty} \sup_{\sigma, \tau}\mathbb{E} \left\{\left| \prod_{\mathfrak{u} \in \mathcal{U}} g(X^{n}_{\mathfrak{u}}(\sigma), U^{n}_{\mathfrak{u}}(\sigma)) -\prod_{\mathfrak{u} \in \mathcal{U}} g(X^{n}_{\mathfrak{u}}(\tau), U^{n}_{\mathfrak{u}}(\tau)) \right| \wedge 1 \right\} \\
+   =\lim_{h \to 0} \limsup_{n \to \infty} \sup_{\sigma, \tau}\mathbb{E} \left\{\left| \prod_{\mathfrak{u} \in \mathcal{U}} g(X^{n}_{\mathfrak{u}}(\sigma \wedge \rho_{A_g}), U^{n}_{\mathfrak{u}}(\sigma \wedge \rho_{A_g})) -\prod_{\mathfrak{u} \in \mathcal{U}} g(X^{n}_{\mathfrak{u}}(\tau \wedge \rho_{A_g}), U^{n}_{\mathfrak{u}}(\tau \wedge \rho_{A_g})) \right| \wedge 1 : \rho_{A_g} \geq t \right\}\\
+   + \lim_{h \to 0} \limsup_{n \to \infty} \sup_{\sigma, \tau}\mathbb{E} \left\{\left| \prod_{\mathfrak{u} \in \mathcal{U}} g(X^{n}_{\mathfrak{u}}(\sigma ), U^{n}_{\mathfrak{u}}(\sigma )) -\prod_{\mathfrak{u} \in \mathcal{U}} g(X^{n}_{\mathfrak{u}}(\tau ), U^{n}_{\mathfrak{u}}(\tau)) \right| \wedge 1 : \rho_{A_g} \leq t \right\}\\
+   \leq \lim_{h \to 0} \limsup_{n \to \infty} \sup_{\sigma, \tau}\mathbb{E} \left\{\left| \prod_{\mathfrak{u} \in A_g} g(X^{n}_{\mathfrak{u}}(\sigma), U^{n}_{\mathfrak{u}}(\sigma )) -\prod_{\mathfrak{u} \in A_g} g(X^{n}_{\mathfrak{u}}(\tau), U^{n}_{\mathfrak{u}}(\tau)) \right| \wedge 1 : \rho_{A_g} \geq t \right\}\\
+   + \limsup_{n \to \infty} 2 \mathbb{P}\{ \rho_{A_g,n} \leq t\} \leq 0+\varepsilon=\varepsilon. 
+\end{multline}
+The final inequality holds as tightness of our particle system in $\mathfrak{p}^{\infty}$ topology ensures the jump increments over finite product is controlled, and the jump increments are always bounded above by $2$ as the products are at most $1$.
+As $\varepsilon$ is arbitrary, we have shown Equation \eqref{eq: infinite product tightness criteria}.
+\end{proof}
+
+Finally, we will state and prove a generalised version of Theorem A.12 in \cite{kurtz/rodrigues:2011} which serves as a framework to prove convergence of our models to solutions of partial differential equations.
+
+\begin{theorem}\label{teo: Theorem A12 Kurtz Rodrigues generalised}
+Let $\xi^{n}(t)_{t \geq 0}$ be a sequence of cadlag $\mathcal{N}_f(\mathbb{R}^d \times [0, \infty])$-valued processes and define $$\Xi^{n}(t):=\frac{1}{\lambda_n}\xi^{n}(t,dx \times [0,\lambda_n]),$$ which gives a $\mathcal{M}_{f}(\mathbb{R}^d)$-valued process.
+Assume furthermore that for all $t>0$,
+\begin{equation}\label{Markov Mapping Cox Condition}
+\mathbb{E}\left[e^{-\int_{S \times [0,\lambda_n]} f(x,u) \xi^n(t,dx \times du)}\bigg| \mathcal{F}^{\Xi^{n}}_t\right]=e^{-\int F^{n}_f(x) \Xi^{n}_t(dx)},
+\end{equation}
+where 
+$$F^{n}_f(x):=-\lambda_n\log \left(\frac{1}{\lambda_n}\int_{0}^{\lambda_n}e^{-f(x,u)}du\right)=-\lambda_n\log \left(1-\frac{1}{\lambda_n}\int_{0}^{\lambda_n}(1-e^{-f(x,u)})du\right).$$
+In other words, conditioned on $\Xi^n_t$, the levels of individual particles in $\xi^{n}_t$ are identical and uniformly distributed between $[0, \lambda_n]$.
+Finally, assume that as $n \to \infty$, $(\xi^{n}_t)_{t \geq 0}$ converges to $(\xi^{\infty}(t))_{t \geq 0}$ in $\mathcal{D}_{[0,\infty)}\left(\mathcal{N}_f(\mathbb{R}^d \times [0, \infty)\right)$ where $\mathcal{N}_f(\mathbb{R}^d \times [0, \infty)$ is equipped with the metric $\mathfrak{d}'$.
+
+Then $(\Xi^{n}_t)_{t \geq 0}$ converges to $(\Xi^{\infty}_t)_{t \geq 0}$ in $\mathcal{D}_{[0,\infty)}\left(\mathcal{M}_f(\mathbb{R}^d \right)$, where $\mathcal{M}_f(\mathbb{R}^d)$ is equipped with the weak topology.
+In particular, $\Xi^{\infty}(t) \times \Lambda$ is the Cox measure of $\xi^{\infty}(t)$ and, specifically, $\Xi^{\infty}(t):= \lim_{u_0 \to \infty}\frac{1}{u_0}\xi^{\infty}(t,dx\times [0,u_0])$.
+\end{theorem}
+\begin{proof}
+\textbf{Part I (Pointwise Convergence):}
+
+First we prove that for any fixed $t$, $\xi^n_t \to \xi^{\infty}_t$ in $\mathfrak{p}^{wv}$ topology implies convergence of $\Xi^n_t$ to $\Xi^{\infty}_t$ in the weak topology on $\mathcal{M}_f(\mathbb{R}^d)$.
+For all $f(x) \in C_0(\mathbb{R}^d)$, $h(u) \in \mathcal{C}_{c}([0, \infty])$ and $K>0$,
+
+\begin{equation}\label{eq: A12 derivation fixed time}
+\begin{aligned}
+\mathbb{E}\left[e^{-\int_{S \times [0,K]} f(x)h(u) \xi^\infty(t,dx \times du)}\right]=&\lim_{n \to \infty}\mathbb{E}\left[e^{-\int_{S \times [0,K]} f(x)h(u) \xi^n(t,dx \times du)}\right]\\
+=&\lim_{n \to \infty}\mathbb{E}\left[e^{-\int_{S \times [0,\lambda_n]} f(x)h(u) \xi^n(t,dx \times du)}\right]\\
+= & \lim_{n \to \infty}\mathbb{E}\bigg[e^{-\int \left(-\lambda_n\log \left(1-\frac{1}{\lambda_n}\int_{0}^{\lambda_n}(1-e^{-f(x)h(u)})du\right)\right) \Xi^{n}_t(dx)}\bigg].
+\end{aligned}    
+\end{equation}
+
+For fixed $t>0$, $\xi^n_t \to \xi^{\infty}_t$ in the $\mathfrak{p}^{wv}$-topology, so the collection of random variables $$\left\{\int_{S \times [0,K]} f(x)h(u) \xi^n(t,dx \times du): n \in \mathbb{N}\right\}$$ is stochastically bounded and tight.
+Note that
+\begin{equation}
+\begin{aligned}
+G^{\lambda_n}_{K,\varepsilon,f}(x):=&-\lambda_n\log \left(1-\frac{1}{\lambda_n}\int_{0}^{K}(1-e^{-\varepsilon f(x)h(u)})du\right) \\
+ \geq& \int_{0}^{K}(1-e^{-\varepsilon f(x)h(u)})du\\
+ \geq& \int_{0}^{K}\varepsilon e^{-\varepsilon f(x)h(u)}f(x)h(u)du\\
+ \geq &\varepsilon e^{-\varepsilon||fh||_{\infty}}f(x)K||h||_{\infty}.
+\end{aligned}    
+\end{equation}
+
+As a result, we have that
+\begin{equation}\label{eq: Control Xi with xi}
+\begin{aligned}
+\mathbb{E}[1-e^{-\int_{S \times [0,K]} \varepsilon f(x)h(u) d \xi^n}]=&  \mathbb{E}[1-e^{-\int_{S } G^{\lambda_n}_{K,\varepsilon,f} d \Xi^n}]\\
+\geq&\mathbb{E}[1-e^{-\varepsilon e^{-\varepsilon||fh||_{\infty}} K||h||_{\infty}\int_{S } f(x)  \Xi^n(dx)}]\\
+\geq&\left(1-e^{-\varepsilon e^{-\varepsilon||fh||_{\infty}} K||h||_{\infty}C}\right)\mathbb{P}\bigg[\int_{S } f(x)  \Xi^n(dx) > C\bigg].
+\end{aligned}
+\end{equation}
+
+Taking $\varepsilon=C^{-1}$ gives that for any arbitrary $h \in C_{c}([0, \infty])$, for all $f \in C_0(\mathbb{R}^d)$ and for any $K>0$,
+
+$$\mathbb{P}\bigg[\int_{S } f(x)  \Xi^n(dx) > C\bigg] \leq \frac{\mathbb{E}[1-e^{-\int_{S \times [0,K]} C^{-1}f(x)h(u) d \xi^n}]}{1-e^{-e^{-C^{-1} ||fh||_{\infty}} K||h||_{\infty}}}.$$
+
+Furthermore, if we pick $h(u)$ such that $h(x)=1$ on $[0,K]$ and decreases to $0$ outside $K$ in some finite region, we have that gives 
+\begin{equation}\label{eq: Markov inequality for Xi}
+\mathbb{P}\bigg[\int_{S } f(x)  \Xi^n(dx) > C\bigg] \leq \frac{\mathbb{E}[1-e^{-\int_{S \times [0,K]} C^{-1}f(x) d \xi^n}]}{1-e^{-e^{-C^{-1} ||f||_{\infty}} K}} 
+\end{equation}
+for arbitrary $K>0$. A similar argument gives us 
+\begin{equation}\label{eq: Markov inequality for Xi, infinity case}
+\mathbb{P}\bigg[\int_{S } f(x)  \Xi^\infty(dx) > C\bigg] \leq \frac{\mathbb{E}[1-e^{-\int_{S \times [0,K]} C^{-1}f(x) d \xi^\infty}]}{1-e^{-e^{-C^{-1} ||f||_{\infty}} K}} 
+\end{equation}
+for arbitrary $K>0$.
+
+As a result of the above inequalities, stochastic boundedness of integrals against $\xi^n$ implies stochastic boundedness (and similarly tightness) of the random variables  
+$$\left\{\int_{S \times [0,K]} f(x) \Xi^n(t,dx): n \in \mathbb{N}\right\}$$
+in the weak topology. As a result, $\Xi^{n}$ converges to some $\Xi^{\infty}$ weakly.
+
+Finally, note that for large enough $\lambda_n$, 
+\begin{equation}
+\begin{aligned}
+\exp\bigg(-\lambda_n\log \left(1-\frac{1}{\lambda_n}\int_{0}^{\lambda_n}(1-e^{-f(x)h(u)})du\right)\bigg)=&  \left(1-\frac{1}{\lambda_n}\int_{0}^{\infty}(1-e^{-f(x)h(u)})du\right)^{-\lambda_n} \\
+\to& \exp\bigg(\int_{0}^{\infty}(1-e^{-f(x)h(u)})du\bigg)
+\end{aligned}    
+\end{equation}
+uniformly (in space) as $n \to \infty$, so the last equality of Equation \eqref{eq: A12 derivation fixed time} gives for any fixed time $t >0 $,
+\begin{equation}\label{eq: A12 derivation fixed time conclusion}
+\begin{aligned}
+\mathbb{E}\left[e^{-\int_{S \times [0,K]} f(x)h(u) \xi^\infty(t,dx \times du)}\right]
+= & \lim_{n \to \infty}\mathbb{E}\bigg[e^{-\int \left(-\lambda_n\log \left(1-\frac{1}{\lambda_n}\int_{0}^{\lambda_n}(1-e^{-f(x)h(u)})du\right)\right) \Xi^{n}_t(dx)}\bigg]\\
+= & \mathbb{E}\bigg[e^{-\int \left(\int_{0}^{\infty}(1-e^{-f(x)h(u)})du\right) \Xi^{\infty}_t(dx)}\bigg],
+\end{aligned}    
+\end{equation}
+which characterises $\xi^{\infty}_t$ as a conditionally Poisson point process with Cox measure $\Xi^{\infty}_t \times \Lambda$.
+
+\textbf{Part II (Finite-dimensional Convergence):}
+
+The finite-dimensional distribution of $(\xi^n(t))_{t \geq 0}$ converges, so for any k-tuples $(t_1,...,t_k) \in (\mathbb{R}^{+})^{k}$, $f(x) \in C_0(\mathbb{R}^d)$, $h(u) \in \mathcal{C}_{c}([0, \infty])$ and $K >0$,
+\begin{equation}\label{eq: A12 derivation finite dimensional, xi}
+\begin{aligned}
+\mathbb{E}\left[\prod_{i=1}^{k}\int_{S \times [0,K]} f(x)h(u) \xi^\infty(t_i,dx \times du)\right]=&\lim_{n \to \infty}\mathbb{E}\left[\prod_{i=1}^{k}\int_{S \times [0,K]} f(x)h(u) \xi^n(t_i,dx \times du)\right].
+\end{aligned}    
+\end{equation}
+We aim to prove the convergence of finite-dimensional distribution of $\Xi^{n}(t)$, i.e. 
+\begin{equation}\label{eq: A12 derivation finite dimensional, Xi}
+\begin{aligned}
+\mathbb{E}\left[\prod_{i=1}^{k}\int_{S} f(x) \Xi^\infty(t_i,dx)\right]=&\lim_{n \to \infty}\mathbb{E}\left[\prod_{i=1}^{k}\int_{S} f(x) \Xi^n(t_i,dx)\right].
+\end{aligned}    
+\end{equation}
+First of all, note that 
+$$\mathbb{E}\left[\int_{S \times [0,K]} f(x)h(u) \xi^\infty(t_i,dx \times du)\right]=\mathbb{E}\left[\int_{S}f(x)\Xi^\infty(t_i,dx)\int_{[0,K]}h(u)du\right].$$
+For convenience we will denote $I_{K}(h):=\int_{[0,K]}h(u)du$.
+
+We use Chebyschev's inequality to obtain
+\begin{multline}
+\mathbb{P}\left[\bigg|\frac{1}{I_K(h)}\int_{S \times [0,K]} f(x)h(u) \xi^\infty(t_i,dx \times du)-\int_{S} f(x)  \Xi^\infty(t_i,dx)\bigg|>\delta \Bigg| \Xi^{\infty}\right] \\
+\leq \frac{Var\left[\int_{S \times [0,K]} f(x)h(u) \xi^\infty(t_i,dx \times du)\right]}{I_K(h)^2\delta^2}\wedge 1   \\
+\leq \frac{\int_{S} f^2(x) \Xi^\infty(t_i,dx) \int_{[0,K]} h^2(u) du}{I_K(h)^2\delta^2}\wedge 1   \\
+\leq \frac{CI_K(h^2)}{I_K(h)^2\delta^2} + \mathbbm{1}_{\{\int_{S}f^2(x)\Xi^{\infty}(t_i,dx) > C\}},
+\end{multline}
+Taking expectations (with respect to the law of $\Xi^{\infty}$) gives for any $\delta>0$, $C>0$, $K,K'>0$,
+\begin{multline}\label{eq: Chebyschev inequality for Xi infinity}
+\mathbb{P}\left[\bigg|\frac{1}{I_K(h)}\int_{S \times [0,K]} f(x)h(u) \xi^\infty(t_i,dx \times du)-\int_{S} f(x)  \Xi^\infty(t_i,dx)\bigg|>\delta \right]\\
+\leq  \frac{CI_K(h^2)}{I_K(h)^2\delta^2} + \mathbb{P}\{\int_{S}f^2(x)\Xi^{\infty}(t_i,dx) > C\}\\
+ \leq \frac{CI_K(h^2)}{I_K(h)^2\delta^2} +\frac{\mathbb{E}[1-e^{-C^{-1}\int_{S \times [0,K']} f^2(x) d \xi^\infty(t_i,dx \times du)}]}{1-e^{-e^{-C^{-1} ||f^2||_{\infty}} K'}} ,
+\end{multline}
+where the last equality uses Equation \eqref{eq: Markov inequality for Xi}.
+
+Since $h$ is continuous, bounded with compact support, we can apply Cauchy Inequality to bound $\frac{I_K(h^2)}{I_K(h)^2}$.
+By picking $C$ to be sufficiently large, the second term term on the right hand side of Equality \eqref{eq: Chebyschev inequality for Xi infinity} can be arbitrarily small.
+This is because the integral in the exponent given fixed $K'$ is finite.
+To control the first term, we pick $K >> \frac{C}{\delta^2}$, and pick $h$ such that $h(x)=1$ for all $x \in [0,K]$ and decreases to $0$ in finite region.
+Then $\frac{I_K(h^2)}{I_K(h)^2}=\frac{1}{K}$ which will make the first term arbitrarily small.
+
+Similarly, for $K< \lambda_n$,
+\begin{align*}
+\mathbb{E}\left[\int_{S \times [0,K]} f(x)h(u) \xi^n(t_i,dx \times du)\right]=&\mathbb{E}\left[\frac{1}{\lambda_n}\int_{[0,K]}h(u)du\int_{S}f(x)\xi^n(t_i,dx\times [0, \lambda_n])\right]\\
+=&\mathbb{E}\left[I_K(h)\int_{S}f(x)\Xi^n(t_i,dx)\right],
+\end{align*}
+and 
+$$Var\left[\int_{S \times [0,K]} f(x)h(u) \xi^\infty(t_i,dx \times du)\right]=\left\{\lambda_n^{-1}I_k(h^2)-\lambda_n^{-2}I_K(h)^2\right\} \int_{S} f^2(x) \Xi^\infty(t_i,dx),$$
+so we have that
+\begin{multline}\label{eq: Controlling Xi minus xi}
+\mathbb{P}\left[\bigg|\frac{1}{I_K(h)}\int_{S \times [0,K]} f(x)h(u) \xi^n(t_i,dx \times du)-\int_{S} f(x)  \Xi^n(t_i,dx)\bigg|>\delta \right]\\
+ \leq \frac{C\left\{\lambda_n^{-1}I_K(h^2)-\lambda_n^{-2}I_K(h)^2\right\}}{I_K(h)^2\delta^2} +\frac{\mathbb{E}[1-e^{-C^{-1}\int_{S \times [0,K']} f^2(x) d \xi^n}]}{1-e^{-K'e^{-C^{-1} ||f^2||_{\infty}} }} .
+\end{multline}
+ As $n \to \infty$, $\lambda_n \to \infty$.
+Convergence in finite-dimension of $\xi^n$ also gives stochastic boundedness of integrals against $d\xi^n$ uniformly across $n$.
+The same argument for controlling $\xi^\infty$ therefore applies.
+
+Finally, since we are evaluating the expectation over a finite product, convergence in probability for the stochastic integrals at each time $t_i$ gives convergence in finite-dimensional distributions.
+
+\textbf{Part III (Tightness):}
+
+To prove tightness in $\mathcal{M}_{F}(\mathbb{R}^d)$, we aim to prove that for all $f \in C_{0}(\mathbb{R}^d)$, and $t >0$,
+\begin{equation}\label{eq: Empirical Measure Tightness Criteria}
+   \lim_{s \to 0} \limsup_{n \to \infty} \sup_{\sigma, \tau}\mathbb{E} \left\{\left|\int_{S } f(x) \Xi^n(\sigma,dx) - \int_{S} f(x) \Xi^n(\tau,dx)\right| \wedge 1 \right\} =0.
+\end{equation}
+where the sup extends over all $\mathcal{F}^n$-optional times $\sigma, \tau \leq t$ with $\sigma \leq \tau \leq \sigma +s$.
+
+With triangle inequality, we have that 
+\begin{multline}\label{eq: Triangle inequality on integral against mean measure}
+\left|\int_{S } f(x) \Xi^n(\sigma,dx) - \int_{S} f(x) \Xi^n(\tau,dx)\right|  \\
+\leq \left|\int_{S } f(x) \Xi^n(\sigma,dx) -\frac{1}{I_K(h)}\int_{S \times [0,K]} f(x)h(u) \xi^n(\sigma,dx \times du)\right|\\
++ \left|\int_{S }\frac{1}{I_K(h)}\int_{S \times [0,K]} f(x)h(u) \xi^n(\tau,dx \times du) - \int_{S} f(x) \Xi^n(\tau,dx)\right|\\
++\left|\frac{1}{I_K(h)}\int_{S \times [0,K]} f(x)h(u) \xi^n(\sigma,dx \times du) - \frac{1}{I_K(h)}\int_{S \times [0,K]} f(x)h(u) \xi^n(\tau,dx \times du)\right|.
+\end{multline}
+By concavity of the function $x \to 1-\exp(-C^{-1}x)$, we have that 
+\begin{multline}
+   \lim_{s \to 0} \limsup_{n \to \infty} \sup_{\sigma \leq t}\mathbb{E} \left\{ 1-e^{- C^{-1}\int_{S \times [0,K']} f^2(x) d \xi^n(\sigma,dx \times du)} \right\}\\
+   \leq 
+   \lim_{s \to 0} \limsup_{n \to \infty} \sup_{\sigma \leq t} 1-e^{- C^{-1}\mathbb{E} \left\{\int_{S \times [0,K']} f^2(x) d \xi^n(\sigma,dx \times du) \right\} }.
+\end{multline}
+As the sequence of processes $\xi^n$ converges, the expectation on the right hand side can be uniformly bounded across all $\sigma < t$ and $n \in \mathbb{N}$, and so by taking large $C$ and $K>>C$ in Equation \eqref{eq: Controlling Xi minus xi}, the first two terms in Equation \eqref{eq: Triangle inequality on integral against mean measure} can be arbitrarily small.
+
+Finally, as $\xi^n$ converges in the Skorokhod topology, for any $f \in C_{0}(\mathbb{R}^d), h \in C_{c}([0,\infty)$, the sequence of real-valued stochastic processes 
+$$\left\{\left(\int_{S \times [0,K]} f(x)h(u) \xi^n(t,dx \times du)\right)_{t \geq 0} : n \in \mathbb{N}\right\}$$
+is tight. Therefore, we have that  
+\begin{multline}
+     \lim_{s \to 0} \limsup_{n \to \infty} \sup_{\sigma, \tau}\mathbb{E} \left\{\left|\int_{S \times [0,K]} f(x)h(u) \xi^n(\sigma,dx \times du) - \int_{S \times [0,K]} f(x)h(u) \xi^n(\tau,dx \times du)\right|   \right\}=0,
+\end{multline}
+where the sup extends over all $\mathcal{F}^n$-optional times $\sigma, \tau \leq t$ with $\sigma \leq \tau \leq \sigma +s$.
+Combining these inequalities we have proven Equation \eqref{eq: Empirical Measure Tightness Criteria}.
+
+To conclude, we have shown tightness of our processes  
+$$\left\{\left(\int_{S \times [0,K]} f(x) \Xi^n(t,dx)\right)_{t \geq 0}: n \in \mathbb{N}\right\}$$
+for all $f \in C_{0}(\mathbb{R}^d)$ as well as finite-dimensional convergence of our processes to $\left(\int_{S \times [0,K]} f(x) \Xi^\infty(t,dx)\right)_{t \geq 0}$.
+Thus we have proved convergence of $(\Xi^{n}_t)_{t \geq 0}$ to $(\Xi^{\infty}_t)_{t \geq 0}$ in $\mathcal{D}_{[0,\infty)}\left(\mathcal{M}_f(\mathbb{R}^d \right)$, where $\mathcal{M}_f(\mathbb{R}^d)$ is equipped with the weak topology, and its distribution is characterised through Equation \eqref{eq: A12 derivation fixed time conclusion}.
+\end{proof}
 
 \bibliographystyle{plainnat}
-\bibliography{refs.bib}
+\bibliography{refs.bib,plr_refs.bib}
 

### 2022-05-26 forwards-and-backwards.tex
Update on Overleaf.

@@
 regime, denoted as
-$\tau^{N}_a$,
-is identical in distribution
-for all $N > 0$.
+$\tau^{N}_a$ converges to $0$
+as $N \to \infty$.
 This is because the birth time
@@
 in the 2nd generation, etc..
-Therefore $\tau^N_{a} \sim Gamma(\sum_{i=1}^{k}a_i,1)$.
+Furthermore,
+these birth times are
+independent of the environment. Finally,
+we rescale time by a factor of $\theta$,
+so $\tau^N_{a} \sim Gamma(\theta\sum_{i=1}^{k}a_i,1) \to 0$.
 
@@
 \sum_{j=1}^{a_i-1}
-(1-\kappa_{[a]_{i-1}\concat j}) y_{[a]_{i-1}\concat j} \ind_{U^N_{[a]_{i-1}\concat j}(\tau_{[a]_{i-1}\concat j}) < N}\\
+\ind_{\kappa_{[a]_{i-1}\concat j}=0}  \ind_{U^N_{[a]_{i-1}\concat j}(\tau_{[a]_{i-1}\concat j}) < N}y_{[a]_{i-1}\concat j}\\
 &+ \sum_{i=1}^{k}
-\kappa_{[a]_i} y_{[a]_i} \ind_{U^N_{[a]_i}(\tau_{[a]_i}) < N}.
+\ind_{\kappa_{[a]_{i-1}\concat j}=1} \ind_{U^N_{[a]_i}(\tau_{[a]_i}) < N}y_{[a]_i} .
 \end{aligned}    
@@
 for each $i$ and $j$,
-and that the sum above is finite,
-it suffices to show that
-the quantities 
-\begin{equation}
-\mathbb{P}(U^N_{[a]_{i-1} \concat j}(\tau_{[a]_{i-1} \concat j}) < N)    
-\end{equation}
-converges
-for all $i=1,..,k$ and $j=1,..,a_i$.
-
-Writing out
-$U^N_{[a]_{i-1} \concat j}(\tau_{[a]_{i-1} \concat j})$,
-we have
+we can give a simple bound
+on $\mathbb{E}[(X^{N}_{[a]_{k}}(\tau^N_{a})- X^{N}_{[a]_{0}}(0))^2]$.
+
+First of all, 
+note that the total number
+of jumps
+the ancestral lineage 
+has until time $\tau_{a}$
+is at most $\sum_{i=1}^{k}a_i$.
+Furthermore, each jump is independent and has mean $\meanq(x)/\theta$ and covariance matrix $\covq(x)/\theta$
+that is bounded uniformly across
+the environment.
+
+As a result, as $N \to \infty$,
 \begin{equation}
 \begin{aligned}
-&\mathbb{P}(U^N_{[a]_{i-1} \concat j}(\tau_{[a]_{i-1} \concat j}) < N) \\
-=&\mathbb{P}(U^N_{[a]_{i-1} }(\tau_{[a]_{i-1} \concat j})
-    +
-    \ell(
-    X^N_{[a]_{i-1} }(\tau_{[a]_{i-1} \concat j}-),
-    y_{[a]_{i-1} \concat j},
-    \eta^{N}(\tau_{[a]_{i-1} \concat j}-),
-    v_{[a]_{i-1} \concat j})
-    < N)\\
-=&\mathbb{P}\left(
-    \frac{
-        v_{[a]_{i-1} \concat j}
-    }{
-        2 N^{-1} \theta \gamma(x, \eta) r(x + y, \eta)
-    }
-    < N-U^N_{[a]_{i-1} }(\tau_{[a]_{i-1} \concat j})
-    \right)\\
-=&\mathbb{P}\left(
-            v^N_{[a]_{i-1} \concat j}
-    < (2 \theta \gamma(x, \eta) r(x + y, \eta)-  2 N^{-1} \theta \gamma(x, \eta) r(x + y, \eta)U^N_{[a]_{i-1} }(\tau_{[a]_{i-1} \concat j}))
-    \right)\\
-=& \frac{(2 \theta \gamma(x, \eta) r(x + y, \eta)-  2 N^{-1} \theta \gamma(x, \eta) r(x + y, \eta)U^N_{[a]_{i-1} }(\tau_{[a]_{i-1} \concat j}))}{N}\\
-\to & 2\alpha \gamma(x, \eta) r(x + y, \eta).
+&\quad\mathbb{E}[(X^{N}_{[a]_{k}}(\tau^N_{a})- X^{N}_{[a]_{0}}(0))^2]\\
+\leq & \quad\mathbb{E}\left[\left(\sum_{i=1}^{k}
+\sum_{j=1}^{a_i-1} y_{[a]_{i-1}\concat j}+ \sum_{i=1}^{k}
+y_{[a]_i}\right)^2\right]\\
+\leq & \quad\mathbb{E}\left[\left(\sum_{i=1}^{k}
+\sum_{j=1}^{a_i} y_{[a]_{i-1}\concat j}\right)^2\right]\\
+=& \quad{ka_k \choose 2}\sup_{x \in \mathbb{R}^d}(||\meanq(x)||^2)/\theta^2 + ka_k \left(\sup_{x \in \mathbb{R}^d}(||\meanq(x)||^2)/\theta^2+\sup_{x \in \mathbb{R}^d}|tr(\covq(x) )|\right)\\
+ \to &  \quad 0.
 \end{aligned}    
 \end{equation}
+
+This is expected
+as in the infinitesimal limit,
+births are instantaneous. 
+Therefore, all offspring 
+within small number of generations
+($k << \theta$)
+from the original
+ancestors are born
+almost instantaneously
+at the position of its
+ancestor.
 

### 2022-06-09 OneStepConvergence.tex
Update on Overleaf.

@@
 \begin{document}
-
 These notes are an attempt of writing the one-step convergence of the particle system to a PDE limit.
@@
 [M(\phi)]_t&:=\frac{\theta}{N}\int_{0}^{t}\bigg\{ \left\langle \int_{\mathbb{R}^d} \phi^2(y) q_\theta(x,dy), \overline{\eta}_s^{\varepsilon, \theta, N}(dx) \right\rangle \nonumber\\
-&+ \left\langle  \left(2 + \frac{F(\langle \rho_\epsilon(y-x), \overline{\eta}_s(dy)\rangle )}{\theta } \right)\phi^2(x), \overline{\eta}_s^{\varepsilon, \theta, N}(dx))\right\rangle   \bigg\}ds.
+&+ \left\langle  \left(1 + \frac{F(\langle \rho_\epsilon(y-x), \overline{\eta}_s(dy)\rangle )}{\theta } \right)\phi^2(x), \overline{\eta}_s^{\varepsilon, \theta, N}(dx))\right\rangle   \bigg\}ds.
 \label{mgp2}
@@
  \todo[inline]{Question: Why do we need that regularity on $u_0$?
-I believe all we need is that (\ref{aprox3}) holds, and for that I am almost sure that $u_0$ only need to satisfy the first three hypothesis for $\overline{\eta}_0(x)$.
+I believe all we need is that (\ref{aprox3}) holds, and for that, I am almost sure that $u_0$ only needs to satisfy the first three hypotheses for $\overline{\eta}_0(x)$.
 Furthermore,  if I am not mistaken, those are all implied by $u_0(x) \in L^1(\mathbb{R}^d) \cap L^2(\mathbb{R}^d) \cap \mathcal{C}^1(\mathbb{R}^d)$ in case we want a nice space to put on the result.}
+\todo[inline]{Questions 2: The conditions on $F$ implies that $F(x)1_{x>0} = (A-Bx)1_{x>0}$ for some $A,B>0$, or not?
+At least that is the only polynomial that is bounded above with a bounded derivative.
+Maybe we could rewrite the result for that explicit $F$?}
 
@@
 \begin{align} \label{eq:QVTotalMass}
-[M]_t = \frac{\theta}{N}\int_0^t \langle 2 + \frac{F(\rho_\epsilon* \overline{\eta}_s)}{\theta}, \overline{\eta}_s \rangle d s 
+[M]_t = \frac{\theta}{N}\int_0^t \langle 1 + \frac{F(\rho_\epsilon* \overline{\eta}_s)}{\theta}, \overline{\eta}_s \rangle d s 
 \end{align}
 By taking expectations in (\ref{eq:MPTotalMass}) we get,
-\[ \EE[\langle 1, \overline{\eta}_t \rangle] =  \EE[\langle 1, \overline{\eta}_0 \rangle]  + \int_0^t \langle F(\rho * \overline{\eta}_s), \overline{\eta}_s \rangle ds ]   \leq C +   C \mathbb{E}\left[ \int_0^t \langle 1, \overline{\eta}_s \rangle ds \right].\]
+\[ \EE[\langle 1, \overline{\eta}_t \rangle] =  \EE[\langle 1, \overline{\eta}_0 \rangle]  + \EE[ \int_0^t \langle F(\rho * \overline{\eta}_s), \overline{\eta}_s \rangle ds ]   \leq C +   C \mathbb{E}\left[ \int_0^t \langle 1, \overline{\eta}_s \rangle ds \right].\]
 In last inequality we used that $F(x)1_{x >0}$ and $\langle 1, \overline{\eta}_0 \rangle$ are uniformly bounded above.
@@
 Hence, by taking expectations in (\ref{eq:QVTotalMass}) and using again the bound on $F(x)1_{x>0}$ we get,
-\[ \EE\left[ [M]_t \right] \leq \frac{\theta}{N} C \int_0^t \mathbb{E}\left[ \langle 1, \overline{\eta}_s \rangle ds \right] \leq \frac{\theta}{N}C t \]
+\begin{equation} \EE\left[ [M]_t \right] \leq \frac{\theta}{N} C \int_0^t \mathbb{E}\left[ \langle 1, \overline{\eta}_s \rangle ds \right] \leq \frac{\theta}{N}C t \label{eq:quadvarMass} \end{equation}
 Note that, with this, $\EE[ [M]_t]$ is bounded (and in fact $\mathcal{O}(\theta/N)$). By the Burkholder-Davis-Gundy inequality and then's Jensen inequality we get
@@
 Taking supremum and then expectation in (\ref{eq:MPTotalMass}) and using the last inequality gives the result.
+\end{proof}
+We will require also a second moment bound on the total mass.
+
+\begin{proposition}
+Under the assumptions of Theorem~\ref{TeoremOneStepConvergence} there is a finite constant $C$ (independent of $\epsilon, N, \theta$) such that, for all $t \in [0,T]$ and for big enough $N$ and $\theta$, $\EE[ \langle 1, \overline{\eta}_t \rangle^2] \leq C$.\label{Prop:SecondMomentMass}
+\end{proposition} 
+\begin{proof}
+By using in (\ref{eq:MPTotalMass}) that, by assumption, $\langle 1, \overline{\eta}_0 \rangle$  and $F(x)1_{x > 0}$ are bounded above we get,
+\begin{align*}
+ \langle 1, \overline{\eta}_t \rangle^2 \leq C \langle 1, \overline{\eta}_t \rangle + C\langle 1,\overline{\eta}_t \rangle \int_0^t \langle 1, \overline{\eta}_s\rangle ds + M_t \langle 1, \overline{\eta}_t \rangle \end{align*}
+Taking expectation we obtain,
+\begin{align*}
+\EE[ \langle 1, \overline{\eta}_t \rangle^2 ] & \leq C \EE[\langle 1, \overline{\eta}_t \rangle] + C\EE[  \langle 1,\overline{\eta}_t \rangle \int_0^t \langle 1, \overline{\eta}_s\rangle ds ] + \EE[ M_t \langle 1, \overline{\eta}_t \rangle] \\ & \leq C + C\EE[\frac{1}{2} \langle 1, \overline{\eta}_t\rangle^2] + \frac{1}{2} \EE[t \int_0^t \langle 1, \overline{\eta}_s \rangle^2 ds ] + (\EE[M_t^2] \EE[\langle 1, \overline{\eta}_t \rangle^2])^{1/2}
+\end{align*}
+where in the second inequality we have used Lemma~\ref{Lemma:UniformlyBoundedMass} on the first term, that $2ab \leq a^2 + b^2$ and Jensen's inequality in the second term and Holder's inequality in the third term.
+Note that by the Burkholder-Davis-Gundy inequality and (\ref{eq:quadvarMass}) we have that,
+\[ \EE[ M_t^2 ] = \mathcal{O}\left( \frac{\theta}{N} \right). \]
+Hence, by using that for positive $a$ we have $a^{1/2} \leq a+1$ we can deduce that,
+\begin{align*}
+\frac{1}{2} \EE[ \langle 1, \overline{\eta}_t \rangle^2 ] \leq C + \frac{1}{2} \EE[t \int_0^t \langle 1, \overline{\eta}_s \rangle^2 ds ] + \mathcal{O}\left( \left(\frac{\theta}{N}\right)^{1/2} \right) +\mathcal{O}\left( \left(\frac{\theta}{N}\right)^{1/2} \right) \EE[\langle 1, \overline{\eta}_t \rangle^2].
+\end{align*}
+Let $\theta$ and $N$ big enough so $\theta/N < 1/16$. From the last equation we then can deduce,
+\[ \frac{1}{4}\EE[ \langle 1, \overline{\eta}_t \rangle^2 ] \leq C + \frac{C}{2} t \int_0^t\EE[\langle 1, \overline{\eta}_s \rangle^2 ] ds\]
+An application of Grownwall's inequality yields
+\[ \EE[ \langle 1, \overline{\eta}_t \rangle^2 ] \leq C \exp(2 C t^2) \leq C \exp(2 C T^2),  \]
+finishing the proof.
 \end{proof}
@@
 \begin{proof}
-The first claim of this result follows immediately from $\mathcal{L}^\theta$ being the generator of a continuous random walk, where jumps with mean $0$ and variance $1/\theta$ arrive at rate $\theta$.
+The first claim of this result follows immediately from $\mathcal{L}^\theta$ being the generator of a continuous random walk, where Gaussian jumps with mean $0$ and variance $1/\theta$ arrive at rate $\theta$.
 
@@
 \begin{lemma}
-For every $x \in \mathbb{R}^d$ and $t>0$ we have,
+For every $x,y \in \mathbb{R}^d$ and $t>0$ we have,
 \begin{align*}
-|\psi_t^{\epsilon,x} - p_{\epsilon^2+t}(x,y)| &\leq \frac{C}{\epsilon^2 \theta}\left(\psi_t^{\epsilon,x}(y) + p_{\epsilon^2+t}(x,y) + p_{3/2(\epsilon^2+t)}(x,y)+p_{3(\epsilon^2+t)}(x,y) \right)
+|\psi_t^{\epsilon,x}(y) - p_{\epsilon^2+t}(x,y)| &\leq \frac{C}{\epsilon^2 \theta}\left(\psi_t^{\epsilon,x}(y) + p_{\epsilon^2+t}(x,y) + p_{3/2(\epsilon^2+t)}(x,y)+p_{3(\epsilon^2+t)}(x,y) \right)
 \end{align*} \label{Lemma:BoundPsiHS2}
@@
 with $M_t(\phi_\cdot(\cdot))$ a martingale with having quadratic variation:
-\[ [M(\phi_\cdot(\cdot))]_t = \frac{\theta}{N}\int_0^t \langle \int_{\mathbb{R}^d} \phi_s(z)^2 q_\theta(y,dz) + \left( 2 + \frac{F(\rho_\epsilon*\overline{\eta}_s(y))}{\theta}\right) \phi_s(y)^2, \overline{\eta}_s(dy) \rangle ds \]
+\[ [M(\phi_\cdot(\cdot))]_t = \frac{\theta}{N}\int_0^t \langle \int_{\mathbb{R}^d} \phi_s(z)^2 q_\theta(y,dz) + \left( 1 + \frac{F(\rho_\epsilon*\overline{\eta}_s(y))}{\theta}\right) \phi_s(y)^2, \overline{\eta}_s(dy) \rangle ds \]
 \section{Tightness}
 
-\subsection{Uniform bound for $\{ \rho_\epsilon * \overline{\eta}_s (x)\}_{0 \leq s \leq T}$ for fixed $T$}
+\subsection{Bounds for $\{ \rho_\epsilon * \overline{\eta}_s (x)\}_{0 \leq s \leq T}$}
 \begin{lemma} \label{FirstBoundLocalDensity}
@@
 \begin{align}
-(\rho_\epsilon*\overline{\eta}_t(x)) = \langle \psi_t^{\epsilon,x}(y), \overline{\eta}_0(dy) \rangle  + \int_0^t \langle \psi_{t-s}^{\epsilon,x}(y) F(\rho_\epsilon*\overline{\eta}_s(y)), \overline{\eta}_s(dy) \rangle ds + M_t \label{MartingaleProblemMolifier}
+(\rho_\epsilon*\overline{\eta}_t(x)) = \langle \psi_t^{\epsilon,x}(y), \overline{\eta}_0(dy) \rangle  + \int_0^t \langle \psi_{t-s}^{\epsilon,x}(y) F(\rho_\epsilon*\overline{\eta}_s(y)), \overline{\eta}_s(dy) \rangle ds + M_t(x) \label{MartingaleProblemMolifier}
 \end{align}
@@
 \begin{corollary}
-Let $(M_t)_{t \geq 0}$ be the martingale in (\ref{MartingaleProblemMolifier}). Then
-\[ \EE\left[ [M]_t \right] \leq \frac{C \theta}{ N \epsilon^{d}} \]
+Let $(M_t(x))_{t \geq 0}$ be the martingale in (\ref{MartingaleProblemMolifier}). Then
+\[ \EE\left[ [M(x)]_t \right] \leq \frac{C \theta}{ N \epsilon^{d}} \]
 where $C$ is independent of $\epsilon,\theta,N$. \label{Cor:ControlQVMQ}
@@
 Indeed, note we can explicitly write the quadratic variation of $M_t$ by,
-\[ [M]_t = \frac{\theta}{N} \int_0^t \langle \int_{\mathbb{R}^d} \psi_{t-s}^{\epsilon,x}(z)^2 q_\theta(y,dz) + \left(2+\frac{F(\rho_\epsilon * \overline{\eta}_s(y))}{\theta}\right)\psi_{t-s}^{\epsilon,x}(y)^2, \overline{\eta}_s(dy) \rangle  ds\]
+\[ [M(x)]_t = \frac{\theta}{N} \int_0^t \langle \int_{\mathbb{R}^d} \psi_{t-s}^{\epsilon,x}(z)^2 q_\theta(y,dz) + \left(1+\frac{F(\rho_\epsilon * \overline{\eta}_s(y))}{\theta}\right)\psi_{t-s}^{\epsilon,x}(y)^2, \overline{\eta}_s(dy) \rangle  ds\]
 using Lemma~\ref{PsiBoundHS} we can get the following bound,
@@
 Hence, by using the last inequality the upper bound on $F(x)1_{x}$ we deduce that:
-\begin{align*}
-[M]_t &\leq \frac{C \theta}{\epsilon^d N} \int_0^t \left\{  \langle \int \psi_{t-s}^{\epsilon,x}(z) q_\theta(y,dz), \overline{\eta}_s(dy) \rangle + \langle \psi_{t-s}^{\epsilon,x}(y), \overline{\eta}_s(dy)\rangle \right\} ds
-\end{align*}
+\begin{align}
+[M(x)]_t &\leq \frac{C \theta}{\epsilon^d N} \int_0^t \left\{  \langle \int \psi_{t-s}^{\epsilon,x}(z) q_\theta(y,dz), \overline{\eta}_s(dy) \rangle + \langle \psi_{t-s}^{\epsilon,x}(y), \overline{\eta}_s(dy)\rangle \right\} ds
+\label{QuadVarBound} \end{align}
 Taking expectations and using the bound of Lemma~\ref{FirstBoundLocalDensity} we get the result.
@@
 
+By reusing the computations in the last Corollary we can prove a certain integrability of $M_t(x)$.
+\begin{proposition}
+Let $(M_t(x))_{t \geq 0}$ be the martingale in (\ref{MartingaleProblemMolifier}). Then
+\[ \int \EE\left[ M_t(x)^2 \right] dx \leq \frac{C \theta}{ N \epsilon^{d}} \]
+where $C$ is independent of $\epsilon,\theta,N$. \label{IntegrabilityOfM}
+\end{proposition}
+\begin{proof}
+Recall that since $M_t(x)$ is a martingale, then,
+\[ \EE\left[ M_t(x)^2 \right] = \EE\left[ [M(x)]_t \right].  \]
+Hence, using (\ref{QuadVarBound}),
+\begin{align*}
+\int &\EE\left[ M_t(x)^2 \right] dx \\ & \leq \frac{C \theta}{\varepsilon^d N} \int \int_0^t \EE\left[ \langle \int \psi_{t-s}^{\epsilon,x}(z) q_\theta(y,dz), \overline{\eta}_s(dy) \rangle + \langle \psi_{t-s}^{\epsilon,x}(y), \overline{\eta}_s(dy)\rangle \right] ds  dx \\ &=  \frac{C \theta}{\varepsilon^d N}  \int_0^t \EE \left[  \langle \int \left( \int \psi_{t-s}^{\epsilon,x}(z) dx \right) q_\theta(y,dz), \overline{\eta}_s(dy) \rangle + \langle \left( \int  \psi_{t-s}^{\epsilon,x}(y) dx \right), \overline{\eta}_s(dy)\rangle \right] ds.
+\end{align*}
+Now using Lemma~\ref{PsiBoundHS} we have that,
+\begin{align*}
+\int \psi_t^{\epsilon, x}(y) dx & = \int \EE[p_{\epsilon^2+T(t)}(x,y)] dx \\ &= \EE[ \int p_{\epsilon^2+T(t)}(y,x) dx ] = 1.
+\end{align*}
+Thus,
+\begin{align*}
+\int \EE\left[ M_t(x)^2 \right] dx & \leq  \frac{C \theta}{\varepsilon^d N}  \int_0^t \EE \left[  \langle \int  q_\theta(y,dz), \overline{\eta}_s(dy) \rangle + \langle 1, \overline{\eta}_s(dy)\rangle \right] ds.
+\\ & \leq \frac{C \theta}{\varepsilon^d N} \int_0^t \EE[ \langle 1, \overline{\eta}_s(dy) \rangle ] ds \\ & \leq T \frac{C \theta}{ \varepsilon^d N}
+\end{align*}
+proving the result.
+\end{proof}
+
+By doing the same pattern used to prove Proposition~\ref{Prop:SecondMomentMass} (replacing the use of equation (\ref{eq:MPTotalMass}) by equation (\ref{MartingaleProblemMolifier}) and the used of equation \ref{eq:quadvarMass} by Corollary~\ref{Cor:ControlQVMQ}) we can get the following result.
+\begin{proposition}
+Under the assumptions of Theorem~\ref{TeoremOneStepConvergence} there is a finite constant $C$ (independent of $\epsilon, N, \theta$) such that, for all $t \in [0,T]$, $x \in \mathbb{R}^d$ and for big enough $N$ and $\theta$, $\EE[ (\rho_\epsilon*\overline{\eta}_t(x))^2] \leq C$.\label{Prop:SecondMomentDensity}
+\end{proposition}
+
+%\begin{remark}\label{FisUniformlyBounded}
+%Let $\delta>0$.By the Markov's inequality and Proposition~\ref{FirstBoundLocalDensity} we have that, for any $x \in \mathbb{R}^d$,
+%\[ \PP[ (\rho_\epsilon*\overline{\eta}_t)(x) > \delta^{-1/2}] = \PP[ (\rho_\epsilon*\overline{\eta}_t)(x)^2 > \delta^{-1}]  \leq C \delta \]
+%In another words, up to an error that is independent of $\theta, N, \epsilon$, we can assume $(\rho_\epsilon*\overline{\eta}_t)(x)$ is bounded.
+From our assumption that $|F'(x)1_{x>0}|$ is uniformly bounded by some constant $C_{F'}$ we can then compute that,
+%\begin{align*}
+% \PP[|F(\rho_\epsilon*\overline{\eta}_t(x))| > |F(0)|+C_{F'}\epsilon^{-1/4}] &\leq \PP[|F(0)|+  C_{F'}\rho_\epsilon*\overline{\eta}_t(x) > |F(0)|+C_{F'}\epsilon^{-1/4}] \\ &= \PP[\rho_\epsilon*\overline{\eta}_t(x) > \epsilon^{-1/4}] \\ &\leq C \epsilon^{1/2}.
+\end{align*}
+%We can then assume, up to an error that is independent of $\theta, N, \epsilon$, that $F(\rho_\epsilon*\overline{\eta}_t)$ is uniformly bounded (not only bounded above). 
+%\end{remark}
+%\todo[inline]{Note from Ian: We will need this remark later to avoid imposing that $F(x)$ is.
+uniformly bounded.
+This is something we clearly don't want to impose, since we want to cover the standard F-KPP equation.
+}
 %\begin{corollary}
@@
 %\end{proof}
-
-%\todo[inline]{Do we need that? May erase it latter if we dont.}
 
@@
 \begin{align*}
-\int f(x) \rho_\epsilon * \overline{\eta}_t(x) dx &= \int \int f(x) \rho_\epsilon (x-y) \overline{\eta}(dy) dx \\ & = \langle \int fd(x) \rho_\epsilon(x-y) dx, \overline{\eta}(dy) \rangle \\ &= \langle T_{\epsilon^2} f(y), \overline{\eta}_t(dy) \rangle
+\int f(x) \rho_\epsilon * \overline{\eta}_t(x) dx &= \int \int f(x) \rho_\epsilon (x-y) \overline{\eta}(dy) dx \\ & = \langle \int f(x) \rho_\epsilon(x-y) dx, \overline{\eta}(dy) \rangle \\ &= \langle T_{\epsilon^2} f(y), \overline{\eta}_t(dy) \rangle
 \end{align*}
@@
 To proceed we note that the quadratic variation of $\widehat{M}_t$ is;
-\[ [ \widehat{M}]_t = \frac{\theta}{N}\int_0^t \langle T_{1/\theta}(T_{\epsilon^2}f(\cdot)^2)(y) + \left(2+\frac{F(\rho_\epsilon*\overline{\eta}_s(y))}{\theta}\right)T_{\epsilon^2}f(y)^2, \overline{\eta}_s(dy) \rangle ds \]
+\[ [ \widehat{M}]_t = \frac{\theta}{N}\int_0^t \langle T_{1/\theta}(T_{\epsilon^2}f(\cdot)^2)(y) + \left(1+\frac{F(\rho_\epsilon*\overline{\eta}_s(y))}{\theta}\right)T_{\epsilon^2}f(y)^2, \overline{\eta}_s(dy) \rangle ds \]
 And so, computing as in the last inequality of (\ref{ShortBoundLaplacianHS}) gives that,
@@
 Therefore, by taking supremum and expectation and in (\ref{MGPT_epsilon}) we conclude that
-\[ \EE[\sup_{0 \leq t \leq T} \langle T_{\epsilon^2} f, \overline{\eta}_t \rangle ] \text{ is uniformly bounded (for fixed } f \text{)} \]
+\begin{equation} \EE[\sup_{0 \leq t \leq T} \langle T_{\epsilon^2} f, \overline{\eta}_t \rangle ] \text{ is uniformly bounded (for fixed } f \text{)} \label{eq:boundedIntegralAgainstf} \end{equation}
 To conclude $C$-tightness we would require that, for $T>0$, $\alpha > 0$ there is some $\delta >0$ so that for $\theta$ and $N$ large enough,
@@
 \end{proof}
+\begin{remark} \label{remark:BoundedIntegral}
+Similar as we got equation (\ref{eq:boundedIntegralAgainstf}), from equation \ref{MGPT_epsilon} we can conclude that
+\[ \EE\left[\sup_{0 \leq t \leq T} \int \rho_{\epsilon/2} * \overline{\eta}_t(x) dx \right] = C < \infty. \]
+By using this and the same pattern used to prove Proposition~\ref{Prop:SecondMomentMass}, we can then conclude that,
+\[ \EE\left[  \sup_{0 \leq t \leq T} \int \left(\rho_{\epsilon/2} * \overline{\eta}_t(x) \right)^2 dx \right] = C < \infty. \]
+Since,
+\begin{align*}
+\langle \rho_\epsilon * \overline{\eta}_t(z), \overline{\eta}(dz) \rangle & = \sum_{y \in \overline{\eta}_t} \sum_{z \in \overline{\eta}_t} \rho_\epsilon(y-z) \overline{\eta}(z) \overline{\eta}(y) \\ &= \int  \sum_{y \in \overline{\eta}_t} \sum_{z \in \overline{\eta}_t} \rho_{\epsilon/2}(y-x) \rho_{\epsilon/2}(z-x) \overline{\eta}(z) \overline{\eta}(y) \\ &= \int (\rho_{\epsilon/2}*\overline{\eta}_t(x))^2 dx.
+\end{align*}
+This allows us to conclude that $\EE[\langle \rho_\epsilon*\overline{\eta}_t(z),\overline{\eta}_t(dz) \rangle ] < \infty$. This bound will be useful in the next section.
+\end{remark}
 \section{Identifying the limit}
@@
 In this section we prove the following continuity estimate for $\rho_\epsilon * \overline{\eta}_t(x)$.
-
 \begin{proposition} \label{ContinuityEstimate}
-Under the same conditions of Theorem~\ref{TeoremOneStepConvergence} we have that for all $y,x \in \mathbb{R}^d$,
-\[ \EE[|\rho_\epsilon*\overline{\eta}_s(x) -\rho_\epsilon*\overline{\eta}_s(y)| ] \leq \mathcal{O}\left( |y-x| + \left(\frac{\theta}{N \epsilon^2}\right)^{1/2} + \frac{1}{\epsilon^2 \theta} \right)\]
+Under the same conditions of Theorem~\ref{TeoremOneStepConvergence} we have that for all $x \in \mathbb{R}^d$, $\delta>0$,
+\[
+\int |\rho_\epsilon*\overline{\eta}_s(x) -\rho_\epsilon*\overline{\eta}_s(y)| \rho_\delta(x-y) dy \]
+is bounded by
+\begin{align*}
+\frac{\delta}{\sqrt{\epsilon^2+s}} \langle 1,\overline{\eta}_0(dz) \rangle &+ \int_0^s \frac{\delta}{\sqrt{\epsilon^2+s-r}} (\langle 1, \overline{\eta}_r(dz)\rangle + \langle \rho_\epsilon*\overline{\eta}_r(z), \overline{\eta}_r(dz)\rangle)dr \\ &+ |M_s(x)| + \int |M_s(y)| \rho_\delta(y-x)dy + \mathcal{O}\left( \frac{1}{\epsilon^2 \theta}\right)
+\end{align*} 
 \end{proposition}
+where $M_s(x)$ is the martingale in (\ref{MartingaleProblemMolifier}).
 \begin{proof}
-By using (\ref{MartingaleProblemMolifier}) (and an obvious abuse of notation) we can write,
+Recall from our assumptions that $|F'(x)1_{x>0}|$ is uniformly bounded. Hence, we can always write,
+\begin{align} \label{StrongBoundOnF}
+|F(\rho_\epsilon*\overline{\eta}_t(x))| \leq |F(0)| + C \rho_\epsilon*\overline{\eta}_t(x)
+\end{align}
+So, by (\ref{MartingaleProblemMolifier}) we can write,
 \begin{align}
-& |\rho_\epsilon*\overline{\eta}_t(x)-\rho_\epsilon*\overline{\eta}_t(y)| \nonumber \\ &= |\langle \rho_\epsilon(y-z)-\rho_\epsilon(x-z),\overline{\eta}_t(dz) \rangle | \nonumber\\ &\leq  |M_t(x)-M_t(y)|  +\langle \psi_t^{\epsilon,y}(z)-\psi_t^{\epsilon,x}(z), \overline{\eta}_0(dz)\rangle \nonumber \\ &+ |\int_0^t \langle (\psi_{t-s}^{\epsilon,z}(x) - \psi_{t-s}^{\epsilon, y}(x) )F(\rho_\epsilon*\overline{\eta}_s(x)), \overline{\eta}_s(dx) \rangle  ds |  \label{eq:bound1CE} \end{align}
-For the martingale term; note that Corollary~\ref{Cor:ControlQVMQ} and the Burkholder-Davis-Gundy inequality give,
-\[
-\EE[\sup_{s \leq t} M_t(x) + M_t(y)] \leq C\left(\frac{\theta}{N \epsilon^d}\right)^{1/2}. \]
-On the other hand, since $F(x)1_{x >0}$ is bounded above, by combining Lemma~\ref{FirstBoundLocalDensity}, Remark~\ref{Remark:BoundLocalDensity} and Lemma~\ref{Lemma:BoundPsiHS2} we can replace $\psi_t^{\epsilon, y}$ and $\psi_t^{\epsilon,x}$ by the heat kernels by paying an error of order $\mathcal{O}(1/(\epsilon^2\theta))$.
-That is,
+& |\rho_\epsilon*\overline{\eta}_t(x)-\rho_\epsilon*\overline{\eta}_t(y)| \nonumber \\ &= |\langle \rho_\epsilon(y-z)-\rho_\epsilon(x-z),\overline{\eta}_t(dz) \rangle | \nonumber\\ &\leq  |M_t(x)-M_t(y)|  +\langle \psi_t^{\epsilon,y}(z)-\psi_t^{\epsilon,x}(z), \overline{\eta}_0(dz)\rangle \nonumber \\ &+ C\int_0^t \langle |\psi_{t-s}^{\epsilon,x}(z) - \psi_{t-s}^{\epsilon, y}(z) |, \overline{\eta}_s(dz) \rangle  ds | \\ &+ C \int_0^t \langle |\psi_{t-s}^{\epsilon,x}(z) - \psi_{t-s}^{\epsilon, y}(z) | \rho_\epsilon*\overline{\eta}(z), \overline{\eta}_s(dz) \rangle  ds | \label{eq:bound1CE} \end{align}
+By using Lemma~\ref{Lemma:BoundPsiHS2} we can then write, 
 \begin{align*}
-&\EE\left[|\rho_\epsilon*\overline{\eta}_t(x)-\rho_\epsilon*\overline{\eta}_t(y)| \right] \leq \EE[|\langle p_{\epsilon^2+t}(y,z)-p_{\epsilon^2+t}(x,z),\overline{\eta}_0(dz)\rangle|]  \\ &+\mathbb{E}\left[ \int_0^t C \langle |p_{\epsilon^2+t}(y,z)-p_{\epsilon^2+t}(x,z)|,\overline{\eta}_s(dz)\rangle ds \right]+ \mathcal{O}\left( \left( \frac{\theta}{N \epsilon^d}\right)^{1/2} + \frac{1}{\epsilon^2 \theta} \right)\end{align*}
-By using Lemma~\ref{Lemma:ContinuityHS}, Lemma~\ref{FirstBoundLocalDensity}, Remark~\ref{Remark:BoundLocalDensity} and our hypothesis on the initial condition we get that,
+ \int &|\rho_\epsilon*\overline{\eta}_s(x) -\rho_\epsilon*\overline{\eta}_s(y)| \rho_\delta(x-y) dy  \leq \int |p_{\epsilon^2+s}(y,z)-p_{\epsilon^2+s}(x,z)|\overline{\eta}_0(dz) \rho_\delta(x-y)dy \\&+ C\int_0^s \langle p_{\epsilon^2+s-r}(y,z)-p_{\epsilon^2+s-r}(x,z)|, \overline{\eta}_r(dz) \rangle \rho_\delta (x-y) dr  \\  & + C \int_0^s \langle |p_{\epsilon+s-r}(y,z) - p_{\epsilon+s-r}(x,z) | \rho_\epsilon*\overline{\eta}_r(z), \overline{\eta}_r(dz) \rangle  dr | + \int|M_s(y)-M_s(x)| \rho_\delta(y-x)dy  \\  & + \frac{C}{\epsilon^2 \theta} \int \langle \rho_\epsilon*\overline{\eta}(z),\overline{\eta}_s(dz)\rangle ds   +\mathcal{O}\left( \frac{1}{\epsilon^2 \theta} \right)
+\end{align*}
+By Remark~\ref{remark:BoundedIntegral} the last integral term is of order $(\epsilon^2 \theta)^{-1}$.
+By using Lemma~\ref{Lemma:ContinuityHS} we get that the contribution of the first three terms is bounded by,
 \begin{align*}
-\EE\left[|\rho_\epsilon*\overline{\eta}_t(x)-\rho_\epsilon*\overline{\eta}_t(y)| \right] &\leq \EE[|\langle p_{\epsilon^2+t}(y,z)-p_{\epsilon^2+t}(x,z),\overline{\eta}_0(dz)\rangle|] \\ & + C \int_0^t \frac{1}{\sqrt{s+\epsilon^2}} ds |x-y| \\ &\leq C|x-y| +\mathcal{O}\left( \left( \frac{\theta}{N \epsilon^d}\right)^{1/2} + \frac{1}{\epsilon^2 \theta} \right)
+\int &\frac{|y-x|}{\sqrt{\epsilon^2+s}} \rho_{\delta}(y-x) dy \langle 1, \overline{\eta}_0(dz)\rangle + \int \int_0^s  \langle \frac{|y-x|}{\sqrt{\sqrt{\epsilon^2+s-r}}}, \overline{\eta}_r(dz) \rangle \rho_\delta(x-y) dy dr \\ & +  \int \int_0^s \langle \frac{|y-x| \rho_\epsilon*\overline{\eta}(z)}{\sqrt{\epsilon^2+s-r}}, \overline{\eta}_r(dz) \rangle \rho_\delta(y-x) dy dr \\ & \leq \frac{\delta}{\sqrt{\epsilon^2+s}} \langle 1, \overline{\eta}_0(dz) \rangle + \int_0^s \frac{\delta}{\sqrt{\epsilon^2+s-r}} (\langle 1, \overline{\eta}_r(dz) \rangle + \langle \rho_\epsilon*\overline{\eta}_r(z), \overline{\eta}_r(dz) \rangle) dr.
 \end{align*}
-as required.
+To finish the proof just notice that,
+\begin{align*}
+\int |M_s(y)-M_s(x)| \rho_\delta(y-x)dy \leq |M_s(x)| + \int |M_s(y)| \rho_\delta(y-x)dy.
+\end{align*}
 \end{proof}
-
 \subsection{Identifying the limit of $\langle T_{\epsilon^2} f(y), \overline{\eta}_t (dy) \rangle$.}
@@
 \begin{equation*}
-\EE[|\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\overline{\eta}_s(dy)), \overline{\eta}_s(dy) \rangle - \langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \overline{\eta}_s(dy)), \rho_\epsilon * \overline{\eta}_s(y) dy \rangle|]
+\int_0^t \EE[|\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\overline{\eta}_s(dy)), \overline{\eta}_s(dy) \rangle - \langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \overline{\eta}_s(dy)), \rho_\epsilon * \overline{\eta}_s(y) dy \rangle|]
 \end{equation*}
@@
 \begin{equation*}
-C \left( \left(\frac{\theta}{\epsilon^d N}\right)^{1/2} + \frac{1}{\epsilon^2 \theta}+ \left(\frac{\theta}{\epsilon^d N}\right)^{1/3} + \epsilon +  \epsilon^2\right) 
+\mathcal{O}\left( \frac{1}{\epsilon^2 \theta} + \epsilon^2 + \epsilon + \epsilon^{1/3}  + \left( \frac{\theta}{N \epsilon^d} \right)^{1/2}\right)
 \end{equation*}
@@
 \begin{align*}
-    &\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\overline{\eta}_s(dy)), \overline{\eta}_s(dy) \rangle - \langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \overline{\eta}_s(dy)), \rho_\epsilon * \overline{\eta}_s(y) dy \rangle \\ & = \langle \int T_{\epsilon^2} f(y) F(\rho_\epsilon * \overline{\eta}_s(y))\rho_\epsilon(y-w) dy, \overline{\eta}(dw)\rangle - \langle T_{\epsilon^2} f(w) F(\rho_\epsilon*\overline{\eta}_s(w)), \overline{\eta_s}(dw) \rangle \\ &= \langle \int \{ T_{\epsilon^2} f(y) F(\rho_\epsilon*\overline{\eta}_s(y))-T_{\epsilon^2}f(w) F(\rho_\epsilon*\overline{\eta}_s(w))\} \rho_\epsilon(w-y)dy, \overline{\eta}_s(dw) \rangle.
+    &\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\overline{\eta}_s(dy)), \overline{\eta}_s(dy) \rangle - \langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \overline{\eta}_s(dy)), \rho_\epsilon * \overline{\eta}_s(y) dy \rangle \\ & = \langle \int T_{\epsilon^2} f(y) F(\rho_\epsilon * \overline{\eta}_s(y))\rho_\epsilon(y-w) dy, \overline{\eta}_s(dw)\rangle - \langle T_{\epsilon^2} f(w) F(\rho_\epsilon*\overline{\eta}_s(w)), \overline{\eta}_s(dw) \rangle \\ &= \langle \int \{ T_{\epsilon^2} f(y) F(\rho_\epsilon*\overline{\eta}_s(y))-T_{\epsilon^2}f(w) F(\rho_\epsilon*\overline{\eta}_s(w))\} \rho_\epsilon(w-y)dy, \overline{\eta}_s(dw) \rangle.
 \end{align*}
@@
 where in the last inequality we have used $F(x)1_{x>0}$ and $|F'(x)1_{x>0}|$ are both bounded above.
-We now aim to replace $\rho_\epsilon*\overline{\eta}_s(y)-\rho_\epsilon*\overline{\eta}_s(w)$ with its expectation.
-For this note that,
+We want to use Proposition~\ref{ContinuityEstimate} in the last equation, but the terms that we would obtain would be too hard to control unless we first control the total mass and their noise.
+Let us define,
+\begin{align*}
+A_{t} &:= \left\{ \sup_{0 \leq s \leq t} \langle 1, \overline{\eta}_s(dz) \rangle > \epsilon^{-2/3} \right\}. \end{align*}
+Note that, by Markov's inequality and Lemma~\ref{Lemma:UniformlyBoundedMass} the event $A_{t}$ has probability of order $\epsilon^{2/3}$.
+Hence, writing $I = I(1_{A^c_{t}} + 1_{A_{t}})$ and proceeding as before we can use Proposition~\ref{ContinuityEstimate} in (\ref{FirstBoundCT}) to get,
 \begin{align}
-Var( \overline{\eta}_s*\rho_\epsilon(z)) &=  Var( \overline{\eta}_s*\rho_\epsilon(z) - \mathbb{E}(\overline{\eta}_s*\rho_\epsilon(z))) \nonumber \\ &= \EE[ [ \overline{\eta}*\rho_\epsilon(z) ]_s] \nonumber \\ &= \EE[ [ M]_s ] = \mathcal{O}\left( \frac{\theta}{\epsilon^{d} N} \right) \label{eq:AlmostDeterministic}
+&\int_0^t \EE[|\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\overline{\eta}_s(dy)), \overline{\eta}_s(dy) \rangle - \langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \overline{\eta}_s(dy)), \rho_\epsilon * \overline{\eta}_s(y) dy \rangle|] \nonumber \\ &\leq   \int_0^t \EE[ \frac{\epsilon}{\sqrt{\epsilon^2 + s}} \langle 1,\overline{\eta}_0(dz) \rangle \langle 1, \overline{\eta}_s(dz)\rangle ] ds +  \int_0^t \EE[  \int_0^s \frac{\epsilon}{\sqrt{\epsilon^2 + s - r}} \langle 1, \overline{\eta}_r (dz) \rangle dr \langle 1, \overline{\eta}_s(dz) \rangle  ] ds \nonumber\\ & + \int_0^t \EE[   1_{A^c_{t}} \int_0^s \frac{\epsilon}{\sqrt{\epsilon^2 + s - r}} \langle \rho_\epsilon*\overline{\eta}_r(z), \overline{\eta}_r(dz) \rangle dr \langle 1, \overline{\eta}_s(dz) \rangle  ] ds + \int_0^t \EE[\langle |M_s(x)|,\overline{\eta}_s(dx) \rangle] ds \nonumber \\ &+ \int_0^t \int \EE[|M_s(y)|\rho_\epsilon*\overline{\eta}_s(y)] dy ds  +\mathcal{O}\left( \frac{1}{\epsilon^2 \theta} + \epsilon^2 + \epsilon^{1/3} \right)  \label{ThingsToBound}
 \end{align}
-in the second equality we have used that $\overline{\eta}_s*\rho_\epsilon(z) - \mathbb{E}(\overline{\eta}_s*\rho_\epsilon(z))$ is a mean zero martingale and in the third one that $M(\rho_\epsilon)$ and $\overline{\eta} * \rho_\epsilon(z)$ differ only on finite variation terms and hence have the same quadratic variation.
-The last inequality is then an application of Corollary~\ref{Cor:ControlQVMQ}.
-By a polarization argument is then follows that:
-\[ Var(\rho_\epsilon * \overline{\eta}_s(y) - \rho_\epsilon * \overline{\eta}_s(w)) = \mathcal{O}\left(\frac{\theta}{N \epsilon^d}\right).\]
-Hence, by  Tshecyshev inequality we got that, there is a constant $C$ such that, 
-\[ \PP\left[|\rho_\epsilon * \overline{\eta}_s(y) - \rho_\epsilon * \overline{\eta}_s(w) - \EE[\rho_\epsilon * \overline{\eta}_s(y) - \rho_\epsilon * \overline{\eta}_s(w)]| > C \left(\frac{\theta}{\epsilon^d N}\right)^{1/3}\right] \leq \mathcal{O}\left(\frac{\theta}{\epsilon^d N}\right)^{1/3} \]
-Using this last bound, Proposition~\ref{ContinuityEstimate}, Lemma~\ref{Lemma:UniformlyBoundedMass} and (\ref{FirstBoundCT}) gives that,
+Note we have bounded $1_{A^c_{t}}$ by one in all the terms expect the third one, which is the one that will require it.
+For the first two term we can use our hypothesis on the initial condition and that $2 ab \leq a^2+b^2$ to get that their contribution is bounded by,
 \begin{align*}
-&\EE[|\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\overline{\eta}_s(dy)), \overline{\eta}_s(dy) \rangle - \langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \overline{\eta}_s(dy)), \rho_\epsilon * \overline{\eta}_s(y) dy \rangle|] \\ &\leq   C \EE[ \langle \int | y - w |  \rho_\epsilon(w-y)dy, \overline{\eta}_s(dw) \rangle  ]  \\  &+ \mathcal{O}\left( \left(\frac{\theta}{\epsilon^d N}\right)^{1/2} + \frac{1}{\epsilon^2 \theta}+ \left(\frac{\theta}{\epsilon^d N}\right)^{1/3} + \epsilon^2\right) \\ &= \mathcal{O}\left( \left(\frac{\theta}{\epsilon^d N}\right)^{1/2} + \frac{1}{\epsilon^2 \theta}+ \left(\frac{\theta}{\epsilon^d N}\right)^{1/3} + \epsilon +  \epsilon^2\right)
+\int_0^t C \frac{\epsilon}{\sqrt{\epsilon^2+s}}\EE[\langle 1, \overline{\eta}_s(dz) \rangle] ds + \int_0^t \int_0^s \frac{\epsilon}{\sqrt{\epsilon^2+s-r}}\EE[\langle 1, \overline{\eta}_r(dz)\rangle^2 + \langle 1, \overline{\eta}_s(dz)\rangle^2] ds,
 \end{align*}
-which completes the proof.
+which, due to Proposition~\ref{Prop:SecondMomentMass}, is of order $\epsilon$. To bound the third integral term we use the event $A_{t}$ to get it is bounded by,
+\begin{align*}
+\int_0^t \int_0^s \frac{\epsilon^{1/3}}{\sqrt{\epsilon^2+s-r}} \EE[ \langle \rho*\overline{\eta}_r(z), \overline{\eta}(dz) \rangle] dr ds = \mathcal{O}(\epsilon^{1/3})
+\end{align*}
+where we have used Remark~\ref{remark:BoundedIntegral}. 
+We now proceed to control the terms with martingales in (\ref{ThingsToBound}). For the first one note that, by using Cauchy-Schwartz in $L^2(\mathbb{P})$ and then in $L^2(\mathbb{R}^d)$,
+\begin{align}
+\int_0^t \int \EE[|M_s(y)|\rho_\epsilon*\overline{\eta}_s(y)] dy ds & \leq \int_0^t \int \EE[|M^2_s(y)]^{1/2} \EE[\rho_\epsilon * \overline{\eta}_s(y)^2]^{1/2} dy dy \nonumber \\ & \leq \int_0^t \left( \int \EE[|M_s(y)^2|] dy \int \EE[\rho_\epsilon * \overline{\eta}_s(y)^2] dy \right)^{1/2} ds  \nonumber \\ &= \mathcal{O}\left( \left( \frac{\theta}{N \epsilon^d} \right)^{1/2} \right)
+\label{TwiceCS} \end{align}
+where in the last inequality we used Proposition~\ref{IntegrabilityOfM} and Remark~\ref{remark:BoundedIntegral}.
+For the second term with a Martingale in (\ref{ThingsToBound}) we need to proceed with more care.
+For this we first rewrite explicitly the dependency on $\epsilon$ of $M_t(x)$ by using $M_t^{\varepsilon^2}(x)$.
+We can then write from (\ref{MartingaleProblemMolifier}) and Lemma~\ref{Lemma:BoundPsiHS2}) that,
+\begin{align*}
+ M_t^{\epsilon^2}(x) &= \langle p_{\epsilon^2}(x,y), \overline{\eta}_t(dx) \rangle - \langle p_{t + \epsilon^2}(x,y), \overline{\eta}_0(dx) \rangle \\ &- \int_0^t \langle F(\rho_\epsilon*\overline{\eta}_s(y)) p_{t-s+\epsilon^2}(x,y), \overline{\eta}_s(dy) \rangle ds + \mathcal{O}\left(\frac{1}{\epsilon^2 \theta} \right) \end{align*}
+ It follows then that $M_s^{\epsilon^2}= p_{\epsilon^2/2}*M_s^{\epsilon^2/2} + \mathcal{O}\left(1/\epsilon^2 \theta\right)$. Using this we can then bound,
+ \begin{align*}
+\int_0^t &\EE[ \langle |M_s^{\epsilon^2}(x)|, \overline{\eta}_s(dx) \rangle ] ds \\ &= \int_0^t \EE[ \langle | p_{\epsilon^2/2}*M_s^{\epsilon^2/2}(x)|, \overline{\eta}_s(dx) \rangle] ds \\ & \leq  \int_0^t \EE[ \langle p_{\epsilon^2/2}*| M_s^{\epsilon^2/2}(x)|, \overline{\eta}_s(dx) \rangle] ds \\ &= \int_0^t \EE[ \langle \int p_{\epsilon^2/2}(x,y) |M_s^{\epsilon^2/2}(y)|dy, \overline{\eta}_s(dx) \rangle] ds \\ &= \int_0^t \EE[ \int |M_s^{\epsilon^2/2}(y)| p_{\epsilon^2/2}*\overline{\eta}_s(y) dy ] ds \\ &= \int_0^t \int \EE[ M_s^{\epsilon^2/2}(y)| p_{\epsilon^2/2} * \overline{\eta}_s(dy)] dy ds
+ \end{align*}
+ An analogues computation as the one performed to obatin (\ref{TwiceCS}) gives the last term is $\mathcal{O}\left( \left( \frac{\theta}{N \epsilon^d} \right)^{1/2} \right)$.
  \end{proof}
@@
 \label{aprox2}
-\langle f, (\overline{\eta}_s * \rho_\epsilon)^2 \rangle \sim \int \int f(z) (\rho_\epsilon * \overline{\eta}_s)(z) K_\delta (z,y) (\rho_\epsilon * \overline{\eta}_s)(y) dz dy.
+\langle f, (\overline{\eta}_s * \rho_\epsilon)^2 \rangle \sim \int \int f(z) (\rho_\epsilon * \overline{\eta}_s)(z) \rho_\delta (z-y) (\rho_\epsilon * \overline{\eta}_s)(y) dz dy.
 \end{equation}
-where $K_\delta$ is a smooth Kernel that converges (weakly) to a Dirac mass when $\delta$ goes to $0$ (we will take the heat kernel at time $\delta$).
-We first argue why this is enough.
-Note the right hand side of (\ref{aprox2}) can written with some abuse of notation as
-\[ \int_{\mathbb{R}^{d} \otimes \mathbb{R}^d} f(z) K_\delta(z,y) (\rho_\epsilon * \overline{\eta}_s(dz) \otimes (\rho_\epsilon * \overline{\eta}_s(dy)). \]
-Weak convergence of $\rho_\epsilon * \overline{\eta}$ (plus continuity of the mapping $(z,y) \rightarrow f(z) K_\delta(z,y)$) gives that the last term converges in $L^1$ to
-\[ \int_{\mathbb{R}^{d} \otimes \mathbb{R}^d} f(z) K_\delta(z,y) (u_s(dz) \otimes (u_s(dy)). \]
+Before proceeding with a proof of (\ref{aprox2}), we argue why this is enough to conclude Theorem~\ref{TeoremOneStepConvergence}. Note the right hand side of (\ref{aprox2}) can written as
+\[ \int_{\mathbb{R}^{d} \otimes \mathbb{R}^d} f(z) \rho_\delta(z-y) (\rho_\epsilon * \overline{\eta}_s(dz) \otimes (\rho_\epsilon * \overline{\eta}_s(dy)). \]
+Weak convergence of $\rho_\epsilon * \overline{\eta}$ (plus continuity of the mapping $(z,y) \rightarrow f(z) \rho_\delta(z-y)$) gives that the last term converges in $L^1$ to
+\[ \int_{\mathbb{R}^{d} \otimes \mathbb{R}^d} f(z) \rho_\delta(z-y) (u_s(dz) \otimes (u_s(dy)). \]
 Finally, by a direct analogue of (\ref{aprox2}) we can say that
-\begin{equation} \int_{\mathbb{R}^{d} \otimes \mathbb{R}^d} f(z) K_\delta(z,y) (u_s(dz) \otimes (u_s(dy)) \sim \langle f(x), u_s^2(x) dx \rangle. \label{aprox3} \end{equation}
-which is what we seek. We proceed then to prove (\ref{aprox2}), with the understanding that (\ref{aprox3}) follows in a similar way and give even better error terms.
+\begin{equation} \int_{\mathbb{R}^{d} \otimes \mathbb{R}^d} f(z) \rho_\delta(z-y) (u_s(dz) \otimes (u_s(dy)) \sim \langle f(x), u_s^2(x) dx \rangle. \label{aprox3} \end{equation}
+which is what we seek. We proceed now to prove (\ref{aprox2}), with the understanding that (\ref{aprox3}) follows in a similar way and give even better error terms.
 \begin{theorem}
-Under the conditions of Theorem~\ref{TeoremOneStepConvergence}, we have that for any $s>0$,
+Under the conditions of Theorem~\ref{TeoremOneStepConvergence}, we have that
 \begin{align*}
-\mathbb{E}&\left[\left| \langle f(y), (\overline{\eta}_s * \rho_\epsilon(y))^2) dy\rangle - \int \int f(x) (\rho_\epsilon * \overline{\eta}_s)(z) K_\delta (z,y) (\rho_\epsilon * \overline{\eta}_s)(y) dz dy.
-\right|\right]
+\int_0^t \mathbb{E}&\left[\left| \langle f(y), (\overline{\eta}_s * \rho_\epsilon(y))^2) dy\rangle - \int \int f(y) (\rho_\epsilon * \overline{\eta}_s)(z) \rho_\delta (z-y) (\rho_\epsilon * \overline{\eta}_s)(y) dz dy.
+\right|\right] ds
 \end{align*}
 is bounded by,
-\[  \mathcal{O}\left(\delta+\frac{\theta}{\epsilon^d N} + \left( \frac{\theta}{\epsilon^d N} \right)^{1/2} + \frac{1}{\epsilon^2 \theta} \right)  \]
-in particular, under (\ref{ConditionsForConvergence}), the last term goes to $0$ uniformly in $\theta,\epsilon,N$ and $\delta$.
+\[  \mathcal{O}\left(\delta^{1/3} + \delta +  \frac{1}{\epsilon^2 \theta} + \left( \frac{\theta}{N \epsilon^2}\right)^{1/2} \right)  \]
+in particular, under (\ref{ConditionsForConvergence}), the last term goes to $0$ uniformly in $\theta,\epsilon,N$ and $\delta$ (when $\delta$, $\epsilon$ go to $0$ and $N,\theta$ to infinity).
 \end{theorem}
@@
 \begin{align}
-\mathbb{E}&\left[| \langle f, (\overline{\eta}_s * \rho_\epsilon(y))^2) dy \rangle - \int \int f(x) (\rho_\epsilon * \overline{\eta}_s)(z) K_\delta (z,y) (\rho_\epsilon * \overline{\eta}_s)(y) dz dy.
-|\right] \nonumber \\ &\leq  \Vert f \Vert_\infty \int_{S_f} \int \left| \mathbb{E}\left[ \left\{ (\rho_\epsilon * \overline{\eta}_s)(z)-(\rho_\epsilon * \overline{\eta}_s)(y) \right\} (\rho_\epsilon * \overline{\eta}_s)(z)\right] \right| K_\delta(z,y) dz dy    \label{b1}
+&\int_0^t \mathbb{E}\left[| \langle f(y), (\overline{\eta}_s * \rho_\epsilon(y))^2) dy \rangle - \int \int f(y) (\rho_\epsilon * \overline{\eta}_s)(z) \rho_\delta (z-y) (\rho_\epsilon * \overline{\eta}_s)(y) dz dy.
+|\right] ds \nonumber \\ &\leq  \Vert f \Vert_\infty \int_{S_f}  \int_0^t  \mathbb{E}\left[ \int \left\{ \left|(\rho_\epsilon * \overline{\eta}_s)(y)-(\rho_\epsilon * \overline{\eta}_s)(z) \right|   \rho_\delta(z-y) dz \right\} (\rho_\epsilon *\overline{\eta}_s)(y) \right] ds  dy \label{b1}
 \end{align}
-
-For separating the last product in the expected value we note that (\ref{eq:AlmostDeterministic}) implies that:
-\begin{equation}
-\label{yeet1}
-\EE[\overline{\eta}_s*\rho_\epsilon(z)^2] = \EE[\overline{\eta}_s*\rho_\epsilon(z)]^2 + \mathcal{O}\left( \frac{\theta}{\epsilon^{d}N} \right)
-\end{equation}
-And furthermore, by a polarization argument, we can get:
-\begin{equation}
-\label{yeet2}
-\EE[\overline{\eta}_s*\rho_\epsilon(z) \overline{\eta}_s*\rho_\epsilon(y)] = \EE[\overline{\eta}_s*\rho_\epsilon(z)]\EE[\overline{\eta}_s*\rho_\epsilon(y)] + \mathcal{O}\left( \frac{\theta}{\epsilon^{d}N} \right)
-\end{equation}
-Using (\ref{yeet1}) and (\ref{yeet2}) we get that the right hand side of (\ref{b1}) can be bounded by;
+We want then to bound (\ref{b1}) by using Proposition~\ref{ContinuityEstimate}. For this consider the event,
+\[ B_{s,y} := \{ \rho_\epsilon * \overline{\eta}_s(y) > \delta^{-2/3} \}. \]
+Note that by Markov's inequality and Lemma~\ref{FirstBoundLocalDensity} the event $B_{s,y}$ has probability of order $\delta^{2/3}$ (and independent of $s$ and $y$).
+Thus, proceeding as how get (\ref{ThingsToBound}), the integral against $ds$ in the right hand side of (\ref{b1}) is bounded by
 \begin{align}
-&\Vert f \Vert_\infty \int_{S_f} \int \mathbb{E}\left[| (\rho_\epsilon * \overline{\eta}_s)(z)-(\rho_\epsilon * \overline{\eta}_s)(y) | (\rho_\epsilon * \overline{\eta}_s)(z)\right] K_\delta(z,y) dy dz   \nonumber \\ &\leq C \Vert f \Vert_\infty \int_{S_f} \int \mathbb{E}\left[| (\rho_\epsilon * \overline{\eta}_s)(z)-(\rho_\epsilon * \overline{\eta}_s)(y) |\right] \mathbb{E}\left[\rho_\epsilon * \overline{\eta}_s(z) \right] K_\delta(z,y) dy dz + \mathcal{O}\left( \frac{\theta}{\epsilon^{d}N} \right)   \label{b1andahalf}
+&\int_0^t \EE[ \frac{\delta}{\sqrt{\epsilon^2 + s}} \langle 1,\overline{\eta}_0(dz) \rangle (\rho_\epsilon *\overline{\eta}_s)(y) ] ds +  \int_0^t \EE[  \int_0^s \frac{\delta}{\sqrt{\epsilon^2 + s - r}} \langle 1, \overline{\eta}_r (dz) \rangle dr(\rho_\epsilon *\overline{\eta}_s)(y)  ] ds \nonumber\\ & + \int_0^t \EE[   1_{B^c_{s,\delta}} \int_0^s \frac{\delta}{\sqrt{\epsilon^2 + s - r}} \langle \rho_\epsilon*\overline{\eta}_r(z), \overline{\eta}_r(dz) \rangle dr (\rho_\epsilon *\overline{\eta}_s)(y) ] ds + \int_0^t \EE[\langle |M_s(x)|,\overline{\eta}_s(dx) \rangle] ds \nonumber \\ & + \int_0^t  \EE[|M_s(y)|\rho_{\epsilon+\delta}*\overline{\eta}_s(y)] ds  +\mathcal{O}\left( \frac{1}{\epsilon^2 \theta} + \delta^{1/3} \right)  \label{ThingsToBound2}
 \end{align}
-An application of Proposition~\ref{ContinuityEstimate} then gives that (\ref{b1andahalf}) is bounded by,
-\begin{align*}
-&C\Vert f \Vert_\infty \int_{S_f} \int C   | y - z|  K_\delta(z,y) dy dz + \mathcal{O}\left( \frac{\theta}{\epsilon^d N} + \left( \frac{\theta}{\epsilon^d N} \right)^{1/2} + \frac{1}{\epsilon^2 \theta} \right)  \\ & \leq  \mathcal{O}\left(\delta +  \frac{\theta}{\epsilon^d N} + \left( \frac{\theta}{\epsilon^d N} \right)^{1/2} + \frac{1}{\epsilon^2 \theta} \right)
-\end{align*}
+From this point onward we can proceed as how we bounded (\ref{ThingsToBound}) in Proposition~\ref{CuadraticApprox} to obtain that the right hand side of (\ref{b1}) is bounded by,
+\[  \mathcal{O}\left(\delta^{1/3} + \delta+ \frac{1}{\epsilon^2 \theta} + \left( \frac{\theta}{N \epsilon^2}\right)^{1/2} \right)  \]
 Concluding the result.

### 2022-06-09 forwards-and-backwards.tex
Update on Overleaf.

--- 2022-05-10 forwards-and-backwards.tex
@@
 the new individual labeled $a \concat j$ is produced,
+\plr{TODO: explain why this does the right thing}
 and $\kappa$ determines which label is associated with the new location,
@@
 % % % % % % % % % % % % %
-\subsection{Proof of convergence for the lookdown process}
-
-The proof of the main result in Section~\ref{sec:lookdown}.
-
-This will depend on Sections~\ref{sec:lookdown_tightness_proofs}
-and \ref{sec:lookdown_generator_proofs}.
-
-% % % % % % % % % % % % %
 \subsection{Tightness of the lookdown process}
     \label{sec:lookdown_tightness_proofs}
+
+In this section,
+we will prove tightness
+of the spatial and level trajectory
+of a line of descent
+(constructed in \S \ref{sec: individual lines of descent})
+as a forward-in-time process.
+
+In Appendix \ref{sec: Topologies on Lookdown},
+we will prove that
+tightness of the whole lookdown process
+holds given
+tightness of 
+all ancestral lineages
+in a countable product topology.
+
+To prove tightness of the 
+spatial and level locations
+of a typical line of descent,
+we will show that the
+jumps in
+spatial and level locations
+of the line of descent
+in finite time
+can be controlled.
+
+Recall that the lines of descents
+track chains of descendant
+individuals forwards through time following the \textit{levels}.
+
+\subsubsection{Tightness of Spatial Trajectories}
+Before proving tightness of our spatial trajectories, 
+note that for a fixed label
+$a=(a_0,a_1,..,a_k)$,
+the spatial evolution of 
+$X^N_{a}(t)$ for $t \geq \tau^N_{a}$
+is determined
+purely by the last term 
+in Equation \eqref{eq: space_across_lineage}.
+
+As a result, the spatial jumps are 
+driven by 
+an underlying Poisson point process. 
+It is therefore sufficient
+to prove that square of 
+these increments are bounded
+in small time scales.
+
+\begin{lemma} \label{lem: tightness of individual spatial trajectory}
+For fixed $a=(a_0,a_1,..,a_k)$,
+$\{(X^{N}_{a}(t))_{t \geq \tau^{N}_a}: N \in \mathbb{N},  \}$ is relatively compact in 
+$D_{\mathbb{R}^d}[0,\infty )$ where $\mathbb{R}^d$ is equipped with the standard Euclidean metric. 
+\end{lemma}
+\begin{proof}
+We write $S_{t,r}:=(t,t+r  ]\times [0,\infty )\times [0,1]\times 
+\{0,1\}$ to be the region for the Poisson measure driving $(X^{N}_{a}(t))_{t \geq \tau_a}$ between time $t$ and $(t+r)$ and write $\tilde\Pi_{\tau_u}(ds,dv,dy,d\kappa):=\Pi_{\tau_u}(ds,dv,dy, d\kappa) - ds\times dv\times dy \times (\frac{1}{2}\delta_{0}+\frac{1}{2}\delta_{1})d\kappa$ to be the compensated Poisson point process of $\Pi_{\tau_u}$.
+For $t\geq\tau_\mathfrak{u}$, we can compute
+\small
+\begin{eqnarray*}
+&&\mathbb{E}[|X^{N}_{\tau_{\mathfrak{u}}}(t+r )-X^{N}_{\tau_{\mathfrak{u}}}(t)|^2|{\cal F}_t^{
+\eta}]\\
+&&= \mathbb{E}\left[\left|\int_{S_{t,r}}{\bf 1}_{\{U_{\tau_{\mathfrak{u}}}(s)+\frac v{2\lambda^{-1}\theta \gamma^{\mathfrak{m}}_\theta(X^{N}_{
+\tau_{\mathfrak{u}}}(s-),\overline{\eta}^{N}(s-))}<\lambda \}}\kappa 
+y\Pi_{\tau_{\mathfrak{u}}}(ds,dv,dy,d\kappa )\right|^2\Bigg|{\cal F}_t^{\eta}\right]\\
+&&\leq 2\mathbb{E}\left[\left|\int_{S_{t,r}}{\bf 1}_{\{v < 2 \theta \gamma^{\mathfrak{m}}_\theta(X^{N}_{
+\tau}(s-),\overline{\eta}^{N}(s-))\}}{\bf 1}_{\kappa =1}
+y\tilde\Pi_{\tau_{\mathfrak{u}}}(ds,dv,dy,d\kappa )\right|^2\Bigg|{\cal F}_t^{\eta}\right]\\
+&&\quad +2\mathbb{E}\left[\left|\int_{t}^{t+r}\int_{\{v < 2 \theta \gamma^{\mathfrak{m}}_\theta(X^{N}_{
+\tau_{\mathfrak{u}}}(s-),\overline{\eta}^{N}(s-))\}}\frac{1}{2}\left| \int_{\mathbb{R}^d} (y-X^{N}_{\tau}(s-)) q^{\mathfrak{m}}_{\theta, \varepsilon}(X^{N}_{\tau}(s-),\overline{\eta}^{N}(s-),dy) \right|
+dvds \right|^2\Bigg|{\cal F}_t^{\eta}\right]\\
+&&\leq 2\mathbb{E}\left[\int_{t}^{(t+r)   }\theta (1+C_G)\int_{{\mathbb{R}}^d}|y-X^{N}_{
+\tau_{\mathfrak{u}}}(s)|^2q^{\mathfrak{m}}_{\varepsilon,\theta}(X^{N}_{\tau_{\mathfrak{u}}}(s),\bar{\eta}^{\varepsilon,\theta,\lambda}(s-),dy)ds\Bigg|{\cal F}_t^{\eta}\right]\\
+&&\quad +2\mathbb{E}\left[\left|\int_{t}^{(t+r)    } \theta (1+C_G)\left|\int_{{\mathbb{R}}^d}
+(y-X^{N}_{\tau_{\mathfrak{u}}}(s))q^{\mathfrak{m}}_{\varepsilon,\theta}(X^{N}_{\tau_{\mathfrak{u}}}(s),
+\overline{\eta}^{N}(s),dy)\right|ds\right|^2\Bigg|{\cal F}_t^{\eta}\right]\\
+&&\leq 2r \overline{\beta}(1+C_G)+2(r \overline{\alpha}(1+C_G))^2.\end{eqnarray*}
+\normalsize
+
+The first inequality uses the fact that $(A+B)^2 \leq 2A^2+2B^2$ as well as the definition of the transition kernel $H$.
+The second inequality holds because birth events occur at rate $2 \theta \gamma^{\mathfrak{m}}_{\theta}$ bounded above by $2\theta (1+C_G)$.
+The third inequality holds given the assumptions on the dispersal kernel.
+
+Finally, since $\overline{\eta}_0$ has compact support, we can take $t=\tau_u$ and apply Markov inequality to get that for every $\delta>0$, there exists $N_{\delta}>0$ such that
+\begin{equation}\label{eq: Compact Containment Condition for individual spatial motion}
+\sup_{\varepsilon, \theta, \lambda}\sup_{T>0}\mathbb{P}\left[|X^{N}_{\tau_{\mathfrak{u}}}(\tau_{\mathfrak{u}}+T)-X^{N}_{\tau_{\mathfrak{u}}}(\tau_{\mathfrak{u}})|>N_{\delta}\right]\leq   \frac{2r \overline{\beta}(1+C_G)+2(r \overline{\alpha}(1+C_G))^2}{N_{\delta}^2}  < \delta,
+\end{equation}
+giving us compact containment condition. Relative compactness thus follows by Theorem 3.8.6.
+of \cite{ethier/kurtz:1986}.
+\end{proof}
+\begin{remark}
+Note that under the assumptions laid out in Theorem \ref{teo: Non-local interaction Convergence} and Theorem \ref{teo: Local Interaction Convergence}, $r \equiv 1$, so 
+$$\gamma^{\mathfrak{m}}_{\varepsilon,\theta}(x, \overline{\eta})=\tilde\gamma_{\theta}(x, \varrho_{\varepsilon}*\overline{\eta})= 1+\frac{G(\varrho_{\varepsilon}*\overline{\eta})}{\theta} \leq (1+C_G)$$
+for all $\theta > 1$, and 
+$$q^{\mathfrak{m}}_{\varepsilon,\theta,\lambda}(x,\overline{\eta},dy)=q_{\theta}(x,dy).$$
+In particular, we have the inequalities
+\begin{align}
+   \sup_{\varepsilon, \theta}\limsup_{x, \overline{\eta}} \theta \left| \int_{\mathbb{R}^d} (y-x) q^{\mathfrak{m}}_{ \varepsilon, \theta}(x,\overline{\eta},dy) \right| =& \sup_{\theta}\limsup_{x} \theta \left| \int_{\mathbb{R}^d} (y-x) q_{\theta}(x,dy) \right| =  0,\\
+   \sup_{\varepsilon, \theta}\limsup_{x, \overline{\eta}} \theta \int_{\mathbb{R}^d} |y-x|^2 q^{\mathfrak{m}}_{ \varepsilon, \theta}(x,\overline{\eta},dy)  =& \sup_{\theta}\limsup_{x} \theta \int_{\mathbb{R}^d} |y-x|^2 q_{\theta}(x,dy) =  1,
+\end{align}
+as the last term can be expressed as $\theta \mathbb{E}_{x}[(B_{1/\theta}-x)^2]=1$.
+As a result, Lemma \ref{lem: tightness of individual spatial trajectory} holds for the setting in Theorem \ref{teo: Non-local interaction Convergence} and Theorem \ref{teo: Local Interaction Convergence}.
+\end{remark}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Tightness of Level Processes}
+Proving tightness of the level process is slightly trickier as the levels of many particles will drift towards infinity in finite time.
+These particles however will not contribute to the metric associated with the vague topology and thus we will retain relative compactness.
+The main argument relies on the observation that particles with levels lower than some threshold $\overline{U}_{N, \delta}$  have regulated level increments of order $\delta$ over any small time interval of length $r$ given large enough $\lambda$.
+As a result, we can evaluate our level process against test functions $(g_n)_{n=1,..,N}$ with cut off smaller than $\overline{U}_{N, \delta}$.
+
+\begin{lemma} \label{tightness of levels} For fixed $\mathfrak{u}\in \mathcal{U}$,
+$\{(U^{N}_{\tau_\mathfrak{u}}(t))_{t \geq 0}, \lambda >0\}$ is relatively compact in 
+$\mathcal{D}_{[0,\infty]}[0,\infty )$ where $[0,\infty]$ is equipped with the metric $\mathfrak{d}$ for the vague topology in $[0,\infty]$ (see Theorem  \ref{Vague times Euclidean is Polish}).
+\end{lemma}
+
+\begin{proof}
+
+\textbf{Introducing a cutoff range:} It suffices to show that for any $\delta > 0$ and for any particle $\mathfrak{u} \in \mathcal{U}$, there exists small enough  $r>0$ such that $\mathbb{E}[\mathfrak{d}(U^{N}_{\tau_{\mathfrak{u}}}(t+r),U^{N}_{\tau_{\mathfrak{u}}}(t))|{\cal F}_t^{
+\eta}]< \delta$. \\
+For this, pick $K_{\delta} \in \mathbb{N}$ such that $\frac{1}{2^{K_{\delta}}} < \delta/2$. then we have that 
+\begin{multline}
+\mathfrak{d}(U^{N}_{\tau_{\mathfrak{u}}}(t+r),U^{N}_{\tau_{\mathfrak{u}}}(t))\leq  \sum_{n=1}^{K_{\delta}}\frac{1 \wedge |g_n(U^{N}_{\tau_{\mathfrak{u}}}(t+r))-g_n(U^{N}_{\tau_{\mathfrak{u}}}(t))|}{2^n} +  \delta/2.
+\end{multline}
+Now it suffices to prove that for small enough $r$, $|g_n(U^{N}_{\tau_{\mathfrak{u}}}(t+r))-g_n(U^{N}_{\tau_{\mathfrak{u}}}(t))| < \delta / (2K_{\delta})$.
+
+Pick $\overline{U}_{K_{\delta}, \delta}>0$ large enough such that $\text{supp}(g_n)\subset [0,\overline{U}_{K_{\delta}, \delta}]$ for all $n=1,..,K_{\delta}$.
+Since we picked $g_n$ to be continuous and differentiable with compact support, by Mean Value Theorem we have that
+$$|g_n(U^{N}_{\tau_{\mathfrak{u}}}(t+r))-g_n(U^{N}_{\tau_{\mathfrak{u}}}(t))|<C'_{g_1,..,g_{K_\delta}}(|U^{N}_{\tau_{\mathfrak{u}}}(t+r)-U^{N}_{\tau_{\mathfrak{u}}}(t)|\wedge \overline{U}_{K_{\delta}, \delta}), $$
+uniformly over $n=1,..,K_{\delta}$ for some constant $C'_{g_1,...,g_{K_{\delta}}}$.
+Note that it suffices to consider $|U^{N}_{\tau_{\mathfrak{u}}}(t+r)-U^{N}_{\tau_{\mathfrak{u}}}(t)|\wedge \overline{U}_{K_{\delta}, \delta}$ because $g_n(u)=g_n(\overline{U}_{K_{\delta}, \delta})=0$ for all $u > \overline{U}_{K_{\delta}, \delta}$.
+We proceed to bound $|U^{N}_{\tau_{\mathfrak{u}}}(t+r)-U^{N}_{\tau_{\mathfrak{u}}}(t)|$ given that $U^{N}_{\tau_{\mathfrak{u}}}(t) < \overline{U}_{K_{\delta}, \delta}$.
+
+\textbf{Controlling downward drift:} We first consider the case where $\tau_{\mathfrak{u}}< t$, i.e. the particle $\mathfrak{u}$ is born before time $t$. 
+We have that 
+\small
+\begin{equation}
+\begin{aligned}
+U^{N}_{\tau_{\mathfrak{u}}}(t+r)-U^{N}_{\tau_{\mathfrak{u}}}(t) =  &   \int_{t}^{(t+r)  }\frac{1}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon, \theta}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s),\Xi^{\varepsilon, \theta, \lambda}(s))}dV^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s)\\
+&+\int_{t}^{(t+r)  }\bigg(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon, \theta}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s),\Xi^{\varepsilon, \theta, \lambda}(s))U^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s)^2 - b_{\varepsilon, \theta, \lambda}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s),\Xi^{\varepsilon, \theta, \lambda}(s))U^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s)\bigg)ds,
+\end{aligned}
+\end{equation}
+\normalsize
+where the first term corresponds to positive jumps and the second term corresponds to the evolution according to a quadratic differential equation.
+To control the downward drift of our levels from the quadratic evolution,
+we neglect all positive drift and obtain
+\begin{equation}
+\begin{aligned}
+\mathbb{E}[U^{N}_{\tau_{\mathfrak{u}}}(t+r)-U^{N}_{\tau_{\mathfrak{u}}}(t)] \geq   &   - \int_{t}^{(t+r)  } G(\varrho_{\varepsilon}*\Xi^{\varepsilon, \theta, \lambda}_s(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s))) U^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s)ds\\
+\geq& - rC_G\overline{U}_{K_{\delta}, \delta}.
+\end{aligned}    
+\end{equation}
+
+\textbf{Controlling Upward Drift with Comparison Principle:}
+On the other hand, the positive increments are due to jumps and the quadratic evolution. To control the quadratic upward drift, we apply comparison principle.
+
+The process $(W_s)_{s \geq 0}:=(U^{N}_{\tau_{\mathfrak{u}}}(t+s)\wedge \overline{U}_{K_{\delta}, \delta})_{s \geq 0}$ satisfy the differential inequality with jumps of the form 
+\begin{equation}
+\begin{aligned}
+ dW_s \leq& \frac{1}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon, \theta}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s),\Xi^{\varepsilon, \theta, \lambda}(s))}dV^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s)\wedge \overline{U}_{K_{\delta}, \delta}\\
+ &+\bigg(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon, \theta}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s),\Xi^{\varepsilon, \theta, \lambda}(s))W_s^2 - b_{\varepsilon, \theta, \lambda}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s),\Xi^{\varepsilon, \theta, \lambda}(s))W_s\bigg)\mathbbm{1}_{W_s \leq \overline{U}_{K_{\delta}, \delta}}ds,
+\end{aligned}
+\end{equation}
+with initial condition $W_0=U^{N}_{\tau_{\mathfrak{u}}}(t)\leq \overline{U}_{K_{\delta},\delta}$.
+The first term is due to the fact that all jumps of $(U^{N}_{\tau_{\mathfrak{u}}}(t+s))_{s \geq 0}$ that lands above $\overline{U}_{K_{\delta}, \delta}$ will result in  the process $(W_s)_{s \geq 0}$ landing on $\overline{U}_{K_{\delta}, \delta}$.
+The indicator function in the second term is due to the process staying at $\overline{U}_{K_{\delta}, \delta}$ once the process hit the value.
+
+Note that we have $\gamma^{\mathfrak{m}}_{\varepsilon, \theta}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s),\Xi^{\varepsilon, \theta, \lambda}(s)) \leq (1+C_G),$ and $- b_{\varepsilon, \theta, \lambda}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s),\Xi^{\varepsilon, \theta, \lambda}(s)) \leq \varrho_{\varepsilon}*\Xi^{\varepsilon, \theta, \lambda}_{s}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s)).$ Furthermore, recall that $V_{\tau}(t)=\sum_{k=1}^{m}v_k\mathbbm{1}_{[0, \tau_k]}  (t)  $ and all jumps are at most of size $\overline{U}_{K_{\delta}, \delta}$ for the process $(W_s)_{s \geq 0}$, By the comparison principle, for any $s \geq 0$, $W_s-W_0$ is bounded above by the increment $\widetilde{W}_s-\widetilde{W}_0$ of a process $(\widetilde{W}_s)_{s \geq 0}$ which satisfies
+\begin{equation}
+\begin{aligned}
+ d\widetilde{W}_s =& \overline{U}_{K_{\delta}, \delta} dN_{\tau_\mathfrak{u}}(s) +\bigg(\lambda^{-1} \theta (1+C_G)\overline{U}_{K_{\delta}, \delta}^2 + \varrho_{\varepsilon}*\Xi^{\varepsilon, \theta, \lambda}_{s}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s)) \overline{U}_{K_{\delta}, \delta}\bigg)ds.
+\end{aligned}
+\end{equation}
+Here $(N_{\tau_\mathfrak{u}}(s))_{s \geq 0}$ is the Poisson point process $N_{\tau_\mathfrak{u}}(t)=\sum_{k=1}^{m}\mathbbm{1}_{[0, \tau_k]}  (t) $ with rate $1$ and $\widetilde{W}_0 = \overline{U}_{K_{\delta}, \delta}$.
+
+Taking expectations, we have that 
+\begin{equation}
+\begin{aligned}
+\mathbb{E}[\widetilde{W}_{t+r}-\widetilde{W}_t] \leq &   \overline{U}_{K_{\delta}, \delta}r + \lambda^{-1} \theta (1+C_G)\overline{U}_{K_{\delta}, \delta}^2r + \overline{U}_{K_{\delta}, \delta} \int_{t}^{t+r}\mathbb{E}\left[\varrho_{\varepsilon}*\Xi^{\varepsilon, \theta, \lambda}_{s}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s))\right]ds\\
+\leq & \overline{U}_{K_{\delta}, \delta}r + \lambda^{-1} \theta (1+C_G)\overline{U}_{K_{\delta}, \delta}^2r +\overline{U}_{K_{\delta}, \delta} \int_{t}^{t+r}\left(C_0
++   K' e^{C_G s}\right)e^s ds \\
+= & \overline{U}_{K_{\delta}, \delta}r + \lambda^{-1} \theta (1+C_G)\overline{U}_{K_{\delta}, \delta}^2r +\overline{U}_{K_{\delta}, \delta} +(C_0e^t+\frac{C_0K'}{C_G+1}e^{C_G+1})(e^{r}-1).
+\end{aligned}
+\end{equation}
+
+\textbf{Controlling Increments by Birth Events:}
+Now consider the scenario where $t > \tau_u$, i.e.
+the particle $\mathfrak{u}$ has not been born at time $t$.
+Denote $\mathcal{B}^{N}_{\mathfrak{u}}([t,t+r  ])$ to be the event that particle $\mathfrak{u}$ is born between $[t,t+r  ]$ with level smaller than $U_{K_{\delta}, \delta}$.
+In this case,
+\begin{multline}
+ |g_n(U^{N}_{\tau_{\mathfrak{u}}}(t+r))-g_n(U^{N}_{\tau_{\mathfrak{u}}}(t))|\\
+ =g_n(U^{N}_{\tau_{\mathfrak{u}}}(t+r))\times\mathbbm{1}_{\mathcal{B}^{N}_{\mathfrak{u}}([t,t+r  ])}\\
+ < C_{g_1,...,g_n}\times \mathbbm{1}_{\mathcal{B}^{N}_{\mathfrak{u}}([t,t+r  ])},   
+\end{multline}
+for some uniform bound $C_{g_1,...,g_n}$ over $\{||g_n||_{\infty}: n =1,...,N \}$.
+It suffices therefore to show that the probability for a particle $\mathfrak{u}$ to be born or gives birth in some time interval of length less than or equal to $r$ can be arbitrarily small given small enough $r$.
+Let $\mathcal{N}^{N}_{\mathfrak{u}}([t,t+r  ])$ to be the number of particles born between $[t,t+r]$ with level smaller than $U_{K_{\delta}, \delta}$.
+Then
+\begin{equation}
+\begin{aligned}
+\mathbb{P}[\mathcal{B}^{N}_{\mathfrak{u}}([t,t+r  ])]  \leq&  \mathbb{P}[\mathcal{N}^{N}_{\mathfrak{u}}([t,t+r  ]) \geq 1]\\
+\leq & \mathbb{E}[\mathcal{N}^{N}_{\mathfrak{u}}([t,t+r  ]) ].
+\end{aligned}
+\end{equation}
+Recall that we have bounds over the total mass of the particle systems, so at time $t$, the expected number of particles alive in the $N$-th stage of scaling is bounded above $\lambda_NC_0e^{C_Gt}$ (with $\lambda_N=N$).
+The particles have levels that are independently and uniformly distributed between $[0, \lambda_N]$.
+Therefore, the expected number of particles with levels between $[0,U_{K_{\delta}, \delta}]$ is $U_{K_{\delta}, \delta}C_0e^{C_Gt}$.
+The number of births within an interval of length $r$ is a sum of Poisson random variables, and so we have
+$$\mathbb{E}[\mathcal{N}^{N}_{\mathfrak{u}}([t,t+r  ]) ]=U_{K_{\delta}, \delta}C_0e^{C_Gt}r.$$
+
+\textbf{Conclusion:} Combining all of the above results, we have that for any $\delta > 0$,
+\begin{equation}
+\begin{aligned}
+\mathbb{E}[\mathfrak{d}(U^{N}_{\tau_{\mathfrak{u}}}(t+r),U^{N}_{\tau_{\mathfrak{u}}}(t))] \leq & \mathbb{E}\left[\sum_{n=1}^{K_{\delta}}\frac{1 \wedge |g_n(U^{N}_{\tau_{\mathfrak{u}}}(t+r))-g_n(U^{N}_{\tau_{\mathfrak{u}}}(t))|}{2^n}\right] +  \delta/2\\
+\leq &\mathbb{E}\left[\sum_{n=1}^{K_{\delta}}\frac{1 \wedge |g_n(U^{N}_{\tau_{\mathfrak{u}}}(t+r))-g_n(U^{N}_{\tau_{\mathfrak{u}}}(t))|}{2^n}: \tau_{\mathfrak{u}} \leq t \right]\\
+& + \mathbb{E}\left[\sum_{n=1}^{K_{\delta}}\frac{1 \wedge |g_n(U^{N}_{\tau_{\mathfrak{u}}}(t+r))-g_n(U^{N}_{\tau_{\mathfrak{u}}}(t))|}{2^n}: \tau_{\mathfrak{u}} \geq t \right] + \delta/2\\
+\leq & C'_{g_1,...,g_n}\bigg(\overline{U}_{K_{\delta}, \delta}r + \lambda^{-1} \theta (1+C_G)\overline{U}_{K_{\delta}, \delta}^2r\\
+& \qquad \qquad  +\overline{U}_{K_{\delta}, \delta} +(C_0e^t+\frac{C_0K'}{C_G+1}e^{C_G+1})(e^{r}-1)\bigg)\\
+& + C'_{g_1,...,g_n}U_{K_{\delta}, \delta}C_0e^{C_Gt}r+\delta/2\\
+< & \delta 
+\end{aligned}    
+\end{equation}
+for small enough $r>0$. In particular, this choice of $r$ is independent of $\varepsilon, \theta, \lambda$. Therefore we have proved tightness of our level processes by \cite{EK} Theorem 3.8.6.
+\end{proof}
+\subsubsection{Convergence in $\mathcal{D}_{[0,\infty)}\left(\mathcal{N}_f(\mathbb{R}^d \times [0, \infty)\right)$ to $(\xi^{ \infty}_t)_{t \geq 0}$, where $\mathcal{N}_f(\mathbb{R}^d \times [0, \infty)$}
+Now that we have proven tightness for individual level and spatial trajectories, by Corollary \ref{cor: convergence in p implies convergence in p-infty}, Lemma \ref{lem: Countable Implies Vague} and Theorem \ref{teo: Theorem A12 Kurtz Rodrigues generalised}, we have proved that the particle system $(\xi^{\varepsilon_N, \theta_N,\lambda_N}_t)_{t \geq 0}$ converges in $\mathcal{D}_{[0,\infty)}\left(\mathcal{N}_f(\mathbb{R}^d \times [0, \infty)\right)$ to $(\xi^{ \infty}_t)_{t \geq 0}$, where $\mathcal{N}_f(\mathbb{R}^d \times [0, \infty)$ is equipped with the $\mathfrak{p}^{wv}$-topology.
+Furthermore, its spatial projection $(\overline{\eta}^{\varepsilon_N, \theta_N,\lambda_N}_t)_{t \geq 0}$ converges to $(\overline{\eta}^{\infty}_t)_{t \geq 0}$ in $\mathcal{D}_{[0,\infty)}\left(\mathcal{M}_f(\mathbb{R}^d \right)$, where $\mathcal{M}_f(\mathbb{R}^d)$ is equipped with the weak topology.
+
+In the next section, we will show how we identify the limit process.
 
@@
 \end{proof}
+\section{Topological Results on Lookdown Representations}
+\label{sec: Topologies on Lookdown}
+
+\subsection{Euclidean-Vague Topology on $\mathbb{R}^d \times [0,\infty]$}\label{sec: Convergence in Product Topology}
+We first define a topology on $\mathbb{R}^d \times [0,\infty]$ which is Euclidean on $\mathbb{R}^d$ and vague in $[0,\infty]$.
+\begin{definition}
+We define the topology $\mathfrak{p}$ on $\mathbb{R}^d \times [0,\infty]:$
+we say $(x_n,u_n) \to (x,u)$ in topology $\mathfrak{p}$ if 
+\begin{enumerate}
+    \item $|x_n-x| \to 0$ in $\mathbb{R}^d$.
+    \item  For all $g \in C_{c}([0,\infty])$, the space of continuous functions with compact support on $[0,\infty]$, $g(u_n) \to g(u).$ Since this is the vague convergence for $(\delta_{u_n})_{n \in \mathbb{N}}$ we will abuse a bit the notation and denote this by the symbol $u_n \xrightarrow{vague} u$.
+\end{enumerate}
+\end{definition}
+
+In other words, our topology is Euclidean in space $\mathbb{R}^d$ and vague in levels in $[0,\infty]$.
+\begin{lemma}\label{Vague times Euclidean is Polish}
+The space $\mathbb{R}^d \times [0,\infty]$ under topology $\mathfrak{p}$ is Polish.
+\end{lemma}
+\begin{proof}
+The space $C_c([0,\infty])$ is dense, so we pick a countable dense subset $S:=\{h_n: n \in \mathbb{N}\} \subset C^{1}_c([0,\infty])$ and define the metric $\mathfrak{d}$ such that $\mathfrak{d}(u,v)=\sum_{n=1}^{\infty}\frac{1 \wedge |h_n(u)-h_n(v)|}{2^n}$.
+
+Assume that $u_n \xrightarrow{vague} u$.
+Pick arbitrary $\delta>0$ and take $N$ large enough such that $\frac{1}{2^N}<\delta/2$.
+Furthermore, pick $n$ large enough such that $\inf_{i=1,2,...,N}|h_i(u_n)-h_i(u)|<\delta/2$.
+From this we immediately have that $\mathfrak{d}(u_n,u)<\delta$.
+Thus $\mathfrak{d}(u_n,u) \to 0$.
+
+Conversely assume that $\mathfrak{d}(u_n,u) \to 0$.
+For any $h \in \mathcal{C}^{1}_c([0,\infty])$ and for any $\delta>0$, pick $g_N$ such that $||h-h_N||_{\infty}<\delta /3$ and $n$ large enough such that $\mathfrak{d}(u_n,u)< \frac{\delta}{3 \times 2^N}$.
+Then $|h(u)-h(u_n)|< |h(u)-h_N(u)|+|h_N(u)-h_N(u_n)|+|h_N(u_n)-h(u_n)|<\delta$, and so $h(u_n) \to h(u)$.
+
+Finally, one can easily check that $\mathbb{Q}$ is a countable dense set in $[0,\infty]$ equipped with the metric $\mathfrak{d}$.
+Defining the metric $d_{\mathfrak{p}}$
+by
+$$d_{\mathfrak{p}}((x_1,u_1),(x_2,u_2))=||x_1-x_2||+\mathfrak{d}(u_1,u_2),$$
+we can show easily that
+convergence in $d_{\mathfrak{p}}$
+is equivalent to convergence in 
+$\mathfrak{p}$ topology.
+\end{proof}
+
+\subsection{Weak-Vague Topology on Measures}\label{sec: Empirical Measure Topology}
+
+We now characterise the lookdown representation
+of our particle system
+as a measure on 
+$(\mathbb{R}^d \times [0, \infty], \mathfrak{p})$.
+We endow the vague topology
+on these measures for
+convergence of lookdown representations.
+We refer to Theorem A.23 and Theorem A.24 in \cite{kallenberg1997foundations}.
+
+First of all,
+as $(\mathbb{R}^d \times [0, \infty], \mathfrak{p})$
+is Polish,
+the family of $C^{+}_K$ of continuous functions
+$$f: \mathbb{R^d} \times [0, \infty] \to \mathbb{R}^{+}$$
+with compact support
+is separable in the uniform metric. 
+The sets $K_n =[-n, n]^d \times [0,n]$ clearly forms a sequence of compact sets and $K_n \uparrow \mathbb{R^d} \times [0, \infty]$.
+
+We denote $\mathcal{M}(\mathbb{R^d} \times [0, \infty])$ as the class of measures on $\mathbb{R^d} \times [0, \infty]$ that are 
+locally finite (i.e. bounded on bounded intervals),
+and write $\pi_B, \pi_f$ 
+for the mappings 
+$\mu \to \mu B$, $\mu \to \mu f := \int f d\mu$,
+respectively,
+on $\mathcal{M}(\mathbb{R^d} \times [0, \infty])$.
+
+The \textit{vague topology} in $\mathcal{M}(\mathbb{R^d} \times [0, \infty)$ is generated by the maps $\pi_f, f \in C^{+}_K$, and 
+we write the cague convergence of $\mu_n$ toward $\mu$
+as $\mu_n \xrightarrow{v} \mu$.
+
+Taking $S= \mathbb{R^d} \times [0, \infty]$
+in Theorem A.23
+in \cite{kallenberg1997foundations},
+we have
+\begin{theorem}[vague topology]
+\label{teo: Kallenberg vague results}
+
+The following holds:
+\begin{enumerate}
+    \item $\mathcal{M}(\mathbb{R^d} \times [0, \infty])$ is a Polish space in the vague topology
+    \item A set $A \subset \mathcal{M}(\mathbb{R^d} \times [0, \infty])$ is vaguely relatively compact iff 
+    $\sup_{\mu \in A} \mu f < \infty$ for all $f \in C^{+}_K$
+    \item if $\mu_n \xrightarrow{v} \mu$ and a set $B$ is finite with $\mu \partial B = 0$, then $\mu_n B \to \mu B$.
+\end{enumerate}
+
+\end{theorem}
+
+\begin{corollary}
+For any arbitrary $N,K>0$, the set $$\mathcal{M}_K([-N,N]^d \times [0,N]):= \{\mu \in \mathcal{M}(\mathbb{R^d} \times [0, \infty]): \mu([-N,N]^d \times [0,N]) \leq K\}$$   
+is a compact subset in 
+$\mathcal{M}(\mathbb{R^d} \times [0, \infty])$ 
+under the vague topology.
+\end{corollary}
+\begin{proof}
+For any function $f \in C^{+}_K$, it is compactly supported and
+so there exists a constant $C_f > ||f||_{\infty}$.
+As a result, 
+$$\sup_{\mu \in \mathcal{M}_K([-N,N]^d \times [0,N])} \mu f < C_f \times \mu \{ supp(f) \cap [-N,N]^d \times [0,N]\} \leq C_f K < \infty.$$
+
+Since $f$ is arbitrary, by (ii) of Theorem \ref{teo: Kallenberg vague results}, 
+the set
+$\mathcal{M}_K([-N,N]^d \times [0,N])$
+is vaguely relatively compact.
+
+We now prove that $\mathcal{M}_K([-N,N]^d \times [0,N])$ is a closed subset of $\mathcal{M}(\mathbb{R^d} \times [0, \infty])$.
+
+Since $[-N,N]^d \times [0,N]$ is finite, by part 3 of Theorem \ref{teo: Kallenberg vague results},
+for any sequence in $(\mu_n)_{n \in \mathbb{N}}$ in  $\mathcal{M}_K([-N,N]^d \times [0,N])$ that converges vaguely to $\mu$ in 
+$ \mathcal{M}(\mathbb{R^d} \times [0, \infty])$, 
+$$K \geq \mu_n([-N,N]^d \times [0,N]) \to \mu([-N,N]^d \times [0,N]).$$
+Therefore, $\mu \in \mathcal{M}_K([-N,N]^d \times [0,N])$.
+As a result, $\mathcal{M}_K([-N,N]^d \times [0,N])$ is closed and relatively vaguely compact, so it is vaguely compact.
+\end{proof}
+
+\begin{definition}
+We define $\mathfrak{G}_{\leq 1}$ to be the set of functions $g \in \mathcal{C}(\mathbb{R}^d \times [0, \infty) \to \mathbb{R})$ such that 
+$g(\cdot, u) \in \mathcal{C}_{0}(\mathbb{R}^d)$ for all $u \geq 0$, and there exists some $C_g>0$, such that $g(x,u)=1$ for all $u \geq C_g$.
+\end{definition}
+
+\begin{lemma}\label{lem: Dense set for test functions on empirical measures} For $g \in \mathfrak{G}_{\leq 1}$, define $F_g(\xi):= \exp(-\langle \log g, \cdot \rangle )$. The set of functions 
+$$\left\{\sum_{m=1}^{N}a_m F_{g_m}(\cdot) ~~|~~ g_1,...,g_N \in \mathfrak{G}_{\leq 1}\right\}$$
+is dense in $C(\mathcal{M}(\mathbb{R^d} \times [0, \infty]),\mathbb{R})$.
+\end{lemma}
+\begin{proof}
+Direct application of Stone-Weierstrass Theorem.
+These finite combinations are closed under addition by construction, and they are closed under multiplication as $F_{g_1}(\cdot) \times F_{g_2}(\cdot):=F_{g_1 \times g_2}(\cdot)$.
+Thus we have a subalgebra that also clearly separates points and vanishes nowhere.
+\end{proof}
 
 \bibliographystyle{plainnat}
-\bibliography{refs.bib}
+\bibliography{refs.bib,plr_refs.bib}
 

### 2022-06-15 forwards-and-backwards.tex
Update on Overleaf.

@@
 $$
-    q_\theta^\mathfrak{m}(x, dy)
+    q_\theta^\mathfrak{m}(x,\eta,  dy)
     :=
@@
     \lim_{N \to \infty}
-    \theta \int (f(y) - f(x)) q_\theta^\mathfrak{m}(x, dy)
+    \theta \int (f(y) - f(x)) q_\theta^\mathfrak{m}(x, \eta, dy)
     &=
@@
     Under the assumptions of Theorem~\ref{thm:nonlocal_convergence},
-    if the limit is deterministic (i.e., $\theta / N \to \alpha = 0$),
+    if the limit is deterministic (i.e., $N^{-1}\theta \to \alpha = 0$),
     then any limit $\eta_t$ is a weak solution to the nonlocal partial differential equation
@@
 The mean measure is a product of Lebesgue measure on the first two coordinates,
-$q(0, \cdot)$ on $\IR^d$, and $(\delta_0 + \delta_1)/2$ on $\{0, 1\}$.
+the density of the standard Gaussian $N(0,1)$ on $\IR^d$, and $(\delta_0 + \delta_1)/2$ on $\{0, 1\}$.
 It will also be convenient
@@
 although the precise order of this enumeration is irrelevant.
-If $(t, v, y, \kappa)$ is the $j^\text{th}$ point in $\Pi_a$,
+If $(t, v, z, \kappa)$ is the $j^\text{th}$ point in $\Pi_a$,
 then $t$ will determine possible birth times,
 $v$ will determine levels of the offspring,
-$y$ will give the spatial displacement of the offspring relative to the parent,
+$z$ will give the spatial displacement of the offspring relative to the parent,
 $\kappa$ will be used to determine whether parent or offspring are assigned the new level,
@@
 Potential reproduction events occur at times $\tau_a + s$
-for each point $(s, v, y, \kappa) \in \Pi_a$.
+for each point $(s, v, w, \kappa) \in \Pi_a$.
 We say `potential' since if the resulting level is greater than $N$,
@@
 the new label is $a \concat j$, the (potential) birth time is $\tau_{a \concat j} = \tau_a + s$.
+Similarly, the potential birth location is 
+$$y(z) = \frac{1}{\theta}\meanq(X_a(\tau_{a+j}-)) + \frac{1}{\sqrt{\theta}}K(X_a(\tau_{a+j}-))z,$$
+where $K(x)K^{T}(x)=\covq(x)$.
+
 For convenience define
@@
 
+Finally, we write $S(\tau_{[a]_k},t):=[\tau_{[a]_k},t]\times[0,\infty)\times\mathbb{R}^d \times \{0,1\}$.
 Under this notation, for $t>\tau_{[a]_k}$,
@@
 \kappa_{[a]_i} y_{[a]_i} \ind_{U_{[a]_i}(\tau_{[a]_i}) < N}\\
-&+\int_{\tau_{[a]_k}}^{t}
-(1-\kappa)y
+&+\int_{S(\tau_{[a]_k},t)}
+(1-\kappa)y(z)
 \ind_{ \{
@@
       } 
-\Pi_{[a]_k}(dsdvdyd\kappa),
+\Pi_{[a]_k}(dsdvdzd\kappa),
 \end{aligned}    
@@
 with birth time $\tau_{a \concat j} = \tau_a + t$,
-location $X_{a \concat j}(\tau_a + t) = X_a(tau_a + t)$, and level
+location $X_{a \concat j}(\tau_a + t) = X_a(\tau_a + t)$, and level
 $$
@@
     \begin{align}
+        \label{eq: Growth function bound on running sup}
         \IE\left[
@@
 \end{equation}
-As $\theta / N \to \alpha$ as $N \to \infty$,
+As $N^{-1}\theta \to \alpha$ as $N \to \infty$,
 there exists some $K'>0$ such that 
-$\sup_{\theta > \theta_0} \theta / N < K'$.
+$\sup_{\theta > \theta_0} N^{-1}\theta < K'$.
 An application of Markov's inequality proves that
@@
 % % % % % % % % % % % % %
-\subsection{Tightness of the lookdown process}
+\subsection{Tightness of the Lines of Descent}
     \label{sec:lookdown_tightness_proofs}
@@
 as a forward-in-time process.
-
-In Appendix \ref{sec: Topologies on Lookdown},
-we will prove that
-tightness of the whole lookdown process
-holds given
-tightness of 
-all ancestral lineages
-in a countable product topology.
 
@@
 \begin{lemma} \label{lem: tightness of individual spatial trajectory}
-For fixed $a=(a_0,a_1,..,a_k)$,
-$\{(X^{N}_{a}(t))_{t \geq \tau^{N}_a}: N \in \mathbb{N},  \}$ is relatively compact in 
+Assume that the jump kernel $q_\theta^\mathfrak{m}(x, \eta, dy)$ of the form
+$$
+    q_\theta^\mathfrak{m}(x,\eta,  dy)
+    :=
+    \frac{
+        r(y, \smooth{r} \eta(y)) q_\theta(x, dy)
+    }{
+        \int r(x, \smooth{r} \eta(z)) q_\theta(x, dz)
+    } 
+$$
+satisfies the inequalities
+\begin{align}
+   \sup_{\theta}\mathbb{E}\left[\limsup_{x, \eta} \theta \left| \int_{\mathbb{R}^d} (y-x) q^{\mathfrak{m}}_{ \theta}(x,\eta,dy) \right|\right] \leq & \quad \overline{\alpha},\\
+   \sup_{\theta}\mathbb{E}\left[\limsup_{x, \eta} \theta \int_{\mathbb{R}^d} |y-x|^2 q^{\mathfrak{m}}_{ \theta}(x,\eta,dy)\right]  \leq & \quad \overline{\beta}.
+\end{align}
+Furthermore, assume that the birth rate satisfies 
+$$\sup_{x, \eta}\gamma_{\theta}(x, \varrho_{\gamma}*\eta(x)) < C_G,$$ 
+then for fixed $a=(a_0,a_1,..,a_k)$,
+$\{(X^{N}_{a}(t))_{\tau^{N}_a\leq t < \sigma^{N}_{a}}: N \in \mathbb{N},  \}$ is relatively compact in 
 $D_{\mathbb{R}^d}[0,\infty )$ where $\mathbb{R}^d$ is equipped with the standard Euclidean metric. 
@@
 \begin{proof}
-We write $S_{t,r}:=(t,t+r  ]\times [0,\infty )\times [0,1]\times 
-\{0,1\}$ to be the region for the Poisson measure driving $(X^{N}_{a}(t))_{t \geq \tau_a}$ between time $t$ and $(t+r)$ and write $\tilde\Pi_{\tau_u}(ds,dv,dy,d\kappa):=\Pi_{\tau_u}(ds,dv,dy, d\kappa) - ds\times dv\times dy \times (\frac{1}{2}\delta_{0}+\frac{1}{2}\delta_{1})d\kappa$ to be the compensated Poisson point process of $\Pi_{\tau_u}$.
-For $t\geq\tau_\mathfrak{u}$, we can compute
+We write $S_{t,r}:=(t,t+r  ]\times [0,\infty )\times \mathbb{R}^d\times 
+\{0,1\}$ to be the region for the Poisson measure driving $(X^{N}_{a}(t))_{t \geq \tau_a}$ between time $t$ and $(t+r)$ and write $\tilde\Pi_{a}(ds,dv,dz,d\kappa):=\Pi_{a}(ds,dv,dz, d\kappa) - ds\times dv\times dz \times (\frac{1}{2}\delta_{0}+\frac{1}{2}\delta_{1})d\kappa$ to be the compensated Poisson point process of $\Pi_{a}$.
+For $\tau_a \leq t < t+r < \sigma_a$, we can compute
 \small
-\begin{eqnarray*}
-&&\mathbb{E}[|X^{N}_{\tau_{\mathfrak{u}}}(t+r )-X^{N}_{\tau_{\mathfrak{u}}}(t)|^2|{\cal F}_t^{
+\begin{align*}
+&\mathbb{E}[|X^{N}_{a}(t+r )-X^{N}_{a}(t)|^2|{\cal F}_t^{
 \eta}]\\
-&&= \mathbb{E}\left[\left|\int_{S_{t,r}}{\bf 1}_{\{U_{\tau_{\mathfrak{u}}}(s)+\frac v{2\lambda^{-1}\theta \gamma^{\mathfrak{m}}_\theta(X^{N}_{
-\tau_{\mathfrak{u}}}(s-),\overline{\eta}^{N}(s-))}<\lambda \}}\kappa 
-y\Pi_{\tau_{\mathfrak{u}}}(ds,dv,dy,d\kappa )\right|^2\Bigg|{\cal F}_t^{\eta}\right]\\
-&&\leq 2\mathbb{E}\left[\left|\int_{S_{t,r}}{\bf 1}_{\{v < 2 \theta \gamma^{\mathfrak{m}}_\theta(X^{N}_{
-\tau}(s-),\overline{\eta}^{N}(s-))\}}{\bf 1}_{\kappa =1}
-y\tilde\Pi_{\tau_{\mathfrak{u}}}(ds,dv,dy,d\kappa )\right|^2\Bigg|{\cal F}_t^{\eta}\right]\\
-&&\quad +2\mathbb{E}\left[\left|\int_{t}^{t+r}\int_{\{v < 2 \theta \gamma^{\mathfrak{m}}_\theta(X^{N}_{
-\tau_{\mathfrak{u}}}(s-),\overline{\eta}^{N}(s-))\}}\frac{1}{2}\left| \int_{\mathbb{R}^d} (y-X^{N}_{\tau}(s-)) q^{\mathfrak{m}}_{\theta, \varepsilon}(X^{N}_{\tau}(s-),\overline{\eta}^{N}(s-),dy) \right|
-dvds \right|^2\Bigg|{\cal F}_t^{\eta}\right]\\
-&&\leq 2\mathbb{E}\left[\int_{t}^{(t+r)   }\theta (1+C_G)\int_{{\mathbb{R}}^d}|y-X^{N}_{
-\tau_{\mathfrak{u}}}(s)|^2q^{\mathfrak{m}}_{\varepsilon,\theta}(X^{N}_{\tau_{\mathfrak{u}}}(s),\bar{\eta}^{\varepsilon,\theta,\lambda}(s-),dy)ds\Bigg|{\cal F}_t^{\eta}\right]\\
-&&\quad +2\mathbb{E}\left[\left|\int_{t}^{(t+r)    } \theta (1+C_G)\left|\int_{{\mathbb{R}}^d}
-(y-X^{N}_{\tau_{\mathfrak{u}}}(s))q^{\mathfrak{m}}_{\varepsilon,\theta}(X^{N}_{\tau_{\mathfrak{u}}}(s),
-\overline{\eta}^{N}(s),dy)\right|ds\right|^2\Bigg|{\cal F}_t^{\eta}\right]\\
-&&\leq 2r \overline{\beta}(1+C_G)+2(r \overline{\alpha}(1+C_G))^2.\end{eqnarray*}
+=& \mathbb{E}\left[\left|
+\int_{S_{t,r}}
+(1-\kappa)y(z)
+\ind_{ \{
+        U_{a}(\tau_{a}+s)
+        +\ell(X_{a}(\tau_{a}+s),y(z),\eta_{a}(\tau_{a}+s),v) < N
+        \}
+      } 
+\Pi_{a}(dsdvdzd\kappa)
+\right|^2
+\Bigg|{\cal F}_t^{\eta}\right]\\
+\leq&
+ 2\mathbb{E}\left[
+ \left|
+ \int_{S_{t,r}}
+ {\bf 1}_{\{v < 2  \theta \gamma_{\theta}(x, \eta) r_{\theta}(x + y, \eta) \}}{\bf 1}_{\kappa =1}
+y(z)
+\tilde\Pi_{a}(ds,dv,dy,d\kappa )
+\right|^2
+\Bigg|{\cal F}_t^{\eta}
+\right]\\
+&\quad +2\mathbb{E}\left[
+\left|
+\int_{t}^{t+r}\int_{\{v < 2\theta \gamma_{\theta}(x, \eta) r_{\theta}(x + y, \eta) \}}
+\frac{1}{2}\left| \int_{\mathbb{R}^d} (y-X^{N}_{\tau}(s-)) q^{\mathfrak{m}}_{\theta}(X^{N}_{\tau}(s-),\eta^{N}(s-),dy) 
+\right|
+dvds \right|^2
+\Bigg|{\cal F}_t^{\eta}
+\right]\\
+&\leq 
+2\mathbb{E}\left[
+\int_{t}^{(t+r)   }
+(1+C_G) \theta 
+\int_{{\mathbb{R}}^d}|y-X^{N}_{
+a}(s)|^2q^{\mathfrak{m}}_{\theta}(X^{N}_{a}(s),\eta^{N}(s),dy)ds
+\Bigg|{\cal F}_t^{\eta}\right]\\
+&\quad +2\mathbb{E}\left[
+\left|
+\int_{t}^{(t+r)}
+(1+C_G)\theta 
+\left|
+\int_{{\mathbb{R}}^d}
+(y-X^{N}_{a}(s))q^{\mathfrak{m}}_{\theta}(X^{N}_{a}(s),
+\eta^{N}(s),dy)
+\right|
+ds
+\right|^2
+\Bigg|{\cal F}_t^{\eta}\right]\\
+\leq& 2r \overline{\beta}(1+C_G)+2(r \overline{\alpha}(1+C_G))^2.
+\end{align*}
 \normalsize
 
-The first inequality uses the fact that $(A+B)^2 \leq 2A^2+2B^2$ as well as the definition of the transition kernel $H$.
-The second inequality holds because birth events occur at rate $2 \theta \gamma^{\mathfrak{m}}_{\theta}$ bounded above by $2\theta (1+C_G)$.
-The third inequality holds given the assumptions on the dispersal kernel.
-
-Finally, since $\overline{\eta}_0$ has compact support, we can take $t=\tau_u$ and apply Markov inequality to get that for every $\delta>0$, there exists $N_{\delta}>0$ such that
+The first inequality uses of the inequality $(A+B)^2 \leq 2A^2+2B^2$ as well as the fact that $(N-U_{a})N^{-1} \leq 1$.
+The second inequality holds 
+because birth events occur
+at rate $2\theta \gamma_{\theta}(x, \eta) r_{\theta}(x + y, \eta)$
+which is bounded above by $2\theta (1+C_G)$. The third inequality holds due to the assumptions on the dispersal kernel.
+
+Finally, since $\eta_0$ has compact support, we can take $t=\tau_u$ and apply Markov inequality to get that for every $\delta>0$, there exists $N_{\delta}>0$ such that
 \begin{equation}\label{eq: Compact Containment Condition for individual spatial motion}
-\sup_{\varepsilon, \theta, \lambda}\sup_{T>0}\mathbb{P}\left[|X^{N}_{\tau_{\mathfrak{u}}}(\tau_{\mathfrak{u}}+T)-X^{N}_{\tau_{\mathfrak{u}}}(\tau_{\mathfrak{u}})|>N_{\delta}\right]\leq   \frac{2r \overline{\beta}(1+C_G)+2(r \overline{\alpha}(1+C_G))^2}{N_{\delta}^2}  < \delta,
+\sup_{N>N_{\delta}}\sup_{T>0}\mathbb{P}\left[|X^{N}_{a}(\tau_{a}+T)-X^{N}_{a}(\tau_{a})|>N_{\delta}\right]\leq   \frac{2r \overline{\beta}(1+C_G)+2(r \overline{\alpha}(1+C_G))^2}{N_{\delta}^2}  < \delta,
 \end{equation}
@@
 \begin{remark}
-Note that under the assumptions laid out in Theorem \ref{teo: Non-local interaction Convergence} and Theorem \ref{teo: Local Interaction Convergence}, $r \equiv 1$, so 
-$$\gamma^{\mathfrak{m}}_{\varepsilon,\theta}(x, \overline{\eta})=\tilde\gamma_{\theta}(x, \varrho_{\varepsilon}*\overline{\eta})= 1+\frac{G(\varrho_{\varepsilon}*\overline{\eta})}{\theta} \leq (1+C_G)$$
-for all $\theta > 1$, and 
-$$q^{\mathfrak{m}}_{\varepsilon,\theta,\lambda}(x,\overline{\eta},dy)=q_{\theta}(x,dy).$$
-In particular, we have the inequalities
+Note that if we assume $r \equiv 1$, then 
+$q^{\mathfrak{m}}_{\theta}(x,\eta,dy)=q_{\theta}(x,dy).$
+In particular, if we let $q_{\theta}$ be the standard Gaussian normal, we have the inequalities
 \begin{align}
-   \sup_{\varepsilon, \theta}\limsup_{x, \overline{\eta}} \theta \left| \int_{\mathbb{R}^d} (y-x) q^{\mathfrak{m}}_{ \varepsilon, \theta}(x,\overline{\eta},dy) \right| =& \sup_{\theta}\limsup_{x} \theta \left| \int_{\mathbb{R}^d} (y-x) q_{\theta}(x,dy) \right| =  0,\\
-   \sup_{\varepsilon, \theta}\limsup_{x, \overline{\eta}} \theta \int_{\mathbb{R}^d} |y-x|^2 q^{\mathfrak{m}}_{ \varepsilon, \theta}(x,\overline{\eta},dy)  =& \sup_{\theta}\limsup_{x} \theta \int_{\mathbb{R}^d} |y-x|^2 q_{\theta}(x,dy) =  1,
+   \sup_{\theta}\limsup_{x, \eta} \theta \left| \int_{\mathbb{R}^d} (y-x) q^{\mathfrak{m}}_{ \theta}(x,\eta,dy) \right| =& \sup_{\theta}\limsup_{x} \theta \left| \int_{\mathbb{R}^d} (y-x) q_{\theta}(x,dy) \right| =  0,\\
+   \sup_{\theta}\limsup_{x, \eta} \theta \int_{\mathbb{R}^d} |y-x|^2 q^{\mathfrak{m}}_{ \theta}(x,\eta,dy)  =& \sup_{\theta}\limsup_{x} \theta \int_{\mathbb{R}^d} |y-x|^2 q_{\theta}(x,dy) =  1,
 \end{align}
 as the last term can be expressed as $\theta \mathbb{E}_{x}[(B_{1/\theta}-x)^2]=1$.
-As a result, Lemma \ref{lem: tightness of individual spatial trajectory} holds for the setting in Theorem \ref{teo: Non-local interaction Convergence} and Theorem \ref{teo: Local Interaction Convergence}.
+
+As a result, we have tightness for all populations with unbiased isotropic dispersal.
+
+Furthermore, the assumption on $\gamma$ is natural as we typically assume an uniform upper bound on the total fecundity rate, i.e.
+$\sup_{u \geq 0} u\gamma(x,u) < C$.
 \end{remark}
@@
 \subsubsection{Tightness of Level Processes}
+We have now proved that the spatial trajectories of a line of descent during its lifetime is relatively compact as $N \to \infty$.
+However, we will still need to show that the level process is also well controlled, i.e.
+a line of descent with an initial level smaller than $K << N$ will have a level larger than $N$ in very small time-scale with very low probability.
+This will then prevent a line of descent from dying instantaneously in the scaling limit.
+
+To make this precise, we must work in the vague topology.
 Proving tightness of the level process is slightly trickier as the levels of many particles will drift towards infinity in finite time.
 These particles however will not contribute to the metric associated with the vague topology and thus we will retain relative compactness.
-The main argument relies on the observation that particles with levels lower than some threshold $\overline{U}_{N, \delta}$  have regulated level increments of order $\delta$ over any small time interval of length $r$ given large enough $\lambda$.
+The main argument relies on the observation that particles with levels lower than some threshold $\overline{U}_{N, \delta}$  have regulated level increments of order $\epsilon$ over any small time interval of length $\delta t$ given large enough $N$.
 As a result, we can evaluate our level process against test functions $(g_n)_{n=1,..,N}$ with cut off smaller than $\overline{U}_{N, \delta}$.
 
-\begin{lemma} \label{tightness of levels} For fixed $\mathfrak{u}\in \mathcal{U}$,
-$\{(U^{N}_{\tau_\mathfrak{u}}(t))_{t \geq 0}, \lambda >0\}$ is relatively compact in 
-$\mathcal{D}_{[0,\infty]}[0,\infty )$ where $[0,\infty]$ is equipped with the metric $\mathfrak{d}$ for the vague topology in $[0,\infty]$ (see Theorem  \ref{Vague times Euclidean is Polish}).
+\begin{lemma} \label{tightness of levels} For fixed $a\in \mathcal{U}$, let $U^N_{a}(\tau_a)=U_0$, i.e. the level of the line of descent $a$ at birth is $U_0>0$.
+On top of the assumptions laid out in Lemma \ref{lem: tightness of individual spatial trajectory}, assume that 
+$$
+    \sup_{\theta}\mathbb{E}\left[ \sup_{x, \eta}b_\theta(x, \eta) \right]
+    :=
+    \sup_{\theta}
+    \theta 
+    \mathbb{E}\left[ \sup_{x, \eta} \left(
+    \gamma_\theta(x,\eta) \int_{\IR^d} r_\theta(y, \eta) q_\theta(x, dy)
+    -
+    \mu_\theta(x,\eta)
+    \right)\right] 
+    \leq C_G,
+$$
+and there exists some $C_F \geq 0$ such that
+\begin{align} 
+\begin{split}
+b_{\theta}(x, \eta)
+&=
+    \theta \gamma_{\theta}(x, \eta) \int_{\IR^d} \left( r_{\theta}(y, \eta) - r_{\theta}(x, \eta) \right) q_{\theta}(x, dy)
+    + F_{\theta}(x, \eta) \\
+& \geq - C_F \varrho_F*\eta(x)
+\end{split}
+\end{align}
+for all $x \in \mathbb{R}^d$ and  $\eta \in \mathcal{M}_{F}(\mathbb{R}^d)$.
+
+Then
+$\{(U^{N}_{a}(t))_{t \geq \tau_a}, N >0\}$ is relatively compact in 
+$\mathcal{D}_{[0,\infty]}[0,\infty )$, where $[0,\infty]$ is equipped with the metric $\mathfrak{d}$ for the vague topology in $[0,\infty]$ (see Theorem  \ref{Vague times Euclidean is Polish}).
 \end{lemma}
 
-\begin{proof}
-
-\textbf{Introducing a cutoff range:} It suffices to show that for any $\delta > 0$ and for any particle $\mathfrak{u} \in \mathcal{U}$, there exists small enough  $r>0$ such that $\mathbb{E}[\mathfrak{d}(U^{N}_{\tau_{\mathfrak{u}}}(t+r),U^{N}_{\tau_{\mathfrak{u}}}(t))|{\cal F}_t^{
-\eta}]< \delta$. \\
-For this, pick $K_{\delta} \in \mathbb{N}$ such that $\frac{1}{2^{K_{\delta}}} < \delta/2$. then we have that 
-\begin{multline}
-\mathfrak{d}(U^{N}_{\tau_{\mathfrak{u}}}(t+r),U^{N}_{\tau_{\mathfrak{u}}}(t))\leq  \sum_{n=1}^{K_{\delta}}\frac{1 \wedge |g_n(U^{N}_{\tau_{\mathfrak{u}}}(t+r))-g_n(U^{N}_{\tau_{\mathfrak{u}}}(t))|}{2^n} +  \delta/2.
-\end{multline}
-Now it suffices to prove that for small enough $r$, $|g_n(U^{N}_{\tau_{\mathfrak{u}}}(t+r))-g_n(U^{N}_{\tau_{\mathfrak{u}}}(t))| < \delta / (2K_{\delta})$.
-
-Pick $\overline{U}_{K_{\delta}, \delta}>0$ large enough such that $\text{supp}(g_n)\subset [0,\overline{U}_{K_{\delta}, \delta}]$ for all $n=1,..,K_{\delta}$.
+\begin{proof} Recall that for a fixed line of descent, the level process is determined only by the integral equation of the form 
+\begin{align*}
+&U^{N}_{a}(t+r)-U^{N}_{a}(t)\\
+=&\int_{t}^{t+r}
+\left(
+        \frac{\theta}{N} \gamma_{\theta}(X^N_{a}(s),\eta^N_s)
+        \int_{\IR^d} r_{\theta}(z,\eta^N_s) q_{\theta}(X^N_a(s),dz) U^N_a(s)^2
+        -
+        b_{\theta}(X^N_a(s),\eta^N_s) U^N_a(s)
+    \right)
+    ds.
+\end{align*}
+
+To control the level process, we consider two scenarios, one where the local density of the system between $[0,r]$ is never too big, i.e.
+$$h(r)=\sup_{x \in \mathbb{R}^d}\sup_{s\in [0,r]}\left\{\varrho_F*\eta^N_s(X^N_a(s)) \right\} \leq H_{\epsilon}(r),$$
+and otherwise.
+
+When the local density is smaller than $H_{\epsilon}$, we will show that the level grows steadily.
+Consequently, the level grows very fast and hit some level $\overline{U}_{K_{\epsilon}}$ very quickly only when the local density is larger than $H_{\epsilon}$.
+In this case, the effective increment in levels observed under the vague topology is bounded above by $\overline{U}_{K_{\epsilon}}$.
+We will first make this statement precise.
+We will also show that the probability of such event is very small.
+As a result, the level process is tight.
+
+We will first make our convergence statement precise under the vague topology. 
+We will then prove tightness in the high density scenario,
+and finally
+prove tightness in the scenario where population density is well controlled
+with a comparison principle.
+
+\textbf{Introducing a cutoff range:} It suffices to show that for any $\epsilon > 0$ and for any line of descent $a \in \mathcal{U}$, there exists small enough  $\delta t>0$ such that $\mathbb{E}[\mathfrak{d}(U^{N}_{a}(t+\delta t),U^{N}_{a}(t))|{\cal F}_t^{
+\eta}]< \epsilon$. \\
+For this, pick $K_{\epsilon} \in \mathbb{N}$ such that $\frac{1}{2^{K_{\epsilon}}} < \epsilon/2$. then we have that 
+\begin{equation}
+\mathfrak{d}(U^{N}_{a}(t+\delta t),U^{N}_{a}(t))\leq  \sum_{n=1}^{K_{\epsilon}}\frac{1 \wedge |g_n(U^{N}_{a}(t+\delta t))-g_n(U^{N}_{a}(t))|}{2^n} +  \epsilon/2. 
+\end{equation}
+Now it suffices to prove that for small enough $\delta t>0$, $|g_n(U^{N}_{a}(t+\delta t))-g_n(U^{N}_{a}(t))| < \epsilon / (2K_{\epsilon})$.
+
+Pick $\overline{U}_{K_{\epsilon}, \epsilon}>0$ large enough such that $\text{supp}(g_n)\subset [0,\overline{U}_{K_{\epsilon}, \epsilon}]$ for all $n=1,..,K_{\epsilon}$.
 Since we picked $g_n$ to be continuous and differentiable with compact support, by Mean Value Theorem we have that
-$$|g_n(U^{N}_{\tau_{\mathfrak{u}}}(t+r))-g_n(U^{N}_{\tau_{\mathfrak{u}}}(t))|<C'_{g_1,..,g_{K_\delta}}(|U^{N}_{\tau_{\mathfrak{u}}}(t+r)-U^{N}_{\tau_{\mathfrak{u}}}(t)|\wedge \overline{U}_{K_{\delta}, \delta}), $$
-uniformly over $n=1,..,K_{\delta}$ for some constant $C'_{g_1,...,g_{K_{\delta}}}$.
-Note that it suffices to consider $|U^{N}_{\tau_{\mathfrak{u}}}(t+r)-U^{N}_{\tau_{\mathfrak{u}}}(t)|\wedge \overline{U}_{K_{\delta}, \delta}$ because $g_n(u)=g_n(\overline{U}_{K_{\delta}, \delta})=0$ for all $u > \overline{U}_{K_{\delta}, \delta}$.
-We proceed to bound $|U^{N}_{\tau_{\mathfrak{u}}}(t+r)-U^{N}_{\tau_{\mathfrak{u}}}(t)|$ given that $U^{N}_{\tau_{\mathfrak{u}}}(t) < \overline{U}_{K_{\delta}, \delta}$.
-
-\textbf{Controlling downward drift:} We first consider the case where $\tau_{\mathfrak{u}}< t$, i.e. the particle $\mathfrak{u}$ is born before time $t$. 
-We have that 
-\small
+$$|g_n(U^{N}_{a}(t+\delta t ))-g_n(U^{N}_{a}(t))|<C_{g_1,..,g_{K_{\epsilon}}}(|U^{N}_{a}(t+\delta t)-U^{N}_{a}(t)|\wedge \overline{U}_{K_{\epsilon}, \epsilon}), $$
+uniformly over $n=1,..,K_{\epsilon}$ for some constant $C'_{g_1,...,g_{K_{\epsilon}}}$.
+Note that it suffices to consider $|U^{N}_{a}(t+\delta t)-U^{N}_{a}(t)|\wedge \overline{U}_{K_{\epsilon}, \epsilon}$ because $g_n(u)=g_n(\overline{U}_{K_{\epsilon}, \epsilon})=0$ for all $u > \overline{U}_{K_{\epsilon}, \epsilon}$.
+
+Therefore, it suffices to show that for all $\epsilon > 0$, there exists $\delta t>0$ small enough such that 
+\begin{equation}
+\mathbb{E}[C_{g_1,..,g_{K_{\epsilon}}}|U^{N}_{a}(t+\delta t)-U^{N}_{a}(t)|\wedge \overline{U}_{K_{\epsilon}, \epsilon} ~|~{\cal F}_t^{
+\eta} ] < \epsilon /2    
+\end{equation}
+uniformly over $N \geq N_0$.
+
+\textbf{Controlling high density events:}
+Recall that in Lemma \ref{lem: Compact Containment}, we have established compact containment for the total mass process. Therefore for any $\epsilon>0$ and $r>0$, there exists some large 
+\begin{equation}
+    \label{eq: Mass Bound Constant}
+H_{\epsilon}(r):=\frac{\epsilon}{2||\varrho_F||_{\infty}C(r) \overline{U}_{K_{\epsilon}}C_{g_1,..,g_{K_{\epsilon}}}}>0    
+\end{equation}
+
+such that 
+the event 
+$$A_{H_{\epsilon}}:= \left\{ \omega \in \Omega: \sup_{s\in [0,r]}\left\{\varrho_F*\eta^N_s(X^N_a(t+s)) \right\}(\omega) \geq H_{\epsilon}(r) \right\}$$
+satisfies
+\begin{equation}
+\limsup_{N \to \infty}\mathbb{P}\left[A_{H_{\epsilon}}\right]
+\leq  \frac{||\varrho_F||_{\infty}\mathbb{E}[\sup_{s\in [t,t+r]}\langle 1,  \eta^N_s \rangle ]}{H_{\epsilon}(r)}
+\leq  \frac{||\varrho_F||_{\infty}C(t+r)}{H_{\epsilon}(r)}
+< \frac{\epsilon}{2 \overline{U}_{K_{\epsilon}}C_{g_1,..,g_{K_{\epsilon}}}},
+\end{equation}
+where $(C(t))_{t \geq 0}$ is the growth function that bounds the expected value of the running supremum of the total mass in Equation \eqref{eq: Growth function bound on running sup}.
+
+As a result, for any $s < r$,
 \begin{equation}
 \begin{aligned}
-U^{N}_{\tau_{\mathfrak{u}}}(t+r)-U^{N}_{\tau_{\mathfrak{u}}}(t) =  &   \int_{t}^{(t+r)  }\frac{1}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon, \theta}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s),\Xi^{\varepsilon, \theta, \lambda}(s))}dV^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s)\\
-&+\int_{t}^{(t+r)  }\bigg(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon, \theta}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s),\Xi^{\varepsilon, \theta, \lambda}(s))U^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s)^2 - b_{\varepsilon, \theta, \lambda}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s),\Xi^{\varepsilon, \theta, \lambda}(s))U^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s)\bigg)ds,
+\mathbb{E}\left[\mathfrak{d}(U^{N}_{a}(t+s),U^{N}_{a}(t)) : A_{H_{\epsilon}} ~|~{\cal F}_t^{
+\eta} \right] & \leq  
+  \mathbb{E}\left[\sum_{n=1}^{K_{\epsilon}}\frac{1 \wedge |g_n(U^{N}_{a}(t+s))-g_n(U^{N}_{a}(t))|}{2^n} +  \epsilon/2: A_{H_{\epsilon}} ~\bigg|~{\cal F}_t^{
+\eta} \right]  \\
+ & \leq  \sum_{n=1}^{K_{\epsilon}}\frac{\mathbb{E}\left[C_{g_1,..,g_{K_{\epsilon}}} \overline{U}_{K_{\epsilon}, \epsilon}: A_{H_{\epsilon}} \right] }{2^n} +  \epsilon/2  \\
+& \leq  \sum_{n=1}^{K_{\epsilon}}\frac{C_{g_1,..,g_{K_{\epsilon}}} \overline{U}_{K_{\epsilon}, \epsilon}\mathbb{P}\left[ A_{H_{\epsilon}} \right] }{2^n} +  \epsilon/2 \\
+& \leq  \sum_{n=1}^{K_{\epsilon}}\frac{\epsilon /2 }{2^n} +  \epsilon/2 \\
+& < \epsilon.
 \end{aligned}
 \end{equation}
-\normalsize
-where the first term corresponds to positive jumps and the second term corresponds to the evolution according to a quadratic differential equation.
+
+\textbf{Controlling bounded density events:}
+We now consider $A_{H_{\epsilon}}^{c}$.
 To control the downward drift of our levels from the quadratic evolution,
@@
 \begin{aligned}
-\mathbb{E}[U^{N}_{\tau_{\mathfrak{u}}}(t+r)-U^{N}_{\tau_{\mathfrak{u}}}(t)] \geq   &   - \int_{t}^{(t+r)  } G(\varrho_{\varepsilon}*\Xi^{\varepsilon, \theta, \lambda}_s(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s))) U^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s)ds\\
-\geq& - rC_G\overline{U}_{K_{\delta}, \delta}.
+\mathbb{E}[U^{N}_{a}(t+r)-U^{N}_{a}(t)] \geq   &   - \mathbb{E}\left[\int_{t}^{(t+r)  } b_{\theta}(X^N_a(s),\eta^N_s) U^N_a(s)ds\right]\\
+\geq& - rC_G\overline{U}_{K_{\epsilon}, \epsilon}.
 \end{aligned}    
@@
 
-\textbf{Controlling Upward Drift with Comparison Principle:}
-On the other hand, the positive increments are due to jumps and the quadratic evolution. To control the quadratic upward drift, we apply comparison principle.
-
-The process $(W_s)_{s \geq 0}:=(U^{N}_{\tau_{\mathfrak{u}}}(t+s)\wedge \overline{U}_{K_{\delta}, \delta})_{s \geq 0}$ satisfy the differential inequality with jumps of the form 
+We can also control the upward drift by comparing our process $(U^N_{a}(\tau_a+r))_{r \geq 0}$ with another process $(W^N_a(r))_{r \geq 0}$, where 
+\begin{align*}
+&W^{N}_{a}(r)-W^{N}_{a}(0)\\
+=&\int_{0}^{r}
+\left(
+        \frac{\theta}{N} C_G W^N_a(s)^2
+        +
+        C_F H_{\epsilon}(r) W^N_a(s)
+    \right)
+    ds,
+\end{align*}
+with $H_{\epsilon}(r) > \sup_{s\in [0,r]}\left\{\varrho_F*\eta^N_s(X^N_a(s)) \right\}$,
+and $W^N_a(0)=U^N_a(\tau_a) = U_0 \leq \overline{U}_{K_{\epsilon}, \epsilon}$.
+
+This is because $\gamma_{\theta} \leq C_G$, $r_{\theta} \leq 1$, and $-b_{\theta}(x, \eta) \leq  C_F \varrho_F * \eta(x) < -C_F H_{\epsilon}(r)$.
+Therefore, the growth rate of the differential equation governing $(U^N_a(t+s))_{s \geq 0}$ is smaller than that of $(W^N_a(s))_{s \geq 0}$ at all time instances.
+
+Note that $(W^N_a(s))_{s \geq 0}$ can be solved explicitly and 
+\begin{equation}
+W^N_a(s) = \frac{C_F H_{\epsilon}(r) U_0 \exp(C_F H_{\epsilon}(r) s)}{C_F H_{\epsilon}(r)+C_G  N^{-1}\theta U_0(1- \exp(C_F H_{\epsilon}(r) s))}\leq \overline{U}_{K_{\epsilon}, \epsilon}    
+\end{equation}
+for 
+\begin{equation}
+    \label{eq: Bound on Level Hitting Time}
+s \leq  \frac{1}{C_F H_{\epsilon}(r)} \log\left\{
+1+
+\frac{C_F H_{\epsilon}(r)
+(\overline{U}_{K_{\epsilon}, \epsilon}
+-U_0)
+}
+{C_F H_{\epsilon}(r)U_0 +C_G  N^{-1}\theta \overline{U}_{K_{\epsilon}, \epsilon}    U_0}
+\right\}.
+\end{equation}
+As $\theta / N $ converges in the limit, we may take some constant $A$ such that for large enough $N$,
+the level process $(U^N_{a}(s))_{s \geq 0}$ will not hit  $\overline{U}_{K_{\epsilon}, \epsilon}$ as long as
+\begin{equation}
+s \leq  \frac{1}{C_F H_{\epsilon}(r)} \log\left\{
+1+
+\frac{C_F H_{\epsilon}(r)
+(\overline{U}_{K_{\epsilon}, \epsilon}
+-U_0)
+}
+{C_F H_{\epsilon}(r)U_0 +C_G  A \overline{U}_{K_{\epsilon},\epsilon}    U_0}
+\right\}:=T(U_0,\overline{U}_{K_{\epsilon},\epsilon},r).
+\end{equation}
+
+Note that $T$ only depends on the initial level $U_0$, the upper limit $\overline{U}_{K_{\epsilon}, \epsilon}$ and the bound on total mass $C(r)$ at time $r$, and is independent to $N$. 
+In particular, 
+\begin{equation}
+\label{eq: Compact Containment for Levels}
+\limsup_{N \to \infty}
+\mathbb{P}\left[
+\sup_{t \in [0, T(U_0,\overline{U}_{K_{\epsilon},\epsilon},r)]}
+U^N_{a}(\tau_a + t)
+\geq \overline{U}_{K_{\epsilon},\epsilon} 
+\right]  
+\leq \mathbb{P}[A_{H_{\epsilon}}]
+< \frac{\epsilon}{2 \overline{U}_{K_{\epsilon}}C_{g_1,..,g_{K_{\epsilon}}}},
+\end{equation}
+so we have therefore proven compact containment condition for our level process up to time $T(U_0,\overline{U}_{K_{\epsilon},\epsilon},r)$.
+
+As a result, for all time $ 0 < t , t+ \delta t \leq T(U_0,\overline{U}_{K_{\epsilon},\epsilon},r),$
+
+\begin{align*}
+W^N_a(t+\delta t)-W^N_a(t) 
+\leq &\int_{t}^{t+\delta t} 
+        \left( \frac{\theta}{N} C_G \overline{U}_{K_{\epsilon}, \epsilon}^2
+        +
+        C_F H_{\epsilon}(r) \overline{U}_{K_{\epsilon}, \epsilon}
+        \right)
+        ds\\
+=&\left( \frac{\theta}{N} C_G \overline{U}_{K_{\epsilon}, \epsilon}^2
+        +
+        C_F H_{\epsilon}(r) \overline{U}_{K_{\epsilon}, \epsilon}
+        \right) \delta t \\
+\leq&\left( A C_G \overline{U}_{K_{\epsilon}, \epsilon}^2
+        +
+        C_F H_{\epsilon}(r) \overline{U}_{K_{\epsilon}, \epsilon}
+        \right) \delta t
+\end{align*}
+
+Combining the results together, we have that for any $\delta t > 0$ small enough such that 
+\begin{equation}
+\delta t < \frac{\epsilon  }{4C_{g_1,..,g_{K_{\epsilon}}}}\min\left\{\frac{1}{C_G \overline{U}_{K_{\epsilon}, \epsilon}}, \frac{1}{A C_G \overline{U}_{K_{\epsilon}, \epsilon}^2
+        +
+        C_F H_{\epsilon}(r) \overline{U}_{K_{\epsilon}, \epsilon}}\right\}    
+\end{equation}
+holds, then we have for all $t \leq T(U_0,\overline{U}_{K_{\epsilon},\epsilon},r)$,
 \begin{equation}
 \begin{aligned}
- dW_s \leq& \frac{1}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon, \theta}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s),\Xi^{\varepsilon, \theta, \lambda}(s))}dV^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s)\wedge \overline{U}_{K_{\delta}, \delta}\\
- &+\bigg(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon, \theta}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s),\Xi^{\varepsilon, \theta, \lambda}(s))W_s^2 - b_{\varepsilon, \theta, \lambda}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s),\Xi^{\varepsilon, \theta, \lambda}(s))W_s\bigg)\mathbbm{1}_{W_s \leq \overline{U}_{K_{\delta}, \delta}}ds,
+\mathbb{E}\left[\mathfrak{d}(U^{N}_{a}(t+\delta t),U^{N}_{a}(t)) : A_{H_{\epsilon}}^{c} \right] \leq  &  
+  \mathbb{E}\left[\sum_{n=1}^{K_{\epsilon}}\frac{1 \wedge |g_n(U^{N}_{a}(t+\delta t))-g_n(U^{N}_{a}(t))|}{2^n} +  \epsilon/2: A_{H_{\epsilon}}^{c} ~\bigg|~{\cal F}_t^{
+\eta}\right]  \\
+ \leq &   \sum_{n=1}^{K_{\epsilon}}\frac{\mathbb{E}\left[C_{g_1,..,g_{K_{\epsilon}}} |U^{N}_{a}(t+r)-U^{N}_{a}(t)|: A_{H_{\epsilon}}^{c} ~\bigg|~{\cal F}_t^{
+\eta} \right] }{2^n} +  \epsilon/2  \\
+\leq&   \sum_{n=1}^{K_{\epsilon}}\frac{\mathbb{E}\left[C_{g_1,..,g_{K_{\epsilon}}} |C_G \overline{U}_{K_{\epsilon}, \epsilon} \delta t|  : A_{H_{\epsilon}}^{c} ~\bigg|~{\cal F}_t^{
+\eta} \right] }{2^n}  \\
+ & + \sum_{n=1}^{K_{\epsilon}}\frac{\mathbb{E}\left[C_{g_1,..,g_{K_{\epsilon}}}  |W^N_a(t+\delta t)-W^N_a(t)|: A_{H_{\epsilon}}^{c} ~\bigg|~{\cal F}_t^{
+\eta} \right] }{2^n} +  \epsilon/2  \\
+\leq  &  \sum_{n=1}^{K_{\epsilon}}\frac{\epsilon /2 }{2^n} +  \epsilon/2 \\
+< &  \epsilon.
 \end{aligned}
 \end{equation}
-with initial condition $W_0=U^{N}_{\tau_{\mathfrak{u}}}(t)\leq \overline{U}_{K_{\delta},\delta}$.
-The first term is due to the fact that all jumps of $(U^{N}_{\tau_{\mathfrak{u}}}(t+s))_{s \geq 0}$ that lands above $\overline{U}_{K_{\delta}, \delta}$ will result in  the process $(W_s)_{s \geq 0}$ landing on $\overline{U}_{K_{\delta}, \delta}$.
-The indicator function in the second term is due to the process staying at $\overline{U}_{K_{\delta}, \delta}$ once the process hit the value.
-
-Note that we have $\gamma^{\mathfrak{m}}_{\varepsilon, \theta}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s),\Xi^{\varepsilon, \theta, \lambda}(s)) \leq (1+C_G),$ and $- b_{\varepsilon, \theta, \lambda}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s),\Xi^{\varepsilon, \theta, \lambda}(s)) \leq \varrho_{\varepsilon}*\Xi^{\varepsilon, \theta, \lambda}_{s}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s)).$ Furthermore, recall that $V_{\tau}(t)=\sum_{k=1}^{m}v_k\mathbbm{1}_{[0, \tau_k]}  (t)  $ and all jumps are at most of size $\overline{U}_{K_{\delta}, \delta}$ for the process $(W_s)_{s \geq 0}$, By the comparison principle, for any $s \geq 0$, $W_s-W_0$ is bounded above by the increment $\widetilde{W}_s-\widetilde{W}_0$ of a process $(\widetilde{W}_s)_{s \geq 0}$ which satisfies
+
+\textbf{Conclusion:} Combining all of the above results, for any $\epsilon > 0$, we pick arbitrary $r>0$ and
+generate $T(U_0,\overline{U}_{K_{\epsilon},\epsilon},r)$ by 
+Equation \eqref{eq: Bound on Level Hitting Time} and Equation \eqref{eq: Mass Bound Constant}.
+
+We have proven that for all $t \in [0, T(U_0,\overline{U}_{K_{\epsilon},\epsilon},r)]$,
 \begin{equation}
 \begin{aligned}
- d\widetilde{W}_s =& \overline{U}_{K_{\delta}, \delta} dN_{\tau_\mathfrak{u}}(s) +\bigg(\lambda^{-1} \theta (1+C_G)\overline{U}_{K_{\delta}, \delta}^2 + \varrho_{\varepsilon}*\Xi^{\varepsilon, \theta, \lambda}_{s}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s)) \overline{U}_{K_{\delta}, \delta}\bigg)ds.
+\mathbb{E}[\mathfrak{d}(U^{N}_{a}(t+\delta t),U^{N}_{a}(t))~|~{\cal F}_t^{
+\eta}] \leq & \mathbb{E}\left[\mathfrak{d}(U^{N}_{a}(t+\delta t),U^{N}_{a}(t)) : A_{H_{\epsilon}} ~|~{\cal F}_t^{
+\eta}\right]\\
+&+ \mathbb{E}\left[\mathfrak{d}(U^{N}_{a}(t+\delta t),U^{N}_{a}(t)) : A_{H_{\epsilon}}^{c} ~|~{\cal F}_t^{
+\eta}\right] \\
+< & \epsilon + \epsilon = 2\epsilon
 \end{aligned}    
 \end{equation}
-Here $(N_{\tau_\mathfrak{u}}(s))_{s \geq 0}$ is the Poisson point process $N_{\tau_\mathfrak{u}}(t)=\sum_{k=1}^{m}\mathbbm{1}_{[0, \tau_k]}  (t) $ with rate $1$ and $\widetilde{W}_0 = \overline{U}_{K_{\delta}, \delta}$.
-
-Taking expectations, we have that 
-\begin{equation}
-\begin{aligned}
-\mathbb{E}[\widetilde{W}_{t+r}-\widetilde{W}_t] \leq &   \overline{U}_{K_{\delta}, \delta}r + \lambda^{-1} \theta (1+C_G)\overline{U}_{K_{\delta}, \delta}^2r + \overline{U}_{K_{\delta}, \delta} \int_{t}^{t+r}\mathbb{E}\left[\varrho_{\varepsilon}*\Xi^{\varepsilon, \theta, \lambda}_{s}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s))\right]ds\\
-\leq & \overline{U}_{K_{\delta}, \delta}r + \lambda^{-1} \theta (1+C_G)\overline{U}_{K_{\delta}, \delta}^2r +\overline{U}_{K_{\delta}, \delta} \int_{t}^{t+r}\left(C_0
-+   K' e^{C_G s}\right)e^s ds \\
-= & \overline{U}_{K_{\delta}, \delta}r + \lambda^{-1} \theta (1+C_G)\overline{U}_{K_{\delta}, \delta}^2r +\overline{U}_{K_{\delta}, \delta} +(C_0e^t+\frac{C_0K'}{C_G+1}e^{C_G+1})(e^{r}-1).
-\end{aligned}
-\end{equation}
-
-\textbf{Controlling Increments by Birth Events:}
-Now consider the scenario where $t > \tau_u$, i.e.
-the particle $\mathfrak{u}$ has not been born at time $t$.
-Denote $\mathcal{B}^{N}_{\mathfrak{u}}([t,t+r  ])$ to be the event that particle $\mathfrak{u}$ is born between $[t,t+r  ]$ with level smaller than $U_{K_{\delta}, \delta}$.
-In this case,
-\begin{multline}
- |g_n(U^{N}_{\tau_{\mathfrak{u}}}(t+r))-g_n(U^{N}_{\tau_{\mathfrak{u}}}(t))|\\
- =g_n(U^{N}_{\tau_{\mathfrak{u}}}(t+r))\times\mathbbm{1}_{\mathcal{B}^{N}_{\mathfrak{u}}([t,t+r  ])}\\
- < C_{g_1,...,g_n}\times \mathbbm{1}_{\mathcal{B}^{N}_{\mathfrak{u}}([t,t+r  ])},   
-\end{multline}
-for some uniform bound $C_{g_1,...,g_n}$ over $\{||g_n||_{\infty}: n =1,...,N \}$.
-It suffices therefore to show that the probability for a particle $\mathfrak{u}$ to be born or gives birth in some time interval of length less than or equal to $r$ can be arbitrarily small given small enough $r$.
-Let $\mathcal{N}^{N}_{\mathfrak{u}}([t,t+r  ])$ to be the number of particles born between $[t,t+r]$ with level smaller than $U_{K_{\delta}, \delta}$.
-Then
-\begin{equation}
-\begin{aligned}
-\mathbb{P}[\mathcal{B}^{N}_{\mathfrak{u}}([t,t+r  ])]  \leq&  \mathbb{P}[\mathcal{N}^{N}_{\mathfrak{u}}([t,t+r  ]) \geq 1]\\
-\leq & \mathbb{E}[\mathcal{N}^{N}_{\mathfrak{u}}([t,t+r  ]) ].
-\end{aligned}
-\end{equation}
-Recall that we have bounds over the total mass of the particle systems, so at time $t$, the expected number of particles alive in the $N$-th stage of scaling is bounded above $\lambda_NC_0e^{C_Gt}$ (with $\lambda_N=N$).
-The particles have levels that are independently and uniformly distributed between $[0, \lambda_N]$.
-Therefore, the expected number of particles with levels between $[0,U_{K_{\delta}, \delta}]$ is $U_{K_{\delta}, \delta}C_0e^{C_Gt}$.
-The number of births within an interval of length $r$ is a sum of Poisson random variables, and so we have
-$$\mathbb{E}[\mathcal{N}^{N}_{\mathfrak{u}}([t,t+r  ]) ]=U_{K_{\delta}, \delta}C_0e^{C_Gt}r.$$
-
-\textbf{Conclusion:} Combining all of the above results, we have that for any $\delta > 0$,
-\begin{equation}
-\begin{aligned}
-\mathbb{E}[\mathfrak{d}(U^{N}_{\tau_{\mathfrak{u}}}(t+r),U^{N}_{\tau_{\mathfrak{u}}}(t))] \leq & \mathbb{E}\left[\sum_{n=1}^{K_{\delta}}\frac{1 \wedge |g_n(U^{N}_{\tau_{\mathfrak{u}}}(t+r))-g_n(U^{N}_{\tau_{\mathfrak{u}}}(t))|}{2^n}\right] +  \delta/2\\
-\leq &\mathbb{E}\left[\sum_{n=1}^{K_{\delta}}\frac{1 \wedge |g_n(U^{N}_{\tau_{\mathfrak{u}}}(t+r))-g_n(U^{N}_{\tau_{\mathfrak{u}}}(t))|}{2^n}: \tau_{\mathfrak{u}} \leq t \right]\\
-& + \mathbb{E}\left[\sum_{n=1}^{K_{\delta}}\frac{1 \wedge |g_n(U^{N}_{\tau_{\mathfrak{u}}}(t+r))-g_n(U^{N}_{\tau_{\mathfrak{u}}}(t))|}{2^n}: \tau_{\mathfrak{u}} \geq t \right] + \delta/2\\
-\leq & C'_{g_1,...,g_n}\bigg(\overline{U}_{K_{\delta}, \delta}r + \lambda^{-1} \theta (1+C_G)\overline{U}_{K_{\delta}, \delta}^2r\\
-& \qquad \qquad  +\overline{U}_{K_{\delta}, \delta} +(C_0e^t+\frac{C_0K'}{C_G+1}e^{C_G+1})(e^{r}-1)\bigg)\\
-& + C'_{g_1,...,g_n}U_{K_{\delta}, \delta}C_0e^{C_Gt}r+\delta/2\\
-< & \delta 
-\end{aligned}    
-\end{equation}
-for small enough $r>0$. In particular, this choice of $r$ is independent of $\varepsilon, \theta, \lambda$. Therefore we have proved tightness of our level processes by \cite{EK} Theorem 3.8.6.
+for  
+\begin{equation*}
+\delta t < \frac{\epsilon  }{4C_{g_1,..,g_{K_{\epsilon}}}}\min\left\{\frac{1}{C_G \overline{U}_{K_{\epsilon}, \epsilon}}, \frac{1}{A C_G \overline{U}_{K_{\epsilon}, \epsilon}^2
+        +
+        C_F H_{\epsilon}(r) \overline{U}_{K_{\epsilon}, \epsilon}}\right\}.    
+\end{equation*}
+
+We have also proven Compact Containment Condition in Equation \eqref{eq: Compact Containment for Levels}.
+
+Therefore we have proved tightness of our level processes by \cite{EK} Theorem 3.8.6.
 \end{proof}
-\subsubsection{Convergence in $\mathcal{D}_{[0,\infty)}\left(\mathcal{N}_f(\mathbb{R}^d \times [0, \infty)\right)$ to $(\xi^{ \infty}_t)_{t \geq 0}$, where $\mathcal{N}_f(\mathbb{R}^d \times [0, \infty)$}
-Now that we have proven tightness for individual level and spatial trajectories, by Corollary \ref{cor: convergence in p implies convergence in p-infty}, Lemma \ref{lem: Countable Implies Vague} and Theorem \ref{teo: Theorem A12 Kurtz Rodrigues generalised}, we have proved that the particle system $(\xi^{\varepsilon_N, \theta_N,\lambda_N}_t)_{t \geq 0}$ converges in $\mathcal{D}_{[0,\infty)}\left(\mathcal{N}_f(\mathbb{R}^d \times [0, \infty)\right)$ to $(\xi^{ \infty}_t)_{t \geq 0}$, where $\mathcal{N}_f(\mathbb{R}^d \times [0, \infty)$ is equipped with the $\mathfrak{p}^{wv}$-topology.
-Furthermore, its spatial projection $(\overline{\eta}^{\varepsilon_N, \theta_N,\lambda_N}_t)_{t \geq 0}$ converges to $(\overline{\eta}^{\infty}_t)_{t \geq 0}$ in $\mathcal{D}_{[0,\infty)}\left(\mathcal{M}_f(\mathbb{R}^d \right)$, where $\mathcal{M}_f(\mathbb{R}^d)$ is equipped with the weak topology.
-
-In the next section, we will show how we identify the limit process.
+
+\subsection{Tightness of the Lookdown Representation}
+
+We have now proved tightness of the spatial and level process for a line of descent.
+To prove that the lookdown representation is tight, we generalise the vague topology to the setting of measure-valued processes.
+For a detailed description of the vague topology, refer to Appendix \ref{sec: Empirical Measure Topology}.
+
+We will lay out the steps we follow to prove tightness.
+First of all, we will show that compact containment condition is satisfied if we can control the total mass of particles in our system living in a finite region in space with a level lower than some $u_{*}$.
+Since a control on total mass has already been shown in Lemma \ref{lem: Compact Containment}, we have immediately established compact containment condition for our lookdown processes.
+
+Then, we apply Theorem A.24 in \cite{kallenberg1997foundations} (Theorem \ref{teo: Vague Relative Compactness through Projection}) and use a corollary of Stone-Weierstrass Theorem (Lemma \ref{lem: Dense set for test functions on empirical measures}) to show that our lookdown representation $\{\xi^N_t: N \in \mathbb{N}\}$ is tight as a $\mathcal{M}(\mathbb{R^d} \times [0, \infty])$-valued stochastic process in the vague topology as long as $\{F_g(\xi^N_t): N \in \mathbb{N}\}$ is tight as real-valued stochastic processes for a huge class of $F_g$.
+Explicitly, $F_g(\xi):= \prod_{(x_i,u_i)\in \xi}g(x_i,u_i)$, where $g(x,u)$ satisfies the property that $g(x,u) = 1 $ for all $u \geq u_{*}$ for some $u_{*}>0$.
 
@@
 \begin{equation}\label{Markov Mapping Theorem Cox Condition}
-\mathbb{E}\left[e^{-\int_{S \times [0,\lambda]} f(x,u) \xi^{\epsilon,\theta,\lambda}(dx \times du)}\bigg| \mathcal{F}^{\Xi^{\epsilon,\theta, \lambda}}_t\right]=e^{-\int F^{\epsilon,\theta,\lambda}_f(x) \Xi^{\epsilon,\theta,\lambda}_t(dx)},
+\mathbb{E}\left[e^{-\int_{S \times [0,\lambda]} f(x,u) \xi^{\epsilon,\theta,\lambda}(dx \times du)}\bigg| \mathcal{F}^{\Xi^{\epsilon,N}}_t\right]=e^{-\int F^{\epsilon,\theta,\lambda}_f(x) \Xi^{\epsilon,\theta,\lambda}_t(dx)},
 \end{equation}
@@
 
-\subsection{Weak-Vague Topology on Measures}\label{sec: Empirical Measure Topology}
+\subsection{Vague Topology on Measures}\label{sec: Empirical Measure Topology}
 
@@
 
+\begin{theorem}
+    \label{teo: Vague Relative Compactness through Projection}
+For any Polish space $S$, let $f_1,f_2,...,$ be a dense collection of functions in $C^{+}_{K}$ that is closed under addition, then a set $A \in \mathcal{D}_{\mathcal{M}(S)}([0,\infty))$ is relative compact if and only if $Af_j = \{xf_j: x \in A\}$ is relatively compact on $\mathcal{D}_{[0, \infty)}([0,\infty))$ for every $j \in \mathbb{N}$.
+\end{theorem}
+\begin{proof}
+See \cite{kallenberg1997foundations} Theorem A2.4.
+\end{proof}
 \begin{definition}
 We define $\mathfrak{G}_{\leq 1}$ to be the set of functions $g \in \mathcal{C}(\mathbb{R}^d \times [0, \infty) \to \mathbb{R})$ such that 
-$g(\cdot, u) \in \mathcal{C}_{0}(\mathbb{R}^d)$ for all $u \geq 0$, and there exists some $C_g>0$, such that $g(x,u)=1$ for all $u \geq C_g$.
+$g(\cdot, u) \in \mathcal{C}_{0}(\mathbb{R}^d)$ for all $u \geq 0$, and there exists some $u_{*}>0$, such that $g(x,u)=1$ for all $u \geq u_{*}$.
 \end{definition}
@@
 
+Combining Theorem \ref{teo: Vague Relative Compactness through Projection} and Lemma \ref{lem: Dense set for test functions on empirical measures}, we have that $\{\xi^N_t: N \in \mathbb{N}\}$ is tight as a $\mathcal{M}(\mathbb{R^d} \times [0, \infty])$-valued stochastic process in the vague topology as long as $\{F_g(\xi^N_t): N \in \mathbb{N}\}$ is tight as real-valued stochastic processes
+for all $g \in \mathfrak{G}_{\leq 1}$. 
 \bibliographystyle{plainnat}

### 2022-06-25 PDEConvergenceProof.tex
Update on Overleaf.

\documentclass[a4paper,12pt]{article}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bbm}
\usepackage[margin=1in]{geometry}
\usepackage{mathrsfs}
\usepackage[color=yellow]{todonotes}
\usepackage{tikz}
\usepackage{enumitem}
\usetikzlibrary{arrows}
\usetikzlibrary{shapes}

%\usepackage{subcaption} 
\usepackage[utf8]{inputenc}
\usepackage[backend=biber,style=alphabetic, maxbibnames=99]{biblatex}
\addbibresource{MendeleyIan.bib}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{assumptions}[theorem]{Assumptions}
\newtheorem{assumption}[theorem]{Assumption}

\newcommand{\comment}[1]{{\color{blue} \it #1}}
\newcommand{\norma}{\mathrm{Norm}}
\newcommand{\EE}{\mathbb{E}}
\newcommand{\IE}{\mathbb{E}}
\newcommand{\FF}{\mathbb{F}}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\IN}{\mathbb{N}}
\newcommand{\OP}{\mathbb{O}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\IP}{\mathbb{P}}
\newcommand{\QQ}{\mathbb{Q}}
\newcommand{\IQ}{\mathbb{Q}}
\newcommand{\GG}{\mathbb{G}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\IR}{\mathbb{R}}
\newcommand{\AS}{\mathbb{S}}
\newcommand{\AT}{\mathbb{T}}
\newcommand{\IT}{\mathbb{T}}
\newcommand{\VV}{\mathbb{V}}
%\newcommand{\DD}{\mathbb{D}}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\IZ}{\mathbb{Z}}
\newcommand{\qm}{{\mathfrak q}}
\newcommand{\A}{{\cal A}}
\newcommand{\B}{{\cal B}}
\newcommand{\C}{{\cal C}}
\newcommand{\D}{{\cal D}}
\newcommand{\E}{{\cal E}}
\newcommand{\F}{{\cal F}}
\newcommand{\G}{{\cal G}}
\newcommand{\hH}{{\cal H}}
\newcommand{\K}{{\cal K}}
\newcommand{\I}{{\cal I}}
\newcommand{\T}{{\cal T}}
\newcommand{\J}{{\cal J}}
\newcommand{\aL}{{\cal L}}
\newcommand{\aB}{{\bf B}}
\newcommand{\aP}{{\bf P}} 
\newcommand{\aE}{{\bf E}}
\newcommand{\wP}{{\widetilde{P}}}
\newcommand{\M}{{\cal M}}
\newcommand{\N}{{\cal N}}
\newcommand{\cO}{{\cal O}}
\newcommand{\R}{{\cal R}}
\newcommand{\hS}{{\cal S}}
\newcommand{\tT}{{\cal T}}
\newcommand{\U}{{\cal U}}
\newcommand{\V}{{\cal V}}
\newcommand{\dd}{{\mathbbm{d}}}
\newcommand{\DG}{\mathcal{B}}

\newcommand{\bigO}[1]{{\mathcal {O}\left(#1\right)}}
\newcommand{\littleo}[1]{{\emph{o}\left(#1\right)}}

\newcommand{\W}{{\mathbf W}} %%% I AM CHANGING THIS HERE TO SAVE CHANGING ALL THE \W's TO SOMETHING ELSE, BUT WANT CONSISTENT NOTATION FOR ONE-DIMENSIONAL AND MULTI-DIMENSIONAL HISTORICAL PROCESSES

\newcommand{\X}{{\cal X}}
\newcommand{\Y}{{\cal Y}}
\newcommand{\cZ}{{\cal Z}}
\newcommand{\FV}{{SLFVS$\Omega$}}
\newcommand{\oI}{{\overline{I}}}
\newcommand{\oJ}{{\overline{J}}}
\newcommand{\oK}{{\overline{K}}}
\newcommand{\oL}{{\overline{L}}}
\newcommand{\omu}{{\overline{\mu}}}
\newcommand{\orh}{{\overline{\rho}}}
\newcommand{\oAS}{{\overline{\AS}}}
\newcommand{\trho}{{\widehat{\rho}}}
\newcommand{\Int}{{\rm int}}
\newcommand{\oX}{{\G^+_0}}
\newcommand{\Cl}{{\rm cl}}
\newcommand{\1}{{\bf {1}}}
\def\v{\boldsymbol} %for vectors in bold text, use as \v{x
\font\gsymb=cmsy10 scaled \magstep3
\newcommand{\gtimes}{\hbox{\gsymb \char2}}
\def\hbn{\hfill\break\noindent}
\def\hch{\hfill\cr\hfill}
\let\scr=\scriptstyle
\def\sgn{\mathop{\rm sgn}\nolimits}
\def\One{{\mathbf 1}}
\def\one{ {\rm 1 \hskip -2.7pt  I}}
\def\d{^{\delta}}
\newcommand{\ds}{\displaystyle}
\newcommand{\lt}{\leadsto}

\def\v{\boldsymbol} %for vectors in bold text, use as \v{x}

\def\dim{\mathbbm{d}}

\def\Ca{($\mathscr{C}1$)}
\def\Cb{($\mathscr{C}2$)}
\def\Cc{($\mathscr{C}3$)}
\def\Cd{($\mathscr{C}4$)}
\def\Ce{($\mathscr{C}5$)}

\def\epsilon{\varepsilon}

\begin{document}

In this note, I will write the result of the convergence of the non-local Fisher-KPP equation to the local Fisher-KPP. In conjunction with the convergence to non-local PDEs of our particle system, this would finish a two-step approximation to a weak solution of  the local PDEs.

In this notes we assume $(X_t)$ is a diffusion with generator $\DG$ and denotes its transition density by $f_t(x,y)$.

We will prove the following results.
\begin{proposition}
    \label{prop:nonlocal_to_local}
    Suppose that $\varphi^a$ is a weak solution to the equation:
    \begin{equation}
\label{nonlocalPDEv1} \begin{cases}
\partial_t \varphi^a = \DG^* \varphi^a + \varphi^a (F(\varrho_a*\varphi^a)))  & x \in \mathbb{R}^d, t >0, \\ \varphi^a(x,0) = \varphi_0(x) & x \in \mathbb{R}^d.
\end{cases}
\end{equation}
and that $\varphi$ is a weak solution to the equation:
 \begin{equation}
\label{localPDE} \begin{cases}
\partial_t \varphi = \DG^* \varphi + \varphi (F(\varphi)))  & x \in \mathbb{R}^d, t >0, \\ \varphi(x,0) = \varphi_0(x) & x \in \mathbb{R}^d.
\end{cases}
\end{equation}
Assume $\varphi_0$ is positive, Lipschitz and uniformly bounded function. Assume $F$ is a Lipschitz function which is bounded above. Assume the following regularities for $b(x)$ and $C(x)$, the drift and covariance matrix of $\DG$,
\begin{enumerate}
    \item $b(x)$, $C(x)$ are uniformly bounded in each component.
    \item $C(x)$ and $b(x)$ are $\alpha$-Holder, for some $\alpha \in (0,1]$.
    \item $C(x)$ is a symmetric matrix. Furthermore, there is some constant $\Lambda>0$ such that, for all $x \in \mathbb{R}^d$,
    \[ \Lambda I< C(x) \]
    where $I$ is the $d \times d$ identity matrix.
\end{enumerate}
Then, for all $T>0$ there exists a constant $K=K(T, \Vert \varphi_0 \Vert_\infty)>0$ such that, for all $0 \leq t \leq T$ and $a$ small enough,
\[ \Vert \varphi(\cdot,t) - \varphi^a(\cdot,t) \Vert_\infty \leq K\left( e^{-a^{-1/3}/2} + a^{1/9}\right).\]
In particular, as $a$ goes to $0$, we have that $\varphi^a$ converges uniformly in compact intervals of time to $\varphi$.
\end{proposition}

\subsection{A regularity results for $X_t$.}
\begin{lemma} \label{regularityForX1}
Fix $T>0$. There exist a constant $K= K(T)>0$ such that, for any $x,y.z \in \mathbb{R}^d$ and $t \in [0,T]$,
\begin{equation} \label{eq:boundDensityXt}
\int |f_t(x,z)-f_t(y,z)| dz \leq \frac{|x-y|}{\sqrt{t}} K.
\end{equation}
\end{lemma}
\begin{proof}
We first use intermediate value Theorem to get the bound,
\begin{align*}
\int |f_t(x,z)-f_t(y,z)| dz & \leq \int |x-y| |\nabla f_t(w,z)| dz
\end{align*}
where $w \in [x,y]$. But our assumption on $b$ and $C$ we can use \cite{Sheu:1991}, equation (1.3), to get there exists a constant $\gamma=\gamma(T)>0$ such that,
\[ |\nabla f_t(w,z)|  \leq  \frac{\gamma }{\sqrt{t}}p_{ \gamma  t}(w,z), \]
Hence, 
\begin{align*}
\int |f_t(x,z)-f_t(y,z)| dz & \leq \gamma \frac{|x-y|}{\sqrt{t}} \int p_{\gamma  t}(w,z)dz = \gamma  \frac{|x-y|}{\sqrt{t}},
\end{align*}
which proves the result.
\end{proof}
\begin{lemma} \label{regularityForX2}
Fix $T>0$. Let $x,y \in \mathbb{R}^d$, $t \in [0,T]$. Let us denote $X_t^y$ and $X_t^x$ independent copies of the diffusion $X_t$ starting position at $y$ and $x$ respectively. There exists a constant $K=K(T)>0$ such that, 
\[ \EE[|X_t^y-X_t^x|] \leq K(\sqrt{t} + |y-x|) \]
\end{lemma}
\begin{proof}
First we write, 
\[ \EE[|X_t^y-X_t^x|]  = \int \int |u-v| f_t(y,u) f_t(x,v) du dv  \]
By the regularity on $C$, $b$ and using \cite{Sheu:1991}, equation (1.2), there is some constant $\gamma =\gamma (T)>0$ so that we can bound,
\[ f_t(y,u) \leq \gamma  p_{\gamma  t}(y,u) \]
So then we have that,
\begin{align}
  \EE[|X_t^y-X_t^x|]  \leq \int \int |u-v| \gamma ^2 p_{\gamma  t}(y,u) p_{\gamma  t}(x,v) dv du = \gamma ^2 \EE[|B_{\gamma  t}^y-B_{\gamma  t}^x|] \label{eq:ExpDif1}
\end{align}
where $B_t^y$ and $B_t^x$ are independent Brownian motion starting at $y$ and $x$ respectively. It is easy to see $B_{\gamma t} ^y-B_{\gamma t}^x \sim \mathcal{N}(y-x, It \gamma )$. So then $|B_{\gamma t} ^y-B_{\gamma t}^x|$ is a folded normal distribution with parameters $|y-x|$ and $d t \gamma $. Hence,
\begin{align}
\EE[|B_{\gamma  t}^y-B_{\gamma  t}^x|] &= \sqrt{t d \gamma } \sqrt{2/\pi} e^{-(y-x)^2/(2dt\gamma )} + (y-x) (1-2\Phi(-(y-x)/(\gamma  d t))) \nonumber \\ & \leq \sqrt{d \gamma  2/\pi}  \sqrt{t} + |y-x| \label{eq:ExpDif2}
\end{align}
Using (\ref{eq:ExpDif2}) in (\ref{eq:ExpDif1}) gives the result.
\end{proof}
\subsection{Auxiliary results for $\varphi$ and $\varphi^a$.}
To bound $\varphi^a-\varphi$ we first write an expression for $\varphi$ and $\varphi^a$. For this we note that, by a Feynman-Kac representation we can write,
\begin{align}
\varphi(x,t) &= \EE_x[\varphi_0(X_t) + \int_0^t \varphi(X_s,s)F(\varphi(X_s,s)) ds] \label{FK:varphi} \\
\varphi^a(x,t) &= \EE_x[\varphi_0(X_t) + \int_0^t \varphi^a(X_s,s)F(\rho_a*\varphi^a(X_s,s)) ds]
\end{align}
where $(X_t)_{t \geq 0}$ is a process with generator $\DG$. So,
\begin{equation} \varphi(x,t) - \varphi^a(x,t) = \EE_x\left[ \int_0^t (\varphi(X_s,s)F(\varphi(X_s,s))-\varphi^a(X_s,s)F(\rho_a*\varphi^a(X_s,s))) ds \right] \label{FK:diferencesVarphis}\end{equation}
The key will be to replace $F(\varphi(X_s,s))$ by $F(\rho_a*\varphi(X_s,s))$ in the last representation. That way we will have \textit{analogous} terms for $\varphi$ and $\varphi^a$ which simplifies our comparison. This is done on the next three results.

First we need a uniform bound on $\varphi$ and $\varphi^a$.  
\begin{proposition} \label{BoundednessVarphis}
For any $T>0$ there exists $M = M(T, \Vert \varphi_0 \Vert) >0$ such that, for all $0 \leq t \leq T$:
\[ \max\{ \Vert \varphi(\cdot,t) \Vert_\infty, \Vert \varphi^a(\cdot,t) \Vert_\infty\} < M \]
\end{proposition}
\begin{proof}
Using that $\varphi_0$ and $F$ are bounded above  we get,
\begin{align*}
\varphi(x,t) \leq \Vert \varphi_0 \Vert_\infty + K \EE[\int_0^t \varphi(X_s,s) ds]
\end{align*}
In particular,
\[ \Vert \varphi(\cdot,t) \Vert_\infty \leq \Vert \varphi_0 \Vert +  K \int_0^t \Vert \varphi(\cdot,s) \Vert_\infty ds \]
So, by Gronwall's inequality,
\[ \Vert \varphi(\cdot,t) \Vert_\infty \leq \Vert \varphi_0 \Vert \exp\left( K T \right) \]
A totally analogous proof also give that $\Vert \varphi^a(\cdot,t) \Vert_{\infty} \leq \Vert \varphi_0 \Vert \exp\left( K T \right) $.
\end{proof}
We now proof a continuity result on $\varphi$.

\begin{lemma} \label{ContinuityVarphi}
Let $T>0$. There exists a constant $K(T, \Vert \varphi_0\Vert_\infty) = K>0$ and $\delta_0(T, \Vert \varphi_0\Vert_\infty) = \delta_0>0$ such that for all $0 < \delta<\delta_0$ and $0 \leq t \leq T$,
\[  |x-y|<\delta^3 \Rightarrow |\varphi(x,t)-\varphi(y,t)|< K\delta.\]
\end{lemma}
\begin{proof}
First we need some notation. Let $M$ be the constant given in Proposition~\ref{BoundednessVarphis} for $T$ and let $\Vert F \Vert_{M} = \sup_{x \in [0,M]} |F(x)|$. We reserve $\widehat{K}$ for the constant in the right hand side of equation (\ref{eq:boundDensityXt}). We also reserve $K_{\varphi_0}$ for the Lipschitz constant of $\varphi_0$. Having this we can set:
\[ \delta_0=\min(\Vert F \Vert_M^{-2},(M e)^{-1}(2\Vert F \Vert_{M}+ \widehat{K})^{-1}, (K_{\varphi_0} + 2 \Vert F \Vert_M M)^{-1} ,  1)\]
In what follows we let let $0< \delta<\delta_0$.

We first proof that the result holds if $t < \delta^2$. Let $f_t(x,y)$ the transition density of $(X_t)_{t \geq 0}$.  Let $X_t^x$ and $X_t^y$ let independent copies of the diffusion $X_t$ starting at $x$ and $y$ independently. From our Feynman-Kac representation (\ref{FK:varphi}) and Proposition~\ref{BoundednessVarphis}, we can write:
\begin{align*}
|\varphi(x,t)- \varphi(y,t)| &\leq |\EE_x[\varphi_0(X_t)]-\EE_y[\varphi_0(X_t)]| + 2 \Vert F \Vert_M M t \\ & \leq \EE[|\varphi_0(X_t^x)-\varphi_0(X_t^y)|] + 2 \Vert F \Vert_M M t  \\ &\leq K_{\varphi_0}  \EE[|X_t^x-X_t^y|] + 2 \Vert F \Vert_M M t \\ & \leq K_{\varphi_0}  (\sqrt{t} + |y-x|) + 2 \Vert F \Vert_M M t \\ & \leq K_{\varphi_0} (\delta + \delta^3) + 2 \Vert F \Vert_M M \delta^2 \leq (K_{\varphi_0} +1)\delta.
\end{align*}
Where we have used Lemma~\ref{regularityForX2} in the fourth inequality and the definition of $\delta_0$ in the last inequality.

So, in what follows we can assume $\delta^2<t$. In this case, we will follow the pattern in \cite{sarahfkpp}, Lemma 2.2.

First, note that by Feynman-Kac we have the alternative representation for $\varphi(x,t)$, for any $t'<t$,
\[ \varphi(x,t) = \EE_x[ \varphi(t-t',X_{t'}) \exp( \int_0^{t'} F(\varphi(X_s,t-s)) ds ) ] \]
Therefore, for all $z$:
\[ e^{-\delta^2(\Vert F \Vert_{M})}\mathbb{E}_z[  \varphi(t-\delta^2,X_{\delta^2})] \leq  \varphi(t,z) \leq e^{\delta^2(\Vert F \Vert_{M})} \mathbb{E}_z[  \varphi(t-\delta^2,X_{\delta^2})] \]
We can then deduce that,
\begin{align*}
\varphi(t,x)-\varphi(t,y) &\leq e^{\delta^2(\Vert F \Vert_{M}}\mathbb{E}_x[ \varphi(t-\delta^2,B_{\delta^2})] - e^{-\delta^2(\Vert F \Vert_{M}}\mathbb{E}_y[ \varphi(t-\delta^2,X_{\delta^2})] \\ & = e^{\delta^2(\Vert F \Vert_{M}}(\mathbb{E}_x[ \varphi(t-\delta^2,X_{\delta^2})]- \mathbb{E}_y[ \varphi(t-\delta^2,X_{\delta^2}]) \\ &+ (e^{\delta^2(\Vert F \Vert_{M}} - e^{-\delta^2(\Vert F \Vert_{M}}  )\mathbb{E}_y[ \varphi(t-\delta^2,X_{\delta^2})] \\&\leq e^{\delta^2\Vert F \Vert_{M}} (\mathbb{E}_x[ \varphi(t-\delta^2,X_{\delta^2})]- \mathbb{E}_y[ \varphi(t-\delta^2,X_{\delta^2})])\\ &+ M(e^{\delta^2(\Vert F \Vert_{M}}-e^{-\delta^2\Vert F \Vert_{M}})
\end{align*}
where the last line is, again, Proposition~\ref{BoundednessVarphis}. For bounding the differences of the expected values on the last equation, note that, by using again Proposition~\ref{BoundednessVarphis}
\begin{align*}
(\mathbb{E}_x[ &\varphi(t-\delta^2,X_{\delta^2})]- \mathbb{E}_y[ \varphi(t-\delta^2,X_{\delta^2}]) & \\ & = \int \varphi(t-\delta^2,z) (f_{\delta^2}(x,z)-f_{\delta^2}(y,z) ) dz  \\ &\leq M \int |f_{\delta^2}(x,z)-f_{\delta^2}(y,z) | dz \\ &\leq M \widehat{K} \frac{|x-y|}{\delta}  \leq M \widehat{K} \delta^2 
\end{align*}
where in the first inequality we have used, again, Lemma~\ref{regularityForX1}. Hence,
\begin{align*}
\varphi(t,x)-\varphi(t,y)&\leq e^{\delta^2 \Vert F \Vert_{M}} \left(M+M \widehat{K}\delta^2 - M e^{-2\delta^2\Vert F \Vert_{M}}  \right) \\ & \leq e^{\delta^2 \Vert F \Vert_{M}}\left(M \widehat{K}\delta^2 + 2 M \delta^2\Vert F \Vert_{M}  \right) \\ &\leq e \left( M \widehat{K}+2 M \Vert F \Vert_M  \right) \delta^2 \leq  \delta
\end{align*}
where in the second inequality we have used $1-e^{-x} \leq x$ for all $\delta \geq 0$. The last two inequalities follows by definition of $\delta$. Analogously we can get the same bound for $\varphi(t,y)-\varphi(t,x)$ and the result is proven.
\end{proof}
We proceed to prove that we can replace $F(\varphi)$ by $F(\rho_a*\varphi)$. For simplicity, we define,
\[ \widehat{\delta}(a) := 2e^{-a^{-1/3}/2}+a^{1/9}. \]
\begin{lemma} \label{ContinuityConvolution}
Let $T>0$. There exists a constant $K=K(T,\Vert \varphi_0 \Vert_\infty)>0$ such that, for all $0 \leq t \leq T$, for all $a$ small enough,
\begin{equation} \label{ContinuityConvolution1} \Vert \varphi(\cdot,t) - \rho_a*\varphi(\cdot,t) \Vert_\infty = K \widehat{\delta}(a) \end{equation}
Furthermore, there is a constant $K(T, \Vert \varphi_0 \Vert_\infty) = K >0 $ such that, for all $0 \leq t \leq T$,
\begin{equation} \label{ContinuityConvolution2} \Vert F(\varphi(\cdot,t)) - F(\rho_a*\varphi(\cdot,t)) \Vert_\infty \leq K \widehat{\delta}(a). \end{equation}
\end{lemma}
\begin{proof}
Let $a$ be smaller than $\delta_0$ in Lemma~\ref{ContinuityVarphi}. Then,
\begin{align*}
|\varphi(x,t) - \rho_a*\varphi(x,t)| & = \int_{|x-y| > a^{1/3} } p_a(x,y)|\varphi(y,t)-\varphi(x,t)| dy  \\ & + \int_{|x-y| \leq a^{1/3} } p_a(x,y)|\varphi(y,t)-\varphi(x,t)| dy \\ & \leq 2 M \int_{|x-y| > a^{1/3}  } p_a(x,y) dy + \int_{|x-y| \leq a^{1/3}} p_a(x,y) K a^{1/9} \\ &= 2M \PP[|B_a| > a^{1/3}] + K a^{1/9} \\ & \leq  2 d M  e^{-a^{-1/3}/2} + Ka^{1/9}.
\end{align*}
where we used that, for $Z$ a standard random variable, $\PP[Z > x] \leq e^{-x^2/2}$. This proves (\ref{ContinuityConvolution1}). For (\ref{ContinuityConvolution2}) note that, by Proposition~\ref{BoundednessVarphis}, we have that $\varphi(x,t)$ and $\rho_a*\varphi(x,t)$ are bounded by $M$. Let $L_M$ be the (uniform) Lipschitz constant of $F$ on $[0,M]$. Then,
\begin{align*}
 \Vert F(\varphi(\cdot,t)) - F(\rho_a*\varphi(\cdot,t)) \Vert_\infty &\leq L_M \Vert \varphi(\cdot,t)) - (\rho_a*\varphi(\cdot,t)) \Vert_\infty \\ & \leq L_M ( 2 d M e^{-a^{-1/3}/2} + Ka^{1/9}).
\end{align*}
which proves (\ref{ContinuityConvolution2}). 
\end{proof}
\subsection{Conclusion}
\begin{proof}[Proof of Proposition \ref{prop:nonlocal_to_local}]
Let $a$ be small enough so that Lemma~\ref{ContinuityConvolution} holds. Then from the Feynman-Kac representation (\ref{FK:diferencesVarphis}) and Lemma~\ref{ContinuityConvolution} we can write,
\begin{align*}
| &\varphi(x,t) - \varphi^a(x,t)|  \\ & \leq \EE_x\left[ |\int_0^t (\varphi(X_s,s)F(\rho_a*\varphi(X_s,s))-\varphi^a(X_s,s)F(\rho_a*\varphi^a(X_s,s)))| ds \right] +K t \widehat{\delta}(a)   \\ & \leq \EE_x[ \int_0^t |F(\rho_a*\varphi^a(X_s,s))||(\varphi^a(X_s,s)-\varphi(X_s,s))| ds  ] \\ & +  \EE_x[\int_0^t |\varphi(X_s,s)| |F(\rho_a*\varphi^a(X_s,s))-F(\rho_a*\varphi(X_s,s))| ds ] + K t \widehat{\delta}(a)  \\ & \leq \Vert F \Vert_M \int_0^t \Vert \varphi^a(\cdot,s) - \varphi(\cdot,s) \Vert_\infty ds  + M L_M \int_0^t \Vert \rho_a*\varphi^a(\cdot,s)-\rho_a*\varphi(\cdot,s) \Vert_\infty ds + K t \widehat{\delta}(a)  \\ & \leq (\Vert F \Vert_M + M L_M) \int_0^t \Vert \varphi^a(\cdot,s) - \varphi(\cdot,s) \Vert_\infty ds + K t \widehat{\delta}(a).
\end{align*}
Where the second inequality is the triangular inequality and the third one is Proposition~\ref{BoundednessVarphis}. A simple application of Gronwall's inequality then yields,
\begin{align*}
\Vert \varphi^a(\cdot,t)-\varphi(\cdot,t)\Vert_\infty &\leq K t \widehat{\delta}(a)  \exp(t (\Vert F \Vert_M + M L_M)) \\ & \leq  K T \widehat{\delta}(a)  \exp(T(\Vert F \Vert_M + M L_M)),
\end{align*}
giving the result.
\end{proof}

\printbibliography

\end{document}

### 2022-06-29 forwards-and-backwards.tex
Update on Overleaf.

@@
     }{
-        r(x, \smooth{r} \eta^{\theta}(x))
+        r(x, \smooth{r} \eta^{N}(x))
     } .
@@
 are i.i.d. uniformly distributed between $[0,N]$.
-
-Theorem A.10 in \cite{kurtz/rodrigues:2011}
-states that convergence of $(\eta^{N}_t)_{t \geq 0}$
-to a conditionally Poisson system $(\lp_t)_{t \geq 0}$
-with Cox measure $\eta_t \times \Lambda$
-is equivalent to convergence of
-$(\eta^{N}_t)_{t \geq 0}$ to $(\eta_t)_{t \geq 0}$.
-As a result, it suffices for us to focus on
-tightness of $(\eta^{N}_t)_{t \geq 0}$
-and spatial convergence of $(\eta^{N}_t)_{t \geq 0}$
-as $N \to \infty$.
 
@@
     \label{lem: Compact Containment}
-Assume that $\eta^{\theta}_0 \to \eta_0$ weakly,
+Assume that $\eta^{N}_0 \to \eta_0$ weakly,
 then for all $T>0$, there exists some constant $C(T)$,
@@
             \sup_{0 \le t \le T}
-            \langle 1, \eta^\theta_t \rangle
+            \langle 1, \eta^{N}_t \rangle
         \right]
@@
     \mathbb{P}\left[\sup_{s \in [0,T]}
-        \langle 1 ,\eta^{\theta}_{s}\rangle
+        \langle 1 ,\eta^{N}_{s}\rangle
         > K_\epsilon \right]
@@
 \begin{aligned}
-     M^{\theta}_t(1):=&  \langle 1,\eta^{\theta}_t \rangle
-        -\langle 1,\eta^{\theta}_0 \rangle\\
+     M^{\theta}_t(1):=&  \langle 1,\eta^{N}_t \rangle
+        -\langle 1,\eta^{N}_0 \rangle\\
  &-  \int_{0}^{t}\bigg\{   \int\left(   \int \theta
  \left(
-        r\big(z,\rho_{r}*\eta^{\theta}_{s}(z)\big)
-            -r\big(x,\rho_{r}*\eta^{\theta}_{s}(x)\big)
+        r\big(z,\rho_{r}*\eta^{N}_{s}(z)\big)
+            -r\big(x,\rho_{r}*\eta^{N}_{s}(x)\big)
             \right)
                     q_\theta(x,dz)\right)
-                            \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
-                            \eta^{\theta}_{s}(dx)\\
-& \qquad +\int F\big(x,\rho_{F}*\eta^{\theta}_{s}(x)\big)
-\eta^{\theta}_{s}(dx)\bigg\} ds
+                            \gamma\big(x,\rho_{\gamma}*\eta^{N}_{s}(x)\big)
+                            \eta^{N}_{s}(dx)\\
+& \qquad +\int F\big(x,\rho_{F}*\eta^{N}_{s}(x)\big)
+\eta^{N}_{s}(dx)\bigg\} ds
 \end{aligned}    
@@
 \begin{aligned}
-&\mathbb{E}[\langle 1 ,\eta^{\theta}_{t}\rangle] \\
-\leq &  \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle] \\
+&\mathbb{E}[\langle 1 ,\eta^{N}_{t}\rangle] \\
+\leq &  \mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle] \\
 &+ \int_{0}^{t}\mathbb{E}\bigg\langle
-        \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
+        \gamma\big(x,\rho_{\gamma}*\eta^{N}_{s}(x)\big)
             \left| \theta \int_{\mathbb{R}^n}
-                    \big\{r\big(\rho_{r}*\eta^{\theta}_s(y)\big)-r\big(\rho_{r}*\eta^{\theta}_s(x)\big)\big\}
+                    \big\{r\big(\rho_{r}*\eta^{N}_s(y)\big)-r\big(\rho_{r}*\eta^{N}_s(x)\big)\big\}
                     \rho_{1/\theta}(x-y)dy\right| + C_F 
-                            ,\eta^{\theta}_s(dx)  \bigg\rangle ds\\
-\leq &  \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle] + (C_{\gamma,r} + C_F)\int_{0}^{t}\mathbb{E} \langle 1  ,\eta^{\theta}_s(dx) \rangle ds,
+                            ,\eta^{N}_s(dx)  \bigg\rangle ds\\
+\leq &  \mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle] + (C_{\gamma,r} + C_F)\int_{0}^{t}\mathbb{E} \langle 1  ,\eta^{N}_s(dx) \rangle ds,
 \end{aligned}
@@
 \begin{equation}
- \mathbb{E}[\langle 1 ,\eta^{\theta}_{t}\rangle] \leq \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle]e^{(C_{\gamma,r}+C_F)t}.   
+ \mathbb{E}[\langle 1 ,\eta^{N}_{t}\rangle] \leq \mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle]e^{(C_{\gamma,r}+C_F)t}.   
 \end{equation}
@@
 We denote $M^{*}_t(\phi)=\sup_{s \in [0,t]}M_t(\phi)$
-and define $h(t):=\sup_{s \in [0,t]}\langle 1, \eta^{\theta}_{s} \rangle$.
+and define $h(t):=\sup_{s \in [0,t]}\langle 1, \eta^{N}_{s} \rangle$.
 We have that
@@
 \leq& C (1+\mathbb{E}\{[M_t(1)]\})\\
-\leq & C+\frac{\theta}{N}\int_{0}^{t} \left\langle \gamma(\rho_{\gamma}*\eta^{\theta}_{s}(x))\int_{\mathbb{R}^n}r(\rho_{r}*\eta^{\theta}_{s}(y)) q_\theta(x,dy)+\mu(x,\eta^{\theta}_{s}), \eta^{\theta}_{s}(dx) \right\rangle ds \\
-\leq & C+\frac{2\theta}{N}\int_{0}^{t} \left\langle \gamma(\rho_{\gamma}*\eta^{\theta}_{s}(x))r(\rho_{r}*\eta^{\theta}_{s}(x)), \eta^{\theta}_{s}(dx) \right\rangle ds \\
-& + \frac{1}{N}\int_{0}^{t} \left\langle \gamma (\rho_{\gamma}*\eta^{\theta}_{s}(x))\theta\int_{\mathbb{R}^n}\left(r(\rho_{r}*\eta^{\theta}_{s}(y))-r(\rho_{r}*\eta^{\theta}_{s}(x))\right) q_\theta(x,dy), \eta^{\theta}_{s}(dx) \right\rangle ds\\
-\leq & C+ \frac{(2 \theta C_{\gamma,r}+C_{\gamma,r})\mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle]e^{(C_{\gamma,r}+C_F)t}}{N}.
+\leq & C+\frac{\theta}{N}\int_{0}^{t} \left\langle \gamma(\rho_{\gamma}*\eta^{N}_{s}(x))\int_{\mathbb{R}^n}r(\rho_{r}*\eta^{N}_{s}(y)) q_\theta(x,dy)+\mu(x,\eta^{N}_{s}), \eta^{N}_{s}(dx) \right\rangle ds \\
+\leq & C+\frac{2\theta}{N}\int_{0}^{t} \left\langle \gamma(\rho_{\gamma}*\eta^{N}_{s}(x))r(\rho_{r}*\eta^{N}_{s}(x)), \eta^{N}_{s}(dx) \right\rangle ds \\
+& + \frac{1}{N}\int_{0}^{t} \left\langle \gamma (\rho_{\gamma}*\eta^{N}_{s}(x))\theta\int_{\mathbb{R}^n}\left(r(\rho_{r}*\eta^{N}_{s}(y))-r(\rho_{r}*\eta^{N}_{s}(x))\right) q_\theta(x,dy), \eta^{N}_{s}(dx) \right\rangle ds\\
+\leq & C+ \frac{(2 \theta C_{\gamma,r}+C_{\gamma,r})\mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle]e^{(C_{\gamma,r}+C_F)t}}{N}.
 \end{aligned}
@@
 \begin{aligned}
-&\mathbb{E}[h(t)]:=\mathbb{E}\left[\sup_{s \in [0,t]}\langle 1 ,\eta^{\theta}_{s}\rangle\right] \\
-\leq &  \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle] \\
-&+ \sup_{\tau \in [0,t]} \int_{0}^{\tau}\mathbb{E} \bigg\langle \gamma(\rho_{r}*\eta^{\theta}_{s}(x)) \left| \theta \int_{\mathbb{R}^n} \big\{r\big(\rho_{r}*\eta^{\theta}_{s}(y)\big)-r\big(\rho_{r}*\eta^{\theta}_{s}(x)\big)\big\}\rho_{1/\theta}(x-y)dy\right| + C_F ,\eta^{\theta}_{s}(dx)  \bigg\rangle dw\\
+&\mathbb{E}[h(t)]:=\mathbb{E}\left[\sup_{s \in [0,t]}\langle 1 ,\eta^{N}_{s}\rangle\right] \\
+\leq &  \mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle] \\
+&+ \sup_{\tau \in [0,t]} \int_{0}^{\tau}\mathbb{E} \bigg\langle \gamma(\rho_{r}*\eta^{N}_{s}(x)) \left| \theta \int_{\mathbb{R}^n} \big\{r\big(\rho_{r}*\eta^{N}_{s}(y)\big)-r\big(\rho_{r}*\eta^{N}_{s}(x)\big)\big\}\rho_{1/\theta}(x-y)dy\right| + C_F ,\eta^{N}_{s}(dx)  \bigg\rangle dw\\
 &+ \mathbb{E}\{M^{*}_t(1)\}\\
-\leq &  \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle] + (C_{\gamma,r} + C_F)\int_{0}^{t}\mathbb{E} \left[ \sup_{\tau \in [0,s]} \langle 1  ,\eta^{\theta}_{s} \rangle \right]ds+\mathbb{E}\{M^{*}_t(1)\}\\
-\leq &  \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle] + (C_{\gamma,r} + C_F)\int_{0}^{t}\mathbb{E} \left[ h(s) \right]ds+\frac{(2 \theta C_{\gamma,r}+C_{\gamma,r})\mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle]e^{(C_{\gamma,r}+C_F)t}}{N}.
+\leq &  \mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle] + (C_{\gamma,r} + C_F)\int_{0}^{t}\mathbb{E} \left[ \sup_{\tau \in [0,s]} \langle 1  ,\eta^{N}_{s} \rangle \right]ds+\mathbb{E}\{M^{*}_t(1)\}\\
+\leq &  \mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle] + (C_{\gamma,r} + C_F)\int_{0}^{t}\mathbb{E} \left[ h(s) \right]ds+\frac{(2 \theta C_{\gamma,r}+C_{\gamma,r})\mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle]e^{(C_{\gamma,r}+C_F)t}}{N}.
 \end{aligned}
@@
 \mathbb{E}[h(t)] 
-\leq   \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle]
+\leq   \mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle]
             \left(1+\frac{(2 \theta C_{\gamma,r}+C_{\gamma,r})e^{(C_{\gamma,r}+C_F)t}}{N}\right)e^{(C_{\gamma,r}+C_F)t}.  
@@
 \begin{equation}
-\limsup_{N \to \infty}\mathbb{P}\left[\sup_{s \in [0,T]}\langle 1 ,\eta^{\theta}_{s}\rangle \geq K\right] \leq \frac{C(T)}{K}    
+\limsup_{N \to \infty}\mathbb{P}\left[\sup_{s \in [0,T]}\langle 1 ,\eta^{N}_{s}\rangle \geq K\right] \leq \frac{C(T)}{K}    
 \end{equation}
@@
 
-\subsubsection{Tightness of $(\langle f, \eta^{\theta}_t \rangle )_{t>0}$}
-\begin{theorem}[Tightness of $(\langle f, \eta^{\theta}_t \rangle )_{t>0}$]
+\subsubsection{Tightness of $(\langle f, \eta^{N}_t \rangle )_{t>0}$}
+\begin{theorem}[Tightness of $(\langle f, \eta^{N}_t \rangle )_{t>0}$]
     \label{teo: Tightness of real-valued projections}
@@
 the process
-$(\langle f, \eta^{\theta}_t \rangle)_{t \geq 0}$ is tight.
+$(\langle f, \eta^{N}_t \rangle)_{t \geq 0}$ is tight.
 \end{theorem}
@@
 \sup_{s \in [0, \delta]}
-\mathbb{P}\left[\left| \langle f, \eta^{\theta}_{\tau+s}\rangle
-                        - \langle f, \eta^{\theta}_{\tau}\rangle
+\mathbb{P}\left[\left| \langle f, \eta^{N}_{\tau+s}\rangle
+                        - \langle f, \eta^{N}_{\tau}\rangle
                 \right|> \epsilon \right]
@@
 \begin{aligned}
- & \mathbb{E}\left[\left| \langle f, \eta^{\theta}_{\tau+s}\rangle - \langle f, \eta^{\theta}_{\tau}\rangle \right|\right] \\
-\leq & \mathbb{E}\Bigg[\bigg| \int_{\tau}^{\tau+s}\bigg\langle \theta\gamma(\rho_{r}*\eta^{\theta}_{s}(x)) \int_{\mathbb{R}^n} \big\{f(y)r(\rho_{r}*\eta^{\theta}_{s}(y))-f(x)r(\rho_{r}*\eta^{\theta}_{s}(x))\big\}\rho_{1/\theta}(x-y)dy \\
-& \qquad + F(\rho_{F}*\eta^{\theta}_{s}(x)) f(x),\eta^{\theta}_{s}(dx)  \bigg\rangle ds \bigg|\Bigg].
+ & \mathbb{E}\left[\left| \langle f, \eta^{N}_{\tau+s}\rangle - \langle f, \eta^{N}_{\tau}\rangle \right|\right] \\
+\leq & \mathbb{E}\Bigg[\bigg| \int_{\tau}^{\tau+s}\bigg\langle \theta\gamma(\rho_{r}*\eta^{N}_{s}(x)) \int_{\mathbb{R}^n} \big\{f(y)r(\rho_{r}*\eta^{N}_{s}(y))-f(x)r(\rho_{r}*\eta^{N}_{s}(x))\big\}\rho_{1/\theta}(x-y)dy \\
+& \qquad + F(\rho_{F}*\eta^{N}_{s}(x)) f(x),\eta^{N}_{s}(dx)  \bigg\rangle ds \bigg|\Bigg].
 \end{aligned}
@@
 \begin{multline}
- \theta\gamma(\rho_{r}*\eta^{\theta}_{s}(x))\int_{\mathbb{R}^n} \big\{f(y)r(\rho_{r}*\eta^{\theta}_{s}(y))-f(x)r(\rho_{r}*\eta^{\theta}_{s}(x))\big\}\rho_{1/\theta}(x-y)dy \\
- =  f(x)\theta\gamma(\rho_{r}*\eta^{\theta}_{s}(x))\int_{\mathbb{R}^n} \big\{r(\rho_{r}*\eta^{\theta}_{s}(y))-r(\rho_{r}*\eta^{\theta}_{s}(x))\big\}\rho_{1/\theta}(x-y)dy\\
- + \theta\gamma(\rho_{r}*\eta^{\theta}_{s}(x))\int_{\mathbb{R}^n} \big\{(f(y)-f(x))r(\rho_{r}*\eta^{\theta}_{s}(y))\big\}\rho_{1/\theta}(x-y)dy\\
+ \theta\gamma(\rho_{r}*\eta^{N}_{s}(x))\int_{\mathbb{R}^n} \big\{f(y)r(\rho_{r}*\eta^{N}_{s}(y))-f(x)r(\rho_{r}*\eta^{N}_{s}(x))\big\}\rho_{1/\theta}(x-y)dy \\
+ =  f(x)\theta\gamma(\rho_{r}*\eta^{N}_{s}(x))\int_{\mathbb{R}^n} \big\{r(\rho_{r}*\eta^{N}_{s}(y))-r(\rho_{r}*\eta^{N}_{s}(x))\big\}\rho_{1/\theta}(x-y)dy\\
+ + \theta\gamma(\rho_{r}*\eta^{N}_{s}(x))\int_{\mathbb{R}^n} \big\{(f(y)-f(x))r(\rho_{r}*\eta^{N}_{s}(y))\big\}\rho_{1/\theta}(x-y)dy\\
  \leq C_{\gamma,r}||f||_{\infty} + C_{\gamma}||\Delta f||_{\infty},
@@
 
-Finally,  $F(\rho_{F}*\eta^{\theta}_{s}(x)) f(x)$ is bounded above by $C_F||f||_{\infty}$, so 
+Finally,  $F(\rho_{F}*\eta^{N}_{s}(x)) f(x)$ is bounded above by $C_F||f||_{\infty}$, so 
 \begin{multline}
 \mathbb{E}\left[\left|
-                        \langle f, \eta^{\theta}_{\tau+s}\rangle - \langle f, \eta^{\theta}_{\tau}\rangle
+                        \langle f, \eta^{N}_{\tau+s}\rangle - \langle f, \eta^{N}_{\tau}\rangle
                 \right|\right] \\
@@
                         \int_{\tau}^{\tau+s}
-                        \bigg\langle 1,\eta^{\theta}_{s}(dx)  \bigg\rangle 
+                        \bigg\langle 1,\eta^{N}_{s}(dx)  \bigg\rangle 
                         ds
@@
                     +C_F||f||_{\infty})
-                \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle]
+                \mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle]
                         e^{(C_{\gamma,r}+C_F)T}(e^\delta-1).
 \end{multline}
-As $\eta^{\theta}_0$ converges weakly,
+As $\eta^{N}_0$ converges weakly,
 we have that 
-$\sup_{\theta > \theta_0}\mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle] < K$
+$\sup_{\theta > \theta_0}\mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle] < K$
 for some $K>0$.
@@
 \frac{
-\mathbb{E}\left[\left| \langle f, \eta^{\theta}_{\tau+s}\rangle
-                        - \langle f, \eta^{\theta}_{\tau}\rangle
+\mathbb{E}\left[\left| \langle f, \eta^{N}_{\tau+s}\rangle
+                        - \langle f, \eta^{N}_{\tau}\rangle
                 \right| \right]
@@
 \leq &\frac{\theta}{N} \mathbb{E} \Bigg\{ \int_{\tau}^{\tau+s}\bigg|
-\langle \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
-\int f^2(y)r\big(y,\rho_{r}*\eta^{\theta}_{s}(y)\big)q_\theta(x,dy) 
-,\eta^{\theta}_{s}(dx)\rangle\\
-& \qquad \qquad \qquad +\langle \mu\big(x,\eta^{\theta}_{s}\big)f^2(x) 
-,\eta^{\theta}_{s}(dx)\rangle \bigg|ds \Bigg\}\\
-\leq & \frac{2\theta}{N}\mathbb{E} \Bigg\{\int_{\tau}^{\tau+s} \left\langle \gamma(\rho_{\gamma}*\eta^{\theta}_{s}(x))r(\rho_{r}*\eta^{\theta}_{s}(x)), \eta^{\theta}_{s}(dx) \right\rangle ds\Bigg\} \\
-& + \frac{1}{N}\mathbb{E} \Bigg\{\int_{\tau}^{\tau+s} \left\langle \gamma (\rho_{\gamma}*\eta^{\theta}_{s}(x))\theta\int_{\mathbb{R}^n}\left(r(\rho_{r}*\eta^{\theta}_{s}(y))-r(\rho_{r}*\eta^{\theta}_{s}(x))\right) q_\theta(x,dy), \eta^{\theta}_{s}(dx) \right\rangle ds\Bigg\}\\
-\leq & \frac{(2 \theta C_{\gamma,r}+C_{\gamma,r})\mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle]e^{(C_{\gamma,r}+C_F)T}(e^\delta-1)}{N}.
+\langle \gamma\big(x,\rho_{\gamma}*\eta^{N}_{s}(x)\big)
+\int f^2(y)r\big(y,\rho_{r}*\eta^{N}_{s}(y)\big)q_\theta(x,dy) 
+,\eta^{N}_{s}(dx)\rangle\\
+& \qquad \qquad \qquad +\langle \mu\big(x,\eta^{N}_{s}\big)f^2(x) 
+,\eta^{N}_{s}(dx)\rangle \bigg|ds \Bigg\}\\
+\leq & \frac{2\theta}{N}\mathbb{E} \Bigg\{\int_{\tau}^{\tau+s} \left\langle \gamma(\rho_{\gamma}*\eta^{N}_{s}(x))r(\rho_{r}*\eta^{N}_{s}(x)), \eta^{N}_{s}(dx) \right\rangle ds\Bigg\} \\
+& + \frac{1}{N}\mathbb{E} \Bigg\{\int_{\tau}^{\tau+s} \left\langle \gamma (\rho_{\gamma}*\eta^{N}_{s}(x))\theta\int_{\mathbb{R}^n}\left(r(\rho_{r}*\eta^{N}_{s}(y))-r(\rho_{r}*\eta^{N}_{s}(x))\right) q_\theta(x,dy), \eta^{N}_{s}(dx) \right\rangle ds\Bigg\}\\
+\leq & \frac{(2 \theta C_{\gamma,r}+C_{\gamma,r})\mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle]e^{(C_{\gamma,r}+C_F)T}(e^\delta-1)}{N}.
 \end{aligned}
@@
 
-\subsubsection{Tightness of $(\eta^{\theta}_t)_{t \geq 0}$}
+\subsubsection{Tightness of $(\eta^{N}_t)_{t \geq 0}$}
 \begin{theorem}
 The collection of measure-valued processes 
-$\{(\eta^{\theta}_t)_{t \geq 0}: \theta > 0\}$
+$\{(\eta^{N}_t)_{t \geq 0}: \theta > 0\}$
 is tight in $\mathcal{D}_{[0,\infty)}(\mathcal{M}_F(\overline{\mathbb{R}^d}))$.
@@
 To prove relative compactness 
-of the processes $(\eta^{\theta}_t)_{t \geq 0}$,
+of the processes $(\eta^{N}_t)_{t \geq 0}$,
 we apply Theorem 3.9.1. in \cite{EK}.
@@
 Furthermore,
-since each measure $\eta^{\theta}_t$ is concentrated in $\mathbb{R}^d$,
+since each measure $\eta^{N}_t$ is concentrated in $\mathbb{R}^d$,
 it suffices to show that the real-valued processes
-$\langle f, \eta^{\theta}_t \rangle$
+$\langle f, \eta^{N}_t \rangle$
 is tight for all $f \in \mathcal{C}^{2}_{0}(\mathbb{R}^d)$,
@@
 \right)
-\prod_{i=1}^{k}\langle h_i,\eta^{\theta}_{t_i} \rangle
+\prod_{i=1}^{k}\langle h_i,\eta^{N}_{t_i} \rangle
 \right]=0
@@
 \times 
-\prod_{i=1}^{k}\langle h_i,\eta^{\theta}_{t_i} \rangle
+\prod_{i=1}^{k}\langle h_i,\eta^{N}_{t_i} \rangle
 \right]=0
@@
 \end{equation}
-
 such that 
@@
 
+\comment{
+    This comes later because it uses convergence of the population process itself.
+}
+
 We have now proved tightness of the spatial and level process for a line of descent.
@@
 
-Then, we apply Theorem A.24 in \cite{kallenberg1997foundations} (Theorem \ref{teo: Vague Relative Compactness through Projection}) and use a corollary of Stone-Weierstrass Theorem (Lemma \ref{lem: Dense set for test functions on empirical measures}) to show that our lookdown representation $\{\xi^N_t: N \in \mathbb{N}\}$ is tight as a $\mathcal{M}(\mathbb{R^d} \times [0, \infty])$-valued stochastic process in the vague topology as long as $\{F_g(\xi^N_t): N \in \mathbb{N}\}$ is tight as real-valued stochastic processes for a huge class of $F_g$.
-Explicitly, $F_g(\xi):= \prod_{(x_i,u_i)\in \xi}g(x_i,u_i)$, where $g(x,u)$ satisfies the property that $g(x,u) = 1 $ for all $u \geq u_{*}$ for some $u_{*}>0$.
-
-\comment{
-    This comes later because it uses convergence of the population process itself.
-}
+Then, we apply Theorem A.24 in \cite{kallenberg1997foundations}
+(Theorem \ref{teo: Vague Relative Compactness through Projection})
+and use a corollary of Stone-Weierstrass Theorem
+(Lemma \ref{lem: Dense set for test functions on empirical measures})
+to show that our lookdown representation $\{\xi^N_t: N \in \mathbb{N}\}$ is tight
+as a $\mathcal{M}(\mathbb{R^d} \times [0, \infty])$-valued stochastic process
+in the vague topology
+as long as $\{F_g(\xi^N_t): N \in \mathbb{N}\}$ is tight
+as real-valued stochastic processes for a huge class of $F_g$. 
+Explicitly, $F_g(\xi):= \prod_{(x_i,u_i)\in \xi}g(x_i,u_i)$,
+where $g(x,u)$ satisfies the property that
+$g(x,u) = 1 $
+for all $u \geq u_{*}$ for some $u_{*}>0$.
+
+\subsubsection{Compact Containment Condition}
+\begin{definition}
+For any arbitrary $M,K>0$, 
+we denote the set 
+$$\mathcal{M}_{K,M}:= \{\mu \in \mathcal{M}(\mathbb{R^d} \times [0, \infty]): \mu([-M,M]^d \times [0,M])/M \leq K\}$$
+to be the set of measures on $\mathbb{R}^d \times[0,\infty)$ with mass smaller than $K$ in the region $[-M,M]^d \times [0,M]$.
+\end{definition}
+
+In Corollary \ref{cor: Vague Compact sets}, we will prove that $\mathcal{M}_{K,M}$ is vaguely compact.
+
+\begin{lemma}[Compact Containment]
+    \label{lem: Compact Containment}
+Assume that $\xi^{N}_0 \to \xi_0$ weakly,
+then for all $T>0$, there exists some constant $C(T)$,
+such that
+    \begin{align}
+        \label{eq: Growth function bound on running sup, lookdown}
+        \IE\left[
+            \sup_{0 \le t \le T}
+            \frac{1}{N}\langle 1, \xi^{N}_t \rangle
+        \right]
+        \le C(T) ,
+    \end{align}
+uniformly in $N$.
+In particular, for any $\epsilon > 0$, there exists some $M_{\epsilon}>0, K_{\epsilon}>0$,
+such that 
+\begin{equation}
+\limsup_{N \to \infty}
+    \mathbb{P}\left\{ \xi^{N}_t \in \mathcal{M}_{K_{\epsilon},M_{\epsilon}}
+        \text{ for } t\in [0,T] \right\}
+        < \epsilon.
+\end{equation}
+\end{lemma}
+\begin{proof}
+By an application of Markov Mapping Theorem (see \S \ref{sec: Markov Mapping Theorem Application - Prelimit}), we know that
+
+$$\left(\frac{1}{N}\langle 1, \xi^{N}_t(\cdot , [0, N]) \rangle\right)_{t \geq 0} \sim (\eta^N_t(\cdot ))_{t \geq 0},$$
+i.e. the spatial projection of $(\xi^{N}_t)_{t \geq 0}$ has the same distribution as $(\eta^N_t)_{t \geq 0}$ defined in Definition \ref{defn:mgale_construction}. 
+As a result, by Lemma \ref{lem: Compact Containment},
+we have immediately that 
+\begin{align}
+        \IE\left[
+            \sup_{0 \le t \le T}
+            \frac{1}{N}\langle 1, \xi^{N}_t \rangle
+        \right]
+        = \IE\left[
+            \sup_{0 \le t \le T}
+            \langle 1, \eta^{N}_t \rangle
+        \right]
+        \le C(T) ,
+    \end{align}
+for some $C(T)>0$.
+
+Moreover, we know that conditional on the spatial configuration 
+$\frac{1}{N}\langle 1, \xi^{N}_t(\cdot , [0, N]) \rangle,$
+the levels of each individual
+is i.i.d uniformly distributed between $[0,N]$. 
+Therefore, for $N>M_{\varepsilon}$
+\begin{align*}
+     \mathbb{P}\left\{ \xi^{N}_t \in \mathcal{M}_{K_{\epsilon},M_{\epsilon}}
+        \text{ for } t\in [0,T] \right\}
+        =& \mathbb{P}\left\{\sup_{ t\in [0,T]} \frac{1}{M_\varepsilon} \xi^{N}_t([-M_\varepsilon,M_\varepsilon]^d \times [0,M_\varepsilon]) \leq K_\varepsilon
+         \right\}\\
+         \leq& \frac{1}{M_\varepsilon K_{\varepsilon}} \mathbb{E}\left\{\sup_{ t\in [0,T]}  \xi^{N}_t([-M_\varepsilon,M_\varepsilon]^d \times [0,M_\varepsilon]) \right\}\\
+        =& \frac{1}{M_\varepsilon K_{\varepsilon}}             \mathbb{E}_{\eta^N_t}\left\{ N \times
+            \mathbb{E}\left[  
+                \sup_{ t\in [0,T]}  \frac{1}{N}\xi^{N}_t([-M_\varepsilon,M_\varepsilon]^d \times [0,M_\varepsilon])
+                \bigg| \eta^N_t
+                        \right]
+                    \right\}\\
+        =& \frac{1}{M_\varepsilon K_{\varepsilon}} \mathbb{E}_{\eta^N_t}
+                    \left\{ N \times
+                    \sup_{ t\in [0,T]} \eta^{N}_t([-M_\varepsilon,M_\varepsilon]^d) \times \frac{M_{\varepsilon}}{N}
+                    \right\}\\
+        =& \frac{1}{K_{\varepsilon}} \mathbb{E}_{\eta^N_t}
+                    \left\{
+                    \sup_{ t\in [0,T]} \eta^{N}_t([-M_\varepsilon,M_\varepsilon]^d) 
+                    \right\}\\
+        \leq & \frac{1}{K_{\varepsilon}} \mathbb{E}_{\eta^N_t}
+                    \left\{
+                    \sup_{ t\in [0,T]} \langle 1, \eta^{N}_t \rangle 
+                    \right\}\\
+        < & \varepsilon.
+\end{align*}
+The first inequality holds by Markov's inequality, and the following two equalities hold as 
+conditional on $\eta^N_t$,
+$M_{\varepsilon}/N$ proportion of particles in $\xi^N_t$ have levels in $[0,M_{\varepsilon}]$. The final inequality holds as a direct consequence of \ref{lem: Compact Containment}.
+
+We have therefore proved compact containment condition in the vague topology for our lookdown representation.
+\end{proof}
+\subsubsection{Tightness of $(F_g(\xi_t))_{t \geq 0}$}
+
+\begin{definition}
+We define $\mathfrak{G}_{\leq 1}$ to be the set of functions $g \in \mathcal{C}(\mathbb{R}^d \times [0, \infty) \to \mathbb{R}$ such that 
+$g(\cdot, u) \in \mathcal{C}_{0}(\mathbb{R}^d)$ for all $u \geq 0$, and there exists some $u_{*}>0$ such that $g(x,u)=1$ for all $u \geq u_{*}$.
+Furthermore, for $g \in \mathfrak{G}_{\leq 1}$, define $F_g(\xi):= \exp(-\langle \log g, \cdot \rangle )$.
+\end{definition}
+
+To prove tightness of $(\xi_t)_{t \geq 0}$ in the vague topology, it suffices to prove tightness of $(F_g(\xi_t))_{t \geq 0}$ as a real-valued stochastic process.
+For a proof of this statement refer to Appendix \ref{sec: Topologies on Lookdown}.
+
+\begin{lemma}
+For all $g \in \mathfrak{G}_{\leq 1}$, the processes $\{(F_g(\xi^N_t))_{t \geq 0}: N \in \mathbb{N}\}$ is tight as a real-valued stochastic process.
+\end{lemma}
+\begin{proof}
+
+\end{proof}
 
@@
 \begin{corollary}
-For any arbitrary $N,K>0$, the set $$\mathcal{M}_K([-N,N]^d \times [0,N]):= \{\mu \in \mathcal{M}(\mathbb{R^d} \times [0, \infty]): \mu([-N,N]^d \times [0,N]) \leq K\}$$   
+\label{cor: Vague Compact sets}
+For any arbitrary $M,K>0$, the set 
+$$\mathcal{M}_{K,M}:= \{\mu \in \mathcal{M}(\mathbb{R^d} \times [0, \infty]): M^{-1}\mu([-M,M]^d \times [0,M]) \leq K\}$$   
 is a compact subset in 
@@
 As a result, 
-$$\sup_{\mu \in \mathcal{M}_K([-N,N]^d \times [0,N])} \mu f < C_f \times \mu \{ supp(f) \cap [-N,N]^d \times [0,N]\} \leq C_f K < \infty.$$
+$$\sup_{\mu \in \mathcal{M}_{K,M}} \mu f < C_f \times \mu \{ supp(f) \cap [-M,M]^d \times [0,M]\} \leq C_f M^{-1} K < \infty.$$
 
@@
 the set
-$\mathcal{M}_K([-N,N]^d \times [0,N])$
+$\mathcal{M}_{K,M}$
 is vaguely relatively compact.
 
-We now prove that $\mathcal{M}_K([-N,N]^d \times [0,N])$ is a closed subset of $\mathcal{M}(\mathbb{R^d} \times [0, \infty])$.
-
-Since $[-N,N]^d \times [0,N]$ is finite, by part 3 of Theorem \ref{teo: Kallenberg vague results},
-for any sequence in $(\mu_n)_{n \in \mathbb{N}}$ in  $\mathcal{M}_K([-N,N]^d \times [0,N])$ that converges vaguely to $\mu$ in 
+We now prove that $\mathcal{M}_{K,M}$ is a closed subset of $\mathcal{M}(\mathbb{R^d} \times [0, \infty])$.
+
+Since $[-M,M]^d \times [0,M]$ is finite, by part 3 of Theorem \ref{teo: Kallenberg vague results},
+for any sequence in $(\mu_n)_{n \in \mathbb{N}}$ in  $\mathcal{M}_{K,M}$ that converges vaguely to $\mu$ in 
 $ \mathcal{M}(\mathbb{R^d} \times [0, \infty])$, 
-$$K \geq \mu_n([-N,N]^d \times [0,N]) \to \mu([-N,N]^d \times [0,N]).$$
-Therefore, $\mu \in \mathcal{M}_K([-N,N]^d \times [0,N])$.
-As a result, $\mathcal{M}_K([-N,N]^d \times [0,N])$ is closed and relatively vaguely compact, so it is vaguely compact.
+$$MK \geq \mu_n([-M,M]^d \times [0,M]) \to \mu([-M,M]^d \times [0,M]).$$
+Therefore, $\mu \in \mathcal{M}_{K,M}$.
+As a result, $\mathcal{M}_{K,M}$ is closed and relatively vaguely compact, so it is vaguely compact.
 \end{proof}

### 2022-07-03 forwards-and-backwards.tex
.

@@
 \newcommand{\measures}{\mathcal{M}_F(\IR^d)} % finite measures on Rd
+\newcommand{\cmeasures}{\mathcal{M}_F(\overline{\IR}^d)} % finite measures on compactified Rd
+\newcommand{\lpmeasures}{\mathcal{M}(\overline{\IR^d} \times [0,\infty))} % locally finite measures on space x level
 
@@
 
+make sure to put in here that we get convergence of the FKPP
+
+Note: use "reproductive value" instead of "long-term fitness"
+and say clearly that "lineage" means "ancestral lineage".
+
 \vspace{.1in}
@@
 \comment{I think the introduction covers a good set of things in a good order, it's just a bit long.}
+
+\comment{
+    Make sure that we discuss the difference to Flandoli's model
+    (one of the few others that show convergence of FKPP),
+    and say that a novelty of our results is that we show convergence
+    for FKPP and broader models.
+}
 
@@
 % % % % % % % % % % % % % %
-\subsection{Structure of the paper}
-
+\paragraph{Structure of the paper}
 In the paper we study scaling limits of spatial populations,
@@
 
+\plr{TODO: check the conditions below (esp on the derivatives of $F$)}
+
 \begin{definition}[Model parameterization and assumptions]
@@
 Suppose $\gamma(x, m)$, $r(x, m)$, and $F(x, m)$
-are bounded, uniformly continuous functions
-from $\IR^d \times \IR_{\ge 0}$ to $\IR_{\ge 0}$.
+are uniformly continuous functions
+from $\IR^d \times \IR_{\ge 0}$ to $\IR$.
 Furthermore, suppose $r$ takes values in $[0, 1]$
 and has uniformly bounded second derivatives,
-and that $(x, m) \mapsto m^2 \gamma(x, m)$ is uniformly bounded.
+that $\gamma(x,m) \ge 0$,
+and that $m^2 \gamma(x, m)$ is uniformly bounded.
 Fix nonnegative values $\epsilon_r$, $\epsilon_\gamma$, and $\epsilon_F$,
 with $\epsilon_r < \epsilon_\gamma$.
-Suppose $F: \IR^d \times \IR_{\ge 0} \to \IR$ is bounded and uniformly continuous
+Suppose $F(x,m)$ is bounded above
+with uniformly bounded first and second derivatives in $m$,
 and define
@@
 % % % % % % % % % % % % % % %
-\subsection{Main results on population processes}
+\subsection{Scaling limits of the population density process}
 
@@
 See Figure \ref{fig:super_vs_det_2d} for illustrative simulations.
-We suspect that limits are possible the remaining (local, superprocess) case
-in only $d=1$, but do not discuss the case further.
+We suspect that limits are possible in the remaining (local, superprocess) case
+only in $d=1$, but do not discuss the case further.
 
@@
     \begin{align} \label{eqn:mgale_problem}
+        \begin{split}
         M_t
@@
                 \right)(x)
+                \\ &\qquad \qquad \qquad {}
                 +
@@
             \big\rangle ds,
+        \end{split}
     \end{align}
@@
 \end{corollary}
+
+\comment{
+    TODO: put in what Kurtz \& Xiong have to say about uniqueness,
+along the lines of a note saying ``For some conditions under which the limit is known to be unique,
+see Kurtz \& Xiong and/or Dawson \& Li.''
+}
 
@@
 % % % % % % % % % % % %
-\subsection{Main results on lineages}
+\subsection{Ancestral lineages in the scaling limit}
 
@@
 % % % % % % % % % % % %
-\subsection{A nonlinear diffusive population: the Porous Medium Equation}
+\subsection{Beyond reaction-diffusion equations: a population described by the porous medium equation}
+\comment{look up what the technical term is for the nonlinear diffusive bit?
+    and, does "reaction-diffusion" mean parabolic?}
 
@@
 % % % % % % % % % % % %
-\subsection{Traveling waves}
+\subsection{Different types of traveling waves}
 
@@
 % % % % % % % % % % % % % % % %
-\subsection{Nonuniqueness of population density}
+\subsection{Lineage motion is not uniquely determined by population density}
 
@@
 % % % % % % % % % % % % % % % % % %
-\subsection{Population processes}
+\subsection{The population density}
     \label{sec:population_heuristics}
@@
 =
-    r(x,\varrho(x))
+    r(x,\varrho)
     \DG\big(
@@
     \big)(x)
-    + F(x, \varrho(x)) \varrho(x) 
+    + F(x, \varrho) \varrho(x) 
 \end{equation}
@@
 where $\varrho_t$ is the density of $\eta_t$, if it has a density.
+
+\comment{
+    Point out that this is still with $\epsilon > 0$,
+    and put in heuristics for why $N \epsilon^d / \theta \to \infty$
+    and $\theta \epsilon^2 \to \infty$
+    are plausible conditions for the diagonal convergence.
+    (Because we want (a) a macroscopic number of neighbors relative to $\theta$,
+    and (b) to make the initial condition smooth enough
+    since we start with an $\epsilon^2$-smoothed initial condition,
+    and we want this to look like a bunch of $1/\theta$-jumps have already happened.
+}
 
@@
 % % % % % % % % % % % % % % % % % %
-\subsection{Lineages}
+\subsection{Motion of ancestral lineages}
 
@@
 % % % % % % % % % % % % % % % %
-\subsection{Definition and generator of the lookdown process}
+\subsection{Lookdown construction of the population density process}
 \label{sec:lookdown_defn}
@@
 
+Now that the lookdown process has been defined,
+we can present the main convergence theorem that is analogous
+to Theorem~\ref{thm:nonlocal_convergence} for the population process.
+
+\begin{theorem}
+    \label{thm:lookdown_convergence}
+    Let $(\lp_t^N)$ be as defined in Definition~\ref{defn:lookdown_mgale}
+    and assume that as $N \to \infty$,
+    $\theta \to \infty$ in such a way that $\theta/N \to \alpha$.
+    The sequence of stochastic processes $(\lp_t^N)_{t \ge 0}$
+    converges along subsequences in distribution as $N \to \infty$
+    to a measure-valued process $(\lp_t)_{t \ge 0}$ which satisfies,
+    for every $f: \IR^d \to \IR$
+    \plr{TODO: write down limiting martingale characterization}
+\end{theorem}
+
 \comment{I don't think this bit quite makes sense yet without understanding the MMT
@@
 %% %% %% %% %% %% %% %% %% %% %% %%
-\subsection{Construction tracking individual lines of descent} \label{sec: individual lines of descent}
+\subsection{Explicit construction of lines of descent}
+    \label{sec: individual lines of descent}
 
@@
 
-\subsubsection{Evolution of levels along a whole line of descent}
+\comment{
+    Note here that although we have a single construction that couples
+    the processes across all $N$,
+    we don't necessarily have pointwise a.s.\ convergence of trajectories of the process.
+    Furthermore, individuals at all levels may affect others through the population process,
+    and in the deterministic case arbitrarily high levels may drift downwards.
+    HOWEVER, this does suggest that a good approximation to the genealogies
+    might be obtained by simulating up until a sufficiently high level
+    that we have a good approximation to the population process.
+}
+
+% % % % % % % % % % % % %  % % %
+\subsubsection{Lines of descent in the scaling limit}
+
 We now write down expressions
@@
 \begin{align*}
-    \eta_t = \lim_{N \to \infty} \frac{1}{N} \sum_{a : \tau_a \le t < \sigma_a} \delta_{X_a(t)}
+    \eta_t
+    =
+    \lim_{u_0 \to \infty} \frac{1}{u_0}
+        \sum_{a : \tau_a \le t < \sigma_a \;\&\; U_a(t) < u_0} \delta_{X_a(t)}
     \qquad \text{and} \qquad
@@
 \end{align*}
-agree in distribution with those of Definitions~\ref{defn:mgale_construction} and~\ref{defn:lookdown_mgale},
-respectively.
+agree in distribution with those of Definitions~\ref{defn:mgale_construction}
+and~\ref{defn:lookdown_mgale}, respectively.
 \end{proposition}
@@
 
-\comment{
-    TODO: write overview.
-    To prove convergence, we'll be proving
-    (a) tightness
-    (b) convergence of generators, and
-    (c) uniqueness of the limit.
-
-    Then, to get convergence of the lookdown
-    we use the population process (somehow).
-}
+\comment{TODO structure of this section}
+
+% % % % % % % % % % % % %
+\subsection{Convergence of the population density process}
+    \label{sec:population_density_proof}
+
+In this section we prove the main theorem on convergence
+of the population density process, Theorem~\ref{thm:nonlocal_convergence}.
+This is usually implied by convergence of the lookdown process
+(see \citet{kurtz/rodrigues:2011} and \citet{KE});
+however in our situation because the parameters depend on the population process
+we will use convergence of the population process
+in the proofs of tightness and convergence for the lookdown process.
 
 \begin{proof}[Proof of Theorem~\ref{thm:nonlocal_convergence}.]
-
-\comment{INSERT HERE
-    narrative of tightness,
-    proved in Section \ref{sec:population_tightness_proofs},
-    and convergence of generators,
-    proved in Section \ref{sec:population_generators_proofs}.
-}
-
+Here, we need to prove that for any sequence $N_k \to \infty$,
+there is a subsequence $N_{k(j)}$ along which $(\eta^{N_{k(j)}}_t)_{t\ge 0}$ converges in distribution
+(i.e., tightness for the family of distributions on c\`adl\`ag measure-valued paths),
+and that any limit is a solution to the martingale problem stated in the Theorem.
+This would convergence along $N_k$ to a unique limit
+if the solution to the martingale problem was unique;
+however, we only know this to be the case in certain situations.
+
+We prove tightness of $\eta^N$ as $\mathcal{D}_{\cmeasures}([0,\infty))$-valued processes,
+where $\cmeasures$ is the space of finite measures on the one-point compactification of $\IR^d$.
+To do this, we first prove that $\sup_{0 \le t \le T} \langle 1, \eta^N_t \rangle$ is tight
+(a compact containment condition, Lemma~\ref{lem: Compact Containment}).
+(The reason we use $\cmeasures$ instead of $\measures$
+is so that the set of measures with total mass less than $K$ is compact.)
+Next, in Lemma~ we show that the one-dimensional distributions,
+$\langle f, \eta^N_t \rangle$ are tight
+for each $f \in \mathcal{C}^2_0(\overline{\IR^d})$.
+Since this is a dense subset of bounded continuous functions on $\cmeasures$,
+together these results allow us to apply Theorem~3.9.1 of \citet{EK}.
+
+Next, we prove that the limit solves the martingale properties
+of equations~\eqref{eqn:mgale_problem} and~\eqref{eqn:mgale_variation}
+in Lemma~\ref{lem:limit_mgale}
+basically by checking the generators converge,
+which was mostly done in Section~\ref{sec:population_heuristics}.
 \end{proof}
@@
 % % % % % % % % % % % % %
-\subsection{Tightness of empirical measures}
+\subsubsection{Tightness of empirical measures}
     \label{sec:population_tightness_proofs}
@@
 % % % % % % % % % % % % %
-\subsection{Convergence of generators}
+\subsubsection{Convergence of generators}
     \label{sec:population_generators_proofs}
@@
 
-\begin{lemma}[Convergence of generators for the population process]
+\begin{lemma}[Identifying the limit as a solution to the martingale problem]
+    \label{lem:limit_mgale}
+    \comment{
+        Here we need to check that the martingale property is preserved in the limit.
+        But this maybe can be shorter?}
 As $N \to \infty$,
@@
 % % % % % % % % % % % % %
-\subsection{Uniqueness of the limit}
-    \label{sec:uniqueness_proofs}
-
-Here are the proofs of Corollaries~\ref{cor:nonlocal_pde_limits}
-and \ref{cor:superprocess_uniqueness},
-giving conditions in which the limiting process is unique
-(in which case we have convergence, not just on subsequences).
-
-% % % % % % % % % % % % %
 \subsection{Convergence of the nonlocal equation to the local equation}
 
-\comment{... for the cases in which we know this.
+\comment{... for the cases in which we know this: FKPP-type and PME.
 This then shows that we can take the local, deterministic limit
@@
 
-\subsubsection{Porous Media Equation}
+\subsubsection{Fisher-KPP-type}
+
+\comment{Insert TwoStepConvergenceV3 with Alison's markups incorporated here.}
+
+\subsubsection{Porous Medium Equation}
 
@@
 torus of size $K$, and $T,K>0$ are fixed but arbitrary.
+
+\comment{rephrase/shorten this:}
 
@@
     (We won't prove tightness here.)
+    This is where OneStepConvergence goes in.
 }
@@
 \subsection{Tightness of the Lines of Descent}
+    \label{sec:lookdown_convergence}
+
+Now we prove the main theorem on convergence of the lookdown process, 
+Theorem~\ref{thm:lookdown_convergence}.
+This follows a similar pattern as the the proofs of convergence for the population process
+in Section~\ref{sec:population_density_proof},
+although we will need additional estimates to ensure that
+trajectories of individual lines of descent converge,
+not just the population process.
+
+\begin{proof}[Proof of Theorem~\ref{thm:lookdown_convergence}]
+    As in Section~\ref{sec:population_density_proof},
+    the theorem will follow from tightness,
+    ensuring convergence along subsequences,
+    and characterization of the limit.
+    This time, the processes $\lp^N$ take values in $\lpmeasures$,
+    the space of locally finite measures on space $\times$ levels.
+    (They will in fact be point measures, including the limit,
+    but that is a consequence of this theorem.)
+    Again, tightness will follow from a compact containment condition,
+    tightness of one-dimensional distributions,
+    and an application of \citet{EK} Theorem~3.9.1.
+    We show that the martingale properties are preserved in the limit
+    in Section~\ref{sec:lookdown_generator_proofs}.
+    \comment{TODO: write and refer to lemma?}
+
+    Lines of descent can escape to infinite level in finite time,
+    and so we endow $\lpmeasures$ with the vague topology ``in the level coordinate'',
+    i.e., the topology induced by test functions on $\overline{\IR^d} \times [0,\infty)$
+    of the form $f(x) g(u)$, where $f \in C_b(\overline{\IR^d})$ is bounded and continuous
+    and $g \in C_c([0,\infty))$ is continuous with compact support.
+    In this topology, compact containment follows from
+    tightness of the spatial and level motions of a single line of descent
+    (Lemmas~\ref{lem: tightness of individual spatial trajectory}
+    and~\ref{lem:tightness of levels}, respectively),
+    and
+    tightness of $\lp^N(\IR^d \times [0, u_0])$ for each $u_0$
+    (i.e., the number of individuals with level below $u_0$).
+
+    Finally, we must show that the limiting lookdown process $\lp$
+    projects to the limiting process $\eta$, i.e., a solution of the martingale
+    problem in Theorem~\ref{thm:nonlocal_convergence}.
+    Let $N_k \to \infty$ be a sequence along which $\lp^{N_k}$ converges.
+    However, by Theorem~\ref{thm:nonlocal_convergence},
+    there is a subsequence $N_{k(j)}$ along which the projected population processes
+    $\eta^{N_{k(j)}}$ converge, and the limit solves the martingale problem.
+    This implies that any limit of $\lp^N$ projects to a population process $\eta$
+    solving the martingale problem of Theorem~\ref{thm:nonlocal_convergence}.
+
+\comment{MAKE THIS BELOW A LEMMA?}
+
+% BEGIN OLD STUFF
+To prove that the lookdown representation is tight, we generalise the vague
+    topology to the setting of measure-valued processes. For a detailed
+    description of the vague topology, refer to Appendix \ref{sec: Empirical
+    Measure Topology}.
+
+We will lay out the steps we follow to prove tightness. First of all, we will
+    show that compact containment condition is satisfied if we can control the
+    total mass of particles in our system living in a finite region in space
+    with a level lower than some $u_{*}$. Since a control on total mass has
+    already been shown in Lemma \ref{lem: Compact Containment}, we have
+    immediately established compact containment condition for our lookdown
+    processes.
+
+Then, we apply Theorem A 2.4 in \cite{kallenberg1997foundations} (Theorem
+    \ref{teo: Vague Relative Compactness through Projection}) and use a
+    corollary of Stone-Weierstrass Theorem (Lemma \ref{lem: Dense set for test
+    functions on empirical measures}) to show that our lookdown representation
+    $\{\xi^N_t: N \in \mathbb{N}\}$ is tight as a $\mathcal{M}(\mathbb{R^d}
+    \times [0, \infty])$-valued stochastic process in the vague topology as
+    long as $\{F_g(\xi^N_t): N \in \mathbb{N}\}$ is tight as real-valued
+    stochastic processes for a huge class of $F_g$. Explicitly, $F_g(\xi):=
+    \prod_{(x_i,u_i)\in \xi}g(x_i,u_i)$, where $g(x,u)$ satisfies the property
+    that $g(x,u) = 1 $ for all $u \geq u_{*}$ for some $u_{*}>0$.
+% END OLD STUFF
+
+    The process we consider is similar to the state-dependent branching processes
+    of \citet{KR}, so one might expect that the proofs there would carry over with little change.
+    However, there is an important difference:
+    Recall that the level $U_a(t)$ of a line of descent evolves as
+    $$
+    \dot u 
+    =
+    c(x, \eta)
+    u^2
+    - b(x, \eta) ,
+    $$
+    where
+    \begin{align*}
+        c(x, \eta) &= \frac{\theta}{N} \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q(x, dy) \\
+        \text{and}\qquad
+        b(x, \eta)
+        &=
+        \theta \gamma(x, \eta) \int_{\IR^d} \left(r(y, \eta) - r(x, \eta)\right) q(x, dy)
+        + F(x, \eta) 
+    \end{align*}
+    (see equations \eqref{eqn:level_generator} and \eqref{eqn:b_limit}),
+    where $c(x, \eta) \ge 0$ and $b(x, \eta)$ may take either sign.
+    In \citet{kurtz/rodrigues:2011}, $b$ was bounded above and $c$ was bounded away from zero,
+    so they noted that if $U_a(t) \ge b/c$
+    lines of descent would only move upwards from that time onwards.
+    This allows the processes to be jointly and simultaneously constructed
+    for all values of $N$, with a pointwise embedding
+    of $(\xi^N_t)_{t \ge 0}$ within $(\xi^{M})_{t \ge 0}$ for $b/c < N < M$.
+    In other words, individuals with levels above $N > b/c$ at time $t_0$
+    do not affect $(\lp^N_t)_{t \ge t_0}$,
+    thus allowing a comparison of the number of lines of descent below level $u_0$
+    to a branching process.
+    Although we have provided a
+    joint construction of $\lp^N$ for all $N$ in Section~\ref{sec: individual lines of descent},
+    it does not have this monotonicity:
+    for one thing, $b$ and $c$ depend on the population process $\eta$
+    and so all individuals can affect all other ones (even those with lower levels).
+    Furthermore, in the deterministic case $\theta/N$ and hence $c$ converge to zero,
+    and so lines of descent with arbitrarily high level may drift back downwards.
+    Indeed, this must be the case if the population persists,
+    since in the deterministic case there is no branching.
+    In our case $b$ and $c$ depend on the state of the population,
+    so we have no such monotonicity.
+
+    To get around this,
+    first note that both $b$ and $c$ are uniformly bounded above since $\gamma$, $r$ and $F$ are.
+    Also note that by \plr{TODO},
+    for any $\delta > 0$ we can find a $K$ such that
+    $$
+    \IP\left\{
+        \sup_{0 \le t \le T} \sup_x \smooth{F} \eta_t(x) < K
+        \right\} < \delta,
+    $$
+    uniformly in $N$ and over a compact set of initial conditions.
+    Since $F$ is uniformly continuous, this implies that $\sup_{0 \le t \le T} \sup_x F(x, \eta_t)$
+    is similarly tight,
+    as well as the rate of downward drift of the level of a line of descent,
+    i.e., there is a $\bar b$ such that $b(x, \eta_t) \le \bar b$
+    on a set of probability at least $1-\delta$ as well.
+    Therefore, if $u_1 \ge u_0 + \bar b T$, then
+    $$
+    \IP\left\{
+        \inf_{0 \le t \le T} U_a(t) \le u_0
+        \;\big|\;
+        U_a(0) > u_1
+    \right\}
+    \le \delta ,
+    $$
+    and so with high probability any lines of descent that had level below $u_0$
+    at some point $0 \le t \le T$
+    are descended from lines of descent with initial level below $u_1$.
+    Since the number of lines of descent with level below $u_1$
+    converges to a Poisson with finite mean,
+    we need only show that the number of offpring lines of descent
+    produced by this initially finite number is also tight.
+    However, this follows immediately
+    since the rate of production of new lines of descent with level below $u_1$
+    of a line of descent at location $x$ and level $u$ is
+    $2 (u_1 - u) N^{-1} \theta \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q(x, dy)$
+    and therefore uniformly bounded (because we may take $u_1 \le N$).
+
+\end{proof}
+
+% % % % % % % % % % % % %
+\subsubsection{Tightness of the Lines of Descent}
     \label{sec:lookdown_tightness_proofs}
@@
 
-\begin{lemma} \label{tightness of levels} For fixed $a\in \mathcal{U}$, let $U^N_{a}(\tau_a)=U_0$, i.e. the level of the line of descent $a$ at birth is $U_0>0$.
+\begin{lemma} \label{lem:tightness of levels} For fixed $a\in \mathcal{U}$, let $U^N_{a}(\tau_a)=U_0$, i.e. the level of the line of descent $a$ at birth is $U_0>0$.
 On top of the assumptions laid out in Lemma \ref{lem: tightness of individual spatial trajectory}, assume that 
@@
 % % % % % % % % % % % % %
-\subsection{Proof of convergence for the lookdown process}
-
-The proof of the main result in Section~\ref{sec:lookdown}.
-
-This will depend on Sections~\ref{sec:lookdown_tightness_proofs}
-and \ref{sec:lookdown_generator_proofs}.
-
-% % % % % % % % % % % % %
-\subsection{Convergence of generators for the lookdown process}
+\subsubsection{Convergence of generators for the lookdown process}
     \label{sec:lookdown_generator_proofs}

### 2022-07-03 forwards-and-backwards.tex
.
peter edits

@@
 
+\comment{TO CITE: \citet{ghosh2022emergent}}
+
 As one takes a journey, long or short, the landscape changes:
@@
 The aim of this paper is to understand the implications of a broad class of mechanistic spatial models
-that might describe how such populations live, die, and reproduce:
+that might describe how such spatially heterogeneous populations live, die, and reproduce:
 How does population density change across space and time?
-And, how might we learn about the underlying dynamics from genealogical or genetic data?
+How might we learn about the underlying dynamics from genealogical or genetic data?
+And,  how does genetic ancestry spread across geography,
+when looking back through time in these populations?
 We work with individual-based models of a single species in continuous space,
@@
 
+Reproduction of individuals naturally leads to a branching process.
 There is now a huge literature devoted to spatial branching processes,
@@
 challenges,~\cite{jourdain:2000}.
-Recent work in this 
-direction has been spurred on by applications
-in mathematical finance, %where the porous medium arises 
-in particular, in the study of weak limits of systems
-of diffusions interacting through their 
-rank,~\cite{dembo/shkolnikov/varadhan/zeitouni:2016, jourdain/reygner:2013}
-and references therein.
+% Recent work in this 
+% direction has been spurred on by applications
+% in mathematical finance, %where the porous medium arises 
+% in particular, in the study of weak limits of systems
+% of diffusions interacting through their 
+% rank,~\cite{dembo/shkolnikov/varadhan/zeitouni:2016, jourdain/reygner:2013}
+% and references therein.
 Our approach is different.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Notes to ourselves}
-
-\plr{For recording/discussing notation decisions.}
-
-$X$ is the original, unscaled process,
-and $\eta(t) = X(t\theta)/N$.
-
-When the process has a density, it is $\varphi(t, x) = d \eta_t(dx)/dx$.
-
-$$\lim \frac{\theta}{N} =: \alpha$$
-
-Were not using $\lambda$, but only $N$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Model and main results}
@@
 an ``interaction kernel'' -- which, for simplicity, we take to be Gaussian,
-which we write as
+and we write as
 $$
@@
 and for net reproductive rate over a scale of $\epsilon_F$.
-Note that death rates depend in principle on population densities at three different scales,
+Note that death rate depends in principle on population densities at three different scales,
 so that we could write $\mu = \mu(x, \smooth{\gamma} X(x) / N, \smooth{r} X(x) / N, \smooth{F} X(x) / N)$.
@@
 and that $m^2 \gamma(x, m)$ is uniformly bounded.
-Fix nonnegative values $\epsilon_r$, $\epsilon_\gamma$, and $\epsilon_F$,
+Fix positive values $\theta$, $\epsilon_r$, $\epsilon_\gamma$, and $\epsilon_F$,
 with $\epsilon_r < \epsilon_\gamma$.
@@
 \end{align}
+Although the models will make sense without this requirement,
+for the purposes of convergence we will also require that $\theta > 1/(\epsilon_\gamma - \epsilon_r)$.
 \end{definition}
@@
 $$
-and similarly write $\mu(x, \eta)$  for $\mu(x, \smooth{\mu} \eta(x))$ and $r(x, \eta)$ for $r(x, \smooth{r} \eta(x))$.
+and similarly write $r(x, \eta)$ for $r(x, \smooth{r} \eta(x))$
+and $\mu(x, \eta)$ for the expression of equation \eqref{eqn:mu_defn}.
 When convenient, we may also suppress the arguments completely,
@@
 
-For each $N > 0$ and $\theta \ge 1/(\epsilon_\gamma - \epsilon_r)$,
-the process $\left(\eta^N(t)\right)_{t \ge 0}$
+For each value of $N$ and $\theta$,
+the process $\left(\eta^N_t \right)_{t \ge 0}$
 is the continuous-time measure-valued Markov process described above
@@
 offspring of mass $1/N$ are produced at location $x$
-with rate $\theta \gamma(x, \eta) N \eta_s(dx)$
-and adults die at location $x$ with rate $\theta \mu(x, \eta) N \eta_s(dx)$,
+with rate $\theta \gamma(x, \eta) N \eta(dx)$
+and adults die at location $x$ with rate $\theta \mu(x, \eta) N \eta(dx)$,
 (i.e., at rates $\theta \gamma$ and $\theta \mu$ per capita respectively).
@@
 
-We have just effectively defined the process, but to be completely clear,
+We have just effectively defined the process, but for future use,
 we will now give a formal definition as a solution to a martingale problem.
@@
     \label{defn:mgale_construction},
-We define $(\eta^N_t)_{t \geq 0}$ to be the solution to the Martingale Problem,
+For each value of $N$ and $\theta = \theta(N)$,
+we define $(\eta^N_t)_{t \geq 0}$ to be the solution to the Martingale Problem,
 with initial condition $\eta^N_0 \in \measures$,
-such that for all smooth functions $f \in C^{2}_{0}(\mathbb{R}^d)$,
+such that for all smooth functions $f \in C^{\infty}_{0}(\mathbb{R}^d)$,
 writing $\langle f, \eta \rangle = \int_{\IR^d} f(x) \eta(dx)$
@@
     $q_\theta(x, dy)$,
-    to be the density of a multivariate Normal
+    to be the density of a multivariate Gaussian
     with mean $\meanq(x)/\theta$ and covariance matrix $\covq(x)/\theta$
@@
     \to \DG f(x) 
-        \qquad \text{as } N \to \infty .
+        \qquad \text{as } \theta \to \infty .
     \end{align}
     We will also denote the adjoint of $\DG$ by
-    $$
+    \begin{align*}
     \DG^* f(x)
-        =
+        &=
         \sum_{ij} \partial_{x_i} \partial_{x_j} (\covq(x)_{ij} f(x))
-        - \sum_i \partial_{x_i} (f(x) \meanq(x)_i) .
-    $$
+        - \sum_i \partial_{x_i} (f(x) \meanq(x)_i) 
+        \\
+        &=
+        \text{TODO} .
+    \end{align*}
 \end{definition}
@@
     \theta \gamma(x, \smooth{\gamma} \eta(x))
-    \int r(x, \smooth{r} \eta(y)) q(x, dy) ,
+    \int r(y, \smooth{r} \eta(y)) q(x, dy) ,
 $$
@@
     }{
-        \int r(x, \smooth{r} \eta(z)) q_\theta(x, dz)
+        \int r(z, \smooth{r} \eta(z)) q_\theta(x, dz)
     } .
@@
 Clearly, the random walk driven by this dispersal kernel
-should be biased towards regions of higher establishment probability.
+is biased towards regions of higher establishment probability.
 For comparison to future results,
@@
 \begin{align*}
-    \lim_{N \to \infty}
+    \lim_{\theta \to \infty}
     \theta \int (f(y) - f(x)) q_\theta^\mathfrak{m}(x, \eta, dy)
@@
         - 
-        f(\cdot) \DG\left[ r(\cdot, \smooth{r} \eta(\cdot)) \right](x)
+        f(x) \DG\left[ r(\cdot, \smooth{r} \eta(\cdot)) \right](x)
     }{
@@
 \end{align*}
+One might guess that the spatial motion described by following a lineage of successful individuals back through time
+would be described by this generator in the limit.
 However, we will see that following a lineage back through the population
@@
     be as defined in Definition \ref{def:model_setup}
-    and assume that as $N \to \infty$, $N \to \infty$
+    and assume that as $N \to \infty$, also $\theta \to \infty$
     in such a way that $\theta/N \to \alpha$.
@@
     remain constant.)
-
     The sequence of stochastic processes
@@
     to a measure-valued process $(\eta_t)_{t \geq 0}$
-    which satisfies that, for every $f:\mathbb{R}^d \rightarrow \mathbb{R}$,
+    which satisfies that, for every $f \in C^\infty_0(\IR^d)$,
     \begin{align} \label{eqn:mgale_problem}
@@
             \int_0^t \big\langle
-                \gamma(x, \smooth{\gamma} \eta_{s}(x))
+                \gamma(x, \eta_s)
                 \mathcal{B}\left(
-                    f(\cdot) r(\cdot, \smooth{r} \eta_{s}(\cdot))
+                    f(\cdot) r(\cdot, \eta_s)
                 \right)(x)
@@
                 f(x)
-                F(x, \smooth{F} \eta_{s}(x)),
+                F(x, \eta_s),
                 \eta_{s}(dx)
@@
             \left(\gamma\left( x, \eta_{s} \right)
-            r\left(x, \eta_{s} \right)+\mu\left(x, \eta_{s} \right)\right)
+            r\left(x, \eta_{s} \right) + \mu\left(x, \eta_{s} \right)\right)
             f^2(x),
@@
 Theorem \ref{thm:nonlocal_convergence} provided convergence along subsequences;
-i.e., for any sequence of values of $\theta$
-there is a subsequence that converges.
+i.e., for any sequence of values of $N$
+there is a subsequence along which $\eta^N$ converges.
 However, if the limiting process is unique then the convergence is unqualified.
@@
     has a unique solution,
-    then $(\eta^N(t))_{t \ge 0}$ converges to that solution
+    then $(\eta^N_t)_{t \ge 0}$ converges to that solution
     as $N \to \infty$.
@@
 
-Informally, equation \eqref{eqn:nonlocal_pde} is the PDE
-\begin{align} \label{eqn:pde}
-    \dot \varphi = r \DG^* \left( \gamma \varphi \right) + \varphi F ,
-\end{align}
+Informally, equation \eqref{eqn:nonlocal_pde} is the PDE of Definition~\ref{defn:weak_solutions},
 where $\DG$ is an elliptic second order differential operator,
@@
 for instance, if $\eta_t$ has density $\varphi_t$
-then $\gamma(x, \smooth{\gamma} \eta_t(x)) \to \gamma(x, \varphi_t(x))$ as $\epsilon_\gamma \to 0$.
+then $\gamma(x, \smooth{\gamma} \eta_t(x)) \to \gamma(x, \varphi_t(x))$ as $\epsilon_\gamma \to 0$
+(recalling that $\smooth{\gamma}{}$ denotes convolution with the heat kernel at time $\epsilon_\gamma^2$).
 The following propositions give two concrete situations in which that is true.
@@
 The \emph{lookdown construction} in Section~\ref{sec:lookdown}
-provides just such a construction,
-where lineages are retained in the $N \to \infty$ limit.
+provides just such a construction.
 Roughly speaking,
@@
 but not their ancestry.)
+\comment{NOT RIGHT:}
 We expect the answer here to be that a lineage is Markov

### 2022-07-05 forwards-and-backwards.tex
minor corrections

@@
     and let $y$ be a point with $\varphi_T(y) > 0$.
-    We define $(L_s(y))_{s=0}^T$,
+    We define $(L_s)_{s=0}^T$,
     the ancestral lineage in this population of an individual sampled at $y$ at time $T$,
@@
 remember that everything depends on location and density at that location and time --
-for instance, ``$r$'' is actually $r(x, \varphi(x))$.
+for instance, ``$r$'' is actually $r(x, \varphi(x))$ (in the local case),
+or $r(x, \smooth{r} \eta(x))$ (in the nonlocal case).
 
@@
     In addition to the assumptions of Theorem~\ref{thm:lineages},
-    if the dispersal process is isotropic (i.e., $\covq = \sigma^2 I$),
+    if the dispersal process is isotropic
+    (i.e., $\covq = \sigma^2 I$ and $\meanq$ is constant),
     then
@@
         =
-        \sigma^2 r \gamma
+        r \gamma
         \left(
-            \Delta f
+            \sigma^2 \Delta f
             +
             \left(
-                2 \grad \log(\gamma \varphi)
+                2 \sigma^2 \grad \log(\gamma \varphi)
                 - \meanq
@@
     \end{equation}
+\end{corollary}
+
 In other words, 
+the lineage behaves as a diffusion driven by Brownian motion run at speed 
+\comment{TODO: make this right:}
+If $V_s(x) = \log(\varphi_s(x) \gamma(x, \varphi_s)) - \meanq \cdot x / 2 \sigma^2$,
+then the diffusion has drift $\grad V_s$.
+If $\varphi$ does not change with time, 
+then the stationary distribution is proportional to $\exp(V(x))$.
 a lineage behaves as a diffusion
@@
 ($\varphi_s \gamma \exp(-\meanq \cdot x / 2 \sigma^2)$).
-\end{corollary}
 
@@
 Consulting equation~\eqref{eqn:mu_defn},
-this implies that $\mu = (1 + 1/\theta) \varphi - 1/\varphi$.
+this implies that $\mu = (1 + 1/\theta) \varphi - 1/\theta$.
 In other words,
@@
 \end{align*}
-and set $\mu(x, m) = \max(0, \gamma - \theta F)$.
+and set $\mu(x, m) = \max(0, \gamma - F / \theta)$.
 Birth and death rates are equal at density $m = 1$,
@@
 but started from any compact perturbation of a Heaviside function, the 
-solution will converge to the profile $w^F$ with the minimal wavespeed, $c=2$,
-\cite{kolmogorov/petrovsky/piscounov:1937,bramson:1983}.
+solution will converge to the profile $w^F$ with the minimal wavespeed, $c=2$
+\citep{kolmogorov/petrovsky/piscounov:1937,bramson:1983}.
 No matter the initial condition,
@@
 In this case, we must have $r = \gamma = 1$,
-and $F(x, m) = 1 - m$ so $\mu(x, m) = 1 - (1-m)/\theta$.
+and $F(x, m) = 1 - m$ so $\mu(x, m) = 1 + (m-1)/\theta$.
 This implies that
@@
 \end{align*}
-so lineages in the tip are pushed leftwards into the bulk of the wave by a $-2(e^{-x}+1)^{-1}$,
+so lineages in the tip are pushed leftwards into the bulk of the wave at a rate $-2(e^{-x}+1)^{-1}$,
 that gets weaker further to the left.
@@
 continuous population generated by parameters $\gamma$, $\mu$, and $r$
-with $meanq = 0$ and $\covq = I$.
+with $\meanq = 0$ and $\covq = I$.
 Suppose it has a stationary profile $w(x)$, that must satisfy
@@
 then $\DG = \sigma^2 \Delta$, where $\Delta$ denotes the Laplacian.
-Equation~\eqref{eqn:rewritten mean measure}) then converges to
+
+In summary, equation~\eqref{eqn:rewritten mean measure} converges to
 \begin{equation} \label{limit of mean measure equation}
@@
 informal calculations agree with the main result.
-Suppose that we have tracked a lineage to an individual at location $y$ at time $t$.
+Suppose that we have tracked a lineage back to an individual at location $y$ at time $t$.
 Looking further back through time, the lineage will move at the time that individual was born,
@@
 
-\comment{Should we just use $N$ instead of $\lambda$? Change to $N$ but comment that when comparing ot other papers set $\lambda=N$.}
-
 Now we will present a lookdown construction for the general process
@@
 Furthermore, the levels of the individuals present at any spatial location
-are conditionally uniform on $[0, N]$.
+will be conditionally uniform on $[0, N]$.
 However, an individual's level in some sense encodes their future reproductive output:
@@
 
-\comment{
-    I've defined $\eta = \lp / N$ to agree with how we define the generator below,
-    for which birth/death add/remove something of mass 1, not $1/N$.
-}
-
-\comment{TODO: this uses the $\gamma(x, \eta)$ notation, which we haven't settled on.}
-
 Suppose that the initial population is composed of $O(N)$ many particles
@@
 $$
-which disperses to a location relative to $x$ drawn from the kernel $q(\cdot)$.
+which disperses to a location relative to $x$ drawn from the kernel $q(x, \cdot)$.
 (Averaging over the uniform distribution of the level $u$,
@@
 Since levels are uniform,
-it is easy to check that if $\mu$ was constant,
+it is easy to check that if $\mu$ were constant,
 this would imply an exponential lifetime for each individual;
@@
     +
-    \theta \mu(x,\eta) u .
+    \mu(x,\eta) u .
 \end{equation}
@@
 &\to
-    \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta) \qquad \text{as } N \to \infty .
+    \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta) \qquad \text{as } \theta \to \infty .
 \end{split}
@@
 Since the probability of each is 1/2,
-the contribution of birth to the generator is
+the contribution of birth to the generator maps $f(\lp)$ to
 \begin{align}
-f(\lp) \nonumber
-&\mapsto
+    &
     f(\lp)
@@
     r(y, \eta) q(x, dy)
+    du_1
     \\
@@
         r(y, \eta) q(x, dy)
+        du_1
     \bigg\}
@@
 by one at $(x, u_1)$ and another at $(y, u)$.
-We've written it in this form because the two pieces
+We've rewritten it in this form because the two pieces
 each naturally converge to separate terms in the limit.
@@
 we define $(\lp^{N}_t)_{t \geq 0}$
-to be the (unique) solution
+to be the unique solution
 to the Martingale Problem
@@
     2 \gamma(x, \eta)
-    \Bigg\{ \frac 12 N^{-1}\int_u^N g(x,u_1) du_1
-            \times
+    \Bigg\{ \frac{1}{2N} \int_u^N g(x,u_1) du_1
             \frac{
@@
 So, there is a unique label assigned at each birth event,
-and it is assigned to the resulting individual with the higher level.
+assigned to the resulting individual with the higher level,
+and the label of an individual may change throughout its lifetime.
 It would be possible to reconstruct individual identities along a line of descent
@@
 let $\Pi_a$ be an independent Poisson process on $[0, \infty)^2 \times \IR_d \times \{0,1\}$.
-The mean measure is a product of Lebesgue measure on the first two coordinates,
+The mean measure of each $\Pi_a$ is a product of Lebesgue measure on the first two coordinates,
 the density of the standard Gaussian $N(0,1)$ on $\IR^d$, and $(\delta_0 + \delta_1)/2$ on $\{0, 1\}$.
@@
 If $(t, v, z, \kappa)$ is the $j^\text{th}$ point in $\Pi_a$,
-then $t$ will determine possible birth times,
-$v$ will determine levels of the offspring,
+then $t$ will determine a possible birth time,
+$v$ will determine the level of the offspring,
 $z$ will give the spatial displacement of the offspring relative to the parent,
-$\kappa$ will be used to determine whether parent or offspring are assigned the new level,
+$\kappa$ will be used to determine whether parent or offspring is assigned the new level,
 and the new label produced will be $a \concat j$,
-i.e., the label $a$ with $j$ appended (so, if $a \in \IN_{\ge 0}^k$ then $a \concat j \in \IN_{\ge 0}^{k+1}$).
+i.e., the label $a$ with $j$ appended
+(so, if $a = (a_1, \ldots, a_k)$ then $a \concat j = (a_1, \ldots, a_k, j)$).
 Each label $a$ has a birth time $\tau_a$,
@@
 For any $\tau_a \le t \le \sigma_a$ we denote by $X_a(t)$ and $U_a(t)$ the spatial location and level
-of the individual carrying label $a$ at time $t$.
+of the individual carrying label $a$ at time $t$, respectively.
 Now, since we have defined labels so that the level does not jump,
@@
 Similarly, the potential birth location is 
-$$y(z) = \frac{1}{\theta}\meanq(X_a(\tau_{a+j}-)) + \frac{1}{\sqrt{\theta}}K(X_a(\tau_{a+j}-))z,$$
-where $K(x)K^{T}(x)=\covq(x)$.
-
-For convenience define
-$$
-    \ell(x, y, \eta, v)
+$$
+    y
+    :=
+    \frac{1}{\theta}\meanq(X_a(\tau_{a \concat j}-))
+    +
+    \frac{1}{\sqrt{\theta}}K(X_a(\tau_{a \concat j}-))z,
+$$
+where $K(x)K^{T}(x) = \covq(x)$.
+
+Next we must choose the level of the offspring.
+We would like the individual to produce offspring at $y$ at rate
+$2 (1 - u/N) \theta \gamma(x, \eta) r(x + y, \eta)$,
+and to do this
+we will associate the point $(s, v, w, \kappa) \in \Pi_a$ with level $u + v \ell$,
+where $\ell$ is chosen so that this is the rate of appearance of points in $\Pi_a$
+with level below $N$.
+Since the mean measure of $\Pi_a$ is Lebesgue in the $t$ and $v$ directions,
+this requires that $v < (N - u) / \ell$, 
+and so such points appear at rate $(N-u)/\ell$.
+Therefore, we define
+$$
+    \ell(x, y, \eta)
     =
     \frac{
-        v
+        1
     }{
@@
     +
-    \ell(X_a(\tau_{a \concat j}-), y, \eta(\tau_{a \concat j}-), v) .
+    v \ell(X_a(\tau_{a \concat j}-), y, \eta(\tau_{a \concat j}-)) .
 \end{equation*}
@@
 the new individual labeled $a \concat j$ is produced,
-\plr{TODO: explain why this does the right thing}
+\comment{TODO: explain why this does the right thing}
 and $\kappa$ determines which label is associated with the new location,
@@
 
+\comment{TODO: explain a bit more about the infinitely many points in the $v$ direction.}
+
 \comment{
@@
 \subsubsection{Lines of descent in the scaling limit}
+
+\comment{I don't think we need this.}
 
@@
 &+\sum_{i=1}^{k}
-    \left( \ell(X_{[a]_{i-1}}(\tau_{[a]_{i}}-), y_{[a]_{i}}, \eta(\tau_{[a]_{i}}-), v_{[a]_{i}})
+    \left( \ell(X_{[a]_{i-1}}(\tau_{[a]_{i}}-), y_{[a]_{i}}, \eta(\tau_{[a]_{i}}-)) v_{[a]_{i}}
     \right)
@@
         U_{[a]_k}(\tau_{[a]_k}+s)
-        +\ell(X_{[a]_k}(\tau_{[a]_k}+s),y,\eta_{[a]_k}(\tau_{[a]_k}+s),v) < N
+        + \ell(X_{[a]_k}(\tau_{[a]_k}+s),y,\eta_{[a]_k}(\tau_{[a]_k}+s)) v < N
         \}
@@
 is also fixed -- this is the sequence $(s_k, v_k, y_k, \kappa_k)$ associated with a given label $a$.
-Therefore, the processes $\Gamma_a$ are also unchanged.
+Therefore, the processes $\Pi_a$ are also unchanged.
 First, we clearly need that the spatial projections $\eta$ converge.
@@
 and the state of the population is $\eta$,
+applied to $g(x)$,
 \begin{align*}
-    g(x)
-    &\mapsto
+    &
     \left(1 - \frac{u}{N}\right) \gamma(x, \eta)
     \theta \int_{\IR^d} r(x+y, \eta) (g(x+y) - g(x)) q(x, dy) \\
-    &=
+    &\qquad {}
+    =
     \left(1 - \frac{u}{N}\right) \gamma(x, \eta)
@@
     \bigg\} \\
-    &\to
+    &\qquad {}
+    \to
     \gamma(x, \eta)
@@
         \DG(rg)(x) - g(x) \DG(r)(x)
-    \right) .
+    \right) ,
+    \qquad \text{as} N, \theta \to \infty .
 \end{align*}
@@
 The only thing that remains is to describe how the levels change,
-but this is immediate from applying equation~\eqref{eqn:b_limit}
+but this is immediate from applying limit~\eqref{eqn:b_limit}
 to equation~\eqref{differential equation for level}.
@@
 \begin{proposition}[Line of descent construction]
-Let $\beta(x, \eta) = \meanq + 2 \covq \grad \log r(x, \eta)$
-and $K$ such that $\covq = K K^T$.
+Let $\beta(x, \eta) = \meanq(x) + 2 \covq(x) \grad \log r(x, \eta)$
+and $K(x)$ such that $\covq(x) = K(x) K(x)^T$.
 Associate with each label $a \in \labelspace$
@@
 
+In particular, note that if $\alpha=0$,
+no new lines of descent are produced.
+(More precisely, they are produced but ``at infinity'',
+since the spatial motion of the line of descent is the result of production of these lineages.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     \label{sec:population_tightness_proofs}
-To prove tightness of our population process, 
-we first show that the expected total mass of our population process at some fixed time $T>0$,
-is controlled uniformly across $\theta$.
-This is equivalent to the compact containment condition.
-
+
+To prove tightness of the population process $\eta_t$,
+we first show that the expected total mass at some fixed time $T$
+is controlled uniformly across $N$, a compact containment condition.
 To establish this control,
 we first prove a technical lemma which controls spatial density of our population,
-and then we use the BDG inequality on a martingale
-to give us control over the running supremum of our total population mass.
-
+and then we use the Burkholder-Davis-Gundy inequality \comment{TODO CITE}
+to give us control over the running supremum of the total population mass.
 Once we have control over the total mass of the population, 
@@
 This then allows us to prove that the particle system is tight
-by an application of the Aldous-Rebelleon Criterion.
+by an application of the Aldous-Rebolledo criterion \comment{TODO CITE}.
+
+\comment{summarize and move to the appendix}
 
@@
     \label{lem: gamma - r radius comparison}
-    Assume that $\epsilon_{r}^2 + \frac{1}{\theta} < \epsilon_{\gamma}^2,$ then
+    Under the assumptions of Definition~\ref{def:model_setup},
+    if $\epsilon_{r}^2 + \frac{1}{\theta} < \epsilon_{\gamma}^2,$ then
     for all $f \in \mathcal{C}^{2}_{0}(\mathbb{R}^d \times \mathbb{R})$
@@
 
-With the assumptions on $f$, we can bound the magnitude
-of first and second derivatives with 
-some constants $||Df||_{\infty}$ and $||D^2f||_{\infty}$.
-
+Write $||Df||_{\infty}$ and $||D^2f||_{\infty}$
+for the suprema of the first and second derivatives of $f$
+(which we have assumed are bounded).
 Therefore, we have that 
@@
                         \right|\\ 
-        &~ + |Df||_{\infty} 
+        &~ + ||Df||_{\infty} 
             \left| \theta \int_{\mathbb{R}^d}
@@
             q_{\theta}(x,dy) \right| \\
-        &~ + \frac{1}{2}|D^2f||_{\infty}\left|
+        &~ + \frac{1}{2}||D^2f||_{\infty}\left|
                         \theta \int_{\mathbb{R}^d} (y-x)(y-x)^{T} q_{\theta}(x,dy)
                         \right|\\
-        &~ + \frac{1}{2}|D^2f||_{\infty}    
+        &~ + \frac{1}{2}||D^2f||_{\infty}    
                 \sum_{1 \leq i \leq d}\left|
@@
                     \\
-        &~ + \frac{1}{2}|D^2f||_{\infty} \left|
+        &~ + \frac{1}{2}||D^2f||_{\infty} \left|
             \theta \int_{\mathbb{R}^d}
@@
 with mean $\meanq/\theta$
-and Covariance matrix $\covq / \theta$.
+and covariance matrix $\covq / \theta$.
 As a result, the first and third term
 is easily bounded above by 
+\comment{I'm not sure about the L1 norm in the next two equations:}
 $$||Df||_{\infty} \left|
@@
                         \theta \int_{\mathbb{R}^d} (y-x)(y-x)^{T} q_{\theta}(x,dy)
-                        \right| \leq \frac{1}{2}|D^2f||_{\infty} ||\covq||_{1}.$$
+                        \right| \leq \frac{1}{2}||D^2f||_{\infty} ||\covq||_{1}.$$
 For the cross term, we apply Cauchy's inequality to obtain
+\comment{What's $||C||_{1/2}$?}
 \begin{equation}
@@
 \end{equation}
-We are given that $z\gamma(x,z)$ and $z^2 \gamma(x,z)$ is bounded above
+\comment{We've only assumed boundedness of $z^2 \gamma$! Do we need $z \gamma$ also?}
+We have assumed in Definition~\ref{def:model_setup}
+(for this reason) that $z\gamma(x,z)$ and $z^2 \gamma(x,z)$ is bounded above
 for all $z  \geq 0$.
@@
 \begin{equation}
-F(s)=  \frac{\epsilon^d_r }
+J(s)=  \frac{\epsilon^d_r }
         {\left|\covq s +  \epsilon^2_r I \right|^{1/2}}
@@
 \end{equation}
-then $F(0)=0$ and
+then $J(0)=0$ and
 
 \begin{align}
-F'(s)=&  -\frac{\epsilon^d_r |\covq|}
+J'(s)=&  -\frac{\epsilon^d_r |\covq|}
         {2\left|\covq s +  \epsilon^2_r I \right|^{3/2}}
@@
         \right|
-        \leq&  \theta \left(F\left(1 / \theta \right)-1\right) 
+        \leq&  \theta \left(J\left(1 / \theta \right)-1\right) 
                 \times \epsilon_\gamma^d \epsilon_r^{-d}
                 p_{\epsilon^2_\gamma}(x-w)\\
-         =&  F'(u) 
+         =&  J'(u) 
                 \times \epsilon_\gamma^d \epsilon_r^{-d}
@@
 \end{align}
-for some $u \in [0, 1/\theta]$ by Mean Value Theorem. We have therefore established our bound as $F(s)$ has bounded derivative in a neighbourhood around $0$.
+for some $u \in [0, 1/\theta]$ by Mean Value Theorem. We have therefore established our bound as $J(s)$ has bounded derivative in a neighbourhood around $0$.
 
@@
 q_{\theta}(x,dy).$$
-For the proof of Equation \eqref{eq: gaussian density estimate} refer to the Lemma \ref{eq: Gaussin density estimates} in the Appendix.
+For the proof of Equation \eqref{eq: gaussian density estimate} refer to Lemma \ref{eq: Gaussin density estimates} in the Appendix.
 
@@
     \label{lem: Compact Containment}
-Assume that $\eta^{N}_0 \to \eta_0$ weakly,
-then for all $T>0$, there exists some constant $C(T)$,
+If $\eta^{N}_0 \to \eta_0$ weakly as $N \to \infty$,
+then for all $T>0$, there exists some constant $C_T$,
 such that
@@
         \right]
-        \le C(T) ,
+        \le C_T ,
     \end{align}
@@
         > K_\epsilon \right]
-        \leq \frac{C(T)}{K_{\epsilon}} < \epsilon.    
+        \leq \frac{C_T}{K_{\epsilon}} < \epsilon.    
 \end{equation}
 \end{lemma}
+
 \begin{proof}
-We first take $f \equiv 1$ in Equation \eqref{eq: Pre-limit Martingale Characterisation}. We have that 
+    \comment{TODO: superscript $\theta$ should be $N$ below}
+We first take $f \equiv 1$ in Equation \eqref{eq: Pre-limit Martingale Characterisation}.
+\comment{TODO: Write $[M]_t$ instead of $[M_t]$ for quadratic variation.}
+We have that 
 \begin{equation}
@@
 
-Note that as $\theta/N \to \ell$ and $N \to \infty$,
+Note that as $\theta/N \to \alpha$ and $N \to \infty$,
 the inequality on the right is bounded above by a constant $C(T)$
@@
 As a result 
-
 \begin{equation}
@@
         U_{a}(\tau_{a}+s)
-        +\ell(X_{a}(\tau_{a}+s),y(z),\eta_{a}(\tau_{a}+s),v) < N
+        + \ell(X_{a}(\tau_{a}+s),y(z),\eta_{a}(\tau_{a}+s)) v < N
         \}
@@
 \begin{lemma}\label{eq: Gaussin density estimates}
-\begin{equation}\label{eq: gaussian density estimate}
+\begin{equation}
  \theta H_{\theta}(x,w)\rho_r(x-w)\leq \rho_{\gamma}(x-w),

### 2022-07-05 forwards-and-backwards.tex
alisons comments on first half of onestepconvergence

@@
 
+\todo[inline]{BEGIN OneStepConvergence}
+These notes are an attempt of writing the one-step convergence of the particle system to a PDE limit.
+
+\textbf{In this whole document $\rho_\epsilon$ will be the density of a normal with mean $0$ and variance $\epsilon^2$, and $q_\theta$ the density of a normal with mean $0$ and variance $1/\theta$.
+That is, $\rho_\epsilon(x) = p_{\epsilon^2}(x)$ and $q_\theta = p_{1/\theta}(x)$.}
+
+In this document we assume we have the particle system with (unscaled) birth rate constant and equal $1$ and death rate at position $x$ given by $1+F(\rho_\epsilon*\overline{\eta}(x))/\theta$.
+That is, the martingale problem for the scaled system $\overline{\eta}_t$, is that for any smooth function $\phi$ we can write
+\begin{align}
+&\langle\phi(x),\overline{\eta}_{t}(dx)\rangle-\langle\phi(x),\overline{\eta}_{0}(dx)\rangle = M_t(\phi)   + \int_{0}^{t}\langle \theta  \int_{\mathbb{R}^d} \left( \phi(y)-\phi(x)\right) q_\theta(x,dy), \overline{\eta}_s^\epsilon(dx) \rangle ds \nonumber \\
+ & + \int_0^t \langle  F(\langle \rho_\epsilon(y-x), \overline{\eta}_s(dy) \rangle)\phi(x),\overline{\eta}_s^{\varepsilon, \theta, N}(dx)  \rangle ds. \label{mgp1}
+\end{align}
+where $M_t(\phi)$ is a martingale with quadratic variation:
+\begin{align}
+[M(\phi)]_t&:=\frac{\theta}{N}\int_{0}^{t}\bigg\{ \left\langle \int_{\mathbb{R}^d} \phi^2(y) q_\theta(x,dy), \overline{\eta}_s^{\varepsilon, \theta, N}(dx) \right\rangle \nonumber\\
+&+ \left\langle  \left(1 + \frac{F(\langle \rho_\epsilon(y-x), \overline{\eta}_s(dy)\rangle )}{\theta } \right)\phi^2(x), \overline{\eta}_s^{\varepsilon, \theta, N}(dx))\right\rangle   \bigg\}ds.
+\label{mgp2}
+\end{align}
+
+We have the following result.
+
+\begin{theorem} \label{TeoremOneStepConvergence}
+Let $(\overline{\eta}_t)_{t \geq 0}$ be the scaled particle system with $r_\theta \equiv \gamma_\theta = 1$. Suppose $F(x)$ satisfies:
+\begin{enumerate}
+    \item $F(x)1_{x>0}$  is bounded above.
+    \item $|F'(x)1_{x>0}|$ is bounded,
+    \item and $||F''(x)||_\infty < \infty$.
+\end{enumerate}
+We will also suppose $\theta$ is big enough that $1- \frac{F(x)1_{x>0}}{\theta}$ is non-negative.
+
+We will assume $\overline{\eta}_0:=\overline{\eta}_0(\epsilon,N,\theta)$ is a sequence of initial conditions for $(\overline{\eta}_t)_{t \geq 0}$ such that there exists a finite constant $C>0$ independent of $\epsilon, N, \theta$,
+\begin{enumerate}
+\item $\langle 1 , \overline{\eta}_0 \rangle < C $
+\item  $\Vert \rho_\epsilon * \overline{\eta}_0(x) \Vert_\infty < C$ for all $x \in \mathbb{R}^d$
+\item $|\rho_\epsilon * \overline{\eta}_0(x) - \rho_\epsilon * \overline{\eta}_0(y)| \leq C \Vert x - y \Vert  $ for all $x,y \in \mathbb{R}^d$
+\item $(\rho_\epsilon * \overline{\eta}_0(x) dx) \Rightarrow u_0(x)dx$ for some $u_0(x) \in \mathcal{C}^2(\mathbb{R}^d)$, where $\Rightarrow$ denotes weak convergence. 
+\end{enumerate}
+Furthermore, suppose that,
+\begin{equation}
+\frac{\theta}{\epsilon^d N} + \frac{1}{\theta \epsilon^{2}}\rightarrow 0 \label{ConditionsForConvergence}
+\end{equation}
+Fix $T>0$.
+Then, the measure $((\rho_\epsilon *\overline{\eta}_t)(x) dx)_{t \geq 0}$ converges weakly in $D([0,T], \mathcal{M}_F(\mathbb{R}^d))$ to a measure $(\Xi_t(dx))_{t \geq 0}$.
+Moreover, up to a modification on a set of measure zero, $\Xi_t(x) = u_t(x)dx$, where $u_t(x)$ is a weak solution to:
+\[ \partial_t u = \frac{1}{2}\Delta u + u F(u) \]
+with initial condition $u_0$. That is, for every smooth function with compact support $f$ and $t>0$, we have:
+\begin{equation*}
+ \int \partial_t  u_t(x) f(x) dx = \int u_t(x)\frac{1}{2} \Delta f(x) dx + \int f(x) u_t(x) F(u_t(x)) dx.
+\end{equation*}
+\end{theorem}
+
+ \todo[inline]{Question: Why do we need that regularity on $u_0$?
+I believe all we need is that (\ref{aprox3}) holds, and for that, I am almost sure that $u_0$ only needs to satisfy the first three hypotheses for $\overline{\eta}_0(x)$.
+Furthermore,  if I am not mistaken, those are all implied by $u_0(x) \in L^1(\mathbb{R}^d) \cap L^2(\mathbb{R}^d) \cap \mathcal{C}^1(\mathbb{R}^d)$ in case we want a nice space to put on the result.
+ Alison says: $C^1 \cap L^1$ probably enough, but...
+ }
+
+\todo[inline]{Questions 2: The conditions on $F$ implies that $F(x)1_{x>0} = (A-Bx)1_{x>0}$ for some $A,B>0$, or not?
+At least that is the only polynomial that is bounded above with a bounded derivative.
+Maybe we could rewrite the result for that explicit $F$?
+Note: $F$ no longer assumed polynomial.
+}
+
+To prove this we will proceed in a standard pattern, proving $C$-tightness of the measure and then identifying the limit.
+
+As a preliminary, we will prove some basic tools we are going to need all the way through.
+First, we prove that, under the conditions of Theorem~\ref{TeoremOneStepConvergence}, $\overline{\eta}_t$ has a uniformly bounded total mass in expectation.
+We then prove some regularity estimates of a random walk with Gaussian jumps.
+While this may seem disconnected from our goal the generator of this random walk is in the first integral element that appears in the martingale problem for $\overline{\eta}_t$, equation (\ref{mgp1}).
+It is then, no surprise, that we need some control over the regularity this term brings to our particle system.
+
+We then focus on $C$-tighness of $\rho_\epsilon * \overline{\eta}_t(x)dx$.
+For this we will prove that for fixed $x$, the random variable $\rho_\epsilon*\overline{\eta}_t(x)$ has uniformly bounded expectation.
+Using this and the regularity of the random walk mention above, we will be able to prove the $C$-tightness of $\rho_\epsilon * \overline{\eta}_t(x)dx$.
+
+Then we will proceed to identify the limit.
+For this, a continuity estimate for $(\rho_\epsilon*\overline{\eta}_t(x))$ is needed, which is again a consequence of the random walk estimates mentioned above.
+Using this we focus on controlling the convergence of \textit{non-linear terms} in the martingale problem of $(\rho_\epsilon*\overline{\eta}_t(x))$ (as the others converge as a consequence of weak convergence).
+Those do not converge as a consequence of weak convergence, since they are not written as an integral on $M^{\otimes k}(\mathbb{R}^d)$ of $(\rho_\epsilon*\overline{\eta}_t(x) dx)$ (for some $k \in \mathbb{N}$).
+Instead, we will first compare the quadratic terms to terms only involving $\rho_\epsilon*\overline{\eta}_s$ (and not $\overline{\eta}_s(dy)$) and then we will exchange those terms with a suitable integral in $M^{\otimes2}(\mathbb{R}^d)$, for which convergence do follow easily.
+
+\subsubsection{Preliminaries}
+
+\paragraph{Boundedness of the total mass}
+\begin{lemma} \label{Lemma:UniformlyBoundedMass}
+Under the assumptions of Theorem~\ref{TeoremOneStepConvergence}, there is a finite constant $C$ (independent of $\epsilon, N, \theta$), such that $\IE\left[ \sup_{0 \leq s \leq T} \langle 1, \overline{\eta}_s \rangle \right] \leq C$.
+\end{lemma}
+\begin{proof}
+By putting $\phi(x)=1$ in the martingale problem of $\overline{\eta}_t$, equation (\ref{mgp1}), we have,
+\begin{align} \label{eq:MPTotalMass}
+\langle 1, \overline{\eta}_t \rangle &= \langle 1, \overline{\eta}_0 \rangle + \int_0^t \langle F(\rho_\epsilon * \overline{\eta}_s), \overline{\eta}_s \rangle ds + M_t
+\end{align}
+where $M_t$ is a martingale with quadratic variation,
+\begin{align} \label{eq:QVTotalMass}
+[M]_t = \frac{\theta}{N}\int_0^t \langle 1 + \frac{F(\rho_\epsilon* \overline{\eta}_s)}{\theta}, \overline{\eta}_s \rangle d s 
+\end{align}
+By taking expectations in (\ref{eq:MPTotalMass}) we get,
+\[ \IE[\langle 1, \overline{\eta}_t \rangle] =  \IE[\langle 1, \overline{\eta}_0 \rangle]  + \IE[ \int_0^t \langle F(\rho * \overline{\eta}_s), \overline{\eta}_s \rangle ds ]   \leq C +   C \mathbb{E}\left[ \int_0^t \langle 1, \overline{\eta}_s \rangle ds \right].\]
+In last inequality we used that $F(x)1_{x >0}$ and $\langle 1, \overline{\eta}_0 \rangle$ are uniformly bounded above.
+By Gronwall's inequality we deduce $\IE[\langle 1, \overline{\eta}_s \rangle]$ is bounded on $[0,T]$.
+Hence, by taking expectations in (\ref{eq:QVTotalMass}) and using again the bound on $F(x)1_{x>0}$ we get,
+\begin{equation} \IE\left[ [M]_t \right] \leq \frac{\theta}{N} C \int_0^t \mathbb{E}\left[ \langle 1, \overline{\eta}_s \rangle ds \right] \leq \frac{\theta}{N}C t \label{eq:quadvarMass} \end{equation}
+Note that, with this, $\IE[ [M]_t]$ is bounded (and in fact $\mathcal{O}(\theta/N)$). By the Burkholder-Davis-Gundy inequality and then Jensen's inequality we get
+\begin{align*}
+    \IE\left[ \sup_{0 \leq t \leq T} M_t \right]
+    \leq
+    C \IE\left[ [M]_T \right]^{1/2}
+    \leq
+    C \IE[M]_T^{1/2}
+    \leq
+    C  
+\end{align*}
+Taking supremum and then expectation in (\ref{eq:MPTotalMass}) and using the last inequality gives the result.
+
+    \comment{Alison says: I'd actually write out
+    $\sup \langle 1, \eta_s \rangle \le \int_0^T xxx ds + \sup M_t$ .
+    }
+
+\end{proof}
+
+We will require also a second moment bound on the total mass.
+
+\begin{proposition}
+Under the assumptions of Theorem~\ref{TeoremOneStepConvergence} there is a finite constant $C$ (independent of $\epsilon, N, \theta$) such that, for all $t \in [0,T]$ and for big enough $N$ and $\theta$, $\IE[ \langle 1, \overline{\eta}_t \rangle^2] \leq C$.\label{Prop:SecondMomentMass}
+\end{proposition}
+
+\comment{Alison says: Just use the martingale problem and boundedness of $F$ and Gronwall I think. (The proof below is false.)}
+
+\begin{proof}
+By using in (\ref{eq:MPTotalMass}) that, by assumption, $\langle 1, \overline{\eta}_0 \rangle$  and $F(x)1_{x > 0}$ are bounded above we get,
+\begin{align*}
+ \langle 1, \overline{\eta}_t \rangle^2 \leq C \langle 1, \overline{\eta}_t \rangle + C\langle 1,\overline{\eta}_t \rangle \int_0^t \langle 1, \overline{\eta}_s\rangle ds + M_t \langle 1, \overline{\eta}_t \rangle \end{align*}
+Taking expectation we obtain,
+\begin{align*}
+\IE[ \langle 1, \overline{\eta}_t \rangle^2 ]
+    & \leq
+    C \IE[\langle 1, \overline{\eta}_t \rangle] + C\IE[  \langle 1,\overline{\eta}_t \rangle \int_0^t \langle 1, \overline{\eta}_s\rangle ds ] + \IE[ M_t \langle 1, \overline{\eta}_t \rangle] \\
+    & \leq
+    C +
+    C\IE[\frac{1}{2} \langle 1, \overline{\eta}_t\rangle^2] + \frac{1}{2} \IE[t \int_0^t \langle 1, \overline{\eta}_s \rangle^2 ds ] + (\IE[M_t^2] \IE[\langle 1, \overline{\eta}_t \rangle^2])^{1/2}
+\end{align*}
+where in the second inequality we have used Lemma~\ref{Lemma:UniformlyBoundedMass} on the first term, that $2ab \leq a^2 + b^2$ and Jensen's inequality in the second term and Holder's inequality in the third term.
+Note that by the Burkholder-Davis-Gundy inequality and (\ref{eq:quadvarMass}) we have that,
+\[ \IE[ M_t^2 ] = \mathcal{O}\left( \frac{\theta}{N} \right). \]
+Hence, by using that for positive $a$ we have $a^{1/2} \leq a+1$ we can deduce that,
+\comment{Alison says: but you don't have $C < 1$, so not clear how you're doing this.}
+\begin{align*}
+\frac{1}{2} \IE[ \langle 1, \overline{\eta}_t \rangle^2 ] \leq C + \frac{1}{2} \IE[t \int_0^t \langle 1, \overline{\eta}_s \rangle^2 ds ] + \mathcal{O}\left( \left(\frac{\theta}{N}\right)^{1/2} \right) +\mathcal{O}\left( \left(\frac{\theta}{N}\right)^{1/2} \right) \IE[\langle 1, \overline{\eta}_t \rangle^2].
+\end{align*}
+Let $\theta$ and $N$ big enough so $\theta/N < 1/16$. From the last equation we then can deduce,
+\[ \frac{1}{4}\IE[ \langle 1, \overline{\eta}_t \rangle^2 ] \leq C + \frac{C}{2} t \int_0^t\IE[\langle 1, \overline{\eta}_s \rangle^2 ] ds\]
+An application of Grownwall's inequality yields
+\[ \IE[ \langle 1, \overline{\eta}_t \rangle^2 ] \leq C \exp(2 C t^2) \leq C \exp(2 C T^2),  \]
+finishing the proof.
+\end{proof}
+
+\paragraph{Regularity estimates of the density of a independent Gaussian random walk}
+Let us write $\mathcal{L}^\theta f(x) := \theta \int (f(y)-f(x))q_\theta(x,y) dy$ with $q_\theta$ is a Gaussian kernel of mean $0$ and variance $1/\theta$.
+We note that $\mathcal{L}^\theta$ is the generator of a continuous random walk, where at rate $\theta$ we have the arrival of Gaussian jumps of mean $0$ and variance $1/\theta$.
+
+In what follows we let $\psi_t^{\epsilon, x}(y)$ be the solution of:
+\begin{equation} \frac{\partial}{ \partial_t} \psi_t^{\epsilon,x} = \mathcal{L}^\theta \psi_t^{\epsilon, x} \label{AlmostHeatEquation} \end{equation}
+with initial condition $\psi_0^{\epsilon,x}(y) = \rho_\epsilon(y-x)$. We have the following result for $\psi_t^{\epsilon,x}$.
+
+\begin{lemma} \label{PsiBoundHS}
+Fix $t>0$ and let $T(t)$ be a random variable such that $\theta T(t) \sim Poisson(\theta t)$. Then:
+\[ \psi^{\epsilon,x}_t(y) = \mathbb{E}\left[ p_{\epsilon^2+T(t)}(x,y)\right] \]
+Moreover,
+\[ \Vert \psi^{\epsilon,x}_t \Vert_\infty \leq \mathcal{O}\left( \frac{1}{(t+\epsilon^2)^{d/2}} + \frac{1}{\epsilon^2 \theta} \right) \]
+\end{lemma}
+\begin{proof}
+The first claim of this result follows immediately from $\mathcal{L}^\theta$ being the generator of a continuous random walk, where Gaussian jumps with mean $0$ and variance $1/\theta$ arrive at rate $\theta$.
+
+For the second claim we note that $T(t)-t$ has mean $0$ and variance $t/\theta$.  So by Chebyshev's inequality we get,
+\begin{equation}
+\IP\left[  \frac{|T(t)-t|}{\epsilon^2+t} > \frac{1}{2} \right] \leq \frac{4t}{\theta(\epsilon^2+t)^2} \leq \frac{2}{\epsilon^2 \theta}. \label{eq:IneqConcentrationT}
+\end{equation}
+Thus, by using standard bounds for the heat semigroup we get that,
+\begin{align*}
+\Vert \psi^{\epsilon,x} \Vert_\infty & \leq \IE\left[  \frac{1}{2 \pi (\epsilon^2+T(t))^{d/2}}\right] \\ & = \frac{1}{(2 \pi(\epsilon^2+t)^{d/2}} \IE\left[\left(\frac{1}{1+\frac{T(t)-t}{\epsilon^2+t}} \right)^{d/2} \right] \\ &\leq \frac{\pi^{-d/2}}{(\epsilon^2+t)^{d/2}} + \frac{2}{\epsilon^2 \theta}
+\end{align*}
+where in the last inequality we partition over $\{ |T(t)-t| > (\epsilon^2+t)/2\}$ and its complement, and use (\ref{eq:IneqConcentrationT}).
+\end{proof}
+We will need a further comparison of $\psi_t^{\epsilon,x}$ to the heat semigroup.
+\begin{lemma}
+For every $x,y \in \mathbb{R}^d$ and $t>0$ we have,
+\begin{align*}
+|\psi_t^{\epsilon,x}(y) - p_{\epsilon^2+t}(x,y)| &\leq \frac{C}{\epsilon^2 \theta}\left(\psi_t^{\epsilon,x}(y) + p_{\epsilon^2+t}(x,y) + p_{3/2(\epsilon^2+t)}(x,y)+p_{3(\epsilon^2+t)}(x,y) \right)
+\end{align*} \label{Lemma:BoundPsiHS2}
+\end{lemma}
+\begin{proof}
+From Lemma~\ref{PsiBoundHS} we have that $\psi_t^{\epsilon,x} = \IE\left[ p_{N(t)/\theta+\epsilon^2}(x,y) \right]$ with $N(t)$ a Poisson process of rate $\theta$.
+We write $\tau(t) = N(t)/\theta - t$, which has mean $0$ and variance $t/\theta$.
+In particular,
+equation~\eqref{eq:IneqConcentrationT} says that
+\begin{equation}
+\IP[|\tau(t)| > (\epsilon^2+t)/2] \leq \frac{4t}{\theta(\epsilon+t)^2} \leq \frac{2}{\theta \epsilon^2} \label{eq:ConcentrationTau}
+\end{equation}
+Consider first the event in which $|\tau(t)| \leq (\epsilon^2+t)/2$. For such $\tau$ we have that,
+\begin{equation} |p_{\epsilon^2+t+\tau(t)}(x,y) - p_{\epsilon^2+t}(x,y) | = |\tau(t)| \left| \frac{\partial p_s(x,y)}{\partial s} \right| \end{equation}
+for some $s \in (\epsilon^2+t-|\tau(t)|, \epsilon^2+t+|\tau(t)|)$. Without loss of generality we suppose $x=0$ and write $p_s(y):=p_s(0,y)$ to simplify notation. Then,
+\[ \frac{\partial}{\partial s} \frac{1}{(2 \pi s)^{d/2}} \exp(-\frac{\Vert y \Vert^2}{2s}) = - \frac{d}{s} p_s(y) + \frac{y^2}{2 s^2} p_s(y)\]
+Now for $s \in ((\epsilon^2+t)/2,3(\epsilon^2+t)/2)$ we have,
+\[ p_s(y) \leq 3^{d/2} p_{3/2(\epsilon^2+t)}(y) \, \, ,\text{ and } \, \, \frac{1}{s} \leq \frac{2}{\epsilon^2+t}\]
+Morever, since $\frac{y^2}{4s} e^{-y^2/4s} \leq 1$ for all $y$,
+\begin{align*}
+\frac{y^2}{s^2}  p_s(y) &= \frac{1}{s} \frac{4}{(2 \pi s)^{d/2}}\exp(-\frac{y^2}{4s}) \frac{y^2}{4s} \exp( - \frac{y^2}{4 s}) \\ &\leq  4\frac{ 2^{d/2}}{s} p_{2s}(y) \\ &\leq \frac{4}{s}  2^{d/2} 3^{d/2} p_{3(\epsilon^2+t)}(y)  \\ & \leq 8 \frac{ 2^{d/2} 3^{d/2}}{\epsilon^2+t} p_{3(\epsilon^2+t)}(y)
+\end{align*}
+Combining these estimates
+    \comment{Alison says: Not quite. Can bound the second term this way, but for the first it doesn't work.
+    So use a uniform bound of $1/\varepsilon^d$ and then a bound on the probability that $|\tau|$
+    is this big based on the moment generating function.
+    We end up needing $|\log \varepsilon| / (\theta \varepsilon^2) \to 0$.
+    }
+\begin{align*}
+|\psi_t^{\epsilon,x}(y)-p_{\epsilon^2+t}(x,y)|
+    &=
+    | \mathbb{E}\left[ (1_{|\tau(t)| > (\epsilon^2+t)/2}+1_{|\tau(t)| \leq (\epsilon^2+t)/2})(p_{t+\epsilon^2+\tau(t)}(x,y)-p_{\epsilon^2+t}(x,y)) \right]| \\
+    &\leq
+    \IP[|\tau(t)| \geq (\epsilon^2+t)/2] \IE[p_{t+\epsilon^2+\tau(t)}(x,y) + p_{\epsilon^2+t})(x,y)] \\
+    &+
+    \mathbb{E}\left[ \frac{|\tau(t)|}{\epsilon^2+t}\right]\left( 2d3^{d/2} p_{3(\epsilon^2+t)/2} (x,y) + 4 2^{d/2}3^{d/2} p_{3(\epsilon^2+t)}(x,y)\right) \\
+    & \leq
+    \frac{2}{\theta \epsilon^2} (\psi_t^{\epsilon,x}(y)+p_{\epsilon^2+t}(x,y)) + \mathbb{E}\left[ \frac{|\tau(t)|}{\epsilon^2+t}\right] C (p_{3/2(\epsilon^2+t)}(x,y) + p_{3(\epsilon^2+t)}(x,y))
+\end{align*}
+Finally, since
+\[ \mathbb{E}\left[ \frac{|\tau(t)|}{\epsilon^2+t}\right] \leq \mathbb{E}\left[ \frac{\tau(t)^2}{\epsilon^2+t}\right] \leq \frac{1}{2 \theta \epsilon^2} \]
+the result follows.
+\end{proof}
+The last result will be useful when combined with the next bound for the heat kernel.
+\begin{lemma}
+Let $s>0, x, y, z\in \mathbb{R}^d$. The following estimate holds
+\[ |p_s(x,z) - p_s(y,z)| \leq \frac{C|x-y|}{\sqrt{s}} \left(p_{2s}(x,z) + p_{2s}(y,z)\right) \]
+where the constant $C$ does not depend on $x,y,z$ or $s$.\label{Lemma:ContinuityHS}
+\end{lemma}
+\begin{proof}
+Expanding the difference of two squares we can rewrite,
+\begin{align*}
+&\exp\left(-\frac{(y-z)^2}{2 s} \right)-\exp\left(-\frac{(x-z)^2}{2 s} \right) \\ &= \left(\exp\left(-\frac{(y-z)^2}{4 s} \right)-\exp\left(-\frac{(x-z)^2}{4 s} \right) \right)\left(\exp\left(-\frac{(y-z)^2}{4 s} \right)+\exp\left(-\frac{(x-z)^2}{4 s} \right) \right)
+\end{align*}
+by using the Intermediate Value Theorem we can write the right hand side as,
+\[ (y-x) \left( - \frac{2(w-z)}{4s} \exp\left(-\frac{(w-z)^2}{4s}\right)\right) 2^{d/2}\left( p_{2s}(y,z)+p_{2s}(x,z) \right)\]
+for some $w \in [y,z]$. Using the fact that $x e^{-x^2}$ is uniformly bounded we can bounded the first bracket in the last equation by $C/\sqrt{s}$ and the result follows.
+\end{proof}
+
+\paragraph{The martingale problem for a time dependent function.}
+Before proceeding we make the following observation. For any time, dependent function $\phi_t(x)$ the martingale problem for $\overline{\eta}_t$, (\ref{mgp1}), gives that
+\comment{Alison says: not sure this needs spelling out? (Also, $\partial_t \phi_{t-s}$ is a slightly confusing way to write it out but OK.}
+\begin{align}
+\langle \overline{\eta}_t(dx), \phi_0(x)\rangle &= \langle \overline{\eta}_0(dx), \phi_t(x)\rangle +  M_t(\phi_\cdot(\cdot)) - \int_0^t \langle \partial_t \phi_{t-s}(x), \overline{\eta}_s(dx) \rangle  ds \nonumber \\ & + \int_0^t \langle \mathcal{L}^\theta \phi_{t-s}(x), \overline{\eta}_s(dx) \rangle ds+ \int_{0}^t \langle \phi_{t-s}(x)F (\rho_\epsilon*\overline{\eta}_s)(x) ) , \overline{\eta}_s(dx) \rangle ds \label{timeMGP}
+\end{align}
+where $M_t(\phi_\cdot(\cdot))$ has quadratic variation:
+\[ [M(\phi_\cdot(\cdot))]_t = \frac{\theta}{N}\int_0^t \langle \int_{\mathbb{R}^d} \phi_{t-s}(z)^2 q_\theta(y,dz) + \left( 1 + \frac{F(\rho_\epsilon*\overline{\eta}_s(y))}{\theta}\right) \phi_{t-s}(y)^2, \overline{\eta}_s(dy) \rangle ds \]
+
+%%%%%%%%%%%%%%%%%%
+\subsubsection{Tightness}
+
+\paragraph{Bounds for $\{ \rho_\epsilon * \overline{\eta}_s (x)\}_{0 \leq s \leq T}$}
+\begin{lemma} \label{FirstBoundLocalDensity}
+Under the conditions of Theorem~\ref{TeoremOneStepConvergence} there is a constant $C>0$ (independent of $\epsilon, N, \theta, x$ and $T$) such that,
+\[ \IE[ \rho_\epsilon*\overline{\eta}_t(x) ] < C \]
+for all $t \in [0,T]$ and $x \in \mathbb{R}^d$.
+\end{lemma}
+\begin{proof}
+Recall that $\psi_t^{\epsilon,x}$ is the solution of (\ref{AlmostHeatEquation}) with initial condition $\psi_0^{\epsilon,x}(y)=\rho_\epsilon(y-x)$.
+By replacing $\phi_t$ with $\psi_t^{\epsilon,x}$ in (\ref{timeMGP}) we can write,
+\begin{align}
+(\rho_\epsilon*\overline{\eta}_t(x)) = \langle \psi_t^{\epsilon,x}(y), \overline{\eta}_0(dy) \rangle  + \int_0^t \langle \psi_{t-s}^{\epsilon,x}(y) F(\rho_\epsilon*\overline{\eta}_s(y)), \overline{\eta}_s(dy) \rangle ds + M_t(x) \label{MartingaleProblemMolifier}
+\end{align}
+where $F$ is uniformly bounded above. Hence, if we take expectations,
+\begin{align}
+\IE[\rho_\epsilon * \overline{\eta}_t(x)]
+    &\le
+    \IE[\langle \psi_t^{\epsilon,x}(y), \overline{\eta}_0(dy) \rangle] + C \IE[\int_0^t \langle \psi_{t-s}^{\epsilon,x}(y), \overline{\eta}_s(dy) \rangle ds] \nonumber \\ & \leq  \IE[\langle p_{\epsilon^2+T(t)}(x,y),\overline{\eta}_0(dy)\rangle] + C \int_0^t \Vert \psi_{t-s}^{\epsilon,0} \Vert_\infty \IE[\sup_{0 \leq s \leq t} \langle 1, \overline{\eta}_s(dy) \rangle] ds \\ & \leq C + C \int_0^t \Vert \psi_{t-s}^{\epsilon,0} \Vert_\infty ds \label{BoundForMolifier}
+\end{align}
+Where in the last inequality we used Lemma~\ref{Lemma:UniformlyBoundedMass} and our first assumption on the initial condition.
+Furthermore, using Lemma \ref{PsiBoundHS} we can bound $\Vert \psi_{t-s}^{\epsilon,0} \Vert_\infty$ by $C (t-s+\epsilon^2)^{-d/2}$.
+In dimension one the right hand side is immediately uniformly bounded.
+For $d=2$ we can iterate.
+By using again the martingale problem and the same arguments we used to get (\ref{BoundForMolifier}) we get,
+\begin{equation} \label{IterationBoundPsi}
+\IE[\langle \psi_{t-s}^{\epsilon,x}, \overline{\eta}_s(dy)\rangle] \leq \IE[\langle \psi_{t}^{\epsilon,x}(y), \overline{\eta}_0(dy) \rangle]  + C \int_0^s \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du
+\end{equation}
+Hence, using (\ref{IterationBoundPsi}) in (\ref{BoundForMolifier}) gives
+\begin{align*}
+\IE[ \rho_\epsilon * \overline{\eta}_t(x)  ] &\leq \IE[\langle \psi_t^{\epsilon,x}(y), \overline{\eta}_0(dy) \rangle] + \int_0^t C\langle \psi_{t}^{\epsilon,x}, \overline{\eta}_0(dy)\rangle ds + C^2 \int_0^t \int_0^s  \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du ds \\ &= (1+Ct) \IE[ \langle \psi_t^{\epsilon,x}, \overline{\eta}_0(dy) \rangle] + C^2 \int_0^t (t-u) \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du \\ &\leq C(1+t) + C^2 \int_0^t (t-u) \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du
+\end{align*}
+which again is uniformly bounded using Lemma \ref{PsiBoundHS}. It is easy to see that, iterating, we can prove a uniform bound in any dimension.
+
+\end{proof}
+
+\begin{remark} \label{Remark:BoundLocalDensity}
+It is convenient to remark that from $\IE\left[ \langle \rho_\epsilon(x,y), \overline{\eta}_t(dy) \rangle \right]$ being bounded it follows that $\IE[ \langle p_{s+\epsilon^2}(x,y), \overline{\eta}_t(dy) \rangle ]$ is bounded for all $s>0$.
+Indeed, this follows from writing $p_{s+\epsilon^2} = p_s * p_{\epsilon^2}$ and integrating.
+\end{remark}
+
+\begin{corollary}
+Let $(M_t(x))_{t \geq 0}$ be the martingale in (\ref{MartingaleProblemMolifier}). Then
+\[ \IE\left[ [M(x)]_t \right] \leq \frac{C \theta}{ N \epsilon^{d}} \]
+where $C$ is independent of $\epsilon,\theta,N$. \label{Cor:ControlQVMQ}
+\end{corollary}
+\begin{proof}
+We can explicitly write the quadratic variation of $M_t$ as
+\[ [M(x)]_t = \frac{\theta}{N} \int_0^t \langle \int_{\mathbb{R}^d} \psi_{t-s}^{\epsilon,x}(z)^2 q_\theta(y,dz) + \left(1+\frac{F(\rho_\epsilon * \overline{\eta}_s(y))}{\theta}\right)\psi_{t-s}^{\epsilon,x}(y)^2, \overline{\eta}_s(dy) \rangle  ds\]
+so Lemma~\ref{PsiBoundHS} gives the following bound,
+\[ \psi_{t-s}^{\epsilon,x}(y)^2 \leq \psi_{t-s}^{\epsilon,x}(y) \frac{C}{(\epsilon^2+t-s)^{d/2}} \leq \frac{C}{\epsilon^d} \psi_{t-s}^{\epsilon,x}(y). \]
+Hence, by using the last inequality and the upper bound on $F(x)1_{\{x > 0\}}$, we deduce that:
+\begin{align}
+[M(x)]_t &\leq \frac{C \theta}{\epsilon^d N} \int_0^t \left\{  \langle \int \psi_{t-s}^{\epsilon,x}(z) q_\theta(y,dz), \overline{\eta}_s(dy) \rangle + \langle \psi_{t-s}^{\epsilon,x}(y), \overline{\eta}_s(dy)\rangle \right\} ds
+\label{QuadVarBound} \end{align}
+Taking expectations and using the bound of Lemma~\ref{FirstBoundLocalDensity} we get the result.
+\end{proof}
+
+By reusing the computations in the last Corollary we can prove a certain integrability of $M_t(x)$.
+\begin{proposition}
+Let $(M_t(x))_{t \geq 0}$ be the martingale in (\ref{MartingaleProblemMolifier}). Then
+\[ \int \IE\left[ M_t(x)^2 \right] dx \leq \frac{C \theta}{ N \epsilon^{d}} \]
+where $C$ is independent of $\epsilon,\theta,N$. \label{IntegrabilityOfM}
+\end{proposition}
+\begin{proof}
+Recall that since $M_t(x)$ is a martingale, then,
+\[ \IE\left[ M_t(x)^2 \right] = \IE\left[ [M(x)]_t \right].  \]
+Hence, using (\ref{QuadVarBound}),
+\begin{align*}
+\int &\IE\left[ M_t(x)^2 \right] dx \\ & \leq \frac{C \theta}{\varepsilon^d N} \int \int_0^t \IE\left[ \langle \int \psi_{t-s}^{\epsilon,x}(z) q_\theta(y,dz), \overline{\eta}_s(dy) \rangle + \langle \psi_{t-s}^{\epsilon,x}(y), \overline{\eta}_s(dy)\rangle \right] ds  dx \\ &=  \frac{C \theta}{\varepsilon^d N}  \int_0^t \IE \left[  \langle \int \left( \int \psi_{t-s}^{\epsilon,x}(z) dx \right) q_\theta(y,dz), \overline{\eta}_s(dy) \rangle + \langle \left( \int  \psi_{t-s}^{\epsilon,x}(y) dx \right), \overline{\eta}_s(dy)\rangle \right] ds.
+\end{align*}
+Now using Lemma~\ref{PsiBoundHS} we have that,
+\begin{align*}
+\int \psi_t^{\epsilon, x}(y) dx & = \int \IE[p_{\epsilon^2+T(t)}(x,y)] dx \\ &= \IE[ \int p_{\epsilon^2+T(t)}(y,x) dx ] = 1.
+\end{align*}
+Thus,
+\begin{align*}
+\int \IE\left[ M_t(x)^2 \right] dx & \leq  \frac{C \theta}{\varepsilon^d N}  \int_0^t \IE \left[  \langle \int  q_\theta(y,dz), \overline{\eta}_s(dy) \rangle + \langle 1, \overline{\eta}_s(dy)\rangle \right] ds.
+\\ & \leq \frac{C \theta}{\varepsilon^d N} \int_0^t \IE[ \langle 1, \overline{\eta}_s(dy) \rangle ] ds \\ & \leq T \frac{C \theta}{ \varepsilon^d N}
+\end{align*}
+proving the result.
+\end{proof}
+
+By doing the same pattern used to prove Proposition~\ref{Prop:SecondMomentMass} (replacing the use of equation (\ref{eq:MPTotalMass}) by equation (\ref{MartingaleProblemMolifier}) and the used of equation \ref{eq:quadvarMass} by Corollary~\ref{Cor:ControlQVMQ}) we can get the following result.
+\comment{Alison writes: the proof of Proposition~\ref{Prop:SecondMomentMass} above was wrong.
+I think using $\theta/(N \varepsilon^d) \to 0$ this is easy, but should maybe write it out.}
+
+\begin{proposition}
+Under the assumptions of Theorem~\ref{TeoremOneStepConvergence} there is a finite constant $C$ (independent of $\epsilon, N, \theta$) such that, for all $t \in [0,T]$, $x \in \mathbb{R}^d$ and for big enough $N$ and $\theta$, $\IE[ (\rho_\epsilon*\overline{\eta}_t(x))^2] \leq C$.\label{Prop:SecondMomentDensity}
+\end{proposition}
+
+\paragraph{$C$-tightness of $\rho_\epsilon * \overline{\eta}_t(x) dx$ }
+\begin{lemma}
+Under the assumptions of Theorem~\ref{TeoremOneStepConvergence} the sequence of measure valued process $\{ \rho*\overline{\eta}_t(x) dx \}_{t \geq 0}$ (taking values in $D([0,T], \mathcal{M}_F(\mathbb{R}^d))$ is $C$-tight.
+\end{lemma}
+\begin{proof}
+
+Let $f \in C_c^2$ (that is, compactly supported and with smooth second derivative).
+We will show convergence of $\int f(x) \rho_\epsilon * \overline{\eta}_t(x) dx$ (which is enough to establish weak convergence of the measures $\rho_\epsilon * \overline{\eta}_t(x) dx$).
+\comment{Alison writes: no it's not weak - this would be vague convergence. Take $f \in C^2$ to mean bounded first and second derivatives, which is weak convergence.}
+For this note that,
+\begin{align*}
+\int f(x) \rho_\epsilon * \overline{\eta}_t(x) dx &= \int \int f(x) \rho_\epsilon (x-y) \overline{\eta}(dy) dx \\ & = \langle \int f(x) \rho_\epsilon(x-y) dx, \overline{\eta}(dy) \rangle \\ &= \langle T_{\epsilon^2} f(y), \overline{\eta}_t(dy) \rangle
+\end{align*}
+where $T_t$ denotes the heat semigroup. Substituting this into the martingale problem for $\overline{\eta}_t$, (\ref{mgp1}), we get,
+\begin{align}
+\langle T_{\epsilon^2} f(y), \overline{\eta}_t(dy) \rangle & = \langle T_{\epsilon^2}
+ f(y), \overline{\eta}_0(dy) \rangle + \theta \int_0^t \langle \int (T_{\epsilon^2} f(z) - T_{\epsilon^2} f(y))q_\theta(y,z)dz, \overline{\eta}_s(dy)\rangle ds \nonumber \\ &+\int_0^t \langle T_{\epsilon^2} f(y) F(\rho_\epsilon*\overline{\eta}_s(y)), \overline{\eta}_s(dy) \rangle ds + \widehat{M}_t \label{MGPT_epsilon} \end{align}
+ with $\widehat{M}_t$ a martingale. Now note that,
+by the Intermediate Value Theorem,
+ \begin{align}
+    | \theta \int (T_{\epsilon^2} f(z) - T_{\epsilon^2}f(y))q_\theta(y,z) dz | &= |\theta( T_{\epsilon^2 + 1/\theta} f(y) - T_{\epsilon^2}f(y)| \nonumber \\ &= | \Delta T_{\epsilon+1/\tilde{\theta}} f(y) | \nonumber \\ &=|T_{\epsilon^2 + 1/\tilde{\theta}} \Delta f(y) | \leq \Vert \Delta f \Vert_{\infty} \label{ShortBoundLaplacianHS}
+ \end{align}
+for some $\tilde{\theta} \in [0,1/\theta]$.
+Proceeding as in the proof of Lemma~\ref{Lemma:UniformlyBoundedMass}, we can use that $F(x)1_{x > 0}$ is bounded above and Gronwall's inequality to conclude that,
+\[ \IE\left[\langle T_{\epsilon^2} f(y), \overline{\eta}_t(dy) \rangle \right] \text{ is uniformly bounded for } t \in [0,T].\]
+The quadratic variation of $\widehat{M}_t$ is;
+\[ [ \widehat{M}]_t = \frac{\theta}{N}\int_0^t \langle T_{1/\theta}(T_{\epsilon^2}f(\cdot)^2)(y) + \left(1+\frac{F(\rho_\epsilon*\overline{\eta}_s(y))}{\theta}\right)T_{\epsilon^2}f(y)^2, \overline{\eta}_s(dy) \rangle ds \]
+And so, using boundedness of $f$ and $F$,
+\begin{align*}
+\IE\left[ [\widehat{M}]_t \right] \leq \frac{\theta}{N} \Vert f \Vert_\infty C \int_0^t \mathbb{E}\left[ \langle 1, \overline{\eta}_s(dy) \right] ds < \frac{\theta}{N} t C
+\end{align*}
+where in the last inequality we have used Lemma~\ref{Lemma:UniformlyBoundedMass}.Hence, using the Burkholder-Davis-Gundy inequality we can conclude,
+\[ \IE[\sup_{0 \leq t \leq T} [\widehat{M}]_t ] \text{ is uniformly bounded (for fixed } f \text{)} \]
+Therefore, by taking supremum and expectation and in (\ref{MGPT_epsilon}) we conclude that
+\begin{equation} \IE[\sup_{0 \leq t \leq T} \langle T_{\epsilon^2} f, \overline{\eta}_t \rangle ] \text{ is uniformly bounded (for fixed } f \text{)} \label{eq:boundedIntegralAgainstf} \end{equation}
+To conclude $C$-tightness we show that, for $T>0$, $\alpha > 0$ there is some $\delta >0$ so that for $\theta$ and $N$ large enough,
+\begin{align}
+&\IP\left[ \sup_{u,v \in [0,T], |u-v| < \delta} \left| \int f, \rho_\epsilon*\overline{\eta}_u(x) dx   - \int f, \rho_\epsilon*\overline{\eta}_v(x) dx \right|  > \alpha \right]
+    \\ &=
+\IP\left[ \sup_{u,v \in [0,T], |u-v| < \delta} | \langle T_{\epsilon^2} f, \overline{\eta}_u \rangle - \langle T_{\epsilon^2} f,\overline{\eta}_v \rangle > \alpha \right]
+    <
+    \alpha \label{conditionCtightness}
+\end{align}
+But, from our estimates above, we have
+\begin{align*}
+|\langle T_{\epsilon^2} f, \overline{\eta}_u \rangle - \langle T_{\epsilon^2} f,\overline{\eta}_v \rangle|  \leq ( \Vert \Delta f \Vert_\infty + C_F||f||_\infty) |u-v| \sup_{0 \leq s \leq T } \langle 1, \overline{\eta}_s \rangle + \sup_{s \leq T}|\widehat{M}_s|
+\end{align*}
+Taking expectations we get,
+\begin{equation}
+\IE\left[ |\langle T_{\epsilon^2} f, \overline{\eta}_u \rangle - \langle T_{\epsilon^2} f,\overline{\eta}_v \rangle|\right] \leq \widehat{C} |u-v| + \frac{\widehat{C}\theta}{N}\end{equation}
+Using this and Markov's inequality give that (\ref{conditionCtightness}) holds with $\delta = \alpha/(3 \widehat{C}|u-v|)$, for $N,\theta$ big enough so $\widehat{C}\theta/N$ is bounded by $\alpha/3$ (Note the last condition is possible by (\ref{ConditionsForConvergence})).
+Thus we have concluded $C$-tightness.
+\end{proof}
+\begin{remark} \label{remark:BoundedIntegral}
+Similar as we got equation (\ref{eq:boundedIntegralAgainstf}), from equation \ref{MGPT_epsilon} we can conclude that
+\[ \IE\left[\sup_{0 \leq t \leq T} \int \rho_{\epsilon/2} * \overline{\eta}_t(x) dx \right] = C < \infty. \]
+By using this and the same pattern used to prove Proposition~\ref{Prop:SecondMomentMass}, we can then conclude that,
+\[ \IE\left[  \sup_{0 \leq t \leq T} \int \left(\rho_{\epsilon/2} * \overline{\eta}_t(x) \right)^2 dx \right] = C < \infty. \]
+Since,
+\begin{align*}
+\langle \rho_\epsilon * \overline{\eta}_t(z), \overline{\eta}(dz) \rangle & = \sum_{y \in \overline{\eta}_t} \sum_{z \in \overline{\eta}_t} \rho_\epsilon(y-z) \overline{\eta}(z) \overline{\eta}(y) \\ &= \int  \sum_{y \in \overline{\eta}_t} \sum_{z \in \overline{\eta}_t} \rho_{\epsilon/2}(y-x) \rho_{\epsilon/2}(z-x) \overline{\eta}(z) \overline{\eta}(y) \\ &= \int (\rho_{\epsilon/2}*\overline{\eta}_t(x))^2 dx.
+\end{align*}
+This allows us to conclude that $\IE[\langle \rho_\epsilon*\overline{\eta}_t(z),\overline{\eta}_t(dz) \rangle ] < \infty$. This bound will be useful in the next section.
+\end{remark}
+
+\subsubsection{Identifying the limit}
+
+\paragraph{Continuity estimate}
+
+In this section we prove the following continuity estimate for $\rho_\epsilon * \overline{\eta}_t(x)$.
+\begin{proposition} \label{ContinuityEstimate}
+Under the same conditions of Theorem~\ref{TeoremOneStepConvergence} we have that for all $x \in \mathbb{R}^d$, $\delta>0$,
+\[
+\int |\rho_\epsilon*\overline{\eta}_s(x) -\rho_\epsilon*\overline{\eta}_s(y)| \rho_\delta(x-y) dy \]
+is bounded by
+\begin{align*}
+\frac{\delta}{\sqrt{\epsilon^2+s}} \langle 1,\overline{\eta}_0(dz) \rangle &+ \int_0^s \frac{\delta}{\sqrt{\epsilon^2+s-r}} (\langle 1, \overline{\eta}_r(dz)\rangle + \langle \rho_\epsilon*\overline{\eta}_r(z), \overline{\eta}_r(dz)\rangle)dr \\ &+ |M_s(x)| + \int |M_s(y)| \rho_\delta(y-x)dy + \mathcal{O}\left( \frac{1}{\epsilon^2 \theta}\right)
+\end{align*} 
+\end{proposition}
+where $M_s(x)$ is the martingale in (\ref{MartingaleProblemMolifier}).
+\begin{proof}
+Recall from our assumptions that $|F'(x)1_{x>0}|$ is uniformly bounded. Hence, we can always write,
+\begin{align} \label{StrongBoundOnF}
+|F(\rho_\epsilon*\overline{\eta}_t(x))| \leq |F(0)| + C \rho_\epsilon*\overline{\eta}_t(x)
+\end{align}
+So, by (\ref{MartingaleProblemMolifier}) we can write,
+\begin{align}
+& |\rho_\epsilon*\overline{\eta}_t(x)-\rho_\epsilon*\overline{\eta}_t(y)| \nonumber \\ &= |\langle \rho_\epsilon(y-z)-\rho_\epsilon(x-z),\overline{\eta}_t(dz) \rangle | \nonumber\\ &\leq  |M_t(x)-M_t(y)|  +\langle \psi_t^{\epsilon,y}(z)-\psi_t^{\epsilon,x}(z), \overline{\eta}_0(dz)\rangle \nonumber \\ &+ C\int_0^t \langle |\psi_{t-s}^{\epsilon,x}(z) - \psi_{t-s}^{\epsilon, y}(z) |, \overline{\eta}_s(dz) \rangle  ds | \\ &+ C \int_0^t \langle |\psi_{t-s}^{\epsilon,x}(z) - \psi_{t-s}^{\epsilon, y}(z) | \rho_\epsilon*\overline{\eta}(z), \overline{\eta}_s(dz) \rangle  ds | \label{eq:bound1CE} \end{align}
+By using Lemma~\ref{Lemma:BoundPsiHS2} we can then write, 
+\begin{align*}
+ \int &|\rho_\epsilon*\overline{\eta}_s(x) -\rho_\epsilon*\overline{\eta}_s(y)| \rho_\delta(x-y) dy  \leq \int |p_{\epsilon^2+s}(y,z)-p_{\epsilon^2+s}(x,z)|\overline{\eta}_0(dz) \rho_\delta(x-y)dy \\&+ C\int_0^s \langle p_{\epsilon^2+s-r}(y,z)-p_{\epsilon^2+s-r}(x,z)|, \overline{\eta}_r(dz) \rangle \rho_\delta (x-y) dr  \\  & + C \int_0^s \langle |p_{\epsilon+s-r}(y,z) - p_{\epsilon+s-r}(x,z) | \rho_\epsilon*\overline{\eta}_r(z), \overline{\eta}_r(dz) \rangle  dr | + \int|M_s(y)-M_s(x)| \rho_\delta(y-x)dy  \\  & + \frac{C}{\epsilon^2 \theta} \int \langle \rho_\epsilon*\overline{\eta}(z),\overline{\eta}_s(dz)\rangle ds   +\mathcal{O}\left( \frac{1}{\epsilon^2 \theta} \right)
+\end{align*}
+By Remark~\ref{remark:BoundedIntegral} the last integral term is of order $(\epsilon^2 \theta)^{-1}$.
+By using Lemma~\ref{Lemma:ContinuityHS} we get that the contribution of the first three terms is bounded by,
+\begin{align*}
+\int &\frac{|y-x|}{\sqrt{\epsilon^2+s}} \rho_{\delta}(y-x) dy \langle 1, \overline{\eta}_0(dz)\rangle + \int \int_0^s  \langle \frac{|y-x|}{\sqrt{\sqrt{\epsilon^2+s-r}}}, \overline{\eta}_r(dz) \rangle \rho_\delta(x-y) dy dr \\ & +  \int \int_0^s \langle \frac{|y-x| \rho_\epsilon*\overline{\eta}(z)}{\sqrt{\epsilon^2+s-r}}, \overline{\eta}_r(dz) \rangle \rho_\delta(y-x) dy dr \\ & \leq \frac{\delta}{\sqrt{\epsilon^2+s}} \langle 1, \overline{\eta}_0(dz) \rangle + \int_0^s \frac{\delta}{\sqrt{\epsilon^2+s-r}} (\langle 1, \overline{\eta}_r(dz) \rangle + \langle \rho_\epsilon*\overline{\eta}_r(z), \overline{\eta}_r(dz) \rangle) dr.
+\end{align*}
+To finish the proof just notice that,
+\begin{align*}
+\int |M_s(y)-M_s(x)| \rho_\delta(y-x)dy \leq |M_s(x)| + \int |M_s(y)| \rho_\delta(y-x)dy.
+\end{align*}
+\end{proof}
+
+\paragraph{Identifying the limit of $\langle T_{\epsilon^2} f(y), \overline{\eta}_t (dy) \rangle$.}
+We now prove the identification of the limit.
+We recall that, the main difficulty, is the non-linear term of the martingale problem.
+To deal with them, our first step would prove that an approximation of the form:
+\begin{align*}
+\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\overline{\eta}_s(dy)), \overline{\eta}_s(dy) \rangle \sim \langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \overline{\eta}_s(dy)), \rho_\epsilon * \overline{\eta}_s(y) dy \rangle
+\end{align*}
+This is the content of the next result.
+\begin{proposition} \label{CuadraticApprox}
+Under the condition of Theorem~\ref{TeoremOneStepConvergence} there is a constant $C>0$ such that
+\begin{equation*}
+\int_0^t \IE[|\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\overline{\eta}_s(dy)), \overline{\eta}_s(dy) \rangle - \langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \overline{\eta}_s(dy)), \rho_\epsilon * \overline{\eta}_s(y) dy \rangle|]
+\end{equation*}
+is bounded by,
+\begin{equation*}
+\mathcal{O}\left( \frac{1}{\epsilon^2 \theta} + \epsilon^2 + \epsilon + \epsilon^{1/3}  + \left( \frac{\theta}{N \epsilon^d} \right)^{1/2}\right)
+\end{equation*}
+\end{proposition}
+\begin{proof}
+We first note that,
+\begin{align*}
+    &\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\overline{\eta}_s(dy)), \overline{\eta}_s(dy) \rangle - \langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \overline{\eta}_s(dy)), \rho_\epsilon * \overline{\eta}_s(y) dy \rangle \\ & = \langle \int T_{\epsilon^2} f(y) F(\rho_\epsilon * \overline{\eta}_s(y))\rho_\epsilon(y-w) dy, \overline{\eta}_s(dw)\rangle - \langle T_{\epsilon^2} f(w) F(\rho_\epsilon*\overline{\eta}_s(w)), \overline{\eta}_s(dw) \rangle \\ &= \langle \int \{ T_{\epsilon^2} f(y) F(\rho_\epsilon*\overline{\eta}_s(y))-T_{\epsilon^2}f(w) F(\rho_\epsilon*\overline{\eta}_s(w))\} \rho_\epsilon(w-y)dy, \overline{\eta}_s(dw) \rangle.
+\end{align*}
+Let us denote $I$ the integral against $dy$ in the last expresion, that is 
+\[ I :=  \int \{ T_{\epsilon^2} f(y) F(\rho_\epsilon*\overline{\eta}_s(y))-T_{\epsilon^2}f(w) F(\rho_\epsilon*\overline{\eta}_s(w))\} \rho_\epsilon(w-y)dy \]
+And note that $|I|$ is bounded by
+\begin{align}
+& \int \left\{ |F(\rho_\epsilon*\overline{\eta}_s(y))-F(\rho_\epsilon*\overline{\eta}_s(w))|T_{\epsilon^2}f(y)+F(\rho_\epsilon*\overline{\eta}_s(w))|T_{\epsilon^2}f(y)-T_{\epsilon^2}f(w))|\right\} \rho_{\epsilon}(w-y)dy \nonumber \\ &\leq \int C |\rho_\epsilon*\overline{\eta}_s(y)-\rho_\epsilon*\overline{\eta}_s(w)| \rho_\epsilon(w-y)dy + C \epsilon^2 \Vert \Delta f \Vert_2 \label{FirstBoundCT}
+\end{align}
+where in the last inequality we have used $F(x)1_{x>0}$ and $|F'(x)1_{x>0}|$ are both bounded above.
+We want to use Proposition~\ref{ContinuityEstimate} in the last equation, but the terms that we would obtain would be too hard to control unless we first control the total mass and their noise.
+Let us define,
+\begin{align*}
+A_{t} &:= \left\{ \sup_{0 \leq s \leq t} \langle 1, \overline{\eta}_s(dz) \rangle > \epsilon^{-2/3} \right\}. \end{align*}
+Note that, by Markov's inequality and Lemma~\ref{Lemma:UniformlyBoundedMass} the event $A_{t}$ has probability of order $\epsilon^{2/3}$.
+Hence, writing $I = I(1_{A^c_{t}} + 1_{A_{t}})$ and proceeding as before we can use Proposition~\ref{ContinuityEstimate} in (\ref{FirstBoundCT}) to get,
+\begin{align}
+&\int_0^t \IE[|\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\overline{\eta}_s(dy)), \overline{\eta}_s(dy) \rangle - \langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \overline{\eta}_s(dy)), \rho_\epsilon * \overline{\eta}_s(y) dy \rangle|] \nonumber \\ &\leq   \int_0^t \IE[ \frac{\epsilon}{\sqrt{\epsilon^2 + s}} \langle 1,\overline{\eta}_0(dz) \rangle \langle 1, \overline{\eta}_s(dz)\rangle ] ds +  \int_0^t \IE[  \int_0^s \frac{\epsilon}{\sqrt{\epsilon^2 + s - r}} \langle 1, \overline{\eta}_r (dz) \rangle dr \langle 1, \overline{\eta}_s(dz) \rangle  ] ds \nonumber\\ & + \int_0^t \IE[   1_{A^c_{t}} \int_0^s \frac{\epsilon}{\sqrt{\epsilon^2 + s - r}} \langle \rho_\epsilon*\overline{\eta}_r(z), \overline{\eta}_r(dz) \rangle dr \langle 1, \overline{\eta}_s(dz) \rangle  ] ds + \int_0^t \IE[\langle |M_s(x)|,\overline{\eta}_s(dx) \rangle] ds \nonumber \\ &+ \int_0^t \int \IE[|M_s(y)|\rho_\epsilon*\overline{\eta}_s(y)] dy ds  +\mathcal{O}\left( \frac{1}{\epsilon^2 \theta} + \epsilon^2 + \epsilon^{1/3} \right)  \label{ThingsToBound}
+\end{align}
+Note we have bounded $1_{A^c_{t}}$ by one in all the terms expect the third one, which is the one that will require it.
+For the first two term we can use our hypothesis on the initial condition and that $2 ab \leq a^2+b^2$ to get that their contribution is bounded by,
+\begin{align*}
+\int_0^t C \frac{\epsilon}{\sqrt{\epsilon^2+s}}\IE[\langle 1, \overline{\eta}_s(dz) \rangle] ds + \int_0^t \int_0^s \frac{\epsilon}{\sqrt{\epsilon^2+s-r}}\IE[\langle 1, \overline{\eta}_r(dz)\rangle^2 + \langle 1, \overline{\eta}_s(dz)\rangle^2] ds,
+\end{align*}
+which, due to Proposition~\ref{Prop:SecondMomentMass}, is of order $\epsilon$. To bound the third integral term we use the event $A_{t}$ to get it is bounded by,
+\begin{align*}
+\int_0^t \int_0^s \frac{\epsilon^{1/3}}{\sqrt{\epsilon^2+s-r}} \IE[ \langle \rho*\overline{\eta}_r(z), \overline{\eta}(dz) \rangle] dr ds = \mathcal{O}(\epsilon^{1/3})
+\end{align*}
+where we have used Remark~\ref{remark:BoundedIntegral}. 
+We now proceed to control the terms with martingales in (\ref{ThingsToBound}). For the first one note that, by using Cauchy-Schwartz in $L^2(\mathbb{P})$ and then in $L^2(\mathbb{R}^d)$,
+\begin{align}
+\int_0^t \int \IE[|M_s(y)|\rho_\epsilon*\overline{\eta}_s(y)] dy ds & \leq \int_0^t \int \IE[|M^2_s(y)]^{1/2} \IE[\rho_\epsilon * \overline{\eta}_s(y)^2]^{1/2} dy dy \nonumber \\ & \leq \int_0^t \left( \int \IE[|M_s(y)^2|] dy \int \IE[\rho_\epsilon * \overline{\eta}_s(y)^2] dy \right)^{1/2} ds  \nonumber \\ &= \mathcal{O}\left( \left( \frac{\theta}{N \epsilon^d} \right)^{1/2} \right)
+\label{TwiceCS} \end{align}
+where in the last inequality we used Proposition~\ref{IntegrabilityOfM} and Remark~\ref{remark:BoundedIntegral}.
+For the second term with a Martingale in (\ref{ThingsToBound}) we need to proceed with more care.
+For this we first rewrite explicitly the dependency on $\epsilon$ of $M_t(x)$ by using $M_t^{\varepsilon^2}(x)$.
+We can then write from (\ref{MartingaleProblemMolifier}) and Lemma~\ref{Lemma:BoundPsiHS2}) that,
+\begin{align*}
+ M_t^{\epsilon^2}(x) &= \langle p_{\epsilon^2}(x,y), \overline{\eta}_t(dx) \rangle - \langle p_{t + \epsilon^2}(x,y), \overline{\eta}_0(dx) \rangle \\ &- \int_0^t \langle F(\rho_\epsilon*\overline{\eta}_s(y)) p_{t-s+\epsilon^2}(x,y), \overline{\eta}_s(dy) \rangle ds + \mathcal{O}\left(\frac{1}{\epsilon^2 \theta} \right) \end{align*}
+ It follows then that $M_s^{\epsilon^2}= p_{\epsilon^2/2}*M_s^{\epsilon^2/2} + \mathcal{O}\left(1/\epsilon^2 \theta\right)$. Using this we can then bound,
+ \begin{align*}
+\int_0^t &\IE[ \langle |M_s^{\epsilon^2}(x)|, \overline{\eta}_s(dx) \rangle ] ds \\ &= \int_0^t \IE[ \langle | p_{\epsilon^2/2}*M_s^{\epsilon^2/2}(x)|, \overline{\eta}_s(dx) \rangle] ds \\ & \leq  \int_0^t \IE[ \langle p_{\epsilon^2/2}*| M_s^{\epsilon^2/2}(x)|, \overline{\eta}_s(dx) \rangle] ds \\ &= \int_0^t \IE[ \langle \int p_{\epsilon^2/2}(x,y) |M_s^{\epsilon^2/2}(y)|dy, \overline{\eta}_s(dx) \rangle] ds \\ &= \int_0^t \IE[ \int |M_s^{\epsilon^2/2}(y)| p_{\epsilon^2/2}*\overline{\eta}_s(y) dy ] ds \\ &= \int_0^t \int \IE[ M_s^{\epsilon^2/2}(y)| p_{\epsilon^2/2} * \overline{\eta}_s(dy)] dy ds
+ \end{align*}
+ An analogues computation as the one performed to obatin (\ref{TwiceCS}) gives the last term is $\mathcal{O}\left( \left( \frac{\theta}{N \epsilon^d} \right)^{1/2} \right)$.
+ \end{proof}
+Now, to finish the characterisation of the limit, it remain to show that:
+\[ \int f(x) \rho_\epsilon * \overline{\eta}_t(x) F(\rho_\epsilon * \overline{\eta}_t(x)) dx \rightarrow \int f(x) u_t(x) F(u_t(x)) dx \]
+where $u_t(x)dx$ is the limit of $\rho_\epsilon*\overline{\eta}_t(x)dx$.
+As we mention as the start of this note this does now follow from weak convergence of $\rho_\epsilon*\overline{\eta}(x)dx$.
+For proving this, we recall that $F(x)$ is a polynomial, so we just need to prove said convergence of powers of $(\rho_\epsilon*\overline{\eta}_t(x))$.
+To illustrate how to proceed, we will prove the convergence,
+\begin{equation} \label{eq:QuadConvergence} \int f(x) \rho_\epsilon * \overline{\eta}_t(x) \rho_\epsilon * \overline{\eta}_t(x)^2 dx \rightarrow \int f(x) u_t(x) u_t(x)^2 dx \end{equation}
+with the understanding that converge of higher powers will follows in a similar fashion with rougher notation. To achieve (\ref{eq:QuadConvergence}) we proceed by proving an approximation of the form,
+\begin{equation}
+\label{aprox2}
+\langle f, (\overline{\eta}_s * \rho_\epsilon)^2 \rangle \sim \int \int f(z) (\rho_\epsilon * \overline{\eta}_s)(z) \rho_\delta (z-y) (\rho_\epsilon * \overline{\eta}_s)(y) dz dy.
+\end{equation}
+Before proceeding with a proof of (\ref{aprox2}), we argue why this is enough to conclude Theorem~\ref{TeoremOneStepConvergence}. Note the right hand side of (\ref{aprox2}) can written as
+\[ \int_{\mathbb{R}^{d} \otimes \mathbb{R}^d} f(z) \rho_\delta(z-y) (\rho_\epsilon * \overline{\eta}_s(dz) \otimes (\rho_\epsilon * \overline{\eta}_s(dy)). \]
+Weak convergence of $\rho_\epsilon * \overline{\eta}$ (plus continuity of the mapping $(z,y) \rightarrow f(z) \rho_\delta(z-y)$) gives that the last term converges in $L^1$ to
+\[ \int_{\mathbb{R}^{d} \otimes \mathbb{R}^d} f(z) \rho_\delta(z-y) (u_s(dz) \otimes (u_s(dy)). \]
+Finally, by a direct analogue of (\ref{aprox2}) we can say that
+\begin{equation} \int_{\mathbb{R}^{d} \otimes \mathbb{R}^d} f(z) \rho_\delta(z-y) (u_s(dz) \otimes (u_s(dy)) \sim \langle f(x), u_s^2(x) dx \rangle. \label{aprox3} \end{equation}
+which is what we seek. We proceed now to prove (\ref{aprox2}), with the understanding that (\ref{aprox3}) follows in a similar way and give even better error terms.
+\begin{theorem}
+Under the conditions of Theorem~\ref{TeoremOneStepConvergence}, we have that
+\begin{align*}
+\int_0^t \mathbb{E}&\left[\left| \langle f(y), (\overline{\eta}_s * \rho_\epsilon(y))^2) dy\rangle - \int \int f(y) (\rho_\epsilon * \overline{\eta}_s)(z) \rho_\delta (z-y) (\rho_\epsilon * \overline{\eta}_s)(y) dz dy.
+\right|\right] ds
+\end{align*}
+is bounded by,
+\[  \mathcal{O}\left(\delta^{1/3} + \delta +  \frac{1}{\epsilon^2 \theta} + \left( \frac{\theta}{N \epsilon^2}\right)^{1/2} \right)  \]
+in particular, under (\ref{ConditionsForConvergence}), the last term goes to $0$ uniformly in $\theta,\epsilon,N$ and $\delta$ (when $\delta$, $\epsilon$ go to $0$ and $N,\theta$ to infinity).
+\end{theorem}
+\begin{proof}
+First note,
+\begin{align}
+&\int_0^t \mathbb{E}\left[| \langle f(y), (\overline{\eta}_s * \rho_\epsilon(y))^2) dy \rangle - \int \int f(y) (\rho_\epsilon * \overline{\eta}_s)(z) \rho_\delta (z-y) (\rho_\epsilon * \overline{\eta}_s)(y) dz dy.
+|\right] ds \nonumber \\ &\leq  \Vert f \Vert_\infty \int_{S_f}  \int_0^t  \mathbb{E}\left[ \int \left\{ \left|(\rho_\epsilon * \overline{\eta}_s)(y)-(\rho_\epsilon * \overline{\eta}_s)(z) \right|   \rho_\delta(z-y) dz \right\} (\rho_\epsilon *\overline{\eta}_s)(y) \right] ds  dy \label{b1}
+\end{align}
+We want then to bound (\ref{b1}) by using Proposition~\ref{ContinuityEstimate}. For this consider the event,
+\[ B_{s,y} := \{ \rho_\epsilon * \overline{\eta}_s(y) > \delta^{-2/3} \}. \]
+Note that by Markov's inequality and Lemma~\ref{FirstBoundLocalDensity} the event $B_{s,y}$ has probability of order $\delta^{2/3}$ (and independent of $s$ and $y$).
+Thus, proceeding as how get (\ref{ThingsToBound}), the integral against $ds$ in the right hand side of (\ref{b1}) is bounded by
+\begin{align}
+&\int_0^t \IE[ \frac{\delta}{\sqrt{\epsilon^2 + s}} \langle 1,\overline{\eta}_0(dz) \rangle (\rho_\epsilon *\overline{\eta}_s)(y) ] ds +  \int_0^t \IE[  \int_0^s \frac{\delta}{\sqrt{\epsilon^2 + s - r}} \langle 1, \overline{\eta}_r (dz) \rangle dr(\rho_\epsilon *\overline{\eta}_s)(y)  ] ds \nonumber\\ & + \int_0^t \IE[   1_{B^c_{s,\delta}} \int_0^s \frac{\delta}{\sqrt{\epsilon^2 + s - r}} \langle \rho_\epsilon*\overline{\eta}_r(z), \overline{\eta}_r(dz) \rangle dr (\rho_\epsilon *\overline{\eta}_s)(y) ] ds + \int_0^t \IE[\langle |M_s(x)|,\overline{\eta}_s(dx) \rangle] ds \nonumber \\ & + \int_0^t  \IE[|M_s(y)|\rho_{\epsilon+\delta}*\overline{\eta}_s(y)] ds  +\mathcal{O}\left( \frac{1}{\epsilon^2 \theta} + \delta^{1/3} \right)  \label{ThingsToBound2}
+\end{align}
+From this point onward we can proceed as how we bounded (\ref{ThingsToBound}) in Proposition~\ref{CuadraticApprox} to obtain that the right hand side of (\ref{b1}) is bounded by,
+\[  \mathcal{O}\left(\delta^{1/3} + \delta+ \frac{1}{\epsilon^2 \theta} + \left( \frac{\theta}{N \epsilon^2}\right)^{1/2} \right)  \]
+Concluding the result.
+\end{proof}
+
+\paragraph{Conclusion}
+Under the condition (\ref{ConditionsForConvergence}) we have that all the errors in our approximations go to $0$.
+It is then we can deduce that quadratic (and analogously, higher order) terms in the martingale problem for $\rho_\epsilon*\overline{\eta}_t(x)dx$, (\ref{MGPT_epsilon}), converges to the corresponding term of the weak limit.
+Any linear term converge trivially by weak convergence.
+By a Taylor's expansion we can also conclude that,
+\begin{align*}
+\int_0^t \langle \mathcal{L}^\theta T_{\epsilon^2} f, \overline{\eta}_s(dx)\rangle ds &= \int_0^t \langle \frac{1}{2} \Delta T_{\epsilon^2} f(x), \overline{\eta}_s(dx) \rangle + \mathcal{O}(\theta^{-1})
+\\ &= \int_0^t \langle \frac{1}{2} \Delta f(x), \rho_\epsilon* \overline{\eta}_s(x) dx \rangle ds + \mathcal{O}(\theta^{-1} + \epsilon).
+\end{align*}
+Thus, by weak convergence we can deduce
+\[ \int_0^t \langle \mathcal{L}^\theta T_{\epsilon^2} f, \overline{\eta}_s(dx)\rangle ds \rightarrow \int_0^t \langle \frac{1}{2} \Delta f(x), u_s(x) dx \rangle ds \]
+Putting all the convergences together, this identifies the limit of $\rho_\epsilon*\overline{\eta}_s(x)dx$ as we have claimed in Theorem~\ref{TeoremOneStepConvergence}.
+
+\todo[inline]{END OneStepConvergence}
+
 % % % % % % % % % % % % %

### 2022-07-25 forwards-and-backwards.tex
adjustments to main text

@@
 \newpage
-
-\comment{TODO: talk about $N \to \infty$ rather than $\theta \to \infty$.}
 
@@
 although this restriction could be easily lifted
-\citep[as in][]{etheridge/kurtz:2018}.
+\citep[as in Section 3.4 of][]{etheridge/kurtz:2018}.
 Furthermore, individuals do not move during their lifetime,
 and the age of an individual does not affect their fecundity or death rates.
-Finally, there is no notion of mating,
-so availability of mates will not restrict the spread of a population,
-and the lineages we follow will be uniparental.
+Finally, there is no notion of mating
+(although limitations on reproduction due to availability of mates can be incorporated into the birth rate, $\gamma$),
+so the lineages we follow will be uniparental.
 For these reasons, the model is most obviously applicable to bacterial populations or selfing plants,
@@
     =
+    \max\left(0, 
         r(x, \smooth{r} \eta(x))
@@
         - \frac{1}{\theta}
-    F(x, \smooth{F} \eta(x)) .
+        F(x, \smooth{F} \eta(x)) 
+    \right) .
 \end{align}
@@
 is a martingale with quadratic variation
-\begin{equation}
+    \begin{equation} \label{eqn:prelimit_martingale_variation}
 \begin{aligned} \relax
@@
     which satisfies that, for every $f \in C^\infty_0(\IR^d)$,
-    \begin{align} \label{eqn:mgale_problem}
+    \begin{align} \label{eqn:limiting_mgale_problem}
         \begin{split}
@@
     \end{align}
-    is a martingale.
-    The quadratic variation of $M_t$, denoted $\langle M \rangle_t$, is given by 
-    \begin{align} \label{eqn:mgale_variation}
-        \langle M \rangle_t
+    is a martingale,
+    with quadratic variation
+    \begin{align} \label{eqn:limiting_mgale_variation}
+        [ M ]_t
         =
@@
 
-Recall when interpreting~\eqref{eqn:mgale_problem}
+Recall when interpreting~\eqref{eqn:limiting_mgale_problem}
 that for instance $r(x, \eta_s) = r(x, \smooth{r} \eta_s(x))$,
@@
 \begin{corollary}[Superprocess limits] \label{cor:superprocess_uniqueness}
-    In the context of Theorem~\ref{thm:nonlocal_convergence},
+    Under the assumptions of Theorem~\ref{thm:nonlocal_convergence},
     if the martingale problem
-    defined by equations \eqref{eqn:mgale_problem} and \eqref{eqn:mgale_variation}
+    defined by equations \eqref{eqn:limiting_mgale_problem} and \eqref{eqn:limiting_mgale_variation}
     has a unique solution,
@@
 
-\comment{TODO: find some conditions under which we have convergence to a unique solution?}
-\comment{TODO: Tom has conditions (coefficient are Lipschitz?) under which
-    the solution to \eqref{eqn:nonlocal_pdf} has a density (Thm 2.1 in DDMOT);
-    should we insert those here (as a Corollary or Proposition, maybe?)}
+\comment{TODO: Tom has conditions, referring to \citet{KURTZ1999103}, (coefficient are Lipschitz?) under which
+    the solution to \eqref{eqn:nonlocal_pdf} is unique and has a density (Thm 2.1 in DDMOT);
+    insert those here (as a Corollary or Proposition)}
 
@@
 will agree with the purely spatial process defined above.
-Furthermore, the levels of the individuals present at any spatial location
-will be conditionally uniform on $[0, N]$.
+Furthermore, at any time, the levels of the individuals present at any spatial location
+will be exchangeable and conditionally uniform on $[0, N]$:
+in particular, choosing the $k$ individuals with the lowest level in some region of space
+at some time is equivalent to taking a uniform random draw of size $k$ from the individuals in that region
+for the purely spatial process.
 However, an individual's level in some sense encodes their future reproductive output:
@@
 (This provides our justification for using the same notation for both.)
-Finally, note that we first describe the dynamics of individuals
+
+As before, we first describe the dynamics of individuals
 in the original time units -- i.e., before scaling by $\theta$,
-which will appear below.
-
+which will be introduced below.
 Suppose that the initial population is composed of $O(N)$ many particles
@@
 
-The remaining term in the generator is due to the motion of particles' levels:
+The remaining term in the generator is due to the motion of particles' levels,
+mapping $f(\xi)$ to
 \begin{align} \label{eqn:level_generator}
-    f(\lp)
-    \mapsto
     f(\lp)
@@
     \label{defn:lookdown_mgale}
-For given positive values of $N$ and $\theta$,
+For given positive values of $N$ and $\theta$
+and $\lp_0 \in \mathcal{M}_F(\mathbb{R}^d \times [0,N])$,
 we define $(\lp^{N}_t)_{t \geq 0}$
-to be the unique solution
-to the Martingale Problem
-with initial condition $\lp_0 \in \mathcal{M}_F(\mathbb{R}^d \times [0,N])$
-and generator $A^{N}$ that satisfies
+to be the unique solution to the martingale problem
+with initial condition $\lp_0$ and generator $A^{N}$ that satisfies
 \begin{equation*}
@@
 
+Since everything is finite,
+it is clear that the martingale problem for finite $N$ has a unique solution.
+Next we state the limiting martingale problem,
+for which we do not have uniqueness (although we construct an explicit solution later).
+
+\begin{definition}[Martingale Problem Characterisation, $N=\infty$]
+    \label{defn:limiting_lookdown_mgale}
+    For a given value of $\alpha \in [0, \infty)$,
+    define the operator $A$ acting on test functions of the form
+    $f(\xi) = \prod_{(x, u) \in \xi} g(x, u)$ with $g \in C_0^2(\IR^d \times [0, \infty)$
+    and for which there exists a $u_0$ with $g(x, u) = 1$ for all $u > u_0$.
+    Then, let $A f$ be
+    \begin{align} \begin{split} \label{eqn:limiting_lookdown_generator}
+    A f(\lp)
+    &=
+        f(\lp)  \sum_{(x, u) \in \xi}
+        \gamma(x, \eta)
+            \frac{
+                \DG(g(\cdot, u) r(\cdot, \eta))(x) - g(x,u) \DG r(x,\eta)
+            }{
+                g(x, u)
+            }
+    \\ &\qquad {} +
+        f(\lp) \sum_{(x, u) \in \xi}
+        2 \alpha \gamma(x, \eta) r(x, \eta \int_u^\infty (g(x, u_1) - 1) du_1
+    \\ &\qquad {} +
+        f(\lp) \sum_{(x, u) \in \xi}
+        \left(
+            \alpha \gamma(x, \eta) r(x, \eta) u^2
+            -
+            \left\{
+                \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta)
+            \right\} u
+        \right)
+        \frac{\partial_u g(x, u)}{ g(x,u) }  .
+    \end{split} \end{align}
+    We say that a $\lpmeasures$-valued process $(\xi_t)_{t \ge 0}$
+    is a solution to the $(A, \lp_0)$ martingale problem
+    if it has initial distribution $\lp_0$
+    and $f(\lp_t) - \int_0^t Af(\lp_s) ds$ is a martingale for all $f$
+    as defined above.
+\end{definition}
+
+\comment{We talked about having the next paragraph be a Proposition or something?}
+
+The lookdown processes have been carefully constructed so that
+if we average over levels in the expression for the lookdown generator
+(equation~\eqref{eqn:lookdown_generator} or~\eqref{eqn:limiting_lookdown_generator})
+we get the generator for the population process
+(visible in equation~\eqref{eq: Pre-limit Martingale Characterisation}
+or~\eqref{eqn:limiting_mgale_problem}, respectively).
+Once this is verified (and some boundedness conditions)
+in Appendix \ref{sec: Markov Mapping Theorem Application},
+the Markov Mapping Theorem \citep[Thm A.2 in][]{etheridge/kurtz:2018}
+tells us that for any population process $(\eta^N_t)_{t \ge 0}$
+(i.e., solution to the martingale problem of Definition~\ref{defn:mgale_construction})
+% of equations~\eqref{eq: Pre-limit Martingale Characterisation} and \eqref{eqn:prelimit_martingale_variation}
+there is a lookdown representation $(\lp^N_t)_{t \ge 0}$
+(i.e., solution to the martingale problem of Definition~\ref{defn:lookdown_mgale})
+for which $\eta^N_t(\cdot) = \lp^N_t(\cdot \times [0, N])$
+and such that at each $t$, conditioned on $(\eta^N_s){s \le t}$, the levels of $\lp_t^N$
+are independently and uniformly distributed on $[0, N]$.
+The same property holds in the limit:
+for any solution $(\eta_t)_{t \ge 0}$ to the martingale problem of Theorem~\ref{nonlocal_convergence}
+there is a lookdown process $(\lp^N_t)_{t \ge 0}$
+that is a solution to the martingale problem of Theorem~\ref{lookdown_convergence}
+for which $\eta_t(\cdot) = \lim_{u_0 \to \infty} \frac{1}{u_0} \lp_t(\cdot \times [0, u_0))$
+and such that at each $t$,
+$\lp_t$ is conditionally Poisson with Cox measure $\eta_t(dx) \times du$,
+conditioned on $(\eta_s)_{s \le t}$.
+Furthermore, convergence of the lookdown processes would imply convergence of the population processes
+\citep[Thm A.9 in][]{KR}.
+
 Now that the lookdown process has been defined,
@@
     $\theta \to \infty$ in such a way that $\theta/N \to \alpha$.
-    The sequence of stochastic processes $(\lp_t^N)_{t \ge 0}$
+    Suppose also that $\eta^N_0 \to \eta_0$ (as measures on $\IR^d$),
+    and that for each $N$, $\lp^N_0(dx, du)$ is conditionally Poisson on $\IR^d \times [0, N]$
+    with Cox measure $\eta^N_0(dx) \times du$.
+    Then, the sequence of stochastic processes $(\lp_t^N)_{t \ge 0}$
     converges along subsequences in distribution as $N \to \infty$
-    to a measure-valued process $(\lp_t)_{t \ge 0}$ which satisfies,
-    for every $f: \IR^d \to \IR$
-    \plr{TODO: write down limiting martingale characterization}
+    to a measure-valued process $(\lp_t)_{t \ge 0}$
+    with $\lp_0$ conditionally Poisson with Cox measure $\eta_0(dx) \times du$,
+    that is a solution to the martingale problem~\ref{defn:limiting_lookdown_mgale}.
 \end{theorem}
 
-\comment{I don't think this bit quite makes sense yet without understanding the MMT
-section (but, it should be understandable without understanding that section).}
+\comment{TODO: remove this next bit?}
 
@@
 
-Although in Section \ref{sec:proofs} we will show convergence of the lookdown process
-defined by Definition~\ref{defn:lookdown_mgale}
-to a stochastic process in which individuals retain their identities,
-it is convenient to construct the lookdown process
+In this section we explicitly construct the lookdown process
 in a way that explicitly represents the motion of each individual and their offspring.
-This will then make obvious how lineages move in the limit,
+This provides an explicit construction of the solution to
+the limiting martingale problem~\ref{defn:limiting_lookdown_mgale}.
+It will furthermore make it obvious how lineages move in the limit,
 and will allow us to identify all 
@@
 but we don't write this out.
+
+\comment{Perhaps the following is confusing having $t$ for the point of $\Pi_a$,
+and we should instead use... $\tau$?}
 
@@
 
-Potential reproduction events occur at times $\tau_a + s$
-for each point $(s, v, w, \kappa) \in \Pi_a$.
+Potential reproduction events occur at times $t$
+for each point $(t, v, w, \kappa) \in \Pi_a$ with $t \ge \tau_a$.
 We say `potential' since if the resulting level is greater than $N$,
@@
 If this is the $j^\text{th}$ point in $\Pi_a$,
-the new label is $a \concat j$, the (potential) birth time is $\tau_{a \concat j} = \tau_a + s$.
-Similarly, the potential birth location is 
+the new label is $a \concat j$, the (potential) birth time is $\tau_{a \concat j} = t$.
+Similarly, the potential birth location is $y(X(t-), z)$, where
 $$
-    y
+    y(x, z)
     :=
-    \frac{1}{\theta}\meanq(X_a(\tau_{a \concat j}-))
+    \frac{1}{\theta}\meanq(x)
     +
-    \frac{1}{\sqrt{\theta}}K(X_a(\tau_{a \concat j}-))z,
+    \frac{1}{\sqrt{\theta}}K(x) z,
 $$
@@
 \begin{equation*}
-    U_{a \concat j}(\tau_{a \concat j})
+    U_{a \concat j}(t)
     =
-    U_a(\tau_{a \concat j})
+    U_a(t)
     +
-    v \ell(X_a(\tau_{a \concat j}-), y, \eta(\tau_{a \concat j}-)) .
+    v \ell(X_a(t-), y(X_a(t-), z), \eta(t-)) .
 \end{equation*}
-If $U_{a \concat j}(\tau_{a \concat j}) < N$,
+If $U_{a \concat j}(t) < N$,
 the new individual labeled $a \concat j$ is produced,
-\comment{TODO: explain why this does the right thing}
 and $\kappa$ determines which label is associated with the new location,
@@
 \begin{align*}
-    X_{a \concat j}(\tau_{a \concat j})
+    X_{a \concat j}(t)
     &=
-    X_a(\tau_{a \concat j}-) + (1 - \kappa) y .
+    X_a(t-) + (1 - \kappa) y(X_a(t-), z) .
 \end{align*}
 On the other hand
-if $U_{a \concat j}(\tau_{a \concat j}) \ge N$, then $X_a$ is unchanged and $X_{a \concat j}$ is undefined,
+if $U_{a \concat j}(t) \ge N$, then $X_a$ is unchanged and $X_{a \concat j}$ is undefined,
 so
 \begin{align} \label{eqn:X_line_of_descent}
-    X_a(\tau_{a \concat j})
+    X_a(t)
     &=
-    X_a(\tau_{a \concat j}-) + \kappa y \ind_{U_{a \concat j}(\tau_{a \concat j}) < N} .
+    X_a(t-) + \kappa y(X_a(t-), z) \ind_{U_{a \concat j}(t) < N} .
 \end{align}
@@
 and our line of descent switching to the offspring.
+Combining these, $X_a$, for $\tau_a \le T < \sigma_a$, solves the equation 
+\begin{align*}
+    X_a(T)
+    &=
+    \int_{[\tau_a, T) \times [0, \infty) \times \IR \times [0, 1]}
+    y(X_a(t-), z)
+    \kappa
+    \ind_{
+        U_a(t) + v \ell(X_a(t-), y(X_a(t-), z), \eta_t)
+    }
+    d\Pi_a(s, v, z, \kappa) .
+\end{align*}
 
 Although we have described the evolution of a line of descent only for a given label
-(i.e., for $\tau_a \le t < \sigma_a$),
+(i.e., for $\tau_a \le s < \sigma_a$),
 we can extend the definition to earlier times
-by setting for $0 \le t < \sigma_a$
-$X_a(t)$ equal to $X_{[a]_t}(t)$,
-where $[a]_t$ is the label of the ancestor of label $a$ alive at time $t$,
-and similarly for $U_a(t)$.
+by setting for $0 \le s < \sigma_a$
+$X_a(s)$ equal to $X_{[a]_s}(s)$,
+where $[a]_s$ is the label of the ancestor of label $a$ alive at time $s$,
+and similarly for $U_a(s)$.
 It is then straightforward, albeit tedious,
-to write down the time evolution of $(X_a(t), U_a(t))$ for all time back to $t=0$
+to write down the time evolution of $(X_a(s), U_a(s))$ for all time back to $s=0$
 in terms of the driving Poisson processes.
-Although at finite $N$ the spatial process $X_a(t)$ is affected by jumps in the level $U_a(t)$,
+Although at finite $N$ the spatial process $X_a(s)$ is affected by jumps in the level $U_a(s)$,
 we will see that in the $N \to \infty$ limit
-the behavior of $X_a(t)$ is not affected by these jumps.
+the behavior of $X_a(s)$ is not affected by these jumps.
 
@@
 \begin{align*}
-    \eta^N_t = \frac{1}{N} \sum_{a : \tau_a \le t < \sigma_a} \delta_{X_a(t)}
+    \eta^N_s = \frac{1}{N} \sum_{a : \tau_a \le s < \sigma_a} \delta_{X_a(s)}
     \qquad \text{and} \qquad
-    \lp^N_t = \sum_{a : \tau_a \le t < \sigma_a} \delta_{(X_a(t), U_a(t))} .
+    \lp^N_s = \sum_{a : \tau_a \le s < \sigma_a} \delta_{(X_a(s), U_a(s))} .
 \end{align*}
@@
 
+\comment{I also don't think we need this.}
+
 We now write down an expression for the
@@
 The line of descent throws off a new line of descent at a higher level
-when there is a point $(s, v, y, \kappa)$ in $\Pi_a$ with 
+when there is a point $(s, v, y, \kappa)$ in $\Pi_a$ with $s > \tau_a$ and
 \begin{equation} \label{eqn:line_points}
-    v < 2 (N - U_a(\tau_a + s)) N^{-1} \theta \gamma(X_a(\tau_a + s), \eta_{\tau_a + s}) r(X_a(\tau_a + s)+y, \eta_{\tau_a + s}) .
+    v < 2 (N - U_a(s)) N^{-1} \theta \gamma(X_a(s), \eta_s) r(X_a(s) + y, \eta_s) .
 \end{equation}
@@
 $$
-2 \alpha \gamma(X_a(t), \eta_{\tau_a + s}) r(X_a(t), \eta_{\tau_a + s}) 
+2 \alpha \gamma(X_a(t), \eta_t) r(X_a(t), \eta_t) 
 $$
@@
 and that the result is independent of $u$.
+Also recall that $r(x, \eta)$ only depends on $\eta$ through $\smooth{r}\eta(x)$,
+which is guaranteed to be smooth, so that $\DG(r)$ and $\DG(gr)$ are well-defined.
 
@@
 Recall that $\DG g(x) = \sum_i \meanq_i \partial_i g(x) + \sum_{ij} \covq_{ij} \partial_{ij} g(x)$,
-and for the moment write $r(x)$ for $r(\cdot, \eta(\cdot))(x)$,
+and for the moment write $r(x)$ for $r(\cdot, \eta)(x)$,
 so that
@@
 \begin{proposition}[Line of descent construction]
+    \label{prop:limiting_construction}
 Let $\beta(x, \eta) = \meanq(x) + 2 \covq(x) \grad \log r(x, \eta)$
@@
 Suppose that the spatial locations and level of each line of descent $a$
-behave, for $\tau_a \le t < \sigma_a$ as, as
+solve, for $\tau_a \le t < \sigma_a$ as,
+where $\sigma_a = \lim_{K \to \infty} \inf\{t \ge 0: U_a(t) > K\}$,
+as
 \begin{align*}
@@
     + \int_{\tau_a}^{t}
-    \bigg(
-        \beta(x, \eta(s)) ds
-        +
-        K dW_a(s)
-    \bigg)
-    ds  \\
+        \beta(X_a(s), \eta(s)) ds
+    + \int_{\tau_a}^{t}
+        K(X_a(s)) dW_a(s)
+    \\
 U_a(t)
@@
         \alpha \gamma(X_a(s),\eta(s))
-        r(x,\eta(s)) U_a(s)^2
+        r(X_a(s), \eta(s)) U_a(s)^2
 \\ &\qquad \qquad \qquad {}   
@@
 \end{align*}
-Each point in the $R_a$ denotes a potential birth time for $a$:
-if the $j^\text{th}$ point in $R_a$ is $(t, v)$, with $t < \sigma_a - \tau_a$,
+Each point in each $R_a$ denotes a potential birth time for $a$:
+if the $j^\text{th}$ point in $R_a$ is $(t, v)$, with $\sigma_a \le t < \tau_a$,
 then a new line of descent with label $a \concat j$ is produced,
-with birth time $\tau_{a \concat j} = \tau_a + t$,
-location $X_{a \concat j}(\tau_a + t) = X_a(\tau_a + t)$, and level
+with birth time $\tau_{a \concat j} = t$,
+    location $X_{a \concat j}(t) = X_a(t)$, and level
 $$
-    U_{a \concat j}(\tau_a + t) = U_a(\tau_a + t)
-    + \frac{v}{ 2 \alpha \gamma(X_a(\tau_a + t), \eta_{\tau_a + t}) r(X_a(\tau_a + t), \eta_{\tau_a + t}) } .
+    U_{a \concat j}(t) = U_a(t)
+    + \frac{v}{ 2 \alpha \gamma(X_a(t), \eta_t) r(X_a(t), \eta_t) } .
 $$
-For each $a$, let $\sigma_a = \inf\{t \ge 0: U_a(t) < \infty\}$.
-Then, the processes defined by
+For any solution to the equations above, the processes defined by
 \begin{align*}
@@
 \end{align*}
-agree in distribution with those of Definitions~\ref{defn:mgale_construction}
-and~\ref{defn:lookdown_mgale}, respectively.
+are solutions to the martingale problems of
+Theorems~\ref{thm:nonlocal_convergence} and~\ref{thm:lookdown_convergence},
+respectively.
 \end{proposition}
@@
 since the spatial motion of the line of descent is the result of production of these lineages.
+
+\comment{Note that the analogous theorem for finite $N$ is obvious (??) and not stated as a proposition.}
+
+\comment{TODO: find the right place for this proof?}
+\begin{proof}[of Proposition~\ref{prop:limiting_construction}]
+    The fact that a solution to the system of equations
+    is a solution to the martingale problem of Theorem~\ref{thm:lookdown_convergence}
+    is an application of It\^o's theorem.
+    The calculations in \comment{XXX} leading to our application
+    of the Markov Mapping Theorem then show that 
+    the conditional Poisson property of $\lp_0$ is preserved
+    (i.e., holds for $\lp_t$ for all $t$), and so
+    $(\eta_t)_{t \ge 0}$ is well-defined,
+    and furthermore that $\eta_t$ is a solution
+    to the martingale problem of Theorem~\ref{thm:nonlocal_convergence}.
+\end{proof}
 
@@
 Next, we prove that the limit solves the martingale properties
-of equations~\eqref{eqn:mgale_problem} and~\eqref{eqn:mgale_variation}
+of equations~\eqref{eqn:limiting_mgale_problem} and~\eqref{eqn:limiting_mgale_variation}
 in Lemma~\ref{lem:limit_mgale}
@@
 \begin{remark}
-Taking $F(x)=x$ and $F(x)=x^2$, we can recover Equation \eqref{eqn:mgale_problem} and \eqref{eqn:mgale_variation} for the limit.
+Taking $F(x)=x$ and $F(x)=x^2$, we can recover Equation \eqref{eqn:limiting_mgale_problem} and \eqref{eqn:limiting_mgale_variation} for the limit.
 Similarly, we can recover

### 2022-08-01 forwards-and-backwards.tex
fixed up proof of boundedness

@@
 Although the models will make sense without this requirement,
-for the purposes of convergence we will also require that $\theta > 1/(\epsilon_\gamma - \epsilon_r)$.
+for the purposes of convergence we will also require that
+$\theta > 2 \sup_x \sup_{y : \|y\| = 1} y^T \covq(x) y/(\epsilon_\gamma^2 - \epsilon_r^2)$.
 \end{definition}
@@
 
+\comment{TODO: move actual proof after its ingredients; just foreshadow here?}
+
 \begin{proof}[Proof of Theorem~\ref{thm:nonlocal_convergence}.]
@@
 and that any limit is a solution to the martingale problem stated in the Theorem.
-This would convergence along $N_k$ to a unique limit
+This would imply convergence along $N_k$ to a unique limit
 if the solution to the martingale problem was unique;
@@
 we first prove a technical lemma which controls spatial density of our population,
-and then we use the Burkholder-Davis-Gundy inequality \comment{TODO CITE}
+and then we use the Burkholder-Davis-Gundy inequality
 to give us control over the running supremum of the total population mass.
@@
 This then allows us to prove that the particle system is tight
-by an application of the Aldous-Rebolledo criterion \comment{TODO CITE}.
-
-\comment{summarize and move to the appendix}
-
+by an application of the Aldous-Rebolledo criterion \citet{rebolledo:1980,alisonsup}.
+
+% % % % % % % % % % % % %
 \subsubsection{Compact Containment Condition}
-Before proving compact containment condition,
-we first prove a technical lemma that involves a bound on the Gaussian kernels.
+
+To show compact containment, we will need boundedness
+of the total net reproduction rate.
+This does not follow immediately from our assumption that $F$ is bounded above
+because reproduction is not local.
+\comment{say more about the difference between $F$ and the total net reproduction rate}
+The following lemma will be useful.
+
 \begin{lemma}
-    \label{lem: gamma - r radius comparison}
+    \label{lem:q_bound}
     Under the assumptions of Definition~\ref{def:model_setup},
-    if $\epsilon_{r}^2 + \frac{1}{\theta} < \epsilon_{\gamma}^2,$ then
-    for all $f \in \mathcal{C}^{2}_{0}(\mathbb{R}^d \times \mathbb{R})$
+    for all $f \in \mathcal{C}^{2}_{0}(\IR^d \times [0,\infty))$,
+    then there exists a $C_f < \infty$ such that
+    for all $\theta > 0$ and all $\eta \in \measures$,
+    \begin{equation*}
+        \left| \theta 
+            \int_{\IR^n} 
+                \left\{
+                    f\left(y, \smooth{r}\eta(y)\right)
+                    -
+                    f\left(x, \smooth{r}\eta(x)\right)
+                \right\}
+            q_{\theta}(x,dy)
+        \right|
+        \leq
+        C_f \left( 1 + \smooth{\gamma} \eta(x)^2 \right)
+    \end{equation*}
+\end{lemma}
+
+\begin{proof}[of Lemma \ref{lem:q_bound}]
+    The key assumption here from Definition~\ref{def:model_setup}
+    will be that $\epsilon_{r}^2 + \frac{2\lambda}{\theta} < \epsilon_{\gamma}^2$,
+    where $\lambda = \sup_x \sup_{y : \|y\| = 1} y^T \covq(x) y$
+    is the largest eigenvalue of $\covq(x)$ across all $x$.
+    First note that 
+    \begin{align} \label{eqn:q_bound_split}
+    &
+        \left| \theta 
+            \int_{\IR^n} 
+                \left\{
+                    f\left(y, \smooth{r}\eta(y)\right)
+                    -
+                    f\left(x, \smooth{r}\eta(x)\right)
+                \right\}
+            q_{\theta}(x,dy)
+        \right|
+    \\ &\qquad {} \leq
+        \left| \theta 
+            \int_{\IR^n} 
+                \left\{
+                    f\left(y, \smooth{r}\eta(y)\right)
+                    -
+                    f\left(x, \smooth{r}\eta(y)\right)
+                \right\}
+            q_{\theta}(x,dy)
+        \right|
+    \\ &\qquad \qquad {}  +
+        \left| \theta 
+            \int_{\IR^n} 
+                \left\{
+                    f\left(x, \smooth{r}\eta(y)\right)
+                    -
+                    f\left(x, \smooth{r}\eta(x)\right)
+                \right\}
+            q_{\theta}(x,dy) 
+        \right| .
+    \end{align}
+
+    Since 
+    \begin{align*}
+        f\left(y, \smooth{r}\eta(y)\right) - f\left(x, \smooth{r}\eta(y)\right)
+        &=
+        \sum_i (y_i - x_i) \partial_{x_i} f \left(x, \smooth{r}\eta(y)\right) 
+        \\ &\qquad {}
+        +
+        \frac{1}{2} \sum_{ij} (y_i - x_i)(y_j - x_j)
+            \partial_{x_i x_j} f \left(z, \smooth{r}\eta(y)\right) 
+    \end{align*}
+    where $z = t x + (1-t) y$ for some $0 \le t \le 1$,
+    writing
+    $K_1 = \sup_{x,m} \max_i |\partial_{x_i} f(x, m)|$
+    and 
+    $K_2 = \sup_{x,m} \max_{i,j} |\partial_{x_i x_j} f(x, m)|$
+    for the bounds on the spatial derivatives of $f$,
+    the first term is bounded by
+    \begin{align*}
+        K_1 \left|
+            \theta \int_{\IR^d} \sum_i (y_i - x_i) q_\theta(x, dy)
+        \right|
+        +
+        K_2 \left|
+            \theta \int_{\IR^d} \sum_{ij} (y_i - x_i) (y_j - x_j)  q_\theta(x, dy)
+        \right| .
+    \end{align*}
+    This is bounded uniformly because
+    $q_\theta(x, dy)$ is the density of a Gaussian with mean $\meanq(x)/\theta$
+    and covariance $\covq(x)/\theta$, and both $\meanq(x)$ and $\covq(x)$
+    are bounded uniformly in $x$.
+
+    Similarly, 
+    \begin{align*}
+        f(x, \smooth{r}\eta(y)) - f(x, \smooth{r}\eta(x))
+        &=
+        (\smooth{r}\eta(y) - \smooth{r}\eta(x)) f'(x, \smooth{r}\eta(x))
+        + \frac{1}{2} (\smooth{r}\eta(y) - \smooth{r}\eta(x))^2 f''(x, m)
+    \end{align*}
+    for some $\smooth{r}\eta(x) \le m \le \smooth{r}\eta(y)$,
+    where $f'$ and $f''$ denote the first and second derivatives with respect to the second argument.
+    So,
+    the second term in~\eqref{eqn:q_bound_split} is bounded by
+    \begin{align*}
+        \|f'\|_\infty
+        \left|
+            \theta \int_{\IR^d}
+                (\smooth{r}\eta(y) - \smooth{r}\eta(x))
+            q_\theta(x, dy)
+        \right|
+        +
+        \|f''\|_\infty
+        \left|
+            \theta \int_{\IR^d}
+                (\smooth{r}\eta(y) - \smooth{r}\eta(x))^2
+            q_\theta(x, dy)
+        \right| .
+    \end{align*}
+    Therefore, it suffices to show that there is a $K < \infty$ such that
+    for all $\eta \in \measures$ and $x \in \IR^d$,
+    \begin{equation}
+        \label{eqn:first_moment_rho}
+        \left|\theta \int_{\mathbb{R}^d}
+            ( \smooth{r} \eta(y)-\smooth{r} \eta(x) )
+        q_\theta(x,dy)\right|
+        \leq K \smooth{\gamma} \eta(x)
+    \end{equation}
+    and
+    \begin{equation}
+        \label{eqn:second_moment_rho}
+        \theta \int_{\mathbb{R}^d}
+                \left( \smooth{r} \eta(y) - \smooth{r} \eta(x) \right)^2
+        q_\theta(x,dy)
+        \leq K \left(\smooth{\gamma}\eta(x) \right)^2 .
+    \end{equation}
+    Note that the right hand side of each is the average density
+    over a wider region (since $\epsilon_\gamma > \epsilon_r$).
+
+    First we prove \eqref{eqn:first_moment_rho}.
+    Recall that $\smooth{r} \eta(x) = \int p_{\epsilon^2_r}(x - w) \eta(dw)$,
+    where $p_t$ is the density of a Gaussian with mean 0 and variance $t$,
+    so that applying Fubini, \eqref{eqn:first_moment_rho} is
+    \begin{align*}
+        \left|
+        \int_{\IR^d}
+        \theta
+            \int_{\IR^d}
+                ( p_{\epsilon_r^2}(y - w) - p_{\epsilon_r^2}(x - w) )
+            q_\theta(x, dy)
+        \eta(dw)
+        \right| .
+    \end{align*}
+    Write $p_{s, x}(\cdot)$ for the density of a Gaussian
+    with mean $s \meanq(x)$ and covariance $\epsilon_r^2 I + s \covq(x)$,
+    so that $\int p_{\epsilon_r^2}(y - w) q_\theta(x, dy) = p_{\epsilon_r^2, 1/\theta, x}(w-x)$.
+    It therefore suffices to show that for all $x$ and $w \in \IR^d$,
+    \begin{align*}
+        \left|
+        \theta
+            \int_{\IR^d}
+                ( p_{\epsilon_r^2}(y-w) - p_{\epsilon_r^2}(x-w) )
+            q_\theta(x, dy)
+        \right|
+        &=
+        \theta \left|
+            p_{1/\theta, x}(w-x) - p_{0, x}(w-x)
+        \right|
+        \le
+        p_{\epsilon^2_\gamma}(w-x) .
+    \end{align*}
+    However,
+    $\theta( p_{1/\theta, x}(z) - p_{0, x}(z) )
+    = \partial_s p_{s, x}(z)$ for some $0 \le s \le 1/\theta$.
+    Write $\Gamma(s,x) = \epsilon_r^2 I + s \covq(x)$,
+    so that
+    \begin{align*}
+        p_{s, x}(z)
+        &=
+        \frac{1}{\left(2 \pi |\Gamma(s,x)|\right)^{d/2}}
+        \exp\left(
+            -\frac{1}{2} (z - s\meanq(x))^T \Gamma(s,x)^{-1} (z - s\meanq(x))
+        \right) ,
+    \end{align*}
+    and note that if $\lambda_i$ are the eigenvalues of $\covq(x)$
+    then $|\Gamma(s, x)| = \prod_i (\epsilon_r^2 + s \lambda_i)$,
+    and
+    $\partial_s |\Gamma(s, x)| = \sum_i \lambda_i |\Gamma(s, x)| / (\epsilon_r^2 + s \lambda_i)$.
+    Therefore,
+    \begin{align*}
+        \partial_s p_{s, x}(z)
+        &=
+        \left(
+            \meanq(x)^T \Gamma(s,x)^{-1} (z - s \meanq)
+            +
+            (z - s \meanq)^T
+            \Gamma(s,x)^{-1} \covq(x) \Gamma(s,x)^{-1}
+            (z - s \meanq)
+            -
+            \sum_i \frac{\lambda_i}{\epsilon_r^2 + s \lambda_i}
+        \right)
+        p_{s, x}(z) ,
+    \end{align*}
+    where $z^T$ is the transpose of $z$.
+    Since $\partial_s p_{s, x}(z) / p_{s, x}(z)$ is a polynomial in $z$
+    with coefficients that are uniformly bounded for $s \ge 1$,
+    it is evident that
+    $\sup_z \partial_s p_{\epsilon_r^2, s, x}(z) / p_{\epsilon_\gamma^2}(z) < \infty$
+    if and only if
+    \begin{align*}
+        \frac{1}{2\epsilon_\gamma^2} \|z\|^2
+        -\frac{1}{2} (z - s\meanq(x))^T \Gamma(s,x)^{-1} (z - s\meanq(x))
+    \end{align*}
+    is negative for all $z$ outside a bounded region.
+    Since $\inf_z z^T \Gamma(s,x)^{-1} z / \|z\|^2 = 1 / (s \lambda(x) + \epsilon_r^2)$,
+    where $\lambda(x) = \sup z^T \covq(x) z / \|z\|^2$ is the largest eigenvalue of $\covq(x)$,
+    equation~\eqref{eqn:first_moment_rho} follows from the assumption
+    that $\epsilon_r^2 + 2 \sup_x \lambda(x)/\theta < \epsilon_\gamma^2$.
+    (Note that we do not yet need the factor of 2.)
+
+    Next we prove equation~\eqref{eqn:second_moment_rho}, in a similar way.
+    Again applying Fubini,
+    \begin{align*}
+        &
+        \theta \int_{\mathbb{R}^d}
+                \left( \smooth{r} \eta(y) - \smooth{r} \eta(x) \right)^2
+        q_\theta(x,dy)
+        \\ &\qquad
+        =
+        \int_{\IR^d} \int_{\IR^d}
+        \theta \int_{\IR^d}
+            ( p_{\epsilon_r^2}(y - w) - p_{\epsilon_r^2}(x - w) )
+            ( p_{\epsilon_r^2}(y - v) - p_{\epsilon_r^2}(x - v) )
+        q_\theta(x, dy)
+        \eta(dv) \eta(dw) ,
+    \end{align*}
+    and so as before, equation~\eqref{eqn:second_moment_rho} will follow if
+    the integrand is bounded by $K p_\gamma(x-w) p_\gamma(x - v)$.
+    % \begin{align*}
+    %     \theta \int_{\IR^d}
+    %         ( p_{\epsilon_r^2}(y - w) - p_{\epsilon_r^2}(x - w) )
+    %         ( p_{\epsilon_r^2}(y - v) - p_{\epsilon_r^2}(x - v) )
+    %     q_\theta(x, dy)
+    %     \le K p_\gamma(x-w) p_\gamma(x - v) .
+    % \end{align*}
+    Now, let $Y_1$, $Y_2$, and $Z$ be independent $d$-dimensional Gaussians with mean zero,
+    where $Y_1$ and $Y_2$ have covariance $\sigma^2_r I$,
+    and $Z$ has covariance $\covq(x)$.
+    Write $p_{s,t,x}(\cdot, \cdot)$ for the joint density of
+    $Y_1 + \sqrt{s} Z + s \meanq(x)$ and $Y_2 + \sqrt{t} Z + t \meanq(x)$.
+    Then, observe that
+    \begin{align*}
+        &
+        \theta \int_{\IR^d}
+            ( p_{\epsilon_r^2}(y - w) - p_{\epsilon_r^2}(x - w) )
+            ( p_{\epsilon_r^2}(y - v) - p_{\epsilon_r^2}(x - v) )
+        q_\theta(x, dy)
+        \\ &\qquad
+        =
+        \theta \left(
+            p_{1/\theta, 1/\theta, x}(x-w, x-v)
+            - p_{0, 1/\theta, x}(x-w, x-v)
+        \right. \\ &\qquad \qquad \left. {}
+            - p_{1/\theta, 0, x}(x-w, x-v)
+            + p_{0, 0, x}(x-w, x-v)
+        \right) 
+        \\ &\qquad 
+        =
+            \partial_s p_{s, 1/\theta, x}(x-w, x-v)
+            - \partial_t p_{0, t, x}(x-w, x-v) ,
+    \end{align*}
+    for some $0 \le s, t \le 1/\theta$.
+    As before, $\partial_s p_{s, t, x}(y_1, y_2)$ has polynomial terms multiplying
+    $$
+        \exp\left(
+            - \frac{1}{2} [y_1, y_2[^T \Gamma(s, t, x)^{-1} [y_1, y_2]
+        \right) ,
+    $$
+    where $[y_1, y_2]$ is the $\IR^{2d}$ vector formed by concatenating $y_1$ and $y_2$,
+    and $\Gamma(s, t, x)$ is the block matrix
+    \begin{align*}
+        \Gamma(s, t, x)
+        =
+        \left[
+        \begin{array}{cc}
+            \epsilon_r^2 I + s \covq(x) & \sqrt{st} \covq(x) \\
+            \sqrt{st} \covq(x) & \epsilon_r^2 I + t \covq(x) \\
+        \end{array}
+        \right] .
+    \end{align*}
+    If $\covq(x) u = a u$ for some $a \in \IR$,
+    then $[u \sqrt{s}, u \sqrt{t}]$ is an eigenvector of $\Gamma(s, t, x)$
+    with eigenvalue $\epsilon^2_r + (s+t) a$,
+    and $[u \sqrt{t}, - u \sqrt{s}]$ is an eigenvector of $\Gamma(s, t, x)$
+    with eigenvalue 0.
+    This implies the largest eigenvalue of $\Gamma(s, t, x)$
+    is equal to $\epsilon^2_r + (s+t) \lambda(x)$,
+    where $\lambda(x)$ is again the largest eigenvalue of $\covq(x)$.
+    Therefore, if $s + t \le 2 / \theta$,
+    \begin{align*}
+        &
+        (\|y_1\|^2 + \|y_2\|^2) / \epsilon^2_\gamma
+            - [y_1, y_2[^T \Gamma(s, t, x)^{-1} [y_1, y_2]
+        \\ &\qquad \le
+        (\|y_1\|^2 + \|y_2\|^2) \left(
+            \frac{1}{\epsilon^2_\gamma}
+            - \frac{1}{\epsilon^2_r +  2\lambda(x)/\theta}
+        \right) ,
+    \end{align*}
+    which is negative by assumption.
+    Therefore, there is a $K$ such that
+    \begin{align*}
+        \frac{ \left|
+            \partial_s p_{s, 1/\theta, x}(x-w, x-v)
+            - \partial_t p_{0, t, x}(x-w, x-v)
+        \right| }{
+            p_{\epsilon^2_\gamma}(x - w)
+            p_{\epsilon^2_\gamma}(x - v)
+        }
+        \le K
+    \end{align*}
+    for all $\theta > 1$ and all $x$, $v$, and $w \in \IR^d$,
+    proving equation~\eqref{eqn:second_moment_rho} and hence the lemma.
+\end{proof}
+
+\begin{corollary}
+    \label{cor:gamma_bound}
+    Under the assumptions of Definition~\ref{def:model_setup},
+    including that $\epsilon_{r}^2 + \frac{1}{\theta} < \epsilon_{\gamma}^2$,
+    for all $f \in \mathcal{C}^{2}_{0}(\IR^d \times \IR)$
     with bounded first and second derivatives
-    and for all $\eta \in \mathcal{M}_{f}(\mathbb{R}^d)$, we have
-
+    and for all $\eta \in \measures$, we have
     \begin{equation}\label{eq: gamma - r radius comparison bound}
@@
     \left| \theta 
-        \int_{\mathbb{R}^n} 
+        \int_{\IR^n} 
             \big\{
@@
     for some constant $C_{\gamma,f}$ independent of $\eta$ and $\theta$. 
-\end{lemma}
+\end{corollary}
+
 \begin{proof}
@@
 for some $u \in [0, 1/\theta]$ by Mean Value Theorem. We have therefore established our bound as $J(s)$ has bounded derivative in a neighbourhood around $0$.
+\comment{This is not enough, since we need to show the constant holds for all $x$, and $J$ depends on $x$.}
 
@@
 \end{equation}
-where the last inequality holds by Lemma \ref{lem: gamma - r radius comparison}.
+where the last inequality holds by Lemma \ref{cor:gamma_bound}.
 
@@
 \end{multline}
-since the first term is bounded above by $C_{\gamma,r}f(x)$ by Lemma \ref{lem: gamma - r radius comparison}
+since the first term is bounded above by $C_{\gamma,r}f(x)$ by Lemma \ref{cor:gamma_bound}
 and the second term by $C_{\gamma} \Delta f(x)$ as $r \leq 1$.

### 2022-08-02 forwards-and-backwards.tex
.

@@
 \begin{equation}
-    \label{eq: Pre-limit Martingale Characterisation}
+    \label{eqn:eta_martingale}
 \begin{aligned}
@@
 since individuals are produced at rate $N \gamma \eta$ but have mass $1/N$ each,
-these factors of $N$ cancel in~\eqref{eq: Pre-limit Martingale Characterisation}.
+these factors of $N$ cancel in~\eqref{eqn:eta_martingale}.
 Since we are taking a diffusion limit,
@@
 we get the generator for the population process
-(visible in equation~\eqref{eq: Pre-limit Martingale Characterisation}
+(visible in equation~\eqref{eqn:eta_martingale}
 or~\eqref{eqn:limiting_mgale_problem}, respectively).
@@
 (i.e., solution to the martingale problem of Definition~\ref{defn:mgale_construction})
-% of equations~\eqref{eq: Pre-limit Martingale Characterisation} and \eqref{eqn:prelimit_martingale_variation}
+% of equations~\eqref{eqn:eta_martingale} and \eqref{eqn:prelimit_martingale_variation}
 there is a lookdown representation $(\lp^N_t)_{t \ge 0}$
@@
 To do this, we first prove that $\sup_{0 \le t \le T} \langle 1, \eta^N_t \rangle$ is tight
-(a compact containment condition, Lemma~\ref{lem: Compact Containment}).
+(a compact containment condition, Lemma~\ref{lem:eta_compact_containment}).
 (The reason we use $\cmeasures$ instead of $\measures$
@@
 To show compact containment, we will need boundedness
-of the total net reproduction rate.
+of the net per-capita reproduction rate.
 This does not follow immediately from our assumption that $F$ is bounded above
-because reproduction is not local.
-\comment{say more about the difference between $F$ and the total net reproduction rate}
-The following lemma will be useful.
+because reproduction is not local:
+the net per-capita reproduction rate of an individual at $x$ is
+$$
+\theta \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q_\theta(x, dy) - \theta \mu(x, \eta)
+=
+F(x, \eta) + \gamma(x, \eta) \theta \int_{\IR^d} (r(y, \eta) - r(x, \eta)) q_\theta(x, dy) .
+$$
+We have assumed that $F$ is bounded,
+but we still need to show that our assumptions imply that
+the second term is bounded, uniformly as $\theta$ grows.
 
 \begin{lemma}
-    \label{lem:q_bound}
+    \label{lem:gamma_bound}
     Under the assumptions of Definition~\ref{def:model_setup},
     for all $f \in \mathcal{C}^{2}_{0}(\IR^d \times [0,\infty))$,
-    then there exists a $C_f < \infty$ such that
+    there exists a $K_f < \infty$ such that
     for all $\theta > 0$ and all $\eta \in \measures$,
+    \begin{equation} \label{eqn:gamma_bound}
+    \gamma\big(x,\smooth{\gamma} \eta(x)\big)
+    \left| \theta 
+        \int_{\IR^n} 
+            \left\{
+                f(y, \smooth{r} \eta(y)) - f(x, \smooth{r} \eta(x))
+            \right\}
+        q_{\theta}(x,dy)
+    \right|
+    \leq C_f     .
+    \end{equation}
+\end{lemma}
+
+The key assumption here from Definition~\ref{def:model_setup}
+will be that the spatial scale over which local density affects birth rate
+is larger than the scale over which it affects establishment:
+concretely, that $\epsilon_{r}^2 + \frac{2\lambda}{\theta} < \epsilon_{\gamma}^2$,
+where $\lambda = \sup_x \sup_{y : \|y\| = 1} y^T \covq(x) y$
+is the largest eigenvalue of $\covq(x)$ across all $x$.
+In the simple case of $\meanq = 0$ and $\covq = \sigma^2 I$,
+the condition is simply that $\epsilon_r^2 + 2\sigma^2 / \theta < \epsilon_\gamma^2$.
+
+\begin{proof}[of Lemma \ref{lem:gamma_bound}]
+
+    Since we have assumed that there is a $K$ for which $m^2 \gamma(x, m) < K$
+    for all $x \in \IR^d$ and $m \ge 0$,
+    equation~\eqref{eqn:gamma_bound} will follow if we can show that
     \begin{equation*}
@@
         \leq
-        C_f \left( 1 + \smooth{\gamma} \eta(x)^2 \right)
+        C_f \left( 1 + \smooth{\gamma} \eta(x)^2 \right) .
     \end{equation*}
-\end{lemma}
-
-\begin{proof}[of Lemma \ref{lem:q_bound}]
-    The key assumption here from Definition~\ref{def:model_setup}
-    will be that $\epsilon_{r}^2 + \frac{2\lambda}{\theta} < \epsilon_{\gamma}^2$,
-    where $\lambda = \sup_x \sup_{y : \|y\| = 1} y^T \covq(x) y$
-    is the largest eigenvalue of $\covq(x)$ across all $x$.
-    First note that 
+    To do this, first note that 
     \begin{align} \label{eqn:q_bound_split}
@@
     with mean $s \meanq(x)$ and covariance $\epsilon_r^2 I + s \covq(x)$,
-    so that $\int p_{\epsilon_r^2}(y - w) q_\theta(x, dy) = p_{\epsilon_r^2, 1/\theta, x}(w-x)$.
+    so that $\int p_{\epsilon_r^2}(y - w) q_\theta(x, dy) = p_{1/\theta, x}(w-x)$.
     It therefore suffices to show that for all $x$ and $w \in \IR^d$,
-    \begin{align*}
+    there exists $K$ such that
+    \begin{align} \label{eqn:goal1}
         \left|
@@
         \le
-        p_{\epsilon^2_\gamma}(w-x) .
-    \end{align*}
+        K p_{\epsilon^2_\gamma}(w-x) .
+    \end{align}
     However,
@@
             +
-            (z - s \meanq)^T
+            (z - s \meanq(x))^T
             \Gamma(s,x)^{-1} \covq(x) \Gamma(s,x)^{-1}
-            (z - s \meanq)
+            (z - s \meanq(x))
+        \right. \\ & \qquad \qquad \qquad \left. {}
             -
@@
     where $z^T$ is the transpose of $z$.
-    Since $\partial_s p_{s, x}(z) / p_{s, x}(z)$ is a polynomial in $z$
-    with coefficients that are uniformly bounded for $s \ge 1$,
-    it is evident that
-    $\sup_z \partial_s p_{\epsilon_r^2, s, x}(z) / p_{\epsilon_\gamma^2}(z) < \infty$
-    if and only if
-    \begin{align*}
+    This implies that
+    \begin{align*}
+        \frac{
+        \theta
+            \int_{\IR^d}
+                ( p_{\epsilon_r^2}(y-w) - p_{\epsilon_r^2}(x-w) )
+            q_\theta(x, dy)
+        }{
+            p_{\epsilon^2_\gamma}(w-x) .
+        }
+        =
+        h(z) e^{k(z)},
+    \end{align*}
+    where $h(z)$ and $k(z)$ are quadratic polynomials in $z$
+    whose coefficients depend on $s$ and $x$ but are uniformly bounded for $s \ge 1$
+    and $x \in \IR^d$.
+    Therefore, \eqref{eqn:goal1} holds for some finite $K$
+    if and only if $k(z) < 0$ for all $z$ outside some bounded region.
+    This is
+    \begin{align*}
+        k(z)
+        =
         \frac{1}{2\epsilon_\gamma^2} \|z\|^2
-        -\frac{1}{2} (z - s\meanq(x))^T \Gamma(s,x)^{-1} (z - s\meanq(x))
-    \end{align*}
-    is negative for all $z$ outside a bounded region.
+        -\frac{1}{2} (z - s\meanq(x))^T \Gamma(s,x)^{-1} (z - s\meanq(x)) ,
+    \end{align*}
+    which is negative for all $z$ outside a bounded region.
     Since $\inf_z z^T \Gamma(s,x)^{-1} z / \|z\|^2 = 1 / (s \lambda(x) + \epsilon_r^2)$,
@@
     Now, let $Y_1$, $Y_2$, and $Z$ be independent $d$-dimensional Gaussians with mean zero,
-    where $Y_1$ and $Y_2$ have covariance $\sigma^2_r I$,
+    where $Y_1$ and $Y_2$ have covariance $\epsilon^2_r I$,
     and $Z$ has covariance $\covq(x)$.
@@
     for some $0 \le s, t \le 1/\theta$.
-    As before, $\partial_s p_{s, t, x}(y_1, y_2)$ has polynomial terms multiplying
-    $$
-        \exp\left(
-            - \frac{1}{2} [y_1, y_2[^T \Gamma(s, t, x)^{-1} [y_1, y_2]
-        \right) ,
-    $$
-    where $[y_1, y_2]$ is the $\IR^{2d}$ vector formed by concatenating $y_1$ and $y_2$,
+    As before,
+    \begin{align*}
+        \frac{
+            \theta \int_{\IR^d}
+                ( p_{\epsilon_r^2}(y - w) - p_{\epsilon_r^2}(x - w) )
+                ( p_{\epsilon_r^2}(y - v) - p_{\epsilon_r^2}(x - v) )
+            q_\theta(x, dy)
+        }{
+            p_{\epsilon_\gamma^2}(x - w)
+            p_{\epsilon_\gamma^2}(x - v)
+        }
+        =
+        h(x-w, x-v) e^{ k(x-w, x-v) },
+    \end{align*}
+    where $h(z_1, z_2)$ is a polynomial with uniformly bounded coefficients and
+    \begin{align*}
+        k(z_1, z_2)
+        =
+        (\|z_1\|^2 + \|z_2\|^2)/(2 \epsilon_\gamma^2)
+            - \frac{1}{2} [z_1, z_2[^T \Gamma(s, t, x)^{-1} [z_1, z_2] ,
+    \end{align*}
+    where $[z_1, z_2]$ is the $\IR^{2d}$ vector formed by concatenating $z_1$ and $z_2$,
     and $\Gamma(s, t, x)$ is the block matrix
@@
         &
-        (\|y_1\|^2 + \|y_2\|^2) / \epsilon^2_\gamma
-            - [y_1, y_2[^T \Gamma(s, t, x)^{-1} [y_1, y_2]
+        (\|z_1\|^2 + \|z_2\|^2) / \epsilon^2_\gamma
+            - [z_1, z_2[^T \Gamma(s, t, x)^{-1} [z_1, z_2]
         \\ &\qquad \le
-        (\|y_1\|^2 + \|y_2\|^2) \left(
+        (\|z_1\|^2 + \|z_2\|^2) \left(
             \frac{1}{\epsilon^2_\gamma}
@@
 
-\begin{corollary}
-    \label{cor:gamma_bound}
+\begin{lemma}
+    \label{lem:eta_f_bound}
     Under the assumptions of Definition~\ref{def:model_setup},
-    including that $\epsilon_{r}^2 + \frac{1}{\theta} < \epsilon_{\gamma}^2$,
-    for all $f \in \mathcal{C}^{2}_{0}(\IR^d \times \IR)$
-    with bounded first and second derivatives
-    and for all $\eta \in \measures$, we have
-    \begin{equation}\label{eq: gamma - r radius comparison bound}
-    \gamma\big(x,\rho_{\gamma}*\eta(x)\big)
-    \left| \theta 
-        \int_{\IR^n} 
-            \big\{
-                f\big(y,\rho_{r}*\eta(y)\big)-f\big(x,\rho_{r}*\eta(x)\big)
-            \big\}
-        q_{\theta}(x,dy)
-    \right|
-    \leq C_{\gamma, f}    
-    \end{equation}
-    for some constant $C_{\gamma,f}$ independent of $\eta$ and $\theta$. 
-\end{corollary}
+    if $\eta^{N}_0 \to \eta_0$ weakly as $N \to \infty$,
+    then for all $f \in C^2_0(\IR^d)$ there exists a $C_f < \infty$
+    such that
+    $$
+        \IE[\langle f, \eta^N_t \rangle]
+        \le
+        \IE[\langle f, \eta^N_0 \rangle]
+        e^{Ct}
+    $$
+    for all $N > 0$.
+\end{lemma}
 
 \begin{proof}
-Since $f(x_1,...,x_d,w)$ is twice differentiable, we can Taylor expand $f$ around  $(x_1,...,x_d,\rho_{r}*\eta(x))$ up to second order and obtain that for $x=(x_1,..,x_d)$,
-\begin{equation}
-\begin{aligned}
-&~f\big(y,\rho_{r}*\eta(y)\big)-f\big(x,\rho_{r}*\eta(x)\big)\\
-=&~ \nabla_x f \big(x,\rho_{r}*\eta(x)\big)
-            \cdot (y-x)\\ 
-        &~ + \frac{\partial f}{\partial w}
-            \big(x,\rho_{r}*\eta(x)\big) \left(\rho_{r}*\eta(y)-\rho_{r}*\eta(x)\right)\\
-        &~ + \frac{1}{2}\sum_{1 \leq i,j \leq d }\frac{\partial^2 f}{\partial x_i x_j}
-            \big(z,\rho_{r}*\eta(z)\big) (y_i-x_i)(y_j-x_j)\\
-        &~ + \frac{1}{2}\sum_{1 \leq i \leq d}
-                \frac{\partial^2 f}{\partial w \partial x_i}
-                 \big(z,\rho_{r}*\eta(z)\big) (y_i-x_i)
-                    \left(\rho_{r}*\eta(y)-\rho_{r}*\eta(x)\right)\\
-        &~ + \frac{1}{2}\frac{\partial^2 f}{\partial^2 w}
-            \big(z,\rho_{r}*\eta(z)\big)
-            \left(
-            \rho_{r}*\eta(y)-\rho_{r}*\eta(x)
-            \right)^2,
-\end{aligned}    
-\end{equation}
-where $z=ty+(1-t)x$ for some $t \in [0,1]$.
-
-Write $||Df||_{\infty}$ and $||D^2f||_{\infty}$
-for the suprema of the first and second derivatives of $f$
-(which we have assumed are bounded).
-Therefore, we have that 
-\begin{equation}
-\begin{aligned}
-&~\left| 
-        \theta \int_{\mathbb{R}^d}
-                f\big(y,\rho_{r}*\eta(y)\big)-f\big(x,\rho_{r}*\eta(x)\big)
-                q_{\theta}(x,dy)
-\right|\\
-\leq &~ ||Df||_{\infty} \left|
-                        \theta \int_{\mathbb{R}^d} \sum_{i=1,..,d}(y_i-x_i) q_{\theta}(x,dy)
-                        \right|\\ 
-        &~ + ||Df||_{\infty} 
-            \left| \theta \int_{\mathbb{R}^d}
-               \left(\rho_{r}*\eta(y)-\rho_{r}*\eta(x)\right)
-            q_{\theta}(x,dy) \right| \\
-        &~ + \frac{1}{2}||D^2f||_{\infty}\left|
-                        \theta \int_{\mathbb{R}^d} (y-x)(y-x)^{T} q_{\theta}(x,dy)
-                        \right|\\
-        &~ + \frac{1}{2}||D^2f||_{\infty}    
-                \sum_{1 \leq i \leq d}\left|
-                        \theta \int_{\mathbb{R}^d}
-                        \left(\rho_{r}*\eta(y)-\rho_{r}*\eta(x)\right)
-                  (y_i-x_i)
-                        q_{\theta}(x,dy)
-                        \right|
-                    \\
-        &~ + \frac{1}{2}||D^2f||_{\infty} \left|
-            \theta \int_{\mathbb{R}^d}
-            \left(\rho_{r}*\eta(y)-\rho_{r}*\eta(x)
-            \right)^2
-            q_\theta(x,dy) \right|
-\end{aligned}    
-\end{equation}
-Recall that $q_{\theta}(x,dy)$ is a Gaussian kernel
-with mean $\meanq/\theta$
-and covariance matrix $\covq / \theta$.
-As a result, the first and third term
-is easily bounded above by 
-\comment{I'm not sure about the L1 norm in the next two equations:}
-$$||Df||_{\infty} \left|
-                        \theta \int_{\mathbb{R}^d} \sum_{i=1,..,d}(y_i-x_i) q_{\theta}(x,dy)
-                        \right|
-                        \leq  ||Df||_{\infty}||\meanq||_{1},$$
-and 
-$$ \frac{1}{2}|D^2f||_{\infty}\left|
-                        \theta \int_{\mathbb{R}^d} (y-x)(y-x)^{T} q_{\theta}(x,dy)
-                        \right| \leq \frac{1}{2}||D^2f||_{\infty} ||\covq||_{1}.$$
-For the cross term, we apply Cauchy's inequality to obtain
-\comment{What's $||C||_{1/2}$?}
-\begin{equation}
-\begin{aligned}
-&\frac{1}{2}|D^2f||_{\infty}\sum_{1 \leq i \leq d}    
-                \left|
-                        \theta \int_{\mathbb{R}^d}
-                        \left(\rho_{r}*\eta(y)-\rho_{r}*\eta(x)\right)
-                  (y_i-x_i)
-                        q_{\theta}(x,dy)
-                        \right|\\
-\leq& \frac{1}{2}|D^2f||_{\infty} \sum_{1 \leq i \leq d} 
-        \sqrt{\theta \int_{\mathbb{R}^d}
-           (y_i-x_i)^2
-            q_\theta(x,dy)
-            }
-        \sqrt{
-            \theta \int_{\mathbb{R}^d}
-            \left(\rho_{r}*\eta(y)-\rho_{r}*\eta(x)
-            \right)^2
-            q_\theta(x,dy) 
-            }    \\
-\leq& \frac{1}{2}|D^2f||_{\infty} ||\covq||_{1/2}
-        \sqrt{
-            \theta \int_{\mathbb{R}^d}
-            \left(\rho_{r}*\eta(y)-\rho_{r}*\eta(x)
-            \right)^2
-            q_\theta(x,dy) 
-            }.    
-\end{aligned}
-\end{equation}
-\comment{We've only assumed boundedness of $z^2 \gamma$! Do we need $z \gamma$ also?}
-We have assumed in Definition~\ref{def:model_setup}
-(for this reason) that $z\gamma(x,z)$ and $z^2 \gamma(x,z)$ is bounded above
-for all $z  \geq 0$.
-Therefore, it suffices to show that
-for all $\eta \in \mathcal{M}_{f}(\mathbb{R}^d)$,
-\begin{equation}
-    \label{eq: r-gamma first moment control}
-\left|\theta \int_{\mathbb{R}^d}
-            \left(\rho_{r}*\eta(y)-\rho_{r}*\eta(x)
-            \right)
-            q_\theta(x,dy)\right|
-            \leq \rho_{\gamma}*\eta(x),    
-\end{equation}
-and
-\begin{equation}
-    \label{eq: r-gamma comparison square term}
-\theta \int_{\mathbb{R}^d}
-            \left(\rho_{r}*\eta(y)-\rho_{r}*\eta(x)
-            \right)^2
-            q_\theta(x,dy)
-            \leq \rho_{\gamma}*\eta(x)^2.    
-\end{equation}
-We first prove Equation \eqref{eq: r-gamma first moment control}.
-Note that 
-$$ \left(\rho_{r}*\eta(y)-\rho_{r}*\eta(x)\right)
-        = \left\langle p_{\epsilon^2_r}(y-w)-p_{\epsilon^2_r}(x-w),             \eta(dw)\right \rangle,$$
-so applying Fubini's theorem, 
-\begin{equation}
-\left|\theta \int_{\mathbb{R}^d}
-            \left(\rho_{r}*\eta(y)-\rho_{r}*\eta(x)
-            \right)
-            q_\theta(x,dy)\right|
-            = \left\langle \left| \theta \int_{\mathbb{R}^d} \left(p_{\epsilon^2_r}(y-w)-p_{\epsilon^2_r}(x-w)\right)
-            q_\theta(x,dy) \right| , \eta(dw)\right \rangle.    
-\end{equation}
-It suffices therefore to show that for all $w \in \mathbb{R}^d$,
-\begin{equation}
-\left| \theta \int_{\mathbb{R}^d} \left(p_{\epsilon^2_r}(y-w)-p_{\epsilon^2_r}(x-w)\right)
-            q_\theta(x,dy) \right| \leq p_{\epsilon^2_{\gamma}}(x-w).
-\end{equation}
-By the Chapman-Kolmogorov equality, we have
-\begin{align}
-&\left| \theta \int_{\mathbb{R}^d}
-                \left(p_{\epsilon^2_r}(y-w)
-                        -p_{\epsilon^2_r}(x-w)
-                \right)
-                q_\theta(x,dy)
-        \right|\\
-        =& \theta \left\{
-                    \frac{\epsilon^d_r }{\left|\covq / \theta +  \epsilon^2_r I \right|^{1/2}}
-                    \exp \left(
-                    \frac{(x-w-\meanq / \theta)^{T}
-                        (\covq /\theta +  \epsilon^2_r I)^{-1}
-                        (x-w-\meanq / \theta)}{2}
-                        -\frac{|x-w|^2}{2\epsilon^2}
-                    \right)
-                    -1\right\}\\
-         & \times p_{\epsilon^2_r}(x-w).
-\end{align}
-If we write 
-\begin{equation}
-J(s)=  \frac{\epsilon^d_r }
-        {\left|\covq s +  \epsilon^2_r I \right|^{1/2}}
-        \exp \left(
-                    \frac{(x-w-\meanq s)^{T}
-                        (\covq s +  \epsilon^2_r I)^{-1}
-                        (x-w-\meanq s)}{2}
-                        -\frac{|x-w|^2}{2\epsilon^2}
-            \right)
-        -1,   
-\end{equation}
-then $J(0)=0$ and
-
-\begin{align}
-J'(s)=&  -\frac{\epsilon^d_r |\covq|}
-        {2\left|\covq s +  \epsilon^2_r I \right|^{3/2}}
-        \exp \left(
-                    \frac{(x-w-\meanq s)^{T}
-                        (\covq s +  \epsilon^2_r I)^{-1}
-                        (x-w-\meanq s)}{2}
-                        -\frac{|x-w|^2}{2\epsilon^2}
-            \right)\\
-    &+\frac{\epsilon^d_r }
-        {\left|\covq s +  \epsilon^2_r I \right|^{1/2}}
-        \exp \left(
-                    \frac{(x-w-\meanq s)^{T}
-                        (\covq s +  \epsilon^2_r I)^{-1}
-                        (x-w-\meanq s)}{2}
-                        -\frac{|x-w|^2}{2\epsilon^2}
-            \right) \\
-    & \qquad \times \frac{1}{2}
-                    \bigg\{
-                         -\meanq^{T}(\covq s + \epsilon^2_r I)^{-1}(x-w-\meanq s)\\
-    & \qquad \qquad     -(x-w-\meanq s)^{T}
-                        (\covq s +  \epsilon^2_r I)^{-1}\meanq\\
-    & \qquad \qquad     -(x-w-\meanq s)^{T}
-                        \covq(\covq s +  \epsilon^2_r I)^{-2}(x-w-\meanq s)                    
-                    \bigg\},
-\end{align}
-which is continuous and bounded near $s=0$.
-As a result,
-\begin{align}
-\left| \theta \int_{\mathbb{R}^d}
-                \left(p_{\epsilon^2_r}(y-w)
-                        -p_{\epsilon^2_r}(x-w)
-                \right)
-                q_\theta(x,dy)
-        \right|
-        \leq&  \theta \left(J\left(1 / \theta \right)-1\right) 
-                \times \epsilon_\gamma^d \epsilon_r^{-d}
-                p_{\epsilon^2_\gamma}(x-w)\\
-         =&  J'(u) 
-                \times \epsilon_\gamma^d \epsilon_r^{-d}
-                p_{\epsilon^2_\gamma}(x-w)        
-\end{align}
-for some $u \in [0, 1/\theta]$ by Mean Value Theorem. We have therefore established our bound as $J(s)$ has bounded derivative in a neighbourhood around $0$.
-\comment{This is not enough, since we need to show the constant holds for all $x$, and $J$ depends on $x$.}
-
-We now prove Equation \eqref{eq: r-gamma comparison square term}. Applying Jensen's inequality, we have
-\begin{align}
-&\left\{
-            \rho_r * \eta(y)
-            -
-            \rho_r * \eta(x)
-\right\}^2  \\
-&\qquad
-=
-\left\{
-\int
-    \left(
-        \rho_r(y-w)
-        -
-        \rho_r(x-w)
-    \right)
-\eta(dw)
-\right\}^2  \\
-&\qquad
-=
-\left\{
-\int
-    \left(
-        \frac{\rho_r(y-w)}{\rho_r(x-w)}
-        -
-        1
-    \right)
-    \rho_r(x-w)
-\eta(dw)
-\right\}^2  \\
-&\qquad
-=
-\left(\rho_r * \eta(x)\right)^2 \left\{
-\int
-    \left(
-        \frac{\rho_r(y-w)}{\rho_r(x-w)}
-        -
-        1
-    \right)
-    \frac{\rho_r(x-w)}{\rho_r * \eta(x)}
-\eta(dw)
-\right\}^2  \\
-&\qquad
-\le
-\left(\rho_r * \eta(x)\right)^2 
-\int
-    \left(
-        \frac{\rho_r(y-w)}{\rho_r(x-w)}
-        -
-        1
-    \right)^2
-    \frac{\rho_r(x-w)}{\rho_r * \eta(x)}
-\eta(dw) \\
-&\qquad
-=
-\rho_r * \eta(x)
-\int
-    \left(
-        \frac{\rho_r(y-w)}{\rho_r(x-w)}
-        -
-        1
-    \right)^2
-    \rho_r(x-w)
-\eta(dw).
-\end{align}
-Note that since $\epsilon_{\gamma}>\epsilon_{r}$,
-\begin{equation}
-    \label{eq: gamma-r convolution comparison}
-\begin{aligned}
- \rho_r * \eta(x)=& \int p_{\epsilon^2_r}(x-w) \eta(dw)\\
-                 =&  \int \frac{p_{\epsilon^2_r}(x-w)}{p_{\epsilon^2_\gamma}(x-w)}
-                  p_{\epsilon^2_\gamma}(x-w) \eta(dw)\\
-            \leq & \int \epsilon_\gamma^d \epsilon_r^{-d}
-                   e^{-(x-w)^2(\frac{1}{\epsilon^2_r}-\frac{1}{\epsilon^2_\gamma})}
-                   p_{\epsilon^2_\gamma}(x-w) \eta(dw)\\
-            \leq & \epsilon_\gamma^d \epsilon_r^{-d}\rho_\gamma * \eta(x),
-\end{aligned}
-\end{equation}
-it suffices to show that 
-\begin{equation}\label{eq: gaussian density estimate}
- \theta H_{\theta}(x,w)\rho_r(x-w)\leq \rho_{\gamma}(x-w),
-\end{equation}
-where
-$$H_{\theta}(x,w)=\int_{\mathbb{R}^d}
-    \left(
-        \frac{\rho_r(y-w)}{\rho_r(x-w)}
-        -
-        1
-    \right)^2
-q_{\theta}(x,dy).$$
-For the proof of Equation \eqref{eq: gaussian density estimate} refer to Lemma \ref{eq: Gaussin density estimates} in the Appendix.
-
+    \comment{TODO: copy over from below}
 \end{proof}
 
-\begin{lemma}[Compact Containment for the population process]
-    \label{lem: Compact Containment}
-If $\eta^{N}_0 \to \eta_0$ weakly as $N \to \infty$,
-then for all $T>0$, there exists some constant $C_T$,
+With a bound on per-capita net growth rate in hand,
+bounds on the total population size follow easily.
+
+\begin{lemma}[Compact containment for the population process]
+    \label{lem:eta_compact_containment}
+    Under the assumptions of Definition~\ref{def:model_setup},
+    if $\theta/N \to \alpha$ and $\eta^{N}_0 \to \eta_0$ weakly as $N \to \infty$,
+    then for all $T>0$ and $N > 0$, there exists some constant $C_T$,
     such that
     \begin{align}
-        \label{eq: Growth function bound on running sup}
+        \label{eqn:eta_mass_bound}
         \IE\left[
@@
         \right]
-        \le C_T ,
+        \le C_T .
     \end{align}
-uniformly in $\theta$.
     In particular, for any $\epsilon > 0$, there exists some $K_{\epsilon}>0$ such that
@@
 \begin{proof}
-    \comment{TODO: superscript $\theta$ should be $N$ below}
-We first take $f \equiv 1$ in Equation \eqref{eq: Pre-limit Martingale Characterisation}.
-\comment{TODO: Write $[M]_t$ instead of $[M_t]$ for quadratic variation.}
-We have that 
-\begin{equation}
-    \label{eq: Total Mass Martingale Characterisation}
-\begin{aligned}
-     M^{\theta}_t(1):=&  \langle 1,\eta^{N}_t \rangle
-        -\langle 1,\eta^{N}_0 \rangle\\
- &-  \int_{0}^{t}\bigg\{   \int\left(   \int \theta
- \left(
-        r\big(z,\rho_{r}*\eta^{N}_{s}(z)\big)
-            -r\big(x,\rho_{r}*\eta^{N}_{s}(x)\big)
-            \right)
-                    q_\theta(x,dz)\right)
-                            \gamma\big(x,\rho_{\gamma}*\eta^{N}_{s}(x)\big)
-                            \eta^{N}_{s}(dx)\\
-& \qquad +\int F\big(x,\rho_{F}*\eta^{N}_{s}(x)\big)
-\eta^{N}_{s}(dx)\bigg\} ds
-\end{aligned}    
-\end{equation}
-is a martingale.
-Therefore, taking expectations, we have
-\begin{equation}\label{eq: Total mass control generalised}
-\begin{aligned}
-&\mathbb{E}[\langle 1 ,\eta^{N}_{t}\rangle] \\
-\leq &  \mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle] \\
-&+ \int_{0}^{t}\mathbb{E}\bigg\langle
-        \gamma\big(x,\rho_{\gamma}*\eta^{N}_{s}(x)\big)
-            \left| \theta \int_{\mathbb{R}^n}
-                    \big\{r\big(\rho_{r}*\eta^{N}_s(y)\big)-r\big(\rho_{r}*\eta^{N}_s(x)\big)\big\}
-                    \rho_{1/\theta}(x-y)dy\right| + C_F 
-                            ,\eta^{N}_s(dx)  \bigg\rangle ds\\
-\leq &  \mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle] + (C_{\gamma,r} + C_F)\int_{0}^{t}\mathbb{E} \langle 1  ,\eta^{N}_s(dx) \rangle ds,
-\end{aligned}
-\end{equation}
-where the last inequality holds by Lemma \ref{cor:gamma_bound}.
-
-Applying Gronwall's inequality, we have that 
-\begin{equation}
- \mathbb{E}[\langle 1 ,\eta^{N}_{t}\rangle] \leq \mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle]e^{(C_{\gamma,r}+C_F)t}.   
-\end{equation}
-
-To prove compact containment condition, we apply BDG inequality.
-We denote $M^{*}_t(\phi)=\sup_{s \in [0,t]}M_t(\phi)$
-and define $h(t):=\sup_{s \in [0,t]}\langle 1, \eta^{N}_{s} \rangle$.
-We have that
-\begin{equation}\label{eq: Control quadratic variation}
-\begin{aligned}
-\mathbb{E}\{M^{*}_t(1)\} \leq & C \mathbb{E}\{[M_t(1)]^{1/2}\}\\
-\leq& C (1+\mathbb{E}\{[M_t(1)]\})\\
-\leq & C+\frac{\theta}{N}\int_{0}^{t} \left\langle \gamma(\rho_{\gamma}*\eta^{N}_{s}(x))\int_{\mathbb{R}^n}r(\rho_{r}*\eta^{N}_{s}(y)) q_\theta(x,dy)+\mu(x,\eta^{N}_{s}), \eta^{N}_{s}(dx) \right\rangle ds \\
-\leq & C+\frac{2\theta}{N}\int_{0}^{t} \left\langle \gamma(\rho_{\gamma}*\eta^{N}_{s}(x))r(\rho_{r}*\eta^{N}_{s}(x)), \eta^{N}_{s}(dx) \right\rangle ds \\
-& + \frac{1}{N}\int_{0}^{t} \left\langle \gamma (\rho_{\gamma}*\eta^{N}_{s}(x))\theta\int_{\mathbb{R}^n}\left(r(\rho_{r}*\eta^{N}_{s}(y))-r(\rho_{r}*\eta^{N}_{s}(x))\right) q_\theta(x,dy), \eta^{N}_{s}(dx) \right\rangle ds\\
-\leq & C+ \frac{(2 \theta C_{\gamma,r}+C_{\gamma,r})\mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle]e^{(C_{\gamma,r}+C_F)t}}{N}.
-\end{aligned}
-\end{equation}
-
-As a result, we have that 
-\begin{equation}\label{eq: Total mass control supremum control}
-\begin{aligned}
-&\mathbb{E}[h(t)]:=\mathbb{E}\left[\sup_{s \in [0,t]}\langle 1 ,\eta^{N}_{s}\rangle\right] \\
-\leq &  \mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle] \\
-&+ \sup_{\tau \in [0,t]} \int_{0}^{\tau}\mathbb{E} \bigg\langle \gamma(\rho_{r}*\eta^{N}_{s}(x)) \left| \theta \int_{\mathbb{R}^n} \big\{r\big(\rho_{r}*\eta^{N}_{s}(y)\big)-r\big(\rho_{r}*\eta^{N}_{s}(x)\big)\big\}\rho_{1/\theta}(x-y)dy\right| + C_F ,\eta^{N}_{s}(dx)  \bigg\rangle dw\\
-&+ \mathbb{E}\{M^{*}_t(1)\}\\
-\leq &  \mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle] + (C_{\gamma,r} + C_F)\int_{0}^{t}\mathbb{E} \left[ \sup_{\tau \in [0,s]} \langle 1  ,\eta^{N}_{s} \rangle \right]ds+\mathbb{E}\{M^{*}_t(1)\}\\
-\leq &  \mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle] + (C_{\gamma,r} + C_F)\int_{0}^{t}\mathbb{E} \left[ h(s) \right]ds+\frac{(2 \theta C_{\gamma,r}+C_{\gamma,r})\mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle]e^{(C_{\gamma,r}+C_F)t}}{N}.
-\end{aligned}
-\end{equation}
-Once again, with Gronwall's inequality we have 
-\begin{equation}
-\mathbb{E}[h(t)] 
-\leq   \mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle]
-            \left(1+\frac{(2 \theta C_{\gamma,r}+C_{\gamma,r})e^{(C_{\gamma,r}+C_F)t}}{N}\right)e^{(C_{\gamma,r}+C_F)t}.  
-\end{equation}
+    We first take $f \equiv 1$ in Equation \eqref{eqn:eta_martingale},
+    so that
+    \begin{align} \label{eqn:mass_martingale_decomp}
+        \langle 1, \eta^N_t \rangle
+        &=
+        \langle 1, \eta^N_0 \rangle
+        + \int_0^t \int_{\IR^d} \left\{
+            B(x, \eta^N_s)
+            + F(x, \eta^N_s)
+            \right\} \eta^N_s(dx) ds
+        + M^N_t(1) ,
+    \end{align}
+    where $M^N_t(1)$ is a martingale and for the moment we are defining
+    \begin{equation*}
+        B(x, \eta) = \gamma(x, \eta) \int_{\IR^d} \theta (r(y, \eta) - r(x, \eta)) q_\theta(x, dy) .
+    \end{equation*}
+    By Lemma~\ref{lem:eta_compact_containment} and the assumption that $F$ is bounded above,
+    $B(x, \eta) + F(x, \eta) \le C$ for some $C$,
+    and so, taking expectations,
+    \begin{align*}
+        \IE\left[ \langle 1, \eta^N_t \rangle \right]
+        &\le
+        \IE\left[ \langle 1, \eta^N_0 \rangle \right]
+        + C \int_0^t \IE\left[ \langle 1, \eta^N_s \rangle \right] dt .
+    \end{align*}
+    Applying Grownwall's inequality, we have that
+    \begin{align*}
+        \IE\left[ \langle 1, \eta^N_t \rangle \right]
+        \le
+        \IE\left[ \langle 1, \eta^N_0 \rangle \right] e^{Ct} .
+    \end{align*}
+    Now, let $M^*_t(\phi) = \sup_{0 \le s \le t} M_t(\phi)$,
+    and as before $[M(\phi)]_t$ the quadratic variation of $M_t(\phi)$,
+    so that by the Burkholder-Davis-Gundy inequality, there is a $C'$ so that
+    \begin{align*}
+        \IE\left[ M^*_t(1) \right]
+        &\le
+        C' \IE\left[ \sqrt{[M^*(1)]_t} \right]
+        \\ &\le
+        C'\left( 1 + \IE\left[ [M^*(1)]_t \right] \right)
+        \\ &=
+        C'\left( 1 + \frac{\theta}{N} \IE\left[
+            \int_0^t
+            \int_{\IR^d} \left\{
+                \gamma(x, \eta^N_s)
+                \int_{\IR^d} r(y, \eta^N_s) q_\theta(x, dy)
+                + \mu(x, \eta^N_s)
+            \right\} \eta_s^N(dx)
+            dt
+            \right] \right)
+        \\ &=
+        C'\left( 1 + \IE\left[
+            \int_0^t
+            \int_{\IR^d} \left\{
+                \frac{2\theta}{N} \gamma(x, \eta^N_s) r(x, \eta^N_s)
+                + \frac{1}{N} B(x, \eta^N_s)
+            \right\} \eta_s^N(dx)
+            dt
+            \right] \right) .
+    \end{align*}
+    Since $\gamma(x, \eta) r(x, \eta)$ and $B(x, \eta)$ are bounded,
+    and $\theta/N \to \alpha < \infty$,
+    combining constants and again using Gronwall's inequality, we get that
+    \begin{align*}
+        \IE\left[ M^*_t(1) \right]
+        % &\le
+        % C'\left( 1 + \IE\left[
+        %     \int_0^t
+        %     \int_{\IR^d} \left\{ C'' \right\} \eta_s^N(dx)
+        %     dt
+        %     \right] \right) \\
+        &\le
+        C' + C'' \IE[ \langle 1, \eta_0^N \rangle ] e^{tC} .
+    \end{align*}
+    Taking suprema and expectations on both sides of equation~\eqref{eqn:mass_martingale_decomp},
+    then again using the fact that $B(x, \eta) + F(x, \eta) \le C$,
+    \begin{align*}
+        \IE\left[\sup_{0 \le s \le t} \langle 1, \eta^N_s \rangle \right]
+        &\le
+        \IE[\langle 1, \eta^N_0 \rangle]
+        + \IE\left[
+            \sup_{0 \le s \le t}
+            \int_0^t \int_{\IR^d} \left\{
+            B(x, \eta^N_s)
+            + F(x, \eta^N_s)
+            \right\} \eta^N_s(dx) ds
+        \right]
+        + \IE[M^*_t(1)] 
+        \\
+        &\le
+        \IE[\langle 1, \eta^N_0 \rangle]
+        + C \IE\left[
+            \int_0^t \sup_{0 \le s \le t} \langle 1, \eta^N_s \rangle ds
+        \right]
+        + C' + C'' \IE[ \langle 1, \eta_0^N \rangle ] e^{tC} .
+    \end{align*}
+    Once again applying Gronwall's inequality,
+    \begin{align*}
+        \IE\left[\sup_{0 \le s \le t} \langle 1, \eta^N_s \rangle \right]
+        &\le
+        C'' 
+        \left(\IE[\langle 1, \eta^N_0 \rangle] + C'\right)
+        \IE[ \langle 1, \eta_0^N \rangle ] e^{2tC} .
+    \end{align*}
+    For any $T$,
+    the inequality on the right is bounded above by a constant $C(T)$ independent of $N$.
+    As a result, for any $K > 0$,
+    \begin{equation*}
+    \limsup_{N \to \infty}
+        \IP\left[ \sup_{0 \le s \le T} \langle 1, \eta^{N}_{s} \rangle \geq K \right]
+        \leq
+        \frac{C(T)}{K}.
+    \end{equation*}
 \end{proof}
 
-Note that as $\theta/N \to \alpha$ and $N \to \infty$,
-the inequality on the right is bounded above by a constant $C(T)$
-independent of $\theta, N$.
-As a result 
-\begin{equation}
-\limsup_{N \to \infty}\mathbb{P}\left[\sup_{s \in [0,T]}\langle 1 ,\eta^{N}_{s}\rangle \geq K\right] \leq \frac{C(T)}{K}    
-\end{equation}
-for any $K > 0$, giving us compact containment condition.
-
-\subsubsection{Tightness of $(\langle f, \eta^{N}_t \rangle )_{t>0}$}
-\begin{theorem}[Tightness of $(\langle f, \eta^{N}_t \rangle )_{t>0}$]
-    \label{teo: Tightness of real-valued projections}
+Now that we have a compact containment condition for $\eta^N$,
+we need tightness of the one-dimensional distributions.
+
+\begin{lemma}[Tightness of $(\langle f, \eta^{N}_t \rangle )_{t>0}$]
+    \label{lem:eta_projections_tightness}
 For all $f \in C^{2}_{0}(\mathbb{R}^d)$, 
-the process
-$(\langle f, \eta^{N}_t \rangle)_{t \geq 0}$ is tight.
-\end{theorem}
+the collection of processes
+$(\langle f, \eta^{N}_t \rangle)_{t \geq 0}$
+for $N = 1, 2, \ldots$ is tight as a sequence of c\`adl\`ag, real-valued processes.
+\end{lemma}
+
 \begin{proof}
-We apply the Aldous-Rebolledo criterion \cite{rebolledo:1980}.
-It suffices to show that for all stopping time
-$\tau \in [0,T]$ and for each $\epsilon>0$, there exists $\delta>0$ and $\theta_0>0$ such that 
-\begin{equation}
-\begin{aligned}
-\sup_{\theta > \theta_0}
+As in the proof of Lemma~\ref{lem:gamma_bound},
+we use the semimartingale representation of $\langle f, \eta^N_t\rangle$
+from Definition~\ref{defn:mgale_construction},
+\begin{align*}
+    \langle f, \eta^{N}_{\tau+s}\rangle
+    -
+    \langle f, \eta^{N}_{\tau}\rangle
+    &=
+    M^N_{\tau + s}(f) - M^N_\tau(f)
+    +
+    \int_\tau^{\tau + s} 
+    \int_{\IR^d}
+    \left\{
+        B_f(x, \eta^N_s)
+        + f(x) F(x, \eta^N_s)
+    \right\} 
+    \eta^N_s(dx)
+    ds,
+\end{align*}
+where
+$$
+    B_f(x, \eta)
+    =
+    \gamma(x, \eta) \int_{\IR^d} \theta ( f(y) r(y, \eta) - f(x) r(x, \eta) ) q_\theta(x, dy) .
+$$
+% By Lemma~\ref{lem:gamma_bound} and the assumption that $F$ is bounded above,
+% $B_f(x, \eta) + f(x) F(x, \eta) \le C_f$ for some constant $C_f$.
+We apply the Aldous-Rebolledo criterion \citep{rebolledo:1980}, which says that
+it suffices to show that 
+$\{\langle f, \eta^N_t \rangle\}_{N \ge 1}$ is tight for each $t$, and that
+for any sequence of stopping times $\tau_N$ bounded by $T$,
+and for each $\epsilon > 0$, there exists $\delta > 0$ and $N_0 > 0$ such that 
+\begin{gather*}
+    \sup_{N > N_0}
     \sup_{s \in [0, \delta]}
-\mathbb{P}\left[\left| \langle f, \eta^{N}_{\tau+s}\rangle
-                        - \langle f, \eta^{N}_{\tau}\rangle
+    \IP\left[\left|
+            \int_\tau^{\tau + s} 
+            \int_{\IR^d}
+            \left\{
+                B_f(x, \eta^N_s)
+                + f(x) F(x, \eta^N_s)
+            \right\} 
+            \eta^N_s(dx)
+            ds
         \right|> \epsilon \right]
-                & < \epsilon;\\
-\sup_{\theta > \theta_0}
+        < \epsilon ,
+    \\ \text{and} \qquad
+    \sup_{N > N_0}
     \sup_{s \in [0, \delta]}
-\mathbb{P}\left[\big| [M^{\theta}_{\tau+s}(f)] 
-                        - [M^{\theta}_{\tau}(f)] \big|
-                        > \epsilon\right]
-                & < \epsilon.
-\end{aligned}    
-\end{equation}
-Note that
-\begin{equation}
-\begin{aligned}
- & \mathbb{E}\left[\left| \langle f, \eta^{N}_{\tau+s}\rangle - \langle f, \eta^{N}_{\tau}\rangle \right|\right] \\
-\leq & \mathbb{E}\Bigg[\bigg| \int_{\tau}^{\tau+s}\bigg\langle \theta\gamma(\rho_{r}*\eta^{N}_{s}(x)) \int_{\mathbb{R}^n} \big\{f(y)r(\rho_{r}*\eta^{N}_{s}(y))-f(x)r(\rho_{r}*\eta^{N}_{s}(x))\big\}\rho_{1/\theta}(x-y)dy \\
-& \qquad + F(\rho_{F}*\eta^{N}_{s}(x)) f(x),\eta^{N}_{s}(dx)  \bigg\rangle ds \bigg|\Bigg].
-\end{aligned}
-\end{equation}
+    \IP\left[\big| [M^{N}(f)]_{\tau+s} 
+                            - [M^{N}(f)]_\tau \big|
+                            > \epsilon \right]
+                    < \epsilon.
+\end{gather*}
+Tightness of $\langle f, \eta^N_t\rangle$ for fixed $t$
+follows from Lemma~\ref{lem:eta_f_bound} and Markov's inequality,
+so we focus on the remaining conditions.
+
+\comment{The following is NOT RIGHT because $F$ is not bounded below!}
+
 In particular,
@@
 is compact in $\mathcal{M}_F(\overline{\mathbb{R}^d})$.
-Therefore, by Lemma \ref{lem: Compact Containment},
+Therefore, by Lemma \ref{lem:eta_compact_containment},
 our processes satisfy the compact containment condition.
@@
 which is proven in
-Theorem \ref{teo: Tightness of real-valued projections}.
+Theorem \ref{lem:eta_projections_tightness}.
 \end{proof}
@@
 %{\bf Proof}
+
 \begin{proof}
+    \comment{Check where we use compactness of the mollifier.}
 
@@
     with a level lower than some $u_{*}$. Since a control on total mass has
-    already been shown in Lemma \ref{lem: Compact Containment}, we have
+    already been shown in Lemma \ref{lem:eta_compact_containment}, we have
     immediately established compact containment condition for our lookdown
@@
 \textbf{Controlling high density events:}
-Recall that in Lemma \ref{lem: Compact Containment}, we have established compact containment for the total mass process. Therefore for any $\epsilon>0$ and $r>0$, there exists some large 
+Recall that in Lemma \ref{lem:eta_compact_containment}, we have established compact containment for the total mass process. Therefore for any $\epsilon>0$ and $r>0$, there exists some large 
 \begin{equation}
@@
 \end{equation}
-where $(C(t))_{t \geq 0}$ is the growth function that bounds the expected value of the running supremum of the total mass in Equation \eqref{eq: Growth function bound on running sup}.
+where $(C(t))_{t \geq 0}$ is the growth function that bounds the expected value of the running supremum of the total mass in Equation \eqref{eqn:eta_mass_bound}.
 
@@
 First of all, we will show that compact containment condition is satisfied if we can control the total mass of particles in our system living in a finite region in space with a level lower than some $u_{*}$.
-Since a control on total mass has already been shown in Lemma \ref{lem: Compact Containment}, we have immediately established compact containment condition for our lookdown processes.
+Since a control on total mass has already been shown in Lemma \ref{lem:eta_compact_containment}, we have immediately established compact containment condition for our lookdown processes.
 
@@
 \begin{lemma}[Compact Containment]
-    \label{lem: Compact Containment}
+    \label{lem:lp_compact_containment}
 Assume that $\xi^{N}_0 \to \xi_0$ weakly,
@@
     \begin{align}
-        \label{eq: Growth function bound on running sup, lookdown}
+        \label{eqn:lp_mass_bound}
         \IE\left[
@@
 i.e. the spatial projection of $(\xi^{N}_t)_{t \geq 0}$ has the same distribution as $(\eta^N_t)_{t \geq 0}$ defined in Definition \ref{defn:mgale_construction}. 
-As a result, by Lemma \ref{lem: Compact Containment},
+As a result, by Lemma \ref{lem:lp_compact_containment},
 we have immediately that 
@@
 conditional on $\eta^N_t$,
-$M_{\varepsilon}/N$ proportion of particles in $\xi^N_t$ have levels in $[0,M_{\varepsilon}]$. The final inequality holds as a direct consequence of \ref{lem: Compact Containment}.
+$M_{\varepsilon}/N$ proportion of particles in $\xi^N_t$ have levels in $[0,M_{\varepsilon}]$. The final inequality holds as a direct consequence of \ref{lem:eta_compact_containment}.
 

### 2022-08-04 forwards-and-backwards.tex
more proofs

@@
 with uniformly bounded first and second derivatives in $m$,
+that $\sup_x F(x,m)$ is finite for all $m$,
 and define
@@
         \IE[\langle f, \eta^N_0 \rangle]
-        e^{Ct}
+        e^{C_f t}
     $$
@@
 \begin{proof}
-    \comment{TODO: copy over from below}
+    Consider the semimartingale decomposition of Equation \eqref{eqn:eta_martingale},
+    \begin{align} \label{eqn:eta_f_mgale_decomp}
+        \langle f, \eta^N_t \rangle
+        &=
+        \langle f, \eta^N_0 \rangle
+        + \int_0^t \int_{\IR^d} \left\{
+            \gamma(x, \eta^N_s) B_f(x, \eta^N_s)
+            + f(x) F(x, \eta^N_s)
+            \right\} \eta^N_s(dx) ds
+        + M^N_t(f) ,
+    \end{align}
+    where $M^N_t(f)$ is a martingale and for the moment we are defining
+    \begin{equation*}
+        B_f(x, \eta) = \int_{\IR^d} \theta (f(y) r(y, \eta) - f(x) r(x, \eta)) q_\theta(x, dy) .
+    \end{equation*}
+    By Lemma~\ref{lem:eta_compact_containment} and the assumption that $F$ is bounded above,
+    $\gamma(x, \eta) B_f(x, \eta) + f(x) F(x, \eta) \le C_f$ for some $C_f$,
+    and so, taking expectations,
+    \begin{align*}
+        \IE\left[ \langle f, \eta^N_t \rangle \right]
+        &\le
+        \IE\left[ \langle f, \eta^N_0 \rangle \right]
+        + C_f \int_0^t \IE\left[ \langle f, \eta^N_s \rangle \right] dt .
+    \end{align*}
+    The bound then follows from Grownwall's inequality.
 \end{proof}
@@
     \limsup_{N \to \infty}
-        \mathbb{P}\left[\sup_{s \in [0,T]}
+        \IP \left\{ \sup_{s \in [0,T]}
             \langle 1 ,\eta^{N}_{s}\rangle
-            > K_\epsilon \right]
-            \leq \frac{C_T}{K_{\epsilon}} < \epsilon.    
+            > K_\epsilon \right\}
+        \leq \frac{C_T}{K_{\epsilon}}
+        < \epsilon .
     \end{equation}
@@
 \begin{proof}
-    We first take $f \equiv 1$ in Equation \eqref{eqn:eta_martingale},
-    so that
-    \begin{align} \label{eqn:mass_martingale_decomp}
-        \langle 1, \eta^N_t \rangle
-        &=
-        \langle 1, \eta^N_0 \rangle
-        + \int_0^t \int_{\IR^d} \left\{
-            B(x, \eta^N_s)
-            + F(x, \eta^N_s)
-            \right\} \eta^N_s(dx) ds
-        + M^N_t(1) ,
-    \end{align}
-    where $M^N_t(1)$ is a martingale and for the moment we are defining
-    \begin{equation*}
-        B(x, \eta) = \gamma(x, \eta) \int_{\IR^d} \theta (r(y, \eta) - r(x, \eta)) q_\theta(x, dy) .
-    \end{equation*}
-    By Lemma~\ref{lem:eta_compact_containment} and the assumption that $F$ is bounded above,
-    $B(x, \eta) + F(x, \eta) \le C$ for some $C$,
-    and so, taking expectations,
-    \begin{align*}
-        \IE\left[ \langle 1, \eta^N_t \rangle \right]
-        &\le
-        \IE\left[ \langle 1, \eta^N_0 \rangle \right]
-        + C \int_0^t \IE\left[ \langle 1, \eta^N_s \rangle \right] dt .
-    \end{align*}
-    Applying Grownwall's inequality, we have that
-    \begin{align*}
-        \IE\left[ \langle 1, \eta^N_t \rangle \right]
-        \le
-        \IE\left[ \langle 1, \eta^N_0 \rangle \right] e^{Ct} .
-    \end{align*}
-    Now, let $M^*_t(\phi) = \sup_{0 \le s \le t} M_t(\phi)$,
-    and as before $[M(\phi)]_t$ the quadratic variation of $M_t(\phi)$,
+    First note that by Lemma~\ref{lem:eta_f_bound},
+    $\IE[\langle 1, \eta^N_t \rangle] \le \IE[\langle 1, \eta^N_0 \rangle] e^{Ct}$
+    for some $C$.
+    Now, let $M^*_t(f) = \sup_{0 \le s \le t} M_t(f)$,
+    and as before $[M(f)]_t$ the quadratic variation of $M_t(f)$,
     so that by the Burkholder-Davis-Gundy inequality, there is a $C'$ so that
@@
     \end{align*}
-    Taking suprema and expectations on both sides of equation~\eqref{eqn:mass_martingale_decomp},
-    then again using the fact that $B(x, \eta) + F(x, \eta) \le C$,
+    Taking suprema and expectations on both sides of equation~\eqref{eqn:eta_f_mgale_decomp},
+    then again using the fact that $\gamma(x, \eta) B(x, \eta) + F(x, \eta) \le C$,
     \begin{align*}
@@
             \int_0^t \int_{\IR^d} \left\{
+                \gamma(x, \eta^N_s)
                 B(x, \eta^N_s)
@@
 
+\begin{lemma}
+    \label{lem:tightness_for_F}
+    Fix a $\sigma > 0$ and a continuous function $f \in C(\IR^d, [0, \infty))$
+    such that $\sup_x f(x, m)$ is finite for each $m$.
+    Under the assumptions of Definition~\ref{def:model_setup},
+    and if $\eta^N_0$ converges in distribution,
+    for all $\epsilon > 0$ and $T \ge 0$
+    there exists a $K_f$ such that for all $N > 0$,
+    \begin{align*}
+        \IP\left\{
+            \sup_{0 \le s \le T}
+            \int_{\IR^d}
+            f(x, p_{\sigma^2}*\eta^N_s(x))
+            \eta^N_s(dx)
+            > K_f
+        \right\}
+        \le \epsilon ,
+    \end{align*}
+    where recall that $p_{\sigma^2}*\eta(\cdot)$ denotes convolution of the Gaussian kernel
+    with mean 0 and variance $\sigma^2 I$ with the measure $\eta$.
+\end{lemma}
+
+\begin{proof}[of Lemma~\ref{lem:tightness_for_F}]
+    Let $\bar f(m) = \sup_x \sup_{k \le m} f(x, k)$, which is finite by assumption.
+    Since $p_{\sigma^2}*\eta(x) \le \langle 1, \eta \rangle / (2 \pi \sigma^2)^{d/2}$,
+    we have that
+    $$
+        \sup_{0 \le s \le T} \sup_{x \in \IR^d} f(x, p_{\sigma^2}*\eta^N_s(x))
+        \le
+        \bar f( \sup_{0 \le s \le T} \langle 1, \eta^N_s \rangle  / (2 \pi \sigma^2)^{d/2} ) .
+    $$
+    This implies that if $0 \le s \le T$ then
+    $$
+            \int_{\IR^d} f(x, p_{\sigma^2}*\eta^N_s(x)) \eta^N_s(dx)
+            \le
+            \bar f(\sup_{0 \le s \le T} \langle 1, \eta^N_s \rangle)
+            \sup_{0 \le s \le T} \langle 1, \eta^N_s \rangle .
+    $$
+    Now, if we let $g(m) = m \bar f(m/ (2 \pi \sigma^2)^{d/2})$,
+    which again is finite and nondecreasing,
+    then the lemma follows by choosing $K_f = g^{-1}(K_\epsilon)$
+    in Lemma~\ref{lem:eta_compact_containment}.
+\end{proof}
+
 Now that we have a compact containment condition for $\eta^N$,
@@
 \begin{proof}
-As in the proof of Lemma~\ref{lem:gamma_bound},
-we use the semimartingale representation of $\langle f, \eta^N_t\rangle$
-from Definition~\ref{defn:mgale_construction},
-\begin{align*}
-    \langle f, \eta^{N}_{\tau+s}\rangle
-    -
-    \langle f, \eta^{N}_{\tau}\rangle
-    &=
-    M^N_{\tau + s}(f) - M^N_\tau(f)
-    +
-    \int_\tau^{\tau + s} 
-    \int_{\IR^d}
-    \left\{
-        B_f(x, \eta^N_s)
-        + f(x) F(x, \eta^N_s)
-    \right\} 
-    \eta^N_s(dx)
-    ds,
-\end{align*}
-where
-$$
-    B_f(x, \eta)
-    =
-    \gamma(x, \eta) \int_{\IR^d} \theta ( f(y) r(y, \eta) - f(x) r(x, \eta) ) q_\theta(x, dy) .
-$$
-% By Lemma~\ref{lem:gamma_bound} and the assumption that $F$ is bounded above,
-% $B_f(x, \eta) + f(x) F(x, \eta) \le C_f$ for some constant $C_f$.
-We apply the Aldous-Rebolledo criterion \citep{rebolledo:1980}, which says that
-it suffices to show that 
+We apply the Aldous-Rebolledo criterion \citep{rebolledo:1980}, which 
+applied to the semimartingale representation of $\langle f, \eta^N_t\rangle$
+of equation~\eqref{eqn:eta_f_mgale_decomp},
+says that it suffices to show that 
 $\{\langle f, \eta^N_t \rangle\}_{N \ge 1}$ is tight for each $t$, and that
@@
 and for each $\epsilon > 0$, there exists $\delta > 0$ and $N_0 > 0$ such that 
-\begin{gather*}
+\begin{gather}
+        \label{eqn:eta_projections_goal1}
     \sup_{N > N_0}
-    \sup_{s \in [0, \delta]}
-    \IP\left[\left|
-            \int_\tau^{\tau + s} 
+    \sup_{t \in [0, \delta]}
+    \IP\left\{\left|
+            \int_\tau^{\tau + t}
             \int_{\IR^d}
             \left\{
-                B_f(x, \eta^N_s)
+                \gamma(x, \eta^N_s) B_f(x, \eta^N_s)
                 + f(x) F(x, \eta^N_s)
@@
             ds
-        \right|> \epsilon \right]
+        \right|> \epsilon \right\}
         < \epsilon ,
     \\ \text{and} \qquad
+        \label{eqn:eta_projections_goal2}
     \sup_{N > N_0}
-    \sup_{s \in [0, \delta]}
-    \IP\left[\big| [M^{N}(f)]_{\tau+s} 
+    \sup_{t \in [0, \delta]}
+    \IP\left\{\big|
+        [M^{N}(f)]_{\tau + t} 
             - [M^{N}(f)]_\tau \big|
-                            > \epsilon \right]
+        > \epsilon
+    \right\}
     < \epsilon.
-\end{gather*}
+\end{gather}
 Tightness of $\langle f, \eta^N_t\rangle$ for fixed $t$
@@
 
-\comment{The following is NOT RIGHT because $F$ is not bounded below!}
-
-In particular,
-\begin{multline}
- \theta\gamma(\rho_{r}*\eta^{N}_{s}(x))\int_{\mathbb{R}^n} \big\{f(y)r(\rho_{r}*\eta^{N}_{s}(y))-f(x)r(\rho_{r}*\eta^{N}_{s}(x))\big\}\rho_{1/\theta}(x-y)dy \\
- =  f(x)\theta\gamma(\rho_{r}*\eta^{N}_{s}(x))\int_{\mathbb{R}^n} \big\{r(\rho_{r}*\eta^{N}_{s}(y))-r(\rho_{r}*\eta^{N}_{s}(x))\big\}\rho_{1/\theta}(x-y)dy\\
- + \theta\gamma(\rho_{r}*\eta^{N}_{s}(x))\int_{\mathbb{R}^n} \big\{(f(y)-f(x))r(\rho_{r}*\eta^{N}_{s}(y))\big\}\rho_{1/\theta}(x-y)dy\\
- \leq C_{\gamma,r}||f||_{\infty} + C_{\gamma}||\Delta f||_{\infty},
-\end{multline}
-since the first term is bounded above by $C_{\gamma,r}f(x)$ by Lemma \ref{cor:gamma_bound}
-and the second term by $C_{\gamma} \Delta f(x)$ as $r \leq 1$.
-
-Finally,  $F(\rho_{F}*\eta^{N}_{s}(x)) f(x)$ is bounded above by $C_F||f||_{\infty}$, so 
-\begin{multline}
-\mathbb{E}\left[\left|
-                        \langle f, \eta^{N}_{\tau+s}\rangle - \langle f, \eta^{N}_{\tau}\rangle
-                \right|\right] \\
-\leq (C_{\gamma,r}||f||_{\infty}
-        + C_{\gamma,r}||\Delta f||_{\infty}
-            +C_F||f||_{\infty})
-    \mathbb{E}\bigg\{
-                        \int_{\tau}^{\tau+s}
-                        \bigg\langle 1,\eta^{N}_{s}(dx)  \bigg\rangle 
+Next, note that for $0 \le t \le \delta$,
+if we choose $K_f$ as in Lemma~\ref{lem:tightness_for_F}
+and $C_f$ as in Lemma~\ref{lem:gamma_bound},
+then
+\begin{align*}
+    &
+    \IP\left\{
+        \int_\tau^{\tau + t}
+        \int_{\IR^d}
+        \left\{
+            \gamma(x, \eta^N_s) B_f(x, \eta^N_s)
+            + f(x) F(x, \eta^N_s)
+        \right\} 
+        \eta^N_s(dx)
         ds
-                \bigg\} \\
-\leq (C_{\gamma,r}||f||_{\infty}
-            + C_{\gamma,r}||\Delta f||_{\infty}
-                    +C_F||f||_{\infty})
-                \mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle]
-                        e^{(C_{\gamma,r}+C_F)T}(e^\delta-1).
-\end{multline}
-As $\eta^{N}_0$ converges weakly,
-we have that 
-$\sup_{\theta > \theta_0}\mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle] < K$
-for some $K>0$.
-Applying Markov's Inequality,
-we can pick small enough $\delta > 0$ such that 
-\begin{equation}
-\begin{aligned}
-\sup_{\theta > \theta_0}
-\sup_{s \in [0, \delta]}
-\mathbb{P}\left[\left| \langle f, \eta^{N}_{\tau+s}\rangle
-                        - \langle f, \eta^{N}_{\tau}\rangle
-                \right|> \epsilon \right]
-& \leq \sup_{\theta > \theta_0}
-\sup_{s \in [0, \delta]}
-\frac{
-\mathbb{E}\left[\left| \langle f, \eta^{N}_{\tau+s}\rangle
-                        - \langle f, \eta^{N}_{\tau}\rangle
-                \right| \right]
-        }{\epsilon}\\
-& < \frac{(C_{\gamma,r}||f||_{\infty}
-            + C_{\gamma,r}||\Delta f||_{\infty}
-                    +C_F||f||_{\infty})
-                Ke^{(C_{\gamma,r}+C_F)T}(e^\delta-1)
-         }{\epsilon}\\
-& < \epsilon.
-\end{aligned}    
-\end{equation}
-Similarly, the control on the second moment is given by Equation \eqref{eq: Control quadratic variation}.
-\begin{equation}
-    \label{eq: Controlling Quadratic Jumps}
-\begin{aligned}
-& \sup_{\theta > \theta_0}
-\sup_{s \in [0, \delta]}\mathbb{E}\left[\big| [M^{\theta}_{\tau+s}(f)] - [M^{\theta}_{\tau}(f)] \big|\right]\\
-\leq &\frac{\theta}{N} \mathbb{E} \Bigg\{ \int_{\tau}^{\tau+s}\bigg|
-\langle \gamma\big(x,\rho_{\gamma}*\eta^{N}_{s}(x)\big)
-\int f^2(y)r\big(y,\rho_{r}*\eta^{N}_{s}(y)\big)q_\theta(x,dy) 
-,\eta^{N}_{s}(dx)\rangle\\
-& \qquad \qquad \qquad +\langle \mu\big(x,\eta^{N}_{s}\big)f^2(x) 
-,\eta^{N}_{s}(dx)\rangle \bigg|ds \Bigg\}\\
-\leq & \frac{2\theta}{N}\mathbb{E} \Bigg\{\int_{\tau}^{\tau+s} \left\langle \gamma(\rho_{\gamma}*\eta^{N}_{s}(x))r(\rho_{r}*\eta^{N}_{s}(x)), \eta^{N}_{s}(dx) \right\rangle ds\Bigg\} \\
-& + \frac{1}{N}\mathbb{E} \Bigg\{\int_{\tau}^{\tau+s} \left\langle \gamma (\rho_{\gamma}*\eta^{N}_{s}(x))\theta\int_{\mathbb{R}^n}\left(r(\rho_{r}*\eta^{N}_{s}(y))-r(\rho_{r}*\eta^{N}_{s}(x))\right) q_\theta(x,dy), \eta^{N}_{s}(dx) \right\rangle ds\Bigg\}\\
-\leq & \frac{(2 \theta C_{\gamma,r}+C_{\gamma,r})\mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle]e^{(C_{\gamma,r}+C_F)T}(e^\delta-1)}{N}.
-\end{aligned}
-\end{equation}
-As $N^{-1}\theta \to \alpha$ as $N \to \infty$,
-there exists some $K'>0$ such that 
-$\sup_{\theta > \theta_0} N^{-1}\theta < K'$.
-An application of Markov's inequality proves that
-for small enough $\delta > 0,$
-\begin{equation}
-\begin{aligned}
-\sup_{\theta > \theta_0}
-\sup_{s \in [0, \delta]}
-\mathbb{P}\left[\big| [M^{\theta}_{\tau+s}(f)] 
-                        - [M^{\theta}_{\tau}(f)] \big|
-                        > \epsilon\right]
-&\leq  \sup_{\theta > \theta_0}
-\sup_{s \in [0, \delta]}
-\mathbb{E}\left[\big| [M^{\theta}_{\tau+s}(f)] 
-                        - [M^{\theta}_{\tau}(f)] \big|
-                        \right]/\epsilon \\
-&< K'e^{(C_{\gamma,r}+C_F)T}(e^\delta-1)/\epsilon < \epsilon.
-\end{aligned}    
-\end{equation}
+        > (K_f + C_f) \delta
+    \right\}
+    \\ & \qquad \le
+    \IP\left\{
+        \sup_{0 \le s \le \delta}
+        \int_{\IR^d} \left\{
+            \gamma(x, \eta^N_s) B_f(x, \eta^N_s)
+            + f(x) F(x, \eta^N_s)
+        \right\} \eta^N_s(dx)
+        >
+        K_f + C_f
+    \right\}
+    < \epsilon .
+\end{align*}
+Therefore, setting $\delta = \epsilon / (K_f + C_f)$
+obtains \eqref{eqn:eta_projections_goal1}.
+
+Similarly,
+\begin{align*}
+    &
+    [M^{N}(f)]_{\tau + t} 
+        - [M^{N}(f)]_\tau \big|
+    \\ & \qquad =
+    \int_{\tau}^{\tau + t}
+        \frac{\theta}{N}
+        \int_{\IR^d}
+        \left\{
+            \gamma(x, \eta^N_s)
+            \int_{\IR^d} f^2(y) r(y, \eta^N_s) q_\theta(x, dy)
+            +
+            \mu(x, \eta^N_s) f^2(x)
+        \right\}
+        \eta^N_s(dx)
+    ds .
+    \\ & \qquad =
+    \int_{\tau}^{\tau + t}
+        \frac{\theta}{N}
+        \int_{\IR^d}
+        \left\{
+            \gamma(x, \eta^N_s)
+            \left(
+                2 f^2(x) r(x, \eta^N_s)
+                +
+                B_{f^2}(x, \eta^N_s)
+            \right)
+            +
+            f^2(x) F(x, \eta^N_s) / \theta
+        \right\}
+        \eta^N_s(dx)
+    ds ,
+\end{align*}
+and so using the fact that $\theta/N \to \alpha < \infty$,
+an argument similar to 
+that for \eqref{eqn:eta_projections_goal1}.
+also obtains \eqref{eqn:eta_projections_goal2}.
+
 \end{proof}
 
-\subsubsection{Tightness of $(\eta^{N}_t)_{t \geq 0}$}
-\begin{theorem}
+% % % % % % % % %
+\begin{theorem}[Tightness of $(\eta^{N}_t)_{t \geq 0}$]
 The collection of measure-valued processes 

### 2022-08-04 forwards-and-backwards.tex
tightness

@@
     The collection of measure-valued processes 
-$\{(\eta^{N}_t)_{t \geq 0}: \theta > 0\}$
-is tight in $\mathcal{D}_{[0,\infty)}(\mathcal{M}_F(\overline{\mathbb{R}^d}))$.
+    $\{(\eta^{N}_t)_{t \geq 0}: N > 0\}$
+    is tight in $\mathcal{D}_{[0,\infty)}(\measures)$.
 \end{theorem}
+
 \begin{proof}
-To prove relative compactness 
-of the processes $(\eta^{N}_t)_{t \geq 0}$,
-we apply Theorem 3.9.1. in \cite{EK}.
-
-First of all, the set of measures 
-$\{ \mu: \langle 1, \mu \rangle \leq K \} $
-is compact in $\mathcal{M}_F(\overline{\mathbb{R}^d})$.
-Therefore, by Lemma \ref{lem:eta_compact_containment},
-our processes satisfy the compact containment condition.
-
-Secondly, the set of functions $\mathcal{C}^{2}_{0}(\overline{\mathbb{R}^d})$ is a dense subset of all continuous functions on $\mathcal{M}_f(\overline{\mathbb{R}^d})$
+    Theorem 3.9.1~in \cite{EK},
+    says that if the collection of $E$-valued processes
+    satisfies a compact containment condition
+    (for any $\epsilon > 0$ and $T>0$, there is a compact set
+    such that the processes stay within that set up to time $T$ with probability at least $1-\epsilon$),
+    then the collection is relatively compact
+    if and only if
+    $\{(f(\eta^{N}_t))_{t \geq 0}: N > 0\}$ is relatively compact
+    for all $f$ in a dense subset of $C_0(E)$
     under the topology of uniform convergence in compact sets.
 
-Furthermore,
-since each measure $\eta^{N}_t$ is concentrated in $\mathbb{R}^d$,
-it suffices to show that the real-valued processes
-$\langle f, \eta^{N}_t \rangle$
-is tight for all $f \in \mathcal{C}^{2}_{0}(\mathbb{R}^d)$,
-which is proven in
-Theorem \ref{lem:eta_projections_tightness}.
+    First of all,
+    the set of measures $\{ \mu: \langle 1, \mu \rangle \leq K \} $ is compact in $\cmeasures$,
+    so Lemma \ref{lem:eta_compact_containment}
+    shows that our processes satisfy a compact containment condition.
+    Secondly, Lemma \ref{lem:eta_projections_tightness}
+    shows that the real-valued processes $\langle f, \eta^{N}_t \rangle$
+    are relatively compact for all $f \in \mathcal{C}^{2}_{0}(\overline{\IR^d})$.
+    Since the set of finite sums and products of terms of this form
+    is dense in the space of bounded continuous functions on $\cmeasures$,
+    we have relative compactness in $\mathcal{D}_{[0,\infty)}(\cmeasures)$.
+    Finally,
+    since each measure $\eta^{N}_t$ is concentrated in $\IR^d$,
+    any limit point must in fact be in $\measures$,
+    and so we have 
+    tightness in $\mathcal{D}_{[0,\infty)}(\measures)$.
 \end{proof}

### 2022-08-08 forwards-and-backwards.tex
.

@@
     are relatively compact for all $f \in \mathcal{C}^{2}_{0}(\overline{\IR^d})$.
-    Since the set of finite sums and products of terms of this form
+    Since by the Stone-Weierstrass theorem,
+    the algebra of finite sums and products of terms of this form
     is dense in the space of bounded continuous functions on $\cmeasures$,
@@
     \label{lem:limit_mgale}
-    \comment{
-        Here we need to check that the martingale property is preserved in the limit.
-        But this maybe can be shorter?}
+    \comment{Here we need to check that the martingale property is preserved in the limit.}
 As $N \to \infty$,

### 2022-09-01 forwards-and-backwards.tex
.

@@
 We start with a population of
-$\bigO(N)$ individuals per unit area distributed in $\mathbb{R}^d$.
+$\bigO(N)$ individuals per unit area distributed in $\IR^d$.
 For applications, $d=1$ or $d=2$, but our results apply more generally.
@@
 with initial condition $\eta^N_0 \in \measures$,
-such that for all smooth functions $f \in C^{\infty}_{0}(\mathbb{R}^d)$,
+such that for all smooth functions $f \in C^{\infty}_{0}(\IR^d)$,
 writing $\langle f, \eta \rangle = \int_{\IR^d} f(x) \eta(dx)$
@@
 of Definition~\ref{defn:mgale_construction}
-acting on test functions of the form $F( \langle f, \eta \rangle )$,
+acting on test functions of the form $G( \langle f, \eta \rangle )$,
 where $f \geq 0$ is smooth and compactly supported on $\IR^d$ and 
-$F \in C^\infty ([0,\infty))$.
+$G \in C^\infty ([0,\infty))$.
 Recall that $\theta \to \infty$ along with $N$,
@@
     \Pgen^N
-    F(\langle f,\eta \rangle)
+    G(\langle f,\eta \rangle)
     =
-    F'(\langle f, \eta \rangle)
+    G'(\langle f, \eta \rangle)
     \lim_{\delta t\downarrow 0} \frac{1}{\delta t}
@@
     + \frac{1}{2}
-        F''(\langle f,\eta\rangle)
+        G''(\langle f,\eta\rangle)
     \lim_{\delta t\downarrow 0}\frac{1}{\delta t}
@@
     +
-    \epsilon_N(f, F, \eta),
+    \epsilon_N(f, G, \eta),
 \end{multline*}
 where the terms that make up 
-$\epsilon_N(f, F, \eta)$
+$\epsilon_N(f, G, \eta)$
 will be negligible in our scaling limit.
@@
 \begin{align*}
-& F''(\langle f,\eta\rangle)
+& G''(\langle f,\eta\rangle)
 \frac{1}{2} N \theta
@@
 &\qquad
-= \frac{1}{2} F''(\langle f, \eta \rangle)
+= \frac{1}{2} G''(\langle f, \eta \rangle)
     \frac{\theta}{N}
@@
 \begin{align*}
-\frac{\alpha}{2} F''(\langle f, \eta \rangle)
+\frac{\alpha}{2} G''(\langle f, \eta \rangle)
     \langle
@@
 
-Finally, the term $\epsilon_{\theta,N}(f, F, \eta)$ will be 
+Finally, the term $\epsilon_{\theta,N}(f, G, \eta)$ will be 
 $\bigO(\theta/N^2)$.
@@
 For given positive values of $N$ and $\theta$
-and $\lp_0 \in \mathcal{M}_F(\mathbb{R}^d \times [0,N])$,
+and $\lp_0 \in \mathcal{M}_F(\IR^d \times [0,N])$,
 we define $(\lp^{N}_t)_{t \geq 0}$
@@
             \frac{
-                \theta \int_{\mathbb{R}^d}
+                \theta \int_{\IR^d}
                 (g(y,u) - g(x,u))
@@
         \frac{\theta}{N} \int_u^N
-        \int_{\mathbb{R}^d}\left(
+        \int_{\IR^d}\left(
             \frac{ g(y,u_1) + g(x,u_1) }{ 2 } - 1
@@
 \end{equation*}
-for all smooth functions $g \in C^{2}_{0}(\mathbb{R}^d)$,
+for all smooth functions $g \in C^{2}_{0}(\IR^d)$,
 where $f(\lp) = \prod_{(x, u) \in \lp} g(x, u)$ as defined in \eqref{eqn:test_functions},
@@
 assigning each particle an i.i.d. uniform $[0,N]$-level,
-and for any $\lp \in \mathcal{M}_f(\mathbb{R}^d \times [0,\infty))$, we denote
+and for any $\lp \in \mathcal{M}_f(\IR^d \times [0,\infty))$, we denote
 $$\hat{f}(\lp)=\int f(\lp) \Gamma (d\textbf{u})$$ 
@@
 
-Finally, we write $S(\tau_{[a]_k},t):=[\tau_{[a]_k},t]\times[0,\infty)\times\mathbb{R}^d \times \{0,1\}$.
+Finally, we write $S(\tau_{[a]_k},t):=[\tau_{[a]_k},t]\times[0,\infty)\times\IR^d \times \{0,1\}$.
 Under this notation, for $t>\tau_{[a]_k}$,
@@
         \label{eqn:first_moment_rho}
-        \left|\theta \int_{\mathbb{R}^d}
+        \left|\theta \int_{\IR^d}
             ( \smooth{r} \eta(y)-\smooth{r} \eta(x) )
@@
         \label{eqn:second_moment_rho}
-        \theta \int_{\mathbb{R}^d}
+        \theta \int_{\IR^d}
                 \left( \smooth{r} \eta(y) - \smooth{r} \eta(x) \right)^2
@@
         &
-        \theta \int_{\mathbb{R}^d}
+        \theta \int_{\IR^d}
                 \left( \smooth{r} \eta(y) - \smooth{r} \eta(x) \right)^2
@@
     \end{equation*}
-    By Lemma~\ref{lem:eta_compact_containment} and the assumption that $F$ is bounded above,
+    By Lemma~\ref{lem:gamma_bound} and the assumption that $F$ is bounded above,
     $\gamma(x, \eta) B_f(x, \eta) + f(x) F(x, \eta) \le C_f$ for some $C_f$,
@@
     Taking suprema and expectations on both sides of equation~\eqref{eqn:eta_f_mgale_decomp},
-    then again using the fact that $\gamma(x, \eta) B(x, \eta) + F(x, \eta) \le C$,
+    then again using the fact that $\gamma(x, \eta) B_f(x, \eta) + F(x, \eta) \le C$,
     \begin{align*}
@@
                 \gamma(x, \eta^N_s)
-                B(x, \eta^N_s)
+                B_f(x, \eta^N_s)
                 + F(x, \eta^N_s)
@@
     \label{lem:eta_projections_tightness}
-For all $f \in C^{2}_{0}(\mathbb{R}^d)$, 
+For all $f \in C^{2}_{0}(\IR^d)$, 
 the collection of processes
@@
     \label{def: MP definition of limit}
-Let $F \in \mathcal{C}^{2}(\mathbb{R})$ and $f \in \mathcal{C}_{0}(\mathbb{R}^d)$.
+Let $F \in \mathcal{C}^{2}(\IR)$ and $f \in \mathcal{C}_{0}(\IR^d)$.
 We define $\Pgen$ to be a generator
@@
 We define $(\eta^{\infty}(t))_{t \geq 0}$ to be the solution to the Martingale Problem $(\Pgen^{\infty}, \eta_0)$, i.e. 
-for all $F \in \mathcal{C}^{2}(\mathbb{R})$
-and $f \in \mathcal{C}_{0}(\mathbb{R}^d)$,
+for all $F \in \mathcal{C}^{2}(\IR)$
+and $f \in \mathcal{C}_{0}(\IR^d)$,
 $$M_t:=F_f(\eta^{\infty}_t)-F_f(\eta_0)
@@
     \label{def: MP definition of pre-limit}
-Let $F \in \mathcal{C}^{2}(\mathbb{R})$ and $f \in \mathcal{C}_{0}(\mathbb{R}^d)$.
+Let $F \in \mathcal{C}^{2}(\IR)$ and $f \in \mathcal{C}_{0}(\IR^d)$.
 We define $\Pgen^N$ to be a generator
@@
 \begin{aligned}
-\Pgen^{N} F_f(\eta):=& \int_{\mathbb{R}^d} \theta\gamma(x, \eta) \left\{\int_{\mathbb{R}^d} \left\{F(\langle f, \eta \rangle + f(y)/N )-F(\langle f, \eta \rangle )\right\}r(y, \eta)q_{\theta}(x,dy)\right\}N\eta(dx)\\
-&+\int_{\mathbb{R}^d} \theta \mu(x, \eta) \left\{F(\langle f, \eta \rangle - f(x)/N )-F(\langle f, \eta \rangle )\right\}N\eta(dx).
+\Pgen^{N} F_f(\eta):=& \int_{\IR^d} \theta\gamma(x, \eta) \left\{\int_{\IR^d} \left\{F(\langle f, \eta \rangle + f(y)/N )-F(\langle f, \eta \rangle )\right\}r(y, \eta)q_{\theta}(x,dy)\right\}N\eta(dx)\\
+&+\int_{\IR^d} \theta \mu(x, \eta) \left\{F(\langle f, \eta \rangle - f(x)/N )-F(\langle f, \eta \rangle )\right\}N\eta(dx).
 \end{aligned}    
@@
 In this case, our pre-limit model $(\eta^{N}(t))_{t \geq 0}$ is the solution to the Martingale Problem $(\Pgen^{N}, \eta_0)$, i.e. 
-for all $F \in \mathcal{C}^{2}(\mathbb{R})$
-and $f \in \mathcal{C}_{0}(\mathbb{R}^d)$,
+for all $F \in \mathcal{C}^{2}(\IR)$
+and $f \in \mathcal{C}_{0}(\IR^d)$,
 $$M_t:=F_f(\eta^{N}_t)-F_f(\eta_0)
@@
 As $N \to \infty$,
-$(\eta^{N}_t)_{t \geq 0}$ converges in $\mathcal{D}_{[0,\infty)}(\mathcal{M}_f(\mathbb{R}^d))$
+$(\eta^{N}_t)_{t \geq 0}$ converges in $\mathcal{D}_{[0,\infty)}(\mathcal{M}_f(\IR^d))$
 to $(\eta^{N}(t))_{t \geq 0}$.
@@
 $\{F_f(\eta):= F(\langle f, \eta \rangle ),~
-F \in \mathcal{C}^{2}(\mathbb{R}), ~
-f \in \mathcal{C}_{0}(\mathbb{R}^d)\}$
+F \in \mathcal{C}^{2}(\IR), ~
+f \in \mathcal{C}_{0}(\IR^d)\}$
 is a dense and convergence-determining 
-subset of functions in $\mathcal{M}_f(\mathbb{R}^d)$.
+subset of functions in $\mathcal{M}_f(\IR^d)$.
 Therefore, it suffices to show that for any $t>0$,
@@
 for all $k\geq 0$, $0\leq t_1<t_2<...,t_k \leq t < t+\tau$,
-and $h_1,...,h_k \in \mathcal{C}_{0}(\mathbb{R}^d)$.
+and $h_1,...,h_k \in \mathcal{C}_{0}(\IR^d)$.
 
@@
 \begin{aligned}
-\Pgen^{N} F_f(\eta):=& F'(\langle f, \eta \rangle)\int_{\mathbb{R}^d}  \theta\left\{\int_{\mathbb{R}^d} \left\{f(y)\gamma(x, \eta) r(y,\eta) -f(x)\mu(x, \eta)\right\}q_{\theta}(x,dy)\right\}\eta(dx)\\
-&+\frac{1}{2}\frac{\theta}{N}F''(\langle f, \eta \rangle)\int_{\mathbb{R}^d} 
- \left\{\gamma(x, \eta)\int_{\mathbb{R}^d} \left\{f^2(y) r(y,\eta) \right\}q_{\theta}(x,dy)+f^2(x)\mu(x, \eta)\right\}\eta(dx)\\
-&+\frac{1}{6}\frac{\theta}{N^2}\int_{\mathbb{R}^d}\left\{ 
-F'''(w) \left\{\gamma(x, \eta)\int_{\mathbb{R}^d} f^3(y) r(y,\eta) q_{\theta}(x,dy)\right\}-F'''(v)f^3(x)\mu(x, \eta)\right\}\eta(dx)
+\Pgen^{N} F_f(\eta):=& F'(\langle f, \eta \rangle)\int_{\IR^d}  \theta\left\{\int_{\IR^d} \left\{f(y)\gamma(x, \eta) r(y,\eta) -f(x)\mu(x, \eta)\right\}q_{\theta}(x,dy)\right\}\eta(dx)\\
+&+\frac{1}{2}\frac{\theta}{N}F''(\langle f, \eta \rangle)\int_{\IR^d} 
+ \left\{\gamma(x, \eta)\int_{\IR^d} \left\{f^2(y) r(y,\eta) \right\}q_{\theta}(x,dy)+f^2(x)\mu(x, \eta)\right\}\eta(dx)\\
+&+\frac{1}{6}\frac{\theta}{N^2}\int_{\IR^d}\left\{ 
+F'''(w) \left\{\gamma(x, \eta)\int_{\IR^d} f^3(y) r(y,\eta) q_{\theta}(x,dy)\right\}-F'''(v)f^3(x)\mu(x, \eta)\right\}\eta(dx)
 \end{aligned}    
@@
 and 
-$$\int_{\mathbb{R}^d} f^m(y) r(y,\eta) q_{\theta}(x,dy) \to f^m(x)r(x, \eta)$$
+$$\int_{\IR^d} f^m(y) r(y,\eta) q_{\theta}(x,dy) \to f^m(x)r(x, \eta)$$
 for $m=2,3$,
@@
 \begin{multline}
- \theta\left\{\int_{\mathbb{R}^d} \left\{f(y)\gamma(x, \eta) r(y,\eta) -f(x)\mu(x, \eta)\right\}q_{\theta}(x,dy)\right\}
+ \theta\left\{\int_{\IR^d} \left\{f(y)\gamma(x, \eta) r(y,\eta) -f(x)\mu(x, \eta)\right\}q_{\theta}(x,dy)\right\}
  \\
@@
 
-\comment{
-    Convergence of generators along (something like) the diagonal,
-    taking $\epsilon \to 0$ at the same time as the other coefficient.
-    (We won't prove tightness here.)
-    This is where OneStepConvergence goes in.
-}
-
-In this section we prove Theorem~\ref{them:nonlocal_pde_limits}.
+In this section we prove Theorem~\ref{them:nonlocal_pde_limits},
+which takes interaction distances to zero in the limit as well.
 
 \todo[inline]{BEGIN OneStepConvergence}
-These notes are an attempt of writing the one-step convergence of the particle system to a PDE limit.
-
-\textbf{In this whole document $\rho_\epsilon$ will be the density of a normal with mean $0$ and variance $\epsilon^2$, and $q_\theta$ the density of a normal with mean $0$ and variance $1/\theta$.
-That is, $\rho_\epsilon(x) = p_{\epsilon^2}(x)$ and $q_\theta = p_{1/\theta}(x)$.}
-
-In this document we assume we have the particle system with (unscaled) birth rate constant and equal $1$ and death rate at position $x$ given by $1+F(\rho_\epsilon*\overline{\eta}(x))/\theta$.
-That is, the martingale problem for the scaled system $\overline{\eta}_t$, is that for any smooth function $\phi$ we can write
-\begin{align}
-&\langle\phi(x),\overline{\eta}_{t}(dx)\rangle-\langle\phi(x),\overline{\eta}_{0}(dx)\rangle = M_t(\phi)   + \int_{0}^{t}\langle \theta  \int_{\mathbb{R}^d} \left( \phi(y)-\phi(x)\right) q_\theta(x,dy), \overline{\eta}_s^\epsilon(dx) \rangle ds \nonumber \\
- & + \int_0^t \langle  F(\langle \rho_\epsilon(y-x), \overline{\eta}_s(dy) \rangle)\phi(x),\overline{\eta}_s^{\varepsilon, \theta, N}(dx)  \rangle ds. \label{mgp1}
-\end{align}
-where $M_t(\phi)$ is a martingale with quadratic variation:
-\begin{align}
-[M(\phi)]_t&:=\frac{\theta}{N}\int_{0}^{t}\bigg\{ \left\langle \int_{\mathbb{R}^d} \phi^2(y) q_\theta(x,dy), \overline{\eta}_s^{\varepsilon, \theta, N}(dx) \right\rangle \nonumber\\
-&+ \left\langle  \left(1 + \frac{F(\langle \rho_\epsilon(y-x), \overline{\eta}_s(dy)\rangle )}{\theta } \right)\phi^2(x), \overline{\eta}_s^{\varepsilon, \theta, N}(dx))\right\rangle   \bigg\}ds.
-\label{mgp2}
-\end{align}
-
-We have the following result.
+\textbf{PREVIOUSLY, In this whole document $\rho_\epsilon$ will be the density of a normal with mean $0$ and variance $\epsilon^2$, and $q_\theta$ the density of a normal with mean $0$ and variance $1/\theta$.
+That is, $\rho_\epsilon(x) = p_{\epsilon^2}(x)$ and $q_\theta = p_{1/\theta}(x)$.
+This is HOPEFULLY FIXED NOW.}
 
 \begin{theorem} \label{TeoremOneStepConvergence}
-Let $(\overline{\eta}_t)_{t \geq 0}$ be the scaled particle system with $r_\theta \equiv \gamma_\theta = 1$. Suppose $F(x)$ satisfies:
+    Let $(\eta_t)_{t \geq 0}$ be the scaled particle system with $r(x, \eta) \equiv \gamma(x, \eta) \equiv 1$.
+    Suppose $F(x)$ satisfies:
     \begin{enumerate}
@@
     \end{enumerate}
-We will also suppose $\theta$ is big enough that $1- \frac{F(x)1_{x>0}}{\theta}$ is non-negative.
-
-We will assume $\overline{\eta}_0:=\overline{\eta}_0(\epsilon,N,\theta)$ is a sequence of initial conditions for $(\overline{\eta}_t)_{t \geq 0}$ such that there exists a finite constant $C>0$ independent of $\epsilon, N, \theta$,
+    We will also suppose $\theta$ is big enough that $1- F(x)1_{x>0}/\theta$ is non-negative.
+
+    We will assume $\eta_0 := \eta_0(\epsilon,N,\theta)$
+    is a sequence of initial conditions for $(\eta_t)_{t \geq 0}$
+    such that there exists a finite constant $C>0$ independent of $\epsilon$, $N$, and $\theta$
+    such that
     \begin{enumerate}
-\item $\langle 1 , \overline{\eta}_0 \rangle < C $
-\item  $\Vert \rho_\epsilon * \overline{\eta}_0(x) \Vert_\infty < C$ for all $x \in \mathbb{R}^d$
-\item $|\rho_\epsilon * \overline{\eta}_0(x) - \rho_\epsilon * \overline{\eta}_0(y)| \leq C \Vert x - y \Vert  $ for all $x,y \in \mathbb{R}^d$
-\item $(\rho_\epsilon * \overline{\eta}_0(x) dx) \Rightarrow u_0(x)dx$ for some $u_0(x) \in \mathcal{C}^2(\mathbb{R}^d)$, where $\Rightarrow$ denotes weak convergence. 
+        \item $\langle 1 , \eta_0 \rangle < C $
+        \item  $\| \rho_\epsilon * \eta_0(x) \|_\infty < C$ for all $x \in \IR^d$
+        \item $|\rho_\epsilon * \eta_0(x) - \rho_\epsilon * \eta_0(y)| \leq C \| x - y \|$ for all $x,y \in \IR^d$, and
+        \item $\rho_\epsilon * \eta_0(x) dx$ converges weakly to $u_0(x)dx$ for some $u_0(x) \in \mathcal{C}^2(\IR^d)$.
     \end{enumerate}
-Furthermore, suppose that,
+    Furthermore, suppose that
     \begin{equation}
-\frac{\theta}{\epsilon^d N} + \frac{1}{\theta \epsilon^{2}}\rightarrow 0 \label{ConditionsForConvergence}
+        \frac{\theta}{\epsilon^d N} + \frac{1}{\theta \epsilon^{2}} \to 0 . \label{ConditionsForConvergence}
     \end{equation}
     Fix $T>0$.
-Then, the measure $((\rho_\epsilon *\overline{\eta}_t)(x) dx)_{t \geq 0}$ converges weakly in $D([0,T], \mathcal{M}_F(\mathbb{R}^d))$ to a measure $(\Xi_t(dx))_{t \geq 0}$.
+Then, the measure $((\rho_\epsilon *\eta_t)(x) dx)_{t \geq 0}$ converges weakly in $D([0,T], \measures)$ to a measure $(\Xi_t(dx))_{t \geq 0}$.
 Moreover, up to a modification on a set of measure zero, $\Xi_t(x) = u_t(x)dx$, where $u_t(x)$ is a weak solution to:
@@
 \todo[inline]{Question: Why do we need that regularity on $u_0$?
-I believe all we need is that (\ref{aprox3}) holds, and for that, I am almost sure that $u_0$ only needs to satisfy the first three hypotheses for $\overline{\eta}_0(x)$.
-Furthermore,  if I am not mistaken, those are all implied by $u_0(x) \in L^1(\mathbb{R}^d) \cap L^2(\mathbb{R}^d) \cap \mathcal{C}^1(\mathbb{R}^d)$ in case we want a nice space to put on the result.
+I believe all we need is that (\ref{aprox3}) holds, and for that, I am almost sure that $u_0$ only needs to satisfy the first three hypotheses for $\eta_0(x)$.
+Furthermore,  if I am not mistaken, those are all implied by $u_0(x) \in L^1(\IR^d) \cap L^2(\IR^d) \cap \mathcal{C}^1(\IR^d)$ in case we want a nice space to put on the result.
  Alison says: $C^1 \cap L^1$ probably enough, but...
@@
 
-\todo[inline]{Questions 2: The conditions on $F$ implies that $F(x)1_{x>0} = (A-Bx)1_{x>0}$ for some $A,B>0$, or not?
-At least that is the only polynomial that is bounded above with a bounded derivative.
-Maybe we could rewrite the result for that explicit $F$?
-Note: $F$ no longer assumed polynomial.
-}
+\todo[inline]{TODO: Below what we write as $\rho_\epsilon$ is actually $\rho_F = p_{\epsilon_F^2}$; resolve this somehow. (it seems nice to retain the dependence on $\epsilon$ somehow)}
 
@@
 As a preliminary, we will prove some basic tools we are going to need all the way through.
-First, we prove that, under the conditions of Theorem~\ref{TeoremOneStepConvergence}, $\overline{\eta}_t$ has a uniformly bounded total mass in expectation.
+First, we prove that, under the conditions of Theorem~\ref{TeoremOneStepConvergence}, $\eta_t$ has a uniformly bounded total mass in expectation.
 We then prove some regularity estimates of a random walk with Gaussian jumps.
-While this may seem disconnected from our goal the generator of this random walk is in the first integral element that appears in the martingale problem for $\overline{\eta}_t$, equation (\ref{mgp1}).
+While this may seem disconnected from our goal the generator of this random walk is in the first integral element that appears in the martingale problem for $\eta_t$, equation (\ref{mgp1}).
 It is then, no surprise, that we need some control over the regularity this term brings to our particle system.
 
-We then focus on $C$-tighness of $\rho_\epsilon * \overline{\eta}_t(x)dx$.
-For this we will prove that for fixed $x$, the random variable $\rho_\epsilon*\overline{\eta}_t(x)$ has uniformly bounded expectation.
-Using this and the regularity of the random walk mention above, we will be able to prove the $C$-tightness of $\rho_\epsilon * \overline{\eta}_t(x)dx$.
+We then focus on $C$-tighness of $\rho_\epsilon * \eta_t(x)dx$.
+For this we will prove that for fixed $x$, the random variable $\rho_\epsilon*\eta_t(x)$ has uniformly bounded expectation.
+Using this and the regularity of the random walk mention above, we will be able to prove the $C$-tightness of $\rho_\epsilon * \eta_t(x)dx$.
 
 Then we will proceed to identify the limit.
-For this, a continuity estimate for $(\rho_\epsilon*\overline{\eta}_t(x))$ is needed, which is again a consequence of the random walk estimates mentioned above.
-Using this we focus on controlling the convergence of \textit{non-linear terms} in the martingale problem of $(\rho_\epsilon*\overline{\eta}_t(x))$ (as the others converge as a consequence of weak convergence).
-Those do not converge as a consequence of weak convergence, since they are not written as an integral on $M^{\otimes k}(\mathbb{R}^d)$ of $(\rho_\epsilon*\overline{\eta}_t(x) dx)$ (for some $k \in \mathbb{N}$).
-Instead, we will first compare the quadratic terms to terms only involving $\rho_\epsilon*\overline{\eta}_s$ (and not $\overline{\eta}_s(dy)$) and then we will exchange those terms with a suitable integral in $M^{\otimes2}(\mathbb{R}^d)$, for which convergence do follow easily.
+For this, a continuity estimate for $(\rho_\epsilon*\eta_t(x))$ is needed, which is again a consequence of the random walk estimates mentioned above.
+Using this we focus on controlling the convergence of \textit{non-linear terms} in the martingale problem of $(\rho_\epsilon*\eta_t(x))$ (as the others converge as a consequence of weak convergence).
+Those do not converge as a consequence of weak convergence, since they are not written as an integral on $M^{\otimes k}(\IR^d)$ of $(\rho_\epsilon*\eta_t(x) dx)$ (for some $k \in \mathbb{N}$).
+Instead, we will first compare the quadratic terms to terms only involving $\rho_\epsilon*\eta_s$ (and not $\eta_s(dy)$) and then we will exchange those terms with a suitable integral in $M^{\otimes2}(\IR^d)$, for which convergence do follow easily.
 
@@
 
-\paragraph{Boundedness of the total mass}
-\begin{lemma} \label{Lemma:UniformlyBoundedMass}
-Under the assumptions of Theorem~\ref{TeoremOneStepConvergence}, there is a finite constant $C$ (independent of $\epsilon, N, \theta$), such that $\IE\left[ \sup_{0 \leq s \leq T} \langle 1, \overline{\eta}_s \rangle \right] \leq C$.
+Since we're assuming that $\gamma$ and $r$ are identically 1,
+the death rate is $1 + F(x, \eta) / \theta$.
+For reference,
+the martingale problem (REF) for $\eta_t$ gives that for any smooth function $\phi$,
+\begin{align}
+&
+    \langle \phi(x), \eta_{t}(dx) \rangle
+    -
+    \langle \phi(x), \eta_{0}(dx)\rangle
+    =
+    M_t(\phi)
+    +
+    \int_{0}^{t} \langle \theta \int_{\IR^d}
+            \left( \phi(y) -\phi(x) \right)
+        q_\theta(x,dy), \eta_s(dx)
+    \rangle ds
+\nonumber \\
+&
+    {} +
+    \int_0^t \langle
+        F(x, \eta_s) \phi(x),
+        \eta_s(dx)
+    \rangle ds , \label{mgp1}
+\end{align}
+where $M_t(\phi)$ is a martingale with quadratic variation:
+\begin{align}
+[ M(\phi) ]_t
+    &:=
+    \frac{\theta}{N}
+    \int_{0}^{t} \bigg\{
+        \left\langle \int_{\IR^d} \phi^2(y) q_\theta(x,dy), \eta_s(dx) \right\rangle
+    \nonumber\\
+    & {} +
+    \left\langle \left(1 + \frac{F(x, \eta_s)}{\theta } \right)
+        \phi^2(x), \eta_s(dx)) \right\rangle 
+    \bigg\} ds.  \label{mgp2}
+\end{align}
+
+Above, we showed in Lemma~\ref{lem:eta_compact_containment}
+uniform boundedness the total mass under the assumption of fixed $\epsilon$.
+It is easy to see that the same proof applies
+in this situation -- indeed, the hardest part, Lemma~\ref{lem:gamma_bound} is not needed,
+since $r$ and $\gamma$ are 1 --
+and gives us the following result.
+
+\begin{lemma}[Boundedness of total mass] \label{Lemma:UniformlyBoundedMass}
+    Under the assumptions of Theorem~\ref{TeoremOneStepConvergence},
+    for each $T \ge 0$ there is a finite constant $C$ (independent of $\epsilon, N, \theta$),
+    such that $\IE\left[ \sup_{0 \leq s \leq T} \langle 1, \eta_s \rangle \right] \leq C$.
 \end{lemma}
-\begin{proof}
-By putting $\phi(x)=1$ in the martingale problem of $\overline{\eta}_t$, equation (\ref{mgp1}), we have,
-\begin{align} \label{eq:MPTotalMass}
-\langle 1, \overline{\eta}_t \rangle &= \langle 1, \overline{\eta}_0 \rangle + \int_0^t \langle F(\rho_\epsilon * \overline{\eta}_s), \overline{\eta}_s \rangle ds + M_t
-\end{align}
-where $M_t$ is a martingale with quadratic variation,
-\begin{align} \label{eq:QVTotalMass}
-[M]_t = \frac{\theta}{N}\int_0^t \langle 1 + \frac{F(\rho_\epsilon* \overline{\eta}_s)}{\theta}, \overline{\eta}_s \rangle d s 
-\end{align}
-By taking expectations in (\ref{eq:MPTotalMass}) we get,
-\[ \IE[\langle 1, \overline{\eta}_t \rangle] =  \IE[\langle 1, \overline{\eta}_0 \rangle]  + \IE[ \int_0^t \langle F(\rho * \overline{\eta}_s), \overline{\eta}_s \rangle ds ]   \leq C +   C \mathbb{E}\left[ \int_0^t \langle 1, \overline{\eta}_s \rangle ds \right].\]
-In last inequality we used that $F(x)1_{x >0}$ and $\langle 1, \overline{\eta}_0 \rangle$ are uniformly bounded above.
-By Gronwall's inequality we deduce $\IE[\langle 1, \overline{\eta}_s \rangle]$ is bounded on $[0,T]$.
+
+%% PLR: removing, since we can just refer to the above?
+% \begin{proof}
+% By putting $\phi(x)=1$ in the martingale problem of $\eta_t$, equation (\ref{mgp1}), we have,
+% \begin{align} \label{eq:MPTotalMass}
+% \langle 1, \eta_t \rangle &= \langle 1, \eta_0 \rangle + \int_0^t \langle F(\rho_\epsilon * \eta_s), \eta_s \rangle ds + M_t
+% \end{align}
+% where $M_t$ is a martingale with quadratic variation,
+% \begin{align} \label{eq:QVTotalMass}
+% [M]_t = \frac{\theta}{N}\int_0^t \langle 1 + \frac{F(\rho_\epsilon* \eta_s)}{\theta}, \eta_s \rangle d s 
+% \end{align}
+% By taking expectations in (\ref{eq:MPTotalMass}) we get,
+% \[ \IE[\langle 1, \eta_t \rangle] =  \IE[\langle 1, \eta_0 \rangle]  + \IE[ \int_0^t \langle F(\rho * \eta_s), \eta_s \rangle ds ]   \leq C +   C \mathbb{E}\left[ \int_0^t \langle 1, \eta_s \rangle ds \right].\]
+% In last inequality we used that $F(x)1_{x >0}$ and $\langle 1, \eta_0 \rangle$ are uniformly bounded above.
+By Gronwall's inequality we deduce $\IE[\langle 1, \eta_s \rangle]$ is bounded on $[0,T]$.
 Hence, by taking expectations in (\ref{eq:QVTotalMass}) and using again the bound on $F(x)1_{x>0}$ we get,
-\begin{equation} \IE\left[ [M]_t \right] \leq \frac{\theta}{N} C \int_0^t \mathbb{E}\left[ \langle 1, \overline{\eta}_s \rangle ds \right] \leq \frac{\theta}{N}C t \label{eq:quadvarMass} \end{equation}
-Note that, with this, $\IE[ [M]_t]$ is bounded (and in fact $\mathcal{O}(\theta/N)$). By the Burkholder-Davis-Gundy inequality and then Jensen's inequality we get
-\begin{align*}
-    \IE\left[ \sup_{0 \leq t \leq T} M_t \right]
-    \leq
-    C \IE\left[ [M]_T \right]^{1/2}
-    \leq
-    C \IE[M]_T^{1/2}
-    \leq
-    C  
-\end{align*}
-Taking supremum and then expectation in (\ref{eq:MPTotalMass}) and using the last inequality gives the result.
-
-    \comment{Alison says: I'd actually write out
-    $\sup \langle 1, \eta_s \rangle \le \int_0^T xxx ds + \sup M_t$ .
-    }
-
-\end{proof}
+% \begin{equation} \IE\left[ [M]_t \right] \leq \frac{\theta}{N} C \int_0^t \mathbb{E}\left[ \langle 1, \eta_s \rangle ds \right] \leq \frac{\theta}{N}C t \label{eq:quadvarMass} \end{equation}
+% Note that, with this, $\IE[ [M]_t]$ is bounded (and in fact $\mathcal{O}(\theta/N)$). By the Burkholder-Davis-Gundy inequality and then Jensen's inequality we get
+% \begin{align*}
+%     \IE\left[ \sup_{0 \leq t \leq T} M_t \right]
+%     \leq
+%     C \IE\left[ [M]_T \right]^{1/2}
+%     \leq
+%     C \IE[M]_T^{1/2}
+%     \leq
+%     C  
+% \end{align*}
+% Taking supremum and then expectation in (\ref{eq:MPTotalMass}) and using the last inequality gives the result.
+% 
+%     \comment{Alison says: I'd actually write out
+%     $\sup \langle 1, \eta_s \rangle \le \int_0^T xxx ds + \sup M_t$ .
+%     }
+% 
+% \end{proof}
 
@@
 \begin{proposition}
-Under the assumptions of Theorem~\ref{TeoremOneStepConvergence} there is a finite constant $C$ (independent of $\epsilon, N, \theta$) such that, for all $t \in [0,T]$ and for big enough $N$ and $\theta$, $\IE[ \langle 1, \overline{\eta}_t \rangle^2] \leq C$.\label{Prop:SecondMomentMass}
+Under the assumptions of Theorem~\ref{TeoremOneStepConvergence} there is a finite constant $C$ (independent of $\epsilon, N, \theta$) such that, for all $t \in [0,T]$ and for big enough $N$ and $\theta$, $\IE[ \langle 1, \eta_t \rangle^2] \leq C$.\label{Prop:SecondMomentMass}
 \end{proposition}
 
-\comment{Alison says: Just use the martingale problem and boundedness of $F$ and Gronwall I think. (The proof below is false.)}
-
-\begin{proof}
-By using in (\ref{eq:MPTotalMass}) that, by assumption, $\langle 1, \overline{\eta}_0 \rangle$  and $F(x)1_{x > 0}$ are bounded above we get,
-\begin{align*}
- \langle 1, \overline{\eta}_t \rangle^2 \leq C \langle 1, \overline{\eta}_t \rangle + C\langle 1,\overline{\eta}_t \rangle \int_0^t \langle 1, \overline{\eta}_s\rangle ds + M_t \langle 1, \overline{\eta}_t \rangle \end{align*}
-Taking expectation we obtain,
-\begin{align*}
-\IE[ \langle 1, \overline{\eta}_t \rangle^2 ]
-    & \leq
-    C \IE[\langle 1, \overline{\eta}_t \rangle] + C\IE[  \langle 1,\overline{\eta}_t \rangle \int_0^t \langle 1, \overline{\eta}_s\rangle ds ] + \IE[ M_t \langle 1, \overline{\eta}_t \rangle] \\
-    & \leq
-    C +
-    C\IE[\frac{1}{2} \langle 1, \overline{\eta}_t\rangle^2] + \frac{1}{2} \IE[t \int_0^t \langle 1, \overline{\eta}_s \rangle^2 ds ] + (\IE[M_t^2] \IE[\langle 1, \overline{\eta}_t \rangle^2])^{1/2}
-\end{align*}
-where in the second inequality we have used Lemma~\ref{Lemma:UniformlyBoundedMass} on the first term, that $2ab \leq a^2 + b^2$ and Jensen's inequality in the second term and Holder's inequality in the third term.
-Note that by the Burkholder-Davis-Gundy inequality and (\ref{eq:quadvarMass}) we have that,
-\[ \IE[ M_t^2 ] = \mathcal{O}\left( \frac{\theta}{N} \right). \]
-Hence, by using that for positive $a$ we have $a^{1/2} \leq a+1$ we can deduce that,
-\comment{Alison says: but you don't have $C < 1$, so not clear how you're doing this.}
-\begin{align*}
-\frac{1}{2} \IE[ \langle 1, \overline{\eta}_t \rangle^2 ] \leq C + \frac{1}{2} \IE[t \int_0^t \langle 1, \overline{\eta}_s \rangle^2 ds ] + \mathcal{O}\left( \left(\frac{\theta}{N}\right)^{1/2} \right) +\mathcal{O}\left( \left(\frac{\theta}{N}\right)^{1/2} \right) \IE[\langle 1, \overline{\eta}_t \rangle^2].
-\end{align*}
-Let $\theta$ and $N$ big enough so $\theta/N < 1/16$. From the last equation we then can deduce,
-\[ \frac{1}{4}\IE[ \langle 1, \overline{\eta}_t \rangle^2 ] \leq C + \frac{C}{2} t \int_0^t\IE[\langle 1, \overline{\eta}_s \rangle^2 ] ds\]
-An application of Grownwall's inequality yields
-\[ \IE[ \langle 1, \overline{\eta}_t \rangle^2 ] \leq C \exp(2 C t^2) \leq C \exp(2 C T^2),  \]
-finishing the proof.
+\begin{proof}[of Proposition~\ref{Prop:SecondMomentMass}]
+    % Referring to section~\ref{sec:heuristics} with $f=1$ and $G(m) = m^2$,
+    When the population is in state $\eta$,
+    individuals of mass $1/N$ are born at rate $\theta \langle 1, \eta \rangle$
+    and die at rate $\theta \langle 1 + F/\theta, \eta \rangle$.
+    Similar to the arguments in section~\ref{sec:heuristics} with $f=1$ and $G(m) = m^2$,
+    since $N G(m \pm 1/N) - G(m) = \pm 2m + 1/N$,
+    \begin{align*}
+        \IE[\langle 1, \eta_t \rangle^2]
+        &=
+        \IE[\langle 1, \eta_0 \rangle^2]
+        +
+        \IE\left[
+        \int_0^t
+        \left\{
+            \theta \langle 1, \eta_s \rangle
+            \left( 2 \langle 1, \eta_s \rangle + 1/N \right)
+            +
+            \theta \langle 1 + F/\theta, \eta_s \rangle
+            \left( - 2 \langle 1, \eta_s \rangle + 1/N \right)
+        \right\}
+        ds
+        \right]
+        \\
+        &=
+        \IE[\langle 1, \eta_0 \rangle^2]
+        +
+        \IE\left[
+        \int_0^t \left\{
+            \frac{2\theta}{N} \langle 1, \eta_s \rangle ds
+            -
+            2 \langle F, \eta_s \rangle \left(\langle 1, \eta_s \rangle - \frac{1}{N} \right)
+        \right\} ds \right].
+    \end{align*}
+    Since $F(m)1_{m > 0}$ is bounded above and $\theta/N$ converges,
+    we have for an appropriate $C$ that
+    \begin{align*}
+        \IE[\langle 1, \eta_t \rangle^2]
+        \le
+        C + C \int_0^t \IE[\langle 1, \eta_s \rangle] ds
+        + C \int_0^t \IE[\langle 1, \eta_s \rangle^2] ds .
+    \end{align*}
+    The result follows from Lemma~\ref{Lemma:UniformlyBoundedMass} and Gronwall's inequality.
 \end{proof}
@@
 In what follows we let $\psi_t^{\epsilon, x}(y)$ be the solution of:
-\begin{equation} \frac{\partial}{ \partial_t} \psi_t^{\epsilon,x} = \mathcal{L}^\theta \psi_t^{\epsilon, x} \label{AlmostHeatEquation} \end{equation}
-with initial condition $\psi_0^{\epsilon,x}(y) = \rho_\epsilon(y-x)$. We have the following result for $\psi_t^{\epsilon,x}$.
+\begin{equation}
+    \frac{\partial}{ \partial_t} \psi_t^{\epsilon,x}
+    =
+    \mathcal{L}^\theta \psi_t^{\epsilon, x}
+    \label{AlmostHeatEquation}
+\end{equation}
+with initial condition $\psi_0^{\epsilon,x}(y) = \rho_\epsilon(y-x)$.
+We have the following result for $\psi_t^{\epsilon,x}$.
 
 \begin{lemma} \label{PsiBoundHS}
-Fix $t>0$ and let $T(t)$ be a random variable such that $\theta T(t) \sim Poisson(\theta t)$. Then:
-\[ \psi^{\epsilon,x}_t(y) = \mathbb{E}\left[ p_{\epsilon^2+T(t)}(x,y)\right] \]
-Moreover,
-\[ \Vert \psi^{\epsilon,x}_t \Vert_\infty \leq \mathcal{O}\left( \frac{1}{(t+\epsilon^2)^{d/2}} + \frac{1}{\epsilon^2 \theta} \right) \]
+    Fix $t>0$,
+    let $(N(s))_{s \ge 0}$ be a rate 1 Poisson process,
+    and let $T(t) = N(\theta t) / \theta$.
+    Then
+    \[
+        \psi^{\epsilon,x}_t(y)
+        =
+        \IE\left[ p_{\epsilon^2+T(t)}(x,y)\right],
+    \]
+    and moreover, there is a $C$ independent of $\epsilon$ or $t$ such that
+    \[
+        \| \psi^{\epsilon,x}_t \|_\infty
+        \leq
+        \frac{C}{(\epsilon^2 + t)^{d/2}}
+        \left(
+            1 + \exp\left(-\frac{\epsilon^2 \theta}{2}\right)
+        \right) .
+    \]
 \end{lemma}
+
 \begin{proof}
-The first claim of this result follows immediately from $\mathcal{L}^\theta$ being the generator of a continuous random walk, where Gaussian jumps with mean $0$ and variance $1/\theta$ arrive at rate $\theta$.
-
-For the second claim we note that $T(t)-t$ has mean $0$ and variance $t/\theta$.  So by Chebyshev's inequality we get,
-\begin{equation}
-\IP\left[  \frac{|T(t)-t|}{\epsilon^2+t} > \frac{1}{2} \right] \leq \frac{4t}{\theta(\epsilon^2+t)^2} \leq \frac{2}{\epsilon^2 \theta}. \label{eq:IneqConcentrationT}
-\end{equation}
-Thus, by using standard bounds for the heat semigroup we get that,
-\begin{align*}
-\Vert \psi^{\epsilon,x} \Vert_\infty & \leq \IE\left[  \frac{1}{2 \pi (\epsilon^2+T(t))^{d/2}}\right] \\ & = \frac{1}{(2 \pi(\epsilon^2+t)^{d/2}} \IE\left[\left(\frac{1}{1+\frac{T(t)-t}{\epsilon^2+t}} \right)^{d/2} \right] \\ &\leq \frac{\pi^{-d/2}}{(\epsilon^2+t)^{d/2}} + \frac{2}{\epsilon^2 \theta}
-\end{align*}
-where in the last inequality we partition over $\{ |T(t)-t| > (\epsilon^2+t)/2\}$ and its complement, and use (\ref{eq:IneqConcentrationT}).
+    The first claim follows immediately from $\mathcal{L}^\theta$ being the generator
+    of a continuous-time random walk,
+    where independent Gaussian jumps with mean $0$ and variance $1/\theta$
+    arrive at rate $\theta$.
+
+    For the second claim, first define $\tau(t) = T(t)-t$.
+    % which has mean $0$ and variance $t/\theta$.
+    % so by Chebyshev's inequality,
+    % \begin{equation}
+    %     \IP\left\{ \tau(t) < - \frac{\epsilon^2 + t}{2} \right\}
+    %     \leq
+    %     \IP\left\{  \frac{|T(t)-t|}{\epsilon^2+t} > \frac{1}{2} \right\}
+    %     \leq
+    %     \frac{4t}{\theta(\epsilon^2+t)^2} \leq \frac{2}{\epsilon^2 \theta}.
+    %     \label{eq:IneqConcentrationT}
+    % \end{equation}
+    Since if $\tau(t) \ge -(\epsilon^2 + t)/2$,
+    then $1/(\epsilon^2 + T(t)) \le 2/(\epsilon^2 + t)$,
+    while $\epsilon^2 + T(t) \ge \epsilon^2$ always,
+    then partitioning over
+    $\{ \tau(t) \ge -(\epsilon^2 + t)/2 \}$ and its complement,
+    \begin{align}
+    \| \psi^{\epsilon,x} \|_\infty
+    &=
+        \IE\left[ 
+            \frac{1}{2 \pi (\epsilon^2+T(t))^{d/2}}
+        \right] \nonumber
+    \\ & \le
+        \frac{C}{(\epsilon^2 + t)^{d/2}}
+        + 
+        \frac{C}{\epsilon^d}
+        \IP\left\{
+            \tau(t) < - (\epsilon^2 + t) / 2
+        \right\} \label{eqn:psi_infty_bound}
+    \end{align}
+    Now, observe that since $\IE[e^{-N(\theta t)}] = \exp(-\theta t (1 - e^{-1}))$,
+    then by Markov's inequality,
+    \begin{align*}
+        \IP\left\{
+            \tau(t) < - \frac{\epsilon^2 + t}{2}
+        \right\}
+        &=
+        \IP\left\{
+            e^{-N(\theta t)} > e^{-\theta (t - \epsilon^2) / 2}
+        \right\}
+        \\&\le
+        \frac{
+            \exp(- \theta t(1 - e^{-1}))
+        }{
+            \exp(- \theta (t - \epsilon^2) / 2)
+        }
+        \\&=
+        \exp\left\{ - \delta \theta t - \frac{\theta \epsilon^2}{2} \right\} ,
+    \end{align*}
+    where $\delta = 1/2 - e^{-1} > 0$.
+    The second term in \eqref{eqn:psi_infty_bound} is therefore bounded by
+    \[
+        C \left(1 + \frac{t}{\epsilon^2}\right)^{d/2} e^{-\delta \theta t}
+        \frac{1}{(\epsilon^2 + t)^{d/2}} e^{-\epsilon^2 \theta / 2} .
+    \]
+    Now, $e^{-\delta \theta t} (1 + t/\epsilon^2)^{d/2}$ is decreasing in $t$
+    for all $t$ if $\epsilon^2 \theta$ is sufficiently large:
+    this holds because its derivative is
+    is
+    \[
+        \left( \frac{d}{2 \epsilon^2} - \left(1 + \frac{t}{\epsilon^2}\right) \delta \theta \right)
+        \left( 1 + \frac{t}{\epsilon^2} \right)^{d/2 - 1} e^{-\delta \theta t} ,
+    \]
+    which is negative if $\theta(\epsilon^2 + t) > d/2 \delta$.
+    Therfore, the second term in \eqref{eqn:psi_infty_bound} 
+    is bounded by $C e^{-\epsilon^2 \theta / 2} / (\epsilon^2 + t)^{d/2}$
+    (for a different constant $C$).
+    Substituting this into \eqref{eqn:psi_infty_bound} obtains the result.
 \end{proof}
-We will need a further comparison of $\psi_t^{\epsilon,x}$ to the heat semigroup.
+
+We will need a further comparison of $\psi_t^{\epsilon,x}$ to the heat semigroup,
+and for this we will first need the following fact about large deviations
+of a Poisson process.
+
 \begin{lemma}
-For every $x,y \in \mathbb{R}^d$ and $t>0$ we have,
+    \label{lem:poisson_ld}
+    Fix $A > e^3 - 1$ (so that $\log(1 + A) > 3$).
+    In the notation of Lemma~\ref{PsiBoundHS},
+    \begin{align*}
+        \limsup_{\theta \to \infty}
+        \frac{1}{\theta} \log
+        \IP\left\{
+            T(t) - t > A(\epsilon^2 + t)
+        \right\}
+    \le
+        - (\epsilon^2 + t) \frac{A}{2}
+        - \log(1 + A)\left( \frac{t + A(\epsilon^2 + t)}{2} \right) .
+    \end{align*}
+\end{lemma}
+
+\begin{proof}[of Lemma~\ref{lem:poisson_ld}]
+    We apply Cram\'er's Theorem.
+    First note that
+    \begin{align*}
+        \IP\left\{
+            T(t) - t > A(\epsilon^2 + t)
+        \right\}
+        =
+        \IP\left\{
+            N(\theta) t) / \theta
+            >
+            t + A(\epsilon^2 + t)
+        \right\} .
+    \end{align*}
+    For convenience, suppose $\theta$ is an integer,
+    and so we may write $N(\theta t) = Z_1(t) + \cdots + Z_\theta(t)$,
+    where the $Z_i(t)$ are i.i.d.~ Poisson($t$) random variables.
+    To apply Cram\'er's Theorem, we need the rate function for the Poisson($t$) distribution,
+    which is
+    \[
+        \Lambda^*(x) = \sup_{\alpha > 0} \left[ \alpha x - \lambda(\alpha) \right],
+    \]
+    where $\lambda(\alpha) = \log \IE[\exp(\alpha Z_1(t))] = t(e^\alpha - 1)$.
+    Now, the supremum of $\alpha x + t - te^\alpha$ is attained at $x = t e^\alpha$,
+    and so
+    \[
+        \Lambda^*(x) = x \log(x/t) - x + t .
+    \]
+    Cram\'er's Theorem then gives
+    \begin{align*}
+        \limsup_{\theta \to \infty}
+        \frac{1}{\theta} \log
+        \IP\left\{
+            \frac{N(\theta t)}{\theta}
+            > A(\epsilon^2 + t)
+        \right\}
+    &\le
+        - \Lambda^*(t + A(\epsilon^2 + t))
+    \\ &=
+        A(\epsilon^2 + t)
+        -
+        (t + A(\epsilon^2 + t)) \log\left( 1 + \frac{A(\epsilon^2 + t)}{t} \right) 
+    \\ &\le
+        A(\epsilon^2 + t)
+        -
+        (t + A(\epsilon^2 + t)) \log(1 + A)
+    \\ &\le
+        A(\epsilon^2 + t) \left( 1 - \frac{1}{2} \log(1 + A) \right)
+        -
+        \frac{1}{2} (t + A(\epsilon^2 + t)) \log(1 + A)  .
+    \end{align*}
+    Since $(1/2) \log(1 + A) > 3/2$, hence $1 - (1/2) \log(1 + A) < - 1/2$,
+    and we are done.
+\end{proof}
+
+Now we would like to show that $\psi_t^{\epsilon,x}(y)$
+is uniformly close to $p_{\epsilon^2 + t}(x, y)$
+under the assumptions.
+
+\begin{lemma}
+    \label{lem:psi_approx_p}
+    In the notation of Lemma~\ref{PsiBoundHS},
+    and with $A$ as in Lemma~\ref{lem:poisson_ld},
+    \begin{align*}
+        \left|
+            \psi_t^{\epsilon, x}(y)
+            -
+            p_{\epsilon^2 + t}(x, y)
+        \right|
+        \le
+        \frac{C}{\epsilon^2 \theta}^{d/2}
+        p_{2(A+1)(\epsilon^2+t)}(x, y)
+        +
+        C \exp(- \epsilon^2 \theta / 2)
+        +
+        \frac{C}{(\epsilon^2 + t)^{d/2}}
+        \IP\left\{
+            \tau(t) > A(\epsilon^2 + t)
+        \right\} .
+    \end{align*}
+\end{lemma}
+
+\begin{proof}[of Lemma~\ref{lem:psi_approx_p}]
+    We will partition into three events according to the value of $\tau(t)$:
+    let $A_1 = \{ \tau(t) < - (\epsilon^2 + t)/2 \}$,
+    let $A_2 = \{ \tau(t) > A(\epsilon^2 + t) \}$,
+    and $A_3$ the remaining event, $\{ - (\epsilon^2 + t)/2 \le \tau(t) \le A(\epsilon^2 + t) \}$.
+    Then,
+    \begin{align*}
+        \left|
+            \psi_t^{\epsilon, x}(y)
+            -
+            p_{\epsilon^2 + t}(x, y)
+        \right|
+        &=
+        \left|
+        \IE\left[
+            p_{\epsilon^2 + t + \tau(t)}(x, y)
+            -
+            p_{\epsilon^2 + t}(x, y)
+        \right]
+        \right|
+        \\&\le
+        \IE\left[
+            (1_{A_1} + 1_{A_2} + 1_{A_3})
+            \left|
+            p_{\epsilon^2 + t + \tau(t)}(x, y)
+            -
+            p_{\epsilon^2 + t}(x, y)
+        \right|
+        \right] .
+    \end{align*}
+
+    For the first term, note that if $a < b$ then
+    \begin{align*}
+        |p_a(x, y) - p_b(x, y)| 
+        &=
+        \frac{1}{(2\pi)^{d/2}}
+        \left|
+            \frac{1}{a^{d/2}}
+            e^{-\|x - y\|^2 / 2a}
+            -
+            \frac{1}{b^{d/2}}
+            e^{-\|x - y\|^2 / 2b}
+        \right|
+        \\ &=
+        \frac{1}{(2\pi a^2)^{d/2}}
+            e^{-\|x - y\|^2 / 2b}
+        \left|
+            e^{-\|x - y\|^2 \left(\frac{1}{2a} - \frac{1}{2b}\right)}
+            -
+            \left(\frac{a}{b}\right)^{d/2}
+        \right|
+        \\ &\le
+        C \left(\frac{b}{a}\right)^{d/2}
+        p_b(x, y) ,
+    \end{align*}
+    where the inequality follows because both terms in the absolute values are less than 1.
+    % note the original had $p_{b/2}$ on the right.
+    Applying this with $a = \epsilon^2 + t + \tau(t)$ and $b = \epsilon^2 + t$,
+    and using the same bound as we did for the second term of equation~\ref{eqn:psi_infty_bound},
+    \begin{align*}
+        \IE\left[
+            1_{A_1} |p_a(x, y) - p_b(x, y)| 
+        \right]
+        & \le
+            C \left(\frac{\epsilon^2 + t}{\epsilon^2}\right)^{d/2}
+            p_{\epsilon^2 + t}(x, y) 
+            \IP\left\{ \tau(t) < - \frac{\epsilon^2 + t}{2} \right\}
+        \\ & \le
+            C \frac{1}{\epsilon^d}
+            \IP\left\{ \tau(t) < - \frac{\epsilon^2 + t}{2} \right\}
+        \\ & \le
+        C \exp\left(-\frac{\theta \epsilon^2}{2} \right) .
+    \end{align*}
+
+    For the third term, we will first collect some facts.
+    Observe that on this event,
+    $\epsilon^2 + t + \tau(t)$ is in the interval
+    $((\epsilon^2 + t)/ 2, (A + 1)(\epsilon^2 + t))$,
+    and for any $s$ in this interval,
+    \begin{align}
+        p_{2s}(y)
+        &\le \nonumber
+        \left( \frac{
+            2 (\epsilon^2 + t)(A + 1)
+        }{
+            \epsilon^2 + t
+        } \right)^{d/2}
+        p_{2(A+1)(\epsilon^2 + t)}(x, y)
+        \\ &= \label{eqn:p_bounded_on_interval}
+        (2(A+1))^{d/2}
+        p_{2(A+1)(\epsilon^2 + t)}(x, y) .
+    \end{align}
+    Moreover, since $u e^{-u} \le e^{-1}$ for all $u \ge 0$,
+    \begin{align}
+        \frac{\|x - y\|^2}{s} p_s(x, y)
+        &= \nonumber
+        \frac{4}{(2 \pi s)^{d/2}}
+        e^{- \frac{ \|x-y\|^2 }{ 4s }}
+        \frac{\|x-y\|^2}{4s}
+        e^{- \frac{ \|x-y\|^2 }{ 4s }}
+        \\ &\le \label{eqn:p_deriv_term2}
+        C p_{2s}(x, y) .
+    \end{align}
+    Now, by the Intermediate Value Theorem,
+    \begin{align*}
+        \left|
+            p_{\epsilon^2 + t + \tau(t)}(x, y)
+            -
+            p_{\epsilon^2 + t}(x, y)
+        \right|
+        &=
+        \left| \tau(t) \right|
+        \left| \frac{\partial p_s(x, y)}{\partial s} \right|
+    \end{align*}
+    for some $s$ between $\epsilon^2 + t + \tau(t)$ and $\epsilon^2 + t$.
+    Now,
+    \begin{align*}
+        \frac{\partial}{\partial s} p_s(x, y)
+        &=
+        \frac{\partial}{\partial s}
+        \left(
+            \frac{1}{(2 \pi s)^{d/2}}
+            \exp\left( - \frac{\|x - y\|^2}{2 s} \right)
+        \right)
+        \\ &=
+        - \frac{d}{2s} p_s(x, y) + \frac{\|x - y\|^2}{2 s^2} p_s(x, y)  .
+    \end{align*}
+    Applying the inequality~\eqref{eqn:p_deriv_term2},
+    using the fact that $p_s(x, y) \le C p_{2s}(x,y)$,
+    and then \eqref{eqn:p_bounded_on_interval},
+    we have that for any $s \in ((\epsilon^2 + t)/ 2, (A + 1)(\epsilon^2 + t))$,
+    \begin{align*}
+        \left| \frac{\partial}{\partial s} p_s(x, y) \right|
+        \le
+        \frac{C}{s} p_{2s}(x, y) 
+        \le
+        \frac{C}{\epsilon^2 + t} p_{2(A + 1)(\epsilon^2 + t)}(x, y) .
+    \end{align*}
+    Therefore, recalling that $\IE[\tau(t)^2] = t / \theta$,
+    \begin{align*}
+        \IE\left[
+            1_{A_3}
+            \left|
+                p_{\epsilon^2 + t + \tau(t)}(x, y)
+                -
+                p_{\epsilon^2 + t}(x, y)
+            \right|
+        \right]
+        &\le
+            \frac{C}{\epsilon^2 + t}
+                p_{2(A + 1)(\epsilon^2 + t)}(x, y)
+            \IE\left[|\tau(t)|\right]
+        \\ &\le
+            \frac{C}{\epsilon^2 + t}
+                p_{2(A + 1)(\epsilon^2 + t)}(x, y)
+            \IE\left[\tau(t)^2\right]^{1/2}
+        \\ &=
+            \left( \frac{Ct}{\theta(\epsilon^2 + t)^2} \right)^{1/2}
+                p_{2(A + 1)(\epsilon^2 + t)}(x, y)
+        \\ &\le
+            \frac{C}{\sqrt{\theta \epsilon^2}}
+                p_{2(A + 1)(\epsilon^2 + t)}(x, y) ,
+    \end{align*}
+    where the last inequality follows from $2 \epsilon^2 t \le (\epsilon^2 + t)^2$.
+\end{proof}
+
+\begin{lemma}
+    OLD VERSION, IS WRONG
+For every $x,y \in \IR^d$ and $t>0$ we have,
 \begin{align*}
@@
 for some $s \in (\epsilon^2+t-|\tau(t)|, \epsilon^2+t+|\tau(t)|)$. Without loss of generality we suppose $x=0$ and write $p_s(y):=p_s(0,y)$ to simplify notation. Then,
-\[ \frac{\partial}{\partial s} \frac{1}{(2 \pi s)^{d/2}} \exp(-\frac{\Vert y \Vert^2}{2s}) = - \frac{d}{s} p_s(y) + \frac{y^2}{2 s^2} p_s(y)\]
+\[ \frac{\partial}{\partial s} \frac{1}{(2 \pi s)^{d/2}} \exp(-\frac{\| y \|^2}{2s}) = - \frac{d}{s} p_s(y) + \frac{y^2}{2 s^2} p_s(y)\]
 Now for $s \in ((\epsilon^2+t)/2,3(\epsilon^2+t)/2)$ we have,
@@
 \begin{lemma}
-Let $s>0, x, y, z\in \mathbb{R}^d$. The following estimate holds
+Let $s>0, x, y, z\in \IR^d$. The following estimate holds
 \[ |p_s(x,z) - p_s(y,z)| \leq \frac{C|x-y|}{\sqrt{s}} \left(p_{2s}(x,z) + p_{2s}(y,z)\right) \]
@@
 \paragraph{The martingale problem for a time dependent function.}
-Before proceeding we make the following observation. For any time, dependent function $\phi_t(x)$ the martingale problem for $\overline{\eta}_t$, (\ref{mgp1}), gives that
+Before proceeding we make the following observation. For any time, dependent function $\phi_t(x)$ the martingale problem for $\eta_t$, (\ref{mgp1}), gives that
 \comment{Alison says: not sure this needs spelling out? (Also, $\partial_t \phi_{t-s}$ is a slightly confusing way to write it out but OK.}
 \begin{align}
-\langle \overline{\eta}_t(dx), \phi_0(x)\rangle &= \langle \overline{\eta}_0(dx), \phi_t(x)\rangle +  M_t(\phi_\cdot(\cdot)) - \int_0^t \langle \partial_t \phi_{t-s}(x), \overline{\eta}_s(dx) \rangle  ds \nonumber \\ & + \int_0^t \langle \mathcal{L}^\theta \phi_{t-s}(x), \overline{\eta}_s(dx) \rangle ds+ \int_{0}^t \langle \phi_{t-s}(x)F (\rho_\epsilon*\overline{\eta}_s)(x) ) , \overline{\eta}_s(dx) \rangle ds \label{timeMGP}
+\langle \eta_t(dx), \phi_0(x)\rangle &= \langle \eta_0(dx), \phi_t(x)\rangle +  M_t(\phi_\cdot(\cdot)) - \int_0^t \langle \partial_t \phi_{t-s}(x), \eta_s(dx) \rangle  ds \nonumber \\ & + \int_0^t \langle \mathcal{L}^\theta \phi_{t-s}(x), \eta_s(dx) \rangle ds+ \int_{0}^t \langle \phi_{t-s}(x)F (\rho_\epsilon*\eta_s)(x) ) , \eta_s(dx) \rangle ds \label{timeMGP}
 \end{align}
 where $M_t(\phi_\cdot(\cdot))$ has quadratic variation:
-\[ [M(\phi_\cdot(\cdot))]_t = \frac{\theta}{N}\int_0^t \langle \int_{\mathbb{R}^d} \phi_{t-s}(z)^2 q_\theta(y,dz) + \left( 1 + \frac{F(\rho_\epsilon*\overline{\eta}_s(y))}{\theta}\right) \phi_{t-s}(y)^2, \overline{\eta}_s(dy) \rangle ds \]
+\[ [M(\phi_\cdot(\cdot))]_t = \frac{\theta}{N}\int_0^t \langle \int_{\IR^d} \phi_{t-s}(z)^2 q_\theta(y,dz) + \left( 1 + \frac{F(\rho_\epsilon*\eta_s(y))}{\theta}\right) \phi_{t-s}(y)^2, \eta_s(dy) \rangle ds \]
 
@@
 
-\paragraph{Bounds for $\{ \rho_\epsilon * \overline{\eta}_s (x)\}_{0 \leq s \leq T}$}
+\paragraph{Bounds for $\{ \rho_\epsilon * \eta_s (x)\}_{0 \leq s \leq T}$}
 \begin{lemma} \label{FirstBoundLocalDensity}
 Under the conditions of Theorem~\ref{TeoremOneStepConvergence} there is a constant $C>0$ (independent of $\epsilon, N, \theta, x$ and $T$) such that,
-\[ \IE[ \rho_\epsilon*\overline{\eta}_t(x) ] < C \]
-for all $t \in [0,T]$ and $x \in \mathbb{R}^d$.
+\[ \IE[ \rho_\epsilon*\eta_t(x) ] < C \]
+for all $t \in [0,T]$ and $x \in \IR^d$.
 \end{lemma}
@@
 \begin{align}
-(\rho_\epsilon*\overline{\eta}_t(x)) = \langle \psi_t^{\epsilon,x}(y), \overline{\eta}_0(dy) \rangle  + \int_0^t \langle \psi_{t-s}^{\epsilon,x}(y) F(\rho_\epsilon*\overline{\eta}_s(y)), \overline{\eta}_s(dy) \rangle ds + M_t(x) \label{MartingaleProblemMolifier}
+(\rho_\epsilon*\eta_t(x)) = \langle \psi_t^{\epsilon,x}(y), \eta_0(dy) \rangle  + \int_0^t \langle \psi_{t-s}^{\epsilon,x}(y) F(\rho_\epsilon*\eta_s(y)), \eta_s(dy) \rangle ds + M_t(x) \label{MartingaleProblemMolifier}
 \end{align}
@@
 \begin{align}
-\IE[\rho_\epsilon * \overline{\eta}_t(x)]
+\IE[\rho_\epsilon * \eta_t(x)]
     &\le
-    \IE[\langle \psi_t^{\epsilon,x}(y), \overline{\eta}_0(dy) \rangle] + C \IE[\int_0^t \langle \psi_{t-s}^{\epsilon,x}(y), \overline{\eta}_s(dy) \rangle ds] \nonumber \\ & \leq  \IE[\langle p_{\epsilon^2+T(t)}(x,y),\overline{\eta}_0(dy)\rangle] + C \int_0^t \Vert \psi_{t-s}^{\epsilon,0} \Vert_\infty \IE[\sup_{0 \leq s \leq t} \langle 1, \overline{\eta}_s(dy) \rangle] ds \\ & \leq C + C \int_0^t \Vert \psi_{t-s}^{\epsilon,0} \Vert_\infty ds \label{BoundForMolifier}
+    \IE[\langle \psi_t^{\epsilon,x}(y), \eta_0(dy) \rangle] + C \IE[\int_0^t \langle \psi_{t-s}^{\epsilon,x}(y), \eta_s(dy) \rangle ds] \nonumber \\ & \leq  \IE[\langle p_{\epsilon^2+T(t)}(x,y),\eta_0(dy)\rangle] + C \int_0^t \Vert \psi_{t-s}^{\epsilon,0} \Vert_\infty \IE[\sup_{0 \leq s \leq t} \langle 1, \eta_s(dy) \rangle] ds \\ & \leq C + C \int_0^t \Vert \psi_{t-s}^{\epsilon,0} \Vert_\infty ds \label{BoundForMolifier}
 \end{align}
@@
 \begin{equation} \label{IterationBoundPsi}
-\IE[\langle \psi_{t-s}^{\epsilon,x}, \overline{\eta}_s(dy)\rangle] \leq \IE[\langle \psi_{t}^{\epsilon,x}(y), \overline{\eta}_0(dy) \rangle]  + C \int_0^s \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du
+\IE[\langle \psi_{t-s}^{\epsilon,x}, \eta_s(dy)\rangle] \leq \IE[\langle \psi_{t}^{\epsilon,x}(y), \eta_0(dy) \rangle]  + C \int_0^s \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du
 \end{equation}
@@
 \begin{align*}
-\IE[ \rho_\epsilon * \overline{\eta}_t(x)  ] &\leq \IE[\langle \psi_t^{\epsilon,x}(y), \overline{\eta}_0(dy) \rangle] + \int_0^t C\langle \psi_{t}^{\epsilon,x}, \overline{\eta}_0(dy)\rangle ds + C^2 \int_0^t \int_0^s  \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du ds \\ &= (1+Ct) \IE[ \langle \psi_t^{\epsilon,x}, \overline{\eta}_0(dy) \rangle] + C^2 \int_0^t (t-u) \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du \\ &\leq C(1+t) + C^2 \int_0^t (t-u) \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du
+\IE[ \rho_\epsilon * \eta_t(x)  ] &\leq \IE[\langle \psi_t^{\epsilon,x}(y), \eta_0(dy) \rangle] + \int_0^t C\langle \psi_{t}^{\epsilon,x}, \eta_0(dy)\rangle ds + C^2 \int_0^t \int_0^s  \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du ds \\ &= (1+Ct) \IE[ \langle \psi_t^{\epsilon,x}, \eta_0(dy) \rangle] + C^2 \int_0^t (t-u) \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du \\ &\leq C(1+t) + C^2 \int_0^t (t-u) \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du
 \end{align*}
@@
 \begin{remark} \label{Remark:BoundLocalDensity}
-It is convenient to remark that from $\IE\left[ \langle \rho_\epsilon(x,y), \overline{\eta}_t(dy) \rangle \right]$ being bounded it follows that $\IE[ \langle p_{s+\epsilon^2}(x,y), \overline{\eta}_t(dy) \rangle ]$ is bounded for all $s>0$.
+It is convenient to remark that from $\IE\left[ \langle \rho_\epsilon(x,y), \eta_t(dy) \rangle \right]$ being bounded it follows that $\IE[ \langle p_{s+\epsilon^2}(x,y), \eta_t(dy) \rangle ]$ is bounded for all $s>0$.
 Indeed, this follows from writing $p_{s+\epsilon^2} = p_s * p_{\epsilon^2}$ and integrating.
@@
 We can explicitly write the quadratic variation of $M_t$ as
-\[ [M(x)]_t = \frac{\theta}{N} \int_0^t \langle \int_{\mathbb{R}^d} \psi_{t-s}^{\epsilon,x}(z)^2 q_\theta(y,dz) + \left(1+\frac{F(\rho_\epsilon * \overline{\eta}_s(y))}{\theta}\right)\psi_{t-s}^{\epsilon,x}(y)^2, \overline{\eta}_s(dy) \rangle  ds\]
+\[ [M(x)]_t = \frac{\theta}{N} \int_0^t \langle \int_{\IR^d} \psi_{t-s}^{\epsilon,x}(z)^2 q_\theta(y,dz) + \left(1+\frac{F(\rho_\epsilon * \eta_s(y))}{\theta}\right)\psi_{t-s}^{\epsilon,x}(y)^2, \eta_s(dy) \rangle  ds\]
 so Lemma~\ref{PsiBoundHS} gives the following bound,
@@
 \begin{align}
-[M(x)]_t &\leq \frac{C \theta}{\epsilon^d N} \int_0^t \left\{  \langle \int \psi_{t-s}^{\epsilon,x}(z) q_\theta(y,dz), \overline{\eta}_s(dy) \rangle + \langle \psi_{t-s}^{\epsilon,x}(y), \overline{\eta}_s(dy)\rangle \right\} ds
+[M(x)]_t &\leq \frac{C \theta}{\epsilon^d N} \int_0^t \left\{  \langle \int \psi_{t-s}^{\epsilon,x}(z) q_\theta(y,dz), \eta_s(dy) \rangle + \langle \psi_{t-s}^{\epsilon,x}(y), \eta_s(dy)\rangle \right\} ds
 \label{QuadVarBound} \end{align}
@@
 \begin{align*}
-\int &\IE\left[ M_t(x)^2 \right] dx \\ & \leq \frac{C \theta}{\varepsilon^d N} \int \int_0^t \IE\left[ \langle \int \psi_{t-s}^{\epsilon,x}(z) q_\theta(y,dz), \overline{\eta}_s(dy) \rangle + \langle \psi_{t-s}^{\epsilon,x}(y), \overline{\eta}_s(dy)\rangle \right] ds  dx \\ &=  \frac{C \theta}{\varepsilon^d N}  \int_0^t \IE \left[  \langle \int \left( \int \psi_{t-s}^{\epsilon,x}(z) dx \right) q_\theta(y,dz), \overline{\eta}_s(dy) \rangle + \langle \left( \int  \psi_{t-s}^{\epsilon,x}(y) dx \right), \overline{\eta}_s(dy)\rangle \right] ds.
+\int &\IE\left[ M_t(x)^2 \right] dx \\ & \leq \frac{C \theta}{\varepsilon^d N} \int \int_0^t \IE\left[ \langle \int \psi_{t-s}^{\epsilon,x}(z) q_\theta(y,dz), \eta_s(dy) \rangle + \langle \psi_{t-s}^{\epsilon,x}(y), \eta_s(dy)\rangle \right] ds  dx \\ &=  \frac{C \theta}{\varepsilon^d N}  \int_0^t \IE \left[  \langle \int \left( \int \psi_{t-s}^{\epsilon,x}(z) dx \right) q_\theta(y,dz), \eta_s(dy) \rangle + \langle \left( \int  \psi_{t-s}^{\epsilon,x}(y) dx \right), \eta_s(dy)\rangle \right] ds.
 \end{align*}
@@
 \begin{align*}
-\int \IE\left[ M_t(x)^2 \right] dx & \leq  \frac{C \theta}{\varepsilon^d N}  \int_0^t \IE \left[  \langle \int  q_\theta(y,dz), \overline{\eta}_s(dy) \rangle + \langle 1, \overline{\eta}_s(dy)\rangle \right] ds.
-\\ & \leq \frac{C \theta}{\varepsilon^d N} \int_0^t \IE[ \langle 1, \overline{\eta}_s(dy) \rangle ] ds \\ & \leq T \frac{C \theta}{ \varepsilon^d N}
+\int \IE\left[ M_t(x)^2 \right] dx & \leq  \frac{C \theta}{\varepsilon^d N}  \int_0^t \IE \left[  \langle \int  q_\theta(y,dz), \eta_s(dy) \rangle + \langle 1, \eta_s(dy)\rangle \right] ds.
+\\ & \leq \frac{C \theta}{\varepsilon^d N} \int_0^t \IE[ \langle 1, \eta_s(dy) \rangle ] ds \\ & \leq T \frac{C \theta}{ \varepsilon^d N}
 \end{align*}
@@
 \begin{proposition}
-Under the assumptions of Theorem~\ref{TeoremOneStepConvergence} there is a finite constant $C$ (independent of $\epsilon, N, \theta$) such that, for all $t \in [0,T]$, $x \in \mathbb{R}^d$ and for big enough $N$ and $\theta$, $\IE[ (\rho_\epsilon*\overline{\eta}_t(x))^2] \leq C$.\label{Prop:SecondMomentDensity}
+Under the assumptions of Theorem~\ref{TeoremOneStepConvergence} there is a finite constant $C$ (independent of $\epsilon, N, \theta$) such that, for all $t \in [0,T]$, $x \in \IR^d$ and for big enough $N$ and $\theta$, $\IE[ (\rho_\epsilon*\eta_t(x))^2] \leq C$.\label{Prop:SecondMomentDensity}
 \end{proposition}
 
-\paragraph{$C$-tightness of $\rho_\epsilon * \overline{\eta}_t(x) dx$ }
+\paragraph{$C$-tightness of $\rho_\epsilon * \eta_t(x) dx$ }
 \begin{lemma}
-Under the assumptions of Theorem~\ref{TeoremOneStepConvergence} the sequence of measure valued process $\{ \rho*\overline{\eta}_t(x) dx \}_{t \geq 0}$ (taking values in $D([0,T], \mathcal{M}_F(\mathbb{R}^d))$ is $C$-tight.
+Under the assumptions of Theorem~\ref{TeoremOneStepConvergence} the sequence of measure valued process $\{ \rho*\eta_t(x) dx \}_{t \geq 0}$ (taking values in $D([0,T], \mathcal{M}_F(\IR^d))$ is $C$-tight.
 \end{lemma}
@@
 Let $f \in C_c^2$ (that is, compactly supported and with smooth second derivative).
-We will show convergence of $\int f(x) \rho_\epsilon * \overline{\eta}_t(x) dx$ (which is enough to establish weak convergence of the measures $\rho_\epsilon * \overline{\eta}_t(x) dx$).
+We will show convergence of $\int f(x) \rho_\epsilon * \eta_t(x) dx$ (which is enough to establish weak convergence of the measures $\rho_\epsilon * \eta_t(x) dx$).
 \comment{Alison writes: no it's not weak - this would be vague convergence. Take $f \in C^2$ to mean bounded first and second derivatives, which is weak convergence.}
@@
 \begin{align*}
-\int f(x) \rho_\epsilon * \overline{\eta}_t(x) dx &= \int \int f(x) \rho_\epsilon (x-y) \overline{\eta}(dy) dx \\ & = \langle \int f(x) \rho_\epsilon(x-y) dx, \overline{\eta}(dy) \rangle \\ &= \langle T_{\epsilon^2} f(y), \overline{\eta}_t(dy) \rangle
-\end{align*}
-where $T_t$ denotes the heat semigroup. Substituting this into the martingale problem for $\overline{\eta}_t$, (\ref{mgp1}), we get,
+\int f(x) \rho_\epsilon * \eta_t(x) dx &= \int \int f(x) \rho_\epsilon (x-y) \eta(dy) dx \\ & = \langle \int f(x) \rho_\epsilon(x-y) dx, \eta(dy) \rangle \\ &= \langle T_{\epsilon^2} f(y), \eta_t(dy) \rangle
+\end{align*}
+where $T_t$ denotes the heat semigroup. Substituting this into the martingale problem for $\eta_t$, (\ref{mgp1}), we get,
 \begin{align}
-\langle T_{\epsilon^2} f(y), \overline{\eta}_t(dy) \rangle & = \langle T_{\epsilon^2}
- f(y), \overline{\eta}_0(dy) \rangle + \theta \int_0^t \langle \int (T_{\epsilon^2} f(z) - T_{\epsilon^2} f(y))q_\theta(y,z)dz, \overline{\eta}_s(dy)\rangle ds \nonumber \\ &+\int_0^t \langle T_{\epsilon^2} f(y) F(\rho_\epsilon*\overline{\eta}_s(y)), \overline{\eta}_s(dy) \rangle ds + \widehat{M}_t \label{MGPT_epsilon} \end{align}
+\langle T_{\epsilon^2} f(y), \eta_t(dy) \rangle & = \langle T_{\epsilon^2}
+ f(y), \eta_0(dy) \rangle + \theta \int_0^t \langle \int (T_{\epsilon^2} f(z) - T_{\epsilon^2} f(y))q_\theta(y,z)dz, \eta_s(dy)\rangle ds \nonumber \\ &+\int_0^t \langle T_{\epsilon^2} f(y) F(\rho_\epsilon*\eta_s(y)), \eta_s(dy) \rangle ds + \widehat{M}_t \label{MGPT_epsilon} \end{align}
  with $\widehat{M}_t$ a martingale. Now note that,
@@
 Proceeding as in the proof of Lemma~\ref{Lemma:UniformlyBoundedMass}, we can use that $F(x)1_{x > 0}$ is bounded above and Gronwall's inequality to conclude that,
-\[ \IE\left[\langle T_{\epsilon^2} f(y), \overline{\eta}_t(dy) \rangle \right] \text{ is uniformly bounded for } t \in [0,T].\]
+\[ \IE\left[\langle T_{\epsilon^2} f(y), \eta_t(dy) \rangle \right] \text{ is uniformly bounded for } t \in [0,T].\]
 The quadratic variation of $\widehat{M}_t$ is;
-\[ [ \widehat{M}]_t = \frac{\theta}{N}\int_0^t \langle T_{1/\theta}(T_{\epsilon^2}f(\cdot)^2)(y) + \left(1+\frac{F(\rho_\epsilon*\overline{\eta}_s(y))}{\theta}\right)T_{\epsilon^2}f(y)^2, \overline{\eta}_s(dy) \rangle ds \]
+\[ [ \widehat{M}]_t = \frac{\theta}{N}\int_0^t \langle T_{1/\theta}(T_{\epsilon^2}f(\cdot)^2)(y) + \left(1+\frac{F(\rho_\epsilon*\eta_s(y))}{\theta}\right)T_{\epsilon^2}f(y)^2, \eta_s(dy) \rangle ds \]
 And so, using boundedness of $f$ and $F$,
 \begin{align*}
-\IE\left[ [\widehat{M}]_t \right] \leq \frac{\theta}{N} \Vert f \Vert_\infty C \int_0^t \mathbb{E}\left[ \langle 1, \overline{\eta}_s(dy) \right] ds < \frac{\theta}{N} t C
+\IE\left[ [\widehat{M}]_t \right] \leq \frac{\theta}{N} \Vert f \Vert_\infty C \int_0^t \mathbb{E}\left[ \langle 1, \eta_s(dy) \right] ds < \frac{\theta}{N} t C
 \end{align*}
@@
 Therefore, by taking supremum and expectation and in (\ref{MGPT_epsilon}) we conclude that
-\begin{equation} \IE[\sup_{0 \leq t \leq T} \langle T_{\epsilon^2} f, \overline{\eta}_t \rangle ] \text{ is uniformly bounded (for fixed } f \text{)} \label{eq:boundedIntegralAgainstf} \end{equation}
+\begin{equation} \IE[\sup_{0 \leq t \leq T} \langle T_{\epsilon^2} f, \eta_t \rangle ] \text{ is uniformly bounded (for fixed } f \text{)} \label{eq:boundedIntegralAgainstf} \end{equation}
 To conclude $C$-tightness we show that, for $T>0$, $\alpha > 0$ there is some $\delta >0$ so that for $\theta$ and $N$ large enough,
 \begin{align}
-&\IP\left[ \sup_{u,v \in [0,T], |u-v| < \delta} \left| \int f, \rho_\epsilon*\overline{\eta}_u(x) dx   - \int f, \rho_\epsilon*\overline{\eta}_v(x) dx \right|  > \alpha \right]
+&\IP\left[ \sup_{u,v \in [0,T], |u-v| < \delta} \left| \int f, \rho_\epsilon*\eta_u(x) dx   - \int f, \rho_\epsilon*\eta_v(x) dx \right|  > \alpha \right]
     \\ &=
-\IP\left[ \sup_{u,v \in [0,T], |u-v| < \delta} | \langle T_{\epsilon^2} f, \overline{\eta}_u \rangle - \langle T_{\epsilon^2} f,\overline{\eta}_v \rangle > \alpha \right]
+\IP\left[ \sup_{u,v \in [0,T], |u-v| < \delta} | \langle T_{\epsilon^2} f, \eta_u \rangle - \langle T_{\epsilon^2} f,\eta_v \rangle > \alpha \right]
     <
@@
 \begin{align*}
-|\langle T_{\epsilon^2} f, \overline{\eta}_u \rangle - \langle T_{\epsilon^2} f,\overline{\eta}_v \rangle|  \leq ( \Vert \Delta f \Vert_\infty + C_F||f||_\infty) |u-v| \sup_{0 \leq s \leq T } \langle 1, \overline{\eta}_s \rangle + \sup_{s \leq T}|\widehat{M}_s|
+|\langle T_{\epsilon^2} f, \eta_u \rangle - \langle T_{\epsilon^2} f,\eta_v \rangle|  \leq ( \Vert \Delta f \Vert_\infty + C_F||f||_\infty) |u-v| \sup_{0 \leq s \leq T } \langle 1, \eta_s \rangle + \sup_{s \leq T}|\widehat{M}_s|
 \end{align*}
@@
 \begin{equation}
-\IE\left[ |\langle T_{\epsilon^2} f, \overline{\eta}_u \rangle - \langle T_{\epsilon^2} f,\overline{\eta}_v \rangle|\right] \leq \widehat{C} |u-v| + \frac{\widehat{C}\theta}{N}\end{equation}
+\IE\left[ |\langle T_{\epsilon^2} f, \eta_u \rangle - \langle T_{\epsilon^2} f,\eta_v \rangle|\right] \leq \widehat{C} |u-v| + \frac{\widehat{C}\theta}{N}\end{equation}
 Using this and Markov's inequality give that (\ref{conditionCtightness}) holds with $\delta = \alpha/(3 \widehat{C}|u-v|)$, for $N,\theta$ big enough so $\widehat{C}\theta/N$ is bounded by $\alpha/3$ (Note the last condition is possible by (\ref{ConditionsForConvergence})).
@@
 Similar as we got equation (\ref{eq:boundedIntegralAgainstf}), from equation \ref{MGPT_epsilon} we can conclude that
-\[ \IE\left[\sup_{0 \leq t \leq T} \int \rho_{\epsilon/2} * \overline{\eta}_t(x) dx \right] = C < \infty. \]
+\[ \IE\left[\sup_{0 \leq t \leq T} \int \rho_{\epsilon/2} * \eta_t(x) dx \right] = C < \infty. \]
 By using this and the same pattern used to prove Proposition~\ref{Prop:SecondMomentMass}, we can then conclude that,
-\[ \IE\left[  \sup_{0 \leq t \leq T} \int \left(\rho_{\epsilon/2} * \overline{\eta}_t(x) \right)^2 dx \right] = C < \infty. \]
+\[ \IE\left[  \sup_{0 \leq t \leq T} \int \left(\rho_{\epsilon/2} * \eta_t(x) \right)^2 dx \right] = C < \infty. \]
 Since,
 \begin{align*}
-\langle \rho_\epsilon * \overline{\eta}_t(z), \overline{\eta}(dz) \rangle & = \sum_{y \in \overline{\eta}_t} \sum_{z \in \overline{\eta}_t} \rho_\epsilon(y-z) \overline{\eta}(z) \overline{\eta}(y) \\ &= \int  \sum_{y \in \overline{\eta}_t} \sum_{z \in \overline{\eta}_t} \rho_{\epsilon/2}(y-x) \rho_{\epsilon/2}(z-x) \overline{\eta}(z) \overline{\eta}(y) \\ &= \int (\rho_{\epsilon/2}*\overline{\eta}_t(x))^2 dx.
-\end{align*}
-This allows us to conclude that $\IE[\langle \rho_\epsilon*\overline{\eta}_t(z),\overline{\eta}_t(dz) \rangle ] < \infty$. This bound will be useful in the next section.
+\langle \rho_\epsilon * \eta_t(z), \eta(dz) \rangle & = \sum_{y \in \eta_t} \sum_{z \in \eta_t} \rho_\epsilon(y-z) \eta(z) \eta(y) \\ &= \int  \sum_{y \in \eta_t} \sum_{z \in \eta_t} \rho_{\epsilon/2}(y-x) \rho_{\epsilon/2}(z-x) \eta(z) \eta(y) \\ &= \int (\rho_{\epsilon/2}*\eta_t(x))^2 dx.
+\end{align*}
+This allows us to conclude that $\IE[\langle \rho_\epsilon*\eta_t(z),\eta_t(dz) \rangle ] < \infty$. This bound will be useful in the next section.
 \end{remark}
@@
 
-In this section we prove the following continuity estimate for $\rho_\epsilon * \overline{\eta}_t(x)$.
+In this section we prove the following continuity estimate for $\rho_\epsilon * \eta_t(x)$.
 \begin{proposition} \label{ContinuityEstimate}
-Under the same conditions of Theorem~\ref{TeoremOneStepConvergence} we have that for all $x \in \mathbb{R}^d$, $\delta>0$,
+Under the same conditions of Theorem~\ref{TeoremOneStepConvergence} we have that for all $x \in \IR^d$, $\delta>0$,
 \[
-\int |\rho_\epsilon*\overline{\eta}_s(x) -\rho_\epsilon*\overline{\eta}_s(y)| \rho_\delta(x-y) dy \]
+\int |\rho_\epsilon*\eta_s(x) -\rho_\epsilon*\eta_s(y)| \rho_\delta(x-y) dy \]
 is bounded by
 \begin{align*}
-\frac{\delta}{\sqrt{\epsilon^2+s}} \langle 1,\overline{\eta}_0(dz) \rangle &+ \int_0^s \frac{\delta}{\sqrt{\epsilon^2+s-r}} (\langle 1, \overline{\eta}_r(dz)\rangle + \langle \rho_\epsilon*\overline{\eta}_r(z), \overline{\eta}_r(dz)\rangle)dr \\ &+ |M_s(x)| + \int |M_s(y)| \rho_\delta(y-x)dy + \mathcal{O}\left( \frac{1}{\epsilon^2 \theta}\right)
+\frac{\delta}{\sqrt{\epsilon^2+s}} \langle 1,\eta_0(dz) \rangle &+ \int_0^s \frac{\delta}{\sqrt{\epsilon^2+s-r}} (\langle 1, \eta_r(dz)\rangle + \langle \rho_\epsilon*\eta_r(z), \eta_r(dz)\rangle)dr \\ &+ |M_s(x)| + \int |M_s(y)| \rho_\delta(y-x)dy + \mathcal{O}\left( \frac{1}{\epsilon^2 \theta}\right)
 \end{align*} 
@@
 \begin{align} \label{StrongBoundOnF}
-|F(\rho_\epsilon*\overline{\eta}_t(x))| \leq |F(0)| + C \rho_\epsilon*\overline{\eta}_t(x)
+|F(\rho_\epsilon*\eta_t(x))| \leq |F(0)| + C \rho_\epsilon*\eta_t(x)
 \end{align}
@@
 \begin{align}
-& |\rho_\epsilon*\overline{\eta}_t(x)-\rho_\epsilon*\overline{\eta}_t(y)| \nonumber \\ &= |\langle \rho_\epsilon(y-z)-\rho_\epsilon(x-z),\overline{\eta}_t(dz) \rangle | \nonumber\\ &\leq  |M_t(x)-M_t(y)|  +\langle \psi_t^{\epsilon,y}(z)-\psi_t^{\epsilon,x}(z), \overline{\eta}_0(dz)\rangle \nonumber \\ &+ C\int_0^t \langle |\psi_{t-s}^{\epsilon,x}(z) - \psi_{t-s}^{\epsilon, y}(z) |, \overline{\eta}_s(dz) \rangle  ds | \\ &+ C \int_0^t \langle |\psi_{t-s}^{\epsilon,x}(z) - \psi_{t-s}^{\epsilon, y}(z) | \rho_\epsilon*\overline{\eta}(z), \overline{\eta}_s(dz) \rangle  ds | \label{eq:bound1CE} \end{align}
+& |\rho_\epsilon*\eta_t(x)-\rho_\epsilon*\eta_t(y)| \nonumber \\ &= |\langle \rho_\epsilon(y-z)-\rho_\epsilon(x-z),\eta_t(dz) \rangle | \nonumber\\ &\leq  |M_t(x)-M_t(y)|  +\langle \psi_t^{\epsilon,y}(z)-\psi_t^{\epsilon,x}(z), \eta_0(dz)\rangle \nonumber \\ &+ C\int_0^t \langle |\psi_{t-s}^{\epsilon,x}(z) - \psi_{t-s}^{\epsilon, y}(z) |, \eta_s(dz) \rangle  ds | \\ &+ C \int_0^t \langle |\psi_{t-s}^{\epsilon,x}(z) - \psi_{t-s}^{\epsilon, y}(z) | \rho_\epsilon*\eta(z), \eta_s(dz) \rangle  ds | \label{eq:bound1CE} \end{align}
 By using Lemma~\ref{Lemma:BoundPsiHS2} we can then write, 
 \begin{align*}
- \int &|\rho_\epsilon*\overline{\eta}_s(x) -\rho_\epsilon*\overline{\eta}_s(y)| \rho_\delta(x-y) dy  \leq \int |p_{\epsilon^2+s}(y,z)-p_{\epsilon^2+s}(x,z)|\overline{\eta}_0(dz) \rho_\delta(x-y)dy \\&+ C\int_0^s \langle p_{\epsilon^2+s-r}(y,z)-p_{\epsilon^2+s-r}(x,z)|, \overline{\eta}_r(dz) \rangle \rho_\delta (x-y) dr  \\  & + C \int_0^s \langle |p_{\epsilon+s-r}(y,z) - p_{\epsilon+s-r}(x,z) | \rho_\epsilon*\overline{\eta}_r(z), \overline{\eta}_r(dz) \rangle  dr | + \int|M_s(y)-M_s(x)| \rho_\delta(y-x)dy  \\  & + \frac{C}{\epsilon^2 \theta} \int \langle \rho_\epsilon*\overline{\eta}(z),\overline{\eta}_s(dz)\rangle ds   +\mathcal{O}\left( \frac{1}{\epsilon^2 \theta} \right)
+ \int &|\rho_\epsilon*\eta_s(x) -\rho_\epsilon*\eta_s(y)| \rho_\delta(x-y) dy  \leq \int |p_{\epsilon^2+s}(y,z)-p_{\epsilon^2+s}(x,z)|\eta_0(dz) \rho_\delta(x-y)dy \\&+ C\int_0^s \langle p_{\epsilon^2+s-r}(y,z)-p_{\epsilon^2+s-r}(x,z)|, \eta_r(dz) \rangle \rho_\delta (x-y) dr  \\  & + C \int_0^s \langle |p_{\epsilon+s-r}(y,z) - p_{\epsilon+s-r}(x,z) | \rho_\epsilon*\eta_r(z), \eta_r(dz) \rangle  dr | + \int|M_s(y)-M_s(x)| \rho_\delta(y-x)dy  \\  & + \frac{C}{\epsilon^2 \theta} \int \langle \rho_\epsilon*\eta(z),\eta_s(dz)\rangle ds   +\mathcal{O}\left( \frac{1}{\epsilon^2 \theta} \right)
 \end{align*}
@@
 \begin{align*}
-\int &\frac{|y-x|}{\sqrt{\epsilon^2+s}} \rho_{\delta}(y-x) dy \langle 1, \overline{\eta}_0(dz)\rangle + \int \int_0^s  \langle \frac{|y-x|}{\sqrt{\sqrt{\epsilon^2+s-r}}}, \overline{\eta}_r(dz) \rangle \rho_\delta(x-y) dy dr \\ & +  \int \int_0^s \langle \frac{|y-x| \rho_\epsilon*\overline{\eta}(z)}{\sqrt{\epsilon^2+s-r}}, \overline{\eta}_r(dz) \rangle \rho_\delta(y-x) dy dr \\ & \leq \frac{\delta}{\sqrt{\epsilon^2+s}} \langle 1, \overline{\eta}_0(dz) \rangle + \int_0^s \frac{\delta}{\sqrt{\epsilon^2+s-r}} (\langle 1, \overline{\eta}_r(dz) \rangle + \langle \rho_\epsilon*\overline{\eta}_r(z), \overline{\eta}_r(dz) \rangle) dr.
+\int &\frac{|y-x|}{\sqrt{\epsilon^2+s}} \rho_{\delta}(y-x) dy \langle 1, \eta_0(dz)\rangle + \int \int_0^s  \langle \frac{|y-x|}{\sqrt{\sqrt{\epsilon^2+s-r}}}, \eta_r(dz) \rangle \rho_\delta(x-y) dy dr \\ & +  \int \int_0^s \langle \frac{|y-x| \rho_\epsilon*\eta(z)}{\sqrt{\epsilon^2+s-r}}, \eta_r(dz) \rangle \rho_\delta(y-x) dy dr \\ & \leq \frac{\delta}{\sqrt{\epsilon^2+s}} \langle 1, \eta_0(dz) \rangle + \int_0^s \frac{\delta}{\sqrt{\epsilon^2+s-r}} (\langle 1, \eta_r(dz) \rangle + \langle \rho_\epsilon*\eta_r(z), \eta_r(dz) \rangle) dr.
 \end{align*}
@@
 
-\paragraph{Identifying the limit of $\langle T_{\epsilon^2} f(y), \overline{\eta}_t (dy) \rangle$.}
+\paragraph{Identifying the limit of $\langle T_{\epsilon^2} f(y), \eta_t (dy) \rangle$.}
 We now prove the identification of the limit.
@@
 \begin{align*}
-\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\overline{\eta}_s(dy)), \overline{\eta}_s(dy) \rangle \sim \langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \overline{\eta}_s(dy)), \rho_\epsilon * \overline{\eta}_s(y) dy \rangle
+\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\eta_s(dy)), \eta_s(dy) \rangle \sim \langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \eta_s(dy)), \rho_\epsilon * \eta_s(y) dy \rangle
 \end{align*}
@@
 \begin{equation*}
-\int_0^t \IE[|\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\overline{\eta}_s(dy)), \overline{\eta}_s(dy) \rangle - \langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \overline{\eta}_s(dy)), \rho_\epsilon * \overline{\eta}_s(y) dy \rangle|]
+\int_0^t \IE[|\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\eta_s(dy)), \eta_s(dy) \rangle - \langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \eta_s(dy)), \rho_\epsilon * \eta_s(y) dy \rangle|]
 \end{equation*}
@@
 \begin{align*}
-    &\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\overline{\eta}_s(dy)), \overline{\eta}_s(dy) \rangle - \langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \overline{\eta}_s(dy)), \rho_\epsilon * \overline{\eta}_s(y) dy \rangle \\ & = \langle \int T_{\epsilon^2} f(y) F(\rho_\epsilon * \overline{\eta}_s(y))\rho_\epsilon(y-w) dy, \overline{\eta}_s(dw)\rangle - \langle T_{\epsilon^2} f(w) F(\rho_\epsilon*\overline{\eta}_s(w)), \overline{\eta}_s(dw) \rangle \\ &= \langle \int \{ T_{\epsilon^2} f(y) F(\rho_\epsilon*\overline{\eta}_s(y))-T_{\epsilon^2}f(w) F(\rho_\epsilon*\overline{\eta}_s(w))\} \rho_\epsilon(w-y)dy, \overline{\eta}_s(dw) \rangle.
+    &\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\eta_s(dy)), \eta_s(dy) \rangle - \langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \eta_s(dy)), \rho_\epsilon * \eta_s(y) dy \rangle \\ & = \langle \int T_{\epsilon^2} f(y) F(\rho_\epsilon * \eta_s(y))\rho_\epsilon(y-w) dy, \eta_s(dw)\rangle - \langle T_{\epsilon^2} f(w) F(\rho_\epsilon*\eta_s(w)), \eta_s(dw) \rangle \\ &= \langle \int \{ T_{\epsilon^2} f(y) F(\rho_\epsilon*\eta_s(y))-T_{\epsilon^2}f(w) F(\rho_\epsilon*\eta_s(w))\} \rho_\epsilon(w-y)dy, \eta_s(dw) \rangle.
 \end{align*}
 Let us denote $I$ the integral against $dy$ in the last expresion, that is 
-\[ I :=  \int \{ T_{\epsilon^2} f(y) F(\rho_\epsilon*\overline{\eta}_s(y))-T_{\epsilon^2}f(w) F(\rho_\epsilon*\overline{\eta}_s(w))\} \rho_\epsilon(w-y)dy \]
+\[ I :=  \int \{ T_{\epsilon^2} f(y) F(\rho_\epsilon*\eta_s(y))-T_{\epsilon^2}f(w) F(\rho_\epsilon*\eta_s(w))\} \rho_\epsilon(w-y)dy \]
 And note that $|I|$ is bounded by
 \begin{align}
-& \int \left\{ |F(\rho_\epsilon*\overline{\eta}_s(y))-F(\rho_\epsilon*\overline{\eta}_s(w))|T_{\epsilon^2}f(y)+F(\rho_\epsilon*\overline{\eta}_s(w))|T_{\epsilon^2}f(y)-T_{\epsilon^2}f(w))|\right\} \rho_{\epsilon}(w-y)dy \nonumber \\ &\leq \int C |\rho_\epsilon*\overline{\eta}_s(y)-\rho_\epsilon*\overline{\eta}_s(w)| \rho_\epsilon(w-y)dy + C \epsilon^2 \Vert \Delta f \Vert_2 \label{FirstBoundCT}
+& \int \left\{ |F(\rho_\epsilon*\eta_s(y))-F(\rho_\epsilon*\eta_s(w))|T_{\epsilon^2}f(y)+F(\rho_\epsilon*\eta_s(w))|T_{\epsilon^2}f(y)-T_{\epsilon^2}f(w))|\right\} \rho_{\epsilon}(w-y)dy \nonumber \\ &\leq \int C |\rho_\epsilon*\eta_s(y)-\rho_\epsilon*\eta_s(w)| \rho_\epsilon(w-y)dy + C \epsilon^2 \Vert \Delta f \Vert_2 \label{FirstBoundCT}
 \end{align}
@@
 \begin{align*}
-A_{t} &:= \left\{ \sup_{0 \leq s \leq t} \langle 1, \overline{\eta}_s(dz) \rangle > \epsilon^{-2/3} \right\}. \end{align*}
+A_{t} &:= \left\{ \sup_{0 \leq s \leq t} \langle 1, \eta_s(dz) \rangle > \epsilon^{-2/3} \right\}. \end{align*}
 Note that, by Markov's inequality and Lemma~\ref{Lemma:UniformlyBoundedMass} the event $A_{t}$ has probability of order $\epsilon^{2/3}$.
@@
 \begin{align}
-&\int_0^t \IE[|\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\overline{\eta}_s(dy)), \overline{\eta}_s(dy) \rangle - \langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \overline{\eta}_s(dy)), \rho_\epsilon * \overline{\eta}_s(y) dy \rangle|] \nonumber \\ &\leq   \int_0^t \IE[ \frac{\epsilon}{\sqrt{\epsilon^2 + s}} \langle 1,\overline{\eta}_0(dz) \rangle \langle 1, \overline{\eta}_s(dz)\rangle ] ds +  \int_0^t \IE[  \int_0^s \frac{\epsilon}{\sqrt{\epsilon^2 + s - r}} \langle 1, \overline{\eta}_r (dz) \rangle dr \langle 1, \overline{\eta}_s(dz) \rangle  ] ds \nonumber\\ & + \int_0^t \IE[   1_{A^c_{t}} \int_0^s \frac{\epsilon}{\sqrt{\epsilon^2 + s - r}} \langle \rho_\epsilon*\overline{\eta}_r(z), \overline{\eta}_r(dz) \rangle dr \langle 1, \overline{\eta}_s(dz) \rangle  ] ds + \int_0^t \IE[\langle |M_s(x)|,\overline{\eta}_s(dx) \rangle] ds \nonumber \\ &+ \int_0^t \int \IE[|M_s(y)|\rho_\epsilon*\overline{\eta}_s(y)] dy ds  +\mathcal{O}\left( \frac{1}{\epsilon^2 \theta} + \epsilon^2 + \epsilon^{1/3} \right)  \label{ThingsToBound}
+&\int_0^t \IE[|\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\eta_s(dy)), \eta_s(dy) \rangle - \langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \eta_s(dy)), \rho_\epsilon * \eta_s(y) dy \rangle|] \nonumber \\ &\leq   \int_0^t \IE[ \frac{\epsilon}{\sqrt{\epsilon^2 + s}} \langle 1,\eta_0(dz) \rangle \langle 1, \eta_s(dz)\rangle ] ds +  \int_0^t \IE[  \int_0^s \frac{\epsilon}{\sqrt{\epsilon^2 + s - r}} \langle 1, \eta_r (dz) \rangle dr \langle 1, \eta_s(dz) \rangle  ] ds \nonumber\\ & + \int_0^t \IE[   1_{A^c_{t}} \int_0^s \frac{\epsilon}{\sqrt{\epsilon^2 + s - r}} \langle \rho_\epsilon*\eta_r(z), \eta_r(dz) \rangle dr \langle 1, \eta_s(dz) \rangle  ] ds + \int_0^t \IE[\langle |M_s(x)|,\eta_s(dx) \rangle] ds \nonumber \\ &+ \int_0^t \int \IE[|M_s(y)|\rho_\epsilon*\eta_s(y)] dy ds  +\mathcal{O}\left( \frac{1}{\epsilon^2 \theta} + \epsilon^2 + \epsilon^{1/3} \right)  \label{ThingsToBound}
 \end{align}
@@
 \begin{align*}
-\int_0^t C \frac{\epsilon}{\sqrt{\epsilon^2+s}}\IE[\langle 1, \overline{\eta}_s(dz) \rangle] ds + \int_0^t \int_0^s \frac{\epsilon}{\sqrt{\epsilon^2+s-r}}\IE[\langle 1, \overline{\eta}_r(dz)\rangle^2 + \langle 1, \overline{\eta}_s(dz)\rangle^2] ds,
+\int_0^t C \frac{\epsilon}{\sqrt{\epsilon^2+s}}\IE[\langle 1, \eta_s(dz) \rangle] ds + \int_0^t \int_0^s \frac{\epsilon}{\sqrt{\epsilon^2+s-r}}\IE[\langle 1, \eta_r(dz)\rangle^2 + \langle 1, \eta_s(dz)\rangle^2] ds,
 \end{align*}
@@
 \begin{align*}
-\int_0^t \int_0^s \frac{\epsilon^{1/3}}{\sqrt{\epsilon^2+s-r}} \IE[ \langle \rho*\overline{\eta}_r(z), \overline{\eta}(dz) \rangle] dr ds = \mathcal{O}(\epsilon^{1/3})
+\int_0^t \int_0^s \frac{\epsilon^{1/3}}{\sqrt{\epsilon^2+s-r}} \IE[ \langle \rho*\eta_r(z), \eta(dz) \rangle] dr ds = \mathcal{O}(\epsilon^{1/3})
 \end{align*}
 where we have used Remark~\ref{remark:BoundedIntegral}. 
-We now proceed to control the terms with martingales in (\ref{ThingsToBound}). For the first one note that, by using Cauchy-Schwartz in $L^2(\mathbb{P})$ and then in $L^2(\mathbb{R}^d)$,
+We now proceed to control the terms with martingales in (\ref{ThingsToBound}). For the first one note that, by using Cauchy-Schwartz in $L^2(\mathbb{P})$ and then in $L^2(\IR^d)$,
 \begin{align}
-\int_0^t \int \IE[|M_s(y)|\rho_\epsilon*\overline{\eta}_s(y)] dy ds & \leq \int_0^t \int \IE[|M^2_s(y)]^{1/2} \IE[\rho_\epsilon * \overline{\eta}_s(y)^2]^{1/2} dy dy \nonumber \\ & \leq \int_0^t \left( \int \IE[|M_s(y)^2|] dy \int \IE[\rho_\epsilon * \overline{\eta}_s(y)^2] dy \right)^{1/2} ds  \nonumber \\ &= \mathcal{O}\left( \left( \frac{\theta}{N \epsilon^d} \right)^{1/2} \right)
+\int_0^t \int \IE[|M_s(y)|\rho_\epsilon*\eta_s(y)] dy ds & \leq \int_0^t \int \IE[|M^2_s(y)]^{1/2} \IE[\rho_\epsilon * \eta_s(y)^2]^{1/2} dy dy \nonumber \\ & \leq \int_0^t \left( \int \IE[|M_s(y)^2|] dy \int \IE[\rho_\epsilon * \eta_s(y)^2] dy \right)^{1/2} ds  \nonumber \\ &= \mathcal{O}\left( \left( \frac{\theta}{N \epsilon^d} \right)^{1/2} \right)
 \label{TwiceCS} \end{align}
@@
 \begin{align*}
- M_t^{\epsilon^2}(x) &= \langle p_{\epsilon^2}(x,y), \overline{\eta}_t(dx) \rangle - \langle p_{t + \epsilon^2}(x,y), \overline{\eta}_0(dx) \rangle \\ &- \int_0^t \langle F(\rho_\epsilon*\overline{\eta}_s(y)) p_{t-s+\epsilon^2}(x,y), \overline{\eta}_s(dy) \rangle ds + \mathcal{O}\left(\frac{1}{\epsilon^2 \theta} \right) \end{align*}
+ M_t^{\epsilon^2}(x) &= \langle p_{\epsilon^2}(x,y), \eta_t(dx) \rangle - \langle p_{t + \epsilon^2}(x,y), \eta_0(dx) \rangle \\ &- \int_0^t \langle F(\rho_\epsilon*\eta_s(y)) p_{t-s+\epsilon^2}(x,y), \eta_s(dy) \rangle ds + \mathcal{O}\left(\frac{1}{\epsilon^2 \theta} \right) \end{align*}
  It follows then that $M_s^{\epsilon^2}= p_{\epsilon^2/2}*M_s^{\epsilon^2/2} + \mathcal{O}\left(1/\epsilon^2 \theta\right)$. Using this we can then bound,
  \begin{align*}
-\int_0^t &\IE[ \langle |M_s^{\epsilon^2}(x)|, \overline{\eta}_s(dx) \rangle ] ds \\ &= \int_0^t \IE[ \langle | p_{\epsilon^2/2}*M_s^{\epsilon^2/2}(x)|, \overline{\eta}_s(dx) \rangle] ds \\ & \leq  \int_0^t \IE[ \langle p_{\epsilon^2/2}*| M_s^{\epsilon^2/2}(x)|, \overline{\eta}_s(dx) \rangle] ds \\ &= \int_0^t \IE[ \langle \int p_{\epsilon^2/2}(x,y) |M_s^{\epsilon^2/2}(y)|dy, \overline{\eta}_s(dx) \rangle] ds \\ &= \int_0^t \IE[ \int |M_s^{\epsilon^2/2}(y)| p_{\epsilon^2/2}*\overline{\eta}_s(y) dy ] ds \\ &= \int_0^t \int \IE[ M_s^{\epsilon^2/2}(y)| p_{\epsilon^2/2} * \overline{\eta}_s(dy)] dy ds
+\int_0^t &\IE[ \langle |M_s^{\epsilon^2}(x)|, \eta_s(dx) \rangle ] ds \\ &= \int_0^t \IE[ \langle | p_{\epsilon^2/2}*M_s^{\epsilon^2/2}(x)|, \eta_s(dx) \rangle] ds \\ & \leq  \int_0^t \IE[ \langle p_{\epsilon^2/2}*| M_s^{\epsilon^2/2}(x)|, \eta_s(dx) \rangle] ds \\ &= \int_0^t \IE[ \langle \int p_{\epsilon^2/2}(x,y) |M_s^{\epsilon^2/2}(y)|dy, \eta_s(dx) \rangle] ds \\ &= \int_0^t \IE[ \int |M_s^{\epsilon^2/2}(y)| p_{\epsilon^2/2}*\eta_s(y) dy ] ds \\ &= \int_0^t \int \IE[ M_s^{\epsilon^2/2}(y)| p_{\epsilon^2/2} * \eta_s(dy)] dy ds
  \end{align*}
@@
 Now, to finish the characterisation of the limit, it remain to show that:
-\[ \int f(x) \rho_\epsilon * \overline{\eta}_t(x) F(\rho_\epsilon * \overline{\eta}_t(x)) dx \rightarrow \int f(x) u_t(x) F(u_t(x)) dx \]
-where $u_t(x)dx$ is the limit of $\rho_\epsilon*\overline{\eta}_t(x)dx$.
-As we mention as the start of this note this does now follow from weak convergence of $\rho_\epsilon*\overline{\eta}(x)dx$.
-For proving this, we recall that $F(x)$ is a polynomial, so we just need to prove said convergence of powers of $(\rho_\epsilon*\overline{\eta}_t(x))$.
+\[ \int f(x) \rho_\epsilon * \eta_t(x) F(\rho_\epsilon * \eta_t(x)) dx \rightarrow \int f(x) u_t(x) F(u_t(x)) dx \]
+where $u_t(x)dx$ is the limit of $\rho_\epsilon*\eta_t(x)dx$.
+As we mention as the start of this note this does now follow from weak convergence of $\rho_\epsilon*\eta(x)dx$.
+For proving this, we recall that $F(x)$ is a polynomial, so we just need to prove said convergence of powers of $(\rho_\epsilon*\eta_t(x))$.
 To illustrate how to proceed, we will prove the convergence,
-\begin{equation} \label{eq:QuadConvergence} \int f(x) \rho_\epsilon * \overline{\eta}_t(x) \rho_\epsilon * \overline{\eta}_t(x)^2 dx \rightarrow \int f(x) u_t(x) u_t(x)^2 dx \end{equation}
+\begin{equation} \label{eq:QuadConvergence} \int f(x) \rho_\epsilon * \eta_t(x) \rho_\epsilon * \eta_t(x)^2 dx \rightarrow \int f(x) u_t(x) u_t(x)^2 dx \end{equation}
 with the understanding that converge of higher powers will follows in a similar fashion with rougher notation. To achieve (\ref{eq:QuadConvergence}) we proceed by proving an approximation of the form,
@@
 \label{aprox2}
-\langle f, (\overline{\eta}_s * \rho_\epsilon)^2 \rangle \sim \int \int f(z) (\rho_\epsilon * \overline{\eta}_s)(z) \rho_\delta (z-y) (\rho_\epsilon * \overline{\eta}_s)(y) dz dy.
+\langle f, (\eta_s * \rho_\epsilon)^2 \rangle \sim \int \int f(z) (\rho_\epsilon * \eta_s)(z) \rho_\delta (z-y) (\rho_\epsilon * \eta_s)(y) dz dy.
 \end{equation}
 Before proceeding with a proof of (\ref{aprox2}), we argue why this is enough to conclude Theorem~\ref{TeoremOneStepConvergence}. Note the right hand side of (\ref{aprox2}) can written as
-\[ \int_{\mathbb{R}^{d} \otimes \mathbb{R}^d} f(z) \rho_\delta(z-y) (\rho_\epsilon * \overline{\eta}_s(dz) \otimes (\rho_\epsilon * \overline{\eta}_s(dy)). \]
-Weak convergence of $\rho_\epsilon * \overline{\eta}$ (plus continuity of the mapping $(z,y) \rightarrow f(z) \rho_\delta(z-y)$) gives that the last term converges in $L^1$ to
-\[ \int_{\mathbb{R}^{d} \otimes \mathbb{R}^d} f(z) \rho_\delta(z-y) (u_s(dz) \otimes (u_s(dy)). \]
+\[ \int_{\IR^{d} \otimes \IR^d} f(z) \rho_\delta(z-y) (\rho_\epsilon * \eta_s(dz) \otimes (\rho_\epsilon * \eta_s(dy)). \]
+Weak convergence of $\rho_\epsilon * \eta$ (plus continuity of the mapping $(z,y) \rightarrow f(z) \rho_\delta(z-y)$) gives that the last term converges in $L^1$ to
+\[ \int_{\IR^{d} \otimes \IR^d} f(z) \rho_\delta(z-y) (u_s(dz) \otimes (u_s(dy)). \]
 Finally, by a direct analogue of (\ref{aprox2}) we can say that
-\begin{equation} \int_{\mathbb{R}^{d} \otimes \mathbb{R}^d} f(z) \rho_\delta(z-y) (u_s(dz) \otimes (u_s(dy)) \sim \langle f(x), u_s^2(x) dx \rangle. \label{aprox3} \end{equation}
+\begin{equation} \int_{\IR^{d} \otimes \IR^d} f(z) \rho_\delta(z-y) (u_s(dz) \otimes (u_s(dy)) \sim \langle f(x), u_s^2(x) dx \rangle. \label{aprox3} \end{equation}
 which is what we seek. We proceed now to prove (\ref{aprox2}), with the understanding that (\ref{aprox3}) follows in a similar way and give even better error terms.
@@
 \begin{align*}
-\int_0^t \mathbb{E}&\left[\left| \langle f(y), (\overline{\eta}_s * \rho_\epsilon(y))^2) dy\rangle - \int \int f(y) (\rho_\epsilon * \overline{\eta}_s)(z) \rho_\delta (z-y) (\rho_\epsilon * \overline{\eta}_s)(y) dz dy.
+\int_0^t \mathbb{E}&\left[\left| \langle f(y), (\eta_s * \rho_\epsilon(y))^2) dy\rangle - \int \int f(y) (\rho_\epsilon * \eta_s)(z) \rho_\delta (z-y) (\rho_\epsilon * \eta_s)(y) dz dy.
 \right|\right] ds
@@
 \begin{align}
-&\int_0^t \mathbb{E}\left[| \langle f(y), (\overline{\eta}_s * \rho_\epsilon(y))^2) dy \rangle - \int \int f(y) (\rho_\epsilon * \overline{\eta}_s)(z) \rho_\delta (z-y) (\rho_\epsilon * \overline{\eta}_s)(y) dz dy.
-|\right] ds \nonumber \\ &\leq  \Vert f \Vert_\infty \int_{S_f}  \int_0^t  \mathbb{E}\left[ \int \left\{ \left|(\rho_\epsilon * \overline{\eta}_s)(y)-(\rho_\epsilon * \overline{\eta}_s)(z) \right|   \rho_\delta(z-y) dz \right\} (\rho_\epsilon *\overline{\eta}_s)(y) \right] ds  dy \label{b1}
+&\int_0^t \mathbb{E}\left[| \langle f(y), (\eta_s * \rho_\epsilon(y))^2) dy \rangle - \int \int f(y) (\rho_\epsilon * \eta_s)(z) \rho_\delta (z-y) (\rho_\epsilon * \eta_s)(y) dz dy.
+|\right] ds \nonumber \\ &\leq  \Vert f \Vert_\infty \int_{S_f}  \int_0^t  \mathbb{E}\left[ \int \left\{ \left|(\rho_\epsilon * \eta_s)(y)-(\rho_\epsilon * \eta_s)(z) \right|   \rho_\delta(z-y) dz \right\} (\rho_\epsilon *\eta_s)(y) \right] ds  dy \label{b1}
 \end{align}
 We want then to bound (\ref{b1}) by using Proposition~\ref{ContinuityEstimate}. For this consider the event,
-\[ B_{s,y} := \{ \rho_\epsilon * \overline{\eta}_s(y) > \delta^{-2/3} \}. \]
+\[ B_{s,y} := \{ \rho_\epsilon * \eta_s(y) > \delta^{-2/3} \}. \]
 Note that by Markov's inequality and Lemma~\ref{FirstBoundLocalDensity} the event $B_{s,y}$ has probability of order $\delta^{2/3}$ (and independent of $s$ and $y$).
@@
 \begin{align}
-&\int_0^t \IE[ \frac{\delta}{\sqrt{\epsilon^2 + s}} \langle 1,\overline{\eta}_0(dz) \rangle (\rho_\epsilon *\overline{\eta}_s)(y) ] ds +  \int_0^t \IE[  \int_0^s \frac{\delta}{\sqrt{\epsilon^2 + s - r}} \langle 1, \overline{\eta}_r (dz) \rangle dr(\rho_\epsilon *\overline{\eta}_s)(y)  ] ds \nonumber\\ & + \int_0^t \IE[   1_{B^c_{s,\delta}} \int_0^s \frac{\delta}{\sqrt{\epsilon^2 + s - r}} \langle \rho_\epsilon*\overline{\eta}_r(z), \overline{\eta}_r(dz) \rangle dr (\rho_\epsilon *\overline{\eta}_s)(y) ] ds + \int_0^t \IE[\langle |M_s(x)|,\overline{\eta}_s(dx) \rangle] ds \nonumber \\ & + \int_0^t  \IE[|M_s(y)|\rho_{\epsilon+\delta}*\overline{\eta}_s(y)] ds  +\mathcal{O}\left( \frac{1}{\epsilon^2 \theta} + \delta^{1/3} \right)  \label{ThingsToBound2}
+&\int_0^t \IE[ \frac{\delta}{\sqrt{\epsilon^2 + s}} \langle 1,\eta_0(dz) \rangle (\rho_\epsilon *\eta_s)(y) ] ds +  \int_0^t \IE[  \int_0^s \frac{\delta}{\sqrt{\epsilon^2 + s - r}} \langle 1, \eta_r (dz) \rangle dr(\rho_\epsilon *\eta_s)(y)  ] ds \nonumber\\ & + \int_0^t \IE[   1_{B^c_{s,\delta}} \int_0^s \frac{\delta}{\sqrt{\epsilon^2 + s - r}} \langle \rho_\epsilon*\eta_r(z), \eta_r(dz) \rangle dr (\rho_\epsilon *\eta_s)(y) ] ds + \int_0^t \IE[\langle |M_s(x)|,\eta_s(dx) \rangle] ds \nonumber \\ & + \int_0^t  \IE[|M_s(y)|\rho_{\epsilon+\delta}*\eta_s(y)] ds  +\mathcal{O}\left( \frac{1}{\epsilon^2 \theta} + \delta^{1/3} \right)  \label{ThingsToBound2}
 \end{align}
@@
 Under the condition (\ref{ConditionsForConvergence}) we have that all the errors in our approximations go to $0$.
-It is then we can deduce that quadratic (and analogously, higher order) terms in the martingale problem for $\rho_\epsilon*\overline{\eta}_t(x)dx$, (\ref{MGPT_epsilon}), converges to the corresponding term of the weak limit.
+It is then we can deduce that quadratic (and analogously, higher order) terms in the martingale problem for $\rho_\epsilon*\eta_t(x)dx$, (\ref{MGPT_epsilon}), converges to the corresponding term of the weak limit.
 Any linear term converge trivially by weak convergence.
@@
 \begin{align*}
-\int_0^t \langle \mathcal{L}^\theta T_{\epsilon^2} f, \overline{\eta}_s(dx)\rangle ds &= \int_0^t \langle \frac{1}{2} \Delta T_{\epsilon^2} f(x), \overline{\eta}_s(dx) \rangle + \mathcal{O}(\theta^{-1})
-\\ &= \int_0^t \langle \frac{1}{2} \Delta f(x), \rho_\epsilon* \overline{\eta}_s(x) dx \rangle ds + \mathcal{O}(\theta^{-1} + \epsilon).
+\int_0^t \langle \mathcal{L}^\theta T_{\epsilon^2} f, \eta_s(dx)\rangle ds &= \int_0^t \langle \frac{1}{2} \Delta T_{\epsilon^2} f(x), \eta_s(dx) \rangle + \mathcal{O}(\theta^{-1}) 
+\\ &= \int_0^t \langle \frac{1}{2} \Delta f(x), \rho_\epsilon* \eta_s(x) dx \rangle ds + \mathcal{O}(\theta^{-1} + \epsilon).
 \end{align*}
 Thus, by weak convergence we can deduce
-\[ \int_0^t \langle \mathcal{L}^\theta T_{\epsilon^2} f, \overline{\eta}_s(dx)\rangle ds \rightarrow \int_0^t \langle \frac{1}{2} \Delta f(x), u_s(x) dx \rangle ds \]
-Putting all the convergences together, this identifies the limit of $\rho_\epsilon*\overline{\eta}_s(x)dx$ as we have claimed in Theorem~\ref{TeoremOneStepConvergence}.
+\[ \int_0^t \langle \mathcal{L}^\theta T_{\epsilon^2} f, \eta_s(dx)\rangle ds \rightarrow \int_0^t \langle \frac{1}{2} \Delta f(x), u_s(x) dx \rangle ds \]
+Putting all the convergences together, this identifies the limit of $\rho_\epsilon*\eta_s(x)dx$ as we have claimed in Theorem~\ref{TeoremOneStepConvergence}.
 
@@
     functions on empirical measures}) to show that our lookdown representation
-    $\{\xi^N_t: N \in \mathbb{N}\}$ is tight as a $\mathcal{M}(\mathbb{R^d}
+    $\{\xi^N_t: N \in \mathbb{N}\}$ is tight as a $\mathcal{M}(\IR^d
     \times [0, \infty])$-valued stochastic process in the vague topology as
@@
 \begin{align}
-   \sup_{\theta}\mathbb{E}\left[\limsup_{x, \eta} \theta \left| \int_{\mathbb{R}^d} (y-x) q^{\mathfrak{m}}_{ \theta}(x,\eta,dy) \right|\right] \leq & \quad \overline{\alpha},\\
-   \sup_{\theta}\mathbb{E}\left[\limsup_{x, \eta} \theta \int_{\mathbb{R}^d} |y-x|^2 q^{\mathfrak{m}}_{ \theta}(x,\eta,dy)\right]  \leq & \quad \overline{\beta}.
+   \sup_{\theta}\mathbb{E}\left[\limsup_{x, \eta} \theta \left| \int_{\IR^d} (y-x) q^{\mathfrak{m}}_{ \theta}(x,\eta,dy) \right|\right] \leq & \quad \overline{\alpha},\\
+   \sup_{\theta}\mathbb{E}\left[\limsup_{x, \eta} \theta \int_{\IR^d} |y-x|^2 q^{\mathfrak{m}}_{ \theta}(x,\eta,dy)\right]  \leq & \quad \overline{\beta}.
 \end{align}
@@
 $\{(X^{N}_{a}(t))_{\tau^{N}_a\leq t < \sigma^{N}_{a}}: N \in \mathbb{N},  \}$ is relatively compact in 
-$D_{\mathbb{R}^d}[0,\infty )$ where $\mathbb{R}^d$ is equipped with the standard Euclidean metric. 
+$D_{\IR^d}[0,\infty )$ where $\IR^d$ is equipped with the standard Euclidean metric. 
 \end{lemma}
 \begin{proof}
-We write $S_{t,r}:=(t,t+r  ]\times [0,\infty )\times \mathbb{R}^d\times 
+We write $S_{t,r}:=(t,t+r  ]\times [0,\infty )\times \IR^d\times 
 \{0,1\}$ to be the region for the Poisson measure driving $(X^{N}_{a}(t))_{t \geq \tau_a}$ between time $t$ and $(t+r)$ and write $\tilde\Pi_{a}(ds,dv,dz,d\kappa):=\Pi_{a}(ds,dv,dz, d\kappa) - ds\times dv\times dz \times (\frac{1}{2}\delta_{0}+\frac{1}{2}\delta_{1})d\kappa$ to be the compensated Poisson point process of $\Pi_{a}$.
@@
 \int_{t}^{t+r}\int_{\{v < 2\theta \gamma_{\theta}(x, \eta) r_{\theta}(x + y, \eta) \}}
-\frac{1}{2}\left| \int_{\mathbb{R}^d} (y-X^{N}_{\tau}(s-)) q^{\mathfrak{m}}_{\theta}(X^{N}_{\tau}(s-),\eta^{N}(s-),dy) 
+\frac{1}{2}\left| \int_{\IR^d} (y-X^{N}_{\tau}(s-)) q^{\mathfrak{m}}_{\theta}(X^{N}_{\tau}(s-),\eta^{N}(s-),dy) 
 \right|
@@
 (1+C_G) \theta 
-\int_{{\mathbb{R}}^d}|y-X^{N}_{
+\int_{{\IR}^d}|y-X^{N}_{
 a}(s)|^2q^{\mathfrak{m}}_{\theta}(X^{N}_{a}(s),\eta^{N}(s),dy)ds
@@
 \left|
-\int_{{\mathbb{R}}^d}
+\int_{{\IR}^d}
 (y-X^{N}_{a}(s))q^{\mathfrak{m}}_{\theta}(X^{N}_{a}(s),
@@
 \begin{align}
-   \sup_{\theta}\limsup_{x, \eta} \theta \left| \int_{\mathbb{R}^d} (y-x) q^{\mathfrak{m}}_{ \theta}(x,\eta,dy) \right| =& \sup_{\theta}\limsup_{x} \theta \left| \int_{\mathbb{R}^d} (y-x) q_{\theta}(x,dy) \right| =  0,\\
-   \sup_{\theta}\limsup_{x, \eta} \theta \int_{\mathbb{R}^d} |y-x|^2 q^{\mathfrak{m}}_{ \theta}(x,\eta,dy)  =& \sup_{\theta}\limsup_{x} \theta \int_{\mathbb{R}^d} |y-x|^2 q_{\theta}(x,dy) =  1,
+   \sup_{\theta}\limsup_{x, \eta} \theta \left| \int_{\IR^d} (y-x) q^{\mathfrak{m}}_{ \theta}(x,\eta,dy) \right| =& \sup_{\theta}\limsup_{x} \theta \left| \int_{\IR^d} (y-x) q_{\theta}(x,dy) \right| =  0,\\
+   \sup_{\theta}\limsup_{x, \eta} \theta \int_{\IR^d} |y-x|^2 q^{\mathfrak{m}}_{ \theta}(x,\eta,dy)  =& \sup_{\theta}\limsup_{x} \theta \int_{\IR^d} |y-x|^2 q_{\theta}(x,dy) =  1,
 \end{align}
@@
 \end{align}
-for all $x \in \mathbb{R}^d$ and  $\eta \in \mathcal{M}_{F}(\mathbb{R}^d)$.
+for all $x \in \IR^d$ and  $\eta \in \mathcal{M}_{F}(\IR^d)$.
 
@@
 To control the level process, we consider two scenarios, one where the local density of the system between $[0,r]$ is never too big, i.e.
-$$h(r)=\sup_{x \in \mathbb{R}^d}\sup_{s\in [0,r]}\left\{\varrho_F*\eta^N_s(X^N_a(s)) \right\} \leq H_{\epsilon}(r),$$
+$$h(r)=\sup_{x \in \IR^d}\sup_{s\in [0,r]}\left\{\varrho_F*\eta^N_s(X^N_a(s)) \right\} \leq H_{\epsilon}(r),$$
 and otherwise.
@@
 $$\mathcal{M}_{K,M}:= \{\mu \in \mathcal{M}(\mathbb{R^d} \times [0, \infty]): \mu([-M,M]^d \times [0,M])/M \leq K\}$$
-to be the set of measures on $\mathbb{R}^d \times[0,\infty)$ with mass smaller than $K$ in the region $[-M,M]^d \times [0,M]$.
+to be the set of measures on $\IR^d \times[0,\infty)$ with mass smaller than $K$ in the region $[-M,M]^d \times [0,M]$.
 \end{definition}
@@
 \begin{definition}
-We define $\mathfrak{G}_{\leq 1}$ to be the set of functions $g \in \mathcal{C}(\mathbb{R}^d \times [0, \infty) \to \mathbb{R}$ such that 
-$g(\cdot, u) \in \mathcal{C}_{0}(\mathbb{R}^d)$ for all $u \geq 0$, and there exists some $u_{*}>0$ such that $g(x,u)=1$ for all $u \geq u_{*}$.
+We define $\mathfrak{G}_{\leq 1}$ to be the set of functions $g \in \mathcal{C}(\IR^d \times [0, \infty) \to \IR$ such that 
+$g(\cdot, u) \in \mathcal{C}_{0}(\IR^d)$ for all $u \geq 0$, and there exists some $u_{*}>0$ such that $g(x,u)=1$ for all $u \geq u_{*}$.
 Furthermore, for $g \in \mathfrak{G}_{\leq 1}$, define $F_g(\xi):= \exp(-\langle \log g, \cdot \rangle )$.
@@
     \hline\\
-      $S$   &  $\mathcal{M}(\mathbb{R}^d \times [0, \lambda))$\\\\
-       $S_0$  &  $\mathcal{M}(\mathbb{R}^d)$\\\\
+      $S$   &  $\mathcal{M}(\IR^d \times [0, \lambda))$\\\\
+       $S_0$  &  $\mathcal{M}(\IR^d)$\\\\
        $A$ & $A^{\theta}$\\\\
        $(X_t)_{t \geq 0}$ & $(\xi^{\theta}_t)_{t \geq 0}$\\\\
-       $\mu_0$ & $\Xi^{\theta}_0 \in \mathcal{M}(\mathbb{R}^d)$\\\\
-       $\nu_0$ & $\xi^{\theta}_0 \in \mathcal{M}(\mathbb{R}^d \times [0,\lambda])$\\\\
+       $\mu_0$ & $\Xi^{\theta}_0 \in \mathcal{M}(\IR^d)$\\\\
+       $\nu_0$ & $\xi^{\theta}_0 \in \mathcal{M}(\IR^d \times [0,\lambda])$\\\\
        $f(\xi)$ & $\prod_{(x,u) \in \xi} g(x,u)$\\\\
-        $\gamma_M$ & $ \mathcal{M}(\mathbb{R}^d \times [0, \lambda)) \ni \xi \to \frac{1}{\lambda}\sum_{(x,u) \in \xi, u < \lambda} \delta_{x} \in \mathcal{M}(\mathbb{R}^d)$\\\\
+        $\gamma_M$ & $ \mathcal{M}(\IR^d \times [0, \lambda)) \ni \xi \to \frac{1}{\lambda}\sum_{(x,u) \in \xi, u < \lambda} \delta_{x} \in \mathcal{M}(\IR^d)$\\\\
        $\alpha_M$ & $ \alpha_M(\Xi,d \nu) =     \begin{cases}
@@
 \end{remark}
-First of all, note that $\gamma_M$ is Borel-measurable and $\alpha_M$ is a transition function from $\mathcal{M}(\mathbb{R}^d \times [0, \lambda))$ to $\mathcal{M}(\mathbb{R}^d)$.
+First of all, note that $\gamma_M$ is Borel-measurable and $\alpha_M$ is a transition function from $\mathcal{M}(\IR^d \times [0, \lambda))$ to $\mathcal{M}(\IR^d)$.
 More importantly, we have the following simplified expression for an integral against $\alpha_M$:
 \begin{equation}
-\int_{\mathcal{M}(\mathbb{R}^d\times [0,\lambda])}A^{\theta}f(\nu)\alpha_M(\Xi,d\nu)= \int   A^{\theta}f(\textbf{x},\textbf{u})\Gamma(d\textbf{u}). 
+\int_{\mathcal{M}(\IR^d\times [0,\lambda])}A^{\theta}f(\nu)\alpha_M(\Xi,d\nu)= \int   A^{\theta}f(\textbf{x},\textbf{u})\Gamma(d\textbf{u}). 
 \end{equation}
@@
     \item The process $(\gamma_M \circ \xi^{\theta}_t)_{t \geq 0}:= \left(\frac{1}{\lambda}\sum_{(x,u)\in \xi^{\theta}_t, u < \lambda} \delta_x\right)_{t \geq 0}=(\Xi^{\theta}_t)_{t \geq 0}$ solves the Martingale Problem \eqref{Markov Mapping Theorem Martingale Condition Simplified}.
-    \item $\mathbb{P}\{\xi^{\theta}_t \in B | \mathcal{F}^{\Xi^{\theta}}_t\}=\alpha_M(\Xi^{\theta}(t),\meanq), ~~~B \in \mathcal{B}(\mathcal{M}(\mathbb{R}^d \times [0,\lambda])).$
+    \item $\mathbb{P}\{\xi^{\theta}_t \in B | \mathcal{F}^{\Xi^{\theta}}_t\}=\alpha_M(\Xi^{\theta}(t),\meanq), ~~~B \in \mathcal{B}(\mathcal{M}(\IR^d \times [0,\lambda])).$
 \end{enumerate}
@@
 \int_u^{
-\lambda}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\mathbb{R}^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
+\lambda}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\IR^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
 \xi },dy) \nonumber \\
-& \qquad \qquad \qquad \qquad +\int_{\mathbb{R}^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy)\Bigg)dv_1 \nonumber\\
+& \qquad \qquad \qquad \qquad +\int_{\IR^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy)\Bigg)dv_1 \nonumber\\
 &+f(\xi )\sum_{(x,u)\in\xi}\,\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)},
@@
 \int_u^{
-\lambda}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\mathbb{R}^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
+\lambda}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\IR^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
 \xi },dy)\Bigg)dv_1,\\
@@
 \int_u^{
-\lambda}\Bigg(\frac{1}{2}\int_{\mathbb{R}^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy)\Bigg)dv_1,\\
+\lambda}\Bigg(\frac{1}{2}\int_{\IR^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy)\Bigg)dv_1,\\
 A^{\theta,3}f(\xi)=&f(\xi )\sum_{(x,u)\in\xi}\,\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)},
@@
 \int_u^{
-\lambda}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\mathbb{R}^d}(g(y,u)-g(x,u))q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
+\lambda}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\IR^d}(g(y,u)-g(x,u))q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
 \xi },dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
@@
 \int_u^{
-\lambda}\Bigg(\frac 12 g(x,v_1)\int_{\mathbb{R}^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
+\lambda}\Bigg(\frac 12 g(x,v_1)\int_{\IR^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
 \xi },dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
@@
 \int_u^{
-\lambda} g(x,v_1)dv_1\times \int_{\mathbb{R}^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
+\lambda} g(x,v_1)dv_1\times \int_{\IR^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
 \xi },dy)\right\}du\\
-&=\sum_{(x,u)\in\xi}\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\int_{\mathbb{R}^d} \left\{\int_{0}^{\lambda}
+&=\sum_{(x,u)\in\xi}\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\int_{\IR^d} \left\{\int_{0}^{\lambda}
 \int_u^{
@@
 \int_u^{
-\lambda}\Bigg(\int_{\mathbb{R}^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
+\lambda}\Bigg(\int_{\IR^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
 &=\sum_{(x,u)\in\xi}\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\int \Bigg\{f(\xi)\times
 \int_u^{
-\lambda}\Bigg(\int_{\mathbb{R}^d}\left(g(y,v_1)+g(x,v_1)-2\right)q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
-&=\sum_{(x,u)\in\xi}\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i) \frac{1}{\lambda}\int_{\mathbb{R}^d}\Bigg\{\int_{0}^{\lambda}
+\lambda}\Bigg(\int_{\IR^d}\left(g(y,v_1)+g(x,v_1)-2\right)q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
+&=\sum_{(x,u)\in\xi}\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i) \frac{1}{\lambda}\int_{\IR^d}\Bigg\{\int_{0}^{\lambda}
 \int_u^{
@@
 &\int \Bigg(A^{1}_{\theta}f(\xi)+A^{2}_{\theta}f(\xi)+A^{3}_{\theta}f(\xi)\Bigg)\Gamma(d\mathbf{u})\\
-&=  \sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)}\hat{g}(x_i) \left( \int_{\mathbb{R}^n} \hat{g}(y) q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy) - 2+\frac{1}{\hat{g}(x)}\right)+\sum_{(x,u) \in \xi } \prod_{(x_i,u_i)}\hat{g}(x_i)b_{\theta}(x,\Xi)\left(1-\frac{1}{\hat{g}(x)}\right)\\
-&=  \hat{f}(\xi)\sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi) \left(\int_{\mathbb{R}^n} \hat{g}(y) q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy) -1\right)+\hat{f}(\xi)\sum_{(x,u) \in \xi } (b_{\theta}(x,\Xi)-\theta\gamma^{\mathfrak{m}}_{\theta}(x,\xi))\left(1-\frac{1}{\hat{g}(x)}\right)\\
-&=  \hat{f}(\xi)\sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi) \left(\int_{\mathbb{R}^n} \hat{g}(y) q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy) -1\right) -\hat{f}(\xi)\sum_{(x,u) \in \xi } \theta \mu_{\epsilon,\theta}(x,\Xi)\left(1-\frac{1}{\hat{g}(x)}\right),
+&=  \sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)}\hat{g}(x_i) \left( \int_{\IR^n} \hat{g}(y) q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy) - 2+\frac{1}{\hat{g}(x)}\right)+\sum_{(x,u) \in \xi } \prod_{(x_i,u_i)}\hat{g}(x_i)b_{\theta}(x,\Xi)\left(1-\frac{1}{\hat{g}(x)}\right)\\
+&=  \hat{f}(\xi)\sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi) \left(\int_{\IR^n} \hat{g}(y) q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy) -1\right)+\hat{f}(\xi)\sum_{(x,u) \in \xi } (b_{\theta}(x,\Xi)-\theta\gamma^{\mathfrak{m}}_{\theta}(x,\xi))\left(1-\frac{1}{\hat{g}(x)}\right)\\
+&=  \hat{f}(\xi)\sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi) \left(\int_{\IR^n} \hat{g}(y) q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy) -1\right) -\hat{f}(\xi)\sum_{(x,u) \in \xi } \theta \mu_{\epsilon,\theta}(x,\Xi)\left(1-\frac{1}{\hat{g}(x)}\right),
 \end{align*}
@@
 \end{equation}
-where our test measure $\eta$ takes value on $\mathcal{M}_F(\mathbb{R}\times [0,\infty))$ and $\Xi:=\lim_{u_0\rightarrow\infty}\frac 1{u_0}\sum_{(u,x)\in \eta:u\leq u_0}\delta_x$.
+where our test measure $\eta$ takes value on $\mathcal{M}_F(\IR\times [0,\infty))$ and $\Xi:=\lim_{u_0\rightarrow\infty}\frac 1{u_0}\sum_{(u,x)\in \eta:u\leq u_0}\delta_x$.
 
@@
 Similar to the calculations above, we write $\alpha(\Xi,\cdot)$ for the distribution of a conditionally
-Poisson random measure $\eta^{\infty}$ on $\mathbb{R}^d\times [0,\infty)$ with mean measure
+Poisson random measure $\eta^{\infty}$ on $\IR^d\times [0,\infty)$ with mean measure
 $\Xi(dx)\times \Lambda$ and we calculate $\alpha A^{\text{nl}}_{\epsilon}f(\eta)$.
@@
 where
-$$H_{\theta}(x,w)=\int_{\mathbb{R}^d}
+$$H_{\theta}(x,w)=\int_{\IR^d}
     \left(
@@
 \end{equation}
-for $v \in \mathbb{R}^d$ and $C>0$. 
+for $v \in \IR^d$ and $C>0$. 
 We have 
@@
 with $K = \frac{1}{\epsilon_r^2} - \frac{1}{\epsilon_\gamma^2}$.
-Therefore it suffices to show that for all $x,w \in \mathbb{R}^d$ and $s \in [0, 1/\theta]$, 
+Therefore it suffices to show that for all $x,w \in \IR^d$ and $s \in [0, 1/\theta]$, 
 \begin{align}\label{eqn:goal3}
@@
 
-\subsection{Euclidean-Vague Topology on $\mathbb{R}^d \times [0,\infty]$}\label{sec: Convergence in Product Topology}
-We first define a topology on $\mathbb{R}^d \times [0,\infty]$ which is Euclidean on $\mathbb{R}^d$ and vague in $[0,\infty]$.
+\subsection{Euclidean-Vague Topology on $\IR^d \times [0,\infty]$}\label{sec: Convergence in Product Topology}
+We first define a topology on $\IR^d \times [0,\infty]$ which is Euclidean on $\IR^d$ and vague in $[0,\infty]$.
 \begin{definition}
-We define the topology $\mathfrak{p}$ on $\mathbb{R}^d \times [0,\infty]:$
+We define the topology $\mathfrak{p}$ on $\IR^d \times [0,\infty]:$
 we say $(x_n,u_n) \to (x,u)$ in topology $\mathfrak{p}$ if 
 \begin{enumerate}
-    \item $|x_n-x| \to 0$ in $\mathbb{R}^d$.
+    \item $|x_n-x| \to 0$ in $\IR^d$.
     \item  For all $g \in C_{c}([0,\infty])$, the space of continuous functions with compact support on $[0,\infty]$, $g(u_n) \to g(u).$ Since this is the vague convergence for $(\delta_{u_n})_{n \in \mathbb{N}}$ we will abuse a bit the notation and denote this by the symbol $u_n \xrightarrow{vague} u$.
@@
 
-In other words, our topology is Euclidean in space $\mathbb{R}^d$ and vague in levels in $[0,\infty]$.
+In other words, our topology is Euclidean in space $\IR^d$ and vague in levels in $[0,\infty]$.
 \begin{lemma}\label{Vague times Euclidean is Polish}
-The space $\mathbb{R}^d \times [0,\infty]$ under topology $\mathfrak{p}$ is Polish.
+The space $\IR^d \times [0,\infty]$ under topology $\mathfrak{p}$ is Polish.
 \end{lemma}
@@
 as a measure on 
-$(\mathbb{R}^d \times [0, \infty], \mathfrak{p})$.
+$(\IR^d \times [0, \infty], \mathfrak{p})$.
 We endow the vague topology
@@
 First of all,
-as $(\mathbb{R}^d \times [0, \infty], \mathfrak{p})$
+as $(\IR^d \times [0, \infty], \mathfrak{p})$
 is Polish,
 the family of $C^{+}_K$ of continuous functions
-$$f: \mathbb{R^d} \times [0, \infty] \to \mathbb{R}^{+}$$
+$$f: \mathbb{R^d} \times [0, \infty] \to \IR^{+}$$
 with compact support
@@
 \begin{definition}
-We define $\mathfrak{G}_{\leq 1}$ to be the set of functions $g \in \mathcal{C}(\mathbb{R}^d \times [0, \infty) \to \mathbb{R})$ such that 
-$g(\cdot, u) \in \mathcal{C}_{0}(\mathbb{R}^d)$ for all $u \geq 0$, and there exists some $u_{*}>0$, such that $g(x,u)=1$ for all $u \geq u_{*}$.
+We define $\mathfrak{G}_{\leq 1}$ to be the set of functions $g \in \mathcal{C}(\IR^d \times [0, \infty) \to \IR)$ such that 
+$g(\cdot, u) \in \mathcal{C}_{0}(\IR^d)$ for all $u \geq 0$, and there exists some $u_{*}>0$, such that $g(x,u)=1$ for all $u \geq u_{*}$.
 \end{definition}
@@
 $$\left\{\sum_{m=1}^{N}a_m F_{g_m}(\cdot) ~~|~~ g_1,...,g_N \in \mathfrak{G}_{\leq 1}\right\}$$
-is dense in $C(\mathcal{M}(\mathbb{R^d} \times [0, \infty]),\mathbb{R})$.
+is dense in $C(\mathcal{M}(\mathbb{R^d} \times [0, \infty]),\IR)$.
 \end{lemma}

### 2022-09-04 forwards-and-backwards.tex
.

@@
         &\le
-        C' \IE\left[ \sqrt{[M^*(1)]_t} \right]
+        C' \IE\left[ \sqrt{[M(1)]_t} \right]
         \\ &\le
-        C'\left( 1 + \IE\left[ [M^*(1)]_t \right] \right)
+        C'\left( 1 + \IE\left[ [M(1)]_t \right] \right)
         \\ &=
@@
     Let $(\eta_t)_{t \geq 0}$ be the scaled particle system with $r(x, \eta) \equiv \gamma(x, \eta) \equiv 1$.
-    Suppose $F(x)$ satisfies:
+    Suppose $F(x)$ satisfies for $x \ge 0$:
     \begin{enumerate}
-        \item $F(x)1_{x>0}$  is bounded above.
-        \item $|F'(x)1_{x>0}|$ is bounded,
+        \item $F(x)$  is bounded above.
+        \item $|F'(x)|$ is bounded,
         \item and $||F''(x)||_\infty < \infty$.
     \end{enumerate}
-    We will also suppose $\theta$ is big enough that $1- F(x)1_{x>0}/\theta$ is non-negative.
+    We will also suppose $\theta$ is big enough that $1- F(x)/\theta$ is non-negative.
 
@@
     \begin{enumerate}
-        \item $\langle 1 , \eta_0 \rangle < C $
-        \item  $\| \rho_\epsilon * \eta_0(x) \|_\infty < C$ for all $x \in \IR^d$
-        \item $|\rho_\epsilon * \eta_0(x) - \rho_\epsilon * \eta_0(y)| \leq C \| x - y \|$ for all $x,y \in \IR^d$, and
-        \item $\rho_\epsilon * \eta_0(x) dx$ converges weakly to $u_0(x)dx$ for some $u_0(x) \in \mathcal{C}^2(\IR^d)$.
+        \item[(i)] $\langle 1 , \eta_0 \rangle < C $
+        \item[(ii)]  $\| \rho_\epsilon * \eta_0(x) \|_\infty < C$ for all $x \in \IR^d$
+        \item[(iii)] $|\rho_\epsilon * \eta_0(x) - \rho_\epsilon * \eta_0(y)| \leq C \| x - y \|$ for all $x,y \in \IR^d$, and
+        \item[(iv)] $\rho_\epsilon * \eta_0(x) dx$ converges weakly to $u_0(x)dx$ for some $u_0(x) \in \mathcal{C}^2(\IR^d)$.
     \end{enumerate}
@@
 For reference,
-the martingale problem (REF) for $\eta_t$ gives that for any smooth function $\phi$,
-\begin{align}
-&
+the martingale problem (Definition \ref{defn:mgale_construction})
+for $\eta_t$ gives that for any smooth function $\phi$,
+\begin{align} \label{mgp1}
     \langle \phi(x), \eta_{t}(dx) \rangle
@@
     \langle \phi(x), \eta_{0}(dx)\rangle
-    =
+    &= \nonumber
     M_t(\phi)
@@
     \rangle ds
-\nonumber \\
-&
-    {} +
+    \\ & {}
+    +
     \int_0^t \langle
@@
         \eta_s(dx)
-    \rangle ds , \label{mgp1}
+    \rangle ds ,
 \end{align}
 where $M_t(\phi)$ is a martingale with quadratic variation:
-\begin{align}
+\begin{align} \label{mgp2}
+    \begin{split}
 [ M(\phi) ]_t
@@
         \left\langle \int_{\IR^d} \phi^2(y) q_\theta(x,dy), \eta_s(dx) \right\rangle
-    \nonumber\\
-    & {} +
+    \\
+    & \qquad \qquad {} +
     \left\langle \left(1 + \frac{F(x, \eta_s)}{\theta } \right)
         \phi^2(x), \eta_s(dx)) \right\rangle 
-    \bigg\} ds.  \label{mgp2}
+    \bigg\} ds. 
+    \end{split}
+\end{align}
+
+Several times below we will need to bound second moments,
+and for this purpose it will be useful to record that \eqref{mgp1} and \eqref{mgp2}
+imply that the following is a martingale:
+\begin{align} \label{mgp3}
+    \nonumber
+    \langle \phi, \eta_t \rangle^2
+    -
+    & \langle \phi, \eta_0 \rangle^2
+    -
+    \int_0^t
+        2 \langle \phi, \eta_s \rangle
+        \left\langle
+            \theta \int_{\IR^d} (\phi(y) - \phi(x)) q_\theta(x, dy)
+            + F(x, \eta_s) \phi(x),
+            \eta_s(dx)
+        \right\rangle
+    ds
+    \\ & {}
+    -
+    \frac{\theta}{N}
+    \int_0^t
+        \left\langle
+            \int_{\IR^d} \phi^2(y) q_\theta(x, dy)
+            +
+            \left(1 + \frac{F(x, \eta_s)}{\theta}\right) \phi^2(x),
+            \eta_s(dx)
+        \right\rangle
+    ds .
 \end{align}
@@
 
-We will require also a second moment bound on the total mass.
-
-\begin{proposition}
-Under the assumptions of Theorem~\ref{TeoremOneStepConvergence} there is a finite constant $C$ (independent of $\epsilon, N, \theta$) such that, for all $t \in [0,T]$ and for big enough $N$ and $\theta$, $\IE[ \langle 1, \eta_t \rangle^2] \leq C$.\label{Prop:SecondMomentMass}
-\end{proposition}
-
-\begin{proof}[of Proposition~\ref{Prop:SecondMomentMass}]
-    % Referring to section~\ref{sec:heuristics} with $f=1$ and $G(m) = m^2$,
-    When the population is in state $\eta$,
-    individuals of mass $1/N$ are born at rate $\theta \langle 1, \eta \rangle$
-    and die at rate $\theta \langle 1 + F/\theta, \eta \rangle$.
-    Similar to the arguments in section~\ref{sec:heuristics} with $f=1$ and $G(m) = m^2$,
-    since $N G(m \pm 1/N) - G(m) = \pm 2m + 1/N$,
+\begin{lemma}
+        \label{lem:SecondMomentMass}
+    Under the assumptions of Theorem~\ref{TeoremOneStepConvergence}
+    there is a finite constant $C$ (independent of $\epsilon, N, \theta$) such that,
+    for all $t \in [0,T]$ and for big enough $N$ and $\theta$,
+    $\IE[ \langle 1, \eta_t \rangle^2] \leq C$.
+\end{lemma}
+
+\begin{proof}[of Lemma~\ref{lem:SecondMomentMass}]
+    Using equation~\eqref{mgp3} with $\phi = 1$,
     \begin{align*}
@@
         \int_0^t
-        \left\{
-            \theta \langle 1, \eta_s \rangle
-            \left( 2 \langle 1, \eta_s \rangle + 1/N \right)
+            2 \langle 1, \eta_s \rangle
+            \langle F(x, \eta_s), \eta_s(dx) \rangle
             +
-            \theta \langle 1 + F/\theta, \eta_s \rangle
-            \left( - 2 \langle 1, \eta_s \rangle + 1/N \right)
-        \right\}
+            \frac{\theta}{N} \langle 2 + F(x, \eta_s)/\theta, \eta_s(dx) \rangle
         ds
-        \right]
-        \\
-        &=
-        \IE[\langle 1, \eta_0 \rangle^2]
-        +
-        \IE\left[
-        \int_0^t \left\{
-            \frac{2\theta}{N} \langle 1, \eta_s \rangle ds
-            -
-            2 \langle F, \eta_s \rangle \left(\langle 1, \eta_s \rangle - \frac{1}{N} \right)
-        \right\} ds \right].
+        \right] .
     \end{align*}
@@
         \leq
-        \frac{C}{(\epsilon^2 + t)^{d/2}}
-        \left(
-            1 + \exp\left(-\frac{\epsilon^2 \theta}{2}\right)
-        \right) .
+        \frac{C}{(\epsilon^2 + t)^{d/2}} .
     \]
@@
     \[
-        C \left(1 + \frac{t}{\epsilon^2}\right)^{d/2} e^{-\delta \theta t}
-        \frac{1}{(\epsilon^2 + t)^{d/2}} e^{-\epsilon^2 \theta / 2} .
+        C \left(1 + \frac{t}{\epsilon^2}\right)^{d/2} e^{-\delta \theta t - \epsilon^2 \theta / 2}
+        \frac{1}{(\epsilon^2 + t)^{d/2}} .
     \]
-    Now, $e^{-\delta \theta t} (1 + t/\epsilon^2)^{d/2}$ is decreasing in $t$
+    Now, $e^{-\delta \theta t - \epsilon^2 \theta / 2} (1 + t/\epsilon^2)^{d/2}$ is decreasing in $t$
     for all $t$ if $\epsilon^2 \theta$ is sufficiently large:
@@
         \left( \frac{d}{2 \epsilon^2} - \left(1 + \frac{t}{\epsilon^2}\right) \delta \theta \right)
-        \left( 1 + \frac{t}{\epsilon^2} \right)^{d/2 - 1} e^{-\delta \theta t} ,
+        \left( 1 + \frac{t}{\epsilon^2} \right)^{d/2 - 1} e^{-\delta \theta t - \epsilon^2 \theta / 2} ,
     \]
@@
     Therfore, the second term in \eqref{eqn:psi_infty_bound} 
-    is bounded by $C e^{-\epsilon^2 \theta / 2} / (\epsilon^2 + t)^{d/2}$
+    is bounded by $C / (\epsilon^2 + t)^{d/2}$
     (for a different constant $C$).
@@
 
-We will need a further comparison of $\psi_t^{\epsilon,x}$ to the heat semigroup,
+We will need further comparisons of $\psi_t^{\epsilon,x}$ to the heat semigroup,
 and for this we will first need the following fact about large deviations
@@
 \begin{lemma}
-    \label{lem:psi_approx_p}
+    \label{Lemma:BoundPsiHS2}
     In the notation of Lemma~\ref{PsiBoundHS},
@@
 
-\begin{proof}[of Lemma~\ref{lem:psi_approx_p}]
-    We will partition into three events according to the value of $\tau(t)$:
+\begin{proof}[of Lemma~\ref{Lemma:BoundPsiHS2}]
+    The three terms on the right hand side of the Lemma
+    correspond to bound obtained by partitioning
+    into three events according to the value of $\tau(t)$:
     let $A_1 = \{ \tau(t) < - (\epsilon^2 + t)/2 \}$,
@@
     Observe that on this event,
-    $\epsilon^2 + t + \tau(t)$ is in the interval
-    $((\epsilon^2 + t)/ 2, (A + 1)(\epsilon^2 + t))$,
+    $\epsilon^2 + t + \tau(t)$ is between
+    $(\epsilon^2 + t)/ 2$ and $(A + 1)(\epsilon^2 + t))$,
     and for any $s$ in this interval,
@@
     Applying the inequality~\eqref{eqn:p_deriv_term2},
-    using the fact that $p_s(x, y) \le C p_{2s}(x,y)$,
+    using the fact that $p_s(x, y) \le \sqrt{2} p_{2s}(x,y)$,
     and then \eqref{eqn:p_bounded_on_interval},
@@
     where the last inequality follows from $2 \epsilon^2 t \le (\epsilon^2 + t)^2$.
+
+    Finally, on the event $A_2 = \{\tau(t) > A(\epsilon^2 + t)\}$,
+    we simply use
+    \begin{align*}
+        \left|
+            p_{\epsilon^2 + t + \tau(t)}(x, y)
+            -
+            p_{\epsilon^2 + t}(x, y)
+        \right|
+        \le
+        \frac{C}{(\epsilon^2 + t)^{d/2}} ,
+    \end{align*}
+    so that
+    \begin{align*}
+        \IE\left[
+        1_{A_2}
+        \left|
+            p_{\epsilon^2 + t + \tau(t)}(x, y)
+            -
+            p_{\epsilon^2 + t}(x, y)
+        \right|
+        \right]
+        \le
+        \frac{C}{(\epsilon^2 + t)^{d/2}}
+        \IP\left\{
+            \tau(t) > A (\epsilon^2 + t)
+        \right\} .
+    \end{align*}
 \end{proof}
 
+The last result will be useful when combined with the next bound for the heat kernel.
+
 \begin{lemma}
-    OLD VERSION, IS WRONG
-For every $x,y \in \IR^d$ and $t>0$ we have,
-\begin{align*}
-|\psi_t^{\epsilon,x}(y) - p_{\epsilon^2+t}(x,y)| &\leq \frac{C}{\epsilon^2 \theta}\left(\psi_t^{\epsilon,x}(y) + p_{\epsilon^2+t}(x,y) + p_{3/2(\epsilon^2+t)}(x,y)+p_{3(\epsilon^2+t)}(x,y) \right)
-\end{align*} \label{Lemma:BoundPsiHS2}
+    \label{Lemma:ContinuityHS}
+Let $s>0, x, y, z\in \IR^d$. The following estimate holds:
+\[
+    |p_s(x,z) - p_s(y,z)|
+    \leq
+    \frac{C|x-y|}{\sqrt{s}} \left(p_{2s}(x,z) + p_{2s}(y,z)\right) ,
+\]
+where the constant $C$ does not depend on $x,y,z$ or $s$.
 \end{lemma}
+
 \begin{proof}
-From Lemma~\ref{PsiBoundHS} we have that $\psi_t^{\epsilon,x} = \IE\left[ p_{N(t)/\theta+\epsilon^2}(x,y) \right]$ with $N(t)$ a Poisson process of rate $\theta$.
-We write $\tau(t) = N(t)/\theta - t$, which has mean $0$ and variance $t/\theta$.
-In particular,
-equation~\eqref{eq:IneqConcentrationT} says that
-\begin{equation}
-\IP[|\tau(t)| > (\epsilon^2+t)/2] \leq \frac{4t}{\theta(\epsilon+t)^2} \leq \frac{2}{\theta \epsilon^2} \label{eq:ConcentrationTau}
-\end{equation}
-Consider first the event in which $|\tau(t)| \leq (\epsilon^2+t)/2$. For such $\tau$ we have that,
-\begin{equation} |p_{\epsilon^2+t+\tau(t)}(x,y) - p_{\epsilon^2+t}(x,y) | = |\tau(t)| \left| \frac{\partial p_s(x,y)}{\partial s} \right| \end{equation}
-for some $s \in (\epsilon^2+t-|\tau(t)|, \epsilon^2+t+|\tau(t)|)$. Without loss of generality we suppose $x=0$ and write $p_s(y):=p_s(0,y)$ to simplify notation. Then,
-\[ \frac{\partial}{\partial s} \frac{1}{(2 \pi s)^{d/2}} \exp(-\frac{\| y \|^2}{2s}) = - \frac{d}{s} p_s(y) + \frac{y^2}{2 s^2} p_s(y)\]
-Now for $s \in ((\epsilon^2+t)/2,3(\epsilon^2+t)/2)$ we have,
-\[ p_s(y) \leq 3^{d/2} p_{3/2(\epsilon^2+t)}(y) \, \, ,\text{ and } \, \, \frac{1}{s} \leq \frac{2}{\epsilon^2+t}\]
-Morever, since $\frac{y^2}{4s} e^{-y^2/4s} \leq 1$ for all $y$,
-\begin{align*}
-\frac{y^2}{s^2}  p_s(y) &= \frac{1}{s} \frac{4}{(2 \pi s)^{d/2}}\exp(-\frac{y^2}{4s}) \frac{y^2}{4s} \exp( - \frac{y^2}{4 s}) \\ &\leq  4\frac{ 2^{d/2}}{s} p_{2s}(y) \\ &\leq \frac{4}{s}  2^{d/2} 3^{d/2} p_{3(\epsilon^2+t)}(y)  \\ & \leq 8 \frac{ 2^{d/2} 3^{d/2}}{\epsilon^2+t} p_{3(\epsilon^2+t)}(y)
-\end{align*}
-Combining these estimates
-    \comment{Alison says: Not quite. Can bound the second term this way, but for the first it doesn't work.
-    So use a uniform bound of $1/\varepsilon^d$ and then a bound on the probability that $|\tau|$
-    is this big based on the moment generating function.
-    We end up needing $|\log \varepsilon| / (\theta \varepsilon^2) \to 0$.
-    }
-\begin{align*}
-|\psi_t^{\epsilon,x}(y)-p_{\epsilon^2+t}(x,y)|
+    Expanding the difference of two squares,
+    \begin{align*}
+        e^{- \frac{(y-z)^2}{2 s}}
+        -
+        e^{- \frac{(x-z)^2}{2 s}}
         &=
-    | \mathbb{E}\left[ (1_{|\tau(t)| > (\epsilon^2+t)/2}+1_{|\tau(t)| \leq (\epsilon^2+t)/2})(p_{t+\epsilon^2+\tau(t)}(x,y)-p_{\epsilon^2+t}(x,y)) \right]| \\
-    &\leq
-    \IP[|\tau(t)| \geq (\epsilon^2+t)/2] \IE[p_{t+\epsilon^2+\tau(t)}(x,y) + p_{\epsilon^2+t})(x,y)] \\
-    &+
-    \mathbb{E}\left[ \frac{|\tau(t)|}{\epsilon^2+t}\right]\left( 2d3^{d/2} p_{3(\epsilon^2+t)/2} (x,y) + 4 2^{d/2}3^{d/2} p_{3(\epsilon^2+t)}(x,y)\right) \\
-    & \leq
-    \frac{2}{\theta \epsilon^2} (\psi_t^{\epsilon,x}(y)+p_{\epsilon^2+t}(x,y)) + \mathbb{E}\left[ \frac{|\tau(t)|}{\epsilon^2+t}\right] C (p_{3/2(\epsilon^2+t)}(x,y) + p_{3(\epsilon^2+t)}(x,y))
-\end{align*}
-Finally, since
-\[ \mathbb{E}\left[ \frac{|\tau(t)|}{\epsilon^2+t}\right] \leq \mathbb{E}\left[ \frac{\tau(t)^2}{\epsilon^2+t}\right] \leq \frac{1}{2 \theta \epsilon^2} \]
-the result follows.
+        \left(
+            e^{-\frac{(y-z)^2}{4 s}}
+            -
+            e^{-\frac{(x-z)^2}{4 s}}
+        \right)
+        \left(
+            e^{-\frac{(y-z)^2}{4 s}}
+            +
+            e^{-\frac{(x-z)^2}{4 s}}
+        \right) .
+    \end{align*}
+    % % (big version of the previous equation:)
+    % \begin{align*}
+    %     &\exp\left( - \frac{(y-z)^2}{2 s} \right)
+    %     -
+    %     \exp\left( - \frac{(x-z)^2}{2 s} \right)
+    %     \\ &=
+    %     \left(
+    %         \exp\left(-\frac{(y-z)^2}{4 s} \right)
+    %         -
+    %         \exp\left(-\frac{(x-z)^2}{4 s} \right)
+    %     \right)
+    %     \left(
+    %         \exp\left(-\frac{(y-z)^2}{4 s} \right)
+    %         +
+    %         \exp\left(-\frac{(x-z)^2}{4 s} \right)
+    %     \right) .
+    % \end{align*}
+    By using the Intermediate Value Theorem we can write the right hand side as
+    \[
+        (y-x)
+        \left( - \frac{2(w-z)}{4s} \exp\left(-\frac{(w-z)^2}{4s}\right)\right)
+        (4 \pi s)^{d/2}
+        \left( p_{2s}(y,z)+p_{2s}(x,z) \right)
+    \]
+    for some $w \in [y,z]$.
+    Using the fact that $x e^{-x^2}$ is uniformly bounded,
+    we can bound the first bracket in the last equation by $C/\sqrt{s}$, and the result follows.
 \end{proof}
-The last result will be useful when combined with the next bound for the heat kernel.
-\begin{lemma}
-Let $s>0, x, y, z\in \IR^d$. The following estimate holds
-\[ |p_s(x,z) - p_s(y,z)| \leq \frac{C|x-y|}{\sqrt{s}} \left(p_{2s}(x,z) + p_{2s}(y,z)\right) \]
-where the constant $C$ does not depend on $x,y,z$ or $s$.\label{Lemma:ContinuityHS}
-\end{lemma}
-\begin{proof}
-Expanding the difference of two squares we can rewrite,
-\begin{align*}
-&\exp\left(-\frac{(y-z)^2}{2 s} \right)-\exp\left(-\frac{(x-z)^2}{2 s} \right) \\ &= \left(\exp\left(-\frac{(y-z)^2}{4 s} \right)-\exp\left(-\frac{(x-z)^2}{4 s} \right) \right)\left(\exp\left(-\frac{(y-z)^2}{4 s} \right)+\exp\left(-\frac{(x-z)^2}{4 s} \right) \right)
-\end{align*}
-by using the Intermediate Value Theorem we can write the right hand side as,
-\[ (y-x) \left( - \frac{2(w-z)}{4s} \exp\left(-\frac{(w-z)^2}{4s}\right)\right) 2^{d/2}\left( p_{2s}(y,z)+p_{2s}(x,z) \right)\]
-for some $w \in [y,z]$. Using the fact that $x e^{-x^2}$ is uniformly bounded we can bounded the first bracket in the last equation by $C/\sqrt{s}$ and the result follows.
-\end{proof}
 
 \paragraph{The martingale problem for a time dependent function.}
-Before proceeding we make the following observation. For any time, dependent function $\phi_t(x)$ the martingale problem for $\eta_t$, (\ref{mgp1}), gives that
-\comment{Alison says: not sure this needs spelling out? (Also, $\partial_t \phi_{t-s}$ is a slightly confusing way to write it out but OK.}
+Before proceeding we make the following observation.
+For any time-dependent function $\phi_t(x)$
+with time derivative $\dot \phi_t(x) = \frac{d}{dt} \phi_t(x)$,
+the martingale problem for $\eta_t$, (like \ref{mgp1}),
+is
+% \comment{Alison says: not sure this needs spelling out?}
 \begin{align}
-\langle \eta_t(dx), \phi_0(x)\rangle &= \langle \eta_0(dx), \phi_t(x)\rangle +  M_t(\phi_\cdot(\cdot)) - \int_0^t \langle \partial_t \phi_{t-s}(x), \eta_s(dx) \rangle  ds \nonumber \\ & + \int_0^t \langle \mathcal{L}^\theta \phi_{t-s}(x), \eta_s(dx) \rangle ds+ \int_{0}^t \langle \phi_{t-s}(x)F (\rho_\epsilon*\eta_s)(x) ) , \eta_s(dx) \rangle ds \label{timeMGP}
+        \label{timeMGP}
+    \langle \phi_0(x), \eta_t(dx) \rangle
+    &= \nonumber 
+    \langle \phi_t(x), \eta_0(dx) \rangle
+    +
+    M_t(\phi_\cdot(\cdot))
+    +
+    \int_0^t \langle \mathcal{L}^\theta \phi_{t-s}(x) - \dot \phi_{t-s}(x), \eta_s(dx) \rangle ds
+    \\ & {}
+    +
+    \int_{0}^t \langle \phi_{t-s}(x) F(x, \eta_s) , \eta_s(dx) \rangle ds ,
 \end{align}
-where $M_t(\phi_\cdot(\cdot))$ has quadratic variation:
-\[ [M(\phi_\cdot(\cdot))]_t = \frac{\theta}{N}\int_0^t \langle \int_{\IR^d} \phi_{t-s}(z)^2 q_\theta(y,dz) + \left( 1 + \frac{F(\rho_\epsilon*\eta_s(y))}{\theta}\right) \phi_{t-s}(y)^2, \eta_s(dy) \rangle ds \]
+where $M_t(\phi_\cdot(\cdot))$ has quadratic variation
+\begin{align}
+        \label{timeMGP2}
+    [M(\phi_\cdot(\cdot))]_t
+    =
+    \frac{\theta}{N} \int_0^t \langle
+        \int_{\IR^d} \phi_{t-s}(z)^2 q_\theta(y,dz)
+        +
+        \left( 1 + \frac{F(y, \eta_s)}{\theta}\right) \phi_{t-s}(y)^2,
+    \eta_s(dy) \rangle ds .
+\end{align}
 
@@
 \paragraph{Bounds for $\{ \rho_\epsilon * \eta_s (x)\}_{0 \leq s \leq T}$}
-\begin{lemma} \label{FirstBoundLocalDensity}
-Under the conditions of Theorem~\ref{TeoremOneStepConvergence} there is a constant $C>0$ (independent of $\epsilon, N, \theta, x$ and $T$) such that,
+
+\begin{lemma}
+        \label{FirstBoundLocalDensity}
+    Under the conditions of Theorem~\ref{TeoremOneStepConvergence}
+    there is a constant $C>0$ (independent of $\epsilon$, $N$, $\theta$, and $x$) such that,
     \[ \IE[ \rho_\epsilon*\eta_t(x) ] < C \]
@@
 \end{lemma}
+
 \begin{proof}
-Recall that $\psi_t^{\epsilon,x}$ is the solution of (\ref{AlmostHeatEquation}) with initial condition $\psi_0^{\epsilon,x}(y)=\rho_\epsilon(y-x)$.
-By replacing $\phi_t$ with $\psi_t^{\epsilon,x}$ in (\ref{timeMGP}) we can write,
+    Recall that $\psi_t^{\epsilon,x}$ is the solution of (\ref{AlmostHeatEquation})
+    with initial condition $\psi_0^{\epsilon,x}(y)=\rho_\epsilon(y-x)$.
+    By replacing $\phi_t$ with $\psi_t^{\epsilon,x}$ in (\ref{timeMGP}) we can write
+    for each $x$
     \begin{align}
-(\rho_\epsilon*\eta_t(x)) = \langle \psi_t^{\epsilon,x}(y), \eta_0(dy) \rangle  + \int_0^t \langle \psi_{t-s}^{\epsilon,x}(y) F(\rho_\epsilon*\eta_s(y)), \eta_s(dy) \rangle ds + M_t(x) \label{MartingaleProblemMolifier}
+            \label{MartingaleProblemMolifier}
+        \rho_\epsilon*\eta_t(x)
+        =
+        \langle \psi_t^{\epsilon,x}(y), \eta_0(dy) \rangle
+        +
+        \int_0^t \langle
+            \psi_{t-s}^{\epsilon,x}(y) F(y, \eta_s),
+        \eta_s(dy) \rangle ds
+        +
+        M_t^x .
     \end{align}
-where $F$ is uniformly bounded above. Hence, if we take expectations,
+    First recall that our second assumptions on $\eta_0$
+    was (ii) $\|\rho_\epsilon * \eta_0\|_\infty < C$.
+    Since 
+    \[
+        \langle \psi_t^{\epsilon,x}(y), \eta_0(dy) \rangle
+        =
+        \IE \left[ \langle
+            p_{\epsilon^2 + T(t)}(x, y), \eta_0(dy)
+        \rangle \right]
+        =
+        \IE \left[ \int_{\IR^d} p_{T(t)}(x, y) \rho_\epsilon * \eta_0(y) dy \right],
+    \]
+    this implies that
+    $\langle \psi_t^{\epsilon,x}(y), \eta_0(dy) \rangle \le C$.
+    Since $F(x)$ is uniformly bounded above,
+    if we take expectations and use Lemma~\ref{Lemma:UniformlyBoundedMass},
     \begin{align}
     \IE[\rho_\epsilon * \eta_t(x)]
-    &\le
-    \IE[\langle \psi_t^{\epsilon,x}(y), \eta_0(dy) \rangle] + C \IE[\int_0^t \langle \psi_{t-s}^{\epsilon,x}(y), \eta_s(dy) \rangle ds] \nonumber \\ & \leq  \IE[\langle p_{\epsilon^2+T(t)}(x,y),\eta_0(dy)\rangle] + C \int_0^t \Vert \psi_{t-s}^{\epsilon,0} \Vert_\infty \IE[\sup_{0 \leq s \leq t} \langle 1, \eta_s(dy) \rangle] ds \\ & \leq C + C \int_0^t \Vert \psi_{t-s}^{\epsilon,0} \Vert_\infty ds \label{BoundForMolifier}
+        &\le \label{BoundForMollifierStart}
+        \IE[\langle \psi_t^{\epsilon,x}(y), \eta_0(dy) \rangle]
+        +
+        C \IE\left[\int_0^t \langle \psi_{t-s}^{\epsilon,x}(y), \eta_s(dy) \rangle ds\right]
+        \\ & \nonumber
+        \leq
+        C
+        +
+        C \int_0^t \Vert \psi_{t-s}^{\epsilon,0} \Vert_\infty
+        \IE\left[\sup_{0 \leq s \leq t} \langle 1, \eta_s(dy) \rangle\right] ds
+        \\ &
+        \leq \label{BoundForMollifier}
+        C + C \int_0^t \Vert \psi_{t-s}^{\epsilon,0} \Vert_\infty ds
     \end{align}
-Where in the last inequality we used Lemma~\ref{Lemma:UniformlyBoundedMass} and our first assumption on the initial condition.
-Furthermore, using Lemma \ref{PsiBoundHS} we can bound $\Vert \psi_{t-s}^{\epsilon,0} \Vert_\infty$ by $C (t-s+\epsilon^2)^{-d/2}$.
-In dimension one the right hand side is immediately uniformly bounded.
+    Now, using Lemma~\ref{PsiBoundHS}, % since $\epsilon^2 \theta \to \infty$,
+    we can bound $\| \psi_{t-s}^{\epsilon,0} \|_\infty$
+    by $C (t-s+\epsilon^2)^{-d/2}$.
+    In dimension one the right hand side of \eqref{BoundForMollifier} is immediately uniformly bounded.
     For $d=2$ we can iterate.
-By using again the martingale problem and the same arguments we used to get (\ref{BoundForMolifier}) we get,
+    By using again the martingale problem and the same arguments
+    we used to get \eqref{BoundForMollifier} we get,
+    % \comment{Alison suggests that writing the term on the right instead as
+    %     $C \IE[\int_0^t \langle \psi_{t-u}^{\epsilon,x}(y), \eta_u(dy) \rangle du ]$
+    %     would look more natural?}
     \begin{equation} \label{IterationBoundPsi}
-\IE[\langle \psi_{t-s}^{\epsilon,x}, \eta_s(dy)\rangle] \leq \IE[\langle \psi_{t}^{\epsilon,x}(y), \eta_0(dy) \rangle]  + C \int_0^s \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du
-\end{equation}
-Hence, using (\ref{IterationBoundPsi}) in (\ref{BoundForMolifier}) gives
-\begin{align*}
-\IE[ \rho_\epsilon * \eta_t(x)  ] &\leq \IE[\langle \psi_t^{\epsilon,x}(y), \eta_0(dy) \rangle] + \int_0^t C\langle \psi_{t}^{\epsilon,x}, \eta_0(dy)\rangle ds + C^2 \int_0^t \int_0^s  \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du ds \\ &= (1+Ct) \IE[ \langle \psi_t^{\epsilon,x}, \eta_0(dy) \rangle] + C^2 \int_0^t (t-u) \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du \\ &\leq C(1+t) + C^2 \int_0^t (t-u) \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du
-\end{align*}
-which again is uniformly bounded using Lemma \ref{PsiBoundHS}. It is easy to see that, iterating, we can prove a uniform bound in any dimension.
-
+        \IE[\langle \psi_{t-s}^{\epsilon,x}, \eta_s(dy)\rangle]
+        \leq
+        \IE[\langle \psi_{t}^{\epsilon,x}(y), \eta_0(dy) \rangle]
+        +
+        C \int_0^s \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du
+    \end{equation}
+    Hence, using \eqref{IterationBoundPsi} in \eqref{BoundForMollifierStart} gives
+    \begin{align*}
+        \IE[ \rho_\epsilon * \eta_t(x) ]
+        &\leq
+        \IE[ \langle \psi_t^{\epsilon,x}(y), \eta_0(dy) \rangle]
+        +
+        \int_0^t C\langle \psi_{t}^{\epsilon,x}, \eta_0(dy)\rangle ds
+        +
+        C^2 \int_0^t \int_0^s  \| \psi_{t-u}^{\epsilon,0} \|_\infty du ds
+        \\ &=
+        (1+Ct) \IE[ \langle \psi_t^{\epsilon,x}, \eta_0(dy) \rangle]
+        +
+        C^2 \int_0^t (t-u) \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du
+        \\ &\leq
+        C(1+t) + C^2 \int_0^t (t-u) \| \psi_{t-u}^{\epsilon,0} \|_\infty du ,
+    \end{align*}
+    which again is uniformly bounded using Lemma \ref{PsiBoundHS}.
+    It is easy to see that, iterating, we can prove a uniform bound in any dimension. 
 \end{proof}
 
-\begin{remark} \label{Remark:BoundLocalDensity}
-It is convenient to remark that from $\IE\left[ \langle \rho_\epsilon(x,y), \eta_t(dy) \rangle \right]$ being bounded it follows that $\IE[ \langle p_{s+\epsilon^2}(x,y), \eta_t(dy) \rangle ]$ is bounded for all $s>0$.
-Indeed, this follows from writing $p_{s+\epsilon^2} = p_s * p_{\epsilon^2}$ and integrating.
-\end{remark}
+\begin{corollary} \label{cor:BoundLocalDensity}
+    Under the conditions of Theorem~\ref{TeoremOneStepConvergence}
+    there is a constant $C > 0$,
+    independent of $\epsilon$, $N$, $\theta$, and $x$,
+    such that
+    \[
+        \IE[ \langle \psi^{\epsilon,x}_s(y), \eta_t(dy) \rangle ]
+        \le C
+    \]
+    for all $s \ge 0$, $t \in [0, T]$ and $x \in \IR^d$.
+\end{corollary}
+
+\comment{This was previously just a Remark, but I wanted to use it below
+    in a place where we have to be careful of exactly what it's uniform over,
+    so I wrote out a proof.}
+
+\begin{proof}[of Corollary~\ref{cor:BoundLocalDensity}]
+    For any random variable $X$ independent of $\eta$,
+    Lemma~\ref{FirstBoundLocalDensity} implies that
+    $\IE[\rho_\epsilon * \eta_t(X)] = \IE[\langle p_{\epsilon^2}(X, y), \eta_t(dy)] \le C$.
+    The Corollary follows immediately 
+    by taking $X$ to have density $p_{T(s)}(x, \cdot)$, since
+    \begin{align*}
+        \IE[ \langle \psi^{\epsilon,x}_s(y), \eta_t(dy)\rangle ]
+        =
+        \IE[ \langle p_{T(s)+\epsilon^2}(x,y), \eta_t(dy) \rangle ]
+        =
+        \IE\left[ \int_{\IR^d} 
+            p_{T(s)}(x, z)
+            \langle p_{\epsilon^2}(z, y), \eta_t(dy) \rangle
+        dz \right] ,
+    \end{align*}
+    with $T(s)$ independent of $\eta$.
+\end{proof}
 
 \begin{corollary}
-Let $(M_t(x))_{t \geq 0}$ be the martingale in (\ref{MartingaleProblemMolifier}). Then
-\[ \IE\left[ [M(x)]_t \right] \leq \frac{C \theta}{ N \epsilon^{d}} \]
+    Let $(M_t^x)_{t \geq 0}$ be the martingale in (\ref{MartingaleProblemMolifier}).
+    Then
+    \[
+        \IE\left[ [M^x]_t \right] \leq \frac{C \theta}{ N \epsilon^{d}} ,
+    \]
     where $C$ is independent of $\epsilon,\theta,N$. \label{Cor:ControlQVMQ}
 \end{corollary}
+
 \begin{proof}
-We can explicitly write the quadratic variation of $M_t$ as
-\[ [M(x)]_t = \frac{\theta}{N} \int_0^t \langle \int_{\IR^d} \psi_{t-s}^{\epsilon,x}(z)^2 q_\theta(y,dz) + \left(1+\frac{F(\rho_\epsilon * \eta_s(y))}{\theta}\right)\psi_{t-s}^{\epsilon,x}(y)^2, \eta_s(dy) \rangle  ds\]
-so Lemma~\ref{PsiBoundHS} gives the following bound,
-\[ \psi_{t-s}^{\epsilon,x}(y)^2 \leq \psi_{t-s}^{\epsilon,x}(y) \frac{C}{(\epsilon^2+t-s)^{d/2}} \leq \frac{C}{\epsilon^d} \psi_{t-s}^{\epsilon,x}(y). \]
-Hence, by using the last inequality and the upper bound on $F(x)1_{\{x > 0\}}$, we deduce that:
-\begin{align}
-[M(x)]_t &\leq \frac{C \theta}{\epsilon^d N} \int_0^t \left\{  \langle \int \psi_{t-s}^{\epsilon,x}(z) q_\theta(y,dz), \eta_s(dy) \rangle + \langle \psi_{t-s}^{\epsilon,x}(y), \eta_s(dy)\rangle \right\} ds
-\label{QuadVarBound} \end{align}
-Taking expectations and using the bound of Lemma~\ref{FirstBoundLocalDensity} we get the result.
+    We can explicitly write the quadratic variation of $M^x_t$ as
+    \[
+        [M^x]_t
+        =
+        \frac{\theta}{N} \int_0^t \langle
+            \int_{\IR^d} \psi_{t-s}^{\epsilon,x}(z)^2 q_\theta(y,dz)
+            +
+            \left(1 + \frac{F(y, \eta_s)}{\theta}\right) \psi_{t-s}^{\epsilon,x}(y)^2,
+        \eta_s(dy) \rangle  ds .
+    \]
+    Lemma~\ref{PsiBoundHS} implies that $\psi_{t-s}^{\epsilon,x}(y) \le C \epsilon^{-d}$.
+    Using this and the fact that $F(x)$ is bounded above,
+    \begin{align} \label{QuadVarBound}
+    [M^x]_t
+        &\leq
+        \frac{C \theta}{N \epsilon^d} \int_0^t \left\{
+            \langle \int \psi_{t-s}^{\epsilon,x}(z) q_\theta(y,dz), \eta_s(dy) \rangle
+            +
+            \langle \psi_{t-s}^{\epsilon,x}(y), \eta_s(dy)\rangle
+        \right\} ds 
+    \end{align}
+    We can now take expectations and use Corollary~\ref{cor:BoundLocalDensity} to prove the result.
 \end{proof}
 
-By reusing the computations in the last Corollary we can prove a certain integrability of $M_t(x)$.
-\begin{proposition}
-Let $(M_t(x))_{t \geq 0}$ be the martingale in (\ref{MartingaleProblemMolifier}). Then
-\[ \int \IE\left[ M_t(x)^2 \right] dx \leq \frac{C \theta}{ N \epsilon^{d}} \]
-where $C$ is independent of $\epsilon,\theta,N$. \label{IntegrabilityOfM}
+By re-using the computations in the last Corollary we can prove a certain integrability of $M_t^x$.
+
+\begin{proposition}  \label{IntegrabilityOfM}
+    Let $(M_t^x)_{t \geq 0}$ be the martingale in (\ref{MartingaleProblemMolifier}).
+    Then
+    \[
+        \int_{\IR^d} \IE\left[ (M_t^x)^2 \right] dx \leq \frac{C \theta}{ N \epsilon^{d}} ,
+    \]
+    where $C$ is independent of $\epsilon$, $\theta$, and $N$.
 \end{proposition}
-\begin{proof}
-Recall that since $M_t(x)$ is a martingale, then,
-\[ \IE\left[ M_t(x)^2 \right] = \IE\left[ [M(x)]_t \right].  \]
+
+\begin{proof}[of Proposition \ref{IntegrabilityOfM}]
+    Recall that since $M^x_t$ is a martingale, then,
+    \[
+        \IE\left[ (M_t^x)^2 \right] = \IE\left[ [M^x]_t \right].
+    \]
     Hence, using (\ref{QuadVarBound}),
     \begin{align*}
-\int &\IE\left[ M_t(x)^2 \right] dx \\ & \leq \frac{C \theta}{\varepsilon^d N} \int \int_0^t \IE\left[ \langle \int \psi_{t-s}^{\epsilon,x}(z) q_\theta(y,dz), \eta_s(dy) \rangle + \langle \psi_{t-s}^{\epsilon,x}(y), \eta_s(dy)\rangle \right] ds  dx \\ &=  \frac{C \theta}{\varepsilon^d N}  \int_0^t \IE \left[  \langle \int \left( \int \psi_{t-s}^{\epsilon,x}(z) dx \right) q_\theta(y,dz), \eta_s(dy) \rangle + \langle \left( \int  \psi_{t-s}^{\epsilon,x}(y) dx \right), \eta_s(dy)\rangle \right] ds.
-\end{align*}
-Now using Lemma~\ref{PsiBoundHS} we have that,
-\begin{align*}
-\int \psi_t^{\epsilon, x}(y) dx & = \int \IE[p_{\epsilon^2+T(t)}(x,y)] dx \\ &= \IE[ \int p_{\epsilon^2+T(t)}(y,x) dx ] = 1.
+        \int_{\IR^d} &\IE\left[ M_t(x)^2 \right] dx
+        \\ & \leq
+        \frac{C \theta}{\varepsilon^d N} \int \int_0^t
+            \IE\left[ \langle \int \psi_{t-s}^{\epsilon,x}(z) q_\theta(y,dz), \eta_s(dy) \rangle
+                + \langle \psi_{t-s}^{\epsilon,x}(y),
+            \eta_s(dy)\rangle \right]
+        ds dx
+        \\ &= 
+        \frac{C \theta}{\varepsilon^d N} \int_0^t \IE \left[
+            \langle \int \left( \int \psi_{t-s}^{\epsilon,x}(z) dx \right) q_\theta(y,dz),
+            \eta_s(dy) \rangle
+            +
+            \langle \left( \int \psi_{t-s}^{\epsilon,x}(y) dx \right), \eta_s(dy)\rangle
+        \right] ds.
+    \end{align*}
+    Now, since (by Lemma~\ref{PsiBoundHS}) $\psi_t^{\epsilon, x}(y) = \IE[p_{\epsilon^2+T(t)}(x,y)]$,
+    note that
+    \begin{align*}
+        \int
+            \psi_t^{\epsilon, x}(y) dx
+            & =
+            % \int \IE[p_{\epsilon^2+T(t)}(x,y)] dx
+            % \\ &=
+            \IE\left[ \int p_{\epsilon^2+T(t)}(y,x) dx \right]
+            = 1.
     \end{align*}
@@
     \begin{align*}
-\int \IE\left[ M_t(x)^2 \right] dx & \leq  \frac{C \theta}{\varepsilon^d N}  \int_0^t \IE \left[  \langle \int  q_\theta(y,dz), \eta_s(dy) \rangle + \langle 1, \eta_s(dy)\rangle \right] ds.
-\\ & \leq \frac{C \theta}{\varepsilon^d N} \int_0^t \IE[ \langle 1, \eta_s(dy) \rangle ] ds \\ & \leq T \frac{C \theta}{ \varepsilon^d N}
+    \int \IE\left[ M_t(x)^2 \right] dx
+        & \leq 
+        \frac{C \theta}{\varepsilon^d N} 
+        \int_0^t \IE \left[ 
+            \langle \int  q_\theta(y,dz), \eta_s(dy) \rangle
+            +
+            \langle 1, \eta_s(dy)\rangle
+        \right] ds
+        \\ & =
+        2 \frac{C \theta}{\varepsilon^d N}
+        \int_0^t \IE[ \langle 1, \eta_s(dy) \rangle ] ds
+        \\ & \leq
+        t \frac{2 C \theta}{ \varepsilon^d N} ,
     \end{align*}
@@
 
-By doing the same pattern used to prove Proposition~\ref{Prop:SecondMomentMass} (replacing the use of equation (\ref{eq:MPTotalMass}) by equation (\ref{MartingaleProblemMolifier}) and the used of equation \ref{eq:quadvarMass} by Corollary~\ref{Cor:ControlQVMQ}) we can get the following result.
-\comment{Alison writes: the proof of Proposition~\ref{Prop:SecondMomentMass} above was wrong.
+% By doing the same pattern used to prove Lemma~\ref{lem:SecondMomentMass} (replacing the use of equation (\ref{eq:MPTotalMass}) by equation (\ref{MartingaleProblemMolifier}) and the used of equation \ref{eq:quadvarMass} by Corollary~\ref{Cor:ControlQVMQ}) we can get the following result.
+
+\comment{Alison writes: previously we just referred to the proof of Lemma~\ref{lem:SecondMomentMass},
+but that was wrong.
 I think using $\theta/(N \varepsilon^d) \to 0$ this is easy, but should maybe write it out.}
 
+\comment{Peter writes: here is a proof! Maybe it's right?
+It's straightforward given everything else we do,
+but the expressions are a bit lengthy thanks to the need to have $x_1 \neq x_2$ below.
+We could replace the proof with another short description?}
+
 \begin{proposition}
-Under the assumptions of Theorem~\ref{TeoremOneStepConvergence} there is a finite constant $C$ (independent of $\epsilon, N, \theta$) such that, for all $t \in [0,T]$, $x \in \IR^d$ and for big enough $N$ and $\theta$, $\IE[ (\rho_\epsilon*\eta_t(x))^2] \leq C$.\label{Prop:SecondMomentDensity}
+        \label{Prop:SecondMomentDensity}
+    Under the assumptions of Theorem~\ref{TeoremOneStepConvergence}
+    there is a finite constant $C$ (independent of $\epsilon, N, \theta$) such that,
+    for all $t \in [0,T]$, $x \in \IR^d$ and for big enough $N$ and $\theta$,
+    $\IE[ (\rho_\epsilon*\eta_t(x))^2] \leq C$.
 \end{proposition}
 
+\begin{proof}[of Proposition~\ref{Prop:SecondMomentDensity}]
+    In fact, we will prove that
+    \begin{align*}
+        \sup_{x_1, x_2} \IE\left[
+            \langle \psi^{\epsilon,x_1}_0(y), \eta_t(dy) \rangle
+            \langle \psi^{\epsilon,x_2}_0(y), \eta_t(dy) \rangle
+        \right]
+        \le C .
+    \end{align*}
+    The martingale properties~\eqref{timeMGP} and~\eqref{timeMGP2} imply that
+    \begin{align*}
+        &
+        \IE\left[
+            \langle \psi^{\epsilon,x_1}_0(y), \eta_t(dy) \rangle
+            \langle \psi^{\epsilon,x_2}_0(y), \eta_t(dy) \rangle
+        \right]
+        =
+        \IE\left[
+            \langle \psi^{\epsilon,x_1}_t(y), \eta_0(dy) \rangle
+            \langle \psi^{\epsilon,x_2}_t(y), \eta_0(dy) \rangle
+        \right]
+        \\ & \qquad {}
+        +
+        \int_0^t 2 \IE\left[
+            \langle \psi^{\epsilon,x_1}_{t-s}(y), \eta_s(dy) \rangle
+            \langle \psi^{\epsilon,x_2}_{t-s}(y) F(y, \eta_s), \eta_s(dy) \rangle
+        \right. \\ & \qquad \qquad \qquad \left. {} 
+            +
+            \langle \psi^{\epsilon,x_2}_{t-s}(y), \eta_s(dy) \rangle
+            \langle \psi^{\epsilon,x_1}_{t-s}(y) F(y, \eta_s), \eta_s(dy) \rangle
+            ,
+            \eta_s(dy) \rangle
+        \right] ds
+        \\ & \qquad {}
+        +
+        \int_0^t \frac{\theta}{N} \IE\left[
+            \left\langle 
+                \int_{\IR^d}
+                    \psi^{\epsilon,x_1}_{t-s}(z)
+                    \psi^{\epsilon,x_2}_{t-s}(z)
+                    q_\theta(y, dz)
+                +
+                \left(1 + F(y, \eta_s)/\theta \right)
+                    \psi^{\epsilon,x_1}_{t-s}(y)
+                    \psi^{\epsilon,x_2}_{t-s}(y)
+                ,
+                \eta_s(dy)
+            \right\rangle
+        \right] ds .
+    \end{align*}
+    The first term is bounded by our assumptions on $\eta_0$.
+    Since $F$ is bounded above, the second term is bounded by
+    \begin{align*}
+        &C \int_0^t \IE\left[
+            \langle \psi^{\epsilon,x_1}_{t-s}(y), \eta_s(dy) \rangle
+            \langle \psi^{\epsilon,x_2}_{t-s}(y), \eta_s(dy) \rangle
+        \right] ds
+        \\
+        &\qquad =
+        C \int_0^t
+        \int_{\IR^d} \int_{\IR^d}
+            \IE\left[
+                p_{T(t-s)}(x_1, z_1) p_{T(t-s)}(x_2, z_2)
+                (\rho_\epsilon * \eta_s(z_1))
+                (\rho_\epsilon * \eta_s(z_2))
+            \right] ds
+        dz_1 dz_2
+        \\
+        &\qquad \le
+        C \int_0^t
+        \sup_{z_1, z_2}
+            \IE\left[
+                (\rho_\epsilon * \eta_s(z_1))
+                (\rho_\epsilon * \eta_s(z_2))
+            \right] ds
+    \end{align*}
+
+    Using Corollary~\ref{cor:BoundLocalDensity},
+    the third term is bounded by a constant times
+    \begin{align*}
+        \int_0^t
+            \|\psi^{\epsilon,x}_{t-s}\|_\infty
+            \IE[ \langle \psi^{\epsilon,x}_{t-s}(y), \eta_s(dy) ]
+        ds 
+        \le
+        C \int_0^t \|\psi^{\epsilon,x}_{t-s}\|_\infty ds ,
+    \end{align*}
+    which can be bounded following the same iterative argument
+    as we used for equation~\ref{BoundForMollifierStart}.
+
+    This leaves us with
+    \begin{align*}
+        \sup_{x_1, x_2} \IE\left[
+            \langle \psi^{\epsilon,x_1}_0(y), \eta_t(dy) \rangle
+            \langle \psi^{\epsilon,x_2}_0(y), \eta_t(dy) \rangle
+        \right]
+        \le C  + C \int_0^t
+            \sup_{x_1, x_2} \IE\left[
+                \langle \psi^{\epsilon,x_1}_0(y), \eta_t(dy) \rangle
+                \langle \psi^{\epsilon,x_2}_0(y), \eta_t(dy) \rangle
+            \right]
+            ds,
+    \end{align*}
+    and so we can apply Gronwall's inequality.
+\end{proof}
+
 \paragraph{$C$-tightness of $\rho_\epsilon * \eta_t(x) dx$ }
+
 \begin{lemma}
-Under the assumptions of Theorem~\ref{TeoremOneStepConvergence} the sequence of measure valued process $\{ \rho*\eta_t(x) dx \}_{t \geq 0}$ (taking values in $D([0,T], \mathcal{M}_F(\IR^d))$ is $C$-tight.
+        \label{lem:density_tightness}
+    Under the assumptions of Theorem~\ref{TeoremOneStepConvergence}
+    the sequence of measure valued processes $\{ \rho*\eta_t(x) dx \}_{t \geq 0}$
+    (taking values in $D([0,T], \measures)$ is $C$-tight.
 \end{lemma}
-\begin{proof}
+
+\comment{Peter: what's $C$-tightness?}
+
+\begin{proof}[of Lemma~\ref{lem:density_tightness}]
 
@@
     \comment{Alison writes: no it's not weak - this would be vague convergence. Take $f \in C^2$ to mean bounded first and second derivatives, which is weak convergence.}
-For this note that,
-\begin{align*}
-\int f(x) \rho_\epsilon * \eta_t(x) dx &= \int \int f(x) \rho_\epsilon (x-y) \eta(dy) dx \\ & = \langle \int f(x) \rho_\epsilon(x-y) dx, \eta(dy) \rangle \\ &= \langle T_{\epsilon^2} f(y), \eta_t(dy) \rangle
-\end{align*}
-where $T_t$ denotes the heat semigroup. Substituting this into the martingale problem for $\eta_t$, (\ref{mgp1}), we get,
+    For this note that
+    \begin{align*}
+        \int f(x) \rho_\epsilon * \eta_t(x) dx
+        &=
+        % \int \int f(x) \rho_\epsilon (x-y) \eta(dy) dx
+        % \\ & =
+        % \langle \int f(x) \rho_\epsilon(x-y) dx, \eta(dy) \rangle
+        % \\ &=
+        \langle \rho_\epsilon f(y), \eta_t(dy) \rangle .
+    \end{align*}
+    Substituting this into the martingale problem for $\eta_t$, \eqref{mgp1},
+    we get
     \begin{align}
-\langle T_{\epsilon^2} f(y), \eta_t(dy) \rangle & = \langle T_{\epsilon^2}
- f(y), \eta_0(dy) \rangle + \theta \int_0^t \langle \int (T_{\epsilon^2} f(z) - T_{\epsilon^2} f(y))q_\theta(y,z)dz, \eta_s(dy)\rangle ds \nonumber \\ &+\int_0^t \langle T_{\epsilon^2} f(y) F(\rho_\epsilon*\eta_s(y)), \eta_s(dy) \rangle ds + \widehat{M}_t \label{MGPT_epsilon} \end{align}
- with $\widehat{M}_t$ a martingale. Now note that,
+         \label{MGPT_epsilon}
+    \langle \rho_{\epsilon} * f, \eta_t \rangle
+        & = \nonumber 
+        \langle \rho_{\epsilon} * f, \eta_0 \rangle
+        +
+        \theta \int_0^t
+            \langle
+                \int (\rho_{\epsilon} * f(z) - \rho_{\epsilon} * f(y)) q_\theta(y, dz) ,
+                \eta_s(dy)
+            \rangle
+        ds
+        \\ & {}
+        +
+        \int_0^t \langle \rho_\epsilon * f(y) F(y, \eta_s), \eta_s(dy) \rangle ds
+        + \widehat{M}_t,
+    \end{align}
+    with $\widehat{M}_t$ a martingale. Now note that
     by the Intermediate Value Theorem,
     \begin{align}
-    | \theta \int (T_{\epsilon^2} f(z) - T_{\epsilon^2}f(y))q_\theta(y,z) dz | &= |\theta( T_{\epsilon^2 + 1/\theta} f(y) - T_{\epsilon^2}f(y)| \nonumber \\ &= | \Delta T_{\epsilon+1/\tilde{\theta}} f(y) | \nonumber \\ &=|T_{\epsilon^2 + 1/\tilde{\theta}} \Delta f(y) | \leq \Vert \Delta f \Vert_{\infty} \label{ShortBoundLaplacianHS}
+        \label{ShortBoundLaplacianHS}
+        \left| \theta \int (\rho_{\epsilon} * f(z) - \rho_{\epsilon} * f(y)) q_\theta(y,z) dz \right|
+        &=
+        \left| \theta( p_{\epsilon^2 + 1/\theta} * f(y) - p_{\epsilon^2} * f(y) ) \right| \nonumber
+        \\ &=
+        \left| \Delta p_{\epsilon+1/\tilde{\theta}} * f(y) \right| \nonumber
+        \\ &=
+        \left| p_{\epsilon^2 + 1/\tilde{\theta}} * \Delta f(y) \right|
+        \leq
+        \| \Delta f \|_{\infty}
     \end{align}
     for some $\tilde{\theta} \in [0,1/\theta]$.
-Proceeding as in the proof of Lemma~\ref{Lemma:UniformlyBoundedMass}, we can use that $F(x)1_{x > 0}$ is bounded above and Gronwall's inequality to conclude that,
-\[ \IE\left[\langle T_{\epsilon^2} f(y), \eta_t(dy) \rangle \right] \text{ is uniformly bounded for } t \in [0,T].\]
-The quadratic variation of $\widehat{M}_t$ is;
-\[ [ \widehat{M}]_t = \frac{\theta}{N}\int_0^t \langle T_{1/\theta}(T_{\epsilon^2}f(\cdot)^2)(y) + \left(1+\frac{F(\rho_\epsilon*\eta_s(y))}{\theta}\right)T_{\epsilon^2}f(y)^2, \eta_s(dy) \rangle ds \]
-And so, using boundedness of $f$ and $F$,
-\begin{align*}
-\IE\left[ [\widehat{M}]_t \right] \leq \frac{\theta}{N} \Vert f \Vert_\infty C \int_0^t \mathbb{E}\left[ \langle 1, \eta_s(dy) \right] ds < \frac{\theta}{N} t C
-\end{align*}
-where in the last inequality we have used Lemma~\ref{Lemma:UniformlyBoundedMass}.Hence, using the Burkholder-Davis-Gundy inequality we can conclude,
-\[ \IE[\sup_{0 \leq t \leq T} [\widehat{M}]_t ] \text{ is uniformly bounded (for fixed } f \text{)} \]
-Therefore, by taking supremum and expectation and in (\ref{MGPT_epsilon}) we conclude that
-\begin{equation} \IE[\sup_{0 \leq t \leq T} \langle T_{\epsilon^2} f, \eta_t \rangle ] \text{ is uniformly bounded (for fixed } f \text{)} \label{eq:boundedIntegralAgainstf} \end{equation}
-To conclude $C$-tightness we show that, for $T>0$, $\alpha > 0$ there is some $\delta >0$ so that for $\theta$ and $N$ large enough,
+    Proceeding as in the proof of Lemma~\ref{lem:eta_f_bound},
+    we can use that $F(x)$ is bounded above and Gronwall's inequality to conclude that
+    \[
+        \IE\left[\langle \rho_{\epsilon} * f(y) F(y, \eta_t), \eta_t(dy) \rangle \right]
+        \text{ is uniformly bounded for } t \in [0,T].
+    \]
+
+    The quadratic variation of $\widehat{M}_t$ is
+    \[
+        [ \widehat{M} ]_t
+        =
+        \frac{\theta}{N} \int_0^t \langle
+            p_{1/\theta}*(p_{\epsilon^2} * f(\cdot)^2)(y)
+            +
+            \left( 1 + \frac{F(\rho_\epsilon*\eta_s(y))}{\theta} \right)
+            p_{\epsilon^2} * f(y)^2
+            ,
+            \eta_s(dy)
+        \rangle ds ,
+    \]
+    so using boundedness of $f$ and $F$,
+    \begin{align*}
+        \IE\left[ [\widehat{M}]_t \right]
+        \leq
+        \frac{\theta}{N} \| f \|_\infty C
+        \int_0^t \mathbb{E}\left[ \langle 1, \eta_s(dy) \right] ds
+        <
+        C \frac{\theta}{N} t ,
+    \end{align*}
+    where in the last inequality we have used Lemma~\ref{Lemma:UniformlyBoundedMass}.
+    Hence, using the Burkholder-Davis-Gundy and Jensen's inequalities we can conclude that
+    \[
+        \IE[\sup_{0 \leq t \leq T} |\widehat{M}_t| ]
+        \le
+        C
+        \IE\left[ [\widehat{M}]_t \right]^{1/2}
+        \le
+        \sqrt{ C \frac{\theta}{N} T } .
+    \]
+    Therefore, by taking supremum and expectation and in \eqref{MGPT_epsilon}
+    we conclude that
+    \begin{equation}
+        \label{eq:boundedIntegralAgainstf}
+        \IE[ \sup_{0 \leq t \leq T} \langle T_{\epsilon^2} f, \eta_t \rangle ]
+        \text{ is uniformly bounded (for fixed } f \text{)}
+    \end{equation}
+    To conclude $C$-tightness we show that, for $T>0$, and $\alpha > 0$
+    there is some $\delta >0$ so that for $\theta$ and $N$ large enough,
     \begin{align}
-&\IP\left[ \sup_{u,v \in [0,T], |u-v| < \delta} \left| \int f, \rho_\epsilon*\eta_u(x) dx   - \int f, \rho_\epsilon*\eta_v(x) dx \right|  > \alpha \right]
+        &
+        \IP\left[
+            \sup_{s,t \in [0,T], |s-t| < \delta}
+            \left|
+                \int f(x) \rho_\epsilon*\eta_s(x) dx
+                -
+                \int f(x) \rho_\epsilon*\eta_t(x) dx
+            \right|
+            >
+            \alpha
+        \right]
         \\ &=
-\IP\left[ \sup_{u,v \in [0,T], |u-v| < \delta} | \langle T_{\epsilon^2} f, \eta_u \rangle - \langle T_{\epsilon^2} f,\eta_v \rangle > \alpha \right]
+        \IP\left[
+            \sup_{s,t \in [0,T], |s-t| < \delta}
+            \left|
+                \langle p_{\epsilon^2} * f, \eta_s \rangle
+                - \langle p_{\epsilon^2} * f, \eta_t \rangle
+            \right|
+            >
+            \alpha
+        \right]
         <
@@
     \begin{align*}
-|\langle T_{\epsilon^2} f, \eta_u \rangle - \langle T_{\epsilon^2} f,\eta_v \rangle|  \leq ( \Vert \Delta f \Vert_\infty + C_F||f||_\infty) |u-v| \sup_{0 \leq s \leq T } \langle 1, \eta_s \rangle + \sup_{s \leq T}|\widehat{M}_s|
+        \left|
+        \langle p_{\epsilon^2} * f, \eta_s \rangle
+        -
+        \langle p_{\epsilon^2} * f, \eta_t \rangle
+        \right|
+        \leq
+        ( \| \Delta f \|_\infty + C_F \|f\|_\infty) |u-v|
+        \sup_{0 \leq u \leq T } \langle 1, \eta_u \rangle
+        +
+        \sup_{u \leq T} |\widehat{M}_u| .
     \end{align*}
@@
     \begin{equation}
-\IE\left[ |\langle T_{\epsilon^2} f, \eta_u \rangle - \langle T_{\epsilon^2} f,\eta_v \rangle|\right] \leq \widehat{C} |u-v| + \frac{\widehat{C}\theta}{N}\end{equation}
-Using this and Markov's inequality give that (\ref{conditionCtightness}) holds with $\delta = \alpha/(3 \widehat{C}|u-v|)$, for $N,\theta$ big enough so $\widehat{C}\theta/N$ is bounded by $\alpha/3$ (Note the last condition is possible by (\ref{ConditionsForConvergence})).
+        \IE\left[ \left|
+            \langle T_{\epsilon^2} f, \eta_s \rangle
+            -
+            \langle T_{\epsilon^2} f, \eta_t \rangle
+        \right| \right]
+        \leq
+        \widehat{C} |s-t|
+        +
+        \widehat{C} \left( \frac{\theta}{N} T \right)^{1/2} .
+    \end{equation}
+    Using this and Markov's inequality give that \eqref{conditionCtightness}
+    holds with $\delta = \alpha/(3 \widehat{C}|s-t|)$,
+    for $N$, $\theta$ big enough so $\widehat{C}\sqrt{T\theta/N}$ is bounded by $\alpha/3$.
+    (Note the last condition is possible by \eqref{ConditionsForConvergence}.)
     Thus we have concluded $C$-tightness. 
 \end{proof}
+
 \begin{remark} \label{remark:BoundedIntegral}
@@
 \[ \IE\left[\sup_{0 \leq t \leq T} \int \rho_{\epsilon/2} * \eta_t(x) dx \right] = C < \infty. \]
-By using this and the same pattern used to prove Proposition~\ref{Prop:SecondMomentMass}, we can then conclude that,
+By using this and the same pattern used to prove Lemma~\ref{lem:SecondMomentMass}, we can then conclude that,
 \[ \IE\left[  \sup_{0 \leq t \leq T} \int \left(\rho_{\epsilon/2} * \eta_t(x) \right)^2 dx \right] = C < \infty. \]
@@
 \end{align*}
-which, due to Proposition~\ref{Prop:SecondMomentMass}, is of order $\epsilon$. To bound the third integral term we use the event $A_{t}$ to get it is bounded by,
+which, due to Lemma~\ref{lem:SecondMomentMass}, is of order $\epsilon$. To bound the third integral term we use the event $A_{t}$ to get it is bounded by,
 \begin{align*}

### 2022-09-15 forwards-and-backwards.tex
various things

@@
     \end{align*}
-    Since $F(m)1_{m > 0}$ is bounded above and $\theta/N$ converges,
+    Since $F$ is bounded above and $\theta/N$ converges,
     we have for an appropriate $C$ that
@@
         \frac{C \theta}{N \epsilon^d} \int_0^t \left\{
-            \langle \int \psi_{t-s}^{\epsilon,x}(z) q_\theta(y,dz), \eta_s(dy) \rangle
+            \langle \int \psi_{t-s}^{\epsilon,x}(z) q_\theta(y,dz)
             +
-            \langle \psi_{t-s}^{\epsilon,x}(y), \eta_s(dy)\rangle
+            \psi_{t-s}^{\epsilon,x}(y)
+            , \eta_s(dy)\rangle
         \right\} ds 
@@
         % \\ &=
-        \langle \rho_\epsilon f(y), \eta_t(dy) \rangle .
+        \langle \rho_\epsilon * f(y), \eta_t(dy) \rangle .
     \end{align*}
@@
     Proceeding as in the proof of Lemma~\ref{lem:eta_f_bound},
-    we can use that $F(x)$ is bounded above and Gronwall's inequality to conclude that
+    we can take expectations of equation~\eqref{MGPT_epsilon},
+    use \eqref{ShortBoundLaplacianHS} and the fact that $F(x)$ is bounded above,
+    and then Gronwall's inequality to conclude that
     \[
-        \IE\left[\langle \rho_{\epsilon} * f(y) F(y, \eta_t), \eta_t(dy) \rangle \right]
+        \IE\left[\langle \rho_{\epsilon} * f(y), \eta_t(dy) \rangle \right]
         \text{ is uniformly bounded for } t \in [0,T].
@@
         \leq
-        \frac{\theta}{N} \| f \|_\infty C
+        \frac{\theta}{N} \| f \|_\infty (1 + C_F/\theta)
         \int_0^t \mathbb{E}\left[ \langle 1, \eta_s(dy) \right] ds
@@
     where in the last inequality we have used Lemma~\ref{Lemma:UniformlyBoundedMass}.
-    Hence, using the Burkholder-Davis-Gundy and Jensen's inequalities we can conclude that
+    Hence, using the Burkholder-Davis-Gundy inequality and then Jensen's inequality we can conclude that
     \[
@@
         C
-        \IE\left[ [\widehat{M}]_t \right]^{1/2}
+        \IE\left[ [\widehat{M}]_T \right]^{1/2}
         \le
@@
         \label{eq:boundedIntegralAgainstf}
-        \IE[ \sup_{0 \leq t \leq T} \langle T_{\epsilon^2} f, \eta_t \rangle ]
-        \text{ is uniformly bounded (for fixed } f \text{)}
+        \IE[ \sup_{0 \leq t \leq T} \langle p_{\epsilon^2} * f, \eta_t \rangle ]
+        \text{ is uniformly bounded (for fixed } f \text{)} .
     \end{equation}
@@
     \begin{align}
-        &
+        % &
+        % \IP\left[
+        %     \sup_{s,t \in [0,T], |s-t| < \delta}
+        %     \left|
+        %         \int f(x) \rho_\epsilon*\eta_s(x) dx
+        %         -
+        %         \int f(x) \rho_\epsilon*\eta_t(x) dx
+        %     \right|
+        %     >
+        %     \alpha
+        % \right]
+        % \\ &=
         \IP\left[
@@
             \left|
-                \int f(x) \rho_\epsilon*\eta_s(x) dx
-                -
-                \int f(x) \rho_\epsilon*\eta_t(x) dx
-            \right|
-            >
-            \alpha
-        \right]
-        \\ &=
-        \IP\left[
-            \sup_{s,t \in [0,T], |s-t| < \delta}
-            \left|
-                \langle p_{\epsilon^2} * f, \eta_s \rangle
-                - \langle p_{\epsilon^2} * f, \eta_t \rangle
+                \langle \rho_{\epsilon} * f, \eta_s \rangle
+                - \langle \rho_{\epsilon} * f, \eta_t \rangle
             \right|
@@
     \end{align}
-    But, from our estimates above, we have
+    Now, we can use \eqref{MGPT_epsilon} to write this difference
+    as an integral, then bound the terms as above to get
     \begin{align*}
         \left|
-        \langle p_{\epsilon^2} * f, \eta_s \rangle
+        \langle \rho_{\epsilon} * f, \eta_s \rangle
         -
-        \langle p_{\epsilon^2} * f, \eta_t \rangle
+        \langle \rho_{\epsilon} * f, \eta_t \rangle
         \right|
         \leq
-        ( \| \Delta f \|_\infty + C_F \|f\|_\infty) |u-v|
+        ( \| \Delta f \|_\infty + C_F \|f\|_\infty) |s - t|
         \sup_{0 \leq u \leq T } \langle 1, \eta_u \rangle
@@
         \IE\left[ \left|
-            \langle T_{\epsilon^2} f, \eta_s \rangle
+            \langle \rho_\epsilon * f, \eta_s \rangle
             -
-            \langle T_{\epsilon^2} f, \eta_t \rangle
+            \langle \rho_\epsilon * f, \eta_t \rangle
         \right| \right]
@@
 
+\comment{
+    Peter writes: the following Remark refers to the proof of Lemma~\ref{lem:SecondMomentMass},
+    which was previously wrong and is now fairly different.
+    However, I don't see how to prove the Remark using any similar method,
+    because to bound $\int p_{\epsilon^2 / 2} * \eta_t(x)^2 dx$
+    it seems like we need control on $\rho_\epsilon * \eta_t(x)$ uniformly in $x$
+    (and, integrability), which I don't think we have?
+    But, I'm probably being dense.
+    See after this for an attempted rewrite.
+}
+
 \begin{remark} \label{remark:BoundedIntegral}
-Similar as we got equation (\ref{eq:boundedIntegralAgainstf}), from equation \ref{MGPT_epsilon} we can conclude that
-\[ \IE\left[\sup_{0 \leq t \leq T} \int \rho_{\epsilon/2} * \eta_t(x) dx \right] = C < \infty. \]
-By using this and the same pattern used to prove Lemma~\ref{lem:SecondMomentMass}, we can then conclude that,
-\[ \IE\left[  \sup_{0 \leq t \leq T} \int \left(\rho_{\epsilon/2} * \eta_t(x) \right)^2 dx \right] = C < \infty. \]
-Since,
-\begin{align*}
-\langle \rho_\epsilon * \eta_t(z), \eta(dz) \rangle & = \sum_{y \in \eta_t} \sum_{z \in \eta_t} \rho_\epsilon(y-z) \eta(z) \eta(y) \\ &= \int  \sum_{y \in \eta_t} \sum_{z \in \eta_t} \rho_{\epsilon/2}(y-x) \rho_{\epsilon/2}(z-x) \eta(z) \eta(y) \\ &= \int (\rho_{\epsilon/2}*\eta_t(x))^2 dx.
-\end{align*}
-This allows us to conclude that $\IE[\langle \rho_\epsilon*\eta_t(z),\eta_t(dz) \rangle ] < \infty$. This bound will be useful in the next section.
+    Similar as we got equation (\ref{eq:boundedIntegralAgainstf}), from equation \ref{MGPT_epsilon} we can conclude there exists a $C < \infty$ such that
+    \[
+        \IE\left[\sup_{0 \leq t \leq T} \int p_{\epsilon^2/2} * \eta_t(x) dx \right] < C .
+    \]
+    By using this and the same pattern used to prove Lemma~\ref{lem:SecondMomentMass},
+    we can then conclude there is a (different) $C < \infty$ such that
+    \[
+        \IE\left[  \sup_{0 \leq t \leq T} \int \left( p_{\epsilon^2/2} * \eta_t(x) \right)^2 dx \right]
+        <
+        C .
+    \]
+    Then, because
+    \begin{align*}
+        \langle p_{\epsilon^2} * \eta_t(x), \eta(dx) \rangle
+        &=
+        \langle p_{\epsilon^2/2} * p_{\epsilon^2/2} * \eta_t(x), \eta(dx) \rangle
+        \\ &=
+        \int_{\IR^d} \left( p_{\epsilon^2/2} * \eta_t(x) \right)^2 dx .
+    \end{align*}
+    we can conclude that
+    $\IE[\langle \rho_\epsilon*\eta_t(x), \eta_t(dx) \rangle ]$ is uniformly bounded,
+    which will be useful in the next section.
+\end{remark}
+
+\comment{Here's my start at rewriting that Remark;
+    however, I'm stuck since $\theta(p_{\epsilon^2 + 1/\theta} - p_{\epsilon^2}) * \eta$
+    isn't bounded by $p_{\epsilon^2} * \eta$ (uniformly in $\epsilon$, anyhow).
+}
+
+\begin{remark} \label{remark:BoundedIntegral2}
+    Below, we will want to bound
+    \[
+        \langle \rho_\epsilon * \eta_t, \eta_t \rangle
+        =
+        \int_{\IR^d} \int_{\IR^d} p_{\epsilon^2}(x, y) \eta_t(dx) \eta_t(dy) .
+    \]
+    Writing $H(\eta) = \langle \rho_\epsilon * \eta, \eta \rangle$,
+    note that since $p_{\epsilon^2}$ is symmetric,
+    $H(\eta + \delta_z / N) = H(\eta) + 2 \rho_\epsilon * \eta(z) / N + p_{\epsilon^2}(z, z) / N^2$,
+    so following Section~\ref{sec:heuristics},
+    \begin{align*}
+        \langle \rho_\epsilon * \eta_t, \eta_t \rangle
+        &=
+        \langle \rho_\epsilon * \eta_0, \eta_0 \rangle
+        +
+        2 \theta \int_0^t \left \langle \int_{\IR^d}
+            \left(
+               \rho_\epsilon * \eta_s(y)
+               -
+               \rho_\epsilon * \eta_s(x)
+            \right)
+            q_\theta(x, dy)
+        , \eta_s(dy) \right \rangle ds
+        \\ & \qquad {}
+        +
+        2 \int_0^t
+        \langle
+            \rho_\epsilon * \eta_s(x) F(x, \eta_s)
+        , \eta_s(dx) \rangle
+        ds
+        +
+        O\left( \frac{1}{\epsilon^d N^2} \right)
+        + M_t ,
+    \end{align*}
+    where $M_t$ is a martingale with quadratic variation
+    \begin{align*}
+        [M]_t
+        &=
+        2 \frac{\theta}{N} \int_0^t
+        \left \langle
+            \int_{\IR^d}
+                \rho_\epsilon * \eta_s(y)^2
+            q_\theta(x, dy)
+        , \eta_s(dx) \right\rangle
+        ds
+        \\ & \qquad {}
+        +
+        2 \int_0^t
+        \left \langle
+            \rho_\epsilon * \eta_s(x)^2 (1 + F(x, \eta_s) / \theta) 
+        , \eta_s(dx) \right\rangle
+        ds
+        +
+        O\left( \frac{1}{\epsilon^d N^2} \right) .
+    \end{align*}
 \end{remark}

### 2022-11-17 forwards-and-backwards-161122.tex
Update on Overleaf.

--- 2022-09-15 forwards-and-backwards.tex
@@
         \|f'\|_\infty
-        \left|
             \theta \int_{\IR^d}
-                (\smooth{r}\eta(y) - \smooth{r}\eta(x))
+               \left| (\smooth{r}\eta(y) - \smooth{r}\eta(x))
+               \right|
             q_\theta(x, dy)
-        \right|
         +
@@
         \label{eqn:first_moment_rho}
-        \left|\theta \int_{\IR^d}
-            ( \smooth{r} \eta(y)-\smooth{r} \eta(x) )
-        q_\theta(x,dy)\right|
+        \theta \int_{\IR^d}
+            \left|( \smooth{r} \eta(y)-\smooth{r} \eta(x) )\right|
+        q_\theta(x,dy)
         \leq K \smooth{\gamma} \eta(x)
@@
     over a wider region (since $\epsilon_\gamma > \epsilon_r$).
+    Furthermore,
+    applying Jensen's inequality on the function
+    $\left|( \smooth{r} \eta(y)-\smooth{r} \eta(x) )\right|^2$,
+    one can bound the first moment directly from estimates of the second moment.
 
@@
 \appendix
-\section{Markov Mapping Theorem Applications}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\section{Results on Lookdown Representations}
     \label{sec: Markov Mapping Theorem Application}
-\subsection{Markov Mapping Theorem Application on Generator $A^{\theta}$}\label{sec: Markov Mapping Theorem Application - Prelimit}
-
-We now introduce some notations to simply our calculations.
-For $\xi=\sum \delta_{(x_i,u_i)}$, we write $\textbf{x}=(x_1,x_2,...), \textbf{u}=(u_1,u_2,...)$ to be the collections of particles locations and levels respectively.
-With this notation we will write $f(\xi), f(\textbf{x},\textbf{u})$ interchangeably.
-We write $\Gamma (d\textbf{u})$ as the probability kernel that corresponds to assigning each particle an i.i.d.
-uniform $[0,\lambda]$-level, i.e.
-$$\int f(\textbf{x},\textbf{u})\Gamma (d\textbf{u})=\frac{1}{\lambda^{|\xi|}}\int_{[0,\lambda]^{|\xi|}}f(\textbf{x},\textbf{u})d\textbf{u},$$
+\subsection{Generators for the spatial processes}
+Before defining the generator of the lookdown representations, 
+we recall the generator of the spatial processes.
+
+We first define our pre-limit
+$(\eta^{N}(t))_{t>0}$ as a solution
+to a Martingale Problem
+with generator $\Pgen^{N}$.
+
+\begin{definition}
+    \label{def2: MP definition of pre-limit}
+Let $F \in \mathcal{C}^{2}(\IR)$ and $f \in \mathcal{C}_{0}(\IR^d)$.
+We define $\Pgen^N$ to be a generator
+acting on test functions of the form
+$F_f(\eta):=F (\langle f, \eta \rangle)$
+such that 
+\begin{equation}
+\begin{aligned}
+\Pgen^{N} F_f(\eta):=& \int_{\IR^d} \theta\gamma(x, \eta) \left\{\int_{\IR^d} \left\{F(\langle f, \eta \rangle + f(y)/N )-F(\langle f, \eta \rangle )\right\}r(y, \eta)q_{\theta}(x,dy)\right\}N\eta(dx)\\
+&+\int_{\IR^d} \theta \mu(x, \eta) \left\{F(\langle f, \eta \rangle - f(x)/N )-F(\langle f, \eta \rangle )\right\}N\eta(dx).
+\end{aligned}    
+\end{equation}
+In this case, our pre-limit model $(\eta^{N}(t))_{t \geq 0}$ is the solution to the Martingale Problem $(\Pgen^{N}, \eta_0)$, i.e. 
+for all $F \in \mathcal{C}^{2}(\IR)$
+and $f \in \mathcal{C}_{0}(\IR^d)$,
+$$M_t:=F_f(\eta^{N}_t)-F_f(\eta_0)
+-\int_{0}^{t}\Pgen^{N}F_f(\eta^{N}_s)ds$$
+is a martingale, and the initial condition is distributed as a Poisson measure with mean measure $\eta_0$.
+\end{definition}
+
+\begin{remark}
+Taking $F(x)=x$ and $F(x)=x^2$, we can recover Equation \eqref{eqn:limiting_mgale_problem} and \eqref{eqn:limiting_mgale_variation} for the limit.
+Similarly, we can recover
+Definition \ref{defn:mgale_construction},
+an equivalent characterisation
+of our pre-limit model.
+\end{remark}
+
+We now write the candidate generator for the limiting object.
+
+\begin{definition}
+    \label{def2: MP definition of limit}
+Let $F \in \mathcal{C}^{2}(\IR)$ and $f \in \mathcal{C}_{0}(\IR^d)$.
+We define $\Pgen$ to be a generator
+acting on test functions of the form
+$F_f(\eta):=F (\langle f, \eta \rangle)$
+such that 
+\begin{equation}
+    \label{eq: Limit Generator Definition}
+\begin{aligned}
+\Pgen^{\infty} F_f(\eta):=& F'(\langle f, \eta \rangle)
+                   \times \left\{
+                   \big\langle
+                        \gamma(x, \smooth{\gamma} \eta(x))
+                            \mathcal{B}\left(
+                            f(\cdot) r(\cdot, \smooth{r} \eta(\cdot))
+                            \right)(x)
+                    +
+                    f(x)
+                        F(x, \smooth{F} \eta(x)),
+                        \eta(dx)
+                    \big\rangle
+                   \right\}\\
+                &+ \alpha F''(\langle f, \eta \rangle)
+                  \times \left\{
+                  \big\langle
+                    \gamma \left( x, \eta \right)
+                    r\left(x,\eta \right)
+                    f^2(x),
+                    \eta (dx)
+                    \big\rangle 
+                  \right\}.
+\end{aligned}    
+\end{equation}
+We define $(\eta^{\infty}(t))_{t \geq 0}$ to be the solution to the Martingale Problem $(\Pgen^{\infty}, \eta_0)$, i.e. 
+for all $F \in \mathcal{C}^{2}(\IR)$
+and $f \in \mathcal{C}_{0}(\IR^d)$,
+$$M_t:=F_f(\eta^{\infty}_t)-F_f(\eta_0)
+-\int_{0}^{t}\Pgen^{\infty}F_f(\eta^{\infty}_s)ds$$
+is a martingale, with initial condition distributed as a Poisson measure with mean measure $\eta_0$.
+\end{definition}
+
+\subsubsection{Convergence of the Generators for the Spatial Models}
+
+Here, just as a sanity check, 
+we make sure that the limiting generator is indeed the limit of the generators.
+
+\begin{lemma}[Identifying the limit as a solution to the martingale problem]
+    \label{lem:limit_mgale}
+As $N \to \infty$,
+$(\eta^{N}_t)_{t \geq 0}$ converges in $\mathcal{D}_{[0,\infty)}(\mathcal{M}_f(\IR^d))$
+to $(\eta^{N}(t))_{t \geq 0}$.
+\end{lemma}
+\begin{proof}
+We use Theorem 4.8.10 in \cite{EK}.
+First of all, the set of functions
+$\{F_f(\eta):= F(\langle f, \eta \rangle ),~
+F \in \mathcal{C}^{2}(\IR), ~
+f \in \mathcal{C}_{0}(\IR^d)\}$
+is a dense and convergence-determining 
+subset of functions in $\mathcal{M}_f(\IR^d)$.
+Therefore, it suffices to show that for any $t>0$,
+\begin{equation}
+    \label{eq: Convergence Condition}
+\lim_{N \to \infty}
+\mathbb{E}\left[
+\left(
+F_f(\eta^{N}_{t+\tau})-F_f(\eta^{N}_t)
+-\int_{t}^{t+\tau}\Pgen^{\infty}F_f(\eta^{N}_s)ds
+\right)
+\prod_{i=1}^{k}\langle h_i,\eta^{N}_{t_i} \rangle
+\right]=0
+\end{equation}
+for all $k\geq 0$, $0\leq t_1<t_2<...,t_k \leq t < t+\tau$,
+and $h_1,...,h_k \in \mathcal{C}_{0}(\IR^d)$.
+
+To prove this,
+we make use of the Martingale Problem characterisation
+of $(\eta^{N}_t)_{t \geq 0}$.
+From Definition \ref{def: MP definition of pre-limit},
+we can apply Tower Law
+and obtain that
+\begin{equation}
+    \label{eq: Prelimit MP Application}
+\lim_{N \to \infty}
+\mathbb{E}\left[
+\left(
+F_f(\eta^{N}_{t+\tau})-F_f(\eta^{N}_t)
+-\int_{t}^{t+\tau}\Pgen^{N}F_f(\eta^{N}_s)ds
+\right)
+\prod_{i=1}^{k}\langle h_i,\eta^{N}_{t_i} \rangle
+\right]=0
+\end{equation}
+for all $k\geq 0$, $0\leq t_1<t_2<...,t_k \leq t < t+\tau$,
+and $h_1,...,h_k \in \mathcal{C}_{0}(\IR^d)$.
+
+Therefore, it suffices to show that 
+\begin{equation}
+    \label{eq: Convergence of Spatial Generator}
+\lim_{N \to \infty}
+\mathbb{E}\left[
+\int_{t}^{t+\tau}
+\left|
+\Pgen^{N}F_f(\eta^{N}_s)
+-\Pgen^{\infty}F_f(\eta^{N}_s)
+\right|
+ds
+\times 
+\prod_{i=1}^{k}\langle h_i,\eta^{N}_{t_i} \rangle
+\right]=0
+\end{equation}
+We apply Taylor Expansion
+around the term $F(\langle f, \eta \rangle )$
+up to third order.
+This gives
+\begin{equation}
+    \label{eq: Taylor Expansion calculations i}
+\begin{aligned}
+&F(\langle f, \eta \rangle + f(y)/N )-F(\langle f, \eta \rangle )\\
+=& F'(\langle f, \eta \rangle ) \frac{f(y)}{N}
++\frac{1}{2}F''(\langle f, \eta \rangle ) \frac{f^2(y)}{N^2}
++\frac{1}{6}F'''(w ) \frac{f^3(y)}{N^3}
+\end{aligned}
+\end{equation}
+for some $w \in [\langle f, \eta \rangle, \langle f, \eta \rangle+ ||f||/N]$.
+Similarly,
+\begin{equation}
+    \label{eq: Taylor Expansion calculations ii}
+\begin{aligned}
+&F(\langle f, \eta \rangle - f(x)/N )-F(\langle f, \eta \rangle )\\
+=& - F'(\langle f, \eta \rangle ) \frac{f(x)}{N}
++\frac{1}{2}F''(\langle f, \eta \rangle ) \frac{f^2(x)}{N^2}
+-\frac{1}{6}F'''(v ) \frac{f^3(x)}{N^3}
+\end{aligned}
+\end{equation}
+for some $v \in [\langle f, \eta \rangle - ||f||/N, \langle f, \eta \rangle ]$.
+
+We may now rewrite $\mathcal{P}^NF(\langle f, \eta \rangle)$ as 
+\small
+\begin{equation} 
+    \label{eq: Pre-Limit Generator Expanded}
+\begin{aligned}
+\Pgen^{N} F_f(\eta):=& F'(\langle f, \eta \rangle)\int_{\IR^d}  \theta\left\{\int_{\IR^d} \left\{f(y)\gamma(x, \eta) r(y,\eta) -f(x)\mu(x, \eta)\right\}q_{\theta}(x,dy)\right\}\eta(dx)\\
+&+\frac{1}{2}\frac{\theta}{N}F''(\langle f, \eta \rangle)\int_{\IR^d} 
+ \left\{\gamma(x, \eta)\int_{\IR^d} \left\{f^2(y) r(y,\eta) \right\}q_{\theta}(x,dy)+f^2(x)\mu(x, \eta)\right\}\eta(dx)\\
+&+\frac{1}{6}\frac{\theta}{N^2}\int_{\IR^d}\left\{ 
+F'''(w) \left\{\gamma(x, \eta)\int_{\IR^d} f^3(y) r(y,\eta) q_{\theta}(x,dy)\right\}-F'''(v)f^3(x)\mu(x, \eta)\right\}\eta(dx)
+\end{aligned}    
+\end{equation}
+\normalsize
+for some $w,v \in [\langle f,\eta \rangle - ||f||/N, \langle f,\eta \rangle + ||f||/N]$.
+
+As $N\to \infty$, 
+$\theta/N \to \alpha$, 
+$\theta/N^2 \to 0$,
+and 
+$$\int_{\IR^d} f^m(y) r(y,\eta) q_{\theta}(x,dy) \to f^m(x)r(x, \eta)$$
+for $m=2,3$,
+the third term in Equation \eqref{eq: Pre-Limit Generator Expanded} vanishes
+while the second term converges to
+that of Equation \eqref{eq: Limit Generator Definition}.
+Furthermore,
+$\mu(x,\eta) = r(x,\eta)\gamma(x,\eta)-\frac{1}{\theta}F(x,\eta) \to r(x,\eta)\gamma(x,\eta),$
+so $f^2(x)\mu(x,\eta) \to r(x,\eta)\gamma(x,\eta) f^2(x)$.
+
+Finally, by Equation \eqref{mean measure},
+\eqref{eqn:rewritten mean measure}, \eqref{eqn:near_critical} and
+\eqref{limit of mean measure equation},
+we have 
+\begin{multline}
+ \theta\left\{\int_{\IR^d} \left\{f(y)\gamma(x, \eta) r(y,\eta) -f(x)\mu(x, \eta)\right\}q_{\theta}(x,dy)\right\}
+ \\
+\to \gamma(x, \eta)                           \mathcal{B}\left(
+                            f(\cdot) r(\cdot, \eta)
+                            \right)(x)
+                    +
+                    f(x)
+                        F(x, \eta),
+\end{multline}
+so comparing terms we have
+\begin{equation}
+\lim_{N\to \infty} |\mathcal{P}^{N}F\langle f, \eta \rangle - \mathcal{P}^{\infty}F\langle f, \eta \rangle| \to 0,   
+\end{equation}
+and so by Dominated Convergence Theorem,
+we establish Equation 
+\eqref{eq: Convergence of Spatial Generator}
+which concludes our proof.
+\end{proof}
+
+\subsection{Generator of Lookdown Representations}
+
+We now define the generator of the lookdown representations.
+\begin{definition}[Martingale Problem Characterisation]
+    \label{defn:lookdown_mgale}
+For given positive values of $N$ and $\theta$
+and $\lp_0 \in \mathcal{M}_F(\IR^d \times [0,N])$,
+we define $(\lp^{N}_t)_{t \geq 0}$
+to be the unique solution to the martingale problem
+with initial condition $\lp_0$ and generator $A^{N}$ that satisfies
+\begin{equation*}
+\begin{split}
+& A^{N}f(\lp ) \\
+&\quad =
+    f(\lp)
+    \,\sum_{(x,u)\in \lp}\,
+    2 \gamma(x, \eta)
+    \Bigg\{ \frac{1}{2N} \int_u^N g(x,u_1) du_1
+            \frac{
+                \theta \int_{\IR^d}
+                (g(y,u) - g(x,u))
+                r(y, \eta) q_{\theta}(x,dy)
+            }{ g(x,u) }
+        \\
+    &\qquad\qquad\qquad\qquad\qquad\qquad\qquad {} +
+        \frac{\theta}{N} \int_u^N
+        \int_{\IR^d}\left(
+            \frac{ g(y,u_1) + g(x,u_1) }{ 2 } - 1
+        \right)
+        r(y, \eta) q_{\theta}(x,dy)
+        du_1
+    \Bigg\}\\
+    &\qquad\qquad {} +
+    f(\lp) \sum_{(x,u)\in\lp}\,
+    \left(
+        \frac{\theta}{N} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q_\theta(x, dy) u^2 -b_{\theta}(x,\eta)u
+    \right)
+    \frac{\partial_u g(x,u)}{g(x,u)}
+    ,
+\end{split}
+\end{equation*}
+for all smooth functions $g \in C^{2}_{0}(\IR^d)$,
+where $f(\lp) = \prod_{(x, u) \in \lp} g(x, u)$ as defined in \eqref{eqn:test_functions},
+and $\eta(\cdot) = \lp(\cdot \times [0, N]) / N$ is the scaled spatial pushforward of $\lp$,
+as before.
+\end{definition}
+
+Similarly, 
+we define the generator for the lookdown representation of the limiting spatial model.
+
+\begin{definition}[Martingale Problem Characterisation, $N=\infty$]
+    \label{defn:limiting_lookdown_mgale}
+    For a given value of $\alpha \in [0, \infty)$,
+    define the operator $A$ acting on test functions of the form
+    $f(\xi) = \prod_{(x, u) \in \xi} g(x, u)$ with $g \in C_0^2(\IR^d \times [0, \infty))$
+    and for which there exists a $u_0$ with $g(x, u) = 1$ for all $u > u_0$.
+    Then, let $A f$ be
+    \begin{equation}
+    \begin{aligned} \label{eqn:limiting_lookdown_generator}
+    A f(\lp)
+    =&
+        f(\lp)  \sum_{(x, u) \in \xi}
+        \gamma(x, \eta)
+            \frac{
+                \DG(g(\cdot, u) r(\cdot, \eta))(x) - g(x,u) \DG r(x,\eta)
+            }{
+                g(x, u)
+            }
+    \\ &+
+        f(\lp) \sum_{(x, u) \in \xi}
+        2 \alpha \gamma(x,\Xi)r(x,\Xi) \int_u^\infty (g(x, u_1) - 1) du_1
+    \\ &+
+        f(\lp) \sum_{(x, u) \in \xi}
+        \left(
+            \alpha \gamma(x,\Xi)r(x,\Xi) u^2
+            -
+            \left\{
+                \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta)
+            \right\} u
+        \right)
+        \frac{\partial_u g(x, u)}{ g(x,u) }  .
+    \end{aligned}
+    \end{equation}
+
+    We say that a $\lpmeasures$-valued process $(\xi_t)_{t \ge 0}$
+    is a solution to the $(A, \lp_0)$ martingale problem
+    if it has initial distribution $\lp_0$
+    and $f(\lp_t) - \int_0^t Af(\lp_s) ds$ is a martingale for all $f$
+    as defined above.
+\end{definition}
+
+\subsubsection{Exact Statement on Markov Mapping Theorem results}
+
+\begin{theorem}
+\label{teo: lookdown on pre-limit well defined}
+For each $N \in \mathbb{N}$,
+there exists a solution $(\lp^N_t)_{t \geq 0}$ to the $(A^N, \lp^N_0)$ martingale problem.
+Furthermore, if we define $\Xi^N_t = \frac{1}{N}\lp^N_t(dx \times [0,N])$ for $t \geq 0$,
+then the pre-limiting model $(\eta^N_t(dx))_{t \geq 0}$ defined in Definition \ref{defn:mgale_construction}
+and $(\Xi^N_t(dx))_{t \geq 0}$
+shares the same distribution on $\mathcal{D}_{\mathcal{M}(\mathbb{R}^d)}[0,\infty)$.
+
+Finally, 
+for all $h\in \mathcal{C}(\mathbb{R}^d \times [0, N])$
+\begin{equation}\label{Markov Mapping Theorem Cox Condition}
+\mathbb{E}\left[e^{-\int_{\mathbb{R}^d \times [0,N]} h(x,u) \xi^{N}(dx \times du)}\bigg| \mathcal{F}^{\Xi^{N}}_t\right]=e^{-\int F^{N}_h(x) \Xi^{N}_t(dx)},
+\end{equation}
+where 
+$$F^{\epsilon,\theta,N}_h(x):=-N\log \left(\frac{1}{N}\int_{0}^{N}e^{-h(x,u)}du\right)=-N\log \left(1-\frac{1}{N}\int_{0}^{N}(1-e^{-h(x,u)})du\right).$$
+In other words,
+conditioned on the spatial configuration $\Xi^N_t$,
+the levels of the particles must be i.i.d uniformly between $[0,N]$.
+
+\end{theorem}
+
+The statement for the limiting case is similar,
+with the only difference being the conditional distribution 
+of the levels given the spatial projection.
+
+\begin{theorem}
+\label{teo: lookdown on limit well defined}
+There exists a solution $(\lp_t)_{t \geq 0}$ to the $(A, \lp_0)$ martingale problem.
+
+Furthermore, if we define $\Xi_t = \lim_{u_0 \to \infty} \frac{1}{u_0}\lp_t(dx \times [0,u_0])$,
+then the limit model $(\eta_t(dx))_{t \geq 0}$ defined in Theorem \label{thm:nonlocal_convergence}
+and $(\Xi_t(dx))_{t \geq 0}$
+shares the same distribution on $\mathcal{D}_{\mathcal{M}(\mathbb{R}^d)}[0,\infty)$.
+
+Finally, 
+for all $h\in \mathcal{C}(\mathbb{R}^d)$ and for all $K>0$,
+\begin{equation}\label{Markov Mapping Theorem Cox Condition limit}
+\mathbb{E}\left[e^{-\int_{\mathbb{R}^d \times [0,K]} h(x) \xi(dx \times du)}\bigg| \mathcal{F}^{\Xi}_t\right]=e^{- K \int_{\mathbb{R^d}}(1-e^{h(x)}) \Xi_t(dx)}.
+\end{equation}
+In other words,
+conditionally on $(\Xi_s)_{0\leq s \leq t}$
+for each $s \in[0,t]$,
+$\xi_s$ is conditionally Poisson with Cox measure $\Xi_s(dx) \times du$.
+\end{theorem}
+
+\subsection{Markov Mapping Theorem Application on Generator $A^{N}$}\label{sec: Markov Mapping Theorem Application - Prelimit}
+
+We now introduce some notations to simplify our calculations.
+For a finite atomic measure $\xi=\sum \delta_{(x_i,u_i)} \in \mathcal{M}(\mathbb{R}^d \times [0,N])$,
+we introduce the test functions
+ $$f_g(\xi)= \prod_{(x_i,u_i)\in \xi} g(x_i,u_i) = \exp (\langle \log g, \xi \rangle),$$
+ where $g \in \mathcal{C}(\mathbb{R}^d \times [0,\infty))$ and $g(x,u)=1$ for all $u \geq N$.
+
+ To avoid any ambiguities in the proofs,
+ we will strictly use the notation $\Xi^N$  
+to represent the scaled push-forward measure of $\lp$,
+i.e. $\Xi^N := \frac{1}{N}\sum_{(x,u) \in \lp} \delta_x$,
+and only use $(\eta^N_t)_{t \geq 0}$
+to refer to the PDE solutions defined in Definition  \ref{defn:mgale_construction}.
+
+We also write $\textbf{x}=(x_1,x_2,...), \textbf{u}=(u_1,u_2,...)$ to be the collections of particles locations and levels respectively.
+With this notation we will write $f_g(\xi), f_g(\textbf{x},\textbf{u})$ interchangeably.
+
+We write $\Gamma^N (d\textbf{u})$ as the probability kernel
+that corresponds to assigning each particle an i.i.d. uniform $[0,N]$-level, i.e.
+$$\int f_g(\textbf{x},\textbf{u})\Gamma^N (d\textbf{u})=\frac{1}{N^{|\xi|}}\int_{[0,N]^{|\xi|}}f_g(\textbf{x},\textbf{u})d\textbf{u},$$
 and we denote
-$$\hat{g}(x):=\frac{1}{\lambda}\int_{0}^{\lambda}g(x,u)du, ~~\hat{f}(\xi)=\int f(\xi) \Gamma (d\textbf{u})$$ 
-to be the spatial test functions with averaged level. By independence of the levels of the particles we have that
-$$\hat{f}(\xi)=\int \prod_{(x,u) \in \xi}g(x,u) \Gamma(d\textbf{u})=\prod_{(x,u)\in \xi}\frac{1}{\lambda}\int_{0}^{\lambda} g(x,u) du=\prod_{x_i \in \Xi}\hat{g}(x_i).$$ 
-We will now apply Markov Mapping Theorem while keeping notations consistent to that introduced in Section A.5 in \cite{kurtz/rodrigues:2011} with the aid of Table \ref{Markov Mapping Theorem Notation Table}.
-\begin{table}[h]
+$$\hat{g}(x):=\frac{1}{N}\int_{0}^{N}g(x,u)du,
+ ~~\hat{f}_g(\xi)=\int f_g(\xi) \Gamma (d\textbf{u})$$ 
+to be the spatial test functions with averaged level.
+By independence of the levels of the particles,
+ we have that
+ \begin{align*}
+\hat{f}_g(\xi)
+=&\int \prod_{(x,u) \in \xi}g(x,u) \Gamma(d\textbf{u})\\
+=&\prod_{(x,u)\in \xi}\frac{1}{N}\int_{0}^{N} g(x,u) du\\
+=&\prod_{(x_i,u_i)\in \xi }\hat{g}(x_i)\\
+=& \exp(N\log \hat{g},\Xi^N).
+ \end{align*}
+
+Furthermore,
+when expressed as a function of $\Xi^N$ explicitly,
+we use the notation $F_{\hat{g},N}(\Xi^N):=\hat{f}_g(\xi)$.
+
+We will now apply Markov Mapping Theorem
+while keeping notations consistent to that introduced in Section A.5 in \cite{kurtz/rodrigues:2011}
+with the aid of Table \ref{Markov Mapping Theorem Notation Table}.
+\begin{table}[!h]
     \centering
     \begin{tabular}{c|c}
-    Notation in \cite{kurtz/rodrigues:2011} & Notation in this paper \\
+    Notation in \cite{kurtz/rodrigues:2011} & Notation in this proof \\
     \hline\\
-      $S$   &  $\mathcal{M}(\IR^d \times [0, \lambda))$\\\\
+      $S$   &  $\mathcal{M}(\IR^d \times [0, N])$\\\\
        $S_0$  &  $\mathcal{M}(\IR^d)$\\\\
-       $A$ & $A^{\theta}$\\\\
-       $(X_t)_{t \geq 0}$ & $(\xi^{\theta}_t)_{t \geq 0}$\\\\
-       $\mu_0$ & $\Xi^{\theta}_0 \in \mathcal{M}(\IR^d)$\\\\
-       $\nu_0$ & $\xi^{\theta}_0 \in \mathcal{M}(\IR^d \times [0,\lambda])$\\\\
-       $f(\xi)$ & $\prod_{(x,u) \in \xi} g(x,u)$\\\\
-        $\gamma_M$ & $ \mathcal{M}(\IR^d \times [0, \lambda)) \ni \xi \to \frac{1}{\lambda}\sum_{(x,u) \in \xi, u < \lambda} \delta_{x} \in \mathcal{M}(\IR^d)$\\\\
-       $\alpha_M$ & $ \alpha_M(\Xi,d \nu) =     \begin{cases}
-      0 & \text{if } \sum_{(x,u) \in \nu, u < \lambda} \delta_x \neq \Xi\\
-       \prod_{(u_i,x_i) \in \nu} \frac{1}{\lambda} \ind_{[0,\lambda]}du_i & \text{if } \sum_{(x,u) \in \nu, u < \lambda} \delta_x = \Xi,\\
+       $A$ & $A^{N}$\\\\
+       $(X_t)_{t \geq 0}$ & $(\xi^N_t)_{t \geq 0}$\\\\
+       $\mu_0$ & $\eta^N_0 \in \mathcal{M}(\IR^d)$\\\\
+       $\nu_0$ & $\xi^N_0 \in \mathcal{M}(\IR^d \times [0,N])$\\\\
+       $f(\xi)$ & $f_g(\xi) := \prod_{(x,u) \in \xi} g(x,u)$\\\\
+        $\gamma_M$ & $ \mathcal{M}(\IR^d \times [0, N]) \ni \xi \to \frac{1}{N}\sum_{(x,u) \in \lp(\cdot, [0,N))} \delta_{x} \in \mathcal{M}(\IR^d)$\\\\
+       $\alpha_M$ & $ \alpha_M(\Xi^N,d \lp) =     \begin{cases}
+      0 & \text{if } \frac{1}{N}\sum_{(x,u) \in \lp(\cdot, [0,N))} \delta_x \neq \Xi^N\\
+       \prod_{(u_i,x_i) \in \nu} \frac{1}{N} \ind_{[0,N]}du_i & \text{if } \frac{1}{N}\sum_{(x,u) \in \lp(\cdot, [0,N))} \delta_x = \Xi^N,\\
     \end{cases} $\\
@@
 \end{table}
+
 \begin{remark}
-Note that $\gamma,\alpha$ in \cite{kurtz/rodrigues:2011} is replaced with $\gamma_M,\alpha_M$ to avoid confusion with the $\gamma, \alpha$ used in previous sections.
+Note that $\gamma,\alpha$ in \cite{kurtz/rodrigues:2011}
+is replaced with $\gamma_M,\alpha_M$ to avoid confusion with the $\gamma, \alpha$ used in previous sections.
 \end{remark}
-First of all, note that $\gamma_M$ is Borel-measurable and $\alpha_M$ is a transition function from $\mathcal{M}(\IR^d \times [0, \lambda))$ to $\mathcal{M}(\IR^d)$.
-More importantly, we have the following simplified expression for an integral against $\alpha_M$:
+
+First of all,
+note that $\gamma_M$ is Borel-measurable
+and $\alpha_M$ is a transition function from $\mathcal{M}(\IR^d \times [0, N))$ to $\mathcal{M}(\IR^d)$.
+
+More importantly, we have the following simplified expression
+for an integral against $\alpha_M$:
 \begin{equation}
-\int_{\mathcal{M}(\IR^d\times [0,\lambda])}A^{\theta}f(\nu)\alpha_M(\Xi,d\nu)= \int   A^{\theta}f(\textbf{x},\textbf{u})\Gamma(d\textbf{u}). 
-\end{equation}
+\int_{\mathcal{M}(\IR^d\times [0,N])}A^{N}f(\xi)\alpha_M(\Xi^N, d\lp)
+= \int   A^Nf(\textbf{x},\textbf{u})\Gamma^N(d\textbf{u}). 
+\end{equation}
+
 As a result, we can establish that
@@
 \begin{aligned}
-\alpha_M(\Xi,\gamma^{-1}(\Xi)) &= \int_{\nu \in \gamma^{-1}(y)}\alpha_M (\Xi,d\nu) \\
-&= \int_{\nu \in \prod_{x_i \in \Xi} \{x_i\}\times [0,\lambda]}\alpha_M (\Xi,d\nu)\\
-&= \prod_{x_i \in \Xi}\frac{1}{\lambda}\int_{0}^{\lambda} du_i =1
+\alpha_M(\Xi^N,\gamma^{-1}(\Xi^N)) 
+&= \int_{\lp \in \gamma^{-1}(y)}\alpha_M (\Xi^N, d\lp) \\
+&= \int_{\{\lp: \sum_{(x,u) \in \lp }\delta_x = N\Xi^N \} }\alpha_M (\Xi^N, d\lp)\\
+&= \prod_{x_i \in N\Xi^N}\frac{1}{N}\int_{0}^{N} du_i =1
 \end{aligned}
@@
 \begin{equation}\label{Markov Mapping Theorem Martingale Condition Simplified}
-C = \left\{\left(\int   f(\textbf{x},\textbf{u})\Gamma(d\textbf{u}),\int   A^{\theta}f(\textbf{x},\textbf{u})\Gamma(d\textbf{u})\right)\right\}    
-\end{equation}
-has a solution, i.e. the process
+C = \left\{\left(\int   f(\textbf{x},\textbf{u})\Gamma^N(d\textbf{u}),\int   A^Nf(\textbf{x},\textbf{u})\Gamma^N(d\textbf{u})\right)\right\}    
+\end{equation}
+has a solution.
+
+We now claim the following lemma.
+
+\begin{lemma}
+\label{lem: representation of lookdown generator - pre-limit}
+Let $\xi$ be a finite atomic measure on $\mathbb{R}^d \times [0,N]$.
+For test functions of the form 
+$$f_g(\xi)= \prod_{(x_i,u_i)\in \xi} g(x_i,u_i) = \exp (\langle \log g, \xi \rangle),$$
+we have the equality
+\begin{equation}
+\int   A^Nf(\textbf{x},\textbf{u})\Gamma^N(d\textbf{u})
+= \int \Pgen^N F_{\hat{g},N}(\Xi^N),
+\end{equation}
+where $\Pgen^N$ is the generator of the spatial process defined in Definition \ref{def2: MP definition of pre-limit}.
+ \end{lemma}
+
+With lemma \ref{lem: representation of lookdown generator - pre-limit},
+the martingale problem can then be re-written as 
+\begin{equation}\label{Markov Mapping Theorem Martingale Condition, projection form}
+C = \left\{\left(\int F_{\hat{g},N}(\Xi^N), \int \Pgen^N F_{\hat{g},N}(\Xi^N)\right)\right\}    
+\end{equation}
+which has $(\eta^N_t)_{t \geq 0}$,
+our spatial population process,
+as a solution.
+
+As a result,
+we can apply Markov Mapping Theorem to establish the following statements:
+\begin{enumerate}
+    \item There exists a $\mathcal{M}_F(\mathbb{R}^d\times[0,N])$-valued process $(\lp^N_t)_{t \geq 0}$
+    such that 
+    $M^N_t:=    f(\xi^N_t)-   f(\xi^N_0)-\int_{0}^{t}  A^Nf(\xi^N_s)ds$ is a martingale for all $f\in D(A^N)$,
+    \item The process $(\gamma_M \circ \xi^N_t)_{t \geq 0}= \left(\Xi^N_t\right)_{t \geq 0}$ 
+    has the same distribution in $\mathcal{D}_{\mathcal{M}(\mathbb{R}^d)}[0,\infty)$ as $(\eta^N_t)_{t \geq 0}$ defined in Definition \ref{def: MP definition of pre-limit}.
+    \item $\mathbb{P}\{\xi^N_t \in B | \mathcal{F}^{\Xi^N}_t\}=\alpha_M(\Xi^N(t),B), ~~~B \in \mathcal{B}(\mathcal{M}(\IR^d \times [0,N])).$
+\end{enumerate}
+Note that in particular,
+from the third statement,
+we can establish that for $h(x,u) \in \mathcal{C}_{c}(\mathbb{R}^d \times[0,N])$ and $h \geq 0$,
+
+\begin{equation}\label{Markov Mapping Theorem Cox Condition}
+\begin{aligned}
+\mathbb{E}\left[e^{-\int_{S \times [0,N]} h(x,u) \xi^{N}(dx \times du)}\bigg| \mathcal{F}^{\Xi^{N}}_t\right]
+&=\mathbb{E}\left[\prod_{(x,u)\in\xi^N_t}e^{-h(x,u)}\bigg| \mathcal{F}^{\Xi^{N}}_t\right]\\
+&=\prod_{x \in N\Xi^N_t} \frac{1}{N} \int_{0}^N. e^{-h(x_i,u_i)} du_i
+&= e^{-\langle F^N_h(x), \Xi^N(dx)\rangle},
+\end{aligned}
+\end{equation}
+where 
+$$F^{N}_h(x):=-N\log \left(\frac{1}{N}\int_{0}^{N}e^{-h(x,u)}du\right)=-N\log \left(1-\frac{1}{N}\int_{0}^{N}(1-e^{-h(x,u)})du\right).$$
+
+Therefore we only need to prove lemma \ref{lem: representation of lookdown generator - pre-limit}.
+The procedure to prove Lemman \ref{lem: representation of lookdown generator - pre-limit}
+is rather standard and set out in \cite{kurtz/rodrigues:2011},
+albeit we will face more technicalities for this setting.
+
+For tidy computations in this proof, 
+we recall the notation that an individual at $x$ gives birth at rate
+$$
+    \gamma^{\mathfrak{m}}_{\theta}(x,\eta) := \theta \gamma(x, \smooth{\gamma} \eta(x))
+    \int r(y, \smooth{r} \eta(y)) q_{\theta}(x, dy) ,
+$$
+and that offspring disperse according to the kernel
+$$
+    q_\theta^\mathfrak{m}(x,\eta,  dy)
+    :=
+    \frac{
+        r(y, \smooth{r} \eta(y)) q_\theta(x, dy)
+    }{
+        \int r(z, \smooth{r} \eta(z)) q_\theta(x, dz)
+    } .
+$$
+
+We will also write $\Xi, \Gamma$ instead of $\Xi^N, \Gamma^N$,
+bearing in mind the dependence of $\Xi, \Gamma$ on $N$.
+
+\begin{proof}[Proof to Lemma \ref{lem: representation of lookdown generator - pre-limit}]
+
+Recall that the lookdown generator of our spatial-level process satisfies
+\begin{align}
+A^Nf(\xi)=&
+f(\xi)\sum_{(x,u)\in\xi}2N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\times
+\int_u^{
+N}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\IR^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\theta}(x,\Xi ,dy) \nonumber \\
+& \qquad \qquad \qquad \qquad +\int_{\IR^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\theta}(x,\Xi,dy)\Bigg)dv_1 \nonumber\\
+&+f(\xi )\sum_{(x,u)\in\xi}\,\left(N^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)},
+\end{align}
+where $f(\xi) =\prod_{(x,u) \in \xi}g(x,u)$.
+
+For easier computation,
+we break the generator into three parts, 
 \begin{equation}
 \begin{aligned}
-M_t:=& \int   f(\textbf{x}_t,\textbf{u}_t)\Gamma(d\textbf{u})-\int   f(\textbf{x}_0,\textbf{u}_0)\Gamma(d\textbf{u})-\int_{0}^{t}\int   A^{\theta}f(\textbf{x}_s,\textbf{u}_s)\Gamma(d\textbf{u})ds\\
-=&\hat{f}(\xi_t)-\hat{f}(\xi_0)-\int_{0}^{t}\int   A^{\theta}f(\xi_s)\Gamma(d\textbf{u})ds
+A^N_1f(\xi)=&f(\xi)\sum_{(x,u)\in\xi}2N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\times
+\int_u^{
+N}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\IR^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\theta}(x,\Xi ,dy)\Bigg)dv_1,\\
+A^N_2f(\xi)=&f(\xi)\sum_{(x,u)\in\xi}2N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\times
+\int_u^{
+N}\Bigg(\frac{1}{2}\int_{\IR^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\theta}(x,\Xi,dy)\Bigg)dv_1,\\
+A^N_3f(\xi)=&f(\xi )\sum_{(x,u)\in\xi}\,\left(N^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)},
 \end{aligned}
 \end{equation}
-is a martingale.\\
-Once we manage to solve the Martingale Problem \eqref{Markov Mapping Theorem Martingale Condition Simplified}, the Markov Mapping Theorem guarantees the following fact:
-\begin{enumerate}
-    \item $N_t:=    f(\xi_t)-   f(\xi_0)-\int_{0}^{t}  A^{\theta}f(\xi_s)ds$ is a martingale for all $f\in D(A^{\theta})$,
-    \item The process $(\gamma_M \circ \xi^{\theta}_t)_{t \geq 0}:= \left(\frac{1}{\lambda}\sum_{(x,u)\in \xi^{\theta}_t, u < \lambda} \delta_x\right)_{t \geq 0}=(\Xi^{\theta}_t)_{t \geq 0}$ solves the Martingale Problem \eqref{Markov Mapping Theorem Martingale Condition Simplified}.
-    \item $\mathbb{P}\{\xi^{\theta}_t \in B | \mathcal{F}^{\Xi^{\theta}}_t\}=\alpha_M(\Xi^{\theta}(t),\meanq), ~~~B \in \mathcal{B}(\mathcal{M}(\IR^d \times [0,\lambda])).$
-\end{enumerate}
-Note that in particular, the third statement is equivalent to the fact that conditioned on the spatial configuration $\Xi^{\theta}_t$, the levels of the particles must be i.i.d uniformly between $[0,\lambda]$.
-We may also express this condition through the following equation:
-\begin{equation}\label{Markov Mapping Theorem Cox Condition}
-\mathbb{E}\left[e^{-\int_{S \times [0,\lambda]} f(x,u) \xi^{\epsilon,\theta,\lambda}(dx \times du)}\bigg| \mathcal{F}^{\Xi^{\epsilon,N}}_t\right]=e^{-\int F^{\epsilon,\theta,\lambda}_f(x) \Xi^{\epsilon,\theta,\lambda}_t(dx)},
-\end{equation}
-where 
-$$F^{\epsilon,\theta,\lambda}_f(x):=-\lambda\log \left(\frac{1}{\lambda}\int_{0}^{\lambda}e^{-f(x,u)}du\right)=-\lambda\log \left(1-\frac{1}{\lambda}\int_{0}^{\lambda}(1-e^{-f(x,u)})du\right).$$
-
-Therefore we only need to solve Martingale Problem \eqref{Markov Mapping Theorem Martingale Condition Simplified}.\\
-
-The procedure to solve the Martingale Problem \eqref{Markov Mapping Theorem Martingale Condition Simplified} is rather standard and set out in \cite{kurtz/rodrigues:2011}, albeit we will face more technicalities for this setting.
-Recall that the lookdown generator of our spatial-level process satisfies
-\begin{align}\label{Lookdown generator N lambda theta prelimit}
-A^{\theta}f(\xi)=&f(\xi)\sum_{(x,u)\in\xi}2\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\times
-\int_u^{
-\lambda}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\IR^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
-\xi },dy) \nonumber \\
-& \qquad \qquad \qquad \qquad +\int_{\IR^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy)\Bigg)dv_1 \nonumber\\
-&+f(\xi )\sum_{(x,u)\in\xi}\,\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)},
-\end{align}
-where $f(\xi) =\prod_{(x,u) \in \xi}g(x,u)$. 
-For easier computation we break the generator into three parts, 
-\begin{equation}
-\begin{aligned}
-A^{\theta,1}f(\xi)=&f(\xi)\sum_{(x,u)\in\xi}2\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\times
-\int_u^{
-\lambda}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\IR^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
-\xi },dy)\Bigg)dv_1,\\
-A^{\theta,2}f(\xi)=&f(\xi)\sum_{(x,u)\in\xi}2\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\times
-\int_u^{
-\lambda}\Bigg(\frac{1}{2}\int_{\IR^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy)\Bigg)dv_1,\\
-A^{\theta,3}f(\xi)=&f(\xi )\sum_{(x,u)\in\xi}\,\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)},
-\end{aligned}
-\end{equation}
 such that 
-$$A^{\theta}f(\xi)=A^{\theta,1}f(\xi)+A^{\theta,2}f(\xi)+A^{\theta,3}f(\xi).$$
+$$A^Nf(\xi)=A^N_1f(\xi)+A^N_2f(\xi)+A^N_3f(\xi).$$
+
 We now calculate each generator evaluated under our probability kernel $\Gamma$.
@@
 \begin{align*}
-&\int A^{\theta,1}f(\xi) \Gamma(d\mathbf{u})\\ &=\int \Bigg\{f(\xi)\sum_{(x,u)\in\xi}2\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)
+&\int A^N_1f(\xi) \Gamma(d\mathbf{u})\\ &=\int \Bigg\{f(\xi)\sum_{(x,u)\in\xi}2N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)
 \int_u^{
-\lambda}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\IR^d}(g(y,u)-g(x,u))q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
-\xi },dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
-&=\sum_{(x,u)\in\xi} \int \Bigg\{\frac{f(\xi)}{g(x,u)}2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi)
+N}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\IR^d}(g(y,u)-g(x,u))q^{\mathfrak{m}}_{\theta}(x,\Xi ,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
+&=\sum_{(x,u)\in\xi} \int \Bigg\{\frac{f(\xi)}{g(x,u)}2N^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi)
 \int_u^{
-\lambda}\Bigg(\frac 12 g(x,v_1)\int_{\IR^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
-\xi },dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
-&=\sum_{(x,u)\in\xi}\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\int_{0}^{\lambda}\left\{
+N}\Bigg(\frac 12 g(x,v_1)\int_{\IR^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\theta}(x,\Xi ,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
+&=\sum_{(x,u)\in\xi}N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{N}\int_{0}^{N}\left\{
 \int_u^{
-\lambda} g(x,v_1)dv_1\times \int_{\IR^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
-\xi },dy)\right\}du\\
-&=\sum_{(x,u)\in\xi}\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\int_{\IR^d} \left\{\int_{0}^{\lambda}
+N} g(x,v_1)dv_1\times \int_{\IR^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\theta}(x,\Xi ,dy)\right\}du\\
+&=\sum_{(x,u)\in\xi}N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{N}\int_{\IR^d} \left\{\int_{0}^{N}
 \int_u^{
-\lambda} g(x,v_1) (g(y,u)-g(x,u))dv_1du\right\}q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
-\xi },dy)
-\end{align*}
+N} g(x,v_1) (g(y,u)-g(x,u))dv_1du\right\}q^{\mathfrak{m}}_{\theta}(x,\Xi ,dy)
+\end{align*}
+
 \normalsize
@@
 \begin{align*}
-&\int A^{\theta,2}f(\xi) \Gamma(d\mathbf{u})\\&=\int \Bigg\{f(\xi)\sum_{(x,u)\in\xi}2\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\times
+&\int A^N_2f(\xi) \Gamma(d\mathbf{u})\\&=\int \Bigg\{f(\xi)\sum_{(x,u)\in\xi}2N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\times
 \int_u^{
-\lambda}\Bigg(\int_{\IR^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
-&=\sum_{(x,u)\in\xi}\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\int \Bigg\{f(\xi)\times
+N}\Bigg(\int_{\IR^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\theta}(x,\Xi,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
+&=\sum_{(x,u)\in\xi}N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\int \Bigg\{f(\xi)\times
 \int_u^{
-\lambda}\Bigg(\int_{\IR^d}\left(g(y,v_1)+g(x,v_1)-2\right)q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
-&=\sum_{(x,u)\in\xi}\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i) \frac{1}{\lambda}\int_{\IR^d}\Bigg\{\int_{0}^{\lambda}
+N}\Bigg(\int_{\IR^d}\left(g(y,v_1)+g(x,v_1)-2\right)q^{\mathfrak{m}}_{\theta}(x,\Xi,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
+&=\sum_{(x,u)\in\xi}N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i) \frac{1}{N}\int_{\IR^d}\Bigg\{\int_{0}^{N}
 \int_u^{
-\lambda}g(x,u) \left(g(y,v_1)+g(x,v_1)-2\right)dv_1 du\Bigg\} q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy).
-\end{align*}  
+N}g(x,u) \left(g(y,v_1)+g(x,v_1)-2\right)dv_1 du\Bigg\} q^{\mathfrak{m}}_{\theta}(x,\Xi,dy).
+\end{align*}
+
 \normalsize
@@
 \begin{align*}
- &\int A^{\theta,3}f(\xi)\Gamma(d\mathbf{u})\\&=\int f(\xi )\,\left(\lambda^{-1} \sum_{(x,u)\in\xi}\theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)}\Gamma(d\mathbf{u}) \\
- &=\sum_{(x,u)\in\xi}\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\int_{0}^{\lambda}  \left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\partial_u g(x,u)du \\
- &=-\sum_{(x,u)\in\xi}\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\int_{0}^{\lambda}  \left(2u\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) -b_{\theta}(x,\Xi)\right)\left(g(x,u)-1\right)du \\
- &=-\sum_{(x,u)\in\xi}\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\int_{0}^{\lambda}   2ug(x,u)du \\
- &+\sum_{(x,u)\in\xi}\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\times \lambda^2+\sum_{(x,u)\in\xi}\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)b_{\theta}(x,\Xi)(\hat{g}(x)-1) \\
-\end{align*}
-Using the symmetry we have
-\begin{align*}
-&\int_{0}^{\lambda}
+ &\int A^N_3f(\xi)\Gamma(d\mathbf{u})\\
+ =&\int f(\xi )\,\left(N^{-1} \sum_{(x,u)\in\xi}\theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)}\Gamma(d\mathbf{u}) \\
+ =&\sum_{(x,u)\in\xi}\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{N}\int_{0}^{N}  \left(N^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\partial_u g(x,u)du \\
+ =&-\sum_{(x,u)\in\xi}\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{N}\int_{0}^{N}  \left(2uN^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) -b_{\theta}(x,\Xi)\right)\left(g(x,u)-1\right)du \\
+ =&-\sum_{(x,u)\in\xi}N^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{N}\int_{0}^{N}   2ug(x,u)du \\
+ &+\sum_{(x,u)\in\xi}N^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{N}\times N^2+\sum_{(x,u)\in\xi}\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)b_{\theta}(x,\Xi)(\hat{g}(x)-1)
+\end{align*}
+
+By symmetry, we have
+\begin{align*}
+&\int_{0}^{N}
 \int_u^{
-\lambda} g(x,v_1) (g(y,u)-g(x,u))dv_1du+\int_{0}^{\lambda}
+N} g(x,v_1) (g(y,u)-g(x,u))dv_1du+\int_{0}^{N}
 \int_u^{
-\lambda}g(x,u) \left(g(y,v_1)+g(x,v_1)-2\right)dv_1 du
-\\&= \int_{0}^{\lambda}
+N}g(x,u) \left(g(y,v_1)+g(x,v_1)-2\right)dv_1 du
+\\&= \int_{0}^{N}
 \int_u^{
-\lambda}g(x,u)g(y,v_1)+g(y,u)g(x,v_1)-2g(x,u) dv_1 du\\
-&=\frac{1}{2}\int_{0}^{\lambda}\int_{0}^{\lambda}g(x,u)g(y,v_1)+g(y,u)g(x,v_1)dv_1 du - 2 \int_{0}^{\lambda}(\lambda-u)g(x,u)du\\
-&=\lambda^2 \hat{g}(x)\hat{g}(y) -2\lambda^2 \hat{g}(x)+2\int_{0}^{\lambda}ug(x,u)du.
-\end{align*}
-Combining the last equations we have 
-\begin{align*}
-&\int \Bigg(A^{1}_{\theta}f(\xi)+A^{2}_{\theta}f(\xi)+A^{3}_{\theta}f(\xi)\Bigg)\Gamma(d\mathbf{u})\\
-&=  \sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)}\hat{g}(x_i) \left( \int_{\IR^n} \hat{g}(y) q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy) - 2+\frac{1}{\hat{g}(x)}\right)+\sum_{(x,u) \in \xi } \prod_{(x_i,u_i)}\hat{g}(x_i)b_{\theta}(x,\Xi)\left(1-\frac{1}{\hat{g}(x)}\right)\\
-&=  \hat{f}(\xi)\sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi) \left(\int_{\IR^n} \hat{g}(y) q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy) -1\right)+\hat{f}(\xi)\sum_{(x,u) \in \xi } (b_{\theta}(x,\Xi)-\theta\gamma^{\mathfrak{m}}_{\theta}(x,\xi))\left(1-\frac{1}{\hat{g}(x)}\right)\\
-&=  \hat{f}(\xi)\sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi) \left(\int_{\IR^n} \hat{g}(y) q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy) -1\right) -\hat{f}(\xi)\sum_{(x,u) \in \xi } \theta \mu_{\epsilon,\theta}(x,\Xi)\left(1-\frac{1}{\hat{g}(x)}\right),
-\end{align*}
-which corresponds to a spatial-branching process that branches at rate $\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)$ leaving offspring around with kernel $ q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy)$ and each particle having death rate given by $\theta \mu_{\epsilon,\theta}(x,\Xi)$.
-This is precisely the martingale problem in Definition \ref{def: Martingale Problem Characterisation - Product Form}.
+N}g(x,u)g(y,v_1)+g(y,u)g(x,v_1)-2g(x,u) dv_1 du\\
+&=\frac{1}{2}\int_{0}^{N}\int_{0}^{N}g(x,u)g(y,v_1)+g(y,u)g(x,v_1)dv_1 du - 2 \int_{0}^{N}(N-u)g(x,u)du\\
+&=N^2 \hat{g}(x)\hat{g}(y) -2N^2 \hat{g}(x)+2\int_{0}^{N}ug(x,u)du.
+\end{align*}
+
+Combining the last equations,
+we have 
+\begin{align*}
+&\int \Bigg(A^N_1f(\xi)+A^N_2f(\xi)+A^N_3f(\xi)\Bigg)\Gamma(d\mathbf{u})\\
+=&  \sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)}\hat{g}(x_i) \left( \int_{\IR^n} \hat{g}(y) q^{\mathfrak{m}}_{\theta}(x,\Xi,dy) - 2+\frac{1}{\hat{g}(x)}\right)\\
+&+\sum_{(x,u) \in \xi } \prod_{(x_i,u_i)}\hat{g}(x_i)b_{\theta}(x,\Xi)\left(1-\frac{1}{\hat{g}(x)}\right)\\
+=&  \hat{f}(\xi)\sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi) \left(\int_{\IR^n} \hat{g}(y) q^{\mathfrak{m}}_{\theta}(x,\Xi,dy) -1\right)\\
+&+\hat{f}(\xi)\sum_{(x,u) \in \xi } (b_{\theta}(x,\Xi)-\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi))\left(1-\frac{1}{\hat{g}(x)}\right)\\
+=&  F_{\hat{g},N}(\Xi^N)\sum_{x \in \Xi}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi) \left(\int_{\IR^n} \hat{g}(y) q^{\mathfrak{m}}_{\theta}(x,\Xi,dy) -1\right) \\
+&-F_{\hat{g},N}(\Xi^N)\sum_{x \in \Xi } \theta \mu_{\epsilon,\theta}(x,\Xi)\left(1-\frac{1}{\hat{g}(x)}\right)\\
+=& \Pgen^N F_{\hat{g},N}(\Xi^N).
+\end{align*}
+
+The last equality holds
+as the second last expression corresponds to a spatial-branching process
+that branches at rate $\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)$,
+leaving offspring around with kernel $ q^{\mathfrak{m}}_{\theta}(x,\Xi,dy)$,
+with each particle having death rate given by $\theta \mu_{\epsilon,\theta}(x,\Xi)$.
+This is precisely the martingale problem in Definition \ref{def: MP definition of pre-limit}.
+
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%
 \newpage
-\subsection{Markov Mapping Theorem Application on Generator $A^{\text{nl}}_{\epsilon}$}\label{sec: Markov Mapping Theorem application - limit}
-In this section we consider a general generator limit for the lookdown representation of our spatial model. 
-We define
+\subsection{Markov Mapping Theorem Application on Generator $A$}\label{sec: Markov Mapping Theorem application - limit}
+
+Now,
+we turn to the generator for the limiting case,
+which has the form
     \begin{equation}
     \begin{aligned}
-A^{\text{nl}}_{\epsilon}f(\eta )  =&f(\eta )\sum_{(x,u)\in\eta}\Bigg\{
- \gamma(x, (\rho_{\epsilon}*\Xi)(x))
- \frac{\mathcal{B}(g(\cdot,u)r( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)-g(x,u)\mathcal{B}r( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)}{g(x,u)}\\
- &
-  +2\gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\times \ell \int_u^{
-\infty}(g(x,v_1)-1)dv_1\\
-&
-+\bigg(\ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x)) u^2 \\
-&~~~~~~~-\big(F(x, (\rho_{\epsilon}*\Xi)(x))+\gamma(x, (\rho_{\epsilon}*\Xi)(x))\mathcal{B}r( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)\big)u\bigg) \frac {\partial_u g(x,u)}{g(x,u)}\Bigg\},
+    A f(\lp)
+    =&
+        f(\lp)  \sum_{(x, u) \in \xi}
+        \gamma(x, \eta)
+            \frac{
+                \DG(g(\cdot, u) r(\cdot, \eta))(x) - g(x,u) \DG r(x,\eta)
+            }{
+                g(x, u)
+            }
+    \\ &+
+        f(\lp) \sum_{(x, u) \in \xi}
+        2 \alpha \gamma(x, \Xi) r(x, \Xi ) \int_u^\infty (g(x, u_1) - 1) du_1
+    \\ &+
+        f(\lp) \sum_{(x, u) \in \xi}
+        \left(
+            \alpha \gamma(x, \Xi) r(x, \Xi ) u^2
+            -
+            \left\{
+                \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta)
+            \right\} u
+        \right)
+        \frac{\partial_u g(x, u)}{ g(x,u) }  .
     \end{aligned}
     \end{equation}
-where our test measure $\eta$ takes value on $\mathcal{M}_F(\IR\times [0,\infty))$ and $\Xi:=\lim_{u_0\rightarrow\infty}\frac 1{u_0}\sum_{(u,x)\in \eta:u\leq u_0}\delta_x$.
-
-If we take $\gamma =1, r=1, \mathcal{B}=\Delta,$ and $F(x, (\rho_{\epsilon}*\Xi)(x))=G( (\rho_{\epsilon}*\Xi)(x))-H( (\rho_{\epsilon}*\Xi)(x))$, then we recover $A^{\epsilon, \infty}$ defined in Equation \eqref{Eq: Non-local Scaling limit Lookdown Generator}.
-
-Similar to the calculations above, we write $\alpha(\Xi,\cdot)$ for the distribution of a conditionally
-Poisson random measure $\eta^{\infty}$ on $\IR^d\times [0,\infty)$ with mean measure
-$\Xi(dx)\times \Lambda$ and we calculate $\alpha A^{\text{nl}}_{\epsilon}f(\eta)$.
-
-Once again, we write
-$$\alpha A^{\text{nl}}_{\epsilon}f(\eta)=\alpha A^{1}_{nl}f(\eta)+\alpha A^{2}_{nl}f(\eta)+\alpha A^{3}_{nl}f(\eta),$$
-where 
-\small
-\begin{equation}\label{Eq: Decomposition of the Non-local Scaling limit Lookdown Generator}
+
+To apply Markov Mapping Theorem,
+we consider Table \ref{Markov Mapping Theorem Notation Table Limit}.
+
+\begin{table}[!h]
+    \centering
+    \begin{tabular}{c|c}
+    Notation in \cite{kurtz/rodrigues:2011} & Notation in this proof \\
+    \hline\\
+      $S$   &  $\mathcal{M}(\IR^d \times [0, \infty])$\\\\
+       $S_0$  &  $\mathcal{M}(\IR^d)$\\\\
+       $A$ & $A$\\\\
+       $(X_t)_{t \geq 0}$ & $(\xi_t)_{t \geq 0}$\\\\
+       $\mu_0$ & $\xi_0 \in \mathcal{M}(\IR^d)$\\\\
+       $\nu_0$ & $\xi_0 \in \mathcal{M}(\IR^d \times [0,\infty])$\\\\
+       $f(\xi)$ & $f_g(\xi) := \prod_{(x,u) \in \xi} g(x,u)$\\\\
+        $\gamma_M$ & $ \mathcal{M}(\IR^d \times [0, \infty]) \ni \xi \to \lim_{u_0 \to \infty}\frac{1}{u_0}\sum_{(x,u) \in \lp(\cdot, [0,u_0))} \delta_{x} \in \mathcal{M}(\IR^d)$\\\\
+       $\alpha_M$ & $ \Gamma^M(\Xi,d \lp) \sim PP(\Xi(dx)\times \Lambda(du)) ~~ \text{if } \gamma_M(\xi)=\Xi$,\\
+       &      where $\Lambda(du)$ is the standard Lebesgue measure on $[0,\infty)$.
+    \end{tabular}
+    \caption{Markov Mapping Theorem Correspondence}
+    \label{Markov Mapping Theorem Notation Table Limit}
+\end{table}
+
+Once again,
+we need to find solutions to the Martingale Problem 
+\begin{equation}
+C = \left(\int f_g(\xi) \Gamma^M(\cdot, d\xi), \int Af_g(\xi) \Gamma^M(\cdot, d\xi))\right),
+\end{equation}
+where $\Gamma^M(\Xi, d\lp)$ is the law of $\xi$,
+which is conditionally Poisson with Cox measure $\Xi(dx) \times \Lambda(du)$.
+
+Since we impose that $\xi$ is conditionally Poisson with Cox measure $\Xi(dx) \times \Lambda(du)$,
+for any test function $l(x,u) > 0$,
+\begin{equation}
+\mathbb{E}\left[e^{-\int_{\mathbb{R}^d \times [0,\infty]} l(x,u) \xi(dx,du)}\big| \Xi \right] = e^{-\int_{\mathbb{R}^d} \int_{0}^{\infty} (1-e^{-l(x,u)}) du \Xi(dx)}.
+\end{equation}
+
+Note that 
+$\prod_{(x,u) \in \xi} g(x,u) = e^{-\int_{\mathbb{R}^d \times [0,\infty]} -\log g(x,u) \xi(dx,du)},$
+so taking $l(x,u)= -\log g(x,u)$ and $h(x,u)= \int_{0}^{\infty} (1 -g(x,u))du$,
+we have the equation
+\begin{equation}
 \begin{aligned}
-A^{1}_{nl}f(\eta )  =&f(\eta )\sum_{(x,u)\in\eta}
- \gamma(x, (\rho_{\epsilon}*\Xi)(x))
- \frac{B(g(\cdot,u)r( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)-g(x,u)Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)}{g(x,u)},\\
-A^{2}_{nl}f(\eta )  = &
-  f(\eta )\sum_{(x,u)\in\eta}2\gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\times \ell \int_u^{
-\infty}(g(x,v_1)-1)dv_1,\\
- A^{3}_{nl}f(\eta )  =&f(\eta )
-\sum_{(x,u)\in\eta}\bigg(\ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x)) u^2\\
-&\qquad \qquad \qquad \qquad -\big(F(x, (\rho_{\epsilon}*\Xi)(x))+\gamma(x, (\rho_{\epsilon}*\Xi)(x))Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)\big)u\bigg)\frac {\partial_u g(x,u)}{g(x,u)}\\
+\int f_g(\xi) \alpha_M(\Xi, d\xi) 
+=&  e^{-\int_{\mathbb{R}^d} \int_{0}^{\infty} (1-e^{-l(x,u)}) du \Xi(dx)}\\
+=&  e^{-\int_{\mathbb{R}^d} \int_{0}^{\infty} (1-g(x,u)) du \Xi(dx)}\\
+=& \exp(\langle -h(x), \Xi(dx)\rangle),
 \end{aligned}
 \end{equation}
-\normalsize
-
-We define $h(x)=\int_{0}^{\infty} (1-g(x,u))du$.
-In this case, we have that $$\alpha f(\eta) = \exp \left(\int\int \big(g(x,u)-1\big) du \Xi(dx)\right)= \exp(\langle -h(x),\Xi(dx) \rangle ).$$  As a result we have that
-\begin{equation}\label{Eq: Averaging the Non-local Scaling limit Lookdown Generator Part 1}
-\footnotesize
+and we will denote the last term as $\mathcal{E}_{-h}(\Xi)$.
+Note that this notation is consistent to the test function
+$F_f(\eta)$ laid out in \ref{def: MP definition of limit},
+if we take $F(\cdot)=\mathcal{E}(\cdot) := \exp(\cdot)$ and $f=-h$.
+
+We now state the crucial lemma that allows us to apply Markov Mapping Theorem.
+\begin{lemma}
+\label{lem: MMT for limit}
+Let $\lp$ be a finite measure on $\mathbb{R}^d \times [0,\infty)$,
+$\Xi$ be a finite measure on $\mathbb{R}^d$,
+and $\Lambda(dx)$ be the Lesbesgue measure on  $[0,\infty)$.
+
+We consider test functions 
+$f(\xi):= \prod_{(x_i,u_i) \in \xi} g(x_i,u_i)$
+with $g \in C^2_{0}(\mathbb{R}^d \times[0,\infty))$
+and for which there exists $u_0$ with 
+$g(x,u)=1$ for all $u>u_0$.
+Furthermore, we define 
+$h(x,u)= \int_{0}^{\infty} (1 -g(x,u))du$
+and $\mathcal{E}_{-h}(\Xi)= \exp(\langle -h(x), \Xi(dx)\rangle)$.
+
+We write $\Gamma^{\Xi}(d\lp)$ to be the law
+on $\mathcal{M}(\mathbb{R}^d \times[0,\infty))$ 
+for a conditionally Poisson random measure $\lp$
+on $\IR^d\times [0,\infty)$
+with Cox measure $\Xi(dx)\times \Lambda(du)$.
+
+Then,
+for generator $A$ defined in Equation \eqref{eqn:limiting_lookdown_generator},
+\begin{equation}
+\int Af(\lp) \Gamma^{\Xi}(d\lp) = \Pgen \mathcal{E}_{-h}(\Xi),
+\end{equation}
+where $\Pgen$ is defined in Definition \ref{def2: MP definition of limit}.
+\end{lemma}
+
+Given the above lemma, 
+the following three statements hold true.
+\begin{enumerate}
+    \item There exists a $\mathcal{M}_F(\mathbb{R}^d\times[0,\infty])$-valued process $(\lp_t)_{t \geq 0}$
+    such that 
+    $M_t:=    f(\xi_t)-   f(\xi_0)-\int_{0}^{t}  Af(\xi_s)ds$ is a martingale for all $f\in D(A)$,
+    \item The process $(\gamma_M \circ \xi_t)_{t \geq 0}= \left( \lim_{u_0 \to \infty}\frac{1}{u_0}\sum_{(x,u) \in \lp_t(\cdot, [0,u_0))} \delta_{x} \right)_{t \geq 0}$ 
+    has the same distribution in $\mathcal{D}_{\mathcal{M}(\mathbb{R}^d)}[0,\infty)$ as $(\eta_t)_{t \geq 0}$ defined in Definition \ref{def: MP definition of limit}.
+    \item $\mathbb{P}\{\xi_t \in B | \mathcal{F}^{\Xi_t}\}=\Gamma^{\Xi_t}(B), ~~~B \in \mathcal{B}(\mathcal{M}(\IR^d \times [0,\infty])).$
+\end{enumerate}
+
+Finally,
+we recall an important equality for conditionally Poisson point processes (\cite{kurtz/rodrigues:2011} Lemma A.3.)
+which will be used extensively in the upcoming proof.
+
+\begin{lemma}
+Let $\lp =\sum_{i}\delta_{Z_i}$ be a Poisson random measure with mean measure $\nu$, 
+then for $\ell \in L^{1}(\nu)$ and $g\geq0$ with $\log g \in L^{1}(\nu)$,
+\begin{equation}
+\mathbb{E}[\sum_{j} \ell(Z_j) \prod_{i}g(Z_i)] = \int \ell g d\nu e^{\int (g-1) d \nu}.
+\end{equation}
+\end{lemma}
+
+In particular,
+taking $\nu(dx,du)=\Xi(dx) \times \Lambda(du)$,
+we have the equation 
+\begin{equation}
+\label{eq: cond_poi_sum_prod}
 \begin{aligned}
-\alpha A^{1}_{nl}f(\eta )  =&
- \alpha \left\{\sum_{(x,u)\in\eta}\gamma(x, (\rho_{\epsilon}*\Xi)(x))\frac{B(g(\cdot,u)r( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)-g(x,u)Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)}{g(x,u)}\prod_{(x_i,u_i)}g(x_i,u_i)\right\}\\
- =&\int\int \bigg( \gamma(x, (\rho_{\epsilon}*\Xi)(x))B((g(\cdot,u)-1)r( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)-(g(x,u)-1)Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)\bigg)du \Xi(dx)\\
- &\times \exp \left(\int\int \big(g(x,u)-1\big) du \Xi(dx)\right),\\
- =& \left\langle \gamma(x, (\rho_{\epsilon}*\Xi)(x))B(h(\cdot) r( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)-h(\cdot)Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x),\Xi(dx) \right\rangle e^{-\langle h(x),\Xi(dx)\rangle} \\
- \alpha A^{2}_{nl}f(\eta )  = &
-   \alpha \left\{2\sum_{(x,u)\in\eta}\gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\times \ell \int_u^{
-\infty}(g(x,v_1)-1)dv_1\prod_{(x_i,u_i)}g(x_i,u_i)\right\}\\
-=& \int\int \bigg(g(x,u)\gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\times \ell \int_u^{
-\infty}(g(x,v_1)-1)dv_1\bigg)du \Xi(dx)e^{-\langle h(x),\Xi(dx)\rangle}\\
-=& 
-\left\langle \ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\int g(x,u)\int_u^{
-\infty}(g(x,v_1)-1)dv_1 du,\Xi(dx)\right\rangle e^{-\langle h(x),\Xi(dx)\rangle}\\
- \alpha A^{3}_{nl}f(\eta )  =&
-\alpha \Bigg\{\sum_{(x,u)\in\eta}\bigg(\ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x)) u^2 -\big(F(x, (\rho_{\epsilon}*\Xi)(x))+\gamma(x, (\rho_{\epsilon}*\Xi)(x))Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)\big)u\bigg)\\
-&\times \frac {\partial_u g(x,u)}{g(x,u)}\prod_{(x_i,u_i)}g(x_i,u_i)\Bigg\}\\
-=& \bigg \langle \ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\int \partial_u g(x,u) u^2 du \\
-& ~~~ - \big(F(x, (\rho_{\epsilon}*\Xi)(x))+\gamma(x, (\rho_{\epsilon}*\Xi)(x))Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)\big) \int u \partial_u g(x,u) du ,\Xi(dx)\bigg\rangle \times e^{-\langle h(x),\Xi(dx)\rangle} .
+\int f(\xi) \sum_{(x,u)\in \xi} \ell(x,u)\Gamma^{\Xi}(d\xi)
+=& \mathbb{E}_{\xi \sim PP(\Xi \times \Lambda)}\left[\sum_{(x_j,u_j)\in \xi} \ell(x_j,u_j) \prod_{(x_i,u_i) \in \xi}g(x_i,u_i)\right]\\
+ =& \left \langle \int_{0}^{\infty} \ell(x,u) g(x,u) du ,\Xi(dx) \right\rangle \exp(\langle -h(x), \Xi(dx) \rangle) \\
+ =& \left \langle \int_{0}^{\infty} \ell(x,u) g(x,u) du ,\Xi(dx) \right\rangle \mathcal{E}_{-h}(\Xi)
 \end{aligned}
 \end{equation}
-\normalsize
-Now note that with integration by parts
-\begin{multline}
- \ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))  \int_{0}^{\infty}\partial_u g(x,u) u^2 du  \\=  2\ell\gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\int_{0}^{\infty} u (g(x,u)-1) du,
-\end{multline}
-\begin{multline}
- \big(F(x, (\rho_{\epsilon}*\Xi)(x))+\gamma(x, (\rho_{\epsilon}*\Xi)(x))Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)\big)\int_{0}^{\infty} u \partial_u g(x,u)du \\=\big(F(x, (\rho_{\epsilon}*\Xi)(x))+\gamma(x, (\rho_{\epsilon}*\Xi)(x))Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)\big)\int_{0}^{\infty} (g(x,u)-1) du\\
- =-\big(F(x, (\rho_{\epsilon}*\Xi)(x))+\gamma(x, (\rho_{\epsilon}*\Xi)(x))Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)\big) h(x)
-\end{multline}
-and furthermore, we apply Fubini theorem to get that 
-\begin{multline}
-  2 \ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x)) \int_{0}^{\infty} u    (g(x,u)-1) du \\
-  =   2 \ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x)) \int_{0}^{\infty} \int_{0}^{u}    dv_1 (g(x,u)-1) du \\
-  =  2 \ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x)) \int_{0}^{\infty}  \int_{v_1}^{\infty}    (g(x,u)-1) du dv_1.
-\end{multline}
-Finally, note also that
-\begin{multline}
-\int 2\bigg(g(x,u)\gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\times \ell \int_u^{
-\infty}(g(x,v_1)-1)dv_1\bigg)du\\
-= 2\ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\int \bigg( g(x,u) \int_u^{
-\infty}(g(x,v_1)-1)dv_1\bigg)du.
-\end{multline}
-\normalsize
-Combining all results we have that
-\small
-\begin{equation}\label{eq: Non-local lookdown generator MMP calculation}
+where $h(x)=\int_{0}^{\infty}(1-g(x,u))du$.
+
+We are now ready to prove Lemma \ref{lem: MMT for limit}.
+
+\begin{proof}[Proof to Lemma \ref{lem: MMT for limit}]
+We write
+$$ Af(\xi)=A_1f(\xi)+A_2f(\xi)+A_3f(\xi),$$
+where the first term is
+\begin{equation}
 \begin{aligned}
-\alpha A^{\text{nl}}_{\epsilon}f(\eta)
-=&~ e^{-\langle h(x),\Xi(dx)\rangle}  \Bigg\{\left\langle \gamma(x, (\rho_{\epsilon}*\Xi)(x))B(h(\cdot) r( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)-h(\cdot)Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x),\Xi(dx) \right\rangle\\
-&+\bigg \langle2\ell\gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\int_{0}^{\infty} u (g(x,u)-1) du \\
- &+ \big(F(x, (\rho_{\epsilon}*\Xi)(x))+\gamma(x, (\rho_{\epsilon}*\Xi)(x))Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)\big) h(x) ,\Xi(dx)\bigg\rangle\\
- & +\left\langle 2 \ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\int g(x,u)\int_u^{
-\infty}(g(x,v_1)-1)dv_1 du,\Xi(dx)\right\rangle \Bigg\}\\
-=&~ e^{-\langle h(x),\Xi(dx)\rangle}  \Bigg\{\left\langle \gamma(x, (\rho_{\epsilon}*\Xi)(x))B(h(\cdot) r( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)+ F(x, (\rho_{\epsilon}*\Xi)(x),\Xi(dx) \right\rangle\\
-&+\bigg \langle 2 \ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x)) \int_{0}^{\infty}  \int_{v_1}^{\infty}    (g(x,u)-1) du dv_1 \\
- & + 2\ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\int_0^{\infty} g(x,u)\int_u^{
-\infty}(g(x,v_1)-1)dv_1 du,\Xi(dx)\bigg\rangle \Bigg\}\\
-=&~ e^{-\langle h(x),\Xi(dx)\rangle}  \Bigg\{\bigg\langle \gamma(x, (\rho_{\epsilon}*\Xi)(x))B(h(\cdot) r( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)+ F(x, (\rho_{\epsilon}*\Xi)(x)\\
-& + \ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))2 \int_0^{\infty} (g(x,u)-1)\int_u^{
-\infty}(g(x,v_1)-1)dv_1 du,\Xi(dx)\bigg\rangle \Bigg\}\\
-=&~ e^{-\langle h(x),\Xi(dx)\rangle} \times \Bigg\{\bigg\langle \gamma(x, (\rho_{\epsilon}*\Xi)(x))B(h(\cdot) r( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)+ F(x, (\rho_{\epsilon}*\Xi)(x)\\
-& + \ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))h(x)^2,\Xi(dx)\bigg\rangle \Bigg\}\\
-:=&~\mathcal{L}^{nl}_{\epsilon}\alpha f(\eta),
+A_1f(\xi) =&
+        f(\lp)  \sum_{(x, u) \in \xi}
+             \frac{
+            	\gamma(x, \Xi)
+                \left(\DG(g(\cdot, u) r(\cdot, \Xi))(x) - g(x,u) \DG r(x,\Xi)\right)
+            }{
+                g(x, u)
+            }\\
+            = & f(\lp)  \sum_{(x, u) \in \xi} \frac{\ell_1(x,u)}{g(x,u)},
 \end{aligned}    
 \end{equation}
-\normalsize
-where $\mathcal{L}^{nl}_{\epsilon}$ is the generator of a non-linear superprocess of the form characterised in Equation \eqref{eq: Empirical Measure Martingale characterisation - product form}.
+the second term is
+\begin{equation}
+\begin{aligned}
+A_2f(\xi)  = &
+  f(\lp) \sum_{(x, u) \in \xi}
+        2 \alpha \gamma(x, \Xi) r(x, \Xi ) \int_u^\infty (g(x, u_1) - 1) du_1\\
+         =&  f(\lp)  \sum_{(x, u) \in \xi} \ell_2(x,u),
+\end{aligned}    
+\end{equation}
+and the final term satisfies
+\begin{equation}
+\begin{aligned}
+A_3f(\xi)  =&f(\lp) \sum_{(x, u) \in \xi}
+                \frac{\left(
+            \alpha \gamma(x, \Xi) r(x, \Xi ) u^2
+            -
+            \left\{
+                \gamma(x, \Xi) \DG r(x, \Xi) + F(x, \Xi)
+            \right\} u
+        \right)
+        \partial_u g(x, u)}{ g(x,u) }\\
+        =& f(\lp) \sum_{(x, u) \in \xi} \frac{\ell_3(x,u)}{g(x,u)}  .
+\end{aligned}    
+\end{equation}
+
+Applying Equation \eqref{eq: cond_poi_sum_prod}
+to the above expressions give 
+\begin{equation}
+\int Af(\xi)\Gamma^{\Xi}(d\xi)
+= \left \langle \int_{0}^{\infty}\left(\ell_1(x,u) + \ell_2(x,u) g(x,u) + \ell_3(x,u)\right)du ,\Xi(dx) \right\rangle \mathcal{E}_{-h}(\Xi)
+\end{equation}
+
+First of all, 
+the operator $\DG$ acts on space while the integral is over levels,
+so we can commute the two operators to obtain
+\begin{equation}
+\begin{aligned}
+\int_{0}^{\infty} \ell_1(x,u) du 
+=& \int_{0}^{\infty} \gamma(x, \Xi)( \DG((g(\cdot, u)-1) r(\cdot, \Xi))(x) - (g(x,u)-1) \DG r(x,\Xi))  du \\
+=& \gamma(x, \Xi)\left\{ \DG\left(\int_{0}^{\infty} (g(\cdot, u)-1)du \times r(\cdot, \Xi)\right)(x) - \int_{0}^{\infty} (g(x,u)-1)du \DG r(x,\Xi)\right\} \\
+=& -\gamma(x, \Xi)\{ \DG(h(\cdot) r(\cdot, \Xi))(x) - h(x) \DG r(x,\Xi)\},
+\end{aligned}
+\end{equation}
+as $h(x,u)= \int_{0}^{\infty} (1 -g(x,u))du$.
+
+Similarly,
+\begin{equation}
+\begin{aligned}
+\int_{0}^{\infty} \ell_2(x,u)g(x,u) du
+=&  \alpha\gamma(x, \Xi) r(x, \Xi ) \times 2 \int_{0}^{\infty} g(x,u)  \int_u^\infty (g(x, u_1) - 1) du_1  du\\
+=&  \alpha\gamma(x, \Xi) r(x, \Xi ) \times I_1.
+\end{aligned}
+\end{equation}
+
+Finally,
+integrating $\ell_3$ by parts, 
+we have
+\begin{equation}
+\begin{aligned}
+\int_{0}^{\infty} \ell_3(x,u)du
+=& \int_{0}^{\infty} \left(
+            \alpha \gamma(x, \Xi) r(x, \Xi ) u^2
+            -
+            \left\{
+                \gamma(x, \Xi) \DG r(x, \Xi) + F(x, \Xi)
+            \right\} u
+        \right)
+        \partial_u g(x, u) du\\
+=& - \alpha\gamma(x, \Xi) r(x, \Xi ) \int_{0}^{\infty} 2u (g(x, u)-1) du\\
+  &+ \left\{\gamma(x, \Xi) \DG r(x, \Xi) + F(x, \Xi) \right\} \int_{0}^{\infty}(g(x,u)-1) du\\
+  =&  - \alpha \gamma(x, \Xi) r(x, \Xi ) I_2 - \left\{\gamma(x, \Xi) \DG r(x, \Xi) + F(x, \Xi) \right\} h(x).
+\end{aligned}
+\end{equation}
+
+Note that $I_1-I_2$ satisfies
+\begin{equation}
+\begin{aligned}
+I_1-I_2 
+=& 2 \int_{0}^{\infty} g(x,u)  \int_u^\infty (g(x, u_1) - 1) du_1  du - 2 \int_{0}^{\infty} u (g(x, u)-1) du\\
+=& 2 \int_{0}^{\infty} g(x,u)  \int_u^\infty (g(x, u_1) - 1) du_1  du - 2 \int_{0}^{\infty} (g(x, u)-1) \int_{0}^{u}dv  du\\
+=& 2 \int_{0}^{\infty} g(x,v)  \int_v^\infty (g(x, u) - 1) du  dv - 2 \int_{0}^{\infty} \int_{v}^{\infty}(g(x, u)-1)  dudv\\
+=& 2 \int_{0}^{\infty} (g(x,v)-1)  \int_v^\infty (g(x, u) - 1) du  dv \\
+=& h^2(x)
+\end{aligned}
+\end{equation}
+
+Combining all the Equations above, 
+we have 
+\begin{equation}
+\begin{aligned}
+& \int_{0}^{\infty}\left(\ell_1(x,u) + \ell_2(x,u) g(x,u) + \ell_3(x,u)\right)du \\
+=& -\gamma(x, \Xi)\DG(h(\cdot) r(\cdot, \Xi))(x) + \gamma(x, \Xi) h(x) \DG r(x,\Xi) -  \gamma(x, \Xi) \DG r(x, \Xi)h(x) - F(x, \Xi)  h(x) \\
+& +\alpha\gamma(x, \Xi) r(x, \Xi )(I_1-I_2)\\
+=&\alpha \gamma(x, \Xi) r(x, \Xi ) h^2(x) -\gamma(x, \Xi)\DG(h(\cdot) r(\cdot, \Xi))(x)  - F(x, \Xi)  h(x).
+\end{aligned}
+\end{equation}
+
+To conclude, 
+\begin{equation}
+\begin{aligned}
+&\int Af(\xi)\Gamma^{\Xi}(d\xi)\\
+= & \left(\alpha \gamma(x, \Xi) r(x, \Xi ) h^2(x) -\gamma(x, \Xi)\DG(h(\cdot) r(\cdot, \Xi))(x)  - F(x, \Xi)  h(x)\right)\mathcal{E}_{-h}(\Xi)\\
+= & \left(\gamma(x, \Xi)\DG(-h(\cdot) r(\cdot, \Xi))(x)  + F(x, \Xi)  (-h(x))\right)\mathcal{E}'(\langle -h, \Xi \rangle )\\
+   &+ \left(\alpha \gamma(x, \Xi) r(x, \Xi ) h^2(x) \right)\mathcal{E}''(\langle -h, \Xi \rangle )\\
+=& \Pgen \mathcal{E}_{-h}(\Xi),
+\end{aligned}
+\end{equation}
+so we have established our equality. 
+\end{proof}
+
+\subsection{Convergence of Lookdown Representation}
+\comment{
+    I did this informal writeup of convergence of the lookdown generator
+    without looking at the previous version
+    mostly to double-check what we have there
+    (which is probably better).
+}
+
+In Definition~\ref{defn:lookdown_mgale} we saw that the generator
+of $(\lp_t)_{t \ge 0}$ is the sum of two parts,
+equations \eqref{eqn:birth_generator} and \eqref{eqn:level_generator}.
+Assume that there is a $u_*$ such that $g(x, u) = 1$ for all $u \ge u_*$.
+We consider these two in turn.
+
+First, the contribution from births is
+\begin{align*}
+\begin{split}
+f(\lp)
+&\mapsto
+    f(\lp)
+    \sum_{(x, u) \in \lp}
+    2 \gamma(x, \eta)
+    \bigg\{
+        \frac{1}{2 N}
+        \int_u^N
+        g(x, u_1) du_1
+        \frac{
+            \theta \int_{\IR^d} (g(y, u) - g(x, u)) r(y, \eta) q(x, dy)
+        }{
+            g(x, u)
+        }
+    \\ & \qquad \qquad \qquad {}
+        + \frac{\theta}{N}
+        \int_u^N \int_{\IR^d}
+        \left( \frac{g(y, u_1) + g(x, u_1)}{2} - 1 \right)
+        r(y, \eta) q(x, dy)
+    \bigg\}
+    .
+    \end{split}
+\end{align*}
+We have that
+\begin{align*}
+    &\theta \int_{\IR^d} (g(y, u) - g(x, u)) r(y, \eta) q(x, dy) \\
+    &\qquad =
+    \theta \int_{\IR^d} (r(y, \eta) g(y, u) - r(x, \eta) g(x, u)) q(x, dy)
+    - \theta \int_{\IR^d} g(x, u) (r(y, \eta) - r(x, \eta)) q(x, dy) \\
+    &\qquad \to
+    \DG(gr)(x) - g(x) \DG r(x) \qquad \text{as }N \to \infty.
+\end{align*}
+i.e., to
+$\DG\left(g(\cdot, u) r(\cdot, \smooth{r}\eta(\cdot))\right)(x)
+- g(\cdot, u) \DG\left(r(\cdot, \smooth{r}\eta(\cdot))\right)(x)$.
+Furthermore, by our assumption on $g$,
+$\int_u^N g(x, u_1) du_1 / N \to 1$ for all $x$ and $u$,
+so the first term here converges to
+\begin{align*}
+    \gamma(x, \eta)
+        \frac{
+            \DG\left( g(\cdot, u) r(\cdot, \smooth{r}\eta(\cdot))\right)(x)
+            -
+            g(\cdot, x) \DG\left( r(\cdot, \smooth{r}\eta(\cdot))\right)(x)
+        }{
+            g(x, u)
+        } .
+\end{align*}
+This corresponds to each particle moving according to the motion induced by
+$g \mapsto \gamma \DG(gr) - g \DG r$.
+\comment{TODO: explain the $r$-tilted $\DG$ motion somewhere earlier, introducing notation for it.}
+As for the second term,
+since $\int g(y, u_1) q(x, dy) \to g(x, u_1)$
+and $\theta/N \to \alpha$,
+it converges to
+\begin{align*}
+    2 \alpha
+    \gamma(x, \eta)
+    r(x, \eta) 
+    \int_u^\infty
+    \left( g(x, u_1) - 1 \right)
+    du_1
+\end{align*}
+This corresponds to births at higher levels at rate $2 \alpha \gamma r$.
+
+The remaining term is \eqref{eqn:level_generator}:
+\begin{align*}
+    f(\lp)
+    \mapsto
+    f(\lp)
+    \sum_{(x, u) \in \lp}
+    \left(
+    \theta
+        N^{-1} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
+        -
+        b(x, \eta)u
+    \right)
+    \frac{\partial_u g(x,u)}{g(x,u)} .
+\end{align*}
+The first part only uses the fact that $\theta/N \to \alpha$,
+while as noted in \eqref{eqn:b_limit}, $b$ converges to $\gamma \DG r + F$,
+so in total this term converges to
+\begin{align*}
+    f(\lp)
+    \mapsto
+    f(\lp)
+    \sum_{(x, u) \in \lp}
+    \left(
+    \alpha
+        \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
+        -
+        \left\{
+            \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta)
+        \right\} u
+    \right)
+    \frac{\partial_u g(x,u)}{g(x,u)} .
+\end{align*}
+In other words, the level of a particle at $x$ evolves according to
+\begin{align*}
+    \dot u
+    =
+    \alpha
+        \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
+        -
+        \left\{
+            \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta)
+        \right\} u .
+\end{align*}
+
+\comment{From Terence: Note that the convergence result above gives the coefficient $\gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy)$ in front of $u^2$.
+As a result, the contribution by death to the quadratic variation of the superprocess is gone in this limit!
+I cannot find a way to resolve the inconsistency between this limiting result and the spatial model.
+Of course, we can take $\alpha=0$, so we are taking a deterministic limit. In this case, we have consistent result. 
+We should discuss this in our next meeting.}
 

### 2023-01-10 forwards-and-backwards.tex
factor of 2
.

@@
         }{
-            p_{\epsilon^2_\gamma}(w-x) .
+            p_{\epsilon^2_\gamma}(x-w) .
         }
         =
-        h(z) e^{k(z)},
+        h(x-w) e^{k(x-w)},
     \end{align*}
@@
             \le
-            \bar f(\sup_{0 \le s \le T} \langle 1, \eta^N_s \rangle)
+            \bar f(\sup_{0 \le s \le T} \langle 1, \eta^N_s \rangle  / (2 \pi \sigma^2)^{d/2} )
             \sup_{0 \le s \le T} \langle 1, \eta^N_s \rangle .
@@
     &
-    [M^{N}(f)]_{\tau + t} 
+    \big| [M^{N}(f)]_{\tau + t} 
         - [M^{N}(f)]_\tau \big|
@@
         \eta^N_s(dx)
-    ds .
+    ds 
     \\ & \qquad =
@@
 an argument similar to 
-that for \eqref{eqn:eta_projections_goal1}.
+that for \eqref{eqn:eta_projections_goal1}
 also obtains \eqref{eqn:eta_projections_goal2}.
@@
         &=
-        2 \frac{\theta}{N} \int_0^t
+        4 \frac{\theta}{N} \int_0^t
         \left \langle
@@
         +
-        2 \int_0^t
+        4 \int_0^t
         \left \langle

### 2023-01-10 forwards-and-backwards.tex
note about non-error
terence changes to appendix

@@
     \begin{align*}
+        % note that the f' term does not depend on x, just y,
+        % so can come out of the integral
         \|f'\|_\infty

### 2023-01-10 forwards-and-backwards.tex
.

@@
 For each point begin a line of descent
-with label $i$, location $X_i(0) = x_i$, level $U_a(0) = u_i$, and birth time $\tau_i = 0$.
+with label $i$, location $X_i(0) = x_i$, level $U_i(0) = u_i$, and birth time $\tau_i = 0$.
 Suppose that the spatial locations and level of each line of descent $a$
@@
     + \int_{\tau_a}^{t}
-        \beta(X_a(s), \eta(s)) ds
+        \beta(X_a(s), \eta_s) ds
     + \int_{\tau_a}^{t}
@@
     \bigg(
-        \alpha \gamma(X_a(s),\eta(s))
-        r(X_a(s), \eta(s)) U_a(s)^2
+        \alpha \gamma(X_a(s),\eta_s)
+        r(X_a(s), \eta_s) U_a(s)^2
 \\ &\qquad \qquad \qquad {}   
@@
         \left\{
-            \gamma(X_a(s),\eta(s)) \DG r(X_a(s),\eta(s))
-            + F(X_a(s), \eta(s))
+            \gamma(X_a(s),\eta_s) \DG r(X_a(s),\eta_s)
+            + F(X_a(s), \eta_s)
         \right\}
@@
     U_{a \concat j}(t) = U_a(t)
-    + \frac{v}{ 2 \alpha \gamma(X_a(t), \eta_t) r(X_a(t), \eta_t) } .
+    + \frac{v}{ 2 \alpha \gamma(X_a(t), \eta_t) r(X_a(t), \eta_t) } ,
 $$
+if this is finite.
 For any solution to the equations above, the processes defined by
@@
 (More precisely, they are produced but ``at infinity'',
-since the spatial motion of the line of descent is the result of production of these lineages.
+since the spatial motion of the line of descent is the result of production of these lineages.)
 

### 2023-01-13 forwards-and-backwards.tex
.
Update on Overleaf.

@@
     u^2
-    - b(x, \eta) ,
+    - b(x, \eta)
+    u,
     $$
@@
 $$
-    \sup_{\theta}\mathbb{E}\left[ \sup_{x, \eta}b_\theta(x, \eta) \right]
+    \sup_{\theta}\mathbb{E}\left[ \sup_{x, \eta} b_\theta(x, \eta) \right]
     :=
@@
 \subsection{Tightness of the Lookdown Representation}
-
-\comment{
-    This comes later because it uses convergence of the population process itself.
-}
-
-We have now proved tightness of the spatial and level process for a line of descent.
-To prove that the lookdown representation is tight, we generalise the vague topology to the setting of measure-valued processes.
-For a detailed description of the vague topology, refer to Appendix \ref{sec: Empirical Measure Topology}.
-
-We will lay out the steps we follow to prove tightness.
-First of all, we will show that compact containment condition is satisfied if we can control the total mass of particles in our system living in a finite region in space with a level lower than some $u_{*}$.
-Since a control on total mass has already been shown in Lemma \ref{lem:eta_compact_containment}, we have immediately established compact containment condition for our lookdown processes.
-
-Then, we apply Theorem A.24 in \cite{kallenberg1997foundations}
-(Theorem \ref{teo: Vague Relative Compactness through Projection})
-and use a corollary of Stone-Weierstrass Theorem
-(Lemma \ref{lem: Dense set for test functions on empirical measures})
-to show that our lookdown representation $\{\xi^N_t: N \in \mathbb{N}\}$ is tight
-as a $\mathcal{M}(\mathbb{R^d} \times [0, \infty])$-valued stochastic process
-in the vague topology
-as long as $\{F_g(\xi^N_t): N \in \mathbb{N}\}$ is tight
-as real-valued stochastic processes for a huge class of $F_g$. 
-Explicitly, $F_g(\xi):= \prod_{(x_i,u_i)\in \xi}g(x_i,u_i)$,
-where $g(x,u)$ satisfies the property that
-$g(x,u) = 1 $
-for all $u \geq u_{*}$ for some $u_{*}>0$.
-
-\subsubsection{Compact Containment Condition}
-\begin{definition}
-For any arbitrary $M,K>0$, 
-we denote the set 
-$$\mathcal{M}_{K,M}:= \{\mu \in \mathcal{M}(\mathbb{R^d} \times [0, \infty]): \mu([-M,M]^d \times [0,M])/M \leq K\}$$
-to be the set of measures on $\IR^d \times[0,\infty)$ with mass smaller than $K$ in the region $[-M,M]^d \times [0,M]$.
-\end{definition}
-
-In Corollary \ref{cor: Vague Compact sets}, we will prove that $\mathcal{M}_{K,M}$ is vaguely compact.
-
-\begin{lemma}[Compact Containment]
-    \label{lem:lp_compact_containment}
-Assume that $\xi^{N}_0 \to \xi_0$ weakly,
-then for all $T>0$, there exists some constant $C(T)$,
-such that
-    \begin{align}
-        \label{eqn:lp_mass_bound}
-        \IE\left[
-            \sup_{0 \le t \le T}
-            \frac{1}{N}\langle 1, \xi^{N}_t \rangle
-        \right]
-        \le C(T) ,
-    \end{align}
-uniformly in $N$.
-In particular, for any $\epsilon > 0$, there exists some $M_{\epsilon}>0, K_{\epsilon}>0$,
-such that 
-\begin{equation}
-\limsup_{N \to \infty}
-    \mathbb{P}\left\{ \xi^{N}_t \in \mathcal{M}_{K_{\epsilon},M_{\epsilon}}
-        \text{ for } t\in [0,T] \right\}
-        < \epsilon.
+\begin{lemma}
+The lookdown representation satisfies
+Equation \eqref{eq: vague compact containment condition}, i.e.
+for all $\epsilon>0$, there exists $N>0$ such that
+\begin{equation}
+ \limsup_{n \to \infty} \mathbb{P}\left\{ \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle > N \right\} < \epsilon,
 \end{equation}
 \end{lemma}
+
 \begin{proof}
-By an application of Markov Mapping Theorem (see \S \ref{sec: Markov Mapping Theorem Application - Prelimit}), we know that
-
-$$\left(\frac{1}{N}\langle 1, \xi^{N}_t(\cdot , [0, N]) \rangle\right)_{t \geq 0} \sim (\eta^N_t(\cdot ))_{t \geq 0},$$
-i.e. the spatial projection of $(\xi^{N}_t)_{t \geq 0}$ has the same distribution as $(\eta^N_t)_{t \geq 0}$ defined in Definition \ref{defn:mgale_construction}. 
-As a result, by Lemma \ref{lem:lp_compact_containment},
-we have immediately that 
-\begin{align}
-        \IE\left[
-            \sup_{0 \le t \le T}
-            \frac{1}{N}\langle 1, \xi^{N}_t \rangle
-        \right]
-        = \IE\left[
-            \sup_{0 \le t \le T}
-            \langle 1, \eta^{N}_t \rangle
-        \right]
-        \le C(T) ,
-    \end{align}
-for some $C(T)>0$.
-
-Moreover, we know that conditional on the spatial configuration 
-$\frac{1}{N}\langle 1, \xi^{N}_t(\cdot , [0, N]) \rangle,$
-the levels of each individual
-is i.i.d uniformly distributed between $[0,N]$. 
-Therefore, for $N>M_{\varepsilon}$
-\begin{align*}
-     \mathbb{P}\left\{ \xi^{N}_t \in \mathcal{M}_{K_{\epsilon},M_{\epsilon}}
-        \text{ for } t\in [0,T] \right\}
-        =& \mathbb{P}\left\{\sup_{ t\in [0,T]} \frac{1}{M_\varepsilon} \xi^{N}_t([-M_\varepsilon,M_\varepsilon]^d \times [0,M_\varepsilon]) \leq K_\varepsilon
-         \right\}\\
-         \leq& \frac{1}{M_\varepsilon K_{\varepsilon}} \mathbb{E}\left\{\sup_{ t\in [0,T]}  \xi^{N}_t([-M_\varepsilon,M_\varepsilon]^d \times [0,M_\varepsilon]) \right\}\\
-        =& \frac{1}{M_\varepsilon K_{\varepsilon}}             \mathbb{E}_{\eta^N_t}\left\{ N \times
-            \mathbb{E}\left[  
-                \sup_{ t\in [0,T]}  \frac{1}{N}\xi^{N}_t([-M_\varepsilon,M_\varepsilon]^d \times [0,M_\varepsilon])
-                \bigg| \eta^N_t
-                        \right]
-                    \right\}\\
-        =& \frac{1}{M_\varepsilon K_{\varepsilon}} \mathbb{E}_{\eta^N_t}
-                    \left\{ N \times
-                    \sup_{ t\in [0,T]} \eta^{N}_t([-M_\varepsilon,M_\varepsilon]^d) \times \frac{M_{\varepsilon}}{N}
-                    \right\}\\
-        =& \frac{1}{K_{\varepsilon}} \mathbb{E}_{\eta^N_t}
-                    \left\{
-                    \sup_{ t\in [0,T]} \eta^{N}_t([-M_\varepsilon,M_\varepsilon]^d) 
-                    \right\}\\
-        \leq & \frac{1}{K_{\varepsilon}} \mathbb{E}_{\eta^N_t}
-                    \left\{
-                    \sup_{ t\in [0,T]} \langle 1, \eta^{N}_t \rangle 
-                    \right\}\\
-        < & \varepsilon.
-\end{align*}
-The first inequality holds by Markov's inequality, and the following two equalities hold as 
-conditional on $\eta^N_t$,
-$M_{\varepsilon}/N$ proportion of particles in $\xi^N_t$ have levels in $[0,M_{\varepsilon}]$. The final inequality holds as a direct consequence of \ref{lem:eta_compact_containment}.
-
-We have therefore proved compact containment condition in the vague topology for our lookdown representation.
+For every $f \in C^{+}_{c}(\overline{\mathbb{R}^d} \times [0,\infty))$,
+there exists $u^* > 0$ such that $f(x,u) = 0$ for all $u \geq u^*$.
+Then,
+\begin{equation}
+\begin{aligned}
+ &\limsup_{n \to \infty} \mathbb{P}\left\{ \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle > N \right\} \\
+ \leq & \limsup_{n \to \infty}\frac{\mathbb{E}\left\{ \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle \right\}}{N}\\
+ \leq & \limsup_{n \to \infty}||f||_{\infty}\frac{\mathbb{E}\left\{ \sup_{t\in [0,T]}\langle 1_{[0,u^*]}, \xi^n_t \rangle \right\}}{N}.
+\end{aligned}
+\end{equation}
+Recall that conditional on 
+$$ \frac{1}{n}\langle 1_{[0,n]}, \xi^n_t \rangle = \eta^n_t,$$
+the level of each individual is independently and uniformly distributed between $[0,n]$.
+Therefore, 
+\begin{equation}
+\mathbb{E}\left\{ \sup_{t\in [0,T]}\langle 1_{[0,u^*]}, \xi^n_t \rangle \right\} = u^* \mathbb{E}\left\{ \sup_{t\in [0,T]}\langle 1, \eta^n_t \rangle \right\}.
+\end{equation}
+Finally, 
+recall that the supremum of the empirical measure process is controlled in Lemma \ref{lem:eta_compact_containment}
+so there exists some constant $C_T$ such that 
+\begin{equation}
+\begin{aligned}
+ &\limsup_{n \to \infty} \mathbb{P}\left\{ \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle > N \right\} \\
+ \leq & \limsup_{n \to \infty}||f||_{\infty}\frac{u^*}{N}\mathbb{E}\left\{ \sup_{t\in [0,T]}\langle 1, \eta^n_t \rangle \right\}\\
+ \leq & ||f||_{\infty}\frac{u^*}{N}C_T\\
+ < & \epsilon
+\end{aligned}
+\end{equation}
+for sufficiently large $N$.
 \end{proof}
+
+It now suffices for us to show that the processes $\{(F_g(\xi^n_t))_{t \geq 0}: n \geq 1\}$ is relatively compact for all test functions $F_g$.
+To do so, we apply Aldous criterion for real-valued processes.
+
 \subsubsection{Tightness of $(F_g(\xi_t))_{t \geq 0}$}
@@
 \begin{proof}
-
+Once again, we intend to apply the Aldous Criterion. 
+To do so, we need to prove that for all $\epsilon > 0$,
+there exists $n_0 > 0$ and $\delta > 0$ such that 
+\begin{equation}
+\sup_{n \geq n_0}\sup_{\theta \in [0, \delta]}\mathbb{P}\{|F_g(\xi^n_{\tau+\theta})-F_g(\xi^n_{\tau})| > \epsilon\} < \epsilon
+\end{equation} 
+holds. 
+It suffices to show that for sufficiently small $\delta > 0$,
+$\limsup_{n \to \infty}\mathbb{E}[|F_g(\xi^n_{\tau_n + s})-F_g(\xi^n_{\tau_n})|^2] < \epsilon$
+for all $\theta \in [0, \delta]$.
+
+First, note that only events happening on particles with levels smaller than $u_g$ at time $\tau_n$ will contribute to the difference $|F_g(\xi^n_{\tau_n + s})-F_g(\xi^n_{\tau_n})|$.
+
+To calculate this difference, we couple $(\xi^n_{\tau_n + s})_{s \in [0,\delta]}$ with the process $(\hat{\xi}^n_{\tau_n + s})_{s \in [0,\delta]}$ which has the same level dynamics as $(\xi^n_{\tau_n + s})_{s \in [0,\delta]}$ but with no birth.
+With this coupling, 
+we have 
+$\mathbb{E}[|F_g(\xi^n_{\tau_n + s})-F_g(\xi^n_{\tau_n})|^2] \leq 2\mathbb{E}[|F_g(\xi^n_{\tau_n + s})-F_g(\hat{\xi}^n_{\tau_n + s})|^2]+ 2\mathbb{E}[|F_g(\hat{\xi}^n_{\tau_n + s})-F_g(\xi^n_{\tau_n})|^2]$
+
+We first try to control $\mathbb{E}[|F_g(\hat{\xi}^n_{\tau_n + s})-F_g(\xi^n_{\tau_n})|^2]$. 
+This difference is simply influenced by the level dynamics. Therefore,
+\begin{equation}
+\begin{aligned}
+ &\mathbb{E}[|F_g(\hat{\xi}^n_{\tau_n + s})-F_g(\xi^n_{\tau_n})|^2]\\
+ \leq &
+ \mathbb{E}\left[ \int_{0}^{\delta} \sum_{(x,u)\in\xi^n_{\tau_n+s}}\,
+    \left|
+        \frac{\theta}{n} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q_\theta(x, dy) u^2 -b_{\theta}(x,\eta)u
+    \right|^2 \partial_u g(x,u)^2 ds\right]\\
+ \leq & ||g'||_{\infty}
+ \mathbb{E}\left[ \int_{0}^{\delta} \sum_{(x,u)\in\xi^n_{\tau_n+s}}\,
+    \left| \frac{\theta}{n}  \gamma(x,\eta)  u_g^2 + (2  \gamma(x,\eta) + F(x,\eta))u_g
+    \right|^2  ds\right] + O(1/\theta)\\
+\leq & ||g'||_{\infty}u_g
+ \mathbb{E}_{\eta}\left[ \int_{\tau_n}^{\tau_n+\delta} \int_{\mathbb{R}^d}
+    \left| \frac{\theta}{n}  \gamma(x,\eta^n_{s})  u_g^2 + (2  \gamma(x,\eta^n_{s}) + F(x,\eta^n_{s}))u_g
+    \right|^2 \eta^N_s(dx) ds\right] + O(1/\theta),
+\end{aligned}
+\end{equation}
+so this term can be controlled with Lemma \ref{lem:tightness_for_F}.
+
+We now control 
+$\mathbb{E}[|F_g(\xi^n_{\tau_n + s})-F_g(\hat{\xi}^n_{\tau_n + s})|^2]$.
+Note that this difference is purely contributed by the number of birth with both the parent and child having levels below $u_g$,
+and the simple inequality 
+$\mathbb{E}[|F_g(\xi^n_{\tau_n + s})-F_g(\hat{\xi}^n_{\tau_n + s})|^2] \leq 4 \mathbb{P}\{|F_g(\xi^n_{\tau_n + s})-F_g(\hat{\xi}^n_{\tau_n + s})|>0\}$
+holds.
+
+Therefore it suffices to prove that within a small interval of length $\delta > 0$,
+the probability of such birth events happening is small.
+
+This term can be controlled by the uniform boundedness of $\gamma(x,m)$.
+For the birth event to contribute to the difference, the parent must have a level below $u_g$, and give birth to a child at level $u + \ell < u_g$.
+Therefore, the total rate of relevant birth events satisfies
+\begin{equation}
+\sum_{(x,u) \in \xi^n_{\tau_n}([0,u_g] \times \overline{\mathbb{R}^d})}  \gamma(x,\eta^n_{\tau_n}) \mathbbm{1}_{u+ \ell < u_g }
+\leq C_{\gamma} \xi^n_{\tau_n}([0,u_g] \times \overline{\mathbb{R}^d}.
+\end{equation}
+Therefore, with an application of Markov inequality, 
+we have
+\begin{equation}
+\begin{aligned}
+\mathbb{P}\{|F_g(\xi^n_{\tau_n + s})-F_g(\hat{\xi}^n_{\tau_n + s})|>0\}
+\leq & \mathbb{P}[Poi(C_{\gamma} \xi^n_{\tau_n}([0,u_g] \times \overline{\mathbb{R}^d})s) \geq  1]\\
+\leq & \mathbb{E}[Poi(C_{\gamma} \xi^n_{\tau_n}([0,u_g] \times \overline{\mathbb{R}^d})s)]\\
+\leq & \mathbb{E}[Poi(C_{\gamma} \xi^n_{\tau_n}([0,u_g] \times \overline{\mathbb{R}^d})s)]\\
+\leq & C_{\gamma}  \mathbb{E}[\xi^n_{\tau_n}([0,u_g] \times \overline{\mathbb{R}^d})]s\\
+\leq & C_{\gamma}  u_g\mathbb{E}[\eta^n_{\tau_n}(\overline{\mathbb{R}^d})]s\\
+<&  \epsilon.
+\end{aligned}
+\end{equation}
+
+Combining all inequalities above, we have established Aldous Criterion and thus, tightness for the lookdown representation. 
 \end{proof}
@@
 \label{sec: Topologies on Lookdown}
-
-\subsection{Euclidean-Vague Topology on $\IR^d \times [0,\infty]$}\label{sec: Convergence in Product Topology}
-We first define a topology on $\IR^d \times [0,\infty]$ which is Euclidean on $\IR^d$ and vague in $[0,\infty]$.
-\begin{definition}
-We define the topology $\mathfrak{p}$ on $\IR^d \times [0,\infty]:$
-we say $(x_n,u_n) \to (x,u)$ in topology $\mathfrak{p}$ if 
-\begin{enumerate}
-    \item $|x_n-x| \to 0$ in $\IR^d$.
-    \item  For all $g \in C_{c}([0,\infty])$, the space of continuous functions with compact support on $[0,\infty]$, $g(u_n) \to g(u).$ Since this is the vague convergence for $(\delta_{u_n})_{n \in \mathbb{N}}$ we will abuse a bit the notation and denote this by the symbol $u_n \xrightarrow{vague} u$.
-\end{enumerate}
-\end{definition}
-
-In other words, our topology is Euclidean in space $\IR^d$ and vague in levels in $[0,\infty]$.
-\begin{lemma}\label{Vague times Euclidean is Polish}
-The space $\IR^d \times [0,\infty]$ under topology $\mathfrak{p}$ is Polish.
-\end{lemma}
-\begin{proof}
-The space $C_c([0,\infty])$ is dense, so we pick a countable dense subset $S:=\{h_n: n \in \mathbb{N}\} \subset C^{1}_c([0,\infty])$ and define the metric $\mathfrak{d}$ such that $\mathfrak{d}(u,v)=\sum_{n=1}^{\infty}\frac{1 \wedge |h_n(u)-h_n(v)|}{2^n}$.
-
-Assume that $u_n \xrightarrow{vague} u$.
-Pick arbitrary $\delta>0$ and take $N$ large enough such that $\frac{1}{2^N}<\delta/2$.
-Furthermore, pick $n$ large enough such that $\inf_{i=1,2,...,N}|h_i(u_n)-h_i(u)|<\delta/2$.
-From this we immediately have that $\mathfrak{d}(u_n,u)<\delta$.
-Thus $\mathfrak{d}(u_n,u) \to 0$.
-
-Conversely assume that $\mathfrak{d}(u_n,u) \to 0$.
-For any $h \in \mathcal{C}^{1}_c([0,\infty])$ and for any $\delta>0$, pick $g_N$ such that $||h-h_N||_{\infty}<\delta /3$ and $n$ large enough such that $\mathfrak{d}(u_n,u)< \frac{\delta}{3 \times 2^N}$.
-Then $|h(u)-h(u_n)|< |h(u)-h_N(u)|+|h_N(u)-h_N(u_n)|+|h_N(u_n)-h(u_n)|<\delta$, and so $h(u_n) \to h(u)$.
-
-Finally, one can easily check that $\mathbb{Q}$ is a countable dense set in $[0,\infty]$ equipped with the metric $\mathfrak{d}$.
-Defining the metric $d_{\mathfrak{p}}$
-by
-$$d_{\mathfrak{p}}((x_1,u_1),(x_2,u_2))=||x_1-x_2||+\mathfrak{d}(u_1,u_2),$$
-we can show easily that
-convergence in $d_{\mathfrak{p}}$
-is equivalent to convergence in 
-$\mathfrak{p}$ topology.
-\end{proof}
-
-\subsection{Vague Topology on Measures}\label{sec: Empirical Measure Topology}
-
-We now characterise the lookdown representation
-of our particle system
-as a measure on 
-$(\IR^d \times [0, \infty], \mathfrak{p})$.
-We endow the vague topology
-on these measures for
-convergence of lookdown representations.
-We refer to Theorem A.23 and Theorem A.24 in \cite{kallenberg1997foundations}.
-
-First of all,
-as $(\IR^d \times [0, \infty], \mathfrak{p})$
-is Polish,
-the family of $C^{+}_K$ of continuous functions
-$$f: \mathbb{R^d} \times [0, \infty] \to \IR^{+}$$
-with compact support
-is separable in the uniform metric. 
-The sets $K_n =[-n, n]^d \times [0,n]$ clearly forms a sequence of compact sets and $K_n \uparrow \mathbb{R^d} \times [0, \infty]$.
-
-We denote $\mathcal{M}(\mathbb{R^d} \times [0, \infty])$ as the class of measures on $\mathbb{R^d} \times [0, \infty]$ that are 
-locally finite (i.e. bounded on bounded intervals),
-and write $\pi_B, \pi_f$ 
-for the mappings 
-$\mu \to \mu B$, $\mu \to \mu f := \int f d\mu$,
-respectively,
-on $\mathcal{M}(\mathbb{R^d} \times [0, \infty])$.
-
-The \textit{vague topology} in $\mathcal{M}(\mathbb{R^d} \times [0, \infty)$ is generated by the maps $\pi_f, f \in C^{+}_K$, and 
-we write the cague convergence of $\mu_n$ toward $\mu$
-as $\mu_n \xrightarrow{v} \mu$.
-
-Taking $S= \mathbb{R^d} \times [0, \infty]$
-in Theorem A.23
-in \cite{kallenberg1997foundations},
+\subsection{Topology for convergence of lookdown representations}
+
+Recall that
+the lookdown representation has a spatial component and a level component.
+Specifically, for fixed $N>0$ and $t>0$,
+the lookdown representation $\xi^N(t)$ 
+is a finite measure on $\overline{\mathbb{R}^d} \times [0,N]$.
+
+To characterise convergence of $\xi^N(t)$ as $N \to \infty$,
+we therefore need to impose an appropriate topology on $\mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty))$,
+the space of finite measures on $\overline{\mathbb{R}^d} \times [0,\infty)$.
+
+We now refer to the vague topology introduced in P564, \S A2 in \cite{kallenberg1997foundations}.
+Let $S$ be a locally compact Polish space and $\hat{S}$ be the class of bounded sets in $S$.
+We consider the family $C^{+}_c(S)$ of positive continuous functions with compact support. It is known that $C^{+}_c$ is separable in the uniform metric.
+We now consider $\mathcal{M}(S)$, the class of measures on $S$ that are locally finite.
+The \textit{vague topology} on $\mathcal{M}(S)$ is generated by the the maps $\mu \to \mu f := \int f d \mu$, where $f\in C^{+}_{c}(S)$.
+In other words, convergence of $\mu^n \to \mu$ in the vague topology holds if 
+$$\int f d\mu^n \to \int f d\mu$$
+for all $f\in C^{+}_{c}(S)$.
+
+We now introduce two important theorems on compactness and convergence in the vague topology.
+\begin{theorem}[Theorem A.23 in \cite{kallenberg1997foundations}]
+For any locally compact, second-countable Hausdorff Space $S$, 
 we have
-\begin{theorem}[vague topology]
-\label{teo: Kallenberg vague results}
-
-The following holds:
-\begin{enumerate}
-    \item $\mathcal{M}(\mathbb{R^d} \times [0, \infty])$ is a Polish space in the vague topology
-    \item A set $A \subset \mathcal{M}(\mathbb{R^d} \times [0, \infty])$ is vaguely relatively compact iff 
-    $\sup_{\mu \in A} \mu f < \infty$ for all $f \in C^{+}_K$
-    \item if $\mu_n \xrightarrow{v} \mu$ and a set $B$ is finite with $\mu \partial B = 0$, then $\mu_n B \to \mu B$.
-\end{enumerate}
-
+\begin{itemize}
+\item $\mathcal{S}$ is Polish in the vague topology,
+\item a set $A\subset \mathcal{S}$ is vaguely relatively compact iff $\sup_{\mu\in A} \mu f < \infty$ for all $f \in C^{+}_{c}$
+\item if $\mu_n \to \mu$ in the vague topology and $B \in \hat{S}$ with $\mu \partial B = 0$, then $\mu_n B \to \mu B$
+\end{itemize}
 \end{theorem}
 
+The following corollary holds immediately.
 \begin{corollary}
-\label{cor: Vague Compact sets}
-For any arbitrary $M,K>0$, the set 
-$$\mathcal{M}_{K,M}:= \{\mu \in \mathcal{M}(\mathbb{R^d} \times [0, \infty]): M^{-1}\mu([-M,M]^d \times [0,M]) \leq K\}$$   
-is a compact subset in 
-$\mathcal{M}(\mathbb{R^d} \times [0, \infty])$ 
-under the vague topology.
+The set $\Gamma_K := \{\mu \in \mathcal{M}(S): \mu(S) \leq K\}$
+is vaguely compact in $\mathcal{M}(S)$.
 \end{corollary}
 \begin{proof}
-For any function $f \in C^{+}_K$, it is compactly supported and
-so there exists a constant $C_f > ||f||_{\infty}$.
-As a result, 
-$$\sup_{\mu \in \mathcal{M}_{K,M}} \mu f < C_f \times \mu \{ supp(f) \cap [-M,M]^d \times [0,M]\} \leq C_f M^{-1} K < \infty.$$
-
-Since $f$ is arbitrary, by (ii) of Theorem \ref{teo: Kallenberg vague results}, 
-the set
-$\mathcal{M}_{K,M}$
-is vaguely relatively compact.
-
-We now prove that $\mathcal{M}_{K,M}$ is a closed subset of $\mathcal{M}(\mathbb{R^d} \times [0, \infty])$.
-
-Since $[-M,M]^d \times [0,M]$ is finite, by part 3 of Theorem \ref{teo: Kallenberg vague results},
-for any sequence in $(\mu_n)_{n \in \mathbb{N}}$ in  $\mathcal{M}_{K,M}$ that converges vaguely to $\mu$ in 
-$ \mathcal{M}(\mathbb{R^d} \times [0, \infty])$, 
-$$MK \geq \mu_n([-M,M]^d \times [0,M]) \to \mu([-M,M]^d \times [0,M]).$$
-Therefore, $\mu \in \mathcal{M}_{K,M}$.
-As a result, $\mathcal{M}_{K,M}$ is closed and relatively vaguely compact, so it is vaguely compact.
+It suffices to show that $\Gamma_K$ is vaguely relatively compact and vaguely closed.
+For any fixed $f \in C^{+}_c$,
+we have that $ \sup_{\mu \in A} \mu f \leq  ||f||_{\infty} \mu(S)  \leq ||f|| K < \infty$,
+so $\Gamma_K$ is vaguely relatively compact.
+
+Now it suffices to prove that $\Gamma_K$ is closed under the vague topology.
+Consider a vaguely converging sequence $(\mu_n)_{n \geq 1}$ in $\Gamma_K$
+satisfying $\mu_n \to \mu \in \mathcal{M}(S)$,
+then for an increasing sequence of functions $f_m \to 1$,
+by the Dominating Convergence Theorem, 
+\begin{equation}
+\mu(S)
+= \lim_{m \to \infty} \mu f_m
+= \lim_{m \to \infty} \lim_{n \to \infty} \mu_n f_m
+= \lim_{n \to \infty}   \mu_n (S)
+\leq K,
+\end{equation}
+and so $\mu \in \Gamma_K$.
+Therefore $\Gamma_K$ is vaguely compact. 
 \end{proof}
 
-\begin{theorem}
-    \label{teo: Vague Relative Compactness through Projection}
-For any Polish space $S$, let $f_1,f_2,...,$ be a dense collection of functions in $C^{+}_{K}$ that is closed under addition, then a set $A \in \mathcal{D}_{\mathcal{M}(S)}([0,\infty))$ is relative compact if and only if $Af_j = \{xf_j: x \in A\}$ is relatively compact on $\mathcal{D}_{[0, \infty)}([0,\infty))$ for every $j \in \mathbb{N}$.
+We now include another theorem that is very relevant to establishing tightness of $\mathcal{M}(S)$-valued processes in the Skorokhod topology.
+
+\begin{theorem}[Theorem A2.4 in \cite{kallenberg1997foundations}]\label{teo: vag_sko_conv}
+Let $f_1,f_2,...$ be a dense collection in $C^{+}_{c}(S)$ closed under addition, 	
+then any set $A \subset \mathcal{D}_{\mathcal{M}(S)}([0,\infty))$
+is relatively compact if and only if for every $j \in \mathbb{N}$,
+$Af_j = \{xf_j, x \in A\}$
+is relatively compact in $\mathcal{D}_{\mathbb{R}^{+}}([0,\infty))$.
 \end{theorem}
+
+To characterise convergence of lookdown representations,
+we take $S = \overline{\mathbb{R}^d} \times [0,\infty)$
+and consider the test functions of the form 
+\begin{equation}
+F_g(\xi) = \prod_{(x,u) \in \xi} g(x,u),
+\end{equation}
+where $g(x,u)$ is differentiable in $u$, smooth in $x$.
+and satisfies the property that $0\leq g(x,u) \leq 1$,
+and that there exists $u^*$ such that for all $u > u^*$,
+$g(x, u) =1$.
+
+In fact, there is a one-to-one correspondence between $C^{+}_c(S)$
+and test functions of the form $F_g$.
+For all $f \in C^{+}_c(S)$,
+if we write $g = e^{-f}$,
+then
+\begin{equation}
+F_g(\xi)= e^{-\langle f, \xi \rangle}.
+\end{equation}
+
+Furthermore,
+we know that for any $x_1, x_2 \in [0,N]$,
+$$|x_1-x_2|\geq |e^{-x_1}-e^{-x_2}| \geq e^{-N}|x_1-x_2|,$$
+so we can control $\langle f, \xi^n_t \rangle $ by controlling $F_g(\xi^n_t)$ as long as 
+there exists some $N > 0$ such that $\langle f, \xi^n_t \rangle < N$.
+
+Combining the above observation and Theorem \ref{teo: vag_sko_conv},
+we have the following lemma.
+
+\begin{lemma}
+We consider a sequence $(\xi^n_t)_{t\geq 0}$ of $\mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty))$-valued cadlag processes.
+Assume that for all test functions of the form $F_g$,
+the sequence $\{(F_g(\xi^n_t))_{t \geq}: n=1,2,...\}$ of real-valued cadlag processes are relatively compact.
+
+Furthermore, assume that for any $f \in C^{+}_{c}(\overline{\mathbb{R}^d} \times [0,\infty))$ and $\epsilon > 0$, there exists $N>0$ (dependent on $f$ and $\epsilon$), 
+such that 
+\begin{equation}
+\label{eq: vague compact containment condition}
+ \limsup_{n \to \infty} \mathbb{P}\left\{ \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle > N \right\} < \epsilon,
+\end{equation}
+
+ then $(\xi^n_t)_{t\geq 0}$ is relatively compact in $\mathcal{D}_{\overline{\mathbb{R}^d} \times[0,\infty)}([0,T])$.
+\end{lemma}
+
 \begin{proof}
-See \cite{kallenberg1997foundations} Theorem A2.4.
+By Theorem \ref{teo: vag_sko_conv},
+it suffices to prove that for all $f \in C^{+}_{c}(\overline{\mathbb{R}^d} \times [0,\infty))$,
+$\{(f(\xi^n_t))_{t \geq 0}: n=1,2,.. \}$ is relatively compact.
+
+We now make use of the Aldous Criterion of tightness on the real-valued sequences
+$\{(f(\xi^n_t))_{t \geq 0}: n=1,2,.. \}$. It suffices to show that
+for fixed sequences of stopping time $\tau_n$ bounded above by $T$,
+for each $\varepsilon>0$,
+there exists $\delta > 0$ and $n_0$ such that
+\begin{equation}
+\sup_{n \geq n_0}\sup_{\theta \in [0, \delta]} \mathbb{P}\left[|\langle f, \xi^n_{\tau_n+\theta}\rangle - \langle f, \xi^n_{\tau_n}\rangle | > \varepsilon \right] \leq \varepsilon.
+\end{equation}
+
+First we pick $N,M>0$ such that 
+ $$\sup_{n \geq M} \mathbb{P}\left\{ \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle > N \right\} < \epsilon /2 .$$
+Then, we can partition the event $\{|\langle f, \xi^n_{\tau_n+\theta}\rangle - \langle f, \xi^n_{\tau_n}\rangle | > \varepsilon\}$ into two subsets according to the event 
+$ \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle > N$.
+
+For all $n>M$,
+\begin{equation}
+\begin{aligned}
+ &\mathbb{P}\left[|\langle f, \xi^n_{\tau_n+\theta}\rangle - \langle f, \xi^n_{\tau_n}\rangle | > \varepsilon \right]\\
+ =& \mathbb{P}\left[|\langle f, \xi^n_{\tau_n+\theta}\rangle - \langle f, \xi^n_{\tau_n}\rangle | > \varepsilon ,  \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle > N \right]\\
+ & + \mathbb{P}\left[|\langle f, \xi^n_{\tau_n+\theta}\rangle - \langle f, \xi^n_{\tau_n}\rangle | > \varepsilon,  \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle \leq N \right]\\
+< & \varepsilon/2 + \mathbb{P}\left[|e^{-\langle f, \xi^n_{\tau_n+\theta}\rangle} - e^{-\langle f, \xi^n_{\tau_n}\rangle }| > e^{-N}\varepsilon,  \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle \leq N \right]\\
+< & \varepsilon/2 + \mathbb{P}\left[|F_g(\xi^n_{\tau_n+\theta})-F_g(\xi^n_{\tau_n})| > e^{-N}\varepsilon\right].
+\end{aligned}
+\end{equation}
+
+Finally, by tightness of the processes $\{F_g(\xi^n_t): n = 1,2,...\}$, 
+we can pick large enough $n_0 > M$ and $\delta > 0$
+such that 
+$$\sup_{n \geq n_0}\sup_{\theta \in [0,\delta]}\mathbb{P}\left[|F_g(\xi^n_{\tau_n+\theta})-F_g(\xi^n_{\tau_n})| > e^{-N}\varepsilon\right]< e^{-N}\varepsilon,$$
+so
+\begin{equation}
+\sup_{n \geq n_0}\sup_{\theta \in [0, \delta]} \mathbb{P}\left[|\langle f, \xi^n_{\tau_n+\theta}\rangle - \langle f, \xi^n_{\tau_n}\rangle | > \varepsilon \right] \leq \varepsilon / 2 + e^{-N} \varepsilon < \varepsilon.
+\end{equation}
+
+ We have proved relative compactness of $\{(f(\xi^n_t))_{t \geq 0}: n=1,2,..
+\}$ and thus relative compactness of  $(\xi^n_t)_{t\geq 0}$ in $\mathcal{D}_{\overline{\mathbb{R}^d} \times[0,\infty)}([0,T])$.
 \end{proof}
-\begin{definition}
-We define $\mathfrak{G}_{\leq 1}$ to be the set of functions $g \in \mathcal{C}(\IR^d \times [0, \infty) \to \IR)$ such that 
-$g(\cdot, u) \in \mathcal{C}_{0}(\IR^d)$ for all $u \geq 0$, and there exists some $u_{*}>0$, such that $g(x,u)=1$ for all $u \geq u_{*}$.
-\end{definition}
-
-\begin{lemma}\label{lem: Dense set for test functions on empirical measures} For $g \in \mathfrak{G}_{\leq 1}$, define $F_g(\xi):= \exp(-\langle \log g, \cdot \rangle )$. The set of functions 
-$$\left\{\sum_{m=1}^{N}a_m F_{g_m}(\cdot) ~~|~~ g_1,...,g_N \in \mathfrak{G}_{\leq 1}\right\}$$
-is dense in $C(\mathcal{M}(\mathbb{R^d} \times [0, \infty]),\IR)$.
-\end{lemma}
-\begin{proof}
-Direct application of Stone-Weierstrass Theorem.
-These finite combinations are closed under addition by construction, and they are closed under multiplication as $F_{g_1}(\cdot) \times F_{g_2}(\cdot):=F_{g_1 \times g_2}(\cdot)$.
-Thus we have a subalgebra that also clearly separates points and vanishes nowhere.
-\end{proof}
-
-Combining Theorem \ref{teo: Vague Relative Compactness through Projection} and Lemma \ref{lem: Dense set for test functions on empirical measures}, we have that $\{\xi^N_t: N \in \mathbb{N}\}$ is tight as a $\mathcal{M}(\mathbb{R^d} \times [0, \infty])$-valued stochastic process in the vague topology as long as $\{F_g(\xi^N_t): N \in \mathbb{N}\}$ is tight as real-valued stochastic processes
-for all $g \in \mathfrak{G}_{\leq 1}$. 
 \bibliographystyle{plainnat}

### 2023-01-13 forwards-and-backwards.tex
.

@@
     To get around this,
-    first note that both $b$ and $c$ are uniformly bounded above since $\gamma$, $r$ and $F$ are.
-    Also note that by \plr{TODO},
-    for any $\delta > 0$ we can find a $K$ such that
+    first note that both $b$ and $c$ are uniformly bounded above 
+    by Lemma~\ref{lem:gamma_bound} and since $\gamma$, $r$, $F$ \comment{(???)}, and $\theta/N$ are.
+    Also note that for any $\delta > 0$ we can find a $K$ such that
     $$
@@
 \begin{itemize}
-\item $\mathcal{S}$ is Polish in the vague topology,
-\item a set $A\subset \mathcal{S}$ is vaguely relatively compact iff $\sup_{\mu\in A} \mu f < \infty$ for all $f \in C^{+}_{c}$
+\item $\mathcal{M}(S)$ is Polish in the vague topology,
+\item a set $A\subset \mathcal{M}(S)$ is vaguely relatively compact iff $\sup_{\mu\in A} \mu f < \infty$ for all $f \in C^{+}_{c}$
 \item if $\mu_n \to \mu$ in the vague topology and $B \in \hat{S}$ with $\mu \partial B = 0$, then $\mu_n B \to \mu B$

### 2023-01-24 forwards-and-backwards.tex
Update on Overleaf.

--- 2023-01-13 forwards-and-backwards.tex
@@
 These particles however will not contribute to the metric associated with the vague topology and thus we will retain relative compactness.
-The main argument relies on the observation that particles with levels lower than some threshold $\overline{U}_{N, \delta}$  have regulated level increments of order $\epsilon$ over any small time interval of length $\delta t$ given large enough $N$.
+The main argument relies on the observation that particles with levels lower than some threshold $\overline{U}_{N, \delta}$  have regulated level increments of order $\epsilon$ over any small time interval of length $r$ given large enough $N$.
 As a result, we can evaluate our level process against test functions $(g_n)_{n=1,..,N}$ with cut off smaller than $\overline{U}_{N, \delta}$.
@@
 $\{(U^{N}_{a}(t))_{t \geq \tau_a}, N >0\}$ is relatively compact in 
-$\mathcal{D}_{[0,\infty]}[0,\infty )$, where $[0,\infty]$ is equipped with the metric $\mathfrak{d}$ for the vague topology in $[0,\infty]$ (see Theorem  \ref{Vague times Euclidean is Polish}).
+$\mathcal{D}_{[0,\infty)}[0,\infty )$, where $[0,\infty)$ is equipped with the vague topology.
 \end{lemma}
@@
 To control the level process, we consider two scenarios, one where the local density of the system between $[0,r]$ is never too big, i.e.
-$$h(r)=\sup_{x \in \IR^d}\sup_{s\in [0,r]}\left\{\varrho_F*\eta^N_s(X^N_a(s)) \right\} \leq H_{\epsilon}(r),$$
+$$h(r)=\sup_{x \in \IR^d}\sup_{s\in [0,r]}\left\{\varrho_F*\eta^N_s(x) \right\} \leq H_{\epsilon}(r),$$
 and otherwise.
@@
 
-\textbf{Introducing a cutoff range:} It suffices to show that for any $\epsilon > 0$ and for any line of descent $a \in \mathcal{U}$, there exists small enough  $\delta t>0$ such that $\mathbb{E}[\mathfrak{d}(U^{N}_{a}(t+\delta t),U^{N}_{a}(t))|{\cal F}_t^{
-\eta}]< \epsilon$. \\
-For this, pick $K_{\epsilon} \in \mathbb{N}$ such that $\frac{1}{2^{K_{\epsilon}}} < \epsilon/2$. then we have that 
-\begin{equation}
-\mathfrak{d}(U^{N}_{a}(t+\delta t),U^{N}_{a}(t))\leq  \sum_{n=1}^{K_{\epsilon}}\frac{1 \wedge |g_n(U^{N}_{a}(t+\delta t))-g_n(U^{N}_{a}(t))|}{2^n} +  \epsilon/2. 
-\end{equation}
-Now it suffices to prove that for small enough $\delta t>0$, $|g_n(U^{N}_{a}(t+\delta t))-g_n(U^{N}_{a}(t))| < \epsilon / (2K_{\epsilon})$.
-
-Pick $\overline{U}_{K_{\epsilon}, \epsilon}>0$ large enough such that $\text{supp}(g_n)\subset [0,\overline{U}_{K_{\epsilon}, \epsilon}]$ for all $n=1,..,K_{\epsilon}$.
-Since we picked $g_n$ to be continuous and differentiable with compact support, by Mean Value Theorem we have that
-$$|g_n(U^{N}_{a}(t+\delta t ))-g_n(U^{N}_{a}(t))|<C_{g_1,..,g_{K_{\epsilon}}}(|U^{N}_{a}(t+\delta t)-U^{N}_{a}(t)|\wedge \overline{U}_{K_{\epsilon}, \epsilon}), $$
-uniformly over $n=1,..,K_{\epsilon}$ for some constant $C'_{g_1,...,g_{K_{\epsilon}}}$.
-Note that it suffices to consider $|U^{N}_{a}(t+\delta t)-U^{N}_{a}(t)|\wedge \overline{U}_{K_{\epsilon}, \epsilon}$ because $g_n(u)=g_n(\overline{U}_{K_{\epsilon}, \epsilon})=0$ for all $u > \overline{U}_{K_{\epsilon}, \epsilon}$.
-
-Therefore, it suffices to show that for all $\epsilon > 0$, there exists $\delta t>0$ small enough such that 
-\begin{equation}
-\mathbb{E}[C_{g_1,..,g_{K_{\epsilon}}}|U^{N}_{a}(t+\delta t)-U^{N}_{a}(t)|\wedge \overline{U}_{K_{\epsilon}, \epsilon} ~|~{\cal F}_t^{
+\textbf{Introducing a cutoff range:} 
+By the characterisation of vague topology on $[0,\infty)$,
+it suffices to prove that for all functions $g\in C_{c}([0,\infty), \mathbb{R}])$ (continuous functions with compact support), 
+the real-valued process
+$\{(g(U^{N}_{a}(t)))_{t \geq \tau_a}, N >0\}$ is relatively compact in 
+$\mathcal{D}_{\mathbb{R}}[0,\infty)$,
+where $\mathbb{R}$ is equipped with the Euclidean metric.
+
+It suffices to show that for any $\epsilon > 0$ and for any line of descent $a \in \mathcal{U}$, there exists small enough  $r>0$ such that $\mathbb{E}[|g(U^{N}_{a}(t+r))-g(U^{N}_{a}(t))||{\cal F}_t^{
+\eta}]< \epsilon$.
+
+Pick $U_{g,\varepsilon}>0$ large enough such that $\text{supp}(g)\subset [0,U_{g,\varepsilon}]$.
+Since we picked $g$ to be continuous and differentiable with compact support, by Mean Value Theorem we have that 
+$$|g(U^{N}_{a}(t+r ))-g(U^{N}_{a}(t))|<C'_{g}(|U^{N}_{a}(t+r)-U^{N}_{a}(t)|\wedge U_{g,\varepsilon}),$$
+for some constant $C'_g$. Note that it suffices to consider $|U^{N}_{a}(t+r)-U^{N}_{a}(t)|\wedge U_{g,\varepsilon}$ because $g_n(u)=g_n(U_{g,\varepsilon})=0$ for all $u > U_{g,\varepsilon}$.
+
+Therefore, it suffices to show that for all $\epsilon > 0$, there exists $r>0$ small enough and $N_0$ large enough such that 
+\begin{equation}
+\mathbb{E}[C'_{g}(|U^{N}_{a}(t+r)-U^{N}_{a}(t)|\wedge U_{g,\varepsilon}) ~|~{\cal F}_t^{
 \eta} ] < \epsilon /2    
@@
     \label{eq: Mass Bound Constant}
-H_{\epsilon}(r):=\frac{\epsilon}{2||\varrho_F||_{\infty}C(r) \overline{U}_{K_{\epsilon}}C_{g_1,..,g_{K_{\epsilon}}}}>0    
+H_{\epsilon}(r):=\frac{\epsilon}{2||\varrho_F||_{\infty}C(r) }>0    
 \end{equation}
@@
 \leq  \frac{||\varrho_F||_{\infty}C(t+r)}{H_{\epsilon}(r)}
-< \frac{\epsilon}{2 \overline{U}_{K_{\epsilon}}C_{g_1,..,g_{K_{\epsilon}}}},
+< \frac{\epsilon}{2 U_{g,\varepsilon}C'_g},
 \end{equation}
@@
 \begin{equation}
-\begin{aligned}
-\mathbb{E}\left[\mathfrak{d}(U^{N}_{a}(t+s),U^{N}_{a}(t)) : A_{H_{\epsilon}} ~|~{\cal F}_t^{
-\eta} \right] & \leq  
-  \mathbb{E}\left[\sum_{n=1}^{K_{\epsilon}}\frac{1 \wedge |g_n(U^{N}_{a}(t+s))-g_n(U^{N}_{a}(t))|}{2^n} +  \epsilon/2: A_{H_{\epsilon}} ~\bigg|~{\cal F}_t^{
-\eta} \right]  \\
- & \leq  \sum_{n=1}^{K_{\epsilon}}\frac{\mathbb{E}\left[C_{g_1,..,g_{K_{\epsilon}}} \overline{U}_{K_{\epsilon}, \epsilon}: A_{H_{\epsilon}} \right] }{2^n} +  \epsilon/2  \\
-& \leq  \sum_{n=1}^{K_{\epsilon}}\frac{C_{g_1,..,g_{K_{\epsilon}}} \overline{U}_{K_{\epsilon}, \epsilon}\mathbb{P}\left[ A_{H_{\epsilon}} \right] }{2^n} +  \epsilon/2 \\
-& \leq  \sum_{n=1}^{K_{\epsilon}}\frac{\epsilon /2 }{2^n} +  \epsilon/2 \\
-& < \epsilon.
-\end{aligned}
+\mathbb{E}\left[|g(U^{N}_{a}(t+r ))-g(U^{N}_{a}(t))| \mathbbm{1}_{A_{H_{\epsilon}}} ~|~{\cal F}_t^{
+\eta} \right] 
+\leq  \mathbb{E}\left[C'_{g} U_{g,\varepsilon}\mathbbm{1}_{A_{H_{\epsilon}}} \right] \leq  C'_{g} U_{g,\varepsilon}\mathbb{P}\left[A_{H_{\epsilon}} \right] < \varepsilon / 2.
 \end{equation}
@@
 \mathbb{E}[U^{N}_{a}(t+r)-U^{N}_{a}(t)] \geq   &   - \mathbb{E}\left[\int_{t}^{(t+r)  } b_{\theta}(X^N_a(s),\eta^N_s) U^N_a(s)ds\right]\\
-\geq& - rC_G\overline{U}_{K_{\epsilon}, \epsilon}.
+\geq& - rC_GU_{g,\varepsilon}.
 \end{aligned}    
@@
 with $H_{\epsilon}(r) > \sup_{s\in [0,r]}\left\{\varrho_F*\eta^N_s(X^N_a(s)) \right\}$,
-and $W^N_a(0)=U^N_a(\tau_a) = U_0 \leq \overline{U}_{K_{\epsilon}, \epsilon}$.
+and $W^N_a(0)=U^N_a(\tau_a) = U_0 \leq U_{g,\varepsilon}$.
 
@@
 \begin{equation}
-W^N_a(s) = \frac{C_F H_{\epsilon}(r) U_0 \exp(C_F H_{\epsilon}(r) s)}{C_F H_{\epsilon}(r)+C_G  N^{-1}\theta U_0(1- \exp(C_F H_{\epsilon}(r) s))}\leq \overline{U}_{K_{\epsilon}, \epsilon}    
+W^N_a(s) = \frac{C_F H_{\epsilon}(r) U_0 \exp(C_F H_{\epsilon}(r) s)}{C_F H_{\epsilon}(r)+C_G  N^{-1}\theta U_0(1- \exp(C_F H_{\epsilon}(r) s))}\leq U_{g,\varepsilon}    
 \end{equation}
@@
 \frac{C_F H_{\epsilon}(r)
-(\overline{U}_{K_{\epsilon}, \epsilon}
+(U_{g,\varepsilon}
 -U_0)
 }
-{C_F H_{\epsilon}(r)U_0 +C_G  N^{-1}\theta \overline{U}_{K_{\epsilon}, \epsilon}    U_0}
+{C_F H_{\epsilon}(r)U_0 +C_G  N^{-1}\theta U_{g,\varepsilon}    U_0}
 \right\}.
 \end{equation}
-As $\theta / N $ converges in the limit, we may take some constant $A$ such that for large enough $N$,
-the level process $(U^N_{a}(s))_{s \geq 0}$ will not hit  $\overline{U}_{K_{\epsilon}, \epsilon}$ as long as
+As $\theta / N $ converges in the limit, we may take some constant $\bar{\alpha}$ such that for large enough $N$,
+the level process $(U^N_{a}(s))_{s \geq 0}$ will not hit  $U_{g,\varepsilon}$ as long as
 \begin{equation}
@@
 \frac{C_F H_{\epsilon}(r)
-(\overline{U}_{K_{\epsilon}, \epsilon}
+(U_{g,\varepsilon}
 -U_0)
 }
-{C_F H_{\epsilon}(r)U_0 +C_G  A \overline{U}_{K_{\epsilon},\epsilon}    U_0}
+{C_F H_{\epsilon}(r)U_0 +C_G  \bar{\alpha} \overline{U}_{K_{\epsilon},\epsilon}    U_0}
 \right\}:=T(U_0,\overline{U}_{K_{\epsilon},\epsilon},r).
@@
 
-Note that $T$ only depends on the initial level $U_0$, the upper limit $\overline{U}_{K_{\epsilon}, \epsilon}$ and the bound on total mass $C(r)$ at time $r$, and is independent to $N$. 
+Note that $T$ only depends on the initial level $U_0$, the upper limit $U_{g,\varepsilon}$ and the bound on total mass $C(r)$ at time $r$, and is independent to $N$. 
 In particular, 
@@
 \leq \mathbb{P}[A_{H_{\epsilon}}]
-< \frac{\epsilon}{2 \overline{U}_{K_{\epsilon}}C_{g_1,..,g_{K_{\epsilon}}}},
+< \frac{\epsilon}{2 U_{g,\varepsilon}C'_g},
 \end{equation}
@@
 
-As a result, for all time $ 0 < t , t+ \delta t \leq T(U_0,\overline{U}_{K_{\epsilon},\epsilon},r),$
-
-\begin{align*}
-W^N_a(t+\delta t)-W^N_a(t) 
-\leq &\int_{t}^{t+\delta t} 
-        \left( \frac{\theta}{N} C_G \overline{U}_{K_{\epsilon}, \epsilon}^2
+As a result, for all time $ 0 < t , t+ r \leq T(U_0,\overline{U}_{K_{\epsilon},\epsilon},r),$
+
+\begin{align*}
+W^N_a(t+r)-W^N_a(t) 
+\leq &\int_{t}^{t+r} 
+        \left( \frac{\theta}{N} C_G U_{g,\varepsilon}^2
         +
-        C_F H_{\epsilon}(r) \overline{U}_{K_{\epsilon}, \epsilon}
+        C_F H_{\epsilon}(r) U_{g,\varepsilon}
         \right)
         ds\\
-=&\left( \frac{\theta}{N} C_G \overline{U}_{K_{\epsilon}, \epsilon}^2
+=&\left( \frac{\theta}{N} C_G U_{g,\varepsilon}^2
         +
-        C_F H_{\epsilon}(r) \overline{U}_{K_{\epsilon}, \epsilon}
-        \right) \delta t \\
-\leq&\left( A C_G \overline{U}_{K_{\epsilon}, \epsilon}^2
+        C_F H_{\epsilon}(r) U_{g,\varepsilon}
+        \right) r \\
+\leq&\left( \bar{\alpha} C_G U_{g,\varepsilon}^2
         +
-        C_F H_{\epsilon}(r) \overline{U}_{K_{\epsilon}, \epsilon}
-        \right) \delta t
-\end{align*}
-
-Combining the results together, we have that for any $\delta t > 0$ small enough such that 
-\begin{equation}
-\delta t < \frac{\epsilon  }{4C_{g_1,..,g_{K_{\epsilon}}}}\min\left\{\frac{1}{C_G \overline{U}_{K_{\epsilon}, \epsilon}}, \frac{1}{A C_G \overline{U}_{K_{\epsilon}, \epsilon}^2
+        C_F H_{\epsilon}(r) U_{g,\varepsilon}
+        \right) r
+\end{align*}
+
+Combining the results together, we have that for any $r > 0$ small enough such that 
+\begin{equation}
+r < \frac{\epsilon  }{4C'_g}\min\left\{\frac{1}{C_G U_{g,\varepsilon}}, \frac{1}{\bar{\alpha} C_G U_{g,\varepsilon}^2
         +
-        C_F H_{\epsilon}(r) \overline{U}_{K_{\epsilon}, \epsilon}}\right\}    
+        C_F H_{\epsilon}(r) U_{g,\varepsilon}}\right\}    
 \end{equation}
 holds, then we have for all $t \leq T(U_0,\overline{U}_{K_{\epsilon},\epsilon},r)$,
+
 \begin{equation}
 \begin{aligned}
-\mathbb{E}\left[\mathfrak{d}(U^{N}_{a}(t+\delta t),U^{N}_{a}(t)) : A_{H_{\epsilon}}^{c} \right] \leq  &  
-  \mathbb{E}\left[\sum_{n=1}^{K_{\epsilon}}\frac{1 \wedge |g_n(U^{N}_{a}(t+\delta t))-g_n(U^{N}_{a}(t))|}{2^n} +  \epsilon/2: A_{H_{\epsilon}}^{c} ~\bigg|~{\cal F}_t^{
-\eta}\right]  \\
- \leq &   \sum_{n=1}^{K_{\epsilon}}\frac{\mathbb{E}\left[C_{g_1,..,g_{K_{\epsilon}}} |U^{N}_{a}(t+r)-U^{N}_{a}(t)|: A_{H_{\epsilon}}^{c} ~\bigg|~{\cal F}_t^{
-\eta} \right] }{2^n} +  \epsilon/2  \\
-\leq&   \sum_{n=1}^{K_{\epsilon}}\frac{\mathbb{E}\left[C_{g_1,..,g_{K_{\epsilon}}} |C_G \overline{U}_{K_{\epsilon}, \epsilon} \delta t|  : A_{H_{\epsilon}}^{c} ~\bigg|~{\cal F}_t^{
-\eta} \right] }{2^n}  \\
- & + \sum_{n=1}^{K_{\epsilon}}\frac{\mathbb{E}\left[C_{g_1,..,g_{K_{\epsilon}}}  |W^N_a(t+\delta t)-W^N_a(t)|: A_{H_{\epsilon}}^{c} ~\bigg|~{\cal F}_t^{
-\eta} \right] }{2^n} +  \epsilon/2  \\
-\leq  &  \sum_{n=1}^{K_{\epsilon}}\frac{\epsilon /2 }{2^n} +  \epsilon/2 \\
-< &  \epsilon.
+\mathbb{E}\left[|g(U^{N}_{a}(t+r ))-g(U^{N}_{a}(t))| \mathbbm{1}_{A_{H_{\epsilon}}^c} ~|~{\cal F}_t^{
+\eta} \right] 
+& \leq  \mathbb{E}\left[C'_{g} |U^{N}_{a}(t+r )-U^{N}_{a}(t)|\mathbbm{1}_{A_{H_{\epsilon}}^c} \right] \\
+&\leq r C'_g \max\{ \bar{\alpha} C_G U_{g,\varepsilon}^2
+        +
+        C_F H_{\epsilon}(r) U_{g,\varepsilon}
+        , C_G U_{g, \varepsilon}\} \\
+        & < \varepsilon.
 \end{aligned}
@@
 \begin{aligned}
-\mathbb{E}[\mathfrak{d}(U^{N}_{a}(t+\delta t),U^{N}_{a}(t))~|~{\cal F}_t^{
-\eta}] \leq & \mathbb{E}\left[\mathfrak{d}(U^{N}_{a}(t+\delta t),U^{N}_{a}(t)) : A_{H_{\epsilon}} ~|~{\cal F}_t^{
-\eta}\right]\\
-&+ \mathbb{E}\left[\mathfrak{d}(U^{N}_{a}(t+\delta t),U^{N}_{a}(t)) : A_{H_{\epsilon}}^{c} ~|~{\cal F}_t^{
+& \mathbb{E}[|g(U^{N}_{a}(t+r ))-g(U^{N}_{a}(t))|~|~{\cal F}_t^{
+\eta}]\\
+\leq & \mathbb{E}\left[|g(U^{N}_{a}(t+r ))-g(U^{N}_{a}(t))| \mathbbm{1}_{A_{H_{\epsilon}}} ~|~{\cal F}_t^{
+\eta}\right]+ \mathbb{E}\left[|g(U^{N}_{a}(t+r ))-g(U^{N}_{a}(t))| \mathbbm{1}_{A_{H_{\epsilon}}^c} ~|~{\cal F}_t^{
 \eta}\right] \\
@@
 \begin{equation*}
-\delta t < \frac{\epsilon  }{4C_{g_1,..,g_{K_{\epsilon}}}}\min\left\{\frac{1}{C_G \overline{U}_{K_{\epsilon}, \epsilon}}, \frac{1}{A C_G \overline{U}_{K_{\epsilon}, \epsilon}^2
+r < \frac{\epsilon  }{4C'_g}\min\left\{\frac{1}{C_G U_{g,\varepsilon}}, \frac{1}{\bar{\alpha} C_G U_{g,\varepsilon}^2
         +
-        C_F H_{\epsilon}(r) \overline{U}_{K_{\epsilon}, \epsilon}}\right\}.    
+        C_F H_{\epsilon}(r) U_{g,\varepsilon}}\right\}.    
 \end{equation*}
@@
 \begin{lemma}
-The lookdown representation satisfies
-Equation \eqref{eq: vague compact containment condition}, i.e.
-for all $\epsilon>0$, there exists $N>0$ such that
-\begin{equation}
- \limsup_{n \to \infty} \mathbb{P}\left\{ \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle > N \right\} < \epsilon,
-\end{equation}
+The lookdown representation satisfies the compact containment condition, 
+Equation \eqref{eq: vague compact containment condition}, 
+for all $\varepsilon > 0$ and fixed time $T > 0$, there exists $N,K> 0$ such that 
+\begin{equation}
+\liminf_{n \to \infty}\mathbb{P}\{ \xi^n_t \in \Gamma_{N,K} \text{ for all } t\in [0,T]\} > 1-\varepsilon,
+\end{equation}
+where $\Gamma_{N,K}$ is the compact set in Lemma \ref{lem: vague compact sets}
 \end{lemma}
@@
 \begin{proof}
-For every $f \in C^{+}_{c}(\overline{\mathbb{R}^d} \times [0,\infty))$,
-there exists $u^* > 0$ such that $f(x,u) = 0$ for all $u \geq u^*$.
-Then,
+Note that
 \begin{equation}
 \begin{aligned}
- &\limsup_{n \to \infty} \mathbb{P}\left\{ \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle > N \right\} \\
- \leq & \limsup_{n \to \infty}\frac{\mathbb{E}\left\{ \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle \right\}}{N}\\
- \leq & \limsup_{n \to \infty}||f||_{\infty}\frac{\mathbb{E}\left\{ \sup_{t\in [0,T]}\langle 1_{[0,u^*]}, \xi^n_t \rangle \right\}}{N}.
+     &1-\mathbb{P}\{ \xi^n_t \in \Gamma_{N,K} \text{ for all } t\in [0,T]\} \\
+     = & \mathbb{P}\left\{ \sup_{t \in[0,T]}\frac{1}{N}\langle 1_{\overline{\mathbb{R}^d}\times [0,N]}, \xi^n_t \rangle \geq K \right\} \\
+ \leq & \frac{\mathbb{E}\left\{ \sup_{t \in[0,T]}\frac{1}{N}\langle 1_{\overline{\mathbb{R}^d}\times [0,N]}, \xi^n_t \rangle\right\}}{K}.
 \end{aligned}
@@
 the level of each individual is independently and uniformly distributed between $[0,n]$.
-Therefore, 
-\begin{equation}
-\mathbb{E}\left\{ \sup_{t\in [0,T]}\langle 1_{[0,u^*]}, \xi^n_t \rangle \right\} = u^* \mathbb{E}\left\{ \sup_{t\in [0,T]}\langle 1, \eta^n_t \rangle \right\}.
-\end{equation}
-Finally, 
-recall that the supremum of the empirical measure process is controlled in Lemma \ref{lem:eta_compact_containment}
-so there exists some constant $C_T$ such that 
-\begin{equation}
-\begin{aligned}
- &\limsup_{n \to \infty} \mathbb{P}\left\{ \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle > N \right\} \\
- \leq & \limsup_{n \to \infty}||f||_{\infty}\frac{u^*}{N}\mathbb{E}\left\{ \sup_{t\in [0,T]}\langle 1, \eta^n_t \rangle \right\}\\
- \leq & ||f||_{\infty}\frac{u^*}{N}C_T\\
- < & \epsilon
-\end{aligned}
-\end{equation}
-for sufficiently large $N$.
+Therefore, for $n \geq N$,
+\begin{equation}
+\frac{\mathbb{E}\left\{ \sup_{t \in[0,T]}\frac{1}{N}\langle 1_{\overline{\mathbb{R}^d}\times [0,N]}, \xi^n_t \rangle\right\}}{K}
+= \frac{\mathbb{E}\left\{ \sup_{t\in [0,T]}\langle 1, \eta^n_t \rangle \right\}}{K} < \varepsilon,
+\end{equation}
+for large enough $K>0$. 
+The last inequality is given by Lemma \ref{lem:eta_compact_containment}.
 \end{proof}
@@
 is a finite measure on $\overline{\mathbb{R}^d} \times [0,N]$.
-
-To characterise convergence of $\xi^N(t)$ as $N \to \infty$,
-we therefore need to impose an appropriate topology on $\mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty))$,
+Furthermore, the level of a particle in our lookdown representation can shoot to infinity in finite time.
+Therefore, to characterise convergence of $\xi^N(t)$ as $N \to \infty$,
+we need to impose an appropriate vague topology on $\mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty))$,
 the space of finite measures on $\overline{\mathbb{R}^d} \times [0,\infty)$.
-
-We now refer to the vague topology introduced in P564, \S A2 in \cite{kallenberg1997foundations}.
+Similarly, to characterise convergence of the level process of individual lineages, we consider the vague topology on $[0,\infty)$.
+
+We now refer to the vague topology on measure spaces introduced in P564, \S A2 in \cite{kallenberg1997foundations}.
 Let $S$ be a locally compact Polish space and $\hat{S}$ be the class of bounded sets in $S$.
@@
 
-We now introduce two important theorems on compactness and convergence in the vague topology.
+We now introduce an important theorem on compactness in the vague topology.
 \begin{theorem}[Theorem A.23 in \cite{kallenberg1997foundations}]
@@
 
-The following corollary holds immediately.
-\begin{corollary}
-The set $\Gamma_K := \{\mu \in \mathcal{M}(S): \mu(S) \leq K\}$
+To characterise convergence of lookdown representations,
+we take $S = \overline{\mathbb{R}^d} \times [0,\infty)$.
+We now identify compact sets under the vague topologies.
+
+\begin{lemma}
+\label{lem: vague compact sets}
+For any fixed $N.0, K>0$, the set 
+$$\Gamma_{N,K} := \left\{\mu \in \mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty)):  \frac{1}{N}\mu(\overline{\mathbb{R}^d}\times [0,N]) \leq K \right\}$$
 is vaguely compact in $\mathcal{M}(S)$.
-\end{corollary}
+\end{lemma}
+
 \begin{proof}
 It suffices to show that $\Gamma_K$ is vaguely relatively compact and vaguely closed.
-For any fixed $f \in C^{+}_c$,
-we have that $ \sup_{\mu \in A} \mu f \leq  ||f||_{\infty} \mu(S)  \leq ||f|| K < \infty$,
-so $\Gamma_K$ is vaguely relatively compact.
+For any fixed $f \in C^{+}_c$, $f$ is bounded above uniformly by $||f||_{\infty}$.
+Therefore, 
+we have that $ \sup_{\mu \in  \Gamma_K} \mu f \leq  ||f||_{\infty} \mu(\overline{\mathbb{R}^d}\times [0,N])  \leq ||f|| K N < \infty$,
+so $\Gamma_{N,K}$ is vaguely relatively compact.
 
 Now it suffices to prove that $\Gamma_K$ is closed under the vague topology.
-Consider a vaguely converging sequence $(\mu_n)_{n \geq 1}$ in $\Gamma_K$
-satisfying $\mu_n \to \mu \in \mathcal{M}(S)$,
-then for an increasing sequence of functions $f_m \to 1$,
-by the Dominating Convergence Theorem, 
-\begin{equation}
-\mu(S)
-= \lim_{m \to \infty} \mu f_m
-= \lim_{m \to \infty} \lim_{n \to \infty} \mu_n f_m
-= \lim_{n \to \infty}   \mu_n (S)
+Consider a vaguely converging sequence $(\mu_n)_{n \geq 1}$ in $\Gamma_{N,K}$
+with limit $\mu_n \to \mu \in \mathcal{M}(S)$.
+We pick some test functions $\{f_m : m \geq 0 \}$ monotonically increasing to $1_{\overline{\mathbb{R}^d}\times[0,N]}(x)$.
+
+Since for each $n>0$ and $m > 0$,
+$\frac{1}{N}\langle f_m , \mu_n \rangle < K$,
+by Dominating Convergence Theorem,
+\begin{equation}
+\frac{1}{N}\mu(\overline{\mathbb{R}^d}\times [0,N])
+= \lim_{m \to \infty} \frac{1}{N}\langle f_m , \mu \rangle
+=\lim_{m \to \infty} \lim_{n \to \infty} \frac{1}{N}\langle f_m , \mu_n \rangle
 \leq K,
 \end{equation}
-and so $\mu \in \Gamma_K$.
-Therefore $\Gamma_K$ is vaguely compact. 
+and so $\mu \in \Gamma_{N,K}$.
+Therefore $\Gamma_{N,K}$ is vaguely compact. 
 \end{proof}
 
-We now include another theorem that is very relevant to establishing tightness of $\mathcal{M}(S)$-valued processes in the Skorokhod topology.
-
-\begin{theorem}[Theorem A2.4 in \cite{kallenberg1997foundations}]\label{teo: vag_sko_conv}
-Let $f_1,f_2,...$ be a dense collection in $C^{+}_{c}(S)$ closed under addition, 	
-then any set $A \subset \mathcal{D}_{\mathcal{M}(S)}([0,\infty))$
-is relatively compact if and only if for every $j \in \mathbb{N}$,
-$Af_j = \{xf_j, x \in A\}$
-is relatively compact in $\mathcal{D}_{\mathbb{R}^{+}}([0,\infty))$.
+We now include another theorem that is very relevant to establishing tightness of $\mathcal{M}(S)$-valued processes in the Skorokhod topology. It can be found as Theorem 3.9.1 in \cite{EK}.
+
+\begin{theorem}[\cite{EK} Theorem 3.9.1]
+\label{teo: EK tightness theorem}
+Let $(S,r)$ be complete and separable, and let $\{X_{\alpha}\}$ be a family of processes with sample paths in $D_{S}([0,\infty))$.
+Suppose that the compact containment condition holds. That is, for every $\eta > 0$ and $T > 0$,
+there exists a compact set $\Gamma_{\eta, T} \subset E$ for which 
+\begin{equation}
+\inf_{\alpha} P \{ X_{\alpha}(t) \in \Gamma_{\eta,T}  ~~ \text{for } 0\leq t \leq T\} \geq 1- \eta
+\end{equation}
+Let $H$ be a dense subset of $\overline{C}(E)$ (bounded continuous functions on $E$) in the topology of uniform convergence on compact sets. 
+Then $\{X_{\alpha}\}$ is relatively compact if and only if $\{f(X_{\alpha})\}$ is relatively compact (as a family of processes with sample paths in $\mathcal{D}_{\mathbb{R}}([0,\infty))$) for each $f \in H$.
 \end{theorem}
 
-To characterise convergence of lookdown representations,
-we take $S = \overline{\mathbb{R}^d} \times [0,\infty)$
-and consider the test functions of the form 
+To apply Theorem \ref{teo: EK tightness theorem},
+we need to identify dense subset of $\overline{C}(\mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty)))$.
+Since the space $\mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty))$ is not compact but locally compact,
+we will apply Stone-Weierstrass theorem for locally compact space.
+
+\begin{lemma}[Stone-Weierstrass Theorem for locally compact space]
+\label{lem: SW locally compact}
+Let $X$ be a locally compact Hausdorff space, and consider the set  $C_{\infty}(X, \mathbb{R})$ of real-valued continuous functions which vanishes at infinity. 
+Let $\mathcal{A}$ be a subalgebra in $C_{\infty}(S)$. Then $\mathcal{A}$ is dense in $C_{\infty}(X, \mathbb{R})$ if and only if it separates points and vanishes nowhere.
+\end{lemma}
+
+With this version of Stone-Weierstrass Theorem, we can prove the following lemma.
+\begin{lemma}
+\label{lem: uniform compact density}
+We write $\mathcal{A}$ for the algebra (closed under multiplication and addition) generated by 
+the collection of functions $\xi \mapsto \langle f, \xi \rangle$, where $ f \in C_c(\overline{\mathbb{R}^d} \times [0,\infty))$ is differentiable in $u$ and smooth in $x$ with bounded support.
+Then $\mathcal{A}$ is dense in $C(\mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty)))$ under the topology of uniform convergence on compact sets.
+\end{lemma}
+\begin{proof}
+Since $\mathcal{A}$ contains the functions $\langle \rho_{\varepsilon}*\mathbbm{1}_{A} , \mu \rangle$,
+where $\rho$ is some mollifier and $A$ is a compact set, it clearly
+separates points and vanishes nowhere.
+Therefore, $\mathcal{A}$ is dense in $C_{\infty}(\mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty)), \mathbb{R})$.
+
+Furthermore, under the topology of uniform convergence on compact sets, 
+$C_{\infty}(\mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty)), \mathbb{R})$ 
+contains the mollified indicator functions $\langle \rho_{\varepsilon}*\mathbbm{1}_{A} , \mu \rangle$,
+which are dense in $C(\mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty)))$.
+\end{proof}
+
+Finally, we include another technical lemma on the products of real-valued stochastic processes. 
+\begin{lemma}
+\label{teo: product tightness}
+Let $\{(X^n_t)_{t \geq 0}: n \geq 0\}, \{(Y^m_t)_{t \geq 0}: m \geq 0\}$ be two tight sequences of real-valued process under the Skorokhod topology.
+Then the sequence of processes $\{(X^n_tY^n_t)_{t \geq 0}: n \geq 1\}$ is tight under the Skorokhod topology.
+\end{lemma}
+
+\begin{proof}
+We apply the Aldous Criterion of tightness on the real-valued sequences
+$\{(X^n_tY^n_t)_{t \geq 0}: n=1,2,.. \}$. 
+It suffices to show that
+for fixed sequences of stopping time $\tau_n$ bounded above by $T$,
+for each $\varepsilon>0$,
+there exists $\delta > 0$ and $n_0$ such that
+\begin{equation}
+\sup_{n \geq n_0}\sup_{\theta \in [0, \delta]} \mathbb{P}\left[|X^n_{\tau_n+\theta}Y^n_{\tau_n+\theta} - X^n_{\tau_n}Y^n_{\tau_n} | > \varepsilon \right] \leq \varepsilon.
+\end{equation}
+
+First note that 
+\begin{equation}
+|X^n_{\tau_n+\theta}Y^n_{\tau_n+\theta} - X^n_{\tau_n}Y^n_{\tau_n} |
+= |X^n_{\tau_n+\theta}(Y^n_{\tau_n+\theta}-Y^n_{\tau_n}) +Y^n_{\tau_n}( X^n_{\tau_n+\theta}- X^n_{\tau_n})|,
+\end{equation}
+therefore
+\begin{equation}
+\begin{aligned}
+& \mathbb{P}\left[|X^n_{\tau_n+\theta}(Y^n_{\tau_n+\theta}-Y^n_{\tau_n}) +Y^n_{\tau_n}( X^n_{\tau_n+\theta}- X^n_{\tau_n})| > \varepsilon \right]\\
+ \leq &
+\mathbb{P}\left[\max\{|X^n_{\tau_n+\theta}(Y^n_{\tau_n+\theta}-Y^n_{\tau_n})|, | Y^n_{\tau_n}( X^n_{\tau_n+\theta}- X^n_{\tau_n}) |\}> \varepsilon/2 \right]\\
+\leq & \mathbb{P}\left[|X^n_{\tau_n+\theta}(Y^n_{\tau_n+\theta}-Y^n_{\tau_n})|> \varepsilon/2 \right] + \mathbb{P}\left[ | Y^n_{\tau_n}( X^n_{\tau_n+\theta}- X^n_{\tau_n}) |> \varepsilon/2 \right]
+\end{aligned}
+\end{equation}
+
+By Corollary 3.7.1 in \cite{EK}, both $\{(X^n_t)_{t \geq 0}: n \geq 0\}, \{(Y^m_t)_{t \geq 0}: m \geq 0\}$ satisfies the compact containment condition, i.e.
+so for any $\varepsilon'>0$ and fixed time $T> 0$, there exists $K_{\varepsilon',T}>0$ such that
+
+\begin{equation}
+ \limsup_{n \to \infty} \mathbb{P}\left\{ \sup_{t\in [0,T]}X^n_t > K_{\varepsilon',T} \right\} < \epsilon',
+\end{equation}
+and 
+\begin{equation}
+ \limsup_{n \to \infty} \mathbb{P}\left\{ \sup_{t\in [0,T]}Y^n_t > K_{\varepsilon',T} \right\} < \epsilon'.
+\end{equation}
+
+Conditioning on the event $\left\{ \sup_{t\in [0,T]}Y^n_t > K_{\varepsilon',T} \right\}$ and $\left\{ \sup_{t\in [0,T]}Y^n_t > K_{\varepsilon',T} \right\},$
+
+\begin{equation}
+\begin{aligned}
+& \mathbb{P}\left[|X^n_{\tau_n+\theta}(Y^n_{\tau_n+\theta}-Y^n_{\tau_n})|> \varepsilon/2 \right] + \mathbb{P}\left[ | Y^n_{\tau_n}( X^n_{\tau_n+\theta}- X^n_{\tau_n}) |> \varepsilon/2 \right]\\
+\leq & \mathbb{P}\left[|(Y^n_{\tau_n+\theta}-Y^n_{\tau_n})|> \frac{\varepsilon}{2K_{\varepsilon',T}}\right] + \mathbb{P}\left[ | Y^n_{\tau_n}( X^n_{\tau_n+\theta}- X^n_{\tau_n}) |> \frac{\varepsilon}{2K_{\varepsilon',T}}\right] + 2 \varepsilon'\\
+\leq & \frac{\varepsilon}{K_{\varepsilon',T}}+2 \varepsilon',
+\end{aligned}
+\end{equation}
+and by tightness of $(X^n_t, Y^n_t)_{t \geq 0}$,
+there exists $\delta > 0$ and $n \geq n_0$ such that the last term is smaller than $\varepsilon$ for 
+for all $\theta < \delta$ and $n\geq n_0$.
+\end{proof}
+
+When we work with lookdown representations, we work on test functions of the form
 \begin{equation}
@@
 
-Combining the above observation and Theorem \ref{teo: vag_sko_conv},
+With the above observation,
 we have the following lemma.
@@
 We consider a sequence $(\xi^n_t)_{t\geq 0}$ of $\mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty))$-valued cadlag processes.
+
+Assume that the sequence $(\xi^n_t)_{t\geq 0}$ satisfies the compact containment condition. That is,
+for all $\varepsilon > 0$ and fixed time $T > 0$, there exists $N, K> 0$ such that 
+\begin{equation}
+\liminf_{n \to \infty} \mathbb{P}\{ \xi^n_t \in \Gamma_{N,K} \text{ for all } t\in [0,T]\} > 1-\varepsilon,
+\end{equation}
+where $\Gamma_{N,K}$ is the compact set in Lemma \ref{lem: vague compact sets}
+
 Assume that for all test functions of the form $F_g$,
@@
 
-Furthermore, assume that for any $f \in C^{+}_{c}(\overline{\mathbb{R}^d} \times [0,\infty))$ and $\epsilon > 0$, there exists $N>0$ (dependent on $f$ and $\epsilon$), 
-such that 
-\begin{equation}
-\label{eq: vague compact containment condition}
- \limsup_{n \to \infty} \mathbb{P}\left\{ \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle > N \right\} < \epsilon,
-\end{equation}
-
- then $(\xi^n_t)_{t\geq 0}$ is relatively compact in $\mathcal{D}_{\overline{\mathbb{R}^d} \times[0,\infty)}([0,T])$.
+Then  $(\xi^n_t )_{t\geq 0}$ is relatively compact in $\mathcal{D}_{\mathcal{M}(\overline{\mathbb{R}^d} \times[0,\infty))}([0,T])$.
 \end{lemma}
@@
 \begin{proof}
-By Theorem \ref{teo: vag_sko_conv},
-it suffices to prove that for all $f \in C^{+}_{c}(\overline{\mathbb{R}^d} \times [0,\infty))$,
-$\{(f(\xi^n_t))_{t \geq 0}: n=1,2,.. \}$ is relatively compact.
-
-We now make use of the Aldous Criterion of tightness on the real-valued sequences
-$\{(f(\xi^n_t))_{t \geq 0}: n=1,2,.. \}$. It suffices to show that
+By Lemma  \ref{lem: uniform compact density}, \ref{teo: product tightness}, and Theorem 3.9.1 in \cite{EK},
+ $(\xi^n_t )_{t\geq 0}$ is relatively compact in $\mathcal{D}_{\mathcal{M}(\overline{\mathbb{R}^d} \times[0,\infty))}([0,T])$
+ if we can prove tightness on the real-valued sequences
+$\{(f(\xi^n_t))_{t \geq 0}: n=1,2,.. \}$.
+
+Applying the Aldous Criterion, it suffices to show that
 for fixed sequences of stopping time $\tau_n$ bounded above by $T$,
@@
 
-For all $n>M$,
+By the compact containment condition, 
+we know that for any $f \in C^{+}_{c}(\overline{\mathbb{R}^d} \times [0,\infty))$ and $\epsilon > 0$, there exists $N>0$ (dependent on $f$ and $\epsilon$), 
+such that 
+\begin{equation}
+\label{eq: vague compact containment condition}
+ \limsup_{n \to \infty} \mathbb{P}\left\{ \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle > N \right\} < \epsilon.
+\end{equation}
+
+Therefore, for all $n>M$,
 \begin{equation}
@@
 
- We have proved relative compactness of $\{(f(\xi^n_t))_{t \geq 0}: n=1,2,..
-\}$ and thus relative compactness of  $(\xi^n_t)_{t\geq 0}$ in $\mathcal{D}_{\overline{\mathbb{R}^d} \times[0,\infty)}([0,T])$.
+We have proved relative compactness of $\{(\langle f, \xi^n_t \rangle )_{t \geq 0}: n=1,2,.. \}$, and thus tightness of 
+ $\{(\xi^n_t )_{t \geq 0}: n=1,2,.. \}.$
 \end{proof}
+
 \bibliographystyle{plainnat}

### 2023-01-28 forwards-and-backwards.tex
alison rewrite through p.65

@@
 \usepackage{amssymb}
+\usepackage{ntheorem}
 \usepackage{graphics} 
@@
 \newtheorem{notation}[theorem]{Notation}
+\newtheorem{assumptions}[theorem]{Assumptions}
+\newtheorem{terminology}[theorem]{Terminology}
+\newtheorem*{terminology-non}[theorem]{Terminology}
 
@@
 }}
-
-% OTHER IDEAS:
-% A class of nonlinear superprocesses
-% Uncovering genealogical structures of locally regulated populations with lookdown constructions on nonlinear superprocesses
 
@@
 
-We do something...
-
-make sure to put in here that we get convergence of the FKPP
-
-Note: use "reproductive value" instead of "long-term fitness"
-and say clearly that "lineage" means "ancestral lineage".
+We introduce a broad class of mechanistic spatial models to describe how spatially 
+heterogeneous populations live, die, and reproduce. Birth and death rates can depend 
+both on spatial position and local population density, defined at a 
+spatial position $x$ to be the convolution 
+of the point measure encoding the distribution of individuals in the population
+with a suitable non-negative integrable kernel
+centred on $x$. We pass to three different scaling limits:
+an interacting superprocess, a nonlocal partial differential equation (PDE), 
+and a classical PDE. 
+The classical PDE is obtained both by a two-step convergence argument, in which we 
+first scale time and population size and
+pass to the nonlocal PDE, 
+and then scale the kernel that 
+determines local population density; and 
+in the important special case in which the limit is a 
+reaction diffusion equation, directly 
+by simultaneously scaling the kernel and the
+timescale and population size in our individual based model.
+
+A novelty of our model is that in describing the dynamics we explicitly
+model a juvenile phase: the number of juveniles produced by an individual depends
+on local population density at the location of the parent. 
+Juvenile offspring are 
+thrown off in a (possibly heterogeneous, anisotropic) Gaussian distribution 
+around the location of the parent; they then reach (instant) maturity with a probability
+that can depend on the local population density (possibly measured through convolution
+with a different kernel from that used in determining fecundity) 
+at the location at which they land. 
+Although we only record mature individuals, a trace of this two-step description 
+remains in our population models, resulting in novel limits in which the spatial
+motion is governed by a nonlinear diffusion.
+
+Using a lookdown representation, we are able to retain information about 
+genealogies relating individuals in our population and, in the case of 
+deterministic limiting models, we use this to deduce 
+the backwards in time motion of the ancestral lineage of an individual
+sampled from the population. We observe that
+knowing the history of the population density is not enough to determine the motion of
+ancestral lineages in our model. We also investigate (and
+contrast) the behaviour of lineages for 
+three different deterministic models of a population expanding its range as a 
+travelling wave: the Fisher-KPP equation, the Allen-Cahn equation, and a porous 
+medium equation with logistic growth.
 
@@
 
-\noindent {\bf Key words:}  population model, nonlinear superprocess, 
+	\comment{Need to thank KAVLI, Paris Cit\'e, various funders}
+
+\vspace{.1in}
+
+\noindent {\bf Key words:}  population model, interacting superprocess, 
 lookdown construction, porous medium equation, 
 reaction-diffusion equation, travelling waves, genealogies,
+Fisher-KPP equation
 
@@
 \section{Introduction}
-
-\comment{I think the introduction covers a good set of things in a good order, it's just a bit long.}
-
-\comment{
-    Make sure that we discuss the difference to Flandoli's model
-    (one of the few others that show convergence of FKPP),
-    and say that a novelty of our results is that we show convergence
-    for FKPP and broader models.
-}
+\label{introduction}
 
@@
 As one takes a journey, long or short, the landscape changes:
-forests thicken or thin or change their composition,
+forests thicken or thin or change their composition;
 springtime grasslands host intergrading mosaics of different types of flowers.
-The aim of this paper is to understand the implications of a broad class of mechanistic spatial models
-that might describe how such spatially heterogeneous populations live, die, and reproduce:
+The aim of this paper is to introduce and study
+a broad class of mechanistic spatial models
+that might describe how spatially heterogeneous populations live, die, and reproduce.
+Questions that we (start to) address include:
 How does population density change across space and time?
 How might we learn about the underlying dynamics from genealogical or genetic data?
-And,  how does genetic ancestry spread across geography,
+And, how does genetic ancestry spread across geography
 when looking back through time in these populations?
-We work with individual-based models of a single species in continuous space,
-where birth, death and establishment may all depend on spatial location
-as well as on local population density, allowing for stable populations through density-dependent feedback.
-
-Reproduction of individuals naturally leads to a branching process.
-There is now a huge literature devoted to spatial branching processes,
+
+Reproduction of individuals naturally leads to spatial branching process models,
 including branching random walk, 
 branching Brownian motion, and the Dawson-Watanabe superprocesses.  
-In addition to possessing a rich and beautiful mathematical structure, 
-the superprocesses are remarkable for demonstrating a certain `universality', 
-arising, as they do, as scaling limits of a vast array of different 
-spatial population models \cite[e.g.,][]{chetwynd-diggle/etheridge:2018,
-cox/perkins:2005,
-cox/durrett/perkins:1999,
-cox/durrett/perkins:2000,
-holmes:2008,
-vanderhofstad/sakai:2010,
-vanderhofstad/slade:2003,
-vanderhofstad/holmes/perkins:2017}.
-
-These models make mathematical sense in very general spaces, but
-in biological applications, typically, 
-individuals are assumed to be scattered across one or two-dimensional
-Euclidean space. In that setting, it is well known that, 
-in the long term, the population will either 
-die out, or it will develop clumps of arbitrary density and extent. 
-To counter this, it is common to
-impose some local regulation by either increasing death rates, or 
-reducing birth rates, in proportion to the local population density,
-so that the population has a tendency to grow in sparsely populated regions
-and shrink where it is overcrowded. This leads to spatial analogues of  
-logistic branching processes.
-
-Although it can be more mathematically convenient to work with branching
-Brownian motions, in many settings it is biologically more natural to 
-develop models based on branching random walk.  
-Individuals produce a random number of offspring,
-that are thrown off according to some (usually symmetric) 
-distribution centred on the location of the parent.   
+However, as a result of the branching assumption (once born, individuals behave 
+independently of one another), 
+a population evolving according to any of these models will
+either die out or grow without bound and, in so doing, it can
+develop clumps of arbitrarily large density and extent. 
+Our starting point here is an individual-based model of a single species 
+in continuous space in which
+birth, death, and establishment may all depend on local population density
+as well as on spatial location,
+allowing for stable populations through density-dependent feedback.
+
+Although it is often mathematically convenient to assume that individuals follow
+Brownian motion during their lifetime, 
+in our model, offspring
+are thrown off according to some 
+spatial distribution centred on the location of the parent.   
 This is particularly appropriate for modelling plant populations, in which
@@
 for example, the number of adults produced by a single parent is determined
-by the degree of crowding at the location of the parent. The novelty
+by the degree of crowding at the location of the parent. A novelty
 of the models that we introduce here is that, although we shall only
@@
 
-We shall consider different classes of scaling limits for our model; the first class consisting of
-(generalised) super-processes limits, and the second class where the limits are deterministic. In the
-superprocess setting, for our approach to work we measure the local population
-density at a point by integrating against a smooth test function, for example 
-a Gaussian density centred on that point.  
+We shall consider three different classes of scaling limits for our model.
+The first yields a class of (generalised) superprocesses in which coefficients 
+governing both the spatial motion and the branching components of the process can depend
+on local population density; the second is a corresponding class of deterministic
+non-local differential equations; and the third are classical PDEs.
+We measure local population density around a point by convolving with
+a smooth kernel $\rho(\cdot)$, which may differ
+for the two stages of reproduction. 
 When the limit is deterministic,
-we can simultaneously reduce the parameter in that Gaussian density so that,
-in the limit, the local population density is simply the population density 
-at that point. Nonetheless, we retain a signal of our two stage approach
-to modelling reproduction, and  
-in this way we recover a nonlinear partial differential equation. 
-This approach requires some technical conditions that we will verify in two important examples,
-the porous medium equation with a logistic growth term of the form 
-$$\partial_t \varphi = \Delta (\varphi^2)+\varphi(1-\varphi),$$
-and a wide class of semi-linear partial differential equations of the form 
-$$\partial_t \varphi = \Delta\varphi+ \varphi \left(G(\varphi)-H(\varphi)\right),$$
-which include the Fisher-KPP equation and the Allen-Cahn equation.
-
-The porous medium equation (PME)
-is a degenerate nonlinear diffusion equation that
-has been the subject of intensive study. We refer to~\cite{vazquez:2007} for 
-a comprehensive reference. The equation has also been studied with various
-forms of noise, see~\cite{barbu/daprato/roeckner:2016}, although not the 
-form of noise that will arise from the population dynamics below. 
-Deriving nonlinear diffusion equations as limits of weakly interacting 
-diffusions goes back at least to~\cite{mckean:1967}, and this 
-programme has been
-carried out for the PME and its generalisations. 
-The degeneracy of the PME
-results in some extra analytic
-challenges,~\cite{jourdain:2000}.
-% Recent work in this 
-% direction has been spurred on by applications
-% in mathematical finance, %where the porous medium arises 
-% in particular, in the study of weak limits of systems
-% of diffusions interacting through their 
-% rank,~\cite{dembo/shkolnikov/varadhan/zeitouni:2016, jourdain/reygner:2013}
-% and references therein.
-Our approach is different.
-We start from individual
-based population models, thus providing a microscopic mechanism that leads to 
-nonlinear diffusion.
-Other microscopic mechanisms have been proposed in the special case of the
-PME, see 
-e.g.~\cite{feng/iscoe/seppalainen:1997, oelschlaeger:1990}; ours
-is specifically motivated by biological considerations.
-
-Another novelty of our models stems from the use of lookdown construction to retain the dynamics of lines of descent in our population while passing to a scaling limit.
-The lookdown construction is first introduced in \cite{donnelly/kurtz:1996} to provide a mechanism to trace lineages while passing through a scaling limit for the Moran model.
-In more recent works, see~\cite{kurtz/rodrigues:2011, etheridge/kurtz:2018}, lookdown constructions are further applied into models of branching populations with spatial structures.
-In \S \ref{Sec: Lookdown Constructions}, we follow closely the techniques presented in these papers to impose lookdown constructions for our models which allow us to retain information about ancestry of individuals in the population as we pass to a large population limit.
-This in turn allows us to write down an explicit expression for the generator of the position of ancestral lineages with respect to the travelling wave fronts for populations modelled by a huge class of semi-linear partial differential equations, see Theorem \ref{teo:ancestral lineages}.
-This attempt is novel and we have provided the first ever rigorous proof to similar results on ancestral lineages.
-This result allows us to compare ancestral lineages of individuals sampled from the front of a population evolving according to the PME with logistic growth to those under the Fisher-KPP and Allen-Cahn equations.
+it is a (weak) solution of an equation of the form
+\begin{equation}
+	\label{general deterministic limit}
+        \partial_t \varphi_t(x)
+        =
+        r\left(x, \varphi_t \right)
+        \DG^* \left[
+            \varphi_t(\cdot)
+            \gamma\big( x, \varphi_t \big)
+        \right](x)
+        +
+        \varphi_t(x)
+        F\left(x, \varphi_t \right)
+        ,
+\end{equation}
+where $\DG^*$ is (the adjoint of) a strictly uniformly elliptic
+second order differential operator, typically
+the Laplacian.
+We shall be more specific about the parameters below.
+
+By replacing $\rho$ by
+$\rho^\epsilon(\cdot)=\rho(\cdot/\epsilon)/\epsilon^d$, 
+we can also scale the ``width'' of the 
+region over which we measure local population density. 
+When the population follows~(\ref{general deterministic limit}), 
+we can expect that taking a second limit by scaling the kernels appearing
+in $r$, $\gamma$, and $F$ in this way, so that
+in the limit as $\epsilon\to 0$
+interactions are pointwise, we should
+recover a nonlinear PDE.
+We verify that this is indeed the case in two important examples:
+a special case of the porous medium equation with a logistic growth term, in which we 
+retain a signal of our two stage approach to modelling in the nonlinear diffusion term
+and the limiting equation takes the form 
+\begin{equation}
+	\label{PME1}
+	\partial_t \varphi = \Delta (\varphi^2)+\varphi(1-\varphi);
+\end{equation}
+and a wide class of semi-linear PDEs of the form 
+\begin{equation}
+\label{semilinear PDE}
+\partial_t \varphi = \DG^*\varphi+ \varphi F(\varphi),
+\end{equation}
+which includes the Fisher-KPP equation and the Allen-Cahn equation.
+
+It is of interest to understand under what conditions we can replace the two-step limiting
+process described above by one in which we simultaneously scale the 
+kernels
+and the other parameters in 
+our population model to arrive at the PDE limit.
+This is mathematically much more challenging, but we establish such 
+one-step convergence in cases for which the limit is a classical 
+reaction diffusion equation of the form~(\ref{semilinear PDE}) with $\DG=\Delta$
+and $\rho_F$ is a Gaussian density. We allow a wide class of reaction terms, $F$, so
+that the Fisher-KPP equation emerges as a special case.
+
+We remark that such results on (one-step) convergence to reaction diffusion 
+equation limits have been
+achieved for a variety of interacting particle systems. The vast majority of these
+results concern spin systems \comment{REFs}. However,~\cite{flandoli/huang:2021} 
+obtain the Fisher-KPP equation (that is equation~(\ref{semilinear PDE}) with 
+$\DG=\Delta$ and $F(\varphi)=1-\varphi$) as a scaling limit of interacting diffusions in
+$\IR^d$. In that setting a major challenge (also apparent in our models), not
+faced in spin systems, is 
+the control of concentration of particles. We also note that the scaling 
+considered in~\cite{flandoli/huang:2021} is different from that considered
+below. In their language we consider only `moderate interactions', meaning that
+the number of individuals in the neighbourhood over which we measure local
+population density tends to infinity, whereas they also consider the situation in which
+that number remains finite; furthermore, whereas we shall consider a scaling in which 
+the reproduction mechanism is near-critical
+and look at large timescales,~\cite{flandoli/huang:2021}
+only scale the number of
+particles in the system and the size of the neighbourhood over which indivduals
+interact.
+
+The history of a natural population is often only accessible indirectly, 
+through patterns of genetic diversity that have been laid down; from 
+genetic data, one can try to infer the genealogical trees that relate 
+individuals in a sample from the population, and these have been shaped 
+by its history. It is therefore of interest
+to establish information about the distribution of genealogical trees 
+under our population model.
+To achieve this we exploit a lookdown construction. 
+Lookdown constructions were first introduced in~\cite{donnelly/kurtz:1996} to provide 
+a mechanism for retaining information about genealogical relationships between individuals
+sampled from a population evolving according to the Moran model when passing to the 
+infinite population limit.
+Since then, they have been extended to a huge range of models. Of particular
+relevance to our work here are the papers of~\cite{kurtz/rodrigues:2011} 
+and~\cite{etheridge/kurtz:2018}, in which
+lookdown constructions are provided for a wide variety of population models, including
+spatially structured branching processes.
+
+In general, even armed with a lookdown construction, calculation of relevant statistics 
+of the genealogy remains a difficult question. 
+However, in special
+circumstances, some progress can be made. As an illustration, 
+we shall consider a scenario that
+has received a great deal of attention in recent years, in which 
+a population is expanding into new territory as a travelling wave. 
+In Section~\ref{ancestral lineages for travelling waves}
+we shall consider three different (deterministic) wavefronts, moving 
+across $\IR^1$, and we shall explore the position of a single ancestral 
+lineage relative to that front.
+
+Most work has focused on models that caricature the classical Fisher-KPP equation with a 
+stochastic term, i.e.
+$$dw=\big(\Delta w +sw(1-w)\big)dt +\sqrt{\frac{\alpha(w)}{N}}W(dt,dx),$$
+where $W$ is space-time white noise, and $N$ is a measure of the 
+local population density. The coefficient
+$\alpha(w)$ is generally taken to be either
+$w$, corresponding to a superprocess limit, or $w(1-w)$ giving a 
+spatial analogue of a Wright-Fisher diffusion. 
+For very large $N$, and on suitable timescales, 
+starting with the pioneering work of~\cite{brunet/derrida/mueller/munier:2006},
+a considerable body of evidence has been amassed to underpin the
+conjecture that for this, and a wide class of 
+related models, 
+genealogies converge to a 
+Bolthausen-Sznitman coalescent. %, e.g.~\cite{brunet/derrida/mueller/munier:2007}.
+This reflects the fact that, for this equation, 
+ancestral lineages become trapped in 
+the wavefront, where the growth rate of the population is highest. 
+Once there, they will experience 
+rapid periods of coalescence 
+corresponding to significant proportions of individuals in the front being 
+descended from particularly reproductively successful ancestors.
+
+If one replaces the logistic growth term of the classical
+Fisher-KPP equation with a nonlinearity that reflects cooperative
+behaviour in the population, such as
+\begin{equation}
+	\label{Birzu nonlinearity}
+	wF(w)=w(1-w)(Cw-1),
+\end{equation}
+then, for sufficiently large $C$ (strong cooperation),
+the nature of the deterministic
+wave changes from ``pulled'' to ``pushed'', \cite{birzu/hallatschek/korolev:2017}.
+In that setting, the genealogies will be quite different
+from the Fisher-KPP case. \comment{Could refer to more recent Birzu et al paper here.}
+For example, \cite{etheridge/penington:2022}
+show that for a discrete space model corresponding to this 
+nonlinearity with $C>2$, after suitable scaling, the genealogy of a
+sample converges not to a Bolthausen-Sznitman coalescent, but to
+a Kingman coalescent. 
+The reason, roughly, is that ancestral lineages
+settle to a stationary distribution relative to the position of the 
+wavefront which puts very little weight close to the `tip' of the wave, so
+that when ancestral lineages meet
+it is typically at a location in which population density is
+high, where no single ancestor produces a disproportionately large number of 
+descendants in a short space of time.
+
+The shape of the wave is not determined solely by the reaction term.
 For example, as a result of the nonlinear diffusion, 
 for suitable initial conditions, the solution to the one-dimensional 
-porous medium equation with logistic growth converges to a travelling
+porous medium equation with logistic growth~(\ref{PME1}) converges to a travelling
 wave with a sharp cut-off; i.e., in contrast to the classical 
@@
 $c>0$, \cite{kamin/rosenau:2004}.
-
-\comment{Need a transition or otherwise to merge this with the above.}
-The history of a natural population is often only accessible indirectly 
-through patterns of genetic diversity that have been laid down. From 
-genetic data, one can try to infer the genealogical trees that relate 
-individuals in a sample from the population. It is therefore of interest
-to establish the distribution of genealogical trees relating individuals
-sampled from a population evolving according to any proposed mathematical
-model.
-
-In general this is an extremely difficult question. However, in special
-circumstances, some progress can be made. One of the settings that
-has received a great deal of attention in recent years is that in which 
-a population is expanding into new territory as a travelling wave. 
-Typically one considers a stationary wavefront moving across $\IR^1$, and
-most work has focussed on the classical Fisher-KPP equation with a 
-stochastic term, i.e.
-$$dw=\big(\Delta w +sw(1-w)\Big)dt +\sqrt{\frac{\alpha(w)}{N}}W(dt,dx),$$
-where $W$ is space-time white noise, and $N$ is a measure of the 
-local population density. The coefficient
-$\alpha(w)$ is generally taken to be either
-$w$, corresponding to a superprocess limit, or $w(1-w)$ giving a 
-spatial analogue of a Wright-Fisher diffusion. The first is 
-appropriate for modelling the range of an expanding population,
-the second for the spread of a selectively advantageous 
-mutation through an established (selectively neutral) population. 
-Because of the logistic control of the growth rate,
-individuals in the wavefront can have much greater reproductive success
-than those in the `bulk' of the expanding population. 
-Tracing backwards in time, individuals sampled
-from behind the wave are `caught' by the wave, upon which they become
-trapped in the wavefront. If the population density is very high, then over
-suitable timescales, the genealogical trees will be dominated by 
-periods of extremely rapid coalescence corresponding to a significant 
-proportion of the individuals in the front being descended from a particularly
-reproductively successful ancestor. For a surprisingly wide range of models, 
-it is believed that, for very large $N$ and on suitable timescales, 
-genealogies converge to a 
-Bolthausen-Sznitman coalescent, e.g.~\cite{brunet/derrida/mueller/munier:2007}. 
-On the other hand, if one replaces the logistic growth term of the classical
-Fisher-KPP equation with a nonlinearity that reflects cooperative
-behaviour in the population, such as
-$$wF(w)=w(1-w)(Cw-1),$$
-then, for sufficiently large $C$ (strong cooperation),
-the nature of the deterministic
-wave changes from `pulled' to `pushed', \cite{birzu/hallatschek/korolev:2017}.
-In that setting, the genealogies will also be quite different
-from the Fisher-KPP case. For example, \cite{etheridge/penington:2020}
-shows that for a discrete space model corresponding to this 
-nonlinearity with $C>4$, after suitable scaling, the genealogy of a
-sample converges not to a Bolthausen-Sznitman coalescent, but to
-a Kingman coalescent. 
-\todo[inline]{Is that condition $C>4$ correct?
-the paper with Sarah is done for the equation $\partial_t u = \Delta u + u(1-u)(2u-1+\alpha)$ and valid for $\alpha \in (0,1)$.
-Factorising we would get that equation would be $\partial_t u = \Delta u + (1-\alpha) u(1-u)(\frac{2}{1-\alpha}u-1)$.
-Supposing the $(1-\alpha)$ in front does not affect the result (which I suppose wouldn't) we get that $C= \frac{2}{1-\alpha}$ and so $\alpha \in (0,1)$ if and only if $C>2$ ...}
-The reason, roughly, is that ancestral lineages
-settle to a stationary distribution relative to the position of the 
-wavefront which puts very little weight close to the `tip' of the wave, so
-that when ancestral lineages meet,
-it is typically in a location where population density is
-high, where no single ancestor produces a disproportionately large number of 
-descendants in a short space of time.
-
 As a first step towards understanding what we should expect in models with
-nonlinear diffusion, we consider the position of an ancestral lineage
-relative to the wavefront in the deterministic models, and compare that 
-to what we see for a classical Fisher-KPP equation. 
-In~\S\ref{sec: wright-malecot}, we then indicate how to extend these ideas to 
-extract information about relatedness between two individuals in the 
-superprocess limit, at least when population intensity is very high, and
-we present some evidence to support the conjecture that genealogies 
-for populations expanding according to 
-our superprocess models with nonlinear diffusion
-can be very different from those under 
-the classical Fisher-KPP equation.
+nonlinear diffusion, one can ask about the position of an ancestral lineage
+relative to the wavefront in the deterministic models. In 
+Section~\ref{ancestral lineages for travelling waves}
+we shall see that in our framework, even with logistic growth, the nonlinear diffusion 
+corresponding to the porous medium equation results
+in a stationary distribution that is concentrated behind the wavefront, leading 
+us to conjecture that in the stochastic equation
+the cooperative behaviour captured by the nonlinear diffusion will also 
+result in a qualitatively different pattern of coalescence to that seen under the 
+stochastic Fisher-KPP equation. Indeed, we believe that it should be feasible to 
+show that in an appropriate limit one recovers a Kingman coalescent.
 
@@
 \paragraph{Structure of the paper}
-In the paper we study scaling limits of spatial populations,
+
+\comment{This paragraph to be rewritten last}
+
+In this paper we study scaling limits of spatial population models,
 obtaining convergence of both the population process
@@
 although strictly speaking it is a measure that may not have a density)
-as well as of lineages traced back through such a population.
-We retain linages through the rescaling process
+and of lineages traced back through such a population.
+We retain information about lineages as we pass to the scaling limit
 by means of a lookdown construction.
-First, in section~\ref{sec: Model and main results},
-we describe the model and the main theorems
+First, in Section~\ref{sec: Model and main results},
+we describe the model and the main results
 (Theorems~\ref{thm:nonlocal_convergence}, \ref{thm:local_convergence}, and~\ref{thm:lineages}).
@@
 namely, X Y and Z \comment{TODO}.
-In section \ref{sec:heuristics}, we provide heuristic explanations
+In Section~\ref{sec:heuristics}, we provide heuristic explanations
 of why the theorems ought to be true,
 and some key ideas behind them.
-In Section \ref{sec:lookdown} we define and discuss the lookdown process that retains the levels.
-This is followed by the technical proofs in section \ref{sec:proofs}.
+In Section \ref{sec:lookdown} we define and discuss the lookdown construction.
+This is followed by the technical proofs in Section~\ref{sec:proofs}.
+
+\comment{What's in the Appendix?}
 
@@
 
-The model we work with is a fairly general model
-of individuals living in continuous space.
-We start with a population of
-$\bigO(N)$ individuals per unit area distributed in $\IR^d$.
-For applications, $d=1$ or $d=2$, but our results apply more generally.
-The population will be distributed over a bounded region,
+Our model is one of individuals distributed across a continuous space 
+which we shall take to be $\IR^d$. 
+For applications, $d=1$ or $d=2$, but our main results apply more generally.
+At time zero, the population is distributed over a bounded region, with 
+$\bigO(N)$ individuals per unit area in that region,
 so the total number of individuals will also be $\bigO(N)$.
 The population changes in continuous time, and
-we describe the state of the population at time $t$ with a counting measure $X(t)$,
+we encode the state of the population at time $t$ by a counting measure $X(t)$,
 which assigns one unit of mass to the location of each individual.
@@
 each of which can depend on spatial location and local population density
-in a way we specify later.
-Each individual gives birth at rate $\gamma$ to a single offspring,
-and the offspring
-then disperses according to a kernel $q(\cdot)$ away from the location of the parent.
+in a way specified below.
+Each individual gives birth at rate $\gamma$ to a single (juvenile) offspring,
+which is dispersed according to a kernel $q(x, \cdot)$ away from the location $x$ of the parent.
 We assume that $q$ is the density of a multivariate Gaussian,
@@
 
-We aim to obtain universal behavior by taking the density, $N$, to infinity,
-and also scaling time by a factor of $\theta$,
-so that defining $\eta(t) = X(\theta t) / N$,
-the process $\{\eta(t)\}_{t \ge 0}$
+We aim to capture universal behaviour by passing to a scaling limit. Specifically, 
+we shall take the ``density'', $N$, to infinity,
+and also scale time by a factor of $\theta$,
+in such a way that defining $\eta^N(t) = X(\theta t) / N$,
+the process $\{\eta^N(t)\}_{t \ge 0}$
 will converge to a suitable measure-valued process
@@
 with the nature of the limit depending on how they tend to infinity together.
-Demographic rates in our model
-will be determined by local population density relative to $N$,
-so that population dynamics depend more naturally on $\eta$ (rather than $X$).
-However, to avoid confusion arising from the time scaling,
-we describe the model in terms of $X$ next.
-See Figure~\ref{fig:model_setup} for a conceptual depiction.
-
-\begin{figure}
-    \begin{center}
-        \includegraphics{figures/conceptual_figure}
-    \end{center}
-    \caption{
-        \comment{Perhaps we should have two panels, one with the PME example (currently panel A) and the other with FKPP;
-        right now panel B is not very helpful I think, so maybe should be omitted or added to so it better describes the whole process
-        (including dispersal and establishment).}
-        Conceptual figure of the model.
-        \textbf{(A)} Example plot of $\gamma$, $\mu$, and $F$
-        (calculated here with $r=1$) against scaled local population density.
-        In this example, both birth and death rates increase with population density,
-        but death increases faster,
-        and equilibrium occurs where they cross
-        (and hence where $F=0$).
-        \textbf{(B)} Cartoon of interaction ($\epsilon$) and dispersal ($\sigma$) distances.
-        \label{fig:model_setup}
-    }
-\end{figure}
+Evidently, we shall also need to scale the dispersal kernel if we are to obtain a
+nontrivial limit. We write $q_\theta(x,\cdot)$ for the density of the 
+multivariate Gaussian obtained by
+multiplying the mean and variance components corresponding to $q(x,\cdot)$ by $1/\theta$.
 
@@
 the counting measure with mass $1/N$ placed at the location of each individual.
-To measure local population density, we convolve the population measure with
-an ``interaction kernel'' -- which, for simplicity, we take to be Gaussian,
-and we write as
-$$
-    p_{\epsilon^2}(x) := \frac{1}{(2 \pi \epsilon^2)^{d/2}} e^{-\|x\|^2 / 2 \epsilon^2} ,
-$$
-for an ``interaction distance'' $\epsilon$.
 First consider birth rates, defined by
 a nonnegative function $\gamma(x, m) : \IR^d \times \IR_{\ge 0} \to \IR_{\ge 0}$
-of location $x$ and local population density $m$,
-and an interaction distance $\epsilon_\gamma > 0$.
-Local population density enters through the convolution of $X$ with $p_{\epsilon_\gamma^2}$,
-which we write as $\smooth{\gamma} X$.
-Then, the birth rate of an individual at location $x$ when the state of the population is $X$
-is $\gamma(x, \smooth{\gamma} X(x) / N)$.
-Similarly, the establishment probability of an offspring at location $x$ is
-is $r(x, \smooth{r} X(x) / N)$,
-where $r(x, m) : \IR^d \times \IR_{\ge 0} \to [0, 1]$
-and again $\smooth{r} X$ is the convolution of $p_{\epsilon_r^2}$ with $X$.
-Rather than defining a function $\mu(x, m)$ for the death rate,
-it turns out to be more convenient to parameterize in terms of the net reproductive rate,
-which we denote by $F(x, m)$,
-scaled by $1/\theta$
-so that the population density changes over a time scale of $\theta$.
-(This corresponds to a ``near-critical branching'' assumption.)
-Informally, we would like that
-$$
-    F = \theta (r \gamma - \mu) ,
-$$
-and to arrange this we define
+of location $x$ 
+and local population density $m$.
+Local population density is defined as the convolution of $X/N$ with 
+a smooth (non-negative, integrable) kernel $\rho_\gamma(\cdot)$.
+We write this convolution as $\smooth{\gamma} X/N$.
+Then, when the state of the population is $X$, an individual at location $x$ 
+gives birth to a single juvenile offspring at rate
+$\gamma(x, \smooth{\gamma} X(x) / N)$.
+Similarly, the establishment probability of an offspring at location $y$ is
+is $r(y, \smooth{r} X(y) / N)$,
+where $r(y, m) : \IR^d \times \IR_{\ge 0} \to [0, 1]$
+and again $\smooth{r} X$ is the convolution of 
+$X/N$ with the smooth kernel $\rho_r$.
+
+We shall write $\mu_\theta(x, X/N)$ for the per-capita death rate of mature individuals
+in the population.
+In order for the 
+population density to change over timescales of order $\theta$, we should like the net 
+per capita reproductive rate 
+to scale as $1/\theta$. 
+In classical models, in which $r$, $\gamma$, and $\mu$ are constant, 
+this quantity is simply $r\gamma -\mu$. 
+Here, because production of juveniles and their establishment are
+mediated by population density measured relative to different points, 
+the net reproductive rate will take a more complicated form. 
+In particular, the total rate of production of mature offspring by an individual at $x$ will be
+\[
+	\gamma\big(x,\smooth{\gamma}X(x)/N\big)\int r\big(y, \smooth{r}X(y)/N\big)q_{\theta}(x,dy).
+\]
+Nonetheless it will be convenient to define the death rate $\mu_\theta$ in terms of 
+its deviation from $r\gamma$. 
+To this end, we define
 the death rate of an individual at $x$ to be
 \begin{align} \label{eqn:mu_defn}
-    \mu
+    \mu_\theta(x)
     =
@@
 \end{align}
-where again $F(x, m) : \IR^d \times \IR_{\ge 0} \to \IR_{\ge 0}$
-and $\kernel_F = p_{\epsilon_F^2}$.
-
-In summary, each of the three demographic parameters depend on local density measured
-with a Gaussian kernel with possibly different scales:
-for birth over a scale of $\epsilon_\gamma$,
-for establishment over a scale of $\epsilon_r$,
-and for net reproductive rate over a scale of $\epsilon_F$.
-Note that death rate depends in principle on population densities at three different scales,
-so that we could write $\mu = \mu(x, \smooth{\gamma} X(x) / N, \smooth{r} X(x) / N, \smooth{F} X(x) / N)$.
-It might seem like
-we have introduced unnecessary complexity
-with these three different spatial scales on which interactions occur.
-However,
-it will turn out to be useful in the proofs to have $\epsilon_r < \epsilon_\gamma$,
-although in the limit they can be taken equal to each other
-(and $\epsilon_F$ is unconstrained),
-so informally we think of local density as being determined on a scale of $\epsilon$.
+where $F(x, m) : \IR^d \times \IR_{\ge 0} \to \IR$ and
+$\rho_F$ is again a smooth kernel.
+
+Note that each of the three demographic parameters $r$, $\gamma$, $F$,
+depends on local density,
+measured by convolution with a smooth kernel. Each of the three kernels can be different.
+As a result, death rate depends (in principle) on population densities measured in 
+three different ways, 
+so that we could write 
+$\mu_\theta(x) = \mu_\theta(x, \smooth{\gamma} X(x) / N, \smooth{r} X(x) / N, \smooth{F} X(x) / N)$.
+This may seem unnecessarily complex.
+However, not only is it natural from a 
+biological perspective, it also turns out to be necessary if we are
+to capture nontrivial examples in our scaling results.
 
@@
 Furthermore, individuals do not move during their lifetime,
-and the age of an individual does not affect their fecundity or death rates.
+and the age of an individual does not affect its fecundity or death rate.
 Finally, there is no notion of mating
@@
 
-We next summarize the dynamics of the rescaled model $\eta(t) = X(\theta t)/N$,
-and state some assumptions on the parameters.
-The process takes values in the space of finite measures on $\IR^d$,
-which we write as $\measures$.
-
-\plr{TODO: check the conditions below (esp on the derivatives of $F$)}
-
-\begin{definition}[Model parameterization and assumptions]
-\label{def:model_setup}
-Suppose $\gamma(x, m)$, $r(x, m)$, and $F(x, m)$
-are uniformly continuous functions
-from $\IR^d \times \IR_{\ge 0}$ to $\IR$.
-Furthermore, suppose $r$ takes values in $[0, 1]$
-and has uniformly bounded second derivatives,
-that $\gamma(x,m) \ge 0$,
-and that $m^2 \gamma(x, m)$ is uniformly bounded.
-Fix positive values $\theta$, $\epsilon_r$, $\epsilon_\gamma$, and $\epsilon_F$,
-with $\epsilon_r < \epsilon_\gamma$.
-Suppose $F(x,m)$ is bounded above
-with uniformly bounded first and second derivatives in $m$,
-that $\sup_x F(x,m)$ is finite for all $m$,
-and define
-\begin{align} \label{eqn:mu_defn}
-    \mu(x, \eta)
-    =
-    \max\left(0, 
-        r(x, \smooth{r} \eta(x))
-        \gamma(\smooth{\gamma} \eta(x))
-        - \frac{1}{\theta}
-        F(x, \smooth{F} \eta(x)) 
-    \right) .
-\end{align}
-Although the models will make sense without this requirement,
-for the purposes of convergence we will also require that
-$\theta > 2 \sup_x \sup_{y : \|y\| = 1} y^T \covq(x) y/(\epsilon_\gamma^2 - \epsilon_r^2)$.
-\end{definition}
-
-Expressions like $\gamma(x, \smooth{\gamma} \eta(x))$ will appear often in the paper.
-To make formula more readable, we overload notation to define
+For each $N$ and $\theta$, the rescaled process
+$\big(\eta^N_t\big)_{t\geq 0} := \big(X(\theta t)/N\big)_{t\geq 0}$, 
+takes values in the space of c\`adl\`ag paths in
+$\measures$ (the space of finite measures on $\IR^d$
+endowed with the weak topology).
+
+\begin{notation}
+Expressions like $\gamma(x, \smooth{\gamma} \eta(x))$ will appear repeatedly in what follows.
+To make formulae more readable, we overload notation to define
 $$
@@
 and similarly write $r(x, \eta)$ for $r(x, \smooth{r} \eta(x))$
-and $\mu(x, \eta)$ for the expression of equation \eqref{eqn:mu_defn}.
+and $\mu_\theta(x, \eta)$ for the expression of equation \eqref{eqn:mu_defn}.
 When convenient, we may also suppress the arguments completely,
-writing simply $\gamma$, $\mu$, and $r$ for these quantities.
-
-For each value of $N$ and $\theta$,
-the process $\left(\eta^N_t \right)_{t \ge 0}$
-is the continuous-time measure-valued Markov process described above
-with birth rates, establishment probabilities, and death rates
-determined as follows.
-When the state of the process is $\eta \in \measures$,
-offspring of mass $1/N$ are produced at location $x$
-with rate $\theta \gamma(x, \eta) N \eta(dx)$
-and adults die at location $x$ with rate $\theta \mu(x, \eta) N \eta(dx)$,
-(i.e., at rates $\theta \gamma$ and $\theta \mu$ per capita respectively).
-Each offspring disperses to a location offset from the parent's location
+writing simply $\gamma$, $r$, and $\mu_\theta$ for these quantities.
+\end{notation}
+
+\begin{terminology*}
+In our prelimiting model,
+the population is represented by a point measure in which each
+individual is assigned a mass $1/N$. We use the term ``population density'' for
+this process, as it is supposed to measure population size relative to a 
+nominal occupancy of $N$ individuals per unit area. There is no implication 
+that the measure representing the population is absolutely continuous with
+respect to Lebesgue measure; indeed in the prelimit it is certainly not.
+\end{terminology*}
+
+In summary, at each time $t$, $\eta^N_t$ is purely atomic, consisting of atoms of mass $1/N$.
+At instantaneous rate $\theta \gamma(x, \eta^N_t) N \eta^N_t(dx)$ an offspring of mass $1/N$ is 
+produced at location $x$; it disperses to 
+a location $y$ offset from $x$
 by an independent Gaussian with mean $\meanq(x) / \theta$
-and covariance matrix $\covq(x) / \theta$;
-an offspring at $x$ establishes instantaneously
-with probability $r(x, \eta)$, or else dies.
-
-We have just effectively defined the process, but for future use,
-we will now give a formal definition as a solution to a martingale problem.
-
+and covariance matrix $\covq(x) / \theta$, and once there establishes instantaneously
+with probability $r(y, \eta^N_t)$, or else dies. 
+At instantaneous rate $\theta \mu_\theta(x, \eta^N_t) N \eta^N_t(dx)$ an individual at location 
+$x$ dies.
+Note that the process 
+$\left(\eta^N_t\right)_{t\ge 0}$, which
+records numbers and locations of adult individuals, is just a scaled spatial birth and 
+death process. If, for example, we insist that $\gamma(x,m)$ is bounded, then 
+existence (and in particular non-explosion) is guaranteed by comparison with
+a pure birth process. We do not dwell on this, as we shall require more stringent conditions
+if we are to pass to the limit as $\theta$ and $N$ tend to infinity.
+
+It is convenient to characterise the process as a solution to a martingale problem.
+We write $C_b^\infty(\IR^d)$ for the space of bounded smooth functions on $\IR^d$, and, where
+convenient, we
+write $\langle f, \eta \rangle = \int_{\IR^d} f(x) \eta(dx)$.
 \begin{definition}[Martingale Problem Characterisation]
-    \label{defn:mgale_construction},
-For each value of $N$ and $\theta = \theta(N)$,
-we define $(\eta^N_t)_{t \geq 0}$ to be the solution to the Martingale Problem,
-with initial condition $\eta^N_0 \in \measures$,
-such that for all smooth functions $f \in C^{\infty}_{0}(\IR^d)$,
-writing $\langle f, \eta \rangle = \int_{\IR^d} f(x) \eta(dx)$
-and $q_\theta(x, dy)$ as the Gaussian kernel
+    \label{defn:mgale_construction}
+	For each value of $N$ and $\theta$, and each purely atomic 
+$\eta_0^N\in\measures$ with atoms of mass $1/N$,
+$(\eta^N_t)_{t \geq 0}$ is the (scaled) empirical measure of a birth-death 
+process with c\`adl\`ag paths in $\measures$ for which,
+for all $f \in C^{\infty}_{b}(\IR^d)$,
+writing $q_\theta(x, dy)$ for the Gaussian kernel
 with mean $x + \meanq(x)/\theta$ and covariance $\covq(x) / \theta$,
@@
         \times \gamma(x, \eta^N_{s}) \eta^N_{s}(dx)
-\\ & \qquad \qquad {}
+%\\ & \qquad \qquad {}
     + \int f(x) F(x, \eta^N_{s}) \eta^N_{s}(dx)
@@
 \end{equation}
-is a martingale with quadratic variation
+is a martingale (with respect to the natural filtration), 
+with quadratic variation
     \begin{equation} \label{eqn:prelimit_martingale_variation}
 \begin{aligned} \relax
-[ M^N_t(f)] =& 
+[ M^N(f)]_t =& 
 \frac{\theta}{N} \int_{0}^{t}\bigg\{
-    \langle \gamma(x, \eta^N_{s})
-        \int f^2(y)r(y, \eta^N_{s}) q_\theta(x,dy) 
-    , \eta^N_{s}(dx) \rangle \\
+    \Big\langle \gamma(x, \eta^N_{s})
+        \int f^2(z)r(z, \eta^N_{s}) q_\theta(x,dz) 
+    , \eta^N_{s}(dx) \Big\rangle \\
 & \qquad \qquad {}
-    + \langle \mu(x, \eta^N_{s}) f^2(x) 
-    , \eta^N_{s}(dx)\rangle
+    + \Big\langle \mu_\theta(x, \eta^N_{s}) f^2(x) 
+    , \eta^N_{s}(dx)\Big\rangle
     \bigg\}ds. 
@@
 \end{definition}
-
-Note that
-since individuals are produced at rate $N \gamma \eta$ but have mass $1/N$ each,
+The form of~(\ref{eqn:eta_martingale}) and~(\ref{eqn:prelimit_martingale_variation})
+is explained in Section~\ref{sec:heuristics}.
+Note that since individuals are produced at rate $N \gamma \eta$, but each
+has mass $1/N$,
 these factors of $N$ cancel in~\eqref{eqn:eta_martingale}. 
-Since we are taking a diffusion limit,
-we will have use for the following notation:
+Under our scaling, $N$ and $\theta=\theta(N)$ will tend to infinity in such a 
+way that $\alpha:=\lim_{N\to\infty}\theta(N)/N$ exists. From the 
+expression~(\ref{eqn:prelimit_martingale_variation}) it is easy to guess that 
+whether the limit points will be deterministic or stochastic processes 
+is determined by whether $\alpha$ is zero or nonzero.
+%c.f.~Section~\ref{sec:heuristics}.
+
+%In order to specify the assumptions that we shall need on the parameters of our model
+%if we are to pass to a scaling limit, 
+It is convenient to record some notation for the 
+generator of the diffusion 
+limit of a random walk with jump distribution determined by $q_\theta(x,dy)$.
 
@@
     \label{def:dispersal_generator}
-    Recall that we have defined the dispersal kernel,
+    We define the dispersal kernel,
     $q_\theta(x, dy)$,
@@
     We will also denote the adjoint of $\DG$ by
-    \begin{align*}
+    \begin{align}
+	    \nonumber
     \DG^* f(x)
@@
         \\
+	    \label{drift in adjoint}
         &=
-        \text{TODO} .
-    \end{align*}
+        \sum_{ij} \partial_{x_i} \partial_{x_j} (\covq(x)_{ij} f(x))
+	    -\nabla f(x)\cdot \meanq(x)-f(x)\nabla\cdot\meanq(x).
+        %\text{TODO} .
+    \end{align}
 \end{definition}
 
-\paragraph{Remark:}
+\begin{remark}
+\label{ancestral lineages: first guess}
 An equivalent way to describe the model would be to say that
@@
 is biased towards regions of higher establishment probability.
-For comparison to future results,
+For comparison with future results,
 it is interesting to write down the limiting generator:
-\begin{align*}
+\begin{align}
+	\label{weighted dispersal}
     \lim_{\theta \to \infty}
@@
     } .
-\end{align*}
-In the simplest case of unbiased, isotropic dispersal,
-$\meanq = 0$ and $\covq = I$, so $\DG = \Delta$,
-and this is equal to
+\end{align}
+In the simplest case of unbiased isotropic dispersal
+(i.e.,~$\meanq = 0$ and $\covq = I$), $\DG = \Delta$,
+and~(\ref{weighted dispersal}) is equal to
 \begin{align*}
@@
 \end{align*}
-One might guess that the spatial motion described by following a lineage of successful individuals back through time
-would be described by this generator in the limit.
-However, we will see that following a lineage back through the population
-has a different behavior yet again.
+One might guess that the spatial motion described by following  
+the ancestral lineage of an individual 
+back through time
+would be described (in the limit) by the adjoint of this generator.
+However, we will see in Section~\ref{sec:ancestral lineages}
+that this is not in fact the case.
+\end{remark}
+In order to pass to a scaling limit, we will need to impose some 
+conditions on the parameters of our model.
+\begin{assumptions}%[Assumptions]
+\label{def:model_setup}
+We shall make the following assumptions on the parameters of our model.
+
+{\bf Dispersal generator:}
+We assume that
+\begin{enumerate}
+    \item $\meanq(x)$, $\covq(x)$ are uniformly bounded in each component;
+    \item $\meanq(x)$ and $\covq(x)$ are $\alpha$-H\"older continuous in each component, 
+	    for some $\alpha \in (0,1]$;
+    \item the operator $\DG$ is uniformly strictly elliptic.
+\end{enumerate}
+
+{\bf Reproduction parameters:}
+
+We assume that 
+\begin{enumerate}
+\item The function $F(x,m)$ satisfies 
+\begin{enumerate}
+\item $F(x,m)$ is locally Lipschitz in $m$;
+\item $F(x,m)$ is uniformly bounded above (but not necessarily below);
+\item for each fixed $m$, $\sup_{x\in\IR^d}\sup_{k\leq m}|F(x,k)|<\infty$;
+\end{enumerate}
+\item The functions $r(x,m)$, $\gamma(x,m)$ have bounded first and second 
+derivatives in both arguments;
+\item $\gamma(x,m)$ is uniformly bounded above;
+\item Either
+\begin{enumerate}
+\item
+\label{control through r} 
+$|\partial_{x_i}r(x,\smooth{r}\eta(x)|$ and 
+$|\partial_{x_ix_j}r(x,\smooth{r}\eta(x)|$
+are uniformly bounded for $x\in\IR^d$, $\eta\in\measures$;
+\item 
+\label{control through gamma}
+or, $m^2\gamma(x,m)$ is uniformly bounded and there exists $C<\infty$
+such that for $\theta$ sufficiently large, and all $x\in\IR^d$, $\eta\in\measures$,
+\[
+\theta\int\big(\smooth{r}\eta(y)-\smooth{r}\eta(x)\big)q_\theta(x,dy)\leq C\smooth{\gamma}\eta(x),
+\]
+and
+\[\theta\int\big(\smooth{r}\eta(y)-\smooth{r}\eta(x)\big)^2q_\theta(x,dy)
+\leq C(\smooth{\gamma}\eta(x))^2.
+\]
+\end{enumerate} 
+\end{enumerate}
+
+To keep expressions manageable, we shall also assume that 
+\[
+\mu_\theta(x) = r(x, \smooth{r} X(x) / N) \gamma(x, \smooth{\gamma} X(x) / N)
+        - \frac{1}{\theta} F(x, \smooth{F} X(x) / N),
+\]
+that is, this expression is non-negative so that there is no need to take the maximum
+with zero in~(\ref{eqn:mu_defn}).
+\end{assumptions}
+
+The purpose of the conditions that we have placed on the reproduction parameters is to 
+ensure that the net per capita reproduction rate is order $1/\theta$. As remarked above, 
+because of the non-local reproduction mechanism, it no longer suffices to assume that 
+$r(x,\smooth{r}\eta(x))\gamma(x, \smooth{\gamma}\eta(x))-\mu_\theta(x)$ is of order 
+$1/\theta$. The conditions that we have imposed are to ensure that the difference 
+between the establishment probability of a juvenile born of a parent at $x$ and dispersed
+to a position $y$, determined by $q_{\theta}(x,dy)$, and its establishment probability had
+it remained at $x$ are also order $1/\theta$.
+
+If $r(x,m)$ is independent of $m$, then the conditions are easy to 
+satisfy; they just require some regularity of $r$ as a function of $x$. 
+Condition~\ref{control through r} is satisfied if 
+$\|\nabla\rho_r\|\leq C\rho_r$ 
+and $m\partial_mr(x,m)$, $m^2\partial_{mm}r(x,m)$ are bounded.
+This will be satsified if $\rho_r$ decays 
+no faster than
+exponentially.
+On the other hand, it might, for example, seem more natural to take $\rho_r$ to be a Gaussian 
+density with parameter $\sigma_r$, say. Then, as we check in Lemma~\ref{old 6.1}, 
+Condition~\ref{control through gamma} is satisfied if $\rho_\gamma$ is also
+Gaussian with parameter $\sigma_\gamma$ and $\sigma_\gamma>\sigma_r$. For large enough
+$\theta$, this condition guarantees that 
+$\epsilon_r+1/\theta <\epsilon_\gamma$, so that the establishment probability of a juvenile
+is controlled by individuals that are already `felt' by the fecundity kernel $\rho_\gamma$
+at the location of their parent.
 
 % % % % % % % % % % % % % % %
-\subsection{Scaling limits of the population density process}
+\subsection{Scaling limits of the population process}
 
@@
 Is the limiting process deterministic or a (generalized) superprocess?
-And, are interactions local in the limit or not?
-Below we have results for deterministic limits with local and nonlocal interactions,
+And, are interactions pointwise in the limit or nonlocal?
+Below we have results for deterministic limits with pointwise and nonlocal interactions,
 and for superprocess limits with nonlocal interactions.
 See Figure \ref{fig:super_vs_det_2d} for illustrative simulations.
-We suspect that limits are possible in the remaining (local, superprocess) case
-only in $d=1$, but do not discuss the case further.
 
@@
     \begin{center}
-        \includegraphics{figures/ex1a/fkpp_123.locations}
-        \includegraphics{figures/ex1b/fkpp_123.locations}
+        %\includegraphics{figures/ex1a/fkpp_123.locations}
+        %\includegraphics{figures/ex1b/fkpp_123.locations}
     \end{center}
     \caption{
-        Snapshots of two simulations, with small $\theta$ (left) and large $\theta$ (right).
-        Simulations are run with a FKPP-like parameterization:
+        Snapshots of two simulations, with small $\alpha=\theta/N$ (left) and large 
+	$\alpha =\theta/N$ (right).
+        Simulations are run with a Fisher-KPP-like parameterization:
         birth and establishment are constant, while death increases linearly with density,
         at slope $1/\theta$.
-        Left: $\theta=1$. Right: $\theta=100$.
+        Left: $\alpha=0.1$. Right: $\alpha=10$.
         Other parameters were the same:
@@
 
+\paragraph{Scaling limits with nonlocal interactions}
+
+Recall that the process $(\eta_t^N)_{t\geq 0}$ takes its values in the space
+${\cal D}([0,\infty),\measures)$ of c\`adl\`ag
+paths on $\measures$. We endow $\measures$ with the topology of weak convergence
+and 
+${\cal D}([0,\infty),\measures)$ with the Skorohod topology.
+A sequence of processes taking values in 
+${\cal D}([0,\infty),\measures)$ is said to be tight if the corresponding
+sequence of distributions
+is tight, so that any infinite sequence has a weakly convergent subsequence.
+Our first result establishes tightness of our rescaled population processes in 
+the case in which interactions remain nonlocal under the scaling, and 
+characterises limit points as solutions to a martingale problem.
+
 \begin{theorem} \label{thm:nonlocal_convergence}
     Let $(\eta^N_t)_{t \geq 0}$
-    be as defined in Definition \ref{def:model_setup}
-    and assume that as $N \to \infty$, also $\theta \to \infty$
-    in such a way that $\theta/N \to \alpha$.
-    (However, interaction distances $\epsilon_r$, $\epsilon_\gamma$, and $\epsilon_F$
-    remain constant.)
-    The sequence of stochastic processes
-    $(\eta^N_t)_{t \geq 0}$
-    converges along subsequences in distribution as $N \to \infty$
-    to a measure-valued process $(\eta_t)_{t \geq 0}$
-    which satisfies that, for every $f \in C^\infty_0(\IR^d)$,
+    be as defined in Definition~\ref{defn:mgale_construction}
+	and assume that as $N \to \infty$, $\theta(N) \to \infty$
+	in such a way that $\theta(N)/N \to \alpha$.
+    (However, the kernels $\rho_r$, $\rho_\gamma$, and $\rho_F$
+    remain fixed.) 
+Suppose that Assumptions~\ref{def:model_setup} hold and, 
+further, that $\{\eta_0^N\}_{N\geq 1}$ is tight 
+in $\measures$.
+    Then the sequence of processes
+    $(\eta^N_t)_{t \geq 0}$ is tight, and for any limit point
+    $(\eta_t)_{t \geq 0}$, for every $f \in C^\infty_b(\IR^d)$,
     \begin{align} \label{eqn:limiting_mgale_problem}
         \begin{split}
-        M_t
+        M_t(f)
             &:=
@@
                 \right)(x)
-                \\ &\qquad \qquad \qquad {}
+                %\\ &\qquad \qquad \qquad {}
                 +
@@
                 \eta_{s}(dx)
-            \big\rangle ds,
+            \big\rangle ds
         \end{split}
@@
     \begin{align} \label{eqn:limiting_mgale_variation}
-        [ M ]_t
+        [ M(f) ]_t
         =
@@
         \big\langle
-            \left(\gamma\left( x, \eta_{s} \right)
-            r\left(x, \eta_{s} \right) + \mu\left(x, \eta_{s} \right)\right)
+            %\left(
+	    2\gamma\left( x, \eta_{s} \right)
+            r\left(x, \eta_{s} \right)% + \mu\left(x, \eta_{s} \right)\right)
             f^2(x),
@@
     \end{align}
-    In other words, the limit is a measure-valued process with non-local interactions.
     Furthermore, if $\alpha = 0$ the limit is deterministic.
@@
 Recall when interpreting~\eqref{eqn:limiting_mgale_problem}
-that for instance $r(x, \eta_s) = r(x, \smooth{r} \eta_s(x))$,
+that, for instance, $r(x, \eta_s) = r(x, \smooth{r} \eta_s(x))$,
 and so $\DG(fr)(x) = \DG(f(\cdot) r(\cdot, \smooth{r} \eta_s(\cdot)))(x)$.
 
-Theorem \ref{thm:nonlocal_convergence} provided convergence along subsequences;
-i.e., for any sequence of values of $N$
-there is a subsequence along which $\eta^N$ converges.
-However, if the limiting process is unique then the convergence is unqualified.
-In the deterministic case, we have convergence to a nonlocal PDE.
-
-\begin{corollary}[Superprocess limits] \label{cor:superprocess_uniqueness}
+Theorem \ref{thm:nonlocal_convergence} provides tightness of the
+rescaled processes. If the limit points are unique, then this
+is enough to guarantee convergence.
+
+\begin{corollary} \label{cor:superprocess_uniqueness}
     Under the assumptions of Theorem~\ref{thm:nonlocal_convergence},
@@
     has a unique solution,
-    then $(\eta^N_t)_{t \ge 0}$ converges to that solution
+    then $(\eta^N_t)_{t \ge 0}$ converges weakly
+to that solution
     as $N \to \infty$.
-    \comment{
-        Is this what we want to say here? Could be said better.
-        TODO: see what Dawson \& Li say about uniqueness
-        so we have at least some conditions under which this happens.
-    }
 \end{corollary}
-
-\comment{
-    TODO: put in what Kurtz \& Xiong have to say about uniqueness,
-along the lines of a note saying ``For some conditions under which the limit is known to be unique,
-see Kurtz \& Xiong and/or Dawson \& Li.''
-}
-
-Our results will show that in deterministic limits ``$\eta_t$ solves a PDE'',
-but since $\eta_t$ is a measure for which we don't always know there exists a density,
-we need to formalize the weak sense in which it solves the PDE.
-The notation in the following definition
-is written to suggest the case in which $\eta_t(dx)$ has a density $\varphi_t(x)$.
-
+When $\alpha>0$, the limit points can be thought of as interacting superprocesses. For
+example, when $r$ and $\gamma$ are constant, and 
+$F(x,\eta_s)=1-\smooth{F} \eta_s(x)$,
+we recover the superprocess with nonlinear death rates corresponding to logistic growth.
+We are not aware of a general result to determine when we will have uniqueness of 
+solutions to the martingale problem of Theorem~\ref{thm:nonlocal_convergence}
+when $\alpha>0$.
+However, the Dawson Girsanov transform tells us that we have uniqueness in this special 
+case of the superprocess with nonlinear death rates, and 
+Perkins stochastic calculus (and its adaptation to a 
+lookdown setting) provides uniqueness for cases with interactions in the spatial component of
+the superprocess. We refer 
+to~\cite{dawson:1993, perkins:1992}, and \cite{donnelly/kurtz:1999} 
+for approaches to showing that the martingale problem is well-posed in the case $\alpha>0$.
+
+Recall the following notion of solution to a PDE.
 \begin{definition}[Weak solutions]
     \label{defn:weak_solutions}
-    We say that $(\eta_t)_{t \ge 0}$, with $\eta_t \in \measures$
+    We say that $(\eta_t)_{t \ge 0}$, with $\eta_t \in \measures$,
     is a \emph{weak solution} to the PDE
-    $$
+   \[ 
 	\dot \varphi = r \DG^*(\gamma \varphi) + \varphi F
-    $$
-    if for all $f \in C_0^\infty(\IR^d)$,
-    $$
+    \]
+	(where $r$, $\gamma$ and $F$ can all be functions of $\varphi$)
+    if, for all $f \in C_b^\infty(\IR^d)$,
+    \[
         \frac{d}{dt} \langle f, \eta_t \rangle
@@
         \rangle .
-    $$
-    \comment{Write this out with $(x)$'s?}
+    \]
 \end{definition}
-
-\begin{corollary}[Deterministic limits]
-    \label{cor:nonlocal_pde_limits}
-    Under the assumptions of Theorem~\ref{thm:nonlocal_convergence},
-    if the limit is deterministic (i.e., $N^{-1}\theta \to \alpha = 0$),
-    then any limit $\eta_t$ is a weak solution to the nonlocal partial differential equation
+the notation $\varphi$ is meant to be suggestive of a density.
+Because Theorem~\ref{thm:nonlocal_convergence} only tells us about 
+weak convergence, in the case $\alpha=0$ we can only deduce that 
+any limit point $\eta_t$ is a weak solution to the nonlocal PDE
     \begin{equation} \label{eqn:nonlocal_pde}
@@
         F\left(x, \smooth{F} \varphi_t(x) \right)
-        ,
-    \end{equation}
-    in the sense of Definition~\ref{defn:weak_solutions}.
-    If equation \eqref{eqn:nonlocal_pde} has a unique solution,
-    then $(\eta^N_t)_{t \ge 0}$ converges to that solution.
-\end{corollary}
-
-\comment{TODO: Tom has conditions, referring to \citet{KURTZ1999103}, (coefficient are Lipschitz?) under which
-    the solution to \eqref{eqn:nonlocal_pdf} is unique and has a density (Thm 2.1 in DDMOT);
-    insert those here (as a Corollary or Proposition)}
-
-Informally, equation \eqref{eqn:nonlocal_pde} is the PDE of Definition~\ref{defn:weak_solutions},
-where $\DG$ is an elliptic second order differential operator,
-and the coefficients $r$, $\gamma$, and $F$
-at $x$ depend nonlocally on $\varphi$
-(i.e., through a smoothed version of $\varphi$).
-To see why it is $\DG^*$ and not $\DG$ that appears in this equation,
-consider the case where dispersal has a mean drift to the right,
-so that the drift term in $\DG$ is $d/dx$.
-Then, the population density at a location with positive slope
-will tend to \emph{decrease}, i.e., proportional to $-d/dx$,
-because the density at a location is determined by the offspring that disperse \emph{to}
-that location, not away from it.
-Furthermore, if dispersal tends to move offspring away from a region
-(i.e., if divergence $\grad \cdot \meanq > 0$)
-this will tend to decrease the local density.
+        .
+    \end{equation}
+
+\citet{KURTZ1999103} provides general conditions under which we
+have existence and uniqueness of solutions to~(\ref{eqn:nonlocal_pde}) which
+have an $L^2$-density with respect to Lebesgue measure. 
+Recall that the Wasserstein metric, defined by 
+\[\rho (\nu_1,\nu_2)=\sup\Big\{\Big|\int fd\nu_1-\int fd\nu_2\Big|:\sup_x|f(x
+)|\leq 1,|f(x)-f(y)|\leq \|x-y\|\Big\},\]
+determines the topology of weak convergence on $\measures$.
+
+We write 
+$\gamma(x,\eta)C(x)=J(x,\eta)J(x,\eta)^T$, and 
+$\beta(x,\eta)=\gamma(x,\eta)\big(\meanq(x)+2C(x)\nabla\log r(x,\eta)\big)$.
+If $J$, $\beta$, and $F$ are bounded and Lipschitz in the sense 
+that
+\begin{equation}
+\label{lipschitz for kurtz xiong}
+|J (x_1, \nu_1)-J (x_2, \nu_2)|,|\beta (x_1,\nu_1)-\beta 
+	(x_2,\nu_2)|, |F(x_1,\nu_1)-F(x_2,\nu_2)|
+	%,|b(x_1,\nu_1)-b(x_2,\nu_2)|
+	\leq C(\|x_1-x_2\|+\rho (\nu_ 1,\nu_2))
+\end{equation}
+for some $C>0$,   
+the methods of \cite{KURTZ1999103} show that %under the conditions
+%of Theorem~\ref{thm:kurtzxiong}, 
+if the initial condition $\eta_0$ for our 
+population process has
+an $L^2$ density, then so does $\eta_t$ for $t>0$. 
+Although the necessary estimates (for which we refer to the original paper)
+are highly nontrivial, 
+the idea of the proof is simple. Take a solution to the
+equation and use it to calculate the coefficients $r$, $\gamma$ and $F$ that depend
+on local population density. Then $\eta$ solves the 
+{\em linear} equation obtained by regarding those values of $r$, $\gamma$ and $F$ as given.
+It remains to prove that the solution to the linear equation has a density
+which is achieved by obtaining
+$L^2$ bounds on its convolution with the heat semigroup at time $\delta$ and letting 
+$\delta\to 0$.
+We also have the following uniqueness result.
+\begin{theorem}[Special case of \cite{KURTZ1999103}, Theorem~3.5]
+	\label{thm:kurtzxiong}
+Suppose  $J$, $\beta$, and $F$ are bounded and Lipschitz in the sense 
+of~(\ref{lipschitz for kurtz xiong}).
+%that
+%\[|J (x_1, \nu_1)-J (x_2, \nu_2)|,|\beta (x_1,\nu_1)-\beta 
+%	(x_2,\nu_2)|, |F(x_1,\nu_1)-F(x_2,\nu_2)|
+	%,|b(x_1,\nu_1)-b(x_2,\nu_2)|
+%	\leq C(\|x_1-x_2\|+\rho (\nu_ 1,\nu_2))\]
+%for some $C>0$.  
+%
+If $\eta_0$ has an $L^2({\mathbb R}^d)$-density, then there 
+exists a unique $L^2({\mathbb R}^d)$-valued  
+	solution of (\ref{eqn:nonlocal_pde}) in the sense of 
+	Definition~\ref{defn:weak_solutions}.
+\end{theorem}
+\begin{remark}
+\cite{KURTZ1999103} considers an infinite system of stochastic differential equations
+for the locations and weights of a collection of particles that interact through their 
+weighted empirical measure, which is shown to be the unique solution to a stochastic
+	PDE. As we shall see through our lookdown representation in 
+Section~\ref{sec:lookdown}, the
+	solution to our
+	deterministic equation can be seen as the empirical measure of a 
+	countable number of particles which, in the notation above, evolve according
+	to 
+	\[X(t)=X(0)+\int_0^t\beta\big(X(s), \eta_s\big)ds
++\int_0^tJ\big(X(s), \eta_s\big)dW(s)\]
+	(with an independent Brownian motion $W$ for each particle).
+\end{remark}
+
+To understand the form of equation~(\ref{eqn:nonlocal_pde}) a little better, 
+and, in particular, why we see $\DG^*$ rather than $\DG$ in the equation for the 
+limiting population density, we consider the two terms that contribute to the drift in our 
+expression~(\ref{drift in adjoint})
+for $\DG^*$. First consider a special case in which dispersal has a mean drift 
+to the right, so that the drift term in $\DG$ is $d/dx$, and the effect of the drift is 
+just to shift the population profile to the right. If we are at a point where the 
+slope of the population density is positive, then the shift will {\em reduce} the
+population density at the point; the change in population density is proportional
+to $-d/dx$. Similarly, if dispersal tends to move offspring away from a region, that
+is if $\grad\cdot\meanq >0$, 
+then it will push down the population density, hence the term $-\grad\cdot\meanq$ in
+equation~(\ref{eqn:nonlocal_pde}).
+
+\paragraph{Two-step convergence to PDE}
 
 Although the coefficients at $x$ in \eqref{eqn:nonlocal_pde} are nonlocal,
-they depend only on the region nearby to $x$,
-and so we would expect solutions of the nonlocal PDE to be close to the corresponding local PDE
-as the interaction distances $\epsilon_r$, $\epsilon_\gamma$ and $\epsilon_F$
-go to zero:
-for instance, if $\eta_t$ has density $\varphi_t$
-then $\gamma(x, \smooth{\gamma} \eta_t(x)) \to \gamma(x, \varphi_t(x))$ as $\epsilon_\gamma \to 0$
-(recalling that $\smooth{\gamma}{}$ denotes convolution with the heat kernel at time $\epsilon_\gamma^2$).
-The following propositions give two concrete situations in which that is true.
-
+we can choose our kernels $\rho_\gamma$, $\rho_r$, and $\rho_F$
+in such a way that they depend only on the population in a region close to $x$,
+and so we expect that under rather general conditions
+solutions of the nonlocal PDE will be close to the corresponding 
+classical PDE.
+The following propositions provide two concrete situations in which this is true.
+In the first, the PDE is a reaction diffusion equation, and we borrow
+an idea from~\cite{penington:2017} to express the solutions to both the nonlocal
+equation and the classical PDE through a Feynman-Kac formula. 
 \begin{proposition}
     \label{prop:nonlocal_to_local}
-    Suppose that $\eta^\epsilon_t$ is a weak solution to equation \eqref{eqn:nonlocal_pde}
-    with $r(x, m) = 1$ for all $x$ and $m$
-    and some $\epsilon_r + 1/\theta < \epsilon_\gamma = \epsilon_F = \epsilon$
-    \comment{and assumptions on $\gamma$? and $F$?}.
-    Then $\eta^\epsilon_t(dx)$ converges \comment{in what sense?} as $\epsilon \to 0$
-    to $\varphi_t(x) dx$, which is a (strong) solution to
-    \begin{align} \label{eqn:PDE}
-        \partial_t \varphi(t, x)
-        =
-        \DG^* \left( \gamma(\cdot, \varphi(t, \cdot)) \varphi(t, \cdot)  \right)(x)
-        + F(x, \varphi(t, x)) \varphi(t, x) .
-    \end{align}
+Recall the notation $\rho^\epsilon_F(x)=\rho_F\big(x/\epsilon)/\epsilon^d$.
+Assume $\varphi_0\in L^2(\IR)$ is a positive, uniformly Lipschitz, and uniformly bounded function. 
+Suppose that $\varphi^\epsilon\in L^2(\IR^d)$ is a weak solution to the equation
+\begin{equation}
+\label{nonlocalPDEv1} 
+%\begin{cases}
+\partial_t \varphi^\epsilon = \DG^* \varphi^\epsilon + 
+\varphi^\epsilon F(\rho_F^\epsilon*\varphi^\epsilon),  
+	%& 
+\qquad x \in \mathbb{R}^d,\, t >0, %\\ 
+%	\varphi^\epsilon(0,x) = \varphi_0(x) & x \in \mathbb{R}^d;
+%\end{cases}
+\end{equation}
+with initial condition $\varphi_0(\cdot)$,
+and that $\varphi$ is a weak solution to the equation
+ \begin{equation}
+\label{localPDE} 
+%\begin{cases}
+\partial_t \varphi = \DG^* \varphi + \varphi F(\varphi),  
+%	& 
+\qquad x \in \mathbb{R}^d,\, t >0, %\\ 
+%	\varphi(0,x) = \varphi_0(x) & x \in \mathbb{R}^d.
+%\end{cases}
+\end{equation}
+also with initial condition $\varphi_0(\cdot)$.
+%Assume $\varphi_0\in L^2(\IR)$ is a positive, Lipschitz, and uniformly bounded function; 
+Suppose further that $F$ is a Lipschitz function which is bounded above, and that
+$b(x)$ and $C(x)$, the drift and 
+covariance matrix of $\DG$, satisfy the conditions of 
+Assumptions~\ref{def:model_setup}.
+Then, for all $T>0$ there exists a constant $K=K(T, \Vert \varphi_0 \Vert_\infty)>0$,
+and a function $\delta(\epsilon)$ (dependent on $\rho_F$) with $\delta(\epsilon)\to 0$ 
+as $\epsilon\to 0$,
+such that, for all $0 \leq t \leq T$, and $\epsilon$ small enough,
+\[ 
+\Vert \varphi_t(\cdot) - \varphi_t^\epsilon(\cdot) \Vert_\infty\leq K\delta(\epsilon). 
+\]
+In particular, as $\epsilon\to 0$, we have that $\varphi^\epsilon$ converges 
+uniformly in compact intervals of time to $\varphi$.
 \end{proposition}
+\begin{remark}
+Note that Theorem~\ref{thm:kurtzxiong} guarantees uniqueness of solutions
+to equation~(\ref{nonlocalPDEv1}). 
+\end{remark}
+Our second example is a nonlocal version of a porous medium equation with
+logistic growth. That is, 
+we consider non-negative solutions to the equation
+\begin{equation}
+\label{mollified equation}
+\partial_t \psi^\epsilon=
+\Delta\left(\psi^\epsilon \cdot \rho^{\epsilon}_\gamma*\psi^\epsilon\right)
++\psi^\epsilon\left(1-\rho^{\epsilon}_\gamma*\psi^\epsilon\right).
+\end{equation}
+The case without the reaction term (and with $\IR^d$ replaced by a torus) is considered 
+by~\cite{lions/mas-gallic:2001} who use
+it as a basis for a particle method for numerical solution of the porous medium equation.
+Of course this does not quite fit into our framework, since in the notation of our 
+population models this would necessitate $\gamma(x,m)=\smooth{\epsilon}m$ which is
+not bounded. However, this can be overcome by an additional layer of approximation
+(c.f.~our numerical experiments of Section~\ref{beyond linear diffusion})
+and we do not allow this to detain us here. Existence and uniqueness of solutions 
+to~(\ref{mollified equation}) can be obtained using the approach
+of~\cite{lions/mas-gallic:2001}.
+
+We should like to prove that as $\epsilon\to 0$ we have
+convergence to the solution to the porous medium equation with
+logistic growth:
+\begin{equation}
+\label{PME}
+\partial_t\psi=
+\Delta\left(\psi^2\right)
++\psi\left(1-\psi\right).
+\end{equation}
+
+\begin{notation}
+We use $\rightharpoonup$ to denote weak convergence in the sense of analysts;
+that is, $\psi^\epsilon\rightharpoonup \psi$ in $L^1$ means 
+$\int \psi^\epsilon v d x
+\rightarrow\int \psi v d x$ for all $v\in L^\infty$.
+
+We write $L_t^2(H^1)$ for functions for which the $H^1$ norm in
+space is in $L^2$ with respect to time, i.e.
+$$\int_0^T\int \left\{\psi_t(x)^2+\left\| \nabla \psi_t(x)\right\|^2\right\}
+dx dt <\infty,$$
+and $C_t(L^1)$
+will denote functions for which the $L^1$ norm in space is continuous in time.
+\end{notation}
+
+\begin{proposition}
+	\label{nonlocalPME to PME}
+Suppose that
+we can write $\rho_\gamma=\zeta*\check{\zeta}$, where $\check{\zeta}(x)=\zeta(-x)$ and
+$\zeta\in\mathcal{S}(\IR^d)$ (the Schwartz space of rapidly decreasing functions).
+Furthermore, suppose that %$\psi_0^\epsilon\in L^1(\IR^d)$, 
+$\psi_0^\epsilon\geq 0$ is such that
+there exist $\lambda\in (0,1)$ and $C\in (0,\infty)$ (independent
+of $\epsilon$) such that 
+\begin{equation*}
+\int\exp(\lambda \|x\|)\psi_0^\epsilon(x)dx<C,\quad\mbox{ and }
+\sup_\epsilon\int \psi_0^\epsilon|\log \psi_0^\epsilon|dx<\infty,
+\end{equation*}
+with
+$\psi_0^\epsilon\rightharpoonup \psi_0$ as $\epsilon\to 0$. Then
+writing $\psi^\epsilon$ for the solution to~(\ref{mollified equation})
+on $[0,T]\times \IR^d$ with
+initial condition $\psi_0^\epsilon$,
+$\psi^\epsilon\rightharpoonup \psi$ as $\epsilon\to 0$ where
+$\psi\in L_t^2(H^1)\cap C_t(L^1)$, $\int \psi|\log \psi| dx<\infty$, and
+$\psi$ solves~(\ref{PME}) on $[0,T]\times \IR^d$. 
+%Moreover, strong convergence
+%of the initial conditions implies strong convergence of the solutions.
+\end{proposition}
+
+\begin{remark}
+Although it seems hard to formulate an all-encompassing result,
+Propositions~\ref{prop:nonlocal_to_local} and~\ref{nonlocalPME to PME} are by no
+means exhaustive. When our scaling limit is deterministic, one can 
+expect analogous results under rather general conditions. However, when the limit
+points are stochastic, they resemble `nonlinear superprocesses' and so one cannot
+expect a density with respect to Lebesgue measure in $d\geq 2$. It is then not
+reasonable to 
+expect to be able to make sense of the limit if we scale the kernels in this way.
+Moreover, in one dimension, where the classical superprocess does have a density with 
+respect to Lebesgue measure, the form of~(\ref{eqn:limiting_mgale_problem})
+suggests that even if one can remove the local averaging from $\gamma$, we
+would need to retain averaging of $r$ in order to obtain a well-defined limit. 
+\end{remark}
+
+\paragraph{One-step convergence to PDE}
 
 Theorem \ref{thm:nonlocal_convergence} combined with Proposition \ref{prop:nonlocal_to_local}
-imply that we can take the $N \to \infty$ limit
-followed by $\epsilon \to 0$
-to obtain solutions to the PDE \eqref{eqn:PDE}.
+implies that we can take the limit $N \to \infty$
+followed by the limit $\epsilon \to 0$
+to obtain solutions to the PDE \eqref{localPDE}.
 However, it is of substantial interest to know whether
@@
 The general case seems difficult,
-but we can prove such ``diagonal'' convergence in the following situation.
+but we prove such ``diagonal'' convergence in the following situation.
 
@@
     \label{thm:local_convergence}
+\comment{Need to add conditions on initial condition}
+
+\comment{Need to introduce notion of $C$-tight and say that's what we prove.}
+
     Let $(\eta^N_t)_{t \geq 0}$
-    be as defined in Definition \ref{def:model_setup}
-    and assume that as $N \to \infty$, $\theta \to \infty$
-    and $\epsilon_r + 1/\theta < \epsilon_\gamma = \epsilon_F = \epsilon \to 0$
-    in such a way that $\theta/N \to 0$
-    and
-    \comment{TODO: some conditions on $\epsilon$ and $r$ and $\gamma$ and $F$}.
-    Then the sequence of stochastic processes $(\eta^N_t)_{t \ge 0}$
-    converges \comment{in some sense}
+    be as defined in Definition~\ref{defn:mgale_construction} with
+$r(x,m)\equiv 1\equiv \gamma(r,m)$, $F(x,m)\equiv F(m)$, 
+$\rho^\epsilon_F$ a Gaussian density with parameter $\epsilon^2$,
+and $\DG=\Delta$. 
+Further suppose that $F(m)$ is a polynomial with $F(m)\ind_{m\geq 0}$ bounded above.
+%there exists $k\in\IN$ such that $F$ is $k$-times differentiable
+%with 
+%$\|F^{(k)}(m)\|_{\infty}<\infty$.
+Finally assume that $N \to \infty$, $\theta \to \infty$
+and $\epsilon \to 0$ in such a way that
+\begin{equation}
+\frac{1}{\theta\epsilon^2}+\frac{\theta}{N\epsilon^d}\to 0.
+\end{equation}
+Then the sequence of stochastic processes $\big(\rho_F^\epsilon*\eta^N_t\big)_{t \ge 0}$
+converges weakly
 to a measure-valued process with a density $\varphi(t, x)$
@@
 \begin{align}
-        \partial_t \varphi(t, x)
-        &=
-        \text{whatever the final form is here} .
+        \partial_t \varphi(t, x)=\Delta \varphi (t,x) +\varphi(t,x) F(\varphi(t,x)).
 \end{align}
 \end{theorem}
+\begin{remark}
+In fact,
+our proof goes through without significant change under that conditions that
+$F(m)\ind_{m\geq 0}$ is bounded above (but not necessarily below), and that
+for all $m,n\in[0,\infty)$
+\[
+|F(m)|\leq\sum_{j=1}^ka_jm^j, \quad\mbox{ and }
+|F(n)-F(m)|
+\leq|n-m|\sum_{j=1}^{k'}b_j\Big(n^j+m^j),
+\]
+for some non-negative constants $\{a_j\}_{j=0}^k$, $\{b_j\}_{j=0}^{k'}$.
+We take $F$ to be polynomial to somewhat simplify notation in the proof.
+\end{remark}
 
@@
 \subsection{Ancestral lineages in the scaling limit}
-
-Now that we have established what we can say about how population density changes with time,
+\label{sec:ancestral lineages}
+
+Now that we have established what we can say about how 
+population density changes with time,
 we turn to results on ancestral lineages,
@@
 Informally,
-a \emph{lineage} $(L_t)_{t \ge 0}$
-begun at spatial location $L_0 = x$
-can be obtained by picking a focal individual uniformly at $x$,
-and then for each amount of time $t$ in the past,
-setting $L_t$ to the spatial location of the individual from whom
-the focal individual inherits at that time in the past.
+a \emph{lineage} $(L_t^N)_{t \ge 0}$,
+begun at spatial location $L_0 = x$,
+can be obtained by picking a focal individual uniformly at 
+random from the population at $x$,
+and then, for each time $t$,
+setting $L_t^N$ to be the spatial location of the individual alive at time $t$
+before the present from
+whom the focal individual is descended.
 Since in our model individuals have only one parent, this is unambiguous.
 Although we did not explicitly retain such information,
-it is clear that for finite $N$
-one could construct the distribution of a lineage $(L_t)_{t=0}^T$
+it is clear that for finite $N$, since individuals are born one at a time, 
+one could construct the distribution of a lineage $(L_t^N)_{t=0}^T$
 given the history of the population $(\eta^N_t)_{t = 0}^T$,
 for each starting location to which $\eta^N_T$ assigns positive mass.
-It is less clear, however, how to formally retain such information in the limit.
+It is less clear, however, how to formally retain such information when we 
+pass to the scaling limit.
+
 The \emph{lookdown construction} in Section~\ref{sec:lookdown}
-provides just such a construction.
+will enable us to recover information about ancestry in the infinite
+population limit.
 Roughly speaking,
-this works by assigning to each particle a unique ``level''
-that functions as a label and thus allows reconstruction of lineages,
-but also (in some sense) orders individuals by eventual reproductive output,
-allowing a formal limit.
+each particle is assigned a unique ``level'' from $[0,\infty)$
+that functions as a label and thus allows reconstruction of lineages.
+The key to the approach is that levels are assigned in such a way as to be exchangeable, 
+so that sampling a finite number, $k$ say, of
+individuals from a given 
+region is equivalent to looking at the individuals in that region with the $k$ lowest
+levels. Moreover, as we pass to 
+the infinite population (and therefore infinite level) limit,
+the collection of (individual, level) pairs 
+for which the levels are below 
+any fixed value converge, Theorem~\ref{}. 
 See~\citet{etheridge/kurtz:2018} for an introduction to these ideas.
-
-A lineage is, in general, a well-defined stochastic process,
-but there are two important questions
-that affect its tractability.
-First, when is it a Markov process given the population process?
-(In other words, given $(\eta_t)_{t=0}^T$ that records numbers of individuals
-but not their ancestry.)
-\comment{NOT RIGHT:}
-We expect the answer here to be that a lineage is Markov
-only in the $N \to \infty$ limit
-(see \citet{barton/depaulis/etheridge:2002} for discussion).
+In particular, even in the infinite
+population limit, we can sample an individual
+from a region (it will be the individual in that region with the lowest level) 
+and trace its line of descent. 
+This will, in principle, allow us to calculate, for each $y\in\IR^d$, the proportion of
+the population at location $x$ in the present day population that are descended from 
+a parent who was at location $y$ at time $t$ in the past. To make
+sense of this in our framework, in Section~\ref{ancestral lineages}, 
+we justify a weak reformulation of this idea.
+
+We are interested in two questions.
+When is the motion of an ancestral 
+lineage, given complete knowledge of the population process,
+ a well-defined Markov process?
+In other words, is knowledge of the process $(\eta_t)_{t=0}^T$ that records 
+numbers of individuals
+but not their ancestry sufficient to define the distribution of $(L_t)_{t=0}^T$?
 Second, does the process have a tractable description?
-If the population process has a density,
-then it turns out that a lineage is a diffusion driven by the density.
-The remaining case is the superprocess limit ($\theta/N \to \alpha > 0$);
-in this case, we expect that a lineage could still be described as a generalized diffusion,
-but moving within a stochastic landscape that is singular in $d \ge 2$.
-We focus on the more tractable situation where the population process is deterministic.
-However, the results here apply to either the local or nonlocal case
-(i.e., where the density solves a local or nonlocal PDE).
-
-\begin{definition}[Generator of a lineage] \label{def:lineage_generator}
+
+We focus on the simplest situation in which the population process is deterministic.
+However, the results here apply when the population process solves 
+either a nonlocal or a classical PDE.
+There will be no 
+coalescence of ancestral lineages in the deterministic limit, but our results can
+be seen as a first step towards understanding genealogies for very high population 
+densities. 
+\begin{definition}[Ancestral lineage] 
+\label{def:lineage_generator}
     Let $(\varphi_t(x))_{0 \le t \le T}$
-    denote the density of a population that solves \eqref{eqn:nonlocal_pde},
+    denote the density of the scaling limit of our population model, 
+solving \eqref{eqn:nonlocal_pde},
     and let $y$ be a point with $\varphi_T(y) > 0$.
     We define $(L_s)_{s=0}^T$,
-    the ancestral lineage in this population of an individual sampled at $y$ at time $T$,
-    to be the position of the unique ancestor of $y$ alive at time $T - s$.
+    the ancestral lineage of an individual sampled from the
+population at $y$ at time $T$, by setting $L_s$
+    to be the position of the unique ancestor of that individual at time $T - s$.
     We define
     $(Q_s)_{s \geq 0}$
-    to be the time inhomogeneous semi-group satisfying
+    to be the time inhomogeneous semigroup satisfying
     \begin{align*}
@@
 
-Our main result identifies a lineage as a diffusion
+Our next result identifies the ancestral lineage as a diffusion
 by characterizing its generator.
@@
         \left[
-            \sum_{ij} \covq_{ij} \partial_{ij} f
-            + \sum_j \vec{m}(s)_j \partial_j f
+            \sum_{ij} \covq_{ij} \partial_{x_ix_j} f
+            + \sum_j \vec{m}_j \partial_{x_j} f
         \right] ,
@@
     $$
-    \vec{m}(s)_j
+    \vec{m}_j
     =
-    2 \sum_i C_{ij} \partial_i \log(\gamma \varphi)
-    + 2 \sum_i \partial_i C_{ij}
+    2 \sum_i C_{ij} \partial_{x_i} \log(\gamma \varphi)
+    + 2 \sum_i \partial_{x_i} C_{ij}
     - \meanq_j .
     $$
-    Then $\Lgen_{\varphi_{T-s}}$ is the generator of the semigroup $Q_s$
-    of Definition~\ref{def:lineage_generator}.
+    Then the generator of the semigroup $Q_s$
+    of Definition~\ref{def:lineage_generator} is given by
+	$\partial_sQ_sf(y)= \Lgen_{\varphi_{T-s}}Q_sf(y).$ 
 \end{theorem}
-
+\begin{remark}
 As usual,
@@
 remember that everything depends on location and density at that location and time --
-for instance, ``$r$'' is actually $r(x, \varphi(x))$ (in the local case),
+for instance, ``$r$'' is actually $r(x, \varphi(x))$ (in the classical case),
 or $r(x, \smooth{r} \eta(x))$ (in the nonlocal case).
+
+Moreover, we haven't proved any regularity of the population density process $\varphi$,
+so, as written, the generator~(\ref{eqn:lineage_generator})
+may not make sense. Instead, it should be interpreted in a weak sense which is made precise
+in Section~\ref{ancestral lineages}.
+\end{remark}
 
@@
 In other words, 
-the lineage behaves as a diffusion driven by Brownian motion run at speed 
-\comment{TODO: make this right:}
-If $V_s(x) = \log(\varphi_s(x) \gamma(x, \varphi_s)) - \meanq \cdot x / 2 \sigma^2$,
-then the diffusion has drift $\grad V_s$.
-If $\varphi$ does not change with time, 
-then the stationary distribution is proportional to $\exp(V(x))$.
-a lineage behaves as a diffusion
-that is driven by a Brownian motion 
-run at speed $\sigma^2$ multiplied by the local per-capita production of offspring ($r \gamma$)
-in a potential equal to the local birth output tilted by migration bias
-($\varphi_s \gamma \exp(-\meanq \cdot x / 2 \sigma^2)$).
+the lineage behaves as a diffusion driven by Brownian motion 
+run at speed $\sigma^2$ multiplied by the local per-capita production of 
+mature offspring 
+($r \gamma$)
+in a potential equal to the local output of juveniles tilted by migration bias
+($\varphi_s \gamma \exp(-\meanq \cdot x / 2 \sigma^2)$). In particular,
+lineages are drawn to regions of high fecundity (production of juveniles), but their
+speed is determined by the rate of production of mature offspring.
+This can be compared to Remark~\ref{ancestral lineages: first guess}.
 
@@
     In addition to the assumptions of Corollary~\ref{cor:lineages_simple},
-    suppose that the population process is described by a traveling wave with speed $\wavespeed$,
+    suppose that the population process is described by a travelling wave with 
+velocity $\wavespeed$,
     i.e., the population has density
@@
     \begin{align*}
-        r \Delta (\gamma w) + w F + \wavespeed \cdot \grad w = 0 .
-    \end{align*}
-    Then the semigroup 
+        r \DG* (\gamma w) + w F + \wavespeed \cdot \grad w = 
+r\sigma^2\Delta (\gamma w) -\meanq \cdot\grad (\gamma w) +\wavespeed \cdot \grad w =0 .
+    \end{align*}
+    Then the semigroup $Q_s$
     of the motion of a linages in this population 
-    $Q_s$ is time-homogeneous with generator
+    is time-homogeneous with generator
     \begin{align}
+\label{Lgen}
         \Lgen f
@@
         \right)
-        + (\wavespeed - \meanq) \cdot \grad f .
+        + (\wavespeed - r\gamma \meanq) \cdot \grad f .
     \end{align}
@@
 
-Next,
-we cover some illustrative examples
-and interesting applications.
+We now turn to some examples and applications. %Next,
+%we cover some illustrative examples
+%and interesting applications.
 
 % % % % % % % % % % % %
-\subsection{Beyond reaction-diffusion equations: a population described by the porous medium equation}
-\comment{look up what the technical term is for the nonlinear diffusive bit?
-    and, does "reaction-diffusion" mean parabolic?}
-
-Consider the porous medium equation (PME) with logistic growth,
-\begin{equation}
-    \label{eqn:pme}
-    \partial_t v = \partial_x^2 (v^2) + v (1 - v) ,
-\end{equation}
-an example of a reaction-diffusion equation with a nonlinear diffusion term.
+\subsection{Beyond linear diffusion}
+\label{beyond linear diffusion}
+
+Equation~(\ref{eqn:nonlocal_pde}) is a nonlocal version of a reaction diffusion equation with nonlinear
+diffusion; in other words the diffusivity of the population depends on the population
+density. Passing to the classical limit, we recover equations
+like~(\ref{PME}).
 Such equations are widely used in a number of contexts in biology in which
@@
 thought of as modelling the density of an expanding population. 
-
-Comparing \eqref{eqn:pme} to \eqref{eqn:pde},
-we see that to set up a limit in which the population density $\varphi$ follows the PME,
+\cite{li/buenzli/simpson:2022} write down an interacting particle
+system on a hexagonal
+lattice (with at most one individual per site) that incorporates an effect
+of local crowding on individual motion. Their equation
+corresponds to a reaction-diffusion equation with nonlinear diffusion and a 
+bistable reaction term of the form~(\ref{Birzu nonlinearity}) and they
+investigate the interplay between nonlinear diffusion and long-term 
+survival or extinction of the population. We focus instead on 
+the monostable reaction of~(\ref{PME}).
+
+Comparing %\eqref{PME} 
+with \eqref{eqn:nonlocal_pde},
+we see that to set up a limit in which the population density $\varphi$ follows the 
+porous medium equation with logistic growth of~(\ref{PME}),
 we need $r=1$,
@@
 Consulting equation~\eqref{eqn:mu_defn},
-this implies that $\mu = (1 + 1/\theta) \varphi - 1/\theta$.
+this implies that $\mu_\theta = \max\big(0, (1 + 1/\theta) \varphi - 1/\theta\big)$.
 In other words,
@@
 Alert readers will notice that
-for finite $\theta$ death rates may be negative,
-and furthermore rates are not bounded;
-in practice we choose a suitably small value for $\beta$ and define
-\begin{align*}
-    \gamma(x, m) &= (1 - \exp(- \beta m)) / \beta \\
-    F(x, m) &= \exp(- \beta m) / \beta ,
-\end{align*}
-and set $\mu(x, m) = \max(0, \gamma - F / \theta)$.
+the assumption from Assumptions~\ref{def:model_setup} 
+that $\gamma (x,m)$ be uniformly bounded 
+is violated.
+This can be corrected by use of a cut-off, and in fact the downwards drift
+provided by the logistic control of the population size prevents $m$ from 
+getting too big. 
+In practice in our simulations we choose a suitably small value for $\beta$, define
+\begin{align*}
+    \gamma(x, m) = (1 - \exp(- \beta m)) / \beta, \qquad
+    F(x, m) = \exp(- \beta m) / \beta ,
+\end{align*}
+and set $\mu_\theta(x, m) = \max(0, \gamma - F / \theta)$.
 Birth and death rates are equal at density $m = 1$,
@@
     \begin{center}
-        \includegraphics[width=0.45\textwidth]{figures/ex2a/pme_123.steps}
-        \includegraphics[width=0.45\textwidth]{figures/ex2b/pme_123.steps}
+        %\includegraphics[width=0.45\textwidth]{figures/ex2a/pme_123.steps}
+        %\includegraphics[width=0.45\textwidth]{figures/ex2b/pme_123.steps}
     \end{center}
     \caption{
-        Two panels, showing simulated 1D populations under the PME, comparing the simulated
+        Two panels, showing simulated 1D populations under a
+porous medium equation with logistic growth~(\ref{PME}), comparing the simulated
         profile to the analytical solution;
@@
 
-This equation has an explicit travelling wave solution
+In one dimension, equation~(\ref{PME}) has an explicit travelling wave solution
 \begin{align} \label{eqn:pme_wave}
@@
 the solution converges to \eqref{eqn:pme_wave} \citep{kamin/rosenau:2004}.
-
-Indeed, simulations of this process
-shown in Figure~\ref{fig:pme_waves}
-display traveling wave solutions
-similar to numerical solutions of the PME,
+In Figure~\ref{fig:pme_waves} we show simulations of the individual based model
+described above. They
+display travelling wave solutions
+similar to numerical solutions of~(\ref{PME}),
 with increasingly good agreement for larger $\theta$ and $N$.
 As expected, noise slows down the wave.
+\comment{Not sure that noise will slow things drastically because the 
+biggest production of
+mass happens behind the wavefront.}
 
 % % % % % % % % % % % %
-\subsection{Different types of traveling waves}
+\subsection{Ancestry in different types of travelling waves}
+\label{ancestral lineages for travelling waves}
 
@@
     \begin{center}
-        \includegraphics{figures/ex3_fkpp/fkpp_123.lineages}
-        \includegraphics{figures/ex3_fkpp/fkpp_123.lineagehist}
-        \includegraphics{figures/ex3_pme/pme_123.lineages}
-        \includegraphics{figures/ex3_pme/pme_123.lineagehist}
-        \includegraphics{figures/ex3_allen-cahn/allen-cahn_123.lineages}
-        \includegraphics{figures/ex3_allen-cahn/allen-cahn_123.lineagehist}
+        %\includegraphics{figures/ex3_fkpp/fkpp_123.lineages}
+        %\includegraphics{figures/ex3_fkpp/fkpp_123.lineagehist}
+        %\includegraphics{figures/ex3_pme/pme_123.lineages}
+        %\includegraphics{figures/ex3_pme/pme_123.lineagehist}
+        %\includegraphics{figures/ex3_allen-cahn/allen-cahn_123.lineages}
+        %\includegraphics{figures/ex3_allen-cahn/allen-cahn_123.lineagehist}
     \end{center}
     \caption{
-        Six panels: one pair for FKPP, one for PME, and one for Allen-Cahn.
+        Six panels: one pair for FKPP, one for the porous medium 
+equation with logistic growth~(\ref{PME}), and one for 
+the Allen-Cahn equation~(\ref{eqn:allen_cahn}).
         Each pair shows (top) lineage traced back in wavefront,
         and (bottom) stationary distribution of lineage location,
-        compared to analytical solution for PME.
+        compared to analytical solution for the porous medium case.
         \label{fig:pme_vs_fkpp}
@@
 
-It is interesting to investigate the motion of an ancestral lineage
-in special cases in which we have an explicit expression for the travelling
-wave profile $w$. 
-We consider three relatively well-studied examples:
-the Porous Media equation (above),
+Although it remains challenging to establish the distribution of genealogical
+trees relating individuals sampled from our population model, as described in
+the introduction, we can gain some insight by investigating the motion of a
+single ancestral lineage. Here we do that in the context of a one-dimensional
+population expanding into new territory as a travelling wave. 
+We focus on three cases in which we have 
+explicit information about the shape of the travelling wave profile:
 the Fisher-KPP equation,
-and the Allen-Cahn equation.
-We will work here in one dimension,
+a special case of the Allen-Cahn equation with a bistable nonlinearity, and
+equation~(\ref{PME}).
+We work here in one dimension,
 and take $\sigma^2 = 1$ and $\meanq = 0$.
@@
 %%%%%%%%%%
-\paragraph{Porous Media:}
-Setting $x_0=0$ (for definiteness) and substituting
+
+%%%%%%%%%%
+\paragraph{Fisher-KPP equation:}
+Consider the classical Fisher-KPP equation,
+\begin{align} \label{eqn:fkpp}
+    \partial_t\varphi = \partial_{xx}\varphi + \varphi (1-\varphi) .
+\end{align}
+Even though we do not have an explicit formula for the wave shape in this case,
+our methods provide information about ancestral lineages.
+The equation has non-negative travelling wave solutions of 
+speed $c$ for all $c \geq 2$, 
+but started from any compact perturbation of a Heaviside function, the 
+solution will converge to the profile $w^F$ with the minimal wavespeed, $c=2$
+\citep{kolmogorov/petrovsky/piscounov:1937,bramson:1983}.
+No matter what initial condition,
+for any $t>0$ the support of the 
+solution will be the whole real line. 
+In this case, we must have $r = \gamma = 1$,
+and $F(x, m) = 1 - m$ so $\mu_\theta(x, m) = 1 + (m-1)/\theta$.
+This implies that
+the generator of the motion of an ancestral lineage is
+\begin{equation} \label{eqn:fkpp_generator}
+    \Lgen_1  f
+    =
+    \partial_{xx}f + 2 \frac{\partial_xw^F}{w^F} \partial_x f + 2 \partial_xf .
+\end{equation}
+Near the tip of the wave (for $x$ large), $w^F(x) \sim e^{-x}$,
+so \eqref{eqn:fkpp_generator} implies that
+the motion of a lineage is close to unbiased Brownian motion.
+On the other hand, in the ``bulk'', %for $x < 0$ 
+a lineage behaves approximately as
+Brownian motion with drift at rate two to the right.
+This implies that
+ancestral lineages are pushed into the tip of the wave,
+and there is no stationary distribution,
+so that long-term dynamics of genetic inheritance
+depend on the part of the wave not well-approximated by a smooth profile,
+in agreement with the results described in Section~\ref{introduction}.
+
+%%%%%%%%%%
+\paragraph{Allen-Cahn equation:}
+Now take the following case of the Allen-Cahn equation:
+\begin{align} \label{eqn:allen_cahn}
+    \partial_t\varphi = \partial_{xx}\varphi + \varphi(1-\varphi)(2\varphi-1+s),
+\end{align}
+for a given $s \in (0,2)$.
+Once again we have taken $r=\gamma=1$, but now the reaction term is bistable.
+This equation can be used to model the motion of so-called 
+hybrid zones in population genetics; see, for example,
+\cite{barton:1979, gooding:2018, etheridge/gooding/letter:2022}.
+This equation has an explicit travelling wave solution with speed $s$
+and shape
+\[ w^A(x) = (1+e^{x})^{-1}. \]
+That is $\phi_t(x)=w^A(x-st)$ solves~(\ref{eqn:allen_cahn}).
+Substituting $w^A$ in place of $w^F$ in~(\ref{eqn:fkpp_generator}),
+we find that the generator of an ancestral lineage is now, 
+\begin{align*}
+\Lgen_2 f
+    &=
+    \partial_{xx}f
+    + 
+    2 \frac{\partial_xw^A}{w^A} \partial_xf
+    +
+    s \partial_x f\\
+    \qquad &=
+    \partial_{xx}f
+    -
+    2 \frac{e^x}{1+e^x} \partial_xf 
+    + 
+    s \partial_xf,
+\end{align*}
+so lineages in the tip are pushed leftwards into the bulk of the 
+wave at a rate $-2e^x/(1+e^{x})$.
+The strength of this drift decreases exponentially as $x\to -\infty$.
+The density of the speed measure for this diffusion is
+$$
+    m(x) \propto e^{sx}(1+e^x)^{-2},
+$$
+which is integrable, and so determines the unique stationary distribution.
+Thus the position of the ancestral lineage will converge to a stationary 
+distribution which is maximised away from the extreme tip of the wave.
+This is consistent with~\cite{etheridge/penington:2022}, who consider an analogous
+stochastic population model, although the stronger result there (that the genealogy
+of a sample from behind the wavefront is approximately a Kingman coalecsent) requires
+the stronger condition $s<1$.
+
+% % % % % % % % % % % % % % % %
+
+\paragraph{Porous Medium equation with logistic growth:}
+Finally, consider equation~(\ref{PME}). Setting $x_0=0$ (for definiteness) and substituting
 the form of $w^P$ from equation \eqref{eqn:pme_wave}
@@
 and $F(x, m) = (1 - m)$,
-the lineage's generator is, for $x < 0$,
-with $f_x$ denoting the spatial derivative of $f$,
-\begin{align*}
-    \Lgen f
+the generator of the diffusion governing the position of the ancestral lineage 
+is, for $x < 0$,
+%with $f_x$ denoting the spatial derivative of $f$,
+\begin{align*}
+    \Lgen_3 f
     &=
-        w(x)
+        w^P
         \left(
-         f_{xx}(x)
+        \partial_{xx} f
          +
-         2 \frac{(w(x)^2)_x}{w(x)^2} f_x(x)
+         2 \frac{\partial_x((w^P)^2)}{(w^P)^2} \partial_xf
         \right)
-        + f_x(x) \\
+        + \partial_xf \\
     &=
         \left(1 - e^{\frac{1}{2} x} \right)
-        f_{xx}(x)
+        \partial_{xx}f
         -
-        2 e^{\frac{1}{2} x} f_x(x)
+        2 e^{\frac{1}{2} x} \partial_xf
         +
-        f_x(x) .
-\end{align*}
-The speed measure corresponding to this diffusion is,
-again for $x < 0$,
-\begin{align*}
-    m(d\xi)
+        \partial_xf .
+\end{align*}
+The speed measure corresponding to this diffusion has density
+%again for $\xi < 0$,
+\begin{align*}
+    m(\xi)
     &\propto
@@
 which is integrable and so when suitably normalised gives the unique stationary distribution.
-Notice that at stationarity
+Notice that even though we have the same reaction term as in the Fisher-KPP equation, with this 
+form of nonlinear diffusion, at stationarity
 the lineage will typically be significantly behind the front.
 
-%%%%%%%%%%
-\paragraph{Fisher--KPP:}
-A great deal more attention has been paid to the classical Fisher-KPP equation,
-\begin{align} \label{eqn:fkpp}
-    v_t = v_{xx} + v (1-v) .
-\end{align}
-Even though we do not have an explicit formula for the wave shape in this case,
-our methods provide information about ancestral lineages.
-The equation has non-negative travelling wave solutions of speed $c$ for all $c \geq 2$, 
-but started from any compact perturbation of a Heaviside function, the 
-solution will converge to the profile $w^F$ with the minimal wavespeed, $c=2$
-\citep{kolmogorov/petrovsky/piscounov:1937,bramson:1983}.
-No matter the initial condition,
-for any $t>0$ the support of the 
-solution will be the whole real line. 
-In this case, we must have $r = \gamma = 1$,
-and $F(x, m) = 1 - m$ so $\mu(x, m) = 1 + (m-1)/\theta$.
-This implies that
-the generator of the motion of an ancestral lineage is
-\begin{equation} \label{eqn:fkpp_generator}
-    \Lgen \phi
-    =
-    \phi_{xx} + 2 \frac{w_x}{w} \phi_x + 2 \phi_x .
-\end{equation}
-Near the tip of the wave (for $x$ large), $w^F(x) \sim e^{-x}$,
-so \eqref{eqn:fkpp_generator} implies that
-the motion of a lineage is close to unbiased Brownian motion.
-On the other hand, for $x < 0$ a lineage behaves approximately as
-Brownian motion with drift at rate two to the right.
-This implies that
-ancestral lineages are pushed into the tip of the wave,
-and there is no stationary distribution,
-so that long-term dynamics of genetic inheritance
-depend on the part of the wave not well-approximated by a smooth profile.
-These results agree with those of \comment{TODO: citations}.
-
-%%%%%%%%%%
-\paragraph{Allen-Cahn:}
-Finally, we take the Allen-Cahn equation
-\begin{align} \label{eqn:allen_cahn}
-    v_t = v_{xx} + v(1-v)(2v-1+s),
-\end{align}
-for a given $s \in (0,2)$,
-which is used to model populations evolving under selection \cite{Sarah}.
-This equation also has an explicit travelling wave solution with speed $s$
-and shape
-\[ w^A(x) = (1+e^{x})^{-1}. \]
-The generator for ancestral lineages is, just as in the Fisher-KPP case,
-\begin{align*}
-    \hat{\mathcal{L}}\phi
-    &=
-    \phi_{xx}
-    + 
-    2 \frac{w_x}{w} \phi_x
-    +
-    s \nabla \phi \\
-    \qquad &=
-    \phi_{xx}
-    -
-    2 \frac{e^x}{1+e^x} \phi_x 
-    + 
-    s \nabla \phi,
-\end{align*}
-so lineages in the tip are pushed leftwards into the bulk of the wave at a rate $-2(e^{-x}+1)^{-1}$,
-that gets weaker further to the left.
-This diffusion has speed measure
-$$
-    m(d\xi) \propto e^{sx}(1+e^x)^{-2},
-$$
-which is concentrated around $\log(s/(2-s))$ and decays like $e^{x(s-2)}$ away from this point.
-These results agree with those of \cite{etheridge/penington:2020}.
-
-% % % % % % % % % % % % % % % %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Clumping from nonlocal interactions}
@@
 Consider a deterministic,
-continuous population generated by parameters $\gamma$, $\mu$, and $r$
+continuous population generated by parameters $\gamma$, $\mu_\theta$, and $r$
 with $\meanq = 0$ and $\covq = I$.
@@
 $$
-   r \Delta(\gamma w) + (r \gamma - \mu) w = 0 .
+   r \Delta(\gamma w) + (r \gamma - \mu_\theta) w = 0 .
 $$
-It is easy to see that $w$ does not uniquely specify $\gamma$, $\mu$, and $r$:
-let $\beta(x)$ be a smooth, nonnegative function on $\IR^d$,
-and let $r'(x, m) = \beta(x) r(x, m)$ and $\mu'(x, m) = \beta(x) \mu(x, m)$
+It is easy to see that $w$ does not uniquely specify $\gamma$, $\mu_\theta$, and $r$:
+let $\lambda(x)$ be a smooth, nonnegative function on $\IR^d$,
+and let $r'(x, m) = \lambda(x) r(x, m)$ and $\mu_\theta'(x, m) = \lambda(x) \mu_\theta(x, m)$
 (and, let $\gamma' = \gamma$).
-Then the population with parameters $\gamma'$, $\mu'$, and $r'$
+Then the population with parameters $\gamma'$, $\mu_\theta'$, and $r'$
 has the same stationary profile(s) as the original population.
@@
 \]
-while the second has lineage generator $f \mapsto \beta(x) \Lgen f(x)$.
+while the second has lineage generator $f \mapsto \lambda(x) \Lgen f(x)$.
 In other words,
 although the stationary profile of the population is unchanged when we scale
-local establishment and death by $\beta$,
-the motion of lineages is sped up locally by $\beta$.
-This corresponds to making areas with $\beta > 1$ more ``sink-like'' and $\beta < 1$ ``source-like'':
-if $\beta(x) > 1$, then at $x$ both the death rate and establishment of new individuals are higher.
-As a result, lineages in the second model spend more time in areas with $\beta < 1$,
-i.e., those areas have higher long-term fitness,
-something that is in principle discernible from genetic data.
+local establishment and death by $\lambda$,
+the motion of lineages is sped up locally by $\lambda$.
+This corresponds to making areas with $\lambda > 1$ more ``sink-like'' 
+and $\lambda < 1$ more ``source-like'':
+if $\lambda(x) > 1$, then at $x$ both the death rate and probability of 
+establishment of new individuals are higher.
+As a result, lineages in the second model spend more time in areas with $\lambda < 1$,
+i.e., those areas have higher reproductive value, %long-term fitness
+something that is, in principle, discernible from genetic data.
 
@@
 
-In this section we give heuristic arguments for our main results,
+In this section we perform some preliminary calculations and use them 
+to provide heuristic arguments for our main results,
 to build intuition before the formal proofs.
@@
     \label{sec:population_heuristics}
+
+{\em We reiterate that in our prelimiting model,
+the population is represented by a point measure in which each
+individual is assigned a mass $1/N$. We use the term ``population density'' for
+this process, as it is supposed to measure population size relative to a 
+nominal occupancy of $N$ individuals per unit area, but it is not
+absolutely continuous with respect to Lebesgue measure.}
 
@@
 acting on test functions of the form $G( \langle f, \eta \rangle )$,
-where $f \geq 0$ is smooth and compactly supported on $\IR^d$ and 
+where $f \geq 0$ is smooth and bounded on $\IR^d$ and 
 $G \in C^\infty ([0,\infty))$.
-Recall that $\theta \to \infty$ along with $N$,
-although we don't remind the reader with extra superscripts.
+Recall that $\theta =\theta(N) \to \infty$ as $N\to\infty$ in such 
+a way that $\theta(N)/N\to\alpha$.
+%,
+%although we don't remind the reader with extra superscripts.
 
 A Taylor expansion allows us to write
-\begin{multline*}
+\begin{multline}
+	\label{generator prelimit}
     \Pgen^N
@@
     \epsilon_N(f, G, \eta),
-\end{multline*}
+\end{multline}
 where the terms that make up 
@@
 
-Recall that in our parameterization only death rates $\mu$
-and the dispersal kernel $q$ depend on $\theta$.
-For a suitable (smooth, compactly supported) test function $f$, we find
+Recall that in our parameterization only death rates $\mu_\theta$
+and the dispersal kernel $q_\theta$ depend on $\theta$.
+For a suitable test function $f$, we find
 \begin{equation} \label{mean measure}
@@
     \qquad \stackrel{\theta\to\infty}{\longrightarrow} \qquad  
-    \DG \big(r(\cdot,\Xi)f(\cdot)\big)(x) .
+    \DG \big(r(\cdot,\eta)f(\cdot)\big)(x) .
 \end{align}
-To make this more familiar,
-remember that if dispersal is simply standard multivariate Gaussian
+In particular,
+if dispersal is simply standard multivariate Gaussian
 with mean zero and covariance $\sigma^2 I / \theta$,
@@
 \end{equation}
-This gives the martingale of Theorem~\ref{thm:nonlocal_convergence}.
-More generally, we expect everything to work
-if the remaining parameters ($r$, $\gamma$, and $F$)
-also depended on $N$, but converged as $N \to \infty$.
+This explains the form of the martingale of Theorem~\ref{thm:nonlocal_convergence}.
+%More generally, we expect everything to work
+%if the remaining parameters ($r$, $\gamma$, and $F$)
+%also depend on $N$, but converge as $N \to \infty$.
 
@@
 
-We now look at the second order term.
+We now look at the second order term in~(\ref{generator prelimit}).
 An individual at location $x$ gives birth 
@@
 $$
-\langle
+\big\langle
     N \theta \gamma(x,\eta)
@@
     , \eta(dx)
-\rangle .
+\big\rangle .
 $$
@@
 \left\{
-    \langle
+    \Big\langle
         \gamma(x,\eta)
         \int \frac{1}{N^2}f^2(y)r(y,\eta)q_\theta(x,dy) 
-    , \eta(dx)\rangle
+    , \eta(dx)\Big\rangle
     +
-    \langle
-        \mu(x,\eta)\frac{1}{N^2}f^2(x) 
-    ,\eta(dx)\rangle
+    \Big\langle
+        \mu_\theta(x,\eta)\frac{1}{N^2}f^2(x) 
+    ,\eta(dx)\Big\rangle
 \right\} \\
@@
     \frac{\theta}{N}
-    \langle
-        \gamma(x, \eta) \int f^2(y) r(y, \eta) q_\theta(x, dy) + f^2(x) \mu(x, \eta),
+    \big\langle
+        \gamma(x, \eta) \int f^2(y) r(y, \eta) q_\theta(x, dy) + f^2(x) \mu_\theta(x, \eta),
         \eta(dx)
-    \rangle .
+    \big\rangle .
 \end{align*}
 Since $\int f^2(y) r(y, \eta) q_\theta(x, dy) \to f^2(x) r(x, \eta)$
-and $\gamma r + \mu = 2 \gamma r - F / \theta \to 2 \gamma r$
+and $r\gamma  + \mu_\theta = 2 r \gamma  - F / \theta \to 2 r \gamma$
 as $\theta \to \infty$,
@@
 \frac{\alpha}{2} G''(\langle f, \eta \rangle)
-    \langle
-        2 \gamma(x, \eta) r(x, \eta),
+    \big\langle
+	2 r(x, \eta) \gamma(x, \eta),
         \eta(dx)
-    \rangle .
-\end{align*}
-
-Finally, the term $\epsilon_{\theta,N}(f, G, \eta)$ will be 
-$\bigO(\theta/N^2)$.
-
-By choosing $\theta/N \rightarrow 0$, the second order term in the generator 
+    \big\rangle .
+\end{align*}
+
+An entirely analogous argument shows that if $G'''$ is bounded, then
+the term $\epsilon_{\theta,N}(f, G, \eta)$ 
+in~(\ref{generator prelimit}) will be $\bigO(\theta/N^2)$.
+
+If we hold $\rho_\gamma$, $\rho_r$, $\rho_F$ fixed, then 
+by choosing $\theta/N \rightarrow 0$, the second order term in the generator 
 will vanish and we expect a deterministic limit,
-for which $d/dt \langle f, \eta_t \rangle$ is equal to~\eqref{limit of mean measure equation}.
+for which $\partial_t \langle f, \eta_t \rangle$ is equal to~\eqref{limit of mean measure equation}.
 In other words, the limit is a weak solution to the deterministic equation
@@
 \label{deterministic limit}
-\frac{d\varrho(x)}{dt}
+\partial_t\varphi_t(x)
 =
-    r(x,\varrho)
+    r(x,\varphi_t)
     \DG\big(
-        \gamma(\cdot,\varrho) \varrho(\cdot)
+        \gamma(\cdot,\varphi_t) \varphi_t(\cdot)
     \big)(x)
-    + F(x, \varrho) \varrho(x) 
+    + F(x, \varphi_t) \varphi_t(x) 
 \end{equation}
 in the sense of Definition~\ref{defn:weak_solutions},
-where $\varrho_t$ is the density of $\eta_t$, if it has a density.
-
-\comment{
-    Point out that this is still with $\epsilon > 0$,
-    and put in heuristics for why $N \epsilon^d / \theta \to \infty$
-    and $\theta \epsilon^2 \to \infty$
-    are plausible conditions for the diagonal convergence.
-    (Because we want (a) a macroscopic number of neighbors relative to $\theta$,
-    and (b) to make the initial condition smooth enough
-    since we start with an $\epsilon^2$-smoothed initial condition,
-    and we want this to look like a bunch of $1/\theta$-jumps have already happened.
-}
-
+where $\varphi_t$ is the density of $\eta_t$, if it has a density.
 On the other hand, if $N = \alpha \theta$ for some $\alpha > 0$,
@@
 
+\paragraph{One-step convergence:}
+In order to pass directly to a classical PDE limit
+in Theorem~\ref{thm:local_convergence}
+we impose the stronger condition
+that $\theta/N\epsilon^d\to 0$ and also require that
+$\theta\epsilon^2\to\infty$. 
+Recall that in this case, we take $\rho_F$ to be a Gaussian density with parameter 
+$\epsilon^2$. The condition $\theta\epsilon^2\to\infty$ 
+ensures that $\epsilon^2$ is large enough relative to $1/\theta$
+that the regularity gained by smoothing our population density by convolution with
+$p_{\epsilon^2}$ is preserved under the dynamics dictated by $q_{\theta}$.
+To understand the first condition, note that we are aiming to obtain a 
+deterministic expression for the limiting population density. 
+It is helpful to think
+about a classical Wright-Fisher model (with no spatial structure and just two types, say). 
+We know then that if the
+timescale $\theta$ is on the same order as population size $N$, we see stochastic
+fluctuations in the frequencies of the two types in the limit as $N\to\infty$; to 
+obtain a deterministic limit, we look over shorter timescales relative to population
+size. In our setting, the total population size is replaced by the local population
+size, as measured by convolution with $p_{\epsilon^2}$, which we expect to be 
+of order $N\epsilon^d$, and so in order to ensure a deterministic limit we 
+take $\theta/(N\epsilon^d)\to 0$.
+
 % % % % % % % % % % % % % % % % % %
@@
 uses the explicit representation in terms of the lookdown process,
-informal calculations agree with the main result.
-Suppose that we have tracked a lineage back to an individual at location $y$ at time $t$.
-Looking further back through time, the lineage will move at the time that individual was born,
-and will jump to that individual's parents' locations.
-Now, the rate at which new individuals are born to parents at $x$ and establish at $y$
-is
+the result can be understood through informal calculations.
+Suppose that we have traced a lineage back to an individual 
+at location $y$ at time $t$.
+Looking further back through time, at the time of the birth of that 
+individual, the lineage will jump to the location of the parent of the
+individual.
+Now, the rate at which new individuals are born to parents at $x$ 
+and establish at $y$ is
 $$
-    \gamma(x, \eta_t) q(x, dy) r(y, \eta_t) .
+\theta N\eta^N_t(dx)    \gamma(x, \eta^N_t) q(x, dy) r(y, \eta^N_t) .
 $$
-\comment{TODO: explain this more.}
-Happily, we are interested in the case when $\eta$ has a density,
-say $\eta_t(dx) = \varphi_t(x) dx$,
-so interpreting these rates is not too difficult.
-This implies that the probability a randomly chosen individual near $y$
-is a new offspring from a parent at $x$ in $[t, t+dt)$ is, informally,
+Suppose that $\eta^N$ did have a density (in the prelimit it does not),
+say $\eta^N_t(dx) = \varphi^N_t(x) dx$. Informally, the 
+probability that a randomly chosen individual near $y$
+is a new offspring from a parent at $x$ in $[t, t+dt)$ is
 \begin{equation} \label{eqn:informal_rates}
-\frac{
-    \gamma(x, \eta_t) r(y, \eta_t) \varphi_t(x)
+\frac{\theta
+    \gamma(x, \eta^N_t) r(y, \eta^N_t) \varphi^N_t(x)
 }{
-    \varphi_t(y)
+    \varphi^N_t(y)
 } \frac{ q_\theta(x, dy) }{ dy } dx dt .
 \end{equation}
-Leaving aside questions of whether a lineage can be treated as a randomly chosen individual,
-we might then proceed by defining a continuous-time jump process
-whose transition rates are given by \eqref{eqn:informal_rates} given $(\varphi_t)_{t=0}^T$.
-Let $(L^N_s)_{s=0}^T$ be the location of a lineage that moves according to these jump rates,
-back through time (i.e., with the substitution that $s = T-t$).
-Then, for the moment writing $q_\theta(x, y)$ for the density of $q_\theta$,
+Leaving aside questions of whether a lineage can be treated 
+as a randomly chosen individual, we define
+a continuous-time jump process 
+whose transition rates, conditional on $(\varphi^N_t)_{t=0}^T$, 
+are given by \eqref{eqn:informal_rates}. Because we are tracing the
+lineage backwards 
+in time we make the substitution $s=T-t$ and write
+$(L^N_s)_{s=0}^T$ for the location of a lineage that moves 
+according to these jump rates.
+Then, abusing notation to write 
+$q_\theta(x, y)$ for the density of $q_\theta$,
 \begin{align} \label{eqn:lineage_generator_Edt}
     \begin{split}
-    &\IE[f(L^N_{s+ds}) - f(y) \;|\; L_s = y]
+    &\IE[f(L^N_{s+ds}) - f(y) \;|\; L^N_s = y]
     \\&\qquad 
     =
-    ds \int \left(f(x) - f(y)\right)
+    ds \theta \int \left(f(x) - f(y)\right)
     \frac{
-        \varphi_{T-s}(x) \gamma(x, \eta_{T-s}) r(y, \eta_{T-s})
+        \varphi^N_{T-s}(x) \gamma(x, \eta^N_{T-s}) r(y, \eta^N_{T-s})
     }{
-        \varphi_{T-s}(y)
+        \varphi^N_{T-s}(y)
     }
@@
 \end{align}
+(Note that this integral is with respect to $x$.)
 Referring back to Definition~\ref{def:dispersal_generator},
 a quick calculation shows that as $N \to \infty$,
-\begin{align*}
-    \theta \int (f(x) - f(y)) q_\theta(x, y) dx
-    &\to
-    \DG^* f(x)  - f(x) \DG^* 1 .
-\end{align*}
-Consequently,
+%\begin{align*}
+%    \theta \int (h(x) - h(y)) q_\theta(x, y) dx
+%    &\to
+%    \DG^* h(y)  - h(y) \DG^* 1 .
+%\end{align*}
+%Consequently,
 \begin{align*}
@@
 
-Now we will present a lookdown construction for the general process
-(i.e., of Definition \ref{defn:mgale_construction}),
+Our characterisation of the motion of lines of descent (from which we establish
+that of ancestral lineages) when we pass
+to the scaling limit in our model will be justified via a lookdown construction.
+In this section 
+we present a lookdown construction for the general population model 
+of Definition~\ref{defn:mgale_construction}. It will be
 in the spirit of~\cite{kurtz/rodrigues:2011}. 
 The general set-up is as follows.
-Each individual will be labeled with a ``level'',
+Each individual will be labelled with a ``level'',
 which will be a number in $[0, N]$.
@@
 Note that each individual contributes mass 1 to the measure,
-not $1/N$ as above.
-In some sense, these levels do not affect the process:
-the pushforward of this measure-valued ``spatial-level process'',
-divided by $N$,
-will agree with the purely spatial process defined above.
-Furthermore, at any time, the levels of the individuals present at any spatial location
+not $1/N$ as above. If we assign mass $1/N$ to each individual and 
+ignore the levels we will recover our population model. 
+Moreover, at any time, the levels of 
+individuals in a given spatial region 
 will be exchangeable and conditionally uniform on $[0, N]$:
-in particular, choosing the $k$ individuals with the lowest level in some region of space
-at some time is equivalent to taking a uniform random draw of size $k$ from the individuals in that region
-for the purely spatial process.
-However, an individual's level in some sense encodes their future reproductive output:
+in particular, choosing the $k$ individuals with the lowest levels 
+in that region
+is equivalent to taking a uniform random sample of size $k$ 
+from the population in the region.
+However, an individual's level 
+encodes information about their future reproductive output;
 individuals with lower levels tend to live longer, and have more offspring.
 For more explanation of the set-up and how this is possible,
-see \citet{etheridge/kurtz:2018} and \citet{kurtz/rodrigues:2011}
+see \citet{kurtz/rodrigues:2011} and \citet{etheridge/kurtz:2018} 
 (and note that our $N$ corresponds to the $\lambda$ of those papers).
-Furthermore, the limiting spatial-level process will still be a point measure,
-and so we explicitly retain the notion of individuals and lineages through to the 
-large-population-density limit.
+The power of this approach is that we can pass to a limit under the
+same scalings as described in Theorem~\ref{thm:nonlocal_convergence}, 
+and 
+the limiting ``spatial-level'' process will still be a point measure.
+In this way, 
+we explicitly retain the notion of individuals and lineages as we pass to the 
+infinite-population limit.
 
 % % % % % % % % % % % % % % % %
-\subsection{Lookdown construction of the population density process}
+\subsection{Lookdown representation of the model of 
+Definition~\ref{defn:mgale_construction}}
 \label{sec:lookdown_defn}
 
+For the remainder of this section, when there is no risk of ambiguity we shall
+suppress the superscript $N$ on the processes $\eta$ and $\xi$.
 In this section,
-we'll define the process $(\lp_t)_{t \ge 0}$ in terms of the dynamics of labeled particles,
+we'll define the process $(\lp_t)_{t \ge 0}$ in terms of the 
+dynamics of labelled particles,
 and write down its generator.
-Since the dynamics depend on the spatial locations of particles,
-in this section we define $\eta_t$ to be the corresponding spatial measure,
+The dynamics depend on the spatial locations of particles,
+and in this section $\eta_t$ is the corresponding spatial measure,
 i.e.,
@@
 A nontrivial consequence of the way we define $\lp_t$ will be that
-this process has the same distribution as the process $(\eta_t)_{t \ge 0}$ defined above
-in Definition~\ref{defn:mgale_construction}.
+this process has the same distribution as the process $(\eta_t)_{t \ge 0}$ 
+of Definition~\ref{defn:mgale_construction}.
 (This provides our justification for using the same notation for both.)
 
-As before, we first describe the dynamics of individuals
-in the original time units -- i.e., before scaling by $\theta$,
-which will be introduced below.
-Suppose that the initial population is composed of $O(N)$ many particles
-with levels uniformly distributed between $[0, N]$.
-Suppose the current state of the population is $\lp$,
+We describe the representation of the scaled process.
+Following~\cite{etheridge/kurtz:2018}, we build the generator step by step
+from its 
+component parts. 
+Suppose that the initial population is composed of $O(N)$ particles
+with levels uniformly distributed between $[0, N]$,
+and that the current state of the population is $\lp$,
 with spatial projection $\eta$.
@@
 $$
-2 \left(1 - \frac{u}{N}\right) \gamma(x, \eta) ,
+2 \theta \left(1 - \frac{u}{N}\right) \gamma(x, \eta) ,
 $$
-which disperses to a location relative to $x$ drawn from the kernel $q(x, \cdot)$.
-(Averaging over the uniform distribution of the level $u$,
-we recover the birth rate $\gamma(x, \eta)$.)
-This juvenile -- suppose it's location is $y$ --
+which disperses to a location relative to $x$ drawn 
+from the kernel $q_{\theta}(x, \cdot)$.
+Averaging over the uniform distribution of the level $u$,
+we recover the birth rate $\theta\gamma(x, \eta)$.
+This juvenile -- suppose its location is $y$ --
 either survives, with probability $r(y, \eta)$, or immediately dies.
@@
 A new level $u_1$ is sampled independently and uniformly from $[u,N]$,
-and the parent and the offspring are assigned in random order to the levels $\{u, u_1\}$.
+and the parent and the offspring are assigned in random order to the 
+levels $\{u, u_1\}$.
 This random assignment of levels to parent
-and offspring ensures that conditional on $\eta$,
-the levels of each individual at any point in time are independent, uniform random variables.
+and offspring will ensure that assignment of individuals to levels will
+be exchangeable.
 
@@
 of individuals with higher levels.
-To restore the property that,
-conditional on $\eta$,
-the distribution of levels is conditionally uniform,
+To restore the property that
+the distribution of levels is conditionally uniform
+given $\eta$,
 we impose that 
-the level of an individual at location $x$
+the level $v$ of an individual at location $x$
 evolves according to the differential equation
@@
     % \gamma^{\mathfrak{m}}(x, \eta) \left\{N^{-1}(N -v)^{2} -(N -v)\right\}.
-    - \frac{v}{N} \left(N - v\right)
-    \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q(x, dy) .
+    -\theta \frac{v}{N} \left(N - v\right)
+    \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q_\theta(x, dy) .
 $$
@@
 while particles whose levels move above $N$ are regarded as dead
-(and do not affect to the population any more).
+(and are removed from the population).
 Therefore, in order to incorporate death,
 the level of the individual at location $x$ with level $u$
-moves upwards at an additional rate $\mu(x,\eta) u$.
+moves upwards at an additional rate $\theta\mu_\theta(x,\eta) u$.
 Since levels are uniform,
-it is easy to check that if $\mu$ were constant,
+it is easy to check that if $\mu_\theta$ were constant,
 this would imply an exponential lifetime for each individual;
-see~\cite{etheridge/kurtz:2018}, Section \comment{TODO}
+see~\cite{etheridge/kurtz:2018}, Section~3.1
 for more general justification.
@@
     =
-    - \frac{1}{N} u \left(N - u\right)
-    \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q(x, dy) 
+    - \theta\frac{1}{N} u \left(N - u\right)
+    \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q_\theta(x, dy) 
     +
-    \mu(x,\eta) u .
+    \theta\mu_\theta(x,\eta) u .
 \end{equation}
@@
 $$
-    b(x, \eta)
+    b_\theta(x, \eta)
     :=
     \theta\left(
-    \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy)
+    \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q_\theta(x, dy)
     -
-    \mu(x,\eta)
+    \mu_\theta(x,\eta)
     \right) ,
 $$
-which captures the local net difference between reproduction and death,
-i.e., the deviation from criticality of the branching mechanism.
+which captures the local net difference between reproduction and death.
+%i.e., the deviation from criticality of the branching mechanism.
 Recall from equation \eqref{eqn:mu_defn} that
-$F(x,\eta) = \theta(r(x,\eta)\gamma(x,\eta) - \mu(x,\eta))$,
-and so we will have that
-\begin{align} \label{eqn:b_limit}
-\begin{split}
-b(x, \eta)
-&=
-    \theta \gamma(x, \eta) \int_{\IR^d} \left( r(y, \eta) - r(x, \eta) \right) q(x, dy)
-    + F(x, \eta) \\
-&\to
-    \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta) \qquad \text{as } \theta \to \infty .
-\end{split}
-\end{align}
+$F(x,\eta) = \theta(r(x,\eta)\gamma(x,\eta) - \mu_\theta(x,\eta))$,
+and so 
+\begin{equation*} 
+b_\theta(x, \eta)
+=    \theta \gamma(x, \eta) \int_{\IR^d} \left( r(y, \eta) - r(x, \eta) \right) 
+	q_\theta(x, dy)
+    + F(x, \eta). 
+\end{equation*}
+Under Assumptions~\ref{def:model_setup}
+this will tend to
+\begin{equation}
+\label{eqn:b_limit}
+    \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta)
+\end{equation}
+as $\theta \to \infty$.
 
 We can then rewrite the differential equation 
-governing how the level of each individual evolves as
+governing the dynamics of the level of each individual as
 \begin{align}
@@
     &=
-    \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy)
+    \theta\gamma(x,\eta) \int_{\IR^d} r(y, \eta) q_\theta(x, dy)
     \left\{
@@
     -
-    b(x,\eta) u / \theta
+	b_\theta(x,\eta) u
     \nonumber \\
     &=
-    \frac{1}{N} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
+    \frac{\theta}{N} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
     -
-    b(x, \eta) u / \theta
+	b_\theta(x, \eta)u
     . \label{differential equation for level}
@@
 In what follows, we will write sums (and, products) over ``$(x, u) \in \xi$''
-to mean as a sum over the (location, level) pairs of each individual in the population.
-Test functions for $\lp$ then take the form
+to mean a sum over the (location, level) pairs of each individual in the population.
+Test functions for $\lp$ will take the form
 \begin{equation} \label{eqn:test_functions}
@@
 
-Recall that just as with $\eta_t$, in defining $(\lp_t)_{t \ge 0}$
-we sped up time by a factor of $\theta$.
-As a result, per-capita rates below will have a factor of $\theta$
-not present in the expressions above.
-
 First consider the terms in the generator that come from birth events.
@@
 \begin{align}
+\label{partition over level assignment}
     &
@@
     \right)
-    r(y, \eta) q(x, dy)
+    r(y, \eta) q_\theta(x, dy)
     du_1
@@
         \frac{
-            \theta \int_{\IR^d} (g(y, u) - g(x, u)) r(y, \eta) q(x, dy)
+            \theta \int_{\IR^d} (g(y, u) - g(x, u)) r(y, \eta) q_\theta(x, dy)
         }{
@@
         \left( \frac{g(y, u_1) + g(x, u_1)}{2} - 1 \right)
-        r(y, \eta) q(x, dy)
+        r(y, \eta) q_\theta(x, dy)
         du_1
@@
 \end{align}
-Here, $u_1$ is the new level and $y$ is the offspring's location,
+In (\ref{partition over level assignment}),
+$u_1$ is the new level and $y$ is the offspring's location,
 and so the two terms in the integral correspond to the two situations:
@@
 by one at $(x, u_1)$ and another at $(y, u)$.
-We've rewritten it in this form because the two pieces
-each naturally converge to separate terms in the limit.
-
-The remaining term in the generator is due to the motion of particles' levels,
-mapping $f(\xi)$ to
+We've rewritten it in the form~(\ref{eqn:birth_generator})
+because each of the two pieces
+naturally converges to a separate term in the limit.
+
+The remaining term in the generator is due to the motion of particles' levels.
+Reading off from~(\ref{differential equation for level}),
+it takes the form
 \begin{align} \label{eqn:level_generator}
@@
     \frac{\theta}{N}
-        \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
+        \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q_\theta(x, dy) u^2
         -
-        b(x, \eta)u
+        b_\theta(x, \eta)u
     \right)
@@
 with initial condition $\lp_0$ and generator $A^{N}$ that satisfies
-\begin{equation*}
+\begin{equation}
+	\label{eqn:lookdown_generator}
 \begin{split}
@@
 \end{split}
-\end{equation*}
-for all smooth functions $g \in C^{2}_{0}(\IR^d)$,
-where $f(\lp) = \prod_{(x, u) \in \lp} g(x, u)$ as defined in \eqref{eqn:test_functions},
-and $\eta(\cdot) = \lp(\cdot \times [0, N]) / N$ is the scaled spatial pushforward of $\lp$,
+\end{equation}
+where $f(\lp) = \prod_{(x, u) \in \lp} g(x, u)$ is as defined in \eqref{eqn:test_functions},
+and $\eta(\cdot) = \lp(\cdot \times [0, N]) / N$
 as before.
@@
 
-Since everything is finite,
-it is clear that the martingale problem for finite $N$ has a unique solution.
+The martingale problem for finite $N$ has a unique solution.
 Next we state the limiting martingale problem,
-for which we do not have uniqueness (although we construct an explicit solution later).
-
-\begin{definition}[Martingale Problem Characterisation, $N=\infty$]
+for which we do not have uniqueness.
+%(although we construct an explicit solution later).
+As before, the parameter $\alpha$ will correspond to 
+$\lim_{N\to\infty}\theta(N)/N$. Whereas for finite $N$, conditional
+on the population process $\eta_t^N$, the levels of particles are
+independent and 
+uniformly distributed on $[0,N]$, in the infinite population limit, 
+conditional on $\eta_t$ the process $\xi_t$ is 
+Poisson distributed on 
+$\IR^d\times [0,\infty)$ with mean measure $\eta_t\times\ell$, where $\ell$
+is Lebesgue measure.
+
+\begin{definition}[Martingale Problem Characterisation, scaling limit]
     \label{defn:limiting_lookdown_mgale}
-    For a given value of $\alpha \in [0, \infty)$,
-    define the operator $A$ acting on test functions of the form
-    $f(\xi) = \prod_{(x, u) \in \xi} g(x, u)$ with $g \in C_0^2(\IR^d \times [0, \infty)$
-    and for which there exists a $u_0$ with $g(x, u) = 1$ for all $u > u_0$.
-    Then, let $A f$ be
+    Fix $\alpha \in [0, \infty)$, and define  
+    test functions $f$ by 
+    $f(\xi) = \prod_{(x, u) \in \xi} g(x, u)$ 
+	with $g$ differentiable in $u$, smooth in $x$, satisfying 
+$0\leq g(x,u)\leq 1$ and
+    such that there exists a $u_0$ with $g(x, u) = 1$ for all $u > u_0$.
+    Then, define the operator $A$ on such test functions by 
     \begin{align} \begin{split} \label{eqn:limiting_lookdown_generator}
@@
     \end{split} \end{align}
-    We say that a $\lpmeasures$-valued process $(\xi_t)_{t \ge 0}$
+    Write ${\cal C}(\IR^d\times [0,\infty))$ for the point measures on $\IR^d\times [0,\infty)$.
+We say that a ${\cal C}(\IR^d\times [0,\infty))$-valued process $(\xi_t)_{t \ge 0}$
     is a solution to the $(A, \lp_0)$ martingale problem
     if it has initial distribution $\lp_0$
-    and $f(\lp_t) - \int_0^t Af(\lp_s) ds$ is a martingale for all $f$
+    and $f(\lp_t) - f(\lp_0)-\int_0^t Af(\lp_s) ds$ is a martingale for all 
+test functions $f$
     as defined above.
@@
 
-\comment{We talked about having the next paragraph be a Proposition or something?}
+\comment{We talked about having the next paragraph be a Proposition or something?
+I am putting off rewriting this paragraph until I know what has been proved.}
 
 The lookdown processes have been carefully constructed so that
-if we average over levels in the expression for the lookdown generator
+past observations about the spatial positions of individuals in 
+the population do not give us any information about the assignment of 
+individuals to levels. In other words, the dynamics of the lookdown
+process preserve the conditionally uniform (resp.~conditionally Poisson)
+structure.
+Moreover, if we average over levels in the expression for the generator
 (equation~\eqref{eqn:lookdown_generator} or~\eqref{eqn:limiting_lookdown_generator})
-we get the generator for the population process
-(visible in equation~\eqref{eqn:eta_martingale}
-or~\eqref{eqn:limiting_mgale_problem}, respectively).
-Once this is verified (and some boundedness conditions)
-in Appendix \ref{sec: Markov Mapping Theorem Application},
+we recover the generator for the population process.
+%(visible in equation~\eqref{eqn:eta_martingale}
+%or~\eqref{eqn:limiting_mgale_problem}, respectively).
+Once this is verified (along with some boundedness conditions)
+in Appendix~\ref{sec: Markov Mapping Theorem Application},
+\comment{Refer more precisely}
 the Markov Mapping Theorem \citep[Thm A.2 in][]{etheridge/kurtz:2018}
-tells us that for any population process $(\eta^N_t)_{t \ge 0}$
-(i.e., solution to the martingale problem of Definition~\ref{defn:mgale_construction})
+tells us that by ``removing labels'' in this way we recover the Markov
+process describing our population.
+In particular, for any %population process $(\eta^N_t)_{t \ge 0}$
+%(i.e.,
+solution to the martingale problem of Definition~\ref{defn:mgale_construction})
 % of equations~\eqref{eqn:eta_martingale} and \eqref{eqn:prelimit_martingale_variation}
-there is a lookdown representation $(\lp^N_t)_{t \ge 0}$
-(i.e., solution to the martingale problem of Definition~\ref{defn:lookdown_mgale})
-for which $\eta^N_t(\cdot) = \lp^N_t(\cdot \times [0, N])$
-and such that at each $t$, conditioned on $(\eta^N_s){s \le t}$, the levels of $\lp_t^N$
+there is a % lookdown representation $(\lp^N_t)_{t \ge 0}$
+%(i.e., 
+solution to the martingale problem of Definition~\ref{defn:lookdown_mgale})
+for which $\eta^N_t(\cdot) = \lp^N_t(\cdot \times [0, N])/N$
+and such that at each $t$, conditioned on $(\eta^N_s)_{s \le t}$, the levels of $\lp_t^N$
 are independently and uniformly distributed on $[0, N]$.
-The same property holds in the limit:
-for any solution $(\eta_t)_{t \ge 0}$ to the martingale problem of Theorem~\ref{nonlocal_convergence}
-there is a lookdown process $(\lp^N_t)_{t \ge 0}$
-that is a solution to the martingale problem of Theorem~\ref{lookdown_convergence}
+Similarly, in the scaling limit:
+for any solution $(\eta_t)_{t \ge 0}$ to the martingale problem of 
+Theorem~\ref{nonlocal_convergence}
+%there is a lookdown process $(\lp^N_t)_{t \ge 0}$
+there is a solution to the martingale problem of Theorem~\ref{lookdown_convergence}
 for which $\eta_t(\cdot) = \lim_{u_0 \to \infty} \frac{1}{u_0} \lp_t(\cdot \times [0, u_0))$
-and such that at each $t$,
-$\lp_t$ is conditionally Poisson with Cox measure $\eta_t(dx) \times du$,
-conditioned on $(\eta_s)_{s \le t}$.
+and such that at each $t$, conditional on $(\eta_s)_{s\leq t}$, 
+$\lp_t$ is conditionally Poisson with mean measure $\eta_t(dx) \times du$.
 Furthermore, convergence of the lookdown processes would imply convergence of the population processes
-\citep[Thm A.9 in][]{KR}.
+\citep[Thm A.9 in][]{kurtz/rodrigues:2011}.
 
@@
 to Theorem~\ref{thm:nonlocal_convergence} for the population process.
+
+\comment{the next theorem needs rewriting along the lines of Thm A.12 in 
+Kurtz and Rodrigues.}
 
@@
 
-\comment{TODO: remove this next bit?}
-
-In Appendix \ref{sec: Markov Mapping Theorem Application},
-we will show that
-if we define $\Gamma (d\textbf{u})$
-as the probability kernel that corresponds to
-assigning each particle an i.i.d. uniform $[0,N]$-level,
-and for any $\lp \in \mathcal{M}_f(\IR^d \times [0,\infty))$, we denote
-$$\hat{f}(\lp)=\int f(\lp) \Gamma (d\textbf{u})$$ 
-to be the spatial test functions with averaged level,
-then the process
-\begin{equation}
-\begin{aligned}
-M^{N}_t:=&\hat{f}(\lp_t)-\hat{f}(\lp_0)-\int_{0}^{t}\int   A^{N}f(\lp_s)\Gamma(d\textbf{u})ds\\
-:=&\hat{f}(\lp_t)-\hat{f}(\lp_0)-\int_{0}^{t}   \Pgen^{N}\hat{f}(\lp_s)ds
-\end{aligned}    
-\end{equation}
-is a martingale.
-
-By the Markov Mapping Theorem,
-there exists a solution $(\lp^{N}_t)_{t \geq 0}$
-to the Martingale Problem with generator $A^{N}$.
-Furthermore,
-the spatial projection of $(\lp^{N}_t)_{t \geq 0}$
-shares the same law of $(\eta^{N}(t))_{t \geq 0}$,
-i.e.
-$$(\eta^{N}(t))_{t \geq 0}
-\sim \left(\frac{1}{N}\sum\limits_{(X(t),U(t))\in \lp^{N}(t)} \delta_{X(t)}\right)_{t \geq 0},$$
-and conditional on 
-$(\eta^{N}(t))_{t \geq 0}$,
-the levels of particles in $(\lp^{N}_t)_{t \geq 0}$
-are i.i.d. uniformly distributed between $[0,N]$.
-
 %% %% %% %% %% %% %% %% %% %% %% %%
@@
 
-In this section we explicitly construct the lookdown process
-in a way that explicitly represents the motion of each individual and their offspring.
-This provides an explicit construction of the solution to
-the limiting martingale problem~\ref{defn:limiting_lookdown_mgale}.
-It will furthermore make it obvious how lineages move in the limit,
-and will allow us to identify all 
+The main interest in using a lookdown construction for our population
+processes is that it allows us to retain information about the 
+relatedness of individuals as we pass to the infinite population limit.
+In order to exploit this, in this section we write down stochastic 
+equations for the locations and levels of individuals in the lookdown
+representation of the prelimiting model.
+We will then be able to pass to the scaling limit.
+This explicit description of the solution to
+the limiting martingale problem of Definition~\ref{defn:limiting_lookdown_mgale}
+will enable us to identify all 
 individuals in the current population that are descendants of a
@@
 sampled from the present day population. This idea draws on the notion
-of `tracers', popular in statistical physics and used in population
+of ``tracers'', popular in statistical physics and used in population
 genetics by a number of authors including 
@@
 
-We will construct the process using a Ulam-Harris indexing scheme,
-which associates the outcomes of each branching event with a label obtained
-by appending to the previous label.
-To begin, we assign each extant individual a label from $\IN_{\ge 0}$.
+We will construct the process using a Ulam-Harris indexing scheme.
+First, we assign each extant individual a unique label from $\IN_{\ge 0}$.
 Suppose an individual with label $a$ and level $u$ reproduces,
@@
 retaining the label $a$ for the individual with the old level $u$.
-So, there is a unique label assigned at each birth event,
+In this way, at each birth event, a unique label is 
 assigned to the resulting individual with the higher level,
 and the label of an individual may change throughout its lifetime.
-It would be possible to reconstruct individual identities along a line of descent
-from this construction,
-but we don't write this out.
-
-\comment{Perhaps the following is confusing having $t$ for the point of $\Pi_a$,
-and we should instead use... $\tau$?}
 
 Concretely, then: for each label $a$ in
-$\labelspace = \bigcup_{k \ge 1} \IN_{\ge 1}^k$
-let $\Pi_a$ be an independent Poisson process on $[0, \infty)^2 \times \IR_d \times \{0,1\}$.
-The mean measure of each $\Pi_a$ is a product of Lebesgue measure on the first two coordinates,
-the density of the standard Gaussian $N(0,1)$ on $\IR^d$, and $(\delta_0 + \delta_1)/2$ on $\{0, 1\}$.
+$\labelspace = \bigcup_{k \ge 1} \IN_{\ge 1}^k$,
+let $\Pi_a$ be an independent Poisson process on 
+$[0, \infty)^2 \times \IR^d \times \{0,1\}$.
+The mean measure of each $\Pi_a$ is a product of Lebesgue 
+measure on the first two coordinates,
+the density of the standard Gaussian $N(0,1)$ on $\IR^d$, and 
+$(\delta_0 + \delta_1)/2$ on $\{0, 1\}$.
 It will also be convenient
@@
 although the precise order of this enumeration is irrelevant.
-If $(t, v, z, \kappa)$ is the $j^\text{th}$ point in $\Pi_a$,
-then $t$ will determine a possible birth time,
+If $(\tau, v, z, \kappa)$ is the $j^\text{th}$ point in $\Pi_a$,
+then $\tau$ will determine a possible birth time,
 $v$ will determine the level of the offspring,
@@
 Now, since we have defined labels so that the level does not jump,
-$U_a$ satisfies~\eqref{eqn:dot_u} for $\tau_a \le t \le \sigma_a$, i.e.,
+$U_a$ satisfies~\eqref{differential equation for level}
+	for $\tau_a \le t \le \sigma_a$, i.e.,
 \begin{equation} \label{eqn:U_line_of_descent}
@@
 
-Potential reproduction events occur at times $t$
-for each point $(t, v, w, \kappa) \in \Pi_a$ with $t \ge \tau_a$.
-We say `potential' since if the resulting level is greater than $N$,
+Potential reproduction events occur at times $\tau$
+for each point $(\tau, v, z, \kappa) \in \Pi_a$ with $\tau \ge \tau_a$.
+We say ``potential'' since if the resulting level is greater than $N$,
 the event does not happen.
 If this is the $j^\text{th}$ point in $\Pi_a$,
-the new label is $a \concat j$, the (potential) birth time is $\tau_{a \concat j} = t$.
-Similarly, the potential birth location is $y(X(t-), z)$, where
+the new label is $a \concat j$, the (potential) birth time is $\tau_{a \concat j} = \tau$.
+Similarly, the potential birth location is $y(X(\tau-), z)$, where
 $$
@@
 $$
-where $K(x)K^{T}(x) = \covq(x)$.
-
-Next we must choose the level of the offspring.
-We would like the individual to produce offspring at $y$ at rate
-$2 (1 - u/N) \theta \gamma(x, \eta) r(x + y, \eta)$,
-and to do this
-we will associate the point $(s, v, w, \kappa) \in \Pi_a$ with level $u + v \ell$,
-where $\ell$ is chosen so that this is the rate of appearance of points in $\Pi_a$
-with level below $N$.
-Since the mean measure of $\Pi_a$ is Lebesgue in the $t$ and $v$ directions,
-this requires that $v < (N - u) / \ell$, 
-and so such points appear at rate $(N-u)/\ell$.
-Therefore, we define
-$$
+and $K(x)K^{T}(x) = \covq(x)$.
+
+Next we must choose the new level created at the birth event.
+We would like an individual with level $u$ and at spatial position $x$
+to produce offspring at $y$ at instantaneous rate
+\begin{equation}
+	\label{rate of birth}
+	2 \Big(1 - \frac{u}{N}\Big) \theta \gamma(x, \eta) r(x + y, \eta).
+\end{equation}
+To do this
+we will associate the point $(\tau, v, z, \kappa) \in \Pi_a$ with 
+level $u + v \ell$,
+where $\ell$ is chosen so that the rate of appearance of points in 
+$\Pi_a$ with level below $N$, that is points with
+$\ell v<N-u$, is given by~(\ref{rate of birth}).
+Since the mean measure of $\Pi_a$ is Lebesgue measure
+in the $t$ and $v$ directions, we must take
+\begin{equation}
+	\label{expression for ell}
     \ell(x, y, \eta)
     =
-    \frac{
-        1
-    }{
-        2 N^{-1} \theta \gamma(x, \eta) r(x + y, \eta)
-    } ,
-$$
+    \frac{N-u}{2 (1-u/N) \theta \gamma(x, \eta) r(x + y, \eta) } 
+    =\frac{1}{2N^{-1} \theta \gamma(x, \eta) r(x + y, \eta) } 
+    ,
+\end{equation}
 and using this, the (potential) new level is
 \begin{equation*}
-    U_{a \concat j}(t)
+    U_{a \concat j}(\tau)
     =
-    U_a(t)
+    U_a(\tau)
     +
-    v \ell(X_a(t-), y(X_a(t-), z), \eta(t-)) .
+    v \ell(X_a(\tau-), y(X_a(\tau-), z), \eta(\tau-)) .
 \end{equation*}
-If $U_{a \concat j}(t) < N$,
+If $U_{a \concat j}(\tau) < N$,
 the new individual labeled $a \concat j$ is produced,
-and $\kappa$ determines which label is associated with the new location,
+and $\kappa$ determines which label, $a$ or $a\concat j$,
+is associated with the new location,
 so
 \begin{align*}
-    X_{a \concat j}(t)
+    X_{a \concat j}(\tau)
     &=
-    X_a(t-) + (1 - \kappa) y(X_a(t-), z) .
+    X_a(\tau-) + (1 - \kappa) y(X_a(\tau-), z) .
 \end{align*}
 On the other hand
-if $U_{a \concat j}(t) \ge N$, then $X_a$ is unchanged and $X_{a \concat j}$ is undefined,
+if $U_{a \concat j}(\tau) \ge N$, then $X_a$ is unchanged and 
+$X_{a \concat j}$ is undefined,
 so
 \begin{align} \label{eqn:X_line_of_descent}
-    X_a(t)
+    X_a(\tau)
     &=
-    X_a(t-) + \kappa y(X_a(t-), z) \ind_{U_{a \concat j}(t) < N} .
+    X_a(\tau-) + \kappa y(X_a(\tau-), z) \ind_{U_{a \concat j}(\tau) < N} .
 \end{align}
@@
 and our line of descent switching to the offspring.
-Combining these, $X_a$, for $\tau_a \le T < \sigma_a$, solves the equation 
-\begin{align*}
-    X_a(T)
+Combining these, $X_a$, for $\tau_a \le t < \sigma_a$, solves the equation 
+\begin{align*}
+    X_a(t)
     &=
-    \int_{[\tau_a, T) \times [0, \infty) \times \IR \times [0, 1]}
-    y(X_a(t-), z)
+    \int_{[\tau_a, t) \times [0, \infty) \times \IR \times [0, 1]}
+    y(X_a(\tau-), z)
     \kappa
     \ind_{
-        U_a(t) + v \ell(X_a(t-), y(X_a(t-), z), \eta_t)
+        U_a(\tau) + v \ell(X_a(\tau-), y(X_a(\tau-), z), \eta_{\tau-})<N
     }
-    d\Pi_a(s, v, z, \kappa) .
+    d\Pi_a(\tau, v, z, \kappa) .
 \end{align*}
@@
 Although we have described the evolution of a line of descent only for a given label
-(i.e., for $\tau_a \le s < \sigma_a$),
-we can extend the definition to earlier times
-by setting for $0 \le s < \sigma_a$
-$X_a(s)$ equal to $X_{[a]_s}(s)$,
-where $[a]_s$ is the label of the ancestor of label $a$ alive at time $s$,
-and similarly for $U_a(s)$.
+(i.e., for $\tau_a \le t < \sigma_a$),
+we can extend the definition to times
+$0 \le t < \sigma_a$ by setting
+$X_a(t)$ equal to $X_{[a]_t}(t)$,
+where $[a]_t$ is the label of the ancestor of label $a$ alive at time $t$,
+and similarly for $U_a(t)$.
 It is then straightforward, albeit tedious,
-to write down the time evolution of $(X_a(s), U_a(s))$ for all time back to $s=0$
+to write down the time evolution of $(X_a(t), U_a(t))$ for all time back 
+to $t=0$
 in terms of the driving Poisson processes.
-Although at finite $N$ the spatial process $X_a(s)$ is affected by jumps in the level $U_a(s)$,
-we will see that in the $N \to \infty$ limit
-the behavior of $X_a(s)$ is not affected by these jumps.
 
@@
 \begin{align*}
-    \eta^N_s = \frac{1}{N} \sum_{a : \tau_a \le s < \sigma_a} \delta_{X_a(s)}
+    \eta^N_t = \frac{1}{N} \sum_{a : \tau_a \le t < \sigma_a} \delta_{X_a(t)}
     \qquad \text{and} \qquad
-    \lp^N_s = \sum_{a : \tau_a \le s < \sigma_a} \delta_{(X_a(s), U_a(s))} .
-\end{align*}
-
-\comment{TODO: explain a bit more about the infinitely many points in the $v$ direction.}
-
-\comment{
+    \lp^N_t = \sum_{a : \tau_a \le t < \sigma_a} \delta_{(X_a(t), U_a(t))} .
+\end{align*}
+
+\begin{remark}
     Note here that although we have a single construction that couples
-    the processes across all $N$,
-    we don't necessarily have pointwise a.s.\ convergence of trajectories of the process.
-    Furthermore, individuals at all levels may affect others through the population process,
-    and in the deterministic case arbitrarily high levels may drift downwards.
-    HOWEVER, this does suggest that a good approximation to the genealogies
-    might be obtained by simulating up until a sufficiently high level
+    the processes across all $N$, the actual 
+trajectories do not necessarily coincide for 
+different values of $N$, since they are affected by the whole 
+population process.
+    However, this does suggest approximating the genealogies
+    by simulating up until a sufficiently high level
     that we have a good approximation to the population process.
-}
+\end{remark}
 
 % % % % % % % % % % % % %  % % %
-\subsubsection{Lines of descent in the scaling limit}
-
-\comment{I don't think we need this.}
-
-We now write down expressions
-that give the spatial and level dynamic
-of a whole line of descent.
-In particular, our description is consistent
-for any $N \in \mathbb{N}$.
-
-Recall that
-the particle with label $(a_0,a_1,..,a_k)$
-is the offspring
-with a new level
-from the $a_k$-th potential birth
-of $(a_0,...,a_{k-1})$,
-who is again the offspring
-with a new level from
-the $a_{k-1}$-th potential birth
-of $(a_0,...,a_{k-2})$, 
-etc..
-In particular, 
-the particle with label $(a_0)$
-is the direct descendant of
-the $a_0$-th original ancestor
-of the whole population, i.e.
-it has never experienced
-a jump in level throughout
-its ancestry.
-
-For simplicity, for $a=(a_0,..,a_k)$,
-we denote $[a]_{i}:=(a_0,..,a_i)$
-to be the $i$-th generation 
-ancestor of the lineage $a$.
-In particular, if at time $t$,
-if the ancestral lineage $[a]_t$
-is at its $i(t)$-th generation,
-then $[a]_t = [a]_{i(t)}$.
-
-We also write 
-$(s_{[a]_{i}}, v_{[a]_{i}}, y_{[a]_{i}}, \kappa_{[a]_{i}})
-\in \Pi_{[a]_{i-1}}$
-to be the reproduction event
-that creates $[a]_{i}$ from $[a]_{i-1}$,
-and similarly,
-$(s_{[a]_{i} \concat j}, v_{[a]_{i} \concat j}, y_{[a]_{i} \concat j}, \kappa_{[a]_{i} \concat j})
-\in \Pi_{[a]_{i-1}}$
-to be the reproduction event 
-that creates $[a]_{i} \concat j$
-from $[a]_{i-1}$.
-
-We first write down an expression
-for the level of particle $a=(a_0,a_1,..,a_k)$ at time $t$.
-Since we ensure that
-the level of a particle
-only jumps when a reproduction event
-creates a new label,
-the level of particle $a=(a_0,a_1,..,a_k)$ is determined
-by $k$ many jumps,
-and subsequent continuous evolutions
-given by Equation \eqref{eqn:U_line_of_descent}.
-
-Under this notation, for $t> 0$,
-\begin{equation}
-\label{eq: level_across_lineage}
-\begin{aligned}
-&U^{N}_{[a]_{k}}(t)- U^{N}_{[a]_{0}}(0)\\
-=& \sum_{i=1}^{k} \int_{\tau_{[a]_{i-1}}}^{\tau_{[a]_{i}}}
-\left(
-        \frac{\theta}{N} \gamma(X_{[a]_{i-1}}(s),\eta_s)
-        \int_{\IR^d} r(z,\eta_s) q(X_{[a]_{i-1}}(s),dz) U_{[a]_{i-1}}(s)^2
-        -
-        b(X_{[a]_{i-1}}(s),\eta_s) U_{[a]_{i-1}}(s)
-    \right)
-    ds\\
-&+\int_{\tau_{[a]_{i}}}^{t}
-\left(
-        \frac{\theta}{N} \gamma(X_{[a]_{i}}(s),\eta_s)
-        \int_{\IR^d} r(z,\eta_s) q(X_{[a]_{i}}(s),dz) U_{[a]_{i}}(s)^2
-        -
-        b(X_{[a]_{i}}(s),\eta_s) U_{[a]_{i}}(s)
-    \right)
-    ds\\
-&+\sum_{i=1}^{k}
-    \left( \ell(X_{[a]_{i-1}}(\tau_{[a]_{i}}-), y_{[a]_{i}}, \eta(\tau_{[a]_{i}}-)) v_{[a]_{i}}
-    \right)
-\end{aligned}    
-\end{equation}
-where the first two terms correspond to
-sum of the evolution along the same generation,
-and the second term corresponds
-to the sum of jumps in levels
-when a new label is introduced.
-
-To preserve consistency 
-as we send $N \to \infty$
-in our scaling limit,
-we allow $U_{[a]_t}(t)$ to hit $\infty$.
-To identify dead lines of descent,
-for a label $a$,
-we define
-$\sigma_{a}^{N}:= \inf\{t \geq 0 : U_{[a]_t}(t) > N\}$.
-In the $N$-th scaling regime,
-we proclaim the individual
-$a$ to be dead
-at time $t$
-when $t > \sigma_{a}^{N}$
-
-Note that in particular,
-if $U_{[a]_i}(t)>N$
-at some time $t$
-in the $i$-th generation,
-then $U_{[a]_j}(t)>N$
-for all $j \geq i$
-and
-$\sigma_{[a]_j}^{N}=\sigma_{[a]_i}^{N}$.
-In words, all descendants of dead
-particles are dead by default.
-
-Similarly, we generalise the notion of death above
-to the infinity case by considering 
-$\sigma_{[a]_t}^{\infty}:=\inf\{t \geq 0 : U_{[a]_t}(t) =\infty\}$.
-
-\subsubsection{Spatial jumps along a whole line of descent}
-
-\comment{I also don't think we need this.}
-
-We now write down an expression for the
-spatial location of $[a]_t$ at time $t$.
-Note that in the spatial case,
-jumps occur along the same generation
-whenever $\kappa = 0$ in successful birth events,
-and occur across two generations
-whenever $\kappa = 1$ in successful birth
-events.
-
-To illustrate this, consider the spatial location of $(a_0,a_1)=(2,3)$ with birth time $\tau_{(2,3)}$ at some time $t>\tau_{(2,3)}$.
-If $U_{(2,1)}(\tau_{(2,1)}) < N$,
-the first birth event of the ancestor
-with label $(2)$
-is successful.
-If $\kappa = 0$ in this birth event,
-the parent and offspring swap labels,
-resulting in
-a spatial jump for the label $(2)$.
-On the contrary, 
-if $U_{(2,2)}(\tau_{(2,2)}) \geq N$
-or $\kappa = 1$
-in the second birth event of $(2)$,
-the parent does not give birth
-or retains its label,
-so there is no spatial jump.
-
-On the other hand, 
-if $\kappa=1$ when $(2,3)$ is born,
-the new label is given to
-the offspring
-with new spatial location,
-resulting in a jump,
-and vice versa.
-
-After $(2,3)$ is born,
-whenever the particle with label
-$(2,3)$ gives birth, 
-if $\kappa = 0$, the label $(2,3)$
-is adopted by the offspring
-which results in a spatial jump
-in the position of $(2,3)$
-again.
-
-Finally, we write $S(\tau_{[a]_k},t):=[\tau_{[a]_k},t]\times[0,\infty)\times\IR^d \times \{0,1\}$.
-Under this notation, for $t>\tau_{[a]_k}$,
-
-\begin{equation}
-\label{eq: space_across_lineage}
-\begin{aligned}
-&X^{N}_{[a]_{k}}(t)- X^{N}_{[a]_{0}}(0)\\
-=& \sum_{i=1}^{k}
-\sum_{j=1}^{a_i-1}
-(1-\kappa_{[a]_{i-1}\concat j}) y_{[a]_{i-1}\concat j} \ind_{U_{[a]_{i-1}\concat j}(\tau_{[a]_{i-1}\concat j}) < N}\\
-&+ \sum_{i=1}^{k}
-\kappa_{[a]_i} y_{[a]_i} \ind_{U_{[a]_i}(\tau_{[a]_i}) < N}\\
-&+\int_{S(\tau_{[a]_k},t)}
-(1-\kappa)y(z)
-\ind_{ \{
-        U_{[a]_k}(\tau_{[a]_k}+s)
-        + \ell(X_{[a]_k}(\tau_{[a]_k}+s),y,\eta_{[a]_k}(\tau_{[a]_k}+s)) v < N
-        \}
-      } 
-\Pi_{[a]_k}(dsdvdzd\kappa),
-\end{aligned}    
-\end{equation}
-where the first term
-corresponds to 
-the sum of $a_{i}-1$ many potential jumps
-in the $(i-1)-th$ generation;
-the second term corresponds to 
-the sum of $k$ many potential jumps
-when the $k$-th generation is introduced;
-and the last term
-corresponds to sum of 
-potential jumps that occured in
-the current generation from 
-time $\tau_{[a]_k}$
-to current time $t >\tau_{[a]_k}$.
 
@@
 
-The previous section constructs the lookdown process
-in a way that makes individual lines of descent converge pointwise as $N \to \infty$,
-using the same underlying Poisson processes $\{\Pi_a\}_{a \in \labelspace}$.
+The previous section constructed the lookdown process
+using the same underlying Poisson processes $\{\Pi_a\}_{a \in \labelspace}$ for
+different values of $N$.
+As a result, individual lines of descent converge pointwise as $N \to \infty$.
 To see this, first note that if the Poisson processes are fixed
 then the set of events to which a given label $a \in \labelspace$ is associated
-is also fixed -- this is the sequence $(s_k, v_k, y_k, \kappa_k)$ associated with a given label $a$.
-Therefore, the processes $\Pi_a$ are also unchanged.
-First, we clearly need that the spatial projections $\eta$ converge.
-
+is also fixed -- this is the sequence $(\tau_k, v_k, z_k, \kappa_k)$ associated 
+with the label $a$.
+To conclude that the lines of descent converge, 
+first, we clearly need that the spatial projections $\eta$ converge.
+%
 Supposing that they do,
 consider how a line of descent $(X_a(t), U_a(t))$ evolves.
-The line of descent throws off a new line of descent at a higher level
-when there is a point $(s, v, y, \kappa)$ in $\Pi_a$ with $s > \tau_a$ and
+It throws off a new line of descent at a higher level
+when there is a point $(\tau, v, z, \kappa)$ in $\Pi_a$ with $\tau > \tau_a$ and
 \begin{equation} \label{eqn:line_points}
-    v < 2 (N - U_a(s)) N^{-1} \theta \gamma(X_a(s), \eta_s) r(X_a(s) + y, \eta_s) .
-\end{equation}
-Since the mean measure of the $v$ coordinate is Lebesgue,
+    v < 2 \frac{\big(N - U_a(\tau-)\big)}{N} \theta \gamma(X_a(\tau-), \eta_{\tau-}) 
+	r\Big(X_a(\tau-) + y\big(X_a(\tau-),z\big), \eta_{\tau-}\Big) .
+\end{equation}
+Since the mean measure of the $v$ coordinate is Lebesgue measure,
 $\theta/N \to \alpha$,
-and $q(x, dy) \to \delta_x(dy)$,
-this corresponds in the limit to new lines of descent being thrown off at all times,
-i.e., according to a Poisson process with rate
+and $q_\theta(x, dy) \to \delta_x(dy)$,
+this corresponds in the limit to new lines of descent being thrown off 
+according to a Poisson Point Process with intensity
+%at all times,
+%i.e., according to a Poisson process with rate
 $$
-2 \alpha \gamma(X_a(t), \eta_t) r(X_a(t), \eta_t) 
+2 \alpha \gamma(X_a(t), \eta_t) r(X_a(t), \eta_t)dt \times du.
 $$
-and uniform intensity on higher levels.
-Again, since in the limit the dispersal distance is zero,
-new levels are produced at the same spatial location.
-However, this affects the location of the line of descent:
-for each new line of descent, there is a $1/2$ chance
-that the line of descent switches location (i.e., moves to $X_a(t) + y$).
+%and uniform intensity on higher levels.
+Now consider the location of the line of descent:
+at each birth event, with probability one half
+the line of descent jumps to $X_a(t) + y$.
 Taking $g$ to be a suitable test function on $\IR^d$, 
-and rewriting~\eqref{eqn:line_points},
-the generator of this motion is, when the level is $u$
-and the state of the population is $\eta$,
-applied to $g(x)$,
+and rewriting~\eqref{eqn:line_points}, when the level is $u$
+and the state of the population is $\eta$, the generator of the
+spatial motion of the line of descent
+applied to $g(x)$ is
 \begin{align*}
@@
     \left(1 - \frac{u}{N}\right) \gamma(x, \eta)
-    \theta \int_{\IR^d} r(x+y, \eta) (g(x+y) - g(x)) q(x, dy) \\
+    \theta \int_{\IR^d} r(x+y, \eta) (g(x+y) - g(x)) q_\theta(x, dy) \\
     &\qquad {}
@@
     \bigg\{
-        \theta \int_{\IR^d} (r(x+y, \eta) g(x+y) - r(x, \eta) g(x)) q(x, dy) \\
+        \theta \int_{\IR^d} (r(x+y, \eta) g(x+y) - r(x, \eta) g(x)) q_\theta(x, dy) \\
         &\qquad \qquad {}
         -
-        \theta \int_{\IR^d} (r(x+y, \eta) - r(x, \eta) ) g(x) q(x, dy) 
+        \theta \int_{\IR^d} (r(x+y, \eta) - r(x, \eta) ) g(x) q_\theta(x, dy) 
     \bigg\} \\
@@
     \right) ,
-    \qquad \text{as} N, \theta \to \infty .
-\end{align*}
-Notice that the factors of 2 have canceled,
+    \qquad \text{as } N, \theta \to \infty .
+\end{align*}
+Notice that the factors of 2 have cancelled,
 and that the result is independent of $u$.
-Also recall that $r(x, \eta)$ only depends on $\eta$ through $\smooth{r}\eta(x)$,
-which is guaranteed to be smooth, so that $\DG(r)$ and $\DG(gr)$ are well-defined.
-
-The only thing that remains is to describe how the levels change,
-but this is immediate from applying limit~\eqref{eqn:b_limit}
-to equation~\eqref{differential equation for level}.
-
-To write out the joint motion of spatial coordinate and levels,
-it is useful to work out the differential operator above in more detail.
+Also recall that $r(x, \eta)$ depends on $\eta$ only
+through $\smooth{r}\eta(x)$,
+which is guaranteed to be smooth, so that $\DG(r)$ 
+and $\DG(gr)$ are well-defined.
+
+We write out the differential operator above in more detail.
 Recall that $\DG g(x) = \sum_i \meanq_i \partial_i g(x) + \sum_{ij} \covq_{ij} \partial_{ij} g(x)$,
@@
 
+The only thing that remains is to describe how the levels change,
+but this is immediate from applying limit~\eqref{eqn:b_limit}
+to equation~\eqref{differential equation for level}.
+
 We summarize the results in a proposition.
@@
     \label{prop:limiting_construction}
-Let $\beta(x, \eta) = \meanq(x) + 2 \covq(x) \grad \log r(x, \eta)$
-and $K(x)$ such that $\covq(x) = K(x) K(x)^T$.
+Let 
+$J(x,\eta)$ be such that $\gamma(x,\eta)\covq(x) = J(x,\eta) J(x,\eta)^T$, and set
+$\beta(x, \eta) = \gamma(x,\eta)\big(\meanq(x) + 2 \covq(x) \grad \log r(x, \eta)\big).$
 Associate with each label $a \in \labelspace$
@@
 let $(x_i, u_i)$ be the points of a Poisson process
-with mean measure on $\IR^d \times [0, \infty)$ a product of $\eta_0$ and Lebesgue measure.
+with mean measure on $\IR^d \times [0, \infty)$ the product of $\eta_0$ and Lebesgue measure.
 For each point begin a line of descent
-with label $i$, location $X_i(0) = x_i$, level $U_i(0) = u_i$, and birth time $\tau_i = 0$.
+with label $i$, location $X_i(0) = x_i$, level $U_a(0) = u_i$, and birth time $\tau_i = 0$.
+We write $\tau_a$ for the birth time of the label $a$ and 
+$\sigma_a = \lim_{K \to \infty} \inf\{t \ge 0: U_a(t) > K\}$
+is the first time the level corresponding to the label $a$ exceeds $K$.
 Suppose that the spatial locations and level of each line of descent $a$
-solve, for $\tau_a \le t < \sigma_a$ as,
-where $\sigma_a = \lim_{K \to \infty} \inf\{t \ge 0: U_a(t) > K\}$,
-as
+solve, for $\tau_a \le t < \sigma_a$,
 \begin{align*}
@@
     + \int_{\tau_a}^{t}
-        K(X_a(s)) dW_a(s)
+        J(X_a(s),\eta_s) dW_a(s)
     \\
@@
         -
-        \left\{
+        \big\{
             \gamma(X_a(s),\eta_s) \DG r(X_a(s),\eta_s)
             + F(X_a(s), \eta_s)
-        \right\}
+        \big\}
         U_a(s)
@@
 Each point in each $R_a$ denotes a potential birth time for $a$:
-if the $j^\text{th}$ point in $R_a$ is $(t, v)$, with $\sigma_a \le t < \tau_a$,
+if the $j^\text{th}$ point in $R_a$ is $(\tau, v)$, with $\tau_a \le t < \sigma_a$,
 then a new line of descent with label $a \concat j$ is produced,
-with birth time $\tau_{a \concat j} = t$,
-    location $X_{a \concat j}(t) = X_a(t)$, and level
+with birth time $\tau_{a \concat j} = \tau$,
+    location $X_{a \concat j}(\tau) = X_a(\tau)$, and level
 $$
-    U_{a \concat j}(t) = U_a(t)
-    + \frac{v}{ 2 \alpha \gamma(X_a(t), \eta_t) r(X_a(t), \eta_t) } ,
+    U_{a \concat j}(\tau) = U_a(\tau)
+    + \frac{v}{ 2 \alpha \gamma(X_a(\tau), \eta_\tau) r(X_a(\tau), \eta_\tau) } .
 $$
-if this is finite.
 For any solution to the equations above, the processes defined by
@@
     \lim_{u_0 \to \infty} \frac{1}{u_0}
-        \sum_{a : \tau_a \le t < \sigma_a \;\&\; U_a(t) < u_0} \delta_{X_a(t)}
+        \sum_{a : \tau_a \le t < \sigma_a \; ; \; U_a(t) < u_0} \delta_{X_a(t)}
     \qquad \text{and} \qquad
@@
 no new lines of descent are produced.
-(More precisely, they are produced but ``at infinity'',
-since the spatial motion of the line of descent is the result of production of these lineages.)
-
-\comment{Note that the analogous theorem for finite $N$ is obvious (??) and not stated as a proposition.}
+More precisely, comparing with~(\ref{expression for ell}),
+they are produced, but ``at infinity'',
+and their trace is seen in the 
+spatial motion of the line of descent which results from
+the production of these lineages.
 
@@
 
+\comment{Don't we have to state everything in terms of subsequences along which the
+empirical measures converge?}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Motion of ancestral lineages}
+\label{ancestral lineages}
+
+We now show how, in the case in which the scaling limit of the population 
+process is deterministic, one can read off a description of 
+the motion of ancestral lineages from that of 
+the lines of descent derived in the previous subsection.
+
+Consider then a population evolving according to one of our deterministic
+limiting models. There are no births of new levels; 
+changes in population size are reflected only through the motion 
+of levels.
+
+We shall restrict ourselves
+to the setting in which the population is expanding as a travelling wave
+through $\IR$, with fixed profile $w(x)$ moving at rate $c$. That is 
+$$\Xi_t(x)=w(x-ct),$$
+for some fixed function $w$ and some $c>0$.
+The profile $w$ will satisfy
+\begin{equation}
+\label{profile}
+r\DG^*(\gamma w)+Fw+c\partial_x w=0.
+\end{equation} 
+It is convenient to work in a moving frame so that the wavefront is fixed.
+Let $Y$ denote the diffusion followed by a single line of descent in this frame; 
+i.e.~the diffusion with generator 
+${\cal L}^Yf=\gamma \DG(rf)-\gamma f\DG(r)-c\partial_x f$.
+%\overline{B}(w)\phi-c\phi_x$.
+For the motion of its level, note that 
+$b=\gamma\DG(r)+F$, and,  
+since we are in the deterministic limit, $\alpha=0$.
+
+Informally, the intensity of levels at $y$ at time $t$ that are descended from 
+individuals that were at $x$ at time $0$ is
+\begin{equation}
+\label{formal intensity}
+w(x)\IE_x\left[\exp\left(\int_0^t b(Y_s)ds\right)\ind_{Y_t=y}\right]dy,
+\end{equation}
+where the subscript $x$ in the expectation indicates that $Y_0=x$.
+To see why this should be true, 
+suppose that an ancestor has level $u$. Conditional on its 
+spatial motion $\{Y_s\}_{0\leq s\leq t}$, its level at time $t$ will
+be $u\exp(-\int_0^tb(Y_s)ds)$. This will be less than a given level 
+$\lambda$ if $u<\lambda \exp(\int_0^tb(Y_s)ds)$. 
+The intensity of levels at $y$ that are descended from individuals at
+$x$ can therefore be obtained as the limit as $\lambda\to\infty$ of 
+$1/\lambda$ times the number of levels at $x$ at time zero with
+$u<\lambda \exp(\int_0^tb(Y_s)ds)$ and for which
+the corresponding individual is at $y$ at time $t$, which is 
+precisely the quantity in~(\ref{formal intensity}).
+
+Note that at time $0$ the expression in~(\ref{formal intensity}) is satisfied, and that
+writing 
+\[
+\psi(t,x)=
+\IE_x\left[\exp\left(\int_0^t b(Y_s)ds\right)\ind_{Y_t=y}\right],
+\]
+and substituting the expressions for ${\cal L}^Y$ and $b$ from above, we have
+\begin{eqnarray*}
+\frac{d}{dt}\int
+w(x)\psi(t,x)dx&=& \int w(x)\Big\{\Big(\gamma\DG(r\psi)-\gamma\psi\DG(r)-c\partial_x\psi\Big)
++\psi\gamma\DG(r)+\psi F\Big\}dx
+\\
+&=&\int\psi\Big\{r\DG^*(\gamma w)+Fw+c\partial_x w\Big\}dx=0.
+\end{eqnarray*}
+Thus when we integrate~(\ref{formal intensity})
+with respect to $x$ we recover $w(y)dy$. 
+As a consequence of~(\ref{formal intensity}), writing $p(t,y,x)$ for
+the probability density that the ancestor at time $t$ units before the present 
+of an individual sampled 
+at $y$ was at $x$, then, still informally,
+\begin{equation}
+\label{ptyx}
+p(t,y,x)=\frac{w(x)}{w(y)}\IE_x\left[\exp\left(\int_0^t b(Y_s)ds\right)
+\ind_{Y_t=y}\right].
+\end{equation}
+
+To make~(\ref{ptyx}) meaningful, we multiply by suitable test functions and 
+integrate.
+$$\int\int \psi(y)w(y)p(t,y,x)\phi(x)dydx=\int\phi(x)w(x)
+\IE_x\left[\exp\left(\int_0^tb(Y_s)ds\right)\psi(Y_t)\right]dydx.$$
+
+Writing $\hat{T}_t$ for the semigroup corresponding to the motion of 
+ancestral lineages backwards in time (that is the semigroup corresponding
+to $p(t,x,y)$), we can write this as 
+$$\int \psi(y)w(y)\hat{T}_t\phi(y)dy=\int\phi(x)w(x)
+\IE_x\left[\exp\left(\int_0^tb(Y_s)ds\right)\psi(Y_t)\right]dx.$$
+Differentiating with respect to $t$ at $t=0$, and writing 
+$\hat{\mathcal L}$ for the generator of $\hat{T}_t$, we find
+\begin{eqnarray*}
+\int \psi(y)w(y)\widehat{\mathcal L}\phi(y)dy&=&
+\int\phi(x)w(x)\left({\mathcal L}^Y+b\right)\psi(x)dx\\
+&=&\int\phi(x)w(x)\left(\gamma\DG(r\psi)-\gamma\psi\DG r -c\nabla\psi 
++b\psi\right)dx\\
+&=&\int\phi(x)w(x)\left(\gamma\DG(r\psi)-c\nabla\psi+F\psi\right)dx\\
+&=&
+\int\psi(x)\left[r\DG^*(\gamma \phi w)+F\phi w+c\nabla(\phi w)\right]dx.
+\end{eqnarray*}
+Since $\psi$ was arbitrary,
+
+\begin{eqnarray*}
+\hat{\mathcal L}\phi&=&\frac{1}{w}\left[ r\DG^* (\gamma\phi w)+F\phi w
++c\nabla(\phi w)\right]\\
+&=&\frac{\phi}{w}\left[r\sigma^2\Delta(\gamma w)+Fw+-\meanq \grad(\gamma\phi) w +c\nabla w\right]
+\\
+&& +\frac{1}{w}\left[r\gamma w\sigma^2\Delta \phi +2r\sigma^2\nabla (\gamma w)
+\nabla\phi -\meanq \gamma\phi \grad w+cw\nabla\phi\right]\\
+&=&r\gamma\left(\sigma^2\Delta\phi+2\sigma^2r\frac{\nabla(\gamma w)}{\gamma w}\nabla\phi\right)
+-\meanq\gamma\nabla\phi+c\nabla\phi,
+\end{eqnarray*}
+where we have used that $w$ solves~(\ref{profile}), and we have recovered~(\ref{Lgen}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Proofs}
@@
 % % % % % % % % % % % % %
-\subsection{Convergence of the population density process}
+%\subsection{Convergence of the population density process}
+\subsection{Proof of Theorem~\ref{thm:nonlocal_convergence}: nonlocal limit points}
     \label{sec:population_density_proof}
 
-In this section we prove the main theorem on convergence
-of the population density process, Theorem~\ref{thm:nonlocal_convergence}.
-This is usually implied by convergence of the lookdown process
-(see \citet{kurtz/rodrigues:2011} and \citet{KE});
-however in our situation because the parameters depend on the population process
-we will use convergence of the population process
-in the proofs of tightness and convergence for the lookdown process.
-
-\comment{TODO: move actual proof after its ingredients; just foreshadow here?}
+In this section we prove 
+Theorem~\ref{thm:nonlocal_convergence}.
+This would be implied by convergence of the lookdown process
+(see \citet{kurtz/rodrigues:2011} and \citet{etheridge/kurtz:2019});
+however in our setting,
+because the parameters in the lookdown process
+depend on the empirical distribution,
+we actually use tightness of the sequence of population processes
+in the proofs of tightness for the corresponding lookdown processes.
 
 \begin{proof}[Proof of Theorem~\ref{thm:nonlocal_convergence}.]
-Here, we need to prove that for any sequence $N_k \to \infty$,
-there is a subsequence $N_{k(j)}$ along which $(\eta^{N_{k(j)}}_t)_{t\ge 0}$ converges in distribution
-(i.e., tightness for the family of distributions on c\`adl\`ag measure-valued paths),
-and that any limit is a solution to the martingale problem stated in the Theorem.
-This would imply convergence along $N_k$ to a unique limit
-if the solution to the martingale problem was unique;
-however, we only know this to be the case in certain situations.
-
-We prove tightness of $\eta^N$ as $\mathcal{D}_{\cmeasures}([0,\infty))$-valued processes,
-where $\cmeasures$ is the space of finite measures on the one-point compactification of $\IR^d$.
-To do this, we first prove that $\sup_{0 \le t \le T} \langle 1, \eta^N_t \rangle$ is tight
-(a compact containment condition, Lemma~\ref{lem:eta_compact_containment}).
-(The reason we use $\cmeasures$ instead of $\measures$
-is so that the set of measures with total mass less than $K$ is compact.)
-Next, in Lemma~ we show that the one-dimensional distributions,
-$\langle f, \eta^N_t \rangle$ are tight
-for each $f \in \mathcal{C}^2_0(\overline{\IR^d})$.
-Since this is a dense subset of bounded continuous functions on $\cmeasures$,
-together these results allow us to apply Theorem~3.9.1 of \citet{EK}.
-
-Next, we prove that the limit solves the martingale properties
-of equations~\eqref{eqn:limiting_mgale_problem} and~\eqref{eqn:limiting_mgale_variation}
-in Lemma~\ref{lem:limit_mgale}
-basically by checking the generators converge,
-which was mostly done in Section~\ref{sec:population_heuristics}.
+The proof follows a familiar pattern. First we extend $\IR^d$ 
+to its one-point compactification $\overline{\IR}^d$ and 
+establish, in Lemma~\ref{lem:eta_compact_containment},
+compact containment of the 
+sequence of scaled population
+processes in $\cmeasures$ %$\cal{M}_F(\widehat{\IR}^d)$ 
+(for which, since we have compactified $\IR^d$,
+it suffices to consider the sequence of total masses); armed with this, 
+%Theorem~3.9.1 of~\cite{ethier/kurtz:1986} tells us that 
+tightness of the population processes 
+in $\mathcal{D}_{\cmeasures}([0,\infty))$
+will follow if we can 
+establish tightness of the 
+real-valued processes $(G(\eta_t))_{t\geq 0}$ for a sufficiently large
+class of test functions $G$, which we check 
+through an application of the
+Aldous-Rebolledo criterion in Lemma~\ref{lem:eta_projections_tightness}.
+%{compactnedd projections}.
+These ingredients are gathered together in 
+Proposition~\ref{tightness in one point compactification}
+to deduce tightness of the scaled population processes in 
+the larger space $\mathcal{D}_{\cmeasures}([0,\infty))$.
+
+We then characterise
+limit points as solutions to a martingale problem in
+Lemma~\ref{lem:limit_mgale}; finally in Lemma~\ref{no mass at infty}
+we check that 
+in the process of passing to the limit, no mass `escaped to infinity', so that
+in fact the limit points take values in $\mathcal{D}_{\measures}([0,\infty))$.
 \end{proof}
-
-% % % % % % % % % % % % %
-\subsubsection{Tightness of empirical measures}
-    \label{sec:population_tightness_proofs}
-
-To prove tightness of the population process $\eta_t$,
-we first show that the expected total mass at some fixed time $T$
-is controlled uniformly across $N$, a compact containment condition.
-To establish this control,
-we first prove a technical lemma which controls spatial density of our population,
-and then we use the Burkholder-Davis-Gundy inequality
-to give us control over the running supremum of the total population mass.
-Once we have control over the total mass of the population, 
-we will also have control over local densities.
-This then allows us to prove that the particle system is tight
-by an application of the Aldous-Rebolledo criterion \citet{rebolledo:1980,alisonsup}.
 
@@
 
-To show compact containment, we will need boundedness
+As advertised, we work with the one-point compactification of $\IR^d$ and
+consider $(\eta^N_t)_{t\geq 0}$ as a sequence of 
+$\cmeasures$-valued processes. Since, for each $K>0$,
+$\{\eta: \langle 1,\eta\rangle\leq K\}$
+is a compact set in $\cmeasures$, we shall focus on 
+controlling $(\langle 1,\eta^N_t\rangle)_{t\geq 0}$.
+the key is that our Assumptions~\ref{def:model_setup}
+are precisely chosen to guarantee boundedness
 of the net per-capita reproduction rate.
-This does not follow immediately from our assumption that $F$ is bounded above
-because reproduction is not local:
-the net per-capita reproduction rate of an individual at $x$ is
-$$
-\theta \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q_\theta(x, dy) - \theta \mu(x, \eta)
-=
-F(x, \eta) + \gamma(x, \eta) \theta \int_{\IR^d} (r(y, \eta) - r(x, \eta)) q_\theta(x, dy) .
-$$
-We have assumed that $F$ is bounded,
-but we still need to show that our assumptions imply that
-the second term is bounded, uniformly as $\theta$ grows.
-
-\begin{lemma}
-    \label{lem:gamma_bound}
-    Under the assumptions of Definition~\ref{def:model_setup},
-    for all $f \in \mathcal{C}^{2}_{0}(\IR^d \times [0,\infty))$,
-    there exists a $K_f < \infty$ such that
-    for all $\theta > 0$ and all $\eta \in \measures$,
-    \begin{equation} \label{eqn:gamma_bound}
-    \gamma\big(x,\smooth{\gamma} \eta(x)\big)
-    \left| \theta 
-        \int_{\IR^n} 
-            \left\{
-                f(y, \smooth{r} \eta(y)) - f(x, \smooth{r} \eta(x))
-            \right\}
-        q_{\theta}(x,dy)
-    \right|
-    \leq C_f     .
-    \end{equation}
-\end{lemma}
-
-The key assumption here from Definition~\ref{def:model_setup}
-will be that the spatial scale over which local density affects birth rate
-is larger than the scale over which it affects establishment:
-concretely, that $\epsilon_{r}^2 + \frac{2\lambda}{\theta} < \epsilon_{\gamma}^2$,
-where $\lambda = \sup_x \sup_{y : \|y\| = 1} y^T \covq(x) y$
-is the largest eigenvalue of $\covq(x)$ across all $x$.
-In the simple case of $\meanq = 0$ and $\covq = \sigma^2 I$,
-the condition is simply that $\epsilon_r^2 + 2\sigma^2 / \theta < \epsilon_\gamma^2$.
-
-\begin{proof}[of Lemma \ref{lem:gamma_bound}]
-
-    Since we have assumed that there is a $K$ for which $m^2 \gamma(x, m) < K$
-    for all $x \in \IR^d$ and $m \ge 0$,
-    equation~\eqref{eqn:gamma_bound} will follow if we can show that
-    \begin{equation*}
-        \left| \theta 
-            \int_{\IR^n} 
-                \left\{
-                    f\left(y, \smooth{r}\eta(y)\right)
-                    -
-                    f\left(x, \smooth{r}\eta(x)\right)
-                \right\}
-            q_{\theta}(x,dy)
-        \right|
-        \leq
-        C_f \left( 1 + \smooth{\gamma} \eta(x)^2 \right) .
-    \end{equation*}
-    To do this, first note that 
-    \begin{align} \label{eqn:q_bound_split}
-    &
-        \left| \theta 
-            \int_{\IR^n} 
-                \left\{
-                    f\left(y, \smooth{r}\eta(y)\right)
-                    -
-                    f\left(x, \smooth{r}\eta(x)\right)
-                \right\}
-            q_{\theta}(x,dy)
-        \right|
-    \\ &\qquad {} \leq
-        \left| \theta 
-            \int_{\IR^n} 
-                \left\{
-                    f\left(y, \smooth{r}\eta(y)\right)
-                    -
-                    f\left(x, \smooth{r}\eta(y)\right)
-                \right\}
-            q_{\theta}(x,dy)
-        \right|
-    \\ &\qquad \qquad {}  +
-        \left| \theta 
-            \int_{\IR^n} 
-                \left\{
-                    f\left(x, \smooth{r}\eta(y)\right)
-                    -
-                    f\left(x, \smooth{r}\eta(x)\right)
-                \right\}
-            q_{\theta}(x,dy) 
-        \right| .
-    \end{align}
-
-    Since 
-    \begin{align*}
-        f\left(y, \smooth{r}\eta(y)\right) - f\left(x, \smooth{r}\eta(y)\right)
-        &=
-        \sum_i (y_i - x_i) \partial_{x_i} f \left(x, \smooth{r}\eta(y)\right) 
-        \\ &\qquad {}
-        +
-        \frac{1}{2} \sum_{ij} (y_i - x_i)(y_j - x_j)
-            \partial_{x_i x_j} f \left(z, \smooth{r}\eta(y)\right) 
-    \end{align*}
-    where $z = t x + (1-t) y$ for some $0 \le t \le 1$,
-    writing
-    $K_1 = \sup_{x,m} \max_i |\partial_{x_i} f(x, m)|$
-    and 
-    $K_2 = \sup_{x,m} \max_{i,j} |\partial_{x_i x_j} f(x, m)|$
-    for the bounds on the spatial derivatives of $f$,
-    the first term is bounded by
-    \begin{align*}
-        K_1 \left|
-            \theta \int_{\IR^d} \sum_i (y_i - x_i) q_\theta(x, dy)
-        \right|
-        +
-        K_2 \left|
-            \theta \int_{\IR^d} \sum_{ij} (y_i - x_i) (y_j - x_j)  q_\theta(x, dy)
-        \right| .
-    \end{align*}
-    This is bounded uniformly because
-    $q_\theta(x, dy)$ is the density of a Gaussian with mean $\meanq(x)/\theta$
-    and covariance $\covq(x)/\theta$, and both $\meanq(x)$ and $\covq(x)$
-    are bounded uniformly in $x$.
-
-    Similarly, 
-    \begin{align*}
-        f(x, \smooth{r}\eta(y)) - f(x, \smooth{r}\eta(x))
-        &=
-        (\smooth{r}\eta(y) - \smooth{r}\eta(x)) f'(x, \smooth{r}\eta(x))
-        + \frac{1}{2} (\smooth{r}\eta(y) - \smooth{r}\eta(x))^2 f''(x, m)
-    \end{align*}
-    for some $\smooth{r}\eta(x) \le m \le \smooth{r}\eta(y)$,
-    where $f'$ and $f''$ denote the first and second derivatives with respect to the second argument.
-    So,
-    the second term in~\eqref{eqn:q_bound_split} is bounded by
-    \begin{align*}
-        % note that the f' term does not depend on x, just y,
-        % so can come out of the integral
-        \|f'\|_\infty
-        \left|
-            \theta \int_{\IR^d}
-                (\smooth{r}\eta(y) - \smooth{r}\eta(x))
-            q_\theta(x, dy)
-        \right|
-        +
-        \|f''\|_\infty
-        \left|
-            \theta \int_{\IR^d}
-                (\smooth{r}\eta(y) - \smooth{r}\eta(x))^2
-            q_\theta(x, dy)
-        \right| .
-    \end{align*}
-    Therefore, it suffices to show that there is a $K < \infty$ such that
-    for all $\eta \in \measures$ and $x \in \IR^d$,
-    \begin{equation}
-        \label{eqn:first_moment_rho}
-        \left|\theta \int_{\IR^d}
-            ( \smooth{r} \eta(y)-\smooth{r} \eta(x) )
-        q_\theta(x,dy)\right|
-        \leq K \smooth{\gamma} \eta(x)
-    \end{equation}
-    and
-    \begin{equation}
-        \label{eqn:second_moment_rho}
-        \theta \int_{\IR^d}
-                \left( \smooth{r} \eta(y) - \smooth{r} \eta(x) \right)^2
-        q_\theta(x,dy)
-        \leq K \left(\smooth{\gamma}\eta(x) \right)^2 .
-    \end{equation}
-    Note that the right hand side of each is the average density
-    over a wider region (since $\epsilon_\gamma > \epsilon_r$).
-
-    First we prove \eqref{eqn:first_moment_rho}.
-    Recall that $\smooth{r} \eta(x) = \int p_{\epsilon^2_r}(x - w) \eta(dw)$,
-    where $p_t$ is the density of a Gaussian with mean 0 and variance $t$,
-    so that applying Fubini, \eqref{eqn:first_moment_rho} is
-    \begin{align*}
-        \left|
-        \int_{\IR^d}
-        \theta
-            \int_{\IR^d}
-                ( p_{\epsilon_r^2}(y - w) - p_{\epsilon_r^2}(x - w) )
-            q_\theta(x, dy)
-        \eta(dw)
-        \right| .
-    \end{align*}
-    Write $p_{s, x}(\cdot)$ for the density of a Gaussian
-    with mean $s \meanq(x)$ and covariance $\epsilon_r^2 I + s \covq(x)$,
-    so that $\int p_{\epsilon_r^2}(y - w) q_\theta(x, dy) = p_{1/\theta, x}(w-x)$.
-    It therefore suffices to show that for all $x$ and $w \in \IR^d$,
-    there exists $K$ such that
-    \begin{align} \label{eqn:goal1}
-        \left|
-        \theta
-            \int_{\IR^d}
-                ( p_{\epsilon_r^2}(y-w) - p_{\epsilon_r^2}(x-w) )
-            q_\theta(x, dy)
-        \right|
-        &=
-        \theta \left|
-            p_{1/\theta, x}(w-x) - p_{0, x}(w-x)
-        \right|
-        \le
-        K p_{\epsilon^2_\gamma}(w-x) .
-    \end{align}
-    However,
-    $\theta( p_{1/\theta, x}(z) - p_{0, x}(z) )
-    = \partial_s p_{s, x}(z)$ for some $0 \le s \le 1/\theta$.
-    Write $\Gamma(s,x) = \epsilon_r^2 I + s \covq(x)$,
-    so that
-    \begin{align*}
-        p_{s, x}(z)
-        &=
-        \frac{1}{\left(2 \pi |\Gamma(s,x)|\right)^{d/2}}
-        \exp\left(
-            -\frac{1}{2} (z - s\meanq(x))^T \Gamma(s,x)^{-1} (z - s\meanq(x))
-        \right) ,
-    \end{align*}
-    and note that if $\lambda_i$ are the eigenvalues of $\covq(x)$
-    then $|\Gamma(s, x)| = \prod_i (\epsilon_r^2 + s \lambda_i)$,
-    and
-    $\partial_s |\Gamma(s, x)| = \sum_i \lambda_i |\Gamma(s, x)| / (\epsilon_r^2 + s \lambda_i)$.
-    Therefore,
-    \begin{align*}
-        \partial_s p_{s, x}(z)
-        &=
-        \left(
-            \meanq(x)^T \Gamma(s,x)^{-1} (z - s \meanq)
-            +
-            (z - s \meanq(x))^T
-            \Gamma(s,x)^{-1} \covq(x) \Gamma(s,x)^{-1}
-            (z - s \meanq(x))
-        \right. \\ & \qquad \qquad \qquad \left. {}
-            -
-            \sum_i \frac{\lambda_i}{\epsilon_r^2 + s \lambda_i}
-        \right)
-        p_{s, x}(z) ,
-    \end{align*}
-    where $z^T$ is the transpose of $z$.
-    This implies that
-    \begin{align*}
-        \frac{
-        \theta
-            \int_{\IR^d}
-                ( p_{\epsilon_r^2}(y-w) - p_{\epsilon_r^2}(x-w) )
-            q_\theta(x, dy)
-        }{
-            p_{\epsilon^2_\gamma}(x-w) .
-        }
-        =
-        h(x-w) e^{k(x-w)},
-    \end{align*}
-    where $h(z)$ and $k(z)$ are quadratic polynomials in $z$
-    whose coefficients depend on $s$ and $x$ but are uniformly bounded for $s \ge 1$
-    and $x \in \IR^d$.
-    Therefore, \eqref{eqn:goal1} holds for some finite $K$
-    if and only if $k(z) < 0$ for all $z$ outside some bounded region.
-    This is
-    \begin{align*}
-        k(z)
-        =
-        \frac{1}{2\epsilon_\gamma^2} \|z\|^2
-        -\frac{1}{2} (z - s\meanq(x))^T \Gamma(s,x)^{-1} (z - s\meanq(x)) ,
-    \end{align*}
-    which is negative for all $z$ outside a bounded region.
-    Since $\inf_z z^T \Gamma(s,x)^{-1} z / \|z\|^2 = 1 / (s \lambda(x) + \epsilon_r^2)$,
-    where $\lambda(x) = \sup z^T \covq(x) z / \|z\|^2$ is the largest eigenvalue of $\covq(x)$,
-    equation~\eqref{eqn:first_moment_rho} follows from the assumption
-    that $\epsilon_r^2 + 2 \sup_x \lambda(x)/\theta < \epsilon_\gamma^2$.
-    (Note that we do not yet need the factor of 2.)
-
-    Next we prove equation~\eqref{eqn:second_moment_rho}, in a similar way.
-    Again applying Fubini,
-    \begin{align*}
-        &
-        \theta \int_{\IR^d}
-                \left( \smooth{r} \eta(y) - \smooth{r} \eta(x) \right)^2
-        q_\theta(x,dy)
-        \\ &\qquad
-        =
-        \int_{\IR^d} \int_{\IR^d}
-        \theta \int_{\IR^d}
-            ( p_{\epsilon_r^2}(y - w) - p_{\epsilon_r^2}(x - w) )
-            ( p_{\epsilon_r^2}(y - v) - p_{\epsilon_r^2}(x - v) )
-        q_\theta(x, dy)
-        \eta(dv) \eta(dw) ,
-    \end{align*}
-    and so as before, equation~\eqref{eqn:second_moment_rho} will follow if
-    the integrand is bounded by $K p_\gamma(x-w) p_\gamma(x - v)$.
-    % \begin{align*}
-    %     \theta \int_{\IR^d}
-    %         ( p_{\epsilon_r^2}(y - w) - p_{\epsilon_r^2}(x - w) )
-    %         ( p_{\epsilon_r^2}(y - v) - p_{\epsilon_r^2}(x - v) )
-    %     q_\theta(x, dy)
-    %     \le K p_\gamma(x-w) p_\gamma(x - v) .
-    % \end{align*}
-    Now, let $Y_1$, $Y_2$, and $Z$ be independent $d$-dimensional Gaussians with mean zero,
-    where $Y_1$ and $Y_2$ have covariance $\epsilon^2_r I$,
-    and $Z$ has covariance $\covq(x)$.
-    Write $p_{s,t,x}(\cdot, \cdot)$ for the joint density of
-    $Y_1 + \sqrt{s} Z + s \meanq(x)$ and $Y_2 + \sqrt{t} Z + t \meanq(x)$.
-    Then, observe that
-    \begin{align*}
-        &
-        \theta \int_{\IR^d}
-            ( p_{\epsilon_r^2}(y - w) - p_{\epsilon_r^2}(x - w) )
-            ( p_{\epsilon_r^2}(y - v) - p_{\epsilon_r^2}(x - v) )
-        q_\theta(x, dy)
-        \\ &\qquad
-        =
-        \theta \left(
-            p_{1/\theta, 1/\theta, x}(x-w, x-v)
-            - p_{0, 1/\theta, x}(x-w, x-v)
-        \right. \\ &\qquad \qquad \left. {}
-            - p_{1/\theta, 0, x}(x-w, x-v)
-            + p_{0, 0, x}(x-w, x-v)
-        \right) 
-        \\ &\qquad 
-        =
-            \partial_s p_{s, 1/\theta, x}(x-w, x-v)
-            - \partial_t p_{0, t, x}(x-w, x-v) ,
-    \end{align*}
-    for some $0 \le s, t \le 1/\theta$.
-    As before,
-    \begin{align*}
-        \frac{
-            \theta \int_{\IR^d}
-                ( p_{\epsilon_r^2}(y - w) - p_{\epsilon_r^2}(x - w) )
-                ( p_{\epsilon_r^2}(y - v) - p_{\epsilon_r^2}(x - v) )
-            q_\theta(x, dy)
-        }{
-            p_{\epsilon_\gamma^2}(x - w)
-            p_{\epsilon_\gamma^2}(x - v)
-        }
-        =
-        h(x-w, x-v) e^{ k(x-w, x-v) },
-    \end{align*}
-    where $h(z_1, z_2)$ is a polynomial with uniformly bounded coefficients and
-    \begin{align*}
-        k(z_1, z_2)
-        =
-        (\|z_1\|^2 + \|z_2\|^2)/(2 \epsilon_\gamma^2)
-            - \frac{1}{2} [z_1, z_2[^T \Gamma(s, t, x)^{-1} [z_1, z_2] ,
-    \end{align*}
-    where $[z_1, z_2]$ is the $\IR^{2d}$ vector formed by concatenating $z_1$ and $z_2$,
-    and $\Gamma(s, t, x)$ is the block matrix
-    \begin{align*}
-        \Gamma(s, t, x)
-        =
-        \left[
-        \begin{array}{cc}
-            \epsilon_r^2 I + s \covq(x) & \sqrt{st} \covq(x) \\
-            \sqrt{st} \covq(x) & \epsilon_r^2 I + t \covq(x) \\
-        \end{array}
-        \right] .
-    \end{align*}
-    If $\covq(x) u = a u$ for some $a \in \IR$,
-    then $[u \sqrt{s}, u \sqrt{t}]$ is an eigenvector of $\Gamma(s, t, x)$
-    with eigenvalue $\epsilon^2_r + (s+t) a$,
-    and $[u \sqrt{t}, - u \sqrt{s}]$ is an eigenvector of $\Gamma(s, t, x)$
-    with eigenvalue 0.
-    This implies the largest eigenvalue of $\Gamma(s, t, x)$
-    is equal to $\epsilon^2_r + (s+t) \lambda(x)$,
-    where $\lambda(x)$ is again the largest eigenvalue of $\covq(x)$.
-    Therefore, if $s + t \le 2 / \theta$,
-    \begin{align*}
-        &
-        (\|z_1\|^2 + \|z_2\|^2) / \epsilon^2_\gamma
-            - [z_1, z_2[^T \Gamma(s, t, x)^{-1} [z_1, z_2]
-        \\ &\qquad \le
-        (\|z_1\|^2 + \|z_2\|^2) \left(
-            \frac{1}{\epsilon^2_\gamma}
-            - \frac{1}{\epsilon^2_r +  2\lambda(x)/\theta}
-        \right) ,
-    \end{align*}
-    which is negative by assumption.
-    Therefore, there is a $K$ such that
-    \begin{align*}
-        \frac{ \left|
-            \partial_s p_{s, 1/\theta, x}(x-w, x-v)
-            - \partial_t p_{0, t, x}(x-w, x-v)
-        \right| }{
-            p_{\epsilon^2_\gamma}(x - w)
-            p_{\epsilon^2_\gamma}(x - v)
-        }
-        \le K
-    \end{align*}
-    for all $\theta > 1$ and all $x$, $v$, and $w \in \IR^d$,
-    proving equation~\eqref{eqn:second_moment_rho} and hence the lemma.
-\end{proof}
 
@@
     \label{lem:eta_f_bound}
-    Under the assumptions of Definition~\ref{def:model_setup},
-    if $\eta^{N}_0 \to \eta_0$ weakly as $N \to \infty$,
-    then for all $f \in C^2_0(\IR^d)$ there exists a $C_f < \infty$
+    Under Assumptions~\ref{def:model_setup},
+    for all $f \in C^2_b(\IR^d)$ there exists a $C_f < \infty$, independent of $N$,
     such that
-    $$
+    \begin{equation}
+\label{eta_f_bound}
         \IE[\langle f, \eta^N_t \rangle]
@@
         e^{C_f t}
-    $$
-    for all $N > 0$.
+    \end{equation}
+    for all $N \geq 1$.
 \end{lemma}
@@
 \begin{proof}
-    Consider the semimartingale decomposition of Equation \eqref{eqn:eta_martingale},
+    Consider the semimartingale decomposition of Equation \eqref{eqn:eta_martingale}:
     \begin{align} \label{eqn:eta_f_mgale_decomp}
@@
     \end{align}
-    where $M^N_t(f)$ is a martingale and for the moment we are defining
+    where $M^N_t(f)$ is a martingale and, for the moment, we are defining
     \begin{equation*}
@@
     \end{equation*}
-    By Lemma~\ref{lem:gamma_bound} and the assumption that $F$ is bounded above,
-    $\gamma(x, \eta) B_f(x, \eta) + f(x) F(x, \eta) \le C_f$ for some $C_f$,
-    and so, taking expectations,
-    \begin{align*}
+
+We need a bound on $\gamma(x,\eta)B_f(x,\eta)+F$. First suppose that
+Condition~\ref{control through r} of  
+Assumptions~\ref{def:model_setup} is satisfied.
+We write
+    \begin{align*}
+        f(y)r\big(y,\rho_r*\eta(y)\big) - f(x)r\big(x,\rho_r*\eta(x)\big)
+        &=
+        \sum_i (y_i - x_i) \partial_{x_i} \Big(f(x)r\big(x,\rho_r*\eta(x)\big)\Big) 
+        \\ &\qquad {}
+        +
+        \frac{1}{2} \sum_{ij} (y_i - x_i)(y_j - x_j)
+            \partial_{x_i x_j} \Big(f(z)r\big(\smooth{r}\eta(z)\big)\Big) 
+    \end{align*}
+    where $z = t x + (1-t) y$ for some $0 \le t \le 1$. Condition~\ref{control through r} 
+gives uniform bounds on the derivatives of $r(x, \rho_r*\eta(x))$ 
+in this expression and so, provided $f$ also has uniformly bounded first
+and second derivatives, we have a bound of the form
+\begin{multline*}
+\Big| f(y)r\big(y,\rho_r*\eta(y)\big) - f(x)r\big(x,\rho_r*\eta(x)\big) \Big|
+\\
+\leq
+        K_1 \left|
+            \theta \int_{\IR^d} \sum_i (y_i - x_i) q_\theta(x, dy)
+        \right|
+        +
+        K_2 \left|
+            \theta \int_{\IR^d} \sum_{ij} (y_i - x_i) (y_j - x_j)  q_\theta(x, dy)
+        \right| 
+\end{multline*}
+for suitable constants $K_1$, $K_2$.
+This is bounded uniformly because
+$q_\theta(x, dy)$ is the density of a Gaussian with mean $\meanq(x)/\theta$
+and covariance $\covq(x)/\theta$, and both $\meanq(x)$ and $\covq(x)$
+are bounded uniformly in $x$.
+
+Now suppose that instead
+Condition~\ref{control through gamma} of Assumptions~\ref{def:model_setup}
+is satisfied.
+First note that,  
+    \begin{align} \label{eqn:q_bound_split}
+    &
+        \left| \theta 
+            \int_{\IR^n} 
+                \left\{
+                    f(y) r\big(y,\smooth{r}\eta(y)\big)
+                    -
+                    f(x) r\big(x, \smooth{r}\eta(x)\big)
+                \right\}
+            q_{\theta}(x,dy)
+        \right|
+    \\ &\qquad {} \leq
+        \left| \theta 
+            \int_{\IR^n} 
+                \left\{
+                    f(y) r\big(y, \smooth{r}\eta(y)\big)
+                    -
+                    f(x) r\big(x,\smooth{r}\eta(y)\big)
+                \right\}
+            q_{\theta}(x,dy)
+        \right|
+    \\ &\qquad \qquad {}  +
+        \left| \theta 
+            \int_{\IR^n} 
+                \left\{
+                    f(x) r\big(x,\smooth{r}\eta(y)\big)
+                    -
+                    f(x) r\big(x,\smooth{r}\eta(x)\big)
+                \right\}
+            q_{\theta}(x,dy) 
+        \right| .
+    \end{align}
+
+ Writing
+    $K_3 = \sup_{x,m} \max_i |\partial_{x_i} f(x)r(x, m)|$
+    and 
+    $K_4 = \sup_{x,m} \max_{i,j} |\partial_{x_i x_j} f(x)r(x, m)|$, the first term
+is bounded exactly as above. For the second, 
+    \begin{multline*}
+        r(x, \smooth{r}\eta(y)) - r(x, \smooth{r}\eta(x))
+        \\
+=
+        (\smooth{r}\eta(y) - \smooth{r}\eta(x)) r'(x,\smooth{r}\eta(x))
+        + \frac{1}{2} (\smooth{r}\eta(y) - \smooth{r}\eta(x))^2 r''(x, \overline{m}),
+    \end{multline*}
+    where $\overline{m}= t'\smooth{r}\eta(x) +(1-t') \smooth{r}\eta(y)$ for some $0\leq t'\leq 1$, and
+    we have used $r'$ and $r''$ to denote the first and second derivatives of $r(x,m)$
+with respect to the second argument.
+    So, writing $K_5=\|f\|_\infty\|r'\|_\infty$ and $K_6=\|f\|_\infty\|r''\|_\infty$, in
+this case 
+    the second term in~\eqref{eqn:q_bound_split} is bounded by
+    \begin{align*}
+       K_5
+        \left|
+            \theta \int_{\IR^d}
+                (\smooth{r}\eta(y) - \smooth{r}\eta(x))
+            q_\theta(x, dy)
+        \right|
+        +
+       K_6
+        \left|
+            \theta \int_{\IR^d}
+                (\smooth{r}\eta(y) - \smooth{r}\eta(x))^2
+            q_\theta(x, dy)
+        \right| .
+    \end{align*}
+Under Condition~\ref{control through gamma} of 
+Assumptions~\ref{def:model_setup}, the right hand side is bounded by 
+a constant times $\smooth{\gamma}\eta(x)+(\smooth{\gamma}\eta(x))^2$ and 
+$m^2\gamma(m)$ is bounded. We have shown that $B_f$ is bounded, and so recalling that
+$F$ is bounded above, we can now conclude that
+under Assumptions~\ref{def:model_setup}
+    $\gamma(x, \eta) B_f(x, \eta) + f(x) F(x, \eta) \le C_f $ for some $C_f$.
+
+Taking expectations in~(\ref{eqn:eta_f_mgale_decomp}),
+    \begin{align}
+\label{bound on intfdeta}
         \IE\left[ \langle f, \eta^N_t \rangle \right]
@@
         \IE\left[ \langle f, \eta^N_0 \rangle \right]
-        + C_f \int_0^t \IE\left[ \langle f, \eta^N_s \rangle \right] dt .
-    \end{align*}
-    The bound then follows from Grownwall's inequality.
+        + C_f \int_0^t \IE\left[ \langle 1, \eta^N_s \rangle \right] dt .
+    \end{align}
+The bound~(\ref{eta_f_bound}) then follows by first applying Gronwall's
+inequality in the case $f=1$, and then, after substitution of 
+the resulting bound into the
+expression above, a second 
+application of Gronwall's inequality.
 \end{proof}
@@
 With a bound on per-capita net growth rate in hand,
-bounds on the total population size follow easily.
+bounds on the expectation of the supremum of 
+the total population size over a finite time interval also follow easily.
 
@@
     \label{lem:eta_compact_containment}
-    Under the assumptions of Definition~\ref{def:model_setup},
+    Under Assumptions~\ref{def:model_setup},
     if $\theta/N \to \alpha$ and $\eta^{N}_0 \to \eta_0$ weakly as $N \to \infty$,
@@
     \end{align}
-    In particular, for any $\epsilon > 0$, there exists some $K_{\epsilon}>0$ such that
+    In particular, for any $\delta > 0$, there exists $K_{\delta}>0$ such that
     \begin{equation}
@@
             \langle 1 ,\eta^{N}_{s}\rangle
-            > K_\epsilon \right\}
-        \leq \frac{C_T}{K_{\epsilon}}
-        < \epsilon .
+            > K_\delta \right\}
+        \leq \frac{C_T}{K_{\delta}}
+        < \delta.
     \end{equation}
@@
                 \int_{\IR^d} r(y, \eta^N_s) q_\theta(x, dy)
-                + \mu(x, \eta^N_s)
+                + \mu_\theta(x, \eta^N_s)
             \right\} \eta_s^N(dx)
@@
                 \frac{2\theta}{N} \gamma(x, \eta^N_s) r(x, \eta^N_s)
-                + \frac{1}{N} B(x, \eta^N_s)
+		+ \frac{\gamma(x,\eta_s^N)}{N} B_1(x, \eta^N_s)-\frac{1}{N}F(x,\eta^N_s)
             \right\} \eta_s^N(dx)
@@
     \end{align*}
-    Since $\gamma(x, \eta) r(x, \eta)$ and $B(x, \eta)$ are bounded,
-    and $\theta/N \to \alpha < \infty$,
-    combining constants and again using Gronwall's inequality, we get that
+
+	We have not assumed that $F$ is bounded below, but to see that the 
+	term involving $-F$ does not cause us problems, we rearrange
+	equation~(\ref{eqn:eta_f_mgale_decomp}) 
+	with $f=1$ to see that
+\[
+\IE\left[\int_0^t \Big\langle -\frac{1}{N}F(x, \eta^N_s), \eta^N_s(dx)
+	\Big\rangle\right]
+	=\IE[\langle 1, \eta^N_0\rangle] -\IE[\langle 1,\eta^N_t\rangle]
+	+\IE\left[\int_0^t\Big\langle %int_{\IR^d}
+\gamma(x,\eta_s^N)
+	B_1(x, \eta_s^N),\eta_s^N(dx)\Big\rangle ds\right],
+\]
+which is bounded since $\gamma (x,\eta)$ and $B_1(x,\eta)$ are both bounded and 
+$\langle 1,\eta_t\rangle\geq 0$. 
+    Since $\theta/N \to \alpha < \infty$,
+    combining constants and again using Gronwall's inequality, we obtain that
     \begin{align*}
@@
     Taking suprema and expectations on both sides of equation~\eqref{eqn:eta_f_mgale_decomp},
-    then again using the fact that $\gamma(x, \eta) B_f(x, \eta) + F(x, \eta) \le C$,
+    then again using the fact that $\gamma(x, \eta) B_1(x, \eta) + F(x, \eta) \le C$,
     \begin{align*}
@@
                 \gamma(x, \eta^N_s)
-                B_f(x, \eta^N_s)
+                B_1(x, \eta^N_s)
                 + F(x, \eta^N_s)
@@
         \right]
-        + \IE[M^*_t(1)] 
+        \\
+ & + \IE[M^*_t(1)] 
         \\
@@
         &\le
-        C'' 
-        \left(\IE[\langle 1, \eta^N_0 \rangle] + C'\right)
-        \IE[ \langle 1, \eta_0^N \rangle ] e^{2tC} .
+        C''' 
+        \left(1+ \IE[\langle 1, \eta^N_0 \rangle]\right) e^{2tC} .
     \end{align*}
@@
 
-\begin{lemma}
-    \label{lem:tightness_for_F}
-    Fix a $\sigma > 0$ and a continuous function $f \in C(\IR^d, [0, \infty))$
-    such that $\sup_x f(x, m)$ is finite for each $m$.
-    Under the assumptions of Definition~\ref{def:model_setup},
-    and if $\eta^N_0$ converges in distribution,
-    for all $\epsilon > 0$ and $T \ge 0$
-    there exists a $K_f$ such that for all $N > 0$,
-    \begin{align*}
-        \IP\left\{
-            \sup_{0 \le s \le T}
-            \int_{\IR^d}
-            f(x, p_{\sigma^2}*\eta^N_s(x))
-            \eta^N_s(dx)
-            > K_f
-        \right\}
-        \le \epsilon ,
-    \end{align*}
-    where recall that $p_{\sigma^2}*\eta(\cdot)$ denotes convolution of the Gaussian kernel
-    with mean 0 and variance $\sigma^2 I$ with the measure $\eta$.
-\end{lemma}
-
-\begin{proof}[of Lemma~\ref{lem:tightness_for_F}]
-    Let $\bar f(m) = \sup_x \sup_{k \le m} f(x, k)$, which is finite by assumption.
-    Since $p_{\sigma^2}*\eta(x) \le \langle 1, \eta \rangle / (2 \pi \sigma^2)^{d/2}$,
-    we have that
-    $$
-        \sup_{0 \le s \le T} \sup_{x \in \IR^d} f(x, p_{\sigma^2}*\eta^N_s(x))
-        \le
-        \bar f( \sup_{0 \le s \le T} \langle 1, \eta^N_s \rangle  / (2 \pi \sigma^2)^{d/2} ) .
-    $$
-    This implies that if $0 \le s \le T$ then
-    $$
-            \int_{\IR^d} f(x, p_{\sigma^2}*\eta^N_s(x)) \eta^N_s(dx)
-            \le
-            \bar f(\sup_{0 \le s \le T} \langle 1, \eta^N_s \rangle  / (2 \pi \sigma^2)^{d/2} )
-            \sup_{0 \le s \le T} \langle 1, \eta^N_s \rangle .
-    $$
-    Now, if we let $g(m) = m \bar f(m/ (2 \pi \sigma^2)^{d/2})$,
-    which again is finite and nondecreasing,
-    then the lemma follows by choosing $K_f = g^{-1}(K_\epsilon)$
-    in Lemma~\ref{lem:eta_compact_containment}.
-\end{proof}
-
-Now that we have a compact containment condition for $\eta^N$,
-we need tightness of the one-dimensional distributions.
+\subsubsection{Tightness}
+
+Our next task is to show tightness of 
+$(\langle f,\eta_t^N\rangle)_{t\geq 0}$ for 
+$f\in C_b^\infty(\overline{\IR}^d)$.
 
@@
     \label{lem:eta_projections_tightness}
-For all $f \in C^{2}_{0}(\IR^d)$, 
+	For each $f \in C^{\infty}_{b}(\overline{\IR}^d)$, 
 the collection of processes
 $(\langle f, \eta^{N}_t \rangle)_{t \geq 0}$
-for $N = 1, 2, \ldots$ is tight as a sequence of c\`adl\`ag, real-valued processes.
+for $N = 1, 2, \ldots$ is tight
+as a sequence of c\`adl\`ag, real-valued processes.
 \end{lemma}
-
 \begin{proof}
-We apply the Aldous-Rebolledo criterion \citep{rebolledo:1980}, which 
+The Aldous-Rebolledo criterion (found in the form we use here in \cite{rebolledo:1980}),
 applied to the semimartingale representation of $\langle f, \eta^N_t\rangle$
-of equation~\eqref{eqn:eta_f_mgale_decomp},
-says that it suffices to show that 
-$\{\langle f, \eta^N_t \rangle\}_{N \ge 1}$ is tight for each $t$, and that
+of equation~\eqref{eqn:eta_f_mgale_decomp}, tells us
+that it suffices to show that for each $T>0$, for each fixed 
+$0\leq t\leq T$, the sequence 
+$\{\langle f, \eta^N_t \rangle\}_{N \ge 1}$ is tight, and that
 for any sequence of stopping times $\tau_N$ bounded by $T$,
-and for each $\epsilon > 0$, there exists $\delta > 0$ and $N_0 > 0$ such that 
+and for each $\nu > 0$, there exist $\delta > 0$ and $N_0 > 0$ such that 
 \begin{gather}
@@
             ds
-        \right|> \epsilon \right\}
-        < \epsilon ,
+        \right|> \nu \right\}
+        < \nu ,
     \\ \text{and} \qquad
@@
             - [M^{N}(f)]_\tau \big|
-        > \epsilon
+        > \nu
     \right\}
-    < \epsilon.
+    < \nu.
 \end{gather}
@@
 
-Next, note that for $0 \le t \le \delta$,
-if we choose $K_f$ as in Lemma~\ref{lem:tightness_for_F}
-and $C_f$ as in Lemma~\ref{lem:gamma_bound},
-then
-\begin{align*}
-    &
-    \IP\left\{
-        \int_\tau^{\tau + t}
-        \int_{\IR^d}
-        \left\{
-            \gamma(x, \eta^N_s) B_f(x, \eta^N_s)
-            + f(x) F(x, \eta^N_s)
-        \right\} 
-        \eta^N_s(dx)
-        ds
-        > (K_f + C_f) \delta
-    \right\}
-    \\ & \qquad \le
-    \IP\left\{
-        \sup_{0 \le s \le \delta}
-        \int_{\IR^d} \left\{
-            \gamma(x, \eta^N_s) B_f(x, \eta^N_s)
-            + f(x) F(x, \eta^N_s)
-        \right\} \eta^N_s(dx)
-        >
-        K_f + C_f
-    \right\}
-    < \epsilon .
-\end{align*}
-Therefore, setting $\delta = \epsilon / (K_f + C_f)$
-obtains \eqref{eqn:eta_projections_goal1}.
+The proof of Lemma~\ref{lem:eta_f_bound}
+provides a uniform bound on $\gamma B_f$, but we only know
+that $F$ is bounded above. However, since, by 
+assumption, for each fixed value of
+$m$, $\sup_{k\leq m}|F(x,k)|$ is uniformly bounded as a function of $x$, 
+noting that $\smooth{F}\eta\leq
+\langle 1,\eta\rangle\|\rho_F\|_\infty$,
+and using Lemma~\ref{lem:eta_compact_containment} 
+to choose $N_0$ and $K$ such that
+$$\IP\left[\sup_{0\leq s\leq T}\langle 1, \eta_s^N\rangle\geq K\right]<\nu,$$
+we now choose $\delta_1$ so that
+$$\sup\big\{
+\sup_{x}|F(x,k)|
+: k\leq K\|\rho_F\|_\infty \big\}\delta_1
+<\nu/2,
+\qquad
+\sup_{x,\eta}\gamma(x,\eta)B_f(\,\eta)\delta_1<\nu/2,$$
+and~(\ref{eqn:eta_projections_goal1}) is satisfied.
 
@@
     \\ & \qquad =
-    \int_{\tau}^{\tau + t}
+  \Big|  \int_{\tau}^{\tau + t}
         \frac{\theta}{N}
@@
             +
-            \mu(x, \eta^N_s) f^2(x)
+            \mu_\theta(x, \eta^N_s) f^2(x)
         \right\}
         \eta^N_s(dx)
-    ds 
+    ds \Big|
     \\ & \qquad =
-    \int_{\tau}^{\tau + t}
+   \Big| \int_{\tau}^{\tau + t}
         \frac{\theta}{N}
@@
             \right)
-            +
-            f^2(x) F(x, \eta^N_s) / \theta
+            -
+            f^2(x) \frac{F(x, \eta^N_s)}{ \theta}
         \right\}
         \eta^N_s(dx)
-    ds ,
+    ds\Big| ,
 \end{align*}
 and so using the fact that $\theta/N \to \alpha < \infty$,
-an argument similar to 
+an argument entirely analogous to 
 that for \eqref{eqn:eta_projections_goal1}
-also obtains \eqref{eqn:eta_projections_goal2}.
+yields a $\delta_2$ for which \eqref{eqn:eta_projections_goal2} is
+satsified. Taking $\delta=\min\{\delta_1,\delta_2\}$, the result follows.
 
@@
 % % % % % % % % %
-\begin{theorem}[Tightness of $(\eta^{N}_t)_{t \geq 0}$]
+
+We collect the results of the last two subsections into a proposition.
+\begin{proposition}[Tightness of $(\eta^{N}_t)_{t \geq 0}$]
+\label{tightness in one point compactification}
     The collection of measure-valued processes 
-    $\{(\eta^{N}_t)_{t \geq 0}: N > 0\}$
-    is tight in $\mathcal{D}_{[0,\infty)}(\measures)$.
-\end{theorem}
+    $\{(\eta^{N}_t)_{t \geq 0}: N \geq 1\}$
+    is tight in $\mathcal{D}_{[0,\infty)}(\cmeasures)$.
+\end{proposition}
 
 \begin{proof}
-    Theorem 3.9.1~in \cite{EK},
+    Theorem 3.9.1~in \cite{ethier/kurtz:1986}
     says that if the collection of $E$-valued processes
@@
     such that the processes stay within that set up to time $T$ with probability at least $1-\epsilon$),
-    then the collection is relatively compact
+    then the collection is relatively compact (which is equivalent to tightness
+since we are working on a Polish space)
     if and only if
-    $\{(f(\eta^{N}_t))_{t \geq 0}: N > 0\}$ is relatively compact
-    for all $f$ in a dense subset of $C_0(E)$
+    $\{(f(\eta^{N}_t))_{t \geq 0}: N \geq 1\}$ is relatively compact
+    for all $f$ in a dense subset of $C_b(E)$
     under the topology of uniform convergence in compact sets.
 
-    First of all,
-    the set of measures $\{ \mu: \langle 1, \mu \rangle \leq K \} $ is compact in $\cmeasures$,
-    so Lemma \ref{lem:eta_compact_containment}
-    shows that our processes satisfy a compact containment condition.
-    Secondly, Lemma \ref{lem:eta_projections_tightness}
+Since $\{ \nu: \langle 1, \nu \rangle \leq K \} $ is compact in $\cmeasures$,
+    Lemma~\ref{lem:eta_compact_containment}
+    gives compact containment.
+    Lemma \ref{lem:eta_projections_tightness}
     shows that the real-valued processes $\langle f, \eta^{N}_t \rangle$
-    are relatively compact for all $f \in \mathcal{C}^{2}_{0}(\overline{\IR^d})$.
+    are relatively compact for all 
+$f \in \mathcal{C}^{\infty}_{b}(\overline{\IR}^d)$.
     Since by the Stone-Weierstrass theorem,
@@
     we have relative compactness in $\mathcal{D}_{[0,\infty)}(\cmeasures)$.
-    Finally,
-    since each measure $\eta^{N}_t$ is concentrated in $\IR^d$,
-    any limit point must in fact be in $\measures$,
-    and so we have 
-    tightness in $\mathcal{D}_{[0,\infty)}(\measures)$.
 \end{proof}
@@
 % % % % % % % % % % % % %
-\subsubsection{Convergence of generators}
+\subsubsection{Characterisation of the limit points}
     \label{sec:population_generators_proofs}
 
-Before we prove convergence, we define our limit $(\eta^{\infty}(t))_{t>0}$ as a solution to a Martingale Problem with generator $\Pgen^{\infty}$.
+We wish to characterise the limit points of
+$\{(\eta^{N}_t)_{t>0}\}_{N\geq 1}$ as solutions to a martingale problem 
+with generator $\Pgen^{\infty}$ which we now identify. Most of the work
+was done in Section~\ref{sec:heuristics}.
 
@@
     \label{def: MP definition of limit}
-Let $F \in \mathcal{C}^{2}(\IR)$ and $f \in \mathcal{C}_{0}(\IR^d)$.
-We define $\Pgen$ to be a generator
-acting on test functions of the form
-$F_f(\eta):=F (\langle f, \eta \rangle)$
-such that 
+For $G \in \mathcal{C}^{\infty}(\IR)$ with $\|G'''\|_\infty<\infty$,
+and 
+$f \in \mathcal{C}_{b}^\infty(\overline{\IR}^d)$, define the 
+function $G_f$ by 
+$G_f(\eta):=G (\langle f, \eta \rangle)$.
+Let $\Pgen^\infty$ be the generator
+given by
 \begin{equation}
@@
 \begin{aligned}
-\Pgen^{\infty} F_f(\eta):=& F'(\langle f, \eta \rangle)
-                   \times \left\{
+\Pgen^{\infty} G_f(\eta):=& G'(\langle f, \eta \rangle)
+                   %\times 
+\left\{
                    \big\langle
@@
                    \right\}\\
-                &+ \frac{\alpha}{2} F''(\langle f, \eta \rangle)
-                  \times \left\{
+                &+ \frac{\alpha}{2} G''(\langle f, \eta \rangle)
+                  %\times 
+\left\{
                   \big\langle
-                    \left(\gamma\left( x, \eta \right)
+                    2\gamma\left( x, \eta \right)
                     r\left(x,\eta \right)
-                    +\mu\left(x,\eta \right)
-                    \right)
+                    %+\mu\left(x,\eta \right)
                     f^2(x),
@@
 \end{equation}
-We define $(\eta^{\infty}(t))_{t \geq 0}$ to be the solution to the Martingale Problem $(\Pgen^{\infty}, \eta_0)$, i.e. 
-for all $F \in \mathcal{C}^{2}(\IR)$
-and $f \in \mathcal{C}_{0}(\IR^d)$,
-$$M_t:=F_f(\eta^{\infty}_t)-F_f(\eta_0)
--\int_{0}^{t}\Pgen^{\infty}F_f(\eta^{\infty}_s)ds$$
-is a martingale, with initial condition distributed as a Poisson measure with mean measure $\eta_0$.
+We say that $(\eta^{\infty}_t)_{t \geq 0}$ is a solution 
+to the Martingale Problem $(\Pgen^{\infty}, \eta_0)$ if 
+for all such test functions %$G \in \mathcal{C}^{2}(\IR)$
+%and $f \in \mathcal{C}_{b}(\IR^d)$,
+$$M_t:=G_f(\eta^{\infty}_t)-G_f(\eta_0)
+-\int_{0}^{t}\Pgen^{\infty}G_f(\eta^{\infty}_s)ds$$
+is a martingale. 
 \end{definition}
 
-In a similar manner,
-we may also define our pre-limit
-$(\eta^{N}(t))_{t>0}$ as a solution
-to a Martingale Problem
-with generator $\Pgen^{N}$.
-
-\begin{definition}
-    \label{def: MP definition of pre-limit}
-Let $F \in \mathcal{C}^{2}(\IR)$ and $f \in \mathcal{C}_{0}(\IR^d)$.
-We define $\Pgen^N$ to be a generator
-acting on test functions of the form
-$F_f(\eta):=F (\langle f, \eta \rangle)$
-such that 
-\begin{equation}
-\begin{aligned}
-\Pgen^{N} F_f(\eta):=& \int_{\IR^d} \theta\gamma(x, \eta) \left\{\int_{\IR^d} \left\{F(\langle f, \eta \rangle + f(y)/N )-F(\langle f, \eta \rangle )\right\}r(y, \eta)q_{\theta}(x,dy)\right\}N\eta(dx)\\
-&+\int_{\IR^d} \theta \mu(x, \eta) \left\{F(\langle f, \eta \rangle - f(x)/N )-F(\langle f, \eta \rangle )\right\}N\eta(dx).
-\end{aligned}    
-\end{equation}
-In this case, our pre-limit model $(\eta^{N}(t))_{t \geq 0}$ is the solution to the Martingale Problem $(\Pgen^{N}, \eta_0)$, i.e. 
-for all $F \in \mathcal{C}^{2}(\IR)$
-and $f \in \mathcal{C}_{0}(\IR^d)$,
-$$M_t:=F_f(\eta^{N}_t)-F_f(\eta_0)
--\int_{0}^{t}\Pgen^{N}F_f(\eta^{N}_s)ds$$
-is a martingale, and the initial condition is distributed as a Poisson measure with mean measure $\eta_0$.
-\end{definition}
-
-\begin{remark}
-Taking $F(x)=x$ and $F(x)=x^2$, we can recover Equation \eqref{eqn:limiting_mgale_problem} and \eqref{eqn:limiting_mgale_variation} for the limit.
-Similarly, we can recover
-Definition \ref{defn:mgale_construction},
-an equivalent characterisation
-of our pre-limit model.
-\end{remark}
-
-\begin{lemma}[Identifying the limit as a solution to the martingale problem]
+\begin{lemma}[Characterisation of limit points]
     \label{lem:limit_mgale}
-    \comment{Here we need to check that the martingale property is preserved in the limit.}
-As $N \to \infty$,
-$(\eta^{N}_t)_{t \geq 0}$ converges in $\mathcal{D}_{[0,\infty)}(\mathcal{M}_f(\IR^d))$
-to $(\eta^{N}(t))_{t \geq 0}$.
+Suppose that $(\eta^{N}_0)_{N\geq 1}$ converges weakly to $\eta_0$ as 
+$N\to\infty$.
+Then any limit point of $\{(\eta^{N}_t)_{t \geq 0}\}_{N\geq 1}$ 
+in $\mathcal{D}_{[0,\infty)}(\cmeasures)$ %(\mathcal{M}_f(\IR^d))$
+is a solution to the martingale problem for 
+$(\Pgen^\infty, \eta_0)$.
 \end{lemma}
 \begin{proof}
-We use Theorem 4.8.10 in \cite{EK}.
-First of all, the set of functions
-$\{F_f(\eta):= F(\langle f, \eta \rangle ),~
-F \in \mathcal{C}^{2}(\IR), ~
-f \in \mathcal{C}_{0}(\IR^d)\}$
-is a dense and convergence-determining 
-subset of functions in $\mathcal{M}_f(\IR^d)$.
+We use Theorem 4.8.2 in \cite{ethier/kurtz:1986}.
+First observe that the set of functions
+$\{G_f(\eta):= G(\langle f, \eta \rangle ),~
+G \in \mathcal{C}^{\infty}(\IR), \|G'''\|_\infty<\infty,~
+f \in \mathcal{C}_{b}^\infty(\overline{\IR}^d)\}$
+is separating 
+on $\mathcal{M}_F(\overline{\IR}^d)$.
 Therefore, it suffices to show that for any $t>0$,
@@
 \left(
-F_f(\eta^{N}_{t+\tau})-F_f(\eta^{N}_t)
--\int_{t}^{t+\tau}\Pgen^{\infty}F_f(\eta^{N}_s)ds
+G_f(\eta^{N}_{t+\tau})-G_f(\eta^{N}_t)
+-\int_{t}^{t+\tau}\Pgen^{\infty}G_f(\eta^{N}_s)ds
 \right)
-\prod_{i=1}^{k}\langle h_i,\eta^{N}_{t_i} \rangle
+\prod_{i=1}^{k} h_i(\eta^{N}_{t_i})
 \right]=0
@@
 for all $k\geq 0$, $0\leq t_1<t_2<...,t_k \leq t < t+\tau$,
-and $h_1,...,h_k \in \mathcal{C}_{0}(\IR^d)$.
-
-To prove this,
-we make use of the Martingale Problem characterisation
-of $(\eta^{N}_t)_{t \geq 0}$.
-From Definition \ref{def: MP definition of pre-limit},
-we can apply Tower Law
-and obtain that
+and $h_1,...,h_k \in \mathcal{C}_{b}(\cmeasures)$.
+
+Since $(\eta^N_t)_{t\geq 0}$ is Markov, the tower property gives that,
+for each choice of $G_f$ and for each $N$,
 \begin{equation}
     \label{eq: Prelimit MP Application}
-\lim_{N \to \infty}
+%\lim_{N \to \infty}
 \mathbb{E}\left[
 \left(
-F_f(\eta^{N}_{t+\tau})-F_f(\eta^{N}_t)
--\int_{t}^{t+\tau}\Pgen^{N}F_f(\eta^{N}_s)ds
+G_f(\eta^{N}_{t+\tau})-G_f(\eta^{N}_t)
+-\int_{t}^{t+\tau}\Pgen^{N}G_f(\eta^{N}_s)ds
 \right)
-\prod_{i=1}^{k}\langle h_i,\eta^{N}_{t_i} \rangle
+\prod_{i=1}^{k}h_i(\eta^{N}_{t_i})
 \right]=0
@@
 for all $k\geq 0$, $0\leq t_1<t_2<...,t_k \leq t < t+\tau$,
-and $h_1,...,h_k \in \mathcal{C}_{0}(\IR^d)$.
-
+and $h_1,...,h_k \in \mathcal{C}_{b}(\cmeasures)$.
+%
 Therefore, it suffices to show that 
@@
 \left|
-\Pgen^{N}F_f(\eta^{N}_s)
--\Pgen^{\infty}F_f(\eta^{N}_s)
+\Pgen^{N}G_f(\eta^{N}_s)
+-\Pgen^{\infty}G_f(\eta^{N}_s)
 \right|
 ds
-\times 
-\prod_{i=1}^{k}\langle h_i,\eta^{N}_{t_i} \rangle
-\right]=0
-\end{equation}
-We apply Taylor Expansion
-around the term $F(\langle f, \eta \rangle )$
-up to third order.
-This gives
-\begin{equation}
-    \label{eq: Taylor Expansion calculations i}
-\begin{aligned}
-&F(\langle f, \eta \rangle + f(y)/N )-F(\langle f, \eta \rangle )\\
-=& F'(\langle f, \eta \rangle ) \frac{f(y)}{N}
-+\frac{1}{2}F''(\langle f, \eta \rangle ) \frac{f^2(y)}{N^2}
-+\frac{1}{6}F'''(w ) \frac{f^3(y)}{N^3}
-\end{aligned}
-\end{equation}
-for some $w \in [\langle f, \eta \rangle, \langle f, \eta \rangle+ ||f||/N]$.
-Similarly,
-\begin{equation}
-    \label{eq: Taylor Expansion calculations ii}
-\begin{aligned}
-&F(\langle f, \eta \rangle - f(x)/N )-F(\langle f, \eta \rangle )\\
-=& - F'(\langle f, \eta \rangle ) \frac{f(x)}{N}
-+\frac{1}{2}F''(\langle f, \eta \rangle ) \frac{f^2(x)}{N^2}
--\frac{1}{6}F'''(v ) \frac{f^3(x)}{N^3}
-\end{aligned}
-\end{equation}
-for some $v \in [\langle f, \eta \rangle - ||f||/N, \langle f, \eta \rangle ]$.
-
-We may now rewrite $\mathcal{P}^NF(\langle f, \eta \rangle)$ as 
-\small
+\prod_{i=1}^{k}h_i(\eta^{N}_{t_i})
+\right]=0,
+\end{equation}
+and again using the tower property, since the functions $h_i$ are
+bounded, this will follow if
+\begin{equation}
+\lim_{N \to \infty}
+\mathbb{E}\left[\left.
+\int_{t}^{t+\tau}
+\left|
+\Pgen^{N}G_f(\eta^{N}_s)
+-\Pgen^{\infty}G_f(\eta^{N}_s)
+\right|
+ds\right| {\cal F}_t\right]=0
+\end{equation}
+(where $\{{\cal F}_t\}_{t\geq 0}$ is the natural $\sigma$-field).
+
+We rewrite $\Pgen^NG_f(\eta^N_s)$ using a 
+Taylor series expansion up to third order for
+$G\big(\langle f,\eta\rangle\pm f(y)/N\big)$ around
+$G(\langle f, \eta \rangle )$.
+As in Section~\ref{sec:heuristics} (except that now we are more explicit about
+the error term), we find
 \begin{equation} 
@@
 \begin{aligned}
-\Pgen^{N} F_f(\eta):=& F'(\langle f, \eta \rangle)\int_{\IR^d}  \theta\left\{\int_{\IR^d} \left\{f(y)\gamma(x, \eta) r(y,\eta) -f(x)\mu(x, \eta)\right\}q_{\theta}(x,dy)\right\}\eta(dx)\\
-&+\frac{1}{2}\frac{\theta}{N}F''(\langle f, \eta \rangle)\int_{\IR^d} 
- \left\{\gamma(x, \eta)\int_{\IR^d} \left\{f^2(y) r(y,\eta) \right\}q_{\theta}(x,dy)+f^2(x)\mu(x, \eta)\right\}\eta(dx)\\
-&+\frac{1}{6}\frac{\theta}{N^2}\int_{\IR^d}\left\{ 
-F'''(w) \left\{\gamma(x, \eta)\int_{\IR^d} f^3(y) r(y,\eta) q_{\theta}(x,dy)\right\}-F'''(v)f^3(x)\mu(x, \eta)\right\}\eta(dx)
+\Pgen^{N} G_f(\eta):=& G'(\langle f, \eta \rangle)\int_{\IR^d}  
+\theta\Big\langle\int_{\IR^d} \big\{f(y)\gamma(x, \eta) r(y,\eta) 
+-f(x)\mu_\theta(x, \eta)\big\}q_{\theta}(x,dy), \eta(dx)\Big\rangle\\
+&+\frac{1}{2}\frac{\theta}{N}G''(\langle f, \eta \rangle)\int_{\IR^d} 
+ \Big\langle\gamma(x, \eta)\int_{\IR^d} f^2(y) r(y,\eta)q_{\theta}(x,dy)+f^2(x)
+\mu_\theta(x, \eta), \eta(dx)\Big\rangle\\
+&+\frac{1}{6}\frac{\theta}{N^2}\Big\langle \big\{
+G'''(w) \gamma(x, \eta)\int_{\IR^d} f^3(y) r(y,\eta) 
+q_{\theta}(x,dy)
+-G'''(v)f^3(x)\mu_\theta(x, \eta)\big\}, \eta(dx)\Big\rangle
 \end{aligned}    
 \end{equation}
-\normalsize
-for some $w,v \in [\langle f,\eta \rangle - ||f||/N, \langle f,\eta \rangle + ||f||/N]$.
-
-As $N\to \infty$, 
-$\theta/N \to \alpha$, 
-$\theta/N^2 \to 0$,
-and 
-$$\int_{\IR^d} f^m(y) r(y,\eta) q_{\theta}(x,dy) \to f^m(x)r(x, \eta)$$
-for $m=2,3$,
-the third term in Equation \eqref{eq: Pre-Limit Generator Expanded} vanishes
-while the second term converges to
-that of Equation \eqref{eq: Limit Generator Definition}.
-
-Finally, by Equation \eqref{mean measure},
-\eqref{eqn:rewritten mean measure}, \eqref{eqn:near_critical} and
-\eqref{limit of mean measure equation},
-we have 
-\begin{multline}
- \theta\left\{\int_{\IR^d} \left\{f(y)\gamma(x, \eta) r(y,\eta) -f(x)\mu(x, \eta)\right\}q_{\theta}(x,dy)\right\}
- \\
-\to \gamma(x, \eta)                           \mathcal{B}\left(
-                            f(\cdot) r(\cdot, \eta)
-                            \right)(x)
-                    +
-                    f(x)
-                        F(x, \eta),
-\end{multline}
-so comparing terms we have
-\begin{equation}
-\lim_{N\to \infty} |\mathcal{P}^{N}F\langle f, \eta \rangle - \mathcal{P}^{\infty}F\langle f, \eta \rangle| \to 0,   
-\end{equation}
-and so by Dominated Convergence Theorem,
-we establish Equation 
-\eqref{eq: Convergence of Spatial Generator}
+%\normalsize
+for some $w,v \in [\langle f,\eta \rangle - \|f\|_\infty/N, 
+\langle f,\eta \rangle + \|f\|_\infty/N]$.
+
+Combining with equation~\eqref{limit of mean measure equation}, and the fact
+that $\mu_\theta(x,\eta) \to r(x,\eta)\gamma(x,\eta)$ as $\theta\to\infty$, we have
+pointwise convergence:
+\begin{equation}
+\lim_{N\to \infty} |\mathcal{P}^{N}G(\langle f, \eta \rangle) 
+- \mathcal{P}^{\infty}G(\langle f, \eta \rangle)| = 0,   
+\end{equation}
+To conclude convergence of the expectation, 
+we would like to apply the Dominated Convergence 
+Theorem in~(\ref{eq: Convergence of Spatial Generator}).
+Recall that $f$ and $G$ and their derivatives are bounded, $\gamma(x,\eta)$ is
+bounded, and, in the notation of Lemma~\ref{lem:eta_f_bound}
+$\gamma(x,\eta) B_f(x,\eta)$ is bounded. Moreover $\theta/N^2\to 0$ as $N\to\infty$. Thus we can 
+dominate 
+$\left|
+\Pgen^{N}G_f(\eta^{N}_s)
+-\Pgen^{\infty}G_f(\eta^{N}_s)
+\right|$ by 
+a constant multiple of
+$\theta \big\langle |r(x,\eta^N_s)\gamma(x,\eta^N_s)-\mu_\theta(x,\eta^N_s)|,
+\eta^N_s(dx)\big\rangle$, 
+which we  
+recognise as $\langle |F(x,\eta^N_s)|,\eta^N_s(dx)\rangle$.
+Since $F$ is bounded above, there is a constant $K$ such that $|F|\leq K-F$ so
+that exactly as in the proof of 
+Lemma~\ref{lem:eta_compact_containment},
+we can check that
+\[
+\IE\Big[\left.\int_t^{t+\tau}\big\langle |F(x,\eta^N_s)|,\eta^N_s(dx)\big\rangle ds
+\right| {\cal F}_t\Big]<\infty,
+\]
 which concludes our proof.
@@
 
+The last step in the proof of Theorem~\ref{thm:nonlocal_convergence}
+is to check that
+any limit point $(\eta_t)_{t\geq 0}$ of $\{(\eta_t)_{t\geq 0}\}_{N\geq 1}$
+actually takes its values in $\measures$, that is ``no mass has escaped to infinity''.
+
+\begin{lemma}
+\label{no mass at infty}
+Let $(\eta_t)_{t\geq 0}$ be a limit point of $\{(\eta_t)_{t\geq 0}\}_{N\geq 1}$. 
+Given $\delta>0$, 
+\[
+\IP\big[\eta_t\big(\{\|x\|>R\}\big)>\delta\big]\to 0\qquad\mbox{ as }R\to\infty.
+\]
+\end{lemma}
+\begin{proof}[Sketch]
+To avoid the idea being buried in notation, we sketch the proof in the 
+special case of $d=1$ and $\DG=\Delta$.
+For any $f\in C_b^\infty(\IR)$,
+\begin{multline}
+\label{special case first moment equation}
+\IE[\langle f,\eta_t\rangle] 
+=\IE[\langle f,\eta_0\rangle]
+\\
++\IE\Big[\int_0^t\Big\langle\gamma(x, \smooth{\gamma}\eta_s(x))
+\Delta \big(f(\cdot)r(\cdot,\smooth{r}\eta_s(\cdot))\big)(x)
++F(x,\smooth{F}\eta_s(x)) f(x),
+\eta_s(dx)\Big\rangle ds\Big]
+\end{multline} 
+We take a sequence of test functions $f_n$ increasing to
+$\exp(\lambda x)$, with $\lambda>0$. Having passed
+to the limit,
+substituted in~(\ref{special case first moment equation}) and 
+expanded the term involving the Laplacian,we obtain
+\begin{multline}
+\label{exponential moment}
+\IE[\langle \exp(\lambda x),\eta_t\rangle]
+=\IE[\langle \exp(\lambda x),\eta_0\rangle]
++\IE\Big[\int_0^t\Big\langle\gamma(x, \smooth{\gamma}\eta_s(x))
+\exp(\lambda x)
+\Big\{\lambda^2 r(x, \smooth{r}\eta_s(x))
+\\
++2\lambda\partial_x\big(r(\cdot,\smooth{r}\eta_s(\cdot)\big)(x)
++\partial_{xx} r(\cdot,\smooth{r}\eta_s(\cdot)\big)(x)
++F(x,\smooth{F}\eta_s(x))\Big\} ,
+\eta_s(dx)\Big\rangle ds\Big].
+\end{multline} 
+Evidently, in much the same way as in the proof of
+Lemma~\ref{lem:eta_f_bound},
+our conditions on $r$ and $F$ ensure
+that the integrand on the right hand side 
+of~(\ref{exponential moment})
+is bounded by $C\langle\exp(\lambda x),\eta_s(dx)\rangle$ for some constant
+$C$. Gronwall's inequality then implies that 
+$\IE[\langle\exp(\lambda x),\eta_t(dx)\rangle]$ 
+is uniformly bounded for $t\in [0,T]$, and an application of Markov's inequality
+tells us that for any $\delta >0$,
+$\IP[\eta_t([R,\infty])>\delta]\to 0$ as $R\to\infty$. A symmetric argument
+yields the corresponding bound for $\IP[\eta_t([-\infty, -R])>\delta$ and the 
+result is proved.
+\end{proof}
+
 % % % % % % % % % % % % %
-\subsection{Convergence of the nonlocal equation to the local equation}
-
-\comment{... for the cases in which we know this: FKPP-type and PME.
-This then shows that we can take the local, deterministic limit
-by taking $\theta, N \to \infty$ first, and then $\epsilon \to 0$ after.
-}
-
-In this section we prove Proposition~\ref{prop:nonlocal_pde_limits}.
-
-\subsubsection{Fisher-KPP-type}
-
-\comment{Insert TwoStepConvergenceV3 with Alison's markups incorporated here.}
+\subsection{Convergence of some nonlocal equations to classical PDEs}
+
+It is natural to conjecture that when the limit of the rescaled 
+population process that we obtained in the previous section solves a nonlocal
+PDE, then if we further scale the kernels 
+$\rho_r$, $\rho_\gamma$, and $\rho_F$ by setting 
+$\rho^\epsilon(\cdot)=\rho(\cdot/\epsilon)/\epsilon$, then as $\epsilon\to 0$, the 
+corresponding solutions should converge to a limiting
+population density that solves the corresponding ``classical'' PDE. We verify
+this in two examples; the first in which the nonlocal equation is a reaction
+diffusion equation with the ``nonlocality'' only appearing in the 
+reaction term, and the second in which the nonlocal PDE is a special 
+case of a nonlinear porous medium equation. These, in particular,
+capture the examples that we explored in 
+Section~\ref{ancestral lineages for travelling waves}.
+
+\subsubsection{Reaction diffusion equation limits}
+\label{two-step convergence to FKPP}
+
+In this subsection we prove Proposition~\ref{prop:nonlocal_to_local}. {\em The conditions of the
+proposition are in force throughout this subsection.} 
+The proof rests on a Feynman-Kac representation.
+We write $(Z_t)_{t\geq 0}$ for a diffusion with generator $\DG^*$ and denotes 
+its transition density by $f_t(x,y)$. The first step is a regularity
+result for this density.
+
+\begin{lemma} \label{regularityForX1}
+Fix $T>0$. There exists a constant $K= K(T)>0$ such that, for any 
+$x, y, z \in \mathbb{R}^d$ and $t \in [0,T]$,
+\begin{equation} \label{eq:boundDensityXt}
+\int |f_t(x,z)-f_t(y,z)| dz \leq \frac{|x-y|}{\sqrt{t}} K.
+\end{equation}
+\end{lemma}
+\begin{proof}
+We first use the Intermediate Value Theorem to obtain the bound
+\begin{align*}
+\int |f_t(x,z)-f_t(y,z)| dz & \leq \int |x-y| |\nabla f_t(w,z)| dz
+\end{align*}
+where $\nabla$ acts on the first coordinate only and $w$ is in the line 
+segment $[x,y]$ joining $x$ to $y$. 
+Under our assumptions on $b$ and $C$, equation~(1.3) 
+of~\cite{sheu:1991}, gives existence of constants 
+$\lambda=\lambda(T)>0$ and $K$ such that,
+\[ |\nabla f_t(w,z)|  \leq  \frac{K }{\sqrt{t}}p_{ \lambda  t}(w,z), \]
+where $p_s(x,y)$ is the Brownian transition density.
+Hence, 
+\begin{align*}
+\int |f_t(x,z)-f_t(y,z)| dz & \leq K 
+\frac{|x-y|}{\sqrt{t}} \int p_{\lambda  t}(w,z)dz = 
+K  \frac{|x-y|}{\sqrt{t}},
+\end{align*}
+which proves the result.
+\end{proof}
+\begin{lemma} \label{regularityForX2}
+Fix $T>0$. Let $x,y \in \mathbb{R}^d$, $t \in [0,T]$. Let us denote by 
+$(Z_t^y)_{t\geq 0}$ and $(Z_t^x)_{t\geq 0}$ independent copies of the 
+diffusion $(Z_t)_{t\geq 0}$ starting 
+from $y$ and $x$ respectively. There exists a constant $K=K(T)>0$ such that, 
+\[ \IE[\|Z_t^y-Z_t^x\|] \leq K(\sqrt{t} + \|y-x\|). \]
+\end{lemma}
+\begin{proof}
+First we write, 
+\[ \IE[\|Z_t^y-Z_t^x\|]  = \int \int \|u-v\| f_t(y,u) f_t(x,v) du dv . \]
+Under our regularity assumptions on $C$, $b$, using Equation~(1.2)
+of~\cite{sheu:1991}, there exist constants $K$, $\lambda =\lambda (T)>0$ 
+for which,
+\[ f_t(y,u) \leq K  p_{\lambda  t}(y,u). \]
+It then follows that,
+\begin{align}
+  \IE[\|Z_t^y-Z_t^x\|]  \leq \int \int \|u-v\| K^2 p_{\lambda  t}(y,u) 
+p_{\lambda  t}(x,v) dv du = K^2 \IE[\|B_{\lambda  t}^y-B_{\lambda  t}^x\|], 
+\label{eq:ExpDif1}
+\end{align}
+where $(B_t^y)_{t\geq 0}$ and $(B_t^x)_{t\geq 0}$ are 
+independent Brownian motions starting at $y$ and $x$ respectively. 
+Using the triangle inequality, and writing $(B^0_t)_{t\geq 0}$ for a 
+Brownian motion started from the origin,
+\begin{equation}
+\IE[\|B_{\lambda  t}^y-B_{\lambda  t}^x\|]\leq \|y-x\|+\IE[\|B^0_{2\lambda t}\|] 
+%&= \sqrt{ d \lambda t } \sqrt{2/\pi} e^{-(y-x)^2/(2d\lambda t )} + 
+%(y-x) (1-2\Phi(-(y-x)/(\lambda  d t))) \nonumber \\ 
+%& \leq \sqrt{2d \lambda  /\pi}  \sqrt{t} + 
+\leq \|y-x\|+C\sqrt{t}. \label{eq:ExpDif2}
+\end{equation}
+Substituting (\ref{eq:ExpDif2}) in (\ref{eq:ExpDif1}) gives the result.
+\end{proof}
+
+We use the representations:
+\begin{align}
+\varphi_t(x) &= \IE_x\Big[\varphi_0(Z_t) 
++ \int_0^t \varphi_s(Z_s)F(\varphi_s(Z_s)) ds\Big], \label{FK:varphi} \\
+\varphi^\epsilon_t(x) &= \IE_x\Big[\varphi_0(Z_t) 
++ \int_0^t \varphi^\epsilon_s(Z_s)F(\rho^\epsilon_F*\varphi^\epsilon_s(Z_s)) ds\Big],
+\end{align}
+from which
+\begin{equation} 
+\varphi_t(x) - \varphi^\epsilon_t(x) = 
+\IE_x\left[ \int_0^t \Big(\varphi_s(Z_s)F\big(\varphi_s(Z_s)\big)
+-\varphi^\epsilon_s(Z_s)F\big(\rho_\epsilon*\varphi^\epsilon_s(Z_s)\big)\Big) ds \right]. 
+\label{FK:diferencesVarphis}
+\end{equation}
+The key to our proof of Proposition~\ref{prop:nonlocal_to_local}
+will be to replace $F(\varphi_s(Z_s))$ by $F(\rho^\epsilon_F*\varphi_s(Z_s))$ 
+in this expression. 
+We achieve this through three lemmas.
+
+First we need a uniform bound on $\varphi$ and $\varphi^\epsilon$.  
+\begin{lemma} 
+\label{BoundednessVarphis}
+For any $T>0$ there exists $M = M(T, \Vert \varphi_0 \Vert) >0$ such that, 
+for all $0 \leq t \leq T$:
+\[ \max\{ \| \varphi_t(\cdot) \|_\infty, \| \varphi^\epsilon_t(\cdot) \|_\infty\} 
+< M.
+ \]
+\end{lemma}
+\begin{proof}
+Using that $\varphi_0$ and $F$ are bounded above, from the
+representation~(\ref{FK:varphi}), we have
+\begin{align*}
+\varphi_t(x) \leq \| \varphi_0 \|_\infty + 
+K \IE\Big[\int_0^t \varphi_s(Z_s) ds\Big].
+\end{align*}
+In particular, since $\varphi_s$ is non-negative,
+\[ \| \varphi_t(\cdot) \|_\infty \leq \| \varphi_0 \| 
++  K \int_0^t \| \varphi_s(\cdot) \|_\infty ds, \]
+so, by Gronwall's inequality,
+\[ \| \varphi_t(\cdot) \|_\infty \leq \| \varphi_0 \|_\infty \exp\left( K T \right). \]
+Similarly,
+$\| \varphi^\epsilon_t(\cdot) \|_{\infty} \leq \| \varphi_0 \|_\infty \exp\left( K T \right) $.
+\end{proof}
+
+We also need a continuity estimate for $\varphi$.
+\begin{lemma} 
+\label{ContinuityVarphi}
+Let $T>0$. There exists a constant 
+$K=K(T, \| \varphi_0\|_\infty)>0$ and 
+$\delta_0=\delta_0(T, \| \varphi_0\|_\infty) >0$ such that 
+for all $0 < \delta<\delta_0$ and $0 \leq t \leq T$,
+\[ 
+ \|x-y\|<\delta^3 \Rightarrow |\varphi_t(x)-\varphi_t(y)|< K\delta.
+\]
+\end{lemma}
+\begin{proof}
+First we need some notation. 
+Fix $T>0$ and write $M$ for the corresponding constant from 
+Proposition~\ref{BoundednessVarphis}. Let 
+$\| F \|_{M} = \sup_{x \in [0,M]} |F(x)|$. We reserve $\widehat{K}$ for 
+the constant on the right hand side of 
+equation~(\ref{eq:boundDensityXt}). 
+We write $K_{\varphi_0}$ for the Lipschitz constant of 
+$\varphi_0$. Set %Having this we can set:
+\[ 
+\delta_0=\min\Big( \frac{1}{\| F \|_M^{2}},\frac{1}{M e\big(2\| F \|_{M}+ \widehat{K}\big)}, 
+\frac{1}{K_{\varphi_0} + 2 \| F \|_M M},  1\Big).
+\]
+In what follows we take $0< \delta<\delta_0$.
+
+We first prove that the result holds if $t < \delta^2$. As before
+% $f_t(x,y)$ be 
+%the transition density of $(X_t)_{t \geq 0}$.  Let 
+let $Z_t^x$ and $Z_t^y$ be 
+independent copies of the diffusion $Z_t$ starting at $x$ and $y$ respectively. 
+From our representation (\ref{FK:varphi}) and 
+Lemma~\ref{BoundednessVarphis}, we can write:
+\begin{align*}
+|\varphi_t(x)- \varphi_t(y)| 
+&\leq \big|\IE_x[\varphi_0(Z_t)]-\IE_y[\varphi_0(Z_t)]\big| 
++ 2 \| F \|_M M t 
+\\ 
+& \leq \IE[|\varphi_0(Z_t^x)-\varphi_0(Z_t^y)|] 
++ 2 \| F \|_M M t  \\ 
+&\leq K_{\varphi_0}  \IE[\|Z_t^x-Z_t^y\|] 
++ 2 \| F \|_M M t \\ 
+& \leq K_{\varphi_0}  (\sqrt{t} + \|y-x\|) 
++ 2 \| F \|_M M t \\ 
+& \leq K_{\varphi_0} (\delta + \delta^3) 
++ 2 \| F \|_M M \delta^2 
+\leq (K_{\varphi_0} +1)\delta,
+\end{align*}
+where we have used Lemma~\ref{regularityForX2} in the fourth inequality and the definition of $\delta_0$ in the last inequality.
+
+Suppose now that $\delta^2<t$.
+We will follow the pattern in Lemma~2.2 of~\cite{penington:2017}. 
+First, note that by the Feynman-Kac formula we have an alternative 
+representation for $\varphi_t(x)$: for any $t'<t$,
+\[ 
+\varphi_t(x) = \IE_x\big[ \varphi_{t-t'}(Z_{t'}) 
+\exp\big( \int_0^{t'} F(\varphi_{t-s}(Z_s)) ds \big) \big]. 
+\]
+Therefore, setting $t'=\delta^2$, for all $z$
+\[ 
+e^{-\delta^2\| F \|_{M}}\IE_z\big[ \varphi_{t-\delta^2}(Z_{\delta^2})\big] 
+\leq  
+\varphi_t(z) 
+\leq e^{\delta^2\| F \|_{M}} \IE_z\big[  \varphi_{t-\delta^2}(Z_{\delta^2})\big]. 
+\]
+We can then deduce that,
+\begin{align}
+\nonumber
+\varphi_t(x)-\varphi_t(y) 
+&\leq e^{\delta^2\| F \|_{M}}\IE_x\big[ \varphi_{t-\delta^2}(Z_{\delta^2})\big] 
+- e^{-\delta^2\| F \|_{M}}\IE_y\big[ \varphi_{t-\delta^2}(Z_{\delta^2})\big] 
+\\ 
+\nonumber
+& = e^{\delta^2\| F \|_{M}}
+\Big(\IE_x\big[ \varphi_{t-\delta^2}(Z_{\delta^2})\big]
+- \IE_y\big[ \varphi_{t-\delta^2}(Z_{\delta^2})\big]\Big) 
+\\ 
+\nonumber
+&\qquad \qquad 
++ \big(e^{\delta^2\| F \|_{M}} - e^{-\delta^2\| F \|_{M}}  \big)
+\IE_y\big[ \varphi_{t-\delta^2}(Z_{\delta^2})\big] 
+\\
+\label{difference}
+&\leq e^{\delta^2\| F \|_{M}} 
+\Big(\IE_x\big[ \varphi_{t-\delta^2}(Z_{\delta^2})\big]- 
+\IE_y\big[ \varphi_{t-\delta^2}(Z_{\delta^2})\big]) 
++ M\big(e^{\delta^2\| F \|_{M}}-e^{-\delta^2\| F \|_{M}}\big),
+\end{align}
+where the last line follows from Lemma~\ref{BoundednessVarphis}.
+
+To bound the differences of the expected values in the last equation 
+note that, by using again Lemma~\ref{BoundednessVarphis},
+\begin{align*}
+\IE_x\big[ &\varphi_{t-\delta^2}(Z_{\delta^2})\big]
+- \IE_y[ \varphi_{t-\delta^2}(Z_{\delta^2})\big] & \\ 
+& = \int \varphi_{t-\delta^2}(z) (f_{\delta^2}(x,z)-f_{\delta^2}(y,z) ) dz  \\ 
+&\leq M \int \big|f_{\delta^2}(x,z)-f_{\delta^2}(y,z) \big| dz \\ 
+&\leq M \widehat{K} \frac{\|x-y\|}{\delta}  
+\leq M \widehat{K} \delta^2, 
+\end{align*}
+where in the first inequality we have used Lemma~\ref{regularityForX1}. 
+Substituting in~(\ref{difference}),
+\begin{align*}
+\varphi_t(x)-\varphi_t(y)
+&\leq e^{\delta^2 \| F \|_{M}} 
+\left(M \widehat{K}\delta^2 +M - M e^{-2\delta^2\| F \|_{M}}  \right) \\ 
+& \leq e^{\delta^2 \| F \|_{M}}\left(M \widehat{K}\delta^2 
++ 2 M \delta^2\| F \|_{M}  \right) \\ 
+&\leq e \left( M \widehat{K}+2 M \| F \|_M  \right) \delta^2 \leq  \delta,
+\end{align*}
+where the last two inequalities follow from the definition of $\delta$. 
+Interchanging $x$ and $y$ yields the same bound for $\varphi_t(y)-\varphi_t(x)$, and the result 
+follows.
+\end{proof}
+
+We proceed to control the difference between $F(\varphi)$ and 
+$F(\rho^\epsilon_F*\varphi)$. 
+Note first that since $\rho_F\in L^1$, 
+\[
+I(\epsilon):=\int_{\{\|y\|>\epsilon^{3/4}\}}\rho^\epsilon_F(y)dy
+=\int_{\{\|y\|>\epsilon^{-1/4}\}}\rho_F(y)dy
+\to 0\qquad\mbox{ as }
+\epsilon\to 0.
+\]
+
+%For simplicity, we define,
+%\[ \widehat{\delta}(\epsilon) := 2e^{-\epsilon^{-1/3}/2}+\epsilon^{1/9}. \]
+\begin{lemma} 
+\label{ContinuityConvolution}
+Let $T>0$. There exists a constant 
+$C=C(T,\| \varphi_0 \|_\infty)>0$ such that, for all $0 \leq t \leq T$, 
+for all $\epsilon$ small enough,
+\begin{equation} 
+\label{ContinuityConvolution1} 
+\| \varphi_t(\cdot) - \rho^\epsilon_F*\varphi_t(\cdot) \|_\infty 
+\leq C (I(\epsilon)+\epsilon^{1/4}). 
+\end{equation}
+Furthermore, there is a constant $\widetilde{C}(T, \| \varphi_0 \|_\infty) = \widetilde{C} >0 $ 
+such that, for all $0 \leq t \leq T$,
+\begin{equation} 
+\label{ContinuityConvolution2} 
+\| F(\varphi_t(\cdot)) - F(\rho^\epsilon_F*\varphi_t(\cdot)) \|_\infty 
+\leq \widetilde{C}\big(I(\epsilon)+\epsilon^{1/4}\big). % \widehat{\delta}(\epsilon). 
+\end{equation}
+\end{lemma}
+\begin{proof}
+Let $\epsilon<\delta_0^4$, with $\delta_0$ from Lemma~\ref{ContinuityVarphi}. Then,
+\begin{align*}
+|\varphi_t(x) - \rho^\epsilon_F*\varphi_t(x)| & = 
+\int_{\|x-y\| > \epsilon^{3/4} } \rho^\epsilon_F(x-y)|\varphi_t(y)-\varphi_t(x)| dy  \\ 
+& + \int_{\|x-y\| \leq \epsilon^{3/4} } \rho^\epsilon_F(x-y)|\varphi_t(y)-\varphi_t(x)| dy \\ 
+& \leq 2 M \int_{\|x-y\| > \epsilon^{3/4}  } \rho^\epsilon_F(x-y) dy 
++ \int_{\|x-y\| \leq \epsilon^{3/4}} \rho^\epsilon_F(x-y) K \epsilon^{1/4} dy \\
+&\leq 2M I(\epsilon) + K \epsilon^{1/4},
+\end{align*}
+where we used 
+the estimates of Lemma~\ref{BoundednessVarphis}
+and Lemma~\ref{ContinuityVarphi}.
+This proves (\ref{ContinuityConvolution1}). For (\ref{ContinuityConvolution2}), % note that, 
+%by Proposition~\ref{BoundednessVarphis}, we have that $\varphi_t(x)$ and 
+%$\rho_\epsilon*\varphi_t(x)$ are bounded by $M$. 
+let $L_M$ be the (uniform) Lipschitz constant of $F$ on $[0,M]$. Then,
+\begin{align*}
+ \| F(\varphi_t(\cdot)) - F(\rho^\epsilon_F*\varphi_t(\cdot)) \|_\infty 
+&\leq L_M \| \varphi_t(\cdot)) - (\rho^\epsilon_F*\varphi_t(\cdot)) \|_\infty \\ 
+& \leq L_M ( 2 M I(\epsilon) + K\epsilon^{1/4}),
+\end{align*}
+which proves (\ref{ContinuityConvolution2}). 
+\end{proof}
+
+\begin{proof}[of Proposition \ref{prop:nonlocal_to_local}]
+Let $\epsilon$ be small enough that Lemma~\ref{ContinuityConvolution} holds. 
+We use the notation $\widehat{\delta}(\epsilon)$ for the quantity on the right hand side 
+of~(\ref{ContinuityConvolution2}).
+Then from the representation~(\ref{FK:diferencesVarphis}) 
+and Lemma~\ref{ContinuityConvolution} we can write,
+\begin{align*}
+| &\varphi_t(x) - \varphi^\epsilon_t(x)|  \\ 
+& \leq \IE_x\left[ \int_0^t\Big| \varphi_s(Z_s)
+F(\rho^\epsilon_F*\varphi_s(Z_s))
+-\varphi^\epsilon_s(Z_s)
+F\big(\rho^\epsilon_F*\varphi^\epsilon_s(Z_s)\big)\Big| ds \right] 
++M t \widehat{\delta}(\epsilon)   \\ 
+& \leq \IE_x\left[ \int_0^t \big|F(\rho^\epsilon_F*\varphi^\epsilon_s(Z_s))\big|\cdot
+\big|\varphi^\epsilon_s(Z_s)-\varphi_s(Z_s)\big| ds  \right] \\ 
+& \qquad +  \IE_x\left[\int_0^t |\varphi_s(Z_s)| 
+\big|F(\rho^\epsilon_F*\varphi^\epsilon_s(Z_s))
+-F(\rho^\epsilon_F*\varphi_s(Z_s))\big| ds \right] 
++ M t \widehat{\delta}(\epsilon)  \\ 
+& \leq \| F \|_M \int_0^t \| \varphi^\epsilon_s(\cdot) 
+- \varphi_s(\cdot) \|_\infty ds
+  + M L_M \int_0^t \| \rho^\epsilon_F*\varphi^\epsilon_s(\cdot)
+-\rho^\epsilon_F*\varphi_s(\cdot) \|_\infty ds 
++  M  t \widehat{\delta}(\epsilon)  \\ 
+& \leq (\| F \|_M + M L_M) 
+\int_0^t \| \varphi^\epsilon_s(\cdot) - \varphi_s(\cdot) \|_\infty ds 
++ M  t \widehat{\delta}(\epsilon),
+\end{align*}
+where the second inequality is the triangle inequality, 
+and the third is Lemma~\ref{BoundednessVarphis}. 
+An application of Gronwall's inequality then yields,
+\begin{align*}
+\| \varphi^\epsilon_t(\cdot)-\varphi_t(\cdot)\|_\infty 
+&\leq M  t \widehat{\delta}(\epsilon)  
+\exp(t (\| F \|_M + M L_M)) \\ 
+& \leq  M  T \widehat{\delta}(\epsilon)  \exp(T(\| F \|_M + M L_M)),
+\end{align*}
+giving the result.
+\end{proof}
 
@@
 
-\plr{This is from pme.tex.}
-
-We are concerned with non-negative solutions to the equation
-\begin{equation}
-\label{mollified equation}
-\frac{\partial u^\epsilon}{\partial t}=
-%\frac{\partial^2}{\partial x^2}
-\Delta\left(u^\epsilon \cdot u^\epsilon *\zeta_\epsilon\right)
-+u^\epsilon\left(1-u^\epsilon*\zeta_\epsilon\right);
-\end{equation}
-where $*$ denotes convolution and we define
-a (non-negative) mollifier by
-$\zeta_\epsilon=\frac{1}{\epsilon}\zeta(\cdot/\epsilon)$, where $\zeta$
-satisfies
-$\zeta\in\cal{S}(\IR)$, $\int\zeta(x)dx=1$. Indeed, for convenience, in
-what follows we shall suppose that $\zeta =\rho*\check{\rho}$ where
-$\check{\rho}(z)=\rho(-z)$ and $\rho$ has
-compact support, although that
-is certainly stronger than we need.
-In particular, we should like to prove that as $\epsilon\to 0$ we have
+In this subsection we prove Proposition~\ref{nonlocalPME to PME}.
+To ease notation, we drop the subscript $\gamma$ on $\rho_\gamma$ and we present 
+the proof in $d=1$ (although we retain the notation $\nabla$).
+It should be clear that it extends almost without change
+to higher dimensions.
+
+Recall that 
+we are concerned with non-negative solutions to the equation~(\ref{mollified equation}):
+\begin{equation*}
+%\label{mollified equation}
+	\partial_t\psi_t^\epsilon(x) =
+	\Delta\left(\psi_t^\epsilon \, \rho^\epsilon *\psi_t^\epsilon\right)(x)
+	+\psi_t^\epsilon(x)\left(1-\rho^\epsilon *\psi_t^\epsilon(x) %*\zeta_\epsilon
+\right),
+\end{equation*}
+and 
+we assume that $\rho=\zeta*\check{\zeta}$ with $\zeta$ a rapidly decreasing function. 
+The example we have in mind is $\zeta$ (and therefore $\rho$) being the density of
+a mean zero Gaussian random variable.  
+We shall prove that under the 
+assumptions of Proposition~\ref{nonlocalPME to PME},
+as $\epsilon\to 0$, we have
 convergence to the solution to the porous medium equation with
@@
 \begin{equation}
-\label{PME}
-\frac{\partial u}{\partial t}=
+\label{PMEold}
+	\partial_t \psi_t(x)=
 %\frac{\partial^2}{\partial x^2}
-\Delta\left(u^2\right)
-+u\left(1-u\right).
-\end{equation}
-
-We work on $[0,T]\times \IT_K$ where $\IT_K$ is the one-dimensional
-torus of size $K$, and $T,K>0$ are fixed but arbitrary.
-
-\comment{rephrase/shorten this:}
-
-\begin{remark}
-By taking a sequence $K_n\to\infty$, and doing a bit of work,
-we can presumably then recover the result
-we need for, e.g., a population expanding its range from a compact
-set containing the origin (for which we know the solution to the PME
-converges to two travelling waves, travelling in opposite directions
-\cite{kamin/rosenau:2004}). Such waves have bounded support, even when
-we consider the equation on
-the whole real line, and travel at a fixed speed, so don't feel the boundedness
-of the torus,
-so this should be straightforward. The challenge will be to control the
-mass of the approximating functions that falls beyond that wavefront,
-since they themselves will have full support and so arguably `feel' that they
-are on the torus.
-It is not clear that it is worth doing the details for this paper - this is
-meant as an example.
-\end{remark}
-
-\begin{notation}
-
-Whenever we integrate with respect to $x$, this is implicitly over the
-whole torus $\IT_K$.
-
-We use $\rightharpoonup$ to denote weak convergence in the sense of analysts;
-that is, $u^\epsilon\rightharpoonup u$ in $L^1$ means $\int u^\epsilon v \dif x
-\rightarrow\int uv\dif x$ for all $v\in L^\infty$.
-
-We write $L_t^2(H^1)$ for functions for which the $H^1$ norm in
-space is in $L^2$ with respect to time, i.e.
-$$\int_0^T\int \left\{u(t,x)^2+\left(\frac{d}{dx} u(t,x)\right)^2\right\} \dif x \dif t <\infty,$$
-and $C_t(L^1)$
-will denote functions for which the $L^1$ norm in space is continuous in time.
-\end{notation}
-
-\begin{proposition}
-Suppose that $u_0^\epsilon\in L^1(\IT_K)$, $u_0^\epsilon\geq 0$, and
-$\sup_\epsilon\int u_0^\epsilon|\log u_0^\epsilon|dx<\infty$ with
-$u_0^\epsilon\rightharpoonup u_0^\epsilon$ as $\epsilon\to 0$. Then
-writing $u^\epsilon$ for the solution to~(\ref{mollified equation})
-on $[0,T]\times \IT_K$ with
-initial condition $u_0^\epsilon$,
-$u^\epsilon\rightharpoonup u$ as $\epsilon\to 0$ where
-$u\in L_t^2(H^1)\cap C_t(L^1)$, $\int u|\log u| dx<\infty$, and
-$u$ solves~(\ref{PME}) on $[0,T]\times \IT_K$. Moreover, strong convergence
-of the initial conditions implies strong convergence of the solutions.
-\end{proposition}
-%\noindent
-%{\bf Proof}
-
+	\Delta\left(\psi_t^2\right)(x)
+	+\psi_t(x)\left(1-\psi_t(x)\right).
+\end{equation}
+
+We work on the time interval $[0,T]$.
+We will require a lower bound on $\int \psi_t^\epsilon(x)\log \psi_t^\epsilon(x) dx$ 
+which we record as a lemma.
+\begin{lemma}
+\label{lower bound on ulogu}
+Suppose that there exists $\lambda<1$ and $C<\infty$, both independent of
+$\epsilon$, such that $\int \exp(\lambda |x|) \psi_0^\epsilon(x) dx<C$.
+Then there exists
+a constant $K<\infty$, independent of $\epsilon$, such that  
+ $\int \psi_t^\epsilon(x)\log \psi_t^\epsilon (x)dx>-K$ for all $t\in [0,T]$. 
+\end{lemma}
 \begin{proof}
-    \comment{Check where we use compactness of the mollifier.}
-
-Our proof owes a lot to~\cite{lions/mas-gallic:2001}.
+
+Consider 
+\begin{multline}
+\frac{d}{dt}\int \exp(\lambda x) \psi_t^\epsilon (x)dx
+	=\int \exp(\lambda x)\Delta \big(\psi_t^\epsilon \, \rho^{\epsilon}*\psi_t^\epsilon\big)(x) dx
+	\\
+%*\zeta_\epsilon)\dif x
+	+\int \exp(\lambda x)\psi_t^\epsilon(x)\big(1-\rho^{\epsilon}*\psi_t^\epsilon(x)\big) dx\\
+	=\int (\lambda^2-1)\exp(\lambda x) \psi_t^\epsilon(x) \rho^{\epsilon}*
+	\psi_t^\epsilon(x) dx 
+%*\zeta_\epsilon)\dif x
+	+\int \exp(\lambda x)\psi_t^\epsilon(x) dx\\
+\leq
+	\int \exp(\lambda x)\psi_t^\epsilon(x) dx,
+\end{multline}
+and so, by Gronwall's inequality, 
+$\int \exp(\lambda x)\psi_t^\epsilon (x)dx$ is uniformly bounded on $[0,T]$.
+In particular, combining with the Mean Value Theorem, we find 
+\begin{equation*}
+\int_x^{x+1}\psi_t^\epsilon(y)dy\leq C\exp(-\lambda x),
+\end{equation*}
+where the constant $C$ is independent of $x>1$.
+A fortiori, 
+\begin{equation}
+\label{exp decay of u} 
+\int_x^{x+1}\psi_t^\epsilon(y)\ind_{\psi_t^\epsilon(y)\leq 1}dy\leq C\exp(-\lambda x).
+\end{equation}
+Now the function $\psi\mapsto \ind_{0\leq \psi\leq 1}\psi|\log \psi|$ is concave, and so 
+using Jensen's inequality and~(\ref{exp decay of u}),
+\begin{equation*}
+\int_x^{x+1}\psi_t^\epsilon(y)
+|\log \psi_t^\epsilon (y)|\ind_{\psi_t^\epsilon(y)\leq 1}dy
+\leq C'x \exp(-\lambda x).
+\end{equation*}
+Evidently a symmetric argument applies for $x<-1$.
+Summing over $x$, we find
+\begin{equation*}
+\int \psi_t^\epsilon (x) \log \psi_t^\epsilon (x) dx
+\geq -C''\sum_{x=1}^\infty x\exp(-\lambda x)>-K>-\infty,  
+\end{equation*}
+as required.
+\end{proof}
+
+\begin{proof}[Proof of Proposition~\ref{nonlocalPME to PME}]
+
 First observe that
 \begin{multline*}
-\int u^\epsilon\cdot u^\epsilon*\zeta_\epsilon\dif x
-= \int\int\int u^\epsilon(x)u^\epsilon(x-y)\rho_\epsilon(y-z)
-\check{\rho}_\epsilon(z)\dif z\dif y\dif x
+	\int \psi_t^\epsilon(x)\, \rho^{\epsilon}*\psi_t^\epsilon(x) dx 
+=
+\int\int\int \psi_t^\epsilon(x)\psi_t^\epsilon(x-y)\zeta^{\epsilon}(y-z)
+\check{\zeta}^{\epsilon}(z) dz dy dx %\dif z\dif y\dif x
 \\
 =
-\int\int\int u^\epsilon(\tilde{x}-\tilde{z})
-u^\epsilon(\tilde{x}-\tilde{y})
-\rho_\epsilon(\tilde{y})
-\rho_\epsilon(\tilde{z})\dif \tilde{z}\dif \tilde{y}\dif \tilde{x}
-=\int\left(u^\epsilon*\rho_\epsilon\right(x))^2\dif x,
+\int\int\int \psi_t^\epsilon(\tilde{x}-\tilde{z})
+\psi_t^\epsilon(\tilde{x}-\tilde{y})
+\zeta^{\epsilon}(\tilde{y})
+\zeta^{\epsilon}(\tilde{z}) d\tilde{z} d\tilde{y} d \tilde{x}
+	=\int\left(\zeta^{\epsilon}*\psi_t^\epsilon(x)\right)^2 dx,
+%*\rho_\epsilon\right(x))^2\dif x,
 \end{multline*}
@@
 Now note that
-$$\frac{d}{dt}\int u^\epsilon (t,x) \dif x=\int \Delta (u^\epsilon*\zeta_\epsilon)\dif x
-+\int u^\epsilon(1-u^\epsilon*\zeta_\epsilon)\dif x= \int u^\epsilon \dif x
--\int (u^\epsilon*\rho)^2 \dif x.$$
-Thus $\int u^\epsilon(t,x)\dif x$ is uniformly bounded above in $t$
-and $\epsilon$ on $[0,T]$. Note that this also then gives a uniform
-bound on the rate of change of $\int u^\epsilon (t,x) \dif x$, and since
+\begin{eqnarray*}
+\frac{d}{dt}\int \psi_t^\epsilon (x) dx
+	&=&
+\int \Delta \big(\psi_t^\epsilon \, \rho^{\epsilon}*\psi_t^\epsilon\big)(x) dx 
+	+\int \psi_t^\epsilon(x)\big(1-\rho^{\epsilon}*\psi_t^\epsilon(x)\big) dx
+\\	
+&=&
+ \int \psi_t^\epsilon (x) d x
+	-\int \big(\zeta^{\epsilon}*\psi_t^\epsilon(x)\big)^2  dx.
+\end{eqnarray*}
+Thus $\int \psi_t^\epsilon(x) dx$ is uniformly bounded above in
+$\epsilon$ and $t\in [0,T]$. Note that this also then gives a uniform
+bound on the rate of change of $\int \psi_t^\epsilon (x) d x$, and since
 we are working on $[0,T]$ this will be enough to give continuity in time of the
@@
 Now consider
-\begin{eqnarray*}
-\frac{d}{dt}\int u^\epsilon\log u^\epsilon \dif x &=&
-\int (1+\log u^\epsilon)\left[\Delta (u^\epsilon\cdot
-u^\epsilon*\zeta_\epsilon)+u^\epsilon(1-u^\epsilon*\zeta_\epsilon)\right]
-\dif x
+\begin{eqnarray}
+	\frac{d}{dt}\int \psi_t^\epsilon\log \psi_t^\epsilon dx &=&
+	\int (1+\log \psi_t^\epsilon)\left[\Delta \big(\psi_t^\epsilon\,
+	\rho^{\epsilon}*\psi_t^\epsilon\big)
+	+\psi_t^\epsilon\big(1-\rho^{\epsilon}*\psi_t^\epsilon\big)\right]
+dx
+\nonumber
 \\
 &=&
-\int (1+\log u^\epsilon)\left[\nabla\left(u^\epsilon\cdot
-\nabla(u^\epsilon*\zeta_\epsilon)+
-\nabla u^\epsilon\cdot u^\epsilon*\zeta_\epsilon\right)
-+u^\epsilon(1-u^\epsilon*\zeta_\epsilon)\right] \dif x
+	\int (1+\log \psi_t^\epsilon)\left[\nabla\Big(\psi_t^\epsilon\,
+	\nabla(\rho^{\epsilon}*\psi_t^\epsilon)+
+	\nabla \psi_t^\epsilon\, \rho^{\epsilon}*\psi_t^\epsilon\Big)
+	+\psi_t^\epsilon\big(1-\rho^{\epsilon}*\psi_t^\epsilon\big)\right]  dx
+\nonumber
 	\\
 &=&
-\int \left[-\frac{\nabla u^\epsilon}{u^\epsilon}
-\left(u^\epsilon\cdot \nabla(u^\epsilon*\zeta_\epsilon)
-+\nabla u^\epsilon\cdot u^\epsilon*\zeta_\epsilon\right)+
-(1+\log u^\epsilon)u^\epsilon(1-u^\epsilon*\zeta_\epsilon)\right]\dif x
+\int \left[-\frac{\nabla \psi_t^\epsilon}{\psi_t^\epsilon}
+\Big(\psi_t^\epsilon\, \nabla(\rho^{\epsilon}*\psi_t^\epsilon)
++\nabla \psi_t^\epsilon\, \rho^{\epsilon}*\psi_t^\epsilon\Big)+
+(1+\log \psi_t^\epsilon)\psi_t^\epsilon(1-\rho^{\epsilon}*\psi_t^\epsilon)\right] d x
+\nonumber
 	\\
 &=&
--\int \left(\nabla (u^\epsilon*\rho_\epsilon)\right)^2 \dif x
--\int (\nabla u^\epsilon)^2\frac{u^\epsilon*\zeta_\epsilon}{u^\epsilon} \dif x
+-\int \left(\nabla (\zeta^{\epsilon}*\psi_t^\epsilon)\right)^2  dx
+-\int (\nabla \psi_t^\epsilon)^2\frac{\rho^{\epsilon}*\psi_t^\epsilon}{\psi_t^\epsilon}  dx
+\nonumber
 	\\
 &&+\int
-\left[u^\epsilon+u^\epsilon\log u^\epsilon(1-u^\epsilon*\zeta_\epsilon)
--u^\epsilon\cdot u^\epsilon*\zeta_\epsilon\right]\dif x\\
+\left[\psi_t^\epsilon+\psi_t^\epsilon\log \psi_t^\epsilon
+\big(1-\rho^{\epsilon}*\psi_t^\epsilon\big)
+-\psi_t^\epsilon\, \rho^{\epsilon}*\psi_t^\epsilon\right] dx
+\nonumber
+	\\
 &=&
--\int \left(\nabla (u^\epsilon*\rho_\epsilon)\right)^2 \dif x
--\int (\nabla u^\epsilon)^2\frac{u^\epsilon*\zeta_\epsilon}{u^\epsilon} \dif x
--\int (u^\epsilon*\rho_\epsilon)^2\dif x
+-\int \left(\nabla (\zeta^{\epsilon}*\psi_t^\epsilon)\right)^2  dx
+-\int (\nabla \psi_t^\epsilon)^2\frac{\rho^{\epsilon}*\psi_t^\epsilon}{\psi_t^\epsilon} dx
+-\int (\zeta^{\epsilon}*\psi_t^\epsilon)^2  dx
+\nonumber
 	\\
 &&+\int
-\left[u^\epsilon+u^\epsilon\log u^\epsilon(1-u^\epsilon*\zeta_\epsilon)
+\left[\psi_t^\epsilon+\psi_t^\epsilon\log \psi_t^\epsilon
+\big(1-\rho^{\epsilon}*\psi_t^\epsilon\big)
 %-u^\epsilon\cdot u^\epsilon*\zeta_\epsilon
-\right]\dif x .
-\end{eqnarray*}
+\right] dx .
+	\label{change in ulogu}
+\end{eqnarray}
 The first three terms are negative; and we already
 saw that the $L^1$ norm
-of $u^\epsilon$ is uniformly bounded.
-Moreover, since $u^\epsilon\log u^\epsilon$ is uniformly bounded below,
-$$-\int u^\epsilon \log u^\epsilon \cdot u^\epsilon*\zeta_\epsilon \dif x
-\leq C\int u^\epsilon*\zeta_\epsilon \dif x=\int u^\epsilon \dif x.$$
-From this we see immediately that $\int u^\epsilon \log u^\epsilon \dif x$
+of $\psi_t^\epsilon$ is uniformly bounded.
+%
+Moreover, since $\psi_t^\epsilon\log \psi_t^\epsilon$ is uniformly bounded below,
+$$-\int \psi_t^\epsilon \log \psi_t^\epsilon \, \rho^{\epsilon}*\psi_t^\epsilon d x
+\leq C\int \rho^{\epsilon}*\psi_t^\epsilon d x=\int \psi_t^\epsilon dx.$$
+From this and~(\ref{change in ulogu}),
+we see immediately that $\int \psi_t^\epsilon \log \psi_t^\epsilon dx$
 is uniformly bounded
-above in $\epsilon$ and $t\in [0,T]$. Moreover,
-since we are working on the bounded space $\IT_K$, the lower bound
-on $u^\epsilon\log u^\epsilon$ also allows us to
-bound $\int u^\epsilon\log u^\epsilon \dif x$ uniformly
-below, from which we deduce that
-we have a uniform bound on $\int u^\epsilon|\log u^\epsilon| \dif x$.
+above in $\epsilon$ and $t\in [0,T]$. 
+Combining with Lemma~\ref{lower bound on ulogu},
+we deduce that
+we have a uniform bound on $\int \psi_s^\epsilon(x)|\log \psi_s^\epsilon(x)| d x$.
 This in turn means that both
-$\int_0^t (u^\epsilon*\rho_\epsilon)^2 \dif x$ and
-$\int_0^t \big(\nabla (u^\epsilon*\rho_\epsilon)\big)^2 \dif x$
+$\int_0^t \int(\zeta^{\epsilon}*\psi_s^\epsilon(x))^2  dx ds$ and
+$\int_0^t \int \big(\nabla (\zeta^{\epsilon}*\psi_s^\epsilon(x))\big)^2  dx ds$
 are uniformly bounded in
@@
 \label{total equation}
-\int\Delta\left((u^\epsilon*\zeta_\epsilon)u^\epsilon\right)\phi \dif x =
-\int \nabla(u^\epsilon*\zeta_\epsilon)\cdot
-u^\epsilon\cdot\nabla\phi \dif x +\int u^\epsilon*\zeta_\epsilon
-\cdot\nabla u^\epsilon
-\cdot \nabla\phi \dif x.
+\int\Delta\left((\rho^{\epsilon}*\psi_t^\epsilon)\psi_t^\epsilon\right)\phi  dx =
+\int \nabla(\rho^{\epsilon}*\psi_t^\epsilon)\,
+\psi_t^\epsilon\,\nabla\phi dx +\int \rho^{\epsilon}*\psi_t^\epsilon
+\,\nabla \psi_t^\epsilon
+\, \nabla\phi d x.
 \end{equation}
@@
 \nonumber
-\int \nabla(u^\epsilon*\zeta_\epsilon)\cdot u^\epsilon\cdot\nabla\phi \dif x
+\int \nabla(\rho^{\epsilon}*\psi_t^\epsilon)\, \psi_t^\epsilon\, \nabla\phi  dx
 &=&
-\int\int\int\nabla u^\epsilon(x-y)\rho_\epsilon(y-z)\check{\rho}_\epsilon(z)
-u^\epsilon(x)\nabla\phi(x)\dif z \dif y \dif x
+\int\int\int\nabla \psi_t^\epsilon(x-y)\zeta^{\epsilon}(y-z)
+\check{\zeta}^{\epsilon}(z)
+\psi_t^\epsilon(x)\nabla\phi(x) dz  dy  dx
 \\
@@
 &=&
-\int\int\int\nabla u^\epsilon(\tilde{x}-\tilde{y})\rho_\epsilon(\tilde{y})
-\rho_\epsilon(\tilde{z})u^\epsilon(\tilde{x}-\tilde{z})
-\nabla\phi(\tilde{x}-\tilde{z})\dif \tilde{z}\dif \tilde{y} \dif \tilde{x}
+\int\int\int\nabla \psi_t^\epsilon(\tilde{x}-\tilde{y})
+\zeta^{\epsilon}(\tilde{y})
+\zeta^{\epsilon}(\tilde{z})\psi_t^\epsilon(\tilde{x}-\tilde{z})
+\nabla\phi(\tilde{x}-\tilde{z}) d\tilde{z} d\tilde{y} d\tilde{x}
 \\
 \nonumber
-&=&\int(\nabla u^\epsilon*\rho_\epsilon)\cdot
-\left((u^\epsilon\nabla\phi)*\rho_\epsilon\right)
-\dif x\\
+&=&\int(\nabla \zeta^{\epsilon}*\psi_t^\epsilon)\,
+\left(\zeta^{\epsilon}*(\psi_t^\epsilon\nabla\phi)\right)
+d x\\
 \nonumber
 &=&
-\frac{1}{2}\int\nabla ((u^\epsilon*\rho_\epsilon)^2)\cdot\nabla\phi \dif x
+\frac{1}{2}\int\nabla ((\zeta^{\epsilon}*\psi_t^\epsilon)^2)
+\,\nabla\phi  dx
 \\
@@
 &&+
-\int\nabla(u^\epsilon*\rho_\epsilon)
-\left[(u^\epsilon\cdot\nabla\phi)*\rho_\epsilon-
-\nabla\phi\cdot((u^\epsilon*\rho_\epsilon)\right]\dif x,
+\int\nabla(\zeta^{\epsilon}*\psi_t^\epsilon)
+\left[\zeta^{\epsilon}*(\psi_t^\epsilon\,\nabla\phi)-
+\nabla\phi\,(\zeta^{\epsilon}*\psi_t^\epsilon)\right] dx,
 \end{eqnarray}
@@
 \begin{multline*}
-\left|\int\left[u^\epsilon(x-y)\nabla\phi(x-y)\rho_\epsilon(y)-
-\nabla\phi(x)u^\epsilon(x-y)\rho_\epsilon(y)
-\right]\dif y\right|
+\left|\int\left[\psi_t^\epsilon(x-y)\nabla\phi(x-y)\zeta^{\epsilon}(y)-
+\nabla\phi(x)\psi_t^\epsilon(x-y)\zeta^{\epsilon}(y)
+\right] dy\right|
 \\
-\leq C\|\Delta\phi\|_\infty\int u^\epsilon (x-y)\rho_\epsilon(y)y\dif y.
+\leq C\|\Delta\phi\|_\infty\int \psi_t^\epsilon (x-y)y\zeta^{\epsilon}(y) d y.
 \end{multline*}
-Since we chose $\rho$ to have compact support,
-$y\rho_\epsilon(y)\leq C\epsilon\rho_\epsilon(y)$
-in the last integral and so the expression~(\ref{error 1}) is
+Since $\zeta\in\mathcal{S}(\IR)$, 
+%Using the bound 
+%$yp_{\epsilon^2/2}(y)\leq C\epsilon p_{\epsilon^2}(y)$ 
+%(c.f.~(\ref{first use of trick}) above)
+the integral in this expression is
 $\mathcal{O}(\epsilon)$.
@@
 \nonumber
-\int (u^\epsilon*\zeta_\epsilon)\cdot \nabla u^\epsilon\cdot\nabla\phi \dif x
+\int (\rho^{\epsilon}*\psi_t^\epsilon)\, \nabla \psi_t^\epsilon\, \nabla\phi dx
 &=&
-\int\int\int u^\epsilon(x-y)\rho_\epsilon(y-z)
-\check{\rho}_\epsilon(z)\nabla u^\epsilon(x)\nabla\phi(x)\dif z \dif y \dif x
+\int\int\int \psi_t^\epsilon(x-y)\zeta^{\epsilon}(y-z)
+\check{\zeta}^{\epsilon}(z)\nabla \psi_t^\epsilon(x)\nabla\phi(x) dz dy  dx
 \\
@@
 &=&
-\int\int\int u^\epsilon(\tilde{x}-\tilde{y})\rho_\epsilon(\tilde{y})
-\rho_\epsilon(\tilde{z})\nabla u^\epsilon(\tilde{x}-\tilde{z})
-\nabla\phi(\tilde{x}-\tilde{z})\dif \tilde{z}\dif \tilde{y} \dif\tilde{x}
+\int\int\int \psi_t^\epsilon(\tilde{x}-\tilde{y})\zeta^{\epsilon}(\tilde{y})
+\zeta^{\epsilon}(\tilde{z})\nabla \psi_t^\epsilon(\tilde{x}-\tilde{z})
+\nabla\phi(\tilde{x}-\tilde{z}) d \tilde{z} d\tilde{y} d\tilde{x}
 \\
 \nonumber
-&=&\int(u^\epsilon*\rho_\epsilon)\cdot
-\left((\nabla u^\epsilon\nabla\phi)*\rho_\epsilon\right) \dif x\\
+	&=&\int(\zeta^{\epsilon}*\psi_t^\epsilon)\,
+\left(\zeta^{\epsilon}*(\nabla \psi_t^\epsilon \, \nabla\phi)\right)  dx\\
 \nonumber
 &=&
-\frac{1}{2}\int\nabla ((u^\epsilon*\rho_\epsilon)^2)\cdot\nabla\phi \dif x
+\frac{1}{2}\int\nabla ((\zeta^{\epsilon}*\psi_t^\epsilon)^2)
+\, \nabla\phi  dx
 \\
@@
 &&+
-\int (u^\epsilon*\rho_\epsilon)
-\left[(\nabla u^\epsilon\cdot\nabla\phi)*\rho_\epsilon-
-\nabla\phi\cdot((\nabla u^\epsilon*\rho_\epsilon)\right]\dif x,
+\int (\zeta^{\epsilon}*\psi_t^\epsilon)
+\left[\zeta^{\epsilon}*(\nabla \psi_t^\epsilon\, \nabla\phi)-
+\nabla\phi\,(\nabla \zeta^{\epsilon}*\psi_t^\epsilon)\right] dx,
 \end{eqnarray}
-and~(\ref{error 2}) is controlled in the same way as~(\ref{error 1})
+and~(\ref{error 2}) is controlled in the same way as~(\ref{error 1}):
 using the Intermediate Value Theorem:
 \begin{multline*}
-\left|\int\left[\nabla u^\epsilon(x-y)\nabla\phi(x-y)\rho_\epsilon(y)
--\nabla\phi(x)\nabla u^\epsilon(x-y)\rho_\epsilon(y)
-\right]\dif y\right|
+\left|\int\left[\nabla \psi_t^\epsilon(x-y)\nabla\phi(x-y)\zeta^{\epsilon}(y)
+-\nabla\phi(x)\nabla \psi_t^\epsilon(x-y)\zeta^{\epsilon}(y)
+\right] dy\right|
 \\
-\leq C\|\Delta\phi\|_\infty\left|\int \nabla u^\epsilon(x-y)\rho_\epsilon(y)y
-\dif y\right|\\
-\leq C'\|\Delta\phi\|_\infty\epsilon \int\left|
-\nabla u^\epsilon(x-y)\rho_\epsilon(y)
-\right|\dif y.
+\leq C\|\Delta\phi\|_\infty\left|\int \nabla \psi_t^\epsilon(x-y)
+y \zeta^{\epsilon}(y)
+d y\right|,
 \end{multline*}
+which again is $\mathcal{O}(\epsilon)$.
 
@@
 The calculations above yield both a uniform (in $\epsilon$) bound on
-$u^\epsilon*\rho_\epsilon$ in
-$L^1\cap L^2\big([0,T]\times \IT_K\big)$, and
+$\zeta^{\epsilon}*\psi_t^\epsilon$ in
+$L^1\cap L^2\big([0,T]\times \IR\big)$, and
 \begin{multline}
-\int u^\epsilon(t,x)\phi(x)\dif x-\int u^\epsilon (0,x)\phi(x)\dif x
-=\int_0^t\int (u^\epsilon*\rho_\epsilon)^2\Delta\phi(x)\dif x
+\int \psi_t^\epsilon(x)\phi(x) dx-\int \psi_0^\epsilon (x)\phi(x) dx
+	=\int_0^t\int (\zeta^{\epsilon}*\psi_s^\epsilon(x))^2\Delta\phi(x) dx
 \\
-+\int_0^t \int u^\epsilon*\rho_\epsilon\left(1- u^\epsilon*\rho_\epsilon\right)
-\phi(x)\dif x
+	+\int_0^t \int \zeta^{\epsilon}*\psi_s^\epsilon(x)
+	\left(1- \zeta^{\epsilon}*\psi_s^\epsilon(x)\right)
+\phi(x) dx
 +\mathcal{O}(\epsilon)
@@
 (for sufficiently regular $\phi$). Since
-$\int u^\epsilon(t,x)\phi(x)\dif x-
-\int (u^\epsilon*\rho_\epsilon)(t,x)\phi(x)\dif x$ is order $\epsilon$, we see
-that $u^\epsilon*\rho_\epsilon$ converges weakly in $L^1$ to the (unique)
+$\int \psi_t^\epsilon(x)\phi(x) d x-
+\int \zeta^{\epsilon}*\psi_t^\epsilon (x)\phi(x) d x$ is order $\epsilon$, we see
+that $\zeta^{\epsilon}*\psi^\epsilon\rightharpoonup \psi$ in $L^1$, where $\psi$ is the (unique)
 solution
 to equation~(\ref{PME})
-and, so, therefore, does $u^\epsilon$. Strong convergence, that is
-$\int |u^\epsilon -u|\phi\dif x \to 0$, follows from the
-uniform integrability of $u^\epsilon$ that we
+and, so, therefore, does $\psi^\epsilon$. In fact, strong convergence, that is
+$\int |\psi^\epsilon -\psi|\phi dx \to 0$, follows from the
+uniform integrability of $\psi^\epsilon$ that we
 deduce from the uniform control of
-$\int u^\epsilon|\log u^\epsilon|\dif x$ that we proved above.
+$\int \psi^\epsilon|\log \psi^\epsilon| d x$ that we proved above.
 \end{proof}
@@
 
-In this section we prove Theorem~\ref{them:nonlocal_pde_limits},
-which takes interaction distances to zero in the limit as well.
-
-\todo[inline]{BEGIN OneStepConvergence}
-\textbf{PREVIOUSLY, In this whole document $\rho_\epsilon$ will be the density of a normal with mean $0$ and variance $\epsilon^2$, and $q_\theta$ the density of a normal with mean $0$ and variance $1/\theta$.
-That is, $\rho_\epsilon(x) = p_{\epsilon^2}(x)$ and $q_\theta = p_{1/\theta}(x)$.
-This is HOPEFULLY FIXED NOW.}
-
-\begin{theorem} \label{TeoremOneStepConvergence}
-    Let $(\eta_t)_{t \geq 0}$ be the scaled particle system with $r(x, \eta) \equiv \gamma(x, \eta) \equiv 1$.
-    Suppose $F(x)$ satisfies for $x \ge 0$:
-    \begin{enumerate}
-        \item $F(x)$  is bounded above.
-        \item $|F'(x)|$ is bounded,
-        \item and $||F''(x)||_\infty < \infty$.
-    \end{enumerate}
-    We will also suppose $\theta$ is big enough that $1- F(x)/\theta$ is non-negative.
-
-    We will assume $\eta_0 := \eta_0(\epsilon,N,\theta)$
-    is a sequence of initial conditions for $(\eta_t)_{t \geq 0}$
-    such that there exists a finite constant $C>0$ independent of $\epsilon$, $N$, and $\theta$
-    such that
-    \begin{enumerate}
-        \item[(i)] $\langle 1 , \eta_0 \rangle < C $
-        \item[(ii)]  $\| \rho_\epsilon * \eta_0(x) \|_\infty < C$ for all $x \in \IR^d$
-        \item[(iii)] $|\rho_\epsilon * \eta_0(x) - \rho_\epsilon * \eta_0(y)| \leq C \| x - y \|$ for all $x,y \in \IR^d$, and
-        \item[(iv)] $\rho_\epsilon * \eta_0(x) dx$ converges weakly to $u_0(x)dx$ for some $u_0(x) \in \mathcal{C}^2(\IR^d)$.
-    \end{enumerate}
-    Furthermore, suppose that
-    \begin{equation}
-        \frac{\theta}{\epsilon^d N} + \frac{1}{\theta \epsilon^{2}} \to 0 . \label{ConditionsForConvergence}
-    \end{equation}
-    Fix $T>0$.
-Then, the measure $((\rho_\epsilon *\eta_t)(x) dx)_{t \geq 0}$ converges weakly in $D([0,T], \measures)$ to a measure $(\Xi_t(dx))_{t \geq 0}$.
-Moreover, up to a modification on a set of measure zero, $\Xi_t(x) = u_t(x)dx$, where $u_t(x)$ is a weak solution to:
-    \[ \partial_t u = \frac{1}{2}\Delta u + u F(u) \]
-    with initial condition $u_0$. That is, for every smooth function with compact support $f$ and $t>0$, we have:
-    \begin{equation*}
-     \int \partial_t  u_t(x) f(x) dx = \int u_t(x)\frac{1}{2} \Delta f(x) dx + \int f(x) u_t(x) F(u_t(x)) dx.
-    \end{equation*}
-\end{theorem}
-
-\todo[inline]{Question: Why do we need that regularity on $u_0$?
-I believe all we need is that (\ref{aprox3}) holds, and for that, I am almost sure that $u_0$ only needs to satisfy the first three hypotheses for $\eta_0(x)$.
-Furthermore,  if I am not mistaken, those are all implied by $u_0(x) \in L^1(\IR^d) \cap L^2(\IR^d) \cap \mathcal{C}^1(\IR^d)$ in case we want a nice space to put on the result.
- Alison says: $C^1 \cap L^1$ probably enough, but...
- }
-
-\todo[inline]{TODO: Below what we write as $\rho_\epsilon$ is actually $\rho_F = p_{\epsilon_F^2}$; resolve this somehow. (it seems nice to retain the dependence on $\epsilon$ somehow)}
-
-To prove this we will proceed in a standard pattern, proving $C$-tightness of the measure and then identifying the limit.
-
-As a preliminary, we will prove some basic tools we are going to need all the way through.
-First, we prove that, under the conditions of Theorem~\ref{TeoremOneStepConvergence}, $\eta_t$ has a uniformly bounded total mass in expectation.
-We then prove some regularity estimates of a random walk with Gaussian jumps.
-While this may seem disconnected from our goal the generator of this random walk is in the first integral element that appears in the martingale problem for $\eta_t$, equation (\ref{mgp1}).
-It is then, no surprise, that we need some control over the regularity this term brings to our particle system.
-
-We then focus on $C$-tighness of $\rho_\epsilon * \eta_t(x)dx$.
-For this we will prove that for fixed $x$, the random variable $\rho_\epsilon*\eta_t(x)$ has uniformly bounded expectation.
-Using this and the regularity of the random walk mention above, we will be able to prove the $C$-tightness of $\rho_\epsilon * \eta_t(x)dx$.
-
-Then we will proceed to identify the limit.
-For this, a continuity estimate for $(\rho_\epsilon*\eta_t(x))$ is needed, which is again a consequence of the random walk estimates mentioned above.
-Using this we focus on controlling the convergence of \textit{non-linear terms} in the martingale problem of $(\rho_\epsilon*\eta_t(x))$ (as the others converge as a consequence of weak convergence).
-Those do not converge as a consequence of weak convergence, since they are not written as an integral on $M^{\otimes k}(\IR^d)$ of $(\rho_\epsilon*\eta_t(x) dx)$ (for some $k \in \mathbb{N}$).
-Instead, we will first compare the quadratic terms to terms only involving $\rho_\epsilon*\eta_s$ (and not $\eta_s(dy)$) and then we will exchange those terms with a suitable integral in $M^{\otimes2}(\IR^d)$, for which convergence do follow easily.
-
-\subsubsection{Preliminaries}
-
-Since we're assuming that $\gamma$ and $r$ are identically 1,
-the death rate is $1 + F(x, \eta) / \theta$.
-For reference,
-the martingale problem (Definition \ref{defn:mgale_construction})
-for $\eta_t$ gives that for any smooth function $\phi$,
-\begin{align} \label{mgp1}
-    \langle \phi(x), \eta_{t}(dx) \rangle
-    -
-    \langle \phi(x), \eta_{0}(dx)\rangle
-    &= \nonumber
-    M_t(\phi)
-    +
-    \int_{0}^{t} \langle \theta \int_{\IR^d}
-            \left( \phi(y) -\phi(x) \right)
-        q_\theta(x,dy), \eta_s(dx)
-    \rangle ds
-    \\ & {}
-    +
-    \int_0^t \langle
-        F(x, \eta_s) \phi(x),
-        \eta_s(dx)
-    \rangle ds ,
-\end{align}
-where $M_t(\phi)$ is a martingale with quadratic variation:
-\begin{align} \label{mgp2}
-    \begin{split}
-[ M(\phi) ]_t
-    &:=
-    \frac{\theta}{N}
-    \int_{0}^{t} \bigg\{
-        \left\langle \int_{\IR^d} \phi^2(y) q_\theta(x,dy), \eta_s(dx) \right\rangle
-    \\
-    & \qquad \qquad {} +
-    \left\langle \left(1 + \frac{F(x, \eta_s)}{\theta } \right)
-        \phi^2(x), \eta_s(dx)) \right\rangle 
-    \bigg\} ds. 
-    \end{split}
-\end{align}
-
-Several times below we will need to bound second moments,
-and for this purpose it will be useful to record that \eqref{mgp1} and \eqref{mgp2}
-imply that the following is a martingale:
-\begin{align} \label{mgp3}
-    \nonumber
-    \langle \phi, \eta_t \rangle^2
-    -
-    & \langle \phi, \eta_0 \rangle^2
-    -
-    \int_0^t
-        2 \langle \phi, \eta_s \rangle
-        \left\langle
-            \theta \int_{\IR^d} (\phi(y) - \phi(x)) q_\theta(x, dy)
-            + F(x, \eta_s) \phi(x),
-            \eta_s(dx)
-        \right\rangle
-    ds
-    \\ & {}
-    -
-    \frac{\theta}{N}
-    \int_0^t
-        \left\langle
-            \int_{\IR^d} \phi^2(y) q_\theta(x, dy)
-            +
-            \left(1 + \frac{F(x, \eta_s)}{\theta}\right) \phi^2(x),
-            \eta_s(dx)
-        \right\rangle
-    ds .
-\end{align}
-
-Above, we showed in Lemma~\ref{lem:eta_compact_containment}
-uniform boundedness the total mass under the assumption of fixed $\epsilon$.
-It is easy to see that the same proof applies
-in this situation -- indeed, the hardest part, Lemma~\ref{lem:gamma_bound} is not needed,
-since $r$ and $\gamma$ are 1 --
-and gives us the following result.
-
-\begin{lemma}[Boundedness of total mass] \label{Lemma:UniformlyBoundedMass}
-    Under the assumptions of Theorem~\ref{TeoremOneStepConvergence},
-    for each $T \ge 0$ there is a finite constant $C$ (independent of $\epsilon, N, \theta$),
-    such that $\IE\left[ \sup_{0 \leq s \leq T} \langle 1, \eta_s \rangle \right] \leq C$.
-\end{lemma}
-
-%% PLR: removing, since we can just refer to the above?
-% \begin{proof}
-% By putting $\phi(x)=1$ in the martingale problem of $\eta_t$, equation (\ref{mgp1}), we have,
-% \begin{align} \label{eq:MPTotalMass}
-% \langle 1, \eta_t \rangle &= \langle 1, \eta_0 \rangle + \int_0^t \langle F(\rho_\epsilon * \eta_s), \eta_s \rangle ds + M_t
-% \end{align}
-% where $M_t$ is a martingale with quadratic variation,
-% \begin{align} \label{eq:QVTotalMass}
-% [M]_t = \frac{\theta}{N}\int_0^t \langle 1 + \frac{F(\rho_\epsilon* \eta_s)}{\theta}, \eta_s \rangle d s 
-% \end{align}
-% By taking expectations in (\ref{eq:MPTotalMass}) we get,
-% \[ \IE[\langle 1, \eta_t \rangle] =  \IE[\langle 1, \eta_0 \rangle]  + \IE[ \int_0^t \langle F(\rho * \eta_s), \eta_s \rangle ds ]   \leq C +   C \mathbb{E}\left[ \int_0^t \langle 1, \eta_s \rangle ds \right].\]
-% In last inequality we used that $F(x)1_{x >0}$ and $\langle 1, \eta_0 \rangle$ are uniformly bounded above.
-By Gronwall's inequality we deduce $\IE[\langle 1, \eta_s \rangle]$ is bounded on $[0,T]$.
-Hence, by taking expectations in (\ref{eq:QVTotalMass}) and using again the bound on $F(x)1_{x>0}$ we get,
-% \begin{equation} \IE\left[ [M]_t \right] \leq \frac{\theta}{N} C \int_0^t \mathbb{E}\left[ \langle 1, \eta_s \rangle ds \right] \leq \frac{\theta}{N}C t \label{eq:quadvarMass} \end{equation}
-% Note that, with this, $\IE[ [M]_t]$ is bounded (and in fact $\mathcal{O}(\theta/N)$). By the Burkholder-Davis-Gundy inequality and then Jensen's inequality we get
-% \begin{align*}
-%     \IE\left[ \sup_{0 \leq t \leq T} M_t \right]
-%     \leq
-%     C \IE\left[ [M]_T \right]^{1/2}
-%     \leq
-%     C \IE[M]_T^{1/2}
-%     \leq
-%     C  
-% \end{align*}
-% Taking supremum and then expectation in (\ref{eq:MPTotalMass}) and using the last inequality gives the result.
-% 
-%     \comment{Alison says: I'd actually write out
-%     $\sup \langle 1, \eta_s \rangle \le \int_0^T xxx ds + \sup M_t$ .
-%     }
-% 
-% \end{proof}
-
-\begin{lemma}
-        \label{lem:SecondMomentMass}
-    Under the assumptions of Theorem~\ref{TeoremOneStepConvergence}
-    there is a finite constant $C$ (independent of $\epsilon, N, \theta$) such that,
-    for all $t \in [0,T]$ and for big enough $N$ and $\theta$,
-    $\IE[ \langle 1, \eta_t \rangle^2] \leq C$.
-\end{lemma}
-
-\begin{proof}[of Lemma~\ref{lem:SecondMomentMass}]
-    Using equation~\eqref{mgp3} with $\phi = 1$,
-    \begin{align*}
-        \IE[\langle 1, \eta_t \rangle^2]
-        &=
-        \IE[\langle 1, \eta_0 \rangle^2]
-        +
-        \IE\left[
-        \int_0^t
-            2 \langle 1, \eta_s \rangle
-            \langle F(x, \eta_s), \eta_s(dx) \rangle
-            +
-            \frac{\theta}{N} \langle 2 + F(x, \eta_s)/\theta, \eta_s(dx) \rangle
-        ds
-        \right] .
-    \end{align*}
-    Since $F$ is bounded above and $\theta/N$ converges,
-    we have for an appropriate $C$ that
-    \begin{align*}
-        \IE[\langle 1, \eta_t \rangle^2]
-        \le
-        C + C \int_0^t \IE[\langle 1, \eta_s \rangle] ds
-        + C \int_0^t \IE[\langle 1, \eta_s \rangle^2] ds .
-    \end{align*}
-    The result follows from Lemma~\ref{Lemma:UniformlyBoundedMass} and Gronwall's inequality.
-\end{proof}
-
-\paragraph{Regularity estimates of the density of a independent Gaussian random walk}
-Let us write $\mathcal{L}^\theta f(x) := \theta \int (f(y)-f(x))q_\theta(x,y) dy$ with $q_\theta$ is a Gaussian kernel of mean $0$ and variance $1/\theta$.
-We note that $\mathcal{L}^\theta$ is the generator of a continuous random walk, where at rate $\theta$ we have the arrival of Gaussian jumps of mean $0$ and variance $1/\theta$.
-
-In what follows we let $\psi_t^{\epsilon, x}(y)$ be the solution of:
-\begin{equation}
-    \frac{\partial}{ \partial_t} \psi_t^{\epsilon,x}
+In this section we prove Theorem~\ref{thm:local_convergence},
+which simultaneously scales the parameters $\theta$ and $N$ and the interaction 
+kernel $\rho_F$ in the special case in which $r\equiv 1\equiv\gamma$, $q_{\theta}(x,dy)$
+is isotropic with zero mean, the kernel
+$\rho_F$ is Gaussian, and the scaling 
+limit is a reaction diffusion equation.
+
+To simplify notation, in this section we shall write 
+$$\rho_\epsilon*\eta(x)=\rho_F^\epsilon*\eta(x)
+=\langle p_{\epsilon^2}(x,y),\eta(dy)\rangle,$$
+where $p_t(x,y)$ denotes the heat semigroup.
+
+The first part of the proof mirrors that of Theorem~\ref{thm:nonlocal_convergence}:
+we establish sufficient bounds on the moments of $\rho_\epsilon*\eta_t(x)$ to
+establish $C$-tightness and then apply standard results on 
+convergence of Markov processes from~\cite{ethier/kurtz:1986}. Although
+we prove the required bounds, we skip the details of this part. The challenge
+comes in identifying the limit points. This is much more intricate than the case in 
+which we do not scale the interaction kernel, as weak convergence will no longer
+be sufficient to guarantee the form of the nonlinear terms in the limiting equation.
+Identification of the limit will rest on regularity inherited from continuity 
+estimates for a random walk with Gaussian jumps which we prove in 
+Subsection~\ref{continuity for random walk}.
+Various bounds on $\rho_\epsilon*\eta_t$ are then provided in 
+Subsection~\ref{bounds on rhoepsilon},
+and we identify the limit points in Subsection~\ref{limit in onestep case}.
+
+\subsubsection{Continuity estimates for a Gaussian random walk}
+\label{continuity for random walk}
+
+Let us write $\mathcal{L}^\theta f(x) := \theta \int (f(y)-f(x))q_\theta(x,y) dy$ 
+where $q_\theta$ is a Gaussian kernel of mean $0$ and variance $1/\theta$. 
+We note that $\mathcal{L}^\theta$ is the generator of a continuous (time and 
+space) random walk, which makes jumps of mean $0$ and variance $1/\theta$ at
+rate $\theta$.
+
+In what follows we write $\psi_t^{\epsilon, x}(y)$ for the solution of
+\begin{equation}
+    \partial_t \psi_t^{\epsilon,x}
     =
-    \mathcal{L}^\theta \psi_t^{\epsilon, x}
+    \mathcal{L}^\theta \psi_t^{\epsilon, x},
     \label{AlmostHeatEquation}
 \end{equation}
-with initial condition $\psi_0^{\epsilon,x}(y) = \rho_\epsilon(y-x)$.
-We have the following result for $\psi_t^{\epsilon,x}$.
+with initial condition 
+$\psi_0^{\epsilon,x}(y) = \rho_\epsilon(y-x) =p_{\epsilon^2}(x,y)$.
+%We have the following result for $\psi_t^{\epsilon,x}$.
 
@@
     Fix $t>0$,
-    let $(N(s))_{s \ge 0}$ be a rate 1 Poisson process,
+    let $(N(s))_{s \ge 0}$ be a rate one Poisson process,
     and let $T(t) = N(\theta t) / \theta$.
@@
     \]
-    and moreover, there is a $C$ independent of $\epsilon$ or $t$ such that
+    and, moreover, there is a $C$ independent of $\epsilon$ or $t$ such that
     \[
@@
 \begin{proof}
-    The first claim follows immediately from $\mathcal{L}^\theta$ being the generator
-    of a continuous-time random walk,
-    where independent Gaussian jumps with mean $0$ and variance $1/\theta$
-    arrive at rate $\theta$.
+    The first claim is immediate from the definition of the random walk 
+with generator $\mathcal{L}^\theta$.
 
 For the second claim, first define $\tau(t) = T(t)-t$.
-    % which has mean $0$ and variance $t/\theta$.
-    % so by Chebyshev's inequality,
-    % \begin{equation}
-    %     \IP\left\{ \tau(t) < - \frac{\epsilon^2 + t}{2} \right\}
-    %     \leq
-    %     \IP\left\{  \frac{|T(t)-t|}{\epsilon^2+t} > \frac{1}{2} \right\}
-    %     \leq
-    %     \frac{4t}{\theta(\epsilon^2+t)^2} \leq \frac{2}{\epsilon^2 \theta}.
-    %     \label{eq:IneqConcentrationT}
-    % \end{equation}
 Since if $\tau(t) \ge -(\epsilon^2 + t)/2$,
@@
         \IE\left[ 
-            \frac{1}{2 \pi (\epsilon^2+T(t))^{d/2}}
+            \frac{1}{\big(2 \pi (\epsilon^2+T(t))\big)^{d/2}}
         \right] \nonumber
@@
     Now, observe that since $\IE[e^{-N(\theta t)}] = \exp(-\theta t (1 - e^{-1}))$,
-    then by Markov's inequality,
-    \begin{align*}
+    by Markov's inequality,
+    \begin{align}
         \IP\left\{
@@
         \right\}
-        \\&\le
+\nonumber
+\\
+&\leq \frac{\IE[\exp\big(-N(\theta t)\big)]}{\exp\big(-\theta(t-\epsilon^2)/2\big)}
+\nonumber
+        \\&=
         \frac{
@@
         }
+\nonumber
         \\&=
         \exp\left\{ - \delta \theta t - \frac{\theta \epsilon^2}{2} \right\} ,
-    \end{align*}
+\label{bound for negative tau}
+    \end{align}
     where $\delta = 1/2 - e^{-1} > 0$.
@@
     \]
-    Now, $e^{-\delta \theta t - \epsilon^2 \theta / 2} (1 + t/\epsilon^2)^{d/2}$ is decreasing in $t$
-    for all $t$ if $\epsilon^2 \theta$ is sufficiently large:
-    this holds because its derivative is
+    Now observe that the derivative (with respect to $t$) of 
+$e^{-\delta \theta t - \epsilon^2 \theta / 2} (1 + t/\epsilon^2)^{d/2}$ 
 is
@@
     \]
-    which is negative if $\theta(\epsilon^2 + t) > d/2 \delta$.
-    Therfore, the second term in \eqref{eqn:psi_infty_bound} 
+    which is negative if $\theta(\epsilon^2 + t) > d/2 \delta$,
+so that
+the second term in \eqref{eqn:psi_infty_bound} 
 is bounded by $C / (\epsilon^2 + t)^{d/2}$
 (for a different constant $C$).
-    Substituting this into \eqref{eqn:psi_infty_bound} obtains the result.
+Substituting this into \eqref{eqn:psi_infty_bound} yields the result.
 \end{proof}
 
-We will need further comparisons of $\psi_t^{\epsilon,x}$ to the heat semigroup,
-and for this we will first need the following fact about large deviations
-of a Poisson process.
+We are going to approximate $\psi_t^{\epsilon,x}(\cdot)$ by $p_{\epsilon^2+t}(x, \cdot)$,
+and to control the error that this introduces we 
+need to control $T(t)-t$. We achieve this through a large deviations bound.
 
@@
 
-\begin{proof}[of Lemma~\ref{lem:poisson_ld}]
+\begin{proof}%[of Lemma~\ref{lem:poisson_ld}]
     We apply Cram\'er's Theorem.
@@
         =
-        \IP\left\{
-            N(\theta) t) / \theta
+        \IP\Big\{
+            \frac{N(\theta t)}{ \theta}
             >
             t + A(\epsilon^2 + t)
-        \right\} .
+        \Big\} .
     \end{align*}
@@
 and so we may write $N(\theta t) = Z_1(t) + \cdots + Z_\theta(t)$,
-    where the $Z_i(t)$ are i.i.d.~ Poisson($t$) random variables.
-    To apply Cram\'er's Theorem, we need the rate function for the Poisson($t$) distribution,
+where the $Z_i(t)$ are i.i.d.~Poisson($t$) random variables.
+    To apply Cram\'er's Theorem, we need the rate function for the 
+Poisson($t$) distribution,
     which is
@@
         -
-        (t + A(\epsilon^2 + t)) \log\left( 1 + \frac{A(\epsilon^2 + t)}{t} \right) 
+        \big(t + A(\epsilon^2 + t)\big) \log\left( 1 + \frac{A(\epsilon^2 + t)}{t} \right) 
     \\ &\le
@@
         -
-        (t + A(\epsilon^2 + t)) \log(1 + A)
+        \big(t + A(\epsilon^2 + t)\big) \log(1 + A)
     \\ &\le
@@
         -
-        \frac{1}{2} (t + A(\epsilon^2 + t)) \log(1 + A)  .
-    \end{align*}
-    Since $(1/2) \log(1 + A) > 3/2$, hence $1 - (1/2) \log(1 + A) < - 1/2$,
-    and we are done.
+        \frac{1}{2} \big(t + A(\epsilon^2 + t)\big) \log(1 + A)  .
+    \end{align*}
+    Since $(1/2) \log(1 + A) > 3/2$, from which $1 - (1/2) \log(1 + A) < - 1/2$,
+    the proof is complete.
 \end{proof}
 
-Now we would like to show that $\psi_t^{\epsilon,x}(y)$
-is uniformly close to $p_{\epsilon^2 + t}(x, y)$
-under the assumptions.
+As advertised, we wish to control the difference between
+$\psi_t^{\epsilon,x}(y)$
+and $p_{\epsilon^2 + t}(x, y)$.
 
@@
     and with $A$ as in Lemma~\ref{lem:poisson_ld},
-    \begin{align*}
+    \begin{multline}
+\label{heat kernel estimate}
         \left|
@@
         \right|
+        \\
 \le
-        \frac{C}{\epsilon^2 \theta}^{d/2}
+        \frac{C}{(\epsilon^2 \theta)^{d/2}}
         p_{2(A+1)(\epsilon^2+t)}(x, y)
@@
         \right\} .
-    \end{align*}
+    \end{multline}
 \end{lemma}
 
-\begin{proof}[of Lemma~\ref{Lemma:BoundPsiHS2}]
-    The three terms on the right hand side of the Lemma
-    correspond to bound obtained by partitioning
-    into three events according to the value of $\tau(t)$:
-    let $A_1 = \{ \tau(t) < - (\epsilon^2 + t)/2 \}$,
-    let $A_2 = \{ \tau(t) > A(\epsilon^2 + t) \}$,
+\begin{proof}%[of Lemma~\ref{Lemma:BoundPsiHS2}]
+    Still using the notation of Lemma~\ref{PsiBoundHS},
+the three terms on the right hand side of 
+equation~(\ref{heat kernel estimate})
+    correspond to bounds obtained by partitioning
+    into three events according to the value of $\tau(t)$.
+    Let $A_1 = \{ \tau(t) < - (\epsilon^2 + t)/2 \}$,
+    $A_2 = \{ \tau(t) > A(\epsilon^2 + t) \}$,
     and $A_3$ the remaining event, $\{ - (\epsilon^2 + t)/2 \le \tau(t) \le A(\epsilon^2 + t) \}$.
@@
     \end{align*}
-
     For the first term, note that if $a < b$ then
@@
     \end{align*}
-    where the inequality follows because both terms in the absolute values are less than 1.
+    where the inequality follows because both terms under the absolute value 
+are less than 1.
     % note the original had $p_{b/2}$ on the right.
-    Applying this with $a = \epsilon^2 + t + \tau(t)$ and $b = \epsilon^2 + t$,
-    and using the same bound as we did for the second term of equation~\ref{eqn:psi_infty_bound},
+Since, on the event $A_1$, $\tau(t)<0$, we can  
+apply this with $a = \epsilon^2 + t + \tau(t)$ and $b = \epsilon^2 + t$,
+and, using the bound~(\ref{bound for negative tau}),
     \begin{align*}
@@
     For the third term, we will first collect some facts.
-    Observe that on this event,
+    Observe that on the event $A_3$,
     $\epsilon^2 + t + \tau(t)$ is between
@@
     Now, by the Intermediate Value Theorem,
-    \begin{align*}
+    \begin{align}
+\label{deduction from IVT}
         \left|
@@
         \left| \frac{\partial p_s(x, y)}{\partial s} \right|
-    \end{align*}
+    \end{align}
     for some $s$ between $\epsilon^2 + t + \tau(t)$ and $\epsilon^2 + t$.
-    Now,
+   Since 
     \begin{align*}
@@
         \\ &=
-        - \frac{d}{2s} p_s(x, y) + \frac{\|x - y\|^2}{2 s^2} p_s(x, y)  .
-    \end{align*}
-    Applying the inequality~\eqref{eqn:p_deriv_term2},
-    using the fact that $p_s(x, y) \le \sqrt{2} p_{2s}(x,y)$,
+        - \frac{d}{2s} p_s(x, y) + \frac{\|x - y\|^2}{2 s^2} p_s(x, y),
+    \end{align*}
+    applying the inequality~\eqref{eqn:p_deriv_term2},
+    using the fact that $p_s(x, y) \le 2^{d/2} p_{2s}(x,y)$,
     and then \eqref{eqn:p_bounded_on_interval},
@@
     \end{align*}
-    Therefore, recalling that $\IE[\tau(t)^2] = t / \theta$,
+    Therefore, recalling that $\IE[\tau(t)^2] = t / \theta$, substituting 
+into~(\ref{deduction from IVT}),
     \begin{align*}
@@
     \label{Lemma:ContinuityHS}
-Let $s>0, x, y, z\in \IR^d$. The following estimate holds:
+Let $s>0$, and $x, y, z\in \IR^d$. The following estimate holds:
 \[
@@
     \leq
-    \frac{C|x-y|}{\sqrt{s}} \left(p_{2s}(x,z) + p_{2s}(y,z)\right) ,
+    \frac{C\|x-y\|}{\sqrt{s}} \left(p_{2s}(x,z) + p_{2s}(y,z)\right) ,
 \]
@@
 \begin{proof}
+
     Expanding the difference of two squares,
     \begin{align*}
-        e^{- \frac{(y-z)^2}{2 s}}
+        e^{- \frac{\|y-z\|^2}{2 s}}
         -
-        e^{- \frac{(x-z)^2}{2 s}}
+        e^{- \frac{\|x-z\|^2}{2 s}}
         &=
         \left(
-            e^{-\frac{(y-z)^2}{4 s}}
+            e^{-\frac{\|y-z\|^2}{4 s}}
             -
-            e^{-\frac{(x-z)^2}{4 s}}
+            e^{-\frac{\|x-z\|^2}{4 s}}
         \right)
         \left(
-            e^{-\frac{(y-z)^2}{4 s}}
+            e^{-\frac{\|y-z\|^2}{4 s}}
             +
-            e^{-\frac{(x-z)^2}{4 s}}
+            e^{-\frac{\|x-z\|^2}{4 s}}
         \right) .
     \end{align*}
-    % % (big version of the previous equation:)
-    % \begin{align*}
-    %     &\exp\left( - \frac{(y-z)^2}{2 s} \right)
-    %     -
-    %     \exp\left( - \frac{(x-z)^2}{2 s} \right)
-    %     \\ &=
-    %     \left(
-    %         \exp\left(-\frac{(y-z)^2}{4 s} \right)
-    %         -
-    %         \exp\left(-\frac{(x-z)^2}{4 s} \right)
-    %     \right)
-    %     \left(
-    %         \exp\left(-\frac{(y-z)^2}{4 s} \right)
-    %         +
-    %         \exp\left(-\frac{(x-z)^2}{4 s} \right)
-    %     \right) .
-    % \end{align*}
-    By using the Intermediate Value Theorem we can write the right hand side as
+Now, thinking of the first term in brackets as a function of a single variable on
+the line segment $[y,z]$ connecting $y$ to $z$, we can apply the
+Intermediate Value Theorem and take the modulus to bound this expression by 
     \[
-        (y-x)
-        \left( - \frac{2(w-z)}{4s} \exp\left(-\frac{(w-z)^2}{4s}\right)\right)
+        \|y-x\|
+        \left( \frac{2\|w-z\|}{4s} \exp\left(-\frac{\|w-z\|^2}{4s}\right)\right)
         (4 \pi s)^{d/2}
@@
     \]
-    for some $w \in [y,z]$.
+    for some $w\in [y,z]$.
     Using the fact that $x e^{-x^2}$ is uniformly bounded,
@@
 
-\paragraph{The martingale problem for a time dependent function.}
-Before proceeding we make the following observation.
+\subsubsection{Moment bounds for $\rho_\epsilon*\eta$}
+\label{bounds on rhoepsilon}
+
+\begin{lemma}
+\label{bounds on moments}
+For each $T\in [0,\infty)$, and $k\in\IN$, there exist constants $C=C(k,T)$ and
+$\widetilde{C}=\widetilde{C}(k,T)$, independent of $\epsilon$, such that for all 
+$x\in\IR^d$ and all $u,t\in [0,T]$ with $u<t$,
+\begin{equation}
+\label{moment bound rhoepsilon}
+\IE\Big[\left.\big(\rho_\epsilon*\eta_t(x)\big)^k\right| {\cal F}_u\Big]
+\leq C\IE\Big[\langle\psi_{t-u}^{\epsilon,x}(z), \eta_u(dz)\rangle^k\Big]
++C\frac{\theta}{N\epsilon^d}
+\IE\Big[\langle\psi_{t-u}^{\epsilon,x}(z), \eta_u(dz)\rangle\Big];
+\end{equation} 
+and
+\begin{multline}
+\label{flandoli trick for rhoepsilon}
+\IE\Big[\left. \int_u^t\langle\psi_{t-s}^{\epsilon,x}(z),\eta_s(dz)\rangle^{k-1}
+\big\langle\psi_{t-s}^{\epsilon,x}(z)|F(\rho_\epsilon*\eta_s(z))|,
+\eta_s(dz)\big\rangle ds\right| {\cal F}_u\Big]
+\\
+\leq\widetilde{C}\IE\Big[\langle\psi_{t-u}^{\epsilon,x}(z), \eta_u(dz)\rangle^k\Big]
++\widetilde{C}\frac{\theta}{N\epsilon^d}
+\IE\Big[\langle\psi_{t-u}^{\epsilon,x}(z), \eta_u(dz)\rangle\Big];
+\end{multline}
+where the function $\psi^{\epsilon,x}_t(\cdot)$ was
+defined in~(\ref{AlmostHeatEquation}).
+In particular, %since $\IE[\langle 1,\eta_0\rangle^k\]$ is finite, 
+under the assumptions of Theorem~\ref{thm:local_convergence}, the
+quantities on the right hand side of~(\ref{moment bound rhoepsilon})
+and~(\ref{flandoli trick for rhoepsilon}) are both integrable 
+with respect to Lebesgue measure.  
+\end{lemma}
+\begin{proof}
+To simplify our expressions, we shall consider the case $u=0$, but
+the proof goes through unchanged for other values of $u$.
+
+The proof proceeds by induction.
+
 For any time-dependent function $\phi_t(x)$
-with time derivative $\dot \phi_t(x) = \frac{d}{dt} \phi_t(x)$,
-the martingale problem for $\eta_t$, (like \ref{mgp1}),
-is
-% \comment{Alison says: not sure this needs spelling out?}
-\begin{align}
-        \label{timeMGP}
+with time derivative $\dot \phi_t(x) = \partial_t \phi_t(x)$,
+\begin{align*}
+%        \label{timeMGP}
     \langle \phi_0(x), \eta_t(dx) \rangle
-    &= \nonumber 
+    &= %\nonumber 
     \langle \phi_t(x), \eta_0(dx) \rangle
@@
     \int_{0}^t \langle \phi_{t-s}(x) F(x, \eta_s) , \eta_s(dx) \rangle ds ,
-\end{align}
-where $M_t(\phi_\cdot(\cdot))$ has quadratic variation
-\begin{align}
-        \label{timeMGP2}
-    [M(\phi_\cdot(\cdot))]_t
+\end{align*}
+where $M_t(\phi_\cdot(\cdot))$ is a martingale. 
+Taking $\phi_t(\cdot)=\psi_t^{\epsilon,x}(\cdot)$,
+\begin{eqnarray}
+\nonumber
+\rho_\epsilon*\eta_t(x)&=&\langle\psi^{\epsilon,x}_0(y),\eta_t(dy)\rangle
+\\
+&=&\langle\psi^{\epsilon,x}_t(y),\eta_0(dy)\rangle
++\int_0^t\langle\psi^{\epsilon,x}_{t-s}(y)F\big(\rho_\epsilon*\eta_s(y)\big), \eta_s(dy)\rangle ds
++M_t(x),
+\label{expn rhoepsilon}
+\end{eqnarray}
+where $M_t(x)$ is a martingale. 
+% DON'T DELETE THIS - I'LL NEED IT LATER
+%\begin{equation}
+%\label{qv M(x)}
+%[M(x)]_t=\frac{\theta}{N}\int_0^t\Big\langle\int\psi^{\epsilon,x}_{t-s}(z)^2q_\theta(y,dz)
+%+\Big(1-\frac{F(\rho_\epsilon*\eta(y)}{\theta}\Big)\psi^{\epsilon,x}_{t-s}(y)^2,\eta_s(dy)
+%\Big\rangle.
+%\end{equation}
+Taking expectations in~(\ref{expn rhoepsilon}), using that $F$ is bounded above, and 
+applying Gronwall's inequality, we obtain~(\ref{moment bound rhoepsilon})
+in the case $k=1$. 
+Moreover, rearranging~(\ref{expn rhoepsilon}) we find 
+\begin{equation}
+-\int_0^t\langle\psi^{\epsilon,x}_{t-s}(y)F(\rho_\epsilon*\eta_s(y), \eta_s(dy)\rangle ds
+=\langle\psi^{\epsilon,x}_t(y),\eta_0(dy)\rangle
+-\langle \psi^{\epsilon,x}_0(y),\eta_t(dy)\rangle +M_t(x),
+\end{equation} 
+and taking expectations again this yields 
+$$\IE\Big[-\int_0^t\langle\psi^{\epsilon,x}_{t-s}(y)F(\rho_\epsilon*\eta_s(y), 
+\eta_s(dy)\rangle ds\Big]
+\leq \widehat{C}\IE\big[\langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle\big].$$
+Since $F$ is bounded above, there exists a constant $K$ such that $|F|\leq K-F$ and so 
+combined with the bound on $\IE[\langle\psi^{\epsilon, x}_0(y),\eta_t(dy)\rangle]$ just
+obtained, this in turn yields 
+$$\IE\Big[\int_0^t\langle\psi^{\epsilon,x}_{t-s}(y)|F(\rho_\epsilon*\eta_s(y)|, 
+\eta_s(dy)\rangle ds\Big]\leq 
+\widetilde{C}\IE\big[\langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle\big],$$
+which is~(\ref{flandoli trick for rhoepsilon})
+in the case $k=1$.
+
+Now suppose that we have established~(\ref{moment bound rhoepsilon}) 
+and~(\ref{flandoli trick for rhoepsilon}) for all exponents $j<k$.
+First we calculate the generator $\Pgen^N$ of our scaled population process applied
+to functions of the form $\langle f,\eta\rangle^k$.
+Recalling that each jump of the process involves the birth or death or a single 
+individual, and so increments $\langle f,\eta\rangle$ by $\pm f/N$ at the location of
+that individual, we find 
+\begin{multline}
+\label{pgen applied to kth moment}
+\Pgen^N\Big(\langle f,\eta\rangle^k\Big)
 =
-    \frac{\theta}{N} \int_0^t \langle
-        \int_{\IR^d} \phi_{t-s}(z)^2 q_\theta(y,dz)
+\Big\langle
+\int\theta N\Big\{k\frac{f(y)}{N}\langle f,\eta\rangle^{k-1}+
+\binom{k}{2}\frac{f(y)^2}{N^2}\langle f,\eta\rangle^{k-2}+\cdots
++\frac{f(y)^{k}}{N^{k}}\Big\}q_\theta(x,dy),\eta(dx)\Big\rangle
+\\
 +
-        \left( 1 + \frac{F(y, \eta_s)}{\theta}\right) \phi_{t-s}(y)^2,
-    \eta_s(dy) \rangle ds .
-\end{align}
-
-%%%%%%%%%%%%%%%%%%
-\subsubsection{Tightness}
-
-\paragraph{Bounds for $\{ \rho_\epsilon * \eta_s (x)\}_{0 \leq s \leq T}$}
-
-\begin{lemma}
-        \label{FirstBoundLocalDensity}
-    Under the conditions of Theorem~\ref{TeoremOneStepConvergence}
-    there is a constant $C>0$ (independent of $\epsilon$, $N$, $\theta$, and $x$) such that,
-    \[ \IE[ \rho_\epsilon*\eta_t(x) ] < C \]
-    for all $t \in [0,T]$ and $x \in \IR^d$.
-\end{lemma}
-
-\begin{proof}
-    Recall that $\psi_t^{\epsilon,x}$ is the solution of (\ref{AlmostHeatEquation})
-    with initial condition $\psi_0^{\epsilon,x}(y)=\rho_\epsilon(y-x)$.
-    By replacing $\phi_t$ with $\psi_t^{\epsilon,x}$ in (\ref{timeMGP}) we can write
-    for each $x$
-    \begin{align}
-            \label{MartingaleProblemMolifier}
-        \rho_\epsilon*\eta_t(x)
+\Big\langle\theta N\Big(1-\frac{F(\rho_\epsilon*\eta(x))}{\theta}\Big)
+\Big\{-k\frac{f(x)}{N}\langle f,\eta\rangle^{k-1}+
+\binom{k}{2}\frac{f(x)^2}{N^2}\langle f,\eta\rangle^{k-2}+\cdots
++\frac{(-1)^{k}f(x)^{k}}{N^{k}}\Big\},\eta(dx)\Big\rangle.
+\end{multline}
+Mimicking what we did above, we set $f(\cdot)=\psi^{\epsilon,x}_t(\cdot)$ and 
+write
+\begin{multline}
+\label{kth moment for time varying function}
+\IE\Big[\langle \psi^{\epsilon,x}_0,\eta_t\rangle^k\Big]
+=\langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle^k
++\IE\Big[\int_0^t\Pgen^N\big(\langle\psi^{\epsilon,x}_{t-s}(y)\big),\eta_s(dy)\rangle ds
+\\
+-\int_0^t\langle k\dot{\psi}^{\epsilon,x}_{t-s}(y), \eta_s(dy)\rangle
+\langle \psi^{\epsilon, x}_{t-s}(y),\eta_s(dy)\rangle^{k-1}ds\Big].
+\end{multline}
+Using that $\sup_s\|\psi^{\epsilon,x}_s(\cdot)\|_\infty=C/\epsilon^d$,
+$N\epsilon^d>1$,
+%$\langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle^{j}
+%\leq C\langle\psi^{\epsilon, x}_{t}(y),\eta_0(dy)\rangle$, 
+and our inductive
+hypothesis, we find
+\begin{multline*}
+\IE\Big[
+\Big\langle
+\int_0^t\theta N\Big\{\sum_{j=2}^{k}\binom{k}{j}\frac{\psi_{t-s}^{\epsilon,x}(y)^j}{N^j}\langle \psi^{\epsilon,x}_{t-s},\eta_s\rangle^{k-j}
+\Big(1+(-1)^j\Big(1-\frac{F(\rho_\epsilon*\eta_s(y))}{\theta}\Big)\Big),
+\eta_s(dy)\Big\rangle ds\Big]
+\\
+\leq 
+C\IE\Big[\Big\langle\int_0^t\sum_{j=2}^k\frac{\theta}{N\epsilon^d}
+\Big(\frac{1}{(N\epsilon^d)^{j-2}}\Big)
+\Big\langle
+\Big(2+\frac{|F(\rho_\epsilon*\eta_s(y))|}{\theta}\Big),\eta_s(dy)\Big\rangle
+\langle\psi^{\epsilon,x}_{t-s},\eta_s\rangle^{k-j}ds\Big]
+\\
+\leq
+C'\frac{\theta}{N\epsilon^d}\sum_{j=1}^{k-1}
+\IE\big[\langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle^j\big]
+\leq
+C''\frac{\theta}{N\epsilon^d}
+\Big(\IE\big[\langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle^k\big]
++\IE\big[\langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle\big]\Big).
+\end{multline*}
+Combining this with~(\ref{pgen applied to kth moment})
+and~(\ref{kth moment for time varying function}), using once again the fact that $F$
+is bounded above, we find 
+\begin{multline*}
+\label{kth step of induction}
+\IE\Big[\langle \psi^{\epsilon,x}_0,\eta_t\rangle^k\Big]
+\leq
+\IE\big[\langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle^k\big]
++\tilde{C}\IE\Big[\int_0^t
+\langle\psi^{\epsilon, x}_{t-s}(y),\eta_s(dy)\rangle^k ds\Big]
+\\
++C''\frac{\theta}{N\epsilon^d}
+\Big(\IE\big[\langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle^k\big]+
+\IE\big[\langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle\big]\Big)
+%\langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle^j
+,
+\end{multline*}
+and~(\ref{moment bound rhoepsilon}) 
+follows from Gronwall's inequality. Rearranging exactly as in the case $k=1$, we 
+recover~(\ref{flandoli trick for rhoepsilon}) 
+and the inductive step is complete.
+\end{proof}
+
+We shall need the following consequence of the bounds that we obtained in 
+Lemma~\ref{bounds on moments}:
+\begin{corollary}
+Under the assumptions of Lemma~\ref{bounds on moments},
+for each $k\geq 1$,
+\begin{equation}
+\label{double integrals with respect to eta}
+\IE\Big[\big\langle (\rho_\epsilon*\eta_t)^{k},\eta_t\big\rangle \Big]<C(k)<\infty.
+\end{equation}
+\end{corollary}
+\begin{proof}[Sketch]
+First observe that if $A\in (0,1)$, then 
+\begin{equation}
+\label{heat equation at smaller time}
+p_{A\epsilon^2}(x,y)
+=\frac{1}{A^{d/2}}p_{\epsilon^2}(x,y)\exp\big(-\frac{\|x-y\|^2}{2\epsilon^2}
+\left(\frac{1}{A}-1\right)\big)\leq \frac{1}{A^{d/2}}p_{\epsilon^2}(x,y).
+\end{equation}
+Now consider
+    \begin{align*}
+\IE\big[\langle \rho_\epsilon*\eta_t(x),\eta_t(dx)\rangle\big]&=
+\IE\big[\int\int p_{\epsilon^2}(x,z)\eta_t(dz)\eta_t(dx)\big]
+\\        
+&=
+\IE\big[\int\int\int p_{\epsilon^2/2}(x,y) p_{\epsilon^2/2}(y,z)dy\eta_t(dz)\eta_t(dx)\big]
+       % \langle p_{\epsilon^2/2} * p_{\epsilon^2/2} * \eta_t(x), \eta(dx) \rangle
+        \\ &=
+       \IE\Big[ \int \left( p_{\epsilon^2/2} * \eta_t(y) \right)^2 dy \Big]
+\\&\leq C\int \IE\big[\big(\rho_\epsilon*\eta_t(x)\big)^2\big] dx,
+    \end{align*}
+where we used~(\ref{heat equation at smaller time}) in the last line.
+Using Lemma~\ref{bounds on moments}
+and our assumptions on $\eta_0$, this quantity is finite.
+
+To illustrate the inductive step, now consider
+\begin{multline}
+\label{rewrite for inductive step}
+\IE\big[\langle \rho_\epsilon*\eta_t(x)^2,\eta_t(dx)\rangle\big] 
 =
-        \langle \psi_t^{\epsilon,x}(y), \eta_0(dy) \rangle
-        +
-        \int_0^t \langle
-            \psi_{t-s}^{\epsilon,x}(y) F(y, \eta_s),
-        \eta_s(dy) \rangle ds
-        +
-        M_t^x .
-    \end{align}
-    First recall that our second assumptions on $\eta_0$
-    was (ii) $\|\rho_\epsilon * \eta_0\|_\infty < C$.
-    Since 
+\IE\Big[\int\int\int p_{\epsilon^2}(x,z_1) p_{\epsilon^2}(x,z_2)
+\eta_t(dz_1)\eta_t(dz_2)\eta_t(dx)\Big]
+\\
+=
+\IE\Big[\int\cdots\int p_{\epsilon^2/2}(x,y_1) 
+p_{\epsilon^2/2}(x,y_2)p_{\epsilon^2/2}(y_1,z_1)
+p_{\epsilon^2/2}(y_2,z_2)
+\eta_t(dz_1)\eta_t(dz_2)dy_1dy_2\eta_t(dx)\Big].
+\end{multline}
+We use the identity
 \[
-        \langle \psi_t^{\epsilon,x}(y), \eta_0(dy) \rangle
-        =
-        \IE \left[ \langle
-            p_{\epsilon^2 + T(t)}(x, y), \eta_0(dy)
-        \rangle \right]
-        =
-        \IE \left[ \int_{\IR^d} p_{T(t)}(x, y) \rho_\epsilon * \eta_0(y) dy \right],
+p_{\epsilon^2/2}(x,y_1) p_{\epsilon^2/2}(x,y_2)
+=p_{\epsilon^2}(y_1,y_2)p_{\epsilon^2/4}\Big(x, \frac{y_1+y_2}{2}\Big)
 \]
-    this implies that
-    $\langle \psi_t^{\epsilon,x}(y), \eta_0(dy) \rangle \le C$.
-    Since $F(x)$ is uniformly bounded above,
-    if we take expectations and use Lemma~\ref{Lemma:UniformlyBoundedMass},
-    \begin{align}
-    \IE[\rho_\epsilon * \eta_t(x)]
-        &\le \label{BoundForMollifierStart}
-        \IE[\langle \psi_t^{\epsilon,x}(y), \eta_0(dy) \rangle]
-        +
-        C \IE\left[\int_0^t \langle \psi_{t-s}^{\epsilon,x}(y), \eta_s(dy) \rangle ds\right]
-        \\ & \nonumber
+to rewrite~(\ref{rewrite for inductive step}) as
+\begin{align*}
+&\IE\Big[\int p_{\epsilon^2/2}*\eta_t(y_1) p_{\epsilon^2/2}*\eta_t(y_2)
+p_{\epsilon^2/4}*\eta_y\big(\frac{y_1+y_2}{2}\big)p_{\epsilon^2}(y_1,y_2)dy_1dy_2\Big]
+\\
+&\leq 
+\IE\Big[\int\Big\{
+\big(p_{\epsilon^2/2}*\eta_t(y_1)\big)^3+ \big(p_{\epsilon^2/2}*\eta_t(y_2)\big)^3+
+\big(p_{\epsilon^2/4}*\eta_t\big(\frac{y_1+y_2}{2}\big)\big)^3
+\Big\}p_{\epsilon^2}(y_1,y_2)dy_1dy_2\Big],
+\end{align*}
+where we have used that for any non-negative real numbers
+$\beta_1$, $\beta_2$, $\beta_3$, 
+$\beta_1\beta_2\beta_3\leq \beta_1^3+\beta_2^3+\beta_3^3$.
+For the first two terms in the sum we integrate with respect to $y_2$ and $y_1$
+respectively to reduce to an expression of the form considered in 
+Lemma~\ref{bounds on moments}. For the final term, the change of variables
+$z_1=y_1+y_2$, $z_2=y_1-y_2$ in the integral similarly 
+allows us to integrate out the heat kernel, and we conclude that the result
+holds for $k=2$.
+
+We can proceed in the same way for larger values of $k$, using repeatedly that
+\[
+p_{t_1}(x,y_1)p_{t_2}(x,y_2)=p_{\frac{t_1t_2}{t_1+t_2}}
+\Big(x,\frac{t_2y_1+t_1y_2}{t_1+t_2}\Big)p_{t_1+t_2}(y_1,y_2)
+\]
+to write 
+\[
+\prod_{j=1}^k p_{\tau}(x,x_j)
+=\prod_{j=2}^{k}p_{\frac{j\tau}{j-1}}\big(x_j,X_{j-1}\big)
+p_{\frac{\tau}{k}}(x, X_k)
+\]
+where
+\[
+X_1=x_1, \qquad X_j=\frac{j-1}{j}x_j+\frac{1}{j}X_{j-1}, \mbox{for }j\geq 2.
+\]
+This yields
+\begin{multline*}
+\big\langle\big(\rho_\epsilon*\eta_t(x)\big)^k,\eta_t(dx)\big\rangle
+=\int\cdots\int\prod_{i=2}^kp_{\epsilon^2 i/(i-1)}(y_,X_i)
+\prod_{i=1}^kp_{\epsilon^2/2}*\eta_t(y_i)p_{\epsilon^2/k}*\eta_t(X_k)
+dy_1\ldots dy_k
+\\
 \leq
-        C
-        +
-        C \int_0^t \Vert \psi_{t-s}^{\epsilon,0} \Vert_\infty
-        \IE\left[\sup_{0 \leq s \leq t} \langle 1, \eta_s(dy) \rangle\right] ds
-        \\ &
-        \leq \label{BoundForMollifier}
-        C + C \int_0^t \Vert \psi_{t-s}^{\epsilon,0} \Vert_\infty ds
-    \end{align}
-    Now, using Lemma~\ref{PsiBoundHS}, % since $\epsilon^2 \theta \to \infty$,
-    we can bound $\| \psi_{t-s}^{\epsilon,0} \|_\infty$
-    by $C (t-s+\epsilon^2)^{-d/2}$.
-    In dimension one the right hand side of \eqref{BoundForMollifier} is immediately uniformly bounded.
-    For $d=2$ we can iterate.
-    By using again the martingale problem and the same arguments
-    we used to get \eqref{BoundForMollifier} we get,
-    % \comment{Alison suggests that writing the term on the right instead as
-    %     $C \IE[\int_0^t \langle \psi_{t-u}^{\epsilon,x}(y), \eta_u(dy) \rangle du ]$
-    %     would look more natural?}
-    \begin{equation} \label{IterationBoundPsi}
-        \IE[\langle \psi_{t-s}^{\epsilon,x}, \eta_s(dy)\rangle]
-        \leq
-        \IE[\langle \psi_{t}^{\epsilon,x}(y), \eta_0(dy) \rangle]
-        +
-        C \int_0^s \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du
-    \end{equation}
-    Hence, using \eqref{IterationBoundPsi} in \eqref{BoundForMollifierStart} gives
-    \begin{align*}
-        \IE[ \rho_\epsilon * \eta_t(x) ]
-        &\leq
-        \IE[ \langle \psi_t^{\epsilon,x}(y), \eta_0(dy) \rangle]
-        +
-        \int_0^t C\langle \psi_{t}^{\epsilon,x}, \eta_0(dy)\rangle ds
-        +
-        C^2 \int_0^t \int_0^s  \| \psi_{t-u}^{\epsilon,0} \|_\infty du ds
-        \\ &=
-        (1+Ct) \IE[ \langle \psi_t^{\epsilon,x}, \eta_0(dy) \rangle]
-        +
-        C^2 \int_0^t (t-u) \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du
-        \\ &\leq
-        C(1+t) + C^2 \int_0^t (t-u) \| \psi_{t-u}^{\epsilon,0} \|_\infty du ,
-    \end{align*}
-    which again is uniformly bounded using Lemma \ref{PsiBoundHS}.
-    It is easy to see that, iterating, we can prove a uniform bound in any dimension. 
+\int\cdots\int 
+\prod_{i=2}^kp_{\epsilon^2 i/(i-1)}(y_i,X_i)
+\Big\{\sum_{i=1}^k\big(p_{\epsilon^2/2}*\eta_t(y_i)\big)^{k+1}
++\big(p_{\epsilon^2/k}*\eta_t(X_k)\big)^{k+1}\Big\}dy_1\ldots dy_k,
+\end{multline*}
+and once again we can change variables in the integrals and 
+use~(\ref{heat equation at smaller time}) to bound this by a constant 
+multiple of $\int\IE\big[\big(\rho_\epsilon*\eta_t(x)\big)^{k+1}\big]dx$, and
+the inductive step is complete.
 \end{proof}
 
-\begin{corollary} \label{cor:BoundLocalDensity}
-    Under the conditions of Theorem~\ref{TeoremOneStepConvergence}
-    there is a constant $C > 0$,
-    independent of $\epsilon$, $N$, $\theta$, and $x$,
-    such that
-    \[
-        \IE[ \langle \psi^{\epsilon,x}_s(y), \eta_t(dy) \rangle ]
-        \le C
-    \]
-    for all $s \ge 0$, $t \in [0, T]$ and $x \in \IR^d$.
-\end{corollary}
-
-\comment{This was previously just a Remark, but I wanted to use it below
-    in a place where we have to be careful of exactly what it's uniform over,
-    so I wrote out a proof.}
-
-\begin{proof}[of Corollary~\ref{cor:BoundLocalDensity}]
-    For any random variable $X$ independent of $\eta$,
-    Lemma~\ref{FirstBoundLocalDensity} implies that
-    $\IE[\rho_\epsilon * \eta_t(X)] = \IE[\langle p_{\epsilon^2}(X, y), \eta_t(dy)] \le C$.
-    The Corollary follows immediately 
-    by taking $X$ to have density $p_{T(s)}(x, \cdot)$, since
-    \begin{align*}
-        \IE[ \langle \psi^{\epsilon,x}_s(y), \eta_t(dy)\rangle ]
-        =
-        \IE[ \langle p_{T(s)+\epsilon^2}(x,y), \eta_t(dy) \rangle ]
-        =
-        \IE\left[ \int_{\IR^d} 
-            p_{T(s)}(x, z)
-            \langle p_{\epsilon^2}(z, y), \eta_t(dy) \rangle
-        dz \right] ,
-    \end{align*}
-    with $T(s)$ independent of $\eta$.
-\end{proof}
-
-\begin{corollary}
-    Let $(M_t^x)_{t \geq 0}$ be the martingale in (\ref{MartingaleProblemMolifier}).
-    Then
-    \[
-        \IE\left[ [M^x]_t \right] \leq \frac{C \theta}{ N \epsilon^{d}} ,
-    \]
-    where $C$ is independent of $\epsilon,\theta,N$. \label{Cor:ControlQVMQ}
-\end{corollary}
-
-\begin{proof}
-    We can explicitly write the quadratic variation of $M^x_t$ as
-    \[
-        [M^x]_t
-        =
-        \frac{\theta}{N} \int_0^t \langle
-            \int_{\IR^d} \psi_{t-s}^{\epsilon,x}(z)^2 q_\theta(y,dz)
-            +
-            \left(1 + \frac{F(y, \eta_s)}{\theta}\right) \psi_{t-s}^{\epsilon,x}(y)^2,
-        \eta_s(dy) \rangle  ds .
-    \]
-    Lemma~\ref{PsiBoundHS} implies that $\psi_{t-s}^{\epsilon,x}(y) \le C \epsilon^{-d}$.
-    Using this and the fact that $F(x)$ is bounded above,
-    \begin{align} \label{QuadVarBound}
-    [M^x]_t
-        &\leq
-        \frac{C \theta}{N \epsilon^d} \int_0^t \left\{
-            \langle \int \psi_{t-s}^{\epsilon,x}(z) q_\theta(y,dz)
-            +
-            \psi_{t-s}^{\epsilon,x}(y)
-            , \eta_s(dy)\rangle
-        \right\} ds 
-    \end{align}
-    We can now take expectations and use Corollary~\ref{cor:BoundLocalDensity} to prove the result.
-\end{proof}
-
-By re-using the computations in the last Corollary we can prove a certain integrability of $M_t^x$.
-
-\begin{proposition}  \label{IntegrabilityOfM}
-    Let $(M_t^x)_{t \geq 0}$ be the martingale in (\ref{MartingaleProblemMolifier}).
-    Then
-    \[
-        \int_{\IR^d} \IE\left[ (M_t^x)^2 \right] dx \leq \frac{C \theta}{ N \epsilon^{d}} ,
-    \]
-    where $C$ is independent of $\epsilon$, $\theta$, and $N$.
-\end{proposition}
-
-\begin{proof}[of Proposition \ref{IntegrabilityOfM}]
-    Recall that since $M^x_t$ is a martingale, then,
-    \[
-        \IE\left[ (M_t^x)^2 \right] = \IE\left[ [M^x]_t \right].
-    \]
-    Hence, using (\ref{QuadVarBound}),
-    \begin{align*}
-        \int_{\IR^d} &\IE\left[ M_t(x)^2 \right] dx
-        \\ & \leq
-        \frac{C \theta}{\varepsilon^d N} \int \int_0^t
-            \IE\left[ \langle \int \psi_{t-s}^{\epsilon,x}(z) q_\theta(y,dz), \eta_s(dy) \rangle
-                + \langle \psi_{t-s}^{\epsilon,x}(y),
-            \eta_s(dy)\rangle \right]
-        ds dx
-        \\ &= 
-        \frac{C \theta}{\varepsilon^d N} \int_0^t \IE \left[
-            \langle \int \left( \int \psi_{t-s}^{\epsilon,x}(z) dx \right) q_\theta(y,dz),
-            \eta_s(dy) \rangle
-            +
-            \langle \left( \int \psi_{t-s}^{\epsilon,x}(y) dx \right), \eta_s(dy)\rangle
-        \right] ds.
-    \end{align*}
-    Now, since (by Lemma~\ref{PsiBoundHS}) $\psi_t^{\epsilon, x}(y) = \IE[p_{\epsilon^2+T(t)}(x,y)]$,
-    note that
-    \begin{align*}
-        \int
-            \psi_t^{\epsilon, x}(y) dx
-            & =
-            % \int \IE[p_{\epsilon^2+T(t)}(x,y)] dx
-            % \\ &=
-            \IE\left[ \int p_{\epsilon^2+T(t)}(y,x) dx \right]
-            = 1.
-    \end{align*}
-    Thus,
-    \begin{align*}
-    \int \IE\left[ M_t(x)^2 \right] dx
-        & \leq 
-        \frac{C \theta}{\varepsilon^d N} 
-        \int_0^t \IE \left[ 
-            \langle \int  q_\theta(y,dz), \eta_s(dy) \rangle
-            +
-            \langle 1, \eta_s(dy)\rangle
-        \right] ds
-        \\ & =
-        2 \frac{C \theta}{\varepsilon^d N}
-        \int_0^t \IE[ \langle 1, \eta_s(dy) \rangle ] ds
-        \\ & \leq
-        t \frac{2 C \theta}{ \varepsilon^d N} ,
-    \end{align*}
-    proving the result.
-\end{proof}
-
-% By doing the same pattern used to prove Lemma~\ref{lem:SecondMomentMass} (replacing the use of equation (\ref{eq:MPTotalMass}) by equation (\ref{MartingaleProblemMolifier}) and the used of equation \ref{eq:quadvarMass} by Corollary~\ref{Cor:ControlQVMQ}) we can get the following result.
-
-\comment{Alison writes: previously we just referred to the proof of Lemma~\ref{lem:SecondMomentMass},
-but that was wrong.
-I think using $\theta/(N \varepsilon^d) \to 0$ this is easy, but should maybe write it out.}
-
-\comment{Peter writes: here is a proof! Maybe it's right?
-It's straightforward given everything else we do,
-but the expressions are a bit lengthy thanks to the need to have $x_1 \neq x_2$ below.
-We could replace the proof with another short description?}
-
-\begin{proposition}
-        \label{Prop:SecondMomentDensity}
-    Under the assumptions of Theorem~\ref{TeoremOneStepConvergence}
-    there is a finite constant $C$ (independent of $\epsilon, N, \theta$) such that,
-    for all $t \in [0,T]$, $x \in \IR^d$ and for big enough $N$ and $\theta$,
-    $\IE[ (\rho_\epsilon*\eta_t(x))^2] \leq C$.
-\end{proposition}
-
-\begin{proof}[of Proposition~\ref{Prop:SecondMomentDensity}]
-    In fact, we will prove that
-    \begin{align*}
-        \sup_{x_1, x_2} \IE\left[
-            \langle \psi^{\epsilon,x_1}_0(y), \eta_t(dy) \rangle
-            \langle \psi^{\epsilon,x_2}_0(y), \eta_t(dy) \rangle
-        \right]
-        \le C .
-    \end{align*}
-    The martingale properties~\eqref{timeMGP} and~\eqref{timeMGP2} imply that
-    \begin{align*}
-        &
-        \IE\left[
-            \langle \psi^{\epsilon,x_1}_0(y), \eta_t(dy) \rangle
-            \langle \psi^{\epsilon,x_2}_0(y), \eta_t(dy) \rangle
-        \right]
-        =
-        \IE\left[
-            \langle \psi^{\epsilon,x_1}_t(y), \eta_0(dy) \rangle
-            \langle \psi^{\epsilon,x_2}_t(y), \eta_0(dy) \rangle
-        \right]
-        \\ & \qquad {}
-        +
-        \int_0^t 2 \IE\left[
-            \langle \psi^{\epsilon,x_1}_{t-s}(y), \eta_s(dy) \rangle
-            \langle \psi^{\epsilon,x_2}_{t-s}(y) F(y, \eta_s), \eta_s(dy) \rangle
-        \right. \\ & \qquad \qquad \qquad \left. {} 
-            +
-            \langle \psi^{\epsilon,x_2}_{t-s}(y), \eta_s(dy) \rangle
-            \langle \psi^{\epsilon,x_1}_{t-s}(y) F(y, \eta_s), \eta_s(dy) \rangle
-            ,
-            \eta_s(dy) \rangle
-        \right] ds
-        \\ & \qquad {}
-        +
-        \int_0^t \frac{\theta}{N} \IE\left[
-            \left\langle 
-                \int_{\IR^d}
-                    \psi^{\epsilon,x_1}_{t-s}(z)
-                    \psi^{\epsilon,x_2}_{t-s}(z)
-                    q_\theta(y, dz)
-                +
-                \left(1 + F(y, \eta_s)/\theta \right)
-                    \psi^{\epsilon,x_1}_{t-s}(y)
-                    \psi^{\epsilon,x_2}_{t-s}(y)
-                ,
-                \eta_s(dy)
-            \right\rangle
-        \right] ds .
-    \end{align*}
-    The first term is bounded by our assumptions on $\eta_0$.
-    Since $F$ is bounded above, the second term is bounded by
-    \begin{align*}
-        &C \int_0^t \IE\left[
-            \langle \psi^{\epsilon,x_1}_{t-s}(y), \eta_s(dy) \rangle
-            \langle \psi^{\epsilon,x_2}_{t-s}(y), \eta_s(dy) \rangle
-        \right] ds
-        \\
-        &\qquad =
-        C \int_0^t
-        \int_{\IR^d} \int_{\IR^d}
-            \IE\left[
-                p_{T(t-s)}(x_1, z_1) p_{T(t-s)}(x_2, z_2)
-                (\rho_\epsilon * \eta_s(z_1))
-                (\rho_\epsilon * \eta_s(z_2))
-            \right] ds
-        dz_1 dz_2
-        \\
-        &\qquad \le
-        C \int_0^t
-        \sup_{z_1, z_2}
-            \IE\left[
-                (\rho_\epsilon * \eta_s(z_1))
-                (\rho_\epsilon * \eta_s(z_2))
-            \right] ds
-    \end{align*}
-
-    Using Corollary~\ref{cor:BoundLocalDensity},
-    the third term is bounded by a constant times
-    \begin{align*}
-        \int_0^t
-            \|\psi^{\epsilon,x}_{t-s}\|_\infty
-            \IE[ \langle \psi^{\epsilon,x}_{t-s}(y), \eta_s(dy) ]
-        ds 
-        \le
-        C \int_0^t \|\psi^{\epsilon,x}_{t-s}\|_\infty ds ,
-    \end{align*}
-    which can be bounded following the same iterative argument
-    as we used for equation~\ref{BoundForMollifierStart}.
-
-    This leaves us with
-    \begin{align*}
-        \sup_{x_1, x_2} \IE\left[
-            \langle \psi^{\epsilon,x_1}_0(y), \eta_t(dy) \rangle
-            \langle \psi^{\epsilon,x_2}_0(y), \eta_t(dy) \rangle
-        \right]
-        \le C  + C \int_0^t
-            \sup_{x_1, x_2} \IE\left[
-                \langle \psi^{\epsilon,x_1}_0(y), \eta_t(dy) \rangle
-                \langle \psi^{\epsilon,x_2}_0(y), \eta_t(dy) \rangle
-            \right]
-            ds,
-    \end{align*}
-    and so we can apply Gronwall's inequality.
-\end{proof}
-
-\paragraph{$C$-tightness of $\rho_\epsilon * \eta_t(x) dx$ }
-
-\begin{lemma}
+\begin{corollary}[$C$-tightness of $\{(\rho_\epsilon*\eta_t(x) dx)_{t\geq 0}\}$]
         \label{lem:density_tightness}
@@
     (taking values in $D([0,T], \measures)$ is $C$-tight.
-\end{lemma}
-
-\comment{Peter: what's $C$-tightness?}
-
-\begin{proof}[of Lemma~\ref{lem:density_tightness}]
-
-    Let $f \in C_c^2$ (that is, compactly supported and with smooth second derivative).
-    We will show convergence of $\int f(x) \rho_\epsilon * \eta_t(x) dx$ (which is enough to establish weak convergence of the measures $\rho_\epsilon * \eta_t(x) dx$).
-    \comment{Alison writes: no it's not weak - this would be vague convergence. Take $f \in C^2$ to mean bounded first and second derivatives, which is weak convergence.}
-    For this note that
-    \begin{align*}
-        \int f(x) \rho_\epsilon * \eta_t(x) dx
-        &=
-        % \int \int f(x) \rho_\epsilon (x-y) \eta(dy) dx
-        % \\ & =
-        % \langle \int f(x) \rho_\epsilon(x-y) dx, \eta(dy) \rangle
-        % \\ &=
-        \langle \rho_\epsilon * f(y), \eta_t(dy) \rangle .
-    \end{align*}
-    Substituting this into the martingale problem for $\eta_t$, \eqref{mgp1},
-    we get
+\end{corollary}
+\begin{proof}
+Since the quadratic variation of the martingale $M_t(x)$ of 
+equation~(\ref{expn rhoepsilon}) is
+\begin{equation*}
+%\label{qv M(x)}
+[M(x)]_t=\frac{\theta}{N}\int_0^t\Big\langle\int\psi^{\epsilon,x}_{t-s}(z)^2q_\theta(y,dz)
++\Big(1-\frac{F(\rho_\epsilon*\eta(y)}{\theta}\Big)\psi^{\epsilon,x}_{t-s}(y)^2,\eta_s(dy)
+\Big\rangle ds,
+\end{equation*}
+in exactly the same way as we proved that $\IE[\sup_{0\leq t\leq T} \langle 1,\eta_t\rangle]$ is 
+bounded in Lemma~\ref{lem:eta_compact_containment}, 
+using~(\ref{moment bound rhoepsilon}) 
+and~(\ref{flandoli trick for rhoepsilon}) with $k=1$, 
+we can deduce that $\IE[\sup_{0\leq t\leq T}M_t(x)]$ is bounded independently of
+$N$, $\theta$ and $\epsilon$ (in fact that it tends to zero) and
+by an application of Gronwall's inequality we deduce 
+that $\IE[\sup_{0\leq t\leq T} \rho_\epsilon*\eta_t(x)]$ is
+bounded. This proves compact containment.
+
+    To conclude $C$-tightness we show that, for $T>0$, and any
+$f\in C_b^\infty (\IR^d)$ with bounded second derivatives, given $\nu>0$,
+    there exists $\delta=\delta(f,T,\nu) >0$ so that for $\theta$ and $N$ large enough,
     \begin{align}
-         \label{MGPT_epsilon}
-    \langle \rho_{\epsilon} * f, \eta_t \rangle
-        & = \nonumber 
-        \langle \rho_{\epsilon} * f, \eta_0 \rangle
-        +
-        \theta \int_0^t
-            \langle
-                \int (\rho_{\epsilon} * f(z) - \rho_{\epsilon} * f(y)) q_\theta(y, dz) ,
-                \eta_s(dy)
-            \rangle
-        ds
-        \\ & {}
-        +
-        \int_0^t \langle \rho_\epsilon * f(y) F(y, \eta_s), \eta_s(dy) \rangle ds
-        + \widehat{M}_t,
-    \end{align}
-    with $\widehat{M}_t$ a martingale. Now note that
-    by the Intermediate Value Theorem,
-    \begin{align}
-        \label{ShortBoundLaplacianHS}
-        \left| \theta \int (\rho_{\epsilon} * f(z) - \rho_{\epsilon} * f(y)) q_\theta(y,z) dz \right|
-        &=
-        \left| \theta( p_{\epsilon^2 + 1/\theta} * f(y) - p_{\epsilon^2} * f(y) ) \right| \nonumber
-        \\ &=
-        \left| \Delta p_{\epsilon+1/\tilde{\theta}} * f(y) \right| \nonumber
-        \\ &=
-        \left| p_{\epsilon^2 + 1/\tilde{\theta}} * \Delta f(y) \right|
-        \leq
-        \| \Delta f \|_{\infty}
-    \end{align}
-    for some $\tilde{\theta} \in [0,1/\theta]$.
-    Proceeding as in the proof of Lemma~\ref{lem:eta_f_bound},
-    we can take expectations of equation~\eqref{MGPT_epsilon},
-    use \eqref{ShortBoundLaplacianHS} and the fact that $F(x)$ is bounded above,
-    and then Gronwall's inequality to conclude that
-    \[
-        \IE\left[\langle \rho_{\epsilon} * f(y), \eta_t(dy) \rangle \right]
-        \text{ is uniformly bounded for } t \in [0,T].
-    \]
-
-    The quadratic variation of $\widehat{M}_t$ is
-    \[
-        [ \widehat{M} ]_t
-        =
-        \frac{\theta}{N} \int_0^t \langle
-            p_{1/\theta}*(p_{\epsilon^2} * f(\cdot)^2)(y)
-            +
-            \left( 1 + \frac{F(\rho_\epsilon*\eta_s(y))}{\theta} \right)
-            p_{\epsilon^2} * f(y)^2
-            ,
-            \eta_s(dy)
-        \rangle ds ,
-    \]
-    so using boundedness of $f$ and $F$,
-    \begin{align*}
-        \IE\left[ [\widehat{M}]_t \right]
-        \leq
-        \frac{\theta}{N} \| f \|_\infty (1 + C_F/\theta)
-        \int_0^t \mathbb{E}\left[ \langle 1, \eta_s(dy) \right] ds
-        <
-        C \frac{\theta}{N} t ,
-    \end{align*}
-    where in the last inequality we have used Lemma~\ref{Lemma:UniformlyBoundedMass}.
-    Hence, using the Burkholder-Davis-Gundy inequality and then Jensen's inequality we can conclude that
-    \[
-        \IE[\sup_{0 \leq t \leq T} |\widehat{M}_t| ]
-        \le
-        C
-        \IE\left[ [\widehat{M}]_T \right]^{1/2}
-        \le
-        \sqrt{ C \frac{\theta}{N} T } .
-    \]
-    Therefore, by taking supremum and expectation and in \eqref{MGPT_epsilon}
-    we conclude that
-    \begin{equation}
-        \label{eq:boundedIntegralAgainstf}
-        \IE[ \sup_{0 \leq t \leq T} \langle p_{\epsilon^2} * f, \eta_t \rangle ]
-        \text{ is uniformly bounded (for fixed } f \text{)} .
-    \end{equation}
-    To conclude $C$-tightness we show that, for $T>0$, and $\alpha > 0$
-    there is some $\delta >0$ so that for $\theta$ and $N$ large enough,
-    \begin{align}
-        % &
-        % \IP\left[
-        %     \sup_{s,t \in [0,T], |s-t| < \delta}
-        %     \left|
-        %         \int f(x) \rho_\epsilon*\eta_s(x) dx
-        %         -
-        %         \int f(x) \rho_\epsilon*\eta_t(x) dx
-        %     \right|
-        %     >
-        %     \alpha
-        % \right]
-        % \\ &=
-        \IP\left[
+        \IP\Big[
             \sup_{s,t \in [0,T], |s-t| < \delta}
@@
             >
-            \alpha
-        \right]
+            \nu
+        \Big]
         <
-        \alpha \label{conditionCtightness}
+        \nu \label{conditionCtightness}
     \end{align}
+
+First, observe that
+\begin{multline}
+\label{C-tightness estimate}
+\left|
+\langle \rho_{\epsilon} * f, \eta_t \rangle 
+- \langle \rho_{\epsilon} * f, \eta_s \rangle            
+\right|
+\leq
+\left|
+\int_s^t\Big\langle\theta\int\big(\rho_\epsilon*f(y)-\rho_\epsilon*f(x)\big)
+q_{\theta}(x,dy),\eta_u(dx)\Big\rangle du
+\right|
+\\
++\int_s^t\Big\langle |F\big(\rho_\epsilon*\eta_u(x)\big)|\rho_\epsilon*f(x), 
+\eta_u(dx)\Big\rangle du +2\sup_{0\leq u\leq T}|\widehat{M}^N(f)_u|,
+\end{multline}
+where $\widehat{M}(f)$ is the martingale of~(\ref{eqn:eta_martingale})
+with the test function $f$ replaced by $\rho_\epsilon*f$. In particular, 
+just as for $M_t(x)$ above, we can deduce that its supremum tends to zero under
+our scaling.
+
+Again using the approach of Lemma~\ref{lem:eta_compact_containment}, we have that 
+$\IE[\sup_{0\leq t\leq T} \langle 1,\eta_t\rangle]$ is bounded,
+% and using that
+%$|F|\leq K-F$ and rearranging the equation for $\langle 1,\eta_t\rangle>$ in the usual
+%way to find an expression for 
+%$-\int_s^t\langle F\big(\rho_\epsilon*\eta_u(x)\big), \eta_u(dx)\rangle du$, we can bound
+and so combining with the corresponding estimate for $\rho_\epsilon*\eta_u$, 
+by Markov's inequality, we can choose $m_\nu$, $\widetilde{m}_\nu$, so that 
+$$\IP[\sup_{0\leq u\leq T}\langle<1,\eta> >\tilde{m}_\nu]<\nu/2$$
+$$\IP[\sup_{0\leq u\leq T}\langle<1,\eta> >\tilde{m}_\nu]<\nu/2$$
+UP TO HERE
+
+By the Intermediate Value Theorem, using $T_t$ to denote the heat semigroup,
+there exists $s\in (0,1/\theta)$ such that
+\begin{multline*}
+\left|
+\theta\int\big(\rho_\epsilon*f(y)-\rho_\epsilon*f(x)\big)
+q_{\theta}(x,dy) \right|
+=
+\left|\theta\Big(T_{\epsilon^2+1/\theta}f(x)-T_{\epsilon^2}f(x)\Big)\right|
+\\
+=
+\left|\partial_sT_{\epsilon^2+s}f(x)\right|=\left|T_{\epsilon^2+s}\Delta f(x)\right|
+\leq\|\Delta f\|_\infty.
+\end{multline*}
+
     Now, we can use \eqref{MGPT_epsilon} to write this difference
@@
     and therefore uniformly bounded (because we may take $u_1 \le N$).
+
+\end{proof}
+
+% % % % % % % % % % % % %
+\subsubsection{New stuff}
+
+\comment{TODO: reference this elsewhere, if we keep it?}
+We record for future reference
+the Aldous-Rebolledo criteria for tightness of a sequence real-valued processes:
+
+\begin{theorem}[\citet{rebolledo:1980}]
+    \label{thm:aldous_rebolledo}
+    Let $\{Y^(n)\}_{n \ge 1}$ be a sequence of real-valued processes
+    with c\`adl\`ag paths.
+    Suppose that the following conditions are satisfied.
+    \begin{enumerate}
+        \item For each fixed $t$, $\{Y_t^(n)\}_{n \ge 1}$  is tight.
+        \item Given a sequence of stopping times $\tau_n$, bounded by $T$,
+            for each $\epsilon > 0$ there exists $\delta > 0$ and $n_0$ such that
+            \begin{align*}
+                \sup_{n \ge n_0}
+                \sup_{\theta \in [0, \delta]}
+                \IP\left\{ \left|
+                    Y^{(n)}_{\tau_n + \theta} - Y^{(n)}_{\tau_n}
+                \right| > \epsilon
+                \right\}
+                \le \epsilon .
+            \end{align*}
+    \end{enumerate}
+    Then the sequence $\{Y^(n)\}_{n \ge 1}$ is tight.
+\end{theorem}
+
+\begin{lemma}
+    \label{lem:test_fn_tightness}
+    Let $f$ be a bounded, continuous real-valued function on $\IR^d \times [0, \infty)$
+    with uniformly bounded first and second derivatives
+    for which there exists a $u_0$ such that if $u > u_0$ then $f(x, u) = 0$.
+    Then, the sequence of real-valued processes $(\langle f, \xi_t^N \rangle)_{t \ge 0}$
+    are tight in the space of c\`adl\`ag processes.
+\end{lemma}
+
+\begin{proof}[of Lemma \ref{lem:test_fn_tightness}]
+    First, a reminder of the description of the process
+    \comment{(TODO: figure out if the notation here for $a$ and $b$ should be used above;
+        if so, move it up; if not, replace it here.)}
+    Recall when the state of the process is $\eta$,
+    the level of a line of descent at spatial location $x$ and level $u$
+    changes following
+    $$
+        \dot u = a^N(x, \eta) u^2 - b^N(x, \eta) u,
+    $$
+    where
+    $$
+        a^N(x, \eta)
+        =
+        \frac{\theta}{N} \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q(x, dy) ,
+    $$
+    and
+    $$
+        b^N(x, \eta)
+        =
+        \theta \gamma(x, \eta) \int_{\IR^d} (r(y, \eta) - r(x, \eta)) q(x, dy) + F(x, \eta) .
+    $$
+    Furthermore, the line of descent
+    gives birth to lines at higher levels at rate $2 (N - u) a^N(x, \eta)$,
+    that each such new line chooses a level uniformly from $[u, N]$,
+    a spatial location $y$ from the kernel
+    $$
+        q^m(x, dy, \eta)
+        =
+        r(y, \eta) q(x, dy) / \int_{\IR^d} r(y, \eta) q(x, dy),
+    $$
+    and the two lines swap spatial locations with probability 1/2.
+
+    It is evident from the description of the process
+    (or, by differentiating in Definition~\ref{defn:lookdown_mgale})
+    that
+    \begin{align*}
+    \begin{split}
+    M^f_s
+        &=
+        \langle f, \xi_t^N \rangle
+        -
+        \langle f, \xi_0^N \rangle
+    \\ & \qquad \qquad {}
+        -
+        \int_0^t
+        \big\langle
+            a^N(x, \eta^N_t)
+            \int_u^N \int_{\IR^d}
+            \left(
+                f(y, u_1) + f(x, u_1) + f(y, u) - f(x, u)
+            \right)
+            du_1 q^m(x, dy, \eta^N_s)
+    \\ & \qquad \qquad \qquad \qquad {}
+            +
+            \left(
+                a^N(x, \eta^N_s) u^2
+                - b^N(x, \eta^N_s) u
+            \right)
+            \frac{d}{du} f(x, u)
+        ,
+        \xi_s^N(dx, du) \big \rangle
+        ds
+    \end{split}
+    \end{align*}
+    is a martingale.
+    Now we would like to bound the terms in the integral,
+    to arrive at a bound using Gronwall's inequality, as before.
+
+    First, note that there exists a constant $C_a$
+    such that $a^N(x, \eta) \le C_a$
+    (since $\gamma$ and $r$ are bounded above, and $\theta/N \to \alpha \ge 0$),
+    and for any $\epsilon > 0$ and $T$ there is a $C_b$ such that for all $N$,
+    $$
+        \IP\left\{
+            \sup_{0 \le s \le T} \sup_x |b^N(x, \eta_s^N)| > C_b
+        \right\}
+        < \epsilon 
+    $$
+    \comment{reference where we show this above}.
+    Now, since $f$ vanishes for $u \ge u_0$,
+    on the event that $\sup_x |b^N(x, \eta_s^N)| \le C_b$ then
+    if $N \ge u_0$,
+    \begin{align*}
+    &
+        \int_{\IR^d} \int_0^N
+            \left(
+                a^N(x, \eta^N_s) u^2
+                - b^N(x, \eta^N_s) u
+            \right)
+            \frac{d}{du} f(x, u)
+        \xi_s^N(dx, du)
+    \\  & \qquad
+    \le
+        \int_{\IR^d} \int_0^{u_0}
+            \left(
+                C_a u_0^2
+                + C_b u_0
+            \right)
+            \left\| \frac{d}{du} f \right\|_\infty
+        \xi_s^N(dx, du) .
+    \\  & \qquad
+    \le
+        C_0 \xi_s^N(\IR^d \times [0, u_0]) .
+    \end{align*}
+
+    Next, observe that for any $\eta$,
+    $$
+    \int_{\IR^d} \int_u^N (f(y, u_1) + f(x, u_1)) du_1 q^m(x, dy, \eta)
+    \le 2 u_0 \|f\|_\infty .
+    $$
+    Furthermore,
+    recall that we have assumed \comment{(check where we do this)}
+    that $q^m$ is uniformly elliptic,
+    and so since $f$ has bounded first and second derivatives,
+    there is a $C_1$ depending on $f$ such that for all $\eta$,
+    $\theta \int_{\IR^d} (f(y, u) - f(x, u)) q^m(x, dy, \eta) \le C_1$.
+    Therefore, using boundedness of $\theta/N$,
+    \begin{align*}
+        &
+        \int_{\IR^d} \int_u^N (f(y, u) - f(x, u)) du_1 q^m(x, dy, \eta^N_s)
+        \\ &\qquad
+        = (N - u) \int_{\IR^d} (f(y, u) - f(x, u)) q^m(x, dy, \eta^N_s)
+        \\ &\qquad
+        = \frac{N}{\theta} \left(1 - \frac{u}{N}\right) \theta \int_{\IR^d}
+            (f(y, u) - f(x, u)) q^m(x, dy, \eta^N_s)
+        \\ &\qquad
+        \le C_1 \frac{N}{\theta} \ind_{u \le u_0} .
+    \end{align*}
+
+    Putting this together,
+    \begin{align*}
+        \IE\left[
+            \langle f, \xi_t^N \rangle
+        \right]
+        \le
+    \end{align*}
 

### 2023-01-29 forwards-and-backwards.tex
compact containment

@@
 \newcommand{\measures}{\mathcal{M}_F(\IR^d)} % finite measures on Rd
-\newcommand{\cmeasures}{\mathcal{M}_F(\overline{\IR}^d)} % finite measures on compactified Rd
+\newcommand{\cmeasures}{\mathcal{M}_F(\overline{\IR^d})} % finite measures on compactified Rd
 \newcommand{\lpmeasures}{\mathcal{M}(\overline{\IR^d} \times [0,\infty))} % locally finite measures on space x level
@@
 
-Now we prove the main theorem on convergence of the lookdown process, 
-Theorem~\ref{thm:lookdown_convergence}.
-This follows a similar pattern as the the proofs of convergence for the population process
-in Section~\ref{sec:population_density_proof},
-although we will need additional estimates to ensure that
-trajectories of individual lines of descent converge,
-not just the population process.
-
-\begin{proof}[Proof of Theorem~\ref{thm:lookdown_convergence}]
-    As in Section~\ref{sec:population_density_proof},
-    the theorem will follow from tightness,
-    ensuring convergence along subsequences,
-    and characterization of the limit.
-    This time, the processes $\lp^N$ take values in $\lpmeasures$,
-    the space of locally finite measures on space $\times$ levels.
-    (They will in fact be point measures, including the limit,
-    but that is a consequence of this theorem.)
-    Again, tightness will follow from a compact containment condition,
-    tightness of one-dimensional distributions,
-    and an application of \citet{EK} Theorem~3.9.1.
-    We show that the martingale properties are preserved in the limit
-    in Section~\ref{sec:lookdown_generator_proofs}.
-    \comment{TODO: write and refer to lemma?}
-
-    Lines of descent can escape to infinite level in finite time,
-    and so we endow $\lpmeasures$ with the vague topology ``in the level coordinate'',
-    i.e., the topology induced by test functions on $\overline{\IR^d} \times [0,\infty)$
-    of the form $f(x) g(u)$, where $f \in C_b(\overline{\IR^d})$ is bounded and continuous
-    and $g \in C_c([0,\infty))$ is continuous with compact support.
-    In this topology, compact containment follows from
-    tightness of the spatial and level motions of a single line of descent
-    (Lemmas~\ref{lem: tightness of individual spatial trajectory}
-    and~\ref{lem:tightness of levels}, respectively),
-    and
-    tightness of $\lp^N(\IR^d \times [0, u_0])$ for each $u_0$
-    (i.e., the number of individuals with level below $u_0$).
-
-    Finally, we must show that the limiting lookdown process $\lp$
-    projects to the limiting process $\eta$, i.e., a solution of the martingale
-    problem in Theorem~\ref{thm:nonlocal_convergence}.
-    Let $N_k \to \infty$ be a sequence along which $\lp^{N_k}$ converges.
-    However, by Theorem~\ref{thm:nonlocal_convergence},
-    there is a subsequence $N_{k(j)}$ along which the projected population processes
-    $\eta^{N_{k(j)}}$ converge, and the limit solves the martingale problem.
-    This implies that any limit of $\lp^N$ projects to a population process $\eta$
-    solving the martingale problem of Theorem~\ref{thm:nonlocal_convergence}.
-
-\comment{MAKE THIS BELOW A LEMMA?}
-
-% BEGIN OLD STUFF
-To prove that the lookdown representation is tight, we generalise the vague
-    topology to the setting of measure-valued processes. For a detailed
-    description of the vague topology, refer to Appendix \ref{sec: Empirical
-    Measure Topology}.
-
-We will lay out the steps we follow to prove tightness. First of all, we will
-    show that compact containment condition is satisfied if we can control the
-    total mass of particles in our system living in a finite region in space
-    with a level lower than some $u_{*}$. Since a control on total mass has
-    already been shown in Lemma \ref{lem:eta_compact_containment}, we have
-    immediately established compact containment condition for our lookdown
-    processes.
-
-Then, we apply Theorem A 2.4 in \cite{kallenberg1997foundations} (Theorem
-    \ref{teo: Vague Relative Compactness through Projection}) and use a
-    corollary of Stone-Weierstrass Theorem (Lemma \ref{lem: Dense set for test
-    functions on empirical measures}) to show that our lookdown representation
-    $\{\xi^N_t: N \in \mathbb{N}\}$ is tight as a $\mathcal{M}(\IR^d
-    \times [0, \infty])$-valued stochastic process in the vague topology as
-    long as $\{F_g(\xi^N_t): N \in \mathbb{N}\}$ is tight as real-valued
-    stochastic processes for a huge class of $F_g$. Explicitly, $F_g(\xi):=
-    \prod_{(x_i,u_i)\in \xi}g(x_i,u_i)$, where $g(x,u)$ satisfies the property
-    that $g(x,u) = 1 $ for all $u \geq u_{*}$ for some $u_{*}>0$.
-% END OLD STUFF
+Now we turn to the main theorem on convergence of the lookdown process, 
+Theorem~\ref{thm:lookdown_convergence}, whose proof
+follows a similar pattern as the the proofs of convergence for the population process
+in Section~\ref{sec:population_density_proof}.
 
@@
 for all values of $N$, with a pointwise embedding
-    of $(\xi^N_t)_{t \ge 0}$ within $(\xi^{M})_{t \ge 0}$ for $b/c < N < M$.
+of $(\lp^N_t)_{t \ge 0}$ within $(\lp^{M})_{t \ge 0}$ for $b/c < N < M$.
 In other words, individuals with levels above $N > b/c$ at time $t_0$
@@
 so we have no such monotonicity.
+
+\begin{proof}[Proof of Theorem~\ref{thm:lookdown_convergence}]
+    As in Section~\ref{sec:population_density_proof},
+    the theorem will follow from tightness and characterization of the limit.
+    This time, the processes $\lp^N$ take values in $\lpmeasures$,
+    the space of locally finite measures on space $\times$ levels.
+    (They will in fact be point measures, including the limit,
+    but that is a consequence of this theorem.)
+
+    Again, tightness follows from a compact containment condition
+    (Lemma~\ref{lem:compact containment lookdown}),
+    tightness of one-dimensional distributions,
+    and an application of \citet{EK} Theorem~3.9.1.
+    Lines of descent can escape to infinite level in finite time,
+    and so we endow $\lpmeasures$ with the vague topology ``in the level coordinate'',
+    i.e., the topology induced by test functions on $\overline{\IR^d} \times [0,\infty)$
+    of the form $g(x) h(u)$, where $g \in C_b(\overline{\IR^d})$ is bounded and continuous
+    and $h \in C_c([0,\infty))$ is continuous with compact support.
+    Theorem~3.9.1 of \citet{EK} requires that $\{(F(\lp^N_t))_{t \ge 0}\}_N$
+    is tight as a sequence of real-valued c\`adl\`ag processes for all $F$ in a subset
+    of $\bar C(\lpmeasures)$, the bounded, continuous functions on $\lpmeasures$,
+    that is dense with respect to uniform convergence on compact subsets.
+    Lemma~\ref{lem:test_fn_tightness} shows that $\{\langle f, \lp^N_t \rangle\}_N$ is a tight sequence
+    for any $f: \overline{\IR^d} \times [0,\infty) \to \IR$ with compact support
+    in the level direction.
+    The functions $\lp \mapsto \langle f, \lp \rangle$
+    do not form not a dense subset of $\bar C(\lpmeasures)$,
+    but they do separate points and vanish nowhere, so
+    by the Stone-Weierstrass theorem, the algebra they generate is dense in $C_0(\lpmeasures)$,
+    the continuous functions that vanish at infinity
+    (i.e., are less than $\epsilon$ outside of a compact set, for any $\epsilon$).
+    Since $C_0(\lpmeasures)$ is dense in $\bar C(\lpmeasures)$
+    with respect to uniform convergence on compact subsets,
+    it suffices to show that tightness for the processes $\langle f, \lp^N_t\rangle$
+    extends to finite sums and products of these processes,
+    which is shown in Lemma~\ref{lem:product_tightness}.
+
+    We show that the martingale properties are preserved in the limit
+    in Section~\ref{sec:lookdown_generator_proofs}.
+    Finally, we must show that the limiting lookdown process $\lp$
+    projects to the limiting process $\eta$, i.e., a solution of the martingale
+    problem in Theorem~\ref{thm:nonlocal_convergence}.
+    Let $N_k \to \infty$ be a sequence along which $\lp^{N_k}$ converges.
+    However, by Theorem~\ref{thm:nonlocal_convergence},
+    there is a subsequence $N_{k(j)}$ along which the projected population processes
+    $\eta^{N_{k(j)}}$ converge, and the limit solves the martingale problem.
+    This implies that any limit of $\lp^N$ projects to a population process $\eta$
+    solving the martingale problem of Theorem~\ref{thm:nonlocal_convergence}.
+\end{proof}
+
+Let $C_c^+$ denote the set of nonnegative continuous functions on $\overline{\IR^d} \times [0, \infty)$
+for which there exists a $u_f \ge 0$ such that $u > u_f$ implies that $f(x, u) = 0$.
+Recall that we are working with the vague topology ``in the level direction'',
+so that $m_n \to m$ in $\lpmeasures$ if and only if $\langle f, m_n \rangle \to \langle f, m \rangle$
+for all $f \in C_c^+$.
+By Theorem~A.23 in \citet{kallenberg1997foundations},
+the space $\lpmeasures$ is separable and metrizable,
+and $K \subset \lpmeasures$ is relatively compact if and only if
+$\sup_{\lp \in K} \langle f, \lp \rangle < \infty$
+for any $f \in C_c^+$.
+% The compact sets we consider are those with bounded total mass of their spatial projection,
+% i.e., of the form
+% $$
+%     K_M = \left\{
+%         \lp \in \lpmeasures \;:\;
+%         \sup_{L \ge 1} \frac{1}{L} \lp\left(\overline{\IR^d} \times [0, L]\right) \le M
+%     \right\} .
+% $$
+% These sets are compact 
+% because if $\lp \in K_M$ and $f \in C_c^+$ then $\langle f, \lp\rangle \le M u_f \|f\|_\infty$.
+Let $\mathcal{H} = \{h_n\}_{n \ge 1}$ be a sequence of
+monotone, nonnegative, compactly supported, differentiable functions
+on $[0, \infty)$ such that there exist sequences $u_n \to \infty$ and $c_n$ such that
+\begin{enumerate}
+    \item $h_n(u) > 1$ for $u \le u_n/2$,
+    \item $h_n(u) = 0$ for $u \ge u_n$,
+    \item $- h_n(u) \le h_n'(u) \le 0$, and
+    \item $\max\left( \int_u^\infty h_n(v) dv, \int_u^\infty h_n(v)^2 dv \right) \le c_n h_n(u)$.
+\end{enumerate}
+For instance, we could take $h_n(u)$ to be a mollified version of $\min(1, e^{-(u-n)})$,
+and then $u_n = c_n = n$.
+The compact sets we consider are those with uniformly bounded integrals against $\mathcal{H}$,
+i.e., of the form
+$$
+    K_C = \left\{
+        \lp \in \lpmeasures \;:\;
+        \langle h_n, \lp \rangle \le C_n
+        \text{ for all } n \ge 1
+    \right\} ,
+$$
+for some sequence of constants $(C_1, C_2, \ldots)$.
+This set is compact because any $f \in C_c^+$ is bounded by a constant multiple of some $h_n$.
+\comment{check: why is it closed?}
+
+\begin{lemma}[Compact containment for $\lp$]
+    \label{lem:compact containment lookdown}
+    Under Assumptions~\ref{},
+    if $\theta/N \to \alpha$ and $\lp_0^N \to \lp_0$ weakly as $N \to \infty$
+    \comment{and they are conditionally Poisson},
+    for any $T$ and $\delta > 0$ there exists a sequence
+    $(C_1, C_2, \ldots)$ of finite constants such that
+    \begin{align} \label{eqn:compact eqn lookdown}
+    \limsup_{N \to \infty}
+    \IP\left\{
+        \sup_{0 \le t \le T} \langle h_n, \lp^N_t \rangle > C_n
+        \text{ for some } n \ge 1
+    \right\}
+    < \delta .
+    \end{align}
+\end{lemma}
+
+In other words, the processes $\lp^N$ stay in $K_C$ for all $0 \le t \le T$
+with uniformly high probability.
+We will prove this Lemma using the following one:
+
+\begin{lemma}
+    \label{lem:compact containment hn}
+    Under the assumptions of Lemma~\ref{lem:compact containment lookdown},
+    for any $T$, $M$ and $n$ there exists a constant $K_n$ such that
+    $$ 
+    \limsup_{N \to \infty} \IP\left\{ \sup_{0 \le t \le T} \langle h_n, \lp^N_t \rangle > M \right\}
+    <
+    \frac{K_n}{M} .
+    $$
+\end{lemma}
+
+\begin{proof}[of Lemma~\ref{lem:compact containment lookdown}]
+    By a union bound,
+    $$ 
+    \IP\left\{
+        \sup_{0 \le t \le T} \langle h_n, \lp^N_t \rangle > C_n
+        \text{ for some } n \ge 1
+    \right\}
+    \le
+    \sum_{n \ge 1}
+    \IP\left\{
+        \sup_{0 \le t \le T} \langle h_n, \lp^N_t \rangle > C_n
+    \right\} ,
+    $$
+    so \eqref{eqn:compact eqn lookdown} follows
+    by taking $C_n = 2^{n-1} K_n / \delta$ in Lemma~\ref{lem:compact containment hn}.
+\end{proof}
+
+\begin{proof}[of Lemma~\ref{lem:compact containment hn}]
+    \comment{TODO: just give bounds on moments and say this follows
+        the proof of Lemma~\ref{lem:eta_compact_containment} exactly, otherwise.
+        Or make the basic idea a lemma in the appendix?}
+    Let $h \in \mathcal{H}$.
+    It is evident from the description of the process
+    (or, by differentiating in Definition~\ref{defn:lookdown_mgale})
+    that
+    \begin{align*}
+    \begin{split}
+        \langle h^n(u), \lp_t^N(dx, du) \rangle
+        &=
+        \langle h^n(u), \lp_0^N(dx, du) \rangle
+        + M^{h_n}_t 
+        \\ & \qquad \qquad {}
+        +
+        \int_0^t
+        \big\langle
+            2 a^N(x, \eta^N_s) \int_u^N h_n(u_1) du_1
+        ,
+        \lp_s^N(dx, du) \big \rangle
+        ds
+        \\ & \qquad \qquad {}
+        +
+        \int_0^t
+        \big\langle
+            \left(
+                a^N(x, \eta^N_s) u^2
+                - b^N(x, \eta^N_s) u
+            \right)
+            h_n'(u)
+        ,
+        \lp_s^N(dx, du) \big \rangle
+        ds
+    \end{split}
+    \end{align*}
+    where $M^{h_n}_t$ is a martingale
+    with quadratic variation
+    \begin{align*}
+        [M^{h_n}]_t
+        &=
+        \int_0^t
+        \langle 2 a^N(x, \eta_s^N) \int_u^N h(u_1)^2 du_1
+        ,
+        \lp_s^N(dx, du) \big \rangle
+        ds .
+    \end{align*}
+    Now, note that $0 \le a^N(x, \eta_x^N) \le C_a$ for some $C_a < \infty$,
+    and we have assumed that $\int_u^\infty h_n(u_1) du_1 \le C_n h_n(u)$,
+    so that 
+    \begin{align*}
+        & \int_0^t
+        \big\langle
+            2 a^N(x, \eta^N_s) \int_u^N h(u_1) du_1
+        ,
+        \lp_s^N(dx, du) \big \rangle
+        ds
+        \\ & \qquad
+        \le
+        2 C_a C_n \int_0^t \big\langle h_n(u), \lp_s^N(dx, du) \big \rangle .
+    \end{align*}
+    In the next line, the contribution from $a^N(x, \eta^N_s) u^2 h'(u)$ is nonpositive because
+    $a^N \ge 0$ and $h'(u) \le 0$.
+    Similarly, since $b^N(x, \eta_x^N) \le C_b$ for some $C_b < \infty$,
+    and by assumption
+    $- h'(u) \le C_n h(u)$ and $h'(u) = 0$ for $u \ge u_n$,
+    and so
+    \begin{align*}
+        & \int_0^t
+        \big\langle
+            \left(
+                a^N(x, \eta^N_s) u^2
+                - b^N(x, \eta^N_s) u
+            \right)
+            h_n'(u)
+        ,
+        \lp_s^N(dx, du) \big \rangle
+        ds
+        \le
+        C_b u_n C_n \int_0^t \big\langle h_n(u), \lp_s^N(dx, du) \big \rangle .
+    \end{align*}
+    Putting this together, we have that
+    \begin{align} \label{eqn:hn_bound}
+        \langle h^n, \lp_t^N \rangle
+        &\le
+        \langle h^n, \lp_0^N \rangle
+        + M^{h_n}_t 
+        + (2 C_a + C_b u_n) C_n \int_0^t 
+            \langle h^n, \lp_s^N \rangle
+        ds .
+    \end{align}
+    By Gronwall's inequality, with $C = (2 C_a + C_b u_n) C_n$
+    \begin{align*}
+        \IE\left[ \langle h^n, \lp_t^N \rangle \right]
+        &\le
+        \IE\left[ \langle h^n, \lp_0^N \rangle \right] e^{Ct} .
+    \end{align*}
+
+    Now consider the maximum. By \eqref{eqn:hn_bound},
+    \begin{align*}
+        \sup_{0 \le t \le T} \langle h^n, \lp_t^N \rangle
+        &\le
+        \langle h^n, \lp_0^N \rangle
+        + \sup_{0 \le t \le T} M^{h_n}_t 
+        + C \int_0^t 
+            \sup_{0 \le t \le T} \langle h^n, \lp_s^N \rangle
+        ds .
+    \end{align*}
+    Again since $\sqrt{x} \le 1 + x$ for $x \ge 0$,
+    The Burkholder-Davis-Gundy inequality
+    tells us that there is a $C'$ such that
+    \begin{align*}
+    \IE\left[ \sup_{0 \le t \le T} M^{h_n}_t \right]
+    & \le
+        C'\left( 1 + \IE\left[ [M^{h_n}]_t \right] \right)
+    \\ & \le
+        C' \left( 1 + \int_0^t \IE\left[
+        \langle 2 a^N(x, \eta_s^N) \int_u^N h(u_1)^2 du_1
+        ,
+        \lp_s^N(dx, du) \big \rangle
+        \right] ds \right) 
+    \\ & \le
+        C' \left( 1 + 2 C_a C_n \int_0^t \IE\left[
+        \langle h_n, \lp_s^N \big \rangle
+        \right] ds \right) 
+    \\ & \le 
+        C' \left( 1 + C'' e^{Ct} \IE[ \langle h^n, \lp_t^N \rangle ] \right) ,
+    \end{align*}
+    where $C'' = 2 C_a C_n / C$.
+    Therefore, 
+    \begin{align*}
+        \IE\left[ \sup_{0 \le t \le T} \langle h^n, \lp_t^N \rangle \right]
+        &\le
+        C' + \IE\left[ \langle h^n, \lp_0^N \rangle \right]( 1 + C'' e^{Ct} )
+        + C \int_0^t 
+            \IE\left[ \sup_{0 \le t \le T} \langle h^n, \lp_s^N \rangle \right]
+        ds ,
+    \end{align*}
+    and so once again by Gronwall's inequality, there is a $C'''$ such that
+    \begin{align*}
+        \IE\left[ \sup_{0 \le t \le T} \langle h^n, \lp_t^N \rangle \right]
+        &\le
+        C'''(1 + \IE[\langle h^n, \lp_0^N \rangle]) e^{2Ct} ,
+    \end{align*}
+    and so
+    \begin{align*}
+        \IP\left\{ \sup_{0 \le t \le T} \langle h^n, \lp_t^N \rangle > K \right\}
+        &\le
+        \frac{
+            C'''(1 + \IE[\langle h^n, \lp_0^N \rangle]) e^{2CT} ,
+        }{ K } .
+    \end{align*}
+\end{proof}
+
+We record for future reference
+the Aldous-Rebolledo criteria for tightness of a sequence real-valued processes:
+\comment{TODO: reference this elsewhere, if we keep it?}
+
+\begin{theorem}[\citet{rebolledo:1980}]
+    \label{thm:aldous_rebolledo}
+    Let $\{Y^(n)\}_{n \ge 1}$ be a sequence of real-valued processes
+    with c\`adl\`ag paths.
+    Suppose that the following conditions are satisfied.
+    \begin{enumerate}
+        \item For each fixed $t$, $\{Y_t^{(n)}\}_{n \ge 1}$  is tight.
+        \item Given a sequence of stopping times $\tau_n$, bounded by $T$,
+            for each $\epsilon > 0$ there exists $\delta > 0$ and $n_0$ such that
+            \begin{align*}
+                \sup_{n \ge n_0}
+                \sup_{\theta \in [0, \delta]}
+                \IP\left\{ \left|
+                    Y^{(n)}_{\tau_n + \theta} - Y^{(n)}_{\tau_n}
+                \right| > \epsilon
+                \right\}
+                \le \epsilon .
+            \end{align*}
+    \end{enumerate}
+    Then the sequence $\{Y^{(n)}\}_{n \ge 1}$ is tight.
+\end{theorem}
+
+\begin{lemma}
+    \label{lem:product_tightness}
+    Let $\{X^{(n)}\}_{n \ge 1}$ and $\{Y^{(n)}\}_{n \ge 1}$ sequences of jointly defined
+    real-valued processes with c\`adl\`ag paths
+    satisfying the conditions of Theorem~\ref{thm:aldous_rebolledo}.
+    Then $\{X^{(n)}Y^{(n)}\}_{n \ge 1}$ and $\{X^{(n)} + Y^{(n)}\}_{n \ge 1}$ also
+    satisfy the conditions of Theorem~\ref{thm:aldous_rebolledo}.
+\end{lemma}
+
+By ``jointly defined'' we mean that $X^{(n)}$ and $Y^{(n)}$ are defined on the same
+probability space, so that the products and sums make sense.
+
+\begin{proof}[of Lemma~\ref{lem:product_tightness}]
+    The proof for $X^{(n)} + Y^{(n)}$ is similar to but more straightforward than
+    for $X^{(n)} Y^{(n)}$, so on only prove the Lemma for the latter.
+    First, note that for any $\epsilon > 0$, by tightness of $X^{(n)}_t$ and $Y^{(n)}_t$
+    there is a $K$ such that
+    $\IP\{ X^{(n)}_t > \sqrt{K} \}$ and $\IP\{ Y^{(n)}_t > \sqrt{K} \}$
+    are both less than $\epsilon/2$,
+    and hence
+    \begin{align*}
+        \IP\{
+            X^{(n)}_t Y^{(n)}_t > K
+        \}
+        \le
+        \IP\{
+            X^{(n)}_t > \sqrt{K}
+        \}
+        +
+        \IP\{
+            Y^{(n)}_t > \sqrt{K}
+        \} 
+        \le \epsilon.
+    \end{align*}
+    Therefore, $X^{(n)}_t Y^{(n)}_t$ is tight.
+
+    Next, note that for $0 \le \tau_n \le T$,
+    \begin{align*}
+        &
+        \sup_{0 \le \theta \le \min(\delta, T-\tau_n)} 
+        \left|
+            X^{(n)}_{\tau_n + \theta} Y^{(n)}_{\tau_n + \theta} 
+            -
+            X^{(n)}_{\tau_n} Y^{(n)}_{\tau_n} 
+        \right|
+        \\ &\qquad 
+        \le
+        \sup_{0 \le \theta \le \min(\delta, T-\tau_n)} 
+        \left| X^{(n)}_{\tau_n + \theta} \right|
+        \left|
+            Y^{(n)}_{\tau_n + \theta} 
+            -
+            Y^{(n)}_{\tau_n} 
+        \right|
+        +
+        \left|
+            X^{(n)}_{\tau_n + \theta}
+            -
+            X^{(n)}_{\tau_n}
+        \right|
+        \left| Y^{(n)}_{\tau_n} \right|
+        \\ &\qquad 
+        \le
+        \sup_{0 \le t \le T}
+            \left| X^{(n)}_t \right|
+        \sup_{0 \le \theta \le \min(\delta, T-\tau_n)} 
+        \left|
+            Y^{(n)}_{\tau_n + \theta} 
+            -
+            Y^{(n)}_{\tau_n} 
+        \right|
+        +
+        \sup_{0 \le \theta \le \min(\delta, T-\tau_n)} 
+        \left|
+            X^{(n)}_{\tau_n + \theta}
+            -
+            X^{(n)}_{\tau_n}
+        \right|
+        \sup_{0 \le t \le T}
+        \left| Y^{(n)}_t \right| ,
+    \end{align*}
+    so that for any $C$,
+    \begin{align} \label{eqn:xy_bound}
+        \begin{split}
+        &
+        \IP\left\{
+        \sup_{0 \le \theta \le \min(\delta, T-\tau_n)} 
+        \left|
+            X^{(n)}_{\tau_n + \theta} Y^{(n)}_{\tau_n + \theta} 
+            -
+            X^{(n)}_{\tau_n} Y^{(n)}_{\tau_n} 
+        \right|
+        > \epsilon
+        \right\}
+    \\ &\qquad \le
+        \IP\left\{
+            \sup_{0 \le t \le T}
+                \left| X^{(n)}_t \right|
+            > C
+        \right\}
+    +
+        \IP\left\{
+        \sup_{0 \le \theta \le \min(\delta, T-\tau_n)} 
+        \left|
+            Y^{(n)}_{\tau_n + \theta} 
+            -
+            Y^{(n)}_{\tau_n} 
+        \right|
+            > \epsilon/C
+        \right\}
+    \\ &\qquad {} +
+        \IP\left\{
+        \sup_{0 \le \theta \le \min(\delta, T-\tau_n)} 
+        \left|
+            X^{(n)}_{\tau_n + \theta} 
+            -
+            X^{(n)}_{\tau_n} 
+        \right|
+            > \epsilon/C
+        \right\}
+    +
+        \IP\left\{
+            \sup_{0 \le t \le T}
+                \left| Y^{(n)}_t \right|
+            > C
+        \right\}
+        \end{split}
+    \end{align}
+    Now, since $\max_{0 \le t \le T} X^{(n)}_t$ is tight (and likewise for $Y$)
+    (see, e.g., Remark 3.7.3 in \citet{EK}),
+    we may choose a $C \ge 4$ for which
+    $$
+    \IP\left\{
+        \sup_{0 \le t \le T}
+            \left| X^{(n)}_t \right|
+        > C
+    \right\} \le \frac{\epsilon}{4} .
+    $$
+    Simliarly, by assumption we can choose a $\delta$ for which
+    $$
+        \IP\left\{
+        \sup_{0 \le \theta \le \min(\delta, T-\tau_n)} 
+        \left|
+            X^{(n)}_{\tau_n + \theta} 
+            -
+            X^{(n)}_{\tau_n} 
+        \right|
+            > \epsilon/C
+        \right\}
+        \le \frac{\epsilon}{C} .
+    $$
+    If we choose $C$ and $\delta$ that do this for both $X^{(n)}$ and $Y^{(n)}$,
+    then each of the terms in equation~\eqref{eqn:xy_bound} are bounded by $\epsilon/4$,
+    and condition (2) is satisfied for the product process.
+\end{proof}
+
+\begin{lemma}
+    \label{lem:test_fn_tightness}
+    Let $f$ be a bounded, continuous real-valued function on $\IR^d \times [0, \infty)$
+    with uniformly bounded first and second derivatives
+    for which there exists a $u_0$ such that if $u > u_0$ then $f(x, u) = 0$.
+    Then, the sequence of real-valued processes $(\langle f, \lp_t^N \rangle)_{t \ge 0}$
+    are tight in the space of c\`adl\`ag processes.
+\end{lemma}
+
+\begin{proof}[of Lemma \ref{lem:test_fn_tightness}]
+    First, a reminder of the description of the process
+    \comment{(TODO: figure out if the notation here for $a$ and $b$ should be used above;
+        if so, move it up; if not, replace it here.)}
+    Recall when the state of the process is $\eta$,
+    the level of a line of descent at spatial location $x$ and level $u$
+    changes following
+    $$
+        \dot u = a^N(x, \eta) u^2 - b^N(x, \eta) u,
+    $$
+    where
+    $$
+        a^N(x, \eta)
+        =
+        \frac{\theta}{N} \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q(x, dy) ,
+    $$
+    and
+    $$
+        b^N(x, \eta)
+        =
+        \theta \gamma(x, \eta) \int_{\IR^d} (r(y, \eta) - r(x, \eta)) q(x, dy) + F(x, \eta) .
+    $$
+    Furthermore, the line of descent
+    gives birth to lines at higher levels at rate $2 (N - u) a^N(x, \eta)$,
+    that each such new line chooses a level uniformly from $[u, N]$,
+    a spatial location $y$ from the kernel
+    $$
+        q^m(x, dy, \eta)
+        =
+        r(y, \eta) q(x, dy) / \int_{\IR^d} r(y, \eta) q(x, dy),
+    $$
+    and the two lines swap spatial locations with probability 1/2.
+
+    It is evident from the description of the process
+    (or, by differentiating in Definition~\ref{defn:lookdown_mgale})
+    that
+    \begin{align*}
+    \begin{split}
+    M^f_t
+        &=
+        \langle f, \lp_t^N \rangle
+        -
+        \langle f, \lp_0^N \rangle
+    \\ & \qquad \qquad {}
+        -
+        \int_0^t
+        \big\langle
+            a^N(x, \eta^N_s)
+            \int_u^N \int_{\IR^d}
+            \left(
+                f(y, u_1) + f(x, u_1) + f(y, u) - f(x, u)
+            \right)
+            du_1 q^m(x, dy, \eta^N_s)
+    \\ & \qquad \qquad \qquad \qquad {}
+            +
+            \left(
+                a^N(x, \eta^N_s) u^2
+                - b^N(x, \eta^N_s) u
+            \right)
+            \frac{d}{du} f(x, u)
+        ,
+        \lp_s^N(dx, du) \big \rangle
+        ds
+    \end{split}
+    \end{align*}
+    is a martingale,
+    with quadratic variation
+    \begin{align*}
+        [M^f]_t
+        &=
+        \int_0^t
+        \langle a^N(x, \eta_s^N) \int_u^N \int_{\IR^d}
+            f(y, u_1)^2 +
+            \left( f(x, u_1) + f(y, u) - f(x, u) \right)^2
+        du_1 q^m(x, dy, \eta^N_s)
+        \lp_s^N(dx, du) \big \rangle
+        ds .
+    \end{align*}
+
+    Now we would like to bound the terms in the integral,
+    to arrive at a bound using Gronwall's inequality, as before.
+
+    First, note that there exists a constant $C_a$
+    such that $a^N(x, \eta) \le C_a$
+    (since $\gamma$ and $r$ are bounded above, and $\theta/N \to \alpha \ge 0$),
+    and for any $\epsilon > 0$ and $T$ there is a $C_b$ such that for all $N$,
+    $$
+        \IP\left\{
+            \sup_{0 \le s \le T} \sup_x |b^N(x, \eta_s^N)| > C_b
+        \right\}
+        < \epsilon 
+    $$
+    \comment{reference where we show this above}.
+    Now, since $f$ vanishes for $u \ge u_0$,
+    on the event that $\sup_x |b^N(x, \eta_s^N)| \le C_b$ then
+    if $N \ge u_0$,
+    \begin{align*}
+    &
+        \int_{\IR^d} \int_0^N
+            \left(
+                a^N(x, \eta^N_s) u^2
+                - b^N(x, \eta^N_s) u
+            \right)
+            \frac{d}{du} f(x, u)
+        \lp_s^N(dx, du)
+    \\  & \qquad
+    \le
+        \int_{\IR^d} \int_0^{u_0}
+            \left(
+                C_a u_0^2
+                + C_b u_0
+            \right)
+            \left\| \frac{d}{du} f \right\|_\infty
+        \lp_s^N(dx, du) .
+    \\  & \qquad
+    \le
+        C_0 \lp_s^N(\IR^d \times [0, u_0]) .
+    \end{align*}
+
+    Next, observe that for any $\eta$,
+    $$
+    \int_{\IR^d} \int_u^N (f(y, u_1) + f(x, u_1)) du_1 q^m(x, dy, \eta)
+    \le 2 u_0 \|f\|_\infty .
+    $$
+    Furthermore,
+    recall that we have assumed \comment{(check where we do this)}
+    that $q^m$ is uniformly elliptic,
+    and so since $f$ has bounded first and second derivatives,
+    there is a $C_1$ depending on $f$ such that for all $\eta$,
+    $\theta \int_{\IR^d} (f(y, u) - f(x, u)) q^m(x, dy, \eta) \le C_1$.
+    Therefore, using boundedness of $\theta/N$,
+    \begin{align*}
+        &
+        \int_{\IR^d} \int_u^N (f(y, u) - f(x, u)) du_1 q^m(x, dy, \eta^N_s)
+        \\ &\qquad
+        = (N - u) \int_{\IR^d} (f(y, u) - f(x, u)) q^m(x, dy, \eta^N_s)
+        \\ &\qquad
+        = \frac{N}{\theta} \left(1 - \frac{u}{N}\right) \theta \int_{\IR^d}
+            (f(y, u) - f(x, u)) q^m(x, dy, \eta^N_s)
+        \\ &\qquad
+        \le C_1 \frac{N}{\theta} \ind_{u \le u_0} .
+    \end{align*}
+
+    Putting this together,
+    \begin{align*}
+        \IE\left[
+            \langle f, \lp_t^N \rangle
+        \right]
+        \le
+    \end{align*}
+
+\end{proof}
+
+\subsubsection{OLD STUFF REMOVE}
 
@@
     and therefore uniformly bounded (because we may take $u_1 \le N$).
-
-\end{proof}
-
-% % % % % % % % % % % % %
-\subsubsection{New stuff}
-
-\comment{TODO: reference this elsewhere, if we keep it?}
-We record for future reference
-the Aldous-Rebolledo criteria for tightness of a sequence real-valued processes:
-
-\begin{theorem}[\citet{rebolledo:1980}]
-    \label{thm:aldous_rebolledo}
-    Let $\{Y^(n)\}_{n \ge 1}$ be a sequence of real-valued processes
-    with c\`adl\`ag paths.
-    Suppose that the following conditions are satisfied.
-    \begin{enumerate}
-        \item For each fixed $t$, $\{Y_t^(n)\}_{n \ge 1}$  is tight.
-        \item Given a sequence of stopping times $\tau_n$, bounded by $T$,
-            for each $\epsilon > 0$ there exists $\delta > 0$ and $n_0$ such that
-            \begin{align*}
-                \sup_{n \ge n_0}
-                \sup_{\theta \in [0, \delta]}
-                \IP\left\{ \left|
-                    Y^{(n)}_{\tau_n + \theta} - Y^{(n)}_{\tau_n}
-                \right| > \epsilon
-                \right\}
-                \le \epsilon .
-            \end{align*}
-    \end{enumerate}
-    Then the sequence $\{Y^(n)\}_{n \ge 1}$ is tight.
-\end{theorem}
-
-\begin{lemma}
-    \label{lem:test_fn_tightness}
-    Let $f$ be a bounded, continuous real-valued function on $\IR^d \times [0, \infty)$
-    with uniformly bounded first and second derivatives
-    for which there exists a $u_0$ such that if $u > u_0$ then $f(x, u) = 0$.
-    Then, the sequence of real-valued processes $(\langle f, \xi_t^N \rangle)_{t \ge 0}$
-    are tight in the space of c\`adl\`ag processes.
-\end{lemma}
-
-\begin{proof}[of Lemma \ref{lem:test_fn_tightness}]
-    First, a reminder of the description of the process
-    \comment{(TODO: figure out if the notation here for $a$ and $b$ should be used above;
-        if so, move it up; if not, replace it here.)}
-    Recall when the state of the process is $\eta$,
-    the level of a line of descent at spatial location $x$ and level $u$
-    changes following
-    $$
-        \dot u = a^N(x, \eta) u^2 - b^N(x, \eta) u,
-    $$
-    where
-    $$
-        a^N(x, \eta)
-        =
-        \frac{\theta}{N} \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q(x, dy) ,
-    $$
-    and
-    $$
-        b^N(x, \eta)
-        =
-        \theta \gamma(x, \eta) \int_{\IR^d} (r(y, \eta) - r(x, \eta)) q(x, dy) + F(x, \eta) .
-    $$
-    Furthermore, the line of descent
-    gives birth to lines at higher levels at rate $2 (N - u) a^N(x, \eta)$,
-    that each such new line chooses a level uniformly from $[u, N]$,
-    a spatial location $y$ from the kernel
-    $$
-        q^m(x, dy, \eta)
-        =
-        r(y, \eta) q(x, dy) / \int_{\IR^d} r(y, \eta) q(x, dy),
-    $$
-    and the two lines swap spatial locations with probability 1/2.
-
-    It is evident from the description of the process
-    (or, by differentiating in Definition~\ref{defn:lookdown_mgale})
-    that
-    \begin{align*}
-    \begin{split}
-    M^f_s
-        &=
-        \langle f, \xi_t^N \rangle
-        -
-        \langle f, \xi_0^N \rangle
-    \\ & \qquad \qquad {}
-        -
-        \int_0^t
-        \big\langle
-            a^N(x, \eta^N_t)
-            \int_u^N \int_{\IR^d}
-            \left(
-                f(y, u_1) + f(x, u_1) + f(y, u) - f(x, u)
-            \right)
-            du_1 q^m(x, dy, \eta^N_s)
-    \\ & \qquad \qquad \qquad \qquad {}
-            +
-            \left(
-                a^N(x, \eta^N_s) u^2
-                - b^N(x, \eta^N_s) u
-            \right)
-            \frac{d}{du} f(x, u)
-        ,
-        \xi_s^N(dx, du) \big \rangle
-        ds
-    \end{split}
-    \end{align*}
-    is a martingale.
-    Now we would like to bound the terms in the integral,
-    to arrive at a bound using Gronwall's inequality, as before.
-
-    First, note that there exists a constant $C_a$
-    such that $a^N(x, \eta) \le C_a$
-    (since $\gamma$ and $r$ are bounded above, and $\theta/N \to \alpha \ge 0$),
-    and for any $\epsilon > 0$ and $T$ there is a $C_b$ such that for all $N$,
-    $$
-        \IP\left\{
-            \sup_{0 \le s \le T} \sup_x |b^N(x, \eta_s^N)| > C_b
-        \right\}
-        < \epsilon 
-    $$
-    \comment{reference where we show this above}.
-    Now, since $f$ vanishes for $u \ge u_0$,
-    on the event that $\sup_x |b^N(x, \eta_s^N)| \le C_b$ then
-    if $N \ge u_0$,
-    \begin{align*}
-    &
-        \int_{\IR^d} \int_0^N
-            \left(
-                a^N(x, \eta^N_s) u^2
-                - b^N(x, \eta^N_s) u
-            \right)
-            \frac{d}{du} f(x, u)
-        \xi_s^N(dx, du)
-    \\  & \qquad
-    \le
-        \int_{\IR^d} \int_0^{u_0}
-            \left(
-                C_a u_0^2
-                + C_b u_0
-            \right)
-            \left\| \frac{d}{du} f \right\|_\infty
-        \xi_s^N(dx, du) .
-    \\  & \qquad
-    \le
-        C_0 \xi_s^N(\IR^d \times [0, u_0]) .
-    \end{align*}
-
-    Next, observe that for any $\eta$,
-    $$
-    \int_{\IR^d} \int_u^N (f(y, u_1) + f(x, u_1)) du_1 q^m(x, dy, \eta)
-    \le 2 u_0 \|f\|_\infty .
-    $$
-    Furthermore,
-    recall that we have assumed \comment{(check where we do this)}
-    that $q^m$ is uniformly elliptic,
-    and so since $f$ has bounded first and second derivatives,
-    there is a $C_1$ depending on $f$ such that for all $\eta$,
-    $\theta \int_{\IR^d} (f(y, u) - f(x, u)) q^m(x, dy, \eta) \le C_1$.
-    Therefore, using boundedness of $\theta/N$,
-    \begin{align*}
-        &
-        \int_{\IR^d} \int_u^N (f(y, u) - f(x, u)) du_1 q^m(x, dy, \eta^N_s)
-        \\ &\qquad
-        = (N - u) \int_{\IR^d} (f(y, u) - f(x, u)) q^m(x, dy, \eta^N_s)
-        \\ &\qquad
-        = \frac{N}{\theta} \left(1 - \frac{u}{N}\right) \theta \int_{\IR^d}
-            (f(y, u) - f(x, u)) q^m(x, dy, \eta^N_s)
-        \\ &\qquad
-        \le C_1 \frac{N}{\theta} \ind_{u \le u_0} .
-    \end{align*}
-
-    Putting this together,
-    \begin{align*}
-        \IE\left[
-            \langle f, \xi_t^N \rangle
-        \right]
-        \le
-    \end{align*}
-
-\end{proof}
 

### 2023-01-30 forwards-and-backwards.tex
edits!

@@
 % % % % % % % % % % % % %
-\subsection{Tightness of the Lines of Descent}
+\subsection{Tightness of the Lookdown Process}
     \label{sec:lookdown_convergence}
@@
 Recall that the level $U_a(t)$ of a line of descent evolves as
+\comment{TODO: harmonize notation with above}
 $$
@@
 =
-c(x, \eta)
+c^N(x, \eta)
 u^2
-- b(x, \eta)
+- b^N(x, \eta)
 u,
@@
 \begin{align*}
-    c(x, \eta) &= \frac{\theta}{N} \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q(x, dy) \\
+    c^N(x, \eta) &= \frac{\theta}{N} \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q(x, dy) \\
     \text{and}\qquad
-    b(x, \eta)
+    b^N(x, \eta)
     &=
@@
 \end{align*}
-(see equations \eqref{eqn:level_generator} and \eqref{eqn:b_limit}),
-where $c(x, \eta) \ge 0$ and $b(x, \eta)$ may take either sign.
-In \citet{kurtz/rodrigues:2011}, $b$ was bounded above and $c$ was bounded away from zero,
-so they noted that if $U_a(t) \ge b/c$
+(see equations \eqref{eqn:level_generator} and \eqref{eqn:b_limit}), where
+$c^N(x, \eta) \ge 0$ and $b^N(x, \eta)$ may take either sign.
+Assumptions~\ref{def:model_setup} imply that $c^N(x, \eta)$ is bounded
+and $b^N(x, \eta)$, because of $F(x, \eta)$, is bounded above but not necessarily below.
+In \citet{kurtz/rodrigues:2011}, $b^N$ was bounded above and $c^N$ was bounded away from zero,
+so they noted that if $U_a(t) \ge b^N/c^N$
 lines of descent would only move upwards from that time onwards.
@@
 for all values of $N$, with a pointwise embedding
-of $(\lp^N_t)_{t \ge 0}$ within $(\lp^{M})_{t \ge 0}$ for $b/c < N < M$.
-In other words, individuals with levels above $N > b/c$ at time $t_0$
+of $(\lp^N_t)_{t \ge 0}$ within $(\lp^{M})_{t \ge 0}$ for $b^N/c^N < N < M$.
+In other words, individuals with levels above $N > b^N/c^N$ at time $t_0$
 do not affect $(\lp^N_t)_{t \ge t_0}$,
@@
 it does not have this monotonicity:
-for one thing, $b$ and $c$ depend on the population process $\eta$
+for one thing, $b^N$ and $c^N$ depend on the population process $\eta$
 and so all individuals can affect all other ones (even those with lower levels).
@@
 since in the deterministic case there is no branching.
-In our case $b$ and $c$ depend on the state of the population,
+In our case $b^N$ and $c^N$ depend on the state of the population,
 so we have no such monotonicity.
+
+To complete the description of the process,
+each line of descent
+gives birth to lines at higher levels at rate $2 (N - u) c^N(x, \eta)$,
+and each such new line chooses a level uniformly from $[u, N]$,
+a spatial location $y$ from the kernel
+$$
+    q^m(x, dy, \eta)
+    =
+    r(y, \eta) q(x, dy) / \int_{\IR^d} r(y, \eta) q(x, dy),
+$$
+and the two lines swap spatial locations with probability 1/2.
+
+It is evident from the description of the process
+(or, by differentiating in Definition~\ref{defn:lookdown_mgale})
+that
+\begin{align} \label{eqn:f_xi_mgale}
+\begin{split}
+    \langle f, \lp_t^N \rangle
+    &=
+    \langle f, \lp_0^N \rangle
+    + M^f_t
+\\ & \qquad {}
+    +
+    \int_0^t
+    \big\langle
+        c^N(x, \eta^N_s)
+        \int_u^N \int_{\IR^d}
+        \left(
+            f(y, u_1) + f(x, u_1) + f(y, u) - f(x, u)
+        \right)
+        du_1 q^m(x, dy, \eta^N_s)
+\\ & \qquad \qquad \qquad \qquad {}
+        +
+        \left(
+            c^N(x, \eta^N_s) u^2
+            - b^N(x, \eta^N_s) u
+        \right)
+        \frac{d}{du} f(x, u)
+    ,
+    \lp_s^N(dx, du) \bigg \rangle
+    ds ,
+\end{split}
+\end{align}
+where $M^f$ is a martingale
+with quadratic variation
+\begin{align} \label{eqn:f_xi_qv}
+    [M^f]_t
+    &=
+    \int_0^t
+    \bigg \langle c^N(x, \eta_s^N) \int_u^N \int_{\IR^d}
+        \big[ f(y, u_1)^2
+\\&\qquad \qquad {}
+        + \left( f(x, u_1) + f(y, u) - f(x, u) \right)^2 \big]
+    du_1 q^m(x, dy, \eta^N_s)
+    ,
+    \lp_s^N(dx, du) \bigg \rangle
+    ds .
+\end{align}
+
+In addition to tightness of the measure-values processes $\lp^N$,
+the bounds used in the proofs below also imply
+tightness of the number of lines of descent and the number of births below a fixed level,
+and of the motion of individual lines of descent.
+In other words, the limiting ``line of descent'' construction holds.
 
@@
 monotone, nonnegative, compactly supported, differentiable functions
-on $[0, \infty)$ such that there exist sequences $u_n \to \infty$ and $c_n$ such that
+on $[0, \infty)$ such that there exist sequences $u_n \to \infty$ and $k_n$ such that
 \begin{enumerate}
@@
     \item $- h_n(u) \le h_n'(u) \le 0$, and
-    \item $\max\left( \int_u^\infty h_n(v) dv, \int_u^\infty h_n(v)^2 dv \right) \le c_n h_n(u)$.
+    \item $\max\left( \int_u^\infty h_n(v) dv, \int_u^\infty h_n(v)^2 dv \right) \le k_n h_n(u)$.
 \end{enumerate}
 For instance, we could take $h_n(u)$ to be a mollified version of $\min(1, e^{-(u-n)})$,
-and then $u_n = c_n = n$.
+and then $u_n = k_n = n$.
+\comment{(or we could just take those functions? they are differentiable almost everywhere.)}
 The compact sets we consider are those with uniformly bounded integrals against $\mathcal{H}$,
@@
 This set is compact because any $f \in C_c^+$ is bounded by a constant multiple of some $h_n$.
-\comment{check: why is it closed?}
 
@@
     \label{lem:compact containment lookdown}
-    Under Assumptions~\ref{},
+    Under Assumptions~\ref{def:model_setup},
     if $\theta/N \to \alpha$ and $\lp_0^N \to \lp_0$ weakly as $N \to \infty$
@@
     so \eqref{eqn:compact eqn lookdown} follows
-    by taking $C_n = 2^{n-1} K_n / \delta$ in Lemma~\ref{lem:compact containment hn}.
+    by taking $C_n = 2^{n-1} K_n / \delta$ and using Lemma~\ref{lem:compact containment hn}.
 \end{proof}
@@
 \begin{proof}[of Lemma~\ref{lem:compact containment hn}]
-    \comment{TODO: just give bounds on moments and say this follows
+    \comment{TODO: just give bounds and say this follows
         the proof of Lemma~\ref{lem:eta_compact_containment} exactly, otherwise.
         Or make the basic idea a lemma in the appendix?}
-    Let $h \in \mathcal{H}$.
+    Let $h_n \in \mathcal{H}$.
     It is evident from the description of the process
@@
     that
+    Applied to $f(x, u) = h_n(u)$, the martinagle representation~\eqref{eqn:f_xi_mgale} is
     \begin{align*}
     \begin{split}
-        \langle h^n(u), \lp_t^N(dx, du) \rangle
+        \langle h_n, \lp_t^N \rangle
         &=
-        \langle h^n(u), \lp_0^N(dx, du) \rangle
+        \langle h_n, \lp_0^N \rangle
         + M^{h_n}_t 
@@
         \lp_s^N(dx, du) \big \rangle
-        ds
+        ds ,
     \end{split}
@@
         \int_0^t
-        \langle 2 a^N(x, \eta_s^N) \int_u^N h(u_1)^2 du_1
+        \langle 2 a^N(x, \eta_s^N) \int_u^N h_n(u_1)^2 du_1
         ,
@@
     Now, note that $0 \le a^N(x, \eta_x^N) \le C_a$ for some $C_a < \infty$,
-    and we have assumed that $\int_u^\infty h_n(u_1) du_1 \le C_n h_n(u)$,
+    and we have assumed that $\int_u^\infty h_n(u_1) du_1 \le k_n h_n(u)$,
     so that 
@@
         \big\langle
-            2 a^N(x, \eta^N_s) \int_u^N h(u_1) du_1
+            2 a^N(x, \eta^N_s) \int_u^N h_n(u_1) du_1
         ,
@@
         \le
-        2 C_a C_n \int_0^t \big\langle h_n(u), \lp_s^N(dx, du) \big \rangle .
+        2 C_a k_n \int_0^t \big\langle h_n(u), \lp_s^N(dx, du) \big \rangle .
     \end{align*}
@@
     and by assumption
-    $- h'(u) \le C_n h(u)$ and $h'(u) = 0$ for $u \ge u_n$,
+    $- h_n'(u) \le k_n h_n(u)$ and $h_n'(u) = 0$ for $u \ge u_n$,
     and so
@@
         \le
-        C_b u_n C_n \int_0^t \big\langle h_n(u), \lp_s^N(dx, du) \big \rangle .
+        C_b u_n k_n \int_0^t \big\langle h_n(u), \lp_s^N(dx, du) \big \rangle .
     \end{align*}
@@
     \begin{align} \label{eqn:hn_bound}
-        \langle h^n, \lp_t^N \rangle
+        \langle h_n, \lp_t^N \rangle
         &\le
-        \langle h^n, \lp_0^N \rangle
+        \langle h_n, \lp_0^N \rangle
         + M^{h_n}_t 
-        + (2 C_a + C_b u_n) C_n \int_0^t 
-            \langle h^n, \lp_s^N \rangle
+        + (2 C_a + C_b u_n) k_n \int_0^t 
+            \langle h_n, \lp_s^N \rangle
         ds .
     \end{align}
-    By Gronwall's inequality, with $C = (2 C_a + C_b u_n) C_n$
-    \begin{align*}
-        \IE\left[ \langle h^n, \lp_t^N \rangle \right]
+    By Gronwall's inequality, with $C = (2 C_a + C_b u_n) k_n$
+    \begin{align*}
+        \IE\left[ \langle h_n, \lp_t^N \rangle \right]
         &\le
-        \IE\left[ \langle h^n, \lp_0^N \rangle \right] e^{Ct} .
+        \IE\left[ \langle h_n, \lp_0^N \rangle \right] e^{Ct} .
     \end{align*}
@@
     \begin{align*}
-        \sup_{0 \le t \le T} \langle h^n, \lp_t^N \rangle
+        \sup_{0 \le t \le T} \langle h_n, \lp_t^N \rangle
         &\le
-        \langle h^n, \lp_0^N \rangle
+        \langle h_n, \lp_0^N \rangle
         + \sup_{0 \le t \le T} M^{h_n}_t 
         + C \int_0^t 
-            \sup_{0 \le t \le T} \langle h^n, \lp_s^N \rangle
+            \sup_{0 \le t \le T} \langle h_n, \lp_s^N \rangle
         ds .
@@
         C' \left( 1 + \int_0^t \IE\left[
-        \langle 2 a^N(x, \eta_s^N) \int_u^N h(u_1)^2 du_1
+        \langle 2 a^N(x, \eta_s^N) \int_u^N h_n(u_1)^2 du_1
         ,
@@
     \\ & \le
-        C' \left( 1 + 2 C_a C_n \int_0^t \IE\left[
+        C' \left( 1 + 2 C_a k_n \int_0^t \IE\left[
         \langle h_n, \lp_s^N \big \rangle
@@
     \\ & \le 
-        C' \left( 1 + C'' e^{Ct} \IE[ \langle h^n, \lp_t^N \rangle ] \right) ,
-    \end{align*}
-    where $C'' = 2 C_a C_n / C$.
+        C' \left( 1 + C'' e^{Ct} \IE[ \langle h_n, \lp_t^N \rangle ] \right) ,
+    \end{align*}
+    where $C'' = 2 C_a k_n / C$.
     Therefore, 
     \begin{align*}
-        \IE\left[ \sup_{0 \le t \le T} \langle h^n, \lp_t^N \rangle \right]
+        \IE\left[ \sup_{0 \le t \le T} \langle h_n, \lp_t^N \rangle \right]
         &\le
-        C' + \IE\left[ \langle h^n, \lp_0^N \rangle \right]( 1 + C'' e^{Ct} )
+        C' + \IE\left[ \langle h_n, \lp_0^N \rangle \right]( 1 + C'' e^{Ct} )
         + C \int_0^t 
-            \IE\left[ \sup_{0 \le t \le T} \langle h^n, \lp_s^N \rangle \right]
+            \IE\left[ \sup_{0 \le t \le T} \langle h_n, \lp_s^N \rangle \right]
         ds ,
@@
     \begin{align*}
-        \IE\left[ \sup_{0 \le t \le T} \langle h^n, \lp_t^N \rangle \right]
+        \IE\left[ \sup_{0 \le t \le T} \langle h_n, \lp_t^N \rangle \right]
         &\le
-        C'''(1 + \IE[\langle h^n, \lp_0^N \rangle]) e^{2Ct} ,
+        C'''(1 + \IE[\langle h_n, \lp_0^N \rangle]) e^{2Ct} ,
     \end{align*}
@@
     \begin{align*}
-        \IP\left\{ \sup_{0 \le t \le T} \langle h^n, \lp_t^N \rangle > K \right\}
+        \IP\left\{ \sup_{0 \le t \le T} \langle h_n, \lp_t^N \rangle > K \right\}
         &\le
         \frac{
-            C'''(1 + \IE[\langle h^n, \lp_0^N \rangle]) e^{2CT} ,
+            C'''(1 + \IE[\langle h_n, \lp_0^N \rangle]) e^{2CT} 
         }{ K } .
@@
 
-We record for future reference
-the Aldous-Rebolledo criteria for tightness of a sequence real-valued processes:
+\begin{lemma}
+    \label{lem:test_fn_tightness}
+    Let $f$ be a bounded, continuous real-valued function on $\IR^d \times [0, \infty)$
+    with uniformly bounded first and second derivatives
+    for which there exists a $u_0$ such that if $u > u_0$ then $f(x, u) = 0$.
+    Then, the sequence of real-valued processes $(\langle f, \lp_t^N \rangle)_{t \ge 0}$
+    are tight in the space of c\`adl\`ag processes.
+\end{lemma}
+
+\begin{proof}[of Lemma \ref{lem:test_fn_tightness}]
+    Again, we use the Aldous-Rebolledo criterion.
+    Tightness of $\langle f, \lp_t \rangle$ for a fixed $t$
+    follows from Lemma~\ref{lem:compact containment hn},
+    so we need only prove conditions analogous to
+    \eqref{eqn:eta_projections_goal1}
+    and \eqref{eqn:eta_projections_goal2}
+    applied to the martingale representation
+    of equations~\eqref{eqn:f_xi_mgale} and~\eqref{eqn:f_xi_qv}.
+    Indeed, the proof follows exactly as the proof of
+    Lemma~\ref{lem:eta_projections_tightness},
+    except that terms are bounded by constant multiples of $\langle h_n, \xi^N_s \rangle$
+    instead of $\langle 1, \eta^N_s \rangle$,
+    where $h_n$ is bounded below on $[0, u_*]$.
+    \comment{(or we could say that $u_n \ge 2 u_*$)}
+    There is only one term that might use explanation,
+    which is
+    \begin{align*}
+        &
+        \frac{\theta}{N} \int_{\IR^d} \int_u^N (f(y, u) - f(x, u)) du_1 q^m(x, dy, \eta^N_s)
+        \\ &\qquad
+        % = \frac{\theta}{N} (N - u) \int_{\IR^d} (f(y, u) - f(x, u)) q^m(x, dy, \eta^N_s) \\ &\qquad
+        = \left(1 - \frac{u}{N}\right) \theta \int_{\IR^d}
+            (f(y, u) - f(x, u)) q^m(x, dy, \eta^N_s) ,
+    \end{align*}
+    but this is now clearly bounded by a constant multiple of $h_n(u)$.
+\end{proof}
+
+% % % % % % % % % % % % %
+\subsection{Motion of ancestral lineages}
+
+In this section we prove Theorem~\ref{thm:lineages}.
+The argument follows directly from the discussion in Section \ref{sec:limiting_lines_of_descent}.
+
+\begin{proof}[of Theorem~\ref{thm:lineages}]
+
+\comment{(TODO: Use notation for the motion of a lineage introduced in statement of theorem.)}
+
+Here
+\comment{(and in the statement of the theorem)}
+we take the high-density, deterministic limit
+(so, $\theta, N \to \infty$ and $\theta/N \to 0$)
+and so suppose that the limiting process has density $\varphi_t(x)$
+at location $x$ and time $t$.
+Let $Y$ denote the spatial motion followed by a single line of descent.
+Above equation~\eqref{eqn:limiting_generator},
+we showed that $Y$ is a diffusion with generator at time $s$
+$$
+    \mathcal{L}^Y_s g(x) = \gamma ( \DG(rg)(x) - g \DG r(x) ) .
+$$
+The diffusion is time-inhomogeneous if the density is not constant with time
+(since recall that the coefficients $\gamma$ and $r$ depend on the density).
+Formally, the intensity of levels at $y$ at time $t$
+that are descended from individuals that were at $x$ at time $s$
+(with $s < t$) is
+\begin{equation} \label{eqn:formal_intensity}
+    \varphi_s(x) \IE_{s,x} \left[
+        \exp\left(
+            \int_s^t (F + \gamma \DG r)(Y_u) du
+        \right)
+        \ind_{Y_t = y}
+    \right]
+    dy ,
+\end{equation}
+where the subscript $s, x$ in the expectation indicates that $Y_s = x$.
+To see why this should be true, 
+suppose that an ancestor has level $v$. Conditional on its 
+spatial motion $\{Y_u\}_{s\leq u\leq t}$, its level at time $t$ will
+be $v \exp(-\int_s^t(F+\gamma\Delta r)(Y_u)du)$. This will be less than a given level 
+$N$ if $v < N \exp(\int_s^t(F+\gamma\Delta r)(Y_u)du)$. 
+The intensity of levels at $y$ that are descended from individuals at
+$x$ can therefore be obtained as the limit as $N\to\infty$ of 
+$1/N$ times the number of levels at $x$ at time zero with
+$u<N \exp(\int_s^t(F+\gamma\Delta r)(Y_u)du)$ and for which
+the corresponding individual is at $y$ at time $t$, which is 
+precisely the quantity in~\eqref{eqn:formal_intensity}.
+
+By our construction in Section~\ref{sec:limiting_lines_of_descent},
+when we integrate~\eqref{eqn:formal_intensity}
+with respect to $x$ we recover $\varphi_t(y)dy$. 
+Consider an individual sampled at location $y$ at time $t$,
+and write $p(t,s,y,x)$ for the probability density
+that their ancestor at time $s$ was at $x$.
+As a consequence of~\eqref{eqn:formal_intensity},
+still formally,
+\begin{equation}
+\label{eqn:ptsyx}
+    p(t,s,y,x)
+    =
+    \frac{\varphi_s(x)}{\varphi_t(y)}
+    \IE_{s,x}\left[
+        \exp\left( \int_s^t (F + \gamma\DG r)(Y_u) du \right)
+        \ind_{Y_t=y}
+    \right]
+\qquad \text{ for } s < t.
+\end{equation}
+
+To make~(\ref{eqn:ptsyx}) meaningful, we multiply by suitable test functions
+$f$ and $g$ and integrate.
+\begin{align*}
+&\int \int f(y) \varphi_t(y) p(t,s,y,x) g(x) dy dx \\
+&\qquad =
+\int g(x) \varphi_s(x)
+\IE_{x,s}\left[
+    \exp\left(
+        \int_s^t(F+\gamma\DG r)(Y_u)du
+    \right)f(Y_t)
+\right] dx .
+\end{align*}
+
+Writing $\hat{T}_{t,s}$ for the time-inhomogeneous semigroup
+corresponding to the motion of ancestral lineages backwards in time
+(that is, $\hat{T}_{t,s} f(y) = \int p(t,s,x,y) f(x) dy$),
+we can write this as 
+$$
+    \int f(y)\varphi_t(y)\hat{T}_{t,s}g(y)dy
+    =
+    \int g(x) \varphi_s(x)
+        \IE_{s,x} \left[
+            \exp\left(
+                \int_s^t(F+\gamma\DG r)(Y_u)du
+            \right)f(Y_t)
+        \right]dx.
+$$
+Differentiating with respect to $t$ at $t=s$, and writing 
+$\Lgen_s$ for the generator of $\hat{T}_{t,s}$ at time $s$, we find
+\begin{align*}
+&
+    \int f(y) \left\{
+        \varphi_s(y) \Lgen_s g(y)
+        + \left(
+            r(y) \DG^*(\gamma \varphi_s)(y) + \varphi_s(y) F(y)
+        \right) g(y)
+    \right\} dy \\
+&\qquad =
+    \int g(x) \varphi_s(x) \left(
+        {\mathcal L}^Y_s f(x) + (F(x)+\gamma(x) \DG r(x)) f(x)
+    \right) dx \\
+&\qquad =
+    \int f(x) \left(
+        ({\mathcal L}^Y_s)^* (\varphi_s g)(x) + (F(x) + \gamma(x) \DG r(x)) \varphi_s(x) g(x)
+    \right) dx ,
+\end{align*}
+where $({\mathcal L}^Y_s)^*$ is the adjoint of ${\mathcal L}^Y_s$
+and we have used that $\varphi_s$ solves $\dot \varphi = r \DG^*(\gamma \varphi) + F \varphi$.
+Since $f$ was arbitrary,
+\begin{eqnarray*}
+\Lgen_s g
+    &=&
+    \frac{1}{\varphi_s} \left[
+        ({\mathcal L}^Y_s)^* (\varphi_s g)
+        + \gamma \varphi_s g \DG(r)
+        - r g \DG^*(\gamma \varphi_s)
+    \right] .
+\end{eqnarray*}
+(Note that the $\phi_s F g$ terms have cancelled.)
+Since the adjoint of ${\mathcal L}^Y_s$ is
+\begin{align*}
+    ({\mathcal L}^Y_s)^* f
+    &=
+    r \DG^* (\gamma f) - \gamma f \DG r ,
+\end{align*}
+we can rewrite the generator of a lineage as 
+\begin{eqnarray*}
+\Lgen_s g
+    &=&
+    \frac{r}{\varphi_s} \left[
+        \DG^* (\gamma \varphi_s g)
+        - g \DG^*(\gamma \varphi_s)
+    \right] .
+\end{eqnarray*}
+This is equation \eqref{eqn:lineage_generator}.
+
+To simplify to equation \eqref{eqn:lineage_generator2},
+this, first define
+$
+    \DD f(x) = \sum_{ij} \covq_{ij} \partial_{ij} f(x),
+$
+% and note that $\DD$ satisfies the following identity:
+% \begin{align}
+%     \DD(fg)
+%     &=
+%     f \DD g
+%     + 2 (\covq \grad f) \cdot \grad g
+%     + g \DD f .
+% \end{align}
+and so the adjoint of $\DD$ is
+$$
+    \DD^* f(x)
+    =
+    \sum_{ij} \partial_{ij} (\covq_{ij} f(x)) .
+$$
+Note that $\DD^*$ satisfies the following identity:
+\begin{align*}
+    \DD^*(fg)
+%     &=
+%     \sum_{ij} \left\{
+%         g \partial_{ij} (\covq_{ij} f)
+%         + 2 \partial_{i} (\covq_{ij} f) \partial_j(g)
+%         + \covq_{ij} f \partial_{ij} g
+%     \right\} \\
+    &=
+    \sum_{ij} \left\{
+        g \partial_{ij} (\covq_{ij} f)
+        + 2 f \partial_{i} (\covq_{ij}) \partial_j(g)
+        + 2 \covq_{ij} \partial_{i} (f) \partial_j(g)
+        + \covq_{ij} f \partial_{ij} g
+    \right\} \\
+    &=
+    g \DD^* f
+    + 2 f \vec{c} \cdot \grad g
+    + 2 (C \grad f) \cdot \grad g
+    + f \DD g ,
+\end{align*}
+where $\vec{c}_j = \sum_i \partial_j C_{ij}$.
+So, with $f = \gamma \varphi_s$,
+\begin{eqnarray*}
+\Lgen_s g
+    &=&
+    \frac{r}{\varphi_s} \left[
+        \DD^*(\gamma \varphi_s g) - \grad \cdot (\gamma \varphi_s g \meanq)
+        - g \DD^*(\gamma \varphi_s) + g \grad \cdot (\gamma \varphi_s \meanq)
+    \right] \\
+    &=&
+    \frac{r}{\varphi_s} \left[
+        \gamma \varphi_s \DD g
+        + 2 \gamma \varphi_s \vec{c} \cdot \grad g
+        + 2 (C \grad (\gamma \varphi_s)) \cdot \grad g
+        - \gamma \varphi_s \meanq \cdot \grad g
+    \right] \\
+    &=&
+    r \gamma \left[
+        \DD g
+        + 2 \vec{c} \cdot \grad g
+        + 2 (C \grad \log(\gamma \varphi_s)) \cdot \grad g
+        - \meanq \cdot \grad g
+    \right] ,
+\end{eqnarray*}
+which is equation \eqref{eqn:lineage_generator}.
+
+\end{proof}
+
+\begin{proof}[of Corollary \ref{cor:lineages_simple}]
+
+In this section, we need only
+simplify equation \eqref{eqn:lineage_generator}
+in the case where $\covq = \sigma^2 I$.
+
+    \comment{TODO}
+
+\end{proof}
+
+\begin{proof}[of Corollary~\ref{cor:wavefront}
+    \comment{
+        TODO make non-redundant with proof of Theorem \ref{thm:lineages}.
+    }
+
+Let $Y$ denote the diffusion followed by following a single descendent line in this frame; 
+i.e.~the diffusion with generator ${\cal L}^Y\phi=\gamma\Delta(r\phi)-\gamma\phi\Delta r -\mathfrak{c}\nabla\phi $.
+Note in particular here we take $\mathcal{B}=\Delta$.
+We start by expressing the evolution of a singles ancestry line in terms of the descendent line $Y$.
+
+Formally, the intensity of levels at $y$ at time $t$ that are descended from 
+individuals that were at $x$ at time $0$ is
+\begin{equation}
+\label{formal intensity}
+w(x)\IE_x\left[\exp\left(\int_0^t (F+\gamma \Delta r)(Y_s)ds\right)\ind_{Y_t=y}\right]dy,
+\end{equation}
+where the subscript $x$ in the expectation indicates that $Y_0=x$.
+To see why this should be true, 
+suppose that an ancestor has level $u$. Conditional on its 
+spatial motion $\{Y_s\}_{0\leq s\leq t}$, its level at time $t$ will
+be $u\exp(-\int_0^t(F+\gamma\Delta r)(Y_s)ds)$. This will be less than a given level 
+$N$ if $u<N \exp(\int_0^t(F+\gamma\Delta r)(Y_s)ds)$. 
+The intensity of levels at $y$ that are descended from individuals at
+$x$ can therefore be obtained as the limit as $N\to\infty$ of 
+$1/N$ times the number of levels at $x$ at time zero with
+$u<N \exp(\int_0^t(F+\gamma\Delta r)(Y_s)ds)$ and for which
+the corresponding individual is at $y$ at time $t$, which is 
+precisely the quantity in~(\ref{formal intensity}).
+
+It is easy to check that when we integrate~(\ref{formal intensity})
+with respect to $x$ we recover $w(y)dy$. 
+As a consequence of~(\ref{formal intensity}), writing $p(t,y,x)$ for
+the probability density that the ancestor $t$ units in 
+the past of an individual sampled 
+at $y$ was at $x$, then, still formally,
+\begin{equation}
+\label{ptyx}
+p(t,y,x)=\frac{w(x)}{w(y)}\IE_x\left[\exp\left(\int_0^t (F+\gamma\Delta r)(Y_s)ds\right)
+\ind_{Y_t=y}\right].
+\end{equation}
+
+To make~(\ref{ptyx}) meaningful, we multiply by suitable test functions and 
+integrate.
+$$\int\int \psi(y)w(y)p(t,y,x)\phi(x)dydx=\int\phi(x)w(x)
+\IE_x\left[\exp\left(\int_0^t(F+\gamma\Delta r)(Y_s)ds\right)\psi(Y_t)\right]dydx.$$
+
+Writing $\hat{T}_t$ for the semigroup corresponding to the motion of 
+ancestral lineages backwards in time (that is the semigroup corresponding
+to $p(t,x,y)$), we can write this as 
+$$\int \psi(y)w(y)\hat{T}_t\phi(y)dy=\int\phi(x)w(x)
+\IE_x\left[\exp\left(\int_0^t(F+\gamma\Delta r)(Y_s)ds\right)\psi(Y_t)\right]dx.$$
+Differentiating with respect to $t$ at $t=0$, and writing 
+$\hat{\mathcal L}$ for the generator of $\hat{T}_t$, we find
+\begin{eqnarray*}
+\int \psi(y)w(y)\widehat{\mathcal L}\phi(y)dy&=&
+\int\phi(x)w(x)\left({\mathcal L}^Y\psi(x)+\psi(x)(F+\gamma\Delta r)\psi(x)\right)dx\\
+&=&\int\phi(x)w(x)\left(\gamma\Delta(r\psi)-\gamma\psi\Delta r -\mathfrak{c}\nabla\psi 
++(F+\gamma\Delta r)(\psi)\right)dx\\
+&=&\int\phi(x)w(x)\left(\gamma\Delta(r\psi)-\mathfrak{c}\nabla\psi+F(\psi)\right)dx\\
+&=&
+\int\psi(x)\left[r\Delta(\gamma \phi w)+F\phi w+\mathfrak{c}\nabla(\phi w)\right]dx.
+\end{eqnarray*}
+Since $\psi$ was arbitrary,
+\begin{eqnarray*}
+\hat{\mathcal L}\phi&=&\frac{1}{w}\left[ r\Delta (\gamma\phi w)+F\phi w
++\mathfrak{c}\nabla(\phi w)\right]\\
+&=&\frac{\phi}{w}\left[r\Delta(\gamma w)+Fw+\mathfrak{c}\nabla w\right]
++\frac{1}{w}\left[r\gamma w\Delta \phi +2\nabla (\gamma w)
+\nabla\phi+\mathfrak{c}w\nabla\phi\right]\\
+&=&r\gamma\left(\Delta\phi+2\frac{\nabla(\gamma w)}{\gamma w}\nabla\phi\right)
++\mathfrak{c}\nabla\phi,
+\end{eqnarray*}
+where we have used that $w$ solves~(\ref{profile}).
+
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\appendix
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results on Lookdown Representations}
+    \label{sec: Markov Mapping Theorem Application}
+
+% % % % % % % % % % % % %
+\subsubsection{Convergence of generators for the lookdown process}
+    \label{sec:lookdown_generator_proofs}
+
+\comment{
+    I did this informal writeup of convergence of the lookdown generator
+    without looking at the previous version
+    mostly to double-check what we have there
+    (which is probably better).
+}
+
+In Definition~\ref{defn:lookdown_mgale} we saw that the generator
+of $(\lp_t)_{t \ge 0}$ is the sum of two parts,
+equations \eqref{eqn:birth_generator} and \eqref{eqn:level_generator}.
+Assume that there is a $u_*$ such that $g(x, u) = 1$ for all $u \ge u_*$.
+We consider these two in turn.
+
+First, the contribution from births is
+\begin{align*}
+\begin{split}
+f(\lp)
+&\mapsto
+    f(\lp)
+    \sum_{(x, u) \in \lp}
+    2 \gamma(x, \eta)
+    \bigg\{
+        \frac{1}{2 N}
+        \int_u^N
+        g(x, u_1) du_1
+        \frac{
+            \theta \int_{\IR^d} (g(y, u) - g(x, u)) r(y, \eta) q(x, dy)
+        }{
+            g(x, u)
+        }
+    \\ & \qquad \qquad \qquad {}
+        + \frac{\theta}{N}
+        \int_u^N \int_{\IR^d}
+        \left( \frac{g(y, u_1) + g(x, u_1)}{2} - 1 \right)
+        r(y, \eta) q(x, dy)
+    \bigg\}
+    .
+    \end{split}
+\end{align*}
+We have that
+\begin{align*}
+    &\theta \int_{\IR^d} (g(y, u) - g(x, u)) r(y, \eta) q(x, dy) \\
+    &\qquad =
+    \theta \int_{\IR^d} (r(y, \eta) g(y, u) - r(x, \eta) g(x, u)) q(x, dy)
+    - \theta \int_{\IR^d} g(x, u) (r(y, \eta) - r(x, \eta)) q(x, dy) \\
+    &\qquad \to
+    \DG(gr)(x) - g(x) \DG r(x) \qquad \text{as }N \to \infty.
+\end{align*}
+i.e., to
+$\DG\left(g(\cdot, u) r(\cdot, \smooth{r}\eta(\cdot))\right)(x)
+- g(\cdot, u) \DG\left(r(\cdot, \smooth{r}\eta(\cdot))\right)(x)$.
+Furthermore, by our assumption on $g$,
+$\int_u^N g(x, u_1) du_1 / N \to 1$ for all $x$ and $u$,
+so the first term here converges to
+\begin{align*}
+    \gamma(x, \eta)
+        \frac{
+            \DG\left( g(\cdot, u) r(\cdot, \smooth{r}\eta(\cdot))\right)(x)
+            -
+            g(\cdot, x) \DG\left( r(\cdot, \smooth{r}\eta(\cdot))\right)(x)
+        }{
+            g(x, u)
+        } .
+\end{align*}
+This corresponds to each particle moving according to the motion induced by
+$g \mapsto \gamma \DG(gr) - g \DG r$.
+\comment{TODO: explain the $r$-tilted $\DG$ motion somewhere earlier, introducing notation for it.}
+As for the second term,
+since $\int g(y, u_1) q(x, dy) \to g(x, u_1)$
+and $\theta/N \to \alpha$,
+it converges to
+\begin{align*}
+    2 \alpha
+    \gamma(x, \eta)
+    r(x, \eta) 
+    \int_u^\infty
+    \left( g(x, u_1) - 1 \right)
+    du_1
+\end{align*}
+This corresponds to births at higher levels at rate $2 \alpha \gamma r$.
+
+The remaining term is \eqref{eqn:level_generator}:
+\begin{align*}
+    f(\lp)
+    \mapsto
+    f(\lp)
+    \sum_{(x, u) \in \lp}
+    \left(
+    \theta
+        N^{-1} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
+        -
+        b(x, \eta)u
+    \right)
+    \frac{\partial_u g(x,u)}{g(x,u)} .
+\end{align*}
+The first part only uses the fact that $\theta/N \to \alpha$,
+while as noted in \eqref{eqn:b_limit}, $b$ converges to $\gamma \DG r + F$,
+so in total this term converges to
+\begin{align*}
+    f(\lp)
+    \mapsto
+    f(\lp)
+    \sum_{(x, u) \in \lp}
+    \left(
+    \alpha
+        \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
+        -
+        \left\{
+            \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta)
+        \right\} u
+    \right)
+    \frac{\partial_u g(x,u)}{g(x,u)} .
+\end{align*}
+In other words, the level of a particle at $x$ evolves according to
+\begin{align*}
+    \dot u
+    =
+    \alpha
+        \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
+        -
+        \left\{
+            \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta)
+        \right\} u .
+\end{align*}
+
+\subsection{Generators for the spatial processes}
+Before defining the generator of the lookdown representations, 
+we recall the generator of the spatial processes.
+
+We first define our pre-limit
+$(\eta^{N}(t))_{t>0}$ as a solution
+to a Martingale Problem
+with generator $\Pgen^{N}$.
+
+\begin{definition}
+    \label{def2: MP definition of pre-limit}
+Let $F \in \mathcal{C}^{2}(\IR)$ and $f \in \mathcal{C}_{0}(\IR^d)$.
+We define $\Pgen^N$ to be a generator
+acting on test functions of the form
+$F_f(\eta):=F (\langle f, \eta \rangle)$
+such that 
+\begin{equation}
+\begin{aligned}
+\Pgen^{N} F_f(\eta):=& \int_{\IR^d} \theta\gamma(x, \eta) \left\{\int_{\IR^d} \left\{F(\langle f, \eta \rangle + f(y)/N )-F(\langle f, \eta \rangle )\right\}r(y, \eta)q_{\theta}(x,dy)\right\}N\eta(dx)\\
+&+\int_{\IR^d} \theta \mu(x, \eta) \left\{F(\langle f, \eta \rangle - f(x)/N )-F(\langle f, \eta \rangle )\right\}N\eta(dx).
+\end{aligned}    
+\end{equation}
+In this case, our pre-limit model $(\eta^{N}(t))_{t \geq 0}$ is the solution to the Martingale Problem $(\Pgen^{N}, \eta_0)$, i.e. 
+for all $F \in \mathcal{C}^{2}(\IR)$
+and $f \in \mathcal{C}_{0}(\IR^d)$,
+$$M_t:=F_f(\eta^{N}_t)-F_f(\eta_0)
+-\int_{0}^{t}\Pgen^{N}F_f(\eta^{N}_s)ds$$
+is a martingale, and the initial condition is distributed as a Poisson measure with mean measure $\eta_0$.
+\end{definition}
+
+\begin{remark}
+Taking $F(x)=x$ and $F(x)=x^2$, we can recover Equation \eqref{eqn:limiting_mgale_problem} and \eqref{eqn:limiting_mgale_variation} for the limit.
+Similarly, we can recover
+Definition \ref{defn:mgale_construction},
+an equivalent characterisation
+of our pre-limit model.
+\end{remark}
+
+We now write the candidate generator for the limiting object.
+
+\begin{definition}
+    \label{def2: MP definition of limit}
+Let $F \in \mathcal{C}^{2}(\IR)$ and $f \in \mathcal{C}_{0}(\IR^d)$.
+We define $\Pgen$ to be a generator
+acting on test functions of the form
+$F_f(\eta):=F (\langle f, \eta \rangle)$
+such that 
+\begin{equation}
+    \label{eq: Limit Generator Definition}
+\begin{aligned}
+\Pgen^{\infty} F_f(\eta):=& F'(\langle f, \eta \rangle)
+                   \times \left\{
+                   \big\langle
+                        \gamma(x, \smooth{\gamma} \eta(x))
+                            \mathcal{B}\left(
+                            f(\cdot) r(\cdot, \smooth{r} \eta(\cdot))
+                            \right)(x)
+                    +
+                    f(x)
+                        F(x, \smooth{F} \eta(x)),
+                        \eta(dx)
+                    \big\rangle
+                   \right\}\\
+                &+ \alpha F''(\langle f, \eta \rangle)
+                  \times \left\{
+                  \big\langle
+                    \gamma \left( x, \eta \right)
+                    r\left(x,\eta \right)
+                    f^2(x),
+                    \eta (dx)
+                    \big\rangle 
+                  \right\}.
+\end{aligned}    
+\end{equation}
+We define $(\eta^{\infty}(t))_{t \geq 0}$ to be the solution to the Martingale Problem $(\Pgen^{\infty}, \eta_0)$, i.e. 
+for all $F \in \mathcal{C}^{2}(\IR)$
+and $f \in \mathcal{C}_{0}(\IR^d)$,
+$$M_t:=F_f(\eta^{\infty}_t)-F_f(\eta_0)
+-\int_{0}^{t}\Pgen^{\infty}F_f(\eta^{\infty}_s)ds$$
+is a martingale, with initial condition distributed as a Poisson measure with mean measure $\eta_0$.
+\end{definition}
+
+\subsubsection{Convergence of the Generators for the Spatial Models}
+
+Here, just as a sanity check, 
+we make sure that the limiting generator is indeed the limit of the generators.
+
+\begin{lemma}[Identifying the limit as a solution to the martingale problem]
+    \label{lem:limit_mgale}
+As $N \to \infty$,
+$(\eta^{N}_t)_{t \geq 0}$ converges in $\mathcal{D}_{[0,\infty)}(\mathcal{M}_f(\IR^d))$
+to $(\eta^{N}(t))_{t \geq 0}$.
+\end{lemma}
+\begin{proof}
+We use Theorem 4.8.10 in \cite{EK}.
+First of all, the set of functions
+$\{F_f(\eta):= F(\langle f, \eta \rangle ),~
+F \in \mathcal{C}^{2}(\IR), ~
+f \in \mathcal{C}_{0}(\IR^d)\}$
+is a dense and convergence-determining 
+subset of functions in $\mathcal{M}_f(\IR^d)$.
+Therefore, it suffices to show that for any $t>0$,
+\begin{equation}
+    \label{eq: Convergence Condition}
+\lim_{N \to \infty}
+\mathbb{E}\left[
+\left(
+F_f(\eta^{N}_{t+\tau})-F_f(\eta^{N}_t)
+-\int_{t}^{t+\tau}\Pgen^{\infty}F_f(\eta^{N}_s)ds
+\right)
+\prod_{i=1}^{k}\langle h_i,\eta^{N}_{t_i} \rangle
+\right]=0
+\end{equation}
+for all $k\geq 0$, $0\leq t_1<t_2<...,t_k \leq t < t+\tau$,
+and $h_1,...,h_k \in \mathcal{C}_{0}(\IR^d)$.
+
+To prove this,
+we make use of the Martingale Problem characterisation
+of $(\eta^{N}_t)_{t \geq 0}$.
+From Definition \ref{def: MP definition of pre-limit},
+we can apply Tower Law
+and obtain that
+\begin{equation}
+    \label{eq: Prelimit MP Application}
+\lim_{N \to \infty}
+\mathbb{E}\left[
+\left(
+F_f(\eta^{N}_{t+\tau})-F_f(\eta^{N}_t)
+-\int_{t}^{t+\tau}\Pgen^{N}F_f(\eta^{N}_s)ds
+\right)
+\prod_{i=1}^{k}\langle h_i,\eta^{N}_{t_i} \rangle
+\right]=0
+\end{equation}
+for all $k\geq 0$, $0\leq t_1<t_2<...,t_k \leq t < t+\tau$,
+and $h_1,...,h_k \in \mathcal{C}_{0}(\IR^d)$.
+
+Therefore, it suffices to show that 
+\begin{equation}
+    \label{eq: Convergence of Spatial Generator}
+\lim_{N \to \infty}
+\mathbb{E}\left[
+\int_{t}^{t+\tau}
+\left|
+\Pgen^{N}F_f(\eta^{N}_s)
+-\Pgen^{\infty}F_f(\eta^{N}_s)
+\right|
+ds
+\times 
+\prod_{i=1}^{k}\langle h_i,\eta^{N}_{t_i} \rangle
+\right]=0
+\end{equation}
+We apply Taylor Expansion
+around the term $F(\langle f, \eta \rangle )$
+up to third order.
+This gives
+\begin{equation}
+    \label{eq: Taylor Expansion calculations i}
+\begin{aligned}
+&F(\langle f, \eta \rangle + f(y)/N )-F(\langle f, \eta \rangle )\\
+=& F'(\langle f, \eta \rangle ) \frac{f(y)}{N}
++\frac{1}{2}F''(\langle f, \eta \rangle ) \frac{f^2(y)}{N^2}
++\frac{1}{6}F'''(w ) \frac{f^3(y)}{N^3}
+\end{aligned}
+\end{equation}
+for some $w \in [\langle f, \eta \rangle, \langle f, \eta \rangle+ ||f||/N]$.
+Similarly,
+\begin{equation}
+    \label{eq: Taylor Expansion calculations ii}
+\begin{aligned}
+&F(\langle f, \eta \rangle - f(x)/N )-F(\langle f, \eta \rangle )\\
+=& - F'(\langle f, \eta \rangle ) \frac{f(x)}{N}
++\frac{1}{2}F''(\langle f, \eta \rangle ) \frac{f^2(x)}{N^2}
+-\frac{1}{6}F'''(v ) \frac{f^3(x)}{N^3}
+\end{aligned}
+\end{equation}
+for some $v \in [\langle f, \eta \rangle - ||f||/N, \langle f, \eta \rangle ]$.
+
+We may now rewrite $\mathcal{P}^NF(\langle f, \eta \rangle)$ as 
+\small
+\begin{equation} 
+    \label{eq: Pre-Limit Generator Expanded}
+\begin{aligned}
+\Pgen^{N} F_f(\eta):=& F'(\langle f, \eta \rangle)\int_{\IR^d}  \theta\left\{\int_{\IR^d} \left\{f(y)\gamma(x, \eta) r(y,\eta) -f(x)\mu(x, \eta)\right\}q_{\theta}(x,dy)\right\}\eta(dx)\\
+&+\frac{1}{2}\frac{\theta}{N}F''(\langle f, \eta \rangle)\int_{\IR^d} 
+ \left\{\gamma(x, \eta)\int_{\IR^d} \left\{f^2(y) r(y,\eta) \right\}q_{\theta}(x,dy)+f^2(x)\mu(x, \eta)\right\}\eta(dx)\\
+&+\frac{1}{6}\frac{\theta}{N^2}\int_{\IR^d}\left\{ 
+F'''(w) \left\{\gamma(x, \eta)\int_{\IR^d} f^3(y) r(y,\eta) q_{\theta}(x,dy)\right\}-F'''(v)f^3(x)\mu(x, \eta)\right\}\eta(dx)
+\end{aligned}    
+\end{equation}
+\normalsize
+for some $w,v \in [\langle f,\eta \rangle - ||f||/N, \langle f,\eta \rangle + ||f||/N]$.
+
+As $N\to \infty$, 
+$\theta/N \to \alpha$, 
+$\theta/N^2 \to 0$,
+and 
+$$\int_{\IR^d} f^m(y) r(y,\eta) q_{\theta}(x,dy) \to f^m(x)r(x, \eta)$$
+for $m=2,3$,
+the third term in Equation \eqref{eq: Pre-Limit Generator Expanded} vanishes
+while the second term converges to
+that of Equation \eqref{eq: Limit Generator Definition}.
+Furthermore,
+$\mu(x,\eta) = r(x,\eta)\gamma(x,\eta)-\frac{1}{\theta}F(x,\eta) \to r(x,\eta)\gamma(x,\eta),$
+so $f^2(x)\mu(x,\eta) \to r(x,\eta)\gamma(x,\eta) f^2(x)$.
+
+Finally, by Equation \eqref{mean measure},
+\eqref{eqn:rewritten mean measure}, \eqref{eqn:near_critical} and
+\eqref{limit of mean measure equation},
+we have 
+\begin{multline}
+ \theta\left\{\int_{\IR^d} \left\{f(y)\gamma(x, \eta) r(y,\eta) -f(x)\mu(x, \eta)\right\}q_{\theta}(x,dy)\right\}
+ \\
+\to \gamma(x, \eta)                           \mathcal{B}\left(
+                            f(\cdot) r(\cdot, \eta)
+                            \right)(x)
+                    +
+                    f(x)
+                        F(x, \eta),
+\end{multline}
+so comparing terms we have
+\begin{equation}
+\lim_{N\to \infty} |\mathcal{P}^{N}F\langle f, \eta \rangle - \mathcal{P}^{\infty}F\langle f, \eta \rangle| \to 0,   
+\end{equation}
+and so by Dominated Convergence Theorem,
+we establish Equation 
+\eqref{eq: Convergence of Spatial Generator}
+which concludes our proof.
+\end{proof}
+
+\subsection{Generator of Lookdown Representations}
+
+We now define the generator of the lookdown representations.
+\begin{definition}[Martingale Problem Characterisation]
+    \label{defn:lookdown_mgale}
+For given positive values of $N$ and $\theta$
+and $\lp_0 \in \mathcal{M}_F(\IR^d \times [0,N])$,
+we define $(\lp^{N}_t)_{t \geq 0}$
+to be the unique solution to the martingale problem
+with initial condition $\lp_0$ and generator $A^{N}$ that satisfies
+\begin{equation*}
+\begin{split}
+& A^{N}f(\lp ) \\
+&\quad =
+    f(\lp)
+    \,\sum_{(x,u)\in \lp}\,
+    2 \gamma(x, \eta)
+    \Bigg\{ \frac{1}{2N} \int_u^N g(x,u_1) du_1
+            \frac{
+                \theta \int_{\IR^d}
+                (g(y,u) - g(x,u))
+                r(y, \eta) q_{\theta}(x,dy)
+            }{ g(x,u) }
+        \\
+    &\qquad\qquad\qquad\qquad\qquad\qquad\qquad {} +
+        \frac{\theta}{N} \int_u^N
+        \int_{\IR^d}\left(
+            \frac{ g(y,u_1) + g(x,u_1) }{ 2 } - 1
+        \right)
+        r(y, \eta) q_{\theta}(x,dy)
+        du_1
+    \Bigg\}\\
+    &\qquad\qquad {} +
+    f(\lp) \sum_{(x,u)\in\lp}\,
+    \left(
+        \frac{\theta}{N} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q_\theta(x, dy) u^2 -b_{\theta}(x,\eta)u
+    \right)
+    \frac{\partial_u g(x,u)}{g(x,u)}
+    ,
+\end{split}
+\end{equation*}
+for all smooth functions $g \in C^{2}_{0}(\IR^d)$,
+where $f(\lp) = \prod_{(x, u) \in \lp} g(x, u)$ as defined in \eqref{eqn:test_functions},
+and $\eta(\cdot) = \lp(\cdot \times [0, N]) / N$ is the scaled spatial pushforward of $\lp$,
+as before.
+\end{definition}
+
+Similarly, 
+we define the generator for the lookdown representation of the limiting spatial model.
+
+\begin{definition}[Martingale Problem Characterisation, $N=\infty$]
+    \label{defn:limiting_lookdown_mgale}
+    For a given value of $\alpha \in [0, \infty)$,
+    define the operator $A$ acting on test functions of the form
+    $f(\xi) = \prod_{(x, u) \in \xi} g(x, u)$ with $g \in C_0^2(\IR^d \times [0, \infty))$
+    and for which there exists a $u_0$ with $g(x, u) = 1$ for all $u > u_0$.
+    Then, let $A f$ be
+    \begin{equation}
+    \begin{aligned} \label{eqn:limiting_lookdown_generator}
+    A f(\lp)
+    =&
+        f(\lp)  \sum_{(x, u) \in \xi}
+        \gamma(x, \eta)
+            \frac{
+                \DG(g(\cdot, u) r(\cdot, \eta))(x) - g(x,u) \DG r(x,\eta)
+            }{
+                g(x, u)
+            }
+    \\ &+
+        f(\lp) \sum_{(x, u) \in \xi}
+        2 \alpha \gamma(x,\Xi)r(x,\Xi) \int_u^\infty (g(x, u_1) - 1) du_1
+    \\ &+
+        f(\lp) \sum_{(x, u) \in \xi}
+        \left(
+            \alpha \gamma(x,\Xi)r(x,\Xi) u^2
+            -
+            \left\{
+                \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta)
+            \right\} u
+        \right)
+        \frac{\partial_u g(x, u)}{ g(x,u) }  .
+    \end{aligned}
+    \end{equation}
+
+    We say that a $\lpmeasures$-valued process $(\xi_t)_{t \ge 0}$
+    is a solution to the $(A, \lp_0)$ martingale problem
+    if it has initial distribution $\lp_0$
+    and $f(\lp_t) - \int_0^t Af(\lp_s) ds$ is a martingale for all $f$
+    as defined above.
+\end{definition}
+
+\subsubsection{Exact Statement on Markov Mapping Theorem results}
+
+\begin{theorem}
+\label{teo: lookdown on pre-limit well defined}
+For each $N \in \mathbb{N}$,
+there exists a solution $(\lp^N_t)_{t \geq 0}$ to the $(A^N, \lp^N_0)$ martingale problem.
+Furthermore, if we define $\Xi^N_t = \frac{1}{N}\lp^N_t(dx \times [0,N])$ for $t \geq 0$,
+then the pre-limiting model $(\eta^N_t(dx))_{t \geq 0}$ defined in Definition \ref{defn:mgale_construction}
+and $(\Xi^N_t(dx))_{t \geq 0}$
+shares the same distribution on $\mathcal{D}_{\mathcal{M}(\mathbb{R}^d)}[0,\infty)$.
+
+Finally, 
+for all $h\in \mathcal{C}(\mathbb{R}^d \times [0, N])$
+\begin{equation}\label{Markov Mapping Theorem Cox Condition}
+\mathbb{E}\left[e^{-\int_{\mathbb{R}^d \times [0,N]} h(x,u) \xi^{N}(dx \times du)}\bigg| \mathcal{F}^{\Xi^{N}}_t\right]=e^{-\int F^{N}_h(x) \Xi^{N}_t(dx)},
+\end{equation}
+where 
+$$F^{\epsilon,\theta,N}_h(x):=-N\log \left(\frac{1}{N}\int_{0}^{N}e^{-h(x,u)}du\right)=-N\log \left(1-\frac{1}{N}\int_{0}^{N}(1-e^{-h(x,u)})du\right).$$
+In other words,
+conditioned on the spatial configuration $\Xi^N_t$,
+the levels of the particles must be i.i.d uniformly between $[0,N]$.
+
+\end{theorem}
+
+The statement for the limiting case is similar,
+with the only difference being the conditional distribution 
+of the levels given the spatial projection.
+
+\begin{theorem}
+\label{teo: lookdown on limit well defined}
+There exists a solution $(\lp_t)_{t \geq 0}$ to the $(A, \lp_0)$ martingale problem.
+
+Furthermore, if we define $\Xi_t = \lim_{u_0 \to \infty} \frac{1}{u_0}\lp_t(dx \times [0,u_0])$,
+then the limit model $(\eta_t(dx))_{t \geq 0}$ defined in Theorem \label{thm:nonlocal_convergence}
+and $(\Xi_t(dx))_{t \geq 0}$
+shares the same distribution on $\mathcal{D}_{\mathcal{M}(\mathbb{R}^d)}[0,\infty)$.
+
+Finally, 
+for all $h\in \mathcal{C}(\mathbb{R}^d)$ and for all $K>0$,
+\begin{equation}\label{Markov Mapping Theorem Cox Condition limit}
+\mathbb{E}\left[e^{-\int_{\mathbb{R}^d \times [0,K]} h(x) \xi(dx \times du)}\bigg| \mathcal{F}^{\Xi}_t\right]=e^{- K \int_{\mathbb{R^d}}(1-e^{h(x)}) \Xi_t(dx)}.
+\end{equation}
+In other words,
+conditionally on $(\Xi_s)_{0\leq s \leq t}$
+for each $s \in[0,t]$,
+$\xi_s$ is conditionally Poisson with Cox measure $\Xi_s(dx) \times du$.
+\end{theorem}
+
+\subsection{Markov Mapping Theorem Application on Generator $A^{N}$}\label{sec: Markov Mapping Theorem Application - Prelimit}
+
+We now introduce some notations to simplify our calculations.
+For a finite atomic measure $\xi=\sum \delta_{(x_i,u_i)} \in \mathcal{M}(\mathbb{R}^d \times [0,N])$,
+we introduce the test functions
+ $$f_g(\xi)= \prod_{(x_i,u_i)\in \xi} g(x_i,u_i) = \exp (\langle \log g, \xi \rangle),$$
+ where $g \in \mathcal{C}(\mathbb{R}^d \times [0,\infty))$ and $g(x,u)=1$ for all $u \geq N$.
+
+ To avoid any ambiguities in the proofs,
+ we will strictly use the notation $\Xi^N$  
+to represent the scaled push-forward measure of $\lp$,
+i.e. $\Xi^N := \frac{1}{N}\sum_{(x,u) \in \lp} \delta_x$,
+and only use $(\eta^N_t)_{t \geq 0}$
+to refer to the PDE solutions defined in Definition  \ref{defn:mgale_construction}.
+
+We also write $\textbf{x}=(x_1,x_2,...), \textbf{u}=(u_1,u_2,...)$ to be the collections of particles locations and levels respectively.
+With this notation we will write $f_g(\xi), f_g(\textbf{x},\textbf{u})$ interchangeably.
+
+We write $\Gamma^N (d\textbf{u})$ as the probability kernel
+that corresponds to assigning each particle an i.i.d. uniform $[0,N]$-level, i.e.
+$$\int f_g(\textbf{x},\textbf{u})\Gamma^N (d\textbf{u})=\frac{1}{N^{|\xi|}}\int_{[0,N]^{|\xi|}}f_g(\textbf{x},\textbf{u})d\textbf{u},$$
+and we denote
+$$\hat{g}(x):=\frac{1}{N}\int_{0}^{N}g(x,u)du,
+ ~~\hat{f}_g(\xi)=\int f_g(\xi) \Gamma (d\textbf{u})$$ 
+to be the spatial test functions with averaged level.
+By independence of the levels of the particles,
+ we have that
+ \begin{align*}
+\hat{f}_g(\xi)
+=&\int \prod_{(x,u) \in \xi}g(x,u) \Gamma(d\textbf{u})\\
+=&\prod_{(x,u)\in \xi}\frac{1}{N}\int_{0}^{N} g(x,u) du\\
+=&\prod_{(x_i,u_i)\in \xi }\hat{g}(x_i)\\
+=& \exp(N\log \hat{g},\Xi^N).
+ \end{align*}
+
+Furthermore,
+when expressed as a function of $\Xi^N$ explicitly,
+we use the notation $F_{\hat{g},N}(\Xi^N):=\hat{f}_g(\xi)$.
+
+We will now apply Markov Mapping Theorem
+while keeping notations consistent to that introduced in Section A.5 in \cite{kurtz/rodrigues:2011}
+with the aid of Table \ref{Markov Mapping Theorem Notation Table}.
+\begin{table}[!h]
+    \centering
+    \begin{tabular}{c|c}
+    Notation in \cite{kurtz/rodrigues:2011} & Notation in this proof \\
+    \hline\\
+      $S$   &  $\mathcal{M}(\IR^d \times [0, N])$\\\\
+       $S_0$  &  $\mathcal{M}(\IR^d)$\\\\
+       $A$ & $A^{N}$\\\\
+       $(X_t)_{t \geq 0}$ & $(\xi^N_t)_{t \geq 0}$\\\\
+       $\mu_0$ & $\eta^N_0 \in \mathcal{M}(\IR^d)$\\\\
+       $\nu_0$ & $\xi^N_0 \in \mathcal{M}(\IR^d \times [0,N])$\\\\
+       $f(\xi)$ & $f_g(\xi) := \prod_{(x,u) \in \xi} g(x,u)$\\\\
+        $\gamma_M$ & $ \mathcal{M}(\IR^d \times [0, N]) \ni \xi \to \frac{1}{N}\sum_{(x,u) \in \lp(\cdot, [0,N))} \delta_{x} \in \mathcal{M}(\IR^d)$\\\\
+       $\alpha_M$ & $ \alpha_M(\Xi^N,d \lp) =     \begin{cases}
+      0 & \text{if } \frac{1}{N}\sum_{(x,u) \in \lp(\cdot, [0,N))} \delta_x \neq \Xi^N\\
+       \prod_{(u_i,x_i) \in \nu} \frac{1}{N} \ind_{[0,N]}du_i & \text{if } \frac{1}{N}\sum_{(x,u) \in \lp(\cdot, [0,N))} \delta_x = \Xi^N,\\
+    \end{cases} $\\
+&      where $du_i$ is the standard Lebesgue measure.
+    \end{tabular}
+    \caption{Markov Mapping Theorem Correspondence}
+    \label{Markov Mapping Theorem Notation Table}
+\end{table}
+
+\begin{remark}
+Note that $\gamma,\alpha$ in \cite{kurtz/rodrigues:2011}
+is replaced with $\gamma_M,\alpha_M$ to avoid confusion with the $\gamma, \alpha$ used in previous sections.
+\end{remark}
+
+First of all,
+note that $\gamma_M$ is Borel-measurable
+and $\alpha_M$ is a transition function from $\mathcal{M}(\IR^d \times [0, N))$ to $\mathcal{M}(\IR^d)$.
+
+More importantly, we have the following simplified expression
+for an integral against $\alpha_M$:
+\begin{equation}
+\int_{\mathcal{M}(\IR^d\times [0,N])}A^{N}f(\xi)\alpha_M(\Xi^N, d\lp)
+= \int   A^Nf(\textbf{x},\textbf{u})\Gamma^N(d\textbf{u}). 
+\end{equation}
+
+As a result, we can establish that
+\begin{equation}
+\begin{aligned}
+\alpha_M(\Xi^N,\gamma^{-1}(\Xi^N)) 
+&= \int_{\lp \in \gamma^{-1}(y)}\alpha_M (\Xi^N, d\lp) \\
+&= \int_{\{\lp: \sum_{(x,u) \in \lp }\delta_x = N\Xi^N \} }\alpha_M (\Xi^N, d\lp)\\
+&= \prod_{x_i \in N\Xi^N}\frac{1}{N}\int_{0}^{N} du_i =1
+\end{aligned}
+\end{equation}
+With the simplified integral, it now suffices to show that the Martingale Problem 
+\begin{equation}\label{Markov Mapping Theorem Martingale Condition Simplified}
+C = \left\{\left(\int   f(\textbf{x},\textbf{u})\Gamma^N(d\textbf{u}),\int   A^Nf(\textbf{x},\textbf{u})\Gamma^N(d\textbf{u})\right)\right\}    
+\end{equation}
+has a solution.
+
+We now claim the following lemma.
+
+\begin{lemma}
+\label{lem: representation of lookdown generator - pre-limit}
+Let $\xi$ be a finite atomic measure on $\mathbb{R}^d \times [0,N]$.
+For test functions of the form 
+$$f_g(\xi)= \prod_{(x_i,u_i)\in \xi} g(x_i,u_i) = \exp (\langle \log g, \xi \rangle),$$
+we have the equality
+\begin{equation}
+\int   A^Nf(\textbf{x},\textbf{u})\Gamma^N(d\textbf{u})
+= \int \Pgen^N F_{\hat{g},N}(\Xi^N),
+\end{equation}
+where $\Pgen^N$ is the generator of the spatial process defined in Definition \ref{def2: MP definition of pre-limit}.
+ \end{lemma}
+
+With lemma \ref{lem: representation of lookdown generator - pre-limit},
+the martingale problem can then be re-written as 
+\begin{equation}\label{Markov Mapping Theorem Martingale Condition, projection form}
+C = \left\{\left(\int F_{\hat{g},N}(\Xi^N), \int \Pgen^N F_{\hat{g},N}(\Xi^N)\right)\right\}    
+\end{equation}
+which has $(\eta^N_t)_{t \geq 0}$,
+our spatial population process,
+as a solution.
+
+As a result,
+we can apply Markov Mapping Theorem to establish the following statements:
+\begin{enumerate}
+    \item There exists a $\mathcal{M}_F(\mathbb{R}^d\times[0,N])$-valued process $(\lp^N_t)_{t \geq 0}$
+    such that 
+    $M^N_t:=    f(\xi^N_t)-   f(\xi^N_0)-\int_{0}^{t}  A^Nf(\xi^N_s)ds$ is a martingale for all $f\in D(A^N)$,
+    \item The process $(\gamma_M \circ \xi^N_t)_{t \geq 0}= \left(\Xi^N_t\right)_{t \geq 0}$ 
+    has the same distribution in $\mathcal{D}_{\mathcal{M}(\mathbb{R}^d)}[0,\infty)$ as $(\eta^N_t)_{t \geq 0}$ defined in Definition \ref{def: MP definition of pre-limit}.
+    \item $\mathbb{P}\{\xi^N_t \in B | \mathcal{F}^{\Xi^N}_t\}=\alpha_M(\Xi^N(t),B), ~~~B \in \mathcal{B}(\mathcal{M}(\IR^d \times [0,N])).$
+\end{enumerate}
+Note that in particular,
+from the third statement,
+we can establish that for $h(x,u) \in \mathcal{C}_{c}(\mathbb{R}^d \times[0,N])$ and $h \geq 0$,
+
+\begin{equation}\label{Markov Mapping Theorem Cox Condition}
+\begin{aligned}
+\mathbb{E}\left[e^{-\int_{S \times [0,N]} h(x,u) \xi^{N}(dx \times du)}\bigg| \mathcal{F}^{\Xi^{N}}_t\right]
+&=\mathbb{E}\left[\prod_{(x,u)\in\xi^N_t}e^{-h(x,u)}\bigg| \mathcal{F}^{\Xi^{N}}_t\right]\\
+&=\prod_{x \in N\Xi^N_t} \frac{1}{N} \int_{0}^N. e^{-h(x_i,u_i)} du_i
+&= e^{-\langle F^N_h(x), \Xi^N(dx)\rangle},
+\end{aligned}
+\end{equation}
+where 
+$$F^{N}_h(x):=-N\log \left(\frac{1}{N}\int_{0}^{N}e^{-h(x,u)}du\right)=-N\log \left(1-\frac{1}{N}\int_{0}^{N}(1-e^{-h(x,u)})du\right).$$
+
+Therefore we only need to prove lemma \ref{lem: representation of lookdown generator - pre-limit}.
+The procedure to prove Lemman \ref{lem: representation of lookdown generator - pre-limit}
+is rather standard and set out in \cite{kurtz/rodrigues:2011},
+albeit we will face more technicalities for this setting.
+
+For tidy computations in this proof, 
+we recall the notation that an individual at $x$ gives birth at rate
+$$
+    \gamma^{\mathfrak{m}}_{\theta}(x,\eta) := \theta \gamma(x, \smooth{\gamma} \eta(x))
+    \int r(y, \smooth{r} \eta(y)) q_{\theta}(x, dy) ,
+$$
+and that offspring disperse according to the kernel
+$$
+    q_\theta^\mathfrak{m}(x,\eta,  dy)
+    :=
+    \frac{
+        r(y, \smooth{r} \eta(y)) q_\theta(x, dy)
+    }{
+        \int r(z, \smooth{r} \eta(z)) q_\theta(x, dz)
+    } .
+$$
+
+We will also write $\Xi, \Gamma$ instead of $\Xi^N, \Gamma^N$,
+bearing in mind the dependence of $\Xi, \Gamma$ on $N$.
+
+\begin{proof}[Proof to Lemma \ref{lem: representation of lookdown generator - pre-limit}]
+
+Recall that the lookdown generator of our spatial-level process satisfies
+\begin{align}
+A^Nf(\xi)=&
+f(\xi)\sum_{(x,u)\in\xi}2N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\times
+\int_u^{
+N}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\IR^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\theta}(x,\Xi ,dy) \nonumber \\
+& \qquad \qquad \qquad \qquad +\int_{\IR^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\theta}(x,\Xi,dy)\Bigg)dv_1 \nonumber\\
+&+f(\xi )\sum_{(x,u)\in\xi}\,\left(N^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)},
+\end{align}
+where $f(\xi) =\prod_{(x,u) \in \xi}g(x,u)$.
+
+For easier computation,
+we break the generator into three parts, 
+\begin{equation}
+\begin{aligned}
+A^N_1f(\xi)=&f(\xi)\sum_{(x,u)\in\xi}2N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\times
+\int_u^{
+N}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\IR^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\theta}(x,\Xi ,dy)\Bigg)dv_1,\\
+A^N_2f(\xi)=&f(\xi)\sum_{(x,u)\in\xi}2N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\times
+\int_u^{
+N}\Bigg(\frac{1}{2}\int_{\IR^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\theta}(x,\Xi,dy)\Bigg)dv_1,\\
+A^N_3f(\xi)=&f(\xi )\sum_{(x,u)\in\xi}\,\left(N^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)},
+\end{aligned}
+\end{equation}
+such that 
+$$A^Nf(\xi)=A^N_1f(\xi)+A^N_2f(\xi)+A^N_3f(\xi).$$
+
+We now calculate each generator evaluated under our probability kernel $\Gamma$.
+\footnotesize 
+\begin{align*}
+&\int A^N_1f(\xi) \Gamma(d\mathbf{u})\\ &=\int \Bigg\{f(\xi)\sum_{(x,u)\in\xi}2N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)
+\int_u^{
+N}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\IR^d}(g(y,u)-g(x,u))q^{\mathfrak{m}}_{\theta}(x,\Xi ,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
+&=\sum_{(x,u)\in\xi} \int \Bigg\{\frac{f(\xi)}{g(x,u)}2N^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi)
+\int_u^{
+N}\Bigg(\frac 12 g(x,v_1)\int_{\IR^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\theta}(x,\Xi ,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
+&=\sum_{(x,u)\in\xi}N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{N}\int_{0}^{N}\left\{
+\int_u^{
+N} g(x,v_1)dv_1\times \int_{\IR^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\theta}(x,\Xi ,dy)\right\}du\\
+&=\sum_{(x,u)\in\xi}N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{N}\int_{\IR^d} \left\{\int_{0}^{N}
+\int_u^{
+N} g(x,v_1) (g(y,u)-g(x,u))dv_1du\right\}q^{\mathfrak{m}}_{\theta}(x,\Xi ,dy)
+\end{align*}
+
+\normalsize
+For the second generator, we have
+\footnotesize
+\begin{align*}
+&\int A^N_2f(\xi) \Gamma(d\mathbf{u})\\&=\int \Bigg\{f(\xi)\sum_{(x,u)\in\xi}2N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\times
+\int_u^{
+N}\Bigg(\int_{\IR^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\theta}(x,\Xi,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
+&=\sum_{(x,u)\in\xi}N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\int \Bigg\{f(\xi)\times
+\int_u^{
+N}\Bigg(\int_{\IR^d}\left(g(y,v_1)+g(x,v_1)-2\right)q^{\mathfrak{m}}_{\theta}(x,\Xi,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
+&=\sum_{(x,u)\in\xi}N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i) \frac{1}{N}\int_{\IR^d}\Bigg\{\int_{0}^{N}
+\int_u^{
+N}g(x,u) \left(g(y,v_1)+g(x,v_1)-2\right)dv_1 du\Bigg\} q^{\mathfrak{m}}_{\theta}(x,\Xi,dy).
+\end{align*}
+
+\normalsize
+For the third generator we have that 
+\begin{align*}
+ &\int A^N_3f(\xi)\Gamma(d\mathbf{u})\\
+ =&\int f(\xi )\,\left(N^{-1} \sum_{(x,u)\in\xi}\theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)}\Gamma(d\mathbf{u}) \\
+ =&\sum_{(x,u)\in\xi}\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{N}\int_{0}^{N}  \left(N^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\partial_u g(x,u)du \\
+ =&-\sum_{(x,u)\in\xi}\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{N}\int_{0}^{N}  \left(2uN^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) -b_{\theta}(x,\Xi)\right)\left(g(x,u)-1\right)du \\
+ =&-\sum_{(x,u)\in\xi}N^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{N}\int_{0}^{N}   2ug(x,u)du \\
+ &+\sum_{(x,u)\in\xi}N^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{N}\times N^2+\sum_{(x,u)\in\xi}\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)b_{\theta}(x,\Xi)(\hat{g}(x)-1)
+\end{align*}
+
+By symmetry, we have
+\begin{align*}
+&\int_{0}^{N}
+\int_u^{
+N} g(x,v_1) (g(y,u)-g(x,u))dv_1du+\int_{0}^{N}
+\int_u^{
+N}g(x,u) \left(g(y,v_1)+g(x,v_1)-2\right)dv_1 du
+\\&= \int_{0}^{N}
+\int_u^{
+N}g(x,u)g(y,v_1)+g(y,u)g(x,v_1)-2g(x,u) dv_1 du\\
+&=\frac{1}{2}\int_{0}^{N}\int_{0}^{N}g(x,u)g(y,v_1)+g(y,u)g(x,v_1)dv_1 du - 2 \int_{0}^{N}(N-u)g(x,u)du\\
+&=N^2 \hat{g}(x)\hat{g}(y) -2N^2 \hat{g}(x)+2\int_{0}^{N}ug(x,u)du.
+\end{align*}
+
+Combining the last equations,
+we have 
+\begin{align*}
+&\int \Bigg(A^N_1f(\xi)+A^N_2f(\xi)+A^N_3f(\xi)\Bigg)\Gamma(d\mathbf{u})\\
+=&  \sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)}\hat{g}(x_i) \left( \int_{\IR^n} \hat{g}(y) q^{\mathfrak{m}}_{\theta}(x,\Xi,dy) - 2+\frac{1}{\hat{g}(x)}\right)\\
+&+\sum_{(x,u) \in \xi } \prod_{(x_i,u_i)}\hat{g}(x_i)b_{\theta}(x,\Xi)\left(1-\frac{1}{\hat{g}(x)}\right)\\
+=&  \hat{f}(\xi)\sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi) \left(\int_{\IR^n} \hat{g}(y) q^{\mathfrak{m}}_{\theta}(x,\Xi,dy) -1\right)\\
+&+\hat{f}(\xi)\sum_{(x,u) \in \xi } (b_{\theta}(x,\Xi)-\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi))\left(1-\frac{1}{\hat{g}(x)}\right)\\
+=&  F_{\hat{g},N}(\Xi^N)\sum_{x \in \Xi}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi) \left(\int_{\IR^n} \hat{g}(y) q^{\mathfrak{m}}_{\theta}(x,\Xi,dy) -1\right) \\
+&-F_{\hat{g},N}(\Xi^N)\sum_{x \in \Xi } \theta \mu_{\epsilon,\theta}(x,\Xi)\left(1-\frac{1}{\hat{g}(x)}\right)\\
+=& \Pgen^N F_{\hat{g},N}(\Xi^N).
+\end{align*}
+
+The last equality holds
+as the second last expression corresponds to a spatial-branching process
+that branches at rate $\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)$,
+leaving offspring around with kernel $ q^{\mathfrak{m}}_{\theta}(x,\Xi,dy)$,
+with each particle having death rate given by $\theta \mu_{\epsilon,\theta}(x,\Xi)$.
+This is precisely the martingale problem in Definition \ref{def: MP definition of pre-limit}.
+
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%
+\subsection{Markov Mapping Theorem Application on Generator $A$}\label{sec: Markov Mapping Theorem application - limit}
+
+Now,
+we turn to the generator for the limiting case,
+which has the form
+    \begin{equation}
+    \begin{aligned}
+    A f(\lp)
+    =&
+        f(\lp)  \sum_{(x, u) \in \xi}
+        \gamma(x, \eta)
+            \frac{
+                \DG(g(\cdot, u) r(\cdot, \eta))(x) - g(x,u) \DG r(x,\eta)
+            }{
+                g(x, u)
+            }
+    \\ &+
+        f(\lp) \sum_{(x, u) \in \xi}
+        2 \alpha \gamma(x, \Xi) r(x, \Xi ) \int_u^\infty (g(x, u_1) - 1) du_1
+    \\ &+
+        f(\lp) \sum_{(x, u) \in \xi}
+        \left(
+            \alpha \gamma(x, \Xi) r(x, \Xi ) u^2
+            -
+            \left\{
+                \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta)
+            \right\} u
+        \right)
+        \frac{\partial_u g(x, u)}{ g(x,u) }  .
+    \end{aligned}
+    \end{equation}
+
+To apply Markov Mapping Theorem,
+we consider Table \ref{Markov Mapping Theorem Notation Table Limit}.
+
+\begin{table}[!h]
+    \centering
+    \begin{tabular}{c|c}
+    Notation in \cite{kurtz/rodrigues:2011} & Notation in this proof \\
+    \hline\\
+      $S$   &  $\mathcal{M}(\IR^d \times [0, \infty])$\\\\
+       $S_0$  &  $\mathcal{M}(\IR^d)$\\\\
+       $A$ & $A$\\\\
+       $(X_t)_{t \geq 0}$ & $(\xi_t)_{t \geq 0}$\\\\
+       $\mu_0$ & $\xi_0 \in \mathcal{M}(\IR^d)$\\\\
+       $\nu_0$ & $\xi_0 \in \mathcal{M}(\IR^d \times [0,\infty])$\\\\
+       $f(\xi)$ & $f_g(\xi) := \prod_{(x,u) \in \xi} g(x,u)$\\\\
+        $\gamma_M$ & $ \mathcal{M}(\IR^d \times [0, \infty]) \ni \xi \to \lim_{u_0 \to \infty}\frac{1}{u_0}\sum_{(x,u) \in \lp(\cdot, [0,u_0))} \delta_{x} \in \mathcal{M}(\IR^d)$\\\\
+       $\alpha_M$ & $ \Gamma^M(\Xi,d \lp) \sim PP(\Xi(dx)\times \Lambda(du)) ~~ \text{if } \gamma_M(\xi)=\Xi$,\\
+       &      where $\Lambda(du)$ is the standard Lebesgue measure on $[0,\infty)$.
+    \end{tabular}
+    \caption{Markov Mapping Theorem Correspondence}
+    \label{Markov Mapping Theorem Notation Table Limit}
+\end{table}
+
+Once again,
+we need to find solutions to the Martingale Problem 
+\begin{equation}
+C = \left(\int f_g(\xi) \Gamma^M(\cdot, d\xi), \int Af_g(\xi) \Gamma^M(\cdot, d\xi))\right),
+\end{equation}
+where $\Gamma^M(\Xi, d\lp)$ is the law of $\xi$,
+which is conditionally Poisson with Cox measure $\Xi(dx) \times \Lambda(du)$.
+
+Since we impose that $\xi$ is conditionally Poisson with Cox measure $\Xi(dx) \times \Lambda(du)$,
+for any test function $l(x,u) > 0$,
+\begin{equation}
+\mathbb{E}\left[e^{-\int_{\mathbb{R}^d \times [0,\infty]} l(x,u) \xi(dx,du)}\big| \Xi \right] = e^{-\int_{\mathbb{R}^d} \int_{0}^{\infty} (1-e^{-l(x,u)}) du \Xi(dx)}.
+\end{equation}
+
+Note that 
+$\prod_{(x,u) \in \xi} g(x,u) = e^{-\int_{\mathbb{R}^d \times [0,\infty]} -\log g(x,u) \xi(dx,du)},$
+so taking $l(x,u)= -\log g(x,u)$ and $h(x,u)= \int_{0}^{\infty} (1 -g(x,u))du$,
+we have the equation
+\begin{equation}
+\begin{aligned}
+\int f_g(\xi) \alpha_M(\Xi, d\xi) 
+=&  e^{-\int_{\mathbb{R}^d} \int_{0}^{\infty} (1-e^{-l(x,u)}) du \Xi(dx)}\\
+=&  e^{-\int_{\mathbb{R}^d} \int_{0}^{\infty} (1-g(x,u)) du \Xi(dx)}\\
+=& \exp(\langle -h(x), \Xi(dx)\rangle),
+\end{aligned}
+\end{equation}
+and we will denote the last term as $\mathcal{E}_{-h}(\Xi)$.
+Note that this notation is consistent to the test function
+$F_f(\eta)$ laid out in \ref{def: MP definition of limit},
+if we take $F(\cdot)=\mathcal{E}(\cdot) := \exp(\cdot)$ and $f=-h$.
+
+We now state the crucial lemma that allows us to apply Markov Mapping Theorem.
+\begin{lemma}
+\label{lem: MMT for limit}
+Let $\lp$ be a finite measure on $\mathbb{R}^d \times [0,\infty)$,
+$\Xi$ be a finite measure on $\mathbb{R}^d$,
+and $\Lambda(dx)$ be the Lesbesgue measure on  $[0,\infty)$.
+
+We consider test functions 
+$f(\xi):= \prod_{(x_i,u_i) \in \xi} g(x_i,u_i)$
+with $g \in C^2_{0}(\mathbb{R}^d \times[0,\infty))$
+and for which there exists $u_0$ with 
+$g(x,u)=1$ for all $u>u_0$.
+Furthermore, we define 
+$h(x,u)= \int_{0}^{\infty} (1 -g(x,u))du$
+and $\mathcal{E}_{-h}(\Xi)= \exp(\langle -h(x), \Xi(dx)\rangle)$.
+
+We write $\Gamma^{\Xi}(d\lp)$ to be the law
+on $\mathcal{M}(\mathbb{R}^d \times[0,\infty))$ 
+for a conditionally Poisson random measure $\lp$
+on $\IR^d\times [0,\infty)$
+with Cox measure $\Xi(dx)\times \Lambda(du)$.
+
+Then,
+for generator $A$ defined in Equation \eqref{eqn:limiting_lookdown_generator},
+\begin{equation}
+\int Af(\lp) \Gamma^{\Xi}(d\lp) = \Pgen \mathcal{E}_{-h}(\Xi),
+\end{equation}
+where $\Pgen$ is defined in Definition \ref{def2: MP definition of limit}.
+\end{lemma}
+
+Given the above lemma, 
+the following three statements hold true.
+\begin{enumerate}
+    \item There exists a $\mathcal{M}_F(\mathbb{R}^d\times[0,\infty])$-valued process $(\lp_t)_{t \geq 0}$
+    such that 
+    $M_t:=    f(\xi_t)-   f(\xi_0)-\int_{0}^{t}  Af(\xi_s)ds$ is a martingale for all $f\in D(A)$,
+    \item The process $(\gamma_M \circ \xi_t)_{t \geq 0}= \left( \lim_{u_0 \to \infty}\frac{1}{u_0}\sum_{(x,u) \in \lp_t(\cdot, [0,u_0))} \delta_{x} \right)_{t \geq 0}$ 
+    has the same distribution in $\mathcal{D}_{\mathcal{M}(\mathbb{R}^d)}[0,\infty)$ as $(\eta_t)_{t \geq 0}$ defined in Definition \ref{def: MP definition of limit}.
+    \item $\mathbb{P}\{\xi_t \in B | \mathcal{F}^{\Xi_t}\}=\Gamma^{\Xi_t}(B), ~~~B \in \mathcal{B}(\mathcal{M}(\IR^d \times [0,\infty])).$
+\end{enumerate}
+
+Finally,
+we recall an important equality for conditionally Poisson point processes (\cite{kurtz/rodrigues:2011} Lemma A.3.)
+which will be used extensively in the upcoming proof.
+
+\begin{lemma}
+Let $\lp =\sum_{i}\delta_{Z_i}$ be a Poisson random measure with mean measure $\nu$, 
+then for $\ell \in L^{1}(\nu)$ and $g\geq0$ with $\log g \in L^{1}(\nu)$,
+\begin{equation}
+\mathbb{E}[\sum_{j} \ell(Z_j) \prod_{i}g(Z_i)] = \int \ell g d\nu e^{\int (g-1) d \nu}.
+\end{equation}
+\end{lemma}
+
+In particular,
+taking $\nu(dx,du)=\Xi(dx) \times \Lambda(du)$,
+we have the equation 
+\begin{equation}
+\label{eq: cond_poi_sum_prod}
+\begin{aligned}
+\int f(\xi) \sum_{(x,u)\in \xi} \ell(x,u)\Gamma^{\Xi}(d\xi)
+=& \mathbb{E}_{\xi \sim PP(\Xi \times \Lambda)}\left[\sum_{(x_j,u_j)\in \xi} \ell(x_j,u_j) \prod_{(x_i,u_i) \in \xi}g(x_i,u_i)\right]\\
+ =& \left \langle \int_{0}^{\infty} \ell(x,u) g(x,u) du ,\Xi(dx) \right\rangle \exp(\langle -h(x), \Xi(dx) \rangle) \\
+ =& \left \langle \int_{0}^{\infty} \ell(x,u) g(x,u) du ,\Xi(dx) \right\rangle \mathcal{E}_{-h}(\Xi)
+\end{aligned}
+\end{equation}
+where $h(x)=\int_{0}^{\infty}(1-g(x,u))du$.
+
+We are now ready to prove Lemma \ref{lem: MMT for limit}.
+
+\begin{proof}[Proof to Lemma \ref{lem: MMT for limit}]
+We write
+$$ Af(\xi)=A_1f(\xi)+A_2f(\xi)+A_3f(\xi),$$
+where the first term is
+\begin{equation}
+\begin{aligned}
+A_1f(\xi) =&
+        f(\lp)  \sum_{(x, u) \in \xi}
+             \frac{
+            	\gamma(x, \Xi)
+                \left(\DG(g(\cdot, u) r(\cdot, \Xi))(x) - g(x,u) \DG r(x,\Xi)\right)
+            }{
+                g(x, u)
+            }\\
+            = & f(\lp)  \sum_{(x, u) \in \xi} \frac{\ell_1(x,u)}{g(x,u)},
+\end{aligned}    
+\end{equation}
+the second term is
+\begin{equation}
+\begin{aligned}
+A_2f(\xi)  = &
+  f(\lp) \sum_{(x, u) \in \xi}
+        2 \alpha \gamma(x, \Xi) r(x, \Xi ) \int_u^\infty (g(x, u_1) - 1) du_1\\
+         =&  f(\lp)  \sum_{(x, u) \in \xi} \ell_2(x,u),
+\end{aligned}    
+\end{equation}
+and the final term satisfies
+\begin{equation}
+\begin{aligned}
+A_3f(\xi)  =&f(\lp) \sum_{(x, u) \in \xi}
+                \frac{\left(
+            \alpha \gamma(x, \Xi) r(x, \Xi ) u^2
+            -
+            \left\{
+                \gamma(x, \Xi) \DG r(x, \Xi) + F(x, \Xi)
+            \right\} u
+        \right)
+        \partial_u g(x, u)}{ g(x,u) }\\
+        =& f(\lp) \sum_{(x, u) \in \xi} \frac{\ell_3(x,u)}{g(x,u)}  .
+\end{aligned}    
+\end{equation}
+
+Applying Equation \eqref{eq: cond_poi_sum_prod}
+to the above expressions give 
+\begin{equation}
+\int Af(\xi)\Gamma^{\Xi}(d\xi)
+= \left \langle \int_{0}^{\infty}\left(\ell_1(x,u) + \ell_2(x,u) g(x,u) + \ell_3(x,u)\right)du ,\Xi(dx) \right\rangle \mathcal{E}_{-h}(\Xi)
+\end{equation}
+
+First of all, 
+the operator $\DG$ acts on space while the integral is over levels,
+so we can commute the two operators to obtain
+\begin{equation}
+\begin{aligned}
+\int_{0}^{\infty} \ell_1(x,u) du 
+=& \int_{0}^{\infty} \gamma(x, \Xi)( \DG((g(\cdot, u)-1) r(\cdot, \Xi))(x) - (g(x,u)-1) \DG r(x,\Xi))  du \\
+=& \gamma(x, \Xi)\left\{ \DG\left(\int_{0}^{\infty} (g(\cdot, u)-1)du \times r(\cdot, \Xi)\right)(x) - \int_{0}^{\infty} (g(x,u)-1)du \DG r(x,\Xi)\right\} \\
+=& -\gamma(x, \Xi)\{ \DG(h(\cdot) r(\cdot, \Xi))(x) - h(x) \DG r(x,\Xi)\},
+\end{aligned}
+\end{equation}
+as $h(x,u)= \int_{0}^{\infty} (1 -g(x,u))du$.
+
+Similarly,
+\begin{equation}
+\begin{aligned}
+\int_{0}^{\infty} \ell_2(x,u)g(x,u) du
+=&  \alpha\gamma(x, \Xi) r(x, \Xi ) \times 2 \int_{0}^{\infty} g(x,u)  \int_u^\infty (g(x, u_1) - 1) du_1  du\\
+=&  \alpha\gamma(x, \Xi) r(x, \Xi ) \times I_1.
+\end{aligned}
+\end{equation}
+
+Finally,
+integrating $\ell_3$ by parts, 
+we have
+\begin{equation}
+\begin{aligned}
+\int_{0}^{\infty} \ell_3(x,u)du
+=& \int_{0}^{\infty} \left(
+            \alpha \gamma(x, \Xi) r(x, \Xi ) u^2
+            -
+            \left\{
+                \gamma(x, \Xi) \DG r(x, \Xi) + F(x, \Xi)
+            \right\} u
+        \right)
+        \partial_u g(x, u) du\\
+=& - \alpha\gamma(x, \Xi) r(x, \Xi ) \int_{0}^{\infty} 2u (g(x, u)-1) du\\
+  &+ \left\{\gamma(x, \Xi) \DG r(x, \Xi) + F(x, \Xi) \right\} \int_{0}^{\infty}(g(x,u)-1) du\\
+  =&  - \alpha \gamma(x, \Xi) r(x, \Xi ) I_2 - \left\{\gamma(x, \Xi) \DG r(x, \Xi) + F(x, \Xi) \right\} h(x).
+\end{aligned}
+\end{equation}
+
+Note that $I_1-I_2$ satisfies
+\begin{equation}
+\begin{aligned}
+I_1-I_2 
+=& 2 \int_{0}^{\infty} g(x,u)  \int_u^\infty (g(x, u_1) - 1) du_1  du - 2 \int_{0}^{\infty} u (g(x, u)-1) du\\
+=& 2 \int_{0}^{\infty} g(x,u)  \int_u^\infty (g(x, u_1) - 1) du_1  du - 2 \int_{0}^{\infty} (g(x, u)-1) \int_{0}^{u}dv  du\\
+=& 2 \int_{0}^{\infty} g(x,v)  \int_v^\infty (g(x, u) - 1) du  dv - 2 \int_{0}^{\infty} \int_{v}^{\infty}(g(x, u)-1)  dudv\\
+=& 2 \int_{0}^{\infty} (g(x,v)-1)  \int_v^\infty (g(x, u) - 1) du  dv \\
+=& h^2(x)
+\end{aligned}
+\end{equation}
+
+Combining all the Equations above, 
+we have 
+\begin{equation}
+\begin{aligned}
+& \int_{0}^{\infty}\left(\ell_1(x,u) + \ell_2(x,u) g(x,u) + \ell_3(x,u)\right)du \\
+=& -\gamma(x, \Xi)\DG(h(\cdot) r(\cdot, \Xi))(x) + \gamma(x, \Xi) h(x) \DG r(x,\Xi) -  \gamma(x, \Xi) \DG r(x, \Xi)h(x) - F(x, \Xi)  h(x) \\
+& +\alpha\gamma(x, \Xi) r(x, \Xi )(I_1-I_2)\\
+=&\alpha \gamma(x, \Xi) r(x, \Xi ) h^2(x) -\gamma(x, \Xi)\DG(h(\cdot) r(\cdot, \Xi))(x)  - F(x, \Xi)  h(x).
+\end{aligned}
+\end{equation}
+
+To conclude, 
+\begin{equation}
+\begin{aligned}
+&\int Af(\xi)\Gamma^{\Xi}(d\xi)\\
+= & \left(\alpha \gamma(x, \Xi) r(x, \Xi ) h^2(x) -\gamma(x, \Xi)\DG(h(\cdot) r(\cdot, \Xi))(x)  - F(x, \Xi)  h(x)\right)\mathcal{E}_{-h}(\Xi)\\
+= & \left(\gamma(x, \Xi)\DG(-h(\cdot) r(\cdot, \Xi))(x)  + F(x, \Xi)  (-h(x))\right)\mathcal{E}'(\langle -h, \Xi \rangle )\\
+   &+ \left(\alpha \gamma(x, \Xi) r(x, \Xi ) h^2(x) \right)\mathcal{E}''(\langle -h, \Xi \rangle )\\
+=& \Pgen \mathcal{E}_{-h}(\Xi),
+\end{aligned}
+\end{equation}
+so we have established our equality. 
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Technical Lemmas}
+
+\subsection{Gaussian Kernel Estimates}
+
+\begin{lemma}\label{eq: Gaussin density estimates}
+\begin{equation}
+ \theta H_{\theta}(x,w)\rho_r(x-w)\leq \rho_{\gamma}(x-w),
+\end{equation}
+where
+$$H_{\theta}(x,w)=\int_{\IR^d}
+    \left(
+        \frac{\rho_r(y-w)}{\rho_r(x-w)}
+        -
+        1
+    \right)^2
+q_{\theta}(x,dy).$$
+\end{lemma}
+\begin{proof}
+
+Writing out $H$,
+\begin{align}
+H_\theta(x, w)
+=
+\int
+    \left(
+        \exp\left(
+            - \frac{1}{2\epsilon_r^2}
+            \left\{
+                ||y - w||^2 - ||x - w||^2
+            \right\}
+        \right)
+        -
+        1
+    \right)^2
+    \frac{
+        e^{-\theta (y - x-\meanq)^{T}\covq^{-1}(y - x-\meanq)  / 2}
+    }{
+        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
+    }
+dy.
+\end{align}
+Writing $z=y-x-\meanq$, we have that 
+\begin{equation}
+\begin{aligned}
+||y - w||^2 - ||x - w||^2 
+=& ||y||^2-||x||^2 -2\langle y-x, w\rangle \\
+=&||x+z+ \meanq||^2-||x||^2-2 \langle z+ \meanq, w\rangle\\
+=&2\langle x, z+ \meanq \rangle + ||z+ \meanq||^2-2 \langle z+ \meanq, w\rangle \\
+=& 2 \langle x-w, z+ \meanq \rangle + ||z+ \meanq||^2\\
+=& 2\langle x-w+ \meanq,\meanq \rangle + 2\langle x-w+ \meanq, z \rangle +||z||^2
+\end{aligned}
+\end{equation}
+As a result, we have 
+\begin{align}
+H_\theta(x, w)
+=&
+\int
+    \left(
+        \exp\left(
+            - \frac{1}{2\epsilon_r^2}
+            \left\{
+                2 \langle x-w, z+ \meanq \rangle + ||z+ \meanq||^2
+            \right\}
+        \right)
+        -
+        1
+    \right)^2
+    \frac{
+        e^{-\theta z^{T}\covq^{-1}z  / 2}
+    }{
+        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
+    }
+dz\\
+=&\exp\left(-\frac{2}{\epsilon_r^2}\langle x-w+ \meanq,\meanq \rangle \right)\\
+& \times \int
+        \frac{
+        \exp\left(
+            - \frac{2}{\epsilon_r^2} \langle x-w+ \meanq, z \rangle
+            - \frac{1}{\epsilon_r^2} ||z||^2
+            \right)
+            e^{-\theta z^{T}\covq^{-1}z  / 2}
+    }{
+        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
+    }
+dz\\ \label{eq: Second moment term matrix calculation}
+&-2\exp\left(-\frac{1}{\epsilon_r^2}\langle x-w+ \meanq,\meanq \rangle \right)\\
+& \qquad \qquad \times     \int
+    \frac{ \exp\left(
+             -\frac{1}{\epsilon_r^2}\langle x-w+ \meanq, z \rangle
+              -\frac{1}{2\epsilon_r^2} ||z||^2
+            \right)e^{-\theta z^{T}\covq^{-1}z  / 2}
+        }{
+        (2 \pi/ \theta)^{d/2} |\covq|^{1/2} \label{eq: first moment term matrix calculation}
+    }
+dz\\
+&+1.
+\end{align}
+We now consider the integral of the form 
+\begin{equation}
+\int \exp(v^{T}z-C||z||^2) \frac{
+        e^{-\theta z^{T}\covq^{-1}z  / 2}
+    }{
+        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
+    }
+dz   
+\end{equation}
+for $v \in \IR^d$ and $C>0$. 
+We have 
+\begin{equation}
+\begin{aligned}
+&\int \exp(v^{T}z-C||z||^2) \frac{
+        e^{-\theta z^{T}\covq^{-1}z  / 2}
+    }{
+        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
+    }
+dz\\
+=&\frac{1}{|\covq|^{1/2}|  |\covq^{-1}(I+2C\covq/\theta )|^{1/2}  }\int \exp(v^{T}z) \frac{
+        e^{-\theta z^{T}\covq^{-1}(I+2C\covq/\theta )z  / 2}
+    }{
+        (2 \pi/ \theta)^{d/2}|\covq^{-1}(I+2C\covq/\theta )|^{-1/2} 
+    }
+dz\\
+=& \frac{1}{|I+2C\covq/\theta |^{1/2}} \mathbb{E}_{Z}[\exp (v^{T}Z)]\\
+=&\frac{1}{|I+2C\covq/\theta |^{1/2}}
+\exp 
+\left(
+\frac{1}{2}v^{T}\covq/\theta(I+2C\covq/\theta )^{-1}v
+\right),
+\end{aligned}
+\end{equation}
+where $Z \sim N(0, \covq/\theta \times (I+2C\covq/\theta )^{-1})$.
+
+Now writing $v=\frac{2}{\epsilon_r^2}( w-x-\meanq)$
+and $C=\frac{1}{\epsilon_r^2}$,
+we have the expression in Equation
+\eqref{eq: Second moment term matrix calculation} is 
+$$\frac{1}{|I+2\covq/(\epsilon_r^2\theta) |^{1/2}}
+\exp 
+\left(
+\frac{2}{\epsilon_r^4}( w-x-\meanq)^{T}\covq/\theta\left(I+2\covq/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
+\right).$$
+Similarly, writing $v=\frac{1}{\epsilon_r^2}( w-x-\meanq)$
+and $C=\frac{1}{2\epsilon_r^2}$,
+we have the expression in Equation
+\eqref{eq: first moment term matrix calculation} is 
+$$\frac{1}{|I+\covq/(\epsilon_r^2\theta) |^{1/2}}
+\exp 
+\left(
+\frac{1}{2\epsilon_r^4}( w-x-\meanq)^{T}\covq\left(I+\covq/\theta/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
+\right).$$
+As a result, we have 
+\begin{align*}
+&H_{\theta}(x,w)\\
+=& \frac{1}{|I+2\covq/(\epsilon_r^2\theta) |^{1/2}}
+\exp 
+\left(
+\frac{2}{\epsilon_r^4}( w-x-\meanq)^{T}\covq/\theta\left(I+2\covq/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
+\right)\\
+&-2\frac{1}{|I+\covq/(\epsilon_r^2\theta) |^{1/2}}
+\exp 
+\left(
+\frac{1}{2\epsilon_r^4}( w-x-\meanq)^{T}\covq/\theta\left(I+\covq/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
+\right)\\
+&+1.
+\end{align*}
+If we write $F(1/\theta)=H_{\theta}(x,w)$, i.e.
+\begin{align*}
+&F(s)\\
+=& \frac{1}{|I+2/\epsilon_r^2 \covq s |^{1/2}}
+\exp 
+\left(
+\frac{2}{\epsilon_r^4}( w-x-\meanq)^{T}\covq s \left(I+2/\epsilon_r^2 \covq s\right)^{-1}( w-x-\meanq)
+\right)\\
+&-2\frac{1}{|I+2/\epsilon_r^2 \covq s |^{1/2}}
+\exp 
+\left(
+\frac{1}{2\epsilon_r^4}( w-x-\meanq)^{T}\covq s \left(I+2/\epsilon_r^2 \covq s\right)^{-1}( w-x-\meanq)
+\right)\\
+&+1\\
+&=G_1(s)+2G_2(s)+1
+\end{align*}
+we can check that $F(0)=0$.
+As a result, 
+$$\theta H_{\theta}(x,w)\rho_r(x-w)= \theta F(1/\theta)\rho_r(x-w)=F'(s)\rho_r(x-w),$$
+for some $s \in [0, 1/\theta]$.
+
+In Equation \eqref{eq: gamma-r convolution comparison}, we have established that 
+$\rho_r(x-w) / \rho_\gamma(x-w) = C' \exp(-K (x-w)^2 / 2)$
+with $K = \frac{1}{\epsilon_r^2} - \frac{1}{\epsilon_\gamma^2}$.
+Therefore it suffices to show that for all $x,w \in \IR^d$ and $s \in [0, 1/\theta]$, 
+\begin{align}\label{eqn:goal3}
+    F'(s) \exp\left(-A (x-w)^2 \right) \le C .
+\end{align}
+
+We consider how to differentiate function $G$ of the form 
+$$G(s):=\frac{1}{|I+As|^{1/2}}\exp(v^{T}Bs(I+Cs)^{-1}v),$$
+where $A,B,C$ are matrices with non-negative entries and $I$ is the identity matrix.
+
+Since 
+\begin{equation}
+\begin{aligned}
+G'(s)=& - \frac{|A|}{2|I+As|^{3/2}}\exp(v^{T}Bs(I+Cs)^{-1}v)\\
+      & + \frac{1}{|I+As|^{1/2}}\exp(v^{T}Bs(I+Cs)^{-1}v)\\
+      & \qquad \times \left\{ v^{T}B(I+Cs)^{-1}v
+                            - sv^{T}BC(I+Cs)^{-2}v
+                    \right\}\\
+      &=\left(- \frac{|A|}{2|I+As|}+v^{T}B(I+Cs)^{-2}v
+        \right)\\
+      & \qquad \times
+        \frac{1}{|I+As|^{1/2}}\exp(v^{T}Bs(I+Cs)^{-1}v),
+\end{aligned}
+\end{equation}
+using non-negativity of $A,B,C$ we have
+\begin{equation}
+\label{eq: bounds on G'}
+|G'(s)| \leq (|A|+||B||_{2}||v||_2^2)G(s).    
+\end{equation}
+As a result, we have that 
+\begin{equation}
+\label{eq: bounds on G}
+G(s) \leq K e^{|A|+||B||_{2}||v||_2^2)s}, ~~   G'(s)(|A|+||B||_{2}||v||_2^2)K e^{|A|+||B||_{2}||v||_2^2)s}.  
+\end{equation}
+
+Finally note that, 
+$$F'(s) \leq G_1'(s)+2G_2'(s),$$
+where 
+$$A_1= 2\epsilon_r^{-2} \covq, ~ v_1=\epsilon_r^{-2}(w-x-\meanq), ~B_1 = 2\covq, ~C_1=2\epsilon_r^{-2} \covq,$$
+and 
+$$A_2= 2\epsilon_r^{-2} \covq, ~ v_2=\epsilon_r^{-2}(w-x-\meanq), ~B_2 = \covq/2, ~C_2=2\epsilon_r^{-2} \covq,$$
+Substituting these quantities on Equation \eqref{eq: bounds on G} shows that Equation \eqref{eqn:goal3} is satisfied as long as $\epsilon_r < \epsilon_\gamma$.
+
+\end{proof}
+
+\subsection{Tightness of processes}
+\label{apx:aldous rebolledo}
+
+We record for reference above
+one version of the Aldous-Rebolledo criteria for tightness of a sequence real-valued processes
+(as it appears in \citet{etheridge2000introduction}):
 \comment{TODO: reference this elsewhere, if we keep it?}
@@
 
-\begin{lemma}
-    \label{lem:test_fn_tightness}
-    Let $f$ be a bounded, continuous real-valued function on $\IR^d \times [0, \infty)$
-    with uniformly bounded first and second derivatives
-    for which there exists a $u_0$ such that if $u > u_0$ then $f(x, u) = 0$.
-    Then, the sequence of real-valued processes $(\langle f, \lp_t^N \rangle)_{t \ge 0}$
-    are tight in the space of c\`adl\`ag processes.
-\end{lemma}
-
-\begin{proof}[of Lemma \ref{lem:test_fn_tightness}]
-    First, a reminder of the description of the process
-    \comment{(TODO: figure out if the notation here for $a$ and $b$ should be used above;
-        if so, move it up; if not, replace it here.)}
-    Recall when the state of the process is $\eta$,
-    the level of a line of descent at spatial location $x$ and level $u$
-    changes following
-    $$
-        \dot u = a^N(x, \eta) u^2 - b^N(x, \eta) u,
-    $$
-    where
-    $$
-        a^N(x, \eta)
-        =
-        \frac{\theta}{N} \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q(x, dy) ,
-    $$
-    and
-    $$
-        b^N(x, \eta)
-        =
-        \theta \gamma(x, \eta) \int_{\IR^d} (r(y, \eta) - r(x, \eta)) q(x, dy) + F(x, \eta) .
-    $$
-    Furthermore, the line of descent
-    gives birth to lines at higher levels at rate $2 (N - u) a^N(x, \eta)$,
-    that each such new line chooses a level uniformly from $[u, N]$,
-    a spatial location $y$ from the kernel
-    $$
-        q^m(x, dy, \eta)
-        =
-        r(y, \eta) q(x, dy) / \int_{\IR^d} r(y, \eta) q(x, dy),
-    $$
-    and the two lines swap spatial locations with probability 1/2.
-
-    It is evident from the description of the process
-    (or, by differentiating in Definition~\ref{defn:lookdown_mgale})
-    that
-    \begin{align*}
-    \begin{split}
-    M^f_t
-        &=
-        \langle f, \lp_t^N \rangle
-        -
-        \langle f, \lp_0^N \rangle
-    \\ & \qquad \qquad {}
-        -
-        \int_0^t
-        \big\langle
-            a^N(x, \eta^N_s)
-            \int_u^N \int_{\IR^d}
-            \left(
-                f(y, u_1) + f(x, u_1) + f(y, u) - f(x, u)
-            \right)
-            du_1 q^m(x, dy, \eta^N_s)
-    \\ & \qquad \qquad \qquad \qquad {}
-            +
-            \left(
-                a^N(x, \eta^N_s) u^2
-                - b^N(x, \eta^N_s) u
-            \right)
-            \frac{d}{du} f(x, u)
-        ,
-        \lp_s^N(dx, du) \big \rangle
-        ds
-    \end{split}
-    \end{align*}
-    is a martingale,
-    with quadratic variation
-    \begin{align*}
-        [M^f]_t
-        &=
-        \int_0^t
-        \langle a^N(x, \eta_s^N) \int_u^N \int_{\IR^d}
-            f(y, u_1)^2 +
-            \left( f(x, u_1) + f(y, u) - f(x, u) \right)^2
-        du_1 q^m(x, dy, \eta^N_s)
-        \lp_s^N(dx, du) \big \rangle
-        ds .
-    \end{align*}
-
-    Now we would like to bound the terms in the integral,
-    to arrive at a bound using Gronwall's inequality, as before.
-
-    First, note that there exists a constant $C_a$
-    such that $a^N(x, \eta) \le C_a$
-    (since $\gamma$ and $r$ are bounded above, and $\theta/N \to \alpha \ge 0$),
-    and for any $\epsilon > 0$ and $T$ there is a $C_b$ such that for all $N$,
-    $$
-        \IP\left\{
-            \sup_{0 \le s \le T} \sup_x |b^N(x, \eta_s^N)| > C_b
-        \right\}
-        < \epsilon 
-    $$
-    \comment{reference where we show this above}.
-    Now, since $f$ vanishes for $u \ge u_0$,
-    on the event that $\sup_x |b^N(x, \eta_s^N)| \le C_b$ then
-    if $N \ge u_0$,
-    \begin{align*}
-    &
-        \int_{\IR^d} \int_0^N
-            \left(
-                a^N(x, \eta^N_s) u^2
-                - b^N(x, \eta^N_s) u
-            \right)
-            \frac{d}{du} f(x, u)
-        \lp_s^N(dx, du)
-    \\  & \qquad
-    \le
-        \int_{\IR^d} \int_0^{u_0}
-            \left(
-                C_a u_0^2
-                + C_b u_0
-            \right)
-            \left\| \frac{d}{du} f \right\|_\infty
-        \lp_s^N(dx, du) .
-    \\  & \qquad
-    \le
-        C_0 \lp_s^N(\IR^d \times [0, u_0]) .
-    \end{align*}
-
-    Next, observe that for any $\eta$,
-    $$
-    \int_{\IR^d} \int_u^N (f(y, u_1) + f(x, u_1)) du_1 q^m(x, dy, \eta)
-    \le 2 u_0 \|f\|_\infty .
-    $$
-    Furthermore,
-    recall that we have assumed \comment{(check where we do this)}
-    that $q^m$ is uniformly elliptic,
-    and so since $f$ has bounded first and second derivatives,
-    there is a $C_1$ depending on $f$ such that for all $\eta$,
-    $\theta \int_{\IR^d} (f(y, u) - f(x, u)) q^m(x, dy, \eta) \le C_1$.
-    Therefore, using boundedness of $\theta/N$,
-    \begin{align*}
-        &
-        \int_{\IR^d} \int_u^N (f(y, u) - f(x, u)) du_1 q^m(x, dy, \eta^N_s)
-        \\ &\qquad
-        = (N - u) \int_{\IR^d} (f(y, u) - f(x, u)) q^m(x, dy, \eta^N_s)
-        \\ &\qquad
-        = \frac{N}{\theta} \left(1 - \frac{u}{N}\right) \theta \int_{\IR^d}
-            (f(y, u) - f(x, u)) q^m(x, dy, \eta^N_s)
-        \\ &\qquad
-        \le C_1 \frac{N}{\theta} \ind_{u \le u_0} .
-    \end{align*}
-
-    Putting this together,
-    \begin{align*}
-        \IE\left[
-            \langle f, \lp_t^N \rangle
-        \right]
-        \le
-    \end{align*}
-
-\end{proof}
-
-\subsubsection{OLD STUFF REMOVE}
-
-    To get around this,
-    first note that both $b$ and $c$ are uniformly bounded above 
-    by Lemma~\ref{lem:gamma_bound} and since $\gamma$, $r$, $F$ \comment{(???)}, and $\theta/N$ are.
-    Also note that for any $\delta > 0$ we can find a $K$ such that
-    $$
-    \IP\left\{
-        \sup_{0 \le t \le T} \sup_x \smooth{F} \eta_t(x) < K
-        \right\} < \delta,
-    $$
-    uniformly in $N$ and over a compact set of initial conditions.
-    Since $F$ is uniformly continuous, this implies that $\sup_{0 \le t \le T} \sup_x F(x, \eta_t)$
-    is similarly tight,
-    as well as the rate of downward drift of the level of a line of descent,
-    i.e., there is a $\bar b$ such that $b(x, \eta_t) \le \bar b$
-    on a set of probability at least $1-\delta$ as well.
-    Therefore, if $u_1 \ge u_0 + \bar b T$, then
-    $$
-    \IP\left\{
-        \inf_{0 \le t \le T} U_a(t) \le u_0
-        \;\big|\;
-        U_a(0) > u_1
-    \right\}
-    \le \delta ,
-    $$
-    and so with high probability any lines of descent that had level below $u_0$
-    at some point $0 \le t \le T$
-    are descended from lines of descent with initial level below $u_1$.
-    Since the number of lines of descent with level below $u_1$
-    converges to a Poisson with finite mean,
-    we need only show that the number of offpring lines of descent
-    produced by this initially finite number is also tight.
-    However, this follows immediately
-    since the rate of production of new lines of descent with level below $u_1$
-    of a line of descent at location $x$ and level $u$ is
-    $2 (u_1 - u) N^{-1} \theta \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q(x, dy)$
-    and therefore uniformly bounded (because we may take $u_1 \le N$).
-
-% % % % % % % % % % % % %
-\subsubsection{Tightness of the Lines of Descent}
-    \label{sec:lookdown_tightness_proofs}
-
-In this section,
-we will prove tightness
-of the spatial and level trajectory
-of a line of descent
-(constructed in \S \ref{sec: individual lines of descent})
-as a forward-in-time process.
-
-To prove tightness of the 
-spatial and level locations
-of a typical line of descent,
-we will show that the
-jumps in
-spatial and level locations
-of the line of descent
-in finite time
-can be controlled.
-
-Recall that the lines of descents
-track chains of descendant
-individuals forwards through time following the \textit{levels}.
-
-\subsubsection{Tightness of Spatial Trajectories}
-Before proving tightness of our spatial trajectories, 
-note that for a fixed label
-$a=(a_0,a_1,..,a_k)$,
-the spatial evolution of 
-$X^N_{a}(t)$ for $t \geq \tau^N_{a}$
-is determined
-purely by the last term 
-in Equation \eqref{eq: space_across_lineage}.
-
-As a result, the spatial jumps are 
-driven by 
-an underlying Poisson point process. 
-It is therefore sufficient
-to prove that square of 
-these increments are bounded
-in small time scales.
-
-\begin{lemma} \label{lem: tightness of individual spatial trajectory}
-Assume that the jump kernel $q_\theta^\mathfrak{m}(x, \eta, dy)$ of the form
-$$
-    q_\theta^\mathfrak{m}(x,\eta,  dy)
-    :=
-    \frac{
-        r(y, \smooth{r} \eta(y)) q_\theta(x, dy)
-    }{
-        \int r(x, \smooth{r} \eta(z)) q_\theta(x, dz)
-    } 
-$$
-satisfies the inequalities
-\begin{align}
-   \sup_{\theta}\mathbb{E}\left[\limsup_{x, \eta} \theta \left| \int_{\IR^d} (y-x) q^{\mathfrak{m}}_{ \theta}(x,\eta,dy) \right|\right] \leq & \quad \overline{\alpha},\\
-   \sup_{\theta}\mathbb{E}\left[\limsup_{x, \eta} \theta \int_{\IR^d} |y-x|^2 q^{\mathfrak{m}}_{ \theta}(x,\eta,dy)\right]  \leq & \quad \overline{\beta}.
-\end{align}
-Furthermore, assume that the birth rate satisfies 
-$$\sup_{x, \eta}\gamma_{\theta}(x, \varrho_{\gamma}*\eta(x)) < C_G,$$ 
-then for fixed $a=(a_0,a_1,..,a_k)$,
-$\{(X^{N}_{a}(t))_{\tau^{N}_a\leq t < \sigma^{N}_{a}}: N \in \mathbb{N},  \}$ is relatively compact in 
-$D_{\IR^d}[0,\infty )$ where $\IR^d$ is equipped with the standard Euclidean metric. 
-\end{lemma}
-\begin{proof}
-We write $S_{t,r}:=(t,t+r  ]\times [0,\infty )\times \IR^d\times 
-\{0,1\}$ to be the region for the Poisson measure driving $(X^{N}_{a}(t))_{t \geq \tau_a}$ between time $t$ and $(t+r)$ and write $\tilde\Pi_{a}(ds,dv,dz,d\kappa):=\Pi_{a}(ds,dv,dz, d\kappa) - ds\times dv\times dz \times (\frac{1}{2}\delta_{0}+\frac{1}{2}\delta_{1})d\kappa$ to be the compensated Poisson point process of $\Pi_{a}$.
-For $\tau_a \leq t < t+r < \sigma_a$, we can compute
-\small
-\begin{align*}
-&\mathbb{E}[|X^{N}_{a}(t+r )-X^{N}_{a}(t)|^2|{\cal F}_t^{
-\eta}]\\
-=& \mathbb{E}\left[\left|
-\int_{S_{t,r}}
-(1-\kappa)y(z)
-\ind_{ \{
-        U_{a}(\tau_{a}+s)
-        + \ell(X_{a}(\tau_{a}+s),y(z),\eta_{a}(\tau_{a}+s)) v < N
-        \}
-      } 
-\Pi_{a}(dsdvdzd\kappa)
-\right|^2
-\Bigg|{\cal F}_t^{\eta}\right]\\
-\leq&
- 2\mathbb{E}\left[
- \left|
- \int_{S_{t,r}}
- {\bf 1}_{\{v < 2  \theta \gamma_{\theta}(x, \eta) r_{\theta}(x + y, \eta) \}}{\bf 1}_{\kappa =1}
-y(z)
-\tilde\Pi_{a}(ds,dv,dy,d\kappa )
-\right|^2
-\Bigg|{\cal F}_t^{\eta}
-\right]\\
-&\quad +2\mathbb{E}\left[
-\left|
-\int_{t}^{t+r}\int_{\{v < 2\theta \gamma_{\theta}(x, \eta) r_{\theta}(x + y, \eta) \}}
-\frac{1}{2}\left| \int_{\IR^d} (y-X^{N}_{\tau}(s-)) q^{\mathfrak{m}}_{\theta}(X^{N}_{\tau}(s-),\eta^{N}(s-),dy) 
-\right|
-dvds \right|^2
-\Bigg|{\cal F}_t^{\eta}
-\right]\\
-&\leq 
-2\mathbb{E}\left[
-\int_{t}^{(t+r)   }
-(1+C_G) \theta 
-\int_{{\IR}^d}|y-X^{N}_{
-a}(s)|^2q^{\mathfrak{m}}_{\theta}(X^{N}_{a}(s),\eta^{N}(s),dy)ds
-\Bigg|{\cal F}_t^{\eta}\right]\\
-&\quad +2\mathbb{E}\left[
-\left|
-\int_{t}^{(t+r)}
-(1+C_G)\theta 
-\left|
-\int_{{\IR}^d}
-(y-X^{N}_{a}(s))q^{\mathfrak{m}}_{\theta}(X^{N}_{a}(s),
-\eta^{N}(s),dy)
-\right|
-ds
-\right|^2
-\Bigg|{\cal F}_t^{\eta}\right]\\
-\leq& 2r \overline{\beta}(1+C_G)+2(r \overline{\alpha}(1+C_G))^2.
-\end{align*}
-\normalsize
-
-The first inequality uses of the inequality $(A+B)^2 \leq 2A^2+2B^2$ as well as the fact that $(N-U_{a})N^{-1} \leq 1$.
-The second inequality holds 
-because birth events occur
-at rate $2\theta \gamma_{\theta}(x, \eta) r_{\theta}(x + y, \eta)$
-which is bounded above by $2\theta (1+C_G)$. The third inequality holds due to the assumptions on the dispersal kernel.
-
-Finally, since $\eta_0$ has compact support, we can take $t=\tau_u$ and apply Markov inequality to get that for every $\delta>0$, there exists $N_{\delta}>0$ such that
-\begin{equation}\label{eq: Compact Containment Condition for individual spatial motion}
-\sup_{N>N_{\delta}}\sup_{T>0}\mathbb{P}\left[|X^{N}_{a}(\tau_{a}+T)-X^{N}_{a}(\tau_{a})|>N_{\delta}\right]\leq   \frac{2r \overline{\beta}(1+C_G)+2(r \overline{\alpha}(1+C_G))^2}{N_{\delta}^2}  < \delta,
-\end{equation}
-giving us compact containment condition. Relative compactness thus follows by Theorem 3.8.6.
-of \cite{ethier/kurtz:1986}.
-\end{proof}
-\begin{remark}
-Note that if we assume $r \equiv 1$, then 
-$q^{\mathfrak{m}}_{\theta}(x,\eta,dy)=q_{\theta}(x,dy).$
-In particular, if we let $q_{\theta}$ be the standard Gaussian normal, we have the inequalities
-\begin{align}
-   \sup_{\theta}\limsup_{x, \eta} \theta \left| \int_{\IR^d} (y-x) q^{\mathfrak{m}}_{ \theta}(x,\eta,dy) \right| =& \sup_{\theta}\limsup_{x} \theta \left| \int_{\IR^d} (y-x) q_{\theta}(x,dy) \right| =  0,\\
-   \sup_{\theta}\limsup_{x, \eta} \theta \int_{\IR^d} |y-x|^2 q^{\mathfrak{m}}_{ \theta}(x,\eta,dy)  =& \sup_{\theta}\limsup_{x} \theta \int_{\IR^d} |y-x|^2 q_{\theta}(x,dy) =  1,
-\end{align}
-as the last term can be expressed as $\theta \mathbb{E}_{x}[(B_{1/\theta}-x)^2]=1$.
-
-As a result, we have tightness for all populations with unbiased isotropic dispersal.
-
-Furthermore, the assumption on $\gamma$ is natural as we typically assume an uniform upper bound on the total fecundity rate, i.e.
-$\sup_{u \geq 0} u\gamma(x,u) < C$.
-\end{remark}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Tightness of Level Processes}
-We have now proved that the spatial trajectories of a line of descent during its lifetime is relatively compact as $N \to \infty$.
-However, we will still need to show that the level process is also well controlled, i.e.
-a line of descent with an initial level smaller than $K << N$ will have a level larger than $N$ in very small time-scale with very low probability.
-This will then prevent a line of descent from dying instantaneously in the scaling limit.
-
-To make this precise, we must work in the vague topology.
-Proving tightness of the level process is slightly trickier as the levels of many particles will drift towards infinity in finite time.
-These particles however will not contribute to the metric associated with the vague topology and thus we will retain relative compactness.
-The main argument relies on the observation that particles with levels lower than some threshold $\overline{U}_{N, \delta}$  have regulated level increments of order $\epsilon$ over any small time interval of length $r$ given large enough $N$.
-As a result, we can evaluate our level process against test functions $(g_n)_{n=1,..,N}$ with cut off smaller than $\overline{U}_{N, \delta}$.
-
-\begin{lemma} \label{lem:tightness of levels} For fixed $a\in \mathcal{U}$, let $U^N_{a}(\tau_a)=U_0$, i.e. the level of the line of descent $a$ at birth is $U_0>0$.
-On top of the assumptions laid out in Lemma \ref{lem: tightness of individual spatial trajectory}, assume that 
-$$
-    \sup_{\theta}\mathbb{E}\left[ \sup_{x, \eta} b_\theta(x, \eta) \right]
-    :=
-    \sup_{\theta}
-    \theta 
-    \mathbb{E}\left[ \sup_{x, \eta} \left(
-    \gamma_\theta(x,\eta) \int_{\IR^d} r_\theta(y, \eta) q_\theta(x, dy)
-    -
-    \mu_\theta(x,\eta)
-    \right)\right] 
-    \leq C_G,
-$$
-and there exists some $C_F \geq 0$ such that
-\begin{align} 
-\begin{split}
-b_{\theta}(x, \eta)
-&=
-    \theta \gamma_{\theta}(x, \eta) \int_{\IR^d} \left( r_{\theta}(y, \eta) - r_{\theta}(x, \eta) \right) q_{\theta}(x, dy)
-    + F_{\theta}(x, \eta) \\
-& \geq - C_F \varrho_F*\eta(x)
-\end{split}
-\end{align}
-for all $x \in \IR^d$ and  $\eta \in \mathcal{M}_{F}(\IR^d)$.
-
-Then
-$\{(U^{N}_{a}(t))_{t \geq \tau_a}, N >0\}$ is relatively compact in 
-$\mathcal{D}_{[0,\infty)}[0,\infty )$, where $[0,\infty)$ is equipped with the vague topology.
-\end{lemma}
-
-\begin{proof} Recall that for a fixed line of descent, the level process is determined only by the integral equation of the form 
-\begin{align*}
-&U^{N}_{a}(t+r)-U^{N}_{a}(t)\\
-=&\int_{t}^{t+r}
-\left(
-        \frac{\theta}{N} \gamma_{\theta}(X^N_{a}(s),\eta^N_s)
-        \int_{\IR^d} r_{\theta}(z,\eta^N_s) q_{\theta}(X^N_a(s),dz) U^N_a(s)^2
-        -
-        b_{\theta}(X^N_a(s),\eta^N_s) U^N_a(s)
-    \right)
-    ds.
-\end{align*}
-
-To control the level process, we consider two scenarios, one where the local density of the system between $[0,r]$ is never too big, i.e.
-$$h(r)=\sup_{x \in \IR^d}\sup_{s\in [0,r]}\left\{\varrho_F*\eta^N_s(x) \right\} \leq H_{\epsilon}(r),$$
-and otherwise.
-
-When the local density is smaller than $H_{\epsilon}$, we will show that the level grows steadily.
-Consequently, the level grows very fast and hit some level $\overline{U}_{K_{\epsilon}}$ very quickly only when the local density is larger than $H_{\epsilon}$.
-In this case, the effective increment in levels observed under the vague topology is bounded above by $\overline{U}_{K_{\epsilon}}$.
-We will first make this statement precise.
-We will also show that the probability of such event is very small.
-As a result, the level process is tight.
-
-We will first make our convergence statement precise under the vague topology. 
-We will then prove tightness in the high density scenario,
-and finally
-prove tightness in the scenario where population density is well controlled
-with a comparison principle.
-
-\textbf{Introducing a cutoff range:} 
-By the characterisation of vague topology on $[0,\infty)$,
-it suffices to prove that for all functions $g\in C_{c}([0,\infty), \mathbb{R}])$ (continuous functions with compact support), 
-the real-valued process
-$\{(g(U^{N}_{a}(t)))_{t \geq \tau_a}, N >0\}$ is relatively compact in 
-$\mathcal{D}_{\mathbb{R}}[0,\infty)$,
-where $\mathbb{R}$ is equipped with the Euclidean metric.
-
-It suffices to show that for any $\epsilon > 0$ and for any line of descent $a \in \mathcal{U}$, there exists small enough  $r>0$ such that $\mathbb{E}[|g(U^{N}_{a}(t+r))-g(U^{N}_{a}(t))||{\cal F}_t^{
-\eta}]< \epsilon$.
-
-Pick $U_{g,\varepsilon}>0$ large enough such that $\text{supp}(g)\subset [0,U_{g,\varepsilon}]$.
-Since we picked $g$ to be continuous and differentiable with compact support, by Mean Value Theorem we have that 
-$$|g(U^{N}_{a}(t+r ))-g(U^{N}_{a}(t))|<C'_{g}(|U^{N}_{a}(t+r)-U^{N}_{a}(t)|\wedge U_{g,\varepsilon}),$$
-for some constant $C'_g$. Note that it suffices to consider $|U^{N}_{a}(t+r)-U^{N}_{a}(t)|\wedge U_{g,\varepsilon}$ because $g_n(u)=g_n(U_{g,\varepsilon})=0$ for all $u > U_{g,\varepsilon}$.
-
-Therefore, it suffices to show that for all $\epsilon > 0$, there exists $r>0$ small enough and $N_0$ large enough such that 
-\begin{equation}
-\mathbb{E}[C'_{g}(|U^{N}_{a}(t+r)-U^{N}_{a}(t)|\wedge U_{g,\varepsilon}) ~|~{\cal F}_t^{
-\eta} ] < \epsilon /2    
-\end{equation}
-uniformly over $N \geq N_0$.
-
-\textbf{Controlling high density events:}
-Recall that in Lemma \ref{lem:eta_compact_containment}, we have established compact containment for the total mass process. Therefore for any $\epsilon>0$ and $r>0$, there exists some large 
-\begin{equation}
-    \label{eq: Mass Bound Constant}
-H_{\epsilon}(r):=\frac{\epsilon}{2||\varrho_F||_{\infty}C(r) }>0    
-\end{equation}
-such that 
-the event 
-$$A_{H_{\epsilon}}:= \left\{ \omega \in \Omega: \sup_{s\in [0,r]}\left\{\varrho_F*\eta^N_s(X^N_a(t+s)) \right\}(\omega) \geq H_{\epsilon}(r) \right\}$$
-satisfies
-\begin{equation}
-\limsup_{N \to \infty}\mathbb{P}\left[A_{H_{\epsilon}}\right]
-\leq  \frac{||\varrho_F||_{\infty}\mathbb{E}[\sup_{s\in [t,t+r]}\langle 1,  \eta^N_s \rangle ]}{H_{\epsilon}(r)}
-\leq  \frac{||\varrho_F||_{\infty}C(t+r)}{H_{\epsilon}(r)}
-< \frac{\epsilon}{2 U_{g,\varepsilon}C'_g},
-\end{equation}
-where $(C(t))_{t \geq 0}$ is the growth function that bounds the expected value of the running supremum of the total mass in Equation \eqref{eqn:eta_mass_bound}.
-
-As a result, for any $s < r$,
-\begin{equation}
-\mathbb{E}\left[|g(U^{N}_{a}(t+r ))-g(U^{N}_{a}(t))| \mathbbm{1}_{A_{H_{\epsilon}}} ~|~{\cal F}_t^{
-\eta} \right] 
-\leq  \mathbb{E}\left[C'_{g} U_{g,\varepsilon}\mathbbm{1}_{A_{H_{\epsilon}}} \right] \leq  C'_{g} U_{g,\varepsilon}\mathbb{P}\left[A_{H_{\epsilon}} \right] < \varepsilon / 2.
-\end{equation}
-
-\textbf{Controlling bounded density events:}
-We now consider $A_{H_{\epsilon}}^{c}$.
-To control the downward drift of our levels from the quadratic evolution,
-we neglect all positive drift and obtain
-\begin{equation}
-\begin{aligned}
-\mathbb{E}[U^{N}_{a}(t+r)-U^{N}_{a}(t)] \geq   &   - \mathbb{E}\left[\int_{t}^{(t+r)  } b_{\theta}(X^N_a(s),\eta^N_s) U^N_a(s)ds\right]\\
-\geq& - rC_GU_{g,\varepsilon}.
-\end{aligned}    
-\end{equation}
-
-We can also control the upward drift by comparing our process $(U^N_{a}(\tau_a+r))_{r \geq 0}$ with another process $(W^N_a(r))_{r \geq 0}$, where 
-\begin{align*}
-&W^{N}_{a}(r)-W^{N}_{a}(0)\\
-=&\int_{0}^{r}
-\left(
-        \frac{\theta}{N} C_G W^N_a(s)^2
-        +
-        C_F H_{\epsilon}(r) W^N_a(s)
-    \right)
-    ds,
-\end{align*}
-with $H_{\epsilon}(r) > \sup_{s\in [0,r]}\left\{\varrho_F*\eta^N_s(X^N_a(s)) \right\}$,
-and $W^N_a(0)=U^N_a(\tau_a) = U_0 \leq U_{g,\varepsilon}$.
-
-This is because $\gamma_{\theta} \leq C_G$, $r_{\theta} \leq 1$, and $-b_{\theta}(x, \eta) \leq  C_F \varrho_F * \eta(x) < -C_F H_{\epsilon}(r)$.
-Therefore, the growth rate of the differential equation governing $(U^N_a(t+s))_{s \geq 0}$ is smaller than that of $(W^N_a(s))_{s \geq 0}$ at all time instances.
-
-Note that $(W^N_a(s))_{s \geq 0}$ can be solved explicitly and 
-\begin{equation}
-W^N_a(s) = \frac{C_F H_{\epsilon}(r) U_0 \exp(C_F H_{\epsilon}(r) s)}{C_F H_{\epsilon}(r)+C_G  N^{-1}\theta U_0(1- \exp(C_F H_{\epsilon}(r) s))}\leq U_{g,\varepsilon}    
-\end{equation}
-for 
-\begin{equation}
-    \label{eq: Bound on Level Hitting Time}
-s \leq  \frac{1}{C_F H_{\epsilon}(r)} \log\left\{
-1+
-\frac{C_F H_{\epsilon}(r)
-(U_{g,\varepsilon}
--U_0)
-}
-{C_F H_{\epsilon}(r)U_0 +C_G  N^{-1}\theta U_{g,\varepsilon}    U_0}
-\right\}.
-\end{equation}
-As $\theta / N $ converges in the limit, we may take some constant $\bar{\alpha}$ such that for large enough $N$,
-the level process $(U^N_{a}(s))_{s \geq 0}$ will not hit  $U_{g,\varepsilon}$ as long as
-\begin{equation}
-s \leq  \frac{1}{C_F H_{\epsilon}(r)} \log\left\{
-1+
-\frac{C_F H_{\epsilon}(r)
-(U_{g,\varepsilon}
--U_0)
-}
-{C_F H_{\epsilon}(r)U_0 +C_G  \bar{\alpha} \overline{U}_{K_{\epsilon},\epsilon}    U_0}
-\right\}:=T(U_0,\overline{U}_{K_{\epsilon},\epsilon},r).
-\end{equation}
-
-Note that $T$ only depends on the initial level $U_0$, the upper limit $U_{g,\varepsilon}$ and the bound on total mass $C(r)$ at time $r$, and is independent to $N$. 
-In particular, 
-\begin{equation}
-\label{eq: Compact Containment for Levels}
-\limsup_{N \to \infty}
-\mathbb{P}\left[
-\sup_{t \in [0, T(U_0,\overline{U}_{K_{\epsilon},\epsilon},r)]}
-U^N_{a}(\tau_a + t)
-\geq \overline{U}_{K_{\epsilon},\epsilon} 
-\right]  
-\leq \mathbb{P}[A_{H_{\epsilon}}]
-< \frac{\epsilon}{2 U_{g,\varepsilon}C'_g},
-\end{equation}
-so we have therefore proven compact containment condition for our level process up to time $T(U_0,\overline{U}_{K_{\epsilon},\epsilon},r)$.
-
-As a result, for all time $ 0 < t , t+ r \leq T(U_0,\overline{U}_{K_{\epsilon},\epsilon},r),$
-
-\begin{align*}
-W^N_a(t+r)-W^N_a(t) 
-\leq &\int_{t}^{t+r} 
-        \left( \frac{\theta}{N} C_G U_{g,\varepsilon}^2
-        +
-        C_F H_{\epsilon}(r) U_{g,\varepsilon}
-        \right)
-        ds\\
-=&\left( \frac{\theta}{N} C_G U_{g,\varepsilon}^2
-        +
-        C_F H_{\epsilon}(r) U_{g,\varepsilon}
-        \right) r \\
-\leq&\left( \bar{\alpha} C_G U_{g,\varepsilon}^2
-        +
-        C_F H_{\epsilon}(r) U_{g,\varepsilon}
-        \right) r
-\end{align*}
-
-Combining the results together, we have that for any $r > 0$ small enough such that 
-\begin{equation}
-r < \frac{\epsilon  }{4C'_g}\min\left\{\frac{1}{C_G U_{g,\varepsilon}}, \frac{1}{\bar{\alpha} C_G U_{g,\varepsilon}^2
-        +
-        C_F H_{\epsilon}(r) U_{g,\varepsilon}}\right\}    
-\end{equation}
-holds, then we have for all $t \leq T(U_0,\overline{U}_{K_{\epsilon},\epsilon},r)$,
-
-\begin{equation}
-\begin{aligned}
-\mathbb{E}\left[|g(U^{N}_{a}(t+r ))-g(U^{N}_{a}(t))| \mathbbm{1}_{A_{H_{\epsilon}}^c} ~|~{\cal F}_t^{
-\eta} \right] 
-& \leq  \mathbb{E}\left[C'_{g} |U^{N}_{a}(t+r )-U^{N}_{a}(t)|\mathbbm{1}_{A_{H_{\epsilon}}^c} \right] \\
-&\leq r C'_g \max\{ \bar{\alpha} C_G U_{g,\varepsilon}^2
-        +
-        C_F H_{\epsilon}(r) U_{g,\varepsilon}
-        , C_G U_{g, \varepsilon}\} \\
-        & < \varepsilon.
-\end{aligned}
-\end{equation}
-
-\textbf{Conclusion:} Combining all of the above results, for any $\epsilon > 0$, we pick arbitrary $r>0$ and
-generate $T(U_0,\overline{U}_{K_{\epsilon},\epsilon},r)$ by 
-Equation \eqref{eq: Bound on Level Hitting Time} and Equation \eqref{eq: Mass Bound Constant}.
-
-We have proven that for all $t \in [0, T(U_0,\overline{U}_{K_{\epsilon},\epsilon},r)]$,
-\begin{equation}
-\begin{aligned}
-& \mathbb{E}[|g(U^{N}_{a}(t+r ))-g(U^{N}_{a}(t))|~|~{\cal F}_t^{
-\eta}]\\
-\leq & \mathbb{E}\left[|g(U^{N}_{a}(t+r ))-g(U^{N}_{a}(t))| \mathbbm{1}_{A_{H_{\epsilon}}} ~|~{\cal F}_t^{
-\eta}\right]+ \mathbb{E}\left[|g(U^{N}_{a}(t+r ))-g(U^{N}_{a}(t))| \mathbbm{1}_{A_{H_{\epsilon}}^c} ~|~{\cal F}_t^{
-\eta}\right] \\
-< & \epsilon + \epsilon = 2\epsilon
-\end{aligned}    
-\end{equation}
-for  
-\begin{equation*}
-r < \frac{\epsilon  }{4C'_g}\min\left\{\frac{1}{C_G U_{g,\varepsilon}}, \frac{1}{\bar{\alpha} C_G U_{g,\varepsilon}^2
-        +
-        C_F H_{\epsilon}(r) U_{g,\varepsilon}}\right\}.    
-\end{equation*}
-
-We have also proven Compact Containment Condition in Equation \eqref{eq: Compact Containment for Levels}.
-
-Therefore we have proved tightness of our level processes by \cite{EK} Theorem 3.8.6.
-\end{proof}
-
-\subsection{Tightness of the Lookdown Representation}
-\begin{lemma}
-The lookdown representation satisfies the compact containment condition, 
-Equation \eqref{eq: vague compact containment condition}, 
-for all $\varepsilon > 0$ and fixed time $T > 0$, there exists $N,K> 0$ such that 
-\begin{equation}
-\liminf_{n \to \infty}\mathbb{P}\{ \xi^n_t \in \Gamma_{N,K} \text{ for all } t\in [0,T]\} > 1-\varepsilon,
-\end{equation}
-where $\Gamma_{N,K}$ is the compact set in Lemma \ref{lem: vague compact sets}
-\end{lemma}
-
-\begin{proof}
-Note that
-\begin{equation}
-\begin{aligned}
-     &1-\mathbb{P}\{ \xi^n_t \in \Gamma_{N,K} \text{ for all } t\in [0,T]\} \\
-     = & \mathbb{P}\left\{ \sup_{t \in[0,T]}\frac{1}{N}\langle 1_{\overline{\mathbb{R}^d}\times [0,N]}, \xi^n_t \rangle \geq K \right\} \\
- \leq & \frac{\mathbb{E}\left\{ \sup_{t \in[0,T]}\frac{1}{N}\langle 1_{\overline{\mathbb{R}^d}\times [0,N]}, \xi^n_t \rangle\right\}}{K}.
-\end{aligned}
-\end{equation}
-Recall that conditional on 
-$$ \frac{1}{n}\langle 1_{[0,n]}, \xi^n_t \rangle = \eta^n_t,$$
-the level of each individual is independently and uniformly distributed between $[0,n]$.
-Therefore, for $n \geq N$,
-\begin{equation}
-\frac{\mathbb{E}\left\{ \sup_{t \in[0,T]}\frac{1}{N}\langle 1_{\overline{\mathbb{R}^d}\times [0,N]}, \xi^n_t \rangle\right\}}{K}
-= \frac{\mathbb{E}\left\{ \sup_{t\in [0,T]}\langle 1, \eta^n_t \rangle \right\}}{K} < \varepsilon,
-\end{equation}
-for large enough $K>0$. 
-The last inequality is given by Lemma \ref{lem:eta_compact_containment}.
-\end{proof}
-
-It now suffices for us to show that the processes $\{(F_g(\xi^n_t))_{t \geq 0}: n \geq 1\}$ is relatively compact for all test functions $F_g$.
-To do so, we apply Aldous criterion for real-valued processes.
-
-\subsubsection{Tightness of $(F_g(\xi_t))_{t \geq 0}$}
-
-\begin{definition}
-We define $\mathfrak{G}_{\leq 1}$ to be the set of functions $g \in \mathcal{C}(\IR^d \times [0, \infty) \to \IR$ such that 
-$g(\cdot, u) \in \mathcal{C}_{0}(\IR^d)$ for all $u \geq 0$, and there exists some $u_{*}>0$ such that $g(x,u)=1$ for all $u \geq u_{*}$.
-Furthermore, for $g \in \mathfrak{G}_{\leq 1}$, define $F_g(\xi):= \exp(-\langle \log g, \cdot \rangle )$.
-\end{definition}
-
-To prove tightness of $(\xi_t)_{t \geq 0}$ in the vague topology, it suffices to prove tightness of $(F_g(\xi_t))_{t \geq 0}$ as a real-valued stochastic process.
-For a proof of this statement refer to Appendix \ref{sec: Topologies on Lookdown}.
-
-\begin{lemma}
-For all $g \in \mathfrak{G}_{\leq 1}$, the processes $\{(F_g(\xi^N_t))_{t \geq 0}: N \in \mathbb{N}\}$ is tight as a real-valued stochastic process.
-\end{lemma}
-\begin{proof}
-Once again, we intend to apply the Aldous Criterion. 
-To do so, we need to prove that for all $\epsilon > 0$,
-there exists $n_0 > 0$ and $\delta > 0$ such that 
-\begin{equation}
-\sup_{n \geq n_0}\sup_{\theta \in [0, \delta]}\mathbb{P}\{|F_g(\xi^n_{\tau+\theta})-F_g(\xi^n_{\tau})| > \epsilon\} < \epsilon
-\end{equation} 
-holds. 
-It suffices to show that for sufficiently small $\delta > 0$,
-$\limsup_{n \to \infty}\mathbb{E}[|F_g(\xi^n_{\tau_n + s})-F_g(\xi^n_{\tau_n})|^2] < \epsilon$
-for all $\theta \in [0, \delta]$.
-
-First, note that only events happening on particles with levels smaller than $u_g$ at time $\tau_n$ will contribute to the difference $|F_g(\xi^n_{\tau_n + s})-F_g(\xi^n_{\tau_n})|$.
-
-To calculate this difference, we couple $(\xi^n_{\tau_n + s})_{s \in [0,\delta]}$ with the process $(\hat{\xi}^n_{\tau_n + s})_{s \in [0,\delta]}$ which has the same level dynamics as $(\xi^n_{\tau_n + s})_{s \in [0,\delta]}$ but with no birth.
-With this coupling, 
-we have 
-$\mathbb{E}[|F_g(\xi^n_{\tau_n + s})-F_g(\xi^n_{\tau_n})|^2] \leq 2\mathbb{E}[|F_g(\xi^n_{\tau_n + s})-F_g(\hat{\xi}^n_{\tau_n + s})|^2]+ 2\mathbb{E}[|F_g(\hat{\xi}^n_{\tau_n + s})-F_g(\xi^n_{\tau_n})|^2]$
-
-We first try to control $\mathbb{E}[|F_g(\hat{\xi}^n_{\tau_n + s})-F_g(\xi^n_{\tau_n})|^2]$. 
-This difference is simply influenced by the level dynamics. Therefore,
-\begin{equation}
-\begin{aligned}
- &\mathbb{E}[|F_g(\hat{\xi}^n_{\tau_n + s})-F_g(\xi^n_{\tau_n})|^2]\\
- \leq &
- \mathbb{E}\left[ \int_{0}^{\delta} \sum_{(x,u)\in\xi^n_{\tau_n+s}}\,
-    \left|
-        \frac{\theta}{n} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q_\theta(x, dy) u^2 -b_{\theta}(x,\eta)u
-    \right|^2 \partial_u g(x,u)^2 ds\right]\\
- \leq & ||g'||_{\infty}
- \mathbb{E}\left[ \int_{0}^{\delta} \sum_{(x,u)\in\xi^n_{\tau_n+s}}\,
-    \left| \frac{\theta}{n}  \gamma(x,\eta)  u_g^2 + (2  \gamma(x,\eta) + F(x,\eta))u_g
-    \right|^2  ds\right] + O(1/\theta)\\
-\leq & ||g'||_{\infty}u_g
- \mathbb{E}_{\eta}\left[ \int_{\tau_n}^{\tau_n+\delta} \int_{\mathbb{R}^d}
-    \left| \frac{\theta}{n}  \gamma(x,\eta^n_{s})  u_g^2 + (2  \gamma(x,\eta^n_{s}) + F(x,\eta^n_{s}))u_g
-    \right|^2 \eta^N_s(dx) ds\right] + O(1/\theta),
-\end{aligned}
-\end{equation}
-so this term can be controlled with Lemma \ref{lem:tightness_for_F}.
-
-We now control 
-$\mathbb{E}[|F_g(\xi^n_{\tau_n + s})-F_g(\hat{\xi}^n_{\tau_n + s})|^2]$.
-Note that this difference is purely contributed by the number of birth with both the parent and child having levels below $u_g$,
-and the simple inequality 
-$\mathbb{E}[|F_g(\xi^n_{\tau_n + s})-F_g(\hat{\xi}^n_{\tau_n + s})|^2] \leq 4 \mathbb{P}\{|F_g(\xi^n_{\tau_n + s})-F_g(\hat{\xi}^n_{\tau_n + s})|>0\}$
-holds.
-
-Therefore it suffices to prove that within a small interval of length $\delta > 0$,
-the probability of such birth events happening is small.
-
-This term can be controlled by the uniform boundedness of $\gamma(x,m)$.
-For the birth event to contribute to the difference, the parent must have a level below $u_g$, and give birth to a child at level $u + \ell < u_g$.
-Therefore, the total rate of relevant birth events satisfies
-\begin{equation}
-\sum_{(x,u) \in \xi^n_{\tau_n}([0,u_g] \times \overline{\mathbb{R}^d})}  \gamma(x,\eta^n_{\tau_n}) \mathbbm{1}_{u+ \ell < u_g }
-\leq C_{\gamma} \xi^n_{\tau_n}([0,u_g] \times \overline{\mathbb{R}^d}.
-\end{equation}
-Therefore, with an application of Markov inequality, 
-we have
-\begin{equation}
-\begin{aligned}
-\mathbb{P}\{|F_g(\xi^n_{\tau_n + s})-F_g(\hat{\xi}^n_{\tau_n + s})|>0\}
-\leq & \mathbb{P}[Poi(C_{\gamma} \xi^n_{\tau_n}([0,u_g] \times \overline{\mathbb{R}^d})s) \geq  1]\\
-\leq & \mathbb{E}[Poi(C_{\gamma} \xi^n_{\tau_n}([0,u_g] \times \overline{\mathbb{R}^d})s)]\\
-\leq & \mathbb{E}[Poi(C_{\gamma} \xi^n_{\tau_n}([0,u_g] \times \overline{\mathbb{R}^d})s)]\\
-\leq & C_{\gamma}  \mathbb{E}[\xi^n_{\tau_n}([0,u_g] \times \overline{\mathbb{R}^d})]s\\
-\leq & C_{\gamma}  u_g\mathbb{E}[\eta^n_{\tau_n}(\overline{\mathbb{R}^d})]s\\
-<&  \epsilon.
-\end{aligned}
-\end{equation}
-
-Combining all inequalities above, we have established Aldous Criterion and thus, tightness for the lookdown representation. 
-\end{proof}
-
-% % % % % % % % % % % % %
-\subsubsection{Convergence of generators for the lookdown process}
-    \label{sec:lookdown_generator_proofs}
-
-\comment{
-    I did this informal writeup of convergence of the lookdown generator
-    without looking at the previous version
-    mostly to double-check what we have there
-    (which is probably better).
-}
-
-In Definition~\ref{defn:lookdown_mgale} we saw that the generator
-of $(\lp_t)_{t \ge 0}$ is the sum of two parts,
-equations \eqref{eqn:birth_generator} and \eqref{eqn:level_generator}.
-Assume that there is a $u_*$ such that $g(x, u) = 1$ for all $u \ge u_*$.
-We consider these two in turn.
-
-First, the contribution from births is
-\begin{align*}
-\begin{split}
-f(\lp)
-&\mapsto
-    f(\lp)
-    \sum_{(x, u) \in \lp}
-    2 \gamma(x, \eta)
-    \bigg\{
-        \frac{1}{2 N}
-        \int_u^N
-        g(x, u_1) du_1
-        \frac{
-            \theta \int_{\IR^d} (g(y, u) - g(x, u)) r(y, \eta) q(x, dy)
-        }{
-            g(x, u)
-        }
-    \\ & \qquad \qquad \qquad {}
-        + \frac{\theta}{N}
-        \int_u^N \int_{\IR^d}
-        \left( \frac{g(y, u_1) + g(x, u_1)}{2} - 1 \right)
-        r(y, \eta) q(x, dy)
-    \bigg\}
-    .
-    \end{split}
-\end{align*}
-We have that
-\begin{align*}
-    &\theta \int_{\IR^d} (g(y, u) - g(x, u)) r(y, \eta) q(x, dy) \\
-    &\qquad =
-    \theta \int_{\IR^d} (r(y, \eta) g(y, u) - r(x, \eta) g(x, u)) q(x, dy)
-    - \theta \int_{\IR^d} g(x, u) (r(y, \eta) - r(x, \eta)) q(x, dy) \\
-    &\qquad \to
-    \DG(gr)(x) - g(x) \DG r(x) \qquad \text{as }N \to \infty.
-\end{align*}
-i.e., to
-$\DG\left(g(\cdot, u) r(\cdot, \smooth{r}\eta(\cdot))\right)(x)
-- g(\cdot, u) \DG\left(r(\cdot, \smooth{r}\eta(\cdot))\right)(x)$.
-Furthermore, by our assumption on $g$,
-$\int_u^N g(x, u_1) du_1 / N \to 1$ for all $x$ and $u$,
-so the first term here converges to
-\begin{align*}
-    \gamma(x, \eta)
-        \frac{
-            \DG\left( g(\cdot, u) r(\cdot, \smooth{r}\eta(\cdot))\right)(x)
-            -
-            g(\cdot, x) \DG\left( r(\cdot, \smooth{r}\eta(\cdot))\right)(x)
-        }{
-            g(x, u)
-        } .
-\end{align*}
-This corresponds to each particle moving according to the motion induced by
-$g \mapsto \gamma \DG(gr) - g \DG r$.
-\comment{TODO: explain the $r$-tilted $\DG$ motion somewhere earlier, introducing notation for it.}
-As for the second term,
-since $\int g(y, u_1) q(x, dy) \to g(x, u_1)$
-and $\theta/N \to \alpha$,
-it converges to
-\begin{align*}
-    2 \alpha
-    \gamma(x, \eta)
-    r(x, \eta) 
-    \int_u^\infty
-    \left( g(x, u_1) - 1 \right)
-    du_1
-\end{align*}
-This corresponds to births at higher levels at rate $2 \alpha \gamma r$.
-
-The remaining term is \eqref{eqn:level_generator}:
-\begin{align*}
-    f(\lp)
-    \mapsto
-    f(\lp)
-    \sum_{(x, u) \in \lp}
-    \left(
-    \theta
-        N^{-1} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
-        -
-        b(x, \eta)u
-    \right)
-    \frac{\partial_u g(x,u)}{g(x,u)} .
-\end{align*}
-The first part only uses the fact that $\theta/N \to \alpha$,
-while as noted in \eqref{eqn:b_limit}, $b$ converges to $\gamma \DG r + F$,
-so in total this term converges to
-\begin{align*}
-    f(\lp)
-    \mapsto
-    f(\lp)
-    \sum_{(x, u) \in \lp}
-    \left(
-    \alpha
-        \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
-        -
-        \left\{
-            \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta)
-        \right\} u
-    \right)
-    \frac{\partial_u g(x,u)}{g(x,u)} .
-\end{align*}
-In other words, the level of a particle at $x$ evolves according to
-\begin{align*}
-    \dot u
-    =
-    \alpha
-        \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
-        -
-        \left\{
-            \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta)
-        \right\} u .
-\end{align*}
-
-% % % % % % % % % % % % %
-\subsection{Motion of ancestral lineages}
-
-In this section we prove Theorem~\ref{thm:lineages}.
-The argument follows directly from the discussion in Section \ref{sec:limiting_lines_of_descent}.
-
-\begin{proof}[of Theorem~\ref{thm:lineages}]
-
-\comment{(TODO: Use notation for the motion of a lineage introduced in statement of theorem.)}
-
-Here
-\comment{(and in the statement of the theorem)}
-we take the high-density, deterministic limit
-(so, $\theta, N \to \infty$ and $\theta/N \to 0$)
-and so suppose that the limiting process has density $\varphi_t(x)$
-at location $x$ and time $t$.
-Let $Y$ denote the spatial motion followed by a single line of descent.
-Above equation~\eqref{eqn:limiting_generator},
-we showed that $Y$ is a diffusion with generator at time $s$
-$$
-    \mathcal{L}^Y_s g(x) = \gamma ( \DG(rg)(x) - g \DG r(x) ) .
-$$
-The diffusion is time-inhomogeneous if the density is not constant with time
-(since recall that the coefficients $\gamma$ and $r$ depend on the density).
-Formally, the intensity of levels at $y$ at time $t$
-that are descended from individuals that were at $x$ at time $s$
-(with $s < t$) is
-\begin{equation} \label{eqn:formal_intensity}
-    \varphi_s(x) \IE_{s,x} \left[
-        \exp\left(
-            \int_s^t (F + \gamma \DG r)(Y_u) du
-        \right)
-        \ind_{Y_t = y}
-    \right]
-    dy ,
-\end{equation}
-where the subscript $s, x$ in the expectation indicates that $Y_s = x$.
-To see why this should be true, 
-suppose that an ancestor has level $v$. Conditional on its 
-spatial motion $\{Y_u\}_{s\leq u\leq t}$, its level at time $t$ will
-be $v \exp(-\int_s^t(F+\gamma\Delta r)(Y_u)du)$. This will be less than a given level 
-$N$ if $v < N \exp(\int_s^t(F+\gamma\Delta r)(Y_u)du)$. 
-The intensity of levels at $y$ that are descended from individuals at
-$x$ can therefore be obtained as the limit as $N\to\infty$ of 
-$1/N$ times the number of levels at $x$ at time zero with
-$u<N \exp(\int_s^t(F+\gamma\Delta r)(Y_u)du)$ and for which
-the corresponding individual is at $y$ at time $t$, which is 
-precisely the quantity in~\eqref{eqn:formal_intensity}.
-
-By our construction in Section~\ref{sec:limiting_lines_of_descent},
-when we integrate~\eqref{eqn:formal_intensity}
-with respect to $x$ we recover $\varphi_t(y)dy$. 
-Consider an individual sampled at location $y$ at time $t$,
-and write $p(t,s,y,x)$ for the probability density
-that their ancestor at time $s$ was at $x$.
-As a consequence of~\eqref{eqn:formal_intensity},
-still formally,
-\begin{equation}
-\label{eqn:ptsyx}
-    p(t,s,y,x)
-    =
-    \frac{\varphi_s(x)}{\varphi_t(y)}
-    \IE_{s,x}\left[
-        \exp\left( \int_s^t (F + \gamma\DG r)(Y_u) du \right)
-        \ind_{Y_t=y}
-    \right]
-\qquad \text{ for } s < t.
-\end{equation}
-
-To make~(\ref{eqn:ptsyx}) meaningful, we multiply by suitable test functions
-$f$ and $g$ and integrate.
-\begin{align*}
-&\int \int f(y) \varphi_t(y) p(t,s,y,x) g(x) dy dx \\
-&\qquad =
-\int g(x) \varphi_s(x)
-\IE_{x,s}\left[
-    \exp\left(
-        \int_s^t(F+\gamma\DG r)(Y_u)du
-    \right)f(Y_t)
-\right] dx .
-\end{align*}
-
-Writing $\hat{T}_{t,s}$ for the time-inhomogeneous semigroup
-corresponding to the motion of ancestral lineages backwards in time
-(that is, $\hat{T}_{t,s} f(y) = \int p(t,s,x,y) f(x) dy$),
-we can write this as 
-$$
-    \int f(y)\varphi_t(y)\hat{T}_{t,s}g(y)dy
-    =
-    \int g(x) \varphi_s(x)
-        \IE_{s,x} \left[
-            \exp\left(
-                \int_s^t(F+\gamma\DG r)(Y_u)du
-            \right)f(Y_t)
-        \right]dx.
-$$
-Differentiating with respect to $t$ at $t=s$, and writing 
-$\Lgen_s$ for the generator of $\hat{T}_{t,s}$ at time $s$, we find
-\begin{align*}
-&
-    \int f(y) \left\{
-        \varphi_s(y) \Lgen_s g(y)
-        + \left(
-            r(y) \DG^*(\gamma \varphi_s)(y) + \varphi_s(y) F(y)
-        \right) g(y)
-    \right\} dy \\
-&\qquad =
-    \int g(x) \varphi_s(x) \left(
-        {\mathcal L}^Y_s f(x) + (F(x)+\gamma(x) \DG r(x)) f(x)
-    \right) dx \\
-&\qquad =
-    \int f(x) \left(
-        ({\mathcal L}^Y_s)^* (\varphi_s g)(x) + (F(x) + \gamma(x) \DG r(x)) \varphi_s(x) g(x)
-    \right) dx ,
-\end{align*}
-where $({\mathcal L}^Y_s)^*$ is the adjoint of ${\mathcal L}^Y_s$
-and we have used that $\varphi_s$ solves $\dot \varphi = r \DG^*(\gamma \varphi) + F \varphi$.
-Since $f$ was arbitrary,
-\begin{eqnarray*}
-\Lgen_s g
-    &=&
-    \frac{1}{\varphi_s} \left[
-        ({\mathcal L}^Y_s)^* (\varphi_s g)
-        + \gamma \varphi_s g \DG(r)
-        - r g \DG^*(\gamma \varphi_s)
-    \right] .
-\end{eqnarray*}
-(Note that the $\phi_s F g$ terms have cancelled.)
-Since the adjoint of ${\mathcal L}^Y_s$ is
-\begin{align*}
-    ({\mathcal L}^Y_s)^* f
-    &=
-    r \DG^* (\gamma f) - \gamma f \DG r ,
-\end{align*}
-we can rewrite the generator of a lineage as 
-\begin{eqnarray*}
-\Lgen_s g
-    &=&
-    \frac{r}{\varphi_s} \left[
-        \DG^* (\gamma \varphi_s g)
-        - g \DG^*(\gamma \varphi_s)
-    \right] .
-\end{eqnarray*}
-This is equation \eqref{eqn:lineage_generator}.
-
-To simplify to equation \eqref{eqn:lineage_generator2},
-this, first define
-$
-    \DD f(x) = \sum_{ij} \covq_{ij} \partial_{ij} f(x),
-$
-% and note that $\DD$ satisfies the following identity:
-% \begin{align}
-%     \DD(fg)
-%     &=
-%     f \DD g
-%     + 2 (\covq \grad f) \cdot \grad g
-%     + g \DD f .
-% \end{align}
-and so the adjoint of $\DD$ is
-$$
-    \DD^* f(x)
-    =
-    \sum_{ij} \partial_{ij} (\covq_{ij} f(x)) .
-$$
-Note that $\DD^*$ satisfies the following identity:
-\begin{align*}
-    \DD^*(fg)
-%     &=
-%     \sum_{ij} \left\{
-%         g \partial_{ij} (\covq_{ij} f)
-%         + 2 \partial_{i} (\covq_{ij} f) \partial_j(g)
-%         + \covq_{ij} f \partial_{ij} g
-%     \right\} \\
-    &=
-    \sum_{ij} \left\{
-        g \partial_{ij} (\covq_{ij} f)
-        + 2 f \partial_{i} (\covq_{ij}) \partial_j(g)
-        + 2 \covq_{ij} \partial_{i} (f) \partial_j(g)
-        + \covq_{ij} f \partial_{ij} g
-    \right\} \\
-    &=
-    g \DD^* f
-    + 2 f \vec{c} \cdot \grad g
-    + 2 (C \grad f) \cdot \grad g
-    + f \DD g ,
-\end{align*}
-where $\vec{c}_j = \sum_i \partial_j C_{ij}$.
-So, with $f = \gamma \varphi_s$,
-\begin{eqnarray*}
-\Lgen_s g
-    &=&
-    \frac{r}{\varphi_s} \left[
-        \DD^*(\gamma \varphi_s g) - \grad \cdot (\gamma \varphi_s g \meanq)
-        - g \DD^*(\gamma \varphi_s) + g \grad \cdot (\gamma \varphi_s \meanq)
-    \right] \\
-    &=&
-    \frac{r}{\varphi_s} \left[
-        \gamma \varphi_s \DD g
-        + 2 \gamma \varphi_s \vec{c} \cdot \grad g
-        + 2 (C \grad (\gamma \varphi_s)) \cdot \grad g
-        - \gamma \varphi_s \meanq \cdot \grad g
-    \right] \\
-    &=&
-    r \gamma \left[
-        \DD g
-        + 2 \vec{c} \cdot \grad g
-        + 2 (C \grad \log(\gamma \varphi_s)) \cdot \grad g
-        - \meanq \cdot \grad g
-    \right] ,
-\end{eqnarray*}
-which is equation \eqref{eqn:lineage_generator}.
-
-\end{proof}
-
-\begin{proof}[of Corollary \ref{cor:lineages_simple}]
-
-In this section, we need only
-simplify equation \eqref{eqn:lineage_generator}
-in the case where $\covq = \sigma^2 I$.
-
-    \comment{TODO}
-
-\end{proof}
-
-\begin{proof}[of Corollary~\ref{cor:wavefront}
-    \comment{
-        TODO make non-redundant with proof of Theorem \ref{thm:lineages}.
-    }
-
-Let $Y$ denote the diffusion followed by following a single descendent line in this frame; 
-i.e.~the diffusion with generator ${\cal L}^Y\phi=\gamma\Delta(r\phi)-\gamma\phi\Delta r -\mathfrak{c}\nabla\phi $.
-Note in particular here we take $\mathcal{B}=\Delta$.
-We start by expressing the evolution of a singles ancestry line in terms of the descendent line $Y$.
-
-Formally, the intensity of levels at $y$ at time $t$ that are descended from 
-individuals that were at $x$ at time $0$ is
-\begin{equation}
-\label{formal intensity}
-w(x)\IE_x\left[\exp\left(\int_0^t (F+\gamma \Delta r)(Y_s)ds\right)\ind_{Y_t=y}\right]dy,
-\end{equation}
-where the subscript $x$ in the expectation indicates that $Y_0=x$.
-To see why this should be true, 
-suppose that an ancestor has level $u$. Conditional on its 
-spatial motion $\{Y_s\}_{0\leq s\leq t}$, its level at time $t$ will
-be $u\exp(-\int_0^t(F+\gamma\Delta r)(Y_s)ds)$. This will be less than a given level 
-$N$ if $u<N \exp(\int_0^t(F+\gamma\Delta r)(Y_s)ds)$. 
-The intensity of levels at $y$ that are descended from individuals at
-$x$ can therefore be obtained as the limit as $N\to\infty$ of 
-$1/N$ times the number of levels at $x$ at time zero with
-$u<N \exp(\int_0^t(F+\gamma\Delta r)(Y_s)ds)$ and for which
-the corresponding individual is at $y$ at time $t$, which is 
-precisely the quantity in~(\ref{formal intensity}).
-
-It is easy to check that when we integrate~(\ref{formal intensity})
-with respect to $x$ we recover $w(y)dy$. 
-As a consequence of~(\ref{formal intensity}), writing $p(t,y,x)$ for
-the probability density that the ancestor $t$ units in 
-the past of an individual sampled 
-at $y$ was at $x$, then, still formally,
-\begin{equation}
-\label{ptyx}
-p(t,y,x)=\frac{w(x)}{w(y)}\IE_x\left[\exp\left(\int_0^t (F+\gamma\Delta r)(Y_s)ds\right)
-\ind_{Y_t=y}\right].
-\end{equation}
-
-To make~(\ref{ptyx}) meaningful, we multiply by suitable test functions and 
-integrate.
-$$\int\int \psi(y)w(y)p(t,y,x)\phi(x)dydx=\int\phi(x)w(x)
-\IE_x\left[\exp\left(\int_0^t(F+\gamma\Delta r)(Y_s)ds\right)\psi(Y_t)\right]dydx.$$
-
-Writing $\hat{T}_t$ for the semigroup corresponding to the motion of 
-ancestral lineages backwards in time (that is the semigroup corresponding
-to $p(t,x,y)$), we can write this as 
-$$\int \psi(y)w(y)\hat{T}_t\phi(y)dy=\int\phi(x)w(x)
-\IE_x\left[\exp\left(\int_0^t(F+\gamma\Delta r)(Y_s)ds\right)\psi(Y_t)\right]dx.$$
-Differentiating with respect to $t$ at $t=0$, and writing 
-$\hat{\mathcal L}$ for the generator of $\hat{T}_t$, we find
-\begin{eqnarray*}
-\int \psi(y)w(y)\widehat{\mathcal L}\phi(y)dy&=&
-\int\phi(x)w(x)\left({\mathcal L}^Y\psi(x)+\psi(x)(F+\gamma\Delta r)\psi(x)\right)dx\\
-&=&\int\phi(x)w(x)\left(\gamma\Delta(r\psi)-\gamma\psi\Delta r -\mathfrak{c}\nabla\psi 
-+(F+\gamma\Delta r)(\psi)\right)dx\\
-&=&\int\phi(x)w(x)\left(\gamma\Delta(r\psi)-\mathfrak{c}\nabla\psi+F(\psi)\right)dx\\
-&=&
-\int\psi(x)\left[r\Delta(\gamma \phi w)+F\phi w+\mathfrak{c}\nabla(\phi w)\right]dx.
-\end{eqnarray*}
-Since $\psi$ was arbitrary,
-\begin{eqnarray*}
-\hat{\mathcal L}\phi&=&\frac{1}{w}\left[ r\Delta (\gamma\phi w)+F\phi w
-+\mathfrak{c}\nabla(\phi w)\right]\\
-&=&\frac{\phi}{w}\left[r\Delta(\gamma w)+Fw+\mathfrak{c}\nabla w\right]
-+\frac{1}{w}\left[r\gamma w\Delta \phi +2\nabla (\gamma w)
-\nabla\phi+\mathfrak{c}w\nabla\phi\right]\\
-&=&r\gamma\left(\Delta\phi+2\frac{\nabla(\gamma w)}{\gamma w}\nabla\phi\right)
-+\mathfrak{c}\nabla\phi,
-\end{eqnarray*}
-where we have used that $w$ solves~(\ref{profile}).
-
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\appendix
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\section{Results on Lookdown Representations}
-    \label{sec: Markov Mapping Theorem Application}
-\subsection{Generators for the spatial processes}
-Before defining the generator of the lookdown representations, 
-we recall the generator of the spatial processes.
-
-We first define our pre-limit
-$(\eta^{N}(t))_{t>0}$ as a solution
-to a Martingale Problem
-with generator $\Pgen^{N}$.
-
-\begin{definition}
-    \label{def2: MP definition of pre-limit}
-Let $F \in \mathcal{C}^{2}(\IR)$ and $f \in \mathcal{C}_{0}(\IR^d)$.
-We define $\Pgen^N$ to be a generator
-acting on test functions of the form
-$F_f(\eta):=F (\langle f, \eta \rangle)$
-such that 
-\begin{equation}
-\begin{aligned}
-\Pgen^{N} F_f(\eta):=& \int_{\IR^d} \theta\gamma(x, \eta) \left\{\int_{\IR^d} \left\{F(\langle f, \eta \rangle + f(y)/N )-F(\langle f, \eta \rangle )\right\}r(y, \eta)q_{\theta}(x,dy)\right\}N\eta(dx)\\
-&+\int_{\IR^d} \theta \mu(x, \eta) \left\{F(\langle f, \eta \rangle - f(x)/N )-F(\langle f, \eta \rangle )\right\}N\eta(dx).
-\end{aligned}    
-\end{equation}
-In this case, our pre-limit model $(\eta^{N}(t))_{t \geq 0}$ is the solution to the Martingale Problem $(\Pgen^{N}, \eta_0)$, i.e. 
-for all $F \in \mathcal{C}^{2}(\IR)$
-and $f \in \mathcal{C}_{0}(\IR^d)$,
-$$M_t:=F_f(\eta^{N}_t)-F_f(\eta_0)
--\int_{0}^{t}\Pgen^{N}F_f(\eta^{N}_s)ds$$
-is a martingale, and the initial condition is distributed as a Poisson measure with mean measure $\eta_0$.
-\end{definition}
-
-\begin{remark}
-Taking $F(x)=x$ and $F(x)=x^2$, we can recover Equation \eqref{eqn:limiting_mgale_problem} and \eqref{eqn:limiting_mgale_variation} for the limit.
-Similarly, we can recover
-Definition \ref{defn:mgale_construction},
-an equivalent characterisation
-of our pre-limit model.
-\end{remark}
-
-We now write the candidate generator for the limiting object.
-
-\begin{definition}
-    \label{def2: MP definition of limit}
-Let $F \in \mathcal{C}^{2}(\IR)$ and $f \in \mathcal{C}_{0}(\IR^d)$.
-We define $\Pgen$ to be a generator
-acting on test functions of the form
-$F_f(\eta):=F (\langle f, \eta \rangle)$
-such that 
-\begin{equation}
-    \label{eq: Limit Generator Definition}
-\begin{aligned}
-\Pgen^{\infty} F_f(\eta):=& F'(\langle f, \eta \rangle)
-                   \times \left\{
-                   \big\langle
-                        \gamma(x, \smooth{\gamma} \eta(x))
-                            \mathcal{B}\left(
-                            f(\cdot) r(\cdot, \smooth{r} \eta(\cdot))
-                            \right)(x)
-                    +
-                    f(x)
-                        F(x, \smooth{F} \eta(x)),
-                        \eta(dx)
-                    \big\rangle
-                   \right\}\\
-                &+ \alpha F''(\langle f, \eta \rangle)
-                  \times \left\{
-                  \big\langle
-                    \gamma \left( x, \eta \right)
-                    r\left(x,\eta \right)
-                    f^2(x),
-                    \eta (dx)
-                    \big\rangle 
-                  \right\}.
-\end{aligned}    
-\end{equation}
-We define $(\eta^{\infty}(t))_{t \geq 0}$ to be the solution to the Martingale Problem $(\Pgen^{\infty}, \eta_0)$, i.e. 
-for all $F \in \mathcal{C}^{2}(\IR)$
-and $f \in \mathcal{C}_{0}(\IR^d)$,
-$$M_t:=F_f(\eta^{\infty}_t)-F_f(\eta_0)
--\int_{0}^{t}\Pgen^{\infty}F_f(\eta^{\infty}_s)ds$$
-is a martingale, with initial condition distributed as a Poisson measure with mean measure $\eta_0$.
-\end{definition}
-
-\subsubsection{Convergence of the Generators for the Spatial Models}
-
-Here, just as a sanity check, 
-we make sure that the limiting generator is indeed the limit of the generators.
-
-\begin{lemma}[Identifying the limit as a solution to the martingale problem]
-    \label{lem:limit_mgale}
-As $N \to \infty$,
-$(\eta^{N}_t)_{t \geq 0}$ converges in $\mathcal{D}_{[0,\infty)}(\mathcal{M}_f(\IR^d))$
-to $(\eta^{N}(t))_{t \geq 0}$.
-\end{lemma}
-\begin{proof}
-We use Theorem 4.8.10 in \cite{EK}.
-First of all, the set of functions
-$\{F_f(\eta):= F(\langle f, \eta \rangle ),~
-F \in \mathcal{C}^{2}(\IR), ~
-f \in \mathcal{C}_{0}(\IR^d)\}$
-is a dense and convergence-determining 
-subset of functions in $\mathcal{M}_f(\IR^d)$.
-Therefore, it suffices to show that for any $t>0$,
-\begin{equation}
-    \label{eq: Convergence Condition}
-\lim_{N \to \infty}
-\mathbb{E}\left[
-\left(
-F_f(\eta^{N}_{t+\tau})-F_f(\eta^{N}_t)
--\int_{t}^{t+\tau}\Pgen^{\infty}F_f(\eta^{N}_s)ds
-\right)
-\prod_{i=1}^{k}\langle h_i,\eta^{N}_{t_i} \rangle
-\right]=0
-\end{equation}
-for all $k\geq 0$, $0\leq t_1<t_2<...,t_k \leq t < t+\tau$,
-and $h_1,...,h_k \in \mathcal{C}_{0}(\IR^d)$.
-
-To prove this,
-we make use of the Martingale Problem characterisation
-of $(\eta^{N}_t)_{t \geq 0}$.
-From Definition \ref{def: MP definition of pre-limit},
-we can apply Tower Law
-and obtain that
-\begin{equation}
-    \label{eq: Prelimit MP Application}
-\lim_{N \to \infty}
-\mathbb{E}\left[
-\left(
-F_f(\eta^{N}_{t+\tau})-F_f(\eta^{N}_t)
--\int_{t}^{t+\tau}\Pgen^{N}F_f(\eta^{N}_s)ds
-\right)
-\prod_{i=1}^{k}\langle h_i,\eta^{N}_{t_i} \rangle
-\right]=0
-\end{equation}
-for all $k\geq 0$, $0\leq t_1<t_2<...,t_k \leq t < t+\tau$,
-and $h_1,...,h_k \in \mathcal{C}_{0}(\IR^d)$.
-
-Therefore, it suffices to show that 
-\begin{equation}
-    \label{eq: Convergence of Spatial Generator}
-\lim_{N \to \infty}
-\mathbb{E}\left[
-\int_{t}^{t+\tau}
-\left|
-\Pgen^{N}F_f(\eta^{N}_s)
--\Pgen^{\infty}F_f(\eta^{N}_s)
-\right|
-ds
-\times 
-\prod_{i=1}^{k}\langle h_i,\eta^{N}_{t_i} \rangle
-\right]=0
-\end{equation}
-We apply Taylor Expansion
-around the term $F(\langle f, \eta \rangle )$
-up to third order.
-This gives
-\begin{equation}
-    \label{eq: Taylor Expansion calculations i}
-\begin{aligned}
-&F(\langle f, \eta \rangle + f(y)/N )-F(\langle f, \eta \rangle )\\
-=& F'(\langle f, \eta \rangle ) \frac{f(y)}{N}
-+\frac{1}{2}F''(\langle f, \eta \rangle ) \frac{f^2(y)}{N^2}
-+\frac{1}{6}F'''(w ) \frac{f^3(y)}{N^3}
-\end{aligned}
-\end{equation}
-for some $w \in [\langle f, \eta \rangle, \langle f, \eta \rangle+ ||f||/N]$.
-Similarly,
-\begin{equation}
-    \label{eq: Taylor Expansion calculations ii}
-\begin{aligned}
-&F(\langle f, \eta \rangle - f(x)/N )-F(\langle f, \eta \rangle )\\
-=& - F'(\langle f, \eta \rangle ) \frac{f(x)}{N}
-+\frac{1}{2}F''(\langle f, \eta \rangle ) \frac{f^2(x)}{N^2}
--\frac{1}{6}F'''(v ) \frac{f^3(x)}{N^3}
-\end{aligned}
-\end{equation}
-for some $v \in [\langle f, \eta \rangle - ||f||/N, \langle f, \eta \rangle ]$.
-
-We may now rewrite $\mathcal{P}^NF(\langle f, \eta \rangle)$ as 
-\small
-\begin{equation} 
-    \label{eq: Pre-Limit Generator Expanded}
-\begin{aligned}
-\Pgen^{N} F_f(\eta):=& F'(\langle f, \eta \rangle)\int_{\IR^d}  \theta\left\{\int_{\IR^d} \left\{f(y)\gamma(x, \eta) r(y,\eta) -f(x)\mu(x, \eta)\right\}q_{\theta}(x,dy)\right\}\eta(dx)\\
-&+\frac{1}{2}\frac{\theta}{N}F''(\langle f, \eta \rangle)\int_{\IR^d} 
- \left\{\gamma(x, \eta)\int_{\IR^d} \left\{f^2(y) r(y,\eta) \right\}q_{\theta}(x,dy)+f^2(x)\mu(x, \eta)\right\}\eta(dx)\\
-&+\frac{1}{6}\frac{\theta}{N^2}\int_{\IR^d}\left\{ 
-F'''(w) \left\{\gamma(x, \eta)\int_{\IR^d} f^3(y) r(y,\eta) q_{\theta}(x,dy)\right\}-F'''(v)f^3(x)\mu(x, \eta)\right\}\eta(dx)
-\end{aligned}    
-\end{equation}
-\normalsize
-for some $w,v \in [\langle f,\eta \rangle - ||f||/N, \langle f,\eta \rangle + ||f||/N]$.
-
-As $N\to \infty$, 
-$\theta/N \to \alpha$, 
-$\theta/N^2 \to 0$,
-and 
-$$\int_{\IR^d} f^m(y) r(y,\eta) q_{\theta}(x,dy) \to f^m(x)r(x, \eta)$$
-for $m=2,3$,
-the third term in Equation \eqref{eq: Pre-Limit Generator Expanded} vanishes
-while the second term converges to
-that of Equation \eqref{eq: Limit Generator Definition}.
-Furthermore,
-$\mu(x,\eta) = r(x,\eta)\gamma(x,\eta)-\frac{1}{\theta}F(x,\eta) \to r(x,\eta)\gamma(x,\eta),$
-so $f^2(x)\mu(x,\eta) \to r(x,\eta)\gamma(x,\eta) f^2(x)$.
-
-Finally, by Equation \eqref{mean measure},
-\eqref{eqn:rewritten mean measure}, \eqref{eqn:near_critical} and
-\eqref{limit of mean measure equation},
-we have 
-\begin{multline}
- \theta\left\{\int_{\IR^d} \left\{f(y)\gamma(x, \eta) r(y,\eta) -f(x)\mu(x, \eta)\right\}q_{\theta}(x,dy)\right\}
- \\
-\to \gamma(x, \eta)                           \mathcal{B}\left(
-                            f(\cdot) r(\cdot, \eta)
-                            \right)(x)
-                    +
-                    f(x)
-                        F(x, \eta),
-\end{multline}
-so comparing terms we have
-\begin{equation}
-\lim_{N\to \infty} |\mathcal{P}^{N}F\langle f, \eta \rangle - \mathcal{P}^{\infty}F\langle f, \eta \rangle| \to 0,   
-\end{equation}
-and so by Dominated Convergence Theorem,
-we establish Equation 
-\eqref{eq: Convergence of Spatial Generator}
-which concludes our proof.
-\end{proof}
-
-\subsection{Generator of Lookdown Representations}
-
-We now define the generator of the lookdown representations.
-\begin{definition}[Martingale Problem Characterisation]
-    \label{defn:lookdown_mgale}
-For given positive values of $N$ and $\theta$
-and $\lp_0 \in \mathcal{M}_F(\IR^d \times [0,N])$,
-we define $(\lp^{N}_t)_{t \geq 0}$
-to be the unique solution to the martingale problem
-with initial condition $\lp_0$ and generator $A^{N}$ that satisfies
-\begin{equation*}
-\begin{split}
-& A^{N}f(\lp ) \\
-&\quad =
-    f(\lp)
-    \,\sum_{(x,u)\in \lp}\,
-    2 \gamma(x, \eta)
-    \Bigg\{ \frac{1}{2N} \int_u^N g(x,u_1) du_1
-            \frac{
-                \theta \int_{\IR^d}
-                (g(y,u) - g(x,u))
-                r(y, \eta) q_{\theta}(x,dy)
-            }{ g(x,u) }
-        \\
-    &\qquad\qquad\qquad\qquad\qquad\qquad\qquad {} +
-        \frac{\theta}{N} \int_u^N
-        \int_{\IR^d}\left(
-            \frac{ g(y,u_1) + g(x,u_1) }{ 2 } - 1
-        \right)
-        r(y, \eta) q_{\theta}(x,dy)
-        du_1
-    \Bigg\}\\
-    &\qquad\qquad {} +
-    f(\lp) \sum_{(x,u)\in\lp}\,
-    \left(
-        \frac{\theta}{N} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q_\theta(x, dy) u^2 -b_{\theta}(x,\eta)u
-    \right)
-    \frac{\partial_u g(x,u)}{g(x,u)}
-    ,
-\end{split}
-\end{equation*}
-for all smooth functions $g \in C^{2}_{0}(\IR^d)$,
-where $f(\lp) = \prod_{(x, u) \in \lp} g(x, u)$ as defined in \eqref{eqn:test_functions},
-and $\eta(\cdot) = \lp(\cdot \times [0, N]) / N$ is the scaled spatial pushforward of $\lp$,
-as before.
-\end{definition}
-
-Similarly, 
-we define the generator for the lookdown representation of the limiting spatial model.
-
-\begin{definition}[Martingale Problem Characterisation, $N=\infty$]
-    \label{defn:limiting_lookdown_mgale}
-    For a given value of $\alpha \in [0, \infty)$,
-    define the operator $A$ acting on test functions of the form
-    $f(\xi) = \prod_{(x, u) \in \xi} g(x, u)$ with $g \in C_0^2(\IR^d \times [0, \infty))$
-    and for which there exists a $u_0$ with $g(x, u) = 1$ for all $u > u_0$.
-    Then, let $A f$ be
-    \begin{equation}
-    \begin{aligned} \label{eqn:limiting_lookdown_generator}
-    A f(\lp)
-    =&
-        f(\lp)  \sum_{(x, u) \in \xi}
-        \gamma(x, \eta)
-            \frac{
-                \DG(g(\cdot, u) r(\cdot, \eta))(x) - g(x,u) \DG r(x,\eta)
-            }{
-                g(x, u)
-            }
-    \\ &+
-        f(\lp) \sum_{(x, u) \in \xi}
-        2 \alpha \gamma(x,\Xi)r(x,\Xi) \int_u^\infty (g(x, u_1) - 1) du_1
-    \\ &+
-        f(\lp) \sum_{(x, u) \in \xi}
-        \left(
-            \alpha \gamma(x,\Xi)r(x,\Xi) u^2
-            -
-            \left\{
-                \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta)
-            \right\} u
-        \right)
-        \frac{\partial_u g(x, u)}{ g(x,u) }  .
-    \end{aligned}
-    \end{equation}
-
-    We say that a $\lpmeasures$-valued process $(\xi_t)_{t \ge 0}$
-    is a solution to the $(A, \lp_0)$ martingale problem
-    if it has initial distribution $\lp_0$
-    and $f(\lp_t) - \int_0^t Af(\lp_s) ds$ is a martingale for all $f$
-    as defined above.
-\end{definition}
-
-\subsubsection{Exact Statement on Markov Mapping Theorem results}
-
-\begin{theorem}
-\label{teo: lookdown on pre-limit well defined}
-For each $N \in \mathbb{N}$,
-there exists a solution $(\lp^N_t)_{t \geq 0}$ to the $(A^N, \lp^N_0)$ martingale problem.
-Furthermore, if we define $\Xi^N_t = \frac{1}{N}\lp^N_t(dx \times [0,N])$ for $t \geq 0$,
-then the pre-limiting model $(\eta^N_t(dx))_{t \geq 0}$ defined in Definition \ref{defn:mgale_construction}
-and $(\Xi^N_t(dx))_{t \geq 0}$
-shares the same distribution on $\mathcal{D}_{\mathcal{M}(\mathbb{R}^d)}[0,\infty)$.
-
-Finally, 
-for all $h\in \mathcal{C}(\mathbb{R}^d \times [0, N])$
-\begin{equation}\label{Markov Mapping Theorem Cox Condition}
-\mathbb{E}\left[e^{-\int_{\mathbb{R}^d \times [0,N]} h(x,u) \xi^{N}(dx \times du)}\bigg| \mathcal{F}^{\Xi^{N}}_t\right]=e^{-\int F^{N}_h(x) \Xi^{N}_t(dx)},
-\end{equation}
-where 
-$$F^{\epsilon,\theta,N}_h(x):=-N\log \left(\frac{1}{N}\int_{0}^{N}e^{-h(x,u)}du\right)=-N\log \left(1-\frac{1}{N}\int_{0}^{N}(1-e^{-h(x,u)})du\right).$$
-In other words,
-conditioned on the spatial configuration $\Xi^N_t$,
-the levels of the particles must be i.i.d uniformly between $[0,N]$.
-
-\end{theorem}
-
-The statement for the limiting case is similar,
-with the only difference being the conditional distribution 
-of the levels given the spatial projection.
-
-\begin{theorem}
-\label{teo: lookdown on limit well defined}
-There exists a solution $(\lp_t)_{t \geq 0}$ to the $(A, \lp_0)$ martingale problem.
-
-Furthermore, if we define $\Xi_t = \lim_{u_0 \to \infty} \frac{1}{u_0}\lp_t(dx \times [0,u_0])$,
-then the limit model $(\eta_t(dx))_{t \geq 0}$ defined in Theorem \label{thm:nonlocal_convergence}
-and $(\Xi_t(dx))_{t \geq 0}$
-shares the same distribution on $\mathcal{D}_{\mathcal{M}(\mathbb{R}^d)}[0,\infty)$.
-
-Finally, 
-for all $h\in \mathcal{C}(\mathbb{R}^d)$ and for all $K>0$,
-\begin{equation}\label{Markov Mapping Theorem Cox Condition limit}
-\mathbb{E}\left[e^{-\int_{\mathbb{R}^d \times [0,K]} h(x) \xi(dx \times du)}\bigg| \mathcal{F}^{\Xi}_t\right]=e^{- K \int_{\mathbb{R^d}}(1-e^{h(x)}) \Xi_t(dx)}.
-\end{equation}
-In other words,
-conditionally on $(\Xi_s)_{0\leq s \leq t}$
-for each $s \in[0,t]$,
-$\xi_s$ is conditionally Poisson with Cox measure $\Xi_s(dx) \times du$.
-\end{theorem}
-
-\subsection{Markov Mapping Theorem Application on Generator $A^{N}$}\label{sec: Markov Mapping Theorem Application - Prelimit}
-
-We now introduce some notations to simplify our calculations.
-For a finite atomic measure $\xi=\sum \delta_{(x_i,u_i)} \in \mathcal{M}(\mathbb{R}^d \times [0,N])$,
-we introduce the test functions
- $$f_g(\xi)= \prod_{(x_i,u_i)\in \xi} g(x_i,u_i) = \exp (\langle \log g, \xi \rangle),$$
- where $g \in \mathcal{C}(\mathbb{R}^d \times [0,\infty))$ and $g(x,u)=1$ for all $u \geq N$.
-
- To avoid any ambiguities in the proofs,
- we will strictly use the notation $\Xi^N$  
-to represent the scaled push-forward measure of $\lp$,
-i.e. $\Xi^N := \frac{1}{N}\sum_{(x,u) \in \lp} \delta_x$,
-and only use $(\eta^N_t)_{t \geq 0}$
-to refer to the PDE solutions defined in Definition  \ref{defn:mgale_construction}.
-
-We also write $\textbf{x}=(x_1,x_2,...), \textbf{u}=(u_1,u_2,...)$ to be the collections of particles locations and levels respectively.
-With this notation we will write $f_g(\xi), f_g(\textbf{x},\textbf{u})$ interchangeably.
-
-We write $\Gamma^N (d\textbf{u})$ as the probability kernel
-that corresponds to assigning each particle an i.i.d. uniform $[0,N]$-level, i.e.
-$$\int f_g(\textbf{x},\textbf{u})\Gamma^N (d\textbf{u})=\frac{1}{N^{|\xi|}}\int_{[0,N]^{|\xi|}}f_g(\textbf{x},\textbf{u})d\textbf{u},$$
-and we denote
-$$\hat{g}(x):=\frac{1}{N}\int_{0}^{N}g(x,u)du,
- ~~\hat{f}_g(\xi)=\int f_g(\xi) \Gamma (d\textbf{u})$$ 
-to be the spatial test functions with averaged level.
-By independence of the levels of the particles,
- we have that
- \begin{align*}
-\hat{f}_g(\xi)
-=&\int \prod_{(x,u) \in \xi}g(x,u) \Gamma(d\textbf{u})\\
-=&\prod_{(x,u)\in \xi}\frac{1}{N}\int_{0}^{N} g(x,u) du\\
-=&\prod_{(x_i,u_i)\in \xi }\hat{g}(x_i)\\
-=& \exp(N\log \hat{g},\Xi^N).
- \end{align*}
-
-Furthermore,
-when expressed as a function of $\Xi^N$ explicitly,
-we use the notation $F_{\hat{g},N}(\Xi^N):=\hat{f}_g(\xi)$.
-
-We will now apply Markov Mapping Theorem
-while keeping notations consistent to that introduced in Section A.5 in \cite{kurtz/rodrigues:2011}
-with the aid of Table \ref{Markov Mapping Theorem Notation Table}.
-\begin{table}[!h]
-    \centering
-    \begin{tabular}{c|c}
-    Notation in \cite{kurtz/rodrigues:2011} & Notation in this proof \\
-    \hline\\
-      $S$   &  $\mathcal{M}(\IR^d \times [0, N])$\\\\
-       $S_0$  &  $\mathcal{M}(\IR^d)$\\\\
-       $A$ & $A^{N}$\\\\
-       $(X_t)_{t \geq 0}$ & $(\xi^N_t)_{t \geq 0}$\\\\
-       $\mu_0$ & $\eta^N_0 \in \mathcal{M}(\IR^d)$\\\\
-       $\nu_0$ & $\xi^N_0 \in \mathcal{M}(\IR^d \times [0,N])$\\\\
-       $f(\xi)$ & $f_g(\xi) := \prod_{(x,u) \in \xi} g(x,u)$\\\\
-        $\gamma_M$ & $ \mathcal{M}(\IR^d \times [0, N]) \ni \xi \to \frac{1}{N}\sum_{(x,u) \in \lp(\cdot, [0,N))} \delta_{x} \in \mathcal{M}(\IR^d)$\\\\
-       $\alpha_M$ & $ \alpha_M(\Xi^N,d \lp) =     \begin{cases}
-      0 & \text{if } \frac{1}{N}\sum_{(x,u) \in \lp(\cdot, [0,N))} \delta_x \neq \Xi^N\\
-       \prod_{(u_i,x_i) \in \nu} \frac{1}{N} \ind_{[0,N]}du_i & \text{if } \frac{1}{N}\sum_{(x,u) \in \lp(\cdot, [0,N))} \delta_x = \Xi^N,\\
-    \end{cases} $\\
-&      where $du_i$ is the standard Lebesgue measure.
-    \end{tabular}
-    \caption{Markov Mapping Theorem Correspondence}
-    \label{Markov Mapping Theorem Notation Table}
-\end{table}
-
-\begin{remark}
-Note that $\gamma,\alpha$ in \cite{kurtz/rodrigues:2011}
-is replaced with $\gamma_M,\alpha_M$ to avoid confusion with the $\gamma, \alpha$ used in previous sections.
-\end{remark}
-
-First of all,
-note that $\gamma_M$ is Borel-measurable
-and $\alpha_M$ is a transition function from $\mathcal{M}(\IR^d \times [0, N))$ to $\mathcal{M}(\IR^d)$.
-
-More importantly, we have the following simplified expression
-for an integral against $\alpha_M$:
-\begin{equation}
-\int_{\mathcal{M}(\IR^d\times [0,N])}A^{N}f(\xi)\alpha_M(\Xi^N, d\lp)
-= \int   A^Nf(\textbf{x},\textbf{u})\Gamma^N(d\textbf{u}). 
-\end{equation}
-
-As a result, we can establish that
-\begin{equation}
-\begin{aligned}
-\alpha_M(\Xi^N,\gamma^{-1}(\Xi^N)) 
-&= \int_{\lp \in \gamma^{-1}(y)}\alpha_M (\Xi^N, d\lp) \\
-&= \int_{\{\lp: \sum_{(x,u) \in \lp }\delta_x = N\Xi^N \} }\alpha_M (\Xi^N, d\lp)\\
-&= \prod_{x_i \in N\Xi^N}\frac{1}{N}\int_{0}^{N} du_i =1
-\end{aligned}
-\end{equation}
-With the simplified integral, it now suffices to show that the Martingale Problem 
-\begin{equation}\label{Markov Mapping Theorem Martingale Condition Simplified}
-C = \left\{\left(\int   f(\textbf{x},\textbf{u})\Gamma^N(d\textbf{u}),\int   A^Nf(\textbf{x},\textbf{u})\Gamma^N(d\textbf{u})\right)\right\}    
-\end{equation}
-has a solution.
-
-We now claim the following lemma.
-
-\begin{lemma}
-\label{lem: representation of lookdown generator - pre-limit}
-Let $\xi$ be a finite atomic measure on $\mathbb{R}^d \times [0,N]$.
-For test functions of the form 
-$$f_g(\xi)= \prod_{(x_i,u_i)\in \xi} g(x_i,u_i) = \exp (\langle \log g, \xi \rangle),$$
-we have the equality
-\begin{equation}
-\int   A^Nf(\textbf{x},\textbf{u})\Gamma^N(d\textbf{u})
-= \int \Pgen^N F_{\hat{g},N}(\Xi^N),
-\end{equation}
-where $\Pgen^N$ is the generator of the spatial process defined in Definition \ref{def2: MP definition of pre-limit}.
- \end{lemma}
-
-With lemma \ref{lem: representation of lookdown generator - pre-limit},
-the martingale problem can then be re-written as 
-\begin{equation}\label{Markov Mapping Theorem Martingale Condition, projection form}
-C = \left\{\left(\int F_{\hat{g},N}(\Xi^N), \int \Pgen^N F_{\hat{g},N}(\Xi^N)\right)\right\}    
-\end{equation}
-which has $(\eta^N_t)_{t \geq 0}$,
-our spatial population process,
-as a solution.
-
-As a result,
-we can apply Markov Mapping Theorem to establish the following statements:
-\begin{enumerate}
-    \item There exists a $\mathcal{M}_F(\mathbb{R}^d\times[0,N])$-valued process $(\lp^N_t)_{t \geq 0}$
-    such that 
-    $M^N_t:=    f(\xi^N_t)-   f(\xi^N_0)-\int_{0}^{t}  A^Nf(\xi^N_s)ds$ is a martingale for all $f\in D(A^N)$,
-    \item The process $(\gamma_M \circ \xi^N_t)_{t \geq 0}= \left(\Xi^N_t\right)_{t \geq 0}$ 
-    has the same distribution in $\mathcal{D}_{\mathcal{M}(\mathbb{R}^d)}[0,\infty)$ as $(\eta^N_t)_{t \geq 0}$ defined in Definition \ref{def: MP definition of pre-limit}.
-    \item $\mathbb{P}\{\xi^N_t \in B | \mathcal{F}^{\Xi^N}_t\}=\alpha_M(\Xi^N(t),B), ~~~B \in \mathcal{B}(\mathcal{M}(\IR^d \times [0,N])).$
-\end{enumerate}
-Note that in particular,
-from the third statement,
-we can establish that for $h(x,u) \in \mathcal{C}_{c}(\mathbb{R}^d \times[0,N])$ and $h \geq 0$,
-
-\begin{equation}\label{Markov Mapping Theorem Cox Condition}
-\begin{aligned}
-\mathbb{E}\left[e^{-\int_{S \times [0,N]} h(x,u) \xi^{N}(dx \times du)}\bigg| \mathcal{F}^{\Xi^{N}}_t\right]
-&=\mathbb{E}\left[\prod_{(x,u)\in\xi^N_t}e^{-h(x,u)}\bigg| \mathcal{F}^{\Xi^{N}}_t\right]\\
-&=\prod_{x \in N\Xi^N_t} \frac{1}{N} \int_{0}^N. e^{-h(x_i,u_i)} du_i
-&= e^{-\langle F^N_h(x), \Xi^N(dx)\rangle},
-\end{aligned}
-\end{equation}
-where 
-$$F^{N}_h(x):=-N\log \left(\frac{1}{N}\int_{0}^{N}e^{-h(x,u)}du\right)=-N\log \left(1-\frac{1}{N}\int_{0}^{N}(1-e^{-h(x,u)})du\right).$$
-
-Therefore we only need to prove lemma \ref{lem: representation of lookdown generator - pre-limit}.
-The procedure to prove Lemman \ref{lem: representation of lookdown generator - pre-limit}
-is rather standard and set out in \cite{kurtz/rodrigues:2011},
-albeit we will face more technicalities for this setting.
-
-For tidy computations in this proof, 
-we recall the notation that an individual at $x$ gives birth at rate
-$$
-    \gamma^{\mathfrak{m}}_{\theta}(x,\eta) := \theta \gamma(x, \smooth{\gamma} \eta(x))
-    \int r(y, \smooth{r} \eta(y)) q_{\theta}(x, dy) ,
-$$
-and that offspring disperse according to the kernel
-$$
-    q_\theta^\mathfrak{m}(x,\eta,  dy)
-    :=
-    \frac{
-        r(y, \smooth{r} \eta(y)) q_\theta(x, dy)
-    }{
-        \int r(z, \smooth{r} \eta(z)) q_\theta(x, dz)
-    } .
-$$
-
-We will also write $\Xi, \Gamma$ instead of $\Xi^N, \Gamma^N$,
-bearing in mind the dependence of $\Xi, \Gamma$ on $N$.
-
-\begin{proof}[Proof to Lemma \ref{lem: representation of lookdown generator - pre-limit}]
-
-Recall that the lookdown generator of our spatial-level process satisfies
-\begin{align}
-A^Nf(\xi)=&
-f(\xi)\sum_{(x,u)\in\xi}2N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\times
-\int_u^{
-N}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\IR^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\theta}(x,\Xi ,dy) \nonumber \\
-& \qquad \qquad \qquad \qquad +\int_{\IR^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\theta}(x,\Xi,dy)\Bigg)dv_1 \nonumber\\
-&+f(\xi )\sum_{(x,u)\in\xi}\,\left(N^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)},
-\end{align}
-where $f(\xi) =\prod_{(x,u) \in \xi}g(x,u)$.
-
-For easier computation,
-we break the generator into three parts, 
-\begin{equation}
-\begin{aligned}
-A^N_1f(\xi)=&f(\xi)\sum_{(x,u)\in\xi}2N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\times
-\int_u^{
-N}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\IR^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\theta}(x,\Xi ,dy)\Bigg)dv_1,\\
-A^N_2f(\xi)=&f(\xi)\sum_{(x,u)\in\xi}2N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\times
-\int_u^{
-N}\Bigg(\frac{1}{2}\int_{\IR^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\theta}(x,\Xi,dy)\Bigg)dv_1,\\
-A^N_3f(\xi)=&f(\xi )\sum_{(x,u)\in\xi}\,\left(N^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)},
-\end{aligned}
-\end{equation}
-such that 
-$$A^Nf(\xi)=A^N_1f(\xi)+A^N_2f(\xi)+A^N_3f(\xi).$$
-
-We now calculate each generator evaluated under our probability kernel $\Gamma$.
-\footnotesize 
-\begin{align*}
-&\int A^N_1f(\xi) \Gamma(d\mathbf{u})\\ &=\int \Bigg\{f(\xi)\sum_{(x,u)\in\xi}2N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)
-\int_u^{
-N}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\IR^d}(g(y,u)-g(x,u))q^{\mathfrak{m}}_{\theta}(x,\Xi ,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
-&=\sum_{(x,u)\in\xi} \int \Bigg\{\frac{f(\xi)}{g(x,u)}2N^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi)
-\int_u^{
-N}\Bigg(\frac 12 g(x,v_1)\int_{\IR^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\theta}(x,\Xi ,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
-&=\sum_{(x,u)\in\xi}N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{N}\int_{0}^{N}\left\{
-\int_u^{
-N} g(x,v_1)dv_1\times \int_{\IR^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\theta}(x,\Xi ,dy)\right\}du\\
-&=\sum_{(x,u)\in\xi}N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{N}\int_{\IR^d} \left\{\int_{0}^{N}
-\int_u^{
-N} g(x,v_1) (g(y,u)-g(x,u))dv_1du\right\}q^{\mathfrak{m}}_{\theta}(x,\Xi ,dy)
-\end{align*}
-
-\normalsize
-For the second generator, we have
-\footnotesize
-\begin{align*}
-&\int A^N_2f(\xi) \Gamma(d\mathbf{u})\\&=\int \Bigg\{f(\xi)\sum_{(x,u)\in\xi}2N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\times
-\int_u^{
-N}\Bigg(\int_{\IR^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\theta}(x,\Xi,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
-&=\sum_{(x,u)\in\xi}N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\int \Bigg\{f(\xi)\times
-\int_u^{
-N}\Bigg(\int_{\IR^d}\left(g(y,v_1)+g(x,v_1)-2\right)q^{\mathfrak{m}}_{\theta}(x,\Xi,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
-&=\sum_{(x,u)\in\xi}N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i) \frac{1}{N}\int_{\IR^d}\Bigg\{\int_{0}^{N}
-\int_u^{
-N}g(x,u) \left(g(y,v_1)+g(x,v_1)-2\right)dv_1 du\Bigg\} q^{\mathfrak{m}}_{\theta}(x,\Xi,dy).
-\end{align*}
-
-\normalsize
-For the third generator we have that 
-\begin{align*}
- &\int A^N_3f(\xi)\Gamma(d\mathbf{u})\\
- =&\int f(\xi )\,\left(N^{-1} \sum_{(x,u)\in\xi}\theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)}\Gamma(d\mathbf{u}) \\
- =&\sum_{(x,u)\in\xi}\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{N}\int_{0}^{N}  \left(N^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\partial_u g(x,u)du \\
- =&-\sum_{(x,u)\in\xi}\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{N}\int_{0}^{N}  \left(2uN^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) -b_{\theta}(x,\Xi)\right)\left(g(x,u)-1\right)du \\
- =&-\sum_{(x,u)\in\xi}N^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{N}\int_{0}^{N}   2ug(x,u)du \\
- &+\sum_{(x,u)\in\xi}N^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{N}\times N^2+\sum_{(x,u)\in\xi}\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)b_{\theta}(x,\Xi)(\hat{g}(x)-1)
-\end{align*}
-
-By symmetry, we have
-\begin{align*}
-&\int_{0}^{N}
-\int_u^{
-N} g(x,v_1) (g(y,u)-g(x,u))dv_1du+\int_{0}^{N}
-\int_u^{
-N}g(x,u) \left(g(y,v_1)+g(x,v_1)-2\right)dv_1 du
-\\&= \int_{0}^{N}
-\int_u^{
-N}g(x,u)g(y,v_1)+g(y,u)g(x,v_1)-2g(x,u) dv_1 du\\
-&=\frac{1}{2}\int_{0}^{N}\int_{0}^{N}g(x,u)g(y,v_1)+g(y,u)g(x,v_1)dv_1 du - 2 \int_{0}^{N}(N-u)g(x,u)du\\
-&=N^2 \hat{g}(x)\hat{g}(y) -2N^2 \hat{g}(x)+2\int_{0}^{N}ug(x,u)du.
-\end{align*}
-
-Combining the last equations,
-we have 
-\begin{align*}
-&\int \Bigg(A^N_1f(\xi)+A^N_2f(\xi)+A^N_3f(\xi)\Bigg)\Gamma(d\mathbf{u})\\
-=&  \sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)}\hat{g}(x_i) \left( \int_{\IR^n} \hat{g}(y) q^{\mathfrak{m}}_{\theta}(x,\Xi,dy) - 2+\frac{1}{\hat{g}(x)}\right)\\
-&+\sum_{(x,u) \in \xi } \prod_{(x_i,u_i)}\hat{g}(x_i)b_{\theta}(x,\Xi)\left(1-\frac{1}{\hat{g}(x)}\right)\\
-=&  \hat{f}(\xi)\sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi) \left(\int_{\IR^n} \hat{g}(y) q^{\mathfrak{m}}_{\theta}(x,\Xi,dy) -1\right)\\
-&+\hat{f}(\xi)\sum_{(x,u) \in \xi } (b_{\theta}(x,\Xi)-\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi))\left(1-\frac{1}{\hat{g}(x)}\right)\\
-=&  F_{\hat{g},N}(\Xi^N)\sum_{x \in \Xi}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi) \left(\int_{\IR^n} \hat{g}(y) q^{\mathfrak{m}}_{\theta}(x,\Xi,dy) -1\right) \\
-&-F_{\hat{g},N}(\Xi^N)\sum_{x \in \Xi } \theta \mu_{\epsilon,\theta}(x,\Xi)\left(1-\frac{1}{\hat{g}(x)}\right)\\
-=& \Pgen^N F_{\hat{g},N}(\Xi^N).
-\end{align*}
-
-The last equality holds
-as the second last expression corresponds to a spatial-branching process
-that branches at rate $\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)$,
-leaving offspring around with kernel $ q^{\mathfrak{m}}_{\theta}(x,\Xi,dy)$,
-with each particle having death rate given by $\theta \mu_{\epsilon,\theta}(x,\Xi)$.
-This is precisely the martingale problem in Definition \ref{def: MP definition of pre-limit}.
-
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%
-\newpage
-\subsection{Markov Mapping Theorem Application on Generator $A$}\label{sec: Markov Mapping Theorem application - limit}
-
-Now,
-we turn to the generator for the limiting case,
-which has the form
-    \begin{equation}
-    \begin{aligned}
-    A f(\lp)
-    =&
-        f(\lp)  \sum_{(x, u) \in \xi}
-        \gamma(x, \eta)
-            \frac{
-                \DG(g(\cdot, u) r(\cdot, \eta))(x) - g(x,u) \DG r(x,\eta)
-            }{
-                g(x, u)
-            }
-    \\ &+
-        f(\lp) \sum_{(x, u) \in \xi}
-        2 \alpha \gamma(x, \Xi) r(x, \Xi ) \int_u^\infty (g(x, u_1) - 1) du_1
-    \\ &+
-        f(\lp) \sum_{(x, u) \in \xi}
-        \left(
-            \alpha \gamma(x, \Xi) r(x, \Xi ) u^2
-            -
-            \left\{
-                \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta)
-            \right\} u
-        \right)
-        \frac{\partial_u g(x, u)}{ g(x,u) }  .
-    \end{aligned}
-    \end{equation}
-
-To apply Markov Mapping Theorem,
-we consider Table \ref{Markov Mapping Theorem Notation Table Limit}.
-
-\begin{table}[!h]
-    \centering
-    \begin{tabular}{c|c}
-    Notation in \cite{kurtz/rodrigues:2011} & Notation in this proof \\
-    \hline\\
-      $S$   &  $\mathcal{M}(\IR^d \times [0, \infty])$\\\\
-       $S_0$  &  $\mathcal{M}(\IR^d)$\\\\
-       $A$ & $A$\\\\
-       $(X_t)_{t \geq 0}$ & $(\xi_t)_{t \geq 0}$\\\\
-       $\mu_0$ & $\xi_0 \in \mathcal{M}(\IR^d)$\\\\
-       $\nu_0$ & $\xi_0 \in \mathcal{M}(\IR^d \times [0,\infty])$\\\\
-       $f(\xi)$ & $f_g(\xi) := \prod_{(x,u) \in \xi} g(x,u)$\\\\
-        $\gamma_M$ & $ \mathcal{M}(\IR^d \times [0, \infty]) \ni \xi \to \lim_{u_0 \to \infty}\frac{1}{u_0}\sum_{(x,u) \in \lp(\cdot, [0,u_0))} \delta_{x} \in \mathcal{M}(\IR^d)$\\\\
-       $\alpha_M$ & $ \Gamma^M(\Xi,d \lp) \sim PP(\Xi(dx)\times \Lambda(du)) ~~ \text{if } \gamma_M(\xi)=\Xi$,\\
-       &      where $\Lambda(du)$ is the standard Lebesgue measure on $[0,\infty)$.
-    \end{tabular}
-    \caption{Markov Mapping Theorem Correspondence}
-    \label{Markov Mapping Theorem Notation Table Limit}
-\end{table}
-
-Once again,
-we need to find solutions to the Martingale Problem 
-\begin{equation}
-C = \left(\int f_g(\xi) \Gamma^M(\cdot, d\xi), \int Af_g(\xi) \Gamma^M(\cdot, d\xi))\right),
-\end{equation}
-where $\Gamma^M(\Xi, d\lp)$ is the law of $\xi$,
-which is conditionally Poisson with Cox measure $\Xi(dx) \times \Lambda(du)$.
-
-Since we impose that $\xi$ is conditionally Poisson with Cox measure $\Xi(dx) \times \Lambda(du)$,
-for any test function $l(x,u) > 0$,
-\begin{equation}
-\mathbb{E}\left[e^{-\int_{\mathbb{R}^d \times [0,\infty]} l(x,u) \xi(dx,du)}\big| \Xi \right] = e^{-\int_{\mathbb{R}^d} \int_{0}^{\infty} (1-e^{-l(x,u)}) du \Xi(dx)}.
-\end{equation}
-
-Note that 
-$\prod_{(x,u) \in \xi} g(x,u) = e^{-\int_{\mathbb{R}^d \times [0,\infty]} -\log g(x,u) \xi(dx,du)},$
-so taking $l(x,u)= -\log g(x,u)$ and $h(x,u)= \int_{0}^{\infty} (1 -g(x,u))du$,
-we have the equation
-\begin{equation}
-\begin{aligned}
-\int f_g(\xi) \alpha_M(\Xi, d\xi) 
-=&  e^{-\int_{\mathbb{R}^d} \int_{0}^{\infty} (1-e^{-l(x,u)}) du \Xi(dx)}\\
-=&  e^{-\int_{\mathbb{R}^d} \int_{0}^{\infty} (1-g(x,u)) du \Xi(dx)}\\
-=& \exp(\langle -h(x), \Xi(dx)\rangle),
-\end{aligned}
-\end{equation}
-and we will denote the last term as $\mathcal{E}_{-h}(\Xi)$.
-Note that this notation is consistent to the test function
-$F_f(\eta)$ laid out in \ref{def: MP definition of limit},
-if we take $F(\cdot)=\mathcal{E}(\cdot) := \exp(\cdot)$ and $f=-h$.
-
-We now state the crucial lemma that allows us to apply Markov Mapping Theorem.
-\begin{lemma}
-\label{lem: MMT for limit}
-Let $\lp$ be a finite measure on $\mathbb{R}^d \times [0,\infty)$,
-$\Xi$ be a finite measure on $\mathbb{R}^d$,
-and $\Lambda(dx)$ be the Lesbesgue measure on  $[0,\infty)$.
-
-We consider test functions 
-$f(\xi):= \prod_{(x_i,u_i) \in \xi} g(x_i,u_i)$
-with $g \in C^2_{0}(\mathbb{R}^d \times[0,\infty))$
-and for which there exists $u_0$ with 
-$g(x,u)=1$ for all $u>u_0$.
-Furthermore, we define 
-$h(x,u)= \int_{0}^{\infty} (1 -g(x,u))du$
-and $\mathcal{E}_{-h}(\Xi)= \exp(\langle -h(x), \Xi(dx)\rangle)$.
-
-We write $\Gamma^{\Xi}(d\lp)$ to be the law
-on $\mathcal{M}(\mathbb{R}^d \times[0,\infty))$ 
-for a conditionally Poisson random measure $\lp$
-on $\IR^d\times [0,\infty)$
-with Cox measure $\Xi(dx)\times \Lambda(du)$.
-
-Then,
-for generator $A$ defined in Equation \eqref{eqn:limiting_lookdown_generator},
-\begin{equation}
-\int Af(\lp) \Gamma^{\Xi}(d\lp) = \Pgen \mathcal{E}_{-h}(\Xi),
-\end{equation}
-where $\Pgen$ is defined in Definition \ref{def2: MP definition of limit}.
-\end{lemma}
-
-Given the above lemma, 
-the following three statements hold true.
-\begin{enumerate}
-    \item There exists a $\mathcal{M}_F(\mathbb{R}^d\times[0,\infty])$-valued process $(\lp_t)_{t \geq 0}$
-    such that 
-    $M_t:=    f(\xi_t)-   f(\xi_0)-\int_{0}^{t}  Af(\xi_s)ds$ is a martingale for all $f\in D(A)$,
-    \item The process $(\gamma_M \circ \xi_t)_{t \geq 0}= \left( \lim_{u_0 \to \infty}\frac{1}{u_0}\sum_{(x,u) \in \lp_t(\cdot, [0,u_0))} \delta_{x} \right)_{t \geq 0}$ 
-    has the same distribution in $\mathcal{D}_{\mathcal{M}(\mathbb{R}^d)}[0,\infty)$ as $(\eta_t)_{t \geq 0}$ defined in Definition \ref{def: MP definition of limit}.
-    \item $\mathbb{P}\{\xi_t \in B | \mathcal{F}^{\Xi_t}\}=\Gamma^{\Xi_t}(B), ~~~B \in \mathcal{B}(\mathcal{M}(\IR^d \times [0,\infty])).$
-\end{enumerate}
-
-Finally,
-we recall an important equality for conditionally Poisson point processes (\cite{kurtz/rodrigues:2011} Lemma A.3.)
-which will be used extensively in the upcoming proof.
-
-\begin{lemma}
-Let $\lp =\sum_{i}\delta_{Z_i}$ be a Poisson random measure with mean measure $\nu$, 
-then for $\ell \in L^{1}(\nu)$ and $g\geq0$ with $\log g \in L^{1}(\nu)$,
-\begin{equation}
-\mathbb{E}[\sum_{j} \ell(Z_j) \prod_{i}g(Z_i)] = \int \ell g d\nu e^{\int (g-1) d \nu}.
-\end{equation}
-\end{lemma}
-
-In particular,
-taking $\nu(dx,du)=\Xi(dx) \times \Lambda(du)$,
-we have the equation 
-\begin{equation}
-\label{eq: cond_poi_sum_prod}
-\begin{aligned}
-\int f(\xi) \sum_{(x,u)\in \xi} \ell(x,u)\Gamma^{\Xi}(d\xi)
-=& \mathbb{E}_{\xi \sim PP(\Xi \times \Lambda)}\left[\sum_{(x_j,u_j)\in \xi} \ell(x_j,u_j) \prod_{(x_i,u_i) \in \xi}g(x_i,u_i)\right]\\
- =& \left \langle \int_{0}^{\infty} \ell(x,u) g(x,u) du ,\Xi(dx) \right\rangle \exp(\langle -h(x), \Xi(dx) \rangle) \\
- =& \left \langle \int_{0}^{\infty} \ell(x,u) g(x,u) du ,\Xi(dx) \right\rangle \mathcal{E}_{-h}(\Xi)
-\end{aligned}
-\end{equation}
-where $h(x)=\int_{0}^{\infty}(1-g(x,u))du$.
-
-We are now ready to prove Lemma \ref{lem: MMT for limit}.
-
-\begin{proof}[Proof to Lemma \ref{lem: MMT for limit}]
-We write
-$$ Af(\xi)=A_1f(\xi)+A_2f(\xi)+A_3f(\xi),$$
-where the first term is
-\begin{equation}
-\begin{aligned}
-A_1f(\xi) =&
-        f(\lp)  \sum_{(x, u) \in \xi}
-             \frac{
-            	\gamma(x, \Xi)
-                \left(\DG(g(\cdot, u) r(\cdot, \Xi))(x) - g(x,u) \DG r(x,\Xi)\right)
-            }{
-                g(x, u)
-            }\\
-            = & f(\lp)  \sum_{(x, u) \in \xi} \frac{\ell_1(x,u)}{g(x,u)},
-\end{aligned}    
-\end{equation}
-the second term is
-\begin{equation}
-\begin{aligned}
-A_2f(\xi)  = &
-  f(\lp) \sum_{(x, u) \in \xi}
-        2 \alpha \gamma(x, \Xi) r(x, \Xi ) \int_u^\infty (g(x, u_1) - 1) du_1\\
-         =&  f(\lp)  \sum_{(x, u) \in \xi} \ell_2(x,u),
-\end{aligned}    
-\end{equation}
-and the final term satisfies
-\begin{equation}
-\begin{aligned}
-A_3f(\xi)  =&f(\lp) \sum_{(x, u) \in \xi}
-                \frac{\left(
-            \alpha \gamma(x, \Xi) r(x, \Xi ) u^2
-            -
-            \left\{
-                \gamma(x, \Xi) \DG r(x, \Xi) + F(x, \Xi)
-            \right\} u
-        \right)
-        \partial_u g(x, u)}{ g(x,u) }\\
-        =& f(\lp) \sum_{(x, u) \in \xi} \frac{\ell_3(x,u)}{g(x,u)}  .
-\end{aligned}    
-\end{equation}
-
-Applying Equation \eqref{eq: cond_poi_sum_prod}
-to the above expressions give 
-\begin{equation}
-\int Af(\xi)\Gamma^{\Xi}(d\xi)
-= \left \langle \int_{0}^{\infty}\left(\ell_1(x,u) + \ell_2(x,u) g(x,u) + \ell_3(x,u)\right)du ,\Xi(dx) \right\rangle \mathcal{E}_{-h}(\Xi)
-\end{equation}
-
-First of all, 
-the operator $\DG$ acts on space while the integral is over levels,
-so we can commute the two operators to obtain
-\begin{equation}
-\begin{aligned}
-\int_{0}^{\infty} \ell_1(x,u) du 
-=& \int_{0}^{\infty} \gamma(x, \Xi)( \DG((g(\cdot, u)-1) r(\cdot, \Xi))(x) - (g(x,u)-1) \DG r(x,\Xi))  du \\
-=& \gamma(x, \Xi)\left\{ \DG\left(\int_{0}^{\infty} (g(\cdot, u)-1)du \times r(\cdot, \Xi)\right)(x) - \int_{0}^{\infty} (g(x,u)-1)du \DG r(x,\Xi)\right\} \\
-=& -\gamma(x, \Xi)\{ \DG(h(\cdot) r(\cdot, \Xi))(x) - h(x) \DG r(x,\Xi)\},
-\end{aligned}
-\end{equation}
-as $h(x,u)= \int_{0}^{\infty} (1 -g(x,u))du$.
-
-Similarly,
-\begin{equation}
-\begin{aligned}
-\int_{0}^{\infty} \ell_2(x,u)g(x,u) du
-=&  \alpha\gamma(x, \Xi) r(x, \Xi ) \times 2 \int_{0}^{\infty} g(x,u)  \int_u^\infty (g(x, u_1) - 1) du_1  du\\
-=&  \alpha\gamma(x, \Xi) r(x, \Xi ) \times I_1.
-\end{aligned}
-\end{equation}
-
-Finally,
-integrating $\ell_3$ by parts, 
-we have
-\begin{equation}
-\begin{aligned}
-\int_{0}^{\infty} \ell_3(x,u)du
-=& \int_{0}^{\infty} \left(
-            \alpha \gamma(x, \Xi) r(x, \Xi ) u^2
-            -
-            \left\{
-                \gamma(x, \Xi) \DG r(x, \Xi) + F(x, \Xi)
-            \right\} u
-        \right)
-        \partial_u g(x, u) du\\
-=& - \alpha\gamma(x, \Xi) r(x, \Xi ) \int_{0}^{\infty} 2u (g(x, u)-1) du\\
-  &+ \left\{\gamma(x, \Xi) \DG r(x, \Xi) + F(x, \Xi) \right\} \int_{0}^{\infty}(g(x,u)-1) du\\
-  =&  - \alpha \gamma(x, \Xi) r(x, \Xi ) I_2 - \left\{\gamma(x, \Xi) \DG r(x, \Xi) + F(x, \Xi) \right\} h(x).
-\end{aligned}
-\end{equation}
-
-Note that $I_1-I_2$ satisfies
-\begin{equation}
-\begin{aligned}
-I_1-I_2 
-=& 2 \int_{0}^{\infty} g(x,u)  \int_u^\infty (g(x, u_1) - 1) du_1  du - 2 \int_{0}^{\infty} u (g(x, u)-1) du\\
-=& 2 \int_{0}^{\infty} g(x,u)  \int_u^\infty (g(x, u_1) - 1) du_1  du - 2 \int_{0}^{\infty} (g(x, u)-1) \int_{0}^{u}dv  du\\
-=& 2 \int_{0}^{\infty} g(x,v)  \int_v^\infty (g(x, u) - 1) du  dv - 2 \int_{0}^{\infty} \int_{v}^{\infty}(g(x, u)-1)  dudv\\
-=& 2 \int_{0}^{\infty} (g(x,v)-1)  \int_v^\infty (g(x, u) - 1) du  dv \\
-=& h^2(x)
-\end{aligned}
-\end{equation}
-
-Combining all the Equations above, 
-we have 
-\begin{equation}
-\begin{aligned}
-& \int_{0}^{\infty}\left(\ell_1(x,u) + \ell_2(x,u) g(x,u) + \ell_3(x,u)\right)du \\
-=& -\gamma(x, \Xi)\DG(h(\cdot) r(\cdot, \Xi))(x) + \gamma(x, \Xi) h(x) \DG r(x,\Xi) -  \gamma(x, \Xi) \DG r(x, \Xi)h(x) - F(x, \Xi)  h(x) \\
-& +\alpha\gamma(x, \Xi) r(x, \Xi )(I_1-I_2)\\
-=&\alpha \gamma(x, \Xi) r(x, \Xi ) h^2(x) -\gamma(x, \Xi)\DG(h(\cdot) r(\cdot, \Xi))(x)  - F(x, \Xi)  h(x).
-\end{aligned}
-\end{equation}
-
-To conclude, 
-\begin{equation}
-\begin{aligned}
-&\int Af(\xi)\Gamma^{\Xi}(d\xi)\\
-= & \left(\alpha \gamma(x, \Xi) r(x, \Xi ) h^2(x) -\gamma(x, \Xi)\DG(h(\cdot) r(\cdot, \Xi))(x)  - F(x, \Xi)  h(x)\right)\mathcal{E}_{-h}(\Xi)\\
-= & \left(\gamma(x, \Xi)\DG(-h(\cdot) r(\cdot, \Xi))(x)  + F(x, \Xi)  (-h(x))\right)\mathcal{E}'(\langle -h, \Xi \rangle )\\
-   &+ \left(\alpha \gamma(x, \Xi) r(x, \Xi ) h^2(x) \right)\mathcal{E}''(\langle -h, \Xi \rangle )\\
-=& \Pgen \mathcal{E}_{-h}(\Xi),
-\end{aligned}
-\end{equation}
-so we have established our equality. 
-\end{proof}
-
-\subsection{Convergence of Lookdown Representation}
-\comment{
-    I did this informal writeup of convergence of the lookdown generator
-    without looking at the previous version
-    mostly to double-check what we have there
-    (which is probably better).
-}
-
-In Definition~\ref{defn:lookdown_mgale} we saw that the generator
-of $(\lp_t)_{t \ge 0}$ is the sum of two parts,
-equations \eqref{eqn:birth_generator} and \eqref{eqn:level_generator}.
-Assume that there is a $u_*$ such that $g(x, u) = 1$ for all $u \ge u_*$.
-We consider these two in turn.
-
-First, the contribution from births is
-\begin{align*}
-\begin{split}
-f(\lp)
-&\mapsto
-    f(\lp)
-    \sum_{(x, u) \in \lp}
-    2 \gamma(x, \eta)
-    \bigg\{
-        \frac{1}{2 N}
-        \int_u^N
-        g(x, u_1) du_1
-        \frac{
-            \theta \int_{\IR^d} (g(y, u) - g(x, u)) r(y, \eta) q(x, dy)
-        }{
-            g(x, u)
-        }
-    \\ & \qquad \qquad \qquad {}
-        + \frac{\theta}{N}
-        \int_u^N \int_{\IR^d}
-        \left( \frac{g(y, u_1) + g(x, u_1)}{2} - 1 \right)
-        r(y, \eta) q(x, dy)
-    \bigg\}
-    .
-    \end{split}
-\end{align*}
-We have that
-\begin{align*}
-    &\theta \int_{\IR^d} (g(y, u) - g(x, u)) r(y, \eta) q(x, dy) \\
-    &\qquad =
-    \theta \int_{\IR^d} (r(y, \eta) g(y, u) - r(x, \eta) g(x, u)) q(x, dy)
-    - \theta \int_{\IR^d} g(x, u) (r(y, \eta) - r(x, \eta)) q(x, dy) \\
-    &\qquad \to
-    \DG(gr)(x) - g(x) \DG r(x) \qquad \text{as }N \to \infty.
-\end{align*}
-i.e., to
-$\DG\left(g(\cdot, u) r(\cdot, \smooth{r}\eta(\cdot))\right)(x)
-- g(\cdot, u) \DG\left(r(\cdot, \smooth{r}\eta(\cdot))\right)(x)$.
-Furthermore, by our assumption on $g$,
-$\int_u^N g(x, u_1) du_1 / N \to 1$ for all $x$ and $u$,
-so the first term here converges to
-\begin{align*}
-    \gamma(x, \eta)
-        \frac{
-            \DG\left( g(\cdot, u) r(\cdot, \smooth{r}\eta(\cdot))\right)(x)
-            -
-            g(\cdot, x) \DG\left( r(\cdot, \smooth{r}\eta(\cdot))\right)(x)
-        }{
-            g(x, u)
-        } .
-\end{align*}
-This corresponds to each particle moving according to the motion induced by
-$g \mapsto \gamma \DG(gr) - g \DG r$.
-\comment{TODO: explain the $r$-tilted $\DG$ motion somewhere earlier, introducing notation for it.}
-As for the second term,
-since $\int g(y, u_1) q(x, dy) \to g(x, u_1)$
-and $\theta/N \to \alpha$,
-it converges to
-\begin{align*}
-    2 \alpha
-    \gamma(x, \eta)
-    r(x, \eta) 
-    \int_u^\infty
-    \left( g(x, u_1) - 1 \right)
-    du_1
-\end{align*}
-This corresponds to births at higher levels at rate $2 \alpha \gamma r$.
-
-The remaining term is \eqref{eqn:level_generator}:
-\begin{align*}
-    f(\lp)
-    \mapsto
-    f(\lp)
-    \sum_{(x, u) \in \lp}
-    \left(
-    \theta
-        N^{-1} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
-        -
-        b(x, \eta)u
-    \right)
-    \frac{\partial_u g(x,u)}{g(x,u)} .
-\end{align*}
-The first part only uses the fact that $\theta/N \to \alpha$,
-while as noted in \eqref{eqn:b_limit}, $b$ converges to $\gamma \DG r + F$,
-so in total this term converges to
-\begin{align*}
-    f(\lp)
-    \mapsto
-    f(\lp)
-    \sum_{(x, u) \in \lp}
-    \left(
-    \alpha
-        \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
-        -
-        \left\{
-            \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta)
-        \right\} u
-    \right)
-    \frac{\partial_u g(x,u)}{g(x,u)} .
-\end{align*}
-In other words, the level of a particle at $x$ evolves according to
-\begin{align*}
-    \dot u
-    =
-    \alpha
-        \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
-        -
-        \left\{
-            \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta)
-        \right\} u .
-\end{align*}
-
-\comment{From Terence: Note that the convergence result above gives the coefficient $\gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy)$ in front of $u^2$.
-As a result, the contribution by death to the quadratic variation of the superprocess is gone in this limit!
-I cannot find a way to resolve the inconsistency between this limiting result and the spatial model.
-Of course, we can take $\alpha=0$, so we are taking a deterministic limit. In this case, we have consistent result. 
-We should discuss this in our next meeting.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-
-\section{Technical Lemmas}
-\subsection{Gaussian Kernel Estimates}
-
-\begin{lemma}\label{eq: Gaussin density estimates}
-\begin{equation}
- \theta H_{\theta}(x,w)\rho_r(x-w)\leq \rho_{\gamma}(x-w),
-\end{equation}
-where
-$$H_{\theta}(x,w)=\int_{\IR^d}
-    \left(
-        \frac{\rho_r(y-w)}{\rho_r(x-w)}
-        -
-        1
-    \right)^2
-q_{\theta}(x,dy).$$
-\end{lemma}
-\begin{proof}
-
-Writing out $H$,
-\begin{align}
-H_\theta(x, w)
-=
-\int
-    \left(
-        \exp\left(
-            - \frac{1}{2\epsilon_r^2}
-            \left\{
-                ||y - w||^2 - ||x - w||^2
-            \right\}
-        \right)
-        -
-        1
-    \right)^2
-    \frac{
-        e^{-\theta (y - x-\meanq)^{T}\covq^{-1}(y - x-\meanq)  / 2}
-    }{
-        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
-    }
-dy.
-\end{align}
-Writing $z=y-x-\meanq$, we have that 
-\begin{equation}
-\begin{aligned}
-||y - w||^2 - ||x - w||^2 
-=& ||y||^2-||x||^2 -2\langle y-x, w\rangle \\
-=&||x+z+ \meanq||^2-||x||^2-2 \langle z+ \meanq, w\rangle\\
-=&2\langle x, z+ \meanq \rangle + ||z+ \meanq||^2-2 \langle z+ \meanq, w\rangle \\
-=& 2 \langle x-w, z+ \meanq \rangle + ||z+ \meanq||^2\\
-=& 2\langle x-w+ \meanq,\meanq \rangle + 2\langle x-w+ \meanq, z \rangle +||z||^2
-\end{aligned}
-\end{equation}
-As a result, we have 
-\begin{align}
-H_\theta(x, w)
-=&
-\int
-    \left(
-        \exp\left(
-            - \frac{1}{2\epsilon_r^2}
-            \left\{
-                2 \langle x-w, z+ \meanq \rangle + ||z+ \meanq||^2
-            \right\}
-        \right)
-        -
-        1
-    \right)^2
-    \frac{
-        e^{-\theta z^{T}\covq^{-1}z  / 2}
-    }{
-        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
-    }
-dz\\
-=&\exp\left(-\frac{2}{\epsilon_r^2}\langle x-w+ \meanq,\meanq \rangle \right)\\
-& \times \int
-        \frac{
-        \exp\left(
-            - \frac{2}{\epsilon_r^2} \langle x-w+ \meanq, z \rangle
-            - \frac{1}{\epsilon_r^2} ||z||^2
-            \right)
-            e^{-\theta z^{T}\covq^{-1}z  / 2}
-    }{
-        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
-    }
-dz\\ \label{eq: Second moment term matrix calculation}
-&-2\exp\left(-\frac{1}{\epsilon_r^2}\langle x-w+ \meanq,\meanq \rangle \right)\\
-& \qquad \qquad \times     \int
-    \frac{ \exp\left(
-             -\frac{1}{\epsilon_r^2}\langle x-w+ \meanq, z \rangle
-              -\frac{1}{2\epsilon_r^2} ||z||^2
-            \right)e^{-\theta z^{T}\covq^{-1}z  / 2}
-        }{
-        (2 \pi/ \theta)^{d/2} |\covq|^{1/2} \label{eq: first moment term matrix calculation}
-    }
-dz\\
-&+1.
-\end{align}
-We now consider the integral of the form 
-\begin{equation}
-\int \exp(v^{T}z-C||z||^2) \frac{
-        e^{-\theta z^{T}\covq^{-1}z  / 2}
-    }{
-        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
-    }
-dz   
-\end{equation}
-for $v \in \IR^d$ and $C>0$. 
-We have 
-\begin{equation}
-\begin{aligned}
-&\int \exp(v^{T}z-C||z||^2) \frac{
-        e^{-\theta z^{T}\covq^{-1}z  / 2}
-    }{
-        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
-    }
-dz\\
-=&\frac{1}{|\covq|^{1/2}|  |\covq^{-1}(I+2C\covq/\theta )|^{1/2}  }\int \exp(v^{T}z) \frac{
-        e^{-\theta z^{T}\covq^{-1}(I+2C\covq/\theta )z  / 2}
-    }{
-        (2 \pi/ \theta)^{d/2}|\covq^{-1}(I+2C\covq/\theta )|^{-1/2} 
-    }
-dz\\
-=& \frac{1}{|I+2C\covq/\theta |^{1/2}} \mathbb{E}_{Z}[\exp (v^{T}Z)]\\
-=&\frac{1}{|I+2C\covq/\theta |^{1/2}}
-\exp 
-\left(
-\frac{1}{2}v^{T}\covq/\theta(I+2C\covq/\theta )^{-1}v
-\right),
-\end{aligned}
-\end{equation}
-where $Z \sim N(0, \covq/\theta \times (I+2C\covq/\theta )^{-1})$.
-
-Now writing $v=\frac{2}{\epsilon_r^2}( w-x-\meanq)$
-and $C=\frac{1}{\epsilon_r^2}$,
-we have the expression in Equation
-\eqref{eq: Second moment term matrix calculation} is 
-$$\frac{1}{|I+2\covq/(\epsilon_r^2\theta) |^{1/2}}
-\exp 
-\left(
-\frac{2}{\epsilon_r^4}( w-x-\meanq)^{T}\covq/\theta\left(I+2\covq/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
-\right).$$
-Similarly, writing $v=\frac{1}{\epsilon_r^2}( w-x-\meanq)$
-and $C=\frac{1}{2\epsilon_r^2}$,
-we have the expression in Equation
-\eqref{eq: first moment term matrix calculation} is 
-$$\frac{1}{|I+\covq/(\epsilon_r^2\theta) |^{1/2}}
-\exp 
-\left(
-\frac{1}{2\epsilon_r^4}( w-x-\meanq)^{T}\covq\left(I+\covq/\theta/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
-\right).$$
-As a result, we have 
-\begin{align*}
-&H_{\theta}(x,w)\\
-=& \frac{1}{|I+2\covq/(\epsilon_r^2\theta) |^{1/2}}
-\exp 
-\left(
-\frac{2}{\epsilon_r^4}( w-x-\meanq)^{T}\covq/\theta\left(I+2\covq/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
-\right)\\
-&-2\frac{1}{|I+\covq/(\epsilon_r^2\theta) |^{1/2}}
-\exp 
-\left(
-\frac{1}{2\epsilon_r^4}( w-x-\meanq)^{T}\covq/\theta\left(I+\covq/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
-\right)\\
-&+1.
-\end{align*}
-If we write $F(1/\theta)=H_{\theta}(x,w)$, i.e.
-\begin{align*}
-&F(s)\\
-=& \frac{1}{|I+2/\epsilon_r^2 \covq s |^{1/2}}
-\exp 
-\left(
-\frac{2}{\epsilon_r^4}( w-x-\meanq)^{T}\covq s \left(I+2/\epsilon_r^2 \covq s\right)^{-1}( w-x-\meanq)
-\right)\\
-&-2\frac{1}{|I+2/\epsilon_r^2 \covq s |^{1/2}}
-\exp 
-\left(
-\frac{1}{2\epsilon_r^4}( w-x-\meanq)^{T}\covq s \left(I+2/\epsilon_r^2 \covq s\right)^{-1}( w-x-\meanq)
-\right)\\
-&+1\\
-&=G_1(s)+2G_2(s)+1
-\end{align*}
-we can check that $F(0)=0$.
-As a result, 
-$$\theta H_{\theta}(x,w)\rho_r(x-w)= \theta F(1/\theta)\rho_r(x-w)=F'(s)\rho_r(x-w),$$
-for some $s \in [0, 1/\theta]$.
-
-In Equation \eqref{eq: gamma-r convolution comparison}, we have established that 
-$\rho_r(x-w) / \rho_\gamma(x-w) = C' \exp(-K (x-w)^2 / 2)$
-with $K = \frac{1}{\epsilon_r^2} - \frac{1}{\epsilon_\gamma^2}$.
-Therefore it suffices to show that for all $x,w \in \IR^d$ and $s \in [0, 1/\theta]$, 
-\begin{align}\label{eqn:goal3}
-    F'(s) \exp\left(-A (x-w)^2 \right) \le C .
-\end{align}
-
-We consider how to differentiate function $G$ of the form 
-$$G(s):=\frac{1}{|I+As|^{1/2}}\exp(v^{T}Bs(I+Cs)^{-1}v),$$
-where $A,B,C$ are matrices with non-negative entries and $I$ is the identity matrix.
-
-Since 
-\begin{equation}
-\begin{aligned}
-G'(s)=& - \frac{|A|}{2|I+As|^{3/2}}\exp(v^{T}Bs(I+Cs)^{-1}v)\\
-      & + \frac{1}{|I+As|^{1/2}}\exp(v^{T}Bs(I+Cs)^{-1}v)\\
-      & \qquad \times \left\{ v^{T}B(I+Cs)^{-1}v
-                            - sv^{T}BC(I+Cs)^{-2}v
-                    \right\}\\
-      &=\left(- \frac{|A|}{2|I+As|}+v^{T}B(I+Cs)^{-2}v
-        \right)\\
-      & \qquad \times
-        \frac{1}{|I+As|^{1/2}}\exp(v^{T}Bs(I+Cs)^{-1}v),
-\end{aligned}
-\end{equation}
-using non-negativity of $A,B,C$ we have
-\begin{equation}
-\label{eq: bounds on G'}
-|G'(s)| \leq (|A|+||B||_{2}||v||_2^2)G(s).    
-\end{equation}
-As a result, we have that 
-\begin{equation}
-\label{eq: bounds on G}
-G(s) \leq K e^{|A|+||B||_{2}||v||_2^2)s}, ~~   G'(s)(|A|+||B||_{2}||v||_2^2)K e^{|A|+||B||_{2}||v||_2^2)s}.  
-\end{equation}
-
-Finally note that, 
-$$F'(s) \leq G_1'(s)+2G_2'(s),$$
-where 
-$$A_1= 2\epsilon_r^{-2} \covq, ~ v_1=\epsilon_r^{-2}(w-x-\meanq), ~B_1 = 2\covq, ~C_1=2\epsilon_r^{-2} \covq,$$
-and 
-$$A_2= 2\epsilon_r^{-2} \covq, ~ v_2=\epsilon_r^{-2}(w-x-\meanq), ~B_2 = \covq/2, ~C_2=2\epsilon_r^{-2} \covq,$$
-Substituting these quantities on Equation \eqref{eq: bounds on G} shows that Equation \eqref{eqn:goal3} is satisfied as long as $\epsilon_r < \epsilon_\gamma$.
-
-\end{proof}
-\section{Topological Results on Lookdown Representations}
-\label{sec: Topologies on Lookdown}
-\subsection{Topology for convergence of lookdown representations}
-
-Recall that
-the lookdown representation has a spatial component and a level component.
-Specifically, for fixed $N>0$ and $t>0$,
-the lookdown representation $\xi^N(t)$ 
-is a finite measure on $\overline{\mathbb{R}^d} \times [0,N]$.
-Furthermore, the level of a particle in our lookdown representation can shoot to infinity in finite time.
-Therefore, to characterise convergence of $\xi^N(t)$ as $N \to \infty$,
-we need to impose an appropriate vague topology on $\mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty))$,
-the space of finite measures on $\overline{\mathbb{R}^d} \times [0,\infty)$.
-Similarly, to characterise convergence of the level process of individual lineages, we consider the vague topology on $[0,\infty)$.
-
-We now refer to the vague topology on measure spaces introduced in P564, \S A2 in \cite{kallenberg1997foundations}.
-Let $S$ be a locally compact Polish space and $\hat{S}$ be the class of bounded sets in $S$.
-We consider the family $C^{+}_c(S)$ of positive continuous functions with compact support. It is known that $C^{+}_c$ is separable in the uniform metric.
-We now consider $\mathcal{M}(S)$, the class of measures on $S$ that are locally finite.
-The \textit{vague topology} on $\mathcal{M}(S)$ is generated by the the maps $\mu \to \mu f := \int f d \mu$, where $f\in C^{+}_{c}(S)$.
-In other words, convergence of $\mu^n \to \mu$ in the vague topology holds if 
-$$\int f d\mu^n \to \int f d\mu$$
-for all $f\in C^{+}_{c}(S)$.
-
-We now introduce an important theorem on compactness in the vague topology.
-\begin{theorem}[Theorem A.23 in \cite{kallenberg1997foundations}]
-For any locally compact, second-countable Hausdorff Space $S$, 
-we have
-\begin{itemize}
-\item $\mathcal{M}(S)$ is Polish in the vague topology,
-\item a set $A\subset \mathcal{M}(S)$ is vaguely relatively compact iff $\sup_{\mu\in A} \mu f < \infty$ for all $f \in C^{+}_{c}$
-\item if $\mu_n \to \mu$ in the vague topology and $B \in \hat{S}$ with $\mu \partial B = 0$, then $\mu_n B \to \mu B$
-\end{itemize}
-\end{theorem}
-
-To characterise convergence of lookdown representations,
-we take $S = \overline{\mathbb{R}^d} \times [0,\infty)$.
-We now identify compact sets under the vague topologies.
-
-\begin{lemma}
-\label{lem: vague compact sets}
-For any fixed $N.0, K>0$, the set 
-$$\Gamma_{N,K} := \left\{\mu \in \mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty)):  \frac{1}{N}\mu(\overline{\mathbb{R}^d}\times [0,N]) \leq K \right\}$$
-is vaguely compact in $\mathcal{M}(S)$.
-\end{lemma}
-
-\begin{proof}
-It suffices to show that $\Gamma_K$ is vaguely relatively compact and vaguely closed.
-For any fixed $f \in C^{+}_c$, $f$ is bounded above uniformly by $||f||_{\infty}$.
-Therefore, 
-we have that $ \sup_{\mu \in  \Gamma_K} \mu f \leq  ||f||_{\infty} \mu(\overline{\mathbb{R}^d}\times [0,N])  \leq ||f|| K N < \infty$,
-so $\Gamma_{N,K}$ is vaguely relatively compact.
-
-Now it suffices to prove that $\Gamma_K$ is closed under the vague topology.
-Consider a vaguely converging sequence $(\mu_n)_{n \geq 1}$ in $\Gamma_{N,K}$
-with limit $\mu_n \to \mu \in \mathcal{M}(S)$.
-We pick some test functions $\{f_m : m \geq 0 \}$ monotonically increasing to $1_{\overline{\mathbb{R}^d}\times[0,N]}(x)$.
-
-Since for each $n>0$ and $m > 0$,
-$\frac{1}{N}\langle f_m , \mu_n \rangle < K$,
-by Dominating Convergence Theorem,
-\begin{equation}
-\frac{1}{N}\mu(\overline{\mathbb{R}^d}\times [0,N])
-= \lim_{m \to \infty} \frac{1}{N}\langle f_m , \mu \rangle
-=\lim_{m \to \infty} \lim_{n \to \infty} \frac{1}{N}\langle f_m , \mu_n \rangle
-\leq K,
-\end{equation}
-and so $\mu \in \Gamma_{N,K}$.
-Therefore $\Gamma_{N,K}$ is vaguely compact. 
-\end{proof}
-
-We now include another theorem that is very relevant to establishing tightness of $\mathcal{M}(S)$-valued processes in the Skorokhod topology. It can be found as Theorem 3.9.1 in \cite{EK}.
-
-\begin{theorem}[\cite{EK} Theorem 3.9.1]
-\label{teo: EK tightness theorem}
-Let $(S,r)$ be complete and separable, and let $\{X_{\alpha}\}$ be a family of processes with sample paths in $D_{S}([0,\infty))$.
-Suppose that the compact containment condition holds. That is, for every $\eta > 0$ and $T > 0$,
-there exists a compact set $\Gamma_{\eta, T} \subset E$ for which 
-\begin{equation}
-\inf_{\alpha} P \{ X_{\alpha}(t) \in \Gamma_{\eta,T}  ~~ \text{for } 0\leq t \leq T\} \geq 1- \eta
-\end{equation}
-Let $H$ be a dense subset of $\overline{C}(E)$ (bounded continuous functions on $E$) in the topology of uniform convergence on compact sets. 
-Then $\{X_{\alpha}\}$ is relatively compact if and only if $\{f(X_{\alpha})\}$ is relatively compact (as a family of processes with sample paths in $\mathcal{D}_{\mathbb{R}}([0,\infty))$) for each $f \in H$.
-\end{theorem}
-
-To apply Theorem \ref{teo: EK tightness theorem},
-we need to identify dense subset of $\overline{C}(\mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty)))$.
-Since the space $\mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty))$ is not compact but locally compact,
-we will apply Stone-Weierstrass theorem for locally compact space.
-
-\begin{lemma}[Stone-Weierstrass Theorem for locally compact space]
-\label{lem: SW locally compact}
-Let $X$ be a locally compact Hausdorff space, and consider the set  $C_{\infty}(X, \mathbb{R})$ of real-valued continuous functions which vanishes at infinity. 
-Let $\mathcal{A}$ be a subalgebra in $C_{\infty}(S)$. Then $\mathcal{A}$ is dense in $C_{\infty}(X, \mathbb{R})$ if and only if it separates points and vanishes nowhere.
-\end{lemma}
-
-With this version of Stone-Weierstrass Theorem, we can prove the following lemma.
-\begin{lemma}
-\label{lem: uniform compact density}
-We write $\mathcal{A}$ for the algebra (closed under multiplication and addition) generated by 
-the collection of functions $\xi \mapsto \langle f, \xi \rangle$, where $ f \in C_c(\overline{\mathbb{R}^d} \times [0,\infty))$ is differentiable in $u$ and smooth in $x$ with bounded support.
-Then $\mathcal{A}$ is dense in $C(\mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty)))$ under the topology of uniform convergence on compact sets.
-\end{lemma}
-\begin{proof}
-Since $\mathcal{A}$ contains the functions $\langle \rho_{\varepsilon}*\mathbbm{1}_{A} , \mu \rangle$,
-where $\rho$ is some mollifier and $A$ is a compact set, it clearly
-separates points and vanishes nowhere.
-Therefore, $\mathcal{A}$ is dense in $C_{\infty}(\mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty)), \mathbb{R})$.
-
-Furthermore, under the topology of uniform convergence on compact sets, 
-$C_{\infty}(\mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty)), \mathbb{R})$ 
-contains the mollified indicator functions $\langle \rho_{\varepsilon}*\mathbbm{1}_{A} , \mu \rangle$,
-which are dense in $C(\mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty)))$.
-\end{proof}
-
-Finally, we include another technical lemma on the products of real-valued stochastic processes. 
-\begin{lemma}
-\label{teo: product tightness}
-Let $\{(X^n_t)_{t \geq 0}: n \geq 0\}, \{(Y^m_t)_{t \geq 0}: m \geq 0\}$ be two tight sequences of real-valued process under the Skorokhod topology.
-Then the sequence of processes $\{(X^n_tY^n_t)_{t \geq 0}: n \geq 1\}$ is tight under the Skorokhod topology.
-\end{lemma}
-
-\begin{proof}
-We apply the Aldous Criterion of tightness on the real-valued sequences
-$\{(X^n_tY^n_t)_{t \geq 0}: n=1,2,.. \}$. 
-It suffices to show that
-for fixed sequences of stopping time $\tau_n$ bounded above by $T$,
-for each $\varepsilon>0$,
-there exists $\delta > 0$ and $n_0$ such that
-\begin{equation}
-\sup_{n \geq n_0}\sup_{\theta \in [0, \delta]} \mathbb{P}\left[|X^n_{\tau_n+\theta}Y^n_{\tau_n+\theta} - X^n_{\tau_n}Y^n_{\tau_n} | > \varepsilon \right] \leq \varepsilon.
-\end{equation}
-
-First note that 
-\begin{equation}
-|X^n_{\tau_n+\theta}Y^n_{\tau_n+\theta} - X^n_{\tau_n}Y^n_{\tau_n} |
-= |X^n_{\tau_n+\theta}(Y^n_{\tau_n+\theta}-Y^n_{\tau_n}) +Y^n_{\tau_n}( X^n_{\tau_n+\theta}- X^n_{\tau_n})|,
-\end{equation}
-therefore
-\begin{equation}
-\begin{aligned}
-& \mathbb{P}\left[|X^n_{\tau_n+\theta}(Y^n_{\tau_n+\theta}-Y^n_{\tau_n}) +Y^n_{\tau_n}( X^n_{\tau_n+\theta}- X^n_{\tau_n})| > \varepsilon \right]\\
- \leq &
-\mathbb{P}\left[\max\{|X^n_{\tau_n+\theta}(Y^n_{\tau_n+\theta}-Y^n_{\tau_n})|, | Y^n_{\tau_n}( X^n_{\tau_n+\theta}- X^n_{\tau_n}) |\}> \varepsilon/2 \right]\\
-\leq & \mathbb{P}\left[|X^n_{\tau_n+\theta}(Y^n_{\tau_n+\theta}-Y^n_{\tau_n})|> \varepsilon/2 \right] + \mathbb{P}\left[ | Y^n_{\tau_n}( X^n_{\tau_n+\theta}- X^n_{\tau_n}) |> \varepsilon/2 \right]
-\end{aligned}
-\end{equation}
-
-By Corollary 3.7.1 in \cite{EK}, both $\{(X^n_t)_{t \geq 0}: n \geq 0\}, \{(Y^m_t)_{t \geq 0}: m \geq 0\}$ satisfies the compact containment condition, i.e.
-so for any $\varepsilon'>0$ and fixed time $T> 0$, there exists $K_{\varepsilon',T}>0$ such that
-
-\begin{equation}
- \limsup_{n \to \infty} \mathbb{P}\left\{ \sup_{t\in [0,T]}X^n_t > K_{\varepsilon',T} \right\} < \epsilon',
-\end{equation}
-and 
-\begin{equation}
- \limsup_{n \to \infty} \mathbb{P}\left\{ \sup_{t\in [0,T]}Y^n_t > K_{\varepsilon',T} \right\} < \epsilon'.
-\end{equation}
-
-Conditioning on the event $\left\{ \sup_{t\in [0,T]}Y^n_t > K_{\varepsilon',T} \right\}$ and $\left\{ \sup_{t\in [0,T]}Y^n_t > K_{\varepsilon',T} \right\},$
-
-\begin{equation}
-\begin{aligned}
-& \mathbb{P}\left[|X^n_{\tau_n+\theta}(Y^n_{\tau_n+\theta}-Y^n_{\tau_n})|> \varepsilon/2 \right] + \mathbb{P}\left[ | Y^n_{\tau_n}( X^n_{\tau_n+\theta}- X^n_{\tau_n}) |> \varepsilon/2 \right]\\
-\leq & \mathbb{P}\left[|(Y^n_{\tau_n+\theta}-Y^n_{\tau_n})|> \frac{\varepsilon}{2K_{\varepsilon',T}}\right] + \mathbb{P}\left[ | Y^n_{\tau_n}( X^n_{\tau_n+\theta}- X^n_{\tau_n}) |> \frac{\varepsilon}{2K_{\varepsilon',T}}\right] + 2 \varepsilon'\\
-\leq & \frac{\varepsilon}{K_{\varepsilon',T}}+2 \varepsilon',
-\end{aligned}
-\end{equation}
-and by tightness of $(X^n_t, Y^n_t)_{t \geq 0}$,
-there exists $\delta > 0$ and $n \geq n_0$ such that the last term is smaller than $\varepsilon$ for 
-for all $\theta < \delta$ and $n\geq n_0$.
-\end{proof}
-
-When we work with lookdown representations, we work on test functions of the form
-\begin{equation}
-F_g(\xi) = \prod_{(x,u) \in \xi} g(x,u),
-\end{equation}
-where $g(x,u)$ is differentiable in $u$, smooth in $x$.
-and satisfies the property that $0\leq g(x,u) \leq 1$,
-and that there exists $u^*$ such that for all $u > u^*$,
-$g(x, u) =1$.
-
-In fact, there is a one-to-one correspondence between $C^{+}_c(S)$
-and test functions of the form $F_g$.
-For all $f \in C^{+}_c(S)$,
-if we write $g = e^{-f}$,
-then
-\begin{equation}
-F_g(\xi)= e^{-\langle f, \xi \rangle}.
-\end{equation}
-
-Furthermore,
-we know that for any $x_1, x_2 \in [0,N]$,
-$$|x_1-x_2|\geq |e^{-x_1}-e^{-x_2}| \geq e^{-N}|x_1-x_2|,$$
-so we can control $\langle f, \xi^n_t \rangle $ by controlling $F_g(\xi^n_t)$ as long as 
-there exists some $N > 0$ such that $\langle f, \xi^n_t \rangle < N$.
-
-With the above observation,
-we have the following lemma.
-
-\begin{lemma}
-We consider a sequence $(\xi^n_t)_{t\geq 0}$ of $\mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty))$-valued cadlag processes.
-
-Assume that the sequence $(\xi^n_t)_{t\geq 0}$ satisfies the compact containment condition. That is,
-for all $\varepsilon > 0$ and fixed time $T > 0$, there exists $N, K> 0$ such that 
-\begin{equation}
-\liminf_{n \to \infty} \mathbb{P}\{ \xi^n_t \in \Gamma_{N,K} \text{ for all } t\in [0,T]\} > 1-\varepsilon,
-\end{equation}
-where $\Gamma_{N,K}$ is the compact set in Lemma \ref{lem: vague compact sets}
-
-Assume that for all test functions of the form $F_g$,
-the sequence $\{(F_g(\xi^n_t))_{t \geq}: n=1,2,...\}$ of real-valued cadlag processes are relatively compact.
-
-Then  $(\xi^n_t )_{t\geq 0}$ is relatively compact in $\mathcal{D}_{\mathcal{M}(\overline{\mathbb{R}^d} \times[0,\infty))}([0,T])$.
-\end{lemma}
-
-\begin{proof}
-By Lemma  \ref{lem: uniform compact density}, \ref{teo: product tightness}, and Theorem 3.9.1 in \cite{EK},
- $(\xi^n_t )_{t\geq 0}$ is relatively compact in $\mathcal{D}_{\mathcal{M}(\overline{\mathbb{R}^d} \times[0,\infty))}([0,T])$
- if we can prove tightness on the real-valued sequences
-$\{(f(\xi^n_t))_{t \geq 0}: n=1,2,.. \}$.
-
-Applying the Aldous Criterion, it suffices to show that
-for fixed sequences of stopping time $\tau_n$ bounded above by $T$,
-for each $\varepsilon>0$,
-there exists $\delta > 0$ and $n_0$ such that
-\begin{equation}
-\sup_{n \geq n_0}\sup_{\theta \in [0, \delta]} \mathbb{P}\left[|\langle f, \xi^n_{\tau_n+\theta}\rangle - \langle f, \xi^n_{\tau_n}\rangle | > \varepsilon \right] \leq \varepsilon.
-\end{equation}
-
-First we pick $N,M>0$ such that 
- $$\sup_{n \geq M} \mathbb{P}\left\{ \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle > N \right\} < \epsilon /2 .$$
-Then, we can partition the event $\{|\langle f, \xi^n_{\tau_n+\theta}\rangle - \langle f, \xi^n_{\tau_n}\rangle | > \varepsilon\}$ into two subsets according to the event 
-$ \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle > N$.
-
-By the compact containment condition, 
-we know that for any $f \in C^{+}_{c}(\overline{\mathbb{R}^d} \times [0,\infty))$ and $\epsilon > 0$, there exists $N>0$ (dependent on $f$ and $\epsilon$), 
-such that 
-\begin{equation}
-\label{eq: vague compact containment condition}
- \limsup_{n \to \infty} \mathbb{P}\left\{ \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle > N \right\} < \epsilon.
-\end{equation}
-
-Therefore, for all $n>M$,
-\begin{equation}
-\begin{aligned}
- &\mathbb{P}\left[|\langle f, \xi^n_{\tau_n+\theta}\rangle - \langle f, \xi^n_{\tau_n}\rangle | > \varepsilon \right]\\
- =& \mathbb{P}\left[|\langle f, \xi^n_{\tau_n+\theta}\rangle - \langle f, \xi^n_{\tau_n}\rangle | > \varepsilon ,  \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle > N \right]\\
- & + \mathbb{P}\left[|\langle f, \xi^n_{\tau_n+\theta}\rangle - \langle f, \xi^n_{\tau_n}\rangle | > \varepsilon,  \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle \leq N \right]\\
-< & \varepsilon/2 + \mathbb{P}\left[|e^{-\langle f, \xi^n_{\tau_n+\theta}\rangle} - e^{-\langle f, \xi^n_{\tau_n}\rangle }| > e^{-N}\varepsilon,  \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle \leq N \right]\\
-< & \varepsilon/2 + \mathbb{P}\left[|F_g(\xi^n_{\tau_n+\theta})-F_g(\xi^n_{\tau_n})| > e^{-N}\varepsilon\right].
-\end{aligned}
-\end{equation}
-
-Finally, by tightness of the processes $\{F_g(\xi^n_t): n = 1,2,...\}$, 
-we can pick large enough $n_0 > M$ and $\delta > 0$
-such that 
-$$\sup_{n \geq n_0}\sup_{\theta \in [0,\delta]}\mathbb{P}\left[|F_g(\xi^n_{\tau_n+\theta})-F_g(\xi^n_{\tau_n})| > e^{-N}\varepsilon\right]< e^{-N}\varepsilon,$$
-so
-\begin{equation}
-\sup_{n \geq n_0}\sup_{\theta \in [0, \delta]} \mathbb{P}\left[|\langle f, \xi^n_{\tau_n+\theta}\rangle - \langle f, \xi^n_{\tau_n}\rangle | > \varepsilon \right] \leq \varepsilon / 2 + e^{-N} \varepsilon < \varepsilon.
-\end{equation}
-
-We have proved relative compactness of $\{(\langle f, \xi^n_t \rangle )_{t \geq 0}: n=1,2,.. \}$, and thus tightness of 
- $\{(\xi^n_t )_{t \geq 0}: n=1,2,.. \}.$
-\end{proof}
-
 \bibliographystyle{plainnat}

### 2023-01-30 tightness_of_paths.tex
edits!

--- 2022-09-04 forwards-and-backwards.tex
@@
-\documentclass[12pt]{article}
-\usepackage{fullpage}
-\usepackage{amssymb}
-\usepackage{graphics} 
-\usepackage{amsmath}
-\usepackage[color=yellow]{todonotes}
-\usepackage{url}
-\usepackage{xcolor}
-\usepackage{longtable}
-\usepackage[hidelinks]{hyperref}
-\usepackage{bbm}
-
-\usepackage{natbib}
-
-\newenvironment {proof}{{\noindent\bf Proof }}{\hfill $\Box$ \medskip}
-
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{condition}[theorem]{Condition}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{remark}[theorem]{Remark}
-\newtheorem{hypothesis}[theorem]{Hypothesis}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{example}[theorem]{Example}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{notation}[theorem]{Notation}
-
-\renewcommand{\theequation}{\arabic{section}.\arabic{equation}}
-\def \non{{\nonumber}}
-\def \hat{\widehat}
-\def \tilde{\widetilde}
-\def \bar{\overline}
-\newcommand{\IP}{\mathbb P}
-\newcommand{\IQ}{\mathbb Q}
-\newcommand{\IE}{\mathbb E}
-\newcommand{\IR}{\mathbb R}
-\newcommand{\IZ}{\mathbb Z}
-\newcommand{\IN}{\mathbb N}
-\newcommand{\IT}{\mathbb T}
-\newcommand{\IC}{\mathbb C}
-\newcommand{\ind}{\mathbf{1}}
-\newcommand{\bigO}{\mathcal{O}}
-\newcommand{\grad}{\nabla}
-\newcommand{\dif}{\mathrm{d}\,}
-
-%%%%%%% notation
-\newcommand{\DG}{\mathcal{B}}  % generator of the dispersal process
-\newcommand{\DD}{\mathcal{D}}  % the second-order part of the generator of dispersal
-\newcommand{\meanq}{\vec b}    % mean of dispersal, times theta
-\newcommand{\covq}{C}     % covariance matrix of dispersal, times theta
-\newcommand{\kernel}{\rho}  % interaction kernels
-\newcommand{\smooth}[1]{\kernel_{#1} \! * \!}  % convolution by the interaction kernel
-\newcommand{\wavespeed}{\mathfrak{c}}    % speed (vector) of a wave
-\newcommand{\Lgen}{\mathcal{L}}    % generator of a lineage
-\newcommand{\Pgen}{\mathcal{P}}    % generator of the population process
-\newcommand{\lp}{\xi}              % process with levels
-\newcommand{\labelspace}{\mathcal{I}} % space of labels
-\newcommand{\concat}{\oplus}   % concatenation of labels
-\newcommand{\measures}{\mathcal{M}_F(\IR^d)} % finite measures on Rd
-\newcommand{\cmeasures}{\mathcal{M}_F(\overline{\IR}^d)} % finite measures on compactified Rd
-\newcommand{\lpmeasures}{\mathcal{M}(\overline{\IR^d} \times [0,\infty))} % locally finite measures on space x level
-
-\newcommand{\plr}[1]{\todo[inline]{Peter: #1}}
-\newcommand{\comment}[1]{{\color{blue} \it #1}}
-
-\begin{document}
-
-\title{\large{\bf
-Looking forwards and backwards through locally regulated populations
-}}
-
-% OTHER IDEAS:
-% A class of nonlinear superprocesses
-% Uncovering genealogical structures of locally regulated populations with lookdown constructions on nonlinear superprocesses
-
-\author{ \begin{small}
-\begin{tabular}{ll}                              
-Alison M. Etheridge 
- & Thomas G. Kurtz \\   
-Department of Statistics & Departments of Mathematics and Statistics\\       
-Oxford University & University of Wisconsin - Madison \\                   
-24-29 St Giles & 480 Lincoln Drive\\                                                         
-Oxford OX1 3LB & Madison, WI  53706-1388\\
-UK & USA \\                        
-etheridg@stats.ox.ac.uk & kurtz@math.wisc.edu     \\
-\url{http://www.stats.ox.ac.uk/~etheridg/} & 
-\url{http://www.math.wisc.edu/~kurtz/}  \\       \\
-\\
-Ian Letter&  Peter L. Ralph 
-\\   
-Department of Statistics & Department of Mathematics \\
-Oxford University &University of Oregon\\                   
-24-29 St Giles & Fenton Hall\\
-Oxford OX1 3LB & Eugene, OR 97403-1222\\
-UK & USA \\
-restucci@stats.ox.ac.uk  & plr@oregon.edu \\
-\url{https://www.stats.ox.ac.uk/~restucci/}&
-\url{https://math.uoregon.edu/profile/plr} \\
-\\
-Terence Tsui 
- &  \\   
-Department of Statistics & \\
-Oxford University & \\                   
-24-29 St Giles& \\
-Oxford OX1 3LB & \\
-UK & \\
-terence.tsui@sjc.ox.ac.uk &      \\
-\url{https://www.maths.ox.ac.uk/people/terence.tsui}&  \\
-\end{tabular}
-\end{small}}
-
-\date{\today}
-\maketitle
-
-\begin{abstract}
-
-We do something...
-
-make sure to put in here that we get convergence of the FKPP
-
-Note: use "reproductive value" instead of "long-term fitness"
-and say clearly that "lineage" means "ancestral lineage".
-
-\vspace{.1in}
-
-\noindent {\bf Key words:}  population model, nonlinear superprocess, 
-lookdown construction, porous medium equation, 
-reaction-diffusion equation, travelling waves, genealogies,
-
-\vspace{.1in}
-
-\noindent {\bf MSC 20}10 {\bf Subject Classification:}  Primary:  
-%60J25, 92D10, 92D15, 92D25 92D40  
-\\Secondary:   %60F05, 60G09, 60G55, 60G57, 60H15, 60J68
-
-\end{abstract}
-\tableofcontents
-\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-
-\comment{I think the introduction covers a good set of things in a good order, it's just a bit long.}
-
-\comment{
-    Make sure that we discuss the difference to Flandoli's model
-    (one of the few others that show convergence of FKPP),
-    and say that a novelty of our results is that we show convergence
-    for FKPP and broader models.
-}
-
-\comment{TO CITE: \citet{ghosh2022emergent}}
-
-As one takes a journey, long or short, the landscape changes:
-forests thicken or thin or change their composition,
-springtime grasslands host intergrading mosaics of different types of flowers.
-The aim of this paper is to understand the implications of a broad class of mechanistic spatial models
-that might describe how such spatially heterogeneous populations live, die, and reproduce:
-How does population density change across space and time?
-How might we learn about the underlying dynamics from genealogical or genetic data?
-And,  how does genetic ancestry spread across geography,
-when looking back through time in these populations?
-We work with individual-based models of a single species in continuous space,
-where birth, death and establishment may all depend on spatial location
-as well as on local population density, allowing for stable populations through density-dependent feedback.
-
-Reproduction of individuals naturally leads to a branching process.
-There is now a huge literature devoted to spatial branching processes,
-including branching random walk, 
-branching Brownian motion, and the Dawson-Watanabe superprocesses.  
-In addition to possessing a rich and beautiful mathematical structure, 
-the superprocesses are remarkable for demonstrating a certain `universality', 
-arising, as they do, as scaling limits of a vast array of different 
-spatial population models \cite[e.g.,][]{chetwynd-diggle/etheridge:2018,
-cox/perkins:2005,
-cox/durrett/perkins:1999,
-cox/durrett/perkins:2000,
-holmes:2008,
-vanderhofstad/sakai:2010,
-vanderhofstad/slade:2003,
-vanderhofstad/holmes/perkins:2017}.
-
-These models make mathematical sense in very general spaces, but
-in biological applications, typically, 
-individuals are assumed to be scattered across one or two-dimensional
-Euclidean space. In that setting, it is well known that, 
-in the long term, the population will either 
-die out, or it will develop clumps of arbitrary density and extent. 
-To counter this, it is common to
-impose some local regulation by either increasing death rates, or 
-reducing birth rates, in proportion to the local population density,
-so that the population has a tendency to grow in sparsely populated regions
-and shrink where it is overcrowded. This leads to spatial analogues of  
-logistic branching processes.
-
-Although it can be more mathematically convenient to work with branching
-Brownian motions, in many settings it is biologically more natural to 
-develop models based on branching random walk.  
-Individuals produce a random number of offspring,
-that are thrown off according to some (usually symmetric) 
-distribution centred on the location of the parent.   
-This is particularly appropriate for modelling plant populations, in which
-this dispersal of offspring around the parent is the only source of
-spatial motion.
-
-Most models do not distinguish between juveniles and adults, so,
-for example, the number of adults produced by a single parent is determined
-by the degree of crowding at the location of the parent. The novelty
-of the models that we introduce here is that, although we shall only
-follow the adult population, in formulating the dynamics of the
-models we shall distinguish
-between production of juveniles, which will depend upon the location of 
-the adult, and their successful establishment, which will depend on the
-location in which a juvenile lands. The result is that not only the absolute 
-number, but also the spatial distribution
-around their parent, 
-of those offspring that survive to adulthood
-will depend upon the local population 
-density.
-
-We shall consider different classes of scaling limits for our model; the first class consisting of
-(generalised) super-processes limits, and the second class where the limits are deterministic. In the
-superprocess setting, for our approach to work we measure the local population
-density at a point by integrating against a smooth test function, for example 
-a Gaussian density centred on that point.  
-When the limit is deterministic,
-we can simultaneously reduce the parameter in that Gaussian density so that,
-in the limit, the local population density is simply the population density 
-at that point. Nonetheless, we retain a signal of our two stage approach
-to modelling reproduction, and  
-in this way we recover a nonlinear partial differential equation. 
-This approach requires some technical conditions that we will verify in two important examples,
-the porous medium equation with a logistic growth term of the form 
-$$\partial_t \varphi = \Delta (\varphi^2)+\varphi(1-\varphi),$$
-and a wide class of semi-linear partial differential equations of the form 
-$$\partial_t \varphi = \Delta\varphi+ \varphi \left(G(\varphi)-H(\varphi)\right),$$
-which include the Fisher-KPP equation and the Allen-Cahn equation.
-
-The porous medium equation (PME)
-is a degenerate nonlinear diffusion equation that
-has been the subject of intensive study. We refer to~\cite{vazquez:2007} for 
-a comprehensive reference. The equation has also been studied with various
-forms of noise, see~\cite{barbu/daprato/roeckner:2016}, although not the 
-form of noise that will arise from the population dynamics below. 
-Deriving nonlinear diffusion equations as limits of weakly interacting 
-diffusions goes back at least to~\cite{mckean:1967}, and this 
-programme has been
-carried out for the PME and its generalisations. 
-The degeneracy of the PME
-results in some extra analytic
-challenges,~\cite{jourdain:2000}.
-% Recent work in this 
-% direction has been spurred on by applications
-% in mathematical finance, %where the porous medium arises 
-% in particular, in the study of weak limits of systems
-% of diffusions interacting through their 
-% rank,~\cite{dembo/shkolnikov/varadhan/zeitouni:2016, jourdain/reygner:2013}
-% and references therein.
-Our approach is different.
-We start from individual
-based population models, thus providing a microscopic mechanism that leads to 
-nonlinear diffusion.
-Other microscopic mechanisms have been proposed in the special case of the
-PME, see 
-e.g.~\cite{feng/iscoe/seppalainen:1997, oelschlaeger:1990}; ours
-is specifically motivated by biological considerations.
-
-Another novelty of our models stems from the use of lookdown construction to retain the dynamics of lines of descent in our population while passing to a scaling limit.
-The lookdown construction is first introduced in \cite{donnelly/kurtz:1996} to provide a mechanism to trace lineages while passing through a scaling limit for the Moran model.
-In more recent works, see~\cite{kurtz/rodrigues:2011, etheridge/kurtz:2018}, lookdown constructions are further applied into models of branching populations with spatial structures.
-In \S \ref{Sec: Lookdown Constructions}, we follow closely the techniques presented in these papers to impose lookdown constructions for our models which allow us to retain information about ancestry of individuals in the population as we pass to a large population limit.
-This in turn allows us to write down an explicit expression for the generator of the position of ancestral lineages with respect to the travelling wave fronts for populations modelled by a huge class of semi-linear partial differential equations, see Theorem \ref{teo:ancestral lineages}.
-This attempt is novel and we have provided the first ever rigorous proof to similar results on ancestral lineages.
-This result allows us to compare ancestral lineages of individuals sampled from the front of a population evolving according to the PME with logistic growth to those under the Fisher-KPP and Allen-Cahn equations.
-For example, as a result of the nonlinear diffusion,
-for suitable initial conditions, the solution to the one-dimensional 
-porous medium equation with logistic growth converges to a travelling
-wave with a sharp cut-off; i.e., in contrast to the classical 
-Fisher KPP equation, the solution at time $t$
-vanishes beyond $x=x_0+ct$ for some constant wavespeed
-$c>0$, \cite{kamin/rosenau:2004}.
-
-\comment{Need a transition or otherwise to merge this with the above.}
-The history of a natural population is often only accessible indirectly 
-through patterns of genetic diversity that have been laid down. From 
-genetic data, one can try to infer the genealogical trees that relate 
-individuals in a sample from the population. It is therefore of interest
-to establish the distribution of genealogical trees relating individuals
-sampled from a population evolving according to any proposed mathematical
-model.
-
-In general this is an extremely difficult question. However, in special
-circumstances, some progress can be made. One of the settings that
-has received a great deal of attention in recent years is that in which 
-a population is expanding into new territory as a travelling wave. 
-Typically one considers a stationary wavefront moving across $\IR^1$, and
-most work has focussed on the classical Fisher-KPP equation with a 
-stochastic term, i.e.
-$$dw=\big(\Delta w +sw(1-w)\Big)dt +\sqrt{\frac{\alpha(w)}{N}}W(dt,dx),$$
-where $W$ is space-time white noise, and $N$ is a measure of the 
-local population density. The coefficient
-$\alpha(w)$ is generally taken to be either
-$w$, corresponding to a superprocess limit, or $w(1-w)$ giving a 
-spatial analogue of a Wright-Fisher diffusion. The first is 
-appropriate for modelling the range of an expanding population,
-the second for the spread of a selectively advantageous 
-mutation through an established (selectively neutral) population. 
-Because of the logistic control of the growth rate,
-individuals in the wavefront can have much greater reproductive success
-than those in the `bulk' of the expanding population. 
-Tracing backwards in time, individuals sampled
-from behind the wave are `caught' by the wave, upon which they become
-trapped in the wavefront. If the population density is very high, then over
-suitable timescales, the genealogical trees will be dominated by 
-periods of extremely rapid coalescence corresponding to a significant 
-proportion of the individuals in the front being descended from a particularly
-reproductively successful ancestor. For a surprisingly wide range of models, 
-it is believed that, for very large $N$ and on suitable timescales, 
-genealogies converge to a 
-Bolthausen-Sznitman coalescent, e.g.~\cite{brunet/derrida/mueller/munier:2007}. 
-On the other hand, if one replaces the logistic growth term of the classical
-Fisher-KPP equation with a nonlinearity that reflects cooperative
-behaviour in the population, such as
-$$wF(w)=w(1-w)(Cw-1),$$
-then, for sufficiently large $C$ (strong cooperation),
-the nature of the deterministic
-wave changes from `pulled' to `pushed', \cite{birzu/hallatschek/korolev:2017}.
-In that setting, the genealogies will also be quite different
-from the Fisher-KPP case. For example, \cite{etheridge/penington:2020}
-shows that for a discrete space model corresponding to this 
-nonlinearity with $C>4$, after suitable scaling, the genealogy of a
-sample converges not to a Bolthausen-Sznitman coalescent, but to
-a Kingman coalescent. 
-\todo[inline]{Is that condition $C>4$ correct?
-the paper with Sarah is done for the equation $\partial_t u = \Delta u + u(1-u)(2u-1+\alpha)$ and valid for $\alpha \in (0,1)$.
-Factorising we would get that equation would be $\partial_t u = \Delta u + (1-\alpha) u(1-u)(\frac{2}{1-\alpha}u-1)$.
-Supposing the $(1-\alpha)$ in front does not affect the result (which I suppose wouldn't) we get that $C= \frac{2}{1-\alpha}$ and so $\alpha \in (0,1)$ if and only if $C>2$ ...}
-The reason, roughly, is that ancestral lineages
-settle to a stationary distribution relative to the position of the 
-wavefront which puts very little weight close to the `tip' of the wave, so
-that when ancestral lineages meet,
-it is typically in a location where population density is
-high, where no single ancestor produces a disproportionately large number of 
-descendants in a short space of time.
-
-As a first step towards understanding what we should expect in models with
-nonlinear diffusion, we consider the position of an ancestral lineage
-relative to the wavefront in the deterministic models, and compare that 
-to what we see for a classical Fisher-KPP equation. 
-In~\S\ref{sec: wright-malecot}, we then indicate how to extend these ideas to 
-extract information about relatedness between two individuals in the 
-superprocess limit, at least when population intensity is very high, and
-we present some evidence to support the conjecture that genealogies 
-for populations expanding according to 
-our superprocess models with nonlinear diffusion
-can be very different from those under 
-the classical Fisher-KPP equation.
-
-% % % % % % % % % % % % % %
-\paragraph{Structure of the paper}
-In the paper we study scaling limits of spatial populations,
-obtaining convergence of both the population process
-(i.e., the population density as a function of time,
-although strictly speaking it is a measure that may not have a density)
-as well as of lineages traced back through such a population.
-We retain linages through the rescaling process
-by means of a lookdown construction.
-First, in section~\ref{sec: Model and main results},
-we describe the model and the main theorems
-(Theorems~\ref{thm:nonlocal_convergence}, \ref{thm:local_convergence}, and~\ref{thm:lineages}).
-Next, in Section~\ref{sec:applications}, we discuss a few striking consequences of these results,
-namely, X Y and Z \comment{TODO}.
-In section \ref{sec:heuristics}, we provide heuristic explanations
-of why the theorems ought to be true,
-and some key ideas behind them.
-In Section \ref{sec:lookdown} we define and discuss the lookdown process that retains the levels.
-This is followed by the technical proofs in section \ref{sec:proofs}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Model and main results}
-    \label{sec: Model and main results}
-
-The model we work with is a fairly general model
-of individuals living in continuous space.
-We start with a population of
-$\bigO(N)$ individuals per unit area distributed in $\IR^d$.
-For applications, $d=1$ or $d=2$, but our results apply more generally.
-The population will be distributed over a bounded region,
-so the total number of individuals will also be $\bigO(N)$.
-The population changes in continuous time, and
-we describe the state of the population at time $t$ with a counting measure $X(t)$,
-which assigns one unit of mass to the location of each individual.
-
-Population dynamics are controlled by three quantities,
-birth ($\gamma$), establishment ($r$), and death ($\mu$),
-each of which can depend on spatial location and local population density
-in a way we specify later.
-Each individual gives birth at rate $\gamma$ to a single offspring,
-and the offspring
-then disperses according to a kernel $q(\cdot)$ away from the location of the parent.
-We assume that $q$ is the density of a multivariate Gaussian,
-allowing a nonzero mean and anisotropic variance.
-Both the mean and covariance can change across space,
-but do not depend on population density.
-The offspring does not necessarily survive to be counted in the population:
-it ``establishes'' with probability $r$,
-or else it dies immediately.
-Independently, each individual dies with rate $\mu$.
-
-We aim to obtain universal behavior by taking the density, $N$, to infinity,
-and also scaling time by a factor of $\theta$,
-so that defining $\eta(t) = X(\theta t) / N$,
-the process $\{\eta(t)\}_{t \ge 0}$
-will converge to a suitable measure-valued process
-as $N$ and $\theta$ tend to infinity,
-with the nature of the limit depending on how they tend to infinity together.
-Demographic rates in our model
-will be determined by local population density relative to $N$,
-so that population dynamics depend more naturally on $\eta$ (rather than $X$).
-However, to avoid confusion arising from the time scaling,
-we describe the model in terms of $X$ next.
-See Figure~\ref{fig:model_setup} for a conceptual depiction.
-
-\begin{figure}
-    \begin{center}
-        \includegraphics{figures/conceptual_figure}
-    \end{center}
-    \caption{
-        \comment{Perhaps we should have two panels, one with the PME example (currently panel A) and the other with FKPP;
-        right now panel B is not very helpful I think, so maybe should be omitted or added to so it better describes the whole process
-        (including dispersal and establishment).}
-        Conceptual figure of the model.
-        \textbf{(A)} Example plot of $\gamma$, $\mu$, and $F$
-        (calculated here with $r=1$) against scaled local population density.
-        In this example, both birth and death rates increase with population density,
-        but death increases faster,
-        and equilibrium occurs where they cross
-        (and hence where $F=0$).
-        \textbf{(B)} Cartoon of interaction ($\epsilon$) and dispersal ($\sigma$) distances.
-        \label{fig:model_setup}
-    }
-\end{figure}
-
-Birth, establishment, and death can depend on the location of the individual
-and the local population density.
-Since we would like the population density to scale with $N$,
-these are functions of $X/N$, i.e.,
-the counting measure with mass $1/N$ placed at the location of each individual.
-To measure local population density, we convolve the population measure with
-an ``interaction kernel'' -- which, for simplicity, we take to be Gaussian,
-and we write as
-$$
-    p_{\epsilon^2}(x) := \frac{1}{(2 \pi \epsilon^2)^{d/2}} e^{-\|x\|^2 / 2 \epsilon^2} ,
-$$
-for an ``interaction distance'' $\epsilon$.
-First consider birth rates, defined by
-a nonnegative function $\gamma(x, m) : \IR^d \times \IR_{\ge 0} \to \IR_{\ge 0}$
-of location $x$ and local population density $m$,
-and an interaction distance $\epsilon_\gamma > 0$.
-Local population density enters through the convolution of $X$ with $p_{\epsilon_\gamma^2}$,
-which we write as $\smooth{\gamma} X$.
-Then, the birth rate of an individual at location $x$ when the state of the population is $X$
-is $\gamma(x, \smooth{\gamma} X(x) / N)$.
-Similarly, the establishment probability of an offspring at location $x$ is
-is $r(x, \smooth{r} X(x) / N)$,
-where $r(x, m) : \IR^d \times \IR_{\ge 0} \to [0, 1]$
-and again $\smooth{r} X$ is the convolution of $p_{\epsilon_r^2}$ with $X$.
-Rather than defining a function $\mu(x, m)$ for the death rate,
-it turns out to be more convenient to parameterize in terms of the net reproductive rate,
-which we denote by $F(x, m)$,
-scaled by $1/\theta$
-so that the population density changes over a time scale of $\theta$.
-(This corresponds to a ``near-critical branching'' assumption.)
-Informally, we would like that
-$$
-    F = \theta (r \gamma - \mu) ,
-$$
-and to arrange this we define
-the death rate of an individual at $x$ to be
-\begin{align} \label{eqn:mu_defn}
-    \mu
-    =
-    \max\left\{0, 
-        r(x, \smooth{r} X(x) / N) \gamma(x, \smooth{\gamma} X(x) / N)
-        - \frac{1}{\theta} F(x, \smooth{F} X(x) / N)
-    \right\} ,
-\end{align}
-where again $F(x, m) : \IR^d \times \IR_{\ge 0} \to \IR_{\ge 0}$
-and $\kernel_F = p_{\epsilon_F^2}$.
-
-In summary, each of the three demographic parameters depend on local density measured
-with a Gaussian kernel with possibly different scales:
-for birth over a scale of $\epsilon_\gamma$,
-for establishment over a scale of $\epsilon_r$,
-and for net reproductive rate over a scale of $\epsilon_F$.
-Note that death rate depends in principle on population densities at three different scales,
-so that we could write $\mu = \mu(x, \smooth{\gamma} X(x) / N, \smooth{r} X(x) / N, \smooth{F} X(x) / N)$.
-It might seem like
-we have introduced unnecessary complexity
-with these three different spatial scales on which interactions occur.
-However,
-it will turn out to be useful in the proofs to have $\epsilon_r < \epsilon_\gamma$,
-although in the limit they can be taken equal to each other
-(and $\epsilon_F$ is unconstrained),
-so informally we think of local density as being determined on a scale of $\epsilon$.
-
-\begin{remark}
-Although this model allows fairly general birth and death mechanisms,
-there are a number of limitations.
-Perhaps most obviously, to simplify the notation
-individuals give birth to only one offspring at a time,
-although this restriction could be easily lifted
-\citep[as in Section 3.4 of][]{etheridge/kurtz:2018}.
-Furthermore, individuals do not move during their lifetime,
-and the age of an individual does not affect their fecundity or death rates.
-Finally, there is no notion of mating
-(although limitations on reproduction due to availability of mates can be incorporated into the birth rate, $\gamma$),
-so the lineages we follow will be uniparental.
-For these reasons, the model is most obviously applicable to bacterial populations or selfing plants,
-although we do not anticipate that incorporation of these complications
-will change the general picture.
-\end{remark}
-
-We next summarize the dynamics of the rescaled model $\eta(t) = X(\theta t)/N$,
-and state some assumptions on the parameters.
-The process takes values in the space of finite measures on $\IR^d$,
-which we write as $\measures$.
-
-\plr{TODO: check the conditions below (esp on the derivatives of $F$)}
-
-\begin{definition}[Model parameterization and assumptions]
-\label{def:model_setup}
-Suppose $\gamma(x, m)$, $r(x, m)$, and $F(x, m)$
-are uniformly continuous functions
-from $\IR^d \times \IR_{\ge 0}$ to $\IR$.
-Furthermore, suppose $r$ takes values in $[0, 1]$
-and has uniformly bounded second derivatives,
-that $\gamma(x,m) \ge 0$,
-and that $m^2 \gamma(x, m)$ is uniformly bounded.
-Fix positive values $\theta$, $\epsilon_r$, $\epsilon_\gamma$, and $\epsilon_F$,
-with $\epsilon_r < \epsilon_\gamma$.
-Suppose $F(x,m)$ is bounded above
-with uniformly bounded first and second derivatives in $m$,
-that $\sup_x F(x,m)$ is finite for all $m$,
-and define
-\begin{align} \label{eqn:mu_defn}
-    \mu(x, \eta)
-    =
-    \max\left(0, 
-        r(x, \smooth{r} \eta(x))
-        \gamma(\smooth{\gamma} \eta(x))
-        - \frac{1}{\theta}
-        F(x, \smooth{F} \eta(x)) 
-    \right) .
-\end{align}
-Although the models will make sense without this requirement,
-for the purposes of convergence we will also require that
-$\theta > 2 \sup_x \sup_{y : \|y\| = 1} y^T \covq(x) y/(\epsilon_\gamma^2 - \epsilon_r^2)$.
-\end{definition}
-
-Expressions like $\gamma(x, \smooth{\gamma} \eta(x))$ will appear often in the paper.
-To make formula more readable, we overload notation to define
-$$
-    \gamma(x, \eta) := \gamma(x, \smooth{\gamma} \eta(x)) ,
-$$
-and similarly write $r(x, \eta)$ for $r(x, \smooth{r} \eta(x))$
-and $\mu(x, \eta)$ for the expression of equation \eqref{eqn:mu_defn}.
-When convenient, we may also suppress the arguments completely,
-writing simply $\gamma$, $\mu$, and $r$ for these quantities.
-
-For each value of $N$ and $\theta$,
-the process $\left(\eta^N_t \right)_{t \ge 0}$
-is the continuous-time measure-valued Markov process described above
-with birth rates, establishment probabilities, and death rates
-determined as follows.
-When the state of the process is $\eta \in \measures$,
-offspring of mass $1/N$ are produced at location $x$
-with rate $\theta \gamma(x, \eta) N \eta(dx)$
-and adults die at location $x$ with rate $\theta \mu(x, \eta) N \eta(dx)$,
-(i.e., at rates $\theta \gamma$ and $\theta \mu$ per capita respectively).
-Each offspring disperses to a location offset from the parent's location
-by an independent Gaussian with mean $\meanq(x) / \theta$
-and covariance matrix $\covq(x) / \theta$;
-an offspring at $x$ establishes instantaneously
-with probability $r(x, \eta)$, or else dies.
-
-We have just effectively defined the process, but for future use,
-we will now give a formal definition as a solution to a martingale problem.
-
-\begin{definition}[Martingale Problem Characterisation]
-    \label{defn:mgale_construction},
-For each value of $N$ and $\theta = \theta(N)$,
-we define $(\eta^N_t)_{t \geq 0}$ to be the solution to the Martingale Problem,
-with initial condition $\eta^N_0 \in \measures$,
-such that for all smooth functions $f \in C^{\infty}_{0}(\IR^d)$,
-writing $\langle f, \eta \rangle = \int_{\IR^d} f(x) \eta(dx)$
-and $q_\theta(x, dy)$ as the Gaussian kernel
-with mean $x + \meanq(x)/\theta$ and covariance $\covq(x) / \theta$,
-\begin{equation}
-    \label{eqn:eta_martingale}
-\begin{aligned}
-M^N_t(f)
-&:=  \langle f, \eta^N_t \rangle
-        -\langle f, \eta^N_0 \rangle
- \\ &\qquad {}
- -  \int_{0}^{t}\bigg\{
-        \int\left( \int \theta
-             \left(
-                f(z)r(z, \eta^N_{s})
-                - f(x)r(x, \eta^N_{s})
-            \right)
-        q_\theta(x,dz) \right)
-\\ & \qquad \qquad \qquad \qquad {}
-        \times \gamma(x, \eta^N_{s}) \eta^N_{s}(dx)
-\\ & \qquad \qquad {}
-    + \int f(x) F(x, \eta^N_{s}) \eta^N_{s}(dx)
-    \bigg\} ds
-\end{aligned}    
-\end{equation}
-is a martingale with quadratic variation
-    \begin{equation} \label{eqn:prelimit_martingale_variation}
-\begin{aligned} \relax
-[ M^N_t(f)] =& 
-\frac{\theta}{N} \int_{0}^{t}\bigg\{
-    \langle \gamma(x, \eta^N_{s})
-        \int f^2(y)r(y, \eta^N_{s}) q_\theta(x,dy) 
-    , \eta^N_{s}(dx) \rangle \\
-& \qquad \qquad {}
-    + \langle \mu(x, \eta^N_{s}) f^2(x) 
-    , \eta^N_{s}(dx)\rangle
-    \bigg\}ds. 
-\end{aligned}    
-\end{equation}
-\end{definition}
-
-Note that
-since individuals are produced at rate $N \gamma \eta$ but have mass $1/N$ each,
-these factors of $N$ cancel in~\eqref{eqn:eta_martingale}.
-Since we are taking a diffusion limit,
-we will have use for the following notation:
-
-\begin{definition}[Dispersal generator]
-    \label{def:dispersal_generator}
-    Recall that we have defined the dispersal kernel,
-    $q_\theta(x, dy)$,
-    to be the density of a multivariate Gaussian
-    with mean $\meanq(x)/\theta$ and covariance matrix $\covq(x)/\theta$
-    (although sometimes we omit the dependence of $\meanq$ and $\covq$ on $x$).
-    This implies that if we define, for $f : \IR^d \to \IR$,
-    \begin{align}
-    \DG f(x)
-        =
-        \sum_{ij} \covq(x)_{ij} \partial_{x_i} \partial_{x_j} f(x)
-        + \sum_i \meanq(x)_i \partial_{x_i} f(x)
-    \end{align}
-    then
-    \begin{align}
-        \theta \int \left(
-            f(y) - f(x)
-        \right) q_\theta(x, dy)
-    \to \DG f(x) 
-        \qquad \text{as } \theta \to \infty .
-    \end{align}
-    We will also denote the adjoint of $\DG$ by
-    \begin{align*}
-    \DG^* f(x)
-        &=
-        \sum_{ij} \partial_{x_i} \partial_{x_j} (\covq(x)_{ij} f(x))
-        - \sum_i \partial_{x_i} (f(x) \meanq(x)_i) 
-        \\
-        &=
-        \text{TODO} .
-    \end{align*}
-\end{definition}
-
-\paragraph{Remark:}
-An equivalent way to describe the model would be to say that
-when the state of the population is $\eta$,
-an individual at $x$ gives birth at rate
-$$
-    \theta \gamma(x, \smooth{\gamma} \eta(x))
-    \int r(y, \smooth{r} \eta(y)) q(x, dy) ,
-$$
-and that offspring disperse according to the kernel
-$$
-    q_\theta^\mathfrak{m}(x,\eta,  dy)
-    :=
-    \frac{
-        r(y, \smooth{r} \eta(y)) q_\theta(x, dy)
-    }{
-        \int r(z, \smooth{r} \eta(z)) q_\theta(x, dz)
-    } .
-$$
-Clearly, the random walk driven by this dispersal kernel
-is biased towards regions of higher establishment probability.
-For comparison to future results,
-it is interesting to write down the limiting generator:
-\begin{align*}
-    \lim_{\theta \to \infty}
-    \theta \int (f(y) - f(x)) q_\theta^\mathfrak{m}(x, \eta, dy)
-    &=
-    \frac{
-        \DG\left[ f(\cdot) r(\cdot, \smooth{r} \eta(\cdot)) \right](x)
-        - 
-        f(x) \DG\left[ r(\cdot, \smooth{r} \eta(\cdot)) \right](x)
-    }{
-        r(x, \smooth{r} \eta^{N}(x))
-    } .
-\end{align*}
-In the simplest case of unbiased, isotropic dispersal,
-$\meanq = 0$ and $\covq = I$, so $\DG = \Delta$,
-and this is equal to
-\begin{align*}
-    \Delta f(x) + 2 \grad f(x) \cdot \grad \log r(\cdot, \smooth{r} \eta(\cdot))(x) .
-\end{align*}
-One might guess that the spatial motion described by following a lineage of successful individuals back through time
-would be described by this generator in the limit.
-However, we will see that following a lineage back through the population
-has a different behavior yet again.
-
-% % % % % % % % % % % % % % %
-\subsection{Scaling limits of the population density process}
-
-Our main results depend on two dichotomies:
-Is the limiting process deterministic or a (generalized) superprocess?
-And, are interactions local in the limit or not?
-Below we have results for deterministic limits with local and nonlocal interactions,
-and for superprocess limits with nonlocal interactions.
-See Figure \ref{fig:super_vs_det_2d} for illustrative simulations.
-We suspect that limits are possible in the remaining (local, superprocess) case
-only in $d=1$, but do not discuss the case further.
-
-\begin{figure}
-    \begin{center}
-        \includegraphics{figures/ex1a/fkpp_123.locations}
-        \includegraphics{figures/ex1b/fkpp_123.locations}
-    \end{center}
-    \caption{
-        Snapshots of two simulations, with small $\theta$ (left) and large $\theta$ (right).
-        Simulations are run with a FKPP-like parameterization:
-        birth and establishment are constant, while death increases linearly with density,
-        at slope $1/\theta$.
-        Left: $\theta=1$. Right: $\theta=100$.
-        Other parameters were the same:
-        dispersal and interactions distance were set to 1,
-        and the equilibrium density is 10 individuals per unit area.
-        \label{fig:super_vs_det_2d}
-    }
-\end{figure}
-
-\begin{theorem} \label{thm:nonlocal_convergence}
-    Let $(\eta^N_t)_{t \geq 0}$
-    be as defined in Definition \ref{def:model_setup}
-    and assume that as $N \to \infty$, also $\theta \to \infty$
-    in such a way that $\theta/N \to \alpha$.
-    (However, interaction distances $\epsilon_r$, $\epsilon_\gamma$, and $\epsilon_F$
-    remain constant.)
-    The sequence of stochastic processes
-    $(\eta^N_t)_{t \geq 0}$
-    converges along subsequences in distribution as $N \to \infty$
-    to a measure-valued process $(\eta_t)_{t \geq 0}$
-    which satisfies that, for every $f \in C^\infty_0(\IR^d)$,
-    \begin{align} \label{eqn:limiting_mgale_problem}
-        \begin{split}
-        M_t
-            &:=
-            \langle f(x), \eta_t(dx) \rangle
-            -
-            \langle f(x), \eta_0(dx) \rangle
-            \\ & \qquad
-            -
-            \int_0^t \big\langle
-                \gamma(x, \eta_s)
-                \mathcal{B}\left(
-                    f(\cdot) r(\cdot, \eta_s)
-                \right)(x)
-                \\ &\qquad \qquad \qquad {}
-                +
-                f(x)
-                F(x, \eta_s),
-                \eta_{s}(dx)
-            \big\rangle ds,
-        \end{split}
-    \end{align}
-    is a martingale,
-    with quadratic variation
-    \begin{align} \label{eqn:limiting_mgale_variation}
-        [ M ]_t
-        =
-        \alpha
-        \int_0^t
-        \big\langle
-            \left(\gamma\left( x, \eta_{s} \right)
-            r\left(x, \eta_{s} \right) + \mu\left(x, \eta_{s} \right)\right)
-            f^2(x),
-            \eta_{s} (dx)
-        \big\rangle ds. 
-    \end{align}
-    In other words, the limit is a measure-valued process with non-local interactions.
-    Furthermore, if $\alpha = 0$ the limit is deterministic.
-\end{theorem}
-
-Recall when interpreting~\eqref{eqn:limiting_mgale_problem}
-that for instance $r(x, \eta_s) = r(x, \smooth{r} \eta_s(x))$,
-and so $\DG(fr)(x) = \DG(f(\cdot) r(\cdot, \smooth{r} \eta_s(\cdot)))(x)$.
-
-Theorem \ref{thm:nonlocal_convergence} provided convergence along subsequences;
-i.e., for any sequence of values of $N$
-there is a subsequence along which $\eta^N$ converges.
-However, if the limiting process is unique then the convergence is unqualified.
-In the deterministic case, we have convergence to a nonlocal PDE.
-
-\begin{corollary}[Superprocess limits] \label{cor:superprocess_uniqueness}
-    Under the assumptions of Theorem~\ref{thm:nonlocal_convergence},
-    if the martingale problem
-    defined by equations \eqref{eqn:limiting_mgale_problem} and \eqref{eqn:limiting_mgale_variation}
-    has a unique solution,
-    then $(\eta^N_t)_{t \ge 0}$ converges to that solution
-    as $N \to \infty$.
-    \comment{
-        Is this what we want to say here? Could be said better.
-        TODO: see what Dawson \& Li say about uniqueness
-        so we have at least some conditions under which this happens.
-    }
-\end{corollary}
-
-\comment{
-    TODO: put in what Kurtz \& Xiong have to say about uniqueness,
-along the lines of a note saying ``For some conditions under which the limit is known to be unique,
-see Kurtz \& Xiong and/or Dawson \& Li.''
-}
-
-Our results will show that in deterministic limits ``$\eta_t$ solves a PDE'',
-but since $\eta_t$ is a measure for which we don't always know there exists a density,
-we need to formalize the weak sense in which it solves the PDE.
-The notation in the following definition
-is written to suggest the case in which $\eta_t(dx)$ has a density $\varphi_t(x)$.
-
-\begin{definition}[Weak solutions]
-    \label{defn:weak_solutions}
-    We say that $(\eta_t)_{t \ge 0}$, with $\eta_t \in \measures$
-    is a \emph{weak solution} to the PDE
-    $$
-        \dot \varphi = r \DG^*(\gamma \varphi) + \varphi F
-    $$
-    if for all $f \in C_0^\infty(\IR^d)$,
-    $$
-        \frac{d}{dt} \langle f, \eta_t \rangle
-        =
-        \langle
-            \gamma \DG(rf) + f F,
-            \eta_t
-        \rangle .
-    $$
-    \comment{Write this out with $(x)$'s?}
-\end{definition}
-
-\begin{corollary}[Deterministic limits]
-    \label{cor:nonlocal_pde_limits}
-    Under the assumptions of Theorem~\ref{thm:nonlocal_convergence},
-    if the limit is deterministic (i.e., $N^{-1}\theta \to \alpha = 0$),
-    then any limit $\eta_t$ is a weak solution to the nonlocal partial differential equation
-    \begin{equation} \label{eqn:nonlocal_pde}
-        \partial_t \varphi_t(x)
-        =
-        r\left(x, \smooth{r} \varphi_t(x) \right)
-        \DG^* \left[
-            \varphi_t(\cdot)
-            \gamma\big( x, \smooth{\gamma} \varphi_t(\cdot) \big)
-        \right](x)
-        +
-        \varphi_t(x)
-        F\left(x, \smooth{F} \varphi_t(x) \right)
-        ,
-    \end{equation}
-    in the sense of Definition~\ref{defn:weak_solutions}.
-    If equation \eqref{eqn:nonlocal_pde} has a unique solution,
-    then $(\eta^N_t)_{t \ge 0}$ converges to that solution.
-\end{corollary}
-
-\comment{TODO: Tom has conditions, referring to \citet{KURTZ1999103}, (coefficient are Lipschitz?) under which
-    the solution to \eqref{eqn:nonlocal_pdf} is unique and has a density (Thm 2.1 in DDMOT);
-    insert those here (as a Corollary or Proposition)}
-
-Informally, equation \eqref{eqn:nonlocal_pde} is the PDE of Definition~\ref{defn:weak_solutions},
-where $\DG$ is an elliptic second order differential operator,
-and the coefficients $r$, $\gamma$, and $F$
-at $x$ depend nonlocally on $\varphi$
-(i.e., through a smoothed version of $\varphi$).
-To see why it is $\DG^*$ and not $\DG$ that appears in this equation,
-consider the case where dispersal has a mean drift to the right,
-so that the drift term in $\DG$ is $d/dx$.
-Then, the population density at a location with positive slope
-will tend to \emph{decrease}, i.e., proportional to $-d/dx$,
-because the density at a location is determined by the offspring that disperse \emph{to}
-that location, not away from it.
-Furthermore, if dispersal tends to move offspring away from a region
-(i.e., if divergence $\grad \cdot \meanq > 0$)
-this will tend to decrease the local density.
-
-Although the coefficients at $x$ in \eqref{eqn:nonlocal_pde} are nonlocal,
-they depend only on the region nearby to $x$,
-and so we would expect solutions of the nonlocal PDE to be close to the corresponding local PDE
-as the interaction distances $\epsilon_r$, $\epsilon_\gamma$ and $\epsilon_F$
-go to zero:
-for instance, if $\eta_t$ has density $\varphi_t$
-then $\gamma(x, \smooth{\gamma} \eta_t(x)) \to \gamma(x, \varphi_t(x))$ as $\epsilon_\gamma \to 0$
-(recalling that $\smooth{\gamma}{}$ denotes convolution with the heat kernel at time $\epsilon_\gamma^2$).
-The following propositions give two concrete situations in which that is true.
-
-\begin{proposition}
-    \label{prop:nonlocal_to_local}
-    Suppose that $\eta^\epsilon_t$ is a weak solution to equation \eqref{eqn:nonlocal_pde}
-    with $r(x, m) = 1$ for all $x$ and $m$
-    and some $\epsilon_r + 1/\theta < \epsilon_\gamma = \epsilon_F = \epsilon$
-    \comment{and assumptions on $\gamma$? and $F$?}.
-    Then $\eta^\epsilon_t(dx)$ converges \comment{in what sense?} as $\epsilon \to 0$
-    to $\varphi_t(x) dx$, which is a (strong) solution to
-    \begin{align} \label{eqn:PDE}
-        \partial_t \varphi(t, x)
-        =
-        \DG^* \left( \gamma(\cdot, \varphi(t, \cdot)) \varphi(t, \cdot)  \right)(x)
-        + F(x, \varphi(t, x)) \varphi(t, x) .
-    \end{align}
-\end{proposition}
-
-Theorem \ref{thm:nonlocal_convergence} combined with Proposition \ref{prop:nonlocal_to_local}
-imply that we can take the $N \to \infty$ limit
-followed by $\epsilon \to 0$
-to obtain solutions to the PDE \eqref{eqn:PDE}.
-However, it is of substantial interest to know whether
-we can take those two limits simultaneously.
-The general case seems difficult,
-but we can prove such ``diagonal'' convergence in the following situation.
-
-\begin{theorem}[Convergence to a PDE]
-    \label{thm:local_convergence}
-    Let $(\eta^N_t)_{t \geq 0}$
-    be as defined in Definition \ref{def:model_setup}
-    and assume that as $N \to \infty$, $\theta \to \infty$
-    and $\epsilon_r + 1/\theta < \epsilon_\gamma = \epsilon_F = \epsilon \to 0$
-    in such a way that $\theta/N \to 0$
-    and
-    \comment{TODO: some conditions on $\epsilon$ and $r$ and $\gamma$ and $F$}.
-    Then the sequence of stochastic processes $(\eta^N_t)_{t \ge 0}$
-    converges \comment{in some sense}
-    to a measure-valued process with a density $\varphi(t, x)$
-    that solves
-    \begin{align}
-        \partial_t \varphi(t, x)
-        &=
-        \text{whatever the final form is here} .
-    \end{align}
-\end{theorem}
-
-% % % % % % % % % % % %
-\subsection{Ancestral lineages in the scaling limit}
-
-Now that we have established what we can say about how population density changes with time,
-we turn to results on ancestral lineages,
-i.e., how genealogical ancestry can be traced back across the landscape.
-Informally,
-a \emph{lineage} $(L_t)_{t \ge 0}$
-begun at spatial location $L_0 = x$
-can be obtained by picking a focal individual uniformly at $x$,
-and then for each amount of time $t$ in the past,
-setting $L_t$ to the spatial location of the individual from whom
-the focal individual inherits at that time in the past.
-Since in our model individuals have only one parent, this is unambiguous.
-Although we did not explicitly retain such information,
-it is clear that for finite $N$
-one could construct the distribution of a lineage $(L_t)_{t=0}^T$
-given the history of the population $(\eta^N_t)_{t = 0}^T$,
-for each starting location to which $\eta^N_T$ assigns positive mass.
-It is less clear, however, how to formally retain such information in the limit.
-The \emph{lookdown construction} in Section~\ref{sec:lookdown}
-provides just such a construction.
-Roughly speaking,
-this works by assigning to each particle a unique ``level''
-that functions as a label and thus allows reconstruction of lineages,
-but also (in some sense) orders individuals by eventual reproductive output,
-allowing a formal limit.
-See~\citet{etheridge/kurtz:2018} for an introduction to these ideas.
-
-A lineage is, in general, a well-defined stochastic process,
-but there are two important questions
-that affect its tractability.
-First, when is it a Markov process given the population process?
-(In other words, given $(\eta_t)_{t=0}^T$ that records numbers of individuals
-but not their ancestry.)
-\comment{NOT RIGHT:}
-We expect the answer here to be that a lineage is Markov
-only in the $N \to \infty$ limit
-(see \citet{barton/depaulis/etheridge:2002} for discussion).
-Second, does the process have a tractable description?
-If the population process has a density,
-then it turns out that a lineage is a diffusion driven by the density.
-The remaining case is the superprocess limit ($\theta/N \to \alpha > 0$);
-in this case, we expect that a lineage could still be described as a generalized diffusion,
-but moving within a stochastic landscape that is singular in $d \ge 2$.
-We focus on the more tractable situation where the population process is deterministic.
-However, the results here apply to either the local or nonlocal case
-(i.e., where the density solves a local or nonlocal PDE).
-
-\begin{definition}[Generator of a lineage] \label{def:lineage_generator}
-    Let $(\varphi_t(x))_{0 \le t \le T}$
-    denote the density of a population that solves \eqref{eqn:nonlocal_pde},
-    and let $y$ be a point with $\varphi_T(y) > 0$.
-    We define $(L_s)_{s=0}^T$,
-    the ancestral lineage in this population of an individual sampled at $y$ at time $T$,
-    to be the position of the unique ancestor of $y$ alive at time $T - s$.
-    We define
-    $(Q_s)_{s \geq 0}$
-    to be the time inhomogeneous semi-group satisfying
-    \begin{align*}
-        Q_s f(y) := \IE_y[ f(L_s) ] .
-    \end{align*}
-\end{definition}
-
-Our main result identifies a lineage as a diffusion
-by characterizing its generator.
-
-\begin{theorem} \label{thm:lineages}
-    For $\varphi: \IR^d \to \IR$, define
-    \begin{align}
-        \label{eqn:lineage_generator}
-        \Lgen_\varphi f
-        &=
-        \frac{r}{\varphi}
-        \left[
-            \DG^*(\gamma \varphi f) 
-            - f \DG^* (\gamma \varphi)
-        \right] \\
-        &= \label{eqn:lineage_generator2}
-        r\gamma
-        \left[
-            \sum_{ij} \covq_{ij} \partial_{ij} f
-            + \sum_j \vec{m}(s)_j \partial_j f
-        \right] ,
-    \end{align}
-    where $\vec{m}$ is the vector
-    $$
-    \vec{m}(s)_j
-    =
-    2 \sum_i C_{ij} \partial_i \log(\gamma \varphi)
-    + 2 \sum_i \partial_i C_{ij}
-    - \meanq_j .
-    $$
-    Then $\Lgen_{\varphi_{T-s}}$ is the generator of the semigroup $Q_s$
-    of Definition~\ref{def:lineage_generator}.
-\end{theorem}
-
-As usual,
-to make the generator readable, we've written it in concise notation,
-omitting the dependencies on location and population density,
-which itself changes with time.
-When interpreting this,
-remember that everything depends on location and density at that location and time --
-for instance, ``$r$'' is actually $r(x, \varphi(x))$ (in the local case),
-or $r(x, \smooth{r} \eta(x))$ (in the nonlocal case).
-
-\begin{corollary} \label{cor:lineages_simple}
-    In addition to the assumptions of Theorem~\ref{thm:lineages},
-    if the dispersal process is isotropic
-    (i.e., $\covq = \sigma^2 I$ and $\meanq$ is constant),
-    then
-    \begin{equation}
-        \Lgen_\varphi f
-        =
-        r \gamma
-        \left(
-            \sigma^2 \Delta f
-            +
-            \left(
-                2 \sigma^2 \grad \log(\gamma \varphi)
-                - \meanq
-            \right)
-            \cdot \grad f
-        \right) .
-    \end{equation}
-\end{corollary}
-
-In other words, 
-the lineage behaves as a diffusion driven by Brownian motion run at speed 
-\comment{TODO: make this right:}
-If $V_s(x) = \log(\varphi_s(x) \gamma(x, \varphi_s)) - \meanq \cdot x / 2 \sigma^2$,
-then the diffusion has drift $\grad V_s$.
-If $\varphi$ does not change with time, 
-then the stationary distribution is proportional to $\exp(V(x))$.
-a lineage behaves as a diffusion
-that is driven by a Brownian motion 
-run at speed $\sigma^2$ multiplied by the local per-capita production of offspring ($r \gamma$)
-in a potential equal to the local birth output tilted by migration bias
-($\varphi_s \gamma \exp(-\meanq \cdot x / 2 \sigma^2)$).
-
-\begin{corollary} \label{cor:wavefront}
-    In addition to the assumptions of Corollary~\ref{cor:lineages_simple},
-    suppose that the population process is described by a traveling wave with speed $\wavespeed$,
-    i.e., the population has density
-    $\varphi(t, x) = w(x - t \wavespeed)$
-    where $w$ solves
-    \begin{align*}
-        r \Delta (\gamma w) + w F + \wavespeed \cdot \grad w = 0 .
-    \end{align*}
-    Then the semigroup 
-    of the motion of a linages in this population 
-    $Q_s$ is time-homogeneous with generator
-    \begin{align}
-        \Lgen f
-        &=
-        \sigma^2 r \gamma
-        \left(
-            \Delta f
-            +
-            2 \grad \log (\gamma w)
-            \cdot \grad f
-        \right)
-        + (\wavespeed - \meanq) \cdot \grad f .
-    \end{align}
-\end{corollary}
-
-%%%%%%%%%%%%%%%%%%%%%%
-\section{Examples and applications}
-\label{sec:applications}
-
-Next,
-we cover some illustrative examples
-and interesting applications.
-
-% % % % % % % % % % % %
-\subsection{Beyond reaction-diffusion equations: a population described by the porous medium equation}
-\comment{look up what the technical term is for the nonlinear diffusive bit?
-    and, does "reaction-diffusion" mean parabolic?}
-
-Consider the porous medium equation (PME) with logistic growth,
-\begin{equation}
-    \label{eqn:pme}
-    \partial_t v = \partial_x^2 (v^2) + v (1 - v) ,
-\end{equation}
-an example of a reaction-diffusion equation with a nonlinear diffusion term.
-Such equations are widely used in a number of contexts in biology in which
-it is clear that motility within a population varies with population density.
-For example, density dependent dispersal is a common feature in spatial
-models in ecology, eukaryotic cell biology, and avascular tumour growth;
-see~\cite{sherratt:2010} and references therein for further discussion. 
-In particular, it has been suggested as a model for
-the expansion of a certain type of bacteria % of the type {\em Paenbacillus dendritiformis}
-on a thin layer of agar in a petri dish 
-\citep{cohen/golding/kozlovsky/benjacob/ron:1999}. 
-We shall pay particular attention to the case in which the equation can be 
-thought of as modelling the density of an expanding population.
-
-Comparing \eqref{eqn:pme} to \eqref{eqn:pde},
-we see that to set up a limit in which the population density $\varphi$ follows the PME,
-we need $r=1$,
-$\gamma = \varphi$, and $F = 1 - \varphi$.
-Consulting equation~\eqref{eqn:mu_defn},
-this implies that $\mu = (1 + 1/\theta) \varphi - 1/\theta$.
-In other words,
-establishment is certain
-and birth rates increase linearly with population density,
-but to compensate, death rates increase slightly faster (also linearly),
-as shown in Figure~\ref{fig:pme_waves}.
-Alert readers will notice that
-for finite $\theta$ death rates may be negative,
-and furthermore rates are not bounded;
-in practice we choose a suitably small value for $\beta$ and define
-\begin{align*}
-    \gamma(x, m) &= (1 - \exp(- \beta m)) / \beta \\
-    F(x, m) &= \exp(- \beta m) / \beta ,
-\end{align*}
-and set $\mu(x, m) = \max(0, \gamma - F / \theta)$.
-Birth and death rates are equal at density $m = 1$,
-corresponding to an unscaled density of $N$ individuals per unit area.
-
-\begin{figure}
-    \begin{center}
-        \includegraphics[width=0.45\textwidth]{figures/ex2a/pme_123.steps}
-        \includegraphics[width=0.45\textwidth]{figures/ex2b/pme_123.steps}
-    \end{center}
-    \caption{
-        Two panels, showing simulated 1D populations under the PME, comparing the simulated
-        profile to the analytical solution;
-        $\theta/N$ not small on left; small on right.
-        (Note: noisier wave should move slower, we'll see this.)
-        \label{fig:pme_waves}
-    }
-\end{figure}
-
-This equation has an explicit travelling wave solution
-\begin{align} \label{eqn:pme_wave}
-    w^P(t, x)
-    :=
-    \left( 1 - e^{ \frac{1}{2} (x - x_0 - t) } \right)_+ .
-\end{align}
-Notice that the wave profile has a sharp boundary at $x = x_0 + t$.
-There are also travelling wave solutions with $c>1$ \citep{gilding/kersner:2005},
-which lack this property.
-However, for initial conditions that decay sufficiently rapidly at infinity,
-such as one might use in modelling a population invading new territory,
-the solution converges to \eqref{eqn:pme_wave} \citep{kamin/rosenau:2004}.
-
-Indeed, simulations of this process
-shown in Figure~\ref{fig:pme_waves}
-display traveling wave solutions
-similar to numerical solutions of the PME,
-with increasingly good agreement for larger $\theta$ and $N$.
-As expected, noise slows down the wave.
-
-% % % % % % % % % % % %
-\subsection{Different types of traveling waves}
-
-\begin{figure}
-    \begin{center}
-        \includegraphics{figures/ex3_fkpp/fkpp_123.lineages}
-        \includegraphics{figures/ex3_fkpp/fkpp_123.lineagehist}
-        \includegraphics{figures/ex3_pme/pme_123.lineages}
-        \includegraphics{figures/ex3_pme/pme_123.lineagehist}
-        \includegraphics{figures/ex3_allen-cahn/allen-cahn_123.lineages}
-        \includegraphics{figures/ex3_allen-cahn/allen-cahn_123.lineagehist}
-    \end{center}
-    \caption{
-        Six panels: one pair for FKPP, one for PME, and one for Allen-Cahn.
-        Each pair shows (top) lineage traced back in wavefront,
-        and (bottom) stationary distribution of lineage location,
-        compared to analytical solution for PME.
-        \label{fig:pme_vs_fkpp}
-    }
-\end{figure}
-
-It is interesting to investigate the motion of an ancestral lineage
-in special cases in which we have an explicit expression for the travelling
-wave profile $w$. 
-We consider three relatively well-studied examples:
-the Porous Media equation (above),
-the Fisher-KPP equation,
-and the Allen-Cahn equation.
-We will work here in one dimension,
-and take $\sigma^2 = 1$ and $\meanq = 0$.
-
-%%%%%%%%%%
-\paragraph{Porous Media:}
-Setting $x_0=0$ (for definiteness) and substituting
-the form of $w^P$ from equation \eqref{eqn:pme_wave}
-into Corollary~\ref{cor:wavefront},
-with $c=1$,
-$\gamma(x, m) = m$,
-$r(x,w) = 1$,
-and $F(x, m) = (1 - m)$,
-the lineage's generator is, for $x < 0$,
-with $f_x$ denoting the spatial derivative of $f$,
-\begin{align*}
-    \Lgen f
-    &=
-        w(x)
-        \left(
-         f_{xx}(x)
-         +
-         2 \frac{(w(x)^2)_x}{w(x)^2} f_x(x)
-        \right)
-        + f_x(x) \\
-    &=
-        \left(1 - e^{\frac{1}{2} x} \right)
-        f_{xx}(x)
-        -
-        2 e^{\frac{1}{2} x} f_x(x)
-        +
-        f_x(x) .
-\end{align*}
-The speed measure corresponding to this diffusion is,
-again for $x < 0$,
-\begin{align*}
-    m(d\xi)
-    &\propto
-        \frac{ 1 }{ 2 (1 - e^{\xi/2}) }
-        \exp\left(
-            \int_\eta^\xi \left\{
-                1 - \frac{e^{x/2}}{1 - e^{x/2}}
-            \right\} dx
-        \right) \\
-    &\propto
-        e^\xi\left(1-e^{\xi/2}\right),
-        \quad
-        \text{for } \xi < 0 ,
-\end{align*}
-which is integrable and so when suitably normalised gives the unique stationary distribution.
-Notice that at stationarity
-the lineage will typically be significantly behind the front.
-
-%%%%%%%%%%
-\paragraph{Fisher--KPP:}
-A great deal more attention has been paid to the classical Fisher-KPP equation,
-\begin{align} \label{eqn:fkpp}
-    v_t = v_{xx} + v (1-v) .
-\end{align}
-Even though we do not have an explicit formula for the wave shape in this case,
-our methods provide information about ancestral lineages.
-The equation has non-negative travelling wave solutions of speed $c$ for all $c \geq 2$, 
-but started from any compact perturbation of a Heaviside function, the 
-solution will converge to the profile $w^F$ with the minimal wavespeed, $c=2$
-\citep{kolmogorov/petrovsky/piscounov:1937,bramson:1983}.
-No matter the initial condition,
-for any $t>0$ the support of the 
-solution will be the whole real line. 
-In this case, we must have $r = \gamma = 1$,
-and $F(x, m) = 1 - m$ so $\mu(x, m) = 1 + (m-1)/\theta$.
-This implies that
-the generator of the motion of an ancestral lineage is
-\begin{equation} \label{eqn:fkpp_generator}
-    \Lgen \phi
-    =
-    \phi_{xx} + 2 \frac{w_x}{w} \phi_x + 2 \phi_x .
-\end{equation}
-Near the tip of the wave (for $x$ large), $w^F(x) \sim e^{-x}$,
-so \eqref{eqn:fkpp_generator} implies that
-the motion of a lineage is close to unbiased Brownian motion.
-On the other hand, for $x < 0$ a lineage behaves approximately as
-Brownian motion with drift at rate two to the right.
-This implies that
-ancestral lineages are pushed into the tip of the wave,
-and there is no stationary distribution,
-so that long-term dynamics of genetic inheritance
-depend on the part of the wave not well-approximated by a smooth profile.
-These results agree with those of \comment{TODO: citations}.
-
-%%%%%%%%%%
-\paragraph{Allen-Cahn:}
-Finally, we take the Allen-Cahn equation
-\begin{align} \label{eqn:allen_cahn}
-    v_t = v_{xx} + v(1-v)(2v-1+s),
-\end{align}
-for a given $s \in (0,2)$,
-which is used to model populations evolving under selection \cite{Sarah}.
-This equation also has an explicit travelling wave solution with speed $s$
-and shape
-\[ w^A(x) = (1+e^{x})^{-1}. \]
-The generator for ancestral lineages is, just as in the Fisher-KPP case,
-\begin{align*}
-    \hat{\mathcal{L}}\phi
-    &=
-    \phi_{xx}
-    + 
-    2 \frac{w_x}{w} \phi_x
-    +
-    s \nabla \phi \\
-    \qquad &=
-    \phi_{xx}
-    -
-    2 \frac{e^x}{1+e^x} \phi_x 
-    + 
-    s \nabla \phi,
-\end{align*}
-so lineages in the tip are pushed leftwards into the bulk of the wave at a rate $-2(e^{-x}+1)^{-1}$,
-that gets weaker further to the left.
-This diffusion has speed measure
-$$
-    m(d\xi) \propto e^{sx}(1+e^x)^{-2},
-$$
-which is concentrated around $\log(s/(2-s))$ and decays like $e^{x(s-2)}$ away from this point.
-These results agree with those of \cite{etheridge/penington:2020}.
-
-% % % % % % % % % % % % % % % %
-\subsection{Clumping from nonlocal interactions}
-
-\comment{
-    Description of the process;
-    discussion of when it happens;
-    (TODO: how's it affected by $\theta$?)
-}
-
-\begin{figure}
-    \begin{center}
-        FIGURE
-    \end{center}
-    \caption{
-        Two panels: left is 2D picture of clumped population;
-        right is a bumpy expanding wavefront.
-        \label{fig:clumping}
-    }
-\end{figure}
-
-% % % % % % % % % % % % % % % %
-\subsection{Lineage motion is not uniquely determined by population density}
-
-It is natural for applications to wonder about identifiability:
-when can the observed quantities like population density
-or certain summaries of lineage movement uniquely determine
-the underlying demographic parameters?
-Consider a deterministic,
-continuous population generated by parameters $\gamma$, $\mu$, and $r$
-with $\meanq = 0$ and $\covq = I$.
-Suppose it has a stationary profile $w(x)$, that must satisfy
-$$
-   r \Delta(\gamma w) + (r \gamma - \mu) w = 0 .
-$$
-It is easy to see that $w$ does not uniquely specify $\gamma$, $\mu$, and $r$:
-let $\beta(x)$ be a smooth, nonnegative function on $\IR^d$,
-and let $r'(x, m) = \beta(x) r(x, m)$ and $\mu'(x, m) = \beta(x) \mu(x, m)$
-(and, let $\gamma' = \gamma$).
-Then the population with parameters $\gamma'$, $\mu'$, and $r'$
-has the same stationary profile(s) as the original population.
-
-Can these two situations be distinguished from summaries of lineage movement?
-The first has lineage generator
-\[
-    f \mapsto \Lgen f = r \gamma \left( \Delta f + 2 \grad \log(\gamma w) \cdot \grad f \right),
-\]
-while the second has lineage generator $f \mapsto \beta(x) \Lgen f(x)$.
-In other words,
-although the stationary profile of the population is unchanged when we scale
-local establishment and death by $\beta$,
-the motion of lineages is sped up locally by $\beta$.
-This corresponds to making areas with $\beta > 1$ more ``sink-like'' and $\beta < 1$ ``source-like'':
-if $\beta(x) > 1$, then at $x$ both the death rate and establishment of new individuals are higher.
-As a result, lineages in the second model spend more time in areas with $\beta < 1$,
-i.e., those areas have higher long-term fitness,
-something that is in principle discernible from genetic data.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Heuristics}
-    \label{sec:heuristics}
-
-In this section we give heuristic arguments for our main results,
-to build intuition before the formal proofs.
-
-% % % % % % % % % % % % % % % % % %
-\subsection{The population density}
-    \label{sec:population_heuristics}
-
-We write $\Pgen^N$
-for the generator of the scaled population process $\eta^N$
-of Definition~\ref{defn:mgale_construction}
-acting on test functions of the form $G( \langle f, \eta \rangle )$,
-where $f \geq 0$ is smooth and compactly supported on $\IR^d$ and 
-$G \in C^\infty ([0,\infty))$.
-Recall that $\theta \to \infty$ along with $N$,
-although we don't remind the reader with extra superscripts.
-
-A Taylor expansion allows us to write
-\begin{multline*}
-    \Pgen^N
-    G(\langle f,\eta \rangle)
-    =
-    G'(\langle f, \eta \rangle)
-    \lim_{\delta t\downarrow 0} \frac{1}{\delta t}
-    \IE\left[
-        \left. \langle f, \eta_{\delta t} \rangle
-        -
-        \langle f, \eta \rangle
-        \right| \eta_0=\eta
-    \right]
-    \\
-    \qquad {}
-    + \frac{1}{2}
-        G''(\langle f,\eta\rangle)
-    \lim_{\delta t\downarrow 0}\frac{1}{\delta t}
-    \IE\left[
-        \left.\big(\langle f,\eta_{\delta t}\rangle
-        -
-        \langle f, \eta\rangle\big)^2 \right|\eta_0=\eta
-    \right]
-    +
-    \epsilon_N(f, G, \eta),
-\end{multline*}
-where the terms that make up 
-$\epsilon_N(f, G, \eta)$
-will be negligible in our scaling limit.
-
-% % % % % % % 
-\subsubsection*{Mean measure}
-
-Recall that in our parameterization only death rates $\mu$
-and the dispersal kernel $q$ depend on $\theta$.
-For a suitable (smooth, compactly supported) test function $f$, we find
-\begin{equation} \label{mean measure}
-    \begin{split}
-    \Pgen^N \langle f, \eta \rangle
-    &=
-    \lim_{\delta t\downarrow 0} \frac{1}{\delta t}
-    \IE\left[ \left.
-        \langle f, \eta_{\delta t} \rangle
-        -
-        \langle f, \eta\rangle
-        \right| \eta_0 = \eta
-    \right]
-    \\
-    &=
-    \theta \int
-        \int f(z) r(z,\eta) q_\theta(x,dz)
-    \gamma(x, \eta) \eta(dx)
-    -
-    \theta \int f(x)\mu_\theta(x, \eta)
-    \eta(dx).
-    \end{split}
-\end{equation}
-The first term is the increment in $\langle f,\eta\rangle$
-resulting from a birth event (recalling that
-we don't kill the parent) integrated against the rate of such events,
-and the second reflects death events.
-In both terms,
-the rate of events has a factor of $N$ (because events happen at a rate 
-proportional to the number of individuals,
-whereas $\eta$ has mass $1/N$ for each individual)
-which is offset by the fact that  
-the birth or loss of a single 
-individual at the point $y$, say, changes $\langle f,\eta\rangle$
-by $f(y)/N$.
-
-We use the fact that $\int q_\theta(x,dz)=1$ to rewrite~(\ref{mean measure})
-as 
-\begin{equation}
-\label{eqn:rewritten mean measure}
-\begin{split}
-    \int\left(
-        \int \theta \left( f(z) r(z,\eta)- f(x) r(x,\eta) \right) q_\theta(x,dz)
-    \right)
-    \gamma(x,\eta)
-    \eta(dx)
-    \\
-    + \int \int f(x) \theta \Big(
-        r(x,\eta) \gamma(x,\eta)
-        - \mu_\theta(x,\eta)
-    \Big) \eta(dx).
-\end{split}
-\end{equation}
-We have defined $\mu_\theta$ so that the second term is simple:
-\begin{align*}
-    \theta \Big( r(x,\eta) \gamma(x,\eta) - \mu_\theta(x,\eta) \Big)
-    = F(x, \eta) .
-\end{align*}
-Furthermore, recall from Definition~\ref{def:dispersal_generator} that
-\begin{align} \label{eqn:near_critical}
-    \int \theta \Big(
-        r(z,\eta) f(z)
-        -
-        r(x,\eta) f(x)
-    \Big) q_\theta(x,dz) 
-    \qquad \stackrel{\theta\to\infty}{\longrightarrow} \qquad  
-    \DG \big(r(\cdot,\Xi)f(\cdot)\big)(x) .
-\end{align}
-To make this more familiar,
-remember that if dispersal is simply standard multivariate Gaussian
-with mean zero and covariance $\sigma^2 I / \theta$,
-then $\DG = \sigma^2 \Delta$, where $\Delta$ denotes the Laplacian.
-
-In summary, equation~\eqref{eqn:rewritten mean measure} converges to
-\begin{equation} \label{limit of mean measure equation}
-\int \gamma(x,\eta)
-\DG \big(f(\cdot)r(\cdot,\eta)\big)(x)
-\eta(dx)
-+
-\int f(x)
-F(x,\eta)
-\eta(dx) .
-\end{equation}
-This gives the martingale of Theorem~\ref{thm:nonlocal_convergence}.
-More generally, we expect everything to work
-if the remaining parameters ($r$, $\gamma$, and $F$)
-also depended on $N$, but converged as $N \to \infty$.
-
-% % % % % % % 
-\subsubsection*{Quadratic variation}
-
-% Note: this bit in firstversionplus.tex has things written out in detail for
-% the Poisson offspring number case.
-
-We now look at the second order term.
-An individual at location $x$ gives birth 
-to a surviving offspring at $y$ at rate
-$$
-\gamma(x,\eta) r(y,\eta) q_{\theta}(x, dy) ,
-$$
-and since this increments $\langle f, \eta \rangle$ by $f(y) / N$,
-the contribution to the quadratic variation from birth events,
-which occur at rate $\theta$ per individual 
-(so, rate $N\theta |\eta|$ overall), is
-$$
-\langle
-    N \theta \gamma(x,\eta)
-    \int \frac{1}{N^2} f^2(y) r(y,\eta)
-    q_\theta(x,dy) 
-    , \eta(dx)
-\rangle .
-$$
-Similarly, the increment in $\langle f, \eta\rangle$ resulting from 
-the death of an individual at $x$ is $f(x)/N$, and so combining with the 
-above, the second order term in the generator takes the form
-\begin{align*}
-& G''(\langle f,\eta\rangle)
-\frac{1}{2} N \theta
-\left\{
-    \langle
-        \gamma(x,\eta)
-        \int \frac{1}{N^2}f^2(y)r(y,\eta)q_\theta(x,dy) 
-    , \eta(dx)\rangle
-    +
-    \langle
-        \mu(x,\eta)\frac{1}{N^2}f^2(x) 
-    ,\eta(dx)\rangle
-\right\} \\
-&\qquad
-= \frac{1}{2} G''(\langle f, \eta \rangle)
-    \frac{\theta}{N}
-    \langle
-        \gamma(x, \eta) \int f^2(y) r(y, \eta) q_\theta(x, dy) + f^2(x) \mu(x, \eta),
-        \eta(dx)
-    \rangle .
-\end{align*}
-Since $\int f^2(y) r(y, \eta) q_\theta(x, dy) \to f^2(x) r(x, \eta)$
-and $\gamma r + \mu = 2 \gamma r - F / \theta \to 2 \gamma r$
-as $\theta \to \infty$,
-this converges to
-\begin{align*}
-\frac{\alpha}{2} G''(\langle f, \eta \rangle)
-    \langle
-        2 \gamma(x, \eta) r(x, \eta),
-        \eta(dx)
-    \rangle .
-\end{align*}
-
-Finally, the term $\epsilon_{\theta,N}(f, G, \eta)$ will be 
-$\bigO(\theta/N^2)$.
-
-By choosing $\theta/N \rightarrow 0$, the second order term in the generator 
-will vanish and we expect a deterministic limit,
-for which $d/dt \langle f, \eta_t \rangle$ is equal to~\eqref{limit of mean measure equation}.
-In other words, the limit is a weak solution to the deterministic equation
-\begin{equation}
-\label{deterministic limit}
-\frac{d\varrho(x)}{dt}
-=
-    r(x,\varrho)
-    \DG\big(
-        \gamma(\cdot,\varrho) \varrho(\cdot)
-    \big)(x)
-    + F(x, \varrho) \varrho(x) 
-\end{equation}
-in the sense of Definition~\ref{defn:weak_solutions},
-where $\varrho_t$ is the density of $\eta_t$, if it has a density.
-
-\comment{
-    Point out that this is still with $\epsilon > 0$,
-    and put in heuristics for why $N \epsilon^d / \theta \to \infty$
-    and $\theta \epsilon^2 \to \infty$
-    are plausible conditions for the diagonal convergence.
-    (Because we want (a) a macroscopic number of neighbors relative to $\theta$,
-    and (b) to make the initial condition smooth enough
-    since we start with an $\epsilon^2$-smoothed initial condition,
-    and we want this to look like a bunch of $1/\theta$-jumps have already happened.
-}
-
-On the other hand, if $N = \alpha \theta$ for some $\alpha > 0$,
-the second order term remains, and we expect a ``generalised superprocess'' limit.
-The limiting quadratic variation
-is exactly as seen in Theorem~\ref{thm:nonlocal_convergence}.
-
-% % % % % % % % % % % % % % % % % %
-\subsection{Motion of ancestral lineages}
-
-Although our proof of Theorem~\ref{thm:lineages}
-uses the explicit representation in terms of the lookdown process,
-informal calculations agree with the main result.
-Suppose that we have tracked a lineage back to an individual at location $y$ at time $t$.
-Looking further back through time, the lineage will move at the time that individual was born,
-and will jump to that individual's parents' locations.
-Now, the rate at which new individuals are born to parents at $x$ and establish at $y$
-is
-$$
-    \gamma(x, \eta_t) q(x, dy) r(y, \eta_t) .
-$$
-\comment{TODO: explain this more.}
-Happily, we are interested in the case when $\eta$ has a density,
-say $\eta_t(dx) = \varphi_t(x) dx$,
-so interpreting these rates is not too difficult.
-This implies that the probability a randomly chosen individual near $y$
-is a new offspring from a parent at $x$ in $[t, t+dt)$ is, informally,
-\begin{equation} \label{eqn:informal_rates}
-\frac{
-    \gamma(x, \eta_t) r(y, \eta_t) \varphi_t(x)
-}{
-    \varphi_t(y)
-} \frac{ q_\theta(x, dy) }{ dy } dx dt .
-\end{equation}
-Leaving aside questions of whether a lineage can be treated as a randomly chosen individual,
-we might then proceed by defining a continuous-time jump process
-whose transition rates are given by \eqref{eqn:informal_rates} given $(\varphi_t)_{t=0}^T$.
-Let $(L^N_s)_{s=0}^T$ be the location of a lineage that moves according to these jump rates,
-back through time (i.e., with the substitution that $s = T-t$).
-Then, for the moment writing $q_\theta(x, y)$ for the density of $q_\theta$,
-\begin{align} \label{eqn:lineage_generator_Edt}
-    \begin{split}
-    &\IE[f(L^N_{s+ds}) - f(y) \;|\; L_s = y]
-    \\&\qquad 
-    =
-    ds \int \left(f(x) - f(y)\right)
-    \frac{
-        \varphi_{T-s}(x) \gamma(x, \eta_{T-s}) r(y, \eta_{T-s})
-    }{
-        \varphi_{T-s}(y)
-    }
-    q_\theta(x, y) dx .
-    \end{split}
-\end{align}
-Referring back to Definition~\ref{def:dispersal_generator},
-a quick calculation shows that as $N \to \infty$,
-\begin{align*}
-    \theta \int (f(x) - f(y)) q_\theta(x, y) dx
-    &\to
-    \DG^* f(x)  - f(x) \DG^* 1 .
-\end{align*}
-Consequently,
-\begin{align*}
-    &
-    \theta \int (f(x) - f(y)) g(x) q_\theta(x, y) dx \\
-    &\qquad =
-    \theta \int \left\{
-        (f(x) g(x) - f(y) g(y)) - f(y) (g(x) - g(y))
-    \right\} q_\theta(x, y) dx \\
-    &\qquad \to
-        \DG^*(fg)(y) - f(y) \DG^* g(y) . 
-\end{align*}
-Applying this to~\eqref{eqn:lineage_generator_Edt} with $g = \varphi_{T-s} \gamma$,
-this suggests that the generator of the limiting process is
-\begin{align} \label{eqn:heuristic_lineage_generator}
-    \Lgen_s f
-    &=
-    \frac{r}{\varphi_{T-s}}
-    \left\{
-        \DG^*(\gamma \varphi_{T-s} f) - f \DG^*(\gamma \varphi_{T-s})
-    \right\} .
-\end{align}
-This agrees with Theorem~\ref{thm:lineages}.
-
-%%%%%%%%%%%%%%%%%%%
-\section{The lookdown process}
-    \label{sec:lookdown}
-
-Now we will present a lookdown construction for the general process
-(i.e., of Definition \ref{defn:mgale_construction}),
-in the spirit of~\cite{kurtz/rodrigues:2011}. 
-The general set-up is as follows.
-Each individual will be labeled with a ``level'',
-which will be a number in $[0, N]$.
-We will still encode the process embellished by these levels
-as a point measure:
-if the $i^\mathrm{th}$ individual's spatial location is $x_i$
-and level is $u_i$, then we will write:
-$$
-    \lp = \sum_i \delta_{x_i, u_i} ,
-$$
-which is a measure on $\IR^d \times [0, N]$.
-Note that each individual contributes mass 1 to the measure,
-not $1/N$ as above.
-In some sense, these levels do not affect the process:
-the pushforward of this measure-valued ``spatial-level process'',
-divided by $N$,
-will agree with the purely spatial process defined above.
-Furthermore, at any time, the levels of the individuals present at any spatial location
-will be exchangeable and conditionally uniform on $[0, N]$:
-in particular, choosing the $k$ individuals with the lowest level in some region of space
-at some time is equivalent to taking a uniform random draw of size $k$ from the individuals in that region
-for the purely spatial process.
-However, an individual's level in some sense encodes their future reproductive output:
-individuals with lower levels tend to live longer, and have more offspring.
-For more explanation of the set-up and how this is possible,
-see \citet{etheridge/kurtz:2018} and \citet{kurtz/rodrigues:2011}
-(and note that our $N$ corresponds to the $\lambda$ of those papers).
-Furthermore, the limiting spatial-level process will still be a point measure,
-and so we explicitly retain the notion of individuals and lineages through to the 
-large-population-density limit.
-
-% % % % % % % % % % % % % % % %
-\subsection{Lookdown construction of the population density process}
-\label{sec:lookdown_defn}
-
-In this section,
-we'll define the process $(\lp_t)_{t \ge 0}$ in terms of the dynamics of labeled particles,
-and write down its generator.
-Since the dynamics depend on the spatial locations of particles,
-in this section we define $\eta_t$ to be the corresponding spatial measure,
-i.e.,
-$$
-    \eta_t(\cdot) = \frac{1}{N} \lp_t(\cdot \times [0, N])  .
-$$
-A nontrivial consequence of the way we define $\lp_t$ will be that
-this process has the same distribution as the process $(\eta_t)_{t \ge 0}$ defined above
-in Definition~\ref{defn:mgale_construction}.
-(This provides our justification for using the same notation for both.)
-
-As before, we first describe the dynamics of individuals
-in the original time units -- i.e., before scaling by $\theta$,
-which will be introduced below.
-Suppose that the initial population is composed of $O(N)$ many particles
-with levels uniformly distributed between $[0, N]$.
-Suppose the current state of the population is $\lp$,
-with spatial projection $\eta$.
-An individual at spatial location $x$ with level $u$
-produces one juvenile offspring at rate 
-$$
-2 \left(1 - \frac{u}{N}\right) \gamma(x, \eta) ,
-$$
-which disperses to a location relative to $x$ drawn from the kernel $q(x, \cdot)$.
-(Averaging over the uniform distribution of the level $u$,
-we recover the birth rate $\gamma(x, \eta)$.)
-This juvenile -- suppose it's location is $y$ --
-either survives, with probability $r(y, \eta)$, or immediately dies.
-(As before, ``maturity'' is instantaneous.)
-
-A new level $u_1$ is sampled independently and uniformly from $[u,N]$,
-and the parent and the offspring are assigned in random order to the levels $\{u, u_1\}$.
-This random assignment of levels to parent
-and offspring ensures that conditional on $\eta$,
-the levels of each individual at any point in time are independent, uniform random variables.
-
-Evidently this mechanism increases the proportion
-of individuals with higher levels.
-To restore the property that,
-conditional on $\eta$,
-the distribution of levels is conditionally uniform,
-we impose that 
-the level of an individual at location $x$
-evolves according to the differential equation
-$$
-    \dot{v}
-    =
-    % \gamma^{\mathfrak{m}}(x, \eta) \left\{N^{-1}(N -v)^{2} -(N -v)\right\}.
-    - \frac{v}{N} \left(N - v\right)
-    \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q(x, dy) .
-$$
-Since $v \in [0, N]$, this moves levels down;
-see~\cite{etheridge/kurtz:2018}, Section~3.4 for a detailed explanation.
-
-In the lookdown model, levels never cross below 0,
-while particles whose levels move above $N$ are regarded as dead
-(and do not affect to the population any more).
-Therefore, in order to incorporate death,
-the level of the individual at location $x$ with level $u$
-moves upwards at an additional rate $\mu(x,\eta) u$.
-Since levels are uniform,
-it is easy to check that if $\mu$ were constant,
-this would imply an exponential lifetime for each individual;
-see~\cite{etheridge/kurtz:2018}, Section \comment{TODO}
-for more general justification.
-
-Putting these together,
-the level $u$ of an individual at $x$ evolves according to:
-\begin{equation} \label{eqn:dot_u}
-    \dot u
-    =
-    - \frac{1}{N} u \left(N - u\right)
-    \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q(x, dy) 
-    +
-    \mu(x,\eta) u .
-\end{equation}
-We shall write 
-$$
-    b(x, \eta)
-    :=
-    \theta\left(
-    \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy)
-    -
-    \mu(x,\eta)
-    \right) ,
-$$
-which captures the local net difference between reproduction and death,
-i.e., the deviation from criticality of the branching mechanism.
-Recall from equation \eqref{eqn:mu_defn} that
-$F(x,\eta) = \theta(r(x,\eta)\gamma(x,\eta) - \mu(x,\eta))$,
-and so we will have that
-\begin{align} \label{eqn:b_limit}
-\begin{split}
-b(x, \eta)
-&=
-    \theta \gamma(x, \eta) \int_{\IR^d} \left( r(y, \eta) - r(x, \eta) \right) q(x, dy)
-    + F(x, \eta) \\
-&\to
-    \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta) \qquad \text{as } \theta \to \infty .
-\end{split}
-\end{align}
-
-We can then rewrite the differential equation 
-governing how the level of each individual evolves as
-\begin{align}
-\dot{u}
-    &=
-    \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy)
-    \left\{
-        -\frac{u}{N}\left(N - u\right)
-        + u
-    \right\}
-    -
-    b(x,\eta) u / \theta
-    \nonumber \\
-    &=
-    \frac{1}{N} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
-    -
-    b(x, \eta) u / \theta
-    . \label{differential equation for level}
-\end{align}
-
-Now, we can write down the generator for $(\lp_t)_{t \ge 0}$,
-the lookdown process.
-In what follows, we will write sums (and, products) over ``$(x, u) \in \xi$''
-to mean as a sum over the (location, level) pairs of each individual in the population.
-Test functions for $\lp$ then take the form
-\begin{equation} \label{eqn:test_functions}
-f(\lp)=\prod_{(x,u)\in \lp}g(x,u)=\exp\left(\int \log g(x,u)\lp(dx, du)\right),
-\end{equation}
-where
-$g(x,u)$ is differentiable in $u$ and 
-smooth in $x$.
-We will also assume that $0\leq g(x,u) \leq 1$ for all $u\in [0,N]$,
-and $g(x,u)\equiv 1$ for $u\geq N$.
-In the expressions that follow,
-we shall often see one or more factor of $1/g(x,u)$;
-it should be understood that if $g(x,u)=0$,
-then it simply cancels 
-the corresponding factor in $f(\lp)$.
-
-Recall that just as with $\eta_t$, in defining $(\lp_t)_{t \ge 0}$
-we sped up time by a factor of $\theta$.
-As a result, per-capita rates below will have a factor of $\theta$
-not present in the expressions above.
-
-First consider the terms in the generator that come from birth events.
-When a birth successfully establishes,
-a new level is generated above the parent's level,
-and this new level is assigned to either the offspring or the parent.
-Since the probability of each is 1/2,
-the contribution of birth to the generator maps $f(\lp)$ to
-\begin{align}
-    &
-    f(\lp)
-    \sum_{(x, u) \in \lp}
-    2 \frac{\theta}{N} \gamma(x, \eta)
-    \int_u^N
-    \int_{\IR^d}
-    \left(
-    \frac{1}{2}
-    \bigg\{
-            g(y, u_1)
-        + \frac{ g(y, u) g(x, u_1) }{ g(x, u) }
-    \bigg\}
-        - 1
-    \right)
-    r(y, \eta) q(x, dy)
-    du_1
-    \\
-    \begin{split} \label{eqn:birth_generator}
-&=
-    f(\lp)
-    \sum_{(x, u) \in \lp}
-    2 \gamma(x, \eta)
-    \bigg\{
-        \frac{1}{2 N}
-        \int_u^N
-        g(x, u_1) du_1
-        \frac{
-            \theta \int_{\IR^d} (g(y, u) - g(x, u)) r(y, \eta) q(x, dy)
-        }{
-            g(x, u)
-        }
-    \\ & \qquad \qquad \qquad {}
-        + \frac{\theta}{N}
-        \int_u^N \int_{\IR^d}
-        \left( \frac{g(y, u_1) + g(x, u_1)}{2} - 1 \right)
-        r(y, \eta) q(x, dy)
-        du_1
-    \bigg\}
-    .
-    \end{split}
-\end{align}
-Here, $u_1$ is the new level and $y$ is the offspring's location,
-and so the two terms in the integral correspond to the two situations:
-in the first, we have added an individual at $(y, u_1)$,
-while in the second, we replace an individual at $(x, u)$
-by one at $(x, u_1)$ and another at $(y, u)$.
-We've rewritten it in this form because the two pieces
-each naturally converge to separate terms in the limit.
-
-The remaining term in the generator is due to the motion of particles' levels,
-mapping $f(\xi)$ to
-\begin{align} \label{eqn:level_generator}
-    f(\lp)
-    \sum_{(x, u) \in \lp}
-    \left(
-    \frac{\theta}{N}
-        \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
-        -
-        b(x, \eta)u
-    \right)
-    \frac{\partial_u g(x,u)}{g(x,u)} .
-\end{align}
-
-We can now define the spatial-level process
-explicitly as a solution to a Martingale Problem,
-whose generator is just the sum of
-\eqref{eqn:birth_generator} and \eqref{eqn:level_generator}.
-
-% % % % % % % %
-\begin{definition}[Martingale Problem Characterisation]
-    \label{defn:lookdown_mgale}
-For given positive values of $N$ and $\theta$
-and $\lp_0 \in \mathcal{M}_F(\IR^d \times [0,N])$,
-we define $(\lp^{N}_t)_{t \geq 0}$
-to be the unique solution to the martingale problem
-with initial condition $\lp_0$ and generator $A^{N}$ that satisfies
-\begin{equation*}
-\begin{split}
-& A^{N}f(\lp ) \\
-&\quad =
-    f(\lp)
-    \,\sum_{(x,u)\in \lp}\,
-    2 \gamma(x, \eta)
-    \Bigg\{ \frac{1}{2N} \int_u^N g(x,u_1) du_1
-            \frac{
-                \theta \int_{\IR^d}
-                (g(y,u) - g(x,u))
-                r(y, \eta) q_{\theta}(x,dy)
-            }{ g(x,u) }
-        \\
-    &\qquad\qquad\qquad\qquad\qquad\qquad\qquad {} +
-        \frac{\theta}{N} \int_u^N
-        \int_{\IR^d}\left(
-            \frac{ g(y,u_1) + g(x,u_1) }{ 2 } - 1
-        \right)
-        r(y, \eta) q_{\theta}(x,dy)
-        du_1
-    \Bigg\}\\
-    &\qquad\qquad {} +
-    f(\lp) \sum_{(x,u)\in\lp}\,
-    \left(
-        \frac{\theta}{N} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q_\theta(x, dy) u^2 -b_{\theta}(x,\eta)u
-    \right)
-    \frac{\partial_u g(x,u)}{g(x,u)}
-    ,
-\end{split}
-\end{equation*}
-for all smooth functions $g \in C^{2}_{0}(\IR^d)$,
-where $f(\lp) = \prod_{(x, u) \in \lp} g(x, u)$ as defined in \eqref{eqn:test_functions},
-and $\eta(\cdot) = \lp(\cdot \times [0, N]) / N$ is the scaled spatial pushforward of $\lp$,
-as before.
-\end{definition}
-
-Since everything is finite,
-it is clear that the martingale problem for finite $N$ has a unique solution.
-Next we state the limiting martingale problem,
-for which we do not have uniqueness (although we construct an explicit solution later).
-
-\begin{definition}[Martingale Problem Characterisation, $N=\infty$]
-    \label{defn:limiting_lookdown_mgale}
-    For a given value of $\alpha \in [0, \infty)$,
-    define the operator $A$ acting on test functions of the form
-    $f(\xi) = \prod_{(x, u) \in \xi} g(x, u)$ with $g \in C_0^2(\IR^d \times [0, \infty)$
-    and for which there exists a $u_0$ with $g(x, u) = 1$ for all $u > u_0$.
-    Then, let $A f$ be
-    \begin{align} \begin{split} \label{eqn:limiting_lookdown_generator}
-    A f(\lp)
-    &=
-        f(\lp)  \sum_{(x, u) \in \xi}
-        \gamma(x, \eta)
-            \frac{
-                \DG(g(\cdot, u) r(\cdot, \eta))(x) - g(x,u) \DG r(x,\eta)
-            }{
-                g(x, u)
-            }
-    \\ &\qquad {} +
-        f(\lp) \sum_{(x, u) \in \xi}
-        2 \alpha \gamma(x, \eta) r(x, \eta \int_u^\infty (g(x, u_1) - 1) du_1
-    \\ &\qquad {} +
-        f(\lp) \sum_{(x, u) \in \xi}
-        \left(
-            \alpha \gamma(x, \eta) r(x, \eta) u^2
-            -
-            \left\{
-                \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta)
-            \right\} u
-        \right)
-        \frac{\partial_u g(x, u)}{ g(x,u) }  .
-    \end{split} \end{align}
-    We say that a $\lpmeasures$-valued process $(\xi_t)_{t \ge 0}$
-    is a solution to the $(A, \lp_0)$ martingale problem
-    if it has initial distribution $\lp_0$
-    and $f(\lp_t) - \int_0^t Af(\lp_s) ds$ is a martingale for all $f$
-    as defined above.
-\end{definition}
-
-\comment{We talked about having the next paragraph be a Proposition or something?}
-
-The lookdown processes have been carefully constructed so that
-if we average over levels in the expression for the lookdown generator
-(equation~\eqref{eqn:lookdown_generator} or~\eqref{eqn:limiting_lookdown_generator})
-we get the generator for the population process
-(visible in equation~\eqref{eqn:eta_martingale}
-or~\eqref{eqn:limiting_mgale_problem}, respectively).
-Once this is verified (and some boundedness conditions)
-in Appendix \ref{sec: Markov Mapping Theorem Application},
-the Markov Mapping Theorem \citep[Thm A.2 in][]{etheridge/kurtz:2018}
-tells us that for any population process $(\eta^N_t)_{t \ge 0}$
-(i.e., solution to the martingale problem of Definition~\ref{defn:mgale_construction})
-% of equations~\eqref{eqn:eta_martingale} and \eqref{eqn:prelimit_martingale_variation}
-there is a lookdown representation $(\lp^N_t)_{t \ge 0}$
-(i.e., solution to the martingale problem of Definition~\ref{defn:lookdown_mgale})
-for which $\eta^N_t(\cdot) = \lp^N_t(\cdot \times [0, N])$
-and such that at each $t$, conditioned on $(\eta^N_s){s \le t}$, the levels of $\lp_t^N$
-are independently and uniformly distributed on $[0, N]$.
-The same property holds in the limit:
-for any solution $(\eta_t)_{t \ge 0}$ to the martingale problem of Theorem~\ref{nonlocal_convergence}
-there is a lookdown process $(\lp^N_t)_{t \ge 0}$
-that is a solution to the martingale problem of Theorem~\ref{lookdown_convergence}
-for which $\eta_t(\cdot) = \lim_{u_0 \to \infty} \frac{1}{u_0} \lp_t(\cdot \times [0, u_0))$
-and such that at each $t$,
-$\lp_t$ is conditionally Poisson with Cox measure $\eta_t(dx) \times du$,
-conditioned on $(\eta_s)_{s \le t}$.
-Furthermore, convergence of the lookdown processes would imply convergence of the population processes
-\citep[Thm A.9 in][]{KR}.
-
-Now that the lookdown process has been defined,
-we can present the main convergence theorem that is analogous
-to Theorem~\ref{thm:nonlocal_convergence} for the population process.
-
-\begin{theorem}
-    \label{thm:lookdown_convergence}
-    Let $(\lp_t^N)$ be as defined in Definition~\ref{defn:lookdown_mgale}
-    and assume that as $N \to \infty$,
-    $\theta \to \infty$ in such a way that $\theta/N \to \alpha$.
-    Suppose also that $\eta^N_0 \to \eta_0$ (as measures on $\IR^d$),
-    and that for each $N$, $\lp^N_0(dx, du)$ is conditionally Poisson on $\IR^d \times [0, N]$
-    with Cox measure $\eta^N_0(dx) \times du$.
-    Then, the sequence of stochastic processes $(\lp_t^N)_{t \ge 0}$
-    converges along subsequences in distribution as $N \to \infty$
-    to a measure-valued process $(\lp_t)_{t \ge 0}$
-    with $\lp_0$ conditionally Poisson with Cox measure $\eta_0(dx) \times du$,
-    that is a solution to the martingale problem~\ref{defn:limiting_lookdown_mgale}.
-\end{theorem}
-
-\comment{TODO: remove this next bit?}
-
-In Appendix \ref{sec: Markov Mapping Theorem Application},
-we will show that
-if we define $\Gamma (d\textbf{u})$
-as the probability kernel that corresponds to
-assigning each particle an i.i.d. uniform $[0,N]$-level,
-and for any $\lp \in \mathcal{M}_f(\IR^d \times [0,\infty))$, we denote
-$$\hat{f}(\lp)=\int f(\lp) \Gamma (d\textbf{u})$$ 
-to be the spatial test functions with averaged level,
-then the process
-\begin{equation}
-\begin{aligned}
-M^{N}_t:=&\hat{f}(\lp_t)-\hat{f}(\lp_0)-\int_{0}^{t}\int   A^{N}f(\lp_s)\Gamma(d\textbf{u})ds\\
-:=&\hat{f}(\lp_t)-\hat{f}(\lp_0)-\int_{0}^{t}   \Pgen^{N}\hat{f}(\lp_s)ds
-\end{aligned}    
-\end{equation}
-is a martingale.
-
-By the Markov Mapping Theorem,
-there exists a solution $(\lp^{N}_t)_{t \geq 0}$
-to the Martingale Problem with generator $A^{N}$.
-Furthermore,
-the spatial projection of $(\lp^{N}_t)_{t \geq 0}$
-shares the same law of $(\eta^{N}(t))_{t \geq 0}$,
-i.e.
-$$(\eta^{N}(t))_{t \geq 0}
-\sim \left(\frac{1}{N}\sum\limits_{(X(t),U(t))\in \lp^{N}(t)} \delta_{X(t)}\right)_{t \geq 0},$$
-and conditional on 
-$(\eta^{N}(t))_{t \geq 0}$,
-the levels of particles in $(\lp^{N}_t)_{t \geq 0}$
-are i.i.d. uniformly distributed between $[0,N]$.
-
-%% %% %% %% %% %% %% %% %% %% %% %%
-\subsection{Explicit construction of lines of descent}
-    \label{sec: individual lines of descent}
-
-In this section we explicitly construct the lookdown process
-in a way that explicitly represents the motion of each individual and their offspring.
-This provides an explicit construction of the solution to
-the limiting martingale problem~\ref{defn:limiting_lookdown_mgale}.
-It will furthermore make it obvious how lineages move in the limit,
-and will allow us to identify all 
-individuals in the current population that are descendants of a
-given ancestor at time zero. In theory at least, this allows us to
-recover all the information about genealogies relating individuals 
-sampled from the present day population. This idea draws on the notion
-of `tracers', popular in statistical physics and used in population
-genetics by a number of authors including 
-\cite{biswas/etheridge/klimek:2018, durrett/fan:2016, hallatschek/nelson:2008}.
-
-We will construct the process using a Ulam-Harris indexing scheme,
-which associates the outcomes of each branching event with a label obtained
-by appending to the previous label.
-To begin, we assign each extant individual a label from $\IN_{\ge 0}$.
-Suppose an individual with label $a$ and level $u$ reproduces,
-and as a result there are two individuals, one with level $u$ and one with a new level $u_1 > u$.
-The parent individual, previously labeled $a$, might be assigned either level.
-We will track chains of descendant individuals forwards through time
-following levels, rather than individuals, and will call this a \emph{line of descent}.
-So, after reproduction, we give a new label to \emph{only} the individual
-that is given the new level $u_1$,
-retaining the label $a$ for the individual with the old level $u$.
-So, there is a unique label assigned at each birth event,
-assigned to the resulting individual with the higher level,
-and the label of an individual may change throughout its lifetime.
-It would be possible to reconstruct individual identities along a line of descent
-from this construction,
-but we don't write this out.
-
-\comment{Perhaps the following is confusing having $t$ for the point of $\Pi_a$,
-and we should instead use... $\tau$?}
-
-Concretely, then: for each label $a$ in
-$\labelspace = \bigcup_{k \ge 1} \IN_{\ge 1}^k$
-let $\Pi_a$ be an independent Poisson process on $[0, \infty)^2 \times \IR_d \times \{0,1\}$.
-The mean measure of each $\Pi_a$ is a product of Lebesgue measure on the first two coordinates,
-the density of the standard Gaussian $N(0,1)$ on $\IR^d$, and $(\delta_0 + \delta_1)/2$ on $\{0, 1\}$.
-It will also be convenient
-to suppose that for each label $a$ we have an enumeration of the points in $\Pi_a$,
-so we may refer to ``the $j^\text{th}$ point in $\Pi_a$'',
-although the precise order of this enumeration is irrelevant.
-If $(t, v, z, \kappa)$ is the $j^\text{th}$ point in $\Pi_a$,
-then $t$ will determine a possible birth time,
-$v$ will determine the level of the offspring,
-$z$ will give the spatial displacement of the offspring relative to the parent,
-$\kappa$ will be used to determine whether parent or offspring is assigned the new level,
-and the new label produced will be $a \concat j$,
-i.e., the label $a$ with $j$ appended
-(so, if $a = (a_1, \ldots, a_k)$ then $a \concat j = (a_1, \ldots, a_k, j)$).
-Each label $a$ has a birth time $\tau_a$,
-when it is first assigned,
-and a death time $\sigma_a$, when its level first hits $N$.
-For any $\tau_a \le t \le \sigma_a$ we denote by $X_a(t)$ and $U_a(t)$ the spatial location and level
-of the individual carrying label $a$ at time $t$, respectively.
-Now, since we have defined labels so that the level does not jump,
-$U_a$ satisfies~\eqref{eqn:dot_u} for $\tau_a \le t \le \sigma_a$, i.e.,
-\begin{equation} \label{eqn:U_line_of_descent}
-    \begin{split}
-& U_a(t)
-    =
-    U_a(\tau_a) \\
-&\qquad {}   
-    + \int_{\tau_a}^{t}
-    \left(
-        \frac{\theta}{N} \gamma(X_a(s),\eta_s)
-        \int_{\IR^d} r(z,\eta_s) q(X_a(s),dz) U_a(s)^2
-        -
-        b(X_a(s),\eta_s) U_a(s)
-    \right)
-    ds ,
-\end{split}
-\end{equation}
-and, of course, $\sigma_a = \inf\{t \ge \tau_a : U_a(t) > N\}$.
-
-Potential reproduction events occur at times $t$
-for each point $(t, v, w, \kappa) \in \Pi_a$ with $t \ge \tau_a$.
-We say `potential' since if the resulting level is greater than $N$,
-the event does not happen.
-If this is the $j^\text{th}$ point in $\Pi_a$,
-the new label is $a \concat j$, the (potential) birth time is $\tau_{a \concat j} = t$.
-Similarly, the potential birth location is $y(X(t-), z)$, where
-$$
-    y(x, z)
-    :=
-    \frac{1}{\theta}\meanq(x)
-    +
-    \frac{1}{\sqrt{\theta}}K(x) z,
-$$
-where $K(x)K^{T}(x) = \covq(x)$.
-
-Next we must choose the level of the offspring.
-We would like the individual to produce offspring at $y$ at rate
-$2 (1 - u/N) \theta \gamma(x, \eta) r(x + y, \eta)$,
-and to do this
-we will associate the point $(s, v, w, \kappa) \in \Pi_a$ with level $u + v \ell$,
-where $\ell$ is chosen so that this is the rate of appearance of points in $\Pi_a$
-with level below $N$.
-Since the mean measure of $\Pi_a$ is Lebesgue in the $t$ and $v$ directions,
-this requires that $v < (N - u) / \ell$, 
-and so such points appear at rate $(N-u)/\ell$.
-Therefore, we define
-$$
-    \ell(x, y, \eta)
-    =
-    \frac{
-        1
-    }{
-        2 N^{-1} \theta \gamma(x, \eta) r(x + y, \eta)
-    } ,
-$$
-and using this, the (potential) new level is
-\begin{equation*}
-    U_{a \concat j}(t)
-    =
-    U_a(t)
-    +
-    v \ell(X_a(t-), y(X_a(t-), z), \eta(t-)) .
-\end{equation*}
-If $U_{a \concat j}(t) < N$,
-the new individual labeled $a \concat j$ is produced,
-and $\kappa$ determines which label is associated with the new location,
-so
-\begin{align*}
-    X_{a \concat j}(t)
-    &=
-    X_a(t-) + (1 - \kappa) y(X_a(t-), z) .
-\end{align*}
-On the other hand
-if $U_{a \concat j}(t) \ge N$, then $X_a$ is unchanged and $X_{a \concat j}$ is undefined,
-so
-\begin{align} \label{eqn:X_line_of_descent}
-    X_a(t)
-    &=
-    X_a(t-) + \kappa y(X_a(t-), z) \ind_{U_{a \concat j}(t) < N} .
-\end{align}
-Recall that the parental \emph{individual} always retains their spatial location,
-so that $\kappa = 0$ corresponds to the parent being assigned a new level,
-and our line of descent switching to the offspring.
-Combining these, $X_a$, for $\tau_a \le T < \sigma_a$, solves the equation 
-\begin{align*}
-    X_a(T)
-    &=
-    \int_{[\tau_a, T) \times [0, \infty) \times \IR \times [0, 1]}
-    y(X_a(t-), z)
-    \kappa
-    \ind_{
-        U_a(t) + v \ell(X_a(t-), y(X_a(t-), z), \eta_t)
-    }
-    d\Pi_a(s, v, z, \kappa) .
-\end{align*}
-
-Although we have described the evolution of a line of descent only for a given label
-(i.e., for $\tau_a \le s < \sigma_a$),
-we can extend the definition to earlier times
-by setting for $0 \le s < \sigma_a$
-$X_a(s)$ equal to $X_{[a]_s}(s)$,
-where $[a]_s$ is the label of the ancestor of label $a$ alive at time $s$,
-and similarly for $U_a(s)$.
-It is then straightforward, albeit tedious,
-to write down the time evolution of $(X_a(s), U_a(s))$ for all time back to $s=0$
-in terms of the driving Poisson processes.
-Although at finite $N$ the spatial process $X_a(s)$ is affected by jumps in the level $U_a(s)$,
-we will see that in the $N \to \infty$ limit
-the behavior of $X_a(s)$ is not affected by these jumps.
-
-We can now express the population processes using these levels:
-\begin{align*}
-    \eta^N_s = \frac{1}{N} \sum_{a : \tau_a \le s < \sigma_a} \delta_{X_a(s)}
-    \qquad \text{and} \qquad
-    \lp^N_s = \sum_{a : \tau_a \le s < \sigma_a} \delta_{(X_a(s), U_a(s))} .
-\end{align*}
-
-\comment{TODO: explain a bit more about the infinitely many points in the $v$ direction.}
-
-\comment{
-    Note here that although we have a single construction that couples
-    the processes across all $N$,
-    we don't necessarily have pointwise a.s.\ convergence of trajectories of the process.
-    Furthermore, individuals at all levels may affect others through the population process,
-    and in the deterministic case arbitrarily high levels may drift downwards.
-    HOWEVER, this does suggest that a good approximation to the genealogies
-    might be obtained by simulating up until a sufficiently high level
-    that we have a good approximation to the population process.
-}
-
-% % % % % % % % % % % % %  % % %
-\subsubsection{Lines of descent in the scaling limit}
-
-\comment{I don't think we need this.}
-
-We now write down expressions
-that give the spatial and level dynamic
-of a whole line of descent.
-In particular, our description is consistent
-for any $N \in \mathbb{N}$.
-
-Recall that
-the particle with label $(a_0,a_1,..,a_k)$
-is the offspring
-with a new level
-from the $a_k$-th potential birth
-of $(a_0,...,a_{k-1})$,
-who is again the offspring
-with a new level from
-the $a_{k-1}$-th potential birth
-of $(a_0,...,a_{k-2})$, 
-etc..
-In particular, 
-the particle with label $(a_0)$
-is the direct descendant of
-the $a_0$-th original ancestor
-of the whole population, i.e.
-it has never experienced
-a jump in level throughout
-its ancestry.
-
-For simplicity, for $a=(a_0,..,a_k)$,
-we denote $[a]_{i}:=(a_0,..,a_i)$
-to be the $i$-th generation 
-ancestor of the lineage $a$.
-In particular, if at time $t$,
-if the ancestral lineage $[a]_t$
-is at its $i(t)$-th generation,
-then $[a]_t = [a]_{i(t)}$.
-
-We also write 
-$(s_{[a]_{i}}, v_{[a]_{i}}, y_{[a]_{i}}, \kappa_{[a]_{i}})
-\in \Pi_{[a]_{i-1}}$
-to be the reproduction event
-that creates $[a]_{i}$ from $[a]_{i-1}$,
-and similarly,
-$(s_{[a]_{i} \concat j}, v_{[a]_{i} \concat j}, y_{[a]_{i} \concat j}, \kappa_{[a]_{i} \concat j})
-\in \Pi_{[a]_{i-1}}$
-to be the reproduction event 
-that creates $[a]_{i} \concat j$
-from $[a]_{i-1}$.
-
-We first write down an expression
-for the level of particle $a=(a_0,a_1,..,a_k)$ at time $t$.
-Since we ensure that
-the level of a particle
-only jumps when a reproduction event
-creates a new label,
-the level of particle $a=(a_0,a_1,..,a_k)$ is determined
-by $k$ many jumps,
-and subsequent continuous evolutions
-given by Equation \eqref{eqn:U_line_of_descent}.
-
-Under this notation, for $t> 0$,
-\begin{equation}
-\label{eq: level_across_lineage}
-\begin{aligned}
-&U^{N}_{[a]_{k}}(t)- U^{N}_{[a]_{0}}(0)\\
-=& \sum_{i=1}^{k} \int_{\tau_{[a]_{i-1}}}^{\tau_{[a]_{i}}}
-\left(
-        \frac{\theta}{N} \gamma(X_{[a]_{i-1}}(s),\eta_s)
-        \int_{\IR^d} r(z,\eta_s) q(X_{[a]_{i-1}}(s),dz) U_{[a]_{i-1}}(s)^2
-        -
-        b(X_{[a]_{i-1}}(s),\eta_s) U_{[a]_{i-1}}(s)
-    \right)
-    ds\\
-&+\int_{\tau_{[a]_{i}}}^{t}
-\left(
-        \frac{\theta}{N} \gamma(X_{[a]_{i}}(s),\eta_s)
-        \int_{\IR^d} r(z,\eta_s) q(X_{[a]_{i}}(s),dz) U_{[a]_{i}}(s)^2
-        -
-        b(X_{[a]_{i}}(s),\eta_s) U_{[a]_{i}}(s)
-    \right)
-    ds\\
-&+\sum_{i=1}^{k}
-    \left( \ell(X_{[a]_{i-1}}(\tau_{[a]_{i}}-), y_{[a]_{i}}, \eta(\tau_{[a]_{i}}-)) v_{[a]_{i}}
-    \right)
-\end{aligned}    
-\end{equation}
-where the first two terms correspond to
-sum of the evolution along the same generation,
-and the second term corresponds
-to the sum of jumps in levels
-when a new label is introduced.
-
-To preserve consistency 
-as we send $N \to \infty$
-in our scaling limit,
-we allow $U_{[a]_t}(t)$ to hit $\infty$.
-To identify dead lines of descent,
-for a label $a$,
-we define
-$\sigma_{a}^{N}:= \inf\{t \geq 0 : U_{[a]_t}(t) > N\}$.
-In the $N$-th scaling regime,
-we proclaim the individual
-$a$ to be dead
-at time $t$
-when $t > \sigma_{a}^{N}$
-
-Note that in particular,
-if $U_{[a]_i}(t)>N$
-at some time $t$
-in the $i$-th generation,
-then $U_{[a]_j}(t)>N$
-for all $j \geq i$
-and
-$\sigma_{[a]_j}^{N}=\sigma_{[a]_i}^{N}$.
-In words, all descendants of dead
-particles are dead by default.
-
-Similarly, we generalise the notion of death above
-to the infinity case by considering 
-$\sigma_{[a]_t}^{\infty}:=\inf\{t \geq 0 : U_{[a]_t}(t) =\infty\}$.
-
-\subsubsection{Spatial jumps along a whole line of descent}
-
-\comment{I also don't think we need this.}
-
-We now write down an expression for the
-spatial location of $[a]_t$ at time $t$.
-Note that in the spatial case,
-jumps occur along the same generation
-whenever $\kappa = 0$ in successful birth events,
-and occur across two generations
-whenever $\kappa = 1$ in successful birth
-events.
-
-To illustrate this, consider the spatial location of $(a_0,a_1)=(2,3)$ with birth time $\tau_{(2,3)}$ at some time $t>\tau_{(2,3)}$.
-If $U_{(2,1)}(\tau_{(2,1)}) < N$,
-the first birth event of the ancestor
-with label $(2)$
-is successful.
-If $\kappa = 0$ in this birth event,
-the parent and offspring swap labels,
-resulting in
-a spatial jump for the label $(2)$.
-On the contrary, 
-if $U_{(2,2)}(\tau_{(2,2)}) \geq N$
-or $\kappa = 1$
-in the second birth event of $(2)$,
-the parent does not give birth
-or retains its label,
-so there is no spatial jump.
-
-On the other hand, 
-if $\kappa=1$ when $(2,3)$ is born,
-the new label is given to
-the offspring
-with new spatial location,
-resulting in a jump,
-and vice versa.
-
-After $(2,3)$ is born,
-whenever the particle with label
-$(2,3)$ gives birth, 
-if $\kappa = 0$, the label $(2,3)$
-is adopted by the offspring
-which results in a spatial jump
-in the position of $(2,3)$
-again.
-
-Finally, we write $S(\tau_{[a]_k},t):=[\tau_{[a]_k},t]\times[0,\infty)\times\IR^d \times \{0,1\}$.
-Under this notation, for $t>\tau_{[a]_k}$,
-
-\begin{equation}
-\label{eq: space_across_lineage}
-\begin{aligned}
-&X^{N}_{[a]_{k}}(t)- X^{N}_{[a]_{0}}(0)\\
-=& \sum_{i=1}^{k}
-\sum_{j=1}^{a_i-1}
-(1-\kappa_{[a]_{i-1}\concat j}) y_{[a]_{i-1}\concat j} \ind_{U_{[a]_{i-1}\concat j}(\tau_{[a]_{i-1}\concat j}) < N}\\
-&+ \sum_{i=1}^{k}
-\kappa_{[a]_i} y_{[a]_i} \ind_{U_{[a]_i}(\tau_{[a]_i}) < N}\\
-&+\int_{S(\tau_{[a]_k},t)}
-(1-\kappa)y(z)
-\ind_{ \{
-        U_{[a]_k}(\tau_{[a]_k}+s)
-        + \ell(X_{[a]_k}(\tau_{[a]_k}+s),y,\eta_{[a]_k}(\tau_{[a]_k}+s)) v < N
-        \}
-      } 
-\Pi_{[a]_k}(dsdvdzd\kappa),
-\end{aligned}    
-\end{equation}
-where the first term
-corresponds to 
-the sum of $a_{i}-1$ many potential jumps
-in the $(i-1)-th$ generation;
-the second term corresponds to 
-the sum of $k$ many potential jumps
-when the $k$-th generation is introduced;
-and the last term
-corresponds to sum of 
-potential jumps that occured in
-the current generation from 
-time $\tau_{[a]_k}$
-to current time $t >\tau_{[a]_k}$.
-
-%% %% %% %% %% %% %% %% %% %% %% %%
-\subsection{Limiting processes for lines of descent}
-\label{sec:limiting_lines_of_descent}
-
-The previous section constructs the lookdown process
-in a way that makes individual lines of descent converge pointwise as $N \to \infty$,
-using the same underlying Poisson processes $\{\Pi_a\}_{a \in \labelspace}$.
-To see this, first note that if the Poisson processes are fixed
-then the set of events to which a given label $a \in \labelspace$ is associated
-is also fixed -- this is the sequence $(s_k, v_k, y_k, \kappa_k)$ associated with a given label $a$.
-Therefore, the processes $\Pi_a$ are also unchanged.
-First, we clearly need that the spatial projections $\eta$ converge.
-
-Supposing that they do,
-consider how a line of descent $(X_a(t), U_a(t))$ evolves.
-The line of descent throws off a new line of descent at a higher level
-when there is a point $(s, v, y, \kappa)$ in $\Pi_a$ with $s > \tau_a$ and
-\begin{equation} \label{eqn:line_points}
-    v < 2 (N - U_a(s)) N^{-1} \theta \gamma(X_a(s), \eta_s) r(X_a(s) + y, \eta_s) .
-\end{equation}
-Since the mean measure of the $v$ coordinate is Lebesgue,
-$\theta/N \to \alpha$,
-and $q(x, dy) \to \delta_x(dy)$,
-this corresponds in the limit to new lines of descent being thrown off at all times,
-i.e., according to a Poisson process with rate
-$$
-2 \alpha \gamma(X_a(t), \eta_t) r(X_a(t), \eta_t) 
-$$
-and uniform intensity on higher levels.
-Again, since in the limit the dispersal distance is zero,
-new levels are produced at the same spatial location.
-However, this affects the location of the line of descent:
-for each new line of descent, there is a $1/2$ chance
-that the line of descent switches location (i.e., moves to $X_a(t) + y$).
-Taking $g$ to be a suitable test function on $\IR^d$, 
-and rewriting~\eqref{eqn:line_points},
-the generator of this motion is, when the level is $u$
-and the state of the population is $\eta$,
-applied to $g(x)$,
-\begin{align*}
-    &
-    \left(1 - \frac{u}{N}\right) \gamma(x, \eta)
-    \theta \int_{\IR^d} r(x+y, \eta) (g(x+y) - g(x)) q(x, dy) \\
-    &\qquad {}
-    =
-    \left(1 - \frac{u}{N}\right) \gamma(x, \eta)
-    \bigg\{
-        \theta \int_{\IR^d} (r(x+y, \eta) g(x+y) - r(x, \eta) g(x)) q(x, dy) \\
-        &\qquad \qquad {}
-        -
-        \theta \int_{\IR^d} (r(x+y, \eta) - r(x, \eta) ) g(x) q(x, dy) 
-    \bigg\} \\
-    &\qquad {}
-    \to
-    \gamma(x, \eta)
-    \left(
-        \DG(rg)(x) - g(x) \DG(r)(x)
-    \right) ,
-    \qquad \text{as} N, \theta \to \infty .
-\end{align*}
-Notice that the factors of 2 have canceled,
-and that the result is independent of $u$.
-Also recall that $r(x, \eta)$ only depends on $\eta$ through $\smooth{r}\eta(x)$,
-which is guaranteed to be smooth, so that $\DG(r)$ and $\DG(gr)$ are well-defined.
-
-The only thing that remains is to describe how the levels change,
-but this is immediate from applying limit~\eqref{eqn:b_limit}
-to equation~\eqref{differential equation for level}.
-
-To write out the joint motion of spatial coordinate and levels,
-it is useful to work out the differential operator above in more detail.
-Recall that $\DG g(x) = \sum_i \meanq_i \partial_i g(x) + \sum_{ij} \covq_{ij} \partial_{ij} g(x)$,
-and for the moment write $r(x)$ for $r(\cdot, \eta)(x)$,
-so that
-\begin{align}
-\DG(rg)(x) - g(x) \DG(r)(x)
-    &= \nonumber
-    r(x) \sum_i \meanq_i \partial_i g(x)
-    + 2 \sum_{ij} \meanq_i \partial_i r(x) \covq_{ij} \partial_j g(x)
-    + r(x) \sum_{ij} \covq_{ij} \partial_{ij} g(x) \\
-    &= \label{eqn:limiting_generator}
-    r(x) \left\{
-        \left(
-        \meanq
-        + 2 \covq \grad \log r(x)
-        \right)
-        \cdot
-        \grad g(x)
-        +
-        \sum_{ij} \covq_{ij} \partial_{ij} g(x)
-    \right\} .
-\end{align}
-
-We summarize the results in a proposition.
-
-\begin{proposition}[Line of descent construction]
-    \label{prop:limiting_construction}
-Let $\beta(x, \eta) = \meanq(x) + 2 \covq(x) \grad \log r(x, \eta)$
-and $K(x)$ such that $\covq(x) = K(x) K(x)^T$.
-Associate with each label $a \in \labelspace$
-an independent $d$-dimensional Brownian motion $W_a$
-and an independent Poisson process $R_a$ on $[0, \infty)^2$
-with Lebesgue mean measure,
-as before with points ordered in some way.
-Given $\eta_0 \in \measures$,
-let $(x_i, u_i)$ be the points of a Poisson process
-with mean measure on $\IR^d \times [0, \infty)$ a product of $\eta_0$ and Lebesgue measure.
-For each point begin a line of descent
-with label $i$, location $X_i(0) = x_i$, level $U_a(0) = u_i$, and birth time $\tau_i = 0$.
-Suppose that the spatial locations and level of each line of descent $a$
-solve, for $\tau_a \le t < \sigma_a$ as,
-where $\sigma_a = \lim_{K \to \infty} \inf\{t \ge 0: U_a(t) > K\}$,
-as
-\begin{align*}
-X_a(t)
-    &=
-    X_a(\tau_a)
-    + \int_{\tau_a}^{t}
-        \beta(X_a(s), \eta(s)) ds
-    + \int_{\tau_a}^{t}
-        K(X_a(s)) dW_a(s)
-    \\
-U_a(t)
-    &=
-    U_a(\tau_a)
-    + \int_{\tau_a}^{t}
-    \bigg(
-        \alpha \gamma(X_a(s),\eta(s))
-        r(X_a(s), \eta(s)) U_a(s)^2
-\\ &\qquad \qquad \qquad {}   
-        -
-        \left\{
-            \gamma(X_a(s),\eta(s)) \DG r(X_a(s),\eta(s))
-            + F(X_a(s), \eta(s))
-        \right\}
-        U_a(s)
-    \bigg)
-    ds .
-\end{align*}
-Each point in each $R_a$ denotes a potential birth time for $a$:
-if the $j^\text{th}$ point in $R_a$ is $(t, v)$, with $\sigma_a \le t < \tau_a$,
-then a new line of descent with label $a \concat j$ is produced,
-with birth time $\tau_{a \concat j} = t$,
-    location $X_{a \concat j}(t) = X_a(t)$, and level
-$$
-    U_{a \concat j}(t) = U_a(t)
-    + \frac{v}{ 2 \alpha \gamma(X_a(t), \eta_t) r(X_a(t), \eta_t) } .
-$$
-For any solution to the equations above, the processes defined by
-\begin{align*}
-    \eta_t
-    =
-    \lim_{u_0 \to \infty} \frac{1}{u_0}
-        \sum_{a : \tau_a \le t < \sigma_a \;\&\; U_a(t) < u_0} \delta_{X_a(t)}
-    \qquad \text{and} \qquad
-    \lp_t = \sum_{a : \tau_a \le t < \sigma_a} \delta_{(X_a(t), U_a(t))} 
-\end{align*}
-are solutions to the martingale problems of
-Theorems~\ref{thm:nonlocal_convergence} and~\ref{thm:lookdown_convergence},
-respectively.
-\end{proposition}
-
-In particular, note that if $\alpha=0$,
-no new lines of descent are produced.
-(More precisely, they are produced but ``at infinity'',
-since the spatial motion of the line of descent is the result of production of these lineages.
-
-\comment{Note that the analogous theorem for finite $N$ is obvious (??) and not stated as a proposition.}
-
-\comment{TODO: find the right place for this proof?}
-\begin{proof}[of Proposition~\ref{prop:limiting_construction}]
-    The fact that a solution to the system of equations
-    is a solution to the martingale problem of Theorem~\ref{thm:lookdown_convergence}
-    is an application of It\^o's theorem.
-    The calculations in \comment{XXX} leading to our application
-    of the Markov Mapping Theorem then show that 
-    the conditional Poisson property of $\lp_0$ is preserved
-    (i.e., holds for $\lp_t$ for all $t$), and so
-    $(\eta_t)_{t \ge 0}$ is well-defined,
-    and furthermore that $\eta_t$ is a solution
-    to the martingale problem of Theorem~\ref{thm:nonlocal_convergence}.
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Proofs}
-\label{sec:proofs}
-
-\comment{TODO structure of this section}
-
-% % % % % % % % % % % % %
-\subsection{Convergence of the population density process}
-    \label{sec:population_density_proof}
-
-In this section we prove the main theorem on convergence
-of the population density process, Theorem~\ref{thm:nonlocal_convergence}.
-This is usually implied by convergence of the lookdown process
-(see \citet{kurtz/rodrigues:2011} and \citet{KE});
-however in our situation because the parameters depend on the population process
-we will use convergence of the population process
-in the proofs of tightness and convergence for the lookdown process.
-
-\comment{TODO: move actual proof after its ingredients; just foreshadow here?}
-
-\begin{proof}[Proof of Theorem~\ref{thm:nonlocal_convergence}.]
-Here, we need to prove that for any sequence $N_k \to \infty$,
-there is a subsequence $N_{k(j)}$ along which $(\eta^{N_{k(j)}}_t)_{t\ge 0}$ converges in distribution
-(i.e., tightness for the family of distributions on c\`adl\`ag measure-valued paths),
-and that any limit is a solution to the martingale problem stated in the Theorem.
-This would imply convergence along $N_k$ to a unique limit
-if the solution to the martingale problem was unique;
-however, we only know this to be the case in certain situations.
-
-We prove tightness of $\eta^N$ as $\mathcal{D}_{\cmeasures}([0,\infty))$-valued processes,
-where $\cmeasures$ is the space of finite measures on the one-point compactification of $\IR^d$.
-To do this, we first prove that $\sup_{0 \le t \le T} \langle 1, \eta^N_t \rangle$ is tight
-(a compact containment condition, Lemma~\ref{lem:eta_compact_containment}).
-(The reason we use $\cmeasures$ instead of $\measures$
-is so that the set of measures with total mass less than $K$ is compact.)
-Next, in Lemma~ we show that the one-dimensional distributions,
-$\langle f, \eta^N_t \rangle$ are tight
-for each $f \in \mathcal{C}^2_0(\overline{\IR^d})$.
-Since this is a dense subset of bounded continuous functions on $\cmeasures$,
-together these results allow us to apply Theorem~3.9.1 of \citet{EK}.
-
-Next, we prove that the limit solves the martingale properties
-of equations~\eqref{eqn:limiting_mgale_problem} and~\eqref{eqn:limiting_mgale_variation}
-in Lemma~\ref{lem:limit_mgale}
-basically by checking the generators converge,
-which was mostly done in Section~\ref{sec:population_heuristics}.
-\end{proof}
-
-% % % % % % % % % % % % %
-\subsubsection{Tightness of empirical measures}
-    \label{sec:population_tightness_proofs}
-
-To prove tightness of the population process $\eta_t$,
-we first show that the expected total mass at some fixed time $T$
-is controlled uniformly across $N$, a compact containment condition.
-To establish this control,
-we first prove a technical lemma which controls spatial density of our population,
-and then we use the Burkholder-Davis-Gundy inequality
-to give us control over the running supremum of the total population mass.
-Once we have control over the total mass of the population, 
-we will also have control over local densities.
-This then allows us to prove that the particle system is tight
-by an application of the Aldous-Rebolledo criterion \citet{rebolledo:1980,alisonsup}.
-
-% % % % % % % % % % % % %
-\subsubsection{Compact Containment Condition}
-
-To show compact containment, we will need boundedness
-of the net per-capita reproduction rate.
-This does not follow immediately from our assumption that $F$ is bounded above
-because reproduction is not local:
-the net per-capita reproduction rate of an individual at $x$ is
-$$
-\theta \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q_\theta(x, dy) - \theta \mu(x, \eta)
-=
-F(x, \eta) + \gamma(x, \eta) \theta \int_{\IR^d} (r(y, \eta) - r(x, \eta)) q_\theta(x, dy) .
-$$
-We have assumed that $F$ is bounded,
-but we still need to show that our assumptions imply that
-the second term is bounded, uniformly as $\theta$ grows.
-
-\begin{lemma}
-    \label{lem:gamma_bound}
-    Under the assumptions of Definition~\ref{def:model_setup},
-    for all $f \in \mathcal{C}^{2}_{0}(\IR^d \times [0,\infty))$,
-    there exists a $K_f < \infty$ such that
-    for all $\theta > 0$ and all $\eta \in \measures$,
-    \begin{equation} \label{eqn:gamma_bound}
-    \gamma\big(x,\smooth{\gamma} \eta(x)\big)
-    \left| \theta 
-        \int_{\IR^n} 
-            \left\{
-                f(y, \smooth{r} \eta(y)) - f(x, \smooth{r} \eta(x))
-            \right\}
-        q_{\theta}(x,dy)
-    \right|
-    \leq C_f     .
-    \end{equation}
-\end{lemma}
-
-The key assumption here from Definition~\ref{def:model_setup}
-will be that the spatial scale over which local density affects birth rate
-is larger than the scale over which it affects establishment:
-concretely, that $\epsilon_{r}^2 + \frac{2\lambda}{\theta} < \epsilon_{\gamma}^2$,
-where $\lambda = \sup_x \sup_{y : \|y\| = 1} y^T \covq(x) y$
-is the largest eigenvalue of $\covq(x)$ across all $x$.
-In the simple case of $\meanq = 0$ and $\covq = \sigma^2 I$,
-the condition is simply that $\epsilon_r^2 + 2\sigma^2 / \theta < \epsilon_\gamma^2$.
-
-\begin{proof}[of Lemma \ref{lem:gamma_bound}]
-
-    Since we have assumed that there is a $K$ for which $m^2 \gamma(x, m) < K$
-    for all $x \in \IR^d$ and $m \ge 0$,
-    equation~\eqref{eqn:gamma_bound} will follow if we can show that
-    \begin{equation*}
-        \left| \theta 
-            \int_{\IR^n} 
-                \left\{
-                    f\left(y, \smooth{r}\eta(y)\right)
-                    -
-                    f\left(x, \smooth{r}\eta(x)\right)
-                \right\}
-            q_{\theta}(x,dy)
-        \right|
-        \leq
-        C_f \left( 1 + \smooth{\gamma} \eta(x)^2 \right) .
-    \end{equation*}
-    To do this, first note that 
-    \begin{align} \label{eqn:q_bound_split}
-    &
-        \left| \theta 
-            \int_{\IR^n} 
-                \left\{
-                    f\left(y, \smooth{r}\eta(y)\right)
-                    -
-                    f\left(x, \smooth{r}\eta(x)\right)
-                \right\}
-            q_{\theta}(x,dy)
-        \right|
-    \\ &\qquad {} \leq
-        \left| \theta 
-            \int_{\IR^n} 
-                \left\{
-                    f\left(y, \smooth{r}\eta(y)\right)
-                    -
-                    f\left(x, \smooth{r}\eta(y)\right)
-                \right\}
-            q_{\theta}(x,dy)
-        \right|
-    \\ &\qquad \qquad {}  +
-        \left| \theta 
-            \int_{\IR^n} 
-                \left\{
-                    f\left(x, \smooth{r}\eta(y)\right)
-                    -
-                    f\left(x, \smooth{r}\eta(x)\right)
-                \right\}
-            q_{\theta}(x,dy) 
-        \right| .
-    \end{align}
-
-    Since 
-    \begin{align*}
-        f\left(y, \smooth{r}\eta(y)\right) - f\left(x, \smooth{r}\eta(y)\right)
-        &=
-        \sum_i (y_i - x_i) \partial_{x_i} f \left(x, \smooth{r}\eta(y)\right) 
-        \\ &\qquad {}
-        +
-        \frac{1}{2} \sum_{ij} (y_i - x_i)(y_j - x_j)
-            \partial_{x_i x_j} f \left(z, \smooth{r}\eta(y)\right) 
-    \end{align*}
-    where $z = t x + (1-t) y$ for some $0 \le t \le 1$,
-    writing
-    $K_1 = \sup_{x,m} \max_i |\partial_{x_i} f(x, m)|$
-    and 
-    $K_2 = \sup_{x,m} \max_{i,j} |\partial_{x_i x_j} f(x, m)|$
-    for the bounds on the spatial derivatives of $f$,
-    the first term is bounded by
-    \begin{align*}
-        K_1 \left|
-            \theta \int_{\IR^d} \sum_i (y_i - x_i) q_\theta(x, dy)
-        \right|
-        +
-        K_2 \left|
-            \theta \int_{\IR^d} \sum_{ij} (y_i - x_i) (y_j - x_j)  q_\theta(x, dy)
-        \right| .
-    \end{align*}
-    This is bounded uniformly because
-    $q_\theta(x, dy)$ is the density of a Gaussian with mean $\meanq(x)/\theta$
-    and covariance $\covq(x)/\theta$, and both $\meanq(x)$ and $\covq(x)$
-    are bounded uniformly in $x$.
-
-    Similarly, 
-    \begin{align*}
-        f(x, \smooth{r}\eta(y)) - f(x, \smooth{r}\eta(x))
-        &=
-        (\smooth{r}\eta(y) - \smooth{r}\eta(x)) f'(x, \smooth{r}\eta(x))
-        + \frac{1}{2} (\smooth{r}\eta(y) - \smooth{r}\eta(x))^2 f''(x, m)
-    \end{align*}
-    for some $\smooth{r}\eta(x) \le m \le \smooth{r}\eta(y)$,
-    where $f'$ and $f''$ denote the first and second derivatives with respect to the second argument.
-    So,
-    the second term in~\eqref{eqn:q_bound_split} is bounded by
-    \begin{align*}
-        \|f'\|_\infty
-        \left|
-            \theta \int_{\IR^d}
-                (\smooth{r}\eta(y) - \smooth{r}\eta(x))
-            q_\theta(x, dy)
-        \right|
-        +
-        \|f''\|_\infty
-        \left|
-            \theta \int_{\IR^d}
-                (\smooth{r}\eta(y) - \smooth{r}\eta(x))^2
-            q_\theta(x, dy)
-        \right| .
-    \end{align*}
-    Therefore, it suffices to show that there is a $K < \infty$ such that
-    for all $\eta \in \measures$ and $x \in \IR^d$,
-    \begin{equation}
-        \label{eqn:first_moment_rho}
-        \left|\theta \int_{\IR^d}
-            ( \smooth{r} \eta(y)-\smooth{r} \eta(x) )
-        q_\theta(x,dy)\right|
-        \leq K \smooth{\gamma} \eta(x)
-    \end{equation}
-    and
-    \begin{equation}
-        \label{eqn:second_moment_rho}
-        \theta \int_{\IR^d}
-                \left( \smooth{r} \eta(y) - \smooth{r} \eta(x) \right)^2
-        q_\theta(x,dy)
-        \leq K \left(\smooth{\gamma}\eta(x) \right)^2 .
-    \end{equation}
-    Note that the right hand side of each is the average density
-    over a wider region (since $\epsilon_\gamma > \epsilon_r$).
-
-    First we prove \eqref{eqn:first_moment_rho}.
-    Recall that $\smooth{r} \eta(x) = \int p_{\epsilon^2_r}(x - w) \eta(dw)$,
-    where $p_t$ is the density of a Gaussian with mean 0 and variance $t$,
-    so that applying Fubini, \eqref{eqn:first_moment_rho} is
-    \begin{align*}
-        \left|
-        \int_{\IR^d}
-        \theta
-            \int_{\IR^d}
-                ( p_{\epsilon_r^2}(y - w) - p_{\epsilon_r^2}(x - w) )
-            q_\theta(x, dy)
-        \eta(dw)
-        \right| .
-    \end{align*}
-    Write $p_{s, x}(\cdot)$ for the density of a Gaussian
-    with mean $s \meanq(x)$ and covariance $\epsilon_r^2 I + s \covq(x)$,
-    so that $\int p_{\epsilon_r^2}(y - w) q_\theta(x, dy) = p_{1/\theta, x}(w-x)$.
-    It therefore suffices to show that for all $x$ and $w \in \IR^d$,
-    there exists $K$ such that
-    \begin{align} \label{eqn:goal1}
-        \left|
-        \theta
-            \int_{\IR^d}
-                ( p_{\epsilon_r^2}(y-w) - p_{\epsilon_r^2}(x-w) )
-            q_\theta(x, dy)
-        \right|
-        &=
-        \theta \left|
-            p_{1/\theta, x}(w-x) - p_{0, x}(w-x)
-        \right|
-        \le
-        K p_{\epsilon^2_\gamma}(w-x) .
-    \end{align}
-    However,
-    $\theta( p_{1/\theta, x}(z) - p_{0, x}(z) )
-    = \partial_s p_{s, x}(z)$ for some $0 \le s \le 1/\theta$.
-    Write $\Gamma(s,x) = \epsilon_r^2 I + s \covq(x)$,
-    so that
-    \begin{align*}
-        p_{s, x}(z)
-        &=
-        \frac{1}{\left(2 \pi |\Gamma(s,x)|\right)^{d/2}}
-        \exp\left(
-            -\frac{1}{2} (z - s\meanq(x))^T \Gamma(s,x)^{-1} (z - s\meanq(x))
-        \right) ,
-    \end{align*}
-    and note that if $\lambda_i$ are the eigenvalues of $\covq(x)$
-    then $|\Gamma(s, x)| = \prod_i (\epsilon_r^2 + s \lambda_i)$,
-    and
-    $\partial_s |\Gamma(s, x)| = \sum_i \lambda_i |\Gamma(s, x)| / (\epsilon_r^2 + s \lambda_i)$.
-    Therefore,
-    \begin{align*}
-        \partial_s p_{s, x}(z)
-        &=
-        \left(
-            \meanq(x)^T \Gamma(s,x)^{-1} (z - s \meanq)
-            +
-            (z - s \meanq(x))^T
-            \Gamma(s,x)^{-1} \covq(x) \Gamma(s,x)^{-1}
-            (z - s \meanq(x))
-        \right. \\ & \qquad \qquad \qquad \left. {}
-            -
-            \sum_i \frac{\lambda_i}{\epsilon_r^2 + s \lambda_i}
-        \right)
-        p_{s, x}(z) ,
-    \end{align*}
-    where $z^T$ is the transpose of $z$.
-    This implies that
-    \begin{align*}
-        \frac{
-        \theta
-            \int_{\IR^d}
-                ( p_{\epsilon_r^2}(y-w) - p_{\epsilon_r^2}(x-w) )
-            q_\theta(x, dy)
-        }{
-            p_{\epsilon^2_\gamma}(w-x) .
-        }
-        =
-        h(z) e^{k(z)},
-    \end{align*}
-    where $h(z)$ and $k(z)$ are quadratic polynomials in $z$
-    whose coefficients depend on $s$ and $x$ but are uniformly bounded for $s \ge 1$
-    and $x \in \IR^d$.
-    Therefore, \eqref{eqn:goal1} holds for some finite $K$
-    if and only if $k(z) < 0$ for all $z$ outside some bounded region.
-    This is
-    \begin{align*}
-        k(z)
-        =
-        \frac{1}{2\epsilon_\gamma^2} \|z\|^2
-        -\frac{1}{2} (z - s\meanq(x))^T \Gamma(s,x)^{-1} (z - s\meanq(x)) ,
-    \end{align*}
-    which is negative for all $z$ outside a bounded region.
-    Since $\inf_z z^T \Gamma(s,x)^{-1} z / \|z\|^2 = 1 / (s \lambda(x) + \epsilon_r^2)$,
-    where $\lambda(x) = \sup z^T \covq(x) z / \|z\|^2$ is the largest eigenvalue of $\covq(x)$,
-    equation~\eqref{eqn:first_moment_rho} follows from the assumption
-    that $\epsilon_r^2 + 2 \sup_x \lambda(x)/\theta < \epsilon_\gamma^2$.
-    (Note that we do not yet need the factor of 2.)
-
-    Next we prove equation~\eqref{eqn:second_moment_rho}, in a similar way.
-    Again applying Fubini,
-    \begin{align*}
-        &
-        \theta \int_{\IR^d}
-                \left( \smooth{r} \eta(y) - \smooth{r} \eta(x) \right)^2
-        q_\theta(x,dy)
-        \\ &\qquad
-        =
-        \int_{\IR^d} \int_{\IR^d}
-        \theta \int_{\IR^d}
-            ( p_{\epsilon_r^2}(y - w) - p_{\epsilon_r^2}(x - w) )
-            ( p_{\epsilon_r^2}(y - v) - p_{\epsilon_r^2}(x - v) )
-        q_\theta(x, dy)
-        \eta(dv) \eta(dw) ,
-    \end{align*}
-    and so as before, equation~\eqref{eqn:second_moment_rho} will follow if
-    the integrand is bounded by $K p_\gamma(x-w) p_\gamma(x - v)$.
-    % \begin{align*}
-    %     \theta \int_{\IR^d}
-    %         ( p_{\epsilon_r^2}(y - w) - p_{\epsilon_r^2}(x - w) )
-    %         ( p_{\epsilon_r^2}(y - v) - p_{\epsilon_r^2}(x - v) )
-    %     q_\theta(x, dy)
-    %     \le K p_\gamma(x-w) p_\gamma(x - v) .
-    % \end{align*}
-    Now, let $Y_1$, $Y_2$, and $Z$ be independent $d$-dimensional Gaussians with mean zero,
-    where $Y_1$ and $Y_2$ have covariance $\epsilon^2_r I$,
-    and $Z$ has covariance $\covq(x)$.
-    Write $p_{s,t,x}(\cdot, \cdot)$ for the joint density of
-    $Y_1 + \sqrt{s} Z + s \meanq(x)$ and $Y_2 + \sqrt{t} Z + t \meanq(x)$.
-    Then, observe that
-    \begin{align*}
-        &
-        \theta \int_{\IR^d}
-            ( p_{\epsilon_r^2}(y - w) - p_{\epsilon_r^2}(x - w) )
-            ( p_{\epsilon_r^2}(y - v) - p_{\epsilon_r^2}(x - v) )
-        q_\theta(x, dy)
-        \\ &\qquad
-        =
-        \theta \left(
-            p_{1/\theta, 1/\theta, x}(x-w, x-v)
-            - p_{0, 1/\theta, x}(x-w, x-v)
-        \right. \\ &\qquad \qquad \left. {}
-            - p_{1/\theta, 0, x}(x-w, x-v)
-            + p_{0, 0, x}(x-w, x-v)
-        \right) 
-        \\ &\qquad 
-        =
-            \partial_s p_{s, 1/\theta, x}(x-w, x-v)
-            - \partial_t p_{0, t, x}(x-w, x-v) ,
-    \end{align*}
-    for some $0 \le s, t \le 1/\theta$.
-    As before,
-    \begin{align*}
-        \frac{
-            \theta \int_{\IR^d}
-                ( p_{\epsilon_r^2}(y - w) - p_{\epsilon_r^2}(x - w) )
-                ( p_{\epsilon_r^2}(y - v) - p_{\epsilon_r^2}(x - v) )
-            q_\theta(x, dy)
-        }{
-            p_{\epsilon_\gamma^2}(x - w)
-            p_{\epsilon_\gamma^2}(x - v)
-        }
-        =
-        h(x-w, x-v) e^{ k(x-w, x-v) },
-    \end{align*}
-    where $h(z_1, z_2)$ is a polynomial with uniformly bounded coefficients and
-    \begin{align*}
-        k(z_1, z_2)
-        =
-        (\|z_1\|^2 + \|z_2\|^2)/(2 \epsilon_\gamma^2)
-            - \frac{1}{2} [z_1, z_2[^T \Gamma(s, t, x)^{-1} [z_1, z_2] ,
-    \end{align*}
-    where $[z_1, z_2]$ is the $\IR^{2d}$ vector formed by concatenating $z_1$ and $z_2$,
-    and $\Gamma(s, t, x)$ is the block matrix
-    \begin{align*}
-        \Gamma(s, t, x)
-        =
-        \left[
-        \begin{array}{cc}
-            \epsilon_r^2 I + s \covq(x) & \sqrt{st} \covq(x) \\
-            \sqrt{st} \covq(x) & \epsilon_r^2 I + t \covq(x) \\
-        \end{array}
-        \right] .
-    \end{align*}
-    If $\covq(x) u = a u$ for some $a \in \IR$,
-    then $[u \sqrt{s}, u \sqrt{t}]$ is an eigenvector of $\Gamma(s, t, x)$
-    with eigenvalue $\epsilon^2_r + (s+t) a$,
-    and $[u \sqrt{t}, - u \sqrt{s}]$ is an eigenvector of $\Gamma(s, t, x)$
-    with eigenvalue 0.
-    This implies the largest eigenvalue of $\Gamma(s, t, x)$
-    is equal to $\epsilon^2_r + (s+t) \lambda(x)$,
-    where $\lambda(x)$ is again the largest eigenvalue of $\covq(x)$.
-    Therefore, if $s + t \le 2 / \theta$,
-    \begin{align*}
-        &
-        (\|z_1\|^2 + \|z_2\|^2) / \epsilon^2_\gamma
-            - [z_1, z_2[^T \Gamma(s, t, x)^{-1} [z_1, z_2]
-        \\ &\qquad \le
-        (\|z_1\|^2 + \|z_2\|^2) \left(
-            \frac{1}{\epsilon^2_\gamma}
-            - \frac{1}{\epsilon^2_r +  2\lambda(x)/\theta}
-        \right) ,
-    \end{align*}
-    which is negative by assumption.
-    Therefore, there is a $K$ such that
-    \begin{align*}
-        \frac{ \left|
-            \partial_s p_{s, 1/\theta, x}(x-w, x-v)
-            - \partial_t p_{0, t, x}(x-w, x-v)
-        \right| }{
-            p_{\epsilon^2_\gamma}(x - w)
-            p_{\epsilon^2_\gamma}(x - v)
-        }
-        \le K
-    \end{align*}
-    for all $\theta > 1$ and all $x$, $v$, and $w \in \IR^d$,
-    proving equation~\eqref{eqn:second_moment_rho} and hence the lemma.
-\end{proof}
-
-\begin{lemma}
-    \label{lem:eta_f_bound}
-    Under the assumptions of Definition~\ref{def:model_setup},
-    if $\eta^{N}_0 \to \eta_0$ weakly as $N \to \infty$,
-    then for all $f \in C^2_0(\IR^d)$ there exists a $C_f < \infty$
-    such that
-    $$
-        \IE[\langle f, \eta^N_t \rangle]
-        \le
-        \IE[\langle f, \eta^N_0 \rangle]
-        e^{C_f t}
-    $$
-    for all $N > 0$.
-\end{lemma}
-
-\begin{proof}
-    Consider the semimartingale decomposition of Equation \eqref{eqn:eta_martingale},
-    \begin{align} \label{eqn:eta_f_mgale_decomp}
-        \langle f, \eta^N_t \rangle
-        &=
-        \langle f, \eta^N_0 \rangle
-        + \int_0^t \int_{\IR^d} \left\{
-            \gamma(x, \eta^N_s) B_f(x, \eta^N_s)
-            + f(x) F(x, \eta^N_s)
-            \right\} \eta^N_s(dx) ds
-        + M^N_t(f) ,
-    \end{align}
-    where $M^N_t(f)$ is a martingale and for the moment we are defining
-    \begin{equation*}
-        B_f(x, \eta) = \int_{\IR^d} \theta (f(y) r(y, \eta) - f(x) r(x, \eta)) q_\theta(x, dy) .
-    \end{equation*}
-    By Lemma~\ref{lem:gamma_bound} and the assumption that $F$ is bounded above,
-    $\gamma(x, \eta) B_f(x, \eta) + f(x) F(x, \eta) \le C_f$ for some $C_f$,
-    and so, taking expectations,
-    \begin{align*}
-        \IE\left[ \langle f, \eta^N_t \rangle \right]
-        &\le
-        \IE\left[ \langle f, \eta^N_0 \rangle \right]
-        + C_f \int_0^t \IE\left[ \langle f, \eta^N_s \rangle \right] dt .
-    \end{align*}
-    The bound then follows from Grownwall's inequality.
-\end{proof}
-
-With a bound on per-capita net growth rate in hand,
-bounds on the total population size follow easily.
-
-\begin{lemma}[Compact containment for the population process]
-    \label{lem:eta_compact_containment}
-    Under the assumptions of Definition~\ref{def:model_setup},
-    if $\theta/N \to \alpha$ and $\eta^{N}_0 \to \eta_0$ weakly as $N \to \infty$,
-    then for all $T>0$ and $N > 0$, there exists some constant $C_T$,
-    such that
-    \begin{align}
-        \label{eqn:eta_mass_bound}
-        \IE\left[
-            \sup_{0 \le t \le T}
-            \langle 1, \eta^{N}_t \rangle
-        \right]
-        \le C_T .
-    \end{align}
-    In particular, for any $\epsilon > 0$, there exists some $K_{\epsilon}>0$ such that
-    \begin{equation}
-    \limsup_{N \to \infty}
-        \IP \left\{ \sup_{s \in [0,T]}
-            \langle 1 ,\eta^{N}_{s}\rangle
-            > K_\epsilon \right\}
-        \leq \frac{C_T}{K_{\epsilon}}
-        < \epsilon .
-    \end{equation}
-\end{lemma}
-
-\begin{proof}
-    First note that by Lemma~\ref{lem:eta_f_bound},
-    $\IE[\langle 1, \eta^N_t \rangle] \le \IE[\langle 1, \eta^N_0 \rangle] e^{Ct}$
-    for some $C$.
-    Now, let $M^*_t(f) = \sup_{0 \le s \le t} M_t(f)$,
-    and as before $[M(f)]_t$ the quadratic variation of $M_t(f)$,
-    so that by the Burkholder-Davis-Gundy inequality, there is a $C'$ so that
-    \begin{align*}
-        \IE\left[ M^*_t(1) \right]
-        &\le
-        C' \IE\left[ \sqrt{[M(1)]_t} \right]
-        \\ &\le
-        C'\left( 1 + \IE\left[ [M(1)]_t \right] \right)
-        \\ &=
-        C'\left( 1 + \frac{\theta}{N} \IE\left[
-            \int_0^t
-            \int_{\IR^d} \left\{
-                \gamma(x, \eta^N_s)
-                \int_{\IR^d} r(y, \eta^N_s) q_\theta(x, dy)
-                + \mu(x, \eta^N_s)
-            \right\} \eta_s^N(dx)
-            dt
-            \right] \right)
-        \\ &=
-        C'\left( 1 + \IE\left[
-            \int_0^t
-            \int_{\IR^d} \left\{
-                \frac{2\theta}{N} \gamma(x, \eta^N_s) r(x, \eta^N_s)
-                + \frac{1}{N} B(x, \eta^N_s)
-            \right\} \eta_s^N(dx)
-            dt
-            \right] \right) .
-    \end{align*}
-    Since $\gamma(x, \eta) r(x, \eta)$ and $B(x, \eta)$ are bounded,
-    and $\theta/N \to \alpha < \infty$,
-    combining constants and again using Gronwall's inequality, we get that
-    \begin{align*}
-        \IE\left[ M^*_t(1) \right]
-        % &\le
-        % C'\left( 1 + \IE\left[
-        %     \int_0^t
-        %     \int_{\IR^d} \left\{ C'' \right\} \eta_s^N(dx)
-        %     dt
-        %     \right] \right) \\
-        &\le
-        C' + C'' \IE[ \langle 1, \eta_0^N \rangle ] e^{tC} .
-    \end{align*}
-    Taking suprema and expectations on both sides of equation~\eqref{eqn:eta_f_mgale_decomp},
-    then again using the fact that $\gamma(x, \eta) B_f(x, \eta) + F(x, \eta) \le C$,
-    \begin{align*}
-        \IE\left[\sup_{0 \le s \le t} \langle 1, \eta^N_s \rangle \right]
-        &\le
-        \IE[\langle 1, \eta^N_0 \rangle]
-        + \IE\left[
-            \sup_{0 \le s \le t}
-            \int_0^t \int_{\IR^d} \left\{
-                \gamma(x, \eta^N_s)
-                B_f(x, \eta^N_s)
-                + F(x, \eta^N_s)
-            \right\} \eta^N_s(dx) ds
-        \right]
-        + \IE[M^*_t(1)] 
-        \\
-        &\le
-        \IE[\langle 1, \eta^N_0 \rangle]
-        + C \IE\left[
-            \int_0^t \sup_{0 \le s \le t} \langle 1, \eta^N_s \rangle ds
-        \right]
-        + C' + C'' \IE[ \langle 1, \eta_0^N \rangle ] e^{tC} .
-    \end{align*}
-    Once again applying Gronwall's inequality,
-    \begin{align*}
-        \IE\left[\sup_{0 \le s \le t} \langle 1, \eta^N_s \rangle \right]
-        &\le
-        C'' 
-        \left(\IE[\langle 1, \eta^N_0 \rangle] + C'\right)
-        \IE[ \langle 1, \eta_0^N \rangle ] e^{2tC} .
-    \end{align*}
-    For any $T$,
-    the inequality on the right is bounded above by a constant $C(T)$ independent of $N$.
-    As a result, for any $K > 0$,
-    \begin{equation*}
-    \limsup_{N \to \infty}
-        \IP\left[ \sup_{0 \le s \le T} \langle 1, \eta^{N}_{s} \rangle \geq K \right]
-        \leq
-        \frac{C(T)}{K}.
-    \end{equation*}
-\end{proof}
-
-\begin{lemma}
-    \label{lem:tightness_for_F}
-    Fix a $\sigma > 0$ and a continuous function $f \in C(\IR^d, [0, \infty))$
-    such that $\sup_x f(x, m)$ is finite for each $m$.
-    Under the assumptions of Definition~\ref{def:model_setup},
-    and if $\eta^N_0$ converges in distribution,
-    for all $\epsilon > 0$ and $T \ge 0$
-    there exists a $K_f$ such that for all $N > 0$,
-    \begin{align*}
-        \IP\left\{
-            \sup_{0 \le s \le T}
-            \int_{\IR^d}
-            f(x, p_{\sigma^2}*\eta^N_s(x))
-            \eta^N_s(dx)
-            > K_f
-        \right\}
-        \le \epsilon ,
-    \end{align*}
-    where recall that $p_{\sigma^2}*\eta(\cdot)$ denotes convolution of the Gaussian kernel
-    with mean 0 and variance $\sigma^2 I$ with the measure $\eta$.
-\end{lemma}
-
-\begin{proof}[of Lemma~\ref{lem:tightness_for_F}]
-    Let $\bar f(m) = \sup_x \sup_{k \le m} f(x, k)$, which is finite by assumption.
-    Since $p_{\sigma^2}*\eta(x) \le \langle 1, \eta \rangle / (2 \pi \sigma^2)^{d/2}$,
-    we have that
-    $$
-        \sup_{0 \le s \le T} \sup_{x \in \IR^d} f(x, p_{\sigma^2}*\eta^N_s(x))
-        \le
-        \bar f( \sup_{0 \le s \le T} \langle 1, \eta^N_s \rangle  / (2 \pi \sigma^2)^{d/2} ) .
-    $$
-    This implies that if $0 \le s \le T$ then
-    $$
-            \int_{\IR^d} f(x, p_{\sigma^2}*\eta^N_s(x)) \eta^N_s(dx)
-            \le
-            \bar f(\sup_{0 \le s \le T} \langle 1, \eta^N_s \rangle)
-            \sup_{0 \le s \le T} \langle 1, \eta^N_s \rangle .
-    $$
-    Now, if we let $g(m) = m \bar f(m/ (2 \pi \sigma^2)^{d/2})$,
-    which again is finite and nondecreasing,
-    then the lemma follows by choosing $K_f = g^{-1}(K_\epsilon)$
-    in Lemma~\ref{lem:eta_compact_containment}.
-\end{proof}
-
-Now that we have a compact containment condition for $\eta^N$,
-we need tightness of the one-dimensional distributions.
-
-\begin{lemma}[Tightness of $(\langle f, \eta^{N}_t \rangle )_{t>0}$]
-    \label{lem:eta_projections_tightness}
-For all $f \in C^{2}_{0}(\IR^d)$, 
-the collection of processes
-$(\langle f, \eta^{N}_t \rangle)_{t \geq 0}$
-for $N = 1, 2, \ldots$ is tight as a sequence of c\`adl\`ag, real-valued processes.
-\end{lemma}
-
-\begin{proof}
-We apply the Aldous-Rebolledo criterion \citep{rebolledo:1980}, which 
-applied to the semimartingale representation of $\langle f, \eta^N_t\rangle$
-of equation~\eqref{eqn:eta_f_mgale_decomp},
-says that it suffices to show that 
-$\{\langle f, \eta^N_t \rangle\}_{N \ge 1}$ is tight for each $t$, and that
-for any sequence of stopping times $\tau_N$ bounded by $T$,
-and for each $\epsilon > 0$, there exists $\delta > 0$ and $N_0 > 0$ such that 
-\begin{gather}
-        \label{eqn:eta_projections_goal1}
-    \sup_{N > N_0}
-    \sup_{t \in [0, \delta]}
-    \IP\left\{\left|
-            \int_\tau^{\tau + t}
-            \int_{\IR^d}
-            \left\{
-                \gamma(x, \eta^N_s) B_f(x, \eta^N_s)
-                + f(x) F(x, \eta^N_s)
-            \right\} 
-            \eta^N_s(dx)
-            ds
-        \right|> \epsilon \right\}
-        < \epsilon ,
-    \\ \text{and} \qquad
-        \label{eqn:eta_projections_goal2}
-    \sup_{N > N_0}
-    \sup_{t \in [0, \delta]}
-    \IP\left\{\big|
-        [M^{N}(f)]_{\tau + t} 
-            - [M^{N}(f)]_\tau \big|
-        > \epsilon
-    \right\}
-    < \epsilon.
-\end{gather}
-Tightness of $\langle f, \eta^N_t\rangle$ for fixed $t$
-follows from Lemma~\ref{lem:eta_f_bound} and Markov's inequality,
-so we focus on the remaining conditions.
-
-Next, note that for $0 \le t \le \delta$,
-if we choose $K_f$ as in Lemma~\ref{lem:tightness_for_F}
-and $C_f$ as in Lemma~\ref{lem:gamma_bound},
-then
-\begin{align*}
-    &
-    \IP\left\{
-        \int_\tau^{\tau + t}
-        \int_{\IR^d}
-        \left\{
-            \gamma(x, \eta^N_s) B_f(x, \eta^N_s)
-            + f(x) F(x, \eta^N_s)
-        \right\} 
-        \eta^N_s(dx)
-        ds
-        > (K_f + C_f) \delta
-    \right\}
-    \\ & \qquad \le
-    \IP\left\{
-        \sup_{0 \le s \le \delta}
-        \int_{\IR^d} \left\{
-            \gamma(x, \eta^N_s) B_f(x, \eta^N_s)
-            + f(x) F(x, \eta^N_s)
-        \right\} \eta^N_s(dx)
-        >
-        K_f + C_f
-    \right\}
-    < \epsilon .
-\end{align*}
-Therefore, setting $\delta = \epsilon / (K_f + C_f)$
-obtains \eqref{eqn:eta_projections_goal1}.
-
-Similarly,
-\begin{align*}
-    &
-    [M^{N}(f)]_{\tau + t} 
-        - [M^{N}(f)]_\tau \big|
-    \\ & \qquad =
-    \int_{\tau}^{\tau + t}
-        \frac{\theta}{N}
-        \int_{\IR^d}
-        \left\{
-            \gamma(x, \eta^N_s)
-            \int_{\IR^d} f^2(y) r(y, \eta^N_s) q_\theta(x, dy)
-            +
-            \mu(x, \eta^N_s) f^2(x)
-        \right\}
-        \eta^N_s(dx)
-    ds .
-    \\ & \qquad =
-    \int_{\tau}^{\tau + t}
-        \frac{\theta}{N}
-        \int_{\IR^d}
-        \left\{
-            \gamma(x, \eta^N_s)
-            \left(
-                2 f^2(x) r(x, \eta^N_s)
-                +
-                B_{f^2}(x, \eta^N_s)
-            \right)
-            +
-            f^2(x) F(x, \eta^N_s) / \theta
-        \right\}
-        \eta^N_s(dx)
-    ds ,
-\end{align*}
-and so using the fact that $\theta/N \to \alpha < \infty$,
-an argument similar to 
-that for \eqref{eqn:eta_projections_goal1}.
-also obtains \eqref{eqn:eta_projections_goal2}.
-
-\end{proof}
-
-% % % % % % % % %
-\begin{theorem}[Tightness of $(\eta^{N}_t)_{t \geq 0}$]
-    The collection of measure-valued processes 
-    $\{(\eta^{N}_t)_{t \geq 0}: N > 0\}$
-    is tight in $\mathcal{D}_{[0,\infty)}(\measures)$.
-\end{theorem}
-
-\begin{proof}
-    Theorem 3.9.1~in \cite{EK},
-    says that if the collection of $E$-valued processes
-    satisfies a compact containment condition
-    (for any $\epsilon > 0$ and $T>0$, there is a compact set
-    such that the processes stay within that set up to time $T$ with probability at least $1-\epsilon$),
-    then the collection is relatively compact
-    if and only if
-    $\{(f(\eta^{N}_t))_{t \geq 0}: N > 0\}$ is relatively compact
-    for all $f$ in a dense subset of $C_0(E)$
-    under the topology of uniform convergence in compact sets.
-
-    First of all,
-    the set of measures $\{ \mu: \langle 1, \mu \rangle \leq K \} $ is compact in $\cmeasures$,
-    so Lemma \ref{lem:eta_compact_containment}
-    shows that our processes satisfy a compact containment condition.
-    Secondly, Lemma \ref{lem:eta_projections_tightness}
-    shows that the real-valued processes $\langle f, \eta^{N}_t \rangle$
-    are relatively compact for all $f \in \mathcal{C}^{2}_{0}(\overline{\IR^d})$.
-    Since by the Stone-Weierstrass theorem,
-    the algebra of finite sums and products of terms of this form
-    is dense in the space of bounded continuous functions on $\cmeasures$,
-    we have relative compactness in $\mathcal{D}_{[0,\infty)}(\cmeasures)$.
-    Finally,
-    since each measure $\eta^{N}_t$ is concentrated in $\IR^d$,
-    any limit point must in fact be in $\measures$,
-    and so we have 
-    tightness in $\mathcal{D}_{[0,\infty)}(\measures)$.
-\end{proof}
-
-% % % % % % % % % % % % %
-\subsubsection{Convergence of generators}
-    \label{sec:population_generators_proofs}
-
-Before we prove convergence, we define our limit $(\eta^{\infty}(t))_{t>0}$ as a solution to a Martingale Problem with generator $\Pgen^{\infty}$.
-
-\begin{definition}
-    \label{def: MP definition of limit}
-Let $F \in \mathcal{C}^{2}(\IR)$ and $f \in \mathcal{C}_{0}(\IR^d)$.
-We define $\Pgen$ to be a generator
-acting on test functions of the form
-$F_f(\eta):=F (\langle f, \eta \rangle)$
-such that 
-\begin{equation}
-    \label{eq: Limit Generator Definition}
-\begin{aligned}
-\Pgen^{\infty} F_f(\eta):=& F'(\langle f, \eta \rangle)
-                   \times \left\{
-                   \big\langle
-                        \gamma(x, \smooth{\gamma} \eta(x))
-                            \mathcal{B}\left(
-                            f(\cdot) r(\cdot, \smooth{r} \eta(\cdot))
-                            \right)(x)
-                    +
-                    f(x)
-                        F(x, \smooth{F} \eta(x)),
-                        \eta(dx)
-                    \big\rangle
-                   \right\}\\
-                &+ \frac{\alpha}{2} F''(\langle f, \eta \rangle)
-                  \times \left\{
-                  \big\langle
-                    \left(\gamma\left( x, \eta \right)
-                    r\left(x,\eta \right)
-                    +\mu\left(x,\eta \right)
-                    \right)
-                    f^2(x),
-                    \eta (dx)
-                    \big\rangle 
-                  \right\}.
-\end{aligned}    
-\end{equation}
-We define $(\eta^{\infty}(t))_{t \geq 0}$ to be the solution to the Martingale Problem $(\Pgen^{\infty}, \eta_0)$, i.e. 
-for all $F \in \mathcal{C}^{2}(\IR)$
-and $f \in \mathcal{C}_{0}(\IR^d)$,
-$$M_t:=F_f(\eta^{\infty}_t)-F_f(\eta_0)
--\int_{0}^{t}\Pgen^{\infty}F_f(\eta^{\infty}_s)ds$$
-is a martingale, with initial condition distributed as a Poisson measure with mean measure $\eta_0$.
-\end{definition}
-
-In a similar manner,
-we may also define our pre-limit
-$(\eta^{N}(t))_{t>0}$ as a solution
-to a Martingale Problem
-with generator $\Pgen^{N}$.
-
-\begin{definition}
-    \label{def: MP definition of pre-limit}
-Let $F \in \mathcal{C}^{2}(\IR)$ and $f \in \mathcal{C}_{0}(\IR^d)$.
-We define $\Pgen^N$ to be a generator
-acting on test functions of the form
-$F_f(\eta):=F (\langle f, \eta \rangle)$
-such that 
-\begin{equation}
-\begin{aligned}
-\Pgen^{N} F_f(\eta):=& \int_{\IR^d} \theta\gamma(x, \eta) \left\{\int_{\IR^d} \left\{F(\langle f, \eta \rangle + f(y)/N )-F(\langle f, \eta \rangle )\right\}r(y, \eta)q_{\theta}(x,dy)\right\}N\eta(dx)\\
-&+\int_{\IR^d} \theta \mu(x, \eta) \left\{F(\langle f, \eta \rangle - f(x)/N )-F(\langle f, \eta \rangle )\right\}N\eta(dx).
-\end{aligned}    
-\end{equation}
-In this case, our pre-limit model $(\eta^{N}(t))_{t \geq 0}$ is the solution to the Martingale Problem $(\Pgen^{N}, \eta_0)$, i.e. 
-for all $F \in \mathcal{C}^{2}(\IR)$
-and $f \in \mathcal{C}_{0}(\IR^d)$,
-$$M_t:=F_f(\eta^{N}_t)-F_f(\eta_0)
--\int_{0}^{t}\Pgen^{N}F_f(\eta^{N}_s)ds$$
-is a martingale, and the initial condition is distributed as a Poisson measure with mean measure $\eta_0$.
-\end{definition}
-
-\begin{remark}
-Taking $F(x)=x$ and $F(x)=x^2$, we can recover Equation \eqref{eqn:limiting_mgale_problem} and \eqref{eqn:limiting_mgale_variation} for the limit.
-Similarly, we can recover
-Definition \ref{defn:mgale_construction},
-an equivalent characterisation
-of our pre-limit model.
-\end{remark}
-
-\begin{lemma}[Identifying the limit as a solution to the martingale problem]
-    \label{lem:limit_mgale}
-    \comment{Here we need to check that the martingale property is preserved in the limit.}
-As $N \to \infty$,
-$(\eta^{N}_t)_{t \geq 0}$ converges in $\mathcal{D}_{[0,\infty)}(\mathcal{M}_f(\IR^d))$
-to $(\eta^{N}(t))_{t \geq 0}$.
-\end{lemma}
-\begin{proof}
-We use Theorem 4.8.10 in \cite{EK}.
-First of all, the set of functions
-$\{F_f(\eta):= F(\langle f, \eta \rangle ),~
-F \in \mathcal{C}^{2}(\IR), ~
-f \in \mathcal{C}_{0}(\IR^d)\}$
-is a dense and convergence-determining 
-subset of functions in $\mathcal{M}_f(\IR^d)$.
-Therefore, it suffices to show that for any $t>0$,
-\begin{equation}
-    \label{eq: Convergence Condition}
-\lim_{N \to \infty}
-\mathbb{E}\left[
-\left(
-F_f(\eta^{N}_{t+\tau})-F_f(\eta^{N}_t)
--\int_{t}^{t+\tau}\Pgen^{\infty}F_f(\eta^{N}_s)ds
-\right)
-\prod_{i=1}^{k}\langle h_i,\eta^{N}_{t_i} \rangle
-\right]=0
-\end{equation}
-for all $k\geq 0$, $0\leq t_1<t_2<...,t_k \leq t < t+\tau$,
-and $h_1,...,h_k \in \mathcal{C}_{0}(\IR^d)$.
-
-To prove this,
-we make use of the Martingale Problem characterisation
-of $(\eta^{N}_t)_{t \geq 0}$.
-From Definition \ref{def: MP definition of pre-limit},
-we can apply Tower Law
-and obtain that
-\begin{equation}
-    \label{eq: Prelimit MP Application}
-\lim_{N \to \infty}
-\mathbb{E}\left[
-\left(
-F_f(\eta^{N}_{t+\tau})-F_f(\eta^{N}_t)
--\int_{t}^{t+\tau}\Pgen^{N}F_f(\eta^{N}_s)ds
-\right)
-\prod_{i=1}^{k}\langle h_i,\eta^{N}_{t_i} \rangle
-\right]=0
-\end{equation}
-for all $k\geq 0$, $0\leq t_1<t_2<...,t_k \leq t < t+\tau$,
-and $h_1,...,h_k \in \mathcal{C}_{0}(\IR^d)$.
-
-Therefore, it suffices to show that 
-\begin{equation}
-    \label{eq: Convergence of Spatial Generator}
-\lim_{N \to \infty}
-\mathbb{E}\left[
-\int_{t}^{t+\tau}
-\left|
-\Pgen^{N}F_f(\eta^{N}_s)
--\Pgen^{\infty}F_f(\eta^{N}_s)
-\right|
-ds
-\times 
-\prod_{i=1}^{k}\langle h_i,\eta^{N}_{t_i} \rangle
-\right]=0
-\end{equation}
-We apply Taylor Expansion
-around the term $F(\langle f, \eta \rangle )$
-up to third order.
-This gives
-\begin{equation}
-    \label{eq: Taylor Expansion calculations i}
-\begin{aligned}
-&F(\langle f, \eta \rangle + f(y)/N )-F(\langle f, \eta \rangle )\\
-=& F'(\langle f, \eta \rangle ) \frac{f(y)}{N}
-+\frac{1}{2}F''(\langle f, \eta \rangle ) \frac{f^2(y)}{N^2}
-+\frac{1}{6}F'''(w ) \frac{f^3(y)}{N^3}
-\end{aligned}
-\end{equation}
-for some $w \in [\langle f, \eta \rangle, \langle f, \eta \rangle+ ||f||/N]$.
-Similarly,
-\begin{equation}
-    \label{eq: Taylor Expansion calculations ii}
-\begin{aligned}
-&F(\langle f, \eta \rangle - f(x)/N )-F(\langle f, \eta \rangle )\\
-=& - F'(\langle f, \eta \rangle ) \frac{f(x)}{N}
-+\frac{1}{2}F''(\langle f, \eta \rangle ) \frac{f^2(x)}{N^2}
--\frac{1}{6}F'''(v ) \frac{f^3(x)}{N^3}
-\end{aligned}
-\end{equation}
-for some $v \in [\langle f, \eta \rangle - ||f||/N, \langle f, \eta \rangle ]$.
-
-We may now rewrite $\mathcal{P}^NF(\langle f, \eta \rangle)$ as 
-\small
-\begin{equation} 
-    \label{eq: Pre-Limit Generator Expanded}
-\begin{aligned}
-\Pgen^{N} F_f(\eta):=& F'(\langle f, \eta \rangle)\int_{\IR^d}  \theta\left\{\int_{\IR^d} \left\{f(y)\gamma(x, \eta) r(y,\eta) -f(x)\mu(x, \eta)\right\}q_{\theta}(x,dy)\right\}\eta(dx)\\
-&+\frac{1}{2}\frac{\theta}{N}F''(\langle f, \eta \rangle)\int_{\IR^d} 
- \left\{\gamma(x, \eta)\int_{\IR^d} \left\{f^2(y) r(y,\eta) \right\}q_{\theta}(x,dy)+f^2(x)\mu(x, \eta)\right\}\eta(dx)\\
-&+\frac{1}{6}\frac{\theta}{N^2}\int_{\IR^d}\left\{ 
-F'''(w) \left\{\gamma(x, \eta)\int_{\IR^d} f^3(y) r(y,\eta) q_{\theta}(x,dy)\right\}-F'''(v)f^3(x)\mu(x, \eta)\right\}\eta(dx)
-\end{aligned}    
-\end{equation}
-\normalsize
-for some $w,v \in [\langle f,\eta \rangle - ||f||/N, \langle f,\eta \rangle + ||f||/N]$.
-
-As $N\to \infty$, 
-$\theta/N \to \alpha$, 
-$\theta/N^2 \to 0$,
-and 
-$$\int_{\IR^d} f^m(y) r(y,\eta) q_{\theta}(x,dy) \to f^m(x)r(x, \eta)$$
-for $m=2,3$,
-the third term in Equation \eqref{eq: Pre-Limit Generator Expanded} vanishes
-while the second term converges to
-that of Equation \eqref{eq: Limit Generator Definition}.
-
-Finally, by Equation \eqref{mean measure},
-\eqref{eqn:rewritten mean measure}, \eqref{eqn:near_critical} and
-\eqref{limit of mean measure equation},
-we have 
-\begin{multline}
- \theta\left\{\int_{\IR^d} \left\{f(y)\gamma(x, \eta) r(y,\eta) -f(x)\mu(x, \eta)\right\}q_{\theta}(x,dy)\right\}
- \\
-\to \gamma(x, \eta)                           \mathcal{B}\left(
-                            f(\cdot) r(\cdot, \eta)
-                            \right)(x)
-                    +
-                    f(x)
-                        F(x, \eta),
-\end{multline}
-so comparing terms we have
-\begin{equation}
-\lim_{N\to \infty} |\mathcal{P}^{N}F\langle f, \eta \rangle - \mathcal{P}^{\infty}F\langle f, \eta \rangle| \to 0,   
-\end{equation}
-and so by Dominated Convergence Theorem,
-we establish Equation 
-\eqref{eq: Convergence of Spatial Generator}
-which concludes our proof.
-\end{proof}
-
-% % % % % % % % % % % % %
-\subsection{Convergence of the nonlocal equation to the local equation}
-
-\comment{... for the cases in which we know this: FKPP-type and PME.
-This then shows that we can take the local, deterministic limit
-by taking $\theta, N \to \infty$ first, and then $\epsilon \to 0$ after.
-}
-
-In this section we prove Proposition~\ref{prop:nonlocal_pde_limits}.
-
-\subsubsection{Fisher-KPP-type}
-
-\comment{Insert TwoStepConvergenceV3 with Alison's markups incorporated here.}
-
-\subsubsection{Porous Medium Equation}
-
-\plr{This is from pme.tex.}
-
-We are concerned with non-negative solutions to the equation
-\begin{equation}
-\label{mollified equation}
-\frac{\partial u^\epsilon}{\partial t}=
-%\frac{\partial^2}{\partial x^2}
-\Delta\left(u^\epsilon \cdot u^\epsilon *\zeta_\epsilon\right)
-+u^\epsilon\left(1-u^\epsilon*\zeta_\epsilon\right);
-\end{equation}
-where $*$ denotes convolution and we define
-a (non-negative) mollifier by
-$\zeta_\epsilon=\frac{1}{\epsilon}\zeta(\cdot/\epsilon)$, where $\zeta$
-satisfies
-$\zeta\in\cal{S}(\IR)$, $\int\zeta(x)dx=1$. Indeed, for convenience, in
-what follows we shall suppose that $\zeta =\rho*\check{\rho}$ where
-$\check{\rho}(z)=\rho(-z)$ and $\rho$ has
-compact support, although that
-is certainly stronger than we need.
-In particular, we should like to prove that as $\epsilon\to 0$ we have
-convergence to the solution to the porous medium equation with
-logistic growth:
-\begin{equation}
-\label{PME}
-\frac{\partial u}{\partial t}=
-%\frac{\partial^2}{\partial x^2}
-\Delta\left(u^2\right)
-+u\left(1-u\right).
-\end{equation}
-
-We work on $[0,T]\times \IT_K$ where $\IT_K$ is the one-dimensional
-torus of size $K$, and $T,K>0$ are fixed but arbitrary.
-
-\comment{rephrase/shorten this:}
-
-\begin{remark}
-By taking a sequence $K_n\to\infty$, and doing a bit of work,
-we can presumably then recover the result
-we need for, e.g., a population expanding its range from a compact
-set containing the origin (for which we know the solution to the PME
-converges to two travelling waves, travelling in opposite directions
-\cite{kamin/rosenau:2004}). Such waves have bounded support, even when
-we consider the equation on
-the whole real line, and travel at a fixed speed, so don't feel the boundedness
-of the torus,
-so this should be straightforward. The challenge will be to control the
-mass of the approximating functions that falls beyond that wavefront,
-since they themselves will have full support and so arguably `feel' that they
-are on the torus.
-It is not clear that it is worth doing the details for this paper - this is
-meant as an example.
-\end{remark}
-
-\begin{notation}
-
-Whenever we integrate with respect to $x$, this is implicitly over the
-whole torus $\IT_K$.
-
-We use $\rightharpoonup$ to denote weak convergence in the sense of analysts;
-that is, $u^\epsilon\rightharpoonup u$ in $L^1$ means $\int u^\epsilon v \dif x
-\rightarrow\int uv\dif x$ for all $v\in L^\infty$.
-
-We write $L_t^2(H^1)$ for functions for which the $H^1$ norm in
-space is in $L^2$ with respect to time, i.e.
-$$\int_0^T\int \left\{u(t,x)^2+\left(\frac{d}{dx} u(t,x)\right)^2\right\} \dif x \dif t <\infty,$$
-and $C_t(L^1)$
-will denote functions for which the $L^1$ norm in space is continuous in time.
-\end{notation}
-
-\begin{proposition}
-Suppose that $u_0^\epsilon\in L^1(\IT_K)$, $u_0^\epsilon\geq 0$, and
-$\sup_\epsilon\int u_0^\epsilon|\log u_0^\epsilon|dx<\infty$ with
-$u_0^\epsilon\rightharpoonup u_0^\epsilon$ as $\epsilon\to 0$. Then
-writing $u^\epsilon$ for the solution to~(\ref{mollified equation})
-on $[0,T]\times \IT_K$ with
-initial condition $u_0^\epsilon$,
-$u^\epsilon\rightharpoonup u$ as $\epsilon\to 0$ where
-$u\in L_t^2(H^1)\cap C_t(L^1)$, $\int u|\log u| dx<\infty$, and
-$u$ solves~(\ref{PME}) on $[0,T]\times \IT_K$. Moreover, strong convergence
-of the initial conditions implies strong convergence of the solutions.
-\end{proposition}
-%\noindent
-%{\bf Proof}
-
-\begin{proof}
-    \comment{Check where we use compactness of the mollifier.}
-
-Our proof owes a lot to~\cite{lions/mas-gallic:2001}.
-First observe that
-\begin{multline*}
-\int u^\epsilon\cdot u^\epsilon*\zeta_\epsilon\dif x
-= \int\int\int u^\epsilon(x)u^\epsilon(x-y)\rho_\epsilon(y-z)
-\check{\rho}_\epsilon(z)\dif z\dif y\dif x
-\\
-=
-\int\int\int u^\epsilon(\tilde{x}-\tilde{z})
-u^\epsilon(\tilde{x}-\tilde{y})
-\rho_\epsilon(\tilde{y})
-\rho_\epsilon(\tilde{z})\dif \tilde{z}\dif \tilde{y}\dif \tilde{x}
-=\int\left(u^\epsilon*\rho_\epsilon\right(x))^2\dif x,
-\end{multline*}
-where we have set $\tilde{x}=x-z$, $\tilde{y}=y-z$, $\tilde{z}=-z$.
-
-Now note that
-$$\frac{d}{dt}\int u^\epsilon (t,x) \dif x=\int \Delta (u^\epsilon*\zeta_\epsilon)\dif x
-+\int u^\epsilon(1-u^\epsilon*\zeta_\epsilon)\dif x= \int u^\epsilon \dif x
--\int (u^\epsilon*\rho)^2 \dif x.$$
-Thus $\int u^\epsilon(t,x)\dif x$ is uniformly bounded above in $t$
-and $\epsilon$ on $[0,T]$. Note that this also then gives a uniform
-bound on the rate of change of $\int u^\epsilon (t,x) \dif x$, and since
-we are working on $[0,T]$ this will be enough to give continuity in time of the
-$L^1$ norm of the limit
-when we pass to a convergent subsequence.
-
-Now consider
-\begin{eqnarray*}
-\frac{d}{dt}\int u^\epsilon\log u^\epsilon \dif x &=&
-\int (1+\log u^\epsilon)\left[\Delta (u^\epsilon\cdot
-u^\epsilon*\zeta_\epsilon)+u^\epsilon(1-u^\epsilon*\zeta_\epsilon)\right]
-\dif x
-\\
-&=&
-\int (1+\log u^\epsilon)\left[\nabla\left(u^\epsilon\cdot
-\nabla(u^\epsilon*\zeta_\epsilon)+
-\nabla u^\epsilon\cdot u^\epsilon*\zeta_\epsilon\right)
-+u^\epsilon(1-u^\epsilon*\zeta_\epsilon)\right] \dif x
-\\
-&=&
-\int \left[-\frac{\nabla u^\epsilon}{u^\epsilon}
-\left(u^\epsilon\cdot \nabla(u^\epsilon*\zeta_\epsilon)
-+\nabla u^\epsilon\cdot u^\epsilon*\zeta_\epsilon\right)+
-(1+\log u^\epsilon)u^\epsilon(1-u^\epsilon*\zeta_\epsilon)\right]\dif x
-\\
-&=&
--\int \left(\nabla (u^\epsilon*\rho_\epsilon)\right)^2 \dif x
--\int (\nabla u^\epsilon)^2\frac{u^\epsilon*\zeta_\epsilon}{u^\epsilon} \dif x
-\\
-&&+\int
-\left[u^\epsilon+u^\epsilon\log u^\epsilon(1-u^\epsilon*\zeta_\epsilon)
--u^\epsilon\cdot u^\epsilon*\zeta_\epsilon\right]\dif x\\
-&=&
--\int \left(\nabla (u^\epsilon*\rho_\epsilon)\right)^2 \dif x
--\int (\nabla u^\epsilon)^2\frac{u^\epsilon*\zeta_\epsilon}{u^\epsilon} \dif x
--\int (u^\epsilon*\rho_\epsilon)^2\dif x
-\\
-&&+\int
-\left[u^\epsilon+u^\epsilon\log u^\epsilon(1-u^\epsilon*\zeta_\epsilon)
-%-u^\epsilon\cdot u^\epsilon*\zeta_\epsilon
-\right]\dif x .
-\end{eqnarray*}
-The first three terms are negative; and we already
-saw that the $L^1$ norm
-of $u^\epsilon$ is uniformly bounded.
-Moreover, since $u^\epsilon\log u^\epsilon$ is uniformly bounded below,
-$$-\int u^\epsilon \log u^\epsilon \cdot u^\epsilon*\zeta_\epsilon \dif x
-\leq C\int u^\epsilon*\zeta_\epsilon \dif x=\int u^\epsilon \dif x.$$
-From this we see immediately that $\int u^\epsilon \log u^\epsilon \dif x$
-is uniformly bounded
-above in $\epsilon$ and $t\in [0,T]$. Moreover,
-since we are working on the bounded space $\IT_K$, the lower bound
-on $u^\epsilon\log u^\epsilon$ also allows us to
-bound $\int u^\epsilon\log u^\epsilon \dif x$ uniformly
-below, from which we deduce that
-we have a uniform bound on $\int u^\epsilon|\log u^\epsilon| \dif x$.
-This in turn means that both
-$\int_0^t (u^\epsilon*\rho_\epsilon)^2 \dif x$ and
-$\int_0^t \big(\nabla (u^\epsilon*\rho_\epsilon)\big)^2 \dif x$
-are uniformly bounded in
-$\epsilon$ and $t\in [0,T]$.
-Now observe that
-\begin{equation}
-\label{total equation}
-\int\Delta\left((u^\epsilon*\zeta_\epsilon)u^\epsilon\right)\phi \dif x =
-\int \nabla(u^\epsilon*\zeta_\epsilon)\cdot
-u^\epsilon\cdot\nabla\phi \dif x +\int u^\epsilon*\zeta_\epsilon
-\cdot\nabla u^\epsilon
-\cdot \nabla\phi \dif x.
-\end{equation}
-For the first term
-\begin{eqnarray}
-\nonumber
-\int \nabla(u^\epsilon*\zeta_\epsilon)\cdot u^\epsilon\cdot\nabla\phi \dif x
-&=&
-\int\int\int\nabla u^\epsilon(x-y)\rho_\epsilon(y-z)\check{\rho}_\epsilon(z)
-u^\epsilon(x)\nabla\phi(x)\dif z \dif y \dif x
-\\
-\nonumber
-&=&
-\int\int\int\nabla u^\epsilon(\tilde{x}-\tilde{y})\rho_\epsilon(\tilde{y})
-\rho_\epsilon(\tilde{z})u^\epsilon(\tilde{x}-\tilde{z})
-\nabla\phi(\tilde{x}-\tilde{z})\dif \tilde{z}\dif \tilde{y} \dif \tilde{x}
-\\
-\nonumber
-&=&\int(\nabla u^\epsilon*\rho_\epsilon)\cdot
-\left((u^\epsilon\nabla\phi)*\rho_\epsilon\right)
-\dif x\\
-\nonumber
-&=&
-\frac{1}{2}\int\nabla ((u^\epsilon*\rho_\epsilon)^2)\cdot\nabla\phi \dif x
-\\
-\label{error 1}
-&&+
-\int\nabla(u^\epsilon*\rho_\epsilon)
-\left[(u^\epsilon\cdot\nabla\phi)*\rho_\epsilon-
-\nabla\phi\cdot((u^\epsilon*\rho_\epsilon)\right]\dif x,
-\end{eqnarray}
-where, as before, we have substituted $\tilde{x}=x-z$, $\tilde{y}=y-z$,
-$\tilde{z}=-z$.
-
-To control the term~(\ref{error 1})
-we use the Intermediate Value Theorem to see that
-\begin{multline*}
-\left|\int\left[u^\epsilon(x-y)\nabla\phi(x-y)\rho_\epsilon(y)-
-\nabla\phi(x)u^\epsilon(x-y)\rho_\epsilon(y)
-\right]\dif y\right|
-\\
-\leq C\|\Delta\phi\|_\infty\int u^\epsilon (x-y)\rho_\epsilon(y)y\dif y.
-\end{multline*}
-Since we chose $\rho$ to have compact support,
-$y\rho_\epsilon(y)\leq C\epsilon\rho_\epsilon(y)$
-in the last integral and so the expression~(\ref{error 1}) is
-$\mathcal{O}(\epsilon)$.
-
-Similarly, for the second term in~(\ref{total equation}),
-\begin{eqnarray}
-\nonumber
-\int (u^\epsilon*\zeta_\epsilon)\cdot \nabla u^\epsilon\cdot\nabla\phi \dif x
-&=&
-\int\int\int u^\epsilon(x-y)\rho_\epsilon(y-z)
-\check{\rho}_\epsilon(z)\nabla u^\epsilon(x)\nabla\phi(x)\dif z \dif y \dif x
-\\
-\nonumber
-&=&
-\int\int\int u^\epsilon(\tilde{x}-\tilde{y})\rho_\epsilon(\tilde{y})
-\rho_\epsilon(\tilde{z})\nabla u^\epsilon(\tilde{x}-\tilde{z})
-\nabla\phi(\tilde{x}-\tilde{z})\dif \tilde{z}\dif \tilde{y} \dif\tilde{x}
-\\
-\nonumber
-&=&\int(u^\epsilon*\rho_\epsilon)\cdot
-\left((\nabla u^\epsilon\nabla\phi)*\rho_\epsilon\right) \dif x\\
-\nonumber
-&=&
-\frac{1}{2}\int\nabla ((u^\epsilon*\rho_\epsilon)^2)\cdot\nabla\phi \dif x
-\\
-\label{error 2}
-&&+
-\int (u^\epsilon*\rho_\epsilon)
-\left[(\nabla u^\epsilon\cdot\nabla\phi)*\rho_\epsilon-
-\nabla\phi\cdot((\nabla u^\epsilon*\rho_\epsilon)\right]\dif x,
-\end{eqnarray}
-and~(\ref{error 2}) is controlled in the same way as~(\ref{error 1})
-using the Intermediate Value Theorem:
-\begin{multline*}
-\left|\int\left[\nabla u^\epsilon(x-y)\nabla\phi(x-y)\rho_\epsilon(y)
--\nabla\phi(x)\nabla u^\epsilon(x-y)\rho_\epsilon(y)
-\right]\dif y\right|
-\\
-\leq C\|\Delta\phi\|_\infty\left|\int \nabla u^\epsilon(x-y)\rho_\epsilon(y)y
-\dif y\right|\\
-\leq C'\|\Delta\phi\|_\infty\epsilon \int\left|
-\nabla u^\epsilon(x-y)\rho_\epsilon(y)
-\right|\dif y.
-\end{multline*}
-
-We now have the ingredients that we need.
-The calculations above yield both a uniform (in $\epsilon$) bound on
-$u^\epsilon*\rho_\epsilon$ in
-$L^1\cap L^2\big([0,T]\times \IT_K\big)$, and
-\begin{multline}
-\int u^\epsilon(t,x)\phi(x)\dif x-\int u^\epsilon (0,x)\phi(x)\dif x
-=\int_0^t\int (u^\epsilon*\rho_\epsilon)^2\Delta\phi(x)\dif x
-\\
-+\int_0^t \int u^\epsilon*\rho_\epsilon\left(1- u^\epsilon*\rho_\epsilon\right)
-\phi(x)\dif x
-+\mathcal{O}(\epsilon)
-\end{multline}
-(for sufficiently regular $\phi$). Since
-$\int u^\epsilon(t,x)\phi(x)\dif x-
-\int (u^\epsilon*\rho_\epsilon)(t,x)\phi(x)\dif x$ is order $\epsilon$, we see
-that $u^\epsilon*\rho_\epsilon$ converges weakly in $L^1$ to the (unique)
-solution
-to equation~(\ref{PME})
-and, so, therefore, does $u^\epsilon$. Strong convergence, that is
-$\int |u^\epsilon -u|\phi\dif x \to 0$, follows from the
-uniform integrability of $u^\epsilon$ that we
-deduce from the uniform control of
-$\int u^\epsilon|\log u^\epsilon|\dif x$ that we proved above.
-\end{proof}
-
-% % % % % % % % % % % % %
-\subsection{Simultaneous scaling with interaction distance}
-
-In this section we prove Theorem~\ref{them:nonlocal_pde_limits},
-which takes interaction distances to zero in the limit as well.
-
-\todo[inline]{BEGIN OneStepConvergence}
-\textbf{PREVIOUSLY, In this whole document $\rho_\epsilon$ will be the density of a normal with mean $0$ and variance $\epsilon^2$, and $q_\theta$ the density of a normal with mean $0$ and variance $1/\theta$.
-That is, $\rho_\epsilon(x) = p_{\epsilon^2}(x)$ and $q_\theta = p_{1/\theta}(x)$.
-This is HOPEFULLY FIXED NOW.}
-
-\begin{theorem} \label{TeoremOneStepConvergence}
-    Let $(\eta_t)_{t \geq 0}$ be the scaled particle system with $r(x, \eta) \equiv \gamma(x, \eta) \equiv 1$.
-    Suppose $F(x)$ satisfies for $x \ge 0$:
-    \begin{enumerate}
-        \item $F(x)$  is bounded above.
-        \item $|F'(x)|$ is bounded,
-        \item and $||F''(x)||_\infty < \infty$.
-    \end{enumerate}
-    We will also suppose $\theta$ is big enough that $1- F(x)/\theta$ is non-negative.
-
-    We will assume $\eta_0 := \eta_0(\epsilon,N,\theta)$
-    is a sequence of initial conditions for $(\eta_t)_{t \geq 0}$
-    such that there exists a finite constant $C>0$ independent of $\epsilon$, $N$, and $\theta$
-    such that
-    \begin{enumerate}
-        \item[(i)] $\langle 1 , \eta_0 \rangle < C $
-        \item[(ii)]  $\| \rho_\epsilon * \eta_0(x) \|_\infty < C$ for all $x \in \IR^d$
-        \item[(iii)] $|\rho_\epsilon * \eta_0(x) - \rho_\epsilon * \eta_0(y)| \leq C \| x - y \|$ for all $x,y \in \IR^d$, and
-        \item[(iv)] $\rho_\epsilon * \eta_0(x) dx$ converges weakly to $u_0(x)dx$ for some $u_0(x) \in \mathcal{C}^2(\IR^d)$.
-    \end{enumerate}
-    Furthermore, suppose that
-    \begin{equation}
-        \frac{\theta}{\epsilon^d N} + \frac{1}{\theta \epsilon^{2}} \to 0 . \label{ConditionsForConvergence}
-    \end{equation}
-    Fix $T>0$.
-Then, the measure $((\rho_\epsilon *\eta_t)(x) dx)_{t \geq 0}$ converges weakly in $D([0,T], \measures)$ to a measure $(\Xi_t(dx))_{t \geq 0}$.
-Moreover, up to a modification on a set of measure zero, $\Xi_t(x) = u_t(x)dx$, where $u_t(x)$ is a weak solution to:
-    \[ \partial_t u = \frac{1}{2}\Delta u + u F(u) \]
-    with initial condition $u_0$. That is, for every smooth function with compact support $f$ and $t>0$, we have:
-    \begin{equation*}
-     \int \partial_t  u_t(x) f(x) dx = \int u_t(x)\frac{1}{2} \Delta f(x) dx + \int f(x) u_t(x) F(u_t(x)) dx.
-    \end{equation*}
-\end{theorem}
-
-\todo[inline]{Question: Why do we need that regularity on $u_0$?
-I believe all we need is that (\ref{aprox3}) holds, and for that, I am almost sure that $u_0$ only needs to satisfy the first three hypotheses for $\eta_0(x)$.
-Furthermore,  if I am not mistaken, those are all implied by $u_0(x) \in L^1(\IR^d) \cap L^2(\IR^d) \cap \mathcal{C}^1(\IR^d)$ in case we want a nice space to put on the result.
- Alison says: $C^1 \cap L^1$ probably enough, but...
- }
-
-\todo[inline]{TODO: Below what we write as $\rho_\epsilon$ is actually $\rho_F = p_{\epsilon_F^2}$; resolve this somehow. (it seems nice to retain the dependence on $\epsilon$ somehow)}
-
-To prove this we will proceed in a standard pattern, proving $C$-tightness of the measure and then identifying the limit.
-
-As a preliminary, we will prove some basic tools we are going to need all the way through.
-First, we prove that, under the conditions of Theorem~\ref{TeoremOneStepConvergence}, $\eta_t$ has a uniformly bounded total mass in expectation.
-We then prove some regularity estimates of a random walk with Gaussian jumps.
-While this may seem disconnected from our goal the generator of this random walk is in the first integral element that appears in the martingale problem for $\eta_t$, equation (\ref{mgp1}).
-It is then, no surprise, that we need some control over the regularity this term brings to our particle system.
-
-We then focus on $C$-tighness of $\rho_\epsilon * \eta_t(x)dx$.
-For this we will prove that for fixed $x$, the random variable $\rho_\epsilon*\eta_t(x)$ has uniformly bounded expectation.
-Using this and the regularity of the random walk mention above, we will be able to prove the $C$-tightness of $\rho_\epsilon * \eta_t(x)dx$.
-
-Then we will proceed to identify the limit.
-For this, a continuity estimate for $(\rho_\epsilon*\eta_t(x))$ is needed, which is again a consequence of the random walk estimates mentioned above.
-Using this we focus on controlling the convergence of \textit{non-linear terms} in the martingale problem of $(\rho_\epsilon*\eta_t(x))$ (as the others converge as a consequence of weak convergence).
-Those do not converge as a consequence of weak convergence, since they are not written as an integral on $M^{\otimes k}(\IR^d)$ of $(\rho_\epsilon*\eta_t(x) dx)$ (for some $k \in \mathbb{N}$).
-Instead, we will first compare the quadratic terms to terms only involving $\rho_\epsilon*\eta_s$ (and not $\eta_s(dy)$) and then we will exchange those terms with a suitable integral in $M^{\otimes2}(\IR^d)$, for which convergence do follow easily.
-
-\subsubsection{Preliminaries}
-
-Since we're assuming that $\gamma$ and $r$ are identically 1,
-the death rate is $1 + F(x, \eta) / \theta$.
-For reference,
-the martingale problem (Definition \ref{defn:mgale_construction})
-for $\eta_t$ gives that for any smooth function $\phi$,
-\begin{align} \label{mgp1}
-    \langle \phi(x), \eta_{t}(dx) \rangle
-    -
-    \langle \phi(x), \eta_{0}(dx)\rangle
-    &= \nonumber
-    M_t(\phi)
-    +
-    \int_{0}^{t} \langle \theta \int_{\IR^d}
-            \left( \phi(y) -\phi(x) \right)
-        q_\theta(x,dy), \eta_s(dx)
-    \rangle ds
-    \\ & {}
-    +
-    \int_0^t \langle
-        F(x, \eta_s) \phi(x),
-        \eta_s(dx)
-    \rangle ds ,
-\end{align}
-where $M_t(\phi)$ is a martingale with quadratic variation:
-\begin{align} \label{mgp2}
-    \begin{split}
-[ M(\phi) ]_t
-    &:=
-    \frac{\theta}{N}
-    \int_{0}^{t} \bigg\{
-        \left\langle \int_{\IR^d} \phi^2(y) q_\theta(x,dy), \eta_s(dx) \right\rangle
-    \\
-    & \qquad \qquad {} +
-    \left\langle \left(1 + \frac{F(x, \eta_s)}{\theta } \right)
-        \phi^2(x), \eta_s(dx)) \right\rangle 
-    \bigg\} ds. 
-    \end{split}
-\end{align}
-
-Several times below we will need to bound second moments,
-and for this purpose it will be useful to record that \eqref{mgp1} and \eqref{mgp2}
-imply that the following is a martingale:
-\begin{align} \label{mgp3}
-    \nonumber
-    \langle \phi, \eta_t \rangle^2
-    -
-    & \langle \phi, \eta_0 \rangle^2
-    -
-    \int_0^t
-        2 \langle \phi, \eta_s \rangle
-        \left\langle
-            \theta \int_{\IR^d} (\phi(y) - \phi(x)) q_\theta(x, dy)
-            + F(x, \eta_s) \phi(x),
-            \eta_s(dx)
-        \right\rangle
-    ds
-    \\ & {}
-    -
-    \frac{\theta}{N}
-    \int_0^t
-        \left\langle
-            \int_{\IR^d} \phi^2(y) q_\theta(x, dy)
-            +
-            \left(1 + \frac{F(x, \eta_s)}{\theta}\right) \phi^2(x),
-            \eta_s(dx)
-        \right\rangle
-    ds .
-\end{align}
-
-Above, we showed in Lemma~\ref{lem:eta_compact_containment}
-uniform boundedness the total mass under the assumption of fixed $\epsilon$.
-It is easy to see that the same proof applies
-in this situation -- indeed, the hardest part, Lemma~\ref{lem:gamma_bound} is not needed,
-since $r$ and $\gamma$ are 1 --
-and gives us the following result.
-
-\begin{lemma}[Boundedness of total mass] \label{Lemma:UniformlyBoundedMass}
-    Under the assumptions of Theorem~\ref{TeoremOneStepConvergence},
-    for each $T \ge 0$ there is a finite constant $C$ (independent of $\epsilon, N, \theta$),
-    such that $\IE\left[ \sup_{0 \leq s \leq T} \langle 1, \eta_s \rangle \right] \leq C$.
-\end{lemma}
-
-%% PLR: removing, since we can just refer to the above?
-% \begin{proof}
-% By putting $\phi(x)=1$ in the martingale problem of $\eta_t$, equation (\ref{mgp1}), we have,
-% \begin{align} \label{eq:MPTotalMass}
-% \langle 1, \eta_t \rangle &= \langle 1, \eta_0 \rangle + \int_0^t \langle F(\rho_\epsilon * \eta_s), \eta_s \rangle ds + M_t
-% \end{align}
-% where $M_t$ is a martingale with quadratic variation,
-% \begin{align} \label{eq:QVTotalMass}
-% [M]_t = \frac{\theta}{N}\int_0^t \langle 1 + \frac{F(\rho_\epsilon* \eta_s)}{\theta}, \eta_s \rangle d s 
-% \end{align}
-% By taking expectations in (\ref{eq:MPTotalMass}) we get,
-% \[ \IE[\langle 1, \eta_t \rangle] =  \IE[\langle 1, \eta_0 \rangle]  + \IE[ \int_0^t \langle F(\rho * \eta_s), \eta_s \rangle ds ]   \leq C +   C \mathbb{E}\left[ \int_0^t \langle 1, \eta_s \rangle ds \right].\]
-% In last inequality we used that $F(x)1_{x >0}$ and $\langle 1, \eta_0 \rangle$ are uniformly bounded above.
-By Gronwall's inequality we deduce $\IE[\langle 1, \eta_s \rangle]$ is bounded on $[0,T]$.
-Hence, by taking expectations in (\ref{eq:QVTotalMass}) and using again the bound on $F(x)1_{x>0}$ we get,
-% \begin{equation} \IE\left[ [M]_t \right] \leq \frac{\theta}{N} C \int_0^t \mathbb{E}\left[ \langle 1, \eta_s \rangle ds \right] \leq \frac{\theta}{N}C t \label{eq:quadvarMass} \end{equation}
-% Note that, with this, $\IE[ [M]_t]$ is bounded (and in fact $\mathcal{O}(\theta/N)$). By the Burkholder-Davis-Gundy inequality and then Jensen's inequality we get
-% \begin{align*}
-%     \IE\left[ \sup_{0 \leq t \leq T} M_t \right]
-%     \leq
-%     C \IE\left[ [M]_T \right]^{1/2}
-%     \leq
-%     C \IE[M]_T^{1/2}
-%     \leq
-%     C  
-% \end{align*}
-% Taking supremum and then expectation in (\ref{eq:MPTotalMass}) and using the last inequality gives the result.
-% 
-%     \comment{Alison says: I'd actually write out
-%     $\sup \langle 1, \eta_s \rangle \le \int_0^T xxx ds + \sup M_t$ .
-%     }
-% 
-% \end{proof}
-
-\begin{lemma}
-        \label{lem:SecondMomentMass}
-    Under the assumptions of Theorem~\ref{TeoremOneStepConvergence}
-    there is a finite constant $C$ (independent of $\epsilon, N, \theta$) such that,
-    for all $t \in [0,T]$ and for big enough $N$ and $\theta$,
-    $\IE[ \langle 1, \eta_t \rangle^2] \leq C$.
-\end{lemma}
-
-\begin{proof}[of Lemma~\ref{lem:SecondMomentMass}]
-    Using equation~\eqref{mgp3} with $\phi = 1$,
-    \begin{align*}
-        \IE[\langle 1, \eta_t \rangle^2]
-        &=
-        \IE[\langle 1, \eta_0 \rangle^2]
-        +
-        \IE\left[
-        \int_0^t
-            2 \langle 1, \eta_s \rangle
-            \langle F(x, \eta_s), \eta_s(dx) \rangle
-            +
-            \frac{\theta}{N} \langle 2 + F(x, \eta_s)/\theta, \eta_s(dx) \rangle
-        ds
-        \right] .
-    \end{align*}
-    Since $F(m)1_{m > 0}$ is bounded above and $\theta/N$ converges,
-    we have for an appropriate $C$ that
-    \begin{align*}
-        \IE[\langle 1, \eta_t \rangle^2]
-        \le
-        C + C \int_0^t \IE[\langle 1, \eta_s \rangle] ds
-        + C \int_0^t \IE[\langle 1, \eta_s \rangle^2] ds .
-    \end{align*}
-    The result follows from Lemma~\ref{Lemma:UniformlyBoundedMass} and Gronwall's inequality.
-\end{proof}
-
-\paragraph{Regularity estimates of the density of a independent Gaussian random walk}
-Let us write $\mathcal{L}^\theta f(x) := \theta \int (f(y)-f(x))q_\theta(x,y) dy$ with $q_\theta$ is a Gaussian kernel of mean $0$ and variance $1/\theta$.
-We note that $\mathcal{L}^\theta$ is the generator of a continuous random walk, where at rate $\theta$ we have the arrival of Gaussian jumps of mean $0$ and variance $1/\theta$.
-
-In what follows we let $\psi_t^{\epsilon, x}(y)$ be the solution of:
-\begin{equation}
-    \frac{\partial}{ \partial_t} \psi_t^{\epsilon,x}
-    =
-    \mathcal{L}^\theta \psi_t^{\epsilon, x}
-    \label{AlmostHeatEquation}
-\end{equation}
-with initial condition $\psi_0^{\epsilon,x}(y) = \rho_\epsilon(y-x)$.
-We have the following result for $\psi_t^{\epsilon,x}$.
-
-\begin{lemma} \label{PsiBoundHS}
-    Fix $t>0$,
-    let $(N(s))_{s \ge 0}$ be a rate 1 Poisson process,
-    and let $T(t) = N(\theta t) / \theta$.
-    Then
-    \[
-        \psi^{\epsilon,x}_t(y)
-        =
-        \IE\left[ p_{\epsilon^2+T(t)}(x,y)\right],
-    \]
-    and moreover, there is a $C$ independent of $\epsilon$ or $t$ such that
-    \[
-        \| \psi^{\epsilon,x}_t \|_\infty
-        \leq
-        \frac{C}{(\epsilon^2 + t)^{d/2}} .
-    \]
-\end{lemma}
-
-\begin{proof}
-    The first claim follows immediately from $\mathcal{L}^\theta$ being the generator
-    of a continuous-time random walk,
-    where independent Gaussian jumps with mean $0$ and variance $1/\theta$
-    arrive at rate $\theta$.
-
-    For the second claim, first define $\tau(t) = T(t)-t$.
-    % which has mean $0$ and variance $t/\theta$.
-    % so by Chebyshev's inequality,
-    % \begin{equation}
-    %     \IP\left\{ \tau(t) < - \frac{\epsilon^2 + t}{2} \right\}
-    %     \leq
-    %     \IP\left\{  \frac{|T(t)-t|}{\epsilon^2+t} > \frac{1}{2} \right\}
-    %     \leq
-    %     \frac{4t}{\theta(\epsilon^2+t)^2} \leq \frac{2}{\epsilon^2 \theta}.
-    %     \label{eq:IneqConcentrationT}
-    % \end{equation}
-    Since if $\tau(t) \ge -(\epsilon^2 + t)/2$,
-    then $1/(\epsilon^2 + T(t)) \le 2/(\epsilon^2 + t)$,
-    while $\epsilon^2 + T(t) \ge \epsilon^2$ always,
-    then partitioning over
-    $\{ \tau(t) \ge -(\epsilon^2 + t)/2 \}$ and its complement,
-    \begin{align}
-    \| \psi^{\epsilon,x} \|_\infty
-    &=
-        \IE\left[ 
-            \frac{1}{2 \pi (\epsilon^2+T(t))^{d/2}}
-        \right] \nonumber
-    \\ & \le
-        \frac{C}{(\epsilon^2 + t)^{d/2}}
-        + 
-        \frac{C}{\epsilon^d}
-        \IP\left\{
-            \tau(t) < - (\epsilon^2 + t) / 2
-        \right\} \label{eqn:psi_infty_bound}
-    \end{align}
-    Now, observe that since $\IE[e^{-N(\theta t)}] = \exp(-\theta t (1 - e^{-1}))$,
-    then by Markov's inequality,
-    \begin{align*}
-        \IP\left\{
-            \tau(t) < - \frac{\epsilon^2 + t}{2}
-        \right\}
-        &=
-        \IP\left\{
-            e^{-N(\theta t)} > e^{-\theta (t - \epsilon^2) / 2}
-        \right\}
-        \\&\le
-        \frac{
-            \exp(- \theta t(1 - e^{-1}))
-        }{
-            \exp(- \theta (t - \epsilon^2) / 2)
-        }
-        \\&=
-        \exp\left\{ - \delta \theta t - \frac{\theta \epsilon^2}{2} \right\} ,
-    \end{align*}
-    where $\delta = 1/2 - e^{-1} > 0$.
-    The second term in \eqref{eqn:psi_infty_bound} is therefore bounded by
-    \[
-        C \left(1 + \frac{t}{\epsilon^2}\right)^{d/2} e^{-\delta \theta t - \epsilon^2 \theta / 2}
-        \frac{1}{(\epsilon^2 + t)^{d/2}} .
-    \]
-    Now, $e^{-\delta \theta t - \epsilon^2 \theta / 2} (1 + t/\epsilon^2)^{d/2}$ is decreasing in $t$
-    for all $t$ if $\epsilon^2 \theta$ is sufficiently large:
-    this holds because its derivative is
-    is
-    \[
-        \left( \frac{d}{2 \epsilon^2} - \left(1 + \frac{t}{\epsilon^2}\right) \delta \theta \right)
-        \left( 1 + \frac{t}{\epsilon^2} \right)^{d/2 - 1} e^{-\delta \theta t - \epsilon^2 \theta / 2} ,
-    \]
-    which is negative if $\theta(\epsilon^2 + t) > d/2 \delta$.
-    Therfore, the second term in \eqref{eqn:psi_infty_bound} 
-    is bounded by $C / (\epsilon^2 + t)^{d/2}$
-    (for a different constant $C$).
-    Substituting this into \eqref{eqn:psi_infty_bound} obtains the result.
-\end{proof}
-
-We will need further comparisons of $\psi_t^{\epsilon,x}$ to the heat semigroup,
-and for this we will first need the following fact about large deviations
-of a Poisson process.
-
-\begin{lemma}
-    \label{lem:poisson_ld}
-    Fix $A > e^3 - 1$ (so that $\log(1 + A) > 3$).
-    In the notation of Lemma~\ref{PsiBoundHS},
-    \begin{align*}
-        \limsup_{\theta \to \infty}
-        \frac{1}{\theta} \log
-        \IP\left\{
-            T(t) - t > A(\epsilon^2 + t)
-        \right\}
-    \le
-        - (\epsilon^2 + t) \frac{A}{2}
-        - \log(1 + A)\left( \frac{t + A(\epsilon^2 + t)}{2} \right) .
-    \end{align*}
-\end{lemma}
-
-\begin{proof}[of Lemma~\ref{lem:poisson_ld}]
-    We apply Cram\'er's Theorem.
-    First note that
-    \begin{align*}
-        \IP\left\{
-            T(t) - t > A(\epsilon^2 + t)
-        \right\}
-        =
-        \IP\left\{
-            N(\theta) t) / \theta
-            >
-            t + A(\epsilon^2 + t)
-        \right\} .
-    \end{align*}
-    For convenience, suppose $\theta$ is an integer,
-    and so we may write $N(\theta t) = Z_1(t) + \cdots + Z_\theta(t)$,
-    where the $Z_i(t)$ are i.i.d.~ Poisson($t$) random variables.
-    To apply Cram\'er's Theorem, we need the rate function for the Poisson($t$) distribution,
-    which is
-    \[
-        \Lambda^*(x) = \sup_{\alpha > 0} \left[ \alpha x - \lambda(\alpha) \right],
-    \]
-    where $\lambda(\alpha) = \log \IE[\exp(\alpha Z_1(t))] = t(e^\alpha - 1)$.
-    Now, the supremum of $\alpha x + t - te^\alpha$ is attained at $x = t e^\alpha$,
-    and so
-    \[
-        \Lambda^*(x) = x \log(x/t) - x + t .
-    \]
-    Cram\'er's Theorem then gives
-    \begin{align*}
-        \limsup_{\theta \to \infty}
-        \frac{1}{\theta} \log
-        \IP\left\{
-            \frac{N(\theta t)}{\theta}
-            > A(\epsilon^2 + t)
-        \right\}
-    &\le
-        - \Lambda^*(t + A(\epsilon^2 + t))
-    \\ &=
-        A(\epsilon^2 + t)
-        -
-        (t + A(\epsilon^2 + t)) \log\left( 1 + \frac{A(\epsilon^2 + t)}{t} \right) 
-    \\ &\le
-        A(\epsilon^2 + t)
-        -
-        (t + A(\epsilon^2 + t)) \log(1 + A)
-    \\ &\le
-        A(\epsilon^2 + t) \left( 1 - \frac{1}{2} \log(1 + A) \right)
-        -
-        \frac{1}{2} (t + A(\epsilon^2 + t)) \log(1 + A)  .
-    \end{align*}
-    Since $(1/2) \log(1 + A) > 3/2$, hence $1 - (1/2) \log(1 + A) < - 1/2$,
-    and we are done.
-\end{proof}
-
-Now we would like to show that $\psi_t^{\epsilon,x}(y)$
-is uniformly close to $p_{\epsilon^2 + t}(x, y)$
-under the assumptions.
-
-\begin{lemma}
-    \label{Lemma:BoundPsiHS2}
-    In the notation of Lemma~\ref{PsiBoundHS},
-    and with $A$ as in Lemma~\ref{lem:poisson_ld},
-    \begin{align*}
-        \left|
-            \psi_t^{\epsilon, x}(y)
-            -
-            p_{\epsilon^2 + t}(x, y)
-        \right|
-        \le
-        \frac{C}{\epsilon^2 \theta}^{d/2}
-        p_{2(A+1)(\epsilon^2+t)}(x, y)
-        +
-        C \exp(- \epsilon^2 \theta / 2)
-        +
-        \frac{C}{(\epsilon^2 + t)^{d/2}}
-        \IP\left\{
-            \tau(t) > A(\epsilon^2 + t)
-        \right\} .
-    \end{align*}
-\end{lemma}
-
-\begin{proof}[of Lemma~\ref{Lemma:BoundPsiHS2}]
-    The three terms on the right hand side of the Lemma
-    correspond to bound obtained by partitioning
-    into three events according to the value of $\tau(t)$:
-    let $A_1 = \{ \tau(t) < - (\epsilon^2 + t)/2 \}$,
-    let $A_2 = \{ \tau(t) > A(\epsilon^2 + t) \}$,
-    and $A_3$ the remaining event, $\{ - (\epsilon^2 + t)/2 \le \tau(t) \le A(\epsilon^2 + t) \}$.
-    Then,
-    \begin{align*}
-        \left|
-            \psi_t^{\epsilon, x}(y)
-            -
-            p_{\epsilon^2 + t}(x, y)
-        \right|
-        &=
-        \left|
-        \IE\left[
-            p_{\epsilon^2 + t + \tau(t)}(x, y)
-            -
-            p_{\epsilon^2 + t}(x, y)
-        \right]
-        \right|
-        \\&\le
-        \IE\left[
-            (1_{A_1} + 1_{A_2} + 1_{A_3})
-            \left|
-            p_{\epsilon^2 + t + \tau(t)}(x, y)
-            -
-            p_{\epsilon^2 + t}(x, y)
-        \right|
-        \right] .
-    \end{align*}
-
-    For the first term, note that if $a < b$ then
-    \begin{align*}
-        |p_a(x, y) - p_b(x, y)| 
-        &=
-        \frac{1}{(2\pi)^{d/2}}
-        \left|
-            \frac{1}{a^{d/2}}
-            e^{-\|x - y\|^2 / 2a}
-            -
-            \frac{1}{b^{d/2}}
-            e^{-\|x - y\|^2 / 2b}
-        \right|
-        \\ &=
-        \frac{1}{(2\pi a^2)^{d/2}}
-            e^{-\|x - y\|^2 / 2b}
-        \left|
-            e^{-\|x - y\|^2 \left(\frac{1}{2a} - \frac{1}{2b}\right)}
-            -
-            \left(\frac{a}{b}\right)^{d/2}
-        \right|
-        \\ &\le
-        C \left(\frac{b}{a}\right)^{d/2}
-        p_b(x, y) ,
-    \end{align*}
-    where the inequality follows because both terms in the absolute values are less than 1.
-    % note the original had $p_{b/2}$ on the right.
-    Applying this with $a = \epsilon^2 + t + \tau(t)$ and $b = \epsilon^2 + t$,
-    and using the same bound as we did for the second term of equation~\ref{eqn:psi_infty_bound},
-    \begin{align*}
-        \IE\left[
-            1_{A_1} |p_a(x, y) - p_b(x, y)| 
-        \right]
-        & \le
-            C \left(\frac{\epsilon^2 + t}{\epsilon^2}\right)^{d/2}
-            p_{\epsilon^2 + t}(x, y) 
-            \IP\left\{ \tau(t) < - \frac{\epsilon^2 + t}{2} \right\}
-        \\ & \le
-            C \frac{1}{\epsilon^d}
-            \IP\left\{ \tau(t) < - \frac{\epsilon^2 + t}{2} \right\}
-        \\ & \le
-        C \exp\left(-\frac{\theta \epsilon^2}{2} \right) .
-    \end{align*}
-
-    For the third term, we will first collect some facts.
-    Observe that on this event,
-    $\epsilon^2 + t + \tau(t)$ is between
-    $(\epsilon^2 + t)/ 2$ and $(A + 1)(\epsilon^2 + t))$,
-    and for any $s$ in this interval,
-    \begin{align}
-        p_{2s}(y)
-        &\le \nonumber
-        \left( \frac{
-            2 (\epsilon^2 + t)(A + 1)
-        }{
-            \epsilon^2 + t
-        } \right)^{d/2}
-        p_{2(A+1)(\epsilon^2 + t)}(x, y)
-        \\ &= \label{eqn:p_bounded_on_interval}
-        (2(A+1))^{d/2}
-        p_{2(A+1)(\epsilon^2 + t)}(x, y) .
-    \end{align}
-    Moreover, since $u e^{-u} \le e^{-1}$ for all $u \ge 0$,
-    \begin{align}
-        \frac{\|x - y\|^2}{s} p_s(x, y)
-        &= \nonumber
-        \frac{4}{(2 \pi s)^{d/2}}
-        e^{- \frac{ \|x-y\|^2 }{ 4s }}
-        \frac{\|x-y\|^2}{4s}
-        e^{- \frac{ \|x-y\|^2 }{ 4s }}
-        \\ &\le \label{eqn:p_deriv_term2}
-        C p_{2s}(x, y) .
-    \end{align}
-    Now, by the Intermediate Value Theorem,
-    \begin{align*}
-        \left|
-            p_{\epsilon^2 + t + \tau(t)}(x, y)
-            -
-            p_{\epsilon^2 + t}(x, y)
-        \right|
-        &=
-        \left| \tau(t) \right|
-        \left| \frac{\partial p_s(x, y)}{\partial s} \right|
-    \end{align*}
-    for some $s$ between $\epsilon^2 + t + \tau(t)$ and $\epsilon^2 + t$.
-    Now,
-    \begin{align*}
-        \frac{\partial}{\partial s} p_s(x, y)
-        &=
-        \frac{\partial}{\partial s}
-        \left(
-            \frac{1}{(2 \pi s)^{d/2}}
-            \exp\left( - \frac{\|x - y\|^2}{2 s} \right)
-        \right)
-        \\ &=
-        - \frac{d}{2s} p_s(x, y) + \frac{\|x - y\|^2}{2 s^2} p_s(x, y)  .
-    \end{align*}
-    Applying the inequality~\eqref{eqn:p_deriv_term2},
-    using the fact that $p_s(x, y) \le \sqrt{2} p_{2s}(x,y)$,
-    and then \eqref{eqn:p_bounded_on_interval},
-    we have that for any $s \in ((\epsilon^2 + t)/ 2, (A + 1)(\epsilon^2 + t))$,
-    \begin{align*}
-        \left| \frac{\partial}{\partial s} p_s(x, y) \right|
-        \le
-        \frac{C}{s} p_{2s}(x, y) 
-        \le
-        \frac{C}{\epsilon^2 + t} p_{2(A + 1)(\epsilon^2 + t)}(x, y) .
-    \end{align*}
-    Therefore, recalling that $\IE[\tau(t)^2] = t / \theta$,
-    \begin{align*}
-        \IE\left[
-            1_{A_3}
-            \left|
-                p_{\epsilon^2 + t + \tau(t)}(x, y)
-                -
-                p_{\epsilon^2 + t}(x, y)
-            \right|
-        \right]
-        &\le
-            \frac{C}{\epsilon^2 + t}
-                p_{2(A + 1)(\epsilon^2 + t)}(x, y)
-            \IE\left[|\tau(t)|\right]
-        \\ &\le
-            \frac{C}{\epsilon^2 + t}
-                p_{2(A + 1)(\epsilon^2 + t)}(x, y)
-            \IE\left[\tau(t)^2\right]^{1/2}
-        \\ &=
-            \left( \frac{Ct}{\theta(\epsilon^2 + t)^2} \right)^{1/2}
-                p_{2(A + 1)(\epsilon^2 + t)}(x, y)
-        \\ &\le
-            \frac{C}{\sqrt{\theta \epsilon^2}}
-                p_{2(A + 1)(\epsilon^2 + t)}(x, y) ,
-    \end{align*}
-    where the last inequality follows from $2 \epsilon^2 t \le (\epsilon^2 + t)^2$.
-
-    Finally, on the event $A_2 = \{\tau(t) > A(\epsilon^2 + t)\}$,
-    we simply use
-    \begin{align*}
-        \left|
-            p_{\epsilon^2 + t + \tau(t)}(x, y)
-            -
-            p_{\epsilon^2 + t}(x, y)
-        \right|
-        \le
-        \frac{C}{(\epsilon^2 + t)^{d/2}} ,
-    \end{align*}
-    so that
-    \begin{align*}
-        \IE\left[
-        1_{A_2}
-        \left|
-            p_{\epsilon^2 + t + \tau(t)}(x, y)
-            -
-            p_{\epsilon^2 + t}(x, y)
-        \right|
-        \right]
-        \le
-        \frac{C}{(\epsilon^2 + t)^{d/2}}
-        \IP\left\{
-            \tau(t) > A (\epsilon^2 + t)
-        \right\} .
-    \end{align*}
-\end{proof}
-
-The last result will be useful when combined with the next bound for the heat kernel.
-
-\begin{lemma}
-    \label{Lemma:ContinuityHS}
-Let $s>0, x, y, z\in \IR^d$. The following estimate holds:
-\[
-    |p_s(x,z) - p_s(y,z)|
-    \leq
-    \frac{C|x-y|}{\sqrt{s}} \left(p_{2s}(x,z) + p_{2s}(y,z)\right) ,
-\]
-where the constant $C$ does not depend on $x,y,z$ or $s$.
-\end{lemma}
-
-\begin{proof}
-    Expanding the difference of two squares,
-    \begin{align*}
-        e^{- \frac{(y-z)^2}{2 s}}
-        -
-        e^{- \frac{(x-z)^2}{2 s}}
-        &=
-        \left(
-            e^{-\frac{(y-z)^2}{4 s}}
-            -
-            e^{-\frac{(x-z)^2}{4 s}}
-        \right)
-        \left(
-            e^{-\frac{(y-z)^2}{4 s}}
-            +
-            e^{-\frac{(x-z)^2}{4 s}}
-        \right) .
-    \end{align*}
-    % % (big version of the previous equation:)
-    % \begin{align*}
-    %     &\exp\left( - \frac{(y-z)^2}{2 s} \right)
-    %     -
-    %     \exp\left( - \frac{(x-z)^2}{2 s} \right)
-    %     \\ &=
-    %     \left(
-    %         \exp\left(-\frac{(y-z)^2}{4 s} \right)
-    %         -
-    %         \exp\left(-\frac{(x-z)^2}{4 s} \right)
-    %     \right)
-    %     \left(
-    %         \exp\left(-\frac{(y-z)^2}{4 s} \right)
-    %         +
-    %         \exp\left(-\frac{(x-z)^2}{4 s} \right)
-    %     \right) .
-    % \end{align*}
-    By using the Intermediate Value Theorem we can write the right hand side as
-    \[
-        (y-x)
-        \left( - \frac{2(w-z)}{4s} \exp\left(-\frac{(w-z)^2}{4s}\right)\right)
-        (4 \pi s)^{d/2}
-        \left( p_{2s}(y,z)+p_{2s}(x,z) \right)
-    \]
-    for some $w \in [y,z]$.
-    Using the fact that $x e^{-x^2}$ is uniformly bounded,
-    we can bound the first bracket in the last equation by $C/\sqrt{s}$, and the result follows.
-\end{proof}
-
-\paragraph{The martingale problem for a time dependent function.}
-Before proceeding we make the following observation.
-For any time-dependent function $\phi_t(x)$
-with time derivative $\dot \phi_t(x) = \frac{d}{dt} \phi_t(x)$,
-the martingale problem for $\eta_t$, (like \ref{mgp1}),
-is
-% \comment{Alison says: not sure this needs spelling out?}
-\begin{align}
-        \label{timeMGP}
-    \langle \phi_0(x), \eta_t(dx) \rangle
-    &= \nonumber 
-    \langle \phi_t(x), \eta_0(dx) \rangle
-    +
-    M_t(\phi_\cdot(\cdot))
-    +
-    \int_0^t \langle \mathcal{L}^\theta \phi_{t-s}(x) - \dot \phi_{t-s}(x), \eta_s(dx) \rangle ds
-    \\ & {}
-    +
-    \int_{0}^t \langle \phi_{t-s}(x) F(x, \eta_s) , \eta_s(dx) \rangle ds ,
-\end{align}
-where $M_t(\phi_\cdot(\cdot))$ has quadratic variation
-\begin{align}
-        \label{timeMGP2}
-    [M(\phi_\cdot(\cdot))]_t
-    =
-    \frac{\theta}{N} \int_0^t \langle
-        \int_{\IR^d} \phi_{t-s}(z)^2 q_\theta(y,dz)
-        +
-        \left( 1 + \frac{F(y, \eta_s)}{\theta}\right) \phi_{t-s}(y)^2,
-    \eta_s(dy) \rangle ds .
-\end{align}
-
-%%%%%%%%%%%%%%%%%%
-\subsubsection{Tightness}
-
-\paragraph{Bounds for $\{ \rho_\epsilon * \eta_s (x)\}_{0 \leq s \leq T}$}
-
-\begin{lemma}
-        \label{FirstBoundLocalDensity}
-    Under the conditions of Theorem~\ref{TeoremOneStepConvergence}
-    there is a constant $C>0$ (independent of $\epsilon$, $N$, $\theta$, and $x$) such that,
-    \[ \IE[ \rho_\epsilon*\eta_t(x) ] < C \]
-    for all $t \in [0,T]$ and $x \in \IR^d$.
-\end{lemma}
-
-\begin{proof}
-    Recall that $\psi_t^{\epsilon,x}$ is the solution of (\ref{AlmostHeatEquation})
-    with initial condition $\psi_0^{\epsilon,x}(y)=\rho_\epsilon(y-x)$.
-    By replacing $\phi_t$ with $\psi_t^{\epsilon,x}$ in (\ref{timeMGP}) we can write
-    for each $x$
-    \begin{align}
-            \label{MartingaleProblemMolifier}
-        \rho_\epsilon*\eta_t(x)
-        =
-        \langle \psi_t^{\epsilon,x}(y), \eta_0(dy) \rangle
-        +
-        \int_0^t \langle
-            \psi_{t-s}^{\epsilon,x}(y) F(y, \eta_s),
-        \eta_s(dy) \rangle ds
-        +
-        M_t^x .
-    \end{align}
-    First recall that our second assumptions on $\eta_0$
-    was (ii) $\|\rho_\epsilon * \eta_0\|_\infty < C$.
-    Since 
-    \[
-        \langle \psi_t^{\epsilon,x}(y), \eta_0(dy) \rangle
-        =
-        \IE \left[ \langle
-            p_{\epsilon^2 + T(t)}(x, y), \eta_0(dy)
-        \rangle \right]
-        =
-        \IE \left[ \int_{\IR^d} p_{T(t)}(x, y) \rho_\epsilon * \eta_0(y) dy \right],
-    \]
-    this implies that
-    $\langle \psi_t^{\epsilon,x}(y), \eta_0(dy) \rangle \le C$.
-    Since $F(x)$ is uniformly bounded above,
-    if we take expectations and use Lemma~\ref{Lemma:UniformlyBoundedMass},
-    \begin{align}
-    \IE[\rho_\epsilon * \eta_t(x)]
-        &\le \label{BoundForMollifierStart}
-        \IE[\langle \psi_t^{\epsilon,x}(y), \eta_0(dy) \rangle]
-        +
-        C \IE\left[\int_0^t \langle \psi_{t-s}^{\epsilon,x}(y), \eta_s(dy) \rangle ds\right]
-        \\ & \nonumber
-        \leq
-        C
-        +
-        C \int_0^t \Vert \psi_{t-s}^{\epsilon,0} \Vert_\infty
-        \IE\left[\sup_{0 \leq s \leq t} \langle 1, \eta_s(dy) \rangle\right] ds
-        \\ &
-        \leq \label{BoundForMollifier}
-        C + C \int_0^t \Vert \psi_{t-s}^{\epsilon,0} \Vert_\infty ds
-    \end{align}
-    Now, using Lemma~\ref{PsiBoundHS}, % since $\epsilon^2 \theta \to \infty$,
-    we can bound $\| \psi_{t-s}^{\epsilon,0} \|_\infty$
-    by $C (t-s+\epsilon^2)^{-d/2}$.
-    In dimension one the right hand side of \eqref{BoundForMollifier} is immediately uniformly bounded.
-    For $d=2$ we can iterate.
-    By using again the martingale problem and the same arguments
-    we used to get \eqref{BoundForMollifier} we get,
-    % \comment{Alison suggests that writing the term on the right instead as
-    %     $C \IE[\int_0^t \langle \psi_{t-u}^{\epsilon,x}(y), \eta_u(dy) \rangle du ]$
-    %     would look more natural?}
-    \begin{equation} \label{IterationBoundPsi}
-        \IE[\langle \psi_{t-s}^{\epsilon,x}, \eta_s(dy)\rangle]
-        \leq
-        \IE[\langle \psi_{t}^{\epsilon,x}(y), \eta_0(dy) \rangle]
-        +
-        C \int_0^s \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du
-    \end{equation}
-    Hence, using \eqref{IterationBoundPsi} in \eqref{BoundForMollifierStart} gives
-    \begin{align*}
-        \IE[ \rho_\epsilon * \eta_t(x) ]
-        &\leq
-        \IE[ \langle \psi_t^{\epsilon,x}(y), \eta_0(dy) \rangle]
-        +
-        \int_0^t C\langle \psi_{t}^{\epsilon,x}, \eta_0(dy)\rangle ds
-        +
-        C^2 \int_0^t \int_0^s  \| \psi_{t-u}^{\epsilon,0} \|_\infty du ds
-        \\ &=
-        (1+Ct) \IE[ \langle \psi_t^{\epsilon,x}, \eta_0(dy) \rangle]
-        +
-        C^2 \int_0^t (t-u) \Vert \psi_{t-u}^{\epsilon,0} \Vert_\infty du
-        \\ &\leq
-        C(1+t) + C^2 \int_0^t (t-u) \| \psi_{t-u}^{\epsilon,0} \|_\infty du ,
-    \end{align*}
-    which again is uniformly bounded using Lemma \ref{PsiBoundHS}.
-    It is easy to see that, iterating, we can prove a uniform bound in any dimension. 
-\end{proof}
-
-\begin{corollary} \label{cor:BoundLocalDensity}
-    Under the conditions of Theorem~\ref{TeoremOneStepConvergence}
-    there is a constant $C > 0$,
-    independent of $\epsilon$, $N$, $\theta$, and $x$,
-    such that
-    \[
-        \IE[ \langle \psi^{\epsilon,x}_s(y), \eta_t(dy) \rangle ]
-        \le C
-    \]
-    for all $s \ge 0$, $t \in [0, T]$ and $x \in \IR^d$.
-\end{corollary}
-
-\comment{This was previously just a Remark, but I wanted to use it below
-    in a place where we have to be careful of exactly what it's uniform over,
-    so I wrote out a proof.}
-
-\begin{proof}[of Corollary~\ref{cor:BoundLocalDensity}]
-    For any random variable $X$ independent of $\eta$,
-    Lemma~\ref{FirstBoundLocalDensity} implies that
-    $\IE[\rho_\epsilon * \eta_t(X)] = \IE[\langle p_{\epsilon^2}(X, y), \eta_t(dy)] \le C$.
-    The Corollary follows immediately 
-    by taking $X$ to have density $p_{T(s)}(x, \cdot)$, since
-    \begin{align*}
-        \IE[ \langle \psi^{\epsilon,x}_s(y), \eta_t(dy)\rangle ]
-        =
-        \IE[ \langle p_{T(s)+\epsilon^2}(x,y), \eta_t(dy) \rangle ]
-        =
-        \IE\left[ \int_{\IR^d} 
-            p_{T(s)}(x, z)
-            \langle p_{\epsilon^2}(z, y), \eta_t(dy) \rangle
-        dz \right] ,
-    \end{align*}
-    with $T(s)$ independent of $\eta$.
-\end{proof}
-
-\begin{corollary}
-    Let $(M_t^x)_{t \geq 0}$ be the martingale in (\ref{MartingaleProblemMolifier}).
-    Then
-    \[
-        \IE\left[ [M^x]_t \right] \leq \frac{C \theta}{ N \epsilon^{d}} ,
-    \]
-    where $C$ is independent of $\epsilon,\theta,N$. \label{Cor:ControlQVMQ}
-\end{corollary}
-
-\begin{proof}
-    We can explicitly write the quadratic variation of $M^x_t$ as
-    \[
-        [M^x]_t
-        =
-        \frac{\theta}{N} \int_0^t \langle
-            \int_{\IR^d} \psi_{t-s}^{\epsilon,x}(z)^2 q_\theta(y,dz)
-            +
-            \left(1 + \frac{F(y, \eta_s)}{\theta}\right) \psi_{t-s}^{\epsilon,x}(y)^2,
-        \eta_s(dy) \rangle  ds .
-    \]
-    Lemma~\ref{PsiBoundHS} implies that $\psi_{t-s}^{\epsilon,x}(y) \le C \epsilon^{-d}$.
-    Using this and the fact that $F(x)$ is bounded above,
-    \begin{align} \label{QuadVarBound}
-    [M^x]_t
-        &\leq
-        \frac{C \theta}{N \epsilon^d} \int_0^t \left\{
-            \langle \int \psi_{t-s}^{\epsilon,x}(z) q_\theta(y,dz), \eta_s(dy) \rangle
-            +
-            \langle \psi_{t-s}^{\epsilon,x}(y), \eta_s(dy)\rangle
-        \right\} ds 
-    \end{align}
-    We can now take expectations and use Corollary~\ref{cor:BoundLocalDensity} to prove the result.
-\end{proof}
-
-By re-using the computations in the last Corollary we can prove a certain integrability of $M_t^x$.
-
-\begin{proposition}  \label{IntegrabilityOfM}
-    Let $(M_t^x)_{t \geq 0}$ be the martingale in (\ref{MartingaleProblemMolifier}).
-    Then
-    \[
-        \int_{\IR^d} \IE\left[ (M_t^x)^2 \right] dx \leq \frac{C \theta}{ N \epsilon^{d}} ,
-    \]
-    where $C$ is independent of $\epsilon$, $\theta$, and $N$.
-\end{proposition}
-
-\begin{proof}[of Proposition \ref{IntegrabilityOfM}]
-    Recall that since $M^x_t$ is a martingale, then,
-    \[
-        \IE\left[ (M_t^x)^2 \right] = \IE\left[ [M^x]_t \right].
-    \]
-    Hence, using (\ref{QuadVarBound}),
-    \begin{align*}
-        \int_{\IR^d} &\IE\left[ M_t(x)^2 \right] dx
-        \\ & \leq
-        \frac{C \theta}{\varepsilon^d N} \int \int_0^t
-            \IE\left[ \langle \int \psi_{t-s}^{\epsilon,x}(z) q_\theta(y,dz), \eta_s(dy) \rangle
-                + \langle \psi_{t-s}^{\epsilon,x}(y),
-            \eta_s(dy)\rangle \right]
-        ds dx
-        \\ &= 
-        \frac{C \theta}{\varepsilon^d N} \int_0^t \IE \left[
-            \langle \int \left( \int \psi_{t-s}^{\epsilon,x}(z) dx \right) q_\theta(y,dz),
-            \eta_s(dy) \rangle
-            +
-            \langle \left( \int \psi_{t-s}^{\epsilon,x}(y) dx \right), \eta_s(dy)\rangle
-        \right] ds.
-    \end{align*}
-    Now, since (by Lemma~\ref{PsiBoundHS}) $\psi_t^{\epsilon, x}(y) = \IE[p_{\epsilon^2+T(t)}(x,y)]$,
-    note that
-    \begin{align*}
-        \int
-            \psi_t^{\epsilon, x}(y) dx
-            & =
-            % \int \IE[p_{\epsilon^2+T(t)}(x,y)] dx
-            % \\ &=
-            \IE\left[ \int p_{\epsilon^2+T(t)}(y,x) dx \right]
-            = 1.
-    \end{align*}
-    Thus,
-    \begin{align*}
-    \int \IE\left[ M_t(x)^2 \right] dx
-        & \leq 
-        \frac{C \theta}{\varepsilon^d N} 
-        \int_0^t \IE \left[ 
-            \langle \int  q_\theta(y,dz), \eta_s(dy) \rangle
-            +
-            \langle 1, \eta_s(dy)\rangle
-        \right] ds
-        \\ & =
-        2 \frac{C \theta}{\varepsilon^d N}
-        \int_0^t \IE[ \langle 1, \eta_s(dy) \rangle ] ds
-        \\ & \leq
-        t \frac{2 C \theta}{ \varepsilon^d N} ,
-    \end{align*}
-    proving the result.
-\end{proof}
-
-% By doing the same pattern used to prove Lemma~\ref{lem:SecondMomentMass} (replacing the use of equation (\ref{eq:MPTotalMass}) by equation (\ref{MartingaleProblemMolifier}) and the used of equation \ref{eq:quadvarMass} by Corollary~\ref{Cor:ControlQVMQ}) we can get the following result.
-
-\comment{Alison writes: previously we just referred to the proof of Lemma~\ref{lem:SecondMomentMass},
-but that was wrong.
-I think using $\theta/(N \varepsilon^d) \to 0$ this is easy, but should maybe write it out.}
-
-\comment{Peter writes: here is a proof! Maybe it's right?
-It's straightforward given everything else we do,
-but the expressions are a bit lengthy thanks to the need to have $x_1 \neq x_2$ below.
-We could replace the proof with another short description?}
-
-\begin{proposition}
-        \label{Prop:SecondMomentDensity}
-    Under the assumptions of Theorem~\ref{TeoremOneStepConvergence}
-    there is a finite constant $C$ (independent of $\epsilon, N, \theta$) such that,
-    for all $t \in [0,T]$, $x \in \IR^d$ and for big enough $N$ and $\theta$,
-    $\IE[ (\rho_\epsilon*\eta_t(x))^2] \leq C$.
-\end{proposition}
-
-\begin{proof}[of Proposition~\ref{Prop:SecondMomentDensity}]
-    In fact, we will prove that
-    \begin{align*}
-        \sup_{x_1, x_2} \IE\left[
-            \langle \psi^{\epsilon,x_1}_0(y), \eta_t(dy) \rangle
-            \langle \psi^{\epsilon,x_2}_0(y), \eta_t(dy) \rangle
-        \right]
-        \le C .
-    \end{align*}
-    The martingale properties~\eqref{timeMGP} and~\eqref{timeMGP2} imply that
-    \begin{align*}
-        &
-        \IE\left[
-            \langle \psi^{\epsilon,x_1}_0(y), \eta_t(dy) \rangle
-            \langle \psi^{\epsilon,x_2}_0(y), \eta_t(dy) \rangle
-        \right]
-        =
-        \IE\left[
-            \langle \psi^{\epsilon,x_1}_t(y), \eta_0(dy) \rangle
-            \langle \psi^{\epsilon,x_2}_t(y), \eta_0(dy) \rangle
-        \right]
-        \\ & \qquad {}
-        +
-        \int_0^t 2 \IE\left[
-            \langle \psi^{\epsilon,x_1}_{t-s}(y), \eta_s(dy) \rangle
-            \langle \psi^{\epsilon,x_2}_{t-s}(y) F(y, \eta_s), \eta_s(dy) \rangle
-        \right. \\ & \qquad \qquad \qquad \left. {} 
-            +
-            \langle \psi^{\epsilon,x_2}_{t-s}(y), \eta_s(dy) \rangle
-            \langle \psi^{\epsilon,x_1}_{t-s}(y) F(y, \eta_s), \eta_s(dy) \rangle
-            ,
-            \eta_s(dy) \rangle
-        \right] ds
-        \\ & \qquad {}
-        +
-        \int_0^t \frac{\theta}{N} \IE\left[
-            \left\langle 
-                \int_{\IR^d}
-                    \psi^{\epsilon,x_1}_{t-s}(z)
-                    \psi^{\epsilon,x_2}_{t-s}(z)
-                    q_\theta(y, dz)
-                +
-                \left(1 + F(y, \eta_s)/\theta \right)
-                    \psi^{\epsilon,x_1}_{t-s}(y)
-                    \psi^{\epsilon,x_2}_{t-s}(y)
-                ,
-                \eta_s(dy)
-            \right\rangle
-        \right] ds .
-    \end{align*}
-    The first term is bounded by our assumptions on $\eta_0$.
-    Since $F$ is bounded above, the second term is bounded by
-    \begin{align*}
-        &C \int_0^t \IE\left[
-            \langle \psi^{\epsilon,x_1}_{t-s}(y), \eta_s(dy) \rangle
-            \langle \psi^{\epsilon,x_2}_{t-s}(y), \eta_s(dy) \rangle
-        \right] ds
-        \\
-        &\qquad =
-        C \int_0^t
-        \int_{\IR^d} \int_{\IR^d}
-            \IE\left[
-                p_{T(t-s)}(x_1, z_1) p_{T(t-s)}(x_2, z_2)
-                (\rho_\epsilon * \eta_s(z_1))
-                (\rho_\epsilon * \eta_s(z_2))
-            \right] ds
-        dz_1 dz_2
-        \\
-        &\qquad \le
-        C \int_0^t
-        \sup_{z_1, z_2}
-            \IE\left[
-                (\rho_\epsilon * \eta_s(z_1))
-                (\rho_\epsilon * \eta_s(z_2))
-            \right] ds
-    \end{align*}
-
-    Using Corollary~\ref{cor:BoundLocalDensity},
-    the third term is bounded by a constant times
-    \begin{align*}
-        \int_0^t
-            \|\psi^{\epsilon,x}_{t-s}\|_\infty
-            \IE[ \langle \psi^{\epsilon,x}_{t-s}(y), \eta_s(dy) ]
-        ds 
-        \le
-        C \int_0^t \|\psi^{\epsilon,x}_{t-s}\|_\infty ds ,
-    \end{align*}
-    which can be bounded following the same iterative argument
-    as we used for equation~\ref{BoundForMollifierStart}.
-
-    This leaves us with
-    \begin{align*}
-        \sup_{x_1, x_2} \IE\left[
-            \langle \psi^{\epsilon,x_1}_0(y), \eta_t(dy) \rangle
-            \langle \psi^{\epsilon,x_2}_0(y), \eta_t(dy) \rangle
-        \right]
-        \le C  + C \int_0^t
-            \sup_{x_1, x_2} \IE\left[
-                \langle \psi^{\epsilon,x_1}_0(y), \eta_t(dy) \rangle
-                \langle \psi^{\epsilon,x_2}_0(y), \eta_t(dy) \rangle
-            \right]
-            ds,
-    \end{align*}
-    and so we can apply Gronwall's inequality.
-\end{proof}
-
-\paragraph{$C$-tightness of $\rho_\epsilon * \eta_t(x) dx$ }
-
-\begin{lemma}
-        \label{lem:density_tightness}
-    Under the assumptions of Theorem~\ref{TeoremOneStepConvergence}
-    the sequence of measure valued processes $\{ \rho*\eta_t(x) dx \}_{t \geq 0}$
-    (taking values in $D([0,T], \measures)$ is $C$-tight.
-\end{lemma}
-
-\comment{Peter: what's $C$-tightness?}
-
-\begin{proof}[of Lemma~\ref{lem:density_tightness}]
-
-    Let $f \in C_c^2$ (that is, compactly supported and with smooth second derivative).
-    We will show convergence of $\int f(x) \rho_\epsilon * \eta_t(x) dx$ (which is enough to establish weak convergence of the measures $\rho_\epsilon * \eta_t(x) dx$).
-    \comment{Alison writes: no it's not weak - this would be vague convergence. Take $f \in C^2$ to mean bounded first and second derivatives, which is weak convergence.}
-    For this note that
-    \begin{align*}
-        \int f(x) \rho_\epsilon * \eta_t(x) dx
-        &=
-        % \int \int f(x) \rho_\epsilon (x-y) \eta(dy) dx
-        % \\ & =
-        % \langle \int f(x) \rho_\epsilon(x-y) dx, \eta(dy) \rangle
-        % \\ &=
-        \langle \rho_\epsilon f(y), \eta_t(dy) \rangle .
-    \end{align*}
-    Substituting this into the martingale problem for $\eta_t$, \eqref{mgp1},
-    we get
-    \begin{align}
-         \label{MGPT_epsilon}
-    \langle \rho_{\epsilon} * f, \eta_t \rangle
-        & = \nonumber 
-        \langle \rho_{\epsilon} * f, \eta_0 \rangle
-        +
-        \theta \int_0^t
-            \langle
-                \int (\rho_{\epsilon} * f(z) - \rho_{\epsilon} * f(y)) q_\theta(y, dz) ,
-                \eta_s(dy)
-            \rangle
-        ds
-        \\ & {}
-        +
-        \int_0^t \langle \rho_\epsilon * f(y) F(y, \eta_s), \eta_s(dy) \rangle ds
-        + \widehat{M}_t,
-    \end{align}
-    with $\widehat{M}_t$ a martingale. Now note that
-    by the Intermediate Value Theorem,
-    \begin{align}
-        \label{ShortBoundLaplacianHS}
-        \left| \theta \int (\rho_{\epsilon} * f(z) - \rho_{\epsilon} * f(y)) q_\theta(y,z) dz \right|
-        &=
-        \left| \theta( p_{\epsilon^2 + 1/\theta} * f(y) - p_{\epsilon^2} * f(y) ) \right| \nonumber
-        \\ &=
-        \left| \Delta p_{\epsilon+1/\tilde{\theta}} * f(y) \right| \nonumber
-        \\ &=
-        \left| p_{\epsilon^2 + 1/\tilde{\theta}} * \Delta f(y) \right|
-        \leq
-        \| \Delta f \|_{\infty}
-    \end{align}
-    for some $\tilde{\theta} \in [0,1/\theta]$.
-    Proceeding as in the proof of Lemma~\ref{lem:eta_f_bound},
-    we can use that $F(x)$ is bounded above and Gronwall's inequality to conclude that
-    \[
-        \IE\left[\langle \rho_{\epsilon} * f(y) F(y, \eta_t), \eta_t(dy) \rangle \right]
-        \text{ is uniformly bounded for } t \in [0,T].
-    \]
-
-    The quadratic variation of $\widehat{M}_t$ is
-    \[
-        [ \widehat{M} ]_t
-        =
-        \frac{\theta}{N} \int_0^t \langle
-            p_{1/\theta}*(p_{\epsilon^2} * f(\cdot)^2)(y)
-            +
-            \left( 1 + \frac{F(\rho_\epsilon*\eta_s(y))}{\theta} \right)
-            p_{\epsilon^2} * f(y)^2
-            ,
-            \eta_s(dy)
-        \rangle ds ,
-    \]
-    so using boundedness of $f$ and $F$,
-    \begin{align*}
-        \IE\left[ [\widehat{M}]_t \right]
-        \leq
-        \frac{\theta}{N} \| f \|_\infty C
-        \int_0^t \mathbb{E}\left[ \langle 1, \eta_s(dy) \right] ds
-        <
-        C \frac{\theta}{N} t ,
-    \end{align*}
-    where in the last inequality we have used Lemma~\ref{Lemma:UniformlyBoundedMass}.
-    Hence, using the Burkholder-Davis-Gundy and Jensen's inequalities we can conclude that
-    \[
-        \IE[\sup_{0 \leq t \leq T} |\widehat{M}_t| ]
-        \le
-        C
-        \IE\left[ [\widehat{M}]_t \right]^{1/2}
-        \le
-        \sqrt{ C \frac{\theta}{N} T } .
-    \]
-    Therefore, by taking supremum and expectation and in \eqref{MGPT_epsilon}
-    we conclude that
-    \begin{equation}
-        \label{eq:boundedIntegralAgainstf}
-        \IE[ \sup_{0 \leq t \leq T} \langle T_{\epsilon^2} f, \eta_t \rangle ]
-        \text{ is uniformly bounded (for fixed } f \text{)}
-    \end{equation}
-    To conclude $C$-tightness we show that, for $T>0$, and $\alpha > 0$
-    there is some $\delta >0$ so that for $\theta$ and $N$ large enough,
-    \begin{align}
-        &
-        \IP\left[
-            \sup_{s,t \in [0,T], |s-t| < \delta}
-            \left|
-                \int f(x) \rho_\epsilon*\eta_s(x) dx
-                -
-                \int f(x) \rho_\epsilon*\eta_t(x) dx
-            \right|
-            >
-            \alpha
-        \right]
-        \\ &=
-        \IP\left[
-            \sup_{s,t \in [0,T], |s-t| < \delta}
-            \left|
-                \langle p_{\epsilon^2} * f, \eta_s \rangle
-                - \langle p_{\epsilon^2} * f, \eta_t \rangle
-            \right|
-            >
-            \alpha
-        \right]
-        <
-        \alpha \label{conditionCtightness}
-    \end{align}
-    But, from our estimates above, we have
-    \begin{align*}
-        \left|
-        \langle p_{\epsilon^2} * f, \eta_s \rangle
-        -
-        \langle p_{\epsilon^2} * f, \eta_t \rangle
-        \right|
-        \leq
-        ( \| \Delta f \|_\infty + C_F \|f\|_\infty) |u-v|
-        \sup_{0 \leq u \leq T } \langle 1, \eta_u \rangle
-        +
-        \sup_{u \leq T} |\widehat{M}_u| .
-    \end{align*}
-    Taking expectations we get,
-    \begin{equation}
-        \IE\left[ \left|
-            \langle T_{\epsilon^2} f, \eta_s \rangle
-            -
-            \langle T_{\epsilon^2} f, \eta_t \rangle
-        \right| \right]
-        \leq
-        \widehat{C} |s-t|
-        +
-        \widehat{C} \left( \frac{\theta}{N} T \right)^{1/2} .
-    \end{equation}
-    Using this and Markov's inequality give that \eqref{conditionCtightness}
-    holds with $\delta = \alpha/(3 \widehat{C}|s-t|)$,
-    for $N$, $\theta$ big enough so $\widehat{C}\sqrt{T\theta/N}$ is bounded by $\alpha/3$.
-    (Note the last condition is possible by \eqref{ConditionsForConvergence}.)
-    Thus we have concluded $C$-tightness. 
-\end{proof}
-
-\begin{remark} \label{remark:BoundedIntegral}
-Similar as we got equation (\ref{eq:boundedIntegralAgainstf}), from equation \ref{MGPT_epsilon} we can conclude that
-\[ \IE\left[\sup_{0 \leq t \leq T} \int \rho_{\epsilon/2} * \eta_t(x) dx \right] = C < \infty. \]
-By using this and the same pattern used to prove Lemma~\ref{lem:SecondMomentMass}, we can then conclude that,
-\[ \IE\left[  \sup_{0 \leq t \leq T} \int \left(\rho_{\epsilon/2} * \eta_t(x) \right)^2 dx \right] = C < \infty. \]
-Since,
-\begin{align*}
-\langle \rho_\epsilon * \eta_t(z), \eta(dz) \rangle & = \sum_{y \in \eta_t} \sum_{z \in \eta_t} \rho_\epsilon(y-z) \eta(z) \eta(y) \\ &= \int  \sum_{y \in \eta_t} \sum_{z \in \eta_t} \rho_{\epsilon/2}(y-x) \rho_{\epsilon/2}(z-x) \eta(z) \eta(y) \\ &= \int (\rho_{\epsilon/2}*\eta_t(x))^2 dx.
-\end{align*}
-This allows us to conclude that $\IE[\langle \rho_\epsilon*\eta_t(z),\eta_t(dz) \rangle ] < \infty$. This bound will be useful in the next section.
-\end{remark}
-
-\subsubsection{Identifying the limit}
-
-\paragraph{Continuity estimate}
-
-In this section we prove the following continuity estimate for $\rho_\epsilon * \eta_t(x)$.
-\begin{proposition} \label{ContinuityEstimate}
-Under the same conditions of Theorem~\ref{TeoremOneStepConvergence} we have that for all $x \in \IR^d$, $\delta>0$,
-\[
-\int |\rho_\epsilon*\eta_s(x) -\rho_\epsilon*\eta_s(y)| \rho_\delta(x-y) dy \]
-is bounded by
-\begin{align*}
-\frac{\delta}{\sqrt{\epsilon^2+s}} \langle 1,\eta_0(dz) \rangle &+ \int_0^s \frac{\delta}{\sqrt{\epsilon^2+s-r}} (\langle 1, \eta_r(dz)\rangle + \langle \rho_\epsilon*\eta_r(z), \eta_r(dz)\rangle)dr \\ &+ |M_s(x)| + \int |M_s(y)| \rho_\delta(y-x)dy + \mathcal{O}\left( \frac{1}{\epsilon^2 \theta}\right)
-\end{align*} 
-\end{proposition}
-where $M_s(x)$ is the martingale in (\ref{MartingaleProblemMolifier}).
-\begin{proof}
-Recall from our assumptions that $|F'(x)1_{x>0}|$ is uniformly bounded. Hence, we can always write,
-\begin{align} \label{StrongBoundOnF}
-|F(\rho_\epsilon*\eta_t(x))| \leq |F(0)| + C \rho_\epsilon*\eta_t(x)
-\end{align}
-So, by (\ref{MartingaleProblemMolifier}) we can write,
-\begin{align}
-& |\rho_\epsilon*\eta_t(x)-\rho_\epsilon*\eta_t(y)| \nonumber \\ &= |\langle \rho_\epsilon(y-z)-\rho_\epsilon(x-z),\eta_t(dz) \rangle | \nonumber\\ &\leq  |M_t(x)-M_t(y)|  +\langle \psi_t^{\epsilon,y}(z)-\psi_t^{\epsilon,x}(z), \eta_0(dz)\rangle \nonumber \\ &+ C\int_0^t \langle |\psi_{t-s}^{\epsilon,x}(z) - \psi_{t-s}^{\epsilon, y}(z) |, \eta_s(dz) \rangle  ds | \\ &+ C \int_0^t \langle |\psi_{t-s}^{\epsilon,x}(z) - \psi_{t-s}^{\epsilon, y}(z) | \rho_\epsilon*\eta(z), \eta_s(dz) \rangle  ds | \label{eq:bound1CE} \end{align}
-By using Lemma~\ref{Lemma:BoundPsiHS2} we can then write, 
-\begin{align*}
- \int &|\rho_\epsilon*\eta_s(x) -\rho_\epsilon*\eta_s(y)| \rho_\delta(x-y) dy  \leq \int |p_{\epsilon^2+s}(y,z)-p_{\epsilon^2+s}(x,z)|\eta_0(dz) \rho_\delta(x-y)dy \\&+ C\int_0^s \langle p_{\epsilon^2+s-r}(y,z)-p_{\epsilon^2+s-r}(x,z)|, \eta_r(dz) \rangle \rho_\delta (x-y) dr  \\  & + C \int_0^s \langle |p_{\epsilon+s-r}(y,z) - p_{\epsilon+s-r}(x,z) | \rho_\epsilon*\eta_r(z), \eta_r(dz) \rangle  dr | + \int|M_s(y)-M_s(x)| \rho_\delta(y-x)dy  \\  & + \frac{C}{\epsilon^2 \theta} \int \langle \rho_\epsilon*\eta(z),\eta_s(dz)\rangle ds   +\mathcal{O}\left( \frac{1}{\epsilon^2 \theta} \right)
-\end{align*}
-By Remark~\ref{remark:BoundedIntegral} the last integral term is of order $(\epsilon^2 \theta)^{-1}$.
-By using Lemma~\ref{Lemma:ContinuityHS} we get that the contribution of the first three terms is bounded by,
-\begin{align*}
-\int &\frac{|y-x|}{\sqrt{\epsilon^2+s}} \rho_{\delta}(y-x) dy \langle 1, \eta_0(dz)\rangle + \int \int_0^s  \langle \frac{|y-x|}{\sqrt{\sqrt{\epsilon^2+s-r}}}, \eta_r(dz) \rangle \rho_\delta(x-y) dy dr \\ & +  \int \int_0^s \langle \frac{|y-x| \rho_\epsilon*\eta(z)}{\sqrt{\epsilon^2+s-r}}, \eta_r(dz) \rangle \rho_\delta(y-x) dy dr \\ & \leq \frac{\delta}{\sqrt{\epsilon^2+s}} \langle 1, \eta_0(dz) \rangle + \int_0^s \frac{\delta}{\sqrt{\epsilon^2+s-r}} (\langle 1, \eta_r(dz) \rangle + \langle \rho_\epsilon*\eta_r(z), \eta_r(dz) \rangle) dr.
-\end{align*}
-To finish the proof just notice that,
-\begin{align*}
-\int |M_s(y)-M_s(x)| \rho_\delta(y-x)dy \leq |M_s(x)| + \int |M_s(y)| \rho_\delta(y-x)dy.
-\end{align*}
-\end{proof}
-
-\paragraph{Identifying the limit of $\langle T_{\epsilon^2} f(y), \eta_t (dy) \rangle$.}
-We now prove the identification of the limit.
-We recall that, the main difficulty, is the non-linear term of the martingale problem.
-To deal with them, our first step would prove that an approximation of the form:
-\begin{align*}
-\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\eta_s(dy)), \eta_s(dy) \rangle \sim \langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \eta_s(dy)), \rho_\epsilon * \eta_s(y) dy \rangle
-\end{align*}
-This is the content of the next result.
-\begin{proposition} \label{CuadraticApprox}
-Under the condition of Theorem~\ref{TeoremOneStepConvergence} there is a constant $C>0$ such that
-\begin{equation*}
-\int_0^t \IE[|\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\eta_s(dy)), \eta_s(dy) \rangle - \langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \eta_s(dy)), \rho_\epsilon * \eta_s(y) dy \rangle|]
-\end{equation*}
-is bounded by,
-\begin{equation*}
-\mathcal{O}\left( \frac{1}{\epsilon^2 \theta} + \epsilon^2 + \epsilon + \epsilon^{1/3}  + \left( \frac{\theta}{N \epsilon^d} \right)^{1/2}\right)
-\end{equation*}
-\end{proposition}
-\begin{proof}
-We first note that,
-\begin{align*}
-    &\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\eta_s(dy)), \eta_s(dy) \rangle - \langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \eta_s(dy)), \rho_\epsilon * \eta_s(y) dy \rangle \\ & = \langle \int T_{\epsilon^2} f(y) F(\rho_\epsilon * \eta_s(y))\rho_\epsilon(y-w) dy, \eta_s(dw)\rangle - \langle T_{\epsilon^2} f(w) F(\rho_\epsilon*\eta_s(w)), \eta_s(dw) \rangle \\ &= \langle \int \{ T_{\epsilon^2} f(y) F(\rho_\epsilon*\eta_s(y))-T_{\epsilon^2}f(w) F(\rho_\epsilon*\eta_s(w))\} \rho_\epsilon(w-y)dy, \eta_s(dw) \rangle.
-\end{align*}
-Let us denote $I$ the integral against $dy$ in the last expresion, that is 
-\[ I :=  \int \{ T_{\epsilon^2} f(y) F(\rho_\epsilon*\eta_s(y))-T_{\epsilon^2}f(w) F(\rho_\epsilon*\eta_s(w))\} \rho_\epsilon(w-y)dy \]
-And note that $|I|$ is bounded by
-\begin{align}
-& \int \left\{ |F(\rho_\epsilon*\eta_s(y))-F(\rho_\epsilon*\eta_s(w))|T_{\epsilon^2}f(y)+F(\rho_\epsilon*\eta_s(w))|T_{\epsilon^2}f(y)-T_{\epsilon^2}f(w))|\right\} \rho_{\epsilon}(w-y)dy \nonumber \\ &\leq \int C |\rho_\epsilon*\eta_s(y)-\rho_\epsilon*\eta_s(w)| \rho_\epsilon(w-y)dy + C \epsilon^2 \Vert \Delta f \Vert_2 \label{FirstBoundCT}
-\end{align}
-where in the last inequality we have used $F(x)1_{x>0}$ and $|F'(x)1_{x>0}|$ are both bounded above.
-We want to use Proposition~\ref{ContinuityEstimate} in the last equation, but the terms that we would obtain would be too hard to control unless we first control the total mass and their noise.
-Let us define,
-\begin{align*}
-A_{t} &:= \left\{ \sup_{0 \leq s \leq t} \langle 1, \eta_s(dz) \rangle > \epsilon^{-2/3} \right\}. \end{align*}
-Note that, by Markov's inequality and Lemma~\ref{Lemma:UniformlyBoundedMass} the event $A_{t}$ has probability of order $\epsilon^{2/3}$.
-Hence, writing $I = I(1_{A^c_{t}} + 1_{A_{t}})$ and proceeding as before we can use Proposition~\ref{ContinuityEstimate} in (\ref{FirstBoundCT}) to get,
-\begin{align}
-&\int_0^t \IE[|\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\eta_s(dy)), \eta_s(dy) \rangle - \langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \eta_s(dy)), \rho_\epsilon * \eta_s(y) dy \rangle|] \nonumber \\ &\leq   \int_0^t \IE[ \frac{\epsilon}{\sqrt{\epsilon^2 + s}} \langle 1,\eta_0(dz) \rangle \langle 1, \eta_s(dz)\rangle ] ds +  \int_0^t \IE[  \int_0^s \frac{\epsilon}{\sqrt{\epsilon^2 + s - r}} \langle 1, \eta_r (dz) \rangle dr \langle 1, \eta_s(dz) \rangle  ] ds \nonumber\\ & + \int_0^t \IE[   1_{A^c_{t}} \int_0^s \frac{\epsilon}{\sqrt{\epsilon^2 + s - r}} \langle \rho_\epsilon*\eta_r(z), \eta_r(dz) \rangle dr \langle 1, \eta_s(dz) \rangle  ] ds + \int_0^t \IE[\langle |M_s(x)|,\eta_s(dx) \rangle] ds \nonumber \\ &+ \int_0^t \int \IE[|M_s(y)|\rho_\epsilon*\eta_s(y)] dy ds  +\mathcal{O}\left( \frac{1}{\epsilon^2 \theta} + \epsilon^2 + \epsilon^{1/3} \right)  \label{ThingsToBound}
-\end{align}
-Note we have bounded $1_{A^c_{t}}$ by one in all the terms expect the third one, which is the one that will require it.
-For the first two term we can use our hypothesis on the initial condition and that $2 ab \leq a^2+b^2$ to get that their contribution is bounded by,
-\begin{align*}
-\int_0^t C \frac{\epsilon}{\sqrt{\epsilon^2+s}}\IE[\langle 1, \eta_s(dz) \rangle] ds + \int_0^t \int_0^s \frac{\epsilon}{\sqrt{\epsilon^2+s-r}}\IE[\langle 1, \eta_r(dz)\rangle^2 + \langle 1, \eta_s(dz)\rangle^2] ds,
-\end{align*}
-which, due to Lemma~\ref{lem:SecondMomentMass}, is of order $\epsilon$. To bound the third integral term we use the event $A_{t}$ to get it is bounded by,
-\begin{align*}
-\int_0^t \int_0^s \frac{\epsilon^{1/3}}{\sqrt{\epsilon^2+s-r}} \IE[ \langle \rho*\eta_r(z), \eta(dz) \rangle] dr ds = \mathcal{O}(\epsilon^{1/3})
-\end{align*}
-where we have used Remark~\ref{remark:BoundedIntegral}. 
-We now proceed to control the terms with martingales in (\ref{ThingsToBound}). For the first one note that, by using Cauchy-Schwartz in $L^2(\mathbb{P})$ and then in $L^2(\IR^d)$,
-\begin{align}
-\int_0^t \int \IE[|M_s(y)|\rho_\epsilon*\eta_s(y)] dy ds & \leq \int_0^t \int \IE[|M^2_s(y)]^{1/2} \IE[\rho_\epsilon * \eta_s(y)^2]^{1/2} dy dy \nonumber \\ & \leq \int_0^t \left( \int \IE[|M_s(y)^2|] dy \int \IE[\rho_\epsilon * \eta_s(y)^2] dy \right)^{1/2} ds  \nonumber \\ &= \mathcal{O}\left( \left( \frac{\theta}{N \epsilon^d} \right)^{1/2} \right)
-\label{TwiceCS} \end{align}
-where in the last inequality we used Proposition~\ref{IntegrabilityOfM} and Remark~\ref{remark:BoundedIntegral}.
-For the second term with a Martingale in (\ref{ThingsToBound}) we need to proceed with more care.
-For this we first rewrite explicitly the dependency on $\epsilon$ of $M_t(x)$ by using $M_t^{\varepsilon^2}(x)$.
-We can then write from (\ref{MartingaleProblemMolifier}) and Lemma~\ref{Lemma:BoundPsiHS2}) that,
-\begin{align*}
- M_t^{\epsilon^2}(x) &= \langle p_{\epsilon^2}(x,y), \eta_t(dx) \rangle - \langle p_{t + \epsilon^2}(x,y), \eta_0(dx) \rangle \\ &- \int_0^t \langle F(\rho_\epsilon*\eta_s(y)) p_{t-s+\epsilon^2}(x,y), \eta_s(dy) \rangle ds + \mathcal{O}\left(\frac{1}{\epsilon^2 \theta} \right) \end{align*}
- It follows then that $M_s^{\epsilon^2}= p_{\epsilon^2/2}*M_s^{\epsilon^2/2} + \mathcal{O}\left(1/\epsilon^2 \theta\right)$. Using this we can then bound,
- \begin{align*}
-\int_0^t &\IE[ \langle |M_s^{\epsilon^2}(x)|, \eta_s(dx) \rangle ] ds \\ &= \int_0^t \IE[ \langle | p_{\epsilon^2/2}*M_s^{\epsilon^2/2}(x)|, \eta_s(dx) \rangle] ds \\ & \leq  \int_0^t \IE[ \langle p_{\epsilon^2/2}*| M_s^{\epsilon^2/2}(x)|, \eta_s(dx) \rangle] ds \\ &= \int_0^t \IE[ \langle \int p_{\epsilon^2/2}(x,y) |M_s^{\epsilon^2/2}(y)|dy, \eta_s(dx) \rangle] ds \\ &= \int_0^t \IE[ \int |M_s^{\epsilon^2/2}(y)| p_{\epsilon^2/2}*\eta_s(y) dy ] ds \\ &= \int_0^t \int \IE[ M_s^{\epsilon^2/2}(y)| p_{\epsilon^2/2} * \eta_s(dy)] dy ds
- \end{align*}
- An analogues computation as the one performed to obatin (\ref{TwiceCS}) gives the last term is $\mathcal{O}\left( \left( \frac{\theta}{N \epsilon^d} \right)^{1/2} \right)$.
- \end{proof}
-Now, to finish the characterisation of the limit, it remain to show that:
-\[ \int f(x) \rho_\epsilon * \eta_t(x) F(\rho_\epsilon * \eta_t(x)) dx \rightarrow \int f(x) u_t(x) F(u_t(x)) dx \]
-where $u_t(x)dx$ is the limit of $\rho_\epsilon*\eta_t(x)dx$.
-As we mention as the start of this note this does now follow from weak convergence of $\rho_\epsilon*\eta(x)dx$.
-For proving this, we recall that $F(x)$ is a polynomial, so we just need to prove said convergence of powers of $(\rho_\epsilon*\eta_t(x))$.
-To illustrate how to proceed, we will prove the convergence,
-\begin{equation} \label{eq:QuadConvergence} \int f(x) \rho_\epsilon * \eta_t(x) \rho_\epsilon * \eta_t(x)^2 dx \rightarrow \int f(x) u_t(x) u_t(x)^2 dx \end{equation}
-with the understanding that converge of higher powers will follows in a similar fashion with rougher notation. To achieve (\ref{eq:QuadConvergence}) we proceed by proving an approximation of the form,
-\begin{equation}
-\label{aprox2}
-\langle f, (\eta_s * \rho_\epsilon)^2 \rangle \sim \int \int f(z) (\rho_\epsilon * \eta_s)(z) \rho_\delta (z-y) (\rho_\epsilon * \eta_s)(y) dz dy.
-\end{equation}
-Before proceeding with a proof of (\ref{aprox2}), we argue why this is enough to conclude Theorem~\ref{TeoremOneStepConvergence}. Note the right hand side of (\ref{aprox2}) can written as
-\[ \int_{\IR^{d} \otimes \IR^d} f(z) \rho_\delta(z-y) (\rho_\epsilon * \eta_s(dz) \otimes (\rho_\epsilon * \eta_s(dy)). \]
-Weak convergence of $\rho_\epsilon * \eta$ (plus continuity of the mapping $(z,y) \rightarrow f(z) \rho_\delta(z-y)$) gives that the last term converges in $L^1$ to
-\[ \int_{\IR^{d} \otimes \IR^d} f(z) \rho_\delta(z-y) (u_s(dz) \otimes (u_s(dy)). \]
-Finally, by a direct analogue of (\ref{aprox2}) we can say that
-\begin{equation} \int_{\IR^{d} \otimes \IR^d} f(z) \rho_\delta(z-y) (u_s(dz) \otimes (u_s(dy)) \sim \langle f(x), u_s^2(x) dx \rangle. \label{aprox3} \end{equation}
-which is what we seek. We proceed now to prove (\ref{aprox2}), with the understanding that (\ref{aprox3}) follows in a similar way and give even better error terms.
-\begin{theorem}
-Under the conditions of Theorem~\ref{TeoremOneStepConvergence}, we have that
-\begin{align*}
-\int_0^t \mathbb{E}&\left[\left| \langle f(y), (\eta_s * \rho_\epsilon(y))^2) dy\rangle - \int \int f(y) (\rho_\epsilon * \eta_s)(z) \rho_\delta (z-y) (\rho_\epsilon * \eta_s)(y) dz dy.
-\right|\right] ds
-\end{align*}
-is bounded by,
-\[  \mathcal{O}\left(\delta^{1/3} + \delta +  \frac{1}{\epsilon^2 \theta} + \left( \frac{\theta}{N \epsilon^2}\right)^{1/2} \right)  \]
-in particular, under (\ref{ConditionsForConvergence}), the last term goes to $0$ uniformly in $\theta,\epsilon,N$ and $\delta$ (when $\delta$, $\epsilon$ go to $0$ and $N,\theta$ to infinity).
-\end{theorem}
-\begin{proof}
-First note,
-\begin{align}
-&\int_0^t \mathbb{E}\left[| \langle f(y), (\eta_s * \rho_\epsilon(y))^2) dy \rangle - \int \int f(y) (\rho_\epsilon * \eta_s)(z) \rho_\delta (z-y) (\rho_\epsilon * \eta_s)(y) dz dy.
-|\right] ds \nonumber \\ &\leq  \Vert f \Vert_\infty \int_{S_f}  \int_0^t  \mathbb{E}\left[ \int \left\{ \left|(\rho_\epsilon * \eta_s)(y)-(\rho_\epsilon * \eta_s)(z) \right|   \rho_\delta(z-y) dz \right\} (\rho_\epsilon *\eta_s)(y) \right] ds  dy \label{b1}
-\end{align}
-We want then to bound (\ref{b1}) by using Proposition~\ref{ContinuityEstimate}. For this consider the event,
-\[ B_{s,y} := \{ \rho_\epsilon * \eta_s(y) > \delta^{-2/3} \}. \]
-Note that by Markov's inequality and Lemma~\ref{FirstBoundLocalDensity} the event $B_{s,y}$ has probability of order $\delta^{2/3}$ (and independent of $s$ and $y$).
-Thus, proceeding as how get (\ref{ThingsToBound}), the integral against $ds$ in the right hand side of (\ref{b1}) is bounded by
-\begin{align}
-&\int_0^t \IE[ \frac{\delta}{\sqrt{\epsilon^2 + s}} \langle 1,\eta_0(dz) \rangle (\rho_\epsilon *\eta_s)(y) ] ds +  \int_0^t \IE[  \int_0^s \frac{\delta}{\sqrt{\epsilon^2 + s - r}} \langle 1, \eta_r (dz) \rangle dr(\rho_\epsilon *\eta_s)(y)  ] ds \nonumber\\ & + \int_0^t \IE[   1_{B^c_{s,\delta}} \int_0^s \frac{\delta}{\sqrt{\epsilon^2 + s - r}} \langle \rho_\epsilon*\eta_r(z), \eta_r(dz) \rangle dr (\rho_\epsilon *\eta_s)(y) ] ds + \int_0^t \IE[\langle |M_s(x)|,\eta_s(dx) \rangle] ds \nonumber \\ & + \int_0^t  \IE[|M_s(y)|\rho_{\epsilon+\delta}*\eta_s(y)] ds  +\mathcal{O}\left( \frac{1}{\epsilon^2 \theta} + \delta^{1/3} \right)  \label{ThingsToBound2}
-\end{align}
-From this point onward we can proceed as how we bounded (\ref{ThingsToBound}) in Proposition~\ref{CuadraticApprox} to obtain that the right hand side of (\ref{b1}) is bounded by,
-\[  \mathcal{O}\left(\delta^{1/3} + \delta+ \frac{1}{\epsilon^2 \theta} + \left( \frac{\theta}{N \epsilon^2}\right)^{1/2} \right)  \]
-Concluding the result.
-\end{proof}
-
-\paragraph{Conclusion}
-Under the condition (\ref{ConditionsForConvergence}) we have that all the errors in our approximations go to $0$.
-It is then we can deduce that quadratic (and analogously, higher order) terms in the martingale problem for $\rho_\epsilon*\eta_t(x)dx$, (\ref{MGPT_epsilon}), converges to the corresponding term of the weak limit.
-Any linear term converge trivially by weak convergence.
-By a Taylor's expansion we can also conclude that,
-\begin{align*}
-\int_0^t \langle \mathcal{L}^\theta T_{\epsilon^2} f, \eta_s(dx)\rangle ds &= \int_0^t \langle \frac{1}{2} \Delta T_{\epsilon^2} f(x), \eta_s(dx) \rangle + \mathcal{O}(\theta^{-1}) 
-\\ &= \int_0^t \langle \frac{1}{2} \Delta f(x), \rho_\epsilon* \eta_s(x) dx \rangle ds + \mathcal{O}(\theta^{-1} + \epsilon).
-\end{align*}
-Thus, by weak convergence we can deduce
-\[ \int_0^t \langle \mathcal{L}^\theta T_{\epsilon^2} f, \eta_s(dx)\rangle ds \rightarrow \int_0^t \langle \frac{1}{2} \Delta f(x), u_s(x) dx \rangle ds \]
-Putting all the convergences together, this identifies the limit of $\rho_\epsilon*\eta_s(x)dx$ as we have claimed in Theorem~\ref{TeoremOneStepConvergence}.
-
-\todo[inline]{END OneStepConvergence}
-
-% % % % % % % % % % % % %
-\subsection{Tightness of the Lines of Descent}
-    \label{sec:lookdown_convergence}
-
-Now we prove the main theorem on convergence of the lookdown process, 
-Theorem~\ref{thm:lookdown_convergence}.
-This follows a similar pattern as the the proofs of convergence for the population process
-in Section~\ref{sec:population_density_proof},
-although we will need additional estimates to ensure that
-trajectories of individual lines of descent converge,
-not just the population process.
-
-\begin{proof}[Proof of Theorem~\ref{thm:lookdown_convergence}]
-    As in Section~\ref{sec:population_density_proof},
-    the theorem will follow from tightness,
-    ensuring convergence along subsequences,
-    and characterization of the limit.
-    This time, the processes $\lp^N$ take values in $\lpmeasures$,
-    the space of locally finite measures on space $\times$ levels.
-    (They will in fact be point measures, including the limit,
-    but that is a consequence of this theorem.)
-    Again, tightness will follow from a compact containment condition,
-    tightness of one-dimensional distributions,
-    and an application of \citet{EK} Theorem~3.9.1.
-    We show that the martingale properties are preserved in the limit
-    in Section~\ref{sec:lookdown_generator_proofs}.
-    \comment{TODO: write and refer to lemma?}
-
-    Lines of descent can escape to infinite level in finite time,
-    and so we endow $\lpmeasures$ with the vague topology ``in the level coordinate'',
-    i.e., the topology induced by test functions on $\overline{\IR^d} \times [0,\infty)$
-    of the form $f(x) g(u)$, where $f \in C_b(\overline{\IR^d})$ is bounded and continuous
-    and $g \in C_c([0,\infty))$ is continuous with compact support.
-    In this topology, compact containment follows from
-    tightness of the spatial and level motions of a single line of descent
-    (Lemmas~\ref{lem: tightness of individual spatial trajectory}
-    and~\ref{lem:tightness of levels}, respectively),
-    and
-    tightness of $\lp^N(\IR^d \times [0, u_0])$ for each $u_0$
-    (i.e., the number of individuals with level below $u_0$).
-
-    Finally, we must show that the limiting lookdown process $\lp$
-    projects to the limiting process $\eta$, i.e., a solution of the martingale
-    problem in Theorem~\ref{thm:nonlocal_convergence}.
-    Let $N_k \to \infty$ be a sequence along which $\lp^{N_k}$ converges.
-    However, by Theorem~\ref{thm:nonlocal_convergence},
-    there is a subsequence $N_{k(j)}$ along which the projected population processes
-    $\eta^{N_{k(j)}}$ converge, and the limit solves the martingale problem.
-    This implies that any limit of $\lp^N$ projects to a population process $\eta$
-    solving the martingale problem of Theorem~\ref{thm:nonlocal_convergence}.
-
-\comment{MAKE THIS BELOW A LEMMA?}
-
-% BEGIN OLD STUFF
-To prove that the lookdown representation is tight, we generalise the vague
-    topology to the setting of measure-valued processes. For a detailed
-    description of the vague topology, refer to Appendix \ref{sec: Empirical
-    Measure Topology}.
-
-We will lay out the steps we follow to prove tightness. First of all, we will
-    show that compact containment condition is satisfied if we can control the
-    total mass of particles in our system living in a finite region in space
-    with a level lower than some $u_{*}$. Since a control on total mass has
-    already been shown in Lemma \ref{lem:eta_compact_containment}, we have
-    immediately established compact containment condition for our lookdown
-    processes.
-
-Then, we apply Theorem A 2.4 in \cite{kallenberg1997foundations} (Theorem
-    \ref{teo: Vague Relative Compactness through Projection}) and use a
-    corollary of Stone-Weierstrass Theorem (Lemma \ref{lem: Dense set for test
-    functions on empirical measures}) to show that our lookdown representation
-    $\{\xi^N_t: N \in \mathbb{N}\}$ is tight as a $\mathcal{M}(\IR^d
-    \times [0, \infty])$-valued stochastic process in the vague topology as
-    long as $\{F_g(\xi^N_t): N \in \mathbb{N}\}$ is tight as real-valued
-    stochastic processes for a huge class of $F_g$. Explicitly, $F_g(\xi):=
-    \prod_{(x_i,u_i)\in \xi}g(x_i,u_i)$, where $g(x,u)$ satisfies the property
-    that $g(x,u) = 1 $ for all $u \geq u_{*}$ for some $u_{*}>0$.
-% END OLD STUFF
-
-    The process we consider is similar to the state-dependent branching processes
-    of \citet{KR}, so one might expect that the proofs there would carry over with little change.
-    However, there is an important difference:
-    Recall that the level $U_a(t)$ of a line of descent evolves as
-    $$
-    \dot u 
-    =
-    c(x, \eta)
-    u^2
-    - b(x, \eta) ,
-    $$
-    where
-    \begin{align*}
-        c(x, \eta) &= \frac{\theta}{N} \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q(x, dy) \\
-        \text{and}\qquad
-        b(x, \eta)
-        &=
-        \theta \gamma(x, \eta) \int_{\IR^d} \left(r(y, \eta) - r(x, \eta)\right) q(x, dy)
-        + F(x, \eta) 
-    \end{align*}
-    (see equations \eqref{eqn:level_generator} and \eqref{eqn:b_limit}),
-    where $c(x, \eta) \ge 0$ and $b(x, \eta)$ may take either sign.
-    In \citet{kurtz/rodrigues:2011}, $b$ was bounded above and $c$ was bounded away from zero,
-    so they noted that if $U_a(t) \ge b/c$
-    lines of descent would only move upwards from that time onwards.
-    This allows the processes to be jointly and simultaneously constructed
-    for all values of $N$, with a pointwise embedding
-    of $(\xi^N_t)_{t \ge 0}$ within $(\xi^{M})_{t \ge 0}$ for $b/c < N < M$.
-    In other words, individuals with levels above $N > b/c$ at time $t_0$
-    do not affect $(\lp^N_t)_{t \ge t_0}$,
-    thus allowing a comparison of the number of lines of descent below level $u_0$
-    to a branching process.
-    Although we have provided a
-    joint construction of $\lp^N$ for all $N$ in Section~\ref{sec: individual lines of descent},
-    it does not have this monotonicity:
-    for one thing, $b$ and $c$ depend on the population process $\eta$
-    and so all individuals can affect all other ones (even those with lower levels).
-    Furthermore, in the deterministic case $\theta/N$ and hence $c$ converge to zero,
-    and so lines of descent with arbitrarily high level may drift back downwards.
-    Indeed, this must be the case if the population persists,
-    since in the deterministic case there is no branching.
-    In our case $b$ and $c$ depend on the state of the population,
-    so we have no such monotonicity.
-
-    To get around this,
-    first note that both $b$ and $c$ are uniformly bounded above since $\gamma$, $r$ and $F$ are.
-    Also note that by \plr{TODO},
-    for any $\delta > 0$ we can find a $K$ such that
-    $$
-    \IP\left\{
-        \sup_{0 \le t \le T} \sup_x \smooth{F} \eta_t(x) < K
-        \right\} < \delta,
-    $$
-    uniformly in $N$ and over a compact set of initial conditions.
-    Since $F$ is uniformly continuous, this implies that $\sup_{0 \le t \le T} \sup_x F(x, \eta_t)$
-    is similarly tight,
-    as well as the rate of downward drift of the level of a line of descent,
-    i.e., there is a $\bar b$ such that $b(x, \eta_t) \le \bar b$
-    on a set of probability at least $1-\delta$ as well.
-    Therefore, if $u_1 \ge u_0 + \bar b T$, then
-    $$
-    \IP\left\{
-        \inf_{0 \le t \le T} U_a(t) \le u_0
-        \;\big|\;
-        U_a(0) > u_1
-    \right\}
-    \le \delta ,
-    $$
-    and so with high probability any lines of descent that had level below $u_0$
-    at some point $0 \le t \le T$
-    are descended from lines of descent with initial level below $u_1$.
-    Since the number of lines of descent with level below $u_1$
-    converges to a Poisson with finite mean,
-    we need only show that the number of offpring lines of descent
-    produced by this initially finite number is also tight.
-    However, this follows immediately
-    since the rate of production of new lines of descent with level below $u_1$
-    of a line of descent at location $x$ and level $u$ is
-    $2 (u_1 - u) N^{-1} \theta \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q(x, dy)$
-    and therefore uniformly bounded (because we may take $u_1 \le N$).
-
-\end{proof}
-
 % % % % % % % % % % % % %
@@
 
-As a result, for all time $ 0 < t , t+ \delta t \leq T(U_0,\overline{U}_{K_{\epsilon},\epsilon},r),$
+As a result, for all time $ 0 < t , t+ r \leq T(U_0,\overline{U}_{K_{\epsilon},\epsilon},r),$
 
 \begin{align*}
-W^N_a(t+\delta t)-W^N_a(t) 
-\leq &\int_{t}^{t+\delta t} 
-        \left( \frac{\theta}{N} C_G \overline{U}_{K_{\epsilon}, \epsilon}^2
-        +
-        C_F H_{\epsilon}(r) \overline{U}_{K_{\epsilon}, \epsilon}
+W^N_a(t+r)-W^N_a(t) 
+\leq &\int_{t}^{t+r} 
+        \left( \frac{\theta}{N} C_G U_{g,\varepsilon}^2
+        +
+        C_F H_{\epsilon}(r) U_{g,\varepsilon}
         \right)
         ds\\
-=&\left( \frac{\theta}{N} C_G \overline{U}_{K_{\epsilon}, \epsilon}^2
-        +
-        C_F H_{\epsilon}(r) \overline{U}_{K_{\epsilon}, \epsilon}
-        \right) \delta t \\
-\leq&\left( A C_G \overline{U}_{K_{\epsilon}, \epsilon}^2
-        +
-        C_F H_{\epsilon}(r) \overline{U}_{K_{\epsilon}, \epsilon}
-        \right) \delta t
+=&\left( \frac{\theta}{N} C_G U_{g,\varepsilon}^2
+        +
+        C_F H_{\epsilon}(r) U_{g,\varepsilon}
+        \right) r \\
+\leq&\left( \bar{\alpha} C_G U_{g,\varepsilon}^2
+        +
+        C_F H_{\epsilon}(r) U_{g,\varepsilon}
+        \right) r
 \end{align*}
 
-Combining the results together, we have that for any $\delta t > 0$ small enough such that 
-\begin{equation}
-\delta t < \frac{\epsilon  }{4C_{g_1,..,g_{K_{\epsilon}}}}\min\left\{\frac{1}{C_G \overline{U}_{K_{\epsilon}, \epsilon}}, \frac{1}{A C_G \overline{U}_{K_{\epsilon}, \epsilon}^2
-        +
-        C_F H_{\epsilon}(r) \overline{U}_{K_{\epsilon}, \epsilon}}\right\}    
+Combining the results together, we have that for any $r > 0$ small enough such that 
+\begin{equation}
+r < \frac{\epsilon  }{4C'_g}\min\left\{\frac{1}{C_G U_{g,\varepsilon}}, \frac{1}{\bar{\alpha} C_G U_{g,\varepsilon}^2
+        +
+        C_F H_{\epsilon}(r) U_{g,\varepsilon}}\right\}    
 \end{equation}
 holds, then we have for all $t \leq T(U_0,\overline{U}_{K_{\epsilon},\epsilon},r)$,
+
 \begin{equation}
 \begin{aligned}
-\mathbb{E}\left[\mathfrak{d}(U^{N}_{a}(t+\delta t),U^{N}_{a}(t)) : A_{H_{\epsilon}}^{c} \right] \leq  &  
-  \mathbb{E}\left[\sum_{n=1}^{K_{\epsilon}}\frac{1 \wedge |g_n(U^{N}_{a}(t+\delta t))-g_n(U^{N}_{a}(t))|}{2^n} +  \epsilon/2: A_{H_{\epsilon}}^{c} ~\bigg|~{\cal F}_t^{
-\eta}\right]  \\
- \leq &   \sum_{n=1}^{K_{\epsilon}}\frac{\mathbb{E}\left[C_{g_1,..,g_{K_{\epsilon}}} |U^{N}_{a}(t+r)-U^{N}_{a}(t)|: A_{H_{\epsilon}}^{c} ~\bigg|~{\cal F}_t^{
-\eta} \right] }{2^n} +  \epsilon/2  \\
-\leq&   \sum_{n=1}^{K_{\epsilon}}\frac{\mathbb{E}\left[C_{g_1,..,g_{K_{\epsilon}}} |C_G \overline{U}_{K_{\epsilon}, \epsilon} \delta t|  : A_{H_{\epsilon}}^{c} ~\bigg|~{\cal F}_t^{
-\eta} \right] }{2^n}  \\
- & + \sum_{n=1}^{K_{\epsilon}}\frac{\mathbb{E}\left[C_{g_1,..,g_{K_{\epsilon}}}  |W^N_a(t+\delta t)-W^N_a(t)|: A_{H_{\epsilon}}^{c} ~\bigg|~{\cal F}_t^{
-\eta} \right] }{2^n} +  \epsilon/2  \\
-\leq  &  \sum_{n=1}^{K_{\epsilon}}\frac{\epsilon /2 }{2^n} +  \epsilon/2 \\
-< &  \epsilon.
+\mathbb{E}\left[|g(U^{N}_{a}(t+r ))-g(U^{N}_{a}(t))| \mathbbm{1}_{A_{H_{\epsilon}}^c} ~|~{\cal F}_t^{
+\eta} \right] 
+& \leq  \mathbb{E}\left[C'_{g} |U^{N}_{a}(t+r )-U^{N}_{a}(t)|\mathbbm{1}_{A_{H_{\epsilon}}^c} \right] \\
+&\leq r C'_g \max\{ \bar{\alpha} C_G U_{g,\varepsilon}^2
+        +
+        C_F H_{\epsilon}(r) U_{g,\varepsilon}
+        , C_G U_{g, \varepsilon}\} \\
+        & < \varepsilon.
 \end{aligned}
@@
 \begin{equation*}
-\delta t < \frac{\epsilon  }{4C_{g_1,..,g_{K_{\epsilon}}}}\min\left\{\frac{1}{C_G \overline{U}_{K_{\epsilon}, \epsilon}}, \frac{1}{A C_G \overline{U}_{K_{\epsilon}, \epsilon}^2
-        +
-        C_F H_{\epsilon}(r) \overline{U}_{K_{\epsilon}, \epsilon}}\right\}.    
+r < \frac{\epsilon  }{4C'_g}\min\left\{\frac{1}{C_G U_{g,\varepsilon}}, \frac{1}{\bar{\alpha} C_G U_{g,\varepsilon}^2
+        +
+        C_F H_{\epsilon}(r) U_{g,\varepsilon}}\right\}.    
 \end{equation*}
@@
 \subsection{Tightness of the Lookdown Representation}
-
-\comment{
-    This comes later because it uses convergence of the population process itself.
-}
-
-We have now proved tightness of the spatial and level process for a line of descent.
-To prove that the lookdown representation is tight, we generalise the vague topology to the setting of measure-valued processes.
-For a detailed description of the vague topology, refer to Appendix \ref{sec: Empirical Measure Topology}.
-
-We will lay out the steps we follow to prove tightness.
-First of all, we will show that compact containment condition is satisfied if we can control the total mass of particles in our system living in a finite region in space with a level lower than some $u_{*}$.
-Since a control on total mass has already been shown in Lemma \ref{lem:eta_compact_containment}, we have immediately established compact containment condition for our lookdown processes.
-
-Then, we apply Theorem A.24 in \cite{kallenberg1997foundations}
-(Theorem \ref{teo: Vague Relative Compactness through Projection})
-and use a corollary of Stone-Weierstrass Theorem
-(Lemma \ref{lem: Dense set for test functions on empirical measures})
-to show that our lookdown representation $\{\xi^N_t: N \in \mathbb{N}\}$ is tight
-as a $\mathcal{M}(\mathbb{R^d} \times [0, \infty])$-valued stochastic process
-in the vague topology
-as long as $\{F_g(\xi^N_t): N \in \mathbb{N}\}$ is tight
-as real-valued stochastic processes for a huge class of $F_g$. 
-Explicitly, $F_g(\xi):= \prod_{(x_i,u_i)\in \xi}g(x_i,u_i)$,
-where $g(x,u)$ satisfies the property that
-$g(x,u) = 1 $
-for all $u \geq u_{*}$ for some $u_{*}>0$.
-
-\subsubsection{Compact Containment Condition}
-\begin{definition}
-For any arbitrary $M,K>0$, 
-we denote the set 
-$$\mathcal{M}_{K,M}:= \{\mu \in \mathcal{M}(\mathbb{R^d} \times [0, \infty]): \mu([-M,M]^d \times [0,M])/M \leq K\}$$
-to be the set of measures on $\IR^d \times[0,\infty)$ with mass smaller than $K$ in the region $[-M,M]^d \times [0,M]$.
-\end{definition}
-
-In Corollary \ref{cor: Vague Compact sets}, we will prove that $\mathcal{M}_{K,M}$ is vaguely compact.
-
-\begin{lemma}[Compact Containment]
-    \label{lem:lp_compact_containment}
-Assume that $\xi^{N}_0 \to \xi_0$ weakly,
-then for all $T>0$, there exists some constant $C(T)$,
-such that
-    \begin{align}
-        \label{eqn:lp_mass_bound}
-        \IE\left[
-            \sup_{0 \le t \le T}
-            \frac{1}{N}\langle 1, \xi^{N}_t \rangle
-        \right]
-        \le C(T) ,
-    \end{align}
-uniformly in $N$.
-In particular, for any $\epsilon > 0$, there exists some $M_{\epsilon}>0, K_{\epsilon}>0$,
-such that 
-\begin{equation}
-\limsup_{N \to \infty}
-    \mathbb{P}\left\{ \xi^{N}_t \in \mathcal{M}_{K_{\epsilon},M_{\epsilon}}
-        \text{ for } t\in [0,T] \right\}
-        < \epsilon.
-\end{equation}
+\begin{lemma}
+The lookdown representation satisfies the compact containment condition, 
+Equation \eqref{eq: vague compact containment condition}, 
+for all $\varepsilon > 0$ and fixed time $T > 0$, there exists $N,K> 0$ such that 
+\begin{equation}
+\liminf_{n \to \infty}\mathbb{P}\{ \xi^n_t \in \Gamma_{N,K} \text{ for all } t\in [0,T]\} > 1-\varepsilon,
+\end{equation}
+where $\Gamma_{N,K}$ is the compact set in Lemma \ref{lem: vague compact sets}
 \end{lemma}
+
 \begin{proof}
-By an application of Markov Mapping Theorem (see \S \ref{sec: Markov Mapping Theorem Application - Prelimit}), we know that
-
-$$\left(\frac{1}{N}\langle 1, \xi^{N}_t(\cdot , [0, N]) \rangle\right)_{t \geq 0} \sim (\eta^N_t(\cdot ))_{t \geq 0},$$
-i.e. the spatial projection of $(\xi^{N}_t)_{t \geq 0}$ has the same distribution as $(\eta^N_t)_{t \geq 0}$ defined in Definition \ref{defn:mgale_construction}. 
-As a result, by Lemma \ref{lem:lp_compact_containment},
-we have immediately that 
-\begin{align}
-        \IE\left[
-            \sup_{0 \le t \le T}
-            \frac{1}{N}\langle 1, \xi^{N}_t \rangle
-        \right]
-        = \IE\left[
-            \sup_{0 \le t \le T}
-            \langle 1, \eta^{N}_t \rangle
-        \right]
-        \le C(T) ,
-    \end{align}
-for some $C(T)>0$.
-
-Moreover, we know that conditional on the spatial configuration 
-$\frac{1}{N}\langle 1, \xi^{N}_t(\cdot , [0, N]) \rangle,$
-the levels of each individual
-is i.i.d uniformly distributed between $[0,N]$. 
-Therefore, for $N>M_{\varepsilon}$
-\begin{align*}
-     \mathbb{P}\left\{ \xi^{N}_t \in \mathcal{M}_{K_{\epsilon},M_{\epsilon}}
-        \text{ for } t\in [0,T] \right\}
-        =& \mathbb{P}\left\{\sup_{ t\in [0,T]} \frac{1}{M_\varepsilon} \xi^{N}_t([-M_\varepsilon,M_\varepsilon]^d \times [0,M_\varepsilon]) \leq K_\varepsilon
-         \right\}\\
-         \leq& \frac{1}{M_\varepsilon K_{\varepsilon}} \mathbb{E}\left\{\sup_{ t\in [0,T]}  \xi^{N}_t([-M_\varepsilon,M_\varepsilon]^d \times [0,M_\varepsilon]) \right\}\\
-        =& \frac{1}{M_\varepsilon K_{\varepsilon}}             \mathbb{E}_{\eta^N_t}\left\{ N \times
-            \mathbb{E}\left[  
-                \sup_{ t\in [0,T]}  \frac{1}{N}\xi^{N}_t([-M_\varepsilon,M_\varepsilon]^d \times [0,M_\varepsilon])
-                \bigg| \eta^N_t
-                        \right]
-                    \right\}\\
-        =& \frac{1}{M_\varepsilon K_{\varepsilon}} \mathbb{E}_{\eta^N_t}
-                    \left\{ N \times
-                    \sup_{ t\in [0,T]} \eta^{N}_t([-M_\varepsilon,M_\varepsilon]^d) \times \frac{M_{\varepsilon}}{N}
-                    \right\}\\
-        =& \frac{1}{K_{\varepsilon}} \mathbb{E}_{\eta^N_t}
-                    \left\{
-                    \sup_{ t\in [0,T]} \eta^{N}_t([-M_\varepsilon,M_\varepsilon]^d) 
-                    \right\}\\
-        \leq & \frac{1}{K_{\varepsilon}} \mathbb{E}_{\eta^N_t}
-                    \left\{
-                    \sup_{ t\in [0,T]} \langle 1, \eta^{N}_t \rangle 
-                    \right\}\\
-        < & \varepsilon.
-\end{align*}
-The first inequality holds by Markov's inequality, and the following two equalities hold as 
-conditional on $\eta^N_t$,
-$M_{\varepsilon}/N$ proportion of particles in $\xi^N_t$ have levels in $[0,M_{\varepsilon}]$. The final inequality holds as a direct consequence of \ref{lem:eta_compact_containment}.
-
-We have therefore proved compact containment condition in the vague topology for our lookdown representation.
+Note that
+\begin{equation}
+\begin{aligned}
+     &1-\mathbb{P}\{ \xi^n_t \in \Gamma_{N,K} \text{ for all } t\in [0,T]\} \\
+     = & \mathbb{P}\left\{ \sup_{t \in[0,T]}\frac{1}{N}\langle 1_{\overline{\mathbb{R}^d}\times [0,N]}, \xi^n_t \rangle \geq K \right\} \\
+ \leq & \frac{\mathbb{E}\left\{ \sup_{t \in[0,T]}\frac{1}{N}\langle 1_{\overline{\mathbb{R}^d}\times [0,N]}, \xi^n_t \rangle\right\}}{K}.
+\end{aligned}
+\end{equation}
+Recall that conditional on 
+$$ \frac{1}{n}\langle 1_{[0,n]}, \xi^n_t \rangle = \eta^n_t,$$
+the level of each individual is independently and uniformly distributed between $[0,n]$.
+Therefore, for $n \geq N$,
+\begin{equation}
+\frac{\mathbb{E}\left\{ \sup_{t \in[0,T]}\frac{1}{N}\langle 1_{\overline{\mathbb{R}^d}\times [0,N]}, \xi^n_t \rangle\right\}}{K}
+= \frac{\mathbb{E}\left\{ \sup_{t\in [0,T]}\langle 1, \eta^n_t \rangle \right\}}{K} < \varepsilon,
+\end{equation}
+for large enough $K>0$. 
+The last inequality is given by Lemma \ref{lem:eta_compact_containment}.
 \end{proof}
+
+It now suffices for us to show that the processes $\{(F_g(\xi^n_t))_{t \geq 0}: n \geq 1\}$ is relatively compact for all test functions $F_g$.
+To do so, we apply Aldous criterion for real-valued processes.
+
 \subsubsection{Tightness of $(F_g(\xi_t))_{t \geq 0}$}
@@
 \begin{proof}
-
+Once again, we intend to apply the Aldous Criterion. 
+To do so, we need to prove that for all $\epsilon > 0$,
+there exists $n_0 > 0$ and $\delta > 0$ such that 
+\begin{equation}
+\sup_{n \geq n_0}\sup_{\theta \in [0, \delta]}\mathbb{P}\{|F_g(\xi^n_{\tau+\theta})-F_g(\xi^n_{\tau})| > \epsilon\} < \epsilon
+\end{equation} 
+holds. 
+It suffices to show that for sufficiently small $\delta > 0$,
+$\limsup_{n \to \infty}\mathbb{E}[|F_g(\xi^n_{\tau_n + s})-F_g(\xi^n_{\tau_n})|^2] < \epsilon$
+for all $\theta \in [0, \delta]$.
+
+First, note that only events happening on particles with levels smaller than $u_g$ at time $\tau_n$ will contribute to the difference $|F_g(\xi^n_{\tau_n + s})-F_g(\xi^n_{\tau_n})|$.
+
+To calculate this difference, we couple $(\xi^n_{\tau_n + s})_{s \in [0,\delta]}$ with the process $(\hat{\xi}^n_{\tau_n + s})_{s \in [0,\delta]}$ which has the same level dynamics as $(\xi^n_{\tau_n + s})_{s \in [0,\delta]}$ but with no birth.
+With this coupling, 
+we have 
+$\mathbb{E}[|F_g(\xi^n_{\tau_n + s})-F_g(\xi^n_{\tau_n})|^2] \leq 2\mathbb{E}[|F_g(\xi^n_{\tau_n + s})-F_g(\hat{\xi}^n_{\tau_n + s})|^2]+ 2\mathbb{E}[|F_g(\hat{\xi}^n_{\tau_n + s})-F_g(\xi^n_{\tau_n})|^2]$
+
+We first try to control $\mathbb{E}[|F_g(\hat{\xi}^n_{\tau_n + s})-F_g(\xi^n_{\tau_n})|^2]$. 
+This difference is simply influenced by the level dynamics. Therefore,
+\begin{equation}
+\begin{aligned}
+ &\mathbb{E}[|F_g(\hat{\xi}^n_{\tau_n + s})-F_g(\xi^n_{\tau_n})|^2]\\
+ \leq &
+ \mathbb{E}\left[ \int_{0}^{\delta} \sum_{(x,u)\in\xi^n_{\tau_n+s}}\,
+    \left|
+        \frac{\theta}{n} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q_\theta(x, dy) u^2 -b_{\theta}(x,\eta)u
+    \right|^2 \partial_u g(x,u)^2 ds\right]\\
+ \leq & ||g'||_{\infty}
+ \mathbb{E}\left[ \int_{0}^{\delta} \sum_{(x,u)\in\xi^n_{\tau_n+s}}\,
+    \left| \frac{\theta}{n}  \gamma(x,\eta)  u_g^2 + (2  \gamma(x,\eta) + F(x,\eta))u_g
+    \right|^2  ds\right] + O(1/\theta)\\
+\leq & ||g'||_{\infty}u_g
+ \mathbb{E}_{\eta}\left[ \int_{\tau_n}^{\tau_n+\delta} \int_{\mathbb{R}^d}
+    \left| \frac{\theta}{n}  \gamma(x,\eta^n_{s})  u_g^2 + (2  \gamma(x,\eta^n_{s}) + F(x,\eta^n_{s}))u_g
+    \right|^2 \eta^N_s(dx) ds\right] + O(1/\theta),
+\end{aligned}
+\end{equation}
+so this term can be controlled with Lemma \ref{lem:tightness_for_F}.
+
+We now control 
+$\mathbb{E}[|F_g(\xi^n_{\tau_n + s})-F_g(\hat{\xi}^n_{\tau_n + s})|^2]$.
+Note that this difference is purely contributed by the number of birth with both the parent and child having levels below $u_g$,
+and the simple inequality 
+$\mathbb{E}[|F_g(\xi^n_{\tau_n + s})-F_g(\hat{\xi}^n_{\tau_n + s})|^2] \leq 4 \mathbb{P}\{|F_g(\xi^n_{\tau_n + s})-F_g(\hat{\xi}^n_{\tau_n + s})|>0\}$
+holds.
+
+Therefore it suffices to prove that within a small interval of length $\delta > 0$,
+the probability of such birth events happening is small.
+
+This term can be controlled by the uniform boundedness of $\gamma(x,m)$.
+For the birth event to contribute to the difference, the parent must have a level below $u_g$, and give birth to a child at level $u + \ell < u_g$.
+Therefore, the total rate of relevant birth events satisfies
+\begin{equation}
+\sum_{(x,u) \in \xi^n_{\tau_n}([0,u_g] \times \overline{\mathbb{R}^d})}  \gamma(x,\eta^n_{\tau_n}) \mathbbm{1}_{u+ \ell < u_g }
+\leq C_{\gamma} \xi^n_{\tau_n}([0,u_g] \times \overline{\mathbb{R}^d}.
+\end{equation}
+Therefore, with an application of Markov inequality, 
+we have
+\begin{equation}
+\begin{aligned}
+\mathbb{P}\{|F_g(\xi^n_{\tau_n + s})-F_g(\hat{\xi}^n_{\tau_n + s})|>0\}
+\leq & \mathbb{P}[Poi(C_{\gamma} \xi^n_{\tau_n}([0,u_g] \times \overline{\mathbb{R}^d})s) \geq  1]\\
+\leq & \mathbb{E}[Poi(C_{\gamma} \xi^n_{\tau_n}([0,u_g] \times \overline{\mathbb{R}^d})s)]\\
+\leq & \mathbb{E}[Poi(C_{\gamma} \xi^n_{\tau_n}([0,u_g] \times \overline{\mathbb{R}^d})s)]\\
+\leq & C_{\gamma}  \mathbb{E}[\xi^n_{\tau_n}([0,u_g] \times \overline{\mathbb{R}^d})]s\\
+\leq & C_{\gamma}  u_g\mathbb{E}[\eta^n_{\tau_n}(\overline{\mathbb{R}^d})]s\\
+<&  \epsilon.
+\end{aligned}
+\end{equation}
+
+Combining all inequalities above, we have established Aldous Criterion and thus, tightness for the lookdown representation. 
 \end{proof}
-
-% % % % % % % % % % % % %
-\subsubsection{Convergence of generators for the lookdown process}
-    \label{sec:lookdown_generator_proofs}
-
-\comment{
-    I did this informal writeup of convergence of the lookdown generator
-    without looking at the previous version
-    mostly to double-check what we have there
-    (which is probably better).
-}
-
-In Definition~\ref{defn:lookdown_mgale} we saw that the generator
-of $(\lp_t)_{t \ge 0}$ is the sum of two parts,
-equations \eqref{eqn:birth_generator} and \eqref{eqn:level_generator}.
-Assume that there is a $u_*$ such that $g(x, u) = 1$ for all $u \ge u_*$.
-We consider these two in turn.
-
-First, the contribution from births is
-\begin{align*}
-\begin{split}
-f(\lp)
-&\mapsto
-    f(\lp)
-    \sum_{(x, u) \in \lp}
-    2 \gamma(x, \eta)
-    \bigg\{
-        \frac{1}{2 N}
-        \int_u^N
-        g(x, u_1) du_1
-        \frac{
-            \theta \int_{\IR^d} (g(y, u) - g(x, u)) r(y, \eta) q(x, dy)
-        }{
-            g(x, u)
-        }
-    \\ & \qquad \qquad \qquad {}
-        + \frac{\theta}{N}
-        \int_u^N \int_{\IR^d}
-        \left( \frac{g(y, u_1) + g(x, u_1)}{2} - 1 \right)
-        r(y, \eta) q(x, dy)
-    \bigg\}
-    .
-    \end{split}
-\end{align*}
-We have that
-\begin{align*}
-    &\theta \int_{\IR^d} (g(y, u) - g(x, u)) r(y, \eta) q(x, dy) \\
-    &\qquad =
-    \theta \int_{\IR^d} (r(y, \eta) g(y, u) - r(x, \eta) g(x, u)) q(x, dy)
-    - \theta \int_{\IR^d} g(x, u) (r(y, \eta) - r(x, \eta)) q(x, dy) \\
-    &\qquad \to
-    \DG(gr)(x) - g(x) \DG r(x) \qquad \text{as }N \to \infty.
-\end{align*}
-i.e., to
-$\DG\left(g(\cdot, u) r(\cdot, \smooth{r}\eta(\cdot))\right)(x)
-- g(\cdot, u) \DG\left(r(\cdot, \smooth{r}\eta(\cdot))\right)(x)$.
-Furthermore, by our assumption on $g$,
-$\int_u^N g(x, u_1) du_1 / N \to 1$ for all $x$ and $u$,
-so the first term here converges to
-\begin{align*}
-    \gamma(x, \eta)
-        \frac{
-            \DG\left( g(\cdot, u) r(\cdot, \smooth{r}\eta(\cdot))\right)(x)
-            -
-            g(\cdot, x) \DG\left( r(\cdot, \smooth{r}\eta(\cdot))\right)(x)
-        }{
-            g(x, u)
-        } .
-\end{align*}
-This corresponds to each particle moving according to the motion induced by
-$g \mapsto \gamma \DG(gr) - g \DG r$.
-\comment{TODO: explain the $r$-tilted $\DG$ motion somewhere earlier, introducing notation for it.}
-As for the second term,
-since $\int g(y, u_1) q(x, dy) \to g(x, u_1)$
-and $\theta/N \to \alpha$,
-it converges to
-\begin{align*}
-    2 \alpha
-    \gamma(x, \eta)
-    r(x, \eta) 
-    \int_u^\infty
-    \left( g(x, u_1) - 1 \right)
-    du_1
-\end{align*}
-This corresponds to births at higher levels at rate $2 \alpha \gamma r$.
-
-The remaining term is \eqref{eqn:level_generator}:
-\begin{align*}
-    f(\lp)
-    \mapsto
-    f(\lp)
-    \sum_{(x, u) \in \lp}
-    \left(
-    \theta
-        N^{-1} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
-        -
-        b(x, \eta)u
-    \right)
-    \frac{\partial_u g(x,u)}{g(x,u)} .
-\end{align*}
-The first part only uses the fact that $\theta/N \to \alpha$,
-while as noted in \eqref{eqn:b_limit}, $b$ converges to $\gamma \DG r + F$,
-so in total this term converges to
-\begin{align*}
-    f(\lp)
-    \mapsto
-    f(\lp)
-    \sum_{(x, u) \in \lp}
-    \left(
-    \alpha
-        \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
-        -
-        \left\{
-            \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta)
-        \right\} u
-    \right)
-    \frac{\partial_u g(x,u)}{g(x,u)} .
-\end{align*}
-In other words, the level of a particle at $x$ evolves according to
-\begin{align*}
-    \dot u
-    =
-    \alpha
-        \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
-        -
-        \left\{
-            \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta)
-        \right\} u .
-\end{align*}
-
-% % % % % % % % % % % % %
-\subsection{Motion of ancestral lineages}
-
-In this section we prove Theorem~\ref{thm:lineages}.
-The argument follows directly from the discussion in Section \ref{sec:limiting_lines_of_descent}.
-
-\begin{proof}[of Theorem~\ref{thm:lineages}]
-
-\comment{(TODO: Use notation for the motion of a lineage introduced in statement of theorem.)}
-
-Here
-\comment{(and in the statement of the theorem)}
-we take the high-density, deterministic limit
-(so, $\theta, N \to \infty$ and $\theta/N \to 0$)
-and so suppose that the limiting process has density $\varphi_t(x)$
-at location $x$ and time $t$.
-Let $Y$ denote the spatial motion followed by a single line of descent.
-Above equation~\eqref{eqn:limiting_generator},
-we showed that $Y$ is a diffusion with generator at time $s$
-$$
-    \mathcal{L}^Y_s g(x) = \gamma ( \DG(rg)(x) - g \DG r(x) ) .
-$$
-The diffusion is time-inhomogeneous if the density is not constant with time
-(since recall that the coefficients $\gamma$ and $r$ depend on the density).
-Formally, the intensity of levels at $y$ at time $t$
-that are descended from individuals that were at $x$ at time $s$
-(with $s < t$) is
-\begin{equation} \label{eqn:formal_intensity}
-    \varphi_s(x) \IE_{s,x} \left[
-        \exp\left(
-            \int_s^t (F + \gamma \DG r)(Y_u) du
-        \right)
-        \ind_{Y_t = y}
-    \right]
-    dy ,
-\end{equation}
-where the subscript $s, x$ in the expectation indicates that $Y_s = x$.
-To see why this should be true, 
-suppose that an ancestor has level $v$. Conditional on its 
-spatial motion $\{Y_u\}_{s\leq u\leq t}$, its level at time $t$ will
-be $v \exp(-\int_s^t(F+\gamma\Delta r)(Y_u)du)$. This will be less than a given level 
-$N$ if $v < N \exp(\int_s^t(F+\gamma\Delta r)(Y_u)du)$. 
-The intensity of levels at $y$ that are descended from individuals at
-$x$ can therefore be obtained as the limit as $N\to\infty$ of 
-$1/N$ times the number of levels at $x$ at time zero with
-$u<N \exp(\int_s^t(F+\gamma\Delta r)(Y_u)du)$ and for which
-the corresponding individual is at $y$ at time $t$, which is 
-precisely the quantity in~\eqref{eqn:formal_intensity}.
-
-By our construction in Section~\ref{sec:limiting_lines_of_descent},
-when we integrate~\eqref{eqn:formal_intensity}
-with respect to $x$ we recover $\varphi_t(y)dy$. 
-Consider an individual sampled at location $y$ at time $t$,
-and write $p(t,s,y,x)$ for the probability density
-that their ancestor at time $s$ was at $x$.
-As a consequence of~\eqref{eqn:formal_intensity},
-still formally,
-\begin{equation}
-\label{eqn:ptsyx}
-    p(t,s,y,x)
-    =
-    \frac{\varphi_s(x)}{\varphi_t(y)}
-    \IE_{s,x}\left[
-        \exp\left( \int_s^t (F + \gamma\DG r)(Y_u) du \right)
-        \ind_{Y_t=y}
-    \right]
-\qquad \text{ for } s < t.
-\end{equation}
-
-To make~(\ref{eqn:ptsyx}) meaningful, we multiply by suitable test functions
-$f$ and $g$ and integrate.
-\begin{align*}
-&\int \int f(y) \varphi_t(y) p(t,s,y,x) g(x) dy dx \\
-&\qquad =
-\int g(x) \varphi_s(x)
-\IE_{x,s}\left[
-    \exp\left(
-        \int_s^t(F+\gamma\DG r)(Y_u)du
-    \right)f(Y_t)
-\right] dx .
-\end{align*}
-
-Writing $\hat{T}_{t,s}$ for the time-inhomogeneous semigroup
-corresponding to the motion of ancestral lineages backwards in time
-(that is, $\hat{T}_{t,s} f(y) = \int p(t,s,x,y) f(x) dy$),
-we can write this as 
-$$
-    \int f(y)\varphi_t(y)\hat{T}_{t,s}g(y)dy
-    =
-    \int g(x) \varphi_s(x)
-        \IE_{s,x} \left[
-            \exp\left(
-                \int_s^t(F+\gamma\DG r)(Y_u)du
-            \right)f(Y_t)
-        \right]dx.
-$$
-Differentiating with respect to $t$ at $t=s$, and writing 
-$\Lgen_s$ for the generator of $\hat{T}_{t,s}$ at time $s$, we find
-\begin{align*}
-&
-    \int f(y) \left\{
-        \varphi_s(y) \Lgen_s g(y)
-        + \left(
-            r(y) \DG^*(\gamma \varphi_s)(y) + \varphi_s(y) F(y)
-        \right) g(y)
-    \right\} dy \\
-&\qquad =
-    \int g(x) \varphi_s(x) \left(
-        {\mathcal L}^Y_s f(x) + (F(x)+\gamma(x) \DG r(x)) f(x)
-    \right) dx \\
-&\qquad =
-    \int f(x) \left(
-        ({\mathcal L}^Y_s)^* (\varphi_s g)(x) + (F(x) + \gamma(x) \DG r(x)) \varphi_s(x) g(x)
-    \right) dx ,
-\end{align*}
-where $({\mathcal L}^Y_s)^*$ is the adjoint of ${\mathcal L}^Y_s$
-and we have used that $\varphi_s$ solves $\dot \varphi = r \DG^*(\gamma \varphi) + F \varphi$.
-Since $f$ was arbitrary,
-\begin{eqnarray*}
-\Lgen_s g
-    &=&
-    \frac{1}{\varphi_s} \left[
-        ({\mathcal L}^Y_s)^* (\varphi_s g)
-        + \gamma \varphi_s g \DG(r)
-        - r g \DG^*(\gamma \varphi_s)
-    \right] .
-\end{eqnarray*}
-(Note that the $\phi_s F g$ terms have cancelled.)
-Since the adjoint of ${\mathcal L}^Y_s$ is
-\begin{align*}
-    ({\mathcal L}^Y_s)^* f
-    &=
-    r \DG^* (\gamma f) - \gamma f \DG r ,
-\end{align*}
-we can rewrite the generator of a lineage as 
-\begin{eqnarray*}
-\Lgen_s g
-    &=&
-    \frac{r}{\varphi_s} \left[
-        \DG^* (\gamma \varphi_s g)
-        - g \DG^*(\gamma \varphi_s)
-    \right] .
-\end{eqnarray*}
-This is equation \eqref{eqn:lineage_generator}.
-
-To simplify to equation \eqref{eqn:lineage_generator2},
-this, first define
-$
-    \DD f(x) = \sum_{ij} \covq_{ij} \partial_{ij} f(x),
-$
-% and note that $\DD$ satisfies the following identity:
-% \begin{align}
-%     \DD(fg)
-%     &=
-%     f \DD g
-%     + 2 (\covq \grad f) \cdot \grad g
-%     + g \DD f .
-% \end{align}
-and so the adjoint of $\DD$ is
-$$
-    \DD^* f(x)
-    =
-    \sum_{ij} \partial_{ij} (\covq_{ij} f(x)) .
-$$
-Note that $\DD^*$ satisfies the following identity:
-\begin{align*}
-    \DD^*(fg)
-%     &=
-%     \sum_{ij} \left\{
-%         g \partial_{ij} (\covq_{ij} f)
-%         + 2 \partial_{i} (\covq_{ij} f) \partial_j(g)
-%         + \covq_{ij} f \partial_{ij} g
-%     \right\} \\
-    &=
-    \sum_{ij} \left\{
-        g \partial_{ij} (\covq_{ij} f)
-        + 2 f \partial_{i} (\covq_{ij}) \partial_j(g)
-        + 2 \covq_{ij} \partial_{i} (f) \partial_j(g)
-        + \covq_{ij} f \partial_{ij} g
-    \right\} \\
-    &=
-    g \DD^* f
-    + 2 f \vec{c} \cdot \grad g
-    + 2 (C \grad f) \cdot \grad g
-    + f \DD g ,
-\end{align*}
-where $\vec{c}_j = \sum_i \partial_j C_{ij}$.
-So, with $f = \gamma \varphi_s$,
-\begin{eqnarray*}
-\Lgen_s g
-    &=&
-    \frac{r}{\varphi_s} \left[
-        \DD^*(\gamma \varphi_s g) - \grad \cdot (\gamma \varphi_s g \meanq)
-        - g \DD^*(\gamma \varphi_s) + g \grad \cdot (\gamma \varphi_s \meanq)
-    \right] \\
-    &=&
-    \frac{r}{\varphi_s} \left[
-        \gamma \varphi_s \DD g
-        + 2 \gamma \varphi_s \vec{c} \cdot \grad g
-        + 2 (C \grad (\gamma \varphi_s)) \cdot \grad g
-        - \gamma \varphi_s \meanq \cdot \grad g
-    \right] \\
-    &=&
-    r \gamma \left[
-        \DD g
-        + 2 \vec{c} \cdot \grad g
-        + 2 (C \grad \log(\gamma \varphi_s)) \cdot \grad g
-        - \meanq \cdot \grad g
-    \right] ,
-\end{eqnarray*}
-which is equation \eqref{eqn:lineage_generator}.
-
-\end{proof}
-
-\begin{proof}[of Corollary \ref{cor:lineages_simple}]
-
-In this section, we need only
-simplify equation \eqref{eqn:lineage_generator}
-in the case where $\covq = \sigma^2 I$.
-
-    \comment{TODO}
-
-\end{proof}
-
-\begin{proof}[of Corollary~\ref{cor:wavefront}
-    \comment{
-        TODO make non-redundant with proof of Theorem \ref{thm:lineages}.
-    }
-
-Let $Y$ denote the diffusion followed by following a single descendent line in this frame; 
-i.e.~the diffusion with generator ${\cal L}^Y\phi=\gamma\Delta(r\phi)-\gamma\phi\Delta r -\mathfrak{c}\nabla\phi $.
-Note in particular here we take $\mathcal{B}=\Delta$.
-We start by expressing the evolution of a singles ancestry line in terms of the descendent line $Y$.
-
-Formally, the intensity of levels at $y$ at time $t$ that are descended from 
-individuals that were at $x$ at time $0$ is
-\begin{equation}
-\label{formal intensity}
-w(x)\IE_x\left[\exp\left(\int_0^t (F+\gamma \Delta r)(Y_s)ds\right)\ind_{Y_t=y}\right]dy,
-\end{equation}
-where the subscript $x$ in the expectation indicates that $Y_0=x$.
-To see why this should be true, 
-suppose that an ancestor has level $u$. Conditional on its 
-spatial motion $\{Y_s\}_{0\leq s\leq t}$, its level at time $t$ will
-be $u\exp(-\int_0^t(F+\gamma\Delta r)(Y_s)ds)$. This will be less than a given level 
-$N$ if $u<N \exp(\int_0^t(F+\gamma\Delta r)(Y_s)ds)$. 
-The intensity of levels at $y$ that are descended from individuals at
-$x$ can therefore be obtained as the limit as $N\to\infty$ of 
-$1/N$ times the number of levels at $x$ at time zero with
-$u<N \exp(\int_0^t(F+\gamma\Delta r)(Y_s)ds)$ and for which
-the corresponding individual is at $y$ at time $t$, which is 
-precisely the quantity in~(\ref{formal intensity}).
-
-It is easy to check that when we integrate~(\ref{formal intensity})
-with respect to $x$ we recover $w(y)dy$. 
-As a consequence of~(\ref{formal intensity}), writing $p(t,y,x)$ for
-the probability density that the ancestor $t$ units in 
-the past of an individual sampled 
-at $y$ was at $x$, then, still formally,
-\begin{equation}
-\label{ptyx}
-p(t,y,x)=\frac{w(x)}{w(y)}\IE_x\left[\exp\left(\int_0^t (F+\gamma\Delta r)(Y_s)ds\right)
-\ind_{Y_t=y}\right].
-\end{equation}
-
-To make~(\ref{ptyx}) meaningful, we multiply by suitable test functions and 
-integrate.
-$$\int\int \psi(y)w(y)p(t,y,x)\phi(x)dydx=\int\phi(x)w(x)
-\IE_x\left[\exp\left(\int_0^t(F+\gamma\Delta r)(Y_s)ds\right)\psi(Y_t)\right]dydx.$$
-
-Writing $\hat{T}_t$ for the semigroup corresponding to the motion of 
-ancestral lineages backwards in time (that is the semigroup corresponding
-to $p(t,x,y)$), we can write this as 
-$$\int \psi(y)w(y)\hat{T}_t\phi(y)dy=\int\phi(x)w(x)
-\IE_x\left[\exp\left(\int_0^t(F+\gamma\Delta r)(Y_s)ds\right)\psi(Y_t)\right]dx.$$
-Differentiating with respect to $t$ at $t=0$, and writing 
-$\hat{\mathcal L}$ for the generator of $\hat{T}_t$, we find
-\begin{eqnarray*}
-\int \psi(y)w(y)\widehat{\mathcal L}\phi(y)dy&=&
-\int\phi(x)w(x)\left({\mathcal L}^Y\psi(x)+\psi(x)(F+\gamma\Delta r)\psi(x)\right)dx\\
-&=&\int\phi(x)w(x)\left(\gamma\Delta(r\psi)-\gamma\psi\Delta r -\mathfrak{c}\nabla\psi 
-+(F+\gamma\Delta r)(\psi)\right)dx\\
-&=&\int\phi(x)w(x)\left(\gamma\Delta(r\psi)-\mathfrak{c}\nabla\psi+F(\psi)\right)dx\\
-&=&
-\int\psi(x)\left[r\Delta(\gamma \phi w)+F\phi w+\mathfrak{c}\nabla(\phi w)\right]dx.
-\end{eqnarray*}
-Since $\psi$ was arbitrary,
-\begin{eqnarray*}
-\hat{\mathcal L}\phi&=&\frac{1}{w}\left[ r\Delta (\gamma\phi w)+F\phi w
-+\mathfrak{c}\nabla(\phi w)\right]\\
-&=&\frac{\phi}{w}\left[r\Delta(\gamma w)+Fw+\mathfrak{c}\nabla w\right]
-+\frac{1}{w}\left[r\gamma w\Delta \phi +2\nabla (\gamma w)
-\nabla\phi+\mathfrak{c}w\nabla\phi\right]\\
-&=&r\gamma\left(\Delta\phi+2\frac{\nabla(\gamma w)}{\gamma w}\nabla\phi\right)
-+\mathfrak{c}\nabla\phi,
-\end{eqnarray*}
-where we have used that $w$ solves~(\ref{profile}).
-
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\appendix
-\section{Markov Mapping Theorem Applications}
-    \label{sec: Markov Mapping Theorem Application}
-\subsection{Markov Mapping Theorem Application on Generator $A^{\theta}$}\label{sec: Markov Mapping Theorem Application - Prelimit}
-
-We now introduce some notations to simply our calculations.
-For $\xi=\sum \delta_{(x_i,u_i)}$, we write $\textbf{x}=(x_1,x_2,...), \textbf{u}=(u_1,u_2,...)$ to be the collections of particles locations and levels respectively.
-With this notation we will write $f(\xi), f(\textbf{x},\textbf{u})$ interchangeably.
-We write $\Gamma (d\textbf{u})$ as the probability kernel that corresponds to assigning each particle an i.i.d.
-uniform $[0,\lambda]$-level, i.e.
-$$\int f(\textbf{x},\textbf{u})\Gamma (d\textbf{u})=\frac{1}{\lambda^{|\xi|}}\int_{[0,\lambda]^{|\xi|}}f(\textbf{x},\textbf{u})d\textbf{u},$$
-and we denote
-$$\hat{g}(x):=\frac{1}{\lambda}\int_{0}^{\lambda}g(x,u)du, ~~\hat{f}(\xi)=\int f(\xi) \Gamma (d\textbf{u})$$ 
-to be the spatial test functions with averaged level. By independence of the levels of the particles we have that
-$$\hat{f}(\xi)=\int \prod_{(x,u) \in \xi}g(x,u) \Gamma(d\textbf{u})=\prod_{(x,u)\in \xi}\frac{1}{\lambda}\int_{0}^{\lambda} g(x,u) du=\prod_{x_i \in \Xi}\hat{g}(x_i).$$ 
-We will now apply Markov Mapping Theorem while keeping notations consistent to that introduced in Section A.5 in \cite{kurtz/rodrigues:2011} with the aid of Table \ref{Markov Mapping Theorem Notation Table}.
-\begin{table}[h]
-    \centering
-    \begin{tabular}{c|c}
-    Notation in \cite{kurtz/rodrigues:2011} & Notation in this paper \\
-    \hline\\
-      $S$   &  $\mathcal{M}(\IR^d \times [0, \lambda))$\\\\
-       $S_0$  &  $\mathcal{M}(\IR^d)$\\\\
-       $A$ & $A^{\theta}$\\\\
-       $(X_t)_{t \geq 0}$ & $(\xi^{\theta}_t)_{t \geq 0}$\\\\
-       $\mu_0$ & $\Xi^{\theta}_0 \in \mathcal{M}(\IR^d)$\\\\
-       $\nu_0$ & $\xi^{\theta}_0 \in \mathcal{M}(\IR^d \times [0,\lambda])$\\\\
-       $f(\xi)$ & $\prod_{(x,u) \in \xi} g(x,u)$\\\\
-        $\gamma_M$ & $ \mathcal{M}(\IR^d \times [0, \lambda)) \ni \xi \to \frac{1}{\lambda}\sum_{(x,u) \in \xi, u < \lambda} \delta_{x} \in \mathcal{M}(\IR^d)$\\\\
-       $\alpha_M$ & $ \alpha_M(\Xi,d \nu) =     \begin{cases}
-      0 & \text{if } \sum_{(x,u) \in \nu, u < \lambda} \delta_x \neq \Xi\\
-       \prod_{(u_i,x_i) \in \nu} \frac{1}{\lambda} \ind_{[0,\lambda]}du_i & \text{if } \sum_{(x,u) \in \nu, u < \lambda} \delta_x = \Xi,\\
-    \end{cases} $\\
-&      where $du_i$ is the standard Lebesgue measure.
-    \end{tabular}
-    \caption{Markov Mapping Theorem Correspondence}
-    \label{Markov Mapping Theorem Notation Table}
-\end{table}
-\begin{remark}
-Note that $\gamma,\alpha$ in \cite{kurtz/rodrigues:2011} is replaced with $\gamma_M,\alpha_M$ to avoid confusion with the $\gamma, \alpha$ used in previous sections.
-\end{remark}
-First of all, note that $\gamma_M$ is Borel-measurable and $\alpha_M$ is a transition function from $\mathcal{M}(\IR^d \times [0, \lambda))$ to $\mathcal{M}(\IR^d)$.
-More importantly, we have the following simplified expression for an integral against $\alpha_M$:
-\begin{equation}
-\int_{\mathcal{M}(\IR^d\times [0,\lambda])}A^{\theta}f(\nu)\alpha_M(\Xi,d\nu)= \int   A^{\theta}f(\textbf{x},\textbf{u})\Gamma(d\textbf{u}). 
-\end{equation}
-As a result, we can establish that
-\begin{equation}
-\begin{aligned}
-\alpha_M(\Xi,\gamma^{-1}(\Xi)) &= \int_{\nu \in \gamma^{-1}(y)}\alpha_M (\Xi,d\nu) \\
-&= \int_{\nu \in \prod_{x_i \in \Xi} \{x_i\}\times [0,\lambda]}\alpha_M (\Xi,d\nu)\\
-&= \prod_{x_i \in \Xi}\frac{1}{\lambda}\int_{0}^{\lambda} du_i =1
-\end{aligned}
-\end{equation}
-With the simplified integral, it now suffices to show that the Martingale Problem 
-\begin{equation}\label{Markov Mapping Theorem Martingale Condition Simplified}
-C = \left\{\left(\int   f(\textbf{x},\textbf{u})\Gamma(d\textbf{u}),\int   A^{\theta}f(\textbf{x},\textbf{u})\Gamma(d\textbf{u})\right)\right\}    
-\end{equation}
-has a solution, i.e. the process
-\begin{equation}
-\begin{aligned}
-M_t:=& \int   f(\textbf{x}_t,\textbf{u}_t)\Gamma(d\textbf{u})-\int   f(\textbf{x}_0,\textbf{u}_0)\Gamma(d\textbf{u})-\int_{0}^{t}\int   A^{\theta}f(\textbf{x}_s,\textbf{u}_s)\Gamma(d\textbf{u})ds\\
-=&\hat{f}(\xi_t)-\hat{f}(\xi_0)-\int_{0}^{t}\int   A^{\theta}f(\xi_s)\Gamma(d\textbf{u})ds
-\end{aligned}    
-\end{equation}
-is a martingale.\\
-Once we manage to solve the Martingale Problem \eqref{Markov Mapping Theorem Martingale Condition Simplified}, the Markov Mapping Theorem guarantees the following fact:
-\begin{enumerate}
-    \item $N_t:=    f(\xi_t)-   f(\xi_0)-\int_{0}^{t}  A^{\theta}f(\xi_s)ds$ is a martingale for all $f\in D(A^{\theta})$,
-    \item The process $(\gamma_M \circ \xi^{\theta}_t)_{t \geq 0}:= \left(\frac{1}{\lambda}\sum_{(x,u)\in \xi^{\theta}_t, u < \lambda} \delta_x\right)_{t \geq 0}=(\Xi^{\theta}_t)_{t \geq 0}$ solves the Martingale Problem \eqref{Markov Mapping Theorem Martingale Condition Simplified}.
-    \item $\mathbb{P}\{\xi^{\theta}_t \in B | \mathcal{F}^{\Xi^{\theta}}_t\}=\alpha_M(\Xi^{\theta}(t),\meanq), ~~~B \in \mathcal{B}(\mathcal{M}(\IR^d \times [0,\lambda])).$
-\end{enumerate}
-Note that in particular, the third statement is equivalent to the fact that conditioned on the spatial configuration $\Xi^{\theta}_t$, the levels of the particles must be i.i.d uniformly between $[0,\lambda]$.
-We may also express this condition through the following equation:
-\begin{equation}\label{Markov Mapping Theorem Cox Condition}
-\mathbb{E}\left[e^{-\int_{S \times [0,\lambda]} f(x,u) \xi^{\epsilon,\theta,\lambda}(dx \times du)}\bigg| \mathcal{F}^{\Xi^{\epsilon,N}}_t\right]=e^{-\int F^{\epsilon,\theta,\lambda}_f(x) \Xi^{\epsilon,\theta,\lambda}_t(dx)},
-\end{equation}
-where 
-$$F^{\epsilon,\theta,\lambda}_f(x):=-\lambda\log \left(\frac{1}{\lambda}\int_{0}^{\lambda}e^{-f(x,u)}du\right)=-\lambda\log \left(1-\frac{1}{\lambda}\int_{0}^{\lambda}(1-e^{-f(x,u)})du\right).$$
-
-Therefore we only need to solve Martingale Problem \eqref{Markov Mapping Theorem Martingale Condition Simplified}.\\
-
-The procedure to solve the Martingale Problem \eqref{Markov Mapping Theorem Martingale Condition Simplified} is rather standard and set out in \cite{kurtz/rodrigues:2011}, albeit we will face more technicalities for this setting.
-Recall that the lookdown generator of our spatial-level process satisfies
-\begin{align}\label{Lookdown generator N lambda theta prelimit}
-A^{\theta}f(\xi)=&f(\xi)\sum_{(x,u)\in\xi}2\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\times
-\int_u^{
-\lambda}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\IR^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
-\xi },dy) \nonumber \\
-& \qquad \qquad \qquad \qquad +\int_{\IR^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy)\Bigg)dv_1 \nonumber\\
-&+f(\xi )\sum_{(x,u)\in\xi}\,\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)},
-\end{align}
-where $f(\xi) =\prod_{(x,u) \in \xi}g(x,u)$. 
-For easier computation we break the generator into three parts, 
-\begin{equation}
-\begin{aligned}
-A^{\theta,1}f(\xi)=&f(\xi)\sum_{(x,u)\in\xi}2\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\times
-\int_u^{
-\lambda}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\IR^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
-\xi },dy)\Bigg)dv_1,\\
-A^{\theta,2}f(\xi)=&f(\xi)\sum_{(x,u)\in\xi}2\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\times
-\int_u^{
-\lambda}\Bigg(\frac{1}{2}\int_{\IR^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy)\Bigg)dv_1,\\
-A^{\theta,3}f(\xi)=&f(\xi )\sum_{(x,u)\in\xi}\,\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)},
-\end{aligned}
-\end{equation}
-such that 
-$$A^{\theta}f(\xi)=A^{\theta,1}f(\xi)+A^{\theta,2}f(\xi)+A^{\theta,3}f(\xi).$$
-We now calculate each generator evaluated under our probability kernel $\Gamma$.
-\footnotesize 
-\begin{align*}
-&\int A^{\theta,1}f(\xi) \Gamma(d\mathbf{u})\\ &=\int \Bigg\{f(\xi)\sum_{(x,u)\in\xi}2\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)
-\int_u^{
-\lambda}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\IR^d}(g(y,u)-g(x,u))q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
-\xi },dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
-&=\sum_{(x,u)\in\xi} \int \Bigg\{\frac{f(\xi)}{g(x,u)}2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi)
-\int_u^{
-\lambda}\Bigg(\frac 12 g(x,v_1)\int_{\IR^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
-\xi },dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
-&=\sum_{(x,u)\in\xi}\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\int_{0}^{\lambda}\left\{
-\int_u^{
-\lambda} g(x,v_1)dv_1\times \int_{\IR^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
-\xi },dy)\right\}du\\
-&=\sum_{(x,u)\in\xi}\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\int_{\IR^d} \left\{\int_{0}^{\lambda}
-\int_u^{
-\lambda} g(x,v_1) (g(y,u)-g(x,u))dv_1du\right\}q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
-\xi },dy)
-\end{align*}
-\normalsize
-For the second generator, we have
-\footnotesize
-\begin{align*}
-&\int A^{\theta,2}f(\xi) \Gamma(d\mathbf{u})\\&=\int \Bigg\{f(\xi)\sum_{(x,u)\in\xi}2\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\times
-\int_u^{
-\lambda}\Bigg(\int_{\IR^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
-&=\sum_{(x,u)\in\xi}\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\int \Bigg\{f(\xi)\times
-\int_u^{
-\lambda}\Bigg(\int_{\IR^d}\left(g(y,v_1)+g(x,v_1)-2\right)q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
-&=\sum_{(x,u)\in\xi}\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i) \frac{1}{\lambda}\int_{\IR^d}\Bigg\{\int_{0}^{\lambda}
-\int_u^{
-\lambda}g(x,u) \left(g(y,v_1)+g(x,v_1)-2\right)dv_1 du\Bigg\} q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy).
-\end{align*}  
-\normalsize
-For the third generator we have that 
-\begin{align*}
- &\int A^{\theta,3}f(\xi)\Gamma(d\mathbf{u})\\&=\int f(\xi )\,\left(\lambda^{-1} \sum_{(x,u)\in\xi}\theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)}\Gamma(d\mathbf{u}) \\
- &=\sum_{(x,u)\in\xi}\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\int_{0}^{\lambda}  \left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\partial_u g(x,u)du \\
- &=-\sum_{(x,u)\in\xi}\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\int_{0}^{\lambda}  \left(2u\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) -b_{\theta}(x,\Xi)\right)\left(g(x,u)-1\right)du \\
- &=-\sum_{(x,u)\in\xi}\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\int_{0}^{\lambda}   2ug(x,u)du \\
- &+\sum_{(x,u)\in\xi}\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\times \lambda^2+\sum_{(x,u)\in\xi}\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)b_{\theta}(x,\Xi)(\hat{g}(x)-1) \\
-\end{align*}
-Using the symmetry we have
-\begin{align*}
-&\int_{0}^{\lambda}
-\int_u^{
-\lambda} g(x,v_1) (g(y,u)-g(x,u))dv_1du+\int_{0}^{\lambda}
-\int_u^{
-\lambda}g(x,u) \left(g(y,v_1)+g(x,v_1)-2\right)dv_1 du
-\\&= \int_{0}^{\lambda}
-\int_u^{
-\lambda}g(x,u)g(y,v_1)+g(y,u)g(x,v_1)-2g(x,u) dv_1 du\\
-&=\frac{1}{2}\int_{0}^{\lambda}\int_{0}^{\lambda}g(x,u)g(y,v_1)+g(y,u)g(x,v_1)dv_1 du - 2 \int_{0}^{\lambda}(\lambda-u)g(x,u)du\\
-&=\lambda^2 \hat{g}(x)\hat{g}(y) -2\lambda^2 \hat{g}(x)+2\int_{0}^{\lambda}ug(x,u)du.
-\end{align*}
-Combining the last equations we have 
-\begin{align*}
-&\int \Bigg(A^{1}_{\theta}f(\xi)+A^{2}_{\theta}f(\xi)+A^{3}_{\theta}f(\xi)\Bigg)\Gamma(d\mathbf{u})\\
-&=  \sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)}\hat{g}(x_i) \left( \int_{\IR^n} \hat{g}(y) q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy) - 2+\frac{1}{\hat{g}(x)}\right)+\sum_{(x,u) \in \xi } \prod_{(x_i,u_i)}\hat{g}(x_i)b_{\theta}(x,\Xi)\left(1-\frac{1}{\hat{g}(x)}\right)\\
-&=  \hat{f}(\xi)\sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi) \left(\int_{\IR^n} \hat{g}(y) q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy) -1\right)+\hat{f}(\xi)\sum_{(x,u) \in \xi } (b_{\theta}(x,\Xi)-\theta\gamma^{\mathfrak{m}}_{\theta}(x,\xi))\left(1-\frac{1}{\hat{g}(x)}\right)\\
-&=  \hat{f}(\xi)\sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi) \left(\int_{\IR^n} \hat{g}(y) q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy) -1\right) -\hat{f}(\xi)\sum_{(x,u) \in \xi } \theta \mu_{\epsilon,\theta}(x,\Xi)\left(1-\frac{1}{\hat{g}(x)}\right),
-\end{align*}
-which corresponds to a spatial-branching process that branches at rate $\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)$ leaving offspring around with kernel $ q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy)$ and each particle having death rate given by $\theta \mu_{\epsilon,\theta}(x,\Xi)$.
-This is precisely the martingale problem in Definition \ref{def: Martingale Problem Characterisation - Product Form}.
-\newpage
-\subsection{Markov Mapping Theorem Application on Generator $A^{\text{nl}}_{\epsilon}$}\label{sec: Markov Mapping Theorem application - limit}
-In this section we consider a general generator limit for the lookdown representation of our spatial model. 
-We define
-\begin{equation}
-\begin{aligned}
-A^{\text{nl}}_{\epsilon}f(\eta )  =&f(\eta )\sum_{(x,u)\in\eta}\Bigg\{
- \gamma(x, (\rho_{\epsilon}*\Xi)(x))
- \frac{\mathcal{B}(g(\cdot,u)r( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)-g(x,u)\mathcal{B}r( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)}{g(x,u)}\\
- &
-  +2\gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\times \ell \int_u^{
-\infty}(g(x,v_1)-1)dv_1\\
-&
-+\bigg(\ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x)) u^2 \\
-&~~~~~~~-\big(F(x, (\rho_{\epsilon}*\Xi)(x))+\gamma(x, (\rho_{\epsilon}*\Xi)(x))\mathcal{B}r( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)\big)u\bigg) \frac {\partial_u g(x,u)}{g(x,u)}\Bigg\},
-\end{aligned}    
-\end{equation}
-where our test measure $\eta$ takes value on $\mathcal{M}_F(\IR\times [0,\infty))$ and $\Xi:=\lim_{u_0\rightarrow\infty}\frac 1{u_0}\sum_{(u,x)\in \eta:u\leq u_0}\delta_x$.
-
-If we take $\gamma =1, r=1, \mathcal{B}=\Delta,$ and $F(x, (\rho_{\epsilon}*\Xi)(x))=G( (\rho_{\epsilon}*\Xi)(x))-H( (\rho_{\epsilon}*\Xi)(x))$, then we recover $A^{\epsilon, \infty}$ defined in Equation \eqref{Eq: Non-local Scaling limit Lookdown Generator}.
-
-Similar to the calculations above, we write $\alpha(\Xi,\cdot)$ for the distribution of a conditionally
-Poisson random measure $\eta^{\infty}$ on $\IR^d\times [0,\infty)$ with mean measure
-$\Xi(dx)\times \Lambda$ and we calculate $\alpha A^{\text{nl}}_{\epsilon}f(\eta)$.
-
-Once again, we write
-$$\alpha A^{\text{nl}}_{\epsilon}f(\eta)=\alpha A^{1}_{nl}f(\eta)+\alpha A^{2}_{nl}f(\eta)+\alpha A^{3}_{nl}f(\eta),$$
-where 
-\small
-\begin{equation}\label{Eq: Decomposition of the Non-local Scaling limit Lookdown Generator}
-\begin{aligned}
-A^{1}_{nl}f(\eta )  =&f(\eta )\sum_{(x,u)\in\eta}
- \gamma(x, (\rho_{\epsilon}*\Xi)(x))
- \frac{B(g(\cdot,u)r( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)-g(x,u)Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)}{g(x,u)},\\
-A^{2}_{nl}f(\eta )  = &
-  f(\eta )\sum_{(x,u)\in\eta}2\gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\times \ell \int_u^{
-\infty}(g(x,v_1)-1)dv_1,\\
- A^{3}_{nl}f(\eta )  =&f(\eta )
-\sum_{(x,u)\in\eta}\bigg(\ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x)) u^2\\
-&\qquad \qquad \qquad \qquad -\big(F(x, (\rho_{\epsilon}*\Xi)(x))+\gamma(x, (\rho_{\epsilon}*\Xi)(x))Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)\big)u\bigg)\frac {\partial_u g(x,u)}{g(x,u)}\\
-\end{aligned}    
-\end{equation}
-\normalsize
-
-We define $h(x)=\int_{0}^{\infty} (1-g(x,u))du$.
-In this case, we have that $$\alpha f(\eta) = \exp \left(\int\int \big(g(x,u)-1\big) du \Xi(dx)\right)= \exp(\langle -h(x),\Xi(dx) \rangle ).$$  As a result we have that
-\begin{equation}\label{Eq: Averaging the Non-local Scaling limit Lookdown Generator Part 1}
-\footnotesize
-\begin{aligned}
-\alpha A^{1}_{nl}f(\eta )  =&
- \alpha \left\{\sum_{(x,u)\in\eta}\gamma(x, (\rho_{\epsilon}*\Xi)(x))\frac{B(g(\cdot,u)r( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)-g(x,u)Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)}{g(x,u)}\prod_{(x_i,u_i)}g(x_i,u_i)\right\}\\
- =&\int\int \bigg( \gamma(x, (\rho_{\epsilon}*\Xi)(x))B((g(\cdot,u)-1)r( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)-(g(x,u)-1)Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)\bigg)du \Xi(dx)\\
- &\times \exp \left(\int\int \big(g(x,u)-1\big) du \Xi(dx)\right),\\
- =& \left\langle \gamma(x, (\rho_{\epsilon}*\Xi)(x))B(h(\cdot) r( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)-h(\cdot)Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x),\Xi(dx) \right\rangle e^{-\langle h(x),\Xi(dx)\rangle} \\
- \alpha A^{2}_{nl}f(\eta )  = &
-   \alpha \left\{2\sum_{(x,u)\in\eta}\gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\times \ell \int_u^{
-\infty}(g(x,v_1)-1)dv_1\prod_{(x_i,u_i)}g(x_i,u_i)\right\}\\
-=& \int\int \bigg(g(x,u)\gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\times \ell \int_u^{
-\infty}(g(x,v_1)-1)dv_1\bigg)du \Xi(dx)e^{-\langle h(x),\Xi(dx)\rangle}\\
-=& 
-\left\langle \ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\int g(x,u)\int_u^{
-\infty}(g(x,v_1)-1)dv_1 du,\Xi(dx)\right\rangle e^{-\langle h(x),\Xi(dx)\rangle}\\
- \alpha A^{3}_{nl}f(\eta )  =&
-\alpha \Bigg\{\sum_{(x,u)\in\eta}\bigg(\ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x)) u^2 -\big(F(x, (\rho_{\epsilon}*\Xi)(x))+\gamma(x, (\rho_{\epsilon}*\Xi)(x))Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)\big)u\bigg)\\
-&\times \frac {\partial_u g(x,u)}{g(x,u)}\prod_{(x_i,u_i)}g(x_i,u_i)\Bigg\}\\
-=& \bigg \langle \ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\int \partial_u g(x,u) u^2 du \\
-& ~~~ - \big(F(x, (\rho_{\epsilon}*\Xi)(x))+\gamma(x, (\rho_{\epsilon}*\Xi)(x))Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)\big) \int u \partial_u g(x,u) du ,\Xi(dx)\bigg\rangle \times e^{-\langle h(x),\Xi(dx)\rangle} .
- \end{aligned}    
-\end{equation}
-\normalsize
-Now note that with integration by parts
-\begin{multline}
- \ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))  \int_{0}^{\infty}\partial_u g(x,u) u^2 du  \\=  2\ell\gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\int_{0}^{\infty} u (g(x,u)-1) du,
-\end{multline}
-\begin{multline}
- \big(F(x, (\rho_{\epsilon}*\Xi)(x))+\gamma(x, (\rho_{\epsilon}*\Xi)(x))Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)\big)\int_{0}^{\infty} u \partial_u g(x,u)du \\=\big(F(x, (\rho_{\epsilon}*\Xi)(x))+\gamma(x, (\rho_{\epsilon}*\Xi)(x))Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)\big)\int_{0}^{\infty} (g(x,u)-1) du\\
- =-\big(F(x, (\rho_{\epsilon}*\Xi)(x))+\gamma(x, (\rho_{\epsilon}*\Xi)(x))Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)\big) h(x)
-\end{multline}
-and furthermore, we apply Fubini theorem to get that 
-\begin{multline}
-  2 \ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x)) \int_{0}^{\infty} u    (g(x,u)-1) du \\
-  =   2 \ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x)) \int_{0}^{\infty} \int_{0}^{u}    dv_1 (g(x,u)-1) du \\
-  =  2 \ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x)) \int_{0}^{\infty}  \int_{v_1}^{\infty}    (g(x,u)-1) du dv_1.
-\end{multline}
-Finally, note also that
-\begin{multline}
-\int 2\bigg(g(x,u)\gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\times \ell \int_u^{
-\infty}(g(x,v_1)-1)dv_1\bigg)du\\
-= 2\ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\int \bigg( g(x,u) \int_u^{
-\infty}(g(x,v_1)-1)dv_1\bigg)du.
-\end{multline}
-\normalsize
-Combining all results we have that
-\small
-\begin{equation}\label{eq: Non-local lookdown generator MMP calculation}
-\begin{aligned}
-\alpha A^{\text{nl}}_{\epsilon}f(\eta)
-=&~ e^{-\langle h(x),\Xi(dx)\rangle}  \Bigg\{\left\langle \gamma(x, (\rho_{\epsilon}*\Xi)(x))B(h(\cdot) r( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)-h(\cdot)Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x),\Xi(dx) \right\rangle\\
-&+\bigg \langle2\ell\gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\int_{0}^{\infty} u (g(x,u)-1) du \\
- &+ \big(F(x, (\rho_{\epsilon}*\Xi)(x))+\gamma(x, (\rho_{\epsilon}*\Xi)(x))Br( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)\big) h(x) ,\Xi(dx)\bigg\rangle\\
- & +\left\langle 2 \ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\int g(x,u)\int_u^{
-\infty}(g(x,v_1)-1)dv_1 du,\Xi(dx)\right\rangle \Bigg\}\\
-=&~ e^{-\langle h(x),\Xi(dx)\rangle}  \Bigg\{\left\langle \gamma(x, (\rho_{\epsilon}*\Xi)(x))B(h(\cdot) r( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)+ F(x, (\rho_{\epsilon}*\Xi)(x),\Xi(dx) \right\rangle\\
-&+\bigg \langle 2 \ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x)) \int_{0}^{\infty}  \int_{v_1}^{\infty}    (g(x,u)-1) du dv_1 \\
- & + 2\ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))\int_0^{\infty} g(x,u)\int_u^{
-\infty}(g(x,v_1)-1)dv_1 du,\Xi(dx)\bigg\rangle \Bigg\}\\
-=&~ e^{-\langle h(x),\Xi(dx)\rangle}  \Bigg\{\bigg\langle \gamma(x, (\rho_{\epsilon}*\Xi)(x))B(h(\cdot) r( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)+ F(x, (\rho_{\epsilon}*\Xi)(x)\\
-& + \ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))2 \int_0^{\infty} (g(x,u)-1)\int_u^{
-\infty}(g(x,v_1)-1)dv_1 du,\Xi(dx)\bigg\rangle \Bigg\}\\
-=&~ e^{-\langle h(x),\Xi(dx)\rangle} \times \Bigg\{\bigg\langle \gamma(x, (\rho_{\epsilon}*\Xi)(x))B(h(\cdot) r( \cdot, (\rho_{\epsilon}* \Xi)(\cdot))(x)+ F(x, (\rho_{\epsilon}*\Xi)(x)\\
-& + \ell \gamma(x, (\rho_{\epsilon}*\Xi)(x)) r(x, (\rho_{\epsilon}*\Xi)(x))h(x)^2,\Xi(dx)\bigg\rangle \Bigg\}\\
-:=&~\mathcal{L}^{nl}_{\epsilon}\alpha f(\eta),
-\end{aligned}
-\end{equation}
-\normalsize
-where $\mathcal{L}^{nl}_{\epsilon}$ is the generator of a non-linear superprocess of the form characterised in Equation \eqref{eq: Empirical Measure Martingale characterisation - product form}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-
-\section{Technical Lemmas}
-\subsection{Gaussian Kernel Estimates}
-
-\begin{lemma}\label{eq: Gaussin density estimates}
-\begin{equation}
- \theta H_{\theta}(x,w)\rho_r(x-w)\leq \rho_{\gamma}(x-w),
-\end{equation}
-where
-$$H_{\theta}(x,w)=\int_{\IR^d}
-    \left(
-        \frac{\rho_r(y-w)}{\rho_r(x-w)}
-        -
-        1
-    \right)^2
-q_{\theta}(x,dy).$$
-\end{lemma}
-\begin{proof}
-
-Writing out $H$,
-\begin{align}
-H_\theta(x, w)
-=
-\int
-    \left(
-        \exp\left(
-            - \frac{1}{2\epsilon_r^2}
-            \left\{
-                ||y - w||^2 - ||x - w||^2
-            \right\}
-        \right)
-        -
-        1
-    \right)^2
-    \frac{
-        e^{-\theta (y - x-\meanq)^{T}\covq^{-1}(y - x-\meanq)  / 2}
-    }{
-        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
-    }
-dy.
-\end{align}
-Writing $z=y-x-\meanq$, we have that 
-\begin{equation}
-\begin{aligned}
-||y - w||^2 - ||x - w||^2 
-=& ||y||^2-||x||^2 -2\langle y-x, w\rangle \\
-=&||x+z+ \meanq||^2-||x||^2-2 \langle z+ \meanq, w\rangle\\
-=&2\langle x, z+ \meanq \rangle + ||z+ \meanq||^2-2 \langle z+ \meanq, w\rangle \\
-=& 2 \langle x-w, z+ \meanq \rangle + ||z+ \meanq||^2\\
-=& 2\langle x-w+ \meanq,\meanq \rangle + 2\langle x-w+ \meanq, z \rangle +||z||^2
-\end{aligned}
-\end{equation}
-As a result, we have 
-\begin{align}
-H_\theta(x, w)
-=&
-\int
-    \left(
-        \exp\left(
-            - \frac{1}{2\epsilon_r^2}
-            \left\{
-                2 \langle x-w, z+ \meanq \rangle + ||z+ \meanq||^2
-            \right\}
-        \right)
-        -
-        1
-    \right)^2
-    \frac{
-        e^{-\theta z^{T}\covq^{-1}z  / 2}
-    }{
-        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
-    }
-dz\\
-=&\exp\left(-\frac{2}{\epsilon_r^2}\langle x-w+ \meanq,\meanq \rangle \right)\\
-& \times \int
-        \frac{
-        \exp\left(
-            - \frac{2}{\epsilon_r^2} \langle x-w+ \meanq, z \rangle
-            - \frac{1}{\epsilon_r^2} ||z||^2
-            \right)
-            e^{-\theta z^{T}\covq^{-1}z  / 2}
-    }{
-        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
-    }
-dz\\ \label{eq: Second moment term matrix calculation}
-&-2\exp\left(-\frac{1}{\epsilon_r^2}\langle x-w+ \meanq,\meanq \rangle \right)\\
-& \qquad \qquad \times     \int
-    \frac{ \exp\left(
-             -\frac{1}{\epsilon_r^2}\langle x-w+ \meanq, z \rangle
-              -\frac{1}{2\epsilon_r^2} ||z||^2
-            \right)e^{-\theta z^{T}\covq^{-1}z  / 2}
-        }{
-        (2 \pi/ \theta)^{d/2} |\covq|^{1/2} \label{eq: first moment term matrix calculation}
-    }
-dz\\
-&+1.
-\end{align}
-We now consider the integral of the form 
-\begin{equation}
-\int \exp(v^{T}z-C||z||^2) \frac{
-        e^{-\theta z^{T}\covq^{-1}z  / 2}
-    }{
-        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
-    }
-dz   
-\end{equation}
-for $v \in \IR^d$ and $C>0$. 
-We have 
-\begin{equation}
-\begin{aligned}
-&\int \exp(v^{T}z-C||z||^2) \frac{
-        e^{-\theta z^{T}\covq^{-1}z  / 2}
-    }{
-        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
-    }
-dz\\
-=&\frac{1}{|\covq|^{1/2}|  |\covq^{-1}(I+2C\covq/\theta )|^{1/2}  }\int \exp(v^{T}z) \frac{
-        e^{-\theta z^{T}\covq^{-1}(I+2C\covq/\theta )z  / 2}
-    }{
-        (2 \pi/ \theta)^{d/2}|\covq^{-1}(I+2C\covq/\theta )|^{-1/2} 
-    }
-dz\\
-=& \frac{1}{|I+2C\covq/\theta |^{1/2}} \mathbb{E}_{Z}[\exp (v^{T}Z)]\\
-=&\frac{1}{|I+2C\covq/\theta |^{1/2}}
-\exp 
-\left(
-\frac{1}{2}v^{T}\covq/\theta(I+2C\covq/\theta )^{-1}v
-\right),
-\end{aligned}
-\end{equation}
-where $Z \sim N(0, \covq/\theta \times (I+2C\covq/\theta )^{-1})$.
-
-Now writing $v=\frac{2}{\epsilon_r^2}( w-x-\meanq)$
-and $C=\frac{1}{\epsilon_r^2}$,
-we have the expression in Equation
-\eqref{eq: Second moment term matrix calculation} is 
-$$\frac{1}{|I+2\covq/(\epsilon_r^2\theta) |^{1/2}}
-\exp 
-\left(
-\frac{2}{\epsilon_r^4}( w-x-\meanq)^{T}\covq/\theta\left(I+2\covq/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
-\right).$$
-Similarly, writing $v=\frac{1}{\epsilon_r^2}( w-x-\meanq)$
-and $C=\frac{1}{2\epsilon_r^2}$,
-we have the expression in Equation
-\eqref{eq: first moment term matrix calculation} is 
-$$\frac{1}{|I+\covq/(\epsilon_r^2\theta) |^{1/2}}
-\exp 
-\left(
-\frac{1}{2\epsilon_r^4}( w-x-\meanq)^{T}\covq\left(I+\covq/\theta/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
-\right).$$
-As a result, we have 
-\begin{align*}
-&H_{\theta}(x,w)\\
-=& \frac{1}{|I+2\covq/(\epsilon_r^2\theta) |^{1/2}}
-\exp 
-\left(
-\frac{2}{\epsilon_r^4}( w-x-\meanq)^{T}\covq/\theta\left(I+2\covq/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
-\right)\\
-&-2\frac{1}{|I+\covq/(\epsilon_r^2\theta) |^{1/2}}
-\exp 
-\left(
-\frac{1}{2\epsilon_r^4}( w-x-\meanq)^{T}\covq/\theta\left(I+\covq/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
-\right)\\
-&+1.
-\end{align*}
-If we write $F(1/\theta)=H_{\theta}(x,w)$, i.e.
-\begin{align*}
-&F(s)\\
-=& \frac{1}{|I+2/\epsilon_r^2 \covq s |^{1/2}}
-\exp 
-\left(
-\frac{2}{\epsilon_r^4}( w-x-\meanq)^{T}\covq s \left(I+2/\epsilon_r^2 \covq s\right)^{-1}( w-x-\meanq)
-\right)\\
-&-2\frac{1}{|I+2/\epsilon_r^2 \covq s |^{1/2}}
-\exp 
-\left(
-\frac{1}{2\epsilon_r^4}( w-x-\meanq)^{T}\covq s \left(I+2/\epsilon_r^2 \covq s\right)^{-1}( w-x-\meanq)
-\right)\\
-&+1\\
-&=G_1(s)+2G_2(s)+1
-\end{align*}
-we can check that $F(0)=0$.
-As a result, 
-$$\theta H_{\theta}(x,w)\rho_r(x-w)= \theta F(1/\theta)\rho_r(x-w)=F'(s)\rho_r(x-w),$$
-for some $s \in [0, 1/\theta]$.
-
-In Equation \eqref{eq: gamma-r convolution comparison}, we have established that 
-$\rho_r(x-w) / \rho_\gamma(x-w) = C' \exp(-K (x-w)^2 / 2)$
-with $K = \frac{1}{\epsilon_r^2} - \frac{1}{\epsilon_\gamma^2}$.
-Therefore it suffices to show that for all $x,w \in \IR^d$ and $s \in [0, 1/\theta]$, 
-\begin{align}\label{eqn:goal3}
-    F'(s) \exp\left(-A (x-w)^2 \right) \le C .
-\end{align}
-
-We consider how to differentiate function $G$ of the form 
-$$G(s):=\frac{1}{|I+As|^{1/2}}\exp(v^{T}Bs(I+Cs)^{-1}v),$$
-where $A,B,C$ are matrices with non-negative entries and $I$ is the identity matrix.
-
-Since 
-\begin{equation}
-\begin{aligned}
-G'(s)=& - \frac{|A|}{2|I+As|^{3/2}}\exp(v^{T}Bs(I+Cs)^{-1}v)\\
-      & + \frac{1}{|I+As|^{1/2}}\exp(v^{T}Bs(I+Cs)^{-1}v)\\
-      & \qquad \times \left\{ v^{T}B(I+Cs)^{-1}v
-                            - sv^{T}BC(I+Cs)^{-2}v
-                    \right\}\\
-      &=\left(- \frac{|A|}{2|I+As|}+v^{T}B(I+Cs)^{-2}v
-        \right)\\
-      & \qquad \times
-        \frac{1}{|I+As|^{1/2}}\exp(v^{T}Bs(I+Cs)^{-1}v),
-\end{aligned}
-\end{equation}
-using non-negativity of $A,B,C$ we have
-\begin{equation}
-\label{eq: bounds on G'}
-|G'(s)| \leq (|A|+||B||_{2}||v||_2^2)G(s).    
-\end{equation}
-As a result, we have that 
-\begin{equation}
-\label{eq: bounds on G}
-G(s) \leq K e^{|A|+||B||_{2}||v||_2^2)s}, ~~   G'(s)(|A|+||B||_{2}||v||_2^2)K e^{|A|+||B||_{2}||v||_2^2)s}.  
-\end{equation}
-
-Finally note that, 
-$$F'(s) \leq G_1'(s)+2G_2'(s),$$
-where 
-$$A_1= 2\epsilon_r^{-2} \covq, ~ v_1=\epsilon_r^{-2}(w-x-\meanq), ~B_1 = 2\covq, ~C_1=2\epsilon_r^{-2} \covq,$$
-and 
-$$A_2= 2\epsilon_r^{-2} \covq, ~ v_2=\epsilon_r^{-2}(w-x-\meanq), ~B_2 = \covq/2, ~C_2=2\epsilon_r^{-2} \covq,$$
-Substituting these quantities on Equation \eqref{eq: bounds on G} shows that Equation \eqref{eqn:goal3} is satisfied as long as $\epsilon_r < \epsilon_\gamma$.
-
-\end{proof}
-\section{Topological Results on Lookdown Representations}
-\label{sec: Topologies on Lookdown}
-
-\subsection{Euclidean-Vague Topology on $\IR^d \times [0,\infty]$}\label{sec: Convergence in Product Topology}
-We first define a topology on $\IR^d \times [0,\infty]$ which is Euclidean on $\IR^d$ and vague in $[0,\infty]$.
-\begin{definition}
-We define the topology $\mathfrak{p}$ on $\IR^d \times [0,\infty]:$
-we say $(x_n,u_n) \to (x,u)$ in topology $\mathfrak{p}$ if 
-\begin{enumerate}
-    \item $|x_n-x| \to 0$ in $\IR^d$.
-    \item  For all $g \in C_{c}([0,\infty])$, the space of continuous functions with compact support on $[0,\infty]$, $g(u_n) \to g(u).$ Since this is the vague convergence for $(\delta_{u_n})_{n \in \mathbb{N}}$ we will abuse a bit the notation and denote this by the symbol $u_n \xrightarrow{vague} u$.
-\end{enumerate}
-\end{definition}
-
-In other words, our topology is Euclidean in space $\IR^d$ and vague in levels in $[0,\infty]$.
-\begin{lemma}\label{Vague times Euclidean is Polish}
-The space $\IR^d \times [0,\infty]$ under topology $\mathfrak{p}$ is Polish.
-\end{lemma}
-\begin{proof}
-The space $C_c([0,\infty])$ is dense, so we pick a countable dense subset $S:=\{h_n: n \in \mathbb{N}\} \subset C^{1}_c([0,\infty])$ and define the metric $\mathfrak{d}$ such that $\mathfrak{d}(u,v)=\sum_{n=1}^{\infty}\frac{1 \wedge |h_n(u)-h_n(v)|}{2^n}$.
-
-Assume that $u_n \xrightarrow{vague} u$.
-Pick arbitrary $\delta>0$ and take $N$ large enough such that $\frac{1}{2^N}<\delta/2$.
-Furthermore, pick $n$ large enough such that $\inf_{i=1,2,...,N}|h_i(u_n)-h_i(u)|<\delta/2$.
-From this we immediately have that $\mathfrak{d}(u_n,u)<\delta$.
-Thus $\mathfrak{d}(u_n,u) \to 0$.
-
-Conversely assume that $\mathfrak{d}(u_n,u) \to 0$.
-For any $h \in \mathcal{C}^{1}_c([0,\infty])$ and for any $\delta>0$, pick $g_N$ such that $||h-h_N||_{\infty}<\delta /3$ and $n$ large enough such that $\mathfrak{d}(u_n,u)< \frac{\delta}{3 \times 2^N}$.
-Then $|h(u)-h(u_n)|< |h(u)-h_N(u)|+|h_N(u)-h_N(u_n)|+|h_N(u_n)-h(u_n)|<\delta$, and so $h(u_n) \to h(u)$.
-
-Finally, one can easily check that $\mathbb{Q}$ is a countable dense set in $[0,\infty]$ equipped with the metric $\mathfrak{d}$.
-Defining the metric $d_{\mathfrak{p}}$
-by
-$$d_{\mathfrak{p}}((x_1,u_1),(x_2,u_2))=||x_1-x_2||+\mathfrak{d}(u_1,u_2),$$
-we can show easily that
-convergence in $d_{\mathfrak{p}}$
-is equivalent to convergence in 
-$\mathfrak{p}$ topology.
-\end{proof}
-
-\subsection{Vague Topology on Measures}\label{sec: Empirical Measure Topology}
-
-We now characterise the lookdown representation
-of our particle system
-as a measure on 
-$(\IR^d \times [0, \infty], \mathfrak{p})$.
-We endow the vague topology
-on these measures for
-convergence of lookdown representations.
-We refer to Theorem A.23 and Theorem A.24 in \cite{kallenberg1997foundations}.
-
-First of all,
-as $(\IR^d \times [0, \infty], \mathfrak{p})$
-is Polish,
-the family of $C^{+}_K$ of continuous functions
-$$f: \mathbb{R^d} \times [0, \infty] \to \IR^{+}$$
-with compact support
-is separable in the uniform metric. 
-The sets $K_n =[-n, n]^d \times [0,n]$ clearly forms a sequence of compact sets and $K_n \uparrow \mathbb{R^d} \times [0, \infty]$.
-
-We denote $\mathcal{M}(\mathbb{R^d} \times [0, \infty])$ as the class of measures on $\mathbb{R^d} \times [0, \infty]$ that are 
-locally finite (i.e. bounded on bounded intervals),
-and write $\pi_B, \pi_f$ 
-for the mappings 
-$\mu \to \mu B$, $\mu \to \mu f := \int f d\mu$,
-respectively,
-on $\mathcal{M}(\mathbb{R^d} \times [0, \infty])$.
-
-The \textit{vague topology} in $\mathcal{M}(\mathbb{R^d} \times [0, \infty)$ is generated by the maps $\pi_f, f \in C^{+}_K$, and 
-we write the cague convergence of $\mu_n$ toward $\mu$
-as $\mu_n \xrightarrow{v} \mu$.
-
-Taking $S= \mathbb{R^d} \times [0, \infty]$
-in Theorem A.23
-in \cite{kallenberg1997foundations},
-we have
-\begin{theorem}[vague topology]
-\label{teo: Kallenberg vague results}
-
-The following holds:
-\begin{enumerate}
-    \item $\mathcal{M}(\mathbb{R^d} \times [0, \infty])$ is a Polish space in the vague topology
-    \item A set $A \subset \mathcal{M}(\mathbb{R^d} \times [0, \infty])$ is vaguely relatively compact iff 
-    $\sup_{\mu \in A} \mu f < \infty$ for all $f \in C^{+}_K$
-    \item if $\mu_n \xrightarrow{v} \mu$ and a set $B$ is finite with $\mu \partial B = 0$, then $\mu_n B \to \mu B$.
-\end{enumerate}
-
-\end{theorem}
-
-\begin{corollary}
-\label{cor: Vague Compact sets}
-For any arbitrary $M,K>0$, the set 
-$$\mathcal{M}_{K,M}:= \{\mu \in \mathcal{M}(\mathbb{R^d} \times [0, \infty]): M^{-1}\mu([-M,M]^d \times [0,M]) \leq K\}$$   
-is a compact subset in 
-$\mathcal{M}(\mathbb{R^d} \times [0, \infty])$ 
-under the vague topology.
-\end{corollary}
-\begin{proof}
-For any function $f \in C^{+}_K$, it is compactly supported and
-so there exists a constant $C_f > ||f||_{\infty}$.
-As a result, 
-$$\sup_{\mu \in \mathcal{M}_{K,M}} \mu f < C_f \times \mu \{ supp(f) \cap [-M,M]^d \times [0,M]\} \leq C_f M^{-1} K < \infty.$$
-
-Since $f$ is arbitrary, by (ii) of Theorem \ref{teo: Kallenberg vague results}, 
-the set
-$\mathcal{M}_{K,M}$
-is vaguely relatively compact.
-
-We now prove that $\mathcal{M}_{K,M}$ is a closed subset of $\mathcal{M}(\mathbb{R^d} \times [0, \infty])$.
-
-Since $[-M,M]^d \times [0,M]$ is finite, by part 3 of Theorem \ref{teo: Kallenberg vague results},
-for any sequence in $(\mu_n)_{n \in \mathbb{N}}$ in  $\mathcal{M}_{K,M}$ that converges vaguely to $\mu$ in 
-$ \mathcal{M}(\mathbb{R^d} \times [0, \infty])$, 
-$$MK \geq \mu_n([-M,M]^d \times [0,M]) \to \mu([-M,M]^d \times [0,M]).$$
-Therefore, $\mu \in \mathcal{M}_{K,M}$.
-As a result, $\mathcal{M}_{K,M}$ is closed and relatively vaguely compact, so it is vaguely compact.
-\end{proof}
-
-\begin{theorem}
-    \label{teo: Vague Relative Compactness through Projection}
-For any Polish space $S$, let $f_1,f_2,...,$ be a dense collection of functions in $C^{+}_{K}$ that is closed under addition, then a set $A \in \mathcal{D}_{\mathcal{M}(S)}([0,\infty))$ is relative compact if and only if $Af_j = \{xf_j: x \in A\}$ is relatively compact on $\mathcal{D}_{[0, \infty)}([0,\infty))$ for every $j \in \mathbb{N}$.
-\end{theorem}
-\begin{proof}
-See \cite{kallenberg1997foundations} Theorem A2.4.
-\end{proof}
-\begin{definition}
-We define $\mathfrak{G}_{\leq 1}$ to be the set of functions $g \in \mathcal{C}(\IR^d \times [0, \infty) \to \IR)$ such that 
-$g(\cdot, u) \in \mathcal{C}_{0}(\IR^d)$ for all $u \geq 0$, and there exists some $u_{*}>0$, such that $g(x,u)=1$ for all $u \geq u_{*}$.
-\end{definition}
-
-\begin{lemma}\label{lem: Dense set for test functions on empirical measures} For $g \in \mathfrak{G}_{\leq 1}$, define $F_g(\xi):= \exp(-\langle \log g, \cdot \rangle )$. The set of functions 
-$$\left\{\sum_{m=1}^{N}a_m F_{g_m}(\cdot) ~~|~~ g_1,...,g_N \in \mathfrak{G}_{\leq 1}\right\}$$
-is dense in $C(\mathcal{M}(\mathbb{R^d} \times [0, \infty]),\IR)$.
-\end{lemma}
-\begin{proof}
-Direct application of Stone-Weierstrass Theorem.
-These finite combinations are closed under addition by construction, and they are closed under multiplication as $F_{g_1}(\cdot) \times F_{g_2}(\cdot):=F_{g_1 \times g_2}(\cdot)$.
-Thus we have a subalgebra that also clearly separates points and vanishes nowhere.
-\end{proof}
-
-Combining Theorem \ref{teo: Vague Relative Compactness through Projection} and Lemma \ref{lem: Dense set for test functions on empirical measures}, we have that $\{\xi^N_t: N \in \mathbb{N}\}$ is tight as a $\mathcal{M}(\mathbb{R^d} \times [0, \infty])$-valued stochastic process in the vague topology as long as $\{F_g(\xi^N_t): N \in \mathbb{N}\}$ is tight as real-valued stochastic processes
-for all $g \in \mathfrak{G}_{\leq 1}$. 
-\bibliographystyle{plainnat}
-\bibliography{refs.bib,plr_refs.bib}
-
-\end{document}

### 2023-01-30 topological.tex
edits!

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Topological Results on Lookdown Representations}
\label{sec: Topologies on Lookdown}
\subsection{Topology for convergence of lookdown representations}

Recall that
the lookdown representation has a spatial component and a level component.
Specifically, for fixed $N>0$ and $t>0$,
the lookdown representation $\xi^N(t)$ 
is a finite measure on $\overline{\mathbb{R}^d} \times [0,N]$.
Furthermore, the level of a particle in our lookdown representation can shoot to infinity in finite time.
Therefore, to characterise convergence of $\xi^N(t)$ as $N \to \infty$,
we need to impose an appropriate vague topology on $\mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty))$,
the space of finite measures on $\overline{\mathbb{R}^d} \times [0,\infty)$.
Similarly, to characterise convergence of the level process of individual lineages, we consider the vague topology on $[0,\infty)$.

We now refer to the vague topology on measure spaces introduced in P564, \S A2 in \cite{kallenberg1997foundations}.
Let $S$ be a locally compact Polish space and $\hat{S}$ be the class of bounded sets in $S$.
We consider the family $C^{+}_c(S)$ of positive continuous functions with compact support. It is known that $C^{+}_c$ is separable in the uniform metric.
We now consider $\mathcal{M}(S)$, the class of measures on $S$ that are locally finite.
The \textit{vague topology} on $\mathcal{M}(S)$ is generated by the the maps $\mu \to \mu f := \int f d \mu$, where $f\in C^{+}_{c}(S)$.
In other words, convergence of $\mu^n \to \mu$ in the vague topology holds if 
$$\int f d\mu^n \to \int f d\mu$$
for all $f\in C^{+}_{c}(S)$.

We now introduce an important theorem on compactness in the vague topology.
\begin{theorem}[Theorem A.23 in \cite{kallenberg1997foundations}]
For any locally compact, second-countable Hausdorff Space $S$, 
we have
\begin{itemize}
\item $\mathcal{M}(S)$ is Polish in the vague topology,
\item a set $A\subset \mathcal{M}(S)$ is vaguely relatively compact iff $\sup_{\mu\in A} \mu f < \infty$ for all $f \in C^{+}_{c}$
\item if $\mu_n \to \mu$ in the vague topology and $B \in \hat{S}$ with $\mu \partial B = 0$, then $\mu_n B \to \mu B$
\end{itemize}
\end{theorem}

To characterise convergence of lookdown representations,
we take $S = \overline{\mathbb{R}^d} \times [0,\infty)$.
We now identify compact sets under the vague topologies.

\begin{lemma}
\label{lem: vague compact sets}
For any fixed $N.0, K>0$, the set 
$$\Gamma_{N,K} := \left\{\mu \in \mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty)):  \frac{1}{N}\mu(\overline{\mathbb{R}^d}\times [0,N]) \leq K \right\}$$
is vaguely compact in $\mathcal{M}(S)$.
\end{lemma}

\begin{proof}
It suffices to show that $\Gamma_K$ is vaguely relatively compact and vaguely closed.
For any fixed $f \in C^{+}_c$, $f$ is bounded above uniformly by $||f||_{\infty}$.
Therefore, 
we have that $ \sup_{\mu \in  \Gamma_K} \mu f \leq  ||f||_{\infty} \mu(\overline{\mathbb{R}^d}\times [0,N])  \leq ||f|| K N < \infty$,
so $\Gamma_{N,K}$ is vaguely relatively compact.

Now it suffices to prove that $\Gamma_K$ is closed under the vague topology.
Consider a vaguely converging sequence $(\mu_n)_{n \geq 1}$ in $\Gamma_{N,K}$
with limit $\mu_n \to \mu \in \mathcal{M}(S)$.
We pick some test functions $\{f_m : m \geq 0 \}$ monotonically increasing to $1_{\overline{\mathbb{R}^d}\times[0,N]}(x)$.

Since for each $n>0$ and $m > 0$,
$\frac{1}{N}\langle f_m , \mu_n \rangle < K$,
by Dominating Convergence Theorem,
\begin{equation}
\frac{1}{N}\mu(\overline{\mathbb{R}^d}\times [0,N])
= \lim_{m \to \infty} \frac{1}{N}\langle f_m , \mu \rangle
=\lim_{m \to \infty} \lim_{n \to \infty} \frac{1}{N}\langle f_m , \mu_n \rangle
\leq K,
\end{equation}
and so $\mu \in \Gamma_{N,K}$.
Therefore $\Gamma_{N,K}$ is vaguely compact. 
\end{proof}

We now include another theorem that is very relevant to establishing tightness of $\mathcal{M}(S)$-valued processes in the Skorokhod topology. It can be found as Theorem 3.9.1 in \cite{EK}.

\begin{theorem}[\cite{EK} Theorem 3.9.1]
\label{teo: EK tightness theorem}
Let $(S,r)$ be complete and separable, and let $\{X_{\alpha}\}$ be a family of processes with sample paths in $D_{S}([0,\infty))$.
Suppose that the compact containment condition holds. That is, for every $\eta > 0$ and $T > 0$,
there exists a compact set $\Gamma_{\eta, T} \subset E$ for which 
\begin{equation}
\inf_{\alpha} P \{ X_{\alpha}(t) \in \Gamma_{\eta,T}  ~~ \text{for } 0\leq t \leq T\} \geq 1- \eta
\end{equation}
Let $H$ be a dense subset of $\overline{C}(E)$ (bounded continuous functions on $E$) in the topology of uniform convergence on compact sets. 
Then $\{X_{\alpha}\}$ is relatively compact if and only if $\{f(X_{\alpha})\}$ is relatively compact (as a family of processes with sample paths in $\mathcal{D}_{\mathbb{R}}([0,\infty))$) for each $f \in H$.
\end{theorem}

To apply Theorem \ref{teo: EK tightness theorem},
we need to identify dense subset of $\overline{C}(\mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty)))$.
Since the space $\mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty))$ is not compact but locally compact,
we will apply Stone-Weierstrass theorem for locally compact space.

\begin{lemma}[Stone-Weierstrass Theorem for locally compact space]
\label{lem: SW locally compact}
Let $X$ be a locally compact Hausdorff space, and consider the set  $C_{\infty}(X, \mathbb{R})$ of real-valued continuous functions which vanishes at infinity. 
Let $\mathcal{A}$ be a subalgebra in $C_{\infty}(S)$. Then $\mathcal{A}$ is dense in $C_{\infty}(X, \mathbb{R})$ if and only if it separates points and vanishes nowhere.
\end{lemma}

With this version of Stone-Weierstrass Theorem, we can prove the following lemma.
\begin{lemma}
\label{lem: uniform compact density}
We write $\mathcal{A}$ for the algebra (closed under multiplication and addition) generated by 
the collection of functions $\xi \mapsto \langle f, \xi \rangle$, where $ f \in C_c(\overline{\mathbb{R}^d} \times [0,\infty))$ is differentiable in $u$ and smooth in $x$ with bounded support.
Then $\mathcal{A}$ is dense in $C(\mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty)))$ under the topology of uniform convergence on compact sets.
\end{lemma}
\begin{proof}
Since $\mathcal{A}$ contains the functions $\langle \rho_{\varepsilon}*\mathbbm{1}_{A} , \mu \rangle$,
where $\rho$ is some mollifier and $A$ is a compact set, it clearly
separates points and vanishes nowhere.
Therefore, $\mathcal{A}$ is dense in $C_{\infty}(\mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty)), \mathbb{R})$.

Furthermore, under the topology of uniform convergence on compact sets, 
$C_{\infty}(\mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty)), \mathbb{R})$ 
contains the mollified indicator functions $\langle \rho_{\varepsilon}*\mathbbm{1}_{A} , \mu \rangle$,
which are dense in $C(\mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty)))$.
\end{proof}

Finally, we include another technical lemma on the products of real-valued stochastic processes. 
\begin{lemma}
\label{teo: product tightness}
Let $\{(X^n_t)_{t \geq 0}: n \geq 0\}, \{(Y^m_t)_{t \geq 0}: m \geq 0\}$ be two tight sequences of real-valued process under the Skorokhod topology.
Then the sequence of processes $\{(X^n_tY^n_t)_{t \geq 0}: n \geq 1\}$ is tight under the Skorokhod topology.
\end{lemma}

\begin{proof}
We apply the Aldous Criterion of tightness on the real-valued sequences
$\{(X^n_tY^n_t)_{t \geq 0}: n=1,2,.. \}$. 
It suffices to show that
for fixed sequences of stopping time $\tau_n$ bounded above by $T$,
for each $\varepsilon>0$,
there exists $\delta > 0$ and $n_0$ such that
\begin{equation}
\sup_{n \geq n_0}\sup_{\theta \in [0, \delta]} \mathbb{P}\left[|X^n_{\tau_n+\theta}Y^n_{\tau_n+\theta} - X^n_{\tau_n}Y^n_{\tau_n} | > \varepsilon \right] \leq \varepsilon.
\end{equation}

First note that 
\begin{equation}
|X^n_{\tau_n+\theta}Y^n_{\tau_n+\theta} - X^n_{\tau_n}Y^n_{\tau_n} |
= |X^n_{\tau_n+\theta}(Y^n_{\tau_n+\theta}-Y^n_{\tau_n}) +Y^n_{\tau_n}( X^n_{\tau_n+\theta}- X^n_{\tau_n})|,
\end{equation}
therefore
\begin{equation}
\begin{aligned}
& \mathbb{P}\left[|X^n_{\tau_n+\theta}(Y^n_{\tau_n+\theta}-Y^n_{\tau_n}) +Y^n_{\tau_n}( X^n_{\tau_n+\theta}- X^n_{\tau_n})| > \varepsilon \right]\\
 \leq &
\mathbb{P}\left[\max\{|X^n_{\tau_n+\theta}(Y^n_{\tau_n+\theta}-Y^n_{\tau_n})|, | Y^n_{\tau_n}( X^n_{\tau_n+\theta}- X^n_{\tau_n}) |\}> \varepsilon/2 \right]\\
\leq & \mathbb{P}\left[|X^n_{\tau_n+\theta}(Y^n_{\tau_n+\theta}-Y^n_{\tau_n})|> \varepsilon/2 \right] + \mathbb{P}\left[ | Y^n_{\tau_n}( X^n_{\tau_n+\theta}- X^n_{\tau_n}) |> \varepsilon/2 \right]
\end{aligned}
\end{equation}

By Corollary 3.7.1 in \cite{EK}, both $\{(X^n_t)_{t \geq 0}: n \geq 0\}, \{(Y^m_t)_{t \geq 0}: m \geq 0\}$ satisfies the compact containment condition, i.e. so for any $\varepsilon'>0$ and fixed time $T> 0$, there exists $K_{\varepsilon',T}>0$ such that

\begin{equation}
 \limsup_{n \to \infty} \mathbb{P}\left\{ \sup_{t\in [0,T]}X^n_t > K_{\varepsilon',T} \right\} < \epsilon',
\end{equation}
and 
\begin{equation}
 \limsup_{n \to \infty} \mathbb{P}\left\{ \sup_{t\in [0,T]}Y^n_t > K_{\varepsilon',T} \right\} < \epsilon'.
\end{equation}

Conditioning on the event $\left\{ \sup_{t\in [0,T]}Y^n_t > K_{\varepsilon',T} \right\}$ and $\left\{ \sup_{t\in [0,T]}Y^n_t > K_{\varepsilon',T} \right\},$

\begin{equation}
\begin{aligned}
& \mathbb{P}\left[|X^n_{\tau_n+\theta}(Y^n_{\tau_n+\theta}-Y^n_{\tau_n})|> \varepsilon/2 \right] + \mathbb{P}\left[ | Y^n_{\tau_n}( X^n_{\tau_n+\theta}- X^n_{\tau_n}) |> \varepsilon/2 \right]\\
\leq & \mathbb{P}\left[|(Y^n_{\tau_n+\theta}-Y^n_{\tau_n})|> \frac{\varepsilon}{2K_{\varepsilon',T}}\right] + \mathbb{P}\left[ | Y^n_{\tau_n}( X^n_{\tau_n+\theta}- X^n_{\tau_n}) |> \frac{\varepsilon}{2K_{\varepsilon',T}}\right] + 2 \varepsilon'\\
\leq & \frac{\varepsilon}{K_{\varepsilon',T}}+2 \varepsilon',
\end{aligned}
\end{equation}
and by tightness of $(X^n_t, Y^n_t)_{t \geq 0}$,
there exists $\delta > 0$ and $n \geq n_0$ such that the last term is smaller than $\varepsilon$ for 
for all $\theta < \delta$ and $n\geq n_0$.
\end{proof}

When we work with lookdown representations, we work on test functions of the form
\begin{equation}
F_g(\xi) = \prod_{(x,u) \in \xi} g(x,u),
\end{equation}
where $g(x,u)$ is differentiable in $u$, smooth in $x$.
and satisfies the property that $0\leq g(x,u) \leq 1$,
and that there exists $u^*$ such that for all $u > u^*$,
$g(x, u) =1$.

In fact, there is a one-to-one correspondence between $C^{+}_c(S)$
and test functions of the form $F_g$.
For all $f \in C^{+}_c(S)$,
if we write $g = e^{-f}$,
then
\begin{equation}
F_g(\xi)= e^{-\langle f, \xi \rangle}.
\end{equation}

Furthermore,
we know that for any $x_1, x_2 \in [0,N]$,
$$|x_1-x_2|\geq |e^{-x_1}-e^{-x_2}| \geq e^{-N}|x_1-x_2|,$$
so we can control $\langle f, \xi^n_t \rangle $ by controlling $F_g(\xi^n_t)$ as long as 
there exists some $N > 0$ such that $\langle f, \xi^n_t \rangle < N$.

With the above observation,
we have the following lemma.

\begin{lemma}
We consider a sequence $(\xi^n_t)_{t\geq 0}$ of $\mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty))$-valued cadlag processes.

Assume that the sequence $(\xi^n_t)_{t\geq 0}$ satisfies the compact containment condition. That is,
for all $\varepsilon > 0$ and fixed time $T > 0$, there exists $N, K> 0$ such that 
\begin{equation}
\liminf_{n \to \infty} \mathbb{P}\{ \xi^n_t \in \Gamma_{N,K} \text{ for all } t\in [0,T]\} > 1-\varepsilon,
\end{equation}
where $\Gamma_{N,K}$ is the compact set in Lemma \ref{lem: vague compact sets}

Assume that for all test functions of the form $F_g$,
the sequence $\{(F_g(\xi^n_t))_{t \geq}: n=1,2,...\}$ of real-valued cadlag processes are relatively compact.

Then  $(\xi^n_t )_{t\geq 0}$ is relatively compact in $\mathcal{D}_{\mathcal{M}(\overline{\mathbb{R}^d} \times[0,\infty))}([0,T])$.
\end{lemma}

\begin{proof}
By Lemma  \ref{lem: uniform compact density}, \ref{teo: product tightness}, and Theorem 3.9.1 in \cite{EK},
 $(\xi^n_t )_{t\geq 0}$ is relatively compact in $\mathcal{D}_{\mathcal{M}(\overline{\mathbb{R}^d} \times[0,\infty))}([0,T])$
 if we can prove tightness on the real-valued sequences
$\{(f(\xi^n_t))_{t \geq 0}: n=1,2,.. \}$.

Applying the Aldous Criterion, it suffices to show that
for fixed sequences of stopping time $\tau_n$ bounded above by $T$,
for each $\varepsilon>0$,
there exists $\delta > 0$ and $n_0$ such that
\begin{equation}
\sup_{n \geq n_0}\sup_{\theta \in [0, \delta]} \mathbb{P}\left[|\langle f, \xi^n_{\tau_n+\theta}\rangle - \langle f, \xi^n_{\tau_n}\rangle | > \varepsilon \right] \leq \varepsilon.
\end{equation}

First we pick $N,M>0$ such that 
 $$\sup_{n \geq M} \mathbb{P}\left\{ \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle > N \right\} < \epsilon /2 .$$
Then, we can partition the event $\{|\langle f, \xi^n_{\tau_n+\theta}\rangle - \langle f, \xi^n_{\tau_n}\rangle | > \varepsilon\}$ into two subsets according to the event 
$ \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle > N$.

By the compact containment condition, 
we know that for any $f \in C^{+}_{c}(\overline{\mathbb{R}^d} \times [0,\infty))$ and $\epsilon > 0$, there exists $N>0$ (dependent on $f$ and $\epsilon$), 
such that 
\begin{equation}
\label{eq: vague compact containment condition}
 \limsup_{n \to \infty} \mathbb{P}\left\{ \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle > N \right\} < \epsilon.
\end{equation}

Therefore, for all $n>M$,
\begin{equation}
\begin{aligned}
 &\mathbb{P}\left[|\langle f, \xi^n_{\tau_n+\theta}\rangle - \langle f, \xi^n_{\tau_n}\rangle | > \varepsilon \right]\\
 =& \mathbb{P}\left[|\langle f, \xi^n_{\tau_n+\theta}\rangle - \langle f, \xi^n_{\tau_n}\rangle | > \varepsilon ,  \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle > N \right]\\
 & + \mathbb{P}\left[|\langle f, \xi^n_{\tau_n+\theta}\rangle - \langle f, \xi^n_{\tau_n}\rangle | > \varepsilon,  \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle \leq N \right]\\
< & \varepsilon/2 + \mathbb{P}\left[|e^{-\langle f, \xi^n_{\tau_n+\theta}\rangle} - e^{-\langle f, \xi^n_{\tau_n}\rangle }| > e^{-N}\varepsilon,  \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle \leq N \right]\\
< & \varepsilon/2 + \mathbb{P}\left[|F_g(\xi^n_{\tau_n+\theta})-F_g(\xi^n_{\tau_n})| > e^{-N}\varepsilon\right].
\end{aligned}
\end{equation}

Finally, by tightness of the processes $\{F_g(\xi^n_t): n = 1,2,...\}$, 
we can pick large enough $n_0 > M$ and $\delta > 0$
such that 
$$\sup_{n \geq n_0}\sup_{\theta \in [0,\delta]}\mathbb{P}\left[|F_g(\xi^n_{\tau_n+\theta})-F_g(\xi^n_{\tau_n})| > e^{-N}\varepsilon\right]< e^{-N}\varepsilon,$$
so
\begin{equation}
\sup_{n \geq n_0}\sup_{\theta \in [0, \delta]} \mathbb{P}\left[|\langle f, \xi^n_{\tau_n+\theta}\rangle - \langle f, \xi^n_{\tau_n}\rangle | > \varepsilon \right] \leq \varepsilon / 2 + e^{-N} \varepsilon < \varepsilon.
\end{equation}

We have proved relative compactness of $\{(\langle f, \xi^n_t \rangle )_{t \geq 0}: n=1,2,.. \}$, and thus tightness of 
 $\{(\xi^n_t )_{t \geq 0}: n=1,2,.. \}.$
\end{proof}

### 2023-02-15 forwards-and-backwards.tex
tightness now with improved corectness

@@
     Write ${\cal C}(\IR^d\times [0,\infty))$ for the point measures on $\IR^d\times [0,\infty)$.
-We say that a ${\cal C}(\IR^d\times [0,\infty))$-valued process $(\xi_t)_{t \ge 0}$
+We say that a ${\cal C}(\IR^d\times [0,\infty))$-valued process $(\lp_t)_{t \ge 0}$
     is a solution to the $(A, \lp_0)$ martingale problem
@@
 
-    Again, tightness follows from a compact containment condition
-    (Lemma~\ref{lem:compact containment lookdown}),
+    Again, tightness follows from a compact containment condition,
     tightness of one-dimensional distributions,
     and an application of \citet{EK} Theorem~3.9.1.
-    Lines of descent can escape to infinite level in finite time,
-    and so we endow $\lpmeasures$ with the vague topology ``in the level coordinate'',
-    i.e., the topology induced by test functions on $\overline{\IR^d} \times [0,\infty)$
+
+    % Lines of descent can escape to infinite level in finite time, and so
+    % we endow $\lpmeasures$ with the vague topology ``in the level coordinate'',
+    \comment{Should this be a separate definition (along the lines of Condition 2.1 in \citet{etheridge/kurtz:2018})?}
+    Let $\{h_k\}$ be a separating class of nonnegative functions in $C^1_b([0, \infty))$
+    such that
+    $\int_0^\infty \int_u^\infty h_k(v) dv du$,
+    $\int_0^\infty u^2 |h_k'(u)| du$,
+    and $\int_0^\infty h_k(u)^2 du$
+    are all finite for all $k$,
+    and assume furthermore that $h_0$ is a positive, nonincreasing function 
+    that bounds all other $h_k$, i.e., for any $k$,
+    there is a $c_k$ such that $h_k(u) \le c_k h_0(u)$ for all $u \ge 0$.
+    (For instance, we may take $h_0(u) = e^{-u}$ and the remaining $h_k$
+    to be a separating class of $C^1$ functions with compact support.)
+    Following \citet{etheridge/kurtz:2018} (see Condition 2.1),
+    we endow $\lpmeasures$ with
+    the topology induced by test functions on $\overline{\IR^d} \times [0,\infty)$
     of the form $g(x) h(u)$, where $g \in C_b(\overline{\IR^d})$ is bounded and continuous
-    and $h \in C_c([0,\infty))$ is continuous with compact support.
+    and $h \in \{h_k\}_{k \ge 0}$.
+    This space is completely metrizable,
+    and a subset $K \subset \lpmeasures$ is relatively compact if and only if
+    $\sup_{\lp \in K} \langle h_k, \lp \rangle < \infty$ for each $k$;
+    therefore, compact containment follows from Lemma~\ref{lem:compact containment lookdown}.
+
     Theorem~3.9.1 of \citet{EK} requires that $\{(F(\lp^N_t))_{t \ge 0}\}_N$
@@
 
-Let $C_c^+$ denote the set of nonnegative continuous functions on $\overline{\IR^d} \times [0, \infty)$
-for which there exists a $u_f \ge 0$ such that $u > u_f$ implies that $f(x, u) = 0$.
-Recall that we are working with the vague topology ``in the level direction'',
-so that $m_n \to m$ in $\lpmeasures$ if and only if $\langle f, m_n \rangle \to \langle f, m \rangle$
-for all $f \in C_c^+$.
-By Theorem~A.23 in \citet{kallenberg1997foundations},
-the space $\lpmeasures$ is separable and metrizable,
-and $K \subset \lpmeasures$ is relatively compact if and only if
-$\sup_{\lp \in K} \langle f, \lp \rangle < \infty$
-for any $f \in C_c^+$.
-% The compact sets we consider are those with bounded total mass of their spatial projection,
-% i.e., of the form
-% $$
-%     K_M = \left\{
-%         \lp \in \lpmeasures \;:\;
-%         \sup_{L \ge 1} \frac{1}{L} \lp\left(\overline{\IR^d} \times [0, L]\right) \le M
-%     \right\} .
-% $$
-% These sets are compact 
-% because if $\lp \in K_M$ and $f \in C_c^+$ then $\langle f, \lp\rangle \le M u_f \|f\|_\infty$.
-Let $\mathcal{H} = \{h_n\}_{n \ge 1}$ be a sequence of
-monotone, nonnegative, compactly supported, differentiable functions
-on $[0, \infty)$ such that there exist sequences $u_n \to \infty$ and $k_n$ such that
-\begin{enumerate}
-    \item $h_n(u) > 1$ for $u \le u_n/2$,
-    \item $h_n(u) = 0$ for $u \ge u_n$,
-    \item $- h_n(u) \le h_n'(u) \le 0$, and
-    \item $\max\left( \int_u^\infty h_n(v) dv, \int_u^\infty h_n(v)^2 dv \right) \le k_n h_n(u)$.
-\end{enumerate}
-For instance, we could take $h_n(u)$ to be a mollified version of $\min(1, e^{-(u-n)})$,
-and then $u_n = k_n = n$.
-\comment{(or we could just take those functions? they are differentiable almost everywhere.)}
-The compact sets we consider are those with uniformly bounded integrals against $\mathcal{H}$,
-i.e., of the form
-$$
-    K_C = \left\{
-        \lp \in \lpmeasures \;:\;
-        \langle h_n, \lp \rangle \le C_n
-        \text{ for all } n \ge 1
-    \right\} ,
-$$
-for some sequence of constants $(C_1, C_2, \ldots)$.
-This set is compact because any $f \in C_c^+$ is bounded by a constant multiple of some $h_n$.
-
 \begin{lemma}[Compact containment for $\lp$]
@@
     if $\theta/N \to \alpha$ and $\lp_0^N \to \lp_0$ weakly as $N \to \infty$
-    \comment{and they are conditionally Poisson},
+    \comment{and they are conditionally Uniform with the limit conditionally Poisson},
     for any $T$ and $\delta > 0$ there exists a sequence
@@
     \IP\left\{
-        \sup_{0 \le t \le T} \langle h_n, \lp^N_t \rangle > C_n
-        \text{ for some } n \ge 1
+        \sup_{0 \le t \le T} \langle h_k, \lp^N_t \rangle > C_n
+        \text{ for some } k \ge 1
     \right\}
@@
 
-In other words, the processes $\lp^N$ stay in $K_C$ for all $0 \le t \le T$
+In other words, the processes $\lp^N$ stay in 
+the compact set
+$$
+    \left\{
+        \lp \in \lpmeasures \;:\;
+        \langle h_k, \lp \rangle \le C_k
+        \text{ for all } k \ge 1
+    \right\} ,
+$$
+for all $0 \le t \le T$
 with uniformly high probability.
@@
     Under the assumptions of Lemma~\ref{lem:compact containment lookdown},
-    for any $T$, $M$ and $n$ there exists a constant $K_n$ such that
+    for any $T$ and $k$ there exists a constant $K_k$ such that
     $$ 
-    \limsup_{N \to \infty} \IP\left\{ \sup_{0 \le t \le T} \langle h_n, \lp^N_t \rangle > M \right\}
+    \limsup_{N \to \infty} \IP\left\{ \sup_{0 \le t \le T} \langle h_k, \lp^N_t \rangle > M \right\}
     <
-    \frac{K_n}{M} .
+    \frac{K_k}{M} .
     $$
@@
     \IP\left\{
-        \sup_{0 \le t \le T} \langle h_n, \lp^N_t \rangle > C_n
-        \text{ for some } n \ge 1
+        \sup_{0 \le t \le T} \langle h_k, \lp^N_t \rangle > C_k
+        \text{ for some } k \ge 1
     \right\}
     \le
-    \sum_{n \ge 1}
+    \sum_{k \ge 1}
     \IP\left\{
-        \sup_{0 \le t \le T} \langle h_n, \lp^N_t \rangle > C_n
+        \sup_{0 \le t \le T} \langle h_k, \lp^N_t \rangle > C_k
     \right\} ,
@@
     so \eqref{eqn:compact eqn lookdown} follows
-    by taking $C_n = 2^{n-1} K_n / \delta$ and using Lemma~\ref{lem:compact containment hn}.
+    by taking $C_k = 2^{k-1} K_k / \delta$ and using Lemma~\ref{lem:compact containment hn}.
 \end{proof}
@@
 \begin{proof}[of Lemma~\ref{lem:compact containment hn}]
-    \comment{TODO: just give bounds and say this follows
-        the proof of Lemma~\ref{lem:eta_compact_containment} exactly, otherwise.
-        Or make the basic idea a lemma in the appendix?}
-    Let $h_n \in \mathcal{H}$.
-    It is evident from the description of the process
-    (or, by differentiating in Definition~\ref{defn:lookdown_mgale})
-    that
-    Applied to $f(x, u) = h_n(u)$, the martinagle representation~\eqref{eqn:f_xi_mgale} is
+    \comment{TODO: shorten and make constants have reasonable notation}
+    First note that since $h_k(u) \le c_k h_0(u)$ for all $u$,
+    so $\langle h_k, \lp_t^N \rangle \le c_k \langle h_0, \lp_t^N \rangle$,
+    and so we need only prove the Lemma for $h_0$.
+    Henceforth, let $h = h_0$.
+    Applied to $f(x, u) = h(u)$, the martinagle representation~\eqref{eqn:f_xi_mgale} is
     \begin{align*}
     \begin{split}
-        \langle h_n, \lp_t^N \rangle
+        \langle h, \lp_t^N \rangle
         &=
-        \langle h_n, \lp_0^N \rangle
-        + M^{h_n}_t 
-        \\ & \qquad \qquad {}
+        \langle h, \lp_0^N \rangle
+        + M^{h}_t 
+        \\ & \qquad {}
         +
@@
         \big\langle
-            2 a^N(x, \eta^N_s) \int_u^N h_n(u_1) du_1
+            2 c^N(x, \eta^N_s) \int_u^N h(v) dv
         ,
@@
             \left(
-                a^N(x, \eta^N_s) u^2
+                c^N(x, \eta^N_s) u^2
                 - b^N(x, \eta^N_s) u
             \right)
-            h_n'(u)
+            h'(u)
         ,
@@
     \end{align*}
-    where $M^{h_n}_t$ is a martingale
+    where $M^{h}_t$ is a martingale
     with quadratic variation
     \begin{align*}
-        [M^{h_n}]_t
+        [M^{h}]_t
         &=
         \int_0^t
-        \langle 2 a^N(x, \eta_s^N) \int_u^N h_n(u_1)^2 du_1
+        \langle 2 c^N(x, \eta_s^N) \int_u^N h(v)^2 dv
         ,
@@
     \end{align*}
-    Now, note that $0 \le a^N(x, \eta_x^N) \le C_a$ for some $C_a < \infty$,
-    and we have assumed that $\int_u^\infty h_n(u_1) du_1 \le k_n h_n(u)$,
-    so that 
-    \begin{align*}
-        & \int_0^t
+    Now, note that $0 \le c^N(x, \eta_x^N) \le C_a < \infty$
+    and $b^N(x, \eta_s^N) \le C_b < \infty$,
+    and we have assumed that $h'(u) \le 0$ (since $h_0$ is nonincreasing),
+    so we may bound
+    \begin{align} \label{eqn:hn_bound},
+    \begin{split} 
+        \langle h, \lp_t^N \rangle
+        &\le
+        \langle h, \lp_0^N \rangle
+        + M^{h}_t
+        \\ & \qquad {}
+        +
+        \int_0^t
         \big\langle
-            2 a^N(x, \eta^N_s) \int_u^N h_n(u_1) du_1
+            2 C_a \int_u^\infty h(v) dv
+            + \left( C_a u^2 + C_b u \right) |h'(u)|
         ,
         \lp_s^N(dx, du) \big \rangle
-        ds
-        \\ & \qquad
-        \le
-        2 C_a k_n \int_0^t \big\langle h_n(u), \lp_s^N(dx, du) \big \rangle .
-    \end{align*}
-    In the next line, the contribution from $a^N(x, \eta^N_s) u^2 h'(u)$ is nonpositive because
-    $a^N \ge 0$ and $h'(u) \le 0$.
-    Similarly, since $b^N(x, \eta_x^N) \le C_b$ for some $C_b < \infty$,
-    and by assumption
-    $- h_n'(u) \le k_n h_n(u)$ and $h_n'(u) = 0$ for $u \ge u_n$,
-    and so
-    \begin{align*}
-        & \int_0^t
+        ds .
+    \end{split}
+    \end{align}
+    Now, since $\lp_t^N$ is conditionally uniform given $\eta_t^N$,
+    we know that for appropriate $f$,
+    $  \IE[\langle f, \lp^N_t \rangle] = \IE[\langle \widetilde{f}, \eta^N_t \rangle] , $
+    where $\widetilde{f}(x) = \int_0^\infty f(x, u) du$.
+    By our assumptions on $h=h_0$,
+    we know that
+    $$
+        \int_0^\infty \left( 2 C_a \int_u^\infty h(v) dv
+        + \left( C_a u^2 + C_b u \right) |h'(u)| \right) du
+        < C
+    $$
+    for some $C < \infty$, and so
+    \begin{align*}
+    \begin{split}
+        \IE\left[ \langle h, \lp_t^N \rangle \right]
+        &\le
+        \IE\left[ \langle h, \lp_0^N \rangle \right]
+        +
+        C
+        \int_0^t
+        \IE\bigg[
             \big\langle
-            \left(
-                a^N(x, \eta^N_s) u^2
-                - b^N(x, \eta^N_s) u
-            \right)
-            h_n'(u)
+            1
+            ,
+            \eta_s^N(dx, du) \big \rangle
+        \bigg]
+        ds ,
+    \end{split}
+    \end{align*}
+    which we know by Lemma~\ref{lem:eta_f_bound}
+    is bounded by $C_0 e^{C_1 t}$ for some other constants $C_0$ and $C_1$.
+
+    Now consider the maximum. By \eqref{eqn:hn_bound},
+    \begin{align*}
+        \sup_{0 \le t \le T} \langle h, \lp_t^N \rangle
+        &\le
+        \langle h, \lp_0^N \rangle
+        + \sup_{0 \le t \le T} M^{h}_t 
+        \\ & \qquad {}
+        + \int_0^T 
+        \big \langle
+            2 C_a \int_u^\infty h(v) dv
+            + \left( C_a u^2 + C_b u \right) |h'(u)|
         ,
         \lp_s^N(dx, du) \big \rangle
-        ds
-        \le
-        C_b u_n k_n \int_0^t \big\langle h_n(u), \lp_s^N(dx, du) \big \rangle .
-    \end{align*}
-    Putting this together, we have that
-    \begin{align} \label{eqn:hn_bound}
-        \langle h_n, \lp_t^N \rangle
-        &\le
-        \langle h_n, \lp_0^N \rangle
-        + M^{h_n}_t 
-        + (2 C_a + C_b u_n) k_n \int_0^t 
-            \langle h_n, \lp_s^N \rangle
-        ds .
-    \end{align}
-    By Gronwall's inequality, with $C = (2 C_a + C_b u_n) k_n$
-    \begin{align*}
-        \IE\left[ \langle h_n, \lp_t^N \rangle \right]
-        &\le
-        \IE\left[ \langle h_n, \lp_0^N \rangle \right] e^{Ct} .
-    \end{align*}
-
-    Now consider the maximum. By \eqref{eqn:hn_bound},
-    \begin{align*}
-        \sup_{0 \le t \le T} \langle h_n, \lp_t^N \rangle
-        &\le
-        \langle h_n, \lp_0^N \rangle
-        + \sup_{0 \le t \le T} M^{h_n}_t 
-        + C \int_0^t 
-            \sup_{0 \le t \le T} \langle h_n, \lp_s^N \rangle
-        ds .
-    \end{align*}
+        ds ,
+    \end{align*}
+    where there is no supremum before the integral because the integrand is nonnegative.
+
     Again since $\sqrt{x} \le 1 + x$ for $x \ge 0$,
@@
     \begin{align*}
-    \IE\left[ \sup_{0 \le t \le T} M^{h_n}_t \right]
+    \IE\left[ \sup_{0 \le t \le T} M^{h}_t \right]
     & \le
-        C'\left( 1 + \IE\left[ [M^{h_n}]_t \right] \right)
+        C'\left( 1 + \IE\left[ [M^{h}]_T \right] \right)
     \\ & \le
-        C' \left( 1 + \int_0^t \IE\left[
-        \langle 2 a^N(x, \eta_s^N) \int_u^N h_n(u_1)^2 du_1
+        C' \left( 1 + \int_0^T \IE\left[
+        \langle 2 c^N(x, \eta_s^N) \int_u^\infty h(v)^2 dv
         ,
@@
         \right] ds \right) 
-    \\ & \le
-        C' \left( 1 + 2 C_a k_n \int_0^t \IE\left[
-        \langle h_n, \lp_s^N \big \rangle
+    \\ & =
+        C' \left( 1 + 2 C_a \int_0^\infty h(v)^2 dv
+        \int_0^T \IE\left[
+            \langle 1 , \lp_s^N(dx, du) \big \rangle
         \right] ds \right)  
     \\ & \le
-        C' \left( 1 + C'' e^{Ct} \IE[ \langle h_n, \lp_t^N \rangle ] \right) ,
-    \end{align*}
-    where $C'' = 2 C_a k_n / C$.
+        C'' e^{C_1 T} ,
+    \end{align*}
+    for a constant $C''$ which is finite
+    by our assumption that $\int_0^\infty h_0(v)^2 dv < \infty$.
+
     Therefore, 
     \begin{align*}
-        \IE\left[ \sup_{0 \le t \le T} \langle h_n, \lp_t^N \rangle \right]
+        \IE\left[ \sup_{0 \le t \le T} \langle h, \lp_t^N \rangle \right]
         &\le
-        C' + \IE\left[ \langle h_n, \lp_0^N \rangle \right]( 1 + C'' e^{Ct} )
-        + C \int_0^t 
-            \IE\left[ \sup_{0 \le t \le T} \langle h_n, \lp_s^N \rangle \right]
-        ds ,
-    \end{align*}
-    and so once again by Gronwall's inequality, there is a $C'''$ such that
-    \begin{align*}
-        \IE\left[ \sup_{0 \le t \le T} \langle h_n, \lp_t^N \rangle \right]
-        &\le
-        C'''(1 + \IE[\langle h_n, \lp_0^N \rangle]) e^{2Ct} ,
+        \IE\left[ \langle h, \lp_0^N \rangle \right]
+        + (C'' + C_0 / C_1) e^{C_1 T},
     \end{align*}
@@
         \frac{
-            C'''(1 + \IE[\langle h_n, \lp_0^N \rangle]) e^{2CT} 
+            \IE\left[ \langle h, \lp_0^N \rangle \right]
+            + (C'' + C_0 / C_1) e^{C_1 T}
         }{ K } .
@@
     Lemma~\ref{lem:eta_projections_tightness},
-    except that terms are bounded by constant multiples of $\langle h_n, \xi^N_s \rangle$
-    instead of $\langle 1, \eta^N_s \rangle$,
-    where $h_n$ is bounded below on $[0, u_*]$.
-    \comment{(or we could say that $u_n \ge 2 u_*$)}
+    except that terms are bounded by constant multiples of $\langle h_0, \xi^N_s \rangle$
+    instead of $\langle 1, \eta^N_s \rangle$.
     There is only one term that might use explanation,
@@
     \end{align*}
-    but this is now clearly bounded by a constant multiple of $h_n(u)$.
+    but this is now bounded as in the proof of Lemma~\ref{lem:eta_f_bound}.
 \end{proof}

### 2023-02-16 forwards-and-backwards.tex
mmt first draft

@@
 
-\comment{We talked about having the next paragraph be a Proposition or something?
-I am putting off rewriting this paragraph until I know what has been proved.}
+Elsewhere we have written $\eta^N$ for the spatial projection of the lookdown process $\lp^N$,
+although $\eta^N$ was defined first as a solution to a martingale problem.
+For the purposes of this result --
+the application of the Markov Mapping Theorem \citep[Thm A.2 in][]{etheridge/kurtz:2018} --
+we must disambiguate these, and so define the spatial projection
+maps $\gamma^N: \mathcal{M}(\IR^d \times [0, N]) \to \mathcal{M}(\IR^d)$
+by $\gamma^N(\xi^N)(\cdot) = \xi^N(\cdot \times [0, N]) / N$,
+and $\gamma: \mathcal{M}(\IR^d \times [0, \infty)) \to \mathcal{M}(\IR^d)$
+by $\gamma(\xi)(\cdot) = \lim_{u_0 \to \infty} \xi(\cdot \times [0, u_0]) / u_0$.
+We will also need an inverse notion:
+for a measure $\lp^N$ on $\IR^d \times [0, N]$ and a sigma-field $\mathcal{F}$,
+we say that \emph{$\lp$ is conditionally uniform given $\mathcal{F}$}
+if for all compactly supported $f$,
+\begin{align} \label{eqn:conditionally_uniform}
+    \IE[ e^{-\langle f, \lp \rangle} \;|\; \mathcal{F} ]
+    &=
+    e^{-\langle F_f^N, \gamma(\lp) \rangle} ,
+\end{align}
+where
+$$ F_f^N(x) = - N \log \frac{1}{N} \int_0^N e^{-f(x, u)} du . $$
+(In other words, the $[0, N]$ components of $\lp$
+are independent, uniformly distributed on $[0, N]$, and independent of $\gamma(\lp)$.)
+Similarly, for a measure $\lp$ on $\IR^d \times [0, \infty)$
+we say that \emph{$\lp$ is a conditionally Poisson random measure given $\mathcal{F}$}
+if for all compactly supported $f$,
+\begin{align} \label{eqn:conditionally_poisson}
+    \IE[ e^{-\langle f, \lp \rangle} \;|\; \mathcal{F} ]
+    &=
+    e^{-\langle \int_0^\infty (1 - e^{-f(x, u)}) du, \gamma(\lp)(dx) \rangle} .
+\end{align}
+(In other words, $\lp$ is conditionally Poisson with Cox measure $\gamma(\lp) \times \Lambda$.)
+
+\begin{proposition}
+    \label{thm:mmt_application}
+    Let $\mu_0$ be a probability distribution on $\measures$,
+    and $\nu_0^N$ a probability distribution on $\mathcal{M}(\IR^d \times [0, N])$
+    such that a draw $\lp^N_0$ from $\nu_0^N$ is conditionally uniform given $\gamma(\lp^N_0)$
+    in the sense of \eqref{eqn:conditionally_uniform}.
+    If $\tilde \eta^N$ is a solution
+    of the martingale problem of Definition~\ref{defn:mgale_construction}
+    with initial distribution $\mu_0$
+    then there exists a solution $\lp^N$
+    of the martingale problem of Definition~\ref{defn:lookdown_mgale}
+    with initial distribution $\nu_0^N$
+    such that $\eta^N = \gamma \cdot \lp^N$
+    has the same distribution on $D_{\measures}[0, \infty)$
+    as $\tilde \eta^N$.
+    Furthermore, $\lp^N$ is conditionally uniform given given $\mathcal{F}^{\eta}_t$
+    in the sense of \eqref{eqn:conditionally_uniform}.
+
+    \comment{Theorem~\label{thm:nonlocal_convergence}
+        isn't written as ``the $(A, \mu)$ martingale problem is'';
+        rephrase here or there?}
+
+    Similarly,
+    let $\mu_0$ be a probability distribution on $\measures$,
+    and $\nu_0$ a probability distribution on $\mathcal{M}(\IR^d \times [0, \infty))$
+    such that a draw $\lp_0$ from $\nu_0$ is conditionally Poisson given $\gamma(\lp_0)$
+    in the sense of \eqref{eqn:conditionally_poisson}.
+    If $\tilde \eta$ is a solution
+    of the limiting martingale problem of Theorem~\label{thm:nonlocal_convergence}
+    with initial distribution $\mu_0$
+    then there exists a solution $\lp$
+    of the martingale problem of of Definition~\ref{defn:limiting_lookdown_mgale}
+    with initial distribution $\nu_0$
+    such that $\eta = \gamma \cdot \lp$
+    has the same distribution on $D_{\measures}[0, \infty)$
+    as $\tilde \eta$.
+    Furthermore, $\lp_t$ is conditionally Poisson given $\mathcal{F}^{\eta}_t$
+    in the sense of \eqref{eqn:conditionally_poisson}.
+\end{proposition}
+
+\begin{proof}[of Proposition~\ref{thm:mmt_application}]
+    This is the content of the Markov Mapping Theorem applied to our situation,
+    \citet[Thm A.2 in][]{etheridge/kurtz:2018}.
+    In the notation of that theorem, $\gamma$ is as above,
+    $\alpha$ is the transition function that assigns levels uniformly on $[0, N]$ (in the first case)
+    or as a Poisson process with Lesbegue intensity (in the limiting case),
+    and we need a continuous $\psi^N(\lp)$ such that $|A^N f(\lp)| \le c_f \psi^N(\lp)$
+    for all $f \in \mathcal{D}(A^N)$ (and similarly a function $\psi$ for $A$).
+    We also need that applying the lookdown generator to a function and averaging over levels
+    is equivalent to applying the population process generator to the function
+    whose dependence on levels has been averaged out,
+    which we precisely state, and verify, in Appendix~\ref{sec: Markov Mapping Theorem Application}.
+
+    For finite $N$,
+    taking $f(\lp)$ of the form \eqref{eqn:test_functions},
+    we can use $\psi^N(\lp) = \langle C + u |F(x, \eta)|, \lp(dx, du) \rangle$
+    for an appropriate constant $C$.
+    For the scaling limit, recall that the test functions $f$ are of the form
+    $f(\lp) = \prod_{(x, u) \in \lp} g(x, u)$
+    with $g(x, u) = 1$ for $u \ge u_0$,
+    and so taking for example the mostly troublesome term in $Af(\lp)$,
+    we see that since $0 \le f(\lp) / g(x, u) \le 1$ for any $(x, u) \in \lp$,
+    \begin{align*}
+        \big| f(\lp) \sum_{(x, u) \in \lp} F(x, \eta) u \frac{\partial_u g(x, u)}{g(x, u)} \big|
+        & \le
+        \| \partial_u g \|_\infty \sum_{(x, u) \in lp} | F(x, \eta) u \ind_{u \le u_0} | \\
+        & \le
+        \| \partial_u g \|_\infty e^{u_0} \sum_{(x, u) \in lp} | F(x, \eta) u e^{-u} | .
+    \end{align*}
+    The second line would be just what we want,
+    except that $\psi(\lp)$ cannot depend on $f$, and hence neither on $u_0$.
+    So, the third line provides us with the required bound,
+    absorbing $\| \partial_u g \|_\infty e^{u_0}$ into $c_f$
+    and $\langle |F(x, \eta u e^{-u}|, \lp \rangle$ into $\psi(\lp)$.
+    To do this we must restrict $\lp$ to lie in the space of measures
+    for which this is finite.
+\end{proof}
 
@@
     but that is a consequence of this theorem.)
-
     Again, tightness follows from a compact containment condition,
@@
 
-    % Lines of descent can escape to infinite level in finite time, and so
-    % we endow $\lpmeasures$ with the vague topology ``in the level coordinate'',
-    \comment{Should this be a separate definition (along the lines of Condition 2.1 in \citet{etheridge/kurtz:2018})?}
-    Let $\{h_k\}$ be a separating class of nonnegative functions in $C^1_b([0, \infty))$
-    such that
-    $\int_0^\infty \int_u^\infty h_k(v) dv du$,
-    $\int_0^\infty u^2 |h_k'(u)| du$,
-    and $\int_0^\infty h_k(u)^2 du$
-    are all finite for all $k$,
-    and assume furthermore that $h_0$ is a positive, nonincreasing function 
-    that bounds all other $h_k$, i.e., for any $k$,
-    there is a $c_k$ such that $h_k(u) \le c_k h_0(u)$ for all $u \ge 0$.
-    (For instance, we may take $h_0(u) = e^{-u}$ and the remaining $h_k$
-    to be a separating class of $C^1$ functions with compact support.)
-    Following \citet{etheridge/kurtz:2018} (see Condition 2.1),
-    we endow $\lpmeasures$ with
-    the topology induced by test functions on $\overline{\IR^d} \times [0,\infty)$
+    Lines of descent can escape to infinite level in finite time, and so
+    we endow $\lpmeasures$ with the vague topology ``in the level coordinate'',
+    induced by test functions on $\overline{\IR^d} \times [0,\infty)$
     of the form $g(x) h(u)$, where $g \in C_b(\overline{\IR^d})$ is bounded and continuous
-    and $h \in \{h_k\}_{k \ge 0}$.
+    and $h \in C_c([0, \infty))$.
     This space is completely metrizable,
-    and a subset $K \subset \lpmeasures$ is relatively compact if and only if
-    $\sup_{\lp \in K} \langle h_k, \lp \rangle < \infty$ for each $k$;
+    and we may choose a countable set of nonnegative, compactly supported $f_k$
+    such that a subset $K \subset \lpmeasures$ is relatively compact if and only if
+    $\sup_{\lp \in K} \langle f_k, \lp \rangle < \infty$ for each $k$;
     therefore, compact containment follows from Lemma~\ref{lem:compact containment lookdown}.
@@
 
+What we need for compact containment will come from the following Lemma.
+The generality is unimportant --
+for concreteness one may take $h(u) = e^{-u}$.
+
+\begin{lemma}
+        \label{lem:h_containment}
+    Let $h$ be a positive, continuous, nondecreasing, differentiable function on $[0, \infty)$
+    such that
+    $\int_0^\infty \int_u^\infty h(v) dv du$,
+    $\int_0^\infty u^2 |h'(u)| du$,
+    and $\int_0^\infty h(u)^2 du$
+    are all finite,
+    Then under the assumptions of Lemma~\ref{lem:compact containment lookdown},
+    for any $T$ there exists a constant $K$ such that for all $M > 0$,
+    $$ 
+    \limsup_{N \to \infty} \IP\left\{ \sup_{0 \le t \le T} \langle h, \lp^N_t \rangle > M \right\}
+    <
+    \frac{K}{M} .
+    $$
+\end{lemma}
+
+We postpone the proof of this Lemma to show how it gets us to compact containment.
+First, we show that this implies compact containment for arbitrary
+compactly supported functions.
+
+\begin{lemma}
+    \label{lem:compact containment hn}
+    Under the assumptions of Lemma~\ref{lem:compact containment lookdown},
+    for any $T$ and $k$ there exists a constant $K_k$ such that for all $M > 0$,
+    $$ 
+    \limsup_{N \to \infty} \IP\left\{ \sup_{0 \le t \le T} \langle h_k, \lp^N_t \rangle > M \right\}
+    <
+    \frac{K_k}{M} .
+    $$
+\end{lemma}
+
+\begin{proof}[of Lemma~\ref{lem:compact containment hn}]
+    Let $h$ be as in Lemma~\ref{lem:h_containment}.
+    For any $f \in C(\bar \IR^d \times [0, \infty))$ with compact support,
+    there is a $c_f < \infty$ such that $f(x, u) \le c_f h(u)$.
+    Therefore, $\langle f, \xi \rangle \le \langle h, \xi \rangle$,
+    and so by Lemma~\ref{lem:h_containment},
+    \begin{align*}
+        \limsup_{N \to \infty} \IP\left\{ \sup_{0 \le t \le T} \langle f, \lp^N_t \rangle > M \right\}
+        \le
+        \limsup_{N \to \infty} \IP\left\{ \sup_{0 \le t \le T} \langle h, \lp^N_t \rangle > M/c_f \right\}
+        <
+        \frac{K c_f}{M} .
+    \end{align*}
+\end{proof}
+
 \begin{lemma}[Compact containment for $\lp$]
@@
 with uniformly high probability.
-We will prove this Lemma using the following one:
-
-\begin{lemma}
-    \label{lem:compact containment hn}
-    Under the assumptions of Lemma~\ref{lem:compact containment lookdown},
-    for any $T$ and $k$ there exists a constant $K_k$ such that
-    $$ 
-    \limsup_{N \to \infty} \IP\left\{ \sup_{0 \le t \le T} \langle h_k, \lp^N_t \rangle > M \right\}
-    <
-    \frac{K_k}{M} .
-    $$
-\end{lemma}
+\comment{
+    Note that we could instead of the vague topology on locally finite measures,
+    take the space of measures with $\langle h, \xi \rangle < \infty$
+    for which $\xi_n \to \xi$ if $\langle f, \xi \rangle < \infty$ for all $f$ for which $f \le c_f h$,
+    which is completely metrizable
+    as in Condition 2.1 of \citet{etheridge/kurtz:2019}.
+}
 
@@
 
+Finally, we prove the key lemma.
+
 \begin{proof}[of Lemma~\ref{lem:compact containment hn}]
-    \comment{TODO: shorten and make constants have reasonable notation}
-    First note that since $h_k(u) \le c_k h_0(u)$ for all $u$,
-    so $\langle h_k, \lp_t^N \rangle \le c_k \langle h_0, \lp_t^N \rangle$,
-    and so we need only prove the Lemma for $h_0$.
-    Henceforth, let $h = h_0$.
+    \comment{(TODO: shorten and make constants have reasonable notation)}
     Applied to $f(x, u) = h(u)$, the martinagle representation~\eqref{eqn:f_xi_mgale} is
@@
     and $b^N(x, \eta_s^N) \le C_b < \infty$,
-    and we have assumed that $h'(u) \le 0$ (since $h_0$ is nonincreasing),
+    and we have assumed that $h'(u) \le 0$ (since $h$ is nonincreasing),
     so we may bound
@@
     where $\widetilde{f}(x) = \int_0^\infty f(x, u) du$.
-    By our assumptions on $h=h_0$,
+    By our assumptions on $h$,
     we know that
@@
     for a constant $C''$ which is finite
-    by our assumption that $\int_0^\infty h_0(v)^2 dv < \infty$.
+    by our assumption that $\int_0^\infty h(v)^2 dv < \infty$.
 
@@
     Lemma~\ref{lem:eta_projections_tightness},
-    except that terms are bounded by constant multiples of $\langle h_0, \xi^N_s \rangle$
+    except that terms are bounded by constant multiples of $\langle h, \xi^N_s \rangle$
     instead of $\langle 1, \eta^N_s \rangle$.
@@
 \end{proof}
-
-\subsection{Generator of Lookdown Representations}
-
-We now define the generator of the lookdown representations.
-\begin{definition}[Martingale Problem Characterisation]
-    \label{defn:lookdown_mgale}
-For given positive values of $N$ and $\theta$
-and $\lp_0 \in \mathcal{M}_F(\IR^d \times [0,N])$,
-we define $(\lp^{N}_t)_{t \geq 0}$
-to be the unique solution to the martingale problem
-with initial condition $\lp_0$ and generator $A^{N}$ that satisfies
-\begin{equation*}
-\begin{split}
-& A^{N}f(\lp ) \\
-&\quad =
-    f(\lp)
-    \,\sum_{(x,u)\in \lp}\,
-    2 \gamma(x, \eta)
-    \Bigg\{ \frac{1}{2N} \int_u^N g(x,u_1) du_1
-            \frac{
-                \theta \int_{\IR^d}
-                (g(y,u) - g(x,u))
-                r(y, \eta) q_{\theta}(x,dy)
-            }{ g(x,u) }
-        \\
-    &\qquad\qquad\qquad\qquad\qquad\qquad\qquad {} +
-        \frac{\theta}{N} \int_u^N
-        \int_{\IR^d}\left(
-            \frac{ g(y,u_1) + g(x,u_1) }{ 2 } - 1
-        \right)
-        r(y, \eta) q_{\theta}(x,dy)
-        du_1
-    \Bigg\}\\
-    &\qquad\qquad {} +
-    f(\lp) \sum_{(x,u)\in\lp}\,
-    \left(
-        \frac{\theta}{N} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q_\theta(x, dy) u^2 -b_{\theta}(x,\eta)u
-    \right)
-    \frac{\partial_u g(x,u)}{g(x,u)}
-    ,
-\end{split}
-\end{equation*}
-for all smooth functions $g \in C^{2}_{0}(\IR^d)$,
-where $f(\lp) = \prod_{(x, u) \in \lp} g(x, u)$ as defined in \eqref{eqn:test_functions},
-and $\eta(\cdot) = \lp(\cdot \times [0, N]) / N$ is the scaled spatial pushforward of $\lp$,
-as before.
-\end{definition}
-
-Similarly, 
-we define the generator for the lookdown representation of the limiting spatial model.
-
-\begin{definition}[Martingale Problem Characterisation, $N=\infty$]
-    \label{defn:limiting_lookdown_mgale}
-    For a given value of $\alpha \in [0, \infty)$,
-    define the operator $A$ acting on test functions of the form
-    $f(\xi) = \prod_{(x, u) \in \xi} g(x, u)$ with $g \in C_0^2(\IR^d \times [0, \infty))$
-    and for which there exists a $u_0$ with $g(x, u) = 1$ for all $u > u_0$.
-    Then, let $A f$ be
-    \begin{equation}
-    \begin{aligned} \label{eqn:limiting_lookdown_generator}
-    A f(\lp)
-    =&
-        f(\lp)  \sum_{(x, u) \in \xi}
-        \gamma(x, \eta)
-            \frac{
-                \DG(g(\cdot, u) r(\cdot, \eta))(x) - g(x,u) \DG r(x,\eta)
-            }{
-                g(x, u)
-            }
-    \\ &+
-        f(\lp) \sum_{(x, u) \in \xi}
-        2 \alpha \gamma(x,\Xi)r(x,\Xi) \int_u^\infty (g(x, u_1) - 1) du_1
-    \\ &+
-        f(\lp) \sum_{(x, u) \in \xi}
-        \left(
-            \alpha \gamma(x,\Xi)r(x,\Xi) u^2
-            -
-            \left\{
-                \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta)
-            \right\} u
-        \right)
-        \frac{\partial_u g(x, u)}{ g(x,u) }  .
-    \end{aligned}
-    \end{equation}
-
-    We say that a $\lpmeasures$-valued process $(\xi_t)_{t \ge 0}$
-    is a solution to the $(A, \lp_0)$ martingale problem
-    if it has initial distribution $\lp_0$
-    and $f(\lp_t) - \int_0^t Af(\lp_s) ds$ is a martingale for all $f$
-    as defined above.
-\end{definition}
 

### 2023-02-17 forwards-and-backwards.tex
.

@@
     we see that since $0 \le f(\lp) / g(x, u) \le 1$ for any $(x, u) \in \lp$,
-    \begin{align*}
+    \begin{align} \label{eqn:part_of_psi}
         \big| f(\lp) \sum_{(x, u) \in \lp} F(x, \eta) u \frac{\partial_u g(x, u)}{g(x, u)} \big|
         & \le
-        \| \partial_u g \|_\infty \sum_{(x, u) \in lp} | F(x, \eta) u \ind_{u \le u_0} | \\
+        \| \partial_u g \|_\infty \sum_{(x, u) \in \lp} | F(x, \eta) u \ind_{u \le u_0} | \\
         & \le
-        \| \partial_u g \|_\infty e^{u_0} \sum_{(x, u) \in lp} | F(x, \eta) u e^{-u} | .
-    \end{align*}
+        \| \partial_u g \|_\infty e^{u_0} \sum_{(x, u) \in \lp} | F(x, \eta) u e^{-u} | .
+    \end{align}
     The second line would be just what we want,
@@
     absorbing $\| \partial_u g \|_\infty e^{u_0}$ into $c_f$
-    and $\langle |F(x, \eta u e^{-u}|, \lp \rangle$ into $\psi(\lp)$.
+    and $\langle |F(x, \eta) u e^{-u}|, \lp \rangle$ into $\psi(\lp)$.
+    Furthermore, since $F(x, \eta)$ only depends on spatial location, not level,
+    for a given $\lp$ (and hence $\eta = \gamma(\lp)$),
+    $\sup_x |F(x, \eta)|$ is finite.
+    Therefore, we may bound \eqref{eqn:part_of_psi} by
+    $\sup_x |F(x, \eta)| \langle u e^{-u}, \lp \rangle$.
     To do this we must restrict $\lp$ to lie in the space of measures
-    for which this is finite.
+    for which this is finite;
+    however, this is a completely metrizable space
+    \citep[see Condition 2.1 in][]{etheridge/kurtz:2018},
+    and our processes fall in this space (by conditional uniformity).
 \end{proof}
@@
             ,
-            \eta_s^N(dx, du) \big \rangle
+            \eta_s^N \big \rangle
         \bigg]
@@
     instead of $\langle 1, \eta^N_s \rangle$.
+    \comment{Give an example of this.}
     There is only one term that might use explanation,

### 2023-02-17 forwards-and-backwards.tex
alison edits 2/15/23

@@
 \newcommand{\measures}{\mathcal{M}_F(\IR^d)} % finite measures on Rd
-\newcommand{\cmeasures}{\mathcal{M}_F(\overline{\IR^d})} % finite measures on compactified Rd
+\newcommand{\cmeasures}{\mathcal{M}_F(\overline{\IR}^d)} % finite measures on compactified Rd
 \newcommand{\lpmeasures}{\mathcal{M}(\overline{\IR^d} \times [0,\infty))} % locally finite measures on space x level
@@
 one-step convergence in cases for which the limit is a classical 
-reaction diffusion equation of the form~(\ref{semilinear PDE}) with $\DG=\Delta$
+reaction diffusion equation of the form~(\ref{semilinear PDE}) with 
+$\DG=\Delta$,
 and $\rho_F$ is a Gaussian density. We allow a wide class of reaction terms, $F$, so
@@
 relevance to our work here are the papers of~\cite{kurtz/rodrigues:2011} 
-and~\cite{etheridge/kurtz:2018}, in which
+and~\cite{etheridge/kurtz:2019}, in which
 lookdown constructions are provided for a wide variety of population models, including
@@
 we shall take the ``density'', $N$, to infinity,
-and also scale time by a factor of $\theta$,
+and also scale time by a factor of $\theta = \theta(N)$,
 in such a way that defining $\eta^N(t) = X(\theta t) / N$,
@@
 although this restriction could be easily lifted
-\citep[as in Section 3.4 of][]{etheridge/kurtz:2018}.
+\citep[as in Section 3.4 of][]{etheridge/kurtz:2019}.
 Furthermore, individuals do not move during their lifetime,
@@
 and similarly write $r(x, \eta)$ for $r(x, \smooth{r} \eta(x))$
-and $\mu_\theta(x, \eta)$ for the expression of equation \eqref{eqn:mu_defn}.
+and $\mu_\theta(x, \eta)$ for the expression of equation~\eqref{eqn:mu_defn}.
 When convenient, we may also suppress the arguments completely,
@@
 a location $y$ offset from $x$
-by an independent Gaussian with mean $\meanq(x) / \theta$
+by an independent Gaussian random variable with mean $\meanq(x) / \theta$
 and covariance matrix $\covq(x) / \theta$, and once there establishes instantaneously
@@
         q_\theta(x,dz) \right)
-\\ & \qquad \qquad \qquad \qquad {}
-        \times \gamma(x, \eta^N_{s}) \eta^N_{s}(dx)
-%\\ & \qquad \qquad {}
+%\\ & \qquad \qquad \qquad \qquad {}
+         \gamma(x, \eta^N_{s}) \eta^N_{s}(dx)
+\\ & \qquad \qquad \qquad \qquad \qquad {}
     + \int f(x) F(x, \eta^N_{s}) \eta^N_{s}(dx)
@@
 is explained in Section~\ref{sec:heuristics}.
-Note that since individuals are produced at rate $N \gamma \eta$, but each
+Note that since (juvenile) individuals are produced at rate $N \gamma \eta$, but each
 has mass $1/N$,
@@
     \label{def:dispersal_generator}
-    We define the dispersal kernel,
+    As above, we define the dispersal kernel,
     $q_\theta(x, dy)$,
@@
 derivatives in both arguments;
-\item $\gamma(x,m)$ is uniformly bounded above;
+\item $\gamma(x,m)$ is uniformly bounded;
 \item Either
@@
 The purpose of the conditions that we have placed on the reproduction parameters is to 
-ensure that the net per capita reproduction rate is order $1/\theta$. As remarked above, 
+ensure that the net per capita reproduction rate (before time scaling)
+is order $1/\theta$. As remarked above, 
 because of the non-local reproduction mechanism, it no longer suffices to assume that 
@@
 satisfy; they just require some regularity of $r$ as a function of $x$. 
+\comment{Not sure next sentence strictly true - probably assuming a bit
+more - certainly some regularity.}
 Condition~\ref{control through r} is satisfied if 
@@
 On the other hand, it might, for example, seem more natural to take $\rho_r$ to be a Gaussian 
-density with parameter $\sigma_r$, say. Then, as we check in Lemma~\ref{old 6.1}, 
+density with parameter $\sigma_r$, say. Then, 
+as we check in Lemma~\ref{old 6.1}, \comment{this is referring to the
+old Lemma 6.1, now to go in Appendix,}
 Condition~\ref{control through gamma} is satisfied if $\rho_\gamma$ is also
@@
 $\theta$, this condition guarantees that 
-$\epsilon_r+1/\theta <\epsilon_\gamma$, so that the establishment probability of a juvenile
+$\sigma_r+1/\theta <\sigma_\gamma$, so that the establishment probability of a juvenile
 is controlled by individuals that are already `felt' by the fecundity kernel $\rho_\gamma$
@@
 Suppose that Assumptions~\ref{def:model_setup} hold and, 
-further, that $\{\eta_0^N\}_{N\geq 1}$ is tight 
-in $\measures$.
+further, that $\{\eta_0^N\}_{N\geq 1}$ is a sequence of 
+purely atomic measures, with atoms of mass $1/N$, which is
+tight 
+in $\measures$ and such that there exists $\lambda>0$ for 
+which $\langle e^{\lambda\|x\|}, \eta_0^N(dx)\rangle<C<\infty$
+with $C$ independent of $N$.
     Then the sequence of processes
@@
     \end{align}
-    is a martingale,
+    is a martingale (with respect to the natural filtration),
     with quadratic variation
@@
     if the martingale problem
-    defined by equations \eqref{eqn:limiting_mgale_problem} and \eqref{eqn:limiting_mgale_variation}
+    defined by equations~\eqref{eqn:limiting_mgale_problem} 
+and~\eqref{eqn:limiting_mgale_variation}
     has a unique solution,
@@
 Perkins stochastic calculus (and its adaptation to a 
-lookdown setting) provides uniqueness for cases with interactions in the spatial component of
+lookdown setting) provides uniqueness for cases with interactions in the 
+dispersal mechanism of
 the superprocess. We refer 
@@
 
-\citet{KURTZ1999103} provides general conditions under which we
+Specialising the results of 
+\citet{KURTZ1999103} to the deterministic setting
+provides general conditions under which we
 have existence and uniqueness of solutions to~(\ref{eqn:nonlocal_pde}) which
@@
 	deterministic equation can be seen as the empirical measure of a 
-	countable number of particles which, in the notation above, evolve according
+	countable number of particles (all with the same weight)
+which, in the notation above, evolve according
 	to 
@@
 \end{proposition}
-
+The example that we have in mind for the kernel $\rho_gamma$ is a Gaussian
+kernel.
 \begin{remark}
@@
 Propositions~\ref{prop:nonlocal_to_local} and~\ref{nonlocalPME to PME} are by no
-means exhaustive. When our scaling limit is deterministic, one can 
+means exhaustive. When the scaling limit is deterministic, one can 
 expect analogous results under rather general conditions. However, when the limit
@@
 respect to Lebesgue measure, the form of~(\ref{eqn:limiting_mgale_problem})
-suggests that even if one can remove the local averaging from $\gamma$, we
-would need to retain averaging of $r$ in order to obtain a well-defined limit. 
+suggests that even if one can remove the local averaging from $\gamma$, it
+will be necessary
+to retain averaging of $r$ in order to obtain a well-defined limit. 
 \end{remark}
@@
 $r(x,m)\equiv 1\equiv \gamma(r,m)$, $F(x,m)\equiv F(m)$, 
-$\rho^\epsilon_F$ a Gaussian density with parameter $\epsilon^2$,
+$\rho^\epsilon_F$ a symmetric Gaussian density with variance
+parameter $\epsilon^2$,
 and $\DG=\Delta$. 
@@
 \end{equation}
-Then the sequence of stochastic processes $\big(\rho_F^\epsilon*\eta^N_t\big)_{t \ge 0}$
+Then the sequence of 
+${\cal D}([0,\infty), \measures)$-valued
+stochastic processes $\big(\rho_F^\epsilon*\eta^N_t(x)dx\big)_{t \ge 0}$
 converges weakly
@@
 a \emph{lineage} $(L_t^N)_{t \ge 0}$,
-begun at spatial location $L_0 = x$,
+begun at spatial location $L_0^N = x$,
 can be obtained by picking a focal individual uniformly at 
 random from the population at $x$,
+\comment{actually there will be at most one individual at any point $x$}
 and then, for each time $t$,
@@
 for which the levels are below 
-any fixed value converge, Theorem~\ref{}. 
-See~\citet{etheridge/kurtz:2018} for an introduction to these ideas.
+any fixed value converges, Theorem~\ref{}. 
+See~\citet{etheridge/kurtz:2019} for an introduction to these ideas.
 In particular, even in the infinite
@@
 We are interested in two questions.
-When is the motion of an ancestral 
+First, when is the motion of an ancestral 
 lineage, given complete knowledge of the population process,
@@
 
+\comment{Maybe check for more recent references for paragraph below.}
 Equation~(\ref{eqn:nonlocal_pde}) is a nonlocal version of a reaction diffusion equation with nonlinear
@@
 Alert readers will notice that
-the assumption from Assumptions~\ref{def:model_setup} 
+the condition from Assumptions~\ref{def:model_setup} 
 that $\gamma (x,m)$ be uniformly bounded 
@@
 and set $\mu_\theta(x, m) = \max(0, \gamma - F / \theta)$.
+\comment{I don't understand this - something has gone wrong.}
 Birth and death rates are equal at density $m = 1$,
@@
 speed $c$ for all $c \geq 2$, 
-but started from any compact perturbation of a Heaviside function, the 
+but, started from any compact perturbation of a Heaviside function, the 
 solution will converge to the profile $w^F$ with the minimal wavespeed, $c=2$
@@
 Finally, consider equation~(\ref{PME}). Setting $x_0=0$ (for definiteness) and substituting
-the form of $w^P$ from equation \eqref{eqn:pme_wave}
+the form of $w^P$ from equation~\eqref{eqn:pme_wave}
 into Corollary~\ref{cor:wavefront},
@@
 form of nonlinear diffusion, at stationarity
-the lineage will typically be significantly behind the front.
+the lineage will typically be significantly behind the front, 
+suggesting a different genealogy.
 
@@
 Consider a deterministic,
-continuous population generated by parameters $\gamma$, $\mu_\theta$, and $r$
+continuous population generated by parameters $\gamma$, $\mu_\theta$, and $r$,
 with $\meanq = 0$ and $\covq = I$.
@@
 $\epsilon_N(f, G, \eta)$
-will be negligible in our scaling limit.
+will be negligible in our scaling limit (at least if $G'''<\infty$).
 
@@
 In particular,
-if dispersal is simply standard multivariate Gaussian
+if dispersal is determined by a standard multivariate Gaussian
 with mean zero and covariance $\sigma^2 I / \theta$,
@@
 Similarly, the increment in $\langle f, \eta\rangle$ resulting from 
-the death of an individual at $x$ is $f(x)/N$, and so combining with the 
+the death of an individual at $x$ is $-f(x)/N$, and so combining with the 
 above, the second order term in the generator takes the form
@@
 $\theta\epsilon^2\to\infty$. 
-Recall that in this case, we take $\rho_F$ to be a Gaussian density with parameter 
+Recall that in this case, we take $\rho_F^\epsilon$ 
+to be a symmetric Gaussian density with variance 
 $\epsilon^2$. The condition $\theta\epsilon^2\to\infty$ 
@@
 that the regularity gained by smoothing our population density by convolution with
-$p_{\epsilon^2}$ is preserved under the dynamics dictated by $q_{\theta}$.
+$\rho_\epsilon=p_{\epsilon^2}$ is preserved under the dynamics dictated by $q_{\theta}$.
 To understand the first condition, note that we are aiming to obtain a 
@@
 Then, abusing notation to write 
-$q_\theta(x, y)$ for the density of $q_\theta$,
+$q_\theta(x, y)$ for the density of $q_\theta(x,dy)$,
 \begin{align} \label{eqn:lineage_generator_Edt}
@@
     =
-    ds \theta \int \left(f(x) - f(y)\right)
+    ds\, \theta \int \left(f(x) - f(y)\right)
     \frac{
@@
     &
-    \theta \int (f(x) - f(y)) g(x) q_\theta(x, y) dx \\
+    \theta \int \big(f(x) - f(y)\big) g(x) q_\theta(x, y) dx \\
     &\qquad =
-    \theta \int \left\{
+    \theta \int \big\{
         (f(x) g(x) - f(y) g(y)) - f(y) (g(x) - g(y))
-    \right\} q_\theta(x, y) dx \\
+    \big\} q_\theta(x, y) dx \\
     &\qquad \to
@@
 if the $i^\mathrm{th}$ individual's spatial location is $x_i$
-and level is $u_i$, then we will write:
-$$
+and level is $u_i$, then we will write
+\[
     \lp = \sum_i \delta_{x_i, u_i} ,
-$$
+\]
 which is a measure on $\IR^d \times [0, N]$.
@@
 For more explanation of the set-up and how this is possible,
-see \citet{kurtz/rodrigues:2011} and \citet{etheridge/kurtz:2018} 
+see \citet{kurtz/rodrigues:2011} and \citet{etheridge/kurtz:2019} 
 (and note that our $N$ corresponds to the $\lambda$ of those papers).
@@
 
-For the remainder of this section, when there is no risk of ambiguity we shall
-suppress the superscript $N$ on the processes $\eta$ and $\xi$.
-In this section,
+{\em For the remainder of this section, when there is no risk of ambiguity we shall
+suppress the superscript $N$ on the processes $\eta$ and $\xi$.}
+
+In this subsection,
 we'll define the process $(\lp_t)_{t \ge 0}$ in terms of the 
@@
 We describe the representation of the scaled process.
-Following~\cite{etheridge/kurtz:2018}, we build the generator step by step
+Following~\cite{etheridge/kurtz:2019}, we build the generator step by step
 from its 
@@
 Suppose that the initial population is composed of $O(N)$ particles
-with levels uniformly distributed between $[0, N]$,
+with levels uniformly distributed on $[0, N]$,
 and that the current state of the population is $\lp$,
@@
 
-A new level $u_1$ is sampled independently and uniformly from $[u,N]$,
+If it survives, 
+a new level $u_1$ is sampled independently and uniformly from $[u,N]$,
 and the parent and the offspring are assigned in random order to the 
@@
 Since $v \in [0, N]$, this moves levels down;
-see~\cite{etheridge/kurtz:2018}, Section~3.4 for a detailed explanation.
+see~\cite{etheridge/kurtz:2019}, Section~3.4 for a detailed explanation.
 
@@
 this would imply an exponential lifetime for each individual;
-see~\cite{etheridge/kurtz:2018}, Section~3.1
+see~\cite{etheridge/kurtz:2019}, Section~3.1
 for more general justification.
@@
 %i.e., the deviation from criticality of the branching mechanism.
-Recall from equation \eqref{eqn:mu_defn} that
+Recall from equation~\eqref{eqn:mu_defn} that
 $F(x,\eta) = \theta(r(x,\eta)\gamma(x,\eta) - \mu_\theta(x,\eta))$,
@@
 
-% % % % % % % %
+We need some notation. 
+Write ${\mathcal C}={\mathcal C}(\IR^d\times [0,\infty)$ for the point measures 
+on $\IR^d\times [0,\infty)$ and ${\mathcal C}_N$ for the subset consisting of 
+counting measures on $\IR^d\times [0,N]$.
+%We say that a ${\mathcal D}([0,\infty), {\mathcal C})$-valued process 
+%$(\xi_t)_{t \ge 0}$
+%    is a solution to the $(A, \lp_0)$ martingale problem
+%    if %it has initial distribution $\lp_0$ and 
+%$f(\lp_t) - f(\lp_0)-\int_0^t Af(\lp_s) ds$ is a martingale (with 
+%respect to the natural filtration) for all 
+%test functions $f$ 
+%    as defined above.
 \begin{definition}[Martingale Problem Characterisation]
     \label{defn:lookdown_mgale}
-For given positive values of $N$ and $\theta$
-and $\lp_0 \in \mathcal{M}_F(\IR^d \times [0,N])$,
-we define $(\lp^{N}_t)_{t \geq 0}$
-to be the unique solution to the martingale problem
-with initial condition $\lp_0$ and generator $A^{N}$ that satisfies
+For given positive values of $N$ and $\theta$, define the generator $A^N$
+by
+%and $\lp_0 \in {\mathcal C}_N$, %\mathcal{M}_F(\IR^d \times [0,N])$,
+%we define $(\lp^{N}_t)_{t \geq 0}$
+%to be the unique solution to the martingale problem
+%with initial condition $\lp_0$ and generator $A^{N}$ that satisfies
 \begin{equation}
@@
 as before. 
+Given $\lp_0 \in {\mathcal C}_N$, %\mathcal{M}_F(\IR^d \times [0,N])$,
+%we define $(\lp^{N}_t)_{t \geq 0}$
+we say that a ${\mathcal D}([0,\infty), {\mathcal C}_N)$-valued process 
+$(\xi_t)_{t \ge 0}$
+   is a solution to the $(A, \lp_0)$ martingale problem
+    if %it has initial distribution $\lp_0$ and 
+$f(\lp_t) - f(\lp_0)-\int_0^t Af(\lp_s) ds$ is a martingale (with 
+respect to the natural filtration) for all 
+test functions $f$ 
+    as defined above.
+%to be the unique solution to the martingale problem
+%with initial condition $\lp_0$ and generator $A^{N}$ that satisfies
 \end{definition}
@@
 Poisson distributed on 
-$\IR^d\times [0,\infty)$ with mean measure $\eta_t\times\ell$, where $\ell$
+$\IR^d\times [0,\infty)$ with mean measure $\eta_t\times\lambda$, where 
+$\lambda$ %%%place changed notation for Lebesgue measure
 is Lebesgue measure.
@@
     \end{split} \end{align}
-    Write ${\cal C}(\IR^d\times [0,\infty))$ for the point measures on $\IR^d\times [0,\infty)$.
-We say that a ${\cal C}(\IR^d\times [0,\infty))$-valued process $(\lp_t)_{t \ge 0}$
+ %   Write ${\cal C}(\IR^d\times [0,\infty))$ for the point measures on $\IR^d\times [0,\infty)$.
+We say that a ${\cal C}(\IR^d\times [0,\infty))$-valued process $(\xi_t)_{t \ge 0}$
     is a solution to the $(A, \lp_0)$ martingale problem
     if it has initial distribution $\lp_0$
-    and $f(\lp_t) - f(\lp_0)-\int_0^t Af(\lp_s) ds$ is a martingale for all 
+    and $f(\lp_t) - f(\lp_0)-\int_0^t Af(\lp_s) ds$ is a martingale (with
+respect to the natural filtration) for all 
 test functions $f$
@@
 
+In this section I haven't specified the filtration for the martingale problem.}
+
 The lookdown processes have been carefully constructed so that
@@
 \comment{Refer more precisely}
-the Markov Mapping Theorem \citep[Thm A.2 in][]{etheridge/kurtz:2018}
+the Markov Mapping Theorem \citep[Thm A.2 in][]{etheridge/kurtz:2019}
 tells us that by ``removing labels'' in this way we recover the Markov
@@
 We will then be able to pass to the scaling limit.
-This explicit description of the solution to
+This provides an explicit description of the solution to
 the limiting martingale problem of Definition~\ref{defn:limiting_lookdown_mgale}
-will enable us to identify all 
+which will enable us to identify all 
 individuals in the current population that are descendants of a
@@
 genetics by a number of authors including 
-\cite{biswas/etheridge/klimek:2018, durrett/fan:2016, hallatschek/nelson:2008}.
+\cite{hallatschek/nelson:2008, durrett/fan:2016, biswas/etheridge/klimek:2018}.
 
@@
 Concretely, then: for each label $a$ in
-$\labelspace = \bigcup_{k \ge 1} \IN_{\ge 1}^k$,
+$\labelspace = \bigcup_{k \ge 1} \IN^k$,
 let $\Pi_a$ be an independent Poisson process on 
@@
 when it is first assigned,
-and a death time $\sigma_a$, when its level first hits $N$.
+and a (possibly infinite) death time $\sigma_a$, when its level first hits $N$.
 For any $\tau_a \le t \le \sigma_a$ we denote by $X_a(t)$ and $U_a(t)$ the spatial location and level
@@
     +
-    v \ell(X_a(\tau-), y(X_a(\tau-), z), \eta(\tau-)) .
+    v \ell\big(X_a(\tau-), y(X_a(\tau-), z), \eta(\tau-)\big) .
 \end{equation*}
@@
     &=
-    X_a(\tau-) + (1 - \kappa) y(X_a(\tau-), z) .
+    X_a(\tau-) + (1 - \kappa) y\big(X_a(\tau-), z\big) .
 \end{align*}
@@
 and our line of descent switching to the offspring.
-Combining these, $X_a$, for $\tau_a \le t < \sigma_a$, solves the equation 
+Combining these observations, $X_a$, for $\tau_a \le t < \sigma_a$, solves the equation 
 \begin{align*}
@@
 \begin{remark}
-    Note here that although we have a single construction that couples
+    Although we have a single construction that couples
     the processes across all $N$, the actual 
-trajectories do not necessarily coincide for 
+trajectories, $X_a(\cdot)$, do not necessarily coincide for 
 different values of $N$, since they are affected by the whole 
@@
 Recall that $\DG g(x) = \sum_i \meanq_i \partial_i g(x) + \sum_{ij} \covq_{ij} \partial_{ij} g(x)$,
-and for the moment write $r(x)$ for $r(\cdot, \eta)(x)$,
+and for the moment write $r(x)$ for $r(x, \eta)$,
 so that
@@
 $\beta(x, \eta) = \gamma(x,\eta)\big(\meanq(x) + 2 \covq(x) \grad \log r(x, \eta)\big).$
-Associate with each label $a \in \labelspace$
+Associate with each label $a \in \labelspace = \cup_{k\geq 1}\IN^k$
 an independent $d$-dimensional Brownian motion $W_a$
@@
 with Lebesgue mean measure,
-as before with points ordered in some way.
+and with points ordered in some way.
 Given $\eta_0 \in \measures$,
-let $(x_i, u_i)$ be the points of a Poisson process
-with mean measure on $\IR^d \times [0, \infty)$ the product of $\eta_0$ and Lebesgue measure.
-For each point begin a line of descent
-with label $i$, location $X_i(0) = x_i$, level $U_a(0) = u_i$, and birth time $\tau_i = 0$.
+let $(x_i, u_i)$ be the points of a Poisson process $R_0$
+on $\IR^d \times [0, \infty)$ 
+with mean measure $\eta_0\times \lambda$
+(the product of $\eta_0$ and Lebesgue measure).
+For each point of $R_0$, begin a line of descent
+with label $i$, location $X_i(0) = x_i$, 
+level $U_i(0) = u_i$, and birth time $\tau_i = 0$.
+
 We write $\tau_a$ for the birth time of the label $a$ and 
@@
 Each point in each $R_a$ denotes a potential birth time for $a$:
-if the $j^\text{th}$ point in $R_a$ is $(\tau, v)$, with $\tau_a \le t < \sigma_a$,
+if the $j^\text{th}$ point in $R_a$ is $(\tau, v)$, with 
+$\tau_a \le \tau < \sigma_a$,
 then a new line of descent with label $a \concat j$ is produced,
@@
 with respect to $x$ we recover $w(y)dy$. 
-As a consequence of~(\ref{formal intensity}), writing $p(t,y,x)$ for
+As a consequence of~(\ref{formal intensity}), writing 
+$\mathfrak{p}(t,y,x)$ for
 the probability density that the ancestor at time $t$ units before the present 
@@
 \label{ptyx}
-p(t,y,x)=\frac{w(x)}{w(y)}\IE_x\left[\exp\left(\int_0^t b(Y_s)ds\right)
+\mathfrak{p}(t,y,x)=\frac{w(x)}{w(y)}\IE_x\left[\exp\left(\int_0^t b(Y_s)ds\right)
 \ind_{Y_t=y}\right].
@@
 integrate.
-$$\int\int \psi(y)w(y)p(t,y,x)\phi(x)dydx=\int\phi(x)w(x)
+$$\int\int \psi(y)w(y)\mathfrak{p}(t,y,x)\phi(x)dydx=\int\phi(x)w(x)
 \IE_x\left[\exp\left(\int_0^tb(Y_s)ds\right)\psi(Y_t)\right]dydx.$$
@@
 ancestral lineages backwards in time (that is the semigroup corresponding
-to $p(t,x,y)$), we can write this as 
+to $\mathfrak{p}(t,y,x)$), we can write this as 
 $$\int \psi(y)w(y)\hat{T}_t\phi(y)dy=\int\phi(x)w(x)
@@
 
-\comment{TODO structure of this section}
+In this section we present formal proofs of our 
+three
+scaling limits. In
+Subsection~\ref{sec:population_density_proof} 
+we prove Theorem~\ref{thm:nonlocal_convergence}, to obtain a limit in
+which interactions between individuals in the population are nonlocal.
+In Subsection~\ref{subsec:nonlocal to local}
+we show how, in two important examples in which the nonlocal
+limit is respectively a deterministic solution to a non-local equation of 
+reaction diffusion type and a deterministic solution to a nonlocal 
+porous medium equation with an additional logistic growth term, 
+one can pass to a further 
+limit to obtain a classical PDE. In 
+Subsection~\ref{subsec:one step convergence proof}
+we prove our third scaling limit, in which 
+we pass from our population model 
+directly to a reaction diffusion equation without going via a nonlocal
+limit.
+
+\comment{TODO add sentences about the sections Peter is editing}
 
@@
 controlling $(\langle 1,\eta^N_t\rangle)_{t\geq 0}$.
-the key is that our Assumptions~\ref{def:model_setup}
+The key is that Assumptions~\ref{def:model_setup}
 are precisely chosen to guarantee boundedness
@@
     Under Assumptions~\ref{def:model_setup},
-    for all $f \in C^2_b(\IR^d)$ there exists a $C_f < \infty$, independent of $N$,
+    for all $f \in C^2_b(\IR^d)$ with uniformly bounded first and 
+second derivatives, there exists a $C_f < \infty$, independent of $N$,
     such that
@@
 \begin{proof}
-    Consider the semimartingale decomposition of Equation \eqref{eqn:eta_martingale}:
+    Consider the semimartingale decomposition from equation~\eqref{eqn:eta_martingale}:
     \begin{align} \label{eqn:eta_f_mgale_decomp}
@@
         \langle f, \eta^N_0 \rangle
-        + \int_0^t \int_{\IR^d} \left\{
+        + \int_0^t \int_{\IR^d} \big\{
             \gamma(x, \eta^N_s) B_f(x, \eta^N_s)
             + f(x) F(x, \eta^N_s)
-            \right\} \eta^N_s(dx) ds
+            \big\} \eta^N_s(dx) ds
         + M^N_t(f) ,
@@
     where $M^N_t(f)$ is a martingale and, for the moment, we are defining
-    \begin{equation*}
+    \begin{equation}
+\label{generator Bf}
         B_f(x, \eta) = \int_{\IR^d} \theta (f(y) r(y, \eta) - f(x) r(x, \eta)) q_\theta(x, dy) .
-    \end{equation*}
+    \end{equation}
 
@@
     \end{align*}
-    where $z = t x + (1-t) y$ for some $0 \le t \le 1$. Condition~\ref{control through r} 
+    where $z = \kappa x + (1-\kappa) y$ for some $0 \le \kappa \le 1$. Condition~\ref{control through r} 
 gives uniform bounds on the derivatives of $r(x, \rho_r*\eta(x))$ 
@@
 and covariance $\covq(x)/\theta$, and both $\meanq(x)$ and $\covq(x)$
-are bounded uniformly in $x$.
+are bounded uniformly in $x$ under Assumptions~\ref{def:model_setup}.
 
@@
             \int_{\IR^n} 
-                \left\{
+                \big\{
                     f(y) r\big(y,\smooth{r}\eta(y)\big)
@@
                     f(x) r\big(x, \smooth{r}\eta(x)\big)
-                \right\}
+                \big\}
             q_{\theta}(x,dy)
@@
             \int_{\IR^n} 
-                \left\{
+                \big\{
                     f(y) r\big(y, \smooth{r}\eta(y)\big)
@@
                     f(x) r\big(x,\smooth{r}\eta(y)\big)
-                \right\}
+                \big\}
             q_{\theta}(x,dy)
@@
             \int_{\IR^n} 
-                \left\{
+                \big\{
                     f(x) r\big(x,\smooth{r}\eta(y)\big)
@@
                     f(x) r\big(x,\smooth{r}\eta(x)\big)
-                \right\}
+                \big\}
             q_{\theta}(x,dy) 
@@
     and 
-    $K_4 = \sup_{x,m} \max_{i,j} |\partial_{x_i x_j} f(x)r(x, m)|$, the first term
+    $K_4 = \sup_{x,m} \max_{i,j} |\partial_{x_i x_j} f(x)r(x, m)|$, since
+\[\big|\partial_{x_i}\big(f(x)r(x,\rho_r*\eta(y))\big|\leq K_3\]
+and
+\[\big|\partial_{x_ix_j}\big(f(x)r(x,\rho_r*\eta(y))\big|\leq K_4,\]
+the first term
 is bounded exactly as above. For the second, 
@@
     \end{multline*}
-    where $\overline{m}= t'\smooth{r}\eta(x) +(1-t') \smooth{r}\eta(y)$ for some $0\leq t'\leq 1$, and
+    where $\overline{m}= \kappa'\smooth{r}\eta(x) +(1-\kappa') 
+\smooth{r}\eta(y)$ for some $0\leq \kappa'\leq 1$, and
     we have used $r'$ and $r''$ to denote the first and second derivatives of $r(x,m)$
@@
 inequality in the case $f=1$, and then, after substitution of 
-the resulting bound into the
+the resulting bound on $\langle 1,\eta_s\rangle$ into the
 expression above, a second 
@@
     \label{lem:eta_compact_containment}
-    Under Assumptions~\ref{def:model_setup},
-    if $\theta/N \to \alpha$ and $\eta^{N}_0 \to \eta_0$ weakly as $N \to \infty$,
-    then for all $T>0$ and $N > 0$, there exists some constant $C_T$,
+    Under the assumptions of Theorem~\ref{thm:nonlocal_convergence},
+%Assumptions~\ref{def:model_setup},
+%    if $\theta/N \to \alpha$ and $\eta^{N}_0 \to \eta_0$ weakly as $N \to \infty$,
+    for each $T>0$, there exists some constant $C_T$,
+independent of $N$,
     such that
@@
         \right]
-        \le C_T .
+        \le C_T \IE[\langle 1,\eta_0\rangle].
     \end{align}
@@
     $\IE[\langle 1, \eta^N_t \rangle] \le \IE[\langle 1, \eta^N_0 \rangle] e^{Ct}$
-    for some $C$.
+    for some $C$ (independent of $N$).
     Now, let $M^*_t(f) = \sup_{0 \le s \le t} M_t(f)$,
@@
 Since $F$ is bounded above, there is a constant $K$ such that $|F|\leq K-F$ so
-that exactly as in the proof of 
+that, exactly as in the proof of 
 Lemma~\ref{lem:eta_compact_containment},
@@
 any limit point $(\eta_t)_{t\geq 0}$ of $\{(\eta_t)_{t\geq 0}\}_{N\geq 1}$
-actually takes its values in $\measures$, that is ``no mass has escaped to infinity''.
+actually takes its values in $\measures$; that is ``no mass has escaped to infinity''.
 
@@
 \label{no mass at infty}
-Let $(\eta_t)_{t\geq 0}$ be a limit point of $\{(\eta_t)_{t\geq 0}\}_{N\geq 1}$. 
+Under the assumptions of Theorem~\ref{thm:nonlocal_convergence},
+let $(\eta_t)_{t\geq 0}$ be a limit point of $\{(\eta^N_t)_{t\geq 0}\}_{N\geq 1}$. 
 Given $\delta>0$, 
@@
 +F(x,\smooth{F}\eta_s(x)) f(x),
-\eta_s(dx)\Big\rangle ds\Big]
+\eta_s(dx)\Big\rangle ds\Big].
 \end{multline} 
@@
 substituted in~(\ref{special case first moment equation}) and 
-expanded the term involving the Laplacian,we obtain
+expanded the term involving the Laplacian, we obtain
 \begin{multline}
@@
 \subsection{Convergence of some nonlocal equations to classical PDEs}
+\label{subsec:nonlocal to local}
 
@@
 $\rho_r$, $\rho_\gamma$, and $\rho_F$ by setting 
-$\rho^\epsilon(\cdot)=\rho(\cdot/\epsilon)/\epsilon$, then as $\epsilon\to 0$, the 
+$\rho^\epsilon(\cdot)=\rho(\cdot/\epsilon)/\epsilon$, as $\epsilon\to 0$, the 
 corresponding solutions should converge to a limiting
 population density that solves the corresponding ``classical'' PDE. We verify
-this in two examples; the first in which the nonlocal equation is a reaction
+this in two examples; in the first the nonlocal equation is a reaction
 diffusion equation with the ``nonlocality'' only appearing in the 
-reaction term, and the second in which the nonlocal PDE is a special 
+reaction term; in the second the nonlocal PDE is a special 
 case of a nonlinear porous medium equation. These, in particular,
@@
 Fix $T>0$. There exists a constant $K= K(T)>0$ such that, for any 
-$x, y, z \in \mathbb{R}^d$ and $t \in [0,T]$,
+$x, y\in \mathbb{R}^d$ and $t \in [0,T]$,
 \begin{equation} \label{eq:boundDensityXt}
-\int |f_t(x,z)-f_t(y,z)| dz \leq \frac{|x-y|}{\sqrt{t}} K.
+\int |f_t(x,z)-f_t(y,z)| dz \leq \frac{\|x-y\|}{\sqrt{t}} K.
 \end{equation}
@@
 \begin{align*}
-\int |f_t(x,z)-f_t(y,z)| dz & \leq \int |x-y| |\nabla f_t(w,z)| dz
+\int |f_t(x,z)-f_t(y,z)| dz & \leq \int \|x-y\| \|\nabla f_t(w,z)\| dz
 \end{align*}
@@
 $\lambda=\lambda(T)>0$ and $K$ such that,
-\[ |\nabla f_t(w,z)|  \leq  \frac{K }{\sqrt{t}}p_{ \lambda  t}(w,z), \]
+\[ \|\nabla f_t(w,z)\|  \leq  \frac{K }{\sqrt{t}}p_{ \lambda  t}(w,z), \]
 where $p_s(x,y)$ is the Brownian transition density.
@@
 \int |f_t(x,z)-f_t(y,z)| dz & \leq K 
-\frac{|x-y|}{\sqrt{t}} \int p_{\lambda  t}(w,z)dz = 
-K  \frac{|x-y|}{\sqrt{t}},
+\frac{\|x-y\|}{\sqrt{t}} \int p_{\lambda  t}(w,z)dz = 
+K  \frac{\|x-y\|}{\sqrt{t}},
 \end{align*}
@@
 \[ \IE[\|Z_t^y-Z_t^x\|]  = \int \int \|u-v\| f_t(y,u) f_t(x,v) du dv . \]
-Under our regularity assumptions on $C$, $b$, using Equation~(1.2)
+Under our regularity assumptions on $C$, $b$, using equation~(1.2)
 of~\cite{sheu:1991}, there exist constants $K$, $\lambda =\lambda (T)>0$ 
@@
 \begin{align*}
-|\varphi_t(x) - \rho^\epsilon_F*\varphi_t(x)| & = 
+|\varphi_t(x) - \rho^\epsilon_F*\varphi_t(x)| & \leq 
 \int_{\|x-y\| > \epsilon^{3/4} } \rho^\epsilon_F(x-y)|\varphi_t(y)-\varphi_t(x)| dy  \\ 
@@
 %$\rho_\epsilon*\varphi_t(x)$ are bounded by $M$. 
-let $L_M$ be the (uniform) Lipschitz constant of $F$ on $[0,M]$. Then,
+let $L_M$ be the (uniform) Lipschitz constant of $F$ on $[0,M]$, with
+$M$ still taken from Lemma~\ref{BoundednessVarphis}. Then,
 \begin{align*}
@@
 \begin{proof}
-
-Consider 
+First observe that, since $x\log x$ is bounded below, 
+$\int_{-1}^1\psi_t^\epsilon(x)\log\psi_t^\epsilon(x) dx$ is bounded below.
+
+Now consider 
 \begin{multline}
@@
 \end{equation*}
-where the constant $C$ is independent of $x>1$.
+where the constant $C$ is independent of $x\geq1$.
 A fortiori, 
@@
 \end{equation*}
-Evidently a symmetric argument applies for $x<-1$.
+Evidently a symmetric argument applies for $x\leq -1$.
 Summing over $x$, we find
@@
 \subsection{Simultaneous scaling with interaction distance}
+\label{subsec:one step convergence proof}
 
@@
 we establish sufficient bounds on the moments of $\rho_\epsilon*\eta_t(x)$ to
-establish $C$-tightness and then apply standard results on 
+establish tightness and then apply standard results on 
 convergence of Markov processes from~\cite{ethier/kurtz:1986}. Although
@@
     Fix $t>0$,
-    let $(N(s))_{s \ge 0}$ be a rate one Poisson process,
-    and let $T(t) = N(\theta t) / \theta$.
+    let $(\Pi(s))_{s \ge 0}$ be a rate one Poisson process,
+    and let $T(t) = \Pi(\theta t) / \theta$.
     Then
@@
     \end{align}
-    Now, observe that since $\IE[e^{-N(\theta t)}] = \exp(-\theta t (1 - e^{-1}))$,
+    Now, observe that since $\IE[e^{-\Pi(\theta t)}] = \exp(-\theta t (1 - e^{-1}))$,
     by Markov's inequality,
@@
         \IP\left\{
-            e^{-N(\theta t)} > e^{-\theta (t - \epsilon^2) / 2}
+            e^{-\Pi(\theta t)} > e^{-\theta (t - \epsilon^2) / 2}
         \right\}
@@
 \\
-&\leq \frac{\IE[\exp\big(-N(\theta t)\big)]}{\exp\big(-\theta(t-\epsilon^2)/2\big)}
+&\leq \frac{\IE[\exp\big(-\Pi(\theta t)\big)]}{\exp\big(-\theta(t-\epsilon^2)/2\big)}
 \nonumber
@@
         \IP\Big\{
-            \frac{N(\theta t)}{ \theta}
+            \frac{\Pi(\theta t)}{ \theta}
             >
@@
 For convenience, suppose $\theta$ is an integer,
-and so we may write $N(\theta t) = Z_1(t) + \cdots + Z_\theta(t)$,
+and so we may write $\Pi(\theta t) = Z_1(t) + \cdots + Z_\theta(t)$,
 where the $Z_i(t)$ are i.i.d.~Poisson($t$) random variables.
@@
         \IP\left\{
-            \frac{N(\theta t)}{\theta}
+            \frac{\Pi(\theta t)}{\theta}
             > A(\epsilon^2 + t)
@@
 \label{bounds on moments}
-For each $T\in [0,\infty)$, and $k\in\IN$, there exist constants $C=C(k,T)$ and
+Let $\{{\cal F}_t\}_{t\geq 0}$ denote the natural filtration. 
+Under the assumptions of Theorem~\ref{thm:local_convergence},
+for each $T\in [0,\infty)$, and $k\in\IN$, there exist constants $C=C(k,T)$ and
 $\widetilde{C}=\widetilde{C}(k,T)$, independent of $\epsilon$, such that for all 
@@
 \IE\Big[\left.\big(\rho_\epsilon*\eta_t(x)\big)^k\right| {\cal F}_u\Big]
-\leq C\IE\Big[\langle\psi_{t-u}^{\epsilon,x}(z), \eta_u(dz)\rangle^k\Big]
+\leq C\langle\psi_{t-u}^{\epsilon,x}(z), \eta_u(dz)\rangle^k
 +C\frac{\theta}{N\epsilon^d}
-\IE\Big[\langle\psi_{t-u}^{\epsilon,x}(z), \eta_u(dz)\rangle\Big];
+\langle\psi_{t-u}^{\epsilon,x}(z), \eta_u(dz)\rangle;
 \end{equation} 
@@
 \\
-\leq\widetilde{C}\IE\Big[\langle\psi_{t-u}^{\epsilon,x}(z), \eta_u(dz)\rangle^k\Big]
+\leq\widetilde{C}\langle\psi_{t-u}^{\epsilon,x}(z), \eta_u(dz)\rangle^k
 +\widetilde{C}\frac{\theta}{N\epsilon^d}
-\IE\Big[\langle\psi_{t-u}^{\epsilon,x}(z), \eta_u(dz)\rangle\Big];
+\langle\psi_{t-u}^{\epsilon,x}(z), \eta_u(dz)\rangle;
 \end{multline}
@@
 under the assumptions of Theorem~\ref{thm:local_convergence}, the
+expected values of the
 quantities on the right hand side of~(\ref{moment bound rhoepsilon})
@@
 
-The proof proceeds by induction.
+We proceed by induction.
 
@@
 with time derivative $\dot \phi_t(x) = \partial_t \phi_t(x)$,
-\begin{align*}
+\begin{multline}
+\label{time dep mg prob}
 %        \label{timeMGP}
     \langle \phi_0(x), \eta_t(dx) \rangle
-    &= %\nonumber 
+    = %\nonumber 
     \langle \phi_t(x), \eta_0(dx) \rangle
@@
     +
-    \int_0^t \langle \mathcal{L}^\theta \phi_{t-s}(x) - \dot \phi_{t-s}(x), \eta_s(dx) \rangle ds
-    \\ & {}
+    \int_0^t \big\langle \mathcal{L}^\theta \phi_{t-s}(x) 
+- \dot \phi_{t-s}(x), \eta_s(dx) \big\rangle ds
+    \\  {}
     +
-    \int_{0}^t \langle \phi_{t-s}(x) F(x, \eta_s) , \eta_s(dx) \rangle ds ,
-\end{align*}
+ \int_{0}^t \big\langle \phi_{t-s}(x) F(x, \eta_s) , \eta_s(dx) \big\rangle ds ,
+\end{multline}
 where $M_t(\phi_\cdot(\cdot))$ is a martingale. 
@@
 &=&\langle\psi^{\epsilon,x}_t(y),\eta_0(dy)\rangle
-+\int_0^t\langle\psi^{\epsilon,x}_{t-s}(y)F\big(\rho_\epsilon*\eta_s(y)\big), \eta_s(dy)\rangle ds
++\int_0^t\big\langle\psi^{\epsilon,x}_{t-s}(y)
+F\big(\rho_\epsilon*\eta_s(y)\big), \eta_s(dy)\big\rangle ds
 +M_t(x),
@@
 Taking expectations in~(\ref{expn rhoepsilon}), using that $F$ is bounded above, and 
-applying Gronwall's inequality, we obtain~(\ref{moment bound rhoepsilon})
+applying Gronwall's inequality to 
+$\langle\psi^{\epsilon,x}_{t-s}, \eta_s\rangle$ 
+we obtain~(\ref{moment bound rhoepsilon})
 in the case $k=1$. 
@@
 \begin{equation}
--\int_0^t\langle\psi^{\epsilon,x}_{t-s}(y)F(\rho_\epsilon*\eta_s(y), \eta_s(dy)\rangle ds
+-\int_0^t\big\langle\psi^{\epsilon,x}_{t-s}(y)
+F(\rho_\epsilon*\eta_s(y), \eta_s(dy)\big\rangle ds
 =\langle\psi^{\epsilon,x}_t(y),\eta_0(dy)\rangle
@@
 \end{equation} 
-and taking expectations again this yields 
+and taking expectations again, 
+since $\langle\psi^{\epsilon,x}_0,\eta_t\rangle>0$, and $M_0(x)=0$,
+this yields 
 $$\IE\Big[-\int_0^t\langle\psi^{\epsilon,x}_{t-s}(y)F(\rho_\epsilon*\eta_s(y), 
-\eta_s(dy)\rangle ds\Big]
-\leq \widehat{C}\IE\big[\langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle\big].$$
+\eta_s(dy)\rangle ds\Big|{\cal F}_0\Big]
+\leq \widehat{C}\langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle.$$
 Since $F$ is bounded above, there exists a constant $K$ such that $|F|\leq K-F$ and so 
@@
 obtained, this in turn yields 
-$$\IE\Big[\int_0^t\langle\psi^{\epsilon,x}_{t-s}(y)|F(\rho_\epsilon*\eta_s(y)|, 
-\eta_s(dy)\rangle ds\Big]\leq 
-\widetilde{C}\IE\big[\langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle\big],$$
+$$\IE\Big[\int_0^t\big\langle\psi^{\epsilon,x}_{t-s}(y)
+|F(\rho_\epsilon*\eta_s(y)|, 
+\eta_s(dy)\big\rangle ds\Big|{\cal F}_0\Big]\leq 
+\widetilde{C}\langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle,$$
 which is~(\ref{flandoli trick for rhoepsilon})
@@
 \label{kth moment for time varying function}
-\IE\Big[\langle \psi^{\epsilon,x}_0,\eta_t\rangle^k\Big]
+\IE\Big[\langle \psi^{\epsilon,x}_0,\eta_t\rangle^k\Big|{\cal F}_0\Big]
 =\langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle^k
-+\IE\Big[\int_0^t\Pgen^N\big(\langle\psi^{\epsilon,x}_{t-s}(y)\big),\eta_s(dy)\rangle ds
++\IE\Big[\int_0^t\Pgen^N\big(\langle\psi^{\epsilon,x}_{t-s}(y),\eta_s(dy)\rangle^k\big) ds
 \\
 -\int_0^t\langle k\dot{\psi}^{\epsilon,x}_{t-s}(y), \eta_s(dy)\rangle
-\langle \psi^{\epsilon, x}_{t-s}(y),\eta_s(dy)\rangle^{k-1}ds\Big].
+\big\langle \psi^{\epsilon, x}_{t-s}(y),\eta_s(dy)\big\rangle^{k-1}ds
+\Big|{\cal F}_0\Big].
 \end{multline}
@@
 \Big\langle
-\int_0^t\theta N\Big\{\sum_{j=2}^{k}\binom{k}{j}\frac{\psi_{t-s}^{\epsilon,x}(y)^j}{N^j}\langle \psi^{\epsilon,x}_{t-s},\eta_s\rangle^{k-j}
-\Big(1+(-1)^j\Big(1-\frac{F(\rho_\epsilon*\eta_s(y))}{\theta}\Big)\Big),
-\eta_s(dy)\Big\rangle ds\Big]
+\int_0^t\theta N\sum_{j=2}^{k}\binom{k}{j}\int
+\frac{\psi_{t-s}^{\epsilon,x}(z)^j}{N^j}
+\langle \psi^{\epsilon,x}_{t-s},\eta_s\rangle^{k-j}
+q_\theta(y,dz),
+%+(-1)^j\Big(1-\frac{F(\rho_\epsilon*\eta_s(x))}{\theta}\Big)\Big),
+\eta_s(dy)\Big\rangle ds %\Big]
+\\
++
+\int_0^t\theta N\sum_{j=2}^{k}\binom{k}{j}\frac{\psi_{t-s}^{\epsilon,x}(y)^j}{N^j}\langle \psi^{\epsilon,x}_{t-s},\eta_s\rangle^{k-j}
+%\Big(1+
+(-1)^j\Big(1-\frac{F(\rho_\epsilon*\eta_s(y))}{\theta} %\Big)
+\Big),
+\eta_s(dy)\Big\rangle ds\Big|{\cal F}_0\Big]
 \\
@@
 \Big(2+\frac{|F(\rho_\epsilon*\eta_s(y))|}{\theta}\Big),\eta_s(dy)\Big\rangle
-\langle\psi^{\epsilon,x}_{t-s},\eta_s\rangle^{k-j}ds\Big]
+\langle\psi^{\epsilon,x}_{t-s},\eta_s\rangle^{k-j}ds\big|{\cal F}_0\Big]
 \\
@@
 C'\frac{\theta}{N\epsilon^d}\sum_{j=1}^{k-1}
-\IE\big[\langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle^j\big]
+\langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle^j
 \leq
 C''\frac{\theta}{N\epsilon^d}
-\Big(\IE\big[\langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle^k\big]
-+\IE\big[\langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle\big]\Big).
+\Big(\langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle^k
++\langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle\Big).
 \end{multline*}
@@
 \label{kth step of induction}
-\IE\Big[\langle \psi^{\epsilon,x}_0,\eta_t\rangle^k\Big]
+\IE\Big[\langle \psi^{\epsilon,x}_0,\eta_t\rangle^k\Big|{\cal F}_0\Big]
 \leq
-\IE\big[\langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle^k\big]
+\langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle^k
 +\tilde{C}\IE\Big[\int_0^t
-\langle\psi^{\epsilon, x}_{t-s}(y),\eta_s(dy)\rangle^k ds\Big]
+\langle\psi^{\epsilon, x}_{t-s}(y),\eta_s(dy)\rangle^k ds
+\Big|{\cal F}_0\Big]
 \\
 +C''\frac{\theta}{N\epsilon^d}
-\Big(\IE\big[\langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle^k\big]+
-\IE\big[\langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle\big]\Big)
+\Big(\langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle^k+
+\langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle\Big)
 %\langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle^j
@@
 
-We shall need the following consequence of the bounds that we obtained in 
+We shall also need the following consequence of the bounds that we obtained in 
 Lemma~\ref{bounds on moments}:
 \begin{corollary}
-Under the assumptions of Lemma~\ref{bounds on moments},
-for each $k\geq 1$,
+\label{alternative form moment bounds}
+Under the assumptions of Theorem~\ref{thm:local_convergence},
+%Lemma~\ref{bounds on moments},
+for each $k\geq 1$, $T>0$,
 \begin{equation}
 \label{double integrals with respect to eta}
-\IE\Big[\big\langle (\rho_\epsilon*\eta_t)^{k},\eta_t\big\rangle \Big]<C(k)<\infty.
+\IE\Big[\big\langle (\rho_\epsilon*\eta_t)^{k},\eta_t\big\rangle \Big]
+<C(k,T)<\infty, \qquad\mbox{ for all }t\in [0,T].
 \end{equation}
@@
 \IE\big[\langle \rho_\epsilon*\eta_t(x),\eta_t(dx)\rangle\big]&=
-\IE\big[\int\int p_{\epsilon^2}(x,z)\eta_t(dz)\eta_t(dx)\big]
+\IE\Big[\int\int p_{\epsilon^2}(x,z)\eta_t(dz)\eta_t(dx)\Big]
 \\        
 &=
-\IE\big[\int\int\int p_{\epsilon^2/2}(x,y) p_{\epsilon^2/2}(y,z)dy\eta_t(dz)\eta_t(dx)\big]
+\IE\Big[\int\int\int p_{\epsilon^2/2}(x,y) 
+p_{\epsilon^2/2}(y,z)dy\eta_t(dz)\eta_t(dx)\Big]
        % \langle p_{\epsilon^2/2} * p_{\epsilon^2/2} * \eta_t(x), \eta(dx) \rangle
@@
 \begin{align*}
-&\IE\Big[\int p_{\epsilon^2/2}*\eta_t(y_1) p_{\epsilon^2/2}*\eta_t(y_2)
-p_{\epsilon^2/4}*\eta_y\big(\frac{y_1+y_2}{2}\big)p_{\epsilon^2}(y_1,y_2)dy_1dy_2\Big]
+&\IE\Big[\int p_{\epsilon^2/2}*\eta_t(y_1)\, p_{\epsilon^2/2}*\eta_t(y_2)\,
+p_{\epsilon^2/4}*\eta_y\big(\frac{y_1+y_2}{2}\big)\, 
+p_{\epsilon^2}(y_1,y_2)dy_1dy_2\Big]
 \\
@@
 
-\begin{corollary}[$C$-tightness of $\{(\rho_\epsilon*\eta_t(x) dx)_{t\geq 0}\}$]
+\begin{corollary}[Tightness of $\{(\rho_\epsilon*\eta_t(x) dx)_{t\geq 0}\}$]
 \label{lem:density_tightness} 
-    Under the assumptions of Theorem~\ref{TeoremOneStepConvergence}
+Under the assumptions of Theorem~\ref{thm:local_convergence},
 the sequence of measure valued processes $\{ \rho*\eta_t(x) dx \}_{t \geq 0}$
-    (taking values in $D([0,T], \measures)$ is $C$-tight.
+(taking values in $D([0,T], \measures)$ is tight.
 \end{corollary}
 \begin{proof}
-Since the quadratic variation of the martingale $M_t(x)$ of 
-equation~(\ref{expn rhoepsilon}) is
-\begin{equation*}
-%\label{qv M(x)}
-[M(x)]_t=\frac{\theta}{N}\int_0^t\Big\langle\int\psi^{\epsilon,x}_{t-s}(z)^2q_\theta(y,dz)
-+\Big(1-\frac{F(\rho_\epsilon*\eta(y)}{\theta}\Big)\psi^{\epsilon,x}_{t-s}(y)^2,\eta_s(dy)
-\Big\rangle ds,
-\end{equation*}
-in exactly the same way as we proved that $\IE[\sup_{0\leq t\leq T} \langle 1,\eta_t\rangle]$ is 
-bounded in Lemma~\ref{lem:eta_compact_containment}, 
-using~(\ref{moment bound rhoepsilon}) 
-and~(\ref{flandoli trick for rhoepsilon}) with $k=1$, 
-we can deduce that $\IE[\sup_{0\leq t\leq T}M_t(x)]$ is bounded independently of
-$N$, $\theta$ and $\epsilon$ (in fact that it tends to zero) and
-by an application of Gronwall's inequality we deduce 
-that $\IE[\sup_{0\leq t\leq T} \rho_\epsilon*\eta_t(x)]$ is
-bounded. This proves compact containment.
-
-    To conclude $C$-tightness we show that, for $T>0$, and any
-$f\in C_b^\infty (\IR^d)$ with bounded second derivatives, given $\nu>0$,
-    there exists $\delta=\delta(f,T,\nu) >0$ so that for $\theta$ and $N$ large enough,
-    \begin{align}
-        \IP\Big[
-            \sup_{s,t \in [0,T], |s-t| < \delta}
-            \left|
-                \langle \rho_{\epsilon} * f, \eta_s \rangle
-                - \langle \rho_{\epsilon} * f, \eta_t \rangle
-            \right|
-            >
-            \nu
-        \Big]
-        <
-        \nu \label{conditionCtightness}
-    \end{align}
-
-First, observe that
+
+First observe that the proof from Lemma~\ref{lem:eta_compact_containment}, 
+that 
+$\IE[\sup_{0\leq t\leq T} \langle 1,\eta_t\rangle]$ is 
+bounded goes through unchanged, and since 
+$\langle 1, \rho_\epsilon*\eta_t(x)dx\rangle=\langle 1, \eta_t\rangle$,  
+compact containment follows.
+
+As in the nonlocal case, it suffices to prove that for 
+for $T>0$, and any
+$f\in C_b^\infty (\IR^d)$ with bounded second derivatives, the
+sequence of real-valued processes 
+$\big\{\big(\int f(x)\rho_\epsilon*\eta_t^N(x)dx\big)_{t\geq 0}\big\}_{N\geq 1}$is tight.  
+Let us temporarily write $X_f^N(t)$ for $\int f(x)\rho_\epsilon*\eta_t^N(x)dx$
+and set
+\[
+w'\big(X^N,\delta,T\big)= \inf_{\{t_i\}}\max_i\sup_{s,t\in [t_{i-1},t_i)}
+\big| X_f^N(t)-X_f^N(s)\big|,
+\]
+where $\{t_i\}$ ranges over all partitions of the form 
+$0=t_0<t_1<\cdots <t_{n-1}<T\leq t_n$ with 
+$\min_{1\leq i\leq n}(t_i-t_{i-1})>\delta$ and $n\geq 1$.
+Using Corollary~3.7.4 (p.129) of~\cite{ethier/kurtz:1986}, 
+to prove tightness
+of the sequence of real-valued processes $X_f^N$
+it suffices to check compact containment of 
+the sequence $\{\rho_\epsilon*\eta_t(x)dx\}_{N\geq 1}$ at any rational time $t$ and
+that for every $\nu>0$ and $T>0$, there exists $\delta>0$ such that
+\[
+\limsup_{N\to\infty}\IP\big[w'\big(X_f^N,\delta,T\big)>\nu\big]<\nu.
+\]
+Evidently this will follow 
+if we can show that this condition is satisfied when we replace the 
+minimum over all partitions with mesh at least $\delta$ in the 
+definition of $w'$, by the partition into
+intervals of length exactly $\delta$.
+
+We have
 \begin{multline}
-\label{C-tightness estimate}
+\label{tightness estimate}
 \left|
@@
 where $\widehat{M}(f)$ is the martingale of~(\ref{eqn:eta_martingale})
-with the test function $f$ replaced by $\rho_\epsilon*f$. In particular, 
-just as for $M_t(x)$ above, we can deduce that its supremum tends to zero under
-our scaling.
-
-Again using the approach of Lemma~\ref{lem:eta_compact_containment}, we have that 
-$\IE[\sup_{0\leq t\leq T} \langle 1,\eta_t\rangle]$ is bounded,
-% and using that
-%$|F|\leq K-F$ and rearranging the equation for $\langle 1,\eta_t\rangle>$ in the usual
-%way to find an expression for 
-%$-\int_s^t\langle F\big(\rho_\epsilon*\eta_u(x)\big), \eta_u(dx)\rangle du$, we can bound
-and so combining with the corresponding estimate for $\rho_\epsilon*\eta_u$, 
-by Markov's inequality, we can choose $m_\nu$, $\widetilde{m}_\nu$, so that 
-$$\IP[\sup_{0\leq u\leq T}\langle<1,\eta> >\tilde{m}_\nu]<\nu/2$$
-$$\IP[\sup_{0\leq u\leq T}\langle<1,\eta> >\tilde{m}_\nu]<\nu/2$$
-UP TO HERE
+with the test function $f$ replaced by $\rho_\epsilon*f$. 
+We control each of the three terms on the right hand side separately.
+%In particular, 
+%just as for $M_t(x)$ above, we can deduce that its supremum tends to zero under
+%our scaling.
 
@@
 \end{multline*}
-
-    Now, we can use \eqref{MGPT_epsilon} to write this difference
-    as an integral, then bound the terms as above to get
-    \begin{align*}
+%Since $F$ is a polynomial, 
+We therefore have
+\begin{multline*}
         \left|
+        \langle \rho_{\epsilon} * f, \eta_t \rangle
+        -
         \langle \rho_{\epsilon} * f, \eta_s \rangle
-        -
-        \langle \rho_{\epsilon} * f, \eta_t \rangle
         \right|
         \leq
-        ( \| \Delta f \|_\infty + C_F \|f\|_\infty) |s - t|
+        \| \Delta f \|_\infty |t-s|
         \sup_{0 \leq u \leq T } \langle 1, \eta_u \rangle
+\\
 +
-        \sup_{u \leq T} |\widehat{M}_u| .
+\|f\|_\infty \int_s^t
+%\Big\langle \sum_{k=1}^n|a_k|
+%\big(\rho_\epsilon*\eta_u(x)\big)^k, 
+\big\langle \big|F\big(\rho_\epsilon*\eta_u(x)\big)\big|,
+\eta_u(dx)\big\rangle du +2\sup_{0\leq u\leq T}|\widehat{M}^N(f)_u|.
+    \end{multline*}
+Using the Burkholder-Davis-Gundy inequality, our
+moment bounds, and Markov's inequality
+\begin{equation}
+\label{martingale term to zero}
+\limsup_{N\to\infty}\IP\Big[
+2\sup_{0\leq u\leq T}|\widehat{M}^N(f)_u|
+>\frac{\nu}{3}
+\Big]\leq \limsup_{N\to\infty}\frac{36}{\nu^2}\IE\big[[\widehat{M}^N(f)]_t\big]
+\leq \limsup_{N\to\infty}\frac{36}{\nu^2}\frac{C\theta}{N\epsilon^d} 
+=0. 
+\end{equation}
+Now consider
+\begin{multline*}
+\IE\Big[
+\Big(\int_s^t\big\langle \big|F\big(\rho_\epsilon*\eta_u(x)\big)\big|,
+\eta_u(dx)\big\rangle du\Big)^2\Big]
+\\
+=
+\IE\Big[
+\int_s^t\big\langle \big|F\big(\rho_\epsilon*\eta_u(x)\big)\big|,
+\eta_u(dx)\big\rangle 
+\int_u^t\big\langle \big|F\big(\rho_\epsilon*\eta_r(x)\big)\big|,
+\eta_r(dx)\big\rangle dr
+du\Big].
+\end{multline*}
+Since $F$ is polynomial, using our moment bounds we see that this 
+quantity is bounded by $C(t-s)^2$ for some constant $C$ which we can 
+take to be independent of $s$, $t$ and $\epsilon$. Markov's inequality 
+then gives
+\[
+\IP\Big[\|f\|_\infty\int_s^t
+\big\langle \big|F\big(\rho_\epsilon*\eta_u(x)\big)\big|,
+\eta_u(dx)\big\rangle du \geq \frac{\nu}{3}\Big]
+\leq C\frac{(t-s)^2}{\nu^2}.
+\]
+A union bound gives that
+\begin{equation}
+\label{union bound}
+\IP\Big[\max_i\|f\|_\infty\int_{t_{i-1}}^{t_i}
+\big\langle \big|F\big(\rho_\epsilon*\eta_u(x)\big)\big|,
+\eta_u(dx)\big\rangle du \geq \frac{\nu}{3}\Big]
+\leq C\frac{\delta}{T\nu^2}.
+\end{equation}
+Now using Markov's inequality, we can choose $K$ so that
+\[
+\IP\Big[\|\Delta f\|_\infty\, \sup_{0\leq t\leq T} \langle 1,\eta_t\rangle 
+>K\Big]<\frac{\nu}{3}, 
+\]
+and so choosing $\delta$ so that $K\delta<\nu/3$ in this 
+expression and $C\delta<T\nu^3/3$ in~(\ref{union bound}),
+combining with~(\ref{martingale term to zero}), the result follows.
+\end{proof}
+
+\subsubsection{Identification of the limit}
+\label{limit in onestep case}
+
+We now turn to the identification of the limit points of the sequence 
+$\big\{\big(\rho_\epsilon*\eta_t(x)dx\big)_{t\geq 0}\big\}_{N\geq 1}$.
+Since we only know that for every sequence there is a weakly convergent subsequence,
+the difficulty is the non-linear term in the martingale problem. 
+The first step is to prove an approximation of the form:
+\begin{align*}
+\IE\Big[
+\int_0^t\big\langle T_{\epsilon^2} f(y) F\big(\rho_\epsilon *\eta_s(y)\big), 
+\eta_s(dy) \big\rangle ds\Big]
+\sim 
+\IE\Big[
+\int_0^t\big\langle T_{\epsilon^2} f(y) F\big(\rho_\epsilon * \eta_s(y)\big), 
+\rho_\epsilon * \eta_s(y) dy \big\rangle ds\Big].
 \end{align*}
-    Taking expectations we get,
-    \begin{equation}
-        \IE\left[ \left|
-            \langle \rho_\epsilon * f, \eta_s \rangle
-            -
-            \langle \rho_\epsilon * f, \eta_t \rangle
-        \right| \right]
-        \leq
-        \widehat{C} |s-t|
-        +
-        \widehat{C} \left( \frac{\theta}{N} T \right)^{1/2} .
-    \end{equation}
-    Using this and Markov's inequality give that \eqref{conditionCtightness}
-    holds with $\delta = \alpha/(3 \widehat{C}|s-t|)$,
-    for $N$, $\theta$ big enough so $\widehat{C}\sqrt{T\theta/N}$ is bounded by $\alpha/3$.
-    (Note the last condition is possible by \eqref{ConditionsForConvergence}.)
-    Thus we have concluded $C$-tightness. 
-\end{proof}
-
-\comment{
-    Peter writes: the following Remark refers to the proof of Lemma~\ref{lem:SecondMomentMass},
-    which was previously wrong and is now fairly different.
-    However, I don't see how to prove the Remark using any similar method,
-    because to bound $\int p_{\epsilon^2 / 2} * \eta_t(x)^2 dx$
-    it seems like we need control on $\rho_\epsilon * \eta_t(x)$ uniformly in $x$
-    (and, integrability), which I don't think we have?
-    But, I'm probably being dense.
-    See after this for an attempted rewrite.
-}
-
-\begin{remark} \label{remark:BoundedIntegral}
-    Similar as we got equation (\ref{eq:boundedIntegralAgainstf}), from equation \ref{MGPT_epsilon} we can conclude there exists a $C < \infty$ such that
+This is the content of Proposition~\ref{CuadraticApprox}, 
+but first we need a continuity 
+estimate on $\rho_\epsilon*\eta$.
+
+%\begin{lemma} \label{ContinuityEstimate}
+%Under the conditions of Theorem~\ref{TeoremOneStepConvergence} we have that 
+%for all $x \in \IR^d$, $\delta>0$,
+%\[
+%\int |\rho_\epsilon*\eta_s(x) -\rho_\epsilon*\eta_s(y)| \rho_\delta(x-y) dy \]
+%is bounded by
+%\comment{Will need to be restated once corrected. Notice we want to put in powers of 
+%$\rho_\epsilon*\eta_s(x)$ and $\rho_\epsilon*\eta_s(y)$ }
+%\begin{align*}
+%\frac{\delta}{\sqrt{\epsilon^2+s}} \langle 1,\eta_0(dz) \rangle &+ \int_0^s \frac{\delta}{\sqrt{\epsilon^2+s-r}} (\langle 1, \eta_r(dz)\rangle + \langle \rho_\epsilon*\eta_r(z), \eta_r(dz)\rangle)dr \\ &+ |M_s(x)| + \int |M_s(y)| \rho_\delta(y-x)dy + \mathcal{O}\left( \frac{1}{\epsilon^2 \theta}\right)
+%\end{align*} 
+%where $M_s(x)$ is the martingale in (\ref{MartingaleProblemMolifier}).
+%\end{lemma}
+
+%\begin{proof}
+We fix $\delta>0$ and 
+suppose that $s>\delta$.
+Let us write
 \[
-        \IE\left[\sup_{0 \leq t \leq T} \int p_{\epsilon^2/2} * \eta_t(x) dx \right] < C .
+\widehat{\epsilon}(\delta,\epsilon,\theta):=
+e^{-\epsilon^2\theta}+\frac{1}{(\epsilon^2+\delta)^{d/2}}
+\frac{1}{(A+1)^{\epsilon^2\theta}}e^{-\epsilon^2\theta},
 \]
-    By using this and the same pattern used to prove Lemma~\ref{lem:SecondMomentMass},
-    we can then conclude there is a (different) $C < \infty$ such that
-    \[
-        \IE\left[  \sup_{0 \leq t \leq T} \int \left( p_{\epsilon^2/2} * \eta_t(x) \right)^2 dx \right]
-        <
-        C .
-    \]
-    Then, because
-    \begin{align*}
-        \langle p_{\epsilon^2} * \eta_t(x), \eta(dx) \rangle
-        &=
-        \langle p_{\epsilon^2/2} * p_{\epsilon^2/2} * \eta_t(x), \eta(dx) \rangle
-        \\ &=
-        \int_{\IR^d} \left( p_{\epsilon^2/2} * \eta_t(x) \right)^2 dx .
-    \end{align*}
-    we can conclude that
-    $\IE[\langle \rho_\epsilon*\eta_t(x), \eta_t(dx) \rangle ]$ is uniformly bounded,
-    which will be useful in the next section.
-\end{remark}
-
-\comment{Here's my start at rewriting that Remark;
-    however, I'm stuck since $\theta(p_{\epsilon^2 + 1/\theta} - p_{\epsilon^2}) * \eta$
-    isn't bounded by $p_{\epsilon^2} * \eta$ (uniformly in $\epsilon$, anyhow).
-}
-
-\begin{remark} \label{remark:BoundedIntegral2}
-    Below, we will want to bound
-    \[
-        \langle \rho_\epsilon * \eta_t, \eta_t \rangle
-        =
-        \int_{\IR^d} \int_{\IR^d} p_{\epsilon^2}(x, y) \eta_t(dx) \eta_t(dy) .
-    \]
-    Writing $H(\eta) = \langle \rho_\epsilon * \eta, \eta \rangle$,
-    note that since $p_{\epsilon^2}$ is symmetric,
-    $H(\eta + \delta_z / N) = H(\eta) + 2 \rho_\epsilon * \eta(z) / N + p_{\epsilon^2}(z, z) / N^2$,
-    so following Section~\ref{sec:heuristics},
-    \begin{align*}
-        \langle \rho_\epsilon * \eta_t, \eta_t \rangle
-        &=
-        \langle \rho_\epsilon * \eta_0, \eta_0 \rangle
-        +
-        2 \theta \int_0^t \left \langle \int_{\IR^d}
-            \left(
-               \rho_\epsilon * \eta_s(y)
-               -
-               \rho_\epsilon * \eta_s(x)
-            \right)
-            q_\theta(x, dy)
-        , \eta_s(dy) \right \rangle ds
-        \\ & \qquad {}
-        +
-        2 \int_0^t
-        \langle
-            \rho_\epsilon * \eta_s(x) F(x, \eta_s)
-        , \eta_s(dx) \rangle
-        ds
-        +
-        O\left( \frac{1}{\epsilon^d N^2} \right)
-        + M_t ,
-    \end{align*}
-    where $M_t$ is a martingale with quadratic variation
-    \begin{align*}
-        [M]_t
-        &=
-        4 \frac{\theta}{N} \int_0^t
-        \left \langle
-            \int_{\IR^d}
-                \rho_\epsilon * \eta_s(y)^2
-            q_\theta(x, dy)
-        , \eta_s(dx) \right\rangle
-        ds
-        \\ & \qquad {}
-        +
-        4 \int_0^t
-        \left \langle
-            \rho_\epsilon * \eta_s(x)^2 (1 + F(x, \eta_s) / \theta) 
-        , \eta_s(dx) \right\rangle
-        ds
-        +
-        O\left( \frac{1}{\epsilon^d N^2} \right) .
-    \end{align*}
-\end{remark}
-
-\subsubsection{Identifying the limit}
-
-\paragraph{Continuity estimate}
-
-In this section we prove the following continuity estimate for $\rho_\epsilon * \eta_t(x)$.
-\begin{proposition} \label{ContinuityEstimate}
-Under the same conditions of Theorem~\ref{TeoremOneStepConvergence} we have that for all $x \in \IR^d$, $\delta>0$,
-\[
-\int |\rho_\epsilon*\eta_s(x) -\rho_\epsilon*\eta_s(y)| \rho_\delta(x-y) dy \]
-is bounded by
-\begin{align*}
-\frac{\delta}{\sqrt{\epsilon^2+s}} \langle 1,\eta_0(dz) \rangle &+ \int_0^s \frac{\delta}{\sqrt{\epsilon^2+s-r}} (\langle 1, \eta_r(dz)\rangle + \langle \rho_\epsilon*\eta_r(z), \eta_r(dz)\rangle)dr \\ &+ |M_s(x)| + \int |M_s(y)| \rho_\delta(y-x)dy + \mathcal{O}\left( \frac{1}{\epsilon^2 \theta}\right)
-\end{align*} 
-\end{proposition}
-where $M_s(x)$ is the martingale in (\ref{MartingaleProblemMolifier}).
-\begin{proof}
-Recall from our assumptions that $|F'(x)1_{x>0}|$ is uniformly bounded. Hence, we can always write,
-\begin{align} \label{StrongBoundOnF}
-|F(\rho_\epsilon*\eta_t(x))| \leq |F(0)| + C \rho_\epsilon*\eta_t(x)
+and note that under the assumption that $\epsilon^2\theta\to \infty$, for 
+each fixed $\delta>0$,  
+$\lim_{\epsilon\to 0, \theta\to\infty}
+\widehat{\epsilon}(\delta,\epsilon,\theta)=0$. 
+Using the semimartingale decomposition~(\ref{expn rhoepsilon}),
+and Lemmas~\ref{lem:poisson_ld} and~\ref{Lemma:BoundPsiHS2}
+we have
+\begin{align}
+& |\rho_\epsilon*\eta_s(y)-\rho_\epsilon*\eta_s(w)| \nonumber 
+= |\langle p_{\epsilon^2}(y,z)-p_{\epsilon^2}(w,z),\eta_s(dz) \rangle | 
+\nonumber
+\\ 
+&\leq 
+%\big\langle |\psi_t^{\epsilon,x}(z)-\psi_t^{\epsilon,y}(z)|, 
+\big\langle |p_{\epsilon^2+s}(y,z)-p_{\epsilon^2+s}(w,z)|, 
+\eta_0(dz)\big\rangle \nonumber 
+%\\
++\frac{C}{(\theta\epsilon^2)^{d/2}}\big\langle 
+p_{2(A+1)(\epsilon^2+s)}(y,z)+p_{2(A+1)(\epsilon^2+s)}(w,z), \eta_0(dz)
+\big\rangle
+\nonumber
+\\ 
+&+ \int_{s-\delta}^s \big\langle 
+|\psi_{s-r}^{\epsilon,y}(z) + \psi_{s-r}^{\epsilon, w}(z) |
+\cdot |F(\rho_\epsilon*\eta_r(z)|, 
+\eta_r(dz) \big\rangle  dr
+\nonumber
+\\
+&+
+\int_0^{s-\delta}
+\big\langle |p_{s-r+\epsilon^2}(y,z)-p_{s-r+\epsilon^2}(w,z)|, 
+\cdot |F(\rho_\epsilon*\eta_r(z)|, 
+\eta_r(dz) \big\rangle  dr
+\nonumber
+\\
+&+
+\frac{C}{(\epsilon^2\theta)^{d/2}}
+\int_0^{s-\delta}
+\big\langle |p_{2(A+1)(s-r+\epsilon^2)}(y,z)+
+p_{2(A+1)(s-r+\epsilon^2)}(w,z)|, 
+\cdot |F(\rho_\epsilon*\eta_r(z)|, 
+\eta_r(dz) \big\rangle  dr
+\nonumber
+\\
+&
++|M_s(y)|+|M_s(w)| 
++\mathcal{O}\big(\widehat{\epsilon}(\delta,\epsilon,\theta)
+\big)  
+\nonumber
+\\
+&
+\leq \Big\langle \frac{\|y-w\|}{\sqrt{s+\epsilon^2}}
+\big(p_{2(s+\epsilon^2}(y,z)+p_{2(s+\epsilon^2}(w,z)\big),\eta_0(dz)\Big\rangle
+\nonumber
+\\
+&+
+\int_0^{s-\delta}\Big\langle\frac{\|y-w\|}{\sqrt{s-r+\epsilon^2}}
+\big(p_{2(s-t+\epsilon^2}(y,z)+p_{2(s-r+\epsilon^2}(w,z)\big)
+\cdot |F(\rho_\epsilon*\eta_r(z)|, 
+\eta_r(dz)\Big\rangle dr
+\nonumber
+\\
+&
++\frac{C}{(\theta\epsilon^2)^{d/2}}\big\langle 
+p_{2(A+1)(\epsilon^2+s)}(y,z)+p_{2(A+1)(\epsilon^2+s)}(w,z), \eta_0(dz)
+\big\rangle
+\nonumber
+\\
+&+
+\frac{C}{(\epsilon^2\theta)^{d/2}}
+\int_0^{s-\delta}
+\big\langle |p_{2(A+1)(s-r+\epsilon^2)}(y,z)+
+p_{2(A+1)(s-r+\epsilon^2)}(w,z)|, 
+\cdot |F(\rho_\epsilon*\eta_r(z)|, 
+\eta_r(dz) \big\rangle  dr
+\nonumber
+\\
+&
++|M_s(y)|+|M_s(w)| 
++\mathcal{O}\big(\widehat{\epsilon}(\delta,\epsilon,\theta)
+\big) . 
+\label{difference in rhos}
+%\\ 
+%&+ C \int_0^t \langle |\psi_{t-s}^{\epsilon,x}(z) - \psi_{t-s}^{\epsilon, y}(z) | 
+%\rho_\epsilon*\eta(z), \eta_s(dz) \rangle  ds | 
+%\label{eq:bound1CE} 
 \end{align} 
-So, by (\ref{MartingaleProblemMolifier}) we can write,
-\begin{align}
-& |\rho_\epsilon*\eta_t(x)-\rho_\epsilon*\eta_t(y)| \nonumber \\ &= |\langle \rho_\epsilon(y-z)-\rho_\epsilon(x-z),\eta_t(dz) \rangle | \nonumber\\ &\leq  |M_t(x)-M_t(y)|  +\langle \psi_t^{\epsilon,y}(z)-\psi_t^{\epsilon,x}(z), \eta_0(dz)\rangle \nonumber \\ &+ C\int_0^t \langle |\psi_{t-s}^{\epsilon,x}(z) - \psi_{t-s}^{\epsilon, y}(z) |, \eta_s(dz) \rangle  ds | \\ &+ C \int_0^t \langle |\psi_{t-s}^{\epsilon,x}(z) - \psi_{t-s}^{\epsilon, y}(z) | \rho_\epsilon*\eta(z), \eta_s(dz) \rangle  ds | \label{eq:bound1CE} \end{align}
-By using Lemma~\ref{Lemma:BoundPsiHS2} we can then write, 
-\begin{align*}
- \int &|\rho_\epsilon*\eta_s(x) -\rho_\epsilon*\eta_s(y)| \rho_\delta(x-y) dy  \leq \int |p_{\epsilon^2+s}(y,z)-p_{\epsilon^2+s}(x,z)|\eta_0(dz) \rho_\delta(x-y)dy \\&+ C\int_0^s \langle p_{\epsilon^2+s-r}(y,z)-p_{\epsilon^2+s-r}(x,z)|, \eta_r(dz) \rangle \rho_\delta (x-y) dr  \\  & + C \int_0^s \langle |p_{\epsilon+s-r}(y,z) - p_{\epsilon+s-r}(x,z) | \rho_\epsilon*\eta_r(z), \eta_r(dz) \rangle  dr | + \int|M_s(y)-M_s(x)| \rho_\delta(y-x)dy  \\  & + \frac{C}{\epsilon^2 \theta} \int \langle \rho_\epsilon*\eta(z),\eta_s(dz)\rangle ds   +\mathcal{O}\left( \frac{1}{\epsilon^2 \theta} \right)
-\end{align*}
-By Remark~\ref{remark:BoundedIntegral} the last integral term is of order $(\epsilon^2 \theta)^{-1}$.
-By using Lemma~\ref{Lemma:ContinuityHS} we get that the contribution of the first three terms is bounded by,
-\begin{align*}
-\int &\frac{|y-x|}{\sqrt{\epsilon^2+s}} \rho_{\delta}(y-x) dy \langle 1, \eta_0(dz)\rangle + \int \int_0^s  \langle \frac{|y-x|}{\sqrt{\sqrt{\epsilon^2+s-r}}}, \eta_r(dz) \rangle \rho_\delta(x-y) dy dr \\ & +  \int \int_0^s \langle \frac{|y-x| \rho_\epsilon*\eta(z)}{\sqrt{\epsilon^2+s-r}}, \eta_r(dz) \rangle \rho_\delta(y-x) dy dr \\ & \leq \frac{\delta}{\sqrt{\epsilon^2+s}} \langle 1, \eta_0(dz) \rangle + \int_0^s \frac{\delta}{\sqrt{\epsilon^2+s-r}} (\langle 1, \eta_r(dz) \rangle + \langle \rho_\epsilon*\eta_r(z), \eta_r(dz) \rangle) dr.
-\end{align*}
-To finish the proof just notice that,
-\begin{align*}
-\int |M_s(y)-M_s(x)| \rho_\delta(y-x)dy \leq |M_s(x)| + \int |M_s(y)| \rho_\delta(y-x)dy.
-\end{align*}
-\end{proof}
-
-\paragraph{Identifying the limit of $\langle T_{\epsilon^2} f(y), \eta_t (dy) \rangle$.}
-We now prove the identification of the limit.
-We recall that, the main difficulty, is the non-linear term of the martingale problem.
-To deal with them, our first step would prove that an approximation of the form:
-\begin{align*}
-\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\eta_s(dy)), \eta_s(dy) \rangle \sim \langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \eta_s(dy)), \rho_\epsilon * \eta_s(y) dy \rangle
-\end{align*}
-This is the content of the next result.
+%Recalling that $F$ is a polynomial, and 
+%using Lemma~\ref{Lemma:BoundPsiHS2} we can then write, 
+%\begin{align*}
+% \int &|\rho_\epsilon*\eta_s(x) -\rho_\epsilon*\eta_s(y)| \rho_\delta(x-y) dy  
+%\leq 
+%\int |p_{\epsilon^2+s}(y,z)-p_{\epsilon^2+s}(x,z)|\eta_0(dz) \rho_\delta(x-y)dy 
+%\\
+%&+ 
+%C\int_0^s \langle p_{\epsilon^2+s-r}(y,z)-p_{\epsilon^2+s-r}(x,z)|, \eta_r(dz) \rangle 
+%\rho_\delta (x-y) dr  
+%\\  
+%& + C \int\int_0^s \langle |p_{\epsilon^2+s-r}(y,z) - p_{\epsilon^2+s-r}(x,z) | 
+%\sum_{k=0}^na_k\rho_\epsilon*\eta_r(z)^k, \eta_r(dz) \rangle  dr\rho_\delta(y-x)dy    
+%\\ & + \int|M_s(y)-M_s(x)| \rho_\delta(y-x)dy  
+%\\  & 
+%+ \frac{C}{\epsilon^2 \theta} \int \langle \sum_{k=0}^na_k\rho_\epsilon*\eta(z)^k,
+%\eta_s(dz)\rangle ds   
+%+\mathcal{O}\left( \frac{1}{\epsilon^2 \theta} \right), 
+%\end{align*}
+%for some non-negative constants $a_k$.
+%By Lemma~\ref{} the last integral term is of 
+%order $(\epsilon^2 \theta)^{-1}$. 
+%Using Lemma~\ref{Lemma:ContinuityHS}, the contribution of the first 
+%three terms is bounded by,
+%\begin{align*}
+%\int &\langle \frac{|y-x|}{\sqrt{\epsilon^2+s}}
+%\Big(p_{2(\epsilon^2+s)}(x,z) +p_{2(\epsilon^2+s)}(y,z)\Big) 
+%\rho_{\delta}(y-x) dy, \eta_0(dz)\rangle 
+%\\
+%& + \int \int_0^s  
+%\langle \frac{\|y-x\|}{\sqrt{\epsilon^2+s-r}} 
+%\Big(p_{2(\epsilon^2+s-r)}(x,z) +p_{2(\epsilon^2+s-r)}(y,z)\Big) 
+%\rho_\delta(x-y) dy 
+%\sum_{k=0}^n\rho_\epsilon*\eta_r(z)^k, \eta_r(dz) dr 
+%\\ 
+%& +  \int \int_0^s \langle \frac{|y-x| \rho_\epsilon*\eta(z)}{\sqrt{\epsilon^2+s-r}}, \eta_r(dz) \rangle \rho_\delta(y-x) dy dr \\ 
+%& \leq 
+%\frac{\delta}{\sqrt{\epsilon^2+s}} %\langle 1, \eta_0(dz) \rangle 
+%+ \int_0^s \frac{\delta}{\sqrt{\epsilon^2+s-r}} 
+%\Big(p_{2(\epsilon^2+s-r)}(x,z) +p_{2(\epsilon^2+s-r+\delta)}(y,z)\Big) 
+%\sum_{k=0}^n a_k\rho_\epsilon*\eta_r(z)^k,
+%\eta_r(dz) \rangle dr.
+%\end{align*}
+%To finish the proof just notice that,
+%\begin{align*}
+%\int |M_s(y)-M_s(x)| \rho_\delta(y-x)dy \leq |M_s(x)| + \int |M_s(y)| \rho_\delta(y-x)dy.
+%\end{align*}
+%\end{proof}
+%
+
+Although this expression is lengthy, when we need to control its 
+contribution to expressions below, it will really just be a matter of
+applying the tower property and our moment bounds from 
+Lemma~\ref{bounds on moments} and 
+Corollary~\ref{alternative form moment bounds}.
+
 \begin{proposition} \label{CuadraticApprox}
-Under the condition of Theorem~\ref{TeoremOneStepConvergence} there is a constant $C>0$ such that
-\begin{equation*}
-\int_0^t \IE[|\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\eta_s(dy)), \eta_s(dy) \rangle - \langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \eta_s(dy)), \rho_\epsilon * \eta_s(y) dy \rangle|]
-\end{equation*}
-is bounded by,
-\begin{equation*}
-\mathcal{O}\left( \frac{1}{\epsilon^2 \theta} + \epsilon^2 + \epsilon + \epsilon^{1/3}  + \left( \frac{\theta}{N \epsilon^d} \right)^{1/2}\right)
-\end{equation*}
+Under the conditions of Theorem~\ref{thm:local_convergence},
+\begin{equation}
+\label{replacing nonlinear term}
+\lim_{N\to\infty}\Big|\int_0^t \IE\Big[\big\langle T_{\epsilon^2} f(y) 
+F(\rho_\epsilon *\eta_s(y)), \eta_s(y) \big\rangle 
+- \big\langle T_{\epsilon^2} f(y) 
+F(\rho_\epsilon * \eta_s(y)), \rho_\epsilon * \eta_s(y) dy 
+\big\rangle\Big]ds \Big|
+=0.
+\end{equation}
+%is of order
+%\comment{Equation below needs to be filled in when we have the proof}
+%\begin{equation*}
+%\mathcal{O}\left( \frac{1}{\epsilon^2 \theta} + \epsilon^2 + \epsilon + \epsilon^{1/3}  + \left( \frac{\theta}{N \epsilon^d} \right)^{1/2}\right)
+%\end{equation*}
 \end{proposition}
 \begin{proof}
+In fact we are going to fix $\delta>0$, and show that
+the expression on the left hand side of~\eqref{replacing nonlinear term} is
+less than a constant times $\delta$, with a constant independent of $\delta$
+and $N$. Since $\delta$ is arbitrary, the result will follow.
+
 We first note that,
 \begin{align*}
-    &\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\eta_s(dy)), \eta_s(dy) \rangle - \langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \eta_s(dy)), \rho_\epsilon * \eta_s(y) dy \rangle \\ & = \langle \int T_{\epsilon^2} f(y) F(\rho_\epsilon * \eta_s(y))\rho_\epsilon(y-w) dy, \eta_s(dw)\rangle - \langle T_{\epsilon^2} f(w) F(\rho_\epsilon*\eta_s(w)), \eta_s(dw) \rangle \\ &= \langle \int \{ T_{\epsilon^2} f(y) F(\rho_\epsilon*\eta_s(y))-T_{\epsilon^2}f(w) F(\rho_\epsilon*\eta_s(w))\} \rho_\epsilon(w-y)dy, \eta_s(dw) \rangle.
+    &
+\langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \eta_s(y)), 
+\rho_\epsilon * \eta_s(y) dy \rangle 
+-\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\eta_s(dy)), \eta_s(dy) \rangle 
+\\ 
+& = 
+\langle \int T_{\epsilon^2} f(y) 
+F(\rho_\epsilon * \eta_s(y))\rho_\epsilon(y-w) dy, \eta_s(dw)\rangle - \langle 
+T_{\epsilon^2} f(w) F(\rho_\epsilon*\eta_s(w)), \eta_s(dw) \rangle 
+\\ 
+&= 
+\langle \int \big\{ T_{\epsilon^2} f(y) F(\rho_\epsilon*\eta_s(y))-T_{\epsilon^2}f(w) 
+F(\rho_\epsilon*\eta_s(w))\big\} 
+\rho_\epsilon(w-y)dy, \eta_s(dw) \rangle.
 \end{align*}
-Let us denote $I$ the integral against $dy$ in the last expresion, that is 
-\[ I :=  \int \{ T_{\epsilon^2} f(y) F(\rho_\epsilon*\eta_s(y))-T_{\epsilon^2}f(w) F(\rho_\epsilon*\eta_s(w))\} \rho_\epsilon(w-y)dy \]
-And note that $|I|$ is bounded by
+Let us denote the integral against $dy$ in the last expression by $I$, that is 
+\[ I :=  \int \{ T_{\epsilon^2} f(y) 
+F(\rho_\epsilon*\eta_s(y))-T_{\epsilon^2}f(w) 
+F(\rho_\epsilon*\eta_s(w))\} \rho_\epsilon(w-y)dy, \]
+and note that $|I|$ is bounded by
 \begin{align}
-& \int \left\{ |F(\rho_\epsilon*\eta_s(y))-F(\rho_\epsilon*\eta_s(w))|T_{\epsilon^2}f(y)+F(\rho_\epsilon*\eta_s(w))|T_{\epsilon^2}f(y)-T_{\epsilon^2}f(w))|\right\} \rho_{\epsilon}(w-y)dy \nonumber \\ &\leq \int C |\rho_\epsilon*\eta_s(y)-\rho_\epsilon*\eta_s(w)| \rho_\epsilon(w-y)dy + C \epsilon^2 \Vert \Delta f \Vert_2 \label{FirstBoundCT}
+& \int 
+\Big\{ |F(\rho_\epsilon*\eta_s(y))-F(\rho_\epsilon*\eta_s(w))|T_{\epsilon^2}f(y)+
+F(\rho_\epsilon*\eta_s(w))|T_{\epsilon^2}f(y)-T_{\epsilon^2}f(w))|\Big\} 
+\rho_{\epsilon}(w-y)dy
+\nonumber \\ &\leq \int \| f\|_{\infty} 
+\big|F(\rho_\epsilon*\eta_s(y))-F(\rho_\epsilon*\eta_s(w))\big| \rho_\epsilon(w-y)dy + 
+C \epsilon\|f' \|_\infty |F(\rho_\epsilon*\eta_s(w))|, \label{FirstBoundCT}
 \end{align}
-where in the last inequality we have used $F(x)1_{x>0}$ and $|F'(x)1_{x>0}|$ are both bounded above.
-We want to use Proposition~\ref{ContinuityEstimate} in the last equation, but the terms that we would obtain would be too hard to control unless we first control the total mass and their noise.
-Let us define,
-\begin{align*}
-A_{t} &:= \left\{ \sup_{0 \leq s \leq t} \langle 1, \eta_s(dz) \rangle > \epsilon^{-2/3} \right\}. \end{align*}
-Note that, by Markov's inequality and Lemma~\ref{Lemma:UniformlyBoundedMass} the event $A_{t}$ has probability of order $\epsilon^{2/3}$.
-Hence, writing $I = I(1_{A^c_{t}} + 1_{A_{t}})$ and proceeding as before we can use Proposition~\ref{ContinuityEstimate} in (\ref{FirstBoundCT}) to get,
-\begin{align}
-&\int_0^t \IE[|\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\eta_s(dy)), \eta_s(dy) \rangle - \langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \eta_s(dy)), \rho_\epsilon * \eta_s(y) dy \rangle|] \nonumber \\ &\leq   \int_0^t \IE[ \frac{\epsilon}{\sqrt{\epsilon^2 + s}} \langle 1,\eta_0(dz) \rangle \langle 1, \eta_s(dz)\rangle ] ds +  \int_0^t \IE[  \int_0^s \frac{\epsilon}{\sqrt{\epsilon^2 + s - r}} \langle 1, \eta_r (dz) \rangle dr \langle 1, \eta_s(dz) \rangle  ] ds \nonumber\\ & + \int_0^t \IE[   1_{A^c_{t}} \int_0^s \frac{\epsilon}{\sqrt{\epsilon^2 + s - r}} \langle \rho_\epsilon*\eta_r(z), \eta_r(dz) \rangle dr \langle 1, \eta_s(dz) \rangle  ] ds + \int_0^t \IE[\langle |M_s(x)|,\eta_s(dx) \rangle] ds \nonumber \\ &+ \int_0^t \int \IE[|M_s(y)|\rho_\epsilon*\eta_s(y)] dy ds  +\mathcal{O}\left( \frac{1}{\epsilon^2 \theta} + \epsilon^2 + \epsilon^{1/3} \right)  \label{ThingsToBound}
-\end{align}
-Note we have bounded $1_{A^c_{t}}$ by one in all the terms expect the third one, which is the one that will require it.
-For the first two term we can use our hypothesis on the initial condition and that $2 ab \leq a^2+b^2$ to get that their contribution is bounded by,
-\begin{align*}
-\int_0^t C \frac{\epsilon}{\sqrt{\epsilon^2+s}}\IE[\langle 1, \eta_s(dz) \rangle] ds + \int_0^t \int_0^s \frac{\epsilon}{\sqrt{\epsilon^2+s-r}}\IE[\langle 1, \eta_r(dz)\rangle^2 + \langle 1, \eta_s(dz)\rangle^2] ds,
-\end{align*}
-which, due to Lemma~\ref{lem:SecondMomentMass}, is of order $\epsilon$. To bound the third integral term we use the event $A_{t}$ to get it is bounded by,
-\begin{align*}
-\int_0^t \int_0^s \frac{\epsilon^{1/3}}{\sqrt{\epsilon^2+s-r}} \IE[ \langle \rho*\eta_r(z), \eta(dz) \rangle] dr ds = \mathcal{O}(\epsilon^{1/3})
-\end{align*}
-where we have used Remark~\ref{remark:BoundedIntegral}. 
-We now proceed to control the terms with martingales in (\ref{ThingsToBound}). For the first one note that, by using Cauchy-Schwartz in $L^2(\mathbb{P})$ and then in $L^2(\IR^d)$,
-\begin{align}
-\int_0^t \int \IE[|M_s(y)|\rho_\epsilon*\eta_s(y)] dy ds & \leq \int_0^t \int \IE[|M^2_s(y)]^{1/2} \IE[\rho_\epsilon * \eta_s(y)^2]^{1/2} dy dy \nonumber \\ & \leq \int_0^t \left( \int \IE[|M_s(y)^2|] dy \int \IE[\rho_\epsilon * \eta_s(y)^2] dy \right)^{1/2} ds  \nonumber \\ &= \mathcal{O}\left( \left( \frac{\theta}{N \epsilon^d} \right)^{1/2} \right)
-\label{TwiceCS} \end{align}
-where in the last inequality we used Proposition~\ref{IntegrabilityOfM} and Remark~\ref{remark:BoundedIntegral}.
-For the second term with a Martingale in (\ref{ThingsToBound}) we need to proceed with more care.
-For this we first rewrite explicitly the dependency on $\epsilon$ of $M_t(x)$ by using $M_t^{\varepsilon^2}(x)$.
-We can then write from (\ref{MartingaleProblemMolifier}) and Lemma~\ref{Lemma:BoundPsiHS2}) that,
-\begin{align*}
- M_t^{\epsilon^2}(x) &= \langle p_{\epsilon^2}(x,y), \eta_t(dx) \rangle - \langle p_{t + \epsilon^2}(x,y), \eta_0(dx) \rangle \\ &- \int_0^t \langle F(\rho_\epsilon*\eta_s(y)) p_{t-s+\epsilon^2}(x,y), \eta_s(dy) \rangle ds + \mathcal{O}\left(\frac{1}{\epsilon^2 \theta} \right) \end{align*}
- It follows then that $M_s^{\epsilon^2}= p_{\epsilon^2/2}*M_s^{\epsilon^2/2} + \mathcal{O}\left(1/\epsilon^2 \theta\right)$. Using this we can then bound,
- \begin{align*}
-\int_0^t &\IE[ \langle |M_s^{\epsilon^2}(x)|, \eta_s(dx) \rangle ] ds \\ &= \int_0^t \IE[ \langle | p_{\epsilon^2/2}*M_s^{\epsilon^2/2}(x)|, \eta_s(dx) \rangle] ds \\ & \leq  \int_0^t \IE[ \langle p_{\epsilon^2/2}*| M_s^{\epsilon^2/2}(x)|, \eta_s(dx) \rangle] ds \\ &= \int_0^t \IE[ \langle \int p_{\epsilon^2/2}(x,y) |M_s^{\epsilon^2/2}(y)|dy, \eta_s(dx) \rangle] ds \\ &= \int_0^t \IE[ \int |M_s^{\epsilon^2/2}(y)| p_{\epsilon^2/2}*\eta_s(y) dy ] ds \\ &= \int_0^t \int \IE[ M_s^{\epsilon^2/2}(y)| p_{\epsilon^2/2} * \eta_s(dy)] dy ds
- \end{align*}
- An analogues computation as the one performed to obatin (\ref{TwiceCS}) gives the last term is $\mathcal{O}\left( \left( \frac{\theta}{N \epsilon^d} \right)^{1/2} \right)$.
+where we have used that 
+\[
+\int |T_{\epsilon^2}f(y)-T_{\epsilon^2}f(w)| p_{\epsilon^2}(w,y)dy
+\leq \|f'\|_\infty\int|y-w|p_{\epsilon^2}(w,y)dy.
+\]
+Now recall that $F$ is a polynomial of degree $n$, and so 
+there exist real numbers $b_k$ such
+that $F(a)-F(b)= (a-b)\sum_{k=1}^{n-1}b_kx^ky^{n-1-k}$ and so 
+\[
+|F(\rho_\epsilon*\eta_s(y))-F(\rho_\epsilon*\eta_s(w))|
+\leq 
+|\rho_\epsilon*\eta_s(y)-\rho_\epsilon*\eta_s(w)|
+\sum_{k=1}^{n-1}|b_k|\left(\rho_\epsilon*\eta_s(y)^k+\rho_\epsilon*\eta_s(w)^k\right).
+\]
+
+Combining the above, we have reduced the problem to showing that 
+\begin{equation}
+\label{target expression}
+\int_0^t\big\langle \int |\rho_\epsilon*\eta_s(y)-\rho_\epsilon*\eta_s(w)|
+\left(\rho_\epsilon*\eta_s(y))^k+\rho_\epsilon*\eta_s(w)^k\right)
+p_{\epsilon^2}(w,y)dy, \eta_s(dw)\big\rangle ds
+\end{equation}
+goes to zero as $\epsilon\to 0$.
+
+We are going to use the estimate~(\ref{difference in rhos}).
+First note that by Lemma~\ref{bounds on moments}
+the contribution to~(\ref{target expression}) from the integral over
+the time interval $[0,\delta]$ is ${\mathcal O}(\delta)$. We focus instead
+on the interval $(\delta, t]$.
+
+The first term in~(\ref{difference in rhos}) gives
+\begin{multline*}
+\int_\delta^t\IE\Big[\big\langle\frac{\|y-w\|}{\sqrt{s+\epsilon^2}}
+\big(p_{2(s+\epsilon^2)}(y,z)+p_{2(s+\epsilon^2)}(w,z)\big),\eta_o(dz)\big\rangle
+\\
+\big(\rho_\epsilon*\eta_s(y)^k+\rho_\epsilon*\eta_s(w)^k\big)
+p_{\epsilon^2}(w,y)dy, \eta_s(dw)\big\rangle\Big] ds.
+\end{multline*}
+We ``borrow'' from the exponential term in $p_\epsilon^2(w,y)$ to bound
+this by
+\begin{multline}
+C\int_\delta^t\frac{\epsilon}{\sqrt{s+\epsilon^2}}
+\IE\Big[\big\langle
+\big(p_{2(s+\epsilon^2)}(y,z)+p_{2(s+\epsilon^2)}(w,z)\big),\eta_0(dz)
+\big\rangle
+\\
+\big(\rho_\epsilon*\eta_s(y)^k+\rho_\epsilon*\eta_s(w)^k\big)
+p_{2\epsilon^2}(w,y)dy, \eta_s(dw)\big\rangle ds\Big] .
+\label{contribution from initial condition terms}
+\end{multline}
+The four terms in the product are taken separately, according to the
+combinations of $w$ and $y$ appearing. First,
+\[
+\int_\delta^t\frac{\epsilon}{\sqrt{s+\epsilon^2}}
+\IE\Big[\big\langle
+p_{2(s+\epsilon^2)}(y,z)   %+p_{2(s+\epsilon^2)}(w,z)\big)
+,\eta_0(dz)
+\big\rangle
+\rho_\epsilon*\eta_s(y)^k %+\rho_\epsilon*\eta_s(w)^k\big)
+p_{2\epsilon^2}(w,y)dy, \eta_s(dw)\big\rangle  \Big] ds
+\]
+can be rewritten as
+\begin{multline*}
+\int_\delta^t\frac{\epsilon}{\sqrt{s+\epsilon^2}}
+\IE\Big[\big\langle
+p_{2(s+\epsilon^2)}(y,z)   %+p_{2(s+\epsilon^2)}(w,z)\big)
+,\eta_0(dz)
+\big\rangle
+\rho_\epsilon*\eta_s(y)^k %+\rho_\epsilon*\eta_s(w)^k\big)
+p_{\epsilon^2}(x,y)dy \rho_\epsilon*\eta_s(x) dy dx ds\big\rangle ds \Big]
+\\
+\leq
+\int_\delta^t\frac{\epsilon}{\sqrt{s+\epsilon^2}}
+\IE\Big[\big\langle
+p_{2(s+\epsilon^2)}(y,z)   %+p_{2(s+\epsilon^2)}(w,z)\big)
+,\eta_0(dz)
+\big\rangle
+\big(\rho_\epsilon*\eta_s(y)^{k+1} +\rho_\epsilon*\eta_s(x)^{k+1}\big)\Big]
+p_{\epsilon^2}(x,y) dy dx \big\rangle ds,
+\end{multline*}
+and using Lemma~\ref{bounds on moments} and the tower property, and integrating
+with respect to $s$, under our assumptions on $\eta_0$,
+this is 
+bounded by
+\begin{multline*}
+C\epsilon \int_\delta^t\frac{1}{\sqrt{s+\epsilon^2}}
+\IE\Big[\big\langle
+p_{2(s+\epsilon^2)}(y,z)   %+p_{2(s+\epsilon^2)}(w,z)\big)
+,\eta_0(dz)
+\big\rangle
+\\
+\big(\rho_\epsilon*\eta_0(y)+\rho_\epsilon*\eta_0(y)^{k+1} 
++\rho_\epsilon*\eta_0(x)+
++\rho_\epsilon*\eta_0(x)^{k+1}\big)\Big]
+p_{\epsilon^2}(x,y) dy dx ds 
+={\mathcal O}(\epsilon).
+\end{multline*}
+The term involving 
+$ %\[
+\big\langle
+p_{2(s+\epsilon^2)}(w,z)   %+p_{2(s+\epsilon^2)}(w,z)\big)
+,\eta_0(dz)
+\big\rangle
+\rho_\epsilon*\eta_s(w)^k
+$ %\]
+is handled similarly.
+
+On the other hand
+\begin{multline*}
+\big\langle\langle p_{2(s+\epsilon^2)}(y,z), \eta_0(dz)\rangle
+\rho_\epsilon*\eta_s(w)^kp_{2\epsilon^2}(w,y)dy, \eta_s(dw)\big\rangle
+\\
+\leq \frac{C}{(s+\epsilon^2)^{d/2}}\langle 1,\eta_0\rangle\big\langle
+\rho_\epsilon*\eta_s(w)^k,\eta_s(dw)\big\rangle,
+\end{multline*}
+and since $\langle 1,\eta_0\rangle$ is uniformly bounded we apply 
+Corollary~\ref{alternative form moment bounds} to obtain a bound on
+the contribution to~(\ref{contribution from initial condition terms})
+from this term of the form $C\epsilon/\delta^{(d+1)/2}$.
+Note that for fixed $\delta$, this bound tends to zero as $\epsilon\to 0$.
+
+Now consider
+\begin{multline*}
+\int_\delta^t\int_0^{s-\delta}\Big\langle\frac{\|y-x\|}{\sqrt{s-r+\epsilon^2}}
+\big\langle\big(p_{2(s-r+\epsilon^2)}(y,z)+ p_{2(s-r+\epsilon^2)}(w,z)\big)
+\rho_\epsilon*\eta_r(z)^j,\eta_r(dz)\big\rangle dr
+\\
+\rho_\epsilon*\eta_s(y)^kp_{\epsilon^2}(y,w),\eta_s(dw)
+\Big\rangle ds
+\\
+\leq C\epsilon
+\int_\delta^t\int_0^{s-\delta}\Big\langle\frac{1}{\sqrt{s-r+\epsilon^2}}
+\big\langle
+\big(p_{2(s-r+\epsilon^2)}(y,z)+ p_{2(s-r+\epsilon^2)}(w,z)\big)
+\rho_\epsilon*\eta_r(z)^j,\eta_r(dz)\big\rangle dr
+\\
+\rho_\epsilon*\eta_s(y)^kp_{2\epsilon^2}(y,w),\eta_s(dw)
+\Big\rangle ds,
+\end{multline*}
+where as usual we have ``borrowed'' from the exponential term in
+$p_\epsilon^2(y,w)$ to replace $\|y-w\|$ by a constant times $\epsilon$.
+
+Once again, our approach is to rearrange terms so that we can apply
+Lemma~\ref{bounds on moments}
+or 
+Corollary~\ref{alternative form moment bounds} to obtain a bound on
+the contribution to~(\ref{target expression})
+from these terms of the form $C\epsilon$ (where $C$ may depend on $\delta$
+but not $\epsilon$).
+
+For example, using the Chapman-Kolmogorov equation to rewrite
+\[
+\int\Big\langle 
+\big\langle p_{2(s-r+\epsilon^2}(y,z)\rho_\epsilon*\eta_r(z)^j, \eta_r(dz)
+\big\rangle
+\rho_\epsilon*\eta_s(y)^k p_{2\epsilon^2}(y,w), \eta_s(dw)\Big\rangle dy
+\]
+as 
+\[
+\int\int
+\big\langle p_{2(s-r+\epsilon^2}(y,z)\rho_\epsilon*\eta_r(z)^j, \eta_r(dz)
+\big\rangle
+\rho_\epsilon*\eta_s(y)^k p_{\epsilon^2}(y,x)\rho_\epsilon*\eta_s(x) dx dy,
+\]
+and using Lemma~\ref{bounds on moments} and the tower property, we are led to 
+control terms of the form
+\[
+\IE\Big[\int\big\langle p_{2(s-r+\epsilon^2)}(y,z)\rho_\epsilon*\eta_r(z)^j, 
+\eta_r(dz)\big\rangle \rho_\epsilon*\eta_r(y)^{k+1} dy\Big].
+\]
+This, in turn, is at most
+\begin{multline*}
+\IE\Big[\big\langle \rho_\epsilon*\eta_r(z)^{j+k+1}, \eta_r(dz)\rangle\Big]
++\IE\Big[\int p_{2(s-r)}(y,x)\rho_\epsilon*\eta_r(x)\rho_\epsilon*\eta_r(y)^{k+1} dy dx\Big]
+\\
+\leq
+\IE\Big[\big\langle \rho_\epsilon*\eta_r(z)^{j+k+1}, \eta_r(dz)\rangle\Big]
++2\int\IE\Big[\rho_\epsilon*\eta_r(x)^{k+2}\Big]dx,
+\end{multline*} 
+which is bounded by Lemma~\ref{bounds on moments}.
+
+It remains to control the contribution arising from the martingale terms 
+in~(\ref{difference in rhos}):
+\[
+\IE\Big[
+\int_\delta^t\Big\langle\int 
+\big(|M_s(y)|+|M_s(w)|\big)\big(\rho_\epsilon*\eta_s(y)^k+
+\rho_\epsilon*\eta_s(w)^k\big)p_{\epsilon^2}(w,y)dy, \eta_s(dw)\Big\rangle ds
+\Big] .
+\]
+To deal with the two terms in the produce involving $|M_s(y)|$, we write 
+the first as $\int |M_s(y)|\rho_\epsilon*\eta_s(y)^{k+1}dy$ and then use
+H\"older's inequality, Lemma~\ref{bounds on moments}, and the fact
+that $\IE\big[|M_s(y)|^2\big]$ is ${\mathcal O}\big(\theta/(N\epsilon^d)\big)$
+to see that the contribution from this term tends to zero in the limit.
+For the second, we use the idea of the proof of 
+Corollary~\ref{alternative form moment bounds} to reduce to a form to which
+we can apply H\"older's inequality.
+
+\comment{Probably should put a bit more detail in here?}
+
+The other terms follow in a similar way.
+
+Combining the above, we see that given $\delta>0$, 
+\[
+\lim_{\epsilon\to 0}\Big|\int_0^t \IE\Big[\big\langle T_{\epsilon^2} f(y) 
+F(\rho_\epsilon *\eta_s(y)), \eta_s(y) \big\rangle 
+- \big\langle T_{\epsilon^2} f(y) 
+F(\rho_\epsilon * \eta_s(y)), \rho_\epsilon * \eta_s(y) dy 
+\big\rangle\Big]ds\Big|
+<C\delta,
+\]
+where the constant $C$ is independent of $\delta$.
+Since $\delta$ was arbitrary, the proof is complete.
 \end{proof}
-Now, to finish the characterisation of the limit, it remain to show that:
-\[ \int f(x) \rho_\epsilon * \eta_t(x) F(\rho_\epsilon * \eta_t(x)) dx \rightarrow \int f(x) u_t(x) F(u_t(x)) dx \]
-where $u_t(x)dx$ is the limit of $\rho_\epsilon*\eta_t(x)dx$.
-As we mention as the start of this note this does now follow from weak convergence of $\rho_\epsilon*\eta(x)dx$.
-For proving this, we recall that $F(x)$ is a polynomial, so we just need to prove said convergence of powers of $(\rho_\epsilon*\eta_t(x))$.
-To illustrate how to proceed, we will prove the convergence,
-\begin{equation} \label{eq:QuadConvergence} \int f(x) \rho_\epsilon * \eta_t(x) \rho_\epsilon * \eta_t(x)^2 dx \rightarrow \int f(x) u_t(x) u_t(x)^2 dx \end{equation}
-with the understanding that converge of higher powers will follows in a similar fashion with rougher notation. To achieve (\ref{eq:QuadConvergence}) we proceed by proving an approximation of the form,
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+To complete the characterisation of the limit, it remains to show that if we
+take a convergent subsequence 
+$\big\{\big(\rho_\epsilon*\eta_t(dx)\big)_{t\geq 0}\big\}$ 
+converging to a limit point $\big(u_t(x)dx\big)_{t\geq 0}$, then
+\[ 
+\int f(x) \rho_\epsilon * \eta_t(x) F(\rho_\epsilon * \eta_t(x)) dx 
+\rightarrow \int f(x) u_t(x) F(u_t(x)) dx. 
+\]
+Since $F$ is a polynomial, we consider powers of $\rho_\epsilon*\eta$.
+To illustrate the approach, we first prove that
+\begin{equation} 
+\label{eq:QuadConvergence} 
+\int f(x) \rho_\epsilon * \eta_t(x) \rho_\epsilon * \eta_t(x)^2 dx 
+\rightarrow \int f(x) u_t(x) u_t(x)^2 dx. 
+\end{equation}
+The converge of higher powers will follow in an entirely analogous manner, but
+with more complex expressions.
+
+The approach is standard. We fix $\delta>0$ and in keeping with
+our notation $\rho_\epsilon$ in this subsection, use $\rho_\delta$ to 
+denote the symmetric Gaussian kernel with variance parameter $\delta^2$.
+Our strategy is to show that, up to an error of $\mathcal{O}(\delta)$,
 \begin{equation}
 \label{aprox2}
-\langle f, (\eta_s * \rho_\epsilon)^2 \rangle \sim \int \int f(z) (\rho_\epsilon * \eta_s)(z) \rho_\delta (z-y) (\rho_\epsilon * \eta_s)(y) dz dy.
-\end{equation}
-Before proceeding with a proof of (\ref{aprox2}), we argue why this is enough to conclude Theorem~\ref{TeoremOneStepConvergence}. Note the right hand side of (\ref{aprox2}) can written as
-\[ \int_{\IR^{d} \otimes \IR^d} f(z) \rho_\delta(z-y) (\rho_\epsilon * \eta_s(dz) \otimes (\rho_\epsilon * \eta_s(dy)). \]
-Weak convergence of $\rho_\epsilon * \eta$ (plus continuity of the mapping $(z,y) \rightarrow f(z) \rho_\delta(z-y)$) gives that the last term converges in $L^1$ to
-\[ \int_{\IR^{d} \otimes \IR^d} f(z) \rho_\delta(z-y) (u_s(dz) \otimes (u_s(dy)). \]
-Finally, by a direct analogue of (\ref{aprox2}) we can say that
-\begin{equation} \int_{\IR^{d} \otimes \IR^d} f(z) \rho_\delta(z-y) (u_s(dz) \otimes (u_s(dy)) \sim \langle f(x), u_s^2(x) dx \rangle. \label{aprox3} \end{equation}
-which is what we seek. We proceed now to prove (\ref{aprox2}), with the understanding that (\ref{aprox3}) follows in a similar way and give even better error terms.
+\int f(z) \rho_\epsilon*\eta_s(z)^2 dz
+%(\eta_s * \rho_\epsilon)^2 \rangle 
+\sim 
+\int \int f(z) (\rho_\epsilon * \eta_s)(z) 
+\rho_\delta (z-y) (\rho_\epsilon * \eta_s)(y) dz dy.
+\end{equation}
+Analogously, also up to an error of $\mathcal{O}(\delta)$,
+\begin{equation}
+\label{aprox3}
+\int f(z) u_s(z)^2 dz
+%(\eta_s * \rho_\epsilon)^2 \rangle 
+\sim 
+\int \int f(z) u_s(z) 
+\rho_\delta (z-y) u_s(y) dz dy.
+\end{equation}
+On the other hand,
+weak convergence of $\rho_\epsilon * \eta$ 
+(plus continuity of the mapping $(z,y) \rightarrow f(z) \rho_\delta(z-y)$) 
+gives that 
+\begin{equation}
+\int \int f(z) (\rho_\epsilon * \eta_s)(z) 
+\rho_\delta (z-y) (\rho_\epsilon * \eta_s)(y) dz dy
+\to \int \int f(z) u_s(z) 
+\rho_\delta (z-y) u_s(y) dz dy.
+\end{equation}
+Since $\delta$ is arbitrary, the 
+convergence~(\ref{eq:QuadConvergence})
+will follow.
+
+UP TO HERE
+
 \begin{theorem}
@@
 \begin{align}
-&\int_0^t \mathbb{E}\left[| \langle f(y), (\eta_s * \rho_\epsilon(y))^2) dy \rangle - \int \int f(y) (\rho_\epsilon * \eta_s)(z) \rho_\delta (z-y) (\rho_\epsilon * \eta_s)(y) dz dy.
-|\right] ds \nonumber \\ &\leq  \Vert f \Vert_\infty \int_{S_f}  \int_0^t  \mathbb{E}\left[ \int \left\{ \left|(\rho_\epsilon * \eta_s)(y)-(\rho_\epsilon * \eta_s)(z) \right|   \rho_\delta(z-y) dz \right\} (\rho_\epsilon *\eta_s)(y) \right] ds  dy \label{b1}
+&\int_0^t 
+\mathbb{E}\left[| \langle f(y), (\eta_s * \rho_\epsilon(y))^2) dy \rangle 
+- \int \int f(y) (\rho_\epsilon * \eta_s)(z) \rho_\delta (z-y) 
+(\rho_\epsilon * \eta_s)(y) dz dy. |\right] ds 
+\nonumber 
+\\ 
+&\leq  
+\Vert f \Vert_\infty \int  \int_0^t  
+\mathbb{E}\left[ \int \left\{ \left|(\rho_\epsilon * \eta_s)(y)
+-(\rho_\epsilon * \eta_s)(z) \right|   \rho_\delta(z-y) dz \right\} 
+(\rho_\epsilon *\eta_s)(y) \right] ds  dy 
+\label{b1}
 \end{align}
-We want then to bound (\ref{b1}) by using Proposition~\ref{ContinuityEstimate}. For this consider the event,
-\[ B_{s,y} := \{ \rho_\epsilon * \eta_s(y) > \delta^{-2/3} \}. \]
-Note that by Markov's inequality and Lemma~\ref{FirstBoundLocalDensity} the event $B_{s,y}$ has probability of order $\delta^{2/3}$ (and independent of $s$ and $y$).
-Thus, proceeding as how get (\ref{ThingsToBound}), the integral against $ds$ in the right hand side of (\ref{b1}) is bounded by
-\begin{align}
-&\int_0^t \IE[ \frac{\delta}{\sqrt{\epsilon^2 + s}} \langle 1,\eta_0(dz) \rangle (\rho_\epsilon *\eta_s)(y) ] ds +  \int_0^t \IE[  \int_0^s \frac{\delta}{\sqrt{\epsilon^2 + s - r}} \langle 1, \eta_r (dz) \rangle dr(\rho_\epsilon *\eta_s)(y)  ] ds \nonumber\\ & + \int_0^t \IE[   1_{B^c_{s,\delta}} \int_0^s \frac{\delta}{\sqrt{\epsilon^2 + s - r}} \langle \rho_\epsilon*\eta_r(z), \eta_r(dz) \rangle dr (\rho_\epsilon *\eta_s)(y) ] ds + \int_0^t \IE[\langle |M_s(x)|,\eta_s(dx) \rangle] ds \nonumber \\ & + \int_0^t  \IE[|M_s(y)|\rho_{\epsilon+\delta}*\eta_s(y)] ds  +\mathcal{O}\left( \frac{1}{\epsilon^2 \theta} + \delta^{1/3} \right)  \label{ThingsToBound2}
-\end{align}
-From this point onward we can proceed as how we bounded (\ref{ThingsToBound}) in Proposition~\ref{CuadraticApprox} to obtain that the right hand side of (\ref{b1}) is bounded by,
-\[  \mathcal{O}\left(\delta^{1/3} + \delta+ \frac{1}{\epsilon^2 \theta} + \left( \frac{\theta}{N \epsilon^2}\right)^{1/2} \right)  \]
-Concluding the result.
 \end{proof}
@@
 \todo[inline]{END OneStepConvergence}
+
+\comment{I haven't turned the $\mu$ into $\mu_\theta$ below this point.}
 
@@
 \begin{equation}
-\label{formal intensity}
+\label{formal intensity [1]}
 w(x)\IE_x\left[\exp\left(\int_0^t (F+\gamma \Delta r)(Y_s)ds\right)\ind_{Y_t=y}\right]dy,

### 2023-02-23 forwards-and-backwards.tex
alison edits feb 21

@@
 the nature of the deterministic
-wave changes from ``pulled'' to ``pushed'', \cite{birzu/hallatschek/korolev:2017}.
+wave changes from ``pulled'' to ``pushed'', 
+\cite{birzu/hallatschek/korolev:2017, birzu/hallatschek/korolev:2021}.
 In that setting, the genealogies will be quite different
-from the Fisher-KPP case. \comment{Could refer to more recent Birzu et al paper here.}
+from the Fisher-KPP case. 
+%\comment{Could refer to more recent Birzu et al paper here.}
 For example, \cite{etheridge/penington:2022}
@@
 $\measures$ (the space of finite measures on $\IR^d$
-endowed with the weak topology).
+endowed with the weak topology). In fact $\eta_t^N$ will be a purely atomic
+measure comprised of atoms of mass $1/N$.
 
@@
 is determined by whether $\alpha$ is zero or nonzero.
-%c.f.~Section~\ref{sec:heuristics}.
-
-%In order to specify the assumptions that we shall need on the parameters of our model
-%if we are to pass to a scaling limit, 
+
 It is convenient to record some notation for the 
@@
     with mean $\meanq(x)/\theta$ and covariance matrix $\covq(x)/\theta$
-    (although sometimes we omit the dependence of $\meanq$ and $\covq$ on $x$).
+    (although often we omit the dependence of $\meanq$ and $\covq$ on $x$).
     This implies that if we define, for $f : \IR^d \to \IR$,
@@
 that is, this expression is non-negative so that there is no need to take the maximum
-with zero in~(\ref{eqn:mu_defn}).
+	with zero in~(\ref{eqn:mu_defn}). (This is anyway true for 
+	sufficiently large $\theta$.)
 \end{assumptions}
@@
 satisfy; they just require some regularity of $r$ as a function of $x$. 
-\comment{Not sure next sentence strictly true - probably assuming a bit
-more - certainly some regularity.}
 Condition~\ref{control through r} is satisfied if 
@@
 and $m\partial_mr(x,m)$, $m^2\partial_{mm}r(x,m)$ are bounded.
-This will be satsified if $\rho_r$ decays 
-no faster than
+This will be satsified, for example, if $\rho_r$ decays 
 exponentially.
@@
 
-\paragraph{Scaling limits with nonlocal interactions}
+\paragraph{Scaling limits with nonlocal interactions:}
 
@@
 further, that $\{\eta_0^N\}_{N\geq 1}$ is a sequence of 
-purely atomic measures, with atoms of mass $1/N$, which is
+purely atomic measures, with $\eta^N$ comprised of atoms of mass $1/N$, which is
 tight 
@@
    \[ 
-	\dot \varphi = r \DG^*(\gamma \varphi) + \varphi F
+	\partial_t \varphi = r \DG^*(\gamma \varphi) + \varphi F
     \]
@@
 of~(\ref{lipschitz for kurtz xiong}).
-%that
-%\[|J (x_1, \nu_1)-J (x_2, \nu_2)|,|\beta (x_1,\nu_1)-\beta 
-%	(x_2,\nu_2)|, |F(x_1,\nu_1)-F(x_2,\nu_2)|
-	%,|b(x_1,\nu_1)-b(x_2,\nu_2)|
-%	\leq C(\|x_1-x_2\|+\rho (\nu_ 1,\nu_2))\]
-%for some $C>0$.  
-%
 If $\eta_0$ has an $L^2({\mathbb R}^d)$-density, then there 
@@
 
-\paragraph{Two-step convergence to PDE}
+\paragraph{Two-step convergence to PDE:}
 
@@
 \partial_t \psi^\epsilon=
-\Delta\left(\psi^\epsilon \cdot \rho^{\epsilon}_\gamma*\psi^\epsilon\right)
+\Delta\left(\psi^\epsilon \, \rho^{\epsilon}_\gamma*\psi^\epsilon\right)
 +\psi^\epsilon\left(1-\rho^{\epsilon}_\gamma*\psi^\epsilon\right).
@@
 $\psi$ solves~(\ref{PME}) on $[0,T]\times \IR^d$. 
-%Moreover, strong convergence
-%of the initial conditions implies strong convergence of the solutions.
 \end{proposition}
-The example that we have in mind for the kernel $\rho_gamma$ is a Gaussian
+The example that we have in mind for the kernel $\rho_\gamma$ is a Gaussian
 kernel.
@@
 expect analogous results under rather general conditions. However, when the limit
-points are stochastic, they resemble `nonlinear superprocesses' and so one cannot
+points are stochastic, they resemble ``nonlinear superprocesses'' and so one cannot
 expect a density with respect to Lebesgue measure in $d\geq 2$. It is then not
@@
 
-\paragraph{One-step convergence to PDE}
-
-Theorem \ref{thm:nonlocal_convergence} combined with Proposition \ref{prop:nonlocal_to_local}
+\paragraph{One-step convergence to PDE:}
+
+Theorem \ref{thm:nonlocal_convergence}, combined with Proposition \ref{prop:nonlocal_to_local},
 implies that we can take the limit $N \to \infty$
@@
 
-\comment{Need to introduce notion of $C$-tight and say that's what we prove.}
-
     Let $(\eta^N_t)_{t \geq 0}$
@@
 Further suppose that $F(m)$ is a polynomial with $F(m)\ind_{m\geq 0}$ bounded above.
-%there exists $k\in\IN$ such that $F$ is $k$-times differentiable
-%with 
-%$\|F^{(k)}(m)\|_{\infty}<\infty$.
+We assume that $\langle 1,\eta_0\rangle$ is bounded, and that for all 
+$x\in\IR^d$ and $k\in \IN$,
+	\[
+		\limsup_{\epsilon\to 0} 
+		\IE\big[\rho_F^\epsilon*\eta_0(x)^k\big]<\infty,
+	\]
+	and 
+\[
+	\int \IE\big[\rho_F^\epsilon*\eta_0(x)^k\big] dx<\infty.
+\]
 Finally assume that $N \to \infty$, $\theta \to \infty$
@@
 \begin{align}
+	\label{target equation in local convergence}
         \partial_t \varphi(t, x)=\Delta \varphi (t,x) +\varphi(t,x) F(\varphi(t,x)).
@@
 can be obtained by picking a focal individual uniformly at 
-random from the population at $x$,
-\comment{actually there will be at most one individual at any point $x$}
+random from the population at $x$
+(actually, in the prelimit,
+there will be at most one individual at any point $x$),
 and then, for each time $t$,
@@
     Then the semigroup $Q_s$
-    of the motion of a linages in this population 
+    of the motion of a lineages in this population 
     is time-homogeneous with generator
@@
 
-We now turn to some examples and applications. %Next,
-%we cover some illustrative examples
-%and interesting applications.
+We now turn to some examples and applications.
 
@@
 This explains the form of the martingale of Theorem~\ref{thm:nonlocal_convergence}.
-%More generally, we expect everything to work
-%if the remaining parameters ($r$, $\gamma$, and $F$)
-%also depend on $N$, but converge as $N \to \infty$.
 
@@
 a quick calculation shows that as $N \to \infty$,
-%\begin{align*}
-%    \theta \int (h(x) - h(y)) q_\theta(x, y) dx
-%    &\to
-%    \DG^* h(y)  - h(y) \DG^* 1 .
-%\end{align*}
-%Consequently,
 \begin{align*}
@@
 with spatial projection $\eta$.
+
 An individual at spatial location $x$ with level $u$
@@
 (As before, ``maturity'' is instantaneous.)
-
 If it survives, 
@@
     =
-    % \gamma^{\mathfrak{m}}(x, \eta) \left\{N^{-1}(N -v)^{2} -(N -v)\right\}.
     -\theta \frac{v}{N} \left(N - v\right)
@@
 which captures the local net difference between reproduction and death.
-%i.e., the deviation from criticality of the branching mechanism.
 Recall from equation~\eqref{eqn:mu_defn} that
@@
 We can now define the spatial-level process
-explicitly as a solution to a Martingale Problem,
+explicitly as a solution to a martingale problem,
 whose generator is just the sum of
 \eqref{eqn:birth_generator} and \eqref{eqn:level_generator}.
-
 We need some notation. 
@@
 counting measures on $\IR^d\times [0,N]$.
-%We say that a ${\mathcal D}([0,\infty), {\mathcal C})$-valued process 
-%$(\xi_t)_{t \ge 0}$
-%    is a solution to the $(A, \lp_0)$ martingale problem
-%    if %it has initial distribution $\lp_0$ and 
-%$f(\lp_t) - f(\lp_0)-\int_0^t Af(\lp_s) ds$ is a martingale (with 
-%respect to the natural filtration) for all 
-%test functions $f$ 
-%    as defined above.
 \begin{definition}[Martingale Problem Characterisation]
@@
 by
-%and $\lp_0 \in {\mathcal C}_N$, %\mathcal{M}_F(\IR^d \times [0,N])$,
-%we define $(\lp^{N}_t)_{t \geq 0}$
-%to be the unique solution to the martingale problem
-%with initial condition $\lp_0$ and generator $A^{N}$ that satisfies
 \begin{equation}
@@
 as before. 
-Given $\lp_0 \in {\mathcal C}_N$, %\mathcal{M}_F(\IR^d \times [0,N])$,
-%we define $(\lp^{N}_t)_{t \geq 0}$
+Given $\lp_0 \in {\mathcal C}_N$, 
 we say that a ${\mathcal D}([0,\infty), {\mathcal C}_N)$-valued process 
 $(\xi_t)_{t \ge 0}$
-   is a solution to the $(A, \lp_0)$ martingale problem
-    if %it has initial distribution $\lp_0$ and 
-$f(\lp_t) - f(\lp_0)-\int_0^t Af(\lp_s) ds$ is a martingale (with 
+   is a solution to the $(A^N, \lp_0)$ martingale problem
+    if 
+$f(\lp_t) - f(\lp_0)-\int_0^t A^Nf(\lp_s) ds$ is a martingale (with 
 respect to the natural filtration) for all 
@@
     as defined above.
-%to be the unique solution to the martingale problem
-%with initial condition $\lp_0$ and generator $A^{N}$ that satisfies
 \end{definition}
@@
 for which we do not have uniqueness.
-%(although we construct an explicit solution later).
 As before, the parameter $\alpha$ will correspond to 
@@
     \end{split} \end{align}
- %   Write ${\cal C}(\IR^d\times [0,\infty))$ for the point measures on $\IR^d\times [0,\infty)$.
 We say that a ${\cal C}(\IR^d\times [0,\infty))$-valued process $(\xi_t)_{t \ge 0}$
@@
 
-    \comment{Theorem~\label{thm:nonlocal_convergence}
+    \comment{Theorem~\ref{thm:nonlocal_convergence}
         isn't written as ``the $(A, \mu)$ martingale problem is'';
@@
     If $\tilde \eta$ is a solution
-    of the limiting martingale problem of Theorem~\label{thm:nonlocal_convergence}
+    of the limiting martingale problem of Theorem~\ref{thm:nonlocal_convergence}
     with initial distribution $\mu_0$
@@
 
-In this section I haven't specified the filtration for the martingale problem.}
+\comment{In this section I haven't specified the filtration for the martingale problem.}
 
@@
 $v$ will determine the level of the offspring,
-$z$ will give the spatial displacement of the offspring relative to the parent,
+$z$ will determine the spatial displacement of the offspring relative to the parent,
 $\kappa$ will be used to determine whether parent or offspring is assigned the new level,
@@
 $\Pi_a$ with level below $N$, that is points with
-$\ell v<N-u$, is given by~(\ref{rate of birth}).
+$v \ell <N-u$, is given by~(\ref{rate of birth}).
 Since the mean measure of $\Pi_a$ is Lebesgue measure
@@
 \end{equation}
-and using this, the (potential) new level is
+and, using this, the (potential) new level is
 \begin{equation*}
@@
 different values of $N$.
-As a result, individual lines of descent converge pointwise as $N \to \infty$.
+As a result, if the spatial projections $\eta$ converge, then
+individual lines of descent converge pointwise as $N \to \infty$.
 To see this, first note that if the Poisson processes are fixed
@@
 according to a Poisson Point Process with intensity
-%at all times,
-%i.e., according to a Poisson process with rate
 $$
@@
 $$
-%and uniform intensity on higher levels.
 Now consider the location of the line of descent:
@@
 % % % % % % % % % % % % %
-%\subsection{Convergence of the population density process}
 \subsection{Proof of Theorem~\ref{thm:nonlocal_convergence}: nonlocal limit points}
@@
 sequence of scaled population
-processes in $\cmeasures$ %$\cal{M}_F(\widehat{\IR}^d)$ 
+processes in $\cmeasures$ 
 (for which, since we have compactified $\IR^d$,
@@
 Aldous-Rebolledo criterion in Lemma~\ref{lem:eta_projections_tightness}.
-%{compactnedd projections}.
 These ingredients are gathered together in 
@@
     for all $f \in C^2_b(\IR^d)$ with uniformly bounded first and 
-second derivatives, there exists a $C_f < \infty$, independent of $N$,
+	second derivatives, and all $T>0$, there exists a $C=C(f,T) < \infty$, 
+	independent of $N$,
     such that
@@
         \le
-        \IE[\langle f, \eta^N_0 \rangle]
-        e^{C_f t}
+	    C\IE[\langle 1, \eta^N_0 \rangle]
+        %e^{C_f t}
     \end{equation}
@@
         \frac{1}{2} \sum_{ij} (y_i - x_i)(y_j - x_j)
-            \partial_{x_i x_j} \Big(f(z)r\big(\smooth{r}\eta(z)\big)\Big) 
+            \partial_{x_i x_j} \Big(f(z)r\big(\smooth{r}\eta(z)\big)\Big) ,
     \end{align*}
@@
 First note that,  
-    \begin{align} \label{eqn:q_bound_split}
+    \begin{align}
+	    \nonumber
     &
@@
         \right|
-    \\ &\qquad {} \leq
+    \\ 
+ \label{eqn:q_bound_split}
+	    &\qquad {} \leq
         \left| \theta 
@@
         \right|
-    \\ &\qquad \qquad {}  +
+    \\ 
+\nonumber
+	    &\qquad \qquad {}  +
         \left| \theta 
@@
 this case 
-    the second term in~\eqref{eqn:q_bound_split} is bounded by
+    the term in~\eqref{eqn:q_bound_split} is bounded by
     \begin{align*}
@@
 The bound~(\ref{eta_f_bound}) then follows by first applying Gronwall's
-inequality in the case $f=1$, and then, after substitution of 
-the resulting bound on $\langle 1,\eta_s\rangle$ into the
-expression above, a second 
-application of Gronwall's inequality.
+inequality in the case $f=1$, which yields
+\[
+	\IE\big[\langle 1,\eta_t^N\rangle\big]\leq e^{Ct}\IE\big[\langle 1,\eta_0^N\rangle\big],
+\]
+with $C$ independent of $N$, and then substituting 
+the resulting bound on $\IE\big[\langle 1,\eta_s^N\rangle\big]$ into the
+expression above.
 \end{proof}
@@
     Under the assumptions of Theorem~\ref{thm:nonlocal_convergence},
-%Assumptions~\ref{def:model_setup},
-%    if $\theta/N \to \alpha$ and $\eta^{N}_0 \to \eta_0$ weakly as $N \to \infty$,
     for each $T>0$, there exists some constant $C_T$,
@@
     and as before $[M(f)]_t$ the quadratic variation of $M_t(f)$,
-    so that by the Burkholder-Davis-Gundy inequality, there is a $C'$ so that
+    so that by the Burkholder-Davis-Gundy inequality, there is a $C'$ so that,
+in the notation of Lemma~\ref{lem:eta_f_bound},
     \begin{align*}
@@
             \int_0^t
-            \int_{\IR^d} \left\{
+            %\int_{\IR^d} 
+	    \Big\langle\left\{
                 \gamma(x, \eta^N_s)
@@
                 + \mu_\theta(x, \eta^N_s)
-            \right\} \eta_s^N(dx)
+            \right\}, \eta_s^N(dx)\Big\rangle
             dt
@@
             \int_0^t
-            \int_{\IR^d} \left\{
+            %\int_{\IR^d} 
+	    \Big\langle\left\{
                 \frac{2\theta}{N} \gamma(x, \eta^N_s) r(x, \eta^N_s)
-		+ \frac{\gamma(x,\eta_s^N)}{N} B_1(x, \eta^N_s)-\frac{1}{N}F(x,\eta^N_s)
-            \right\} \eta_s^N(dx)
+		+ \frac{\gamma(x,\eta_s^N)}{N} 
+		B_1(x, \eta^N_s)-\frac{1}{N}F(x,\eta^N_s)
+            \right\}, \eta_s^N(dx) \Big\rangle
             dt
@@
 	with $f=1$ to see that
-\[
-\IE\left[\int_0^t \Big\langle -\frac{1}{N}F(x, \eta^N_s), \eta^N_s(dx)
+	\begin{equation}
+		\label{integral of -F}
+\IE\left[\int_0^t \Big\langle -F(x, \eta^N_s), \eta^N_s(dx)
 	\Big\rangle\right]
@@
 	B_1(x, \eta_s^N),\eta_s^N(dx)\Big\rangle ds\right],
-\]
+	\end{equation}
 which is bounded since $\gamma (x,\eta)$ and $B_1(x,\eta)$ are both bounded and 
@@
     Since $\theta/N \to \alpha < \infty$,
-    combining constants and again using Gronwall's inequality, we obtain that
+    combining constants, we obtain that
     \begin{align*}
         \IE\left[ M^*_t(1) \right]
-        % &\le
-        % C'\left( 1 + \IE\left[
-        %     \int_0^t
-        %     \int_{\IR^d} \left\{ C'' \right\} \eta_s^N(dx)
-        %     dt
-        %     \right] \right) \\
         &\le
@@
             \sup_{0 \le s \le t}
-            \int_0^t \int_{\IR^d} \left\{
+            \int_0^t 
+	    %\int_{\IR^d} 
+	    \Big\langle\left\{
                 \gamma(x, \eta^N_s)
@@
                 + F(x, \eta^N_s)
-            \right\} \eta^N_s(dx) ds
+            \right\}, \eta^N_s(dx) \Big\rangle ds
         \right]
@@
 We say that $(\eta^{\infty}_t)_{t \geq 0}$ is a solution 
-to the Martingale Problem $(\Pgen^{\infty}, \eta_0)$ if 
-for all such test functions %$G \in \mathcal{C}^{2}(\IR)$
-%and $f \in \mathcal{C}_{b}(\IR^d)$,
+to the $(\Pgen^{\infty}, \eta_0)$-martingale problem if 
+for all such test functions 
 $$M_t:=G_f(\eta^{\infty}_t)-G_f(\eta_0)
 -\int_{0}^{t}\Pgen^{\infty}G_f(\eta^{\infty}_s)ds$$
-is a martingale. 
+	is a martingale (with respect to the natural $\sigma$-field). 
 \end{definition}
@@
 Then any limit point of $\{(\eta^{N}_t)_{t \geq 0}\}_{N\geq 1}$ 
-in $\mathcal{D}_{[0,\infty)}(\cmeasures)$ %(\mathcal{M}_f(\IR^d))$
+in $\mathcal{D}_{[0,\infty)}(\cmeasures)$ 
 is a solution to the martingale problem for 
@@
     \label{eq: Prelimit MP Application}
-%\lim_{N \to \infty}
 \mathbb{E}\left[
@@
 Since $F$ is bounded above, there is a constant $K$ such that $|F|\leq K-F$ so
-that, exactly as in the proof of 
-Lemma~\ref{lem:eta_compact_containment},
+that, exactly as in equation~(\ref{integral of -F}), 
 we can check that
@@
 \begin{equation}
-\IE[\|B_{\lambda  t}^y-B_{\lambda  t}^x\|]\leq \|y-x\|+\IE[\|B^0_{2\lambda t}\|] 
-%&= \sqrt{ d \lambda t } \sqrt{2/\pi} e^{-(y-x)^2/(2d\lambda t )} + 
-%(y-x) (1-2\Phi(-(y-x)/(\lambda  d t))) \nonumber \\ 
-%& \leq \sqrt{2d \lambda  /\pi}  \sqrt{t} + 
+\IE[\|B_{\lambda  t}^y-B_{\lambda  t}^x\|]
+	\leq \|y-x\|+\IE[\|B^0_{2\lambda t}\|] 
 \leq \|y-x\|+C\sqrt{t}. \label{eq:ExpDif2}
@@
 the constant on the right hand side of 
-equation~(\ref{eq:boundDensityXt}). 
-We write $K_{\varphi_0}$ for the Lipschitz constant of 
-$\varphi_0$. Set %Having this we can set:
+equation~(\ref{eq:boundDensityXt}), and 
+we write $K_{\varphi_0}$ for the Lipschitz constant of 
+$\varphi_0$. Set 
 \[ 
@@
 We first prove that the result holds if $t < \delta^2$. As before
-% $f_t(x,y)$ be 
-%the transition density of $(X_t)_{t \geq 0}$.  Let 
 let $Z_t^x$ and $Z_t^y$ be 
@@
 \[ 
-\varphi_t(x) = \IE_x\big[ \varphi_{t-t'}(Z_{t'}) 
-\exp\big( \int_0^{t'} F(\varphi_{t-s}(Z_s)) ds \big) \big]. 
+\varphi_t(x) = \IE_x\Big[ \varphi_{t-t'}(Z_{t'}) 
+\exp\big( \int_0^{t'} F(\varphi_{t-s}(Z_s)) ds \big) \Big]. 
 \]
-Therefore, setting $t'=\delta^2$, for all $z$
+Therefore, setting $t'=\delta^2$, for all $z$,
 \[ 
@@
 \]
-We can then deduce that,
+We can then deduce that
 \begin{align}
@@
 
-%For simplicity, we define,
-%\[ \widehat{\delta}(\epsilon) := 2e^{-\epsilon^{-1/3}/2}+\epsilon^{1/9}. \]
 \begin{lemma} 
@@
 \| F(\varphi_t(\cdot)) - F(\rho^\epsilon_F*\varphi_t(\cdot)) \|_\infty 
-\leq \widetilde{C}\big(I(\epsilon)+\epsilon^{1/4}\big). % \widehat{\delta}(\epsilon). 
+\leq \widetilde{C}\big(I(\epsilon)+\epsilon^{1/4}\big). 
 \end{equation}
@@
 and Lemma~\ref{ContinuityVarphi}.
-This proves (\ref{ContinuityConvolution1}). For (\ref{ContinuityConvolution2}), % note that, 
-%by Proposition~\ref{BoundednessVarphis}, we have that $\varphi_t(x)$ and 
-%$\rho_\epsilon*\varphi_t(x)$ are bounded by $M$. 
+This proves (\ref{ContinuityConvolution1}). For (\ref{ContinuityConvolution2}),
 let $L_M$ be the (uniform) Lipschitz constant of $F$ on $[0,M]$, with
@@
 \end{align*}
-giving the result.
+	giving the result, since $\widehat{\delta}\to 0$ as $\epsilon\to 0$.
 \end{proof}
@@
 \begin{equation*}
-%\label{mollified equation}
 	\partial_t\psi_t^\epsilon(x) =
 	\Delta\left(\psi_t^\epsilon \, \rho^\epsilon *\psi_t^\epsilon\right)(x)
-	+\psi_t^\epsilon(x)\left(1-\rho^\epsilon *\psi_t^\epsilon(x) %*\zeta_\epsilon
+	+\psi_t^\epsilon(x)\left(1-\rho^\epsilon *\psi_t^\epsilon(x) 
 \right),
@@
 	\partial_t \psi_t(x)=
-%\frac{\partial^2}{\partial x^2}
 	\Delta\left(\psi_t^2\right)(x)
@@
 \label{lower bound on ulogu}
-Suppose that there exists $\lambda<1$ and $C<\infty$, both independent of
+	Suppose that there exists $\lambda\in (0,1)$ and $C<\infty$, both independent of
 $\epsilon$, such that $\int \exp(\lambda |x|) \psi_0^\epsilon(x) dx<C$.
@@
 	\\
-%*\zeta_\epsilon)\dif x
 	+\int \exp(\lambda x)\psi_t^\epsilon(x)\big(1-\rho^{\epsilon}*\psi_t^\epsilon(x)\big) dx\\
@@
 	\psi_t^\epsilon(x) dx 
-%*\zeta_\epsilon)\dif x
 	+\int \exp(\lambda x)\psi_t^\epsilon(x) dx\\
@@
 \int\int\int \psi_t^\epsilon(x)\psi_t^\epsilon(x-y)\zeta^{\epsilon}(y-z)
-\check{\zeta}^{\epsilon}(z) dz dy dx %\dif z\dif y\dif x
+\check{\zeta}^{\epsilon}(z) dz dy dx 
 \\
@@
 	=\int\left(\zeta^{\epsilon}*\psi_t^\epsilon(x)\right)^2 dx,
-%*\rho_\epsilon\right(x))^2\dif x,
 \end{multline*}
@@
 \big(1-\rho^{\epsilon}*\psi_t^\epsilon\big)
-%-u^\epsilon\cdot u^\epsilon*\zeta_\epsilon
 \right] dx .
@@
 Since $\zeta\in\mathcal{S}(\IR)$, 
-%Using the bound 
-%$yp_{\epsilon^2/2}(y)\leq C\epsilon p_{\epsilon^2}(y)$ 
-%(c.f.~(\ref{first use of trick}) above)
 the integral in this expression is
@@
 and~(\ref{error 2}) is controlled in the same way as~(\ref{error 1}):
-using the Intermediate Value Theorem:
+using the Intermediate Value Theorem,
 \begin{multline*}
@@
 
-To simplify notation, in this section we shall write 
+{\em To simplify notation, in this section we shall write 
 $$\rho_\epsilon*\eta(x)=\rho_F^\epsilon*\eta(x)
@@
 where $p_t(x,y)$ denotes the heat semigroup. 
+The assumptions of Theorem~\ref{thm:local_convergence} will be in 
+force throughout, in particular,
+\begin{equation}
+	\label{conditions for one step}
+	\epsilon^2\theta\to\infty, \qquad\mbox{and }\frac{\theta}{N\epsilon^d}\to 0.
+\end{equation}
+That $N, \theta\to \infty$ and $\epsilon\to 0$ simultaneously will be 
+implicit, so for example if we write $\lim_{\epsilon\to 0}$, it should be 
+understood that $\theta, N\to\infty$ in such a way 
+that~(\ref{conditions for one step}) is satisfied. 
+Moreover, where there is no risk of confusion, except where it is helpful
+for emphasis, we 
+suppress dependence of $\eta$ on $N$.}
 
@@
 establish tightness and then apply standard results on 
-convergence of Markov processes from~\cite{ethier/kurtz:1986}. Although
-we prove the required bounds, we skip the details of this part. The challenge
+convergence of Markov processes from~\cite{ethier/kurtz:1986}. 
+The challenge
 comes in identifying the limit points. This is much more intricate than the case in 
@@
 Subsection~\ref{continuity for random walk}.
-Various bounds on $\rho_\epsilon*\eta_t$ are then provided in 
+Various bounds on the moments of $\rho_\epsilon*\eta_t$, one consequence of 
+which is tightness, are then provided in 
 Subsection~\ref{bounds on rhoepsilon},
@@
 $\psi_0^{\epsilon,x}(y) = \rho_\epsilon(y-x) =p_{\epsilon^2}(x,y)$.
-%We have the following result for $\psi_t^{\epsilon,x}$.
 
@@
 
-\begin{proof}%[of Lemma~\ref{lem:poisson_ld}]
+\begin{proof}
     We apply Cram\'er's Theorem.
@@
 
-\begin{proof}%[of Lemma~\ref{Lemma:BoundPsiHS2}]
+\begin{proof}
     Still using the notation of Lemma~\ref{PsiBoundHS},
@@
 are less than 1.
-    % note the original had $p_{b/2}$ on the right.
 Since, on the event $A_1$, $\tau(t)<0$, we can  
@@
     \begin{align*}
-        \frac{\partial}{\partial s} p_s(x, y)
+        \partial_ s p_s(x, y)
         &=
-        \frac{\partial}{\partial s}
+        \partial_s
         \left(
@@
 defined in~(\ref{AlmostHeatEquation}).
-In particular, %since $\IE[\langle 1,\eta_0\rangle^k\]$ is finite, 
+In particular, 
 under the assumptions of Theorem~\ref{thm:local_convergence}, the
@@
 \label{time dep mg prob}
-%        \label{timeMGP}
     \langle \phi_0(x), \eta_t(dx) \rangle
-    = %\nonumber 
+    = 
     \langle \phi_t(x), \eta_0(dx) \rangle
@@
 where $M_t(x)$ is a martingale. 
-% DON'T DELETE THIS - I'LL NEED IT LATER
-%\begin{equation}
-%\label{qv M(x)}
-%[M(x)]_t=\frac{\theta}{N}\int_0^t\Big\langle\int\psi^{\epsilon,x}_{t-s}(z)^2q_\theta(y,dz)
-%+\Big(1-\frac{F(\rho_\epsilon*\eta(y)}{\theta}\Big)\psi^{\epsilon,x}_{t-s}(y)^2,\eta_s(dy)
-%\Big\rangle.
-%\end{equation}
 Taking expectations in~(\ref{expn rhoepsilon}), using that $F$ is bounded above, and 
@@
 $N\epsilon^d>1$,
-%$\langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle^{j}
-%\leq C\langle\psi^{\epsilon, x}_{t}(y),\eta_0(dy)\rangle$, 
 and our inductive
@@
 q_\theta(y,dz),
-%+(-1)^j\Big(1-\frac{F(\rho_\epsilon*\eta_s(x))}{\theta}\Big)\Big),
-\eta_s(dy)\Big\rangle ds %\Big]
+\eta_s(dy)\Big\rangle ds 
 \\
@@
 \int_0^t\theta N\sum_{j=2}^{k}\binom{k}{j}\frac{\psi_{t-s}^{\epsilon,x}(y)^j}{N^j}\langle \psi^{\epsilon,x}_{t-s},\eta_s\rangle^{k-j}
-%\Big(1+
-(-1)^j\Big(1-\frac{F(\rho_\epsilon*\eta_s(y))}{\theta} %\Big)
+(-1)^j\Big(1-\frac{F(\rho_\epsilon*\eta_s(y))}{\theta} 
 \Big),
@@
 \Big(\frac{1}{(N\epsilon^d)^{j-2}}\Big)
-\Big\langle
+	\Big\langle \psi^{\epsilon,x}_{t-s}(y)
 \Big(2+\frac{|F(\rho_\epsilon*\eta_s(y))|}{\theta}\Big),\eta_s(dy)\Big\rangle
@@
 \langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle\Big)
-%\langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle^j
 ,
@@
 Under the assumptions of Theorem~\ref{thm:local_convergence},
-%Lemma~\ref{bounds on moments},
 for each $k\geq 1$, $T>0$,
@@
 p_{A\epsilon^2}(x,y)
-=\frac{1}{A^{d/2}}p_{\epsilon^2}(x,y)\exp\big(-\frac{\|x-y\|^2}{2\epsilon^2}
-\left(\frac{1}{A}-1\right)\big)\leq \frac{1}{A^{d/2}}p_{\epsilon^2}(x,y).
+=\frac{1}{A^{d/2}}p_{\epsilon^2}(x,y)\exp\Big(-\frac{\|x-y\|^2}{2\epsilon^2}
+\big(\frac{1}{A}-1\big)\Big)\leq \frac{1}{A^{d/2}}p_{\epsilon^2}(x,y).
 \end{equation}
@@
 p_{\epsilon^2/2}(y,z)dy\eta_t(dz)\eta_t(dx)\Big]
-       % \langle p_{\epsilon^2/2} * p_{\epsilon^2/2} * \eta_t(x), \eta(dx) \rangle
         \\ &=
@@
 
-\begin{corollary}[Tightness of $\{(\rho_\epsilon*\eta_t(x) dx)_{t\geq 0}\}$]
+\begin{corollary}[Tightness of $\{(\rho_\epsilon*\eta_t^N(x) dx)_{t\geq 0}\}$]
 \label{lem:density_tightness} 
 Under the assumptions of Theorem~\ref{thm:local_convergence},
-the sequence of measure valued processes $\{ \rho*\eta_t(x) dx \}_{t \geq 0}$
+the sequence of measure valued processes $\{ \rho*\eta_t^N(x) dx \}_{t \geq 0}$
 (taking values in $D([0,T], \measures)$ is tight.
@@
 
-First observe that the proof from Lemma~\ref{lem:eta_compact_containment}, 
+First observe that the proof, from Lemma~\ref{lem:eta_compact_containment}, 
 that 
-$\IE[\sup_{0\leq t\leq T} \langle 1,\eta_t\rangle]$ is 
+$\IE[\sup_{0\leq t\leq T} \langle 1,\eta_t^N\rangle]$ is 
 bounded goes through unchanged, and since 
-$\langle 1, \rho_\epsilon*\eta_t(x)dx\rangle=\langle 1, \eta_t\rangle$,  
+$\langle 1, \rho_\epsilon*\eta_t^N(x)dx\rangle=\langle 1, \eta_t^N\rangle$,  
 compact containment follows.
@@
 sequence of real-valued processes 
-$\big\{\big(\int f(x)\rho_\epsilon*\eta_t^N(x)dx\big)_{t\geq 0}\big\}_{N\geq 1}$is tight.  
+$\big\{\big(\int f(x)\rho_\epsilon*\eta_t^N(x)dx\big)_{t\geq 0}\big\}_{N\geq 1}$ is tight.  
 Let us temporarily write $X_f^N(t)$ for $\int f(x)\rho_\epsilon*\eta_t^N(x)dx$
@@
 $\min_{1\leq i\leq n}(t_i-t_{i-1})>\delta$ and $n\geq 1$.
-Using Corollary~3.7.4 (p.129) of~\cite{ethier/kurtz:1986}, 
+Using Corollary~3.7.4 of~\cite{ethier/kurtz:1986}, 
 to prove tightness
@@
 it suffices to check compact containment of 
-the sequence $\{\rho_\epsilon*\eta_t(x)dx\}_{N\geq 1}$ at any rational time $t$ and
+the sequence $\{\rho_\epsilon*\eta_t^N(x)dx\}_{N\geq 1}$ at any rational time $t$ and
 that for every $\nu>0$ and $T>0$, there exists $\delta>0$ such that
@@
 \left|
-\langle \rho_{\epsilon} * f, \eta_t \rangle 
-- \langle \rho_{\epsilon} * f, \eta_s \rangle            
+\langle \rho_{\epsilon} * f, \eta_t^N \rangle 
+- \langle \rho_{\epsilon} * f, \eta_s^N \rangle            
 \right|
@@
 \int_s^t\Big\langle\theta\int\big(\rho_\epsilon*f(y)-\rho_\epsilon*f(x)\big)
-q_{\theta}(x,dy),\eta_u(dx)\Big\rangle du
+q_{\theta}(x,dy),\eta_u^N(dx)\Big\rangle du
 \right|
 \\
-+\int_s^t\Big\langle |F\big(\rho_\epsilon*\eta_u(x)\big)|\rho_\epsilon*f(x), 
-\eta_u(dx)\Big\rangle du +2\sup_{0\leq u\leq T}|\widehat{M}^N(f)_u|,
++\int_s^t\Big\langle |F\big(\rho_\epsilon*\eta_u^N(x)\big)|\rho_\epsilon*f(x), 
+\eta_u^N(dx)\Big\rangle du +2\sup_{0\leq u\leq T}|\widehat{M}^N(f)_u|,
 \end{multline}
-where $\widehat{M}(f)$ is the martingale of~(\ref{eqn:eta_martingale})
+where $\widehat{M}^N(f)$ is the martingale of~(\ref{eqn:eta_martingale})
 with the test function $f$ replaced by $\rho_\epsilon*f$. 
 We control each of the three terms on the right hand side separately.
-%In particular, 
-%just as for $M_t(x)$ above, we can deduce that its supremum tends to zero under
-%our scaling.
 
@@
 \end{multline*}
-%Since $F$ is a polynomial, 
 We therefore have
@@
         \left|
-        \langle \rho_{\epsilon} * f, \eta_t \rangle
+        \langle \rho_{\epsilon} * f, \eta_t^N \rangle
         -
-        \langle \rho_{\epsilon} * f, \eta_s \rangle
+        \langle \rho_{\epsilon} * f, \eta_s^N \rangle
         \right|
@@
         \| \Delta f \|_\infty |t-s|
-        \sup_{0 \leq u \leq T } \langle 1, \eta_u \rangle
+        \sup_{0 \leq u \leq T } \langle 1, \eta_u^N \rangle
 \\
 +
-\|f\|_\infty \int_s^t
-%\Big\langle \sum_{k=1}^n|a_k|
-%\big(\rho_\epsilon*\eta_u(x)\big)^k, 
-\big\langle \big|F\big(\rho_\epsilon*\eta_u(x)\big)\big|,
-\eta_u(dx)\big\rangle du +2\sup_{0\leq u\leq T}|\widehat{M}^N(f)_u|.
+	\int_s^t
+	\big\langle \rho_\epsilon*|f|(x)\, \big|F\big(\rho_\epsilon*\eta_u^N(x)\big)\big|,
+\eta_u^N(dx)\big\rangle du +2\sup_{0\leq u\leq T}|\widehat{M}^N(f)_u|.
     \end{multline*}
@@
 >\frac{\nu}{3}
-\Big]\leq \limsup_{N\to\infty}\frac{36}{\nu^2}\IE\big[[\widehat{M}^N(f)]_t\big]
+\Big]\leq \limsup_{N\to\infty}\frac{36}{\nu^2}\IE\big[[\widehat{M}^N(f)]_T\big]
 \leq \limsup_{N\to\infty}\frac{36}{\nu^2}\frac{C\theta}{N\epsilon^d} 
@@
 Now consider
+\begin{multline}
+	\label{square of F-integral}
+\IE\Big[
+	\Big(\int_s^t\big\langle\rho_\epsilon*|f|(x) \big|F\big(\rho_\epsilon*\eta_u^N(x)\big)\big|,
+\eta_u^N(dx)\big\rangle du\Big)^2\Big]
+\\
+=
+2\IE\Big[
+	\int_s^t\big\langle\rho_\epsilon*|f|(x) \big|F\big(\rho_\epsilon*\eta_u^N(x)\big)\big|,
+\eta_u^N(dx)\big\rangle 
+	\int_u^t\big\langle \rho_\epsilon*|f|(x)\big|F\big(\rho_\epsilon*\eta_r^N(x)\big)\big|,
+\eta_r^N(dx)\big\rangle dr
+du\Big].
+\end{multline}
+Since $F$ is polynomial, we use the approach
+of Corollary~\ref{alternative form moment bounds}, the tower 
+property, and 
+Lemma~\ref{bounds on moments}, to bound this
+in terms of sums of terms of the form
+\[
+\IE\Big[\int_s^t(t-u)\int\rho_\epsilon*|f|(x)\rho_\epsilon*\eta_u^N(x)^jdx
+\int\rho_\epsilon*|f|(y)\rho_\epsilon*\eta_u^N(y)^kdydu\Big].
+\]
+Now observe that, again using Lemma~\ref{bounds on moments}, 
 \begin{multline*}
-\IE\Big[
-\Big(\int_s^t\big\langle \big|F\big(\rho_\epsilon*\eta_u(x)\big)\big|,
-\eta_u(dx)\big\rangle du\Big)^2\Big]
-\\
-=
-\IE\Big[
-\int_s^t\big\langle \big|F\big(\rho_\epsilon*\eta_u(x)\big)\big|,
-\eta_u(dx)\big\rangle 
-\int_u^t\big\langle \big|F\big(\rho_\epsilon*\eta_r(x)\big)\big|,
-\eta_r(dx)\big\rangle dr
-du\Big].
+	\int\int\rho_\epsilon*|f|(x)\rho_\epsilon*\eta_u^N(x)^j
+	\rho_\epsilon*|f|(y)\rho_\epsilon*\eta_u^N(y)^k dx dy
+	\\
+	\leq
+	\int\int\|f\|_\infty\rho_\epsilon*\eta_u^N(x)^{j+k}
+	\rho_\epsilon*|f|(y)
+	dx dy
++
+	\int\int
+	\rho_\epsilon*|f|(x)
+	\|f\|_\infty
+	\rho_\epsilon*\eta_u^N(y)^{j+k}
+dx dy
+	\\ \leq C\int |f|(x)dx.
 \end{multline*}
-Since $F$ is polynomial, using our moment bounds we see that this 
-quantity is bounded by $C(t-s)^2$ for some constant $C$ which we can 
+Thus the quantity~(\ref{square of F-integral}) 
+is bounded by $C(t-s)^2$ for some constant $C$ which we can 
 take to be independent of $s$, $t$ and $\epsilon$. Markov's inequality 
@@
 \IP\Big[\|f\|_\infty\int_s^t
-\big\langle \big|F\big(\rho_\epsilon*\eta_u(x)\big)\big|,
-\eta_u(dx)\big\rangle du \geq \frac{\nu}{3}\Big]
+\big\langle \big|F\big(\rho_\epsilon*\eta_u^N(x)\big)\big|,
+\eta_u^N(dx)\big\rangle du \geq \frac{\nu}{3}\Big]
 \leq C\frac{(t-s)^2}{\nu^2}.
@@
 \IP\Big[\max_i\|f\|_\infty\int_{t_{i-1}}^{t_i}
-\big\langle \big|F\big(\rho_\epsilon*\eta_u(x)\big)\big|,
-\eta_u(dx)\big\rangle du \geq \frac{\nu}{3}\Big]
+\big\langle \big|F\big(\rho_\epsilon*\eta_u^N(x)\big)\big|,
+\eta_u^N(dx)\big\rangle du \geq \frac{\nu}{3}\Big]
 \leq C\frac{\delta}{T\nu^2}.
@@
 \[
-\IP\Big[\|\Delta f\|_\infty\, \sup_{0\leq t\leq T} \langle 1,\eta_t\rangle 
+\IP\Big[\|\Delta f\|_\infty\, \sup_{0\leq t\leq T} \langle 1,\eta_t^N\rangle 
 >K\Big]<\frac{\nu}{3}, 
@@
 We now turn to the identification of the limit points of the sequence 
-$\big\{\big(\rho_\epsilon*\eta_t(x)dx\big)_{t\geq 0}\big\}_{N\geq 1}$.
-Since we only know that for every sequence there is a weakly convergent subsequence,
+$\big\{\big(\rho_\epsilon*\eta_t^N(x)dx\big)_{t\geq 0}\big\}_{N\geq 1}$.
+We consider the terms in the semimartingale 
+decomposition~(\ref{eqn:eta_martingale})
+of $\langle f, \rho_\epsilon*\eta_t^N(x)dx\rangle=
+\langle \rho_\epsilon*f, \eta_t^N(dx)\rangle$.
+By a Taylor expansion, writing $\{T_t\}_{t\geq 0}$ for the heat semigroup,
+\begin{align*}
+\int_0^t \big\langle \mathcal{L}^\theta T_{\epsilon^2} f, 
+	\eta_s^N(dx)\big\rangle ds 
+&= \int_0^t \big\langle \frac{1}{2} \Delta T_{\epsilon^2} f(x), 
+	\eta_s^N(dx) \big\rangle 
+	+ \mathcal{O}\Big(\frac{1}{\theta}\Big) 
+\\ &= \int_0^t \big\langle \frac{1}{2} \Delta f(x), \rho_\epsilon* \eta_s^N(x) dx 
+	\big\rangle ds + \mathcal{O}\Big(\frac{1}{\theta}\Big).
+\end{align*}
+Thus, from weak convergence we can deduce that under our scaling,
+for any convergent subsequence $\{\rho_\epsilon*\eta^N(x)dx\}_{N\geq 1}$,
+\[ 
+\int_0^t \big\langle \mathcal{L}^\theta T_{\epsilon^2} f, 
+\eta_s^N(dx)\big\rangle ds 
+\rightarrow \int_0^t \big\langle \frac{1}{2} \Delta f(x), 
+\varphi (s,x) dx \big\rangle ds. 
+\]
+
+Since we only know that for every sequence of measures satisfying the
+conditions of Theorem~\ref{thm:local_convergence}
+there is a {\em weakly} convergent subsequence,
 the difficulty is the non-linear term in the martingale problem. 
@@
 
-%\begin{lemma} \label{ContinuityEstimate}
-%Under the conditions of Theorem~\ref{TeoremOneStepConvergence} we have that 
-%for all $x \in \IR^d$, $\delta>0$,
-%\[
-%\int |\rho_\epsilon*\eta_s(x) -\rho_\epsilon*\eta_s(y)| \rho_\delta(x-y) dy \]
-%is bounded by
-%\comment{Will need to be restated once corrected. Notice we want to put in powers of 
-%$\rho_\epsilon*\eta_s(x)$ and $\rho_\epsilon*\eta_s(y)$ }
-%\begin{align*}
-%\frac{\delta}{\sqrt{\epsilon^2+s}} \langle 1,\eta_0(dz) \rangle &+ \int_0^s \frac{\delta}{\sqrt{\epsilon^2+s-r}} (\langle 1, \eta_r(dz)\rangle + \langle \rho_\epsilon*\eta_r(z), \eta_r(dz)\rangle)dr \\ &+ |M_s(x)| + \int |M_s(y)| \rho_\delta(y-x)dy + \mathcal{O}\left( \frac{1}{\epsilon^2 \theta}\right)
-%\end{align*} 
-%where $M_s(x)$ is the martingale in (\ref{MartingaleProblemMolifier}).
-%\end{lemma}
-
-%\begin{proof}
 We fix $\delta>0$ and 
@@
 Using the semimartingale decomposition~(\ref{expn rhoepsilon}),
-and Lemmas~\ref{lem:poisson_ld} and~\ref{Lemma:BoundPsiHS2}
+and Lemmas~\ref{lem:poisson_ld} and~\ref{Lemma:BoundPsiHS2},
 we have
@@
 &\leq 
-%\big\langle |\psi_t^{\epsilon,x}(z)-\psi_t^{\epsilon,y}(z)|, 
 \big\langle |p_{\epsilon^2+s}(y,z)-p_{\epsilon^2+s}(w,z)|, 
 \eta_0(dz)\big\rangle \nonumber 
-%\\
 +\frac{C}{(\theta\epsilon^2)^{d/2}}\big\langle 
@@
 \int_0^{s-\delta}
-\big\langle |p_{s-r+\epsilon^2}(y,z)-p_{s-r+\epsilon^2}(w,z)|, 
+\big\langle |p_{s-r+\epsilon^2}(y,z)-p_{s-r+\epsilon^2}(w,z)| 
 \cdot |F(\rho_\epsilon*\eta_r(z)|, 
@@
 \big\langle |p_{2(A+1)(s-r+\epsilon^2)}(y,z)+
-p_{2(A+1)(s-r+\epsilon^2)}(w,z)|, 
+p_{2(A+1)(s-r+\epsilon^2)}(w,z)|
 \cdot |F(\rho_\epsilon*\eta_r(z)|, 
@@
 \big\langle |p_{2(A+1)(s-r+\epsilon^2)}(y,z)+
-p_{2(A+1)(s-r+\epsilon^2)}(w,z)|, 
+p_{2(A+1)(s-r+\epsilon^2)}(w,z)| 
 \cdot |F(\rho_\epsilon*\eta_r(z)|, 
@@
 \label{difference in rhos}
-%\\ 
-%&+ C \int_0^t \langle |\psi_{t-s}^{\epsilon,x}(z) - \psi_{t-s}^{\epsilon, y}(z) | 
-%\rho_\epsilon*\eta(z), \eta_s(dz) \rangle  ds | 
-%\label{eq:bound1CE} 
 \end{align} 
-%Recalling that $F$ is a polynomial, and 
-%using Lemma~\ref{Lemma:BoundPsiHS2} we can then write, 
-%\begin{align*}
-% \int &|\rho_\epsilon*\eta_s(x) -\rho_\epsilon*\eta_s(y)| \rho_\delta(x-y) dy  
-%\leq 
-%\int |p_{\epsilon^2+s}(y,z)-p_{\epsilon^2+s}(x,z)|\eta_0(dz) \rho_\delta(x-y)dy 
-%\\
-%&+ 
-%C\int_0^s \langle p_{\epsilon^2+s-r}(y,z)-p_{\epsilon^2+s-r}(x,z)|, \eta_r(dz) \rangle 
-%\rho_\delta (x-y) dr  
-%\\  
-%& + C \int\int_0^s \langle |p_{\epsilon^2+s-r}(y,z) - p_{\epsilon^2+s-r}(x,z) | 
-%\sum_{k=0}^na_k\rho_\epsilon*\eta_r(z)^k, \eta_r(dz) \rangle  dr\rho_\delta(y-x)dy    
-%\\ & + \int|M_s(y)-M_s(x)| \rho_\delta(y-x)dy  
-%\\  & 
-%+ \frac{C}{\epsilon^2 \theta} \int \langle \sum_{k=0}^na_k\rho_\epsilon*\eta(z)^k,
-%\eta_s(dz)\rangle ds   
-%+\mathcal{O}\left( \frac{1}{\epsilon^2 \theta} \right), 
-%\end{align*}
-%for some non-negative constants $a_k$.
-%By Lemma~\ref{} the last integral term is of 
-%order $(\epsilon^2 \theta)^{-1}$. 
-%Using Lemma~\ref{Lemma:ContinuityHS}, the contribution of the first 
-%three terms is bounded by,
-%\begin{align*}
-%\int &\langle \frac{|y-x|}{\sqrt{\epsilon^2+s}}
-%\Big(p_{2(\epsilon^2+s)}(x,z) +p_{2(\epsilon^2+s)}(y,z)\Big) 
-%\rho_{\delta}(y-x) dy, \eta_0(dz)\rangle 
-%\\
-%& + \int \int_0^s  
-%\langle \frac{\|y-x\|}{\sqrt{\epsilon^2+s-r}} 
-%\Big(p_{2(\epsilon^2+s-r)}(x,z) +p_{2(\epsilon^2+s-r)}(y,z)\Big) 
-%\rho_\delta(x-y) dy 
-%\sum_{k=0}^n\rho_\epsilon*\eta_r(z)^k, \eta_r(dz) dr 
-%\\ 
-%& +  \int \int_0^s \langle \frac{|y-x| \rho_\epsilon*\eta(z)}{\sqrt{\epsilon^2+s-r}}, \eta_r(dz) \rangle \rho_\delta(y-x) dy dr \\ 
-%& \leq 
-%\frac{\delta}{\sqrt{\epsilon^2+s}} %\langle 1, \eta_0(dz) \rangle 
-%+ \int_0^s \frac{\delta}{\sqrt{\epsilon^2+s-r}} 
-%\Big(p_{2(\epsilon^2+s-r)}(x,z) +p_{2(\epsilon^2+s-r+\delta)}(y,z)\Big) 
-%\sum_{k=0}^n a_k\rho_\epsilon*\eta_r(z)^k,
-%\eta_r(dz) \rangle dr.
-%\end{align*}
-%To finish the proof just notice that,
-%\begin{align*}
-%\int |M_s(y)-M_s(x)| \rho_\delta(y-x)dy \leq |M_s(x)| + \int |M_s(y)| \rho_\delta(y-x)dy.
-%\end{align*}
-%\end{proof}
-%
-
 Although this expression is lengthy, when we need to control its 
@@
 
-\begin{proposition} \label{CuadraticApprox}
+\begin{proposition} 
+\label{CuadraticApprox}
 Under the conditions of Theorem~\ref{thm:local_convergence},
@@
 \label{replacing nonlinear term}
-\lim_{N\to\infty}\Big|\int_0^t \IE\Big[\big\langle T_{\epsilon^2} f(y) 
+\lim_{\epsilon\to 0}\Big|\int_0^t \IE\Big[\big\langle T_{\epsilon^2} f(y) 
 F(\rho_\epsilon *\eta_s(y)), \eta_s(y) \big\rangle 
@@
 \end{equation}
-%is of order
-%\comment{Equation below needs to be filled in when we have the proof}
-%\begin{equation*}
-%\mathcal{O}\left( \frac{1}{\epsilon^2 \theta} + \epsilon^2 + \epsilon + \epsilon^{1/3}  + \left( \frac{\theta}{N \epsilon^d} \right)^{1/2}\right)
-%\end{equation*}
 \end{proposition}
@@
 the expression on the left hand side of~\eqref{replacing nonlinear term} is
-less than a constant times $\delta$, with a constant independent of $\delta$
-and $N$. Since $\delta$ is arbitrary, the result will follow.
+less than a constant times $\delta$, with a constant independent of $\delta$,
+$N$, and $\epsilon$. Since $\delta$ is arbitrary, the result will follow.
 
@@
 \label{target expression}
+	\lim_{\epsilon\to 0}
 	\int_0^t\big\langle \int |\rho_\epsilon*\eta_s(y)-\rho_\epsilon*\eta_s(w)|
@@
 p_{\epsilon^2}(w,y)dy, \eta_s(dw)\big\rangle ds
-\end{equation}
-goes to zero as $\epsilon\to 0$.
+=0.
+\end{equation}
 
@@
 \begin{multline*}
-\int_\delta^t\IE\Big[\big\langle\frac{\|y-w\|}{\sqrt{s+\epsilon^2}}
+\int_\delta^t\IE\Big[\Big\langle\int
+	\big\langle\frac{\|y-w\|}{\sqrt{s+\epsilon^2}}
 \big(p_{2(s+\epsilon^2)}(y,z)+p_{2(s+\epsilon^2)}(w,z)\big),\eta_o(dz)\big\rangle
@@
 \big(\rho_\epsilon*\eta_s(y)^k+\rho_\epsilon*\eta_s(w)^k\big)
-p_{\epsilon^2}(w,y)dy, \eta_s(dw)\big\rangle\Big] ds.
+p_{\epsilon^2}(w,y)dy, \eta_s(dw)\Big\rangle\Big] ds.
 \end{multline*}
@@
 C\int_\delta^t\frac{\epsilon}{\sqrt{s+\epsilon^2}}
-\IE\Big[\big\langle
+\IE\Big[\Big\langle\int\big\langle
 \big(p_{2(s+\epsilon^2)}(y,z)+p_{2(s+\epsilon^2)}(w,z)\big),\eta_0(dz)
@@
 \big(\rho_\epsilon*\eta_s(y)^k+\rho_\epsilon*\eta_s(w)^k\big)
-p_{2\epsilon^2}(w,y)dy, \eta_s(dw)\big\rangle ds\Big] .
+p_{2\epsilon^2}(w,y)dy, \eta_s(dw)\Big\rangle ds\Big] .
 \label{contribution from initial condition terms}
@@
 \int_\delta^t\frac{\epsilon}{\sqrt{s+\epsilon^2}}
-\IE\Big[\big\langle
-p_{2(s+\epsilon^2)}(y,z)   %+p_{2(s+\epsilon^2)}(w,z)\big)
+\IE\Big[\Big\langle\int\big\langle
+p_{2(s+\epsilon^2)}(y,z)   
 ,\eta_0(dz)
 \big\rangle
-\rho_\epsilon*\eta_s(y)^k %+\rho_\epsilon*\eta_s(w)^k\big)
-p_{2\epsilon^2}(w,y)dy, \eta_s(dw)\big\rangle  \Big] ds
+\rho_\epsilon*\eta_s(y)^k 
+p_{2\epsilon^2}(w,y)dy, \eta_s(dw)\Big\rangle  \Big] ds
 \]
@@
 \int_\delta^t\frac{\epsilon}{\sqrt{s+\epsilon^2}}
-\IE\Big[\big\langle
-p_{2(s+\epsilon^2)}(y,z)   %+p_{2(s+\epsilon^2)}(w,z)\big)
+\IE\Big[\int\int\big\langle
+p_{2(s+\epsilon^2)}(y,z)  
 ,\eta_0(dz)
 \big\rangle
-\rho_\epsilon*\eta_s(y)^k %+\rho_\epsilon*\eta_s(w)^k\big)
-p_{\epsilon^2}(x,y)dy \rho_\epsilon*\eta_s(x) dy dx ds\big\rangle ds \Big]
+\rho_\epsilon*\eta_s(y)^k 
+p_{\epsilon^2}(x,y) \rho_\epsilon*\eta_s(x) dy dx ds \Big]
 \\
@@
 \int_\delta^t\frac{\epsilon}{\sqrt{s+\epsilon^2}}
-\IE\Big[\big\langle
-p_{2(s+\epsilon^2)}(y,z)   %+p_{2(s+\epsilon^2)}(w,z)\big)
+\IE\Big[\int\int\big\langle
+p_{2(s+\epsilon^2)}(y,z)  
 ,\eta_0(dz)
@@
 \big(\rho_\epsilon*\eta_s(y)^{k+1} +\rho_\epsilon*\eta_s(x)^{k+1}\big)\Big]
-p_{\epsilon^2}(x,y) dy dx \big\rangle ds,
+p_{\epsilon^2}(x,y) dy dx ds,
 \end{multline*}
@@
 C\epsilon \int_\delta^t\frac{1}{\sqrt{s+\epsilon^2}}
-\IE\Big[\big\langle
-p_{2(s+\epsilon^2)}(y,z)   %+p_{2(s+\epsilon^2)}(w,z)\big)
+\IE\Big[\int\int\big\langle
+p_{2(s+\epsilon^2)}(y,z)  
 ,\eta_0(dz)
@@
 \big(\rho_\epsilon*\eta_0(y)+\rho_\epsilon*\eta_0(y)^{k+1} 
-+\rho_\epsilon*\eta_0(x)+
++\rho_\epsilon*\eta_0(x)
 +\rho_\epsilon*\eta_0(x)^{k+1}\big)\Big]
@@
 The term involving 
-$ %\[
+$ 
 \big\langle
-p_{2(s+\epsilon^2)}(w,z)   %+p_{2(s+\epsilon^2)}(w,z)\big)
+p_{2(s+\epsilon^2)}(w,z)   
 ,\eta_0(dz)
@@
 \rho_\epsilon*\eta_s(w)^k
-$ %\]
+$ 
 is handled similarly.
@@
 the contribution to~(\ref{contribution from initial condition terms})
-from this term of the form $C\epsilon/\delta^{(d+1)/2}$.
+from this term of the form
+\[C\epsilon\int_\delta^t\frac{1}{(s+\epsilon^2)^{d/2}}ds.\]
 Note that for fixed $\delta$, this bound tends to zero as $\epsilon\to 0$.
 
-Now consider
+Now consider the contribution to he left hand side of~(\ref{target expression})
+from the second term in~(\ref{difference in rhos}). Since $F$ is a polynomial,
+it is bounded by a sum of terms of the form
 \begin{multline*}
-\int_\delta^t\int_0^{s-\delta}\Big\langle\frac{\|y-x\|}{\sqrt{s-r+\epsilon^2}}
+\int_\delta^t\int_0^{s-\delta}\Big\langle\int\frac{\|y-w\|}{\sqrt{s-r+\epsilon^2}}
 \big\langle\big(p_{2(s-r+\epsilon^2)}(y,z)+ p_{2(s-r+\epsilon^2)}(w,z)\big)
@@
 \\
-\rho_\epsilon*\eta_s(y)^kp_{\epsilon^2}(y,w),\eta_s(dw)
+\rho_\epsilon*\eta_s(y)^kp_{\epsilon^2}(y,w)dy,\eta_s(dw)
 \Big\rangle ds
@@
 \leq C\epsilon
-\int_\delta^t\int_0^{s-\delta}\Big\langle\frac{1}{\sqrt{s-r+\epsilon^2}}
+\int_\delta^t\int_0^{s-\delta}
+	\frac{1}{\sqrt{s-r+\epsilon^2}}
+	\Big\langle\int
 \big\langle
@@
 \\
-\rho_\epsilon*\eta_s(y)^kp_{2\epsilon^2}(y,w),\eta_s(dw)
+\rho_\epsilon*\eta_s(y)^kp_{2\epsilon^2}(y,w)dy,\eta_s(dw)
 \Big\rangle ds,
@@
 \int\Big\langle 
-\big\langle p_{2(s-r+\epsilon^2}(y,z)\rho_\epsilon*\eta_r(z)^j, \eta_r(dz)
+\big\langle p_{2(s-r+\epsilon^2)}(y,z)\rho_\epsilon*\eta_r(z)^j, \eta_r(dz)
 \big\rangle
@@
 \int\int
-\big\langle p_{2(s-r+\epsilon^2}(y,z)\rho_\epsilon*\eta_r(z)^j, \eta_r(dz)
+\big\langle p_{2(s-r+\epsilon^2)}(y,z)\rho_\epsilon*\eta_r(z)^j, \eta_r(dz)
 \big\rangle
@@
 \IE\Big[\big\langle \rho_\epsilon*\eta_r(z)^{j+k+1}, \eta_r(dz)\rangle\Big]
-+\IE\Big[\int p_{2(s-r)}(y,x)\rho_\epsilon*\eta_r(x)\rho_\epsilon*\eta_r(y)^{k+1} dy dx\Big]
++\IE\Big[\int\int p_{2(s-r)}(y,x)\rho_\epsilon*\eta_r(x)\rho_\epsilon*\eta_r(y)^{k+1} dy dx\Big]
 \\
@@
 
-It remains to control the contribution arising from the martingale terms 
+We now turn to the contribution arising from the martingale terms 
 in~(\ref{difference in rhos}):
@@
 
-The other terms follow in a similar way.
+Control of the terms arising from approximating $\psi^{\epsilon,x}$
+by the heat kernel follows in an entirely analogous way.
 
@@
 take a convergent subsequence 
-$\big\{\big(\rho_\epsilon*\eta_t(dx)\big)_{t\geq 0}\big\}$ 
-converging to a limit point $\big(u_t(x)dx\big)_{t\geq 0}$, then
+$\big\{\big(\rho_\epsilon*\eta_t^N(dx)\big)_{t\geq 0}\big\}$ 
+converging to a limit point $\big(\varphi(t,x)dx\big)_{t\geq 0}$, then
 \[ 
-\int f(x) \rho_\epsilon * \eta_t(x) F(\rho_\epsilon * \eta_t(x)) dx 
-\rightarrow \int f(x) u_t(x) F(u_t(x)) dx. 
+\int_0^t
+\int f(x) \rho_\epsilon * \eta_s(x) F(\rho_\epsilon * \eta_s^N(x)) dx ds 
+\rightarrow \int_0^t\int f(x) \varphi(s,x) F(\varphi(s,x)) dx ds. 
 \]
@@
 \label{eq:QuadConvergence} 
-\int f(x) \rho_\epsilon * \eta_t(x) \rho_\epsilon * \eta_t(x)^2 dx 
-\rightarrow \int f(x) u_t(x) u_t(x)^2 dx. 
+\int_0^t\int f(x) 
+\rho_\epsilon * \eta_s^N(x)^2 dx ds
+\rightarrow \int_0^t \int f(x) 
+\varphi(s,x)^2 dx ds. 
 \end{equation}
@@
 
-The approach is standard. We fix $\delta>0$ and in keeping with
-our notation $\rho_\epsilon$ in this subsection, use $\rho_\delta$ to 
-denote the symmetric Gaussian kernel with variance parameter $\delta^2$.
-Our strategy is to show that, up to an error of $\mathcal{O}(\delta)$,
-\begin{equation}
-\label{aprox2}
-\int f(z) \rho_\epsilon*\eta_s(z)^2 dz
-%(\eta_s * \rho_\epsilon)^2 \rangle 
+The approach is standard. We fix $\tau>0$ and, in keeping with
+our notation $\rho_\epsilon$, in this subsection, use $\rho_\tau$ to 
+denote the symmetric Gaussian kernel with variance parameter $\tau^2$.
+Our strategy is to show that, up to an error that tends
+to zero as $\tau \to 0$, 
+\begin{equation}
+\label{approx2}
+\int_0^t\int f(z) \rho_\epsilon*\eta_s(z)^2 dz ds
 \sim 
-\int \int f(z) (\rho_\epsilon * \eta_s)(z) 
-\rho_\delta (z-y) (\rho_\epsilon * \eta_s)(y) dz dy.
-\end{equation}
-Analogously, also up to an error of $\mathcal{O}(\delta)$,
-\begin{equation}
-\label{aprox3}
-\int f(z) u_s(z)^2 dz
-%(\eta_s * \rho_\epsilon)^2 \rangle 
+\int_0^t\int \int f(z) (\rho_\epsilon * \eta_s)(z) 
+\rho_\tau (z-y) (\rho_\epsilon * \eta_s)(y) dz dy ds.
+\end{equation}
+Analogously, also up to an error that vanishes as $\tau \to 0$,
+\begin{equation}
+\label{approx3}
+\int_0^t\int f(z) \varphi(s,z)^2 dz ds
 \sim 
-\int \int f(z) u_s(z) 
-\rho_\delta (z-y) u_s(y) dz dy.
+\int_0^t\int \int f(z) \varphi(s,z) 
+\rho_\tau (z-y) \varphi(s,y) dz dy ds.
 \end{equation}
@@
 weak convergence of $\rho_\epsilon * \eta$ 
-(plus continuity of the mapping $(z,y) \rightarrow f(z) \rho_\delta(z-y)$) 
+(plus continuity of the mapping $(z,y) \rightarrow f(z) \rho_\tau(z-y)$) 
 gives that 
 \begin{equation}
-\int \int f(z) (\rho_\epsilon * \eta_s)(z) 
-\rho_\delta (z-y) (\rho_\epsilon * \eta_s)(y) dz dy
-\to \int \int f(z) u_s(z) 
-\rho_\delta (z-y) u_s(y) dz dy.
-\end{equation}
-Since $\delta$ is arbitrary, the 
+\int_0^t\int \int f(z) (\rho_\epsilon * \eta_s)(z) 
+\rho_\tau (z-y) (\rho_\epsilon * \eta_s)(y) dz dy ds
+\to \int_0^t \int \int f(z) \varphi(s,z) 
+\rho_\tau (z-y) \varphi(s,y) dz dy ds.
+\end{equation}
+Since $\tau$ is arbitrary, the 
 convergence~(\ref{eq:QuadConvergence})
@@
 
-UP TO HERE
-
-\begin{theorem}
-Under the conditions of Theorem~\ref{TeoremOneStepConvergence}, we have that
-\begin{align*}
-\int_0^t \mathbb{E}&\left[\left| \langle f(y), (\eta_s * \rho_\epsilon(y))^2) dy\rangle - \int \int f(y) (\rho_\epsilon * \eta_s)(z) \rho_\delta (z-y) (\rho_\epsilon * \eta_s)(y) dz dy.
-\right|\right] ds
-\end{align*}
-is bounded by,
-\[  \mathcal{O}\left(\delta^{1/3} + \delta +  \frac{1}{\epsilon^2 \theta} + \left( \frac{\theta}{N \epsilon^2}\right)^{1/2} \right)  \]
-in particular, under (\ref{ConditionsForConvergence}), the last term goes to $0$ uniformly in $\theta,\epsilon,N$ and $\delta$ (when $\delta$, $\epsilon$ go to $0$ and $N,\theta$ to infinity).
-\end{theorem}
+\begin{proposition}
+	\label{quadratic convergence}
+Under the conditions of Theorem~\ref{thm:local_convergence}, we have that
+along any convergent subsequence,
+\begin{multline}
+\label{approx4}
+\limsup_{\epsilon \to 0}
+\IE\Big[\Big|
+\int_0^t\int f(y) \rho_\epsilon*\eta_s(y)^2 dy ds
+\\
+-
+\int_0^t\int \int f(z) (\rho_\epsilon * \eta_s)(z) 
+\rho_\tau (z-y) (\rho_\epsilon * \eta_s)(y) dz dy ds\Big|\Big]\leq C\tau,
+\end{multline}
+where $C$ is independent of $\tau$.
+\end{proposition}
 \begin{proof}
@@
 &\int_0^t 
-\mathbb{E}\left[| \langle f(y), (\eta_s * \rho_\epsilon(y))^2) dy \rangle 
-- \int \int f(y) (\rho_\epsilon * \eta_s)(z) \rho_\delta (z-y) 
-(\rho_\epsilon * \eta_s)(y) dz dy. |\right] ds 
+\mathbb{E}\left[\big| \langle f(y), (\eta_s * \rho_\epsilon(y))^2) dy \rangle 
+- \int \int f(y) (\rho_\epsilon * \eta_s)(z) \rho_\tau (z-y) 
+(\rho_\epsilon * \eta_s)(y) dz dy \big|\right] ds 
 \nonumber 
@@
 \mathbb{E}\left[ \int \left\{ \left|(\rho_\epsilon * \eta_s)(y)
--(\rho_\epsilon * \eta_s)(z) \right|   \rho_\delta(z-y) dz \right\} 
+-(\rho_\epsilon * \eta_s)(z) \right|   \rho_\tau(z-y) dz \right\} 
 (\rho_\epsilon *\eta_s)(y) \right] ds  dy 
@@
 \end{align}
+Now proceed exactly as in the proof of 
+Proposition~\ref{CuadraticApprox}.
+The only distinction is that $|p_{\epsilon^2}(y,z)-p_{\epsilon^2}(w,z)|$
+is replaced by $|p_{\tau}(y,z)-p_{\tau}(w,z)|$ and 
+the estimate $\|y-w\|p_{\tau^2}(y,w)\leq C\tau p_{2\tau^2}(y,w)$
+replaces the corresponding statement with $\epsilon^2$ replacing 
+$\tau^2$ in our previous argument.
 \end{proof}
 
-\paragraph{Conclusion}
-Under the condition (\ref{ConditionsForConvergence}) we have that all the errors in our approximations go to $0$.
-It is then we can deduce that quadratic (and analogously, higher order) terms in the martingale problem for $\rho_\epsilon*\eta_t(x)dx$, (\ref{MGPT_epsilon}), converges to the corresponding term of the weak limit.
-Any linear term converge trivially by weak convergence.
-By a Taylor's expansion we can also conclude that,
-\begin{align*}
-\int_0^t \langle \mathcal{L}^\theta T_{\epsilon^2} f, \eta_s(dx)\rangle ds &= \int_0^t \langle \frac{1}{2} \Delta T_{\epsilon^2} f(x), \eta_s(dx) \rangle + \mathcal{O}(\theta^{-1}) 
-\\ &= \int_0^t \langle \frac{1}{2} \Delta f(x), \rho_\epsilon* \eta_s(x) dx \rangle ds + \mathcal{O}(\theta^{-1} + \epsilon).
-\end{align*}
-Thus, by weak convergence we can deduce
-\[ \int_0^t \langle \mathcal{L}^\theta T_{\epsilon^2} f, \eta_s(dx)\rangle ds \rightarrow \int_0^t \langle \frac{1}{2} \Delta f(x), u_s(x) dx \rangle ds \]
-Putting all the convergences together, this identifies the limit of $\rho_\epsilon*\eta_s(x)dx$ as we have claimed in Theorem~\ref{TeoremOneStepConvergence}.
-
-\todo[inline]{END OneStepConvergence}
+The extension of Proposition~\ref{quadratic convergence}
+to higher moments is straightforward, if notationally messy. For 
+fixed (but arbitrary) $\tau$, one shows that
+\begin{multline*}
+	\limsup_{\epsilon\to 0}
+	\IE\Big[\Big|
+	\int_0^t\int f(y)\rho_\epsilon*\eta_s^N(y)^k dy ds
+\\
+	- \int_0^t\int\cdots\int f(y_1)
+	\rho_\epsilon*\eta_s^N(y_1) 
+\prod_{i=2}^{k}\rho_\tau (y_i-y_{i-1})\rho_\epsilon*\eta_s^N(y_i)
+dy_{k}\ldots dy_1 ds\Big| \Big]
+	\\
+	\leq C\tau,
+\end{multline*}
+with a corresponding statement when $\rho_\epsilon*\eta_s^N(x)$ is replaced
+by $\varphi(s,x)$ and then use weak convergence to see that, up to an error 
+of order $\tau$, any limit point of
+the sequence $\{\rho_\epsilon*\eta^N(x)dx\}$ solves (the weak form 
+of) equation~(\ref{target equation in local convergence}).
+Since $\tau$ was arbitrary, the proof of Theorem~\ref{thm:local_convergence}
+is complete.
 
@@
 Furthermore, if we define $\Xi_t = \lim_{u_0 \to \infty} \frac{1}{u_0}\lp_t(dx \times [0,u_0])$,
-then the limit model $(\eta_t(dx))_{t \geq 0}$ defined in Theorem \label{thm:nonlocal_convergence}
+then the limit model $(\eta_t(dx))_{t \geq 0}$ defined in Theorem \ref{thm:nonlocal_convergence}
 and $(\Xi_t(dx))_{t \geq 0}$

### 2023-03-09 forwards-and-backwards.tex
up until MMT

@@
 \\   
-Department of Statistics & Department of Mathematics \\
+Department of Statistics & Departments of Mathematics and Biology\\
 Oxford University &University of Oregon\\                   
@@
 We introduce a broad class of mechanistic spatial models to describe how spatially 
-heterogeneous populations live, die, and reproduce. Birth and death rates can depend 
-both on spatial position and local population density, defined at a 
-spatial position $x$ to be the convolution 
-of the point measure encoding the distribution of individuals in the population
+heterogeneous populations live, die, and reproduce.
+Individuals are represented by points of a point measure,
+whose birth and death rates can depend 
+both on spatial position and local population density, defined at a location
+to be the convolution of the point measure
 with a suitable non-negative integrable kernel
-centred on $x$. We pass to three different scaling limits:
+centred on that location. We pass to three different scaling limits:
 an interacting superprocess, a nonlocal partial differential equation (PDE), 
@@
 
-A novelty of our model is that in describing the dynamics we explicitly
+A novelty of our model is that we explicitly
 model a juvenile phase: the number of juveniles produced by an individual depends
@@
 around the location of the parent; they then reach (instant) maturity with a probability
-that can depend on the local population density (possibly measured through convolution
-with a different kernel from that used in determining fecundity) 
+that can depend on the local population density
+% (possibly measured through convolution with a different kernel from that used in determining fecundity) 
 at the location at which they land. 
@@
 a population evolving according to any of these models will
-either die out or grow without bound and, in so doing, it can
+either die out or grow without bound and, in so doing, can
 develop clumps of arbitrarily large density and extent. 
@@
 Brownian motion during their lifetime, 
-in our model, offspring
-are thrown off according to some 
-spatial distribution centred on the location of the parent.   
+in our model, offspring are thrown off according to some 
+spatial distribution centred on the location of the parent
+and do not subsequently move.
 This is particularly appropriate for modelling plant populations, in which
@@
 for example, the number of adults produced by a single parent is determined
-by the degree of crowding at the location of the parent. A novelty
-of the models that we introduce here is that, although we shall only
-follow the adult population, in formulating the dynamics of the
+by the degree of crowding at the location of the parent.
+Although we shall similarly only follow the adult population, in formulating the dynamics of the
 models we shall distinguish
@@
 for the two stages of reproduction. 
-When the limit is deterministic,
+When the limiting population process is deterministic,
 it is a (weak) solution of an equation of the form
@@
 \end{equation}
-where $\DG^*$ is (the adjoint of) a strictly uniformly elliptic
-second order differential operator, typically
-the Laplacian.
+where
+$\varphi_t(x)$ can be thought of as the population density at $x$
+(although the limit may be a measure without a density), and
+$\DG^*$ is (the adjoint of) a strictly uniformly elliptic second order differential operator, typically the Laplacian.
+The dependence of each of the terms $r$, $\gamma$, and $F$ on $\varphi$ is only through the local density at $x$,
+e.g., $F(x, \varphi) = F(x, \smooth{} \varphi(x))$.
 We shall be more specific about the parameters below.
@@
 When the population follows~(\ref{general deterministic limit}), 
-we can expect that taking a second limit by scaling the kernels appearing
-in $r$, $\gamma$, and $F$ in this way, so that
-in the limit as $\epsilon\to 0$
-interactions are pointwise, we should
-recover a nonlinear PDE.
+we expect that if we take a second limit of $\epsilon \to 0$,
+thus scaling the kernels appearing in $r$, $\gamma$, and $F$ and making interactions are pointwise,
+we should recover a nonlinear PDE.
 We verify that this is indeed the case in two important examples:
@@
 and $\rho_F$ is a Gaussian density. We allow a wide class of reaction terms, $F$, so
-that the Fisher-KPP equation emerges as a special case.
+that the Fisher-KPP equation 
+(that is equation~(\ref{semilinear PDE}) with $\DG=\Delta$ and $F(\varphi)=1-\varphi$)
+emerges as a special case.
 
@@
 results concern spin systems \comment{REFs}. However,~\cite{flandoli/huang:2021} 
-obtain the Fisher-KPP equation (that is equation~(\ref{semilinear PDE}) with 
-$\DG=\Delta$ and $F(\varphi)=1-\varphi$) as a scaling limit of interacting diffusions in
+obtain the Fisher-KPP equation
+as a scaling limit of interacting diffusions in
 $\IR^d$. In that setting a major challenge (also apparent in our models), not
@@
 population density tends to infinity, whereas they also consider the situation in which
-that number remains finite; furthermore, whereas we shall consider a scaling in which 
-the reproduction mechanism is near-critical
-and look at large timescales,~\cite{flandoli/huang:2021}
-only scale the number of
-particles in the system and the size of the neighbourhood over which indivduals
-interact.
+that number remains finite; furthermore.
+On the other hand, we shall consider a scaling in which 
+the reproduction mechanism is near-critical and look at large timescales,
+while \citet{flandoli/huang:2021} only scale the number of
+particles in the system and the size of the neighbourhood over which indivduals interact.
 
@@
 individuals in a sample from the population, and these have been shaped 
-by its history. It is therefore of interest
-to establish information about the distribution of genealogical trees 
+by its history \citep{neigel1993application,kelleher2019inferring}.
+It is therefore of interest to establish information about the distribution of genealogical trees 
 under our population model.
@@
 
-Most work has focused on models that caricature the classical Fisher-KPP equation with a 
+Most work on this topic has focused on models that caricature the classical Fisher-KPP equation with a 
 stochastic term, i.e.
@@
 wave changes from ``pulled'' to ``pushed'', 
-\cite{birzu/hallatschek/korolev:2017, birzu/hallatschek/korolev:2021}.
+\citep{birzu/hallatschek/korolev:2017, birzu/hallatschek/korolev:2021}.
 In that setting, the genealogies will be quite different
@@
 %\comment{Could refer to more recent Birzu et al paper here.}
-For example, \cite{etheridge/penington:2022}
+For example, \citet{etheridge/penington:2022}
 show that for a discrete space model corresponding to this 
@@
 Fisher KPP equation, the solution at time $t$
-vanishes beyond $x=x_0+ct$ for some constant wavespeed
-$c>0$, \cite{kamin/rosenau:2004}.
+vanishes beyond $x=x_0+ct$ for some constant wavespeed $c>0$, \citep{kamin/rosenau:2004}.
 As a first step towards understanding what we should expect in models with
@@
 which we shall take to be $\IR^d$. 
-For applications, $d=1$ or $d=2$, but our main results apply more generally.
+For applications, $d=1$ or $d=2$
+(or even $d=3$ for cells within the body),
+but our main results apply more generally.
 At time zero, the population is distributed over a bounded region, with 
@@
 \end{align}
-where $F(x, m) : \IR^d \times \IR_{\ge 0} \to \IR$ and
-$\rho_F$ is again a smooth kernel.
+where this equation defines $F(x, m) : \IR^d \times \IR_{\ge 0} \to \IR$,
+the net per capita reproductive rate, scaled by $\theta$,
+and $\rho_F$ is again a smooth kernel. 
+It will be convenient to work with $F$ instead of $\mu$.
 
@@
 $$
-and similarly write $r(x, \eta)$ for $r(x, \smooth{r} \eta(x))$
+and similarly write $r(x, \eta)$ for $r(x, \smooth{r} \eta(x))$,
+$F(x, \eta)$ for $F(x, \smooth{F} \eta(x))$,
 and $\mu_\theta(x, \eta)$ for the expression of equation~\eqref{eqn:mu_defn}.
 When convenient, we may also suppress the arguments completely,
-writing simply $\gamma$, $r$, and $\mu_\theta$ for these quantities.
+writing simply $\gamma$, $r$, $F$, and $\mu_\theta$ for these quantities.
 \end{notation}
 
+\comment{Do we need a "Terminology" heading for this?}
 \begin{terminology*}
@@
 Under our scaling, $N$ and $\theta=\theta(N)$ will tend to infinity in such a 
-way that $\alpha:=\lim_{N\to\infty}\theta(N)/N$ exists. From the 
-expression~(\ref{eqn:prelimit_martingale_variation}) it is easy to guess that 
-whether the limit points will be deterministic or stochastic processes 
+way that $\alpha:=\lim_{N\to\infty}\theta(N)/N$ exists and is finite.
+From the expression~(\ref{eqn:prelimit_martingale_variation}) it is easy to guess that 
+whether the limiting processes will be deterministic or stochastic
 is determined by whether $\alpha$ is zero or nonzero.
@@
 	    \label{drift in adjoint}
+        % &=
+        % \sum_{ij} \partial_{x_i} \partial_{x_j} (\covq(x)_{ij} f(x))
+	    % -\nabla f(x)\cdot \meanq(x)-f(x)\nabla\cdot\meanq(x).
         &=
-        \sum_{ij} \partial_{x_i} \partial_{x_j} (\covq(x)_{ij} f(x))
-	    -\nabla f(x)\cdot \meanq(x)-f(x)\nabla\cdot\meanq(x).
-        %\text{TODO} .
+        \sum_{ij} C_{ij}(x) \partial_{x_i} \partial_{x_j} f(x)
+        + \sum_i \left(
+            \sum_j \partial_{x_j} C_{ij}(x) - \meanq_i(x)
+        \right) \partial_{x_i} f(x)
+        \\ & \qquad {}
+        + \left(
+            \sum_{ij} \partial_{x_i} \partial_{x_j} C_{ij}(x)
+            -
+            \sum_i \partial_{x_i} \meanq_i(x)
+        \right) f(x) .
     \end{align}
@@
 \begin{enumerate}
-    \item $\meanq(x)$, $\covq(x)$ are uniformly bounded in each component;
-    \item $\meanq(x)$ and $\covq(x)$ are $\alpha$-H\"older continuous in each component, 
-	    for some $\alpha \in (0,1]$;
+    \item $\meanq(x)$ and $\covq(x)$ are
+        $\alpha$-H\"older continuous for some $\alpha \in (0, 1]$
+        and uniformly bounded
+        in each component;
+    % \item $\meanq(x)$ and $\covq(x)$ are $\alpha$-H\"older continuous in each component, for some $\alpha \in (0,1]$;
     \item the operator $\DG$ is uniformly strictly elliptic.
@@
 \item $\gamma(x,m)$ is uniformly bounded;
-\item Either
+\item $|\gamma(x, \smooth{\gamma} \eta(x)) \theta \int (r(y, \smooth{r} \eta(y)) - r(x, \smooth{r} \eta(x))) q_\theta(x, dy)|$
+    is uniformly bounded for $x \in \IR^d$ and $\eta \in \measures$.
+\end{enumerate}
+
+To keep expressions manageable, we shall also assume that 
+\[
+\mu_\theta(x) = r(x, \smooth{r} X(x) / N) \gamma(x, \smooth{\gamma} X(x) / N)
+        - \frac{1}{\theta} F(x, \smooth{F} X(x) / N),
+\]
+that is, this expression is non-negative so that there is no need to take the maximum
+	with zero in~(\ref{eqn:mu_defn}). (This is anyway true for 
+	sufficiently large $\theta$.)
+\end{assumptions}
+
+We give two more concrete conditions under which the fourth condition is satisfied.
+
+\begin{lemma}
+    \label{lem:conditions on r}
+If either
 \begin{enumerate}
@@
 \label{control through r} 
-$|\partial_{x_i}r(x,\smooth{r}\eta(x)|$ and 
-$|\partial_{x_ix_j}r(x,\smooth{r}\eta(x)|$
+    $|\partial_{x_i}r(x,\smooth{r}\eta(x))|$ and 
+    $|\partial_{x_ix_j}r(x,\smooth{r}\eta(x))|$
     are uniformly bounded for $x\in\IR^d$, $\eta\in\measures$;
@@
 \end{enumerate} 
-\end{enumerate}
-
-To keep expressions manageable, we shall also assume that 
-\[
-\mu_\theta(x) = r(x, \smooth{r} X(x) / N) \gamma(x, \smooth{\gamma} X(x) / N)
-        - \frac{1}{\theta} F(x, \smooth{F} X(x) / N),
-\]
-that is, this expression is non-negative so that there is no need to take the maximum
-	with zero in~(\ref{eqn:mu_defn}). (This is anyway true for 
-	sufficiently large $\theta$.)
-\end{assumptions}
+then
+$|\gamma(x, \smooth{\gamma} \eta(x)) \theta \int (r(y, \smooth{r} \eta(y)) - r(x, \smooth{r} \eta(x))) q_\theta(x, dy)|$
+is uniformly bounded for $x \in \IR^d$ and $\eta \in \measures$.
+\end{lemma}
 
@@
 because of the non-local reproduction mechanism, it no longer suffices to assume that 
-$r(x,\smooth{r}\eta(x))\gamma(x, \smooth{\gamma}\eta(x))-\mu_\theta(x)$ is of order 
-$1/\theta$. The conditions that we have imposed are to ensure that the difference 
-between the establishment probability of a juvenile born of a parent at $x$ and dispersed
-to a position $y$, determined by $q_{\theta}(x,dy)$, and its establishment probability had
-it remained at $x$ are also order $1/\theta$.
+$r(x,\smooth{r}\eta(x))\gamma(x, \smooth{\gamma}\eta(x))-\mu_\theta(x)$ is of order $1/\theta$.
+An instructive example is the case where $\gamma \equiv 1$ and $F \equiv 0$, so that $\mu_\theta = r$,
+and the population has all individuals at a single location (so, $\eta = \delta_x$),
+in which case the mean rate of change of the total population size
+is $\int (r(y, N \smooth{r}(y) ) - r(x, N \smooth{r}(x))) q_\theta(x, dy)$;
+the first condition of Lemma~\ref{conditions on r} would ensure this is of order $1/\theta$.
 
@@
 and for superprocess limits with nonlocal interactions.
-See Figure \ref{fig:super_vs_det_2d} for illustrative simulations.
+See Figure \ref{fig:super_vs_det_2d} for illustrative simulations,
+from direct simulation of the process using SLiM \citep{haller_slim_2019}.
 
@@
     \begin{center}
-        %\includegraphics{figures/ex1a/fkpp_123.locations}
-        %\includegraphics{figures/ex1b/fkpp_123.locations}
+        \includegraphics{figures/ex1a/fkpp_123.locations}
+        \includegraphics{figures/ex1b/fkpp_123.locations}
     \end{center}
@@
 when $\alpha>0$.
-However, the Dawson Girsanov transform tells us that we have uniqueness in this special 
+However, the Dawson--Girsanov transform tells us that we have uniqueness in this special 
 case of the superprocess with nonlinear death rates, and 
@@
     is a \emph{weak solution} to the PDE
-   \[ 
+    \begin{equation} \label{eqn:nonlocal_pde}
         \partial_t \varphi = r \DG^*(\gamma \varphi) + \varphi F
-    \]
+    \end{equation}
 	(where $r$, $\gamma$ and $F$ can all be functions of $\varphi$)
@@
 \end{definition}
-the notation $\varphi$ is meant to be suggestive of a density.
-Because Theorem~\ref{thm:nonlocal_convergence} only tells us about 
-weak convergence, in the case $\alpha=0$ we can only deduce that 
-any limit point $\eta_t$ is a weak solution to the nonlocal PDE
-    \begin{equation} \label{eqn:nonlocal_pde}
+The notation $\varphi$ is meant to be suggestive of a density,
+and recall that equation~\eqref{eqn:nonlocal_pde} has made dependencies on $x$ and $\varphi$ implicit;
+written out more explicitly, \eqref{eqn:nonlocal_pde} is
+\[
     \partial_t \varphi_t(x)
@@
     .
-    \end{equation}
+\]
+Because Theorem~\ref{thm:nonlocal_convergence} only tells us about 
+weak convergence, in the case $\alpha=0$ we can only deduce that 
+any limit point $\eta_t$ is a weak solution to this nonlocal PDE.
 
@@
 We write 
-$\gamma(x,\eta)C(x)=J(x,\eta)J(x,\eta)^T$, and 
-$\beta(x,\eta)=\gamma(x,\eta)\big(\meanq(x)+2C(x)\nabla\log r(x,\eta)\big)$.
+$r(x,\eta) \gamma(x,\eta) C(x) = J(x,\eta) J(x,\eta)^T$, and 
+$\beta(x,\eta) = r(x,\eta) \gamma(x,\eta) \big(\meanq(x)+2C(x)\nabla\log r(x,\eta)\big)$
+(quantities that will appear in Proposition~\ref{prop:limiting_construction}).
 If $J$, $\beta$, and $F$ are bounded and Lipschitz in the sense 
@@
 
-To understand the form of equation~(\ref{eqn:nonlocal_pde}) a little better, 
-and, in particular, why we see $\DG^*$ rather than $\DG$ in the equation for the 
-limiting population density, we consider the two terms that contribute to the drift in our 
-expression~(\ref{drift in adjoint})
-for $\DG^*$. First consider a special case in which dispersal has a mean drift 
-to the right, so that the drift term in $\DG$ is $d/dx$, and the effect of the drift is 
-just to shift the population profile to the right. If we are at a point where the 
-slope of the population density is positive, then the shift will {\em reduce} the
-population density at the point; the change in population density is proportional
-to $-d/dx$. Similarly, if dispersal tends to move offspring away from a region, that
-is if $\grad\cdot\meanq >0$, 
-then it will push down the population density, hence the term $-\grad\cdot\meanq$ in
-equation~(\ref{eqn:nonlocal_pde}).
+% PLR: perhaps we don't need this?
+% To understand the form of equation~(\ref{eqn:nonlocal_pde}) a little better, 
+% and, in particular, why we see $\DG^*$ rather than $\DG$ in the equation for the 
+% limiting population density, we consider the two terms that contribute to the drift in our 
+% expression~(\ref{drift in adjoint})
+% for $\DG^*$. First consider a special case in which dispersal has a mean drift 
+% to the right, so that the drift term in $\DG$ is $d/dx$, and the effect of the drift is 
+% just to shift the population profile to the right. If we are at a point where the 
+% slope of the population density is positive, then the shift will {\em reduce} the
+% population density at the point; the change in population density is proportional
+% to $-d/dx$. Similarly, if dispersal tends to move offspring away from a region, that
+% is if $\grad\cdot\meanq >0$, 
+% then it will push down the population density, hence the term $-\grad\cdot\meanq$ in
+% equation~(\ref{eqn:nonlocal_pde}).
 
 \paragraph{Two-step convergence to PDE:}
-
 Although the coefficients at $x$ in \eqref{eqn:nonlocal_pde} are nonlocal,
@@
 |F(n)-F(m)|
-\leq|n-m|\sum_{j=1}^{k'}b_j\Big(n^j+m^j),
+\leq|n-m|\sum_{j=1}^{k'}b_j\Big(n^j+m^j\Big),
 \]
@@
 a \emph{lineage} $(L_t^N)_{t \ge 0}$,
-begun at spatial location $L_0^N = x$,
-can be obtained by picking a focal individual uniformly at 
-random from the population at $x$
-(actually, in the prelimit,
-there will be at most one individual at any point $x$),
-and then, for each time $t$,
+begun at a spatial location $L_0^N = x$
+where there is a focal individual in the present day
+can be obtained by, for each time $t$,
 setting $L_t^N$ to be the spatial location of the individual alive at time $t$
@@
 individuals from a given 
-region is equivalent to looking at the individuals in that region with the $k$ lowest
-levels. Moreover, as we pass to 
+region is equivalent to looking at the individuals in that region with the $k$ lowest levels.
+Moreover, as we pass to 
 the infinite population (and therefore infinite level) limit,
 the collection of (individual, level) pairs 
-for which the levels are below 
-any fixed value converges, Theorem~\ref{}. 
+converges, Theorem~\ref{thm:lookdown_convergence}.
 See~\citet{etheridge/kurtz:2019} for an introduction to these ideas.
@@
 There will be no 
-coalescence of ancestral lineages in the deterministic limit, but our results can
+coalescence of ancestral lineages in the deterministic limit,
+but understanding motion of single lineages is useful in practice,
+and our results can
 be seen as a first step towards understanding genealogies for very high population 
@@
 
+\begin{corollary}
+    \comment{TODO: write corollary saying what's in the previous sentence 
+    and what the stationary distribution is?}
+\end{corollary}
+
 \begin{corollary} \label{cor:wavefront}
@@
     \begin{align*}
-        r \DG* (\gamma w) + w F + \wavespeed \cdot \grad w = 
+        r \DG^* (\gamma w) + w F + \wavespeed \cdot \grad w = 
 r\sigma^2\Delta (\gamma w) -\meanq \cdot\grad (\gamma w) +\wavespeed \cdot \grad w =0 .
@@
 \comment{I don't understand this - something has gone wrong.}
+\comment{TODO: peter to look into this}
 Birth and death rates are equal at density $m = 1$,
@@
     \begin{center}
-        %\includegraphics[width=0.45\textwidth]{figures/ex2a/pme_123.steps}
-        %\includegraphics[width=0.45\textwidth]{figures/ex2b/pme_123.steps}
+        \includegraphics[width=0.45\textwidth]{figures/ex2a/pme_123.steps}
+        \includegraphics[width=0.45\textwidth]{figures/ex2b/pme_123.steps}
     \end{center}
@@
     \begin{center}
-        %\includegraphics{figures/ex3_fkpp/fkpp_123.lineages}
-        %\includegraphics{figures/ex3_fkpp/fkpp_123.lineagehist}
-        %\includegraphics{figures/ex3_pme/pme_123.lineages}
-        %\includegraphics{figures/ex3_pme/pme_123.lineagehist}
-        %\includegraphics{figures/ex3_allen-cahn/allen-cahn_123.lineages}
-        %\includegraphics{figures/ex3_allen-cahn/allen-cahn_123.lineagehist}
+        \includegraphics{figures/ex3_fkpp/fkpp_123.lineages}
+        \includegraphics{figures/ex3_fkpp/fkpp_123.lineagehist}
+        \includegraphics{figures/ex3_pme/pme_123.lineages}
+        \includegraphics{figures/ex3_pme/pme_123.lineagehist}
+        \includegraphics{figures/ex3_allen-cahn/allen-cahn_123.lineages}
+        \includegraphics{figures/ex3_allen-cahn/allen-cahn_123.lineagehist}
     \end{center}
@@
 the Fisher-KPP equation,
-a special case of the Allen-Cahn equation with a bistable nonlinearity, and
-equation~(\ref{PME}).
+a special case of the Allen-Cahn equation with a bistable nonlinearity,
+and the porous media equation with logistic growth, equation~(\ref{PME}).
 We work here in one dimension,
@@
 and $F(x, m) = 1 - m$ so $\mu_\theta(x, m) = 1 + (m-1)/\theta$.
-This implies that
+By Corollary~\ref{cor:wavefront},
 the generator of the motion of an ancestral lineage is
@@
 \paragraph{Allen-Cahn equation:}
-Now take the following case of the Allen-Cahn equation:
+Now take the Allen-Cahn equation:
 \begin{align} \label{eqn:allen_cahn}
@@
 and shape
-\[ w^A(x) = (1+e^{x})^{-1}. \]
-That is $\phi_t(x)=w^A(x-st)$ solves~(\ref{eqn:allen_cahn}).
+\[ w^A(x) = (1+e^{x})^{-1} , \]
+i.e., $\phi_t(x)=w^A(x-st)$ solves~(\ref{eqn:allen_cahn}).
 Substituting $w^A$ in place of $w^F$ in~(\ref{eqn:fkpp_generator}),
@@
 which is integrable, and so determines the unique stationary distribution.
-Thus the position of the ancestral lineage will converge to a stationary 
+Thus the position of the ancestral lineage relative to the wavefront will converge to a stationary 
 distribution which is maximised away from the extreme tip of the wave.
@@
 
-\comment{
-    Description of the process;
-    discussion of when it happens;
-    (TODO: how's it affected by $\theta$?)
+Simulating these processes and exploring parameter space,
+one sooner or later comes upon a strange observation:
+with certain parameter combinations, the population spontaneously forms a regular grid
+of more or less dicrete patches, separated by areas with nearly no individuals.
+The phenomenon is discussed in Section~16.10 of \citet{haller2022evolutionary},
+and has been described in similar models, e.g., by \citet{sasaki1997clumped,hernandezgarcia2004clustering,young2001reproductive}.
+\comment{TODO: add traveling wave citations}
+Heuristically, this can occur if density-dependent effects of individuals
+extend sufficiently farther than the typical dispersal distance:
+the patches are stable because new offspring landing between two clumps
+effectively compete with \emph{both} neighboring clumps,
+while individuals within a clump effectively compete with only one.
+
+The implication here is that the equilibrium solution to~\eqref{general deterministic limit}
+may not be unique,
+and a stable solution may have oscillations on a scale determined by the interaction distance.
+We can see this easily in the simple case that
+$\DG = \sigma^2 \Delta$,
+the interaction kernels $\rho_r$, $\rho_\gamma$, and $\rho_F$
+are all equal to $p_{\epsilon^2}$ (the heat kernel at time $\epsilon^2$),
+and all parameters are spatially homogeneous,
+so that $r(x, \eta) = r(\smooth{r}\eta(x))$, and similarly for $\gamma$ and $F$.
+Let $\varphi_0$ be a value so that $F(\varphi_0) = 0$ and $F'(\varphi_0) < 0$,
+so that we would expect $\varphi(x) \equiv \varphi_0$ to be a stable equilibrium solution.
+Let us linearize~\eqref{general deterministic limit} about $\varphi_0$:
+let $\varphi_t(x) = \varphi_0 + \psi_t(x)$,
+and (informally) $r(x) \approx r(\varphi_0) + r'(\varphi_0) \smooth{r} \psi(x)$.
+Writing $r_0 = r(\varphi_0)$ and $r'_0 = r'(\varphi_0)$,
+and similarly for $\gamma$ and $F$,
+\begin{align*}
+    \partial_t \psi
+    &\approx
+    \sigma^2 \varphi_0 r_0 \gamma_0' \Delta \smooth{\gamma} \psi
+    + \sigma^2 r_0 \gamma_0 \Delta \psi
+    + \varphi_0 F'_0 \smooth{F} \psi .
+\end{align*}
+Letting $\hat \psi(u) = \int e^{2\pi i u x} \psi(x) dx$,
+\begin{align*}
+    \partial_t \hat \psi(u)
+    &\approx
+    \left(
+        - \sigma^2 \varphi_0 r_0 \gamma_0' u^2 e^{-\epsilon^2 u^2 /2}
+        - \sigma^2 r_0 \gamma_0 u^2
+        + \varphi_0 F'_0 e^{-\epsilon^2 u^2 /2} 
+    \right) \hat \psi(u) .
+\end{align*}
+Since $F'_0 < 0$, the last two terms are negative,
+but on the other hand we expect $\gamma_0' < 0$
+(i.e., per capita birth rate decreases with density near equilibrium),
+and so the stability of the constant solution $\varphi \equiv \varphi_0$
+depends on the balance between the first and latter two terms.
+Writing
+$A_1 = - \sigma^2 \varphi_0 r_0 \gamma'_0$,
+$A_2 = \sigma^2 r_0 \gamma_0$,
+and $A_3 = - \varphi_0 F'_0$
+(with signs chosen so each is positive),
+and defining
+$$ g(v) = A_1 v - A_2 v e^{\epsilon^2 v /2} - A_3 , $$
+we have $\partial_t \hat \psi(u) = g(u^2) e^{\epsilon^2 u^2 /2} \psi(u)$.
+The term $g(v)$ is maximized at $v_*$ solving
+$e^{\epsilon^2 v_*/2} = A_1 / (A_2 (\epsilon^2 v_*/ 2 + 1))$,
+which is positive if $A_1 > A_2$,
+i.e., if $-\varphi_0 \gamma_0' > \gamma_0$.
+If so, then the constant solution is unstable with respect to perturbations
+that oscillate with frequency around $\sqrt{v_*}$.
+\comment{This seems wrong, since it doesn't involve $\sigma$?
+    But at least note the unstable frequencies scale with $\epsilon$.
+    We might say more by linearizing the exponential term,
+    which gives $v_* = (A_1 - A_2 + A_3 \epsilon^2/2)/(A_1 \epsilon^2)$,
+    although the resulting expression isn't terribly helpful.
 }
@@
     \begin{center}
-        FIGURE
+        \comment{TODO} FIGURE
     \end{center}
@@
 and the second reflects death events.
+The factor of $\theta$ appears from the time rescaling.
 In both terms,
@@
 $$
-\big\langle
+\int_{\IR^d}
     N \theta \gamma(x,\eta)
@@
     q_\theta(x,dy) 
-    , \eta(dx)
-\big\rangle .
+\eta(dx) .
 $$
@@
 \left\{
-    \Big\langle
+    \int_{\IR^d}
         \gamma(x,\eta)
         \int \frac{1}{N^2}f^2(y)r(y,\eta)q_\theta(x,dy) 
-    , \eta(dx)\Big\rangle
+    \eta(dx)
     +
-    \Big\langle
+    \int_{\IR^d}
         \mu_\theta(x,\eta)\frac{1}{N^2}f^2(x) 
-    ,\eta(dx)\Big\rangle
+    \eta(dx)
 \right\} \\
@@
     \frac{\theta}{N}
-    \big\langle
+    \int_{\IR^d}
         \gamma(x, \eta) \int f^2(y) r(y, \eta) q_\theta(x, dy) + f^2(x) \mu_\theta(x, \eta),
-        \eta(dx)
-    \big\rangle .
+    \eta(dx) .
 \end{align*}
@@
 If we hold $\rho_\gamma$, $\rho_r$, $\rho_F$ fixed, then 
-by choosing $\theta/N \rightarrow 0$, the second order term in the generator 
+by taking $\theta/N \rightarrow 0$, the second order term in the generator 
 will vanish and we expect a deterministic limit,
@@
 that the regularity gained by smoothing our population density by convolution with
-$\rho_\epsilon=p_{\epsilon^2}$ is preserved under the dynamics dictated by $q_{\theta}$.
+$\rho_\epsilon$ is preserved under the dynamics dictated by $q_{\theta}$.
 To understand the first condition, note that we are aiming to obtain a 
@@
 fluctuations in the frequencies of the two types in the limit as $N\to\infty$; to 
-obtain a deterministic limit, we look over shorter timescales relative to population
+obtain a deterministic limit, we look over timescales that are short relative to population
 size. In our setting, the total population size is replaced by the local population
-size, as measured by convolution with $p_{\epsilon^2}$, which we expect to be 
+size, as measured by convolution with $\rho_{\epsilon}$, which we expect to be 
 of order $N\epsilon^d$, and so in order to ensure a deterministic limit we 
@@
 \frac{\theta
-    \gamma(x, \eta^N_t) r(y, \eta^N_t) \varphi^N_t(x)
+    \varphi^N_t(x) \gamma(x, \eta^N_t) r(y, \eta^N_t)
 }{
@@
 \[
-    \lp = \sum_i \delta_{x_i, u_i} ,
+    \lp^N = \sum_i \delta_{x_i, u_i} ,
 \]
@@
 from the population in the region.
-However, an individual's level 
-encodes information about their future reproductive output;
-individuals with lower levels tend to live longer, and have more offspring.
+However, this exchangeability is only as regards the \emph{past}:
+an individual's level encodes information about their future reproductive output,
+since individuals with lower levels tend to live longer, and have more offspring.
 For more explanation of the set-up and how this is possible,
@@
 
-We describe the representation of the scaled process.
 Following~\cite{etheridge/kurtz:2019}, we build the generator step by step
@@
 This random assignment of levels to parent
-and offspring will ensure that assignment of individuals to levels will
-be exchangeable.
+and offspring will ensure that assignment of individuals to levels remains exchangeable.
 
@@
 
-In the lookdown model, levels never cross below 0,
+Levels never cross below 0,
 while particles whose levels move above $N$ are regarded as dead
@@
     =
-    - \theta\frac{1}{N} u \left(N - u\right)
+    - \theta\frac{u}{N} \left(N - u\right)
     \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q_\theta(x, dy) 
@@
 $$
-which captures the local net difference between reproduction and death.
+which captures the local net difference between reproduction and death,
+and
+$$
+    c_\theta(x, \eta)
+    :=
+    \frac{\theta}{N} \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q_\theta(x, dy) ,
+$$
+which captures the local rate of production of successful offspring.
 Recall from equation~\eqref{eqn:mu_defn} that
@@
 \end{equation*}
-Under Assumptions~\ref{def:model_setup}
-this will tend to
+Under Assumptions~\ref{def:model_setup}, as $\theta \to \infty$
+$c_\theta(x, \eta)$ will tend to $\alpha \gamma(x, \eta) r(x, \eta)$
+and $b_\theta(x, \eta)$ will tend to
 \begin{equation}
 \label{eqn:b_limit}
-    \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta)
-\end{equation}
-as $\theta \to \infty$.
+    \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta) .
+\end{equation}
 
@@
     &=
-    \frac{\theta}{N} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
+    c_\theta(x, \eta) u^2
     -
-	b_\theta(x, \eta)u
+	b_\theta(x, \eta) u
     . \label{differential equation for level}
@@
 \begin{equation} \label{eqn:test_functions}
-f(\lp)=\prod_{(x,u)\in \lp}g(x,u)=\exp\left(\int \log g(x,u)\lp(dx, du)\right),
+    f(\lp) = \prod_{(x,u)\in \lp}g(x,u)=\exp\left(\int \log g(x,u)\lp(dx, du)\right),
 \end{equation}
@@
     \frac{\theta}{N}
-        \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q_\theta(x, dy) u^2
+        c_\theta(x, \eta) u^2
         -
-        b_\theta(x, \eta)u
+        b_\theta(x, \eta) u
     \right)
@@
     \left(
-        \frac{\theta}{N} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q_\theta(x, dy) u^2 -b_{\theta}(x,\eta)u
+        c_\theta(x,\eta) u^2 - b_{\theta}(x,\eta)u
     \right)
@@
     if 
-$f(\lp_t) - f(\lp_0)-\int_0^t A^Nf(\lp_s) ds$ is a martingale (with 
+$f(\lp_t) - f(\lp_0)-\int_0^t A^N f(\lp_s) ds$ is a martingale (with 
 respect to the natural filtration) for all 
@@
 for which we do not have uniqueness.
+\comment{Do we not have uniqueness, or not know if there is uniqueness?}
 As before, the parameter $\alpha$ will correspond to 
@@
         f(\lp) \sum_{(x, u) \in \xi}
-        2 \alpha \gamma(x, \eta) r(x, \eta \int_u^\infty (g(x, u_1) - 1) du_1
+        2 \alpha \gamma(x, \eta) r(x, \eta) \int_u^\infty (g(x, u_1) - 1) du_1
     \\ &\qquad {} +
@@
 
+\subsection{Preliminaries}
+
+First, we prove Lemma~\ref{conditions on r}.
+
+\begin{proof}[of Lemma~\ref{conditions on r}]
+    TODO MOVE PROOF HERE
+\end{proof}
+
 % % % % % % % % % % % % %
@@
 
-We need a bound on $\gamma(x,\eta)B_f(x,\eta)+F$. First suppose that
+\comment{TODO MOVE SOME OF THIS TO PROOF OF LEMMA~\ref{lem:conditions on r}}
+We need a bound on $\gamma(x,\eta)B_f(x,\eta)+F$.
+First suppose that
 Condition~\ref{control through r} of  

### 2023-03-10 forwards-and-backwards.tex
up to 6.26

@@
 \newcommand{\meanq}{\vec b}    % mean of dispersal, times theta
-\newcommand{\covq}{C}     % covariance matrix of dispersal, times theta
+\newcommand{\covq}{\mathbf{C}}     % covariance matrix of dispersal, times theta
 \newcommand{\kernel}{\rho}  % interaction kernels
@@
 is $\int (r(y, N \smooth{r}(y) ) - r(x, N \smooth{r}(x))) q_\theta(x, dy)$;
-the first condition of Lemma~\ref{conditions on r} would ensure this is of order $1/\theta$.
+the first condition of Lemma~\ref{lem:conditions on r} would ensure this is of order $1/\theta$.
 
@@
 We shall write 
-$$
+\begin{align} \label{b_defn}
     b_\theta(x, \eta)
@@
     \right) ,
-$$
+\end{align}
 which captures the local net difference between reproduction and death,
 and
-$$
+\begin{align} \label{c_defn}
     c_\theta(x, \eta)
@@
     \frac{\theta}{N} \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q_\theta(x, dy) ,
-$$
+\end{align}
 which captures the local rate of production of successful offspring.
@@
 counting measures on $\IR^d\times [0,N]$.
+
 \begin{definition}[Martingale Problem Characterisation]
@@
 
-Elsewhere we have written $\eta^N$ for the spatial projection of the lookdown process $\lp^N$,
-although $\eta^N$ was defined first as a solution to a martingale problem.
-For the purposes of this result --
-the application of the Markov Mapping Theorem \citep[Thm A.2 in][]{etheridge/kurtz:2018} --
-we must disambiguate these, and so define the spatial projection
-maps $\gamma^N: \mathcal{M}(\IR^d \times [0, N]) \to \mathcal{M}(\IR^d)$
-by $\gamma^N(\xi^N)(\cdot) = \xi^N(\cdot \times [0, N]) / N$,
-and $\gamma: \mathcal{M}(\IR^d \times [0, \infty)) \to \mathcal{M}(\IR^d)$
-by $\gamma(\xi)(\cdot) = \lim_{u_0 \to \infty} \xi(\cdot \times [0, u_0]) / u_0$.
+The lookdown processes have been carefully constructed so that
+observations about the past spatial positions of individuals in 
+the population do not give us any information about the assignment of 
+individuals to levels.
+In other words, the dynamics of the lookdown
+process preserve the conditionally uniform (or in the limit, conditionally Poisson) structure
+-- if started with uniform levels,
+levels are uniform at all future times.
+Moreover, if we average over levels in the expression for the generator
+(equation~\eqref{eqn:lookdown_generator} or~\eqref{eqn:limiting_lookdown_generator})
+we recover the generator for the population process.
+%(visible in equation~\eqref{eqn:eta_martingale}
+%or~\eqref{eqn:limiting_mgale_problem}, respectively).
+Once this is verified (along with some boundedness conditions)
+the Markov Mapping Theorem \citep[Thm A.2 in][]{etheridge/kurtz:2019}
+tells us that by ``removing labels'' from the lookdown process $\lp$
+we recover the population process $\eta$.
+% In particular, for any
+% solution to the martingale problem of Definition~\ref{defn:mgale_construction}
+% % of equations~\eqref{eqn:eta_martingale} and \eqref{eqn:prelimit_martingale_variation}
+% there is a % lookdown representation $(\lp^N_t)_{t \ge 0}$
+% solution to the martingale problem of Definition~\ref{defn:lookdown_mgale})
+% for which $\eta^N_t(\cdot) = \lp^N_t(\cdot \times [0, N])/N$
+% and such that at each $t$, conditioned on $(\eta^N_s)_{s \le t}$, the levels of $\lp_t^N$
+% are independently and uniformly distributed on $[0, N]$.
+% Similarly, in the scaling limit:
+% for any solution $(\eta_t)_{t \ge 0}$ to the martingale problem of 
+% Theorem~\ref{nonlocal_convergence}
+% %there is a lookdown process $(\lp^N_t)_{t \ge 0}$
+% there is a solution to the martingale problem of Theorem~\ref{lookdown_convergence}
+% for which $\eta_t(\cdot) = \lim_{u_0 \to \infty} \frac{1}{u_0} \lp_t(\cdot \times [0, u_0))$
+% and such that at each $t$, conditional on $(\eta_s)_{s\leq t}$, 
+% $\lp_t$ is conditionally Poisson with mean measure $\eta_t(dx) \times du$.
+Furthermore, convergence of the lookdown processes would imply convergence of the population processes
+\citep[Thm A.9 in][]{kurtz/rodrigues:2011}.
+
+To make this precise,
+define the spatial projection maps
+$\kappa^N: \mathcal{M}(\IR^d \times [0, N]) \to \mathcal{M}(\IR^d)$
+by $\kappa^N(\xi^N)(\cdot) = \xi^N(\cdot \times [0, N]) / N$,
+and $\kappa: \mathcal{M}(\IR^d \times [0, \infty)) \to \mathcal{M}(\IR^d)$
+by $\kappa(\xi)(\cdot) = \lim_{u_0 \to \infty} \xi(\cdot \times [0, u_0]) / u_0$.
 We will also need an inverse notion:
 for a measure $\lp^N$ on $\IR^d \times [0, N]$ and a sigma-field $\mathcal{F}$,
-we say that \emph{$\lp$ is conditionally uniform given $\mathcal{F}$}
+we say that \emph{$\lp^N$ is conditionally uniform given $\mathcal{F}$}
 if for all compactly supported $f$,
@@
     &=
-    e^{-\langle F_f^N, \gamma(\lp) \rangle} ,
+    e^{-\langle F_f^N, \kappa(\lp) \rangle} ,
 \end{align}
@@
 $$ F_f^N(x) = - N \log \frac{1}{N} \int_0^N e^{-f(x, u)} du . $$
-(In other words, the $[0, N]$ components of $\lp$
-are independent, uniformly distributed on $[0, N]$, and independent of $\gamma(\lp)$.)
+In other words, the $[0, N]$ components of $\lp$
+are independent, uniformly distributed on $[0, N]$, and independent of $\kappa(\lp)$.
 Similarly, for a measure $\lp$ on $\IR^d \times [0, \infty)$
@@
     &=
-    e^{-\langle \int_0^\infty (1 - e^{-f(x, u)}) du, \gamma(\lp)(dx) \rangle} .
+    e^{-\langle \int_0^\infty (1 - e^{-f(x, u)}) du, \kappa(\lp)(dx) \rangle} .
 \end{align}
-(In other words, $\lp$ is conditionally Poisson with Cox measure $\gamma(\lp) \times \Lambda$.)
+In other words, $\lp$ is conditionally Poisson with Cox measure $\kappa(\lp) \times \lambda$,
+where $\lambda$ is Lesbegue measure.
 
@@
     \label{thm:mmt_application}
-    Let $\mu_0$ be a probability distribution on $\measures$,
-    and $\nu_0^N$ a probability distribution on $\mathcal{M}(\IR^d \times [0, N])$
-    such that a draw $\lp^N_0$ from $\nu_0^N$ is conditionally uniform given $\gamma(\lp^N_0)$
-    in the sense of \eqref{eqn:conditionally_uniform}.
     If $\tilde \eta^N$ is a solution
     of the martingale problem of Definition~\ref{defn:mgale_construction}
-    with initial distribution $\mu_0$
+    with initial distribution $\eta^N_0$
     then there exists a solution $\lp^N$
-    of the martingale problem of Definition~\ref{defn:lookdown_mgale}
-    with initial distribution $\nu_0^N$
-    such that $\eta^N = \gamma \cdot \lp^N$
+    of the $(A^N, \lp^N_0)$-martingale problem of Definition~\ref{defn:lookdown_mgale}
+    such that $\eta^N = \kappa \circ \lp^N$
     has the same distribution on $D_{\measures}[0, \infty)$
     as $\tilde \eta^N$.
-    Furthermore, $\lp^N$ is conditionally uniform given given $\mathcal{F}^{\eta}_t$
+    Furthermore, for each $t$, $\lp^N_t$ is conditionally uniform given given $\mathcal{F}^{\eta^N}_t$
     in the sense of \eqref{eqn:conditionally_uniform}.
 
-    \comment{Theorem~\ref{thm:nonlocal_convergence}
-        isn't written as ``the $(A, \mu)$ martingale problem is'';
-        rephrase here or there?}
-
     Similarly,
-    let $\mu_0$ be a probability distribution on $\measures$,
-    and $\nu_0$ a probability distribution on $\mathcal{M}(\IR^d \times [0, \infty))$
-    such that a draw $\lp_0$ from $\nu_0$ is conditionally Poisson given $\gamma(\lp_0)$
-    in the sense of \eqref{eqn:conditionally_poisson}.
-    If $\tilde \eta$ is a solution
+    if $\tilde \eta$ is a solution
     of the limiting martingale problem of Theorem~\ref{thm:nonlocal_convergence}
-    with initial distribution $\mu_0$
+    with initial distribution $\eta_0$
     then there exists a solution $\lp$
     of the martingale problem of of Definition~\ref{defn:limiting_lookdown_mgale}
-    with initial distribution $\nu_0$
-    such that $\eta = \gamma \cdot \lp$
+    such that $\eta = \kappa \circ \lp$
     has the same distribution on $D_{\measures}[0, \infty)$
@@
 
-\begin{proof}[of Proposition~\ref{thm:mmt_application}]
-    This is the content of the Markov Mapping Theorem applied to our situation,
-    \citet[Thm A.2 in][]{etheridge/kurtz:2018}.
-    In the notation of that theorem, $\gamma$ is as above,
-    $\alpha$ is the transition function that assigns levels uniformly on $[0, N]$ (in the first case)
-    or as a Poisson process with Lesbegue intensity (in the limiting case),
-    and we need a continuous $\psi^N(\lp)$ such that $|A^N f(\lp)| \le c_f \psi^N(\lp)$
-    for all $f \in \mathcal{D}(A^N)$ (and similarly a function $\psi$ for $A$).
-    We also need that applying the lookdown generator to a function and averaging over levels
-    is equivalent to applying the population process generator to the function
-    whose dependence on levels has been averaged out,
-    which we precisely state, and verify, in Appendix~\ref{sec: Markov Mapping Theorem Application}.
-
-    For finite $N$,
-    taking $f(\lp)$ of the form \eqref{eqn:test_functions},
-    we can use $\psi^N(\lp) = \langle C + u |F(x, \eta)|, \lp(dx, du) \rangle$
-    for an appropriate constant $C$.
-    For the scaling limit, recall that the test functions $f$ are of the form
-    $f(\lp) = \prod_{(x, u) \in \lp} g(x, u)$
-    with $g(x, u) = 1$ for $u \ge u_0$,
-    and so taking for example the mostly troublesome term in $Af(\lp)$,
-    we see that since $0 \le f(\lp) / g(x, u) \le 1$ for any $(x, u) \in \lp$,
-    \begin{align} \label{eqn:part_of_psi}
-        \big| f(\lp) \sum_{(x, u) \in \lp} F(x, \eta) u \frac{\partial_u g(x, u)}{g(x, u)} \big|
-        & \le
-        \| \partial_u g \|_\infty \sum_{(x, u) \in \lp} | F(x, \eta) u \ind_{u \le u_0} | \\
-        & \le
-        \| \partial_u g \|_\infty e^{u_0} \sum_{(x, u) \in \lp} | F(x, \eta) u e^{-u} | .
-    \end{align}
-    The second line would be just what we want,
-    except that $\psi(\lp)$ cannot depend on $f$, and hence neither on $u_0$.
-    So, the third line provides us with the required bound,
-    absorbing $\| \partial_u g \|_\infty e^{u_0}$ into $c_f$
-    and $\langle |F(x, \eta) u e^{-u}|, \lp \rangle$ into $\psi(\lp)$.
-    Furthermore, since $F(x, \eta)$ only depends on spatial location, not level,
-    for a given $\lp$ (and hence $\eta = \gamma(\lp)$),
-    $\sup_x |F(x, \eta)|$ is finite.
-    Therefore, we may bound \eqref{eqn:part_of_psi} by
-    $\sup_x |F(x, \eta)| \langle u e^{-u}, \lp \rangle$.
-    To do this we must restrict $\lp$ to lie in the space of measures
-    for which this is finite;
-    however, this is a completely metrizable space
-    \citep[see Condition 2.1 in][]{etheridge/kurtz:2018},
-    and our processes fall in this space (by conditional uniformity).
-\end{proof}
-
 \comment{In this section I haven't specified the filtration for the martingale problem.}
 
-The lookdown processes have been carefully constructed so that
-past observations about the spatial positions of individuals in 
-the population do not give us any information about the assignment of 
-individuals to levels. In other words, the dynamics of the lookdown
-process preserve the conditionally uniform (resp.~conditionally Poisson)
-structure.
-Moreover, if we average over levels in the expression for the generator
-(equation~\eqref{eqn:lookdown_generator} or~\eqref{eqn:limiting_lookdown_generator})
-we recover the generator for the population process.
-%(visible in equation~\eqref{eqn:eta_martingale}
-%or~\eqref{eqn:limiting_mgale_problem}, respectively).
-Once this is verified (along with some boundedness conditions)
-in Appendix~\ref{sec: Markov Mapping Theorem Application},
-\comment{Refer more precisely}
-the Markov Mapping Theorem \citep[Thm A.2 in][]{etheridge/kurtz:2019}
-tells us that by ``removing labels'' in this way we recover the Markov
-process describing our population.
-In particular, for any %population process $(\eta^N_t)_{t \ge 0}$
-%(i.e.,
-solution to the martingale problem of Definition~\ref{defn:mgale_construction})
-% of equations~\eqref{eqn:eta_martingale} and \eqref{eqn:prelimit_martingale_variation}
-there is a % lookdown representation $(\lp^N_t)_{t \ge 0}$
-%(i.e., 
-solution to the martingale problem of Definition~\ref{defn:lookdown_mgale})
-for which $\eta^N_t(\cdot) = \lp^N_t(\cdot \times [0, N])/N$
-and such that at each $t$, conditioned on $(\eta^N_s)_{s \le t}$, the levels of $\lp_t^N$
-are independently and uniformly distributed on $[0, N]$.
-Similarly, in the scaling limit:
-for any solution $(\eta_t)_{t \ge 0}$ to the martingale problem of 
-Theorem~\ref{nonlocal_convergence}
-%there is a lookdown process $(\lp^N_t)_{t \ge 0}$
-there is a solution to the martingale problem of Theorem~\ref{lookdown_convergence}
-for which $\eta_t(\cdot) = \lim_{u_0 \to \infty} \frac{1}{u_0} \lp_t(\cdot \times [0, u_0))$
-and such that at each $t$, conditional on $(\eta_s)_{s\leq t}$, 
-$\lp_t$ is conditionally Poisson with mean measure $\eta_t(dx) \times du$.
-Furthermore, convergence of the lookdown processes would imply convergence of the population processes
-\citep[Thm A.9 in][]{kurtz/rodrigues:2011}.
-
-Now that the lookdown process has been defined,
-we can present the main convergence theorem that is analogous
+Now we can present the main convergence theorem that is analogous
 to Theorem~\ref{thm:nonlocal_convergence} for the population process.
 
-\comment{the next theorem needs rewriting along the lines of Thm A.12 in 
-Kurtz and Rodrigues.}
+\comment{the next theorem needs rewriting along the lines of Thm A.12 in Kurtz and Rodrigues.}
+\comment{TODO: it's been rewritten some; but needs checking against that Thm yet}
 
@@
     \label{thm:lookdown_convergence}
-    Let $(\lp_t^N)$ be as defined in Definition~\ref{defn:lookdown_mgale}
+    Let $(\lp_t^N)$ satisfy Definition~\ref{defn:lookdown_mgale}
     and assume that as $N \to \infty$,
     $\theta \to \infty$ in such a way that $\theta/N \to \alpha$.
-    Suppose also that $\eta^N_0 \to \eta_0$ (as measures on $\IR^d$),
-    and that for each $N$, $\lp^N_0(dx, du)$ is conditionally Poisson on $\IR^d \times [0, N]$
-    with Cox measure $\eta^N_0(dx) \times du$.
+    Let $\eta_0^N = \kappa(\lp_0^N)$ and
+    suppose also that $\eta^N_0 \to \eta_0$ (as finite measures on $\IR^d$),
+    and that for each $N$, $\lp^N_0$ is conditionally uniform given $\eta_0^N$
+    in the sense of \eqref{eqn:conditionally_uniform}.
     Then, the sequence of stochastic processes $(\lp_t^N)_{t \ge 0}$
@@
     to a measure-valued process $(\lp_t)_{t \ge 0}$
-    with $\lp_0$ conditionally Poisson with Cox measure $\eta_0(dx) \times du$,
-    that is a solution to the martingale problem~\ref{defn:limiting_lookdown_mgale}.
+    with $\lp_0$ conditionally Poisson given $\eta_0 = \kappa(\lp_0)$
+    in the sense of \eqref{eqn:conditionally_poisson},
+    that is a solution to the martingale problem of Definition~\ref{defn:limiting_lookdown_mgale}.
 \end{theorem}
@@
 In order to exploit this, in this section we write down stochastic 
-equations for the locations and levels of individuals in the lookdown
-representation of the prelimiting model.
+equations for the locations and levels of individuals in the prelimiting lookdown model.
 We will then be able to pass to the scaling limit.
@@
 genetics by a number of authors including 
-\cite{hallatschek/nelson:2008, durrett/fan:2016, biswas/etheridge/klimek:2018}.
+\citet{hallatschek/nelson:2008}, \citet{durrett/fan:2016}, and \citet{biswas/etheridge/klimek:2018}.
 
 We will construct the process using a Ulam-Harris indexing scheme.
-First, we assign each extant individual a unique label from $\IN_{\ge 0}$.
+First, we assign each individual alive at time 0 a unique label from $\IN$.
 Suppose an individual with label $a$ and level $u$ reproduces,
@@
 The parent individual, previously labeled $a$, might be assigned either level.
-We will track chains of descendant individuals forwards through time
+We will track chains of descendant individuals forwards through time by
 following levels, rather than individuals, and will call this a \emph{line of descent}.
@@
 $[0, \infty)^2 \times \IR^d \times \{0,1\}$.
-The mean measure of each $\Pi_a$ is a product of Lebesgue 
-measure on the first two coordinates,
-the density of the standard Gaussian $N(0,1)$ on $\IR^d$, and 
+The mean measure of each $\Pi_a$ is a product of Lebesgue measure on $[0, \infty)^2$,
+the density of the standard Gaussian on $\IR^d$, and 
 $(\delta_0 + \delta_1)/2$ on $\{0, 1\}$.
@@
 of the individual carrying label $a$ at time $t$, respectively.
+Furthermore, define
+\begin{align*}
+    \eta^N_t = \frac{1}{N} \sum_{a : \tau_a \le t < \sigma_a} \delta_{X_a(t)}
+    \qquad \text{and} \qquad
+    \lp^N_t = \sum_{a : \tau_a \le t < \sigma_a} \delta_{(X_a(t), U_a(t))} .
+\end{align*}
+
 Now, since we have defined labels so that the level does not jump,
@@
     \left(
-        \frac{\theta}{N} \gamma(X_a(s),\eta_s)
-        \int_{\IR^d} r(z,\eta_s) q(X_a(s),dz) U_a(s)^2
+        c_\theta(X_a(s),\eta_s) U_a(s)^2
         -
-        b(X_a(s),\eta_s) U_a(s)
+        b_\theta(X_a(s),\eta_s) U_a(s)
     \right)
@@
 Potential reproduction events occur at times $\tau$
-for each point $(\tau, v, z, \kappa) \in \Pi_a$ with $\tau \ge \tau_a$.
-We say ``potential'' since if the resulting level is greater than $N$,
-the event does not happen.
+for each point $(\tau, v, z, \kappa) \in \Pi_a$ with $\tau_a \le \tau < \sigma_a$.
+(We say ``potential'' since if the level of the resulting offspring is greater than $N$,
+the event does not happen.)
 If this is the $j^\text{th}$ point in $\Pi_a$,
-the new label is $a \concat j$, the (potential) birth time is $\tau_{a \concat j} = \tau$.
-Similarly, the potential birth location is $y(X(\tau-), z)$, where
+the potential new label is $a \concat j$, the birth time is $\tau_{a \concat j} = \tau$,
+and the spatial displacement of the potential ogfspring is $y(X(\tau-), z)$, where
 $$
@@
     +
-    v \ell\big(X_a(\tau-), y(X_a(\tau-), z), \eta(\tau-)\big) .
+    v \ell\big(X_a(\tau-), y(X_a(\tau-), z), \eta_{\tau-} \big) .
 \end{equation*}
@@
     &=
+    X_a(\tau_a) + 
     \int_{[\tau_a, t) \times [0, \infty) \times \IR \times [0, 1]}
@@
 
-We can now express the population processes using these levels:
-\begin{align*}
-    \eta^N_t = \frac{1}{N} \sum_{a : \tau_a \le t < \sigma_a} \delta_{X_a(t)}
-    \qquad \text{and} \qquad
-    \lp^N_t = \sum_{a : \tau_a \le t < \sigma_a} \delta_{(X_a(t), U_a(t))} .
-\end{align*}
-
 \begin{remark}
-    Although we have a single construction that couples
-    the processes across all $N$, the actual 
-trajectories, $X_a(\cdot)$, do not necessarily coincide for 
-different values of $N$, since they are affected by the whole 
-population process.
-    However, this does suggest approximating the genealogies
+Although we have a single construction that couples the processes across all $N$,
+unlike in \citet{kurtz/rodrigues:2011},
+the actual trajectories, $X_a(\cdot)$, do not necessarily coincide for 
+different values of $N$, since they are affected by the whole population process.
+However, this does suggest approximating the genealogies in the infinite density limit
 by simulating up until a sufficiently high level
@@
 \begin{equation} \label{eqn:line_points}
-    v < 2 \frac{\big(N - U_a(\tau-)\big)}{N} \theta \gamma(X_a(\tau-), \eta_{\tau-}) 
+    v < 2 \frac{\big(N - U_a(\tau)\big)}{N} \theta \gamma(X_a(\tau-), \eta_{\tau-}) 
 	r\Big(X_a(\tau-) + y\big(X_a(\tau-),z\big), \eta_{\tau-}\Big) .
@@
 this corresponds in the limit to new lines of descent being thrown off 
-according to a Poisson Point Process with intensity
+according to a Poisson process with intensity
 $$
@@
 Recall that $\DG g(x) = \sum_i \meanq_i \partial_i g(x) + \sum_{ij} \covq_{ij} \partial_{ij} g(x)$,
-and for the moment write $r(x)$ for $r(x, \eta)$,
+and for the moment write $r(x)$ for $r(x, \eta)$, $\meanq(x) = \meanq$, and $\covq(x) = \covq$
 so that
@@
     r(x) \sum_i \meanq_i \partial_i g(x)
-    + 2 \sum_{ij} \meanq_i \partial_i r(x) \covq_{ij} \partial_j g(x)
+    + 2 \sum_{ij} \partial_i r(x) \covq_{ij} \partial_j g(x)
     + r(x) \sum_{ij} \covq_{ij} \partial_{ij} g(x) \\
@@
 Let 
-$J(x,\eta)$ be such that $\gamma(x,\eta)\covq(x) = J(x,\eta) J(x,\eta)^T$, and set
-$\beta(x, \eta) = \gamma(x,\eta)\big(\meanq(x) + 2 \covq(x) \grad \log r(x, \eta)\big).$
+$J(x,\eta)$ be such that $r(x,\eta)\gamma(x,\eta)\covq(x) = J(x,\eta) J(x,\eta)^T$, and set
+$\beta(x, \eta) = r(x,\eta)\gamma(x,\eta)\big(\meanq(x) + 2 \covq(x) \grad \log r(x, \eta)\big).$
 Associate with each label $a \in \labelspace = \cup_{k\geq 1}\IN^k$
@@
 (the product of $\eta_0$ and Lebesgue measure).
-For each point of $R_0$, begin a line of descent
+For each $i$, with $(x_i, u_i)$ the $i^\text{th}$  point of $R_0$, begin a line of descent
 with label $i$, location $X_i(0) = x_i$, 
@@
 
-We write $\tau_a$ for the birth time of the label $a$ and 
+Write $\tau_a$ for the birth time of the label $a$ and 
 $\sigma_a = \lim_{K \to \infty} \inf\{t \ge 0: U_a(t) > K\}$
-is the first time the level corresponding to the label $a$ exceeds $K$.
+the time the level hits $\infty$.
 Suppose that the spatial locations and level of each line of descent $a$
@@
     U_{a \concat j}(\tau) = U_a(\tau)
-    + \frac{v}{ 2 \alpha \gamma(X_a(\tau), \eta_\tau) r(X_a(\tau), \eta_\tau) } .
+    + \frac{v}{ 2 \alpha \gamma(X_a(\tau), \eta_\tau) r(X_a(\tau), \eta_\tau) } ,
 $$
+if this is finite.
 For any solution to the equations above, the processes defined by
@@
 
-\comment{TODO: find the right place for this proof?}
 \begin{proof}[of Proposition~\ref{prop:limiting_construction}]
@@
     is an application of It\^o's theorem.
-    The calculations in \comment{XXX} leading to our application
-    of the Markov Mapping Theorem then show that 
+    Theorem~\ref{thm:mmt_application} shows that
     the conditional Poisson property of $\lp_0$ is preserved
@@
 \end{proof}
-
-\comment{Don't we have to state everything in terms of subsequences along which the
-empirical measures converge?}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Motion of ancestral lineages}
-\label{ancestral lineages}
-
-We now show how, in the case in which the scaling limit of the population 
-process is deterministic, one can read off a description of 
-the motion of ancestral lineages from that of 
-the lines of descent derived in the previous subsection.
-
-Consider then a population evolving according to one of our deterministic
-limiting models. There are no births of new levels; 
-changes in population size are reflected only through the motion 
-of levels.
-
-We shall restrict ourselves
-to the setting in which the population is expanding as a travelling wave
-through $\IR$, with fixed profile $w(x)$ moving at rate $c$. That is 
-$$\Xi_t(x)=w(x-ct),$$
-for some fixed function $w$ and some $c>0$.
-The profile $w$ will satisfy
-\begin{equation}
-\label{profile}
-r\DG^*(\gamma w)+Fw+c\partial_x w=0.
-\end{equation} 
-It is convenient to work in a moving frame so that the wavefront is fixed.
-Let $Y$ denote the diffusion followed by a single line of descent in this frame; 
-i.e.~the diffusion with generator 
-${\cal L}^Yf=\gamma \DG(rf)-\gamma f\DG(r)-c\partial_x f$.
-%\overline{B}(w)\phi-c\phi_x$.
-For the motion of its level, note that 
-$b=\gamma\DG(r)+F$, and,  
-since we are in the deterministic limit, $\alpha=0$.
-
-Informally, the intensity of levels at $y$ at time $t$ that are descended from 
-individuals that were at $x$ at time $0$ is
-\begin{equation}
-\label{formal intensity}
-w(x)\IE_x\left[\exp\left(\int_0^t b(Y_s)ds\right)\ind_{Y_t=y}\right]dy,
-\end{equation}
-where the subscript $x$ in the expectation indicates that $Y_0=x$.
-To see why this should be true, 
-suppose that an ancestor has level $u$. Conditional on its 
-spatial motion $\{Y_s\}_{0\leq s\leq t}$, its level at time $t$ will
-be $u\exp(-\int_0^tb(Y_s)ds)$. This will be less than a given level 
-$\lambda$ if $u<\lambda \exp(\int_0^tb(Y_s)ds)$. 
-The intensity of levels at $y$ that are descended from individuals at
-$x$ can therefore be obtained as the limit as $\lambda\to\infty$ of 
-$1/\lambda$ times the number of levels at $x$ at time zero with
-$u<\lambda \exp(\int_0^tb(Y_s)ds)$ and for which
-the corresponding individual is at $y$ at time $t$, which is 
-precisely the quantity in~(\ref{formal intensity}).
-
-Note that at time $0$ the expression in~(\ref{formal intensity}) is satisfied, and that
-writing 
-\[
-\psi(t,x)=
-\IE_x\left[\exp\left(\int_0^t b(Y_s)ds\right)\ind_{Y_t=y}\right],
-\]
-and substituting the expressions for ${\cal L}^Y$ and $b$ from above, we have
-\begin{eqnarray*}
-\frac{d}{dt}\int
-w(x)\psi(t,x)dx&=& \int w(x)\Big\{\Big(\gamma\DG(r\psi)-\gamma\psi\DG(r)-c\partial_x\psi\Big)
-+\psi\gamma\DG(r)+\psi F\Big\}dx
-\\
-&=&\int\psi\Big\{r\DG^*(\gamma w)+Fw+c\partial_x w\Big\}dx=0.
-\end{eqnarray*}
-Thus when we integrate~(\ref{formal intensity})
-with respect to $x$ we recover $w(y)dy$. 
-As a consequence of~(\ref{formal intensity}), writing 
-$\mathfrak{p}(t,y,x)$ for
-the probability density that the ancestor at time $t$ units before the present 
-of an individual sampled 
-at $y$ was at $x$, then, still informally,
-\begin{equation}
-\label{ptyx}
-\mathfrak{p}(t,y,x)=\frac{w(x)}{w(y)}\IE_x\left[\exp\left(\int_0^t b(Y_s)ds\right)
-\ind_{Y_t=y}\right].
-\end{equation}
-
-To make~(\ref{ptyx}) meaningful, we multiply by suitable test functions and 
-integrate.
-$$\int\int \psi(y)w(y)\mathfrak{p}(t,y,x)\phi(x)dydx=\int\phi(x)w(x)
-\IE_x\left[\exp\left(\int_0^tb(Y_s)ds\right)\psi(Y_t)\right]dydx.$$
-
-Writing $\hat{T}_t$ for the semigroup corresponding to the motion of 
-ancestral lineages backwards in time (that is the semigroup corresponding
-to $\mathfrak{p}(t,y,x)$), we can write this as 
-$$\int \psi(y)w(y)\hat{T}_t\phi(y)dy=\int\phi(x)w(x)
-\IE_x\left[\exp\left(\int_0^tb(Y_s)ds\right)\psi(Y_t)\right]dx.$$
-Differentiating with respect to $t$ at $t=0$, and writing 
-$\hat{\mathcal L}$ for the generator of $\hat{T}_t$, we find
-\begin{eqnarray*}
-\int \psi(y)w(y)\widehat{\mathcal L}\phi(y)dy&=&
-\int\phi(x)w(x)\left({\mathcal L}^Y+b\right)\psi(x)dx\\
-&=&\int\phi(x)w(x)\left(\gamma\DG(r\psi)-\gamma\psi\DG r -c\nabla\psi 
-+b\psi\right)dx\\
-&=&\int\phi(x)w(x)\left(\gamma\DG(r\psi)-c\nabla\psi+F\psi\right)dx\\
-&=&
-\int\psi(x)\left[r\DG^*(\gamma \phi w)+F\phi w+c\nabla(\phi w)\right]dx.
-\end{eqnarray*}
-Since $\psi$ was arbitrary,
-
-\begin{eqnarray*}
-\hat{\mathcal L}\phi&=&\frac{1}{w}\left[ r\DG^* (\gamma\phi w)+F\phi w
-+c\nabla(\phi w)\right]\\
-&=&\frac{\phi}{w}\left[r\sigma^2\Delta(\gamma w)+Fw+-\meanq \grad(\gamma\phi) w +c\nabla w\right]
-\\
-&& +\frac{1}{w}\left[r\gamma w\sigma^2\Delta \phi +2r\sigma^2\nabla (\gamma w)
-\nabla\phi -\meanq \gamma\phi \grad w+cw\nabla\phi\right]\\
-&=&r\gamma\left(\sigma^2\Delta\phi+2\sigma^2r\frac{\nabla(\gamma w)}{\gamma w}\nabla\phi\right)
--\meanq\gamma\nabla\phi+c\nabla\phi,
-\end{eqnarray*}
-where we have used that $w$ solves~(\ref{profile}), and we have recovered~(\ref{Lgen}).
 
@@
 
-First, we prove Lemma~\ref{conditions on r}.
-
-\begin{proof}[of Lemma~\ref{conditions on r}]
+First, we prove Lemma~\ref{lem:conditions on r}.
+
+\begin{proof}[of Lemma~\ref{lem:conditions on r}]
     TODO MOVE PROOF HERE
@@
 % % % % % % % % % % % % %
-\subsection{Proof of Theorem~\ref{thm:nonlocal_convergence}: nonlocal limit points}
+\subsection{Proof of Theorem~\ref{thm:nonlocal_convergence}: limit points for the nonlocal process}
     \label{sec:population_density_proof}
@@
 %Theorem~3.9.1 of~\cite{ethier/kurtz:1986} tells us that 
-tightness of the population processes 
-in $\mathcal{D}_{\cmeasures}([0,\infty))$
-will follow if we can 
-establish tightness of the 
-real-valued processes $(G(\eta_t))_{t\geq 0}$ for a sufficiently large
-class of test functions $G$, which we check 
-through an application of the
+tightness of the population processes in $\mathcal{D}_{\cmeasures}([0,\infty))$
+follows from tightness of the real-valued processes $(G(\eta_t))_{t\geq 0}$ for a sufficiently large
+class of test functions $G$, which we establish through an application of the
 Aldous-Rebolledo criterion in Lemma~\ref{lem:eta_projections_tightness}.
@@
 a constant times $\smooth{\gamma}\eta(x)+(\smooth{\gamma}\eta(x))^2$ and 
-$m^2\gamma(m)$ is bounded. We have shown that $B_f$ is bounded, and so recalling that
+$m^2\gamma(m)$ is bounded. We have shown that $\gamma B_f$ is bounded, and so recalling that
 $F$ is bounded above, we can now conclude that
@@
     Now, let $M^*_t(f) = \sup_{0 \le s \le t} M_t(f)$,
-    and as before $[M(f)]_t$ the quadratic variation of $M_t(f)$,
+    and as before let $[M(f)]_t$ be the quadratic variation of $M_t(f)$,
     so that by the Burkholder-Davis-Gundy inequality, there is a $C'$ so that,
@@
             \right\}, \eta_s^N(dx)\Big\rangle
-            dt
+            ds
             \right] \right)
@@
             \right\}, \eta_s^N(dx) \Big\rangle
-            dt
+            ds
             \right] \right) .
@@
 \IE\left[\int_0^t \Big\langle -F(x, \eta^N_s), \eta^N_s(dx)
-	\Big\rangle\right]
+	\Big\rangle ds \right]
 	=\IE[\langle 1, \eta^N_0\rangle] -\IE[\langle 1,\eta^N_t\rangle]
@@
 
-\subsubsection{Tightness}
-
 Our next task is to show tightness of 
@@
 of equation~\eqref{eqn:eta_f_mgale_decomp}, tells us
-that it suffices to show that for each $T>0$, for each fixed 
-$0\leq t\leq T$, the sequence 
-$\{\langle f, \eta^N_t \rangle\}_{N \ge 1}$ is tight, and that
-for any sequence of stopping times $\tau_N$ bounded by $T$,
+that it suffices to show that for each $T>0$,
+(a) for each fixed $0\leq t\leq T$, the sequence $\{\langle f, \eta^N_t \rangle\}_{N \ge 1}$ is tight,
+and (b) for any sequence of stopping times $\tau_N$ bounded by $T$,
 and for each $\nu > 0$, there exist $\delta > 0$ and $N_0 > 0$ such that 
@@
 to choose $N_0$ and $K$ such that
-$$\IP\left[\sup_{0\leq s\leq T}\langle 1, \eta_s^N\rangle\geq K\right]<\nu,$$
+if $N > N_0$, then
+$$
+    \IP\left\{\sup_{0\leq s\leq T}\langle 1, \eta_s^N\rangle\geq K\right\} < \nu,
+$$
 we now choose $\delta_1$ so that
-$$\sup\big\{
-\sup_{x}|F(x,k)|
-: k\leq K\|\rho_F\|_\infty \big\}\delta_1
-<\nu/2,
+$$
+    \delta_1 \|f\|_\infty \sup\big\{ \sup_{x}|F(x,k)| : k\leq K\|\rho_F\|_\infty \big\}
+    <
+    \nu/2,
     \qquad
-\sup_{x,\eta}\gamma(x,\eta)B_f(\,\eta)\delta_1<\nu/2,$$
-and~(\ref{eqn:eta_projections_goal1}) is satisfied.
+    \sup_{x,\eta}\gamma(x,\eta)B_f(\,\eta)\delta_1<\nu/2,
+$$
+so that~\eqref{eqn:eta_projections_goal1} is satisfied with $\delta = \delta_1$.
 
@@
 
-% % % % % % % % % % % % %
-\subsubsection{Characterisation of the limit points}
-    \label{sec:population_generators_proofs}
-
 We wish to characterise the limit points of
@@
 was done in Section~\ref{sec:heuristics}.
-
-\begin{definition}
+First, we record an equivalent formulation
+of the martingale problem for the limiting process,
+that follows by application of It\^o's lemma.
+
+\begin{lemma}
     \label{def: MP definition of limit}
@@
 \end{equation}
-We say that $(\eta^{\infty}_t)_{t \geq 0}$ is a solution 
-to the $(\Pgen^{\infty}, \eta_0)$-martingale problem if 
-for all such test functions 
-$$M_t:=G_f(\eta^{\infty}_t)-G_f(\eta_0)
--\int_{0}^{t}\Pgen^{\infty}G_f(\eta^{\infty}_s)ds$$
+A process $(\eta^{\infty}_t)_{t \geq 0}$ 
+is a solution to the $(A, \lp_0)$-martingale problem of Definition~\ref{defn:limiting_lookdown_mgale}
+if and only if it is a solution 
+to the $(\Pgen^{\infty}, \eta_0)$-martingale problem, i.e.,
+if for all such test functions 
+$$
+    M_t :=
+    G_f(\eta^{\infty}_t)-G_f(\eta_0)
+    - \int_{0}^{t}\Pgen^{\infty}G_f(\eta^{\infty}_s)ds
+$$
 is a martingale (with respect to the natural $\sigma$-field). 
-\end{definition}
+\end{lemma}
+
+\comment{TODO: define $\mathcal{P}^N$.}
 
@@
 on $\mathcal{M}_F(\overline{\IR}^d)$.
-Therefore, it suffices to show that for any $t>0$,
+Therefore, it suffices to show that for any $t>0$ and $\tau > 0$ that
 \begin{equation}
@@
 \lim_{N\to \infty} |\mathcal{P}^{N}G(\langle f, \eta \rangle) 
-- \mathcal{P}^{\infty}G(\langle f, \eta \rangle)| = 0,   
+- \mathcal{P}^{\infty}G(\langle f, \eta \rangle)| = 0 .
 \end{equation}
@@
 is to check that
-any limit point $(\eta_t)_{t\geq 0}$ of $\{(\eta_t)_{t\geq 0}\}_{N\geq 1}$
-actually takes its values in $\measures$; that is ``no mass has escaped to infinity''.
+any limit point $(\eta_t)_{t\geq 0}$ of $\{(\eta^N_t)_{t\geq 0}\}_{N\geq 1}$
+actually takes its values in $\measures$, that is, ``no mass has escaped to infinity''.
 
@@
 let $(\eta_t)_{t\geq 0}$ be a limit point of $\{(\eta^N_t)_{t\geq 0}\}_{N\geq 1}$. 
-Given $\delta>0$, 
+For any $\delta>0$, 
 \[
@@
     \IE[\langle \exp(\lambda x),\eta_t\rangle]
-=\IE[\langle \exp(\lambda x),\eta_0\rangle]
-+\IE\Big[\int_0^t\Big\langle\gamma(x, \smooth{\gamma}\eta_s(x))
+    =
+    \IE[\langle \exp(\lambda x),\eta_0\rangle]
+    +
+    \IE\Big[\int_0^t\Big\langle\gamma(x, \smooth{\gamma}\eta_s(x))
     \exp(\lambda x)
-\Big\{\lambda^2 r(x, \smooth{r}\eta_s(x))
-\\
-+2\lambda\partial_x\big(r(\cdot,\smooth{r}\eta_s(\cdot)\big)(x)
-+\partial_{xx} r(\cdot,\smooth{r}\eta_s(\cdot)\big)(x)
-+F(x,\smooth{F}\eta_s(x))\Big\} ,
-\eta_s(dx)\Big\rangle ds\Big].
+    \Big\{
+        \lambda^2 r(x, \smooth{r}\eta_s(x))
+    \\ {}
+        + 2\lambda\partial_x\big(r(\cdot,\smooth{r}\eta_s(\cdot)\big)(x)
+        + \partial_{xx} r(\cdot,\smooth{r}\eta_s(\cdot)\big)(x)
+    \Big\} 
+    + F(x,\smooth{F}\eta_s(x)),
+    \eta_s(dx)\Big\rangle ds\Big] .
 \end{multline} 
@@
 population density that solves the corresponding ``classical'' PDE. We verify
-this in two examples; in the first the nonlocal equation is a reaction
-diffusion equation with the ``nonlocality'' only appearing in the 
+this in two examples; in the first the nonlocal equation is a reaction-- diffusion equation
+with the ``nonlocality'' only appearing in the 
 reaction term; in the second the nonlocal PDE is a special 
@@
 
-\subsubsection{Reaction diffusion equation limits}
+\subsubsection{Reaction--diffusion equation limits}
 \label{two-step convergence to FKPP}
@@
 \end{proof}
+
 \begin{lemma} \label{regularityForX2}
@@
 
-We use the representations:
+We use the representations of the solutions to equations \eqref{localPDE} and \eqref{nonlocalPDEv1} respectively:
 \begin{align}
@@
 \IE_x\left[ \int_0^t \Big(\varphi_s(Z_s)F\big(\varphi_s(Z_s)\big)
--\varphi^\epsilon_s(Z_s)F\big(\rho_\epsilon*\varphi^\epsilon_s(Z_s)\big)\Big) ds \right]. 
+-\varphi^\epsilon_s(Z_s)F\big(\rho_\epsilon*\varphi^\epsilon_s(Z_s)\big)\Big) ds \right] ,
 \label{FK:diferencesVarphis}
 \end{equation}
+where $\IE_x$ denotes expectation for $Z$ with $Z_0 = x$.
 The key to our proof of Proposition~\ref{prop:nonlocal_to_local}
@@
 \end{align*}
-In particular, since $\varphi_s$ is non-negative,
-\[ \| \varphi_t(\cdot) \|_\infty \leq \| \varphi_0 \| 
+In particular, % since $\varphi_s$ is non-negative,
+\[ \| \varphi_t(\cdot) \|_\infty \leq \| \varphi_0 \|_\infty
 +  K \int_0^t \| \varphi_s(\cdot) \|_\infty ds, \]
@@
 Fix $T>0$ and write $M$ for the corresponding constant from 
-Proposition~\ref{BoundednessVarphis}. Let 
-$\| F \|_{M} = \sup_{x \in [0,M]} |F(x)|$. We reserve $\widehat{K}$ for 
-the constant on the right hand side of 
-equation~(\ref{eq:boundDensityXt}), and 
-we write $K_{\varphi_0}$ for the Lipschitz constant of 
+Proposition~\ref{BoundednessVarphis}.
+Let $\| F \|_{M} = \sup_{m \in [0,M]} |F(m)|$.
+We reserve $\widehat{K}$ for the constant on the right hand side of 
+equation~(\ref{eq:boundDensityXt})
+and $\widetilde{K}$ for the constant in Lemma~\ref{regularityForX2},
+and write $K_{\varphi_0}$ for the Lipschitz constant of 
 $\varphi_0$. Set 
@@
 &\leq \big|\IE_x[\varphi_0(Z_t)]-\IE_y[\varphi_0(Z_t)]\big| 
-+ 2 \| F \|_M M t 
-\\ 
+    + 2 \| F \|_M M t \\ 
 & \leq \IE[|\varphi_0(Z_t^x)-\varphi_0(Z_t^y)|] 
@@
     + 2 \| F \|_M M t \\ 
-& \leq K_{\varphi_0}  (\sqrt{t} + \|y-x\|) 
+& \leq \widetilde{K} K_{\varphi_0}  (\sqrt{t} + \|y-x\|) 
     + 2 \| F \|_M M t \\ 
-& \leq K_{\varphi_0} (\delta + \delta^3) 
+& \leq \widetilde{K} K_{\varphi_0} (\delta + \delta^3) 
     + 2 \| F \|_M M \delta^2 
-\leq (K_{\varphi_0} +1)\delta,
+\leq (\widetilde{K} K_{\varphi_0} +1)\delta,
 \end{align*}
@@
 \]
-Therefore, setting $t'=\delta^2$, for all $z$,
+Therefore, setting $t'=\delta^2$ and using Lemma~\ref{BoundednessVarPhis}, for all $z$,
 \[ 
@@
 \IE_y\big[ \varphi_{t-\delta^2}(Z_{\delta^2})\big]) 
-+ M\big(e^{\delta^2\| F \|_{M}}-e^{-\delta^2\| F \|_{M}}\big),
++ M\big(e^{\delta^2\| F \|_{M}}-e^{-\delta^2\| F \|_{M}}\big) .
 \end{align}
-where the last line follows from Lemma~\ref{BoundednessVarphis}.
 
@@
 \end{align*}
-where in the first inequality we have used Lemma~\ref{regularityForX1}. 
+where we have used Lemma~\ref{regularityForX1} and that $\|x-y\| < \delta^3$.
 Substituting in~(\ref{difference}),
@@
 \frac{d}{dt}\int \exp(\lambda x) \psi_t^\epsilon (x)dx
-	=\int \exp(\lambda x)\Delta \big(\psi_t^\epsilon \, \rho^{\epsilon}*\psi_t^\epsilon\big)(x) dx
-	\\
-	+\int \exp(\lambda x)\psi_t^\epsilon(x)\big(1-\rho^{\epsilon}*\psi_t^\epsilon(x)\big) dx\\
-	=\int (\lambda^2-1)\exp(\lambda x) \psi_t^\epsilon(x) \rho^{\epsilon}*
-	\psi_t^\epsilon(x) dx 
-	+\int \exp(\lambda x)\psi_t^\epsilon(x) dx\\
-\leq
-	\int \exp(\lambda x)\psi_t^\epsilon(x) dx,
+	= \int \exp(\lambda x)\Delta \big(\psi_t^\epsilon \, \rho^{\epsilon}*\psi_t^\epsilon\big)(x) dx
+	\\
+	+ \int \exp(\lambda x)\psi_t^\epsilon(x)\big(1-\rho^{\epsilon}*\psi_t^\epsilon(x)\big) dx
+    \\
+	= \int (\lambda^2-1)\exp(\lambda x) \psi_t^\epsilon(x) \smooth{\epsilon}* \psi_t^\epsilon(x) dx 
+	+ \int \exp(\lambda x)\psi_t^\epsilon(x) dx
+    \\
+    \leq \int \exp(\lambda x)\psi_t^\epsilon(x) dx,
 \end{multline}
@@
 \end{eqnarray*}
-Thus $\int \psi_t^\epsilon(x) dx$ is uniformly bounded above in
+Thus, Gronwall's inequality implies that $\int \psi_t^\epsilon(x) dx$ is uniformly bounded above in
 $\epsilon$ and $t\in [0,T]$. Note that this also then gives a uniform
@@
 Moreover, since $\psi_t^\epsilon\log \psi_t^\epsilon$ is uniformly bounded below,
-$$-\int \psi_t^\epsilon \log \psi_t^\epsilon \, \rho^{\epsilon}*\psi_t^\epsilon d x
-\leq C\int \rho^{\epsilon}*\psi_t^\epsilon d x=\int \psi_t^\epsilon dx.$$
+$$
+    -\int \psi_t^\epsilon \log \psi_t^\epsilon \, \rho^{\epsilon}*\psi_t^\epsilon dx
+    \leq
+    C\int \rho^{\epsilon}*\psi_t^\epsilon dx
+    =
+    C \int \psi_t^\epsilon dx.
+$$
 From this and~(\ref{change in ulogu}),
@@
 we have a uniform bound on $\int \psi_s^\epsilon(x)|\log \psi_s^\epsilon(x)| d x$.
-This in turn means that both
+From \eqref{change in ulogu}, this in turn means that both
 $\int_0^t \int(\zeta^{\epsilon}*\psi_s^\epsilon(x))^2  dx ds$ and
@@
     and let $T(t) = \Pi(\theta t) / \theta$.
+    \comment{Suppose also that $\theta \epsilon^2$ is bounded below.
+    (We could alternatively put a $1/\theta\epsilon^2$ term in the lemma.)}
     Then
@@
 \]
-    which is negative if $\theta(\epsilon^2 + t) > d/2 \delta$,
-so that
-the second term in \eqref{eqn:psi_infty_bound} 
+which is negative if $\theta(\epsilon^2 + t) > d/2 \delta$.
+At the maximum, $(\epsilon^2 + t) = d \delta / (2 \theta)$,
+so $(1 + t/\epsilon^2) = d \delta/(2 \theta \epsilon^2)$,
+and so this quantity is bounded uniformly over only $t$ but also $\epsilon$.
+\comment{That's where we use bounded-below-ness of $\theta \epsilon^2$.}
+Therefore, the second term in \eqref{eqn:psi_infty_bound} 
 is bounded by $C / (\epsilon^2 + t)^{d/2}$
@@
             \frac{\Pi(\theta t)}{\theta}
-            > A(\epsilon^2 + t)
+            > t + A(\epsilon^2 + t)
         \right\}
@@
 % % % % % % % % % % % % %
+\section{Lookdown Proofs}
+
+Now we turn to results about the lookdown process,
+first establishing the basic connection between the processes, Proposition~\ref{thm:mmt_application},
+and then in the next section, convergence of the lookdown process itself.
+
+\begin{proof}[of Proposition~\ref{thm:mmt_application}]
+    This proposition is the content of the Markov Mapping Theorem,
+    Theorem A.2 in \citet{etheridge/kurtz:2019},
+    applied to our situation.
+    In the notation of that theorem, $\gamma$ is what we have called $\kappa$ above,
+    $\alpha$ is the transition function that assigns levels uniformly on $[0, N]$ (in the first case)
+    or as a Poisson process with Lesbegue intensity (in the limiting case),
+    and we need a continuous $\psi^N(\lp)$ such that $|A^N f(\lp)| \le c_f \psi^N(\lp)$
+    for all $f \in \mathcal{D}(A^N)$ (and similarly a function $\psi$ for $A$).
+    We also need that applying the lookdown generator to a function and averaging over levels
+    is equivalent to applying the population process generator to the function
+    whose dependence on levels has been averaged out,
+    a condition which we precisely state, and verify,
+    in Appendix~\ref{sec: Markov Mapping Theorem Application}.
+
+    For finite $N$,
+    taking $f(\lp)$ of the form \eqref{eqn:test_functions},
+    we can use $\psi^N(\lp) = \langle C (1+ + u |F(x, \eta)|), \lp(dx, du) \rangle$
+    for an appropriate constant $C$.
+    For the scaling limit, recall that the test functions $f$ are of the form
+    $f(\lp) = \prod_{(x, u) \in \lp} g(x, u)$
+    with $g(x, u) = 1$ for $u \ge u_0$,
+    and so taking for example the most troublesome term in $Af(\lp)$,
+    we see that since $0 \le f(\lp) / g(x, u) \le 1$ for any $(x, u) \in \lp$,
+    \begin{align*} % \label{eqn:part_of_psi}
+        \big| f(\lp) \sum_{(x, u) \in \lp} F(x, \eta) u \frac{\partial_u g(x, u)}{g(x, u)} \big|
+        & \le
+        \| \partial_u g \|_\infty \sum_{(x, u) \in \lp} | F(x, \eta) u \ind_{u \le u_0} | \\
+        & \le
+        \| \partial_u g \|_\infty e^{u_0} \sum_{(x, u) \in \lp} | F(x, \eta) u e^{-u} | .
+    \end{align*}
+    The first line would be just what we want,
+    except that $\psi(\lp)$ cannot depend on $f$, and hence neither on $u_0$.
+    So, the second line provides us with the required bound,
+    absorbing $\| \partial_u g \|_\infty e^{u_0}$ into $c_f$
+    and $\langle |F(x, \eta) u e^{-u}|, \lp \rangle$ into $\psi(\lp)$.
+    % Furthermore, since $F(x, \eta)$ only depends on spatial location, not level,
+    % for a given $\lp$ (and hence $\eta = \kappa(\lp)$),
+    % $\sup_x |F(x, \eta)|$ is finite.
+    % Therefore, we may bound \eqref{eqn:part_of_psi} by
+    % $\sup_x |F(x, \eta)| \langle u e^{-u}, \lp \rangle$.
+    % To do this we must restrict $\lp$ to lie in the space of measures
+    % for which this is finite;
+    % however, this is a completely metrizable space
+    % \citep[see Condition 2.1 in][]{etheridge/kurtz:2018},
+    % and our processes fall in this space (by conditional uniformity).
+\end{proof}
+
+% % % % % % % % % % % % %
 \subsection{Tightness of the Lookdown Process}
@@
 Recall that the level $U_a(t)$ of a line of descent evolves as
-\comment{TODO: harmonize notation with above}
 $$
-\dot u 
-=
-c^N(x, \eta)
-u^2
-- b^N(x, \eta)
-u,
+\dot u = c_\theta(x, \eta) u^2 - b_\theta(x, \eta) u,
 $$
-where
-\begin{align*}
-    c^N(x, \eta) &= \frac{\theta}{N} \gamma(x, \eta) \int_{\IR^d} r(y, \eta) q(x, dy) \\
-    \text{and}\qquad
-    b^N(x, \eta)
-    &=
-    \theta \gamma(x, \eta) \int_{\IR^d} \left(r(y, \eta) - r(x, \eta)\right) q(x, dy)
-    + F(x, \eta) 
-\end{align*}
-(see equations \eqref{eqn:level_generator} and \eqref{eqn:b_limit}), where
-$c^N(x, \eta) \ge 0$ and $b^N(x, \eta)$ may take either sign.
-Assumptions~\ref{def:model_setup} imply that $c^N(x, \eta)$ is bounded
-and $b^N(x, \eta)$, because of $F(x, \eta)$, is bounded above but not necessarily below.
+where $b_\theta(x, \eta)$ and $c_\theta(x, \eta)$ are defined in \eqref{b_defn}
+and \eqref{c_defn} respectively.
+Note that $c_\theta(x, \eta) \ge 0$ and $b_\theta(x, \eta)$ may take either sign.
+Assumptions~\ref{def:model_setup} imply that $c^N(x, \eta)$ is bounded,
+while $b^N(x, \eta)$, because of $F(x, \eta)$, is bounded above but not necessarily below.
 In \citet{kurtz/rodrigues:2011}, $b^N$ was bounded above and $c^N$ was bounded away from zero,
-so they noted that if $U_a(t) \ge b^N/c^N$
-lines of descent would only move upwards from that time onwards.
-This allows the processes to be jointly and simultaneously constructed
+so they noted that if $U_a(t) \ge b^N/c^N$ for some label $a$,
+that line of descent would only move upwards from that time onwards.
+Furthermore, coefficients did not depend on the state of the process (i.e., on $\eta$),
+thus allowing the processes to be jointly and simultaneously constructed
 for all values of $N$, with a pointwise embedding
@@
 since in the deterministic case there is no branching.
-In our case $b^N$ and $c^N$ depend on the state of the population,
-so we have no such monotonicity.
 
@@
 each line of descent
-gives birth to lines at higher levels at rate $2 (N - u) c^N(x, \eta)$,
+gives birth to lines at higher levels at rate $2 (N - u) c_\theta(x, \eta)$,
 and each such new line chooses a level uniformly from $[u, N]$,
@@
         \right)
-        du_1 q^m(x, dy, \eta^N_s)
+        q^m(x, dy, \eta^N_s) du_1 
 \\ & \qquad \qquad \qquad \qquad {}
@@
 \begin{align} \label{eqn:f_xi_qv}
+    \begin{split}
     [M^f]_t
@@
     ds .
-\end{align}
+\end{split}\end{align}
 
@@
     of the form $g(x) h(u)$, where $g \in C_b(\overline{\IR^d})$ is bounded and continuous
-    and $h \in C_c([0, \infty))$.
+    and $h \in C_c([0, \infty))$ is compactly supported.
     This space is completely metrizable,
@@
     $\sup_{\lp \in K} \langle f_k, \lp \rangle < \infty$ for each $k$;
-    therefore, compact containment follows from Lemma~\ref{lem:compact containment lookdown}.
-
-    Theorem~3.9.1 of \citet{EK} requires that $\{(F(\lp^N_t))_{t \ge 0}\}_N$
-    is tight as a sequence of real-valued c\`adl\`ag processes for all $F$ in a subset
+    therefore, compact containment will follow from Lemma~\ref{lem:compact containment lookdown}.
+
+    We require that $\{(F(\lp^N_t))_{t \ge 0}\}_N$
+    is tight as a sequence of real-valued c\`adl\`ag processes, for all $F$ in a subset
     of $\bar C(\lpmeasures)$, the bounded, continuous functions on $\lpmeasures$,
@@
     but they do separate points and vanish nowhere, so
-    by the Stone-Weierstrass theorem, the algebra they generate is dense in $C_0(\lpmeasures)$,
-    the continuous functions that vanish at infinity
-    (i.e., are less than $\epsilon$ outside of a compact set, for any $\epsilon$).
-    Since $C_0(\lpmeasures)$ is dense in $\bar C(\lpmeasures)$
-    with respect to uniform convergence on compact subsets,
-    it suffices to show that tightness for the processes $\langle f, \lp^N_t\rangle$
+    by the Stone-Weierstrass theorem, the algebra they generate is dense
+    % in $C_0(\lpmeasures)$, the continuous functions that vanish at infinity
+    % (i.e., are less than $\epsilon$ outside of a compact set, for any $\epsilon$).
+    % Since $C_0(\lpmeasures)$ is dense
+    in $\bar C(\lpmeasures)$ (with respect to uniform convergence on compact subsets).
+    So, it suffices to show that tightness for the processes $\langle f, \lp^N_t\rangle$
     extends to finite sums and products of these processes,
@@
     in Section~\ref{sec:lookdown_generator_proofs}.
+    \comment{TODO: refer to correct thing}
     Finally, we must show that the limiting lookdown process $\lp$
@@
     Then under the assumptions of Lemma~\ref{lem:compact containment lookdown},
-    for any $T$ there exists a constant $K$ such that for all $M > 0$,
+    for any $T$ there exists a constant $K(T)$ such that for all $M > 0$,
     $$ 
@@
     <
-    \frac{K}{M} .
+    \frac{K(T)}{M} .
     $$
@@
     \label{lem:compact containment hn}
+    Suppose $f \in C(\bar \IR^d \times [0, \infty))$ and there is a $u_f$ such that
+    $f(x, u) = 0$ for all $x$ and $u \ge u_f$.
     Under the assumptions of Lemma~\ref{lem:compact containment lookdown},
-    for any $T$ and $k$ there exists a constant $K_k$ such that for all $M > 0$,
+    for any $T$ there exists a constant $K(f,T)$ such that for all $M > 0$,
     $$ 
-    \limsup_{N \to \infty} \IP\left\{ \sup_{0 \le t \le T} \langle h_k, \lp^N_t \rangle > M \right\}
+    \limsup_{N \to \infty} \IP\left\{ \sup_{0 \le t \le T} \langle f, \lp^N_t \rangle > M \right\}
     <
-    \frac{K_k}{M} .
+    \frac{K(f,T)}{M} .
     $$
@@
 \begin{proof}[of Lemma~\ref{lem:compact containment hn}]
-    Let $h$ be as in Lemma~\ref{lem:h_containment}.
-    For any $f \in C(\bar \IR^d \times [0, \infty))$ with compact support,
-    there is a $c_f < \infty$ such that $f(x, u) \le c_f h(u)$.
+    Let $h$ be as in Lemma~\ref{lem:h_containment},
+    so there is a $c_f < \infty$ such that $f(x, u) \le c_f h(u)$ for all $x$ and $u$.
     Therefore, $\langle f, \xi \rangle \le \langle h, \xi \rangle$,
@@
         <
-        \frac{K c_f}{M} .
+        \frac{K(T) c_f}{M} .
     \end{align*}
@@
 
-\begin{lemma}[Compact containment for $\lp$]
-    \label{lem:compact containment lookdown}
+\begin{lemma}[Compact containment for $\lp$] \label{lem:compact containment lookdown}
+    Let $f_1, f_2, \ldots$ be a sequence of functions each satisfying the conditions
+    of Lemma~\ref{lem:compact containment hn}.
     Under Assumptions~\ref{def:model_setup},
-    if $\theta/N \to \alpha$ and $\lp_0^N \to \lp_0$ weakly as $N \to \infty$
-    \comment{and they are conditionally Uniform with the limit conditionally Poisson},
-    for any $T$ and $\delta > 0$ there exists a sequence
+    if $\theta/N \to \alpha$ and $\lp_0^N \to \lp_0$ weakly as $N \to \infty$,
+    where each $\lp_0^N$ is conditionally uniform given $\eta_0^N$
+    in the sense of \eqref{eqn:conditionally_uniform}
+    and $\lp_0$ is conditionally uniform given $\eta_0$
+    in the sense of \eqref{eqn:conditionally_poisson},
+    then for any $T$ and $\delta > 0$ there exists a sequence
     $(C_1, C_2, \ldots)$ of finite constants such that
@@
     \IP\left\{
-        \sup_{0 \le t \le T} \langle h_k, \lp^N_t \rangle > C_n
+        \sup_{0 \le t \le T} \langle f_k, \lp^N_t \rangle > C_k
         \text{ for some } k \ge 1
@@
 In other words, the processes $\lp^N$ stay in 
-the compact set
+the set
 $$
@@
 for all $0 \le t \le T$
-with uniformly high probability.
-\comment{
-    Note that we could instead of the vague topology on locally finite measures,
-    take the space of measures with $\langle h, \xi \rangle < \infty$
-    for which $\xi_n \to \xi$ if $\langle f, \xi \rangle < \infty$ for all $f$ for which $f \le c_f h$,
-    which is completely metrizable
-    as in Condition 2.1 of \citet{etheridge/kurtz:2019}.
-}
+with uniformly high probability,
+a set which is compact if we choose $\{f_k\}$ appropriately.
+% \comment{
+%     Note that we could instead of the vague topology on locally finite measures,
+%     take the space of measures with $\langle h, \xi \rangle < \infty$
+%     for which $\xi_n \to \xi$ if $\langle f, \xi \rangle < \infty$ for all $f$ for which $f \le c_f h$,
+%     which is completely metrizable
+%     as in Condition 2.1 of \citet{etheridge/kurtz:2019}.
+% }
 
@@
     \IP\left\{
-        \sup_{0 \le t \le T} \langle h_k, \lp^N_t \rangle > C_k
+        \sup_{0 \le t \le T} \langle f_k, \lp^N_t \rangle > C_k
         \text{ for some } k \ge 1
@@
     \IP\left\{
-        \sup_{0 \le t \le T} \langle h_k, \lp^N_t \rangle > C_k
+        \sup_{0 \le t \le T} \langle f_k, \lp^N_t \rangle > C_k
     \right\} ,
@@
     so \eqref{eqn:compact eqn lookdown} follows
-    by taking $C_k = 2^{k-1} K_k / \delta$ and using Lemma~\ref{lem:compact containment hn}.
+    by taking $C_k = 2^{k-1} K(f_k, T) / \delta$ and using Lemma~\ref{lem:compact containment hn}.
 \end{proof}
@@
 \begin{proof}[of Lemma~\ref{lem:compact containment hn}]
-    \comment{(TODO: shorten and make constants have reasonable notation)}
     Applied to $f(x, u) = h(u)$, the martinagle representation~\eqref{eqn:f_xi_mgale} is
@@
     Now consider the maximum. By \eqref{eqn:hn_bound},
+    using that the integrand is nonnegative,
     \begin{align*}
@@
         \lp_s^N(dx, du) \big \rangle
-        ds ,
-    \end{align*}
-    where there is no supremum before the integral because the integrand is nonnegative.
+        ds .
+    \end{align*}
 
     Again since $\sqrt{x} \le 1 + x$ for $x \ge 0$,
-    The Burkholder-Davis-Gundy inequality
+    the Burkholder-Davis-Gundy inequality
     tells us that there is a $C'$ such that
@@
         \right] ds \right) 
-    \\ & =
+    \\ & \le
         C' \left( 1 + 2 C_a \int_0^\infty h(v)^2 dv
@@
     \\ & \le
-        C'' e^{C_1 T} ,
-    \end{align*}
-    for a constant $C''$ which is finite
+        C_2 e^{C_1 T} ,
+    \end{align*}
+    for a constant $C_2$ which is finite
     by our assumption that $\int_0^\infty h(v)^2 dv < \infty$.
@@
         \IE\left[ \langle h, \lp_0^N \rangle \right]
-        + (C'' + C_0 / C_1) e^{C_1 T},
+        + (C_2 + C_0 / C_1) e^{C_1 T},
     \end{align*}
@@
             \IE\left[ \langle h, \lp_0^N \rangle \right]
-            + (C'' + C_0 / C_1) e^{C_1 T}
+            + (C_2 + C_0 / C_1) e^{C_1 T}
         }{ K } .
@@
 
-Here, just as a sanity check, 
-we make sure that the limiting generator is indeed the limit of the generators.
+\comment{This is a duplicate with Lemma~\ref{lem:limit_mgale}; compare and remove this one.}
 
 \begin{lemma}[Identifying the limit as a solution to the martingale problem]
-    \label{lem:limit_mgale}
+    \label{lem:limit_mgale2}
 As $N \to \infty$,
@@
 \end{lemma}
-\begin{proof}
+
+\begin{proof}[of Lemma~\ref{lem:limit_mgale2}
 We use Theorem 4.8.10 in \cite{EK}.

### 2023-03-10 forwards-and-backwards.tex
edits up to appendix

@@
     \big\langle
-        c^N(x, \eta^N_s)
+        c_\theta(x, \eta^N_s)
         \int_u^N \int_{\IR^d}
@@
         \left(
-            c^N(x, \eta^N_s) u^2
-            - b^N(x, \eta^N_s) u
+            c_\theta(x, \eta^N_s) u^2
+            - b_\theta(x, \eta^N_s) u
         \right)
@@
     \int_0^t
-    \bigg \langle c^N(x, \eta_s^N) \int_u^N \int_{\IR^d}
+    \bigg \langle c_\theta(x, \eta_s^N) \int_u^N \int_{\IR^d}
         \big[ f(y, u_1)^2
@@
     of equations~\eqref{eqn:f_xi_mgale} and~\eqref{eqn:f_xi_qv}.
-    Indeed, the proof follows exactly as the proof of
-    Lemma~\ref{lem:eta_projections_tightness},
-    except that terms are bounded by constant multiples of $\langle h, \xi^N_s \rangle$
-    instead of $\langle 1, \eta^N_s \rangle$.
-    \comment{Give an example of this.}
-    There is only one term that might use explanation,
-    which is
-    \begin{align*}
-        &
-        \frac{\theta}{N} \int_{\IR^d} \int_u^N (f(y, u) - f(x, u)) du_1 q^m(x, dy, \eta^N_s)
-        \\ &\qquad
-        % = \frac{\theta}{N} (N - u) \int_{\IR^d} (f(y, u) - f(x, u)) q^m(x, dy, \eta^N_s) \\ &\qquad
-        = \left(1 - \frac{u}{N}\right) \theta \int_{\IR^d}
-            (f(y, u) - f(x, u)) q^m(x, dy, \eta^N_s) ,
-    \end{align*}
-    but this is now bounded as in the proof of Lemma~\ref{lem:eta_f_bound}.
+    Rewriting~\eqref{eqn:f_xi_mgale} with $c_\theta = c_\theta(x, \eta_s)$,
+    \begin{align*}
+        \langle f, \lp_t \rangle
+        &=
+        \langle f, \lp_0 \rangle
+        + M^f_t
+        + \int_0^t \Big\langle
+            c_\theta \int_u^N \int (f(y, u_1) + f(x, u_1)) q^m(x, dy) du_1
+        \\ {} &\qquad
+            + c_\theta (N - u) \int (f(y, u) - f(x, u)) q^m(x, dy)
+            + (c_\theta u^2 - b_\theta u) \frac{d}{du} f,
+            \lp_s
+        \Big\rangle ds
+        &\le
+        \langle f, \lp_0 \rangle
+        + M^f_t
+        + \int_0^t \Big\langle
+            c_\theta \int_u^N \int (f(y, u_1) + f(x, u_1)) q^m(x, dy) du_1
+        \\ {} &\qquad
+            + c_\theta (N - u) \int (f(y, u) - f(x, u)) q^m(x, dy)
+            + (c_\theta u^2 - b_\theta u) \frac{d}{du} f,
+            \lp_s
+        \Big\rangle ds
+    \end{align*}
+    The bounds analogous to \eqref{eqn:eta_projections_goal1} and \eqref{eqn:eta_projections_goal2}
+    follow as in the proof of Lemma~\ref{lem:eta_projections_tightness}:
+    for instance, observe that using that $c_\theta \le C_0$ for some $C_0$,
+    the predictable part of this semimartingale decomposition is bounded by
+    \begin{align*}
+        \Big\langle
+            2 C_0 \|f\|_\infty u_f
+            + (1 - u/N) \gamma B_f
+            + (C_0 u^2 - b_\theta u) \frac{d}{du} f,
+            \lp_s
+        \Big\rangle
+        &\le
+        \langle
+            C_0 u_f^2 + \sup_x |b_\theta(x, \eta_s)| u_f \|\frac{d}{du} f\|_\infty
+        \rangle ,
+    \end{align*}
+    which can be bounded as we did for \eqref{eqn:eta_projections_goal1}.
 \end{proof}
@@
 
-\comment{(TODO: Use notation for the motion of a lineage introduced in statement of theorem.)}
-
-Here
-\comment{(and in the statement of the theorem)}
-we take the high-density, deterministic limit
+Here we have taken the high-density, deterministic limit
 (so, $\theta, N \to \infty$ and $\theta/N \to 0$)
@@
 $$
-    \mathcal{L}^Y_s g(x) = \gamma ( \DG(rg)(x) - g \DG r(x) ) .
+    \mathcal{L}^Y_s g(x) = \gamma ( \DG(r(\cdot,\eta_s) g(\cdot))(x) - g(x) \DG r(x,\eta_s) ) .
 $$
+% (This is $\mathcal{L}^Y_s g(x) = \gamma ( \DG(rg)(x) - g \DG r(x) )$ in shorter but more cryptic notation.)
 The diffusion is time-inhomogeneous if the density is not constant with time
 (since recall that the coefficients $\gamma$ and $r$ depend on the density).
+Let $\varphi_t(x)$ be the limiting density, which solves \eqref{general deterministic limit},
+$\partial_t \varphi = r \DG^*[ \varphi_t \gamma ] + \varphi F$.
 Formally, the intensity of levels at $y$ at time $t$
@@
 To see why this should be true, 
-suppose that an ancestor has level $v$. Conditional on its 
+suppose that an ancestor at time $s$ has level $v$. Conditional on its 
 spatial motion $\{Y_u\}_{s\leq u\leq t}$, its level at time $t$ will
 be $v \exp(-\int_s^t(F+\gamma\Delta r)(Y_u)du)$. This will be less than a given level 
-$N$ if $v < N \exp(\int_s^t(F+\gamma\Delta r)(Y_u)du)$. 
+$\lambda$ if $v < \lambda \exp(\int_s^t(F+\gamma\Delta r)(Y_u)du)$. 
 The intensity of levels at $y$ that are descended from individuals at
-$x$ can therefore be obtained as the limit as $N\to\infty$ of 
-$1/N$ times the number of levels at $x$ at time zero with
-$u<N \exp(\int_s^t(F+\gamma\Delta r)(Y_u)du)$ and for which
+$x$ can therefore be obtained as the limit as $\lambda\to\infty$ of 
+$1/\lambda$ times the number of levels at $x$ at time zero with
+$u<\lambda \exp(\int_s^t(F+\gamma\Delta r)(Y_u)du)$ and for which
 the corresponding individual is at $y$ at time $t$, which is 
@@
 To simplify to equation \eqref{eqn:lineage_generator2},
-this, first define
+first define
 $
@@
 \end{eqnarray*}
-which is equation \eqref{eqn:lineage_generator}.
-
-\end{proof}
-
-\begin{proof}[of Corollary \ref{cor:lineages_simple}]
-
-In this section, we need only
-simplify equation \eqref{eqn:lineage_generator}
-in the case where $\covq = \sigma^2 I$.
-
-    \comment{TODO}
-
-\end{proof}
-
-\begin{proof}[of Corollary~\ref{cor:wavefront}
-    \comment{
-        TODO make non-redundant with proof of Theorem \ref{thm:lineages}.
-    }
-
-Let $Y$ denote the diffusion followed by following a single descendent line in this frame; 
-i.e.~the diffusion with generator ${\cal L}^Y\phi=\gamma\Delta(r\phi)-\gamma\phi\Delta r -\mathfrak{c}\nabla\phi $.
-Note in particular here we take $\mathcal{B}=\Delta$.
-We start by expressing the evolution of a singles ancestry line in terms of the descendent line $Y$.
-
-Formally, the intensity of levels at $y$ at time $t$ that are descended from 
-individuals that were at $x$ at time $0$ is
-\begin{equation}
-\label{formal intensity [1]}
-w(x)\IE_x\left[\exp\left(\int_0^t (F+\gamma \Delta r)(Y_s)ds\right)\ind_{Y_t=y}\right]dy,
-\end{equation}
-where the subscript $x$ in the expectation indicates that $Y_0=x$.
-To see why this should be true, 
-suppose that an ancestor has level $u$. Conditional on its 
-spatial motion $\{Y_s\}_{0\leq s\leq t}$, its level at time $t$ will
-be $u\exp(-\int_0^t(F+\gamma\Delta r)(Y_s)ds)$. This will be less than a given level 
-$N$ if $u<N \exp(\int_0^t(F+\gamma\Delta r)(Y_s)ds)$. 
-The intensity of levels at $y$ that are descended from individuals at
-$x$ can therefore be obtained as the limit as $N\to\infty$ of 
-$1/N$ times the number of levels at $x$ at time zero with
-$u<N \exp(\int_0^t(F+\gamma\Delta r)(Y_s)ds)$ and for which
-the corresponding individual is at $y$ at time $t$, which is 
-precisely the quantity in~(\ref{formal intensity}).
-
-It is easy to check that when we integrate~(\ref{formal intensity})
-with respect to $x$ we recover $w(y)dy$. 
-As a consequence of~(\ref{formal intensity}), writing $p(t,y,x)$ for
-the probability density that the ancestor $t$ units in 
-the past of an individual sampled 
-at $y$ was at $x$, then, still formally,
-\begin{equation}
-\label{ptyx}
-p(t,y,x)=\frac{w(x)}{w(y)}\IE_x\left[\exp\left(\int_0^t (F+\gamma\Delta r)(Y_s)ds\right)
-\ind_{Y_t=y}\right].
-\end{equation}
-
-To make~(\ref{ptyx}) meaningful, we multiply by suitable test functions and 
-integrate.
-$$\int\int \psi(y)w(y)p(t,y,x)\phi(x)dydx=\int\phi(x)w(x)
-\IE_x\left[\exp\left(\int_0^t(F+\gamma\Delta r)(Y_s)ds\right)\psi(Y_t)\right]dydx.$$
-
-Writing $\hat{T}_t$ for the semigroup corresponding to the motion of 
-ancestral lineages backwards in time (that is the semigroup corresponding
-to $p(t,x,y)$), we can write this as 
-$$\int \psi(y)w(y)\hat{T}_t\phi(y)dy=\int\phi(x)w(x)
-\IE_x\left[\exp\left(\int_0^t(F+\gamma\Delta r)(Y_s)ds\right)\psi(Y_t)\right]dx.$$
-Differentiating with respect to $t$ at $t=0$, and writing 
-$\hat{\mathcal L}$ for the generator of $\hat{T}_t$, we find
-\begin{eqnarray*}
-\int \psi(y)w(y)\widehat{\mathcal L}\phi(y)dy&=&
-\int\phi(x)w(x)\left({\mathcal L}^Y\psi(x)+\psi(x)(F+\gamma\Delta r)\psi(x)\right)dx\\
-&=&\int\phi(x)w(x)\left(\gamma\Delta(r\psi)-\gamma\psi\Delta r -\mathfrak{c}\nabla\psi 
-+(F+\gamma\Delta r)(\psi)\right)dx\\
-&=&\int\phi(x)w(x)\left(\gamma\Delta(r\psi)-\mathfrak{c}\nabla\psi+F(\psi)\right)dx\\
-&=&
-\int\psi(x)\left[r\Delta(\gamma \phi w)+F\phi w+\mathfrak{c}\nabla(\phi w)\right]dx.
-\end{eqnarray*}
-Since $\psi$ was arbitrary,
-\begin{eqnarray*}
-\hat{\mathcal L}\phi&=&\frac{1}{w}\left[ r\Delta (\gamma\phi w)+F\phi w
-+\mathfrak{c}\nabla(\phi w)\right]\\
-&=&\frac{\phi}{w}\left[r\Delta(\gamma w)+Fw+\mathfrak{c}\nabla w\right]
-+\frac{1}{w}\left[r\gamma w\Delta \phi +2\nabla (\gamma w)
-\nabla\phi+\mathfrak{c}w\nabla\phi\right]\\
-&=&r\gamma\left(\Delta\phi+2\frac{\nabla(\gamma w)}{\gamma w}\nabla\phi\right)
-+\mathfrak{c}\nabla\phi,
-\end{eqnarray*}
-where we have used that $w$ solves~(\ref{profile}).
-
+which is equation \eqref{eqn:lineage_generator2},
 \end{proof}

### 2023-03-11 forwards-and-backwards.tex
stationary dist corollary

@@
     In addition to the assumptions of Theorem~\ref{thm:lineages},
-    if the dispersal process is isotropic
-    (i.e., $\covq = \sigma^2 I$ and $\meanq$ is constant),
+    if the covariance of the dispersal process is isotropic
+    (i.e., $\covq = \sigma^2 I$),
     then
@@
     \end{equation}
+    (However, $\meanq$ can still depend on location.)
 \end{corollary}
@@
 run at speed $\sigma^2$ multiplied by the local per-capita production of 
-mature offspring 
-($r \gamma$)
-in a potential equal to the local output of juveniles tilted by migration bias
-($\varphi_s \gamma \exp(-\meanq \cdot x / 2 \sigma^2)$). In particular,
-lineages are drawn to regions of high fecundity (production of juveniles), but their
+mature offspring ($r \gamma$)
+in a potential tilted by migration bias
+($(\varphi_s \gamma)^2 \exp(-\meanq \cdot x / \sigma^2)$).
+In particular, lineages are drawn to regions of high fecundity (production of juveniles), but their
 speed is determined by the rate of production of mature offspring.
@@
 
-\begin{corollary}
-    \comment{TODO: write corollary saying what's in the previous sentence 
-    and what the stationary distribution is?}
+\begin{corollary} \label{cor:stationary_dist}
+    In addition to the assumptions of Corollary~\ref{cor:lineages_simple},
+    the population process is stationary (so $\varphi_t \equiv \varphi$),
+    and $\meanq(x) = \grad h(x)$ for some function $h$,
+    then $Y$ is reversible with respect to
+    \begin{align}
+        \pi(x)
+        =
+        \frac{\gamma}{r} \varphi(x)^2 e^{-h(x) / \sigma^2} .
+    \end{align}
 \end{corollary}
+
+\comment{I'm a bit surprised by the factor of 2 (that manifests as $\varphi^2$),
+    but I've checked where it comes from pretty carefully, and don't see anything wrong.}
+Long-term fitness of an individual
+is proportional to the fraction of lineages from the distant future that pass through the individual,
+and hence the total long-term fitness at a location is proportional to
+the stationary distribution of $Y$ there, if it exists.
+Therefore,
+if $\pi$ is integrable then the per-capita long-term fitness of an individual at $x$
+is proportional to $\pi(x) / \varphi(x)$.
 
@@
 which is equation \eqref{eqn:lineage_generator2},
+\end{proof}
+
+\begin{proof}[of Corollary~\ref{cor:stationary_dist}]
+For the moment, we will write $r(x)$ for $r(x, \eta)$
+and similarly for $\gamma(x)$.
+First, note that in this case
+$$
+    \Lgen f = \sigma^2 r \gamma \left(
+        \Delta f
+        + \grad ( 2 \log(\gamma \varphi) - h ) \cdot \grad f
+    \right) ,
+$$
+and that
+$$
+    \int_{\IR^d} e^{H(x)} f(x) (\Delta + \grad H(x) \cdot \grad) g(x) dx
+    =
+    - \int_{\IR^d} e^{H(x)} \left\{
+        \grad f(x) \cdot \grad g(x)
+    \right\} dx .
+$$
+Therefore, by choosing $H(x) = 2 \log(\gamma(x) \varphi(x)) - h(x)$
+and
+$$ \pi(x)
+    = e^{H(x)} / (\sigma^2 r(x) \gamma(x))
+    = \frac{\gamma(x) \varphi(x)^2 e^{-h(x)}}{\sigma^2 r(x)} ,
+$$
+we have that
+$$
+    \int_{\IR^d} \pi(x) f(x) \Lgen g(x) dx
+    =
+    - \int_{\IR^d} e^{H(x)} \grad f(x) \cdot \grad g(x) dx .
+$$
+Since this is symmetric, the process $Y$ is reversible with respect to $\pi$;
+the constant factor of $\sigma^2$ does not affect the result.
 \end{proof}

### 2023-03-11 forwards-and-backwards.tex
good citation
rewrite with gamma B1 assumption

@@
 
-\comment{TO CITE: \citet{ghosh2022emergent}}
-
 As one takes a journey, long or short, the landscape changes:
@@
 spatial analogue of a Wright-Fisher diffusion. 
+For instance, \citep{ghosh2022emergent}
+derives a stochastic version of~\eqref{semilinear PDE} to describe abundances of mutant bacteria strains
+along the human gut.
 For very large $N$, and on suitable timescales, 
@@
     is uniformly bounded for $x \in \IR^d$ and $\eta \in \measures$.
+        \label{gamma_B_condition}
 \end{enumerate}
@@
 the condition from Assumptions~\ref{def:model_setup} 
-that $\gamma (x,m)$ be uniformly bounded 
+that $\gamma(x,m)$ be uniformly bounded 
 is violated.
@@
 getting too big. 
-In practice in our simulations we choose a suitably small value for $\beta$, define
-\begin{align*}
-    \gamma(x, m) = (1 - \exp(- \beta m)) / \beta, \qquad
-    F(x, m) = \exp(- \beta m) / \beta ,
-\end{align*}
-and set $\mu_\theta(x, m) = \max(0, \gamma - F / \theta)$.
-\comment{I don't understand this - something has gone wrong.}
-\comment{TODO: peter to look into this}
+In practice in our simulations we
+take discrete time steps of length $dt$ (with $dt$ suitably small),
+and have each individual with local density $m$ reproduce and die, respectively, with probabilities
+\begin{align*}
+    p_\text{birth}(m) = \left(1 - e^{- m dt}\right)
+    \qquad 
+    p_\text{death}(m) = \left(1 - e^{- (m (1+1/\theta) - 1/\theta) dt} \right) ,
+\end{align*}
+so that $\gamma(x, m) = p_\text{birth}(m)/dt \approx m$
+and
+\begin{align*}
+    F(x, m) = \theta(\gamma(x, m) - \mu(x, m)) / dt \approx 1 - m .
+\end{align*}
 Birth and death rates are equal at density $m = 1$,
@@
 
-\comment{In this section I haven't specified the filtration for the martingale problem.}
-
 Now we can present the main convergence theorem that is analogous
 to Theorem~\ref{thm:nonlocal_convergence} for the population process.
-
-\comment{the next theorem needs rewriting along the lines of Thm A.12 in Kurtz and Rodrigues.}
-\comment{TODO: it's been rewritten some; but needs checking against that Thm yet}
 
@@
 
+Below we will have frequent use for the quantity
+\begin{equation}
+\label{generator Bf}
+    B_f(x, \eta) = \theta \int_{\IR^d} (f(y) r(y, \eta) - f(x) r(x, \eta)) q_\theta(x, dy) .
+\end{equation}
+
 First, we prove Lemma~\ref{lem:conditions on r}.
@@
 \begin{proof}[of Lemma~\ref{lem:conditions on r}]
-    TODO MOVE PROOF HERE
+Here, we need to prove that $|\gamma(x, \eta) B_1(x, \eta)|$ is bounded,
+uniformly over $x$ and $\eta$.
+First suppose that
+Condition~\ref{control through r} of  
+Lemma~\ref{lem:conditions on r} is satisfied.
+We write
+\begin{align*}
+    r\big(y,\rho_r*\eta(y)\big) - r\big(x,\rho_r*\eta(x)\big)
+    &=
+    \sum_i (y_i - x_i) \partial_{x_i} \Big(r\big(x,\rho_r*\eta(x)\big)\Big) 
+    \\ &\qquad {}
+    +
+    \frac{1}{2} \sum_{ij} (y_i - x_i)(y_j - x_j)
+        \partial_{x_i x_j} \Big(r\big(\smooth{r}\eta(z)\big)\Big) ,
+\end{align*}
+where $z = \kappa x + (1-\kappa) y$ for some $0 \le \kappa \le 1$.
+Condition~\ref{control through r} 
+gives uniform bounds on the derivatives of $r(x, \rho_r*\eta(x))$ 
+in this expression and so we have a bound of the form
+\begin{multline*}
+\Big| r\big(y,\rho_r*\eta(y)\big) - r\big(x,\rho_r*\eta(x)\big) \Big|
+\\
+\leq
+        K_1 \left|
+            \theta \int_{\IR^d} \sum_i (y_i - x_i) q_\theta(x, dy)
+        \right|
+        +
+        K_2 \left|
+            \theta \int_{\IR^d} \sum_{ij} (y_i - x_i) (y_j - x_j)  q_\theta(x, dy)
+        \right| 
+\end{multline*}
+for suitable constants $K_1$, $K_2$.
+This is bounded uniformly because
+$q_\theta(x, dy)$ is the density of a Gaussian with mean $\meanq(x)/\theta$
+and covariance $\covq(x)/\theta$, and both $\meanq(x)$ and $\covq(x)$
+are bounded uniformly in $x$ under Assumptions~\ref{def:model_setup}.
+u implies that $|B_1|$ is uniformly bounded;
+since $\gamma$ is bounded as well, so is $|\gamma B_1|$.
+
+Now suppose that instead
+Condition~\ref{control through gamma} of Lemma~\ref{lem:conditions on r} is satisfied.
+is satisfied.
+First note that
+\begin{multline*}
+    r(x, \smooth{r}\eta(y)) - r(x, \smooth{r}\eta(x))
+    \\
+=
+    (\smooth{r}\eta(y) - \smooth{r}\eta(x)) r'(x,\smooth{r}\eta(x))
+    + \frac{1}{2} (\smooth{r}\eta(y) - \smooth{r}\eta(x))^2 r''(x, \overline{m}),
+\end{multline*}
+where $\overline{m}= \kappa'\smooth{r}\eta(x) +(1-\kappa') 
+\smooth{r}\eta(y)$ for some $0\leq \kappa'\leq 1$, and
+we have used $r'$ and $r''$ to denote the first and second derivatives of $r(x,m)$
+with respect to the second argument.
+So, in this case
+\begin{align*}
+&
+\left| \theta 
+    \int_{\IR^n} 
+        \big\{
+            r\big(x,\smooth{r}\eta(y)\big)
+            -
+            r\big(x,\smooth{r}\eta(x)\big)
+        \big\}
+    q_{\theta}(x,dy) 
+\right| 
+\\ &\qquad
+\le
+   \|r'\|_\infty
+    \left|
+        \theta \int_{\IR^d}
+            (\smooth{r}\eta(y) - \smooth{r}\eta(x))
+        q_\theta(x, dy)
+    \right|
+    +
+   \|r''\|_\infty
+    \left|
+        \theta \int_{\IR^d}
+            (\smooth{r}\eta(y) - \smooth{r}\eta(x))^2
+        q_\theta(x, dy)
+    \right| .
+\end{align*}
+Therefore,
+under Condition~\ref{control through gamma}, $|B_1(x,\eta)|$ is bounded by 
+a constant times $\smooth{\gamma}\eta(x)+(\smooth{\gamma}\eta(x))^2$;
+since $m^2\gamma(m)$ is bounded, so is $|\gamma(x,\eta) B_1(x,\eta)$.
 \end{proof}
@@
 \end{align}
-    where $M^N_t(f)$ is a martingale and, for the moment, we are defining
-    \begin{equation}
-\label{generator Bf}
-        B_f(x, \eta) = \int_{\IR^d} \theta (f(y) r(y, \eta) - f(x) r(x, \eta)) q_\theta(x, dy) .
-    \end{equation}
-
-\comment{TODO MOVE SOME OF THIS TO PROOF OF LEMMA~\ref{lem:conditions on r}}
-We need a bound on $\gamma(x,\eta)B_f(x,\eta)+F$.
-First suppose that
-Condition~\ref{control through r} of  
-Assumptions~\ref{def:model_setup} is satisfied.
-We write
-    \begin{align*}
-        f(y)r\big(y,\rho_r*\eta(y)\big) - f(x)r\big(x,\rho_r*\eta(x)\big)
-        &=
-        \sum_i (y_i - x_i) \partial_{x_i} \Big(f(x)r\big(x,\rho_r*\eta(x)\big)\Big) 
-        \\ &\qquad {}
-        +
-        \frac{1}{2} \sum_{ij} (y_i - x_i)(y_j - x_j)
-            \partial_{x_i x_j} \Big(f(z)r\big(\smooth{r}\eta(z)\big)\Big) ,
-    \end{align*}
-    where $z = \kappa x + (1-\kappa) y$ for some $0 \le \kappa \le 1$. Condition~\ref{control through r} 
-gives uniform bounds on the derivatives of $r(x, \rho_r*\eta(x))$ 
-in this expression and so, provided $f$ also has uniformly bounded first
-and second derivatives, we have a bound of the form
-\begin{multline*}
-\Big| f(y)r\big(y,\rho_r*\eta(y)\big) - f(x)r\big(x,\rho_r*\eta(x)\big) \Big|
-\\
-\leq
-        K_1 \left|
-            \theta \int_{\IR^d} \sum_i (y_i - x_i) q_\theta(x, dy)
-        \right|
-        +
-        K_2 \left|
-            \theta \int_{\IR^d} \sum_{ij} (y_i - x_i) (y_j - x_j)  q_\theta(x, dy)
-        \right| 
-\end{multline*}
-for suitable constants $K_1$, $K_2$.
-This is bounded uniformly because
-$q_\theta(x, dy)$ is the density of a Gaussian with mean $\meanq(x)/\theta$
-and covariance $\covq(x)/\theta$, and both $\meanq(x)$ and $\covq(x)$
-are bounded uniformly in $x$ under Assumptions~\ref{def:model_setup}.
-
-Now suppose that instead
-Condition~\ref{control through gamma} of Assumptions~\ref{def:model_setup}
-is satisfied.
-First note that,  
+where $M^N_t(f)$ is a martingale.
+% and we are defining
+% \begin{equation}
+% \label{generator Bf}
+%     B_f(x, \eta) = \int_{\IR^d} \theta (f(y) r(y, \eta) - f(x) r(x, \eta)) q_\theta(x, dy) .
+% \end{equation}
+
+We need a bound on $\gamma(x,\eta)B_f(x,\eta)+fF$.
+First note that we may rewrite $B_f(x, \eta)$ as
 \begin{align}
@@
 \\ 
- \label{eqn:q_bound_split}
+    &\qquad {} =
+    \Big| \theta 
+        \int_{\IR^n} 
+            ( f(y) - f(x) )
+            r\big(y, \smooth{r}\eta(y)\big)
+        q_{\theta}(x,dy)
+\\ 
+\nonumber
+    &\qquad \qquad {}  +
+    \theta 
+            f(x)
+        \int_{\IR^n} 
+            \big\{
+                r\big(y,\smooth{r}\eta(y)\big)
+                -
+                r\big(x,\smooth{r}\eta(x)\big)
+            \big\}
+        q_{\theta}(x,dy) 
+    \Big| 
+\\ 
     &\qquad {} \leq
@@
         \int_{\IR^n} 
-                \big\{
-                    f(y) r\big(y, \smooth{r}\eta(y)\big)
-                    -
-                    f(x) r\big(x,\smooth{r}\eta(y)\big)
-                \big\}
+            ( f(y) - f(x) )
         q_{\theta}(x,dy)
     \right|
-    \\ 
-\nonumber
-	    &\qquad \qquad {}  +
-        \left| \theta 
-            \int_{\IR^n} 
-                \big\{
-                    f(x) r\big(x,\smooth{r}\eta(y)\big)
-                    -
-                    f(x) r\big(x,\smooth{r}\eta(x)\big)
-                \big\}
-            q_{\theta}(x,dy) 
-        \right| .
+    +
+    \|f\|_\infty |B_1(x, \eta)| .
 \end{align}
-
- Writing
-    $K_3 = \sup_{x,m} \max_i |\partial_{x_i} f(x)r(x, m)|$
-    and 
-    $K_4 = \sup_{x,m} \max_{i,j} |\partial_{x_i x_j} f(x)r(x, m)|$, since
-\[\big|\partial_{x_i}\big(f(x)r(x,\rho_r*\eta(y))\big|\leq K_3\]
-and
-\[\big|\partial_{x_ix_j}\big(f(x)r(x,\rho_r*\eta(y))\big|\leq K_4,\]
-the first term
-is bounded exactly as above. For the second, 
-    \begin{multline*}
-        r(x, \smooth{r}\eta(y)) - r(x, \smooth{r}\eta(x))
-        \\
-=
-        (\smooth{r}\eta(y) - \smooth{r}\eta(x)) r'(x,\smooth{r}\eta(x))
-        + \frac{1}{2} (\smooth{r}\eta(y) - \smooth{r}\eta(x))^2 r''(x, \overline{m}),
-    \end{multline*}
-    where $\overline{m}= \kappa'\smooth{r}\eta(x) +(1-\kappa') 
-\smooth{r}\eta(y)$ for some $0\leq \kappa'\leq 1$, and
-    we have used $r'$ and $r''$ to denote the first and second derivatives of $r(x,m)$
-with respect to the second argument.
-    So, writing $K_5=\|f\|_\infty\|r'\|_\infty$ and $K_6=\|f\|_\infty\|r''\|_\infty$, in
-this case 
-    the term in~\eqref{eqn:q_bound_split} is bounded by
-    \begin{align*}
-       K_5
-        \left|
-            \theta \int_{\IR^d}
-                (\smooth{r}\eta(y) - \smooth{r}\eta(x))
-            q_\theta(x, dy)
-        \right|
-        +
-       K_6
-        \left|
-            \theta \int_{\IR^d}
-                (\smooth{r}\eta(y) - \smooth{r}\eta(x))^2
-            q_\theta(x, dy)
-        \right| .
-    \end{align*}
-Under Condition~\ref{control through gamma} of 
-Assumptions~\ref{def:model_setup}, the right hand side is bounded by 
-a constant times $\smooth{\gamma}\eta(x)+(\smooth{\gamma}\eta(x))^2$ and 
-$m^2\gamma(m)$ is bounded. We have shown that $\gamma B_f$ is bounded, and so recalling that
-$F$ is bounded above, we can now conclude that
+The first term is bounded uniformly
+because $q_\theta(x, dy)$ is the density of a Gaussian with mean $\meanq(x)/\theta$
+and covariance $\covq(x)/\theta$,
+and both $\meanq(x)$ and $\covq(x)$
+are bounded uniformly in $x$ under Assumptions~\ref{def:model_setup}.
+Furthermore, Condition~\ref{gamma_B_condition} of Assumptions~\ref{def:model_setup}
+stipulates that $|\gamma(x, \eta) B_1(x, \eta)|$ is uniformly bounded,
+and so recalling that $F$ is bounded above, we can now conclude that
 under Assumptions~\ref{def:model_setup}

### 2023-03-20 forwards-and-backwards.tex
cites
edits with alison

@@
 	\comment{Need to thank KAVLI, Paris Cit\'e, various funders}
+    \comment{make notation for $\mathcal{D}$ consistent}
 
@@
 \newpage
+
+\comment{TODO: cite \citet{lam2023introduction,cantrell2004spatial}}
 
@@
 we expect that if we take a second limit of $\epsilon \to 0$,
-thus scaling the kernels appearing in $r$, $\gamma$, and $F$ and making interactions are pointwise,
+thus scaling the kernels appearing in $r$, $\gamma$, and $F$ and making interactions pointwise,
 we should recover a nonlinear PDE.
@@
 population density tends to infinity, whereas they also consider the situation in which
-that number remains finite; furthermore.
-On the other hand, we shall consider a scaling in which 
+that number remains finite;
+furthermore we shall consider a scaling in which 
 the reproduction mechanism is near-critical and look at large timescales,
@@
 corresponding to the porous medium equation results
-in a stationary distribution that is concentrated behind the wavefront, leading 
+in a stationary distribution for the ancestral lineage
+that is concentrated behind the wavefront, leading 
 us to conjecture that in the stochastic equation
@@
 \]
-Nonetheless it will be convenient to define the death rate $\mu_\theta$ in terms of 
+Nonetheless, it will be convenient to define the death rate $\mu_\theta$ in terms of 
 its deviation from $r\gamma$. 
@@
 where this equation defines $F(x, m) : \IR^d \times \IR_{\ge 0} \to \IR$,
+and $\rho_F$ is again a smooth kernel. 
+\comment{FIX UP THIS, REFER FORWARD}
+The function $F$ is nearly
 the net per capita reproductive rate, scaled by $\theta$,
-and $\rho_F$ is again a smooth kernel. 
+and would be equal to it in a nonspatial model;
+but 
 It will be convenient to work with $F$ instead of $\mu$.
@@
 
-\comment{Do we need a "Terminology" heading for this?}
 \begin{terminology*}
@@
  -  \int_{0}^{t}\bigg\{
-        \int\left( \int \theta
+        \bigg\langle \left( \int \theta
              \left(
@@
 %\\ & \qquad \qquad \qquad \qquad {}
-         \gamma(x, \eta^N_{s}) \eta^N_{s}(dx)
+         \gamma(x, \eta^N_{s}), \eta^N_{s}(dx) \bigg\rangle
 \\ & \qquad \qquad \qquad \qquad \qquad {}
-    + \int f(x) F(x, \eta^N_{s}) \eta^N_{s}(dx)
+    + \bigg\langle f(x) F(x, \eta^N_{s}),
+    \eta^N_{s}(dx) \bigg\rangle
     \bigg\} ds
@@
 
-We give two more concrete conditions under which the fourth condition is satisfied.
+We give two concrete situations in which the fourth condition is satisfied.
 
@@
 An instructive example is the case where $\gamma \equiv 1$ and $F \equiv 0$, so that $\mu_\theta = r$,
-and the population has all individuals at a single location (so, $\eta = \delta_x$),
+and $\eta = \delta_x$
+(i.e., the population has all individuals at a single location)
 in which case the mean rate of change of the total population size
@@
 satisfy; they just require some regularity of $r$ as a function of $x$. 
-Condition~\ref{control through r} is satisfied if 
+Condition~\ref{control through r} is also satisfied if for example
 $\|\nabla\rho_r\|\leq C\rho_r$ 
 and $m\partial_mr(x,m)$, $m^2\partial_{mm}r(x,m)$ are bounded.
-This will be satsified, for example, if $\rho_r$ decays 
-exponentially.
-On the other hand, it might, for example, seem more natural to take $\rho_r$ to be a Gaussian 
+This is the case, for instance, if $\rho_r$ decays exponentially.
+On the other hand, it might seem more natural to take $\rho_r$ to be a Gaussian 
 density with parameter $\sigma_r$, say. Then, 
@@
 and for superprocess limits with nonlocal interactions.
-See Figure \ref{fig:super_vs_det_2d} for illustrative simulations,
+See Figure \ref{fig:super_vs_det_2d} for snapshots of the population
 from direct simulation of the process using SLiM \citep{haller_slim_2019}.
@@
         and the equilibrium density is 10 individuals per unit area.
+        Blue curves are contours from a kernel density estimate.
         \label{fig:super_vs_det_2d}
@@
 \paragraph{Scaling limits with nonlocal interactions:}
-
 Recall that the process $(\eta_t^N)_{t\geq 0}$ takes its values in the space
@@
 further, that $\{\eta_0^N\}_{N\geq 1}$ is a sequence of 
-purely atomic measures, with $\eta^N$ comprised of atoms of mass $1/N$, which is
+purely atomic measures, with $\eta_0^N$ comprised of atoms of mass $1/N$, which is
 tight 
@@
 $F(x,\eta_s)=1-\smooth{F} \eta_s(x)$,
-we recover the superprocess with nonlinear death rates corresponding to logistic growth.
+we recover a superprocess with nonlinear death rates corresponding to logistic growth
+that is a continuous limit of the Bolker-Pacala model \citep{bolker/pacala:1997,bolker/pacala:1999}.
 We are not aware of a general result to determine when we will have uniqueness of 
@@
     \label{thm:local_convergence}
-\comment{Need to add conditions on initial condition}
-
     Let $(\eta^N_t)_{t \geq 0}$
@@
 \end{theorem}
+
 \begin{remark}
 In fact,
-our proof goes through without significant change under that conditions that
+our proof goes through without significant change under the conditions that
 $F(m)\ind_{m\geq 0}$ is bounded above (but not necessarily below), and that
@@
 a parent who was at location $y$ at time $t$ in the past. To make
-sense of this in our framework, in Section~\ref{ancestral lineages}, 
+sense of this in our framework, in Section~\ref{sec:lineages_proof}, 
 we justify a weak reformulation of this idea.
@@
 First, when is the motion of an ancestral 
-lineage, given complete knowledge of the population process,
- a well-defined Markov process?
+lineage, given complete knowledge of the population process, a well-defined process?
 In other words, is knowledge of the process $(\eta_t)_{t=0}^T$ that records 
@@
 may not make sense. Instead, it should be interpreted in a weak sense which is made precise
-in Section~\ref{ancestral lineages}.
+in Section~\ref{sec:lineages_proof}.
 \end{remark}
@@
     In addition to the assumptions of Corollary~\ref{cor:lineages_simple},
-    the population process is stationary (so $\varphi_t \equiv \varphi$),
+    if the population process is stationary (so $\varphi_t \equiv \varphi$),
     and $\meanq(x) = \grad h(x)$ for some function $h$,
@@
         $\theta/N$ not small on left; small on right.
-        (Note: noisier wave should move slower, we'll see this.)
+        % (Note: noisier wave should move slower, although maybe not much since it's pushed.)
         \label{fig:pme_waves}
@@
 
-\begin{figure}
-    \begin{center}
-        \includegraphics{figures/ex3_fkpp/fkpp_123.lineages}
-        \includegraphics{figures/ex3_fkpp/fkpp_123.lineagehist}
-        \includegraphics{figures/ex3_pme/pme_123.lineages}
-        \includegraphics{figures/ex3_pme/pme_123.lineagehist}
-        \includegraphics{figures/ex3_allen-cahn/allen-cahn_123.lineages}
-        \includegraphics{figures/ex3_allen-cahn/allen-cahn_123.lineagehist}
-    \end{center}
-    \caption{
-        Six panels: one pair for FKPP, one for the porous medium 
-equation with logistic growth~(\ref{PME}), and one for 
-the Allen-Cahn equation~(\ref{eqn:allen_cahn}).
-        Each pair shows (top) lineage traced back in wavefront,
-        and (bottom) stationary distribution of lineage location,
-        compared to analytical solution for the porous medium case.
-        \label{fig:pme_vs_fkpp}
-    }
-\end{figure}
+% \begin{figure}
+%     \begin{center}
+%         \includegraphics{figures/ex3_fkpp/fkpp_123.lineages}
+%         \includegraphics{figures/ex3_fkpp/fkpp_123.lineagehist}
+%         \includegraphics{figures/ex3_pme/pme_123.lineages}
+%         \includegraphics{figures/ex3_pme/pme_123.lineagehist}
+%         \includegraphics{figures/ex3_allen-cahn/allen-cahn_123.lineages}
+%         \includegraphics{figures/ex3_allen-cahn/allen-cahn_123.lineagehist}
+%     \end{center}
+%     \caption{
+%         Six panels: one pair for FKPP, one for the porous medium 
+% equation with logistic growth~(\ref{PME}), and one for 
+% the Allen-Cahn equation~(\ref{eqn:allen_cahn}).
+%     \comment{clarify this is in a moving frame of reference}
+%         Each pair shows (top) lineage traced back in wavefront,
+%         and (bottom) stationary distribution of lineage location,
+%         compared to analytical solution for the porous medium case.
+%         \label{fig:pme_vs_fkpp}
+%     }
+% \end{figure}
 
@@
 solution will converge to the profile $w^F$ with the minimal wavespeed, $c=2$
-\citep{kolmogorov/petrovsky/piscounov:1937,bramson:1983}.
+\citep{kolmogorov/petrovsky/piscounov:1937,fife1977approach,bramson:1983}.
 No matter what initial condition,
@@
 The phenomenon is discussed in Section~16.10 of \citet{haller2022evolutionary},
-and has been described in similar models, e.g., by \citet{sasaki1997clumped,hernandezgarcia2004clustering,young2001reproductive}.
-\comment{TODO: add traveling wave citations}
+and has been described in similar models, e.g.,
+by \citet{britton1990spatial,sasaki1997clumped,hernandezgarcia2004clustering,young2001reproductive,berestycki2009nonlocal}.
 Heuristically, this can occur if density-dependent effects of individuals
@@
 Since $F'_0 < 0$, the last two terms are negative,
-but on the other hand we expect $\gamma_0' < 0$
+but on the other hand if we take $\gamma_0' < 0$
 (i.e., per capita birth rate decreases with density near equilibrium),
-and so the stability of the constant solution $\varphi \equiv \varphi_0$
+then the stability of the constant solution $\varphi \equiv \varphi_0$
 depends on the balance between the first and latter two terms.
@@
 We need some notation. 
-Write ${\mathcal C}={\mathcal C}(\IR^d\times [0,\infty)$ for the point measures 
+Write ${\mathcal C}={\mathcal C}(\IR^d\times [0,\infty)$ for the counting measures 
 on $\IR^d\times [0,\infty)$ and ${\mathcal C}_N$ for the subset consisting of 
@@
 Next we state the limiting martingale problem,
-for which we do not have uniqueness.
-\comment{Do we not have uniqueness, or not know if there is uniqueness?}
+for which we do not necessarily have uniqueness.
 As before, the parameter $\alpha$ will correspond to 
@@
 uniformly distributed on $[0,N]$, in the infinite population limit, 
-conditional on $\eta_t$ the process $\xi_t$ is 
-Poisson distributed on 
+conditional on $\eta_t$, the process $\xi_t$ is Poisson distributed on 
 $\IR^d\times [0,\infty)$ with mean measure $\eta_t\times\lambda$, where 
@@
     \end{split} \end{align}
-We say that a ${\cal C}(\IR^d\times [0,\infty))$-valued process $(\xi_t)_{t \ge 0}$
+    We say that a ${\cal D}([0,\infty), \mathcal{C})$-valued process $(\xi_t)_{t \ge 0}$
     is a solution to the $(A, \lp_0)$ martingale problem
@@
     &=
-    e^{-\langle F_f^N, \kappa(\lp) \rangle} ,
+    e^{-\langle H_f^N, \kappa^N(\lp) \rangle} ,
 \end{align}
 where
-$$ F_f^N(x) = - N \log \frac{1}{N} \int_0^N e^{-f(x, u)} du . $$
+$$ H_f^N(x) = - N \log \frac{1}{N} \int_0^N e^{-f(x, u)} du . $$
 In other words, the $[0, N]$ components of $\lp$
@@
     of the $(A^N, \lp^N_0)$-martingale problem of Definition~\ref{defn:lookdown_mgale}
-    such that $\eta^N = \kappa \circ \lp^N$
+    such that $\eta^N = \kappa^N \circ \lp^N$
     has the same distribution on $D_{\measures}[0, \infty)$
@@
     in the sense of \eqref{eqn:conditionally_uniform}.
-    Then, the sequence of stochastic processes $(\lp_t^N)_{t \ge 0}$
-    converges along subsequences in distribution as $N \to \infty$
+    Then, any sequence of stochastic processes $(\lp_t^N)_{t \ge 0}$
+    has a subsequence which converges in distribution as $N \to \infty$
     to a measure-valued process $(\lp_t)_{t \ge 0}$
@@
     The fact that a solution to the system of equations
+    \comment{label the system and refer to it}
     is a solution to the martingale problem of Theorem~\ref{thm:lookdown_convergence}
     is an application of It\^o's theorem.
-    Theorem~\ref{thm:mmt_application} shows that
+    Furthermore, in Proposition~\ref{thm:mmt_application} we showed that
     the conditional Poisson property of $\lp_0$ is preserved
@@
 are bounded uniformly in $x$ under Assumptions~\ref{def:model_setup}.
+\comment{typo}
 u implies that $|B_1|$ is uniformly bounded;
@@
 tightness of the population processes in $\mathcal{D}_{\cmeasures}([0,\infty))$
-follows from tightness of the real-valued processes $(G(\eta_t))_{t\geq 0}$ for a sufficiently large
-class of test functions $G$, which we establish through an application of the
+follows from tightness of the real-valued processes $(H(\eta_t))_{t\geq 0}$ for a sufficiently large
+class of test functions $H$, which we establish through an application of the
 Aldous-Rebolledo criterion in Lemma~\ref{lem:eta_projections_tightness}.
@@
             ( f(y) - f(x) )
+            r(y, \smooth{r}\eta(y))
         q_{\theta}(x,dy)
@@
 \end{align}
-The first term is bounded uniformly
+\comment{TODO FIX THIS}
+Using the intermediate value theorem,
+then the fact that $0 \le r \le 1$,
+there is a $\kappa$ in $[0, 1]$ such that the first term is
+\begin{align*}
+    &
+    \left| \theta 
+        \int_{\IR^n} 
+            ( f(y) - f(x) )
+            r(y, \eta)
+        q_{\theta}(x,dy)
+    \right|
+    \\ &\qquad =
+    \left| \theta 
+        \int_{\IR^n} 
+            \left(
+                \sum_i (y-x)_i \partial_{x_i} f(x)
+                +
+                \frac{1}{2} \sum_{ij} (y-x)_i (y-x)_j \partial_{x_i x_j} f(x + \kappa(y-x))
+            \right)
+            r(y, \eta)
+        q_{\theta}(x,dy)
+    \right|
+    \\ &\qquad \leq
+    \|f'\|_\infty \left| \theta 
+        \int_{\IR^n} 
+            (y-x) r(y, \eta)
+        q_{\theta}(x,dy)
+    \right|
+    + \frac{1}{2} \|f''\|_\infty \left| \theta 
+        \int_{\IR^n} 
+            (y-x)^2
+        q_{\theta}(x,dy)
+    \right|
+\end{align*}
+bounded uniformly
 because $q_\theta(x, dy)$ is the density of a Gaussian with mean $\meanq(x)/\theta$
@@
 First, we record an equivalent formulation
-of the martingale problem for the limiting process,
-that follows by application of It\^o's lemma.
+of the martingale problems.
+% that follows by application of Dynkin's formula.
 
@@
     \label{def: MP definition of limit}
+\comment{TODO: define $\mathcal{P}^N$ also here.}
 For $G \in \mathcal{C}^{\infty}(\IR)$ with $\|G'''\|_\infty<\infty$,
@@
 
-\comment{TODO: define $\mathcal{P}^N$.}
-
 \begin{lemma}[Characterisation of limit points]
@@
 \end{equation}
-for all $k\geq 0$, $0\leq t_1<t_2<...,t_k \leq t < t+\tau$,
-and $h_1,...,h_k \in \mathcal{C}_{b}(\cmeasures)$.
+for all $k\geq 0$, $0\leq t_1<t_2<\ldots,t_k \leq t < t+\tau$,
+and 
+bounded continuous functions 
+$h_1,\ldots,h_k$ on $\cmeasures$.
 
@@
 \end{equation}
-and again using the tower property, since the functions $h_i$ are
+and, again using the tower property, since the functions $h_i$ are
 bounded, this will follow if
@@
 The proof rests on a Feynman-Kac representation.
-We write $(Z_t)_{t\geq 0}$ for a diffusion with generator $\DG^*$ and denotes 
+We write $(Z_t)_{t\geq 0}$ for a diffusion with generator $\DG^*$ and denote 
 its transition density by $f_t(x,y)$. The first step is a regularity
@@
     \\
-	= \int (\lambda^2-1)\exp(\lambda x) \psi_t^\epsilon(x) \smooth{\epsilon}* \psi_t^\epsilon(x) dx 
+	= \int (\lambda^2-1)\exp(\lambda x) \psi_t^\epsilon(x) \smooth{\epsilon} \psi_t^\epsilon(x) dx 
 	+ \int \exp(\lambda x)\psi_t^\epsilon(x) dx
@@
 uniform integrability of $\psi^\epsilon$ that we
-deduce from the uniform control of
+can deduce from the uniform control of
 $\int \psi^\epsilon|\log \psi^\epsilon| d x$ that we proved above.
@@
 % % % % % % % % % % % % %
-\subsection{Simultaneous scaling with interaction distance}
+\section{Simultaneous scaling with interaction distance}
 \label{subsec:one step convergence proof}
@@
 
-\subsubsection{Continuity estimates for a Gaussian random walk}
+\subsection{Continuity estimates for a Gaussian random walk}
 \label{continuity for random walk}
@@
     and let $T(t) = \Pi(\theta t) / \theta$.
-    \comment{Suppose also that $\theta \epsilon^2$ is bounded below.
-    (We could alternatively put a $1/\theta\epsilon^2$ term in the lemma.)}
     Then
@@
     \]
-    and, moreover, there is a $C$ independent of $\epsilon$ or $t$ such that
+    and, moreover,
+    since under our assumptions $\theta \epsilon^2$ is bounded below,
+    there is a $C$ independent of $\epsilon$ or $t$ such that
     \[
@@
 
-\subsubsection{Moment bounds for $\rho_\epsilon*\eta$}
+\subsection{Moment bounds for $\rho_\epsilon*\eta$}
 \label{bounds on rhoepsilon}
@@
 \eta_u^N(dx)\big\rangle du \geq \frac{\nu}{3}\Big]
-\leq C\frac{\delta}{T\nu^2}.
+\leq C\frac{T\delta}{\nu^2}.
 \end{equation}
@@
 and so choosing $\delta$ so that $K\delta<\nu/3$ in this 
-expression and $C\delta<T\nu^3/3$ in~(\ref{union bound}),
+expression and $C\delta<\nu^3/3T$ in~(\ref{union bound}),
 combining with~(\ref{martingale term to zero}), the result follows.
@@
 
-\subsubsection{Identification of the limit}
+\subsection{Identification of the limit}
 \label{limit in onestep case}
@@
 Thus, from weak convergence we can deduce that under our scaling,
-for any convergent subsequence $\{\rho_\epsilon*\eta^N(x)dx\}_{N\geq 1}$,
+for any (weakly) convergent subsequence $\{\rho_\epsilon*\eta^N(x)dx\}_{N\geq 1}$,
 \[ 
@@
     applied to our situation.
+    \comment{TODO: copy the MMT into our appendix and refer to it}
     In the notation of that theorem, $\gamma$ is what we have called $\kappa$ above,
@@
     taking $f(\lp)$ of the form \eqref{eqn:test_functions},
-    we can use $\psi^N(\lp) = \langle C (1+ + u |F(x, \eta)|), \lp(dx, du) \rangle$
+    we can use $\psi^N(\lp) = \langle C (1 + u |F(x, \eta)|), \lp(dx, du) \rangle$
     for an appropriate constant $C$.
@@
     except that $\psi(\lp)$ cannot depend on $f$, and hence neither on $u_0$.
-    So, the second line provides us with the required bound,
-    absorbing $\| \partial_u g \|_\infty e^{u_0}$ into $c_f$
-    and $\langle |F(x, \eta) u e^{-u}|, \lp \rangle$ into $\psi(\lp)$.
+    So, the second line provides us with the required bound:
+    we absorb $\| \partial_u g \|_\infty e^{u_0}$ into $c_f$
+    and take $\psi(\lp) = \langle F(x, \eta) u e^{-u}, \lp(dx, du) \rangle$.
     % Furthermore, since $F(x, \eta)$ only depends on spatial location, not level,
@@
 Theorem~\ref{thm:lookdown_convergence}, whose proof
-follows a similar pattern as the the proofs of convergence for the population process
+follows a similar pattern to those of convergence for the population processes
 in Section~\ref{sec:population_density_proof}.
 
+\begin{remark}
 The process we consider is similar to the state-dependent branching processes
@@
 and so all individuals can affect all other ones (even those with lower levels).
-Furthermore, in the deterministic case $\theta/N$ and hence $c$ converge to zero,
+Furthermore, in the deterministic case $\theta/N$, and hence $c$, converges to zero,
 and so lines of descent with arbitrarily high level may drift back downwards.
@@
 since in the deterministic case there is no branching.
+\end{remark}
 
@@
     $\sup_{\lp \in K} \langle f_k, \lp \rangle < \infty$ for each $k$;
-    therefore, compact containment will follow from Lemma~\ref{lem:compact containment lookdown}.
+    below, Lemma~\ref{lem:compact containment lookdown} proves exatly this, and therefore compact containment.
 
@@
 
-    We show that the martingale properties are preserved in the limit
-    in Section~\ref{sec:lookdown_generator_proofs}.
+    The analogue of Lemma~\ref{lem:limit_mgale},
+    in particular that the martingale properties are preserved under passage to the limit,
+    are proved in Section~\ref{sec:lookdown_generator_proofs}.
     \comment{TODO: refer to correct thing}
@@
     Let $N_k \to \infty$ be a sequence along which $\lp^{N_k}$ converges.
-    However, by Theorem~\ref{thm:nonlocal_convergence},
+    By Theorem~\ref{thm:nonlocal_convergence},
     there is a subsequence $N_{k(j)}$ along which the projected population processes
     $\eta^{N_{k(j)}}$ converge, and the limit solves the martingale problem.
-    This implies that any limit of $\lp^N$ projects to a population process $\eta$
+    Thus any limit point of $\lp^N$ projects to a population process $\eta$
     solving the martingale problem of Theorem~\ref{thm:nonlocal_convergence}.
@@
         \label{lem:h_containment}
-    Let $h$ be a positive, continuous, nondecreasing, differentiable function on $[0, \infty)$
+    Let $h$ be a positive, continuous, nonincreasing, differentiable function on $[0, \infty)$
     such that
@@
     Then under the assumptions of Lemma~\ref{lem:compact containment lookdown},
+    \comment{MOVE ASSUMPTIONS HERE}
     for any $T$ there exists a constant $K(T)$ such that for all $M > 0$,
@@
 
-\begin{proof}[of Lemma~\ref{lem:compact containment hn}]
+\begin{proof}[of Lemma~\ref{lem:h_containment}]
     Applied to $f(x, u) = h(u)$, the martinagle representation~\eqref{eqn:f_xi_mgale} is
@@
         \Big\rangle ds
-        &\le
+        \\ &\le
         \langle f, \lp_0 \rangle
@@
 \subsection{Motion of ancestral lineages}
+\label{sec:lineages_proof}
 
@@
 $$
-Since this is symmetric, the process $Y$ is reversible with respect to $\pi$;
+Since this is symmetric in $f$ and $g$, the process $Y$ is reversible with respect to $\pi$;
 the constant factor of $\sigma^2$ does not affect the result.
@@
 \bibliographystyle{plainnat}
-\bibliography{refs.bib,plr_refs.bib}
+\bibliography{refs,plr_refs,MendeleyIan}
 

### 2023-03-22 forwards-and-backwards.tex
D notation

@@
 	\comment{Need to thank KAVLI, Paris Cit\'e, various funders}
-    \comment{make notation for $\mathcal{D}$ consistent}
 
@@
 Given $\lp_0 \in {\mathcal C}_N$, 
-we say that a ${\mathcal D}([0,\infty), {\mathcal C}_N)$-valued process 
+we say that a ${\mathcal D}_{[0,\infty)}({\mathcal C}_N)$-valued process 
 $(\xi_t)_{t \ge 0}$
@@
 %Theorem~3.9.1 of~\cite{ethier/kurtz:1986} tells us that 
-tightness of the population processes in $\mathcal{D}_{\cmeasures}([0,\infty))$
+tightness of the population processes in $\mathcal{D}_{[0,\infty)}(\cmeasures)$
 follows from tightness of the real-valued processes $(H(\eta_t))_{t\geq 0}$ for a sufficiently large
@@
 to deduce tightness of the scaled population processes in 
-the larger space $\mathcal{D}_{\cmeasures}([0,\infty))$.
+the larger space $\mathcal{D}_{[0,\infty)}(\cmeasures)$.
 
@@
 in the process of passing to the limit, no mass `escaped to infinity', so that
-in fact the limit points take values in $\mathcal{D}_{\measures}([0,\infty))$.
+in fact the limit points take values in $\mathcal{D}_{[0,\infty)}(\measures)$.
 \end{proof}
@@
 \end{align}
-where $M^N_t(f)$ is a martingale.
+where $M^N_t(f)$ is a martingale
+and $B_f$ is defined in \comment{TODO REFER}.
 % and we are defining
@@
     and we need a continuous $\psi^N(\lp)$ such that $|A^N f(\lp)| \le c_f \psi^N(\lp)$
-    for all $f \in \mathcal{D}(A^N)$ (and similarly a function $\psi$ for $A$).
+    for all $f$ in the domain of $A^N$ (and similarly a function $\psi$ for $A$).
     We also need that applying the lookdown generator to a function and averaging over levels
@@
 and $(\Xi^N_t(dx))_{t \geq 0}$
-shares the same distribution on $\mathcal{D}_{\mathcal{M}(\mathbb{R}^d)}[0,\infty)$.
+shares the same distribution on $\mathcal{D}_{[0,\infty)}(\mathcal{M}(\mathbb{R}^d))$.
 
@@
 and $(\Xi_t(dx))_{t \geq 0}$
-shares the same distribution on $\mathcal{D}_{\mathcal{M}(\mathbb{R}^d)}[0,\infty)$.
+shares the same distribution on $\mathcal{D}_{[0,\infty)}(\mathcal{M}(\mathbb{R}^d))$.
 
@@
     \item The process $(\gamma_M \circ \xi^N_t)_{t \geq 0}= \left(\Xi^N_t\right)_{t \geq 0}$ 
-    has the same distribution in $\mathcal{D}_{\mathcal{M}(\mathbb{R}^d)}[0,\infty)$ as $(\eta^N_t)_{t \geq 0}$ defined in Definition \ref{def: MP definition of pre-limit}.
+    has the same distribution in $\mathcal{D}_{[0,\infty)}(\mathcal{M}(\mathbb{R}^d))$ as $(\eta^N_t)_{t \geq 0}$ defined in Definition \ref{def: MP definition of pre-limit}.
     \item $\mathbb{P}\{\xi^N_t \in B | \mathcal{F}^{\Xi^N}_t\}=\alpha_M(\Xi^N(t),B), ~~~B \in \mathcal{B}(\mathcal{M}(\IR^d \times [0,N])).$

### 2023-03-22 forwards-and-backwards.tex
reinserted old lemma 6.1

@@
 density with parameter $\sigma_r$, say. Then, 
-as we check in Lemma~\ref{old 6.1}, \comment{this is referring to the
-old Lemma 6.1, now to go in Appendix,}
+as we check in Lemma~\ref{lem:gamma_bound},
 Condition~\ref{control through gamma} is satisfied if $\rho_\gamma$ is also
@@
 
+\subsection{Constraints on kernel widths}
+
+\begin{lemma}
+    \label{lem:gamma_bound}
+\comment{TODO; REWRITE TO SAY THAT STHG IMPLIES CONDITION 2 OF LEMMA \ref{lem:conditions on r} (see reference on p.13)}
+    Under the assumptions of Definition~\ref{def:model_setup},
+    for all $f \in \mathcal{C}^{2}_{0}(\IR^d \times [0,\infty))$,
+    there exists a $K_f < \infty$ such that
+    for all $\theta > 0$ and all $\eta \in \measures$,
+    \begin{equation} \label{eqn:gamma_bound}
+    \gamma\big(x,\smooth{\gamma} \eta(x)\big)
+    \left| \theta 
+        \int_{\IR^n} 
+            \left\{
+                f(y, \smooth{r} \eta(y)) - f(x, \smooth{r} \eta(x))
+            \right\}
+        q_{\theta}(x,dy)
+    \right|
+    \leq C_f     .
+    \end{equation}
+\end{lemma}
+
+The key assumption here from Definition~\ref{def:model_setup}
+will be that the spatial scale over which local density affects birth rate
+is larger than the scale over which it affects establishment:
+concretely, that $\epsilon_{r}^2 + \frac{2\lambda}{\theta} < \epsilon_{\gamma}^2$,
+where $\lambda = \sup_x \sup_{y : \|y\| = 1} y^T \covq(x) y$
+is the largest eigenvalue of $\covq(x)$ across all $x$.
+In the simple case of $\meanq = 0$ and $\covq = \sigma^2 I$,
+the condition is simply that $\epsilon_r^2 + 2\sigma^2 / \theta < \epsilon_\gamma^2$.
+
+\begin{proof}[of Lemma \ref{lem:gamma_bound}]
+
+    Since we have assumed that there is a $K$ for which $m^2 \gamma(x, m) < K$
+    for all $x \in \IR^d$ and $m \ge 0$,
+    equation~\eqref{eqn:gamma_bound} will follow if we can show that
+    \begin{equation*}
+        \left| \theta 
+            \int_{\IR^n} 
+                \left\{
+                    f\left(y, \smooth{r}\eta(y)\right)
+                    -
+                    f\left(x, \smooth{r}\eta(x)\right)
+                \right\}
+            q_{\theta}(x,dy)
+        \right|
+        \leq
+        C_f \left( 1 + \smooth{\gamma} \eta(x)^2 \right) .
+    \end{equation*}
+    To do this, first note that 
+    \begin{align} \label{eqn:q_bound_split}
+    &
+        \left| \theta 
+            \int_{\IR^n} 
+                \left\{
+                    f\left(y, \smooth{r}\eta(y)\right)
+                    -
+                    f\left(x, \smooth{r}\eta(x)\right)
+                \right\}
+            q_{\theta}(x,dy)
+        \right|
+    \\ &\qquad {} \leq
+        \left| \theta 
+            \int_{\IR^n} 
+                \left\{
+                    f\left(y, \smooth{r}\eta(y)\right)
+                    -
+                    f\left(x, \smooth{r}\eta(y)\right)
+                \right\}
+            q_{\theta}(x,dy)
+        \right|
+    \\ &\qquad \qquad {}  +
+        \left| \theta 
+            \int_{\IR^n} 
+                \left\{
+                    f\left(x, \smooth{r}\eta(y)\right)
+                    -
+                    f\left(x, \smooth{r}\eta(x)\right)
+                \right\}
+            q_{\theta}(x,dy) 
+        \right| .
+    \end{align}
+
+    Since 
+    \begin{align*}
+        f\left(y, \smooth{r}\eta(y)\right) - f\left(x, \smooth{r}\eta(y)\right)
+        &=
+        \sum_i (y_i - x_i) \partial_{x_i} f \left(x, \smooth{r}\eta(y)\right) 
+        \\ &\qquad {}
+        +
+        \frac{1}{2} \sum_{ij} (y_i - x_i)(y_j - x_j)
+            \partial_{x_i x_j} f \left(z, \smooth{r}\eta(y)\right) 
+    \end{align*}
+    where $z = t x + (1-t) y$ for some $0 \le t \le 1$,
+    writing
+    $K_1 = \sup_{x,m} \max_i |\partial_{x_i} f(x, m)|$
+    and 
+    $K_2 = \sup_{x,m} \max_{i,j} |\partial_{x_i x_j} f(x, m)|$
+    for the bounds on the spatial derivatives of $f$,
+    the first term is bounded by
+    \begin{align*}
+        K_1 \left|
+            \theta \int_{\IR^d} \sum_i (y_i - x_i) q_\theta(x, dy)
+        \right|
+        +
+        K_2 \left|
+            \theta \int_{\IR^d} \sum_{ij} (y_i - x_i) (y_j - x_j)  q_\theta(x, dy)
+        \right| .
+    \end{align*}
+    This is bounded uniformly because
+    $q_\theta(x, dy)$ is the density of a Gaussian with mean $\meanq(x)/\theta$
+    and covariance $\covq(x)/\theta$, and both $\meanq(x)$ and $\covq(x)$
+    are bounded uniformly in $x$.
+
+    Similarly, 
+    \begin{align*}
+        f(x, \smooth{r}\eta(y)) - f(x, \smooth{r}\eta(x))
+        &=
+        (\smooth{r}\eta(y) - \smooth{r}\eta(x)) f'(x, \smooth{r}\eta(x))
+        + \frac{1}{2} (\smooth{r}\eta(y) - \smooth{r}\eta(x))^2 f''(x, m)
+    \end{align*}
+    for some $\smooth{r}\eta(x) \le m \le \smooth{r}\eta(y)$,
+    where $f'$ and $f''$ denote the first and second derivatives with respect to the second argument.
+    So,
+    the second term in~\eqref{eqn:q_bound_split} is bounded by
+    \begin{align*}
+        % note that the f' term does not depend on x, just y,
+        % so can come out of the integral
+        \|f'\|_\infty
+        \left|
+            \theta \int_{\IR^d}
+                (\smooth{r}\eta(y) - \smooth{r}\eta(x))
+            q_\theta(x, dy)
+        \right|
+        +
+        \|f''\|_\infty
+        \left|
+            \theta \int_{\IR^d}
+                (\smooth{r}\eta(y) - \smooth{r}\eta(x))^2
+            q_\theta(x, dy)
+        \right| .
+    \end{align*}
+    Therefore, it suffices to show that there is a $K < \infty$ such that
+    for all $\eta \in \measures$ and $x \in \IR^d$,
+    \begin{equation}
+        \label{eqn:first_moment_rho}
+        \left|\theta \int_{\IR^d}
+            ( \smooth{r} \eta(y)-\smooth{r} \eta(x) )
+        q_\theta(x,dy)\right|
+        \leq K \smooth{\gamma} \eta(x)
+    \end{equation}
+    and
+    \begin{equation}
+        \label{eqn:second_moment_rho}
+        \theta \int_{\IR^d}
+                \left( \smooth{r} \eta(y) - \smooth{r} \eta(x) \right)^2
+        q_\theta(x,dy)
+        \leq K \left(\smooth{\gamma}\eta(x) \right)^2 .
+    \end{equation}
+    Note that the right hand side of each is the average density
+    over a wider region (since $\epsilon_\gamma > \epsilon_r$).
+
+    First we prove \eqref{eqn:first_moment_rho}.
+    Recall that $\smooth{r} \eta(x) = \int p_{\epsilon^2_r}(x - w) \eta(dw)$,
+    where $p_t$ is the density of a Gaussian with mean 0 and variance $t$,
+    so that applying Fubini, \eqref{eqn:first_moment_rho} is
+    \begin{align*}
+        \left|
+        \int_{\IR^d}
+        \theta
+            \int_{\IR^d}
+                ( p_{\epsilon_r^2}(y - w) - p_{\epsilon_r^2}(x - w) )
+            q_\theta(x, dy)
+        \eta(dw)
+        \right| .
+    \end{align*}
+    Write $p_{s, x}(\cdot)$ for the density of a Gaussian
+    with mean $s \meanq(x)$ and covariance $\epsilon_r^2 I + s \covq(x)$,
+    so that $\int p_{\epsilon_r^2}(y - w) q_\theta(x, dy) = p_{1/\theta, x}(w-x)$.
+    It therefore suffices to show that for all $x$ and $w \in \IR^d$,
+    there exists $K$ such that
+    \begin{align} \label{eqn:goal1}
+        \left|
+        \theta
+            \int_{\IR^d}
+                ( p_{\epsilon_r^2}(y-w) - p_{\epsilon_r^2}(x-w) )
+            q_\theta(x, dy)
+        \right|
+        &=
+        \theta \left|
+            p_{1/\theta, x}(w-x) - p_{0, x}(w-x)
+        \right|
+        \le
+        K p_{\epsilon^2_\gamma}(w-x) .
+    \end{align}
+    However,
+    $\theta( p_{1/\theta, x}(z) - p_{0, x}(z) )
+    = \partial_s p_{s, x}(z)$ for some $0 \le s \le 1/\theta$.
+    Write $\Gamma(s,x) = \epsilon_r^2 I + s \covq(x)$,
+    so that
+    \begin{align*}
+        p_{s, x}(z)
+        &=
+        \frac{1}{\left(2 \pi |\Gamma(s,x)|\right)^{d/2}}
+        \exp\left(
+            -\frac{1}{2} (z - s\meanq(x))^T \Gamma(s,x)^{-1} (z - s\meanq(x))
+        \right) ,
+    \end{align*}
+    and note that if $\lambda_i$ are the eigenvalues of $\covq(x)$
+    then $|\Gamma(s, x)| = \prod_i (\epsilon_r^2 + s \lambda_i)$,
+    and
+    $\partial_s |\Gamma(s, x)| = \sum_i \lambda_i |\Gamma(s, x)| / (\epsilon_r^2 + s \lambda_i)$.
+    Therefore,
+    \begin{align*}
+        \partial_s p_{s, x}(z)
+        &=
+        \left(
+            \meanq(x)^T \Gamma(s,x)^{-1} (z - s \meanq)
+            +
+            (z - s \meanq(x))^T
+            \Gamma(s,x)^{-1} \covq(x) \Gamma(s,x)^{-1}
+            (z - s \meanq(x))
+        \right. \\ & \qquad \qquad \qquad \left. {}
+            -
+            \sum_i \frac{\lambda_i}{\epsilon_r^2 + s \lambda_i}
+        \right)
+        p_{s, x}(z) ,
+    \end{align*}
+    where $z^T$ is the transpose of $z$.
+    This implies that
+    \begin{align*}
+        \frac{
+        \theta
+            \int_{\IR^d}
+                ( p_{\epsilon_r^2}(y-w) - p_{\epsilon_r^2}(x-w) )
+            q_\theta(x, dy)
+        }{
+            p_{\epsilon^2_\gamma}(x-w) .
+        }
+        =
+        h(x-w) e^{k(x-w)},
+    \end{align*}
+    where $h(z)$ and $k(z)$ are quadratic polynomials in $z$
+    whose coefficients depend on $s$ and $x$ but are uniformly bounded for $s \ge 1$
+    and $x \in \IR^d$.
+    Therefore, \eqref{eqn:goal1} holds for some finite $K$
+    if and only if $k(z) < 0$ for all $z$ outside some bounded region.
+    This is
+    \begin{align*}
+        k(z)
+        =
+        \frac{1}{2\epsilon_\gamma^2} \|z\|^2
+        -\frac{1}{2} (z - s\meanq(x))^T \Gamma(s,x)^{-1} (z - s\meanq(x)) ,
+    \end{align*}
+    which is negative for all $z$ outside a bounded region.
+    Since $\inf_z z^T \Gamma(s,x)^{-1} z / \|z\|^2 = 1 / (s \lambda(x) + \epsilon_r^2)$,
+    where $\lambda(x) = \sup z^T \covq(x) z / \|z\|^2$ is the largest eigenvalue of $\covq(x)$,
+    equation~\eqref{eqn:first_moment_rho} follows from the assumption
+    that $\epsilon_r^2 + 2 \sup_x \lambda(x)/\theta < \epsilon_\gamma^2$.
+    (Note that we do not yet need the factor of 2.)
+
+    Next we prove equation~\eqref{eqn:second_moment_rho}, in a similar way.
+    Again applying Fubini,
+    \begin{align*}
+        &
+        \theta \int_{\IR^d}
+                \left( \smooth{r} \eta(y) - \smooth{r} \eta(x) \right)^2
+        q_\theta(x,dy)
+        \\ &\qquad
+        =
+        \int_{\IR^d} \int_{\IR^d}
+        \theta \int_{\IR^d}
+            ( p_{\epsilon_r^2}(y - w) - p_{\epsilon_r^2}(x - w) )
+            ( p_{\epsilon_r^2}(y - v) - p_{\epsilon_r^2}(x - v) )
+        q_\theta(x, dy)
+        \eta(dv) \eta(dw) ,
+    \end{align*}
+    and so as before, equation~\eqref{eqn:second_moment_rho} will follow if
+    the integrand is bounded by $K p_\gamma(x-w) p_\gamma(x - v)$.
+    % \begin{align*}
+    %     \theta \int_{\IR^d}
+    %         ( p_{\epsilon_r^2}(y - w) - p_{\epsilon_r^2}(x - w) )
+    %         ( p_{\epsilon_r^2}(y - v) - p_{\epsilon_r^2}(x - v) )
+    %     q_\theta(x, dy)
+    %     \le K p_\gamma(x-w) p_\gamma(x - v) .
+    % \end{align*}
+    Now, let $Y_1$, $Y_2$, and $Z$ be independent $d$-dimensional Gaussians with mean zero,
+    where $Y_1$ and $Y_2$ have covariance $\epsilon^2_r I$,
+    and $Z$ has covariance $\covq(x)$.
+    Write $p_{s,t,x}(\cdot, \cdot)$ for the joint density of
+    $Y_1 + \sqrt{s} Z + s \meanq(x)$ and $Y_2 + \sqrt{t} Z + t \meanq(x)$.
+    Then, observe that
+    \begin{align*}
+        &
+        \theta \int_{\IR^d}
+            ( p_{\epsilon_r^2}(y - w) - p_{\epsilon_r^2}(x - w) )
+            ( p_{\epsilon_r^2}(y - v) - p_{\epsilon_r^2}(x - v) )
+        q_\theta(x, dy)
+        \\ &\qquad
+        =
+        \theta \left(
+            p_{1/\theta, 1/\theta, x}(x-w, x-v)
+            - p_{0, 1/\theta, x}(x-w, x-v)
+        \right. \\ &\qquad \qquad \left. {}
+            - p_{1/\theta, 0, x}(x-w, x-v)
+            + p_{0, 0, x}(x-w, x-v)
+        \right) 
+        \\ &\qquad 
+        =
+            \partial_s p_{s, 1/\theta, x}(x-w, x-v)
+            - \partial_t p_{0, t, x}(x-w, x-v) ,
+    \end{align*}
+    for some $0 \le s, t \le 1/\theta$.
+    As before,
+    \begin{align*}
+        \frac{
+            \theta \int_{\IR^d}
+                ( p_{\epsilon_r^2}(y - w) - p_{\epsilon_r^2}(x - w) )
+                ( p_{\epsilon_r^2}(y - v) - p_{\epsilon_r^2}(x - v) )
+            q_\theta(x, dy)
+        }{
+            p_{\epsilon_\gamma^2}(x - w)
+            p_{\epsilon_\gamma^2}(x - v)
+        }
+        =
+        h(x-w, x-v) e^{ k(x-w, x-v) },
+    \end{align*}
+    where $h(z_1, z_2)$ is a polynomial with uniformly bounded coefficients and
+    \begin{align*}
+        k(z_1, z_2)
+        =
+        (\|z_1\|^2 + \|z_2\|^2)/(2 \epsilon_\gamma^2)
+            - \frac{1}{2} [z_1, z_2[^T \Gamma(s, t, x)^{-1} [z_1, z_2] ,
+    \end{align*}
+    where $[z_1, z_2]$ is the $\IR^{2d}$ vector formed by concatenating $z_1$ and $z_2$,
+    and $\Gamma(s, t, x)$ is the block matrix
+    \begin{align*}
+        \Gamma(s, t, x)
+        =
+        \left[
+        \begin{array}{cc}
+            \epsilon_r^2 I + s \covq(x) & \sqrt{st} \covq(x) \\
+            \sqrt{st} \covq(x) & \epsilon_r^2 I + t \covq(x) \\
+        \end{array}
+        \right] .
+    \end{align*}
+    If $\covq(x) u = a u$ for some $a \in \IR$,
+    then $[u \sqrt{s}, u \sqrt{t}]$ is an eigenvector of $\Gamma(s, t, x)$
+    with eigenvalue $\epsilon^2_r + (s+t) a$,
+    and $[u \sqrt{t}, - u \sqrt{s}]$ is an eigenvector of $\Gamma(s, t, x)$
+    with eigenvalue 0.
+    This implies the largest eigenvalue of $\Gamma(s, t, x)$
+    is equal to $\epsilon^2_r + (s+t) \lambda(x)$,
+    where $\lambda(x)$ is again the largest eigenvalue of $\covq(x)$.
+    Therefore, if $s + t \le 2 / \theta$,
+    \begin{align*}
+        &
+        (\|z_1\|^2 + \|z_2\|^2) / \epsilon^2_\gamma
+            - [z_1, z_2[^T \Gamma(s, t, x)^{-1} [z_1, z_2]
+        \\ &\qquad \le
+        (\|z_1\|^2 + \|z_2\|^2) \left(
+            \frac{1}{\epsilon^2_\gamma}
+            - \frac{1}{\epsilon^2_r +  2\lambda(x)/\theta}
+        \right) ,
+    \end{align*}
+    which is negative by assumption.
+    Therefore, there is a $K$ such that
+    \begin{align*}
+        \frac{ \left|
+            \partial_s p_{s, 1/\theta, x}(x-w, x-v)
+            - \partial_t p_{0, t, x}(x-w, x-v)
+        \right| }{
+            p_{\epsilon^2_\gamma}(x - w)
+            p_{\epsilon^2_\gamma}(x - v)
+        }
+        \le K
+    \end{align*}
+    for all $\theta > 1$ and all $x$, $v$, and $w \in \IR^d$,
+    proving equation~\eqref{eqn:second_moment_rho} and hence the lemma.
+\end{proof}
+
 \subsection{Tightness of processes}

### 2023-03-22 forwards-and-backwards.tex
minor edits

@@
 write $\langle f, \eta \rangle = \int_{\IR^d} f(x) \eta(dx)$.
+
 \begin{definition}[Martingale Problem Characterisation]
@@
 
-In this section we present formal proofs of our 
-three
-scaling limits. In
-Subsection~\ref{sec:population_density_proof} 
+In the following sections we present formal proofs of our three scaling limits.
+In Subsection~\ref{sec:population_density_proof} 
 we prove Theorem~\ref{thm:nonlocal_convergence}, to obtain a limit in
@@
 one can pass to a further 
-limit to obtain a classical PDE. In 
-Subsection~\ref{subsec:one step convergence proof}
+limit to obtain a classical PDE.
+In Section~\ref{subsec:one step convergence proof}
 we prove our third scaling limit, in which 
 we pass from our population model 
-directly to a reaction diffusion equation without going via a nonlocal
-limit.
-
-\comment{TODO add sentences about the sections Peter is editing}
+directly to a reaction diffusion equation without going via a nonlocal limit.
+Finally, in Section~\ref{sec:lookdown_proofs} we prove our results concerning both convergence of the lookdown representation
+and characterization of the lineage process in the deterministic case.
 
@@
 \end{align}
-where $M^N_t(f)$ is a martingale
-and $B_f$ is defined in \comment{TODO REFER}.
-% and we are defining
-% \begin{equation}
-% \label{generator Bf}
-%     B_f(x, \eta) = \int_{\IR^d} \theta (f(y) r(y, \eta) - f(x) r(x, \eta)) q_\theta(x, dy) .
-% \end{equation}
+where $M^N_t(f)$ is a martingale and $B_f$ is defined in \ref{generator Bf}.
 
@@
 First, we record an equivalent formulation
-of the martingale problems.
+of the martingale problems,
+which were essentially laid out in Subsection~\ref{sec:population_heuristics}.
 % that follows by application of Dynkin's formula.
@@
     \label{def: MP definition of limit}
-\comment{TODO: define $\mathcal{P}^N$ also here.}
 For $G \in \mathcal{C}^{\infty}(\IR)$ with $\|G'''\|_\infty<\infty$,
@@
 $G_f(\eta):=G (\langle f, \eta \rangle)$.
-Let $\Pgen^\infty$ be the generator
-given by
+Let $\Pgen^N$ be the generator given by
+\begin{equation}
+\begin{aligned}
+    \Pgen^N G_f(\eta)
+    &:=
+    G'(\langle f, \eta \rangle)
+        \theta \bigg\langle
+        \gamma(x, \eta)
+            \int f(z) r(z,\eta) q_\theta(x,dz)
+        -
+        f(x)\mu_\theta(x, \eta),
+        \eta(dx) \bigg\rangle
+    \\&\qquad {}
+    + \frac{1}{2} G''(\langle f, \eta \rangle)
+    \frac{\theta}{N}
+    \bigg\langle
+        \gamma(x, \eta) \int f^2(y) r(y, \eta) q_\theta(x, dy) + f^2(x) \mu_\theta(x, \eta),
+    \eta(dx) \bigg\rangle .
+\end{aligned}
+\end{equation}
+A process $(\eta^N_t)_{t \geq 0}$ 
+satisfies the martingale characterization of Definition~\ref{defn:mgale_construction}
+if and only if it is a solution 
+to the $(\Pgen^N, \eta_0)$-martingale problem, i.e.,
+if for all such test functions 
+$$
+    M_t :=
+    G_f(\eta^N_t) - G_f(\eta^N_0)
+    - \int_{0}^{t}\Pgen^N G_f(\eta^N_s)ds
+$$
+is a martingale (with respect to the natural $\sigma$-field).
+
+Furthermore, let $\Pgen^\infty$ be the generator given by
 \begin{equation}
@@
 \begin{aligned}
-\Pgen^{\infty} G_f(\eta):=& G'(\langle f, \eta \rangle)
+\Pgen^{\infty} G_f(\eta)
+    &:= G'(\langle f, \eta \rangle)
                    %\times 
@@
                    \right\}\\
-                &+ \frac{\alpha}{2} G''(\langle f, \eta \rangle)
+               &\qquad {}
+               + \frac{\alpha}{2} G''(\langle f, \eta \rangle)
                   %\times 
@@
 A process $(\eta^{\infty}_t)_{t \geq 0}$ 
-is a solution to the $(A, \lp_0)$-martingale problem of Definition~\ref{defn:limiting_lookdown_mgale}
+satisifes the martingale characterization of equations~\ref{eqn:limiting_mgale_problem}
+and~\ref{eqn:limiting_mgale_variation}
 if and only if it is a solution 
-to the $(\Pgen^{\infty}, \eta_0)$-martingale problem, i.e.,
+to the $(\Pgen^{\infty}, \eta^\infty_0)$-martingale problem, i.e.,
 if for all such test functions 
@@
     M_t :=
-    G_f(\eta^{\infty}_t)-G_f(\eta_0)
+    G_f(\eta^{\infty}_t) - G_f(\eta^\infty_0)
     - \int_{0}^{t}\Pgen^{\infty}G_f(\eta^{\infty}_s)ds
@@
 
-\comment{I haven't turned the $\mu$ into $\mu_\theta$ below this point.}
-
 % % % % % % % % % % % % %
 \section{Lookdown Proofs}
+    \label{sec:lookdown_proofs}
 
@@
     are all finite,
-    Then under the assumptions of Lemma~\ref{lem:compact containment lookdown},
-    \comment{MOVE ASSUMPTIONS HERE}
-    for any $T$ there exists a constant $K(T)$ such that for all $M > 0$,
+    Suppose that Assumptions~\ref{def:model_setup} hold,
+    and that $\theta/N \to \alpha$ and $\lp_0^N \to \lp_0$ weakly as $N \to \infty$,
+    where each $\lp_0^N$ is conditionally uniform given $\eta_0^N$
+    in the sense of \eqref{eqn:conditionally_uniform}
+    and $\lp_0$ is conditionally uniform given $\eta_0$
+    in the sense of \eqref{eqn:conditionally_poisson}.
+    Then for any $T$ there exists a constant $K(T)$ such that for all $M > 0$,
     $$ 
@@
     $f(x, u) = 0$ for all $x$ and $u \ge u_f$.
-    Under the assumptions of Lemma~\ref{lem:compact containment lookdown},
+    Under the assumptions of Lemma~\ref{lem:h_containment},
     for any $T$ there exists a constant $K(f,T)$ such that for all $M > 0$,
@@
     of Lemma~\ref{lem:compact containment hn}.
-    Under Assumptions~\ref{def:model_setup},
-    if $\theta/N \to \alpha$ and $\lp_0^N \to \lp_0$ weakly as $N \to \infty$,
-    where each $\lp_0^N$ is conditionally uniform given $\eta_0^N$
-    in the sense of \eqref{eqn:conditionally_uniform}
-    and $\lp_0$ is conditionally uniform given $\eta_0$
-    in the sense of \eqref{eqn:conditionally_poisson},
-    then for any $T$ and $\delta > 0$ there exists a sequence
+    Under the assumptions of Lemma~\ref{lem:h_containment},
+    for any $T$ and $\delta > 0$ there exists a sequence
     $(C_1, C_2, \ldots)$ of finite constants such that
@@
 \Pgen^{N} F_f(\eta):=& \int_{\IR^d} \theta\gamma(x, \eta) \left\{\int_{\IR^d} \left\{F(\langle f, \eta \rangle + f(y)/N )-F(\langle f, \eta \rangle )\right\}r(y, \eta)q_{\theta}(x,dy)\right\}N\eta(dx)\\
-&+\int_{\IR^d} \theta \mu(x, \eta) \left\{F(\langle f, \eta \rangle - f(x)/N )-F(\langle f, \eta \rangle )\right\}N\eta(dx).
+&+\int_{\IR^d} \theta \mu_\theta(x, \eta) \left\{F(\langle f, \eta \rangle - f(x)/N )-F(\langle f, \eta \rangle )\right\}N\eta(dx).
 \end{aligned}    
@@
 \begin{aligned}
-\Pgen^{N} F_f(\eta):=& F'(\langle f, \eta \rangle)\int_{\IR^d}  \theta\left\{\int_{\IR^d} \left\{f(y)\gamma(x, \eta) r(y,\eta) -f(x)\mu(x, \eta)\right\}q_{\theta}(x,dy)\right\}\eta(dx)\\
+\Pgen^{N} F_f(\eta):=& F'(\langle f, \eta \rangle)\int_{\IR^d}  \theta\left\{\int_{\IR^d} \left\{f(y)\gamma(x, \eta) r(y,\eta) -f(x)\mu_\theta(x, \eta)\right\}q_{\theta}(x,dy)\right\}\eta(dx)\\
 &+\frac{1}{2}\frac{\theta}{N}F''(\langle f, \eta \rangle)\int_{\IR^d} 
- \left\{\gamma(x, \eta)\int_{\IR^d} \left\{f^2(y) r(y,\eta) \right\}q_{\theta}(x,dy)+f^2(x)\mu(x, \eta)\right\}\eta(dx)\\
+ \left\{\gamma(x, \eta)\int_{\IR^d} \left\{f^2(y) r(y,\eta) \right\}q_{\theta}(x,dy)+f^2(x)\mu_\theta(x, \eta)\right\}\eta(dx)\\
 &+\frac{1}{6}\frac{\theta}{N^2}\int_{\IR^d}\left\{ 
-F'''(w) \left\{\gamma(x, \eta)\int_{\IR^d} f^3(y) r(y,\eta) q_{\theta}(x,dy)\right\}-F'''(v)f^3(x)\mu(x, \eta)\right\}\eta(dx)
+F'''(w) \left\{\gamma(x, \eta)\int_{\IR^d} f^3(y) r(y,\eta) q_{\theta}(x,dy)\right\}-F'''(v)f^3(x)\mu_\theta(x, \eta)\right\}\eta(dx)
 \end{aligned}    
@@
 Furthermore,
-$\mu(x,\eta) = r(x,\eta)\gamma(x,\eta)-\frac{1}{\theta}F(x,\eta) \to r(x,\eta)\gamma(x,\eta),$
-so $f^2(x)\mu(x,\eta) \to r(x,\eta)\gamma(x,\eta) f^2(x)$.
+$\mu_\theta(x,\eta) = r(x,\eta)\gamma(x,\eta)-\frac{1}{\theta}F(x,\eta) \to r(x,\eta)\gamma(x,\eta),$
+so $f^2(x)\mu_\theta(x,\eta) \to r(x,\eta)\gamma(x,\eta) f^2(x)$.
 
@@
 \begin{multline}
- \theta\left\{\int_{\IR^d} \left\{f(y)\gamma(x, \eta) r(y,\eta) -f(x)\mu(x, \eta)\right\}q_{\theta}(x,dy)\right\}
+ \theta\left\{\int_{\IR^d} \left\{f(y)\gamma(x, \eta) r(y,\eta) -f(x)\mu_\theta(x, \eta)\right\}q_{\theta}(x,dy)\right\}
  \\

### 2023-04-07 forwards-and-backwards.tex
notes from meeting

@@
 \maketitle
+
+\comment{get equations to restart numbering in sections}
 
@@
 If either
+    \comment{which assumptions from 2.7 are in force? since in (1) we need $\gamma$ to be bounded, which is condition 3 above}
 \begin{enumerate}
@@
         Blue curves are contours from a kernel density estimate.
+        \comment{remove blue curves}
         \label{fig:super_vs_det_2d}
@@
 we recover a superprocess with nonlinear death rates corresponding to logistic growth
+\comment{cite Etheridge 2004}
 that is a continuous limit of the Bolker-Pacala model \citep{bolker/pacala:1997,bolker/pacala:1999}.
@@
 something that is, in principle, discernible from genetic data.
+\comment{clarify why: smaller $N_e$}
 
@@
 % $\lp_t$ is conditionally Poisson with mean measure $\eta_t(dx) \times du$.
-Furthermore, convergence of the lookdown processes would imply convergence of the population processes
-\citep[Thm A.9 in][]{kurtz/rodrigues:2011}.
+% Furthermore, convergence of the lookdown processes would imply convergence of the population processes
+% \citep[Thm A.9 in][]{kurtz/rodrigues:2011}.
 
@@
     Let $\eta_0^N = \kappa(\lp_0^N)$ and
-    suppose also that $\eta^N_0 \to \eta_0$ (as finite measures on $\IR^d$),
+    suppose also that $\eta^N_0 \to \eta_0$ in $\measures$,
     and that for each $N$, $\lp^N_0$ is conditionally uniform given $\eta_0^N$
@@
 
+\comment{this section (6) is no long just "proofs" since they're in section 7 and 8 too}
+\comment{make sure this reads okay and describes just this section (6); the end-of-the-intro paragraph describes structure}
 In the following sections we present formal proofs of our three scaling limits.
@@
 Below we will have frequent use for the quantity
+\comment{perhaps $B$ should have a superscript $\theta$}
 \begin{equation}
@@
 a constant times $\smooth{\gamma}\eta(x)+(\smooth{\gamma}\eta(x))^2$;
-since $m^2\gamma(m)$ is bounded, so is $|\gamma(x,\eta) B_1(x,\eta)$.
+since $m^2\gamma(m)$ is bounded, so is $|\gamma(x,\eta) B_1(x,\eta)|$.
 \end{proof}
@@
 \end{multline} 
+    \comment{alison to look at this again; check whether it depends on just bounding $B_1$}
 Evidently, in much the same way as in the proof of
@@
 
+\comment{below $\eta_s^N$ stops having  an $N$ at some point}
+
 In this section we prove Theorem~\ref{thm:local_convergence},
@@
 so $(1 + t/\epsilon^2) = d \delta/(2 \theta \epsilon^2)$,
-and so this quantity is bounded uniformly over only $t$ but also $\epsilon$.
-\comment{That's where we use bounded-below-ness of $\theta \epsilon^2$.}
+and so this quantity is bounded uniformly over not only $t$ but also $\epsilon$.
+\comment{explain that's where we use bounded-below-ness of $\theta \epsilon^2$.}
 Therefore, the second term in \eqref{eqn:psi_infty_bound} 
@@
 
+\comment{perhaps explain: the next proposition is useful because we'll want to use weak convergence of $\smooth{\epsilon}\eta_s$; but in the martingale we have the term on the left in the proposition; probably there are other ways to do this.}
+\comment{ACTUALLY BETTER we want to transfer $T_\epsilon^2$ over onto $\eta$; this happens in two steps, first this proposition; next using that $T_{\epsilon^2}f - f$ is small}
+
 \begin{proposition} 
@@
 \end{proposition}
+
 \begin{proof}
@@
 |\rho_\epsilon*\eta_s(y)-\rho_\epsilon*\eta_s(w)|
-\sum_{k=1}^{n-1}|b_k|\left(\rho_\epsilon*\eta_s(y)^k+\rho_\epsilon*\eta_s(w)^k\right).
+\sum_{k=1}^{n-1}|b_k|\left(\rho_\epsilon*\eta_s(y)^{n-1}+\rho_\epsilon*\eta_s(w)^{n-1}\right).
 \]
@@
 p_{\epsilon^2}(w,y)dy, \eta_s(dw)\big\rangle ds
-=0.
-\end{equation}
+=0,
+\end{equation}
+\comment{which we prove by showing the expectation of this positive quantity goes to zero; e.g. see Lemma 7.5(?)}.
 
@@
 \comment{Probably should put a bit more detail in here?}
+\comment{key bit is that we can always write $M_s(w)$ as a convolution of $p_{\epsilon^2/}$ with something}
 

### 2023-04-10 forwards-and-backwards.tex
minor fixen

@@
 
-\comment{TODO: cite \citet{lam2023introduction,cantrell2004spatial}}
-
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 which includes the Fisher-KPP equation and the Allen-Cahn equation.
+Equations of this form have been studied extensively
+in the context of spatial ecology;
+see for instance \citet{lam2023introduction} and \citet{cantrell2004spatial}.
 
@@
 and $\rho_F$ is again a smooth kernel. 
-\comment{FIX UP THIS, REFER FORWARD}
 The function $F$ is nearly
@@
 and would be equal to it in a nonspatial model;
-but 
-It will be convenient to work with $F$ instead of $\mu$.
+but, as discussed later,
+differs because offsprings' establishment probability is measured at their new location
+rather than their parents', and so differs from $r(x)$.
+For the most part, we work with $F$ instead of $\mu$.
 
@@
 we recover a superprocess with nonlinear death rates corresponding to logistic growth
-\comment{cite Etheridge 2004}
+\citep{etheridge:2004}
 that is a continuous limit of the Bolker-Pacala model \citep{bolker/pacala:1997,bolker/pacala:1999}.
@@
 with increasingly good agreement for larger $\theta$ and $N$.
+\comment{TODO: does it?}
 As expected, noise slows down the wave.
@@
 i.e., those areas have higher reproductive value, %long-term fitness
-something that is, in principle, discernible from genetic data.
-\comment{clarify why: smaller $N_e$}
+something that is, in principle, discernible from genetic data
+(because, for instance, making reproductive value less evenly distributed
+reduces long-term genetic diversity).
 
@@
 solve, for $\tau_a \le t < \sigma_a$,
-\begin{align*}
+\begin{align}
+    \label{eqn:limiting_construction}
+    \begin{split}
 X_a(t)
@@
     ds .
-\end{align*}
+    \end{split}
+\end{align}
 Each point in each $R_a$ denotes a potential birth time for $a$:
@@
 \begin{proof}[of Proposition~\ref{prop:limiting_construction}]
-    The fact that a solution to the system of equations
-    \comment{label the system and refer to it}
+    The fact that a solution to the system of equations~\eqref{eqn:limiting_construction}
     is a solution to the martingale problem of Theorem~\ref{thm:lookdown_convergence}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Proofs}
+\section{Proofs of convergence for nonlocal models}
 \label{sec:proofs}
 
-\comment{this section (6) is no long just "proofs" since they're in section 7 and 8 too}
-\comment{make sure this reads okay and describes just this section (6); the end-of-the-intro paragraph describes structure}
 In the following sections we present formal proofs of our three scaling limits.
@@
 limit to obtain a classical PDE.
-In Section~\ref{subsec:one step convergence proof}
+In subsequent sections (Sections~\ref{subsec:one step convergence proof} and~\ref{sec:lookdown_proofs})
 we prove our third scaling limit, in which 
 we pass from our population model 
-directly to a reaction diffusion equation without going via a nonlocal limit.
-Finally, in Section~\ref{sec:lookdown_proofs} we prove our results concerning both convergence of the lookdown representation
+directly to a reaction diffusion equation without going via a nonlocal limit,
+and finally our results concerning both convergence of the lookdown representation
 and characterization of the lineage process in the deterministic case.
+\comment{TODO: revisit this paragraph}
 
@@
 Below we will have frequent use for the quantity
-\comment{perhaps $B$ should have a superscript $\theta$}
 \begin{equation}
 \label{generator Bf}
-    B_f(x, \eta) = \theta \int_{\IR^d} (f(y) r(y, \eta) - f(x) r(x, \eta)) q_\theta(x, dy) .
+    B^\theta_f(x, \eta) = \theta \int_{\IR^d} (f(y) r(y, \eta) - f(x) r(x, \eta)) q_\theta(x, dy) .
 \end{equation}
@@
 \begin{proof}[of Lemma~\ref{lem:conditions on r}]
-Here, we need to prove that $|\gamma(x, \eta) B_1(x, \eta)|$ is bounded,
+Here, we need to prove that $|\gamma(x, \eta) B^\theta_1(x, \eta)|$ is bounded,
 uniformly over $x$ and $\eta$.
@@
 \comment{typo}
-u implies that $|B_1|$ is uniformly bounded;
-since $\gamma$ is bounded as well, so is $|\gamma B_1|$.
+u implies that $|B^\theta_1|$ is uniformly bounded;
+since $\gamma$ is bounded as well, so is $|\gamma B^\theta_1|$.
 
@@
 Therefore,
-under Condition~\ref{control through gamma}, $|B_1(x,\eta)|$ is bounded by 
+under Condition~\ref{control through gamma}, $|B^\theta_1(x,\eta)|$ is bounded by 
 a constant times $\smooth{\gamma}\eta(x)+(\smooth{\gamma}\eta(x))^2$;
-since $m^2\gamma(m)$ is bounded, so is $|\gamma(x,\eta) B_1(x,\eta)|$.
+since $m^2\gamma(m)$ is bounded, so is $|\gamma(x,\eta) B^\theta_1(x,\eta)|$.
 \end{proof}
@@
     + \int_0^t \int_{\IR^d} \big\{
-        \gamma(x, \eta^N_s) B_f(x, \eta^N_s)
+        \gamma(x, \eta^N_s) B^\theta_f(x, \eta^N_s)
         + f(x) F(x, \eta^N_s)
@@
 \end{align}
-where $M^N_t(f)$ is a martingale and $B_f$ is defined in \ref{generator Bf}.
-
-We need a bound on $\gamma(x,\eta)B_f(x,\eta)+fF$.
-First note that we may rewrite $B_f(x, \eta)$ as
+where $M^N_t(f)$ is a martingale and $B^\theta_f$ is defined in \ref{generator Bf}.
+
+We need a bound on $\gamma(x,\eta)B^\theta_f(x,\eta)+fF$.
+First note that we may rewrite $B^\theta_f(x, \eta)$ as
 \begin{align}
@@
     +
-    \|f\|_\infty |B_1(x, \eta)| .
+    \|f\|_\infty |B^\theta_1(x, \eta)| .
 \end{align}
@@
 Furthermore, Condition~\ref{gamma_B_condition} of Assumptions~\ref{def:model_setup}
-stipulates that $|\gamma(x, \eta) B_1(x, \eta)|$ is uniformly bounded,
+stipulates that $|\gamma(x, \eta) B^\theta_1(x, \eta)|$ is uniformly bounded,
 and so recalling that $F$ is bounded above, we can now conclude that
 under Assumptions~\ref{def:model_setup}
-$\gamma(x, \eta) B_f(x, \eta) + f(x) F(x, \eta) \le C_f $ for some $C_f$.
+$\gamma(x, \eta) B^\theta_f(x, \eta) + f(x) F(x, \eta) \le C_f $ for some $C_f$.
 
@@
 		+ \frac{\gamma(x,\eta_s^N)}{N} 
-		B_1(x, \eta^N_s)-\frac{1}{N}F(x,\eta^N_s)
+		B^\theta_1(x, \eta^N_s)-\frac{1}{N}F(x,\eta^N_s)
             \right\}, \eta_s^N(dx) \Big\rangle
@@
 \gamma(x,\eta_s^N)
-	B_1(x, \eta_s^N),\eta_s^N(dx)\Big\rangle ds\right],
-	\end{equation}
-which is bounded since $\gamma (x,\eta)$ and $B_1(x,\eta)$ are both bounded and 
+	B^\theta_1(x, \eta_s^N),\eta_s^N(dx)\Big\rangle ds\right],
+	\end{equation}
+which is bounded since $\gamma (x,\eta)$ and $B^\theta_1(x,\eta)$ are both bounded and 
 $\langle 1,\eta_t\rangle\geq 0$. 
@@
     Taking suprema and expectations on both sides of equation~\eqref{eqn:eta_f_mgale_decomp},
-    then again using the fact that $\gamma(x, \eta) B_1(x, \eta) + F(x, \eta) \le C$,
+    then again using the fact that $\gamma(x, \eta) B^\theta_1(x, \eta) + F(x, \eta) \le C$,
     \begin{align*}
@@
                 \gamma(x, \eta^N_s)
-                B_1(x, \eta^N_s)
+                B^\theta_1(x, \eta^N_s)
                 + F(x, \eta^N_s)
@@
             \left\{
-                \gamma(x, \eta^N_s) B_f(x, \eta^N_s)
+                \gamma(x, \eta^N_s) B^\theta_f(x, \eta^N_s)
                 + f(x) F(x, \eta^N_s)
@@
 The proof of Lemma~\ref{lem:eta_f_bound}
-provides a uniform bound on $\gamma B_f$, but we only know
+provides a uniform bound on $\gamma B^\theta_f$, but we only know
 that $F$ is bounded above. However, since, by 
@@
     \qquad
-    \sup_{x,\eta}\gamma(x,\eta)B_f(\,\eta)\delta_1<\nu/2,
+    \sup_{x,\eta}\gamma(x,\eta)B^\theta_f(\,\eta)\delta_1<\nu/2,
 $$
@@
                 +
-                B_{f^2}(x, \eta^N_s)
+                B^\theta_{f^2}(x, \eta^N_s)
             \right)
@@
 bounded, and, in the notation of Lemma~\ref{lem:eta_f_bound}
-$\gamma(x,\eta) B_f(x,\eta)$ is bounded. Moreover $\theta/N^2\to 0$ as $N\to\infty$. Thus we can 
+$\gamma(x,\eta) B^\theta_f(x,\eta)$ is bounded. Moreover $\theta/N^2\to 0$ as $N\to\infty$. Thus we can 
 dominate 
@@
 \end{multline} 
-    \comment{alison to look at this again; check whether it depends on just bounding $B_1$}
+    \comment{alison to look at this again; check whether it depends on just bounding $B^\theta_1$}
 Evidently, in much the same way as in the proof of
@@
 so $(1 + t/\epsilon^2) = d \delta/(2 \theta \epsilon^2)$,
-and so this quantity is bounded uniformly over not only $t$ but also $\epsilon$.
-\comment{explain that's where we use bounded-below-ness of $\theta \epsilon^2$.}
+and so this quantity is bounded uniformly over not only $t$ but also $\epsilon$
+(since we've assumed that $\theta \epsilon^2$ is bounded below).
 Therefore, the second term in \eqref{eqn:psi_infty_bound} 
@@
             2 C_0 \|f\|_\infty u_f
-            + (1 - u/N) \gamma B_f
+            + (1 - u/N) \gamma B^\theta_f
             + (C_0 u^2 - b_\theta u) \frac{d}{du} f,
@@
 \appendix
+
+\comment{TODO copy in the MMT and refer to it earlier}
 

### 2023-04-10 figures/make_plots.sh
removed contours

@@ -13,7 +13,7 @@ do
     then
         slim -s 123 ../fkpp.slim
     fi
-    ../lineage_plotting/plot_density.py fkpp_123.trees 3
+    ../lineage_plotting/plot_density.py fkpp_123.trees 3 pdf 3 0.0
     popd
 done
 

### 2023-04-11 forwards-and-backwards.tex
removed contours
fixup of first lemma

@@
 conditions on the parameters of our model.
+
 \begin{assumptions}%[Assumptions]
@@
 {\bf Reproduction parameters:}
-
 We assume that 
@@
     derivatives in both arguments;
+    \label{r_gamma_derivs_condition}
 \item $\gamma(x,m)$ is uniformly bounded;
-\item $|\gamma(x, \smooth{\gamma} \eta(x)) \theta \int (r(y, \smooth{r} \eta(y)) - r(x, \smooth{r} \eta(x))) q_\theta(x, dy)|$
-    is uniformly bounded for $x \in \IR^d$ and $\eta \in \measures$.
+    \label{gamma_bounded_condition}
+\item For each $f \in C_b^2(\IR^d)$, there is a $C_f$ such that
+    $$ |\gamma(x, \smooth{\gamma} \eta(x)) \theta \int 
+    (r(y, \smooth{r} \eta(y)) f(y) - r(x, \smooth{r} \eta(x)) f(x))
+    q_\theta(x, dy)| \le C_f $$
+    for all $x \in \IR^d$ and $\eta \in \measures$.
         \label{gamma_B_condition}
@@
     \label{lem:conditions on r}
+    Assume that Conditions~\ref{def:model_setup} are satisfied,
+    except for condition~\ref{gamma_B_condition}.
     If either
-    \comment{which assumptions from 2.7 are in force? since in (1) we need $\gamma$ to be bounded, which is condition 3 above}
 \begin{enumerate}
@@
     \[\theta\int\big(\smooth{r}\eta(y)-\smooth{r}\eta(x)\big)^2q_\theta(x,dy)
-    \leq C(\smooth{\gamma}\eta(x))^2.
+    \leq C(\smooth{\gamma}\eta(x))^2 ,
     \]
 \end{enumerate} 
-then
-$|\gamma(x, \smooth{\gamma} \eta(x)) \theta \int (r(y, \smooth{r} \eta(y)) - r(x, \smooth{r} \eta(x))) q_\theta(x, dy)|$
-is uniformly bounded for $x \in \IR^d$ and $\eta \in \measures$.
+    then condition~\ref{gamma_B_condition} is also satisfied.
 \end{lemma}
@@
     \begin{center}
-        \includegraphics{figures/ex1a/fkpp_123.locations}
-        \includegraphics{figures/ex1b/fkpp_123.locations}
+        \includegraphics{figures/ex1a/fkpp_123.density.3.0}
+        \includegraphics{figures/ex1b/fkpp_123.density.3.0}
     \end{center}
@@
         Blue curves are contours from a kernel density estimate.
-        \comment{remove blue curves}
         \label{fig:super_vs_det_2d}
@@
 \begin{proof}[of Lemma~\ref{lem:conditions on r}]
-Here, we need to prove that $|\gamma(x, \eta) B^\theta_1(x, \eta)|$ is bounded,
+Here, we need to prove that $|\gamma(x, \eta) B^\theta_f(x, \eta)|$ is bounded,
 uniformly over $x$ and $\eta$.
@@
 \begin{align*}
-    r\big(y,\rho_r*\eta(y)\big) - r\big(x,\rho_r*\eta(x)\big)
+    r\big(y,\rho_r*\eta(y)\big) f(y) - r\big(x,\rho_r*\eta(x)\big) f(x)
     &=
-    \sum_i (y_i - x_i) \partial_{x_i} \Big(r\big(x,\rho_r*\eta(x)\big)\Big) 
+    \sum_i (y_i - x_i) \partial_{x_i} \Big( r\big(x,\rho_r*\eta(x)\big) f(x) \Big) 
     \\ &\qquad {}
@@
     \frac{1}{2} \sum_{ij} (y_i - x_i)(y_j - x_j)
-        \partial_{x_i x_j} \Big(r\big(\smooth{r}\eta(z)\big)\Big) ,
+        \partial_{x_i x_j} \Big( r\big(z, \smooth{r}\eta(z)\big) f(z) \Big) ,
 \end{align*}
@@
 gives uniform bounds on the derivatives of $r(x, \rho_r*\eta(x))$
-in this expression and so we have a bound of the form
+in this expression and so, provided $f$ also has uniformly bounded first and second derivatives,
+we have a bound of the form
 \begin{multline*}
-\Big| r\big(y,\rho_r*\eta(y)\big) - r\big(x,\rho_r*\eta(x)\big) \Big|
-\\
+|B^\theta_f|
 \leq
@@
 are bounded uniformly in $x$ under Assumptions~\ref{def:model_setup}.
-\comment{typo}
-u implies that $|B^\theta_1|$ is uniformly bounded;
-since $\gamma$ is bounded as well, so is $|\gamma B^\theta_1|$.
+Since $\gamma$ is bounded as well, so is $|\gamma B^\theta_f|$.
 
@@
 Condition~\ref{control through gamma} of Lemma~\ref{lem:conditions on r} is satisfied.
-is satisfied.
 First note that
+    \begin{align}
+	    \nonumber
+    & |B_f^\theta| =
+        \left| \theta 
+            \int_{\IR^n} 
+                \big\{
+                    f(y) r\big(y,\smooth{r}\eta(y)\big)
+                    -
+                    f(x) r\big(x, \smooth{r}\eta(x)\big)
+                \big\}
+            q_{\theta}(x,dy)
+        \right|
+    \\ 
+ \label{eqn:q_bound_split}
+	    &\qquad {} \leq
+        \left| \theta 
+            \int_{\IR^n} 
+                \big\{
+                    f(y) r\big(y, \smooth{r}\eta(y)\big)
+                    -
+                    f(x) r\big(x,\smooth{r}\eta(y)\big)
+                \big\}
+            q_{\theta}(x,dy)
+        \right|
+    \\ 
+\nonumber
+	    &\qquad \qquad {}  +
+        \left| \theta 
+            \int_{\IR^n} 
+                \big\{
+                    f(x) r\big(x,\smooth{r}\eta(y)\big)
+                    -
+                    f(x) r\big(x,\smooth{r}\eta(x)\big)
+                \big\}
+            q_{\theta}(x,dy) 
+        \right| .
+    \end{align}
+
+ Writing
+    $K_3 = \sup_{x,m} \max_i |\partial_{x_i} f(x)r(x, m)|$
+    and 
+    $K_4 = \sup_{x,m} \max_{i,j} |\partial_{x_i x_j} f(x)r(x, m)|$, since
+\[\big|\partial_{x_i}\big(f(x)r(x,\rho_r*\eta(y))\big|\leq K_3\]
+and
+\[\big|\partial_{x_ix_j}\big(f(x)r(x,\rho_r*\eta(y))\big|\leq K_4,\]
+the first term
+is bounded exactly as above. For the second, 
     \begin{multline*}
@@
 with respect to the second argument.
-So, in this case
-\begin{align*}
-&
-\left| \theta 
-    \int_{\IR^n} 
-        \big\{
-            r\big(x,\smooth{r}\eta(y)\big)
-            -
-            r\big(x,\smooth{r}\eta(x)\big)
-        \big\}
-    q_{\theta}(x,dy) 
-\right| 
-\\ &\qquad
-\le
-   \|r'\|_\infty
+    So, writing $K_5=\|f\|_\infty\|r'\|_\infty$ and $K_6=\|f\|_\infty\|r''\|_\infty$,
+    the second term in~\eqref{eqn:q_bound_split} is bounded by
+    \begin{align*}
+       K_5
         \left|
@@
         +
-   \|r''\|_\infty
+       K_6
         \left|
@@
     \end{align*}
-Therefore,
-under Condition~\ref{control through gamma}, $|B^\theta_1(x,\eta)|$ is bounded by 
-a constant times $\smooth{\gamma}\eta(x)+(\smooth{\gamma}\eta(x))^2$;
-since $m^2\gamma(m)$ is bounded, so is $|\gamma(x,\eta) B^\theta_1(x,\eta)|$.
+Under Condition~\ref{control through gamma} of 
+Assumptions~\ref{def:model_setup}, the right hand side is bounded by 
+a constant times $\smooth{\gamma}\eta(x)+(\smooth{\gamma}\eta(x))^2$ and 
+$m^2\gamma(m)$ is bounded, so therefore $|\gamma B^\theta_f|$ is bounded.
 \end{proof}
@@
 where $M^N_t(f)$ is a martingale and $B^\theta_f$ is defined in \ref{generator Bf}.
-
-We need a bound on $\gamma(x,\eta)B^\theta_f(x,\eta)+fF$.
-First note that we may rewrite $B^\theta_f(x, \eta)$ as
-\begin{align}
-    \nonumber
-&
-    \left| \theta 
-        \int_{\IR^n} 
-            \big\{
-                f(y) r\big(y,\smooth{r}\eta(y)\big)
-                -
-                f(x) r\big(x, \smooth{r}\eta(x)\big)
-            \big\}
-        q_{\theta}(x,dy)
-    \right|
-\\ 
-    &\qquad {} =
-    \Big| \theta 
-        \int_{\IR^n} 
-            ( f(y) - f(x) )
-            r\big(y, \smooth{r}\eta(y)\big)
-        q_{\theta}(x,dy)
-\\ 
-\nonumber
-    &\qquad \qquad {}  +
-    \theta 
-            f(x)
-        \int_{\IR^n} 
-            \big\{
-                r\big(y,\smooth{r}\eta(y)\big)
-                -
-                r\big(x,\smooth{r}\eta(x)\big)
-            \big\}
-        q_{\theta}(x,dy) 
-    \Big| 
-\\ 
-    &\qquad {} \leq
-    \left| \theta 
-        \int_{\IR^n} 
-            ( f(y) - f(x) )
-            r(y, \smooth{r}\eta(y))
-        q_{\theta}(x,dy)
-    \right|
-    +
-    \|f\|_\infty |B^\theta_1(x, \eta)| .
-\end{align}
-\comment{TODO FIX THIS}
-Using the intermediate value theorem,
-then the fact that $0 \le r \le 1$,
-there is a $\kappa$ in $[0, 1]$ such that the first term is
-\begin{align*}
-    &
-    \left| \theta 
-        \int_{\IR^n} 
-            ( f(y) - f(x) )
-            r(y, \eta)
-        q_{\theta}(x,dy)
-    \right|
-    \\ &\qquad =
-    \left| \theta 
-        \int_{\IR^n} 
-            \left(
-                \sum_i (y-x)_i \partial_{x_i} f(x)
-                +
-                \frac{1}{2} \sum_{ij} (y-x)_i (y-x)_j \partial_{x_i x_j} f(x + \kappa(y-x))
-            \right)
-            r(y, \eta)
-        q_{\theta}(x,dy)
-    \right|
-    \\ &\qquad \leq
-    \|f'\|_\infty \left| \theta 
-        \int_{\IR^n} 
-            (y-x) r(y, \eta)
-        q_{\theta}(x,dy)
-    \right|
-    + \frac{1}{2} \|f''\|_\infty \left| \theta 
-        \int_{\IR^n} 
-            (y-x)^2
-        q_{\theta}(x,dy)
-    \right|
-\end{align*}
-bounded uniformly
-because $q_\theta(x, dy)$ is the density of a Gaussian with mean $\meanq(x)/\theta$
-and covariance $\covq(x)/\theta$,
-and both $\meanq(x)$ and $\covq(x)$
-are bounded uniformly in $x$ under Assumptions~\ref{def:model_setup}.
-Furthermore, Condition~\ref{gamma_B_condition} of Assumptions~\ref{def:model_setup}
-stipulates that $|\gamma(x, \eta) B^\theta_1(x, \eta)|$ is uniformly bounded,
+First note that Condition~\ref{gamma_B_condition} of Assumptions~\ref{def:model_setup}
+stipulates that $|\gamma B^\theta_f|$ is uniformly bounded,
 and so recalling that $F$ is bounded above, we can now conclude that
@@
 
-Taking expectations in~(\ref{eqn:eta_f_mgale_decomp}),
+Now, taking expectations in~(\ref{eqn:eta_f_mgale_decomp}),
     \begin{align}

### 2023-04-11 figures/make_plots.sh
clumpy figure

@@ -42,3 +42,24 @@ do
     ../lineage_plotting/plot_1d_lineages.py ${MODEL}_123.trees 3 1 3 3
     popd
 done
+
+# clumpiness
+DIR="clumpy_2d"
+MODEL="clumpy"
+pushd $DIR
+if [ ! -e ${MODEL}_123.trees ]
+then
+    slim -s 123 ../${MODEL}.slim
+    ../lineage_plotting/plot_density.py ${MODEL}_123.trees 3 pdf 3 0.0
+fi
+popd
+DIR="clumpy_1d"
+MODEL="clumpy"
+pushd $DIR
+if [ ! -e ${MODEL}_123.trees ]
+then
+    slim -s 123 ../${MODEL}.slim
+    ../lineage_plotting/plot_density.py ${MODEL}_123.trees 3 pdf 3 0.0
+    ../plot_wave.py ${MODEL}_123.trees 100 600 12
+fi
+popd

### 2023-04-11 figures/plot_wave.py

@@ -1,0 +1,75 @@
+#!/usr/bin/env python3
+import os, sys
+import tskit, pyslim
+import json
+import numpy as np
+import matplotlib
+from matplotlib import pyplot as plt
+
+usage = """
+Plots the 1D density.
+
+Usage:
+    plot_wave.py [name of treefile] [(start time) (end time) (number of steps)]
+"""
+
+if len(sys.argv) != 2 and len(sys.argv) != 5:
+    raise ValueError(usage)
+
+output_type = "pdf"
+
+treefile = sys.argv[1]
+assert treefile[-6:] == ".trees"
+outbase = treefile[:-6]
+
+input_times = (len(sys.argv) > 2)
+
+if input_times:
+    start_time = float(sys.argv[2])
+    end_time = float(sys.argv[3])
+    num_steps = int(sys.argv[4])
+
+ts = tskit.load(treefile)
+params = ts.metadata['SLiM']['user_metadata']
+for n in params:
+    if len(params[n]) == 1:
+        params[n] = params[n][0]
+
+
+dx = 0.8
+T = params['RUNTIME']
+dt = params["DT"]
+max_gen = ts.metadata["SLiM"]["tick"] - 1
+y_bins = [0, params['HEIGHT']]
+x_bins = np.arange(0, params['WIDTH'] + dx, dx)
+x_mids = x_bins[1:] - np.diff(x_bins)/2
+t_bins = np.arange(0, max_gen + 1)
+
+# Population sizes for each time step within each x bin
+popsize = pyslim.population_size(ts, x_bins, y_bins, t_bins)
+
+# "Observed" values of u
+uhat = np.sum(popsize, axis=1) / (params["K"] * dx)
+assert uhat.shape[0] == len(x_bins) - 1
+assert uhat.shape[1] == len(t_bins) - 1
+
+def plot_times(ax, times):
+    cm = matplotlib.cm.cool
+    steps = np.searchsorted(t_bins, max_gen - times / dt) - 1
+    legend_steps = list(range(0, len(steps) + 1, int((len(steps) + 1) / 4)))
+    for m, (j, t) in enumerate(zip(steps, times)):
+        ax.plot(x_mids, uhat[:, j], c=cm(m / len(steps)),
+                label=f"t={t:0.2f}" if m in legend_steps else None)
+    ax.set_title(f"{min(times)} < t < {max(times)}")
+    ax.set_xlabel("location")
[…]

### 2023-04-12 forwards-and-backwards.tex
clumpy figure
apx start

@@
 \newcommand{\cmeasures}{\mathcal{M}_F(\overline{\IR}^d)} % finite measures on compactified Rd
-\newcommand{\lpmeasures}{\mathcal{M}(\overline{\IR^d} \times [0,\infty))} % locally finite measures on space x level
+\newcommand{\lpmeasures}{\mathcal{M}(\overline{\IR^d} \times [0,\infty))} % locally finite measures on (compactified space) x level
+\newcommand{\flpmeasures}{\mathcal{M}(\IR^d \times [0,\infty))} % locally finite measures on space x level
 
@@
     \begin{center}
+        \includegraphics[width=0.45\textwidth]{figures/clumpy_2d/clumpy_123.density.3.0}
         \comment{TODO} FIGURE
@@
 
-\begin{lemma}
-    \label{def: MP definition of limit}
-For $G \in \mathcal{C}^{\infty}(\IR)$ with $\|G'''\|_\infty<\infty$,
-and 
-$f \in \mathcal{C}_{b}^\infty(\overline{\IR}^d)$, define the 
-function $G_f$ by 
-$G_f(\eta):=G (\langle f, \eta \rangle)$.
-Let $\Pgen^N$ be the generator given by
+\comment{TODO: the previous definition of $\Pgen^N$ was the following wrong thing; fixup below}
 \begin{equation}
 \begin{aligned}
+    \text{ONLY RIGHT TO $O(1/N)$} \qquad
     \Pgen^N G_f(\eta)
@@
         \gamma(x, \eta) \int f^2(y) r(y, \eta) q_\theta(x, dy) + f^2(x) \mu_\theta(x, \eta),
+    \eta(dx) \bigg\rangle .
+\end{aligned}
+\end{equation}
+
+\begin{lemma}
+    \label{def: MP definition of limit}
+For $G \in \mathcal{C}^{\infty}(\IR)$ with $\|G'''\|_\infty<\infty$,
+and 
+$f \in \mathcal{C}_{b}^\infty(\overline{\IR}^d)$, define the 
+function $G_f$ by 
+$G_f(\eta):=G (\langle f, \eta \rangle)$.
+Let $\Pgen^N$ be the generator given by
+\begin{equation}
+\begin{aligned}
+    \Pgen^N G_f(\eta)
+    &:=
+    \theta \bigg\langle
+    \gamma(x, \eta)
+        \int 
+        \left(G(\langle f, \eta \rangle + f(z)/N) - G(\langle f, \eta \rangle)\right)
+        r(z,\eta) q_\theta(x,dz)
+    +
+    \left(G(\langle f, \eta \rangle - f(x)/N) - G(\langle f, \eta \rangle)\right)
+    \mu_\theta(x, \eta),
     \eta(dx) \bigg\rangle .
@@
 
+% %% %% %% %% %% %% %% %% %% %% %% %% %% %% %% %% %%
+\section{Markov Mapping Theorem}
+
+\comment{TODO copy in the MMT and refer to it earlier}
+
+% %% %% %% %% %% %% %% %% %% %% %% %% %% %% %% %% %%
+\subsection{Lookdown Generators}
+
+In this section we verify one of the conditions of the Markov Mapping Theorem,
+namely, that ``integrating out levels'' in the generator of the lookdown process
+we obtain the generator of the projected process.
+We will work with test functions of the form
+$$  f(\lp) = \prod_{(x, u) \in \lp} g(x, u) = \exp\left(\langle \log g, \lp \rangle \right) . $$
+Furthermore, recall that $\kappa^N(\lp)(\cdot) = \lp(\cdot \times [0, N)) / N$
+is the ``spatial projection operator'',
+and define the probability kernel $\Gamma^N : \measures \to \mathcal{M}(\IR^d \times [0,N))$
+so that for $\eta \in \measures$, if $\hat g(x) = \int_0^N g(x, u) du / N$, then
+\begin{align*}
+    F^N_g(\eta)
+    &:=
+    \int f(\lp) \Gamma^N(\eta, d\lp) \\
+    &=
+    \exp\left(
+        N \left\langle
+            \log \frac{1}{N} \int_0^N g(x, u) du, \eta(dx)
+        \right\rangle
+    \right) \\
+    &=
+    \exp\left(
+        N \left\langle \log \hat g(x) \eta(dx) \right\rangle
+    \right) ,
+\end{align*}
+i.e., $\Gamma^N$ assigns independent labels on $[0, N]$ to each of the points in $\eta$.
+It follows from Lemma~\ref{def: MP definition of limit} that for test functions of this form
+\comment{(beware the different definition of $f$ to that lemma)}
+the generator of $\eta^N_t$ is
+\begin{align}
+    \Pgen^N F^N_g(\eta)
+    &=
+    F^N_g(\eta)
+    \theta \bigg\langle
+        \gamma(x, \eta) \int r(z, \eta) \left( \hat g(z) - 1 \right) q_\theta(x, dz)
+        +
+        \mu_\theta(x, \eta) \left( \frac{1}{\hat g(x)} - 1 \right)
+        ,
+        \eta(dx)
+    \bigg\rangle
+\end{align}
+The generator of $\lp^N_t$ is $A^N$, defined in equation~\label{eqn:lookdown_generator}.
+
+\begin{lemma}
+    \label{lem:averaged_generators}
+    For all finite counting measures $\eta$ on $\IR^d$,
+    \begin{align}
+        \int A^N f(\lp) \Gamma^N(\eta, d\lp)
+        &=
+        \Pgen^N F^N_g(\eta) .
+    \end{align}
+\end{lemma}
+
+For the limiting process,
+we now require test functions such that $g(x,u) = 1$ for all $u$ larger than some $u_0$;
+As before, recall that $\kappa(\lp)(\cdot) = \lim_{u \to \infty} \lp(\cdot \times [0, u)) / u$
+is the ``spatial projection operator'',
+and define the probability kernel $\Gamma : \measures \to \flpmeasures$
+so that for $\eta \in \measures$,
+defining $h(x) = \int_0^\infty (g(x, u) - 1) du$,
+\begin{align*}
+    F_g(\eta)
+    &:=
+    \int f(\lp) \Gamma(\eta, d\lp) \\
+    &=
+    \exp\left(
+        \big \langle
+            \int_0^\infty (g(x, u) - 1) du,
+            \eta(dx)
+        \big \rangle
+    \right) \\
+    &=
+    e^{ \langle h(x), \eta(dx) \rangle } .
+\end{align*}
+i.e., $\Gamma(\eta, \cdot)$ is the distribution of a conditionally Poisson process
+with intensity a product of $\eta$ and Lebesgue measure.
+It again follows from Lemma~\ref{def: MP definition of limit} that for test functions of this form
+\comment{(beware the different definition of $f$ to that lemma)}
+the generator of $\eta_t$ is
+\begin{align}
+    \Pgen^\infty F_g(\eta)
+    &=
+    F_g(\eta)
+    \left\langle
+        \gamma(x, \eta)
+        \DG( h(\cdot) r(\cdot) )(x)
+        + F(x, \eta) h(x)
+        + \alpha \gamma(x, \eta) r(x, \eta) h^2(x)
+        ,
+        \eta(dx)
+    \right\rangle .
+\end{align}
+The generator of $\lp_t$ is $A$, defined in equation~\eqref{eqn:limiting_lookdown_generator},
+
+\begin{lemma}
+    \label{lem:averaged_generators_limit}
+    For all $\eta \in \measures$,
+    \begin{align}
+        \int A f(\lp) \Gamma(\eta, d\lp)
+        &=
+        \Pgen^\infty F_g(\eta) .
+    \end{align}
+\end{lemma}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results on Lookdown Representations}
+\section{OLDER STUFF Results on Lookdown Representations}
     \label{sec: Markov Mapping Theorem Application}

### 2023-04-13 forwards-and-backwards.tex
first integral in the appendix done

@@
     &:=
-    \theta \bigg\langle
+    \theta N \bigg\langle
     \gamma(x, \eta)
@@
         r(z,\eta) q_\theta(x,dz)
+    \\ & \qquad \qquad {}
     +
@@
 a spatial location $y$ from the kernel
-$$
+\begin{equation} \label{eqn:qm_defn}
     q^m(x, dy, \eta)
@@
     r(y, \eta) q(x, dy) / \int_{\IR^d} r(y, \eta) q(x, dy),
-$$
+\end{equation}
 and the two lines swap spatial locations with probability 1/2.
@@
         + \int_0^t \Big\langle
-            c_\theta \int_u^N \int (f(y, u_1) + f(x, u_1)) q^m(x, dy) du_1
+            c_\theta \int_u^N \int (f(y, u_1) + f(x, u_1)) q^m(x,dy,\eta) du_1
         \\ {} &\qquad
-            + c_\theta (N - u) \int (f(y, u) - f(x, u)) q^m(x, dy)
+            + c_\theta (N - u) \int (f(y, u) - f(x, u)) q^m(x,dy,\eta)
             + (c_\theta u^2 - b_\theta u) \frac{d}{du} f,
@@
     \exp\left(
-        N \left\langle \log \hat g(x) \eta(dx) \right\rangle
+        N \left\langle \log \hat g(x), \eta(dx) \right\rangle
     \right) ,
@@
 the generator of $\eta^N_t$ is
-\begin{align}
+\begin{align} \label{eqn:pgen_defn_again}
+    \begin{split}
     \Pgen^N F^N_g(\eta)
-    &=
+    =
     F^N_g(\eta)
-    \theta \bigg\langle
+        N \theta & \bigg\langle
         \gamma(x, \eta) \int r(z, \eta) \left( \hat g(z) - 1 \right) q_\theta(x, dz)
+    \\ &\qquad \qquad {}
         +
@@
     \bigg\rangle
+    \end{split}
 \end{align}
-The generator of $\lp^N_t$ is $A^N$, defined in equation~\label{eqn:lookdown_generator}.
+The generator of $\lp^N_t$ is $A^N$, defined in equation~\eqref{eqn:lookdown_generator}.
 
@@
 \end{lemma}
+
+\begin{proof}[of Lemma~\ref{lem:averaged_generators}]
+First, break the generator $A^N$ into three parts, 
+\begin{align*}
+    A^N_1f(\lp)
+    &=
+    f(\lp) \sum_{(x,u)\in\lp} 2 c_\theta(x,\eta)
+    \int_u^{N}\Bigg(
+        \frac{1}{2}\frac{g(x,v_1)}{g(x,u)}
+        \int_{\IR^d} (g(y,u)-g(x,u))q^m_{\theta}(x,dy,\eta)
+    \Bigg)dv_1 ,
+    \\
+    A^N_2f(\lp)
+    &=
+    f(\lp) \sum_{(x,u)\in\lp} 2 c_\theta(x,\eta)
+    \int_u^{N}\Bigg(
+        \frac{1}{2}\int_{\IR^d}
+            \left(\frac{g(y,v_1) + g(x,v_1)}{2} - 1\right)
+        q^m_{\theta}(x,dy,\eta)
+    \Bigg)dv_1 ,
+    \\
+    A^N_3f(\lp)
+    &=
+    f(\lp) \sum_{(x,u)\in\lp}\,
+    \left( c_\theta(x,\eta) u^2 - b_{\theta}(x,\eta)u \right) \frac{\partial_u g(x,u)}{g(x,u)},
+\end{align*}
+where $q^m$ was defined in equation~\eqref{eqn:qm_defn},
+so that 
+$$ A^Nf(\lp) = A^N_1f(\lp) + A^N_2f(\lp) + A^N_3f(\lp). $$
+
+We now integrate each piece against $\Gamma^N$.
+First note that by the product form of $f$,
+$$
+    \int f(\lp) \sum_{(x,u)\in\lp} \frac{h(x,u)}{g(x,u)} \Gamma^N(\eta,d\lp)
+    =
+    F_g^N(\eta) \bigg\langle
+        \frac{1}{N \hat g(x)} \int_0^N h(x,u) du,
+        N \eta(dx)
+    \bigg\rangle .
+$$
+Therefore,
+\footnotesize
+\begin{align*}
+&
+    \int A^N_1f(\lp) \Gamma^N(\eta,d\lp) 
+\\ &\qquad =
+    F_g^N(\eta) \bigg\langle \frac{c_\theta(x,\eta)}{\hat g(x)} \int_0^N \Bigg\{
+        \int_u^N \Bigg(
+            \frac{1}{2} g(x,v_1) \int_{\IR^d}(g(y,u)-g(x,u))q^m_{\theta}(x,dy,\eta)
+        \Bigg) dv_1
+    \Bigg\} du, \eta(dx) \bigg \rangle
+\\ &\qquad =
+    F_g^N(\eta) \bigg\langle \frac{c_\theta(x,\eta)}{\hat g(x)} \Bigg\{
+    \int_{\IR^d} \left\{
+        \int_{0}^{N} \int_u^N g(x,v_1) (g(y,u)-g(x,u)) dv_1 du
+    \right\} q^m_{\theta}(x,dy,\eta)
+    , \eta(dx) \bigg \rangle .
+\end{align*}
+\normalsize
+For the second generator, we have
+\footnotesize
+\begin{align*}
+&
+    \int A^N_2 f(\lp) \Gamma^N(\eta, d\lp)
+\\ &\qquad =
+    F_g^N(\eta) \bigg\langle \frac{c_\theta(x,\eta)}{\hat g(x)} \int_0^N g(x, u) \Bigg\{
+        \int_u^N\Bigg(\int_{\IR^d}
+        \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right) q^m_{\theta}(x,dy,\eta)
+        \Bigg)dv_1 \Bigg\}
+    , \eta(dx) \bigg\rangle
+\\ &\qquad =
+    F_g^N(\eta) \bigg\langle \frac{c_\theta(x,\eta)}{\hat g(x)}
+    \int_{\IR^d}\Bigg\{ \int_{0}^{N}
+    \int_u^N g(x,u) \left(
+        g(y,v_1)+g(x,v_1)-2
+    \right) dv_1 du\Bigg\} q^m_{\theta}(x,dy,\eta)
+    , \eta(dx) \bigg\rangle .
+\end{align*}  
+\normalsize
+For the third generator we have that, since $g(x,N) = 1$,
+\footnotesize
+\begin{align*}
+&
+    \int A^N_3f(\xi)\Gamma^N(\eta,d\lp)
+\\ & \qquad =
+    F_g^N(\eta) \bigg\langle \frac{1}{\hat g(x)}
+    \int_0^N
+        \left( c_\theta(x,\eta) u^2 - b_\theta(x,\eta) u \right) \partial_u g(x,u)
+    du
+    , \eta(dx) \bigg\rangle 
+\\ & \qquad =
+    F_g^N(\eta) \bigg\langle \frac{1}{\hat g(x)}
+    \int_0^N
+        \left( b_\theta(x,\eta) - 2 c_\theta(x,\eta) u \right) (g(x,u) - 1)
+    du
+    , \eta(dx) \bigg\rangle .
+\end{align*}
+\normalsize
+
+Note that $2 \int_0^N \int_u^N g(x,v_1) g(y,u) dv_1 du = N^2 \hat g(x) \hat g(y)$,
+and so
+\footnotesize
+\begin{align*}
+&
+    \int_{0}^{N} \int_u^N g(x,v_1) (g(y,u)-g(x,u)) dv_1 du
+    + \int_{0}^{N} \int_u^N g(x,u) \left(g(y,v_1)+g(x,v_1)-2\right)dv_1 du
+\\ &\qquad = 
+    N^2 \hat{g}(x)(\hat{g}(y) - 2) + 2\int_{0}^{N} u g(x,u) du.
+\end{align*}
+\normalsize
+
+Combining the last equations,
+and using the fact that
+$N c_\theta(x,\eta) - b_\theta(x,\eta) = \theta \mu_\theta(x,\eta)$,
+we have 
+\begin{align*}
+&
+    \int \Bigg( A^N_1 f(\xi) + A^N_2 f(\xi) + A^N_3 f(\xi) \Bigg) \Gamma^N(\eta,d\lp)
+\\ &\qquad =
+    F_g^N(\eta) \bigg\langle
+        c_\theta(x,\eta) N^2 \int_{\IR^d} (\hat g(y) - 2) q^m(x,dy,\eta)
+        +
+        \frac{1}{\hat g(x)} c_\theta(x,\eta) \int_0^N 2u du
+\\ &\qquad \qquad \qquad {}
+        +
+        \frac{1}{\hat g(x)} b_\theta(x,\eta) \int_0^N (g(x,u) - 1) du
+    , \eta(dx) \bigg\rangle 
+\\ &\qquad =
+    F_g^N(\eta) \bigg\langle
+        c_\theta(x,\eta) N^2 \int_{\IR^d} (\hat g(y) - 1) q^m(x,dy,\eta)
+        +
+        N^2 c_\theta(x,\eta) \left(\frac{1}{\hat g(x)} - 1\right)
+\\ &\qquad \qquad \qquad {}
+        +
+        N b_\theta(x,\eta) \left(1 - \frac{1}{\hat g(x)}\right)
+    , \eta(dx) \bigg\rangle 
+\\ &\qquad =
+    F_g^N(\eta) N \bigg\langle
+        N c_\theta(x,\eta) \int_{\IR^d} (\hat g(y) - 1) q^m(x,dy,\eta)
+        +
+        \theta \mu_\theta(x,\eta) \left(\frac{1}{\hat g(x)} - 1\right)
+    , \eta(dx) \bigg\rangle  .
+\end{align*}
+This matches equation~\eqref{eqn:pgen_defn_again}, as desired,
+because $N c_\theta(x,\eta) q_m(x,dy,\eta) = \theta \gamma(x,\eta) q_\theta(x,dy)$.
+\end{proof}
 

### 2023-04-13 forwards-and-backwards.tex
second bit of appendix

@@
                    \big\langle
-                        \gamma(x, \smooth{\gamma} \eta(x))
+                        \gamma(x, \eta)
                             \mathcal{B}\left(
-                            f(\cdot) r(\cdot, \smooth{r} \eta(\cdot))
+                            f(\cdot) r(\cdot, \eta)
                             \right)(x)
                     +
-                    f(x)
-                        F(x, \smooth{F} \eta(x)),
+                    f(x) F(x, \eta),
                     \eta(dx)
@@
 
-For the limiting process,
-we now require test functions such that $g(x,u) = 1$ for all $u$ larger than some $u_0$;
-As before, recall that $\kappa(\lp)(\cdot) = \lim_{u \to \infty} \lp(\cdot \times [0, u)) / u$
-is the ``spatial projection operator'',
-and define the probability kernel $\Gamma : \measures \to \flpmeasures$
-so that for $\eta \in \measures$,
-defining $h(x) = \int_0^\infty (g(x, u) - 1) du$,
-\begin{align*}
-    F_g(\eta)
-    &:=
-    \int f(\lp) \Gamma(\eta, d\lp) \\
-    &=
-    \exp\left(
-        \big \langle
-            \int_0^\infty (g(x, u) - 1) du,
-            \eta(dx)
-        \big \rangle
-    \right) \\
-    &=
-    e^{ \langle h(x), \eta(dx) \rangle } .
-\end{align*}
-i.e., $\Gamma(\eta, \cdot)$ is the distribution of a conditionally Poisson process
-with intensity a product of $\eta$ and Lebesgue measure.
-It again follows from Lemma~\ref{def: MP definition of limit} that for test functions of this form
-\comment{(beware the different definition of $f$ to that lemma)}
-the generator of $\eta_t$ is
-\begin{align}
-    \Pgen^\infty F_g(\eta)
-    &=
-    F_g(\eta)
-    \left\langle
-        \gamma(x, \eta)
-        \DG( h(\cdot) r(\cdot) )(x)
-        + F(x, \eta) h(x)
-        + \alpha \gamma(x, \eta) r(x, \eta) h^2(x)
-        ,
-        \eta(dx)
-    \right\rangle .
-\end{align}
-The generator of $\lp_t$ is $A$, defined in equation~\eqref{eqn:limiting_lookdown_generator},
-
 \begin{lemma}
@@
 $$
-    \int f(\lp) \sum_{(x,u)\in\lp} \frac{h(x,u)}{g(x,u)} \Gamma^N(\eta,d\lp)
+    \int f(\lp) \sum_{(x,u)\in\lp} \frac{\ell(x,u)}{g(x,u)} \Gamma^N(\eta,d\lp)
     =
     F_g^N(\eta) \bigg\langle
-        \frac{1}{N \hat g(x)} \int_0^N h(x,u) du,
+        \frac{1}{N \hat g(x)} \int_0^N \ell(x,u) du,
         N \eta(dx)
@@
 because $N c_\theta(x,\eta) q_m(x,dy,\eta) = \theta \gamma(x,\eta) q_\theta(x,dy)$.
+\end{proof}
+
+For the limiting process,
+we now require test functions such that $g(x,u) = 1$ for all $u$ larger than some $u_0$;
+As before, recall that $\kappa(\lp)(\cdot) = \lim_{u \to \infty} \lp(\cdot \times [0, u)) / u$
+is the ``spatial projection operator'',
+and define the probability kernel $\Gamma : \measures \to \flpmeasures$
+so that for $\eta \in \measures$,
+defining $h(x) = \int_0^\infty (g(x, u) - 1) du$,
+\begin{align*}
+    F_g(\eta)
+    &:=
+    \int f(\lp) \Gamma(\eta, d\lp) \\
+    &=
+    \exp\left(
+        \big \langle
+            \int_0^\infty (g(x, u) - 1) du,
+            \eta(dx)
+        \big \rangle
+    \right) \\
+    &=
+    e^{ \langle h(x), \eta(dx) \rangle } .
+\end{align*}
+i.e., $\Gamma(\eta, \cdot)$ is the distribution of a conditionally Poisson process
+with intensity a product of $\eta$ and Lebesgue measure.
+It again follows from Lemma~\ref{def: MP definition of limit} that for test functions of this form
+\comment{(beware the different definition of $f$ to that lemma)}
+the generator of $\eta_t$ is
+\begin{align} \label{eqn:pgen_infty}
+    \Pgen^\infty F_g(\eta)
+    &=
+    F_g(\eta)
+    \left\langle
+        \gamma(x, \eta)
+        \DG( h(\cdot) r(\cdot) )(x)
+        + F(x, \eta) h(x)
+        + \alpha \gamma(x, \eta) r(x, \eta) h^2(x)
+        ,
+        \eta(dx)
+    \right\rangle .
+\end{align}
+The generator of $\lp_t$ is $A$, defined in equation~\eqref{eqn:limiting_lookdown_generator}.
+
+Before proving Lemma~\ref{lem:averaged_generators_limit},
+we recall an important equality for conditionally
+Poisson point processes (\cite{kurtz/rodrigues:2011} Lemma A.3).
+
+\begin{lemma} \label{lem:poisson_eqn}
+If $\lp = \sum_{i}\delta_{Z_i}$ is a Poisson random measure with mean measure $\nu$, 
+then for $\ell \in L^{1}(\nu)$ and $g\geq0$ with $\log g \in L^{1}(\nu)$,
+\begin{equation}
+\IE\left[\sum_{j} \ell(Z_j) \prod_{i}g(Z_i)\right] = \int \ell g d\nu e^{\int (g-1) d \nu}.
+\end{equation}
+\end{lemma}
+
+\begin{proof}[of Lemma~\ref{lem:averaged_generators_limit}]
+By Lemma~\ref{lem:poisson_eqn},
+$$
+    \int f(\lp) \sum_{(x,u)\in\lp} \frac{\ell(x,u)}{g(x,u)} \Gamma(\eta, \lp)
+    =
+    F_g(\eta) \bigg\langle \int_0^\infty \ell(x,u) du , \eta(dx) \bigg\rangle .
+$$
+Comparing this to the definition of $A$
+(equation~\eqref{eqn:limiting_lookdown_generator}),
+we see that
+\begin{align*}
+    \int Af(\lp) \Gamma(\eta,d\lp)
+    &=
+    F_g(\eta) \bigg\langle
+        \int_0^\infty
+        (\ell_1(x,u) + \ell_2(x,u) + \ell_3(x,u))
+        du, \eta(dx)
+    \bigg\rangle ,
+\end{align*}
+where
+\begin{align*}
+    \ell_1(x,u)
+    &=
+    \gamma(x,\eta)\left(
+        \DG(g(\cdot,u) r(\cdot,\eta))(x) - g(x,u) \DG r(x,\eta)
+    \right) \\
+    &=
+    \gamma(x,\eta)\left(
+        \DG((g(\cdot,u)-1) r(\cdot,\eta))(x) - (g(x,u)-1) \DG r(x,\eta)
+    \right)
+\end{align*}
+and
+\begin{align*}
+    \ell_2(x,u)
+    =
+    2 g(x,u) \alpha \gamma(x,\eta) r(x,\eta) \int_u^\infty(g(x,v) - 1)dv
+\end{align*}
+and
+\begin{align*}
+    \ell_3(x,u)
+    =
+    \left( \alpha \gamma(x,\eta)r(x,\eta)u^2 - \{\gamma(x,\eta)\DG r(x,\eta) + F(x,\eta)\} u \right)
+    \partial_u g(x,u) .
+\end{align*}
+
+First note that since $\DG$ acts on space, it commutes with the integral over levels, and so
+\begin{align*}
+    \int_0^\infty \ell_1(x,u) du
+    &=
+    \gamma(x,\eta)\left(
+        \DG(h(\cdot) r(\cdot,\eta))(x) - h(x) \DG r(x,\eta)
+    \right) ,
+\end{align*}
+since $h(x) = \int_0^\infty (g(x,u) - 1) du$.
+Next,
+\begin{align*}
+    \int_0^\infty \ell_2(x,u) du
+    &=
+    \alpha \gamma(x,\eta) r(x,\eta) 2\int_0^\infty g(x,u) \int_u^\infty (g(x,v)-1) dv du .
+\end{align*}
+Finally, integrating by parts,
+\begin{align*}
+    \int_0^\infty \ell_3(x,u) du
+    &=
+    - \alpha \gamma(x,\eta) r(x,\eta) \int_0^\infty 2u(g(x,u) - 1) du
+    \\ & \qquad {}
+    + \{ \gamma(x,\eta) \DG r(x,\eta) + F(x,\eta) \} h(x)
+\end{align*}
+Now, note that
+\begin{align*}
+&
+    \int_0^\infty g(x,u) \int_u^\infty (g(x,v)-1) dv du - \int_0^\infty u(g(x,u)-1)du
+\\ & \qquad =
+    \int_0^\infty g(x,u) \int_u^\infty (g(x,v)-1) dv du - \int_0^\infty \int_v^\infty (g(x,u) -1) du dv
+\\ & \qquad =
+    \int_0^\infty (g(x,u)-1) \int_u^\infty (g(x,v)-1) dv du
+\\ & \qquad =
+    h(x)^2/2 .
+\end{align*}
+
+Adding these together, we get that
+\begin{align*}
+    &
+    \int_0^\infty (\ell_1(x,u) + \ell_2(x,u) + \ell_3(x,u)) du
+    \\ &\qquad=
+    \gamma(x,\eta) \DG(h(\cdot)r(\cdot,\eta))(x)
+    + F(x,\eta) h(x) 
+    + \alpha \gamma(x,\eta) r(x,\eta) h(x)^2 ,
+\end{align*}
+which agrees with \eqref{eqn:pgen_infty}, as desired.
 \end{proof}

### 2023-04-13 forwards-and-backwards.tex
added MMT

@@
 Once this is verified (along with some boundedness conditions)
-the Markov Mapping Theorem \citep[Thm A.2 in][]{etheridge/kurtz:2019}
+the Markov Mapping Theorem (Theorem~\ref{thm:mmt}; also see \citep{etheridge/kurtz:2019})
 tells us that by ``removing labels'' from the lookdown process $\lp$
@@
     This proposition is the content of the Markov Mapping Theorem,
-    Theorem A.2 in \citet{etheridge/kurtz:2019},
+    reproduced from \citet{etheridge/kurtz:2019} as Theorem~\ref{thm:mmt},
     applied to our situation.
-    \comment{TODO: copy the MMT into our appendix and refer to it}
     In the notation of that theorem, $\gamma$ is what we have called $\kappa$ above,
@@
     a condition which we precisely state, and verify,
-    in Appendix~\ref{sec: Markov Mapping Theorem Application}.
+    in Lemmas~\ref{lem:averaged_generators} and~\ref{lem:averaged_generators_limit}
+    of the Appendix.
 
@@
     % however, this is a completely metrizable space
-    % \citep[see Condition 2.1 in][]{etheridge/kurtz:2018},
+    % \citep[see Condition 2.1 in][]{etheridge/kurtz:2019},
     % and our processes fall in this space (by conditional uniformity).
@@
 
-\comment{TODO copy in the MMT and refer to it earlier}
-
 % %% %% %% %% %% %% %% %% %% %% %% %% %% %% %% %% %%
 \section{Markov Mapping Theorem}
-
-\comment{TODO copy in the MMT and refer to it earlier}
+\label{apx:mmt}
+
+The following appears as Theorem A.2 in \citet{etheridge/kurtz:2019},
+specialized slightly to the case that the processes 
+are c\'adl\'ag and have no fixed points of discontinuity.
+For an $S_0$-valued, measurable process $Y$, $\hat{\mathcal{F}}^Y_t$
+denotes the completion of the $\sigma$-algebra generated by
+$Y(0)$ and $\{\int_0^r h(Y(s)) ds, r \le t, h \in B(S_0)\}$.
+Also, let $D_S[0,\infty)$ denote the space of c\`adl\`ag, $S$-valued functions
+with the Skorohod topology, and $M_S[0,\infty)$ the space of Borel measurable functions
+from $[0,\infty)$ to $S$,
+topologized by convergence in Lesbegue measure.
+For other definitions see \citet{etheridge/kurtz:2019}.
+
+\begin{theorem}[Markov Mapping Theorem] \label{thm:mmt}
+    Let $(S,d)$ and $(S_0,d_0)$ be complete, separable metric spaces.
+    Let $A \subset \bar C(S) \times C(S)$ and $\psi \in C(S)$, $\psi \ge 1$.
+    Suppose that for each $f \in \mathcal{D}(A)$ there exists $c_f$
+    such that
+    $$ |Af(x)| \le c_f \psi(x), \qquad x \in A, $$
+    and define $A_0 f(x) = Af(x) / \psi(x)$.
+
+    Suppose that $A_0$ is a countably determined pre-generator,
+    and suppose that $\mathcal{D}(A) = \mathcal{D}(A_0)$
+    is closed under multiplication and is separating.
+    Let $\gamma : S \to S_0$ be Borel measurable,
+    and let $\alpha$ be a transition function from $S_0$ into $S$
+    ($y \in S_0 \to \alpha(y,\cdot)\in\mathcal{P}(S)$ is Borel measurable)
+    satisfying $\int h\circ\gamma(x)\alpha(y,dx) = h(y)$ for $y \in S_0$ and $h \in B(S_0)$,
+    that is, $\alpha(y,\gamma^{-1}(y)) = 1$.
+    Assume that $\tilde \psi(y) \equiv \int_S \psi(z) \alpha(y,dz) < \infty$ for each $y \in S_0$
+    and define
+    $$  C = \{
+        \int_S f(z) \alpha(\cdot,dz),
+        \int_S Af(z) \alpha(\cdot,dz)
+        \; : \; f \in \mathcal{D}(A)
+    \} . $$
+    Let $\mu_0 \in \mathcal{P}(S_0)$ and define $\nu_0 = \int \alpha(y,\cdot) \mu_0(dy)$.
+    \begin{itemize}
+        \item[(a)]
+            If $\tilde Y$ satisfies $\int_0^t \IE[\tilde \psi(\tilde Y(s))]ds < \infty$
+            for all $t \ge 0$ and $\tilde Y$ is a solution of the martingale problem for $(C,\mu_0)$,
+            then there exists a solution $X$ of the martingale problem for $(A,\nu_0)$
+            such that $\tilde Y$ has the same distribution on $M_{S_0}[0,\infty)$
+            as $Y = \gamma \circ X$.
+            If $Y$ and $\tilde Y$ are c\'adl\'ag, then $Y$ and $\tilde Y$ have the same distribution
+            on $D_{S_0}[0,\infty)$.
+        \item[(b)]
+            For $t \ge 0$,
+            $$ \IP\{ X(t) \in \Gamma \;|\; \hat{\mathcal{F}}^Y_t \}
+            = \alpha(Y(t),\Gamma), \qquad \text{for } \Gamma \in \mathcal{B}(S).
+            $$
+        \item[(c)]
+            If, in addition, uniqueness holds for the martingale problem for $(A,\nu_0)$,
+            then uniqueness holds for the $M_{S_0}[0,\infty)$-martingale problem for $(C,\mu_0)$.
+            If $\tilde Y$ has sample paths in $D_{S_0}[0,\infty)$ then uniqueness holds for the
+            $D_{S_0}[0,\infty)$-martingale problem for $(C,\mu_0)$.
+        \item[(d)]
+            If uniqueness holds for the martingale problem for $(A,\nu_0)$
+            then $Y$ is a Markov process.
+    \end{itemize}
+\end{theorem}
+
+In our application, we have taken $S$ to be the space of locally finite counting measures
+on $\IR^d \times [0,N)$ or on $\IR^d \times [0,\infty)$,
+and $S_0$ the space of finite measures on $\bar \IR^d$.
+Then, $A$ corresponds to the generator for the lookdown process (i.e., either $A^N$ or $A$),
+and $C$ corresponds to the generator for the spatial population process
+(i.e., either $\Pgen^N$ or $\Pgen$).
+The ``$\gamma$'' of the theorem is our spatial projection operator
+that we have called $\kappa^N$ or $\kappa$,
+and the ``$\alpha$'' of the theorem will be named $\Gamma^N$ or $\Gamma$ below.
+Finally, ``$X$'' of the theorem is our lookdown process, $\lp$,
+and ``$Y$'' is our spatial process, $\eta$.
 
@@
 which agrees with \eqref{eqn:pgen_infty}, as desired.
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{OLDER STUFF Results on Lookdown Representations}
-    \label{sec: Markov Mapping Theorem Application}
-
-% % % % % % % % % % % % %
-\subsubsection{Convergence of generators for the lookdown process}
-    \label{sec:lookdown_generator_proofs}
-
-\comment{
-    I did this informal writeup of convergence of the lookdown generator
-    without looking at the previous version
-    mostly to double-check what we have there
-    (which is probably better).
-}
-
-In Definition~\ref{defn:lookdown_mgale} we saw that the generator
-of $(\lp_t)_{t \ge 0}$ is the sum of two parts,
-equations \eqref{eqn:birth_generator} and \eqref{eqn:level_generator}.
-Assume that there is a $u_*$ such that $g(x, u) = 1$ for all $u \ge u_*$.
-We consider these two in turn.
-
-First, the contribution from births is
-\begin{align*}
-\begin{split}
-f(\lp)
-&\mapsto
-    f(\lp)
-    \sum_{(x, u) \in \lp}
-    2 \gamma(x, \eta)
-    \bigg\{
-        \frac{1}{2 N}
-        \int_u^N
-        g(x, u_1) du_1
-        \frac{
-            \theta \int_{\IR^d} (g(y, u) - g(x, u)) r(y, \eta) q(x, dy)
-        }{
-            g(x, u)
-        }
-    \\ & \qquad \qquad \qquad {}
-        + \frac{\theta}{N}
-        \int_u^N \int_{\IR^d}
-        \left( \frac{g(y, u_1) + g(x, u_1)}{2} - 1 \right)
-        r(y, \eta) q(x, dy)
-    \bigg\}
-    .
-    \end{split}
-\end{align*}
-We have that
-\begin{align*}
-    &\theta \int_{\IR^d} (g(y, u) - g(x, u)) r(y, \eta) q(x, dy) \\
-    &\qquad =
-    \theta \int_{\IR^d} (r(y, \eta) g(y, u) - r(x, \eta) g(x, u)) q(x, dy)
-    - \theta \int_{\IR^d} g(x, u) (r(y, \eta) - r(x, \eta)) q(x, dy) \\
-    &\qquad \to
-    \DG(gr)(x) - g(x) \DG r(x) \qquad \text{as }N \to \infty.
-\end{align*}
-i.e., to
-$\DG\left(g(\cdot, u) r(\cdot, \smooth{r}\eta(\cdot))\right)(x)
-- g(\cdot, u) \DG\left(r(\cdot, \smooth{r}\eta(\cdot))\right)(x)$.
-Furthermore, by our assumption on $g$,
-$\int_u^N g(x, u_1) du_1 / N \to 1$ for all $x$ and $u$,
-so the first term here converges to
-\begin{align*}
-    \gamma(x, \eta)
-        \frac{
-            \DG\left( g(\cdot, u) r(\cdot, \smooth{r}\eta(\cdot))\right)(x)
-            -
-            g(\cdot, x) \DG\left( r(\cdot, \smooth{r}\eta(\cdot))\right)(x)
-        }{
-            g(x, u)
-        } .
-\end{align*}
-This corresponds to each particle moving according to the motion induced by
-$g \mapsto \gamma \DG(gr) - g \DG r$.
-\comment{TODO: explain the $r$-tilted $\DG$ motion somewhere earlier, introducing notation for it.}
-As for the second term,
-since $\int g(y, u_1) q(x, dy) \to g(x, u_1)$
-and $\theta/N \to \alpha$,
-it converges to
-\begin{align*}
-    2 \alpha
-    \gamma(x, \eta)
-    r(x, \eta) 
-    \int_u^\infty
-    \left( g(x, u_1) - 1 \right)
-    du_1
-\end{align*}
-This corresponds to births at higher levels at rate $2 \alpha \gamma r$.
-
-The remaining term is \eqref{eqn:level_generator}:
-\begin{align*}
-    f(\lp)
-    \mapsto
-    f(\lp)
-    \sum_{(x, u) \in \lp}
-    \left(
-    \theta
-        N^{-1} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
-        -
-        b(x, \eta)u
-    \right)
-    \frac{\partial_u g(x,u)}{g(x,u)} .
-\end{align*}
-The first part only uses the fact that $\theta/N \to \alpha$,
-while as noted in \eqref{eqn:b_limit}, $b$ converges to $\gamma \DG r + F$,
-so in total this term converges to
-\begin{align*}
-    f(\lp)
-    \mapsto
-    f(\lp)
-    \sum_{(x, u) \in \lp}
-    \left(
-    \alpha
-        \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
-        -
-        \left\{
-            \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta)
-        \right\} u
-    \right)
-    \frac{\partial_u g(x,u)}{g(x,u)} .
-\end{align*}
-In other words, the level of a particle at $x$ evolves according to
-\begin{align*}
-    \dot u
-    =
-    \alpha
-        \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q(x, dy) u^2
-        -
-        \left\{
-            \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta)
-        \right\} u .
-\end{align*}
-
-\subsection{Generators for the spatial processes}
-Before defining the generator of the lookdown representations, 
-we recall the generator of the spatial processes.
-
-We first define our pre-limit
-$(\eta^{N}(t))_{t>0}$ as a solution
-to a Martingale Problem
-with generator $\Pgen^{N}$.
-
-\begin{definition}
-    \label{def2: MP definition of pre-limit}
-Let $F \in \mathcal{C}^{2}(\IR)$ and $f \in \mathcal{C}_{0}(\IR^d)$.
-We define $\Pgen^N$ to be a generator
-acting on test functions of the form
-$F_f(\eta):=F (\langle f, \eta \rangle)$
-such that 
-\begin{equation}
-\begin{aligned}
-\Pgen^{N} F_f(\eta):=& \int_{\IR^d} \theta\gamma(x, \eta) \left\{\int_{\IR^d} \left\{F(\langle f, \eta \rangle + f(y)/N )-F(\langle f, \eta \rangle )\right\}r(y, \eta)q_{\theta}(x,dy)\right\}N\eta(dx)\\
-&+\int_{\IR^d} \theta \mu_\theta(x, \eta) \left\{F(\langle f, \eta \rangle - f(x)/N )-F(\langle f, \eta \rangle )\right\}N\eta(dx).
-\end{aligned}    
-\end{equation}
-In this case, our pre-limit model $(\eta^{N}(t))_{t \geq 0}$ is the solution to the Martingale Problem $(\Pgen^{N}, \eta_0)$, i.e. 
-for all $F \in \mathcal{C}^{2}(\IR)$
-and $f \in \mathcal{C}_{0}(\IR^d)$,
-$$M_t:=F_f(\eta^{N}_t)-F_f(\eta_0)
--\int_{0}^{t}\Pgen^{N}F_f(\eta^{N}_s)ds$$
-is a martingale, and the initial condition is distributed as a Poisson measure with mean measure $\eta_0$.
-\end{definition}
-
-\begin{remark}
-Taking $F(x)=x$ and $F(x)=x^2$, we can recover Equation \eqref{eqn:limiting_mgale_problem} and \eqref{eqn:limiting_mgale_variation} for the limit.
-Similarly, we can recover
-Definition \ref{defn:mgale_construction},
-an equivalent characterisation
-of our pre-limit model.
-\end{remark}
-
-We now write the candidate generator for the limiting object.
-
-\begin{definition}
-    \label{def2: MP definition of limit}
-Let $F \in \mathcal{C}^{2}(\IR)$ and $f \in \mathcal{C}_{0}(\IR^d)$.
-We define $\Pgen$ to be a generator
-acting on test functions of the form
-$F_f(\eta):=F (\langle f, \eta \rangle)$
-such that 
-\begin{equation}
-    \label{eq: Limit Generator Definition}
-\begin{aligned}
-\Pgen^{\infty} F_f(\eta):=& F'(\langle f, \eta \rangle)
-                   \times \left\{
-                   \big\langle
-                        \gamma(x, \smooth{\gamma} \eta(x))
-                            \mathcal{B}\left(
-                            f(\cdot) r(\cdot, \smooth{r} \eta(\cdot))
-                            \right)(x)
-                    +
-                    f(x)
-                        F(x, \smooth{F} \eta(x)),
-                        \eta(dx)
-                    \big\rangle
-                   \right\}\\
-                &+ \alpha F''(\langle f, \eta \rangle)
-                  \times \left\{
-                  \big\langle
-                    \gamma \left( x, \eta \right)
-                    r\left(x,\eta \right)
-                    f^2(x),
-                    \eta (dx)
-                    \big\rangle 
-                  \right\}.
-\end{aligned}    
-\end{equation}
-We define $(\eta^{\infty}(t))_{t \geq 0}$ to be the solution to the Martingale Problem $(\Pgen^{\infty}, \eta_0)$, i.e. 
-for all $F \in \mathcal{C}^{2}(\IR)$
-and $f \in \mathcal{C}_{0}(\IR^d)$,
-$$M_t:=F_f(\eta^{\infty}_t)-F_f(\eta_0)
--\int_{0}^{t}\Pgen^{\infty}F_f(\eta^{\infty}_s)ds$$
-is a martingale, with initial condition distributed as a Poisson measure with mean measure $\eta_0$.
-\end{definition}
-
-\subsubsection{Convergence of the Generators for the Spatial Models}
-
-\comment{This is a duplicate with Lemma~\ref{lem:limit_mgale}; compare and remove this one.}
-
-\begin{lemma}[Identifying the limit as a solution to the martingale problem]
-    \label{lem:limit_mgale2}
-As $N \to \infty$,
-$(\eta^{N}_t)_{t \geq 0}$ converges in $\mathcal{D}_{[0,\infty)}(\mathcal{M}_f(\IR^d))$
-to $(\eta^{N}(t))_{t \geq 0}$.
-\end{lemma}
-
-\begin{proof}[of Lemma~\ref{lem:limit_mgale2}
-We use Theorem 4.8.10 in \cite{EK}.
-First of all, the set of functions
-$\{F_f(\eta):= F(\langle f, \eta \rangle ),~
-F \in \mathcal{C}^{2}(\IR), ~
-f \in \mathcal{C}_{0}(\IR^d)\}$
-is a dense and convergence-determining 
-subset of functions in $\mathcal{M}_f(\IR^d)$.
-Therefore, it suffices to show that for any $t>0$,
-\begin{equation}
-    \label{eq: Convergence Condition}
-\lim_{N \to \infty}
-\mathbb{E}\left[
-\left(
-F_f(\eta^{N}_{t+\tau})-F_f(\eta^{N}_t)
--\int_{t}^{t+\tau}\Pgen^{\infty}F_f(\eta^{N}_s)ds
-\right)
-\prod_{i=1}^{k}\langle h_i,\eta^{N}_{t_i} \rangle
-\right]=0
-\end{equation}
-for all $k\geq 0$, $0\leq t_1<t_2<...,t_k \leq t < t+\tau$,
-and $h_1,...,h_k \in \mathcal{C}_{0}(\IR^d)$.
-
-To prove this,
-we make use of the Martingale Problem characterisation
-of $(\eta^{N}_t)_{t \geq 0}$.
-From Definition \ref{def: MP definition of pre-limit},
-we can apply Tower Law
-and obtain that
-\begin{equation}
-    \label{eq: Prelimit MP Application}
-\lim_{N \to \infty}
-\mathbb{E}\left[
-\left(
-F_f(\eta^{N}_{t+\tau})-F_f(\eta^{N}_t)
--\int_{t}^{t+\tau}\Pgen^{N}F_f(\eta^{N}_s)ds
-\right)
-\prod_{i=1}^{k}\langle h_i,\eta^{N}_{t_i} \rangle
-\right]=0
-\end{equation}
-for all $k\geq 0$, $0\leq t_1<t_2<...,t_k \leq t < t+\tau$,
-and $h_1,...,h_k \in \mathcal{C}_{0}(\IR^d)$.
-
-Therefore, it suffices to show that 
-\begin{equation}
-    \label{eq: Convergence of Spatial Generator}
-\lim_{N \to \infty}
-\mathbb{E}\left[
-\int_{t}^{t+\tau}
-\left|
-\Pgen^{N}F_f(\eta^{N}_s)
--\Pgen^{\infty}F_f(\eta^{N}_s)
-\right|
-ds
-\times 
-\prod_{i=1}^{k}\langle h_i,\eta^{N}_{t_i} \rangle
-\right]=0
-\end{equation}
-We apply Taylor Expansion
-around the term $F(\langle f, \eta \rangle )$
-up to third order.
-This gives
-\begin{equation}
-    \label{eq: Taylor Expansion calculations i}
-\begin{aligned}
-&F(\langle f, \eta \rangle + f(y)/N )-F(\langle f, \eta \rangle )\\
-=& F'(\langle f, \eta \rangle ) \frac{f(y)}{N}
-+\frac{1}{2}F''(\langle f, \eta \rangle ) \frac{f^2(y)}{N^2}
-+\frac{1}{6}F'''(w ) \frac{f^3(y)}{N^3}
-\end{aligned}
-\end{equation}
-for some $w \in [\langle f, \eta \rangle, \langle f, \eta \rangle+ ||f||/N]$.
-Similarly,
-\begin{equation}
-    \label{eq: Taylor Expansion calculations ii}
-\begin{aligned}
-&F(\langle f, \eta \rangle - f(x)/N )-F(\langle f, \eta \rangle )\\
-=& - F'(\langle f, \eta \rangle ) \frac{f(x)}{N}
-+\frac{1}{2}F''(\langle f, \eta \rangle ) \frac{f^2(x)}{N^2}
--\frac{1}{6}F'''(v ) \frac{f^3(x)}{N^3}
-\end{aligned}
-\end{equation}
-for some $v \in [\langle f, \eta \rangle - ||f||/N, \langle f, \eta \rangle ]$.
-
-We may now rewrite $\mathcal{P}^NF(\langle f, \eta \rangle)$ as 
-\small
-\begin{equation} 
-    \label{eq: Pre-Limit Generator Expanded}
-\begin{aligned}
-\Pgen^{N} F_f(\eta):=& F'(\langle f, \eta \rangle)\int_{\IR^d}  \theta\left\{\int_{\IR^d} \left\{f(y)\gamma(x, \eta) r(y,\eta) -f(x)\mu_\theta(x, \eta)\right\}q_{\theta}(x,dy)\right\}\eta(dx)\\
-&+\frac{1}{2}\frac{\theta}{N}F''(\langle f, \eta \rangle)\int_{\IR^d} 
- \left\{\gamma(x, \eta)\int_{\IR^d} \left\{f^2(y) r(y,\eta) \right\}q_{\theta}(x,dy)+f^2(x)\mu_\theta(x, \eta)\right\}\eta(dx)\\
-&+\frac{1}{6}\frac{\theta}{N^2}\int_{\IR^d}\left\{ 
-F'''(w) \left\{\gamma(x, \eta)\int_{\IR^d} f^3(y) r(y,\eta) q_{\theta}(x,dy)\right\}-F'''(v)f^3(x)\mu_\theta(x, \eta)\right\}\eta(dx)
-\end{aligned}    
-\end{equation}
-\normalsize
-for some $w,v \in [\langle f,\eta \rangle - ||f||/N, \langle f,\eta \rangle + ||f||/N]$.
-
-As $N\to \infty$, 
-$\theta/N \to \alpha$, 
-$\theta/N^2 \to 0$,
-and 
-$$\int_{\IR^d} f^m(y) r(y,\eta) q_{\theta}(x,dy) \to f^m(x)r(x, \eta)$$
-for $m=2,3$,
-the third term in Equation \eqref{eq: Pre-Limit Generator Expanded} vanishes
-while the second term converges to
-that of Equation \eqref{eq: Limit Generator Definition}.
-Furthermore,
-$\mu_\theta(x,\eta) = r(x,\eta)\gamma(x,\eta)-\frac{1}{\theta}F(x,\eta) \to r(x,\eta)\gamma(x,\eta),$
-so $f^2(x)\mu_\theta(x,\eta) \to r(x,\eta)\gamma(x,\eta) f^2(x)$.
-
-Finally, by Equation \eqref{mean measure},
-\eqref{eqn:rewritten mean measure}, \eqref{eqn:near_critical} and
-\eqref{limit of mean measure equation},
-we have 
-\begin{multline}
- \theta\left\{\int_{\IR^d} \left\{f(y)\gamma(x, \eta) r(y,\eta) -f(x)\mu_\theta(x, \eta)\right\}q_{\theta}(x,dy)\right\}
- \\
-\to \gamma(x, \eta)                           \mathcal{B}\left(
-                            f(\cdot) r(\cdot, \eta)
-                            \right)(x)
-                    +
-                    f(x)
-                        F(x, \eta),
-\end{multline}
-so comparing terms we have
-\begin{equation}
-\lim_{N\to \infty} |\mathcal{P}^{N}F\langle f, \eta \rangle - \mathcal{P}^{\infty}F\langle f, \eta \rangle| \to 0,   
-\end{equation}
-and so by Dominated Convergence Theorem,
-we establish Equation 
-\eqref{eq: Convergence of Spatial Generator}
-which concludes our proof.
-\end{proof}
-
-\subsubsection{Exact Statement on Markov Mapping Theorem results}
-
-\begin{theorem}
-\label{teo: lookdown on pre-limit well defined}
-For each $N \in \mathbb{N}$,
-there exists a solution $(\lp^N_t)_{t \geq 0}$ to the $(A^N, \lp^N_0)$ martingale problem.
-Furthermore, if we define $\Xi^N_t = \frac{1}{N}\lp^N_t(dx \times [0,N])$ for $t \geq 0$,
-then the pre-limiting model $(\eta^N_t(dx))_{t \geq 0}$ defined in Definition \ref{defn:mgale_construction}
-and $(\Xi^N_t(dx))_{t \geq 0}$
-shares the same distribution on $\mathcal{D}_{[0,\infty)}(\mathcal{M}(\mathbb{R}^d))$.
-
-Finally, 
-for all $h\in \mathcal{C}(\mathbb{R}^d \times [0, N])$
-\begin{equation}\label{Markov Mapping Theorem Cox Condition}
-\mathbb{E}\left[e^{-\int_{\mathbb{R}^d \times [0,N]} h(x,u) \xi^{N}(dx \times du)}\bigg| \mathcal{F}^{\Xi^{N}}_t\right]=e^{-\int F^{N}_h(x) \Xi^{N}_t(dx)},
-\end{equation}
-where 
-$$F^{\epsilon,\theta,N}_h(x):=-N\log \left(\frac{1}{N}\int_{0}^{N}e^{-h(x,u)}du\right)=-N\log \left(1-\frac{1}{N}\int_{0}^{N}(1-e^{-h(x,u)})du\right).$$
-In other words,
-conditioned on the spatial configuration $\Xi^N_t$,
-the levels of the particles must be i.i.d uniformly between $[0,N]$.
-
-\end{theorem}
-
-The statement for the limiting case is similar,
-with the only difference being the conditional distribution 
-of the levels given the spatial projection.
-
-\begin{theorem}
-\label{teo: lookdown on limit well defined}
-There exists a solution $(\lp_t)_{t \geq 0}$ to the $(A, \lp_0)$ martingale problem.
-
-Furthermore, if we define $\Xi_t = \lim_{u_0 \to \infty} \frac{1}{u_0}\lp_t(dx \times [0,u_0])$,
-then the limit model $(\eta_t(dx))_{t \geq 0}$ defined in Theorem \ref{thm:nonlocal_convergence}
-and $(\Xi_t(dx))_{t \geq 0}$
-shares the same distribution on $\mathcal{D}_{[0,\infty)}(\mathcal{M}(\mathbb{R}^d))$.
-
-Finally, 
-for all $h\in \mathcal{C}(\mathbb{R}^d)$ and for all $K>0$,
-\begin{equation}\label{Markov Mapping Theorem Cox Condition limit}
-\mathbb{E}\left[e^{-\int_{\mathbb{R}^d \times [0,K]} h(x) \xi(dx \times du)}\bigg| \mathcal{F}^{\Xi}_t\right]=e^{- K \int_{\mathbb{R^d}}(1-e^{h(x)}) \Xi_t(dx)}.
-\end{equation}
-In other words,
-conditionally on $(\Xi_s)_{0\leq s \leq t}$
-for each $s \in[0,t]$,
-$\xi_s$ is conditionally Poisson with Cox measure $\Xi_s(dx) \times du$.
-\end{theorem}
-
-\subsection{Markov Mapping Theorem Application on Generator $A^{N}$}\label{sec: Markov Mapping Theorem Application - Prelimit}
-
-We now introduce some notations to simplify our calculations.
-For a finite atomic measure $\xi=\sum \delta_{(x_i,u_i)} \in \mathcal{M}(\mathbb{R}^d \times [0,N])$,
-we introduce the test functions
- $$f_g(\xi)= \prod_{(x_i,u_i)\in \xi} g(x_i,u_i) = \exp (\langle \log g, \xi \rangle),$$
- where $g \in \mathcal{C}(\mathbb{R}^d \times [0,\infty))$ and $g(x,u)=1$ for all $u \geq N$.
-
- To avoid any ambiguities in the proofs,
- we will strictly use the notation $\Xi^N$  
-to represent the scaled push-forward measure of $\lp$,
-i.e. $\Xi^N := \frac{1}{N}\sum_{(x,u) \in \lp} \delta_x$,
-and only use $(\eta^N_t)_{t \geq 0}$
-to refer to the PDE solutions defined in Definition  \ref{defn:mgale_construction}.
-
-We also write $\textbf{x}=(x_1,x_2,...), \textbf{u}=(u_1,u_2,...)$ to be the collections of particles locations and levels respectively.
-With this notation we will write $f_g(\xi), f_g(\textbf{x},\textbf{u})$ interchangeably.
-
-We write $\Gamma^N (d\textbf{u})$ as the probability kernel
-that corresponds to assigning each particle an i.i.d. uniform $[0,N]$-level, i.e.
-$$\int f_g(\textbf{x},\textbf{u})\Gamma^N (d\textbf{u})=\frac{1}{N^{|\xi|}}\int_{[0,N]^{|\xi|}}f_g(\textbf{x},\textbf{u})d\textbf{u},$$
-and we denote
-$$\hat{g}(x):=\frac{1}{N}\int_{0}^{N}g(x,u)du,
- ~~\hat{f}_g(\xi)=\int f_g(\xi) \Gamma (d\textbf{u})$$ 
-to be the spatial test functions with averaged level.
-By independence of the levels of the particles,
- we have that
- \begin{align*}
-\hat{f}_g(\xi)
-=&\int \prod_{(x,u) \in \xi}g(x,u) \Gamma(d\textbf{u})\\
-=&\prod_{(x,u)\in \xi}\frac{1}{N}\int_{0}^{N} g(x,u) du\\
-=&\prod_{(x_i,u_i)\in \xi }\hat{g}(x_i)\\
-=& \exp(N\log \hat{g},\Xi^N).
- \end{align*}
-
-Furthermore,
-when expressed as a function of $\Xi^N$ explicitly,
-we use the notation $F_{\hat{g},N}(\Xi^N):=\hat{f}_g(\xi)$.
-
-We will now apply Markov Mapping Theorem
-while keeping notations consistent to that introduced in Section A.5 in \cite{kurtz/rodrigues:2011}
-with the aid of Table \ref{Markov Mapping Theorem Notation Table}.
-\begin{table}[!h]
-    \centering
-    \begin{tabular}{c|c}
-    Notation in \cite{kurtz/rodrigues:2011} & Notation in this proof \\
-    \hline\\
-      $S$   &  $\mathcal{M}(\IR^d \times [0, N])$\\\\
-       $S_0$  &  $\mathcal{M}(\IR^d)$\\\\
-       $A$ & $A^{N}$\\\\
-       $(X_t)_{t \geq 0}$ & $(\xi^N_t)_{t \geq 0}$\\\\
-       $\mu_0$ & $\eta^N_0 \in \mathcal{M}(\IR^d)$\\\\
-       $\nu_0$ & $\xi^N_0 \in \mathcal{M}(\IR^d \times [0,N])$\\\\
-       $f(\xi)$ & $f_g(\xi) := \prod_{(x,u) \in \xi} g(x,u)$\\\\
-        $\gamma_M$ & $ \mathcal{M}(\IR^d \times [0, N]) \ni \xi \to \frac{1}{N}\sum_{(x,u) \in \lp(\cdot, [0,N))} \delta_{x} \in \mathcal{M}(\IR^d)$\\\\
-       $\alpha_M$ & $ \alpha_M(\Xi^N,d \lp) =     \begin{cases}
-      0 & \text{if } \frac{1}{N}\sum_{(x,u) \in \lp(\cdot, [0,N))} \delta_x \neq \Xi^N\\
-       \prod_{(u_i,x_i) \in \nu} \frac{1}{N} \ind_{[0,N]}du_i & \text{if } \frac{1}{N}\sum_{(x,u) \in \lp(\cdot, [0,N))} \delta_x = \Xi^N,\\
-    \end{cases} $\\
-&      where $du_i$ is the standard Lebesgue measure.
-    \end{tabular}
-    \caption{Markov Mapping Theorem Correspondence}
-    \label{Markov Mapping Theorem Notation Table}
-\end{table}
-
-\begin{remark}
-Note that $\gamma,\alpha$ in \cite{kurtz/rodrigues:2011}
-is replaced with $\gamma_M,\alpha_M$ to avoid confusion with the $\gamma, \alpha$ used in previous sections.
-\end{remark}
-
-First of all,
-note that $\gamma_M$ is Borel-measurable
-and $\alpha_M$ is a transition function from $\mathcal{M}(\IR^d \times [0, N))$ to $\mathcal{M}(\IR^d)$.
-
-More importantly, we have the following simplified expression
-for an integral against $\alpha_M$:
-\begin{equation}
-\int_{\mathcal{M}(\IR^d\times [0,N])}A^{N}f(\xi)\alpha_M(\Xi^N, d\lp)
-= \int   A^Nf(\textbf{x},\textbf{u})\Gamma^N(d\textbf{u}). 
-\end{equation}
-
-As a result, we can establish that
-\begin{equation}
-\begin{aligned}
-\alpha_M(\Xi^N,\gamma^{-1}(\Xi^N)) 
-&= \int_{\lp \in \gamma^{-1}(y)}\alpha_M (\Xi^N, d\lp) \\
-&= \int_{\{\lp: \sum_{(x,u) \in \lp }\delta_x = N\Xi^N \} }\alpha_M (\Xi^N, d\lp)\\
-&= \prod_{x_i \in N\Xi^N}\frac{1}{N}\int_{0}^{N} du_i =1
-\end{aligned}
-\end{equation}
-With the simplified integral, it now suffices to show that the Martingale Problem 
-\begin{equation}\label{Markov Mapping Theorem Martingale Condition Simplified}
-C = \left\{\left(\int   f(\textbf{x},\textbf{u})\Gamma^N(d\textbf{u}),\int   A^Nf(\textbf{x},\textbf{u})\Gamma^N(d\textbf{u})\right)\right\}    
-\end{equation}
-has a solution.
-
-We now claim the following lemma.
-
-\begin{lemma}
-\label{lem: representation of lookdown generator - pre-limit}
-Let $\xi$ be a finite atomic measure on $\mathbb{R}^d \times [0,N]$.
-For test functions of the form 
-$$f_g(\xi)= \prod_{(x_i,u_i)\in \xi} g(x_i,u_i) = \exp (\langle \log g, \xi \rangle),$$
-we have the equality
-\begin{equation}
-\int   A^Nf(\textbf{x},\textbf{u})\Gamma^N(d\textbf{u})
-= \int \Pgen^N F_{\hat{g},N}(\Xi^N),
-\end{equation}
-where $\Pgen^N$ is the generator of the spatial process defined in Definition \ref{def2: MP definition of pre-limit}.
- \end{lemma}
-
-With lemma \ref{lem: representation of lookdown generator - pre-limit},
-the martingale problem can then be re-written as 
-\begin{equation}\label{Markov Mapping Theorem Martingale Condition, projection form}
-C = \left\{\left(\int F_{\hat{g},N}(\Xi^N), \int \Pgen^N F_{\hat{g},N}(\Xi^N)\right)\right\}    
-\end{equation}
-which has $(\eta^N_t)_{t \geq 0}$,
-our spatial population process,
-as a solution.
-
-As a result,
-we can apply Markov Mapping Theorem to establish the following statements:
-\begin{enumerate}
-    \item There exists a $\mathcal{M}_F(\mathbb{R}^d\times[0,N])$-valued process $(\lp^N_t)_{t \geq 0}$
-    such that 
-    $M^N_t:=    f(\xi^N_t)-   f(\xi^N_0)-\int_{0}^{t}  A^Nf(\xi^N_s)ds$ is a martingale for all $f\in D(A^N)$,
-    \item The process $(\gamma_M \circ \xi^N_t)_{t \geq 0}= \left(\Xi^N_t\right)_{t \geq 0}$ 
-    has the same distribution in $\mathcal{D}_{[0,\infty)}(\mathcal{M}(\mathbb{R}^d))$ as $(\eta^N_t)_{t \geq 0}$ defined in Definition \ref{def: MP definition of pre-limit}.
-    \item $\mathbb{P}\{\xi^N_t \in B | \mathcal{F}^{\Xi^N}_t\}=\alpha_M(\Xi^N(t),B), ~~~B \in \mathcal{B}(\mathcal{M}(\IR^d \times [0,N])).$
-\end{enumerate}
-Note that in particular,
-from the third statement,
-we can establish that for $h(x,u) \in \mathcal{C}_{c}(\mathbb{R}^d \times[0,N])$ and $h \geq 0$,
-
-\begin{equation}\label{Markov Mapping Theorem Cox Condition}
-\begin{aligned}
-\mathbb{E}\left[e^{-\int_{S \times [0,N]} h(x,u) \xi^{N}(dx \times du)}\bigg| \mathcal{F}^{\Xi^{N}}_t\right]
-&=\mathbb{E}\left[\prod_{(x,u)\in\xi^N_t}e^{-h(x,u)}\bigg| \mathcal{F}^{\Xi^{N}}_t\right]\\
-&=\prod_{x \in N\Xi^N_t} \frac{1}{N} \int_{0}^N. e^{-h(x_i,u_i)} du_i
-&= e^{-\langle F^N_h(x), \Xi^N(dx)\rangle},
-\end{aligned}
-\end{equation}
-where 
-$$F^{N}_h(x):=-N\log \left(\frac{1}{N}\int_{0}^{N}e^{-h(x,u)}du\right)=-N\log \left(1-\frac{1}{N}\int_{0}^{N}(1-e^{-h(x,u)})du\right).$$
-
-Therefore we only need to prove lemma \ref{lem: representation of lookdown generator - pre-limit}.
-The procedure to prove Lemman \ref{lem: representation of lookdown generator - pre-limit}
-is rather standard and set out in \cite{kurtz/rodrigues:2011},
-albeit we will face more technicalities for this setting.
-
-For tidy computations in this proof, 
-we recall the notation that an individual at $x$ gives birth at rate
-$$
-    \gamma^{\mathfrak{m}}_{\theta}(x,\eta) := \theta \gamma(x, \smooth{\gamma} \eta(x))
-    \int r(y, \smooth{r} \eta(y)) q_{\theta}(x, dy) ,
-$$
-and that offspring disperse according to the kernel
-$$
-    q_\theta^\mathfrak{m}(x,\eta,  dy)
-    :=
-    \frac{
-        r(y, \smooth{r} \eta(y)) q_\theta(x, dy)
-    }{
-        \int r(z, \smooth{r} \eta(z)) q_\theta(x, dz)
-    } .
-$$
-
-We will also write $\Xi, \Gamma$ instead of $\Xi^N, \Gamma^N$,
-bearing in mind the dependence of $\Xi, \Gamma$ on $N$.
-
-\begin{proof}[Proof to Lemma \ref{lem: representation of lookdown generator - pre-limit}]
-
-Recall that the lookdown generator of our spatial-level process satisfies
-\begin{align}
-A^Nf(\xi)=&
-f(\xi)\sum_{(x,u)\in\xi}2N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\times
-\int_u^{
-N}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\IR^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\theta}(x,\Xi ,dy) \nonumber \\
-& \qquad \qquad \qquad \qquad +\int_{\IR^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\theta}(x,\Xi,dy)\Bigg)dv_1 \nonumber\\
-&+f(\xi )\sum_{(x,u)\in\xi}\,\left(N^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)},
-\end{align}
-where $f(\xi) =\prod_{(x,u) \in \xi}g(x,u)$.
-
-For easier computation,
-we break the generator into three parts, 
-\begin{equation}
-\begin{aligned}
-A^N_1f(\xi)=&f(\xi)\sum_{(x,u)\in\xi}2N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\times
-\int_u^{
-N}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\IR^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\theta}(x,\Xi ,dy)\Bigg)dv_1,\\
-A^N_2f(\xi)=&f(\xi)\sum_{(x,u)\in\xi}2N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\times
-\int_u^{
-N}\Bigg(\frac{1}{2}\int_{\IR^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\theta}(x,\Xi,dy)\Bigg)dv_1,\\
-A^N_3f(\xi)=&f(\xi )\sum_{(x,u)\in\xi}\,\left(N^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)},
-\end{aligned}
-\end{equation}
-such that 
-$$A^Nf(\xi)=A^N_1f(\xi)+A^N_2f(\xi)+A^N_3f(\xi).$$
-
-We now calculate each generator evaluated under our probability kernel $\Gamma$.
-\footnotesize 
-\begin{align*}
-&\int A^N_1f(\xi) \Gamma(d\mathbf{u})\\ &=\int \Bigg\{f(\xi)\sum_{(x,u)\in\xi}2N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)
-\int_u^{
-N}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\IR^d}(g(y,u)-g(x,u))q^{\mathfrak{m}}_{\theta}(x,\Xi ,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
-&=\sum_{(x,u)\in\xi} \int \Bigg\{\frac{f(\xi)}{g(x,u)}2N^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi)
-\int_u^{
-N}\Bigg(\frac 12 g(x,v_1)\int_{\IR^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\theta}(x,\Xi ,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
-&=\sum_{(x,u)\in\xi}N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{N}\int_{0}^{N}\left\{
-\int_u^{
-N} g(x,v_1)dv_1\times \int_{\IR^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\theta}(x,\Xi ,dy)\right\}du\\
-&=\sum_{(x,u)\in\xi}N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{N}\int_{\IR^d} \left\{\int_{0}^{N}
-\int_u^{
-N} g(x,v_1) (g(y,u)-g(x,u))dv_1du\right\}q^{\mathfrak{m}}_{\theta}(x,\Xi ,dy)
-\end{align*}
-
-\normalsize
-For the second generator, we have
-\footnotesize
-\begin{align*}
-&\int A^N_2f(\xi) \Gamma(d\mathbf{u})\\&=\int \Bigg\{f(\xi)\sum_{(x,u)\in\xi}2N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\times
-\int_u^{
-N}\Bigg(\int_{\IR^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\theta}(x,\Xi,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
-&=\sum_{(x,u)\in\xi}N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\int \Bigg\{f(\xi)\times
-\int_u^{
-N}\Bigg(\int_{\IR^d}\left(g(y,v_1)+g(x,v_1)-2\right)q^{\mathfrak{m}}_{\theta}(x,\Xi,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
-&=\sum_{(x,u)\in\xi}N^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i) \frac{1}{N}\int_{\IR^d}\Bigg\{\int_{0}^{N}
-\int_u^{
-N}g(x,u) \left(g(y,v_1)+g(x,v_1)-2\right)dv_1 du\Bigg\} q^{\mathfrak{m}}_{\theta}(x,\Xi,dy).
-\end{align*}
-
-\normalsize
-For the third generator we have that 
-\begin{align*}
- &\int A^N_3f(\xi)\Gamma(d\mathbf{u})\\
- =&\int f(\xi )\,\left(N^{-1} \sum_{(x,u)\in\xi}\theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)}\Gamma(d\mathbf{u}) \\
- =&\sum_{(x,u)\in\xi}\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{N}\int_{0}^{N}  \left(N^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\partial_u g(x,u)du \\
- =&-\sum_{(x,u)\in\xi}\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{N}\int_{0}^{N}  \left(2uN^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) -b_{\theta}(x,\Xi)\right)\left(g(x,u)-1\right)du \\
- =&-\sum_{(x,u)\in\xi}N^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{N}\int_{0}^{N}   2ug(x,u)du \\
- &+\sum_{(x,u)\in\xi}N^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{N}\times N^2+\sum_{(x,u)\in\xi}\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)b_{\theta}(x,\Xi)(\hat{g}(x)-1)
-\end{align*}
-
-By symmetry, we have
-\begin{align*}
-&\int_{0}^{N}
-\int_u^{
-N} g(x,v_1) (g(y,u)-g(x,u))dv_1du+\int_{0}^{N}
-\int_u^{
-N}g(x,u) \left(g(y,v_1)+g(x,v_1)-2\right)dv_1 du
-\\&= \int_{0}^{N}
-\int_u^{
-N}g(x,u)g(y,v_1)+g(y,u)g(x,v_1)-2g(x,u) dv_1 du\\
-&=\frac{1}{2}\int_{0}^{N}\int_{0}^{N}g(x,u)g(y,v_1)+g(y,u)g(x,v_1)dv_1 du - 2 \int_{0}^{N}(N-u)g(x,u)du\\
-&=N^2 \hat{g}(x)\hat{g}(y) -2N^2 \hat{g}(x)+2\int_{0}^{N}ug(x,u)du.
-\end{align*}
-
-Combining the last equations,
-we have 
-\begin{align*}
-&\int \Bigg(A^N_1f(\xi)+A^N_2f(\xi)+A^N_3f(\xi)\Bigg)\Gamma(d\mathbf{u})\\
-=&  \sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)}\hat{g}(x_i) \left( \int_{\IR^n} \hat{g}(y) q^{\mathfrak{m}}_{\theta}(x,\Xi,dy) - 2+\frac{1}{\hat{g}(x)}\right)\\
-&+\sum_{(x,u) \in \xi } \prod_{(x_i,u_i)}\hat{g}(x_i)b_{\theta}(x,\Xi)\left(1-\frac{1}{\hat{g}(x)}\right)\\
-=&  \hat{f}(\xi)\sum_{(x,u)\in\xi}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi) \left(\int_{\IR^n} \hat{g}(y) q^{\mathfrak{m}}_{\theta}(x,\Xi,dy) -1\right)\\
-&+\hat{f}(\xi)\sum_{(x,u) \in \xi } (b_{\theta}(x,\Xi)-\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi))\left(1-\frac{1}{\hat{g}(x)}\right)\\
-=&  F_{\hat{g},N}(\Xi^N)\sum_{x \in \Xi}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi) \left(\int_{\IR^n} \hat{g}(y) q^{\mathfrak{m}}_{\theta}(x,\Xi,dy) -1\right) \\
-&-F_{\hat{g},N}(\Xi^N)\sum_{x \in \Xi } \theta \mu_{\epsilon,\theta}(x,\Xi)\left(1-\frac{1}{\hat{g}(x)}\right)\\
-=& \Pgen^N F_{\hat{g},N}(\Xi^N).
-\end{align*}
-
-The last equality holds
-as the second last expression corresponds to a spatial-branching process
-that branches at rate $\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)$,
-leaving offspring around with kernel $ q^{\mathfrak{m}}_{\theta}(x,\Xi,dy)$,
-with each particle having death rate given by $\theta \mu_{\epsilon,\theta}(x,\Xi)$.
-This is precisely the martingale problem in Definition \ref{def: MP definition of pre-limit}.
-
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%
-\subsection{Markov Mapping Theorem Application on Generator $A$}\label{sec: Markov Mapping Theorem application - limit}
-
-Now,
-we turn to the generator for the limiting case,
-which has the form
-    \begin{equation}
-    \begin{aligned}
-    A f(\lp)
-    =&
-        f(\lp)  \sum_{(x, u) \in \xi}
-        \gamma(x, \eta)
-            \frac{
-                \DG(g(\cdot, u) r(\cdot, \eta))(x) - g(x,u) \DG r(x,\eta)
-            }{
-                g(x, u)
-            }
-    \\ &+
-        f(\lp) \sum_{(x, u) \in \xi}
-        2 \alpha \gamma(x, \Xi) r(x, \Xi ) \int_u^\infty (g(x, u_1) - 1) du_1
-    \\ &+
-        f(\lp) \sum_{(x, u) \in \xi}
-        \left(
-            \alpha \gamma(x, \Xi) r(x, \Xi ) u^2
-            -
-            \left\{
-                \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta)
-            \right\} u
-        \right)
-        \frac{\partial_u g(x, u)}{ g(x,u) }  .
-    \end{aligned}
-    \end{equation}
-
-To apply Markov Mapping Theorem,
-we consider Table \ref{Markov Mapping Theorem Notation Table Limit}.
-
-\begin{table}[!h]
-    \centering
-    \begin{tabular}{c|c}
-    Notation in \cite{kurtz/rodrigues:2011} & Notation in this proof \\
-    \hline\\
-      $S$   &  $\mathcal{M}(\IR^d \times [0, \infty])$\\\\
-       $S_0$  &  $\mathcal{M}(\IR^d)$\\\\
-       $A$ & $A$\\\\
-       $(X_t)_{t \geq 0}$ & $(\xi_t)_{t \geq 0}$\\\\
-       $\mu_0$ & $\xi_0 \in \mathcal{M}(\IR^d)$\\\\
-       $\nu_0$ & $\xi_0 \in \mathcal{M}(\IR^d \times [0,\infty])$\\\\
-       $f(\xi)$ & $f_g(\xi) := \prod_{(x,u) \in \xi} g(x,u)$\\\\
-        $\gamma_M$ & $ \mathcal{M}(\IR^d \times [0, \infty]) \ni \xi \to \lim_{u_0 \to \infty}\frac{1}{u_0}\sum_{(x,u) \in \lp(\cdot, [0,u_0))} \delta_{x} \in \mathcal{M}(\IR^d)$\\\\
-       $\alpha_M$ & $ \Gamma^M(\Xi,d \lp) \sim PP(\Xi(dx)\times \Lambda(du)) ~~ \text{if } \gamma_M(\xi)=\Xi$,\\
-       &      where $\Lambda(du)$ is the standard Lebesgue measure on $[0,\infty)$.
-    \end{tabular}
-    \caption{Markov Mapping Theorem Correspondence}
-    \label{Markov Mapping Theorem Notation Table Limit}
-\end{table}
-
-Once again,
-we need to find solutions to the Martingale Problem 
-\begin{equation}
-C = \left(\int f_g(\xi) \Gamma^M(\cdot, d\xi), \int Af_g(\xi) \Gamma^M(\cdot, d\xi))\right),
-\end{equation}
-where $\Gamma^M(\Xi, d\lp)$ is the law of $\xi$,
-which is conditionally Poisson with Cox measure $\Xi(dx) \times \Lambda(du)$.
-
-Since we impose that $\xi$ is conditionally Poisson with Cox measure $\Xi(dx) \times \Lambda(du)$,
-for any test function $l(x,u) > 0$,
-\begin{equation}
-\mathbb{E}\left[e^{-\int_{\mathbb{R}^d \times [0,\infty]} l(x,u) \xi(dx,du)}\big| \Xi \right] = e^{-\int_{\mathbb{R}^d} \int_{0}^{\infty} (1-e^{-l(x,u)}) du \Xi(dx)}.
-\end{equation}
-
-Note that 
-$\prod_{(x,u) \in \xi} g(x,u) = e^{-\int_{\mathbb{R}^d \times [0,\infty]} -\log g(x,u) \xi(dx,du)},$
-so taking $l(x,u)= -\log g(x,u)$ and $h(x,u)= \int_{0}^{\infty} (1 -g(x,u))du$,
-we have the equation
-\begin{equation}
-\begin{aligned}
-\int f_g(\xi) \alpha_M(\Xi, d\xi) 
-=&  e^{-\int_{\mathbb{R}^d} \int_{0}^{\infty} (1-e^{-l(x,u)}) du \Xi(dx)}\\
-=&  e^{-\int_{\mathbb{R}^d} \int_{0}^{\infty} (1-g(x,u)) du \Xi(dx)}\\
-=& \exp(\langle -h(x), \Xi(dx)\rangle),
-\end{aligned}
-\end{equation}
-and we will denote the last term as $\mathcal{E}_{-h}(\Xi)$.
-Note that this notation is consistent to the test function
-$F_f(\eta)$ laid out in \ref{def: MP definition of limit},
-if we take $F(\cdot)=\mathcal{E}(\cdot) := \exp(\cdot)$ and $f=-h$.
-
-We now state the crucial lemma that allows us to apply Markov Mapping Theorem.
-\begin{lemma}
-\label{lem: MMT for limit}
-Let $\lp$ be a finite measure on $\mathbb{R}^d \times [0,\infty)$,
-$\Xi$ be a finite measure on $\mathbb{R}^d$,
-and $\Lambda(dx)$ be the Lesbesgue measure on  $[0,\infty)$.
-
-We consider test functions 
-$f(\xi):= \prod_{(x_i,u_i) \in \xi} g(x_i,u_i)$
-with $g \in C^2_{0}(\mathbb{R}^d \times[0,\infty))$
-and for which there exists $u_0$ with 
-$g(x,u)=1$ for all $u>u_0$.
-Furthermore, we define 
-$h(x,u)= \int_{0}^{\infty} (1 -g(x,u))du$
-and $\mathcal{E}_{-h}(\Xi)= \exp(\langle -h(x), \Xi(dx)\rangle)$.
-
-We write $\Gamma^{\Xi}(d\lp)$ to be the law
-on $\mathcal{M}(\mathbb{R}^d \times[0,\infty))$ 
-for a conditionally Poisson random measure $\lp$
-on $\IR^d\times [0,\infty)$
-with Cox measure $\Xi(dx)\times \Lambda(du)$.
-
-Then,
-for generator $A$ defined in Equation \eqref{eqn:limiting_lookdown_generator},
-\begin{equation}
-\int Af(\lp) \Gamma^{\Xi}(d\lp) = \Pgen \mathcal{E}_{-h}(\Xi),
-\end{equation}
-where $\Pgen$ is defined in Definition \ref{def2: MP definition of limit}.
-\end{lemma}
-
-Given the above lemma, 
-the following three statements hold true.
-\begin{enumerate}
-    \item There exists a $\mathcal{M}_F(\mathbb{R}^d\times[0,\infty])$-valued process $(\lp_t)_{t \geq 0}$
-    such that 
-    $M_t:=    f(\xi_t)-   f(\xi_0)-\int_{0}^{t}  Af(\xi_s)ds$ is a martingale for all $f\in D(A)$,
-    \item The process $(\gamma_M \circ \xi_t)_{t \geq 0}= \left( \lim_{u_0 \to \infty}\frac{1}{u_0}\sum_{(x,u) \in \lp_t(\cdot, [0,u_0))} \delta_{x} \right)_{t \geq 0}$ 
-    has the same distribution in $\mathcal{D}_{\mathcal{M}(\mathbb{R}^d)}[0,\infty)$ as $(\eta_t)_{t \geq 0}$ defined in Definition \ref{def: MP definition of limit}.
-    \item $\mathbb{P}\{\xi_t \in B | \mathcal{F}^{\Xi_t}\}=\Gamma^{\Xi_t}(B), ~~~B \in \mathcal{B}(\mathcal{M}(\IR^d \times [0,\infty])).$
-\end{enumerate}
-
-Finally,
-we recall an important equality for conditionally Poisson point processes (\cite{kurtz/rodrigues:2011} Lemma A.3.)
-which will be used extensively in the upcoming proof.
-
-\begin{lemma}
-Let $\lp =\sum_{i}\delta_{Z_i}$ be a Poisson random measure with mean measure $\nu$, 
-then for $\ell \in L^{1}(\nu)$ and $g\geq0$ with $\log g \in L^{1}(\nu)$,
-\begin{equation}
-\mathbb{E}[\sum_{j} \ell(Z_j) \prod_{i}g(Z_i)] = \int \ell g d\nu e^{\int (g-1) d \nu}.
-\end{equation}
-\end{lemma}
-
-In particular,
-taking $\nu(dx,du)=\Xi(dx) \times \Lambda(du)$,
-we have the equation 
-\begin{equation}
-\label{eq: cond_poi_sum_prod}
-\begin{aligned}
-\int f(\xi) \sum_{(x,u)\in \xi} \ell(x,u)\Gamma^{\Xi}(d\xi)
-=& \mathbb{E}_{\xi \sim PP(\Xi \times \Lambda)}\left[\sum_{(x_j,u_j)\in \xi} \ell(x_j,u_j) \prod_{(x_i,u_i) \in \xi}g(x_i,u_i)\right]\\
- =& \left \langle \int_{0}^{\infty} \ell(x,u) g(x,u) du ,\Xi(dx) \right\rangle \exp(\langle -h(x), \Xi(dx) \rangle) \\
- =& \left \langle \int_{0}^{\infty} \ell(x,u) g(x,u) du ,\Xi(dx) \right\rangle \mathcal{E}_{-h}(\Xi)
-\end{aligned}
-\end{equation}
-where $h(x)=\int_{0}^{\infty}(1-g(x,u))du$.
-
-We are now ready to prove Lemma \ref{lem: MMT for limit}.
-
-\begin{proof}[Proof to Lemma \ref{lem: MMT for limit}]
-We write
-$$ Af(\xi)=A_1f(\xi)+A_2f(\xi)+A_3f(\xi),$$
-where the first term is
-\begin{equation}
-\begin{aligned}
-A_1f(\xi) =&
-        f(\lp)  \sum_{(x, u) \in \xi}
-             \frac{
-            	\gamma(x, \Xi)
-                \left(\DG(g(\cdot, u) r(\cdot, \Xi))(x) - g(x,u) \DG r(x,\Xi)\right)
-            }{
-                g(x, u)
-            }\\
-            = & f(\lp)  \sum_{(x, u) \in \xi} \frac{\ell_1(x,u)}{g(x,u)},
-\end{aligned}    
-\end{equation}
-the second term is
-\begin{equation}
-\begin{aligned}
-A_2f(\xi)  = &
-  f(\lp) \sum_{(x, u) \in \xi}
-        2 \alpha \gamma(x, \Xi) r(x, \Xi ) \int_u^\infty (g(x, u_1) - 1) du_1\\
-         =&  f(\lp)  \sum_{(x, u) \in \xi} \ell_2(x,u),
-\end{aligned}    
-\end{equation}
-and the final term satisfies
-\begin{equation}
-\begin{aligned}
-A_3f(\xi)  =&f(\lp) \sum_{(x, u) \in \xi}
-                \frac{\left(
-            \alpha \gamma(x, \Xi) r(x, \Xi ) u^2
-            -
-            \left\{
-                \gamma(x, \Xi) \DG r(x, \Xi) + F(x, \Xi)
-            \right\} u
-        \right)
-        \partial_u g(x, u)}{ g(x,u) }\\
-        =& f(\lp) \sum_{(x, u) \in \xi} \frac{\ell_3(x,u)}{g(x,u)}  .
-\end{aligned}    
-\end{equation}
-
-Applying Equation \eqref{eq: cond_poi_sum_prod}
-to the above expressions give 
-\begin{equation}
-\int Af(\xi)\Gamma^{\Xi}(d\xi)
-= \left \langle \int_{0}^{\infty}\left(\ell_1(x,u) + \ell_2(x,u) g(x,u) + \ell_3(x,u)\right)du ,\Xi(dx) \right\rangle \mathcal{E}_{-h}(\Xi)
-\end{equation}
-
-First of all, 
-the operator $\DG$ acts on space while the integral is over levels,
-so we can commute the two operators to obtain
-\begin{equation}
-\begin{aligned}
-\int_{0}^{\infty} \ell_1(x,u) du 
-=& \int_{0}^{\infty} \gamma(x, \Xi)( \DG((g(\cdot, u)-1) r(\cdot, \Xi))(x) - (g(x,u)-1) \DG r(x,\Xi))  du \\
-=& \gamma(x, \Xi)\left\{ \DG\left(\int_{0}^{\infty} (g(\cdot, u)-1)du \times r(\cdot, \Xi)\right)(x) - \int_{0}^{\infty} (g(x,u)-1)du \DG r(x,\Xi)\right\} \\
-=& -\gamma(x, \Xi)\{ \DG(h(\cdot) r(\cdot, \Xi))(x) - h(x) \DG r(x,\Xi)\},
-\end{aligned}
-\end{equation}
-as $h(x,u)= \int_{0}^{\infty} (1 -g(x,u))du$.
-
-Similarly,
-\begin{equation}
-\begin{aligned}
-\int_{0}^{\infty} \ell_2(x,u)g(x,u) du
-=&  \alpha\gamma(x, \Xi) r(x, \Xi ) \times 2 \int_{0}^{\infty} g(x,u)  \int_u^\infty (g(x, u_1) - 1) du_1  du\\
-=&  \alpha\gamma(x, \Xi) r(x, \Xi ) \times I_1.
-\end{aligned}
-\end{equation}
-
-Finally,
-integrating $\ell_3$ by parts, 
-we have
-\begin{equation}
-\begin{aligned}
-\int_{0}^{\infty} \ell_3(x,u)du
-=& \int_{0}^{\infty} \left(
-            \alpha \gamma(x, \Xi) r(x, \Xi ) u^2
-            -
-            \left\{
-                \gamma(x, \Xi) \DG r(x, \Xi) + F(x, \Xi)
-            \right\} u
-        \right)
-        \partial_u g(x, u) du\\
-=& - \alpha\gamma(x, \Xi) r(x, \Xi ) \int_{0}^{\infty} 2u (g(x, u)-1) du\\
-  &+ \left\{\gamma(x, \Xi) \DG r(x, \Xi) + F(x, \Xi) \right\} \int_{0}^{\infty}(g(x,u)-1) du\\
-  =&  - \alpha \gamma(x, \Xi) r(x, \Xi ) I_2 - \left\{\gamma(x, \Xi) \DG r(x, \Xi) + F(x, \Xi) \right\} h(x).
-\end{aligned}
-\end{equation}
-
-Note that $I_1-I_2$ satisfies
-\begin{equation}
-\begin{aligned}
-I_1-I_2 
-=& 2 \int_{0}^{\infty} g(x,u)  \int_u^\infty (g(x, u_1) - 1) du_1  du - 2 \int_{0}^{\infty} u (g(x, u)-1) du\\
-=& 2 \int_{0}^{\infty} g(x,u)  \int_u^\infty (g(x, u_1) - 1) du_1  du - 2 \int_{0}^{\infty} (g(x, u)-1) \int_{0}^{u}dv  du\\
-=& 2 \int_{0}^{\infty} g(x,v)  \int_v^\infty (g(x, u) - 1) du  dv - 2 \int_{0}^{\infty} \int_{v}^{\infty}(g(x, u)-1)  dudv\\
-=& 2 \int_{0}^{\infty} (g(x,v)-1)  \int_v^\infty (g(x, u) - 1) du  dv \\
-=& h^2(x)
-\end{aligned}
-\end{equation}
-
-Combining all the Equations above, 
-we have 
-\begin{equation}
-\begin{aligned}
-& \int_{0}^{\infty}\left(\ell_1(x,u) + \ell_2(x,u) g(x,u) + \ell_3(x,u)\right)du \\
-=& -\gamma(x, \Xi)\DG(h(\cdot) r(\cdot, \Xi))(x) + \gamma(x, \Xi) h(x) \DG r(x,\Xi) -  \gamma(x, \Xi) \DG r(x, \Xi)h(x) - F(x, \Xi)  h(x) \\
-& +\alpha\gamma(x, \Xi) r(x, \Xi )(I_1-I_2)\\
-=&\alpha \gamma(x, \Xi) r(x, \Xi ) h^2(x) -\gamma(x, \Xi)\DG(h(\cdot) r(\cdot, \Xi))(x)  - F(x, \Xi)  h(x).
-\end{aligned}
-\end{equation}
-
-To conclude, 
-\begin{equation}
-\begin{aligned}
-&\int Af(\xi)\Gamma^{\Xi}(d\xi)\\
-= & \left(\alpha \gamma(x, \Xi) r(x, \Xi ) h^2(x) -\gamma(x, \Xi)\DG(h(\cdot) r(\cdot, \Xi))(x)  - F(x, \Xi)  h(x)\right)\mathcal{E}_{-h}(\Xi)\\
-= & \left(\gamma(x, \Xi)\DG(-h(\cdot) r(\cdot, \Xi))(x)  + F(x, \Xi)  (-h(x))\right)\mathcal{E}'(\langle -h, \Xi \rangle )\\
-   &+ \left(\alpha \gamma(x, \Xi) r(x, \Xi ) h^2(x) \right)\mathcal{E}''(\langle -h, \Xi \rangle )\\
-=& \Pgen \mathcal{E}_{-h}(\Xi),
-\end{aligned}
-\end{equation}
-so we have established our equality. 
 \end{proof}

### 2023-04-14 forwards-and-backwards.tex
numbering
one more fig

@@
 \newcommand{\comment}[1]{{\color{blue} \it #1}}
+
+\numberwithin{equation}{section}
 
@@
 with certain parameter combinations, the population spontaneously forms a regular grid
-of more or less dicrete patches, separated by areas with nearly no individuals.
+of more or less dicrete patches, separated by areas with nearly no individuals,
+as shown in Figure~\ref{fig:clumping}.
 The phenomenon is discussed in Section~16.10 of \citet{haller2022evolutionary},
@@
         \includegraphics[width=0.45\textwidth]{figures/clumpy_2d/clumpy_123.density.3.0}
-        \comment{TODO} FIGURE
+        \includegraphics[width=0.45\textwidth]{figures/clumpy_1d/clumpy_123.steps}
     \end{center}
     \caption{
-        Two panels: left is 2D picture of clumped population;
-        right is a bumpy expanding wavefront.
+        \textbf{Left:} A snapshot of individual locations in a two-dimensional simulation
+        in which the constant density is unstable
+        and a stable, periodic pattern forms.
+        \textbf{Right:} Population density in an expanding wave in a one-dimensional simulation
+        forming a period pattern;
+        each panel shows the wave front in three periods of time;
+        within each period of time the wave front at earlier times is shown in blue
+        and later times in pink.
+        In both cases, $\gamma(m) = 3/(1 + m)$, $\mu \equiv 0.3$, and $r \equiv 1$;
+        dispersal is Gaussian with $\sigma=0.2$ and density is measured with $\rho_\gamma(x) = p_9(x)$,
+        i.e., using a Gaussian kernel with standard deviation 3.
         \label{fig:clumping}
@@
 % that follows by application of Dynkin's formula.
-
-\comment{TODO: the previous definition of $\Pgen^N$ was the following wrong thing; fixup below}
-\begin{equation}
-\begin{aligned}
-    \text{ONLY RIGHT TO $O(1/N)$} \qquad
-    \Pgen^N G_f(\eta)
-    &:=
-    G'(\langle f, \eta \rangle)
-        \theta \bigg\langle
-        \gamma(x, \eta)
-            \int f(z) r(z,\eta) q_\theta(x,dz)
-        -
-        f(x)\mu_\theta(x, \eta),
-        \eta(dx) \bigg\rangle
-    \\&\qquad {}
-    + \frac{1}{2} G''(\langle f, \eta \rangle)
-    \frac{\theta}{N}
-    \bigg\langle
-        \gamma(x, \eta) \int f^2(y) r(y, \eta) q_\theta(x, dy) + f^2(x) \mu_\theta(x, \eta),
-    \eta(dx) \bigg\rangle .
-\end{aligned}
-\end{equation}
 

### 2023-04-14 figures/make_plots.sh

@@ -60,6 +60,6 @@ if [ ! -e ${MODEL}_123.trees ]
 then
     slim -s 123 ../${MODEL}.slim
     ../lineage_plotting/plot_density.py ${MODEL}_123.trees 3 pdf 3 0.0
-    ../plot_wave.py ${MODEL}_123.trees 100 600 12
+    ../plot_wave.py ${MODEL}_123.trees
 fi
 popd

### 2023-04-14 figures/plot_wave.py

@@ -22,28 +22,23 @@ treefile = sys.argv[1]
 assert treefile[-6:] == ".trees"
 outbase = treefile[:-6]
 
-input_times = (len(sys.argv) > 2)
-
-if input_times:
-    start_time = float(sys.argv[2])
-    end_time = float(sys.argv[3])
-    num_steps = int(sys.argv[4])
-
 ts = tskit.load(treefile)
 params = ts.metadata['SLiM']['user_metadata']
 for n in params:
     if len(params[n]) == 1:
         params[n] = params[n][0]
 
-
 dx = 0.8
 T = params['RUNTIME']
 dt = params["DT"]
-max_gen = ts.metadata["SLiM"]["tick"] - 1
+max_gen = ts.metadata["SLiM"]["tick"]
 y_bins = [0, params['HEIGHT']]
 x_bins = np.arange(0, params['WIDTH'] + dx, dx)
 x_mids = x_bins[1:] - np.diff(x_bins)/2
 t_bins = np.arange(0, max_gen + 1)
+
+input_ticks = np.array(params['REMEMBER_TIMES'] + [max_gen])
+output_ticks = max_gen - input_ticks
 
 # Population sizes for each time step within each x bin
 popsize = pyslim.population_size(ts, x_bins, y_bins, t_bins)
@@ -53,23 +48,29 @@ uhat = np.sum(popsize, axis=1) / (params["K"] * dx)
 assert uhat.shape[0] == len(x_bins) - 1
 assert uhat.shape[1] == len(t_bins) - 1
 
-def plot_times(ax, times):
+def plot_ticks(ax, ticks, legend=True, xlab=True, **kwargs):
+    times = (max_gen - ticks) * dt
     cm = matplotlib.cm.cool
-    steps = np.searchsorted(t_bins, max_gen - times / dt) - 1
-    legend_steps = list(range(0, len(steps) + 1, int((len(steps) + 1) / 4)))
-    for m, (j, t) in enumerate(zip(steps, times)):
-        ax.plot(x_mids, uhat[:, j], c=cm(m / len(steps)),
-                label=f"t={t:0.2f}" if m in legend_steps else None)
-    ax.set_title(f"{min(times)} < t < {max(times)}")
-    ax.set_xlabel("location")
+    legend_ticks = list(range(0, len(ticks) + 1, int((len(ticks) + 1) / 4)))
+    for m, (j, t) in enumerate(zip(ticks, times)):
[…]

### 2023-04-14 forwards-and-backwards.tex
edits with alison

@@
 achieved for a variety of interacting particle systems. The vast majority of these
-results concern spin systems \comment{REFs}. However,~\cite{flandoli/huang:2021} 
+results concern spin systems \comment{TODO REFs obtained from Flandoli/Huang etc: Alison}.
+However,~\cite{flandoli/huang:2021} 
 obtain the Fisher-KPP equation
@@
 
-\comment{This paragraph to be rewritten last}
+\comment{TODO: This paragraph to be rewritten last PETER}
 
@@
 
+\comment{TODO: modify condition (4) to say that the $C_f$ only depends on $\|f\|_\infty$, $\|\partial f\|$ and $\|\partial^2 f\|$: PETER}
+
 We give two concrete situations in which the fourth condition is satisfied.
@@
         and the equilibrium density is 10 individuals per unit area.
-        Blue curves are contours from a kernel density estimate.
         \label{fig:super_vs_det_2d}
@@
 
-\comment{I'm a bit surprised by the factor of 2 (that manifests as $\varphi^2$),
-    but I've checked where it comes from pretty carefully, and don't see anything wrong.}
+% \comment{I'm a bit surprised by the factor of 2 (that manifests as $\varphi^2$),
+%     but I've checked where it comes from pretty carefully, and don't see anything wrong.}
 Long-term fitness of an individual
@@
 
-\comment{Maybe check for more recent references for paragraph below.}
 Equation~(\ref{eqn:nonlocal_pde}) is a nonlocal version of a reaction diffusion equation with nonlinear
@@
     \caption{
+        \comment{TODO PETER; maybe remove dotted lines}
         Two panels, showing simulated 1D populations under a
@@
     although the resulting expression isn't terribly helpful.
+    TODO ALISON
 }
@@
         \textbf{Right:} Population density in an expanding wave in a one-dimensional simulation
-        forming a period pattern;
+        forming a periodic pattern;
         each panel shows the wave front in three periods of time;
@@
 and characterization of the lineage process in the deterministic case.
-\comment{TODO: revisit this paragraph}
+\comment{TODO: check/improve this paragraph: ALISON}
 
@@
 \begin{proof}
-The Aldous-Rebolledo criterion (found in the form we use here in \cite{rebolledo:1980}),
+The Aldous-Rebolledo criterion (Theorem~\ref{thm:aldous_rebolledo})
 applied to the semimartingale representation of $\langle f, \eta^N_t\rangle$
@@
 \end{lemma}
+
 \begin{proof}[Sketch]
+    \comment{Change this to a sequence $f_n$ of smooth things with uniformly bounded derivs that increase 1; follows from condition 4. PETER}
 To avoid the idea being buried in notation, we sketch the proof in the 
@@
 \end{multline} 
-    \comment{alison to look at this again; check whether it depends on just bounding $B^\theta_1$}
 Evidently, in much the same way as in the proof of
@@
 
-\comment{below $\eta_s^N$ stops having  an $N$ at some point}
+\comment{TODO: check that $\eta_s^N$ having an $N$ or not is okay}
 
@@
 \comment{perhaps explain: the next proposition is useful because we'll want to use weak convergence of $\smooth{\epsilon}\eta_s$; but in the martingale we have the term on the left in the proposition; probably there are other ways to do this.}
-\comment{ACTUALLY BETTER we want to transfer $T_\epsilon^2$ over onto $\eta$; this happens in two steps, first this proposition; next using that $T_{\epsilon^2}f - f$ is small}
+\comment{ACTUALLY BETTER we want to transfer $T_\epsilon^2$ over onto $\eta$; this happens in two steps, first this proposition; next using that $T_{\epsilon^2}f - f$ is small; ALISON}
 
@@
 \end{equation}
-\comment{which we prove by showing the expectation of this positive quantity goes to zero; e.g. see Lemma 7.5(?)}.
+\comment{check this: which we prove by showing the expectation of this positive quantity goes to zero; e.g., see Lemma 7.5(?): ALISON}.
 
@@
 \comment{Probably should put a bit more detail in here?}
-\comment{key bit is that we can always write $M_s(w)$ as a convolution of $p_{\epsilon^2/}$ with something}
+\comment{key bit is that we can always write $M_s(w)$ as a convolution of $p_{\epsilon^2/2}$ with something: ALISON}
 
@@
     are proved in Section~\ref{sec:lookdown_generator_proofs}.
-    \comment{TODO: refer to correct thing}
+    \comment{TODO: refer to correct thing or just say "like in 6.6": PETER}
     Finally, we must show that the limiting lookdown process $\lp$
@@
 
-We postpone the proof of this Lemma to show how it gets us to compact containment.
+We postpone the proof of this Lemma until we have shown how it yields to compact containment.
 First, we show that this implies compact containment for arbitrary
@@
         \lp \in \lpmeasures \;:\;
-        \langle h_k, \lp \rangle \le C_k
+        \langle f_k, \lp \rangle \le C_k
         \text{ for all } k \ge 1
@@
     so we may bound
-    \begin{align} \label{eqn:hn_bound},
+    \begin{align} \label{eqn:hn_bound}
     \begin{split} 
@@
             2 C_a \int_u^\infty h(v) dv
-            + \left( C_a u^2 + C_b u \right) |h'(u)|
-        ,
+            + \left( C_a u^2 + C_b u \right) |h'(u)|,
         \lp_s^N(dx, du) \big \rangle
@@
 and so suppose that the limiting process has density $\varphi_t(x)$
-at location $x$ and time $t$.
+at location $x$ and time $t$ (which may only exist almost everywhere).
+We first proceed informally, as if the density exists everywhere,
+and follow this with an integration against test functions to make the argument rigorous.
 Let $Y$ denote the spatial motion followed by a single line of descent.
@@
 It follows from Lemma~\ref{def: MP definition of limit} that for test functions of this form
-\comment{(beware the different definition of $f$ to that lemma)}
+\comment{(TODO beware the different definition of $f$ to that lemma) PETER ``in order to adhere to standard notation in the literature''}
 the generator of $\eta^N_t$ is
@@
 
+\comment{TODO: conditions on $f$}
+
 \begin{lemma}
@@
 For the third generator we have that, since $g(x,N) = 1$,
-\footnotesize
 \begin{align*}
@@
 \end{align*}
-\normalsize
 
@@
 and so
-\footnotesize
 \begin{align*}
@@
 It again follows from Lemma~\ref{def: MP definition of limit} that for test functions of this form
-\comment{(beware the different definition of $f$ to that lemma)}
+\comment{(TODO beware the different definition of $f$ to that lemma) PETER}
 the generator of $\eta_t$ is
@@
     \label{lem:gamma_bound}
-\comment{TODO; REWRITE TO SAY THAT STHG IMPLIES CONDITION 2 OF LEMMA \ref{lem:conditions on r} (see reference on p.13)}
+\comment{TODO; REWRITE TO SAY THAT STHG IMPLIES CONDITION 2 OF LEMMA \ref{lem:conditions on r} (see reference on p.13) PETER}
     Under the assumptions of Definition~\ref{def:model_setup},
@@
     To do this, first note that 
-    \begin{align} \label{eqn:q_bound_split}
+    \begin{align} \label{eqn:q_bound_split2}
     &
@@
     So,
-    the second term in~\eqref{eqn:q_bound_split} is bounded by
+    the second term in~\eqref{eqn:q_bound_split2} is bounded by
     \begin{align*}
@@
 
-We record for reference above
+\comment{TODO: explain what this section is doing (tightness of products) PETER}
+We record for reference
 one version of the Aldous-Rebolledo criteria for tightness of a sequence real-valued processes
 (as it appears in \citet{etheridge2000introduction}):
-\comment{TODO: reference this elsewhere, if we keep it?}
 
@@
     \label{thm:aldous_rebolledo}
-    Let $\{Y^(n)\}_{n \ge 1}$ be a sequence of real-valued processes
+    Let $\{Y^{(n)}\}_{n \ge 1}$ be a sequence of real-valued processes
     with c\`adl\`ag paths.

### 2023-04-16 forwards-and-backwards.tex
minor edits

@@
     \label{gamma_bounded_condition}
-\item For each $f \in C_b^2(\IR^d)$, there is a $C_f$ such that
+\item For each $f \in C_b^2(\IR^d)$,
+    there is a $C_f$ such that
     $$ |\gamma(x, \smooth{\gamma} \eta(x)) \theta \int 
@@
     for all $x \in \IR^d$ and $\eta \in \measures$.
-        \label{gamma_B_condition}
+    Furthermore, $C_f$ only depends on the norm of $f$ and it's first two derivatives,
+    i.e., 
+    \[
+        C_f = C(\sup_x \max_{ij} \max(f(x), \partial_{x_i} f(x), \partial_{x_i} \partial_{x_j} f(x))) .
+    \] \label{gamma_B_condition}
 \end{enumerate}
-
 To keep expressions manageable, we shall also assume that 
@@
 \end{assumptions}
-
-\comment{TODO: modify condition (4) to say that the $C_f$ only depends on $\|f\|_\infty$, $\|\partial f\|$ and $\|\partial^2 f\|$: PETER}
 
@@
 satisfy; they just require some regularity of $r$ as a function of $x$. 
-Condition~\ref{control through r} is also satisfied if for example
+Condition~\ref{control through r} of Lemma~\ref{lem:conditions on r} is also satisfied if for example
 $\|\nabla\rho_r\|\leq C\rho_r$ 
@@
 as we check in Lemma~\ref{lem:gamma_bound},
-Condition~\ref{control through gamma} is satisfied if $\rho_\gamma$ is also
+Condition~\ref{control through gamma} of Lemma~\ref{lem:conditions on r}
+is satisfied if $\rho_\gamma$ is also
 Gaussian with parameter $\sigma_\gamma$ and $\sigma_\gamma>\sigma_r$. For large enough
@@
 $m^2\gamma(m)$ is bounded, so therefore $|\gamma B^\theta_f|$ is bounded.
+
+Finally, note that all bounds depended only on $\|f\|_\infty$,
+$\max_i \|\partial_{x_i} f\|_\infty$, or 
+$\max_{ij} \|\partial_{x_i} \partial_{x_j} f\|_\infty$.
 \end{proof}
@@
 \begin{proof}[Sketch]
-    \comment{Change this to a sequence $f_n$ of smooth things with uniformly bounded derivs that increase 1; follows from condition 4. PETER}
 To avoid the idea being buried in notation, we sketch the proof in the 
@@
     =\IE[\langle f,\eta_0\rangle]
-\\
-+\IE\Big[\int_0^t\Big\langle\gamma(x, \smooth{\gamma}\eta_s(x))
+    + \IE\Big[\int_0^t\Big\langle\gamma(x, \smooth{\gamma}\eta_s(x))
     \Delta \big(f(\cdot)r(\cdot,\smooth{r}\eta_s(\cdot))\big)(x)
+    \\ \qquad 
     +F(x,\smooth{F}\eta_s(x)) f(x),
@@
 \end{multline} 
-We take a sequence of test functions $f_n$ increasing to
-$\exp(\lambda x)$, with $\lambda>0$. Having passed
-to the limit,
-substituted in~(\ref{special case first moment equation}) and 
-expanded the term involving the Laplacian, we obtain
-\begin{multline}
-\label{exponential moment}
-    \IE[\langle \exp(\lambda x),\eta_t\rangle]
-    =
-    \IE[\langle \exp(\lambda x),\eta_0\rangle]
+We take a sequence of test functions $f_n$ increasing to the constant function 1,
+and having uniformly bounded first and second derivatives
+so that there is a (single) $C_1$
+from Condition~\ref{gamma_B_condition} of Assumptions~\ref{def:model_setup}
+such that $\gamma(x,\eta) B_{f_n}^\theta(x,\eta) \le C$ for all $x$, $\eta$, and $f_n$.
+This implies that $\gamma(x,\eta) \Delta(f_n(\cdot) r(\cdot,\eta))(x) \le C_1$
+for all $n$, and so in the limit, since $F$ is also bounded above,
+there is a $C$ such that
+\begin{align*}
+    \IE[\langle 1, \eta_t\rangle]
+    &=
+    \IE[\langle 1, \eta_0\rangle]
     +
-    \IE\Big[\int_0^t\Big\langle\gamma(x, \smooth{\gamma}\eta_s(x))
-    \exp(\lambda x)
-    \Big\{
-        \lambda^2 r(x, \smooth{r}\eta_s(x))
-    \\ {}
-        + 2\lambda\partial_x\big(r(\cdot,\smooth{r}\eta_s(\cdot)\big)(x)
-        + \partial_{xx} r(\cdot,\smooth{r}\eta_s(\cdot)\big)(x)
-    \Big\} 
-    + F(x,\smooth{F}\eta_s(x)),
+    \IE\Big[\int_0^t \Big\langle \gamma(x,\eta_s) \Delta r(x,\eta_s) + F(x,\eta_s) ,
     \eta_s(dx)\Big\rangle ds\Big] .
-\end{multline} 
-Evidently, in much the same way as in the proof of
-Lemma~\ref{lem:eta_f_bound},
-our conditions on $r$ and $F$ ensure
-that the integrand on the right hand side 
-of~(\ref{exponential moment})
-is bounded by $C\langle\exp(\lambda x),\eta_s(dx)\rangle$ for some constant
-$C$. Gronwall's inequality then implies that 
-$\IE[\langle\exp(\lambda x),\eta_t(dx)\rangle]$ 
+    \\ &\le
+    \IE[\langle 1, \eta_0\rangle]
+    +
+    C \IE\Big[\int_0^t \Big\langle 1, \eta_s(dx)\Big\rangle ds\Big] .
+\end{align*}
+Gronwall's inequality then implies that 
+$\IE[\langle 1, \eta_t(dx)\rangle]$ 
 is uniformly bounded for $t\in [0,T]$, and an application of Markov's inequality
 tells us that for any $\delta >0$,
-$\IP[\eta_t([R,\infty])>\delta]\to 0$ as $R\to\infty$. A symmetric argument
-yields the corresponding bound for $\IP[\eta_t([-\infty, -R])>\delta$ and the 
-result is proved.
+$\IP[\eta_t([R,\infty])>\delta]\to 0$ as $R\to\infty$.
 \end{proof}
@@
     which is shown in Lemma~\ref{lem:product_tightness}.
-
-    The analogue of Lemma~\ref{lem:limit_mgale},
-    in particular that the martingale properties are preserved under passage to the limit,
-    are proved in Section~\ref{sec:lookdown_generator_proofs}.
-    \comment{TODO: refer to correct thing or just say "like in 6.6": PETER}
+    The fact that martingale properties are preserved under passage to the limit
+    is straightforward, and can be proved in a way analgous to Lemma~\ref{lem:limit_mgale};
+    we omit the proof.
     Finally, we must show that the limiting lookdown process $\lp$
@@
 It follows from Lemma~\ref{def: MP definition of limit} that for test functions of this form
-\comment{(TODO beware the different definition of $f$ to that lemma) PETER ``in order to adhere to standard notation in the literature''}
 the generator of $\eta^N_t$ is
@@
         \eta(dx)
-    \bigg\rangle
+    \bigg\rangle .
     \end{split}
 \end{align}
+(Note that $f$ here differs from the $f$ used in Lemma~\ref{def: MP definition of limit}
+so as to agree with standard usage in the literature on lookdown processes.)
 The generator of $\lp^N_t$ is $A^N$, defined in equation~\eqref{eqn:lookdown_generator}.
@@
 It again follows from Lemma~\ref{def: MP definition of limit} that for test functions of this form
-\comment{(TODO beware the different definition of $f$ to that lemma) PETER}
 the generator of $\eta_t$ is
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Technical Lemmas}
-
-\subsection{Gaussian Kernel Estimates}
-
-\begin{lemma}\label{eq: Gaussin density estimates}
-\begin{equation}
- \theta H_{\theta}(x,w)\rho_r(x-w)\leq \rho_{\gamma}(x-w),
-\end{equation}
-where
-$$H_{\theta}(x,w)=\int_{\IR^d}
-    \left(
-        \frac{\rho_r(y-w)}{\rho_r(x-w)}
-        -
-        1
-    \right)^2
-q_{\theta}(x,dy).$$
-\end{lemma}
-\begin{proof}
-
-Writing out $H$,
-\begin{align}
-H_\theta(x, w)
-=
-\int
-    \left(
-        \exp\left(
-            - \frac{1}{2\epsilon_r^2}
-            \left\{
-                ||y - w||^2 - ||x - w||^2
-            \right\}
-        \right)
-        -
-        1
-    \right)^2
-    \frac{
-        e^{-\theta (y - x-\meanq)^{T}\covq^{-1}(y - x-\meanq)  / 2}
-    }{
-        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
-    }
-dy.
-\end{align}
-Writing $z=y-x-\meanq$, we have that 
-\begin{equation}
-\begin{aligned}
-||y - w||^2 - ||x - w||^2 
-=& ||y||^2-||x||^2 -2\langle y-x, w\rangle \\
-=&||x+z+ \meanq||^2-||x||^2-2 \langle z+ \meanq, w\rangle\\
-=&2\langle x, z+ \meanq \rangle + ||z+ \meanq||^2-2 \langle z+ \meanq, w\rangle \\
-=& 2 \langle x-w, z+ \meanq \rangle + ||z+ \meanq||^2\\
-=& 2\langle x-w+ \meanq,\meanq \rangle + 2\langle x-w+ \meanq, z \rangle +||z||^2
-\end{aligned}
-\end{equation}
-As a result, we have 
-\begin{align}
-H_\theta(x, w)
-=&
-\int
-    \left(
-        \exp\left(
-            - \frac{1}{2\epsilon_r^2}
-            \left\{
-                2 \langle x-w, z+ \meanq \rangle + ||z+ \meanq||^2
-            \right\}
-        \right)
-        -
-        1
-    \right)^2
-    \frac{
-        e^{-\theta z^{T}\covq^{-1}z  / 2}
-    }{
-        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
-    }
-dz\\
-=&\exp\left(-\frac{2}{\epsilon_r^2}\langle x-w+ \meanq,\meanq \rangle \right)\\
-& \times \int
-        \frac{
-        \exp\left(
-            - \frac{2}{\epsilon_r^2} \langle x-w+ \meanq, z \rangle
-            - \frac{1}{\epsilon_r^2} ||z||^2
-            \right)
-            e^{-\theta z^{T}\covq^{-1}z  / 2}
-    }{
-        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
-    }
-dz\\ \label{eq: Second moment term matrix calculation}
-&-2\exp\left(-\frac{1}{\epsilon_r^2}\langle x-w+ \meanq,\meanq \rangle \right)\\
-& \qquad \qquad \times     \int
-    \frac{ \exp\left(
-             -\frac{1}{\epsilon_r^2}\langle x-w+ \meanq, z \rangle
-              -\frac{1}{2\epsilon_r^2} ||z||^2
-            \right)e^{-\theta z^{T}\covq^{-1}z  / 2}
-        }{
-        (2 \pi/ \theta)^{d/2} |\covq|^{1/2} \label{eq: first moment term matrix calculation}
-    }
-dz\\
-&+1.
-\end{align}
-We now consider the integral of the form 
-\begin{equation}
-\int \exp(v^{T}z-C||z||^2) \frac{
-        e^{-\theta z^{T}\covq^{-1}z  / 2}
-    }{
-        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
-    }
-dz   
-\end{equation}
-for $v \in \IR^d$ and $C>0$. 
-We have 
-\begin{equation}
-\begin{aligned}
-&\int \exp(v^{T}z-C||z||^2) \frac{
-        e^{-\theta z^{T}\covq^{-1}z  / 2}
-    }{
-        (2 \pi/ \theta)^{d/2} |\covq|^{1/2}
-    }
-dz\\
-=&\frac{1}{|\covq|^{1/2}|  |\covq^{-1}(I+2C\covq/\theta )|^{1/2}  }\int \exp(v^{T}z) \frac{
-        e^{-\theta z^{T}\covq^{-1}(I+2C\covq/\theta )z  / 2}
-    }{
-        (2 \pi/ \theta)^{d/2}|\covq^{-1}(I+2C\covq/\theta )|^{-1/2} 
-    }
-dz\\
-=& \frac{1}{|I+2C\covq/\theta |^{1/2}} \mathbb{E}_{Z}[\exp (v^{T}Z)]\\
-=&\frac{1}{|I+2C\covq/\theta |^{1/2}}
-\exp 
-\left(
-\frac{1}{2}v^{T}\covq/\theta(I+2C\covq/\theta )^{-1}v
-\right),
-\end{aligned}
-\end{equation}
-where $Z \sim N(0, \covq/\theta \times (I+2C\covq/\theta )^{-1})$.
-
-Now writing $v=\frac{2}{\epsilon_r^2}( w-x-\meanq)$
-and $C=\frac{1}{\epsilon_r^2}$,
-we have the expression in Equation
-\eqref{eq: Second moment term matrix calculation} is 
-$$\frac{1}{|I+2\covq/(\epsilon_r^2\theta) |^{1/2}}
-\exp 
-\left(
-\frac{2}{\epsilon_r^4}( w-x-\meanq)^{T}\covq/\theta\left(I+2\covq/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
-\right).$$
-Similarly, writing $v=\frac{1}{\epsilon_r^2}( w-x-\meanq)$
-and $C=\frac{1}{2\epsilon_r^2}$,
-we have the expression in Equation
-\eqref{eq: first moment term matrix calculation} is 
-$$\frac{1}{|I+\covq/(\epsilon_r^2\theta) |^{1/2}}
-\exp 
-\left(
-\frac{1}{2\epsilon_r^4}( w-x-\meanq)^{T}\covq\left(I+\covq/\theta/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
-\right).$$
-As a result, we have 
-\begin{align*}
-&H_{\theta}(x,w)\\
-=& \frac{1}{|I+2\covq/(\epsilon_r^2\theta) |^{1/2}}
-\exp 
-\left(
-\frac{2}{\epsilon_r^4}( w-x-\meanq)^{T}\covq/\theta\left(I+2\covq/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
-\right)\\
-&-2\frac{1}{|I+\covq/(\epsilon_r^2\theta) |^{1/2}}
-\exp 
-\left(
-\frac{1}{2\epsilon_r^4}( w-x-\meanq)^{T}\covq/\theta\left(I+\covq/(\epsilon_r^2\theta)\right)^{-1}( w-x-\meanq)
-\right)\\
-&+1.
-\end{align*}
-If we write $F(1/\theta)=H_{\theta}(x,w)$, i.e.
-\begin{align*}
-&F(s)\\
-=& \frac{1}{|I+2/\epsilon_r^2 \covq s |^{1/2}}
-\exp 
-\left(
-\frac{2}{\epsilon_r^4}( w-x-\meanq)^{T}\covq s \left(I+2/\epsilon_r^2 \covq s\right)^{-1}( w-x-\meanq)
-\right)\\
-&-2\frac{1}{|I+2/\epsilon_r^2 \covq s |^{1/2}}
-\exp 
-\left(
-\frac{1}{2\epsilon_r^4}( w-x-\meanq)^{T}\covq s \left(I+2/\epsilon_r^2 \covq s\right)^{-1}( w-x-\meanq)
-\right)\\
-&+1\\
-&=G_1(s)+2G_2(s)+1
-\end{align*}
-we can check that $F(0)=0$.
-As a result, 
-$$\theta H_{\theta}(x,w)\rho_r(x-w)= \theta F(1/\theta)\rho_r(x-w)=F'(s)\rho_r(x-w),$$
-for some $s \in [0, 1/\theta]$.
-
-In Equation \eqref{eq: gamma-r convolution comparison}, we have established that 
-$\rho_r(x-w) / \rho_\gamma(x-w) = C' \exp(-K (x-w)^2 / 2)$
-with $K = \frac{1}{\epsilon_r^2} - \frac{1}{\epsilon_\gamma^2}$.
-Therefore it suffices to show that for all $x,w \in \IR^d$ and $s \in [0, 1/\theta]$, 
-\begin{align}\label{eqn:goal3}
-    F'(s) \exp\left(-A (x-w)^2 \right) \le C .
-\end{align}
-
-We consider how to differentiate function $G$ of the form 
-$$G(s):=\frac{1}{|I+As|^{1/2}}\exp(v^{T}Bs(I+Cs)^{-1}v),$$
-where $A,B,C$ are matrices with non-negative entries and $I$ is the identity matrix.
-
-Since 
-\begin{equation}
-\begin{aligned}
-G'(s)=& - \frac{|A|}{2|I+As|^{3/2}}\exp(v^{T}Bs(I+Cs)^{-1}v)\\
-      & + \frac{1}{|I+As|^{1/2}}\exp(v^{T}Bs(I+Cs)^{-1}v)\\
-      & \qquad \times \left\{ v^{T}B(I+Cs)^{-1}v
-                            - sv^{T}BC(I+Cs)^{-2}v
-                    \right\}\\
-      &=\left(- \frac{|A|}{2|I+As|}+v^{T}B(I+Cs)^{-2}v
-        \right)\\
-      & \qquad \times
-        \frac{1}{|I+As|^{1/2}}\exp(v^{T}Bs(I+Cs)^{-1}v),
-\end{aligned}
-\end{equation}
-using non-negativity of $A,B,C$ we have
-\begin{equation}
-\label{eq: bounds on G'}
-|G'(s)| \leq (|A|+||B||_{2}||v||_2^2)G(s).    
-\end{equation}
-As a result, we have that 
-\begin{equation}
-\label{eq: bounds on G}
-G(s) \leq K e^{|A|+||B||_{2}||v||_2^2)s}, ~~   G'(s)(|A|+||B||_{2}||v||_2^2)K e^{|A|+||B||_{2}||v||_2^2)s}.  
-\end{equation}
-
-Finally note that, 
-$$F'(s) \leq G_1'(s)+2G_2'(s),$$
-where 
-$$A_1= 2\epsilon_r^{-2} \covq, ~ v_1=\epsilon_r^{-2}(w-x-\meanq), ~B_1 = 2\covq, ~C_1=2\epsilon_r^{-2} \covq,$$
-and 
-$$A_2= 2\epsilon_r^{-2} \covq, ~ v_2=\epsilon_r^{-2}(w-x-\meanq), ~B_2 = \covq/2, ~C_2=2\epsilon_r^{-2} \covq,$$
-Substituting these quantities on Equation \eqref{eq: bounds on G} shows that Equation \eqref{eqn:goal3} is satisfied as long as $\epsilon_r < \epsilon_\gamma$.
-
-\end{proof}
 
@@
     \label{lem:gamma_bound}
-\comment{TODO; REWRITE TO SAY THAT STHG IMPLIES CONDITION 2 OF LEMMA \ref{lem:conditions on r} (see reference on p.13) PETER}
-    Under the assumptions of Definition~\ref{def:model_setup},
-    for all $f \in \mathcal{C}^{2}_{0}(\IR^d \times [0,\infty))$,
-    there exists a $K_f < \infty$ such that
-    for all $\theta > 0$ and all $\eta \in \measures$,
-    \begin{equation} \label{eqn:gamma_bound}
-    \gamma\big(x,\smooth{\gamma} \eta(x)\big)
-    \left| \theta 
-        \int_{\IR^n} 
-            \left\{
-                f(y, \smooth{r} \eta(y)) - f(x, \smooth{r} \eta(x))
-            \right\}
-        q_{\theta}(x,dy)
-    \right|
-    \leq C_f     .
-    \end{equation}
-\end{lemma}
-
-The key assumption here from Definition~\ref{def:model_setup}
-will be that the spatial scale over which local density affects birth rate
-is larger than the scale over which it affects establishment:
-concretely, that $\epsilon_{r}^2 + \frac{2\lambda}{\theta} < \epsilon_{\gamma}^2$,
-where $\lambda = \sup_x \sup_{y : \|y\| = 1} y^T \covq(x) y$
-is the largest eigenvalue of $\covq(x)$ across all $x$.
-In the simple case of $\meanq = 0$ and $\covq = \sigma^2 I$,
-the condition is simply that $\epsilon_r^2 + 2\sigma^2 / \theta < \epsilon_\gamma^2$.
-
-\begin{proof}[of Lemma \ref{lem:gamma_bound}]
-
-    Since we have assumed that there is a $K$ for which $m^2 \gamma(x, m) < K$
-    for all $x \in \IR^d$ and $m \ge 0$,
-    equation~\eqref{eqn:gamma_bound} will follow if we can show that
-    \begin{equation*}
-        \left| \theta 
-            \int_{\IR^n} 
-                \left\{
-                    f\left(y, \smooth{r}\eta(y)\right)
-                    -
-                    f\left(x, \smooth{r}\eta(x)\right)
-                \right\}
-            q_{\theta}(x,dy)
-        \right|
-        \leq
-        C_f \left( 1 + \smooth{\gamma} \eta(x)^2 \right) .
-    \end{equation*}
-    To do this, first note that 
-    \begin{align} \label{eqn:q_bound_split2}
-    &
-        \left| \theta 
-            \int_{\IR^n} 
-                \left\{
-                    f\left(y, \smooth{r}\eta(y)\right)
-                    -
-                    f\left(x, \smooth{r}\eta(x)\right)
-                \right\}
-            q_{\theta}(x,dy)
-        \right|
-    \\ &\qquad {} \leq
-        \left| \theta 
-            \int_{\IR^n} 
-                \left\{
-                    f\left(y, \smooth{r}\eta(y)\right)
-                    -
-                    f\left(x, \smooth{r}\eta(y)\right)
-                \right\}
-            q_{\theta}(x,dy)
-        \right|
-    \\ &\qquad \qquad {}  +
-        \left| \theta 
-            \int_{\IR^n} 
-                \left\{
-                    f\left(x, \smooth{r}\eta(y)\right)
-                    -
-                    f\left(x, \smooth{r}\eta(x)\right)
-                \right\}
-            q_{\theta}(x,dy) 
-        \right| .
-    \end{align}
-
-    Since 
-    \begin{align*}
-        f\left(y, \smooth{r}\eta(y)\right) - f\left(x, \smooth{r}\eta(y)\right)
-        &=
-        \sum_i (y_i - x_i) \partial_{x_i} f \left(x, \smooth{r}\eta(y)\right) 
-        \\ &\qquad {}
-        +
-        \frac{1}{2} \sum_{ij} (y_i - x_i)(y_j - x_j)
-            \partial_{x_i x_j} f \left(z, \smooth{r}\eta(y)\right) 
-    \end{align*}
-    where $z = t x + (1-t) y$ for some $0 \le t \le 1$,
-    writing
-    $K_1 = \sup_{x,m} \max_i |\partial_{x_i} f(x, m)|$
-    and 
-    $K_2 = \sup_{x,m} \max_{i,j} |\partial_{x_i x_j} f(x, m)|$
-    for the bounds on the spatial derivatives of $f$,
-    the first term is bounded by
-    \begin{align*}
-        K_1 \left|
-            \theta \int_{\IR^d} \sum_i (y_i - x_i) q_\theta(x, dy)
-        \right|
-        +
-        K_2 \left|
-            \theta \int_{\IR^d} \sum_{ij} (y_i - x_i) (y_j - x_j)  q_\theta(x, dy)
-        \right| .
-    \end{align*}
-    This is bounded uniformly because
-    $q_\theta(x, dy)$ is the density of a Gaussian with mean $\meanq(x)/\theta$
-    and covariance $\covq(x)/\theta$, and both $\meanq(x)$ and $\covq(x)$
-    are bounded uniformly in $x$.
-
-    Similarly, 
-    \begin{align*}
-        f(x, \smooth{r}\eta(y)) - f(x, \smooth{r}\eta(x))
-        &=
-        (\smooth{r}\eta(y) - \smooth{r}\eta(x)) f'(x, \smooth{r}\eta(x))
-        + \frac{1}{2} (\smooth{r}\eta(y) - \smooth{r}\eta(x))^2 f''(x, m)
-    \end{align*}
-    for some $\smooth{r}\eta(x) \le m \le \smooth{r}\eta(y)$,
-    where $f'$ and $f''$ denote the first and second derivatives with respect to the second argument.
-    So,
-    the second term in~\eqref{eqn:q_bound_split2} is bounded by
-    \begin{align*}
-        % note that the f' term does not depend on x, just y,
-        % so can come out of the integral
-        \|f'\|_\infty
-        \left|
-            \theta \int_{\IR^d}
-                (\smooth{r}\eta(y) - \smooth{r}\eta(x))
-            q_\theta(x, dy)
-        \right|
-        +
-        \|f''\|_\infty
-        \left|
-            \theta \int_{\IR^d}
-                (\smooth{r}\eta(y) - \smooth{r}\eta(x))^2
-            q_\theta(x, dy)
-        \right| .
-    \end{align*}
-    Therefore, it suffices to show that there is a $K < \infty$ such that
-    for all $\eta \in \measures$ and $x \in \IR^d$,
+    Suppose the first three conditions of Assumptions~\ref{def:model_setup} hold,
+    and furthermore the kernels $\rho_r = p_{\epsilon_r^2}$ and $\rho_\gamma = p_{\epsilon_\gamma^2}$
+    are each Gaussian with standard deviations $\epsilon_r$ and $\epsilon_\gamma$ respectively.
+    Let $\lambda = \sup_x \sup_{y : \|y\| = 1} y^T \covq(x) y$ be the largest eigenvalue of $\covq(x)$
+    across all $x$.
+    If $\epsilon_{r}^2 + \frac{2\lambda}{\theta} < \epsilon_{\gamma}^2$, then 
+    there is a $C < \infty$ such that
+    for all $x\in\IR^d$, $\eta\in\measures$,
     \begin{equation}
@@
         q_\theta(x,dy)\right|
-        \leq K \smooth{\gamma} \eta(x)
+        \leq C \smooth{\gamma} \eta(x)
     \end{equation}
@@
         q_\theta(x,dy)
-        \leq K \left(\smooth{\gamma}\eta(x) \right)^2 .
+        \leq C \left(\smooth{\gamma}\eta(x) \right)^2 .
     \end{equation}
+\end{lemma}
+
 Note that the right hand side of each is the average density
 over a wider region (since $\epsilon_\gamma > \epsilon_r$).
+The key assumption here 
+is that the spatial scale over which local density affects birth rate
+is larger than the scale over which it affects establishment.
+In the simple case of $\meanq = 0$ and $\covq = \sigma^2 I$,
+the condition is simply that $\epsilon_r^2 + 2\sigma^2 / \theta < \epsilon_\gamma^2$.
+This gives a yet more concrete situation in which 
+Condition~\ref{control through gamma} of Lemma~\ref{lem:conditions on r} holds.
+
+\begin{proof}[of Lemma \ref{lem:gamma_bound}]
 
@@
         &=
-        \left(
+        \bigg(
             \meanq(x)^T \Gamma(s,x)^{-1} (z - s \meanq)
@@
             (z - s \meanq(x))
-        \right. \\ & \qquad \qquad \qquad \left. {}
+        \\ & \qquad \qquad \qquad {}
             -
             \sum_i \frac{\lambda_i}{\epsilon_r^2 + s \lambda_i}
-        \right)
+        \bigg)
         p_{s, x}(z) ,
@@
 
-\comment{TODO: explain what this section is doing (tightness of products) PETER}
-We record for reference
+Here we record, for completeness, the fact used above
+that tightness for a family of processes, if determined by the Aldous-Rebolledo criterion,
+extends to sums and products of those processes.
+We first record for reference
 one version of the Aldous-Rebolledo criteria for tightness of a sequence real-valued processes

### 2023-04-16 figures/make_plots.sh

@@ -25,7 +25,7 @@ do
     then
         slim -s 123 ../pme.slim
     fi
-    ../lineage_plotting/plot_1d_lineages.py pme_123.trees 3 1 3 3
+    # ../lineage_plotting/plot_1d_lineages.py pme_123.trees 3 1 3 3
     ../lineage_plotting/pme/plot_pme_density.py pme_123.trees 45 55 6
     popd
 done

### 2023-04-17 forwards-and-backwards.tex
.
figures

@@
     \begin{center}
-        \includegraphics[width=0.45\textwidth]{figures/ex2a/pme_123.steps}
-        \includegraphics[width=0.45\textwidth]{figures/ex2b/pme_123.steps}
+        \includegraphics[width=0.45\textwidth]{figures/ex2a/pme_1234.steps}
+        \includegraphics[width=0.45\textwidth]{figures/ex2b/pme_1234.steps}
     \end{center}
     \caption{
-        \comment{TODO PETER; maybe remove dotted lines}
-        Two panels, showing simulated 1D populations under a
-porous medium equation with logistic growth~(\ref{PME}), comparing the simulated
-        profile to the analytical solution;
-        $\theta/N$ not small on left; small on right.
-        % (Note: noisier wave should move slower, although maybe not much since it's pushed.)
+        Two panels, showing simulated 1D populations under a porous medium equation with logistic growth~(\ref{PME}),
+        % comparing the simulated profile to the analytical solution;
+        $\theta/N$ small on the left; large on the right.
+        Simulation is with $\gamma(m) = m$ and $\mu(m) = (1+1/\theta) m - 1/\theta$
+        (implemented by choosing a small $dt$ taking reproduction probability per time step
+        to be $1 - \exp(- dt m)$
+        and death probability to be $\mu(m) = 1 - \exp(-dt ((1+1/\theta) m - 1/\theta))$).
         \label{fig:pme_waves}
@@
 \]
-Therefore, setting $t'=\delta^2$ and using Lemma~\ref{BoundednessVarPhis}, for all $z$,
+Therefore, setting $t'=\delta^2$ and using Lemma~\ref{BoundednessVarphis}, for all $z$,
 \[ 
@@
 \varphi_t(z) 
-\leq e^{\delta^2\| F \|_{M}} \IE_z\big[  \varphi_{t-\delta^2}(Z_{\delta^2})\big]. 
+\leq e^{\delta^2\| F \|_{M}} \IE_z\big[  \varphi_{t+\delta^2}(Z_{\delta^2})\big]. 
 \]

### 2023-04-17 figures/make_plots.sh

@@ -21,12 +21,12 @@ done
 for DIR in ex2a ex2b
 do
     pushd $DIR
-    if [ ! -e pme_123.trees ]
+    if [ ! -e pme_1234.trees ]
     then
-        slim -s 123 ../pme.slim
+        slim -s 1234 ../pme.slim
     fi
-    # ../lineage_plotting/plot_1d_lineages.py pme_123.trees 3 1 3 3
-    ../lineage_plotting/pme/plot_pme_density.py pme_123.trees 45 55 6
+    # ../lineage_plotting/plot_1d_lineages.py pme_1234.trees 3 1 3 3
+    ../lineage_plotting/pme/plot_pme_density.py pme_1234.trees 10 50 6
     popd
 done
 

### 2023-04-17 forwards-and-backwards.tex
updated figs

@@
     \caption{
-        Two panels, showing simulated 1D populations under a porous medium equation with logistic growth~(\ref{PME}),
+        Two panels, showing simulated 1D populations under a porous medium equation with logistic growth~(\ref{PME}) in $d=1$,
         % comparing the simulated profile to the analytical solution;
-        $\theta/N$ small on the left; large on the right.
+        $\theta$ small on the left; large on the right.
         Simulation is with $\gamma(m) = m$ and $\mu(m) = (1+1/\theta) m - 1/\theta$
@@
         to be $1 - \exp(- dt m)$
-        and death probability to be $\mu(m) = 1 - \exp(-dt ((1+1/\theta) m - 1/\theta))$).
+        and death probability to be $\mu(m) = 1 - \exp(-dt ((1+1/\theta) m - 1/\theta))$);
+        values of $\theta$ are 1 and 100, respectively.
         \label{fig:pme_waves}
@@
 the solution converges to \eqref{eqn:pme_wave} \citep{kamin/rosenau:2004}.
-In Figure~\ref{fig:pme_waves} we show simulations of the individual based model
-described above. They
-display travelling wave solutions
-similar to numerical solutions of~(\ref{PME}),
+In Figure~\ref{fig:pme_waves} we show simulations of the individual based model described above.
+They display travelling wave solutions qualitatively similar to solutions of~(\ref{PME}),
 with increasingly good agreement for larger $\theta$ and $N$.

### 2023-04-17 forwards-and-backwards.tex
.

@@
 They display travelling wave solutions qualitatively similar to solutions of~(\ref{PME}),
-with increasingly good agreement for larger $\theta$ and $N$.
-\comment{TODO: does it?}
-As expected, noise slows down the wave.
-\comment{Not sure that noise will slow things drastically because the 
-biggest production of
-mass happens behind the wavefront.}
+with better agreement for larger $\theta$ and $N$.
 

### 2023-04-17 forwards-and-backwards.tex
.

@@
 We will work with test functions of the form
-$$  f(\lp) = \prod_{(x, u) \in \lp} g(x, u) = \exp\left(\langle \log g, \lp \rangle \right) . $$
+\begin{equation} \label{eqn:f_defn}
+    f(\lp) = \prod_{(x, u) \in \lp} g(x, u) = \exp\left(\langle \log g, \lp \rangle \right) ,
+\end{equation}
+where $0 \le g \le 1$ and $g(x,u) = 1$ for all $u \ge u_g$ for some $u_g < \infty$.
 Furthermore, recall that $\kappa^N(\lp)(\cdot) = \lp(\cdot \times [0, N)) / N$
@@
 
-\comment{TODO: conditions on $f$}
-
 \begin{lemma}
@@
     For all finite counting measures $\eta$ on $\IR^d$,
+    if $f$ is of the form~\eqref{eqn:f_defn}, then
     \begin{align}
@@
     For all $\eta \in \measures$,
+    if $f$ is of the form~\eqref{eqn:f_defn}, then
     \begin{align}

### 2023-04-20 forwards-and-backwards.tex
.

@@
 \title{\large{\bf
-Looking forwards and backwards through locally regulated populations
+Looking forwards and backwards: dynamics and genealogies of locally regulated populations
 }}
@@
 In particular, the total rate of production of mature offspring by an individual at $x$ will be
-\[
+\begin{equation} \label{eqn:total_repro}
 	\gamma\big(x,\smooth{\gamma}X(x)/N\big)\int r\big(y, \smooth{r}X(y)/N\big)q_{\theta}(x,dy).
-\]
+\end{equation}
 Nonetheless, it will be convenient to define the death rate $\mu_\theta$ in terms of 
@@
 and would be equal to it in a nonspatial model;
-but, as discussed later,
-differs because offsprings' establishment probability is measured at their new location
-rather than their parents', and so differs from $r(x)$.
+but, as can be seen from \eqref{eqn:total_repro},
+differs because an offspring's establishment probability is measured at their new location
+rather than that of their parent.
 For the most part, we work with $F$ instead of $\mu$.
@@
     (although often we omit the dependence of $\meanq$ and $\covq$ on $x$).
-    This implies that if we define, for $f : \IR^d \to \IR$,
+    This implies that if we define, for $f \in C_b^\infty(\IR^d)$,
     \begin{align}
@@
 determines the topology of weak convergence on $\measures$.
-
 We write 
-$r(x,\eta) \gamma(x,\eta) C(x) = J(x,\eta) J(x,\eta)^T$, and 
-$\beta(x,\eta) = r(x,\eta) \gamma(x,\eta) \big(\meanq(x)+2C(x)\nabla\log r(x,\eta)\big)$
+$r(x,\eta) \gamma(x,\eta) \covq(x) = J(x,\eta) J(x,\eta)^T$, and 
+$\beta(x,\eta) = r(x,\eta) \gamma(x,\eta) \big(\meanq(x)+2\covq(x)\nabla\log r(x,\eta)\big)$
 (quantities that will appear in Proposition~\ref{prop:limiting_construction}).
@@
 Suppose further that $F$ is a Lipschitz function which is bounded above, and that
-$b(x)$ and $C(x)$, the drift and 
+$\meanq(x)$ and $\covq(x)$, the drift and 
 covariance matrix of $\DG$, satisfy the conditions of 
@@
     Then the semigroup $Q_s$
-    of the motion of a lineages in this population 
+    of the motion of a lineages in frame that is moving at speed $\wavespeed$
     is time-homogeneous with generator
@@
 take discrete time steps of length $dt$ (with $dt$ suitably small),
-and have each individual with local density $m$ reproduce and die, respectively, with probabilities
+and have each individual reproduce and die with probabilities, respectively,
 \begin{align*}
@@
 \end{align*}
-so that $\gamma(x, m) = p_\text{birth}(m)/dt \approx m$
+where $m$ is the local density at their location.
+This makes $\gamma(x, m) = p_\text{birth}(m)/dt \approx m$
 and
@@
     \begin{center}
-        \includegraphics[width=0.45\textwidth]{figures/ex2a/pme_1234.steps}
-        \includegraphics[width=0.45\textwidth]{figures/ex2b/pme_1234.steps}
+        \includegraphics[width=0.7\textwidth]{figures/ex2a/pme_1234.steps}
+        \includegraphics[width=0.7\textwidth]{figures/ex2b/pme_1234.steps}
     \end{center}
     \caption{
-        Two panels, showing simulated 1D populations under a porous medium equation with logistic growth~(\ref{PME}) in $d=1$,
+        Simulated 1D populations under a porous medium equation with logistic growth~(\ref{PME}) in $d=1$,
         % comparing the simulated profile to the analytical solution;
-        $\theta$ small on the left; large on the right.
+        $\theta/N$ small on the left; large on the right.
         Simulation is with $\gamma(m) = m$ and $\mu(m) = (1+1/\theta) m - 1/\theta$
@@
         and death probability to be $\mu(m) = 1 - \exp(-dt ((1+1/\theta) m - 1/\theta))$);
-        values of $\theta$ are 1 and 100, respectively.
+        values of $\theta$ are 1 and 100, respectively, and both values of $N$ are the same.
         \label{fig:pme_waves}
@@
 They display travelling wave solutions qualitatively similar to solutions of~(\ref{PME}),
-with better agreement for larger $\theta$ and $N$.
+with better agreement for smaller $\theta/N$
+(but in both cases, $N$ is reasonably large).
 
@@
 so lineages in the tip are pushed leftwards into the bulk of the 
-wave at a rate $-2e^x/(1+e^{x})$.
+wave at a rate $s-2e^x/(1+e^{x})$.
 The strength of this drift decreases exponentially as $x\to -\infty$.
@@
 and $F(x, m) = (1 - m)$,
-the generator of the diffusion governing the position of the ancestral lineage 
+the generator of the diffusion governing the position of the ancestral lineage relative to the wavefront
 is, for $x < 0$,
@@
         forming a periodic pattern;
-        each panel shows the wave front in three periods of time;
-        within each period of time the wave front at earlier times is shown in blue
+        each panel shows the wavefront in three periods of time;
+        within each period of time the wavefront at earlier times is shown in blue
         and later times in pink.
@@
 we have a bound of the form
-\begin{multline*}
+\begin{align*}
 |B^\theta_f|
@@
         \right| 
-\end{multline*}
+\end{align*}
 for suitable constants $K_1$, $K_2$.
@@
 \begin{proof}[Sketch]
+To avoid the idea being buried in notation, we sketch the proof in the 
+special case of $d=1$.
+We take a sequence of test functions $f_n$ increasing to the function $f(x)=x$
+and having uniformly bounded first and second derivatives.
+Examining the proof of Lemma~\ref{lem:conditions on r},
+so that there is a (single) $C_1$
+from Condition~\ref{gamma_B_condition} of Assumptions~\ref{def:model_setup}
+such that $\gamma(x,\eta) B_{f_n}^\theta(x,\eta) \le C$ for all $x$, $\eta$, and $f_n$.
+
 To avoid the idea being buried in notation, we sketch the proof in the 

### 2023-04-22 forwards-and-backwards.tex
lemma 2.8 fixup

@@
 \end{remark}
+
 In order to pass to a scaling limit, we will need to impose some 
@@
     there is a $C_f$ such that
-    $$ |\gamma(x, \smooth{\gamma} \eta(x)) \theta \int 
+    $$
+        |\gamma(x, \smooth{\gamma} \eta(x)) \theta \int 
         (r(y, \smooth{r} \eta(y)) f(y) - r(x, \smooth{r} \eta(x)) f(x))
-    q_\theta(x, dy)| \le C_f $$
+        q_\theta(x, dy)| \le C_f (1 + |f(x)|)
+    $$
     for all $x \in \IR^d$ and $\eta \in \measures$.
-    Furthermore, $C_f$ only depends on the norm of $f$ and it's first two derivatives,
+    Furthermore, $C_f$ only depends on the norm of the first two derivatives of $f$,
     i.e., 
     \[
-        C_f = C(\sup_x \max_{ij} \max(f(x), \partial_{x_i} f(x), \partial_{x_i} \partial_{x_j} f(x))) .
+        C_f = C(\sup_x \sup_{\|z\|=1} \max( \sum_i z_i \partial_{x_i} f(x), \sum_{ij} z_i z_j \partial_{x_i x_j} f(x))) .
     \] \label{gamma_B_condition}
@@
 
-We give two concrete situations in which the fourth condition is satisfied.
+Since we take bounded $f$,
+for most situations the bound $C_f(1+f(x))$ in condition~\ref{gamma_B_condition} above
+can be safely replaced simply by $C_f$;
+however, this will be useful
+in certain situations where we consider a sequence of $f$ with increasing upper bounds.
+We now give two concrete situations in which the fourth condition is satisfied.
 
@@
     further, that $\{\eta_0^N\}_{N\geq 1}$ is a sequence of 
-purely atomic measures, with $\eta_0^N$ comprised of atoms of mass $1/N$, which is
-tight 
-in $\measures$ and such that there exists $\lambda>0$ for 
-which $\langle e^{\lambda\|x\|}, \eta_0^N(dx)\rangle<C<\infty$
+    purely atomic measures, with $\eta_0^N$ comprised of atoms of mass $1/N$,
+    which is tight in $\measures$ and such that
+    $\langle |x|, \eta_0^N(dx)\rangle<C<\infty$
     with $C$ independent of $N$.
@@
 Lemma~\ref{lem:conditions on r} is satisfied.
+\comment{BEGIN NEW VERSION}
+We write
+\begin{align*}
+    r(y,\eta) f(y) - r(x,\eta) f(x)
+&=
+    r(y,\eta) (f(y) - f(x))
+    + (r(y,\eta) - r(x,\eta)) f(x) 
+\\ &=
+    r(y,\eta) \left(
+        \sum_i (y-x)_i \partial_{x_i} f(x)
+        + \sum_{ij} (y-x)_i (y-x)_j \partial_{x_i x_j} f(z_1)
+    \right)
+\\ &\qquad {}
+    + f(x) \left(
+        \sum_i (y-x)_i \partial_{x_i} r(x,\eta)
+        + \sum_{ij} (y-x)_i (y-x)_j \partial_{x_i x_j} r(z_2,\eta)
+    \right)
+ \\ &=
+    \left( r(x,\eta) + \sum_j (y-x)_j \partial_{x_j} r(z_3,\eta) \right)
+    \left(
+        \sum_i (y-x)_i \partial_{x_i} f(x)
+    \right)
+\\ &\qquad {}
+    + r(y,\eta) 
+        \sum_{ij} (y-x)_i (y-x)_j \partial_{x_i x_j} f(z_1)
+\\ &\qquad {}
+    + f(x) \left(
+        \sum_i (y-x)_i \partial_{x_i} r(x,\eta)
+        + \sum_{ij} (y-x)_i (y-x)_j \partial_{x_i x_j} r(z_2,\eta)
+    \right) ,
+\end{align*}
+for some $z_i = \kappa_i x + (1-\kappa_i) y$.
+Integrating this against $q(x, dy)$, we get that
+\begin{align*}
+& \bigg| \theta \int \left(
+    r(y,\eta) f(y) - r(x,\eta) f(x)
+\right) q_\theta(x, dy) \bigg|
+\\ &\qquad \le
+    \bigg| \sum_i \left( r(x,\eta) \partial_{x_i} f(x) + f(x) \partial_{x_i} r(x,\eta) \right)
+    \theta \int (y-x)_i q_\theta(x, dy) \bigg|
+\\ &\qquad \qquad {} +
+    \bigg| f(x) 
+    \theta \int \sum_{ij} \partial_{x_i x_j} r(z_2,\eta) (y-x)_i (y-x)_j q_\theta(x, dy) \bigg|
+\\ &\qquad \qquad {} +
+    \bigg| \theta \int \sum_{ij} (y-x)_i (y-x)_j 
+        \left(
+            \partial_{x_i} f(x) \partial_{x_j} r(z_3,\eta)
+            + r(y,\eta) \partial_{x_ix_j} f(z_1)
+        \right) q_\theta(x, dy) \bigg|
+\end{align*}
+Since $q_\theta(x,dy)$ is the density of a Gaussian with mean $\meanq(x)/\theta$
+and covariance $\covq(x)/\theta$, and both $\meanq(x)$ and $\covq(x)$ are uniformly bounded,
+so that $\theta \int (y-x)_i q_\theta(x,dy)$ is bounded as well.
+Furthermore, a change of variables that diagonalizes $\covq(x)$
+shows for any $g : \IR^d \to \IR^{d + d}$,
+that if $C_g = \sup_y \sup_{\|z\| = 1} \sum_{ij} g(y)_{ij} z_i z_j$
+and $\lambda_* = \sup_y \sup_{\|z\|=1} \sum_{ij} \covq(y)_{ij} z_i z_j$
+then
+$$ \theta \int \sum_{ij} g(y)_{ij} (y-x)_i (y-x)_j q_\theta(x, dy) \le C_g \lambda_* .  $$
+Condition~\ref{control through r} 
+gives uniform bounds on the derivatives of $r(x,\eta) = r(x,\rho_r*\eta(x))$
+in this expression and so, provided $f$ also has uniformly bounded first and second derivatives,
+we have a bound of the form
+\begin{align*}
+    |B^\theta_f| \leq K_1 + K_2 |f(x)| ,
+\end{align*}
+for suitable constants $K_1$, $K_2$ that depend only on the derivatives of $f$.
+
+\comment{BEGIN PREVIOUS VERSION}
 We write
@@
 \end{align*}
-for suitable constants $K_1$, $K_2$.
+for suitable constants $K_1$, $K_2$
+that depend on $f$ only through 
+$\max_i \|\partial_{x_i} f\|_\infty$ and
+$\max_{ij} \|\partial_{x_i} \partial_{x_j} f\|_\infty$.
 This is bounded uniformly because
@@
 Since $\gamma$ is bounded as well, so is $|\gamma B^\theta_f|$.
+\comment{END OLD VERSION}
 
@@
 with respect to the second argument.
-    So, writing $K_5=\|f\|_\infty\|r'\|_\infty$ and $K_6=\|f\|_\infty\|r''\|_\infty$,
-    the second term in~\eqref{eqn:q_bound_split} is bounded by
+    So, writing $K_5=\|r'\|_\infty$ and $K_6=\|r''\|_\infty$,
+    the second term in~\eqref{eqn:q_bound_split} is bounded by $f(x)$ multiplied by
     \begin{align*}
@@
 Under Condition~\ref{control through gamma} of 
-Assumptions~\ref{def:model_setup}, the right hand side is bounded by 
+Assumptions~\ref{def:model_setup}, this is bounded by 
 a constant times $\smooth{\gamma}\eta(x)+(\smooth{\gamma}\eta(x))^2$ and 
-$m^2\gamma(m)$ is bounded, so therefore $|\gamma B^\theta_f|$ is bounded.
-
-Finally, note that all bounds depended only on $\|f\|_\infty$,
-$\max_i \|\partial_{x_i} f\|_\infty$, or 
-$\max_{ij} \|\partial_{x_i} \partial_{x_j} f\|_\infty$.
+$\sup_x m^2\gamma(x, m)$ is bounded,
+so therefore $|\gamma(x,\eta) B^\theta_f(x,\eta)| \le K_7 + K_8 f(x)$,
+where $K_7$ comes from $K_3$, $K_4$, and the supremum of $\gamma$,
+while $K_8$ comes from $K_5$, $K_6$, and the supremum of $m^2 \gamma(x,m)$.
 \end{proof}
@@
 First note that Condition~\ref{gamma_B_condition} of Assumptions~\ref{def:model_setup}
-stipulates that $|\gamma B^\theta_f|$ is uniformly bounded,
-and so recalling that $F$ is bounded above, we can now conclude that
+stipulates that $|\gamma B^\theta_f|$ is uniformly bounded by a contant times $1 + f$,
+and so recalling that $F$ is bounded above, we conclude that
 under Assumptions~\ref{def:model_setup}
-$\gamma(x, \eta) B^\theta_f(x, \eta) + f(x) F(x, \eta) \le C_f $ for some $C_f$.
+$\gamma(x, \eta) B^\theta_f(x, \eta) + f(x) F(x, \eta) \le C_f (1 + f(x))$ for some $C_f$.
 
@@
         \IE\left[ \langle f, \eta^N_0 \rangle \right]
-        + C_f \int_0^t \IE\left[ \langle 1, \eta^N_s \rangle \right] dt .
+        + C_f \int_0^t \IE\left[ \langle 1 + f, \eta^N_s \rangle \right] dt .
     \end{align}
@@
 We take a sequence of test functions $f_n$ increasing to the function $f(x)=x$
-and having uniformly bounded first and second derivatives.
-Examining the proof of Lemma~\ref{lem:conditions on r},
-so that there is a (single) $C_1$
+and having uniformly bounded first and second derivatives,
+so that there is a (single) $C$
 from Condition~\ref{gamma_B_condition} of Assumptions~\ref{def:model_setup}
-such that $\gamma(x,\eta) B_{f_n}^\theta(x,\eta) \le C$ for all $x$, $\eta$, and $f_n$.
-
-To avoid the idea being buried in notation, we sketch the proof in the 
-special case of $d=1$ and $\DG=\Delta$.
-For any $f\in C_b^\infty(\IR)$,
-\begin{multline}
-\label{special case first moment equation}
-\IE[\langle f,\eta_t\rangle] 
-    =\IE[\langle f,\eta_0\rangle]
-    + \IE\Big[\int_0^t\Big\langle\gamma(x, \smooth{\gamma}\eta_s(x))
-    \Delta \big(f(\cdot)r(\cdot,\smooth{r}\eta_s(\cdot))\big)(x)
-    \\ \qquad 
-    +F(x,\smooth{F}\eta_s(x)) f(x),
-    \eta_s(dx)\Big\rangle ds\Big].
-\end{multline} 
-We take a sequence of test functions $f_n$ increasing to the constant function 1,
-and having uniformly bounded first and second derivatives
-so that there is a (single) $C_1$
-from Condition~\ref{gamma_B_condition} of Assumptions~\ref{def:model_setup}
-such that $\gamma(x,\eta) B_{f_n}^\theta(x,\eta) \le C$ for all $x$, $\eta$, and $f_n$.
-This implies that $\gamma(x,\eta) \Delta(f_n(\cdot) r(\cdot,\eta))(x) \le C_1$
-for all $n$, and so in the limit, since $F$ is also bounded above,
-there is a $C$ such that
-\begin{align*}
-    \IE[\langle 1, \eta_t\rangle]
-    &=
-    \IE[\langle 1, \eta_0\rangle]
+such that $\gamma(x,\eta) B_{f_n}^\theta(x,\eta) \le C(1 + f_n(x))$
+for all $x$, $\eta$, and $f_n$.
+Then, just as we arrived at equation~\eqref{bound on intfdeta},
+\begin{align*}
+    \IE[\langle f_n(x), \eta^N_t(dx) \rangle]
+    &\le
+    \IE[\langle f_n(x), \eta^N_0(dx) \rangle]
     +
-    \IE\Big[\int_0^t \Big\langle \gamma(x,\eta_s) \Delta r(x,\eta_s) + F(x,\eta_s) ,
-    \eta_s(dx)\Big\rangle ds\Big] .
-    \\ &\le
-    \IE[\langle 1, \eta_0\rangle]
-    +
-    C \IE\Big[\int_0^t \Big\langle 1, \eta_s(dx)\Big\rangle ds\Big] .
-\end{align*}
+    C \int_0^t \IE\Big[\Big\langle f_n(x), \eta^N_s(dx) \Big] \Big\rangle ds ,
+\end{align*}
+with the same constant for all $n$ and all $N$.
 Gronwall's inequality then implies that 
-$\IE[\langle 1, \eta_t(dx)\rangle]$ 
-is uniformly bounded for $t\in [0,T]$, and an application of Markov's inequality
-tells us that for any $\delta >0$,
+$\IE[\langle f_n, \eta^N_t\rangle] \le C'$
+for some $C'$ independent of $n$, $N$, and $t \in [0,T]$.
+By first taking $N \to \infty$ and then $n \to \infty$,
+we find that $\IE[\langle x, \eta_t(dx)\rangle] \le C'$
+for $t\in [0,T]$, and an application of Markov's inequality
+tells us that for any $\delta > 0$,
 $\IP[\eta_t([R,\infty])>\delta]\to 0$ as $R\to\infty$.
+The same argument with $f_n(x)$ increasing to $-x$ completes the proof.
 \end{proof}

### 2023-04-24 forwards-and-backwards.tex
.

@@
 which is integrable, and so determines the unique stationary distribution.
+% (agreeing with Lemma~\ref{cor:stationary_dist}).
 Thus the position of the ancestral lineage relative to the wavefront will converge to a stationary 
@@
 suggesting a different genealogy.
+
+It is interesting to compare the stationary distribution we have obtained here
+to the expression that we'd get by setting $\meanq = -\wavespeed$
+and using Lemma~\ref{cor:stationary_dist},
+i.e., by giving each offspring a mean displacement that offsets the motion of the wave.
+In the Fisher-KPP and Allen-Cahn cases above, we get the same expressions,
+but this is only the case because $r\equiv\gamma\equiv1$ in both.
+For the PME with $\meanq = 1$ we have $\DG^* = \Delta + \grad$ 
+and so the equation solved by the population density is
+$$
+    \partial_t \varphi = \Delta \varphi + 2 \varphi \grad \varphi + \varphi (1 - \varphi) ,
+$$
+which has a traveling wave solution of the same shape but moving at half the speed,
+$\varphi(x,t) = w^{P}(x-t/2)$,
+and a stationary distribution of the lineage relative to the wavefront of
+$\pi(\xi) \propto e^{3\xi/2} (1 - e^{\xi/2})^3$.
+% \comment{Details to back that last statement up, which we probably want to comment out?}
+% (We can see that $w^P(x-t/2)$ is a traveling wave solution by using that
+% $\partial_x w^P = -(1 - w^P)/2$;
+% and then the generator of a linage in the moving frame is
+% $\Lgen_{P'} = \varphi \partial_x^2 + (4 \partial_x \varphi + 1/2 + \varphi) \partial_x$,
+% which has speed measure proportional to
+% $\exp(\int^x 3(1/2 dx + d \log \varphi)) / \varphi$.)
+% \begin{align*}
+% m_{P'}(\xi)
+%     &\propto \frac{1}{2(1-e^{\xi/2})} \exp\left(
+%         \frac{3}{2} \int^\xi \left\{
+%             1 - \frac{e^{x/2}}{1 - e^{x/2}}
+%         \right\}dx
+%     \right) .
+% \end{align*}
 
@@
         \Delta f
-        + \grad ( 2 \log(\gamma \varphi) - h ) \cdot \grad f
+        + \grad ( 2 \log(\gamma \varphi) - h/\sigma^2 ) \cdot \grad f
     \right) ,
@@
 $$
-Therefore, by choosing $H(x) = 2 \log(\gamma(x) \varphi(x)) - h(x)$
+Therefore, by choosing $H(x) = 2 \log(\gamma(x) \varphi(x)) - h(x)/\sigma^2$
 and
@@
     = e^{H(x)} / (\sigma^2 r(x) \gamma(x))
-    = \frac{\gamma(x) \varphi(x)^2 e^{-h(x)}}{\sigma^2 r(x)} ,
+    = \frac{\gamma(x) \varphi(x)^2 e^{-h(x)/\sigma^2}}{\sigma^2 r(x)} ,
 $$

### 2023-04-24 forwards-and-backwards.tex
alison edits 4/22

@@
 equation limits have been
-achieved for a variety of interacting particle systems. The vast majority of these
-results concern spin systems \comment{TODO REFs obtained from Flandoli/Huang etc: Alison}.
-However,~\cite{flandoli/huang:2021} 
-obtain the Fisher-KPP equation
-as a scaling limit of interacting diffusions in
-$\IR^d$. In that setting a major challenge (also apparent in our models), not
-faced in spin systems, is 
-the control of concentration of particles. We also note that the scaling 
-considered in~\cite{flandoli/huang:2021} is different from that considered
-below. In their language we consider only `moderate interactions', meaning that
+achieved for a variety of interacting particle systems. 
+\comment{FROM ALISON: I rewrote the rest of this paragraph. Missing references
+are in the latex file, next to the citation, but commented out}
+Following the now classical contributions 
+of~\citet{demasi/ferrari/lebowitz:1986, demasi/presutti:1991,
+oeschlaeger:1985},
+%@article{demasi/ferrari/lebowitz:1986,
+%  title={Reaction-diffusion equations for interacting particle system},
+%  author={De Masi, A. and Ferrari, P. A. and Lebowitz, J. L.},
+%  journal={J. Stat. Phys.},
+%  year={1986},
+%  volume={44},
+%  pages={589-644},
+%  DOI = {10.1007/BF01011311},
+%}
+% A. De Masi and E. Presutti. Mathematical methods for hydrodynamic limits,
+%volume 1501 of Lecture Notes in Mathematics. Springer-Verlag, Berlin, 1991.
+%
+% K. Oeschl\"ager. A law of large numbers for moderately interacting 
+% diffusion processes. Z. Warsch. Verw. Gebiete. 69(2):279-322, 1985
+much of this work has focused on lattice based models with one particle
+per site, or on systems with a fixed number, $N$,
+of interacting diffusions as $N\to\infty$.
+For systems of proliferating particles,
+as considered for example by 
+\citet{oelschlaeger:1989, flandoli/leimbach/olivera:2019,
+flandoli/huang:2021}, 
+% K. Oeschl\"ager. On the derivation of reaction-diffusion equations as limits
+% of systems of moderately interacting stochastic processes. Probab. Th. Rel.
+% Fields 82, 565--586, (1989)
+%
+% F. Flandoli, M. Leimbach, and C. Olivera. Uniform convergence of 
+%proliferating particles to the FKPP equation. J. Math. Anal. Appl. 473(1):
+%27--52, (2019)
+an additional challenge (also apparent in our models), is 
+the control of concentration of particles. 
+We follow 
+\citet{oelschlaeger:1989, flandoli/leimbach/olivera:2019} in considering
+`moderate interactions', meaning that
 the number of individuals in the neighbourhood over which we measure local
-population density tends to infinity, whereas they also consider the situation in which
-that number remains finite;
-furthermore we shall consider a scaling in which 
-the reproduction mechanism is near-critical and look at large timescales,
-while \citet{flandoli/huang:2021} only scale the number of
-particles in the system and the size of the neighbourhood over which indivduals interact.
+population density tends to infinity, whereas 
+\citet{flandoli/huang:2021} also consider the situation in which
+that number remains finite. 
+We refer to \citet{flandoli/huang:2021} for a more thorough 
+literature review, 
+but note that both our model and scaling differ from those considered
+in the body of work discussed there: whereas in those settings, the only 
+scalings are the number of particles in the system and the size of the
+neighbourhood over which individuals interact with one another, in
+keeping with the vast literature on continuous state branching models, we 
+also scale time and so must ensure that births are 
+adequately compensated by deaths to prevent the population from exploding.
 
@@
 \citep{birzu/hallatschek/korolev:2017, birzu/hallatschek/korolev:2021}.
+\comment{The missing reference is
+ G. Birzu, O. Hallatshcek and K. Korolev. Genealogical structure
+ changes as range expansions transition from pushed to pulled. 
+ PNAS 118(34) (2021) 
+ https://doi.org/10.1073/pnas.2026746118}
 In that setting, the genealogies will be quite different
@@
         values of $\theta$ are 1 and 100, respectively, and both values of $N$ are the same.
+	\comment{FROM ALISON Should we say what N is??}
         \label{fig:pme_waves}
@@
 by \citet{britton1990spatial,sasaki1997clumped,hernandezgarcia2004clustering,young2001reproductive,berestycki2009nonlocal}.
-Heuristically, this can occur if density-dependent effects of individuals
-extend sufficiently farther than the typical dispersal distance:
-the patches are stable because new offspring landing between two clumps
-effectively compete with \emph{both} neighboring clumps,
-while individuals within a clump effectively compete with only one.
-
-The implication here is that the equilibrium solution to~\eqref{general deterministic limit}
-may not be unique,
-and a stable solution may have oscillations on a scale determined by the interaction distance.
-We can see this easily in the simple case that
-$\DG = \sigma^2 \Delta$,
-the interaction kernels $\rho_r$, $\rho_\gamma$, and $\rho_F$
-are all equal to $p_{\epsilon^2}$ (the heat kernel at time $\epsilon^2$),
-and all parameters are spatially homogeneous,
+\comment{FROM ALISON: I rewrote the rest of this section - please check!}
+These patches can be stable. For example, if
+the density-dependent effects of individuals
+extend farther, but not too much farther, than the typical dispersal distance,
+new offspring landing between two clumps
+can effectively find themselves in competition with 
+\emph{both} neighbouring clumps,
+while individuals within a clump compete with only one.
+
+More mathematically, consider the case in which
+$\DG = \sigma^2 \Delta$ and all 
+parameters are spatially homogeneous,
 so that $r(x, \eta) = r(\smooth{r}\eta(x))$, and similarly for $\gamma$ and $F$.
-Let $\varphi_0$ be a value so that $F(\varphi_0) = 0$ and $F'(\varphi_0) < 0$,
-so that we would expect $\varphi(x) \equiv \varphi_0$ to be a stable equilibrium solution.
-Let us linearize~\eqref{general deterministic limit} about $\varphi_0$:
+If $\varphi_0$ is such that $F(\varphi_0)=0$ and $F'(\varphi_0)<0$, then the
+constant solution $\varphi\equiv\varphi_0$ is a nontrivial equilibrium
+of~\eqref{general deterministic limit}. However, it may not be unique,
+it may be unstable, and a stable solution may have 
+oscillations on a scale determined by the interaction distance.
+
+To understand the stability of the constant solution $\varphi\equiv\varphi_0$, 
+we
+linearise~\eqref{general deterministic limit} around $\varphi_0$:
 let $\varphi_t(x) = \varphi_0 + \psi_t(x)$,
@@
 Writing $r_0 = r(\varphi_0)$ and $r'_0 = r'(\varphi_0)$,
-and similarly for $\gamma$ and $F$,
+with analogous expressions for $\gamma$ and $F$,
 \begin{align*}
@@
 \end{align*}
-Letting $\hat \psi(u) = \int e^{2\pi i u x} \psi(x) dx$,
-\begin{align*}
+Letting $\hat f(u) = \int e^{2\pi i u x} f(x) dx$ denote the Fourier transform,
+\begin{equation}
+	\label{fourier transform psi}
     \partial_t \hat \psi(u)
-    &\approx
+    \approx
+	\left\{
+	- u^2\sigma^2 \varphi_0 r_0 \gamma_0' \hat{\rho}_\gamma(u) 
+	%e^{-\epsilon^2 u^2 /2}
+        - u^2 \sigma^2 r_0 \gamma_0
+	+ \varphi_0 F'_0 \hat{\rho}_F(u) 
+	%e^{-\epsilon^2 u^2 /2} 
+	\right\} \hat \psi(u) .
+\end{equation}
+In the simplest case, in which $\gamma$ is constant, so $\gamma_0'=0$,
+this reduces to
+\begin{equation} %\begin{align*}
+	\label{simplest FT}
+	\partial_t \hat \psi(u)
+    \approx
     \left(
-        - \sigma^2 \varphi_0 r_0 \gamma_0' u^2 e^{-\epsilon^2 u^2 /2}
-        - \sigma^2 r_0 \gamma_0 u^2
-        + \varphi_0 F'_0 e^{-\epsilon^2 u^2 /2} 
+%	- u^2\sigma^2 \varphi_0 r_0 \gamma_0' \hat{\rho}_\gamma(u) 
+	%e^{-\epsilon^2 u^2 /2}
+        - u^2 \sigma^2 r_0 \gamma_0
+	+ \varphi_0 F'_0 \hat{\rho}_F(u) 
+	%e^{-\epsilon^2 u^2 /2} 
     \right) \hat \psi(u) .
-\end{align*}
-Since $F'_0 < 0$, the last two terms are negative,
-but on the other hand if we take $\gamma_0' < 0$
-(i.e., per capita birth rate decreases with density near equilibrium),
-then the stability of the constant solution $\varphi \equiv \varphi_0$
-depends on the balance between the first and latter two terms.
-Writing
-$A_1 = - \sigma^2 \varphi_0 r_0 \gamma'_0$,
-$A_2 = \sigma^2 r_0 \gamma_0$,
-and $A_3 = - \varphi_0 F'_0$
-(with signs chosen so each is positive),
-and defining
-$$ g(v) = A_1 v - A_2 v e^{\epsilon^2 v /2} - A_3 , $$
-we have $\partial_t \hat \psi(u) = g(u^2) e^{\epsilon^2 u^2 /2} \psi(u)$.
-The term $g(v)$ is maximized at $v_*$ solving
-$e^{\epsilon^2 v_*/2} = A_1 / (A_2 (\epsilon^2 v_*/ 2 + 1))$,
-which is positive if $A_1 > A_2$,
-i.e., if $-\varphi_0 \gamma_0' > \gamma_0$.
-If so, then the constant solution is unstable with respect to perturbations
-that oscillate with frequency around $\sqrt{v_*}$.
-\comment{This seems wrong, since it doesn't involve $\sigma$?
-    But at least note the unstable frequencies scale with $\epsilon$.
-    We might say more by linearizing the exponential term,
-    which gives $v_* = (A_1 - A_2 + A_3 \epsilon^2/2)/(A_1 \epsilon^2)$,
-    although the resulting expression isn't terribly helpful.
-    TODO ALISON
-}
+\end{equation} %\end{align*}
+If we take $\rho_F=p_{\epsilon^2}$, then 
+$\hat{\rho}_F(u)=\exp(-2\pi\epsilon^2 u^2)$ and (recalling 
+that $F_0'<0$) the term in brackets is always negative, and we recover
+the well-known fact that in this case the constant solution is stable.
+If, on the other hand, $\hat{\rho}_F$ changes sign, there may be values of $u$ for which the corresponding quantity is positive. For example, if $d=1$ and
+$\rho_F(x)={\mathbf 1}_{[-\epsilon, \epsilon]}(x)/2\epsilon$, then 
+$\hat{\rho}_F(u)=\sin (2\pi\epsilon u)/(2\pi\epsilon u)$, which is 
+negative for $u\in (1/(2\epsilon), 1/\epsilon)$ (and periodically 
+repeating intervals). Setting $v=\epsilon u$, the bracketed term on 
+the right hand side of~\eqref{simplest FT} becomes 
+\[
+	\varphi_0F_0'\frac{1}{2\pi v}\sin (2\pi v)
+	-\frac{\sigma^2}{\epsilon^2}v^2r_0\gamma_0,
+\]
+and we see that if $\sigma^2/\epsilon^2$ is sufficiently small, there are
+values of $v$ for which this is positive. In other words, in keeping
+with our heuristic above, if dispersal is sufficiently short range relative to
+the range over which individuals interact, there are unstable frequencies that
+scale with the interaction distance $\epsilon$. In two dimensions, replacing 
+the indicator of an interval by that of a ball of radius $\epsilon$, a
+similar analysis applies, except that the sine function is replaced by a 
+Bessel function.
+
+Now suppose that $\gamma$ is not constant. Then, 
+from~\eqref{fourier transform psi},
+if we take 
+$\rho_\gamma=\rho_F=p_\epsilon^2$,
+\begin{equation*}
+	\partial_t \hat \psi(u) = e^{-2\pi^2\epsilon^2 u^2 } 
+	\left\{
+		-\sigma^2\varphi_0 r_0\gamma_0'u^2
+	-\sigma^2r_0\gamma_0u^2e^{2\pi^2\epsilon^2u^2}
+	+\varphi_0 F_0'
+	\right\}
+	\hat{\psi}(u).
+\end{equation*}
+If we make the (reasonable)
+assumption that $\gamma_0'<0$, then we see that even when the Fourier
+transform of $\rho$ does not change sign, there may be parameter values
+for which the constant solution is unstable.
+As before, we set $v=\epsilon u$. The term in brackets becomes
+\[
+	\frac{\sigma^2}{\epsilon^2}v^2\left(-\varphi_0 r_0\gamma_0'
+	-r_0\gamma_0e^{2\pi^2v^2}\right)+\varphi_0F_0',
+\] 
+and, provided $-\varphi_0\gamma_0'/\gamma_0>1$, for sufficiently small $v$ 
+the term in round brackets is positive. We now see that if 
+$\sigma^2/\epsilon^2$ is sufficiently {\em large},
+the equilibrium state $\varphi\equiv\varphi_0$ 
+is unstable. As before, the unstable frequencies will scale with $\epsilon$
+and for given $F$, $r$ and $\gamma$, whether or not such unstable
+frequencies exist will be determined by $\sigma^2/\epsilon^2$, but 
+in this case of Gaussian kernels, 
+it is interaction distance being sufficiently small relative
+to dispersal that will lead to instability.
 
@@
     \frac{\theta}{N}
-    \int_{\IR^d}
-        \gamma(x, \eta) \int f^2(y) r(y, \eta) q_\theta(x, dy) + f^2(x) \mu_\theta(x, \eta),
+	\int_{\IR^d}\left\{
+		\gamma(x, \eta) \int f^2(y) r(y, \eta) q_\theta(x, dy) + f^2(x) \mu_\theta(x, \eta) \right\}
     \eta(dx) .
 \end{align*}
+\comment{FROM ALISON integral against eta in last line corrected}
 Since $\int f^2(y) r(y, \eta) q_\theta(x, dy) \to f^2(x) r(x, \eta)$
@@
 which captures the local rate of production of successful offspring.
+\comment{FROM ALISON This sort of true because it corresponds to lookdown events, but when I read this again I was confused. Is there a better way to say it?} 
 Recall from equation~\eqref{eqn:mu_defn} that
@@
 \end{equation*}
-Under Assumptions~\ref{def:model_setup}, as $\theta \to \infty$
+Under Assumptions~\ref{def:model_setup}, as $\theta \to \infty$,
 $c_\theta(x, \eta)$ will tend to $\alpha \gamma(x, \eta) r(x, \eta)$
@@
 we say that a ${\mathcal D}_{[0,\infty)}({\mathcal C}_N)$-valued process 
+	\comment{FROM ALISON: we have not been consistent in the layout of 
+	the notation for spaces of cadlag paths - it is already different in 
+	the definition below!}
 $(\xi_t)_{t \ge 0}$
@@
 We will also need an inverse notion:
-for a measure $\lp^N$ on $\IR^d \times [0, N]$ and a sigma-field $\mathcal{F}$,
+for a measure $\lp^N$ on $\IR^d \times [0, N]$ and a $\sigma$-field $\mathcal{F}$,
 we say that \emph{$\lp^N$ is conditionally uniform given $\mathcal{F}$}
@@
 In other words, the $[0, N]$ components of $\lp$
-are independent, uniformly distributed on $[0, N]$, and independent of $\kappa(\lp)$.
+are independent, uniformly distributed on $[0, N]$, and independent of 
+$\kappa^N(\lp)$.
+\comment{ALISON: added N, also made sigma $\sigma$ above}
 Similarly, for a measure $\lp$ on $\IR^d \times [0, \infty)$
@@
     as $\tilde \eta^N$.
-    Furthermore, for each $t$, $\lp^N_t$ is conditionally uniform given given $\mathcal{F}^{\eta^N}_t$
+    Furthermore, for each $t$, $\lp^N_t$ is conditionally uniform 
+	\comment{ALISON deleted excess given}
+	given $\mathcal{F}^{\eta^N}_t$
     in the sense of \eqref{eqn:conditionally_uniform}.
@@
     in the sense of \eqref{eqn:conditionally_uniform}.
-    Then, any sequence of stochastic processes $(\lp_t^N)_{t \ge 0}$
+    Then, 
+	\comment{FROM ALISON deleted `any sequence of stochastic processes'
+	which didn't make sense - we want the ones already specified }
+	$(\lp_t^N)_{t \ge 0}$
     has a subsequence which converges in distribution as $N \to \infty$
@@
 \end{theorem}
+
+\comment{FROM ALISON: should we signpost that the proofs of these results can 
+be found in section???}
 
@@
 the potential new label is $a \concat j$, the birth time is $\tau_{a \concat j} = \tau$,
-and the spatial displacement of the potential ogfspring is $y(X(\tau-), z)$, where
+and the spatial displacement of the potential offspring is $y(X(\tau-), z)$, where
 $$
@@
 To see this, first note that if the Poisson processes are fixed
-then the set of events to which a given label $a \in \labelspace$ is associated
+then the set of events with which a given label $a \in \labelspace$ is associated
 is also fixed -- this is the sequence $(\tau_k, v_k, z_k, \kappa_k)$ associated 
@@
 
-In the following sections we present formal proofs of our three scaling limits.
+In this section we present formal proofs of the first two of our
+three scaling limits.
+%following sections we present formal proofs of our three scaling limits.
 In Subsection~\ref{sec:population_density_proof} 
-we prove Theorem~\ref{thm:nonlocal_convergence}, to obtain a limit in
+we prove Theorem~\ref{thm:nonlocal_convergence}, to obtain (both
+stochastic and deterministic) limits in
 which interactions between individuals in the population are nonlocal.
@@
 limit to obtain a classical PDE.
-In subsequent sections (Sections~\ref{subsec:one step convergence proof} and~\ref{sec:lookdown_proofs})
-we prove our third scaling limit, in which 
-we pass from our population model 
-directly to a reaction diffusion equation without going via a nonlocal limit,
-and finally our results concerning both convergence of the lookdown representation
-and characterization of the lineage process in the deterministic case.
-\comment{TODO: check/improve this paragraph: ALISON}
+%In subsequent sections (Sections~\ref{subsec:one step convergence proof} and~\ref{sec:lookdown_proofs})
+%we prove our third scaling limit, in which 
+%we pass from our population model 
+%directly to a reaction diffusion equation without going via a nonlocal limit,
+%and finally our results concerning both convergence of the lookdown representation
+%and characterization of the lineage process in the deterministic case.
+\comment{FROM ALISON: slightly reworded - deleted bit about onestep convergence
+on the basis that we already point to that in the introduction}
 
@@
 \subsubsection{Compact Containment Condition}
+
+\comment{FROM ALISON Does this merit being a subsubsection - if so I would expect 
+some others too}
 

### 2023-04-24 forwards-and-backwards.tex
up to section 7

@@
 
-\comment{get equations to restart numbering in sections}
+\comment{TODO: ALISON SAYS
+The proof of Lemma 6.7 is now problematic.
+We'll be hard pushed to find a sequence of functions increasing to x, or indeed -x.
+Easily fixed of course, but I think that we should anyway change the condition of the theorem to be a bit more general, so say that we assume that $\langle f(x),\eta^N_0(dx)\rangle$  is uniformly bounded for some non-negative, twice differentiable with uniformly bounded first and second derivatives, function $f$ with $f(x)\to\infty$ as $x\to\infty$ and then use Lemma 6.1 and Gronwall to deduce $\langle f,\eta_t\rangle$ has bounded mean for any limit point and so Markov's inequality tells us no mass escaped to infinity.
+}
+
+\comment{``reaction diffusion equation'' or ``reaction-diffusion equation''?}
 
@@
 reaction diffusion equation, directly 
-by simultaneously scaling the kernel and the
+by simultaneously scaling the kernel width,
 timescale and population size in our individual based model.
 
-A novelty of our model is that we explicitly
-model a juvenile phase: the number of juveniles produced by an individual depends
-on local population density at the location of the parent. 
-Juvenile offspring are 
+A novelty of our model is that we explicitly model a juvenile phase.
+The number of juveniles produced by an individual depends
+on local population density at the location of the parent;
+these juvenile offspring are 
 thrown off in a (possibly heterogeneous, anisotropic) Gaussian distribution 
@@
 remains in our population models, resulting in novel limits in which the spatial
-motion is governed by a nonlinear diffusion.
+dynamics are governed by a nonlinear diffusion.
 
@@
 forests thicken or thin or change their composition;
+even in flat plains
 springtime grasslands host intergrading mosaics of different types of flowers.
@@
 
-Most models do not distinguish between juveniles and adults, so,
-for example, the number of adults produced by a single parent is determined
+Often models do not distinguish between juveniles and adults, so,
+for example, the number of adults produced by a single parent is determined only
 by the degree of crowding at the location of the parent.
@@
 We verify that this is indeed the case in two important examples:
-a special case of the porous medium equation with a logistic growth term, in which we 
-retain a signal of our two stage approach to modelling in the nonlinear diffusion term
-and the limiting equation takes the form 
+a special case of the porous medium equation with a logistic growth term, in which
+the limiting equation takes the form 
 \begin{equation}
@@
 in the context of spatial ecology;
-see for instance \citet{lam2023introduction} and \citet{cantrell2004spatial}.
+see for instance \citet{lam2023introduction} and \citet{cantrell2004spatial},
+and in many other fields;
+for instance, \citet{ghosh2022emergent}
+derive a stochastic version of~\eqref{semilinear PDE} to describe abundances of mutant bacteria strains
+along the human gut,
+while \citet{li/buenzli/simpson:2022} study the effects of nonlinear diffusion
+on long-term survival of a lattice-based interacting particle system.
+% MORE DETAILS:
+% \cite{li/buenzli/simpson:2022} write down an interacting particle
+% system on a hexagonal lattice (with at most one individual per site) that incorporates an effect
+% of local crowding on individual motion. Their equation
+% corresponds to a reaction-diffusion equation with nonlinear diffusion and a 
+% bistable reaction term of the form~(\ref{Birzu nonlinearity}) and they
+% investigate the interplay between nonlinear diffusion and long-term 
+% survival or extinction of the population.
 
@@
 
-We remark that such results on (one-step) convergence to reaction diffusion 
+Such results on (one-step) convergence to reaction diffusion 
 equation limits have been
 achieved for a variety of interacting particle systems. 
-\comment{FROM ALISON: I rewrote the rest of this paragraph. Missing references
-are in the latex file, next to the citation, but commented out}
 Following the now classical contributions 
-of~\citet{demasi/ferrari/lebowitz:1986, demasi/presutti:1991,
-oeschlaeger:1985},
-%@article{demasi/ferrari/lebowitz:1986,
-%  title={Reaction-diffusion equations for interacting particle system},
-%  author={De Masi, A. and Ferrari, P. A. and Lebowitz, J. L.},
-%  journal={J. Stat. Phys.},
-%  year={1986},
-%  volume={44},
-%  pages={589-644},
-%  DOI = {10.1007/BF01011311},
-%}
-% A. De Masi and E. Presutti. Mathematical methods for hydrodynamic limits,
-%volume 1501 of Lecture Notes in Mathematics. Springer-Verlag, Berlin, 1991.
-%
-% K. Oeschl\"ager. A law of large numbers for moderately interacting 
-% diffusion processes. Z. Warsch. Verw. Gebiete. 69(2):279-322, 1985
+of~\citet{demasi/ferrari/lebowitz:1986, demasi/presutti:1991, oeschlaeger:1985},
 much of this work has focused on lattice based models with one particle
@@
 as considered for example by 
-\citet{oelschlaeger:1989, flandoli/leimbach/olivera:2019,
-flandoli/huang:2021}, 
-% K. Oeschl\"ager. On the derivation of reaction-diffusion equations as limits
-% of systems of moderately interacting stochastic processes. Probab. Th. Rel.
-% Fields 82, 565--586, (1989)
-%
-% F. Flandoli, M. Leimbach, and C. Olivera. Uniform convergence of 
-%proliferating particles to the FKPP equation. J. Math. Anal. Appl. 473(1):
-%27--52, (2019)
+\citet{oelschlaeger:1989, flandoli/leimbach/olivera:2019, flandoli/huang:2021}, 
 an additional challenge (also apparent in our models), is 
@@
 individuals in a sample from the population, and these have been shaped 
-by its history \citep{neigel1993application,kelleher2019inferring}.
+by its history \citep[see e.g.,][]{neigel1993application,kelleher2019inferring}.
 It is therefore of interest to establish information about the distribution of genealogical trees 
-under our population model.
-To achieve this we exploit a lookdown construction. 
+under our population model, which we do with a lookdown construction. 
 Lookdown constructions were first introduced in~\cite{donnelly/kurtz:1996} to provide 
@@
 infinite population limit.
-Since then, they have been extended to a huge range of models. Of particular
+Since then, they have been extended to a wide range of models. Of particular
 relevance to our work here are the papers of~\cite{kurtz/rodrigues:2011} 
@@
 In Section~\ref{ancestral lineages for travelling waves}
-we shall consider three different (deterministic) wavefronts, moving 
-across $\IR^1$, and we shall explore the position of a single ancestral 
-lineage relative to that front.
-
-Most work on this topic has focused on models that caricature the classical Fisher-KPP equation with a 
+we shall describe the motion of a single ancestral lineage relative to
+three different (deterministic) wavefronts across $\IR^1$.
+
+Most work on the topic of ``waves'' of expanding populations
+has focused on models that caricature the classical Fisher-KPP equation with a 
 stochastic term, i.e.
@@
 spatial analogue of a Wright-Fisher diffusion. 
-For instance, \citep{ghosh2022emergent}
-derives a stochastic version of~\eqref{semilinear PDE} to describe abundances of mutant bacteria strains
-along the human gut.
-For very large $N$, and on suitable timescales, 
-starting with the pioneering work of~\cite{brunet/derrida/mueller/munier:2006},
+Starting with the pioneering work of~\cite{brunet/derrida/mueller/munier:2006},
 a considerable body of evidence has been amassed to underpin the
-conjecture that for this, and a wide class of 
-related models, 
-genealogies converge to a 
-Bolthausen-Sznitman coalescent. %, e.g.~\cite{brunet/derrida/mueller/munier:2007}.
+conjecture that for this, and a wide class of related models, 
+genealogies converge on suitable timescales in the infinite density limit
+to a Bolthausen-Sznitman coalescent. %, e.g.~\cite{brunet/derrida/mueller/munier:2007}.
 This reflects the fact that, for this equation, 
@@
 wave changes from ``pulled'' to ``pushed'', 
-\citep{birzu/hallatschek/korolev:2017, birzu/hallatschek/korolev:2021}.
-\comment{The missing reference is
- G. Birzu, O. Hallatshcek and K. Korolev. Genealogical structure
- changes as range expansions transition from pushed to pulled. 
- PNAS 118(34) (2021) 
- https://doi.org/10.1073/pnas.2026746118}
-In that setting, the genealogies will be quite different
-from the Fisher-KPP case. 
-%\comment{Could refer to more recent Birzu et al paper here.}
+\citep{birzu/hallatschek/korolev:2017, birzu/hallatschek/korolev:2021},
+and so the genealogies will be quite different from the Fisher-KPP case. 
 For example, \citet{etheridge/penington:2022}
@@
 Fisher KPP equation, the solution at time $t$
-vanishes beyond $x=x_0+ct$ for some constant wavespeed $c>0$, \citep{kamin/rosenau:2004}.
+vanishes beyond $x=x_0+ct$ for some constant wavespeed $c>0$ \citep{kamin/rosenau:2004}.
 As a first step towards understanding what we should expect in models with
@@
 
-\comment{TODO: This paragraph to be rewritten last PETER}
-
 In this paper we study scaling limits of spatial population models,
@@
 by means of a lookdown construction.
+
+In what follows we first study various scaling limits of the spatial population process,
+and then turn our attention to lineages traced back through these populations.
 First, in Section~\ref{sec: Model and main results},
-we describe the model and the main results
-(Theorems~\ref{thm:nonlocal_convergence}, \ref{thm:local_convergence}, and~\ref{thm:lineages}).
-Next, in Section~\ref{sec:applications}, we discuss a few striking consequences of these results,
-namely, X Y and Z \comment{TODO}.
+we describe the model and the main results,
+Theorems~\ref{thm:nonlocal_convergence}, \ref{thm:local_convergence}, and~\ref{thm:lineages}.
+Next, in Section~\ref{sec:applications}, we discuss a few striking consequences of these results
+regarding the behavior of genealogies in traveling waves,
+the appearance of periodic ``clumps'' in seemingly homogeneous population models,
+and identifiability of the underlying dynamics from a stationary population profile.
 In Section~\ref{sec:heuristics}, we provide heuristic explanations
 of why the theorems ought to be true,
-and some key ideas behind them.
-In Section \ref{sec:lookdown} we define and discuss the lookdown construction.
-This is followed by the technical proofs in Section~\ref{sec:proofs}.
-
-\comment{What's in the Appendix?}
+and some key ideas behind them,
+and in Section~\ref{sec:lookdown} we define and discuss the lookdown construction.
+Proofs of the results begin in Section~\ref{sec:proofs},
+which proves results for population models with nonlocal interactions,
+while Section~\ref{subsec:one step convergence proof} gives the more difficult proof
+for the case when interaction distances also go to zero in the limit.
+Finally, Section~\ref{sec:lookdown_proofs} gives proofs for convergence of the lookdown process
+and the associated results for the motion of lineages.
+The Appendix contains a few more techinical and less central lemmas.
+The results are illustrated in a few places with individual-based simulations,
+made using SLiM \citep{haller_slim_2019},
+but these are provided for visualization and we do not embark on numerical study.
 
@@
 allowing a nonzero mean and anisotropic variance.
-Both the mean and covariance can change across space,
+Both the mean and covariance of $q$ can change across space,
 but do not depend on population density.
@@
 with the nature of the limit depending on how they tend to infinity together.
-Evidently, we shall also need to scale the dispersal kernel if we are to obtain a
-nontrivial limit. We write $q_\theta(x,\cdot)$ for the density of the 
-multivariate Gaussian obtained by
-multiplying the mean and variance components corresponding to $q(x,\cdot)$ by $1/\theta$.
+Evidently, we also need to scale the dispersal kernel if we are to obtain a
+nontrivial limit, for which we use $q_\theta(x,\cdot)$,
+the density of the multivariate Gaussian obtained by
+multiplying the mean and variance components of $q(x,\cdot)$ by $1/\theta$.
 
@@
 rather than that of their parent.
-For the most part, we work with $F$ instead of $\mu$.
-
-Note that each of the three demographic parameters $r$, $\gamma$, $F$,
-depends on local density,
-measured by convolution with a smooth kernel. Each of the three kernels can be different.
+For the most part, we work with $F$ instead of $\mu_\theta$.
+
+So, each of the three demographic parameters $r$, $\gamma$, and $F$,
+depends on local density, measured by convolution with a smooth kernel,
+each of which can be different.
 As a result, death rate depends (in principle) on population densities measured in 
@@
 However, not only is it natural from a 
-biological perspective, it also turns out to be necessary if we are
-to capture nontrivial examples in our scaling results.
+biological perspective, it also turns out to be convenient for
+capturing nontrivial examples in the scaling limit.
 
@@
 
-For each $N$ and $\theta$, the rescaled process
-$\big(\eta^N_t\big)_{t\geq 0} := \big(X(\theta t)/N\big)_{t\geq 0}$, 
-takes values in the space of c\`adl\`ag paths in
+For each $N$ and $\theta$, we study primarily the process
+with mass scaled by $N$ and time scaled by $\theta$,
+$$ \big(\eta^N_t\big)_{t\geq 0} := \big(X(\theta t)/N\big)_{t\geq 0} , $$ 
+which takes values in the space of c\`adl\`ag paths in
 $\measures$ (the space of finite measures on $\IR^d$
@@
 
-In summary, at each time $t$, $\eta^N_t$ is purely atomic, consisting of atoms of mass $1/N$.
+In summary, at each time $t$, $\eta^N_t$ is purely atomic, consisting of atoms of mass $1/N$
+(which are the individuals).
 At instantaneous rate $\theta \gamma(x, \eta^N_t) N \eta^N_t(dx)$ an offspring of mass $1/N$ is 
@@
     We will also denote the adjoint of $\DG$ by
-    \begin{align}
-	    \nonumber
+    \begin{align*}
     \DG^* f(x)
@@
         \\
-	    \label{drift in adjoint}
+	    % \label{drift in adjoint}
         % &=
@@
         \right) f(x) .
-    \end{align}
+    \end{align*}
 \end{definition}
@@
 $$
-    \theta \gamma(x, \smooth{\gamma} \eta(x))
-    \int r(y, \smooth{r} \eta(y)) q(x, dy) ,
+    \theta \gamma(x, \eta)
+    \int r(y, \eta) q(x, dy) ,
 $$
@@
 $$
-    q_\theta^\mathfrak{m}(x,\eta,  dy)
+    q_\theta^\mathfrak{m}(x,\eta,dy)
     :=
     \frac{
-        r(y, \smooth{r} \eta(y)) q_\theta(x, dy)
+        r(y, \eta) q_\theta(x, dy)
     }{
-        \int r(z, \smooth{r} \eta(z)) q_\theta(x, dz)
+        \int r(z, \eta) q_\theta(x, dz)
     } .
@@
     \frac{
-        \DG\left[ f(\cdot) r(\cdot, \smooth{r} \eta(\cdot)) \right](x)
+        \DG\left[ f(\cdot) r(\cdot, \eta) \right](x)
         - 
-        f(x) \DG\left[ r(\cdot, \smooth{r} \eta(\cdot)) \right](x)
+        f(x) \DG\left[ r(\cdot, \eta) \right](x)
     }{
-        r(x, \smooth{r} \eta^{N}(x))
+        r(x, \eta^{N})
     } .
@@
 (i.e.,~$\meanq = 0$ and $\covq = I$), $\DG = \Delta$,
-and~(\ref{weighted dispersal}) is equal to
+and so~(\ref{weighted dispersal}) is equal to
 \begin{align*}
@@
 \begin{enumerate}
+            \addtocounter{enumi}{2}
 \item The function $F(x,m)$ satisfies 
@@
 in certain situations where we consider a sequence of $f$ with increasing upper bounds.
-We now give two concrete situations in which the fourth condition is satisfied.
+We now give two concrete situations in which condition~\ref{gamma_B_condition} is satisfied.
 
@@
 and $\eta = \delta_x$
-(i.e., the population has all individuals at a single location)
+(i.e., the population has all individuals at a single location),
 in which case the mean rate of change of the total population size
-is $\int (r(y, N \smooth{r}(y) ) - r(x, N \smooth{r}(x))) q_\theta(x, dy)$;
+is $\int (r(y, N \rho_r(y) ) - r(x, N \rho_r(x))) q_\theta(x, dy)$;
 the first condition of Lemma~\ref{lem:conditions on r} would ensure this is of order $1/\theta$.
@@
 $\sigma_r+1/\theta <\sigma_\gamma$, so that the establishment probability of a juvenile
-is controlled by individuals that are already `felt' by the fecundity kernel $\rho_\gamma$
+is controlled by individuals that are already `felt' by the fecundity-regulating kernel $\rho_\gamma$
 at the location of their parent.
@@
 And, are interactions pointwise in the limit or nonlocal?
+See Figure \ref{fig:super_vs_det_2d} for snapshots of the population
+from direct simulation of the process using SLiM \citep{haller_slim_2019}
+illustrating this first dichotomy.
 Below we have results for deterministic limits with pointwise and nonlocal interactions,
 and for superprocess limits with nonlocal interactions.
-See Figure \ref{fig:super_vs_det_2d} for snapshots of the population
-from direct simulation of the process using SLiM \citep{haller_slim_2019}.
 
@@
 ${\cal D}([0,\infty),\measures)$ is said to be tight if the corresponding
-sequence of distributions
-is tight, so that any infinite sequence has a weakly convergent subsequence.
-Our first result establishes tightness of our rescaled population processes in 
+sequence of distributions is tight,
+i.e., that any infinite subsequence has a weakly convergent subsubsequence.
+Our first main result establishes tightness of our rescaled population processes in 
 the case in which interactions remain nonlocal under the scaling, and 
@@
     \end{align}
-    Furthermore, if $\alpha = 0$ the limit is deterministic.
+    If $\alpha = 0$ the limit is deterministic.
 \end{theorem}
@@
 to~\cite{dawson:1993, perkins:1992}, and \cite{donnelly/kurtz:1999} 
-for approaches to showing that the martingale problem is well-posed in the case $\alpha>0$.
-
-Recall the following notion of solution to a PDE.
+for approaches to showing that these sorts of martingale problems are well-posed.
+
+For the deterministic case of $\alpha=0$,
+the limiting process is a weak solution to a nonlocal PDE.
+We next describe some situations in which more is known
+about uniqueness and whether the solution is close to the corresponding local PDE.
+First, recall the following notion of solution to a PDE.
 \begin{definition}[Weak solutions]
@@
 equation and the classical PDE through a Feynman-Kac formula.
+
 \begin{proposition}
     \label{prop:nonlocal_to_local}
-Recall the notation $\rho^\epsilon_F(x)=\rho_F\big(x/\epsilon)/\epsilon^d$.
+Let notation $\rho^\epsilon_F(x)=\rho_F\big(x/\epsilon)/\epsilon^d$.
 Assume $\varphi_0\in L^2(\IR)$ is a positive, uniformly Lipschitz, and uniformly bounded function. 
@@
 Assumptions~\ref{def:model_setup}.
-Then, for all $T>0$ there exists a constant $K=K(T, \Vert \varphi_0 \Vert_\infty)>0$,
+Then, for all $T>0$ there exists a constant $K=K(T, \Vert \varphi_0 \Vert_\infty) < \infty$
 and a function $\delta(\epsilon)$ (dependent on $\rho_F$) with $\delta(\epsilon)\to 0$ 
@@
 \end{proposition}
+
 \begin{remark}
@@
 \end{remark}
-Our second example is a nonlocal version of a porous medium equation with
-logistic growth. That is, 
-we consider non-negative solutions to the equation
+
+Our second example 
+in which we know solutions to the nonlocal PDE converge to
+solutions of the local PDE as interaction distances go to zero
+is a nonlocal version of a porous medium equation with logistic growth.
+That is, we consider non-negative solutions to the equation
 \begin{equation}
@@
 to~(\ref{mollified equation}) can be obtained using the approach
-of~\cite{lions/mas-gallic:2001}.
-
-We should like to prove that as $\epsilon\to 0$ we have
+of~\cite{lions/mas-gallic:2001}, so
+we should like to prove that as $\epsilon\to 0$ we have
 convergence to the solution to the porous medium equation with
@@
 
+\comment{TODO: restrict to Gaussian case}
 \begin{proposition}
@@
 
-Theorem \ref{thm:nonlocal_convergence}, combined with Proposition \ref{prop:nonlocal_to_local},
+Theorem \ref{thm:nonlocal_convergence},
+combined with Proposition \ref{prop:nonlocal_to_local} or~\label{nonlocalPME to PME}
 implies that we can take the limit $N \to \infty$
@@
 Further suppose that $F(m)$ is a polynomial with $F(m)\ind_{m\geq 0}$ bounded above.
-We assume that $\langle 1,\eta_0\rangle$ is bounded, and that for all 
+Assume that $\langle 1,\eta_0\rangle$ is bounded, and that for all 
 $x\in\IR^d$ and $k\in \IN$,
@@
 \[
-	\int \IE\big[\rho_F^\epsilon*\eta_0(x)^k\big] dx<\infty.
+    \limsup_{\epsilon \to 0} \int \IE\big[\rho_F^\epsilon*\eta_0(x)^k\big] dx<\infty.
 \]
@@
 it is clear that for finite $N$, since individuals are born one at a time, 
-one could construct the distribution of a lineage $(L_t^N)_{t=0}^T$
+one could construct the lineage $(L_t^N)_{t=0}^T$
 given the history of the population $(\eta^N_t)_{t = 0}^T$,
@@
 region is equivalent to looking at the individuals in that region with the $k$ lowest levels.
-Moreover, as we pass to 
-the infinite population (and therefore infinite level) limit,
-the collection of (individual, level) pairs 
-converges, Theorem~\ref{thm:lookdown_convergence}.
+Moreover, as we pass to the infinite population limit,
+the collection of (individual, level) pairs converges,
+as we show in Theorem~\ref{thm:lookdown_convergence}.
 See~\citet{etheridge/kurtz:2019} for an introduction to these ideas.
@@
 and trace its line of descent. 
-This will, in principle, allow us to calculate, for each $y\in\IR^d$, the proportion of
+This will allow us to calculate, for each $x$ and $y\in\IR^d$, the proportion of
 the population at location $x$ in the present day population that are descended from 
@@
 
-We focus on the simplest situation in which the population process is deterministic.
+We focus on the simplest situation, that in which the population process is deterministic.
 However, the results here apply when the population process solves 
@@
 and our results can
-be seen as a first step towards understanding genealogies for very high population 
-densities. 
+be seen as a first step towards understanding genealogies for high population densities.
+
 \begin{definition}[Ancestral lineage] 
@@
     the ancestral lineage of an individual sampled from the
-population at $y$ at time $T$, by setting $L_s$
+population at $y$ at time $T$, by setting $L_0=y$ and $L_s$
     to be the position of the unique ancestor of that individual at time $T - s$.
@@
 
-We now turn to some examples and applications.
+We now discuss some consequences of these results.
 
@@
 
-Equation~(\ref{eqn:nonlocal_pde}) is a nonlocal version of a reaction diffusion equation with nonlinear
-diffusion; in other words the diffusivity of the population depends on the population
-density. Passing to the classical limit, we recover equations
-like~(\ref{PME}).
+Equation~(\ref{eqn:nonlocal_pde}) is a nonlocal version of a reaction diffusion equation;
+the diffusion is nonlinear if $\gamma$ depends on population density:
+in other words, if the diffusivity of the population depends on the population density.
+Passing to the classical limit, we recover equations like~(\ref{PME}).
 Such equations are widely used in a number of contexts in biology in which
-it is clear that motility within a population varies with population density.
+motility within a population varies with population density.
 For example, density dependent dispersal is a common feature in spatial
@@
 thought of as modelling the density of an expanding population. 
-\cite{li/buenzli/simpson:2022} write down an interacting particle
-system on a hexagonal
-lattice (with at most one individual per site) that incorporates an effect
-of local crowding on individual motion. Their equation
-corresponds to a reaction-diffusion equation with nonlinear diffusion and a 
-bistable reaction term of the form~(\ref{Birzu nonlinearity}) and they
-investigate the interplay between nonlinear diffusion and long-term 
-survival or extinction of the population. We focus instead on 
-the monostable reaction of~(\ref{PME}).
+We focus instead on the monostable reaction of~(\ref{PME}).
 
@@
 and birth rates increase linearly with population density,
-but to compensate, death rates increase slightly faster (also linearly),
-as shown in Figure~\ref{fig:pme_waves}.
+but to compensate, death rates increase slightly faster (also linearly).
 Alert readers will notice that
@@
 getting too big. 
-In practice in our simulations we
+In practice in our simulations shown in Figure~\ref{fig:pme_waves}
 take discrete time steps of length $dt$ (with $dt$ suitably small),
@@
         $\theta/N$ small on the left; large on the right.
-        Simulation is with $\gamma(m) = m$ and $\mu(m) = (1+1/\theta) m - 1/\theta$
-        (implemented by choosing a small $dt$ taking reproduction probability per time step
-        to be $1 - \exp(- dt m)$
-        and death probability to be $\mu(m) = 1 - \exp(-dt ((1+1/\theta) m - 1/\theta))$);
-        values of $\theta$ are 1 and 100, respectively, and both values of $N$ are the same.
-	\comment{FROM ALISON Should we say what N is??}
+        % Simulation is with $\gamma(m) = m$ and $\mu(m) = (1+1/\theta) m - 1/\theta$
+        % (implemented by choosing a small $dt$ taking reproduction probability per time step
+        % to be $1 - \exp(- dt m)$
+        % and death probability to be $\mu(m) = 1 - \exp(-dt ((1+1/\theta) m - 1/\theta))$);
+        Values of $\theta$ are 1 and 100, respectively, and both have $N$ set
+        so that the density is roughly 100 individuals per unit of habitat
+        (as displayed on the vertical axis).
+        See text for details of the simulations.
         \label{fig:pme_waves}
@@
 the solution converges to \eqref{eqn:pme_wave} \citep{kamin/rosenau:2004}.
-In Figure~\ref{fig:pme_waves} we show simulations of the individual based model described above.
-They display travelling wave solutions qualitatively similar to solutions of~(\ref{PME}),
+In Figure~\ref{fig:pme_waves} we show simulations of the individual based model described above,
+which display travelling wave solutions qualitatively similar to solutions of~(\ref{PME}),
 with better agreement for smaller $\theta/N$
@@
 \begin{equation} \label{eqn:fkpp_generator}
-    \Lgen_1  f
+    \Lgen_F  f
     =
@@
 depend on the part of the wave not well-approximated by a smooth profile,
-in agreement with the results described in Section~\ref{introduction}.
+in agreement with the previous results referred to in the Introduction.
 
@@
 for a given $s \in (0,2)$.
-Once again we have taken $r=\gamma=1$, but now the reaction term is bistable.
+Once again we have taken $r=\gamma=1$, but now the reaction term
+$F(x,m) = (1-m) (2m-1+s)$ is bistable.
 This equation can be used to model the motion of so-called 
 hybrid zones in population genetics; see, for example,
-\cite{barton:1979, gooding:2018, etheridge/gooding/letter:2022}.
+\citet{barton:1979}, \citet{gooding:2018}, and \citet{etheridge/gooding/letter:2022}.
 This equation has an explicit travelling wave solution with speed $s$
@@
 \begin{align*}
-\Lgen_2 f
+\Lgen_A f
     &=
@@
 $$
-    m(x) \propto e^{sx}(1+e^x)^{-2},
+    m_A(x) \propto e^{sx}(1+e^x)^{-2},
 $$
@@
 \begin{align*}
-    \Lgen_3 f
+    \Lgen_P f
     &=
@@
 \begin{align*}
-    m(\xi)
+    m_P(\xi)
     &\propto
@@
 with certain parameter combinations, the population spontaneously forms a regular grid
-of more or less dicrete patches, separated by areas with nearly no individuals,
+of stable, more or less discrete patches, separated by areas with nearly no individuals,
 as shown in Figure~\ref{fig:clumping}.
@@
 and has been described in similar models, e.g.,
-by \citet{britton1990spatial,sasaki1997clumped,hernandezgarcia2004clustering,young2001reproductive,berestycki2009nonlocal}.
+by \citet{britton1990spatial,sasaki1997clumped,hernandezgarcia2004clustering,young2001reproductive}, and \citet{berestycki2009nonlocal}.
 \comment{FROM ALISON: I rewrote the rest of this section - please check!}
-These patches can be stable. For example, if
-the density-dependent effects of individuals
-extend farther, but not too much farther, than the typical dispersal distance,
+For example, if the density-dependent effects of individuals extend farther (but not too much farther)
+than the typical dispersal distance,
+then depending on the interaction kernel
 new offspring landing between two clumps
@@
 constant solution $\varphi\equiv\varphi_0$ is a nontrivial equilibrium
-of~\eqref{general deterministic limit}. However, it may not be unique,
-it may be unstable, and a stable solution may have 
-oscillations on a scale determined by the interaction distance.
+of~\eqref{general deterministic limit}. However, it may be not unique and/or unstable,
+and a stable solution may have oscillations on a scale determined by the interaction distance.
 
@@
 \[
-	\frac{\sigma^2}{\epsilon^2}v^2\left(-\varphi_0 r_0\gamma_0'
-	-r_0\gamma_0e^{2\pi^2v^2}\right)+\varphi_0F_0',
+	\frac{\sigma^2}{\epsilon^2}v^2 r_0 \left(-\varphi_0 \gamma_0' - \gamma_0 e^{2\pi^2v^2}\right)+\varphi_0F_0',
 \] 
@@
 Consider a deterministic,
-continuous population generated by parameters $\gamma$, $\mu_\theta$, and $r$,
+continuous population generated by parameters $\gamma$, $r$, and $F$,
 with $\meanq = 0$ and $\covq = I$.
@@
 $$
-   r \Delta(\gamma w) + (r \gamma - \mu_\theta) w = 0 .
+   r \Delta(\gamma w) + F w = 0 .
 $$
-It is easy to see that $w$ does not uniquely specify $\gamma$, $\mu_\theta$, and $r$:
+It is easy to see that $w$ does not uniquely specify $\gamma$, $F$, and $r$:
 let $\lambda(x)$ be a smooth, nonnegative function on $\IR^d$,
-and let $r'(x, m) = \lambda(x) r(x, m)$ and $\mu_\theta'(x, m) = \lambda(x) \mu_\theta(x, m)$
+and let $r'(x, m) = \lambda(x) r(x, m)$ and $F'(x, m) = \lambda(x) F(x, m)$
 (and, let $\gamma' = \gamma$).
-Then the population with parameters $\gamma'$, $\mu_\theta'$, and $r'$
+Since $\mu = r \gamma - F/\theta$,
+this corresponds to multiplying both establishment probabilities and death rates by $\lambda$.
+Then the population with parameters $\gamma'$, $r'$, and $F'$
 has the same stationary profile(s) as the original population.
@@
 {\em We reiterate that in our prelimiting model,
-the population is represented by a point measure in which each
+the population is represented by a point measure $\eta^N$ in which each
 individual is assigned a mass $1/N$. We use the term ``population density'' for
@@
     \\
-    + \int \int f(x) \theta \Big(
+    + \int f(x) \theta \Big(
         r(x,\eta) \gamma(x,\eta)
@@
 F(x,\eta)
-\eta(dx) .
+\eta(dx) ,
 \end{equation}
-This explains the form of the martingale of Theorem~\ref{thm:nonlocal_convergence}.
+which explains the form of the martingale of Theorem~\ref{thm:nonlocal_convergence}.
 
@@
 $$
-\int_{\IR^d}
+\int
     N \theta \gamma(x,\eta)
@@
 \left\{
-    \int_{\IR^d}
+    \int
         \gamma(x,\eta)
@@
     +
-    \int_{\IR^d}
+    \int
         \mu_\theta(x,\eta)\frac{1}{N^2}f^2(x) 
@@
     \frac{\theta}{N}
-	\int_{\IR^d}\left\{
-		\gamma(x, \eta) \int f^2(y) r(y, \eta) q_\theta(x, dy) + f^2(x) \mu_\theta(x, \eta) \right\}
-    \eta(dx) .
+	\int\left\{
+		\gamma(x, \eta) \int f^2(y) r(y, \eta) q_\theta(x, dy) + f^2(x) \mu_\theta(x, \eta)
+    \right\} \eta(dx) .
 \end{align*}
@@
 Although our proof of Theorem~\ref{thm:lineages}
-uses the explicit representation in terms of the lookdown process,
+uses an explicit representation in terms of the lookdown process,
 the result can be understood through informal calculations.
@@
 $$
-\theta N\eta^N_t(dx)    \gamma(x, \eta^N_t) q(x, dy) r(y, \eta^N_t) .
+\theta N\eta^N_t(dx)    \gamma(x, \eta^N_t) q_\theta(x, dy) r(y, \eta^N_t) .
 $$
 Suppose that $\eta^N$ did have a density (in the prelimit it does not),
-say $\eta^N_t(dx) = \varphi^N_t(x) dx$. Informally, the 
-probability that a randomly chosen individual near $y$
+say $\eta^N_t(dx) = \varphi^N_t(x) dx$.
+Informally,
+since the number of individuals near $y$ is $N\varphi^N_t(y) dy$,
+the probability that a randomly chosen individual near $y$
 is a new offspring from a parent at $x$ in $[t, t+dt)$ is
@@
 that of ancestral lineages) when we pass
-to the scaling limit in our model will be justified via a lookdown construction.
+to the scaling limit in our model will be justified via this construction.
 In this section 
@@
 The general set-up is as follows.
-Each individual will be labelled with a ``level'',
-which will be a number in $[0, N]$.
+Each individual will be labelled with a ``level'', a number in $[0, N]$.
 We will still encode the process embellished by these levels
@@
 and 
-the limiting ``spatial-level'' process will still be a point measure.
-In this way, 
-we explicitly retain the notion of individuals and lineages as we pass to the 
-infinite-population limit.
+the limiting ``spatial-level'' process will still be a point measure,
+and so we explicitly retains the notion of individuals and lineages
+in the infinite-population limit.
 
@@
 We shall write 
-\begin{align} \label{b_defn}
+\begin{align*}
     b_\theta(x, \eta)
@@
     \right) ,
-\end{align}
+\end{align*}
 which captures the local net difference between reproduction and death,
@@
 and so 
-\begin{equation*} 
+\begin{equation}  \label{b_defn}
 b_\theta(x, \eta)
@@
     + F(x, \eta). 
-\end{equation*}
+\end{equation}
 Under Assumptions~\ref{def:model_setup}, as $\theta \to \infty$,
 $c_\theta(x, \eta)$ will tend to $\alpha \gamma(x, \eta) r(x, \eta)$
-and $b_\theta(x, \eta)$ will tend to
 \begin{equation}
 \label{eqn:b_limit}
-    \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta) .
+    b_\theta(x, \eta) \to \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta) .
 \end{equation}
@@
     \left(
-    \frac{\theta}{N}
         c_\theta(x, \eta) u^2
@@
 We need some notation. 
-Write ${\mathcal C}={\mathcal C}(\IR^d\times [0,\infty)$ for the counting measures 
+Write ${\mathcal C}={\mathcal C}(\IR^d\times [0,\infty))$ for the counting measures 
 on $\IR^d\times [0,\infty)$ and ${\mathcal C}_N$ for the subset consisting of 
@@
 Once this is verified (along with some boundedness conditions)
-the Markov Mapping Theorem (Theorem~\ref{thm:mmt}; also see \citep{etheridge/kurtz:2019})
+the Markov Mapping Theorem (Theorem~\ref{thm:mmt}; also see \citet{etheridge/kurtz:2019})
 tells us that by ``removing labels'' from the lookdown process $\lp$
@@
     in the sense of \eqref{eqn:conditionally_uniform}.
-    Then, 
-	\comment{FROM ALISON deleted `any sequence of stochastic processes'
-	which didn't make sense - we want the ones already specified }
-	$(\lp_t^N)_{t \ge 0}$
-    has a subsequence which converges in distribution as $N \to \infty$
+    Then, $(\lp_t^N)_{t \ge 0}$ has a subsequence which converges in distribution as $N \to \infty$
     to a measure-valued process $(\lp_t)_{t \ge 0}$
-    with $\lp_0$ conditionally Poisson given $\eta_0 = \kappa(\lp_0)$
+    with $\lp_t$ conditionally Poisson given $\eta_t = \kappa(\lp_t)$ for each $t$
     in the sense of \eqref{eqn:conditionally_poisson},
@@
 Although we have a single construction that couples the processes across all $N$,
-unlike in \citet{kurtz/rodrigues:2011},
-the actual trajectories, $X_a(\cdot)$, do not necessarily coincide for 
-different values of $N$, since they are affected by the whole population process.
+unlike in \citet{kurtz/rodrigues:2011} the actual trajectories, $X_a(\cdot)$,
+do not necessarily coincide for different values of $N$,
+since they are affected by the whole population process.
 However, this does suggest approximating the genealogies in the infinite density limit
@@
 Given $\eta_0 \in \measures$,
-let $(x_i, u_i)$ be the points of a Poisson process $R_0$
+let $(x_i, u_i)$ be the points of a Poisson process
 on $\IR^d \times [0, \infty)$ 
@@
 (the product of $\eta_0$ and Lebesgue measure).
-For each $i$, with $(x_i, u_i)$ the $i^\text{th}$  point of $R_0$, begin a line of descent
+For each $i$, begin a line of descent
 with label $i$, location $X_i(0) = x_i$, 
@@
 Write $\tau_a$ for the birth time of the label $a$ and 
-$\sigma_a = \lim_{K \to \infty} \inf\{t \ge 0: U_a(t) > K\}$
+$\sigma_a = \lim_{u_0 \to \infty} \inf\{t \ge 0: U_a(t) > u_0\}$
 the time the level hits $\infty$.
@@
 Lemma~\ref{lem:conditions on r} is satisfied.
-\comment{BEGIN NEW VERSION}
 We write
@@
 
-\comment{BEGIN PREVIOUS VERSION}
-We write
-\begin{align*}
-    r\big(y,\rho_r*\eta(y)\big) f(y) - r\big(x,\rho_r*\eta(x)\big) f(x)
-    &=
-    \sum_i (y_i - x_i) \partial_{x_i} \Big( r\big(x,\rho_r*\eta(x)\big) f(x) \Big) 
-    \\ &\qquad {}
-    +
-    \frac{1}{2} \sum_{ij} (y_i - x_i)(y_j - x_j)
-        \partial_{x_i x_j} \Big( r\big(z, \smooth{r}\eta(z)\big) f(z) \Big) ,
-\end{align*}
-where $z = \kappa x + (1-\kappa) y$ for some $0 \le \kappa \le 1$.
-Condition~\ref{control through r} 
-gives uniform bounds on the derivatives of $r(x, \rho_r*\eta(x))$
-in this expression and so, provided $f$ also has uniformly bounded first and second derivatives,
-we have a bound of the form
-\begin{align*}
-|B^\theta_f|
-\leq
-        K_1 \left|
-            \theta \int_{\IR^d} \sum_i (y_i - x_i) q_\theta(x, dy)
-        \right|
-        +
-        K_2 \left|
-            \theta \int_{\IR^d} \sum_{ij} (y_i - x_i) (y_j - x_j)  q_\theta(x, dy)
-        \right| 
-\end{align*}
-for suitable constants $K_1$, $K_2$
-that depend on $f$ only through 
-$\max_i \|\partial_{x_i} f\|_\infty$ and
-$\max_{ij} \|\partial_{x_i} \partial_{x_j} f\|_\infty$.
-This is bounded uniformly because
-$q_\theta(x, dy)$ is the density of a Gaussian with mean $\meanq(x)/\theta$
-and covariance $\covq(x)/\theta$, and both $\meanq(x)$ and $\covq(x)$
-are bounded uniformly in $x$ under Assumptions~\ref{def:model_setup}.
-Since $\gamma$ is bounded as well, so is $|\gamma B^\theta_f|$.
-\comment{END OLD VERSION}
-
-Now suppose that instead
+Now suppose instead that
 Condition~\ref{control through gamma} of Lemma~\ref{lem:conditions on r} is satisfied.
@@
     and 
-    $K_4 = \sup_{x,m} \max_{i,j} |\partial_{x_i x_j} f(x)r(x, m)|$, since
-\[\big|\partial_{x_i}\big(f(x)r(x,\rho_r*\eta(y))\big|\leq K_3\]
-and
-\[\big|\partial_{x_ix_j}\big(f(x)r(x,\rho_r*\eta(y))\big|\leq K_4,\]
-the first term
-is bounded exactly as above. For the second, 
+    $K_4 = \sup_{x,m} \max_{i,j} |\partial_{x_i x_j} f(x)r(x, m)|$,
+% since
+% \[\big|\partial_{x_i}\big(f(x)r(x,\rho_r*\eta(y))\big|\leq K_3\]
+% and
+% \[\big|\partial_{x_ix_j}\big(f(x)r(x,\rho_r*\eta(y))\big|\leq K_4,\]
+the first term is bounded exactly as above. For the second, 
     \begin{multline*}
@@
 
-% % % % % % % % % % % % %
-\subsubsection{Compact Containment Condition}
-
-\comment{FROM ALISON Does this merit being a subsubsection - if so I would expect 
-some others too}
-
 As advertised, we work with the one-point compactification of $\IR^d$ and
@@
 \end{align}
-where $M^N_t(f)$ is a martingale and $B^\theta_f$ is defined in \ref{generator Bf}.
+where $M^N_t(f)$ is a martingale and $B^\theta_f$ is defined in \eqref{generator Bf}.
 First note that Condition~\ref{gamma_B_condition} of Assumptions~\ref{def:model_setup}
@@
     for some $C$ (independent of $N$).
-    Now, let $M^*_t(f) = \sup_{0 \le s \le t} M_t(f)$,
-    and as before let $[M(f)]_t$ be the quadratic variation of $M_t(f)$,
+    Now, let $M^{N*}_t(f) = \sup_{0 \le s \le t} M^N_t(f)$,
+    and as before let $[M^N(f)]_t$ be the quadratic variation of $M^N_t(f)$,
     so that by the Burkholder-Davis-Gundy inequality, there is a $C'$ so that,
@@
     \begin{align*}
-        \IE\left[ M^*_t(1) \right]
+        \IE\left[ M^{N*}_t(1) \right]
         &\le
-        C' \IE\left[ \sqrt{[M(1)]_t} \right]
+        C' \IE\left[ \sqrt{[M^N(1)]_t} \right]
         \\ &\le
-        C'\left( 1 + \IE\left[ [M(1)]_t \right] \right)
+        C'\left( 1 + \IE\left[ [M^N(1)]_t \right] \right)
         \\ &=
@@
         \\ &=
-        C'\left( 1 + \IE\left[
+        C'\Big( 1 + \IE\Big[
             \int_0^t
             %\int_{\IR^d} 
-	    \Big\langle\left\{
+	    \Big\langle\Big\{
                 \frac{2\theta}{N} \gamma(x, \eta^N_s) r(x, \eta^N_s)
+        \\ &\qquad\qquad\qquad\qquad \qquad {}
 		+ \frac{\gamma(x,\eta_s^N)}{N} 
 		B^\theta_1(x, \eta^N_s)-\frac{1}{N}F(x,\eta^N_s)
-            \right\}, \eta_s^N(dx) \Big\rangle
+            \Big\}, \eta_s^N(dx) \Big\rangle
             ds
-            \right] \right) .
+            \Big] \Big) .
     \end{align*}
@@
 	with $f=1$ to see that
-	\begin{equation}
+	\begin{align}
 		\label{integral of -F}
-\IE\left[\int_0^t \Big\langle -F(x, \eta^N_s), \eta^N_s(dx)
-	\Big\rangle ds \right]
-	=\IE[\langle 1, \eta^N_0\rangle] -\IE[\langle 1,\eta^N_t\rangle]
-	+\IE\left[\int_0^t\Big\langle %int_{\IR^d}
-\gamma(x,\eta_s^N)
-	B^\theta_1(x, \eta_s^N),\eta_s^N(dx)\Big\rangle ds\right],
-	\end{equation}
+        \begin{split}
+\IE\left[\int_0^t \Big\langle -F(x, \eta^N_s), \eta^N_s(dx) \Big\rangle ds \right]
+        &= \IE[\langle 1, \eta^N_0\rangle] -\IE[\langle 1,\eta^N_t\rangle]
+            \\&\qquad {}
+	+ \IE\left[\int_0^t\Big\langle \gamma(x,\eta_s^N) B^\theta_1(x, \eta_s^N),\eta_s^N(dx)\Big\rangle ds\right],
+        \end{split}
+	\end{align}
 which is bounded since $\gamma (x,\eta)$ and $B^\theta_1(x,\eta)$ are both bounded and 
@@
     Since $\theta/N \to \alpha < \infty$,
-    combining constants, we obtain that
-    \begin{align*}
-        \IE\left[ M^*_t(1) \right]
+    combining constants, we obtain that for some $C''$,
+    \begin{align*}
+        \IE\left[ M^{N*}_t(1) \right]
         &\le
@@
     \begin{align*}
-        \IE\left[\sup_{0 \le s \le t} \langle 1, \eta^N_s \rangle \right]
+        \IE\left[\sup_{0 \le s \le T} \langle 1, \eta^N_s \rangle \right]
         &\le
@@
         + \IE\left[
-            \sup_{0 \le s \le t}
+            \sup_{0 \le t \le T}
             \int_0^t 
-	    %\int_{\IR^d} 
 	    \Big\langle\left\{
@@
         \right]
-        \\
- & + \IE[M^*_t(1)] 
+        \\ & \qquad\qquad {}
+        + \IE[M^{N*}_t(1)] 
         \\
@@
         + C \IE\left[
-            \int_0^t \sup_{0 \le s \le t} \langle 1, \eta^N_s \rangle ds
+            \int_0^T \sup_{0 \le s \le t} \langle 1, \eta^N_s \rangle dt
         \right]
@@
     \begin{align*}
-        \IE\left[\sup_{0 \le s \le t} \langle 1, \eta^N_s \rangle \right]
+        \IE\left[\sup_{0 \le s \le T} \langle 1, \eta^N_s \rangle \right]
         &\le
         C''' 
-        \left(1+ \IE[\langle 1, \eta^N_0 \rangle]\right) e^{2tC} .
+        \left(1+ \IE[\langle 1, \eta^N_0 \rangle]\right) e^{2TC} .
     \end{align*}
     For any $T$,
-    the inequality on the right is bounded above by a constant $C(T)$ independent of $N$.
+    the quantity on the right is bounded above by a constant $C(T)$ independent of $N$.
     As a result, for any $K > 0$,
@@
 provides a uniform bound on $\gamma B^\theta_f$, but we only know
-that $F$ is bounded above. However, since, by 
-assumption, for each fixed value of
-$m$, $\sup_{k\leq m}|F(x,k)|$ is uniformly bounded as a function of $x$, 
-noting that $\smooth{F}\eta\leq
-\langle 1,\eta\rangle\|\rho_F\|_\infty$,
-and using Lemma~\ref{lem:eta_compact_containment} 
+that $F$ is bounded above. However, by assumption, for each fixed value of
+$m$, $\sup_{k\leq m}|F(x,k)|$ is uniformly bounded as a function of $x$.
+Noting that $\smooth{F}\eta\leq \langle 1,\eta\rangle\|\rho_F\|_\infty$,
+we can use Lemma~\ref{lem:eta_compact_containment} 
 to choose $N_0$ and $K$ such that
@@
 $$
-    \IP\left\{\sup_{0\leq s\leq T}\langle 1, \eta_s^N\rangle\geq K\right\} < \nu,
+    \IP\left\{\sup_{0\leq s\leq T}\langle 1, \eta_s^N\rangle\geq K\right\} < \nu/2,
 $$
@@
     <
-    \nu/2,
+    \nu/4,
     \qquad
-    \sup_{x,\eta}\gamma(x,\eta)B^\theta_f(\,\eta)\delta_1<\nu/2,
+    \sup_{x,\eta}\gamma(x,\eta)B^\theta_f(\,\eta)\delta_1 < \nu/4,
 $$
@@
 
-We collect the results of the last two subsections into a proposition.
+We collect the implications of the last two lemmas into a proposition.
+
 \begin{proposition}[Tightness of $(\eta^{N}_t)_{t \geq 0}$]
@@
     is dense in the space of bounded continuous functions on $\cmeasures$,
+    and tightness of $\langle f, \eta_t^N \rangle$ extends to sums and products of this form
+    by Lemma~\ref{lem:product_tightness},
     we have relative compactness in $\mathcal{D}_{[0,\infty)}(\cmeasures)$.
@@
 \end{equation}
-A process $(\eta^N_t)_{t \geq 0}$ 
-satisfies the martingale characterization of Definition~\ref{defn:mgale_construction}
-if and only if it is a solution 
-to the $(\Pgen^N, \eta_0)$-martingale problem, i.e.,
-if for all such test functions 
+The process $(\eta^N_t)_{t \geq 0}$ of Definition~\ref{defn:mgale_construction}
+is the unique solution to the $(\Pgen^N, \eta_0)$-martingale problem, i.e., if
 $$
@@
     &:= G'(\langle f, \eta \rangle)
-                   %\times 
-\left\{
                    \big\langle
@@
                     \eta(dx)
-                    \big\rangle
-                   \right\}\\
+                    \big\rangle \\
                &\qquad {}
-               + \frac{\alpha}{2} G''(\langle f, \eta \rangle)
-                  %\times 
-\left\{
+               + \alpha G''(\langle f, \eta \rangle)
                   \big\langle
-                    2\gamma\left( x, \eta \right)
+                    \gamma\left( x, \eta \right)
                     r\left(x,\eta \right)
@@
                     \eta (dx)
-                    \big\rangle 
-                  \right\}.
+                    \big\rangle  .
 \end{aligned}    
@@
 A process $(\eta^{\infty}_t)_{t \geq 0}$ 
-satisifes the martingale characterization of equations~\ref{eqn:limiting_mgale_problem}
-and~\ref{eqn:limiting_mgale_variation}
+satisifes the martingale characterization of equations~\eqref{eqn:limiting_mgale_problem}
+and~\eqref{eqn:limiting_mgale_variation}
 if and only if it is a solution 
@@
 $h_1,\ldots,h_k$ on $\cmeasures$.
-
 Since $(\eta^N_t)_{t\geq 0}$ is Markov, the tower property gives that,
-for each choice of $G_f$ and for each $N$,
+% for each choice of $G_f$ and 
+for each $N$,
 \begin{equation}
@@
 \prod_{i=1}^{k}h_i(\eta^{N}_{t_i})
-\right]=0
+\right]=0 .
 \end{equation}
-for all $k\geq 0$, $0\leq t_1<t_2<...,t_k \leq t < t+\tau$,
-and $h_1,...,h_k \in \mathcal{C}_{b}(\cmeasures)$.
-%
+% for all $k\geq 0$, $0\leq t_1<t_2<...,t_k \leq t < t+\tau$, and $h_1,...,h_k \in \mathcal{C}_{b}(\cmeasures)$.
 Therefore, it suffices to show that 
@@
 \begin{aligned}
-\Pgen^{N} G_f(\eta):=& G'(\langle f, \eta \rangle)\int_{\IR^d}  
-\theta\Big\langle\int_{\IR^d} \big\{f(y)\gamma(x, \eta) r(y,\eta) 
--f(x)\mu_\theta(x, \eta)\big\}q_{\theta}(x,dy), \eta(dx)\Big\rangle\\
+\Pgen^{N} G_f(\eta)
+    :=& 
+    G'(\langle f, \eta \rangle)\int_{\IR^d}  
+\theta\Big\langle \gamma(x,\eta) \int_{\IR^d} f(y)r(y,\eta) q_{\theta}(x,dy), 
+    - f(x)\mu_\theta(x,\eta), \eta(dx)\Big\rangle\\
 &+\frac{1}{2}\frac{\theta}{N}G''(\langle f, \eta \rangle)\int_{\IR^d} 
@@
 \mu_\theta(x, \eta), \eta(dx)\Big\rangle\\
-&+\frac{1}{6}\frac{\theta}{N^2}\Big\langle \big\{
+&+\frac{1}{6}\frac{\theta}{N^2}\Big\langle
 G'''(w) \gamma(x, \eta)\int_{\IR^d} f^3(y) r(y,\eta) 
 q_{\theta}(x,dy)
--G'''(v)f^3(x)\mu_\theta(x, \eta)\big\}, \eta(dx)\Big\rangle
+-G'''(v)f^3(x)\mu_\theta(x, \eta), \eta(dx)\Big\rangle
 \end{aligned}    
 \end{equation}
-%\normalsize
 for some $w,v \in [\langle f,\eta \rangle - \|f\|_\infty/N, 
@@
 Theorem in~(\ref{eq: Convergence of Spatial Generator}).
-Recall that $f$ and $G$ and their derivatives are bounded, $\gamma(x,\eta)$ is
-bounded, and, in the notation of Lemma~\ref{lem:eta_f_bound}
-$\gamma(x,\eta) B^\theta_f(x,\eta)$ is bounded. Moreover $\theta/N^2\to 0$ as $N\to\infty$. Thus we can 
-dominate 
-$\left|
-\Pgen^{N}G_f(\eta^{N}_s)
--\Pgen^{\infty}G_f(\eta^{N}_s)
-\right|$ by 
-a constant multiple of
-$\theta \big\langle |r(x,\eta^N_s)\gamma(x,\eta^N_s)-\mu_\theta(x,\eta^N_s)|,
-\eta^N_s(dx)\big\rangle$, 
-which we  
-recognise as $\langle |F(x,\eta^N_s)|,\eta^N_s(dx)\rangle$.
+Recall that $f$ and $G$ and their derivatives are bounded,
+and so $\gamma(x,\eta)$ is bounded independent of $\theta$.
+Since $\theta/N^2 \to 0$,
+rearranging as in \eqref{eqn:rewritten mean measure}
+and using the convergence of \eqref{eqn:near_critical},
+we deduce that we can dominate
+$\left| \Pgen^{N}G_f(\eta^{N}_s) -\Pgen^{\infty}G_f(\eta^{N}_s) \right|$
+by a constant multiple of $\langle 1+F(x),\eta_s(dx)\rangle$.
 Since $F$ is bounded above, there is a constant $K$ such that $|F|\leq K-F$ so
@@
 population process that we obtained in the previous section solves a nonlocal
-PDE, then if we further scale the kernels 
+PDE, if we further scale the kernels 
 $\rho_r$, $\rho_\gamma$, and $\rho_F$ by setting 
@@
 population density that solves the corresponding ``classical'' PDE. We verify
-this in two examples; in the first the nonlocal equation is a reaction-- diffusion equation
+this in two examples; in the first the nonlocal equation is a reaction diffusion equation
 with the ``nonlocality'' only appearing in the 
@@
 \frac{\|x-y\|}{\sqrt{t}} \int p_{\lambda  t}(w,z)dz = 
-K  \frac{\|x-y\|}{\sqrt{t}},
-\end{align*}
-which proves the result.
+K  \frac{\|x-y\|}{\sqrt{t}} .
+\end{align*}
 \end{proof}
@@
 \begin{lemma} \label{regularityForX2}
-Fix $T>0$. Let $x,y \in \mathbb{R}^d$, $t \in [0,T]$. Let us denote by 
+Fix $T>0$. Let $x,y \in \mathbb{R}^d$, $t \in [0,T]$, and denote by 
 $(Z_t^y)_{t\geq 0}$ and $(Z_t^x)_{t\geq 0}$ independent copies of the 
@@
 Fix $T>0$ and write $M$ for the corresponding constant from 
-Proposition~\ref{BoundednessVarphis}.
+Lemma~\ref{BoundednessVarphis}.
 Let $\| F \|_{M} = \sup_{m \in [0,M]} |F(m)|$.
@@
 \delta_0=\min\Big( \frac{1}{\| F \|_M^{2}},\frac{1}{M e\big(2\| F \|_{M}+ \widehat{K}\big)}, 
-\frac{1}{K_{\varphi_0} + 2 \| F \|_M M},  1\Big).
+    \frac{1}{\widetilde{K} K_{\varphi_0} + 2 \| F \|_M M},  1\Big).
 \]
@@
 \varphi_t(z) 
-\leq e^{\delta^2\| F \|_{M}} \IE_z\big[  \varphi_{t+\delta^2}(Z_{\delta^2})\big]. 
+\leq e^{\delta^2\| F \|_{M}} \IE_z\big[  \varphi_{t-\delta^2}(Z_{\delta^2})\big]. 
 \]
@@
 \end{equation}
-Furthermore, there is a constant $\widetilde{C}(T, \| \varphi_0 \|_\infty) = \widetilde{C} >0 $ 
+Furthermore, there is a constant $\widetilde{C}(T, \| \varphi_0 \|_\infty) = \widetilde{C}$
 such that, for all $0 \leq t \leq T$,
@@
 convergence to the solution to the porous medium equation with
-logistic growth:
-\begin{equation}
-\label{PMEold}
+logistic growth,
+equation~\eqref{PME1}:
+\begin{equation*}
 	\partial_t \psi_t(x)=
@@
 	+\psi_t(x)\left(1-\psi_t(x)\right).
-\end{equation}
+\end{equation*}
 
@@
 First observe that, since $x\log x$ is bounded below, 
-$\int_{-1}^1\psi_t^\epsilon(x)\log\psi_t^\epsilon(x) dx$ is bounded below.
+$\int_{-1}^1\psi_t^\epsilon(x)\log\psi_t^\epsilon(x) dx$ is bounded below,
+and recall that $\psi_t^\epsilon(x) \ge 0$.
 
@@
 Evidently a symmetric argument applies for $x\leq -1$.
-Summing over $x$, we find
+Summing over $x$,
+and using that $\psi \log \psi \ge - \psi |\log \psi| \ind_\psi \le 1$,
+we find
 \begin{equation*}
@@
 \begin{proof}[Proof of Proposition~\ref{nonlocalPME to PME}]
-
 First observe that
@@
 $\epsilon$ and $t\in [0,T]$.
-Now observe that
+
+We shall next show that $\zeta^\epsilon * \psi_t^\epsilon$ solves \eqref{PME1}
+up to a remainder of order $\epsilon$.
+First observe that
 \begin{equation}
 \label{total equation}
-\int\Delta\left((\rho^{\epsilon}*\psi_t^\epsilon)\psi_t^\epsilon\right)\phi  dx =
-\int \nabla(\rho^{\epsilon}*\psi_t^\epsilon)\,
-\psi_t^\epsilon\,\nabla\phi dx +\int \rho^{\epsilon}*\psi_t^\epsilon
-\,\nabla \psi_t^\epsilon
-\, \nabla\phi d x.
+\int\Delta\left((\rho^{\epsilon}*\psi_t^\epsilon)\psi_t^\epsilon\right)\phi  dx
+    =
+    - \int \nabla(\rho^{\epsilon}*\psi_t^\epsilon)\, \psi_t^\epsilon\,\nabla\phi dx
+    -\int \rho^{\epsilon}*\psi_t^\epsilon \,\nabla \psi_t^\epsilon \, \nabla\phi dx.
 \end{equation}
+We would like to show that this is close to $\int (\zeta^\epsilon * \psi^\epsilon_t)^2 \Delta \phi dx$.
 For the first term
@@
 $\tilde{z}=-z$.
-
 To control the term~(\ref{error 1})
@@
 $\zeta^{\epsilon}*\psi_t^\epsilon$ in
-$L^1\cap L^2\big([0,T]\times \IR\big)$, and
+$L^1\cap L^2\big([0,T]\times \IR\big)$, and that
 \begin{multline}

### 2023-04-25 forwards-and-backwards.tex
done with printout pass through

@@
 Following the now classical contributions 
-of~\citet{demasi/ferrari/lebowitz:1986, demasi/presutti:1991, oeschlaeger:1985},
+of~\citet{demasi/ferrari/lebowitz:1986, demasi/presutti:1991, oelschlaeger:1985},
 much of this work has focused on lattice based models with one particle
@@
 Theorem \ref{thm:nonlocal_convergence},
-combined with Proposition \ref{prop:nonlocal_to_local} or~\label{nonlocalPME to PME}
+combined with Proposition \ref{prop:nonlocal_to_local} or~\ref{nonlocalPME to PME}
 implies that we can take the limit $N \to \infty$
@@
     applied to our situation.
-    In the notation of that theorem, $\gamma$ is what we have called $\kappa$ above,
-    $\alpha$ is the transition function that assigns levels uniformly on $[0, N]$ (in the first case)
-    or as a Poisson process with Lesbegue intensity (in the limiting case),
-    and we need a continuous $\psi^N(\lp)$ such that $|A^N f(\lp)| \le c_f \psi^N(\lp)$
+    The function $\gamma$ of that theorem is what we have called $\kappa$ above,
+    and the kernel $\alpha$ of that theorem
+    is the transition function that assigns levels uniformly on $[0, N]$ (in the first case)
+    or as a Poisson process with Lesbegue intensity (in the limiting case).
+    We need a continuous $\psi^N(\lp)$ such that $|A^N f(\lp)| \le c_f \psi^N(\lp)$
     for all $f$ in the domain of $A^N$ (and similarly a function $\psi$ for $A$).
@@
 The process we consider is similar to the state-dependent branching processes
-of \citet{KR}, so one might expect that the proofs there would carry over with little change.
+of \citet{kurtz/rodrigues:2011}, so one might expect that the proofs there would carry over with little change.
 However, there is an important difference:
 Recall that the level $U_a(t)$ of a line of descent evolves as
-$$
+\begin{equation} \label{eqn:u_evolution}
 \dot u = c_\theta(x, \eta) u^2 - b_\theta(x, \eta) u,
-$$
+\end{equation}
 where $b_\theta(x, \eta)$ and $c_\theta(x, \eta)$ are defined in \eqref{b_defn}
 and \eqref{c_defn} respectively.
-Note that $c_\theta(x, \eta) \ge 0$ and $b_\theta(x, \eta)$ may take either sign.
-Assumptions~\ref{def:model_setup} imply that $c^N(x, \eta)$ is bounded,
-while $b^N(x, \eta)$, because of $F(x, \eta)$, is bounded above but not necessarily below.
-In \citet{kurtz/rodrigues:2011}, $b^N$ was bounded above and $c^N$ was bounded away from zero,
-so they noted that if $U_a(t) \ge b^N/c^N$ for some label $a$,
+Note that $c_\theta(x, \eta) \ge 0$, while $b_\theta(x, \eta)$ may take either sign.
+Assumptions~\ref{def:model_setup} imply that $c_\theta(x, \eta)$ is bounded,
+while $b_\theta(x, \eta)$, because of $F(x, \eta)$, is bounded above but not necessarily below.
+In \citet{kurtz/rodrigues:2011}, $b_\theta$ was bounded above and $c_\theta$ was bounded away from zero,
+so they noted that if $U_a(t) \ge b_\theta/c_\theta$ for some label $a$,
 that line of descent would only move upwards from that time onwards.
@@
 for all values of $N$, with a pointwise embedding
-of $(\lp^N_t)_{t \ge 0}$ within $(\lp^{M})_{t \ge 0}$ for $b^N/c^N < N < M$.
-In other words, individuals with levels above $N > b^N/c^N$ at time $t_0$
+of $(\lp^N_t)_{t \ge 0}$ within $(\lp^{M})_{t \ge 0}$ for $b_\theta/c_\theta < N < M$.
+In other words, individuals with levels above $N > b_\theta/c_\theta$ at time $t_0$
 do not affect $(\lp^N_t)_{t \ge t_0}$,
@@
 it does not have this monotonicity:
-for one thing, $b^N$ and $c^N$ depend on the population process $\eta$
+for one thing, $b_\theta$ and $c_\theta$ depend on the population process $\eta$
 and so all individuals can affect all other ones (even those with lower levels).
@@
 
-To complete the description of the process,
-each line of descent
+We first give a description of the lookdown process $\lp^N$ in terms of the lines of descent
+introduced in Section~\ref{sec: individual lines of descent}.
+Each line of descent
 gives birth to lines at higher levels at rate $2 (N - u) c_\theta(x, \eta)$,
@@
 \end{equation}
-and the two lines swap spatial locations with probability 1/2.
+and the two lines swap spatial locations with probability 1/2;
+the level of each line of descent evolves according to equation~\eqref{eqn:u_evolution}.
 
@@
     \int_0^t
-    \big\langle
+    \bigg\langle
         c_\theta(x, \eta^N_s)
@@
 and of the motion of individual lines of descent.
-In other words, the limiting ``line of descent'' construction holds.
+In other words, the limiting ``line of descent'' construction
+of Section~\ref{sec: individual lines of descent} holds.
 
@@
     tightness of one-dimensional distributions,
-    and an application of \citet{EK} Theorem~3.9.1.
+    and an application of \citet{ethier/kurtz:1986} Theorem~3.9.1.
 
@@
     in the sense of \eqref{eqn:conditionally_uniform}
-    and $\lp_0$ is conditionally uniform given $\eta_0$
+    and $\lp_0$ is conditionally Poisson given $\eta_0$
     in the sense of \eqref{eqn:conditionally_poisson}.
@@
         \big\langle
-            2 c^N(x, \eta^N_s) \int_u^N h(v) dv
+            2 c_\theta(x, \eta^N_s) \int_u^N h(v) dv
         ,
@@
             \left(
-                c^N(x, \eta^N_s) u^2
-                - b^N(x, \eta^N_s) u
+                c_\theta(x, \eta^N_s) u^2
+                - b_\theta(x, \eta^N_s) u
             \right)
@@
         \int_0^t
-        \langle 2 c^N(x, \eta_s^N) \int_u^N h(v)^2 dv
+        \langle 2 c_\theta(x, \eta_s^N) \int_u^N h(v)^2 dv
         ,
@@
     \end{align*}
-    Now, note that $0 \le c^N(x, \eta_x^N) \le C_a < \infty$
-    and $b^N(x, \eta_s^N) \le C_b < \infty$,
+    Now, note that $0 \le c_\theta(x, \eta_x^N) \le C_a < \infty$
+    and $b_\theta(x, \eta_s^N) \le C_b < \infty$,
     and we have assumed that $h'(u) \le 0$ (since $h$ is nonincreasing),
@@
         C' \left( 1 + \int_0^T \IE\left[
-        \langle 2 c^N(x, \eta_s^N) \int_u^\infty h(v)^2 dv
+        \langle 2 c_\theta(x, \eta_s^N) \int_u^\infty h(v)^2 dv
         ,
@@
         \Big\rangle ds
-        \\ &\le
-        \langle f, \lp_0 \rangle
-        + M^f_t
-        + \int_0^t \Big\langle
-            c_\theta \int_u^N \int (f(y, u_1) + f(x, u_1)) q^m(x,dy,\eta) du_1
-        \\ {} &\qquad
-            + c_\theta (N - u) \int (f(y, u) - f(x, u)) q^m(x,dy,\eta)
-            + (c_\theta u^2 - b_\theta u) \frac{d}{du} f,
-            \lp_s
-        \Big\rangle ds
     \end{align*}
@@
     follow as in the proof of Lemma~\ref{lem:eta_projections_tightness}:
-    for instance, observe that using that $c_\theta \le C_0$ for some $C_0$,
+    for instance, observe that using that $c_\theta \le C_a$ for some $C_a$,
     the predictable part of this semimartingale decomposition is bounded by
@@
         \Big\langle
-            2 C_0 \|f\|_\infty u_f
+            2 C_a \|f\|_\infty u_f
             + (1 - u/N) \gamma B^\theta_f
-            + (C_0 u^2 - b_\theta u) \frac{d}{du} f,
+            + (C_a u^2 - b_\theta u) \frac{d}{du} f,
             \lp_s
-        \Big\rangle
-        &\le
+        \Big\rangle ,
+    \end{align*}
+    the last term of which is bounded by
+    \begin{align*}
         \langle
-            C_0 u_f^2 + \sup_x |b_\theta(x, \eta_s)| u_f \|\frac{d}{du} f\|_\infty
+            C_a u_f^2 + \sup_x |b_\theta(x, \eta_s)| u_f \|\frac{d}{du} f\|_\infty
         \rangle ,
@@
 \begin{proof}[of Theorem~\ref{thm:lineages}]
+For brevity, in the proof we write $\gamma(x)$ or $\gamma$ for $\gamma(x,\eta)$.
 
@@
 $$
-    \mathcal{L}^Y_s g(x) = \gamma ( \DG(r(\cdot,\eta_s) g(\cdot))(x) - g(x) \DG r(x,\eta_s) ) .
+    \mathcal{L}^Y_s g(x) = \gamma(x,\eta_s) ( \DG(r(\cdot,\eta_s) g(\cdot))(x) - g(x) \DG r(x,\eta_s) ) .
 $$
 % (This is $\mathcal{L}^Y_s g(x) = \gamma ( \DG(rg)(x) - g \DG r(x) )$ in shorter but more cryptic notation.)
-The diffusion is time-inhomogeneous if the density is not constant with time
-(since recall that the coefficients $\gamma$ and $r$ depend on the density).
+The diffusion is time-inhomogeneous if the density is not constant with time.
 Let $\varphi_t(x)$ be the limiting density, which solves \eqref{general deterministic limit},
 $\partial_t \varphi = r \DG^*[ \varphi_t \gamma ] + \varphi F$.
-Formally, the intensity of levels at $y$ at time $t$
+Formally, the intensity of individuals at $y$ at time $t$
 that are descended from individuals that were at $x$ at time $s$
@@
 spatial motion $\{Y_u\}_{s\leq u\leq t}$, its level at time $t$ will
-be $v \exp(-\int_s^t(F+\gamma\Delta r)(Y_u)du)$. This will be less than a given level 
-$\lambda$ if $v < \lambda \exp(\int_s^t(F+\gamma\Delta r)(Y_u)du)$. 
+be $v \exp(-\int_s^t(F+\gamma\DG r)(Y_u)du)$. This will be less than a given level 
+$\lambda$ if $v < \lambda \exp(\int_s^t(F+\gamma\DG r)(Y_u)du)$. 
 The intensity of levels at $y$ that are descended from individuals at
 $x$ can therefore be obtained as the limit as $\lambda\to\infty$ of 
-$1/\lambda$ times the number of levels at $x$ at time zero with
-$u<\lambda \exp(\int_s^t(F+\gamma\Delta r)(Y_u)du)$ and for which
+$1/\lambda$ times the number of levels at $x$ at time $s$ with
+$u<\lambda \exp(\int_s^t(F+\gamma\DG r)(Y_u)du)$ and for which
 the corresponding individual is at $y$ at time $t$, which is 
@@
 \end{eqnarray*}
-(Note that the $\phi_s F g$ terms have cancelled.)
+(Note that the $\varphi_s F g$ terms have cancelled.)
 Since the adjoint of ${\mathcal L}^Y_s$ is
@@
     + 2 f \vec{c} \cdot \grad g
-    + 2 (C \grad f) \cdot \grad g
+    + 2 (\covq \grad f) \cdot \grad g
     + f \DD g ,
 \end{align*}
-where $\vec{c}_j = \sum_i \partial_j C_{ij}$.
+where $\vec{c}_j = \sum_i \partial_j \covq_{ij}$.
 So, with $f = \gamma \varphi_s$,
@@
         + 2 \gamma \varphi_s \vec{c} \cdot \grad g
-        + 2 (C \grad (\gamma \varphi_s)) \cdot \grad g
+        + 2 (\covq \grad (\gamma \varphi_s)) \cdot \grad g
         - \gamma \varphi_s \meanq \cdot \grad g
@@
         + 2 \vec{c} \cdot \grad g
-        + 2 (C \grad \log(\gamma \varphi_s)) \cdot \grad g
+        + 2 (\covq \grad \log(\gamma \varphi_s)) \cdot \grad g
         - \meanq \cdot \grad g
@@
 \end{eqnarray*}
-which is equation \eqref{eqn:lineage_generator2},
+which is equation \eqref{eqn:lineage_generator2}.
 \end{proof}
@@
     and define
-    $$  C = \{
+    \begin{align} \label{eqn:C_defn}
+        C = \{
         \int_S f(z) \alpha(\cdot,dz),
@@
         \; : \; f \in \mathcal{D}(A)
-    \} . $$
+    \} . \end{align}
     Let $\mu_0 \in \mathcal{P}(S_0)$ and define $\nu_0 = \int \alpha(y,\cdot) \mu_0(dy)$.
@@
 we obtain the generator of the projected process.
+In the notation of the thoerem,
+we are verifying that $C$ defined in~\eqref{eqn:C_defn} is in fact $\Pgen^N$
+(if defined with $A^N$) or $\Pgen^\infty$ (if defined with $A$).
 We will work with test functions of the form
@@
 is the ``spatial projection operator'',
-and define the probability kernel $\Gamma^N : \measures \to \mathcal{M}(\IR^d \times [0,N))$
+and define the transition function $\Gamma^N : \measures \to \mathcal{M}(\IR^d \times [0,N))$
 so that for $\eta \in \measures$, if $\hat g(x) = \int_0^N g(x, u) du / N$, then
@@
 \end{lemma}
+
+For the limiting process,
+recall that $\kappa(\lp)(\cdot) = \lim_{u \to \infty} \lp(\cdot \times [0, u)) / u$
+is the ``spatial projection operator'',
+and define the probability kernel $\Gamma : \measures \to \flpmeasures$
+so that for $\eta \in \measures$,
+defining $\widetilde{g}(x) = \int_0^\infty (g(x, u) - 1) du$,
+\begin{align*}
+    F_g(\eta)
+    &:=
+    \int f(\lp) \Gamma(\eta, d\lp) \\
+    &=
+    \exp\left(
+        \big \langle
+            \int_0^\infty (g(x, u) - 1) du,
+            \eta(dx)
+        \big \rangle
+    \right) \\
+    &=
+    e^{ \langle \widetilde{g}(x), \eta(dx) \rangle } .
+\end{align*}
+i.e., $\Gamma(\eta, \cdot)$ is the distribution of a conditionally Poisson process
+with intensity a product of $\eta$ and Lebesgue measure.
+It again follows from Lemma~\ref{def: MP definition of limit} that for test functions of this form
+the generator of $\eta_t$ is
+\begin{align} \label{eqn:pgen_infty}
+    \Pgen^\infty F_g(\eta)
+    &=
+    F_g(\eta)
+    \left\langle
+        \gamma(x, \eta)
+        \DG( \widetilde{g}(\cdot) r(\cdot) )(x)
+        + F(x, \eta) \widetilde{g}(x)
+        + \alpha \gamma(x, \eta) r(x, \eta) \widetilde{g}^2(x)
+        ,
+        \eta(dx)
+    \right\rangle .
+\end{align}
+The generator of $\lp_t$ is $A$, defined in equation~\eqref{eqn:limiting_lookdown_generator}.
 
@@
 
-For the limiting process,
-we now require test functions such that $g(x,u) = 1$ for all $u$ larger than some $u_0$;
-As before, recall that $\kappa(\lp)(\cdot) = \lim_{u \to \infty} \lp(\cdot \times [0, u)) / u$
-is the ``spatial projection operator'',
-and define the probability kernel $\Gamma : \measures \to \flpmeasures$
-so that for $\eta \in \measures$,
-defining $h(x) = \int_0^\infty (g(x, u) - 1) du$,
-\begin{align*}
-    F_g(\eta)
-    &:=
-    \int f(\lp) \Gamma(\eta, d\lp) \\
-    &=
-    \exp\left(
-        \big \langle
-            \int_0^\infty (g(x, u) - 1) du,
-            \eta(dx)
-        \big \rangle
-    \right) \\
-    &=
-    e^{ \langle h(x), \eta(dx) \rangle } .
-\end{align*}
-i.e., $\Gamma(\eta, \cdot)$ is the distribution of a conditionally Poisson process
-with intensity a product of $\eta$ and Lebesgue measure.
-It again follows from Lemma~\ref{def: MP definition of limit} that for test functions of this form
-the generator of $\eta_t$ is
-\begin{align} \label{eqn:pgen_infty}
-    \Pgen^\infty F_g(\eta)
-    &=
-    F_g(\eta)
-    \left\langle
-        \gamma(x, \eta)
-        \DG( h(\cdot) r(\cdot) )(x)
-        + F(x, \eta) h(x)
-        + \alpha \gamma(x, \eta) r(x, \eta) h^2(x)
-        ,
-        \eta(dx)
-    \right\rangle .
-\end{align}
-The generator of $\lp_t$ is $A$, defined in equation~\eqref{eqn:limiting_lookdown_generator}.
-
 Before proving Lemma~\ref{lem:averaged_generators_limit},
@@
     \gamma(x,\eta)\left(
-        \DG(h(\cdot) r(\cdot,\eta))(x) - h(x) \DG r(x,\eta)
+        \DG(\widetilde{g}(\cdot) r(\cdot,\eta))(x) - \widetilde{g}(x) \DG r(x,\eta)
     \right) ,
 \end{align*}
-since $h(x) = \int_0^\infty (g(x,u) - 1) du$.
+since $\widetilde{g}(x) = \int_0^\infty (g(x,u) - 1) du$.
 Next,
@@
     \\ & \qquad {}
-    + \{ \gamma(x,\eta) \DG r(x,\eta) + F(x,\eta) \} h(x)
+    + \{ \gamma(x,\eta) \DG r(x,\eta) + F(x,\eta) \} \widetilde{g}(x)
 \end{align*}
@@
 \\ & \qquad =
-    h(x)^2/2 .
+    \widetilde{g}(x)^2/2 .
 \end{align*}
@@
     \\ &\qquad=
-    \gamma(x,\eta) \DG(h(\cdot)r(\cdot,\eta))(x)
-    + F(x,\eta) h(x) 
-    + \alpha \gamma(x,\eta) r(x,\eta) h(x)^2 ,
+    \gamma(x,\eta) \DG(\widetilde{g}(\cdot)r(\cdot,\eta))(x)
+    + F(x,\eta) \widetilde{g}(x) 
+    + \alpha \gamma(x,\eta) r(x,\eta) \widetilde{g}(x)^2 ,
 \end{align*}
@@
     there exists $K$ such that
-    \begin{align} \label{eqn:goal1}
+    \begin{align*}
         \left|
@@
         K p_{\epsilon^2_\gamma}(w-x) .
-    \end{align}
+    \end{align*}
     However,
@@
         \bigg(
-            \meanq(x)^T \Gamma(s,x)^{-1} (z - s \meanq)
+            \meanq(x)^T \Gamma(s,x)^{-1} (z - s \meanq(x))
             +
@@
     where $h(z)$ and $k(z)$ are quadratic polynomials in $z$
-    whose coefficients depend on $s$ and $x$ but are uniformly bounded for $s \ge 1$
-    and $x \in \IR^d$.
-    Therefore, \eqref{eqn:goal1} holds for some finite $K$
-    if and only if $k(z) < 0$ for all $z$ outside some bounded region.
-    This is
+    whose coefficients depend on $s$ and $x$ but are uniformly bounded,
+    and
     \begin{align*}
@@
     \end{align*}
-    which is negative for all $z$ outside a bounded region.
     Since $\inf_z z^T \Gamma(s,x)^{-1} z / \|z\|^2 = 1 / (s \lambda(x) + \epsilon_r^2)$,
     where $\lambda(x) = \sup z^T \covq(x) z / \|z\|^2$ is the largest eigenvalue of $\covq(x)$,
+    this is negative for all $z$ outside a bounded region, and so
     equation~\eqref{eqn:first_moment_rho} follows from the assumption
@@
         (\|z_1\|^2 + \|z_2\|^2)/(2 \epsilon_\gamma^2)
-            - \frac{1}{2} [z_1, z_2[^T \Gamma(s, t, x)^{-1} [z_1, z_2] ,
+            - \frac{1}{2} [z_1, z_2]^T \Gamma(s, t, x)^{-1} [z_1, z_2] ,
     \end{align*}
@@
         (\|z_1\|^2 + \|z_2\|^2) / \epsilon^2_\gamma
-            - [z_1, z_2[^T \Gamma(s, t, x)^{-1} [z_1, z_2]
+            - [z_1, z_2]^T \Gamma(s, t, x)^{-1} [z_1, z_2]
         \\ &\qquad \le
@@
     \begin{enumerate}
-        \item For each fixed $t$, $\{Y_t^{(n)}\}_{n \ge 1}$  is tight.
+        \item For each fixed $t \in [0,T]$, $\{Y_t^{(n)}\}_{n \ge 1}$  is tight.
         \item Given a sequence of stopping times $\tau_n$, bounded by $T$,
@@
                 \sup_{n \ge n_0}
-                \sup_{\theta \in [0, \delta]}
+                \sup_{\theta \in [0, \min(\delta,T-\tau_n)]}
                 \IP\left\{ \left|
@@
     \end{enumerate}
-    Then the sequence $\{Y^{(n)}\}_{n \ge 1}$ is tight.
+    Then the sequence $\{(Y^{(n)}_t)_{t=0}^T\}_{n \ge 1}$ is tight.
 \end{theorem}
@@
     \label{lem:product_tightness}
-    Let $\{X^{(n)}\}_{n \ge 1}$ and $\{Y^{(n)}\}_{n \ge 1}$ sequences of jointly defined
+    Let $\{X^{(n)}\}_{n \ge 1}$ and $\{Y^{(n)}\}_{n \ge 1}$ be sequences of jointly defined
     real-valued processes with c\`adl\`ag paths
@@
     Now, since $\max_{0 \le t \le T} X^{(n)}_t$ is tight (and likewise for $Y$)
-    (see, e.g., Remark 3.7.3 in \citet{EK}),
+    (see, e.g., Remark 3.7.3 in \citet{ethier/kurtz:1986}),
     we may choose a $C \ge 4$ for which

### 2023-04-25 forwards-and-backwards.tex
removed general kernel from PME

@@
 
-\comment{TODO: ALISON SAYS
-The proof of Lemma 6.7 is now problematic.
-We'll be hard pushed to find a sequence of functions increasing to x, or indeed -x.
-Easily fixed of course, but I think that we should anyway change the condition of the theorem to be a bit more general, so say that we assume that $\langle f(x),\eta^N_0(dx)\rangle$  is uniformly bounded for some non-negative, twice differentiable with uniformly bounded first and second derivatives, function $f$ with $f(x)\to\infty$ as $x\to\infty$ and then use Lemma 6.1 and Gronwall to deduce $\langle f,\eta_t\rangle$ has bounded mean for any limit point and so Markov's inequality tells us no mass escaped to infinity.
-}
-
-\comment{``reaction diffusion equation'' or ``reaction-diffusion equation''?}
-
 \begin{abstract}
@@
 in the important special case in which the limit is a 
-reaction diffusion equation, directly 
+reaction-diffusion equation, directly 
 by simultaneously scaling the kernel width,
@@
 one-step convergence in cases for which the limit is a classical 
-reaction diffusion equation of the form~(\ref{semilinear PDE}) with 
+reaction-diffusion equation of the form~(\ref{semilinear PDE}) with 
 $\DG=\Delta$,
@@
 
-Such results on (one-step) convergence to reaction diffusion 
+Such results on (one-step) convergence to reaction-diffusion 
 equation limits have been
@@
     purely atomic measures, with $\eta_0^N$ comprised of atoms of mass $1/N$,
-    which is tight in $\measures$ and such that
-    $\langle |x|, \eta_0^N(dx)\rangle<C<\infty$
-    with $C$ independent of $N$.
+    which is tight in $\measures$.
+    Also assume there exists a nonnegative $f_0 \in C(\IR^d)$
+    with uniformly bounded first and second derivatives
+    (i.e., with $\sup_x \sup_{\|z\|=1} \sum_i \partial_{x_i} f_0(x) z_i$
+    and $\sup_x \sup_{\|z\|=1} \sum_{ij} \partial_{x_i x_j} f_0(x) z_i z_j$ both finite)
+    and $f_0(x) \to \infty$ as $|x| \to \infty$ for which
+    $\langle f_0(x), \eta_0^N(dx)\rangle<C<\infty$
+    for some $C$ independent of $N$.
     Then the sequence of processes
@@
 The following propositions provide two concrete situations in which this is true.
-In the first, the PDE is a reaction diffusion equation, and we borrow
+In the first, the PDE is a reaction-diffusion equation, and we borrow
 an idea from~\cite{penington:2017} to express the solutions to both the nonlocal
@@
 
-\comment{TODO: restrict to Gaussian case}
 \begin{proposition}
@@
 Suppose that
-we can write $\rho_\gamma=\zeta*\check{\zeta}$, where $\check{\zeta}(x)=\zeta(-x)$ and
-$\zeta\in\mathcal{S}(\IR^d)$ (the Schwartz space of rapidly decreasing functions).
-Furthermore, suppose that %$\psi_0^\epsilon\in L^1(\IR^d)$, 
+% we can write $\rho_\gamma=\zeta*\check{\zeta}$, where $\check{\zeta}(x)=\zeta(-x)$ and
+% $\zeta\in\mathcal{S}(\IR^d)$ (the Schwartz space of rapidly decreasing functions).
+$\rho_\gamma = p_{\epsilon^2_\gamma}$,
+and that %$\psi_0^\epsilon\in L^1(\IR^d)$, 
 $\psi_0^\epsilon\geq 0$ is such that
@@
 
-Equation~(\ref{eqn:nonlocal_pde}) is a nonlocal version of a reaction diffusion equation;
+Equation~(\ref{eqn:nonlocal_pde}) is a nonlocal version of a reaction-diffusion equation;
 the diffusion is nonlinear if $\gamma$ depends on population density:
@@
 limit is respectively a deterministic solution to a non-local equation of 
-reaction diffusion type and a deterministic solution to a nonlocal 
+reaction-diffusion type and a deterministic solution to a nonlocal 
 porous medium equation with an additional logistic growth term, 
@@
 %we pass from our population model 
-%directly to a reaction diffusion equation without going via a nonlocal limit,
+%directly to a reaction-diffusion equation without going via a nonlocal limit,
 %and finally our results concerning both convergence of the lookdown representation
@@
 \begin{proof}[Sketch]
-To avoid the idea being buried in notation, we sketch the proof in the 
-special case of $d=1$.
-We take a sequence of test functions $f_n$ increasing to the function $f(x)=x$
+Take $f_0(x)$ as in the statement of Theorem~\ref{thm:nonlocal_convergence},
+i.e., $f_0$ is nonnegative, grows to infinity as $x \to \infty$,
+has uniformly bounded first and second derivatives,
+and has $\langle f_0, \eta^N_0\rangle$ uniformly bounded in $N$.
+We take a sequence of test functions $f_n$ that increase to the function $f_0$
 and having uniformly bounded first and second derivatives,
@@
 By first taking $N \to \infty$ and then $n \to \infty$,
-we find that $\IE[\langle x, \eta_t(dx)\rangle] \le C'$
-for $t\in [0,T]$, and an application of Markov's inequality
+we find that $\IE[\langle f_0, \eta_t(dx)\rangle] \le C'$
+for $t\in [0,T]$, and since $f_0 \to \infty$ as $|x| \to \infty$,
+an application of Markov's inequality
 tells us that for any $\delta > 0$,
-$\IP[\eta_t([R,\infty])>\delta]\to 0$ as $R\to\infty$.
-The same argument with $f_n(x)$ increasing to $-x$ completes the proof.
+$\IP[\eta_t(\{x : \|x\| > R\})>\delta]\to 0$ as $R\to\infty$.
 \end{proof}
@@
 population density that solves the corresponding ``classical'' PDE. We verify
-this in two examples; in the first the nonlocal equation is a reaction diffusion equation
+this in two examples; in the first the nonlocal equation is a reaction-diffusion equation
 with the ``nonlocality'' only appearing in the 
@@
 In this subsection we prove Proposition~\ref{nonlocalPME to PME}.
-To ease notation, we drop the subscript $\gamma$ on $\rho_\gamma$ and we present 
+To ease notation, we present
 the proof in $d=1$ (although we retain the notation $\nabla$).
+However to recall the dependence on $\epsilon$ we write $\rho^\epsilon$ for $\rho_\gamma$
+(which recall for this Proposition we suppose is Gaussian
+and equal to $p_{\epsilon^2_\gamma}$).
 It should be clear that it extends almost without change
@@
 	+\psi_t^\epsilon(x)\left(1-\rho^\epsilon *\psi_t^\epsilon(x) 
-\right),
+\right) .
 \end{equation*}
-and 
-we assume that $\rho=\zeta*\check{\zeta}$ with $\zeta$ a rapidly decreasing function. 
-The example we have in mind is $\zeta$ (and therefore $\rho$) being the density of
-a mean zero Gaussian random variable.  
+% and we assume that $\rho=\zeta*\check{\zeta}$ with $\zeta$ a rapidly decreasing function. 
+% The example we have in mind is $\zeta$ (and therefore $\rho$) being
 We shall prove that under the 
@@
 which we record as a lemma.
+
 \begin{lemma}
@@
 \begin{proof}[Proof of Proposition~\ref{nonlocalPME to PME}]
+Write $\zeta = p_{\epsilon^2_\gamma / 2}$, so that $\rho = \zeta * \zeta$.
 First observe that
@@
 \int\int\int \psi_t^\epsilon(x)\psi_t^\epsilon(x-y)\zeta^{\epsilon}(y-z)
-\check{\zeta}^{\epsilon}(z) dz dy dx 
+{\zeta}^{\epsilon}(z) dz dy dx 
 \\
@@
 \int\int\int\nabla \psi_t^\epsilon(x-y)\zeta^{\epsilon}(y-z)
-\check{\zeta}^{\epsilon}(z)
+{\zeta}^{\epsilon}(z)
 \psi_t^\epsilon(x)\nabla\phi(x) dz  dy  dx
@@
 \int\int\int \psi_t^\epsilon(x-y)\zeta^{\epsilon}(y-z)
-\check{\zeta}^{\epsilon}(z)\nabla \psi_t^\epsilon(x)\nabla\phi(x) dz dy  dx
+{\zeta}^{\epsilon}(z)\nabla \psi_t^\epsilon(x)\nabla\phi(x) dz dy  dx
 \\
@@
 $\rho_F$ is Gaussian, and the scaling 
-limit is a reaction diffusion equation.
+limit is a reaction-diffusion equation.
 

### 2023-04-25 forwards-and-backwards.tex
pass through remaining things

@@
 \maketitle
+
+\comment{TODO: signpost where proofs can be found}
 
@@
 Recall that the process $(\eta_t^N)_{t\geq 0}$ takes its values in the space
-${\cal D}([0,\infty),\measures)$ of c\`adl\`ag
+${\mathcal D}_{[0,\infty)}(\measures)$ of c\`adl\`ag
 paths on $\measures$. We endow $\measures$ with the topology of weak convergence
 and 
-${\cal D}([0,\infty),\measures)$ with the Skorohod topology.
+${\mathcal D}_{[0,\infty)}(\measures)$ with the Skorohod topology.
 A sequence of processes taking values in 
-${\cal D}([0,\infty),\measures)$ is said to be tight if the corresponding
+${\mathcal D}_{[0,\infty)}(\measures)$ is said to be tight if the corresponding
 sequence of distributions is tight,
@@
 Then the sequence of 
-${\cal D}([0,\infty), \measures)$-valued
+    ${\mathcal D}_{[0,\infty)}(\measures)$-valued
 stochastic processes $\big(\rho_F^\epsilon*\eta^N_t(x)dx\big)_{t \ge 0}$
@@
 by \citet{britton1990spatial,sasaki1997clumped,hernandezgarcia2004clustering,young2001reproductive}, and \citet{berestycki2009nonlocal}.
-\comment{FROM ALISON: I rewrote the rest of this section - please check!}
 For example, if the density-dependent effects of individuals extend farther (but not too much farther)
@@
 \end{align*}
-\comment{FROM ALISON integral against eta in last line corrected}
 Since $\int f^2(y) r(y, \eta) q_\theta(x, dy) \to f^2(x) r(x, \eta)$
@@
 \comment{FROM ALISON This sort of true because it corresponds to lookdown events, but when I read this again I was confused. Is there a better way to say it?} 
+\comment{PETER: I'm not sure which bit is confusing?}
 Recall from equation~\eqref{eqn:mu_defn} that
@@
 we say that a ${\mathcal D}_{[0,\infty)}({\mathcal C}_N)$-valued process 
-	\comment{FROM ALISON: we have not been consistent in the layout of 
-	the notation for spaces of cadlag paths - it is already different in 
-	the definition below!}
-$(\xi_t)_{t \ge 0}$
-   is a solution to the $(A^N, \lp_0)$ martingale problem
-    if 
-$f(\lp_t) - f(\lp_0)-\int_0^t A^N f(\lp_s) ds$ is a martingale (with 
+$(\xi_t)_{t \ge 0}$ is a solution to the $(A^N, \lp_0)$ martingale problem
+if $f(\lp_t) - f(\lp_0)-\int_0^t A^N f(\lp_s) ds$ is a martingale (with 
 respect to the natural filtration) for all 
-test functions $f$ 
-    as defined above.
+test functions $f$ as defined above.
 \end{definition}
@@
     \end{split} \end{align}
-    We say that a ${\cal D}([0,\infty), \mathcal{C})$-valued process $(\xi_t)_{t \ge 0}$
+    We say that a ${\mathcal D}_{[0,\infty)}(\mathcal{C})$-valued process $(\xi_t)_{t \ge 0}$
     is a solution to the $(A, \lp_0)$ martingale problem
@@
 $\kappa^N(\lp)$.
-\comment{ALISON: added N, also made sigma $\sigma$ above}
 Similarly, for a measure $\lp$ on $\IR^d \times [0, \infty)$
@@
     Furthermore, for each $t$, $\lp^N_t$ is conditionally uniform 
-	\comment{ALISON deleted excess given}
 	given $\mathcal{F}^{\eta^N}_t$
@@
 %and characterization of the lineage process in the deterministic case.
-\comment{FROM ALISON: slightly reworded - deleted bit about onestep convergence
-on the basis that we already point to that in the introduction}
 

### 2023-04-25 forwards-and-backwards.tex
spellcheck

@@
 and the associated results for the motion of lineages.
-The Appendix contains a few more techinical and less central lemmas.
+The Appendix contains a few more technical and less central lemmas.
 The results are illustrated in a few places with individual-based simulations,
@@
 the expansion of a certain type of bacteria % of the type {\em Paenbacillus dendritiformis}
-on a thin layer of agar in a petri dish 
+on a thin layer of agar in a Petri dish 
 \citep{cohen/golding/kozlovsky/benjacob/ron:1999}. 
@@
     $\sup_{\lp \in K} \langle f_k, \lp \rangle < \infty$ for each $k$;
-    below, Lemma~\ref{lem:compact containment lookdown} proves exatly this, and therefore compact containment.
+    below, Lemma~\ref{lem:compact containment lookdown} proves exactly this, and therefore compact containment.
 
@@
     The fact that martingale properties are preserved under passage to the limit
-    is straightforward, and can be proved in a way analgous to Lemma~\ref{lem:limit_mgale};
+    is straightforward, and can be proved in a way analogous to Lemma~\ref{lem:limit_mgale};
     we omit the proof.
@@
 \begin{proof}[of Lemma~\ref{lem:h_containment}]
-    Applied to $f(x, u) = h(u)$, the martinagle representation~\eqref{eqn:f_xi_mgale} is
+    Applied to $f(x, u) = h(u)$, the martingale representation~\eqref{eqn:f_xi_mgale} is
     \begin{align*}
@@
 we obtain the generator of the projected process.
-In the notation of the thoerem,
+In the notation of the theorem,
 we are verifying that $C$ defined in~\eqref{eqn:C_defn} is in fact $\Pgen^N$
@@
     $$
-    Simliarly, by assumption we can choose a $\delta$ for which
+    Similarly, by assumption we can choose a $\delta$ for which
     $$

### 2023-04-25 forwards-and-backwards.tex
signposts

@@
 
+Proofs of the results so far, on nonlocal processes, are found in Section~\ref{sec:proofs}.
+
 \paragraph{One-step convergence to PDE:}
-
 Theorem \ref{thm:nonlocal_convergence},
@@
 but we prove such ``diagonal'' convergence in the following situation.
+The proof is provided in Section~\ref{subsec:one step convergence proof}.
 
@@
 be seen as a first step towards understanding genealogies for high population densities.
+
+Proofs of results in this section are found in Section~\ref{sec:lookdown_proofs}.
 

### 2023-04-26 forwards-and-backwards.tex
symlinks to figures
alison edits

@@
     \begin{center}
-        \includegraphics{figures/ex1a/fkpp_123.density.3.0}
-        \includegraphics{figures/ex1b/fkpp_123.density.3.0}
+        % \includegraphics{figures/ex1a/fkpp_123.density.3.0}
+        % \includegraphics{figures/ex1b/fkpp_123.density.3.0}
+        \includegraphics{figures/fig1a}
+        \includegraphics{figures/fig1b}
     \end{center}
@@
     \begin{center}
-        \includegraphics[width=0.7\textwidth]{figures/ex2a/pme_1234.steps}
-        \includegraphics[width=0.7\textwidth]{figures/ex2b/pme_1234.steps}
+        % \includegraphics[width=0.7\textwidth]{figures/ex2a/pme_1234.steps}
+        % \includegraphics[width=0.7\textwidth]{figures/ex2b/pme_1234.steps}
+        \includegraphics[width=0.7\textwidth]{figures/fig2a}
+        \includegraphics[width=0.7\textwidth]{figures/fig2b}
     \end{center}
@@
     \begin{center}
-        \includegraphics[width=0.45\textwidth]{figures/clumpy_2d/clumpy_123.density.3.0}
-        \includegraphics[width=0.45\textwidth]{figures/clumpy_1d/clumpy_123.steps}
+        % \includegraphics[width=0.45\textwidth]{figures/clumpy_2d/clumpy_123.density.3.0}
+        % \includegraphics[width=0.45\textwidth]{figures/clumpy_1d/clumpy_123.steps}
+        \includegraphics[width=0.45\textwidth]{figures/fig3a}
+        \includegraphics[width=0.45\textwidth]{figures/fig3b}
     \end{center}
@@
 
-\comment{TODO: check that $\eta_s^N$ having an $N$ or not is okay}
-
 In this section we prove Theorem~\ref{thm:local_convergence},
@@
 convergence of Markov processes from~\cite{ethier/kurtz:1986}. 
+Bounds on the moments of $\rho_\epsilon*\eta_t$
+are established in 
+Subsection~\ref{bounds on rhoepsilon}.
 The challenge
@@
 estimates for a random walk with Gaussian jumps which we prove in 
-Subsection~\ref{continuity for random walk}.
-Various bounds on the moments of $\rho_\epsilon*\eta_t$, one consequence of 
-which is tightness, are then provided in 
-Subsection~\ref{bounds on rhoepsilon},
-and we identify the limit points in Subsection~\ref{limit in onestep case}.
-
-\subsection{Continuity estimates for a Gaussian random walk}
-\label{continuity for random walk}
+Subsection~\ref{continuity for random walk}, before
+identifying the limit points in Subsection~\ref{limit in onestep case}.
+
+\subsection{Moment bounds for $\rho_\epsilon*\eta$}
+\label{bounds on rhoepsilon}
 
@@
 while $\epsilon^2 + T(t) \ge \epsilon^2$ always,
-then partitioning over
+partitioning over
 $\{ \tau(t) \ge -(\epsilon^2 + t)/2 \}$ and its complement,
@@
             \tau(t) < - (\epsilon^2 + t) / 2
-        \right\} \label{eqn:psi_infty_bound}
+        \right\}. \label{eqn:psi_infty_bound}
 \end{align}
@@
     \\&=
-    \exp\left\{ - \delta \theta t - \frac{\theta \epsilon^2}{2} \right\} ,
+    \exp\left\{ - \chi \theta t - \frac{\theta \epsilon^2}{2} \right\} ,
 \label{bound for negative tau}
 \end{align}
-where $\delta = 1/2 - e^{-1} > 0$.
+where $\chi = 1/2 - e^{-1} > 0$.
 The second term in \eqref{eqn:psi_infty_bound} is therefore bounded by
 \[
-    C \left(1 + \frac{t}{\epsilon^2}\right)^{d/2} e^{-\delta \theta t - \epsilon^2 \theta / 2}
+    C \left(1 + \frac{t}{\epsilon^2}\right)^{d/2} e^{-\chi \theta t - \epsilon^2 \theta / 2}
     \frac{1}{(\epsilon^2 + t)^{d/2}} .
@@
 Now observe that the derivative (with respect to $t$) of 
-$e^{-\delta \theta t - \epsilon^2 \theta / 2} (1 + t/\epsilon^2)^{d/2}$ 
+$e^{-\chi \theta t - \epsilon^2 \theta / 2} (1 + t/\epsilon^2)^{d/2}$ 
 is
 \[
-    \left( \frac{d}{2 \epsilon^2} - \left(1 + \frac{t}{\epsilon^2}\right) \delta \theta \right)
-    \left( 1 + \frac{t}{\epsilon^2} \right)^{d/2 - 1} e^{-\delta \theta t - \epsilon^2 \theta / 2} ,
+    \left( \frac{d}{2 \epsilon^2} - \left(1 + \frac{t}{\epsilon^2}\right) \chi \theta \right)
+    \left( 1 + \frac{t}{\epsilon^2} \right)^{d/2 - 1} e^{-\chi \theta t - \epsilon^2 \theta / 2} ,
 \]
-which is negative if $\theta(\epsilon^2 + t) > d/2 \delta$.
-At the maximum, $(\epsilon^2 + t) = d \delta / (2 \theta)$,
-so $(1 + t/\epsilon^2) = d \delta/(2 \theta \epsilon^2)$,
+which is negative if $\theta(\epsilon^2 + t) > d/2 \chi$.
+At the maximum, $(\epsilon^2 + t) = d / (2\chi \theta)$,
+so $(1 + t/\epsilon^2) = d /(2\chi \theta \epsilon^2)$,
 and so this quantity is bounded uniformly over not only $t$ but also $\epsilon$
@@
 \end{proof}
-
-We are going to approximate $\psi_t^{\epsilon,x}(\cdot)$ by $p_{\epsilon^2+t}(x, \cdot)$,
-and to control the error that this introduces we 
-need to control $T(t)-t$. We achieve this through a large deviations bound.
-
-\begin{lemma}
-    \label{lem:poisson_ld}
-    Fix $A > e^3 - 1$ (so that $\log(1 + A) > 3$).
-    In the notation of Lemma~\ref{PsiBoundHS},
-    \begin{align*}
-        \limsup_{\theta \to \infty}
-        \frac{1}{\theta} \log
-        \IP\left\{
-            T(t) - t > A(\epsilon^2 + t)
-        \right\}
-    \le
-        - (\epsilon^2 + t) \frac{A}{2}
-        - \log(1 + A)\left( \frac{t + A(\epsilon^2 + t)}{2} \right) .
-    \end{align*}
-\end{lemma}
-
-\begin{proof}
-    We apply Cram\'er's Theorem.
-    First note that
-    \begin{align*}
-        \IP\left\{
-            T(t) - t > A(\epsilon^2 + t)
-        \right\}
-        =
-        \IP\Big\{
-            \frac{\Pi(\theta t)}{ \theta}
-            >
-            t + A(\epsilon^2 + t)
-        \Big\} .
-    \end{align*}
-For convenience, suppose $\theta$ is an integer,
-and so we may write $\Pi(\theta t) = Z_1(t) + \cdots + Z_\theta(t)$,
-where the $Z_i(t)$ are i.i.d.~Poisson($t$) random variables.
-    To apply Cram\'er's Theorem, we need the rate function for the 
-Poisson($t$) distribution,
-    which is
-    \[
-        \Lambda^*(x) = \sup_{\alpha > 0} \left[ \alpha x - \lambda(\alpha) \right],
-    \]
-    where $\lambda(\alpha) = \log \IE[\exp(\alpha Z_1(t))] = t(e^\alpha - 1)$.
-    Now, the supremum of $\alpha x + t - te^\alpha$ is attained at $x = t e^\alpha$,
-    and so
-    \[
-        \Lambda^*(x) = x \log(x/t) - x + t .
-    \]
-    Cram\'er's Theorem then gives
-    \begin{align*}
-        \limsup_{\theta \to \infty}
-        \frac{1}{\theta} \log
-        \IP\left\{
-            \frac{\Pi(\theta t)}{\theta}
-            > t + A(\epsilon^2 + t)
-        \right\}
-    &\le
-        - \Lambda^*(t + A(\epsilon^2 + t))
-    \\ &=
-        A(\epsilon^2 + t)
-        -
-        \big(t + A(\epsilon^2 + t)\big) \log\left( 1 + \frac{A(\epsilon^2 + t)}{t} \right) 
-    \\ &\le
-        A(\epsilon^2 + t)
-        -
-        \big(t + A(\epsilon^2 + t)\big) \log(1 + A)
-    \\ &\le
-        A(\epsilon^2 + t) \left( 1 - \frac{1}{2} \log(1 + A) \right)
-        -
-        \frac{1}{2} \big(t + A(\epsilon^2 + t)\big) \log(1 + A)  .
-    \end{align*}
-    Since $(1/2) \log(1 + A) > 3/2$, from which $1 - (1/2) \log(1 + A) < - 1/2$,
-    the proof is complete.
-\end{proof}
-
-As advertised, we wish to control the difference between
-$\psi_t^{\epsilon,x}(y)$
-and $p_{\epsilon^2 + t}(x, y)$.
-
-\begin{lemma}
-    \label{Lemma:BoundPsiHS2}
-    In the notation of Lemma~\ref{PsiBoundHS},
-    and with $A$ as in Lemma~\ref{lem:poisson_ld},
-    \begin{multline}
-\label{heat kernel estimate}
-        \left|
-            \psi_t^{\epsilon, x}(y)
-            -
-            p_{\epsilon^2 + t}(x, y)
-        \right|
-        \\
-\le
-        \frac{C}{(\epsilon^2 \theta)^{d/2}}
-        p_{2(A+1)(\epsilon^2+t)}(x, y)
-        +
-        C \exp(- \epsilon^2 \theta / 2)
-        +
-        \frac{C}{(\epsilon^2 + t)^{d/2}}
-        \IP\left\{
-            \tau(t) > A(\epsilon^2 + t)
-        \right\} .
-    \end{multline}
-\end{lemma}
-
-\begin{proof}
-    Still using the notation of Lemma~\ref{PsiBoundHS},
-the three terms on the right hand side of 
-equation~(\ref{heat kernel estimate})
-    correspond to bounds obtained by partitioning
-    into three events according to the value of $\tau(t)$.
-    Let $A_1 = \{ \tau(t) < - (\epsilon^2 + t)/2 \}$,
-    $A_2 = \{ \tau(t) > A(\epsilon^2 + t) \}$,
-    and $A_3$ the remaining event, $\{ - (\epsilon^2 + t)/2 \le \tau(t) \le A(\epsilon^2 + t) \}$.
-    Then,
-    \begin{align*}
-        \left|
-            \psi_t^{\epsilon, x}(y)
-            -
-            p_{\epsilon^2 + t}(x, y)
-        \right|
-        &=
-        \left|
-        \IE\left[
-            p_{\epsilon^2 + t + \tau(t)}(x, y)
-            -
-            p_{\epsilon^2 + t}(x, y)
-        \right]
-        \right|
-        \\&\le
-        \IE\left[
-            (1_{A_1} + 1_{A_2} + 1_{A_3})
-            \left|
-            p_{\epsilon^2 + t + \tau(t)}(x, y)
-            -
-            p_{\epsilon^2 + t}(x, y)
-        \right|
-        \right] .
-    \end{align*}
-    For the first term, note that if $a < b$ then
-    \begin{align*}
-        |p_a(x, y) - p_b(x, y)| 
-        &=
-        \frac{1}{(2\pi)^{d/2}}
-        \left|
-            \frac{1}{a^{d/2}}
-            e^{-\|x - y\|^2 / 2a}
-            -
-            \frac{1}{b^{d/2}}
-            e^{-\|x - y\|^2 / 2b}
-        \right|
-        \\ &=
-        \frac{1}{(2\pi a^2)^{d/2}}
-            e^{-\|x - y\|^2 / 2b}
-        \left|
-            e^{-\|x - y\|^2 \left(\frac{1}{2a} - \frac{1}{2b}\right)}
-            -
-            \left(\frac{a}{b}\right)^{d/2}
-        \right|
-        \\ &\le
-        C \left(\frac{b}{a}\right)^{d/2}
-        p_b(x, y) ,
-    \end{align*}
-    where the inequality follows because both terms under the absolute value 
-are less than 1.
-Since, on the event $A_1$, $\tau(t)<0$, we can  
-apply this with $a = \epsilon^2 + t + \tau(t)$ and $b = \epsilon^2 + t$,
-and, using the bound~(\ref{bound for negative tau}),
-    \begin{align*}
-        \IE\left[
-            1_{A_1} |p_a(x, y) - p_b(x, y)| 
-        \right]
-        & \le
-            C \left(\frac{\epsilon^2 + t}{\epsilon^2}\right)^{d/2}
-            p_{\epsilon^2 + t}(x, y) 
-            \IP\left\{ \tau(t) < - \frac{\epsilon^2 + t}{2} \right\}
-        \\ & \le
-            C \frac{1}{\epsilon^d}
-            \IP\left\{ \tau(t) < - \frac{\epsilon^2 + t}{2} \right\}
-        \\ & \le
-        C \exp\left(-\frac{\theta \epsilon^2}{2} \right) .
-    \end{align*}
-
-    For the third term, we will first collect some facts.
-    Observe that on the event $A_3$,
-    $\epsilon^2 + t + \tau(t)$ is between
-    $(\epsilon^2 + t)/ 2$ and $(A + 1)(\epsilon^2 + t))$,
-    and for any $s$ in this interval,
-    \begin{align}
-        p_{2s}(y)
-        &\le \nonumber
-        \left( \frac{
-            2 (\epsilon^2 + t)(A + 1)
-        }{
-            \epsilon^2 + t
-        } \right)^{d/2}
-        p_{2(A+1)(\epsilon^2 + t)}(x, y)
-        \\ &= \label{eqn:p_bounded_on_interval}
-        (2(A+1))^{d/2}
-        p_{2(A+1)(\epsilon^2 + t)}(x, y) .
-    \end{align}
-    Moreover, since $u e^{-u} \le e^{-1}$ for all $u \ge 0$,
-    \begin{align}
-        \frac{\|x - y\|^2}{s} p_s(x, y)
-        &= \nonumber
-        \frac{4}{(2 \pi s)^{d/2}}
-        e^{- \frac{ \|x-y\|^2 }{ 4s }}
-        \frac{\|x-y\|^2}{4s}
-        e^{- \frac{ \|x-y\|^2 }{ 4s }}
-        \\ &\le \label{eqn:p_deriv_term2}
-        C p_{2s}(x, y) .
-    \end{align}
-    Now, by the Intermediate Value Theorem,
-    \begin{align}
-\label{deduction from IVT}
-        \left|
-            p_{\epsilon^2 + t + \tau(t)}(x, y)
-            -
-            p_{\epsilon^2 + t}(x, y)
-        \right|
-        &=
-        \left| \tau(t) \right|
-        \left| \frac{\partial p_s(x, y)}{\partial s} \right|
-    \end{align}
-    for some $s$ between $\epsilon^2 + t + \tau(t)$ and $\epsilon^2 + t$.
-   Since 
-    \begin{align*}
-        \partial_ s p_s(x, y)
-        &=
-        \partial_s
-        \left(
-            \frac{1}{(2 \pi s)^{d/2}}
-            \exp\left( - \frac{\|x - y\|^2}{2 s} \right)
-        \right)
-        \\ &=
-        - \frac{d}{2s} p_s(x, y) + \frac{\|x - y\|^2}{2 s^2} p_s(x, y),
-    \end{align*}
-    applying the inequality~\eqref{eqn:p_deriv_term2},
-    using the fact that $p_s(x, y) \le 2^{d/2} p_{2s}(x,y)$,
-    and then \eqref{eqn:p_bounded_on_interval},
-    we have that for any $s \in ((\epsilon^2 + t)/ 2, (A + 1)(\epsilon^2 + t))$,
-    \begin{align*}
-        \left| \frac{\partial}{\partial s} p_s(x, y) \right|
-        \le
-        \frac{C}{s} p_{2s}(x, y) 
-        \le
-        \frac{C}{\epsilon^2 + t} p_{2(A + 1)(\epsilon^2 + t)}(x, y) .
-    \end{align*}
-    Therefore, recalling that $\IE[\tau(t)^2] = t / \theta$, substituting 
-into~(\ref{deduction from IVT}),
-    \begin{align*}
-        \IE\left[
-            1_{A_3}
-            \left|
-                p_{\epsilon^2 + t + \tau(t)}(x, y)
-                -
-                p_{\epsilon^2 + t}(x, y)
-            \right|
-        \right]
-        &\le
-            \frac{C}{\epsilon^2 + t}
-                p_{2(A + 1)(\epsilon^2 + t)}(x, y)
-            \IE\left[|\tau(t)|\right]
-        \\ &\le
-            \frac{C}{\epsilon^2 + t}
-                p_{2(A + 1)(\epsilon^2 + t)}(x, y)
-            \IE\left[\tau(t)^2\right]^{1/2}
-        \\ &=
-            \left( \frac{Ct}{\theta(\epsilon^2 + t)^2} \right)^{1/2}
-                p_{2(A + 1)(\epsilon^2 + t)}(x, y)
-        \\ &\le
-            \frac{C}{\sqrt{\theta \epsilon^2}}
-                p_{2(A + 1)(\epsilon^2 + t)}(x, y) ,
-    \end{align*}
-    where the last inequality follows from $2 \epsilon^2 t \le (\epsilon^2 + t)^2$.
-
-    Finally, on the event $A_2 = \{\tau(t) > A(\epsilon^2 + t)\}$,
-    we simply use
-    \begin{align*}
-        \left|
-            p_{\epsilon^2 + t + \tau(t)}(x, y)
-            -
-            p_{\epsilon^2 + t}(x, y)
-        \right|
-        \le
-        \frac{C}{(\epsilon^2 + t)^{d/2}} ,
-    \end{align*}
-    so that
-    \begin{align*}
-        \IE\left[
-        1_{A_2}
-        \left|
-            p_{\epsilon^2 + t + \tau(t)}(x, y)
-            -
-            p_{\epsilon^2 + t}(x, y)
-        \right|
-        \right]
-        \le
-        \frac{C}{(\epsilon^2 + t)^{d/2}}
-        \IP\left\{
-            \tau(t) > A (\epsilon^2 + t)
-        \right\} .
-    \end{align*}
-\end{proof}
-
-The last result will be useful when combined with the next bound for the heat kernel.
-
-\begin{lemma}
-    \label{Lemma:ContinuityHS}
-Let $s>0$, and $x, y, z\in \IR^d$. The following estimate holds:
-\[
-    |p_s(x,z) - p_s(y,z)|
-    \leq
-    \frac{C\|x-y\|}{\sqrt{s}} \left(p_{2s}(x,z) + p_{2s}(y,z)\right) ,
-\]
-where the constant $C$ does not depend on $x,y,z$ or $s$.
-\end{lemma}
-
-\begin{proof}
-
-    Expanding the difference of two squares,
-    \begin{align*}
-        e^{- \frac{\|y-z\|^2}{2 s}}
-        -
-        e^{- \frac{\|x-z\|^2}{2 s}}
-        &=
-        \left(
-            e^{-\frac{\|y-z\|^2}{4 s}}
-            -
-            e^{-\frac{\|x-z\|^2}{4 s}}
-        \right)
-        \left(
-            e^{-\frac{\|y-z\|^2}{4 s}}
-            +
-            e^{-\frac{\|x-z\|^2}{4 s}}
-        \right) .
-    \end{align*}
-Now, thinking of the first term in brackets as a function of a single variable on
-the line segment $[y,z]$ connecting $y$ to $z$, we can apply the
-Intermediate Value Theorem and take the modulus to bound this expression by 
-    \[
-        \|y-x\|
-        \left( \frac{2\|w-z\|}{4s} \exp\left(-\frac{\|w-z\|^2}{4s}\right)\right)
-        (4 \pi s)^{d/2}
-        \left( p_{2s}(y,z)+p_{2s}(x,z) \right)
-    \]
-    for some $w\in [y,z]$.
-    Using the fact that $x e^{-x^2}$ is uniformly bounded,
-    we can bound the first bracket in the last equation by $C/\sqrt{s}$, and the result follows.
-\end{proof}
-
-\subsection{Moment bounds for $\rho_\epsilon*\eta$}
-\label{bounds on rhoepsilon}
 
@@
 \end{multline}
-Using that $\sup_s\|\psi^{\epsilon,x}_s(\cdot)\|_\infty=C/\epsilon^d$,
+Using(from Lemma~\ref{PsiBoundHS}) 
+that $\sup_s\|\psi^{\epsilon,x}_s(\cdot)\|_\infty=C/\epsilon^d$,
 $N\epsilon^d>1$,
@@
 the sequence of measure valued processes $\{ \rho*\eta_t^N(x) dx \}_{t \geq 0}$
-(taking values in $D([0,T], \measures)$ is tight.
+	(taking values in ${\mathcal D}_{[0,T]}(\measures)$) is tight.
 \end{corollary}
@@
 \begin{multline*}
-	\int\int\rho_\epsilon*|f|(x)\rho_\epsilon*\eta_u^N(x)^j
-	\rho_\epsilon*|f|(y)\rho_\epsilon*\eta_u^N(y)^k dx dy
+	\IE\left[	\int\int\rho_\epsilon*|f|(x)\rho_\epsilon*\eta_u^N(x)^j
+	\rho_\epsilon*|f|(y)\rho_\epsilon*\eta_u^N(y)^k dx dy\right]
 	\\
 	\leq
-	\int\int\|f\|_\infty\rho_\epsilon*\eta_u^N(x)^{j+k}
+	\IE\left[\int\int\|f\|_\infty\rho_\epsilon*\eta_u^N(x)^{j+k}
 	\rho_\epsilon*|f|(y)
@@
 	\rho_\epsilon*\eta_u^N(y)^{j+k}
-dx dy
+	dx dy \right]
 	\\ \leq C\int |f|(x)dx.
@@
 
-\subsection{Identification of the limit}
-\label{limit in onestep case}
-
-We now turn to the identification of the limit points of the sequence 
-$\big\{\big(\rho_\epsilon*\eta_t^N(x)dx\big)_{t\geq 0}\big\}_{N\geq 1}$.
-We consider the terms in the semimartingale 
-decomposition~(\ref{eqn:eta_martingale})
-of $\langle f, \rho_\epsilon*\eta_t^N(x)dx\rangle=
-\langle \rho_\epsilon*f, \eta_t^N(dx)\rangle$.
-By a Taylor expansion, writing $\{T_t\}_{t\geq 0}$ for the heat semigroup,
-\begin{align*}
-\int_0^t \big\langle \mathcal{L}^\theta T_{\epsilon^2} f, 
-	\eta_s^N(dx)\big\rangle ds 
-&= \int_0^t \big\langle \frac{1}{2} \Delta T_{\epsilon^2} f(x), 
-	\eta_s^N(dx) \big\rangle 
-	+ \mathcal{O}\Big(\frac{1}{\theta}\Big) 
-\\ &= \int_0^t \big\langle \frac{1}{2} \Delta f(x), \rho_\epsilon* \eta_s^N(x) dx 
-	\big\rangle ds + \mathcal{O}\Big(\frac{1}{\theta}\Big).
-\end{align*}
-Thus, from weak convergence we can deduce that under our scaling,
-for any (weakly) convergent subsequence $\{\rho_\epsilon*\eta^N(x)dx\}_{N\geq 1}$,
+\subsection{Continuity estimates for $\rho_\epsilon*\eta$}
+\label{continuity for random walk}
+
+In order to identify the limit point of any convergent subsequence
+of $\{\rho_\epsilon*\eta^N(x)\}$, 
+we are going to require some control on the spatial continuity of the 
+functions $\rho_\epsilon*\eta^N(x)$. This will be inherited from the regularity
+of the transition density of the 
+Gaussian random walk with generator ${\cal L}^\theta$, which in turn follows
+from its representation
+as that of a Brownian motion evaluated at the random time $T(t)$ defined
+in Lemma~\ref{PsiBoundHS}.
+Our approach will be to 
+approximate $\psi_t^{\epsilon,x}(\cdot)$ by $p_{\epsilon^2+t}(x, \cdot)$,
+and to control the error that this introduces we 
+need to control $T(t)-t$.
+
+\begin{lemma}
+    \label{lem:poisson_ld}
+    In the notation of Lemma~\ref{PsiBoundHS}, for any $A>1$,
+    \begin{align*}
+        %\limsup_{\theta \to \infty}
+        %\frac{1}{\theta} \log
+        \IP\left\{
+            T(t) - t > A(\epsilon^2 + t)
+        \right\}
+    \le
+	    \exp\left(-\frac{\theta A}{4}\big(\epsilon^2+t\big)
+	    %- (\epsilon^2 + t) \frac{A}{2}
+        %- \log(1 + A)\left( \frac{t + A(\epsilon^2 + t)}{2} 
+	    \right) .
+    \end{align*}
+\end{lemma}
+
+\begin{proof}
+    %We apply Cram\'er's Theorem.
+    %First note that
+    This is just a Chernoff bound. With $\Pi$ a rate one Poisson process as
+	in Lemma~\ref{PsiBoundHS}, for any $A>1$,
+	\begin{align*}
+        \IP\left\{
+            T(t) - t > A(\epsilon^2 + t)
+        \right\}
+&=
+        \IP\Big\{
+            \Pi(\theta t)
+            >
+		\theta\Big( t + A(\epsilon^2 + t)\Big)
+        \Big\} \\
+&\leq\frac{\IE\left[\exp\left(\alpha\Pi(\theta t)\right)\right]}
+		{\exp\left(\alpha\theta\big(t+A(\epsilon^2+t)\big)\right)}
+		\\
+		&=\exp\left(\theta t\big(e^\alpha-1\big)-\alpha\theta\big(t+A(\epsilon^2+t)\big)\right)
+		\\
+		&\leq
+		\exp\left(\theta t\big(e^\alpha-\alpha-1-\frac{A\alpha}{2}\big)
+		-\frac{A\alpha}{2}\theta(\epsilon^2+t)\right).
+    \end{align*}
+	Now set $\alpha=1/2$. Since $A>1$, $e^\alpha-\alpha-1-A\alpha/2<0$ and the 
+	result follows.
+%For convenience, suppose $\theta$ is an integer,
+%and so we may write $\Pi(\theta t) = Z_1(t) + \cdots + Z_\theta(t)$,
+%where the $Z_i(t)$ are i.i.d.~Poisson($t$) random variables.
+%    To apply Cram\'er's Theorem, we need the rate function for the 
+%Poisson($t$) distribution,
+%    which is
+%    \[
+%        \Lambda^*(x) = \sup_{\alpha > 0} \left[ \alpha x - \lambda(\alpha) \right],
+%    \]
+%    where $\lambda(\alpha) = \log \IE[\exp(\alpha Z_1(t))] = t(e^\alpha - 1)$.
+%    Now, the supremum of $\alpha x + t - te^\alpha$ is attained at $x = t e^\alpha$,
+%    and so
+%    \[
+%        \Lambda^*(x) = x \log(x/t) - x + t .
+%    \]
+%    Cram\'er's Theorem then gives
+%    \begin{align*}
+%        \limsup_{\theta \to \infty}
+%        \frac{1}{\theta} \log
+%        \IP\left\{
+%            \frac{\Pi(\theta t)}{\theta}
+%            > t + A(\epsilon^2 + t)
+%        \right\}
+%    &\le
+%        - \Lambda^*(t + A(\epsilon^2 + t))
+%    \\ &=
+%        A(\epsilon^2 + t)
+%        -
+%        \big(t + A(\epsilon^2 + t)\big) \log\left( 1 + \frac{A(\epsilon^2 + t)}{t} \right) 
+%    \\ &\le
+%        A(\epsilon^2 + t)
+%        -
+%        \big(t + A(\epsilon^2 + t)\big) \log(1 + A)
+%    \\ &\le
+%        A(\epsilon^2 + t) \left( 1 - \frac{1}{2} \log(1 + A) \right)
+%        -
+%        \frac{1}{2} \big(t + A(\epsilon^2 + t)\big) \log(1 + A)  .
+%    \end{align*}
+%    Since $(1/2) \log(1 + A) > 3/2$, from which $1 - (1/2) \log(1 + A) < - 1/2$,
+%    the proof is complete.
+\end{proof}
+
+As advertised, we wish to control the difference between
+$\psi_t^{\epsilon,x}(y)$
+and $p_{\epsilon^2 + t}(x, y)$.
+
+\begin{lemma}
+    \label{Lemma:BoundPsiHS2}
+    In the notation of Lemma~\ref{PsiBoundHS},
+    %and with $A$ as in Lemma~\ref{lem:poisson_ld},
+    \begin{multline}
+\label{heat kernel estimate}
+        \left|
+            \psi_t^{\epsilon, x}(y)
+            -
+            p_{\epsilon^2 + t}(x, y)
+        \right|
+        \\
+\le
+        \frac{C}{(\epsilon^2 \theta)^{d/2}}
+        p_{6(\epsilon^2+t)}(x, y)
+        +
+	    C \left(1+
+	    \frac{1}{(\epsilon^2 + t)^{d/2}}\right)
+	    \exp(- \epsilon^2 \theta / 2)
+        %+
+        %\frac{C}{(\epsilon^2 + t)^{d/2}}
+        %\IP\left\{
+        %    \tau(t) > A(\epsilon^2 + t)
+        %\right\} 
+	    .
+    \end{multline}
+\end{lemma}
+
+\begin{proof}
+    Still using the notation of Lemma~\ref{PsiBoundHS},
+%the three terms on the right hand side of 
+%equation~(\ref{heat kernel estimate})
+%    correspond to bounds obtained by partitioning
+ we partition into three events according to the value of $\tau(t)$.
+    Let $A_1 = \{ \tau(t) < - (\epsilon^2 + t)/2 \}$,
+    $A_2 = \{ \tau(t) > 2(\epsilon^2 + t) \}$,
+    and $A_3$ the remaining event, $\{ - (\epsilon^2 + t)/2 \le \tau(t) \le 2(\epsilon^2 + t) \}$.
+    Then,
+    \begin{align*}
+        \left|
+            \psi_t^{\epsilon, x}(y)
+            -
+            p_{\epsilon^2 + t}(x, y)
+        \right|
+        &=
+        \left|
+        \IE\left[
+            p_{\epsilon^2 + t + \tau(t)}(x, y)
+            -
+            p_{\epsilon^2 + t}(x, y)
+        \right]
+        \right|
+        \\&\le
+        \IE\left[
+            (1_{A_1} + 1_{A_2} + 1_{A_3})
+            \left|
+            p_{\epsilon^2 + t + \tau(t)}(x, y)
+            -
+            p_{\epsilon^2 + t}(x, y)
+        \right|
+        \right] .
+    \end{align*}
+    For the first term, note that if $a < b$ then
+    \begin{align*}
+        |p_a(x, y) - p_b(x, y)| 
+        &=
+        \frac{1}{(2\pi)^{d/2}}
+        \left|
+            \frac{1}{a^{d/2}}
+            e^{-\|x - y\|^2 / 2a}
+            -
+            \frac{1}{b^{d/2}}
+            e^{-\|x - y\|^2 / 2b}
+        \right|
+        \\ &=
+        \frac{1}{(2\pi a^2)^{d/2}}
+            e^{-\|x - y\|^2 / 2b}
+        \left|
+            e^{-\|x - y\|^2 \left(\frac{1}{2a} - \frac{1}{2b}\right)}
+            -
+            \left(\frac{a}{b}\right)^{d/2}
+        \right|
+        \\ &\le
+        C \left(\frac{b}{a}\right)^{d/2}
+        p_b(x, y) ,
+    \end{align*}
+    where the inequality follows because both terms under the absolute value 
+are less than 1.
+Since, on the event $A_1$, $\tau(t)<0$, we can  
+apply this with $a = \epsilon^2 + t + \tau(t)$ and $b = \epsilon^2 + t$,
+and, using the bound~(\ref{bound for negative tau}),
+    \begin{align*}
+        \IE\left[
+            1_{A_1} |p_a(x, y) - p_b(x, y)| 
+        \right]
+        & \le
+            C \left(\frac{\epsilon^2 + t}{\epsilon^2}\right)^{d/2}
+            p_{\epsilon^2 + t}(x, y) 
+            \IP\left\{ \tau(t) < - \frac{\epsilon^2 + t}{2} \right\}
+        \\ & \le
+            C \frac{1}{\epsilon^d}
+            \IP\left\{ \tau(t) < - \frac{\epsilon^2 + t}{2} \right\}
+        \\ & \le
+        C \exp\left(-\frac{\theta \epsilon^2}{2} \right) .
+    \end{align*}
+
+    For the third term, we will first collect some facts.
+    Observe that on the event $A_3$,
+    $\epsilon^2 + t + \tau(t)$ is between
+    $(\epsilon^2 + t)/ 2$ and $3(\epsilon^2 + t))$,
+    and for any $s$ in this interval,
+    \begin{align}
+        p_{2s}(y)
+        &\le \nonumber
+        \left( \frac{
+            2 (\epsilon^2 + t)3
+        }{
+            \epsilon^2 + t
+        } \right)^{d/2}
+        p_{6(\epsilon^2 + t)}(x, y)
+        \\ &= \label{eqn:p_bounded_on_interval}
+        6^{d/2}
+        p_{6(\epsilon^2 + t)}(x, y) .
+    \end{align}
+    Moreover, since $u e^{-u} \le e^{-1}$ for all $u \ge 0$,
+    \begin{align}
+        \frac{\|x - y\|^2}{s} p_s(x, y)
+        &= \nonumber
+        \frac{4}{(2 \pi s)^{d/2}}
+        e^{- \frac{ \|x-y\|^2 }{ 4s }}
+        \frac{\|x-y\|^2}{4s}
+        e^{- \frac{ \|x-y\|^2 }{ 4s }}
+        \\ &\le \label{eqn:p_deriv_term2}
+        C p_{2s}(x, y) .
+    \end{align}
+    Now, by the Intermediate Value Theorem,
+    \begin{align}
+\label{deduction from IVT}
+        \left|
+            p_{\epsilon^2 + t + \tau(t)}(x, y)
+            -
+            p_{\epsilon^2 + t}(x, y)
+        \right|
+        &=
+        \left| \tau(t) \right|
+        \left| \frac{\partial p_s(x, y)}{\partial s} \right|
+    \end{align}
+    for some $s$ between $\epsilon^2 + t + \tau(t)$ and $\epsilon^2 + t$.
+   Since 
+    \begin{align*}
+        \partial_ s p_s(x, y)
+        &=
+        \partial_s
+        \left(
+            \frac{1}{(2 \pi s)^{d/2}}
+            \exp\left( - \frac{\|x - y\|^2}{2 s} \right)
+        \right)
+        \\ &=
+        - \frac{d}{2s} p_s(x, y) + \frac{\|x - y\|^2}{2 s^2} p_s(x, y),
+    \end{align*}
+    applying the inequality~\eqref{eqn:p_deriv_term2},
+    using the fact that $p_s(x, y) \le 2^{d/2} p_{2s}(x,y)$,
+    and then \eqref{eqn:p_bounded_on_interval},
+    we have that for any $s \in ((\epsilon^2 + t)/ 2, 3(\epsilon^2 + t))$,
+    \begin{align*}
+        \left| \frac{\partial}{\partial s} p_s(x, y) \right|
+        \le
+        \frac{C}{s} p_{2s}(x, y) 
+        \le
+        \frac{C}{\epsilon^2 + t} p_{6(\epsilon^2 + t)}(x, y) .
+    \end{align*}
+    Therefore, recalling that $\IE[\tau(t)^2] = t / \theta$, substituting 
+into~(\ref{deduction from IVT}),
+    \begin{align*}
+        \IE\left[
+            1_{A_3}
+            \left|
+                p_{\epsilon^2 + t + \tau(t)}(x, y)
+                -
+                p_{\epsilon^2 + t}(x, y)
+            \right|
+        \right]
+        &\le
+            \frac{C}{\epsilon^2 + t}
+                p_{6(\epsilon^2 + t)}(x, y)
+            \IE\left[|\tau(t)|\right]
+        \\ &\le
+            \frac{C}{\epsilon^2 + t}
+                p_{6(\epsilon^2 + t)}(x, y)
+            \IE\left[\tau(t)^2\right]^{1/2}
+        \\ &=
+            \left( \frac{Ct}{\theta(\epsilon^2 + t)^2} \right)^{1/2}
+                p_{6(\epsilon^2 + t)}(x, y)
+        \\ &\le
+            \frac{C}{\sqrt{\theta \epsilon^2}}
+                p_{6(\epsilon^2 + t)}(x, y) ,
+    \end{align*}
+    where the last inequality follows from $2 \epsilon^2 t \le (\epsilon^2 + t)^2$.
+
+    Finally, on the event $A_2 = \{\tau(t) > 2(\epsilon^2 + t)\}$,
+    we simply use
+    \begin{align*}
+        \left|
+            p_{\epsilon^2 + t + \tau(t)}(x, y)
+            -
+            p_{\epsilon^2 + t}(x, y)
+        \right|
+        \le
+        \frac{C}{(\epsilon^2 + t)^{d/2}} ,
+    \end{align*}
+    so that
+    \begin{align*}
+        \IE\left[
+        1_{A_2}
+        \left|
+            p_{\epsilon^2 + t + \tau(t)}(x, y)
+            -
+            p_{\epsilon^2 + t}(x, y)
+        \right|
+        \right]
+        \le
+        \frac{C}{(\epsilon^2 + t)^{d/2}}
+        \IP\left\{
+            \tau(t) > 2 (\epsilon^2 + t)
+        \right\} ,
+    \end{align*}
+    and apply Lemma~\ref{lem:poisson_ld}
+    with $A=2$.
+\end{proof}
+
+The last result will be useful when combined with the next bound for the heat kernel.
+
+\begin{lemma}
+    \label{Lemma:ContinuityHS}
+Let $s>0$, and $x, y, z\in \IR^d$. The following estimate holds:
 \[
-\int_0^t \big\langle \mathcal{L}^\theta T_{\epsilon^2} f, 
-\eta_s^N(dx)\big\rangle ds 
-\rightarrow \int_0^t \big\langle \frac{1}{2} \Delta f(x), 
-\varphi (s,x) dx \big\rangle ds. 
+    |p_s(x,z) - p_s(y,z)|
+    \leq
+    \frac{C\|x-y\|}{\sqrt{s}} \left(p_{2s}(x,z) + p_{2s}(y,z)\right) ,
 \]
-
-Since we only know that for every sequence of measures satisfying the
-conditions of Theorem~\ref{thm:local_convergence}
-there is a {\em weakly} convergent subsequence,
-the difficulty is the non-linear term in the martingale problem. 
-The first step is to prove an approximation of the form:
-\begin{align*}
-\IE\Big[
-\int_0^t\big\langle T_{\epsilon^2} f(y) F\big(\rho_\epsilon *\eta_s(y)\big), 
-\eta_s(dy) \big\rangle ds\Big]
-\sim 
-\IE\Big[
-\int_0^t\big\langle T_{\epsilon^2} f(y) F\big(\rho_\epsilon * \eta_s(y)\big), 
-\rho_\epsilon * \eta_s(y) dy \big\rangle ds\Big].
-\end{align*}
-This is the content of Proposition~\ref{CuadraticApprox}, 
-but first we need a continuity 
+where the constant $C$ does not depend on $x,y,z$ or $s$.
+\end{lemma}
+
+\begin{proof}
+
+    Expanding the difference of two squares,
+    \begin{align*}
+        e^{- \frac{\|y-z\|^2}{2 s}}
+        -
+        e^{- \frac{\|x-z\|^2}{2 s}}
+        &=
+        \left(
+            e^{-\frac{\|y-z\|^2}{4 s}}
+            -
+            e^{-\frac{\|x-z\|^2}{4 s}}
+        \right)
+        \left(
+            e^{-\frac{\|y-z\|^2}{4 s}}
+            +
+            e^{-\frac{\|x-z\|^2}{4 s}}
+        \right) .
+    \end{align*}
+Now, thinking of the first term in brackets as a function of a single variable on
+the line segment $[y,z]$ connecting $y$ to $z$, we can apply the
+Intermediate Value Theorem and take the modulus to bound this expression by 
+    \[
+        \|y-x\|
+        \left( \frac{2\|w-z\|}{4s} \exp\left(-\frac{\|w-z\|^2}{4s}\right)\right)
+        (4 \pi s)^{d/2}
+        \left( p_{2s}(y,z)+p_{2s}(x,z) \right)
+    \]
+    for some $w\in [y,z]$.
+    Using the fact that $x e^{-x^2}$ is uniformly bounded,
+    we can bound the first bracket in the last equation by $C/\sqrt{s}$, and the result follows.
+\end{proof}
+
+We now have the ingredients that we need to write down a continuity 
 estimate on $\rho_\epsilon*\eta$.
-
 We fix $\delta>0$ and 
@@
 \widehat{\epsilon}(\delta,\epsilon,\theta):=
-e^{-\epsilon^2\theta}+\frac{1}{(\epsilon^2+\delta)^{d/2}}
-\frac{1}{(A+1)^{\epsilon^2\theta}}e^{-\epsilon^2\theta},
+e^{-\epsilon^2\theta/2}\left(1+\frac{1}{(\epsilon^2+\delta)^{d/2}}\right),
+%\frac{1}{(A+1)^{\epsilon^2\theta}}e^{-\epsilon^2\theta},
 \]
@@
 \big\langle |p_{\epsilon^2+s}(y,z)-p_{\epsilon^2+s}(w,z)|, 
-\eta_0(dz)\big\rangle \nonumber 
-+\frac{C}{(\theta\epsilon^2)^{d/2}}\big\langle 
-p_{2(A+1)(\epsilon^2+s)}(y,z)+p_{2(A+1)(\epsilon^2+s)}(w,z), \eta_0(dz)
-\big\rangle
-\nonumber
-\\ 
-&+ \int_{s-\delta}^s \big\langle 
-|\psi_{s-r}^{\epsilon,y}(z) + \psi_{s-r}^{\epsilon, w}(z) |
-\cdot |F(\rho_\epsilon*\eta_r(z)|, 
-\eta_r(dz) \big\rangle  dr
+\eta_0(dz)\big\rangle 
 \nonumber
@@
 \\ 
-&+
-\frac{C}{(\epsilon^2\theta)^{d/2}}
-\int_0^{s-\delta}
-\big\langle |p_{2(A+1)(s-r+\epsilon^2)}(y,z)+
-p_{2(A+1)(s-r+\epsilon^2)}(w,z)|
+	&+\frac{C}{(\theta\epsilon^2)^{d/2}}\big\langle 
+p_{6(\epsilon^2+s)}(y,z)+p_{6(\epsilon^2+s)}(w,z), \eta_0(dz)
+\big\rangle
+	+\widehat{\epsilon}(\delta,\epsilon,\theta)\langle 1,\eta_0(dz)\rangle
+	\nonumber
+	\\
+&+ \int_{s-\delta}^s \big\langle 
+|\psi_{s-r}^{\epsilon,y}(z) + \psi_{s-r}^{\epsilon, w}(z) |
 \cdot |F(\rho_\epsilon*\eta_r(z)|, 
@@
 \nonumber
+	\\ &+
+\frac{C}{(\epsilon^2\theta)^{d/2}}
+\int_0^{s-\delta}
+\big\langle |p_{6(s-r+\epsilon^2)}(y,z)+
+p_{6(s-r+\epsilon^2)}(w,z)|
+\cdot |F(\rho_\epsilon*\eta_r(z)|, 
+\eta_r(dz) \big\rangle  dr
+\nonumber
 \\
@@
 +|M_s(y)|+|M_s(w)| 
-+\mathcal{O}\big(\widehat{\epsilon}(\delta,\epsilon,\theta)
-\big)  
+%+\mathcal{O}\big(\widehat{\epsilon}(\delta,\epsilon,\theta)
+%\big)  
 \nonumber
@@
 &
-+\frac{C}{(\theta\epsilon^2)^{d/2}}\big\langle 
-p_{2(A+1)(\epsilon^2+s)}(y,z)+p_{2(A+1)(\epsilon^2+s)}(w,z), \eta_0(dz)
+	+\big\langle \frac{C}{(\theta\epsilon^2)^{d/2}}\Big( 
+	p_{6(\epsilon^2+s)}(y,z)+p_{6(\epsilon^2+s)}(w,z)\Big)+
+	\widehat{\epsilon}(\delta,\epsilon,\theta) , \eta_0(dz)
 \big\rangle
@@
 &+
+\int_0^{s-\delta}
+\big\langle \Big\{
 \frac{C}{(\epsilon^2\theta)^{d/2}}
-\int_0^{s-\delta}
-\big\langle |p_{2(A+1)(s-r+\epsilon^2)}(y,z)+
-p_{2(A+1)(s-r+\epsilon^2)}(w,z)| 
+|p_{6(s-r+\epsilon^2)}(y,z)+
+p_{6(s-r+\epsilon^2)}(w,z)| +\widehat{\epsilon}(\delta,\epsilon,\theta)\Big\}
 \cdot |F(\rho_\epsilon*\eta_r(z)|, 
@@
 &
-+|M_s(y)|+|M_s(w)| 
-+\mathcal{O}\big(\widehat{\epsilon}(\delta,\epsilon,\theta)
-\big) . 
++|M_s(y)|+|M_s(w)|. 
+%+\mathcal{O}\big(\widehat{\epsilon}(\delta,\epsilon,\theta)
+%\big) . 
 \label{difference in rhos}
 \end{align} 
-Although this expression is lengthy, when we need to control its 
-contribution to expressions below, it will really just be a matter of
+Although this expression is lengthy, we have successfully isolated the
+terms involving $\|y-w\|$, which will control the regularity as we pass to the
+limit. Asymptotically, we 
+don't expect the martingale terms to contribute, since their 
+quadratic variation scales with $\theta/(N\epsilon^d)$, and we can see that 
+under the assumption that $\epsilon^2\theta\to\infty$, for any fixed $\delta>0$,
+the terms arising from 
+approximating the transition 
+density of the Gaussian 
+walk by the heat kernel at a fixed time, will tend to zero. 
+There is some technical work to be done to rigorously identify the
+limit points of $\rho_\epsilon*\eta^N$, but 
+it really amounts to 
 applying the tower property and our moment bounds from 
@@
 
-\comment{perhaps explain: the next proposition is useful because we'll want to use weak convergence of $\smooth{\epsilon}\eta_s$; but in the martingale we have the term on the left in the proposition; probably there are other ways to do this.}
-\comment{ACTUALLY BETTER we want to transfer $T_\epsilon^2$ over onto $\eta$; this happens in two steps, first this proposition; next using that $T_{\epsilon^2}f - f$ is small; ALISON}
+\subsection{Identification of the limit}
+\label{limit in onestep case}
+
+We now turn to the identification of the limit points of the sequence 
+$\big\{\big(\rho_\epsilon*\eta_t^N(x)dx\big)_{t\geq 0}\big\}_{N\geq 1}$.
+Writing
+$\langle f, \rho_\epsilon*\eta_t^N(x)dx\rangle=
+\langle \rho_\epsilon*f(x), \eta_t^N(dx)\rangle
+=\langle T_{\epsilon^2}f(x),\eta_t^N(dx)\rangle$,
+where $T_{\cdot}$ denotes the heat semigroup, we proceed
+by examining the terms in the semimartingale
+decomposition~(\ref{eqn:eta_martingale})
+%of $\langle f, \rho_\epsilon*\eta_t^N(x)dx\rangle=
+%\langle \rho_\epsilon*f, \eta_t^N(dx)\rangle$.
+when the test function $f$ is replaced by $T_{\epsilon^2}f$.
+
+The linear term is straightforward.
+By a Taylor expansion, writing $\{T_t\}_{t\geq 0}$ for the heat semigroup,
+\begin{align*}
+\int_0^t \big\langle \mathcal{L}^\theta T_{\epsilon^2} f, 
+	\eta_s^N(dx)\big\rangle ds 
+&= \int_0^t \big\langle \frac{1}{2} \Delta T_{\epsilon^2} f(x), 
+	\eta_s^N(dx) \big\rangle 
+	+ \mathcal{O}\Big(\frac{1}{\theta}\Big) 
+\\ &= \int_0^t \big\langle \frac{1}{2} \Delta f(x), \rho_\epsilon* \eta_s^N(x) dx 
+	\big\rangle ds + \mathcal{O}\Big(\frac{1}{\theta}\Big).
+\end{align*}
+Thus, from weak convergence we can deduce that under our scaling,
+for any (weakly) convergent subsequence $\{\rho_\epsilon*\eta^N(x)dx\}_{N\geq 1}$,
+\[ 
+\int_0^t \big\langle \mathcal{L}^\theta T_{\epsilon^2} f, 
+\eta_s^N(dx)\big\rangle ds 
+\rightarrow \int_0^t \big\langle \frac{1}{2} \Delta f(x), 
+\varphi (s,x) dx \big\rangle ds. 
+\]
+
+The nonlinear term in the semimartingale decomposition is more intricate. 
+It takes the form
+%Since we only know that for every sequence of measures satisfying the
+%conditions of Theorem~\ref{thm:local_convergence}
+%there is a {\em weakly} convergent subsequence,
+%the difficulty is the non-linear term in the martingale problem. 
+%The first step is to prove an approximation of the form:
+\[ %\begin{align*}
+\IE\Big[
+\int_0^t\big\langle T_{\epsilon^2} f(y) F\big(\rho_\epsilon *\eta_s(y)\big), 
+\eta_s(dy) \big\rangle ds\Big]
+\]
+and we should like to show that this converges to 
+	\[
+		\int_0^t\int f(y)F(\varphi(s,y))\varphi(s,y)dyds.
+	\]
+	We proceed in stages. First we should like to transfer the 
+	heat semigroup from $T_{\epsilon^2}f$ onto $\eta_s$. 
+	Since $f$ is smooth, this will follow easily if we can show that
+\begin{align*}
+\IE\Big[
+\int_0^t\big\langle T_{\epsilon^2} f(y) F\big(\rho_\epsilon *\eta_s(y)\big), 
+\eta_s(dy) \big\rangle ds\Big]
+	\sim 
+\IE\Big[
+\int_0^t\big\langle T_{\epsilon^2} f(y) F\big(\rho_\epsilon * \eta_s(y)\big), 
+\rho_\epsilon * \eta_s(y) dy \big\rangle ds\Big].
+\end{align*}
+This is the content of Proposition~\ref{CuadraticApprox}.
 
@@
 \label{replacing nonlinear term}
-\lim_{\epsilon\to 0}\Big|\int_0^t \IE\Big[\big\langle T_{\epsilon^2} f(y) 
+\lim_{\epsilon\to 0}\IE\Big[\Big|\int_0^t\big\langle T_{\epsilon^2} f(y) 
 F(\rho_\epsilon *\eta_s(y)), \eta_s(y) \big\rangle 
@@
 F(\rho_\epsilon * \eta_s(y)), \rho_\epsilon * \eta_s(y) dy 
-\big\rangle\Big]ds \Big|
+\big\rangle ds \Big|\Big]
 =0.
@@
 \begin{proof}
-In fact we are going to fix $\delta>0$, and show that
+In fact we are going to fix $\delta>0$, with $t>\delta$, and show that
 the expression on the left hand side of~\eqref{replacing nonlinear term} is
@@
 	\lim_{\epsilon\to 0}
-	\int_0^t\big\langle \int |\rho_\epsilon*\eta_s(y)-\rho_\epsilon*\eta_s(w)|
+	\IE\Big[	\int_0^t\big\langle \int |\rho_\epsilon*\eta_s(y)-\rho_\epsilon*\eta_s(w)|
 \left(\rho_\epsilon*\eta_s(y))^k+\rho_\epsilon*\eta_s(w)^k\right)
-p_{\epsilon^2}(w,y)dy, \eta_s(dw)\big\rangle ds
+	p_{\epsilon^2}(w,y)dy, \eta_s(dw)\big\rangle ds\Big]
 =0,
 \end{equation}
-\comment{check this: which we prove by showing the expectation of this positive quantity goes to zero; e.g., see Lemma 7.5(?): ALISON}.
-
 We are going to use the estimate~(\ref{difference in rhos}).
@@
 	\big\langle\frac{\|y-w\|}{\sqrt{s+\epsilon^2}}
-\big(p_{2(s+\epsilon^2)}(y,z)+p_{2(s+\epsilon^2)}(w,z)\big),\eta_o(dz)\big\rangle
+\big(p_{2(s+\epsilon^2)}(y,z)+p_{2(s+\epsilon^2)}(w,z)\big),\eta_0(dz)\big\rangle
 \\
@@
 \end{multline*}
-We ``borrow'' from the exponential term in $p_\epsilon^2(w,y)$ to bound
+We ``borrow'' from the exponential term to see that 
+$\|y-w\|p_{\epsilon^2}(w,y)\leq C\epsilon p_{2\epsilon^2}(w,y)$
+and so bound
 this by
@@
 
-Now consider the contribution to he left hand side of~(\ref{target expression})
+Now consider the contribution to the left hand side of~(\ref{target expression})
 from the second term in~(\ref{difference in rhos}). Since $F$ is a polynomial,
@@
 \IE\Big[\big\langle \rho_\epsilon*\eta_r(z)^{j+k+1}, \eta_r(dz)\rangle\Big]
-+\IE\Big[\int\int p_{2(s-r)}(y,x)\rho_\epsilon*\eta_r(x)\rho_\epsilon*\eta_r(y)^{k+1} dy dx\Big]
++\IE\Big[\int\int p_{2(s-r)}(y,x)\rho_\epsilon*\eta_r(x)
+	\rho_\epsilon*\eta_r(y)^{j+k+1} dy dx\Big]
 \\
@@
 \IE\Big[\big\langle \rho_\epsilon*\eta_r(z)^{j+k+1}, \eta_r(dz)\rangle\Big]
-+2\int\IE\Big[\rho_\epsilon*\eta_r(x)^{k+2}\Big]dx,
++2\int\IE\Big[\rho_\epsilon*\eta_r(x)^{j+k+2}\Big]dx,
 \end{multline*} 
@@
 \]
+Since $\psi_{t-s}^{\epsilon,x}(y)=p_{T(t-s)+\epsilon^2}(x,y)$, 
+rearranging~(\ref{})
+we see that we can pull a convolution with $p_{\epsilon^2/2}$ out of
+our expressions for $M_s(x)$ and $M_s(w)$ and so all the manipulations 
+that we used to control terms above with still be valid.
 To deal with the two terms in the produce involving $|M_s(y)|$, we write 
@@
 
-\comment{Probably should put a bit more detail in here?}
-\comment{key bit is that we can always write $M_s(w)$ as a convolution of $p_{\epsilon^2/2}$ with something: ALISON}
-
 Control of the terms arising from approximating $\psi^{\epsilon,x}$
@@
 \[
-\lim_{\epsilon\to 0}\Big|\int_0^t \IE\Big[\big\langle T_{\epsilon^2} f(y) 
-F(\rho_\epsilon *\eta_s(y)), \eta_s(y) \big\rangle 
-- \big\langle T_{\epsilon^2} f(y) 
+\lim_{\epsilon\to 0}\IE\Big[\Big|\int_0^t\big\langle T_{\epsilon^2} f(y) 
+F(\rho_\epsilon *\eta_s(y)), \eta_s(y) \big\rangle ds 
+- \int_0^t\big\langle T_{\epsilon^2} f(y) 
 F(\rho_\epsilon * \eta_s(y)), \rho_\epsilon * \eta_s(y) dy 
-\big\rangle\Big]ds\Big|
+\big\rangle ds\Big|\Big]
 <C\delta,
@@
 
-To complete the characterisation of the limit, it remains to show that if we
+Since $f$ is smooth, $T_\epsilon^2f-f$ is ${\mathcal O}(\epsilon)$, 
+with an application of the triangle inquality, 
+\[
+\lim_{\epsilon\to 0}\IE\Big[\Big|\int_0^t\big\langle T_{\epsilon^2} f(y) 
+F(\rho_\epsilon *\eta_s(y)), \eta_s(y) \big\rangle ds 
+- \int_0^t\big\langle f(y) 
+F(\rho_\epsilon * \eta_s(y)), \rho_\epsilon * \eta_s(y) dy 
+\big\rangle ds\Big|\Big]
+<C\delta,
+\]
+now follows immediately.
+Thus to complete the characterisation of the limit, 
+it remains to show that if we
 take a convergent subsequence 
@@
 \end{equation}
-The converge of higher powers will follow in an entirely analogous manner, but
+The convergence of higher powers will follow in an entirely analogous manner, but
 with more complex expressions.
@@
 &\int_0^t 
-\mathbb{E}\left[\big| \langle f(y), (\eta_s * \rho_\epsilon(y))^2) dy \rangle 
+\mathbb{E}\left[\big| \langle f(y), (\rho_\epsilon*\eta_s(y))^2) dy \rangle 
 - \int \int f(y) (\rho_\epsilon * \eta_s)(z) \rho_\tau (z-y) 
@@
 -(\rho_\epsilon * \eta_s)(z) \right|   \rho_\tau(z-y) dz \right\} 
-(\rho_\epsilon *\eta_s)(y) \right] ds  dy 
+(\rho_\epsilon *\eta_s)(y) \right] ds  dy. 
 \label{b1}
@@
 dy_{k}\ldots dy_1 ds\Big| \Big]
-	\\
 	\leq C\tau,

### 2023-04-27 forwards-and-backwards.tex
put back in general kernel for PME

@@
 Suppose that
-% we can write $\rho_\gamma=\zeta*\check{\zeta}$, where $\check{\zeta}(x)=\zeta(-x)$ and
-% $\zeta\in\mathcal{S}(\IR^d)$ (the Schwartz space of rapidly decreasing functions).
-$\rho_\gamma = p_{\epsilon^2_\gamma}$,
-and that %$\psi_0^\epsilon\in L^1(\IR^d)$, 
+we can write $\rho_\gamma=\zeta*\check{\zeta}$, where $\check{\zeta}(x)=\zeta(-x)$ and
+$\zeta\in\mathcal{S}(\IR^d)$ (the Schwartz space of rapidly decreasing functions).
+Furthermore, suppose that %$\psi_0^\epsilon\in L^1(\IR^d)$, 
 $\psi_0^\epsilon\geq 0$ is such that
@@
 the proof in $d=1$ (although we retain the notation $\nabla$).
-However to recall the dependence on $\epsilon$ we write $\rho^\epsilon$ for $\rho_\gamma$
-(which recall for this Proposition we suppose is Gaussian
-and equal to $p_{\epsilon^2_\gamma}$).
+However, to recall the dependence on $\epsilon$ we write $\rho^\epsilon$ for $\rho_\gamma$.
 It should be clear that it extends almost without change
@@
 \end{equation*}
-% and we assume that $\rho=\zeta*\check{\zeta}$ with $\zeta$ a rapidly decreasing function. 
-% The example we have in mind is $\zeta$ (and therefore $\rho$) being
+and 
+we assume that $\rho=\zeta*\check{\zeta}$ with $\zeta$ a rapidly decreasing function. 
+The example we have in mind is $\zeta$ (and therefore $\rho$) being the density of
+a mean zero Gaussian random variable.  
 We shall prove that under the 
@@
 \begin{proof}[Proof of Proposition~\ref{nonlocalPME to PME}]
-Write $\zeta = p_{\epsilon^2_\gamma / 2}$, so that $\rho = \zeta * \zeta$.
 First observe that
@@
 \int\int\int \psi_t^\epsilon(x)\psi_t^\epsilon(x-y)\zeta^{\epsilon}(y-z)
-{\zeta}^{\epsilon}(z) dz dy dx 
+\check{\zeta}^{\epsilon}(z) dz dy dx 
 \\
@@
 \int\int\int\nabla \psi_t^\epsilon(x-y)\zeta^{\epsilon}(y-z)
-{\zeta}^{\epsilon}(z)
+\check{\zeta}^{\epsilon}(z)
 \psi_t^\epsilon(x)\nabla\phi(x) dz  dy  dx
@@
 \int\int\int \psi_t^\epsilon(x-y)\zeta^{\epsilon}(y-z)
-{\zeta}^{\epsilon}(z)\nabla \psi_t^\epsilon(x)\nabla\phi(x) dz dy  dx
+\check{\zeta}^{\epsilon}(z)\nabla \psi_t^\epsilon(x)\nabla\phi(x) dz dy  dx
 \\

### 2023-04-27 forwards-and-backwards.tex
edits after meeting

@@
     $$
-        |\gamma(x, \smooth{\gamma} \eta(x)) \theta \int 
-        (r(y, \smooth{r} \eta(y)) f(y) - r(x, \smooth{r} \eta(x)) f(x))
+        |\gamma(x, \eta) \theta \int 
+        (r(y,\eta) f(y) - r(x, \eta) f(x))
         q_\theta(x, dy)| \le C_f (1 + |f(x)|)
@@
 \[
-\mu_\theta(x) = r(x, \smooth{r} X(x) / N) \gamma(x, \smooth{\gamma} X(x) / N)
-        - \frac{1}{\theta} F(x, \smooth{F} X(x) / N),
+\mu_\theta(x) = r(x,\eta) \gamma(x,\eta) - \frac{1}{\theta} F(x,\eta),
 \]
@@
 Since we take bounded $f$,
-for most situations the bound $C_f(1+f(x))$ in condition~\ref{gamma_B_condition} above
+for most situations the bound $C_f(1+|f(x)|)$ in condition~\ref{gamma_B_condition} above
 can be safely replaced simply by $C_f$;
@@
 \label{control through r} 
-    $|\partial_{x_i}r(x,\smooth{r}\eta(x))|$ and 
-    $|\partial_{x_ix_j}r(x,\smooth{r}\eta(x))|$
+    $|\partial_{x_i}r(x,\eta)|$ and 
+    $|\partial_{x_ix_j}r(x,\eta)|$
     are uniformly bounded for $x\in\IR^d$, $\eta\in\measures$;
@@
 because of the non-local reproduction mechanism, it no longer suffices to assume that 
-$r(x,\smooth{r}\eta(x))\gamma(x, \smooth{\gamma}\eta(x))-\mu_\theta(x)$ is of order $1/\theta$.
-An instructive example is the case where $\gamma \equiv 1$ and $F \equiv 0$, so that $\mu_\theta = r$,
+$r(x,\eta)\gamma(x,\eta)-\mu_\theta(x)$ is of order $1/\theta$.
+Perhaps the simples example in which we can see this
+is the case where $\gamma \equiv 1$ and $F \equiv 0$, so that $\mu_\theta = r$,
 and $\eta = \delta_x$
 (i.e., the population has all individuals at a single location),
-in which case the mean rate of change of the total population size
-is $\int (r(y, N \rho_r(y) ) - r(x, N \rho_r(x))) q_\theta(x, dy)$;
+so that $\smooth{r} \eta(y) = \rho_r(y)$.
+In this case, the mean rate of change of the total population size
+is $\int (r(y, \rho_r(y) ) - r(x, \rho_r(x))) q_\theta(x, dy)$;
 the first condition of Lemma~\ref{lem:conditions on r} would ensure this is of order $1/\theta$.
@@
     \label{prop:nonlocal_to_local}
-Let notation $\rho^\epsilon_F(x)=\rho_F\big(x/\epsilon)/\epsilon^d$.
+Let $\rho^\epsilon_F(x)=\rho_F\big(x/\epsilon)/\epsilon^d$.
 Assume $\varphi_0\in L^2(\IR)$ is a positive, uniformly Lipschitz, and uniformly bounded function. 
@@
 parameter $\epsilon^2$,
-and $\DG=\Delta$. 
+and $\DG=\Delta/2$. 
 Further suppose that $F(m)$ is a polynomial with $F(m)\ind_{m\geq 0}$ bounded above.
-Assume that $\langle 1,\eta_0\rangle$ is bounded, and that for all 
+Assume that $\langle 1,\eta_0^N\rangle$ is uniformly bounded, and that for all 
 $x\in\IR^d$ and $k\in \IN$,
@@
 	\label{target equation in local convergence}
-        \partial_t \varphi(t, x)=\Delta \varphi (t,x) +\varphi(t,x) F(\varphi(t,x)).
+        \partial_t \varphi(t,x) = \frac{1}{2} \Delta \varphi(t,x) +\varphi(t,x) F(\varphi(t,x)).
 \end{align}
@@
     Then the semigroup $Q_s$
-    of the motion of a lineages in frame that is moving at speed $\wavespeed$
+    of the motion of a lineage in the frame that is moving at speed $\wavespeed$
     is time-homogeneous with generator
@@
 thought of as modelling the density of an expanding population. 
-We focus instead on the monostable reaction of~(\ref{PME}).
+We focus on the monostable reaction of~(\ref{PME}).
 
@@
 getting too big. 
-In practice in our simulations shown in Figure~\ref{fig:pme_waves}
+In practice the simulations shown in Figure~\ref{fig:pme_waves}
 take discrete time steps of length $dt$ (with $dt$ suitably small),
@@
     \caption{
-        Simulated 1D populations under a porous medium equation with logistic growth~(\ref{PME}) in $d=1$,
+        Simulated populations under a porous medium equation with logistic growth~(\ref{PME}) in $d=1$,
         % comparing the simulated profile to the analytical solution;
@@
 Substituting $w^A$ in place of $w^F$ in~(\ref{eqn:fkpp_generator}),
-we find that the generator of an ancestral lineage is now, 
+we find that the generator of an ancestral lineage relative to the wavefront is now, 
 \begin{align*}
@@
 wave at a rate $s-2e^x/(1+e^{x})$.
-The strength of this drift decreases exponentially as $x\to -\infty$.
 The density of the speed measure for this diffusion is
@@
 constant solution $\varphi\equiv\varphi_0$ is a nontrivial equilibrium
-of~\eqref{general deterministic limit}. However, it may be not unique and/or unstable,
+of~\eqref{general deterministic limit}.
+However, this constant solution may not be unique, it may be unstable,
 and a stable solution may have oscillations on a scale determined by the interaction distance.
@@
 that of ancestral lineages) when we pass
-to the scaling limit in our model will be justified via this construction.
+to the scaling limit in our model will be justified via a lookdown construction.
 In this section 
-we present a lookdown construction for the general population model 
+we present such a construction for the general population model 
 of Definition~\ref{defn:mgale_construction}. It will be
@@
 the limiting ``spatial-level'' process will still be a point measure,
-and so we explicitly retains the notion of individuals and lineages
+and so we explicitly retain the notion of individuals and lineages
 in the infinite-population limit.
@@
 which captures the local rate of production of successful offspring.
-\comment{FROM ALISON This sort of true because it corresponds to lookdown events, but when I read this again I was confused. Is there a better way to say it?} 
-\comment{PETER: I'm not sure which bit is confusing?}
 Recall from equation~\eqref{eqn:mu_defn} that
@@
 \end{equation}
-Under Assumptions~\ref{def:model_setup}, as $\theta \to \infty$,
+Under Assumptions~\ref{def:model_setup}, as $\theta \to \infty$ and
 $c_\theta(x, \eta)$ will tend to $\alpha \gamma(x, \eta) r(x, \eta)$
@@
 $\left| \Pgen^{N}G_f(\eta^{N}_s) -\Pgen^{\infty}G_f(\eta^{N}_s) \right|$
-by a constant multiple of $\langle 1+F(x),\eta_s(dx)\rangle$.
+by a constant multiple of $\langle 1+|F(x)|,\eta_s(dx)\rangle$.
 Since $F$ is bounded above, there is a constant $K$ such that $|F|\leq K-F$ so
@@
 Summing over $x$,
-and using that $\psi \log \psi \ge - \psi |\log \psi| \ind_\psi \le 1$,
+    and using that $\psi \log \psi \ge - \psi |\log \psi| \ind_{\psi \le 1}$,
 we find
@@
 The first part of the proof mirrors that of Theorem~\ref{thm:nonlocal_convergence}:
-we establish sufficient bounds on the moments of $\rho_\epsilon*\eta_t(x)$ to
-establish tightness and then apply standard results on 
+in Subsection~\ref{bounds on rhoepsilon}
+we establish bounds on the moments of $\rho_\epsilon*\eta_t(x)$ that are sufficient to
+imply tightness and then apply standard results on 
 convergence of Markov processes from~\cite{ethier/kurtz:1986}. 
-Bounds on the moments of $\rho_\epsilon*\eta_t$
-are established in 
-Subsection~\ref{bounds on rhoepsilon}.
 The challenge
@@
 $\psi_0^{\epsilon,x}(y) = \rho_\epsilon(y-x) =p_{\epsilon^2}(x,y)$.
+
+To see why $\psi_t^{\epsilon,x}$ is useful,
+first note that for any time-dependent function $\phi_t(x)$
+with time derivative $\dot \phi_t(x) = \partial_t \phi_t(x)$,
+\begin{multline}
+\label{time dep mg prob}
+    \langle \phi_t(x), \eta_t(dx) \rangle
+    = 
+    \langle \phi_0(x), \eta_0(dx) \rangle
+    +
+    M_t(\phi_\cdot(\cdot))
+    +
+    \int_0^t \big\langle \mathcal{L}^\theta \phi_s(x) 
+        + \dot \phi_s(x), \eta_s(dx) \big\rangle ds
+    \\  {}
+    +
+    \int_{0}^t \big\langle \phi_s(x) F(x, \eta_s) , \eta_s(dx) \big\rangle ds ,
+\end{multline}
+where $M_t(\phi_\cdot(\cdot))$ is a martingale (with respect to the natural filtration)
+with quadratic variation given by~\eqref{eqn:prelimit_martingale_variation}
+with $f$ replaced by $\phi_s(\cdot)$.
+So, taking $\phi_s(\cdot)=\psi_{t-s}^{\epsilon,x}(\cdot)$ for $0 \le s \le t$,
+\begin{eqnarray}
+    \nonumber
+    \rho_\epsilon*\eta_t(x)&=&\langle\psi^{\epsilon,x}_0(y),\eta_t(dy)\rangle
+    \\
+    &=&\langle\psi^{\epsilon,x}_t(y),\eta_0(dy)\rangle
+    +\int_0^t\big\langle\psi^{\epsilon,x}_{t-s}(y)
+    F\big(\rho_\epsilon*\eta_s(y)\big), \eta_s(dy)\big\rangle ds
+    +M_t(x),
+    \label{expn rhoepsilon} 
+\end{eqnarray}
+where $M_t(x)$ has mean zero and a second moment we can easily write down.
 
@@
 \end{lemma}
+
 \begin{proof}
@@
 We proceed by induction. 
-
-For any time-dependent function $\phi_t(x)$
-with time derivative $\dot \phi_t(x) = \partial_t \phi_t(x)$,
-\begin{multline}
-\label{time dep mg prob}
-    \langle \phi_0(x), \eta_t(dx) \rangle
-    = 
-    \langle \phi_t(x), \eta_0(dx) \rangle
-    +
-    M_t(\phi_\cdot(\cdot))
-    +
-    \int_0^t \big\langle \mathcal{L}^\theta \phi_{t-s}(x) 
-- \dot \phi_{t-s}(x), \eta_s(dx) \big\rangle ds
-    \\  {}
-    +
- \int_{0}^t \big\langle \phi_{t-s}(x) F(x, \eta_s) , \eta_s(dx) \big\rangle ds ,
-\end{multline}
-where $M_t(\phi_\cdot(\cdot))$ is a martingale. 
-Taking $\phi_t(\cdot)=\psi_t^{\epsilon,x}(\cdot)$,
-\begin{eqnarray}
-\nonumber
-\rho_\epsilon*\eta_t(x)&=&\langle\psi^{\epsilon,x}_0(y),\eta_t(dy)\rangle
-\\
-&=&\langle\psi^{\epsilon,x}_t(y),\eta_0(dy)\rangle
-+\int_0^t\big\langle\psi^{\epsilon,x}_{t-s}(y)
-F\big(\rho_\epsilon*\eta_s(y)\big), \eta_s(dy)\big\rangle ds
-+M_t(x),
-\label{expn rhoepsilon}
-\end{eqnarray}
-where $M_t(x)$ is a martingale. 
 Taking expectations in~(\ref{expn rhoepsilon}), using that $F$ is bounded above, and 
@@
 we obtain~(\ref{moment bound rhoepsilon})
-in the case $k=1$. 
+(without the second term on the right hand side) in the case $k=1$.
 Moreover, rearranging~(\ref{expn rhoepsilon}) we find 
@@
 and~(\ref{flandoli trick for rhoepsilon}) for all exponents $j<k$.
-First we calculate the generator $\Pgen^N$ of our scaled population process applied
+First we apply the generator $\Pgen^N$ of our scaled population process
 to functions of the form $\langle f,\eta\rangle^k$.
-Recalling that each jump of the process involves the birth or death or a single 
+Recalling that each jump of the process involves the birth or death of a single 
 individual, and so increments $\langle f,\eta\rangle$ by $\pm f/N$ at the location of
@@
 \end{multline}
-Using(from Lemma~\ref{PsiBoundHS}) 
+Using (from Lemma~\ref{PsiBoundHS}) 
 that $\sup_s\|\psi^{\epsilon,x}_s(\cdot)\|_\infty=C/\epsilon^d$,
@@
 Under the assumptions of Theorem~\ref{thm:local_convergence},
-for each $k\geq 1$, $T>0$,
+for each $k\geq 1$, $T>0$, there is a $C(k,T)$ such that
 \begin{equation}
@@
 Under the assumptions of Theorem~\ref{thm:local_convergence},
-the sequence of measure valued processes $\{ \rho*\eta_t^N(x) dx \}_{t \geq 0}$
+the sequence of measure valued processes $\{ \rho_\epsilon*\eta_t^N(x) dx \}_{t \geq 0}$
 	(taking values in ${\mathcal D}_{[0,T]}(\measures)$) is tight.
@@
 
-As in the nonlocal case, it suffices to prove that for 
-for $T>0$, and any
-$f\in C_b^\infty (\IR^d)$ with bounded second derivatives, the
+As in the nonlocal case, it suffices to prove that for $T>0$,
+and any $f\in C_b^\infty (\IR^d)$ with bounded second derivatives, the
 sequence of real-valued processes 
@@
 \\
-+\int_s^t\Big\langle |F\big(\rho_\epsilon*\eta_u^N(x)\big)|\rho_\epsilon*f(x), 
++\int_s^t\Big\langle |F\big(\rho_\epsilon*\eta_u^N(x)\big)|\rho_\epsilon*|f|(x), 
 \eta_u^N(dx)\Big\rangle du +2\sup_{0\leq u\leq T}|\widehat{M}^N(f)_u|,
@@
 \end{multline*}
-We therefore have
-\begin{multline*}
-        \left|
-        \langle \rho_{\epsilon} * f, \eta_t^N \rangle
-        -
-        \langle \rho_{\epsilon} * f, \eta_s^N \rangle
-        \right|
-        \leq
-        \| \Delta f \|_\infty |t-s|
-        \sup_{0 \leq u \leq T } \langle 1, \eta_u^N \rangle
-\\
-+
-	\int_s^t
-	\big\langle \rho_\epsilon*|f|(x)\, \big|F\big(\rho_\epsilon*\eta_u^N(x)\big)\big|,
-\eta_u^N(dx)\big\rangle du +2\sup_{0\leq u\leq T}|\widehat{M}^N(f)_u|.
-    \end{multline*}
-Using the Burkholder-Davis-Gundy inequality, our
-moment bounds, and Markov's inequality
+The first term in~\eqref{tightness estimate} is therefore bounded by
+$$
+    \| \Delta f \|_\infty |t-s| \sup_{0 \leq u \leq T } \langle 1, \eta_u^N \rangle .
+$$
+% We therefore have
+% \begin{multline*}
+%         \left|
+%         \langle \rho_{\epsilon} * f, \eta_t^N \rangle
+%         -
+%         \langle \rho_{\epsilon} * f, \eta_s^N \rangle
+%         \right|
+%         \leq
+%         \| \Delta f \|_\infty |t-s|
+%         \sup_{0 \leq u \leq T } \langle 1, \eta_u^N \rangle
+% \\
+% +
+% 	\int_s^t
+% 	\big\langle \rho_\epsilon*|f|(x)\, \big|F\big(\rho_\epsilon*\eta_u^N(x)\big)\big|,
+% \eta_u^N(dx)\big\rangle du +2\sup_{0\leq u\leq T}|\widehat{M}^N(f)_u|.
+%     \end{multline*}
+By the Burkholder-Davis-Gundy inequality,
+$\IE[\sup_{0 \le u \le T} |\widehat{M}^N(f)_u|^2] \le C \IE[[\widehat{M}^N(f)]_u]$,
+and so using
+and Markov's inequality and
+our moment bounds,
 \begin{equation}
@@
         >\frac{\nu}{3}
-\Big]\leq \limsup_{N\to\infty}\frac{36}{\nu^2}\IE\big[[\widehat{M}^N(f)]_T\big]
-\leq \limsup_{N\to\infty}\frac{36}{\nu^2}\frac{C\theta}{N\epsilon^d} 
+    \Big]
+    \leq
+    \limsup_{N\to\infty} \frac{36}{\nu^2} \IE\big[[\widehat{M}^N(f)]_T\big]
+    \leq
+    \limsup_{N\to\infty}\frac{36}{\nu^2}\frac{C\theta}{N\epsilon^d} 
     =0. 
@@
 Now observe that, again using Lemma~\ref{bounds on moments}, 
+since $a^j b^k \le a^{j+k} b^{j+k}$,
 \begin{multline*}
@@
 We now have the ingredients that we need to write down a continuity 
-estimate on $\rho_\epsilon*\eta$.
+estimate for $\rho_\epsilon*\eta$.
 We fix $\delta>0$ and 
@@
 Using the semimartingale decomposition~(\ref{expn rhoepsilon}),
-and Lemmas~\ref{lem:poisson_ld} and~\ref{Lemma:BoundPsiHS2},
+and Lemma~\ref{Lemma:BoundPsiHS2},
 we have
@@
 \\ 
-&\leq 
+&\qquad
+    \leq 
 \big\langle |p_{\epsilon^2+s}(y,z)-p_{\epsilon^2+s}(w,z)|, 
@@
 \nonumber
-	\\
-	&+
+	\\ &\qquad \qquad {}
+    +
 \int_0^{s-\delta}
@@
 \nonumber
-\\ 
-	&+\frac{C}{(\theta\epsilon^2)^{d/2}}\big\langle 
+    \\ &\qquad \qquad {}
+	+ \frac{C}{(\theta\epsilon^2)^{d/2}}\big\langle 
 p_{6(\epsilon^2+s)}(y,z)+p_{6(\epsilon^2+s)}(w,z), \eta_0(dz)
@@
 	\nonumber
-	\\
-&+ \int_{s-\delta}^s \big\langle 
+    \\ &\qquad \qquad {}
++ \int_{s-\delta}^s \big\langle 
 |\psi_{s-r}^{\epsilon,y}(z) + \psi_{s-r}^{\epsilon, w}(z) |
@@
 \nonumber
-	\\ &+
+    \\ &\qquad \qquad {}
+    +
 \frac{C}{(\epsilon^2\theta)^{d/2}}
@@
 \nonumber
-\\
-&
-+|M_s(y)|+|M_s(w)| 
+\\ & \qquad \qquad {}
++ |M_s(y)|+|M_s(w)| 
 %+\mathcal{O}\big(\widehat{\epsilon}(\delta,\epsilon,\theta)
@@
 \nonumber
-\\
-&
+\\ & \qquad 
 \leq \Big\langle \frac{\|y-w\|}{\sqrt{s+\epsilon^2}}
@@
 \nonumber
-\\
-&+
+\\ & \qquad \qquad  {}
++
 \int_0^{s-\delta}\Big\langle\frac{\|y-w\|}{\sqrt{s-r+\epsilon^2}}
@@
 \nonumber
-\\
-&
-	+\big\langle \frac{C}{(\theta\epsilon^2)^{d/2}}\Big( 
+\\ & \qquad \qquad  {}
+	+ \big\langle \frac{C}{(\theta\epsilon^2)^{d/2}}\Big( 
 	p_{6(\epsilon^2+s)}(y,z)+p_{6(\epsilon^2+s)}(w,z)\Big)+
@@
 \nonumber
-\\
-&+
+\\ & \qquad \qquad  {}
++
 \int_0^{s-\delta}
@@
 \nonumber
-\\
-&
-+|M_s(y)|+|M_s(w)|. 
+\\ & \qquad \qquad  {}
++ |M_s(y)|+|M_s(w)|. 
 %+\mathcal{O}\big(\widehat{\epsilon}(\delta,\epsilon,\theta)
@@
 \end{align} 
+\comment{MISSING A TERM? the $\int_{s-\delta}^s$ one; and say it's bounded because of the moment bounds}
 Although this expression is lengthy, we have successfully isolated the
@@
 don't expect the martingale terms to contribute, since their 
-quadratic variation scales with $\theta/(N\epsilon^d)$, and we can see that 
-under the assumption that $\epsilon^2\theta\to\infty$, for any fixed $\delta>0$,
-the terms arising from 
+quadratic variation scales with $\theta/(N\epsilon^d)$, and
+under the assumption that $\epsilon^2\theta\to\infty$,
+for any fixed $\delta>0$, if $s > \delta$ the terms arising from 
 approximating the transition 
@@
 $\big\{\big(\rho_\epsilon*\eta_t^N(x)dx\big)_{t\geq 0}\big\}_{N\geq 1}$.
-Writing
+We would like to show that any limit point solves~\eqref{target equation in local convergence}
+in the limit, i.e.,
+\begin{equation}\label{eqn:target PDE weak form}
+    \langle f(x), \varphi(t,x)dx \rangle
+    =
+    \int_0^t
+        \Big\langle
+        \frac{1}{2}\Delta f(x) + f(x) F(\varphi(s,x))
+        ,
+        \varphi(s,x) dx
+        \Big\rangle
+    ds .
+\end{equation}
+Since 
 $\langle f, \rho_\epsilon*\eta_t^N(x)dx\rangle=
-\langle \rho_\epsilon*f(x), \eta_t^N(dx)\rangle
-=\langle T_{\epsilon^2}f(x),\eta_t^N(dx)\rangle$,
-where $T_{\cdot}$ denotes the heat semigroup, we proceed
-by examining the terms in the semimartingale
-decomposition~(\ref{eqn:eta_martingale})
-%of $\langle f, \rho_\epsilon*\eta_t^N(x)dx\rangle=
-%\langle \rho_\epsilon*f, \eta_t^N(dx)\rangle$.
-when the test function $f$ is replaced by $T_{\epsilon^2}f$.
+\langle \rho_\epsilon*f(x), \eta_t^N(dx)\rangle$,
+this will follow if we can show that each the terms in the semimartingale
+decomposition~(\ref{eqn:eta_martingale}),
+with the test function $f$ replaced by $\rho_\epsilon*f(\cdot)$,
+converges to the corresponding term in~\eqref{eqn:target PDE weak form}.
 
 The linear term is straightforward.
+Write $T_{\cdot}$ for the heat semigroup, so that
+$\rho_\epsilon*f(x) = T_{\epsilon^2}f(x)$.
 By a Taylor expansion, writing $\{T_t\}_{t\geq 0}$ for the heat semigroup,
@@
 \end{multline*}
-with a corresponding statement when $\rho_\epsilon*\eta_s^N(x)$ is replaced
+as well as a corresponding statement with $\rho_\epsilon*\eta_s^N(x)$ replaced
 by $\varphi(s,x)$ and then use weak convergence to see that, up to an error 

### 2023-04-27 forwards-and-backwards.tex
alison comments

@@
 $r(x,\eta)\gamma(x,\eta)-\mu_\theta(x)$ is of order $1/\theta$.
-Perhaps the simples example in which we can see this
+Perhaps the simplest example in which we can see this
 is the case where $\gamma \equiv 1$ and $F \equiv 0$, so that $\mu_\theta = r$,
@@
 to the expression that we'd get by setting $\meanq = -\wavespeed$
-and using Lemma~\ref{cor:stationary_dist},
+and using Corollary~\ref{cor:stationary_dist},
 i.e., by giving each offspring a mean displacement that offsets the motion of the wave.
@@
 let $\lambda(x)$ be a smooth, nonnegative function on $\IR^d$,
+\comment{TODO Should we worry that we used prime for differentiation before?}
 and let $r'(x, m) = \lambda(x) r(x, m)$ and $F'(x, m) = \lambda(x) F(x, m)$
@@
 
+\comment{TODO I think we need to make the notation for $r(y, \rho_r*\eta(y))$ 
+consistent with what we have (now) used elsewhere, namely $r(y,\eta)$?}
 Now suppose instead that
@@
 \end{proof}
+\comment{ALISON: Actually the last calculation gives a much better bound which we will
+need later. I'll sort this out tomorrow.}
 
@@
 $$
-% We therefore have
-% \begin{multline*}
-%         \left|
-%         \langle \rho_{\epsilon} * f, \eta_t^N \rangle
-%         -
-%         \langle \rho_{\epsilon} * f, \eta_s^N \rangle
-%         \right|
-%         \leq
-%         \| \Delta f \|_\infty |t-s|
-%         \sup_{0 \leq u \leq T } \langle 1, \eta_u^N \rangle
-% \\
-% +
-% 	\int_s^t
-% 	\big\langle \rho_\epsilon*|f|(x)\, \big|F\big(\rho_\epsilon*\eta_u^N(x)\big)\big|,
-% \eta_u^N(dx)\big\rangle du +2\sup_{0\leq u\leq T}|\widehat{M}^N(f)_u|.
-%     \end{multline*}
+
 By the Burkholder-Davis-Gundy inequality,
@@
 and, using the bound~(\ref{bound for negative tau}),
+\comment{ALISON: It's actually using the bound derived just below (7.4) which is 
+much stronger than stated there}
     \begin{align*}

### 2023-04-27 forwards-and-backwards.tex
.

@@
 let $\lambda(x)$ be a smooth, nonnegative function on $\IR^d$,
-\comment{TODO Should we worry that we used prime for differentiation before?}
-and let $r'(x, m) = \lambda(x) r(x, m)$ and $F'(x, m) = \lambda(x) F(x, m)$
-(and, let $\gamma' = \gamma$).
+and let $\widetilde{r}(x, m) = \lambda(x) r(x, m)$ and $\widetilde{F}(x, m) = \lambda(x) F(x, m)$
+(and, let $\widetilde{\gamma} = \gamma$).
 Since $\mu = r \gamma - F/\theta$,
 this corresponds to multiplying both establishment probabilities and death rates by $\lambda$.
-Then the population with parameters $\gamma'$, $r'$, and $F'$
+Then the population with parameters $\widetilde{\gamma}$, $\widetilde{r}$, and $\widetilde{F}$
 has the same stationary profile(s) as the original population.
@@
 
-\comment{TODO I think we need to make the notation for $r(y, \rho_r*\eta(y))$ 
-consistent with what we have (now) used elsewhere, namely $r(y,\eta)$?}
 Now suppose instead that
@@
                     -
-                    f(x) r\big(x, \smooth{r}\eta(x)\big)
+                    f(x) r\big(x,\smooth{r}\eta(x)\big)
                 \big\}
@@
                 \big\{
-                    f(y) r\big(y, \smooth{r}\eta(y)\big)
+                    f(y) r\big(y,\smooth{r}\eta(y)\big)
                     -
@@
 \end{align}
+(Note the extra term introduced here,
+$r(x,\smooth{r}\eta(y))$, has the two arguments to $r$
+``at different locations'', contrary to the usual pattern.)
 

### 2023-04-28 forwards-and-backwards.tex
alison edits

@@
 \[
-    C \left(1 + \frac{t}{\epsilon^2}\right)^{d/2} e^{-\chi \theta t - \epsilon^2 \theta / 2}
-    \frac{1}{(\epsilon^2 + t)^{d/2}} .
+	C \left(1 + \frac{t}{\epsilon^2}\right)^{d/2} e^{-\chi \theta t }%- \epsilon^2 \theta / 2}
+	\frac{1}{(\epsilon^2 + t)^{d/2}}e^{-\epsilon^2 \theta/2} .
 \]
 Now observe that the derivative (with respect to $t$) of 
-$e^{-\chi \theta t - \epsilon^2 \theta / 2} (1 + t/\epsilon^2)^{d/2}$ 
+	$e^{-\chi \theta t} % - \epsilon^2 \theta / 2} 
+	(1 + t/\epsilon^2)^{d/2}$ 
 is
@@
     \left( \frac{d}{2 \epsilon^2} - \left(1 + \frac{t}{\epsilon^2}\right) \chi \theta \right)
-    \left( 1 + \frac{t}{\epsilon^2} \right)^{d/2 - 1} e^{-\chi \theta t - \epsilon^2 \theta / 2} ,
+    \left( 1 + \frac{t}{\epsilon^2} \right)^{d/2 - 1} e^{-\chi \theta t },%- \epsilon^2 \theta / 2} ,
 \]
 which is negative if $\theta(\epsilon^2 + t) > d/2 \chi$.
-At the maximum, $(\epsilon^2 + t) = d / (2\chi \theta)$,
-so $(1 + t/\epsilon^2) = d /(2\chi \theta \epsilon^2)$,
+At the maximum, %$(1+\epsilon^2/t) = d / (2\chi \epsilon^2\theta)$, so
+$(1 + t/\epsilon^2) = d /(2\chi \theta \epsilon^2)$,
 and so this quantity is bounded uniformly over not only $t$ but also $\epsilon$
 (since we've assumed that $\theta \epsilon^2$ is bounded below).
-Therefore, the second term in \eqref{eqn:psi_infty_bound} 
-is bounded by $C / (\epsilon^2 + t)^{d/2}$
-(for a different constant $C$).
+Therefore, 
+we have the bound
+\begin{equation}
+	\label{small tau bound}
+	\frac{1}{\epsilon^d}
+        \IP\left\{
+            \tau(t) < - (\epsilon^2 + t) / 2
+        \right\}
+\leq \frac{C}{(\epsilon^2 + t)^{d/2}} e^{-\epsilon^2\theta/2}.
+\end{equation}
+%(for a different constant $C$).
 Substituting this into \eqref{eqn:psi_infty_bound} yields the result.
 \end{proof}
-\comment{ALISON: Actually the last calculation gives a much better bound which we will
-need later. I'll sort this out tomorrow.}
 
@@
     %and with $A$ as in Lemma~\ref{lem:poisson_ld},
-    \begin{multline}
+	\begin{equation}
 \label{heat kernel estimate}
@@
         \right|
-        \\
+        %\\
 \le
-        \frac{C}{(\epsilon^2 \theta)^{d/2}}
+        \frac{C}{(\epsilon^2 \theta)^{1/2}}
         p_{6(\epsilon^2+t)}(x, y)
         +
-	    C \left(1+
-	    \frac{1}{(\epsilon^2 + t)^{d/2}}\right)
+	    \frac{C}{(\epsilon^2 + t)^{d/2}}
 	    \exp(- \epsilon^2 \theta / 2)
@@
 	    .
-    \end{multline}
+	\end{equation}
 \end{lemma}
@@
 and, using the bound~(\ref{bound for negative tau}),
-\comment{ALISON: It's actually using the bound derived just below (7.4) which is 
-much stronger than stated there}
     \begin{align*}
@@
         \\ & \le
-        C \exp\left(-\frac{\theta \epsilon^2}{2} \right) .
+	    \frac{C}{(\epsilon^2+t)^{d/2}} \exp\left(-\frac{\theta \epsilon^2}{2} \right) .
     \end{align*}
@@
     $\epsilon^2 + t + \tau(t)$ is between
-    $(\epsilon^2 + t)/ 2$ and $3(\epsilon^2 + t))$,
+    $(\epsilon^2 + t)/ 2$ and $3(\epsilon^2 + t)$,
     and for any $s$ in this interval,
@@
 \widehat{\epsilon}(\delta,\epsilon,\theta):=
-e^{-\epsilon^2\theta/2}\left(1+\frac{1}{(\epsilon^2+\delta)^{d/2}}\right),
+\frac{1}{(\epsilon^2+\delta)^{d/2}}
+e^{-\epsilon^2\theta/2}, %\left(1+\frac{1}{(\epsilon^2+\delta)^{d/2}}\right),
 %\frac{1}{(A+1)^{\epsilon^2\theta}}e^{-\epsilon^2\theta},
@@
     \\ &\qquad \qquad {}
-	+ \frac{C}{(\theta\epsilon^2)^{d/2}}\big\langle 
-p_{6(\epsilon^2+s)}(y,z)+p_{6(\epsilon^2+s)}(w,z), \eta_0(dz)
-\big\rangle
-	+\widehat{\epsilon}(\delta,\epsilon,\theta)\langle 1,\eta_0(dz)\rangle
+	+ \big\langle\frac{C}{(\theta\epsilon^2)^{1/2}} \Big(%\big\langle 
+	p_{6(\epsilon^2+s)}(y,z)+p_{6(\epsilon^2+s)}(w,z)\Big) %, \eta_0(dz)
+%\big\rangle
+	+\widehat{\epsilon}(\delta,\epsilon,\theta) %\langle 1
+	,\eta_0(dz)\rangle
 	\nonumber
+    \\ &\qquad \qquad {}
+    +
+\int_0^{s-\delta}
+\big\langle \Big\{
+\frac{C}{(\epsilon^2\theta)^{1/2}}
+|p_{6(s-r+\epsilon^2)}(y,z)+
+p_{6(s-r+\epsilon^2)}(w,z)| +\widehat{\epsilon}(\delta,\epsilon,\theta)\Big\}
+\cdot |F(\rho_\epsilon*\eta_r(z)|, 
+\eta_r(dz) \big\rangle  dr
+\nonumber
+    %\frac{C}{(\epsilon^2\theta)^{1/2}}
+%\int_0^{s-\delta}
+%\big\langle |p_{6(s-r+\epsilon^2)}(y,z)+
+%p_{6(s-r+\epsilon^2)}(w,z)|
+%\cdot |F(\rho_\epsilon*\eta_r(z)|, 
+%\eta_r(dz) \big\rangle  dr
+%\nonumber
     \\ &\qquad \qquad {}
@@
 |\psi_{s-r}^{\epsilon,y}(z) + \psi_{s-r}^{\epsilon, w}(z) |
-\cdot |F(\rho_\epsilon*\eta_r(z)|, 
-\eta_r(dz) \big\rangle  dr
-\nonumber
-    \\ &\qquad \qquad {}
-    +
-\frac{C}{(\epsilon^2\theta)^{d/2}}
-\int_0^{s-\delta}
-\big\langle |p_{6(s-r+\epsilon^2)}(y,z)+
-p_{6(s-r+\epsilon^2)}(w,z)|
 \cdot |F(\rho_\epsilon*\eta_r(z)|, 
@@
 \\ & \qquad \qquad  {}
-	+ \big\langle \frac{C}{(\theta\epsilon^2)^{d/2}}\Big( 
+	+ \big\langle \frac{C}{(\theta\epsilon^2)^{1/2}}\Big( 
 	p_{6(\epsilon^2+s)}(y,z)+p_{6(\epsilon^2+s)}(w,z)\Big)+
@@
 \big\langle \Big\{
-\frac{C}{(\epsilon^2\theta)^{d/2}}
+\frac{C}{(\epsilon^2\theta)^{1/2}}
 |p_{6(s-r+\epsilon^2)}(y,z)+
 p_{6(s-r+\epsilon^2)}(w,z)| +\widehat{\epsilon}(\delta,\epsilon,\theta)\Big\}
+\cdot |F(\rho_\epsilon*\eta_r(z)|, 
+\eta_r(dz) \big\rangle  dr
+\nonumber
+    \\ &\qquad \qquad {}
++ \int_{s-\delta}^s \big\langle 
+|\psi_{s-r}^{\epsilon,y}(z) + \psi_{s-r}^{\epsilon, w}(z) |
 \cdot |F(\rho_\epsilon*\eta_r(z)|, 
@@
 \end{align} 
-\comment{MISSING A TERM? the $\int_{s-\delta}^s$ one; and say it's bounded because of the moment bounds}
 Although this expression is lengthy, we have successfully isolated the
@@
 don't expect the martingale terms to contribute, since their 
-quadratic variation scales with $\theta/(N\epsilon^d)$, and
+quadratic variation scales with $\theta/(N\epsilon^d)$; % and
 under the assumption that $\epsilon^2\theta\to\infty$,
-for any fixed $\delta>0$, if $s > \delta$ the terms arising from 
+for any fixed $\delta>0$, %if $s > \delta$ 
+the terms arising from 
 approximating the transition 
-density of the Gaussian 
-walk by the heat kernel at a fixed time, will tend to zero. 
+density $\psi_{s-r}^{\epsilon, \cdot}(\cdot)$ of the Gaussian 
+walk by $p_{s-r+\epsilon^2}(\cdot,\cdot)$ at times 
+with $s-r>\delta$ will tend to zero; and  
+the moment bounds of Lemma~\ref{bounds on moments} 
+will allow us to control the integral over $[s-\delta, s]$.
 There is some technical work to be done to rigorously identify the
@@
 Since $\psi_{t-s}^{\epsilon,x}(y)=p_{T(t-s)+\epsilon^2}(x,y)$, 
-rearranging~(\ref{})
+rearranging~(\ref{expn rhoepsilon})
 we see that we can pull a convolution with $p_{\epsilon^2/2}$ out of
@@
 that we used to control terms above with still be valid.
-To deal with the two terms in the produce involving $|M_s(y)|$, we write 
+To deal with the two terms in the product involving $|M_s(y)|$, we write 
 the first as $\int |M_s(y)|\rho_\epsilon*\eta_s(y)^{k+1}dy$ and then use

### 2023-04-28 forwards-and-backwards.tex
peter edits to 7.1 and alison comments to 8

@@
 In this section we prove Theorem~\ref{thm:local_convergence},
-which simultaneously scales the parameters $\theta$ and $N$ and the interaction 
-kernel $\rho_F$ in the special case in which $r\equiv 1\equiv\gamma$, $q_{\theta}(x,dy)$
+which proves convergence in the case that the width of the interaction kernel $\rho_F$
+simultaneously scales along with the parameters $\theta$ and $N$,
+in the special case in which $r\equiv 1\equiv\gamma$, $q_{\theta}(x,dy)$
 is isotropic with zero mean, the kernel
@@
 We note that $\mathcal{L}^\theta$ is the generator of a continuous (time and 
-space) random walk, which makes jumps of mean $0$ and variance $1/\theta$ at
-rate $\theta$.
-
+space) random walk, which makes jumps of mean $0$ and variance $1/\theta$ at rate $\theta$.
 In what follows we write $\psi_t^{\epsilon, x}(y)$ for the solution of
@@
     +
-    M_t(\phi_\cdot(\cdot))
+    M_t(\phi)
     +
@@
 \end{multline}
-where $M_t(\phi_\cdot(\cdot))$ is a martingale (with respect to the natural filtration)
+where $M_t(\phi)$ is a martingale (with respect to the natural filtration)
 with quadratic variation given by~\eqref{eqn:prelimit_martingale_variation}
@@
 $\langle\psi^{\epsilon,x}_{t-s}, \eta_s\rangle$ 
-we obtain~(\ref{moment bound rhoepsilon})
-(without the second term on the right hand side) in the case $k=1$.
+we obtain 
+$\IE[\langle \psi_0^{\epsilon,x},\eta_t\rangle] \le C \IE[\langle \psi_t^{\epsilon,x},\eta_0\rangle]$,
+which implies~(\ref{moment bound rhoepsilon}) in the case $k=1$.
 Moreover, rearranging~(\ref{expn rhoepsilon}) we find 
@@
 this yields 
-$$\IE\Big[-\int_0^t\langle\psi^{\epsilon,x}_{t-s}(y)F(\rho_\epsilon*\eta_s(y), 
+$$\IE\Big[-\int_0^t\langle\psi^{\epsilon,x}_{t-s}(y)F(\rho_\epsilon*\eta_s(y)), 
 \eta_s(dy)\rangle ds\Big|{\cal F}_0\Big]
-\leq \widehat{C}\langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle.$$
+\leq \langle\psi^{\epsilon, x}_t(y),\eta_0(dy)\rangle.$$
 Since $F$ is bounded above, there exists a constant $K$ such that $|F|\leq K-F$ and so 
@@
 $$\IE\Big[\int_0^t\big\langle\psi^{\epsilon,x}_{t-s}(y)
-|F(\rho_\epsilon*\eta_s(y)|, 
+|F(\rho_\epsilon*\eta_s(y))|, 
 \eta_s(dy)\big\rangle ds\Big|{\cal F}_0\Big]\leq 
@@
 individual, and so increments $\langle f,\eta\rangle$ by $\pm f/N$ at the location of
-that individual, we find 
+that individual and that $r \equiv \gamma \equiv 1$, we find 
 \begin{multline}
@@
 \Big\langle
-\int\theta N\Big\{k\frac{f(y)}{N}\langle f,\eta\rangle^{k-1}+
-\binom{k}{2}\frac{f(y)^2}{N^2}\langle f,\eta\rangle^{k-2}+\cdots
-+\frac{f(y)^{k}}{N^{k}}\Big\}q_\theta(x,dy),\eta(dx)\Big\rangle
+\int\theta N
+    % \Big\{k\frac{f(y)}{N}\langle f,\eta\rangle^{k-1}+ \binom{k}{2}\frac{f(y)^2}{N^2}\langle f,\eta\rangle^{k-2}+\cdots +\frac{f(y)^{k}}{N^{k}}\Big\}
+    \sum_{j=1}^k \binom{k}{j} \frac{f(y)^j}{N^j} \langle f, \eta\rangle^{k-j}
+    q_\theta(x,dy),\eta(dx)\Big\rangle
 \\
@@
     \Big\langle\theta N\Big(1-\frac{F(\rho_\epsilon*\eta(x))}{\theta}\Big)
-\Big\{-k\frac{f(x)}{N}\langle f,\eta\rangle^{k-1}+
-\binom{k}{2}\frac{f(x)^2}{N^2}\langle f,\eta\rangle^{k-2}+\cdots
-+\frac{(-1)^{k}f(x)^{k}}{N^{k}}\Big\},\eta(dx)\Big\rangle.
+    % \Big\{-k\frac{f(x)}{N}\langle f,\eta\rangle^{k-1}+ \binom{k}{2}\frac{f(x)^2}{N^2}\langle f,\eta\rangle^{k-2}+\cdots +\frac{(-1)^{k}f(x)^{k}}{N^{k}}\Big\}
+    \sum_{j=1}^k \binom{k}{j} (-1)^j \frac{f(x)^j}{N^j} \langle f, \eta\rangle^{k-j}
+    ,\eta(dx)\Big\rangle.
 \end{multline}
@@
 \end{multline}
-Using (from Lemma~\ref{PsiBoundHS}) 
+Since $\dot \psi^{\epsilon,x}_s = \mathcal{L}_\theta \psi^{\epsilon,x}_s$,
+the $j=1$ terms from $\Pgen^N(\langle \psi^{\epsilon,x}_{t-s}(y),\eta_s(dy) \rangle^k)$
+combines with the last term in~\eqref{kth moment for time varying function}
+to obtain 
+$$ \int_0^t k \langle \psi^{\epsilon,x}_{t-s},\eta\rangle^{k-1} \langle F(\rho_\epsilon*\eta_s(y)) \psi^{\epsilon,x}_{t-s}(y), \eta_s(dy) \rangle ds . $$
+As for the remaining terms, using (from Lemma~\ref{PsiBoundHS}) 
 that $\sup_s\|\psi^{\epsilon,x}_s(\cdot)\|_\infty=C/\epsilon^d$,
@@
 +
-\int_0^t\theta N\sum_{j=2}^{k}\binom{k}{j}\frac{\psi_{t-s}^{\epsilon,x}(y)^j}{N^j}\langle \psi^{\epsilon,x}_{t-s},\eta_s\rangle^{k-j}
+\Big\langle \int_0^t\theta N\sum_{j=2}^{k}\binom{k}{j}\frac{\psi_{t-s}^{\epsilon,x}(y)^j}{N^j}\langle \psi^{\epsilon,x}_{t-s},\eta_s\rangle^{k-j}
 (-1)^j\Big(1-\frac{F(\rho_\epsilon*\eta_s(y))}{\theta} 
@@
 \begin{align*}
-&\IE\Big[\int p_{\epsilon^2/2}*\eta_t(y_1)\, p_{\epsilon^2/2}*\eta_t(y_2)\,
-p_{\epsilon^2/4}*\eta_y\big(\frac{y_1+y_2}{2}\big)\, 
+&\IE\Big[\int \int p_{\epsilon^2/2}*\eta_t(y_1)\, p_{\epsilon^2/2}*\eta_t(y_2)\,
+p_{\epsilon^2/4}*\eta_t\big(\frac{y_1+y_2}{2}\big)\, 
 p_{\epsilon^2}(y_1,y_2)dy_1dy_2\Big]
@@
 &\leq 
-\IE\Big[\int\Big\{
+\IE\Big[\int \int\Big\{
 \big(p_{\epsilon^2/2}*\eta_t(y_1)\big)^3+ \big(p_{\epsilon^2/2}*\eta_t(y_2)\big)^3+
@@
 \[
-\prod_{j=1}^k p_{\tau}(x,x_j)
-=\prod_{j=2}^{k}p_{\frac{j\tau}{j-1}}\big(x_j,X_{j-1}\big)
-p_{\frac{\tau}{k}}(x, X_k)
+\prod_{j=1}^k p_{\tau}(y,y_j)
+=\prod_{j=2}^{k}p_{\frac{j\tau}{j-1}}\big(y_j,Y_{j-1}\big)
+p_{\frac{\tau}{k}}(y, Y_k)
 \]
@@
 \[
-X_1=x_1, \qquad X_j=\frac{j-1}{j}x_j+\frac{1}{j}X_{j-1}, \mbox{for }j\geq 2.
+    Y_1=y_1, \qquad Y_j=\frac{j-1}{j}Y_{j-1}+\frac{1}{j}y_j,  \mbox{for }j\geq 2.
 \]
-This yields
+Writing $p_{\epsilon^2}(x,z_j) = \int p_{\epsilon^2/2}(x,y_j) p_{\epsilon^2/2}(y_j,z_j) dy_j$
+and using the above with $\tau = \epsilon^2/2$,
+this yields
 \begin{multline*}
 \big\langle\big(\rho_\epsilon*\eta_t(x)\big)^k,\eta_t(dx)\big\rangle
-=\int\cdots\int\prod_{i=2}^kp_{\epsilon^2 i/(i-1)}(y_,X_i)
-\prod_{i=1}^kp_{\epsilon^2/2}*\eta_t(y_i)p_{\epsilon^2/k}*\eta_t(X_k)
+    =\int\cdots\int \prod_{j=2}^k p_{\epsilon^2 j/2(j-1)}(y_j,Y_{j-1})
+     \prod_{i=1}^k p_{\epsilon^2/2}*\eta_t(y_i)p_{\epsilon^2/2k}*\eta_t(Y_k)
 dy_1\ldots dy_k
@@
 \int\cdots\int 
-\prod_{i=2}^kp_{\epsilon^2 i/(i-1)}(y_i,X_i)
+    \prod_{j=2}^k p_{\epsilon^2 j/2(j-1)}(y_j,Y_{j-1})
     \Big\{\sum_{i=1}^k\big(p_{\epsilon^2/2}*\eta_t(y_i)\big)^{k+1}
-+\big(p_{\epsilon^2/k}*\eta_t(X_k)\big)^{k+1}\Big\}dy_1\ldots dy_k,
+    + \big(p_{\epsilon^2/2k}*\eta_t(Y_k)\big)^{k+1}\Big\}dy_1\ldots dy_k,
 \end{multline*}
@@
 As in the nonlocal case, it suffices to prove that for $T>0$,
-and any $f\in C_b^\infty (\IR^d)$ with bounded second derivatives, the
-sequence of real-valued processes 
+and any $f\in C_b^\infty (\IR^d)$ with bounded second derivatives
+and $\int|f(x)|dx < \infty$, the sequence of real-valued processes 
 $\big\{\big(\int f(x)\rho_\epsilon*\eta_t^N(x)dx\big)_{t\geq 0}\big\}_{N\geq 1}$ is tight.  
@@
 \[
-w'\big(X^N,\delta,T\big)= \inf_{\{t_i\}}\max_i\sup_{s,t\in [t_{i-1},t_i)}
+w'\big(X_f^N,\delta,T\big)= \inf_{\{t_i\}}\max_i\sup_{s,t\in [t_{i-1},t_i)}
 \big| X_f^N(t)-X_f^N(s)\big|,
@@
 it suffices to check compact containment of 
-the sequence $\{\rho_\epsilon*\eta_t^N(x)dx\}_{N\geq 1}$ at any rational time $t$ and
+    the sequence $\{\int f(x) \rho_\epsilon*\eta_t^N(x)dx\}_{N\geq 1}$ at any rational time $t$ and
 that for every $\nu>0$ and $T>0$, there exists $\delta>0$ such that
@@
 \end{multline}
-where $\widehat{M}^N(f)$ is the martingale of~(\ref{eqn:eta_martingale})
+where $\widehat{M}^N(f)$ is the martingale of~(\ref{eqn:eta_f_mgale_decomp})
 with the test function $f$ replaced by $\rho_\epsilon*f$. 
@@
 
-By the Burkholder-Davis-Gundy inequality,
-$\IE[\sup_{0 \le u \le T} |\widehat{M}^N(f)_u|^2] \le C \IE[[\widehat{M}^N(f)]_u]$,
-and so using
-and Markov's inequality and
-our moment bounds,
+Consulting~\eqref{eqn:prelimit_martingale_variation},
+the quadratic variation of $\widehat{M}^N(f)$ satisfies
+$ \IE[[\widehat{M}^N_f]_T] \le C (\theta/N) \int_0^T \langle 1, \eta_s \rangle ds \le C' \theta/N$
+for some constants $C$ and $C'$.
+Now, by the Burkholder-Davis-Gundy inequality,
+$\IE[\sup_{0 \le u \le T} |\widehat{M}^N(f)_u|^2] \le C'' \IE[[\widehat{M}^N(f)]_u]$,
+and so using Markov's inequality,
 \begin{equation}
@@
     \leq
-    \limsup_{N\to\infty} \frac{36}{\nu^2} \IE\big[[\widehat{M}^N(f)]_T\big]
+    \limsup_{N\to\infty} \frac{36}{\nu^2} C'' \IE\big[[\widehat{M}^N(f)]_T\big]
     \leq
-    \limsup_{N\to\infty}\frac{36}{\nu^2}\frac{C\theta}{N\epsilon^d} 
+    \limsup_{N\to\infty}\frac{36}{\nu^2}\frac{C' C''\theta}{N\epsilon^d} 
     =0. 
 \end{equation}
+
 Now consider
@@
 Now observe that, again using Lemma~\ref{bounds on moments}, 
-since $a^j b^k \le a^{j+k} b^{j+k}$,
+since for nonnegative $a$ and $b$, $a^j b^k \le a^{j+k} + b^{j+k}$,
 \begin{multline*}
@@
 Thus the quantity~(\ref{square of F-integral}) 
-is bounded by $C(t-s)^2$ for some constant $C$ which we can 
+is bounded by $C(t-s)^2$ for a new constant $C$ which we can 
 take to be independent of $s$, $t$ and $\epsilon$. Markov's inequality 
@@
 Now we turn to results about the lookdown process,
-first establishing the basic connection between the processes, Proposition~\ref{thm:mmt_application},
+first establishing the basic connection between the processes, 
+\comment{which processes?}
+Proposition~\ref{thm:mmt_application},
 and then in the next section, convergence of the lookdown process itself.
@@
     for all $f$ in the domain of $A^N$ (and similarly a function $\psi$ for $A$).
+	\comment{technically need $\psi\geq 1$, so usually just add $1$ to 
+	whatever you think $\psi$ should be.} 
     We also need that applying the lookdown generator to a function and averaging over levels
@@
     and so taking for example the most troublesome term in $Af(\lp)$,
+	\comment{should we rephrase to say that the most troublesome term is...
+	(because the other one is as above)?}
     we see that since $0 \le f(\lp) / g(x, u) \le 1$ for any $(x, u) \in \lp$,
@@
     and take $\psi(\lp) = \langle F(x, \eta) u e^{-u}, \lp(dx, du) \rangle$.
+	\comment{again add one - and inside the integral to deal with
+	the non-troublesome term}
     % Furthermore, since $F(x, \eta)$ only depends on spatial location, not level,
@@
 Theorem~\ref{thm:lookdown_convergence}, whose proof
-follows a similar pattern to those of convergence for the population processes
+follows a similar pattern to those \comment{`that'?} of convergence for the population processes
 in Section~\ref{sec:population_density_proof}.
@@
 of Section~\ref{sec: individual lines of descent} holds.
+	\comment{Is this paragraph really a separate remark that we want to make?}
 
@@
     the theorem will follow from tightness and characterization of the limit.
+	\comment{characterisation of limit points (given that we have
+	no uniqueness of the limit)?}
     This time, the processes $\lp^N$ take values in $\lpmeasures$,
@@
     below, Lemma~\ref{lem:compact containment lookdown} proves exactly this, and therefore compact containment.
+	\comment{Do we have a reference for this claim about completely
+	metrizable and these sets being enough to 
+	establish relative compactness? The reader may reasonably
+	ask why we had to add a point at infinity to $\IR^d$ and not one
+	to $[0,\infty)$. Also, maybe spell out that the support of $f_k$ is compact in
+	the product space of $\overline{\IR^d}$ times levels?}
 
@@
     do not form not a dense subset of $\bar C(\lpmeasures)$,
-    but they do separate points and vanish nowhere, so
+    but they do separate points and vanish nowhere, 
+	\comment{I don't understand vanish nowhere - I think it may because
+	of the way I am reading the sentence, but it is perfectly possible
+	for $\langle f,\xi\rangle$ to be zero.}
+	so
     by the Stone-Weierstrass theorem, the algebra they generate is dense
@@
     are all finite,
+	\comment{Should be a fullstop.}
     Suppose that Assumptions~\ref{def:model_setup} hold,
@@
 
-We postpone the proof of this Lemma until we have shown how it yields to compact containment.
-First, we show that this implies compact containment for arbitrary
+We postpone the proof of this Lemma until we have shown how it yields 
+\comment{delete `to'} to compact containment.
+First, we show that this implies compact containment
+\comment{compact containment of what?} for arbitrary
 compactly supported functions.
@@
     $f(x, u) = 0$ for all $x$ and $u \ge u_f$.
+	\comment{sounds like $f$ vanishes for all $x$ irrespective of $u$!
+	Can we reword? `all $(x,u)$ with $u\geq u_f$' or something?}
     Under the assumptions of Lemma~\ref{lem:h_containment},
@@
 a set which is compact if we choose $\{f_k\}$ appropriately.
+\comment{Does the reader know how to act `appropriately' in 
+making this choice? Maybe refer back to the right bit above where it 
+is explained.}
 % \comment{
@@
     Now, since $\lp_t^N$ is conditionally uniform given $\eta_t^N$,
-    we know that for appropriate $f$,
+    we know that for appropriate $f$, \comment{A bit vague... can we be 
+    more specific about what makes a function appropriate?}
     $  \IE[\langle f, \lp^N_t \rangle] = \IE[\langle \widetilde{f}, \eta^N_t \rangle] , $
@@
 
-    Again since $\sqrt{x} \le 1 + x$ for $x \ge 0$,
+    Again \comment{Only a very alert reader will remember why we say `again'
+    here...} since $\sqrt{x} \le 1 + x$ for $x \ge 0$,
     the Burkholder-Davis-Gundy inequality
@@
     Then, the sequence of real-valued processes $(\langle f, \lp_t^N \rangle)_{t \ge 0}$
-    are tight in the space of c\`adl\`ag processes.
+	are \comment{`is' - the subject of the sentence is the (single) sequence}
+	tight in the space of \comment{real-valued? or ${\cal D}_\IR$-valued} 
+	c\`adl\`ag processes.
 \end{lemma}
@@
     \end{align*}
+	\comment{limits of integration missing in last integral}
     The bounds analogous to \eqref{eqn:eta_projections_goal1} and \eqref{eqn:eta_projections_goal2}
@@
 at location $x$ and time $t$ (which may only exist almost everywhere).
+	\comment{Is it obvious that it exists almost everywhere? 
+	We just need to be able to integrate against it I guess.}
 We first proceed informally, as if the density exists everywhere,
@@
 % (This is $\mathcal{L}^Y_s g(x) = \gamma ( \DG(rg)(x) - g \DG r(x) )$ in shorter but more cryptic notation.)
-The diffusion is time-inhomogeneous if the density is not constant with time.
-Let $\varphi_t(x)$ be the limiting density, which solves \eqref{general deterministic limit},
+The diffusion is time-inhomogeneous if the density is not constant with
+	\comment{this may be an example of being divided by a common
+	language, but I would say `in time'} time.
+Let $\varphi_t(x)$ be the limiting density, which 
+	\comment{is a weak solution to?} 
+	solves \eqref{general deterministic limit},
 $\partial_t \varphi = r \DG^*[ \varphi_t \gamma ] + \varphi F$.
@@
 $$
-Differentiating with respect to $t$ at $t=s$, and writing 
+Differentiating with respect to $t$ at $t=s$,
+\comment{This is a bit confusing. I think it is partly because it says generator
+of $\widehat{T}_{t,s}$ and of course $t$ disappears. But also it is 
+because we are 
+looking for the generator of the ancestral lineage and so it 
+feels like one wants to 
+differentiate with respect to `-s' if you see what I mean.}
+and writing 
 $\Lgen_s$ for the generator of $\hat{T}_{t,s}$ at time $s$, we find
@@
 First, note that in this case
+	\comment{Should really define our notation - ${\cal L}_s$ is
+	independent of time, so...}
 $$
@@
 specialized slightly to the case that the processes 
-are c\'adl\'ag and have no fixed points of discontinuity.
+are c\`adl\`ag and have no fixed points of discontinuity.
 For an $S_0$-valued, measurable process $Y$, $\hat{\mathcal{F}}^Y_t$

### 2023-05-01 forwards-and-backwards.tex
edits and bib fixes

@@
 Specialising the results of 
-\citet{KURTZ1999103} to the deterministic setting
+\citet{kurtz/xiong:1999} to the deterministic setting
 provides general conditions under which we
@@
 Now we turn to results about the lookdown process,
-first establishing the basic connection between the processes, 
-\comment{which processes?}
+first establishing the basic connection between the population process $\eta^N$
+and the lookdown process $\lp^N$,
 Proposition~\ref{thm:mmt_application},
@@
     or as a Poisson process with Lesbegue intensity (in the limiting case).
-    We need a continuous $\psi^N(\lp)$ such that $|A^N f(\lp)| \le c_f \psi^N(\lp)$
+    We need a continuous $\psi^N(\lp) \ge 1$ such that $|A^N f(\lp)| \le c_f \psi^N(\lp)$
     for all $f$ in the domain of $A^N$ (and similarly a function $\psi$ for $A$).
-	\comment{technically need $\psi\geq 1$, so usually just add $1$ to 
-	whatever you think $\psi$ should be.} 
     We also need that applying the lookdown generator to a function and averaging over levels
@@
     with $g(x, u) = 1$ for $u \ge u_0$,
-    and so taking for example the most troublesome term in $Af(\lp)$,
-	\comment{should we rephrase to say that the most troublesome term is...
-	(because the other one is as above)?}
-    we see that since $0 \le f(\lp) / g(x, u) \le 1$ for any $(x, u) \in \lp$,
+    and consulting~\eqref{eqn:limiting_lookdown_generator},
+    we see that most terms in $Af(\lp)$ can be bounded 
+    as above by constant multiples of $\langle 1, \eta \rangle$.
+    However, the term involving $F$ is, as usual, more troublesome.
+    Since $0 \le f(\lp) / g(x, u) \le 1$ for any $(x, u) \in \lp$,
     \begin{align*} % \label{eqn:part_of_psi}
@@
     we absorb $\| \partial_u g \|_\infty e^{u_0}$ into $c_f$
-    and take $\psi(\lp) = \langle F(x, \eta) u e^{-u}, \lp(dx, du) \rangle$.
-	\comment{again add one - and inside the integral to deal with
-	the non-troublesome term}
+    and take $\psi(\lp) = 1 + \langle 1 + F(x, \eta) u e^{-u}, \lp(dx, du) \rangle$.
     % Furthermore, since $F(x, \eta)$ only depends on spatial location, not level,
@@
 Theorem~\ref{thm:lookdown_convergence}, whose proof
-follows a similar pattern to those \comment{`that'?} of convergence for the population processes
+follows a similar pattern to that of convergence for the population processes
 in Section~\ref{sec:population_density_proof}.
@@
 	\comment{Is this paragraph really a separate remark that we want to make?}
+    \comment{PETER: maybe? Figuring out how to make it more concrete/rigorous seems daunting, though -
+        I'm inclined to remove it.}
 
@@
     As in Section~\ref{sec:population_density_proof},
-    the theorem will follow from tightness and characterization of the limit.
-	\comment{characterisation of limit points (given that we have
-	no uniqueness of the limit)?}
+    the theorem will follow from tightness and characterization of the limit points.
     This time, the processes $\lp^N$ take values in $\lpmeasures$,
@@
     of the form $g(x) h(u)$, where $g \in C_b(\overline{\IR^d})$ is bounded and continuous
-    and $h \in C_c([0, \infty))$ is compactly supported.
-    This space is completely metrizable,
-    and we may choose a countable set of nonnegative, compactly supported $f_k$
-    such that a subset $K \subset \lpmeasures$ is relatively compact if and only if
-    $\sup_{\lp \in K} \langle f_k, \lp \rangle < \infty$ for each $k$;
-    below, Lemma~\ref{lem:compact containment lookdown} proves exactly this, and therefore compact containment.
-	\comment{Do we have a reference for this claim about completely
-	metrizable and these sets being enough to 
-	establish relative compactness? The reader may reasonably
-	ask why we had to add a point at infinity to $\IR^d$ and not one
-	to $[0,\infty)$. Also, maybe spell out that the support of $f_k$ is compact in
-	the product space of $\overline{\IR^d}$ times levels?}
-
-    We require that $\{(F(\lp^N_t))_{t \ge 0}\}_N$
-    is tight as a sequence of real-valued c\`adl\`ag processes, for all $F$ in a subset
-    of $\bar C(\lpmeasures)$, the bounded, continuous functions on $\lpmeasures$,
-    that is dense with respect to uniform convergence on compact subsets.
-    Lemma~\ref{lem:test_fn_tightness} shows that $\{\langle f, \lp^N_t \rangle\}_N$ is a tight sequence
-    for any $f: \overline{\IR^d} \times [0,\infty) \to \IR$ with compact support
-    in the level direction.
+    and $h \in C_c([0, \infty))$ is compactly supported
+    (following, e.g., \citet{etheridge/kurtz:2019}, Condition 2.1).
+    % PLR: NEW DETAILS
+    Several places below we require a dense subset
+    of $\bar C(\lpmeasures)$, the bounded, continuous functions on $\lpmeasures$.
     The functions $\lp \mapsto \langle f, \lp \rangle$
@@
     but they do separate points and vanish nowhere, 
-	\comment{I don't understand vanish nowhere - I think it may because
-	of the way I am reading the sentence, but it is perfectly possible
-	for $\langle f,\xi\rangle$ to be zero.}
-	so
+    i.e., for any $\lp_1$ and $\lp_2$ there is an $f$
+    with $\langle f, \lp_1\rangle \neq \langle f, \lp_2\rangle$,
+    and a $g$ such that $\langle g, \lp_1\rangle \neq 0$.
+	Therefore,
     by the Stone-Weierstrass theorem, the algebra they generate is dense
@@
     in $\bar C(\lpmeasures)$ (with respect to uniform convergence on compact subsets).
-    So, it suffices to show that tightness for the processes $\langle f, \lp^N_t\rangle$
+    % END NEW DETAILS
+    Topologized in this way, the space $\lpmeasures$ completely metrizable,
+    and we may choose a countable set of nonnegative $f_k$,
+    each supported on $\IR^d \times [0,u_k]$ for some $u_k < \infty$,
+    such that a subset $K \subset \lpmeasures$ is relatively compact if and only if
+    $\sup_{\lp \in K} \langle f_k, \lp \rangle < \infty$ for each $k$.
+    (To see this, use Theorem A.2.3 of~\citet{kallenberg1997foundations}
+    and the first argument made in the proof of Lemma~\ref{lem:product_tightness}.)
+    Below, Lemma~\ref{lem:compact containment lookdown} proves exactly this,
+    and therefore compact containment.
+    Here we have compactified $\IR^d$ for convenience
+    (since it turned out to be straightforward to show that mass does not escape to infinity in space);
+    however, we need to use the vague topology ``in the level direction''
+    because \emph{levels} may escape to infinity in finite time in the limit.
+
+    For \citet{ethier/kurtz:1986} Theorem~3.9.1
+    we require that $\{(F(\lp^N_t))_{t \ge 0}\}_N$
+    is tight as a sequence of real-valued c\`adl\`ag processes, for all $F$ in a subset
+    of $\bar C(\lpmeasures)$ %, the bounded, continuous functions on $\lpmeasures$,
+    that is dense with respect to uniform convergence on compact subsets.
+    Lemma~\ref{lem:test_fn_tightness} shows that $\{\langle f, \lp^N_t \rangle\}_N$ is a tight sequence
+    for any $f: \overline{\IR^d} \times [0,\infty) \to \IR$ with compact support
+    in the level direction.
+    % The functions $\lp \mapsto \langle f, \lp \rangle$
+    % do not form not a dense subset of $\bar C(\lpmeasures)$,
+    % but they do separate points and vanish nowhere, 
+    % i.e., for any $\lp_1$ and $\lp_2$ there is an $f$
+    % with $\langle f, \lp_1\rangle \neq \langle f, \lp_2\rangle$,
+    % and a $g$ such that $\langle g, \lp_1\rangle \neq 0$.
+	% Therefore,
+    % by the Stone-Weierstrass theorem, the algebra they generate is dense
+    % % in $C_0(\lpmeasures)$, the continuous functions that vanish at infinity
+    % % (i.e., are less than $\epsilon$ outside of a compact set, for any $\epsilon$).
+    % % Since $C_0(\lpmeasures)$ is dense
+    % in $\bar C(\lpmeasures)$ (with respect to uniform convergence on compact subsets).  So, 
+    Since as above the algebra generated by these are dense in $\bar C(\lpmeasures)$,
+    it suffices to show that tightness for the processes $\langle f, \lp^N_t\rangle$
     extends to finite sums and products of these processes,
@@
     and $\int_0^\infty h(u)^2 du$
-    are all finite,
-	\comment{Should be a fullstop.}
+    are all finite.
     Suppose that Assumptions~\ref{def:model_setup} hold,
@@
 
-We postpone the proof of this Lemma until we have shown how it yields 
-\comment{delete `to'} to compact containment.
-First, we show that this implies compact containment
-\comment{compact containment of what?} for arbitrary
-compactly supported functions.
+We postpone the proof of this Lemma until we have shown how it yields compact containment.
+First, we show that this implies compact containment of the processes $(\langle f, \lp^N_t \rangle)_{0 \le t \le T}$
+for arbitrary compactly supported $f$.
 
@@
     Suppose $f \in C(\bar \IR^d \times [0, \infty))$ and there is a $u_f$ such that
-    $f(x, u) = 0$ for all $x$ and $u \ge u_f$.
-	\comment{sounds like $f$ vanishes for all $x$ irrespective of $u$!
-	Can we reword? `all $(x,u)$ with $u\geq u_f$' or something?}
+    if $u \ge u_f$ then $\sup_x f(x, u) = 0$.
     Under the assumptions of Lemma~\ref{lem:h_containment},
@@
 with uniformly high probability,
-a set which is compact if we choose $\{f_k\}$ appropriately.
-\comment{Does the reader know how to act `appropriately' in 
-making this choice? Maybe refer back to the right bit above where it 
-is explained.}
+a set which (as discussed in the proof of Theorem~\ref{thm:lookdown_convergence})
+is relatively compact by appropriate choice of $\{f_k\}_{k \ge 1}$.
 % \comment{
@@
     Now, since $\lp_t^N$ is conditionally uniform given $\eta_t^N$,
-    we know that for appropriate $f$, \comment{A bit vague... can we be 
-    more specific about what makes a function appropriate?}
-    $  \IE[\langle f, \lp^N_t \rangle] = \IE[\langle \widetilde{f}, \eta^N_t \rangle] , $
-    where $\widetilde{f}(x) = \int_0^\infty f(x, u) du$.
+    we know that if $f \in C(\IR^d \times [0,\infty))$
+    with $\IE[\langle |f|, \lp^N_t \rangle] < \infty$ then
+    $\IE[\langle f, \lp^N_t \rangle] = \IE[\langle \widetilde{f}_N, \eta^N_t \rangle]$,
+    where $\widetilde{f}_N(x) = \int_0^N f(x,u) du$.
     By our assumptions on $h$,
@@
 
-    Again \comment{Only a very alert reader will remember why we say `again'
-    here...} since $\sqrt{x} \le 1 + x$ for $x \ge 0$,
+    Since $\sqrt{x} \le 1 + x$ for $x \ge 0$,
     the Burkholder-Davis-Gundy inequality
@@
     for which there exists a $u_0$ such that if $u > u_0$ then $f(x, u) = 0$.
-    Then, the sequence of real-valued processes $(\langle f, \lp_t^N \rangle)_{t \ge 0}$
-	are \comment{`is' - the subject of the sentence is the (single) sequence}
-	tight in the space of \comment{real-valued? or ${\cal D}_\IR$-valued} 
-	c\`adl\`ag processes.
+    Then, the sequence of real-valued processes $(\langle f, \lp_t^N \rangle)_{t \ge 0}$ for $N \ge 1$
+    is tight in ${\cal D}_{[0\infty)}(\IR)$.
 \end{lemma}
@@
         \\ {} &\qquad
-            + c_\theta (N - u) \int (f(y, u) - f(x, u)) q^m(x,dy,\eta)
+            + c_\theta (N - u) \int_0^t (f(y, u) - f(x, u)) q^m(x,dy,\eta)
             + (c_\theta u^2 - b_\theta u) \frac{d}{du} f,
             \lp_s
-        \Big\rangle ds
-    \end{align*}
-	\comment{limits of integration missing in last integral}
+        \Big\rangle ds .
+    \end{align*}
     The bounds analogous to \eqref{eqn:eta_projections_goal1} and \eqref{eqn:eta_projections_goal2}
@@
 	We just need to be able to integrate against it I guess.}
+    \comment{PETER: I think the point here was to remind the reader that it may not exist everywhere?}
 We first proceed informally, as if the density exists everywhere,
@@
 % (This is $\mathcal{L}^Y_s g(x) = \gamma ( \DG(rg)(x) - g \DG r(x) )$ in shorter but more cryptic notation.)
-The diffusion is time-inhomogeneous if the density is not constant with
-	\comment{this may be an example of being divided by a common
-	language, but I would say `in time'} time.
-Let $\varphi_t(x)$ be the limiting density, which 
-	\comment{is a weak solution to?} 
-	solves \eqref{general deterministic limit},
-$\partial_t \varphi = r \DG^*[ \varphi_t \gamma ] + \varphi F$.
+The diffusion is time-inhomogeneous if the density is not constant in time.
+Let $\varphi_t(x)$ be the limiting density,
+which is a weak solution to \eqref{general deterministic limit},
+$\partial_t \varphi_t = r \DG^*[ \varphi_t \gamma ] + \varphi F$.
 Formally, the intensity of individuals at $y$ at time $t$
@@
 we can write this as 
-$$
+\begin{align} \label{eqn:integrated_semigroups}
     \int f(y)\varphi_t(y)\hat{T}_{t,s}g(y)dy
@@
         \right]dx.
-$$
-Differentiating with respect to $t$ at $t=s$,
-\comment{This is a bit confusing. I think it is partly because it says generator
-of $\widehat{T}_{t,s}$ and of course $t$ disappears. But also it is 
-because we are 
-looking for the generator of the ancestral lineage and so it 
-feels like one wants to 
-differentiate with respect to `-s' if you see what I mean.}
-and writing 
-$\Lgen_s$ for the generator of $\hat{T}_{t,s}$ at time $s$, we find
+\end{align}
+Next, we will differentiate this equation with respect to $t$.
+There are two terms in the product on the left-hand side that depend on $t$,
+so if we
+use that $\partial_t \varphi_t = r \DG^*[ \varphi_t \gamma ] + \varphi F$
+(in a weak sense),
+and write $\Lgen_u$ for the generator of $\hat{T}_{t,s}$ at time $t=u$
+so that $\partial_t \hat{T}_{t,s} g(y) \Big|_{t=s} = \Lgen_s g(y)$,
+then
+\begin{multline*}
+    \qquad \qquad
+    \frac{d}{dt} 
+    \int f(y)\varphi_t(y)\hat{T}_{t,s}g(y)dy
+    \Big|_{t=s}
+    \\ {}
+    =
+    \int f(y) \left\{
+        \varphi_s(y) \Lgen_s g(y)
+        + \left[
+            r(y) \DG^*(\gamma \varphi_s)(y) + \varphi_s(y) F(y)
+        \right] g(y)
+    \right\} dy .
+\end{multline*}
+As for the right-hand side, since $Y_s=x$ under $\IE_{x,s}$,
+\begin{multline*}
+    \frac{d}{dt}
+        \IE_{x,s}\left[
+            \exp\left(
+                \int_s^t(F+\gamma\DG r)(Y_u)du
+            \right)f(Y_t)
+        \right]
+    \Bigg|_{t=s}
+    =
+        \left[F(x)+\gamma(x) \DG r(x)\right] f(x) + \Lgen^Y_s f(x) .
+\end{multline*}
+Therefore, the derivative of~\eqref{eqn:integrated_semigroups}
+(with respect to $t$, evaluated at $t=s$) is
 \begin{align*}
@@
     \int g(x) \varphi_s(x) \left(
-        {\mathcal L}^Y_s f(x) + (F(x)+\gamma(x) \DG r(x)) f(x)
+        \Lgen^Y_s f(x) + \left[F(x)+\gamma(x) \DG r(x)\right] f(x)
     \right) dx \\
@@
     \int f(x) \left(
-        ({\mathcal L}^Y_s)^* (\varphi_s g)(x) + (F(x) + \gamma(x) \DG r(x)) \varphi_s(x) g(x)
+        (\Lgen^Y_s)^* (\varphi_s g)(x) + \left[F(x) + \gamma(x) \DG r(x)\right] \varphi_s(x) g(x)
     \right) dx ,
 \end{align*}
-where $({\mathcal L}^Y_s)^*$ is the adjoint of ${\mathcal L}^Y_s$
-and we have used that $\varphi_s$ solves $\dot \varphi = r \DG^*(\gamma \varphi) + F \varphi$.
+where $(\Lgen^Y_s)^*$ is the adjoint of $\Lgen^Y_s$ .
+% and we have used that $\varphi_s$ solves $\dot \varphi = r \DG^*(\gamma \varphi) + F \varphi$.
 Since $f$ was arbitrary,
@@
     \frac{1}{\varphi_s} \left[
-        ({\mathcal L}^Y_s)^* (\varphi_s g)
+        (\Lgen^Y_s)^* (\varphi_s g)
         + \gamma \varphi_s g \DG(r)
@@
 \begin{proof}[of Corollary~\ref{cor:stationary_dist}]
-For the moment, we will write $r(x)$ for $r(x, \eta)$
-and similarly for $\gamma(x)$.
-First, note that in this case
-	\comment{Should really define our notation - ${\cal L}_s$ is
-	independent of time, so...}
+For the moment, we will write $r(x)$ for $r(x,\eta)$
+and $\gamma(x)$ for $\gamma(x,\eta)$.
+First note that
+since in this case the semigroup does not depend on time, 
+we can write $\Lgen = \Lgen_s$, and
 $$
@@
         + \grad ( 2 \log(\gamma \varphi) - h/\sigma^2 ) \cdot \grad f
-    \right) ,
+    \right) .
 $$
-and that
+Now, observe that
 $$
@@
         \grad f(x) \cdot \grad g(x)
-    \right\} dx .
+    \right\} dx ,
 $$
-Therefore, by choosing $H(x) = 2 \log(\gamma(x) \varphi(x)) - h(x)/\sigma^2$
+so that by choosing $H(x) = 2 \log(\gamma(x) \varphi(x)) - h(x)/\sigma^2$
 and

### 2023-05-01 forwards-and-backwards.tex
minor edits

@@
 We now give two concrete situations in which condition~\ref{gamma_B_condition} is satisfied.
+The proof is in Section~\ref{sec:preliminary_proofs}.
 
@@
 and so $\DG(fr)(x) = \DG(f(\cdot) r(\cdot, \smooth{r} \eta_s(\cdot)))(x)$.
+The proof of this theorem appears in Section~\ref{sec:population_density_proof}.
 
@@
 The following propositions provide two concrete situations in which this is true.
-In the first, the PDE is a reaction-diffusion equation, and we borrow
+In the first, the PDE is a reaction-diffusion equation, and
+in the proof in Section~\ref{two-step convergence to FKPP} we borrow
 an idea from~\cite{penington:2017} to express the solutions to both the nonlocal
@@
 \end{proposition}
-The example that we have in mind for the kernel $\rho_\gamma$ is a Gaussian
-kernel.
+The example that we have in mind for the kernel $\rho_\gamma$ is a Gaussian kernel.
+For the proof, see Section~\ref{sec:pme}.
 \begin{remark}
@@
 \end{remark}
-
-Proofs of the results so far, on nonlocal processes, are found in Section~\ref{sec:proofs}.
 
@@
 
-\comment{FROM ALISON: should we signpost that the proofs of these results can 
-be found in section???}
+Both results are proved in Section~\ref{sec:lookdown_proofs}.
 
@@
 \subsection{Preliminaries}
+\label{sec:preliminary_proofs}
 
@@
 % % % % % % % % % % % % %
-\subsection{Proof of Theorem~\ref{thm:nonlocal_convergence}: limit points for the nonlocal process}
+\subsection{Proof of Theorem~\ref{thm:nonlocal_convergence}: convergence for the nonlocal process}
     \label{sec:population_density_proof}
 
-In this section we prove 
-Theorem~\ref{thm:nonlocal_convergence}.
+In this section we prove Theorem~\ref{thm:nonlocal_convergence}.
 This would be implied by convergence of the lookdown process
@@
 \subsubsection{Porous Medium Equation}
+\label{sec:pme}
 
@@
 
-In order to identify the limit point of any convergent subsequence
+To identify the limit point of any convergent subsequence
 of $\{\rho_\epsilon*\eta^N(x)\}$, 
-we are going to require some control on the spatial continuity of the 
+we will require some control on the spatial continuity of the 
 functions $\rho_\epsilon*\eta^N(x)$. This will be inherited from the regularity
@@
         \left( \frac{
-            2 (\epsilon^2 + t)3
+            6 (\epsilon^2 + t)
         }{
@@
     \end{align*}
-Now, thinking of the first term in brackets as a function of a single variable on
+Now, thinking of the first term in brackets as a function of a single variable $x$ on
 the line segment $[y,z]$ connecting $y$ to $z$, we can apply the
@@
 \int_0^{s-\delta}
-\big\langle |p_{s-r+\epsilon^2}(y,z)-p_{s-r+\epsilon^2}(w,z)| 
+\big\langle (p_{s-r+\epsilon^2}(y,z)-p_{s-r+\epsilon^2}(w,z)|)
 \cdot |F(\rho_\epsilon*\eta_r(z)|, 
@@
     \\ &\qquad \qquad {}
-	+ \big\langle\frac{C}{(\theta\epsilon^2)^{1/2}} \Big(%\big\langle 
-	p_{6(\epsilon^2+s)}(y,z)+p_{6(\epsilon^2+s)}(w,z)\Big) %, \eta_0(dz)
-%\big\rangle
-	+\widehat{\epsilon}(\delta,\epsilon,\theta) %\langle 1
+	+ \big\langle\frac{C}{(\theta\epsilon^2)^{1/2}} \Big(
+	p_{6(\epsilon^2+s)}(y,z)+p_{6(\epsilon^2+s)}(w,z)\Big)
+	+\widehat{\epsilon}(\delta,\epsilon,\theta)
 	,\eta_0(dz)\rangle
@@
 \leq \Big\langle \frac{\|y-w\|}{\sqrt{s+\epsilon^2}}
-\big(p_{2(s+\epsilon^2}(y,z)+p_{2(s+\epsilon^2}(w,z)\big),\eta_0(dz)\Big\rangle
+    \big(p_{2(s+\epsilon^2)}(y,z)+p_{2(s+\epsilon^2)}(w,z)\big),\eta_0(dz)\Big\rangle
 \nonumber
@@
 \int_0^{s-\delta}\Big\langle\frac{\|y-w\|}{\sqrt{s-r+\epsilon^2}}
-\big(p_{2(s-t+\epsilon^2}(y,z)+p_{2(s-r+\epsilon^2}(w,z)\big)
+    \big(p_{2(s-t+\epsilon^2)}(y,z)+p_{2(s-r+\epsilon^2)}(w,z)\big)
 \cdot |F(\rho_\epsilon*\eta_r(z)|, 
@@
 \frac{C}{(\epsilon^2\theta)^{1/2}}
-|p_{6(s-r+\epsilon^2)}(y,z)+
-p_{6(s-r+\epsilon^2)}(w,z)| +\widehat{\epsilon}(\delta,\epsilon,\theta)\Big\}
+(p_{6(s-r+\epsilon^2)}(y,z)+ p_{6(s-r+\epsilon^2)}(w,z))
++\widehat{\epsilon}(\delta,\epsilon,\theta)\Big\}
 \cdot |F(\rho_\epsilon*\eta_r(z)|, 
@@
 \langle \rho_\epsilon*f(x), \eta_t^N(dx)\rangle$,
+and the limit is deterministic,
 this will follow if we can show that each the terms in the semimartingale
@@
 $\rho_\epsilon*f(x) = T_{\epsilon^2}f(x)$.
-By a Taylor expansion, writing $\{T_t\}_{t\geq 0}$ for the heat semigroup,
+By a Taylor expansion,
 \begin{align*}
@@
 there exist real numbers $b_k$ such
-that $F(a)-F(b)= (a-b)\sum_{k=1}^{n-1}b_kx^ky^{n-1-k}$ and so 
+that $F(a)-F(b)= (a-b)\sum_{k=1}^{n-1} b_k a^k b^{n-1-k}$ and so 
 \[
@@
 
-Combining the above, we have reduced the problem to showing that 
+Combining the above, we have reduced the problem to showing that for any $k \ge 0$,
 \begin{equation}
@@
 	p_{\epsilon^2}(w,y)dy, \eta_s(dw)\big\rangle ds\Big]
-=0,
+=0 .
 \end{equation}
@@
 \big\rangle
-\big(\rho_\epsilon*\eta_s(y)^{k+1} +\rho_\epsilon*\eta_s(x)^{k+1}\big)\Big]
-p_{\epsilon^2}(x,y) dy dx ds,
+\big(\rho_\epsilon*\eta_s(y)^{k+1} +\rho_\epsilon*\eta_s(x)^{k+1}\big)
+p_{\epsilon^2}(x,y) dy dx \Big] ds,
 \end{multline*}
@@
 +\rho_\epsilon*\eta_0(x)
-+\rho_\epsilon*\eta_0(x)^{k+1}\big)\Big]
-p_{\epsilon^2}(x,y) dy dx ds 
-={\mathcal O}(\epsilon).
++\rho_\epsilon*\eta_0(x)^{k+1}\big)
+p_{\epsilon^2}(x,y) dy dx \Big] ds 
+\\
+\le C'\epsilon\int_\delta^t\frac{1}{(s+\epsilon^2)^{d/2}}ds .
 \end{multline*}
+For fixed $\delta$, this bound tends to zero as $\epsilon\to 0$.
 The term involving 
@@
 \begin{multline*}
-\big\langle\langle p_{2(s+\epsilon^2)}(y,z), \eta_0(dz)\rangle
+\big\langle \int \langle p_{2(s+\epsilon^2)}(y,z), \eta_0(dz)\rangle
 \rho_\epsilon*\eta_s(w)^kp_{2\epsilon^2}(w,y)dy, \eta_s(dw)\big\rangle
@@
 the contribution to~(\ref{contribution from initial condition terms})
-from this term of the form
-\[C\epsilon\int_\delta^t\frac{1}{(s+\epsilon^2)^{d/2}}ds.\]
-Note that for fixed $\delta$, this bound tends to zero as $\epsilon\to 0$.
+from this term of the same form as the others.
+% \[C\epsilon\int_\delta^t\frac{1}{(s+\epsilon^2)^{d/2}}ds.\]
+% Note that for fixed $\delta$, this bound tends to zero as $\epsilon\to 0$.
 
@@
 \big\langle\big(p_{2(s-r+\epsilon^2)}(y,z)+ p_{2(s-r+\epsilon^2)}(w,z)\big)
-\rho_\epsilon*\eta_r(z)^j,\eta_r(dz)\big\rangle dr
+\rho_\epsilon*\eta_r(z)^j,\eta_r(dz)\big\rangle
 \\
 \rho_\epsilon*\eta_s(y)^kp_{\epsilon^2}(y,w)dy,\eta_s(dw)
-\Big\rangle ds
+\Big\rangle dr ds
 \\
@@
 \big(p_{2(s-r+\epsilon^2)}(y,z)+ p_{2(s-r+\epsilon^2)}(w,z)\big)
-\rho_\epsilon*\eta_r(z)^j,\eta_r(dz)\big\rangle dr
+\rho_\epsilon*\eta_r(z)^j,\eta_r(dz)\big\rangle 
 \\
 \rho_\epsilon*\eta_s(y)^kp_{2\epsilon^2}(y,w)dy,\eta_s(dw)
-\Big\rangle ds,
+\Big\rangle dr ds,
 \end{multline*}
@@
 \]
-Since $\psi_{t-s}^{\epsilon,x}(y)=p_{T(t-s)+\epsilon^2}(x,y)$, 
+Since $\psi_{t-s}^{\epsilon,x}(y)=\IE[p_{T(t-s)+\epsilon^2}(x,y)]$, 
 rearranging~(\ref{expn rhoepsilon})
 we see that we can pull a convolution with $p_{\epsilon^2/2}$ out of
-our expressions for $M_s(x)$ and $M_s(w)$ and so all the manipulations 
+our expression for $M_s(w)$ and so all the manipulations 
 that we used to control terms above with still be valid.
@@
 % % % % % % % % % % % % %
-\section{Lookdown Proofs}
+\section{Proofs of results for the lookdown process and ancestral lineages}
     \label{sec:lookdown_proofs}

### 2023-05-02 forwards-and-backwards.tex
.

@@
 The following appears as Theorem A.2 in \citet{etheridge/kurtz:2019},
-specialized slightly to the case that the processes 
+specialized slightly here to the case that the processes 
 are c\`adl\`ag and have no fixed points of discontinuity.
@@
 and define the transition function $\Gamma^N : \measures \to \mathcal{M}(\IR^d \times [0,N))$
-so that for $\eta \in \measures$, if $\hat g(x) = \int_0^N g(x, u) du / N$, then
+so that for $\eta \in \measures$, if $\hat g_N(x) = \int_0^N g(x, u) du / N$, then
 \begin{align*}
@@
     \exp\left(
-        N \left\langle \log \hat g(x), \eta(dx) \right\rangle
+        N \left\langle \log \hat g_N(x), \eta(dx) \right\rangle
     \right) ,
@@
         N \theta & \bigg\langle
-        \gamma(x, \eta) \int r(z, \eta) \left( \hat g(z) - 1 \right) q_\theta(x, dz)
+        \gamma(x, \eta) \int r(z, \eta) \left( \hat g_N(z) - 1 \right) q_\theta(x, dz)
     \\ &\qquad \qquad {}
         +
-        \mu_\theta(x, \eta) \left( \frac{1}{\hat g(x)} - 1 \right)
+        \mu_\theta(x, \eta) \left( \frac{1}{\hat g_N(x)} - 1 \right)
         ,
@@
     F_g^N(\eta) \bigg\langle
-        \frac{1}{N \hat g(x)} \int_0^N \ell(x,u) du,
+        \frac{1}{N \hat g_N(x)} \int_0^N \ell(x,u) du,
         N \eta(dx)
@@
 \\ &\qquad =
-    F_g^N(\eta) \bigg\langle \frac{c_\theta(x,\eta)}{\hat g(x)} \int_0^N \Bigg\{
+    F_g^N(\eta) \bigg\langle \frac{c_\theta(x,\eta)}{\hat g_N(x)} \int_0^N \Bigg\{
         \int_u^N \Bigg(
@@
 \\ &\qquad =
-    F_g^N(\eta) \bigg\langle \frac{c_\theta(x,\eta)}{\hat g(x)} \Bigg\{
+    F_g^N(\eta) \bigg\langle \frac{c_\theta(x,\eta)}{\hat g_N(x)} \Bigg\{
     \int_{\IR^d} \left\{
@@
 \\ &\qquad =
-    F_g^N(\eta) \bigg\langle \frac{c_\theta(x,\eta)}{\hat g(x)} \int_0^N g(x, u) \Bigg\{
+    F_g^N(\eta) \bigg\langle \frac{c_\theta(x,\eta)}{\hat g_N(x)} \int_0^N g(x, u) \Bigg\{
         \int_u^N\Bigg(\int_{\IR^d}
@@
 \\ &\qquad =
-    F_g^N(\eta) \bigg\langle \frac{c_\theta(x,\eta)}{\hat g(x)}
+    F_g^N(\eta) \bigg\langle \frac{c_\theta(x,\eta)}{\hat g_N(x)}
     \int_{\IR^d}\Bigg\{ \int_{0}^{N}
@@
 \normalsize
-For the third generator we have that, since $g(x,N) = 1$,
+For the third generator we have that
 \begin{align*}
@@
 \\ & \qquad =
-    F_g^N(\eta) \bigg\langle \frac{1}{\hat g(x)}
+    F_g^N(\eta) \bigg\langle \frac{1}{\hat g_N(x)}
     \int_0^N
@@
 
-Note that $2 \int_0^N \int_u^N g(x,v_1) g(y,u) dv_1 du = N^2 \hat g(x) \hat g(y)$,
+Note that $2 \int_0^N \int_u^N g(x,v_1) g(y,u) dv_1 du = N^2 \hat g_N(x) \hat g_N(y)$,
 and so
@@
 \\ &\qquad = 
-    N^2 \hat{g}(x)(\hat{g}(y) - 2) + 2\int_{0}^{N} u g(x,u) du.
+    N^2 \hat{g_N}(x)(\hat{g_N}(y) - 2) + 2\int_{0}^{N} u g(x,u) du.
 \end{align*}
@@
     F_g^N(\eta) \bigg\langle
-        c_\theta(x,\eta) N^2 \int_{\IR^d} (\hat g(y) - 2) q^m(x,dy,\eta)
+        c_\theta(x,\eta) N^2 \int_{\IR^d} (\hat g_N(y) - 2) q^m(x,dy,\eta)
         +
-        \frac{1}{\hat g(x)} c_\theta(x,\eta) \int_0^N 2u du
+        \frac{1}{\hat g_N(x)} c_\theta(x,\eta) \int_0^N 2u du
 \\ &\qquad \qquad \qquad {}
         +
-        \frac{1}{\hat g(x)} b_\theta(x,\eta) \int_0^N (g(x,u) - 1) du
+        \frac{1}{\hat g_N(x)} b_\theta(x,\eta) \int_0^N (g(x,u) - 1) du
     , \eta(dx) \bigg\rangle 
@@
     F_g^N(\eta) \bigg\langle
-        c_\theta(x,\eta) N^2 \int_{\IR^d} (\hat g(y) - 1) q^m(x,dy,\eta)
+        c_\theta(x,\eta) N^2 \int_{\IR^d} (\hat g_N(y) - 1) q^m(x,dy,\eta)
         +
-        N^2 c_\theta(x,\eta) \left(\frac{1}{\hat g(x)} - 1\right)
+        N^2 c_\theta(x,\eta) \left(\frac{1}{\hat g_N(x)} - 1\right)
 \\ &\qquad \qquad \qquad {}
         +
-        N b_\theta(x,\eta) \left(1 - \frac{1}{\hat g(x)}\right)
+        N b_\theta(x,\eta) \left(1 - \frac{1}{\hat g_N(x)}\right)
     , \eta(dx) \bigg\rangle 
@@
     F_g^N(\eta) N \bigg\langle
-        N c_\theta(x,\eta) \int_{\IR^d} (\hat g(y) - 1) q^m(x,dy,\eta)
+        N c_\theta(x,\eta) \int_{\IR^d} (\hat g_N(y) - 1) q^m(x,dy,\eta)
         +
-        \theta \mu_\theta(x,\eta) \left(\frac{1}{\hat g(x)} - 1\right)
+        \theta \mu_\theta(x,\eta) \left(\frac{1}{\hat g_N(x)} - 1\right)
     , \eta(dx) \bigg\rangle  .

### 2023-05-03 forwards-and-backwards.tex
.
one bib file
final final edits, sending to co-authors

@@
 
-\comment{TODO: signpost where proofs can be found}
-
 \begin{abstract}
@@
             \varphi_t(\cdot)
-            \gamma\big( x, \varphi_t \big)
+            \gamma\big(\cdot, \varphi_t \big)
         \right](x)
@@
 for some $C>0$,   
-the methods of \cite{KURTZ1999103} show that %under the conditions
+the methods of \citet{kurtz/xiong:1999} show that %under the conditions
 %of Theorem~\ref{thm:kurtzxiong}, 
@@
 we say that \emph{$\lp^N$ is conditionally uniform given $\mathcal{F}$}
-if for all compactly supported $f$,
+if $\kappa^N(\lp)$ is $\mathcal{F}$-measurable and 
+for all compactly supported $f$,
 \begin{align} \label{eqn:conditionally_uniform}
@@
 we say that \emph{$\lp$ is a conditionally Poisson random measure given $\mathcal{F}$}
-if for all compactly supported $f$,
+if $\kappa(\lp)$ is $\mathcal{F}$-measurable and 
+for all compactly supported $f$,
 \begin{align} \label{eqn:conditionally_poisson}
@@
 combines with the last term in~\eqref{kth moment for time varying function}
-to obtain 
+to yield 
 $$ \int_0^t k \langle \psi^{\epsilon,x}_{t-s},\eta\rangle^{k-1} \langle F(\rho_\epsilon*\eta_s(y)) \psi^{\epsilon,x}_{t-s}(y), \eta_s(dy) \rangle ds . $$
@@
 Consulting~\eqref{eqn:prelimit_martingale_variation},
+and using the approach of Lemma~\ref{lem:limit_mgale},
 the quadratic variation of $\widehat{M}^N(f)$ satisfies
-$ \IE[[\widehat{M}^N_f]_T] \le C (\theta/N) \int_0^T \langle 1, \eta_s \rangle ds \le C' \theta/N$
+$ \IE[[\widehat{M}^N_f]_T] \le C (\theta/N) \int_0^T \IE[\langle 1, \eta_s \rangle] ds \le C' \theta/N$
 for some constants $C$ and $C'$.
@@
     In the notation of Lemma~\ref{PsiBoundHS},
+    there exists a $C < \infty$ such that
     %and with $A$ as in Lemma~\ref{lem:poisson_ld},
@@
 & |\rho_\epsilon*\eta_s(y)-\rho_\epsilon*\eta_s(w)| \nonumber 
-= |\langle p_{\epsilon^2}(y,z)-p_{\epsilon^2}(w,z),\eta_s(dz) \rangle | 
+=
+    |\langle p_{\epsilon^2}(y,z)-p_{\epsilon^2}(w,z),\eta_s(dz) \rangle | 
 \nonumber
-\\ 
-&\qquad
+\\ &\qquad
 \leq 
-\big\langle |p_{\epsilon^2+s}(y,z)-p_{\epsilon^2+s}(w,z)|, 
-\eta_0(dz)\big\rangle 
+\big\langle
+    |p_{\epsilon^2+s}(y,z)-p_{\epsilon^2+s}(w,z)|, 
+\eta_0(dz) \big\rangle 
 \nonumber
@@
 \int_0^{s-\delta}
-\big\langle (p_{s-r+\epsilon^2}(y,z)-p_{s-r+\epsilon^2}(w,z)|)
-\cdot |F(\rho_\epsilon*\eta_r(z)|, 
+    \big\langle |p_{s-r+\epsilon^2}(y,z)-p_{s-r+\epsilon^2}(w,z)||
+    |F(\rho_\epsilon*\eta_r(z)|, 
 \eta_r(dz) \big\rangle  dr
@@
 \\ &\qquad \qquad {}
-	+ \big\langle\frac{C}{(\theta\epsilon^2)^{1/2}} \Big(
-	p_{6(\epsilon^2+s)}(y,z)+p_{6(\epsilon^2+s)}(w,z)\Big)
-	+\widehat{\epsilon}(\delta,\epsilon,\theta)
-	,\eta_0(dz)\rangle
++
+\Big\langle
+    \frac{C}{(\theta\epsilon^2)^{1/2}}
+    \Big(p_{6(\epsilon^2+s)}(y,z)+p_{6(\epsilon^2+s)}(w,z)\Big)
+	+ C\widehat{\epsilon}(\delta,\epsilon,\theta)
+,\eta_0(dz) \Big\rangle
 \nonumber
@@
 p_{6(s-r+\epsilon^2)}(w,z)| +\widehat{\epsilon}(\delta,\epsilon,\theta)\Big\}
-\cdot |F(\rho_\epsilon*\eta_r(z)|, 
+|F(\rho_\epsilon*\eta_r(z)|, 
 \eta_r(dz) \big\rangle  dr
@@
 %p_{6(s-r+\epsilon^2)}(w,z)|
-%\cdot |F(\rho_\epsilon*\eta_r(z)|, 
+%|F(\rho_\epsilon*\eta_r(z)|, 
 %\eta_r(dz) \big\rangle  dr
@@
 |\psi_{s-r}^{\epsilon,y}(z) + \psi_{s-r}^{\epsilon, w}(z) |
-\cdot |F(\rho_\epsilon*\eta_r(z)|, 
+|F(\rho_\epsilon*\eta_r(z)|, 
 \eta_r(dz) \big\rangle  dr
@@
 \\ & \qquad 
-\leq \Big\langle \frac{\|y-w\|}{\sqrt{s+\epsilon^2}}
+\leq
+\Big\langle \frac{\|y-w\|}{\sqrt{s+\epsilon^2}}
     \big(p_{2(s+\epsilon^2)}(y,z)+p_{2(s+\epsilon^2)}(w,z)\big),\eta_0(dz)\Big\rangle
@@
     \big(p_{2(s-t+\epsilon^2)}(y,z)+p_{2(s-r+\epsilon^2)}(w,z)\big)
-\cdot |F(\rho_\epsilon*\eta_r(z)|, 
+    |F(\rho_\epsilon*\eta_r(z)|, 
 \eta_r(dz)\Big\rangle dr
@@
 \\ & \qquad \qquad  {}
-	+ \big\langle \frac{C}{(\theta\epsilon^2)^{1/2}}\Big( 
++
+\Big\langle \frac{C}{(\theta\epsilon^2)^{1/2}}\Big( 
 	p_{6(\epsilon^2+s)}(y,z)+p_{6(\epsilon^2+s)}(w,z)\Big)+
-	\widehat{\epsilon}(\delta,\epsilon,\theta) , \eta_0(dz)
-\big\rangle
+	C \widehat{\epsilon}(\delta,\epsilon,\theta) , \eta_0(dz)
+\Big\rangle
 \nonumber
@@
 +\widehat{\epsilon}(\delta,\epsilon,\theta)\Big\}
-\cdot |F(\rho_\epsilon*\eta_r(z)|, 
+|F(\rho_\epsilon*\eta_r(z)|, 
 \eta_r(dz) \big\rangle  dr
@@
 and the limit is deterministic,
-this will follow if we can show that each the terms in the semimartingale
+this will follow if we can show that each of the terms in the semimartingale
 decomposition~(\ref{eqn:eta_martingale}),
@@
 we see that we can pull a convolution with $p_{\epsilon^2/2}$ out of
-our expression for $M_s(w)$ and so all the manipulations 
+our expressions for $M_s(y)$ and $M_s(w)$ and so all the manipulations 
 that we used to control terms above with still be valid.
@@
 
+\begin{remark}
 In addition to tightness of the measure-values processes $\lp^N$,
@@
 of Section~\ref{sec: individual lines of descent} holds.
-	\comment{Is this paragraph really a separate remark that we want to make?}
-    \comment{PETER: maybe? Figuring out how to make it more concrete/rigorous seems daunting, though -
-        I'm inclined to remove it.}
+\end{remark}
 
@@
     % PLR: NEW DETAILS
-    Several places below we require a dense subset
-    of $\bar C(\lpmeasures)$, the bounded, continuous functions on $\lpmeasures$.
+    In several places below we require a dense subset
+    of $C_b(\lpmeasures)$, the bounded, continuous functions on $\lpmeasures$.
     The functions $\lp \mapsto \langle f, \lp \rangle$
-    do not form not a dense subset of $\bar C(\lpmeasures)$,
+    do not form not a dense subset of $C_b(\lpmeasures)$,
     but they do separate points and vanish nowhere, 
@@
     % Since $C_0(\lpmeasures)$ is dense
-    in $\bar C(\lpmeasures)$ (with respect to uniform convergence on compact subsets).
+    in $C_b(\lpmeasures)$ (with respect to uniform convergence on compact subsets).
     % END NEW DETAILS
-    Topologized in this way, the space $\lpmeasures$ completely metrizable,
+    Topologized in this way, the space $\lpmeasures$ is completely metrizable,
     and we may choose a countable set of nonnegative $f_k$,
@@
 
-    For \citet{ethier/kurtz:1986} Theorem~3.9.1
+    In order to apply \citet{ethier/kurtz:1986} Theorem~3.9.1
     we require that $\{(F(\lp^N_t))_{t \ge 0}\}_N$
     is tight as a sequence of real-valued c\`adl\`ag processes, for all $F$ in a subset
-    of $\bar C(\lpmeasures)$ %, the bounded, continuous functions on $\lpmeasures$,
+    of $C_b(\lpmeasures)$ %, the bounded, continuous functions on $\lpmeasures$,
     that is dense with respect to uniform convergence on compact subsets.
@@
     % The functions $\lp \mapsto \langle f, \lp \rangle$
-    % do not form not a dense subset of $\bar C(\lpmeasures)$,
+    % do not form not a dense subset of $C_b(\lpmeasures)$,
     % but they do separate points and vanish nowhere, 
@@
     % % Since $C_0(\lpmeasures)$ is dense
-    % in $\bar C(\lpmeasures)$ (with respect to uniform convergence on compact subsets).  So, 
-    Since as above the algebra generated by these are dense in $\bar C(\lpmeasures)$,
+    % in $C_b(\lpmeasures)$ (with respect to uniform convergence on compact subsets).  So, 
+    Since as above the algebra generated by the functions $\lp \mapsto \langle f \lp \rangle$
+    is dense in $C_b(\lpmeasures)$,
     it suffices to show that tightness for the processes $\langle f, \lp^N_t\rangle$
@@
 a set which (as discussed in the proof of Theorem~\ref{thm:lookdown_convergence})
-is relatively compact by appropriate choice of $\{f_k\}_{k \ge 1}$.
+is relatively compact for an appropriate choice of $\{f_k\}_{k \ge 1}$.
 % \comment{
@@
     \end{align}
-    Now, since $\lp_t^N$ is conditionally uniform given $\eta_t^N$,
-    we know that if $f \in C(\IR^d \times [0,\infty))$
-    with $\IE[\langle |f|, \lp^N_t \rangle] < \infty$ then
+    Now, since $\lp_t^N$ is conditionally uniform given $\eta_t^N$
+    in the sense of~\eqref{eqn:conditionally_uniform},
+    we know that for compactly supported $f$,
     $\IE[\langle f, \lp^N_t \rangle] = \IE[\langle \widetilde{f}_N, \eta^N_t \rangle]$,
@@
     $$
-    for some $C < \infty$, and so
+    for some $C < \infty$, and so (by dominated convergence)
     \begin{align*}
@@
     Then, the sequence of real-valued processes $(\langle f, \lp_t^N \rangle)_{t \ge 0}$ for $N \ge 1$
-    is tight in ${\cal D}_{[0\infty)}(\IR)$.
+    is tight in ${\cal D}_{[0,\infty)}(\IR)$.
 \end{lemma}
@@
 Here we have taken the high-density, deterministic limit
-(so, $\theta, N \to \infty$ and $\theta/N \to 0$)
-and so suppose that the limiting process has density $\varphi_t(x)$
-at location $x$ and time $t$ (which may only exist almost everywhere).
-	\comment{Is it obvious that it exists almost everywhere? 
-	We just need to be able to integrate against it I guess.}
-    \comment{PETER: I think the point here was to remind the reader that it may not exist everywhere?}
-We first proceed informally, as if the density exists everywhere,
+(so, $\theta, N \to \infty$ and $\theta/N \to 0$).
+We first proceed informally,
+as if the limiting process has a density $\varphi_t(x)$ at location $x$ and time $t$ (which it may not),
 and follow this with an integration against test functions to make the argument rigorous.
@@
 which is a weak solution to \eqref{general deterministic limit},
-$\partial_t \varphi_t = r \DG^*[ \varphi_t \gamma ] + \varphi F$.
+$\partial_t \varphi_t = r \DG^*[ \varphi_t \gamma ] + \varphi_t F$.
 Formally, the intensity of individuals at $y$ at time $t$
@@
     Let $(S,d)$ and $(S_0,d_0)$ be complete, separable metric spaces.
-    Let $A \subset \bar C(S) \times C(S)$ and $\psi \in C(S)$, $\psi \ge 1$.
+    Let $A \subset C_b(S) \times C(S)$ and $\psi \in C(S)$, $\psi \ge 1$.
     Suppose that for each $f \in \mathcal{D}(A)$ there exists $c_f$
@@
 \bibliographystyle{plainnat}
-\bibliography{refs,plr_refs,MendeleyIan}
+\bibliography{refs}
 

### 2023-05-10 forwards-and-backwards.tex
ian and terence comments

@@
 medium equation with logistic growth.
-
-\vspace{.1in}
-
-	\comment{Need to thank KAVLI, Paris Cit\'e, various funders}
 
@@
 $\DG=\Delta$,
-and $\rho_F$ is a Gaussian density. We allow a wide class of reaction terms, $F$, so
+and $\rho$ is a Gaussian density. We allow a wide class of reaction terms, $F$, so
 that the Fisher-KPP equation 
@@
 but these are provided for visualization and we do not embark on numerical study.
+
+\section*{Acknowledgements}
+
+\comment{Need to thank KAVLI, Paris Cit\'e, various funders}
+IL is supported by the ANID/Doctorado en el extranjero doctoral scholarship, grant number 2018-72190055.
+TT supported by the EPSRC Centre for Doctoral Training in Mathematics of Random Systems: Analysis, Modelling and Simulation (EP/S023925/1) and the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) under Germany's Excellence Strategy, EXC-2047/1-390685813.
 
@@
     (although often we omit the dependence of $\meanq$ and $\covq$ on $x$).
-    This implies that if we define, for $f \in C_b^\infty(\IR^d)$,
+    Furthermore, we define for $f \in C_b^\infty(\IR^d)$,
     \begin{align}
@@
     \end{align}
-    then
-    \begin{align}
-        \theta \int \left(
-            f(y) - f(x)
-        \right) q_\theta(x, dy)
-    \to \DG f(x) 
-        \qquad \text{as } \theta \to \infty .
-    \end{align}
-    We will also denote the adjoint of $\DG$ by
+    and denote the adjoint of $\DG$ by
     \begin{align*}
@@
 \end{definition}
+
+\begin{remark}
+    \label{rem:DG_limit}
+    $\DG$ is defined so that
+    \begin{align*}
+        \theta \int \left(
+            f(y) - f(x)
+        \right) q_\theta(x, dy)
+    \to \DG f(x) 
+        \qquad \text{as } \theta \to \infty .
+    \end{align*}
+\end{remark}
 
@@
         and uniformly bounded
-        in each component;
+        in each component, and
     % \item $\meanq(x)$ and $\covq(x)$ are $\alpha$-H\"older continuous in each component, for some $\alpha \in (0,1]$;
-    \item the operator $\DG$ is uniformly strictly elliptic.
+    \item the operator $\DG$ is uniformly strictly elliptic,
+        i.e., $\inf_x \inf_{y:\|y\|=1} \sum_{ij} y_i C(x)_{ij} y_j > 0$.
 \end{enumerate}
@@
 We also have the following uniqueness result.
-\begin{theorem}[Special case of \cite{KURTZ1999103}, Theorem~3.5]
+\begin{theorem}[Special case of \citet{kurtz/xiong:1999}, Theorem~3.5]
 	\label{thm:kurtzxiong}
@@
 \begin{remark}
-\cite{KURTZ1999103} considers an infinite system of stochastic differential equations
+\citet{kurtz/xiong:1999} considers an infinite system of stochastic differential equations
 for the locations and weights of a collection of particles that interact through their 
@@
 in a potential tilted by migration bias
-($(\varphi_s \gamma)^2 \exp(-\meanq \cdot x / \sigma^2)$).
+($(\varphi_s \gamma)^2 \exp(-\meanq \cdot x / \sigma^2)$,
+whose gradient appears in the drift term of the generator).
 In particular, lineages are drawn to regions of high fecundity (production of juveniles), but their
@@
         % and death probability to be $\mu(m) = 1 - \exp(-dt ((1+1/\theta) m - 1/\theta))$);
-        Values of $\theta$ are 1 and 100, respectively, and both have $N$ set
+        Values of $\theta$ in top and bottom figures
+        are 1 and 100, respectively, and both have $N$ set
         so that the density is roughly 100 individuals per unit of habitat
@@
         \quad
-        \text{for } \xi < 0 ,
-\end{align*}
+        \text{for } \xi < 0 
+\end{align*}
+and $m_P(\xi) = 0$ for $\xi \ge 0$,
 which is integrable and so when suitably normalised gives the unique stationary distribution.
@@
 \end{align*}
-Furthermore, recall from Definition~\ref{def:dispersal_generator} that
+Furthermore, recall from Remark~\ref{rem:DG_limit} that
 \begin{align} \label{eqn:near_critical}
@@
 (Note that this integral is with respect to $x$.)
-Referring back to Definition~\ref{def:dispersal_generator},
+Referring back to Remark~\ref{rem:DG_limit},
 a quick calculation shows that as $N \to \infty$,
@@
     \label{prop:limiting_construction}
-Let 
-$J(x,\eta)$ be such that $r(x,\eta)\gamma(x,\eta)\covq(x) = J(x,\eta) J(x,\eta)^T$, and set
-$\beta(x, \eta) = r(x,\eta)\gamma(x,\eta)\big(\meanq(x) + 2 \covq(x) \grad \log r(x, \eta)\big).$
+Define $J(x,\eta)$ and $\beta(x,\eta)$ by
+\begin{gather*}
+    r(x,\eta)\gamma(x,\eta)\covq(x) = J(x,\eta) J(x,\eta)^T \\
+    \beta(x, \eta) = r(x,\eta)\gamma(x,\eta)\big(\meanq(x) + 2 \covq(x) \grad \log r(x, \eta)\big) .
+\end{gather*}
 Associate with each label $a \in \labelspace = \cup_{k\geq 1}\IN^k$
@@
 \end{proof}
+
+Proofs of the remainder of these results are in Section~\ref{sec:lookdown_proofs}.
+
+\begin{remark}
+The process we consider is similar to the state-dependent branching processes
+of \citet{kurtz/rodrigues:2011}, so one might expect that the proofs there would carry over with little change.
+However, there is an important difference:
+Recall that the level $U_a(t)$ of a line of descent evolves as
+\begin{equation} \label{eqn:u_evolution}
+\dot u = c_\theta(x, \eta) u^2 - b_\theta(x, \eta) u,
+\end{equation}
+where $b_\theta(x, \eta)$ and $c_\theta(x, \eta)$ are defined in \eqref{b_defn}
+and \eqref{c_defn} respectively.
+Note that $c_\theta(x, \eta) \ge 0$, while $b_\theta(x, \eta)$ may take either sign.
+Assumptions~\ref{def:model_setup} imply that $c_\theta(x, \eta)$ is bounded,
+while $b_\theta(x, \eta)$, because of $F(x, \eta)$, is bounded above but not necessarily below.
+In \citet{kurtz/rodrigues:2011}, $b_\theta$ was bounded above and $c_\theta$ was bounded away from zero,
+so they noted that if $U_a(t) \ge b_\theta/c_\theta$ for some label $a$,
+that line of descent would only move upwards from that time onwards.
+Furthermore, coefficients did not depend on the state of the process (i.e., on $\eta$),
+thus allowing the processes to be jointly and simultaneously constructed
+for all values of $N$, with a pointwise embedding
+of $(\lp^N_t)_{t \ge 0}$ within $(\lp^{M})_{t \ge 0}$ for $b_\theta/c_\theta < N < M$.
+In other words, individuals with levels above $N > b_\theta/c_\theta$ at time $t_0$
+do not affect $(\lp^N_t)_{t \ge t_0}$,
+thus allowing a comparison of the number of lines of descent below level $u_0$
+to a branching process.
+Although we have provided a
+joint construction of $\lp^N$ for all $N$ in Section~\ref{sec: individual lines of descent},
+it does not have this monotonicity:
+for one thing, $b_\theta$ and $c_\theta$ depend on the population process $\eta$
+and so all individuals can affect all other ones (even those with lower levels).
+Furthermore, in the deterministic case $\theta/N$, and hence $c$, converges to zero,
+and so lines of descent with arbitrarily high level may drift back downwards.
+Indeed, this must be the case if the population persists,
+since in the deterministic case there is no branching.
+\end{remark}
 
@@
     +
-    C \int_0^t \IE\Big[\Big\langle f_n(x), \eta^N_s(dx) \Big] \Big\rangle ds ,
+    C \int_0^t \IE\Big[\Big\langle f_n(x), \eta^N_s(dx) \Big\rangle \Big] ds ,
 \end{align*}
@@
 tells us that for any $\delta > 0$,
-$\IP[\eta_t(\{x : \|x\| > R\})>\delta]\to 0$ as $R\to\infty$.
+$$
+    \IP\big\{ \eta_t(\{x : \|x\| > R\})>\delta \big\}
+    \le \frac{\IE[\langle f_0, \eta_t\rangle]}{\inf_{\{x:\|x\|\ge R\}} f_0(x)}
+    \to 0 \qquad \text{as } R\to\infty .
+$$
 \end{proof}
@@
 and 
-we assume that $\rho=\zeta*\check{\zeta}$ with $\zeta$ a rapidly decreasing function. 
+we assume that $\rho=\zeta*\check{\zeta}$ with $\zeta$ a rapidly decreasing function
+and $\check{\zeta}(x) = \zeta(-x)$.
 The example we have in mind is $\zeta$ (and therefore $\rho$) being the density of
@@
 %
-Moreover, since $\psi_t^\epsilon\log \psi_t^\epsilon$ is uniformly bounded below,
+Moreover, since $\psi_t^\epsilon\log \psi_t^\epsilon$ is uniformly bounded below
+and $\int \rho^\epsilon(x) dx = 1$,
 $$
@@
 $L^1\cap L^2\big([0,T]\times \IR\big)$, and that
-\begin{multline}
+\begin{multline} \label{eqn:weak_approx_pme}
 \int \psi_t^\epsilon(x)\phi(x) dx-\int \psi_0^\epsilon (x)\phi(x) dx
@@
 \end{multline}
-(for sufficiently regular $\phi$). Since
-$\int \psi_t^\epsilon(x)\phi(x) d x-
-\int \zeta^{\epsilon}*\psi_t^\epsilon (x)\phi(x) d x$ is order $\epsilon$, we see
-that $\zeta^{\epsilon}*\psi^\epsilon\rightharpoonup \psi$ in $L^1$, where $\psi$ is the (unique)
-solution
-to equation~(\ref{PME})
+(for sufficiently regular $\phi$).
+Since
+$\int \psi_t^\epsilon(x)\phi(x) d x- \int \zeta^{\epsilon}*\psi_t^\epsilon (x)\phi(x) d x$
+is order $\epsilon$,
+if we replace $\psi^\epsilon$ by $\zeta^{\epsilon}*\psi^\epsilon$ on the left hand side,
+then~\eqref{eqn:weak_approx_pme} says that $\zeta^{\epsilon}*\psi^\epsilon$
+solves~\eqref{PME} weakly up to order $\epsilon$.
+Therefore, $\zeta^{\epsilon}*\psi^\epsilon$ converges weakly to $\psi$ in $L^1$,
+where $\psi$ is the (unique)
+solution to equation~(\ref{PME})
 and, so, therefore, does $\psi^\epsilon$. In fact, strong convergence, that is
@@
 
-\begin{remark}
-The process we consider is similar to the state-dependent branching processes
-of \citet{kurtz/rodrigues:2011}, so one might expect that the proofs there would carry over with little change.
-However, there is an important difference:
-Recall that the level $U_a(t)$ of a line of descent evolves as
-\begin{equation} \label{eqn:u_evolution}
-\dot u = c_\theta(x, \eta) u^2 - b_\theta(x, \eta) u,
-\end{equation}
-where $b_\theta(x, \eta)$ and $c_\theta(x, \eta)$ are defined in \eqref{b_defn}
-and \eqref{c_defn} respectively.
-Note that $c_\theta(x, \eta) \ge 0$, while $b_\theta(x, \eta)$ may take either sign.
-Assumptions~\ref{def:model_setup} imply that $c_\theta(x, \eta)$ is bounded,
-while $b_\theta(x, \eta)$, because of $F(x, \eta)$, is bounded above but not necessarily below.
-In \citet{kurtz/rodrigues:2011}, $b_\theta$ was bounded above and $c_\theta$ was bounded away from zero,
-so they noted that if $U_a(t) \ge b_\theta/c_\theta$ for some label $a$,
-that line of descent would only move upwards from that time onwards.
-Furthermore, coefficients did not depend on the state of the process (i.e., on $\eta$),
-thus allowing the processes to be jointly and simultaneously constructed
-for all values of $N$, with a pointwise embedding
-of $(\lp^N_t)_{t \ge 0}$ within $(\lp^{M})_{t \ge 0}$ for $b_\theta/c_\theta < N < M$.
-In other words, individuals with levels above $N > b_\theta/c_\theta$ at time $t_0$
-do not affect $(\lp^N_t)_{t \ge t_0}$,
-thus allowing a comparison of the number of lines of descent below level $u_0$
-to a branching process.
-Although we have provided a
-joint construction of $\lp^N$ for all $N$ in Section~\ref{sec: individual lines of descent},
-it does not have this monotonicity:
-for one thing, $b_\theta$ and $c_\theta$ depend on the population process $\eta$
-and so all individuals can affect all other ones (even those with lower levels).
-Furthermore, in the deterministic case $\theta/N$, and hence $c$, converges to zero,
-and so lines of descent with arbitrarily high level may drift back downwards.
-Indeed, this must be the case if the population persists,
-since in the deterministic case there is no branching.
-\end{remark}
-
 We first give a description of the lookdown process $\lp^N$ in terms of the lines of descent
@@
     % in $C_b(\lpmeasures)$ (with respect to uniform convergence on compact subsets).  So, 
-    Since as above the algebra generated by the functions $\lp \mapsto \langle f \lp \rangle$
+    Since as above the algebra generated by the functions $\lp \mapsto \langle f, \lp \rangle$
     is dense in $C_b(\lpmeasures)$,
@@
     \begin{align*}
-        \IP\left\{ \sup_{0 \le t \le T} \langle h_n, \lp_t^N \rangle > K \right\}
+        \IP\left\{ \sup_{0 \le t \le T} \langle h, \lp_t^N \rangle > K \right\}
         &\le

### 2023-05-10 forwards-and-backwards.tex
terence name

@@
 \\
-Terence Tsui 
+Terence Tsui Ho Lung
  &  \\   
@@
 IL is supported by the ANID/Doctorado en el extranjero doctoral scholarship, grant number 2018-72190055.
-TT supported by the EPSRC Centre for Doctoral Training in Mathematics of Random Systems: Analysis, Modelling and Simulation (EP/S023925/1) and the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) under Germany's Excellence Strategy, EXC-2047/1-390685813.
+TTHL supported by the EPSRC Centre for Doctoral Training in Mathematics of Random Systems: Analysis, Modelling and Simulation (EP/S023925/1) and the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) under Germany's Excellence Strategy, EXC-2047/1-390685813.
 

### 2023-05-12 forwards-and-backwards.tex
acknow

@@
 
-\section*{Acknowledgements}
-
-\comment{Need to thank KAVLI, Paris Cit\'e, various funders}
-IL is supported by the ANID/Doctorado en el extranjero doctoral scholarship, grant number 2018-72190055.
-TTHL supported by the EPSRC Centre for Doctoral Training in Mathematics of Random Systems: Analysis, Modelling and Simulation (EP/S023925/1) and the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) under Germany's Excellence Strategy, EXC-2047/1-390685813.
+\paragraph{Acknowledgements:}
+Thanks go to Gilia Patterson for identifying the ``clumping'' phenomenon,
+and to Marcin Bownick and David Levin for useful discussions.
+AME thanks everyone in MAPS at Universit\'e Paris Cit\'e for their hospitality
+during the period in which much of this research took place.
+AME and PLR also thank the Kavli Institute for Theoretical Physics
+for their hospitality and birdwatching opportunities.
+PLR was supported by the NIH NHGRI (grant \#HG011395),
+IL by the ANID/Doctorado en el extranjero doctoral scholarship, grant \#2018-72190055,
+and TTHL by the EPSRC Centre for Doctoral Training in Mathematics of Random Systems: Analysis, Modelling and Simulation (EP/S023925/1)
+the Deutsche Forschungsgemeinschaft under Germany's Excellence Strategy, EXC-2047/1-390685813,
+the Rhodes Trust and St.~John's College, Oxford.
 

### 2023-05-22 forwards-and-backwards.tex
angle bracket process; more citations

@@
 Equations of this form have been studied extensively
-in the context of spatial ecology;
-see for instance \citet{lam2023introduction} and \citet{cantrell2004spatial},
+in the context of spatial ecology
+(see for instance \citet{lam2023introduction} and \citet{cantrell2004spatial})
 and in many other fields;
@@
 on long-term survival of a lattice-based interacting particle system.
+However, we do not study the effect of movement of adults,
+which can additionally affect the limiting equations:
+see for instance \citet{holmes/lewis/banks/veit:1994} or \citet{potts/borger:2023}.
 % MORE DETAILS:
@@
 is a martingale (with respect to the natural filtration), 
-with quadratic variation
+with angle bracket process
     \begin{equation} \label{eqn:prelimit_martingale_variation}
 \begin{aligned} \relax
-[ M^N(f)]_t =& 
+\left\langle M^N(f) \right\rangle_t =& 
 \frac{\theta}{N} \int_{0}^{t}\bigg\{
@@
 \end{definition}
+
+The angle bracket process (or, ``conditional quadratic variation'')
+is the unique previsible process making $(M^N(f)_t)^2 - \langle M^N(f) \rangle_t$ a martingale
+with respect to the natural filtration.
+It differs from the usual quadratic variation
+(usually denoted $[M^N(f)]_t$)
+because the process has jumps;
+for the (continuous) limit the two notions will coincide.
+The use of angle brackets for both integrals and this process
+is unfortunately standard but should not cause confusion,
+since the angle bracket process always carries a subscript for time.
+
 The form of~(\ref{eqn:eta_martingale}) and~(\ref{eqn:prelimit_martingale_variation})
@@
 Since we take bounded $f$,
-for most situations the bound $C_f(1+|f(x)|)$ in condition~\ref{gamma_B_condition} above
+for most situations the bound $C_f(1+|f(x)|)$ in Condition~\ref{gamma_B_condition} above
 can be safely replaced simply by $C_f$;
@@
 in certain situations where we consider a sequence of $f$ with increasing upper bounds.
-We now give two concrete situations in which condition~\ref{gamma_B_condition} is satisfied.
+We now give two concrete situations in which Condition~\ref{gamma_B_condition} is satisfied.
 The proof is in Section~\ref{sec:preliminary_proofs}.
@@
     Assume that Conditions~\ref{def:model_setup} are satisfied,
-    except for condition~\ref{gamma_B_condition}.
+    except for Condition~\ref{gamma_B_condition}.
     If either
@@
 \end{enumerate} 
-    then condition~\ref{gamma_B_condition} is also satisfied.
+    then Condition~\ref{gamma_B_condition} is also satisfied.
 \end{lemma}
@@
     is a martingale (with respect to the natural filtration),
-    with quadratic variation
+    with angle bracket process
     \begin{align} \label{eqn:limiting_mgale_variation}
-        [ M(f) ]_t
+        \left\langle M(f) \right\rangle_t
         =
@@
 
-We now look at the second order term in~(\ref{generator prelimit}).
+We now look at the second order term in~(\ref{generator prelimit}),
+which will converge to the quadratic variation of the limiting process.
 An individual at location $x$ gives birth 
@@
     Now, let $M^{N*}_t(f) = \sup_{0 \le s \le t} M^N_t(f)$,
-    and as before let $[M^N(f)]_t$ be the quadratic variation of $M^N_t(f)$,
-    so that by the Burkholder-Davis-Gundy inequality, there is a $C'$ so that,
-    in the notation of Lemma~\ref{lem:eta_f_bound},
+    and as before let $\langle M^N(f) \rangle_t$ be the angle bracket process of $M^N_t(f)$.
+    The Burkholder-Davis-Gundy inequality says that there is a $K$ for which
+    $\IE\left[ M^{N*}_t(1) \right] \le K \IE[\sqrt{[M^N(1)]_t}]$,
+    where $[M^N(1)]_t$ is the quadratic variation of $M^N(1)$.
+    Furthermore, as discussed by \citet{hernandez/jacka:2022},
+    % for $q \le 1$ there exist universal constants $c_q$ such that
+    % for any local martingale with $M_0=0$, $\IE[[M]^{q}_T] \le c_q \IE[\langle M \rangle^q_T]$
+    the expectation of the quadratic variation of a local martingale
+    is bounded by a (universal) constant multiple of the expectation of its angle bracket process
+    \citep[][Item (4.b'), Table 4.1, p. 162]{barlow/jacka/yor:1986}.
+    Now, since $\sqrt{x} \le 1 + x$,
+    in the notation of Lemma~\ref{lem:eta_f_bound}, there is a $C'$ such that
     \begin{align*}
@@
         &\le
-        C' \IE\left[ \sqrt{[M^N(1)]_t} \right]
-        \\ &\le
-        C'\left( 1 + \IE\left[ [M^N(1)]_t \right] \right)
+        C'\left( 1 + \IE\left[ \left\langle M^N(1) \right\rangle_t \right] \right)
         \\ &=
@@
 where $M_t(\phi)$ is a martingale (with respect to the natural filtration)
-with quadratic variation given by~\eqref{eqn:prelimit_martingale_variation}
+with angle bracket process given by~\eqref{eqn:prelimit_martingale_variation}
 with $f$ replaced by $\phi_s(\cdot)$.
@@
 
+We follow the approach of Lemma~\ref{lem:eta_compact_containment}.
 Consulting~\eqref{eqn:prelimit_martingale_variation},
-and using the approach of Lemma~\ref{lem:limit_mgale},
-the quadratic variation of $\widehat{M}^N(f)$ satisfies
-$ \IE[[\widehat{M}^N_f]_T] \le C (\theta/N) \int_0^T \IE[\langle 1, \eta_s \rangle] ds \le C' \theta/N$
+the angle bracket process of $\widehat{M}^N(f)$ satisfies
+$ \IE[\langle\widehat{M}^N_f\rangle_T] \le C (\theta/N) \int_0^T \IE[\langle 1, \eta_s \rangle] ds \le C' \theta/N$
 for some constants $C$ and $C'$.
-Now, by the Burkholder-Davis-Gundy inequality,
-$\IE[\sup_{0 \le u \le T} |\widehat{M}^N(f)_u|^2] \le C'' \IE[[\widehat{M}^N(f)]_u]$,
+Now, using the Burkholder-Davis-Gundy inequality and \citet{hernandez/jacka:2022},
+$\IE[\sup_{0 \le u \le T} |\widehat{M}^N(f)_u|^2] \le C'' \IE[\langle\widehat{M}^N(f)\rangle_u]$,
 and so using Markov's inequality,
@@
     \leq
-    \limsup_{N\to\infty} \frac{36}{\nu^2} C'' \IE\big[[\widehat{M}^N(f)]_T\big]
+    \limsup_{N\to\infty} \frac{36}{\nu^2} C'' \IE\big[\langle\widehat{M}^N(f)\rangle_T\big]
     \leq
@@
 where $M^f$ is a martingale
-with quadratic variation
+with angle bracket process
 \begin{align} \label{eqn:f_xi_qv}
     \begin{split}
-    [M^f]_t
+    \left\langle M^f \right\rangle_t
     &=
@@
     where $M^{h}_t$ is a martingale
-    with quadratic variation
-    \begin{align*}
-        [M^{h}]_t
+    with angle bracket process
+    \begin{align*}
+        \left\langle M^{h} \right\rangle_t
         &=

### 2023-05-23 forwards-and-backwards.tex
.

@@
 for some constants $C$ and $C'$.
-Now, using the Burkholder-Davis-Gundy inequality and \citet{hernandez/jacka:2022},
+Now, using the Burkholder-Davis-Gundy inequality and \citet{barlow/jacka/yor:1986},
 $\IE[\sup_{0 \le u \le T} |\widehat{M}^N(f)_u|^2] \le C'' \IE[\langle\widehat{M}^N(f)\rangle_u]$,

### 2023-05-30 forwards-and-backwards.tex
add KITP grants

@@
 AME and PLR also thank the Kavli Institute for Theoretical Physics
-for their hospitality and birdwatching opportunities.
+for their hospitality and birdwatching opportunities;
+this research was therefore supported in part by the NSF under grant \#PHY-1748958
+and by the Gordon and Betty Moore Foundation grant \#2919.02.
 PLR was supported by the NIH NHGRI (grant \#HG011395),

### 2023-06-05 forwards-and-backwards.tex
more brackets to fix
.

@@
     \IP\left\{\big|
-        [M^{N}(f)]_{\tau + t} 
-            - [M^{N}(f)]_\tau \big|
+        \langle M^{N}(f) \rangle_{\tau + t} 
+            - \langle M^{N}(f) \rangle_\tau \big|
         > \nu
@@
     &
- \big|   [M^{N}(f)]_{\tau + t} 
-        - [M^{N}(f)]_\tau \big|
+ \big|   \langle M^{N}(f) \rangle_{\tau + t} 
+        - \langle M^{N}(f) \rangle_\tau \big|
     \\ & \qquad =
@@
 
-    Since $\sqrt{x} \le 1 + x$ for $x \ge 0$,
-    the Burkholder-Davis-Gundy inequality
+    As in the proof of Lemma~\ref{lem:eta_compact_containment},
+    the Burkholder-Davis-Gundy inequality,
+    \citet{barlow/jacka/yor:1986},
+    and the fact that $\sqrt{x} \le 1 + x$ for $x \ge 0$
     tells us that there is a $C'$ such that

### 2023-06-05 forwards-and-backwards.tex
.

@@
     & \le
-        C'\left( 1 + \IE\left[ [M^{h}]_T \right] \right)
+        C'\left( 1 + \IE\left[ \langle M^{h} \rangle_T \right] \right)
     \\ & \le
@@
 one version of the Aldous-Rebolledo criteria for tightness of a sequence real-valued processes
-(as it appears in \citet{etheridge2000introduction}):
+(as it appears in Theorem~1.17 of \citet{etheridge2000introduction};
+see also Theorem~4.13 of \citet{jacod/shiryaev:2013}):
 

### 2023-06-15 forwards-and-backwards.tex
EJP format

@@
-\documentclass[12pt]{article}
-\usepackage{fullpage}
-\usepackage{amssymb}
-\usepackage{ntheorem}
-\usepackage{graphics} 
-\usepackage{amsmath}
-\usepackage[color=yellow]{todonotes}
-\usepackage{url}
-\usepackage{xcolor}
-\usepackage{longtable}
-\usepackage[hidelinks]{hyperref}
-\usepackage{bbm}
-
-\usepackage{natbib}
-
-\newenvironment {proof}{{\noindent\bf Proof }}{\hfill $\Box$ \medskip}
-
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{condition}[theorem]{Condition}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{remark}[theorem]{Remark}
-\newtheorem{hypothesis}[theorem]{Hypothesis}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{example}[theorem]{Example}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{notation}[theorem]{Notation}
-\newtheorem{assumptions}[theorem]{Assumptions}
-\newtheorem{terminology}[theorem]{Terminology}
-\newtheorem*{terminology-non}[theorem]{Terminology}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                               %%
+%% This is the sample.tex file for the ejpecp document class.    %%
+%% This file is for ejpecp version 1.0                           %%
+%% Please be sure that you are using the lastest version:        %%
+%% https://www.ctan.org/pkg/ejpecp                               %%
+%%                                                               %%
+%% The ejpecp class works *only* with a pdflatex engine.         %%
+%% You need the ejpecp.cls in your current directory or in any   %%
+%% directory scanned for cls files by your pdflatex engine.      %%
+%%                                                               %%
+%% Manual inclusion of page layout commands is useless.          %%
+%%                                                               %%
+%% Note that any complex file will produce delayed publication!  %%
+%%                                                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                               %%
+%% Journal selection: ECP or EJP.                                %%
+%%                                                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\documentclass[EJP]{ejpecp} % replace ECP by EJP if needed.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                               %%
+%% Please uncomment and adapt to your encoding if needed:        %%
+%%                                                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%\usepackage[T1]{fontenc}
+%\usepackage[utf8]{inputenc}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                               %%
+%% Please add here your own packages (be minimalistic please!):  %%
+%% Please avoid using exotic packages and keep things simple.    %%
+%% It is not necessary to include ams* and graphicx packages     %%
+%% since they are automatically included by the ejpecp class.    %%
+%%                                                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%\usepackage{enumerate}  % uncomment to use this package
+
+% \usepackage{xcolor}
+% \usepackage[hidelinks]{hyperref}
+% \usepackage{bbm}
+% \usepackage{natbib}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                               %%
+%% Shorttitle (please edit and customize for running heading):   %%
+%% Title (please edit and customize):                            %%
+%%                                                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\SHORTTITLE{
+Dynamics and genealogies of locally regulated populations
+}
+
+\TITLE{
+Looking forwards and backwards: dynamics and genealogies of locally regulated populations
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                               %%
+%% Authors (please edit and customize):                          %%
+%%                                                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\AUTHORS{%
+    Alison~M.~Etheridge\footnote{Oxford University, UK}
+    \footnote{\EMAIL{etheridge@stats.ox.ac.uk}}
+  \and
+  Thomas~G.~Kurtz\footnote{University of Wisconsin - Madison, USA:
+    \EMAIL{kurtz@math.wisc.edu}}
+  \and
+  Ian~Letter\footnotemark[1]
+  \and
+  Peter~L.~Ralph\footnote{University of Oregon, USA:
+    \EMAIL{plr@uoregon.edu}}
+  \and
+  Terence~Tsui~Ho~Lung\footnotemark[1]
+}%AUTHORS
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                               %%
+%% Please edit and customize the following items:                %%
+%%                                                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\KEYWORDS{population model ; interacting superprocess ; lookdown construction ; porous medium equation ; reaction-diffusion equation ; travelling waves ; genealogies ; Fisher-KPP equation}
+\AMSSUBJ{60J25 ; 92D10 ; 92D15 ; 92D25 ; 92D40}
+\AMSSUBJSECONDARY{60F05 ; 60G09 ; 60G55 ; 60G57 ; 60H15 ; 60J68}
+
+\SUBMITTED{June 14, 2023} % Edit.
+\ACCEPTED{NA} % Edit.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                               %%
+%% Please uncomment and edit if you have an arXiv ID:            %%
+%%                                                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\ARXIVID{2305.14488}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                               %%
+%% The following items will be set by the Managing Editor.       %%
+%%                                                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\VOLUME{0}
+\YEAR{2020}
+\PAPERNUM{0}
+\DOI{10.1214/YY-TN}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                               %%
+%% Please edit and customize the abstract:                       %%
+%%                                                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\ABSTRACT{
+We introduce a broad class of mechanistic spatial models to describe how spatially heterogeneous populations live, die, and reproduce.
+Individuals are represented by points of a point measure, whose birth and death rates can depend both on spatial position and local population density, defined at a location to be the convolution of the point measure with a suitable non-negative integrable kernel centred on that location.
+We pass to three different scaling limits: an interacting superprocess, a nonlocal partial differential equation (PDE), and a classical PDE.
+The classical PDE is obtained both by a two-step convergence argument, in which we first scale time and population size and pass to the nonlocal PDE, and then scale the kernel that determines local population density; and in the important special case in which the limit is a reaction-diffusion equation, directly by simultaneously scaling the kernel width, timescale and population size in our individual based model.
+
+A novelty of our model is that we explicitly model a juvenile phase.
+The number of juveniles produced by an individual depends on local population density at the location of the parent; these juvenile offspring are thrown off in a (possibly heterogeneous, anisotropic) Gaussian distribution around the location of the parent; they then reach (instant) maturity with a probability that can depend on the local population density at the location at which they land.
+Although we only record mature individuals, a trace of this two-step description remains in our population models, resulting in novel limits in which the spatial dynamics are governed by a nonlinear diffusion.
+
+Using a lookdown representation, we are able to retain information about genealogies relating individuals in our population and, in the case of deterministic limiting models, we use this to deduce the backwards in time motion of the ancestral lineage of an individual sampled from the population.
+We observe that knowing the history of the population density is not enough to determine the motion of ancestral lineages in our model.
+We also investigate (and contrast) the behaviour of lineages for three different deterministic models of a population expanding its range as a travelling wave: the Fisher-KPP equation, the Allen-Cahn equation, and a porous medium equation with logistic growth.
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                               %%
+%% Please add your own macros and environments below:            %%
+%%                                                               %%
+%% If possible, avoid using \def and use instead \newcommand     %%
+%% If possible, avoid defining your own environments, and use    %%
+%% instead the environments already defined by ejpecp:           %%
+%%  assumption, assumptions, claim, condition, conjecture,       %%
+%%  corollary, definition, definitions, example, exercise, fact, %%
+%%  facts, heuristics, hypothesis, hypotheses, lemma, notation,  %%
+%%  notations, problem, proposition, remark, theorem             %%
+%%                                                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \renewcommand{\theequation}{\arabic{section}.\arabic{equation}}
-\def \non{{\nonumber}}
-\def \hat{\widehat}
-\def \tilde{\widetilde}
-\def \bar{\overline}
+\renewcommand{\hat}{\widehat}
+\renewcommand{\tilde}{\widetilde}
+\renewcommand{\bar}{\overline}
 \newcommand{\IP}{\mathbb P}
@@
 
-%%%%%%% notation
 \newcommand{\DG}{\mathcal{B}}  % generator of the dispersal process
@@
 
-\newcommand{\plr}[1]{\todo[inline]{Peter: #1}}
-\newcommand{\comment}[1]{{\color{blue} \it #1}}
-
-\numberwithin{equation}{section}
+\newcommand{\citet}[1]{\cite{#1}}
+\newcommand{\citep}[1]{\cite{#1}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                               %%
+%% No macro definitions below this line please!                  %%
+%%                                                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\title{\large{\bf
-Looking forwards and backwards: dynamics and genealogies of locally regulated populations
-}}
-
-\author{ \begin{small}
-\begin{tabular}{ll}                              
-Alison M. Etheridge 
- & Thomas G. Kurtz \\   
-Department of Statistics & Departments of Mathematics and Statistics\\       
-Oxford University & University of Wisconsin - Madison \\                   
-24-29 St Giles & 480 Lincoln Drive\\                                                         
-Oxford OX1 3LB & Madison, WI  53706-1388\\
-UK & USA \\                        
-etheridg@stats.ox.ac.uk & kurtz@math.wisc.edu     \\
-\url{http://www.stats.ox.ac.uk/~etheridg/} & 
-\url{http://www.math.wisc.edu/~kurtz/}  \\       \\
-\\
-Ian Letter&  Peter L. Ralph 
-\\   
-Department of Statistics & Departments of Mathematics and Biology\\
-Oxford University &University of Oregon\\                   
-24-29 St Giles & Fenton Hall\\
-Oxford OX1 3LB & Eugene, OR 97403-1222\\
-UK & USA \\
-restucci@stats.ox.ac.uk  & plr@oregon.edu \\
-\url{https://www.stats.ox.ac.uk/~restucci/}&
-\url{https://math.uoregon.edu/profile/plr} \\
-\\
-Terence Tsui Ho Lung
- &  \\   
-Department of Statistics & \\
-Oxford University & \\                   
-24-29 St Giles& \\
-Oxford OX1 3LB & \\
-UK & \\
-terence.tsui@sjc.ox.ac.uk &      \\
-\url{https://www.maths.ox.ac.uk/people/terence.tsui}&  \\
-\end{tabular}
-\end{small}}
-
-\date{\today}
-\maketitle
-
-\begin{abstract}
-
-We introduce a broad class of mechanistic spatial models to describe how spatially 
-heterogeneous populations live, die, and reproduce.
-Individuals are represented by points of a point measure,
-whose birth and death rates can depend 
-both on spatial position and local population density, defined at a location
-to be the convolution of the point measure
-with a suitable non-negative integrable kernel
-centred on that location. We pass to three different scaling limits:
-an interacting superprocess, a nonlocal partial differential equation (PDE), 
-and a classical PDE. 
-The classical PDE is obtained both by a two-step convergence argument, in which we 
-first scale time and population size and
-pass to the nonlocal PDE, 
-and then scale the kernel that 
-determines local population density; and 
-in the important special case in which the limit is a 
-reaction-diffusion equation, directly 
-by simultaneously scaling the kernel width,
-timescale and population size in our individual based model.
-
-A novelty of our model is that we explicitly model a juvenile phase.
-The number of juveniles produced by an individual depends
-on local population density at the location of the parent;
-these juvenile offspring are 
-thrown off in a (possibly heterogeneous, anisotropic) Gaussian distribution 
-around the location of the parent; they then reach (instant) maturity with a probability
-that can depend on the local population density
-% (possibly measured through convolution with a different kernel from that used in determining fecundity) 
-at the location at which they land. 
-Although we only record mature individuals, a trace of this two-step description 
-remains in our population models, resulting in novel limits in which the spatial
-dynamics are governed by a nonlinear diffusion.
-
-Using a lookdown representation, we are able to retain information about 
-genealogies relating individuals in our population and, in the case of 
-deterministic limiting models, we use this to deduce 
-the backwards in time motion of the ancestral lineage of an individual
-sampled from the population. We observe that
-knowing the history of the population density is not enough to determine the motion of
-ancestral lineages in our model. We also investigate (and
-contrast) the behaviour of lineages for 
-three different deterministic models of a population expanding its range as a 
-travelling wave: the Fisher-KPP equation, the Allen-Cahn equation, and a porous 
-medium equation with logistic growth.
-
-\vspace{.1in}
-
-\noindent {\bf Key words:}  population model, interacting superprocess, 
-lookdown construction, porous medium equation, 
-reaction-diffusion equation, travelling waves, genealogies,
-Fisher-KPP equation
-
-\vspace{.1in}
-
-\noindent {\bf MSC 20}10 {\bf Subject Classification:}  Primary:  
-%60J25, 92D10, 92D15, 92D25 92D40  
-\\Secondary:   %60F05, 60G09, 60G55, 60G57, 60H15, 60J68
-
-\end{abstract}
-\tableofcontents
-\newpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                               %%
+%% No need for \maketitle.                                       %%
+%%                                                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% \author{ \begin{small}
+% \begin{tabular}{ll}                              
+% Alison M. Etheridge 
+%  & Thomas G. Kurtz \\   
+% Department of Statistics & Departments of Mathematics and Statistics\\       
+% Oxford University & University of Wisconsin - Madison \\                   
+% 24-29 St Giles & 480 Lincoln Drive\\                                                         
+% Oxford OX1 3LB & Madison, WI  53706-1388\\
+% UK & USA \\                        
+% etheridg@stats.ox.ac.uk & kurtz@math.wisc.edu     \\
+% \url{http://www.stats.ox.ac.uk/~etheridg/} & 
+% \url{http://www.math.wisc.edu/~kurtz/}  \\       \\
+% \\
+% Ian Letter&  Peter L. Ralph 
+% \\   
+% Department of Statistics & Departments of Mathematics and Biology\\
+% Oxford University &University of Oregon\\                   
+% 24-29 St Giles & Fenton Hall\\
+% Oxford OX1 3LB & Eugene, OR 97403-1222\\
+% UK & USA \\
+% restucci@stats.ox.ac.uk  & plr@oregon.edu \\
+% \url{https://www.stats.ox.ac.uk/~restucci/}&
+% \url{https://math.uoregon.edu/profile/plr} \\
+% \\
+% Terence Tsui Ho Lung
+%  &  \\   
+% Department of Statistics & \\
+% Oxford University & \\                   
+% 24-29 St Giles& \\
+% Oxford OX1 3LB & \\
+% UK & \\
+% terence.tsui@sjc.ox.ac.uk &      \\
+% \url{https://www.maths.ox.ac.uk/people/terence.tsui}&  \\
+% \end{tabular}
+% \end{small}}
 
@@
 individuals in a sample from the population, and these have been shaped 
-by its history \citep[see e.g.,][]{neigel1993application,kelleher2019inferring}.
+by its history (see e.g., \citep{neigel1993application,kelleher2019inferring}).
 It is therefore of interest to establish information about the distribution of genealogical trees 
@@
 but these are provided for visualization and we do not embark on numerical study.
-
-\paragraph{Acknowledgements:}
-Thanks go to Gilia Patterson for identifying the ``clumping'' phenomenon,
-and to Marcin Bownick and David Levin for useful discussions.
-AME thanks everyone in MAPS at Universit\'e Paris Cit\'e for their hospitality
-during the period in which much of this research took place.
-AME and PLR also thank the Kavli Institute for Theoretical Physics
-for their hospitality and birdwatching opportunities;
-this research was therefore supported in part by the NSF under grant \#PHY-1748958
-and by the Gordon and Betty Moore Foundation grant \#2919.02.
-PLR was supported by the NIH NHGRI (grant \#HG011395),
-IL by the ANID/Doctorado en el extranjero doctoral scholarship, grant \#2018-72190055,
-and TTHL by the EPSRC Centre for Doctoral Training in Mathematics of Random Systems: Analysis, Modelling and Simulation (EP/S023925/1)
-the Deutsche Forschungsgemeinschaft under Germany's Excellence Strategy, EXC-2047/1-390685813,
-the Rhodes Trust and St.~John's College, Oxford.
 
@@
 although this restriction could be easily lifted
-\citep[as in Section 3.4 of][]{etheridge/kurtz:2019}.
+(as in Section 3.4 of \cite{etheridge/kurtz:2019}).
 Furthermore, individuals do not move during their lifetime,
@@
 
-\begin{terminology*}
+\begin{remark}
 In our prelimiting model,
@@
 respect to Lebesgue measure; indeed in the prelimit it is certainly not.
-\end{terminology*}
+\end{remark}
 
@@
         % \includegraphics{figures/ex1b/fkpp_123.density.3.0}
-        \includegraphics{figures/fig1a}
-        \includegraphics{figures/fig1b}
+        \includegraphics[width=2.5in]{figures/fig1a}
+        \includegraphics[width=2.5in]{figures/fig1b}
     \end{center}
@@
         % \includegraphics[width=0.7\textwidth]{figures/ex2b/pme_1234.steps}
-        \includegraphics[width=0.7\textwidth]{figures/fig2a}
-        \includegraphics[width=0.7\textwidth]{figures/fig2b}
+        \includegraphics[width=4.5in]{figures/fig2a}
+        \includegraphics[width=4.5in]{figures/fig2b}
     \end{center}
@@
         % \includegraphics[width=0.45\textwidth]{figures/clumpy_1d/clumpy_123.steps}
-        \includegraphics[width=0.45\textwidth]{figures/fig3a}
-        \includegraphics[width=0.45\textwidth]{figures/fig3b}
+        \includegraphics[width=2.5in]{figures/fig3a}
+        \includegraphics[width=2.5in]{figures/fig3b}
     \end{center}
@@
     is bounded by a (universal) constant multiple of the expectation of its angle bracket process
-    \citep[][Item (4.b'), Table 4.1, p. 162]{barlow/jacka/yor:1986}.
+    (\cite{barlow/jacka/yor:1986} Item (4.b'), Table 4.1, p. 162).
     Now, since $\sqrt{x} \le 1 + x$,
@@
 
-\bibliographystyle{plainnat}
-\bibliography{refs}
+% \bibliographystyle{amsplain}
+% \bibliography{refs}
+
+% add below the content of your .bbl file produced by bibtex.
+
+\providecommand{\bysame}{\leavevmode\hbox to3em{\hrulefill}\thinspace}
+\providecommand{\MR}{\relax\ifhmode\unskip\space\fi MR }
+% \MRhref is called by the amsart/book/proc definition of \MR.
+\providecommand{\MRhref}[2]{%
+  \href{http://www.ams.org/mathscinet-getitem?mr=#1}{#2}
+}
+\providecommand{\href}[2]{#2}
+\begin{thebibliography}{10}
+
+\bibitem{barlow/jacka/yor:1986}
+M.~T. Barlow, S.~D. Jacka, and M.~Yor, \emph{Inequalities for a pair of
+  processes stopped at a random time}, Proceedings of the London Mathematical
+  Society \textbf{s3-52} (1986), no.~1, 142--172.
+
+\bibitem{barton:1979}
+N~H Barton, \emph{The dynamics of hybrid zones}, Heredity \textbf{43} (1979),
+  no.~3, 341--359.
+
+\bibitem{berestycki2009nonlocal}
+Henri Berestycki, Gregoire Nadin, Benoit Perthame, and Lenya Ryzhik, \emph{The
+  non-local fisher-kpp equation: travelling waves and steady states},
+  Nonlinearity \textbf{22} (2009), no.~12, 2813--2844.
+
+\bibitem{birzu/hallatschek/korolev:2017}
+Gabriel Birzu, Oskar Hallatschek, and Kirill~S. Korolev, \emph{Fluctuations
+  uncover a distinct class of traveling waves}, Proc. Natl. Acad. Sci. (USA)
+  \textbf{115} (2018), no.~16, 3645--3654.
+
+\bibitem{birzu/hallatschek/korolev:2021}
+Gabriel Birzu, Oskar Hallatschek, and Kirill~S Korolev, \emph{Genealogical
+  structure changes as range expansions transition from pushed to pulled},
+  Proc. Natl. Acad. Sci. (USA) \textbf{118} (2021), no.~34, e2026746118.
+
+\bibitem{biswas/etheridge/klimek:2018}
+Niloy Biswas, Alison Etheridge, and Aleksander Klimek, \emph{The spatial
+  {Lambda}-{Fleming}-{Viot} process with fluctuating selection}, Electron. J.
+  Probab. \textbf{26} (2021), 1 -- 51.
+
+\bibitem{bolker/pacala:1997}
+B~M Bolker and S~W Pacala, \emph{Using moment equations to understand
+  stochastically driven spatial pattern formation in ecological systems},
+  Theor. Pop. Biol. \textbf{52} (1997), no.~3, 179--197.
+
+\bibitem{bolker/pacala:1999}
+\bysame, \emph{Spatial moment equations for plant competition: {Understanding}
+  spatial strategies and the advantages of short dispersal}, American
+  Naturalist \textbf{153} (1999), no.~6, 575--602.
+
+\bibitem{bramson:1983}
+M~Bramson, \emph{{Convergence of solutions of the Kolmogorov equation to
+  travelling waves}}, Mem. Amer. Math. Soc. \textbf{44} (1983), no.~285.
+
+\bibitem{britton1990spatial}
+N.~F. Britton, \emph{Spatial structures and periodic travelling waves in an
+  integro-differential reaction-diffusion population model}, SIAM Journal on
+  Applied Mathematics \textbf{50} (1990), no.~6, 1663--1688.
+
+\bibitem{brunet/derrida/mueller/munier:2006}
+E~Brunet, B~Derrida, A~H Mueller, and S~Munier, \emph{Noisy travelling waves:
+  effect of selection on genealogies}, Europhys. Lett. \textbf{76} (2006),
+  1--7.
+
+\bibitem{cantrell2004spatial}
+Robert~Stephen Cantrell and Chris Cosner, \emph{Spatial ecology via
+  reaction-diffusion equations}, John Wiley \& Sons, 2004.
+
+\bibitem{cohen/golding/kozlovsky/benjacob/ron:1999}
+I~Cohen, I~Golding, Y~Kozlovsky, E~Ben-Jacob, and I~Ron, \emph{Continuous and
+  discrete models of cooperation in complex bacterial colonies}, Fractals
+  \textbf{7} (1999), 235--247.
+
+\bibitem{dawson:1993}
+D~A Dawson, \emph{{Measure-valued Markov processes}}, \'Ecole d'\'et\'e de
+  probabilit\'es de Saint Flour, vol. 1541, Springer-Verlag, 1993.
+
+\bibitem{demasi/ferrari/lebowitz:1986}
+A.~De~Masi, P.~A. Ferrari, and J.~L. Lebowitz, \emph{Reaction-diffusion
+  equations for interacting particle system}, J. Stat. Phys. \textbf{44}
+  (1986), 589--644.
+
+\bibitem{demasi/presutti:1991}
+Anna DeMasi and Errico Presutti, \emph{Mathematical methods for hydrodynamic
+  limits}, Springer, 2006.
+
+\bibitem{donnelly/kurtz:1996}
+P~J Donnelly and T~G Kurtz, \emph{{A countable representation of the
+  Fleming-Viot measure-valued diffusion}}, Ann. Probab. \textbf{24} (1996),
+  698--742.
+
+\bibitem{donnelly/kurtz:1999}
+\bysame, \emph{{Particle representations for measure-valued population
+  models}}, Ann. Probab. \textbf{27} (1999), 166--205.
+
+\bibitem{durrett/fan:2016}
+R~Durrett and W-T Fan, \emph{Genealogies in expanding populations}, Ann. Appl.
+  Probab. \textbf{26} (2016), 3456--3490.
+
+\bibitem{etheridge/gooding/letter:2022}
+A~Etheridge, M~Gooding, and I~Letter, \emph{{On the effects of a wide opening
+  in the domain of the (stochastic) Allen-Cahn equation and the motion of
+  hyrbid zones}}, Electron. J. Probab. \textbf{27} (2022), 1--52.
+
+\bibitem{etheridge/penington:2022}
+A.~Etheridge and S.~Penington, \emph{Genealogies in bistable waves}, Electron.
+  J. Probab. \textbf{27} (2022), no.~121, 1--99.
+
+\bibitem{etheridge:2004}
+A~M Etheridge, \emph{Survival and extinction in a locally regulated
+  population}, Ann. Appl. Probab. \textbf{14} (2004), no.~1, 188--214.
+
+\bibitem{etheridge2000introduction}
+Alison Etheridge, \emph{An introduction to superprocesses}, no.~20, American
+  Mathematical Society, 2000.
+
+\bibitem{etheridge/kurtz:2019}
+Alison~M. Etheridge and Thomas~G. Kurtz, \emph{{Genealogical constructions of
+  population models}}, Ann. Probab. \textbf{47} (2019), no.~4, 1827--1910.
+
+\bibitem{ethier/kurtz:1986}
+Stewart~N. Ethier and Thomas~G. Kurtz, \emph{Markov processes --
+  characterization and convergence}, Wiley Series in Probability and
+  Mathematical Statistics: Probability and Mathematical Statistics, John Wiley
+  \& Sons Inc., New York, 1986. \MR{MR838085 (88a:60130)}
+
+\bibitem{fife1977approach}
+Paul~C. Fife and J.~B. McLeod, \emph{The approach of solutions of nonlinear
+  diffusion equations to travelling front solutions}, Archive for Rational
+  Mechanics and Analysis \textbf{65} (1977), no.~4, 335--361.
+
+\bibitem{flandoli/huang:2021}
+Franco Flandoli and Ruojun Huang, \emph{The {KPP} equation as a scaling limit
+  of locally interacting {Brownian} particles}, J. Differential Equations
+  \textbf{303} (2021), 608--644.
+
+\bibitem{flandoli/leimbach/olivera:2019}
+Franco Flandoli, Matti Leimbach, and Christian Olivera, \emph{Uniform
+  convergence of proliferating particles to the fkpp equation}, Journal of
+  Mathematical Analysis and Applications \textbf{473} (2019), no.~1, 27--52.
+
+\bibitem{ghosh2022emergent}
+Olivia~M. Ghosh and Benjamin~H. Good, \emph{Emergent evolutionary forces in
+  spatial models of microbial growth in the human gut microbiota}, Proc. Natl.
+  Acad. Sci. (USA) \textbf{119} (2022), no.~28, e2114931119.
+
+\bibitem{gilding/kersner:2005}
+B~H Gilding and R~Kersner, \emph{A {Fisher}/{KPP}-type equation with density
+  dependent diffusion and convection: travelling wave solutions}, J. Phys. A:
+  Math. Gen. \textbf{38} (2005), 337--3379.
+
+\bibitem{gooding:2018}
+M.~Gooding, \emph{Long term behaviour of spatial population models with
+  heterozygous or asymmetric homozygous selection}, DPhil thesis, Oxford
+  University, 2018.
+
+\bibitem{hallatschek/nelson:2008}
+O~Hallatschek and D~Nelson, \emph{Gene surfing in expanding populations},
+  Theor. Pop. Biol. \textbf{73} (2008), 158--170.
+
+\bibitem{haller_slim_2019}
+Benjamin~C. Haller and Philipp~W. Messer, \emph{{SLiM} 3: {Forward} genetic
+  simulations beyond the {Wright}-{Fisher} model}, Mol. Biol. Evol. \textbf{36}
+  (2019), no.~3, 632--637.
+
+\bibitem{haller2022evolutionary}
+\bysame, \emph{{SLiM}: An evolutionary simulation framework}, 2022.
+
+\bibitem{hernandezgarcia2004clustering}
+Emilio Hern\'andez-Garc\'{\i}a and Crist\'obal L\'opez, \emph{Clustering,
+  advection, and patterns in a model of population dynamics with
+  neighborhood-dependent rates}, Phys. Rev. E \textbf{70} (2004), no.~1,
+  016216.
+
+\bibitem{hernandez/jacka:2022}
+Ma.~Elena Hern{\'{a}}ndez-Hern{\'{a}}ndez and Saul~D. Jacka, \emph{A
+  generalisation of the burkholder-davis-gundy inequalities}, Electronic
+  Communications in Probability \textbf{27} (2022), no.~none.
+
+\bibitem{holmes/lewis/banks/veit:1994}
+E.~E. Holmes, M.~A. Lewis, J.~E. Banks, and R.~R. Veit, \emph{Partial
+  differential equations in ecology: Spatial interactions and population
+  dynamics}, Ecology \textbf{75} (1994), no.~1, 17--29.
+
+\bibitem{jacod/shiryaev:2013}
+Jean Jacod and Albert Shiryaev, \emph{Limit theorems for stochastic processes},
+  vol. 288, Springer Science \& Business Media, 2013.
+
+\bibitem{kallenberg1997foundations}
+Olav Kallenberg, \emph{Foundations of modern probability}, vol.~2, Springer,
+  1997.
+
+\bibitem{kamin/rosenau:2004}
+S~Kamin and P~Rosenau, \emph{Emergence of waves in a nonlinear
+  convection-reaction-diffusion equation}, Adv. Nonlinear Stud. \textbf{4}
+  (2004), 251--272.
+
+\bibitem{kelleher2019inferring}
+Jerome Kelleher, Yan Wong, Anthony~W. Wohns, Chaimaa Fadil, Patrick~K. Albers,
+  and Gil McVean, \emph{Inferring whole-genome histories in large population
+  datasets}, Nature Genetics \textbf{51} (2019), no.~9, 1330--1338.
+
+\bibitem{kolmogorov/petrovsky/piscounov:1937}
+A~Kolomogorov, I~Petrovsky, and N~Piscounov, \emph{{\'Etude de l'equation de la
+  diffusion avec croissance de la quantit\'e de mati\`ere et son application
+  \`a un probl\`eme biologique}}, Moscow Univ. Math. Bull. \textbf{1} (1937),
+  1--25.
+
+\bibitem{kurtz/rodrigues:2011}
+Thomas~G. Kurtz and Eliane~R. Rodrigues, \emph{Poisson representations of
+  branching {Markov} and measure-valued branching processes}, Ann. Probab.
+  \textbf{39} (2011), no.~3, 939--984.
+
+\bibitem{kurtz/xiong:1999}
+Thomas~G. Kurtz and Jie Xiong, \emph{Particle representations for a class of
+  nonlinear spdes}, Stoch. Proc. Appl. \textbf{83} (1999), no.~1, 103--126.
+
+\bibitem{lam2023introduction}
+King-Yeung Lam and Yuan Lou, \emph{Introduction to reaction-diffusion
+  equations: Theory and applications to spatial ecology and evolutionary
+  biology}, Springer International Publishing AG, 2023.
+
+\bibitem{li/buenzli/simpson:2022}
+Y~Li, P~Buenzli, and M~Simpson, \emph{Interpreting how nonlinear diffusion
+  affects the fate of bistable populations using a discrete modelling
+  framework}, Proc. Roy. Soc. A \textbf{478} (2022).
+
+\bibitem{lions/mas-gallic:2001}
+P-L Lions and S~Mas-Gallic, \emph{{Une m\'ethode particulaire d\'eterministe
+  pour des \'equations diffusives non lin\'eaires}}, C. R. Acad. Sci. Paris
+  \textbf{332, S\'erie I} (2001), 369--376.
+
+\bibitem{neigel1993application}
+J~E Neigel and J~C Avise, \emph{Application of a random walk model to
+  geographic distributions of animal mitochondrial {DNA} variation}, Genetics
+  \textbf{135} (1993), no.~4, 1209--1220.
+
+\bibitem{oelschlaeger:1985}
+Karl Oelschl{\"a}ger, \emph{A law of large numbers for moderately interacting
+  diffusion processes}, Z. Wahrsch. verw. Geb. \textbf{69} (1985), no.~2,
+  279--322.
+
+\bibitem{oelschlaeger:1989}
+\bysame, \emph{On the derivation of reaction-diffusion equations as limit
+  dynamics of systems of moderately interacting stochastic processes}, Prob.
+  Theor. Rel. Fields \textbf{82} (1989), no.~4, 565--586.
+
+\bibitem{penington:2017}
+S~Penington, \emph{{The spreading speed of solutions of the non-local
+  Fisher-KPP equation}}, J. Functional Anal. \textbf{275} (2017), no.~12,
+  3259--3302.
+
+\bibitem{perkins:1992}
+E~A Perkins, \emph{{Measure-valued branching diffusions with spatial
+  interactions}}, Prob. Th. Rel. Fields \textbf{94} (1992), 189--245.
+
+\bibitem{potts/borger:2023}
+Jonathan~R. Potts and Luca Börger, \emph{How to scale up from animal movement
+  decisions to spatiotemporal patterns: An approach via step selection},
+  Journal of Animal Ecology \textbf{92} (2023), no.~1, 16--29.
+
+\bibitem{rebolledo:1980}
+R~Rebolledo, \emph{{Sur l'existence de solutions \'a certains probl\`emes de
+  semimartingales}}, C. R. Acad. Sci. Paris \textbf{290} (1980).
+
+\bibitem{sasaki1997clumped}
+Akira Sasaki, \emph{Clumped distribution by neighbourhood competition}, J.
+  Theor. Biol. \textbf{186} (1997), no.~4, 415--430.
+
+\bibitem{sherratt:2010}
+J~A Sherratt, \emph{On the form of smooth-front travelling waves in a
+  reaction-diffusion equation with degenerate nonlinear diffusion}, Math.
+  Model. Nat. Phenom. \textbf{5} (2010), no.~5, 64--79.
+
+\bibitem{sheu:1991}
+S~J Sheu, \emph{{Some estimates of the transition density of a nondegenerate
+  diffusion Markov process}}, Ann. Probab. \textbf{19} (1991), no.~2, 538--561.
+
+\bibitem{young2001reproductive}
+W.~R. Young, A.~J. Roberts, and G.~Stuhne, \emph{Reproductive pair correlations
+  and the clustering of organisms}, Nature \textbf{412} (2001), no.~6844,
+  328--331.
+
+\end{thebibliography}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                               %%
+%% You may add acknowledgments (optional).                       %%
+%%                                                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{acks}
+Thanks go to Gilia Patterson for identifying the ``clumping'' phenomenon,
+and to Marcin Bownick and David Levin for useful discussions.
+AME thanks everyone in MAPS at Universit\'e Paris Cit\'e for their hospitality
+during the period in which much of this research took place.
+AME and PLR also thank the Kavli Institute for Theoretical Physics
+for their hospitality and birdwatching opportunities;
+this research was therefore supported in part by the NSF under grant \#PHY-1748958
+and by the Gordon and Betty Moore Foundation grant \#2919.02.
+PLR was supported by the NIH NHGRI (grant \#HG011395),
+IL by the ANID/Doctorado en el extranjero doctoral scholarship, grant \#2018-72190055,
+and TTHL by the EPSRC Centre for Doctoral Training in Mathematics of Random Systems: Analysis, Modelling and Simulation (EP/S023925/1)
+the Deutsche Forschungsgemeinschaft under Germany's Excellence Strategy, EXC-2047/1-390685813,
+the Rhodes Trust and St.~John's College, Oxford.
+\end{acks}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                               %%
+%% You have reached the end of your document.                    %%
+%%                                                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \end{document}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                               %%
+%% You may put below funny messages to the Managing Editor:      %%
+%%                                                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%% EOF

### 2023-06-26 forwards-and-backwards.tex
rv not fitness

@@
 %     but I've checked where it comes from pretty carefully, and don't see anything wrong.}
-Long-term fitness of an individual
+The long-term reproductive value of an individual
 is proportional to the fraction of lineages from the distant future that pass through the individual,
-and hence the total long-term fitness at a location is proportional to
+and hence the total long-term reproductive value at a location is proportional to
 the stationary distribution of $Y$ there, if it exists.
 Therefore,
-if $\pi$ is integrable then the per-capita long-term fitness of an individual at $x$
+if $\pi$ is integrable then the per-capita long-term reproductive value of an individual at $x$
 is proportional to $\pi(x) / \varphi(x)$.
@@
 As a result, lineages in the second model spend more time in areas with $\lambda < 1$,
-i.e., those areas have higher reproductive value, %long-term fitness
+i.e., those areas have higher reproductive value,
 something that is, in principle, discernible from genetic data

### 2023-12-06 review-responses.tex
put in reviewer responses

%%%%%%
%%
%%  Don't reorder the reviewer points; that'll mess up the automatic referencing!
%%
%%%%%

\begin{minipage}[b]{2.5in}
  Resubmission Cover Letter \\
  {\it Theoretical Population Biology}
\end{minipage}
\hfill
\begin{minipage}[b]{2.5in}
    Peter Ralph \\
  \today
\end{minipage}

\vskip 2em

\noindent
{\bf To the Editor(s) -- }

\vskip 1em

We are writing to submit a revised version of our manuscript,
ETCETERA

\vskip 2em

\noindent \hspace{4em}
\begin{minipage}{3in}
\noindent
{\bf Sincerely,}

\vskip 2em

{\bf 
Peter Ralph
}\\
on behalf of \\
{\bf 
Alison Etheridge,
Tom Kurtz,
Ian Letter,
and Terence Tsui Ho Lung.
}\\
\end{minipage}

\vskip 4em

\pagebreak

%%%%%%%%%%%%%%
\section*{AE comments:}

%%%%%%%%%%%%%%
\reviewersection{1}

\begin{quote}
The authors introduced a class of spatial population models in which individuals have locations
in the continuum space $\IR^d$. The population dynamics is controlled by three quantities: birth,
establishment and death, each of which can depend on the spatial location and local population
density. For a fixed time $t$, the population can be represented by a point measure $\eta_t^N$ in which
each individual is assigned a mass $1/N$, where $N$ is a parameter such that initially there are $O(N)$
individuals per unit volume in $\IR^d$. The population dynamics is represented by a continuous-time
Markov process $(\eta_t^N)_{t\ge0}$. The key feature of this model is that it distinguishes between juveniles
and adults. The authors obtained three different scaling limits for the model $(\eta_t^N)_{t\ge0}$ as $N \to \infty$,
which are super-processes, non-local differential equation and reaction-diffusion type PDE. The
author also obtained a description of the dynamics of a single lineage as $N \to \infty$, when the
limiting population dynamics is deterministic.

A main contribution of this paper is the rigorous derivation of lineage dynamics through the
lookdown construction. The convergence of the population dynamics to super-processes, non-
local PDE and PDE are also significant, as they inform us of not only the limiting object that are
expected to be robust against model perturbation, but also of the corresponding scaling regimes
and parameter combinations for model reduction. The one-step convergence presents a usual technical
challenge about identifying the limit. The authors overcame the challenge masterfully by
establishing continuity estimates that guarantee good agreement for the nonlinear terms between
the limiting PDE and the stochastic model, under high mixing rate and a high density assumption.
Overall, this is a very high quality paper that contains many interesting and novel results to merit
publication in EJP, after minor revision.
\end{quote}

Thanks ETCETERA

\subsection*{Major comments}

\begin{point}{\revref}
The first paragraph seems sloppy. For example, this expression [for $\mu_\theta(x)$] is non-negative for
what range of values for $(x, \eta)$? Why ``anyway true for sufficiently large $\theta$''? Perhaps this
assumption should be labeled and called upon whenever is it being referred to.
\end{point}

\reply{
}

\begin{point}{\revref}
Definition \ref{def:lineage_generator}, Proposition 2.23: I think these may need to be rewritten/rephrased. Up
to Proposition \ref{thm:lineages}, it is not clear what ``that individual'' is in the limiting model. Therefore,
it is not clear what $L_s$ is. While the definition of the process $L^N$ maybe clear, what is the
precise definition of $L_s$ ? I think these need to be defined through the finite-$N$ models. It may
be good to explain why the process $L$ is Markovian, or at least point out that it is Markovian,
before talking about semigroup. Probably Section \ref{sec:lineage_motion} will need to be modified accordingly.
\end{point}

\reply{
}

\begin{point}{\revref}
The two conditions in equation \eqref{conditions for one step} are crucial for the one-step convergence.
It would be great to mention exactly where each of them are used in Section \ref{subsec:one step convergence proof}.
A brief explanation about these conditions would also be nice. For example, it seems the first (high
migration/mixing rate) condition in \eqref{conditions for one step},
but not the second (high density) condition, is used
to guarantees that $\psi_t^{\epsilon,x}$ is close to a heat kernel?
\end{point}

\reply{
}

\subsection*{Minor comments}

\begin{point}{\revref}
\eqref{eqn:mu_defn}: The authors mentioned ``define the death rate'' and ``where this equation defines F'',
which is confusing. What is being defined here? Please clarify. It seems to me that one has
to first choose $F$, then define $µ_\theta(x)$ as in \eqref{eqn:mu_defn}.
\end{point}

\reply{
}

\begin{point}{\revref}
% P7, paragraph after Remark 2.3:
``and once there establishes...'' It maybe better to split this
long sentence into two complete sentences.
\end{point}

\reply{
}

\begin{point}{\revref}
% P7, paragraph after Remark 2.3:
$\meanq(x)$ and $\covq(x)$ did not appear before. Perhaps mention they
are given/chosen, or simply delete them here, and mention them in Definition \ref{def:dispersal_generator}.
\end{point}

\reply{
}

\begin{point}{\revref}
Remark \ref{ancestral lineages: first guess}
Why use $m$ in the superscript of $q_\theta^m(x, \eta, dy)$?
\end{point}

\reply{
}

\begin{point}{}
Assumptions \ref{def:model_setup}: Should it be ``Assumption 2.8'' instead? Also, $\alpha$ in condition 1 was
used in $\alpha = lim_{N \to \infty} \theta(N)/N$ on Page 8, Figure 1, etc.
\end{point}

\reply{
}

\begin{point}{\revref}
% P9 last line:
    Should the ``$C$'' on the right hand side of the equal sign [in the equation for $C_f$] be deleted ?
\end{point}

\reply{
}

\begin{point}{\revref}
% P10 paragraph below Lemma 2.9:
    Why ``no longer suffices'', and why this is true? . Please
explain. I don’t seem to find this explained in any remark before this.
\end{point}

\reply{
}

\begin{point}{}
Figure 1: What is $N$, the time and other parameters (e.g. $\rho_r$ , $\rho_\gamma$) in the simulations? Same
for other figures. Please at least specify the range of values.
\end{point}

\reply{
}

\begin{point}{\revref}
% P12 paragraph after Corollary 2.11:
A more precise reference, or explanation for why
uniqueness holds for this special case would be helpful, as the references you ave are all
quite extensive.
\end{point}

\reply{
}

\begin{point}{}
Proposition \ref{nonlocalPME to PME}:
    It seems the constant $C$ is not needed. Perhaps just say the supremum
of the first displayed expression over $\epsilon$ finite?
\end{point}

\reply{
}

\begin{point}{}
Remark \ref{remark_on_nonlocal_to_local}: Can you explain a bit more why it will be necessary to retain averaging of r?
\end{point}

\reply{
}

\begin{point}{\revref}
% P16: Second paragraph:
The notation $L_t$ seems to first appear here and was not yet defined.
\end{point}

\reply{
    (Note: they said ``P16: Second paragraph''; I think they just missed it on the previous page.)
}

\begin{point}{}
% P19-20:
    The equations for the lineage dynamics for the three examples [i.e., Fisher-KPP \revref, Allen-Cahn, and Porous Medium] are interesting.
Which is/are new in this paper, and which was/were known before (and related references)?
\end{point}

\reply{
}

\begin{point}{}
This maybe out of the scope of this paper, but it is related. As the authors pointed out, two
lineages probably will not coalesce in the limiting model. However, they will coalesce in
the finite-$N$ model, though it may take a very long time. I wonder if the authors have a
feeling about whether the description of the lineage dynamics in the limit still be a good
approximation for that of the finite model for such a long time.
\end{point}

\reply{
}

\begin{point}{}
The subtitle of section \ref{sec:nonunique_lineage} does not match the actual content in that section. Please
update the subtitle. Also, can you give a reference for the claim in the last sentence in this
section \revref?
\end{point}

\reply{
}

\begin{point}{\revref}
specify ``this process'' in the line below the first displayed equation in
Section 5.1.
\end{point}

\reply{
}

\begin{point}{\revref}
Paragraph starting with ``Levels never cross below 0'': Should it be instead ``Levels never
go above $N$''? If so, what particles are regarded as dead? Perhaps those exit the interval
$[0, N]$? Note that equation \eqref{eqn:dot_u} suggests that levels can now go above $N$.
\end{point}

\reply{
}

\begin{point}{\revref}
``Recall from equation~\eqref{eqn:mu_defn}''
does not seem correct, as there is a max in \eqref{eqn:mu_defn}. Please
correct this.
\end{point}

\reply{
}

\begin{point}{\revref}
Please give a precise reference/explanation to why uniqueness holds for the martingale problem for finite $N$.
\end{point}

\reply{
}

\begin{point}{\revref}
% P32 third line in Section 5.3:
    Pointwise in time?
\end{point}

\reply{
}

\begin{point}{\revref}
Proposition \ref{prop:limiting_construction}: In ``For any solution to the equation above'', what is a ``solution''? Is it
a solution for all time? Also, be specific to ``the equations above'' by labeling and referring
to the precise equations including the unlabeled displayed equation below \eqref{eqn:limiting_construction}.
\end{point}

\reply{
}

\begin{point}{\revref}
The word ``Proof'' is missing in ``Proof of Proposition 5.6''. This word is also
missing in other places in Sections 6-8.
\end{point}

\reply{
}

\begin{point}{}
``Proof of Proposition \ref{prop:limiting_construction}'': Do you also need the unlabeled displayed equation below
\eqref{eqn:limiting_construction}? The solution is for all time.
\end{point}

\reply{
}

\begin{point}{\revref}
Be specific about ``these results'' in ``Proof of the remainder of these results...'' Also, at the
very beginning of Remark \ref{remark_on_branching}, Be specific about what ``The process'' is.
\end{point}

\reply{
}

\begin{point}{\revref}
``Condition 1'' here is that for Lemma 2.9, not that for Assumptions 2.8. Please specify.
\end{point}

\reply{
}

\begin{point}{\revref}
Perhaps give a reference to the ``familiar pattern''.
\end{point}

\reply{
}

\begin{point}{\revref}
% P40 first displayed equation:
Mention $M_t$ is a martingale for all such test functions.
\end{point}

\reply{
}

\begin{point}{\revref}
%    P48:
    The notation $\mathcal{O}(\epsilon)$ seems to first appear here. Please explain its meaning. Do they
depend on x?
\end{point}

\reply{
}

\begin{point}{\revref}
% P54: near the bottom:
    Can you be more specific what in paper \citet{barlow/jacka/yor:1986} is being used here?
\end{point}

\reply{
}

\begin{point}{\revref}
% P60:
The notation $\mathcal{O}(\delta)$ seems to first appear here. Please explain its meaning. Do they
depend on x?
\end{point}

\reply{
}

\begin{point}{\revref}
% P65: Remark 8.1:
measure-values processes $\to$ measure-valued processes
\end{point}

\reply{
}

\begin{point}{}
Section \ref{sec:lineages_proof}8.2 may nned to be modified also based on the second point in ``Major
comments'' above.
\end{point}

\reply{
}

### 2023-12-06 forwards-and-backwards.tex
put in reviewer responses

@@
 \newcommand{\citep}[1]{\cite{#1}}
+
+\newif\ifsubmission
+\submissiontrue
+% \submissionfalse
+\ifsubmission
+    % % stuff for submission
+    \usepackage{lineno}
+    % allow line numbers around math environments
+    % from https://tex.stackexchange.com/questions/43648/why-doesnt-lineno-number-a-paragraph-when-it-is-followed-by-an-align-equation
+        \newcommand*\patchAmsMathEnvironmentForLineno[1]{%
+          \expandafter\let\csname old#1\expandafter\endcsname\csname #1\endcsname
+          \expandafter\let\csname oldend#1\expandafter\endcsname\csname end#1\endcsname
+          \renewenvironment{#1}%
+             {\linenomath\csname old#1\endcsname}%
+             {\csname oldend#1\endcsname\endlinenomath}}% 
+        \newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
+          \patchAmsMathEnvironmentForLineno{#1}%
+          \patchAmsMathEnvironmentForLineno{#1*}}%
+        \AtBeginDocument{%
+        \patchBothAmsMathEnvironmentsForLineno{equation}%
+        \patchBothAmsMathEnvironmentsForLineno{align}%
+        \patchBothAmsMathEnvironmentsForLineno{flalign}%
+        \patchBothAmsMathEnvironmentsForLineno{alignat}%
+        \patchBothAmsMathEnvironmentsForLineno{gather}%
+        \patchBothAmsMathEnvironmentsForLineno{multline}%
+        }
+\else
+    % for the nice version
+\fi
+
+% Responses to reviews
+\input{review-response-commands}
+% set this to show line numbers and include responses to reviews or not
+\newif\ifreviewresponses
+\reviewresponsestrue  % include them
+% \reviewresponsesfalse  % don't include them
+\newcommand{\responsefile}{review-responses}  % name of the review responses file
 
@@
 To this end, we define
-the death rate of an individual at $x$ to be
+the death rate of an individual at $x$ to be \revpoint{1}{4}
 \begin{align} \label{eqn:mu_defn}
@@
 a location $y$ offset from $x$
-by an independent Gaussian random variable with mean $\meanq(x) / \theta$
-and covariance matrix $\covq(x) / \theta$, and once there establishes instantaneously
+by an independent Gaussian random variable with mean $\meanq(x) / \theta$ \revpoint{1}{6}
+and covariance matrix $\covq(x) / \theta$,
+and once there establishes instantaneously \revpoint{1}{5}
 with probability $r(y, \eta^N_t)$, or else dies. 
@@
 \begin{remark}
-\label{ancestral lineages: first guess}
+\label{ancestral lineages: first guess} \revpoint{1}{7}
 An equivalent way to describe the model would be to say that
@@
         C_f = C(\sup_x \sup_{\|z\|=1} \max( \sum_i z_i \partial_{x_i} f(x), \sum_{ij} z_i z_j \partial_{x_i x_j} f(x))) .
-    \] \label{gamma_B_condition}
+    \] \label{gamma_B_condition} \revpoint{1}{9}
 \end{enumerate}
-To keep expressions manageable, we shall also assume that 
+To keep expressions manageable, we shall also assume that  \revpoint{1}{1}
 \[
@@
 is order $1/\theta$. As remarked above, 
-because of the non-local reproduction mechanism, it no longer suffices to assume that 
+because of the non-local reproduction mechanism, it no longer suffices \revpoint{1}{10}
+to assume that 
 $r(x,\eta)\gamma(x,\eta)-\mu_\theta(x)$ is of order $1/\theta$.
@@
 when $\alpha>0$.
-However, the Dawson--Girsanov transform tells us that we have uniqueness in this special 
-case of the superprocess with nonlinear death rates, and 
+However, the Dawson--Girsanov transform tells us that we have uniqueness \revpoint{1}{12}
+in this special case of the superprocess with nonlinear death rates, and 
 Perkins stochastic calculus (and its adaptation to a 
@@
 \end{proposition}
+
 The example that we have in mind for the kernel $\rho_\gamma$ is a Gaussian kernel.
 For the proof, see Section~\ref{sec:pme}.
-\begin{remark}
+
+\begin{remark} \label{remark_on_nonlocal_to_local}
 Although it seems hard to formulate an all-encompassing result,
@@
 numbers of individuals
-but not their ancestry sufficient to define the distribution of $(L_t)_{t=0}^T$?
+but not their ancestry sufficient to define the distribution of $(L_t)_{t=0}^T$? \revpoint{1}{15}
 Second, does the process have a tractable description?
@@
 \begin{definition}[Ancestral lineage] 
-\label{def:lineage_generator}
+\label{def:lineage_generator} \revpoint{1}{2}
     Let $(\varphi_t(x))_{0 \le t \le T}$
@@
 %%%%%%%%%%
-\paragraph{Fisher-KPP equation:}
+\paragraph{Fisher-KPP equation:} \revpoint{1}{16}
 Consider the classical Fisher-KPP equation,
@@
 \subsection{Lineage motion is not uniquely determined by population density}
+\label{sec:nonunique_lineage}
 
@@
 (because, for instance, making reproductive value less evenly distributed
-reduces long-term genetic diversity).
+reduces long-term genetic diversity). \revpoint{1}{18}
 
@@
 \subsection{Motion of ancestral lineages}
+\label{sec:lineage_motion}
 
@@
 A nontrivial consequence of the way we define $\lp_t$ will be that
-this process has the same distribution as the process $(\eta_t)_{t \ge 0}$ 
+this process \revpoint{1}{19}
+has the same distribution as the process $(\eta_t)_{t \ge 0}$ 
 of Definition~\ref{defn:mgale_construction}.
@@
 
-Levels never cross below 0,
+Levels never cross below 0, \revpoint{1}{20}
 while particles whose levels move above $N$ are regarded as dead
@@
 which captures the local rate of production of successful offspring.
-Recall from equation~\eqref{eqn:mu_defn} that
+Recall from equation~\eqref{eqn:mu_defn} that \revpoint{1}{21}
 $F(x,\eta) = \theta(r(x,\eta)\gamma(x,\eta) - \mu_\theta(x,\eta))$,
@@
 
-The martingale problem for finite $N$ has a unique solution.
+The martingale problem for finite $N$ has a unique solution. \revpoint{1}{22}
 Next we state the limiting martingale problem,
@@
 As a result, if the spatial projections $\eta$ converge, then
-individual lines of descent converge pointwise as $N \to \infty$.
+individual lines of descent converge pointwise as $N \to \infty$. \revpoint{1}{23}
 To see this, first note that if the Poisson processes are fixed
@@
 if this is finite.
-For any solution to the equations above, the processes defined by
+For any solution to the equations above, \revpoint{1}{24}
+the processes defined by
 \begin{align*}
@@
 
-\begin{proof}[of Proposition~\ref{prop:limiting_construction}]
+\begin{proof}[of Proposition~\ref{prop:limiting_construction}] \revpoint{1}{25}
     The fact that a solution to the system of equations~\eqref{eqn:limiting_construction}
@@
 
-Proofs of the remainder of these results are in Section~\ref{sec:lookdown_proofs}.
-
-\begin{remark}
+Proofs of the remainder of these results are in Section~\ref{sec:lookdown_proofs}. \revpoint{1}{27}
+
+\begin{remark} \label{remark_on_branching}
 The process we consider is similar to the state-dependent branching processes
@@
 Condition~\ref{control through r} of  
-Lemma~\ref{lem:conditions on r} is satisfied.
+Lemma~\ref{lem:conditions on r} is satisfied. \revpoint{1}{28}
 We write
@@
 \begin{proof}[Proof of Theorem~\ref{thm:nonlocal_convergence}.]
-The proof follows a familiar pattern. First we extend $\IR^d$ 
+The proof follows a familiar pattern. \revpoint{1}{29}
+First we extend $\IR^d$ 
 to its one-point compactification $\overline{\IR}^d$ and 
@@
 is the unique solution to the $(\Pgen^N, \eta_0)$-martingale problem, i.e., if
+\revpoint{1}{30}
 $$
@@
 \end{multline}
+    \revpoint{1}{31}
 (for sufficiently regular $\phi$).
@@
 The assumptions of Theorem~\ref{thm:local_convergence} will be in 
-force throughout, in particular,
+force throughout, in particular, \revpoint{1}{3}
 \begin{equation}
@@
 for some constants $C$ and $C'$.
-Now, using the Burkholder-Davis-Gundy inequality and \citet{barlow/jacka/yor:1986},
+Now, using the Burkholder-Davis-Gundy inequality and \citet{barlow/jacka/yor:1986}, \revpoint{1}{32}
 $\IE[\sup_{0 \le u \le T} |\widehat{M}^N(f)_u|^2] \le C'' \IE[\langle\widehat{M}^N(f)\rangle_u]$,
@@
 the contribution to~(\ref{target expression}) from the integral over
-the time interval $[0,\delta]$ is ${\mathcal O}(\delta)$. We focus instead
+the time interval $[0,\delta]$ is ${\mathcal O}(\delta)$. \revpoint{1}{33}
+We focus instead
 on the interval $(\delta, t]$.
@@
 \begin{remark}
-In addition to tightness of the measure-values processes $\lp^N$,
+In addition to tightness of the measure-values processes $\lp^N$, \revpoint{1}{34}
 the bounds used in the proofs below also imply
@@
 
+% reviews here if toggled above
+\includereviews
+
 \end{document}
@@
 
+Hallooooo, kind Managing Editor!
+
 %% EOF

### 2023-12-08 review-responses.tex
notes with alison

@@
 \reply{
+    Add sentence saying that this is well-defined because we take the finite-$N$ limit.
+    Markovian because it is conditional on the population process, which is deterministic...
 }
@@
 \reply{
+    Add discussion of that here.
 }
@@
 \reply{
+    Since you need to apply the Laplacian to it.
 }
@@
 \reply{
+    The PME is new;
+    probably the others are in Birzu/Korolev/Hallaschek? 
+    Also maybe see Roques et al 2008ish PNAS?
+    It reduces to BM in a potential:
+    find other references for this (i.e., the $\grad \log$...)
 }
@@
 \reply{
+    Just say we don't know, but:
+    see Pennington and Etheridge on bistable waves
+    where fluctuations in the wave happen on long time scales
 }
@@
 \reply{
+    ``Since this is a finite-rate jump process...''
 }
@@
 \begin{point}{}
-Section \ref{sec:lineages_proof}8.2 may nned to be modified also based on the second point in ``Major
+Section \ref{sec:lineages_proof} may need to be modified also based on the second point in ``Major
 comments'' above.

### 2023-12-08 review-responses.tex
.

@@
     Add discussion of that here.
+    (in particular the one condition comes from the crucial lemma 7.2)
 }
@@
 \reply{
+    $\omega$
 }
@@
 \reply{
+    Let $X$, $U$ be solutions to 5.20 on $[0,T]$... then $\eta$ is a solution on $[0,T]$...
 }
@@
 \reply{
+    Alison's superprocess book, section 1.4.
 }
@@
 \reply{
+    i.e., add ``for all such test functions''
 }
@@
 \reply{
+    Alison TODO
 }
@@
 \reply{
+    that we can bound the expectation of the quadratic variation by a constant times the expectation of the angle bracket process
+    (AS BEFORE)
 }
@@
 \reply{
+    Point out we're using 7.2 with $u=0$ and our assumptions about initial conditions.
+    (and maybe write that it's less than a constant times $\delta$;)
 }

### 2023-12-09 forwards-and-backwards.tex
notes with alison
minor corrections from matthias

@@
 
-We shall write $\mu_\theta(x, X/N)$ for the per-capita death rate of mature individuals
-in the population.
+We shall write $\mu_\theta(x, X/N)$ for the per-capita death rate of a mature individual
+at $x$ in the population.
 In order for the 
@@
 \begin{align} \label{eqn:mu_defn}
-    \mu_\theta(x)
+    \mu_\theta(x, X/N)
     =
@@
 \end{align}
-where this equation defines $F(x, m) : \IR^d \times \IR_{\ge 0} \to \IR$,
+where this equation also introduces $F(x, m) : \IR^d \times \IR_{\ge 0} \to \IR$,
 and $\rho_F$ is again a smooth kernel. 
@@
 Let $\rho^\epsilon_F(x)=\rho_F\big(x/\epsilon)/\epsilon^d$.
-Assume $\varphi_0\in L^2(\IR)$ is a positive, uniformly Lipschitz, and uniformly bounded function. 
+Assume $\varphi_0\in L^2(\IR^d)$ is a positive, uniformly Lipschitz, and uniformly bounded function. 
 Suppose that $\varphi^\epsilon\in L^2(\IR^d)$ is a weak solution to the equation
@@
         % comparing the simulated profile to the analytical solution;
-        $\theta/N$ small on the left; large on the right.
+        $\theta/N$ small on the top; large on the bottom.
         % Simulation is with $\gamma(m) = m$ and $\mu(m) = (1+1/\theta) m - 1/\theta$
@@
 \end{align*}
-Letting $\hat f(u) = \int e^{2\pi i u x} f(x) dx$ denote the Fourier transform,
+Letting $\hat f(u) = \int e^{i u x} f(x) dx / \sqrt{2 \pi}$ denote the Fourier transform,
 \begin{equation}
@@
 If we take $\rho_F=p_{\epsilon^2}$, then 
-$\hat{\rho}_F(u)=\exp(-2\pi\epsilon^2 u^2)$ and (recalling 
+$\hat{\rho}_F(u)=\exp(-\epsilon^2 u^2 / 2) / \sqrt{2 \pi}$ and (recalling 
 that $F_0'<0$) the term in brackets is always negative, and we recover
@@
 $\rho_F(x)={\mathbf 1}_{[-\epsilon, \epsilon]}(x)/2\epsilon$, then 
-$\hat{\rho}_F(u)=\sin (2\pi\epsilon u)/(2\pi\epsilon u)$, which is 
-negative for $u\in (1/(2\epsilon), 1/\epsilon)$ (and periodically 
+$\hat{\rho}_F(u)=\sin(\epsilon u)/(\sqrt{2\pi}\epsilon u)$, which is 
+negative for $u\in (\pi/epsilon, 2\pi/\epsilon)$ (and periodically 
 repeating intervals). Setting $v=\epsilon u$, the bracketed term on 
@@
 \[
-	\varphi_0F_0'\frac{1}{2\pi v}\sin (2\pi v)
+    \varphi_0F_0'\frac{1}{\sqrt{2\pi} v} \sin(v)
 	-\frac{\sigma^2}{\epsilon^2}v^2r_0\gamma_0,
@@
 \begin{equation*}
-	\partial_t \hat \psi(u) = e^{-2\pi^2\epsilon^2 u^2 } 
+	\partial_t \hat \psi(u) =
+    \frac{1}{\sqrt{2\pi}}
+    e^{-\epsilon^2 u^2/2} 
 	\left\{
-		-\sigma^2\varphi_0 r_0\gamma_0'u^2
-	-\sigma^2r_0\gamma_0u^2e^{2\pi^2\epsilon^2u^2}
+		-\sigma^2 \varphi_0 r_0 \gamma_0' u^2
+        -\sigma^2 r_0 \gamma_0 u^2 \sqrt{2\pi} e^{\epsilon^2 u^2/2}
         +\varphi_0 F_0'
@@
 \[
-	\frac{\sigma^2}{\epsilon^2}v^2 r_0 \left(-\varphi_0 \gamma_0' - \gamma_0 e^{2\pi^2v^2}\right)+\varphi_0F_0',
+	\frac{\sigma^2}{\epsilon^2}v^2 r_0
+    \left(
+        -\varphi_0 \gamma_0' - \gamma_0 \sqrt{2\pi} e^{v^2/2}
+    \right) + \varphi_0F_0',
 \] 
-and, provided $-\varphi_0\gamma_0'/\gamma_0>1$, for sufficiently small $v$ 
+and, provided $-\varphi_0\gamma_0'/\gamma_0\sqrt{2\pi} >1$, for sufficiently small $v$ 
 the term in round brackets is positive. We now see that if 
@@
 Recall that the parental \emph{individual} always retains their spatial location,
-so that $\kappa = 0$ corresponds to the parent being assigned a new level,
+so that $\kappa = 1$ corresponds to the parent being assigned a new level,
 and our line of descent switching to the offspring.
@@
     G'(\langle f, \eta \rangle)\int_{\IR^d}  
-\theta\Big\langle \gamma(x,\eta) \int_{\IR^d} f(y)r(y,\eta) q_{\theta}(x,dy), 
+\theta\Big\langle \gamma(x,\eta) \int_{\IR^d} f(y)r(y,\eta) q_{\theta}(x,dy) 
     - f(x)\mu_\theta(x,\eta), \eta(dx)\Big\rangle\\
@@
 $\rho_r$, $\rho_\gamma$, and $\rho_F$ by setting 
-$\rho^\epsilon(\cdot)=\rho(\cdot/\epsilon)/\epsilon$, as $\epsilon\to 0$, the 
+$\rho^\epsilon(\cdot)=\rho(\cdot/\epsilon)/\epsilon^d$, as $\epsilon\to 0$, the 
 corresponding solutions should converge to a limiting
@@
 the integral in this expression is
-$\mathcal{O}(\epsilon)$.
+$\mathcal{O}(\epsilon)$.  \revpoint{1}{31}
 
@@
 \end{multline}
-    \revpoint{1}{31}
 (for sufficiently regular $\phi$).
@@
 \begin{remark}
-In addition to tightness of the measure-values processes $\lp^N$, \revpoint{1}{34}
+In addition to tightness of the measure-valued processes $\lp^N$, \revpoint{1}{34}
 the bounds used in the proofs below also imply
@@
     (following, e.g., \citet{etheridge/kurtz:2019}, Condition 2.1).
-    % PLR: NEW DETAILS
     In several places below we require a dense subset
     of $C_b(\lpmeasures)$, the bounded, continuous functions on $\lpmeasures$.
-    The functions $\lp \mapsto \langle f, \lp \rangle$
+    The functions $\lp \mapsto \exp(-\langle f, \lp \rangle)$
+    for nonnegative, compactly supported $f : \overline{\IR^d} \times [0,\infty)$
     do not form not a dense subset of $C_b(\lpmeasures)$,
     but they do separate points and vanish nowhere, 
-    i.e., for any $\lp_1$ and $\lp_2$ there is an $f$
+    since for any $\lp_1$ and $\lp_2$ there is an $f$
     with $\langle f, \lp_1\rangle \neq \langle f, \lp_2\rangle$,
@@
     % Since $C_0(\lpmeasures)$ is dense
-    in $C_b(\lpmeasures)$ (with respect to uniform convergence on compact subsets).
-    % END NEW DETAILS
+    in $C_b(\lpmeasures)$ with respect to uniform convergence on compact subsets.
     Topologized in this way, the space $\lpmeasures$ is completely metrizable,
-    and we may choose a countable set of nonnegative $f_k$,
+    and we may choose a countable set of bounded, nonnegative $f_k$,
     each supported on $\IR^d \times [0,u_k]$ for some $u_k < \infty$,
@@
     $\sup_{\lp \in K} \langle f_k, \lp \rangle < \infty$ for each $k$.
-    (To see this, use Theorem A.2.3 of~\citet{kallenberg1997foundations}
-    and the first argument made in the proof of Lemma~\ref{lem:product_tightness}.)
+    (To see this, use Theorem A.2.3 of~\citet{kallenberg1997foundations}.)
     Below, Lemma~\ref{lem:compact containment lookdown} proves exactly this,
@@
     that is dense with respect to uniform convergence on compact subsets.
-    Lemma~\ref{lem:test_fn_tightness} shows that $\{\langle f, \lp^N_t \rangle\}_N$ is a tight sequence
+    Lemma~\ref{lem:test_fn_tightness} shows that
+    $\{\langle f, \lp^N_t \rangle\}_N$ is a tight sequence
     for any $f: \overline{\IR^d} \times [0,\infty) \to \IR$ with compact support
-    in the level direction.
+    in the level direction,
+    and hence so is $\{e^{-\langle f, \lp^N_t \rangle}\}_N$.
     % The functions $\lp \mapsto \langle f, \lp \rangle$
@@
     % in $C_b(\lpmeasures)$ (with respect to uniform convergence on compact subsets).  So, 
-    Since as above the algebra generated by the functions $\lp \mapsto \langle f, \lp \rangle$
+    Since as above the algebra generated by the functions $\lp \mapsto \exp(-\langle f, \lp \rangle)$
     is dense in $C_b(\lpmeasures)$,
-    it suffices to show that tightness for the processes $\langle f, \lp^N_t\rangle$
-    extends to finite sums and products of these processes,
+    it suffices to show that tightness for the processes $(\exp(-\langle f, \lp^N_t\rangle))_{t \ge 0}$
+    extends to finite sums and products (and constant multiples) of these processes,
     which is shown in Lemma~\ref{lem:product_tightness}.
@@
     for $X^{(n)} Y^{(n)}$, so on only prove the Lemma for the latter.
-    First, note that for any $\epsilon > 0$, by tightness of $X^{(n)}_t$ and $Y^{(n)}_t$
+
+    First, note that for any $\epsilon > 0$, by tightness of ${X^{(n)}_t}_{n\ge0}$ and ${Y^{(n)}_t}_{n\ge0}$
     there is a $K$ such that
@@
     \end{align*}
-    Therefore, $X^{(n)}_t Y^{(n)}_t$ is tight.
+    Therefore, ${X^{(n)}_t Y^{(n)}_t}_{n \ge 0}$ is tight.
 
@@
 
-% \bibliographystyle{amsplain}
-% \bibliography{refs}
+\bibliographystyle{amsplain}
+\bibliography{refs}
 
@@
 
-\providecommand{\bysame}{\leavevmode\hbox to3em{\hrulefill}\thinspace}
-\providecommand{\MR}{\relax\ifhmode\unskip\space\fi MR }
-% \MRhref is called by the amsart/book/proc definition of \MR.
-\providecommand{\MRhref}[2]{%
-  \href{http://www.ams.org/mathscinet-getitem?mr=#1}{#2}
-}
-\providecommand{\href}[2]{#2}
-\begin{thebibliography}{10}
-
-\bibitem{barlow/jacka/yor:1986}
-M.~T. Barlow, S.~D. Jacka, and M.~Yor, \emph{Inequalities for a pair of
-  processes stopped at a random time}, Proceedings of the London Mathematical
-  Society \textbf{s3-52} (1986), no.~1, 142--172.
-
-\bibitem{barton:1979}
-N~H Barton, \emph{The dynamics of hybrid zones}, Heredity \textbf{43} (1979),
-  no.~3, 341--359.
-
-\bibitem{berestycki2009nonlocal}
-Henri Berestycki, Gregoire Nadin, Benoit Perthame, and Lenya Ryzhik, \emph{The
-  non-local fisher-kpp equation: travelling waves and steady states},
-  Nonlinearity \textbf{22} (2009), no.~12, 2813--2844.
-
-\bibitem{birzu/hallatschek/korolev:2017}
-Gabriel Birzu, Oskar Hallatschek, and Kirill~S. Korolev, \emph{Fluctuations
-  uncover a distinct class of traveling waves}, Proc. Natl. Acad. Sci. (USA)
-  \textbf{115} (2018), no.~16, 3645--3654.
-
-\bibitem{birzu/hallatschek/korolev:2021}
-Gabriel Birzu, Oskar Hallatschek, and Kirill~S Korolev, \emph{Genealogical
-  structure changes as range expansions transition from pushed to pulled},
-  Proc. Natl. Acad. Sci. (USA) \textbf{118} (2021), no.~34, e2026746118.
-
-\bibitem{biswas/etheridge/klimek:2018}
-Niloy Biswas, Alison Etheridge, and Aleksander Klimek, \emph{The spatial
-  {Lambda}-{Fleming}-{Viot} process with fluctuating selection}, Electron. J.
-  Probab. \textbf{26} (2021), 1 -- 51.
-
-\bibitem{bolker/pacala:1997}
-B~M Bolker and S~W Pacala, \emph{Using moment equations to understand
-  stochastically driven spatial pattern formation in ecological systems},
-  Theor. Pop. Biol. \textbf{52} (1997), no.~3, 179--197.
-
-\bibitem{bolker/pacala:1999}
-\bysame, \emph{Spatial moment equations for plant competition: {Understanding}
-  spatial strategies and the advantages of short dispersal}, American
-  Naturalist \textbf{153} (1999), no.~6, 575--602.
-
-\bibitem{bramson:1983}
-M~Bramson, \emph{{Convergence of solutions of the Kolmogorov equation to
-  travelling waves}}, Mem. Amer. Math. Soc. \textbf{44} (1983), no.~285.
-
-\bibitem{britton1990spatial}
-N.~F. Britton, \emph{Spatial structures and periodic travelling waves in an
-  integro-differential reaction-diffusion population model}, SIAM Journal on
-  Applied Mathematics \textbf{50} (1990), no.~6, 1663--1688.
-
-\bibitem{brunet/derrida/mueller/munier:2006}
-E~Brunet, B~Derrida, A~H Mueller, and S~Munier, \emph{Noisy travelling waves:
-  effect of selection on genealogies}, Europhys. Lett. \textbf{76} (2006),
-  1--7.
-
-\bibitem{cantrell2004spatial}
-Robert~Stephen Cantrell and Chris Cosner, \emph{Spatial ecology via
-  reaction-diffusion equations}, John Wiley \& Sons, 2004.
-
-\bibitem{cohen/golding/kozlovsky/benjacob/ron:1999}
-I~Cohen, I~Golding, Y~Kozlovsky, E~Ben-Jacob, and I~Ron, \emph{Continuous and
-  discrete models of cooperation in complex bacterial colonies}, Fractals
-  \textbf{7} (1999), 235--247.
-
-\bibitem{dawson:1993}
-D~A Dawson, \emph{{Measure-valued Markov processes}}, \'Ecole d'\'et\'e de
-  probabilit\'es de Saint Flour, vol. 1541, Springer-Verlag, 1993.
-
-\bibitem{demasi/ferrari/lebowitz:1986}
-A.~De~Masi, P.~A. Ferrari, and J.~L. Lebowitz, \emph{Reaction-diffusion
-  equations for interacting particle system}, J. Stat. Phys. \textbf{44}
-  (1986), 589--644.
-
-\bibitem{demasi/presutti:1991}
-Anna DeMasi and Errico Presutti, \emph{Mathematical methods for hydrodynamic
-  limits}, Springer, 2006.
-
-\bibitem{donnelly/kurtz:1996}
-P~J Donnelly and T~G Kurtz, \emph{{A countable representation of the
-  Fleming-Viot measure-valued diffusion}}, Ann. Probab. \textbf{24} (1996),
-  698--742.
-
-\bibitem{donnelly/kurtz:1999}
-\bysame, \emph{{Particle representations for measure-valued population
-  models}}, Ann. Probab. \textbf{27} (1999), 166--205.
-
-\bibitem{durrett/fan:2016}
-R~Durrett and W-T Fan, \emph{Genealogies in expanding populations}, Ann. Appl.
-  Probab. \textbf{26} (2016), 3456--3490.
-
-\bibitem{etheridge/gooding/letter:2022}
-A~Etheridge, M~Gooding, and I~Letter, \emph{{On the effects of a wide opening
-  in the domain of the (stochastic) Allen-Cahn equation and the motion of
-  hyrbid zones}}, Electron. J. Probab. \textbf{27} (2022), 1--52.
-
-\bibitem{etheridge/penington:2022}
-A.~Etheridge and S.~Penington, \emph{Genealogies in bistable waves}, Electron.
-  J. Probab. \textbf{27} (2022), no.~121, 1--99.
-
-\bibitem{etheridge:2004}
-A~M Etheridge, \emph{Survival and extinction in a locally regulated
-  population}, Ann. Appl. Probab. \textbf{14} (2004), no.~1, 188--214.
-
-\bibitem{etheridge2000introduction}
-Alison Etheridge, \emph{An introduction to superprocesses}, no.~20, American
-  Mathematical Society, 2000.
-
-\bibitem{etheridge/kurtz:2019}
-Alison~M. Etheridge and Thomas~G. Kurtz, \emph{{Genealogical constructions of
-  population models}}, Ann. Probab. \textbf{47} (2019), no.~4, 1827--1910.
-
-\bibitem{ethier/kurtz:1986}
-Stewart~N. Ethier and Thomas~G. Kurtz, \emph{Markov processes --
-  characterization and convergence}, Wiley Series in Probability and
-  Mathematical Statistics: Probability and Mathematical Statistics, John Wiley
-  \& Sons Inc., New York, 1986. \MR{MR838085 (88a:60130)}
-
-\bibitem{fife1977approach}
-Paul~C. Fife and J.~B. McLeod, \emph{The approach of solutions of nonlinear
-  diffusion equations to travelling front solutions}, Archive for Rational
-  Mechanics and Analysis \textbf{65} (1977), no.~4, 335--361.
-
-\bibitem{flandoli/huang:2021}
-Franco Flandoli and Ruojun Huang, \emph{The {KPP} equation as a scaling limit
-  of locally interacting {Brownian} particles}, J. Differential Equations
-  \textbf{303} (2021), 608--644.
-
-\bibitem{flandoli/leimbach/olivera:2019}
-Franco Flandoli, Matti Leimbach, and Christian Olivera, \emph{Uniform
-  convergence of proliferating particles to the fkpp equation}, Journal of
-  Mathematical Analysis and Applications \textbf{473} (2019), no.~1, 27--52.
-
-\bibitem{ghosh2022emergent}
-Olivia~M. Ghosh and Benjamin~H. Good, \emph{Emergent evolutionary forces in
-  spatial models of microbial growth in the human gut microbiota}, Proc. Natl.
-  Acad. Sci. (USA) \textbf{119} (2022), no.~28, e2114931119.
-
-\bibitem{gilding/kersner:2005}
-B~H Gilding and R~Kersner, \emph{A {Fisher}/{KPP}-type equation with density
-  dependent diffusion and convection: travelling wave solutions}, J. Phys. A:
-  Math. Gen. \textbf{38} (2005), 337--3379.
-
-\bibitem{gooding:2018}
-M.~Gooding, \emph{Long term behaviour of spatial population models with
-  heterozygous or asymmetric homozygous selection}, DPhil thesis, Oxford
-  University, 2018.
-
-\bibitem{hallatschek/nelson:2008}
-O~Hallatschek and D~Nelson, \emph{Gene surfing in expanding populations},
-  Theor. Pop. Biol. \textbf{73} (2008), 158--170.
-
-\bibitem{haller_slim_2019}
-Benjamin~C. Haller and Philipp~W. Messer, \emph{{SLiM} 3: {Forward} genetic
-  simulations beyond the {Wright}-{Fisher} model}, Mol. Biol. Evol. \textbf{36}
-  (2019), no.~3, 632--637.
-
-\bibitem{haller2022evolutionary}
-\bysame, \emph{{SLiM}: An evolutionary simulation framework}, 2022.
-
-\bibitem{hernandezgarcia2004clustering}
-Emilio Hern\'andez-Garc\'{\i}a and Crist\'obal L\'opez, \emph{Clustering,
-  advection, and patterns in a model of population dynamics with
-  neighborhood-dependent rates}, Phys. Rev. E \textbf{70} (2004), no.~1,
-  016216.
-
-\bibitem{hernandez/jacka:2022}
-Ma.~Elena Hern{\'{a}}ndez-Hern{\'{a}}ndez and Saul~D. Jacka, \emph{A
-  generalisation of the burkholder-davis-gundy inequalities}, Electronic
-  Communications in Probability \textbf{27} (2022), no.~none.
-
-\bibitem{holmes/lewis/banks/veit:1994}
-E.~E. Holmes, M.~A. Lewis, J.~E. Banks, and R.~R. Veit, \emph{Partial
-  differential equations in ecology: Spatial interactions and population
-  dynamics}, Ecology \textbf{75} (1994), no.~1, 17--29.
-
-\bibitem{jacod/shiryaev:2013}
-Jean Jacod and Albert Shiryaev, \emph{Limit theorems for stochastic processes},
-  vol. 288, Springer Science \& Business Media, 2013.
-
-\bibitem{kallenberg1997foundations}
-Olav Kallenberg, \emph{Foundations of modern probability}, vol.~2, Springer,
-  1997.
-
-\bibitem{kamin/rosenau:2004}
-S~Kamin and P~Rosenau, \emph{Emergence of waves in a nonlinear
-  convection-reaction-diffusion equation}, Adv. Nonlinear Stud. \textbf{4}
-  (2004), 251--272.
-
-\bibitem{kelleher2019inferring}
-Jerome Kelleher, Yan Wong, Anthony~W. Wohns, Chaimaa Fadil, Patrick~K. Albers,
-  and Gil McVean, \emph{Inferring whole-genome histories in large population
-  datasets}, Nature Genetics \textbf{51} (2019), no.~9, 1330--1338.
-
-\bibitem{kolmogorov/petrovsky/piscounov:1937}
-A~Kolomogorov, I~Petrovsky, and N~Piscounov, \emph{{\'Etude de l'equation de la
-  diffusion avec croissance de la quantit\'e de mati\`ere et son application
-  \`a un probl\`eme biologique}}, Moscow Univ. Math. Bull. \textbf{1} (1937),
-  1--25.
-
-\bibitem{kurtz/rodrigues:2011}
-Thomas~G. Kurtz and Eliane~R. Rodrigues, \emph{Poisson representations of
-  branching {Markov} and measure-valued branching processes}, Ann. Probab.
-  \textbf{39} (2011), no.~3, 939--984.
-
-\bibitem{kurtz/xiong:1999}
-Thomas~G. Kurtz and Jie Xiong, \emph{Particle representations for a class of
-  nonlinear spdes}, Stoch. Proc. Appl. \textbf{83} (1999), no.~1, 103--126.
-
-\bibitem{lam2023introduction}
-King-Yeung Lam and Yuan Lou, \emph{Introduction to reaction-diffusion
-  equations: Theory and applications to spatial ecology and evolutionary
-  biology}, Springer International Publishing AG, 2023.
-
-\bibitem{li/buenzli/simpson:2022}
-Y~Li, P~Buenzli, and M~Simpson, \emph{Interpreting how nonlinear diffusion
-  affects the fate of bistable populations using a discrete modelling
-  framework}, Proc. Roy. Soc. A \textbf{478} (2022).
-
-\bibitem{lions/mas-gallic:2001}
-P-L Lions and S~Mas-Gallic, \emph{{Une m\'ethode particulaire d\'eterministe
-  pour des \'equations diffusives non lin\'eaires}}, C. R. Acad. Sci. Paris
-  \textbf{332, S\'erie I} (2001), 369--376.
-
-\bibitem{neigel1993application}
-J~E Neigel and J~C Avise, \emph{Application of a random walk model to
-  geographic distributions of animal mitochondrial {DNA} variation}, Genetics
-  \textbf{135} (1993), no.~4, 1209--1220.
-
-\bibitem{oelschlaeger:1985}
-Karl Oelschl{\"a}ger, \emph{A law of large numbers for moderately interacting
-  diffusion processes}, Z. Wahrsch. verw. Geb. \textbf{69} (1985), no.~2,
-  279--322.
-
-\bibitem{oelschlaeger:1989}
-\bysame, \emph{On the derivation of reaction-diffusion equations as limit
-  dynamics of systems of moderately interacting stochastic processes}, Prob.
-  Theor. Rel. Fields \textbf{82} (1989), no.~4, 565--586.
-
-\bibitem{penington:2017}
-S~Penington, \emph{{The spreading speed of solutions of the non-local
-  Fisher-KPP equation}}, J. Functional Anal. \textbf{275} (2017), no.~12,
-  3259--3302.
-
-\bibitem{perkins:1992}
-E~A Perkins, \emph{{Measure-valued branching diffusions with spatial
-  interactions}}, Prob. Th. Rel. Fields \textbf{94} (1992), 189--245.
-
-\bibitem{potts/borger:2023}
-Jonathan~R. Potts and Luca Börger, \emph{How to scale up from animal movement
-  decisions to spatiotemporal patterns: An approach via step selection},
-  Journal of Animal Ecology \textbf{92} (2023), no.~1, 16--29.
-
-\bibitem{rebolledo:1980}
-R~Rebolledo, \emph{{Sur l'existence de solutions \'a certains probl\`emes de
-  semimartingales}}, C. R. Acad. Sci. Paris \textbf{290} (1980).
-
-\bibitem{sasaki1997clumped}
-Akira Sasaki, \emph{Clumped distribution by neighbourhood competition}, J.
-  Theor. Biol. \textbf{186} (1997), no.~4, 415--430.
-
-\bibitem{sherratt:2010}
-J~A Sherratt, \emph{On the form of smooth-front travelling waves in a
-  reaction-diffusion equation with degenerate nonlinear diffusion}, Math.
-  Model. Nat. Phenom. \textbf{5} (2010), no.~5, 64--79.
-
-\bibitem{sheu:1991}
-S~J Sheu, \emph{{Some estimates of the transition density of a nondegenerate
-  diffusion Markov process}}, Ann. Probab. \textbf{19} (1991), no.~2, 538--561.
-
-\bibitem{young2001reproductive}
-W.~R. Young, A.~J. Roberts, and G.~Stuhne, \emph{Reproductive pair correlations
-  and the clustering of organisms}, Nature \textbf{412} (2001), no.~6844,
-  328--331.
-
-\end{thebibliography}
+% \providecommand{\bysame}{\leavevmode\hbox to3em{\hrulefill}\thinspace}
+% \providecommand{\MR}{\relax\ifhmode\unskip\space\fi MR }
+% % \MRhref is called by the amsart/book/proc definition of \MR.
+% \providecommand{\MRhref}[2]{%
+%   \href{http://www.ams.org/mathscinet-getitem?mr=#1}{#2}
+% }
+% \providecommand{\href}[2]{#2}
+% \begin{thebibliography}{10}
+% 
+% \bibitem{barlow/jacka/yor:1986}
+% M.~T. Barlow, S.~D. Jacka, and M.~Yor, \emph{Inequalities for a pair of
+%   processes stopped at a random time}, Proceedings of the London Mathematical
+%   Society \textbf{s3-52} (1986), no.~1, 142--172.
+% 
+% \bibitem{barton:1979}
+% N~H Barton, \emph{The dynamics of hybrid zones}, Heredity \textbf{43} (1979),
+%   no.~3, 341--359.
+% 
+% \bibitem{berestycki2009nonlocal}
+% Henri Berestycki, Gregoire Nadin, Benoit Perthame, and Lenya Ryzhik, \emph{The
+%   non-local fisher-kpp equation: travelling waves and steady states},
+%   Nonlinearity \textbf{22} (2009), no.~12, 2813--2844.
+% 
+% \bibitem{birzu/hallatschek/korolev:2017}
+% Gabriel Birzu, Oskar Hallatschek, and Kirill~S. Korolev, \emph{Fluctuations
+%   uncover a distinct class of traveling waves}, Proc. Natl. Acad. Sci. (USA)
+%   \textbf{115} (2018), no.~16, 3645--3654.
+% 
+% \bibitem{birzu/hallatschek/korolev:2021}
+% Gabriel Birzu, Oskar Hallatschek, and Kirill~S Korolev, \emph{Genealogical
+%   structure changes as range expansions transition from pushed to pulled},
+%   Proc. Natl. Acad. Sci. (USA) \textbf{118} (2021), no.~34, e2026746118.
+% 
+% \bibitem{biswas/etheridge/klimek:2018}
+% Niloy Biswas, Alison Etheridge, and Aleksander Klimek, \emph{The spatial
+%   {Lambda}-{Fleming}-{Viot} process with fluctuating selection}, Electron. J.
+%   Probab. \textbf{26} (2021), 1 -- 51.
+% 
+% \bibitem{bolker/pacala:1997}
+% B~M Bolker and S~W Pacala, \emph{Using moment equations to understand
+%   stochastically driven spatial pattern formation in ecological systems},
+%   Theor. Pop. Biol. \textbf{52} (1997), no.~3, 179--197.
+% 
+% \bibitem{bolker/pacala:1999}
+% \bysame, \emph{Spatial moment equations for plant competition: {Understanding}
+%   spatial strategies and the advantages of short dispersal}, American
+%   Naturalist \textbf{153} (1999), no.~6, 575--602.
+% 
+% \bibitem{bramson:1983}
+% M~Bramson, \emph{{Convergence of solutions of the Kolmogorov equation to
+%   travelling waves}}, Mem. Amer. Math. Soc. \textbf{44} (1983), no.~285.
+% 
+% \bibitem{britton1990spatial}
+% N.~F. Britton, \emph{Spatial structures and periodic travelling waves in an
+%   integro-differential reaction-diffusion population model}, SIAM Journal on
+%   Applied Mathematics \textbf{50} (1990), no.~6, 1663--1688.
+% 
+% \bibitem{brunet/derrida/mueller/munier:2006}
+% E~Brunet, B~Derrida, A~H Mueller, and S~Munier, \emph{Noisy travelling waves:
+%   effect of selection on genealogies}, Europhys. Lett. \textbf{76} (2006),
+%   1--7.
+% 
+% \bibitem{cantrell2004spatial}
+% Robert~Stephen Cantrell and Chris Cosner, \emph{Spatial ecology via
+%   reaction-diffusion equations}, John Wiley \& Sons, 2004.
+% 
+% \bibitem{cohen/golding/kozlovsky/benjacob/ron:1999}
+% I~Cohen, I~Golding, Y~Kozlovsky, E~Ben-Jacob, and I~Ron, \emph{Continuous and
+%   discrete models of cooperation in complex bacterial colonies}, Fractals
+%   \textbf{7} (1999), 235--247.
+% 
+% \bibitem{dawson:1993}
+% D~A Dawson, \emph{{Measure-valued Markov processes}}, \'Ecole d'\'et\'e de
+%   probabilit\'es de Saint Flour, vol. 1541, Springer-Verlag, 1993.
+% 
+% \bibitem{demasi/ferrari/lebowitz:1986}
+% A.~De~Masi, P.~A. Ferrari, and J.~L. Lebowitz, \emph{Reaction-diffusion
+%   equations for interacting particle system}, J. Stat. Phys. \textbf{44}
+%   (1986), 589--644.
+% 
+% \bibitem{demasi/presutti:1991}
+% Anna DeMasi and Errico Presutti, \emph{Mathematical methods for hydrodynamic
+%   limits}, Springer, 2006.
+% 
+% \bibitem{donnelly/kurtz:1996}
+% P~J Donnelly and T~G Kurtz, \emph{{A countable representation of the
+%   Fleming-Viot measure-valued diffusion}}, Ann. Probab. \textbf{24} (1996),
+%   698--742.
+% 
+% \bibitem{donnelly/kurtz:1999}
+% \bysame, \emph{{Particle representations for measure-valued population
+%   models}}, Ann. Probab. \textbf{27} (1999), 166--205.
+% 
+% \bibitem{durrett/fan:2016}
+% R~Durrett and W-T Fan, \emph{Genealogies in expanding populations}, Ann. Appl.
+%   Probab. \textbf{26} (2016), 3456--3490.
+% 
+% \bibitem{etheridge/gooding/letter:2022}
+% A~Etheridge, M~Gooding, and I~Letter, \emph{{On the effects of a wide opening
+%   in the domain of the (stochastic) Allen-Cahn equation and the motion of
+%   hyrbid zones}}, Electron. J. Probab. \textbf{27} (2022), 1--52.
+% 
+% \bibitem{etheridge/penington:2022}
+% A.~Etheridge and S.~Penington, \emph{Genealogies in bistable waves}, Electron.
+%   J. Probab. \textbf{27} (2022), no.~121, 1--99.
+% 
+% \bibitem{etheridge:2004}
+% A~M Etheridge, \emph{Survival and extinction in a locally regulated
+%   population}, Ann. Appl. Probab. \textbf{14} (2004), no.~1, 188--214.
+% 
+% \bibitem{etheridge2000introduction}
+% Alison Etheridge, \emph{An introduction to superprocesses}, no.~20, American
+%   Mathematical Society, 2000.
+% 
+% \bibitem{etheridge/kurtz:2019}
+% Alison~M. Etheridge and Thomas~G. Kurtz, \emph{{Genealogical constructions of
+%   population models}}, Ann. Probab. \textbf{47} (2019), no.~4, 1827--1910.
+% 
+% \bibitem{ethier/kurtz:1986}
+% Stewart~N. Ethier and Thomas~G. Kurtz, \emph{Markov processes --
+%   characterization and convergence}, Wiley Series in Probability and
+%   Mathematical Statistics: Probability and Mathematical Statistics, John Wiley
+%   \& Sons Inc., New York, 1986. \MR{MR838085 (88a:60130)}
+% 
+% \bibitem{fife1977approach}
+% Paul~C. Fife and J.~B. McLeod, \emph{The approach of solutions of nonlinear
+%   diffusion equations to travelling front solutions}, Archive for Rational
+%   Mechanics and Analysis \textbf{65} (1977), no.~4, 335--361.
+% 
+% \bibitem{flandoli/huang:2021}
+% Franco Flandoli and Ruojun Huang, \emph{The {KPP} equation as a scaling limit
+%   of locally interacting {Brownian} particles}, J. Differential Equations
+%   \textbf{303} (2021), 608--644.
+% 
+% \bibitem{flandoli/leimbach/olivera:2019}
+% Franco Flandoli, Matti Leimbach, and Christian Olivera, \emph{Uniform
+%   convergence of proliferating particles to the fkpp equation}, Journal of
+%   Mathematical Analysis and Applications \textbf{473} (2019), no.~1, 27--52.
+% 
+% \bibitem{ghosh2022emergent}
+% Olivia~M. Ghosh and Benjamin~H. Good, \emph{Emergent evolutionary forces in
+%   spatial models of microbial growth in the human gut microbiota}, Proc. Natl.
+%   Acad. Sci. (USA) \textbf{119} (2022), no.~28, e2114931119.
+% 
+% \bibitem{gilding/kersner:2005}
+% B~H Gilding and R~Kersner, \emph{A {Fisher}/{KPP}-type equation with density
+%   dependent diffusion and convection: travelling wave solutions}, J. Phys. A:
+%   Math. Gen. \textbf{38} (2005), 337--3379.
+% 
+% \bibitem{gooding:2018}
+% M.~Gooding, \emph{Long term behaviour of spatial population models with
+%   heterozygous or asymmetric homozygous selection}, DPhil thesis, Oxford
+%   University, 2018.
+% 
+% \bibitem{hallatschek/nelson:2008}
+% O~Hallatschek and D~Nelson, \emph{Gene surfing in expanding populations},
+%   Theor. Pop. Biol. \textbf{73} (2008), 158--170.
+% 
+% \bibitem{haller_slim_2019}
+% Benjamin~C. Haller and Philipp~W. Messer, \emph{{SLiM} 3: {Forward} genetic
+%   simulations beyond the {Wright}-{Fisher} model}, Mol. Biol. Evol. \textbf{36}
+%   (2019), no.~3, 632--637.
+% 
+% \bibitem{haller2022evolutionary}
+% \bysame, \emph{{SLiM}: An evolutionary simulation framework}, 2022.
+% 
+% \bibitem{hernandezgarcia2004clustering}
+% Emilio Hern\'andez-Garc\'{\i}a and Crist\'obal L\'opez, \emph{Clustering,
+%   advection, and patterns in a model of population dynamics with
+%   neighborhood-dependent rates}, Phys. Rev. E \textbf{70} (2004), no.~1,
+%   016216.
+% 
+% \bibitem{hernandez/jacka:2022}
+% Ma.~Elena Hern{\'{a}}ndez-Hern{\'{a}}ndez and Saul~D. Jacka, \emph{A
+%   generalisation of the burkholder-davis-gundy inequalities}, Electronic
+%   Communications in Probability \textbf{27} (2022), no.~none.
+% 
+% \bibitem{holmes/lewis/banks/veit:1994}
+% E.~E. Holmes, M.~A. Lewis, J.~E. Banks, and R.~R. Veit, \emph{Partial
+%   differential equations in ecology: Spatial interactions and population
+%   dynamics}, Ecology \textbf{75} (1994), no.~1, 17--29.
+% 
+% \bibitem{jacod/shiryaev:2013}
+% Jean Jacod and Albert Shiryaev, \emph{Limit theorems for stochastic processes},
+%   vol. 288, Springer Science \& Business Media, 2013.
+% 
+% \bibitem{kallenberg1997foundations}
+% Olav Kallenberg, \emph{Foundations of modern probability}, vol.~2, Springer,
+%   1997.
+% 
+% \bibitem{kamin/rosenau:2004}
+% S~Kamin and P~Rosenau, \emph{Emergence of waves in a nonlinear
+%   convection-reaction-diffusion equation}, Adv. Nonlinear Stud. \textbf{4}
+%   (2004), 251--272.
+% 
+% \bibitem{kelleher2019inferring}
+% Jerome Kelleher, Yan Wong, Anthony~W. Wohns, Chaimaa Fadil, Patrick~K. Albers,
+%   and Gil McVean, \emph{Inferring whole-genome histories in large population
+%   datasets}, Nature Genetics \textbf{51} (2019), no.~9, 1330--1338.
+% 
+% \bibitem{kolmogorov/petrovsky/piscounov:1937}
+% A~Kolomogorov, I~Petrovsky, and N~Piscounov, \emph{{\'Etude de l'equation de la
+%   diffusion avec croissance de la quantit\'e de mati\`ere et son application
+%   \`a un probl\`eme biologique}}, Moscow Univ. Math. Bull. \textbf{1} (1937),
+%   1--25.
+% 
+% \bibitem{kurtz/rodrigues:2011}
+% Thomas~G. Kurtz and Eliane~R. Rodrigues, \emph{Poisson representations of
+%   branching {Markov} and measure-valued branching processes}, Ann. Probab.
+%   \textbf{39} (2011), no.~3, 939--984.
+% 
+% \bibitem{kurtz/xiong:1999}
+% Thomas~G. Kurtz and Jie Xiong, \emph{Particle representations for a class of
+%   nonlinear spdes}, Stoch. Proc. Appl. \textbf{83} (1999), no.~1, 103--126.
+% 
+% \bibitem{lam2023introduction}
+% King-Yeung Lam and Yuan Lou, \emph{Introduction to reaction-diffusion
+%   equations: Theory and applications to spatial ecology and evolutionary
+%   biology}, Springer International Publishing AG, 2023.
+% 
+% \bibitem{li/buenzli/simpson:2022}
+% Y~Li, P~Buenzli, and M~Simpson, \emph{Interpreting how nonlinear diffusion
+%   affects the fate of bistable populations using a discrete modelling
+%   framework}, Proc. Roy. Soc. A \textbf{478} (2022).
+% 
+% \bibitem{lions/mas-gallic:2001}
+% P-L Lions and S~Mas-Gallic, \emph{{Une m\'ethode particulaire d\'eterministe
+%   pour des \'equations diffusives non lin\'eaires}}, C. R. Acad. Sci. Paris
+%   \textbf{332, S\'erie I} (2001), 369--376.
+% 
+% \bibitem{neigel1993application}
+% J~E Neigel and J~C Avise, \emph{Application of a random walk model to
+%   geographic distributions of animal mitochondrial {DNA} variation}, Genetics
+%   \textbf{135} (1993), no.~4, 1209--1220.
+% 
+% \bibitem{oelschlaeger:1985}
+% Karl Oelschl{\"a}ger, \emph{A law of large numbers for moderately interacting
+%   diffusion processes}, Z. Wahrsch. verw. Geb. \textbf{69} (1985), no.~2,
+%   279--322.
+% 
+% \bibitem{oelschlaeger:1989}
+% \bysame, \emph{On the derivation of reaction-diffusion equations as limit
+%   dynamics of systems of moderately interacting stochastic processes}, Prob.
+%   Theor. Rel. Fields \textbf{82} (1989), no.~4, 565--586.
+% 
+% \bibitem{penington:2017}
+% S~Penington, \emph{{The spreading speed of solutions of the non-local
+%   Fisher-KPP equation}}, J. Functional Anal. \textbf{275} (2017), no.~12,
+%   3259--3302.
+% 
+% \bibitem{perkins:1992}
+% E~A Perkins, \emph{{Measure-valued branching diffusions with spatial
+%   interactions}}, Prob. Th. Rel. Fields \textbf{94} (1992), 189--245.
+% 
+% \bibitem{potts/borger:2023}
+% Jonathan~R. Potts and Luca Börger, \emph{How to scale up from animal movement
+%   decisions to spatiotemporal patterns: An approach via step selection},
+%   Journal of Animal Ecology \textbf{92} (2023), no.~1, 16--29.
+% 
+% \bibitem{rebolledo:1980}
+% R~Rebolledo, \emph{{Sur l'existence de solutions \'a certains probl\`emes de
+%   semimartingales}}, C. R. Acad. Sci. Paris \textbf{290} (1980).
+% 
+% \bibitem{sasaki1997clumped}
+% Akira Sasaki, \emph{Clumped distribution by neighbourhood competition}, J.
+%   Theor. Biol. \textbf{186} (1997), no.~4, 415--430.
+% 
+% \bibitem{sherratt:2010}
+% J~A Sherratt, \emph{On the form of smooth-front travelling waves in a
+%   reaction-diffusion equation with degenerate nonlinear diffusion}, Math.
+%   Model. Nat. Phenom. \textbf{5} (2010), no.~5, 64--79.
+% 
+% \bibitem{sheu:1991}
+% S~J Sheu, \emph{{Some estimates of the transition density of a nondegenerate
+%   diffusion Markov process}}, Ann. Probab. \textbf{19} (1991), no.~2, 538--561.
+% 
+% \bibitem{young2001reproductive}
+% W.~R. Young, A.~J. Roberts, and G.~Stuhne, \emph{Reproductive pair correlations
+%   and the clustering of organisms}, Nature \textbf{412} (2001), no.~6844,
+%   328--331.
+% 
+% \end{thebibliography}
 
@@
 \begin{acks}
+Many thanks to Matthias Birkner, Mattias Winkel, and an anonymous reviewer
+for detailed comments and corrections.
 Thanks go to Gilia Patterson for identifying the ``clumping'' phenomenon,

### 2023-12-10 forwards-and-backwards.tex
most of Mattias comments

@@
 
+\RequirePackage{xcolor}
 \documentclass[EJP]{ejpecp} % replace ECP by EJP if needed.
@@
 \newcommand{\flpmeasures}{\mathcal{M}(\IR^d \times [0,\infty))} % locally finite measures on space x level
+\newcommand{\comment}[1]{{\color{blue} \it #1}}
 
@@
 \begin{remark}
-\label{ancestral lineages: first guess} \revpoint{1}{7}
+\label{ancestral lineages: first guess}
 An equivalent way to describe the model would be to say that
@@
 and that offspring disperse according to the kernel
+$q_\theta^\mathfrak{m}$ (with superscript $\mathfrak{m}$ because it is post-\textbf{m}ortality),
+defined by: \revpoint{1}{7}
 $$
@@
     }{
-        r(x, \eta^{N})
+        r(x, \eta)
     } .
@@
 %Assume $\varphi_0\in L^2(\IR)$ is a positive, Lipschitz, and uniformly bounded function; 
-Suppose further that $F$ is a Lipschitz function which is bounded above, and that
-$\meanq(x)$ and $\covq(x)$, the drift and 
-covariance matrix of $\DG$, satisfy the conditions of 
-Assumptions~\ref{def:model_setup}.
+Suppose further that $F$ is a Lipschitz function which is bounded above,
+and that $\meanq(x)$ and $\covq(x)$, the drift and covariance matrix of $\DG$,
+satisfy the conditions of Assumptions~\ref{def:model_setup}
+and are such that $\DG^* 1 = 0$ (see Definition~\ref{def:dispersal_generator}).
 Then, for all $T>0$ there exists a constant $K=K(T, \Vert \varphi_0 \Vert_\infty) < \infty$
@@
 to equation~(\ref{nonlocalPDEv1}). 
+\end{remark}
+
+\begin{remark}
+    Instead of putting the fairly strong constraint that $\DG^* 1(x) = 0$ for all $x$,
+    it would be enough to assume instead that $\DG^* 1(x)$ is uniformly bounded,
+    so that $f \mapsto \DG^*f - f \DG^* 1$ is the generator of a conservative diffusion.
+    Since then $\varphi$ solves
+    $$ \partial_t \varphi = (\DG^* \varphi - \varphi \DG^* 1) + \varphi (F(\varphi) + \DG^* 1) , $$
+    the proof goes through essentially unchanged,
+    with only $F(\varphi(x))$ replaced with $F(\varphi(x)) + \DG^*1(x)$,
+    a bounded perturbation.
 \end{remark}
@@
     \bigg)
-    ds .
+    ds ,
     \end{split}
 \end{align}
+where
+\begin{align*}
+    \eta_t
+    :=
+    \lim_{u_0 \to \infty} \frac{1}{u_0}
+        \sum_{a : \tau_a \le t < \sigma_a \; ; \; U_a(t) < u_0} \delta_{X_a(t)} .
+\end{align*}
 Each point in each $R_a$ denotes a potential birth time for $a$:
@@
 For any solution to the equations above, \revpoint{1}{24}
-the processes defined by
-\begin{align*}
-    \eta_t
-    =
-    \lim_{u_0 \to \infty} \frac{1}{u_0}
-        \sum_{a : \tau_a \le t < \sigma_a \; ; \; U_a(t) < u_0} \delta_{X_a(t)}
-    \qquad \text{and} \qquad
+the process $\eta_t$
+is a solution to the martingale problem of Theorem~\ref{thm:nonlocal_convergence},
+and the process
+\begin{align*}
     \lp_t = \sum_{a : \tau_a \le t < \sigma_a} \delta_{(X_a(t), U_a(t))} 
 \end{align*}
-are solutions to the martingale problems of
-Theorems~\ref{thm:nonlocal_convergence} and~\ref{thm:lookdown_convergence},
-respectively.
+is a solution to the martingale problem of
+Theorem~\ref{thm:lookdown_convergence}.
 \end{proposition}
@@
 the production of these lineages.
+
+\comment{TODO: add note about well-definedness of $\eta_t$.}
 
@@
     is bounded by a (universal) constant multiple of the expectation of its angle bracket process
-    (\cite{barlow/jacka/yor:1986} Item (4.b'), Table 4.1, p. 162).
+    (\cite{barlow/jacka/yor:1986}, Item (4.b'), Table 4.1, p. 162).
     Now, since $\sqrt{x} \le 1 + x$,
@@
 A process $(\eta^{\infty}_t)_{t \geq 0}$ 
-satisifes the martingale characterization of equations~\eqref{eqn:limiting_mgale_problem}
+satisfies the martingale characterization of equations~\eqref{eqn:limiting_mgale_problem}
 and~\eqref{eqn:limiting_mgale_variation}
-if and only if it is a solution 
+if it is a solution % "and only if" requires continuity
 to the $(\Pgen^{\infty}, \eta^\infty_0)$-martingale problem, i.e.,
@@
 \end{lemma}
+
+The converse -- that any solution to equations~\eqref{eqn:limiting_mgale_problem}
+and~\eqref{eqn:limiting_mgale_variation}
+is a solution to the $(\Pgen^{\infty}, \eta^\infty_0)$-martingale problem --
+requires continuity, which we expect to be true, but have not proved.
 
@@
 Under the assumptions of Theorem~\ref{thm:nonlocal_convergence},
-let $(\eta_t)_{t\geq 0}$ be a limit point of $\{(\eta^N_t)_{t\geq 0}\}_{N\geq 1}$. 
-For any $\delta>0$, 
+if $(\eta_t)_{t\geq 0}$ be a limit point of $\{(\eta^N_t)_{t\geq 0}\}_{N\geq 1}$,
+then for any $\delta>0$ and $T>0$,
 \[
-\IP\big[\eta_t\big(\{\|x\|>R\}\big)>\delta\big]\to 0\qquad\mbox{ as }R\to\infty.
+\IP\bigg[
+    \sup_{0 \le t \le T} \eta_t\big(\{\|x\|>R\}\big)>\delta
+\bigg]\to 0\qquad\mbox{ as }R\to\infty.
 \]
@@
 \begin{align*}
-    \IE[\langle f_n(x), \eta^N_t(dx) \rangle]
+    \IE\left[\left\langle f_n(x), \eta^N_t(dx) \right\rangle\right]
     &\le
-    \IE[\langle f_n(x), \eta^N_0(dx) \rangle]
+    \IE\left[\left\langle f_n(x), \eta^N_0(dx) \right\rangle\right]
     +
@@
 By first taking $N \to \infty$ and then $n \to \infty$,
-we find that $\IE[\langle f_0, \eta_t(dx)\rangle] \le C'$
-for $t\in [0,T]$, and since $f_0 \to \infty$ as $|x| \to \infty$,
+we find that $\IE[\langle f_0, \eta_t(dx)\rangle] \le C'$ for $t\in [0,T]$.
+However, this is for a single time --
+we would like instead to uniformly bound
+$\IE[\sup_{0 \le t \le T} \langle f_0, \eta_t(dx)\rangle]$.
+This can be done in a similar but lengthier manner,
+following the proof of Lemma~\ref{lem:eta_compact_containment}
+and observing that bounds can be taken independent of $n$ and $N$.
+
+Finally, since $f_0 \to \infty$ as $|x| \to \infty$,
 an application of Markov's inequality
@@
 $$
-    \IP\big\{ \eta_t(\{x : \|x\| > R\})>\delta \big\}
-    \le \frac{\IE[\langle f_0, \eta_t\rangle]}{\inf_{\{x:\|x\|\ge R\}} f_0(x)}
+    \IP\bigg\{ \sup_{0 \le t \le T} \eta_t(\{x : \|x\| > R\})>\delta \bigg\}
+    \le \frac{\IE[\sup_{0 \le t \le T} \langle f_0, \eta_t\rangle]}{\delta \inf_{\{x:\|x\|\ge R\}} f_0(x)}
     \to 0 \qquad \text{as } R\to\infty .
@@
 
-    First, note that for any $\epsilon > 0$, by tightness of ${X^{(n)}_t}_{n\ge0}$ and ${Y^{(n)}_t}_{n\ge0}$
+    First, note that for any $\epsilon > 0$, by tightness of $(X^{(n)}_t)_{n\ge0}$ and $(Y^{(n)}_t)_{n\ge0}$
     there is a $K$ such that
@@
     \end{align*}
-    Therefore, ${X^{(n)}_t Y^{(n)}_t}_{n \ge 0}$ is tight.
+    Therefore, $(X^{(n)}_t Y^{(n)}_t)_{n \ge 0}$ is tight.
 

### 2023-12-11 forwards-and-backwards.tex
.

@@
 
+\comment{TODO: double-check $\langle \cdot \rangle$ versus $[\cdot]$}
+\comment{TODO: check factor of 2}
+
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 allowing for stable populations through density-dependent feedback.
+The model generalizes those introduced to the ecology literature by
+\citet{bolker/pacala:1997} and \citet{law/murrell/dieckmann:2003},
+and subsequently studied, e.g., by \citet{etheridge:2004} and \citet{fournier2004microscopic}.
 
@@
 To understand the stability of the constant solution $\varphi\equiv\varphi_0$, 
-we
-linearise~\eqref{general deterministic limit} around $\varphi_0$:
+we linearise~\eqref{general deterministic limit} around $\varphi_0$:
 let $\varphi_t(x) = \varphi_0 + \psi_t(x)$,
 and (informally) $r(x) \approx r(\varphi_0) + r'(\varphi_0) \smooth{r} \psi(x)$.
+Recall that in this section we are in $d=1$.
 Writing $r_0 = r(\varphi_0)$ and $r'_0 = r'(\varphi_0)$,
@@
 $\hat{\rho}_F(u)=\sin(\epsilon u)/(\sqrt{2\pi}\epsilon u)$, which is 
-negative for $u\in (\pi/epsilon, 2\pi/\epsilon)$ (and periodically 
+negative for $u\in (\pi/\epsilon, 2\pi/\epsilon)$ (and periodically 
 repeating intervals). Setting $v=\epsilon u$, the bracketed term on 
@@
 Under the assumptions of Theorem~\ref{thm:nonlocal_convergence},
-if $(\eta_t)_{t\geq 0}$ be a limit point of $\{(\eta^N_t)_{t\geq 0}\}_{N\geq 1}$,
+if $(\eta_t)_{t\geq 0}$ is a limit point of $\{(\eta^N_t)_{t\geq 0}\}_{N\geq 1}$,
 then for any $\delta>0$ and $T>0$,

### 2023-12-11 forwards-and-backwards.tex
alison fixup to PME proof

@@
 $\tilde{z}=-z$.
-To control the term~(\ref{error 1})
+We are going to bound the square of the $L^2$-norm of the term in square brackets 
+in~(\ref{error 1}) by the product of its $L^1$-norm (which is bounded
+by a constant times the $L^1$-norm of $\psi_t^\epsilon$) and its $L^\infty$-norm.
+To control the $L^\infty$-norm,
 we use the Intermediate Value Theorem to see that
@@
 \\
-\leq C\|\Delta\phi\|_\infty\int \psi_t^\epsilon (x-y)y\zeta^{\epsilon}(y) d y.
+	\leq C\|\Delta\phi\|_\infty\int \psi_t^\epsilon (x-y)
+	\epsilon\frac{|y|}{\epsilon}\zeta^{\epsilon}(y) d y
+	\leq C\|\Delta\phi\|_\infty\epsilon \|z\zeta(z)\|_\infty\int \psi_t^\epsilon (x-y) dy.
+	%|y|\zeta^{\epsilon}(y) d y
 \end{multline*}
-Since $\zeta\in\mathcal{S}(\IR)$, 
-the integral in this expression is
+Since $\zeta\in\mathcal{S}(\IR)$, and as we checked above $\psi_t^\epsilon$ is 
+uniformly bounded in $L^1$ over $[0,T]$,
+this expression is
 $\mathcal{O}(\epsilon)$.  \revpoint{1}{31}
+
+We can now apply the Cauchy-Schwarz inequality to~(\ref{error 1}) to bound
+it by the square root of
+\begin{equation}
+	C\epsilon\int \big(\nabla(\zeta^\epsilon*\psi_t^\epsilon(x))\big)^2 dx.
+\end{equation}
 
@@
 \left[\zeta^{\epsilon}*(\nabla \psi_t^\epsilon\, \nabla\phi)-
-\nabla\phi\,(\nabla \zeta^{\epsilon}*\psi_t^\epsilon)\right] dx,
+\nabla\phi\,(\nabla \zeta^{\epsilon}*\psi_t^\epsilon)\right] dx.
 \end{eqnarray}
-and~(\ref{error 2}) is controlled in the same way as~(\ref{error 1}):
-using the Intermediate Value Theorem,
+The term in square brackets in~(\ref{error 2}) is %controlled in the same way as~(\ref{error 1}):
+%using the Intermediate Value Theorem,
 \begin{multline*}
@@
 \\
-\leq C\|\Delta\phi\|_\infty\left|\int \nabla \psi_t^\epsilon(x-y)
-y \zeta^{\epsilon}(y)
-d y\right|,
+=
+	\left|\int\left[\psi_t^\epsilon(x-y)
+	\nabla\big((\nabla\phi(x-y)-\nabla\phi(x))\zeta^{\epsilon}(y)\big)
+%-\nabla\phi(x)\nabla \psi_t^\epsilon(x-y)\zeta^{\epsilon}(y)
+\right] dy\right|,
+%\leq C\|\Delta\phi\|_\infty\left|\int \nabla \psi_t^\epsilon(x-y)
+%y \zeta^{\epsilon}(y)
+%d y\right|,
 \end{multline*}
-which again is $\mathcal{O}(\epsilon)$.
-
-We now have the ingredients that we need.
-The calculations above yield both a uniform (in $\epsilon$) bound on
+and expanding $\nabla\phi$ in a Taylor series about $x$ and once again using that
+$\zeta\in \mathcal{S}(\IR)$, we see that the $L^\infty$ norm of this quantity is
+$\mathcal{O}(\epsilon)$.
+
+We can now apply the Cauchy-Schwarz inequality to~(\ref{error 2}) to bound
+it by the square root of
+\begin{equation}
+	C\epsilon\int \big(\zeta^\epsilon*\psi_t^\epsilon(x)\big)^2 dx.
+\end{equation}
+
+We now have the ingredients that we need. Recalling that 
+$\int_0^t \int(\zeta^{\epsilon}*\psi_s^\epsilon(x))^2  dx ds$ and
+$\int_0^t \int \big(\nabla (\zeta^{\epsilon}*\psi_s^\epsilon(x))\big)^2  dx ds$
+are uniformly bounded in
+$\epsilon$ and $t\in [0,T]$,
+the calculations above yield both a uniform (in $\epsilon$) bound on
 $\zeta^{\epsilon}*\psi_t^\epsilon$ in
-$L^1\cap L^2\big([0,T]\times \IR\big)$, and that
+$L^1\cap L^2\big([0,T]\times \IR\big)$, and (with another application of 
+Cauchy-Schwarz, this time applied to the time integral, to control the error terms) that
 \begin{multline} \label{eqn:weak_approx_pme}
@@
 \phi(x) dx
-+\mathcal{O}(\epsilon)
+	+\mathcal{O}(\sqrt{\epsilon})
 \end{multline}

### 2023-12-11 forwards-and-backwards.tex
.

@@
 \end{multline*}
-Since $\zeta\in\mathcal{S}(\IR)$, and as we checked above $\psi_t^\epsilon$ is 
-uniformly bounded in $L^1$ over $[0,T]$,
-this expression is
-$\mathcal{O}(\epsilon)$.  \revpoint{1}{31}
+Since $\zeta\in\mathcal{S}(\IR)$,
+and (as we checked above)
+$\psi_t^\epsilon$ is uniformly bounded in $L^1$ over $[0,T]$,
+this expression is $\mathcal{O}(\epsilon)$ -- \revpoint{1}{31}
+i.e., is bounded by a constant multiple of $\epsilon$
+with a constant that does not depend on $t \in [0,T]$ or $x$.
 

### 2023-12-15 review-responses.tex
minor corrections from matthias
most of Mattias comments
.
addressed most of the comments

--- 2023-12-08 review-responses.tex
@@
 \reply{
+    We've revised this to remove the $\max$ in Equation~\eqref{eqn:mu_defn},
+    and make the assumption that this is nonnegative more consistently:
+    see \revref{} and the new paragraph following Assumptions~\ref{def:model_setup}.
 }
 
-\begin{point}{\revref}
-Definition \ref{def:lineage_generator}, Proposition 2.23: I think these may need to be rewritten/rephrased. Up
+\begin{point}{}
+    Definition \ref{def:lineage_generator}, Proposition \ref{thm:lineages}:
+    I think these may need to be rewritten/rephrased. Up
 to Proposition \ref{thm:lineages}, it is not clear what ``that individual'' is in the limiting model. Therefore,
@@
 \reply{
-    Add sentence saying that this is well-defined because we take the finite-$N$ limit.
-    Markovian because it is conditional on the population process, which is deterministic...
+    This is a bit tricky, because really to justify this being a sensible notion
+    we'd like to refer to the lookdown, which has not yet been introduced.
+    To make things more clear we've added a bit to the earlier introductory paragraph
+    \llname{whatis_lineage},
+    reworded Definition~\ref{def:lineage_generator} somewhat,
+    and added some more explanation after the Definition and before the Proposition,
+    which also points out that it is Markovian \revref.
 }
@@
 \reply{
-    Add discussion of that here.
+    We've added a bit more here \revref,
+    and also referred the reader back to the (at this point long-ago)
+    discussion earlier \llname{one_step_heuristics}.
 }
@@
 which is confusing. What is being defined here? Please clarify. It seems to me that one has
-to first choose $F$, then define $µ_\theta(x)$ as in \eqref{eqn:mu_defn}.
+to first choose $F$, then define $\mu_\theta(x)$ as in \eqref{eqn:mu_defn}.
 \end{point}
@@
 \reply{
+    That's right; we've rearranged this so it's hopefully more clear \revref.
 }
@@
 \reply{
+    We've rearranged this to be shorter  \revref.
 }
@@
 \reply{
+    That's right, this bit was supposed to introduce those functions
+    (and we want to keep them here to emphasize the scaling with $1/\theta$).
+    We've rewritten this to make this more clear \revref.
 }
@@
 \reply{
+    We've added a clarifying point \revref.
 }
@@
 \reply{
+    Good question -- it could go either way,
+    but since there's more than one assumption, we'd like to keep it plural?
+    And, good point about re-use of $\alpha$; we've changed it to 
+    ``$\beta$-H\"older continuous for some $\beta \in (0, 1]$''.
 }
@@
 \reply{
+    The notation there was supposed to convey what exactly about $f$ the constant $C_f$
+    depends on, i.e., it could be defined via a function $C : \IR_{\ge 0} \to \IR_{\ge 0}$
+    whose argument is the stuff in the parentheses.
+    We could write this out explicitly, but think it's fairly standard to write things this way
+    -- if on re-reading it is still confusing, we're happy to change it, though?
 }
@@
 \reply{
+    We intended the \emph{next} sentence to explain why this is true;
+    to make this more clear
+    we changed that sentence from
+    \emph{``Perhaps the simplest example in which we can see this is the case''}
+    to
+    \emph{``Perhaps the simplest example in which we can see
+    that non-local reproduction can lead to rapid growth even when $r\gamma=\mu$''}
+    \revref.
 }
@@
 \begin{point}{}
-Figure 1: What is $N$, the time and other parameters (e.g. $\rho_r$ , $\rho_\gamma$) in the simulations? Same
+    Figure \ref{fig:super_vs_det_2d}: What is $N$, the time and other parameters (e.g. $\rho_r$ , $\rho_\gamma$) in the simulations? Same
 for other figures. Please at least specify the range of values.
@@
 \reply{
+    We've added some more detail to the caption.
 }
@@
 \reply{
+    Perhaps Evans/Perkins 1994 ``Measure-valued branching diffusions'' for Dawson's Girsanov thm?
+    (reproduced as Thm IV.1.6 in Perkins, "Dawson-Watanabe Superprocesses...").
 }
@@
 \reply{
+    Good point! Done.
 }
@@
 \reply{
-    Since you need to apply the Laplacian to it.
+    Good idea; done \revref.
 }
 
-\begin{point}{\revref}
-% P16: Second paragraph:
+\begin{point}{}
+P16: Second paragraph:
 The notation $L_t$ seems to first appear here and was not yet defined.
@@
 \reply{
-    (Note: they said ``P16: Second paragraph''; I think they just missed it on the previous page.)
+    Ah, true - now we introduce it (albeit still informally) earlier \llname{Linf_mention}.
 }
@@
 \reply{
+    We've retitled this section, and added a citation \revref.
 }
@@
 \reply{
+    Done \revref.
 }
@@
 \reply{
+    This was correct as written;
+    we've rephased it to be more clear \revref.
 }
@@
 \reply{
+    We've removed the $\max$ in \eqref{eqn:mu_defn}.
 }
@@
 \reply{
-    ``Since this is a finite-rate jump process...''
+    Done \revref.
 }
@@
 \reply{
+    We mean for each $\omega$; now clarified \revref.
 }
@@
 \reply{
+    Good suggestion; we've clarified, see \revref and \llname{XU_clarification}.
 }
 
-\begin{point}{\revref}
+\begin{point}{}
 The word ``Proof'' is missing in ``Proof of Proposition 5.6''. This word is also
@@
 \reply{
+    Whoops! That was due to a \LaTeX format change; now fixed.
 }
@@
 \reply{
+    We think this was an unedited duplicate of point 1.24 above?
 }
@@
 \reply{
+    Happily, there were no remaining results that we hadn't already said where the proofs were,
+    so this line is deleted. We also said that ``the process'' is $\lp$ \revref.
 }
@@
 \reply{
+    Good point - these were not called ``conditions'' in Lemma~\ref{lem:conditions on r},
+    so we now refer to them as ``assumptions'' \revref.
 }
@@
 \reply{
+    We've made the bounds here (and below) more explicit.
+    \revref
 }
@@
 \reply{
+    The fact is that we can bound the expectation of the quadratic variation by a constant times the expectation of the angle bracket process;
+    rather than explain again here we refer to the previous place we used the same argument
+    \revref.
 }
@@
 The notation $\mathcal{O}(\delta)$ seems to first appear here. Please explain its meaning. Do they
-depend on x?
+depend on $x$?
 \end{point}
@@
 \reply{
+    We've clarified this (but also note that the expression does not depend on $x$) \revref.
 }
@@
 \reply{
+    Done. \revref
 }
@@
 \reply{
+    Thanks! We didn't think that any modifications were necessary, though.
 }

### 2023-12-15 forwards-and-backwards.tex
addressed most of the comments

@@
 
-\comment{TODO: double-check $\langle \cdot \rangle$ versus $[\cdot]$}
-\comment{TODO: check factor of 2}
+\comment{TODO: insert statement that one might be worried about $\eta_t$ being well-defined as a process, in e.g., Def'n 5.2 and following?}
 
@@
 forests thicken or thin or change their composition;
-even in flat plains
-springtime grasslands host intergrading mosaics of different types of flowers.
+even in flat plains,
+springtime prairies host intergrading mosaics of different types of flowers.
 The aim of this paper is to introduce and study
@@
 \citet{bolker/pacala:1997} and \citet{law/murrell/dieckmann:2003},
-and subsequently studied, e.g., by \citet{etheridge:2004} and \citet{fournier2004microscopic}.
+and our work follows various others in the mathematical literature
+(e.g., \citet{etheridge:2004,fournier2004microscopic}).
 
@@
 The history of a natural population is often only accessible indirectly, 
-through patterns of genetic diversity that have been laid down; from 
-genetic data, one can try to infer the genealogical trees that relate 
-individuals in a sample from the population, and these have been shaped 
+through patterns of genetic diversity:
+from genetic data, one can try to infer the genealogical trees that describe how
+individuals in a sample from the population are related, and these have been shaped 
 by its history (see e.g., \citep{neigel1993application,kelleher2019inferring}).
@@
 To this end, we define
-the death rate of an individual at $x$ to be \revpoint{1}{4}
+the death rate of an individual at $x$,  \revpoint{1}{4}
+using a function $F(x, m) : \IR^d \times \IR_{\ge 0} \to \IR$,
+as
 \begin{align} \label{eqn:mu_defn}
@@
     =
-    \max\left\{0, 
         r(x, \smooth{r} X(x) / N) \gamma(x, \smooth{\gamma} X(x) / N)
         - \frac{1}{\theta} F(x, \smooth{F} X(x) / N)
-    \right\} ,
+    ,
 \end{align}
-where this equation also introduces $F(x, m) : \IR^d \times \IR_{\ge 0} \to \IR$,
-and $\rho_F$ is again a smooth kernel. 
+where $\rho_F$ is again a smooth kernel. 
+(We will also assume that parameters are chosen so that this is always nonnegative,
+a point we return to later.)
 The function $F$ is nearly
@@
 At instantaneous rate $\theta \gamma(x, \eta^N_t) N \eta^N_t(dx)$ an offspring of mass $1/N$ is 
-produced at location $x$; it disperses to 
-a location $y$ offset from $x$
-by an independent Gaussian random variable with mean $\meanq(x) / \theta$ \revpoint{1}{6}
-and covariance matrix $\covq(x) / \theta$,
+produced at location $x$, which
+immediately disperses to a location $y$ offset from $x$
+by an independent Gaussian random variable,
 and once there establishes instantaneously \revpoint{1}{5}
 with probability $r(y, \eta^N_t)$, or else dies. 
+The distribution of the dispersal displacement (i.e., $y-x$) may depend on $x$,
+and is specified by functions defining the mean $\meanq(x) / \theta$ \revpoint{1}{6}
+and covariance matrix $\covq(x) / \theta$.
 At instantaneous rate $\theta \mu_\theta(x, \eta^N_t) N \eta^N_t(dx)$ an individual at location 
@@
         =
-        \sum_{ij} \covq(x)_{ij} \partial_{x_i} \partial_{x_j} f(x)
+        \frac{1}{2} \sum_{ij} \covq(x)_{ij} \partial_{x_i} \partial_{x_j} f(x)
         + \sum_i \meanq(x)_i \partial_{x_i} f(x)
@@
         &=
-        \sum_{ij} \partial_{x_i} \partial_{x_j} (\covq(x)_{ij} f(x))
+        \frac{1}{2} \sum_{ij} \partial_{x_i} \partial_{x_j} (\covq(x)_{ij} f(x))
         - \sum_i \partial_{x_i} (f(x) \meanq(x)_i) 
@@
         % &=
-        % \sum_{ij} \partial_{x_i} \partial_{x_j} (\covq(x)_{ij} f(x))
+        % \frac{1}{2} \sum_{ij} \partial_{x_i} \partial_{x_j} (\covq(x)_{ij} f(x))
 	    % -\nabla f(x)\cdot \meanq(x)-f(x)\nabla\cdot\meanq(x).
         &=
-        \sum_{ij} C_{ij}(x) \partial_{x_i} \partial_{x_j} f(x)
+        \frac{1}{2} \sum_{ij} C_{ij}(x) \partial_{x_i} \partial_{x_j} f(x)
         + \sum_i \left(
-            \sum_j \partial_{x_j} C_{ij}(x) - \meanq_i(x)
+            \frac{1}{2} \sum_j \partial_{x_j} C_{ij}(x) - \meanq_i(x)
         \right) \partial_{x_i} f(x)
@@
         + \left(
-            \sum_{ij} \partial_{x_i} \partial_{x_j} C_{ij}(x)
+            \frac{1}{2} \sum_{ij} \partial_{x_i} \partial_{x_j} C_{ij}(x)
             -
@@
 In the simplest case of unbiased isotropic dispersal
-(i.e.,~$\meanq = 0$ and $\covq = I$), $\DG = \Delta$,
+(i.e.,~$\meanq = 0$ and $\covq = I$), $\DG = \Delta/2$,
 and so~(\ref{weighted dispersal}) is equal to
 \begin{align*}
-    \Delta f(x) + 2 \grad f(x) \cdot \grad \log r(\cdot, \smooth{r} \eta(\cdot))(x) .
+    \frac{1}{2} \Delta f(x) + \grad f(x) \cdot \grad \log r(\cdot, \smooth{r} \eta(\cdot))(x) .
 \end{align*}
@@
     \item $\meanq(x)$ and $\covq(x)$ are
-        $\alpha$-H\"older continuous for some $\alpha \in (0, 1]$
+        $\beta$-H\"older continuous for some $\beta \in (0, 1]$
         and uniformly bounded
@@
     \] \label{gamma_B_condition} \revpoint{1}{9}
+\item To keep expressions manageable, we shall also assume that  \revpoint{1}{1}
+    the death rate (as defined in~\eqref{eqn:mu_defn}) is nonnegative, i.e., that
+    \[
+    \mu_\theta(x) = r(x,\eta) \gamma(x,\eta) - \frac{1}{\theta} F(x,\eta) \ge 0 .
+    \]
 \end{enumerate}
-To keep expressions manageable, we shall also assume that  \revpoint{1}{1}
-\[
-\mu_\theta(x) = r(x,\eta) \gamma(x,\eta) - \frac{1}{\theta} F(x,\eta),
-\]
-that is, this expression is non-negative so that there is no need to take the maximum
-	with zero in~(\ref{eqn:mu_defn}). (This is anyway true for 
-	sufficiently large $\theta$.)
 \end{assumptions}
+
+Since $F$ is bounded above,
+the final assumption that $\mu_\theta \ge 0$ --
+or, equivalently, that $F(x,\eta) \le \theta r(x,\eta) \gamma(x,\eta)$ --
+will always be true, for instance, for large enough $\theta$ 
+as long as $r$ and $\gamma$ are bounded away from zero.
 
@@
 $r(x,\eta)\gamma(x,\eta)-\mu_\theta(x)$ is of order $1/\theta$.
-Perhaps the simplest example in which we can see this
-is the case where $\gamma \equiv 1$ and $F \equiv 0$, so that $\mu_\theta = r$,
+Perhaps the simplest example in which we can see
+that non-local reproduction can lead to rapid growth even when $r\gamma=\mu$
+is where $\gamma \equiv 1$ and $F \equiv 0$, so that $\mu_\theta = r$,
 and $\eta = \delta_x$
@@
         Snapshots of two simulations, with small $\alpha=\theta/N$ (left) and large 
-	$\alpha =\theta/N$ (right).
+	$\alpha = \theta/N$ (right).
         Simulations are run with a Fisher-KPP-like parameterization:
@@
         Other parameters were the same:
-        dispersal and interactions distance were set to 1,
-        and the equilibrium density is 10 individuals per unit area.
+        dispersal ($q_\theta$) and interactions (here, only $\rho_F$)
+        are Gaussian with standard deviation 1,
+        and the equilibrium density (also, $N$) is 10 individuals per unit area.
+        The remaining parameters are constant: $r \equiv \gamma \equiv 1$.
         \label{fig:super_vs_det_2d}
@@
 $\psi_0^\epsilon\geq 0$ is such that
-there exist $\lambda\in (0,1)$ and $C\in (0,\infty)$ (independent
-of $\epsilon$) such that 
+there exists $\lambda\in (0,1)$
 \begin{equation*}
-\int\exp(\lambda \|x\|)\psi_0^\epsilon(x)dx<C,\quad\mbox{ and }
-\sup_\epsilon\int \psi_0^\epsilon|\log \psi_0^\epsilon|dx<\infty,
+\sup_\epsilon \int\exp(\lambda \|x\|)\psi_0^\epsilon(x)dx < \infty,\quad\mbox{ and }
+\sup_\epsilon\int \psi_0^\epsilon|\log \psi_0^\epsilon|dx < \infty,
 \end{equation*}
@@
 suggests that even if one can remove the local averaging from $\gamma$, it
-will be necessary
-to retain averaging of $r$ in order to obtain a well-defined limit. 
+will be necessary \revpoint{1}{14}
+to retain averaging of $r$ in order to obtain a well-defined limit 
+(since otherwise the term $\DG(f(\cdot)r(\cdot,\eta))(x)$
+may not be well-defined).
 \end{remark}
@@
 begun at a spatial location $L_0^N = x$
-where there is a focal individual in the present day
-can be obtained by, for each time $t$,
+where there is a focal individual in the present day,
+can be obtained for each time $t$ by
 setting $L_t^N$ to be the spatial location of the individual alive at time $t$
@@
 
-The \emph{lookdown construction} in Section~\ref{sec:lookdown}
-will enable us to recover information about ancestry in the infinite
-population limit.
+However, the \emph{lookdown construction} in Section~\ref{sec:lookdown}
+does just this -- \llabel{whatis_lineage}
+the construction enables us to recover information about ancestry
+in the infinite population limit,
+and thus give a concrete meaning to $(L_t)_{t \ge 0}$. \llabel{Linf_mention}
 Roughly speaking,
@@
 
-We are interested in two questions.
+We are interested in two questions about the limiting process.
 First, when is the motion of an ancestral 
@@
 \begin{definition}[Ancestral lineage] 
-\label{def:lineage_generator} \revpoint{1}{2}
+\label{def:lineage_generator}
     Let $(\varphi_t(x))_{0 \le t \le T}$
@@
 solving \eqref{eqn:nonlocal_pde},
-    and let $y$ be a point with $\varphi_T(y) > 0$.
+    let $y$ be a point with $\varphi_T(y) > 0$,
+    and suppose we have sampled an individual from location $y$ at time $T$.
     We define $(L_s)_{s=0}^T$,
-    the ancestral lineage of an individual sampled from the
-population at $y$ at time $T$, by setting $L_0=y$ and $L_s$
-    to be the position of the unique ancestor of that individual at time $T - s$.
+    the ancestral lineage of that sampled individual by setting $L_0=y$
+    and $L_s$ to be the position of the unique ancestor of that individual at time $T - s$.
     We define
@@
 
-Our next result identifies the ancestral lineage as a diffusion
+The precise sense in which we can look at ``the lineage of a sampled individual'' \revpoint{1}{2}
+in the scaling limit is made clear by the introduction of the lookdown construction,
+in Section~\ref{sec:lookdown}.
+(For now, we can take the definition to refer to the distribution obtained
+from a scaling limit of the finite-$N$ process.)
+It turns out that in the scaling limit,
+the process is Markovian,
+and our next result identifies the ancestral lineage as a diffusion
 by characterizing its generator.
@@
         \left[
-            \sum_{ij} \covq_{ij} \partial_{x_ix_j} f
+            \frac{1}{2} \sum_{ij} \covq_{ij} \partial_{x_ix_j} f
             + \sum_j \vec{m}_j \partial_{x_j} f
@@
     =
-    2 \sum_i C_{ij} \partial_{x_i} \log(\gamma \varphi)
-    + 2 \sum_i \partial_{x_i} C_{ij}
+    \sum_i C_{ij} \partial_{x_i} \log(\gamma \varphi)
+    + \sum_i \partial_{x_i} C_{ij}
     - \meanq_j .
@@
 \end{theorem}
+
 \begin{remark}
@@
         =
+        \frac{\sigma^2}{2}
         r \gamma
         \left(
-            \sigma^2 \Delta f
+            \Delta f
             +
             \left(
-                2 \sigma^2 \grad \log(\gamma \varphi)
-                - \meanq
+                2 \grad \log(\gamma \varphi)
+                - \frac{2 \meanq}{\sigma^2}
             \right)
@@
 mature offspring ($r \gamma$)
-in a potential tilted by migration bias
-($(\varphi_s \gamma)^2 \exp(-\meanq \cdot x / \sigma^2)$,
-whose gradient appears in the drift term of the generator).
+with mean displacement in the direction of $\grad \log(\varphi_s \gamma) - \meanq$.
 In particular, lineages are drawn to regions of high fecundity (production of juveniles), but their
@@
         =
-        \frac{\gamma}{r} \varphi(x)^2 e^{-h(x) / \sigma^2} .
+        \frac{\gamma}{r} \varphi(x)^2 e^{-2 h(x) / \sigma^2} .
     \end{align}
@@
         r \DG^* (\gamma w) + w F + \wavespeed \cdot \grad w = 
-r\sigma^2\Delta (\gamma w) -\meanq \cdot\grad (\gamma w) +\wavespeed \cdot \grad w =0 .
+        \frac{1}{2} r\sigma^2\Delta (\gamma w) -\meanq \cdot\grad (\gamma w) +\wavespeed \cdot \grad w =0 .
     \end{align*}
@@
         &=
-        \sigma^2 r \gamma
+        \frac{1}{2} \sigma^2 r \gamma
         \left(
@@
 see~\cite{sherratt:2010} and references therein for further discussion. 
-In particular, it has been suggested as a model for
+In particular, such equations have been suggested as a model for
 the expansion of a certain type of bacteria % of the type {\em Paenbacillus dendritiformis}
@@
 
-Comparing %\eqref{PME} 
-with \eqref{eqn:nonlocal_pde},
+Comparing with \eqref{eqn:nonlocal_pde},
 we see that to set up a limit in which the population density $\varphi$ follows the 
@@
 Consulting equation~\eqref{eqn:mu_defn},
-this implies that $\mu_\theta = \max\big(0, (1 + 1/\theta) \varphi - 1/\theta\big)$.
+this implies that $\mu_\theta = (1 + 1/\theta) \varphi - 1/\theta$.
 In other words,
@@
 We work here in one dimension,
-and take $\sigma^2 = 1$ and $\meanq = 0$.
+and take $\sigma^2 = 2$ and $\meanq = 0$.
 
@@
 and using Corollary~\ref{cor:stationary_dist},
-i.e., by giving each offspring a mean displacement that offsets the motion of the wave.
+i.e., by giving each offspring a mean displacement that offsets the motion of the wave
+(The model is different because this motion only affects offspring, not adults.)
 In the Fisher-KPP and Allen-Cahn cases above, we get the same expressions,
@@
 as shown in Figure~\ref{fig:clumping}.
-The phenomenon is discussed in Section~16.10 of \citet{haller2022evolutionary},
+The phenomenon is discussed in Section~16.15 of \citet{haller2022evolutionary},
 and has been described in similar models, e.g.,
@@
 More mathematically, consider the case in which
-$\DG = \sigma^2 \Delta$ and all 
-parameters are spatially homogeneous,
+$\DG = \sigma^2 \Delta$
+(so that dispersal variance is $2 \sigma^2$)
+and all parameters are spatially homogeneous,
 so that $r(x, \eta) = r(\smooth{r}\eta(x))$, and similarly for $\gamma$ and $F$.
@@
 \begin{equation*}
-	\partial_t \hat \psi(u) =
+	\partial_t \hat \psi(u) \approx
     \frac{1}{\sqrt{2\pi}}
@@
 % % % % % % % % % % % % % % % %
-\subsection{Lineage motion is not uniquely determined by population density}
+\subsection{Lineage motion distinguishes different models with the same equilibrium density}
 \label{sec:nonunique_lineage}
@@
 (because, for instance, making reproductive value less evenly distributed
-reduces long-term genetic diversity). \revpoint{1}{18}
+reduces long-term genetic diversity \citep{ewens:1982}). \revpoint{1}{18}
 
@@
 with mean zero and covariance $\sigma^2 I / \theta$,
-then $\DG = \sigma^2 \Delta$, where $\Delta$ denotes the Laplacian.
+then $\DG = \sigma^2 \Delta / 2$, where $\Delta$ denotes the Laplacian.
 
@@
 
-\paragraph{One-step convergence:}
+\paragraph{One-step convergence:} \label{sec:one_step_heuristics} \llabel{one_step_heuristics}
 In order to pass directly to a classical PDE limit
@@
 take $\theta/(N\epsilon^d)\to 0$.
+Concretely,
+since $\|\rho^\epsilon_F\| \propto \epsilon^{-e/2}$,
+the quadratic variation of $F(\rho^\epsilon_F\!*\!\eta(x))$
+is proportional to $\theta/(N\epsilon^d)$.
 
@@
 
-{\em For the remainder of this section, when there is no risk of ambiguity we shall
+{\em For the remainder of this subsection, when there is no risk of ambiguity we shall
 suppress the superscript $N$ on the processes $\eta$ and $\xi$.}
@@
 A nontrivial consequence of the way we define $\lp_t$ will be that
-this process \revpoint{1}{19}
+the process $(\eta_t)_{t \ge 0}$ defined in this way \revpoint{1}{19}
 has the same distribution as the process $(\eta_t)_{t \ge 0}$ 
-of Definition~\ref{defn:mgale_construction}.
-(This provides our justification for using the same notation for both.)
+of Definition~\ref{defn:mgale_construction},
+which provides our justification for using the same notation for both.
 
@@
 
-Levels never cross below 0, \revpoint{1}{20}
-while particles whose levels move above $N$ are regarded as dead
+This drift does not allow levels to cross below 0, \revpoint{1}{20}
+while we will declare that particles whose levels move above $N$ are regarded as dead
 (and are removed from the population).
@@
 \end{equation}
-Under Assumptions~\ref{def:model_setup}, as $\theta \to \infty$ and
-$c_\theta(x, \eta)$ will tend to $\alpha \gamma(x, \eta) r(x, \eta)$
+Under Assumptions~\ref{def:model_setup}, as $\theta \to \infty$,
+$c_\theta(x, \eta)$ will tend to $\alpha \gamma(x, \eta) r(x, \eta)$, and
 \begin{equation}
@@
 
-The martingale problem for finite $N$ has a unique solution. \revpoint{1}{22}
+The martingale problem for finite $N$ has a unique solution, \revpoint{1}{22}
+since it is a finite-rate jump process.
 Next we state the limiting martingale problem,
@@
         \right)
-        \frac{\partial_u g(x, u)}{ g(x,u) }  .
+        \frac{\partial_u g(x, u)}{ g(x,u) }  ,
     \end{split} \end{align}
+    where $\eta(\cdot) = \frac{1}{u} \lim_{u \to \infty} \xi(\cdot \times [0, u])$.
     We say that a ${\mathcal D}_{[0,\infty)}(\mathcal{C})$-valued process $(\xi_t)_{t \ge 0}$
@@
 As a result, if the spatial projections $\eta$ converge, then
-individual lines of descent converge pointwise as $N \to \infty$. \revpoint{1}{23}
+individual lines of descent converge pointwise (i.e., for each realization of $\{\Pi_a\}_{a \in \labelspace}$)
+as $N \to \infty$. \revpoint{1}{23}
 To see this, first note that if the Poisson processes are fixed
@@
 We write out the differential operator above in more detail.
-Recall that $\DG g(x) = \sum_i \meanq_i \partial_i g(x) + \sum_{ij} \covq_{ij} \partial_{ij} g(x)$,
+Recall that $\DG g(x) = \sum_i \meanq_i \partial_i g(x) + \frac{1}{2}\sum_{ij} \covq_{ij} \partial_{ij} g(x)$,
 and for the moment write $r(x)$ for $r(x, \eta)$, $\meanq(x) = \meanq$, and $\covq(x) = \covq$
@@
     r(x) \sum_i \meanq_i \partial_i g(x)
-    + 2 \sum_{ij} \partial_i r(x) \covq_{ij} \partial_j g(x)
-    + r(x) \sum_{ij} \covq_{ij} \partial_{ij} g(x) \\
+    + \sum_{ij} \partial_i r(x) \covq_{ij} \partial_j g(x)
+    + \frac{1}{2} r(x) \sum_{ij} \covq_{ij} \partial_{ij} g(x) \\
     &= \label{eqn:limiting_generator}
@@
         \meanq
-        + 2 \covq \grad \log r(x)
+        + \covq \grad \log r(x)
         \right)
@@
         +
-        \sum_{ij} \covq_{ij} \partial_{ij} g(x)
+        \frac{1}{2} \sum_{ij} \covq_{ij} \partial_{ij} g(x)
     \right\} .
@@
     r(x,\eta)\gamma(x,\eta)\covq(x) = J(x,\eta) J(x,\eta)^T \\
-    \beta(x, \eta) = r(x,\eta)\gamma(x,\eta)\big(\meanq(x) + 2 \covq(x) \grad \log r(x, \eta)\big) .
+    \beta(x, \eta) = r(x,\eta)\gamma(x,\eta)\big(\meanq(x) + \covq(x) \grad \log r(x, \eta)\big) .
 \end{gather*}
@@
     location $X_{a \concat j}(\tau) = X_a(\tau)$, and level
-$$
+\begin{align} \label{eqn:limiting_constribution_U}
     U_{a \concat j}(\tau) = U_a(\tau)
     + \frac{v}{ 2 \alpha \gamma(X_a(\tau), \eta_\tau) r(X_a(\tau), \eta_\tau) } ,
-$$
+\end{align}
 if this is finite.
-For any solution to the equations above, \revpoint{1}{24}
+For any solution $\{(X_a(t), U_a(t))_{t \ge 0}: a \in \labelspace \}$  \revpoint{1}{24}
+to~\eqref{eqn:limiting_construction} and~\eqref{eqn:limiting_constribution_U},
 the process $\eta_t$
@@
 and the process
-\begin{align*}
+\begin{align} \label{eqn:lp_defn_XU}
     \lp_t = \sum_{a : \tau_a \le t < \sigma_a} \delta_{(X_a(t), U_a(t))} 
-\end{align*}
+\end{align}
 is a solution to the martingale problem of
@@
 
-\comment{TODO: add note about well-definedness of $\eta_t$.}
-
-\begin{proof}[of Proposition~\ref{prop:limiting_construction}] \revpoint{1}{25}
-    The fact that a solution to the system of equations~\eqref{eqn:limiting_construction}
+\begin{proof}[Proof of Proposition~\ref{prop:limiting_construction}:]
+    Let $(X, U) = \{(X_a(t), U_a(t))_{t \ge 0}: a \in \labelspace \}$ \llabel{XU_clarification}
+    be a solution to the system of equations~\eqref{eqn:limiting_construction}
+    and~\eqref{eqn:limiting_constribution_U}.
+    The fact that $\lp$ defined with these using~\eqref{eqn:lp_defn_XU}
     is a solution to the martingale problem of Theorem~\ref{thm:lookdown_convergence}
@@
     to the martingale problem of Theorem~\ref{thm:nonlocal_convergence}.
+
+\comment{TODO: add note about well-definedness of $\eta_t$.}
+    However, for this to be valid, one should first make sure that $\eta_t$
+    is a well-defined process.
+    We do know that 
 \end{proof}
 
-Proofs of the remainder of these results are in Section~\ref{sec:lookdown_proofs}. \revpoint{1}{27}
-
 \begin{remark} \label{remark_on_branching}
-The process we consider is similar to the state-dependent branching processes
+The process $\lp$ we consider is similar to the state-dependent branching processes \revpoint{1}{27}
 of \citet{kurtz/rodrigues:2011}, so one might expect that the proofs there would carry over with little change.
@@
 
-\begin{proof}[of Lemma~\ref{lem:conditions on r}]
+\begin{proof}[Proof of Lemma~\ref{lem:conditions on r}:]
 Here, we need to prove that $|\gamma(x, \eta) B^\theta_f(x, \eta)|$ is bounded,
@@
 First suppose that
-Condition~\ref{control through r} of  
+assumption~\ref{control through r} of  
 Lemma~\ref{lem:conditions on r} is satisfied. \revpoint{1}{28}
@@
 Now suppose instead that
-Condition~\ref{control through gamma} of Lemma~\ref{lem:conditions on r} is satisfied.
+assumption~\ref{control through gamma} of Lemma~\ref{lem:conditions on r} is satisfied.
 First note that
@@
     So, writing $K_5=\|r'\|_\infty$ and $K_6=\|r''\|_\infty$,
-    the second term in~\eqref{eqn:q_bound_split} is bounded by $f(x)$ multiplied by
+    the second term in~\eqref{eqn:q_bound_split} is bounded by $|f(x)|$ multiplied by
     \begin{align*}
@@
 $\sup_x m^2\gamma(x, m)$ is bounded,
-so therefore $|\gamma(x,\eta) B^\theta_f(x,\eta)| \le K_7 + K_8 f(x)$,
+so therefore $|\gamma(x,\eta) B^\theta_f(x,\eta)| \le K_7 + K_8 |f(x)|$,
 where $K_7$ comes from $K_3$, $K_4$, and the supremum of $\gamma$,
@@
 \begin{proof}[Proof of Theorem~\ref{thm:nonlocal_convergence}.]
-The proof follows a familiar pattern. \revpoint{1}{29}
+The proof follows a familiar pattern \revpoint{1}{29}
+(see, for instance, Section~1.4 of~\citet{etheridge2000introduction}).
 First we extend $\IR^d$ 
@@
 under Assumptions~\ref{def:model_setup}
-$\gamma(x, \eta) B^\theta_f(x, \eta) + f(x) F(x, \eta) \le C_f (1 + f(x))$ for some $C_f$.
+$\gamma(x, \eta) B^\theta_f(x, \eta) + f(x) F(x, \eta) \le C_f (1 + |f(x)|)$ for some $C_f$.
 
@@
         \IE\left[ \langle f, \eta^N_0 \rangle \right]
-        + C_f \int_0^t \IE\left[ \langle 1 + f, \eta^N_s \rangle \right] dt .
+        + C_f \int_0^t \IE\left[ \langle 1 + |f|, \eta^N_s \rangle \right] dt .
     \end{align}
@@
 \]
-with $C$ independent of $N$, and then substituting 
+with $C$ independent of $N$, and then using that $F$ is bounded and substituting 
 the resulting bound on $\IE\big[\langle 1,\eta_s^N\rangle\big]$ into the
@@
 \begin{proof}
-    First note that by Lemma~\ref{lem:eta_f_bound},
+    First note that by the proof of Lemma~\ref{lem:eta_f_bound},
     $\IE[\langle 1, \eta^N_t \rangle] \le \IE[\langle 1, \eta^N_0 \rangle] e^{Ct}$
@@
 which is bounded since $\gamma (x,\eta)$ and $B^\theta_1(x,\eta)$ are both bounded and 
-$\langle 1,\eta_t\rangle\geq 0$. 
+$\langle 1,\eta_t^N \rangle\geq 0$. 
     Since $\theta/N \to \alpha < \infty$,
@@
 $$
-is a martingale (with respect to the natural $\sigma$-field).
+is a martingale for all such test functions (with respect to the natural $\sigma$-field).
 
@@
 Recall that $f$ and $G$ and their derivatives are bounded,
-and so $\gamma(x,\eta)$ is bounded independent of $\theta$.
+and $\gamma(x,\eta)$ is bounded independent of $\theta$.
 Since $\theta/N^2 \to 0$,
@@
 and has $\langle f_0, \eta^N_0\rangle$ uniformly bounded in $N$.
-We take a sequence of test functions $f_n$ that increase to the function $f_0$
+We take a sequence of nonnegative test functions $f_n$ that increase to the function $f_0$
 and having uniformly bounded first and second derivatives,
@@
 we would like instead to uniformly bound
-$\IE[\sup_{0 \le t \le T} \langle f_0, \eta_t(dx)\rangle]$.
+$\IE[\sup_{0 \le t \le T} \langle f_n, \eta^N_t(dx)\rangle]$.
 This can be done in a similar but lengthier manner,
@@
 
-\begin{proof}[of Proposition \ref{prop:nonlocal_to_local}]
+\begin{proof}[Proof of Proposition \ref{prop:nonlocal_to_local}:]
 Let $\epsilon$ be small enough that Lemma~\ref{ContinuityConvolution} holds. 
@@
 where $p_t(x,y)$ denotes the heat semigroup. 
-The assumptions of Theorem~\ref{thm:local_convergence} will be in 
-force throughout, in particular, \revpoint{1}{3}
+The assumptions of Theorem~\ref{thm:local_convergence} will be in force throughout,
+in particular,
 \begin{equation}
     \label{conditions for one step}
-	\epsilon^2\theta\to\infty, \qquad\mbox{and }\frac{\theta}{N\epsilon^d}\to 0.
+	\epsilon^2\theta\to\infty, \qquad\mbox{and}\quad \frac{\theta}{N\epsilon^d}\to 0.
 \end{equation}
@@
 identifying the limit points in Subsection~\ref{limit in onestep case}.
+
+Roughly speaking, the assumption that $\theta/N\epsilon^d$ is small \revpoint{1}{3}
+is used in ensuring a well-defined and deterministic limit,
+while the assumption on $\epsilon^2 \theta$ is used in proving continuity.
+For more motivation behind these assumptions,
+see the last part of Section~\ref{sec:one_step_heuristics}.
 
@@
 for some constants $C$ and $C'$.
-Now, using the Burkholder-Davis-Gundy inequality and \citet{barlow/jacka/yor:1986}, \revpoint{1}{32}
+Now, using the Burkholder-Davis-Gundy inequality
+and the same fact as before from \citet{barlow/jacka/yor:1986}, \revpoint{1}{32}
 $\IE[\sup_{0 \le u \le T} |\widehat{M}^N(f)_u|^2] \le C'' \IE[\langle\widehat{M}^N(f)\rangle_u]$,
 and so using Markov's inequality,
+% \comment{I think for clarity there should be no $\epsilon^d$ in the denominator of the last expression? (This is harmless, though, as dividing by $\epsilon^d$ only makes this upper bound bigger.)}
 \begin{equation}
@@
     \leq
-    \limsup_{N\to\infty}\frac{36}{\nu^2}\frac{C' C''\theta}{N\epsilon^d} 
-    =0. 
+    \limsup_{N\to\infty}\frac{36}{\nu^2}\frac{C' C''\theta}{N}
+    = 0 .
 \end{equation}
@@
 We are going to use the estimate~(\ref{difference in rhos}).
-First note that by Lemma~\ref{bounds on moments}
+First note that by Lemma~\ref{bounds on moments} (with $u=0$),
 the contribution to~(\ref{target expression}) from the integral over
-the time interval $[0,\delta]$ is ${\mathcal O}(\delta)$. \revpoint{1}{33}
+the time interval $[0,\delta]$ is bounded by a constant multiple of $\delta$, \revpoint{1}{33}
+with a constant that depends only on $\eta_0$.
 We focus instead
@@
 our expressions for $M_s(y)$ and $M_s(w)$ and so all the manipulations 
-that we used to control terms above with still be valid.
+that we used to control terms above will still be valid.
 To deal with the two terms in the product involving $|M_s(y)|$, we write 
@@
 \int_0^t
-\int f(x) \rho_\epsilon * \eta_s(x) F(\rho_\epsilon * \eta_s^N(x)) dx ds 
+\int f(x) \rho_\epsilon * \eta_s^N(x) F(\rho_\epsilon * \eta_s^N(x)) dx ds 
 \rightarrow \int_0^t\int f(x) \varphi(s,x) F(\varphi(s,x)) dx ds. 
@@
 
-\begin{proof}[of Proposition~\ref{thm:mmt_application}]
+\begin{proof}[Proof of Proposition~\ref{thm:mmt_application}:]
     This proposition is the content of the Markov Mapping Theorem,
@@
     =
-    r(y, \eta) q(x, dy) / \int_{\IR^d} r(y, \eta) q(x, dy),
+    r(y, \eta) q(x, dy) / \int_{\IR^d} r(z, \eta) q(x, dz),
 \end{equation}
@@
 
-\begin{proof}[of Lemma~\ref{lem:compact containment hn}]
+\begin{proof}[Proof of Lemma~\ref{lem:compact containment hn}:]
     Let $h$ be as in Lemma~\ref{lem:h_containment},
@@
 
-\begin{proof}[of Lemma~\ref{lem:compact containment lookdown}]
+\begin{proof}[Proof of Lemma~\ref{lem:compact containment lookdown}:]
     By a union bound,
@@
 
-\begin{proof}[of Lemma~\ref{lem:h_containment}]
+\begin{proof}[Proof of Lemma~\ref{lem:h_containment}:]
     Applied to $f(x, u) = h(u)$, the martingale representation~\eqref{eqn:f_xi_mgale} is
@@
 
-\begin{proof}[of Lemma \ref{lem:test_fn_tightness}]
+\begin{proof}[Proof of Lemma \ref{lem:test_fn_tightness}:]
     Again, we use the Aldous-Rebolledo criterion.
@@
 
-\begin{proof}[of Theorem~\ref{thm:lineages}]
+\begin{proof}[Proof of Theorem~\ref{thm:lineages}:]
 For brevity, in the proof we write $\gamma(x)$ or $\gamma$ for $\gamma(x,\eta)$.
@@
 so if we
-use that $\partial_t \varphi_t = r \DG^*[ \varphi_t \gamma ] + \varphi F$
+use that $\partial_t \varphi_t = r \DG^*[ \varphi_t \gamma ] + \varphi_t F$
 (in a weak sense),
@@
 \end{align*}
-where $\vec{c}_j = \sum_i \partial_j \covq_{ij}$.
+where $\vec{c}_j = \sum_i \partial_i \covq_{ij}$.
 So, with $f = \gamma \varphi_s$,
@@
     \frac{r}{\varphi_s} \left[
-        \DD^*(\gamma \varphi_s g) - \grad \cdot (\gamma \varphi_s g \meanq)
-        - g \DD^*(\gamma \varphi_s) + g \grad \cdot (\gamma \varphi_s \meanq)
+        \frac{1}{2} \DD^*(\gamma \varphi_s g) - \grad \cdot (\gamma \varphi_s g \meanq)
+        - \frac{1}{2} g \DD^*(\gamma \varphi_s) + g \grad \cdot (\gamma \varphi_s \meanq)
     \right] \\
@@
     \frac{r}{\varphi_s} \left[
-        \gamma \varphi_s \DD g
-        + 2 \gamma \varphi_s \vec{c} \cdot \grad g
-        + 2 (\covq \grad (\gamma \varphi_s)) \cdot \grad g
+        \frac{1}{2} \gamma \varphi_s \DD g
+        + \gamma \varphi_s \vec{c} \cdot \grad g
+        + (\covq \grad (\gamma \varphi_s)) \cdot \grad g
         - \gamma \varphi_s \meanq \cdot \grad g
@@
     r \gamma \left[
-        \DD g
-        + 2 \vec{c} \cdot \grad g
-        + 2 (\covq \grad \log(\gamma \varphi_s)) \cdot \grad g
+        \frac{1}{2} \DD g
+        + \vec{c} \cdot \grad g
+        + (\covq \grad \log(\gamma \varphi_s)) \cdot \grad g
         - \meanq \cdot \grad g
@@
 
-\begin{proof}[of Corollary~\ref{cor:stationary_dist}]
+\begin{proof}[Proof of Corollary~\ref{cor:stationary_dist}:]
 For the moment, we will write $r(x)$ for $r(x,\eta)$
@@
     \Lgen f = \sigma^2 r \gamma \left(
-        \Delta f
-        + \grad ( 2 \log(\gamma \varphi) - h/\sigma^2 ) \cdot \grad f
+        \frac{1}{2} \Delta f
+        + \grad ( 2 \log(\gamma \varphi) - 2h/\sigma^2 ) \cdot \grad f
     \right) .
@@
 $$
-so that by choosing $H(x) = 2 \log(\gamma(x) \varphi(x)) - h(x)/\sigma^2$
+so that by choosing $H(x) = 2 \log(\gamma(x) \varphi(x)) - 2h(x)/\sigma^2$
 and
 $$ \pi(x)
-    = e^{H(x)} / (\sigma^2 r(x) \gamma(x))
-    = \frac{\gamma(x) \varphi(x)^2 e^{-h(x)/\sigma^2}}{\sigma^2 r(x)} ,
+    = \frac{2e^{H(x)} }{ (\sigma^2 r(x) \gamma(x)) }
+    = \frac{2\gamma(x) \varphi(x)^2 e^{-2h(x)/\sigma^2}}{\sigma^2 r(x)} ,
 $$
@@
 $$
-Since this is symmetric in $f$ and $g$, the process $Y$ is reversible with respect to $\pi$;
-the constant factor of $\sigma^2$ does not affect the result.
+Since this Dirichlet form is symmetric in $f$ and $g$,
+the process $Y$ is reversible with respect to $\pi$
+(and the factor of $\sigma^2$ is constant).
 \end{proof}
@@
 
-\begin{proof}[of Lemma~\ref{lem:averaged_generators}]
+\begin{proof}[Proof of Lemma~\ref{lem:averaged_generators}:]
 First, break the generator $A^N$ into three parts, 
@@
 
-\begin{proof}[of Lemma~\ref{lem:averaged_generators_limit}]
+\begin{proof}[Proof of Lemma~\ref{lem:averaged_generators_limit}:]
 By Lemma~\ref{lem:poisson_eqn},
@@
 
-\begin{proof}[of Lemma \ref{lem:gamma_bound}]
+\begin{proof}[Proof of Lemma \ref{lem:gamma_bound}:]
 
@@
 
-\begin{proof}[of Lemma~\ref{lem:product_tightness}]
+\begin{proof}[Proof of Lemma~\ref{lem:product_tightness}:]
     The proof for $X^{(n)} + Y^{(n)}$ is similar to but more straightforward than
@@
 
+\PAGEEND{\thepage}
 % reviews here if toggled above

### 2023-12-15 review-responses.tex
.

@@
 \reply{
+    \comment{TODO:
     Perhaps Evans/Perkins 1994 ``Measure-valued branching diffusions'' for Dawson's Girsanov thm?
-    (reproduced as Thm IV.1.6 in Perkins, "Dawson-Watanabe Superprocesses...").
+    (reproduced as Thm IV.1.6 in Perkins, "Dawson-Watanabe Superprocesses...").}
+    But: that is for two species.
 }
@@
 \reply{
+    \comment{TODO:
     The PME is new;
@@
     find other references for this (i.e., the $\grad \log$...)
+    }
 }
@@
 \reply{
-    Just say we don't know, but:
-    see Pennington and Etheridge on bistable waves
-    where fluctuations in the wave happen on long time scales
+    Good question -- we've added a note about this question \revref.
 }

### 2023-12-15 forwards-and-backwards.tex
.

@@
 However, the Dawson--Girsanov transform tells us that we have uniqueness \revpoint{1}{12}
-in this special case of the superprocess with nonlinear death rates, and 
-Perkins stochastic calculus (and its adaptation to a 
-lookdown setting) provides uniqueness for cases with interactions in the 
-dispersal mechanism of
-the superprocess. We refer 
-to~\cite{dawson:1993, perkins:1992}, and \cite{donnelly/kurtz:1999} 
+in this special case of the superprocess with nonlinear death rates \cite{dawson:1993}.
+The Perkins stochastic calculus
+(and its adaptation to a lookdown setting \cite{donnelly/kurtz:1999})
+provides uniqueness for a different but related class of processes,
+in which interactions affect the dispersal mechanism
+(rather than reproduction) of the superprocess \cite{perkins:1992}.
+We refer to~\cite{dawson:1993, perkins:1992}, and \cite{donnelly/kurtz:1999} 
 for approaches to showing that these sorts of martingale problems are well-posed.
@@
 either a nonlocal or a classical PDE.
-There will be no 
-coalescence of ancestral lineages in the deterministic limit,
+There will be no coalescence of ancestral lineages in the deterministic limit,
 but understanding motion of single lineages is useful in practice,
@@
 be seen as a first step towards understanding genealogies for high population densities. 
+Since the time scale on which coalescence occurs \revpoint{1}{17}
+goes to infinity in the deterministic limit,
+an important question to answer will be whether this description of lineage motion
+is a good approximation over such a long time scale.
+Other information may be important -- for instance, in \citet{etheridge/pennington:2022}
+the form of the coalescent that is obtained depends
+on fluctuations happening on a longer time scale than the mixing time of a lineage.
 

### 2023-12-20 review-responses.tex
final plr edits

@@
 We are writing to submit a revised version of our manuscript,
-ETCETERA
+``Looking forwards and backwards: dynamics and
+genealogies of locally regulated populations''.
+Thanks to the reviewer's comments
+(as well as separate comments from Mattias Birkner),
+we think the manuscript has been improved and clarified in a number of places,
+a few (happily, relatively minor) errors and omissions
+have been fixed,
+and the manuscript is generally improved.
+We hope you agree.
+
+We have submitted a clean version of the revised paper and
+the response to the reviewer as separate PDFs;
+line numbers in this response refer to the ``clean'' version.
+Also, we have submitted a single PDF
+with changes to the previous version shown (with latexdiff)
+and a version of the response to reviewer at the end of the document.
+In this combined ``diff''document, line numbers (and hyperlinks)
+in the reviewer responses are consistent within the document.
 
@@
 
-Thanks ETCETERA
+Thanks for the many kind words.
+We're glad you enjoyed it.
 
@@
 \reply{
-    \comment{TODO:
-    Perhaps Evans/Perkins 1994 ``Measure-valued branching diffusions'' for Dawson's Girsanov thm?
-    (reproduced as Thm IV.1.6 in Perkins, "Dawson-Watanabe Superprocesses...").}
-    But: that is for two species.
+    Good suggestion -- this was rather cryptic.
+    We've expanded on what we meant here \revref.
 }
@@
 \begin{point}{}
-P16: Second paragraph:
+% P16: Second paragraph:
 The notation $L_t$ seems to first appear here and was not yet defined.
@@
 % P19-20:
-    The equations for the lineage dynamics for the three examples [i.e., Fisher-KPP \revref, Allen-Cahn, and Porous Medium] are interesting.
+    The equations for the lineage dynamics for the three examples [i.e., Fisher-KPP, Allen-Cahn, and Porous Medium] are interesting.
 Which is/are new in this paper, and which was/were known before (and related references)?
@@
 \reply{
-    \comment{TODO:
-    The PME is new;
-    probably the others are in Birzu/Korolev/Hallaschek? 
-    Also maybe see Roques et al 2008ish PNAS?
-    It reduces to BM in a potential:
-    find other references for this (i.e., the $\grad \log$...)
-    }
+    As far as we know, the PME case is new,
+    but there's been a fair amount of work on FKPP-like
+    cases covering the other two cases.
+    We've put a note about this, 
+    and some pointers to this literature \revref.
 }
@@
     This was correct as written;
-    we've rephased it to be more clear \revref.
+    we've rephrased it to be more clear \revref.
 }
@@
 \reply{
-    Good suggestion; we've clarified, see \revref and \llname{XU_clarification}.
+    Good suggestion; we've clarified, see \revref{} and \llname{XU_clarification}.
 }
@@
 \reply{
-    Whoops! That was due to a \LaTeX format change; now fixed.
+    Whoops! That was due to a \LaTeX{} format change; now fixed.
 }
@@
 \reply{
-    We think this was an unedited duplicate of point 1.24 above?
+    We think this point was an unedited duplicate of point 1.24 above? (If not, we're not sure what else it's saying?)
 }
@@
 \reply{
-    The fact is that we can bound the expectation of the quadratic variation by a constant times the expectation of the angle bracket process;
-    rather than explain again here we refer to the previous place we used the same argument
+    It was Item (4.b'), Table 4.1, p. 162, again --
+    we've modified this to hopefully 
+    more clearly refer to the previous place we used the same argument
     \revref.

### 2023-12-20 forwards-and-backwards.tex
final plr edits

@@
 
-\comment{TODO: insert statement that one might be worried about $\eta_t$ being well-defined as a process, in e.g., Def'n 5.2 and following?}
-
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 along the human gut,
-while \citet{li/buenzli/simpson:2022} study the effects of nonlinear diffusion
-on long-term survival of a lattice-based interacting particle system.
-However, we do not study the effect of movement of adults,
+\citet{li/buenzli/simpson:2022} study the effects of nonlinear diffusion
+on long-term survival of a lattice-based interacting particle system,
+and \citet{birzu/hallatschek/korolev:2017} describe genetic variation in expanding waves
+using both forwards and backwards-time arguments.
+Most of this work is theoretical; for empirical studies see for instance
+\citet{adler2018interspecific} or \citet{zhu2023density}.
+We do not study the effect of movement of adults,
 which can additionally affect the limiting equations:
-see for instance \citet{holmes/lewis/banks/veit:1994} or \citet{potts/borger:2023}.
+see for instance \citet{holmes/lewis/banks/veit:1994} or \citet{potts/borger:2023},
+especially if movement depends on population density
+(as in \citet{perkins:1992} and \citet{birzu2019genetic}).
 % MORE DETAILS:
@@
 or, equivalently, that $F(x,\eta) \le \theta r(x,\eta) \gamma(x,\eta)$ --
-will always be true, for instance, for large enough $\theta$ 
+will always be true for large enough $\theta$ 
 as long as $r$ and $\gamma$ are bounded away from zero.
@@
         are Gaussian with standard deviation 1,
-        and the equilibrium density (also, $N$) is 10 individuals per unit area.
+        and the equilibrium density ($N$) is 10 individuals per unit area.
         The remaining parameters are constant: $r \equiv \gamma \equiv 1$.
@@
 \end{corollary}
+
 When $\alpha>0$, the limit points can be thought of as interacting superprocesses. For
@@
 We are not aware of a general result to determine when we will have uniqueness of 
-solutions to the martingale problem of Theorem~\ref{thm:nonlocal_convergence}
-when $\alpha>0$.
-However, the Dawson--Girsanov transform tells us that we have uniqueness \revpoint{1}{12}
-in this special case of the superprocess with nonlinear death rates \cite{dawson:1993}.
-The Perkins stochastic calculus
+solutions to the martingale problem of Theorem~\ref{thm:nonlocal_convergence} when $\alpha>0$.
+We do not address the question of uniqueness here,
+but (as stated below in Proposition~\ref{thm:mmt_application}),
+a consequence of the Markov Mapping Theorem (Theorem~\ref{thm:mmt}) is that 
+uniqueness of the martingale problem for the (yet to be defined) lookdown process would imply
+uniqueness of solutions to this process.
+
+Alternatively, the Dawson--Girsanov transform could be used to show uniqueness \revpoint{1}{12}
+in the special case of a superprocess with nonlinear death rates:
+if $r$ and $\gamma$ only depend on $x$ (not $\eta$),
+then the process with $F=0$ is a heterogeneous branching superprocess
+and hence the corresponding martingale problem is unique (see Section 4.3 of \cite{dawson:1993}).
+Then, the Dawson--Girsanov transform (Theorem 7.2.2 of \cite{dawson:1993},
+extended to measures with nonconstant mass as in Section 10.1.2 of \cite{dawson:1993})
+would provide the Radon-Nikodym derivative of the law of the process with more general $F$
+relative to the law of the process with $F=0$
+under suitable conditions.
+% To do this may require some boundedness assumptions
+% (e.g., $r\gamma$ bounded away from zero and $F$ bounded below).
+
+In a different but related setting, the Perkins stochastic calculus
 (and its adaptation to a lookdown setting \cite{donnelly/kurtz:1999})
@@
 (rather than reproduction) of the superprocess \cite{perkins:1992}.
-We refer to~\cite{dawson:1993, perkins:1992}, and \cite{donnelly/kurtz:1999} 
-for approaches to showing that these sorts of martingale problems are well-posed.
+% We refer to~\cite{dawson:1993, perkins:1992}, and \cite{donnelly/kurtz:1999} 
+% for approaches to showing that these sorts of martingale problems are well-posed.
 
@@
 $\psi_0^\epsilon\geq 0$ is such that
-there exists $\lambda\in (0,1)$
+there exists $\lambda\in (0,1)$ for which
 \begin{equation*}
@@
 in the infinite population limit,
-and thus give a concrete meaning to $(L_t)_{t \ge 0}$. \llabel{Linf_mention}
+and thus gives a concrete meaning to $(L_t)_{t \ge 0}$. \llabel{Linf_mention}
 Roughly speaking,
@@
 mature offspring ($r \gamma$)
-with mean displacement in the direction of $\grad \log(\varphi_s \gamma) - \meanq$.
+with mean displacement in the direction of $\grad \log(\varphi_s \gamma) - \meanq/\sigma^2$.
 In particular, lineages are drawn to regions of high fecundity (production of juveniles), but their
@@
 
+Ancestry in traveling waves for populations described by reaction-diffusion equations
+has been studied before by various authors, \revpoint{1}{16}
+although most work assumes the diffusion term is linear
+(in our notation, $r$ and $\gamma$ are constant,
+but $F$ can depend on density).
+For instance, following \citet{hallatschek/nelson:2008},
+various authors (e.g., \citet{roques2012allee,birzu/hallatschek/korolev:2017})
+describe genetic diversity
+and ancestry in (possibly noisy) traveling waves for reaction-diffusion equations
+in a situation that covers our first two examples below.
+However, we are not aware of previous work covering the third case 
+with nonlinear diffusive term (the porous medium equation).
+
 %%%%%%%%%%
-
-%%%%%%%%%%
-\paragraph{Fisher-KPP equation:} \revpoint{1}{16}
+\paragraph{Fisher-KPP equation:}
 Consider the classical Fisher-KPP equation,
@@
     \big\langle
-	2 r(x, \eta) \gamma(x, \eta),
+    2 r(x, \eta) \gamma(x, \eta) f(x)^2,
         \eta(dx)
@@
 Concretely,
-since $\|\rho^\epsilon_F\| \propto \epsilon^{-e/2}$,
-the quadratic variation of $F(\rho^\epsilon_F\!*\!\eta(x))$
-is proportional to $\theta/(N\epsilon^d)$.
+since $\|\rho^\epsilon_F\| \propto \epsilon^{-d/2}$,
+the quadratic variation of $\rho^\epsilon_F\!*\!\eta(x)$
+is $\mathcal{O}(\theta/(N\epsilon^d))$.
 
@@
     \end{split} \end{align}
-    where $\eta(\cdot) = \frac{1}{u} \lim_{u \to \infty} \xi(\cdot \times [0, u])$.
+    where $\eta(\cdot) = \lim_{u_0 \to \infty} \frac{1}{u_0} \xi(\cdot \times [0, u_0])$.
     We say that a ${\mathcal D}_{[0,\infty)}(\mathcal{C})$-valued process $(\xi_t)_{t \ge 0}$
@@
     in the sense of \eqref{eqn:conditionally_uniform}.
+    If uniqueness holds for the $(A^N, \lp^N_0)$-martingale problem,
+    then uniqueness also holds
+    for the martingale problem of Definition~\ref{defn:mgale_construction}.
 
@@
     in the sense of \eqref{eqn:conditionally_poisson}.
+    If uniqueness holds
+    for the martingale problem of Definition~\ref{defn:limiting_lookdown_mgale}
+    then uniqueness also holds for 
+    the martingale problem of Theorem~\ref{thm:nonlocal_convergence}.
 \end{proposition}
@@
 \end{align}
-where
-\begin{align*}
-    \eta_t
+where $\eta_t = \lim_{u_0 \to \infty} \eta_t^{[u_0]}$ and
+\begin{align*}
+    \eta_t^{[u_0]}
     :=
-    \lim_{u_0 \to \infty} \frac{1}{u_0}
+    \frac{1}{u_0}
         \sum_{a : \tau_a \le t < \sigma_a \; ; \; U_a(t) < u_0} \delta_{X_a(t)} .
@@
 
-\comment{TODO: add note about well-definedness of $\eta_t$.}
-    However, for this to be valid, one should first make sure that $\eta_t$
-    is a well-defined process.
-    We do know that 
+    For completeness, we should also show that $\eta_t$ defined in this way is c\`adl\`ag.
+    However, this can be verified by 
+    considering $\eta_t$ as a limit of the c\`adl\`ag processes $\eta^{[u_0]}_t$.
 \end{proof}
@@
 \]
-with $C$ independent of $N$, and then using that $F$ is bounded and substituting 
+with $C$ independent of $N$, and then using that $F$ is bounded above and substituting 
 the resulting bound on $\IE\big[\langle 1,\eta_s^N\rangle\big]$ into the
@@
     G'(\langle f, \eta \rangle)\int_{\IR^d}  
-\theta\Big\langle \gamma(x,\eta) \int_{\IR^d} f(y)r(y,\eta) q_{\theta}(x,dy) 
-    - f(x)\mu_\theta(x,\eta), \eta(dx)\Big\rangle\\
+    \theta\Big\{ \gamma(x,\eta) \int_{\IR^d} f(y)r(y,\eta) q_{\theta}(x,dy) 
+    - f(x)\mu_\theta(x,\eta) \Big\} \eta(dx)\\
 &+\frac{1}{2}\frac{\theta}{N}G''(\langle f, \eta \rangle)\int_{\IR^d} 
- \Big\langle\gamma(x, \eta)\int_{\IR^d} f^2(y) r(y,\eta)q_{\theta}(x,dy)+f^2(x)
-\mu_\theta(x, \eta), \eta(dx)\Big\rangle\\
-&+\frac{1}{6}\frac{\theta}{N^2}\Big\langle
-G'''(w) \gamma(x, \eta)\int_{\IR^d} f^3(y) r(y,\eta) 
+    \Big\{\gamma(x, \eta)\int_{\IR^d} f^2(y) r(y,\eta)q_{\theta}(x,dy)+f^2(x)
+    \mu_\theta(x, \eta) \Big\} \eta(dx) \\
+&+\frac{1}{6}\frac{\theta}{N^2}
+    G'''(w) \gamma(x, \eta)\int_{\IR^d} \Big\{ f^3(y) r(y,\eta) 
     q_{\theta}(x,dy)
--G'''(v)f^3(x)\mu_\theta(x, \eta), \eta(dx)\Big\rangle
+    - G'''(v)f^3(x)\mu_\theta(x, \eta) \Big\} \eta(dx)
 \end{aligned}    
@@
     +
-    C \int_0^t \IE\Big[\Big\langle f_n(x), \eta^N_s(dx) \Big\rangle \Big] ds ,
+    C \int_0^t \IE\left[\left\langle f_n(x), \eta^N_s(dx) \right\rangle \right] ds ,
 \end{align*}
@@
 Since $f$ is smooth, $T_\epsilon^2f-f$ is ${\mathcal O}(\epsilon)$, 
-with an application of the triangle inquality, 
+with an application of the triangle inequality, 
 \[
@@
     in the level direction,
-    and hence so is $\{e^{-\langle f, \lp^N_t \rangle}\}_N$.
+    and hence $\{e^{-\langle f, \lp^N_t \rangle}\}_N$ is tight as well.
     % The functions $\lp \mapsto \langle f, \lp \rangle$
@@
 $$
-    \Lgen f = \sigma^2 r \gamma \left(
-        \frac{1}{2} \Delta f
+    \Lgen f = \frac{\sigma^2}{2} r \gamma \left(
+        \Delta f
         + \grad ( 2 \log(\gamma \varphi) - 2h/\sigma^2 ) \cdot \grad f
@@
 $$ \pi(x)
-    = \frac{2e^{H(x)} }{ (\sigma^2 r(x) \gamma(x)) }
-    = \frac{2\gamma(x) \varphi(x)^2 e^{-2h(x)/\sigma^2}}{\sigma^2 r(x)} ,
+    = \frac{e^{H(x)} }{\sigma^2 r(x) \gamma(x)/2}
+    = \frac{\gamma(x) \varphi(x)^2 e^{-2h(x)/\sigma^2}}{\sigma^2 r(x)/2} ,
 $$
@@
 the process $Y$ is reversible with respect to $\pi$
-(and the factor of $\sigma^2$ is constant).
+(and the factor of $\sigma^2/2$ is constant).
 \end{proof}
@@
             as $Y = \gamma \circ X$.
-            If $Y$ and $\tilde Y$ are c\'adl\'ag, then $Y$ and $\tilde Y$ have the same distribution
+            If $Y$ and $\tilde Y$ are c\`adl\`ag, then $Y$ and $\tilde Y$ have the same distribution
             on $D_{S_0}[0,\infty)$.
@@
 \begin{acks}
-Many thanks to Matthias Birkner, Mattias Winkel, and an anonymous reviewer
+Many thanks to Matthias Birkner, Matthias Winkel, and an anonymous reviewer
 for detailed comments and corrections.
@@
 this research was therefore supported in part by the NSF under grant \#PHY-1748958
-and by the Gordon and Betty Moore Foundation grant \#2919.02.
+and by the Gordon and Betty Moore Foundation grant \#2919.02, both to KITP.
 PLR was supported by the NIH NHGRI (grant \#HG011395),

### 2023-12-30 forwards-and-backwards.tex
AME edits

@@
 
-\KEYWORDS{population model ; interacting superprocess ; lookdown construction ; porous medium equation ; reaction-diffusion equation ; travelling waves ; genealogies ; Fisher-KPP equation}
+\KEYWORDS{population model; interacting superprocess; lookdown construction; porous medium equation; reaction-diffusion equation; travelling waves; genealogies; Fisher-KPP equation}
 \AMSSUBJ{60J25 ; 92D10 ; 92D15 ; 92D25 ; 92D40}
@@
 Since then, they have been extended to a wide range of models. Of particular
-relevance to our work here are the papers of~\cite{kurtz/rodrigues:2011} 
+relevance to our work here are the papers ~\cite{kurtz/rodrigues:2011} 
 and~\cite{etheridge/kurtz:2019}, in which
@@
 Next, in Section~\ref{sec:applications}, we discuss a few striking consequences of these results
-regarding the behavior of genealogies in traveling waves,
+regarding the behavior of genealogies in travelling waves,
 the appearance of periodic ``clumps'' in seemingly homogeneous population models,
@@
 sequence of distributions is tight,
-i.e., that any infinite subsequence has a weakly convergent subsubsequence.
+i.e., if any infinite subsequence has a weakly convergent subsubsequence.
 Our first main result establishes tightness of our rescaled population processes in 
@@
 for each starting location to which $\eta^N_T$ assigns positive mass.
-It is less clear, however, how to formally retain such information when we 
+It is less clear, however, how to rigorously retain such information when we 
 pass to the scaling limit.
@@
 This will allow us to calculate, for each $x$ and $y\in\IR^d$, the proportion of
-the population at location $x$ in the present day population that are descended from 
+the population at location $x$ in the present day population that is descended from 
 a parent who was at location $y$ at time $t$ in the past. To make
@@
 
-Ancestry in traveling waves for populations described by reaction-diffusion equations
+Ancestry in travelling waves for populations described by reaction-diffusion equations
 has been studied before by various authors, \revpoint{1}{16}
@@
 describe genetic diversity
-and ancestry in (possibly noisy) traveling waves for reaction-diffusion equations
+and ancestry in (possibly noisy) travelling waves for reaction-diffusion equations
 in a situation that covers our first two examples below.
@@
 
-It is interesting to compare the stationary distribution we have obtained here
-to the expression that we'd get by setting $\meanq = -\wavespeed$
-and using Corollary~\ref{cor:stationary_dist},
-i.e., by giving each offspring a mean displacement that offsets the motion of the wave
-(The model is different because this motion only affects offspring, not adults.)
-In the Fisher-KPP and Allen-Cahn cases above, we get the same expressions,
-but this is only the case because $r\equiv\gamma\equiv1$ in both.
-For the PME with $\meanq = 1$ we have $\DG^* = \Delta + \grad$ 
-and so the equation solved by the population density is
-$$
-    \partial_t \varphi = \Delta \varphi + 2 \varphi \grad \varphi + \varphi (1 - \varphi) ,
-$$
-which has a traveling wave solution of the same shape but moving at half the speed,
-$\varphi(x,t) = w^{P}(x-t/2)$,
-and a stationary distribution of the lineage relative to the wavefront of
-$\pi(\xi) \propto e^{3\xi/2} (1 - e^{\xi/2})^3$.
+% % Removing this, since it's not actually that interesting:
+% It is interesting to compare the stationary distribution we have obtained here
+% to the expression that we'd get by setting $\meanq = -\wavespeed$
+% and using Corollary~\ref{cor:stationary_dist},
+% i.e., by giving each offspring a mean displacement that offsets the motion of the wave
+% (The model is different because this motion only affects offspring, not adults.)
+% In the Fisher-KPP and Allen-Cahn cases above, we get the same expressions,
+% but this is only the case because $r\equiv\gamma\equiv1$ in both.
+% For the PME with $\meanq = 1$ we have $\DG^* = \Delta + \grad$ 
+% and so the equation solved by the population density is
+% $$
+%     \partial_t \varphi
+%     =
+%     \Delta (\varphi^2) + \grad (\varphi^2) + \varphi (1 - \varphi) ,
+% $$
+% which has a travelling wave solution of the same shape but moving more slowly,
+% $\varphi(x,t) = w^{P}(a(x-2at))$, with $a=(\sqrt{5}-1)/4$,
+% and a stationary distribution of the lineage relative to the wavefront of
+% (NOT RIGHT:) $\pi(\xi) \propto e^{3\xi/2} (1 - e^{\xi/2})^3$.
+% 
 % \comment{Details to back that last statement up, which we probably want to comment out?}
-% (We can see that $w^P(x-t/2)$ is a traveling wave solution by using that
+% (We can see that $w^P(x-t/2)$ is a travelling wave solution by using that
 % $\partial_x w^P = -(1 - w^P)/2$;
@@
 % $\Lgen_{P'} = \varphi \partial_x^2 + (4 \partial_x \varphi + 1/2 + \varphi) \partial_x$,
-% which has speed measure proportional to
+% which has speed measure proportional to (NOT RIGHT)
 % $\exp(\int^x 3(1/2 dx + d \log \varphi)) / \varphi$.)
@@
 % \end{align*}
+% \comment{Alison says:
+%  If one tries a solution of the form $(1-\exp(a(x-ct)))_+$, then we find speed $c=2a$ and $a$ solves $4a^2+2a -1=0$ (I think - at least I got that twice). 
+% }
+% \comment{
+% Checking that:
+% $$(2ff')' + 2 b f f' = 2 f'^2 + 2 ff'' + 2 b f f'$$
+% and so if $f' = -a(1-f)$ and thus $f'' = -a^2(1-f)$ then this is
+% \begin{align*}
+%     (f^2)'' + b (f^2)' + f(1-f)
+%     &= 2 (a^2(1-f)^2 - a^2f(1-f) - abf(1-f)) + f(1-f) \\
+%     &= (1-f) (2a^2(1-f) + (-2a^2-2ab+1)f) \\
+%     &= (1-f) (2a^2 + (-4a^2-2ab+1)f)
+% \end{align*}
+% Now, solutions to $4a^2+2ab-1=0$ are $a_{\pm}=(-b \pm \sqrt{b^2+4})/4$ and for these
+% \begin{align*}
+%     c_\pm 
+%     &= 2a_\pm \\
+%     &= \frac{-b \pm \sqrt{b^2+4}}{2} .
+% \end{align*}
+% }
 
@@
 continuous population generated by parameters $\gamma$, $r$, and $F$,
-with $\meanq = 0$ and $\covq = I$.
+with $\meanq = 0$ and $\covq = 2I$.
 Suppose it has a stationary profile $w(x)$, that must satisfy
@@
 to provide heuristic arguments for our main results,
-to build intuition before the formal proofs.
+to build intuition before the proofs.
 
@@
 we impose the stronger condition
-that $\theta/N\epsilon^d\to 0$ and also require that
+that $\theta/(N\epsilon^d) \to 0$ and also require that
 $\theta\epsilon^2\to\infty$. 
@@
 take $\theta/(N\epsilon^d)\to 0$.
-Concretely,
-since $\|\rho^\epsilon_F\| \propto \epsilon^{-d/2}$,
-the quadratic variation of $\rho^\epsilon_F\!*\!\eta(x)$
-is $\mathcal{O}(\theta/(N\epsilon^d))$.
+% Concretely,
+% the quadratic variation of $\rho^\epsilon_F\!*\!\eta(x)$
+% is $\mathcal{O}(\theta/(N\epsilon^d))$.
 
@@
 
-In this section we present formal proofs of the first two of our
+In this section we present proofs of the first two of our
 three scaling limits.
-%following sections we present formal proofs of our three scaling limits.
 In Subsection~\ref{sec:population_density_proof} 
@@
 uniformly over $x$ and $\eta$.
+Note that Conditions~\ref{def:model_setup} assume nothing about $\eta$,
+and so, for instance, although $r(x,m)$ has uniformly bounded derivatives,
+it might still be the case that $r(x,\eta) = r(x, \smooth{r}\eta(x))$ changes arbitrarily rapidly;
+the additional conditions of the Lemma prevent this from happening.
+
 First suppose that
@@
             + r(y,\eta) \partial_{x_ix_j} f(z_1)
-        \right) q_\theta(x, dy) \bigg|
+        \right) q_\theta(x, dy) \bigg| .
 \end{align*}
@@
 and covariance $\covq(x)/\theta$, and both $\meanq(x)$ and $\covq(x)$ are uniformly bounded,
-so that $\theta \int (y-x)_i q_\theta(x,dy)$ is bounded as well.
+$\theta \int (y-x)_i q_\theta(x,dy)$ is bounded as well.
 Furthermore, a change of variables that diagonalizes $\covq(x)$
@@
 Under Condition~\ref{control through gamma} of 
-Assumptions~\ref{def:model_setup}, this is bounded by 
+Lemma~\ref{lem:conditions on r}, this is bounded by 
 a constant times $\smooth{\gamma}\eta(x)+(\smooth{\gamma}\eta(x))^2$ and 
-$\sup_x m^2\gamma(x, m)$ is bounded,
-so therefore $|\gamma(x,\eta) B^\theta_f(x,\eta)| \le K_7 + K_8 |f(x)|$,
+$\sup_x m^2\gamma(x, m)$ is bounded.
+Therefore $|\gamma(x,\eta) B^\theta_f(x,\eta)| \le K_7 + K_8 |f(x)|$,
 where $K_7$ comes from $K_3$, $K_4$, and the supremum of $\gamma$,
@@
 	\end{align}
-which is bounded since $\gamma (x,\eta)$ and $B^\theta_1(x,\eta)$ are both bounded and 
+which is bounded above since $\gamma (x,\eta)$ and $B^\theta_1(x,\eta)$ are both bounded and 
 $\langle 1,\eta_t^N \rangle\geq 0$. 
@@
     \IP\left\{\left|
-            \int_\tau^{\tau + t}
+            \int_{\tau_N}^{\tau_N + t}
             \int_{\IR^d}
@@
     \IP\left\{\big|
-        \langle M^{N}(f) \rangle_{\tau + t} 
-            - \langle M^{N}(f) \rangle_\tau \big|
+        \langle M^{N}(f) \rangle_{\tau_N + t} 
+            - \langle M^{N}(f) \rangle_{\tau_N} \big|
         > \nu
@@
     &
- \big|   \langle M^{N}(f) \rangle_{\tau + t} 
-        - \langle M^{N}(f) \rangle_\tau \big|
+ \big|   \langle M^{N}(f) \rangle_{\tau_N + t} 
+        - \langle M^{N}(f) \rangle_{\tau_N} \big|
     \\ & \qquad =
-  \Big|  \int_{\tau}^{\tau + t}
+  \Big|  \int_{\tau_N}^{\tau_N + t}
         \frac{\theta}{N}
@@
     \\ & \qquad =
-   \Big| \int_{\tau}^{\tau + t}
+   \Big| \int_{\tau_N}^{\tau_N + t}
         \frac{\theta}{N}
@@
 The process $(\eta^N_t)_{t \geq 0}$ of Definition~\ref{defn:mgale_construction}
-is the unique solution to the $(\Pgen^N, \eta_0)$-martingale problem, i.e., if
+is the unique solution to the $(\Pgen^N, \eta_0)$-martingale problem, i.e.,
 \revpoint{1}{30}
@@
 \varphi_t(x) &= \IE_x\Big[\varphi_0(Z_t) 
-+ \int_0^t \varphi_s(Z_s)F(\varphi_s(Z_s)) ds\Big], \label{FK:varphi} \\
+    + \int_0^t \varphi_s(Z_{t-s})F(\varphi_s(Z_{t-s})) ds\Big], \label{FK:varphi} \\
 \varphi^\epsilon_t(x) &= \IE_x\Big[\varphi_0(Z_t) 
-+ \int_0^t \varphi^\epsilon_s(Z_s)F(\rho^\epsilon_F*\varphi^\epsilon_s(Z_s)) ds\Big],
+    + \int_0^t \varphi^\epsilon_s(Z_{t-s})F(\rho^\epsilon_F*\varphi^\epsilon_s(Z_{t-s})) ds\Big],
 \end{align}
@@
 \varphi_t(x) - \varphi^\epsilon_t(x) = 
-\IE_x\left[ \int_0^t \Big(\varphi_s(Z_s)F\big(\varphi_s(Z_s)\big)
--\varphi^\epsilon_s(Z_s)F\big(\rho_\epsilon*\varphi^\epsilon_s(Z_s)\big)\Big) ds \right] ,
+    \IE_x\left[ \int_0^t \Big(\varphi_s(Z_{t-s})F\big(\varphi_s(Z_{t-s})\big)
+    -\varphi^\epsilon_s(Z_{t-s})F\big(\rho_\epsilon*\varphi^\epsilon_s(Z_{t-s})\big)\Big) ds \right] ,
 \label{FK:diferencesVarphis}
@@
 The key to our proof of Proposition~\ref{prop:nonlocal_to_local}
-will be to replace $F(\varphi_s(Z_s))$ by $F(\rho^\epsilon_F*\varphi_s(Z_s))$ 
+will be to replace $F(\varphi_s(Z_{t-s}))$ by $F(\rho^\epsilon_F*\varphi_s(Z_{t-s}))$ 
 in this expression. 
@@
 \varphi_t(x) \leq \| \varphi_0 \|_\infty + 
-K \IE\Big[\int_0^t \varphi_s(Z_s) ds\Big].
+    K \IE\Big[\int_0^t \varphi_s(Z_{t-s}) ds\Big].
 \end{align*}
@@
 | &\varphi_t(x) - \varphi^\epsilon_t(x)|  \\ 
-& \leq \IE_x\left[ \int_0^t\Big| \varphi_s(Z_s)
-F(\rho^\epsilon_F*\varphi_s(Z_s))
--\varphi^\epsilon_s(Z_s)
-F\big(\rho^\epsilon_F*\varphi^\epsilon_s(Z_s)\big)\Big| ds \right] 
+& \leq \IE_x\left[ \int_0^t\Big| \varphi_s(Z_{t-s})
+    F(\rho^\epsilon_F*\varphi_s(Z_{t-s}))
+    -\varphi^\epsilon_s(Z_{t-s})
+    F\big(\rho^\epsilon_F*\varphi^\epsilon_s(Z_{t-s})\big)\Big| ds \right] 
     +M t \widehat{\delta}(\epsilon)   \\ 
-& \leq \IE_x\left[ \int_0^t \big|F(\rho^\epsilon_F*\varphi^\epsilon_s(Z_s))\big|\cdot
-\big|\varphi^\epsilon_s(Z_s)-\varphi_s(Z_s)\big| ds  \right] \\ 
-& \qquad +  \IE_x\left[\int_0^t |\varphi_s(Z_s)| 
-\big|F(\rho^\epsilon_F*\varphi^\epsilon_s(Z_s))
--F(\rho^\epsilon_F*\varphi_s(Z_s))\big| ds \right] 
+& \leq \IE_x\left[ \int_0^t \big|F(\rho^\epsilon_F*\varphi^\epsilon_s(Z_{t-s}))\big|\cdot
+    \big|\varphi^\epsilon_s(Z_{t-s})-\varphi_s(Z_{t-s})\big| ds  \right] \\ 
+    & \qquad +  \IE_x\left[\int_0^t |\varphi_s(Z_{t-s})| 
+    \big|F(\rho^\epsilon_F*\varphi^\epsilon_s(Z_{t-s}))
+    -F(\rho^\epsilon_F*\varphi_s(Z_{t-s}))\big| ds \right] 
     + M t \widehat{\delta}(\epsilon)  \\ 
@@
 Since $\dot \psi^{\epsilon,x}_s = \mathcal{L}_\theta \psi^{\epsilon,x}_s$,
-the $j=1$ terms from $\Pgen^N(\langle \psi^{\epsilon,x}_{t-s}(y),\eta_s(dy) \rangle^k)$
+the $j=1$ term from $\Pgen^N(\langle \psi^{\epsilon,x}_{t-s}(y),\eta_s(dy) \rangle^k)$
 combines with the last term in~\eqref{kth moment for time varying function}
@@
 and the same fact as before from \citet{barlow/jacka/yor:1986}, \revpoint{1}{32}
-$\IE[\sup_{0 \le u \le T} |\widehat{M}^N(f)_u|^2] \le C'' \IE[\langle\widehat{M}^N(f)\rangle_u]$,
+$\IE[\sup_{0 \le u \le T} |\widehat{M}^N(f)_u|^2] \le C'' \IE[\langle\widehat{M}^N(f)\rangle_T]$,
 and so using Markov's inequality,
@@
     so there is a $c_f < \infty$ such that $f(x, u) \le c_f h(u)$ for all $x$ and $u$.
-    Therefore, $\langle f, \xi \rangle \le \langle h, \xi \rangle$,
+    Therefore, $\langle f, \xi \rangle \le c_f \langle h, \xi \rangle$,
     and so by Lemma~\ref{lem:h_containment},
@@
 % Gabriel Birzu, Oskar Hallatschek, and Kirill~S. Korolev, \emph{Fluctuations
-%   uncover a distinct class of traveling waves}, Proc. Natl. Acad. Sci. (USA)
+%   uncover a distinct class of travelling waves}, Proc. Natl. Acad. Sci. (USA)
 %   \textbf{115} (2018), no.~16, 3645--3654.

### 2023-12-30 forwards-and-backwards.tex
final final edits

@@
 $r(x,\eta) \gamma(x,\eta) \covq(x) = J(x,\eta) J(x,\eta)^T$, and 
-$\beta(x,\eta) = r(x,\eta) \gamma(x,\eta) \big(\meanq(x)+2\covq(x)\nabla\log r(x,\eta)\big)$
+$\beta(x,\eta) = r(x,\eta) \gamma(x,\eta) \big(\meanq(x)+\covq(x)\nabla\log r(x,\eta)\big)$
 (quantities that will appear in Proposition~\ref{prop:limiting_construction}).
@@
 \]
-with $C$ independent of $N$, and then using that $F$ is bounded above and substituting 
-the resulting bound on $\IE\big[\langle 1,\eta_s^N\rangle\big]$ into the
+with $C$ independent of $N$, and then using that $|f|$ is bounded and
+substituting the resulting bound on $\IE\big[\langle 1,\eta_s^N\rangle\big]$ into the
 expression above.

### 2023-12-30 forwards-and-backwards.tex
submitted!

@@
 \]
-with $C$ independent of $N$, and then using that $|f|$ is bounded and
+with $C$ independent of $N$, and
 substituting the resulting bound on $\IE\big[\langle 1,\eta_s^N\rangle\big]$ into the

### 2024-01-05 forwards-and-backwards.tex
one last bit

@@
 The precise sense in which we can look at ``the lineage of a sampled individual'' \revpoint{1}{2}
-in the scaling limit is made clear by the introduction of the lookdown construction,
-in Section~\ref{sec:lookdown}.
+in the scaling limit is made clear by the introduction of the lookdown construction
+in Section~\ref{sec:lookdown}:
+the construction retains an unambiguous notion of ancestral lineages
+through to the scaling limit,
+and Theorem~\ref{thm:lookdown_convergence} shows that the these converge.
 (For now, we can take the definition to refer to the distribution obtained

### 2024-01-05 forwards-and-backwards.tex
halfway through overfull hboxes

@@
 
-\SUBMITTED{June 14, 2023} % Edit.
-\ACCEPTED{NA} % Edit.
+\SUBMITTED{June 14, 2023}
+\ACCEPTED{January 3, 2024}
 
@@
 \newif\ifsubmission
-\submissiontrue
-% \submissionfalse
+% \submissiontrue
+\submissionfalse
 \ifsubmission
@@
     % for the nice version
+    \newcommand{\llabel}[1]{}
+    \newcommand{\revpoint}[2]{}
+    \newcommand{\includereviews}{}
 \fi
 
-% Responses to reviews
-\input{review-response-commands}
-% set this to show line numbers and include responses to reviews or not
-\newif\ifreviewresponses
-\reviewresponsestrue  % include them
+% % Responses to reviews
+% \input{review-response-commands}
+% % set this to show line numbers and include responses to reviews or not
+% \newif\ifreviewresponses
+% % \reviewresponsestrue  % include them
 % \reviewresponsesfalse  % don't include them
-\newcommand{\responsefile}{review-responses}  % name of the review responses file
+% \newcommand{\responsefile}{review-responses}  % name of the review responses file
 
@@
 
-An entirely analogous argument shows that if $G'''$ is bounded, then
+An analogous argument shows that if $G'''$ is bounded, then
 the term $\epsilon_{\theta,N}(f, G, \eta)$ 
@@
 \begin{align*}
-    X_a(t)
-    &=
-    X_a(\tau_a) + 
+    &X_a(t)
+    =
+    X_a(\tau_a) \\
+    &\qquad {} + 
     \int_{[\tau_a, t) \times [0, \infty) \times \IR \times [0, 1]}
@@
 \begin{align*}
-    r(y,\eta) f(y) - r(x,\eta) f(x)
-&=
+    &r(y,\eta) f(y) - r(x,\eta) f(x)
+    \\
+&\qquad\qquad
+    =
     r(y,\eta) (f(y) - f(x))
     + (r(y,\eta) - r(x,\eta)) f(x) 
-\\ &=
+\\ &\qquad\qquad
+    =
     r(y,\eta) \left(
@@
     \right)
-\\ &\qquad {}
+\\ &\qquad\qquad
+    \qquad {}
     + f(x) \left(
@@
     \right)
- \\ &=
+ \\ &\qquad\qquad
+    =
     \left( r(x,\eta) + \sum_j (y-x)_j \partial_{x_j} r(z_3,\eta) \right)
@@
     \right)
-\\ &\qquad {}
+\\ &\qquad\qquad
+    \qquad {}
     + r(y,\eta) 
         \sum_{ij} (y-x)_i (y-x)_j \partial_{x_i x_j} f(z_1)
-\\ &\qquad {}
+\\ &\qquad\qquad
+    \qquad {}
     + f(x) \left(
@@
     \begin{align*}
-        \IE\left[ M^{N*}_t(1) \right]
-        &\le
+        &\IE\left[ M^{N*}_t(1) \right]
+        \le
         C'\left( 1 + \IE\left[ \left\langle M^N(1) \right\rangle_t \right] \right)
-        \\ &=
+        \\ &\hspace{3em}=
         C'\left( 1 + \frac{\theta}{N} \IE\left[
@@
             \right] \right)
-        \\ &=
+        \\ &\hspace{3em}=
         C'\Big( 1 + \IE\Big[
@@
         \IE[\langle 1, \eta^N_0 \rangle]
+        + \IE[M^{N*}_t(1)] 
+        \\ & \qquad\qquad {}
         + \IE\left[
@@
         \right]
-        \\ & \qquad\qquad {}
-        + \IE[M^{N*}_t(1)] 
         \\
@@
         - \langle M^{N}(f) \rangle_{\tau_N} \big|
-    \\ & \qquad =
+    \\ & \hspace{0.2em} =
   \Big|  \int_{\tau_N}^{\tau_N + t}
@@
     ds \Big|
-    \\ & \qquad =
+    \\ & \hspace{0.2em} =
    \Big| \int_{\tau_N}^{\tau_N + t}
@@
 
-We work on the time interval $[0,T]$.
-We will require a lower bound on $\int \psi_t^\epsilon(x)\log \psi_t^\epsilon(x) dx$ 
+We work on the time interval $[0,T]$, and
+will require a lower bound on $\int \psi_t^\epsilon\log \psi_t^\epsilon dx$ 
 which we record as a lemma.
@@
 Now consider
-\begin{eqnarray}
-	\frac{d}{dt}\int \psi_t^\epsilon\log \psi_t^\epsilon dx &=&
+\begin{align}
+& \frac{d}{dt}\int \psi_t^\epsilon\log \psi_t^\epsilon dx 
+\nonumber \\
+&\hspace{3em}=
 	\int (1+\log \psi_t^\epsilon)\left[\Delta \big(\psi_t^\epsilon\,
@@
 \\
-&=&
+&\hspace{3em}=
 	\int (1+\log \psi_t^\epsilon)\left[\nabla\Big(\psi_t^\epsilon\,
@@
 	\\
-&=&
+&\hspace{3em}=
 \int \left[-\frac{\nabla \psi_t^\epsilon}{\psi_t^\epsilon}
@@
 	\\
-&=&
+&\hspace{3em}=
 -\int \left(\nabla (\zeta^{\epsilon}*\psi_t^\epsilon)\right)^2  dx
@@
 	\\
-&&+\int
+&\hspace{3em}
+    +\int
 \left[\psi_t^\epsilon+\psi_t^\epsilon\log \psi_t^\epsilon
@@
 	\label{change in ulogu}
-\end{eqnarray}
+\end{align}
 The first three terms are negative; and we already
@@
 \leq 
-C\IE\Big[\Big\langle\int_0^t\sum_{j=2}^k\frac{\theta}{N\epsilon^d}
-\Big(\frac{1}{(N\epsilon^d)^{j-2}}\Big)
+C\IE\Big[\Big\langle\int_0^t\sum_{j=2}^k
+    \frac{\theta}{N\epsilon^d (N\epsilon^d)^{j-2}}
 	\Big\langle \psi^{\epsilon,x}_{t-s}(y)
@@
 &\leq 
-\IE\Big[\int \int\Big\{
+\IE\Big[\int\! \int\Big\{
 \big(p_{\epsilon^2/2}*\eta_t(y_1)\big)^3+ \big(p_{\epsilon^2/2}*\eta_t(y_2)\big)^3+
 \big(p_{\epsilon^2/4}*\eta_t\big(\frac{y_1+y_2}{2}\big)\big)^3
-\Big\}p_{\epsilon^2}(y_1,y_2)dy_1dy_2\Big],
+\Big\}p_{\epsilon^2}(y_1,y_2)dy_1dy_2\Big]
 \end{align*}
@@
 this yields
-\begin{multline*}
-\big\langle\big(\rho_\epsilon*\eta_t(x)\big)^k,\eta_t(dx)\big\rangle
-    =\int\cdots\int \prod_{j=2}^k p_{\epsilon^2 j/2(j-1)}(y_j,Y_{j-1})
+\begin{align*}
+&\big\langle\big(\rho_\epsilon*\eta_t(x)\big)^k,\eta_t(dx)\big\rangle
+\\ &\hspace{2em}=
+    \int\cdots\int \prod_{j=2}^k p_{\epsilon^2 j/2(j-1)}(y_j,Y_{j-1})
      \prod_{i=1}^k p_{\epsilon^2/2}*\eta_t(y_i)p_{\epsilon^2/2k}*\eta_t(Y_k)
 dy_1\ldots dy_k
-\\
-\leq
+\\ &\hspace{2em}\leq
 \int\cdots\int 
     \prod_{j=2}^k p_{\epsilon^2 j/2(j-1)}(y_j,Y_{j-1})
+\\ &\hspace{8em} {} \times
     \Big\{\sum_{i=1}^k\big(p_{\epsilon^2/2}*\eta_t(y_i)\big)^{k+1}
     + \big(p_{\epsilon^2/2k}*\eta_t(Y_k)\big)^{k+1}\Big\}dy_1\ldots dy_k,
-\end{multline*}
+\end{align*}
 and once again we can change variables in the integrals and 
@@
 the sequence of measure valued processes $\{ \rho_\epsilon*\eta_t^N(x) dx \}_{t \geq 0}$
-	(taking values in ${\mathcal D}_{[0,T]}(\measures)$) is tight.
+    is tight
+	(as measures on ${\mathcal D}_{[0,T]}(\measures)$).
 \end{corollary}
@@
 	\label{square of F-integral}
-\IE\Big[
+    &\IE\Big[
 	\Big(\int_s^t\big\langle\rho_\epsilon*|f|(x) \big|F\big(\rho_\epsilon*\eta_u^N(x)\big)\big|,
@@
 \\
-=
+    &\hspace{4em}=
 2\IE\Big[
@@
 \eta_u^N(dx)\big\rangle 
+    \\&\hspace{8em}
 	\int_u^t\big\langle \rho_\epsilon*|f|(x)\big|F\big(\rho_\epsilon*\eta_r^N(x)\big)\big|,
@@
 \bibliographystyle{amsplain}
-\bibliography{refs}
+% \bibliography{refs}
 
@@
 
-% \providecommand{\bysame}{\leavevmode\hbox to3em{\hrulefill}\thinspace}
-% \providecommand{\MR}{\relax\ifhmode\unskip\space\fi MR }
-% % \MRhref is called by the amsart/book/proc definition of \MR.
-% \providecommand{\MRhref}[2]{%
-%   \href{http://www.ams.org/mathscinet-getitem?mr=#1}{#2}
-% }
-% \providecommand{\href}[2]{#2}
-% \begin{thebibliography}{10}
-% 
-% \bibitem{barlow/jacka/yor:1986}
-% M.~T. Barlow, S.~D. Jacka, and M.~Yor, \emph{Inequalities for a pair of
-%   processes stopped at a random time}, Proceedings of the London Mathematical
-%   Society \textbf{s3-52} (1986), no.~1, 142--172.
-% 
-% \bibitem{barton:1979}
-% N~H Barton, \emph{The dynamics of hybrid zones}, Heredity \textbf{43} (1979),
-%   no.~3, 341--359.
-% 
-% \bibitem{berestycki2009nonlocal}
-% Henri Berestycki, Gregoire Nadin, Benoit Perthame, and Lenya Ryzhik, \emph{The
-%   non-local fisher-kpp equation: travelling waves and steady states},
-%   Nonlinearity \textbf{22} (2009), no.~12, 2813--2844.
-% 
-% \bibitem{birzu/hallatschek/korolev:2017}
-% Gabriel Birzu, Oskar Hallatschek, and Kirill~S. Korolev, \emph{Fluctuations
-%   uncover a distinct class of travelling waves}, Proc. Natl. Acad. Sci. (USA)
-%   \textbf{115} (2018), no.~16, 3645--3654.
-% 
-% \bibitem{birzu/hallatschek/korolev:2021}
-% Gabriel Birzu, Oskar Hallatschek, and Kirill~S Korolev, \emph{Genealogical
-%   structure changes as range expansions transition from pushed to pulled},
-%   Proc. Natl. Acad. Sci. (USA) \textbf{118} (2021), no.~34, e2026746118.
-% 
-% \bibitem{biswas/etheridge/klimek:2018}
-% Niloy Biswas, Alison Etheridge, and Aleksander Klimek, \emph{The spatial
-%   {Lambda}-{Fleming}-{Viot} process with fluctuating selection}, Electron. J.
-%   Probab. \textbf{26} (2021), 1 -- 51.
-% 
-% \bibitem{bolker/pacala:1997}
-% B~M Bolker and S~W Pacala, \emph{Using moment equations to understand
-%   stochastically driven spatial pattern formation in ecological systems},
-%   Theor. Pop. Biol. \textbf{52} (1997), no.~3, 179--197.
-% 
-% \bibitem{bolker/pacala:1999}
-% \bysame, \emph{Spatial moment equations for plant competition: {Understanding}
-%   spatial strategies and the advantages of short dispersal}, American
-%   Naturalist \textbf{153} (1999), no.~6, 575--602.
-% 
-% \bibitem{bramson:1983}
-% M~Bramson, \emph{{Convergence of solutions of the Kolmogorov equation to
-%   travelling waves}}, Mem. Amer. Math. Soc. \textbf{44} (1983), no.~285.
-% 
-% \bibitem{britton1990spatial}
-% N.~F. Britton, \emph{Spatial structures and periodic travelling waves in an
-%   integro-differential reaction-diffusion population model}, SIAM Journal on
-%   Applied Mathematics \textbf{50} (1990), no.~6, 1663--1688.
-% 
-% \bibitem{brunet/derrida/mueller/munier:2006}
-% E~Brunet, B~Derrida, A~H Mueller, and S~Munier, \emph{Noisy travelling waves:
-%   effect of selection on genealogies}, Europhys. Lett. \textbf{76} (2006),
-%   1--7.
-% 
-% \bibitem{cantrell2004spatial}
-% Robert~Stephen Cantrell and Chris Cosner, \emph{Spatial ecology via
-%   reaction-diffusion equations}, John Wiley \& Sons, 2004.
-% 
-% \bibitem{cohen/golding/kozlovsky/benjacob/ron:1999}
-% I~Cohen, I~Golding, Y~Kozlovsky, E~Ben-Jacob, and I~Ron, \emph{Continuous and
-%   discrete models of cooperation in complex bacterial colonies}, Fractals
-%   \textbf{7} (1999), 235--247.
-% 
-% \bibitem{dawson:1993}
-% D~A Dawson, \emph{{Measure-valued Markov processes}}, \'Ecole d'\'et\'e de
-%   probabilit\'es de Saint Flour, vol. 1541, Springer-Verlag, 1993.
-% 
-% \bibitem{demasi/ferrari/lebowitz:1986}
-% A.~De~Masi, P.~A. Ferrari, and J.~L. Lebowitz, \emph{Reaction-diffusion
-%   equations for interacting particle system}, J. Stat. Phys. \textbf{44}
-%   (1986), 589--644.
-% 
-% \bibitem{demasi/presutti:1991}
-% Anna DeMasi and Errico Presutti, \emph{Mathematical methods for hydrodynamic
-%   limits}, Springer, 2006.
-% 
-% \bibitem{donnelly/kurtz:1996}
-% P~J Donnelly and T~G Kurtz, \emph{{A countable representation of the
-%   Fleming-Viot measure-valued diffusion}}, Ann. Probab. \textbf{24} (1996),
-%   698--742.
-% 
-% \bibitem{donnelly/kurtz:1999}
-% \bysame, \emph{{Particle representations for measure-valued population
-%   models}}, Ann. Probab. \textbf{27} (1999), 166--205.
-% 
-% \bibitem{durrett/fan:2016}
-% R~Durrett and W-T Fan, \emph{Genealogies in expanding populations}, Ann. Appl.
-%   Probab. \textbf{26} (2016), 3456--3490.
-% 
-% \bibitem{etheridge/gooding/letter:2022}
-% A~Etheridge, M~Gooding, and I~Letter, \emph{{On the effects of a wide opening
-%   in the domain of the (stochastic) Allen-Cahn equation and the motion of
-%   hyrbid zones}}, Electron. J. Probab. \textbf{27} (2022), 1--52.
-% 
-% \bibitem{etheridge/penington:2022}
-% A.~Etheridge and S.~Penington, \emph{Genealogies in bistable waves}, Electron.
-%   J. Probab. \textbf{27} (2022), no.~121, 1--99.
-% 
-% \bibitem{etheridge:2004}
-% A~M Etheridge, \emph{Survival and extinction in a locally regulated
-%   population}, Ann. Appl. Probab. \textbf{14} (2004), no.~1, 188--214.
-% 
-% \bibitem{etheridge2000introduction}
-% Alison Etheridge, \emph{An introduction to superprocesses}, no.~20, American
-%   Mathematical Society, 2000.
-% 
-% \bibitem{etheridge/kurtz:2019}
-% Alison~M. Etheridge and Thomas~G. Kurtz, \emph{{Genealogical constructions of
-%   population models}}, Ann. Probab. \textbf{47} (2019), no.~4, 1827--1910.
-% 
-% \bibitem{ethier/kurtz:1986}
-% Stewart~N. Ethier and Thomas~G. Kurtz, \emph{Markov processes --
-%   characterization and convergence}, Wiley Series in Probability and
-%   Mathematical Statistics: Probability and Mathematical Statistics, John Wiley
-%   \& Sons Inc., New York, 1986. \MR{MR838085 (88a:60130)}
-% 
-% \bibitem{fife1977approach}
-% Paul~C. Fife and J.~B. McLeod, \emph{The approach of solutions of nonlinear
-%   diffusion equations to travelling front solutions}, Archive for Rational
-%   Mechanics and Analysis \textbf{65} (1977), no.~4, 335--361.
-% 
-% \bibitem{flandoli/huang:2021}
-% Franco Flandoli and Ruojun Huang, \emph{The {KPP} equation as a scaling limit
-%   of locally interacting {Brownian} particles}, J. Differential Equations
-%   \textbf{303} (2021), 608--644.
-% 
-% \bibitem{flandoli/leimbach/olivera:2019}
-% Franco Flandoli, Matti Leimbach, and Christian Olivera, \emph{Uniform
-%   convergence of proliferating particles to the fkpp equation}, Journal of
-%   Mathematical Analysis and Applications \textbf{473} (2019), no.~1, 27--52.
-% 
-% \bibitem{ghosh2022emergent}
-% Olivia~M. Ghosh and Benjamin~H. Good, \emph{Emergent evolutionary forces in
-%   spatial models of microbial growth in the human gut microbiota}, Proc. Natl.
-%   Acad. Sci. (USA) \textbf{119} (2022), no.~28, e2114931119.
-% 
-% \bibitem{gilding/kersner:2005}
-% B~H Gilding and R~Kersner, \emph{A {Fisher}/{KPP}-type equation with density
-%   dependent diffusion and convection: travelling wave solutions}, J. Phys. A:
-%   Math. Gen. \textbf{38} (2005), 337--3379.
-% 
-% \bibitem{gooding:2018}
-% M.~Gooding, \emph{Long term behaviour of spatial population models with
-%   heterozygous or asymmetric homozygous selection}, DPhil thesis, Oxford
-%   University, 2018.
-% 
-% \bibitem{hallatschek/nelson:2008}
-% O~Hallatschek and D~Nelson, \emph{Gene surfing in expanding populations},
-%   Theor. Pop. Biol. \textbf{73} (2008), 158--170.
-% 
-% \bibitem{haller_slim_2019}
-% Benjamin~C. Haller and Philipp~W. Messer, \emph{{SLiM} 3: {Forward} genetic
-%   simulations beyond the {Wright}-{Fisher} model}, Mol. Biol. Evol. \textbf{36}
-%   (2019), no.~3, 632--637.
-% 
-% \bibitem{haller2022evolutionary}
-% \bysame, \emph{{SLiM}: An evolutionary simulation framework}, 2022.
-% 
-% \bibitem{hernandezgarcia2004clustering}
-% Emilio Hern\'andez-Garc\'{\i}a and Crist\'obal L\'opez, \emph{Clustering,
-%   advection, and patterns in a model of population dynamics with
-%   neighborhood-dependent rates}, Phys. Rev. E \textbf{70} (2004), no.~1,
-%   016216.
-% 
-% \bibitem{hernandez/jacka:2022}
-% Ma.~Elena Hern{\'{a}}ndez-Hern{\'{a}}ndez and Saul~D. Jacka, \emph{A
-%   generalisation of the burkholder-davis-gundy inequalities}, Electronic
-%   Communications in Probability \textbf{27} (2022), no.~none.
-% 
-% \bibitem{holmes/lewis/banks/veit:1994}
-% E.~E. Holmes, M.~A. Lewis, J.~E. Banks, and R.~R. Veit, \emph{Partial
-%   differential equations in ecology: Spatial interactions and population
-%   dynamics}, Ecology \textbf{75} (1994), no.~1, 17--29.
-% 
-% \bibitem{jacod/shiryaev:2013}
-% Jean Jacod and Albert Shiryaev, \emph{Limit theorems for stochastic processes},
-%   vol. 288, Springer Science \& Business Media, 2013.
-% 
-% \bibitem{kallenberg1997foundations}
-% Olav Kallenberg, \emph{Foundations of modern probability}, vol.~2, Springer,
-%   1997.
-% 
-% \bibitem{kamin/rosenau:2004}
-% S~Kamin and P~Rosenau, \emph{Emergence of waves in a nonlinear
-%   convection-reaction-diffusion equation}, Adv. Nonlinear Stud. \textbf{4}
-%   (2004), 251--272.
-% 
-% \bibitem{kelleher2019inferring}
-% Jerome Kelleher, Yan Wong, Anthony~W. Wohns, Chaimaa Fadil, Patrick~K. Albers,
-%   and Gil McVean, \emph{Inferring whole-genome histories in large population
-%   datasets}, Nature Genetics \textbf{51} (2019), no.~9, 1330--1338.
-% 
-% \bibitem{kolmogorov/petrovsky/piscounov:1937}
-% A~Kolomogorov, I~Petrovsky, and N~Piscounov, \emph{{\'Etude de l'equation de la
-%   diffusion avec croissance de la quantit\'e de mati\`ere et son application
-%   \`a un probl\`eme biologique}}, Moscow Univ. Math. Bull. \textbf{1} (1937),
-%   1--25.
-% 
-% \bibitem{kurtz/rodrigues:2011}
-% Thomas~G. Kurtz and Eliane~R. Rodrigues, \emph{Poisson representations of
-%   branching {Markov} and measure-valued branching processes}, Ann. Probab.
-%   \textbf{39} (2011), no.~3, 939--984.
-% 
-% \bibitem{kurtz/xiong:1999}
-% Thomas~G. Kurtz and Jie Xiong, \emph{Particle representations for a class of
-%   nonlinear spdes}, Stoch. Proc. Appl. \textbf{83} (1999), no.~1, 103--126.
-% 
-% \bibitem{lam2023introduction}
-% King-Yeung Lam and Yuan Lou, \emph{Introduction to reaction-diffusion
-%   equations: Theory and applications to spatial ecology and evolutionary
-%   biology}, Springer International Publishing AG, 2023.
-% 
-% \bibitem{li/buenzli/simpson:2022}
-% Y~Li, P~Buenzli, and M~Simpson, \emph{Interpreting how nonlinear diffusion
-%   affects the fate of bistable populations using a discrete modelling
-%   framework}, Proc. Roy. Soc. A \textbf{478} (2022).
-% 
-% \bibitem{lions/mas-gallic:2001}
-% P-L Lions and S~Mas-Gallic, \emph{{Une m\'ethode particulaire d\'eterministe
-%   pour des \'equations diffusives non lin\'eaires}}, C. R. Acad. Sci. Paris
-%   \textbf{332, S\'erie I} (2001), 369--376.
-% 
-% \bibitem{neigel1993application}
-% J~E Neigel and J~C Avise, \emph{Application of a random walk model to
-%   geographic distributions of animal mitochondrial {DNA} variation}, Genetics
-%   \textbf{135} (1993), no.~4, 1209--1220.
-% 
-% \bibitem{oelschlaeger:1985}
-% Karl Oelschl{\"a}ger, \emph{A law of large numbers for moderately interacting
-%   diffusion processes}, Z. Wahrsch. verw. Geb. \textbf{69} (1985), no.~2,
-%   279--322.
-% 
-% \bibitem{oelschlaeger:1989}
-% \bysame, \emph{On the derivation of reaction-diffusion equations as limit
-%   dynamics of systems of moderately interacting stochastic processes}, Prob.
-%   Theor. Rel. Fields \textbf{82} (1989), no.~4, 565--586.
-% 
-% \bibitem{penington:2017}
-% S~Penington, \emph{{The spreading speed of solutions of the non-local
-%   Fisher-KPP equation}}, J. Functional Anal. \textbf{275} (2017), no.~12,
-%   3259--3302.
-% 
-% \bibitem{perkins:1992}
-% E~A Perkins, \emph{{Measure-valued branching diffusions with spatial
-%   interactions}}, Prob. Th. Rel. Fields \textbf{94} (1992), 189--245.
-% 
-% \bibitem{potts/borger:2023}
-% Jonathan~R. Potts and Luca Börger, \emph{How to scale up from animal movement
-%   decisions to spatiotemporal patterns: An approach via step selection},
-%   Journal of Animal Ecology \textbf{92} (2023), no.~1, 16--29.
-% 
-% \bibitem{rebolledo:1980}
-% R~Rebolledo, \emph{{Sur l'existence de solutions \'a certains probl\`emes de
-%   semimartingales}}, C. R. Acad. Sci. Paris \textbf{290} (1980).
-% 
-% \bibitem{sasaki1997clumped}
-% Akira Sasaki, \emph{Clumped distribution by neighbourhood competition}, J.
-%   Theor. Biol. \textbf{186} (1997), no.~4, 415--430.
-% 
-% \bibitem{sherratt:2010}
-% J~A Sherratt, \emph{On the form of smooth-front travelling waves in a
-%   reaction-diffusion equation with degenerate nonlinear diffusion}, Math.
-%   Model. Nat. Phenom. \textbf{5} (2010), no.~5, 64--79.
-% 
-% \bibitem{sheu:1991}
-% S~J Sheu, \emph{{Some estimates of the transition density of a nondegenerate
-%   diffusion Markov process}}, Ann. Probab. \textbf{19} (1991), no.~2, 538--561.
-% 
-% \bibitem{young2001reproductive}
-% W.~R. Young, A.~J. Roberts, and G.~Stuhne, \emph{Reproductive pair correlations
-%   and the clustering of organisms}, Nature \textbf{412} (2001), no.~6844,
-%   328--331.
-% 
-% \end{thebibliography}
-
+\providecommand{\bysame}{\leavevmode\hbox to3em{\hrulefill}\thinspace}
+\providecommand{\MR}{\relax\ifhmode\unskip\space\fi MR }
+% \MRhref is called by the amsart/book/proc definition of \MR.
+\providecommand{\MRhref}[2]{%
+  \href{http://www.ams.org/mathscinet-getitem?mr=#1}{#2}
+}
+\providecommand{\href}[2]{#2}
+\begin{thebibliography}{10}
+
+\bibitem{adler2018interspecific}
+Peter~B. Adler, Andrew Kleinhesselink, Giles Hooker, Joshua~B. Taylor, Brittany
+  Teller, and Stephen~P. Ellner, \emph{Weak interspecific interactions in a
+  sagebrush steppe? {Conflicting} evidence from observations and experiments},
+  Ecology \textbf{99} (2018), no.~7, 1621--1632.
+
+\bibitem{barlow/jacka/yor:1986}
+M.~T. Barlow, S.~D. Jacka, and M.~Yor, \emph{Inequalities for a pair of
+  processes stopped at a random time}, Proceedings of the London Mathematical
+  Society \textbf{s3-52} (1986), no.~1, 142--172.
+
+\bibitem{barton:1979}
+N~H Barton, \emph{The dynamics of hybrid zones}, Heredity \textbf{43} (1979),
+  no.~3, 341--359.
+
+\bibitem{berestycki2009nonlocal}
+Henri Berestycki, Gregoire Nadin, Benoit Perthame, and Lenya Ryzhik, \emph{The
+  non-local {Fisher}-{KPP} equation: travelling waves and steady states},
+  Nonlinearity \textbf{22} (2009), no.~12, 2813--2844.
+
+\bibitem{birzu/hallatschek/korolev:2017}
+Gabriel Birzu, Oskar Hallatschek, and Kirill~S. Korolev, \emph{Fluctuations
+  uncover a distinct class of traveling waves}, Proc. Natl. Acad. Sci. (USA)
+  \textbf{115} (2018), no.~16, 3645--3654.
+
+\bibitem{birzu/hallatschek/korolev:2021}
+Gabriel Birzu, Oskar Hallatschek, and Kirill~S Korolev, \emph{Genealogical
+  structure changes as range expansions transition from pushed to pulled},
+  Proc. Natl. Acad. Sci. (USA) \textbf{118} (2021), no.~34, e2026746118.
+
+\bibitem{birzu2019genetic}
+Gabriel Birzu, Sakib Matin, Oskar Hallatschek, and Kirill~S. Korolev,
+  \emph{Genetic drift in range expansions is very sensitive to density
+  dependence in dispersal and growth}, Ecology Letters \textbf{22} (2019),
+  no.~11, 1817--1827.
+
+\bibitem{biswas/etheridge/klimek:2018}
+Niloy Biswas, Alison Etheridge, and Aleksander Klimek, \emph{The spatial
+  {Lambda}-{Fleming}-{Viot} process with fluctuating selection}, Electron. J.
+  Probab. \textbf{26} (2021), 1 -- 51.
+
+\bibitem{bolker/pacala:1997}
+B~M Bolker and S~W Pacala, \emph{Using moment equations to understand
+  stochastically driven spatial pattern formation in ecological systems},
+  Theor. Pop. Biol. \textbf{52} (1997), no.~3, 179--197.
+
+\bibitem{bolker/pacala:1999}
+\bysame, \emph{Spatial moment equations for plant competition: {Understanding}
+  spatial strategies and the advantages of short dispersal}, American
+  Naturalist \textbf{153} (1999), no.~6, 575--602.
+
+\bibitem{bramson:1983}
+M~Bramson, \emph{Convergence of solutions of the kolmogorov equation to
+  travelling waves}, Mem. Amer. Math. Soc. \textbf{44} (1983), no.~285, iv+190.
+
+\bibitem{britton1990spatial}
+N.~F. Britton, \emph{Spatial structures and periodic travelling waves in an
+  integro-differential reaction-diffusion population model}, SIAM Journal on
+  Applied Mathematics \textbf{50} (1990), no.~6, 1663--1688.
+
+\bibitem{brunet/derrida/mueller/munier:2006}
+E~Brunet, B~Derrida, A~H Mueller, and S~Munier, \emph{Noisy travelling waves:
+  effect of selection on genealogies}, Europhys. Lett. \textbf{76} (2006),
+  1--7.
+
+\bibitem{cantrell2004spatial}
+Robert~Stephen Cantrell and Chris Cosner, \emph{Spatial ecology via
+  reaction-diffusion equations}, John Wiley \& Sons, 2004.
+
+\bibitem{cohen/golding/kozlovsky/benjacob/ron:1999}
+I~Cohen, I~Golding, Y~Kozlovsky, E~Ben-Jacob, and I~Ron, \emph{Continuous and
+  discrete models of cooperation in complex bacterial colonies}, Fractals
+  \textbf{7} (1999), 235--247.
+
+\bibitem{dawson:1993}
+D~A Dawson, \emph{{Measure-valued Markov processes}}, \'Ecole d'\'et\'e de
+  probabilit\'es de Saint Flour, vol. 1541, Springer-Verlag, 1993.
+
+\bibitem{demasi/ferrari/lebowitz:1986}
+A.~De~Masi, P.~A. Ferrari, and J.~L. Lebowitz, \emph{Reaction-diffusion
+  equations for interacting particle system}, J. Stat. Phys. \textbf{44}
+  (1986), 589--644.
+
+\bibitem{demasi/presutti:1991}
+Anna DeMasi and Errico Presutti, \emph{Mathematical methods for hydrodynamic
+  limits}, Springer, 2006.
+
+\bibitem{donnelly/kurtz:1996}
+P~J Donnelly and T~G Kurtz, \emph{{A countable representation of the
+  Fleming-Viot measure-valued diffusion}}, Ann. Probab. \textbf{24} (1996),
+  698--742.
+
+\bibitem{donnelly/kurtz:1999}
+\bysame, \emph{{Particle representations for measure-valued population
+  models}}, Ann. Probab. \textbf{27} (1999), 166--205.
+
+\bibitem{durrett/fan:2016}
+R~Durrett and W-T Fan, \emph{Genealogies in expanding populations}, Ann. Appl.
+  Probab. \textbf{26} (2016), 3456--3490.
+
+\bibitem{etheridge/gooding/letter:2022}
+A~Etheridge, M~Gooding, and I~Letter, \emph{{On the effects of a wide opening
+  in the domain of the (stochastic) Allen-Cahn equation and the motion of
+  hyrbid zones}}, Electron. J. Probab. \textbf{27} (2022), 1--52.
+
+\bibitem{etheridge/penington:2022}
+A.~Etheridge and S.~Penington, \emph{Genealogies in bistable waves}, Electron.
+  J. Probab. \textbf{27} (2022), no.~121, 1--99.
+
+\bibitem{etheridge:2004}
+A~M Etheridge, \emph{Survival and extinction in a locally regulated
+  population}, Ann. Appl. Probab. \textbf{14} (2004), no.~1, 188--214.
+
+\bibitem{etheridge2000introduction}
+Alison Etheridge, \emph{An introduction to superprocesses}, no.~20, American
+  Mathematical Society, 2000.
+
+\bibitem{etheridge/pennington:2022}
+Alison Etheridge and Sarah Penington, \emph{Genealogies in bistable waves},
+  Electronic Journal of Probability \textbf{27} (2022), no.~none, 1 -- 99.
+
+\bibitem{etheridge/kurtz:2019}
+Alison~M. Etheridge and Thomas~G. Kurtz, \emph{{Genealogical constructions of
+  population models}}, Ann. Probab. \textbf{47} (2019), no.~4, 1827--1910.
+
+\bibitem{ethier/kurtz:1986}
+Stewart~N. Ethier and Thomas~G. Kurtz, \emph{Markov processes --
+  characterization and convergence}, Wiley Series in Probability and
+  Mathematical Statistics: Probability and Mathematical Statistics, John Wiley
+  \& Sons Inc., New York, 1986. \MR{MR838085 (88a:60130)}
+
+\bibitem{ewens:1982}
+W~J Ewens, \emph{{The concept of the effective population size}}, Theor. Pop.
+  Biol. \textbf{21} (1982), 373--378.
+
+\bibitem{fife1977approach}
+Paul~C. Fife and J.~B. McLeod, \emph{The approach of solutions of nonlinear
+  diffusion equations to travelling front solutions}, Archive for Rational
+  Mechanics and Analysis \textbf{65} (1977), no.~4, 335--361.
+
+\bibitem{flandoli/huang:2021}
+Franco Flandoli and Ruojun Huang, \emph{The {KPP} equation as a scaling limit
+  of locally interacting {Brownian} particles}, J. Differential Equations
+  \textbf{303} (2021), 608--644.
+
+\bibitem{flandoli/leimbach/olivera:2019}
+Franco Flandoli, Matti Leimbach, and Christian Olivera, \emph{Uniform
+  convergence of proliferating particles to the {FKPP} equation}, Journal of
+  Mathematical Analysis and Applications \textbf{473} (2019), no.~1, 27--52.
+
+\bibitem{fournier2004microscopic}
+Nicolas Fournier and Sylvie M\'el\'eard, \emph{A microscopic probabilistic
+  description of a locally regulated population and macroscopic
+  approximations}, The Annals of Applied Probability \textbf{14} (2004), no.~4,
+  1880--1919.
+
+\bibitem{ghosh2022emergent}
+Olivia~M. Ghosh and Benjamin~H. Good, \emph{Emergent evolutionary forces in
+  spatial models of microbial growth in the human gut microbiota}, Proc. Natl.
+  Acad. Sci. (USA) \textbf{119} (2022), no.~28, e2114931119.
+
+\bibitem{gilding/kersner:2005}
+B~H Gilding and R~Kersner, \emph{A {Fisher}/{KPP}-type equation with density
+  dependent diffusion and convection: travelling wave solutions}, J. Phys. A:
+  Math. Gen. \textbf{38} (2005), 337--3379.
+
+\bibitem{gooding:2018}
+M.~Gooding, \emph{Long term behaviour of spatial population models with
+  heterozygous or asymmetric homozygous selection}, DPhil thesis, Oxford
+  University, 2018.
+
+\bibitem{hallatschek/nelson:2008}
+O~Hallatschek and D~Nelson, \emph{Gene surfing in expanding populations},
+  Theor. Pop. Biol. \textbf{73} (2008), 158--170.
+
+\bibitem{haller_slim_2019}
+Benjamin~C. Haller and Philipp~W. Messer, \emph{{SLiM} 3: {Forward} genetic
+  simulations beyond the {Wright}-{Fisher} model}, Mol. Biol. Evol. \textbf{36}
+  (2019), no.~3, 632--637.
+
+\bibitem{haller2022evolutionary}
+\bysame, \emph{{SLiM}: An evolutionary simulation framework}, 2022.
+
+\bibitem{hernandezgarcia2004clustering}
+Emilio Hern\'andez-Garc\'{\i}a and Crist\'obal L\'opez, \emph{Clustering,
+  advection, and patterns in a model of population dynamics with
+  neighborhood-dependent rates}, Phys. Rev. E \textbf{70} (2004), no.~1,
+  016216.
+
+\bibitem{hernandez/jacka:2022}
+Ma.~Elena Hern{\'{a}}ndez-Hern{\'{a}}ndez and Saul~D. Jacka, \emph{A
+  generalisation of the {Burkholder}-{Davis}-{Gundy} inequalities}, Electronic
+  Communications in Probability \textbf{27} (2022), no.~none, 1--8.
+
+\bibitem{holmes/lewis/banks/veit:1994}
+E.~E. Holmes, M.~A. Lewis, J.~E. Banks, and R.~R. Veit, \emph{Partial
+  differential equations in ecology: Spatial interactions and population
+  dynamics}, Ecology \textbf{75} (1994), no.~1, 17--29.
+
+\bibitem{jacod/shiryaev:2013}
+Jean Jacod and Albert Shiryaev, \emph{Limit theorems for stochastic processes},
+  vol. 288, Springer Science \& Business Media, 2013.
+
+\bibitem{kallenberg1997foundations}
+Olav Kallenberg, \emph{Foundations of modern probability}, vol.~2, Springer,
+  1997.
+
+\bibitem{kamin/rosenau:2004}
+S~Kamin and P~Rosenau, \emph{Emergence of waves in a nonlinear
+  convection-reaction-diffusion equation}, Adv. Nonlinear Stud. \textbf{4}
+  (2004), 251--272.
+
+\bibitem{kelleher2019inferring}
+Jerome Kelleher, Yan Wong, Anthony~W. Wohns, Chaimaa Fadil, Patrick~K. Albers,
+  and Gil McVean, \emph{Inferring whole-genome histories in large population
+  datasets}, Nature Genetics \textbf{51} (2019), no.~9, 1330--1338.
+
+\bibitem{kolmogorov/petrovsky/piscounov:1937}
+A~Kolomogorov, I~Petrovsky, and N~Piscounov, \emph{{\'Etude de l'equation de la
+  diffusion avec croissance de la quantit\'e de mati\`ere et son application
+  \`a un probl\`eme biologique}}, Moscow Univ. Math. Bull. \textbf{1} (1937),
+  1--25.
+
+\bibitem{kurtz/rodrigues:2011}
+Thomas~G. Kurtz and Eliane~R. Rodrigues, \emph{Poisson representations of
+  branching {Markov} and measure-valued branching processes}, Ann. Probab.
+  \textbf{39} (2011), no.~3, 939--984.
+
+\bibitem{kurtz/xiong:1999}
+Thomas~G. Kurtz and Jie Xiong, \emph{Particle representations for a class of
+  nonlinear {SPDEs}}, Stoch. Proc. Appl. \textbf{83} (1999), no.~1, 103--126.
+
+\bibitem{lam2023introduction}
+King-Yeung Lam and Yuan Lou, \emph{Introduction to reaction-diffusion
+  equations: Theory and applications to spatial ecology and evolutionary
+  biology}, Springer International Publishing AG, 2023.
+
+\bibitem{law/murrell/dieckmann:2003}
+R~Law, D~J Murrell, and U~Dieckmann, \emph{{Population growth in space and
+  time: spatial logistic equations}}, Ecology \textbf{84} (2003), no.~2,
+  252--262.
+
+\bibitem{li/buenzli/simpson:2022}
+Y~Li, P~Buenzli, and M~Simpson, \emph{Interpreting how nonlinear diffusion
+  affects the fate of bistable populations using a discrete modelling
+  framework}, Proc. Roy. Soc. A \textbf{478} (2022), no.~2262, 20220013.
+
+\bibitem{lions/mas-gallic:2001}
+P-L Lions and S~Mas-Gallic, \emph{{Une m\'ethode particulaire d\'eterministe
+  pour des \'equations diffusives non lin\'eaires}}, C. R. Acad. Sci. Paris
+  \textbf{332, S\'erie I} (2001), 369--376.
+
+\bibitem{neigel1993application}
+J~E Neigel and J~C Avise, \emph{Application of a random walk model to
+  geographic distributions of animal mitochondrial {DNA} variation}, Genetics
+  \textbf{135} (1993), no.~4, 1209--1220.
+
+\bibitem{oelschlaeger:1985}
+Karl Oelschl{\"a}ger, \emph{A law of large numbers for moderately interacting
+  diffusion processes}, Z. Wahrsch. verw. Geb. \textbf{69} (1985), no.~2,
+  279--322.
+
+\bibitem{oelschlaeger:1989}
+\bysame, \emph{On the derivation of reaction-diffusion equations as limit
+  dynamics of systems of moderately interacting stochastic processes}, Prob.
+  Theor. Rel. Fields \textbf{82} (1989), no.~4, 565--586.
+
+\bibitem{penington:2017}
+S~Penington, \emph{{The spreading speed of solutions of the non-local
+  Fisher-KPP equation}}, J. Functional Anal. \textbf{275} (2017), no.~12,
+  3259--3302.
+
+\bibitem{perkins:1992}
+E~A Perkins, \emph{{Measure-valued branching diffusions with spatial
+  interactions}}, Prob. Th. Rel. Fields \textbf{94} (1992), 189--245.
+
+\bibitem{potts/borger:2023}
+Jonathan~R. Potts and Luca Börger, \emph{How to scale up from animal movement
+  decisions to spatiotemporal patterns: An approach via step selection},
+  Journal of Animal Ecology \textbf{92} (2023), no.~1, 16--29.
+
+\bibitem{rebolledo:1980}
+R~Rebolledo, \emph{{Sur l'existence de solutions \'a certains probl\`emes de
+  semimartingales}}, C. R. Acad. Sci. Paris \textbf{290} (1980), 843--846.
+
+\bibitem{roques2012allee}
+Lionel Roques, Jimmy Garnier, François Hamel, and Etienne~K. Klein,
+  \emph{Allee effect promotes diversity in traveling waves of colonization},
+  Proceedings of the National Academy of Sciences \textbf{109} (2012), no.~23,
+  8828--8833.
+
+\bibitem{sasaki1997clumped}
+Akira Sasaki, \emph{Clumped distribution by neighbourhood competition}, J.
+  Theor. Biol. \textbf{186} (1997), no.~4, 415--430.
+
+\bibitem{sherratt:2010}
+J~A Sherratt, \emph{On the form of smooth-front travelling waves in a
+  reaction-diffusion equation with degenerate nonlinear diffusion}, Math.
+  Model. Nat. Phenom. \textbf{5} (2010), no.~5, 64--79.
+
+\bibitem{sheu:1991}
+S~J Sheu, \emph{{Some estimates of the transition density of a nondegenerate
+  diffusion Markov process}}, Ann. Probab. \textbf{19} (1991), no.~2, 538--561.
+
+\bibitem{young2001reproductive}
+W.~R. Young, A.~J. Roberts, and G.~Stuhne, \emph{Reproductive pair correlations
+  and the clustering of organisms}, Nature \textbf{412} (2001), no.~6844,
+  328--331.
+
+\bibitem{zhu2023density}
+Jinlei Zhu, Nataša Lukić, Jörn Pagel, and Frank~M. Schurr, \emph{Density
+  dependence of seed dispersal and fecundity profoundly alters the spread
+  dynamics of plant populations}, Journal of Ecology \textbf{111} (2023),
+  no.~8, 1735--1748.
+
+\end{thebibliography}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2024-01-05 forwards-and-backwards.tex
no more overfull hboxes

@@
 	\label{square of F-integral}
-    &\IE\Big[
+    \IE\Big[
 	\Big(\int_s^t\big\langle\rho_\epsilon*|f|(x) \big|F\big(\rho_\epsilon*\eta_u^N(x)\big)\big|,
@@
 \\
-    &\hspace{4em}=
+    =
 2\IE\Big[
@@
 \eta_u^N(dx)\big\rangle 
-    \\&\hspace{8em}
-	\int_u^t\big\langle \rho_\epsilon*|f|(x)\big|F\big(\rho_\epsilon*\eta_r^N(x)\big)\big|,
+    \\\hspace{8em}
+	\times \int_u^t\big\langle \rho_\epsilon*|f|(x)\big|F\big(\rho_\epsilon*\eta_r^N(x)\big)\big|,
 \eta_r^N(dx)\big\rangle dr
@@
 each fixed $\delta>0$,  
-$\lim_{\epsilon\to 0, \theta\to\infty}
-\widehat{\epsilon}(\delta,\epsilon,\theta)=0$. 
+% $\lim_{\epsilon\to 0, \theta\to\infty} \widehat{\epsilon}(\delta,\epsilon,\theta)=0$. 
+$\widehat{\epsilon}(\delta,\epsilon,\theta) \to 0$
+as $\epsilon\to 0$ and $\theta\to\infty$.
 Using the semimartingale decomposition~(\ref{expn rhoepsilon}),
@@
 p_{6(s-r+\epsilon^2)}(w,z)| +\widehat{\epsilon}(\delta,\epsilon,\theta)\Big\}
+\nonumber \\ &\qquad \qquad {} \hspace{24em} \times
 |F(\rho_\epsilon*\eta_r(z)|, 
@@
 +\widehat{\epsilon}(\delta,\epsilon,\theta)\Big\}
+\nonumber \\ &\qquad \qquad {} \hspace{24em} \times
 |F(\rho_\epsilon*\eta_r(z)|, 
@@
 We now turn to the identification of the limit points of the sequence 
-$\big\{\big(\rho_\epsilon*\eta_t^N(x)dx\big)_{t\geq 0}\big\}_{N\geq 1}$.
+of measure-valued processes
+$\big(\rho_\epsilon*\eta_t^N(x)dx\big)_{t\geq 0}$.
 We would like to show that any limit point solves~\eqref{target equation in local convergence}
@@
 & \int 
-\Big\{ |F(\rho_\epsilon*\eta_s(y))-F(\rho_\epsilon*\eta_s(w))|T_{\epsilon^2}f(y)+
-F(\rho_\epsilon*\eta_s(w))|T_{\epsilon^2}f(y)-T_{\epsilon^2}f(w))|\Big\} 
+\Big\{ |F(\rho_\epsilon*\eta_s(y))-F(\rho_\epsilon*\eta_s(w))|T_{\epsilon^2}f(y)
+    \nonumber \\ & \hspace{12em} {} +
+F(\rho_\epsilon*\eta_s(w))|T_{\epsilon^2}f(y)-T_{\epsilon^2}f(w)|\Big\} 
 \rho_{\epsilon}(w-y)dy
@@
 \int_\delta^t\frac{\epsilon}{\sqrt{s+\epsilon^2}}
-\IE\Big[\int\int\big\langle
+\IE\Big[\int\!\!\int\big\langle
 p_{2(s+\epsilon^2)}(y,z)  
@@
 \big(\rho_\epsilon*\eta_s(y)^{k+1} +\rho_\epsilon*\eta_s(x)^{k+1}\big)
-p_{\epsilon^2}(x,y) dy dx \Big] ds,
+p_{\epsilon^2}(x,y) dy dx \Big] ds
 \end{multline*}
@@
 For fixed $\delta$, this bound tends to zero as $\epsilon\to 0$.
-The term involving 
-$ 
-\big\langle
-p_{2(s+\epsilon^2)}(w,z)   
-,\eta_0(dz)
-\big\rangle
-\rho_\epsilon*\eta_s(w)^k
-$ 
+The term involving  the product of
+$\big\langle p_{2(s+\epsilon^2)}(w,z),\eta_0(dz)\big\rangle$
+and $\rho_\epsilon*\eta_s(w)^k$ 
 is handled similarly.
@@
 gives that 
-\begin{equation}
+\begin{align*}
+&
 \int_0^t\int \int f(z) (\rho_\epsilon * \eta_s)(z) 
 \rho_\tau (z-y) (\rho_\epsilon * \eta_s)(y) dz dy ds
+\\ & \qquad
 \to \int_0^t \int \int f(z) \varphi(s,z) 
 \rho_\tau (z-y) \varphi(s,y) dz dy ds.
-\end{equation}
+\end{align*}
 Since $\tau$ is arbitrary, the 
@@
     For finite $N$,
-    taking $f(\lp)$ of the form \eqref{eqn:test_functions},
+    if we take $f(\lp)$ to be of the form \eqref{eqn:test_functions},
     we can use $\psi^N(\lp) = \langle C (1 + u |F(x, \eta)|), \lp(dx, du) \rangle$
@@
 \begin{split}
-    \langle f, \lp_t^N \rangle
-    &=
+    &\langle f, \lp_t^N \rangle
+    =
     \langle f, \lp_0^N \rangle
     + M^f_t
-\\ & \qquad {}
+\\ & {}
     +
@@
     As before,
-    \begin{align*}
+    \begin{multline*}
         \frac{
@@
         }
+        \\
         =
         h(x-w, x-v) e^{ k(x-w, x-v) },
-    \end{align*}
+    \end{multline*}
     where $h(z_1, z_2)$ is a polynomial with uniformly bounded coefficients and
@@
     satisfying the conditions of Theorem~\ref{thm:aldous_rebolledo}.
+
     Then $\{X^{(n)}Y^{(n)}\}_{n \ge 1}$ and $\{X^{(n)} + Y^{(n)}\}_{n \ge 1}$ also
@@
         \right|
+        \\ &\qquad \qquad \qquad {}
         +
